### 2019-01-09 icml/icml2019_style/example_paper.tex
added icml draft files

%%%%%%%% ICML 2019 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2019} with \usepackage[nohyperref]{icml2019} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
%\usepackage{icml2019}

% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{icml2019}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2019}

\begin{document}

\twocolumn[
\icmltitle{Submission and Formatting Instructions for \\
           International Conference on Machine Learning (ICML 2019)}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2019
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

\section{Electronic Submission}
\label{submission}

Submission to ICML 2019 will be entirely electronic, via a web site
(not email). Information about the submission process and \LaTeX\ templates
are available on the conference web site at:
\begin{center}
\textbf{\texttt{http://icml.cc/}}
\end{center}

The guidelines below will be enforced for initial submissions and
camera-ready copies. Here is a brief summary:
\begin{itemize}
\item Submissions must be in PDF\@.
\item The maximum paper length is \textbf{8 pages excluding references and
    acknowledgements, and 12 pages including references and acknowledgements}
    (pages 9 through 12 must contain only references and acknowledgements).
\item \textbf{Do not include author information or acknowledgements} in your
    initial submission.
\item Your paper should be in \textbf{10 point Times font}.
\item Make sure your PDF file only uses Type-1 fonts.
\item Place figure captions \emph{under} the figure (and omit titles from inside
    the graphic file itself). Place table captions \emph{over} the table.
\item References must include page numbers whenever possible and be as complete
    as possible. Place multiple citations in chronological order.
\item Do not alter the style template; in particular, do not compress the paper
    format by reducing the vertical spaces.
\item Keep your abstract brief and self-contained, one paragraph and roughly
    4--6 sentences. Gross violations will require correction at the
    camera-ready phase. The title should have content words capitalized.
\end{itemize}

\subsection{Submitting Papers}

\textbf{Paper Deadline:} The deadline for paper submission that is
advertised on the conference website is strict. If your full,
anonymized, submission does not reach us on time, it will not be
considered for publication. There is no separate abstract submission.

\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
author information may appear on the title page or in the paper
itself. Section~\ref{author info} gives further details.

\textbf{Simultaneous Submission:} ICML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. ICML submissions must not be
submitted to other conferences during ICML's review period. Authors
may submit to ICML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

Authors must provide their manuscripts in \textbf{PDF} format.
Furthermore, please make sure that files contain only embedded Type-1 fonts
(e.g.,~using the program \texttt{pdffonts} in linux or using
File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
might come from graphics files imported into the document.

Authors using \textbf{Word} must convert their document to PDF\@. Most
of the latest versions of Word have the facility to do this
automatically. Submissions will not be accepted in Word format or any
format other than PDF\@. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
Those using \texttt{latex} and \texttt{dvips} may need the following
two commands:

{\footnotesize
\begin{verbatim}
dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
ps2pdf paper.ps
\end{verbatim}}
It is a zero following the ``-G'', which tells dvips to use
the config.pdf file. Newer \TeX\ distributions don't always need this
option.

Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
results. This program avoids the Type-3 font problem, and supports more
advanced features in the \texttt{microtype} package.

\textbf{Graphics files} should be a reasonable size, and included from
an appropriate format. Use vector formats (.eps/.pdf) for plots,
lossless bitmap formats (.png) for raster graphics with sharp lines, and
jpeg for photo-like images.

The style file uses the \texttt{hyperref} package to make clickable
links in documents. If this causes problems for you, add
\texttt{nohyperref} as one of the options to the \texttt{icml2019}
usepackage statement.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
Section~\ref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{36}^{th}$ International Conference on Machine Learning},
Long Beach, USA, 2019.
Copyright 2019 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{icml2019\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{icml2019\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the ICML
2019 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Length and Dimensions}

Papers must not exceed eight (8) pages, including all figures, tables,
and appendices, but excluding references and acknowledgements. When references and acknowledgements are included,
the paper must not exceed ten (10) pages.
Acknowledgements should be limited to grants and people who contributed to the paper.
Any submission that exceeds
this page limit, or that diverges significantly from the specified format,
will be rejected without review.

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

ICML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{icml2019.sty} file, use
\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via CMT\@. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the ICML2019 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
produced, the number of accepted papers for ICML 2008 was unknown and instead
estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
Figure~\ref{icml-historical}. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
Table~\ref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2019.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\subsection{Software and Data}

We strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, do not
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system. Note that reviewers are not required to look at this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas,
and to funding agencies and corporate sponsors that provided financial
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\textbf{\emph{Do not put content after the references.}}
%
Put anything that you might normally include after the references in a separate
supplementary file.

We recommend that you build supplementary material in a separate document.
If you must create one PDF and cut it up, please be careful to use a tool that
doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
pdftk usually works fine.

\textbf{Please do not use Apple's preview to cut off supplementary material.} In
previous years it has altered margins, and created headaches at the camera-ready
stage. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2019-01-09 icml/icml_local_density_clustering.tex
added icml draft files

%%%%%%%% ICML 2019 submission %%%%%%%%%%%%%%%%%

\documentclass{article}

\usepackage{icml2019}
% \usepackage[accepted]{icml2019}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}

\newcommand{\diam}{\mathrm{diam}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\text{vol}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\Asig}{A_{\sigma}}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\theHalgorithm}{\arabic{algorithm}}

\icmltitlerunning{Local clustering of density upper level sets}

\begin{document}

\twocolumn[
\icmltitle{Local Spectral Clustering of Density Upper Level Sets}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Alden Green}{cmu}
\icmlauthor{Sivaraman Balakrishnan}{cmu}
\icmlauthor{Ryan Tibshirani}{cmu}
\end{icmlauthorlist}

\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}

\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}

\icmlkeywords{local clustering}

\vskip 0.3in
]

\printAffiliationsAndNotice{} % otherwise use the standard text.

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{introduction}

Clustering is a fundamental task in machine learning, which often involves splitting data into groups which satisfy some notion of within-group similarity and between-group difference. In particular, spectral clustering methods are a family of powerful non-parametric clustering algorithms.

Roughly speaking, spectral clustering techniques
embed data points using the spectrum of (some
form of) the graph Laplacian matrix and subsequently 
use this \emph{spectral embedding} to find a clustering of the data.
When applied to large graphs (or large point clouds) classical global spectral 
methods can be computationally cumbersome and 
can be insensitive to the local geometry of the distribution of the samples
\citep{mahoney2012,leskovec2010}.
This in turn has led to the investigation of local spectral algorithms \citep{spielman2013,anderson2006,leskovec2010}
which leverage locally-biased spectra computed using random walks around 
a user-specified seed node.

A natural model to consider when analyzing point cloud data is based on the hypothesis that we receive samples $\set{x_1, \ldots, x_n}$ independently drawn from a distribution $f$. In this case, we are interested in understanding what the output of a clustering algorithm on this finite sample reveals about the unknown distribution $f$. In particular, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters in this context as \emph{connected regions of high-density}, and study the ability of spectral methods to identify these clusters.

Given a matrix $A$ with entries representing the similarity between pairs of data points, and $G  = (V,E)$ a graph representation of $A$ with vertices $V$ and edges $E$, there are many \cite{yang2015,fortunato2010} graph-theoretic measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)

Arguably a natural way to assess cluster quality is via the bicriteria of \textit{external} and \textit{internal connectivity} of $S$, represented by the parameters $\Phi$ and $\Psi$, respectively. As the names suggest, external connectivity should relate to the number of edges between $S$ and $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$ \footnote{We formally define our notions of external and internal connectivity in Section \ref{sec: measures_of_cluster_quality}} . The clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity. We will refer to such a subset as a $(\Phi,\Psi)$-cluster (or partition). Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms can be understood as outputting clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition). \footnote{For slightly different definitions of the internal connectivity $\Psi$}

In the case where $G$ encodes similarities between sampled point-cloud data, some understanding of how graph theoretic quantities such as $\Phi$ and $\Psi$ relate to properties of the underlying distribution $f$ has developed. Continuous analogues to many such graph measures of cluster quality have been defined, and, under appropriate graph construction, convergence of clusters output by spectral algorithm to approximate minimizers of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.

Relating these partitions to the arguably more simply defined high density clusters can be challenging in general. Intuitively, however, under the right conditions such a connection should exist. Given sufficient samples, and an appropriately specified notion of similarity, we can imagine that all points within a high density cluster will have many edges to other points within the cluster, and comparatively few edges to data points outside the cluster. Motivated by this intuition, one primary line of work in this article is to formally establish that, under a natural set of geometric conditions, a connection between certain graph-based criteria and density clusters does exist.

We also study the consequences of these facts as they relate to local spectral clustering algorithms. We restrict our attention in particular to one such popular algorithm: \textit{personalized PageRank} (PPR). We show that a variant of PPR, properly initialized inside a high-density cluster, performs well: not only does the output set of PPR approximate the cluster quality measures of the high-density cluster, the PPR algorithm also consistently recovers the population density cluster.

\subsection{Related Work}

\subsection{Summary of Results}

\begin{enumerate}
	\item 
	Theorem: Well-conditioned density clusters have low conductance.

	\item
	Theorem: Well-conditioned density clusters have high internal connectivity.

	\item 
	Corollary: PPR local clustering algorithm, run on a well-conditioned density cluster and appropriately initialized, will output a low conductance set, which also has low symmetric set difference with the density cluster.

	\item
	Theorem: PPR local clustering algorithm,run on a well-conditioned density cluster and appropriately initialized, exhibits successful density cluster recovery.
\end{enumerate}

\paragraph{Graph notation.}

Let $G = (V,E)$ be an undirected, unweighted graph, with $S,S' \subseteq V$.
The volume of $S$ is given by $\vol(S; G) = \sum_{v \in S} \deg(v; G) $
where $\deg(v; G) = \sum_{u \in V} 1\bigl((u,v) \in E\bigr)$ is the degree of $v$ in $G$. For the random walk over $G$, denote the stationary distribution by $\pi$, where $\pi(S; G) = \frac{\vol(S ; G)}{\vol(V; G)}$.

\vspace{.05 in}

For the sample $\mathbf{X} := \set{x_1, \ldots, x_n} \subset \Rd$ and a set $A \subset \Rd$, define $A[\mathbf{X}] = A \cap \mathbf{X}$. We denote the uniform measure over $\Rd$ by $\nu(\cdot)$.

\section{Measures of cluster quality}
\label{sec: measures_of_cluster_quality}

Let $P$ be a distribution supported on a compact set $\mathcal{X} \subset \Rd$, with continuous density function $f$ (with respect to the uniform measure). The Euclidean distance is denoted by $\norm{ \cdot }$.

\paragraph{Density upper-level set.}
For a number $\tau \geq 0$, let $C_f(\tau)$ be the collection of collected components of the density upper-level set $\set{x \in \mathcal{X}: f(x) \geq \tau}$. Define a \textit{$\tau$-density cluster} to be one such connected component $A \in C_f(\tau)$.  We will sometimes refer to $A[\bf{X}]$ as an \textit{empirical density cluster}.

\paragraph{Graph bicriteria.}
For $G = (V,E)$ an undirected, unweighted graph and $S, S' \subset V$ as before, let $\abs{E(S, S'; G)}$ denote the cut of $S$ and $S'$, given by
\begin{equation*}
\abs{E(S, S'; G)} = \sum_{v \in S} \sum_{u \in S'} 1((v,u) \in E).
\end{equation*}
Define the balance $B(S; G)$ to be
\begin{equation*}
B(S; G) = \min\{\vol(S;G), \vol(V \setminus S;G)\}.
\end{equation*}

We can now formally introduce our first criterion for assessing the quality of graph cuts: the \textbf{conductance}, $\Phi$, given by
\begin{equation}
\label{eqn: conductance}
\Phi(S; G) \defeq \frac{\abs{E(S, V \setminus S; G)}}{B(S; G)}.
\end{equation}
We typically seek a set $S^{\star} \subset V$ such that $\Phi(S^{\star}; G)$ is small.

\textcolor{red}{Introduce and define the \textbf{internal connectivity}.}

\paragraph{Neighborhood graph.}

Given $r \geq 0$, define the neighborhood graph to be $G_{n,r} = (\mathbf{X}, E_n)$, where for $x_i, x_j \in \mathbf{X}$, $(x_i, x_j) \in E_n$ if $\norm{x_i - x_j} \leq r$. (By convention, we do not allow loops, meaning $(x_i, x_i) \not\in E_n$). For ease of notation, for $S \subset \mathbf{X}$, let $\Phi_{n,r}(S) := \Phi(S; G_{n,r})$.

\subsection{Well-conditioned density clusters.}

In order to satisfy the \textcolor{red}{bicriteria}, we must introduce some assumptions on the density $f$. Let $B(x,r)$ be a closed ball with respect to Euclidean distance) of radius $r$ around the point $x$.  Given a set $A \subset \Rd$, and a number $\sigma > 0$, define the set $\Asig = A + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in A} \norm{y - x} \leq \sigma}$. 
\begin{enumerate}[label=(A\arabic*)]
	\item 
	\label{asmp: cluster_regularity}
	\textit{Minimum density:} For numbers $\sigma, \tau_{\sigma} > 0$, a set $A \subset \mathcal{X}$ is said to be \textit{$(\sigma, \tau_{\sigma})$-regular} if
	\begin{equation}
	\inf_{x \in \Asig} f(x) = \tau_{\sigma}
	\end{equation} 
	%and 
	%\begin{equation*}
	%\frac{\diam \Asig}{\sigma} \leq \mu
	%\end{equation*}
	%where $\diam \Asig = \sup \set{d(x,y) : x,y \in \Asig}$

	\item 
	\label{asmp: low_noise_density}
	\textit{Low noise density:} For numbers $\gamma, \sigma > 0$, and a set $A \subset \mathcal{X}$, the density function $f$ is said to be \textit{$(\gamma, \sigma)$- low noise around $A$} if there exists a constant $C_1$ such that for all $x \in \mathcal{X}$ with $0 < \rho(x, \Asig) \leq \sigma$,
	\begin{equation*}
	\inf_{x' \in \Asig} f(x') - f(x) \geq C_1 \rho(x, \Asig)^{\gamma}.
	\end{equation*}
	where $\rho(x,\Asig) = \min_{x_0 \in \Asig} \norm{x - x_0}$.

	\item
	\label{asmp: cluster_separation}
	\textit{Cluster separation:}
	For $\tau,\sigma > 0$, $C_f(\tau)$ the set of connected components of the density upper-level set is said to be \textit{$\sigma$-well separated} if for all $\tau$-density clusters $A, A' \in C_f(\tau)$,
	\begin{equation*}
	\rho(A,A') > \sigma.
	\end{equation*}
	where $\rho(A,A') = \min_{x \in A, x' \in A'} \norm{x - x'}$.
\end{enumerate}

\textcolor{red}{Assumptions are standard, provide references.} We note that these assumptions are all local in nature, further motivating the study of a local algorithm. Assumptions \ref{asmp: cluster_regularity}-\ref{asmp: cluster_separation} are used to upper bound \textcolor{red}{bicriteria 1}, whereas \ref{asmp: cluster_regularity} and \textcolor{red}{(A4)} are necessary to lower bound \textcolor{red}{bicriteria 2}.

\begin{definition}
	For $\tau > 0$ and $A \in C_f(\tau)$ a $\tau$-density cluster, we say that $A$ is a \textit{$(\lambda, \sigma, \gamma)$-well-conditioned cluster} if $A$ is $(\lambda,\sigma)$-regular, the density $f$ is $(\gamma, \sigma)$-low noise around $A^{\sigma}$, and $C_f(\tau)$ is $\sigma$-well separated.
\end{definition}
We note that $\sigma$ plays dual roles here, both in effect precluding arbitrarily narrow and long clusters in \ref{asmp: cluster_regularity} and arbitrarily flat densities in \ref{asmp: low_noise_density}. \textcolor{red}{We give some examples of densities which satisfy these assumptions in Section \ref{section: everything_else}.}

\section{Local Clustering on Density Level Sets}

In this section we show that a well-conditioned cluster $A$ satisfies the bicriteria \textcolor{red}{criteria 1} and \textcolor{red}{criteria 2}, and therefore the \textcolor{red}{PPR algorithm} outputs a low conductance set  which has small symmetric set difference with the empirical cluster.

\begin{theorem}
	\label{thm: conductance_upper_bound}
	For some $\tau > 0$, let a $\tau$-density cluster $A \in C_f(\tau)$ satisfy Assumptions \ref{asmp: cluster_regularity}-\ref{asmp: cluster_separation} for some $\sigma, \tau_{\sigma}, \gamma > 0$. Then, for any $r < \sigma$ and $\delta > 0$, the following statements hold with probability at least $1 - \delta$: 
	\begin{itemize}
		\item 
		\textbf{Additive error bound.} Fix $\epsilon > 0$. Then, for
		\begin{equation}
		\label{eqn: conductance_sample_complexity}
		n \geq \log(2/\delta)\left(\frac{1 + \epsilon/2}{2 \tau_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
		\end{equation}
		we have
		\begin{equation}
		\label{eqn: conductance_additive_error_bound}
		\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \leq C_{\sigma} \frac{\tau}{\tau_{\sigma}} \frac{(\tau_{\sigma} - \frac{r^{\gamma+1}}{\gamma+1})}{\tau_{\sigma}} + \epsilon
		\end{equation}
		\item
		\textcolor{red}{\textbf{Multiplicative error bound.}}
	\end{itemize}
	where $C_0 = 2^{2d+1}d$ and $C_{\sigma} = C_0 / \sigma$. 
\end{theorem}

A few remarks are in order. 
\begin{remark}
	\label{rem: exp_in_d}
	Note that the bound of (\ref{eqn: conductance_additive_error_bound}) depends exponentially on $d$; precisely, on $C_0 = d2^{2d +1}$. It is possible to improve this dependency to the order of $(1 + \frac{r}{\sigma})^{2d}$. However, in this setting, we think of $r$ as being a constant radius (rather than $r = r_n \to 0$ as $n \to \infty$, and therefore even this improvement results in exponential dependency on the dimension $d$. \textcolor{red}{Make references suggesting this type of exponential dependency is not uncommon in non-parametric clustering problems.}
\end{remark}
\begin{remark}
	Other than the looseness implied by Remark \ref{rem: exp_in_d}, the error bound of (\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
	\begin{align*}
	\Asig & = B(0,\sigma), \\
	 f(x) & = 
	 \begin{cases}
	 \tau \text{ for $x \in \Asig$}, \\
	  f(x) = \tau - \rho(x,\Asig)^{\gamma} \text{ for $0 < \rho(x,\Asig) < r$}
	 \end{cases}
	\end{align*}
	we have
	\begin{equation}
	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq C_1 \frac{(\tau - \frac{r^{\epsilon+1}}{\epsilon+1})}{\tau}
	\end{equation}
	for some constant $C_1$, with probability at least $1 - \delta$. (Note that a factor of $1 / \sigma$ is not (\ref{eqn: conductance_additive_error_bound}) replicated in this lower bound.) \textcolor{red}{Provide justification in supplement, and cite it.}
\end{remark}

\section{Implications, extensions, and discussion}
\label{section: everything_else}
\subsection{Examples}
\subsection{Experiments}

\clearpage

\bibliography{icml_bib}
\bibliographystyle{icml2019}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2019-01-09 icml/icml_local_density_clustering_supplement.tex
added icml draft files

%%%%%%%% ICML 2019 submission %%%%%%%%%%%%%%%%%

\documentclass{article}

\usepackage{icml2019}
% \usepackage[accepted]{icml2019}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{xr-hyper}
%\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

\externaldocument{icml_local_density_clustering}

\newcommand{\diam}{\mathrm{diam}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\Asig}{A_{\sigma}}
\newcommand{\Asigr}{A_{\sigma,\sigma + r}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\Err}{\mathrm{Err}}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\newcommand{\theHalgorithm}{\arabic{algorithm}}

\icmltitlerunning{Local clustering of density upper level sets}

\begin{document}

\twocolumn[
\icmltitle{Supplement to ``Local clustering of density upper level sets''}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Alden Green}{cmu}
\icmlauthor{Sivaraman Balakrishnan}{cmu}
\icmlauthor{Ryan Tibshirani}{cmu}
\end{icmlauthorlist}

\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}

\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}

\icmlkeywords{local clustering}

\vskip 0.3in
]

\printAffiliationsAndNotice{} % otherwise use the standard text.

In this supplement, we present proofs for ``Local Clustering of Density Upper Level Sets''. We begin by providing technical lemmas, before moving on to proving the main results of the paper.

\section{Technical Lemmas}
For $A \subset \mathcal{X}$, let $P(A) = \mathbb{P}_{X \sim P}(X \in A)$. To simplify expressions, we will write $A_{\sigma, \sigma + r} := \set{x: 0 < \rho(x, \Asig) \leq r}$. We further let $\widetilde{\mathcal{E}} = \abs{E(\Asig[\mathbf{X}], \mathbf{X} \setminus \Asig[\mathbf{X}]; G_{n,r})}$ be the number of edges between $\Asig[\mathbf{X}]$ and $\mathbf{X} \setminus \Asig[\mathbf{X}]$ in the graph $G_{n,r}$; $\widetilde{\mu} = \mathbb{E}\left[\widetilde{\mathcal{E}}\right]$ be the expected number of such edges; and $\widetilde{p} = \widetilde{\mu} / {n \choose 2}$ the probability of any two vertices $x_i$ and $x_j$ having such an edge. Similarly, $\mathcal{V} = \vol(\Asig[\mathbf{X}]; G_{n,r})$ is the volume of $\Asig[\mathbf{X}]$; $\mu = \mathbb{E}\left[\mathcal{V}\right]$ is the expected volume; and $p = \mu / {n \choose 2}$. Finally, we denote $rB = B(0,r)$.

\subsection{\textcolor{red}{Expected Values}}
\begin{lemma}
	\label{lem: expected_number_boundary_points}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
	\begin{equation*}
	P(A_{\sigma, \sigma + r}) \leq 2^{d-1} \nu(\Asig) \frac{rd}{\sigma}  \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
	\end{equation*}	
\end{lemma}
\begin{proof}
	Recalling that $f$ is the density function for $P$, we have
	\begin{equation}
	\label{eqn: integral_over_epsilon_neighborhood}
	P(A_{\sigma, \sigma + r}) = \int_{A_{\sigma, \sigma + r}} f(x) dx
	\end{equation}
	Now, for $0 = t_0 < t_1 < \ldots < t_k = 1$, we divide up $A_{\sigma, \sigma + r} = \bigcup_{i = 0}^{k-1} \mathcal{T}_i$ where $\mathcal{T}_i = \set{x: rt_i < \rho(x, \Asig) \leq rt_{i+1}}$. We can rewrite the right hand side of (\ref{eqn: integral_over_epsilon_neighborhood}) as
	\begin{align*}
	\int_{A_{\sigma, \sigma + r}} f(x) dx & = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_i} f(x) dx \\
	& \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_i) \max_{x \in \mathcal{T}_i} f(x).
	\end{align*}
	By definition, 
	\begin{equation*}
	\nu(\mathcal{T}_i) = \nu(\Asig + rt_{i+1}B) - \nu(\Asig + rt_{i}B).
	\end{equation*}
	 Moreover, by \ref{asmp: cluster_regularity} and \ref{asmp: low_noise_density} we have
	 \begin{equation*}
	 \max_{x \in \mathcal{T}_i} f(x) \leq \tau_{\sigma} - (rt_i)^{\gamma}.
	 \end{equation*}
	 since for all $x \in \mathcal{T}_i$, $\rho(x, \Asig) > rt_i$.
	 Therefore
	\begin{align}
	\label{eqn: telescoping_sum}
	\sum_{i = 0}^{k-1} \int_{\mathcal{T}_i} f(x) dx & \leq \nonumber \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + rt_{i+1}B) - \\
	& \nu(\Asig + rt_{i}B)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right).
	\end{align}

	Now, we have that $\sigma B \subset \Asig$  which implies, 
	\begin{equation*}
	\nu(\Asig + rt_iB) \leq \nu(\Asig + \frac{r t_i}{\sigma} \Asig)
	\end{equation*}
	and we therefore have the upper bound
	\begin{align}
	\label{eqn: riemann_sum_lem1}
	& \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + rt_{i+1}B) - \nu(\Asig + rt_iB)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) \nonumber \\
	& \leq \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + \frac{r t_{i+1}}{\sigma} \Asig) - \nu(\Asig + \frac{r t_i}{\sigma} \Asig)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) \nonumber \\
	& = \nu(\Asig) \sum_{i = 0}^{k-1} \biggl\{ (1 + \frac{r t_{i+1}}{\sigma})^d - (1 + \frac{r t_{i}}{\sigma})^d \biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) 
	\end{align}
	where the upper bound holds because $\tau_{\sigma} - (rt)^{\gamma}$ is decreasing in $t$.

	Let $t_{i} = i/k$ for $i = 0, \ldots, k$. Taking the limit as $k \to \infty$, we have
	\begin{align*}
	& \lim_{k \to \infty} \sum_{i = 0}^{k-1} \biggl\{ \left(1 + \frac{r (i+1)}{k\sigma}\right)^d - \left(1 + \frac{r i}{k\sigma}\right)^d \biggr\} \left(\tau_{\sigma} - \left(\frac{ri}{k}\right)^{\gamma}\right)  \\
	 & = \int_{0}^{1} \frac{rd}{\sigma} (1 + \frac{r t}{\sigma})^{d-1} (\tau_{\sigma} - (rt)^{\gamma}) dt \\
	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
	\end{align*}
	where the inequality comes from $t \leq 1$ and $r < \sigma$.

	Finally, note that (\ref{eqn: riemann_sum_lem1}) holds for any $k$ and arbitrary $0 = t_0 < t_1 < \ldots < t_k = 1$. In particular, it holds for $t_{i} = i/k$ for $i = 0, \ldots, k$, and in the limit as $k \to \infty$. Therefore, we have
	\begin{equation*}
	P(A_{\sigma, \sigma + r}) \leq \nu(\Asig) 2^{d-1} \frac{rd}{\sigma}  \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
	\end{equation*}
	which is exactly the stated result of Lemma \ref{lem: expected_number_boundary_points}.
\end{proof}

\begin{lemma}
	\label{lem: expected_density_cut}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
	\begin{equation*}
	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write $\widetilde{\mathcal{E}}$ as the sum of indicator functions,
	\begin{equation}
	\label{eqn: density_cut_expansion}
	\widetilde{\mathcal{E}} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig)
	\end{equation}
	Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
	\begin{align*}
	\frac{\widetilde{\mu}}{{n \choose 2}} & = 2 \int_{\Asigr} f(x) \left\{ \int_{B(x,r) \cap \Asig} f(x') dx'\right\} dx \\
	& \overset{(i)}{\leq} 2 \int_{\Asigr} f(x) \nu_d r^d \tau dx \\
	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right) 
	\end{align*}
	where $(i)$ follows from Assumption \ref{asmp: cluster_separation}, which implies $f(x') \leq \tau$ for all $x' \in \Asig \setminus A$, and $(ii)$ follows from Lemma \ref{lem: expected_number_boundary_points}.
\end{proof}

\begin{lemma}
	\label{lem: expected_density_volume}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound},
	\begin{equation*}
	p \geq 2 \tau_{\sigma}^2 \nu(\Asig) \nu_d \left(\frac{r}{2}\right)^d
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write $\mathcal{V}$ as the sum of indicator functions,
	\begin{equation}
	\label{eqn: volume_expansion}
	\mathcal{V} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asig) \1(x_j \in B(x_i, r))
	\end{equation}
		Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
	\begin{equation}
	\label{eqn: expected_volume_integral}
	\frac{\mu}{{n \choose 2}} = 2 \int_{\Asig} f(x) \left\{\int_{B(x,r)} f(x') dx' \right\} dx
	\end{equation}
	For $x \in \Asig$, take $x_0 \in A$ such that $\norm{x - x_0} = \rho(x,A)$ (note that such a minimizer exists because $A$ is closed). Then, by the triangle inequality, we have
	\begin{equation*}
	B\left(\frac{x + x_0}{2}, \frac{r}{2}\right) \in \Asig \cap B(x,r)
	\end{equation*}
	Recall that by (\ref{asmp: cluster_regularity}), we have $f(x') \geq \tau_{\sigma}$ for all $x' \in \Asig$. We can therefore lower bound the right hand side of (\ref{eqn: expected_volume_integral}) by
	\begin{align*}
	& 2\int_{\Asig} f(x) \tau_{\sigma} \nu_d \left(\frac{r}{2}\right)^{d} dx \\
	& \leq 2\tau_{\sigma}^2 \nu(\Asig) \nu_d \left(\frac{r}{2}\right)^d.
	\end{align*}
\end{proof}

\subsection{\textcolor{red}{Concentration inequalities.}}

Given a symmetric kernel function $k: \mathcal{X}^m \to \Reals$, and data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$m$ $U$ statistic} to be 
\begin{equation*}
U := \frac{1}{ {n \choose m} } \sum_{1 \leq i_1 < \ldots < i_m \leq n} k(x_{i_1},\ldots,x_{i_m})
\end{equation*}

For both Lemmas \ref{lem: bounded_difference} and \ref{lem: bernstein}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed. We will additionally assume the order-$m$ kernel function $k$ satisfies the boundedness property $\sup_{x_1, \ldots, x_m} \abs{k(x_1, \ldots, x_m)} \leq 1$.

\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
	\label{lem: bounded_difference}
	For any $t > 0$,
	\begin{equation*}
	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{- \frac{2nt^2}{m}\right\}
	\end{equation*}
	Further, for any $\delta > 0$, we have
	\begin{align*}
	U & \leq \mathbb{E}U + \sqrt{\frac{m \log(1 / \delta)}{2n} }, \\
	U & \geq \mathbb{E}U - \sqrt{\frac{m \log(1 / \delta)}{2n} }
	\end{align*}
	each with probability at least $1 - \delta$. 
\end{lemma}

\begin{lemma}[Bernstein's inequality for $U$-statistics]
	\label{lem: bernstein}
	Additionally, assume $\sigma^2 = \var\left(k(X_1, \ldots, X_m) \right) < \infty$. Then for any $\delta > 0$, 
	\begin{align*}
	\mathbb{P}(U - \mathbb{E}U \geq t) \leq \exp\left\{-\frac{n}{2m}\frac{t^2}{\sigma^2 + t/3}\right\},
	\end{align*}

	Moreover if $\sigma^2 \leq \mu/n$, 
	\begin{align*}
	U & \leq \mathbb{E}U \cdot \left(1 + \max\left\{ \sqrt{\frac{2m\log(1/\Delta)}{\mu}}, \frac{2m \log(1/\Delta)}{3\mu} \right\}\right), \\
	U & \geq \mathbb{E}U \cdot \left(1 - \max\left\{ \sqrt{\frac{2m\log(1/\Delta)}{\mu}}, \frac{2m \log(1/\Delta)}{3\mu} \right\}\right)
	\end{align*}
	each with probability at least $1 - \Delta$.
\end{lemma}

\section{Proof of Theorem \ref{thm: conductance_upper_bound}}

Given the previous lemmas, the proof of Theorem \ref{thm: conductance_upper_bound} is straightforward. We rely on Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} to bound $\widetilde{\mu}$ and $\mu$, respectively, and Lemma \ref{lem: bernstein} to bound the deviations $\widetilde{\mathcal{E}} - \widetilde{\mu}$ and $\mathcal{V} - \mu$ with high probability.

\subsection{Numerator of $\Phi_{n,r}(\Asig[\mathbf{X}])$.}
From (\ref{eqn: density_cut_expansion}), we can see that $\widetilde{\mathcal{E}}$, properly scaled, can be expressed as an order-$2$ $U$-statistic,
\begin{equation*}
\frac{1}{{n \choose 2}}\widetilde{\mathcal{E}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \widetilde{k}(x_i, x_j)
\end{equation*}
where 
\begin{align*}
\tilde{k}(x_i,x_j) = & \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) + \\
& \1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig)
\end{align*}

From Lemma \ref{lem: bounded_difference} we therefore have
\begin{equation}
\label{eqn: numerator_additive_bound}
\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} \leq \widetilde{p} + \sqrt{\frac{\log(1/\delta)}{n}}
\end{equation}
with probability at least $1 - \delta$.

\textcolor{red}{\textbf{Multiplicative bound}: As $\tilde{k}(x_1,x_2)$ is the sum of two Bernoulli random variables with negative covariance (since $\1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) = 1$ implies $\1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig) = 0$ and vice versa), we can upper bound $\var\left(\tilde{k}(x_1, x_2)\right) \leq  \widetilde{p}$, where we recall 
\begin{equation*}
\widetilde{p} = 2\cdot \mathbb{P}\left(\1(x_1 \in \Asigr) \1(x_2 \in B(x_1,r) \cap \Asig)\right)
\end{equation*}
From Lemma \ref{lem: bernstein}, we therefore have
\begin{equation*}
\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} \leq \widetilde{p} + \max\left\{ \sqrt{\frac{4\log(1/\Delta)\widetilde{p}}{n}}, \frac{4 \log(1/\Delta)}{3n} \right\}
\end{equation*}
with probability at least $1 - \Delta$.}

\paragraph{Denominator of $\Phi_{n,r}(\Asig[\mathbf{X}])$.}
We follow a very similar set of steps as above.

By (\ref{eqn: density_cut_expansion}), we see that $\mathcal{V}$ can also be expressed as an order-2 $U$-statistic,
\begin{equation*}
\frac{\mathcal{V}}{ {n \choose 2} } = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n } k'(x_i, x_j)
\end{equation*}
with
\begin{align*}
k'(x_i,x_j)  = & \1(x_i \in A_\sigma)\1(x_j \in B(x_i,r)) ~ + \\
& \1(x_j \in A_{\sigma})\1(x_i \in B(x_j,r))
\end{align*}

From Lemma \ref{lem: bounded_difference} we therefore have
\begin{equation}
\label{eqn: denominator_additive_bound}
\frac{\mathcal{V}}{{n \choose 2}} \geq p - \sqrt{\frac{\log(1/\delta)}{n}}
\end{equation}
with probability at least $1 - \delta$.

\textcolor{red}{Multiplicative bound: The two terms on the right hand side are both distributed $\mathrm{Bernoulli}(p/2)$. Moreover, since $\1(x_i \in A_\sigma) = 1$ implies $\1(x_j \in A_{\sigma}) = 0$, they have negative covariance. We can therefore upper bound $\var(k'(x_i,x_j)) \leq p$, and so from Lemma \ref{lem: bernstein}, we have
\begin{equation*}
\frac{\mathcal{V}}{{n \choose 2}} \geq p - \max\left\{ \sqrt{\frac{4\log(1/\Delta)p}{n}}, \frac{4 \log(1/\Delta)}{3n} \right\}
\end{equation*}
with probability at least $1 - \Delta$. }

\paragraph{Proof of the additive error bound.}
Noting that $\Phi_{n,r}(\Asig[\mathbf{X}]) = \mathcal{\widetilde{E}} / \mathcal{V}$, and multiplying and dividing by ${n \choose 2}$, we have
\begin{equation}
\label{eqn: conductance_representation_1}
\Phi_{n,r}(\Asig[\mathbf{X}]) = \frac{\widetilde{p} + \left(\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} - \widetilde{p}\right)}{p + \left(\frac{\widetilde{\mathcal{V}}}{{n \choose 2}} - p \right)}
\end{equation}
We assume (\ref{eqn: numerator_additive_bound}) and (\ref{eqn: denominator_additive_bound}) hold, keeping in mind that this will happen with probability at least $1 - 2\delta$. Along with (\ref{eqn: conductance_representation_1}) this means
\begin{equation*}
\Phi_{n,r}(\Asig[\mathbf{X}]) \leq \frac{\widetilde{p} + \Err_n}{p - \Err_n}
\end{equation*}
for $\Err_n = \sqrt{\frac{\log(1/\delta)}{n}}$.
Now, some straightforward algebraic manipulations yield
\begin{align*}
\frac{\widetilde{p} + \Err_n}{p - \Err_n} & = \frac{\widetilde{p}}{p} + \left(\frac{\widetilde{p}}{p - \Err_n} - \frac{\widetilde{p}}{p}\right) + \frac{\Err_n}{p - \Err_n} \\
& = \frac{\widetilde{p}}{p} + \frac{\Err_n}{p - \Err_n}\left(\frac{\widetilde{p}}{p} + 1\right) \\
& \leq \frac{\widetilde{p}}{p} + 2 \frac{\Err_n}{p - \Err_n}.
\end{align*}
Finally, combining the upper bound given by Lemma \ref{lem: expected_density_volume} with the lower bound on $n$ specified in the statement of Theorem \ref{thm: conductance_upper_bound}, we have
\begin{equation*}
2 \frac{\Err_n}{p - \Err_n} \leq \epsilon
\end{equation*}
By Lemmas \ref{lem: expected_density_cut} and Lemma \ref{lem: expected_density_volume}, we have
\begin{equation*}
\frac{\widetilde{p}}{p} \leq C_{\sigma} \frac{\tau}{\tau_{\sigma}} \frac{(\tau_{\sigma} - \frac{r^{\gamma+1}}{\gamma+1})}{\tau_{\sigma}}
\end{equation*}
and thus we have shown (\ref{eqn: conductance_additive_error_bound}) occurs with probability at least $1 - 2\delta$. Plugging in $\delta' = \delta/2$ gives the exact statement in Theorem \ref{thm: conductance_upper_bound}.

\end{document}

### 2019-01-09 references/notes/ball97.tex
added icml draft files

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\vr}{\mathrm{vr}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\newcommand{\wt}[1]{\widetilde{#1}}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes on `An Elementary Introduction to Modern Convex Geometry'}
\author{Alden Green}
\date{\today}
\maketitle

\section{Setup}

Let $K$ be a convex body in $\Rd$. Denote the ratio of the $d$-dimensional unit ball by $\nu_d$. Let $Q = [-1,1]^d$ be the unit cube in $\Rd$.

Assuming symmetry of $K$ will often greatly ease proofs.

\begin{definition}
	We say $K$ is \textit{(centrally) symmetric} if $-x \in K$ whenever $x \in K$. This will also imply that $K$ is the unit ball of some norm $\norm{\cdot}_K$ on $\Rd$:
	\begin{equation*}
	K = \set{x: \norm{x}_{K} \leq 1}
	\end{equation*}
\end{definition}

\paragraph{Volume ratio.}

The volume ratio is used to prove reverse isoperimetric inequalities of the form we want. To define it, we first recall the concept of an \textit{ellipsoid}: given $(e_j)_{j=1}^{d}$ an orthonormal basis of $\Rd$ and $(a_j)$ positive numbers, the ellipsoid
\begin{equation*}
\set{x: \sum_{i = 1}^{d} \frac{\dotp{x}{e_j}^2}{\alpha_j^2} \leq 1}
\end{equation*}
has volume $\nu_d \prod \alpha_j$.
\begin{definition}
	Let $K$ be a convex body in $\Rd$. The \textit{volume ratio} of $K$ is
	\begin{equation*}
	\vr(K) := \left(\frac{\vol(K)}{\vol(\E)}\right)^{1/d}
	\end{equation*}
	where $\E$ is the ellipsoid of maximal volume in $K$. 
\end{definition}

Let $B_2^d$ be the $d$-dimensional unit Euclidean ball.
\begin{definition}
	The \textit{surface area} of a convex body $K \in \Rd$, $\partial K$, is defined by
	\begin{equation*}
	\vol(\partial K) = \lim_{\epsilon \to 0} \frac{\vol(K + \epsilon B_2^d) - \vol(K)}{\epsilon}
	\end{equation*}
\end{definition}

\section{Convolutions and Volume Ratios: The Reverse Isoperimetric Problem}

\begin{theorem}
	Let $K$ be a convex body and $T$ a regular solid simplex in $\Rd$. Then there is an affine image of $K$ whose volume is the same as that of $T$ and whose surface area is no larger than that of $T$. 
\end{theorem}

We will prove a related, by far simpler, result.

\begin{theorem}
	\label{thm: reverse_isoperimetry_symmetric_bodies}
	Let $K$ be a symmetric convex body, and $T$ the $d$-dimensional unit cube. Then there is an affine image of $K$ whose volume is the same as that of $T$ and whose surface area is no larger than that of $T$.
\end{theorem}

The result follows from a result showing that the unit cube $Q = [-1,1]^d$ has the largest volume ratio among convex bodies.
\begin{theorem}
	\label{thm: volume_ratio_symmetric_bodies}
	Among symmetric convex bodies the cube has largest volume ratio.
\end{theorem}

\begin{proof}[Proof of Theorem \ref{thm: reverse_isoperimetry_symmetric_bodies}]
	We begin by recall that for $Q$
	\begin{equation*}
	\vol(\partial Q) = 2d \vol(Q)^{(d-1)/d},
	\end{equation*}
	so we wish to show that any other convex body $K$ has an affine image $\wt{K}$ such that
	\begin{equation*}
	\vol(\partial \wt{K}) \leq 2d ~ \vol(\wt{K})^{(d-1)/d}.
	\end{equation*}

	Choose $\wt{K}$ so that its maximal volume ellipsoid is $B_2^n$, the Euclidean ball of radius $1$. Then, by Theorem \ref{thm: volume_ratio_symmetric_bodies}, we have that
	\begin{align*}
	\vr(\wt{K}) \leq \vr(Q)
	\end{align*}
	and since the maximal volume ellipsoid is the same for both $\wt{K}$ and $Q$, this implies $\vol(\wt{K}) \leq \vol(Q) = 2^d$.

	Now, since $\wt{K} \supset B_2^d$, the surface area can be upper bounded
	\begin{align*}
	\lim_{\epsilon \to 0} \frac{\vol(\wt{K} + \epsilon \wt{K}) - \vol(\wt{K})}{\epsilon} & = \vol(\wt{K}) \lim_{\epsilon \to 0} \frac{(1 + \epsilon)^d - 1}{\epsilon} \\
	& = d ~ \vol(\wt{K}) = d ~ \vol(\wt{K})^{1/d} \vol(\wt{K})^{(d-1)/d}  \\
	& \leq 2d \vol(\wt{K})^{(d-1)/d}.
	\end{align*}
\end{proof}

\end{document}

### 2019-01-10 icml/icml_local_density_clustering.tex
mostly finished introduction

@@
 \newcommand{\vol}{\text{vol}}
+\newcommand{\cut}{\mathrm{cut}}
 \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
@@
 \newcommand{\Asig}{A_{\sigma}}
+\newcommand{\x}{\mathbf{x}}
+\newcommand{\1}{\mathbf{1}}
 
@@
 
-Clustering is a fundamental task in machine learning, which often involves splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
+Given data $\mathbf{x} := \set{x_1, \ldots, x_n} \subset \Rd$, our statistical learning task is clustering: splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
+
 In particular, spectral clustering methods are a family of powerful non-parametric clustering algorithms.
+Given a symmetric matrix $A \in \Reals^{n \times n}$ with $(i,j)$th entry representing the similarity between data points $x_i$ and $x_j$, we form the graph Laplacian matrix \footnote{Often, either of the Laplacian matrices  $L_{sym} := D^{\frac{1}{2}}WD^{-\frac{1}{2}}$ or $L_{unn} := D - A$ are used instead.},
+\begin{equation}
+\label{eqn: random_walk_laplacian}
+W := D^{-1}A; ~~~ L = I - W
+\end{equation}
+where the degree matrix $D$ is a diagonal matrix with $D_{ii} := \sum_j A_{ij}$.
 
-Roughly speaking, spectral clustering techniques
-embed data points using the spectrum of (some
-form of) the graph Laplacian matrix and subsequently 
+Roughly speaking, spectral clustering techniques first embed the data $\x$ using the spectrum of the graph Laplacian matrix and subsequently 
 use this \emph{spectral embedding} to find a clustering of the data.
@@
 
-A natural model to consider when analyzing point cloud data is based on the hypothesis that we receive samples $\set{x_1, \ldots, x_n}$ independently drawn from a distribution $f$.
-In this case, we are interested in understanding what the output of a clustering algorithm on this finite sample reveals about the unknown distribution $f$.
-In particular, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters in this context as \emph{connected regions of high-density}, and study the ability of spectral methods to identify these clusters.
+A natural model to consider when analyzing point cloud data is the following:
+\begin{equation}
+x_i \sim P, \text{   independently, for $i = 1,\ldots,n$},
+\end{equation} 
+with $f$ the density function of $P$ with respect to the uniform measure over $\Rd$.
+In this case, we are interested in understanding what the output of a clustering algorithm on this finite sample reveals about the unknown density $f$.
+For $\lambda > 0$ and $\set{x: f(x) \geq \lambda}$, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters to be the connected components $\mathbb{C}_f(\lambda)$ of the upper level set; we call these connected regions of high density \textit{density clusters}, and study the ability of spectral methods to identify such clusters.
 
-Given a matrix $A$ with entries representing the similarity between pairs of data points, and $G  = (V,E)$ a graph representation of $A$ with vertices $V$ and edges $E$, there are many \cite{yang2015,fortunato2010} graph-theoretic measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
+\paragraph{Graph connectivity criteria.}
 
-Arguably a natural way to assess cluster quality is via the bicriteria of \textit{external} and \textit{internal connectivity} of $S$, represented by the parameters $\Phi$ and $\Psi$, respectively.
-As the names suggest, external connectivity should relate to the number of edges between $S$ and $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$ \footnote{We formally define our notions of external and internal connectivity in Section \ref{sec: measures_of_cluster_quality}} .
+A somewhat more standard mode of analyzing spectral clustering methods is through approximation to a pair of graph connectivity criteria.
+
+For $A$ as before, let the graph $G  = (V,E)$, with vertices $V = (v_1, \ldots, v_n)$ corresponding to the $n$ rows of $A$, and edges $E = \set{(v_i,v_j): 1 \leq i < j \leq n: (v_i,v_j) = A_{ij}}$ (Since $A$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops).
+There are many \cite{yang2015,fortunato2010} graph-theoretic measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
+
+Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \textit{external} and \textit{internal connectivity} of $S$, respectively.
+As the names suggest, external connectivity should relate to the number of edges between $S$ and $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
 The clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
-We will refer to such a subset as a $(\Phi,\Psi)$-cluster (or partition).
-Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms can be understood as outputting clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition).
-\footnote{For slightly different definitions of the internal connectivity $\Psi$}
 
-In the case where $G$ encodes similarities between sampled point-cloud data, some understanding of how graph theoretic quantities such as $\Phi$ and $\Psi$ relate to properties of the underlying distribution $f$ has developed.
-Continuous analogues to many such graph measures of cluster quality have been defined, and, under appropriate graph construction, convergence of clusters output by spectral algorithm to approximate minimizers of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.
+We will assess the external connectivity of a subset $S \subseteq V$ through its normalized cut. The cut of $S$ is
+\begin{equation*}
+\cut(S; G) := \sum_{u \in S} \sum_{v \in S^c} \1\left((u,v) \in E \right)
+\end{equation*}
+-- where $S^c = V / S$ is the complement of $S$ in $V$ -- and the volume of $S$ is
+\begin{equation*}
+\vol(S; G) := \sum_{u \in S} \sum_{v \in V} \1\left((u,v) \in E \right).
+\end{equation*}
+Then, the \textit{normalized cut} of $S$ is given by
+\begin{equation}
+\label{eqn: norm_cut}
+\Phi(S; G) := \frac{\cut(S; G)}{ \min\left\{\vol(S; G), \vol(S^c; G) \right\} }
+\end{equation} 
+Intuitively, a set with low \textit{normalized cut} has many more edges which do not cross the cut than edges which do cross the cut.
 
-Relating these partitions to the arguably more simply defined high density clusters can be challenging in general.
-Intuitively, however, under the right conditions such a connection should exist.
-Given sufficient samples, and an appropriately specified notion of similarity, we can imagine that all points within a high density cluster will have many edges to other points within the cluster, and comparatively few edges to data points outside the cluster.
-Motivated by this intuition, one primary line of work in this article is to formally establish that, under a natural set of geometric conditions, a connection between certain graph-based criteria and density clusters does exist.
+Given $S \subseteq V$, the subgraph induced by $S$ is given by $G[S] = (S, E_S)$, where $(u,v) \in E_S$ if both $u$ and $v$ are in $S$ and $(u,v) \in E_S$.
+\textcolor{red}{Introduce and define the \textbf{inverse mixing time}.}
+\begin{equation}
+\label{eqn: inv_mixing_time}
+\Psi(S; G) = 
+\end{equation}
 
-We also study the consequences of these facts as they relate to local spectral clustering algorithms.
-We restrict our attention in particular to one such popular algorithm: \textit{personalized PageRank} (PPR).
-We show that a variant of PPR, properly initialized inside a high-density cluster, performs well: not only does the output set of PPR approximate the cluster quality measures of the high-density cluster, the PPR algorithm also consistently recovers the population density cluster.
+If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no less than $\Psi$, we will refer to it as a $(\Phi,\Psi)$-cluster.
+Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been shown to output clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition), where the optimization is carried out over the graph $G$.
+\footnote{In the case of \cite{kannan04}, the internal connectivity parameter $\phi$ is actually the conductance, i.e.
+the minimum normalized cut within the subgraph $G[S]$.
+See Theorem 3.1 for details; however, note that $\phi^2 / \log(\vol(S)) \leq O(\Psi)$, and so the lower bound on $\phi$ translates to a lower bound on $\Psi$.}
 
-\subsection{Related Work}
+\paragraph{Personalized PageRank.}
+As mentioned previously, global algorithms which find spectral cuts may be computationally infeasible for large graphs; in this setting, local algorithms may be preferred or even required.
+We will restrict our attention in particular to one such popular algorithm: \textit{personalized PageRank} (PPR).
+The personalized PageRank algorithm was first introduced by \cite{haveliwala2003} and variants of this algorithm have been studied further in several recent works \citep{spielman2011,spielman2014,zhu2013,anderson2006,mahoney2012}.
 
-\subsection{Summary of Results}
+The random walk matrix is given by $W$ defined as in (\ref{eqn: random_walk_laplacian}), and vertices $V$ and edges $E$ are as above.
+The PPR vector is defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
+Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for the $v$th node (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \textit{PPR vector} is given by the recursive formulation
+\begin{equation}
+\label{eqn: ppr_vector}
+p(v,\alpha;G) := \alpha e_v + (1 - \alpha) p(v,\alpha;G) W
+\end{equation}
+We note in passing that, for $\alpha > 0$ the vector $p(v,\alpha;G)$ can be well-approximated by a simple local computation (of a random walk with restarts at the node $v$.) We also point out that, from a density clustering standpoint, since density clusters are inherently local, using the PPR algorithm eases the analysis, and as we will observe in the sequel our analysis requires fewer global regularity conditions relative to more classical global spectral algorithms.
+
+To compute a cluster $\widehat{C}_n \subset V$ using the PPR vector, we will take sweep cuts of $p(r, \alpha; G)$.
+For a vector $p$, $p[j]$ be the $j$th entry of $p$, and $p_{(k)}$ be the $k$th \textit{largest} entry of $p$.
+Then the sweep cut $S_k$ is
+\begin{equation}
+\label{eqn: sweep_cuts}
+S_k = \set{u_j: p(r, \alpha; G)[j] > p(r, \alpha; G)_{(k)}}
+\end{equation}
+
+We delay formal introduction of the local clustering algorithm we analyze until we have given defined a method for forming a graph over the data $\x$.
+
+\paragraph{Large sample behavior.}
+
+Given a kernel function $\mathbf{k}: \Rd \times \Rd \to [0,\infty)$ of the form $\mathbf{k}(x,x') = k(\norm{x - x'}/ r_n)$ with $k$ non-increasing and some $r_n > 0$, and data $\x = \set{x_1, \ldots, x_n}$ sampled from $P$ as before, form the (weighted, complete) similarity graph $G_n = (\x, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
+(Here, $\norm{\cdot}$ is used to denote Euclidean norm).
+
+It is worth pointing out that in this context, some theory has been developed regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and others) relate to properties of the underlying distribution $f$ as well as the kernel function $\mathbf{k}$.
+Such analyses typically proceed by defining a continuous analogue to the measure of cluster quality under consideration.
+Then, under appropriate specification of $\mathbf{k}$ and a proper schedule of $\set{r_n}_{n \in N}$, convergence of clusters output by spectral (and other) algorithms to the corresponding minima of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.
+
+These continuous analogues, and their corresponding minimizers, are not always easily identifiable for the particular density function under consideration.
+Relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
+\textcolor{red}{Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.} We formalize this intuition next.
+
+\subsection{Summary of results}
+
+Hereafter, we consider the \textit{uniform kernel function} for a fixed $r > 0$,
+\begin{equation}
+\mathbf{k}(x,x') = \1(\norm{x - x'} \leq r)
+\end{equation}
+and the associated \textit{neighborhood graph} 
+\begin{equation}
+G_{n,r} = (\x, E_{n,r}), \text{  $(x_i,x_j) \in E_{n,r}$ if $\mathbf{k}(x_i,x_j) = 1$}
+\end{equation}
+For a given high density cluster $C \subseteq \mathbb{C}_f(\lambda)$, we call $C[\x] = C \cap \x$ the \textit{empirical density cluster}.
+We now introduce a notion of consistency for the task of density cluster estimation:
+
+\begin{definition}[Consistent density cluster estimation]
+	For an estimator $\widehat{C}_n$, and any $C, C' \in C_f(\lambda),$ we say $\widehat{C}_n$ is a consistent estimator of $C$ if the following statement holds: as the sample size $n \to \infty$,
+	\begin{equation}
+	C[\x] \subseteq \widehat{C}_n, ~\mathrm{ and }~ \widehat{C}_n \cap C'[\x] = \emptyset
+	\end{equation}
+	occurs with probability tending to $1$.
+
+\end{definition}
+
+Our results can now be summarized by the following two points:
 
@@
 	\item 
-	Theorem: Well-conditioned density clusters have low conductance.
+	Under a natural set of geometric conditions\footnote{We formally introduce the geometric conditions in \ref{sec: measures_of_cluster_quality}.
+They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large}, Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2} upper and lower bound, respectively, the normalized cut and inverse mixing time of an empirical density cluster $C[\x]$.
 
 	\item 
-	Theorem: Well-conditioned density clusters have high internal connectivity.
+	We show these bounds on the graph connectivity criteria have algorithmic consequences for the PPR algorithm.
+An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{C}_n$ output by Algorithm \ref{alg: ppr_cluster}, as well as upper bounding the symmetric set difference between $\widehat{C}_n$ and $C[\x]$.
+Further, in Section 4 we show that a careful analysis of the form typical to local clustering algorithms yields \textcolor{red}{Theorem 4}, which states that Algorithm \ref{alg: ppr_cluster}, properly initialized, performs consistent density cluster estimation.
+\end{enumerate}
 
-	\item 
-	Corollary: PPR local clustering algorithm, run on a well-conditioned density cluster and appropriately initialized, will output a low conductance set, which also has low symmetric set difference with the density cluster.
-
-	\item
-	Theorem: PPR local clustering algorithm,run on a well-conditioned density cluster and appropriately initialized, exhibits successful density cluster recovery.
-\end{enumerate}
+\paragraph{Organization.}
+In Section \ref{section: everything_else}, we provide some example density functions, to clarify the relevance of our results.
+In \textcolor{red}{Section 5}, we show empirical performance of the PPR algorithm, which demonstrates that violations of the geometric conditions we set out in Section \ref{sec: measures_of_cluster_quality} manifestly impact density cluster recovery (i.e.
+the conditions are not superfluous), before concluding in \textcolor{red}{Section 6}.
+First, however, we summarize some related work.
+\subsection{Related Work}
 
@@
 We typically seek a set $S^{\star} \subset V$ such that $\Phi(S^{\star}; G)$ is small.
-
-\textcolor{red}{Introduce and define the \textbf{internal connectivity}.}
 

### 2019-01-11 icml/icml_local_density_clustering.tex
related work complete; theorem 2 added

@@
 \usepackage[shortlabels]{enumitem}
+\usepackage{bm}
 
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\newcommand{\Asig}{A_{\sigma}}
-\newcommand{\x}{\mathbf{x}}
 \newcommand{\1}{\mathbf{1}}
+
+%%% Vectors
+\newcommand{\pbf}{\mathbf{p}}
+\newcommand{\ebf}[1]{\mathbf{e}_{#1}}
+\newcommand{\pibf}{\bm{\pi}}
+
+%%% Matrices
+\newcommand{\Abf}{\mathbf{A}}
+\newcommand{\Xbf}{\mathbf{X}}
+\newcommand{\Wbf}{\mathbf{W}}
+\newcommand{\Lbf}{\mathbf{L}}
+\newcommand{\Dbf}{\mathbf{D}}
+\newcommand{\Ibf}[1]{\mathbf{I}_{#1}}
+
+%%% Probability distributions (and related items)
+\newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Cbb}{\mathbb{C}}
+
+%%% Sets
+\newcommand{\Cset}{\mathcal{C}}
+\newcommand{\Aset}{\mathcal{A}}
+\newcommand{\Asig}{\Aset_{\sigma}}
+
+%%% Operators
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 
-Given data $\mathbf{x} := \set{x_1, \ldots, x_n} \subset \Rd$, our statistical learning task is clustering: splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
+Let $\mathbf{X} := (x_1, \ldots, x_n)$ with $x_i \in \Rd$ for $i = 1,\ldots,n$.
+Our statistical learning task is clustering: splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
 
 In particular, spectral clustering methods are a family of powerful non-parametric clustering algorithms.
-Given a symmetric matrix $A \in \Reals^{n \times n}$ with $(i,j)$th entry representing the similarity between data points $x_i$ and $x_j$, we form the graph Laplacian matrix \footnote{Often, either of the Laplacian matrices  $L_{sym} := D^{\frac{1}{2}}WD^{-\frac{1}{2}}$ or $L_{unn} := D - A$ are used instead.},
+Given a symmetric adjacency matrix $\Abf \in \Reals^{n \times n}$ with $(i,j)$th entry representing the similarity between data points $x_i$ and $x_j$, we form the random walk transition probability matrix $\Wbf$, and corresponding graph Laplacian matrix $\Lbf$\footnote{Often, either of the Laplacian matrices  $\Lbf_{sym} := \Dbf^{\frac{1}{2}}\Wbf \Dbf^{-\frac{1}{2}}$ or $\Lbf_{unn} := \Dbf - \Abf$ are used instead.}:
 \begin{equation}
 \label{eqn: random_walk_laplacian}
-W := D^{-1}A; ~~~ L = I - W
+\Wbf := \Dbf^{-1}\Abf; ~~~ \Lbf = \Ibf{n} - \Wbf
 \end{equation}
-where the degree matrix $D$ is a diagonal matrix with $D_{ii} := \sum_j A_{ij}$.
+where the degree matrix $\Dbf$ is a diagonal matrix with $\Dbf_{ii} := \sum_j \Abf_{ij}$, and $\Ibf{n}$ is the $n \times n$ identity matrix.
 
-Roughly speaking, spectral clustering techniques first embed the data $\x$ using the spectrum of the graph Laplacian matrix and subsequently 
+Roughly speaking, spectral clustering techniques first embed the data $\Xbf$ using the spectrum of the graph Laplacian matrix and subsequently 
 use this \emph{spectral embedding} to find a clustering of the data.
@@
 
-A natural model to consider when analyzing point cloud data is the following:
+A natural model to consider when analyzing point cloud data such as $\Xbf$ is the following:
 \begin{equation}
-x_i \sim P, \text{   independently, for $i = 1,\ldots,n$},
+x_i \sim \Pbb, ~~~ \text{independently, for $i = 1,\ldots,n$},
 \end{equation} 
-with $f$ the density function of $P$ with respect to the uniform measure over $\Rd$.
+with $f$ the density function of $\Pbb$ with respect to the uniform measure over $\Rd$.
 In this case, we are interested in understanding what the output of a clustering algorithm on this finite sample reveals about the unknown density $f$.
-For $\lambda > 0$ and $\set{x: f(x) \geq \lambda}$, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters to be the connected components $\mathbb{C}_f(\lambda)$ of the upper level set; we call these connected regions of high density \textit{density clusters}, and study the ability of spectral methods to identify such clusters.
+For $\lambda > 0$ and the upper level set $\set{x: f(x) \geq \lambda}$, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters as the connected components $\mathbb{C}_f(\lambda)$ of the upper level set; we call these connected regions of high density \textit{density clusters}, and study the ability of spectral methods to identify such clusters.
 
@@
 
-A somewhat more standard mode of analyzing spectral clustering methods is through approximation to a pair of graph connectivity criteria.
+A somewhat more standard mode of understanding spectral clustering methods is to view them as approximating some graph connectivity criteria.
 
-For $A$ as before, let the graph $G  = (V,E)$, with vertices $V = (v_1, \ldots, v_n)$ corresponding to the $n$ rows of $A$, and edges $E = \set{(v_i,v_j): 1 \leq i < j \leq n: (v_i,v_j) = A_{ij}}$ (Since $A$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops).
+For $\Wbf$ as before, let the graph $G  = (V,E)$, with vertices $V = \set{v_1, \ldots, v_n}$ corresponding to the $n$ rows of $\Abf$, and (possibly weighted) edges $E = \set{(v_i,v_j,\Abf_{ij}): 1 \leq i < j \leq n, \Abf_{ij} > 0}$ (Since $\Abf$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops, hence $i \neq j$).
 There are many \cite{yang2015,fortunato2010} graph-theoretic measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
@@
 Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \textit{external} and \textit{internal connectivity} of $S$, respectively.
-As the names suggest, external connectivity should relate to the number of edges between $S$ and $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
-The clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
+As the names suggest, external connectivity should relate to the number of edges between $S$ and its complement $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
+The graph clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
 
@@
 Given $S \subseteq V$, the subgraph induced by $S$ is given by $G[S] = (S, E_S)$, where $(u,v) \in E_S$ if both $u$ and $v$ are in $S$ and $(u,v) \in E_S$.
-\textcolor{red}{Introduce and define the \textbf{inverse mixing time}.}
+Letting $\abs{S} = m$, $\Abf_S$ then denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, only over $G[S]$.)
+
+Our internal connectivity parameter $\Psi(S)$ will capture the time it takes for the random walk governed by $\Wbf_S$ to mix (that is, approach a stationary distribution) uniformly over $S$.
+Denoting the stationary distribution $\widetilde{\pibf} = (\widetilde{\pi}_{1}, \ldots, \widetilde{\pi}_{m})$, the \textit{relative pointwise mixing time} $\tau_{\infty}(S; G[S])$ of the random walk over $G[S]$ defined by $\Wbf_S$ is the smallest integer $t_0 > 0$ such that for all $v = v_i,v' = v_j \in S$:
+\begin{equation*}
+\abs{\frac{e_v \Wbf_S^t - \widetilde{\pi}_{j}}{\widetilde{\pi}_{j}}} \leq \frac{1}{4}
+\end{equation*}
+for all $t > t_0$
+\footnote{Given a seed node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.} (Of course, given the definition of $\Wbf_S$ it is well known that the stationary distribution $\pibf_S$ will be defined by $\widetilde{\pi}_{i} = (\Dbf_{S})_{ii} / \vol(S; G[S])$.
+
+Intuitively, the smaller the pointwise mixing time, the more connected every pair of points $v$ and $v'$ are in the graph $G[S]$.
+Therefore, the internal connectivity parameter $\Psi(S; G)$ is simply one over the mixing time:
 \begin{equation}
 \label{eqn: inv_mixing_time}
-\Psi(S; G) = 
+\Psi(S; G) = \frac{1}{\tau_{\infty}(S; G[S])}
 \end{equation}
@@
 
-The random walk matrix is given by $W$ defined as in (\ref{eqn: random_walk_laplacian}), and vertices $V$ and edges $E$ are as above.
-The PPR vector is defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
-Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for the $v$th node (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \textit{PPR vector} is given by the recursive formulation
+The random walk matrix $\Wbf$ over the graph $G = (V,E)$ with associated adjacency matrix $\Abf$ is defined as in (\ref{eqn: random_walk_laplacian}).
+PPR is then defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
+Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \textit{PPR vector} is given by the recursive formulation
 \begin{equation}
 \label{eqn: ppr_vector}
-p(v,\alpha;G) := \alpha e_v + (1 - \alpha) p(v,\alpha;G) W
+\pbf(v,\alpha;G) := \alpha \ebf{v} + (1 - \alpha) \pbf(v,\alpha;G) \Wbf
 \end{equation}
-We note in passing that, for $\alpha > 0$ the vector $p(v,\alpha;G)$ can be well-approximated by a simple local computation (of a random walk with restarts at the node $v$.) We also point out that, from a density clustering standpoint, since density clusters are inherently local, using the PPR algorithm eases the analysis, and as we will observe in the sequel our analysis requires fewer global regularity conditions relative to more classical global spectral algorithms.
+We note in passing that, for $\alpha > 0$, the vector $\pbf(v,\alpha;G)$ can be well-approximated by a simple local computation (of a random walk with restarts at the node $v$.) We also point out that, from a density clustering standpoint, since density clusters are inherently local, using the PPR algorithm eases the analysis, and as we will observe in the sequel our analysis requires fewer global regularity conditions relative to more classical global spectral algorithms.
 
-To compute a cluster $\widehat{C}_n \subset V$ using the PPR vector, we will take sweep cuts of $p(r, \alpha; G)$.
-For a vector $p$, $p[j]$ be the $j$th entry of $p$, and $p_{(k)}$ be the $k$th \textit{largest} entry of $p$.
-Then the sweep cut $S_k$ is
+To compute a cluster $\widehat{C} \subset V$ using the PPR vector, we will take sweep cuts of $\pbf(v, \alpha; G)$.
+Denote the entries of $\pbf(v, \alpha; G)$ by $\pbf(v, \alpha; G) = (p_1, \ldots, p_n)$, and let the \textit{stationary distribution} $\pibf$ of the random walk defined by $\Wbf$ be given by
+\begin{equation*}
+\pibf = (\pi_1, \ldots, \pi_n), ~~~ \pi_j := \frac{\Dbf_{jj}}{\vol(V; G)}.
+\end{equation*}
+Then, for a number $\beta \geq 0$, the sweep cut $S_\beta$ is
 \begin{equation}
 \label{eqn: sweep_cuts}
-S_k = \set{u_j: p(r, \alpha; G)[j] > p(r, \alpha; G)_{(k)}}
+S_\beta = \set{u_j \in V: p_j > \beta \pi_j}.
 \end{equation}
-
-We delay formal introduction of the local clustering algorithm we analyze until we have given defined a method for forming a graph over the data $\x$.
+One such sweep cut will be our chosen cluster $\widehat{C}$.  
+(We delay formal introduction of the local clustering algorithm we analyze until \textcolor{red}{Section 2}, after we have given a method for forming a graph over the data $\Xbf$.)
 
@@
 
-Given a kernel function $\mathbf{k}: \Rd \times \Rd \to [0,\infty)$ of the form $\mathbf{k}(x,x') = k(\norm{x - x'}/ r_n)$ with $k$ non-increasing and some $r_n > 0$, and data $\x = \set{x_1, \ldots, x_n}$ sampled from $P$ as before, form the (weighted, complete) similarity graph $G_n = (\x, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
+Let $(r_n)$ be a sequence of positive numbers.
+Given a sequence of kernel functions $k_n: \Rd \times \Rd \to [0,\infty)$ of the form $k_n(x,x') = k(\norm{x - x'}/ r_n)$ for $k$ a non-increasing function, and data $\Xbf = \set{x_1, \ldots, x_n}$ sampled from $\Pbb$ as before, form the (weighted, complete) similarity graph $G_n = (\Xbf, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
 (Here, $\norm{\cdot}$ is used to denote Euclidean norm).
 
-It is worth pointing out that in this context, some theory has been developed regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and others) relate to properties of the underlying distribution $f$ as well as the kernel function $\mathbf{k}$.
+It is worth pointing out that in this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence of finite sample graph-theoretic functionals to their continuous counterparts has been shown
+\cite{garciatrillos16, arias-castro12, maier11}.
+However these continuous analogues are not always easily interpretable -- and their corresponding minimizers not always easily identifiable -- for the particular density function under consideration.
+Of course, relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
+\textcolor{red}{Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.} We formalize this intuition next.
+
+%It is worth pointing out that in this context, some theory has been developed regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and others) relate to properties of the underlying distribution $f$ as well as the kernel function $k$.
 Such analyses typically proceed by defining a continuous analogue to the measure of cluster quality under consideration.
-Then, under appropriate specification of $\mathbf{k}$ and a proper schedule of $\set{r_n}_{n \in N}$, convergence of clusters output by spectral (and other) algorithms to the corresponding minima of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.
-
-These continuous analogues, and their corresponding minimizers, are not always easily identifiable for the particular density function under consideration.
-Relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
-\textcolor{red}{Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.} We formalize this intuition next.
+Then, under appropriate specification of $k$ and a proper schedule of $(r_n)$, convergence of clusters output by spectral (and other) algorithms to the corresponding minima of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.
 
@@
 \begin{equation}
-\mathbf{k}(x,x') = \1(\norm{x - x'} \leq r)
+k(x,x') = \1(\norm{x - x'} \leq r)
 \end{equation}
@@
 \begin{equation}
-G_{n,r} = (\x, E_{n,r}), \text{  $(x_i,x_j) \in E_{n,r}$ if $\mathbf{k}(x_i,x_j) = 1$}
+\label{eqn: neighborhood_graph}
+G_{n,r} = (\Xbf, E_{n,r}), \text{  $(x_i,x_j) \in E_{n,r}$ if $k(x_i,x_j) = 1$}
 \end{equation}
-For a given high density cluster $C \subseteq \mathbb{C}_f(\lambda)$, we call $C[\x] = C \cap \x$ the \textit{empirical density cluster}.
+For a given high density cluster $\Cset \subseteq \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \textit{empirical density cluster}.
 We now introduce a notion of consistency for the task of density cluster estimation:
@@
 \begin{definition}[Consistent density cluster estimation]
-	For an estimator $\widehat{C}_n$, and any $C, C' \in C_f(\lambda),$ we say $\widehat{C}_n$ is a consistent estimator of $C$ if the following statement holds: as the sample size $n \to \infty$,
+	For an estimator $\widehat{\Cset}_n \subset \Xbf$, and any $\Cset, \Cset' \in \Cbb_f(\lambda),$ we say $\widehat{\Cset}_n$ is a consistent estimator of $\Cset$ if the following statement holds: as the sample size $n \to \infty$, each of the following
 	\begin{equation}
-	C[\x] \subseteq \widehat{C}_n, ~\mathrm{ and }~ \widehat{C}_n \cap C'[\x] = \emptyset
+	\label{eqn: consistent_density_cluster_recovery}
+	\Cset[\Xbf] \subseteq \widehat{\Cset}_n, ~\mathrm{ and }~ \widehat{\Cset}_n \cap \Cset'[\Xbf] = \emptyset
 	\end{equation}
-	occurs with probability tending to $1$.
+	occur with probability tending to $1$.
 
@@
 	\item 
-	Under a natural set of geometric conditions\footnote{We formally introduce the geometric conditions in \ref{sec: measures_of_cluster_quality}.
-They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large}, Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2} upper and lower bound, respectively, the normalized cut and inverse mixing time of an empirical density cluster $C[\x]$.
+	Under a natural set of geometric conditions\footnote{We formally introduce the geometric conditions in Section \ref{sec: background}.
+They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large}, the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$ can be bounded.
+Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2} provide an upper and lower bound, respectively
 
 	\item 
-	We show these bounds on the graph connectivity criteria have algorithmic consequences for the PPR algorithm.
-An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{C}_n$ output by Algorithm \ref{alg: ppr_cluster}, as well as upper bounding the symmetric set difference between $\widehat{C}_n$ and $C[\x]$.
-Further, in Section 4 we show that a careful analysis of the form typical to local clustering algorithms yields \textcolor{red}{Theorem 4}, which states that Algorithm \ref{alg: ppr_cluster}, properly initialized, performs consistent density cluster estimation.
+	We show these bounds on the graph connectivity criteria have algorithmic consequences personalized PageRank.
+An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{\Cset}_n$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{\Cset}_n$ and $\Cset[\Xbf]$.
+Furthermore, in \textcolor{red}{Section 4} we show that a careful analysis of the form typical to local clustering algorithms yields \textcolor{red}{Theorem 4}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
 \end{enumerate}
@@
 In Section \ref{section: everything_else}, we provide some example density functions, to clarify the relevance of our results.
-In \textcolor{red}{Section 5}, we show empirical performance of the PPR algorithm, which demonstrates that violations of the geometric conditions we set out in Section \ref{sec: measures_of_cluster_quality} manifestly impact density cluster recovery (i.e.
-the conditions are not superfluous), before concluding in \textcolor{red}{Section 6}.
+In \textcolor{red}{Section 6}, we show empirical performance of the PPR algorithm, which demonstrates that violations of the geometric conditions we set out in Section \ref{sec: measures_of_cluster_quality} manifestly impact density cluster recovery (i.e.
+the conditions are not superfluous), before concluding in \textcolor{red}{Section 7}.
 First, however, we summarize some related work.
+
 \subsection{Related Work}
+In addition to the background given above, a few related lines of work are worth highlighting.
 
-\paragraph{Graph notation.}
+Global spectral clustering 
+methods were first developed in the context of graph partitioning \cite{fiedler1973,donath1973} 
+and their performance is well-understood in this context (see, for instance, \cite{tolliver2006,luxburg2007}).
+In a similar vein, several recent works \citep{mcsherry2001,lei2015,rohe2011,abbe2018,kamalika2012,balakrishnan2011} have studied the efficacy of spectral methods
+in successfully recovering the community structure in various variants of the
+stochastic block model.
 
-Let $G = (V,E)$ be an undirected, unweighted graph, with $S,S' \subseteq V$.
-The volume of $S$ is given by $\vol(S; G) = \sum_{v \in S} \deg(v; G) $
-where $\deg(v; G) = \sum_{u \in V} 1\bigl((u,v) \in E\bigr)$ is the degree of $v$ in $G$.
-For the random walk over $G$, denote the stationary distribution by $\pi$, where $\pi(S; G) = \frac{\vol(S ; G)}{\vol(V; G)}$.
+Building on the work of \citet{koltchinskii2000} the works \citep{vonluxburg2008,hein2005} for instance, have studied the limiting behaviour of spectral clustering algorithms.
+These works show that when samples are obtained from a distribution, following
+appropriate graph construction, in certain cases the spectrum of the Laplacian 
+converges to that of the Laplace-Beltrami operator on the data-manifold.
+However, relating the partition obtained using the Laplace-Beltrami operator, to 
+the 
+more intuitively defined high-density clusters, can be challenging in general.
 
-\vspace{.05 in}
+Perhaps most similar to our results are \citep{vempala2004,shi2009,schiebinger2015}, 
+which study the consistency of spectral algorithms in recovering the latent labels in certain 
+parametric and non-parametric mixture models.
+These results focus on global rather than local algorithms, and as such impose global rather than local conditions on the nature of the density.
+Moreover, they do not in general ensure recovery of density clusters which is a focus of our work.
 
-For the sample $\mathbf{X} := \set{x_1, \ldots, x_n} \subset \Rd$ and a set $A \subset \Rd$, define $A[\mathbf{X}] = A \cap \mathbf{X}$. We denote the uniform measure over $\Rd$ by $\nu(\cdot)$.
+\section{Background and Assumptions.}
+\label{sec: background}
 
-\section{Measures of cluster quality}
-\label{sec: measures_of_cluster_quality}
-
-Let $P$ be a distribution supported on a compact set $\mathcal{X} \subset \Rd$, with continuous density function $f$ (with respect to the uniform measure).
-The Euclidean distance is denoted by $\norm{ \cdot }$.
-
-\paragraph{Density upper-level set.}
-For a number $\tau \geq 0$, let $C_f(\tau)$ be the collection of collected components of the density upper-level set $\set{x \in \mathcal{X}: f(x) \geq \tau}$.
-Define a \textit{$\tau$-density cluster} to be one such connected component $A \in C_f(\tau)$.
-We will sometimes refer to $A[\bf{X}]$ as an \textit{empirical density cluster}.
-
-\paragraph{Graph bicriteria.}
-For $G = (V,E)$ an undirected, unweighted graph and $S, S' \subset V$ as before, let $\abs{E(S, S'; G)}$ denote the cut of $S$ and $S'$, given by
-\begin{equation*}
-\abs{E(S, S'; G)} = \sum_{v \in S} \sum_{u \in S'} 1((v,u) \in E).
-\end{equation*}
-Define the balance $B(S; G)$ to be
-\begin{equation*}
-B(S; G) = \min\{\vol(S;G), \vol(V \setminus S;G)\}.
-\end{equation*}
-
-We can now formally introduce our first criterion for assessing the quality of graph cuts: the \textbf{conductance}, $\Phi$, given by
-\begin{equation}
-\label{eqn: conductance}
-\Phi(S; G) \defeq \frac{\abs{E(S, V \setminus S; G)}}{B(S; G)}.
-\end{equation}
-We typically seek a set $S^{\star} \subset V$ such that $\Phi(S^{\star}; G)$ is small.
-
-\paragraph{Neighborhood graph.}
-
-Given $r \geq 0$, define the neighborhood graph to be $G_{n,r} = (\mathbf{X}, E_n)$, where for $x_i, x_j \in \mathbf{X}$, $(x_i, x_j) \in E_n$ if $\norm{x_i - x_j} \leq r$.
-(By convention, we do not allow loops, meaning $(x_i, x_i) \not\in E_n$).
-For ease of notation, for $S \subset \mathbf{X}$, let $\Phi_{n,r}(S) := \Phi(S; G_{n,r})$.
+We begin by introducing an defining well-conditioned density clusters before turning to formally define the PPR algorithm under consideration, Algorithm \ref{alg: ppr}, and discussing the choice of tuning-parameters.
 
@@
 
-In order to satisfy the \textcolor{red}{bicriteria}, we must introduce some assumptions on the density $f$.
-Let $B(x,r)$ be a closed ball with respect to Euclidean distance) of radius $r$ around the point $x$.
-Given a set $A \subset \Rd$, and a number $\sigma > 0$, define the set $\Asig = A + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in A} \norm{y - x} \leq \sigma}$.
+In order to provide meaningful bounds on the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$, we must introduce some assumptions on the density $f$.
+
+Let $B(x,r) = \set{y \in \Rd: \norm{y - x} \leq r}$ be a closed ball of radius $r$ around the point $x$.
+Given a set $\Aset \subset \Rd$, and a number $\sigma > 0$, define the set $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
+The assumptions we require are as follows:
 \begin{enumerate}[label=(A\arabic*)]
 	\item 
-	\label{asmp: cluster_regularity}
-	\textit{Minimum density:} For numbers $\sigma, \tau_{\sigma} > 0$, a set $A \subset \mathcal{X}$ is said to be \textit{$(\sigma, \tau_{\sigma})$-regular} if
+	\label{asmp: min_density}
+	\textit{Minimum density:} For numbers $\sigma, \lambda_{\sigma} > 0$, a set $\Aset \subset \Rd$ is said to be \textit{$(\sigma, \lambda_{\sigma})$-regular} if
 	\begin{equation}
-	\inf_{x \in \Asig} f(x) = \tau_{\sigma}
+	\inf_{x \in \Asig} f(x) = \lambda_{\sigma}
 	\end{equation} 
@@
 	\label{asmp: low_noise_density}
-	\textit{Low noise density:} For numbers $\gamma, \sigma > 0$, and a set $A \subset \mathcal{X}$, the density function $f$ is said to be \textit{$(\gamma, \sigma)$- low noise around $A$} if there exists a constant $C_1$ such that for all $x \in \mathcal{X}$ with $0 < \rho(x, \Asig) \leq \sigma$,
+	\textit{Low noise density:} For numbers $\gamma, \sigma > 0$, and a set $\Aset \subset \Rd$, the density function $f$ is said to be \textit{$(\gamma, \sigma)$- low noise around $\Aset$} if there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \rho(x, \Asig) \leq \sigma$,
 	\begin{equation*}
-	\inf_{x' \in \Asig} f(x') - f(x) \geq C_1 \rho(x, \Asig)^{\gamma}.
+	\inf_{x' \in \Asig} f(x') - f(x) \geq c_1 \rho(x, \Asig)^{\gamma},
 	\end{equation*}
@@
 	\textit{Cluster separation:}
-	For $\tau,\sigma > 0$, $C_f(\tau)$ the set of connected components of the density upper-level set is said to be \textit{$\sigma$-well separated} if for all $\tau$-density clusters $A, A' \in C_f(\tau)$,
+	For $\lambda,\sigma > 0$, $\Cset \in \Cbb_f(\lambda)$ is said to be \textit{$\sigma$-well separated} if for all $\Cset' \in \Cbb_f(\lambda)$,
 	\begin{equation*}
-	\rho(A,A') > \sigma.
+	\rho(\Cset,\Cset') > \sigma.
 	\end{equation*}
-	where $\rho(A,A') = \min_{x \in A, x' \in A'} \norm{x - x'}$.
+	where $\rho(\Cset,\Cset') = \min_{x \in \Cset} \rho(x,\Cset')$,
 \end{enumerate}
 
-\textcolor{red}{Assumptions are standard, provide references.} We note that these assumptions are all local in nature, further motivating the study of a local algorithm.
-Assumptions \ref{asmp: cluster_regularity}-\ref{asmp: cluster_separation} are used to upper bound \textcolor{red}{bicriteria 1}, whereas \ref{asmp: cluster_regularity} and \textcolor{red}{(A4)} are necessary to lower bound \textcolor{red}{bicriteria 2}.
+Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: min_density} and \textcolor{red}{(A4)} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
+We note that \ref{asmp: min_density} and \ref{asmp: cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of \cite{chaudhuri2010}, a standard density clustering assumption, while \ref{asmp: low_noise_density} is seen in, for instance, \cite{singh2009}, (as well as many other works on density clustering and level set estimation.) Further, it is worth highlighting that these assumptions are all local in nature, a benefit of studying a local algorithm such as PPR.
 
 \begin{definition}
-	For $\tau > 0$ and $A \in C_f(\tau)$ a $\tau$-density cluster, we say that $A$ is a \textit{$(\lambda, \sigma, \gamma)$-well-conditioned cluster} if $A$ is $(\lambda,\sigma)$-regular, the density $f$ is $(\gamma, \sigma)$-low noise around $A^{\sigma}$, and $C_f(\tau)$ is $\sigma$-well separated.
+	For $\lambda > 0$ we say $\Cset \in \mathbb{C}_f(\lambda)$ is a $(\lambda_{\sigma}, \gamma, \sigma)$-well conditioned cluster if it satisfies Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation}, for some $\lambda_{\sigma}, \gamma, \sigma > 0$.
 \end{definition}
-We note that $\sigma$ plays dual roles here, both in effect precluding arbitrarily narrow and long clusters in \ref{asmp: cluster_regularity} and arbitrarily flat densities in \ref{asmp: low_noise_density}.
-\textcolor{red}{We give some examples of densities which satisfy these assumptions in Section \ref{section: everything_else}.}
+We note that $\sigma$ plays dual roles here, both in effect precluding arbitrarily narrow and long clusters in \ref{asmp: min_density} and arbitrarily flat densities in \ref{asmp: low_noise_density}.
 
+\subsection{Algorithm under consideration.}
+
+Algorithm \ref{alg: ppr} will be the simple procedure we analyze.
+It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\vol_0$, and $v \in \Xbf$, and perform the following steps:
+
+\begin{algorithm}
+	\caption{PPR on a neighborhood graph}
+	\label{alg: ppr}	
+	{\bfseries Input:} data $\Xbf$, radius $r$, teleportation parameter $\alpha \in [0,1]$, seed node $v \in \Xbf$, target volume $\vol_0$. \\
+	{\bfseries Output:} $\widehat{C} \subset V$.
+	\begin{algorithmic}[1]
+		\STATE Form the neighborhood graph $G_{n,r}$ as given in (\ref{eqn: neighborhood_graph})
+		\STATE Compute PPR vector $\pbf(v, \alpha; G_{n,r})$  as defined by (\ref{eqn: ppr_vector}).
+		\STATE For $\beta \in [\frac{1}{8}, \frac{1}{2}]$ compute sweep cuts $S_{\beta}$ as defined by (\ref{eqn: sweep_cuts}).
+		\STATE Return
+		\begin{equation*}
+		\label{eqn: sweep_cuts_min_conductance}
+		\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G_{n,r})
+		\end{equation*}
+	\end{algorithmic}
+\end{algorithm}
+
+As is typical in the local clustering literature, our results will be stated with respect to specific choices or ranges of each of the user-specified parameters, which in this case may depend on the underlying (unknown) density.
+
+\textcolor{red}{Define a well-initialized PPR algorithm}
+
+\textcolor{red}{Make clear via assumption that throughout we require the algorithm to be well-initialized.}
+
+For notational simplicity, hereafter for $S \subseteq \Xbf$ we will refer to $\Phi(S; G_{n,r})$ as $\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$.
 \section{Local Clustering on Density Level Sets}
 
-In this section we show that a well-conditioned cluster $A$ satisfies the bicriteria \textcolor{red}{criteria 1} and \textcolor{red}{criteria 2}, and therefore the \textcolor{red}{PPR algorithm} outputs a low conductance set  which has small symmetric set difference with the empirical cluster.
+In this section we provide bounds for the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$.
+As a result we can lower bound $\Phi(\widehat{C}; G_{n,r})$ for $\widehat{C}$ the output of a well-initialized \textcolor{red}{PPR algorithm}, and lower bound the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
 
@@
 	\label{thm: conductance_upper_bound}
-	For some $\tau > 0$, let a $\tau$-density cluster $A \in C_f(\tau)$ satisfy Assumptions \ref{asmp: cluster_regularity}-\ref{asmp: cluster_separation} for some $\sigma, \tau_{\sigma}, \gamma > 0$.
+	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation} for some $\sigma, \lambda_{\sigma}, \gamma > 0$.
 Then, for any $r < \sigma$ and $\delta > 0$, the following statements hold with probability at least $1 - \delta$:
@@
 		\label{eqn: conductance_sample_complexity}
-		n \geq \log(2/\delta)\left(\frac{1 + \epsilon/2}{2 \tau_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
+		n \geq \log(2/\delta)\left(\frac{1 + \epsilon/2}{2 \lambda_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
 		\end{equation}
@@
 		\label{eqn: conductance_additive_error_bound}
-		\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \leq C_{\sigma} \frac{\tau}{\tau_{\sigma}} \frac{(\tau_{\sigma} - \frac{r^{\gamma+1}}{\gamma+1})}{\tau_{\sigma}} + \epsilon
+		\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \leq c_{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
 		\end{equation}
@@
 	\end{itemize}
-	where $C_0 = 2^{2d+1}d$ and $C_{\sigma} = C_0 / \sigma$. 
+	where $c_0 = 2^{2d+1}d$ and $c_{\sigma} = c_0 / \sigma$. 
 \end{theorem}
 
-A few remarks are in order. 
+The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other theorems, can be found in the supplementary document. A few remarks are in order. 
 \begin{remark}
@@
 It is possible to improve this dependency to the order of $(1 + \frac{r}{\sigma})^{2d}$.
-However, in this setting, we think of $r$ as being a constant radius (rather than $r = r_n \to 0$ as $n \to \infty$, and therefore even this improvement results in exponential dependency on the dimension $d$.
-\textcolor{red}{Make references suggesting this type of exponential dependency is not uncommon in non-parametric clustering problems.}
+However, in this setting, we think of $r$ as being a constant radius (rather than $r = r_n \to 0$ as $n \to \infty$, and therefore even this improvement still retains an exponential dependency on the dimension $d$.
 \end{remark}
 \begin{remark}
-	Other than the looseness implied by Remark \ref{rem: exp_in_d}, the error bound of (\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
+	Aside from the looseness implied by Remark \ref{rem: exp_in_d}, the error bound of (\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
 	\begin{align*}
@@
 	 \begin{cases}
-	 \tau \text{ for $x \in \Asig$}, \\
-	  f(x) = \tau - \rho(x,\Asig)^{\gamma} \text{ for $0 < \rho(x,\Asig) < r$}
+	 \lambda \text{ for $x \in \Asig$}, \\
+	 \lambda - \rho(x,\Asig)^{\gamma} \text{ for $0 < \rho(x,\Asig) < r$}
 	 \end{cases}
 	\end{align*}
-	we have
+	we have that for $n$ within constant order of the lower bound in (\ref{eqn: conductance_sample_complexity}), with probability at least $1 - \delta$
 	\begin{equation}
-	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq C_1 \frac{(\tau - \frac{r^{\epsilon+1}}{\epsilon+1})}{\tau}
+	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c_1 \frac{(\lambda - \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon
 	\end{equation}
-	for some constant $C_1$, with probability at least $1 - \delta$.
+	for some constant $c_1$ which depends only on dimension.
 (Note that a factor of $1 / \sigma$ is not (\ref{eqn: conductance_additive_error_bound}) replicated in this lower bound.) \textcolor{red}{Provide justification in supplement, and cite it.}
 \end{remark}
+
+We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
+\begin{theorem}
+	For $c_d$ a constant which may depend only on the dimension $d$,
+	\begin{equation*}
+	\Psi_{n,r}(\Cset[\Xbf]) \leq c_d \frac{\sigma^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
+	\end{equation*}
+\end{theorem}
 

### 2019-01-11 icml/icml_local_density_clustering_supplement.tex
related work complete; theorem 2 added

@@
 	 & = \int_{0}^{1} \frac{rd}{\sigma} (1 + \frac{r t}{\sigma})^{d-1} (\tau_{\sigma} - (rt)^{\gamma}) dt \\
-	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
+	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma }}{\gamma + 1}\right)
 	\end{align*}
@@
 	\begin{equation*}
-	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
+	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
 	\end{equation*}
@@
 	& \overset{(i)}{\leq} 2 \int_{\Asigr} f(x) \nu_d r^d \tau dx \\
-	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right) 
+	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right) 
 	\end{align*}

### 2019-01-12 icml/icml_local_density_clustering.tex
finished results, abstract, and discussion; added outline for examples

@@
 \newcommand{\defeq}{\overset{\mathrm{def}}{=}}
-\newcommand{\vol}{\text{vol}}
+\newcommand{\vol}{\mathrm{vol}}
 \newcommand{\cut}{\mathrm{cut}}
@@
 \newcommand{\1}{\mathbf{1}}
+\newcommand{\Phibf}{\mathbf{\Phi}}
+\newcommand{\Psibf}{\mathbf{\Psi}}
 
@@
 \newcommand{\Asig}{\Aset_{\sigma}}
+\newcommand{\Csig}{\Cset_{\sigma}}
 
@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+
+%%% Algorithm notation
+\newcommand{\ppr}{{\sc PPR}}
+\newcommand{\pprspace}{{\sc PPR~}}
 
@@
 \newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 
@@
 \begin{abstract}
+	Spectral clustering methods are 
+	a family of popular non-parametric clustering tools.
+	Recent works have proposed and analyzed 
+	\emph{local} spectral methods, which 
+	extract clusters using
+	locally-biased random walks around a user-specified seed node, and are known to have worst-case guarantees for certain graph-based measures of cluster quality.
+	In contrast to existing works, 
+	we analyze the personalized PageRank (\ppr) algorithm in the classical statistical learning setup,
+	where we obtain samples from an unknown distribution, and aim to identify connected
+	regions of high-density (density clusters).
+	With respect to a neighborhood graph formed over these samples, we provide guarantees for a pair of cluster quality criteria evaluated on empirical analogues to these density clusters.
+As a result, the \pprspace algorithm is shown to
+	extract sufficiently salient density clusters, and we 
+	analyze the sample-complexity of the algorithm.
 \end{abstract}
@@
 
-Roughly speaking, spectral clustering techniques first embed the data $\Xbf$ using the spectrum of the graph Laplacian matrix and subsequently 
+Roughly speaking, spectral clustering techniques first embed the data $\Xbf$ using the spectrum of the graph Laplacian, and subsequently 
 use this \emph{spectral embedding} to find a clustering of the data.
@@
 methods can be computationally cumbersome and 
-can be insensitive to the local geometry of the distribution of the samples
+insensitive to the local geometry of the distribution of the samples
 \citep{mahoney2012,leskovec2010}.
@@
 
-For $\Wbf$ as before, let the graph $G  = (V,E)$, with vertices $V = \set{v_1, \ldots, v_n}$ corresponding to the $n$ rows of $\Abf$, and (possibly weighted) edges $E = \set{(v_i,v_j,\Abf_{ij}): 1 \leq i < j \leq n, \Abf_{ij} > 0}$ (Since $\Abf$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops, hence $i \neq j$).
-There are many \cite{yang2015,fortunato2010} graph-theoretic measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
+For $\Abf$ as before, consider the graph $G  = (V,E)$, with vertices $V = \set{v_1, \ldots, v_n}$ corresponding to the $n$ rows of $\Abf$, and (possibly weighted) edges $E = \set{(v_i,v_j,\Abf_{ij}): 1 \leq i < j \leq n, \Abf_{ij} > 0}$ (Since $\Abf$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops, hence $i \neq j$).
+There are many \cite{yang2015,fortunato2010} graph-based measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
 
@@
 \end{equation*}
-Then, the \textit{normalized cut} of $S$ is given by
+Then, the \emph{normalized cut} of $S$ is given by
 \begin{equation}
@@
 Given $S \subseteq V$, the subgraph induced by $S$ is given by $G[S] = (S, E_S)$, where $(u,v) \in E_S$ if both $u$ and $v$ are in $S$ and $(u,v) \in E_S$.
-Letting $\abs{S} = m$, $\Abf_S$ then denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, only over $G[S]$.)
+Letting $\abs{S} = m$, $\Abf_S$ then denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, defined only over $G[S]$.)
 
 Our internal connectivity parameter $\Psi(S)$ will capture the time it takes for the random walk governed by $\Wbf_S$ to mix (that is, approach a stationary distribution) uniformly over $S$.
-Denoting the stationary distribution $\widetilde{\pibf} = (\widetilde{\pi}_{1}, \ldots, \widetilde{\pi}_{m})$, the \textit{relative pointwise mixing time} $\tau_{\infty}(S; G[S])$ of the random walk over $G[S]$ defined by $\Wbf_S$ is the smallest integer $t_0 > 0$ such that for all $v = v_i,v' = v_j \in S$:
+Denoting the stationary distribution of this random walk by $\widetilde{\pibf} = (\widetilde{\pi}_{1}, \ldots, \widetilde{\pi}_{m})$, the \emph{relative pointwise mixing time} $\tau_{\infty}(S; G[S])$ is defined to be: the smallest integer $t_0 > 0$ such that for all $v = v_i,v' = v_j \in S$:
 \begin{equation*}
@@
 for all $t > t_0$
-\footnote{Given a seed node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.} (Of course, given the definition of $\Wbf_S$ it is well known that the stationary distribution $\pibf_S$ will be defined by $\widetilde{\pi}_{i} = (\Dbf_{S})_{ii} / \vol(S; G[S])$.
+\footnote{Given a starting node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.} (Of course, given the definition of $\Wbf_S$ it is well known that the stationary distribution $\pibf_S$ will be defined by $\widetilde{\pi}_{i} = (\Dbf_{S})_{ii} / \vol(S; G[S])$.
 
@@
 If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no less than $\Psi$, we will refer to it as a $(\Phi,\Psi)$-cluster.
-Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been shown to output clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition), where the optimization is carried out over the graph $G$.
+Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been shown to output clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition) for a given graph $G$.
 \footnote{In the case of \cite{kannan04}, the internal connectivity parameter $\phi$ is actually the conductance, i.e.
@@
 As mentioned previously, global algorithms which find spectral cuts may be computationally infeasible for large graphs; in this setting, local algorithms may be preferred or even required.
-We will restrict our attention in particular to one such popular algorithm: \textit{personalized PageRank} (PPR).
+We will restrict our attention in particular to one such popular algorithm: \emph{personalized PageRank} (\ppr).
 The personalized PageRank algorithm was first introduced by \cite{haveliwala2003} and variants of this algorithm have been studied further in several recent works \citep{spielman2011,spielman2014,zhu2013,anderson2006,mahoney2012}.
 
-The random walk matrix $\Wbf$ over the graph $G = (V,E)$ with associated adjacency matrix $\Abf$ is defined as in (\ref{eqn: random_walk_laplacian}).
-PPR is then defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
-Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \textit{PPR vector} is given by the recursive formulation
+The random walk matrix $\Wbf$ over the graph $G = (V,E)$ with associated adjacency matrix $\Abf$ is given by (\ref{eqn: random_walk_laplacian}).
+\pprspace is then defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
+Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \emph{PPR vector} is given by the recursive formulation
 \begin{equation}
@@
 
-To compute a cluster $\widehat{C} \subset V$ using the PPR vector, we will take sweep cuts of $\pbf(v, \alpha; G)$.
-Denote the entries of $\pbf(v, \alpha; G)$ by $\pbf(v, \alpha; G) = (p_1, \ldots, p_n)$, and let the \textit{stationary distribution} $\pibf$ of the random walk defined by $\Wbf$ be given by
+To compute a cluster $\widehat{C} \subset V$ using the \pprspace vector, we will take sweep cuts of $\pbf(v, \alpha; G)$.
+Denote the entries of $\pbf(v, \alpha; G)$ by $\pbf(v, \alpha; G) = (p_1, \ldots, p_n)$, and let the \emph{stationary distribution} $\pibf$ of the random walk defined by $\Wbf$ be given by
 \begin{equation*}
@@
 \end{equation}
-One such sweep cut will be our chosen cluster $\widehat{C}$.  
-(We delay formal introduction of the local clustering algorithm we analyze until \textcolor{red}{Section 2}, after we have given a method for forming a graph over the data $\Xbf$.)
+We will choose one such sweep cut to be our cluster estimate $\widehat{C}$.  
+(We delay formal introduction of the local clustering algorithm we analyze until \ref{sec: background}, after we have given a method for forming a graph over the data $\Xbf$.)
 
@@
 
-It is worth pointing out that in this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence of finite sample graph-theoretic functionals to their continuous counterparts has been shown
+In this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence of finite sample graph-theoretic functionals to their continuous counterparts has been shown
 \cite{garciatrillos16, arias-castro12, maier11}.
@@
 Of course, relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
-\textcolor{red}{Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.} We formalize this intuition next.
+Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.
+We formalize this intuition next.
 
@@
 
-Hereafter, we consider the \textit{uniform kernel function} for a fixed $r > 0$,
+Hereafter, we consider the uniform kernel function for a fixed $r > 0$,
 \begin{equation}
@@
 \end{equation}
-and the associated \textit{neighborhood graph} 
+and the associated neighborhood graph
 \begin{equation}
@@
 \end{equation}
-For a given high density cluster $\Cset \subseteq \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \textit{empirical density cluster}.
+For a given high density cluster $\Cset \subseteq \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}.
 We now introduce a notion of consistency for the task of density cluster estimation:
@@
 \begin{definition}[Consistent density cluster estimation]
+	\label{def: consistent_density_cluster_estimation}
 	For an estimator $\widehat{\Cset}_n \subset \Xbf$, and any $\Cset, \Cset' \in \Cbb_f(\lambda),$ we say $\widehat{\Cset}_n$ is a consistent estimator of $\Cset$ if the following statement holds: as the sample size $n \to \infty$, each of the following
@@
 	\item 
-	We show these bounds on the graph connectivity criteria have algorithmic consequences personalized PageRank.
-An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{\Cset}_n$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{\Cset}_n$ and $\Cset[\Xbf]$.
-Furthermore, in \textcolor{red}{Section 4} we show that a careful analysis of the form typical to local clustering algorithms yields \textcolor{red}{Theorem 4}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
+	We show these bounds on the graph connectivity criteria have algorithmic consequences for personalized PageRank.
+An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{C}$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
+Furthermore, in \ref{sec: consistent_cluster_estimation_with_ppr} we show that a careful analysis of the form typical to local clustering algorithms yields Theorem \ref{thm: consistent_recovery_of_density_clusters}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
 \end{enumerate}
@@
 \paragraph{Organization.}
-In Section \ref{section: everything_else}, we provide some example density functions, to clarify the relevance of our results.
-In \textcolor{red}{Section 6}, we show empirical performance of the PPR algorithm, which demonstrates that violations of the geometric conditions we set out in Section \ref{sec: measures_of_cluster_quality} manifestly impact density cluster recovery (i.e.
-the conditions are not superfluous), before concluding in \textcolor{red}{Section 7}.
+In Section \ref{section: examples}, we provide some example density functions, to clarify the relevance of our results, and empirically demonstrate that violations of the geometric conditions we set out in Section \ref{sec: background} manifestly impact density cluster recovery (i.e.
+the conditions are not superfluous), before concluding in \ref{sec: discussion}.
 First, however, we summarize some related work.
@@
 Let $B(x,r) = \set{y \in \Rd: \norm{y - x} \leq r}$ be a closed ball of radius $r$ around the point $x$.
-Given a set $\Aset \subset \Rd$, and a number $\sigma > 0$, define the set $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
-The assumptions we require are as follows:
+Given a set $\Aset \subset \Rd$, and a number $\sigma > 0$, define the $\sigma$-expansion of $\Aset$ to be $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
+We are now ready to give the assumptions, which we state with respect to a density cluster $\Cset \in \Cbb_f(\lambda)$ for some $\lambda > 0$, and expansion parameter $\sigma > 0$:
 \begin{enumerate}[label=(A\arabic*)]
 	\item
-	\label{asmp: min_density}
-	\textit{Minimum density:} For numbers $\sigma, \lambda_{\sigma} > 0$, a set $\Aset \subset \Rd$ is said to be \textit{$(\sigma, \lambda_{\sigma})$-regular} if
+	\label{asmp: bounded_density}
+	\textit{Bounded density within cluster:} There exist numbers $0 < \lambda_{\sigma} <  \Lambda_{\sigma} < \infty$ such that:
 	\begin{equation}
-	\inf_{x \in \Asig} f(x) = \lambda_{\sigma}
+	\label{eqn: bounded_density}
+	\lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma} 
 	\end{equation} 
@@
 	\label{asmp: low_noise_density}
-	\textit{Low noise density:} For numbers $\gamma, \sigma > 0$, and a set $\Aset \subset \Rd$, the density function $f$ is said to be \textit{$(\gamma, \sigma)$- low noise around $\Aset$} if there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \rho(x, \Asig) \leq \sigma$,
+	\textit{Low noise density:} For some $\gamma > 0 $, there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \rho(x, \Csig) \leq \sigma$,
 	\begin{equation*}
-	\inf_{x' \in \Asig} f(x') - f(x) \geq c_1 \rho(x, \Asig)^{\gamma},
+	\inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \rho(x, \Csig)^{\gamma},
 	\end{equation*}
-	where $\rho(x,\Asig) = \min_{x_0 \in \Asig} \norm{x - x_0}$.
+	where $\rho(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subset \Rd$.
 
@@
 	\textit{Cluster separation:}
-	For $\lambda,\sigma > 0$, $\Cset \in \Cbb_f(\lambda)$ is said to be \textit{$\sigma$-well separated} if for all $\Cset' \in \Cbb_f(\lambda)$,
+	For all $\Cset' \in \Cbb_f(\lambda)$,
 	\begin{equation*}
-	\rho(\Cset,\Cset') > \sigma.
+	\rho(\Csig,\Csig') > \sigma,
 	\end{equation*}
-	where $\rho(\Cset,\Cset') = \min_{x \in \Cset} \rho(x,\Cset')$,
+	where $\rho(\Aset,\Aset') = \min_{x \in \Aset} \rho(x,\Aset')$ for $\Aset' \subset \Rd$.
+
+	\item
+	\label{asmp: cluster_diameter}
+	\textit{Cluster diameter:}
+	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
+	\begin{equation*}
+	\norm{x - x'} \leq D.
+	\end{equation*}
 \end{enumerate}
 
-Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: min_density} and \textcolor{red}{(A4)} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
-We note that \ref{asmp: min_density} and \ref{asmp: cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of \cite{chaudhuri2010}, a standard density clustering assumption, while \ref{asmp: low_noise_density} is seen in, for instance, \cite{singh2009}, (as well as many other works on density clustering and level set estimation.) Further, it is worth highlighting that these assumptions are all local in nature, a benefit of studying a local algorithm such as PPR.
+We note that $\sigma$ plays several roles here, precluding arbitrarily narrow clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
 
-\begin{definition}
-	For $\lambda > 0$ we say $\Cset \in \mathbb{C}_f(\lambda)$ is a $(\lambda_{\sigma}, \gamma, \sigma)$-well conditioned cluster if it satisfies Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation}, for some $\lambda_{\sigma}, \gamma, \sigma > 0$.
+Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
+We note that the lower bound on minimum density in (\ref{eqn: bounded_density}) and \ref{asmp: cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of \cite{chaudhuri2010}, a standard density clustering assumption, while \ref{asmp: low_noise_density} is seen in, for instance, \cite{singh2009}, (as well as many other works on density clustering and level set estimation.) It is worth highlighting that these assumptions are all local in nature, a benefit of studying a local algorithm such as PPR.
+
+Now we make the crucial distinction between the assumptions made in density clustering, and the stronger conditions we will require here. First, we introduce
+\begin{align*}
+\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
+\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \frac{\sigma^d}{D^d} \frac{\lambda_{\sigma}^7}{\Lambda_{\sigma}^7} \frac{1}{\log(\Lambda_{\sigma}^2/(\lambda_{\sigma} \sigma^d \nu_d))}.
+\end{align*}
+
+Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf$ and $\Psibf$.
+\begin{definition}[Well-conditioned density clusters]
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty.$ Letting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ be given by
+	\begin{align*}
+	\kappa_1(\Cset) & := \frac{\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma)}{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)} \\
+	\kappa_2(\Cset) & := \kappa_1(\Cset) \cdot \sqrt{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)},
+	\end{align*}
+	we call $\Cset$ a \textrm{$(\kappa_1, \kappa_2)$-well-conditioned density cluster (with respect to $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).}
 \end{definition}
-We note that $\sigma$ plays dual roles here, both in effect precluding arbitrarily narrow and long clusters in \ref{asmp: min_density} and arbitrarily flat densities in \ref{asmp: low_noise_density}.
+
+As the notation suggests, $\Phibf$ and $\Psibf$ are related to the graph connectivity criteria.
+In fact, as we will see in the next section, for well-conditioned density clusters they are exactly (up to constants) the bounds we derive.
 
@@
 
-Algorithm \ref{alg: ppr} will be the simple procedure we analyze.
-It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\vol_0$, and $v \in \Xbf$, and perform the following steps:
+Algorithm \ref{alg: ppr} will be the simple variant of PPR we analyze. It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\vol_0$, and $v \in \Xbf$.
 
@@
 
-\textcolor{red}{Define a well-initialized PPR algorithm}
+In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
+\begin{align}
+\label{eqn: initialization}
+\textcolor{red}{\alpha \in [1/2, 9/10] \cdot \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)}, & ~r \in [1/2,1]\cdot\sigma  \nonumber \\
+\vol_0 \in [1/2,1]\cdot\vol(\Csig[\Xbf]), & ~v \in \Csig[\Xbf]^g
+\end{align}
+where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
+(Intuitively one can think of $\Csig[\Xbf]^g$ as being the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.) We call a PPR algorithm run with hyperparameters satisfying (\ref{eqn: initialization}) \emph{well-initialized}.
 
-\textcolor{red}{Make clear via assumption that throughout we require the algorithm to be well-initialized.}
+\section{Local Clustering on Density Level Sets}
+\label{sec: local_clustering_on_density_level_set}
+
+In this section we provide bounds for the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$.
+As a result we can lower bound $\Phi(\widehat{C}; G_{n,r})$ for $\widehat{C}$ the output of a well-initialized \textcolor{red}{PPR algorithm}, and upper bound the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
 
 For notational simplicity, hereafter for $S \subseteq \Xbf$ we will refer to $\Phi(S; G_{n,r})$ as $\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$.
-\section{Local Clustering on Density Level Sets}
 
-In this section we provide bounds for the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$.
-As a result we can lower bound $\Phi(\widehat{C}; G_{n,r})$ for $\widehat{C}$ the output of a well-initialized \textcolor{red}{PPR algorithm}, and lower bound the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
-
+We begin with a lower bound on the normalized cut in Theorem \ref{thm: conductance_upper_bound}.
+We will require Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} to hold; however, the upper bound on density in (\ref{eqn: bounded_density}) will not be needed and so we omit the parameter $\Lambda_{\sigma}$ from the statement of the theorem.
 \begin{theorem}
 	\label{thm: conductance_upper_bound}
-	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: min_density}-\ref{asmp: cluster_separation} for some $\sigma, \lambda_{\sigma}, \gamma > 0$.
+	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} for some $\sigma, \lambda_{\sigma}, c_1, \gamma > 0$ .
 Then, for any $r < \sigma$ and $\delta > 0$, the following statements hold with probability at least $1 - \delta$:
@@
 		\label{eqn: conductance_sample_complexity}
-		n \geq \log(2/\delta)\left(\frac{1 + \epsilon/2}{2 \lambda_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
+		n \geq \frac{\log(2/\delta)}{\epsilon^2}\left(\frac{3}{2 \lambda_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
 		\end{equation}
@@
 	\end{itemize}
-	where $c_0 = 2^{2d+1}d$ and $c_{\sigma} = c_0 / \sigma$. 
+	where $c_0 = c_1 2^{2d+1}d$ and $c_{\sigma} = c_0 / \sigma$. 
 \end{theorem}
 
-The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other theorems, can be found in the supplementary document. A few remarks are in order. 
+The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other proofs, can be found in the supplementary document. A few remarks are in order. 
 \begin{remark}
@@
 It is possible to improve this dependency to the order of $(1 + \frac{r}{\sigma})^{2d}$.
-However, in this setting, we think of $r$ as being a constant radius (rather than $r = r_n \to 0$ as $n \to \infty$, and therefore even this improvement still retains an exponential dependency on the dimension $d$.
+However, as indicated by (\ref{eqn: initialization}), we will think of $r$ as being a constant radius of order $\sigma$ (rather than $r = r_n \to 0$ as $n \to \infty$) and therefore even this improvement still retains an exponential dependency on the dimension $d$.
 \end{remark}
@@
 	we have that for $n$ within constant order of the lower bound in (\ref{eqn: conductance_sample_complexity}), with probability at least $1 - \delta$
-	\begin{equation}
-	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c_1 \frac{(\lambda - \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon
-	\end{equation}
-	for some constant $c_1$ which depends only on dimension.
-(Note that a factor of $1 / \sigma$ is not (\ref{eqn: conductance_additive_error_bound}) replicated in this lower bound.) \textcolor{red}{Provide justification in supplement, and cite it.}
+	\begin{equation*}
+	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda - \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon
+	\end{equation*}
+	for some constant $c$ which depends only on dimension. (Note that a factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated in this lower bound.) For justification see the supplementary materials.
 \end{remark}
@@
 \begin{theorem}
-	For $c_d$ a constant which may depend only on the dimension $d$,
+	\label{thm: inverse_mixing_time_lower_bound}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
+Then, for any $r < \sigma$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
+Then for
 	\begin{equation*}
-	\Psi_{n,r}(\Cset[\Xbf]) \leq c_d \frac{\sigma^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
+	\textcolor{red}{n \geq }
 	\end{equation*}
+	we have
+	\begin{equation*}
+	\Psi_{n,r}(\Cset[\Xbf]) \geq c_d \frac{r^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
+	\end{equation*}
+	for \textcolor{red}{$c_d = (1 + \epsilon)$}.
 \end{theorem}
 
-\section{Implications, extensions, and discussion}
-\label{section: everything_else}
-\subsection{Examples}
-\subsection{Experiments}
+\paragraph{Approximate density cluster recovery with PPR.}
+
+In \cite{zhu2013}, building on the work of \cite{anderson2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
+We collect some of the main results of \cite{zhu2013} in Lemma \ref{lem: ppr_cluster}.
+
+For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
+\begin{lemma}[PPR clustering]
+	\label{lem: ppr_cluster}
+	There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix \textcolor{red}{$\alpha = 9 / 10 \Psi(A; G)$}, and compute the page rank vector $\pbf(v,\alpha; G)$.
+Letting
+	\begin{equation*}
+	\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G)
+	\end{equation*}
+	the following guarantees hold:
+	\begin{align*}
+	\vol(\widehat{C} \setminus A) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
+	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
+	\Phi(\widehat{C}; G) & = \textcolor{red}{O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)}
+	\end{align*}
+\end{lemma}
+
+Corollary \ref{cor: ppr_cluster} immediately follows.
+\begin{corollary}
+	\label{cor: ppr_cluster}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).
+Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the following guarantees hold for output set $\widehat{C} \subset \Xbf$:
+	\begin{align*}
+	\vol(\widehat{C} \setminus \Csig[\Xbf]), \vol(\Csig[\Xbf] \setminus \widehat{C})  & \leq 30 \kappa_1(\Cset) \vol(\Csig[X]) \\
+	\Phi_{n,r}(\widehat{C}) & = \textcolor{red}{O\left(\kappa_2(\Cset)\right)}
+	\end{align*}
+\end{corollary}
+
+\section{Consistent cluster estimation with PPR.}
+\label{sec: consistent_cluster_estimation_with_ppr}
+While Corollary \ref{cor: ppr_cluster} is nice, it does not imply consistency of the type laid out in Definition \ref{def: consistent_density_cluster_estimation}.
+
+However, a slightly more subtle argument regarding the way a random walk on $G_{n,r}$ distributes mass over $\Cset[\Xbf]$ and $\Cset'[\Xbf]$ will do the trick, yielding Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+\begin{theorem}
+\label{thm: consistent_recovery_of_density_clusters}
+Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), with
+\begin{equation}
+\label{eqn: kappa2_ub}
+\kappa_2 \leq \left(\frac{1}{5} - \frac{\epsilon}{4}\right) \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\sigma^d \nu_d}{\nu(\Csig)}
+\end{equation}
+for some $\epsilon > 0$.
+
+Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the output set $\widehat{C} \subset \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+\end{theorem}
+
+\begin{remark}
+	When $\lambda_{\sigma} = \Lambda_{\sigma}$ and $\nu(\Csig) = \sigma^d \nu_d$ -- in some sense, the `best' case given our assumptions -- the upper bound of (\ref{eqn: kappa2_ub}) reduces to $\kappa_2 \leq 1/5 - \epsilon/4$.
+That $\kappa_2 = O(1)$ is a minimal requirement for the bounds of Corollary \ref{cor: ppr_cluster} not to be facile; therefore, in this case the assumed upper bound of (\ref{eqn: kappa2_ub}) is not really a stricter requirement.
+\end{remark}
+\section{Examples}
+\label{section: examples}
+
+Example 1 is intended to show how the machinery developed above translates in a specific, common mixture model, and the extent to which bounds are (or are not) tight.
+Example 2 \textcolor{red}{will try to} delve into some of the details of how \pprspace interpolates the conductance and density cut, and will show a case where a poorly conditioned density cluster is not recovered by \pprspace.
+Example 3 will emphasize finite sample cluster recovery, for a well-conditioned but non-convex mixture model
+
+Examples 1 and 2 should be thought of as shedding light on the population performance of \ppr, whereas Example 3 shows performance on a finite sample.
+
+\begin{enumerate}
+	\item 
+	\textit{Gaussian Mixture Model:} 
+	We will compute optimal $\Phibf$ and $\Psibf$ for given $\lambda$, and show the following
+	\begin{itemize}
+		\item A graph comparing $\Phibf$ to $\Phi_{n,r}$ as the value of $\lambda$ changes.
+		\item A graph comparing $\Psibf$ to $\Psi_{n,r}$ as the value of $\lambda$ changes.
+		\item That for some values of $\lambda$, the conditions required for Theorem \ref{thm: consistent_recovery_of_density_clusters} hold.
+	\end{itemize}
+
+	\item
+	\textit{Thin and long parallel clusters, with $\epsilon$-uniform noise: }
+	We will \textcolor{red}{(try to)} show that the set outputted by \pprspace interpolates between the minimum normalized cut solution (fatter) and the density cluster (thinner).
+The \emph{conductance} is
+	\begin{equation*}
+	\Phi^{\star}(G_{n,r}) := \min_{C \subset \Xbf} \Phi_{n,r}(C)
+	\end{equation*}
+	and the conductance cut is $C^{\star} \subset \Xbf$ which achieves the minimum.
+
+	We will show that
+	\begin{itemize}
+		\item For sufficiently small $\epsilon$, all three of the conductance cut, \pprspace cut, and density cut agree.
+		\item For an intermediate value of $\epsilon$, the conductance cut and the density cut disagree. The \pprspace cut interpolates between the two.
+		\item For a sufficiently large value of $\epsilon$, the \pprspace cut fails to recover the density cut, and draws closer to the conductance cut.
+	\end{itemize}
+
+	\item 
+	\textit{Non-convex mixture model:} We will show that, for well-conditioned non-convex mixture model, and a finite sample size $n$, cluster recovery is achieved with high probability over repeated simulations.
+\end{enumerate}
+
+\section{Discussion}
+For a clustering algorithm and a given object (such as a graph or set of points), there are an almost limitless number of ways to define what the 'right' clustering is.
+We have considered a few such ways -- density level sets, and the bicriteria of normalized cut, inverse mixing time -- and shown that under the right conditions, the latter agree with the former, with resulting algorithmic consequences.
+
+There are still many directions worth pursuing in this area.
+Concretely, we might wish to generalize our results to hold over a wider range of kernel functions, and hyperparameter inputs to the \pprspace algorithm.
+More broadly, we do not provide any sort of theoretical lower bound, although we give empirical evidence in Example 2 that poorly conditioned density clusters are not consistently estimated by \pprspace.
+Example 2 also hints at a way of understanding local spectral algorithms -- or, at least, \ppr-- as interpolating between normalized and density cut.
+Exploring this connection is an avenue for future work.
 

### 2019-01-14 icml/icml_local_density_clustering.tex
completed proof of Theorem 1

@@
 Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \textit{external} and \textit{internal connectivity} of $S$, respectively.
-As the names suggest, external connectivity should relate to the number of edges between $S$ and its complement $G / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
+As the names suggest, external connectivity should relate to the number of edges between $S$ and its complement $V / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
 The graph clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
@@
 For notational simplicity, hereafter for $S \subseteq \Xbf$ we will refer to $\Phi(S; G_{n,r})$ as $\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$.
+We will also use $\nu(\cdot)$ to denote the uniform measure over $\Rd$, and $\nu_d = \nu\bigl(B(0,d)\bigr)$ as the measure of the unit ball.
 
@@
 	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} for some $\sigma, \lambda_{\sigma}, c_1, \gamma > 0$ .
-Then, for any $r < \sigma$ and $\delta > 0$, the following statements hold with probability at least $1 - \delta$:
-	\begin{itemize}
-		\item 
-		\textbf{Additive error bound.} Fix $\epsilon > 0$. Then, for
+Then, for any $r < \sigma$ and $\delta \in (0,1]$, the following statements hold with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
+Then, for
 		\begin{equation}
 		\label{eqn: conductance_sample_complexity}
-		n \geq \frac{\log(2/\delta)}{\epsilon^2}\left(\frac{3}{2 \lambda_{\sigma}^2 \nu(\Asig) \nu_d (r/2)^d}\right)^2 
+		n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}{ \lambda_{\sigma}^2 \nu(\Csig) \nu_d r^d}\right)^2 
 		\end{equation}
@@
 		\label{eqn: conductance_additive_error_bound}
-		\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \leq c_{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
+		\frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c_{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
 		\end{equation}
-		\item
-		\textcolor{red}{\textbf{Multiplicative error bound.}}
-	\end{itemize}
-	where $c_0 = c_1 2^{2d+1}d$ and $c_{\sigma} = c_0 / \sigma$. 
+	where $c_0 = 4d$ and $c_{\sigma} = c_0 / \sigma$. 
 \end{theorem}
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
-Then, for any $r < \sigma$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
+Then, for any $r < \sigma/4d$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
 Then for

### 2019-01-14 icml/icml_local_density_clustering_supplement.tex
completed proof of Theorem 1

@@
 
-\usepackage{icml2019}
+% \usepackage{icml2019}
 % \usepackage[accepted]{icml2019}
+
+\renewcommand{\thesection}{\Alph{section}}
+\renewcommand{\theequation}{A.\arabic{equation}}
 
@@
 \usepackage{booktabs}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \usepackage{amsmath}
@@
 \usepackage{xr-hyper}
-%\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+\usepackage{bm}
+\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
 
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\newcommand{\Asig}{A_{\sigma}}
-\newcommand{\Asigr}{A_{\sigma,\sigma + r}}
 \newcommand{\1}{\mathbf{1}}
@@
 \newcommand{\Err}{\mathrm{Err}}
+
+%%% Graph terms
+\newcommand{\cut}{\mathrm{cut}}
+
+%%% Vectors
+\newcommand{\pbf}{\mathbf{p}}
+\newcommand{\ebf}[1]{\mathbf{e}_{#1}}
+\newcommand{\pibf}{\bm{\pi}}
+
+%%% Matrices
+\newcommand{\Abf}{\mathbf{A}}
+\newcommand{\Xbf}{\mathbf{X}}
+\newcommand{\Wbf}{\mathbf{W}}
+\newcommand{\Lbf}{\mathbf{L}}
+\newcommand{\Dbf}{\mathbf{D}}
+\newcommand{\Ibf}[1]{\mathbf{I}_{#1}}
+
+%%% Probability distributions (and related items)
+\newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Cbb}{\mathbb{C}}
+\newcommand{\Ebb}{\mathbb{E}}
+
+%%% Sets
+\newcommand{\Cset}{\mathcal{C}}
+\newcommand{\Aset}{\mathcal{A}}
+\newcommand{\Asig}{\Aset_{\sigma}}
+\newcommand{\Csig}{\Cset_{\sigma}}
+\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
+\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}
+
+%%% Operators
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+%%% Algorithm notation
+\newcommand{\ppr}{{\sc PPR}}
+\newcommand{\pprspace}{{\sc PPR~}}
 
@@
 
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
+%\newcommand{\theHalgorithm}{\arabic{algorithm}}
 
-\icmltitlerunning{Local clustering of density upper level sets}
+%\icmltitlerunning{Local clustering of density upper level sets}
 
@@
 
-\twocolumn[
-\icmltitle{Supplement to ``Local clustering of density upper level sets''}
+%\twocolumn[
+%\icmltitle{Supplement to ``Local clustering of density upper level sets''}
 
-\icmlsetsymbol{equal}{*}
+%\icmlsetsymbol{equal}{*}
 
-\begin{icmlauthorlist}
-\icmlauthor{Alden Green}{cmu}
-\icmlauthor{Sivaraman Balakrishnan}{cmu}
-\icmlauthor{Ryan Tibshirani}{cmu}
-\end{icmlauthorlist}
+%\begin{icmlauthorlist}
+%\icmlauthor{Alden Green}{cmu}
+%\icmlauthor{Sivaraman Balakrishnan}{cmu}
+%\icmlauthor{Ryan Tibshirani}{cmu}
+%\end{icmlauthorlist}
 
-\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}
+%\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}
 
-\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
+%\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
 
-\icmlkeywords{local clustering}
+%\icmlkeywords{local clustering}
 
-\vskip 0.3in
-]
+%\vskip 0.3in
+%]
 
-\printAffiliationsAndNotice{} % otherwise use the standard text.
+%\printAffiliationsAndNotice{} % otherwise use the standard text.
+
+\section{Proofs}
 
@@
 
-\section{Technical Lemmas}
-For $A \subset \mathcal{X}$, let $P(A) = \mathbb{P}_{X \sim P}(X \in A)$.
-To simplify expressions, we will write $A_{\sigma, \sigma + r} := \set{x: 0 < \rho(x, \Asig) \leq r}$.
-We further let $\widetilde{\mathcal{E}} = \abs{E(\Asig[\mathbf{X}], \mathbf{X} \setminus \Asig[\mathbf{X}]; G_{n,r})}$ be the number of edges between $\Asig[\mathbf{X}]$ and $\mathbf{X} \setminus \Asig[\mathbf{X}]$ in the graph $G_{n,r}$; $\widetilde{\mu} = \mathbb{E}\left[\widetilde{\mathcal{E}}\right]$ be the expected number of such edges; and $\widetilde{p} = \widetilde{\mu} / {n \choose 2}$ the probability of any two vertices $x_i$ and $x_j$ having such an edge.
-Similarly, $\mathcal{V} = \vol(\Asig[\mathbf{X}]; G_{n,r})$ is the volume of $\Asig[\mathbf{X}]$; $\mu = \mathbb{E}\left[\mathcal{V}\right]$ is the expected volume; and $p = \mu / {n \choose 2}$.
-Finally, we denote $rB = B(0,r)$.
+Throughout, we will fix $\Aset \subset \Rd$ to be an arbitrary set.
+To simplify expressions, for the $\sigma$-expansion $\Asig$, we will write the set difference between $\Asig$ and the $(\sigma + r)$-expansion $\Aset_{\sigma + r}$ as
+\begin{equation*}
+\Asigr := \set{x: 0 < \rho(x, \Asig) \leq r},
+\end{equation*}
+where $\rho(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
+.
 
-\subsection{\textcolor{red}{Expected Values}}
+For notational ease, we write
+\begin{align*}
+\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
+\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}}
+\end{align*}
+for the random variable, mean, and probability of cut size and volume, respectively.
+
+\subsection{Technical Lemmas}
+
+We state Lemma \ref{lem: expansion_sets} without proof, as it is trivial.
+We formally include it mainly to comment on its (potential) suboptimality; for sets $\Aset$ with diameter much larger than $\sigma$, the volume estimate of Lemma \ref{lem: expansion_sets} will be quite poor.
+
 \begin{lemma}
-	\label{lem: expected_number_boundary_points}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
+	\label{lem: expansion_sets}
+	For any $\sigma > 0$ and the $\sigma$-expansion $\Asig = \Aset + \sigma B$, 
 	\begin{equation*}
-	P(A_{\sigma, \sigma + r}) \leq 2^{d-1} \nu(\Asig) \frac{rd}{\sigma}  \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
+	\sigma B \subset \Asig, ~~\mathrm{and~ }\nu(\Aset + \sigma B) \leq \nu((1 + \sigma)\Aset) = (1 + \sigma)^d \nu(\Aset).
+	\end{equation*}
+\end{lemma}
+
+We will need to carefully control the volume of the expansion set using the above estimate; Lemma \ref{lem: Taylor_series} serves this purpose.
+\begin{lemma}
+	\label{lem: Taylor_series}
+	For any $0 \leq x \leq 1/2d$,
+	\begin{equation*}
+	(1 + x)^d \leq 1 + 2dx.
+	\end{equation*}
+\end{lemma}
+The proof of Lemma \ref{lem: Taylor_series} is based on approximation via Taylor series, and we omit it.
+
+We will repeatedly employ Lemma \ref{lem: expansion_sets} and Lemma \ref{lem: Taylor_series} in tandem.
+As a first example, in Lemma \ref{lem: interior_of_expansion_sets}, we use it to bound the ratio of $\nu(\Asig)$ to $\nu(\Aset_{\sigma - r})$.
+This will be useful when we bound $\vol(\Csig)$.
+
+\begin{lemma}
+	\label{lem: interior_of_expansion_sets}
+	For $\sigma$, $\Asig$ as in Lemma \ref{lem: expansion_sets}, let $r > 0$ satisfy $r \leq \sigma/4d$. Then,
+	\begin{equation*}
+	\frac{\nu(\Asig)}{\nu(\Aset_{\sigma - r})} \leq 2.
 	\end{equation*}
@@
 \begin{proof}
-	Recalling that $f$ is the density function for $P$, we have
+	Fix $q = \sigma - r$. Then,
+	\begin{align*}
+	\nu(\Asig) & = \nu(\Aset_{q + \sigma - q}) = \nu(\Aset_q + (\sigma - q)B ) \\
+	& \leq \nu(\Aset_q + \frac{(\sigma - q)}{q} \Aset_q) = \left(1 + \frac{\sigma - q}{q}\right)^d \nu(\Aset_q)
+	\end{align*}
+	where the inequality follows from Lemma \ref{lem: expansion_sets}.
+Of course, $\sigma - q = r$, and $\frac{r}{q} \leq \frac{1}{2d}$ for $r \leq \frac{1}{4d}$.
+The claim then follows from Lemma \ref{lem: Taylor_series}.
+\end{proof}
+
+\subsection{Cut and volume estimates}
+\begin{lemma}
+	\label{lem: expected_number_boundary_points}
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
+	\begin{equation*}
+	\Pbb(\Csigr) \leq 2 \nu(\Csig) \frac{rd}{\sigma}  \left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
+	\end{equation*}	
+\end{lemma}
+\begin{proof}
+	Recalling that $f$ is the density function for $\Pbb$, we have
 	\begin{equation}
 	\label{eqn: integral_over_epsilon_neighborhood}
-	P(A_{\sigma, \sigma + r}) = \int_{A_{\sigma, \sigma + r}} f(x) dx
+	\Pbb(\Csigr) = \int_{\Csigr} f(x) dx
 	\end{equation}
-	Now, for $0 = t_0 < t_1 < \ldots < t_k = 1$, we divide up $A_{\sigma, \sigma + r} = \bigcup_{i = 0}^{k-1} \mathcal{T}_i$ where $\mathcal{T}_i = \set{x: rt_i < \rho(x, \Asig) \leq rt_{i+1}}$.
-We can rewrite the right hand side of (\ref{eqn: integral_over_epsilon_neighborhood}) as
-	\begin{align*}
-	\int_{A_{\sigma, \sigma + r}} f(x) dx & = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_i} f(x) dx \\
-	& \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_i) \max_{x \in \mathcal{T}_i} f(x).
-	\end{align*}
-	By definition, 
+	We partition $\Csigr$ into slices, based on distance from $\Csig$, as follows: for $k \in \N$,
 	\begin{equation*}
-	\nu(\mathcal{T}_i) = \nu(\Asig + rt_{i+1}B) - \nu(\Asig + rt_{i}B).
+	\mathcal{T}_{i,k} = \set{x \in \Rd: t_{i,k} < \frac{\rho(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
 	\end{equation*}
-	 Moreover, by \ref{asmp: cluster_regularity} and \ref{asmp: low_noise_density} we have
+	where $t_i = i/k$ for $i = 0, \ldots, k - 1$. As a result,
 	\begin{equation*}
-	 \max_{x \in \mathcal{T}_i} f(x) \leq \tau_{\sigma} - (rt_i)^{\gamma}.
+	\int_{\Csigr} f(x) dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
 	\end{equation*}
-	 since for all $x \in \mathcal{T}_i$, $\rho(x, \Asig) > rt_i$.
-	 Therefore
+	We substitute
+	\begin{equation*}
+	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) := \nu_{i+1,k} - \nu_{i,k}. 
+	\end{equation*}
+	where for simplicity we've written $\nu_{i,k} = \nu(\Csig + rt_{i+1,k}B)$.
+	This, in concert with the upper bound
+	\begin{equation*}
+	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - (rt_{i,k})^{\gamma},
+	\end{equation*}
+	which follows from \ref{asmp: bounded_density} and \ref{asmp: low_noise_density}, yields
 	\begin{align}
 	\label{eqn: telescoping_sum}
-	\sum_{i = 0}^{k-1} \int_{\mathcal{T}_i} f(x) dx & \leq \nonumber \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + rt_{i+1}B) - \\
-	& \nu(\Asig + rt_{i}B)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right).
+	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - (rt_{i,k})^{\gamma} \biggr) \nonumber \\
+	& = \sum_{i = 1}^{k} 
+	\underbrace{\nu_{i,k} \biggl( \left[\lambda_{\sigma} - (rt_{i,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - (rt_{i-1,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi_k}
 	\end{align}
 
-	Now, we have that $\sigma B \subset \Asig$  which implies, 
+	We first consider the term $\Sigma_k$. Here we use Lemma \ref{lem: expansion_sets} to upper bound
 	\begin{equation*}
-	\nu(\Asig + rt_iB) \leq \nu(\Asig + \frac{r t_i}{\sigma} \Asig)
+	\nu_{i,k} \leq \vol(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
 	\end{equation*}
-	and we therefore have the upper bound
-	\begin{align}
-	\label{eqn: riemann_sum_lem1}
-	& \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + rt_{i+1}B) - \nu(\Asig + rt_iB)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) \nonumber \\
-	& \leq \sum_{i = 0}^{k-1} \biggl\{\nu(\Asig + \frac{r t_{i+1}}{\sigma} \Asig) - \nu(\Asig + \frac{r t_i}{\sigma} \Asig)\biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) \nonumber \\
-	& = \nu(\Asig) \sum_{i = 0}^{k-1} \biggl\{ (1 + \frac{r t_{i+1}}{\sigma})^d - (1 + \frac{r t_{i}}{\sigma})^d \biggr\} \left(\tau_{\sigma} - (rt_i)^{\gamma}\right) 
-	\end{align}
-	where the upper bound holds because $\tau_{\sigma} - (rt)^{\gamma}$ is decreasing in $t$.
+	and so we can in turn upper bound $\Sigma_k$:
+	\begin{equation}
+	\label{eqn: Sigmak_riemann_sum}
+	\Sigma_k \leq \vol(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i-1,k})^{\gamma} - (t_{i,k})^{\gamma}\biggr).
+	\end{equation}
+	This, of course, is a Riemann sum, and as the inequality holds for all values of $k$ it holds in the limit as well, which we compute to be
+	\begin{align*}
+	\lim_{k \to \infty} \sum_{i = 1}^{k} \left(1 + \frac{rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i-1,k})^{\gamma} - (t_{i,k})^{\gamma}\biggr) & = \gamma \int_{0}^{1} \left(1 + \frac{rt}{\sigma}\right)^d t^{\gamma - 1} dt \\
+	& \overset{(i)}{\leq} \gamma \int_{0}^{1} \left(1 + \frac{2drt}{\sigma}\right) t^{\gamma - 1} dt = \left(1 + \frac{\gamma 2dr}{\gamma + 1}\right).
+	\end{align*}
+	where $(i)$ follows from Lemma \ref{lem: Taylor_series}. 
+	We plug this estimate in to \eqref{eqn: Sigmak_riemann_sum} and obtain
+	\begin{equation*}
+	\lim_{k \to \infty} \Sigma_k \leq \vol(\Csig) r^{\gamma} \left(1 + \frac{\gamma 2dr}{\gamma + 1}\right).
+	\end{equation*}
 
-	Let $t_{i} = i/k$ for $i = 0, \ldots, k$. Taking the limit as $k \to \infty$, we have
+	We now provide an upper bound on $\xi_k$. It will follow the same basic steps as the bound on $\Sigma_k$, but will not involve integration:
 	\begin{align*}
-	& \lim_{k \to \infty} \sum_{i = 0}^{k-1} \biggl\{ \left(1 + \frac{r (i+1)}{k\sigma}\right)^d - \left(1 + \frac{r i}{k\sigma}\right)^d \biggr\} \left(\tau_{\sigma} - \left(\frac{ri}{k}\right)^{\gamma}\right)  \\
-	 & = \int_{0}^{1} \frac{rd}{\sigma} (1 + \frac{r t}{\sigma})^{d-1} (\tau_{\sigma} - (rt)^{\gamma}) dt \\
-	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma }}{\gamma + 1}\right)
+	\xi_k & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{r}{\sigma}\right)^d(\lambda - r^{\gamma}) - \lambda \biggr\} \\
+	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2dr}{\sigma}\right)(\lambda - r^{\gamma}) - \lambda \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda - r^{\gamma}) - r^{\gamma} \biggr\}.
 	\end{align*}
-	where the inequality comes from $t \leq 1$ and $r < \sigma$.
-
-	Finally, note that (\ref{eqn: riemann_sum_lem1}) holds for any $k$ and arbitrary $0 = t_0 < t_1 < \ldots < t_k = 1$.
-In particular, it holds for $t_{i} = i/k$ for $i = 0, \ldots, k$, and in the limit as $k \to \infty$.
-Therefore, we have
-	\begin{equation*}
-	P(A_{\sigma, \sigma + r}) \leq \nu(\Asig) 2^{d-1} \frac{rd}{\sigma}  \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
-	\end{equation*}
-	which is exactly the stated result of Lemma \ref{lem: expected_number_boundary_points}.
+	where $(ii)$ follows from Lemma \ref{lem: expansion_sets} and $(iii)$ from Lemma \ref{lem: Taylor_series}.
+The final result comes from adding together the upper bounds on $\Sigma_k$ and $\xi_k$ and taking the limit as $k \to \infty$.
 \end{proof}
@@
 	\label{lem: expected_density_cut}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
 	\begin{equation*}
-	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
+	p_K \leq \frac{4 \lambda \nu_d r^{d+1} \nu(\Csig)d}{\sigma}  \left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
 	\end{equation*}
@@
 \begin{proof}
-	We can write $\widetilde{\mathcal{E}}$ as the sum of indicator functions,
+	We can write $\cut_{n,r}$ as the sum of indicator functions,
 	\begin{equation}
 	\label{eqn: density_cut_expansion}
-	\widetilde{\mathcal{E}} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig)
+	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Csigr) \1(x_j \in B(x_i,r) \cap \Csig)
 	\end{equation}
-	Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
+	and by linearity of expectation, we can obtain
+	\begin{equation*}
+	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csigr, x_j \in B(x_i,r) \cap \Csig)
+	\end{equation*}
+	Writing this with respect to the density function $f$, we have
 	\begin{align*}
-	\frac{\widetilde{\mu}}{{n \choose 2}} & = 2 \int_{\Asigr} f(x) \left\{ \int_{B(x,r) \cap \Asig} f(x') dx'\right\} dx \\
-	& \overset{(i)}{\leq} 2 \int_{\Asigr} f(x) \nu_d r^d \tau dx \\
-	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right) 
+	p_K & = 2 \int_{\Csigr} f(x) \left\{ \int_{B(x,r) \cap \Csig} f(x') dx' \right\} dx \\
+	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) dx
 	\end{align*}
-	where $(i)$ follows from Assumption \ref{asmp: cluster_separation}, which implies $f(x') \leq \tau$ for all $x' \in \Asig \setminus A$, and $(ii)$ follows from Lemma \ref{lem: expected_number_boundary_points}.
+	where the inequality follows from Assumption \ref{asmp: cluster_separation}, which implies that the density function $f(x') \leq \lambda$ for all $x' \in \Csig \setminus \Cset$ (otherwise, $x'$ would be in some $\Cset' \in \Cbb_f(\lambda)$, which \ref{asmp: cluster_separation} forbids).
+Then, upper bounding the integral using Lemma \ref{lem: expected_density_cut} gives the final result.
 \end{proof}
@@
 	\begin{equation*}
-	p \geq 2 \tau_{\sigma}^2 \nu(\Asig) \nu_d \left(\frac{r}{2}\right)^d
+	p_V \geq \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
 	\end{equation*}
@@
 \begin{proof}
-	We can write $\mathcal{V}$ as the sum of indicator functions,
+	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
 	\begin{equation}
 	\label{eqn: volume_expansion}
-	\mathcal{V} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asig) \1(x_j \in B(x_i, r))
+	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
 	\end{equation}
-		Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
-	\begin{equation}
-	\label{eqn: expected_volume_integral}
-	\frac{\mu}{{n \choose 2}} = 2 \int_{\Asig} f(x) \left\{\int_{B(x,r)} f(x') dx' \right\} dx
-	\end{equation}
-	For $x \in \Asig$, take $x_0 \in A$ such that $\norm{x - x_0} = \rho(x,A)$ (note that such a minimizer exists because $A$ is closed). Then, by the triangle inequality, we have
+	and by linearity of expectation we obtain
 	\begin{equation*}
-	B\left(\frac{x + x_0}{2}, \frac{r}{2}\right) \in \Asig \cap B(x,r)
+	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)).
 	\end{equation*}
-	Recall that by (\ref{asmp: cluster_regularity}), we have $f(x') \geq \tau_{\sigma}$ for all $x' \in \Asig$.
-We can therefore lower bound the right hand side of (\ref{eqn: expected_volume_integral}) by
+	Writing this with respect to the density function $f$, we have
 	\begin{align*}
-	& 2\int_{\Asig} f(x) \tau_{\sigma} \nu_d \left(\frac{r}{2}\right)^{d} dx \\
-	& \leq 2\tau_{\sigma}^2 \nu(\Asig) \nu_d \left(\frac{r}{2}\right)^d.
+	p_V & = 2 \int_{\Csig} f(x) \left\{ \int_{B(x,r)} f(x') dx' \right\} dx \\
+	& \geq 2 \int_{\Cset_{\sigma - r}} f(x) \left\{ \int_{B(x,r)} f(x') dx' \right\} dx \\
+	& \overset{(i)}{\geq} 2 \lambda_{\sigma}^2 \nu_d r^d \int_{\Cset_{\sigma - r}} f(x) dx
 	\end{align*}
+	where $(i)$ follows from the fact that $B(x,r) \subset \Csig$ for all $x \in C_{\sigma - r}$, along with the lower bound in Assumption \ref{asmp: bounded_density}.
+The claim then follows from Lemma \ref{lem: interior_of_expansion_sets}.
 \end{proof}
 
-\subsection{\textcolor{red}{Concentration inequalities.}}
+We now convert from bounds on $p_K$ and $p_V$ to probabilistic bounds on $\cut_{n,r}$ and $\vol_{n,r}$ in Lemmas \ref{lem: prob_bound_cut} and \ref{lem: prob_bound_vol}.
+The key ingredient will be Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics; the proofs for both are nearly identical and we give only a proof for Lemma \ref{lem: prob_bound_cut}.
+
+\begin{lemma}
+	\label{lem: prob_bound_cut}
+	The following statement holds for any $\delta \in (0,1]$: Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, 
+	\begin{equation}
+	\label{eqn: numerator_additive_bound}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation}
+	with probability at least $1 - \delta$. 
+\end{lemma}
+
+\begin{lemma}
+	\label{lem: prob_bound_vol}
+	The following statement holds for any $\delta \in (0,1]$: Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, 
+	\begin{equation}
+	\label{eqn: denominator_additive_bound}
+	\frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation}
+	with probability at least $1 - \delta$. 
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cut}.]
+	From \eqref{eqn: density_cut_expansion}, we see that $\cut_{n,r}$, properly scaled, can be expressed as an order-$2$ $U$-statistic,
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j)
+	\end{equation*}
+	where 
+	\begin{equation*}
+	\phi_K(x_i,x_j) = \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) + \1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig).
+	\end{equation*}
+
+	From Lemma \ref{lem: bounded_difference} we therefore have
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_k + \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation*}
+	with probability at least $1 - \delta$. 
+\end{proof}
+
+\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
+The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, \ref{lem: prob_bound_cut}, and \ref{lem: prob_bound_vol}.
+All that remains is some algebra, which we take care of below.
+
+Fix $\delta \in (0,1]$ and let $\delta' = \delta/2$. Noting that $\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\vol_{n,r}}$, some trivial algebra gives us the expression
+\begin{equation}
+\label{eqn: conductance_representation_1}
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\vol_{n,r}}{{n \choose 2}} - p_V\right)}
+\end{equation}
+We assume (\ref{eqn: numerator_additive_bound}) and (\ref{eqn: denominator_additive_bound}) hold with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
+Along with (\ref{eqn: conductance_representation_1}) this means
+\begin{equation*}
+\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+\end{equation*}
+for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
+Now, some straightforward algebraic manipulations yield
+\begin{align*}
+\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V - \Err_n} - \frac{p_K}{p_V}\right) + \frac{\Err_n}{p_V - \Err_n} \\
+& = \frac{p_k}{p_V} + \frac{\Err_n}{p_V - \Err_n}\left(\frac{p_K}{p_V} + 1\right) \\
+& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
+\end{align*}
+By Lemmas \ref{lem: expected_density_cut} and Lemma \ref{lem: expected_density_volume}, we have
+\begin{equation*}
+\frac{p_K}{p_V} \leq \frac{4rd}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}
+\end{equation*}
+Then, the choice of 
+\begin{equation*}
+n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}{ \lambda_{\sigma}^2 \nu(\Csig) \nu_d r^d}\right)^2 
+\end{equation*}
+
+implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+
+\subsection{Concentration inequalities}
 
@@
 
+\section{OTHER STUFF}
+
 	\begin{lemma}[Bernstein's inequality for $U$-statistics]
@@
 
-\section{Proof of Theorem \ref{thm: conductance_upper_bound}}
-
-Given the previous lemmas, the proof of Theorem \ref{thm: conductance_upper_bound} is straightforward.
-We rely on Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} to bound $\widetilde{\mu}$ and $\mu$, respectively, and Lemma \ref{lem: bernstein} to bound the deviations $\widetilde{\mathcal{E}} - \widetilde{\mu}$ and $\mathcal{V} - \mu$ with high probability.
-
-\subsection{Numerator of $\Phi_{n,r}(\Asig[\mathbf{X}])$.}
-From (\ref{eqn: density_cut_expansion}), we can see that $\widetilde{\mathcal{E}}$, properly scaled, can be expressed as an order-$2$ $U$-statistic,
-\begin{equation*}
-\frac{1}{{n \choose 2}}\widetilde{\mathcal{E}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \widetilde{k}(x_i, x_j)
-\end{equation*}
-where 
-\begin{align*}
-\tilde{k}(x_i,x_j) = & \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) + \\
-& \1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig)
-\end{align*}
-
-From Lemma \ref{lem: bounded_difference} we therefore have
-\begin{equation}
-\label{eqn: numerator_additive_bound}
-\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} \leq \widetilde{p} + \sqrt{\frac{\log(1/\delta)}{n}}
-\end{equation}
-with probability at least $1 - \delta$.
-
 \textcolor{red}{\textbf{Multiplicative bound}: As $\tilde{k}(x_1,x_2)$ is the sum of two Bernoulli random variables with negative covariance (since $\1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) = 1$ implies $\1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig) = 0$ and vice versa), we can upper bound $\var\left(\tilde{k}(x_1, x_2)\right) \leq  \widetilde{p}$, where we recall
@@
 
-\paragraph{Denominator of $\Phi_{n,r}(\Asig[\mathbf{X}])$.}
-We follow a very similar set of steps as above.
-
-By (\ref{eqn: density_cut_expansion}), we see that $\mathcal{V}$ can also be expressed as an order-2 $U$-statistic,
-\begin{equation*}
-\frac{\mathcal{V}}{ {n \choose 2} } = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n } k'(x_i, x_j)
-\end{equation*}
-with
-\begin{align*}
-k'(x_i,x_j)  = & \1(x_i \in A_\sigma)\1(x_j \in B(x_i,r)) ~ + \\
-& \1(x_j \in A_{\sigma})\1(x_i \in B(x_j,r))
-\end{align*}
-
-From Lemma \ref{lem: bounded_difference} we therefore have
-\begin{equation}
-\label{eqn: denominator_additive_bound}
-\frac{\mathcal{V}}{{n \choose 2}} \geq p - \sqrt{\frac{\log(1/\delta)}{n}}
-\end{equation}
-with probability at least $1 - \delta$.
-
 \textcolor{red}{Multiplicative bound: The two terms on the right hand side are both distributed $\mathrm{Bernoulli}(p/2)$.
@@
 	with probability at least $1 - \Delta$. }
-
-\paragraph{Proof of the additive error bound.}
-Noting that $\Phi_{n,r}(\Asig[\mathbf{X}]) = \mathcal{\widetilde{E}} / \mathcal{V}$, and multiplying and dividing by ${n \choose 2}$, we have
-\begin{equation}
-\label{eqn: conductance_representation_1}
-\Phi_{n,r}(\Asig[\mathbf{X}]) = \frac{\widetilde{p} + \left(\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} - \widetilde{p}\right)}{p + \left(\frac{\widetilde{\mathcal{V}}}{{n \choose 2}} - p \right)}
-\end{equation}
-We assume (\ref{eqn: numerator_additive_bound}) and (\ref{eqn: denominator_additive_bound}) hold, keeping in mind that this will happen with probability at least $1 - 2\delta$.
-Along with (\ref{eqn: conductance_representation_1}) this means
-\begin{equation*}
-\Phi_{n,r}(\Asig[\mathbf{X}]) \leq \frac{\widetilde{p} + \Err_n}{p - \Err_n}
-\end{equation*}
-for $\Err_n = \sqrt{\frac{\log(1/\delta)}{n}}$.
-Now, some straightforward algebraic manipulations yield
-\begin{align*}
-\frac{\widetilde{p} + \Err_n}{p - \Err_n} & = \frac{\widetilde{p}}{p} + \left(\frac{\widetilde{p}}{p - \Err_n} - \frac{\widetilde{p}}{p}\right) + \frac{\Err_n}{p - \Err_n} \\
-& = \frac{\widetilde{p}}{p} + \frac{\Err_n}{p - \Err_n}\left(\frac{\widetilde{p}}{p} + 1\right) \\
-& \leq \frac{\widetilde{p}}{p} + 2 \frac{\Err_n}{p - \Err_n}.
-\end{align*}
-Finally, combining the upper bound given by Lemma \ref{lem: expected_density_volume} with the lower bound on $n$ specified in the statement of Theorem \ref{thm: conductance_upper_bound}, we have
-\begin{equation*}
-2 \frac{\Err_n}{p - \Err_n} \leq \epsilon
-\end{equation*}
-By Lemmas \ref{lem: expected_density_cut} and Lemma \ref{lem: expected_density_volume}, we have
-\begin{equation*}
-\frac{\widetilde{p}}{p} \leq C_{\sigma} \frac{\tau}{\tau_{\sigma}} \frac{(\tau_{\sigma} - \frac{r^{\gamma+1}}{\gamma+1})}{\tau_{\sigma}}
-\end{equation*}
-and thus we have shown (\ref{eqn: conductance_additive_error_bound}) occurs with probability at least $1 - 2\delta$.
-Plugging in $\delta' = \delta/2$ gives the exact statement in Theorem \ref{thm: conductance_upper_bound}.
-
 \end{document}

### 2019-01-14 references/notes/kannan05.tex
completed proof of Theorem 1

\documentclass{article}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\Perp}{\perp \! \! \! \perp}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\newcommand{\Rd}{\Reals^d}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\A}{\mathcal{A}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes on 'BLOCKING CONDUCTANCE AND MIXING IN RANDOM WALKS'}
\author{Alden Green}
\date{\today}
\maketitle

\section{SETUP}

\paragraph{Continuous state Markov chains.}

Let $(K, \mathcal{A})$ be a $\sigma$-algebra. For every $u \in K$, let $P_u$ be a probability measure on $(K, \mathcal{A})$, and assume that for every $S \in \mathcal{A}$, the value $P_u(S)$ is a measurable function of $u$. We call $P_u$ the \textbf{1-step transition probability density} out of $u$. The triple $(K, \A, \set{P_u: u \in K})$ is a \textbf{Markov chain}.

Let $\mathcal{M}$ be a continuous state Markov chain with no-atoms. Let the \textbf{random-stopping Markov chain} $\rho^m$ be the distribution induced by choosing an integer $Y \in \set{0, 1, \ldots, m - 1}$ uniformly at random, then stopping after $Y$ steps.

\paragraph{Random walks on geometric sets.}
We specify $\mathcal{M}$ to be the \textbf{ball walk in $K$} with step size $r$. In this walk, at every step, we go from the current point $x \in K$, to a random point in $B(x, r) \cap K$ where $B(x,r)$ is the ball of radius $r$ with center $x$.

Note that the stationary distribution of $\mathcal{M}$ is not exactly the uniform measure. Define \textbf{local conductance}, $\ell(x)$, by
\begin{equation*}
\ell(x) = \frac{\vol(K \cap B(x,r))}{\vol(B(x,r))}
\end{equation*}
for $x \in K$. Then, letting normalizing constant $E$ be
\begin{equation*}
E = \int_{L} \ell(x) dx
\end{equation*}
the stationary distribution $\pi$ of the ball walk has density function $\ell/E$.

\paragraph{Long-run behavior.}

To reason about the long-run convergence of $\rho$, we will need to understand what distribution $\rho$ is convergence towards.

\begin{assumption}
	\label{asmp: long_run_behavior}
	We will assume that our Markov chain is ergodic, time-reversible, atom-free, and has stationary distribution $\pi$.
\end{assumption}

Intuitively, the rate of convergence is affected by how quickly the random walk can escape bottlenecks. The \textbf{ergodic flow} is defined for $X, Y \in \A$ by
\begin{equation*}
Q(X,Y) := \int_X P_x(Y) d \pi(x).
\end{equation*}
Then, we define the \textbf{conductance function} $\Psi(t)$ for $t \in (0,1)$ to be
\begin{equation*}
\Psi(t) := \min_{ \substack{S \subset V, \\ \pi(S) = t} } Q(S, K \setminus S).
\end{equation*}
Large conductance functions mean that there are less pronounced bottlenecks, and therefore $\rho$ should mix faster.

We will also need to formalize what type of convergence we are referring to. Define the \textbf{total variation distance} $d_{TV}$ between two measures $\mu$ and $\nu$ defined over $(K,\mathcal{A})$ to be
\begin{equation*}
d_{TV}(\mu, \nu) = \sup_{A \in \mathcal{A}} \abs{\mu(A) - \nu(A)}.
\end{equation*}

Define the \textbf{total variation mixing time} $\tau_{TV}$ of a sequence of distributions $\rho^1, \rho^2, \ldots$ converging to stationary distribution $\pi$ to be 
\begin{equation*}
\min \set{T: d_{TV}(\rho^t, \pi) \leq 1/4 \text{ for all } t \geq T}.
\end{equation*}

\paragraph{Local spread.}
Markov chains on geometric sets will have the nice property that the chain quickly disperses probability out of small sets. To quantify this, we introduce $\xi(A)$ to be
\begin{equation*}
\xi(A) := \inf \set{P_u(K \setminus A): u \in A} \\ ~~~ \xi(t) = \inf \set{\xi(A): \pi(A) = t} ~~ (0 \leq t \leq 1).
\end{equation*}
Intuitively, on geometric sets, $\xi(t)$ should be large when $t$ is small. Define the \textbf{local spread},$\pi_1$, to be 
\begin{equation*}
\pi_1 := \inf \set{t: \xi(t) \leq 1/10}
\end{equation*}
Part of the theory developed allows us to ignore sets $S$ of stationary probability less than $\pi_1$.

\section{RESULTS}

\begin{theorem}
	\label{thm: conductance_function_lb}
	Consider a continuous state Markov chain $\mathcal{M}$ which satisfies Assumption \ref{asmp: long_run_behavior}, and further assume $\xi(a) > 0$ for some $a > 0$. Suppose that for some $A, B > 0$, an inequality of the form
	\begin{equation}
	\label{eqn: conductance_function_lb}
	\Psi(x) \geq \min \set{ Ax , B x \ln(1 / x)} 
	\end{equation}
	holds for all $a \leq x \leq 1/2$. Then
	\begin{equation*}
	d(\rho^m, \pi) \leq \frac{8 \ln m}{m \xi(a)} + \frac{1}{m} \left(\frac{32}{A^2} \ln\left(\frac{1}{a}\right) + \frac{100}{B^2}\right)
	\end{equation*}
\end{theorem}

To use Theorem \ref{thm: conductance_function_lb}, we will need to both find $a$ and assert (\ref{eqn: conductance_function_lb}) holds for $x \geq a$.

\begin{theorem}
	\label{thm: local_spread}
	The local spread of the proper move walk satisfies $\pi_1 \geq \frac{1}{2} (r / D)^{2d}$.
\end{theorem}

\begin{theorem}
	\label{thm: conductance_function_lb_ballwalk}
	Suppose that $K$ is a convex set in $\Rd$ with diameter at most $D$, containing the unit ball $B = B(0,1)$, and further that the step size for the ball walk in $K$ satisfies $r < \frac{D}{100}$. For $0 < x < 1/2$, we have
	\begin{equation}
	\label{eqn: conductance_function_lb_ballwalk}
	\Psi(x) > \min \set{\frac{1}{288 \sqrt{d}} x, \frac{r}{81 \sqrt{d} D } x \ln(1 + 1/2) }
	\end{equation}
\end{theorem}

Theorem \ref{thm: conductance_function_lb_ballwalk} states that the ball walk satisfies (\ref{eqn: conductance_function_lb}), and Theorem \ref{thm: local_spread} gives us values for $\xi(a)$ and $a$. Deploying Theorem \ref{thm: conductance_function_lb} therefore gives us
\begin{equation*}
\tau_{TV} = \mathcal{O} \biggl(d\left(\frac{D}{r}\right)^2 + d^2\ln(D / r) \biggr)
\end{equation*}

\section{SUPPLEMENTAL RESULTS}

\section{PROOFS}

\end{document}

### 2019-01-16 icml/icml_local_density_clustering_supplement.tex
added mixing time estimate lemmas

@@
 \newcommand{\pibf}{\bm{\pi}}
+\newcommand{\rhobf}{\bm{\rho}}
 
@@
 \newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Qbb}{\mathbb{Q}}
 \newcommand{\Cbb}{\mathbb{C}}
@@
 %%% Sets
+\newcommand{\Sset}{\mathcal{S}}
 \newcommand{\Cset}{\mathcal{C}}
@@
 where $\rho(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
-.
 
@@
 
+As part of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}, we will require an estimate of a function $g(t)$ for $t \in [x_0, 1/2]$ for some $x_0 > 0$.
+For $m > 0$ and $x_0 = t_0 < t_1 < \ldots < t_m = 1/2$, define the \emph{stepwise approximation to $g$} to be $\bar{g}$, given by
+\begin{equation}
+\label{eqn: stepwise_approximation}
+\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
+\end{equation}
+\begin{lemma}
+	\label{lem: stepwise_approximation}
+	Fix
+	\begin{equation*}
+	g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [x_0, 1/2]$}
+	\end{equation*}
+	 If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $g(t) \geq \bar{g}(t)\geq g(t) / 2$.
+\end{lemma}
+\begin{proof}
+	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function.
+
+	By the concavity of the $\log$ function, 
+	\begin{equation*}
+	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
+	\end{equation*}
+	As a result,
+	\begin{equation*}
+	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
+	\end{equation*}
+\end{proof}
+
+The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
+Formally, the discrete local spread $\pi_1(G)$ is given by
+\begin{equation}
+\label{eqn: local_spread}
+\pi_1(G) := \frac{d_{\min}(G)^2}{10 \vol(V; G)} 
+\end{equation}
+where $d_{\min}(G) = \min_{v \in V} d(v)$ is the minimum degree in $G$.
+Intuitively, the discrete local spread gauges how much the walk given by $\Wbf$ has mixed after one step, starting from any node $v$.
+We will denote $\pi_1(G_{n,r}[\Csig[\Xbf]])$ by $\widetilde{\pi}_{1,n}$.
+
+\begin{lemma}
+	\label{lem: local_spread_lb}
+	For $\Csig$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
+	\begin{equation*}
+	\liminf_{n \to \infty}~ \widetilde{\pi}_{1,n} \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}
+	\end{equation*}
+\end{lemma}
+
+\textcolor{red}{Prove Lemma \ref{lem: local_spread_lb}}.
+
 \subsection{Cut and volume estimates}
@@
 	\label{lem: expected_number_boundary_points}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
+	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
 	\begin{equation*}
@@
 
+\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
+
+\textcolor{red}{Give proof structure.}
+
+We begin by introducing some more notation.
+Take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf$.
+We slightly overload notation and let the \emph{conductance function} be given by
+\begin{equation*}
+\Phi(t; G) := \min_{\substack{S \subseteq V \\ \pi(S) \leq t} } \Phi(S; G)
+\end{equation*}
+
+We will pay special attention to the conductance function evaluated over the subgraph $G_{n,r}[\Csig[\Xbf]]$.
+For ease of notation, we therefore introduce $\widetilde{\Phi}_{n,r}(t) = \Phi(t; G_{n,r}[\Csig[\Xbf]])$.
+
+Lemma \ref{lem: montenegro} is from the \textcolor{red}{PhD thesis of Montenegro.} It leverages the conductance function to produce an upper bound on the \textcolor{red}{total variation distance} between the random walk
+\begin{equation*}
+\rhobf^t = \frac{1}{t} \sum_{s = 1}^{t} e_v \Wbf^s
+\end{equation*}
+and the stationary distribution $\pibf$.
+
+\begin{lemma}
+	\label{lem: montenegro}
+	Let $\Wbf$ be the random walk matrix over a graph $G = (V,E)$, with stationary distribution $\pibf$. Then, for any $v \in V$:
+	\begin{equation*}
+	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{t}\left(\frac{4}{\Phi^2(\pi_1(G); G)} + \int_{x = \pi_1(G)}^{1/2} \frac{4}{x \Phi^2(x; G)} dx\right) \right\}
+	\end{equation*}
+	where $\pi_1(G)$ is defined as in \eqref{eqn: local_spread}.
+\end{lemma}
+
+\begin{proof}
+	In \textcolor{red}{the PhD thesis of Montenegro}, letting
+	\begin{equation*}
+	h^t(x_0) = \sup_{S: \pi(S) < x_0}  \bigl(\rhobf^t(S) - \pibf(S) \bigr)
+	\end{equation*}
+	the following statement is shown: for $\pi_{\min} < x_0 < 1/2$, 
+	\begin{equation*}
+	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, h^t(x_0) +  \frac{70}{t}\left(\frac{4}{\Phi^2(x_0); G)} + \int_{x = x_0}^{1/2} \frac{4}{x \Phi^2(x; G)}\right) \right\}
+	\end{equation*}
+	It is also observed therein that the function $h^t(x)$ is decreasing for any fixed $x$, as $t$ increases.
+All that remains for us to show is that $h^s(\pi_1(G)) \leq 1/10$ for some $s \leq t$.
+We choose $s = 1$, and note that for any set $S \subset V$ with $\pibf(S) \leq \pi_1(G)$,
+	\begin{equation*}
+	\rhobf^1(S) \leq \frac{\abs{S}}{d_{\min}(G)} \leq \frac{\pibf(S) \vol(V; G)}{d_{\min}(G)^2} \leq \frac{1}{10},
+	\end{equation*}
+	where we use the fact that $\pibf(S) \geq \frac{\abs{S} d_{\min}(G)}{\vol(V; G)}$.
+\end{proof}
+
+We turn to lower bounding $\widetilde{\Phi}_{n,r}(t)$.
+First, we exhibit a lower bound on a continuous space analogue, over the set $\Csig$.
+Let $\nu_{\Pbb}(\cdot)$ denote the weighted volume; formally, for $\Sset \subset \Rd$
+\begin{equation*}
+\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
+\end{equation*}
+
+The $r$-ball walk over $\Csig$ is a Markov chain with transition probability for $x \in \Csig, \Sset, \Sset' \subset \Csig$ given by,
+\begin{equation*}
+P_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ Q_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx. 
+\end{equation*}
+stationary distribution defined by
+\begin{equation*}
+\ell_{\Pbb,r}(x) := \frac{\nu_\Pbb(\Csig \cap B(x,r))}{\nu_{\Pbb}(B(x,r))}, ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx
+\end{equation*}
+and corresponding conductance function
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}
+\end{equation*}
+Lemma \ref{lem: continuous_conductance_lb} (\textcolor{red}{a weighted analogue of Theorem 4.6 of Kannan}) provides a lower bound on $\widetilde{\Phi}_{\Pbb, r}(t)$, as well as a stepwise approximation to $\widetilde{\Phi}_{\Pbb, r}$.
+\begin{lemma}
+	\label{lem: continuous_conductance_lb}
+	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
+	\begin{itemize}
+		\item 
+		for $0 < t < 1/2$,
+		\begin{equation*}
+		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\end{equation*}
+		\item
+		Let
+		\begin{equation*}
+		m = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
+		\end{equation*}
+		 and $t_i = (i + 1)/m$ for $i = 0, \ldots, m - 1$. Then, for $1/m < t < 1/2$
+		\begin{equation*}
+		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\log\left(\frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\end{equation*}
+		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$. 
+	\end{itemize}
+
+\end{lemma}
+\begin{proof}
+	We begin by stating directly the result of \textcolor{red}{Kannan et al.}: for $0 < t < 1/2$, and any $S$ such that $\pi_{\nu,r}(S) = t$,
+	\begin{equation}
+	\label{eqn: kannan_1}
+	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{1}{t}\right)\right\}.
+	\end{equation}
+	Now, we note that
+	\begin{equation*}
+	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
+	\end{equation*}
+	and plugging these estimates in to \eqref{eqn: kannan_1} gives the final bound on $\widetilde{\Phi}_{\Pbb,r}(t)$.
+The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows immediately from application of Lemma \ref{lem: stepwise_approximation}.
+\end{proof}
+
+The introduction of the stepwise approximation allows us to make use of Lemma \ref{lem: consistency_of_conductance_function}, which gives us (pointwise) consistency of the discrete graph functionals $\widetilde{\Phi}_{n,r}(t)$ to the continuous functionals $\widetilde{\Phi}_{\Pbb,r}(t)$.
+
+\begin{lemma}
+	\label{lem: consistency_of_conductance_function}
+	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, fix any $0 < t < 1/2$. Then the following statement holds: with probability one, as $n \to \infty$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t)
+	\end{equation*}
+	As a consequence, $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
+	\begin{equation}
+	\label{eqn: consistency_of_stepapprox_conductance_function}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+	\end{equation}
+\end{lemma}
+Lemma \ref{lem: consistency_of_conductance_function} stems from \textcolor{red}{Garcia Trillos 16}, with a pair of notable distinctions: here, we do not allow the radius $r$ to go to zero, but rather set it to be constant, and in the minimization we have an additional constraint on the measure $\pi(\cdot)$, in both the discrete and continuous functionals.
+As such, we will need to re-prove a number of the statements of \textcolor{red}{Garcia Trillos 16} to work in this context.
+We defer this work to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}, and here will only show that  \eqref{eqn: consistency_of_stepapprox_conductance_function} is implied immediately by the pointwise result.
+
+\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
+We take as given that for any $0 < t < 1/2$,
+\begin{equation*}
+\lim_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
+\end{equation*}
+In particular, this will occur for $t_0, t_1, \ldots, t_m$ and therefore
+\begin{equation*}
+\lim_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+\end{equation*}
+uniformly over $[1/m,1/2]$.
+But by Lemma \ref{lem: stepwise_approximation}, $\widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{n,r}$, so we have shown \eqref{eqn: consistency_of_stepapprox_conductance_function}.
+\end{proof}
+
+Lemma \ref{lem: consistency_of_conductance_function} coupled with Lemma \ref{lem: montenegro} yields a bound on the total variation mixing time.
+\begin{lemma}
+
+\end{lemma}
+
+\subsection{Proof of pointwise consistency of conductance function.}
+\label{subsection: proof_of_pointwise consitency_of_conductance_function}
+
 \section{OTHER STUFF}

### 2019-01-16 icml/icml_local_density_clustering_supplement.tex
added in conversion to infinity mixing time

@@
 \newcommand{\pbf}{\mathbf{p}}
+\newcommand{\qbf}{\mathbf{q}}
 \newcommand{\ebf}[1]{\mathbf{e}_{#1}}
@@
 \newcommand{\rhobf}{\bm{\rho}}
+\newcommand{\Deltabf}{\bm{\Delta}}
+\newcommand{\deltabf}{\bm{\delta}}
 
@@
 
-The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
+The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also depends on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
 Formally, the discrete local spread $\pi_1(G)$ is given by
@@
 We begin by introducing some more notation.
-Take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf$.
+For vertex set $V = \set{v_1, \ldots, v_N}$, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf$.
 We slightly overload notation and let the \emph{conductance function} be given by
@@
 
-Lemma \ref{lem: montenegro} is from the \textcolor{red}{PhD thesis of Montenegro.} It leverages the conductance function to produce an upper bound on the \textcolor{red}{total variation distance} between the random walk
+Lemma \ref{lem: montenegro} is adapted from the \textcolor{red}{PhD thesis of Montenegro.} It leverages the conductance function to produce an upper bound on the \textcolor{red}{total variation distance} between the random walk
+\begin{equation}
+\label{eqn: uniform_stopping_random_walk}
+\rhobf^t = \frac{1}{t} \sum_{s = 1}^{t} e_v \Wbf^s
+\end{equation}
+and the stationary distribution $\pibf$.
+Consider $\qbf = (\qbf^1, \qbf^2, \ldots)$ a sequence of distributions over $V$, where $\qbf^t = (\qbf_1^t, \ldots, \qbf_{\abs{V}}^t)$.
+The \emph{total variation mixing time} of $\qbf$ to stationary distribution $\pibf$ is given by
 \begin{equation*}
-\rhobf^t = \frac{1}{t} \sum_{s = 1}^{t} e_v \Wbf^s
+\tau_1(\qbf; G) = \min_{t_0 \in N} \set{t: \norm{\qbf^t - \pibf}_{TV} \leq 1/4}
 \end{equation*}
-and the stationary distribution $\pibf$.
+where $\norm{\qbf^t - \pibf}_{TV} = \sum_{v_i \in V} \abs{\qbf_i - \pibf_i}$ is the total variation distance. Then,
 
@@
 	\begin{equation*}
-	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{t}\left(\frac{4}{\Phi^2(\pi_1(G); G)} + \int_{x = \pi_1(G)}^{1/2} \frac{4}{x \Phi^2(x; G)} dx\right) \right\}
+	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{t}\left(5 + \int_{x = \pi_1(G)}^{1/2} \frac{4}{x \Phi^2(x; G)} dx\right) \right\}
 	\end{equation*}
@@
 
-\begin{proof}
+To prove Lemma \ref{lem: montenegro} we must first introduce the concept of a blocking conductance function.\footnote{For more details, see \textcolor{red}{PhD thesis of Montenegro}}
+
+\begin{definition}[Blocking Conductance Function of \textcolor{red}{PhD thesis of Montenegro}]
+	\label{def: bcf}
+	Let $x_0$ satisfy
+	\begin{equation*}
+	x_0 \geq \min_{v \in V} \pibf(v)
+	\end{equation*}
+	A function $\phi(x; G): [x_0, 1/2] \to [0,1]$ is a \emph{blocking conductance function} if for all $S \subset V$ with $\pibf(S) = x \in [x_0, 1/2]$, either of the following hold: 
+	\begin{enumerate}
+		\item \emph{Exterior inequality.} For all $y \in \left[\frac{1}{2}x, x\right]: \phi_{int}(S) \geq \phi(\max\{x_0,y\})$
+		\item \emph{Interior inequality.} For all $y  \in \left[x, \frac{3}{2}x\right]: \phi_{ext}(S) \geq \phi(\max\{y,1 -y\})$.
+	\end{enumerate}
+	where $\phi_{int}$ and $\phi_{ext}$ are defined respectively as
+	\begin{align*}
+	\phi_{int}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2} \\
+	\phi_{ext}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S^c \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2}
+	\end{align*}
+\end{definition}
+
+\begin{proof}[Proof of Lemma \ref{lem: montenegro}]
+	Consider the function $\phi(\cdot, G): [\pi_1(G), 1/2] \to [0,1]$ defined by
+	\begin{equation}
+	\label{eqn: bcf}
+	\phi(x; G) = 
+	\begin{cases}
+	\frac{1}{5}, ~~~~~~~~~~~ x = \pi_1(G) \\
+	\frac{1}{4} \Phi^2(x; G), ~ x \in \left(\pi_1(G), 1/2\right] \\
+	\end{cases}
+	\end{equation}
 	In \textcolor{red}{the PhD thesis of Montenegro}, letting
@@
 	\end{equation*}
-	the following statement is shown: for $\pi_{\min} < x_0 < 1/2$, 
-	\begin{equation*}
-	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, h^t(x_0) +  \frac{70}{t}\left(\frac{4}{\Phi^2(x_0); G)} + \int_{x = x_0}^{1/2} \frac{4}{x \Phi^2(x; G)}\right) \right\}
-	\end{equation*}
-	It is also observed therein that the function $h^t(x)$ is decreasing for any fixed $x$, as $t$ increases.
+	the following theorem is given: if $\phi$ is a blocking conductance function (meaning it satisifies Definition \ref{def: bcf}), 
+	\begin{align*}
+	\norm{\rhobf^t - \pibf}_{TV} & \leq \max\left\{ \frac{1}{4}, h^t(x_0) +  \frac{70}{t}\left(\frac{1}{\phi(x_0; G)} + \int_{x = x_0}^{1/2} \frac{4}{x \phi(x; G)}\right) \right\} \\
+	& = \max\left\{ \frac{1}{4}, h^t(x_0) +  \frac{70}{t}\left(5 + \int_{x = x_0}^{1/2} \frac{4}{x \Phi^2(x; G)}\right) \right\}.
+	\end{align*}
+	We will wait to the end to show the $\phi$ is in fact a blocking conductance function, and first show that the above expression reduces to the desired result.
+
+	It is also observed in \textcolor{red}{the PhD thesis of Montenegro} that the function $h^t(x)$ is decreasing for any fixed $x$, as $t$ increases.
 All that remains for us to show is that $h^s(\pi_1(G)) \leq 1/10$ for some $s \leq t$.
@@
 	where we use the fact that $\pibf(S) \geq \frac{\abs{S} d_{\min}(G)}{\vol(V; G)}$.
+
+	Now we complete the proof by verifying that $\phi$ is in fact a blocking conductance function.
+It is easy to see that $\frac{1}{4} \Phi^2(x;G)$ is a valid blocking conductance function for all $x \in (\pi_1(G), 1/2]$, (as it satisfies the exterior inequality).
+For $x = \pi_1(G)$ we will instead turn to the interior inequality, and show the following: for any $S \subset V$ such that $\pi(S) = \pi_1(G)$,
+	\begin{equation*}
+	\frac{1}{5} \leq \phi_{int}(S).
+	\end{equation*}
+	For any $S$ such that $\pi(S) \leq \pi_1(G)$, the following statement holds: for every $u \in S$, $\cut(u, S^c; G) \geq 9/10 \cdot \deg(u; G)$. 
+	Fixing $\lambda = \pi(S)/2$, we have
+	\begin{align*}
+	\phi_{int}(S) & \geq 4 \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{4 \vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
+	& \geq  \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{9 \lambda \sum_{u \in S \setminus B} \deg(u; G)}{40 \vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
+	& \geq \frac{9\lambda^2}{40[\lambda(1 - \lambda)^2]} \geq \frac{1}{5}. 
+	\end{align*} 
 \end{proof}
@@
 	\end{equation*}
-	As a consequence, $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
+	As a consequence, for $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
 	\begin{equation}
@@
 
-Lemma \ref{lem: consistency_of_conductance_function} coupled with Lemma \ref{lem: montenegro} yields a bound on the total variation mixing time.
+Lemma \ref{lem: consistency_of_conductance_function} coupled with Lemma \ref{lem: montenegro} will yield a bound on the total variation mixing time of $\rhobf^t$.
+Lemma \ref{lem: tv_mixing_to_pointwise_mixing} handles the last step, conversion from the total variation mixing time of $\rhobf^t$ to the relative pointwise mixing time of $e_v \Wbf^t$.
 \begin{lemma}
+\label{lem: tv_mixing_to_pointwise_mixing}
+	Let $\rhobf = (\rhobf^1, \rhobf^2, \ldots)$ be a sequence of distributions, with $\rhobf^t$ defined as in \eqref{eqn: uniform_stopping_random_walk}. Then, for $\qbf = (e_v\Wbf^1, e_v\Wbf^2, \ldots)$
+	\begin{equation*}
+	\tau_{\infty}(\qbf; G) \leq 2752 \tau_1(\rhobf; G) \log \left(\frac{4}{\min\left\{1,10 \pi_1(G)\right\}}\right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We introduce a few pieces of notation to simplify the analysis. Let
+	\begin{equation*}
+	\Delta_k^{(t)} = (e_v\Wbf^t)[k] - \pibf[k], ~~ \delta_k^{(t)} = \frac{\Delta_k^{(t)}}{\pibf[k]}
+	\end{equation*}
+	and $\Deltabf^{(t)} = (\Delta_1^{(t)}, \ldots, \Delta_N^{(t)})$, $\deltabf^{(t)} = (\delta_1^{(t)}, \ldots, \delta_N^{(t)})$.
+For a vector $\Deltabf = (\Delta_1, \ldots, \Delta_{N})$, the $L^{p}(\pibf)$ norm is given by
+	\begin{equation*}
+	\norm{\Deltabf}_{L^p(\pibf)} = \left(\sum_{k = 1}^{N} \left(\Delta_k\right)^{p} \pi_k \right)^{1/p}
+	\end{equation*}
+	The $L^{p}(\pibf)$ norms are relevant because
+	\begin{enumerate}
+		\item If $t > \tau_{\infty}(\qbf; G)$, then $\norm{\deltabf^{(t)}}_{L^{\infty}(\pi)} < 1/4$. 
+		\item If $t > \tau_{1}(\qbf; G)$, then 
+		$\norm{\deltabf^{(t)}}_{L^{1}(\pi)} < 1/4$.
+	\end{enumerate}
 
-\end{lemma}
+	To go between the two, we have
+	\begin{align*}
+	\norm{\deltabf^{(2t)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(t)}}^2_{L^{2}(\pi)} \\
+	& = \norm{(\deltabf^{(t)})^2}^2_{L^{1}(\pi)} \\
+	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)}
+	\end{align*}
+	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
+	\begin{align*}
+	\norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{k  = 1,\ldots,N} \frac{(e_v\Wbf^t)[k]}{\pibf[k]} \right\} \\
+	& \overset{(iii)}{\leq} \max\left\{1, \frac{\vol(V; G)}{d_{\min}(G)^2} \right\} \\
+	& = \max\left\{1, \frac{1}{10 \pi_1(G)}\right\}
+	\end{align*}
+	where $(iii)$ follows from $\pibf[k] \geq d_{\min}(G) / \vol(V; G)$ and $(e_v\Wbf^t) \geq 1/d_{\min}$.
+
+	As a result, it is sufficient to exhibit $t > 0$ such that
+	\begin{equation*}
+	\norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \leq \min \left\{1/4,\frac{10 \pi_1(G)}{4}\right\}
+	\end{equation*}
+	Here, we leverage the following well-known fact (\textcolor{red}{PhD thesis of Montenegro}): for any $\epsilon > 0$, if $t \geq \tau_1(e_v \Wbf^t; G) \cdot \log(1/\epsilon)$ then
+	\begin{equation*}
+	\norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \leq \epsilon
+	\end{equation*}
+	Therefore, picking 
+	\begin{equation*}
+	t_0 = \tau_1(e_v \Wbf^t; G) \cdot \log \left(\frac{1}{\min\left\{1/4,\frac{10 \pi_1(G)}{4}\right\}}\right)
+	\end{equation*} implies $\norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $t \geq 2 t_0$.
+
+	Finally, it is known (\textcolor{red}{PhD thesis of Montenegro}) that
+	\begin{equation*}
+	\tau_{1}(\qbf; G) \leq 1376 \tau_{1}(\rhobf; G)
+	\end{equation*}
+	and so the desired result holds.
+
+\end{proof}
 

### 2019-01-18 icml/icml_local_density_clustering_supplement.tex
began restructuring proof of theorem 2

@@
 \newcommand{\Err}{\mathrm{Err}}
+\newcommand{\Log}{\mathrm{Log}}
 
@@
 \newcommand{\deltabf}{\bm{\delta}}
+
+%%% Random walk vectors
 
@@
 	\label{lem: stepwise_approximation}
-	Fix
+	\begin{itemize}
+		\item For any function $f$ monotone decreasing in $t$ on the interval $[x_0,1/2]$, $\bar{f}(t) \leq f(t)$ for all $t \in [x_0,1/2]$.
+		\item Fix
 		\begin{equation*}
@@
 		\end{equation*}
-	 If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $g(t) \geq \bar{g}(t)\geq g(t) / 2$.
+		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
+	\end{itemize}
+
 \end{lemma}
 \begin{proof}
-	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function.
+	The first statement is immediately obvious, and we turn to proving the second.
+
+	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.
 
@@
 
+\subsection{Mixing time on graphs}
+For $N \in \mathbb{N}$ and a set $V$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf = (\pi_u)_{u \in V}$ where $\pi_v = \frac{\Dbf_{vv}}{\vol(V; G)}$.
+For $v \in V$,
+\begin{equation}
+\label{eqn: random_walk}
+q_{vu}^{(m)} = e_v\Wbf^m e_u, ~~ \qbf_{v}^{(m)} = \left(q_{vu}^{(m)}\right)_{u \in V}, ~~ \qbf_v = (\qbf^{(1)}_{v\cdot},\qbf^{(2)}_{v\cdot}, \ldots), 
+\end{equation}
+denote respectively the $m$-step transition probability, distribution, and sequence distributions of the random walk over $G$ originating at $v$.
+Letting $\qbf = (\qbf_v)_{v \in V}$, the relative pointwise mixing time is thus
+\begin{equation*}
+\tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
+\end{equation*}
+
+Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined to be
+\begin{equation*}
+s(G) := \frac{9D_{\min}}{10}\pi_{\min} 
+\end{equation*}
+for $D_{\min} := \min_{v \in V} \Dbf_{vv}$ and $\pi_{\min} := D_{\min} / \vol(V; G)$.
+
+%\inf \set{t: \forall S \subset V ~\text{with}~ \pi(S) = t, \beta(S) \leq 1/10}
+%\end{equation*}
+where $\beta(S) := \inf_{v \in S} \qbf_{v}^{(1)}(S^c)$, and by convention we let $\pbf(S) = \sum_{u \in S} p_u$ for any distribution vector $\pbf = (p_u)_{u \in V}$ over $V$.
+We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
+\begin{lemma}
+	\label{lem: local_spread_G}
+	\begin{itemize}
+		\item If $\pibf(S) \leq s(G)$, then for every $u \in S$, $\qbf_u^{(1)}(S) \geq 1/10$.
+		\item For any $v, u \in V$, and $m \in N$ greater than $0$, $q_{vu}^{(m)}/ \pi_{\min} \leq 1/s(G)$.
+	\end{itemize}
+
+\end{lemma}
+
+\begin{proof}
+	If $t = \pibf(S) \leq \frac{9 D_{\min}}{10} \pi_{\min}$, divide both sides by $\pi_{\min}$ to obtain
+	\begin{equation*}
+	\abs{S} \leq \frac{9 D_{\min}}{10}
+	\end{equation*}
+	which implies $\qbf_{v}^{(1)}(S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.
+
+	The second statement follows from the fact $q_{vu}^{(m)} \leq 1/D_{\min}$ for any $m$.
+\end{proof}
+
+The local spread facilitates conversion between $\tau_{\infty}(\qbf_v; G)$ and the more easily manageable \emph{total variation} mixing time, given by
+\begin{equation*}
+\tau_1(\rhobf; G) = \min\biggl\{m: \forall v \in V, \norm{\rhobf_v - \pibf}_{TV} \leq 1/4 \biggr\}
+\end{equation*}
+where 
+\begin{equation}
+\label{eqn: uniform_random_walk}
+\rhobf_{v}^{(m)} = \frac{1}{m}\sum_{k = 1}^{m+1} \qbf_{v}^{m}, ~~ \rhobf_v = \left( \rhobf_{v}^{(1)}, \rhobf_{v}^{(2)}, \rhobf_{v}^{(3)} \ldots \right), ~~ \rhobf = \left( \rhobf_v \right)_{v \in V}
+\end{equation}
+and $\norm{\pbf - \pibf}_{TV} = \sum_{v \in V}\abs{p_v - \pi_v}$ is the total variation norm between distributions $\pbf$ and $\pibf$. 
+\begin{lemma}
+	\label{lem: tv_mixing_to_pointwise_mixing1}
+	For $\qbf$ as in \eqref{eqn: random_walk} and $\rhobf$ as in \eqref{eqn: uniform_random_walk},
+	\begin{equation*}
+	\tau_{\infty}(\qbf; G) \leq 2752 \tau_1(\rhobf; G) \log \left(4 \max\left\{1, \frac{1}{10 s(G)}\right\}\right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Masking dependence on $v$ for the moment, let
+	\begin{equation*}
+	\Delta_u^{(m)} = q_{vu}^{(m)} - \pi_u, ~~ \delta_u^{(m)} = \frac{\Delta_u^{(m)}}{\pi_u}
+	\end{equation*}
+	and $\Deltabf^{(m)} = (\Delta_u^{(m)})_{u \in V}$, $\deltabf^{(m)} = (\delta_u^{(m)})_{u \in V}$. For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pibf)$ norm is given by
+	\begin{equation*}
+	\norm{\Deltabf}_{L^p(\pibf)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi_u \right)^{1/p}
+	\end{equation*}
+	To go between the $L^{\infty}(\pibf)$ and $L^{1}(\pibf)$ norms, we have
+	\begin{align*}
+	\norm{\deltabf^{(2m)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(m)}}^2_{L^{2}(\pi)} \\
+	& = \norm{(\deltabf^{(m)})^2}_{L^{1}(\pi)} \\
+	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}
+	\end{align*}
+	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
+	\begin{align*}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q_{vu}^{(m)}}{\pi_u} \right\} \\
+	& \overset{(iii)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\}
+	\end{align*}
+	where $(iii)$ follows from Lemma \ref{lem: local_spread_G}.
+
+	Now, we leverage the following well-known fact (\textcolor{red}{PhD thesis of Montenegro}): for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
+	\begin{equation*}
+	\norm{\qbf_v^{(m)} - \pibf}_{TV} \leq \epsilon.
+	\end{equation*}
+	But $\norm{\qbf_v^{(m)} - \pibf}_{TV}$ is exactly $\norm{(\deltabf^{(m)})}_{L^{1}(\pi)}$. Therefore, picking 
+	\begin{equation*}
+	m_0 = \tau_1(\qbf_v^{(m)}; G) \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
+	\end{equation*} implies $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_0$.  Then, 
+	\begin{equation*}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u}\left\{ \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \right\}.
+	\end{equation*}
+	and since none of the above depended on a specific choice for $v$, the supremum can be taken over all seed nodes $v$ as well. Thus $\tau_{\infty}(\qbf^{(m)}; G) \leq 2m_0$.
+
+	Finally, it is known (\textcolor{red}{PhD thesis of Montenegro}) that
+	\begin{equation*}
+	\tau_{1}(\qbf^{(m)}; G) \leq 1376 \tau_{1}(\rhobf^{(m)}; G)
+	\end{equation*}
+	and so the desired result holds.
+
+\end{proof}
+
+The second key quantity is the \emph{conductance function}
+\begin{equation*}
+\Phi(t; G) := \min_{\substack{S \subseteq V, \\ \pibf(S) \leq t} } \Phi(S; G) ~~~~~~~ (\pi_{\min} \leq t < 1)
+\end{equation*}
+where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}.
+
 \subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
@@
 		\begin{equation*}
-		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
 		\end{equation*}
@@
 		\begin{equation*}
-		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\log\left(\frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
 		\end{equation*}
-		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$. 
+		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
 	\end{itemize}
@@
 	\label{eqn: kannan_1}
-	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{1}{t}\right)\right\}.
+	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{t}\right)\right\}.
 	\end{equation}
@@
 	\end{equation*}
+
 	and plugging these estimates in to \eqref{eqn: kannan_1} gives the final bound on $\widetilde{\Phi}_{\Pbb,r}(t)$.
-The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows immediately from application of Lemma \ref{lem: stepwise_approximation}.
+The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
 \end{proof}
@@
 	\label{eqn: consistency_of_stepapprox_conductance_function}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
 	\end{equation}
@@
 \begin{equation*}
-\lim_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
+\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
 \end{equation*}
@@
 \begin{equation*}
-\lim_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
 \end{equation*}
 uniformly over $[1/m,1/2]$.
-But by Lemma \ref{lem: stepwise_approximation}, $\widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{n,r}$, so we have shown \eqref{eqn: consistency_of_stepapprox_conductance_function}.
 \end{proof}
@@
 	\norm{\deltabf^{(2t)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(t)}}^2_{L^{2}(\pi)} \\
-	& = \norm{(\deltabf^{(t)})^2}^2_{L^{1}(\pi)} \\
+	& = \norm{(\deltabf^{(t)})^2}_{L^{1}(\pi)} \\
 	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)}
@@
 \end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}]
+	Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
+	\begin{equation*}
+	\widetilde{q}_n^{(t)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
+	\end{equation*}
+	be the distribution of a random walk over the subgraph $G_{n,r}[\Csig[\Xbf]]$ after $t$.
+For simplicity, we will refer to the subgraph $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$ hereafter.
+Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.
+
+	By Lemma \ref{lem: tv_mixing_to_pointwise_mixing}, 
+	\begin{equation*}
+	\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{10 \widetilde{\pi}_{1,n}}\right) \right\}
+	\end{equation*}
+
+	We first upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: montenegro}, we have that
+	\begin{equation*}
+	\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{x = \widetilde{\pi}_{1,n}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx\right)
+	\end{equation*}
+	We set aside the constant term for the moment and turn to the integral. By Lemma \ref{lem: local_spread_lb},
+	\begin{equation*}
+	\limsup_{n \to \infty}\int_{x = \widetilde{\pi}_{1,n}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} \leq \limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx
+	\end{equation*}
+	where $\pi_{1,\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$.
+We now replace the discrete conductance function $\widetilde{\Phi}_{n,r}$ by the continuous conductance function $\overline{\Phi}_{n,r}$:
+	\begin{align*}
+	\limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx & \overset{(i)}{\leq} \limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{n,r}^2(x)} dx \\
+	& = \int_{x = \pi_{1,\Pbb,r}}^{1/2} \limsup_{n \to \infty} \frac{4}{\overline{\Phi}_{n,r}^2(x)} dx \\
+	& \overset{(ii)}{\leq} \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{\Pbb,r}^2(x)} dx \\
+	\end{align*}
+	where $(i)$ follows from Lemma \ref{lem: stepwise_approximation} and $(ii)$ from Lemma \ref{lem: consistency_of_conductance_function} (along with the continuous mapping theorem).
+Now, we make use of the lower bound on the continuous conductance function of Lemma \ref{lem: continuous_conductance_lb}:
+	\begin{align*}
+	& \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{\Pbb,r}^2(x)} dx \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
+	\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{d}{x} dx + \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{81dD^2}{r^2x \Log(\frac{\Lambda_{\sigma}^2}{x\lambda_{\sigma}^2})}  \right) dx \\
+	& \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
+	\underbrace{\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{d}{x} dx}_{:= \mathcal{J}_1} + 
+	81\underbrace{\int_{x = \pi_{1,\Pbb,r}}^{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)} \frac{dD^2}{r^2x \log(\frac{\Lambda_{\sigma}^2}{x\lambda_{\sigma}^2})}}_{:= \mathcal{J}_2} +
+	81\underbrace{\int_{x = \lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)}^{1/2} \frac{dD^2}{r^2x \log(1 + \frac{4 \lambda_{\sigma}^2}{\Lambda_{\sigma}^2})}}_{:= \mathcal{J}_3}  \right)
+	\end{align*}
+\end{proof}
+
+Simple integration yields the following upper bounds on $\mathcal{J}_1, \mathcal{J}_2, \mathcal{J}_3$:
+\begin{align*}
+\mathcal{J}_1 & \leq d^2 \log\left( \frac{2D\Lambda_{\sigma}^2}{r\lambda_{\sigma}^2} \right) \\
+\mathcal{J}_2 & \leq \frac{dD^2}{r^2} \left[ \log\left(2d\right) + \log\left(\log\left(\frac{2d}{r}\right)\right) \right] \\
+\mathcal{J}_3 & \overset{(iii)}{\leq} 2 \frac{dD^2}{r^2} \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} \log\left(4 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right)
+\end{align*}
+where $(iii)$ uses the upper bound $\frac{1}{\log(1 + x)} \leq \frac{1}{x}$.
 

### 2019-01-18 icml/icml_local_density_clustering.tex
began restructuring proof of theorem 2
completed re-organization of Theorem 2

@@
 As a result, the \pprspace algorithm is shown to
-	extract sufficiently salient density clusters, and we 
-	analyze the sample-complexity of the algorithm.
+	extract sufficiently salient density clusters.
 \end{abstract}
@@
 	\begin{equation*}
-	\norm{x - x'} \leq D.
+	\norm{x - x'} \leq D,
 	\end{equation*}
+	and \textcolor{red}{$\Csig$ is a convex set.}
 \end{enumerate}
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
-Then, for any $r < \sigma/4d$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
-Then for
-	\begin{equation*}
-	\textcolor{red}{n \geq }
-	\end{equation*}
-	we have
-	\begin{equation*}
-	\Psi_{n,r}(\Cset[\Xbf]) \geq c_d \frac{r^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
-	\end{equation*}
-	for \textcolor{red}{$c_d = (1 + \epsilon)$}.
+Then, for any $r < \sigma/4d$, the following statement holds: with probability one
+	\begin{align}
+	\label{eqn: inverse_mixing_time_lower_bound}
+	\liminf_{n \to \infty} & \Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
+	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{d^2D^2}{r^2} \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
+	& c_3  + \log \log \mu \bigr) \biggr),
+	\end{align}
+	where $\mu = \log(\frac{2D}{r})$, $c_1 = 3852800/3$, $c_2 = 331776$, and $c_3 = \log 2$ are all dimension free, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
 \end{theorem}

### 2019-01-18 icml/icml_local_density_clustering_supplement.tex
completed re-organization of Theorem 2

--- 2019-01-16 icml/icml_local_density_clustering_supplement.tex
@@
 \newcommand{\rhobf}{\bm{\rho}}
+\newcommand{\Deltabf}{\bm{\Delta}}
+\newcommand{\deltabf}{\bm{\delta}}
+
+%%% Random walk vectors
 
@@
 
-As part of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}, we will require an estimate of a function $g(t)$ for $t \in [x_0, 1/2]$ for some $x_0 > 0$.
-For $m > 0$ and $x_0 = t_0 < t_1 < \ldots < t_m = 1/2$, define the \emph{stepwise approximation to $g$} to be $\bar{g}$, given by
-\begin{equation}
-\label{eqn: stepwise_approximation}
-\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
-\end{equation}
-\begin{lemma}
-	\label{lem: stepwise_approximation}
-	Fix
-	\begin{equation*}
-	g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [x_0, 1/2]$}
-	\end{equation*}
-	 If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $g(t) \geq \bar{g}(t)\geq g(t) / 2$.
-\end{lemma}
-\begin{proof}
-	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function.
-
-	By the concavity of the $\log$ function, 
-	\begin{equation*}
-	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
-	\end{equation*}
-	As a result,
-	\begin{equation*}
-	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
-	\end{equation*}
-\end{proof}
-
-The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
+The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also depends on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
 Formally, the discrete local spread $\pi_1(G)$ is given by
@@
 
-\begin{lemma}
-	\label{lem: local_spread_lb}
-	For $\Csig$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
-	\begin{equation*}
-	\liminf_{n \to \infty}~ \widetilde{\pi}_{1,n} \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}
-	\end{equation*}
-\end{lemma}
-
-\textcolor{red}{Prove Lemma \ref{lem: local_spread_lb}}.
+\textcolor{red}{Prove Lemma \ref{lem: local_spread_lower_bound}}.
 
@@
 
-\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
-
-\textcolor{red}{Give proof structure.}
-
-We begin by introducing some more notation.
-Take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf$.
-We slightly overload notation and let the \emph{conductance function} be given by
+\subsection{Mixing time on graphs}
+For $N \in \mathbb{N}$ and a set $V$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf = (\pi_u)_{u \in V}$ where $\pi_v = \frac{\Dbf_{vv}}{\vol(V; G)}$.
+For $v \in V$,
+\begin{equation}
+\label{eqn: random_walk}
+q_{vu}^{(m)} = e_v\Wbf^m e_u, ~~ \qbf_{v}^{(m)} = \left(q_{vu}^{(m)}\right)_{u \in V}, ~~ \qbf_v = (\qbf^{(1)}_{v\cdot},\qbf^{(2)}_{v\cdot}, \ldots), 
+\end{equation}
+denote respectively the $m$-step transition probability, distribution, and sequence distributions of the random walk over $G$ originating at $v$.
+Letting $\qbf = (\qbf_v)_{v \in V}$, the relative pointwise mixing time is thus
 \begin{equation*}
-\Phi(t; G) := \min_{\substack{S \subseteq V \\ \pi(S) \leq t} } \Phi(S; G)
+\tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
 \end{equation*}
 
-We will pay special attention to the conductance function evaluated over the subgraph $G_{n,r}[\Csig[\Xbf]]$.
-For ease of notation, we therefore introduce $\widetilde{\Phi}_{n,r}(t) = \Phi(t; G_{n,r}[\Csig[\Xbf]])$.
+Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined to be
+\begin{equation*}
+s(G) := \frac{9D_{\min}}{10}\pi_{\min} 
+\end{equation*}
+for $D_{\min} := \min_{v \in V} \Dbf_{vv}$ and $\pi_{\min} := D_{\min} / \vol(V; G)$.
 
-Lemma \ref{lem: montenegro} is from the \textcolor{red}{PhD thesis of Montenegro.} It leverages the conductance function to produce an upper bound on the \textcolor{red}{total variation distance} between the random walk
-\begin{equation*}
-\rhobf^t = \frac{1}{t} \sum_{s = 1}^{t} e_v \Wbf^s
-\end{equation*}
-and the stationary distribution $\pibf$.
+%\inf \set{t: \forall S \subset V ~\text{with}~ \pi(S) = t, \beta(S) \leq 1/10}
+%\end{equation*}
+where $\beta(S) := \inf_{v \in S} \qbf_{v}^{(1)}(S^c)$, and by convention we let $\pbf(S) = \sum_{u \in S} p_u$ for any distribution vector $\pbf = (p_u)_{u \in V}$ over $V$.
+We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
+\begin{lemma}
+	\label{lem: local_spread_G}
+	\begin{itemize}
+		\item If $\pibf(S) \leq s(G)$, then for every $u \in S$, $\qbf_u^{(1)}(S^c) \geq 1/10$.
+		\item For any $v, u \in V$, and $m \in N$ greater than $0$, $q_{vu}^{(m)}/ \pi_{\min} \leq 1/s(G)$.
+	\end{itemize}
 
-\begin{lemma}
-	\label{lem: montenegro}
-	Let $\Wbf$ be the random walk matrix over a graph $G = (V,E)$, with stationary distribution $\pibf$. Then, for any $v \in V$:
-	\begin{equation*}
-	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{t}\left(\frac{4}{\Phi^2(\pi_1(G); G)} + \int_{x = \pi_1(G)}^{1/2} \frac{4}{x \Phi^2(x; G)} dx\right) \right\}
-	\end{equation*}
-	where $\pi_1(G)$ is defined as in \eqref{eqn: local_spread}.
 \end{lemma}
@@
 \begin{proof}
-	In \textcolor{red}{the PhD thesis of Montenegro}, letting
+	If $t = \pibf(S) \leq \frac{9 D_{\min}}{10} \pi_{\min}$, divide both sides by $\pi_{\min}$ to obtain
 	\begin{equation*}
-	h^t(x_0) = \sup_{S: \pi(S) < x_0}  \bigl(\rhobf^t(S) - \pibf(S) \bigr)
+	\abs{S} \leq \frac{9 D_{\min}}{10}
 	\end{equation*}
-	the following statement is shown: for $\pi_{\min} < x_0 < 1/2$, 
-	\begin{equation*}
-	\norm{\rho^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, h^t(x_0) +  \frac{70}{t}\left(\frac{4}{\Phi^2(x_0); G)} + \int_{x = x_0}^{1/2} \frac{4}{x \Phi^2(x; G)}\right) \right\}
-	\end{equation*}
-	It is also observed therein that the function $h^t(x)$ is decreasing for any fixed $x$, as $t$ increases.
-All that remains for us to show is that $h^s(\pi_1(G)) \leq 1/10$ for some $s \leq t$.
-We choose $s = 1$, and note that for any set $S \subset V$ with $\pibf(S) \leq \pi_1(G)$,
-	\begin{equation*}
-	\rhobf^1(S) \leq \frac{\abs{S}}{d_{\min}(G)} \leq \frac{\pibf(S) \vol(V; G)}{d_{\min}(G)^2} \leq \frac{1}{10},
-	\end{equation*}
-	where we use the fact that $\pibf(S) \geq \frac{\abs{S} d_{\min}(G)}{\vol(V; G)}$.
+	which implies $\qbf_{v}^{(1)}(S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.
+
+	The second statement follows from the fact $q_{vu}^{(m)} \leq 1/D_{\min}$ for any $m$.
 \end{proof}
 
-We turn to lower bounding $\widetilde{\Phi}_{n,r}(t)$.
-First, we exhibit a lower bound on a continuous space analogue, over the set $\Csig$.
-Let $\nu_{\Pbb}(\cdot)$ denote the weighted volume; formally, for $\Sset \subset \Rd$
+The local spread facilitates conversion between $\tau_{\infty}(\qbf_v; G)$ and the more easily manageable \emph{total variation} mixing time, given by
+\begin{equation*}
+\tau_1(\rhobf; G) = \min\biggl\{m: \forall v \in V, \norm{\rhobf_v - \pibf}_{TV} \leq 1/4 \biggr\}
+\end{equation*}
+where 
+\begin{equation}
+\label{eqn: uniform_random_walk}
+\rhobf_{v}^{(m)} = \frac{1}{m}\sum_{k = 1}^{m+1} \qbf_{v}^{m}, ~~ \rhobf_v = \left( \rhobf_{v}^{(1)}, \rhobf_{v}^{(2)}, \rhobf_{v}^{(3)} \ldots \right), ~~ \rhobf = \left( \rhobf_v \right)_{v \in V}
+\end{equation}
+and $\norm{\pbf - \pibf}_{TV} = \sum_{v \in V}\abs{p_v - \pi_v}$ is the total variation norm between distributions $\pbf$ and $\pibf$. 
+\begin{lemma}
+	\label{lem: tv_mixing_to_pointwise_mixing1}
+	For $\qbf$ as in \eqref{eqn: random_walk} and $\rhobf$ as in \eqref{eqn: uniform_random_walk},
+	\begin{equation*}
+	\tau_{\infty}(\qbf; G) \leq 2752 \tau_1(\rhobf; G) \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\}\right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Masking dependence on the starting vertex $v$ for the moment, let
+	\begin{equation*}
+	\Delta_u^{(m)} = q_{vu}^{(m)} - \pi_u, ~~ \delta_u^{(m)} = \frac{\Delta_u^{(m)}}{\pi_u}
+	\end{equation*}
+	and $\Deltabf^{(m)} = (\Delta_u^{(m)})_{u \in V}$, $\deltabf^{(m)} = (\delta_u^{(m)})_{u \in V}$. For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pibf)$ norm is given by
+	\begin{equation*}
+	\norm{\Deltabf}_{L^p(\pibf)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi_u \right)^{1/p}
+	\end{equation*}
+	To go between the $L^{\infty}(\pibf)$ and $L^{1}(\pibf)$ norms, we have
+	\begin{align*}
+	\norm{\deltabf^{(2m)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(m)}}^2_{L^{2}(\pi)} \\
+	& = \norm{(\deltabf^{(m)})^2}_{L^{1}(\pi)} \\
+	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}
+	\end{align*}
+	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
+	\begin{align*}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q_{vu}^{(m)}}{\pi_u} \right\} \\
+	& \overset{(iii)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\}
+	\end{align*}
+	where $(iii)$ follows from Lemma \ref{lem: local_spread_G}.
+
+	Now, we leverage the following well-known fact (\textcolor{red}{PhD thesis of Montenegro}): for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
+	\begin{equation*}
+	\norm{\qbf_v^{(m)} - \pibf}_{TV} \leq \epsilon.
+	\end{equation*}
+	But $\norm{\qbf_v^{(m)} - \pibf}_{TV}$ is exactly $\norm{(\deltabf^{(m)})}_{L^{1}(\pi)}$. Therefore, picking 
+	\begin{equation*}
+	m_0 = \tau_1(\qbf_v^{(m)}; G) \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
+	\end{equation*} implies $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_0$.  Then, 
+	\begin{equation*}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u}\left\{ \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \right\}.
+	\end{equation*}
+	and since none of the above depended on a specific choice for $v$, the supremum can be taken over all starting vertices $v$ as well. Thus $\tau_{\infty}(\qbf^{(m)}; G) \leq 2m_0$.
+
+	Finally, it is known (\textcolor{red}{PhD thesis of Montenegro}) that
+	\begin{equation*}
+	\tau_{1}(\qbf^{(m)}; G) \leq 1376 \tau_{1}(\rhobf^{(m)}; G)
+	\end{equation*}
+	and so the desired result holds.	
+\end{proof}
+
+The second key quantity is the \emph{conductance function}
+\begin{equation}
+\label{eqn: conductance_function}
+\Phi(t; G) := \min_{\substack{S \subseteq V, \\ \pibf(S) \leq t} } \Phi(S; G) ~~~~~~~ (\pi_{\min} \leq t < 1)
+\end{equation}
+where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}.
+
+Lemma \ref{lem: expansion_to_tv_distance} leverages the conductance function and local spread to produce an upper bound on the total variation distance between $\rhobf_{v}^{(m)}$ and $\pibf.$
+\begin{lemma}
+	\label{lem: expansion_to_tv_distance}
+	If $D_{\min} > 10$, for any $v \in V$:
+	\begin{equation*}
+	\norm{\rhobf_v^{(m)} - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{m}\left(\frac{20}{9} + \int_{t = s'(G)}^{1/2} \frac{4}{t \Phi^2(t; G)} dt\right) \right\}
+	\end{equation*}
+	where $s'(G) = s(G) / 9$.
+\end{lemma}
+
+To prove Lemma \ref{lem: expansion_to_tv_distance} we first introduce a generalization of $\Phi(t;G) \cdot \Phi(t;G)$ known as a blocking conductance function.
+\footnote{For more details, see \textcolor{red}{PhD thesis of Montenegro}}
+
+\begin{definition}[Blocking Conductance Function of \textcolor{red}{PhD thesis of Montenegro}]
+	\label{def: blocking_conductance_function}
+	For $t_0 \geq \pi_{\min}$, a function $\phi(t; G): [t_0, 1/2] \to [0,1]$ is a \emph{blocking conductance function} if for all $S \subset V$ with $\pibf(S) = t \in [t_0, 1/2]$, either of the following hold:
+	\begin{enumerate}
+		\item \emph{Exterior inequality.} For all $y \in \left[\frac{1}{2}t, t\right]: \phi_{int}(S) \geq \phi(\max\{t_0,y\})$
+		\item \emph{Interior inequality.} For all $y  \in \left[t, \frac{3}{2}t\right]: \phi_{ext}(S) \geq \phi(\max\{y,1 - y\})$.
+	\end{enumerate}
+	where $\phi_{int}$ and $\phi_{ext}$ are defined respectively as
+	\begin{align*}
+	\phi_{int}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2} \\
+	\phi_{ext}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S^c \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2}
+	\end{align*}
+\end{definition}
+
+\begin{theorem}[\textcolor{red}{PhD thesis of Montenegro} Theorem 3.2]
+	\label{thm: montenegro}
+	Consider $\phi(t; G): [t_0, 1/2] \to [0,1]$ a blocking conductance function. Then, letting
+	\begin{equation*}
+	h^m(t_0) = \sup_{S: \pibf(S) < t_0}  \bigl(\rhobf_v^{(m)}(S) - \pibf(S) \bigr)
+	\end{equation*}
+	the following statement holds: if $\phi$ is a blocking conductance function,
+	\begin{align*}
+	\norm{\rhobf_v^{(m)} - \pibf}_{TV} & \leq \max\left\{ \frac{1}{4}, h^1(t_0) +  \frac{70}{m}\left(\frac{1}{\phi(t_0; G)} + \int_{t = t_0}^{1/2} \frac{4}{t \phi(t; G)} dt\right) \right\} \\
+	\end{align*}
+\end{theorem}
+
+Note that in \textcolor{red}{PhD thesis of Montenegro} this theorem is stated with respect to $h^0$.
+However, in the subsequent proof it holds with respect to $h^m$, and it is observed that $h^m$ is decreasing in $m$.
+For our purposes it is more useful to state it with respect to $h^1$, as we have done.
+
+\begin{proof}[Proof of Lemma \ref{lem:  expansion_to_tv_distance}]
+	Consider the function $\phi_0(t, G): [s(G), 1/2] \to [0,1]$ defined by
+	\begin{equation}
+	\label{eqn: local_spread_blocking_conductance_function}
+	\phi_0(t; G) = 
+	\begin{cases}
+	\frac{1}{5}, ~~~~~~~~~~~~ t = s'(G) \\
+	\frac{1}{4} \Phi^2(t; G), ~ t \in \left(s'(G), 1/2\right] \\
+	\end{cases}
+	\end{equation}
+	\begin{lemma}
+		\label{lem: local_spread_blocking_conductance_function}
+		If $D_{\min} > 10$, $\phi_0$ is a blocking conductance function.
+	\end{lemma}
+	We take Lemma \ref{lem: local_spread_blocking_conductance_function} as given, and defer the proof until after the proof of Lemma \ref{lem: expansion_to_tv_distance}.
+
+	Lemma \ref{lem: local_spread_blocking_conductance_function} and Theorem \ref{thm: montenegro} together yield:
+	\begin{equation*}
+	\norm{\rhobf^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, h^1(s'(G)) +  \frac{70}{m}\left(5 + \int_{t = s'(G)}^{1/2} \frac{4}{t \Phi^2(t; G)}\right) \right\}
+	\end{equation*}
+
+	Then, $h^1(s'(G)) \leq 1/10$ follows exactly from the proof of Lemma \ref{lem: local_spread_G}, except now $\pibf(S) \leq s'(G)$ results in the sharper bound of $\qbf_u^{(1)}(S^c) \geq 9/10$ for every $u \in S$.
+\end{proof}
+\begin{proof}[Lemma \ref{lem: local_spread_blocking_conductance_function}]
+	The condition $D_{\min} > 10$ ensures that $s(G) \geq \pi_{\min}$.
+
+	It is known that $\frac{1}{4} \Phi^2(x;G)$ satisfies the exterior inequality for all $t \in (\pi_{\min}, 1/2]$.
+
+	For $t = s'(G)$ we will instead use the interior inequality.
+For any $S$ such that $\pibf(S) \leq s'(G)$, the following statement holds: for every $u \in S$, $\cut(u, S^c; G) \geq 9/10 \cdot \deg(u; G)$.
+	Fixing $\lambda = \pi(S)/2$, we have
+	\begin{align*}
+	\phi_{int}(S) & \geq \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
+	& \geq  \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{9 \lambda \sum_{u \in S \setminus B} \deg(u; G)}{10 \vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
+	& \geq \frac{9\lambda^2}{20[\lambda^2(1 - \lambda)^2]} \geq \frac{9}{20}. 
+	\end{align*} 
+\end{proof}
+
+\subsection{Population-level conductance function.}
+
+We will make use of the above theory with respect to the conductance function $\Phi(t; G_{n,r}[\Csig(\Xbf)])$.
+First, however, we introduce a population-level analogue to $\Phi(t; G_{n,r}[\Csig(\Xbf)])$ over the set $\Csig$, which we denote $\widetilde{\Phi}_{\Pbb,r}$.
+(In general, we will adopt the convention of using $\widetilde{f}$ to denote functionals computed with respect to $\Csig$.)
+
+For $\Sset \subset \Rd$
 \begin{equation*}
@@
 \end{equation*} 
+is the weighted volume.
 
-The $r$-ball walk over $\Csig$ is a Markov chain with transition probability for $x \in \Csig, \Sset, \Sset' \subset \Csig$ given by,
+The $r$-ball walk over $\Csig$ is a Markov chain. For $x \in \Csig$ and $\Sset, \Sset' \subset \Csig$ the transition probability is given by
 \begin{equation*}
-P_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ Q_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx. 
+\widetilde{P}_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ \widetilde{Q}_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx,
 \end{equation*}
@@
 \begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}
+\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}.
 \end{equation*}
-Lemma \ref{lem: continuous_conductance_lb} (\textcolor{red}{a weighted analogue of Theorem 4.6 of Kannan}) provides a lower bound on $\widetilde{\Phi}_{\Pbb, r}(t)$, as well as a stepwise approximation to $\widetilde{\Phi}_{\Pbb, r}$.
+
+For $m > 0$ and $0 < t_0 < t_1 < \ldots < t_m < 1$, denote the \emph{stepwise approximation to $g$} by $\bar{g}$, defined as
+\begin{equation}
+\label{eqn: stepwise_approximation}
+\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
+\end{equation}
+The stepwise approximation will be important to showing the consistency results of Section \textcolor{red}{(A.7)} hold across the entire conductance function.
+Lemma \ref{lem: stepwise_approximation} shows that the approximation will not overly degrade our estimates of the population-level conductance function.
 \begin{lemma}
-	\label{lem: continuous_conductance_lb}
+	\label{lem: stepwise_approximation}
+	\begin{itemize}
+		\item For any function $f$ monotone decreasing in $t$ on the interval $[t_0,t_m]$, $\bar{f}(t) \leq f(t)$ for all $t \in [t_0,t_m]$.
+		\item Fix
+		\begin{equation*}
+		g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [t_0, 1/2]$}
+		\end{equation*}
+		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq t_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+	The first statement is immediately obvious, and we turn to proving the second.
+
+	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.
+
+	By the concavity of the $\log$ function, 
+	\begin{equation*}
+	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
+	\end{equation*}
+	As a result,
+	\begin{equation*}
+	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
+	\end{equation*}
+\end{proof}
+
+\begin{theorem}[Restatement of \textcolor{red}{Kannan 2004} Theorem 4.6]
+	\label{thm: kannan}
+	Let $K \subset \Rd$ be a convex body of diameter $D$. Then for any $\Sset \subset K$ with $\pi_{\nu,r}(\Sset) \leq 1/2$,
+	\begin{equation}
+	\label{eqn: kannan}
+	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{\pi_{\nu,r}(\Sset)}\right)\right\}.
+	\end{equation}
+\end{theorem}
+
+\begin{lemma}
+	\label{lem: continuous_conductance_lower_bound}
 	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
@@
 		\begin{equation*}
-		m = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
+		M = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
 		\end{equation*}
-		 and $t_i = (i + 1)/m$ for $i = 0, \ldots, m - 1$. Then, for $1/m < t < 1/2$
+		and $t_i = (i + 1)/M$ for $i = 0, \ldots, m - 1$. Then, for $1/M < t < 1/2$
 		\begin{equation*}
-		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\log\left(\frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
 		\end{equation*}
-		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$. 
+		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{M - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
 	\end{itemize}
-
 \end{lemma}
-\begin{proof}
-	We begin by stating directly the result of \textcolor{red}{Kannan et al.}: for $0 < t < 1/2$, and any $S$ such that $\pi_{\nu,r}(S) = t$,
-	\begin{equation}
-	\label{eqn: kannan_1}
-	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{1}{t}\right)\right\}.
-	\end{equation}
-	Now, we note that
+Before we prove Lemma \ref{lem: continuous_conductance_lower_bound}, note that the choice of $M$ is made to ensure $t_0$ is greater than the local spread of $G_{n,r}\left[\Csig[\Xbf]\right]$, as we will see in Section \ref{sec: consistency}.
+\begin{proof}[Proof of Lemma \ref{lem: continuous_conductance_lower_bound}]
+	We note that
 	\begin{equation*}
@@
 	\end{equation*}
-	and plugging these estimates in to \eqref{eqn: kannan_1} gives the final bound on $\widetilde{\Phi}_{\Pbb,r}(t)$.
-The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows immediately from application of Lemma \ref{lem: stepwise_approximation}.
+
+	Plugging these estimates in to \eqref{eqn: kannan} gives
+	\begin{equation*}
+	\frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \pi_{\Pbb,r}(\Sset)}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+	\end{equation*}
+	and since the right hand side is decreasing in $\pi_{\Pbb,r}(\Sset)$, the desired lower bound holds on $\widetilde{\Phi}_{\Pbb,r}(t)$.
+The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
 \end{proof}
+
+\subsection{Consistency of local spread and conductance function.}
+\label{sec: consistency}
+
+For notational ease, we write 
+\begin{equation*}
+\widetilde{\Phi}_{n,r}(t) = \Phi(t; G_{n,r}[\Csig[\Xbf]]), ~~ \widetilde{s}_{n,r} = s(G_{n,r}[\Csig[\Xbf]])
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: local_spread_lower_bound}
+	For $\Csig$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
+	\begin{equation*}
+	\liminf_{n \to \infty}~ \widetilde{s}_{n,r} \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}
+	\end{equation*}
+\end{lemma}
+
+\textcolor{red}{Prove Lemma \ref{lem: local_spread_lower_bound}}.
 
@@
 	\label{lem: consistency_of_conductance_function}
-	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, fix any $0 < t < 1/2$. Then the following statement holds: with probability one, as $n \to \infty$,
-	\begin{equation*}
+	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
+	\begin{equation}
+	\label{eqn: pointwise_consistency_of_conductance_function}
 	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t)
-	\end{equation*}
-	As a consequence, $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
+	\end{equation}
+	As a consequence, for $M$ and $(t_i)_{i=0}^{M-1}$ defined as in Lemma \ref{lem: continuous_conductance_lower_bound}, we have that
 	\begin{equation}
 	\label{eqn: consistency_of_stepapprox_conductance_function}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
 	\end{equation}
 \end{lemma}
-Lemma \ref{lem: consistency_of_conductance_function} stems from \textcolor{red}{Garcia Trillos 16}, with a pair of notable distinctions: here, we do not allow the radius $r$ to go to zero, but rather set it to be constant, and in the minimization we have an additional constraint on the measure $\pi(\cdot)$, in both the discrete and continuous functionals.
-As such, we will need to re-prove a number of the statements of \textcolor{red}{Garcia Trillos 16} to work in this context.
-We defer this work to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}, and here will only show that  \eqref{eqn: consistency_of_stepapprox_conductance_function} is implied immediately by the pointwise result.
+We defer the proof of pointwise consistency to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}.
+For now, we show assume  that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
 
@@
 	\begin{equation*}
-\lim_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
 	\end{equation*}
@@
 	\begin{equation*}
-\lim_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
 	\end{equation*}
 	uniformly over $[1/m,1/2]$.
-But by Lemma \ref{lem: stepwise_approximation}, $\widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{n,r}$, so we have shown \eqref{eqn: consistency_of_stepapprox_conductance_function}.
 \end{proof}
-
-Lemma \ref{lem: consistency_of_conductance_function} coupled with Lemma \ref{lem: montenegro} yields a bound on the total variation mixing time.
-\begin{lemma}
-
-\end{lemma}
 
@@
 \label{subsection: proof_of_pointwise consitency_of_conductance_function}
+
+\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
+Throughout this proof, we will refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$.
+
+Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
+\begin{equation*}
+\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
+\end{equation*}
+Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.
+
+By Lemmas \ref{lem: local_spread_G} and \ref{lem: local_spread_lower_bound},
+\begin{align*}
+\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{\widetilde{s}_{n,r}}\right) \right\} \nonumber \\
+& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, 4d\log\left(\frac{2D \Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right) \right\}
+\end{align*}
+
+We now upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: expansion_to_tv_distance}, we have that
+\begin{equation}
+\label{eqn: mixing_time_bound_on_neighborhood_graph}
+\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{1,n}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right)
+\end{equation}
+(As $r$ remains constant and $n \to \infty$, $\Dbf_{xx} > C$ will be fulfilled for any $x \in \Csig[\Xbf]$, and any $C < \infty$.)
+We set aside the constant term for the moment and turn to the integral. By Lemma \ref{lem: local_spread_lower_bound},
+\begin{equation*}
+\limsup_{n \to \infty}\int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt \leq \limsup_{n \to \infty}\int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt
+\end{equation*}
+where $s_{\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$.
+We now replace the discrete conductance function $\widetilde{\Phi}_{n,r}$ by the stepwise approximation to the continuous conductance function, $\overline{\Phi}_{n,r}$:
+\begin{align*}
+\limsup_{n \to \infty}\int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt & \overset{(i)}{\leq} \limsup_{n \to \infty}\int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{n,r}^2(t)} dt \\
+& = \int_{s_{\Pbb,r}}^{1/2} \limsup_{n \to \infty} \frac{4}{t\overline{\Phi}_{n,r}^2(t)} dt\\
+& \overset{(ii)}{\leq} \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt \\
+\end{align*}
+where $(i)$ follows from Lemma \ref{lem: stepwise_approximation} and $(ii)$ from Lemma \ref{lem: consistency_of_conductance_function} (along with the continuous mapping theorem).
+Now, we make use of Lemma \ref{lem: continuous_conductance_lower_bound}:
+\begin{align*}
+& \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
+\int_{s_{\Pbb,r}}^{1/2} \frac{d}{t} dt + \int_{s_{\Pbb,r}}^{1/2} \frac{81dD^2}{r^2t \Log(\frac{\Lambda_{\sigma}^2}{t\lambda_{\sigma}^2})}  dt\right) \\
+& \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
+\underbrace{\int_{s_{\Pbb,r}}^{1/2} \frac{d}{t} dt}_{:= \mathcal{J}_1} + 
+81\underbrace{\int_{s_{\Pbb,r}}^{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)} \frac{dD^2}{r^2t \log(\frac{\Lambda_{\sigma}^2}{t\lambda_{\sigma}^2})} dt}_{:= \mathcal{J}_2} +
+81\underbrace{\int_{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)}^{1/2} \frac{dD^2}{r^2t \log(1 + \frac{4 \lambda_{\sigma}^2}{\Lambda_{\sigma}^2})}dt}_{:= \mathcal{J}_3}  \right)
+\end{align*}
+
+Computing a few simple integrals yields the following upper bounds on $\mathcal{J}_1, \mathcal{J}_2, \mathcal{J}_3$:
+\begin{align*}
+\mathcal{J}_1 & \leq d^2 \log\left( \frac{2D\Lambda_{\sigma}^2}{r\lambda_{\sigma}^2} \right) \\
+\mathcal{J}_2 & \leq \frac{dD^2}{r^2} \left[ \log\left(2d\right) + \log\left(\log\left(\frac{2D}{r}\right)\right) \right] \\
+\mathcal{J}_3 & \overset{(iii)}{\leq} 2 \frac{dD^2}{r^2} \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} \log\left(4 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right)
+\end{align*}
+where $(iii)$ uses the upper bound $\frac{1}{\log(1 + x)} \leq \frac{1}{x}$.
+
+Plugging these bounds in to \eqref{eqn: mixing_time_bound_on_neighborhood_graph} gives the desired upper bound on $\tau_{\infty}(\widetilde{q}_n, \widetilde{G}_{n,r})$, which translates to the lower bound of \eqref{eqn: inverse_mixing_time_lower_bound}.
 

### 2019-01-19 icml/icml_local_density_clustering_supplement.tex
midway through first lemma of pointwise consistency

@@
 \newcommand{\Log}{\mathrm{Log}}
+\newcommand{\TV}{\mathrm{TV}}
 
@@
 \newcommand{\pprspace}{{\sc PPR~}}
+
+%%% Tilde notation for quantities over the expansion set 
+\newcommand{\wn}{\widetilde{n}}
+\newcommand{\wX}{\widetilde{\Xbf}}
+\newcommand{\wx}{\widetilde{x}}
+\newcommand{\wu}{\widetilde{u}}
+\newcommand{\wPbb}{\widetilde{\Pbb}}
 
@@
 We defer the proof of pointwise consistency to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}.
-For now, we show assume  that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
+For now, we show that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
 
@@
 \label{subsection: proof_of_pointwise consitency_of_conductance_function}
+
+Throughout, let $\wn = \abs{\Csig[\Xbf]}$, $\wX = \Csig[\Xbf] = \set{\wx_1, \ldots, \wx_{\wn}}$, and 
+\begin{equation*}
+\widetilde{\Pbb}_n := \frac{1}{\wn} \sum_{\wx_i \in \wX} \delta_{\wx_i}
+\end{equation*}
+be the empirical distribution of $\wX$.
+For $S \subset \wX$, we will denote $\vol(S; \widetilde{G}_{n,r})$ by $\widetilde{\vol}_{n,r}(S)$, and likewise $\cut(S; \widetilde{G}_{n,r})$ by $\widetilde{\cut}_{n,r}(S)$.
+
+Consider a sequence of sets $(S_{\wn})_{\wn \in \mathbb{N}}$, with $u_{\wn} = \1_{S_{\wn}}$ the characteristic function of $S_{\wn}$. Similarly, for $\Sset \subset \Csig$ let $u = \1_{\Sset}$. 
+\begin{lemma}
+	If $u_{\wn} \overset{TL^1}{\to} u$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} \geq \widetilde{Q}_{\Pbb,r}(S, \Csig \setminus S) \cdot \left(\int_{\Csig \cap B(x,r)} f(x) \right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We note immediately that $n \to \infty$ implies $\wn \to \infty$ with probability one.
+
+	Now, we can write
+	\begin{align*}
+	 \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\wn^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \bigl( 1 - u_{\wn}(\wx_j) \1(\norm{\wx_i - \wx_j} \leq r) \bigr)  \\
+	& = \int_{\Csig} \left(\int_{\Csig \cap B(x,r)} u_{\wn}(x) \bigl( 1 - u_{\wn}(x') \bigr) d\Pbb_n(x') \right) d\Pbb_n(x) \\
+	& = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') \right) d\Pbb(x).
+	\end{align*}
+
+	Note that
+	\begin{align*}
+	\lim_{n \to \infty} \nu\bigl(B(T_{\wn}(x),r) \setminus B(x,r)\bigr) & = 0 \\
+	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0
+	\end{align*}
+	and therefore 
+	\begin{equation*}
+	\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') = \int_{\Csig \cap B(x,r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x')
+	\end{equation*}
+	Writing $u_{\wn} \circ T_{\wn}(x') = $
+\end{proof}
 

### 2019-01-19 icml/icml_local_density_clustering.tex
added theorem for non-convex setting

@@
 	\begin{equation*}
-	\norm{x - x'} \leq D,
+	\norm{x - x'} \leq D.
 	\end{equation*}
-	and \textcolor{red}{$\Csig$ is a convex set.}
 \end{enumerate}
@@
 
-We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
+We now provide a lower bound for $\Psi_{n,r}(\Cset[\Xbf])$.
+
+\begin{theorem}
+	\label{thm: inverse_mixing_time_lower_bound_nonconvex}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
+Then, for any $r < \sigma/4d$, the following statement holds with probability at least $1 - \delta$: Fix $\epsilon > 0$.
+Then, for
+	\begin{equation*}
+	n \geq ??
+	\end{equation*}
+	we have
+	\begin{align}
+	\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
+	1 / \Psi_{n,r}(\Csig[\Xbf]) & \leq \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
+	& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
+	\end{align}
+	where $\mu = \log(\frac{2D}{r})$, $c_1 = 19264000/3$, $c_2 = 331776$, and $c_3 = 128 9^d c_1/5 \cdot (1 + \epsilon)^4/(1 - \epsilon)^4$ are constants which depend only on dimension, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.
+\end{theorem}
+
 \begin{theorem}

### 2019-01-19 icml/icml_local_density_clustering_supplement.tex
added theorem for non-convex setting

@@
 \newcommand{\deltabf}{\bm{\delta}}
+\newcommand{\zbf}{\mathbf{z}}
 
@@
 \newcommand{\wx}{\widetilde{x}}
+\newcommand{\wz}{\widetilde{z}}
+\newcommand{\wbz}{\widetilde{\bf{z}}}
 \newcommand{\wu}{\widetilde{u}}
@@
 
-For both Lemmas \ref{lem: bounded_difference} and \ref{lem: bernstein}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed.
+For Lemmas \ref{lem: bounded_difference}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed.
 We will additionally assume the order-$m$ kernel function $k$ satisfies the boundedness property $\sup_{x_1, \ldots, x_m} \abs{k(x_1, \ldots, x_m)} \leq 1$.
@@
 	each with probability at least $1 - \delta$. 
+\end{lemma}
+
+We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
+\begin{lemma}
+	\label{lem: multiplicative_Hoeffding}
+	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
+	\begin{align*}
+	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
+	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
+	\end{align*}
 \end{lemma}
@@
 
-\subsection{Population-level conductance function.}
+\subsection{Conductance function and local spread: non-convex case.}
+
+We begin with some notation.
+Write $\Csig[\Xbf] = \wX$, and $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$.
+For $S \subset \wX$, let $\widetilde{\cut}_{n,r}(S) = \cut(S;\widetilde{G}_{n,r})$ and similarly $\widetilde{\vol}_{n,r}(S) = \vol(S;\widetilde{G}_{n,r})$.
+
+Consider $\zbf \subset \Csig$ such that  $\mathcal{N}_{\zbf} = \set{B(z,r/3): z \in \zbf}$ is a covering of $\Csig$, meaning $\mathcal{N}_{\zbf} \supseteq \Csig$. Then, we write
+\begin{align*}
+\widetilde{B}_{\min} = \min_{z \in \zbf} \abs{B(z,r/3) \cap \wX}, ~~
+\widetilde{D}_{\min} = \min_{\wx \in \wX} \abs{\widetilde{\cut}_{n,r}(x)} \\ \widetilde{B}_{\max} = \min_{z \in \zbf} \abs{B(z,r/3) \cap \wX}, ~~
+\widetilde{D}_{\max} = \min_{\wx \in \wX} \abs{\widetilde{\cut}_{n,r}(x)}
+\end{align*}
+Both the conductance function and local spread will depend heavily on these quantities. Lemma \ref{lem: ball_bounds} collects the bounds we will need.
+\begin{lemma}
+	\label{lem: ball_bounds}
+	For sufficiently large $n$, each of the following bounds hold with probability $1 - \delta$:
+	\begin{align*}
+	\widetilde{B}_{\max} & \leq \left(1 + \sqrt{3^d\frac{3(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma} \\
+	\widetilde{B}_{\min} & \geq \left(1 - \sqrt{3^d\frac{2(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \\
+	\widetilde{D}_{\max} & \leq \left(1 + \sqrt{\frac{3(\log n + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d r^d \Lambda_{\sigma} \\
+	\widetilde{D}_{\min} & \geq \left(1 - \sqrt{\frac{2(\log n + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \\
+	\left(1 - \sqrt{\frac{2 \log(1/\delta)}{n \lambda_d \nu_d \sigma^d}}\right) n \lambda_d \nu_d \sigma^d & \leq \widetilde{n} \leq \left(1 + \sqrt{\frac{3 \log(1/\delta)}{n \Lambda_d \nu_d D^d}}\right) n \Lambda_d \nu_d D^d
+	\end{align*}
+	where $\wn = \abs{\wX}$ and \textcolor{red}{$\beta_d = (1 - c_d\frac{r^2}{\sigma^2})$.}
+
+	In particular, fix $\epsilon > 0$. Then, for $n$ as specified in Theorem \ref{thm: inverse_mixing_time_lower_bound}:
+	\begin{align*}
+	\widetilde{B}_{\max} \leq \left(1 + \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma},& ~~ \widetilde{D}_{\max} \leq \left(1 + \epsilon \right) n \nu_d r^d \Lambda_{\sigma} \\
+	\widetilde{B}_{\min} \geq \left(1 - \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_{d},& ~~ \widetilde{D}_{\min} \geq \left(1 - \epsilon \right) n \nu_d r^d \lambda_{\sigma} \beta_{d} \\
+	(1 - \epsilon) n \lambda_{\sigma} \nu_d \sigma^d & \leq \widetilde{n} \leq (1 + \epsilon) n \Lambda_{\sigma} \nu_d D^d 
+	\end{align*}
+	each with probability at least $1 - \delta$.
+\end{lemma}
+The proof comes directly from Lemma \ref{lem: multiplicative_Hoeffding}, and we omit it.
+
+Now, we consider the conductance function and local spread computed over $\widetilde{G}_{n,r}$, which we refer to by
+\begin{equation*}
+\widetilde{\Phi}_{n,r}(t) = \Phi(t; \widetilde{G}_{n,r}), ~~ \widetilde{s}_{n,r} = s(\widetilde{G}_{n,r}).
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: local_spread_lower_bound}
+	For $\Csig$ and $n$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
+	\begin{equation*}
+	\widetilde{s}_{n,r} \geq \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2
+	\end{equation*}
+	with probability at least $1 - \delta$. 
+\end{lemma}
+
+\begin{proof}
+	The local spread can be written as
+	\begin{equation*}
+	\widetilde{s}_{n,r} = \frac{9}{10} \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \geq  \frac{9}{10} \frac{\widetilde{D}_{\min}^2}{\widetilde{D}_{\max} \wn}.
+	\end{equation*}
+	Then apply the relevant results of Lemma \ref{lem: ball_bounds}.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: non_convex_conductance_lower_bound}
+	For $\Csig$ and $n$ satisfying the conditions given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds:
+	\begin{equation*}
+	\widetilde{\Phi}_{n,r}(1/2) \geq \frac{\lambda_{\sigma}(1 - \epsilon)\beta_d}{4\Lambda_{\sigma}(1 + \epsilon)3^d} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)
+	\end{equation*}
+	with probability at least $1 - \delta$.
+\end{lemma}
+
+\begin{proof}
+	Fix $S \subset \wX$ with $\widetilde{\pi}_{n,r}(S) \leq 1/2$. Partition $\mathcal{N}_{\zbf} = \mathcal{N}_{\zbf}^+ \cup \mathcal{N}_{\zbf}^-$, where
+	\begin{align*}
+	\mathcal{N}_{\zbf}^- & = \set{B(z,r/3): 2 \Bigl\vert B(z,r/3) \cap S\Bigr\vert \leq \abs{B(z,r/3) \cap \wX} } \\
+	\mathcal{N}_{\zbf}^+ & = \mathcal{N}_{\zbf} \setminus \mathcal{N}_{\zbf}^-
+	\end{align*}
+	and correspondingly $S^- = \mathcal{N}_{\zbf}^- \cap S$, $S^+ = \mathcal{N}_{\zbf}^+ \cap S$, so
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} = \frac{\widetilde{\cut}_{n,r}(S^-; \widetilde{G}_{n,r} \setminus S) + \widetilde{\cut}_{n,r}(S^+; \widetilde{G}_{n,r} \setminus S)}{\widetilde{\vol}_{n,r}(S^-) + \widetilde{\vol}_{n,r}(S^+)}.
+	\end{equation*}
+	It is immediately apparent that the following bounds hold for all $S \subset \wX$:
+	\begin{align*}
+	\widetilde{\cut}_{n,r}(S^-; \widetilde{G}_{n,r} \setminus S) & \geq \frac{\abs{S^-} \widetilde{B}_{\min}}{2}\\
+	\widetilde{\vol}_{n,r}(S^-) & \leq \abs{S^-} \widetilde{D}_{\max} \\
+	\widetilde{\vol}_{n,r}(S^+) & \leq \widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) \1(\abs{N_{\zbf}^+} > 0 )
+	\end{align*}
+	If moreover $\abs{N_{\zbf}^+} < \abs{N_{\zbf}}$, then 
+	\begin{equation*}
+	\widetilde{\cut}_{n,r}(S^+; \widetilde{G}_{n,r} \setminus S) \geq \frac{\widetilde{B}_{\min}^2}{4} \1(\abs{N_{\zbf}^+} > 0)
+	\end{equation*}
+	follows from the fact that the graph $H_{n,r} = (\zbf, E_H)$, with ($z_i, z_j) \in E_H$ if $\norm{z_i - z_j} \leq r/3$, is connected. As a result, if $\abs{N_{\zbf}^+} < \abs{N_{\zbf}}$ we have
+	\begin{equation}
+	\label{eqn: normalized_cut_1}
+	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{ \widetilde{B}_{\min}}{4\widetilde{D}_{\max}} +  \frac{\widetilde{B}_{\min}^2}{8 \widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}
+	\end{equation}
+	using the inequality $2(A + B)/ (C + D) \geq A/C + B/D$ for $A,B,C,D$ non-negative.
+
+	If, on the other hand , $\abs{\mathcal{N}_{\zbf}^+} = \mathcal{N}_{\zbf}$, then \eqref{eqn: normalized_cut_1} holds with respect to $S^c$. Then, because $\widetilde{\pi}_{n,r}(S) \leq 1/2$, 
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \leq \frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)}
+	\end{equation*}
+	and so we get \eqref{eqn: normalized_cut_1}.
+Noting, as in the proof of Lemma \ref{lem: local_spread_lower_bound}, that  $\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) \leq \wn \cdot \widetilde{D}_{\max}$, the relevant results of Lemma \ref{lem: ball_bounds} yield the desired inequality.
+\end{proof}
+
+\subsection{Population-level conductance function: convex case.}
 
@@
 
-\subsection{Consistency of local spread and conductance function.}
+\subsection{Consistency of local spread and conductance function: convex case.}
 \label{sec: consistency}
-
-For notational ease, we write 
-\begin{equation*}
-\widetilde{\Phi}_{n,r}(t) = \Phi(t; G_{n,r}[\Csig[\Xbf]]), ~~ \widetilde{s}_{n,r} = s(G_{n,r}[\Csig[\Xbf]])
-\end{equation*}
-
-\begin{lemma}
-	\label{lem: local_spread_lower_bound}
-	For $\Csig$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
-	\begin{equation*}
-	\liminf_{n \to \infty}~ \widetilde{s}_{n,r} \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}
-	\end{equation*}
-\end{lemma}
-
-\textcolor{red}{Prove Lemma \ref{lem: local_spread_lower_bound}}.
 
@@
 
-\subsection{Proof of pointwise consistency of conductance function.}
+\subsection{Proof of pointwise consistency of conductance function: convex case.}
 \label{subsection: proof_of_pointwise consitency_of_conductance_function}
@@
 Consider a sequence of sets $(S_{\wn})_{\wn \in \mathbb{N}}$, with $u_{\wn} = \1_{S_{\wn}}$ the characteristic function of $S_{\wn}$. Similarly, for $\Sset \subset \Csig$ let $u = \1_{\Sset}$.
+
+\textcolor{red}{Give Lemma re: stagnating transportation maps and define $TL^1$ convergence.}
 \begin{lemma}
-	If $u_{\wn} \overset{TL^1}{\to} u$,
+	If $(u_{\wn}) \overset{TL^1}{\to} u$,
 	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} \geq \widetilde{Q}_{\Pbb,r}(S, \Csig \setminus S) \cdot \left(\int_{\Csig \cap B(x,r)} f(x) \right)
+	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} = \widetilde{Q}_{\Pbb,r}(S, \Csig \setminus S) \cdot \left(\int_{\Csig \cap B(x,r)} f(x) \right)
 	\end{equation*}
@@
 	\lim_{n \to \infty} \nu\bigl(B(T_{\wn}(x),r) \setminus B(x,r)\bigr) & = 0 \\
-	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0
+	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0.
 	\end{align*}
-	and therefore 
+	Therefore 
 	\begin{equation*}
-	\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') = \int_{\Csig \cap B(x,r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x')
+	\lim_{n \to \infty} \int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') = \lim_{n \to \infty} \int_{\Csig \cap B(x,r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x')
 	\end{equation*}
-	Writing $u_{\wn} \circ T_{\wn}(x') = $
+	and by an application of the bounded convergence theorem
+	\begin{align*}
+	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') \right) d\Pbb(x) = \nonumber \\
+	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x).
+	\end{align*}
+	Letting
+	\begin{align*}
+	\mathcal{I}_n^1 & = \int_{\Csig} \left(u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( u(x') - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) \\
+	\mathcal{I}_n^2 & = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x) - u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) \\
+	\end{align*}
+	we have
+	\begin{align}
+	\label{eqn: pointwise_convergence_1}
+	& \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) = \nonumber \\
+	& \int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\Pbb(x') \right\} d\Pbb(x) + \mathcal{I}_n^1 + \mathcal{I}_n^2. 
+	\end{align}
+
+	Recalling the definition of $\widetilde{Q}_{\Pbb,r}$, we have
+	\begin{align}
+	\label{eqn: pointwise_convergence_2}
+	\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset) & = \int_{\Sset} f(x) \widetilde{P}_{\Pbb,r}(x; \Csig \setminus \Sset) \nonumber \\
+	& = \frac{1}{\int_{\Csig \cap B(x,r)} f(x') dx'}\int_{\Sset} f(x) \int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' dx \nonumber \\
+	& = \frac{1}{\int_{\Csig \cap B(x,r)} f(x') dx'} \int_{\Csig} f(x) u(x){ \int_{\Csig \cap B(x,r)} (1 - u(x')) f(x') dx' }dx 
+	\end{align}
+	Since $(u_{\wn}) \overset{TL^1}{\to} u$, another application of the bounded convergence theorem yields $\lim_{n \to \infty} \mathcal{I}_n^1 = \lim_{n \to \infty} \mathcal{I}_n^2 = 0$.
+Therefore by \eqref{eqn: pointwise_convergence_1} and \eqref{eqn: pointwise_convergence_2} the final result holds.
 \end{proof}
@@
 \subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
+Throughout this proof, we will condition on the events of Lemmas \ref{lem: local_spread_lower_bound} and \ref{lem: non_convex_conductance_lower_bound},
+namely
+\begin{align*}
+\widetilde{s}_{n,r} & \geq \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2 \\
+\widetilde{\Phi}_{n,r}(1/2) & \geq \frac{\lambda_{\sigma}(1 - \epsilon)\beta_d}{4\Lambda_{\sigma}(1 + \epsilon)3^d} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)
+\end{align*}
+noting that for $n$ as chosen in Theorem \ref{thm: inverse_mixing_time_lower_bound} this will occur with probability at least $1 - \delta$.
+
+We refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$. Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
+\begin{equation*}
+\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
+\end{equation*}
+Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.
+
+By Lemma \ref{lem: local_spread_G},
+\begin{align*}
+\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{\widetilde{s}_{n,r}}\right) \right\} \nonumber \\
+& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, 4d\log\left(\frac{D \Lambda_{\sigma}^2}{\beta_d \lambda_{\sigma}^2}\right) \right\}
+\end{align*}
+
+We now upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: expansion_to_tv_distance}, we have that
+\begin{align}
+\label{eqn: mixing_time_bound_on_neighborhood_graph_thm2}
+\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right) \nonumber \\
+& \leq \frac{1400}{3}\left(5 + \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt \right)
+\end{align}
+where $s_{\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$.(Since $r$ remains constant, for sufficiently large $n$ with probability at least $1 - \delta$, $\widetilde{D}_{\min} > 10$.)
+
+Now, we can upper bound the average conductance integral:
+\begin{align*}
+\int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt & \leq \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(1/2)} dt \\
+& \leq 64\frac{9^d\Lambda_{\sigma}^2(1 + \epsilon)^2\beta_d^2}{\lambda_{\sigma}^2(1 - \epsilon)^2} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)^{-2} \log\left(\frac{D \Lambda_{\sigma}^2}{\beta_d \lambda_{\sigma}^2}\right).
+\end{align*}
+
+Plugging this in to \eqref{eqn: mixing_time_bound_on_neighborhood_graph_thm2} gives the desired upper bound on $\tau_{\infty}(\widetilde{q}_n, \widetilde{G}_{n,r})$, which translates to the lower bound of \eqref{eqn: inverse_mixing_time_lower_bound}.
+
+\subsection{Proof of \textcolor{red}{Theorem 3}}
 Throughout this proof, we will refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$.
@@
 \label{eqn: mixing_time_bound_on_neighborhood_graph}
-\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{1,n}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right)
+\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right)
 \end{equation}
-(As $r$ remains constant and $n \to \infty$, $\Dbf_{xx} > C$ will be fulfilled for any $x \in \Csig[\Xbf]$, and any $C < \infty$.)
+(Since $r$ remains constant, for sufficiently large $n$, $\Dbf_{xx} > C$ will be fulfilled for any $x \in \Csig[\Xbf]$, and any $C < \infty$.)
 We set aside the constant term for the moment and turn to the integral. By Lemma \ref{lem: local_spread_lower_bound},

### 2019-01-22 icml/icml_local_density_clustering.tex
added todays changes

--- 2019-01-14 icml/icml_local_density_clustering.tex
@@
 \newcommand{\Psibf}{\mathbf{\Psi}}
+\newcommand{\dist}{\mathrm{dist}}
 
@@
 
-\theoremstyle{remark}
+\newtheoremstyle{aldenrmrk}
+{6pt} % Space above
+{6pt} % Space below
+{} % Body font
+{} % Indent amount
+{\itshape} % Theorem head font
+{.} % Punctuation after theorem head
+{.5em} % Space after theorem head
+{} % Theorem head spec (can be left empty, meaning `normal')
+
+\theoremstyle{aldenrmrk}
 \newtheorem{remark}{Remark}
@@
 	regions of high-density (density clusters).
-	With respect to a neighborhood graph formed over these samples, we provide guarantees for a pair of cluster quality criteria evaluated on empirical analogues to these density clusters.
-As a result, the \pprspace algorithm is shown to
-	extract sufficiently salient density clusters, and we 
-	analyze the sample-complexity of the algorithm.
+	We introduce a bicriteria for evaluating cluster quality and provide guarantees for these criteria evaluated on empirical analogues to these density clusters.
+As a result, the \pprspace algorithm run over a neighborhood graph is shown to
+	extract sufficiently salient density clusters.
 \end{abstract}
@@
 
-Let $\mathbf{X} := (x_1, \ldots, x_n)$ with $x_i \in \Rd$ for $i = 1,\ldots,n$.
+Let $\mathbf{X} := (x_1, \ldots, x_n)$ be a sample drawn i.i.d from a distribution $\Pbb$ with density $f$ supported on $\Rd$.
 Our statistical learning task is clustering: splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
 
-In particular, spectral clustering methods are a family of powerful non-parametric clustering algorithms.
-Given a symmetric adjacency matrix $\Abf \in \Reals^{n \times n}$ with $(i,j)$th entry representing the similarity between data points $x_i$ and $x_j$, we form the random walk transition probability matrix $\Wbf$, and corresponding graph Laplacian matrix $\Lbf$\footnote{Often, either of the Laplacian matrices  $\Lbf_{sym} := \Dbf^{\frac{1}{2}}\Wbf \Dbf^{-\frac{1}{2}}$ or $\Lbf_{unn} := \Dbf - \Abf$ are used instead.}:
+Spectral clustering methods are a family of powerful non-parametric clustering algorithms.
+Let $G = (V,E)$ be an unweighted and undirected graph, with $\Abf \in \Reals^{V \times V}$ the symmetric adjacency where $A_{uv} = 1$ if $(u,v) \in G$.
+We form the random walk transition probability matrix $\Wbf$, and corresponding graph Laplacian matrix $\Lbf$\footnote{Often, either of the Laplacian matrices  $\Lbf_{sym} := \Dbf^{\frac{1}{2}}\Wbf \Dbf^{-\frac{1}{2}}$ or $\Lbf_{unn} := \Dbf - \Abf$ are used instead.}:
 \begin{equation}
@@
 \end{equation}
-where the degree matrix $\Dbf$ is a diagonal matrix with $\Dbf_{ii} := \sum_j \Abf_{ij}$, and $\Ibf{n}$ is the $n \times n$ identity matrix.
+where the degree matrix $\Dbf$ is a diagonal matrix with $\Dbf_{uu} := \sum_{v \in V} \Abf_{uv}$, and $\Ibf{n}$ is the $n \times n$ identity matrix.
 
-Roughly speaking, spectral clustering techniques first embed the data $\Xbf$ using the spectrum of the graph Laplacian, and subsequently 
-use this \emph{spectral embedding} to find a clustering of the data.
+Roughly speaking, spectral clustering techniques first learn an embedding the data $\Xbf$ using the spectrum of the graph Laplacian, and subsequently 
+apply a simple clustering technique (such as k-means) to this \emph{spectral embedding}.
 When applied to large graphs (or large point clouds) classical global spectral 
@@
 
-A natural model to consider when analyzing point cloud data such as $\Xbf$ is the following:
-\begin{equation}
-x_i \sim \Pbb, ~~~ \text{independently, for $i = 1,\ldots,n$},
-\end{equation} 
-with $f$ the density function of $\Pbb$ with respect to the uniform measure over $\Rd$.
-In this case, we are interested in understanding what the output of a clustering algorithm on this finite sample reveals about the unknown density $f$.
+We are interested in understanding what the output of a clustering algorithm on $\Xbf$ reveals about the unknown density $f$.
 For $\lambda > 0$ and the upper level set $\set{x: f(x) \geq \lambda}$, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters as the connected components $\mathbb{C}_f(\lambda)$ of the upper level set; we call these connected regions of high density \textit{density clusters}, and study the ability of spectral methods to identify such clusters.
@@
 A somewhat more standard mode of understanding spectral clustering methods is to view them as approximating some graph connectivity criteria.
+There are many graph-based measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.
+See \cite{yang2015,fortunato2010} for an overview.)
 
-For $\Abf$ as before, consider the graph $G  = (V,E)$, with vertices $V = \set{v_1, \ldots, v_n}$ corresponding to the $n$ rows of $\Abf$, and (possibly weighted) edges $E = \set{(v_i,v_j,\Abf_{ij}): 1 \leq i < j \leq n, \Abf_{ij} > 0}$ (Since $\Abf$ is symmetric, $G$ is an undirected graph; also, by convention, we preclude self-loops, hence $i \neq j$).
-There are many \cite{yang2015,fortunato2010} graph-based measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.)
-
-Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \textit{external} and \textit{internal connectivity} of $S$, respectively.
-As the names suggest, external connectivity should relate to the number of edges between $S$ and its complement $V / S$ (hereafter denoted $S^c$), while internal connectivity in turn measures the number of edges between subsets within $S$.
-The graph clustering task then becomes to find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
-
-We will assess the external connectivity of a subset $S \subseteq V$ through its normalized cut. The cut of $S$ is
+Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \emph{external} and \emph{internal connectivity} of $S$, respectively.
+We define the external connectivity of a subset $S \subseteq V$ to be its normalized cut.
+For $S' \subset V$, the cut between $S$ and $S'$ is
 \begin{equation*}
-\cut(S; G) := \sum_{u \in S} \sum_{v \in S^c} \1\left((u,v) \in E \right)
+\cut(S, S'; G) := \sum_{u \in S} \sum_{v \in S'} \1\left((u,v) \in E \right)
 \end{equation*}
--- where $S^c = V / S$ is the complement of $S$ in $V$ -- and the volume of $S$ is
+and the volume of $S$ is
 \begin{equation*}
@@
 \end{equation*}
-Then, the \emph{normalized cut} of $S$ is given by
+Then, the \emph{normalized cut} of $S$ is
 \begin{equation}
@@
 \end{equation} 
-Intuitively, a set with low \textit{normalized cut} has many more edges which do not cross the cut than edges which do cross the cut.
+(where we abbreviate $\cut(S; G) = \cut(S; S^c; G)$).
 
 Given $S \subseteq V$, the subgraph induced by $S$ is given by $G[S] = (S, E_S)$, where $(u,v) \in E_S$ if both $u$ and $v$ are in $S$ and $(u,v) \in E_S$.
-Letting $\abs{S} = m$, $\Abf_S$ then denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, defined only over $G[S]$.)
+Our internal connectivity parameter $\Psi(S)$ will capture the time it takes for the random walk over $G[S]$ to mix (that is, approach a stationary distribution) uniformly over $S$.
+Letting $\abs{S} = m$, $\Abf_S$ denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, defined only over $G[S]$.)
 
-Our internal connectivity parameter $\Psi(S)$ will capture the time it takes for the random walk governed by $\Wbf_S$ to mix (that is, approach a stationary distribution) uniformly over $S$.
-Denoting the stationary distribution of this random walk by $\widetilde{\pibf} = (\widetilde{\pi}_{1}, \ldots, \widetilde{\pi}_{m})$, the \emph{relative pointwise mixing time} $\tau_{\infty}(S; G[S])$ is defined to be: the smallest integer $t_0 > 0$ such that for all $v = v_i,v' = v_j \in S$:
+For $v \in V$ we write
+\begin{equation}
+\label{eqn: random_walk}
+\pibf = (\pi_{u})_{u \in S}, ~~ q_{vu}^{(m)} = e_v\Wbf_S^m e_u
+\end{equation}
+for the stationary distribution and the $m$-step transition probability of the random walk over $G[S]$ originating at $v$.
+\footnote{Given a starting node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.
+}
+(Of course, given the definition of $\Wbf_S$ it is of course well known that the stationary distribution $\widetilde{\pibf}$ is given by $\widetilde{\pi}_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$.)
+
+The \emph{relative pointwise mixing time} is defined as 
 \begin{equation*}
-\abs{\frac{e_v \Wbf_S^t - \widetilde{\pi}_{j}}{\widetilde{\pi}_{j}}} \leq \frac{1}{4}
+\tau_{\infty}(\qbf; G[S]) := \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pi_u}}{\pi_u} \leq 1/4} 
 \end{equation*}
-for all $t > t_0$
-\footnote{Given a starting node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.} (Of course, given the definition of $\Wbf_S$ it is well known that the stationary distribution $\pibf_S$ will be defined by $\widetilde{\pi}_{i} = (\Dbf_{S})_{ii} / \vol(S; G[S])$.
+where $\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}, \qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$.
 
-Intuitively, the smaller the pointwise mixing time, the more connected every pair of points $v$ and $v'$ are in the graph $G[S]$.
-Therefore, the internal connectivity parameter $\Psi(S; G)$ is simply one over the mixing time:
+The internal connectivity parameter $\Psi(S; G)$ is simply one over the mixing time:
 \begin{equation}
 \label{eqn: inv_mixing_time}
-\Psi(S; G) = \frac{1}{\tau_{\infty}(S; G[S])}
+\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}
 \end{equation}
 
+The graph clustering task is thus find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
 If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no less than $\Psi$, we will refer to it as a $(\Phi,\Psi)$-cluster.
@@
 The random walk matrix $\Wbf$ over the graph $G = (V,E)$ with associated adjacency matrix $\Abf$ is given by (\ref{eqn: random_walk_laplacian}).
-\pprspace is then defined with respect to the following inputs: a user-specified seed node $v_i \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
-Letting $v = v_i$ for notational simplicity, and $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $i$th location and $0$ everywhere else), the \emph{PPR vector} is given by the recursive formulation
+\pprspace is then defined with respect to the following inputs: a user-specified seed node $v \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
+Letting $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $v$th location and $0$ everywhere else), the \emph{PPR vector} is the solution to the following linear equation:
 \begin{equation}
@@
 To compute a cluster $\widehat{C} \subset V$ using the \pprspace vector, we will take sweep cuts of $\pbf(v, \alpha; G)$.
-Denote the entries of $\pbf(v, \alpha; G)$ by $\pbf(v, \alpha; G) = (p_1, \ldots, p_n)$, and let the \emph{stationary distribution} $\pibf$ of the random walk defined by $\Wbf$ be given by
-\begin{equation*}
-\pibf = (\pi_1, \ldots, \pi_n), ~~~ \pi_j := \frac{\Dbf_{jj}}{\vol(V; G)}.
-\end{equation*}
-Then, for a number $\beta \geq 0$, the sweep cut $S_\beta$ is
+To do so we require another parameter $\pi_0$.
+For a number $\beta \geq 0$, the sweep cut $S_\beta$ is then
 \begin{equation}
 \label{eqn: sweep_cuts}
-S_\beta = \set{u_j \in V: p_j > \beta \pi_j}.
+S_\beta = \set{u \in V: p_u > \beta \pi_{0}}.
 \end{equation}
 We will choose one such sweep cut to be our cluster estimate $\widehat{C}$.
-(We delay formal introduction of the local clustering algorithm we analyze until \ref{sec: background}, after we have given a method for forming a graph over the data $\Xbf$.)
 
-\paragraph{Large sample behavior.}
+\paragraph{Neighborhood graph.}
+
+To formally introduce the local clustering algorithm we consider, we must first give a method for forming a graph over the data $\Xbf$.
 
 Let $(r_n)$ be a sequence of positive numbers.
-Given a sequence of kernel functions $k_n: \Rd \times \Rd \to [0,\infty)$ of the form $k_n(x,x') = k(\norm{x - x'}/ r_n)$ for $k$ a non-increasing function, and data $\Xbf = \set{x_1, \ldots, x_n}$ sampled from $\Pbb$ as before, form the (weighted, complete) similarity graph $G_n = (\Xbf, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
+Given a sequence of kernel functions $k_n: \Rd \times \Rd \to [0,\infty)$ of the form $k_n(x,x') = k(\norm{x - x'}/ r_n)$ for $k$ a non-increasing function, and data $\Xbf = \set{x_1, \ldots, x_n}$ sampled from $\Pbb$ as before, form the \emph{neighborhood graph} $G_n = (\Xbf, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
 (Here, $\norm{\cdot}$ is used to denote Euclidean norm).
 
-In this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence of finite sample graph-theoretic functionals to their continuous counterparts has been shown
+Algorithm \ref{alg: ppr} will be the simple variant of PPR we analyze. It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\pi_0$, and $v \in \Xbf$. 
+\begin{algorithm}
+	\caption{PPR on a neighborhood graph}
+	\label{alg: ppr}	
+	{\bfseries Input:} data $\Xbf$, radius $r$, teleportation parameter $\alpha \in [0,1]$, seed node $v \in \Xbf$, target $\pi_0$. \\
+	{\bfseries Output:} $\widehat{C} \subset V$.
+	\begin{algorithmic}[1]
+		\STATE Form the neighborhood graph $G_{n,r}$ as given in (\ref{eqn: neighborhood_graph})
+		\STATE Compute PPR vector $\pbf(v, \alpha; G_{n,r})$  as defined by (\ref{eqn: ppr_vector}).
+		\STATE For $\beta \in (\frac{3}{10}, \frac{1}{2})$ compute sweep cuts $S_{\beta}$ as defined by (\ref{eqn: sweep_cuts}).
+		\STATE Return
+		\begin{equation*}
+		\label{eqn: sweep_cuts_min_conductance}
+		\widehat{C} = \argmin_{\beta \in (\frac{3}{10}, \frac{1}{2})} \Phi(S_{\beta}; G_{n,r})
+		\end{equation*}
+	\end{algorithmic}
+\end{algorithm}
+
+We note that the choice of a specific interval such as $(\frac{3}{10}, \frac{1}{2})$ for the range of $\beta$ is standard in the analysis of \pprspace algorithms.
+
+It is worth calling attention to some other work on computing the normalized cut over neighborhood graphs.
+In this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence finite sample graph-theoretic functionals to their continuous counterparts has been shown
 \cite{garciatrillos16, arias-castro12, maier11}.
-However these continuous analogues are not always easily interpretable -- and their corresponding minimizers not always easily identifiable -- for the particular density function under consideration.
+However, in addition to the graph-minimization problem being computationally infeasible, these continuous analogues are not always easily interpretable -- and their corresponding minimizers not always easily identifiable -- for the particular density function under consideration.
 Of course, relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
@@
 
-Our results can now be summarized by the following two points:
+Our results can now be summarized by the following points:
 
@@
 	\item 
-	Under a natural set of geometric conditions\footnote{We formally introduce the geometric conditions in Section \ref{sec: background}.
-They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large}, the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$ can be bounded.
-Theorems \ref{thm: conductance_upper_bound} and \textcolor{red}{Theorem 2} provide an upper and lower bound, respectively
+	Under a natural set of geometric conditions
+	\footnote{We formally introduce the geometric conditions in Section \ref{sec: background}.
+They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large},
+	the normalized cut of an empirical density cluster $C[\Xbf]$ can be bounded. Theorem \ref{thm: conductance_upper_bound} provides an upper bound.
+
+	\item Under largely the same set of geometric conditions to Theorem \ref{thm: conductance_upper_bound}, Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} provides a lower bound on the inverse mixing time of a random walk over $C[\Xbf]$.
+Theorem \ref{thm: inverse_mixing_time_lower_bound} gives a tighter lower bound, but requires the additional (restrictive) assumption of convexity.
 
 	\item 
-	We show these bounds on the graph connectivity criteria have algorithmic consequences for personalized PageRank.
-An immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, along with the previous work of \cite{zhu2013}, is to yield an upper bound on the normalized cut of the set $\widehat{C}$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
-Furthermore, in \ref{sec: consistent_cluster_estimation_with_ppr} we show that a careful analysis of the form typical to local clustering algorithms yields Theorem \ref{thm: consistent_recovery_of_density_clusters}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
+	In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show these bounds on the graph connectivity criteria have algorithmic consequences for personalized PageRank.
+we show that a careful analysis of the form typical to local clustering algorithms yields Theorem \ref{thm: consistent_recovery_of_density_clusters}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
+
+	\item Corollary \ref{cor: ppr_cluster} follows as an immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, along with the previous work of \cite{zhu2013}.
+It gives an upper bound on the normalized cut of the set $\widehat{C}$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
 \end{enumerate}
@@
 
-\section{Background and Assumptions.}
+\section{Graph Quality Criteria on Well-Conditioned Density Clusters.}
 \label{sec: background}
-
-We begin by introducing an defining well-conditioned density clusters before turning to formally define the PPR algorithm under consideration, Algorithm \ref{alg: ppr}, and discussing the choice of tuning-parameters.
-
-\subsection{Well-conditioned density clusters.}
 
@@
 \begin{enumerate}[label=(A\arabic*)]
+	\item
+	\label{asmp: cluster_separation}
+	\textit{Cluster separation:}
+	For all $\Cset' \in \Cbb_f(\lambda)$,
+	\begin{equation*}
+	\dist(\Csig,\Csig') > \sigma,
+	\end{equation*}
+	where $\dist(\Aset,\Aset') = \min_{x \in \Aset} \dist(x,\Aset')$ for $\Aset' \subset \Rd$.
+
+	\item
+	\label{asmp: cluster_diameter}
+	\textit{Cluster diameter:}
+	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
+	\begin{equation*}
+	\norm{x - x'} \leq D.
+	\end{equation*}
+
 	\item
@@
 	\label{asmp: low_noise_density}
-	\textit{Low noise density:} For some $\gamma > 0 $, there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \rho(x, \Csig) \leq \sigma$,
+	\textit{Low noise density:} For some $\gamma > 0 $, there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,
 	\begin{equation*}
-	\inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \rho(x, \Csig)^{\gamma},
+	\inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \dist(x, \Csig)^{\gamma},
 	\end{equation*}
-	where $\rho(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subset \Rd$.
-
-	\item
-	\label{asmp: cluster_separation}
-	\textit{Cluster separation:}
-	For all $\Cset' \in \Cbb_f(\lambda)$,
-	\begin{equation*}
-	\rho(\Csig,\Csig') > \sigma,
-	\end{equation*}
-	where $\rho(\Aset,\Aset') = \min_{x \in \Aset} \rho(x,\Aset')$ for $\Aset' \subset \Rd$.
-
-	\item
-	\label{asmp: cluster_diameter}
-	\textit{Cluster diameter:}
-	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
-	\begin{equation*}
-	\norm{x - x'} \leq D.
-	\end{equation*}
+	where $\dist(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subset \Rd$.
 \end{enumerate}
 
-We note that $\sigma$ plays several roles here, precluding arbitrarily narrow clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
+We note that $\sigma$ plays several roles here, precluding arbitrarily narrow clusters and long clusters in \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
 
-Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
+Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
 We note that the lower bound on minimum density in (\ref{eqn: bounded_density}) and \ref{asmp: cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of \cite{chaudhuri2010}, a standard density clustering assumption, while \ref{asmp: low_noise_density} is seen in, for instance, \cite{singh2009}, (as well as many other works on density clustering and level set estimation.) It is worth highlighting that these assumptions are all local in nature, a benefit of studying a local algorithm such as PPR.
 
-Now we make the crucial distinction between the assumptions made in density clustering, and the stronger conditions we will require here. First, we introduce
-\begin{align*}
-\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
-\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \frac{\sigma^d}{D^d} \frac{\lambda_{\sigma}^7}{\Lambda_{\sigma}^7} \frac{1}{\log(\Lambda_{\sigma}^2/(\lambda_{\sigma} \sigma^d \nu_d))}.
-\end{align*}
-
-Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf$ and $\Psibf$.
-\begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty.$ Letting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ be given by
-	\begin{align*}
-	\kappa_1(\Cset) & := \frac{\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma)}{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)} \\
-	\kappa_2(\Cset) & := \kappa_1(\Cset) \cdot \sqrt{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)},
-	\end{align*}
-	we call $\Cset$ a \textrm{$(\kappa_1, \kappa_2)$-well-conditioned density cluster (with respect to $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).}
-\end{definition}
-
-As the notation suggests, $\Phibf$ and $\Psibf$ are related to the graph connectivity criteria.
-In fact, as we will see in the next section, for well-conditioned density clusters they are exactly (up to constants) the bounds we derive.
-
-\subsection{Algorithm under consideration.}
-
-Algorithm \ref{alg: ppr} will be the simple variant of PPR we analyze. It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\vol_0$, and $v \in \Xbf$.
-
-\begin{algorithm}
-	\caption{PPR on a neighborhood graph}
-	\label{alg: ppr}	
-	{\bfseries Input:} data $\Xbf$, radius $r$, teleportation parameter $\alpha \in [0,1]$, seed node $v \in \Xbf$, target volume $\vol_0$. \\
-	{\bfseries Output:} $\widehat{C} \subset V$.
-	\begin{algorithmic}[1]
-		\STATE Form the neighborhood graph $G_{n,r}$ as given in (\ref{eqn: neighborhood_graph})
-		\STATE Compute PPR vector $\pbf(v, \alpha; G_{n,r})$  as defined by (\ref{eqn: ppr_vector}).
-		\STATE For $\beta \in [\frac{1}{8}, \frac{1}{2}]$ compute sweep cuts $S_{\beta}$ as defined by (\ref{eqn: sweep_cuts}).
-		\STATE Return
-		\begin{equation*}
-		\label{eqn: sweep_cuts_min_conductance}
-		\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G_{n,r})
-		\end{equation*}
-	\end{algorithmic}
-\end{algorithm}
-
-As is typical in the local clustering literature, our results will be stated with respect to specific choices or ranges of each of the user-specified parameters, which in this case may depend on the underlying (unknown) density.
-
-In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
-\begin{align}
-\label{eqn: initialization}
-\textcolor{red}{\alpha \in [1/2, 9/10] \cdot \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)}, & ~r \in [1/2,1]\cdot\sigma  \nonumber \\
-\vol_0 \in [1/2,1]\cdot\vol(\Csig[\Xbf]), & ~v \in \Csig[\Xbf]^g
-\end{align}
-where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
-(Intuitively one can think of $\Csig[\Xbf]^g$ as being the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.) We call a PPR algorithm run with hyperparameters satisfying (\ref{eqn: initialization}) \emph{well-initialized}.
-
-\section{Local Clustering on Density Level Sets}
-\label{sec: local_clustering_on_density_level_set}
-
-In this section we provide bounds for the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$.
-As a result we can lower bound $\Phi(\widehat{C}; G_{n,r})$ for $\widehat{C}$ the output of a well-initialized \textcolor{red}{PPR algorithm}, and upper bound the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
-
+We are ready to provide bounds on the graph quality bicriteria.
 For notational simplicity, hereafter for $S \subseteq \Xbf$ we will refer to $\Phi(S; G_{n,r})$ as $\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$.
@@
 
-We begin with a lower bound on the normalized cut in Theorem \ref{thm: conductance_upper_bound}.
-We will require Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} to hold; however, the upper bound on density in (\ref{eqn: bounded_density}) will not be needed and so we omit the parameter $\Lambda_{\sigma}$ from the statement of the theorem.
+We begin with an upper bound on the normalized cut in Theorem \ref{thm: conductance_upper_bound}.
+We will require Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} to hold; however, the upper bound on density in (\ref{eqn: bounded_density}) will not be needed and so we omit the parameter $\Lambda_{\sigma}$ from the statement of the theorem.
 \begin{theorem}
 	\label{thm: conductance_upper_bound}
-	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density}-\ref{asmp: cluster_separation} for some $\sigma, \lambda_{\sigma}, c_1, \gamma > 0$ .
-Then, for any $r < \sigma$ and $\delta \in (0,1]$, the following statements hold with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
+	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} for some $\sigma, \lambda_{\sigma}, c_1, \gamma > 0$ .
+Then, for any $r < \sigma/4d$ and $\delta \in (0,1]$, the following statements hold with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
 Then, for
@@
 		\label{eqn: conductance_additive_error_bound}
-		\frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c_{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
+		\frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq 4 c_{\sigma} d \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
 		\end{equation}
-	where $c_0 = 4d$ and $c_{\sigma} = c_0 / \sigma$. 
+	where $c_{\sigma} = 1 / \sigma$. 
 \end{theorem}
 
-The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other proofs, can be found in the supplementary document. A few remarks are in order. 
 \begin{remark}
-	\label{rem: exp_in_d}
-	Note that the bound of (\ref{eqn: conductance_additive_error_bound}) depends exponentially on $d$; precisely, on $C_0 = d2^{2d +1}$.
-It is possible to improve this dependency to the order of $(1 + \frac{r}{\sigma})^{2d}$.
-However, as indicated by (\ref{eqn: initialization}), we will think of $r$ as being a constant radius of order $\sigma$ (rather than $r = r_n \to 0$ as $n \to \infty$) and therefore even this improvement still retains an exponential dependency on the dimension $d$.
+	The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other proofs, can be found in the supplementary document.
+The key point is to note that for any $x \in \Cset$, the simple, (possibly loose) $B(x,\sigma) \subset \Csig$ translates to the upper bound $\nu(\Cset_{\sigma + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$.
+We leverage \ref{asmp: low_noise_density} to find a corresponding bound on the weighted volume, before applying standard concentration inequalities to convert from population to sample based results.
 \end{remark}
 \begin{remark}
-	Aside from the looseness implied by Remark \ref{rem: exp_in_d}, the error bound of (\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
+	(\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
 	\begin{align*}
@@
 	 \lambda \text{ for $x \in \Asig$}, \\
-	 \lambda - \rho(x,\Asig)^{\gamma} \text{ for $0 < \rho(x,\Asig) < r$}
+	 \lambda - \dist(x,\Asig)^{\gamma} \text{ for $0 < \dist(x,\Asig) < r$}
 	 \end{cases}
@@
 	\end{equation*}
-	for some constant $c$ which depends only on dimension. (Note that a factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated in this lower bound.) For justification see the supplementary materials.
+	for some constant $c$. (Note that a factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated in this lower bound.)
 \end{remark}
 
-We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
+We now provide a lower bound on $\Psi_{n,r}(\Cset[\Xbf])$.
+
+\begin{theorem}
+	\label{thm: inverse_mixing_time_lower_bound_nonconvex}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
+Then, for any $r < \sigma/4d$, the following statement holds with probability at least $1 - \delta$: Fix $0 < \epsilon > 1$.
+Then, for $n$ satisfying:
+	\begin{align*}
+	\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d \lambda_{\sigma}}} \leq \epsilon
+	\end{align*}
+	we have
+	\begin{align}
+	\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
+	1 / \Psi_{n,r}(\Csig[\Xbf]) & \leq \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
+	& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
+	\end{align}
+	where $\mu = \log(\frac{2D}{r})$; $c_1$, $c_2$, and $c_3$ are constants which depend only on dimension; and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
+\end{theorem}
+
+\begin{remark}
+	The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[X]]$,
+	\begin{equation*}
+	\widetilde{\Phi} = \min_{S \subset \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]])
+	\end{equation*}
+
+	The factor of $\frac{1}{r^{2d}}$ present in the bound of \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex} is suboptimal.
+This exponential dependence on $d$ stems from a loose bound on the aforementioned conductance in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.In particular, we assert only that any set $S \subset \Csig[X]$ must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding $\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of order $r^d$.
+The presence of $r^{2d}$ comes from upper bounding the mixing time by about $1/\widetilde{\Phi}^2$, this latter bound being a variant of classic results on rapid mixing \cite{jerrum89}.
+\end{remark}
+
+It is possible to sharpen the dependency on $d$, but at the cost of an additional assumption:
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{4}
+	\item 
+	\label{asmp: convex}
+	$\Cset$ is convex.
+\end{enumerate}
+Additionally, the resulting bound holds only asymptotically.
+
 \begin{theorem}
 	\label{thm: inverse_mixing_time_lower_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
-Then, for any $r < \sigma/4d$ and $\delta > 0$, the following statement holds with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
-Then for
-	\begin{equation*}
-	\textcolor{red}{n \geq }
-	\end{equation*}
-	we have
-	\begin{equation*}
-	\Psi_{n,r}(\Cset[\Xbf]) \geq c_d \frac{r^d}{D^d} \frac{\lambda_{\min}^7}{\lambda_{\max}^7} \frac{1}{\log(\lambda_{\max}^2/(\lambda_{\min} r^d \nu_d))}
-	\end{equation*}
-	for \textcolor{red}{$c_d = (1 + \epsilon)$}.
+	Fix $\lambda > 0$, and let the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} hold with respect to $\Cset \in \Cbb_f(\lambda)$.
+Additionally, let $\Cset$ satisfy \ref{asmp: convex}.
+Then, for any $r < \sigma/4d$, the following statement holds: with probability one
+	\begin{align}
+	\label{eqn: inverse_mixing_time_lower_bound}
+	\liminf_{n \to \infty} & \frac{1}{\Psi_{n,r}(\Csig[\Xbf])} \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
+	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
+	& c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
+	\end{align}
+	where $\mu = \log(\frac{2D}{r})$, $c_1,c_2$ and $c_3$ are all global constants, $c_d$ is constant in $r$ but may depend on other quantities,  and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.
+Additionally, $\lim_{r \to 0} o_r(1) = 0$.
 \end{theorem}
 
-\paragraph{Approximate density cluster recovery with PPR.}
+We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound} to those of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part by working with a generalization of the conductance, the \emph{conductance function}
+\begin{equation*}
+\widetilde{\Phi}_n(t) = \min_{\substack{S \subset \Csig[\Xbf] \\ \pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]])
+\end{equation*}
+where $\pi(S)$ is the stationary distribution over $G_{n,r}[\Csig[\Xbf]]$. 
+The utility of the conductance function comes from the known upper bound of mixing time by 
+\begin{equation}
+\label{eqn: average_conductance}
+\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt
+\end{equation}
+ which results in a tighter bound than merely using the conductance when $\widetilde{\Phi}_n(t)$ is large for small values of $t$.
+
+\begin{remark}
+	The only potentially exponential dependence on dimension comes from the factor of $c_d$.
+However, for sufficiently small values of $r$ this will be dominated by the preceding factors, due to the presence of the $o_r(1)$ term.
+\end{remark}
+
+\begin{remark}
+ The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} relies on a to the best of our knowledge novel uniform lower bound on this conductance function over $G_{n,r}$ in terms of a population-level analogue, which we term $\widetilde{\Phi}_{\Pbb,r}$.
+Plugging $\widetilde{\Phi}_{\Pbb,r}$ into \eqref{eqn: average_conductance} yields a bound on mixing time (with respect to total variation distance) of order $d D^2/r^2 + d^2\log(D/r)$ over convex sets.
+By contrast, \eqref{eqn: inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ (ignoring the $o_r(1)$ term) but handles mixing time with respect to relative pointwise distance (which is known to be a stricter metric.)
+\end{remark}
+
+\begin{remark}
+	The convexity requirement is necessary only to lower bound the $\widetilde{\Phi}_{\Pbb,r}$; any bound on $\widetilde{\Phi}_{\Pbb,r}$ which does not require convexity could immediately be plugged into the machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} to achieve a corresponding result.
+Recent work \cite{abbasi17} has developed such population-level bounds on the conductance function, however the Markov chain dealt with there is somewhat different than the one we consider.
+\end{remark}
+
+\section{Consistent cluster estimation with PPR.}
+\label{sec: consistent_cluster_estimation_with_ppr}
+
+For \pprspace to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.
+
+We introduce
+\begin{align*}
+\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
+1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
+& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
+\end{align*}
+
+Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf$ and $\Psibf$.
+\begin{definition}[Well-conditioned density clusters]
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty.$ Letting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ be given by
+	\begin{align*}
+	\kappa_1(\Cset) & := \frac{\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma)}{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)} \\
+	\kappa_2(\Cset) & := \kappa_1(\Cset) \cdot \sqrt{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)},
+	\end{align*}
+	we call $\Cset$ a \textrm{$(\kappa_1, \kappa_2)$-well-conditioned density cluster (with respect to $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).}
+\end{definition}
+
+$\Phibf$ and $\Psibf$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.
+
+\begin{remark}
+	For convenience and maximum generality, we define $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to correspond with the bound given by \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, and assume only \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density}.
+However, if we additionally have \ref{asmp: convex}, then we could sharpen $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to the tighter rate of \eqref{eqn: inverse_mixing_time_lower_bound}, with nothing changing hereafter.
+\end{remark}
+
+As is typical in the local clustering literature, our results will be stated with respect to specific choices or ranges of each of the user-specified parameters, which in this case may depend on the underlying (unknown) density.
+
+In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
+\begin{align}
+\label{eqn: initialization}
+\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D), & ~r \leq \sigma/4d  \nonumber \\
+\pi_0 \in [2/3, 6/5] \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}, & ~v \in \Csig[\Xbf]^g
+\end{align}
+where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
+(Intuitively one can think of $\Csig[\Xbf]^g$ as being the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
+
+\begin{definition}
+	If the input parameters to Algorithm \ref{alg: ppr} satisfy \ref{eqn: initialization} with respect to some $\Csig[\Xbf]$, we say the algorithm is  \emph{well-initialized}.
+\end{definition}
+
+\begin{theorem}
+	\label{thm: consistent_recovery_of_density_clusters}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$). If
+	\begin{equation}
+	\label{eqn: kappa2_ub}
+	\kappa_2 \leq \frac{1}{40 \cdot 36} \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)}.
+	\end{equation}
+	and Algorithm \ref{alg: ppr} is well-initialized, the output set $\widehat{C} \subset \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+\end{theorem}
+
+\begin{remark}
+	We note that larger constants than $40 \cdot 36$ allow for wider range of the parameters in $\eqref{eqn: initialization}$. 
+\end{remark}
+\paragraph{Approximate cluster recovery via PPR.}
 
 In \cite{zhu2013}, building on the work of \cite{anderson2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
+Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut and symmetric set difference of $\widehat{C}$.
+
 We collect some of the main results of \cite{zhu2013} in Lemma \ref{lem: ppr_cluster}.
@@
 	\label{lem: ppr_cluster}
-	There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix \textcolor{red}{$\alpha = 9 / 10 \Psi(A; G)$}, and compute the page rank vector $\pbf(v,\alpha; G)$.
+	There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
 Letting
@@
 	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\Phi(\widehat{C}; G) & = \textcolor{red}{O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)}
+	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
 	\end{align*}
@@
 	\vol(\widehat{C} \setminus \Csig[\Xbf]), \vol(\Csig[\Xbf] \setminus \widehat{C})  & \leq 30 \kappa_1(\Cset) \vol(\Csig[X]) \\
-	\Phi_{n,r}(\widehat{C}) & = \textcolor{red}{O\left(\kappa_2(\Cset)\right)}
+	\Phi_{n,r}(\widehat{C}) & = O\left(\kappa_2(\Cset)\right)
 	\end{align*}
@@
 
-\section{Consistent cluster estimation with PPR.}
-\label{sec: consistent_cluster_estimation_with_ppr}
-While Corollary \ref{cor: ppr_cluster} is nice, it does not imply consistency of the type laid out in Definition \ref{def: consistent_density_cluster_estimation}.
-
-However, a slightly more subtle argument regarding the way a random walk on $G_{n,r}$ distributes mass over $\Cset[\Xbf]$ and $\Cset'[\Xbf]$ will do the trick, yielding Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-\begin{theorem}
-\label{thm: consistent_recovery_of_density_clusters}
-Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), with
-\begin{equation}
-\label{eqn: kappa2_ub}
-\kappa_2 \leq \left(\frac{1}{5} - \frac{\epsilon}{4}\right) \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\sigma^d \nu_d}{\nu(\Csig)}
-\end{equation}
-for some $\epsilon > 0$.
-
-Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the output set $\widehat{C} \subset \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-\end{theorem}
-
-\begin{remark}
-	When $\lambda_{\sigma} = \Lambda_{\sigma}$ and $\nu(\Csig) = \sigma^d \nu_d$ -- in some sense, the `best' case given our assumptions -- the upper bound of (\ref{eqn: kappa2_ub}) reduces to $\kappa_2 \leq 1/5 - \epsilon/4$.
-That $\kappa_2 = O(1)$ is a minimal requirement for the bounds of Corollary \ref{cor: ppr_cluster} not to be facile; therefore, in this case the assumed upper bound of (\ref{eqn: kappa2_ub}) is not really a stricter requirement.
-\end{remark}
 \section{Examples}
@@
 \section{Discussion}
+\label{sec: discussion}
 For a clustering algorithm and a given object (such as a graph or set of points), there are an almost limitless number of ways to define what the 'right' clustering is.

### 2019-01-22 icml/icml_local_density_clustering_supplement.tex
added todays changes

@@
 \usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+\usepackage{natbib}
 
@@
 \newcommand{\TV}{\mathrm{TV}}
+\newcommand{\dist}{\mathrm{dist}}
+\newcommand{\Id}{\mathrm{Id}}
 
@@
 \newcommand{\wPbb}{\widetilde{\Pbb}}
+\newcommand{\wf}{\widetilde{f}}
 
@@
 
-In this supplement, we present proofs for ``Local Clustering of Density Upper Level Sets''. We begin by providing technical lemmas, before moving on to proving the main results of the paper.
-
-Throughout, we will fix $\Aset \subset \Rd$ to be an arbitrary set.
+In this supplement, we present proofs for ``Local Clustering of Density Upper Level Sets''.
+Sections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
+\ref{sec: mixing_time_on_graphs} develops a bound of the form of \eqref{eqn: average_conductance}, which we recall links the conductance function to mixing time; this will be necessary for both Theorems \ref{thm: inverse_mixing_time_lower_bound_nonconvex} and \ref{thm: inverse_mixing_time_lower_bound}.
+\ref{sec: non_convex_conductance_function_and_local_spread} and \ref{sec: inverse_mixing_time_lower_bound_nonconvex} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, while \ref{sec: convex_population_conductance_function}- \ref{sec: inverse_mixing_time_lower_bound} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}.
+
+\subsection{Volume estimates}
+\label{sec: volume_estimates}
+
+We will fix $\Aset \subset \Rd$ to be an arbitrary set.
 To simplify expressions, for the $\sigma$-expansion $\Asig$, we will write the set difference between $\Asig$ and the $(\sigma + r)$-expansion $\Aset_{\sigma + r}$ as
 \begin{equation*}
-\Asigr := \set{x: 0 < \rho(x, \Asig) \leq r},
-\end{equation*}
-where $\rho(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
+\Asigr := \set{x: 0 < \dist(x, \Asig) \leq r},
+\end{equation*}
+where as a reminder $\dist(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
 
@@
 
-\subsection{Technical Lemmas}
-
 We state Lemma \ref{lem: expansion_sets} without proof, as it is trivial.
@@
 	\label{lem: expansion_sets}
-	For any $\sigma > 0$ and the $\sigma$-expansion $\Asig = \Aset + \sigma B$, 
-	\begin{equation*}
-	\sigma B \subset \Asig, ~~\mathrm{and~ }\nu(\Aset + \sigma B) \leq \nu((1 + \sigma)\Aset) = (1 + \sigma)^d \nu(\Aset).
-	\end{equation*}
+	For any $\delta > 0$ and $x \in \Aset_{\sigma}$,
+	\begin{equation*}
+	\sigma B \subset \Asig, ~~\mathrm{and~ }\nu(\Asig + \delta B) \leq \nu\left(\left[1 + \frac{\delta}{\sigma}\right]\Asig\right) = \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig)
+	\end{equation*}
+	where $\Asig = \Aset + \sigma B$ is the $\sigma$-expansion of $\Aset$.
 \end{lemma}
@@
 \end{lemma}
-The proof of Lemma \ref{lem: Taylor_series} is based on approximation via Taylor series, and we omit it.
+\begin{proof}
+	We take the binomial expansion of $(1 + x)^d$:
+	\begin{align*}
+	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
+	& = 1 + dx + dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
+	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{d^{k}}{(2d)^{k-1}d}\right) \\
+	& \leq 1 + 2dx.
+	\end{align*}
+\end{proof}
 
@@
 
-The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} also depends on a parameter -- which we term \emph{discrete local spread} -- to handle the mixing over very small steps.
-Formally, the discrete local spread $\pi_1(G)$ is given by
-\begin{equation}
-\label{eqn: local_spread}
-\pi_1(G) := \frac{d_{\min}(G)^2}{10 \vol(V; G)} 
-\end{equation}
-where $d_{\min}(G) = \min_{v \in V} d(v)$ is the minimum degree in $G$.
-Intuitively, the discrete local spread gauges how much the walk given by $\Wbf$ has mixed after one step, starting from any node $v$.
-We will denote $\pi_1(G_{n,r}[\Csig[\Xbf]])$ by $\widetilde{\pi}_{1,n}$.
-
-\textcolor{red}{Prove Lemma \ref{lem: local_spread_lower_bound}}.
-
-\subsection{Cut and volume estimates}
+\subsection{Density-weighted cut and volume estimates}
+\label{sec: density_weighted_cut_and_volume_estimates}
+
 \begin{lemma}
@@
 	\begin{equation*}
-	\mathcal{T}_{i,k} = \set{x \in \Rd: t_{i,k} < \frac{\rho(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
+	\mathcal{T}_{i,k} = \set{x \in \Rd: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
 	\end{equation*}
@@
 \subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
+\label{sec: proof_of_theorem_1}
+
 The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, \ref{lem: prob_bound_cut}, and \ref{lem: prob_bound_vol}.
@@
 
-\subsection{Concentration inequalities}
-
-Given a symmetric kernel function $k: \mathcal{X}^m \to \Reals$, and data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$m$ $U$ statistic} to be 
-\begin{equation*}
-U := \frac{1}{ {n \choose m} } \sum_{1 \leq i_1 < \ldots < i_m \leq n} k(x_{i_1},\ldots,x_{i_m})
-\end{equation*}
-
-For Lemmas \ref{lem: bounded_difference}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed.
-We will additionally assume the order-$m$ kernel function $k$ satisfies the boundedness property $\sup_{x_1, \ldots, x_m} \abs{k(x_1, \ldots, x_m)} \leq 1$.
-
-\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
-	\label{lem: bounded_difference}
-	For any $t > 0$,
-	\begin{equation*}
-	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{- \frac{2nt^2}{m}\right\}
-	\end{equation*}
-	Further, for any $\delta > 0$, we have
-	\begin{align*}
-	U & \leq \mathbb{E}U + \sqrt{\frac{m \log(1 / \delta)}{2n} }, \\
-	U & \geq \mathbb{E}U - \sqrt{\frac{m \log(1 / \delta)}{2n} }
-	\end{align*}
-	each with probability at least $1 - \delta$. 
-\end{lemma}
-
-We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
-\begin{lemma}
-	\label{lem: multiplicative_Hoeffding}
-	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
-	\begin{align*}
-	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
-	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
-	\end{align*}
-\end{lemma}
-
 \subsection{Mixing time on graphs}
+\label{sec: mixing_time_on_graphs}
+
 For $N \in \mathbb{N}$ and a set $V$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf = (\pi_u)_{u \in V}$ where $\pi_v = \frac{\Dbf_{vv}}{\vol(V; G)}$.
@@
 	\end{align*}
-	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
+	where $(i)$ is a result of \cite{benjamini2003} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
 	\begin{align*}
@@
 
-	Now, we leverage the following well-known fact (\textcolor{red}{PhD thesis of Montenegro}): for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
+	Now, we leverage the following well-known fact \cite{montenegro2002}: for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
 	\begin{equation*}
@@
 
-	Finally, it is known (\textcolor{red}{PhD thesis of Montenegro}) that
+	Finally, it is known \cite{montenegro2002} that
 	\begin{equation*}
@@
 To prove Lemma \ref{lem: expansion_to_tv_distance} we first introduce a generalization of $\Phi(t;G) \cdot \Phi(t;G)$ known as a blocking conductance function.
-\footnote{For more details, see \textcolor{red}{PhD thesis of Montenegro}}
-
-\begin{definition}[Blocking Conductance Function of \textcolor{red}{PhD thesis of Montenegro}]
+\footnote{For more details, see \cite{montenegro2002}}
+
+\begin{definition}[Blocking Conductance Function of \cite{montenegro2002}]
 	\label{def: blocking_conductance_function}
@@
 
-\begin{theorem}[\textcolor{red}{PhD thesis of Montenegro} Theorem 3.2]
+\begin{theorem}[Theorem 3.2 of \cite{montenegro2002}]
 	\label{thm: montenegro}
@@
 
-Note that in \textcolor{red}{PhD thesis of Montenegro} this theorem is stated with respect to $h^0$.
+Note that in \cite{montenegro2002} this theorem is stated with respect to $h^0$.
 However, in the subsequent proof it holds with respect to $h^m$, and it is observed that $h^m$ is decreasing in $m$.
@@
 \subsection{Conductance function and local spread: non-convex case.}
+\label{sec: non_convex_conductance_function_and_local_spread}
 
@@
 
-Consider $\zbf \subset \Csig$ such that  $\mathcal{N}_{\zbf} = \set{B(z,r/3): z \in \zbf}$ is a covering of $\Csig$, meaning $\mathcal{N}_{\zbf} \supseteq \Csig$. Then, we write
+Consider $\zbf \subset \Csig$ such that  $\mathcal{N}_{\zbf} = \set{B(z,r/3): z \in \zbf}$ is an internal covering of $\Csig$, meaning $\mathcal{N}_{\zbf} \supseteq \Csig$. Then, we write
 \begin{align*}
@@
 	\label{lem: ball_bounds}
-	For sufficiently large $n$, each of the following bounds hold with probability $1 - \delta$:
-	\begin{align*}
-	\widetilde{B}_{\max} & \leq \left(1 + \sqrt{3^d\frac{3(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma} \\
-	\widetilde{B}_{\min} & \geq \left(1 - \sqrt{3^d\frac{2(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \\
-	\widetilde{D}_{\max} & \leq \left(1 + \sqrt{\frac{3(\log n + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d r^d \Lambda_{\sigma} \\
-	\widetilde{D}_{\min} & \geq \left(1 - \sqrt{\frac{2(\log n + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \\
-	\left(1 - \sqrt{\frac{2 \log(1/\delta)}{n \lambda_d \nu_d \sigma^d}}\right) n \lambda_d \nu_d \sigma^d & \leq \widetilde{n} \leq \left(1 + \sqrt{\frac{3 \log(1/\delta)}{n \Lambda_d \nu_d D^d}}\right) n \Lambda_d \nu_d D^d
-	\end{align*}
-	where $\wn = \abs{\wX}$ and \textcolor{red}{$\beta_d = (1 - c_d\frac{r^2}{\sigma^2})$.}
-
-	In particular, fix $\epsilon > 0$. Then, for $n$ as specified in Theorem \ref{thm: inverse_mixing_time_lower_bound}:
-	\begin{align*}
-	\widetilde{B}_{\max} \leq \left(1 + \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma},& ~~ \widetilde{D}_{\max} \leq \left(1 + \epsilon \right) n \nu_d r^d \Lambda_{\sigma} \\
-	\widetilde{B}_{\min} \geq \left(1 - \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_{d},& ~~ \widetilde{D}_{\min} \geq \left(1 - \epsilon \right) n \nu_d r^d \lambda_{\sigma} \beta_{d} \\
+	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.	For sufficiently large $n$, and $r \leq \sigma/4d$, each of the following bounds hold with probability $1 - \delta$:
+	\begin{align}
+	\label{eqn: ball_bounds}
+	\widetilde{B}_{\max} & \leq \left(1 + \sqrt{3^d\frac{3(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma} \nonumber \\
+	\widetilde{B}_{\min} & \geq \left(1 - \sqrt{3^d\frac{2(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \nonumber \\
+	\widetilde{D}_{\max} & \leq \left(1 + \sqrt{\frac{3(\log n + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d r^d \Lambda_{\sigma} \nonumber \\
+	\widetilde{D}_{\min} & \geq \left(1 - \sqrt{\frac{2(\log n + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \nonumber \\
+	\left(1 - \sqrt{\frac{2 \log(1/\delta)}{n \lambda_d \nu_d \sigma^d}}\right) n \lambda_{\sigma} \nu_d \sigma^d & \leq \widetilde{n} \leq \left(1 + \sqrt{\frac{3 \log(1/\delta)}{n \Lambda_{\sigma} \nu_d D^d}}\right) n \Lambda_d \nu_d D^d
+	\end{align}
+	where $\wn = \abs{\wX}$ and $\beta_d \geq 1/2^d$.
+
+	In particular, fix $\epsilon > 0$. Then, for $n$ as specified in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, the following event:
+	\begin{align}
+	\label{eqn: ball_bounds_epsilon}
+	\widetilde{B}_{\max} \leq \left(1 + \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma},& ~~ \widetilde{D}_{\max} \leq \left(1 + \epsilon \right) n \nu_d r^d \Lambda_{\sigma} \nonumber \\
+	\widetilde{B}_{\min} \geq \left(1 - \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_{d},& ~~ \widetilde{D}_{\min} \geq \left(1 - \epsilon \right) n \nu_d r^d \lambda_{\sigma} \beta_{d} \nonumber \\
 	(1 - \epsilon) n \lambda_{\sigma} \nu_d \sigma^d & \leq \widetilde{n} \leq (1 + \epsilon) n \Lambda_{\sigma} \nu_d D^d 
-	\end{align*}
-	each with probability at least $1 - \delta$.
-\end{lemma}
-The proof comes directly from Lemma \ref{lem: multiplicative_Hoeffding}, and we omit it.
+	\end{align}
+	occurs with probability at least $1 - \delta$.
+\end{lemma}
+\begin{proof}
+	We observe that for any $s \leq \sigma/4d$ and any $x \in \Csig$,
+	\begin{equation*}
+	\nu(B(x,s) \cap \Csig) \geq \left(\frac{s}{2}\right)^d = s^d \beta_d.
+	\end{equation*}
+	(In fact, tighter bounds can be shown to hold, but we will not need them). Therefore, by \ref{asmp: bounded_density}:
+	\begin{equation*}
+	\lambda_{\sigma} \nu_d s^d \beta_d \leq \Pbb\left(B(z,s) \cap \Csig \right) \leq \Lambda_{\sigma} \nu_d s^d \\
+	\end{equation*}
+	In particular, this holds for $s = r$ and $s = r/3$, and for every $z \in \zbf$ as well as every $z \in \widetilde{\Xbf}$.
+Now, by \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} we also have
+	\begin{equation*}
+	\Lambda_{\sigma} \nu_d \sigma^d \leq \Pbb(\Csig) \leq \Lambda_{\sigma} \nu_d D^d
+	\end{equation*}
+
+	The proof of each statement in \eqref{eqn: ball_bounds} then follows from application of Lemma \ref{lem: multiplicative_Hoeffding}.
+
+	To show \eqref{eqn: ball_bounds_epsilon}, we note that $\abs{\mathcal{N}_z}$ is less than the covering number of the $D$-ball in $d$ dimensions. Therefore
+	\begin{equation*}
+	\abs{\mathcal{N}_z} \leq \left(\frac{6D}{r} + 1\right)^d.
+	\end{equation*}
+	It is then immediately apparent that $n$ chosen as in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} yields \eqref{eqn: ball_bounds_epsilon}.
+\end{proof}
 
@@
 \end{equation*}
+where the restriction in the minimization problem of \eqref{eqn: conductance_function} is with respect to $\widetilde{\pi}_{n,r}$ the stationary distribution over $\widetilde{G}_{n,r}$.
+
+We will bound $\widetilde{\Phi}_{n,r}(1/2)$ and $\widetilde{s}_{n,r}$ under the event that \eqref{eqn: ball_bounds_epsilon} holds, noting that this occurs with probability at least $1 - \delta$.
 
@@
 	\label{lem: local_spread_lower_bound}
-	For $\Csig$ and $n$ satisfying the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound}:
+	If the bounds given by \eqref{eqn: ball_bounds_epsilon} hold, then
 	\begin{equation*}
@@
 	\end{equation*}
-	with probability at least $1 - \delta$. 
 \end{lemma}
@@
 	\label{lem: non_convex_conductance_lower_bound}
-	For $\Csig$ and $n$ satisfying the conditions given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds:
+	If the bounds given by \eqref{eqn: ball_bounds_epsilon} hold, then:
 	\begin{equation*}
@@
 	\end{equation*}
-	with probability at least $1 - \delta$.
 \end{lemma}
@@
 	\end{equation*}
-	and so we get \eqref{eqn: normalized_cut_1}.
+	and so we get the exact statement of \eqref{eqn: normalized_cut_1}.
 Noting, as in the proof of Lemma \ref{lem: local_spread_lower_bound}, that  $\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) \leq \wn \cdot \widetilde{D}_{\max}$, the relevant results of Lemma \ref{lem: ball_bounds} yield the desired inequality.
@@
 
-\subsection{Population-level conductance function: convex case.}
-
-We will make use of the above theory with respect to the conductance function $\Phi(t; G_{n,r}[\Csig(\Xbf)])$.
-First, however, we introduce a population-level analogue to $\Phi(t; G_{n,r}[\Csig(\Xbf)])$ over the set $\Csig$, which we denote $\widetilde{\Phi}_{\Pbb,r}$.
-(In general, we will adopt the convention of using $\widetilde{f}$ to denote functionals computed with respect to $\Csig$.)
-
-For $\Sset \subset \Rd$
-\begin{equation*}
-\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
-\end{equation*} 
-is the weighted volume.
-
-The $r$-ball walk over $\Csig$ is a Markov chain. For $x \in \Csig$ and $\Sset, \Sset' \subset \Csig$ the transition probability is given by
-\begin{equation*}
-\widetilde{P}_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ \widetilde{Q}_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx,
-\end{equation*}
-stationary distribution defined by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \frac{\nu_\Pbb(\Csig \cap B(x,r))}{\nu_{\Pbb}(B(x,r))}, ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx
-\end{equation*}
-and corresponding conductance function
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}.
-\end{equation*}
-
-For $m > 0$ and $0 < t_0 < t_1 < \ldots < t_m < 1$, denote the \emph{stepwise approximation to $g$} by $\bar{g}$, defined as
-\begin{equation}
-\label{eqn: stepwise_approximation}
-\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
-\end{equation}
-The stepwise approximation will be important to showing the consistency results of Section \textcolor{red}{(A.7)} hold across the entire conductance function.
-Lemma \ref{lem: stepwise_approximation} shows that the approximation will not overly degrade our estimates of the population-level conductance function.
-\begin{lemma}
-	\label{lem: stepwise_approximation}
-	\begin{itemize}
-		\item For any function $f$ monotone decreasing in $t$ on the interval $[t_0,t_m]$, $\bar{f}(t) \leq f(t)$ for all $t \in [t_0,t_m]$.
-		\item Fix
-		\begin{equation*}
-		g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [t_0, 1/2]$}
-		\end{equation*}
-		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq t_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
-	\end{itemize}
-\end{lemma}
-
-\begin{proof}
-	The first statement is immediately obvious, and we turn to proving the second.
-
-	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.
-
-	By the concavity of the $\log$ function, 
-	\begin{equation*}
-	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
-	\end{equation*}
-	As a result,
-	\begin{equation*}
-	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
-	\end{equation*}
-\end{proof}
-
-\begin{theorem}[Restatement of \textcolor{red}{Kannan 2004} Theorem 4.6]
-	\label{thm: kannan}
-	Let $K \subset \Rd$ be a convex body of diameter $D$. Then for any $\Sset \subset K$ with $\pi_{\nu,r}(\Sset) \leq 1/2$,
-	\begin{equation}
-	\label{eqn: kannan}
-	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{\pi_{\nu,r}(\Sset)}\right)\right\}.
-	\end{equation}
-\end{theorem}
-
-\begin{lemma}
-	\label{lem: continuous_conductance_lower_bound}
-	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
-	\begin{itemize}
-		\item 
-		for $0 < t < 1/2$,
-		\begin{equation*}
-		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-		\end{equation*}
-		\item
-		Let
-		\begin{equation*}
-		M = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
-		\end{equation*}
-		and $t_i = (i + 1)/M$ for $i = 0, \ldots, m - 1$. Then, for $1/M < t < 1/2$
-		\begin{equation*}
-		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-		\end{equation*}
-		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{M - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
-	\end{itemize}
-\end{lemma}
-Before we prove Lemma \ref{lem: continuous_conductance_lower_bound}, note that the choice of $M$ is made to ensure $t_0$ is greater than the local spread of $G_{n,r}\left[\Csig[\Xbf]\right]$, as we will see in Section \ref{sec: consistency}.
-\begin{proof}[Proof of Lemma \ref{lem: continuous_conductance_lower_bound}]
-	We note that
-	\begin{equation*}
-	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
-	\end{equation*}
-
-	Plugging these estimates in to \eqref{eqn: kannan} gives
-	\begin{equation*}
-	\frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \pi_{\Pbb,r}(\Sset)}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-	\end{equation*}
-	and since the right hand side is decreasing in $\pi_{\Pbb,r}(\Sset)$, the desired lower bound holds on $\widetilde{\Phi}_{\Pbb,r}(t)$.
-The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
-\end{proof}
-
-\subsection{Consistency of local spread and conductance function: convex case.}
-\label{sec: consistency}
-
-The introduction of the stepwise approximation allows us to make use of Lemma \ref{lem: consistency_of_conductance_function}, which gives us (pointwise) consistency of the discrete graph functionals $\widetilde{\Phi}_{n,r}(t)$ to the continuous functionals $\widetilde{\Phi}_{\Pbb,r}(t)$.
-
-\begin{lemma}
-	\label{lem: consistency_of_conductance_function}
-	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
-	\begin{equation}
-	\label{eqn: pointwise_consistency_of_conductance_function}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t)
-	\end{equation}
-	As a consequence, for $M$ and $(t_i)_{i=0}^{M-1}$ defined as in Lemma \ref{lem: continuous_conductance_lower_bound}, we have that
-	\begin{equation}
-	\label{eqn: consistency_of_stepapprox_conductance_function}
-	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
-	\end{equation}
-\end{lemma}
-We defer the proof of pointwise consistency to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}.
-For now, we show that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
-
-\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
-	We take as given that for any $0 < t < 1/2$,
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
-	\end{equation*}
-	In particular, this will occur for $t_0, t_1, \ldots, t_m$ and therefore
-	\begin{equation*}
-	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
-	\end{equation*}
-	uniformly over $[1/m,1/2]$.
-\end{proof}
-
-\subsection{Proof of pointwise consistency of conductance function: convex case.}
-\label{subsection: proof_of_pointwise consitency_of_conductance_function}
-
-Throughout, let $\wn = \abs{\Csig[\Xbf]}$, $\wX = \Csig[\Xbf] = \set{\wx_1, \ldots, \wx_{\wn}}$, and 
-\begin{equation*}
-\widetilde{\Pbb}_n := \frac{1}{\wn} \sum_{\wx_i \in \wX} \delta_{\wx_i}
-\end{equation*}
-be the empirical distribution of $\wX$.
-For $S \subset \wX$, we will denote $\vol(S; \widetilde{G}_{n,r})$ by $\widetilde{\vol}_{n,r}(S)$, and likewise $\cut(S; \widetilde{G}_{n,r})$ by $\widetilde{\cut}_{n,r}(S)$.
-
-Consider a sequence of sets $(S_{\wn})_{\wn \in \mathbb{N}}$, with $u_{\wn} = \1_{S_{\wn}}$ the characteristic function of $S_{\wn}$. Similarly, for $\Sset \subset \Csig$ let $u = \1_{\Sset}$.
-
-\textcolor{red}{Give Lemma re: stagnating transportation maps and define $TL^1$ convergence.}
-\begin{lemma}
-	If $(u_{\wn}) \overset{TL^1}{\to} u$,
-	\begin{equation*}
-	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} = \widetilde{Q}_{\Pbb,r}(S, \Csig \setminus S) \cdot \left(\int_{\Csig \cap B(x,r)} f(x) \right)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We note immediately that $n \to \infty$ implies $\wn \to \infty$ with probability one.
-
-	Now, we can write
-	\begin{align*}
-	 \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\wn^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \bigl( 1 - u_{\wn}(\wx_j) \1(\norm{\wx_i - \wx_j} \leq r) \bigr)  \\
-	& = \int_{\Csig} \left(\int_{\Csig \cap B(x,r)} u_{\wn}(x) \bigl( 1 - u_{\wn}(x') \bigr) d\Pbb_n(x') \right) d\Pbb_n(x) \\
-	& = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') \right) d\Pbb(x).
-	\end{align*}
-
-	Note that
-	\begin{align*}
-	\lim_{n \to \infty} \nu\bigl(B(T_{\wn}(x),r) \setminus B(x,r)\bigr) & = 0 \\
-	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0.
-	\end{align*}
-	Therefore 
-	\begin{equation*}
-	\lim_{n \to \infty} \int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') = \lim_{n \to \infty} \int_{\Csig \cap B(x,r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x')
-	\end{equation*}
-	and by an application of the bounded convergence theorem
-	\begin{align*}
-	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  1 - u_{\wn} \circ T_{\wn}(x') d\Pbb(x') \right) d\Pbb(x) = \nonumber \\
-	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x).
-	\end{align*}
-	Letting
-	\begin{align*}
-	\mathcal{I}_n^1 & = \int_{\Csig} \left(u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( u(x') - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) \\
-	\mathcal{I}_n^2 & = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x) - u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) \\
-	\end{align*}
-	we have
-	\begin{align}
-	\label{eqn: pointwise_convergence_1}
-	& \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\Pbb(x') \right) d\Pbb(x) = \nonumber \\
-	& \int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\Pbb(x') \right\} d\Pbb(x) + \mathcal{I}_n^1 + \mathcal{I}_n^2. 
-	\end{align}
-
-	Recalling the definition of $\widetilde{Q}_{\Pbb,r}$, we have
-	\begin{align}
-	\label{eqn: pointwise_convergence_2}
-	\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset) & = \int_{\Sset} f(x) \widetilde{P}_{\Pbb,r}(x; \Csig \setminus \Sset) \nonumber \\
-	& = \frac{1}{\int_{\Csig \cap B(x,r)} f(x') dx'}\int_{\Sset} f(x) \int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' dx \nonumber \\
-	& = \frac{1}{\int_{\Csig \cap B(x,r)} f(x') dx'} \int_{\Csig} f(x) u(x){ \int_{\Csig \cap B(x,r)} (1 - u(x')) f(x') dx' }dx 
-	\end{align}
-	Since $(u_{\wn}) \overset{TL^1}{\to} u$, another application of the bounded convergence theorem yields $\lim_{n \to \infty} \mathcal{I}_n^1 = \lim_{n \to \infty} \mathcal{I}_n^2 = 0$.
-Therefore by \eqref{eqn: pointwise_convergence_1} and \eqref{eqn: pointwise_convergence_2} the final result holds.
-\end{proof}
-
-\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
+\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}}
+\label{sec: inverse_mixing_time_lower_bound_nonconvex}
+
 Throughout this proof, we will condition on the events of Lemmas \ref{lem: local_spread_lower_bound} and \ref{lem: non_convex_conductance_lower_bound},
@@
 \end{align*}
-noting that for $n$ as chosen in Theorem \ref{thm: inverse_mixing_time_lower_bound} this will occur with probability at least $1 - \delta$.
-
-We refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$. Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
-\begin{equation*}
-\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
-\end{equation*}
-Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.
+noting that for $n$ as chosen in Theorem \ref{thm: inverse_mixing_time_lower_bound}, this will occur with probability at least $1 - \delta$ (by Lemma \ref{lem: ball_bounds}).
+
+As a reminder, we write $\Csig[\Xbf] = \wX$, and $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$. Fix arbitrary $v \in \wX$, and let
+\begin{equation*}
+\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\wX}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{\qbf}_n^{(2)}, \ldots)
+\end{equation*}
+Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$. (As we will see, this bound will hold over all such starting vertices $v \in \wX$.)
 
@@
 \tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{\widetilde{s}_{n,r}}\right) \right\} \nonumber \\
-& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, 4d\log\left(\frac{D \Lambda_{\sigma}^2}{\beta_d \lambda_{\sigma}^2}\right) \right\}
+& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, d\log\left(\frac{8 D (1 + \epsilon)^2 \Lambda_{\sigma}^2}{r (1 - \epsilon)^2 \lambda_{\sigma}^2}\right) \right\}
 \end{align*}
@@
 \end{align}
-where $s_{\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$.(Since $r$ remains constant, for sufficiently large $n$ with probability at least $1 - \delta$, $\widetilde{D}_{\min} > 10$.)
+where $s_{\Pbb,r} = \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2$.(Since $r$ remains constant, for sufficiently large $n$ the lower bound on $\widetilde{D}_{\min}$ of Lemma \ref{lem: ball_bounds} will be at least $10$, and therefore Lemma \ref{lem: local_spread_blocking_conductance_function} holds.)
 
@@
 \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt & \leq \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(1/2)} dt \\
-& \leq 64\frac{9^d\Lambda_{\sigma}^2(1 + \epsilon)^2\beta_d^2}{\lambda_{\sigma}^2(1 - \epsilon)^2} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)^{-2} \log\left(\frac{D \Lambda_{\sigma}^2}{\beta_d \lambda_{\sigma}^2}\right).
+& \leq 64\frac{9^d\Lambda_{\sigma}^2(1 + \epsilon)^2\beta_d^2}{\lambda_{\sigma}^2(1 - \epsilon)^2} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)^{-2} \log s_{\Pbb,r}.
 \end{align*}
@@
 
-\subsection{Proof of \textcolor{red}{Theorem 3}}
+\subsection{Population-level conductance function: convex case.}
+\label{sec: convex_population_conductance_function}
+
+When $\Cset$ is convex, we will make use of the theory developed in \ref{sec: mixing_time_on_graphs} with respect to the conductance function $\Phi(t; G_{n,r}[\Csig(\Xbf)])$.
+First, however, we introduce a population-level analogue to $\Phi(t; G_{n,r}[\Csig(\Xbf)])$ over the set $\Csig$, which we denote $\widetilde{\Phi}_{\Pbb,r}$.
+(In general, we will adopt the convention of using $\widetilde{f}$ to denote functionals computed with respect to $\Csig$.)
+
+For $\Sset \subset \Rd$
+\begin{equation*}
+\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
+\end{equation*} 
+is the weighted volume.
+
+The $r$-ball walk over $\Csig$ is a Markov chain. For $x \in \Csig$ and $\Sset, \Sset' \subset \Csig$, the transition probability is given by
+\begin{equation*}
+\widetilde{P}_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}.
+\end{equation*}
+The stationary distribution $\pi_{\Pbb,r}$ thus satisfies
+\begin{equation*}
+\int_{\Csig}  \widetilde{P}_{\Pbb, r}(x;\Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset)
+\end{equation*}
+for all $\Sset \in \Csig$. A simple calculation yields 
+\begin{equation*}
+\ell_{\Pbb,r}(x) := \nu_\Pbb(\Csig \cap B(x,r)) ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx,
+\end{equation*}
+and therefore the ergodic flow is
+\begin{align*}
+\widetilde{Q}_{\Pbb, r}(\Sset, \Sset') & := \int_{\Sset} d\pi_{\Pbb,r}(x) P_{\Pbb, r}(x;\Sset') dx \\
+& =  \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \left(\int_{\Sset' \cap B(x,r)} f(x') dx' \right) dx
+\end{align*}
+The continuous conductance function is then
+\begin{align*}
+\widetilde{\Phi}_{\Pbb,r}(t) & := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} \\
+& = \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\int_{\Sset} f(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' \right) dx}{\int_{\Sset} f(x) \left(\int_{\Csig \cap B(x,r)} f(x') dx' \right) dx}.
+\end{align*}
+
+For $m > 0$ and $0 < t_0 < t_1 < \ldots < t_m < 1$, denote the \emph{stepwise approximation to $g$} by $\bar{g}$, defined as
+\begin{equation}
+\label{eqn: stepwise_approximation}
+\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
+\end{equation}
+The stepwise approximation will be important to showing the consistency results of Section \ref{sec: pointwise_consistency_of_conductance_function} can be translated to a uniform bound.
+Lemma \ref{lem: stepwise_approximation} shows that the approximation will not overly degrade our estimates of the population-level conductance function.
+\begin{lemma}
+	\label{lem: stepwise_approximation}
+	\begin{itemize}
+		\item For any function $f$ monotone decreasing in $t$ on the interval $[t_0,t_m]$, $\bar{f}(t) \leq f(t)$ for all $t \in [t_0,t_m]$.
+		\item Fix
+		\begin{equation*}
+		g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [t_0, 1/2]$}
+		\end{equation*}
+		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq t_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+	The first statement is immediately obvious, and we turn to proving the second.
+
+	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.
+
+	By the concavity of the $\log$ function, 
+	\begin{equation*}
+	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
+	\end{equation*}
+	As a result,
+	\begin{equation*}
+	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
+	\end{equation*}
+\end{proof}
+
+The following theorem is found in \cite{kannan04}. It gives a bound population-level conductance function over convex bodies, when the density is uniform.
+\begin{theorem}[Restatement of \cite{kannan04} Theorem 4.6]
+	\label{thm: kannan}
+	Let $K \subset \Rd$ be a convex body of diameter $D$. Then for any $\Sset \subset K$ with $\pi_{\nu,r}(\Sset) \leq 1/2$,
+	\begin{equation}
+	\label{eqn: kannan}
+	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{\pi_{\nu,r}(\Sset)}\right)\right\}.
+	\end{equation}
+\end{theorem}
+
+\begin{lemma}
+	\label{lem: continuous_conductance_lower_bound}
+	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
+	\begin{itemize}
+		\item 
+		for $0 < t < 1/2$,
+		\begin{equation*}
+		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\end{equation*}
+		\item
+		Let
+		\begin{equation*}
+		M = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
+		\end{equation*}
+		and $t_i = (i + 1)/M$ for $i = 0, \ldots, m - 1$. Then, for $1/M < t < 1/2$
+		\begin{equation*}
+		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+		\end{equation*}
+		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{M - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
+	\end{itemize}
+\end{lemma}
+Before we prove Lemma \ref{lem: continuous_conductance_lower_bound}, note that the choice of $M$ is made to ensure $t_0$ is greater than the local spread of $G_{n,r}\left[\Csig[\Xbf]\right]$, as we will see in Section \ref{sec: convex_consistency}.
+\begin{proof}[Proof of Lemma \ref{lem: continuous_conductance_lower_bound}]
+	We note that
+	\begin{equation*}
+	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
+	\end{equation*}
+
+	Plugging these estimates in to \eqref{eqn: kannan} gives
+	\begin{equation*}
+	\frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \pi_{\Pbb,r}(\Sset)}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
+	\end{equation*}
+	and since the right hand side is decreasing in $\pi_{\Pbb,r}(\Sset)$, the desired lower bound holds on $\widetilde{\Phi}_{\Pbb,r}(t)$.
+The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
+\end{proof}
+
+\subsection{Consistency of local spread and conductance function: convex case.}
+\label{sec: convex_consistency}
+
+The introduction of the stepwise approximation allows us to make use of Lemma \ref{lem: consistency_of_conductance_function}, which gives us (pointwise) consistency of the discrete graph functionals $\widetilde{\Phi}_{n,r}(t)$ to the continuous functionals $\widetilde{\Phi}_{\Pbb,r}(t)$.
+
+We use $\omega_r(1)$ to denote a term which goes to infinity as $r \to 0$, and likewise $o_r(1)$ to denote a term which goes to $0$ as $r \to 0$.
+
+\begin{lemma}
+	\label{lem: consistency_of_conductance_function}
+	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
+	\begin{equation}
+	\label{eqn: pointwise_consistency_of_conductance_function}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\left\{\widetilde{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
+	\end{equation}
+	where $c_d$ is a constant which may depend on the dimension $d$ (as well as the distribution $\Pbb$), but not $r$.
+
+	As a consequence, for $M$ and $(t_i)_{i=0}^{M-1}$ defined as in Lemma \ref{lem: continuous_conductance_lower_bound}, we have that
+	\begin{equation}
+	\label{eqn: consistency_of_stepapprox_conductance_function}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \min\left\{\overline{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
+	\end{equation}
+\end{lemma}
+We defer the proof of pointwise consistency to Section \ref{sec: pointwise_consistency_of_conductance_function}.
+For now, we show that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
+
+\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
+	We take as given that for any $0 < t < 1/2$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
+	\end{equation*}
+	In particular, for sufficiently large $n$ this will occur for each of $t_0, t_1, \ldots, t_m$ and therefore
+	\begin{equation*}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
+	\end{equation*}
+	uniformly over $[1/m,1/2]$.
+\end{proof}
+
+\subsection{Pointwise consistency of conductance function: convex case.}
+\label{sec: pointwise_consistency_of_conductance_function}
+
+We will rely heavily on results of \cite{garciatrillos16}, which prove the same result but consider only a pointwise result on $\widetilde{\Phi}_{n,r}(1/2)$ rather than over the entire conductance function.
+
+Let $\wX = \Csig[\Xbf] = \set{\wx_1, \ldots, \wx_{\wn}}$, and $\wn = \abs{\wX}$. Then
+\begin{equation*}
+\widetilde{\Pbb}_n := \frac{1}{\wn} \sum_{\wx_i \in \wX} \delta_{\wx_i}
+\end{equation*}
+is the empirical distribution of $\wX$. Likewise, for $\Sset \subset \Csig$ let $\widetilde{\Pbb}$ be the conditional distribution $\Pbb(x \in S \vert x \in \Csig)$, given by
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) := \frac{\nu_{\Pbb}(\Sset)}{\nu_{\Pbb}(\Csig)}.
+\end{equation*}
+A Borel map $T: \Csig \to \wX$ is a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset))
+\end{equation*}
+for all $\Sset \in \Csig$.
+
+\begin{lemma}[Proposition 5 of \cite{garciatrillos16}]
+	There exists a sequence of transportation maps $(T_{\wn})$ from $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ such that
+	\begin{equation*}
+	\limsup_{\wn \to \infty} \frac{\wn^{1/d} \norm{\Id - T_{\wn}}_{\L^{\infty}(\widetilde{\Pbb})}}{(\log \wn)^{p_d} } \leq C
+	\end{equation*}
+	where $p_d = 1/d$ for $d \geq 3$ and $3/4$ if $d = 2$. 
+\end{lemma}
+These are referred to stagnating transportation maps. We refer the curious reader to \cite{garciatrillos16} for more details.
+
+For $S \subset \wX$, we will denote $\vol(S; \widetilde{G}_{n,r})$ by $\widetilde{\vol}_{n,r}(S)$, and likewise $\cut(S; \widetilde{G}_{n,r})$ by $\widetilde{\cut}_{n,r}(S)$.
+
+Consider a sequence of sets $(S_{\wn})_{\wn \in \mathbb{N}}$, with $u_{\wn} = \1_{S_{\wn}}$ the characteristic function of $S_{\wn}$. Similarly, for $\Sset \subset \Csig$ let $u = \1_{\Sset}$.
+
+\begin{definition}
+	For a sequence $(u_{\wn}) \in L^1(\widetilde{\Pbb}_{\wn})$ and $u \in L^1(\widetilde{\Pbb})$, we say $(u_{\wn})$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $(T_{\wn})$ such that
+	\begin{equation*}
+	\int_{\Csig} \abs{u(x) - (u_{\wn}) \circ T_{\wn}(x)} d\widetilde{\Pbb}(x) \to 0
+	\end{equation*}
+	and denote it $u_{\wn} \overset{TL^1}{\to} u$.
+\end{definition}
+
+\begin{lemma}
+	\label{lem: cut_convergence}
+	If $(u_{\wn}) \overset{TL^1}{\to} u$, with probability one
+	\begin{equation*}
+	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} = \int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx
+	\end{equation*}
+	where $\wf$ is the density function of $\wPbb$ over $\Csig$.
+\end{lemma}
+
+\begin{proof}
+	We note immediately that $n \to \infty$ implies $\wn \to \infty$ with probability one.
+
+	Now, we can write
+	\begin{align*}
+	 \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\wn^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \bigl( 1 - u_{\wn}(\wx_j) \1(\norm{\wx_i - \wx_j} \leq r) \bigr)  \\
+	& = \int_{\Csig} \left(\int_{\Csig \cap B(x,r)} u_{\wn}(x) \bigl( 1 - u_{\wn}(x') \bigr) d\wPbb_n(x') \right) d\wPbb_n(x) \\
+	& = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x).
+	\end{align*}
+
+	Note that, for any $x \in \Csig$,
+	\begin{align*}
+	\lim_{n \to \infty} \nu\bigl(B(T_{\wn}(x),r) \setminus B(x,r)\bigr) & = 0 \\
+	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0.
+	\end{align*}
+	and therefore
+	\begin{equation*}
+	\lim_{n \to \infty} \int_{\Csig \cap B(T_{\wn}(x),r)} \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') = \lim_{n \to \infty} \int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x')\right) d\wPbb(x').
+	\end{equation*}
+	An application of the bounded convergence theorem yields
+	\begin{align*}
+	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) = \nonumber \\
+	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x).
+	\end{align*}
+	Letting
+	\begin{align*}
+	\mathcal{I}_n^1 & = \int_{\Csig} \left(u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( u(x') - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) \\
+	\mathcal{I}_n^2 & = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x) - u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) \\
+	\end{align*}
+	we have
+	\begin{align}
+	\label{eqn: pointwise_convergence_1}
+	& \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) = \nonumber \\
+	& \int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\wPbb(x') \right\} d\wPbb(x) + \mathcal{I}_n^1 + \mathcal{I}_n^2. 
+	\end{align}
+
+	Recalling that $u = 1_{\Sset}$, we can see
+	\begin{align}
+	\label{eqn: pointwise_convergence_2}
+	\int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\wPbb(x') \right\} d\wPbb(x) & = \int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx
+	\end{align}
+	Since $(u_{\wn}) \overset{TL^1}{\to} u$, another application of the bounded convergence theorem yields $\lim_{n \to \infty} \mathcal{I}_n^1 = \lim_{n \to \infty} \mathcal{I}_n^2 = 0$.
+Therefore by \eqref{eqn: pointwise_convergence_1} and \eqref{eqn: pointwise_convergence_2} the final result holds.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: vol_convergence}
+	If $u_{\wn} \overset{TL^1}{\to} u$, then
+	\begin{equation*}
+	\lim_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} = 
+	\int_{\Sset} \wf(x) \left(\int_{\Csig \cap B(x,r)} \wf(x') dx' \right) dx
+	\end{equation*}
+	with probability one. 
+\end{lemma}
+\begin{proof}
+	We note that
+	\begin{align*}
+	\frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\widetilde{n}^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \1(\norm{\wx_i - \wx_j} \leq r) - \frac{1}{\widetilde{n}} \\
+	& = \int_{\Csig} \int_{\Csig \cap B(x,r)} \left(u_{\wn}(x) d\wPbb_n(x')\right) d{\wPbb}(x) - \frac{1}{\wn}
+	\end{align*}
+	Of course, $\lim_{n \to \infty}  \frac{1}{\wn} = 0$, and so
+	\begin{equation*}
+	\lim_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} = \lim_{n \to \infty} \int_{\Csig} \left(\Csig \cap B(x,r) u_{\wn}(x) d\wPbb_n(x')\right) d_{\wPbb}(x)
+	\end{equation*}
+	The proof then proceeds analogously to Lemma \ref{lem: cut_convergence}. 
+\end{proof}
+
+Lemma \ref{lem: pre-compactness} can be found in \cite{alberti1998non} (Theorem 3.1) or \cite{garciatrillos16} (Lemma 23).
+\begin{lemma}
+	\label{lem: pre-compactness}
+	If $u_{\wn} \not\overset{TL^1}{\to} u$ for some $u \in L^1{\nu}$, with probability one:
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(\Sset_{\wn})}{\wn^2 } \geq  c_d r^{d+1} \omega_r(1)
+	\end{equation*}
+	where $c_d$ is a constant which does not depend on $r$ but may depend on $\Csig$ and $f$, and $\omega_r(1) \to \infty$ as $r \to 0$. 
+\end{lemma}
+
+\begin{proof}[Proof of \eqref{eqn: pointwise_consistency_of_conductance_function}]
+	Let $(S_{\wn}^{\star})$
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S_{\wn}^{\star})}{\widetilde{\vol}_{n,r}(S_{\wn}^{\star})} = \widetilde{\Phi}_{n,r}(t),~~ \widetilde{\pi}_{n,r}(S_{\wn}) \leq t
+	\end{equation*}
+	be the sequence of minimizers of the normalized cut with stationary distribution at most $t$ in the graph $\widetilde{G}_{n,r}$.
+Denote $u_{\wn}^{\star} = 1_{S_{\wn}^{\star}}$, and assume that $u_{\wn}^{\star} \overset{TL^1}{\to} u$, for $u = 1_{\Sset}, ~\Sset \subset \Csig$.
+	Then, by Lemmas \ref{lem: cut_convergence} and \ref{lem: vol_convergence},
+	\begin{align*}
+	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\widetilde{\vol}_{n,r}(S_{\wn})} & = \frac{\int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx}{\int_{\Sset} \wf(x) \left(\int_{\Csig \cap B(x,r)} \wf(x') dx' \right) dx} \\
+	& \overset{(i)}{=} \frac{\int_{\Sset} f(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' \right) dx}{\int_{\Sset} f(x) \left(\int_{\Csig \cap B(x,r)} f(x') dx' \right) dx} 
+	& = \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}.
+	\end{align*}
+	where $(i)$ holds because the normalization factors present in $\wf$ cancel.
+From Lemma \ref{lem: vol_convergence}, we also have that $\lim_{n \to \infty}\widetilde{\pi}_{n,r}(S_{\wn}) = \pi_{\Pbb,r}(\Sset)$, and therefore $\pi_{\Pbb,r}(\Sset) \leq t$.
+As a result,
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} \geq \widetilde{\Phi}_{\Pbb,r}(t).
+	\end{equation*}
+	On the other hand, if $u_{\wn}^{\star}$ does not converge $TL^1$, then
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} \geq c_d r^{d+1} \omega_r(1)
+	\end{equation*}
+	Additionally,
+	\begin{equation*}
+	\frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} \leq \frac{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}{\wn^2}
+	\end{equation*}
+	and
+	\begin{equation*}
+	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}{\wn^2} \leq \nu_d r^d \Lambda_{\sigma}
+	\end{equation*}
+	As a result,
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\widetilde{\vol}_{n,r}(S_{\wn})} \geq c_d r \omega_r(1).
+	\end{equation*}
+\end{proof}
+
+\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
+\label{sec: inverse_mixing_time_lower_bound}
 Throughout this proof, we will refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$.
@@
 \end{equation*}
-where $s_{\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$.
+where $s_{\Pbb,r}$ is as in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.
 We now replace the discrete conductance function $\widetilde{\Phi}_{n,r}$ by the stepwise approximation to the continuous conductance function, $\overline{\Phi}_{n,r}$:
@@
 & = \int_{s_{\Pbb,r}}^{1/2} \limsup_{n \to \infty} \frac{4}{t\overline{\Phi}_{n,r}^2(t)} dt\\
-& \overset{(ii)}{\leq} \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt \\
+& \overset{(ii)}{\leq} \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt + c_d^2 \log(s_{\Pbb,r}) \frac{1}{r^2} o_r(1)\\
 \end{align*}
@@
 
-\section{OTHER STUFF}
-
-	\begin{lemma}[Bernstein's inequality for $U$-statistics]
-		\label{lem: bernstein}
-		Additionally, assume $\sigma^2 = \var\left(k(X_1, \ldots, X_m) \right) < \infty$. Then for any $\delta > 0$, 
-		\begin{align*}
-		\mathbb{P}(U - \mathbb{E}U \geq t) \leq \exp\left\{-\frac{n}{2m}\frac{t^2}{\sigma^2 + t/3}\right\},
-		\end{align*}
-
-		Moreover if $\sigma^2 \leq \mu/n$, 
-		\begin{align*}
-		U & \leq \mathbb{E}U \cdot \left(1 + \max\left\{ \sqrt{\frac{2m\log(1/\Delta)}{\mu}}, \frac{2m \log(1/\Delta)}{3\mu} \right\}\right), \\
-		U & \geq \mathbb{E}U \cdot \left(1 - \max\left\{ \sqrt{\frac{2m\log(1/\Delta)}{\mu}}, \frac{2m \log(1/\Delta)}{3\mu} \right\}\right)
-		\end{align*}
-		each with probability at least $1 - \Delta$.
-	\end{lemma}
-
-\textcolor{red}{\textbf{Multiplicative bound}: As $\tilde{k}(x_1,x_2)$ is the sum of two Bernoulli random variables with negative covariance (since $\1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) = 1$ implies $\1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig) = 0$ and vice versa), we can upper bound $\var\left(\tilde{k}(x_1, x_2)\right) \leq  \widetilde{p}$, where we recall
-	\begin{equation*}
-	\widetilde{p} = 2\cdot \mathbb{P}\left(\1(x_1 \in \Asigr) \1(x_2 \in B(x_1,r) \cap \Asig)\right)
-	\end{equation*}
-	From Lemma \ref{lem: bernstein}, we therefore have
-	\begin{equation*}
-	\frac{\widetilde{\mathcal{E}}}{{n \choose 2}} \leq \widetilde{p} + \max\left\{ \sqrt{\frac{4\log(1/\Delta)\widetilde{p}}{n}}, \frac{4 \log(1/\Delta)}{3n} \right\}
-	\end{equation*}
-	with probability at least $1 - \Delta$.}
-
-\textcolor{red}{Multiplicative bound: The two terms on the right hand side are both distributed $\mathrm{Bernoulli}(p/2)$.
-Moreover, since $\1(x_i \in A_\sigma) = 1$ implies $\1(x_j \in A_{\sigma}) = 0$, they have negative covariance.
-We can therefore upper bound $\var(k'(x_i,x_j)) \leq p$, and so from Lemma \ref{lem: bernstein}, we have
-	\begin{equation*}
-	\frac{\mathcal{V}}{{n \choose 2}} \geq p - \max\left\{ \sqrt{\frac{4\log(1/\Delta)p}{n}}, \frac{4 \log(1/\Delta)}{3n} \right\}
-	\end{equation*}
-	with probability at least $1 - \Delta$. }
+\subsection{Concentration inequalities}
+
+Given a symmetric kernel function $k: \mathcal{X}^m \to \Reals$, and data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$m$ $U$ statistic} to be 
+\begin{equation*}
+U := \frac{1}{ {n \choose m} } \sum_{1 \leq i_1 < \ldots < i_m \leq n} k(x_{i_1},\ldots,x_{i_m})
+\end{equation*}
+
+For Lemmas \ref{lem: bounded_difference}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed.
+We will additionally assume the order-$m$ kernel function $k$ satisfies the boundedness property $\sup_{x_1, \ldots, x_m} \abs{k(x_1, \ldots, x_m)} \leq 1$.
+
+\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
+	\label{lem: bounded_difference}
+	For any $t > 0$,
+	\begin{equation*}
+	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{- \frac{2nt^2}{m}\right\}
+	\end{equation*}
+	Further, for any $\delta > 0$, we have
+	\begin{align*}
+	U & \leq \mathbb{E}U + \sqrt{\frac{m \log(1 / \delta)}{2n} }, \\
+	U & \geq \mathbb{E}U - \sqrt{\frac{m \log(1 / \delta)}{2n} }
+	\end{align*}
+	each with probability at least $1 - \delta$. 
+\end{lemma}
+
+We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
+\begin{lemma}
+	\label{lem: multiplicative_Hoeffding}
+	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
+	\begin{align*}
+	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
+	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
+	\end{align*}
+\end{lemma}
+
+\clearpage
+\bibliographystyle{plain}
+\bibliography{icml_bib}
+
 \end{document}

### 2019-01-22 icml/proof_of_theorem_4.tex
added todays changes

\documentclass{article}

% \usepackage{icml2019}
% \usepackage[accepted]{icml2019}

\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\theequation}{A.\arabic{equation}}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
%\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{xr-hyper}
\usepackage{bm}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}

\externaldocument{icml_local_density_clustering}

\newcommand{\diam}{\mathrm{diam}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\1}{\mathbf{1}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\Err}{\mathrm{Err}}
\newcommand{\Log}{\mathrm{Log}}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\Id}{\mathrm{Id}}

%%% Graph terms
\newcommand{\cut}{\mathrm{cut}}

%%% Vectors
\newcommand{\pbf}{\mathbf{p}}
\newcommand{\qbf}{\mathbf{q}}
\newcommand{\ebf}[1]{\mathbf{e}_{#1}}
\newcommand{\pibf}{\bm{\pi}}
\newcommand{\rhobf}{\bm{\rho}}
\newcommand{\Deltabf}{\bm{\Delta}}
\newcommand{\deltabf}{\bm{\delta}}
\newcommand{\zbf}{\mathbf{z}}

%%% Random walk vectors

%%% Matrices
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Ibf}[1]{\mathbf{I}_{#1}}

%%% Probability distributions (and related items)
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Cbb}{\mathbb{C}}
\newcommand{\Ebb}{\mathbb{E}}

%%% Sets
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Asig}{\Aset_{\sigma}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}

%%% Operators
\DeclareMathOperator*{\argmin}{arg\,min}

%%% Algorithm notation
\newcommand{\ppr}{{\sc PPR}}
\newcommand{\pprspace}{{\sc PPR~}}

%%% Tilde notation for quantities over the expansion set 
\newcommand{\wn}{\widetilde{n}}
\newcommand{\wX}{\widetilde{\Xbf}}
\newcommand{\wx}{\widetilde{x}}
\newcommand{\wz}{\widetilde{z}}
\newcommand{\wbz}{\widetilde{\bf{z}}}
\newcommand{\wu}{\widetilde{u}}
\newcommand{\wPbb}{\widetilde{\Pbb}}
\newcommand{\wf}{\widetilde{f}}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

%\newcommand{\theHalgorithm}{\arabic{algorithm}}

%\icmltitlerunning{Local clustering of density upper level sets}

\begin{document}

Let $\pbf = (p_u)_{u \in \Xbf}$ denote the \pprspace vector computed over $G_{n,r}$ (where for ease of reading we suppress dependence on the hyperparameter $\alpha$ and seed node $v$.)

\begin{lemma} 
	\label{lem: setup}
	Consider running Algorithm \ref{alg: ppr} with any $r < \sigma$ and

	\begin{equation} 
	\label{eqn: upper_bound_alpha}
	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
	\end{equation}

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ such that the following statements hold for all $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For all $u \in \Cset[\Xbf]$,
		\begin{equation*}
		p_u \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation*}
		\item For all $u' \in \Csig'[\Xbf]$,
		\begin{equation*}
		p_{u'} \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation*}
	\end{itemize}
\end{lemma}

\begin{proof}

	For $S \subseteq X_1^n$, let $I_{S}$ be a diagonal matrix where $I_{jj} = 1$ if $X_j \in S$ and 0 otherwise. Let $D_S$ be the corresponding degree matrix for the subgraph induced by $S$. $D_S$ is a diagonal matrix where for $X_j \in S$, $(D_S)_{jj} = \sum_{i: X_i \in S} A_{ij}$, and if $X_j \not \in S$ then $(D_S)_{jj} = 0$. Then, define \textit{leakage} and \textit{soakage} vectors

	\begin{align*}
	\ell_t & := e_v  (W I_{\Csig[\Xbf]})^t (I - D^{-1} D_{\Csig[\Xbf]}) \\
	\ell & := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t \\
	s_t & := e_v (W I_{\Csig[\Xbf]})^t (W I_{G / \Csig[\Xbf]}) \\
	s & := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t
	\end{align*}

	Roughly, the proof will unfold in four steps. The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).

	\begin{enumerate}
		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to lower bound $p_v(u) \geq 4/5 \widetilde{\pi}(u) - \widetilde{p}_{\ell}(u)$, where $\widetilde{p}$ is the PPR random walk over the subgraph induced by $\Csig[\Xbf]$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$.
		\item Since $r < \sigma$, there are no edges between $u$ and $G / \Csig[\Xbf]$. Therefore, the page-rank vector $\widetilde{p}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. This will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
		\item For vertices $u' \in G / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]pr$.
		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]prthick$. Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$. This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Proposition \ref{thm: setup}.
	\end{enumerate}

	\paragraph{Step 1}
	We will begin by restating the results of \cite{zhu2013}.

	Denote by $\widetilde{p}$ the PageRank vector computed only over the subgraph induced by $\Csig[\Xbf]$.

	\begin{align} \label{eqn: page_rank_body}
	\widetilde{p}_v & = \alpha e_v + (1 - \alpha) \widetilde{p}_v \widetilde{W} \\
	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{W}^t \right)
	\end{align}

	and correspondingly for the leakage vector

	\begin{equation*}
	\widetilde{p}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{p}_{\ell} \widetilde{W}.
	\end{equation*}

	From Lemma 3.1 of \cite{zhu2013} we have for all $u \in \Csig[\Xbf]$

	\begin{equation*} \label{eqn: zhu_body}
	p_v(u) \geq \widetilde{p}_v(u) - \widetilde{p}_{\ell}(u).
	\end{equation*}

	with $||\ell||_1 \leq \frac{2 \Phi^{btw}(\Csig[\Xbf])}{\alpha}$. Moreover if, as we have specified, $\alpha \leq \frac{1}{9 T_{\infty}(\Csig[\Xbf])}$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$

	\begin{equation} \label{eqn: page_rank_mixes}
	\widetilde{p}_v(u) \geq \frac{4}{5} \widetilde{\pi}(u).
	\end{equation}

	\paragraph{Step 2}

	We turn to upper bounding $\widetilde{p}_{\ell}(u)$. We have

	\begin{align} \label{eqn: leakage_page_rank_body}
	\widetilde{p}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{W}^t \right)[u]  \nonumber \\
	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{d_{\min}(\Csig[\Xbf])} 
	\end{align}

	where $\text{(i)}$ follows from the fact that since $r < \sigma$, $E(\Cset'[\Xbf], G / \Csig[\Xbf]) = 0$ and therefore $\ell(u) = 0$. To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{W}^{t-1}$, and then

	\begin{align*}
	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u] & = \left(q W \right)[u] \\
	& \leq \|q\|_1 \|W(\cdot, u)\|_{\infty} \\
	& \overset{\text{(iii)}}{\leq} \frac{1}{d_{\min}(C^{\sigma}_n)}.
	\end{align*}

	where $\text{(iii)}$ comes from the fact that $\|u-v\| \leq r$ means $v \in \Csig[\Xbf]$.
	Combining (\ref{eqn: leakage_page_rank_body}) with (\ref{eqn: page_rank_mixes}), and since $||\ell||_1 \leq 2 \frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$, we have

	\begin{equation*}
	p_v(u) \geq \frac{4}{5} \widetilde{\pi}(u) - 2\frac{9 \Phi^{btw}(\Csig[\Xbf])}{d_{\min}(\Csig[\Xbf]) \alpha}.
	\end{equation*}

	\paragraph{Step 3}
	To get the corresponding upper bound on $p_v(u')$, we will use the soakage vectors $s$ and $s_t$. We will first argue that $s$ is a worse starting distribution -- meaning it puts uniformly more mass outside the cluster -- than simply starting at $v$.

	\begin{lemma} \label{lem: gained mass is soaked_body}
		For all $u' \notin \Csig[\Xbf]$,
		\begin{equation}
		p_v(u') \leq p_{s}(u').
		\end{equation}
	\end{lemma}

	The proof of Lemma \ref{lem: gained mass is soaked_body} is left to the supplement. It follows largely the same steps as Lemma 3.1 of \cite{zhu2013}, except over $G / \Csig[\Xbf]$ rather than $\Csig[\Xbf]$.

	\paragraph{Step 4}

	Just as we upper bounded the probability mass $\widetilde{p}_{\ell}$ could assign to any one vertex, we can upper bound

	\begin{align} \label{eqn: soakage_page_rank_body}
	\widetilde{p}_{s}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \widetilde{W}^t \right)[u]  \nonumber \\
	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
	& \leq \|s\|_1 \frac{1}{d_{\min}(\Csig[\Xbf])}.
	\end{align}

	Finally, by the definition of $s_t = e_v (W I_{\Csig[\Xbf]})^t (W I_{G / \Csig[\Xbf]})$, letting $q_t = e_v (W I_{\Csig[\Xbf]})^t$ for ease of notation, we have
	\begin{align*}
	\|s_t\|_1 & = \|q_t (W I_{G / \Csig[\Xbf]})\|_1 \\
	& = \sum_{u' \in G} \sum_{u \in G} q_t(u) (W I_{G / \Csig[\Xbf]})[u, u'] \\
	& = \sum_{u' \in G / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q(u)}{d(u)} I(e_{u,u'} \in G) \\
	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) (d(u) - d_{\Csig[\Xbf]}(u) )}{d(u)} \\
	& = \|q_t (I - D^{-1} D_{\Csig[\Xbf]})\|_1 = \|\ell_t\|_1.
	\end{align*}

	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.

\end{proof}

\begin{lemma}
	\label{lem: ball_bounds_in_probability}
	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
	\begin{align*}
	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
	\end{align*}
	 where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
\end{lemma}

The statement follows immediately from Lemma \ref{lem: ball_bounds}.

\subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}

We note that by Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, 
\begin{equation*}
\kappa_2(\Cset) \geq \frac{\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])}.
\end{equation*}
As a result Lemma \ref{lem: setup} implies
\begin{align}
\label{eqn: theorem_4_1}
p_u & \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~ (u \in \Cset[\Xbf]) \nonumber \\
p_{u'} & \leq \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~~~~~~~~~~~~~~~~ (u' \in \Cset'[\Xbf])
\end{align}

We then have
\begin{align*}
\widetilde{\pi}_{n,r}(u) & \geq \frac{D_{\min}(\Csig[X]; \widetilde{G}_{n,r})}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \\
& \geq \frac{D_{\min}(\Csig[X]; \widetilde{G}_{n,r})}{\wn \widetilde{D}_{\max}}
\end{align*}
and application of Lemma \ref{lem: ball_bounds_in_probability} yields
\begin{equation}
\label{eqn: theorem_4_2}
\widetilde{\pi}_{n,r}(u) \geq 8 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
\end{equation}
and
\begin{equation}
\label{eqn: theorem_4_3}
\frac{1}{\widetilde{D}_{\min}} \leq \frac{2}{\nu_d r^d \lambda_{\sigma}}
\end{equation}
with probability tending to $1$ as $n \to \infty$, for all $u \in \Cset[\Xbf]$.

Combining \eqref{eqn: theorem_4_1}, \eqref{eqn: theorem_4_2} and \eqref{eqn: theorem_4_3}, along with the requirement on $\kappa_2(\Cset)$ given by \eqref{eqn: kappa2_ub}, we have
\begin{align*}
p_u & \geq 3/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2} \\
p_{u'} & \leq 1/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
\end{align*}
for any $u \in \Cset$, $u' \in \Cset'$. As a result, if $\pi_0 \in (2/5, 3/5)\cdot \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}$, as $n \to \infty$ with probability tending to one any sweep cut of the form of \eqref{eqn: sweep_cuts}, including the output set $\widehat{C}$, will successfully recover $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery}.

\bibliography{icml_bib}
\bibliographystyle{plain}

\end{document}

### 2019-01-23 icml/icml_local_density_clustering.tex
Edits through Sect 1

@@
 \newtheorem{remark}{Remark}
-
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
 
-\icmltitlerunning{Local clustering of density upper level sets}
+%%%%%
+\icmltitlerunning{Local Spectral Clustering of Density Upper Level Sets}
 
@@
 \icmltitle{Local Spectral Clustering of Density Upper Level Sets}
-
 \icmlsetsymbol{equal}{*}
@@
 \icmlauthor{Sivaraman Balakrishnan}{cmu}
-\icmlauthor{Ryan Tibshirani}{cmu}
+\icmlauthor{Ryan J. Tibshirani}{cmu}
 \end{icmlauthorlist}
 
-\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}
-
+\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon
+  University, Pittsburgh PA, USA} 
 \icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
-
 \icmlkeywords{local clustering}
@@
 
-\printAffiliationsAndNotice{} % otherwise use the standard text.
+\printAffiliationsAndNotice{}
 
 \begin{abstract}
-	Spectral clustering methods are 
-	a family of popular non-parametric clustering tools.
-	Recent works have proposed and analyzed 
-	\emph{local} spectral methods, which 
-	extract clusters using
-	locally-biased random walks around a user-specified seed node, and are known to have worst-case guarantees for certain graph-based measures of cluster quality.
-	In contrast to existing works, 
-	we analyze the personalized PageRank (\ppr) algorithm in the classical statistical learning setup,
-	where we obtain samples from an unknown distribution, and aim to identify connected
-	regions of high-density (density clusters).
-	We introduce a bicriteria for evaluating cluster quality and provide guarantees for these criteria evaluated on empirical analogues to these density clusters.
-As a result, the \pprspace algorithm run over a neighborhood graph is shown to
-	extract sufficiently salient density clusters.
+\vskip 0.1 in % RJT: there was no space here and it looked very squished 
+Spectral clustering methods are a family of popular nonparametric clustering
+tools.  Recent works have proposed and analyzed \emph{local} spectral methods,
+which extract clusters using locally-biased random walks around a user-specified
+seed node.  Several local methods, such as the personalized PageRank (PPR)
+algorithm, have been shown to have worst-case guarantees for certain graph-based
+measures of cluster quality.  In contrast to existing works, we analyze PPR in a
+traditional statistical learning setup, where we obtain samples from an unknown
+distribution, and aim to identify connected regions of high-density (density
+clusters).  We introduce two natural criteria for cluster quality, and derive
+bounds for these criteria when evaluated on empirical analogues of density
+clusters. Moreover, we prove that PPR, run on a neighborhood graph, extracts
+sufficiently salient density clusters.   
 \end{abstract}
@@
 \section{Introduction}
-\label{introduction}
+\label{sec: introduction}
 
-Let $\mathbf{X} := (x_1, \ldots, x_n)$ be a sample drawn i.i.d from a distribution $\Pbb$ with density $f$ supported on $\Rd$.
-Our statistical learning task is clustering: splitting data into groups which satisfy some notion of within-group similarity and between-group difference.
+Let $\mathbf{X} = \{x_1, \ldots, x_n\}$ be a sample drawn i.i.d.\ from a
+distribution $\Pbb$ on $\Rd$, with density $f$, and consider the problem of 
+clustering: splitting the data into groups which satisfy some notion of
+within-group similarity and between-group difference.  We focus on spectral
+clustering methods, a family of powerful nonparametric clustering algorithms.
+Roughly speaking, a spectral technique first constructs a geometric graph $G$,
+where vertices are associated with samples, and edges correspond to proximities
+between samples. It then learns a feature embedding based on the Laplacian of
+$G$, and applies a simple clustering technique (such as k-means clustering) in
+the embedded feature space.
 
-Spectral clustering methods are a family of powerful non-parametric clustering algorithms.
-Let $G = (V,E)$ be an unweighted and undirected graph, with $\Abf \in \Reals^{V \times V}$ the symmetric adjacency where $A_{uv} = 1$ if $(u,v) \in G$.
-We form the random walk transition probability matrix $\Wbf$, and corresponding graph Laplacian matrix $\Lbf$\footnote{Often, either of the Laplacian matrices  $\Lbf_{sym} := \Dbf^{\frac{1}{2}}\Wbf \Dbf^{-\frac{1}{2}}$ or $\Lbf_{unn} := \Dbf - \Abf$ are used instead.}:
-\begin{equation}
-\label{eqn: random_walk_laplacian}
-\Wbf := \Dbf^{-1}\Abf; ~~~ \Lbf = \Ibf{n} - \Wbf
-\end{equation}
-where the degree matrix $\Dbf$ is a diagonal matrix with $\Dbf_{uu} := \sum_{v \in V} \Abf_{uv}$, and $\Ibf{n}$ is the $n \times n$ identity matrix.
+To be more precise, let $G=(V,E,w)$ denote a weighted, undirected graph  
+constructed from the samples $\mathbf{X}$, where $V=\{1,\ldots,n\}$, and $w_{uv}
+= K(x_u,x_v) \geq 0$ for $u,v \in V$, and a particular kernel function $K$.
+Here $(u,v) \in E$ if and only if $w_{uv} > 0$.  We denote by $\Abf \in
+\Reals^{n \times n}$ the weighted adjacency matrix, which has entries
+$A_{uv}=w_{uv}$, and by $\Dbf$ the degree matrix, with 
+\smash{$\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$}.  We also denote by $\Wbf,\Lbf$
+the random walk transition probability matrix and normalized\footnote{Other
+  popular choices here include the unnormalized Laplacian, and symmetric
+  normalized Laplacian.} 
+Laplacian matrix, respectively, which are defined as
+$$
+\Wbf = \Dbf^{-1}\Abf, \quad \Lbf = \Ibf{} - \Wbf,
+$$
+where $\Ibf{} \in \Reals^{n\times n}$ is the identity matrix.  Classical global
+spectral methods take a eigendecomposition $L=U \Sigma U^T$, use some 
+number of eigenvectors (columns in $U$) as a feature representation for the
+samples, and then run (say) k-means in this new feature space.
 
-Roughly speaking, spectral clustering techniques first learn an embedding the data $\Xbf$ using the spectrum of the graph Laplacian, and subsequently 
-apply a simple clustering technique (such as k-means) to this \emph{spectral embedding}.
-When applied to large graphs (or large point clouds) classical global spectral 
-methods can be computationally cumbersome and 
-insensitive to the local geometry of the distribution of the samples
-\citep{mahoney2012,leskovec2010}.
-This in turn has led to the investigation of local spectral algorithms \citep{spielman2013,anderson2006,leskovec2010}
-which leverage locally-biased spectra computed using random walks around 
-a user-specified seed node.
+When applied to geometric graphs constructed from a large number of samples,
+global spectral clustering methods can be been computationally cumbersome and   
+insensitive to the local geometry of the underlying distribution
+\citep{leskovec2010,mahoney2012}.  This has led to recent increased interest in
+local spectral algorithms, which leverage locally-biased spectra computed using
+random walks around a user-specified seed node.  A popular local clustering
+algorithm is Personalized PageRank (PPR), first introduced by
+\citet{haveliwala2003}, and further developed by
+\citet{spielman2011,spielman2014,anderson2006,mahoney2012,zhu2013}, among 
+others.
 
-We are interested in understanding what the output of a clustering algorithm on $\Xbf$ reveals about the unknown density $f$.
-For $\lambda > 0$ and the upper level set $\set{x: f(x) \geq \lambda}$, it is intuitive \cite{hartigan1981,chaudhuri2010} to define clusters as the connected components $\mathbb{C}_f(\lambda)$ of the upper level set; we call these connected regions of high density \textit{density clusters}, and study the ability of spectral methods to identify such clusters.
+Local spectral clustering techinques have been practically very successful
+\citep{leskovec2010,mahoney2012,REFS}, which
+has led many authors to develop theory that explains their success 
+\citep{zhu2013,REFS},
+from the perspective of worst-case guarantees on traditional graph-theoretic
+notions of cluster quality (like conductance).  In this paper, we adopt a more
+traditional statistical viewpoint, and examine what the output of a local
+clustering algorithm on $\Xbf$ reveals about the unknown density $f$.  
+In particular, we examine the ability of the PPR algorithm to recover
+\emph{density clusters} of $f$, which are defined as the connected components of
+the upper level set $\{x : f(x) \geq \lambda\}$ for some threshold $\lambda >
+0$ (a central object of central interest in the classical statistical literature
+on clustering, dating back to \citealt{hartigan1981}).
 
-\paragraph{Graph connectivity criteria.}
+\subsection{Graph Connectivity Criteria}
 
-A somewhat more standard mode of understanding spectral clustering methods is to view them as approximating some graph connectivity criteria.
-There are many graph-based measures which assess the cluster quality of a subset $S \subseteq V$ (or more generally the quality of a partition $S_1 \cup \ldots \cup S_m = V$, for $m \geq 2$.
-See \cite{yang2015,fortunato2010} for an overview.)
+Here we define a pair of criteria that reflect the quality of a cluster with
+respect to $G=(V,E,w)$.  There are many graph-based measures of cluster quality  
+that one could consider; see, e.g., \citet{yang2015,fortunato2010} for 
+an overview.  The pair of criteria that we focus on are (arguably) quite
+natural, and moreover, they play a fundamental role in our analysis 
+of the PPR algorithm.  Our two critera capture the \emph{external} and
+\emph{internal} connectivity of a subset $S \subseteq V$, denoted $\Phi(S; G)$
+and $\Psi(S; G)$, respectively, and defined below in turn.
 
-Arguably a natural way to assess cluster quality is via a pair of criteria capturing the \emph{external} and \emph{internal connectivity} of $S$, respectively.
-We define the external connectivity of a subset $S \subseteq V$ to be its normalized cut.
-For $S' \subset V$, the cut between $S$ and $S'$ is
-\begin{equation*}
-\cut(S, S'; G) := \sum_{u \in S} \sum_{v \in S'} \1\left((u,v) \in E \right)
-\end{equation*}
-and the volume of $S$ is
-\begin{equation*}
-\vol(S; G) := \sum_{u \in S} \sum_{v \in V} \1\left((u,v) \in E \right).
-\end{equation*}
-Then, the \emph{normalized cut} of $S$ is
+\paragraph{External Connectivity: Normalized Cut.}
+
+Define the cut between subsets $S,S' \subseteq V$ to be
+$$
+\cut(S, S'; G) = \sum_{u \in S} \sum_{v \in S'} w_{uv},
+$$
+and define
+\smash{$\vol(S; G) = \cut(S, V; G) = \sum_{u \in S} \sum_{v \in V} w_{uv}$}.  
+As our notion of external connectivity, we use the \emph{normalized cut}  
+of $S$, defined as 
 \begin{equation}
 \label{eqn: norm_cut}
-\Phi(S; G) := \frac{\cut(S; G)}{ \min\left\{\vol(S; G), \vol(S^c; G) \right\} }
+\Phi(S; G) = \frac{\cut(S; G)}{\min\{\vol(S; G), \vol(S^c; G)\}},
 \end{equation} 
-(where we abbreviate $\cut(S; G) = \cut(S; S^c; G)$).
+where we abbreviate $\cut(S; G) = \cut(S; S^c; G)$.
 
-Given $S \subseteq V$, the subgraph induced by $S$ is given by $G[S] = (S, E_S)$, where $(u,v) \in E_S$ if both $u$ and $v$ are in $S$ and $(u,v) \in E_S$.
-Our internal connectivity parameter $\Psi(S)$ will capture the time it takes for the random walk over $G[S]$ to mix (that is, approach a stationary distribution) uniformly over $S$.
-Letting $\abs{S} = m$, $\Abf_S$ denotes the $m \times m$ adjacency matrix representation of $G[S]$; similarly, $\Dbf_S$ is the diagonal degree matrix with entries $(\Dbf_{S})_{ii} = \sum_{j: v_j \in S} \Abf_{ij}$, and $\Wbf = \Dbf_S^{-1} \Abf_S$ is the corresponding random walk matrix (again, defined only over $G[S]$.)
+\paragraph{Internal Connectivity: Inverse Mixing Time.}
 
-For $v \in V$ we write
+For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
+$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Abf_S,\Dbf_S$
+be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
+random walk matrix as usual, $\Wbf = \Dbf_S^{-1} \Abf_S$, and for $v \in V$,
+write 
 \begin{equation}
 \label{eqn: random_walk}
-\pibf = (\pi_{u})_{u \in S}, ~~ q_{vu}^{(m)} = e_v\Wbf_S^m e_u
+q_{vu}^{(t)} = e_v\Wbf_S^t e_u
 \end{equation}
-for the stationary distribution and the $m$-step transition probability of the random walk over $G[S]$ originating at $v$.
-\footnote{Given a starting node $v$ and and a random walk defined by transition probability matrix $\mathbf{P}$, the rotation $e_v \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$ steps.
-}
-(Of course, given the definition of $\Wbf_S$ it is of course well known that the stationary distribution $\widetilde{\pibf}$ is given by $\widetilde{\pi}_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$.)
+for the $t$-step transition probability of a random walk over $G[S]$
+originating at $v$.\footnote{Given a starting node $v$ and and a random walk
+  defined by transition probability matrix $\mathbf{P}$, the rotation $e_v
+  \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
+  steps.}   Also write \smash{$\tilde\pibf = (\tilde\pi_{u})_{u \in S}$} for the 
+  stationary distribution of this random walk.  (Given the definition of
+  $\Wbf_S$, it is well-known that the stationariy distribution is given by
+  \smash{$\tilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
 
-The \emph{relative pointwise mixing time} is defined as 
+Our internal connectivity parameter will capture the time it takes for the
+random walk over $G[S]$ to mix (approach the stationary distribution)
+uniformly over $S$.  For this, we first define \emph{relative pointwise mixing
+  time} of $G[S]$ as 
 \begin{equation*}
-\tau_{\infty}(\qbf; G[S]) := \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pi_u}}{\pi_u} \leq 1/4} 
+\tau_{\infty}(\qbf; G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} -
+      \tilde\pi_u|}{\tilde\pi_u} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}, 
 \end{equation*}
-where $\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}, \qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$.
-
-The internal connectivity parameter $\Psi(S; G)$ is simply one over the mixing time:
+where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
+\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. Now our internal 
+connectivity parameter is simply the inverse mixing time,
 \begin{equation}
 \label{eqn: inv_mixing_time}
-\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}
+\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}.
 \end{equation}
 
-The graph clustering task is thus find a subset $S$ (or, for global algorithms, a partition $S_1 \cup \ldots \cup S_m = V$), which has both small external and large internal connectivity.
-If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no less than $\Psi$, we will refer to it as a $(\Phi,\Psi)$-cluster.
-Both local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been shown to output clusters (or partitions) which provably satisfy approximations to the optimal $(\Phi, \Psi)$-cluster (or partition) for a given graph $G$.
-\footnote{In the case of \cite{kannan04}, the internal connectivity parameter $\phi$ is actually the conductance, i.e.
-the minimum normalized cut within the subgraph $G[S]$.
-See Theorem 3.1 for details; however, note that $\phi^2 / \log(\vol(S)) \leq O(\Psi)$, and so the lower bound on $\phi$ translates to a lower bound on $\Psi$.}
+If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no
+less than $\Psi$, we call it as a \emph{$(\Phi,\Psi)$-cluster}. Both
+local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been
+shown to output clusters (or partitions) which approximate the optimal $(\Phi,
+\Psi)$-cluster (or partition) for a given graph $G$.\footnote{In the case of
+  \cite{kannan04}, the internal connectivity parameter $\phi$ is actually the
+  conductance, i.e., the minimum normalized cut within the subgraph $G[S]$. See
+  Theorem 3.1 in their paper for details; however, note that $\phi^2 /
+  \log(\vol(S)) \leq O(\Psi)$, and so the lower bound on $\phi$ translates to a
+  lower bound on $\Psi$.}
 
-\paragraph{Personalized PageRank.}
-As mentioned previously, global algorithms which find spectral cuts may be computationally infeasible for large graphs; in this setting, local algorithms may be preferred or even required.
-We will restrict our attention in particular to one such popular algorithm: \emph{personalized PageRank} (\ppr).
-The personalized PageRank algorithm was first introduced by \cite{haveliwala2003} and variants of this algorithm have been studied further in several recent works \citep{spielman2011,spielman2014,zhu2013,anderson2006,mahoney2012}.
+\subsection{PPR on a Neighborhood Graph}
 
-The random walk matrix $\Wbf$ over the graph $G = (V,E)$ with associated adjacency matrix $\Abf$ is given by (\ref{eqn: random_walk_laplacian}).
-\pprspace is then defined with respect to the following inputs: a user-specified seed node $v \in V$ , and  $\alpha \in [0,1]$ a teleportation parameter.
-Letting $e_{v}$ be the indicator vector for $v$ (meaning $e_v$ has a $1$ in the $v$th location and $0$ everywhere else), the \emph{PPR vector} is the solution to the following linear equation:
+We now describe the clustering algorithm that will be our focus for the rest of 
+the paper. We start with the geometric graph that we form based on the samples 
+$\Xbf$: for a radius $r > 0$, we consider the \emph{$r$-neighborhood graph} of 
+$\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted graph with vertices
+$V=\{1,\ldots,n\}$, and an edge $(u,v) \in E$ if and only if $\norm{x_u - x_v}
+\leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.  Note that this is a
+special case of the general construction introduced above, with 
+$K(u,v) = 1(\norm{x_u - x_v} \leq r)$.
+
+Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, with respect to  
+a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be
+the solution of the following linear system:
 \begin{equation}
 \label{eqn: ppr_vector}
-\pbf(v,\alpha;G) := \alpha \ebf{v} + (1 - \alpha) \pbf(v,\alpha;G) \Wbf
+\pbf = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
 \end{equation}
-We note in passing that, for $\alpha > 0$, the vector $\pbf(v,\alpha;G)$ can be well-approximated by a simple local computation (of a random walk with restarts at the node $v$.) We also point out that, from a density clustering standpoint, since density clusters are inherently local, using the PPR algorithm eases the analysis, and as we will observe in the sequel our analysis requires fewer global regularity conditions relative to more classical global spectral algorithms.
+where $\Wbf$ is the random walk matrix of the underlying graph $G_{n,r}$ 
+and $e_{v}$ denotes indicator vector for node $v$ (with a 1 in the $v$th
+position and 0 elsewhere).  In practice, we can approximately solve the above
+linear system via a simple, efficient random walk, with appropriate restarts to
+$v$.
 
-To compute a cluster $\widehat{C} \subset V$ using the \pprspace vector, we will take sweep cuts of $\pbf(v, \alpha; G)$.
-To do so we require another parameter $\pi_0$.
-For a number $\beta \geq 0$, the sweep cut $S_\beta$ is then
+For a level $\beta > 0$ and a target volume $\pi_0 > 0$, we define a
+\emph{$\beta$-sweep cut} of $\pbf$ as  
 \begin{equation}
 \label{eqn: sweep_cuts}
-S_\beta = \set{u \in V: p_u > \beta \pi_{0}}.
+S_\beta = \{u \in V: p_u > \beta \pi_{0}\}.
 \end{equation}
-We will choose one such sweep cut to be our cluster estimate $\widehat{C}$.
+Having computed sweep cuts over a range \smash{$\beta \in  
+(\frac{3}{10},\frac{1}{2})$},\footnote{The choice of a specific range such as 
+\smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of \pprspace
+algorithms, see, e.g., \citet{zhu2013}.}
+we output a cluster \smash{$\widehat{C} = S_{\beta^*}$}, based on the sweep cut
+$S_{\beta^*}$ that minimizes the normalized cut \smash{$\Phi(S_{\beta^*};
+  G_{n,r})$} as defined in \eqref{eqn: norm_cut}. For concreteness, we summarize
+this procedure in Algorithm \ref{alg: ppr}.
 
-\paragraph{Neighborhood graph.}
-
-To formally introduce the local clustering algorithm we consider, we must first give a method for forming a graph over the data $\Xbf$.
-
-Let $(r_n)$ be a sequence of positive numbers.
-Given a sequence of kernel functions $k_n: \Rd \times \Rd \to [0,\infty)$ of the form $k_n(x,x') = k(\norm{x - x'}/ r_n)$ for $k$ a non-increasing function, and data $\Xbf = \set{x_1, \ldots, x_n}$ sampled from $\Pbb$ as before, form the \emph{neighborhood graph} $G_n = (\Xbf, E_n)$ with $E_n = \set{k(x_i,x_j): 1 \leq i < j \leq n}$.
-(Here, $\norm{\cdot}$ is used to denote Euclidean norm).
-
-Algorithm \ref{alg: ppr} will be the simple variant of PPR we analyze. It will take as input the data $\Xbf$ along with user-specified parameters $r, \alpha$, $\pi_0$, and $v \in \Xbf$. 
 \begin{algorithm}
-	\caption{PPR on a neighborhood graph}
+\caption{PPR on a Neighborhood Graph}
 \label{alg: ppr}	
-	{\bfseries Input:} data $\Xbf$, radius $r$, teleportation parameter $\alpha \in [0,1]$, seed node $v \in \Xbf$, target $\pi_0$. \\
-	{\bfseries Output:} $\widehat{C} \subset V$.
+{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation 
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target volume $\pi_0 >
+0$. \\   
+{\bfseries Output:} cluster $\widehat{C} \subseteq V$.
 \begin{algorithmic}[1]
-		\STATE Form the neighborhood graph $G_{n,r}$ as given in (\ref{eqn: neighborhood_graph})
-		\STATE Compute PPR vector $\pbf(v, \alpha; G_{n,r})$  as defined by (\ref{eqn: ppr_vector}).
-		\STATE For $\beta \in (\frac{3}{10}, \frac{1}{2})$ compute sweep cuts $S_{\beta}$ as defined by (\ref{eqn: sweep_cuts}).
-		\STATE Return
-		\begin{equation*}
-		\label{eqn: sweep_cuts_min_conductance}
-		\widehat{C} = \argmin_{\beta \in (\frac{3}{10}, \frac{1}{2})} \Phi(S_{\beta}; G_{n,r})
-		\end{equation*}
+  \STATE Form the neighborhood graph $G_{n,r}$.
+  \STATE Compute the PPR vector $\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn:
+    ppr_vector}. 
+  \STATE For $\beta \in (\frac{3}{10}, \frac{1}{2})$ compute sweep cuts
+  $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
+  \STATE Return $\widehat{C} = S_{\beta^*}$, where 
+  $$
+  \beta^* = \argmin_{\beta \in (\frac{3}{10}, \frac{1}{2})} \Phi(S_{\beta}; G_{n,r}).
+  $$
 \end{algorithmic}
@@
 
-We note that the choice of a specific interval such as $(\frac{3}{10}, \frac{1}{2})$ for the range of $\beta$ is standard in the analysis of \pprspace algorithms.
+\subsection{Summary of Results}
 
-It is worth calling attention to some other work on computing the normalized cut over neighborhood graphs.
-In this context, continuous analogues to (for instance) normalized cut have been defined, over the data-manifold rather than the graph, and convergence finite sample graph-theoretic functionals to their continuous counterparts has been shown
-\cite{garciatrillos16, arias-castro12, maier11}.
-However, in addition to the graph-minimization problem being computationally infeasible, these continuous analogues are not always easily interpretable -- and their corresponding minimizers not always easily identifiable -- for the particular density function under consideration.
-Of course, relating these partitions to the arguably more simply defined high density clusters can be also challenging in general.
-Intuitively, however, under the right conditions such high-density clusters should have more edges within themselves than to the remainder of the graph.
-We formalize this intuition next.
+% It is worth calling attention to some other work on computing the normalized
+% cut over neighborhood graphs. In this context, continuous analogues to (for
+% instance) normalized cut have been defined, over the data-manifold rather than
+% the graph, and convergence finite sample graph-theoretic functionals to their
+% continuous counterparts has been shown 
+% \cite{garciatrillos16, arias-castro12, maier11}. 
+% However, in addition to the graph-minimization problem being computationally
+% infeasible, these continuous analogues are not always easily interpretable --
+% and their corresponding minimizers not always easily identifiable -- for the
+% particular density function under consideration. Of course, relating these
+% partitions to the arguably more simply defined high density clusters can be
+% also challenging in general. Intuitively, however, under the right conditions
+% such high-density clusters should have more edges within themselves than to
+% the remainder of the graph. We formalize this intuition next.
 
-%It is worth pointing out that in this context, some theory has been developed regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and others) relate to properties of the underlying distribution $f$ as well as the kernel function $k$.
-Such analyses typically proceed by defining a continuous analogue to the measure of cluster quality under consideration.
-Then, under appropriate specification of $k$ and a proper schedule of $(r_n)$, convergence of clusters output by spectral (and other) algorithms to the corresponding minima of these continuous analogues has been shown \cite{vonluxburg2008, garciatrillos18}.
+%% RJT: I didn't know where to put this.  It was out of place, and now I'm not
+%% sure where it goes ... should it go in related work?
 
-\subsection{Summary of results}
+%It is worth pointing out that in this context, some theory has been developed
+%regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and
+%others) relate to properties of the underlying distribution $f$ as well as the
+%kernel function $k$. Such analyses typically proceed by defining a continuous
+%analogue to the measure of cluster quality under consideration. Then, under
+%appropriate specification of $k$ and a proper schedule of $(r_n)$, convergence
+%of clusters output by spectral (and other) algorithms to the corresponding
+%minima of these continuous analogues has been shown \cite{vonluxburg2008,
+%garciatrillos18}.
 
-Hereafter, we consider the uniform kernel function for a fixed $r > 0$,
-\begin{equation}
-k(x,x') = \1(\norm{x - x'} \leq r)
-\end{equation}
-and the associated neighborhood graph
-\begin{equation}
-\label{eqn: neighborhood_graph}
-G_{n,r} = (\Xbf, E_{n,r}), \text{  $(x_i,x_j) \in E_{n,r}$ if $k(x_i,x_j) = 1$}
-\end{equation}
-For a given high density cluster $\Cset \subseteq \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}.
-We now introduce a notion of consistency for the task of density cluster estimation:
+%%% RJT: This was already commented out before
+
+Let $\Cbb_f(\lambda)$ denote the connected components of the density upper level
+set $\{x : f(x) > \lambda\}$.  For a given density cluster $\Cset \in
+\Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
+  density cluster}. Below we define a notion of consistency in density cluster
+estimation.
 
@@
 \label{def: consistent_density_cluster_estimation}
-	For an estimator $\widehat{\Cset}_n \subset \Xbf$, and any $\Cset, \Cset' \in \Cbb_f(\lambda),$ we say $\widehat{\Cset}_n$ is a consistent estimator of $\Cset$ if the following statement holds: as the sample size $n \to \infty$, each of the following
+For an estimator \smash{$\widehat{\Cset} \subseteq \Xbf$} and cluster 
+$\Cset \in \Cbb_f(\lambda)$, we say \smash{$\widehat{\Cset}$} is a consistent
+estimator of $\Cset$ if for all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset \not=
+\Cset'$ the following holds as $n \to \infty$: 
 \begin{equation}
 \label{eqn: consistent_density_cluster_recovery}
-	\Cset[\Xbf] \subseteq \widehat{\Cset}_n, ~\mathrm{ and }~ \widehat{\Cset}_n \cap \Cset'[\Xbf] = \emptyset
+\Cset[\Xbf] \subseteq \widehat{\Cset} \quad \text{and} \quad
+\widehat{\Cset} \cap \Cset'[\Xbf] = \emptyset,
 \end{equation}
-	occur with probability tending to $1$.
-
+with probability tending to 1.
 \end{definition}
 
-Our results can now be summarized by the following points:
+A summary of our main results (and outline for the rest of this paper) is as
+follows.
 
 \begin{enumerate}
-	\item 
-	Under a natural set of geometric conditions
-	\footnote{We formally introduce the geometric conditions in Section \ref{sec: background}.
-They preclude clusters which are too thin and long, or those for which the gap in density between the high density area and the outside is not sufficiently large},
-	the normalized cut of an empirical density cluster $C[\Xbf]$ can be bounded. Theorem \ref{thm: conductance_upper_bound} provides an upper bound.
+\item In Section \ref{sec: PhiPsi}, we derive in Theorem \ref{thm:
+    conductance_upper_bound} an upper bound on the normalized cut of an
+  empirical density cluster $\Cset[\Xbf]$, under a natural set of    
+  geometric conditions (precluding clusters which are too thin and long).
 
-	\item Under largely the same set of geometric conditions to Theorem \ref{thm: conductance_upper_bound}, Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} provides a lower bound on the inverse mixing time of a random walk over $C[\Xbf]$.
-Theorem \ref{thm: inverse_mixing_time_lower_bound} gives a tighter lower bound, but requires the additional (restrictive) assumption of convexity.
+\item Under largely the same set of geometric conditions, we derive in Theorem
+  \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
+  inverse mixing time of a random walk over $\Cset[\Xbf]$.  We also provide in
+  Theorem \ref{thm: inverse_mixing_time_lower_bound} a tighter lower bound, but
+  under more restrictive assumptions (convexity of $\Cset[\Xbf]$).
 
-	\item 
-	In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show these bounds on the graph connectivity criteria have algorithmic consequences for personalized PageRank.
-we show that a careful analysis of the form typical to local clustering algorithms yields Theorem \ref{thm: consistent_recovery_of_density_clusters}, which states that Algorithm \ref{alg: ppr}, properly initialized, performs consistent density cluster estimation in the sense of (\ref{eqn: consistent_density_cluster_recovery}).
+\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
+  Theorem \ref{thm: consistent_recovery_of_density_clusters} that these bounds
+  in bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+    inverse_mixing_time_lower_bound_nonconvex},
+  on the cluster quality criteria, have algorithmic consequences for PPR:
+  properly initialized, Algorithm \ref{alg: ppr} performs consistent density
+  cluster estimation in the sense of \eqref{eqn:
+    consistent_density_cluster_recovery}.
 
-	\item Corollary \ref{cor: ppr_cluster} follows as an immediate consequence of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, along with the previous work of \cite{zhu2013}.
-It gives an upper bound on the normalized cut of the set $\widehat{C}$ output by Algorithm \ref{alg: ppr}, as well as upper bounding the symmetric set difference between $\widehat{C}$ and $\Cset[\Xbf]$.
+\item We show in Corollary \ref{cor: ppr_cluster} that Theorems \ref{thm:
+    conductance_upper_bound} and \ref{thm:
+    inverse_mixing_time_lower_bound_nonconvex}, along with the results in 
+  \citet{zhu2013}, lead to alternative, graph-theoretic guarantees on cluster 
+  quality: an upper bound on the normalized cut of the estimated cluster 
+  \smash{$\widehat{C}$}, and an upper bound on volume of the symmetric set
+  difference between \smash{$\widehat{C}$} and $\Cset[\Xbf]$.
+
+\item In Section \ref{section: examples}, we discuss the implications of our
+  results for some example density functions of interest, and empirically
+  demonstrate that violations of the gometric conditions we require manifestly
+  impact density cluster recovery. 
 \end{enumerate}
 
-\paragraph{Organization.}
-In Section \ref{section: examples}, we provide some example density functions, to clarify the relevance of our results, and empirically demonstrate that violations of the geometric conditions we set out in Section \ref{sec: background} manifestly impact density cluster recovery (i.e.
-the conditions are not superfluous), before concluding in \ref{sec: discussion}.
-First, however, we summarize some related work.
+On the topic of conditions, it is worth mentioning that, as density clusters
+are inherently local, focusing on the PPR algorithm actually eases our analysis
+and allows us to require fewer global regularity conditions relative to those
+needed for more classical global spectral algorithms.
 
 \subsection{Related Work}
-In addition to the background given above, a few related lines of work are worth highlighting.
 
-Global spectral clustering 
-methods were first developed in the context of graph partitioning \cite{fiedler1973,donath1973} 
-and their performance is well-understood in this context (see, for instance, \cite{tolliver2006,luxburg2007}).
-In a similar vein, several recent works \citep{mcsherry2001,lei2015,rohe2011,abbe2018,kamalika2012,balakrishnan2011} have studied the efficacy of spectral methods
-in successfully recovering the community structure in various variants of the
-stochastic block model.
+In addition to the background given above, a few related lines of work are worth
+highlighting. Global spectral clustering methods were first developed in the
+context of graph partitioning \citep{fiedler1973,donath1973} and their
+performance is well-understood in this context (see, e.g.,
+\citealt{tolliver2006,luxburg2007}).  In a similar vein, several recent works
+\citep{mcsherry2001,rohe2011,kamalika2012,balakrishnan2011,lei2015,abbe2018} 
+have studied the efficacy of spectral methods in successfully recovering the
+community structure in the stochastic block model and variants.
 
-Building on the work of \citet{koltchinskii2000} the works \citep{vonluxburg2008,hein2005} for instance, have studied the limiting behaviour of spectral clustering algorithms.
-These works show that when samples are obtained from a distribution, following
-appropriate graph construction, in certain cases the spectrum of the Laplacian 
-converges to that of the Laplace-Beltrami operator on the data-manifold.
-However, relating the partition obtained using the Laplace-Beltrami operator, to 
-the 
-more intuitively defined high-density clusters, can be challenging in general.
+\citet{vonluxburg2008,hein2005}, building on earlier work of
+\citet{koltchinskii2000}, studied the limiting behaviour of spectral clustering
+algorithms. These authors show that when samples are obtained from a
+distribution, and we appropriately construct a geometric graph, the spectrum of
+the Laplacian converges to that of the Laplace-Beltrami operator on the
+data-manifold. However, relating the partition obtained using the
+Laplace-Beltrami operator to the more intuitively defined high-density
+clusters can be challenging in general.
 
-Perhaps most similar to our results are \citep{vempala2004,shi2009,schiebinger2015}, 
-which study the consistency of spectral algorithms in recovering the latent labels in certain 
-parametric and non-parametric mixture models.
-These results focus on global rather than local algorithms, and as such impose global rather than local conditions on the nature of the density.
-Moreover, they do not in general ensure recovery of density clusters which is a focus of our work.
+Perhaps most similar to our results are the works
+\citet{vempala2004,shi2009,schiebinger2015}, who study the consistency of
+spectral algorithms in recovering the latent labels in certain parametric and
+nonparametric mixture models. These results focus on global rather than local
+algorithms, and as such impose global rather than local conditions on the nature
+of the density. Moreover, they do not in general ensure recovery of density
+clusters, which is the focus in our work.
 
-\section{Graph Quality Criteria on Well-Conditioned Density Clusters.}
-\label{sec: background}
+\section{Cluster Quality Criteria on Empirical Density Clusters} 
+\label{sec: PhiPsi}
 
@@
 Let $B(x,r) = \set{y \in \Rd: \norm{y - x} \leq r}$ be a closed ball of radius $r$ around the point $x$.
-Given a set $\Aset \subset \Rd$, and a number $\sigma > 0$, define the $\sigma$-expansion of $\Aset$ to be $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
+Given a set $\Aset \subseteq \Rd$, and a number $\sigma > 0$, define the $\sigma$-expansion of $\Aset$ to be $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
 We are now ready to give the assumptions, which we state with respect to a density cluster $\Cset \in \Cbb_f(\lambda)$ for some $\lambda > 0$, and expansion parameter $\sigma > 0$:
@@
 	\end{equation*}
-	where $\dist(\Aset,\Aset') = \min_{x \in \Aset} \dist(x,\Aset')$ for $\Aset' \subset \Rd$.
+	where $\dist(\Aset,\Aset') = \min_{x \in \Aset} \dist(x,\Aset')$ for $\Aset' \subseteq \Rd$.
 
@@
 	\end{equation*}
-	where $\dist(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subset \Rd$.
+	where $\dist(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subseteq \Rd$.
 \end{enumerate}
@@
 	The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other proofs, can be found in the supplementary document.
-The key point is to note that for any $x \in \Cset$, the simple, (possibly loose) $B(x,\sigma) \subset \Csig$ translates to the upper bound $\nu(\Cset_{\sigma + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$.
+The key point is to note that for any $x \in \Cset$, the simple, (possibly loose) $B(x,\sigma) \subseteq \Csig$ translates to the upper bound $\nu(\Cset_{\sigma + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$.
 We leverage \ref{asmp: low_noise_density} to find a corresponding bound on the weighted volume, before applying standard concentration inequalities to convert from population to sample based results.
@@
 	\begin{equation*}
-	\widetilde{\Phi} = \min_{S \subset \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]])
+	\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]])
 	\end{equation*}
@@
 	The factor of $\frac{1}{r^{2d}}$ present in the bound of \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex} is suboptimal.
-This exponential dependence on $d$ stems from a loose bound on the aforementioned conductance in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.In particular, we assert only that any set $S \subset \Csig[X]$ must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding $\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of order $r^d$.
+This exponential dependence on $d$ stems from a loose bound on the aforementioned conductance in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.In particular, we assert only that any set $S \subseteq \Csig[X]$ must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding $\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of order $r^d$.
 The presence of $r^{2d}$ comes from upper bounding the mixing time by about $1/\widetilde{\Phi}^2$, this latter bound being a variant of classic results on rapid mixing \cite{jerrum89}.
@@
 \begin{equation*}
-\widetilde{\Phi}_n(t) = \min_{\substack{S \subset \Csig[\Xbf] \\ \pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]])
+\widetilde{\Phi}_n(t) = \min_{\substack{S \subseteq \Csig[\Xbf] \\ \pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]])
 \end{equation*}
@@
 	\end{equation}
-	and Algorithm \ref{alg: ppr} is well-initialized, the output set $\widehat{C} \subset \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	and Algorithm \ref{alg: ppr} is well-initialized, the output set $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 \end{theorem}
@@
 	\label{lem: ppr_cluster}
-	There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
+	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
 Letting
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).
-Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the following guarantees hold for output set $\widehat{C} \subset \Xbf$:
+Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the following guarantees hold for output set $\widehat{C} \subseteq \Xbf$:
 	\begin{align*}
@@
 	\begin{equation*}
-	\Phi^{\star}(G_{n,r}) := \min_{C \subset \Xbf} \Phi_{n,r}(C)
+	\Phi^{\star}(G_{n,r}) := \min_{C \subseteq \Xbf} \Phi_{n,r}(C)
 	\end{equation*}
-	and the conductance cut is $C^{\star} \subset \Xbf$ which achieves the minimum.
+	and the conductance cut is $C^{\star} \subseteq \Xbf$ which achieves the minimum.
 

### 2019-01-23 icml/icml_local_density_clustering.tex
Edits through Sect 2

@@
 which extract clusters using locally-biased random walks around a user-specified
-seed node.  Several local methods, such as the personalized PageRank (PPR)
-algorithm, have been shown to have worst-case guarantees for certain graph-based
-measures of cluster quality.  In contrast to existing works, we analyze PPR in a
-traditional statistical learning setup, where we obtain samples from an unknown
+seed node.  Several authors have shown that local methods, such as personalized
+PageRank (PPR), have worst-case guarantees for certain graph-based measures of
+cluster quality.  In contrast to existing works, we analyze PPR in a traditional
+statistical learning setup, where we obtain samples from an unknown
 distribution, and aim to identify connected regions of high-density (density
@@
 \citet{haveliwala2003}, and further developed by
-\citet{spielman2011,spielman2014,anderson2006,mahoney2012,zhu2013}, among 
-others.
+\citet{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
+among others.
 
 Local spectral clustering techinques have been practically very successful
-\citep{leskovec2010,mahoney2012,REFS}, which
-has led many authors to develop theory that explains their success 
-\citep{zhu2013,REFS},
-from the perspective of worst-case guarantees on traditional graph-theoretic
-notions of cluster quality (like conductance).  In this paper, we adopt a more
-traditional statistical viewpoint, and examine what the output of a local
-clustering algorithm on $\Xbf$ reveals about the unknown density $f$.  
-In particular, we examine the ability of the PPR algorithm to recover
-\emph{density clusters} of $f$, which are defined as the connected components of
-the upper level set $\{x : f(x) \geq \lambda\}$ for some threshold $\lambda >
-0$ (a central object of central interest in the classical statistical literature
-on clustering, dating back to \citealt{hartigan1981}).
+\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
+many authors to develop supporting theory
+\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
+guarantees on traditional graph-theoretic notions of cluster quality (like
+conductance).  In this paper, we adopt a more traditional statistical viewpoint,
+and examine what the output of a local clustering algorithm on $\Xbf$ reveals
+about the unknown density $f$.  In particular, we examine the ability of the PPR
+algorithm to recover \emph{density clusters} of $f$, which are defined as the
+connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
+for some threshold $\lambda > 0$ (a central object of central interest in the
+classical statistical literature on clustering, dating back to
+\citealt{hartigan1981}).
 
@@
 less than $\Psi$, we call it as a \emph{$(\Phi,\Psi)$-cluster}. Both
-local \cite{zhu2013} and global \cite{kannan04} spectral algorithms have been
+local \citep{zhu2013} and global \citep{kannan04} spectral algorithms have been
 shown to output clusters (or partitions) which approximate the optimal $(\Phi,
 \Psi)$-cluster (or partition) for a given graph $G$.\footnote{In the case of
-  \cite{kannan04}, the internal connectivity parameter $\phi$ is actually the
+  \citet{kannan04}, the internal connectivity parameter $\phi$ is actually the
   conductance, i.e., the minimum normalized cut within the subgraph $G[S]$. See
@@
 (\frac{3}{10},\frac{1}{2})$},\footnote{The choice of a specific range such as 
-\smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of \pprspace
+\smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of PPR
 algorithms, see, e.g., \citet{zhu2013}.}
@@
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-  \STATE Return $\widehat{C} = S_{\beta^*}$, where 
+  \STATE Return \smash{$\widehat{C} = S_{\beta^*}$}, where 
   $$
@@
 
-%%% RJT: This was already commented out before
+%% RJT: This was already commented out before
 
 Let $\Cbb_f(\lambda)$ denote the connected components of the density upper level
-set $\{x : f(x) > \lambda\}$.  For a given density cluster $\Cset \in
+set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster $\Cset \in
 \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
@@
 \item In Section \ref{sec: PhiPsi}, we derive in Theorem \ref{thm:
-    conductance_upper_bound} an upper bound on the normalized cut of an
-  empirical density cluster $\Cset[\Xbf]$, under a natural set of    
-  geometric conditions (precluding clusters which are too thin and long).
+    conductance_upper_bound} an upper bound on the normalized cut of a
+  (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
+  conditions (precluding clusters that are too thin and long).
 
@@
   \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
-  inverse mixing time of a random walk over $\Cset[\Xbf]$.  We also provide in
+  inverse mixing time of a random walk over $\Csig[\Xbf]$.  We also provide in 
   Theorem \ref{thm: inverse_mixing_time_lower_bound} a tighter lower bound, but
-  under more restrictive assumptions (convexity of $\Cset[\Xbf]$).
+  under more restrictive assumptions (convexity of $\Csig$).
 
@@
 
-\section{Cluster Quality Criteria on Empirical Density Clusters} 
+\section{Cluster Quality Critera Bounds for Density Clusters}  
 \label{sec: PhiPsi}
 
-In order to provide meaningful bounds on the normalized cut and inverse mixing time of an empirical density cluster $\Cset[\Xbf]$, we must introduce some assumptions on the density $f$.
+\subsection{Assumptions}
 
-Let $B(x,r) = \set{y \in \Rd: \norm{y - x} \leq r}$ be a closed ball of radius $r$ around the point $x$.
-Given a set $\Aset \subseteq \Rd$, and a number $\sigma > 0$, define the $\sigma$-expansion of $\Aset$ to be $\Asig = \Aset + B(0,\sigma) = \set{y \in \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma}$.
-We are now ready to give the assumptions, which we state with respect to a density cluster $\Cset \in \Cbb_f(\lambda)$ for some $\lambda > 0$, and expansion parameter $\sigma > 0$:
+In order to provide meaningful bounds on the normalized cut and inverse mixing
+time of an empirical density cluster, we must introduce conditions on the
+density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the ball of
+radius $r$ centered at $x$.  Given a set $\Aset \subseteq \Rd$ and $\sigma > 0$,
+define $\Asig = \Aset + B(0,\sigma) = \{y \in \Rd: \inf_{x \in \Aset} \norm{y - 
+    x} \leq \sigma\}$, which we call the $\sigma$-expansion of $\Aset$.
+
+We are now ready to give the conditions, stated with respect to a density
+cluster $\Cset \in \Cbb_f(\lambda)$, for some $\lambda > 0$, and an expansion 
+parameter $\sigma > 0$.
+
 \begin{enumerate}[label=(A\arabic*)]
 \item
+\label{asmp: bounded_density}
+\emph{Bounded density within cluster:} There are $0 < \lambda_{\sigma} <
+\Lambda_{\sigma} < \infty$ such that
+$$
+\lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq
+\Lambda_{\sigma}.
+$$
+% and 
+% \begin{equation*}
+% \frac{\diam \Asig}{\sigma} \leq \mu
+% \end{equation*}
+% where $\diam \Asig = \sup \set{d(x,y) : x,y \in \Asig}$
+
+\item 
+\label{asmp: low_noise_density}
+\emph{Low noise density:} There exist $\gamma, c_1 > 0$ such that for all $x
+\in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
+$$
+  \inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \dist(x, \Csig)^{\gamma},
+$$
+where \smash{$\dist(x,\Aset) = \inf_{x_0 \in \Aset} \norm{x - x_0}$}.
+% RJT: should we change this to c_0?  c_1 seems to be used below and throughout
+% for other constants, and c_0 is not used
+
+\item
 \label{asmp: cluster_separation}
-	\textit{Cluster separation:}
+\emph{Cluster separation:}
 For all $\Cset' \in \Cbb_f(\lambda)$,
-	\begin{equation*}
+$$
 \dist(\Csig,\Csig') > \sigma,
-	\end{equation*}
-	where $\dist(\Aset,\Aset') = \min_{x \in \Aset} \dist(x,\Aset')$ for $\Aset' \subseteq \Rd$.
+$$
+where \smash{$\dist(\Aset,\Aset') = \inf_{x \in \Aset} \dist(x,\Aset')$}.
 
@@
 \label{asmp: cluster_diameter}
-	\textit{Cluster diameter:}
-	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
-	\begin{equation*}
+\emph{Cluster diameter:}
+There exists $D < \infty$ such that for all $x, x' \in \Csig$,
+$$
 \norm{x - x'} \leq D.
-	\end{equation*}
-
-	\item
-	\label{asmp: bounded_density}
-	\textit{Bounded density within cluster:} There exist numbers $0 < \lambda_{\sigma} <  \Lambda_{\sigma} < \infty$ such that:
-	\begin{equation}
-	\label{eqn: bounded_density}
-	\lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma} 
-	\end{equation} 
-	%and 
-	%\begin{equation*}
-	%\frac{\diam \Asig}{\sigma} \leq \mu
-	%\end{equation*}
-	%where $\diam \Asig = \sup \set{d(x,y) : x,y \in \Asig}$
-
-	\item 
-	\label{asmp: low_noise_density}
-	\textit{Low noise density:} For some $\gamma > 0 $, there exists a constant $c_1 > 0$ such that for all $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,
-	\begin{equation*}
-	\inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \dist(x, \Csig)^{\gamma},
-	\end{equation*}
-	where $\dist(x,\Aset) = \min_{x_0 \in \Aset} \norm{x - x_0}$ for $\Aset \subseteq \Rd$.
+$$
 \end{enumerate}
 
-We note that $\sigma$ plays several roles here, precluding arbitrarily narrow clusters and long clusters in \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
+Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
+clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp:
+  cluster_diameter}, flat densities around the level set in \ref{asmp: 
+  low_noise_density}, and poorly separated clusters in \ref{asmp:
+  cluster_separation}.
 
-Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} are used to upper bound $\Phi(\Cset[\Xbf]; G_{n,r})$, whereas \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} are necessary to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$.
-We note that the lower bound on minimum density in (\ref{eqn: bounded_density}) and \ref{asmp: cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of \cite{chaudhuri2010}, a standard density clustering assumption, while \ref{asmp: low_noise_density} is seen in, for instance, \cite{singh2009}, (as well as many other works on density clustering and level set estimation.) It is worth highlighting that these assumptions are all local in nature, a benefit of studying a local algorithm such as PPR.
+Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
+\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
+G_{n,r})$, whereas \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
+are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
+lower bound on minimum density in \ref{asmp: bounded_density} and \ref{asmp:  
+cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of
+\citet{chaudhuri2010}, a standard density clustering assumption, while
+\ref{asmp: low_noise_density} is seen in, e.g., \citet{singh2009} (as well as
+many other works on density clustering and level set estimation.) It is worth
+highlighting that these assumptions are all local in nature, a benefit of
+studying a local algorithm such as PPR.
 
-We are ready to provide bounds on the graph quality bicriteria.
-For notational simplicity, hereafter for $S \subseteq \Xbf$ we will refer to $\Phi(S; G_{n,r})$ as $\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$.
-We will also use $\nu(\cdot)$ to denote the uniform measure over $\Rd$, and $\nu_d = \nu\bigl(B(0,d)\bigr)$ as the measure of the unit ball.
+In the next several subsections, we will derive bounds on the cluster quality
+criteria evaluated on (thickened) density clusters. For notational simplicity,
+hereafter for $S \subseteq V$, we will denote $\Phi(S; G_{n,r})$ by
+$\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$. We
+will also use $\nu$ for Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for 
+the measure of the unit ball $B=B(0,1)$. 
+% RJT: you had B(0,d) before ... just check this should have been B(0,1)
 
-We begin with an upper bound on the normalized cut in Theorem \ref{thm: conductance_upper_bound}.
-We will require Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} to hold; however, the upper bound on density in (\ref{eqn: bounded_density}) will not be needed and so we omit the parameter $\Lambda_{\sigma}$ from the statement of the theorem.
+\subsection{Upper Bound on Normalized Cut}
+
+We begin by upper bounding the normalized cut of $\Cset_\sigma[\Xbf]$.  (In the
+theorem, the upper bound on the density in Assumption \ref{asmp: 
+  bounded_density} will not actually be needed, so we omit the parameter
+$\Lambda_\sigma>0$ from the theorem statement.)
+
 \begin{theorem}
 \label{thm: conductance_upper_bound}
-	For some $\lambda > 0$, let $\Cset \in \mathbb{C}_f(\lambda)$ satisfy Assumptions \ref{asmp: cluster_separation}, \ref{asmp: bounded_density} and \ref{asmp: low_noise_density} for some $\sigma, \lambda_{\sigma}, c_1, \gamma > 0$ .
-Then, for any $r < \sigma/4d$ and $\delta \in (0,1]$, the following statements hold with probability at least $1 - \delta$:  Fix $\epsilon > 0$.
-Then, for
+Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
+Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
+\ref{asmp: cluster_separation}, for some 
+$\sigma, \lambda_{\sigma}, c_1, \gamma > 0$. Then for any $0 < r <
+\sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and
 \begin{equation}
 \label{eqn: conductance_sample_complexity}
-		n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}{ \lambda_{\sigma}^2 \nu(\Csig) \nu_d r^d}\right)^2 
+n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}
+  { \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
 \end{equation}
@@
   \label{eqn: conductance_additive_error_bound}
-		\frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq 4 c_{\sigma} d \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon
+  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq 4 c_{\sigma} d
+  \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
+    \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
 \end{equation}
-	where $c_{\sigma} = 1 / \sigma$. 
+with probability at least $1-\delta$, where $c_{\sigma} = 1 / \sigma$. 
 \end{theorem}
@@
 \begin{remark}
-	The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other proofs, can be found in the supplementary document.
-The key point is to note that for any $x \in \Cset$, the simple, (possibly loose) $B(x,\sigma) \subseteq \Csig$ translates to the upper bound $\nu(\Cset_{\sigma + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$.
-We leverage \ref{asmp: low_noise_density} to find a corresponding bound on the weighted volume, before applying standard concentration inequalities to convert from population to sample based results.
-\end{remark}
-\begin{remark}
-	(\ref{eqn: conductance_additive_error_bound}) is almost tight. Specifically, choosing
-	\begin{align*}
-	\Asig & = B(0,\sigma), \\
-	 f(x) & = 
-	 \begin{cases}
-	 \lambda \text{ for $x \in \Asig$}, \\
-	 \lambda - \dist(x,\Asig)^{\gamma} \text{ for $0 < \dist(x,\Asig) < r$}
-	 \end{cases}
-	\end{align*}
-	we have that for $n$ within constant order of the lower bound in (\ref{eqn: conductance_sample_complexity}), with probability at least $1 - \delta$
-	\begin{equation*}
-	\frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda - \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon
-	\end{equation*}
-	for some constant $c$. (Note that a factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated in this lower bound.)
+The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other
+proofs in this paper, can be found in the supplementary document. The key 
+idea is that for any $x \in \Cset$, the simple (possibly loose) fact
+$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Cset_{\sigma
+  + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
+  low_noise_density} to find a corresponding bound on the weighted volume,
+then apply standard concentration inequalities to convert from population-
+to sample-based results.  
 \end{remark}
 
-We now provide a lower bound on $\Psi_{n,r}(\Cset[\Xbf])$.
+\begin{remark}
+The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
+tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
+$$
+f(x) = \lambda - \dist(x,\Asig)^{\gamma},
+$$
+% RJT: is this correct (is this what you meant)?  Original formula is below
+% $$
+% f(x)  = \begin{cases}
+%   \lambda &\text{for $x \in \Asig$}, \\
+%   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
+% \end{cases}
+% $$
+we have that for $n$ on the order of the lower bound in \eqref{eqn: 
+  conductance_sample_complexity}, 
+\begin{equation*}
+  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
+    \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
+\end{equation*}
+with probability at least $1 - \delta$, for some constant $c$. (Note that the
+factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
+\end{remark}
+
+\subsection{Lower Bound on Inverse Mixing Time}
+
+We lower bound the inverse mixing time of $\Csig[\Xbf]$.
 
@@
 \label{thm: inverse_mixing_time_lower_bound_nonconvex}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$.
-Then, for any $r < \sigma/4d$, the following statement holds with probability at least $1 - \delta$: Fix $0 < \epsilon > 1$.
-Then, for $n$ satisfying:
-	\begin{align*}
-	\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d \lambda_{\sigma}}} \leq \epsilon
-	\end{align*}
-	we have
-	\begin{align}
+Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
+Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
+for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
+r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
+$$
+\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
+    \lambda_{\sigma}}} \leq \epsilon, 
+$$
+where \smash{$\mu = \log(\frac{2D}{r})$}, we have
+\begin{multline}
 \label{eqn: inverse_mixing_time_lower_bound_nonconvex}
-	1 / \Psi_{n,r}(\Csig[\Xbf]) & \leq \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
-	& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
-	\end{align}
-	where $\mu = \log(\frac{2D}{r})$; $c_1$, $c_2$, and $c_3$ are constants which depend only on dimension; and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
+\Psi_{n,r}(\Csig[\Xbf]) \geq \left(d \log \mu + c_{\lambda} \right)^{-1} \cdot \\
+\left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
+    \log \mu + c_{\lambda}\right)\right)^{-1},
+\end{multline}
+% RJT: confused ... is this correct?
+with probability at least $1 - \delta$, where $c_1,c_2,c_3>0$ are constants
+depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/
+\lambda_{\sigma}^2)$.   
 \end{theorem}
+% RJT: saying that c_1,c_2,c_3 depend on the dimension is a little odd/weak.
+% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
+% will swamp the linear factor of ....
 
 \begin{remark}
-	The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[X]]$,
-	\begin{equation*}
-	\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]])
-	\end{equation*}
-
-	The factor of $\frac{1}{r^{2d}}$ present in the bound of \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex} is suboptimal.
-This exponential dependence on $d$ stems from a loose bound on the aforementioned conductance in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.In particular, we assert only that any set $S \subseteq \Csig[X]$ must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding $\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of order $r^d$.
-The presence of $r^{2d}$ comes from upper bounding the mixing time by about $1/\widetilde{\Phi}^2$, this latter bound being a variant of classic results on rapid mixing \cite{jerrum89}.
+The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies
+on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[X]]$, 
+$$
+\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]]).
+$$
+The factor $1/r^{2d}$ in the lower bound in \eqref{eqn:
+  inverse_mixing_time_lower_bound_nonconvex} is suboptimal. This exponential
+dependence on $d$ stems from a loose bound on the aforementioned
+conductance. In particular, we assert only that any set $S \subseteq \Csig[X]$
+must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding
+$\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of
+order $r^d$. The presence of $r^{2d}$ comes from upper bounding the mixing time
+by about \smash{$1/\widetilde{\Phi}^2$}, this being a variant of classic results
+on rapid mixing \citep{jerrum89}.  
 \end{remark}
 
-It is possible to sharpen the dependency on $d$, but at the cost of an additional assumption:
+\subsection{Tigher Lower Bound Under Convexity}
+
+It is possible to sharpen the dependency on $d$ in 
+\label{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an 
+additional assumption: 
 \begin{enumerate}[label=(A\arabic*)]
@@
 \end{enumerate}
-Additionally, the resulting bound holds only asymptotically.
+% RJT: do we need C to satisfy this, or Csig?  Not sure I know why the former
+% matters ...
+
+With \ref{asmp: convex} in place, we now give a tighter lower bound on the
+inverse mixing time of $C_\sigma[\Xbf]$ (albeit one that holds only
+asymptotically).
 
@@
 \label{thm: inverse_mixing_time_lower_bound}
-	Fix $\lambda > 0$, and let the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} hold with respect to $\Cset \in \Cbb_f(\lambda)$.
-Additionally, let $\Cset$ satisfy \ref{asmp: convex}.
-Then, for any $r < \sigma/4d$, the following statement holds: with probability one
+Assume the conditions of Theorem \ref{thm:
+  inverse_mixing_time_lower_bound_nonconvex}, and additionally, let $\Cset$
+satisfy \ref{asmp: convex}. Then, 
+for any $r < \sigma/4d$, the following statement holds with probability 1: 
 \begin{align}
 \label{eqn: inverse_mixing_time_lower_bound}
-	\liminf_{n \to \infty} & \frac{1}{\Psi_{n,r}(\Csig[\Xbf])} \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
-	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
-	& c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
+  \liminf_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ 
+&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
+  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
+&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
+  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
+&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
 \end{align}
-	where $\mu = \log(\frac{2D}{r})$, $c_1,c_2$ and $c_3$ are all global constants, $c_d$ is constant in $r$ but may depend on other quantities,  and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.
-Additionally, $\lim_{r \to 0} o_r(1) = 0$.
+% RJT: confused ... is this correct?
+where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
+constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
+$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
+% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
 \end{theorem}
+% RJT: this was a lower bound on 1/\Psi and I changed it to \Psi ... just
+% checking
 
-We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound} to those of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part by working with a generalization of the conductance, the \emph{conductance function}
+\begin{remark}
+The only potentially exponential dependence on dimension comes from the
+factor of $c_d$. However, for sufficiently small values of $r$ this will
+be dominated by the preceding factors, due to the presence of the
+$o_r(1)$ term. 
+\end{remark}
+% RJT: Don't get this comment.  You have o_r(1) / r^2, so this might still blow
+% up as r -> 0, right?
+
+\begin{remark}
+We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
+to those in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part
+by working with a generalization of the conductance, the \emph{conductance
+  function},
 \begin{equation*}
-\widetilde{\Phi}_n(t) = \min_{\substack{S \subseteq \Csig[\Xbf] \\ \pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]])
+\widetilde{\Phi}_n(t) = 
+\min_{\substack{S \subseteq \Csig[\Xbf] \\ \tilde\pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]]) 
 \end{equation*}
-where $\pi(S)$ is the stationary distribution over $G_{n,r}[\Csig[\Xbf]]$. 
-The utility of the conductance function comes from the known upper bound of mixing time by 
+where \smash{$\tilde\pi$} is the stationary distribution over
+$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
+known upper bound of mixing time by  
 \begin{equation}
 \label{eqn: average_conductance}
-\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt
+\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
 \end{equation}
- which results in a tighter bound than merely using the conductance when $\widetilde{\Phi}_n(t)$ is large for small values of $t$.
+which results in a tighter bound than merely using the conductance when
+\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.
 
-\begin{remark}
-	The only potentially exponential dependence on dimension comes from the factor of $c_d$.
-However, for sufficiently small values of $r$ this will be dominated by the preceding factors, due to the presence of the $o_r(1)$ term.
+Our proof relies on a novel (to the best of our knowledge) uniform lower bound
+on this conductance function over $G_{n,r}$ in terms of a population-level
+analogue, which we term \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
+\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
+a bound on mixing time (with respect to total variation distance) of order $d
+D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
+  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
+(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
+pointwise distance (which is known to be a stricter metric). 
 \end{remark}
@@
 \begin{remark}
- The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} relies on a to the best of our knowledge novel uniform lower bound on this conductance function over $G_{n,r}$ in terms of a population-level analogue, which we term $\widetilde{\Phi}_{\Pbb,r}$.
-Plugging $\widetilde{\Phi}_{\Pbb,r}$ into \eqref{eqn: average_conductance} yields a bound on mixing time (with respect to total variation distance) of order $d D^2/r^2 + d^2\log(D/r)$ over convex sets.
-By contrast, \eqref{eqn: inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ (ignoring the $o_r(1)$ term) but handles mixing time with respect to relative pointwise distance (which is known to be a stricter metric.)
+  The convexity requirement is necessary only to lower bound the
+  \smash{$\widetilde{\Phi}_{\Pbb,r}$}; any bound on $\widetilde{\Phi}_{\Pbb,r}$
+  which   does not require convexity could immediately be plugged into the
+  machinery of   the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
+  to achieve a corresponding result. Recent work \citep{abbasi17} has developed
+  such population-level bounds on the conductance function, however the Markov
+  chain dealt with there is somewhat different than the one we consider.  
 \end{remark}
 
-\begin{remark}
-	The convexity requirement is necessary only to lower bound the $\widetilde{\Phi}_{\Pbb,r}$; any bound on $\widetilde{\Phi}_{\Pbb,r}$ which does not require convexity could immediately be plugged into the machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound} to achieve a corresponding result.
-Recent work \cite{abbasi17} has developed such population-level bounds on the conductance function, however the Markov chain dealt with there is somewhat different than the one we consider.
-\end{remark}
-
-\section{Consistent cluster estimation with PPR.}
+\section{Consistent Cluster Estimation}
 \label{sec: consistent_cluster_estimation_with_ppr}
 
-For \pprspace to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.
+For PPR to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.
 
@@
 
-In \cite{zhu2013}, building on the work of \cite{anderson2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
+In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
 Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut and symmetric set difference of $\widehat{C}$.

### 2019-01-23 icml/icml_local_density_clustering.tex
Fixed few typos

@@
 \label{eqn: inverse_mixing_time_lower_bound_nonconvex}
-\Psi_{n,r}(\Csig[\Xbf]) \geq \left(d \log \mu + c_{\lambda} \right)^{-1} \cdot \\
+\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq (d \log \mu + c_{\lambda}) \cdot \\  
 \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
-    \log \mu + c_{\lambda}\right)\right)^{-1},
+    \log \mu + c_{\lambda}\right)\right),
 \end{multline}
-% RJT: confused ... is this correct?
 with probability at least $1 - \delta$, where $c_1,c_2,c_3>0$ are constants
@@
 $$
-The factor $1/r^{2d}$ in the lower bound in \eqref{eqn:
+The factor of $1/r^{2d}$ in the bound in \eqref{eqn:
   inverse_mixing_time_lower_bound_nonconvex} is suboptimal. This exponential 
@@
 It is possible to sharpen the dependency on $d$ in 
-\label{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an 
-additional assumption: 
+\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
+additional assumption.
 \begin{enumerate}[label=(A\arabic*)]
@@
 \label{asmp: convex}
-  $\Cset$ is convex.
+\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
 \end{enumerate}
@@
 
-With \ref{asmp: convex} in place, we now give a tighter lower bound on the
-inverse mixing time of $C_\sigma[\Xbf]$ (albeit one that holds only
-asymptotically).
+With \ref{asmp: convex} in place, we give a tighter bound on the
+mixing time (albeit one that holds only asymptotically).
 
@@
 Assume the conditions of Theorem \ref{thm:
-  inverse_mixing_time_lower_bound_nonconvex}, and additionally, let $\Cset$
-satisfy \ref{asmp: convex}. Then, 
-for any $r < \sigma/4d$, the following statement holds with probability 1: 
+  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
+  convex}. Then for any $r < \sigma/4d$, the following holds with probability 1:  
 \begin{align}
 \label{eqn: inverse_mixing_time_lower_bound}
-  \liminf_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ 
+  \limsup_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq \nonumber \\ 
 &\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
@@
 \end{align}
-% RJT: confused ... is this correct?
 where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
@@
 on this conductance function over $G_{n,r}$ in terms of a population-level
-analogue, which we term \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
+analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
 \smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
-a bound on mixing time (with respect to total variation distance) of order $d
+a mixing time bound (with respect to total variation distance) of order $d
 D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
@@
   The convexity requirement is necessary only to lower bound the
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$}; any bound on $\widetilde{\Phi}_{\Pbb,r}$
-  which   does not require convexity could immediately be plugged into the
-  machinery of   the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
-  to achieve a corresponding result. Recent work \citep{abbasi17} has developed
-  such population-level bounds on the conductance function, however the Markov
-  chain dealt with there is somewhat different than the one we consider.  
+  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any bound on
+  \smash{$\widetilde{\Phi}_{\Pbb,r}$} which does not require convexity could
+  immediately be plugged into the machinery of the proof of Theorem \ref{thm:
+    inverse_mixing_time_lower_bound} to achieve a corresponding result. Recent
+  work \citep{abbasi17} has developed such population-level bounds on the
+  conductance function, however the Markov chain dealt with there is somewhat
+  different than the one we consider.   
 \end{remark}

### 2019-01-23 icml/icml_local_density_clustering.tex
Cleaned up RJT comments
A bit of edits and corrections.  Still haven't gone through Sect 3 (or 4)

@@
 
-\paragraph{External Connectivity: Normalized Cut.}
+\paragraph{External Connectivity: Normalized Cut}
 
@@
 
-\paragraph{Internal Connectivity: Inverse Mixing Time.}
+\paragraph{Internal Connectivity: Inverse Mixing Time}
 
@@
 write 
-\begin{equation}
-\label{eqn: random_walk}
+$$
 q_{vu}^{(t)} = e_v\Wbf_S^t e_u
-\end{equation}
+$$
 for the $t$-step transition probability of a random walk over $G[S]$
@@
   \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
-  steps.}   Also write \smash{$\tilde\pibf = (\tilde\pi_{u})_{u \in S}$} for the 
-  stationary distribution of this random walk.  (Given the definition of
+  steps.}   Also write \smash{$\widetilde\pibf = (\widetilde\pi_{u})_{u \in S}$}
+for the stationary distribution of this random walk.  (Given the definition of 
 $\Wbf_S$, it is well-known that the stationariy distribution is given by
-  \smash{$\tilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
+\smash{$\widetilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
 
@@
   time} of $G[S]$ as 
-\begin{equation*}
-\tau_{\infty}(\qbf; G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} -
-      \tilde\pi_u|}{\tilde\pi_u} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}, 
-\end{equation*}
-where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
-\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. Now our internal 
-connectivity parameter is simply the inverse mixing time,
+$$
+\tau_{\infty}(G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} - 
+      \widetilde\pi_u|}{\widetilde\pi_u} \leq \frac{1}{4}, 
+    \; \text{for $u,v \in V$}},  
+$$
+%where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
+%\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. 
+% RJT: I got rid of the notational dependence on \qbf, because these quantities
+% are in turn just defined in terms of the induced subgraph G[S]
+Now our internal connectivity parameter is simply the inverse mixing time, 
 \begin{equation}
 \label{eqn: inv_mixing_time}
-\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}.
+\Psi(S; G) = \frac{1}{\tau_{\infty}(G[S])}.
 \end{equation}
@@
 \begin{enumerate}
-\item In Section \ref{sec: PhiPsi}, we derive in Theorem \ref{thm:
-    conductance_upper_bound} an upper bound on the normalized cut of a
+\item In Section \ref{sec: cluster_quality_bounds}, we derive in Theorem
+  \ref{thm: conductance_upper_bound} an upper bound on the normalized cut of a  
   (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
@@
 \section{Cluster Quality Critera Bounds for Density Clusters}  
-\label{sec: PhiPsi}
+\label{sec: cluster_quality_bounds}
 
-\subsection{Assumptions}
+\subsection{Geometric Conditions on Density Clusters}
 
@@
 time of an empirical density cluster, we must introduce conditions on the
-density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the ball of
-radius $r$ centered at $x$.  Given a set $\Aset \subseteq \Rd$ and $\sigma > 0$,
-define $\Asig = \Aset + B(0,\sigma) = \{y \in \Rd: \inf_{x \in \Aset} \norm{y - 
-    x} \leq \sigma\}$, which we call the $\sigma$-expansion of $\Aset$.
+density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the closed
+ball of radius $r \geq 0$, centered at $x \in \Rd$.  Given a set $\Aset
+\subseteq \Rd$ and $\sigma > 0$, define $\Asig = \Aset + B(0,\sigma) = \{y \in
+\Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma\}$, which we call the
+$\sigma$-expansion of $\Aset$.
 
 We are now ready to give the conditions, stated with respect to a density
-cluster $\Cset \in \Cbb_f(\lambda)$, for some $\lambda > 0$, and an expansion 
-parameter $\sigma > 0$.
+cluster $\Cset \in \Cbb_f(\lambda)$, for some threshold $\lambda > 0$, and an
+expansion parameter $\sigma > 0$.
 
@@
 criteria evaluated on (thickened) density clusters. For notational simplicity,
-hereafter for $S \subseteq V$, we will denote $\Phi(S; G_{n,r})$ by
-$\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$. We
-will also use $\nu$ for Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for 
-the measure of the unit ball $B=B(0,1)$. 
+hereafter for $S \subseteq V$, we will abbreviate $\Phi(S; G_{n,r})$ by
+$\Phi_{n,r}(S)$, and similarly, $\Psi(S; G_{n,r})$ by $\Psi_{n,r}(S)$, and
+$\tau_{\infty}(G_{n,r}[S])$ by $\tau_{n,r}(S)$. We will also use $\nu$ for
+Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for the measure of the unit ball
+$B=B(0,1)$.  
 % RJT: you had B(0,d) before ... just check this should have been B(0,1)
@@
 
-We begin by upper bounding the normalized cut of $\Cset_\sigma[\Xbf]$.  (In the
-theorem, the upper bound on the density in Assumption \ref{asmp: 
-  bounded_density} will not actually be needed, so we omit the parameter
-$\Lambda_\sigma>0$ from the theorem statement.)
+We start with an upper bound on the normalized cut \eqref{eqn: norm_cut} of 
+$\Cset_\sigma[\Xbf]$. (In the theorem, the upper bound on the density in
+Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
+the parameter $\Lambda_\sigma>0$ from the theorem statement.)
 
@@
   conductance_sample_complexity}, 
-\begin{equation*}
+$$
   \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
     \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
-\end{equation*}
+$$
 with probability at least $1 - \delta$, for some constant $c$. (Note that the
@@
 
-We lower bound the inverse mixing time of $\Csig[\Xbf]$.
+Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of 
+$\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) =
+1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time. 
+% RJT: note I changed the next two theorems to be upper bounds on the mixing
+% time.  Upper bounds on the inverse inverse mixing time, which was a bit
+% superfluous.  Just make sure that the supplement is in sync with this
 
@@
 \label{eqn: inverse_mixing_time_lower_bound_nonconvex}
-\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq (d \log \mu + c_{\lambda}) \cdot \\  
+\tau_{n,r}(\Csig[\Xbf]) \leq (d \log \mu + c_{\lambda}) \cdot \\  
 \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
@@
 \end{multline}
-with probability at least $1 - \delta$, where $c_1,c_2,c_3>0$ are constants
+with probability at least $1 - \delta$, where $c_1,c_2>0$ are constants
 depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
@@
 \end{theorem}
-% RJT: saying that c_1,c_2,c_3 depend on the dimension is a little odd/weak.
+% RJT: saying that c_1,c_2 depend on the dimension is a little odd/weak.
 % c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
@@
 
-\subsection{Tigher Lower Bound Under Convexity}
+\subsection{Tighter Lower Bound Under Convexity}
 
@@
 \end{enumerate}
-% RJT: do we need C to satisfy this, or Csig?  Not sure I know why the former
-% matters ...
 
@@
   inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
-  convex}. Then for any $r < \sigma/4d$, the following holds with probability 1:  
+  convex}. Then for any $0 < r < \sigma/4d$, the following holds with
+probability 1:   
 \begin{align}
 \label{eqn: inverse_mixing_time_lower_bound}
-  \limsup_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq \nonumber \\ 
+  \limsup_{n \to \infty} \, &\tau_{n,r}(\Csig[\Xbf]) \leq \nonumber \\ 
 &\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
@@
 \end{theorem}
-% RJT: this was a lower bound on 1/\Psi and I changed it to \Psi ... just
-% checking
 
@@
   function},
-\begin{equation*}
+$$
 \widetilde{\Phi}_n(t) = 
-\min_{\substack{S \subseteq \Csig[\Xbf] \\ \tilde\pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]]) 
-\end{equation*}
-where \smash{$\tilde\pi$} is the stationary distribution over
+\min_{\substack{S \subseteq \Csig[\Xbf] \\ \widetilde\pi(S) \leq t}} 
+\Phi(S; G_{n,r}[\Csig[X]]),
+$$
+where \smash{$\widetilde\pi$} is the stationary distribution over
 $G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
@@
 \smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
-a mixing time bound (with respect to total variation distance) of order $d
+a mixing time bound (with respect to total variation distance) on the order $d 
 D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
@@
 \begin{remark}
-  The convexity requirement is necessary only to lower bound the
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any bound on
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$} which does not require convexity could
-  immediately be plugged into the machinery of the proof of Theorem \ref{thm:
-    inverse_mixing_time_lower_bound} to achieve a corresponding result. Recent
-  work \citep{abbasi17} has developed such population-level bounds on the
-  conductance function, however the Markov chain dealt with there is somewhat
-  different than the one we consider.   
+  The convexity condition is only needed to lower bound 
+  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any lower bound on
+  \smash{$\widetilde{\Phi}_{\Pbb,r}$} could be directly plugged into the 
+  machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
+  to yield an alternative result. In recent work, \citet{abbasi17} developed new
+  population-level bounds on the conductance function (without requiring
+  convexity), however the Markov chain dealt with there is somewhat different 
+  than the one we consider.    
 \end{remark}
@@
 
-For PPR to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.
+\subsection{Well-Conditioned Density Clusters}
 
-We introduce
+For PPR to successfully recover density clusters, the ratio
+$\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.  Let us
+introduce the following notation for the upper bounds in Theorems 
+\ref{thm: conductance_upper_bound} and \ref{thm:
+  inverse_mixing_time_lower_bound_nonconvex}:
 \begin{align*}
-\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
-1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
-& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
+\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) 
+&= \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
+  \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}, \\
+1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) 
+&= \left(d \log \mu + c_{\lambda} \right) \cdot \\ 
+& \left(c_1 + c_2
+  \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + 
+  c_{\lambda}\right)\right)
 \end{align*}
+(where all constants $\lambda_\sigma,c_1,c_2, c_\lambda>0$ are as in these 
+theorems).
 
@@
 \end{remark}
-\paragraph{Approximate cluster recovery via PPR.}
+\paragraph{Approximate cluster recovery via PPR}
 
@@
 
-For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
+For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.r
 \begin{lemma}[PPR clustering]

### 2019-01-23 icml/icml_experiments.tex
final icml version

--- 2019-01-23 icml/icml_local_density_clustering.tex
@@
 \newtheorem{remark}{Remark}
+
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
 
-%%%%%
-\icmltitlerunning{Local Spectral Clustering of Density Upper Level Sets}
+\icmltitlerunning{Local clustering of density upper level sets}
 
@@
 \icmltitle{Local Spectral Clustering of Density Upper Level Sets}
+
 \icmlsetsymbol{equal}{*}
@@
 \icmlauthor{Sivaraman Balakrishnan}{cmu}
-\icmlauthor{Ryan J. Tibshirani}{cmu}
+\icmlauthor{Ryan Tibshirani}{cmu}
 \end{icmlauthorlist}
 
-\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon
-  University, Pittsburgh PA, USA} 
+\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}
+
 \icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
+
 \icmlkeywords{local clustering}
@@
 
-\begin{abstract}
-\vskip 0.1 in % RJT: there was no space here and it looked very squished 
-Spectral clustering methods are a family of popular nonparametric clustering
-tools.  Recent works have proposed and analyzed \emph{local} spectral methods,
-which extract clusters using locally-biased random walks around a user-specified
-seed node.  Several authors have shown that local methods, such as personalized
-PageRank (PPR), have worst-case guarantees for certain graph-based measures of
-cluster quality.  In contrast to existing works, we analyze PPR in a traditional
-statistical learning setup, where we obtain samples from an unknown
-distribution, and aim to identify connected regions of high-density (density
-clusters).  We introduce two natural criteria for cluster quality, and derive
-bounds for these criteria when evaluated on empirical analogues of density
-clusters. Moreover, we prove that PPR, run on a neighborhood graph, extracts
-sufficiently salient density clusters.
-\end{abstract}
+\section{Empirical Performance of PPR on Gaussian Mixture Models}
 
-\section{Introduction}
-\label{sec: introduction}
+The assumptions and theory of Section \textcolor{red}{2} are tailored towards density functions with sharp transitions in gradient around the perimeter of the density cluster.
+These type of functions will satisfy \textcolor{red}{A3} with a small ratio of $\Lambda_{\sigma}$ to $\lambda_{\sigma}$, while still satisfying \textcolor{red}{A4}, potentially for $\gamma << 1$.
 
-Let $\mathbf{X} = \{x_1, \ldots, x_n\}$ be a sample drawn i.i.d.\ from a
-distribution $\Pbb$ on $\Rd$, with density $f$, and consider the problem of 
-clustering: splitting the data into groups which satisfy some notion of
-within-group similarity and between-group difference.  We focus on spectral
-clustering methods, a family of powerful nonparametric clustering algorithms.
-Roughly speaking, a spectral technique first constructs a geometric graph $G$,
-where vertices are associated with samples, and edges correspond to proximities
-between samples. It then learns a feature embedding based on the Laplacian of
-$G$, and applies a simple clustering technique (such as k-means clustering) in
-the embedded feature space.
+As mentioned previously, one line of work on spectral algorithms assesses their performance on mixture models.
+Particularly well-developed is the characterization of clustering performance on Gaussian Mixture Models (GMMs).
+Gaussian Mixture Models have smooth derivatives, and are therefore not good candidates for our work (at least, for reasonable values of the parameters in \textcolor{red}{(A1)-(A4)} ).
+Since they are a classical choice in the clustering literature, we investigate \pprspace performance on them empirically.
 
-To be more precise, let $G=(V,E,w)$ denote a weighted, undirected graph  
-constructed from the samples $\mathbf{X}$, where $V=\{1,\ldots,n\}$, and $w_{uv}
-= K(x_u,x_v) \geq 0$ for $u,v \in V$, and a particular kernel function $K$.
-Here $(u,v) \in E$ if and only if $w_{uv} > 0$.  We denote by $\Abf \in
-\Reals^{n \times n}$ the weighted adjacency matrix, which has entries
-$A_{uv}=w_{uv}$, and by $\Dbf$ the degree matrix, with 
-\smash{$\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$}.  We also denote by $\Wbf,\Lbf$
-the random walk transition probability matrix and normalized\footnote{Other
-  popular choices here include the unnormalized Laplacian, and symmetric
-  normalized Laplacian.} 
-Laplacian matrix, respectively, which are defined as
-$$
-\Wbf = \Dbf^{-1}\Abf, \quad \Lbf = \Ibf{} - \Wbf,
-$$
-where $\Ibf{} \in \Reals^{n\times n}$ is the identity matrix.  Classical global
-spectral methods take a eigendecomposition $L=U \Sigma U^T$, use some 
-number of eigenvectors (columns in $U$) as a feature representation for the
-samples, and then run (say) k-means in this new feature space.
+\begin{figure*}[ht]
+	\vskip 0.2in
+	\begin{center}
+	\centerline{\includegraphics[width=\columnwidth]{graphic_1}}
+	\caption{Algorithm \ref{alg: ppr} run over 4 example datasets.
+Parameters $\alpha$ and $\pi_0$ were tuned to minimize normalized cut of output set.
+Colors represent \pprspace cuts; shapes correspond to the maximum density among mixture components.
+Sample size $n = 400$.}
+	\label{fig: graphic_1}
+	\end{center}
+	\vskip 0.2in
+\end{figure*}
 
-When applied to geometric graphs constructed from a large number of samples,
-global spectral clustering methods can be been computationally cumbersome and   
-insensitive to the local geometry of the underlying distribution
-\citep{leskovec2010,mahoney2012}.  This has led to recent increased interest in
-local spectral algorithms, which leverage locally-biased spectra computed using
-random walks around a user-specified seed node.  A popular local clustering
-algorithm is Personalized PageRank (PPR), first introduced by
-\citet{haveliwala2003}, and further developed by
-\citet{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
-among others.
+Figure \ref{fig: graphic_1} tells a story with roughly the same narrative as our theoretical work.
+The left two plots demonstrate instances, in one and two-dimensions, respectively, where the \pprspace cut has small error relative to a density cut.
+The right two plots, by contrast, show \pprspace failing to recover, even approximately, a density cut.
 
-Local spectral clustering techinques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
-many authors to develop supporting theory
-\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
-guarantees on traditional graph-theoretic notions of cluster quality (like
-conductance).  In this paper, we adopt a more traditional statistical viewpoint,
-and examine what the output of a local clustering algorithm on $\Xbf$ reveals
-about the unknown density $f$.  In particular, we examine the ability of the PPR
-algorithm to recover \emph{density clusters} of $f$, which are defined as the
-connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
-for some threshold $\lambda > 0$ (a central object of central interest in the
-classical statistical literature on clustering, dating back to
-\citealt{hartigan1981}).
-
-\subsection{Graph Connectivity Criteria}
-
-Here we define a pair of criteria that reflect the quality of a cluster with
-respect to $G=(V,E,w)$.  There are many graph-based measures of cluster quality  
-that one could consider; see, e.g., \citet{yang2015,fortunato2010} for 
-an overview.  The pair of criteria that we focus on are (arguably) quite
-natural, and moreover, they play a fundamental role in our analysis 
-of the PPR algorithm.  Our two critera capture the \emph{external} and
-\emph{internal} connectivity of a subset $S \subseteq V$, denoted $\Phi(S; G)$
-and $\Psi(S; G)$, respectively, and defined below in turn.
-
-\paragraph{External Connectivity: Normalized Cut.}
-
-Define the cut between subsets $S,S' \subseteq V$ to be
-$$
-\cut(S, S'; G) = \sum_{u \in S} \sum_{v \in S'} w_{uv},
-$$
-and define
-\smash{$\vol(S; G) = \cut(S, V; G) = \sum_{u \in S} \sum_{v \in V} w_{uv}$}.  
-As our notion of external connectivity, we use the \emph{normalized cut}  
-of $S$, defined as 
-\begin{equation}
-\label{eqn: norm_cut}
-\Phi(S; G) = \frac{\cut(S; G)}{\min\{\vol(S; G), \vol(S^c; G)\}},
-\end{equation} 
-where we abbreviate $\cut(S; G) = \cut(S; S^c; G)$.
-
-\paragraph{Internal Connectivity: Inverse Mixing Time.}
-
-For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
-$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Abf_S,\Dbf_S$
-be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
-random walk matrix as usual, $\Wbf = \Dbf_S^{-1} \Abf_S$, and for $v \in V$,
-write 
-\begin{equation}
-\label{eqn: random_walk}
-q_{vu}^{(t)} = e_v\Wbf_S^t e_u
-\end{equation}
-for the $t$-step transition probability of a random walk over $G[S]$
-originating at $v$.\footnote{Given a starting node $v$ and and a random walk
-  defined by transition probability matrix $\mathbf{P}$, the rotation $e_v
-  \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
-  steps.}   Also write \smash{$\tilde\pibf = (\tilde\pi_{u})_{u \in S}$} for the 
-  stationary distribution of this random walk.  (Given the definition of
-  $\Wbf_S$, it is well-known that the stationariy distribution is given by
-  \smash{$\tilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
-
-Our internal connectivity parameter will capture the time it takes for the
-random walk over $G[S]$ to mix (approach the stationary distribution)
-uniformly over $S$.  For this, we first define \emph{relative pointwise mixing
-  time} of $G[S]$ as 
-\begin{equation*}
-\tau_{\infty}(\qbf; G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} -
-      \tilde\pi_u|}{\tilde\pi_u} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}, 
-\end{equation*}
-where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
-\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. Now our internal 
-connectivity parameter is simply the inverse mixing time,
-\begin{equation}
-\label{eqn: inv_mixing_time}
-\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}.
-\end{equation}
-
-If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no
-less than $\Psi$, we call it as a \emph{$(\Phi,\Psi)$-cluster}. Both
-local \citep{zhu2013} and global \citep{kannan04} spectral algorithms have been
-shown to output clusters (or partitions) which approximate the optimal $(\Phi,
-\Psi)$-cluster (or partition) for a given graph $G$.\footnote{In the case of
-  \citet{kannan04}, the internal connectivity parameter $\phi$ is actually the
-  conductance, i.e., the minimum normalized cut within the subgraph $G[S]$. See
-  Theorem 3.1 in their paper for details; however, note that $\phi^2 /
-  \log(\vol(S)) \leq O(\Psi)$, and so the lower bound on $\phi$ translates to a
-  lower bound on $\Psi$.}
-
-\subsection{PPR on a Neighborhood Graph}
-
-We now describe the clustering algorithm that will be our focus for the rest of 
-the paper. We start with the geometric graph that we form based on the samples 
-$\Xbf$: for a radius $r > 0$, we consider the \emph{$r$-neighborhood graph} of 
-$\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted graph with vertices
-$V=\{1,\ldots,n\}$, and an edge $(u,v) \in E$ if and only if $\norm{x_u - x_v}
-\leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.  Note that this is a
-special case of the general construction introduced above, with 
-$K(u,v) = 1(\norm{x_u - x_v} \leq r)$.
-
-Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, with respect to  
-a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be
-the solution of the following linear system:
-\begin{equation}
-\label{eqn: ppr_vector}
-\pbf = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
-\end{equation}
-where $\Wbf$ is the random walk matrix of the underlying graph $G_{n,r}$ 
-and $e_{v}$ denotes indicator vector for node $v$ (with a 1 in the $v$th
-position and 0 elsewhere).  In practice, we can approximately solve the above
-linear system via a simple, efficient random walk, with appropriate restarts to
-$v$.
-
-For a level $\beta > 0$ and a target volume $\pi_0 > 0$, we define a
-\emph{$\beta$-sweep cut} of $\pbf$ as  
-\begin{equation}
-\label{eqn: sweep_cuts}
-S_\beta = \{u \in V: p_u > \beta \pi_{0}\}.
-\end{equation}
-Having computed sweep cuts over a range \smash{$\beta \in  
-(\frac{3}{10},\frac{1}{2})$},\footnote{The choice of a specific range such as 
-\smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citet{zhu2013}.}
-we output a cluster \smash{$\widehat{C} = S_{\beta^*}$}, based on the sweep cut
-$S_{\beta^*}$ that minimizes the normalized cut \smash{$\Phi(S_{\beta^*};
-  G_{n,r})$} as defined in \eqref{eqn: norm_cut}. For concreteness, we summarize
-this procedure in Algorithm \ref{alg: ppr}.
-
-\begin{algorithm}
-\caption{PPR on a Neighborhood Graph}
-\label{alg: ppr}	
-{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation 
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target volume $\pi_0 >
-0$. \\   
-{\bfseries Output:} cluster $\widehat{C} \subseteq V$.
-\begin{algorithmic}[1]
-  \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn:
-    ppr_vector}. 
-  \STATE For $\beta \in (\frac{3}{10}, \frac{1}{2})$ compute sweep cuts
-  $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-  \STATE Return \smash{$\widehat{C} = S_{\beta^*}$}, where 
-  $$
-  \beta^* = \argmin_{\beta \in (\frac{3}{10}, \frac{1}{2})} \Phi(S_{\beta}; G_{n,r}).
-  $$
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Summary of Results}
-
-% It is worth calling attention to some other work on computing the normalized
-% cut over neighborhood graphs. In this context, continuous analogues to (for
-% instance) normalized cut have been defined, over the data-manifold rather than
-% the graph, and convergence finite sample graph-theoretic functionals to their
-% continuous counterparts has been shown 
-% \cite{garciatrillos16, arias-castro12, maier11}. 
-% However, in addition to the graph-minimization problem being computationally
-% infeasible, these continuous analogues are not always easily interpretable --
-% and their corresponding minimizers not always easily identifiable -- for the
-% particular density function under consideration. Of course, relating these
-% partitions to the arguably more simply defined high density clusters can be
-% also challenging in general. Intuitively, however, under the right conditions
-% such high-density clusters should have more edges within themselves than to
-% the remainder of the graph. We formalize this intuition next.
-
-%% RJT: I didn't know where to put this.  It was out of place, and now I'm not
-%% sure where it goes ... should it go in related work?
-
-%It is worth pointing out that in this context, some theory has been developed
-%regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and
-%others) relate to properties of the underlying distribution $f$ as well as the
-%kernel function $k$. Such analyses typically proceed by defining a continuous
-%analogue to the measure of cluster quality under consideration. Then, under
-%appropriate specification of $k$ and a proper schedule of $(r_n)$, convergence
-%of clusters output by spectral (and other) algorithms to the corresponding
-%minima of these continuous analogues has been shown \cite{vonluxburg2008,
-%garciatrillos18}.
-
-%% RJT: This was already commented out before
-
-Let $\Cbb_f(\lambda)$ denote the connected components of the density upper level
-set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster $\Cset \in
-\Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
-  density cluster}. Below we define a notion of consistency in density cluster
-estimation.
-
-\begin{definition}[Consistent density cluster estimation]
-\label{def: consistent_density_cluster_estimation}
-For an estimator \smash{$\widehat{\Cset} \subseteq \Xbf$} and cluster 
-$\Cset \in \Cbb_f(\lambda)$, we say \smash{$\widehat{\Cset}$} is a consistent
-estimator of $\Cset$ if for all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset \not=
-\Cset'$ the following holds as $n \to \infty$: 
-\begin{equation}
-\label{eqn: consistent_density_cluster_recovery}
-\Cset[\Xbf] \subseteq \widehat{\Cset} \quad \text{and} \quad
-\widehat{\Cset} \cap \Cset'[\Xbf] = \emptyset,
-\end{equation}
-with probability tending to 1.
-\end{definition}
-
-A summary of our main results (and outline for the rest of this paper) is as
-follows.
-
-\begin{enumerate}
-\item In Section \ref{sec: PhiPsi}, we derive in Theorem \ref{thm:
-    conductance_upper_bound} an upper bound on the normalized cut of a
-  (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
-  conditions (precluding clusters that are too thin and long).
-
-\item Under largely the same set of geometric conditions, we derive in Theorem
-  \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
-  inverse mixing time of a random walk over $\Csig[\Xbf]$.  We also provide in 
-  Theorem \ref{thm: inverse_mixing_time_lower_bound} a tighter lower bound, but
-  under more restrictive assumptions (convexity of $\Csig$).
-
-\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
-  Theorem \ref{thm: consistent_recovery_of_density_clusters} that these bounds
-  in bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    inverse_mixing_time_lower_bound_nonconvex},
-  on the cluster quality criteria, have algorithmic consequences for PPR:
-  properly initialized, Algorithm \ref{alg: ppr} performs consistent density
-  cluster estimation in the sense of \eqref{eqn:
-    consistent_density_cluster_recovery}.
-
-\item We show in Corollary \ref{cor: ppr_cluster} that Theorems \ref{thm:
-    conductance_upper_bound} and \ref{thm:
-    inverse_mixing_time_lower_bound_nonconvex}, along with the results in 
-  \citet{zhu2013}, lead to alternative, graph-theoretic guarantees on cluster 
-  quality: an upper bound on the normalized cut of the estimated cluster 
-  \smash{$\widehat{C}$}, and an upper bound on volume of the symmetric set
-  difference between \smash{$\widehat{C}$} and $\Cset[\Xbf]$.
-
-\item In Section \ref{section: examples}, we discuss the implications of our
-  results for some example density functions of interest, and empirically
-  demonstrate that violations of the gometric conditions we require manifestly
-  impact density cluster recovery. 
-\end{enumerate}
-
-On the topic of conditions, it is worth mentioning that, as density clusters
-are inherently local, focusing on the PPR algorithm actually eases our analysis
-and allows us to require fewer global regularity conditions relative to those
-needed for more classical global spectral algorithms.
-
-\subsection{Related Work}
-
-In addition to the background given above, a few related lines of work are worth
-highlighting. Global spectral clustering methods were first developed in the
-context of graph partitioning \citep{fiedler1973,donath1973} and their
-performance is well-understood in this context (see, e.g.,
-\citealt{tolliver2006,luxburg2007}).  In a similar vein, several recent works
-\citep{mcsherry2001,rohe2011,kamalika2012,balakrishnan2011,lei2015,abbe2018} 
-have studied the efficacy of spectral methods in successfully recovering the
-community structure in the stochastic block model and variants.
-
-\citet{vonluxburg2008,hein2005}, building on earlier work of
-\citet{koltchinskii2000}, studied the limiting behaviour of spectral clustering
-algorithms. These authors show that when samples are obtained from a
-distribution, and we appropriately construct a geometric graph, the spectrum of
-the Laplacian converges to that of the Laplace-Beltrami operator on the
-data-manifold. However, relating the partition obtained using the
-Laplace-Beltrami operator to the more intuitively defined high-density
-clusters can be challenging in general.
-
-Perhaps most similar to our results are the works
-\citet{vempala2004,shi2009,schiebinger2015}, who study the consistency of
-spectral algorithms in recovering the latent labels in certain parametric and
-nonparametric mixture models. These results focus on global rather than local
-algorithms, and as such impose global rather than local conditions on the nature
-of the density. Moreover, they do not in general ensure recovery of density
-clusters, which is the focus in our work.
-
-\section{Cluster Quality Critera Bounds for Density Clusters}  
-\label{sec: PhiPsi}
-
-\subsection{Assumptions}
-
-In order to provide meaningful bounds on the normalized cut and inverse mixing
-time of an empirical density cluster, we must introduce conditions on the
-density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the ball of
-radius $r$ centered at $x$.  Given a set $\Aset \subseteq \Rd$ and $\sigma > 0$,
-define $\Asig = \Aset + B(0,\sigma) = \{y \in \Rd: \inf_{x \in \Aset} \norm{y - 
-    x} \leq \sigma\}$, which we call the $\sigma$-expansion of $\Aset$.
-
-We are now ready to give the conditions, stated with respect to a density
-cluster $\Cset \in \Cbb_f(\lambda)$, for some $\lambda > 0$, and an expansion 
-parameter $\sigma > 0$.
-
-\begin{enumerate}[label=(A\arabic*)]
-\item
-\label{asmp: bounded_density}
-\emph{Bounded density within cluster:} There are $0 < \lambda_{\sigma} <
-\Lambda_{\sigma} < \infty$ such that
-$$
-\lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq
-\Lambda_{\sigma}.
-$$
-% and 
-% \begin{equation*}
-% \frac{\diam \Asig}{\sigma} \leq \mu
-% \end{equation*}
-% where $\diam \Asig = \sup \set{d(x,y) : x,y \in \Asig}$
-
-\item 
-\label{asmp: low_noise_density}
-\emph{Low noise density:} There exist $\gamma, c_1 > 0$ such that for all $x
-\in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-$$
-  \inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \dist(x, \Csig)^{\gamma},
-$$
-where \smash{$\dist(x,\Aset) = \inf_{x_0 \in \Aset} \norm{x - x_0}$}.
-% RJT: should we change this to c_0?  c_1 seems to be used below and throughout
-% for other constants, and c_0 is not used
-
-\item
-\label{asmp: cluster_separation}
-\emph{Cluster separation:}
-For all $\Cset' \in \Cbb_f(\lambda)$,
-$$
-\dist(\Csig,\Csig') > \sigma,
-$$
-where \smash{$\dist(\Aset,\Aset') = \inf_{x \in \Aset} \dist(x,\Aset')$}.
-
-\item
-\label{asmp: cluster_diameter}
-\emph{Cluster diameter:}
-There exists $D < \infty$ such that for all $x, x' \in \Csig$,
-$$
-\norm{x - x'} \leq D.
-$$
-\end{enumerate}
-
-Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
-clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp:
-  cluster_diameter}, flat densities around the level set in \ref{asmp: 
-  low_noise_density}, and poorly separated clusters in \ref{asmp:
-  cluster_separation}.
-
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
-G_{n,r})$, whereas \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
-are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
-lower bound on minimum density in \ref{asmp: bounded_density} and \ref{asmp:  
-cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of
-\citet{chaudhuri2010}, a standard density clustering assumption, while
-\ref{asmp: low_noise_density} is seen in, e.g., \citet{singh2009} (as well as
-many other works on density clustering and level set estimation.) It is worth
-highlighting that these assumptions are all local in nature, a benefit of
-studying a local algorithm such as PPR.
-
-In the next several subsections, we will derive bounds on the cluster quality
-criteria evaluated on (thickened) density clusters. For notational simplicity,
-hereafter for $S \subseteq V$, we will denote $\Phi(S; G_{n,r})$ by
-$\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$. We
-will also use $\nu$ for Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for 
-the measure of the unit ball $B=B(0,1)$. 
-% RJT: you had B(0,d) before ... just check this should have been B(0,1)
-
-\subsection{Upper Bound on Normalized Cut}
-
-We begin by upper bounding the normalized cut of $\Cset_\sigma[\Xbf]$.  (In the
-theorem, the upper bound on the density in Assumption \ref{asmp: 
-  bounded_density} will not actually be needed, so we omit the parameter
-$\Lambda_\sigma>0$ from the theorem statement.)
-
-\begin{theorem}
-\label{thm: conductance_upper_bound}
-Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
-\ref{asmp: cluster_separation}, for some 
-$\sigma, \lambda_{\sigma}, c_1, \gamma > 0$. Then for any $0 < r <
-\sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and
-\begin{equation}
-\label{eqn: conductance_sample_complexity}
-n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}
-  { \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
-\end{equation}
-we have
-\begin{equation}
-  \label{eqn: conductance_additive_error_bound}
-  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq 4 c_{\sigma} d
-  \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-    \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
-\end{equation}
-with probability at least $1-\delta$, where $c_{\sigma} = 1 / \sigma$. 
-\end{theorem}
-
-\begin{remark}
-The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other
-proofs in this paper, can be found in the supplementary document. The key 
-idea is that for any $x \in \Cset$, the simple (possibly loose) fact
-$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Cset_{\sigma
-  + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
-  low_noise_density} to find a corresponding bound on the weighted volume,
-then apply standard concentration inequalities to convert from population-
-to sample-based results.  
-\end{remark}
-
-\begin{remark}
-The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
-tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
-$$
-f(x) = \lambda - \dist(x,\Asig)^{\gamma},
-$$
-% RJT: is this correct (is this what you meant)?  Original formula is below
-% $$
-% f(x)  = \begin{cases}
-%   \lambda &\text{for $x \in \Asig$}, \\
-%   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
-% \end{cases}
-% $$
-we have that for $n$ on the order of the lower bound in \eqref{eqn: 
-  conductance_sample_complexity}, 
-\begin{equation*}
-  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
-    \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
-\end{equation*}
-with probability at least $1 - \delta$, for some constant $c$. (Note that the
-factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
-\end{remark}
-
-\subsection{Lower Bound on Inverse Mixing Time}
-
-We lower bound the inverse mixing time of $\Csig[\Xbf]$.
-
-\begin{theorem}
-\label{thm: inverse_mixing_time_lower_bound_nonconvex}
-Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
-for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
-r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
-$$
-\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
-    \lambda_{\sigma}}} \leq \epsilon, 
-$$
-where \smash{$\mu = \log(\frac{2D}{r})$}, we have
-\begin{multline}
-\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
-\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq (d \log \mu + c_{\lambda}) \cdot \\  
-\left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
-    \log \mu + c_{\lambda}\right)\right),
-\end{multline}
-with probability at least $1 - \delta$, where $c_1,c_2,c_3>0$ are constants
-depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/
-\lambda_{\sigma}^2)$.   
-\end{theorem}
-% RJT: saying that c_1,c_2,c_3 depend on the dimension is a little odd/weak.
-% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
-% will swamp the linear factor of ....
-
-\begin{remark}
-The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies
-on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[X]]$, 
-$$
-\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]]).
-$$
-The factor of $1/r^{2d}$ in the bound in \eqref{eqn:
-  inverse_mixing_time_lower_bound_nonconvex} is suboptimal. This exponential 
-dependence on $d$ stems from a loose bound on the aforementioned
-conductance. In particular, we assert only that any set $S \subseteq \Csig[X]$
-must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding
-$\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of
-order $r^d$. The presence of $r^{2d}$ comes from upper bounding the mixing time
-by about \smash{$1/\widetilde{\Phi}^2$}, this being a variant of classic results
-on rapid mixing \citep{jerrum89}.  
-\end{remark}
-
-\subsection{Tigher Lower Bound Under Convexity}
-
-It is possible to sharpen the dependency on $d$ in 
-\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
-additional assumption.
-\begin{enumerate}[label=(A\arabic*)]
-\setcounter{enumi}{4}
-\item 
-\label{asmp: convex}
-\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
-\end{enumerate}
-% RJT: do we need C to satisfy this, or Csig?  Not sure I know why the former
-% matters ...
-
-With \ref{asmp: convex} in place, we give a tighter bound on the
-mixing time (albeit one that holds only asymptotically).
-
-\begin{theorem}
-\label{thm: inverse_mixing_time_lower_bound}
-Assume the conditions of Theorem \ref{thm:
-  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
-  convex}. Then for any $r < \sigma/4d$, the following holds with probability 1:  
-\begin{align}
-\label{eqn: inverse_mixing_time_lower_bound}
-  \limsup_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq \nonumber \\ 
-&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
-  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
-&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
-  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
-&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
-\end{align}
-where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
-constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
-$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
-% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
-\end{theorem}
-% RJT: this was a lower bound on 1/\Psi and I changed it to \Psi ... just
-% checking
-
-\begin{remark}
-The only potentially exponential dependence on dimension comes from the
-factor of $c_d$. However, for sufficiently small values of $r$ this will
-be dominated by the preceding factors, due to the presence of the
-$o_r(1)$ term. 
-\end{remark}
-% RJT: Don't get this comment.  You have o_r(1) / r^2, so this might still blow
-% up as r -> 0, right?
-
-\begin{remark}
-We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
-to those in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part
-by working with a generalization of the conductance, the \emph{conductance
-  function},
-\begin{equation*}
-\widetilde{\Phi}_n(t) = 
-\min_{\substack{S \subseteq \Csig[\Xbf] \\ \tilde\pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]]) 
-\end{equation*}
-where \smash{$\tilde\pi$} is the stationary distribution over
-$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
-known upper bound of mixing time by  
-\begin{equation}
-\label{eqn: average_conductance}
-\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
-\end{equation}
-which results in a tighter bound than merely using the conductance when
-\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.
-
-Our proof relies on a novel (to the best of our knowledge) uniform lower bound
-on this conductance function over $G_{n,r}$ in terms of a population-level
-analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
-\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
-a mixing time bound (with respect to total variation distance) of order $d
-D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
-  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
-(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
-pointwise distance (which is known to be a stricter metric). 
-\end{remark}
-
-\begin{remark}
-  The convexity requirement is necessary only to lower bound the
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any bound on
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$} which does not require convexity could
-  immediately be plugged into the machinery of the proof of Theorem \ref{thm:
-    inverse_mixing_time_lower_bound} to achieve a corresponding result. Recent
-  work \citep{abbasi17} has developed such population-level bounds on the
-  conductance function, however the Markov chain dealt with there is somewhat
-  different than the one we consider.   
-\end{remark}
-
-\section{Consistent Cluster Estimation}
-\label{sec: consistent_cluster_estimation_with_ppr}
-
-For PPR to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.
-
-We introduce
-\begin{align*}
-\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
-1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
-& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
-\end{align*}
-
-Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf$ and $\Psibf$.
-\begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty.$ Letting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ be given by
-	\begin{align*}
-	\kappa_1(\Cset) & := \frac{\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma)}{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)} \\
-	\kappa_2(\Cset) & := \kappa_1(\Cset) \cdot \sqrt{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)},
-	\end{align*}
-	we call $\Cset$ a \textrm{$(\kappa_1, \kappa_2)$-well-conditioned density cluster (with respect to $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).}
-\end{definition}
-
-$\Phibf$ and $\Psibf$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.
-
-\begin{remark}
-	For convenience and maximum generality, we define $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to correspond with the bound given by \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, and assume only \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density}.
-However, if we additionally have \ref{asmp: convex}, then we could sharpen $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to the tighter rate of \eqref{eqn: inverse_mixing_time_lower_bound}, with nothing changing hereafter.
-\end{remark}
-
-As is typical in the local clustering literature, our results will be stated with respect to specific choices or ranges of each of the user-specified parameters, which in this case may depend on the underlying (unknown) density.
-
-In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
-\begin{align}
-\label{eqn: initialization}
-\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D), & ~r \leq \sigma/4d  \nonumber \\
-\pi_0 \in [2/3, 6/5] \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}, & ~v \in \Csig[\Xbf]^g
-\end{align}
-where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
-(Intuitively one can think of $\Csig[\Xbf]^g$ as being the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
-
-\begin{definition}
-	If the input parameters to Algorithm \ref{alg: ppr} satisfy \ref{eqn: initialization} with respect to some $\Csig[\Xbf]$, we say the algorithm is  \emph{well-initialized}.
-\end{definition}
-
-\begin{theorem}
-	\label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$). If
-	\begin{equation}
-	\label{eqn: kappa2_ub}
-	\kappa_2 \leq \frac{1}{40 \cdot 36} \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)}.
-	\end{equation}
-	and Algorithm \ref{alg: ppr} is well-initialized, the output set $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-\end{theorem}
-
-\begin{remark}
-	We note that larger constants than $40 \cdot 36$ allow for wider range of the parameters in $\eqref{eqn: initialization}$. 
-\end{remark}
-\paragraph{Approximate cluster recovery via PPR.}
-
-In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
-Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut and symmetric set difference of $\widehat{C}$.
-
-We collect some of the main results of \cite{zhu2013} in Lemma \ref{lem: ppr_cluster}.
-
-For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
-\begin{lemma}[PPR clustering]
-	\label{lem: ppr_cluster}
-	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
-Letting
-	\begin{equation*}
-	\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G)
-	\end{equation*}
-	the following guarantees hold:
-	\begin{align*}
-	\vol(\widehat{C} \setminus A) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
-	\end{align*}
-\end{lemma}
-
-Corollary \ref{cor: ppr_cluster} immediately follows.
-\begin{corollary}
-	\label{cor: ppr_cluster}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).
-Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the following guarantees hold for output set $\widehat{C} \subseteq \Xbf$:
-	\begin{align*}
-	\vol(\widehat{C} \setminus \Csig[\Xbf]), \vol(\Csig[\Xbf] \setminus \widehat{C})  & \leq 30 \kappa_1(\Cset) \vol(\Csig[X]) \\
-	\Phi_{n,r}(\widehat{C}) & = O\left(\kappa_2(\Cset)\right)
-	\end{align*}
-\end{corollary}
-
-\section{Examples}
-\label{section: examples}
-
-Example 1 is intended to show how the machinery developed above translates in a specific, common mixture model, and the extent to which bounds are (or are not) tight.
-Example 2 \textcolor{red}{will try to} delve into some of the details of how \pprspace interpolates the conductance and density cut, and will show a case where a poorly conditioned density cluster is not recovered by \pprspace.
-Example 3 will emphasize finite sample cluster recovery, for a well-conditioned but non-convex mixture model
-
-Examples 1 and 2 should be thought of as shedding light on the population performance of \ppr, whereas Example 3 shows performance on a finite sample.
-
-\begin{enumerate}
-	\item 
-	\textit{Gaussian Mixture Model:} 
-	We will compute optimal $\Phibf$ and $\Psibf$ for given $\lambda$, and show the following
-	\begin{itemize}
-		\item A graph comparing $\Phibf$ to $\Phi_{n,r}$ as the value of $\lambda$ changes.
-		\item A graph comparing $\Psibf$ to $\Psi_{n,r}$ as the value of $\lambda$ changes.
-		\item That for some values of $\lambda$, the conditions required for Theorem \ref{thm: consistent_recovery_of_density_clusters} hold.
-	\end{itemize}
-
-	\item
-	\textit{Thin and long parallel clusters, with $\epsilon$-uniform noise: }
-	We will \textcolor{red}{(try to)} show that the set outputted by \pprspace interpolates between the minimum normalized cut solution (fatter) and the density cluster (thinner).
-The \emph{conductance} is
-	\begin{equation*}
-	\Phi^{\star}(G_{n,r}) := \min_{C \subseteq \Xbf} \Phi_{n,r}(C)
-	\end{equation*}
-	and the conductance cut is $C^{\star} \subseteq \Xbf$ which achieves the minimum.
-
-	We will show that
-	\begin{itemize}
-		\item For sufficiently small $\epsilon$, all three of the conductance cut, \pprspace cut, and density cut agree.
-		\item For an intermediate value of $\epsilon$, the conductance cut and the density cut disagree. The \pprspace cut interpolates between the two.
-		\item For a sufficiently large value of $\epsilon$, the \pprspace cut fails to recover the density cut, and draws closer to the conductance cut.
-	\end{itemize}
-
-	\item 
-	\textit{Non-convex mixture model:} We will show that, for well-conditioned non-convex mixture model, and a finite sample size $n$, cluster recovery is achieved with high probability over repeated simulations.
-\end{enumerate}
-
-\section{Discussion}
-\label{sec: discussion}
-For a clustering algorithm and a given object (such as a graph or set of points), there are an almost limitless number of ways to define what the 'right' clustering is.
-We have considered a few such ways -- density level sets, and the bicriteria of normalized cut, inverse mixing time -- and shown that under the right conditions, the latter agree with the former, with resulting algorithmic consequences.
-
-There are still many directions worth pursuing in this area.
-Concretely, we might wish to generalize our results to hold over a wider range of kernel functions, and hyperparameter inputs to the \pprspace algorithm.
-More broadly, we do not provide any sort of theoretical lower bound, although we give empirical evidence in Example 2 that poorly conditioned density clusters are not consistently estimated by \pprspace.
-Example 2 also hints at a way of understanding local spectral algorithms -- or, at least, \ppr-- as interpolating between normalized and density cut.
-Exploring this connection is an avenue for future work.
-
-\clearpage
-
-\bibliography{icml_bib}
-\bibliographystyle{icml2019}
+In the bottom right panel in particular, we see the effect of a high diameter on the performance of \pprspace.
+Although any one vertex on the boundary of a density level set may have few cut edges, the length of the boundary is sufficiently long to make the entire cut too large for \pprspace to select it.
+Instead, the \pprspace cut defaults to a more geometrically compact shape, which has much smaller (unweighted) perimeter.
 
 \end{document}
-
-% This document was modified from the file originally made available by
-% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
-% by Iain Murray in 2018, and modified by Alexandre Bouchard in
-% 2019. Previous contributors include Dan Roy, Lise Getoor and Tobias
-% Scheffer, which was slightly modified from the 2010 version by
-% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
-% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
-% slightly modified from Prasad Tadepalli's 2007 version which is a
-% lightly changed version of the previous year's version by Andrew
-% Moore, which was in turn edited from those of Kristian Kersting and
-% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2019-01-23 icml/icml_local_density_clustering.tex
final icml version

@@
 \begin{abstract}
-\vskip 0.1 in % RJT: there was no space here and it looked very squished 
+\vskip 0.1 in % RESOLVED
 Spectral clustering methods are a family of popular nonparametric clustering
@@
 When applied to geometric graphs constructed from a large number of samples,
-global spectral clustering methods can be been computationally cumbersome and   
+global spectral clustering methods can be computationally cumbersome and   
 insensitive to the local geometry of the underlying distribution
@@
 natural, and moreover, they play a fundamental role in our analysis 
-of the PPR algorithm.  Our two critera capture the \emph{external} and
+of the PPR algorithm.  Our two criteria capture the \emph{external} and
 \emph{internal} connectivity of a subset $S \subseteq V$, denoted $\Phi(S; G)$
@@
 for the stationary distribution of this random walk.  (Given the definition of 
-$\Wbf_S$, it is well-known that the stationariy distribution is given by
+$\Wbf_S$, it is well-known that the stationary distribution is given by
 \smash{$\widetilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
@@
 $$
-\tau_{\infty}(G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} - 
+\tau_{\infty}(G[S]) = \min\set{ m: \frac{|q_{vu}^{(m)} - 
       \widetilde\pi_u|}{\widetilde\pi_u} \leq \frac{1}{4}, 
@@
 % are in turn just defined in terms of the induced subgraph G[S]
+% AJG: RESOLVED
 Now our internal connectivity parameter is simply the inverse mixing time, 
@@
 
-For a level $\beta > 0$ and a target volume $\pi_0 > 0$, we define a
+For a level $\beta > 0$ and a target stationary measure $\pi_0 > 0$, we define a
 \emph{$\beta$-sweep cut} of $\pbf$ as  
@@
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation 
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target volume $\pi_0 >
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary measure $\pi_0 >
 0$. \\   
@@
 
-\item In Section \ref{section: examples}, we discuss the implications of our
-  results for some example density functions of interest, and empirically
-  demonstrate that violations of the gometric conditions we require manifestly
+\item In Section \ref{sec: experiments}, we empirically
+  demonstrate that violations of the geometric conditions we require manifestly
   impact density cluster recovery. 
@@
 \subsection{Related Work}
+%In addition to the background given above, a few related lines of work are worth
+%highlighting. For neighborhood graphs of the type we consider, continuous analogues to (for
+%instance) normalized cut have been defined, over the data-manifold rather than
+%the graph, and convergence finite sample graph-theoretic functionals to their
+% continuous counterparts has been shown 
+% \cite{garciatrillos16, arias-castro12, maier11}.
 
 In addition to the background given above, a few related lines of work are worth
-highlighting. Global spectral clustering methods were first developed in the
+highlighting.
+Global spectral clustering methods were first developed in the
 context of graph partitioning \citep{fiedler1973,donath1973} and their
@@
 
-\citet{vonluxburg2008,hein2005}, building on earlier work of
-\citet{koltchinskii2000}, studied the limiting behaviour of spectral clustering
+Building on earlier work of
+\citet{koltchinskii2000}, \citet{vonluxburg2008,hein2005} studied the limiting behaviour of spectral clustering
 algorithms. These authors show that when samples are obtained from a
@@
 \label{asmp: low_noise_density}
-\emph{Low noise density:} There exist $\gamma, c_1 > 0$ such that for all $x
+\emph{Low noise density:} There exists $\gamma > 0$ such that for all $x
 \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
 $$
-  \inf_{x' \in \Csig} f(x') - f(x) \geq c_1 \dist(x, \Csig)^{\gamma},
+  \inf_{x' \in \Csig} f(x') - f(x) \geq  \dist(x, \Csig)^{\gamma},
 $$
@@
 are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
-lower bound on minimum density in \ref{asmp: bounded_density} and \ref{asmp:  
-cluster_separation} combined are similar to the $(\sigma,\epsilon)$-saliency of
+lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
+cluster_separation} are similar to the $(\sigma,\epsilon)$-saliency of
 \citet{chaudhuri2010}, a standard density clustering assumption, while
@@
 In the next several subsections, we will derive bounds on the cluster quality
-criteria evaluated on (thickened) density clusters. For notational simplicity,
+criteria evaluated on ($\sigma$-expansions of) density clusters. For notational simplicity,
 hereafter for $S \subseteq V$, we will abbreviate $\Phi(S; G_{n,r})$ by
@@
 % RJT: you had B(0,d) before ... just check this should have been B(0,1) 
+% AJG: Yep.
 
@@
 \ref{asmp: cluster_separation}, for some 
-$\sigma, \lambda_{\sigma}, c_1, \gamma > 0$. Then for any $0 < r <
+$\sigma, \lambda_{\sigma}, c_1, \gamma > 0$. Moreover, let
+\begin{equation}
+\label{eqn: weighted_cluster_volume}
+\nu_{\Pbb}(\Csig) \leq \frac{1}{2}
+\end{equation}
+where $\nu_{\Pbb}(\Aset) = \int_{\Aset} f(x) dx$ for $\Aset \subset \Rd$.
+ Then for any $0 < r <
 \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and
@@
 $$
-f(x) = \lambda - \dist(x,\Asig)^{\gamma},
+ f(x)  = \begin{cases}
+   \lambda &\text{for $x \in \Asig$}, \\
+   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
+\end{cases}
 $$
-% RJT: is this correct (is this what you meant)?  Original formula is below
-% $$
-% f(x)  = \begin{cases}
-%   \lambda &\text{for $x \in \Asig$}, \\
-%   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
-% \end{cases}
-% $$
 we have that for $n$ on the order of the lower bound in \eqref{eqn: 
@@
   \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
-    \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
+    \frac{r^{\gamma+1}}{\gamma+1})}{\lambda} - \epsilon,
 $$
@@
 % superfluous.  Just make sure that the supplement is in sync with this
+% AJG: Perfect.
 
@@
 \tau_{n,r}(\Csig[\Xbf]) \leq (d \log \mu + c_{\lambda}) \cdot \\  
-\left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
+\left(c_1 + 9^d c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
     \log \mu + c_{\lambda}\right)\right),
 \end{multline}
-with probability at least $1 - \delta$, where $c_1,c_2>0$ are constants
-depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
+with probability at least $1 - \delta$, where $c_1,c_2>0$ are universal constants
+ and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
 \lambda_{\sigma}^2)$.   
@@
 % will swamp the linear factor of ....
+% AJG: Fixed.
 
@@
 The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies
-on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[X]]$, 
+on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[\Xbf]]$, 
 $$
-\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[X]]).
+\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[\Xbf]]).
 $$
@@
 The only potentially exponential dependence on dimension comes from the
-factor of $c_d$. However, for sufficiently small values of $r$ this will
-be dominated by the preceding factors, due to the presence of the
-$o_r(1)$ term. 
+factor of $c_d$.
+However, for sufficiently small values of $r$ $o_r(1)/r^2$ will be dominated by $1/r^2$, and therefore the last term in \eqref{eqn: inverse_mixing_time_lower_bound} will contribute negligibly to the overall bound.
 \end{remark}
-% RJT: Don't get this comment.  You have o_r(1) / r^2, so this might still blow
-% up as r -> 0, right?
-
 \begin{remark}
 We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
-to those in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part 
+to those of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part 
 by working with a generalization of the conductance, the \emph{conductance
@@
 $$
-\widetilde{\Phi}_n(t) = 
+\widetilde{\Phi}_{n,r}(t) = 
 \min_{\substack{S \subseteq \Csig[\Xbf] \\ \widetilde\pi(S) \leq t}} 
@@
 
-Our proof relies on a novel (to the best of our knowledge) uniform lower bound
+Our proof relies on a novel (to the best of our knowledge) lower bound
 on this conductance function over $G_{n,r}$ in terms of a population-level
-analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
+analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}, and define formally in the supplementary document.
+\begin{lemma}
+	\label{lem: consistency_of_conductance_function_main}
+	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
+	\begin{equation}
+	\label{eqn: pointwise_consistency_of_conductance_function}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\left\{\widetilde{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
+	\end{equation}
+	where $c_d$ is the same as in Theorem \ref{thm: inverse_mixing_time_lower_bound}.
+\end{lemma}
+Plugging
 \smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
@@
 
-For PPR to successfully recover density clusters, the ratio
-$\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.  Let us
+For \pprspace to successfully recover density clusters, the ratio
+$\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ should be small.  Let us
 introduce the following notation for the upper bounds in Theorems 
@@
 &= \left(d \log \mu + c_{\lambda} \right) \cdot \\ 
-& \left(c_1 + c_2
+& \left(c_1 + 9^d c_2
   \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + 
@@
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty.$ Letting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ be given by
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
+Then, setting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ to be
 	\begin{align*}
@@
 \begin{remark}
-	For convenience and maximum generality, we define $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to correspond with the bound given by \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, and assume only \ref{asmp: cluster_separation} - \ref{asmp: low_noise_density}.
-However, if we additionally have \ref{asmp: convex}, then we could sharpen $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to the tighter rate of \eqref{eqn: inverse_mixing_time_lower_bound}, with nothing changing hereafter.
+	For convenience and maximum generality, we define $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to correspond with the bound given by \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, and assume only \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter}.
+However, if we additionally have \ref{asmp: convex}, then we could sharpen $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to the tighter rate of \eqref{eqn: inverse_mixing_time_lower_bound}, with no other changes to subsequent results.
 \end{remark}
@@
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg: ppr} satisfy \ref{eqn: initialization} with respect to some $\Csig[\Xbf]$, we say the algorithm is  \emph{well-initialized}.
+	If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn: initialization} with respect to some $\Csig[\Xbf]$, we say the algorithm is  \emph{well-initialized}.
 \end{definition}
@@
 	\label{eqn: kappa2_ub}
-	\kappa_2 \leq \frac{1}{40 \cdot 36} \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)}.
+	\kappa_2 \leq \frac{1}{40 \cdot 36} \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)},
 	\end{equation}
@@
 \begin{remark}
-	We note that larger constants than $40 \cdot 36$ allow for wider range of the parameters in $\eqref{eqn: initialization}$. 
+	We note that replacing $40 \cdot 36$ by larger constants in \eqref{eqn: kappa2_ub} allow for wider ranges of parameters in \eqref{eqn: initialization}. 
 \end{remark}
@@
 In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
-Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut and symmetric set difference of $\widehat{C}$.
+Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut of $\widehat{C}$ and the (volume-weighted) symmetric set difference of $\widehat{C}$ and $\Csig[\Xbf]$.
 
-We collect some of the main results of \cite{zhu2013} in Lemma \ref{lem: ppr_cluster}.
-
-For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.r
-\begin{lemma}[PPR clustering]
-	\label{lem: ppr_cluster}
+We collect some of the main results of \cite{zhu2013} in Theorem \ref{thm: ppr_cluster}.
+For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
+\begin{theorem}[Theorem 1 of \cite{zhu2013}]
+	\label{thm: ppr_cluster}
 	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
@@
 	\begin{align*}
-	\vol(\widehat{C} \setminus A) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
+	\vol(\widehat{C} \setminus A; G) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
+	\vol(A \setminus \widehat{C}; G)  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
 	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
 	\end{align*}
-\end{lemma}
+\end{theorem}
 
-Corollary \ref{cor: ppr_cluster} immediately follows.
+Corollary \ref{cor: ppr_cluster} -- an analogous statement to Theorem \ref{thm: ppr_cluster} but stated specifically with respect to $\Csig[\Xbf]$-- immediately follows.
 \begin{corollary}
@@
 	\begin{align*}
-	\vol(\widehat{C} \setminus \Csig[\Xbf]), \vol(\Csig[\Xbf] \setminus \widehat{C})  & \leq 30 \kappa_1(\Cset) \vol(\Csig[X]) \\
-	\Phi_{n,r}(\widehat{C}) & = O\left(\kappa_2(\Cset)\right)
+	\vol(\widehat{C} \setminus \Csig[\Xbf]; G_{n,r})  & \leq 30 \kappa_2(\Cset) \vol(\Csig[\Xbf]) \\
+	\vol(\Csig[\Xbf] \setminus \widehat{C}; G_{n,r}) & \leq 30 \kappa_2(\Cset) \vol(\Csig[\Xbf]) \\
+	\Phi_{n,r}(\widehat{C}) & = O\left(\kappa_1(\Cset)\right)
 	\end{align*}
@@
 
-\section{Examples}
-\label{section: examples}
+\section{Empirical Performance of PPR on Gaussian Mixture Models}
+\label{sec: experiments}
 
-Example 1 is intended to show how the machinery developed above translates in a specific, common mixture model, and the extent to which bounds are (or are not) tight.
-Example 2 \textcolor{red}{will try to} delve into some of the details of how \pprspace interpolates the conductance and density cut, and will show a case where a poorly conditioned density cluster is not recovered by \pprspace.
-Example 3 will emphasize finite sample cluster recovery, for a well-conditioned but non-convex mixture model
+The assumptions and theory of Section \ref{sec: cluster_quality_bounds} -- and therefore Section \ref{sec: consistent_cluster_estimation_with_ppr} as well-- are tailored towards density functions with sharp transitions in gradient around the perimeter of the density cluster.
+These type of functions will satisfy \ref{asmp: bounded_density} with a small ratio of $\Lambda_{\sigma}$ to $\lambda_{\sigma}$, while still satisfying \ref{asmp: low_noise_density}, potentially for $\gamma << 1$.
 
-Examples 1 and 2 should be thought of as shedding light on the population performance of \ppr, whereas Example 3 shows performance on a finite sample.
+\begin{figure*}
+	\begin{center}
+		\centerline{\includegraphics[width=\columnwidth, height = 3 in]{graphic_1}}
+		\caption{Algorithm \ref{alg: ppr} run over 4 example datasets.
+Parameters $\alpha$ and $\pi_0$ were tuned to minimize normalized cut of output set.
+Colors represent \pprspace cuts; shapes correspond to the maximum density among mixture components.
+Sample size $n = 400$.}
+		\label{fig: graphic_1}
+	\end{center}
+\end{figure*}
 
-\begin{enumerate}
-	\item 
-	\textit{Gaussian Mixture Model:} 
-	We will compute optimal $\Phibf$ and $\Psibf$ for given $\lambda$, and show the following
-	\begin{itemize}
-		\item A graph comparing $\Phibf$ to $\Phi_{n,r}$ as the value of $\lambda$ changes.
-		\item A graph comparing $\Psibf$ to $\Psi_{n,r}$ as the value of $\lambda$ changes.
-		\item That for some values of $\lambda$, the conditions required for Theorem \ref{thm: consistent_recovery_of_density_clusters} hold.
-	\end{itemize}
+As mentioned previously, one line of work on spectral algorithms assesses their performance on mixture models.
+Particularly well-developed is the characterization of clustering performance on Gaussian Mixture Models (GMMs).
+Gaussian Mixture Models have smooth derivatives, and are therefore not good candidates for our work (at least, for reasonable values of the parameters in \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} ).
+Since they are a classical choice in the clustering literature, we investigate \pprspace performance on them empirically.
 
-	\item
-	\textit{Thin and long parallel clusters, with $\epsilon$-uniform noise: }
-	We will \textcolor{red}{(try to)} show that the set outputted by \pprspace interpolates between the minimum normalized cut solution (fatter) and the density cluster (thinner).
-The \emph{conductance} is
+Figure \ref{fig: graphic_1} shows data generated from four different Gaussian mixture models.
+The story follows roughly the same narrative as our theoretical work.
+The left two plots demonstrate instances, in one and two-dimensions, respectively, where the \pprspace cut has small error relative to a density cut.
+The right two plots, by contrast, show \pprspace failing to recover, even approximately, a density cut.
+
+In the top right panel, the leftmost density cluster has a smaller cutsize than the set \pprspace ultimately recovers.
+However, the recovered set (colored in blue) has a higher volume, and therefore a lower normalized cut.
+
+The bottom right panel shows the effect of a high diameter on the performance of \pprspace.
+Although any one vertex on the boundary of a density level set may have few cut edges, the length of the boundary is sufficiently long to make the entire cut too large for \pprspace to select it.
+Instead, the \pprspace cut defaults to a more geometrically compact shape, which has much smaller (unweighted) perimeter.
+
+We also wish to investigate the robustness of these results to clustering problems with differing levels of difficulty. Consider the following mean vector and covariance matrices
+\begin{align*}
+(\bm{\mu}_1, \bm{\mu}_2) & = \bigl((0,0), (\theta,\theta) \bigr) \\
+\bm{\Sigma}^{(1)} & = 
+\begin{bmatrix}
+1/64 & 0 \\
+0 & 1/64
+\end{bmatrix} \\
+\bm{\Sigma}^{(2)} & = 
+\begin{bmatrix}
+9/128 & -7/128 \\
+-7/128 & 9/128
+\end{bmatrix}.
+\end{align*}
+For a given choice of $\theta$, let $f_1^{(\theta)}$ and $f_2^{(\theta)}$ be two-component Gaussian mixture densities supported on $\Reals^2$, defined as
+\begin{align*}
+f_1^{(\theta)}(x) & = \frac{1}{2} \phi_{\bm{\mu}_1,\bm{\Sigma}^{(1)}}(x) + \frac{1}{2} \phi_{\bm{\mu}_2;\bm{\Sigma}^{(1)}}(x) ~~ (\text{isotropic model}) \\
+f_2^{(\theta)}(x) & = \frac{1}{2} \phi_{\bm{\mu}_1,\bm{\Sigma}^{(2)}}(x) + \frac{1}{2} \phi_{\bm{\mu}_2,\bm{\Sigma}^{(2)}}(x) ~~  (\text{anisotropic model})
+\end{align*}
+where $\phi_{\bm{\mu},\bm{\Sigma}}(x)$ is the bivariate Gaussian density with mean vector $\bm{\mu}$ and covariance matrix $\bm{\Sigma}$, evaluated at $x$.
+
+For a given value of $\theta$ we can compute the symmetric set difference between the output of Algorithm \ref{alg: ppr}, initialized near the origin, and the \emph{oracle clusters}
+\begin{align*}
+C_1^{(\theta)} & = \set{x: \phi_{\bm{\mu}_1,\bm{\Sigma}^{(1)}}(x) \geq \phi_{\bm{\mu}_2;\bm{\Sigma}^{(1)}}(x)} \\
+C_2^{(\theta)} & = \set{x: \phi_{\bm{\mu}_1,\bm{\Sigma}^{(2)}}(x) \geq \phi_{\bm{\mu}_2;\bm{\Sigma}^{(2)}}(x)}
+\end{align*}
+(While these oracle clusters are not precisely density clusters as we have defined them, they exhibit similar behavior.)
+For a sequence of $\theta$, we generate data from, for instance, density $f_i^{(\theta)}$, run Algorithm \ref{alg: ppr} (with hyperparameters tuned for lowest normalized cut) with output set $\widehat{C}_i$, and compute the symmetric set difference
 \begin{equation*}
-	\Phi^{\star}(G_{n,r}) := \min_{C \subseteq \Xbf} \Phi_{n,r}(C)
+\Delta(\widehat{C}_i, C_i^{(\theta)}) = \max\left\{\frac{\abs{C_i^{(\theta)} \setminus \widehat{C}_i}}{\abs{C_i^{\theta}}}, \frac{\abs{\widehat{C}_i \setminus C_i^{\theta}}}{|\widehat{C}_i|} \right\}.
 \end{equation*}
-	and the conductance cut is $C^{\star} \subseteq \Xbf$ which achieves the minimum.
-
-	We will show that
-	\begin{itemize}
-		\item For sufficiently small $\epsilon$, all three of the conductance cut, \pprspace cut, and density cut agree.
-		\item For an intermediate value of $\epsilon$, the conductance cut and the density cut disagree. The \pprspace cut interpolates between the two.
-		\item For a sufficiently large value of $\epsilon$, the \pprspace cut fails to recover the density cut, and draws closer to the conductance cut.
-	\end{itemize}
-
-	\item 
-	\textit{Non-convex mixture model:} We will show that, for well-conditioned non-convex mixture model, and a finite sample size $n$, cluster recovery is achieved with high probability over repeated simulations.
-\end{enumerate}
+Figure \ref{fig: graphic_2} plots the relationship between $\sqrt{2}\theta = \norm{\bm{\mu_2} - \bm{\mu_1}}_2$ and the symmetric set difference $\Delta(\widehat{C}_i, C_i^{(\theta)})$ for $i = 1,2$.
+As we can see, for sufficiently large values of $\theta$, \pprspace agrees with the oracle cluster in both the isotropic and anisotropic GMM models, while for sufficiently small values of $\theta$ it fails to even approximately recover the oracle cluster in either case.
+Throughout, the performance is superior for the isotropic model as opposed to the anisotropic one, as we would expect.
+\begin{figure}[!tb]
+	\vskip 0.2in
+	\begin{center}
+		\centerline{\includegraphics[width=\columnwidth, height = 3 in]{graphic_2}}
+		\caption{Symmetric set difference of Algorithm \ref{alg: ppr} run over GMM models with isotropic and anistropic component densities, as the distance between cluster centers changes.}
+		\label{fig: graphic_2}
+	\end{center}
+	\vskip 0.2in
+\end{figure}
 
@@
 Concretely, we might wish to generalize our results to hold over a wider range of kernel functions, and hyperparameter inputs to the \pprspace algorithm.
-More broadly, we do not provide any sort of theoretical lower bound, although we give empirical evidence in Example 2 that poorly conditioned density clusters are not consistently estimated by \pprspace.
-Example 2 also hints at a way of understanding local spectral algorithms -- or, at least, \ppr-- as interpolating between normalized and density cut.
-Exploring this connection is an avenue for future work.
+More broadly, we do not provide any sort of theoretical lower bound, although we give empirical evidence in Figures \ref{fig: graphic_1} and \ref{fig: graphic_2} that poorly conditioned density clusters are not consistently estimated by \pprspace.
+
+The initial motivation for this article was based on the intuition that density level sets, in the right conditions, will have small normalized cut.
+As a result, algorithms with normalized cut based guarantees (such as \pprspace) seemed likely to have density cluster recovery guarantees as well.
+However, the second-order behavior of \pprspace when failing to recover the conductance cut is also of interest.
+Are there situations when the conductance cut and density cut differ, yet \pprspace still recovers the latter?
+This is an open question.
 

### 2019-01-23 icml/icml_local_density_clustering_supplement.tex
final icml version

@@
 \usepackage{booktabs}
-%\usepackage{hyperref}
 \usepackage{amsmath}
@@
 \usepackage{xr-hyper}
+% \usepackage{hyperref}
 \usepackage{bm}
@@
 \newcommand{\wf}{\widetilde{f}}
+\newcommand{\wDbf}{\widetilde{\Dbf}}
 
@@
 \ref{sec: non_convex_conductance_function_and_local_spread} and \ref{sec: inverse_mixing_time_lower_bound_nonconvex} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, while \ref{sec: convex_population_conductance_function}- \ref{sec: inverse_mixing_time_lower_bound} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}.
+\ref{sec: concentration} gives some general concentration results used throughout, before we finish with the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} in \ref{sec: proof_of_consistent_cluster_recovery}.
 
@@
 
-Fix $\delta \in (0,1]$ and let $\delta' = \delta/2$. Noting that $\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\vol_{n,r}}$, some trivial algebra gives us the expression
+Fix $\delta \in (0,1]$ and let $\delta' = \delta/2$.
+For sufficiently large $n$, note that by \eqref{eqn: weighted_cluster_volume}, $\vol_{n,r} \leq 1 - \vol_{n,r}$ with probability at least $1 - \delta$, and therefore $\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\vol_{n,r}}$.
+Some trivial algebra gives us the expression
 \begin{equation}
@@
 \begin{equation*}
-\tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
-\end{equation*}
+\tau_{\infty}(\qbf; G) := \tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
+\end{equation*}
+where we include the extra dependency on $\qbf$ as we will need to consider mixing of various random walks.
 
@@
 	\label{eqn: consistency_of_stepapprox_conductance_function}
-	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \min\left\{\overline{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
+	\liminf_{n \to \infty} \overline{\Phi}_{n,r}(t) \geq \min\left\{\overline{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
 	\end{equation}
@@
 \subsection{Concentration inequalities}
-
+\label{sec: concentration}
 Given a symmetric kernel function $k: \mathcal{X}^m \to \Reals$, and data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$m$ $U$ statistic} to be 
@@
 
+Let $\pbf = (p_u)_{u \in \Xbf}$ denote the \pprspace vector computed over $G_{n,r}$ (where for ease of reading we suppress dependence on the hyperparameter $\alpha$ and seed node $v$.) 
+Recalling that $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$, we write $\widetilde{\pi}_{n,r}(u)$ to denote the stationary distribution evaluated at $u \in \Csig[X]$.
+
+\subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
+\label{sec: proof_of_consistent_cluster_recovery}
+
+Lemma \ref{lem: setup} formalizes the intuitively sensible statement that \pprspace, can be uniformly lower bounded over clusters with small mixing time relative to their normalized cut.
+Importantly, it adds a corresponding upper bound for \pprspace outside of these clusters.
+\begin{lemma} 
+	\label{lem: setup}
+	Consider running Algorithm \ref{alg: ppr} with any $r < \sigma$ and
+
+	\begin{equation} 
+	\label{eqn: upper_bound_alpha}
+	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
+	\end{equation}
+
+	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ such that the following statements hold for all $v \in \Csig[\Xbf]^g$:
+	\begin{itemize}
+		\item For all $u \in \Cset[\Xbf]$,
+		\begin{equation}
+		\label{eqn: lower_bound_PPR_in_cluster}
+		p_u \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
+		\end{equation}
+		\item For all $u' \in \Csig'[\Xbf]$,
+		\begin{equation}
+		\label{eqn: upper_bound_PPR_in_other_cluster}
+		p_{u'} \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
+		\end{equation}
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+	We will write $\Wbf_n = \Dbf_n \Abf_n^{-1}$ for the transition probability matrix over $G_{n,r}$, and let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
+
+	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
+	\begin{align*}
+	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}) \\
+	\ell & := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t \\
+	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c) \\
+	s & := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t
+	\end{align*}
+	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is a diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
+
+	Roughly, the proof will unfold in four steps.
+The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).
+
+	\begin{enumerate}
+		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to produce the lower bound 
+		\begin{equation*}
+		\pbf(u) \geq 4/5 \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
+		\end{equation*}
+		where 
+		\begin{equation*}
+		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
+		\end{equation*}
+		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.
+
+		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $G_{n,r} / \Csig[\Xbf]$.
+Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
+This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
+		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
+		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$.
+Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
+Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$.
+This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
+	\end{enumerate}
+
+	\paragraph{Step 1}
+	We will begin by restating some results of \cite{zhu2013}.
+
+	For seed node $v$, we write
+	\begin{align} \label{eqn: page_rank_body}
+	\widetilde{\pbf}_v & = \alpha e_v + (1 - \alpha) \widetilde{\pbf}_v \widetilde{\Wbf}_n \\
+	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{\Wbf}_n^t \right)
+	\end{align}
+
+	From Lemma 3.1 of \cite{zhu2013} we have that there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ for all $v \in \Csig[\Xbf]^g$, $u \in \Csig[\Xbf]$
+
+	\begin{align} \label{eqn: zhu_body}
+	p_u & \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u) \nonumber \\
+	||\ell||_1 & \leq \frac{2 \widetilde{\Phi}_{n,r}}{\alpha}
+	\end{align}
+	where $\widetilde{\pbf}_v = (\widetilde{\pbf}_v(u))$ and likewise for $\widetilde{\pbf}_{\ell} = (\widetilde{\pbf}_{\ell}(u))$.
+(This will be the only time we need to restrict ourselves to this 'good set'.)
+
+	Moreover if, as we have specified, $\alpha \leq \widetilde{\Psi}_{n,r}/9$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
+	\begin{equation} \label{eqn: page_rank_mixes}
+	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u).
+	\end{equation}
+
+	\paragraph{Step 2}
+
+	We turn to upper bounding $\widetilde{\pbf}_{\ell}(u)$. For any $u \in \Cset[\Xbf]$, we have
+
+	\begin{align} \label{eqn: leakage_page_rank_body}
+	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
+	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{\widetilde{D}_{\min}} 
+	\end{align}
+
+	where we use $\left(\ell \widetilde{\Wbf}_n^t \right)(u)$ to denote $\ell \widetilde{\Wbf}_n^te_u$.
+
+	$\text{(i)}$ follows from the fact that since $r < \sigma$, $\cut(\Cset[\Xbf], G_{n,r} / \Csig[\Xbf]; G_{n,r}) = 0$. Therefore $(\Dbf_n^{-1})_{uu} (\widetilde{\Dbf}_n)_{uu} = 1$, and as a result
+	\begin{equation*}
+	(\ell \widetilde{\Wbf}_n^0)(u) = \ell(u) = 0.
+	\end{equation*}
+	To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^{t-1}$. Then
+
+	\begin{align*}
+	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u) & = \left(q \widetilde{\Wbf}_n \right)(u) \\
+	& \leq \|q\|_1 \|\widetilde{\Wbf}_{\cdot u}\|_{\infty} \\
+	& \overset{\text{(iii)}}{\leq} \frac{1}{\widetilde{D}_{\min}}.
+	\end{align*}
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}_n$.
+$\text{(iii)}$ then follows from the fact that any vertex in $\Cset[\Xbf]$ is connected only to vertices in $\Csig[\Xbf]$, and therefore every entry of $\widetilde{\Wbf}_{\cdot u}$ is either $0$ or at most $1 / \widetilde{D}_{\min}$.
+
+	Combined, (\ref{eqn: leakage_page_rank_body}), (\ref{eqn: page_rank_mixes}), and \eqref{eqn: zhu_body} imply
+	\begin{equation*}
+	p_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - 18\frac{ \Phi_{n,r}(\Csig[\Xbf])}{\widetilde{D}_{\min} \alpha}.
+	\end{equation*}
+	for any $v \in \Csig[\Xbf]$.
+
+	\paragraph{Step 3}
+	To get the corresponding upper bound on $p_v(u')$, we will use the soakage vectors $s$ and $s_t$.
+We will first argue that $s$ is a worse starting distribution -- meaning it puts uniformly more mass outside the cluster -- than simply starting at $v$.
+
+	\begin{lemma} \label{lem: gained mass is soaked_body}
+		For all $u' \notin \Csig[\Xbf]$,
+		\begin{equation}
+		\pbf_v(u') \leq \pbf_{s}(u').
+		\end{equation}
+	\end{lemma}
+
+	\begin{proof}
+
+		We have
+		\begin{align*}
+		\pbf_v(u') & = \alpha \sum_{T=0}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u)\\
+		& \overset{(i)}{=} \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u')
+		\end{align*}
+
+		where $(i)$ follows from $v \in \Csig$ , $u \not\in \Csig$ and therefore $e_v(u) = 0$.
+
+		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
+		\begin{lemma}
+			\label{lem: sum_of_soakages}
+
+			Let $G = (V,E)$ be a graph, with associated random walk matrix $W$.
+
+			For any $T \geq 1$, $q$ vector, $S \subset V$, and $s_t = s_t(S^c,q)$
+			\begin{equation}
+			qW^T = \sum_{t = 0}^{T - 1} s_t W^{T - t - 1} + q(W I_S)^T
+			\end{equation}
+		\end{lemma}
+		We prove Lemma \ref{lem: sum_of_soakages} after completing the proof of Lemma \ref{lem: gained mass is soaked_body}.
+
+		Now, along with the fact $u \not\in \Csig$, we have
+
+		\begin{equation*}
+		\left(e_v \Wbf_n^T \right)(u') = \sum_{t = 0}^{T - 1} \left(s_t \Wbf_n^{T - t - 1} \right)(u')
+		\end{equation*}
+
+		and so
+
+		\begin{align*}
+		\pbf_v(u) & = \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u') \\
+		& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u')\\
+		& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+		& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+		& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u') \\
+		& = \pbf_s(u')
+		\end{align*}
+	\end{proof}
+
+	\begin{proof}[Proof of Lemma \ref{lem: sum_of_soakages}]
+		Proceed by induction. When $T = 1$,
+
+		\begin{align*}
+		qW & = q(WI_S) + q(WI_{S^c}) \\
+		& = q(W I_S)^T + s_0 
+		\end{align*}
+
+		Assume true for $T_0$. For $T = T_0 + 1$,
+
+		\begin{align*}
+		qW^T & = qW^{T_0}W \\
+		& = \left\{ \sum_{t = 0}^{T_0 - 1} s_t W^{T_0 - 1 - t} + q(WI_S)^{T_0} \right\} W \\
+		& =  \sum_{t = 0}^{T_0 - 1} s_t W^{T - 1 - t} + q(WI_S)^{T_0}(WI_S + WI_{S^c}) \\
+		& =  \sum_{t = 0}^{T - 1} s_t W^{T - 1 - t} + q(WI_S)^{T}
+		\end{align*}
+	\end{proof}
+
+	\paragraph{Step 4}
+
+	Just as we upper bounded the probability mass $\widetilde{\pbf}_{\ell}$ could assign to any one vertex, we can upper bound
+
+	\begin{align} \label{eqn: soakage_page_rank_body}
+	\pbf_{s}(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t \right)(u') \nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1} {\Wbf}_n^t \right)(u')\nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  {\Wbf}_n^t \right)(u')\nonumber \\
+	& \leq \|s\|_1 \frac{1}{\widetilde{D}_{\min}}.
+	\end{align}
+
+	Finally, letting $q_t = e_v (\Wbf_n \widetilde{\mathbf{I}}_n)^t$ for ease of notation, we have
+	\begin{align*}
+	\|s_t\|_1 & = \|q_t (\Wbf_n \widetilde{\mathbf{I}}_n)\|_1 \\
+	& = \sum_{u' \in \Xbf} \sum_{u \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n)(u, u')\\
+	& = \sum_{u' \in \Xbf / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1(e_{u,u'} \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
+	& = \|q_t (I - \Dbf_n^{-1} \widetilde{\Dbf}_n)\|_1 = \|\ell_t\|_1.
+	\end{align*}
+
+	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
+
+\end{proof}
+
+\begin{lemma}
+	\label{lem: ball_bounds_in_probability}
+	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
+	\begin{align*}
+	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
+	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
+	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
+	\end{align*}
+	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
+\end{lemma}
+
+The statement follows immediately from Lemma \ref{lem: ball_bounds}.
+
+\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
+
+We note that by Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, 
+\begin{equation*}
+\kappa_2(\Cset) \geq \frac{\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])}.
+\end{equation*}
+As a result Lemma \ref{lem: setup} implies
+\begin{align}
+\label{eqn: theorem_4_1}
+p_u & \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~ (u \in \Cset[\Xbf]) \nonumber \\
+p_{u'} & \leq \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~~~~~~~~~~~~~~~~ (u' \in \Cset'[\Xbf])
+\end{align}
+
+We turn to bounding $\widetilde{\pi}_{n,r}(u)$. Clearly,
+\begin{align*}
+\widetilde{\pi}_{n,r}(u) & \geq \frac{\widetilde{D}_{\min}}{\widetilde{\vol}_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{\widetilde{D}_{\min}}{\wn \widetilde{D}_{\max}}.
+\end{align*}
+Application of Lemma \ref{lem: ball_bounds_in_probability} then yields
+\begin{equation}
+\label{eqn: theorem_4_2}
+\widetilde{\pi}_{n,r}(u) \geq 8 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
+\end{equation}
+as well as
+\begin{equation}
+\label{eqn: theorem_4_3}
+\frac{1}{\widetilde{D}_{\min}} \leq \frac{2}{\nu_d r^d \lambda_{\sigma}}
+\end{equation}
+with probability tending to $1$ as $n \to \infty$, for all $u \in \Cset[\Xbf]$ (indeed, all $u \in \Csig[\Xbf]$.)
+
+Combining \eqref{eqn: theorem_4_1}, \eqref{eqn: theorem_4_2} and \eqref{eqn: theorem_4_3}, along with the requirement on $\kappa_2(\Cset)$ given by \eqref{eqn: kappa2_ub}, we have
+\begin{align*}
+p_u & \geq 3/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2} \\
+p_{u'} & \leq 1/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
+\end{align*}
+for any $u \in \Cset$, $u' \in \Cset'$.
+As a result, if $\pi_0 \in (2/5, 3/5)\cdot \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}$, as $n \to \infty$ with probability tending to one any sweep cut of the form of \eqref{eqn: sweep_cuts}, including the output set $\widehat{C}$, will successfully recover $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+
 \clearpage

### 2019-01-23 icml/proof_of_theorem_4.tex
final icml version

@@
 Let $\pbf = (p_u)_{u \in \Xbf}$ denote the \pprspace vector computed over $G_{n,r}$ (where for ease of reading we suppress dependence on the hyperparameter $\alpha$ and seed node $v$.) 
+Recalling that $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$, we write $\widetilde{\pi}_{n,r}(u)$ to denote the stationary distribution evaluated at $u \in \Csig[X]$.
 
@@
 		\item For all $u \in \Cset[\Xbf]$,
-		\begin{equation*}
+		\begin{equation}
+		\label{eqn: lower_bound_PPR_in_cluster}
 		p_u \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
-		\end{equation*}
+		\end{equation}
 		\item For all $u' \in \Csig'[\Xbf]$,
-		\begin{equation*}
+		\begin{equation}
+		\label{eqn: upper_bound_PPR_in_other_cluster}
 		p_{u'} \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
-		\end{equation*}
+		\end{equation}
 	\end{itemize}
@@
 \begin{proof}
+	We will write $\Wbf_n = \Dbf_n \Abf_n^{-1}$ for the transition probability matrix over $G_{n,r}$, and let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
 
-	For $S \subseteq X_1^n$, let $I_{S}$ be a diagonal matrix where $I_{jj} = 1$ if $X_j \in S$ and 0 otherwise.
-Let $D_S$ be the corresponding degree matrix for the subgraph induced by $S$.
-$D_S$ is a diagonal matrix where for $X_j \in S$, $(D_S)_{jj} = \sum_{i: X_i \in S} A_{ij}$, and if $X_j \not \in S$ then $(D_S)_{jj} = 0$.
-Then, define \textit{leakage} and \textit{soakage} vectors
-
+	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
 	\begin{align*}
-	\ell_t & := e_v  (W I_{\Csig[\Xbf]})^t (I - D^{-1} D_{\Csig[\Xbf]}) \\
+	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}) \\
 	\ell & := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t \\
-	s_t & := e_v (W I_{\Csig[\Xbf]})^t (W I_{G / \Csig[\Xbf]}) \\
+	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c) \\
 	s & := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t
 	\end{align*}
+	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is a diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
 
@@
 	\begin{enumerate}
-		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to lower bound $p_v(u) \geq 4/5 \widetilde{\pi}(u) - \widetilde{p}_{\ell}(u)$, where $\widetilde{p}$ is the PPR random walk over the subgraph induced by $\Csig[\Xbf]$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$.
-		\item Since $r < \sigma$, there are no edges between $u$ and $G / \Csig[\Xbf]$.
-Therefore, the page-rank vector $\widetilde{p}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
-This will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
-		\item For vertices $u' \in G / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]pr$.
-		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]prthick$.
+		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to produce the lower bound 
+		\begin{equation*}
+		\pbf(u) \geq 4/5 \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
+		\end{equation*}
+		where 
+		\begin{equation*}
+		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
+		\end{equation*}
+		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.
+
+		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $G_{n,r} / \Csig[\Xbf]$.
+Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
+This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
+		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
+		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$.
 Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
 Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$.
-This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Proposition \ref{thm: setup}.
+This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
 	\end{enumerate}
@@
 	\paragraph{Step 1}
-	We will begin by restating the results of \cite{zhu2013}.
+	We will begin by restating some results of \cite{zhu2013}.
 
-	Denote by $\widetilde{p}$ the PageRank vector computed only over the subgraph induced by $\Csig[\Xbf]$.
-
+	For seed node $v$, we write
 	\begin{align} \label{eqn: page_rank_body}
-	\widetilde{p}_v & = \alpha e_v + (1 - \alpha) \widetilde{p}_v \widetilde{W} \\
-	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{W}^t \right)
+	\widetilde{\pbf}_v & = \alpha e_v + (1 - \alpha) \widetilde{\pbf}_v \widetilde{\Wbf}_n \\
+	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{\Wbf}_n^t \right)
 	\end{align}
-
-	and correspondingly for the leakage vector
-
-	\begin{equation*}
-	\widetilde{p}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{p}_{\ell} \widetilde{W}.
-	\end{equation*}
 
@@
 
-	\begin{equation*} \label{eqn: zhu_body}
-	p_v(u) \geq \widetilde{p}_v(u) - \widetilde{p}_{\ell}(u).
-	\end{equation*}
+	\begin{align} \label{eqn: zhu_body}
+	p_u & \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u) \nonumber \\
+	||\ell||_1 & \leq \frac{2 \widetilde{\Phi}_{n,r}}{\alpha}
+	\end{align}
+	where $\widetilde{\pbf}_v = (\widetilde{\pbf}_v(u))$ and likewise for $\widetilde{\pbf}_{\ell} = (\widetilde{\pbf}_{\ell}(u))$.
 
-	with $||\ell||_1 \leq \frac{2 \Phi^{btw}(\Csig[\Xbf])}{\alpha}$.
-Moreover if, as we have specified, $\alpha \leq \frac{1}{9 T_{\infty}(\Csig[\Xbf])}$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
-
+	Moreover if, as we have specified, $\alpha \leq \widetilde{\Psi}_{n,r}/9$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
 	\begin{equation} \label{eqn: page_rank_mixes}
-	\widetilde{p}_v(u) \geq \frac{4}{5} \widetilde{\pi}(u).
+	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u).
 	\end{equation}
@@
 
-	We turn to upper bounding $\widetilde{p}_{\ell}(u)$. We have
+	We turn to upper bounding $\widetilde{\pbf}_{\ell}(u)$. For any $u \in \Cset[\Xbf]$, we have
 
 	\begin{align} \label{eqn: leakage_page_rank_body}
-	\widetilde{p}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{W}^t \right)[u]  \nonumber \\
-	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
-	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
-	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{d_{\min}(\Csig[\Xbf])} 
+	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
+	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{\widetilde{D}_{\min}} 
 	\end{align}
 
-	where $\text{(i)}$ follows from the fact that since $r < \sigma$, $E(\Cset'[\Xbf], G / \Csig[\Xbf]) = 0$ and therefore $\ell(u) = 0$.
-To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{W}^{t-1}$, and then
+	where we use $\left(\ell \widetilde{\Wbf}_n^t \right)(u)$ to denote $\ell \widetilde{\Wbf}_n^te_u$.
+
+	$\text{(i)}$ follows from the fact that since $r < \sigma$, $\cut(\Cset'[\Xbf], G_{n,r} / \Csig[\Xbf]; G_{n,r}) = 0$. Therefore $(\Dbf_n^{-1})_{uu} (\widetilde{\Dbf}_n)_{uu} = 1$, and as a result
+	\begin{equation*}
+	(\ell \widetilde{\Wbf}_n^0)(u) = \ell(u) = 0.
+	\end{equation*}
+	To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^{t-1}$. Then
 
 	\begin{align*}
-	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{W}^t \right)[u] & = \left(q W \right)[u] \\
-	& \leq \|q\|_1 \|W(\cdot, u)\|_{\infty} \\
-	& \overset{\text{(iii)}}{\leq} \frac{1}{d_{\min}(C^{\sigma}_n)}.
+	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u) & = \left(q \widetilde{\Wbf}_n \right)(u) \\
+	& \leq \|q\|_1 \|\widetilde{\Wbf}_{\cdot u}\|_{\infty} \\
+	& \overset{\text{(iii)}}{\leq} \frac{1}{\widetilde{D}_{\min}}.
 	\end{align*}
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}_n$.
+$\text{(iii)}$ then follows from the fact that any vertex in $\Cset[\Xbf]$ is connected only to vertices in $\Csig[\Xbf]$, and therefore every entry of $\widetilde{\Wbf}_{\cdot u}$ is either $0$ or at most $1 / \widetilde{D}_{\min}$.
 
-	where $\text{(iii)}$ comes from the fact that $\|u-v\| \leq r$ means $v \in \Csig[\Xbf]$.
-	Combining (\ref{eqn: leakage_page_rank_body}) with (\ref{eqn: page_rank_mixes}), and since $||\ell||_1 \leq 2 \frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$, we have
-
+	Combined, (\ref{eqn: leakage_page_rank_body}), (\ref{eqn: page_rank_mixes}), and \eqref{eqn: zhu_body} imply
 	\begin{equation*}
-	p_v(u) \geq \frac{4}{5} \widetilde{\pi}(u) - 2\frac{9 \Phi^{btw}(\Csig[\Xbf])}{d_{\min}(\Csig[\Xbf]) \alpha}.
+	p_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - 18\frac{ \widetilde{\Phi}_{n,r}}{\widetilde{D}_{\min} \alpha}.
 	\end{equation*}
@@
 		\begin{equation}
-		p_v(u') \leq p_{s}(u').
+		\pbf_v(u') \leq \pbf_{s}(u').
 		\end{equation}
@@
 
-	The proof of Lemma \ref{lem: gained mass is soaked_body} is left to the supplement.
-It follows largely the same steps as Lemma 3.1 of \cite{zhu2013}, except over $G / \Csig[\Xbf]$ rather than $\Csig[\Xbf]$.
+	\begin{proof}
+
+	We have
+	\begin{align*}
+	\pbf_v(u') & = \alpha \sum_{T=0}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u)\\
+	& \overset{(i)}{=} \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u')
+	\end{align*}
+
+	where $(i)$ follows from $v \in \Csig$ , $u \not\in \Csig$ and therefore $e_v(u) = 0$.
+
+	Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
+	\begin{lemma}
+		\label{lem: sum_of_soakages}
+
+		Let $G = (V,E)$ be a graph, with associated random walk matrix $W$.
+
+		For any $T \geq 1$, $q$ vector, $S \subset V$, and $s_t = s_t(S^c,q)$
+		\begin{equation}
+		qW^T = \sum_{t = 0}^{T - 1} s_t W^{T - t - 1} + q(W I_S)^T
+		\end{equation}
+	\end{lemma}
+	We prove Lemma \ref{lem: sum_of_soakages} after completing the proof of Lemma \ref{lem: gained mass is soaked_body}.
+
+	Now, along with the fact $u \not\in \Csig$, we have
+
+	\begin{equation*}
+	\left(e_v \Wbf_n^T \right)(u') = \sum_{t = 0}^{T - 1} \left(s_t \Wbf_n^{T - t - 1} \right)(u')
+	\end{equation*}
+
+	and so
+
+	\begin{align*}
+	\pbf_v(u) & = \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u') \\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u')\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u') \\
+	& = \pbf_s(u')
+	\end{align*}
+	\end{proof}
+
+	\begin{proof}[Proof of Lemma \ref{lem: sum_of_soakages}]
+	Proceed by induction. When $T = 1$,
+
+	\begin{align*}
+	qW & = q(WI_S) + q(WI_{S^c}) \\
+	& = q(W I_S)^T + s_0 
+	\end{align*}
+
+	Assume true for $T_0$. For $T = T_0 + 1$,
+
+	\begin{align*}
+	qW^T & = qW^{T_0}W \\
+	& = \left\{ \sum_{t = 0}^{T_0 - 1} s_t W^{T_0 - 1 - t} + q(WI_S)^{T_0} \right\} W \\
+	& =  \sum_{t = 0}^{T_0 - 1} s_t W^{T - 1 - t} + q(WI_S)^{T_0}(WI_S + WI_{S^c}) \\
+	& =  \sum_{t = 0}^{T - 1} s_t W^{T - 1 - t} + q(WI_S)^{T}
+	\end{align*}
+	\end{proof}
 
@@
 
-	Just as we upper bounded the probability mass $\widetilde{p}_{\ell}$ could assign to any one vertex, we can upper bound
+	Just as we upper bounded the probability mass $\widetilde{\pbf}_{\ell}$ could assign to any one vertex, we can upper bound
 
 	\begin{align} \label{eqn: soakage_page_rank_body}
-	\widetilde{p}_{s}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \widetilde{W}^t \right)[u]  \nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  \widetilde{W}^t \right)[u]\nonumber \\
-	& \leq \|s\|_1 \frac{1}{d_{\min}(\Csig[\Xbf])}.
+	\pbf_{s}(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t \right)(u') \nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1} {\Wbf}_n^t \right)(u')\nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  {\Wbf}_n^t \right)(u')\nonumber \\
+	& \leq \|s\|_1 \frac{1}{\widetilde{D}_{\min}}.
 	\end{align}
 
-	Finally, by the definition of $s_t = e_v (W I_{\Csig[\Xbf]})^t (W I_{G / \Csig[\Xbf]})$, letting $q_t = e_v (W I_{\Csig[\Xbf]})^t$ for ease of notation, we have
+	Finally, letting $q_t = e_v (\Wbf_n \widetilde{\mathbf{I}}_n)^t$ for ease of notation, and writi we have
 	\begin{align*}
-	\|s_t\|_1 & = \|q_t (W I_{G / \Csig[\Xbf]})\|_1 \\
-	& = \sum_{u' \in G} \sum_{u \in G} q_t(u) (W I_{G / \Csig[\Xbf]})[u, u'] \\
-	& = \sum_{u' \in G / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q(u)}{d(u)} I(e_{u,u'} \in G) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) (d(u) - d_{\Csig[\Xbf]}(u) )}{d(u)} \\
-	& = \|q_t (I - D^{-1} D_{\Csig[\Xbf]})\|_1 = \|\ell_t\|_1.
+	\|s_t\|_1 & = \|q_t (\Wbf_n \widetilde{\mathbf{I}}_n)\|_1 \\
+	& = \sum_{u' \in \Xbf} \sum_{u \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n)(u, u')\\
+	& = \sum_{u' \in \Xbf / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1(e_{u,u'} \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
+	& = \|q_t (I - \Dbf_n^{-1} \widetilde{\Dbf}_n)\|_1 = \|\ell_t\|_1.
 	\end{align*}
 
-	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\Phi^{btw}(\Csig[\Xbf])}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
+	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
 

### 2019-03-26 notes/weekly_notes/3.13.19.NotesForWeek.tex
weekly notes updated

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}
\newcommand{\dist}{\mathrm{dist}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}
\newcommand{\Sset}{\mathcal{S}}

\newcommand{\Csig}{\Cset_{\sigma}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for the week of 3/13/19 - 3/17/19}
\author{Alden Green}
\date{\today}
\maketitle

For a given $\sigma > 0$ and some $\Cset \subset \Rd$, let $\Csig = \Cset + B(0,\sigma)$ be the $\sigma$-expansion of $\Cset$. Fix $r > 0$. Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. Consider the \emph{speedy r-ball walk}\footnote{We call it 'speedy' because it only considers moves within $\Csig$.} over $\Csig \subset \Rd$, defined by the following transition probability density function 
\begin{equation*}
\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.

Denote the stationary distribution for this Markov chain by $\pi_{\nu,r}$, which satisfies the relation \footnote{As we will see, in this case the existence of a stationary distribution for the ball walk will be easily verifiable. In order to ensure uniqueness, we could consider only the \emph{lazy} version of the ball walk. For the moment we ignore this technicality.}
\begin{equation*}
\int_{\Omega} \widetilde{P}_{\nu,r}(x; \Sset) d\pi_{\nu,r}(x) = \pi_{\nu,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
Letting the \emph{local conductance} be given by
\begin{equation*}
\ell_{\nu,r}(x) := \frac{\nu(\Csig \cap B(x,r))}{\nu(B(x,r))} \tag{$x \in \Csig$}
\end{equation*}
a bit of algebra verifies that
\begin{equation*}
\pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x)}{\int_{\Csig} \ell_{\nu,r}(x)}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}

We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\nu,r}$, defined by
\begin{equation*}
\widetilde{Q}_{\nu,r}(\Sset, \Sset') := \int_{\Sset} \widetilde{P}_{\nu,r}(x; \Sset) d\pi_{\nu,r}(x) \tag{$\Sset, \Sset' \in \mathfrak{B}(\Csig)$}
\end{equation*}
and the \emph{(continuous) conductance function}
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\nu,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} \tag{$0 < t \leq 1/2 $}
\end{equation*}

\section{Conductance over $\Csig$}
An essential step in upper bounding the mixing time over $G_{n,r}[\Csig(\Xbf)]$ is lower bounding the conductance function $\widetilde{\Phi}_{\nu,r}(t)$.

To do so, our main assumption will relate $\Csig$ to a convex set via a Lipschitz transformation $g$.

\begin{assumption}[Embedding]
	\label{asmp: embedding}
	 Assume there exists $K \subset \Rd$ convex space, and biLipschitz measure preserving mapping $g: \Rd \to \Rd$:
	\begin{equation*}
	\exists L_{\Omega},L_K > 0: \forall x,y \in K,  \frac{1}{L_K} \abs{x - y}\leq \abs{g(x) - g(y)} \leq L_{\Csig} \abs{x - y}, \det(D_x g) = 1
	\end{equation*}
	such that
	\begin{equation*}
	\Csig = g(K).
	\end{equation*}
\end{assumption}

\begin{theorem}[\textcolor{red}{Uniform continuous conductance function}]
	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and biLipschitz function $g$ with Lipschitz constants $L_{\Csig}, L_K <  \infty$. Then, for any $0 < r < 2 \sigma / \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r}(t) \geq \frac{r}{2^{10} D_K L \sqrt{d}}.
	\end{equation*}
\end{theorem}

\section{Supporting theory.}
Begin by recalling the isoperimetric inequality of \textcolor{red}{Dyer and Frieze 1991}.

\begin{theorem}[Isoperimetry of convex sets]
	\label{thm: dyer}
	Let $(R_1, R_2, R_3)$ be a partition of a convex set $\Omega \subset \Rd$. Then,
	\begin{equation*}
	\vol(R_3) \geq 2\frac{d(R_1, R_2)}{D_{K}} \min(\vol(R_1), \vol(R_2))
	\end{equation*}
\end{theorem}

The following result is from \textcolor{red}{AbbasiYadkori18}. It is an adaptation of Theorem \ref{thm: dyer} to hold in the case where $\Omega \subset \Rd$ is not convex, but is a Lipschitz embedding of a convex set in the sense of Assumption \ref{asmp: embedding}.

\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
	Let $\Omega \subset \Rd$ satisfy Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$. Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Omega$, 
	\begin{equation*}
	\vol(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{L D_{K}} \min(\vol(\Omega_1), \vol(\Omega_2))
	\end{equation*}
\end{lemma}
\begin{proof}
	For $\Omega_i, i = 1,2,3$, denote the preimage
	\begin{equation*}
	R_i = \set{x \in K: g(x) \in \Omega_i}
	\end{equation*}
	For any $x \in R_1, y \in R_2$, 
	\begin{equation*}
	\abs{x - y} \geq \frac{1}{L}\abs{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
	\end{equation*}
	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
	\begin{equation*}
	\dist(R_1, R_2) \geq \frac{1}{L} d(\Omega_1, \Omega_2).
	\end{equation*}
	By Theorem \ref{thm: dyer}, therefore
	\begin{align*}
	\vol(R_3) & \geq 2\frac{\dist(R_1, R_2)}{D_{K}} \min(\vol(R_1), \vol(R_2)) \\
	& \geq \frac{2}{D_{K} L} d(\Omega_1, \Omega_2) \min(\vol(R_1), \vol(R_2))
	\end{align*}
	and by the measure-preserving property of $g$, this implies
	\begin{equation*}
	\vol(\Omega_3) \geq\frac{2}{D_{K} L} d(\Omega_1, \Omega_2) \min(\vol(\Omega_1), \vol(\Omega_2)).
	\end{equation*}
\end{proof}

\begin{lemma}[One-step distributions]
	\label{lem: one_step_distributions}
	Let $u,v \in \Csig$ be such that 
	\begin{equation*}
	\abs{u - v} \leq \frac{\sqrt{t} r}{L_{K} L_{\Csig} \sqrt{d}}
	\end{equation*}
	for some $0 < t < 4/9$. Then,
	\begin{equation*}
	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV} \leq 1 - \frac{1}{300(9 + 8t)L_{C_{\sigma}}^d L_{K}^d}.
	\end{equation*}
\end{lemma}
\begin{proof}[\textcolor{red}{Proof of Lemma \ref{lem: one_step_distributions}}]
	Let $S_1 \cup S_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
	\begin{equation*}
	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 - \frac{1}{300(9 + 8t)L_{C_{\sigma}}^d L_{K}^d}
	\end{equation*}
	The following manipulations reduce the problem to that of lower bounding the volume of the intersection of the balls $B(u,r)$ and $B(v,r)$ within $\Csig$. They come directly from the proof of Lemma 3.6 in \textcolor{red}{Kannan 97}. 
	\begin{align*}
	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) & = 1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1)
	\end{align*}
	Denote the intersection $I := B(u,r) \cap B(u,r)$. Then we have
	\begin{equation*}
	\widetilde{P}_{\nu,r}(u; S_2) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap I)
	\end{equation*}
	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; S_1)$. As a result,
	\begin{equation}
	1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1) \geq \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
	\end{equation}

	For shorthand, let $\widetilde{\nu}(\Sset) = \nu(\Sset \cap \Csig)$. We proceed, making repeated use of Assumption \ref{asmp: embedding} along with Lemma \ref{lem: lipschitz_balls_local_conductance},
	\begin{align}
	\widetilde{\nu} \biggl( B(u,r) \cap B(v,r) \biggr) & \geq \nu \Biggl(  g\biggl(B(x, \frac{r}{L_{\Csig}}) \cap B(y, \frac{r}{L_{\Csig}}) \cap K  \biggr) \Biggr) \nonumber \\
	& = \nu \biggl(B(x, \frac{r}{L_{\Csig}}) \cap B(y, \frac{r}{L_{\Csig}}) \cap K  \biggr) \nonumber \\
	& \geq \min \left\{ \nu\biggl( B(x, \frac{r}{L_{\Csig}}) \cap K \biggr), \nu\biggl( B(y, \frac{r}{L_{\Csig}}) \cap K \biggr)  \right\} \cdot \frac{3}{9 + 8t} \label{eqn: one_step}\\
	& \geq \min \left\{ \widetilde{\nu} \biggl( B(u, \frac{r}{L_{\Csig} L_K}) \biggr), \widetilde{\nu} \biggl( B(v, \frac{r}{L_{\Csig} L_K}) \biggr)  \right\} \cdot \frac{3}{9 + 8t} \nonumber \\
	& \geq \min \left\{ \nu \biggl( B(u, \frac{r}{L_{\Csig} L_K}) \biggr), \nu \biggl( B(v, \frac{r}{L_{\Csig} L_K}) \biggr)  \right\} \cdot \frac{1}{10(9 + 8t)} \label{eqn: one_step_2}
	\end{align}
	where \eqref{eqn: one_step} follows from Lemma \ref{lem: overlap_3} and \eqref{eqn: one_step_2} from Lemma \ref{lem: local_conductance}. Plugging \eqref{eqn: one_step_2} back into \eqref{eqn: one_step_1} -- and noting that Lemma \ref{lem: local_conductance} implies $\ell \geq \frac{1}{30}$ -- we have
	\begin{equation*}
	\widetilde{P}_{\nu,r}(u,A) - \widetilde{P}_{\nu,r}(v,A) \leq 1 - \frac{1}{300(9 + 8t)L_{C_{\sigma}}^d L_{K}^d}.
	\end{equation*}
	Since this holds for any $A \subset \Csig$, it holds over the supremum over all such $A$, therefore the desired statement is shown.
\end{proof}

\begin{lemma}[Lipschitz balls and local conductance.]
	\label{lem: lipschitz_balls_local_conductance}
	Under the assumption(s) of Theorem \ref{thm: dyer}, for $x,y \in K$ and $u = g(x), v = g(y)$ such that $\abs{u -v} \leq \frac{rt}{\sqrt{d}}$
	\begin{itemize}
		\item $B(u,r) \cap B(v,r) \cap \Csig \supseteq g\biggl(B(x, \frac{r}{L_{\Csig}}) \cap B(y, \frac{r}{L_{\Csig}}) \cap K  \biggr)$
		\item $\abs{x - y} \leq \frac{tr}{L_{K} \sqrt{d}}$.
		\item $\nu\biggl( B(x, \frac{r}{L_{\Csig}}) \cap K \biggr) \geq \widetilde{\nu} \biggl( B(u, \frac{r}{L_{\Csig} L_K}) \biggr)$ and similarly $\nu\biggl( B(y, \frac{r}{L_{\Csig}}) \cap K \biggr) \geq \widetilde{\nu} \biggl( B(v, \frac{r}{L_{\Csig} L_K}) \biggr)$.
	\end{itemize}
\end{lemma}
\begin{proof}
	\textcolor{red}{See page 18 of handwritten notes.}
\end{proof}

\begin{lemma}[One-step distributions over convex sets.]
	\label{lem: one_step_distributions_convex}
	Let $K \subset \Rd$ be a convex set, and $u,v \in K$, be such that $\abs{u - v} \leq \frac{t r}{\sqrt{d}}$ and $\ell(u), \ell(v) \leq \ell$. Then,
	\begin{equation*}
	\norm{P_{\nu,r}(x; \cdot) - P_{\nu,r}(y; \cdot)}_{TV} \leq 1 + t - \ell
	\end{equation*}
	where $P_{\nu,r}(x; A) = \frac{\nu(B(x,r) \cap A)}{\nu(B(x,r) \cap K)}$. 
\end{lemma}

\section{Proof of \eqref{eqn: one_step}}
\label{sec: proof_of_eqn_onestep}
This section is closely related to the results of \textcolor{red}{Kannan 97.}
We will build, through several lemmas, to \eqref{eqn: one_step}. 
Some preliminary notation: Fix $x,y \in K$, and denote $r' = r/ L_K$. Define
\begin{equation*}
C = B(x,r') \cap B(y,r')
\end{equation*}
the 'moons'
\begin{equation*}
M_x = B(x, r') \setminus B(y, r'),~ M_y = B(y,r') \setminus B(x,y')
\end{equation*}
and set
\begin{equation*}
R_x = M_x \cap (x - y + C),~ R_y = M_y \cap (y - x \cap C).
\end{equation*}
\begin{lemma}
	\label{lem: overlap_1}
	Let $x,y$ be two points in $K$ such that $\abs{x - y} < \sqrt{t}r'/\sqrt{d}$. Let $C'$ be the blowup of $C$ around its center $\frac{1}{2}(x + y)$ by $\alpha^{-1} := \frac{4d + 3t}{4d - t}$. Then
	\begin{equation*}
	M_x \setminus R_x \subseteq C'
	\end{equation*}
\end{lemma}
\begin{proof}
	Assume without loss of generality that $x = -y$, and let $z \in M_x \setminus R_x$. Write $z = \mu x + w$ where $w \perp x$. Then,
	\begin{itemize}
		\item $\abs{z - x} \leq r'$, since $z \in B(x,r')$.
		\item $\abs{z - y} > r'$, since $z \in B(y,r')$.
		\item $\abs{z - 3x} > r'$, since $z \not\in R_x$ means that either $\abs{z - 3x} > r'$ or $\abs{z - x} > r'$, and we know that second inequality will never hold.
	\end{itemize}
	As a result, we have that $\mu \in (0,2)$.

	Now, if $\abs{\alpha z - y} \leq \delta$, this would imply $\alpha z \in C$, and therefore $z \in C'$. We do some straightforward, if tedious, algebra to obtain the desired result:
	\begin{align*}
	\abs{\alpha z - y}^2 & = \abs{\alpha \mu x + \alpha w + x}^2 \\
	& = (\alpha \mu + 1)^2\abs{x}^2 + \alpha^2 \abs{w}^2 \\
	& \leq (\alpha \mu + 1)^2\abs{x}^2 + \alpha^2 ((r')^2 - (\mu - 1)^2 \abs{x}^2) \\
	& = (\alpha \mu + 1)^2 \frac{t(r'^2)}{d} + \alpha^2(\mu - 1)^2 \frac{t(r'^2)}{d} + \alpha^2 (r')^2 \\
	& = (r')^2 \frac{t}{d}\left((4\frac{d}{t} + 3)\alpha^2 + 4 \alpha + 1 \right) \\
	& = (r')^2
	\end{align*}
	where the last line follows from our choice of $\alpha$. 
\end{proof}

\begin{lemma}
	\label{lem: overlap_2}
	Under the notation and conditions of Lemma \ref{lem: overlap_1}, we have
	\begin{equation*}
	\vol(K \cap (M_x \setminus R_x)) \leq (1 + \frac{8t}{3}) \vol(K \cap C)
	\end{equation*}
	whenever $0 < t < 4/9$.
\end{lemma}
\begin{proof}
	From Lemma \ref{lem: overlap_1}, we have
	\begin{align*}
	\vol(K \cap (M_x \setminus R_x)) & \leq \vol(K \cap C') \\
	& \leq \vol((\alpha^{-1})(K \cap C)) \\
	& = (1 + \frac{4t}{4d - t})^d \vol(K \cap C) \\
	& \overset{(i)}{\leq} \left(1 + \frac{8td}{4d - t} \right) \vol(K \cap C) \\
	& \leq (1 + \frac{8t}{3}) \vol(K \cap C)
	\end{align*}
	where $(i)$ follows from a first order Taylor expansion of $(1 + x)^d$ about $x = 0$. 
\end{proof}

The following lemma is taken directly from \textcolor{red}{Kannan 97.}

\begin{lemma}
	\label{lem: volume_log_concave}
	For every convex body $K$,
	\begin{equation*}
	\vol(K \cap C)^2 \geq \vol(K \cap R_x) \vol(K \cap R_y)
	\end{equation*}
\end{lemma}

\begin{lemma}
	\label{lem: overlap_3}
	Under the notation and conditions of Lemma \ref{lem: overlap_1}
	\begin{equation*}
	\vol(K \cap C) \geq \frac{3}{9 + 8t}\min \set{\vol(B(x,r') \cap K), \vol(B(y,r'))}
	\end{equation*}
\end{lemma}
\begin{proof}
	From Lemma \ref{lem: overlap_2}, we have
	\begin{equation*}
	\vol(K \cap R_x) \geq \vol(K \cap M_x) - (1 + \frac{8t}{3}) \vol(K \cap C)
	\end{equation*}
	which, by the identity $B(x,r') = C \cup M_x$, further implies
	\begin{equation*}
	\vol(K \cap R_x) \geq \vol(K \cap B(x,r')) - (2 + \frac{8t}{3}) \vol(K \cap C)
	\end{equation*}
	with a symmetric inequality holding fro $K \cap R_y$. Applying Lemma \ref{lem: volume_log_concave} we obtain
	\begin{equation*}
	\vol(K \cap C) \geq \min \set{\vol(K \cap B(x,r')), \vol(K \cap B(y,r'))} - (2 + \frac{8t}{3}) \vol(K \cap C)
	\end{equation*}
	and the desired result follows after some rearrangement.
\end{proof}

\section{Proof of \eqref{eqn: one_step_2}}
\begin{lemma}
	\label{lem: local_conductance}
	Let $u \in \Csig = \Cset + \sigma B$ for some $\Cset \subseteq \Reals^d$. Then, for any $r' < \frac{\sigma}{4d}$,
	\begin{equation*}
	\nu(B(u,r') \cap \Csig) \geq \nu(B(u,r'))\frac{1}{30}.
	\end{equation*}
\end{lemma}
\begin{proof}
	Since $u \in \Csig$ there exists $v \in \Cset$ such that $u \in B(v, \sigma)$. Writing $r' := \frac{r}{L_{\Csig} L_K}$, we have that
	\begin{equation*}
	\widetilde{\nu}\bigl(B(u, r')\bigr) \geq \nu\bigl(B(u, r') \cap B(v, \sigma)\bigr)
	\end{equation*}
	\textcolor{red}{The volume of such an intersection is clearly minimized when $\abs{u - v} = \sigma$; in this case the intersection is formed by the union of two spherical caps. We will examine the larger of these two spherical caps, the cap of radius $r$ and height}
	\begin{equation*}
	h = r' - (r')^2/2\sigma = r' \left( 1 - \frac{r'}{2 \sigma} \right)
	\end{equation*}	
	Then, the volume of the cap $\nu_{cap}$ is known to be
	\begin{equation*}
	\nu_{cap} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
	\end{equation*}
	where
	\begin{equation*}
	\alpha := 1 - \frac{2 r' h - h^2}{(r')^2} \leq \frac{r'}{2 \sigma}
	\end{equation*}
	and $I(\cdot; \cdot)$ represents the incomplete beta function:
	\begin{equation*}
	I_{\alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{\alpha} u^{z - 1} (1 - u)^{w - 1} du.
	\end{equation*}
	Therefore,
	\begin{align*}
	\nu_{cap} & = \frac{1}{2} \nu_d (r')^d \frac{\Gamma(d/2 + 1)}{\Gamma((d+1)/2) \Gamma(1/2)} \int_{0}^{\alpha} u^{(d - 1)/2} (1 - u)^{-1/2} du \\
	& \geq \nu_d (r')^d \frac{1}{2 \sqrt{\pi} }  \frac{\Gamma(d/2 + 1)}{\Gamma((d+1)/2) } \int_{0}^{\alpha} u^{(d - 1)/2} (1 - u)^{-1/2} du \tag{$\Gamma(1/2) = \sqrt{\pi}$} \\ 
	& \geq \nu_d (r')^d \frac{1}{2 \sqrt{\pi} } \sqrt{\frac{d}{2}} \int_{0}^{\alpha} u^{(d - 1)/2} (1 - u)^{-1/2} du.\tag{Gautschi's inequality}
	\end{align*}
	Turning our attention to the relevant integral, letting $v = 1 - u$ and $\beta = 1/4d$ we obtain
	\begin{align*}
	\int_{0}^{\alpha} u^{(d - 1)/2} (1 - u)^{-1/2} du & = \int_{\alpha}^{1 } (1 - v)^{(d - 1)/2} v^{-1/2} dv \\
	& \geq \int_{\beta}^{2 \beta} (1 - v)^{(d - 1)/2} v^{-1/2} dv \tag{$\alpha \leq \beta \leq 2\beta \leq 1$} \\
	& \geq 2 (1 - 2 \beta)^{(d - 1)/2} \sqrt{\beta} (\sqrt{2} - 1) \\
	& \geq \frac{1}{2}\sqrt{\frac{1}{d}} (\sqrt{2} - 1). \tag{\textcolor{red}{Lemma 2}}
	\end{align*}
	Combining the pieces, we have
	\begin{equation*}
	\nu_{cap} \geq \nu_d (r')^d \frac{(\sqrt{2} - 1)}{2} \cdot \frac{1}{2 \sqrt{2 \pi}} \geq \frac{1}{30} \nu_d (r')^d.
	\end{equation*}

\end{proof}

\section{Notation}
\begin{itemize}
	\item For a set $K \subset \Rd$, $D_K = \max_{x,y \in K} \abs{x - y}$, where $\abs{x - y}$ is the Euclidean norm between of $x - y \in \Rd$. 
	\item $\nu_d$ is the volume of the unit ball $B(0,1)$ in $\Rd$. 
	\item $D_x g = (D_{x_i} {g_j})_{i,j = 1}^{d}$ is the Jacobian matrix of $g$ evaluated at $x$.
	\item $g(K) = \set{y \in \Rd: g(x) = y ~\text{for some}~ x \in K}$ is the image of $K$ under $g$.
	\item For measures $P,Q$ over $(\Sigma, \mathcal{F})$, $\norm{P - Q}_{TV} = \sup_{A \in \mathcal{F}} \abs{P(A) - Q(A)}$.  
\end{itemize}

\end{document}

### 2019-03-26 notes/weekly_notes/3.20.19.NotesForWeek.tex
weekly notes updated

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}
\newcommand{\dist}{\mathrm{dist}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}
\newcommand{\Sset}{\mathcal{S}}

\newcommand{\Csig}{\Cset_{\sigma}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for the week of 3/20/19 - 3/27/19}
\author{Alden Green}
\date{\today}
\maketitle

For a given $\sigma > 0$ and some $\Cset \subset \Rd$, let $\Csig = \Cset + B(0,\sigma)$ be the $\sigma$-expansion of $\Cset$. Fix $r > 0$. Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. Consider the \emph{speedy r-ball walk}\footnote{We call it 'speedy' because it only considers moves within $\Csig$.} over $\Csig \subset \Rd$, defined by the following transition probability density function 
\begin{equation*}
\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.

Denote the stationary distribution for this Markov chain by $\pi_{\nu,r}$, which satisfies the relation \footnote{See Section \ref{sec: stationary_distribution} for verification. In order to ensure a unique stationary distribution, we could consider only the \emph{lazy} version of the ball walk. For the moment we ignore this technicality.}
\begin{equation*}
\int_{\Csig} \widetilde{P}_{\nu,r}(x; \Sset) d\pi_{\nu,r}(x) = \pi_{\nu,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
Letting the \emph{local conductance} be given by
\begin{equation*}
\ell_{\nu,r}(x) := \frac{\nu(\Csig \cap B(x,r))}{\nu(B(x,r))} \tag{$x \in \Csig$}
\end{equation*}
a bit of algebra verifies that
\begin{equation*}
\pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x)}{\int_{\Csig} \ell_{\nu,r}(x)}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}

We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\nu,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
\begin{equation*}
\widetilde{Q}_{\nu,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d\pi_{\nu,r}(x) \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
\end{equation*}
and the \emph{(continuous) conductance profile} is
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\nu,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} \tag{$0 < t \leq 1/2 $}
\end{equation*}

\section{Conductance over $\Csig$}
An essential step in upper bounding the mixing time over $G_{n,r}[\Csig(\Xbf)]$ is lower bounding the conductance profile $\widetilde{\Phi}_{\nu,r}(t)$.

As in \citep{abbasi-yadkori2016}, we will assume $\Csig$ is the image of some convex set $K$ under a measure preserving, lipschitz function $g$.

\begin{assumption}[Embedding]
	\label{asmp: embedding}
	 Assume there exists $K \subset \Rd$ convex space, mapping $g: K \to \Csig$, and constant $L < \infty$ such that
	\begin{equation*}
	\forall x,y \in K,  \abs{g(x) - g(y)} \leq L \abs{x - y},~\text{and}~ \det(D_x g) = 1.
	\end{equation*}
	In other words, $g$ is measure-preserving and $L$-Lipschitz.
\end{assumption}

\begin{theorem}
	\label{thm: continuous_conductance_function}
	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$. Then, for any $0 < r < 2 \sigma / \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r}(t) \geq \frac{r}{2^{12} D_K L \sqrt{d}}.
	\end{equation*}
\end{theorem}
The proof of Theorem \ref{thm: continuous_conductance_function} naturally employs similar techniques to those in the convex setting (e.g. Theorem 5.2 in \cite{vempala2005}), except it employs an isoperimetric inequality which holds for non-convex sets, from \cite{abbasi-yadkori2016a}. Let $\dist(\Sset, \Sset') = \inf_{x \in \Sset, y \in \Sset'} \norm{x - y}$.

\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
	\label{lem: nonconvex_isoperimetry}
	Let $\Omega \subset \Rd$ satisfy Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$. Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Omega$, 
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{L D_{K}} \min(\nu(\Omega_1), \nu(\Omega_2))
	\end{equation*}
\end{lemma}

The ball walk may behave poorly near points of low local conductance. However, because $\Csig$ is a $\sigma$-expanded set, for sufficiently small $r$ all points will have high local conductance, so we do not need to worry about this problem.

\begin{lemma}
	\label{lem: local_conductance}
	Let $u \in \Csig$. Then, for any $r < \frac{\sigma}{2\sqrt{d}}$,
	\begin{equation*}
	\ell_{\nu,r}(u) \geq \frac{6}{25}.
	\end{equation*}
\end{lemma}

As is standard, we will also require that one-step distributions of nearby points be relatively similar.

\begin{lemma}[One-step distributions]
	\label{lem: one_step_distributions}
	Let $u,v \in \Csig$ be such that 
	\begin{equation*}
	\norm{u - v} \leq \frac{r t}{\sqrt{d}}
	\end{equation*}
	for some $0 < t < 1/8$, and further assume there exists $\ell > 0$ such that $\ell(u), \ell(v) \geq \ell$. Then,
	\begin{equation*}
	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
	\end{equation*}
	where for $P,Q$ probabilities over measurable space $(\Omega, \mathfrak{M})$, the total variation distance between $P$ and $Q$ is
	\begin{equation*}
	\norm{P - Q}_{TV} = \sup_{A \in \mathfrak{M}} \abs{P(A) - Q(A)}. 
	\end{equation*}
\end{lemma}

We delay proof of Lemmas \ref{lem: nonconvex_isoperimetry} - \ref{lem: one_step_distributions} to subsequent sections. Armed with these lemmas, we are ready to prove our main result.

\begin{proof}[Proof of Theorem \ref{thm: continuous_conductance_function}]
	Let $S_1 \cup S_2 = \Csig$, and let $\ell = \inf_{x \in \Csig}\ell_{\nu,r(x)}$. We will show that 
	\begin{equation*}
	\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{24 D_K L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
	\end{equation*}
	Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{1}{76}$. Then, dividing both sides by $\pi_{\nu,r}(S_1)$ yields the desired result.

	Now, consider the sets
	\begin{align*}
	S_1' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}} \\
	S_2' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}}
	\end{align*}
	and $S_3' = \Csig \setminus S_1' \setminus S_2'$.

	Suppose $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$. Then,
	\begin{equation*}
	\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(S_1)}{8}
	\end{equation*}
	Similarly, if $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$, then since
	\begin{equation*}
	\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) = \int_{S_2} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x)
	\end{equation*}
	a symmetric result holds.

	So we can assume $\pi_{\nu,r}(S_1') \geq \pi_{\nu,r}(S_1)/2$, and likewise for $S_2$. Now, for every $u \in S_1', v \in S_2'$, we have that
	\begin{equation*}
	\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;S_1) - \widetilde{P}_{\nu,r}(v;S_2) > 1 - \frac{\ell}{2}.
	\end{equation*}

	By Lemma \ref{lem: one_step_distributions}, we therefore have
	\begin{equation*}
	\abs{u - v} \geq \frac{2 \sqrt{2 \pi} r \ell}{3\sqrt{3 d}}.
	\end{equation*}
	and since $u \in S_1', v \in S_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(S_1', S_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
	\begin{equation*}
	\vol(S_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{3 D_K L \sqrt{3 d}} \min \set{\vol(S_1'), \vol(S_2')}
	\end{equation*}
	We now prove the desired result:
	\begin{align*}
	\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) & = \frac{1}{2} \bigl(\int_{S_2} \widetilde{P}_{\nu,r}(x; S_2)  d \pi_{\nu,r}(x) \bigr) \\
	& \geq \frac{\ell}{8} \pi_{\nu,r}(S_3') \\
	& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(S_3') \\
	& \geq \frac{\sqrt{2} r \ell^3}{12 D_K L \sqrt{d} \nu(\Csig)} \min \set{\nu(S_1'), \nu(S_2')} \\
	& \geq \frac{\sqrt{2} r \ell^4}{12 D_K L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1'), \pi_{\nu,r}(S_2')} \\
	& \geq \frac{\sqrt{2} r \ell^4}{24 D_K L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}.
	\end{align*}
\end{proof}

\section{Supporting theory.}

\subsection{Proof of Lemma \ref{lem: nonconvex_isoperimetry}}
The proof of Lemma \ref{lem: nonconvex_isoperimetry} will hinge on the corresponding result in the convex setting, given in \citep{dyer1991}.

\begin{theorem}[Isoperimetry of convex sets]
	\label{thm: dyer}
	Let $(R_1, R_2, R_3)$ be a partition of a convex set $K \subset \Rd$. Then,
	\begin{equation*}
	\vol(R_3) \geq 2\frac{d(R_1, R_2)}{D_{K}} \min(\vol(R_1), \vol(R_2))
	\end{equation*}
\end{theorem}

\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
	For $\Omega_i, i = 1,2,3$, denote the preimage
	\begin{equation*}
	R_i = \set{x \in K: g(x) \in \Omega_i}
	\end{equation*}
	For any $x \in R_1, y \in R_2$, 
	\begin{equation*}
	\abs{x - y} \geq \frac{1}{L}\abs{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
	\end{equation*}
	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
	\begin{equation*}
	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
	\end{equation*}
	By Theorem \ref{thm: dyer}, therefore
	\begin{align*}
	\vol(R_3) & \geq 2\frac{\dist(R_1, R_2)}{D_{K}} \min \{\vol(R_1), \vol(R_2)\} \\
	& \geq \frac{2}{D_{K} L} \dist(\Omega_1, \Omega_2) \min\{\vol(R_1), \vol(R_2)\}
	\end{align*}
	and by the measure-preserving property of $g$, this implies
	\begin{equation*}
	\vol(\Omega_3) \geq\frac{2}{D_{K} L} \dist(\Omega_1, \Omega_2) \min\{\vol(\Omega_1), \vol(\Omega_2)\}.
	\end{equation*}
\end{proof}

\subsection{Proof of Lemma \ref{lem: one_step_distributions}}
	Let $S_1 \cup S_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
	\begin{equation*}
	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
	\end{equation*}
	Since this will hold for arbitrary $S_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $S_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.

	Now, note that
	\begin{align*}
	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) & = 1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1)
	\end{align*}
	Let $I := B(u,r) \cap B(u,r)$. Then we have
	\begin{equation*}
	\widetilde{P}_{\nu,r}(u; S_2) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap I)
	\end{equation*}
	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; S_1)$. As a result,
	\begin{equation}
	1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
	\end{equation}
	As \eqref{eqn: one_step_1} demonstrates, the overlap of the one-step distributions is related to the volume of the intersection between $B(u,r)$ and $B(v,r)$ within $\Csig$.

	From here, some simple manipulations yield
	\begin{align}
	\nu(\Csig \cap I)  & = \nu(I) - \nu(I \setminus \Csig) \nonumber \\
	& \geq \nu(I) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
	\end{align}
	where we delay proof of the last inequality until the following section. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.

\subsection{Proof of \eqref{eqn: one_step_2}}
The following formula for the volume of the spherical cap, stated in terms of the incomplete beta function, is well known. We include it without proof. 
\begin{lemma}
	\label{lem: volume_of_spherical_cap}
	Let $\mathrm{Cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
	\begin{equation*}
	\nu\bigl( \mathrm{Cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
	\end{equation*}
	where
	\begin{equation*}
	\alpha := 1 - \frac{2 r h - h^2}{r^2}
	\end{equation*}
	and
	\begin{equation*}
	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
	\end{equation*}
	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
\end{lemma}

\begin{lemma}
	\label{lem: overlap_balls_1}
	Let $u,v \in \Rd$ be points such that $\abs{u - v} \leq t\frac{r}{\sqrt{d}}$ for some $0 < t < 1/8$. Then,
	\begin{equation*}
	\nu(B(u,r) \cap B(v,r)) \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
	\end{equation*}
\end{lemma}

\eqref{eqn: one_step_2} follows immediately from Lemma \ref{lem: overlap_balls_1} along with the definition of $\ell$ in Lemma \ref{lem: one_step_distributions}. To prove Lemma \ref{lem: overlap_balls_1}, we will rely on the following result, which will also be useful to lower bound the local conductance.

\begin{lemma}
	\label{lem: beta_integral}
	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{4 d}$,
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4 \sqrt{d}}
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write 
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
	\end{equation*}
	The first integral is simply the beta function, with
	\begin{equation*}
	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
	\end{equation*}
	To upper bound the second integral, we apply the Taylor theorem with remainder to $(1 - u)^{-1/2}$, obtaining
	\begin{equation*}
	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
	\end{equation*}
	As a result,
	\begin{align*}
	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2(d+1)}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
	& = \frac{3}{2(d+1)}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
	& \leq \frac{3}{2(d+1)}\alpha^{-1/2} (\alpha(d + 1)) =  \frac{3}{2}\alpha^{1/2}.
	\end{align*}
	and the result follows from the condition $\alpha \leq \frac{t^2}{2d}$. 
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem: overlap_balls_1}]
	We will treat only the case where $\abs{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase. Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ is comprised of the union of two disjoint spherical caps, and thus
	\begin{equation*}
	\nu(I) = 2\nu(\mathrm{Cap}_r(r(1 - \frac{t}{2 \sqrt{d}}))).
	\end{equation*}
	From Lemma \ref{lem: volume_of_spherical_cap} we therefore obtain
	\begin{equation*}
	\nu(I) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
	\end{equation*}
	where
	\begin{equation*}
	\alpha = 1 - \frac{2r^2(1 - \frac{t}{2 \sqrt{d}}) - r^2(1 - \frac{t}{2 \sqrt{d}})^2}{r^2} = \frac{t^2}{4d}.
	\end{equation*}
	Expanding the incomplete beta function in integral form, we therefore have
	\begin{align*}
	\nu(I) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
	& \overset{(i)}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
	& \overset{(ii)}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
	\end{align*}
	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we can validly apply since $\alpha \leq \frac{t^2}{2d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.

\end{proof}

\subsection{Proof of Lemma \ref{lem: local_conductance}}
\begin{proof}
	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as a result
	\begin{equation*}
	{\nu}\bigl(B(u, r) \cap \Csig \bigr) \geq \nu\bigl(B(u, r) \cap B(x, \sigma)\bigr)
	\end{equation*}
	Without loss of generality, let $\abs{u  - x} = \sigma$; it is not hard to see that if $\abs{u - x} < \sigma$, the volume of the overlap will only grow. Then, since $\abs{u  - x} = \sigma$, $B(u, r) \cap B(x, \sigma)$ contains a spherical cap of radius $r$ and height
	\begin{equation*}
	h = r - (r)^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
	\end{equation*}	
	which by Lemma \ref{lem: volume_of_spherical_cap} has volume
	\begin{equation*}
	\nu_{cap} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
	\end{equation*}
	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{4d}$.

	Then by Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
	\begin{align*}
	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{4 \sqrt{d}} \\
	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{2 \pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
	\end{align*}
\end{proof}

\section{Additional Lemmas}
Lemma \ref{lem: beta_function} follows from $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$ (Gautschi's inequality).
\begin{lemma}
	\label{lem: beta_function}
	\begin{equation*}
	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
	\end{equation*}
\end{lemma}

\section{Stationary distribution.}
\label{sec: stationary_distribution}
For completeness, we verify that $\pi_{\nu,r}$ is in fact a stationary distribution of the chain given by $\widetilde{P}_{\nu,r}$. Note that
\begin{equation*}
\frac{d \pi_{\nu,r}(x)}{dx} \propto \ell_{\nu,r}(x).
\end{equation*}
Let $\Sset \in \mathfrak{B}(\Csig)$. Then, 
\begin{align*}
\int_{\Csig} \widetilde{P}_{\nu,r}(x; \Sset) d \pi_{\nu,r}(x) & \propto \int_{\Csig} \widetilde{P}_{\nu,r}(x; \Sset) \ell_{\nu,r}(x) dx \\
& = \int_{\Csig} \frac{\nu(\Sset \cap B(x,r))}{\nu(B(x,r))} dx \\
& = \int_{\Csig} \int_{\Sset} \frac{\1(\norm{x - x'} \leq r)}{\nu(B(x,r))} dx dx' \\
& = \int_{\Sset} \int_{\Csig} \frac{\1(\norm{x - x'} \leq r)}{\nu(B(x,r))} dx dx' \\
& = \int_{\Sset} \ell_{\nu,r}(x) dx
\end{align*}
Since $\pi$ is a probability, we know the normalized constant must be $1 / \int_{\Csig} \ell_{\nu,r}(x) dx$.

\section{Notation}
\begin{itemize}
	\item For a set $K \subset \Rd$, $D_K = \max_{x,y \in K} \abs{x - y}$, where $\abs{x - y}$ is the Euclidean norm between of $x - y \in \Rd$. 
	\item $\nu_d$ is the volume of the unit ball $B(0,1)$ in $\Rd$. 
	\item $D_x g = (D_{x_i} {g_j})_{i,j = 1}^{d}$ is the Jacobian matrix of $g$ evaluated at $x$.
	\item $g(K) = \set{y \in \Rd: g(x) = y ~\text{for some}~ x \in K}$ is the image of $K$ under $g$.
	\item For measures $P,Q$ over $(\Sigma, \mathcal{F})$, $\norm{P - Q}_{TV} = \sup_{A \in \mathcal{F}} \abs{P(A) - Q(A)}$.  
\end{itemize}

\clearpage

\bibliography{../../local_spectral_bibliography}
\bibliographystyle{plain}

\end{document}

### 2019-04-11 notes/weekly_notes/4.8.19.NotesForWeek.tex
added weekly notes

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}
\newcommand{\dist}{\mathrm{dist}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}
\newcommand{\Sset}{\mathcal{S}}

\newcommand{\Csig}{\Cset_{\sigma}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}

%%% Functions over graphs
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\vol}{\mathrm{vol}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for the week of 4/8/19 - 4/12/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $\set{x_1, x_2, \ldots}$ be an infinite sequence of points sampled independently from probability measure $\Pbb$ with density function $f$. For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ . Given some $\lambda, \sigma > 0$, let
\begin{equation*}
\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
\end{equation*}

We will be concerned with the \emph{normalized cut} over the subgraph induced by $\Csig$. For convenience, denote $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{n} = \abs{\widetilde{\Xbf}_n}$, and let
\begin{equation*}
\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}, \widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr).
\end{equation*}
For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
\begin{equation*}
\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \widetilde{\cut}(S) = \abs{ \set{(i,j) \in \widetilde{E}_n: x_i \in S, x_j \not\in S}},~ \widetilde{\vol}(S) = \abs{ \set{(i,j) \in \widetilde{E}_n: x_i \in S} }
\end{equation*}
where in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$.

\paragraph{Convergence under the $TL^1$ metric}

Let
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*} 
be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$). A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,  
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
\end{equation*}
The following lemma shows that, under suitable conditions, transportation maps convergence to the identity mapping at rate $\left(\frac{\log n}{n}\right)^{1/d}$.

\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
	\label{lem: stagnating_transportation_maps}
	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
	\begin{equation*}
	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
	\end{equation*}
	where $Id(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
\end{lemma}
If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}. Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.

\begin{definition}
	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
	\begin{equation}
	\label{eqn: transportation_distance_1}
	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
	\end{equation}
	and denote it $u_n \overset{TL^1}{\to} u$.
\end{definition}

\begin{remark}
	\label{rmk: transportation_distance_equivalence}
	Note that this definition does not make sense on its face, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
	\begin{equation}
	\label{eqn: transportation_distance_2}
	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
	\end{equation}
	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$. However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and 
	\begin{equation*}
	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
	\end{equation*}

	Since this additional condition will clearly be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}. See \textcolor{red}{Garcia Trillos 15} for more details.
\end{remark}

\subsection{Desired result.}

Consider a sequence $S_1,S_2,\ldots,S_n,\ldots$ of sets with $S_n \subseteq \widetilde{\Xbf}_n$ for all $n$, with characteristic functions $u_n: \widetilde{\Xbf}_n \to \set{0,1}, u_n(x_i) = \1(x_i \in S_n)$ for $i \in \set{1, \ldots,n}$. We have already established the behavior of normalized cut when the sequence $\seq{u_n}$ converges $TL^1$ to some $u \in L^1(\widetilde{\Pbb})$. We require a complementary statement, of the form of Lemma \ref{lem: precompactness}.

\begin{lemma}[Precompactness]
	\label{lem: precompactness}
	Let $\seq{S_n}$ and $\seq{u_n}$ be as in the preceding paragraph. Suppose $u_n$ does not converge $TL^1$ to any $u \in L^1(\Pbb)$. Then, with probability one:
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(S_n) \geq c_d r^{1} \textcolor{red}{\omega_r(1)}
	\end{equation*}
	where $c_d$ is a constant which does not depend on $r$ but may depend on $d, \lambda$, $\sigma$ and $f$, and $\omega_r(1)$ represents a term which goes to infinity as $r \to 1$.
\end{lemma}
However, we wish to replace the asymptotic term $\omega_r(1)$ of Lemma \ref{lem: precompactness} with an explicit function of $r$.

\section{Supporting Theory.}

\begin{definition}
	For a sequence $\seq{y_n}$ over a metric space $Y$ equipped with metric $d_Y$, the sequence $\seq{y_n}$ is \emph{precompact} if every subsequence $(y_{n_k})_{k \in \Naturals}$ has an accumulation point in $Y$. 
\end{definition}

For $u_n \in L^1(\widetilde{\Pbb}_n)$, let the \emph{graph total variation} be given by
\begin{equation*}
GTV_{n,r_n}(u_n) = \frac{1}{n^2 r_n^{d + 1}}  \sum_{x_i \in \widetilde{\Xbf}_n} \sum_{x_j \in \widetilde{\Xbf}_n} \1\bigl(\norm{x_i - x_j} \leq r\bigr) \abs{u_n(x_i) - u_n(x_j)}
\end{equation*}

To see the relation between $GTV$ and $\widetilde{\Phi}$, introduce the balance term
\begin{equation*}
B_n(u_n) = \min_{m \in \Reals} \frac{1}{\widetilde{\vol}(\widetilde{\Xbf}_n)} \sum_{x_i \in \widetilde{\Xbf}_n} \widetilde{\deg}(u_n) \abs{u_n(x_i) - m}.
\end{equation*}

Note that if $u_n(x) = \1(x \in S_n)$ is the characteristic function for some $S_n \subseteq \widetilde{\Xbf}_n$, then (assuming $S_n$ is not the empty set)
\begin{equation*}
B_n(u_n) = \frac{\min \set{ \widetilde{\vol}(S_n) , \widetilde{\vol}(S_n^c) }}{\widetilde{\vol}(\widetilde{\Xbf}_n)}, ~\text{and}~ GTV_{n,r_n}\left(\frac{u_n}{B_n(u_n)}\right) = \frac{\vol(\widetilde{\Xbf}_n)}{n^2 r^{d+1}}\widetilde{\Phi}_{n,r_n}(S_n).
\end{equation*}

We introduce an energy functional $E_n$ as shorthand for $GTV_{n,r_n}\left(\frac{u_n}{B_n(u_n)}\right)$:
\begin{equation*}
E_n(v_n) := 
\begin{cases}
GTV_{n,r_n}(v_n),~ & \text{if there is}~ S_n \subseteq \widetilde{X}_n, u_n(x) = 1(x \in S_n) ~\text{with}~ B_n(u_n) > 0 ~\text{such that}~ v_n = \frac{u_n}{B_n(u_n)} \\
\infty,~ & \text{otherwise}
\end{cases}
\end{equation*}

\begin{lemma}[Lemma 23 of \textcolor{red}{Garcia Trillos 16}]
	\label{lem: gt_precompactness}
	Let $\seq{r_n}$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{equation*}
	\lim_{n \to \infty} \frac{(\log n)^{p_d}}{n^{1/d}} \frac{1}{r_n} = 0
	\end{equation*}
	where $p_d = 3/4$ if $d = 2$ and $1/d$ for $d \geq 3$.

	With probability one the following statement holds: for any sequence $\seq{v_n}$ with $v_n \in L^1(\widetilde{\Pbb}_n)$, if
	\begin{equation*}
	\limsup_{n \to \infty} E_n(v_n)  < \infty
	\end{equation*}
	then $v_n$ is precompact in $TL^1$. 
\end{lemma}

\begin{remark}
	As outlined in Remark \ref{rmk: transportation_distance_equivalence}, to be technically precise about $TL^1$ convergence we need to work with distances between $(\widetilde{\Pbb}, v)$ and $(\widetilde{\Pbb}_n, v_n)$. Here, when we say ``$v_n$ is precompact in $TL^1$'' we mean that for every subsequence $(v_{n_k})_{k \in \Naturals}$ there exists some $v \in L^1(\Pbb)$ such that $(\widetilde{\Pbb}, v)$ is an accumulation point of $\bigl( (\widetilde{\Pbb}_{n_k},v_{n_k})_{k \in \Naturals} \bigr)$ with respect to $TL^1$ distance. 
\end{remark}

Lemma \ref{lem: gt_precompactness} builds straightforwardly from Lemma \ref{lem: gt_precompactness_2}. Lemma \ref{lem: gt_precompactness_2} makes a similar statement to Lemma \ref{lem: gt_precompactness} but with respect to the graph total variation functional, meaning it does not take into account the balance term.

\begin{lemma}[Theorem 1.2 of \textcolor{red}{Garcia Trillos 16b}]
	\label{lem: gt_precompactness_2}
	Let $\seq{r_n}$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{equation}
	\label{eqn: r_conv_rate}
	\lim_{n \to \infty} \frac{(\log n)^{p_d}}{n^{1/d}} \frac{1}{r_n} = 0
	\end{equation}
	where $p_d = 3/4$ if $d = 2$ and $1/d$ for $d \geq 3$. Consider a sequence of functions $u_n \in L^1(\widetilde{\Pbb}_n)$. If
	\begin{equation}
	\label{eqn: bounded_norm}
	\sup_{n \in \Naturals} \norm{u_n}_{L^1(\widetilde{\Pbb}_n)} < \infty
	\end{equation}
	and
	\begin{equation}
	\label{eqn: bounded_GTV}
	\sup_{n \in \Naturals} GTV_{n,r_n}(u_n) < \infty
	\end{equation}
	then $\seq{u_n}$ is precompact in $TL^1$.
\end{lemma}

We will apply Lemma \ref{lem: gt_precompactness_2} to the sequence $\seq{v_n}$ specified in the setup of Lemma \ref{lem: gt_precompactness}. To do so, we will need to show $\sup_{n \in \Naturals} \norm{v_n}_{L^1(\widetilde{\Pbb}_n)} < \infty$ is implied by $\limsup_{n \to \infty} E_n(v_n)  < \infty$. This holds thanks to the gamma convergence of the functionals $E_n$ to a continuous analogue. For $u \in L^1(\widetilde{\Pbb})$, recall that the total variation of $u$ is given by
\begin{equation*}
TV(u) := \sup \set{\int_{\Csig} u(x) \dive(\Psi(x)) dx: \Psi \in C_c^1(\Csig: \Reals^d), \abs{\Psi(x)} \leq f^2(x)}
\end{equation*}
where $C_c^1(\Csig: \Reals^d)$ represents the set of $C^1$-functions from $\Csig$ to $\Reals^d$ whose support is compactly contained in $\Csig$.

For $u \in L^1(\widetilde{\Pbb})$, let $B(u)$ be a balance term
\begin{equation*}
B(u) := \min_{m \in \Reals} \frac{\int_{\Csig} \abs{u(x) - m} f^2(x) dx}{\int_{\Csig} f^2(x) dx}.
\end{equation*}
Then, analogously to the discrete case, let the continuous energy functional $E(v)$ be given by
\begin{equation*}
E(v) := 
\begin{cases}
TV(v),~ & \text{if there exists}~  \Sset \subseteq \Csig, u(x) = \1(x \in \Sset) ~\text{with}~ B(u) > 0 ~\text{such that}~ v = \frac{u}{B(u)} \\
\infty, & \text{otherwise}.
\end{cases}
\end{equation*}

\begin{lemma}[Proposition 21 of \textcolor{red}{Garcia Trillos 16b}]
	\label{lem: liminf_E}
	For any $v \in L^1(\widetilde{\Pbb})$ and any sequence $\seq{v_n}$ with $v_n \in L^1(\widetilde{\Pbb}_n)$ that converges to $v$ in $TL^1$,
	\begin{equation*}
	c_1 E(v)  \leq \liminf_{n \to \infty} E_n(v_n)
	\end{equation*}
	where $c_1$ is a universal constant. 
\end{lemma}
\section{Proofs}

\subsection{Proof of Lemma \ref{lem: gt_precompactness}}

By Lemma \ref{lem: gt_precompactness_2}, it is sufficient to show that \eqref{eqn: bounded_norm} and \eqref{eqn: bounded_GTV} are satisfied for $v_n = \frac{1}{B_n(u_n)}u_n$, where $u_n(x) = \1(x \in S_n)$ is the characteristic function for $S_n$. Of course, as we have noted
\begin{equation*}
GTV_{n,r_n}\left(\frac{u_n}{B_n(u_n)}\right) = \frac{\vol(\widetilde{\Xbf}_n)}{n^2 r^{d+1}}\widetilde{\Phi}_{n,r_n}(S_n)
\end{equation*}
and therefore by hypothesis \eqref{eqn: bounded_GTV} holds for $v_n$. We turn now to showing \eqref{eqn: bounded_norm}.

To begin, let
\begin{equation*}
w_n := 
\begin{cases}
v_n,~ & \text{if}~ \vol(S_n) \leq \vol(S_n^c)  \\
(1 - u_n)/B_n(u_n),~ & \text{if}~ \vol(S_n) > \vol(S_n^c).
\end{cases}
\end{equation*}
Note that 
\begin{equation*}
\norm{u_n}_{L^1(\Pbb_n)} = \frac{\abs{S_n}}{\widetilde{n}} \leq \frac{\widetilde{\vol}(S_n)}{\widetilde{d}_{\min} \widetilde{n}}
\end{equation*}
and similarly $\norm{1 - u_n}_{L^1(\Pbb_n)} \leq \frac{\widetilde{\vol}(S_n^c)}{\widetilde{d}_{\min} \widetilde{n}}$. Therefore
\begin{equation*}
\norm{w_n}_{L^1(\Pbb_n)} \leq \frac{\min \set{\widetilde{\vol}(S_n),\widetilde{\vol}(S_n^c)}}{\widetilde{d}_{\min} \widetilde{n} B_n(u_n)} \leq \frac{\widetilde{\vol}(\widetilde{\Xbf}_n)}{\widetilde{n} \widetilde{d}_{\min}} \leq \frac{\widetilde{d}_{\max}}{\widetilde{d}_{\min}}
\end{equation*}
There exists constant $c_{\sigma}$ which depends only on $\sigma$ such that
\begin{equation*}
\limsup_{n \to \infty} \frac{\widetilde{d}_{\max}}{\widetilde{d}_{\min}} \leq c_{\sigma}\frac{\Lambda_{\sigma}}{\lambda_{\sigma}} < \infty.
\end{equation*}
Moreover, $GTV_{n,r_n}(w_n) = GTV_{n,r_n}(v_n)$. Therefore, by Lemma \ref{lem: gt_precompactness_2}, $w_n$ is precompact in $TL^1$, meaning any subsequence of $w_n$ has a further convert subsequence; let $w_{n_k} \overset{TL^1}{\to} w$ denote this convergent subsequence.

Therefore by Lemma \ref{lem: liminf_E}, 
\begin{equation*}
\infty > \liminf_{n \to \infty} E_n(w_{n_k}) \geq c_1 E(w)
\end{equation*}
which in turn implies that $B(w) > 0$. But then
\begin{align*}
\norm{v_{n_k}}_{L^1(\widetilde{\Pbb})}  & = \frac{1}{B_n(u_{n_k})} \norm{u_{n_k}}_{L^1(\widetilde{\Pbb})} \\
& \leq \frac{1}{B_n(u_{n_k})} \\
& = \frac{1}{B_n(w_{n_k})} \to \frac{1}{B(w)} < \infty
\end{align*}
where the proof of convergence $B_n(w_{n_k}) \to B(w)$ is omitted but is straightforward. So every subsequence of $\seq{v_n}$ has a further subsequence $(v_{n_k})_{k \in \Naturals}$ which satisfies \eqref{eqn: bounded_norm} and \eqref{eqn: bounded_GTV} and therefore is precompact in $TL^1$.

\subsection{Proof of Lemma \ref{lem: gt_precompactness_2}}
By Lemma \ref{lem: stagnating_transportation_maps}, there exists a sequence of transportation maps $\seq{T_n}$ such that for a.e. $z,y \in \Csig$ with $\norm{T_n(z) - T_n(x)} > r_n$,
\begin{equation*}
\norm{z - y} > r_n - 2 \norm{\mathrm{Id} - T_n}_{\infty} =: \widetilde{r}_n.
\end{equation*}
and as an immediate implication for a.e. $z,y \in \Csig$,
\begin{equation*}
\norm{z - y} \leq \widetilde{r}_n \Longrightarrow \norm{T_n(z) - T_n(y)} \leq r_n
\end{equation*}

Note that by the lower bound on $r_n$ implied by \eqref{eqn: r_conv_rate}, $\frac{r_n}{\widetilde{r}_n} \to 1$; in particular, $\widetilde{r}_n$ will be positive for sufficiently large $n$ with probability $1$. Therefore for $n$ sufficiently large,
\begin{align*}
\frac{1}{r_n^{d+1}} \iint_{\Csig \times \Csig} & \1(\norm{z - y} \leq \widetilde{r}_n) \abs{u_n \circ T_n(z) - u_n \circ T_n(y)} f(z) f(y) dz dy \\
& \leq \frac{1}{r_n^{d+1}} \iint_{\Csig \times \Csig} \1(\norm{T_n(z) - T_n(y)} \leq r_n) \abs{u_n \circ T_n(z) - u_n \circ T_n(y)} f(z) f(y) dz dy \\
& = GTV_{n,r_n}(u_n)
\end{align*} 
and by hypothesis $\limsup_{n \to \infty} GTV_{n,r_n}(u_n) < \infty$.  But as $\frac{r_n}{\widetilde{r}_n} \to 1$, this implies
\begin{equation*}
\limsup_{n \to \infty} \frac{1}{\widetilde{r}_n} \iint_{\Csig \times \Csig} \frac{\1(\norm{z - y} \leq \widetilde{r}_n)}{\widetilde{r}_n^d} \abs{u_n \circ T_n(z) - u_n \circ T_n(y)} f(z) f(y) dz dy < \infty
\end{equation*}
and so by \textcolor{red}{Proposition 1} $\seq{u_n \circ T_n}$ is precompact in $L^1(\widetilde{\Pbb})$, which is equivalent to $\seq{u_n}$ being precompact in $TL^1$.

Proposition \ref{prop: compactness_nonlocal_TV} -- which we prove in Section \ref{sub: proof_of_prop_compactness_nonlocal_TV} --  is stated with respect to a nonlocal functional $TV_r(u)$, given by
\begin{equation*}
TV_r(u) := \frac{1}{r} \iint_{\Csig \times \Csig} \frac{\1(\norm{x - y} \leq r)}{r^d} \abs{u(x) - u(y)} f(x) f(y) dx dy
\end{equation*}

\begin{proposition}
	\label{prop: compactness_nonlocal_TV}
	Let $\seq{v_{r_n}}$ be a sequence in $L^1(\widetilde{\Pbb})$ such that
	\begin{equation*}
	\sup_{n \in \Naturals} \norm{v_{r_n}}_{L^1(\widetilde{\Pbb})} < \infty 
	\end{equation*}
	and
	\begin{equation*}
	\sup_{n \in \Naturals} TV_{r_n}(v_{r_n}) < \infty.
	\end{equation*}
	Then, $\seq{v_{r_n}}$ is precompact in $L^1(\widetilde{\Pbb})$. 
\end{proposition}

\subsection{Proof of Proposition \ref{prop: compactness_nonlocal_TV}}
\label{sub: proof_of_prop_compactness_nonlocal_TV}

Without loss of generality, let $f \equiv 1$ (since otherwise it is bounded above and below by positive constants over its support). We begin by extending each function $v_{r_n}$ to $\Reals^d$. By assumption, $\forall x \in C^{2\sigma}$ there exists a unique closest point on $\partial C^{\sigma}$; let $Px$ denote this point, and define the local reflection mapping
\begin{equation*}
\widehat{x} = 2Px - x.
\end{equation*}
Letting $\xi(s)$ be a smooth function satisfying
\begin{equation*}
\xi(s) = 1, s \leq \frac{\sigma}{8},~ \text{and}~ \xi(s) = 0, s \geq \frac{\sigma}{4}
\end{equation*}
we define an auxiliary function
\begin{equation*}
\widetilde{v}_{r_n}(x) = \xi(\abs{x - Px}) v_{r_n}(\widehat{x})
\end{equation*}
and \textcolor{red}{claim that} for some constant $C$,
\begin{align*}
\sup_{n \in \Naturals} & \frac{1}{r_n} \iint_{\Reals^d \times \Reals^d} \frac{\1(\norm{x - y} \leq r)}{r^d} \abs{\widetilde{v}_{r_n}(x) - \widetilde{v}_{r_n}(y)} dy dx < \\
& \leq C \sup_{n \in \Naturals} \left(\frac{1}{r_n} \iint_{\Reals^d \times \Reals^d} \frac{\1(\norm{x - y} \leq r)}{r^d} \abs{v_{r_n}(x) - v_{r_n}(y)} dy dx +  \norm{v_{r_n}}_{L^1(\widetilde{\Pbb})}\right)
\end{align*}
which by hypothesis is less than $\infty$.

\section{Additional Notation}
\begin{itemize}
	\item $c_1 = \int_{B(0,1)} \abs{\dotp{x}{e_1}} dx$ where $B(0,1)$ is a $d$-dimensional unit ball centered at the origin.
\end{itemize}

\end{document}

### 2019-04-20 notes/weekly_notes/4.12.19.NotesForWeek.tex
added weekly notes

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}
\newcommand{\dist}{\mathrm{dist}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}
\newcommand{\Sset}{\mathcal{S}}

\newcommand{\Csig}{\Cset_{\sigma}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ebb}{\mathbb{E}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}

%%% Functionals over graphs
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\vol}{\mathrm{vol}}
% \newcommand{\deg}{\mathrm{deg}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for the week of 4/8/19 - 4/12/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $\set{x_1, x_2, \ldots}$ be a sequence of points sampled independently from probability measure $\Pbb$ with density function $f$. For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ . Given some $\lambda, \sigma > 0$, let
\begin{equation*}
\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
\end{equation*}

Write $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}$ and let $\widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr)$.
For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
\begin{equation*}
\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \textrm{where}~ \widetilde{\cut}(S) := \cut(S;\widetilde{G}_{n,r}),~ \widetilde{\vol}(S) := \vol(S;\widetilde{G}_{n,r})
\end{equation*}
and in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$. Then, the \emph{graph conductance profile} over $\widetilde{G}_{n,r}$ is
\begin{equation*}
\widetilde{\Phi}_{n,r}(t) := \min_{\substack{S \subseteq \widetilde{\Xbf}_n: \\ 0 < \widetilde{\pi}_n(S) < t} } \widetilde{\Phi}_{n,r}(S)
\end{equation*}
where $\widetilde{\pi}_{n,r}(S) = \frac{\widetilde{\vol}(S)}{\widetilde{\vol}(\widetilde{\Xbf}_n)}$. We will prove a lower bound on the graph conductance profile by a continuous analogue.

\subsection{Continuous conductance}

Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. For $\Sset \subset \Rd$ a Borel set,
\begin{equation*}
\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
\end{equation*}
is the weighted volume.

The $r$-ball walk over $\Csig$ is a Markov chain, with transition probability given by 
\begin{equation*}
\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\nu_{\Pbb}(\Sset \cap B(x,r))}{\nu_{\Pbb}(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.

Denote the stationary distribution for this Markov chain by $\pi_{\Pbb,r}$, which is defined by the relation
\begin{equation*}
\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
Letting the \emph{local conductance} be given by
\begin{equation*}
\ell_{\Pbb,r}(x) := \nu_{\Pbb}(\Csig \cap B(x,r)) \tag{$x \in \Csig$}
\end{equation*}
a bit of algebra verifies that
\begin{equation*}
\pi_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}

We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
\begin{equation*}
\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\pi_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
\end{equation*}
the \emph{(continuous) normalized cut} by
\begin{equation*}
\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2)}{\min \set{\pi_{\Pbb,r}(\Sset),\pi_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
and the \emph{(continuous) conductance profile} by
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
\end{equation*}
where $\Sset^c = \Csig \setminus \Sset$.

To relate the graph and continuous conductance profiles, we introduce mappings between the data $\widetilde{\Xbf}_n$ and the space $\Csig$.

\subsection{Transportation maps and $TL^1$ distance. }
Let
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*} 
be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$). A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,  
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
\end{equation*}

If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}. Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.
In fact, under suitable conditions, the convergence happens at rate $\left(\frac{\log n}{n}\right)^{1/d}$.

\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
	\label{lem: stagnating_transportation_maps}
	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
	\begin{equation*}
	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
	\end{equation*}
	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
\end{lemma}

\begin{definition}
	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
	\begin{equation}
	\label{eqn: transportation_distance_1}
	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
	\end{equation}
	and denote it $u_n \overset{TL^1}{\to} u$.
\end{definition}

\begin{remark}
	\label{rmk: transportation_distance_equivalence}
	Note that as written this is not a metric, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
	\begin{equation}
	\label{eqn: transportation_distance_2}
	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
	\end{equation}
	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$. However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and 
	\begin{equation*}
	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
	\end{equation*}

	Since this additional condition will be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}. See \textcolor{red}{Garcia Trillos 15} for more details.
\end{remark}

\section{Lower bound graph conductance profile}

In order to lower bound the graph conductance profile $\widetilde{\Phi}_{n,r}(\cdot)$, we will need to split the analysis into two cases based on the size of $S \subseteq \widetilde{\Xbf}_n$. Define the \emph{graph local spread} to be
\begin{equation*}
s(G) := \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \cdot \min_{u \in V} \set{\pi(u;G)}.  \tag{$G = (V,E)$}
\end{equation*}

Theorem \ref{thm: graph_conductance_profile_lb_1} states that for subsets of $\widetilde{\Xbf}_n$ with volume at least $s(G)$, the graph normalized cut can be uniformly lower bounded by the continuous normalized cut. Sections \ref{sec: proof_and_supporting_theory} and \ref{sec: other_results} contains the proof of Theorem \ref{thm: graph_conductance_profile_lb_1} along with other relevant results.

\begin{theorem}
	\label{thm: graph_conductance_profile_lb_1}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then,
	\begin{equation*}
	\liminf_{n \to \infty} \Bigl\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \Bigr\} \geq \frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}
	\end{equation*}
	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \widetilde{\Xbf}_n: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$
\end{theorem}

Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
\begin{lemma}
	\label{lem: graph_conductance_profile_lb_1}
	Let $G = (V,E)$ be an undirected graph, and $\mathcal{L}(G) = \set{S \subseteq V: \pi(S; G) \geq s(G)}$. Then,
	\begin{equation*}
	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
	\end{equation*}
\end{lemma}
\begin{proof}
	Clearly, for any $u \in S$
	\begin{equation}
	\label{eqn: graph_conductance_profile_lb_1}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \abs{S}
	\end{equation}

	Then, since $\pi(S;G) \leq s(G)$,
	\begin{equation*}
	\abs{S} \leq \pi(S;G) \cdot \frac{\vol(V;G)}{\min_{u \in V} \set{\mathrm{deg}(u;G)}} = \frac{\pi(S;G)}{\min_{u \in V} \set{\pi(u;G)}} \leq \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)},
	\end{equation*}
	and therefore by \eqref{eqn: graph_conductance_profile_lb_1}, for any $u \in S$
	\begin{equation*}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \geq \frac{1}{10}\deg(u;G)
	\end{equation*}
	and the statement follows by summing over all $u \in S$. 
\end{proof}

Theorem \ref{thm: graph_conductance_profile_lb_1} and Lemma \ref{lem: graph_conductance_profile_lb_1} together yield Corollary \ref{cor: graph_conductance_profile_lb}, the main result of these notes.

\begin{corollary}[Lower bound on graph conductance profile]
	\label{cor: graph_conductance_profile_lb}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then, with probability one the following asymptotic lower bound holds on the graph conductance function
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\set{\frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}, \frac{1}{10}} \tag{$0 \leq t \leq \frac{1}{2}$}
	\end{equation*}
\end{corollary}

\section{Proofs and Supporting Theory}
\label{sec: proof_and_supporting_theory}

\subsection{Proof of Theorem \ref{thm: graph_conductance_profile_lb_1}.}

By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.

For $S \subseteq \widetilde{\Xbf}_n$, let $T_n^{-1}(S) = \set{x \in \Csig: T_n(x) \in S}$ be the preimage of $T_n$, and note that $T_n^{-1}(S^c) = \Csig \setminus T_n^{-1}(S)$.

Letting
\begin{equation*}
\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx},~ \gamma_n(S) := \frac{\min \set{\pi_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\pi_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^+}(T_n^{-1}(S^c))} } 
\end{equation*}
where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, by Lemma \ref{lem: graph_to_continuous_conductance} and Corollary \ref{cor: nonuniform_continuous_conductance} we have that for all $S \subseteq \widetilde{\Xbf}_n$,
\begin{align}
\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^4r_n^{-}}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
\end{align}

By Lemma \ref{lem: cont_local_conductance}, with probability one
\begin{equation*}
\liminf_{n \to \infty} \xi_n = 1.
\end{equation*}

By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $c > \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}$, there exists some $n \in \Naturals$ such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
\begin{equation*}
\pi_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
\end{equation*}
and therefore by Lemma \ref{lem: cont_stationary_dist}
\begin{equation*}
\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
\end{equation*}

As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.

\subsection{Graph functionals to continuous functionals.}

Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.

\begin{lemma}
	\label{lem: volume_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$
	\begin{equation*}
	\frac{1}{\widetilde{n}^2}\widetilde{\vol}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{equation*}
	where $r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$. 
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	Now, we proceed
	\begin{align}
	\frac{1}{\widetilde{n}^2} \widetilde{\vol}(S_n) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i)} \nonumber \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \label{eqn: vol_ub}\\
	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
	\end{align}

	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
	\begin{align*}
	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) dx \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{align*}
	which is the desired upper bound. The lower bound follows a similar proof, with the only change being \eqref{eqn: vol_ub}, where $r_n^+$ is replaced by $r_n^-$ and the inequality is reversed.
\end{proof}

\begin{lemma}
	\label{lem: cut_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c) 
	\end{equation*}
	where $r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^\infty(\widetilde{\Pbb})}$
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
	\begin{align*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i) - u(x_j)} \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x) - u(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
	\end{align*}
	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
	\begin{align*}
	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
	\end{align*}	
\end{proof}

\begin{lemma}
	\label{lem: graph_to_continuous_conductance}
	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and let
	\begin{equation*}
	r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})},~ r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}.
	\end{equation*}

	Fix $S \subseteq \widetilde{\Xbf}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation}
	\label{eqn: graph_to_continuous_conductance}
	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}  \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
	\end{equation}
\end{lemma}
\begin{proof}

	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
	\begin{equation*}
	\frac{\widetilde{\cut}(S)}{\widetilde{\vol}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset)}
	\end{equation*}

	But, noting that $\Sset^c = \set{x \in \Csig: T_n(x) \in S^c}$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
	\begin{equation*}
	\frac{\widetilde{\cut}(S^c)}{\widetilde{\vol}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\pi_{\Pbb,r_n^+}(\Sset^c)}
	\end{equation*}
	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
	\begin{equation*}
	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} },
	\end{equation*}
	and the proof is complete.
\end{proof}

\subsection{Perturbation asymptotics.}

In light of Lemma \ref{lem: stagnating_transportation_maps}, the error incurred in \eqref{eqn: graph_to_continuous_conductance} by the use of $r_n^{+}$ and $r_n^{-}$ as opposed to $r$ is asymptotically negligible.

\begin{lemma}[Continuity of local conductance]
	\label{lem: cont_local_conductance}
	Letting $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, with probability one the following holds:
	\begin{equation*}
	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
	\begin{equation*}
	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx + \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx.
	\end{equation*}
	and therefore
	\begin{equation*}
	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}. 
	\end{equation*}
	We upper bound the remainder term
	\begin{equation*}
	\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d
	\end{equation*}
	and taking limits as $n \to \infty$ we obtain with probability one
	\begin{equation*}
	\limsup_{n \to \infty} \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \limsup_{n \to \infty} P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d = 0
	\end{equation*}
	by the stagnating property of $\seq{T_n}$.

	We apply a similar analysis to the denominator.
	\begin{equation*}
	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) dy dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d
	\end{equation*}
	and therefore by the stagnating property of $\seq{T_n}$ and Lemma \ref{lem: local_conductance},
	\begin{equation*}
	\liminf_{n \to \infty} \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx  = \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
	\end{equation*}
	again with probability one.

	The desired result then follows from an application of Slutsky's Theorem.
\end{proof}

\begin{lemma}[Continuity of stationary distribution]
	\label{lem: cont_stationary_dist}
	Let $c > 0$ be a fixed constant, $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.  With probability one the following statement holds:
	\begin{equation*}
	\liminf_{n \to \infty} \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } = 1
	\end{equation*}
	uniformly over all sets $\Sset \subseteq \mathfrak{B}(\Csig)$ satisfying $\min \set{\pi_{\Pbb,r}(\Sset), \pi_{\Pbb,r}(\Sset^c)}> c$. 
\end{lemma}
\begin{proof}
	It will be sufficient to show that
	\begin{equation*}
	\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} ~ \text{and} \liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset^c)} = 1.
	\end{equation*}
	and we will show only that $\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1$. The result for $\Sset^c$ is identical.

	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
	\begin{equation*}
	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
	\end{equation*}
	Rewriting
	\begin{equation*}
	 \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\pi_{\Pbb,r_n^+}(\Sset)}
	\end{equation*}
	we have that
	\begin{equation*}
	\liminf_{n \to \infty} \int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \Pbb(\Sset) \Lambda_{\sigma} \liminf_{n \to \infty}\bigl( (r_n^+)^d - (r_n^-)^d\bigr) \nu^d = 0
	\end{equation*}
	where the equality occurs with probability one. On the other hand by hypothesis
	\begin{equation*}
	\limsup_{n \to \infty} \pi_{\Pbb,r_n^+}(\Sset) \geq c > 0.
	\end{equation*}
	and the result follows by Slutsky's Theorem. 
\end{proof}

\begin{lemma}[Stationary distribution lower bound]
	\label{lem: stationary_dist_lb}
	With probability one, the following statement holds: let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$. Then, for any $\epsilon > 0$, there exists some $m \in \Naturals$ such that for all $n \geq m$,
	\begin{equation*}
	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \pi_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}  - \epsilon
	\end{equation*}
\end{lemma}
\begin{proof}
	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary. Write $\Sset := T_n^{-1}(S)$.

	We can upper bound $\widetilde{\pi}_{n,r}(S)$ by $\pi_{\Pbb,r}(\Sset)$ plus a remainder term.
	\begin{align}
	\widetilde{\pi}_{n,r}(S) & \leq \frac{\int_\Sset \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \nonumber \\
	& = \pi_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x- x'} \leq r_n^+) f(x') f(x) dx' dx} \label{eqn: stationary_dist_lb_1}
	\end{align}
	Clearly $\pi_{\Pbb,r_n^-}(\Sset) \leq \pi_{\Pbb,r}(\Sset)$. Moreover
	\begin{equation*}
	\frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
	\end{equation*}
	and by \eqref{eqn: stationary_dist_lb_1}, we have
	\begin{equation*}
	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \pi_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
	\end{equation*}
	The remainder term $\frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d$ is independent of $S$ and asymptotically $o_p(1)$ by Lemma \ref{lem: stagnating_transportation_maps}.
	An application of Lemma \ref{lem: local_spread_lb} completes the proof.
\end{proof}

\subsection{Continuous conductance function.}

In Theorem \ref{thm: continuous_conductance_function}, we restate a necessary result from the 3/20 weekly notes.

\begin{assumption}[Embedding]
	\label{asmp: embedding}
	Assume there exists $K \subset \Rd$ convex space, mapping $g: K \to \Csig$, and constant $L < \infty$ such that
	\begin{equation*}
	\forall x,y \in K,  \abs{g(x) - g(y)} \leq L \abs{x - y},~\text{and}~ \det(D_x g) = 1.
	\end{equation*}
	In other words, $g$ is measure-preserving and $L$-Lipschitz.
\end{assumption}

\begin{theorem}
	\label{thm: continuous_conductance_function}
	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$. Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r}(t) \geq \frac{r}{2^{12} D_K L \sqrt{d}}.
	\end{equation*}
\end{theorem}

Corollary \ref{cor: nonuniform_continuous_conductance} follows \textcolor{red}{almost immediately} for Theorem \ref{thm: continuous_conductance_function}.

\begin{corollary}
	\label{cor: nonuniform_continuous_conductance}
	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$. Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
	\begin{equation*}
	\widetilde{\Phi}_{\Pbb,r}(t) \geq \frac{\lambda_{\sigma}^4 r}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}.
	\end{equation*}
	where we recall $\lambda_{\sigma} = \inf_{x \in \Csig} f(x)$ and $\Lambda_{\sigma} = \sup_{x \in \Csig} f(x)$. 
\end{corollary}

\section{Other results}
\label{sec: other_results}

We state Lemma \ref{lem: local_conductance} without proof. The proof in the uniform case can be found in the 3/20 notes.

\begin{lemma}
	\label{lem: local_conductance}
	Let $x \in \Csig$. Then, for any $r < \frac{\sigma}{2\sqrt{d}}$,
	\begin{equation*}
	\ell_{\Pbb,r}(x) \geq \frac{6\lambda_{\sigma}^2}{25} r^d \nu_d
	\end{equation*}
	and for any $r > 0$,
	\begin{equation*}
	\ell_{\Pbb,r}(x) \leq \Lambda_{\sigma}^2 r^d \nu_d
	\end{equation*}
\end{lemma}

\begin{lemma}
	\label{lem: max_degree} 
	Let 
	\begin{equation*}
	\mu' = \frac{6(n - 1)\lambda_{\sigma}^2}{25} r^d \nu_d,~ \mu = (n-1) \Lambda_{\sigma}^2 r^d \nu_d.
	\end{equation*}
	Then for any $\delta \in [0,1]$,
	\begin{align*}
	\Pr \biggl(\min_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \leq (1 - \delta) \mu' \biggr) \leq (n - 1)\exp\{-\delta^2 \mu' / 2\} \\
	\Pr \biggl(\max_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \geq (1 + \delta) \mu \biggr) \leq (n - 1)\exp\{-\delta^2 \mu / 3\}
	\end{align*}
\end{lemma}
\begin{proof}
	For each $x_i \in \widetilde{\Xbf}_n$, letting $Y_{ij} =  \1(x_j \in \Csig, \norm{x_i - x_j} \leq r)$ we can write $\deg(x_i; \widetilde{G}_{n,r}) = \sum_{i \neq j} Y_{ij}$. Note that $\Ebb(Y_{ij} | x_i) = \ell_{\Pbb,r}(x_i)$, and $Y_ij$ and $Y_{ij'}$ are independent for all $j \neq j'$. Therefore the desired result follows from Lemmas \ref{lem: local_conductance} and \ref{lem: multiplicative_chernoff_bound} along with a union bound. 
\end{proof}

\begin{lemma}
	\label{lem: local_spread_lb}
	With probability one, the following statement holds:
	\begin{equation*}
	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2} 
	\end{equation*}
\end{lemma}
\begin{proof}
	We rewrite
	\begin{align*}
	s(\widetilde{G}_{n,r}) & = \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{\widetilde{\vol}_{n,r}(\widetilde{\Xbf}_n)} \\
	& \geq \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{n \max_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}}
	\end{align*}
	The statement follows by Lemma \ref{lem: max_degree} and the Borel-Cantelli Lemma.
\end{proof}

\begin{lemma}[Multiplicative Chernoff Bound]
	\label{lem: multiplicative_chernoff_bound}
	Let $p', p \in [0,1]$, and let $Y_1, \ldots, Y_n$ be independent $\{0,1\}$-valued random variables with $p' \leq E(Y_i) \leq p$ for all $i = 1,\ldots,n$. Then, letting $\mu = pn$ and $\mu' = p'n$,
	\begin{align*}
	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \leq (1 - \delta)\mu' \biggr) \leq \exp\{-\delta^2 \mu' / 2\} \\
	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \geq (1 + \delta)\mu \biggr) \leq \exp\{-\delta^2 \mu / 3\}
	\end{align*}
	for any $\delta \in [0,1]$.
\end{lemma}

\end{document}

### 2019-04-29 notes/weekly_notes/4.27.19.NotesForWeek.tex
added notes made over the weekend

--- 2019-04-20 notes/weekly_notes/4.12.19.NotesForWeek.tex
@@
 \newcommand{\Csig}{\Cset_{\sigma}}
+\newcommand{\Asig}{\Aset_{\sigma}}
 
@@
 
-\title{Notes for the week of 4/8/19 - 4/12/19}
+\title{Notes for the week of 4/27/19 - 5/3/19}
 \author{Alden Green}
@@
 
-Let $\set{x_1, x_2, \ldots}$ be a sequence of points sampled independently from probability measure $\Pbb$ with density function $f$.
-For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ .
-Given some $\lambda, \sigma > 0$, let
+Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
+Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$.
+
+\begin{theorem}
+	\label{thm: expansion_volume}
+	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
 	\begin{equation*}
-\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
+	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
+	\end{equation*}
+\end{theorem}
+\begin{proof}
+	We will show that for any $\epsilon > 0$, 
+	\begin{equation}
+	\label{eqn: ratio_of_volume}
+	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
+	\end{equation}
+	which is sufficient to prove the claim.
+
+	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ such that
+	\begin{equation*}
+	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon). \tag{$N := N(\epsilon)$}
 	\end{equation*}
 
-Write $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}$ and let $\widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr)$.
-For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
+	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is also compact, $\Asig$ is compact. Moreover,
 	\begin{equation*}
-\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \textrm{where}~ \widetilde{\cut}(S) := \cut(S;\widetilde{G}_{n,r}),~ \widetilde{\vol}(S) := \vol(S;\widetilde{G}_{n,r})
+	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
 	\end{equation*}
-and in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$. Then, the \emph{graph conductance profile} over $\widetilde{G}_{n,r}$ is
+	so by compactness there exists $x_1, \ldots,x_N \in \Aset$ such that
 	\begin{equation*}
-\widetilde{\Phi}_{n,r}(t) := \min_{\substack{S \subseteq \widetilde{\Xbf}_n: \\ 0 < \widetilde{\pi}_n(S) < t} } \widetilde{\Phi}_{n,r}(S)
-\end{equation*}
-where $\widetilde{\pi}_{n,r}(S) = \frac{\widetilde{\vol}(S)}{\widetilde{\vol}(\widetilde{\Xbf}_n)}$. We will prove a lower bound on the graph conductance profile by a continuous analogue.
-
-\subsection{Continuous conductance}
-
-Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. For $\Sset \subset \Rd$ a Borel set,
-\begin{equation*}
-\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
-\end{equation*}
-is the weighted volume.
-
-The $r$-ball walk over $\Csig$ is a Markov chain, with transition probability given by 
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\nu_{\Pbb}(\Sset \cap B(x,r))}{\nu_{\Pbb}(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
-
-Denote the stationary distribution for this Markov chain by $\pi_{\Pbb,r}$, which is defined by the relation
-\begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-Letting the \emph{local conductance} be given by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \nu_{\Pbb}(\Csig \cap B(x,r)) \tag{$x \in \Csig$}
-\end{equation*}
-a bit of algebra verifies that
-\begin{equation*}
-\pi_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
 	\end{equation*}
 
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
+	By the triangle inequality, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$.
+Of course, for each $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
+Summarizing our findings, we have
+	\begin{equation}
+	\label{eqn: finite_subcover}
+	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
+	\end{equation}
+
+	We proceed by giving a lower bound on $\nu(\Asig)$.
+Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and continuing, so that
 	\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\pi_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
+	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
 	\end{equation*}
-the \emph{(continuous) normalized cut} by
+	Of course, by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$. Therefore,
+	\begin{align*}
+	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
+	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))} \\
+	& =: \sigma^d \nu_d \sum_{i = 1}^{N} c_i.
+	\end{align*}
+
+	Now we turn to proving an upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
 	\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2)}{\min \set{\pi_{\Pbb,r}(\Sset),\pi_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-and the \emph{(continuous) conductance profile} by
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$.
-
-To relate the graph and continuous conductance profiles, we introduce mappings between the data $\widetilde{\Xbf}_n$ and the space $\Csig$.
-
-\subsection{Transportation maps and $TL^1$ distance. }
-Let
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*} 
-be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$).
-A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
+	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 1,\ldots,N$}
 	\end{equation*}
 
-If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}.
-Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.
-In fact, under suitable conditions, the convergence happens at rate $\left(\frac{\log n}{n}\right)^{1/d}$.
+	By \eqref{eqn: finite_subcover},
+	\begin{equation*}
+	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
+	\end{equation*}
+	and as a result
+	\begin{align*}
+	\nu(\Aset_{\sigma + \delta}) & \leq \sum_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} \\
+	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
+	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} c_i
+	\end{align*}
+	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
+\end{proof}
 
-\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
-	\label{lem: stagnating_transportation_maps}
-	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
+\section{Additional Theory}
+
+\begin{lemma}
+	\label{lem: covering}
+	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Theorem \ref{thm: expansion_volume},
 	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
-	\end{equation*}
-	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
-\end{lemma}
-
-\begin{definition}
-	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
-	\begin{equation}
-	\label{eqn: transportation_distance_1}
-	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
-	\end{equation}
-	and denote it $u_n \overset{TL^1}{\to} u$.
-\end{definition}
-
-\begin{remark}
-	\label{rmk: transportation_distance_equivalence}
-	Note that as written this is not a metric, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
-	\begin{equation}
-	\label{eqn: transportation_distance_2}
-	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
-	\end{equation}
-	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$.
-However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and
-	\begin{equation*}
-	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
-	\end{equation*}
-
-	Since this additional condition will be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}.
-See \textcolor{red}{Garcia Trillos 15} for more details.
-\end{remark}
-
-\section{Lower bound graph conductance profile}
-
-In order to lower bound the graph conductance profile $\widetilde{\Phi}_{n,r}(\cdot)$, we will need to split the analysis into two cases based on the size of $S \subseteq \widetilde{\Xbf}_n$.
-Define the \emph{graph local spread} to be
-\begin{equation*}
-s(G) := \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \cdot \min_{u \in V} \set{\pi(u;G)}.  \tag{$G = (V,E)$}
-\end{equation*}
-
-Theorem \ref{thm: graph_conductance_profile_lb_1} states that for subsets of $\widetilde{\Xbf}_n$ with volume at least $s(G)$, the graph normalized cut can be uniformly lower bounded by the continuous normalized cut.
-Sections \ref{sec: proof_and_supporting_theory} and \ref{sec: other_results} contains the proof of Theorem \ref{thm: graph_conductance_profile_lb_1} along with other relevant results.
-
-\begin{theorem}
-	\label{thm: graph_conductance_profile_lb_1}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then,
-	\begin{equation*}
-	\liminf_{n \to \infty} \Bigl\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \Bigr\} \geq \frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}
-	\end{equation*}
-	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \widetilde{\Xbf}_n: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$
-\end{theorem}
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb_1}
-	Let $G = (V,E)$ be an undirected graph, and $\mathcal{L}(G) = \set{S \subseteq V: \pi(S; G) \geq s(G)}$. Then,
-	\begin{equation*}
-	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
+	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
 	\end{equation*}
@@
 \begin{proof}
-	Clearly, for any $u \in S$
+	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
+	\begin{equation*}
+	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
+	\end{equation*}
+	since then
+	\begin{equation*}
+	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}).
+	\end{equation*}
+
+	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
 	\begin{equation}
-	\label{eqn: graph_conductance_profile_lb_1}
-	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \abs{S}
+	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
 	\end{equation}
-
-	Then, since $\pi(S;G) \leq s(G)$,
+	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
+Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
 	\begin{equation*}
-	\abs{S} \leq \pi(S;G) \cdot \frac{\vol(V;G)}{\min_{u \in V} \set{\mathrm{deg}(u;G)}} = \frac{\pi(S;G)}{\min_{u \in V} \set{\pi(u;G)}} \leq \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)},
+	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
 	\end{equation*}
-	and therefore by \eqref{eqn: graph_conductance_profile_lb_1}, for any $u \in S$
-	\begin{equation*}
-	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \geq \frac{1}{10}\deg(u;G)
-	\end{equation*}
-	and the statement follows by summing over all $u \in S$. 
+	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
 \end{proof}
 
-Theorem \ref{thm: graph_conductance_profile_lb_1} and Lemma \ref{lem: graph_conductance_profile_lb_1} together yield Corollary \ref{cor: graph_conductance_profile_lb}, the main result of these notes.
-
-\begin{corollary}[Lower bound on graph conductance profile]
-	\label{cor: graph_conductance_profile_lb}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$.
-Then, with probability one the following asymptotic lower bound holds on the graph conductance function
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\set{\frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}, \frac{1}{10}} \tag{$0 \leq t \leq \frac{1}{2}$}
-	\end{equation*}
-\end{corollary}
-
-\section{Proofs and Supporting Theory}
-\label{sec: proof_and_supporting_theory}
-
-\subsection{Proof of Theorem \ref{thm: graph_conductance_profile_lb_1}.}
-
-By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
-
-For $S \subseteq \widetilde{\Xbf}_n$, let $T_n^{-1}(S) = \set{x \in \Csig: T_n(x) \in S}$ be the preimage of $T_n$, and note that $T_n^{-1}(S^c) = \Csig \setminus T_n^{-1}(S)$.
-
-Letting
-\begin{equation*}
-\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx},~ \gamma_n(S) := \frac{\min \set{\pi_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\pi_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
-\end{equation*}
-where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, by Lemma \ref{lem: graph_to_continuous_conductance} and Corollary \ref{cor: nonuniform_continuous_conductance} we have that for all $S \subseteq \widetilde{\Xbf}_n$,
-\begin{align}
-\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
-& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^4r_n^{-}}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
-\end{align}
-
-By Lemma \ref{lem: cont_local_conductance}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \xi_n = 1.
-\end{equation*}
-
-By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $c > \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}$, there exists some $n \in \Naturals$ such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
-\begin{equation*}
-\pi_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
-\end{equation*}
-and therefore by Lemma \ref{lem: cont_stationary_dist}
-\begin{equation*}
-\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
-\end{equation*}
-
-As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
-
-\subsection{Graph functionals to continuous functionals.}
-
-Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
-
-\begin{lemma}
-	\label{lem: volume_bound}
-	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
-	\end{equation*}
-	where $r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$. 
-\end{lemma}
-\begin{proof}
-	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	u(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	Now, we proceed
-	\begin{align}
-	\frac{1}{\widetilde{n}^2} \widetilde{\vol}(S_n) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i)} \nonumber \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \label{eqn: vol_ub}\\
-	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
-	\end{align}
-
-	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
-	\begin{align*}
-	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
-	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) dx \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
-	\end{align*}
-	which is the desired upper bound. The lower bound follows a similar proof, with the only change being \eqref{eqn: vol_ub}, where $r_n^+$ is replaced by $r_n^-$ and the inequality is reversed.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: cut_bound}
-	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c) 
-	\end{equation*}
-	where $r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^\infty(\widetilde{\Pbb})}$
-\end{lemma}
-\begin{proof}
-	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	u(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
-	\begin{align*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i) - u(x_j)} \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x) - u(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
-	\end{align*}
-	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
-	\begin{align*}
-	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{align*}	
-\end{proof}
-
-\begin{lemma}
-	\label{lem: graph_to_continuous_conductance}
-	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and let
-	\begin{equation*}
-	r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})},~ r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}.
-	\end{equation*}
-
-	Fix $S \subseteq \widetilde{\Xbf}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
-	\begin{equation}
-	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}  \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
-	\end{equation}
-\end{lemma}
-\begin{proof}
-
-	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\widetilde{\vol}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset)}
-	\end{equation*}
-
-	But, noting that $\Sset^c = \set{x \in \Csig: T_n(x) \in S^c}$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S^c)}{\widetilde{\vol}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\pi_{\Pbb,r_n^+}(\Sset^c)}
-	\end{equation*}
-	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} },
-	\end{equation*}
-	and the proof is complete.
-\end{proof}
-
-\subsection{Perturbation asymptotics.}
-
-In light of Lemma \ref{lem: stagnating_transportation_maps}, the error incurred in \eqref{eqn: graph_to_continuous_conductance} by the use of $r_n^{+}$ and $r_n^{-}$ as opposed to $r$ is asymptotically negligible.
-
-\begin{lemma}[Continuity of local conductance]
-	\label{lem: cont_local_conductance}
-	Letting $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, with probability one the following holds:
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx + \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx.
-	\end{equation*}
-	and therefore
-	\begin{equation*}
-	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}. 
-	\end{equation*}
-	We upper bound the remainder term
-	\begin{equation*}
-	\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d
-	\end{equation*}
-	and taking limits as $n \to \infty$ we obtain with probability one
-	\begin{equation*}
-	\limsup_{n \to \infty} \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \limsup_{n \to \infty} P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d = 0
-	\end{equation*}
-	by the stagnating property of $\seq{T_n}$.
-
-	We apply a similar analysis to the denominator.
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) dy dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d
-	\end{equation*}
-	and therefore by the stagnating property of $\seq{T_n}$ and Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\liminf_{n \to \infty} \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx  = \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
-	\end{equation*}
-	again with probability one.
-
-	The desired result then follows from an application of Slutsky's Theorem.
-\end{proof}
-
-\begin{lemma}[Continuity of stationary distribution]
-	\label{lem: cont_stationary_dist}
-	Let $c > 0$ be a fixed constant, $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-With probability one the following statement holds:
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } = 1
-	\end{equation*}
-	uniformly over all sets $\Sset \subseteq \mathfrak{B}(\Csig)$ satisfying $\min \set{\pi_{\Pbb,r}(\Sset), \pi_{\Pbb,r}(\Sset^c)}> c$. 
-\end{lemma}
-\begin{proof}
-	It will be sufficient to show that
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} ~ \text{and} \liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset^c)} = 1.
-	\end{equation*}
-	and we will show only that $\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1$. The result for $\Sset^c$ is identical.
-
-	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
-	\begin{equation*}
-	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
-	\end{equation*}
-	Rewriting
-	\begin{equation*}
-	 \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\pi_{\Pbb,r_n^+}(\Sset)}
-	\end{equation*}
-	we have that
-	\begin{equation*}
-	\liminf_{n \to \infty} \int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \Pbb(\Sset) \Lambda_{\sigma} \liminf_{n \to \infty}\bigl( (r_n^+)^d - (r_n^-)^d\bigr) \nu^d = 0
-	\end{equation*}
-	where the equality occurs with probability one. On the other hand by hypothesis
-	\begin{equation*}
-	\limsup_{n \to \infty} \pi_{\Pbb,r_n^+}(\Sset) \geq c > 0.
-	\end{equation*}
-	and the result follows by Slutsky's Theorem. 
-\end{proof}
-
-\begin{lemma}[Stationary distribution lower bound]
-	\label{lem: stationary_dist_lb}
-	With probability one, the following statement holds: let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$.
-Then, for any $\epsilon > 0$, there exists some $m \in \Naturals$ such that for all $n \geq m$,
-	\begin{equation*}
-	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \pi_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}  - \epsilon
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary. Write $\Sset := T_n^{-1}(S)$.
-
-	We can upper bound $\widetilde{\pi}_{n,r}(S)$ by $\pi_{\Pbb,r}(\Sset)$ plus a remainder term.
-	\begin{align}
-	\widetilde{\pi}_{n,r}(S) & \leq \frac{\int_\Sset \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \nonumber \\
-	& = \pi_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x- x'} \leq r_n^+) f(x') f(x) dx' dx} \label{eqn: stationary_dist_lb_1}
-	\end{align}
-	Clearly $\pi_{\Pbb,r_n^-}(\Sset) \leq \pi_{\Pbb,r}(\Sset)$. Moreover
-	\begin{equation*}
-	\frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	and by \eqref{eqn: stationary_dist_lb_1}, we have
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \pi_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	The remainder term $\frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d$ is independent of $S$ and asymptotically $o_p(1)$ by Lemma \ref{lem: stagnating_transportation_maps}.
-	An application of Lemma \ref{lem: local_spread_lb} completes the proof.
-\end{proof}
-
-\subsection{Continuous conductance function.}
-
-In Theorem \ref{thm: continuous_conductance_function}, we restate a necessary result from the 3/20 weekly notes.
-
-\begin{assumption}[Embedding]
-	\label{asmp: embedding}
-	Assume there exists $K \subset \Rd$ convex space, mapping $g: K \to \Csig$, and constant $L < \infty$ such that
-	\begin{equation*}
-	\forall x,y \in K,  \abs{g(x) - g(y)} \leq L \abs{x - y},~\text{and}~ \det(D_x g) = 1.
-	\end{equation*}
-	In other words, $g$ is measure-preserving and $L$-Lipschitz.
-\end{assumption}
-
-\begin{theorem}
-	\label{thm: continuous_conductance_function}
-	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$.
-Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r}(t) \geq \frac{r}{2^{12} D_K L \sqrt{d}}.
-	\end{equation*}
-\end{theorem}
-
-Corollary \ref{cor: nonuniform_continuous_conductance} follows \textcolor{red}{almost immediately} for Theorem \ref{thm: continuous_conductance_function}.
-
-\begin{corollary}
-	\label{cor: nonuniform_continuous_conductance}
-	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$.
-Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r}(t) \geq \frac{\lambda_{\sigma}^4 r}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}.
-	\end{equation*}
-	where we recall $\lambda_{\sigma} = \inf_{x \in \Csig} f(x)$ and $\Lambda_{\sigma} = \sup_{x \in \Csig} f(x)$. 
-\end{corollary}
-
-\section{Other results}
-\label{sec: other_results}
-
-We state Lemma \ref{lem: local_conductance} without proof. The proof in the uniform case can be found in the 3/20 notes.
-
-\begin{lemma}
-	\label{lem: local_conductance}
-	Let $x \in \Csig$. Then, for any $r < \frac{\sigma}{2\sqrt{d}}$,
-	\begin{equation*}
-	\ell_{\Pbb,r}(x) \geq \frac{6\lambda_{\sigma}^2}{25} r^d \nu_d
-	\end{equation*}
-	and for any $r > 0$,
-	\begin{equation*}
-	\ell_{\Pbb,r}(x) \leq \Lambda_{\sigma}^2 r^d \nu_d
-	\end{equation*}
-\end{lemma}
-
-\begin{lemma}
-	\label{lem: max_degree} 
-	Let 
-	\begin{equation*}
-	\mu' = \frac{6(n - 1)\lambda_{\sigma}^2}{25} r^d \nu_d,~ \mu = (n-1) \Lambda_{\sigma}^2 r^d \nu_d.
-	\end{equation*}
-	Then for any $\delta \in [0,1]$,
-	\begin{align*}
-	\Pr \biggl(\min_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \leq (1 - \delta) \mu' \biggr) \leq (n - 1)\exp\{-\delta^2 \mu' / 2\} \\
-	\Pr \biggl(\max_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \geq (1 + \delta) \mu \biggr) \leq (n - 1)\exp\{-\delta^2 \mu / 3\}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	For each $x_i \in \widetilde{\Xbf}_n$, letting $Y_{ij} =  \1(x_j \in \Csig, \norm{x_i - x_j} \leq r)$ we can write $\deg(x_i; \widetilde{G}_{n,r}) = \sum_{i \neq j} Y_{ij}$.
-Note that $\Ebb(Y_{ij} | x_i) = \ell_{\Pbb,r}(x_i)$, and $Y_ij$ and $Y_{ij'}$ are independent for all $j \neq j'$.
-Therefore the desired result follows from Lemmas \ref{lem: local_conductance} and \ref{lem: multiplicative_chernoff_bound} along with a union bound.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: local_spread_lb}
-	With probability one, the following statement holds:
-	\begin{equation*}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2} 
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We rewrite
-	\begin{align*}
-	s(\widetilde{G}_{n,r}) & = \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{\widetilde{\vol}_{n,r}(\widetilde{\Xbf}_n)} \\
-	& \geq \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{n \max_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}}
-	\end{align*}
-	The statement follows by Lemma \ref{lem: max_degree} and the Borel-Cantelli Lemma.
-\end{proof}
-
-\begin{lemma}[Multiplicative Chernoff Bound]
-	\label{lem: multiplicative_chernoff_bound}
-	Let $p', p \in [0,1]$, and let $Y_1, \ldots, Y_n$ be independent $\{0,1\}$-valued random variables with $p' \leq E(Y_i) \leq p$ for all $i = 1,\ldots,n$. Then, letting $\mu = pn$ and $\mu' = p'n$,
-	\begin{align*}
-	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \leq (1 - \delta)\mu' \biggr) \leq \exp\{-\delta^2 \mu' / 2\} \\
-	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \geq (1 + \delta)\mu \biggr) \leq \exp\{-\delta^2 \mu / 3\}
-	\end{align*}
-	for any $\delta \in [0,1]$.
-\end{lemma}
-
 \end{document}

### 2019-04-29 arxiv/arxiv_local_density_clustering.tex
added arxiv version of paper

--- 2019-01-23 icml/icml_local_density_clustering.tex
@@
-%%%%%%%% ICML 2019 submission %%%%%%%%%%%%%%%%%
+%%%%%%%% Local Spectral Clustering of Density Upper Level Sets %%%%%%%%%%%%%%%%%
 
 \documentclass{article}
-
-\usepackage{icml2019}
-% \usepackage[accepted]{icml2019}
-
 \usepackage{microtype}
@@
 \usepackage{booktabs}
+\usepackage{xr-hyper}
 \usepackage{hyperref}
@@
 \usepackage{amsfonts, amsthm, amssymb}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage{graphicx}
@@
 \usepackage{bm}
+\usepackage{fullpage}
+
+\usepackage[square,sort,comma,numbers]{natbib}
+\renewcommand{\bibname}{REFERENCES}
+\renewcommand{\bibsection}{\subsubsection*{\bibname}}
 
@@
 \newtheorem{remark}{Remark}
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-%%%%%
-\icmltitlerunning{Local Spectral Clustering of Density Upper Level Sets}
 
@@
 
-\twocolumn[
-\icmltitle{Local Spectral Clustering of Density Upper Level Sets}
-\icmlsetsymbol{equal}{*}
-
-\begin{icmlauthorlist}
-\icmlauthor{Alden Green}{cmu}
-\icmlauthor{Sivaraman Balakrishnan}{cmu}
-\icmlauthor{Ryan J. Tibshirani}{cmu}
-\end{icmlauthorlist}
-
-\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon
-  University, Pittsburgh PA, USA} 
-\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
-\icmlkeywords{local clustering}
-
-\vskip 0.3in
-]
-
-\printAffiliationsAndNotice{}
+\title{Local Spectral Clustering of Density Upper Level Sets}
+\author{Alden Green, Sivaraman Balakrishnan, and Ryan Tibshirani}
+\date{\today}
+\maketitle
 
@@
 algorithm is Personalized PageRank (PPR), first introduced by
-\citet{haveliwala2003}, and further developed by
-\citet{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
+\citep{haveliwala2003}, and further developed by
+\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
 among others.
@@
 classical statistical literature on clustering, dating back to
-\citealt{hartigan1981}).
+\citet{hartigan1981}).
 
@@
 respect to $G=(V,E,w)$.  There are many graph-based measures of cluster quality  
-that one could consider; see, e.g., \citet{yang2015,fortunato2010} for 
+that one could consider; see, e.g., \citep{yang2015,fortunato2010} for 
 an overview.  The pair of criteria that we focus on are (arguably) quite
@@
 originating at $v$.\footnote{Given a starting node $v$ and and a random walk
-  defined by transition probability matrix $\mathbf{P}$, the rotation $e_v
+  defined by transition probability matrix $\mathbf{P}$, the notation $e_v
   \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
@@
 random walk over $G[S]$ to mix (approach the stationary distribution)
-uniformly over $S$.  For this, we first define \emph{relative pointwise mixing
+uniformly over $S$.  For this, we first define the \emph{relative pointwise mixing
   time} of $G[S]$ as 
@@
       \widetilde\pi_u|}{\widetilde\pi_u} \leq \frac{1}{4}, 
-    \; \text{for $u,v \in V$}},  
+    \; \text{for $u,v \in V$}}. 
 $$
@@
 \Psi)$-cluster (or partition) for a given graph $G$.\footnote{In the case of
-  \citet{kannan04}, the internal connectivity parameter $\phi$ is actually the
+  \citep{kannan04}, the internal connectivity parameter $\phi$ is actually the
   conductance, i.e., the minimum normalized cut within the subgraph $G[S]$. See
@@
 \smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citet{zhu2013}.}
+algorithms, see, e.g., \citep{zhu2013}.}
 we output a cluster \smash{$\widehat{C} = S_{\beta^*}$}, based on the sweep cut
@@
   \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
-  inverse mixing time of a random walk over $\Csig[\Xbf]$.  We also provide in 
-  Theorem \ref{thm: inverse_mixing_time_lower_bound} a tighter lower bound, but
-  under more restrictive assumptions (convexity of $\Csig$).
+  inverse mixing time of a random walk over $\Csig[\Xbf]$.
 
@@
   Theorem \ref{thm: consistent_recovery_of_density_clusters} that these bounds
-  in bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+  in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
     inverse_mixing_time_lower_bound_nonconvex},
@@
     inverse_mixing_time_lower_bound_nonconvex}, along with the results in 
-  \citet{zhu2013}, lead to alternative, graph-theoretic guarantees on cluster 
+  \citep{zhu2013}, lead to alternative, graph-theoretic guarantees on cluster 
   quality: an upper bound on the normalized cut of the estimated cluster 
@@
 Building on earlier work of
-\citet{koltchinskii2000}, \citet{vonluxburg2008,hein2005} studied the limiting behaviour of spectral clustering
+\citep{koltchinskii2000}, \citep{vonluxburg2008,hein2005} studied the limiting behaviour of spectral clustering
 algorithms. These authors show that when samples are obtained from a
@@
 
+% AJG 4/29: I need to rewrite to explain how its similar, because
+% this is a good opportunity to show that implications
+% of the type given in our work are broadly of interest.
+
 Perhaps most similar to our results are the works
-\citet{vempala2004,shi2009,schiebinger2015}, who study the consistency of
+\citep{vempala2004,shi2009,schiebinger2015}, who study the consistency of
 spectral algorithms in recovering the latent labels in certain parametric and
@@
 density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the closed
-ball of radius $r \geq 0$, centered at $x \in \Rd$.  Given a set $\Aset
+ball of radius $r > 0$, centered at $x \in \Rd$.  Given a set $\Aset
 \subseteq \Rd$ and $\sigma > 0$, define $\Asig = \Aset + B(0,\sigma) = \{y \in
 \Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma\}$, which we call the
-$\sigma$-expansion of $\Aset$.
+$\sigma$-expansion of $\Aset$. For a differentiable function $g: \Rd \to \Rd$, write $\nabla g(x)$ to denote the Jacobian of $g$ evaluated at $x \in \Rd$.
 
-We are now ready to give the conditions, stated with respect to a density
-cluster $\Cset \in \Cbb_f(\lambda)$, for some threshold $\lambda > 0$, and an
+We are now ready to give our required conditions, stated with respect to a density
+cluster $\Cset \in \Cbb_f(\lambda)$ for some threshold $\lambda > 0$, and an
 expansion parameter $\sigma > 0$.
@@
 \label{asmp: low_noise_density}
-\emph{Low noise density:} There exists $\gamma > 0$ such that for all $x
+\emph{Low noise density:} There exists $\gamma,c_0 > 0$ such that for all $x
 \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
 $$
-  \inf_{x' \in \Csig} f(x') - f(x) \geq  \dist(x, \Csig)^{\gamma},
+  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma},
 $$
 where \smash{$\dist(x,\Aset) = \inf_{x_0 \in \Aset} \norm{x - x_0}$}.
-% RJT: should we change this to c_0?  c_1 seems to be used below and throughout
-% for other constants, and c_0 is not used
 
@@
 \emph{Cluster separation:}
-For all $\Cset' \in \Cbb_f(\lambda)$,
+For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$,
 $$
@@
 $$
+
+\item
+\label{asmp: biLipschitz_mapping}
+\emph{biLipschitz mapping to convex set:}
+There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
+\begin{equation*}
+\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
+\end{equation*}
+such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
 \end{enumerate}
@@
 
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
-\ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
-G_{n,r})$, whereas \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
-are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
+Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
+\ref{asmp: cluster_separation} and \ref{asmp: biLipschitz_mapping} are used to upper bound $\Phi(\Cset[\Xbf];
+G_{n,r})$, whereas \ref{asmp: bounded_density}, \ref{asmp: cluster_diameter} and \ref{asmp: biLipschitz_mapping} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
 lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
 cluster_separation} are similar to the $(\sigma,\epsilon)$-saliency of
-\citet{chaudhuri2010}, a standard density clustering assumption, while
-\ref{asmp: low_noise_density} is seen in, e.g., \citet{singh2009} (as well as
+\citep{chaudhuri2010}, a standard density clustering assumption, while
+\ref{asmp: low_noise_density} is seen in, e.g., \citep{singh2009} (as well as
 many other works on density clustering and level set estimation.)  It is worth
 highlighting that these assumptions are all local in nature, a benefit of
-studying a local algorithm such as PPR.
+studying a local algorithm such as \ppr.
+
+%%% AJG 4/29: My attempt to explain why our results aren't fatuous.
+
+We also note that while many of these geometric conditions are typical in the density clustering literature, the restrictions we will impose upon them in order to obtain meaningful implications for \pprspace will not be.
+This is natural.
+The spectral algorithm we consider is not specifically designed for the task of level set estimation, and in fact one should expect \pprspace to fail to recover -- either in the sense of \eqref{eqn: consistent_density_cluster_recovery}, or indeed any reasonable notion of cluster recovery -- a density cluster of sufficiently large diameter or sufficiently small thickness (though we do not provide any lower bounds to this effect).
+Indeed, one of the primary motivations of this work was to better understand and characterize the distinctions between those level sets which are well conditioned for spectral algorithms, and those which are not.
 
@@
 $B=B(0,1)$.
-% RJT: you had B(0,d) before ... just check this should have been B(0,1) 
-% AJG: Yep.
 
@@
 We start with an upper bound on the normalized cut \eqref{eqn: norm_cut} of 
-$\Cset_\sigma[\Xbf]$. (In the theorem, the upper bound on the density in
+$\Cset_\sigma[\Xbf]$. (In Theorem \ref{thm: conductance_upper_bound}, the upper bound on the density in
 Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
-the parameter $\Lambda_\sigma>0$ from the theorem statement.)
+the parameter $\Lambda_\sigma>0$ from the theorem statement.) For $\mathcal{S} \subseteq \Reals^d$ and $r > 0$, let
+\begin{equation*}
+\pi_{\Pbb,r}(\mathcal{S}) := \frac{\int_{\mathcal{S}} \Pbb(B(x,r)) f(x) dx }{\int_{\Rd} \Pbb(B(x,r)) f(x) dx}.
+\end{equation*}
 
@@
 Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and
-\ref{asmp: cluster_separation}, for some 
-$\sigma, \lambda_{\sigma}, c_1, \gamma > 0$. Moreover, let
+Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
+and \ref{asmp: cluster_separation}, for some 
+$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/4d$ be such that
 \begin{equation}
 \label{eqn: weighted_cluster_volume}
-\nu_{\Pbb}(\Csig) \leq \frac{1}{2}
+\pi_{\Pbb,r}(\Csig) \leq \frac{1}{2}.
 \end{equation}
-where $\nu_{\Pbb}(\Aset) = \int_{\Aset} f(x) dx$ for $\Aset \subset \Rd$.
- Then for any $0 < r <
-\sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and
+ Then for any $0 < \delta < 1$, $\epsilon > 0$, if
 \begin{equation}
 \label{eqn: conductance_sample_complexity}
-n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}
-  { \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
+n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
+  {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
 \end{equation}
-we have
+then
 \begin{equation}
   \label{eqn: conductance_additive_error_bound}
-  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq 4 c_{\sigma} d
+  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq \frac{4d}{\sigma}
   \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-    \frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
+    c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
 \end{equation}
-with probability at least $1-\delta$, where $c_{\sigma} = 1 / \sigma$. 
+with probability at least $1-\delta$.
 \end{theorem}
@@
 idea is that for any $x \in \Cset$, the simple (possibly loose) fact
-$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Cset_{\sigma
-  + r}) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
+$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Csig + rB) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
   low_noise_density} to find a corresponding bound on the weighted volume,
@@
   machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
-  to yield an alternative result. In recent work, \citet{abbasi17} developed new
+  to yield an alternative result. In recent work, \citep{abbasi-yadkori2016} developed new
   population-level bounds on the conductance function (without requiring
@@
 
-\section{Empirical Performance of PPR on Gaussian Mixture Models}
+\section{Experiments}
 \label{sec: experiments}
-
-The assumptions and theory of Section \ref{sec: cluster_quality_bounds} -- and therefore Section \ref{sec: consistent_cluster_estimation_with_ppr} as well-- are tailored towards density functions with sharp transitions in gradient around the perimeter of the density cluster.
-These type of functions will satisfy \ref{asmp: bounded_density} with a small ratio of $\Lambda_{\sigma}$ to $\lambda_{\sigma}$, while still satisfying \ref{asmp: low_noise_density}, potentially for $\gamma << 1$.
-
-\begin{figure*}
-	\begin{center}
-		\centerline{\includegraphics[width=\columnwidth, height = 3 in]{graphic_1}}
-		\caption{Algorithm \ref{alg: ppr} run over 4 example datasets.
-Parameters $\alpha$ and $\pi_0$ were tuned to minimize normalized cut of output set.
-Colors represent \pprspace cuts; shapes correspond to the maximum density among mixture components.
-Sample size $n = 400$.}
-		\label{fig: graphic_1}
-	\end{center}
-\end{figure*}
-
-As mentioned previously, one line of work on spectral algorithms assesses their performance on mixture models.
-Particularly well-developed is the characterization of clustering performance on Gaussian Mixture Models (GMMs).
-Gaussian Mixture Models have smooth derivatives, and are therefore not good candidates for our work (at least, for reasonable values of the parameters in \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} ).
-Since they are a classical choice in the clustering literature, we investigate \pprspace performance on them empirically.
-
-Figure \ref{fig: graphic_1} shows data generated from four different Gaussian mixture models.
-The story follows roughly the same narrative as our theoretical work.
-The left two plots demonstrate instances, in one and two-dimensions, respectively, where the \pprspace cut has small error relative to a density cut.
-The right two plots, by contrast, show \pprspace failing to recover, even approximately, a density cut.
-
-In the top right panel, the leftmost density cluster has a smaller cutsize than the set \pprspace ultimately recovers.
-However, the recovered set (colored in blue) has a higher volume, and therefore a lower normalized cut.
-
-The bottom right panel shows the effect of a high diameter on the performance of \pprspace.
-Although any one vertex on the boundary of a density level set may have few cut edges, the length of the boundary is sufficiently long to make the entire cut too large for \pprspace to select it.
-Instead, the \pprspace cut defaults to a more geometrically compact shape, which has much smaller (unweighted) perimeter.
-
-We also wish to investigate the robustness of these results to clustering problems with differing levels of difficulty. Consider the following mean vector and covariance matrices
-\begin{align*}
-(\bm{\mu}_1, \bm{\mu}_2) & = \bigl((0,0), (\theta,\theta) \bigr) \\
-\bm{\Sigma}^{(1)} & = 
-\begin{bmatrix}
-1/64 & 0 \\
-0 & 1/64
-\end{bmatrix} \\
-\bm{\Sigma}^{(2)} & = 
-\begin{bmatrix}
-9/128 & -7/128 \\
--7/128 & 9/128
-\end{bmatrix}.
-\end{align*}
-For a given choice of $\theta$, let $f_1^{(\theta)}$ and $f_2^{(\theta)}$ be two-component Gaussian mixture densities supported on $\Reals^2$, defined as
-\begin{align*}
-f_1^{(\theta)}(x) & = \frac{1}{2} \phi_{\bm{\mu}_1,\bm{\Sigma}^{(1)}}(x) + \frac{1}{2} \phi_{\bm{\mu}_2;\bm{\Sigma}^{(1)}}(x) ~~ (\text{isotropic model}) \\
-f_2^{(\theta)}(x) & = \frac{1}{2} \phi_{\bm{\mu}_1,\bm{\Sigma}^{(2)}}(x) + \frac{1}{2} \phi_{\bm{\mu}_2,\bm{\Sigma}^{(2)}}(x) ~~  (\text{anisotropic model})
-\end{align*}
-where $\phi_{\bm{\mu},\bm{\Sigma}}(x)$ is the bivariate Gaussian density with mean vector $\bm{\mu}$ and covariance matrix $\bm{\Sigma}$, evaluated at $x$.
-
-For a given value of $\theta$ we can compute the symmetric set difference between the output of Algorithm \ref{alg: ppr}, initialized near the origin, and the \emph{oracle clusters}
-\begin{align*}
-C_1^{(\theta)} & = \set{x: \phi_{\bm{\mu}_1,\bm{\Sigma}^{(1)}}(x) \geq \phi_{\bm{\mu}_2;\bm{\Sigma}^{(1)}}(x)} \\
-C_2^{(\theta)} & = \set{x: \phi_{\bm{\mu}_1,\bm{\Sigma}^{(2)}}(x) \geq \phi_{\bm{\mu}_2;\bm{\Sigma}^{(2)}}(x)}
-\end{align*}
-(While these oracle clusters are not precisely density clusters as we have defined them, they exhibit similar behavior.)
-For a sequence of $\theta$, we generate data from, for instance, density $f_i^{(\theta)}$, run Algorithm \ref{alg: ppr} (with hyperparameters tuned for lowest normalized cut) with output set $\widehat{C}_i$, and compute the symmetric set difference
-\begin{equation*}
-\Delta(\widehat{C}_i, C_i^{(\theta)}) = \max\left\{\frac{\abs{C_i^{(\theta)} \setminus \widehat{C}_i}}{\abs{C_i^{\theta}}}, \frac{\abs{\widehat{C}_i \setminus C_i^{\theta}}}{|\widehat{C}_i|} \right\}.
-\end{equation*}
-Figure \ref{fig: graphic_2} plots the relationship between $\sqrt{2}\theta = \norm{\bm{\mu_2} - \bm{\mu_1}}_2$ and the symmetric set difference $\Delta(\widehat{C}_i, C_i^{(\theta)})$ for $i = 1,2$.
-As we can see, for sufficiently large values of $\theta$, \pprspace agrees with the oracle cluster in both the isotropic and anisotropic GMM models, while for sufficiently small values of $\theta$ it fails to even approximately recover the oracle cluster in either case.
-Throughout, the performance is superior for the isotropic model as opposed to the anisotropic one, as we would expect.
-\begin{figure}[!tb]
-	\vskip 0.2in
-	\begin{center}
-		\centerline{\includegraphics[width=\columnwidth, height = 3 in]{graphic_2}}
-		\caption{Symmetric set difference of Algorithm \ref{alg: ppr} run over GMM models with isotropic and anistropic component densities, as the distance between cluster centers changes.}
-		\label{fig: graphic_2}
-	\end{center}
-	\vskip 0.2in
-\end{figure}
 
@@
 
-\bibliography{icml_bib}
-\bibliographystyle{icml2019}
+\bibliographystyle{plainnat}
+\bibliography{../local_spectral_bibliography}
 
 \end{document}
-
-% This document was modified from the file originally made available by
-% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
-% by Iain Murray in 2018, and modified by Alexandre Bouchard in
-% 2019. Previous contributors include Dan Roy, Lise Getoor and Tobias
-% Scheffer, which was slightly modified from the 2010 version by
-% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
-% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
-% slightly modified from Prasad Tadepalli's 2007 version which is a
-% lightly changed version of the previous year's version by Andrew
-% Moore, which was in turn edited from those of Kristian Kersting and
-% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2019-04-29 arxiv/arxiv_local_density_clustering_proofs.tex
added arxiv version of paper

--- 2019-01-23 icml/icml_local_density_clustering_supplement.tex
@@
 \documentclass{article}
-
-% \usepackage{icml2019}
-% \usepackage[accepted]{icml2019}
-
 \renewcommand{\thesection}{\Alph{section}}
@@
 \usepackage[shortlabels]{enumitem}
-\usepackage{xr-hyper}
 % \usepackage{hyperref}
@@
 \usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+\usepackage{xr-hyper}
 \usepackage{natbib}
-
-\externaldocument{icml_local_density_clustering}
+\usepackage{fullpage}
+
+\let\pprspace\relax
+\externaldocument{arxiv_local_density_clustering}
 
@@
 
-We will fix $\Aset \subset \Rd$ to be an arbitrary set.
-To simplify expressions, for the $\sigma$-expansion $\Asig$, we will write the set difference between $\Asig$ and the $(\sigma + r)$-expansion $\Aset_{\sigma + r}$ as
-\begin{equation*}
-\Asigr := \set{x: 0 < \dist(x, \Asig) \leq r},
-\end{equation*}
-where as a reminder $\dist(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
-
-For notational ease, we write
-\begin{align*}
-\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}}
-\end{align*}
-for the random variable, mean, and probability of cut size and volume, respectively.
-
-We state Lemma \ref{lem: expansion_sets} without proof, as it is trivial.
-We formally include it mainly to comment on its (potential) suboptimality; for sets $\Aset$ with diameter much larger than $\sigma$, the volume estimate of Lemma \ref{lem: expansion_sets} will be quite poor.
-
-\begin{lemma}
-	\label{lem: expansion_sets}
-	For any $\delta > 0$ and $x \in \Aset_{\sigma}$,
-	\begin{equation*}
-	\sigma B \subset \Asig, ~~\mathrm{and~ }\nu(\Asig + \delta B) \leq \nu\left(\left[1 + \frac{\delta}{\sigma}\right]\Asig\right) = \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig)
-	\end{equation*}
-	where $\Asig = \Aset + \sigma B$ is the $\sigma$-expansion of $\Aset$.
-\end{lemma}
-
-We will need to carefully control the volume of the expansion set using the above estimate; Lemma \ref{lem: Taylor_series} serves this purpose.
+Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
+Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
+
+\begin{lemma}
+	\label{lem: expansion_volume}
+	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
+	\begin{equation*}
+	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We will show that for any $\epsilon > 0$, 
+	\begin{equation}
+	\label{eqn: ratio_of_volume}
+	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
+	\end{equation}
+	which is sufficient to prove the claim.
+
+	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ such that
+	\begin{equation*}
+	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon). \tag{$N := N(\epsilon)$}
+	\end{equation*}
+
+	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is itself compact, $\Asig$ is compact. Moreover,
+	\begin{equation*}
+	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
+	\end{equation*}
+	so by compactness there exists $x_1, \ldots,x_N \in \Aset$ such that
+	\begin{equation*}
+	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
+	\end{equation*}
+
+	By the triangle inequality, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$.
+Of course, for each $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
+Summarizing our findings, we have
+	\begin{equation}
+	\label{eqn: finite_subcover}
+	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
+	\end{equation}
+
+	We next show a lower bound on $\nu(\Asig)$.
+Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and continuing, so that
+	\begin{equation*}
+	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
+	\end{equation*}
+	Observe that $\bigcup_{i = 1}^{N} \Asig^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$.
+As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
+	\begin{align*}
+	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
+	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	We turn to proving an upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
+	\begin{equation*}
+	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
+	\end{equation*}
+
+	As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
+	\begin{equation*}
+	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
+	\end{equation*}
+	and therefore
+	\begin{align*}
+	\nu(\Aset_{\sigma + \delta}) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
+	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
+	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: covering}
+	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Theorem \ref{lem: expansion_volume},
+	\begin{equation*}
+	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
+	\begin{equation*}
+	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
+	\end{equation*}
+	since then
+	\begin{equation*}
+	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{(i)}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{(i)}).
+	\end{equation*}
+
+	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
+	\begin{equation}
+	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
+	\end{equation}
+	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
+Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
+	\begin{equation*}
+	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
+	\end{equation*}
+	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
+\end{proof}
+
+We will need to carefully control the volume of expansion sets using the estimate in Lemma \ref{lem: expansion_volume}; Lemma \ref{lem: Taylor_series} serves this purpose.
 \begin{lemma}
@@
 	& = 1 + dx + dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
-	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{d^{k}}{(2d)^{k-1}d}\right) \\
-	& \leq 1 + 2dx.
-	\end{align*}
-\end{proof}
-
-We will repeatedly employ Lemma \ref{lem: expansion_sets} and Lemma \ref{lem: Taylor_series} in tandem.
-As a first example, in Lemma \ref{lem: interior_of_expansion_sets}, we use it to bound the ratio of $\nu(\Asig)$ to $\nu(\Aset_{\sigma - r})$.
-This will be useful when we bound $\vol(\Csig)$.
-
-\begin{lemma}
-	\label{lem: interior_of_expansion_sets}
-	For $\sigma$, $\Asig$ as in Lemma \ref{lem: expansion_sets}, let $r > 0$ satisfy $r \leq \sigma/4d$. Then,
-	\begin{equation*}
-	\frac{\nu(\Asig)}{\nu(\Aset_{\sigma - r})} \leq 2.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $q = \sigma - r$. Then,
-	\begin{align*}
-	\nu(\Asig) & = \nu(\Aset_{q + \sigma - q}) = \nu(\Aset_q + (\sigma - q)B ) \\
-	& \leq \nu(\Aset_q + \frac{(\sigma - q)}{q} \Aset_q) = \left(1 + \frac{\sigma - q}{q}\right)^d \nu(\Aset_q)
-	\end{align*}
-	where the inequality follows from Lemma \ref{lem: expansion_sets}.
-Of course, $\sigma - q = r$, and $\frac{r}{q} \leq \frac{1}{2d}$ for $r \leq \frac{1}{4d}$.
-The claim then follows from Lemma \ref{lem: Taylor_series}.
-\end{proof}
+	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
+	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2dx.
+	\end{align*}
+\end{proof}
+
+Let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}.
+Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
+
+\begin{lemma}
+	\label{lem: expected_number_boundary_points}
+	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	\Pbb(\Csigr) \leq \frac{2dr}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	\end{equation*}	
+\end{lemma}
+\begin{proof}
+	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
+	\begin{equation*}
+	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
+	\end{equation*}
+	where $t_i = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
+	\begin{equation}
+	\label{eqn: partition_ub}
+	\Pbb(\Csigr) = \int_{\Csigr} f(x) dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
+	\end{equation}
+
+	\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
+	\begin{equation*}
+	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
+	\end{equation*}
+	and writing
+	\begin{equation*}
+	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
+	\end{equation*}
+	we have
+	\begin{align}
+	\label{eqn: telescoping_sum}
+	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
+	& = \sum_{i = 1}^{k} 
+	\underbrace{\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
+	\end{align}
+	where the second equality comes from rearranging terms in the sum.
+
+	We first consider the term $\Sigma_k$.
+$\Cset$ has finite diameter by \ref{asmp: cluster_diameter}, moreover $\Cset$ is closed, due to the continuity of $f$.
+We may therefore apply Lemma \ref{lem: expansion_volume} to $\Csig$ and obtain
+	\begin{equation*}
+	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
+	\end{equation*}
+	which in turn gives
+	\begin{align}
+	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
+	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (u_{i,k} = t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
+	\end{align}
+	\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
+	\begin{align}
+	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
+	& \overset{(i)}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
+	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
+	\end{align}
+	where $(i)$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
+
+	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
+	\begin{align}
+	\xi & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
+	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
+\label{eqn: xi_ub}
+	\end{align}
+	where $(ii)$ follows application of Lemma \ref{lem: expansion_volume} to bound $\nu_{k,k}$ and $(iii)$ from Lemma \ref{lem: Taylor_series}.
+As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
+\end{proof}
+
+Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{local conductance} $\ell_{\nu,r}(u)$ to be
+\begin{equation*}
+\ell_{\nu,r}(u) = \frac{\nu\left(\Csig \cap B(u,r)\right)}{\nu\left(B(u,r)\right)}.
+\end{equation*}
+\begin{lemma}
+	\label{lem: local_conductance}
+	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
+	\begin{equation*}
+	\ell_{\nu,r}(u) \geq \frac{6}{25}. 
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as $B(x,\sigma) \subseteq \Csig$,
+	\begin{equation*}
+	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr).
+	\end{equation*}
+	Without loss of generality, let $\norm{u - x} = \sigma$; it is not hard to see that if $\norm{u - x} < \sigma$, the volume of the overlap will only grow.
+Then, since $\norm{u  - x} = \sigma$, $B(u, r) \cap B(x, \sigma)$ contains a spherical cap of radius $r$ and height
+	\begin{equation*}
+	h = r - (r)^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
+	\end{equation*}	
+	which by Lemma \ref{lem: volume_of_spherical_cap} has volume
+	\begin{equation*}
+	\nu_{cap} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
+	\end{equation*}
+	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{8d}$.
+
+	Then by Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
+	\begin{align*}
+	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{2\sqrt{d}} \\
+	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{\pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
+	\end{align*}
+\end{proof}
+
+The following formula for the volume of the spherical cap, stated in terms of the incomplete beta function, is well known. We include it without proof.
+
+\begin{lemma}
+	\label{lem: volume_of_spherical_cap}
+	Let $\mathrm{Cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
+	\begin{equation*}
+	\nu\bigl( \mathrm{Cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	\end{equation*}
+	where
+	\begin{equation*}
+	\alpha := 1 - \frac{2 r h - h^2}{r^2}
+	\end{equation*}
+	and
+	\begin{equation*}
+	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
+	\end{equation*}
+	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
+\end{lemma}
+
+\begin{lemma}
+	\label{lem: beta_integral}
+	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{8 d}$,
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{2\sqrt{d}}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We can write 
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
+	\end{equation*}
+	The first integral is simply the beta function, with
+	\begin{equation*}
+	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
+	\end{equation*}
+	To upper bound the second integral, we apply the Taylor theorem with remainder to $(1 - u)^{-1/2}$, obtaining
+	\begin{equation*}
+	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
+	\end{equation*}
+	As a result,
+	\begin{align*}
+	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
+	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
+	& \overset{(iv)}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
+	& =  3\alpha^{1/2}.
+	\end{align*}
+	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the condition $\alpha \leq \frac{t^2}{8d}$. The result follows from the condition $\alpha \leq \frac{t^2}{8d}$. 
+\end{proof}
+
+Lemma \ref{lem: beta_function} follows from $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
+\begin{lemma}
+	\label{lem: beta_function}
+	\begin{equation*}
+	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
+	\end{equation*}
+\end{lemma}
 
@@
 
-\begin{lemma}
-	\label{lem: expected_number_boundary_points}
-	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
-	\begin{equation*}
-	\Pbb(\Csigr) \leq 2 \nu(\Csig) \frac{rd}{\sigma}  \left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
-	\end{equation*}	
-\end{lemma}
-\begin{proof}
-	Recalling that $f$ is the density function for $\Pbb$, we have
-	\begin{equation}
-	\label{eqn: integral_over_epsilon_neighborhood}
-	\Pbb(\Csigr) = \int_{\Csigr} f(x) dx
-	\end{equation}
-	We partition $\Csigr$ into slices, based on distance from $\Csig$, as follows: for $k \in \N$,
-	\begin{equation*}
-	\mathcal{T}_{i,k} = \set{x \in \Rd: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
-	\end{equation*}
-	where $t_i = i/k$ for $i = 0, \ldots, k - 1$. As a result,
-	\begin{equation*}
-	\int_{\Csigr} f(x) dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
-	\end{equation*}
-	We substitute
-	\begin{equation*}
-	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) := \nu_{i+1,k} - \nu_{i,k}. 
-	\end{equation*}
-	where for simplicity we've written $\nu_{i,k} = \nu(\Csig + rt_{i+1,k}B)$.
-	This, in concert with the upper bound
-	\begin{equation*}
-	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - (rt_{i,k})^{\gamma},
-	\end{equation*}
-	which follows from \ref{asmp: bounded_density} and \ref{asmp: low_noise_density}, yields
-	\begin{align}
-	\label{eqn: telescoping_sum}
-	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - (rt_{i,k})^{\gamma} \biggr) \nonumber \\
-	& = \sum_{i = 1}^{k} 
-	\underbrace{\nu_{i,k} \biggl( \left[\lambda_{\sigma} - (rt_{i,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - (rt_{i-1,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi_k}
-	\end{align}
-
-	We first consider the term $\Sigma_k$. Here we use Lemma \ref{lem: expansion_sets} to upper bound
-	\begin{equation*}
-	\nu_{i,k} \leq \vol(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
-	\end{equation*}
-	and so we can in turn upper bound $\Sigma_k$:
-	\begin{equation}
-	\label{eqn: Sigmak_riemann_sum}
-	\Sigma_k \leq \vol(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i-1,k})^{\gamma} - (t_{i,k})^{\gamma}\biggr).
-	\end{equation}
-	This, of course, is a Riemann sum, and as the inequality holds for all values of $k$ it holds in the limit as well, which we compute to be
-	\begin{align*}
-	\lim_{k \to \infty} \sum_{i = 1}^{k} \left(1 + \frac{rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i-1,k})^{\gamma} - (t_{i,k})^{\gamma}\biggr) & = \gamma \int_{0}^{1} \left(1 + \frac{rt}{\sigma}\right)^d t^{\gamma - 1} dt \\
-	& \overset{(i)}{\leq} \gamma \int_{0}^{1} \left(1 + \frac{2drt}{\sigma}\right) t^{\gamma - 1} dt = \left(1 + \frac{\gamma 2dr}{\gamma + 1}\right).
-	\end{align*}
-	where $(i)$ follows from Lemma \ref{lem: Taylor_series}. 
-	We plug this estimate in to \eqref{eqn: Sigmak_riemann_sum} and obtain
-	\begin{equation*}
-	\lim_{k \to \infty} \Sigma_k \leq \vol(\Csig) r^{\gamma} \left(1 + \frac{\gamma 2dr}{\gamma + 1}\right).
-	\end{equation*}
-
-	We now provide an upper bound on $\xi_k$. It will follow the same basic steps as the bound on $\Sigma_k$, but will not involve integration:
-	\begin{align*}
-	\xi_k & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{r}{\sigma}\right)^d(\lambda - r^{\gamma}) - \lambda \biggr\} \\
-	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2dr}{\sigma}\right)(\lambda - r^{\gamma}) - \lambda \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda - r^{\gamma}) - r^{\gamma} \biggr\}.
-	\end{align*}
-	where $(ii)$ follows from Lemma \ref{lem: expansion_sets} and $(iii)$ from Lemma \ref{lem: Taylor_series}.
-The final result comes from adding together the upper bounds on $\Sigma_k$ and $\xi_k$ and taking the limit as $k \to \infty$.
-\end{proof}
+For notational ease, we write
+\begin{align*}
+\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
+\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
+\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+\end{align*}
+for the random variable, mean, and probability of cut size and volume, respectively.
 
@@
 	\label{lem: expected_density_cut}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma/2d$,
-	\begin{equation*}
-	p_K \leq \frac{4 \lambda \nu_d r^{d+1} \nu(\Csig)d}{\sigma}  \left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write $\cut_{n,r}$ as the sum of indicator functions,
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We can write $\cut_{n,r}$ as a double sum,
 	\begin{equation}
 	\label{eqn: density_cut_expansion}
-	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Csigr) \1(x_j \in B(x_i,r) \cap \Csig)
-	\end{equation}
-	and by linearity of expectation, we can obtain
-	\begin{equation*}
-	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csigr, x_j \in B(x_i,r) \cap \Csig)
+	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r)
+	\end{equation}
+	and by linearity of expectation, we obtain
+	\begin{equation*}
+	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
 	\end{equation*}
@@
 	\begin{align*}
-	p_K & = 2 \int_{\Csigr} f(x) \left\{ \int_{B(x,r) \cap \Csig} f(x') dx' \right\} dx \\
-	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) dx
-	\end{align*}
-	where the inequality follows from Assumption \ref{asmp: cluster_separation}, which implies that the density function $f(x') \leq \lambda$ for all $x' \in \Csig \setminus \Cset$ (otherwise, $x'$ would be in some $\Cset' \in \Cbb_f(\lambda)$, which \ref{asmp: cluster_separation} forbids).
+	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) dx \\
+	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) dx \\
+	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
+	\end{align*}
+	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
 Then, upper bounding the integral using Lemma \ref{lem: expected_density_cut} gives the final result.
@@
 	\label{lem: expected_density_volume}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound},
-	\begin{equation*}
-	p_V \geq \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
 	\end{equation*}
@@
 	\label{eqn: volume_expansion}
-	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
+	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
 	\end{equation}
@@
 	\begin{equation*}
-	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)).
+	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
 	\end{equation*}
@@
 	\begin{align*}
-	p_V & = 2 \int_{\Csig} f(x) \left\{ \int_{B(x,r)} f(x') dx' \right\} dx \\
-	& \geq 2 \int_{\Cset_{\sigma - r}} f(x) \left\{ \int_{B(x,r)} f(x') dx' \right\} dx \\
-	& \overset{(i)}{\geq} 2 \lambda_{\sigma}^2 \nu_d r^d \int_{\Cset_{\sigma - r}} f(x) dx
-	\end{align*}
-	where $(i)$ follows from the fact that $B(x,r) \subset \Csig$ for all $x \in C_{\sigma - r}$, along with the lower bound in Assumption \ref{asmp: bounded_density}.
-The claim then follows from Lemma \ref{lem: interior_of_expansion_sets}.
-\end{proof}
-
-We now convert from bounds on $p_K$ and $p_V$ to probabilistic bounds on $\cut_{n,r}$ and $\vol_{n,r}$ in Lemmas \ref{lem: prob_bound_cut} and \ref{lem: prob_bound_vol}.
-The key ingredient will be Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics; the proofs for both are nearly identical and we give only a proof for Lemma \ref{lem: prob_bound_cut}.
-
-\begin{lemma}
-	\label{lem: prob_bound_cut}
-	The following statement holds for any $\delta \in (0,1]$: Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, 
+	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) dx \\
+	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) dx
+	\end{align*}
+	whence the claim then follows by Lemma \ref{lem: local_conductance}.
+\end{proof}
+
+To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
+\begin{equation*}
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
+\end{equation*}
+to $p_K$ and $p_V$.
+
+In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
+These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
+
+\begin{lemma}
+	\label{lem: prob_bound_cutvol}
+	For any $\delta \in (0,1]$,
 	\begin{equation}
 	\label{eqn: numerator_additive_bound}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation}
-	with probability at least $1 - \delta$. 
-\end{lemma}
-
-\begin{lemma}
-	\label{lem: prob_bound_vol}
-	The following statement holds for any $\delta \in (0,1]$: Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, 
-	\begin{equation}
-	\label{eqn: denominator_additive_bound}
-	\frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation}
-	with probability at least $1 - \delta$. 
-\end{lemma}
-
-\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cut}.]
-	From \eqref{eqn: density_cut_expansion}, we see that $\cut_{n,r}$, properly scaled, can be expressed as an order-$2$ $U$-statistic,
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j)
-	\end{equation*}
-	where 
-	\begin{equation*}
-	\phi_K(x_i,x_j) = \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig) + \1(x_j \in \Asigr) \1(x_i \in B(x_j,r) \cap \Asig).
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
+	\end{equation}
+	each with probability at least $1 - \delta$. 
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
+	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
+	\end{equation*}
+	with kernels
+	\begin{align*}
+	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
+	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
+	\end{align*}
+
+	Similarly,
+	\begin{equation*}
+	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
+	\end{equation*}
+	with kernel,
+	\begin{equation*}
+	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
 	\end{equation*}
@@
 	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_k + \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation*}
-	with probability at least $1 - \delta$. 
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation*}
+	each with probability at least $1 - \delta$. The claim follows in light of \eqref{eqn: weighted_cluster_volume}, which implies $p_V^c \geq p_V$. 
 \end{proof}
@@
 
-The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, \ref{lem: prob_bound_cut}, and \ref{lem: prob_bound_vol}.
+The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
 All that remains is some algebra, which we take care of below.
 
-Fix $\delta \in (0,1]$ and let $\delta' = \delta/2$.
-For sufficiently large $n$, note that by \eqref{eqn: weighted_cluster_volume}, $\vol_{n,r} \leq 1 - \vol_{n,r}$ with probability at least $1 - \delta$, and therefore $\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\vol_{n,r}}$.
-Some trivial algebra gives us the expression
+Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
 \begin{equation}
 \label{eqn: conductance_representation_1}
-\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\vol_{n,r}}{{n \choose 2}} - p_V\right)}
-\end{equation}
-We assume (\ref{eqn: numerator_additive_bound}) and (\ref{eqn: denominator_additive_bound}) hold with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
+\end{equation}
+Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
 Along with (\ref{eqn: conductance_representation_1}) this means
@@
 \begin{align*}
-\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V - \Err_n} - \frac{p_K}{p_V}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-& = \frac{p_k}{p_V} + \frac{\Err_n}{p_V - \Err_n}\left(\frac{p_K}{p_V} + 1\right) \\
+\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
+& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
 & \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
 \end{align*}
-By Lemmas \ref{lem: expected_density_cut} and Lemma \ref{lem: expected_density_volume}, we have
-\begin{equation*}
-\frac{p_K}{p_V} \leq \frac{4rd}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}
-\end{equation*}
-Then, the choice of 
-\begin{equation*}
-n \geq \frac{9\log(2/\delta)}{\epsilon^2}\left(\frac{1}{ \lambda_{\sigma}^2 \nu(\Csig) \nu_d r^d}\right)^2 
-\end{equation*}
-
-implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
+\begin{equation*}
+\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
+\end{equation*}
+Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
+\begin{equation*}
+n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
+\end{equation*}
+which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
 
@@
 
+\section{\textcolor{red}{OLD STUFF}}
+
+\subsection{Volume estimates}
+We will fix $\Aset \subset \Rd$ to be an arbitrary set.
+To simplify expressions, for the $\sigma$-expansion $\Asig$, we will write the set difference between $\Asig$ and the $(\sigma + r)$-expansion $\Aset_{\sigma + r}$ as
+\begin{equation*}
+\Asigr := \set{x: 0 < \dist(x, \Asig) \leq r},
+\end{equation*}
+where as a reminder $\dist(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
+
+\paragraph{Lemma \ref{lem: interior_of_expansion_sets}.}
+
+We will repeatedly employ Lemma \ref{lem: expansion_sets} and Lemma \ref{lem: Taylor_series} in tandem.
+As a first example, in Lemma \ref{lem: interior_of_expansion_sets}, we bound the ratio of $\nu(\Aset)$ to $\nu(\Aset_{-\delta})$, where we write $\partial \Aset$ for the boundary of $\Aset$, and for $\delta > 0$ we let
+\begin{equation*}
+\Aset_{-\delta} : = \set{x \in \Aset: \dist(x, \partial \Aset) > \delta}.
+\end{equation*}
+
+This will be useful when we bound $\vol(\Csig)$.
+
+\begin{lemma}
+	\label{lem: interior_of_expansion_sets}
+	For $\sigma$, $\Asig$ as in Lemma \ref{lem: expansion_sets}, let $r > 0$ satisfy $r \leq \sigma/4d$. Then,
+	\begin{equation*}
+	\frac{\nu(\Asig)}{\nu(\Aset_{\sigma - r})} \leq 2.
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Fix $q = \sigma - r$. Then,
+	\begin{align*}
+	\nu(\Asig) & = \nu(\Aset_{q + \sigma - q}) = \nu(\Aset_q + (\sigma - q)B ) \\
+	& \leq \nu(\Aset_q + \frac{(\sigma - q)}{q} \Aset_q) = \left(1 + \frac{\sigma - q}{q}\right)^d \nu(\Aset_q)
+	\end{align*}
+	where the inequality follows from Lemma \ref{lem: expansion_sets}.
+Of course, $\sigma - q = r$, and $\frac{r}{q} \leq \frac{1}{2d}$ for $r \leq \frac{1}{4d}$.
+The claim then follows from Lemma \ref{lem: Taylor_series}.
+\end{proof}
+
 \clearpage
 \bibliographystyle{plain}
-\bibliography{icml_bib}
+\bibliography{../local_spectral_bibliography}
 

### 2019-04-30 arxiv/arxiv_local_density_clustering.tex
added examples

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage{float}
+\usepackage[export]{adjustbox}
+\usepackage{subcaption}
 \usepackage{booktabs}
+\usepackage{xcolor}
 \usepackage{xr-hyper}
@@
 \usepackage{algorithmic}
-\usepackage{graphicx}
 \usepackage[parfill]{parskip}
@@
 
-\section{Cluster Quality Critera Bounds for Density Clusters}  
+\section{Cluster Quality Criteria Bounds for Density Clusters}  
 \label{sec: cluster_quality_bounds}
@@
 
+\subsection{Validating Theoretical Bounds}
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/sample2}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/sample1}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/sigma_normalized_cut_plot}
+		\caption{}
+	\end{subfigure}
+
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/sigma_mixing_time_plot}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/diameter_normalized_cut_plot}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.33\linewidth}
+		\includegraphics[width=\linewidth]{example1plots/diameter_mixing_time_plot}
+		\caption{}
+	\end{subfigure}
+	\end{adjustbox}
+\end{figure}
+
+\subsection{Empirical PPR, normalized cut, and density clustering comparison}
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth,scale = .5]{example2plots/row1_true_density_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row1_ppr_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row1_conductance_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row1_density_cluster}
+		\caption{}
+	\end{subfigure}
+
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row2_true_density_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row2_ppr_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row2_conductance_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row2_density_cluster}
+		\caption{}
+	\end{subfigure}
+
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row3_true_density_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row3_ppr_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row3_conductance_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row3_density_cluster}
+		\caption{}
+	\end{subfigure}
+
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
+		\caption{}
+	\end{subfigure}
+	\begin{subfigure}{.24\linewidth}
+		\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
+		\caption{}
+	\end{subfigure}
+	\caption{True density (column 1), \pprspace (column 2), normalized cut (column 3) and estimated density (column 4) clusters for 4 different simulated data sets.
+Seed node for \pprspace denoted by a black cross.}
+	\label{fig:fig2}
+	\end{adjustbox}
+\end{figure}
+
+To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+Formally, the (respective) generative models for the data are
+\begin{align}
+Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
+X(Z,\theta) & = 
+\begin{cases}
+\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
+\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
+\end{cases}
+\end{align}
+
+where 
+\begin{align*}
+\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
+\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
+\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} \\
+\mu_1 & = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}) \tag{row 4}
+\end{align*}
+for $I_d$ the $d \times d$ identity matrix.
+The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \textcolor{red}{Bressson et al.
+2012}; and the last column shows a cut of the cluster tree estimator of \textcolor{red}{Chaudhuri Dasgupta}
+
+Rows 1-3 show the degrading ability of \pprspace to recover density clusters as the two moons become less salient.
+In the first row, the normalized cut conforms to the density cluster, and \pprspace recovers both.
+In the second row, the normalized cut still conforms to the density cluster, but because the internal connectivity of the lower moon is low, \pprspace fails to recover the normalized cut.
+In the third row, the moons have such low saliency that even the normalized cut fails to recover the lower moon; we also see from $(k)$ that \pprspace does not somehow save us in this situation.
+Note that this is not a function of the finite sample: the 4th column shows us that the Chaudhuri Dasgupta cluster tree estimator can be recover the true density cluster.
+
+The fourth row illustrates the effect of dimension.
+The gray dots in $(m)$ (as in $(a), (e)$ and $(i)$ are observations in low-density regions.
+While the \pprspace sweep cut $(n)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C_n$ in the sense of Definition \textcolor{red}{1}.
+
 \section{Discussion}

### 2019-04-30 arxiv/arxiv_local_density_clustering_proofs.tex
added examples

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage[export]{adjustbox}
+\usepackage{subcaption}
 \usepackage{booktabs}
@@
 \usepackage{amsfonts, amsthm, amssymb}
-\usepackage{graphicx}
 \usepackage[parfill]{parskip}
@@
 	For any $0 \leq x \leq 1/2d$,
-	\begin{equation*}
-	(1 + x)^d \leq 1 + 2dx.
-	\end{equation*}
+	\begin{align*}
+	(1 + x)^d & \leq 1 + 2dx \\
+	(1 - x)^d & \geq 1 - 2dx.
+	\end{align*}
 \end{lemma}
@@
 	\end{align*}
+
+	The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
 \end{proof}
@@
 	We first consider the term $\Sigma_k$.
-$\Cset$ has finite diameter by \ref{asmp: cluster_diameter}, moreover $\Cset$ is closed, due to the continuity of $f$.
-We may therefore apply Lemma \ref{lem: expansion_volume} to $\Csig$ and obtain
-	\begin{equation*}
+$\Cset$ has finite diameter by \ref{asmp: cluster_diameter}.
+Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
+As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
+	\begin{equation}
+	\label{eqn: slice_volume_bound}
 	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
-	\end{equation*}
+	\end{equation}
 	which in turn gives
@@
 	\end{align}
-	where $(ii)$ follows application of Lemma \ref{lem: expansion_volume} to bound $\nu_{k,k}$ and $(iii)$ from Lemma \ref{lem: Taylor_series}.
+	where $(ii)$ follows from \eqref{eqn: slice_volume_bound}, and $(iii)$ from Lemma \ref{lem: Taylor_series}.
 As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
@@
 
+\section{Additional Experiments}
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth,scale = .5]{example3plots/true_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth,scale = .5]{example3plots/ppr_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth,scale = .5]{example3plots/conductance_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth,scale = .5]{example3plots/density_cluster}
+			\caption{}
+		\end{subfigure}
+	\caption{}
+	\end{adjustbox}
+\end{figure}
+
 \section{\textcolor{red}{OLD STUFF}}

### 2019-05-01 arxiv/arxiv_local_density_clustering.tex
finalized examples, added partial redraft of proofs for ppr section

@@
 	\end{subfigure}
+	\caption{}
+	\label{fig:fig1}
 	\end{adjustbox}
 \end{figure}
+
+As we do not provide any theoretical lower bounds, we validate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} via simulation.
+We sample points according to the density function $q$, where for $x \in \Rd$
+\begin{equation}
+q(x) :=
+\begin{cases}
+\lambda,~ & x \in [0,\sigma] \times D^{d-1} =: \Cset, \\
+\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
+(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B), \setminus \Csig \\
+0,~ & \textrm{otherwise},
+\end{cases}
+\end{equation}
+where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
+Panels $(a)$ and $(b)$ in Figure \ref{fig:fig1} show $20,000$ samples from two parameterizations of $q$.
+In $(a)$, $\sigma = D = 3.2$, while in $(b)$ $\sigma = .1$ and $D = 3.2$.
+(For both, $d = 2$).
+
+Panels $(c) - (f)$ in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ ($(c)$ and $(d)$) and $D$ ($(e)$ and $(f)$) are varied.
+In panels $(c)$ and $(d)$ $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $D$ is fixed at $3.2$.
+In panels $(e)$ and $(f)$, $D = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
+For each panel, the solid lines show, up to constants \footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
+Therefore only comparison of slopes, rather than intercepts, is meaningful.}, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for panels $(c)$ and $(e)$ and Theorem \ref{thm: inverse_mixing_time_lower_bound} for panels $(d)$ and $(f)$.
+The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in panels $(c)$ and $(e)$, and $m = 20$ for the mixing time, dashed lines in panel $(d)$ and $(f)$).
+For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
+Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
+
+Panels $(d)$ and $(f)$ show the solid lines tracking closely to the dashed lines, in both 2 and 3 dimensions.
+This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: inverse_mixing_time_lower_bound} has the right dependency on both thickness parameter  $\sigma$ and diameter $D$.
+
+\textcolor{red}{The story in panels $(c)$ and $(e)$ is more subtle.
+We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results is mostly due to the relationship when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$.
+It is in these regions that the slopes of the dashed and solid lines appear most distinct.
+As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves converging towards those predicted by theory.
+The takeaway message is that while the dependency in \eqref{eqn: conductance_additive_error_bound} on $\sigma$ and $D$ is loose for clusters with diameter close to thickness, it becomes tighter and tigher as $D/\sigma$ grows.}
 
@@
 
+To drive home the main implications of Theorem \ref{thm: ppr_cluster}, we show the behavior of \pprspace, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
 To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.

### 2019-05-01 arxiv/arxiv_local_density_clustering_proofs.tex
finalized examples, added partial redraft of proofs for ppr section

@@
 
-Let $\pbf = (p_u)_{u \in \Xbf}$ denote the \pprspace vector computed over $G_{n,r}$ (where for ease of reading we suppress dependence on the hyperparameter $\alpha$ and seed node $v$.) 
-Recalling that $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$, we write $\widetilde{\pi}_{n,r}(u)$ to denote the stationary distribution evaluated at $u \in \Csig[X]$.
-
 \subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
@@
 
-Lemma \ref{lem: setup} formalizes the intuitively sensible statement that \pprspace, can be uniformly lower bounded over clusters with small mixing time relative to their normalized cut.
-Importantly, it adds a corresponding upper bound for \pprspace outside of these clusters.
+Recall that for teleportation parameter $\alpha  \in (0,1]$ and seed node $v \in \Xbf$, we write $\pbf(v, \alpha; G_{n,r})$ for the \pprspace vector computed over neighborhood graph $G_{n,r}$; let $\pbf(u)$ denote the entry of $\pbf(v, \alpha; G_{n,r})$ at vertex $u \in \Xbf$.
+Recalling that we write $\widetilde{\pibf}_{n,r}$ for the stationary distribution over $\widetilde{G}_{n,r}$, write $\widetilde{\pibf}_{n,r}(u)$ denote the stationary distribution at vertex $u \in \Csig[\Xbf]$.
+
+Lemma \ref{lem: setup} states the key results needed to link Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} with Theorem \ref{thm: consistent_recovery_of_density_clusters}.
 \begin{lemma} 
 	\label{lem: setup}
-	Consider running Algorithm \ref{alg: ppr} with any $r < \sigma$ and
-
+	Let $0 < r < \sigma$ and
 	\begin{equation} 
@@
 
-	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ such that the following statements hold for all $v \in \Csig[\Xbf]^g$:
+	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
 	\begin{itemize}
-		\item For all $u \in \Cset[\Xbf]$,
+		\item For each $u \in \Cset[\Xbf]$,
 		\begin{equation}
 		\label{eqn: lower_bound_PPR_in_cluster}
-		p_u \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
-		\end{equation}
-		\item For all $u' \in \Csig'[\Xbf]$,
+		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
+		\end{equation}
+		\item For any $\Cset' \in \Cbb_f(\lambda)$ such that $\Cset' \neq \Cset$, and for each $u' \in \Csig'[\Xbf]$,
 		\begin{equation}
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		p_{u'} \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
+		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
 		\end{equation}
@@
 \begin{proof}
-	We will write $\Wbf_n = \Dbf_n \Abf_n^{-1}$ for the transition probability matrix over $G_{n,r}$, and let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
-
-	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
-	\begin{align*}
-	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}) \\
-	\ell & := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t \\
-	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c) \\
-	s & := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t
-	\end{align*}
-	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is a diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
-
-	Roughly, the proof will unfold in four steps.
-The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).
-
-	\begin{enumerate}
-		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to produce the lower bound 
-		\begin{equation*}
-		\pbf(u) \geq 4/5 \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
-		\end{equation*}
-		where 
-		\begin{equation*}
-		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
-		\end{equation*}
-		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.
-
-		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $G_{n,r} / \Csig[\Xbf]$.
-Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
-This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
-		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
-		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$.
-Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
-Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$.
-This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
-	\end{enumerate}
-
-	\paragraph{Step 1}
-	We will begin by restating some results of \cite{zhu2013}.
-
-	For seed node $v$, we write
-	\begin{align} \label{eqn: page_rank_body}
-	\widetilde{\pbf}_v & = \alpha e_v + (1 - \alpha) \widetilde{\pbf}_v \widetilde{\Wbf}_n \\
-	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{\Wbf}_n^t \right)
-	\end{align}
-
-	From Lemma 3.1 of \cite{zhu2013} we have that there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ for all $v \in \Csig[\Xbf]^g$, $u \in \Csig[\Xbf]$
-
-	\begin{align} \label{eqn: zhu_body}
-	p_u & \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u) \nonumber \\
-	||\ell||_1 & \leq \frac{2 \widetilde{\Phi}_{n,r}}{\alpha}
-	\end{align}
-	where $\widetilde{\pbf}_v = (\widetilde{\pbf}_v(u))$ and likewise for $\widetilde{\pbf}_{\ell} = (\widetilde{\pbf}_{\ell}(u))$.
-(This will be the only time we need to restrict ourselves to this 'good set'.)
-
-	Moreover if, as we have specified, $\alpha \leq \widetilde{\Psi}_{n,r}/9$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
-	\begin{equation} \label{eqn: page_rank_mixes}
-	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u).
-	\end{equation}
-
-	\paragraph{Step 2}
-
-	We turn to upper bounding $\widetilde{\pbf}_{\ell}(u)$. For any $u \in \Cset[\Xbf]$, we have
-
-	\begin{align} \label{eqn: leakage_page_rank_body}
+	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult.
+We begin with some notation.
+Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$.
+Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
+Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
+	\begin{equation}
+	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
+	\end{equation}
+	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
+(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v$ for $\widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
+
+	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
+	\begin{align*}
+	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
+	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
+	\end{align*}
+	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
+
+	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at the $t$th step at $u$, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
+For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$.
+By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
+The vectors $\ell$ and $s$ then clearly have the same interpretation, but with respect to the total mass leaked and soaked by the \pprspace vector.
+
+	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation.
+By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
+	\begin{equation}
+	\label{eqn: zhulemma3.1}
+	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
+	\end{equation}
+
+	If moreover $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then additionally by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
+	\begin{equation*}
+	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
+	\end{equation*}
+	and along with \eqref{eqn: zhulemma3.1}, we obtain
+	\begin{equation*}
+	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
+	\end{equation*}
+
+	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
+We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$.
+First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$.
+As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
+
+	Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
+	\begin{align*}
+	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \\
+	& \leq \frac{1}{\widetilde{D}_{\min}}
+	\end{align*}
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore
+	\begin{equation*}
+	\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}.
+	\end{equation*}
+
+	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
+	\begin{align*}
 	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
-	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{\widetilde{D}_{\min}} 
-	\end{align}
-
-	where we use $\left(\ell \widetilde{\Wbf}_n^t \right)(u)$ to denote $\ell \widetilde{\Wbf}_n^te_u$.
-
-	$\text{(i)}$ follows from the fact that since $r < \sigma$, $\cut(\Cset[\Xbf], G_{n,r} / \Csig[\Xbf]; G_{n,r}) = 0$. Therefore $(\Dbf_n^{-1})_{uu} (\widetilde{\Dbf}_n)_{uu} = 1$, and as a result
-	\begin{equation*}
-	(\ell \widetilde{\Wbf}_n^0)(u) = \ell(u) = 0.
-	\end{equation*}
-	To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^{t-1}$. Then
-
-	\begin{align*}
-	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u) & = \left(q \widetilde{\Wbf}_n \right)(u) \\
-	& \leq \|q\|_1 \|\widetilde{\Wbf}_{\cdot u}\|_{\infty} \\
-	& \overset{\text{(iii)}}{\leq} \frac{1}{\widetilde{D}_{\min}}.
-	\end{align*}
-	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}_n$.
-$\text{(iii)}$ then follows from the fact that any vertex in $\Cset[\Xbf]$ is connected only to vertices in $\Csig[\Xbf]$, and therefore every entry of $\widetilde{\Wbf}_{\cdot u}$ is either $0$ or at most $1 / \widetilde{D}_{\min}$.
-
-	Combined, (\ref{eqn: leakage_page_rank_body}), (\ref{eqn: page_rank_mixes}), and \eqref{eqn: zhu_body} imply
-	\begin{equation*}
-	p_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - 18\frac{ \Phi_{n,r}(\Csig[\Xbf])}{\widetilde{D}_{\min} \alpha}.
-	\end{equation*}
-	for any $v \in \Csig[\Xbf]$.
-
-	\paragraph{Step 3}
-	To get the corresponding upper bound on $p_v(u')$, we will use the soakage vectors $s$ and $s_t$.
-We will first argue that $s$ is a worse starting distribution -- meaning it puts uniformly more mass outside the cluster -- than simply starting at $v$.
-
-	\begin{lemma} \label{lem: gained mass is soaked_body}
-		For all $u' \notin \Csig[\Xbf]$,
-		\begin{equation}
-		\pbf_v(u') \leq \pbf_{s}(u').
-		\end{equation}
-	\end{lemma}
-
-	\begin{proof}
-
-		We have
-		\begin{align*}
-		\pbf_v(u') & = \alpha \sum_{T=0}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u)\\
-		& \overset{(i)}{=} \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u')
-		\end{align*}
-
-		where $(i)$ follows from $v \in \Csig$ , $u \not\in \Csig$ and therefore $e_v(u) = 0$.
-
-		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
-		\begin{lemma}
-			\label{lem: sum_of_soakages}
-
-			Let $G = (V,E)$ be a graph, with associated random walk matrix $W$.
-
-			For any $T \geq 1$, $q$ vector, $S \subset V$, and $s_t = s_t(S^c,q)$
-			\begin{equation}
-			qW^T = \sum_{t = 0}^{T - 1} s_t W^{T - t - 1} + q(W I_S)^T
-			\end{equation}
-		\end{lemma}
-		We prove Lemma \ref{lem: sum_of_soakages} after completing the proof of Lemma \ref{lem: gained mass is soaked_body}.
-
-		Now, along with the fact $u \not\in \Csig$, we have
-
-		\begin{equation*}
-		\left(e_v \Wbf_n^T \right)(u') = \sum_{t = 0}^{T - 1} \left(s_t \Wbf_n^{T - t - 1} \right)(u')
-		\end{equation*}
-
-		and so
-
-		\begin{align*}
-		\pbf_v(u) & = \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u') \\
-		& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u')\\
-		& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u') \\
-		& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u') \\
-		& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u') \\
-		& = \pbf_s(u')
-		\end{align*}
-	\end{proof}
-
-	\begin{proof}[Proof of Lemma \ref{lem: sum_of_soakages}]
-		Proceed by induction. When $T = 1$,
-
-		\begin{align*}
-		qW & = q(WI_S) + q(WI_{S^c}) \\
-		& = q(W I_S)^T + s_0 
-		\end{align*}
-
-		Assume true for $T_0$. For $T = T_0 + 1$,
-
-		\begin{align*}
-		qW^T & = qW^{T_0}W \\
-		& = \left\{ \sum_{t = 0}^{T_0 - 1} s_t W^{T_0 - 1 - t} + q(WI_S)^{T_0} \right\} W \\
-		& =  \sum_{t = 0}^{T_0 - 1} s_t W^{T - 1 - t} + q(WI_S)^{T_0}(WI_S + WI_{S^c}) \\
-		& =  \sum_{t = 0}^{T - 1} s_t W^{T - 1 - t} + q(WI_S)^{T}
-		\end{align*}
-	\end{proof}
-
-	\paragraph{Step 4}
-
-	Just as we upper bounded the probability mass $\widetilde{\pbf}_{\ell}$ could assign to any one vertex, we can upper bound
-
-	\begin{align} \label{eqn: soakage_page_rank_body}
-	\pbf_{s}(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t \right)(u') \nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1} {\Wbf}_n^t \right)(u')\nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  {\Wbf}_n^t \right)(u')\nonumber \\
-	& \leq \|s\|_1 \frac{1}{\widetilde{D}_{\min}}.
-	\end{align}
-
-	Finally, letting $q_t = e_v (\Wbf_n \widetilde{\mathbf{I}}_n)^t$ for ease of notation, we have
-	\begin{align*}
-	\|s_t\|_1 & = \|q_t (\Wbf_n \widetilde{\mathbf{I}}_n)\|_1 \\
-	& = \sum_{u' \in \Xbf} \sum_{u \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n)(u, u')\\
-	& = \sum_{u' \in \Xbf / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1(e_{u,u'} \in G_{n,r}) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
-	& = \|q_t (I - \Dbf_n^{-1} \widetilde{\Dbf}_n)\|_1 = \|\ell_t\|_1.
-	\end{align*}
-
-	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
+	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \leq \norm{\ell}_1 \frac{1}{\widetilde{D}_{\min}}.
+	\end{align*}
+	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.
 
@@
 
+\subsection{Proof of Lemma \ref{lem: setup}}
+
+\begin{proof}
+	We will write $\Wbf_n = \Dbf_n \Abf_n^{-1}$ for the transition probability matrix over $G_{n,r}$, and let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
+
+	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
+	\begin{align*}
+	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
+	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
+	\end{align*}
+	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
+
+	Roughly, the proof of Lemma \ref{lem: setup} will unfold in four steps.
+The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).
+We briefly summarize the approach before diving into the formal proof:
+
+	\begin{enumerate}
+		\item For $u \in \Cset[\Xbf]$, we use the results of \cite{zhu2013} to produce the lower bound 
+		\begin{equation*}
+		\pbf(u) \geq \frac{4}{5}\widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
+		\end{equation*}
+		where 
+		\begin{equation*}
+		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
+		\end{equation*}
+		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.
+
+		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $\Xbf \setminus \Csig[\Xbf]$.
+Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
+This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
+		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
+		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$.
+Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
+Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$.
+This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
+	\end{enumerate}
+
+	\paragraph{Step 1}
+	We will begin by restating some results of \cite{zhu2013}.
+
+	For seed node $v$, we write
+	\begin{align} \label{eqn: page_rank_body}
+	\widetilde{\pbf}_v & = \alpha e_v + (1 - \alpha) \widetilde{\pbf}_v \widetilde{\Wbf}_n \\
+	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{\Wbf}_n^t \right)
+	\end{align}
+
+	From Lemma 3.1 of \cite{zhu2013} we have that there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ for all $v \in \Csig[\Xbf]^g$, $u \in \Csig[\Xbf]$
+
+	\begin{align} \label{eqn: zhu_body}
+	p_u & \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u) \nonumber \\
+	||\ell||_1 & \leq \frac{2 \widetilde{\Phi}_{n,r}}{\alpha}
+	\end{align}
+	where $\widetilde{\pbf}_v = (\widetilde{\pbf}_v(u))$ and likewise for $\widetilde{\pbf}_{\ell} = (\widetilde{\pbf}_{\ell}(u))$.
+(This will be the only time we need to restrict ourselves to this 'good set'.)
+
+	Moreover if, as we have specified, $\alpha \leq \widetilde{\Psi}_{n,r}/9$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
+	\begin{equation} \label{eqn: page_rank_mixes}
+	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u).
+	\end{equation}
+
+	\paragraph{Step 2}
+
+	We turn to upper bounding $\widetilde{\pbf}_{\ell}(u)$. For any $u \in \Cset[\Xbf]$, we have
+
+	\begin{align} \label{eqn: leakage_page_rank_body}
+	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
+	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{\widetilde{D}_{\min}} 
+	\end{align}
+
+	where we use $\left(\ell \widetilde{\Wbf}_n^t \right)(u)$ to denote $\ell \widetilde{\Wbf}_n^te_u$.
+
+	$\text{(i)}$ follows from the fact that since $r < \sigma$, $\cut(\Cset[\Xbf], G_{n,r} / \Csig[\Xbf]; G_{n,r}) = 0$. Therefore $(\Dbf_n^{-1})_{uu} (\widetilde{\Dbf}_n)_{uu} = 1$, and as a result
+	\begin{equation*}
+	(\ell \widetilde{\Wbf}_n^0)(u) = \ell(u) = 0.
+	\end{equation*}
+	To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^{t-1}$. Then
+
+	\begin{align*}
+	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u) & = \left(q \widetilde{\Wbf}_n \right)(u) \\
+	& \leq \|q\|_1 \|\widetilde{\Wbf}_{\cdot u}\|_{\infty} \\
+	& \overset{\text{(iii)}}{\leq} \frac{1}{\widetilde{D}_{\min}}.
+	\end{align*}
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}_n$.
+$\text{(iii)}$ then follows from the fact that any vertex in $\Cset[\Xbf]$ is connected only to vertices in $\Csig[\Xbf]$, and therefore every entry of $\widetilde{\Wbf}_{\cdot u}$ is either $0$ or at most $1 / \widetilde{D}_{\min}$.
+
+	Combined, (\ref{eqn: leakage_page_rank_body}), (\ref{eqn: page_rank_mixes}), and \eqref{eqn: zhu_body} imply
+	\begin{equation*}
+	p_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - 18\frac{ \Phi_{n,r}(\Csig[\Xbf])}{\widetilde{D}_{\min} \alpha}.
+	\end{equation*}
+	for any $v \in \Csig[\Xbf]$.
+
+	\paragraph{Step 3}
+	To get the corresponding upper bound on $p_v(u')$, we will use the soakage vectors $s$ and $s_t$.
+We will first argue that $s$ is a worse starting distribution -- meaning it puts uniformly more mass outside the cluster -- than simply starting at $v$.
+
+	\begin{lemma} \label{lem: gained mass is soaked_body}
+		For all $u' \notin \Csig[\Xbf]$,
+		\begin{equation}
+		\pbf_v(u') \leq \pbf_{s}(u').
+		\end{equation}
+	\end{lemma}
+
+	\begin{proof}
+
+		We have
+		\begin{align*}
+		\pbf_v(u') & = \alpha \sum_{T=0}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u)\\
+		& \overset{(i)}{=} \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u')
+		\end{align*}
+
+		where $(i)$ follows from $v \in \Csig$ , $u \not\in \Csig$ and therefore $e_v(u) = 0$.
+
+		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
+		\begin{lemma}
+			\label{lem: sum_of_soakages}
+
+			Let $G = (V,E)$ be a graph, with associated random walk matrix $W$.
+
+			For any $T \geq 1$, $q$ vector, $S \subset V$, and $s_t = s_t(S^c,q)$
+			\begin{equation}
+			qW^T = \sum_{t = 0}^{T - 1} s_t W^{T - t - 1} + q(W I_S)^T
+			\end{equation}
+		\end{lemma}
+		We prove Lemma \ref{lem: sum_of_soakages} after completing the proof of Lemma \ref{lem: gained mass is soaked_body}.
+
+		Now, along with the fact $u \not\in \Csig$, we have
+
+		\begin{equation*}
+		\left(e_v \Wbf_n^T \right)(u') = \sum_{t = 0}^{T - 1} \left(s_t \Wbf_n^{T - t - 1} \right)(u')
+		\end{equation*}
+
+		and so
+
+		\begin{align*}
+		\pbf_v(u) & = \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u') \\
+		& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u')\\
+		& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+		& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u') \\
+		& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u') \\
+		& = \pbf_s(u')
+		\end{align*}
+	\end{proof}
+
+	\begin{proof}[Proof of Lemma \ref{lem: sum_of_soakages}]
+		Proceed by induction. When $T = 1$,
+
+		\begin{align*}
+		qW & = q(WI_S) + q(WI_{S^c}) \\
+		& = q(W I_S)^T + s_0 
+		\end{align*}
+
+		Assume true for $T_0$. For $T = T_0 + 1$,
+
+		\begin{align*}
+		qW^T & = qW^{T_0}W \\
+		& = \left\{ \sum_{t = 0}^{T_0 - 1} s_t W^{T_0 - 1 - t} + q(WI_S)^{T_0} \right\} W \\
+		& =  \sum_{t = 0}^{T_0 - 1} s_t W^{T - 1 - t} + q(WI_S)^{T_0}(WI_S + WI_{S^c}) \\
+		& =  \sum_{t = 0}^{T - 1} s_t W^{T - 1 - t} + q(WI_S)^{T}
+		\end{align*}
+	\end{proof}
+
+	\paragraph{Step 4}
+
+	Just as we upper bounded the probability mass $\widetilde{\pbf}_{\ell}$ could assign to any one vertex, we can upper bound
+
+	\begin{align} \label{eqn: soakage_page_rank_body}
+	\pbf_{s}(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t \right)(u') \nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1} {\Wbf}_n^t \right)(u')\nonumber \\
+	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  {\Wbf}_n^t \right)(u')\nonumber \\
+	& \leq \|s\|_1 \frac{1}{\widetilde{D}_{\min}}.
+	\end{align}
+
+	Finally, letting $q_t = e_v (\Wbf_n \widetilde{\mathbf{I}}_n)^t$ for ease of notation, we have
+	\begin{align*}
+	\|s_t\|_1 & = \|q_t (\Wbf_n \widetilde{\mathbf{I}}_n)\|_1 \\
+	& = \sum_{u' \in \Xbf} \sum_{u \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n)(u, u')\\
+	& = \sum_{u' \in \Xbf / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1(e_{u,u'} \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
+	& = \|q_t (I - \Dbf_n^{-1} \widetilde{\Dbf}_n)\|_1 = \|\ell_t\|_1.
+	\end{align*}
+
+	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
+
+\end{proof}
+
 \clearpage

### 2019-05-02 arxiv/arxiv_local_density_clustering.tex
proofs for cluster recovery section updated

@@
 \item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
-  Theorem \ref{thm: consistent_recovery_of_density_clusters} that these bounds
+  Theorem \ref{thm: consistent_recovery_of_density_clusters} that the bounds
   in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:

### 2019-05-02 arxiv/arxiv_local_density_clustering_proofs.tex
proofs for cluster recovery section updated

@@
-%%%%%%%% ICML 2019 submission %%%%%%%%%%%%%%%%%
+%%%%%%%% Proofs of Local Spectral Clustering of Density Upper Level Sets %%%%%%%%%%%%%%%%%
 
@@
 \newcommand{\cut}{\mathrm{cut}}
+\newcommand{\degminpr}{\deg_{\min}'}
+\newcommand{\piminwt}{\widetilde{\pibf}_{\min}}
 
@@
 
+\begin{lemma}
+	\label{lem: ball_bounds_in_probability}
+	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
+	\begin{align*}
+	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
+	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
+	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
+	\end{align*}
+	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
+\end{lemma}
+
+The statement follows immediately from Lemma \ref{lem: ball_bounds}.
+
 \subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
@@
 		\end{equation}
-		\item For any $\Cset' \in \Cbb_f(\lambda)$ such that $\Cset' \neq \Cset$, and for each $u' \in \Csig'[\Xbf]$,
+		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Csig'[\Xbf]$,
 		\begin{equation}
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
-		\end{equation}
+		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}
+		\end{equation}
+		where $ \deg_{\min}' := \min_{u \in \Cset'[\Xbf]} \deg(u; G_{n,r})$. 
 	\end{itemize}
@@
 	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
-(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v$ for $\widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
+(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
 
 	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
-	\begin{align*}
-	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
+	\begin{align}
+	\label{eqn: leakage_soakage}
+	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
 	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
-	\end{align*}
+	\end{align}
 	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
 
-	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at the $t$th step at $u$, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
+	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
 For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$.
 By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
-The vectors $\ell$ and $s$ then clearly have the same interpretation, but with respect to the total mass leaked and soaked by the \pprspace vector.
+The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
 
@@
 	\end{equation}
-
-	If moreover $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then additionally by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
+	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)
+
+	If additionally $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
 	\begin{equation*}
@@
 As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-
 Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
-	\begin{align*}
-	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \\
+	\begin{align}
+	\label{eqn: one_step_bound}
+	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
 	& \leq \frac{1}{\widetilde{D}_{\min}} 
-	\end{align*}
-	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore
-	\begin{equation*}
-	\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}.
-	\end{equation*}
+	\end{align}
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}$.
 
@@
 
-\end{proof}
-
-\begin{lemma}
-	\label{lem: ball_bounds_in_probability}
-	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
-	\begin{align*}
-	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
-	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
-	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
-	\end{align*}
-	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
-\end{lemma}
-
-The statement follows immediately from Lemma \ref{lem: ball_bounds}.
-
-\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
-
-We note that by Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, 
-\begin{equation*}
-\kappa_2(\Cset) \geq \frac{\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])}.
-\end{equation*}
-As a result Lemma \ref{lem: setup} implies
-\begin{align}
-\label{eqn: theorem_4_1}
-p_u & \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~ (u \in \Cset[\Xbf]) \nonumber \\
-p_{u'} & \leq \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~~~~~~~~~~~~~~~~ (u' \in \Cset'[\Xbf])
-\end{align}
-
-We turn to bounding $\widetilde{\pi}_{n,r}(u)$. Clearly,
-\begin{align*}
-\widetilde{\pi}_{n,r}(u) & \geq \frac{\widetilde{D}_{\min}}{\widetilde{\vol}_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{\widetilde{D}_{\min}}{\wn \widetilde{D}_{\max}}.
-\end{align*}
-Application of Lemma \ref{lem: ball_bounds_in_probability} then yields
-\begin{equation}
-\label{eqn: theorem_4_2}
-\widetilde{\pi}_{n,r}(u) \geq 8 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
-\end{equation}
-as well as
-\begin{equation}
-\label{eqn: theorem_4_3}
-\frac{1}{\widetilde{D}_{\min}} \leq \frac{2}{\nu_d r^d \lambda_{\sigma}}
-\end{equation}
-with probability tending to $1$ as $n \to \infty$, for all $u \in \Cset[\Xbf]$ (indeed, all $u \in \Csig[\Xbf]$.)
-
-Combining \eqref{eqn: theorem_4_1}, \eqref{eqn: theorem_4_2} and \eqref{eqn: theorem_4_3}, along with the requirement on $\kappa_2(\Cset)$ given by \eqref{eqn: kappa2_ub}, we have
-\begin{align*}
-p_u & \geq 3/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2} \\
-p_{u'} & \leq 1/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
-\end{align*}
-for any $u \in \Cset$, $u' \in \Cset'$.
-As a result, if $\pi_0 \in (2/5, 3/5)\cdot \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}$, as $n \to \infty$ with probability tending to one any sweep cut of the form of \eqref{eqn: sweep_cuts}, including the output set $\widehat{C}$, will successfully recover $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+	We turn to showing \eqref{eqn: upper_bound_PPR_in_other_cluster}. By Lemma \ref{lem: soakage_ppr_lb}, for all $u' \not\in \Csig[\Xbf]$,
+	\begin{equation*}
+	\pbf_v(u') \leq \pbf_s(u').
+	\end{equation*}
+
+	Note that by \ref{asmp: cluster_separation}, for every $u \in \Csig[\Xbf], (u',u) \not\in E$ and therefore $s(u') = 0$.
+Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
+	\begin{align*}
+	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
+	& \leq \frac{\norm{s}_1}{\degminpr}
+	\end{align*}
+	where the last inequality follows from precisely the same reasoning as \eqref{eqn: one_step_bound}.
+The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
+\end{proof}
+
+We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
+\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
+~
+
+Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirement of Lemma \ref{lem: setup}, and therefore by that lemma we have the following bounds:
+\begin{align*}
+\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}} \tag{for each $u \in \Cset[\Xbf]$} \\
+\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \tag{for each $u' \in \Cset'[\Xbf]$}
+\end{align*}
+
+We will further show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bound holds with probability tending to one as $n \to \infty$:
+\begin{equation}
+\label{eqn: gap_bounds}
+\frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}, \frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \leq \frac{1}{5} \piminwt,
+\end{equation}
+\textcolor{red}{which will prove the claim.}
+
+By Lemma \ref{lem: ball_bounds_in_probability}, $\degminpr\cdot \widetilde{D}_{\min}$ is upper bounded,
+\begin{equation}
+\label{eqn: pimin_Dmin_lb}
+\piminwt \cdot \widetilde{D}_{\min} = \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \leq \frac{36}{625} \frac{\lambda^2 \nu_d r^d}{\Lambda_{\sigma} \nu_d \Pbb(\Csig)}  
+\end{equation}
+where the bound holds with probability tending to one as $n \to \infty$.
+
+By Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, with probability one as $n \to \infty$,
+\begin{equation}
+\label{eqn: difficulty_bound}
+\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])} \leq \kappa_1(\Cset).
+\end{equation}
+\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa2_ub} together show \eqref{eqn: gap_bounds}.
+
+\subsection{Linear Algebra Facts}
+\label{sec: linalg}
+
+We state here a number of basic facts which follow from matrix manipulations. These will be used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+
+\begin{lemma}
+	\label{lem: soakage_ppr_lb}
+	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
+	\begin{equation*}
+	\pbf_{v}(u) \leq \pbf_{s}(u)
+	\end{equation*}
+	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
+\end{lemma}
+\begin{proof}
+	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
+	\begin{align*}
+	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
+	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
+	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf_n^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf_n^{T - t - 1} \right)(u)\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u) \\
+	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u) \\
+	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u) \\
+	& = \pbf_s(u)
+	\end{align*}
+\end{proof}
+
+Let $s_t := q(\Wbf \Ibf{S})^t(\Wbf(\Ibf{S^c}))$ be the soakage vector out of $S \subseteq V$, where $\Ibf{S}$ is a $\abs{V} \times \abs{V}$ diagonal matrix with $(\Ibf{S})_{uu} = 1$ if $u \in S$ and 0 otherwise, and $\Ibf{S^c} := \Ibf{} - \Ibf{S}$.
+\begin{lemma}
+	\label{lem: sum_of_soakages}
+	Let $G = (V,E)$ be an unweighted, undirected graph with associated random walk matrix $\Wbf$. For any $T \in \mathbb{N}, T \geq 1$, $q \in \Reals^{\abs{V}}$, and $S \subseteq V$
+	\begin{equation}
+	\label{eqn: sum_of_soakages}
+	q\Wbf^T = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} + q(\Wbf \Ibf{S})^T
+	\end{equation}
+	In particular, if $u \in V\setminus S$, then
+	\begin{equation}
+	\label{eqn: sum_of_soakages_2}
+	q\Wbf^T(u) = \sum_{t = 0}^{T - 1} \left(s_t \Wbf^{T - t - 1}\right)(u)
+	\end{equation}
+\end{lemma}
+\begin{proof}	
+	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.
+
+	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,
+	\begin{equation*}
+	q\Wbf = q\Wbf\Ibf{S} + q\Wbf\Ibf{S^c} =  q\Wbf\Ibf{S} + s_0. 
+	\end{equation*}
+
+	Then, for $T \in \mathbb{N},~ T \geq 2$,
+	\begin{align*}
+	q\Wbf^{T} & = q\Wbf^{T - 1}{\Wbf} \\
+	& = \left\{\sum_{t = 0}^{T - 2} s_t \Wbf^{T - 2 - t} + q(\Wbf \Ibf{S})^{T - 1} \right\} \Wbf \tag{by the inductive hypothesis}\\
+	& = \sum_{t = 0}^{T - 2} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S} + \Wbf \Ibf{S^c}) \\
+	& = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S})
+	\end{align*}
+	and the proof is complete.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: total_leakage_equal_total_soakage}
+	Letting $s_t$, $\ell_t$ $s$ and $\ell$ be as in \eqref{eqn: leakage_soakage},
+	\begin{equation*}
+	\norm{s_t}_1 = \norm{\ell_t}_1,~ \textrm{for each $t \geq 0$}
+	\end{equation*}
+	and therefore $\norm{s}_1 = \norm{\ell}_1$. 
+\end{lemma}
+\begin{proof}
+	By the definition of $s_t$ and $\ell_t$, we have
+	\begin{align*}
+	\norm{s_t}_1 & = \norm{q_t (\Wbf_n \widetilde{\mathbf{I}}_n^c)}_1 \\
+	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n^c)(u, u') \\
+	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1((u,u') \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
+	& = \norm{q_t (\Ibf{n} - \Dbf_n^{-1} \widetilde{\Dbf}_n)}_1 = \norm{\ell_t}_1.
+	\end{align*}
+\end{proof}
 
@@
 		\begin{lemma}
-			\label{lem: sum_of_soakages}
 
@@
 	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
-
-\end{proof}
+\end{proof}
+
+\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
+
+We note that by Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, 
+\begin{equation*}
+\kappa_2(\Cset) \geq \frac{\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])}.
+\end{equation*}
+As a result Lemma \ref{lem: setup} implies
+\begin{align}
+\label{eqn: theorem_4_1}
+p_u & \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~ (u \in \Cset[\Xbf]) \nonumber \\
+p_{u'} & \leq \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~~~~~~~~~~~~~~~~ (u' \in \Cset'[\Xbf])
+\end{align}
+
+We turn to bounding $\widetilde{\pi}_{n,r}(u)$. Clearly,
+\begin{align*}
+\widetilde{\pi}_{n,r}(u) & \geq \frac{\widetilde{D}_{\min}}{\widetilde{\vol}_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{\widetilde{D}_{\min}}{\wn \widetilde{D}_{\max}}.
+\end{align*}
+Application of Lemma \ref{lem: ball_bounds_in_probability} then yields
+\begin{equation}
+\label{eqn: theorem_4_2}
+\widetilde{\pi}_{n,r}(u) \geq 8 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
+\end{equation}
+as well as
+\begin{equation}
+\label{eqn: theorem_4_3}
+\frac{1}{\widetilde{D}_{\min}} \leq \frac{2}{\nu_d r^d \lambda_{\sigma}}
+\end{equation}
+with probability tending to $1$ as $n \to \infty$, for all $u \in \Cset[\Xbf]$ (indeed, all $u \in \Csig[\Xbf]$.)
+
+Combining \eqref{eqn: theorem_4_1}, \eqref{eqn: theorem_4_2} and \eqref{eqn: theorem_4_3}, along with the requirement on $\kappa_2(\Cset)$ given by \eqref{eqn: kappa2_ub}, we have
+\begin{align*}
+p_u & \geq 3/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2} \\
+p_{u'} & \leq 1/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
+\end{align*}
+for any $u \in \Cset$, $u' \in \Cset'$.
+As a result, if $\pi_0 \in (2/5, 3/5)\cdot \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}$, as $n \to \infty$ with probability tending to one any sweep cut of the form of \eqref{eqn: sweep_cuts}, including the output set $\widehat{C}$, will successfully recover $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
 

### 2019-05-03 arxiv/arxiv_local_density_clustering_proofs.tex
revised proofs for cluster recovery portion

@@
 \newcommand{\degminpr}{\deg_{\min}'}
+\newcommand{\degminwt}{\widetilde{\deg}_{\min}}
+\newcommand{\degmaxwt}{\widetilde{\deg}_{\max}}
+\newcommand{\degmax}{\deg_{\max}}
 \newcommand{\piminwt}{\widetilde{\pibf}_{\min}}
+\newcommand{\piminpr}{\pibf_{\min}'}
 
@@
 	\begin{align*}
-	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
-	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
-	\end{align*}
-\end{lemma}
+	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
+	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
+	\end{align*}
+\end{lemma}
+
+We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemma \ref{lem: multiplicative_Hoeffding}. Let
+\begin{align*}
+\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
+& \degminpr := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r})
+\end{align*}
 
@@
 	\label{lem: ball_bounds_in_probability}
-	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
-	\begin{align*}
-	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
-	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
-	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
-	\end{align*}
-	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
-\end{lemma}
-
-The statement follows immediately from Lemma \ref{lem: ball_bounds}.
+	Under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, for any $\epsilon > 0$, the following bounds hold with probability tending to $1$ as $n \to \infty$:
+	\begin{align}
+	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_degree_bound}\\
+	\frac{\degmax}{n} & \leq (1 + \epsilon) \Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
+	\frac{\abs{\Csig[\Xbf]}}{n} & \leq \Pbb(\Csig)(1 + \epsilon) \label{eqn: Csig_cardinality_bound}\\
+	\frac{6}{25}(1 - \epsilon)^2 \Pbb(\Csig) \lambda_{\sigma} \nu_d r^d \leq \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n^2} & \leq \Pbb(\Csig) \Lambda_{\sigma} r^d \nu_d (1 + \epsilon)^2 \label{eqn: volume_bounds}
+	\end{align}
+\end{lemma}
+\begin{proof}
+	We note that for any $x \in \Csig \cup \Csig'$, by \textcolor{red}{\ref{asmp: bounded_density}} along with Lemma \ref{lem: local_conductance},
+	\begin{equation*}
+	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r)) \leq \Lambda_{\sigma} r^d \nu_d.
+	\end{equation*}
+	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
+	\begin{equation*}
+	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
+	\end{equation*}
+	As the same bound holds for $\degminpr$, \eqref{eqn: min_degree_bound} is shown, and \eqref{eqn: max_degree_bound} follows from similar reasoning.
+
+	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers, and \eqref{eqn: volume_bounds} from \eqref{eqn: min_degree_bound}, \eqref{eqn: max_degree_bound}, and \eqref{eqn: Csig_cardinality_bound}.
+
+\end{proof}
 
@@
 
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
+We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$, and similarly $\piminpr := \min_{u \in \Cset'[\Xbf]} {\pibf}'_{n,r}(u)$.
 \paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
@@
 
-Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirement of Lemma \ref{lem: setup}, and therefore by that lemma we have the following bounds:
-\begin{align*}
-\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}} \tag{for each $u \in \Cset[\Xbf]$} \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \tag{for each $u' \in \Cset'[\Xbf]$}
-\end{align*}
+Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and therefore by that lemma the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
+\begin{align}
+\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degmaxwt} \nonumber \\
+\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \label{eqn: setup_redux}
+\end{align}
 
@@
 \label{eqn: gap_bounds}
-\frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}, \frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \leq \frac{1}{5} \piminwt,
-\end{equation}
-\textcolor{red}{which will prove the claim.}
-
-By Lemma \ref{lem: ball_bounds_in_probability}, $\degminpr\cdot \widetilde{D}_{\min}$ is upper bounded,
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}},\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \leq \frac{\min \set{\degmaxwt, \degminpr}}{125 \widetilde{\vol}_{n,r}(\Csig[\Xbf])}
+\end{equation}
+By \eqref{eqn: setup_redux} and \eqref{eqn: gap_bounds}, for each $u \in \Cset[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \widetilde{\vol}_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \widetilde{\vol}_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{22}{125 \widetilde{\vol}_{n,r}(\Csig[\Xbf])} \tag{by Lemma \ref{lem: ball_bounds_in_probability}, applied with $\epsilon = \frac{1}{47}$}
+\end{align*}
+and by similar reasoning, for each $u' \in \Cset'[\Xbf]$,
+\begin{equation*}
+\frac{\pbf(u')}{\deg_{n,r}(u')} \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \widetilde{\vol}_{n,r}(\Csig[\Xbf])} \leq \frac{1}{125 \widetilde{\vol}_{n,r}(\Csig[\Xbf])}.
+\end{equation*}
+
+\textcolor{red}{Complete the proof.}
+
+It remains to prove \eqref{eqn: gap_bounds}. By application of Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$, $\piminwt \cdot \degminwt$ can be lower bounded
 \begin{equation}
 \label{eqn: pimin_Dmin_lb}
-\piminwt \cdot \widetilde{D}_{\min} = \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \leq \frac{36}{625} \frac{\lambda^2 \nu_d r^d}{\Lambda_{\sigma} \nu_d \Pbb(\Csig)}  
+\piminwt \cdot \degminwt = \frac{\degminwt^2}{\widetilde{\vol}_{n,r}(\Csig[\Xbf])} \geq \frac{1}{25} \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
 \end{equation}
@@
 
-By Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, with probability one as $n \to \infty$,
+By Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, with probability tending to one as $n \to \infty$,
 \begin{equation}

### 2019-05-07 arxiv/arxiv_local_density_clustering.tex
aPPR and misclassification rates added, proofs refined

@@
 \usepackage{hyperref}
-\usepackage{amsmath}
+\usepackage[reqno]{amsmath}
 \usepackage{amsfonts, amsthm, amssymb}
@@
 \renewcommand{\bibsection}{\subsubsection*{\bibname}}
+
+% Left and right equations
+\makeatletter
+\newcommand{\leqnomode}{\tagsleft@true\let\veqno\@@leqno}
+\newcommand{\reqnomode}{\tagsleft@false\let\veqno\@@eqno}
+\makeatother
 
@@
 
-For a level $\beta > 0$ and a target stationary measure $\pi_0 > 0$, we define a
+For a level $\beta > 0$ and a target volume $\vol_0 > 0$, we define a
 \emph{$\beta$-sweep cut} of $\pbf$ as  
@@
 \label{eqn: sweep_cuts}
-S_\beta = \{u \in V: p_u > \beta \pi_{0}\}.
+S_\beta = \{u \in V: \textcolor{red}{\frac{p_u}{\Dbf_{uu}}} > \frac{\beta}{\vol_{0}}\}.
 \end{equation}
 Having computed sweep cuts over a range \smash{$\beta \in  
-(\frac{3}{10},\frac{1}{2})$},\footnote{The choice of a specific range such as 
-\smash{$(\frac{3}{10}, \frac{1}{2})$} is standard in the analysis of PPR
+(\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
+\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
 algorithms, see, e.g., \citep{zhu2013}.}
@@
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation 
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary measure $\pi_0 >
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume $\pi_0 >
 0$. \\   
@@
     ppr_vector}. 
-  \STATE For $\beta \in (\frac{3}{10}, \frac{1}{2})$ compute sweep cuts
+  \STATE For $\beta \in (\frac{1}{40}, \frac{1}{11})$ compute sweep cuts
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
@@
   $$
-  \beta^* = \argmin_{\beta \in (\frac{3}{10}, \frac{1}{2})} \Phi(S_{\beta}; G_{n,r}).
+  \beta^* = \argmin_{\beta \in (\frac{1}{40}, \frac{1}{11})} \Phi(S_{\beta}; G_{n,r}).
   $$
@@
 \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
-  density cluster}. Below we define a notion of consistency in density cluster
-estimation.
+density cluster}. Below we give two notions of performance of a density cluster estimate.
+
+\begin{definition}[Misclassification rate]
+\label{def: misclassification_rate}
+For an estimator \smash{$\widehat{\Cset} \subseteq \Xbf$} and set
+$\mathcal{S} \subseteq \Reals^d$, the \emph{misclassification rate} of $\mathcal{S}$ by $\widehat{\Cset}$ is
+\begin{equation}
+\label{eqn: misclassification_rate}
+\abs{\widehat{\Cset} \setminus (\mathcal{S} \cap \Xbf)} + \abs{(\mathcal{S} \cap \Xbf) \setminus \widehat{\Cset}}.
+\end{equation}
+\end{definition}
 
@@
   (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
-  conditions (precluding clusters that are too thin and long).
-
-\item Under largely the same set of geometric conditions, we derive in Theorem
+  conditions (precluding clusters that are arbitrarily thin).
+
+\item Under \textcolor{red}{largely the same set of geometric conditions}, we derive in Theorem
   \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
@@
 \item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
-  Theorem \ref{thm: consistent_recovery_of_density_clusters} that the bounds
-  in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    inverse_mixing_time_lower_bound_nonconvex},
-  on the cluster quality criteria, have algorithmic consequences for PPR:
-  properly initialized, Algorithm \ref{alg: ppr} performs consistent density
-  cluster estimation in the sense of \eqref{eqn:
-    consistent_density_cluster_recovery}.
-
-\item We show in Corollary \ref{cor: ppr_cluster} that Theorems \ref{thm:
-    conductance_upper_bound} and \ref{thm:
-    inverse_mixing_time_lower_bound_nonconvex}, along with the results in 
-  \citep{zhu2013}, lead to alternative, graph-theoretic guarantees on cluster 
-  quality: an upper bound on the normalized cut of the estimated cluster 
-  \smash{$\widehat{C}$}, and an upper bound on volume of the symmetric set
-  difference between \smash{$\widehat{C}$} and $\Cset[\Xbf]$.
+  Theorem \ref{thm: consistent_recovery_of_density_clusters} that the bounds on the cluster quality criteria established in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+    inverse_mixing_time_lower_bound_nonconvex} have algorithmic consequences for \ppr: 
+  properly initialized, Algorithm \ref{alg: ppr} has low misclassification rate with respect to a small enlargement of the set $\Cset$, and if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+
+\item We show in Corollary \ref{cor: appr} that these statements hold also with respect to an approximate form of \pprspace, which can be efficiently computed.
 
 \item In Section \ref{sec: experiments}, we empirically
-  demonstrate that violations of the geometric conditions we require manifestly
-  impact density cluster recovery. 
+  demonstrate the tightness of the bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, and provide examples showing how violations of the geometric conditions we require manifestly
+  impact density cluster recovery by \ppr.  
 \end{enumerate}
@@
   \label{eqn: conductance_additive_error_bound}
-  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq \frac{4d}{\sigma}
+  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c \frac{d}{\sigma}
   \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
@@
 
-For \pprspace to successfully recover density clusters, the ratio
-$\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ should be small.  Let us
-introduce the following notation for the upper bounds in Theorems 
-\ref{thm: conductance_upper_bound} and \ref{thm:
-  inverse_mixing_time_lower_bound_nonconvex}:
+For \pprspace to accurately estimate a set, the ratio of normalized cut to inverse mixing time should be small.
+Letting $\theta := (\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the rates in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, further let
 \begin{align*}
-\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) 
-&= \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-  \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}, \\
-1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) 
-&= \left(d \log \mu + c_{\lambda} \right) \cdot \\ 
-& \left(c_1 + 9^d c_2
-  \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + 
-  c_{\lambda}\right)\right)
+\mathbf{\Phi}(\theta) 
+& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \\
+\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \mu + c_3) + \frac{d^2D^2}{r^2} \Bigl( \log d + c_3 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} c_{\lambda} + c_4 + \log \mu \Bigr) \biggr) \Biggr)^{-1}
 \end{align*}
-(where all constants $\lambda_\sigma,c_1,c_2, c_\lambda>0$ are as in these 
+(where all constants $c_0,c_1,c_2,c_3,c_4,c_\lambda>0$ are as in these 
 theorems).
 
-Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf$ and $\Psibf$.
+Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf(\theta)$ and $\Psibf(\theta)$.
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter} with respect to parameters $\sigma, \lambda_{\sigma}, \gamma > 0$ and $\Lambda_{\sigma}, D < \infty$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
-Then, setting $\kappa_1(\Cset)$ and $\kappa_2(\Cset)$ to be
-	\begin{align*}
-	\kappa_1(\Cset) & := \frac{\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma)}{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)} \\
-	\kappa_2(\Cset) & := \kappa_1(\Cset) \cdot \sqrt{\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)},
-	\end{align*}
-	we call $\Cset$ a \textrm{$(\kappa_1, \kappa_2)$-well-conditioned density cluster (with respect to $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).}
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: biLipschitz_mapping} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
+Then, setting
+	\begin{equation*}
+	\kappa(\Cset) := \frac{\mathbf{\Phi}(\theta)}{\mathbf{\Psi}(\theta)}
+	\end{equation*}
+	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster (with respect to $\theta$).}
 \end{definition}
 
-$\Phibf$ and $\Psibf$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.
-
-\begin{remark}
-	For convenience and maximum generality, we define $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to correspond with the bound given by \eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, and assume only \ref{asmp: bounded_density} - \ref{asmp: cluster_diameter}.
-However, if we additionally have \ref{asmp: convex}, then we could sharpen $\mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D)$ to the tighter rate of \eqref{eqn: inverse_mixing_time_lower_bound}, with no other changes to subsequent results.
-\end{remark}
+$\Phibf(\theta)$ and $\Psibf(\theta)$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.
+
+\textcolor{red}{Add a remark here, about how this reinforces the results of Gary Miller and others, that PPR can fail to pick up fat sets even when normalized cut properly identifies them.}
 
@@
 \label{eqn: initialization}
-\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D), & ~r \leq \sigma/4d  \nonumber \\
-\pi_0 \in [2/3, 6/5] \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}, & ~v \in \Csig[\Xbf]^g
+\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta), & ~r \leq \frac{\sigma}{2d} \nonumber,  \\
+\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, & ~v \in \Csig[\Xbf]^g
 \end{align}
 where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
-(Intuitively one can think of $\Csig[\Xbf]^g$ as being the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
+(Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
 
@@
 
+\textcolor{red}{Add a remark here, detailing how one might go about picking these parameters in practice.}
+
+\paragraph{Misclassification rates for \ppr.}
+
+In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
+This work, combined with the results of Section \ref{sec: cluster_quality_bounds}, immediately implies a bound on the volume of $\widehat{C} \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \widehat{C}$),
+\begin{equation}
+\label{eqn: graph_symmetric_set_difference}
+\frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\vol_{n,r}(\Csig[\Xbf])}, \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\vol_{n,r}(\Csig[\Xbf])} = \mathcal{O}\bigl( \kappa(\Cset) \bigr).
+\end{equation}
+
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on \textcolor{red}{misclassification rate}, we make further boundedness restrictions on the density $f$ to preclude vertices $x \in \Xbf$ with arbitrarily small degree.
+Namely,
+
+\begin{equation}
+\label{eqn: global_bounded_density}
+0 < \lambda_{\min} \leq f(x)
+\end{equation}
+
+\begin{theorem}
+	\label{thm: misclassification_rate}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$). Then, with probability tending to one as $n \to \infty$,
+	\begin{equation}
+	\label{eqn: misclassification_rate_ub}
+	\frac{\abs{\Csig[\Xbf] \setminus \widehat{C}}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}
+	\end{equation}
+	and
+	\begin{equation}
+	\label{eqn: misclassification_rate__ub_2}
+	\frac{\abs{\widehat{C} \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
+	\end{equation}
+	for universal constants $c_5, c_6 > 0$. 
+\end{theorem}
+
+\paragraph{Consistent density cluster estimation.}
+
+Neither \eqref{eqn: graph_symmetric_set_difference} nor Theorem \ref{thm: misclassification_rate} imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, u' \in \Cset'$, of the form
+\begin{equation}
+\label{eqn: ppr_gap}
+\frac{\pbf(u')}{\Dbf_{uu}} \leq \frac{c}{\vol_0} < \frac{C}{\vol_0} \leq \frac{\pbf(u)}{\Dbf_{uu}}.
+\end{equation}
+so that a sweep cut $S_{\beta}$ for $\beta \vol_0 \in [c,C]$ would fulfill both conditions laid out in \eqref{eqn: consistent_density_cluster_recovery}.
+Theorem \ref{thm: consistent_recovery_of_density_clusters} provides sufficient conditions under which this gap will appear.
+
+Similar to \eqref{eqn: global_bounded_density}, to preclude any vertices $x \in \Cset'$ from having arbitrarily low degree, we require additional lower bounds on the density
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{4}
+	\item 
+	\label{asmp: C'_bounded_density}
+	\emph{$\Cset'$- bounded density :} For each $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$, for all $x \in \Cset' + \sigma B$,
+	\begin{equation*}
+	\lambda_{\sigma} \leq f(x)
+	\end{equation*}
+	where $\sigma,\lambda_{\sigma}$ are as in \ref{asmp: bounded_density}.
+\end{enumerate}
+
 \begin{theorem}
 	\label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$). If
-	\begin{equation}
-	\label{eqn: kappa2_ub}
-	\kappa_2 \leq \frac{1}{40 \cdot 36} \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)},
-	\end{equation}
-	and Algorithm \ref{alg: ppr} is well-initialized, the output set $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume \ref{asmp: C'_bounded_density} holds.
+If Algorithm \ref{alg: ppr} is well-initialized, there exists universal constant $c_7 > 0$ such that if
+	\begin{equation}
+	\label{eqn: kappa_ub}
+	\kappa(\Cset) \leq c_7 \frac{\lambda_{\sigma}^2r^d \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)},
+	\end{equation}
+	then the output set $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 \end{theorem}
 
-\begin{remark}
-	We note that replacing $40 \cdot 36$ by larger constants in \eqref{eqn: kappa2_ub} allow for wider ranges of parameters in \eqref{eqn: initialization}. 
-\end{remark}
-\paragraph{Approximate cluster recovery via PPR}
-
-In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
-Although not the primary focus of our work, it is perhaps worth noting that these results, coupled with Theorems \ref{thm: conductance_upper_bound}-\ref{thm: inverse_mixing_time_lower_bound}, translate immediately into bounds on the normalized cut of $\widehat{C}$ and the (volume-weighted) symmetric set difference of $\widehat{C}$ and $\Csig[\Xbf]$.
-
-We collect some of the main results of \cite{zhu2013} in Theorem \ref{thm: ppr_cluster}.
-For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
-\begin{theorem}[Theorem 1 of \cite{zhu2013}]
-	\label{thm: ppr_cluster}
-	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$.
-Letting
+\textcolor{red}{Add a remark about how constants don't matter.}
+
+\textcolor{red}{Add a remark about why we should believe the exponential in $d$ requirements are necessary.}
+
+\paragraph{Cluster estimation with the approximate \pprspace vector.}
+
+As mentioned previously, in practice solving \eqref{eqn: ppr_vector} may be too computationally expensive.
+To address this limitation, \citet{andersen2006} introduced the \emph{$\epsilon$-approximate \pprspace vector} (aPPR), which we will denote $\pbf^{(\epsilon)}$.
+We refer the curious reader \citep{anderson2006} for a formal algorithmic definition of the a\pprspace, and limit ourselves to highlighting a few salient points.
+Namely, the aPPR vector requires only order $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ computations, while satisfying the following uniform error bound:
+\begin{equation}
+\label{eqn: appr_error}
+\textrm{for all $x \in \Xbf$}, \quad \pbf(x) - \epsilon \deg_{n,r}(x)\leq \pbf^{(\epsilon)}(x) \leq \pbf(x)
+\end{equation}
+
+Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} leads to analogous results which hold with respect to $\pbf^{(\epsilon)}$.
+
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}.
+Set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\widehat{C}$.
+	\begin{enumerate}
+		\item Assume \eqref{eqn: global_bounded_density} holds. Then \eqref{eqn: misclassification_rate} and \eqref{eqn: misclassification_rate_2} are still valid upper bounds.
+		\item Assume \ref{asmp: C'_bounded_density} holds. If
 		\begin{equation*}
-	\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G)
+		\kappa(\Cset) \leq c_7 \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)}
 		\end{equation*}
-	the following guarantees hold:
-	\begin{align*}
-	\vol(\widehat{C} \setminus A; G) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\vol(A \setminus \widehat{C}; G)  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
-	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
-	\end{align*}
-\end{theorem}
-
-Corollary \ref{cor: ppr_cluster} -- an analogous statement to Theorem \ref{thm: ppr_cluster} but stated specifically with respect to $\Csig[\Xbf]$-- immediately follows.
-\begin{corollary}
-	\label{cor: ppr_cluster}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $(\kappa_1,\kappa_2)$-well conditioned cluster (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$).
-Then, if Algorithm \ref{alg: ppr} is well-initialized (in the sense that the choices of input parameters satisfy (\ref{eqn: initialization})), the following guarantees hold for output set $\widehat{C} \subseteq \Xbf$:
-	\begin{align*}
-	\vol(\widehat{C} \setminus \Csig[\Xbf]; G_{n,r})  & \leq 30 \kappa_2(\Cset) \vol(\Csig[\Xbf]) \\
-	\vol(\Csig[\Xbf] \setminus \widehat{C}; G_{n,r}) & \leq 30 \kappa_2(\Cset) \vol(\Csig[\Xbf]) \\
-	\Phi_{n,r}(\widehat{C}) & = O\left(\kappa_1(\Cset)\right)
-	\end{align*}
+		then $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
 \end{corollary}

### 2019-05-07 arxiv/arxiv_local_density_clustering_proofs.tex
aPPR and misclassification rates added, proofs refined

--- 2019-05-02 arxiv/arxiv_local_density_clustering_proofs.tex
@@
 \let\pprspace\relax
+\let\ppr\relax
 \externaldocument{arxiv_local_density_clustering}
@@
 \newcommand{\degminpr}{\deg_{\min}'}
+\newcommand{\degminwt}{\widetilde{\deg}_{\min}}
+\newcommand{\degmaxwt}{\widetilde{\deg}_{\max}}
+\newcommand{\degmax}{\deg_{\max}}
 \newcommand{\piminwt}{\widetilde{\pibf}_{\min}}
+\newcommand{\piminpr}{\pibf_{\min}'}
+\newcommand{\degmin}{\deg_{\min}}
 
@@
 	\begin{align*}
-	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
-	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
-	\end{align*}
-\end{lemma}
+	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
+	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
+	\end{align*}
+\end{lemma}
+
+We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemma \ref{lem: multiplicative_Hoeffding}. Let
+\begin{alignat*}{2}
+\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ && \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
+\degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
+\degmin & := \min_{u \in \Csig{\Xbf}} \deg(u; G_{n,r}).
+\end{alignat*}
 
@@
 	\label{lem: ball_bounds_in_probability}
-	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
-	\begin{align*}
-	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
-	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
-	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
-	\end{align*}
-	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
-\end{lemma}
-
-The statement follows immediately from Lemma \ref{lem: ball_bounds}.
+	Under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
+	\begin{align}
+	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
+	\frac{\degmin}{n} & \geq  (1 - \epsilon) \lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\frac{\degmax}{n} & \leq (1 + \epsilon) \Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
+	\frac{\abs{\Csig[\Xbf]}}{n} & \leq \Pbb(\Csig)(1 + \epsilon) \label{eqn: Csig_cardinality_bound}\\
+	\label{eqn: volwt_bound}
+	\frac{1}{2}\vol_0 \leq \vol_{n,r}(\Csig[\Xbf]) & \leq \frac{3}{2} \vol_0
+	\end{align}
+\end{lemma}
+\begin{proof}
+	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
+	\begin{equation*}
+	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
+	\end{equation*}
+	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
+	\begin{equation*}
+	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
+	\end{equation*}
+	As the same bound holds for $\degminpr$, \eqref{eqn: min_cluster_degree_bound} is shown. \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
+
+	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
+
+	Finally, note that
+	\begin{equation*}
+	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
+	\end{equation*}
+	can be rewritten as a U-statistic, and furthermore
+	\begin{equation*}
+	\int_{\Csig} \Pbb(B(x,r)) dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
+	\end{equation*}
+
+	Therefore by Lemma \ref{lem: bounded_difference}
+	\begin{equation}
+	\label{eqn: ball_bounds_in_probability_1}
+	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx 
+	\end{equation}
+	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) dx) \to 0$ as $n \to \infty$.
+Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx$ given by \eqref{eqn: initialization}, yields
+	\begin{equation*}
+	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx \leq \frac{1}{2} \vol_0.
+	\end{equation*}
+\end{proof}
+
+\subsection{Proof of Theorem \ref{thm: misclassification_rate}}
+\label{sec: proof_of_misclassification_rate}
+
+In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
+
+Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
+It is stated with respect to an arbitrary $A \subseteq G = (V,E)$, and a good set $A^g \subseteq A$ with $\vol(A^g; G) \geq \vol(A; G)/2$.
+\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(A;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+
+\begin{lemma}
+	\label{lem: zhu}
+	Let $\epsilon \geq 0$, $v \in A^g$, $\alpha \leq \frac{\Psi(A; G)}{9}$, and $\vol_0 \in [1 - c,1 + c] \vol(A;G)$ for $0 < c < 1$.
+Consider taking sweep cuts of the \textcolor{red}{approximate \pprspace vector} $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
+	\begin{equation*}
+	S_{\beta} := \left\{u \in V: \pbf^{(\epsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
+	\end{equation*}
+
+	For any $\beta < \frac{3}{5(1 + c)}$, and $\epsilon \leq \frac{1}{10} \vol(A;G)$ the following bounds hold:
+	\begin{align}
+	\vol(S_{\beta} \setminus A; G) \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(A; G), \label{eqn: zhu_1}\\
+	\vol(A \setminus S_{\beta}; G) \leq \left(\frac{2\Phi(A;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(A;G)\right)\vol(A; G),  \label{eqn: zhu_2}
+	\end{align}
+\end{lemma}
+
+\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
+
+Observe that by Theorem \ref{thm: inverse_mixing_time_lower_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}(\theta)}{9}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Moreover, i) we restrict $v \in \Csig[\Xbf]^g$; ii) the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$; iii) by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$, and iv) the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$.
+All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq \mathbf{\Psi}(\theta)/10$, the following bounds hold with probability tending to 1 as $n \to \infty$:
+\begin{equation*}
+\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
+\end{equation*}
+Noting that
+\begin{align*}
+\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) & \geq \abs{\widehat{C} \setminus \Csig[\Xbf]} \min_{x \in \Xbf} \{\deg_{n,r}(x)\} \\
+\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) & \geq \abs{\Csig[\Xbf] \setminus \widehat{C}} \min_{x \in \Csig[\Xbf]} \{\deg_{n,r}(x)\},~ \textrm{and} \\
+\vol_{n,r}(\Csig[\Xbf]) & \leq \abs{\Csig[\Xbf]} \max_{x \in \Csig[\Xbf]} \set{\deg_{n,r}(x)}
+\end{align*}
+the claim follows in light of Lemma \ref{lem: ball_bounds_in_probability}.
+
+\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
+
+The choice $\epsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\epsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\epsilon)}$.
+All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
 
@@
 
-Recall that for teleportation parameter $\alpha  \in (0,1]$ and seed node $v \in \Xbf$, we write $\pbf(v, \alpha; G_{n,r})$ for the \pprspace vector computed over neighborhood graph $G_{n,r}$; let $\pbf(u)$ denote the entry of $\pbf(v, \alpha; G_{n,r})$ at vertex $u \in \Xbf$.
-Recalling that we write $\widetilde{\pibf}_{n,r}$ for the stationary distribution over $\widetilde{G}_{n,r}$, write $\widetilde{\pibf}_{n,r}(u)$ denote the stationary distribution at vertex $u \in \Csig[\Xbf]$.
-
-Lemma \ref{lem: setup} states the key results needed to link Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} with Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+We begin with some notation.
+Let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and random walk matrices for the induced subgraph $G_{n,r}(\Csig[\Xbf]) = \widetilde{G}_{n,r}$, with vertex set $\widetilde{V} = \Csig[\Xbf]$ and edge set $\widetilde{E} = \set{(u,v) \in G_{n,r}: u,v \in \Csig[\Xbf]}$.
+Consider the function $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$
+\begin{equation*}
+\overline{\pibf}_{n,r}(x) := \frac{\widetilde{\deg}_{n,r}(x)}{\vol_{n,r}(\Csig[\Xbf])}.
+\end{equation*}
+(Note $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
+
+Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(u) - \overline{\pibf}_{n,r}(u)$ over all $x \in \Xbf$ (where in an abuse of notation we consider $\overline{\pibf}_{n,r}(x) = 0$ for $x \in \Xbf \setminus \Csig[\Xbf]$).
 \begin{lemma} 
 	\label{lem: setup}
-	Let $0 < r < \sigma$ and
-	\begin{equation} 
-	\label{eqn: upper_bound_alpha}
-	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
-	\end{equation}
-
-	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
+	Let $0 < r < \sigma$ and $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
 	\begin{itemize}
@@
 		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
-		\end{equation}
-		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Csig'[\Xbf]$,
+		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminwt}
+		\end{equation}
+		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
 		\begin{equation}
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}
-		\end{equation}
-		where $ \deg_{\min}' := \min_{u \in \Cset'[\Xbf]} \deg(u; G_{n,r})$. 
+		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}.
+		\end{equation}
 	\end{itemize}
@@
 \begin{proof}
-	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult.
-We begin with some notation.
-Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$.
-Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
-Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
-	\begin{equation}
-	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
+	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. Given starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
+	\begin{equation}
+	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}
 	\end{equation}
 	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
-(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
+(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \widetilde{V}$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
 
@@
 	\label{eqn: leakage_soakage}
-	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
-	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
+	\ell_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\mathbf{I} - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
+	s_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\Wbf \widetilde{\mathbf{I}}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
 	\end{align}
-	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
-
-	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
-For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$.
-By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
+	where $\mathbf{I}$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}$ is an $n \times n$ diagonal matrix with $\widetilde{\mathbf{I}}_{xx} = 1$ if $x \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}^c = \mathbf{I} - \widetilde{\mathbf{I}}$.
+
+	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
+For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$.
+By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is soaked up into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
 The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
@@
 	\label{eqn: zhulemma3.1}
-	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
+	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
 	\end{equation}
@@
 	\begin{equation*}
-	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
+	\widetilde{\pbf}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
 	\end{equation*}
@@
 	\begin{equation*}
-	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
-	\end{equation*}
-
-	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
-We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$.
-First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$.
+	\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
+	\end{equation*}
+
+	We proceed to show the upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \degminwt$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
+We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$.
+First, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$.
 As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
+Second, for any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$, and any $t \geq 1$,
 	\begin{align}
 	\label{eqn: one_step_bound}
-	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
-	& \leq \frac{1}{\widetilde{D}_{\min}} 
+	q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
+	& \leq \frac{1}{\degminwt} 
 	\end{align}
-	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}$.
+	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
 
@@
 	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& \leq \norm{\ell}_1 \frac{1}{\widetilde{D}_{\min}}.
+	& \leq \frac{\norm{\ell}_1 }{\degminwt}.
 	\end{align*}
@@
 We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
+
 \paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
@@
 
-Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirement of Lemma \ref{lem: setup}, and therefore by that lemma we have the following bounds:
-\begin{align*}
-\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}} \tag{for each $u \in \Cset[\Xbf]$} \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \tag{for each $u' \in \Cset'[\Xbf]$}
-\end{align*}
-
-We will further show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bound holds with probability tending to one as $n \to \infty$:
-\begin{equation}
-\label{eqn: gap_bounds}
-\frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}, \frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \leq \frac{1}{5} \piminwt,
-\end{equation}
-\textcolor{red}{which will prove the claim.}
-
-By Lemma \ref{lem: ball_bounds_in_probability}, $\degminpr\cdot \widetilde{D}_{\min}$ is upper bounded,
+In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
+
+Observe that by Theorem \ref{thm: inverse_mixing_time_lower_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}}{9}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
+\begin{align}
+\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
+\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
+\end{align}
+We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
+\begin{align}
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
+\end{align}
+
+The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\epsilon = \frac{1}{47}$} \\
+& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+Similarly, for each $u' \in \Cset'[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
+& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
+& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
+
+It remains to prove \eqref{eqn: gap_bounds}. Apply Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$ to obtain
 \begin{equation}
 \label{eqn: pimin_Dmin_lb}
-\piminwt \cdot \widetilde{D}_{\min} = \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \leq \frac{36}{625} \frac{\lambda^2 \nu_d r^d}{\Lambda_{\sigma} \nu_d \Pbb(\Csig)}  
+\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
 \end{equation}
@@
 
-By Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, with probability one as $n \to \infty$,
+By Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \mathbf{\Psi}}$ given by \eqref{eqn: initialization}, with probability tending to one as $n \to \infty$,
 \begin{equation}
 \label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])} \leq \kappa_1(\Cset).
-\end{equation}
-\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa2_ub} together show \eqref{eqn: gap_bounds}.
+\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa_1(\Cset).
+\end{equation}
+\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
+
+\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
+
+Using \eqref{eqn: appr_error} with $\epsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
+\begin{equation*}
+\pbf^{(\epsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
+\end{equation*}
+and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
+\begin{equation*}
+\frac{\pbf^{(\epsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
+\end{equation*}
+
+On the other hand $\pbf^{(\epsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\epsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
 
@@
 
-We state here a number of basic facts which follow from matrix manipulations. These will be used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+We state here a number of basic facts which follow from matrix manipulations, which are used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
 

### 2019-05-10 arxiv/arxiv_local_density_clustering.tex
updated mixing time proof and section, edited other sections

@@
 \newcommand{\Cbb}{\mathbb{C}}
+\newcommand{\Ebb}{\mathbb{E}}
 
@@
 \item Under \textcolor{red}{largely the same set of geometric conditions}, we derive in Theorem
-  \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
+  \ref{thm: inverse_lower_bound_nonconvex} a lower bound on the
   inverse mixing time of a random walk over $\Csig[\Xbf]$.
@@
 \item
-\label{asmp: cluster_diameter}
-\emph{Cluster diameter:}
-There exists $D < \infty$ such that for all $x, x' \in \Csig$,
+\label{asmp: embedding}
+\emph{Lipschitz embedding:}
+There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
+\begin{equation*}
+\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
+\end{equation*}
+such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
+Furthermore, there exists $D < \infty$ such that for all $x, x' \in \mathcal{K}$
 $$
@@
 $$
-
-\item
-\label{asmp: biLipschitz_mapping}
-\emph{biLipschitz mapping to convex set:}
-There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
-\begin{equation*}
-\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
-\end{equation*}
-such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
 \end{enumerate}
@@
 Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
-clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp:
-  cluster_diameter}, flat densities around the level set in \ref{asmp: 
-  low_noise_density}, and poorly separated clusters in \ref{asmp:
-  cluster_separation}.
+clusters and long clusters in \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
 
 Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
-\ref{asmp: cluster_separation} and \ref{asmp: biLipschitz_mapping} are used to upper bound $\Phi(\Cset[\Xbf];
-G_{n,r})$, whereas \ref{asmp: bounded_density}, \ref{asmp: cluster_diameter} and \ref{asmp: biLipschitz_mapping} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
+and \ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
+G_{n,r})$, whereas \ref{asmp: bounded_density}, and \ref{asmp: embedding} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
 lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
@@
 \end{equation}
-with probability at least $1-\delta$.
+with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
 \end{theorem}
@@
 proofs in this paper, can be found in the supplementary document. The key 
-idea is that for any $x \in \Cset$, the simple (possibly loose) fact
+idea is that for any $x \in \Cset$, the simple fact
 $B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Csig + rB) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
@@
 \begin{remark}
-The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
-tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
+The inequality in \eqref{eqn: conductance_additive_error_bound} is tight in the case of $\Cset = \set{0}$. To see this, let $\Csig = B(0,\sigma)$ and
 $$
  f(x)  = \begin{cases}
-   \lambda &\text{for $x \in \Asig$}, \\
-   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
+   \lambda &\text{for $x \in \Csig$}, \\
+   \lambda - \dist(x,\Csig)^{\gamma} & \text{ for $0 < \dist(x,\Csig) < r$}, 
 \end{cases}
 $$
-we have that for $n$ on the order of the lower bound in \eqref{eqn: 
-  conductance_sample_complexity}, 
-$$
-  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
-    \frac{r^{\gamma+1}}{\gamma+1})}{\lambda} - \epsilon,
-$$
-with probability at least $1 - \delta$, for some constant $c$. (Note that the
-factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
+Then, some simple calculations yield
+\begin{equation*}
+\frac{\Pbb((\Csig + B(0,r)) \setminus \Csig)}{\Pbb(\Csig)} \geq d\frac{(\lambda - r^{\gamma}) r}{\sigma},
+\end{equation*}
+and for some $c > 0$,
+\begin{equation*}
+\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) \setminus \Csig) \geq c \lambda \nu_d r^d \Pbb((\Csig + B(0,r)), \quad \textrm{and} \quad \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r}) \leq c \lambda \nu_d r^d \Pbb(\Csig)
+\end{equation*}
+so the ratio $\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) / \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r})$ matches \ref{eqn: conductance_additive_error_bound}, up to constants.
+
 \end{remark}
@@
 
-Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of 
-$\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) =
-1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time. 
-% RJT: note I changed the next two theorems to be upper bounds on the mixing
-% time.  Upper bounds on the inverse inverse mixing time, which was a bit
-% superfluous.  Just make sure that the supplement is in sync with this
-% AJG: Perfect.
+Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of $\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) = 1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time.
 
 \begin{theorem}
-\label{thm: inverse_mixing_time_lower_bound_nonconvex}
-Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
-for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
-r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
-$$
-\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
-    \lambda_{\sigma}}} \leq \epsilon, 
-$$
-where \smash{$\mu = \log(\frac{2D}{r})$}, we have
-\begin{multline}
-\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
-\tau_{n,r}(\Csig[\Xbf]) \leq (d \log \mu + c_{\lambda}) \cdot \\  
-\left(c_1 + 9^d c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
-    \log \mu + c_{\lambda}\right)\right),
-\end{multline}
-with probability at least $1 - \delta$, where $c_1,c_2>0$ are universal constants
- and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
-\lambda_{\sigma}^2)$.   
+	\label{thm: mixing_time_upper_bound}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, K > 0$.
+Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
+	\begin{equation*}
+	\limsup_{n \to \infty}\tau_{n,r}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
+	\end{equation*}
 \end{theorem}
-% RJT: saying that c_1,c_2 depend on the dimension is a little odd/weak.
-% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
-% will swamp the linear factor of ....
-% AJG: Fixed.
-
-\begin{remark}
-The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies
-on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[\Xbf]]$, 
-$$
-\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[\Xbf]]).
-$$
-The factor of $1/r^{2d}$ in the bound in \eqref{eqn:
-  inverse_mixing_time_lower_bound_nonconvex} is suboptimal. This exponential 
-dependence on $d$ stems from a loose bound on the aforementioned
-conductance. In particular, we assert only that any set $S \subseteq \Csig[X]$
-must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding
-$\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of
-order $r^d$. The presence of $r^{2d}$ comes from upper bounding the mixing time
-by about \smash{$1/\widetilde{\Phi}^2$}, this being a variant of classic results
-on rapid mixing \citep{jerrum89}.  
-\end{remark}
-
-\subsection{Tighter Lower Bound Under Convexity}
-
-It is possible to sharpen the dependency on $d$ in 
-\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
-additional assumption.
-\begin{enumerate}[label=(A\arabic*)]
-\setcounter{enumi}{4}
-\item 
-\label{asmp: convex}
-\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
-\end{enumerate}
-
-With \ref{asmp: convex} in place, we give a tighter bound on the
-mixing time (albeit one that holds only asymptotically).
-
-\begin{theorem}
-\label{thm: inverse_mixing_time_lower_bound}
-Assume the conditions of Theorem \ref{thm:
-  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
-  convex}. Then for any $0 < r < \sigma/4d$, the following holds with
-probability 1:   
-\begin{align}
-\label{eqn: inverse_mixing_time_lower_bound}
-  \limsup_{n \to \infty} \, &\tau_{n,r}(\Csig[\Xbf]) \leq \nonumber \\ 
-&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
-  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
-&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
-  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
-&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
-\end{align}
-where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
-constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
-$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
-% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
-\end{theorem}
-
-\begin{remark}
-The only potentially exponential dependence on dimension comes from the
-factor of $c_d$.
-However, for sufficiently small values of $r$ $o_r(1)/r^2$ will be dominated by $1/r^2$, and therefore the last term in \eqref{eqn: inverse_mixing_time_lower_bound} will contribute negligibly to the overall bound.
-\end{remark}
-\begin{remark}
-We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
-to those of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part 
-by working with a generalization of the conductance, the \emph{conductance
-  function},
-$$
-\widetilde{\Phi}_{n,r}(t) = 
-\min_{\substack{S \subseteq \Csig[\Xbf] \\ \widetilde\pi(S) \leq t}} 
-\Phi(S; G_{n,r}[\Csig[X]]),
-$$
-where \smash{$\widetilde\pi$} is the stationary distribution over
-$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
-known upper bound of mixing time by  
-\begin{equation}
-\label{eqn: average_conductance}
-\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
-\end{equation}
-which results in a tighter bound than merely using the conductance when
-\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.
-
-Our proof relies on a novel (to the best of our knowledge) lower bound
-on this conductance function over $G_{n,r}$ in terms of a population-level
-analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}, and define formally in the supplementary document.
-\begin{lemma}
-	\label{lem: consistency_of_conductance_function_main}
-	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
-	\begin{equation}
-	\label{eqn: pointwise_consistency_of_conductance_function}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\left\{\widetilde{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
-	\end{equation}
-	where $c_d$ is the same as in Theorem \ref{thm: inverse_mixing_time_lower_bound}.
-\end{lemma}
-Plugging
-\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
-a mixing time bound (with respect to total variation distance) on the order $d 
-D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
-  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
-(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
-pointwise distance (which is known to be a stricter metric). 
-\end{remark}
-
-\begin{remark}
-  The convexity condition is only needed to lower bound 
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any lower bound on
-  \smash{$\widetilde{\Phi}_{\Pbb,r}$} could be directly plugged into the 
-  machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
-  to yield an alternative result. In recent work, \citep{abbasi-yadkori2016} developed new
-  population-level bounds on the conductance function (without requiring
-  convexity), however the Markov chain dealt with there is somewhat different 
-  than the one we consider.    
-\end{remark}
+for $c_2,c_3 > 0$ universal constants.
+
+We will outline the main techniques used to prove Theorem \ref{thm: mixing_time_upper_bound}, but first, we show that a straightforward and perhaps immediately obvious route to upper bounding the mixing time is insufficient for our purposes.
+Let $\widetilde{\Phi}_{n,r}$ be the \emph{conductance} of the induced subgraph $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$, given by
+\begin{equation*}
+\widetilde{\Phi}_{n,r} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; \widetilde{G}_{n,r}),
+\end{equation*}
+and $\widetilde{\mu}_2$ be the 2nd largest eigenvalue of $\Wbf_{\Csig[\Xbf]}$, the random walk matrix over $\widetilde{G}_{n,r}$. The famous Cheeger's inequality
+\begin{equation*}
+\frac{\widetilde{\Phi}_{n,r}^2}{2} \leq 1 - \widetilde{\mu}_2 \leq \widetilde{\Phi}_{n,r}
+\end{equation*}
+applied with well known theory on $\infty$-mixing time yields
+\begin{equation*}
+\abs{\widetilde{\pi}_{n,r}(u) - e_v \Wbf_{\Csig[\Xbf]}^te_u} \leq \left(1 - \frac{\widetilde{\Phi}_{n,r}^2}{2}\right)^t \sqrt{\frac{\deg(u; \widetilde{G}_{n,r})}{\min_{v \in \Csig[\Xbf]} \deg(v; \widetilde{G}_{n,r})}} \tag{$u,v \in \Csig[\Xbf]$}
+\end{equation*}
+where $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$ Unfortunately, even if $\widetilde{G}_{n,r}$ is an approximately degree-regular graph, (meaning we can ignore the term under the square root), this bound only yields \footnote{For sequences of numbers $\set{a_n}_{n \in \mathbb{N}}, \set{b_n}_{n \in \mathbb{N}}$, we say $a_n = \mathcal{O}(b_n)$ when there exists $c$ sufficiently large such that $a_n \leq c b_n$ for all $n$.}
+\begin{equation*}
+\tau_{n,r}(\Csig[\Xbf]) = \mathcal{O} \left( \frac{\log\left(\frac{1}{\widetilde{\pi}_{\min}}\right)}{\widetilde{\Phi}_{n,r}^2} \right).
+\end{equation*}
+where $\widetilde{\pi}_{\min} = \min_{u \in \Csig[\Xbf]} \widetilde{\pi}_{n,r}(u)$.
+As $\widetilde{\pi}_{\min} = \mathcal{O}(1/n)$, the upper bound on the right hand side will be of order $\log(n)$, and the bound becomes trivial as $n \to \infty$.
+
+\textcolor{red}{We therefore apply a more complex approach.}
 
@@
 For \pprspace to accurately estimate a set, the ratio of normalized cut to inverse mixing time should be small.
-Letting $\theta := (\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the rates in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, further let
+Letting $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the bounds given in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, further abbreviate
 \begin{align*}
@@
 & := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \\
-\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \mu + c_3) + \frac{d^2D^2}{r^2} \Bigl( \log d + c_3 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} c_{\lambda} + c_4 + \log \mu \Bigr) \biggr) \Biggr)^{-1}
+\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
 \end{align*}
-(where all constants $c_0,c_1,c_2,c_3,c_4,c_\lambda>0$ are as in these 
-theorems).
+for these bounds (where all constants $c_0,c_1,c_2,c_3 >0$ are as in these theorems).
 
@@
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: biLipschitz_mapping} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: embedding} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
 Then, setting
@@
 
-$\Phibf(\theta)$ and $\Psibf(\theta)$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.
-
-\textcolor{red}{Add a remark here, about how this reinforces the results of Gary Miller and others, that PPR can fail to pick up fat sets even when normalized cut properly identifies them.}
+We focusing for a moment on the neighborhood graph radius $r$.
+While taking $r \to 0$ as $n \to \infty$ -- and thereby ensuring $G_{n,r}$ is sparse-- is computationally attractive, the presence of a factor of $\frac{1}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace for this regime.
+While the restriction to a kernel function fixed in $n$ is standard for theoretical analysis \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
+
+\paragraph{Well-conditioned clusters.}
 
@@
 \end{align}
-where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$.
+where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$.
 (Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
@@
 
-\textcolor{red}{Add a remark here, detailing how one might go about picking these parameters in practice.}
+%%% AJG 5/8/19: My attempt to explain how to choose these parameters
+%%% in practice. Not satisfied with it.
+
+In practice, a reasonable way to choose these hyperparameters is by tuning.
+For example, if one wanted to successfully recover a density cluster, one could vary each hyperparameter over a grid, retaining outputs $\widehat{\Cset}$ of Algorithm \ref{alg: ppr} only if they recover $\Cset[\Xbf]$ for some $\Cset \in \Cbb_f(\lambda)$ and discarding them otherwise.
+Then simply return the minimum normalized cut set from those $\widehat{\Cset}$ which were retained.
+Assuming there existed $\lambda > 0, \Cset \in \Cbb_f(\lambda)$ such that $\Cset$ satisfied the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, and moreover some combination of tuning parameters in the chosen grid satisfied \eqref{eqn: initialization}, this scheme would inherit the consistency guarantees of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
 
@@
 
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on \textcolor{red}{misclassification rate}, we make further boundedness restrictions on the density $f$ to preclude vertices $x \in \Xbf$ with arbitrarily small degree.
-Namely,
-
-\begin{equation}
-\label{eqn: global_bounded_density}
-0 < \lambda_{\min} \leq f(x)
-\end{equation}
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification rate, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
+To do so, we make some regularity assumptions on $\mathcal{X} = \mathrm{supp}(f)$.
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{4}
+	\item 
+	\label{asmp: valid_region}
+	\emph{Valid region:} $0 < \lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
+Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
+\end{enumerate}
+Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, $\mathcal{X}$ is a $\sigma$-expansion.
 
@@
 	\label{thm: misclassification_rate}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$). Then, with probability tending to one as $n \to \infty$,
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
+Then, with probability tending to one as $n \to \infty$,
 	\begin{equation}
@@
 	\begin{equation}
-	\label{eqn: misclassification_rate__ub_2}
+	\label{eqn: misclassification_rate_ub_2}
 	\frac{\abs{\widehat{C} \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
@@
 
+\begin{remark}
+	A notable implication of our theory is that as the diameter $D$ increases, our upper bounded on the normalized cut of $\Csig$ remains unchanged, but $\kappa(\Cset)$, and therefore the misclassification rate, worsens (increases).
+This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
+It suggests that \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$.
+This intuition will be supported by simulations in Section \ref{sec: experiments}.
+\end{remark}
+
 \paragraph{Consistent density cluster estimation.}
@@
 
-Similar to \eqref{eqn: global_bounded_density}, to preclude any vertices $x \in \Cset'$ from having arbitrarily low degree, we require additional lower bounds on the density
+As before, we wish to preclude arbitrarily low degree vertices, this time for points $x \in \Cset'[\Xbf]$.
 \begin{enumerate}[label=(A\arabic*)]
-	\setcounter{enumi}{4}
+	\setcounter{enumi}{5}
 	\item 
@@
 
-\textcolor{red}{Add a remark about how constants don't matter.}
-
-\textcolor{red}{Add a remark about why we should believe the exponential in $d$ requirements are necessary.}
-
 \paragraph{Cluster estimation with the approximate \pprspace vector.}
@@
 To address this limitation, \citet{andersen2006} introduced the \emph{$\epsilon$-approximate \pprspace vector} (aPPR), which we will denote $\pbf^{(\epsilon)}$.
-We refer the curious reader \citep{anderson2006} for a formal algorithmic definition of the a\pprspace, and limit ourselves to highlighting a few salient points.
-Namely, the aPPR vector requires only order $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ computations, while satisfying the following uniform error bound:
+We refer the curious reader to \cite{andersen2006} for a formal algorithmic definition of the a\pprspace vector, and limit ourselves to highlighting a few salient points.
+Namely, the aPPR vector can be computed in $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ time, while satisfying the following uniform error bound:
 \begin{equation}
@@
 Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}.
-Set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\widehat{C}$.
+Set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\widehat{\Cset}$.
 	\begin{enumerate}
-		\item Assume \eqref{eqn: global_bounded_density} holds. Then \eqref{eqn: misclassification_rate} and \eqref{eqn: misclassification_rate_2} are still valid upper bounds.
+		\item Assume \ref{asmp: valid_region} holds. Then \eqref{eqn: misclassification_rate_ub} and \eqref{eqn: misclassification_rate_ub_2} are still valid upper bounds.
 		\item Assume \ref{asmp: C'_bounded_density} holds. If
@@
 		\end{equation*}
-		then $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+		then $\widehat{\Cset} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 	\end{enumerate}
@@
 
-As we do not provide any theoretical lower bounds, we validate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} via simulation.
+As we do not provide any theoretical lower bounds, we validate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
 We sample points according to the density function $q$, where for $x \in \Rd$
@@
 \lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
-(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B), \setminus \Csig \\
+(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
 0,~ & \textrm{otherwise},
@@
 For each panel, the solid lines show, up to constants \footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
-Therefore only comparison of slopes, rather than intercepts, is meaningful.}, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for panels $(c)$ and $(e)$ and Theorem \ref{thm: inverse_mixing_time_lower_bound} for panels $(d)$ and $(f)$.
+Therefore only comparison of slopes, rather than intercepts, is meaningful.}, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for panels $(c)$ and $(e)$ and Theorem \ref{thm: mixing_time_upper_bound} for panels $(d)$ and $(f)$.
 The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in panels $(c)$ and $(e)$, and $m = 20$ for the mixing time, dashed lines in panel $(d)$ and $(f)$).
@@
 Panels $(d)$ and $(f)$ show the solid lines tracking closely to the dashed lines, in both 2 and 3 dimensions.
-This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: inverse_mixing_time_lower_bound} has the right dependency on both thickness parameter  $\sigma$ and diameter $D$.
-
-\textcolor{red}{The story in panels $(c)$ and $(e)$ is more subtle.
-We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results is mostly due to the relationship when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$.
+This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both thickness parameter  $\sigma$ and diameter $D$.
+
+The story in panels $(c)$ and $(e)$ is less obvious.
+We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$.
 It is in these regions that the slopes of the dashed and solid lines appear most distinct.
-As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves converging towards those predicted by theory.
-The takeaway message is that while the dependency in \eqref{eqn: conductance_additive_error_bound} on $\sigma$ and $D$ is loose for clusters with diameter close to thickness, it becomes tighter and tigher as $D/\sigma$ grows.}
+As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
+The takeaway message is that while the dependency in \eqref{eqn: conductance_additive_error_bound} on $\sigma$ and $D$ is loose for clusters with diameter close to thickness, it becomes tighter as $D/\sigma$ grows.
 
@@
 
-To drive home the main implications of Theorem \ref{thm: ppr_cluster}, we show the behavior of \pprspace, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
+To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
 To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
@@
 for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \textcolor{red}{Bressson et al.
-2012}; and the last column shows a cut of the cluster tree estimator of \textcolor{red}{Chaudhuri Dasgupta}
+The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the cluster tree estimator of \cite{chaudhuri2010}.
 
@@
 In the third row, the moons have such low saliency that even the normalized cut fails to recover the lower moon; we also see from $(k)$ that \pprspace does not somehow save us in this situation.
-Note that this is not a function of the finite sample: the 4th column shows us that the Chaudhuri Dasgupta cluster tree estimator can be recover the true density cluster.
+Note that this is not a function of the finite sample: the 4th column shows us that a well-designed density clustering algorithm can recover the true density cluster.
 
@@
 The gray dots in $(m)$ (as in $(a), (e)$ and $(i)$ are observations in low-density regions.
-While the \pprspace sweep cut $(n)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C_n$ in the sense of Definition \textcolor{red}{1}.
+While the \pprspace sweep cut $(n)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C_n$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 

### 2019-05-10 arxiv/arxiv_local_density_clustering_proofs.tex
updated mixing time proof and section, edited other sections

@@
 \newcommand{\set}[1]{\left\{#1\right\}}
+\newcommand{\seq}[1]{\left\{#1\right\}_{n \in \mathbb{N}}}
 \newcommand{\defeq}{\overset{\mathrm{def}}{=}}
@@
 \newcommand{\degmax}{\deg_{\max}}
-\newcommand{\piminwt}{\widetilde{\pibf}_{\min}}
+\newcommand{\piminwt}{\widetilde{\pi}_{\min}}
 \newcommand{\piminpr}{\pibf_{\min}'}
@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\dx}{\,dx}
+\newcommand{\dy}{\,dy}
+\newcommand{\dt}{\,dt}
 
@@
 \newcommand{\wDbf}{\widetilde{\Dbf}}
+\newcommand{\piwt}{\widetilde{\pi}}
 
@@
 {6pt} % Space below
-{\itshape} % Body font
+{\itshape} % Bo\dy font
 {} % Indent amount
@@
 \newtheorem{definition}{Definition}
+\newtheorem{proposition}{Proposition}
 
@@
 	\begin{align*}
-	(1 + x)^d & \leq 1 + 2dx \\
-	(1 - x)^d & \geq 1 - 2dx.
+	(1 + x)^d & \leq 1 + 2\dx \\
+	(1 - x)^d & \geq 1 - 2\dx.
 	\end{align*}
@@
 	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
-	& = 1 + dx + dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
-	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
-	& \leq 1 + dx + dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2dx.
+	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
 	\end{align*}
@@
 	\label{eqn: partition_ub}
-	\Pbb(\Csigr) = \int_{\Csigr} f(x) dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
+	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
 	\end{equation}
@@
 
-Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{local conductance} $\ell_{\nu,r}(u)$ to be
-\begin{equation*}
-\ell_{\nu,r}(u) = \frac{\nu\left(\Csig \cap B(u,r)\right)}{\nu\left(B(u,r)\right)}.
+Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
+\begin{equation*}
+\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr)
 \end{equation*}
@@
 	\begin{equation*}
-	\ell_{\nu,r}(u) \geq \frac{6}{25}. 
+	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
 	\end{equation*}
@@
 	\begin{equation*}
-	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr).
+	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr)
 	\end{equation*}
@@
 	\begin{align*}
-	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) dx \\
-	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) dx \\
-	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
+	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
 	\end{align*}
@@
 	\begin{align*}
-	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) dx \\
-	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) dx
+	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
 	\end{align*}
@@
 
-For $N \in \mathbb{N}$ and a set $V$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf = (\pi_u)_{u \in V}$ where $\pi_v = \frac{\Dbf_{vv}}{\vol(V; G)}$.
-For $v \in V$,
-\begin{equation}
-\label{eqn: random_walk}
-q_{vu}^{(m)} = e_v\Wbf^m e_u, ~~ \qbf_{v}^{(m)} = \left(q_{vu}^{(m)}\right)_{u \in V}, ~~ \qbf_v = (\qbf^{(1)}_{v\cdot},\qbf^{(2)}_{v\cdot}, \ldots), 
-\end{equation}
-denote respectively the $m$-step transition probability, distribution, and sequence distributions of the random walk over $G$ originating at $v$.
-Letting $\qbf = (\qbf_v)_{v \in V}$, the relative pointwise mixing time is thus
-\begin{equation*}
-\tau_{\infty}(\qbf; G) := \tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
-\end{equation*}
-where we include the extra dependency on $\qbf$ as we will need to consider mixing of various random walks.
-
-Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined to be
-\begin{equation*}
-s(G) := \frac{9D_{\min}}{10}\pi_{\min} 
-\end{equation*}
-for $D_{\min} := \min_{v \in V} \Dbf_{vv}$ and $\pi_{\min} := D_{\min} / \vol(V; G)$.
-
-%\inf \set{t: \forall S \subset V ~\text{with}~ \pi(S) = t, \beta(S) \leq 1/10}
-%\end{equation*}
-where $\beta(S) := \inf_{v \in S} \qbf_{v}^{(1)}(S^c)$, and by convention we let $\pbf(S) = \sum_{u \in S} p_u$ for any distribution vector $\pbf = (p_u)_{u \in V}$ over $V$.
-We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
-\begin{lemma}
+For $N \in \mathbb{N}$ and a collection $V = \set{v_1,\ldots,v_N}$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, degree matrix $\Dbf$, and random walk matrix $\Wbf$.
+We consider the stationary distribution $\pi$ to be a mapping from $V$ to $[0,1]$, with $\pi(u) := \frac{\Dbf_{uu}}{\vol(V; G)}$ for $u \in V$.
+For $v \in V$, let $q: V \times V \to [0,1]$ represent the $m$-step transition probability of the random walk over $G$ originating from $v$, $q^{(m)}(v,u) = e_v\Wbf^m e_u$.
+The relative pointwise mixing time over $G$ is then
+\begin{equation*}
+\tau_{\infty}(G) = \min\set{m: \forall u,v \in V, \frac{\abs{q^{(m)}(v,u) - \pi(u)}}{\pi(u)} \leq 1/4}. 
+\end{equation*}
+
+Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined as
+\begin{equation*}
+s(G) := \frac{9}{10} \cdot \min_{v \in V} \set{\deg(v; G)} \cdot \min_{v \in V} \set{\pi(v)}
+\end{equation*}
+For $f: V \to \Reals$, and $S \subseteq V$, write $f(S) := \sum_{u \in S} f(u)$. We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
+\begin{lemma}
+	~
+
 	\label{lem: local_spread_G}
 	\begin{itemize}
-		\item If $\pibf(S) \leq s(G)$, then for every $u \in S$, $\qbf_u^{(1)}(S^c) \geq 1/10$.
-		\item For any $v, u \in V$, and $m \in N$ greater than $0$, $q_{vu}^{(m)}/ \pi_{\min} \leq 1/s(G)$.
+		\item If $\pi(S) \leq s(G)$, then for every $u \in S$, $q^{(1)}(u,S^c) \geq \frac{1}{10}$.
+		\item For any $v, u \in V$, and $m \in \mathbb{N}, m \geq 0$,
+		\begin{equation*}
+		q^{(m)}(v,u) \leq \frac{\min_{v \in V} \set{\pi(v)}}{s(G)}.
+		\end{equation*}
 	\end{itemize}
@@
 \begin{proof}
-	If $t = \pibf(S) \leq \frac{9 D_{\min}}{10} \pi_{\min}$, divide both sides by $\pi_{\min}$ to obtain
-	\begin{equation*}
-	\abs{S} \leq \frac{9 D_{\min}}{10}
-	\end{equation*}
-	which implies $\qbf_{v}^{(1)}(S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.
-
-	The second statement follows from the fact $q_{vu}^{(m)} \leq 1/D_{\min}$ for any $m$.
-\end{proof}
-
-The local spread facilitates conversion between $\tau_{\infty}(\qbf_v; G)$ and the more easily manageable \emph{total variation} mixing time, given by
-\begin{equation*}
-\tau_1(\rhobf; G) = \min\biggl\{m: \forall v \in V, \norm{\rhobf_v - \pibf}_{TV} \leq 1/4 \biggr\}
-\end{equation*}
-where 
-\begin{equation}
-\label{eqn: uniform_random_walk}
-\rhobf_{v}^{(m)} = \frac{1}{m}\sum_{k = 1}^{m+1} \qbf_{v}^{m}, ~~ \rhobf_v = \left( \rhobf_{v}^{(1)}, \rhobf_{v}^{(2)}, \rhobf_{v}^{(3)} \ldots \right), ~~ \rhobf = \left( \rhobf_v \right)_{v \in V}
-\end{equation}
-and $\norm{\pbf - \pibf}_{TV} = \sum_{v \in V}\abs{p_v - \pi_v}$ is the total variation norm between distributions $\pbf$ and $\pibf$. 
+	If $\pi(S) \leq s(G)$, divide both sides by $\min_{v \in V} \set{\pi(v)}$ to obtain $\abs{S} \leq 9\min_{v \in V} \set{\deg(v; G)}/10$,
+	which implies $q^{(1)}(v,S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.
+
+	The second statement follows from the fact $q^{(m)}(v,u) \leq 1/\min_{v \in V} \set{\deg(v; G)}$ for any $m$.
+\end{proof}
+
+The local spread facilitates conversion between $\tau_{\infty}(G)$ and the more easily manageable \emph{total variation} mixing time, given by
+\begin{equation*}
+\tau_1(G) = \min\biggl\{m: \forall v \in V, \norm{\rho^{(m)}(v,\cdot) - \pi}_{TV} \leq 1/4 \biggr\}
+\end{equation*}
+where $\rho^{(m)}(u,v) = \sum_{l = 1}^{m} p^{(l)}(u,v)$ 
+and $\norm{\rho(v,\cdot) - \pi}_{TV} = \sum_{u \in V}\abs{\rho(u,v) - \pi(v)}$ is the total variation norm between distributions $\rho(v,\cdot)$ and $\pi$. 
 \begin{lemma}
 	\label{lem: tv_mixing_to_pointwise_mixing1}
-	For $\qbf$ as in \eqref{eqn: random_walk} and $\rhobf$ as in \eqref{eqn: uniform_random_walk},
-	\begin{equation*}
-	\tau_{\infty}(\qbf; G) \leq 2752 \tau_1(\rhobf; G) \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\}\right)
+	\begin{equation*}
+	\tau_{\infty}(G) \leq 2752 \cdot \tau_1(G) \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\}\right)
 	\end{equation*}
@@
 	\begin{equation*}
-	\Delta_u^{(m)} = q_{vu}^{(m)} - \pi_u, ~~ \delta_u^{(m)} = \frac{\Delta_u^{(m)}}{\pi_u}
-	\end{equation*}
-	and $\Deltabf^{(m)} = (\Delta_u^{(m)})_{u \in V}$, $\deltabf^{(m)} = (\delta_u^{(m)})_{u \in V}$. For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pibf)$ norm is given by
-	\begin{equation*}
-	\norm{\Deltabf}_{L^p(\pibf)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi_u \right)^{1/p}
-	\end{equation*}
-	To go between the $L^{\infty}(\pibf)$ and $L^{1}(\pibf)$ norms, we have
-	\begin{align*}
-	\norm{\deltabf^{(2m)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(m)}}^2_{L^{2}(\pi)} \\
-	& = \norm{(\deltabf^{(m)})^2}_{L^{1}(\pi)} \\
-	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}
-	\end{align*}
-	where $(i)$ is a result of \cite{benjamini2003} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
-	\begin{align*}
-	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q_{vu}^{(m)}}{\pi_u} \right\} \\
-	& \overset{(iii)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\}
-	\end{align*}
-	where $(iii)$ follows from Lemma \ref{lem: local_spread_G}.
-
-	Now, we leverage the following well-known fact \cite{montenegro2002}: for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
-	\begin{equation*}
-	\norm{\qbf_v^{(m)} - \pibf}_{TV} \leq \epsilon.
-	\end{equation*}
-	But $\norm{\qbf_v^{(m)} - \pibf}_{TV}$ is exactly $\norm{(\deltabf^{(m)})}_{L^{1}(\pi)}$. Therefore, picking 
-	\begin{equation*}
-	m_0 = \tau_1(\qbf_v^{(m)}; G) \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
-	\end{equation*} implies $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_0$.  Then, 
-	\begin{equation*}
-	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u}\left\{ \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \right\}.
-	\end{equation*}
-	and since none of the above depended on a specific choice for $v$, the supremum can be taken over all starting vertices $v$ as well. Thus $\tau_{\infty}(\qbf^{(m)}; G) \leq 2m_0$.
-
-	Finally, it is known \cite{montenegro2002} that
-	\begin{equation*}
-	\tau_{1}(\qbf^{(m)}; G) \leq 1376 \tau_{1}(\rhobf^{(m)}; G)
-	\end{equation*}
-	and so the desired result holds.	
-\end{proof}
-
-The second key quantity is the \emph{conductance function}
+	\Delta^{(m)}(u) = q^{(m)}(v,u) - \pi(u), ~~ \delta^{(m)}(u) = \frac{\Delta^{(m)}(u)}{\pi(u)}
+	\end{equation*}
+	and denote $\Deltabf^{(m)} = \bigl(\Delta^{(m)}(u)\bigr)_{u \in V}$, $\deltabf^{(m)} = \bigl(\delta^{(m)}(u)\bigr)_{u \in V}$.
+For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pi)$ norm is given by
+	\begin{equation*}
+	\norm{\Deltabf}_{L^p(\pi)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi(u) \right)^{1/p}
+	\end{equation*}
+	To go between the $L^{\infty}(\pi)$ and $L^{1}(\pi)$ norms, we capitalize on a clever argument developed in \cite{morris2005}. For any $v,u \in V$, by the time-reversibility of the graph random walk,
+	\begin{align}
+	\abs{\frac{q^{(2m)}(v,u) - \pi(u)}{\pi(u)}} & = \abs{\sum_{y \in V} \pi(y) \left( \frac{q^{(m)}(v,y) - \pi(y)}{\pi(y)}\right)\left(\frac{q^{(m)}(u,y) - \pi(y)}{\pi(y)} \right)} \nonumber \\
+	& \leq \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}, \label{eqn: infty_norm_to_one_norm}
+	\end{align}
+	with the second line following by Holder's inequality.
+
+	Now, we upper bound the second factor on the right hand side by observing
+	\begin{align}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q^{(m)}(v,u)}{\pi(u)} \right\} \nonumber \\
+	& \overset{(i)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\} \label{eqn: ub_infinity_norm}
+	\end{align}
+	where $(i)$ follows from Lemma \ref{lem: local_spread_G}.
+
+	Set $m_0 = 1376 \tau_1(G) $, which we will show implies $\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4}$.
+Now, we leverage the following well-known fact (see pg.
+1 of \cite{montenegro2002}): for any $\epsilon > 0$, if $m \geq m_0 \cdot \log(1/\epsilon)$ then for any $v \in V$,
+	\begin{equation}
+	\label{eqn: rapid_mixing}
+	\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \epsilon.
+	\end{equation}
+	But $\norm{q^{(m)}(v,\cdot) - \pi}_{TV}$ is exactly $\norm{\deltabf^{(m)}}_{L^{1}(\pi)}$. Letting
+	\begin{equation*}
+	m_1 = m_0 \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
+	\end{equation*} 
+	by \eqref{eqn: infty_norm_to_one_norm}, \eqref{eqn: ub_infinity_norm}, and \eqref{eqn: rapid_mixing}, $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_1$.  Recall that
+	\begin{equation*}
+	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u \in V}\left\{ \frac{\abs{q^{(m)}(v,u) - \pi(u)}}{\pi(u)} \right\}.
+	\end{equation*}
+	and since none of the above depended on a specific choice of $v$, the supremum can be taken over all starting vertices $v$ as well.
+Thus for all $m \geq 2m_1$, for any $v,u \in V$, $\abs{q^{m}(v,u) - \pi(u)} \leq \frac{\pi(u)}{4}$.
+
+	Finally, it is known (pg.15 of \citep{montenegro2002}) that
+	\begin{equation*}
+	\norm{\rho^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4} \Longrightarrow  \norm{q^{(1376m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4} 
+	\end{equation*}
+	and so $m_0 = 1376 \tau_1(G)$ implies $\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4}$, completing the proof.
+\end{proof}
+
+The second key quantity is the \emph{conductance function}. For $\min_{u \in V}\set{\pi(u)} \leq t \leq 1/2$, the conductance function is defined as
 \begin{equation}
 \label{eqn: conductance_function}
-\Phi(t; G) := \min_{\substack{S \subseteq V, \\ \pibf(S) \leq t} } \Phi(S; G) ~~~~~~~ (\pi_{\min} \leq t < 1)
-\end{equation}
-where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}.
+\Phi(t; G) := \min_{\substack{S \subseteq V, \\ 0 < \pibf(S) \leq t} } \Phi(S; G)
+\end{equation}
+where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}, and in the minimization $S$ may not be the empty set.
 
@@
 
-\subsection{Conductance function and local spread: non-convex case.}
-\label{sec: non_convex_conductance_function_and_local_spread}
-
-We begin with some notation.
-Write $\Csig[\Xbf] = \wX$, and $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$.
-For $S \subset \wX$, let $\widetilde{\cut}_{n,r}(S) = \cut(S;\widetilde{G}_{n,r})$ and similarly $\widetilde{\vol}_{n,r}(S) = \vol(S;\widetilde{G}_{n,r})$.
-
-Consider $\zbf \subset \Csig$ such that  $\mathcal{N}_{\zbf} = \set{B(z,r/3): z \in \zbf}$ is an internal covering of $\Csig$, meaning $\mathcal{N}_{\zbf} \supseteq \Csig$. Then, we write
-\begin{align*}
-\widetilde{B}_{\min} = \min_{z \in \zbf} \abs{B(z,r/3) \cap \wX}, ~~
-\widetilde{D}_{\min} = \min_{\wx \in \wX} \abs{\widetilde{\cut}_{n,r}(x)} \\ \widetilde{B}_{\max} = \min_{z \in \zbf} \abs{B(z,r/3) \cap \wX}, ~~
-\widetilde{D}_{\max} = \min_{\wx \in \wX} \abs{\widetilde{\cut}_{n,r}(x)}
-\end{align*}
-Both the conductance function and local spread will depend heavily on these quantities. Lemma \ref{lem: ball_bounds} collects the bounds we will need.
-\begin{lemma}
-	\label{lem: ball_bounds}
-	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.	For sufficiently large $n$, and $r \leq \sigma/4d$, each of the following bounds hold with probability $1 - \delta$:
+\subsection{Population-level conductance profile.}
+\label{sec: population_conductance_function}
+
+We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability given by 
+\begin{equation*}
+\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
+\end{equation*}
+where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
+
+Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
+\begin{equation*}
+\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\end{equation*}
+Letting the \emph{$\Pbb$-local conductance} be given by
+\begin{equation*}
+\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr) \tag{$x \in \Csig$}
+\end{equation*}
+a bit of algebra verifies that
+\begin{equation*}
+\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\end{equation*}
+
+We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
+\begin{equation*}
+\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
+\end{equation*}
+the \emph{$\Pbb$-(continuous) normalized cut} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\end{equation*}
+and the \emph{$\Pbb$-(continuous) conductance profile} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \piwt_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
+\end{equation*}
+where $\Sset^c = \Csig \setminus \Sset$.
+
+\begin{proposition}
+	\label{prop: nonuniform_continuous_conductance}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the continuous conductance function of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\Pbb,r}(t) > \frac{\lambda_{\sigma}^2 r}{2^{12} \Lambda_{\sigma}^2 D L \sqrt{d}}.
+	\end{equation*}
+	for any $0 < t \leq \frac{1}{2}$. 
+\end{proposition}
+
+Similar results are already known (see e.g.
+\cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
+We first prove an analogous result for the special case of $f \equiv 1$ everywhere on $\Csig$.
+For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let
+\begin{equation*}
+\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) d\pi_{\nu,r}(x).
+\end{equation*}
+The uniform continuous normalized cut and conductance profile are then defined analogously to the weighted case,
+\begin{equation*}
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\nu,r}(\Sset) \leq t} } \widetilde{\Phi}_{\nu,r}(\Sset).
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: uniform_continuous_conductance}
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance function of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\nu,r}(t) > \frac{r}{2^{12} D L \sqrt{d}}.
+	\end{equation*}
+	for any $0 < t \leq 1/2$.
+\end{lemma}
+
+Most of the technical work needed to show Proposition \ref{prop: nonuniform_continuous_conductance} involves proving Lemma \ref{lem: uniform_continuous_conductance}.
+We defer this work to the next subsection, and first show that Proposition \ref{prop: nonuniform_continuous_conductance} is a simple consequence of Lemma \ref{lem: uniform_continuous_conductance} along with \ref{asmp: bounded_density}.
+
+\paragraph{Proof of Proposition \ref{prop: nonuniform_continuous_conductance}.}
+
+Assume Lemma \ref{lem: uniform_continuous_conductance} holds. Since $t \leq 1/2$, for any Borel $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq t$,
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)}
+\end{equation*}
+By \ref{asmp: bounded_density} we obtain
+\begin{align*}
+\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(S \cap B(x,r)) f(x) \dx}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) f(x) \dx} \\
+& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(S \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
+& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \widetilde{\Phi}_{\nu,r}(\Sset)
+\end{align*}
+Noting that $\widetilde{\Phi}_{\nu,r}(\Sset) = \widetilde{\Phi}_{\nu,r}(\Sset^c)$, and as $0 < \piwt_{\Pbb,r}(\Sset) < 1/2$, one of $0 < \pi_{\nu,r}(\Sset) \leq 1/2$ or $0 < \pi_{\nu,r}(\Sset^c) \leq 1/2$ must hold, the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
+
+\subsection{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
+
+As is standard, the proof of a lower bound on the conductance profile relies on an isoperimetric inequality.
+
+\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
+	\label{lem: nonconvex_isoperimetry}
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
+	\begin{equation*}
+	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{L D_{K}} \min(\nu(\Omega_1), \nu(\Omega_2))
+	\end{equation*}
+\end{lemma}
+The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even in the convex setting, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among others.
+Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting implied  Assumption \ref{asmp: embedding} is not difficult.
+
+\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
+	For $\Omega_i, i = 1,2,3$, denote the preimage
+	\begin{equation*}
+	R_i = \set{x \in K: g(x) \in \Omega_i}
+	\end{equation*}
+	For any $x \in R_1, y \in R_2$, 
+	\begin{equation*}
+	\abs{x - y} \geq \frac{1}{L}\abs{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
+	\end{equation*}
+	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
+	\begin{equation*}
+	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
+	\end{equation*}
+	By Theorem 2.2 of \cite{lovasz1990},
+	\begin{align*}
+	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{D} \min \{\nu(R_1), \nu(R_2)\} \\
+	& \geq \frac{2}{D L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
+	\end{align*}
+	and by the measure-preserving property of $g$, this implies
+	\begin{equation*}
+	\nu(\Omega_3) \geq\frac{2}{D L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
+	\end{equation*}
+\end{proof}
+
+We will also need an upper bound on the distance between transition probability densities $\widetilde{P}_{\nu,r}(u,\cdot)$ and $\widetilde{P}_{\nu,r}(v,\cdot)$ for $u,v \in \Csig$ close together. 
+\begin{lemma}[One-step distributions]
+	\label{lem: one_step_distributions}
+	Let $u,v \in \Csig$ be such that 
+	\begin{equation*}
+	\norm{u - v} \leq \frac{r t}{\sqrt{d}}
+	\end{equation*}
+	for some $0 < t < 1/8$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
+	\begin{equation*}
+	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
+	\end{equation*}
+	where $\norm{P - Q}_{TV}$ is the total variation distance between probabilities $P$ and $Q$. 
+\end{lemma}
+
+The key result needed to show Lemma \ref{lem: one_step_distributions} is regarding the volume of the overlap $B(u,r) \cap B(v,r)$.
+
+\begin{lemma}
+	\label{lem: overlap_balls_1}
+	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{\sqrt{d}}$ for some $0 < t < 1/8$. Then,
+	\begin{equation*}
+	\nu(B(u,r) \cap B(v,r)) \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We will treat only the case where $\norm{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
+Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ is comprised of the union of two disjoint spherical caps, and thus
+	\begin{equation*}
+	\nu(I) = 2\nu(\mathrm{Cap}_r(r(1 - \frac{t}{2 \sqrt{d}}))).
+	\end{equation*}
+	From Lemma \ref{lem: volume_of_spherical_cap} we therefore obtain
+	\begin{equation*}
+	\nu(I) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	\end{equation*}
+	where
+	\begin{equation*}
+	\alpha = 1 - \frac{2r^2(1 - \frac{t}{2 \sqrt{d}}) - r^2(1 - \frac{t}{2 \sqrt{d}})^2}{r^2} = \frac{t^2}{4d}.
+	\end{equation*}
+	Expanding the incomplete beta function in integral form, we therefore have
+	\begin{align*}
+	\nu(I) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
+	& \overset{(i)}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
+	& \overset{(ii)}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
+	\end{align*}
+	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we can validly apply since $\alpha \leq \frac{t^2}{2d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem: one_step_distributions}]
+	Let $S_1 \cup S_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
+	\begin{equation*}
+	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
+	\end{equation*}
+	Since this will hold for arbitrary $S_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $S_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.
+
+	Now, note that
+	\begin{align*}
+	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) & = 1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1)
+	\end{align*}
+	Let $I := B(u,r) \cap B(v,r)$. Then we have
+	\begin{equation*}
+	\widetilde{P}_{\nu,r}(u; S_2) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap I)
+	\end{equation*}
+	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; S_1)$. As a result,
+	\begin{equation}
+	1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
+	\end{equation}
+	As \eqref{eqn: one_step_1} demonstrates, the overlap of the one-step distributions is related to the volume of the intersection between $B(u,r)$ and $B(v,r)$ within $\Csig$.
+
+	From here, some simple manipulations yield
 	\begin{align}
-	\label{eqn: ball_bounds}
-	\widetilde{B}_{\max} & \leq \left(1 + \sqrt{3^d\frac{3(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma} \nonumber \\
-	\widetilde{B}_{\min} & \geq \left(1 - \sqrt{3^d\frac{2(\log \abs{\mathcal{N}_{\zbf}} + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \nonumber \\
-	\widetilde{D}_{\max} & \leq \left(1 + \sqrt{\frac{3(\log n + \log(1/\delta))}{n \nu_d r^d \Lambda_{\sigma}}}\right) n \nu_d r^d \Lambda_{\sigma} \nonumber \\
-	\widetilde{D}_{\min} & \geq \left(1 - \sqrt{\frac{2(\log n + \log(1/\delta))}{n \nu_d r^d \lambda_{\sigma} \beta_d}}\right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_d \nonumber \\
-	\left(1 - \sqrt{\frac{2 \log(1/\delta)}{n \lambda_d \nu_d \sigma^d}}\right) n \lambda_{\sigma} \nu_d \sigma^d & \leq \widetilde{n} \leq \left(1 + \sqrt{\frac{3 \log(1/\delta)}{n \Lambda_{\sigma} \nu_d D^d}}\right) n \Lambda_d \nu_d D^d
+	\nu(\Csig \cap I)  & = \nu(I) - \nu(I \setminus \Csig) \nonumber \\
+	& \geq \nu(I) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
+	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
 	\end{align}
-	where $\wn = \abs{\wX}$ and $\beta_d \geq 1/2^d$.
-
-	In particular, fix $\epsilon > 0$. Then, for $n$ as specified in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, the following event:
+	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
+\end{proof}
+
+\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
+	Let $S_1 \cup S_2 = \Csig$, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
+\begin{equation*}
+\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{24 D L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
+\end{equation*}
+Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$. Then, dividing both sides by $\pi_{\nu,r}(S_1)$ yields the desired result.
+
+Now, consider the sets
+\begin{align*}
+S_1' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}} \\
+S_2' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}}
+\end{align*}
+and $S_3' = \Csig \setminus S_1' \setminus S_2'$.
+
+Suppose $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$. Then,
+\begin{equation*}
+\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(S_1)}{8}
+\end{equation*}
+Similarly, if $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$, then since
+\begin{equation*}
+\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) = \int_{S_2} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x)
+\end{equation*}
+a symmetric result holds.
+
+So we can assume $\pi_{\nu,r}(S_1') \geq \pi_{\nu,r}(S_1)/2$, and likewise for $S_2$. Now, for every $u \in S_1', v \in S_2'$, we have that
+\begin{equation*}
+\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;S_1) - \widetilde{P}_{\nu,r}(v;S_2) > 1 - \frac{\ell}{2}.
+\end{equation*}
+
+By Lemma \ref{lem: one_step_distributions}, we therefore have
+\begin{equation*}
+\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{3\sqrt{3 d}}.
+\end{equation*}
+and since $u \in S_1', v \in S_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(S_1', S_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
+\begin{equation*}
+\vol(S_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{3 D L \sqrt{3 d}} \min \set{\vol(S_1'), \vol(S_2')}
+\end{equation*}
+We now prove the desired result:
+\begin{align*}
+\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) & = \frac{1}{2} \bigl(\int_{S_2} \widetilde{P}_{\nu,r}(x; S_2)  d \pi_{\nu,r}(x) \bigr) \\
+& \geq \frac{\ell}{8} \pi_{\nu,r}(S_3') \\
+& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(S_3') \\
+& \geq \frac{\sqrt{2} r \ell^3}{12 D L \sqrt{d} \nu(\Csig)} \min \set{\nu(S_1'), \nu(S_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{12 D L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1'), \pi_{\nu,r}(S_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{24 D L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}.
+\end{align*}
+
+\subsection{Graph conductance profile and local spread.}
+
+Let $\widetilde{G}_{n,r} := G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denote the subgraph induced by $\Csig[\Xbf]$.$\widetilde{{\Phi}}_{n,r}(t)$, the graph conductance profile over $\widetilde{G}_{n,r}$ is defined in \eqref{eqn: graph_conductance_profile}.
+Write $\piminwt := \min_{u \in \Csig[\Xbf]} \piwt_{n,r}(u)$.
+
+\begin{proposition}[Lower bound on graph conductance profile]
+	\label{prop: graph_conductance_profile_lb}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, with probability one the following lower bound holds on the graph conductance function:
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}} \tag{$0 < t \leq \frac{1}{2}$}
+	\end{equation*}
+\end{proposition}
+
+In order to prove Proposition \ref{prop: graph_conductance_profile_lb}, we will need to split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
+For any graph $G = (V,E)$, let $\mathcal{L}(G) = \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G$.)
+
+In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut of all sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
+
+\begin{lemma}
+	\label{lem: graph_conductance_profile_lb}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$ Then with probability one,
+	\begin{equation*}
+	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
+	\end{equation*}
+	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
+\end{lemma}
+
+The proof of Lemma \ref{lem: graph_conductance_profile_lb} is nontrivial, and we devote the following subsection to it.
+
+Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
+\begin{lemma}
+	\label{lem: graph_conductance_profile_lb_1}
+	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
+	\begin{equation*}
+	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Observing that
+	\begin{equation*}
+	\Phi(S;G) \geq \sum_{u \in S} q^{(1)}(u,S^c) \frac{\deg(u;G)}{\vol(S)},
+	\end{equation*}
+	the claim follows by Lemma \ref{lem: local_spread_G}.
+\end{proof}
+
+Proposition \ref{prop: graph_conductance_profile_lb} follows in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}} < \frac{1}{10}$.
+
+\begin{lemma}
+	\label{lem: local_spread_lb}
+	With probability one, the following bound holds:
+	\begin{equation*}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$ Therefore by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
+	\begin{equation*}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
+	\end{equation*}
+\end{proof}
+
+\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+
+Let $\mathfrak{B}(\Csig)$ be the Borel $\sigma$-algebra of $\Csig$, and define the conditional probability measures
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\end{equation*} 
+A Borel map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
+\begin{equation*}
+\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
+\end{equation*}
+where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
+
+If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
+Proposition 5 of \cite{garciatrillos16} establishes that, for open connected domains with Lipschitz boundaries, such stagnating transportation maps exist.
+In particular, as $\Csig[\Xbf]$ consists of $\widetilde{n} = \abs{\Csig[\Xbf]}$ points sampled independently from $\widetilde{\Pbb}$, and $\Csig$ is a connected domain with Lipschitz boundary, the following implication is immediate.
+
+\begin{lemma}
+	\label{lem: stagnating_transportation_maps}
+	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
+	\begin{equation}
+	\label{eqn: stagnating_transportation_maps}
+	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
+	\end{equation}
+	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
+\end{lemma}
+
+%%% AJG 5/9/19: Need to strengthen this?
+
+Note that although $\Csig$ is closed not open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to $\Csig^o$, and \eqref{eqn: stagnating_transportation_maps} will hold for arbitrary extension of $T_n$ to $\Csig$.
+
+\paragraph{Graph cuts to continuous cuts.}
+
+We use stagnating transportation maps to relate the discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
+We fix some notation, letting $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$ for a transportation map $T_n$.
+
+Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
+
+\begin{lemma}
+	\label{lem: volume_bound}
+	Let $S \subseteq \Csig[\Xbf]$ and $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset := T_n^{-1}(S)$,
+	\begin{equation*}
+	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$, meaning
+	\begin{equation*}
+	\varphi(x) = 
+	\begin{cases}
+	1,~ x \in S \\
+	0,~ \text{otherwise}
+	\end{cases}
+	\end{equation*}
+
+	Now, we proceed
 	\begin{align}
-	\label{eqn: ball_bounds_epsilon}
-	\widetilde{B}_{\max} \leq \left(1 + \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \Lambda_{\sigma},& ~~ \widetilde{D}_{\max} \leq \left(1 + \epsilon \right) n \nu_d r^d \Lambda_{\sigma} \nonumber \\
-	\widetilde{B}_{\min} \geq \left(1 - \epsilon \right) n \nu_d \left(\frac{r}{3}\right)^d \lambda_{\sigma} \beta_{d},& ~~ \widetilde{D}_{\min} \geq \left(1 - \epsilon \right) n \nu_d r^d \lambda_{\sigma} \beta_{d} \nonumber \\
-	(1 - \epsilon) n \lambda_{\sigma} \nu_d \sigma^d & \leq \widetilde{n} \leq (1 + \epsilon) n \Lambda_{\sigma} \nu_d D^d 
+	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
+	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
+	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
+	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
+	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
 	\end{align}
-	occurs with probability at least $1 - \delta$.
-\end{lemma}
-\begin{proof}
-	We observe that for any $s \leq \sigma/4d$ and any $x \in \Csig$,
-	\begin{equation*}
-	\nu(B(x,s) \cap \Csig) \geq \left(\frac{s}{2}\right)^d = s^d \beta_d.
-	\end{equation*}
-	(In fact, tighter bounds can be shown to hold, but we will not need them). Therefore, by \ref{asmp: bounded_density}:
-	\begin{equation*}
-	\lambda_{\sigma} \nu_d s^d \beta_d \leq \Pbb\left(B(z,s) \cap \Csig \right) \leq \Lambda_{\sigma} \nu_d s^d \\
-	\end{equation*}
-	In particular, this holds for $s = r$ and $s = r/3$, and for every $z \in \zbf$ as well as every $z \in \widetilde{\Xbf}$.
-Now, by \ref{asmp: cluster_diameter} and \ref{asmp: bounded_density} we also have
-	\begin{equation*}
-	\Lambda_{\sigma} \nu_d \sigma^d \leq \Pbb(\Csig) \leq \Lambda_{\sigma} \nu_d D^d
-	\end{equation*}
-
-	The proof of each statement in \eqref{eqn: ball_bounds} then follows from application of Lemma \ref{lem: multiplicative_Hoeffding}.
-
-	To show \eqref{eqn: ball_bounds_epsilon}, we note that $\abs{\mathcal{N}_z}$ is less than the covering number of the $D$-ball in $d$ dimensions. Therefore
-	\begin{equation*}
-	\abs{\mathcal{N}_z} \leq \left(\frac{6D}{r} + 1\right)^d.
-	\end{equation*}
-	It is then immediately apparent that $n$ chosen as in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} yields \eqref{eqn: ball_bounds_epsilon}.
-\end{proof}
-
-Now, we consider the conductance function and local spread computed over $\widetilde{G}_{n,r}$, which we refer to by
-\begin{equation*}
-\widetilde{\Phi}_{n,r}(t) = \Phi(t; \widetilde{G}_{n,r}), ~~ \widetilde{s}_{n,r} = s(\widetilde{G}_{n,r}).
-\end{equation*}
-where the restriction in the minimization problem of \eqref{eqn: conductance_function} is with respect to $\widetilde{\pi}_{n,r}$ the stationary distribution over $\widetilde{G}_{n,r}$.
-
-We will bound $\widetilde{\Phi}_{n,r}(1/2)$ and $\widetilde{s}_{n,r}$ under the event that \eqref{eqn: ball_bounds_epsilon} holds, noting that this occurs with probability at least $1 - \delta$.
-
-\begin{lemma}
-	\label{lem: local_spread_lower_bound}
-	If the bounds given by \eqref{eqn: ball_bounds_epsilon} hold, then
-	\begin{equation*}
-	\widetilde{s}_{n,r} \geq \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2
-	\end{equation*}
-\end{lemma}
-
-\begin{proof}
-	The local spread can be written as
-	\begin{equation*}
-	\widetilde{s}_{n,r} = \frac{9}{10} \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \geq  \frac{9}{10} \frac{\widetilde{D}_{\min}^2}{\widetilde{D}_{\max} \wn}.
-	\end{equation*}
-	Then apply the relevant results of Lemma \ref{lem: ball_bounds}.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: non_convex_conductance_lower_bound}
-	If the bounds given by \eqref{eqn: ball_bounds_epsilon} hold, then:
-	\begin{equation*}
-	\widetilde{\Phi}_{n,r}(1/2) \geq \frac{\lambda_{\sigma}(1 - \epsilon)\beta_d}{4\Lambda_{\sigma}(1 + \epsilon)3^d} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)
-	\end{equation*}
-\end{lemma}
-
-\begin{proof}
-	Fix $S \subset \wX$ with $\widetilde{\pi}_{n,r}(S) \leq 1/2$. Partition $\mathcal{N}_{\zbf} = \mathcal{N}_{\zbf}^+ \cup \mathcal{N}_{\zbf}^-$, where
-	\begin{align*}
-	\mathcal{N}_{\zbf}^- & = \set{B(z,r/3): 2 \Bigl\vert B(z,r/3) \cap S\Bigr\vert \leq \abs{B(z,r/3) \cap \wX} } \\
-	\mathcal{N}_{\zbf}^+ & = \mathcal{N}_{\zbf} \setminus \mathcal{N}_{\zbf}^-
-	\end{align*}
-	and correspondingly $S^- = \mathcal{N}_{\zbf}^- \cap S$, $S^+ = \mathcal{N}_{\zbf}^+ \cap S$, so
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} = \frac{\widetilde{\cut}_{n,r}(S^-; \widetilde{G}_{n,r} \setminus S) + \widetilde{\cut}_{n,r}(S^+; \widetilde{G}_{n,r} \setminus S)}{\widetilde{\vol}_{n,r}(S^-) + \widetilde{\vol}_{n,r}(S^+)}.
-	\end{equation*}
-	It is immediately apparent that the following bounds hold for all $S \subset \wX$:
-	\begin{align*}
-	\widetilde{\cut}_{n,r}(S^-; \widetilde{G}_{n,r} \setminus S) & \geq \frac{\abs{S^-} \widetilde{B}_{\min}}{2}\\
-	\widetilde{\vol}_{n,r}(S^-) & \leq \abs{S^-} \widetilde{D}_{\max} \\
-	\widetilde{\vol}_{n,r}(S^+) & \leq \widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) \1(\abs{N_{\zbf}^+} > 0 )
-	\end{align*}
-	If moreover $\abs{N_{\zbf}^+} < \abs{N_{\zbf}}$, then 
-	\begin{equation*}
-	\widetilde{\cut}_{n,r}(S^+; \widetilde{G}_{n,r} \setminus S) \geq \frac{\widetilde{B}_{\min}^2}{4} \1(\abs{N_{\zbf}^+} > 0)
-	\end{equation*}
-	follows from the fact that the graph $H_{n,r} = (\zbf, E_H)$, with ($z_i, z_j) \in E_H$ if $\norm{z_i - z_j} \leq r/3$, is connected. As a result, if $\abs{N_{\zbf}^+} < \abs{N_{\zbf}}$ we have
-	\begin{equation}
-	\label{eqn: normalized_cut_1}
-	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{ \widetilde{B}_{\min}}{4\widetilde{D}_{\max}} +  \frac{\widetilde{B}_{\min}^2}{8 \widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}
-	\end{equation}
-	using the inequality $2(A + B)/ (C + D) \geq A/C + B/D$ for $A,B,C,D$ non-negative.
-
-	If, on the other hand , $\abs{\mathcal{N}_{\zbf}^+} = \mathcal{N}_{\zbf}$, then \eqref{eqn: normalized_cut_1} holds with respect to $S^c$. Then, because $\widetilde{\pi}_{n,r}(S) \leq 1/2$, 
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \leq \frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)}
-	\end{equation*}
-	and so we get the exact statement of \eqref{eqn: normalized_cut_1}.
-Noting, as in the proof of Lemma \ref{lem: local_spread_lower_bound}, that  $\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) \leq \wn \cdot \widetilde{D}_{\max}$, the relevant results of Lemma \ref{lem: ball_bounds} yield the desired inequality.
-\end{proof}
-
-\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}}
-\label{sec: inverse_mixing_time_lower_bound_nonconvex}
-
-Throughout this proof, we will condition on the events of Lemmas \ref{lem: local_spread_lower_bound} and \ref{lem: non_convex_conductance_lower_bound},
-namely
-\begin{align*}
-\widetilde{s}_{n,r} & \geq \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2 \\
-\widetilde{\Phi}_{n,r}(1/2) & \geq \frac{\lambda_{\sigma}(1 - \epsilon)\beta_d}{4\Lambda_{\sigma}(1 + \epsilon)3^d} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)
-\end{align*}
-noting that for $n$ as chosen in Theorem \ref{thm: inverse_mixing_time_lower_bound}, this will occur with probability at least $1 - \delta$ (by Lemma \ref{lem: ball_bounds}).
-
-As a reminder, we write $\Csig[\Xbf] = \wX$, and $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$. Fix arbitrary $v \in \wX$, and let
-\begin{equation*}
-\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\wX}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{\qbf}_n^{(2)}, \ldots)
-\end{equation*}
-Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$. (As we will see, this bound will hold over all such starting vertices $v \in \wX$.)
-
-By Lemma \ref{lem: local_spread_G},
-\begin{align*}
-\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{\widetilde{s}_{n,r}}\right) \right\} \nonumber \\
-& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, d\log\left(\frac{8 D (1 + \epsilon)^2 \Lambda_{\sigma}^2}{r (1 - \epsilon)^2 \lambda_{\sigma}^2}\right) \right\}
-\end{align*}
-
-We now upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: expansion_to_tv_distance}, we have that
+
+	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
+	\begin{align*}
+	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
+	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) \dx \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset)
+	\end{align*}
+	which is the desired upper bound.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: cut_bound}
+	Let $S \subseteq \Csig[\Xbf]$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = T_n^{-1}(S)$,
+	\begin{equation*}
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	As in the proof of Lemma \ref{lem: volume_bound}, let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$.
+
+	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
+	\begin{align*}
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
+	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
+	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
+	\end{align*}
+	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
+	\begin{align*}
+	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r_n^-)\bigr)}{\ell_{\Pbb,r_n^-}(x)} d\piwt_{\Pbb,r}(x) \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
+	\end{align*}	
+\end{proof}
+
+\begin{lemma}
+	\label{lem: graph_to_continuous_conductance}
+	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and fix $S \subseteq \Csig[\Xbf]$. Then, letting $\Sset =T_n^{-1}(S)$,
+	\begin{equation}
+	\label{eqn: graph_to_continuous_conductance}
+	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}  \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
+	\end{equation}
+\end{lemma}
+
+\begin{proof}
+
+	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset)}.
+	\end{equation*}
+
+	Then, noting that $\Sset^c = T_n^{-1}(S^c)$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\piwt_{\Pbb,r_n^+}(\Sset^c)}
+	\end{equation*}
+	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
+	\begin{equation*}
+	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} },
+	\end{equation*}
+	and the proof is complete.
+\end{proof}
+
+\paragraph{Perturbation analysis.}
+
+If $r_n^- = r = r_n^+$, \eqref{eqn: graph_to_continuous_conductance} would simplify to $\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)$.
+We show that this conclusion is robust to asymptotically negligible perturbations of $r$.
+
+\begin{lemma}[Continuity of local conductance]
+	\label{lem: cont_local_conductance}
+	For $\seq{T_n}$ a sequence of stagnating transportation maps,
+	\begin{equation*}
+	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Letting $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
+	\begin{equation*}
+	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx + \int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx.
+	\end{equation*}
+	and therefore
+	\begin{equation*}
+	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}.
+	\end{equation*}
+	We upper bound the remainder term
+	\begin{equation*}
+	\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl((r_n^+)^d - r^d) \to 0
+	\end{equation*}
+	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	We apply a similar analysis to the denominator. By Lemma \ref{lem: local_conductance}
+	\begin{equation*}
+	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) \dy \dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d \to \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
+	\end{equation*}
+	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	Then the desired result follows from an application of Slutsky's Theorem.
+\end{proof}
+
+\begin{lemma}[Continuity of stationary distribution]
+	\label{lem: cont_stationary_dist}
+	Let $c > 0$ be a fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } = 1
+	\end{equation*}
+	uniformly over all sets $\Sset \subseteq \mathfrak{B}(\Csig)$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
+\end{lemma}
+\begin{proof}
+	It will be sufficient to show that
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} \quad \text{and}  \quad \liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset^c)} = 1,
+	\end{equation*}
+	and we will show only the former, the proof of the latter being identical.
+
+	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
+	\begin{equation*}
+	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
+	\end{equation*}
+	we may rewrite
+	\begin{equation*}
+	\frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\piwt_{\Pbb,r_n^+}(\Sset)}.
+	\end{equation*}
+
+	By the stagnating property of $T_n$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
+	\end{equation*}
+	where the convergence occurs as $n \to \infty$. On the other hand, by hyptohesis
+	\begin{equation*}
+	\limsup_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
+	\end{equation*}
+	and the result follows by Slutsky's Theorem. 
+\end{proof}
+
+\begin{lemma}[Stationary distribution lower bound]
+	\label{lem: stationary_dist_lb}
+	Let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$. Then with probability one,
+	\begin{equation*}
+	\liminf_{n \to \infty} \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \piwt_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary, writing $\Sset := T_n^{-1}(S)$.
+Letting $\mathcal{R}_n(x)$ be as in the proof of Lemma \ref{lem: cont_stationary_dist}, we have
 	\begin{align}
-\label{eqn: mixing_time_bound_on_neighborhood_graph_thm2}
-\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right) \nonumber \\
-& \leq \frac{1400}{3}\left(5 + \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt \right)
+	\widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}. \label{eqn: stationary_dist_lb_1}
 	\end{align}
-where $s_{\Pbb,r} = \frac{9}{10} \frac{(1 + \epsilon)^2}{(1 - \epsilon)^2}\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{D^d} \beta_d^2$.(Since $r$ remains constant, for sufficiently large $n$ the lower bound on $\widetilde{D}_{\min}$ of Lemma \ref{lem: ball_bounds} will be at least $10$, and therefore Lemma \ref{lem: local_spread_blocking_conductance_function} holds.)
-
-Now, we can upper bound the average conductance integral:
-\begin{align*}
-\int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt & \leq \int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(1/2)} dt \\
-& \leq 64\frac{9^d\Lambda_{\sigma}^2(1 + \epsilon)^2\beta_d^2}{\lambda_{\sigma}^2(1 - \epsilon)^2} \left(1 + \frac{(1 - \epsilon)r^d\lambda_{\sigma}}{(1 + \epsilon)D^d\Lambda_{\sigma}}\right)^{-2} \log s_{\Pbb,r}.
-\end{align*}
-
-Plugging this in to \eqref{eqn: mixing_time_bound_on_neighborhood_graph_thm2} gives the desired upper bound on $\tau_{\infty}(\widetilde{q}_n, \widetilde{G}_{n,r})$, which translates to the lower bound of \eqref{eqn: inverse_mixing_time_lower_bound}.
-
-\subsection{Population-level conductance function: convex case.}
-\label{sec: convex_population_conductance_function}
-
-When $\Cset$ is convex, we will make use of the theory developed in \ref{sec: mixing_time_on_graphs} with respect to the conductance function $\Phi(t; G_{n,r}[\Csig(\Xbf)])$.
-First, however, we introduce a population-level analogue to $\Phi(t; G_{n,r}[\Csig(\Xbf)])$ over the set $\Csig$, which we denote $\widetilde{\Phi}_{\Pbb,r}$.
-(In general, we will adopt the convention of using $\widetilde{f}$ to denote functionals computed with respect to $\Csig$.)
-
-For $\Sset \subset \Rd$
-\begin{equation*}
-\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
-\end{equation*} 
-is the weighted volume.
-
-The $r$-ball walk over $\Csig$ is a Markov chain. For $x \in \Csig$ and $\Sset, \Sset' \subset \Csig$, the transition probability is given by
-\begin{equation*}
-\widetilde{P}_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}.
-\end{equation*}
-The stationary distribution $\pi_{\Pbb,r}$ thus satisfies
-\begin{equation*}
-\int_{\Csig}  \widetilde{P}_{\Pbb, r}(x;\Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset)
-\end{equation*}
-for all $\Sset \in \Csig$. A simple calculation yields 
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \nu_\Pbb(\Csig \cap B(x,r)) ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx,
-\end{equation*}
-and therefore the ergodic flow is
-\begin{align*}
-\widetilde{Q}_{\Pbb, r}(\Sset, \Sset') & := \int_{\Sset} d\pi_{\Pbb,r}(x) P_{\Pbb, r}(x;\Sset') dx \\
-& =  \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \left(\int_{\Sset' \cap B(x,r)} f(x') dx' \right) dx
-\end{align*}
-The continuous conductance function is then
-\begin{align*}
-\widetilde{\Phi}_{\Pbb,r}(t) & := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} \\
-& = \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{\int_{\Sset} f(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' \right) dx}{\int_{\Sset} f(x) \left(\int_{\Csig \cap B(x,r)} f(x') dx' \right) dx}.
-\end{align*}
-
-For $m > 0$ and $0 < t_0 < t_1 < \ldots < t_m < 1$, denote the \emph{stepwise approximation to $g$} by $\bar{g}$, defined as
-\begin{equation}
-\label{eqn: stepwise_approximation}
-\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
-\end{equation}
-The stepwise approximation will be important to showing the consistency results of Section \ref{sec: pointwise_consistency_of_conductance_function} can be translated to a uniform bound.
-Lemma \ref{lem: stepwise_approximation} shows that the approximation will not overly degrade our estimates of the population-level conductance function.
-\begin{lemma}
-	\label{lem: stepwise_approximation}
-	\begin{itemize}
-		\item For any function $f$ monotone decreasing in $t$ on the interval $[t_0,t_m]$, $\bar{f}(t) \leq f(t)$ for all $t \in [t_0,t_m]$.
-		\item Fix
-		\begin{equation*}
-		g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [t_0, 1/2]$}
-		\end{equation*}
-		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq t_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
-	\end{itemize}
-\end{lemma}
-
-\begin{proof}
-	The first statement is immediately obvious, and we turn to proving the second.
-
-	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.
-
-	By the concavity of the $\log$ function, 
-	\begin{equation*}
-	\bar{g}(t) = \log\left(\frac{1}{t_i}\right) \geq \log\left(\frac{1}{t}\right) - \frac{(t_i - t)}{t}.
-	\end{equation*}
-	As a result,
-	\begin{equation*}
-	\bar{g}(t) - \frac{g(t)}{2} \geq \frac{\log\left(\frac{1}{t}\right)}{2} - \frac{(t_i - t)}{t} \geq 1/2 - 1/2 = 0.
-	\end{equation*}
-\end{proof}
-
-The following theorem is found in \cite{kannan04}. It gives a bound population-level conductance function over convex bodies, when the density is uniform.
-\begin{theorem}[Restatement of \cite{kannan04} Theorem 4.6]
-	\label{thm: kannan}
-	Let $K \subset \Rd$ be a convex body of diameter $D$. Then for any $\Sset \subset K$ with $\pi_{\nu,r}(\Sset) \leq 1/2$,
-	\begin{equation}
-	\label{eqn: kannan}
-	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\nu,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{\pi_{\nu,r}(\Sset)}\right)\right\}.
-	\end{equation}
-\end{theorem}
-
-\begin{lemma}
-	\label{lem: continuous_conductance_lower_bound}
-	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
-	\begin{itemize}
-		\item 
-		for $0 < t < 1/2$,
-		\begin{equation*}
-		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-		\end{equation*}
-		\item
-		Let
-		\begin{equation*}
-		M = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
-		\end{equation*}
-		and $t_i = (i + 1)/M$ for $i = 0, \ldots, m - 1$. Then, for $1/M < t < 1/2$
-		\begin{equation*}
-		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-		\end{equation*}
-		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{M - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
-	\end{itemize}
-\end{lemma}
-Before we prove Lemma \ref{lem: continuous_conductance_lower_bound}, note that the choice of $M$ is made to ensure $t_0$ is greater than the local spread of $G_{n,r}\left[\Csig[\Xbf]\right]$, as we will see in Section \ref{sec: convex_consistency}.
-\begin{proof}[Proof of Lemma \ref{lem: continuous_conductance_lower_bound}]
-	We note that
-	\begin{equation*}
-	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
-	\end{equation*}
-
-	Plugging these estimates in to \eqref{eqn: kannan} gives
-	\begin{equation*}
-	\frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \pi_{\Pbb,r}(\Sset)}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
-	\end{equation*}
-	and since the right hand side is decreasing in $\pi_{\Pbb,r}(\Sset)$, the desired lower bound holds on $\widetilde{\Phi}_{\Pbb,r}(t)$.
-The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
-\end{proof}
-
-\subsection{Consistency of local spread and conductance function: convex case.}
-\label{sec: convex_consistency}
-
-The introduction of the stepwise approximation allows us to make use of Lemma \ref{lem: consistency_of_conductance_function}, which gives us (pointwise) consistency of the discrete graph functionals $\widetilde{\Phi}_{n,r}(t)$ to the continuous functionals $\widetilde{\Phi}_{\Pbb,r}(t)$.
-
-We use $\omega_r(1)$ to denote a term which goes to infinity as $r \to 0$, and likewise $o_r(1)$ to denote a term which goes to $0$ as $r \to 0$.
-
-\begin{lemma}
-	\label{lem: consistency_of_conductance_function}
-	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
-	\begin{equation}
-	\label{eqn: pointwise_consistency_of_conductance_function}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\left\{\widetilde{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
-	\end{equation}
-	where $c_d$ is a constant which may depend on the dimension $d$ (as well as the distribution $\Pbb$), but not $r$.
-
-	As a consequence, for $M$ and $(t_i)_{i=0}^{M-1}$ defined as in Lemma \ref{lem: continuous_conductance_lower_bound}, we have that
-	\begin{equation}
-	\label{eqn: consistency_of_stepapprox_conductance_function}
-	\liminf_{n \to \infty} \overline{\Phi}_{n,r}(t) \geq \min\left\{\overline{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
-	\end{equation}
-\end{lemma}
-We defer the proof of pointwise consistency to Section \ref{sec: pointwise_consistency_of_conductance_function}.
-For now, we show that \eqref{eqn: consistency_of_stepapprox_conductance_function} is immediately implied by \eqref{eqn: pointwise_consistency_of_conductance_function}.
-
-\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
-	We take as given that for any $0 < t < 1/2$,
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
-	\end{equation*}
-	In particular, for sufficiently large $n$ this will occur for each of $t_0, t_1, \ldots, t_m$ and therefore
-	\begin{equation*}
-	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
-	\end{equation*}
-	uniformly over $[1/m,1/2]$.
-\end{proof}
-
-\subsection{Pointwise consistency of conductance function: convex case.}
-\label{sec: pointwise_consistency_of_conductance_function}
-
-We will rely heavily on results of \cite{garciatrillos16}, which prove the same result but consider only a pointwise result on $\widetilde{\Phi}_{n,r}(1/2)$ rather than over the entire conductance function.
-
-Let $\wX = \Csig[\Xbf] = \set{\wx_1, \ldots, \wx_{\wn}}$, and $\wn = \abs{\wX}$. Then
-\begin{equation*}
-\widetilde{\Pbb}_n := \frac{1}{\wn} \sum_{\wx_i \in \wX} \delta_{\wx_i}
-\end{equation*}
-is the empirical distribution of $\wX$. Likewise, for $\Sset \subset \Csig$ let $\widetilde{\Pbb}$ be the conditional distribution $\Pbb(x \in S \vert x \in \Csig)$, given by
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) := \frac{\nu_{\Pbb}(\Sset)}{\nu_{\Pbb}(\Csig)}.
-\end{equation*}
-A Borel map $T: \Csig \to \wX$ is a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset))
-\end{equation*}
-for all $\Sset \in \Csig$.
-
-\begin{lemma}[Proposition 5 of \cite{garciatrillos16}]
-	There exists a sequence of transportation maps $(T_{\wn})$ from $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ such that
-	\begin{equation*}
-	\limsup_{\wn \to \infty} \frac{\wn^{1/d} \norm{\Id - T_{\wn}}_{\L^{\infty}(\widetilde{\Pbb})}}{(\log \wn)^{p_d} } \leq C
-	\end{equation*}
-	where $p_d = 1/d$ for $d \geq 3$ and $3/4$ if $d = 2$. 
-\end{lemma}
-These are referred to stagnating transportation maps. We refer the curious reader to \cite{garciatrillos16} for more details.
-
-For $S \subset \wX$, we will denote $\vol(S; \widetilde{G}_{n,r})$ by $\widetilde{\vol}_{n,r}(S)$, and likewise $\cut(S; \widetilde{G}_{n,r})$ by $\widetilde{\cut}_{n,r}(S)$.
-
-Consider a sequence of sets $(S_{\wn})_{\wn \in \mathbb{N}}$, with $u_{\wn} = \1_{S_{\wn}}$ the characteristic function of $S_{\wn}$. Similarly, for $\Sset \subset \Csig$ let $u = \1_{\Sset}$.
-
-\begin{definition}
-	For a sequence $(u_{\wn}) \in L^1(\widetilde{\Pbb}_{\wn})$ and $u \in L^1(\widetilde{\Pbb})$, we say $(u_{\wn})$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $(T_{\wn})$ such that
-	\begin{equation*}
-	\int_{\Csig} \abs{u(x) - (u_{\wn}) \circ T_{\wn}(x)} d\widetilde{\Pbb}(x) \to 0
-	\end{equation*}
-	and denote it $u_{\wn} \overset{TL^1}{\to} u$.
-\end{definition}
-
-\begin{lemma}
-	\label{lem: cut_convergence}
-	If $(u_{\wn}) \overset{TL^1}{\to} u$, with probability one
-	\begin{equation*}
-	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} = \int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx
-	\end{equation*}
-	where $\wf$ is the density function of $\wPbb$ over $\Csig$.
-\end{lemma}
-
-\begin{proof}
-	We note immediately that $n \to \infty$ implies $\wn \to \infty$ with probability one.
-
-	Now, we can write
-	\begin{align*}
-	 \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\wn^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \bigl( 1 - u_{\wn}(\wx_j) \1(\norm{\wx_i - \wx_j} \leq r) \bigr)  \\
-	& = \int_{\Csig} \left(\int_{\Csig \cap B(x,r)} u_{\wn}(x) \bigl( 1 - u_{\wn}(x') \bigr) d\wPbb_n(x') \right) d\wPbb_n(x) \\
-	& = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x).
-	\end{align*}
-
-	Note that, for any $x \in \Csig$,
-	\begin{align*}
-	\lim_{n \to \infty} \nu\bigl(B(T_{\wn}(x),r) \setminus B(x,r)\bigr) & = 0 \\
-	\lim_{n \to \infty} \nu\bigl(B(x,r) \setminus B(T_{\wn}(x),r)\bigr) & = 0.
-	\end{align*}
-	and therefore
-	\begin{equation*}
-	\lim_{n \to \infty} \int_{\Csig \cap B(T_{\wn}(x),r)} \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') = \lim_{n \to \infty} \int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x')\right) d\wPbb(x').
-	\end{equation*}
-	An application of the bounded convergence theorem yields
-	\begin{align*}
-	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(T_{\wn}(x),r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) = \nonumber \\
-	& \lim_{n \to \infty} \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x).
-	\end{align*}
-	Letting
-	\begin{align*}
-	\mathcal{I}_n^1 & = \int_{\Csig} \left(u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( u(x') - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) \\
-	\mathcal{I}_n^2 & = \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x) - u(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left(1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) \\
-	\end{align*}
-	we have
+	Clearly $\piwt_{\Pbb,r_n^-}(\Sset) \leq \piwt_{\Pbb,r}(\Sset)$. Moreover
+	\begin{equation*}
+	\frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
+	\end{equation*}
+	which along with \eqref{eqn: stationary_dist_lb_1} implies
+	\begin{equation*}
+	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d \to \piwt_{\Pbb,r}(\Sset).
+	\end{equation*}
+	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	By Lemma \ref{lem: local_spread_lb}, with probability one as $n \to \infty$,
+	\begin{equation*}
+	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
+	\end{equation*}
+	and the claim is shown.
+\end{proof}
+
+\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+
+By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
+
+Let $S \subseteq \Csig[\Xbf]$ be arbitrary, and define
+\begin{equation*}
+\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx},~ \gamma_n(S) := \frac{\min \set{\piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
+\end{equation*}
+where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
+By Proposition \ref{prop: nonuniform_continuous_conductance} and Lemma \ref{lem: graph_to_continuous_conductance} we have that
 \begin{align}
-	\label{eqn: pointwise_convergence_1}
-	& \int_{\Csig} \left(u_{\wn} \circ T_{\wn}(x)\right) \left(\int_{\Csig \cap B(x,r)}  \left( 1 - u_{\wn} \circ T_{\wn}(x') \right) d\wPbb(x') \right) d\wPbb(x) = \nonumber \\
-	& \int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\wPbb(x') \right\} d\wPbb(x) + \mathcal{I}_n^1 + \mathcal{I}_n^2. 
+\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
+& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{12} \Lambda_{\sigma}^2 D L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
 \end{align}
 
-	Recalling that $u = 1_{\Sset}$, we can see
-	\begin{align}
-	\label{eqn: pointwise_convergence_2}
-	\int_{\Csig} u(x) \left\{ \int_{\Csig \cap B(x,r)} (1 - u(x')) d\wPbb(x') \right\} d\wPbb(x) & = \int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx
-	\end{align}
-	Since $(u_{\wn}) \overset{TL^1}{\to} u$, another application of the bounded convergence theorem yields $\lim_{n \to \infty} \mathcal{I}_n^1 = \lim_{n \to \infty} \mathcal{I}_n^2 = 0$.
-Therefore by \eqref{eqn: pointwise_convergence_1} and \eqref{eqn: pointwise_convergence_2} the final result holds.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: vol_convergence}
-	If $u_{\wn} \overset{TL^1}{\to} u$, then
-	\begin{equation*}
-	\lim_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} = 
-	\int_{\Sset} \wf(x) \left(\int_{\Csig \cap B(x,r)} \wf(x') dx' \right) dx
-	\end{equation*}
-	with probability one. 
-\end{lemma}
-\begin{proof}
-	We note that
-	\begin{align*}
-	\frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} & = \frac{1}{\widetilde{n}^2} \sum_{i = 1}^{\wn} \sum_{j = 1}^{\wn} u_{\wn}(\wx_i) \1(\norm{\wx_i - \wx_j} \leq r) - \frac{1}{\widetilde{n}} \\
-	& = \int_{\Csig} \int_{\Csig \cap B(x,r)} \left(u_{\wn}(x) d\wPbb_n(x')\right) d{\wPbb}(x) - \frac{1}{\wn}
-	\end{align*}
-	Of course, $\lim_{n \to \infty}  \frac{1}{\wn} = 0$, and so
-	\begin{equation*}
-	\lim_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} = \lim_{n \to \infty} \int_{\Csig} \left(\Csig \cap B(x,r) u_{\wn}(x) d\wPbb_n(x')\right) d_{\wPbb}(x)
-	\end{equation*}
-	The proof then proceeds analogously to Lemma \ref{lem: cut_convergence}. 
-\end{proof}
-
-Lemma \ref{lem: pre-compactness} can be found in \cite{alberti1998non} (Theorem 3.1) or \cite{garciatrillos16} (Lemma 23).
-\begin{lemma}
-	\label{lem: pre-compactness}
-	If $u_{\wn} \not\overset{TL^1}{\to} u$ for some $u \in L^1{\nu}$, with probability one:
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(\Sset_{\wn})}{\wn^2 } \geq  c_d r^{d+1} \omega_r(1)
-	\end{equation*}
-	where $c_d$ is a constant which does not depend on $r$ but may depend on $\Csig$ and $f$, and $\omega_r(1) \to \infty$ as $r \to 0$. 
-\end{lemma}
-
-\begin{proof}[Proof of \eqref{eqn: pointwise_consistency_of_conductance_function}]
-	Let $(S_{\wn}^{\star})$
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S_{\wn}^{\star})}{\widetilde{\vol}_{n,r}(S_{\wn}^{\star})} = \widetilde{\Phi}_{n,r}(t),~~ \widetilde{\pi}_{n,r}(S_{\wn}) \leq t
-	\end{equation*}
-	be the sequence of minimizers of the normalized cut with stationary distribution at most $t$ in the graph $\widetilde{G}_{n,r}$.
-Denote $u_{\wn}^{\star} = 1_{S_{\wn}^{\star}}$, and assume that $u_{\wn}^{\star} \overset{TL^1}{\to} u$, for $u = 1_{\Sset}, ~\Sset \subset \Csig$.
-	Then, by Lemmas \ref{lem: cut_convergence} and \ref{lem: vol_convergence},
-	\begin{align*}
-	\lim_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\widetilde{\vol}_{n,r}(S_{\wn})} & = \frac{\int_{\Sset} \wf(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} \wf(x') dx' \right) dx}{\int_{\Sset} \wf(x) \left(\int_{\Csig \cap B(x,r)} \wf(x') dx' \right) dx} \\
-	& \overset{(i)}{=} \frac{\int_{\Sset} f(x) \left(\int_{(\Csig \setminus \Sset) \cap B(x,r)} f(x') dx' \right) dx}{\int_{\Sset} f(x) \left(\int_{\Csig \cap B(x,r)} f(x') dx' \right) dx} 
-	& = \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}.
-	\end{align*}
-	where $(i)$ holds because the normalization factors present in $\wf$ cancel.
-From Lemma \ref{lem: vol_convergence}, we also have that $\lim_{n \to \infty}\widetilde{\pi}_{n,r}(S_{\wn}) = \pi_{\Pbb,r}(\Sset)$, and therefore $\pi_{\Pbb,r}(\Sset) \leq t$.
-As a result,
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)} \geq \widetilde{\Phi}_{\Pbb,r}(t).
-	\end{equation*}
-	On the other hand, if $u_{\wn}^{\star}$ does not converge $TL^1$, then
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\wn^2} \geq c_d r^{d+1} \omega_r(1)
-	\end{equation*}
-	Additionally,
-	\begin{equation*}
-	\frac{\widetilde{\vol}_{n,r}(S_{\wn})}{\wn^2} \leq \frac{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}{\wn^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})}{\wn^2} \leq \nu_d r^d \Lambda_{\sigma}
-	\end{equation*}
-	As a result,
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\widetilde{\cut}_{n,r}(S_{\wn})}{\widetilde{\vol}_{n,r}(S_{\wn})} \geq c_d r \omega_r(1).
-	\end{equation*}
-\end{proof}
-
-\subsection{Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}}
-\label{sec: inverse_mixing_time_lower_bound}
-Throughout this proof, we will refer to the subgraph $G_{n,r}\left[\Csig[\Xbf]\right]$ as $\widetilde{G}_{n,r}$.
-
-Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
-\begin{equation*}
-\widetilde{\qbf}_n^{(m)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
-\end{equation*}
-Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.
-
-By Lemmas \ref{lem: local_spread_G} and \ref{lem: local_spread_lower_bound},
-\begin{align*}
-\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) & \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{\widetilde{s}_{n,r}}\right) \right\} \nonumber \\
-& \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, 4d\log\left(\frac{2D \Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right) \right\}
-\end{align*}
-
-We now upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: expansion_to_tv_distance}, we have that
-\begin{equation}
-\label{eqn: mixing_time_bound_on_neighborhood_graph}
-\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt\right)
-\end{equation}
-(Since $r$ remains constant, for sufficiently large $n$, $\Dbf_{xx} > C$ will be fulfilled for any $x \in \Csig[\Xbf]$, and any $C < \infty$.)
-We set aside the constant term for the moment and turn to the integral. By Lemma \ref{lem: local_spread_lower_bound},
-\begin{equation*}
-\limsup_{n \to \infty}\int_{\widetilde{s}_{n,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt \leq \limsup_{n \to \infty}\int_{ s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt
-\end{equation*}
-where $s_{\Pbb,r}$ is as in the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}.
-We now replace the discrete conductance function $\widetilde{\Phi}_{n,r}$ by the stepwise approximation to the continuous conductance function, $\overline{\Phi}_{n,r}$:
-\begin{align*}
-\limsup_{n \to \infty}\int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\widetilde{\Phi}_{n,r}^2(t)} dt & \overset{(i)}{\leq} \limsup_{n \to \infty}\int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{n,r}^2(t)} dt \\
-& = \int_{s_{\Pbb,r}}^{1/2} \limsup_{n \to \infty} \frac{4}{t\overline{\Phi}_{n,r}^2(t)} dt\\
-& \overset{(ii)}{\leq} \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt + c_d^2 \log(s_{\Pbb,r}) \frac{1}{r^2} o_r(1)\\
-\end{align*}
-where $(i)$ follows from Lemma \ref{lem: stepwise_approximation} and $(ii)$ from Lemma \ref{lem: consistency_of_conductance_function} (along with the continuous mapping theorem).
-Now, we make use of Lemma \ref{lem: continuous_conductance_lower_bound}:
-\begin{align*}
-& \int_{s_{\Pbb,r}}^{1/2} \frac{4}{t\overline{\Phi}_{\Pbb,r}^2(t)} dt \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
-\int_{s_{\Pbb,r}}^{1/2} \frac{d}{t} dt + \int_{s_{\Pbb,r}}^{1/2} \frac{81dD^2}{r^2t \Log(\frac{\Lambda_{\sigma}^2}{t\lambda_{\sigma}^2})}  dt\right) \\
-& \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
-\underbrace{\int_{s_{\Pbb,r}}^{1/2} \frac{d}{t} dt}_{:= \mathcal{J}_1} + 
-81\underbrace{\int_{s_{\Pbb,r}}^{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)} \frac{dD^2}{r^2t \log(\frac{\Lambda_{\sigma}^2}{t\lambda_{\sigma}^2})} dt}_{:= \mathcal{J}_2} +
-81\underbrace{\int_{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)}^{1/2} \frac{dD^2}{r^2t \log(1 + \frac{4 \lambda_{\sigma}^2}{\Lambda_{\sigma}^2})}dt}_{:= \mathcal{J}_3}  \right)
-\end{align*}
-
-Computing a few simple integrals yields the following upper bounds on $\mathcal{J}_1, \mathcal{J}_2, \mathcal{J}_3$:
-\begin{align*}
-\mathcal{J}_1 & \leq d^2 \log\left( \frac{2D\Lambda_{\sigma}^2}{r\lambda_{\sigma}^2} \right) \\
-\mathcal{J}_2 & \leq \frac{dD^2}{r^2} \left[ \log\left(2d\right) + \log\left(\log\left(\frac{2D}{r}\right)\right) \right] \\
-\mathcal{J}_3 & \overset{(iii)}{\leq} 2 \frac{dD^2}{r^2} \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} \log\left(4 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right)
-\end{align*}
-where $(iii)$ uses the upper bound $\frac{1}{\log(1 + x)} \leq \frac{1}{x}$.
-
-Plugging these bounds in to \eqref{eqn: mixing_time_bound_on_neighborhood_graph} gives the desired upper bound on $\tau_{\infty}(\widetilde{q}_n, \widetilde{G}_{n,r})$, which translates to the lower bound of \eqref{eqn: inverse_mixing_time_lower_bound}.
+By Lemma \ref{lem: cont_local_conductance}, with probability one
+\begin{equation*}
+\liminf_{n \to \infty} \xi_n = 1.
+\end{equation*}
+
+By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $0 < c < \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}$, with probability one there exists some $m \in \mathbb{N}$ such that for all $n \geq m$,
+\begin{equation*}
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})}\piwt_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
+\end{equation*}
+and therefore by Lemma \ref{lem: cont_stationary_dist}
+\begin{equation*}
+\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
+\end{equation*}
+
+As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
+
+\subsection{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
+Lemma \ref{lem: expansion_to_tv_distance} implies
+\begin{equation}
+\label{eqn: expansion_to_tv_distance_1}
+\tau_1(\widetilde{G}_{n,r}) \leq 490 \cdot \left(\frac{20}{9} + \int_{s'(\widetilde{G}_{n,r})}^{1/2} \frac{4}{t \widetilde{\Phi}_{n,r}^2(t)} \dt \right)
+\end{equation}
+where we recall $s'(G) = \frac{s(G)}{9}$.
+
+By Lemmas \ref{lem: graph_conductance_profile_lb} and \ref{lem: local_spread_lb} for sufficiently large $n$, and for any $0 < t \leq \frac{1}{2}$
+\begin{equation*}
+s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20 \Lambda_{\sigma}}, \quad \widetilde{\Phi}_{n,r}(t) > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
+\end{equation*}
+which along with \eqref{eqn: expansion_to_tv_distance_1} and Lemma \ref{lem: tv_mixing_to_pointwise_mixing1} implies the desired result.
 
@@
 	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
-	\frac{\degmin}{n} & \geq  (1 - \epsilon) \lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
-	\frac{\degmax}{n} & \leq (1 + \epsilon) \Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
-	\frac{\abs{\Csig[\Xbf]}}{n} & \leq \Pbb(\Csig)(1 + \epsilon) \label{eqn: Csig_cardinality_bound}\\
+	\frac{\degmin}{n} & \geq  (1 - \epsilon)\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
+	\frac{\abs{\Csig[\Xbf]}}{n} & \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}\\
 	\label{eqn: volwt_bound}
@@
 	\end{align}
+
+	Additionally, with probability one,
+	\begin{align*}
+	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \\
+	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d
+	\end{align*}
 \end{lemma}
@@
 	\begin{equation*}
-	\int_{\Csig} \Pbb(B(x,r)) dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
+	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
 	\end{equation*}
@@
 	\label{eqn: ball_bounds_in_probability_1}
-	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx 
-	\end{equation}
-	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) dx) \to 0$ as $n \to \infty$.
-Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx$ given by \eqref{eqn: initialization}, yields
-	\begin{equation*}
-	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx \leq \frac{1}{2} \vol_0.
-	\end{equation*}
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
+	\end{equation}
+	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
+Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
+	\begin{equation*}
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
+	\end{equation*}
+
+	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
+	\begin{equation*}
+	\Pbb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} \geq (1 + \epsilon)\mu \right) \leq \exp(-n\epsilon^2\mu).
+	\end{equation*}
+	The final two statements therefore both follow from the Borel-Cantelli Lemma.
 \end{proof}

### 2019-05-13 neurips/local_spectral_density_clustering.tex
Added weekly notes detailing TV to infinity mixing time for lazy random walk

--- 2019-05-10 arxiv/arxiv_local_density_clustering.tex
@@
-%%%%%%%% Local Spectral Clustering of Density Upper Level Sets %%%%%%%%%%%%%%%%%
-
 \documentclass{article}
+
+% if you need to pass options to natbib, use, e.g.:
+%     \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading neurips_2019
+
+% ready for submission
+% \usepackage{neurips_2019}
+
+% to compile a preprint version, e.g., for submission to arXiv, add add the
+% [preprint] option:
+%     \usepackage[preprint]{neurips_2019}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+%     \usepackage[final]{neurips_2019}
+
+\usepackage{neurips_2019}
+
+% to avoid loading the natbib package, add option nonatbib:
+%     \usepackage[nonatbib]{neurips_2019}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
 \usepackage{microtype}
@@
 \usepackage{bm}
-\usepackage{fullpage}
-
-\usepackage[square,sort,comma,numbers]{natbib}
-\renewcommand{\bibname}{REFERENCES}
-\renewcommand{\bibsection}{\subsubsection*{\bibname}}
-
-% Left and right equations
-\makeatletter
-\newcommand{\leqnomode}{\tagsleft@true\let\veqno\@@leqno}
-\newcommand{\reqnomode}{\tagsleft@false\let\veqno\@@eqno}
-\makeatother
 
@@
 
+\title{Local Spectral Clustering of Density Upper Level Sets}
+
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to LaTeX to determine where to break the
+% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
+% authors names on the first line, and the last on the second line, try using
+% \AND instead of \And before the third author name.
+
+\author{%
+  David S.~Hippocampus\thanks{Use footnote for providing further information
+    about author (webpage, alternative address)---\emph{not} for acknowledging
+    funding agencies.} \\
+  Department of Computer Science\\
+  Cranberry-Lemon University\\
+  Pittsburgh, PA 15213 \\
+  \texttt{hippo@cs.cranberry-lemon.edu} \\
+  % examples of more authors
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \AND
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+}
+
 \begin{document}
 
-\title{Local Spectral Clustering of Density Upper Level Sets}
-\author{Alden Green, Sivaraman Balakrishnan, and Ryan Tibshirani}
-\date{\today}
 \maketitle
@@
 \begin{abstract}
-\vskip 0.1 in % RESOLVED
+\vskip 0.1 in
   Spectral clustering methods are a family of popular nonparametric clustering
@@
   clusters. Moreover, we prove that PPR, run on a neighborhood graph, extracts
-sufficiently salient density clusters.
+  sufficiently salient density clusters. Finally, we provide empirical support of our theory.
 \end{abstract}
@@
 where $\widetilde{\pi}_{\min} = \min_{u \in \Csig[\Xbf]} \widetilde{\pi}_{n,r}(u)$.
-As $\widetilde{\pi}_{\min} = \mathcal{O}(1/n)$, the upper bound on the right hand side will be of order $\log(n)$, and the bound becomes trivial as $n \to \infty$.
+As $\widetilde{\pi}_{\min} = \mathcal{O}(1/n)$, the upper bound on the right hand side will be of order at least $\log(n)$, and the bound becomes trivial as $n \to \infty$.
 
@@
 
+\clearpage
+
 \bibliographystyle{plainnat}

### 2019-05-13 neurips/template.tex
Added weekly notes detailing TV to infinity mixing time for lazy random walk

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2019}

\usepackage{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting Instructions For NeurIPS 2019}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Submission of papers to NeurIPS 2019}

NeurIPS requires electronic submissions.  The electronic submission site is
\begin{center}
  \url{https://cmt.research.microsoft.com/NeurIPS2019/}
\end{center}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2019 must be prepared according to the
instructions presented here. Papers may only be up to eight pages long,
including figures. Additional pages \emph{containing only acknowledgments and/or
  cited references} are allowed. Papers that exceed eight pages of content
(ignoring references) will not be reviewed, or in any other way considered for
presentation at the conference.

The margins in 2019 are the same as since 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2019.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2019+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2019}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All acknowledgments
go at the end of the paper. Do not include acknowledgments in the anonymized
submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references. {\bf Remember that you can use more than eight
  pages as long as the additional pages contain \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2019-05-13 notes/weekly_notes/4.27.19.NotesForWeek.tex
Added weekly notes detailing TV to infinity mixing time for lazy random walk

@@
 
-	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is also compact, $\Asig$ is compact. Moreover,
+	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is itself compact, $\Asig$ is compact. Moreover,
 	\begin{equation*}
@@
 
+\section{Old version of the same result.}
+
+For two sets $\mathcal{X},\mathcal{Y}$ and scalar $\alpha$, we write 
+\begin{equation*}
+\mathcal{X} + \mathcal{Y} := \set{z: z = x + y, x \in \mathcal{X}, y \in \mathcal{Y}},~ \mathcal{X} - \mathcal{Y} := \set{z: z = x - y, x \in \mathcal{X}, y \in \mathcal{Y}}
+\end{equation*}
+and $\alpha \mathcal{X} = \set{z: z = \alpha x, x \in \mathcal{X}}$.
+
+Let $B = B(0,1)$ be the $d$-dimensional unit ball centered at the origin.
+
+\begin{lemma}
+	\label{lem: expansion_sets}
+	Let $\mathcal{K} \subseteq \Reals^d$ be a convex set, and $g: \Reals^d \to \Reals^d$ be a measure preserving Lipschitz mapping, meaning there exists $ L > 0$ such that
+	\begin{equation*}
+	\frac{1}{L} \norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} \tag{for all $x,y \in \Reals^d$}
+	\end{equation*}
+	and $\norm{\nabla g (x)} = 1$ for all $x \in \Reals^d$. Letting $\mathcal{A} = g(\mathcal{K})$, the following statement holds: if for $\sigma > 0$, there exists some $x \in \Rd$ such that 
+	\begin{equation}
+	\label{eqn: expansion_sets}
+	B(x,\sigma) \subseteq \mathcal{A} 
+	\end{equation}
+	then for any $\delta > 0$
+	\begin{equation*}
+	\nu(\mathcal{A} + \delta B) \leq \left(1 + \frac{L^2 \delta}{\sigma}\right)^d \nu(\mathcal{A})
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We begin by showing the statement in the convex case, where $g = \mathrm{Id}$ is the identity mapping, before proceeding to show it in full generality.
+Without loss of generality assume $\sigma B \subseteq \mathcal{A}$, otherwise center by $\mathcal{A} - x$ for some $x$ such that $B(x,\sigma) \subseteq \mathcal{A}$, and as Lebesgue measure is invariant under translation any bound on the volume of $\mathcal{A} - x$ holds for $\mathcal{A}$ as well.
+
+	\textbf{Convex case, $g = \Id$.}
+
+	Note that 
+	\begin{equation}
+	\label{eqn: expansion_sets_1}
+	\mathcal{A} + \delta B \subseteq \mathcal{A} + \frac{\delta}{\sigma}\mathcal{A}
+	\end{equation}
+	as $y \in \delta B$ implies $\frac{\sigma}{\delta}y \in \sigma B \subseteq \mathcal{A}$.
+For $z \in \mathcal{A} + \frac{\delta}{\sigma}\mathcal{A}$, write $z := a + \frac{\delta}{\sigma} a'$ for some $a,a' \in \mathcal{A}$.
+Then
+	\begin{equation}
+	\label{eqn: expansion_sets_2}
+	\frac{1}{1 + \delta/\sigma}z = \frac{1}{1 + \delta/\sigma}a + \frac{\delta/\sigma}{1 + \delta/\sigma} a' \in \mathcal{A}
+	\end{equation}
+	where the last statement follows by the convexity of $\mathcal{A}$.
+Together, \eqref{eqn: expansion_sets_1} and \eqref{eqn: expansion_sets_2} imply $\mathcal{A} + \delta B \subseteq (1 + \frac{\delta}{\sigma})\mathcal{A}$, and therefore
+	\begin{equation*}
+	\nu(\mathcal{A} + \delta B) \leq \nu\Biggl(\left(1 + \frac{\delta}{\sigma}\right)\mathcal{A}\Biggr) = \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\mathcal{A})
+	\end{equation*}
+	where the last statement follows by the change of variables formula.
+
+	\textbf{Non-convex case, $g$ general.} For any $z \in \mathcal{A} + \delta B$, there exists $x \in \mathcal{A}$ such that $\norm{z - x} \leq \delta$. Therefore
+	\begin{equation*}
+	\norm{g^{-1}(z) - g^{-1}(x)} \leq L \delta
+	\end{equation*}
+	and since $g^{-1}(x) \in \mathcal{K}$, $g^{-1}(z) \in \mathcal{K} + L \delta B$. As a result, $\mathcal{A} + \delta B \subseteq g(\mathcal{K} + L \delta B)$; since $g$ is measure-preserving, we have
+	\begin{equation*}
+	\nu(\mathcal{A} + \delta B) \leq \nu(\mathcal{K} + L \delta B)
+	\end{equation*}
+
+	Additionally, note that the hypothesis $\sigma B \subseteq \mathcal{A}$ implies that $g^{-1}(\sigma B) \subseteq \mathcal{K}$, and if $\norm{z} \leq \frac{\sigma}{L}$, then $g(z) \in \sigma(B)$ and $z \in g^{-1}(\sigma B)$.
+Therefore, letting $\sigma' = \frac{\sigma}{L}$, we have
+	\begin{equation*}
+	\sigma' B \subseteq \mathcal{K}
+	\end{equation*}
+	and the general result follows from applying the convex result to $\mathcal{K} + \delta'B$ for $\delta' = \delta L$. 
+\end{proof}
+
 \end{document}

### 2019-05-13 notes/weekly_notes/5.11.19.NotesForWeek.tex
Added weekly notes detailing TV to infinity mixing time for lazy random walk

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}
\newcommand{\dist}{\mathrm{dist}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}
\newcommand{\Sset}{\mathcal{S}}

\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asig}{\Aset_{\sigma}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ebb}{\mathbb{E}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}

%%% Functionals over graphs
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\vol}{\mathrm{vol}}
% \newcommand{\deg}{\mathrm{deg}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for the week of 5/11/19 - 5/17/19}
\author{Alden Green}
\date{\today}
\maketitle

For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf + \Dbf^{-1}\Abf}{2}$, stationary distribution $\pi$. Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$. We wish to upper bound the total variation distance between the distributions $q_v^{(m)} := q^{(m)}(v,\cdot)$ and $\pi$,
\begin{equation*}
\norm{q_v^{(t + 1)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
\end{equation*}
using geometric properties of the graph $\Wbf$. We introduce the \emph{degree, cut} and \emph{volume} functionals over a graph. For $u \in V$, $A \subseteq G$, 
\begin{equation*}
\cut(A;G) = \sum_{u \in A} \sum_{v \in A^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(A;G) = \sum_{u \in A} \deg(u;G)
\end{equation*}

The \emph{local spread} is defined as
\begin{equation*}
s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}
\end{equation*}

Letting \emph{normalized cut} of $A \subseteq G$, $\Phi(A;G)$ be defined as
\begin{equation*}
\Phi(A;G) = \frac{\cut(A, A^c; G)}{\min\set{\vol(A; G),\vol(A^c; G)}},
\end{equation*}
and the \emph{conductance} is
\begin{equation*}
\Phi(G) = \min_{A \subseteq V} \Phi(A;G).
\end{equation*}

\begin{theorem}
	\label{thm: tv_mixing_time}
	For any $v \in V$,
	\begin{equation*}
	\norm{q_v^{(t + 3)} - \pi}_{TV} \leq \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2s(G)/9}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
	\end{equation*}
\end{theorem}

As we will see, Theorem \ref{thm: tv_mixing_time} is an essential step to providing an upper bound on the uniform mixing time, which is what we want. We justify this statement next, before moving on to proving Theorem \ref{thm: tv_mixing_time}.

\paragraph{Uniform mixing time.}
Consider the \emph{uniform} distance \footnote{Note $d_{\textrm{unif}}$ is not a formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
\begin{equation*}
d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
\end{equation*}

\begin{theorem}
	\label{thm: tv_to_uniform_distance}
	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
	\begin{equation*}
	d_{\textrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
	\end{equation*}
\end{theorem}
\begin{proof}
	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
	\begin{align}
	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
	& \overset{(i)}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
	\end{align}
	where $(i)$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.

	Then 
	\begin{align*}
	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \\
	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \\
	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \\
	\end{align*}
	since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$. As $m - 1 \geq t$, it is well known \cite{lovasz} that the laziness  of the random walk guarantees  $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore
	\begin{equation*}
	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \leq \frac{1}{14}.
	\end{equation*}

	Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
	\begin{equation}
	d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{2}{7} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
	\end{equation}
	The recurrence relation of \eqref{eqn: tv_to_uniform_distance_2} along with the initial condition $d_{\textrm{unif}}(q_v^{(t)}, \pi) \leq 1$ yields
	\begin{equation*}
	d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{10}{28} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
	\end{equation*}
	and the claim is shown.
\end{proof}

\section{Proof of Theorem \ref{thm: tv_mixing_time}.}

For arbitrary starting distribution $q$ (meaning $\textrm{supp}(q) \subseteq V$ and $\sum_{u \in V}q(u) = 1$), and for $t \geq 0$ an integer, consider the distance function $h_q^{(t)}, t \geq 0$, 
\begin{equation*}
h_q^{(t)}(x) = \max \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
\end{equation*}
where the maximum is over all $w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$. Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Theorem \ref{thm: lt_ub} and Lemma \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{e_v}^{(t)}(x)$ for all $0 \leq x \leq 1$.

\vskip 0.1 in
\begin{remark}
	$h_q^{(t)}$ permits an equivalent relation. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
	\begin{equation*}
	\frac{q^{(m)}(u_1)}{\pi(u_1)} \geq \frac{q^{(m)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q^{(m)}(u_N)}{\pi(u_N)}
	\end{equation*}
	and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that,
	\begin{equation}
	\label{eqn: lovasz_simonovits_curve}
	h_q^{(t)}(x) = \sum_{j = 1}^{k - 1} (q^{(m)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q^{(m)}(u_k) - \pi(u_k) \right).
	\end{equation}
	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}.
\end{remark}

\paragraph{Mixing over large sets.}

For $0 \leq \mu \leq 1$ and $\mu \leq x \leq 1 - \mu$ let 
\begin{equation*}
\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(1 - \mu)
\end{equation*}
be the linear interpolator between $h_q^{(0)}(\mu)$ and $h_q^{(0)}(1 - \mu)$.

\begin{theorem}
	\label{thm: lt_ub}
	For any $0 \leq \mu \leq 1/2$ and $\mu \leq x \leq 1 - \mu$ and $t \geq 0$, 
	\begin{equation*}
	h_q^{(t)}(x) \leq \ell_{\mu}(x) + \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 }\left(1 - \frac{\Phi^2(G)}{2}\right)^t
	\end{equation*}
\end{theorem}

Theorem \ref{thm: lt_ub} is a direct consequence of Theorem \ref{thm: lovasz_simonovits_1993}. To state the latter, we introduce
\begin{equation*}
C_{\mu} = \max \set{\frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu}
\end{equation*}
\begin{theorem}[Theorem 1.2 of \textcolor{red}{Lovasz-Simonovits 1993}]
	\label{thm: lovasz_simonovits_1993}
	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
	\begin{equation*}
	h_q^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
	\end{equation*}
\end{theorem}

\begin{proof}[Proof of Theorem \ref{thm: lt_ub}]
	Fix $0 \leq \mu \leq \frac{1}{2}$. We will show that for all $\mu \leq x \leq 1 - \mu$
	\begin{equation}
	\label{eqn: lt_ub_1}
	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
	\end{equation}
	whence the claim follows by Theorem \ref{thm: lovasz_simonovits_1993}.

	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
	\begin{equation*}
	h_q^{(0)}(x) \leq h_q^{(0)}(\mu) + (x - \mu)\frac{h_q^{(0)}(\mu)}{\mu}
	\end{equation*}
	by the concavity of $h_0$ along with Lemma \ref{lem: lovasz_simonovits_subdifferential}. Some basic algebra then yields
	\begin{align*}
	h_q^{(0)}(x) - \ell_{\mu}(x) & \leq h_q^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu)\right) + \frac{h_q^{(0)}(\mu)}{\mu}(x - \mu) \\
	& =  \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(\mu) + \frac{h_q^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu) \\
	& \leq \sqrt{x - \mu} \left(\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} \right)
	\end{align*}
	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and Lemma \ref{lem: lovasz_simonovits_subdifferential},  for $x \leq 1 - \mu$
	\begin{equation*}
	h_q^{(0)}(x) \leq h_q^{(0)}(1 - \mu) + (1 - x - \mu).
	\end{equation*}
	Similar manipulations to above give the upper bound
	\begin{align*}
	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
	\end{align*}
	and \eqref{eqn: lt_ub_1} follows.
\end{proof}

\begin{lemma}
	\label{lem: lovasz_simonovits_subdifferential}
	The subdifferential $v(x)$ of $h_q^{(0)}(x)$ satisfies
	\begin{equation*}
	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}
	\end{equation*}
\end{lemma}

\paragraph{Mixing over small sets.}

\begin{lemma}
	\label{lem: mixing_time_small_sets}
	Let $0 \leq a \leq 1$, and $t \geq 1$ an integer. Then for any $x \leq as(G)$ or $x \geq 1 - as(G)$,
	\begin{equation*}
	h_v^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
	\end{equation*}
\end{lemma}
\begin{proof}
	First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
	\begin{equation}
	\label{eqn: mixing_time_small_sets_1}
	h_v^{(t)}(x) \leq q_v^{(m)}(U_{k - 1}) + q_v^{(m)}(u_k)
	\end{equation}

	We will rely on the key fact that for any $u \neq v, t \geq 1$,
	\begin{equation}
	\label{eqn: mixing_time_small_sets_2}
	q_v^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
	\end{equation}

	On the other hand if $u = v$,
	\begin{equation}
	\label{eqn: mixing_time_small_sets_3}
	q_v^{(m)}(u) \leq \frac{1}{2^t} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
	\end{equation}
	Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
	\begin{equation*}
	h_v^{(t)}(x) \leq \frac{1}{2^t} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
	\end{equation*}
	Since $x \leq a s(G)$, 
	\begin{equation*}
	\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
	\end{equation*}

	For any $0 \leq b \leq 1$, $x \geq 1 - b$ implies $h_v^{(t)}(x) \leq b$. Taking $b = a s(G)$, the claim is shown.
\end{proof}

\paragraph{Proof of Theorem \ref{thm: tv_mixing_time}.}
For any $A \subseteq V$ and any integer $t \geq 0$,
\begin{equation*}
\max \set{h_v^{(t)}(\pi(A)), h_v^{(t)}(1 - \pi(A))} \geq \abs{q_v^{(t)}(A) - \pi(A)}
\end{equation*}
and taking max over both sides, we have
\begin{equation*}
\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{TV}.
\end{equation*}

Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_v^{(t)}(x)$. Fix $\mu = \frac{1}{9}s(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Theorem \ref{thm: lt_ub},
\begin{align*}
h_v^{(t + 3)}(x) & = h_q^{(t)}(x) \\
& \leq \max \set{h_q^{(0)}(\mu), h_q^{(0)}(1 - \mu) }  + \left(\frac{1}{1 - 2 \mu} + \frac{1}{2\mu}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t\\
& \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2s(G)/9}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
\end{align*}
where the last inequality comes from application of Lemma \ref{lem: mixing_time_small_sets} to $h_q^{(t)} = h_v^{(t + 3)}$.

For $x \leq \mu$ or $x \geq 1 - \mu$,
\begin{equation*}
h_v^{(t + 3)}(x) \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}}
\end{equation*}
and the proof is complete.

\end{document}

### 2019-05-14 arxiv/arxiv_local_density_clustering.tex
updated proofs, detailed edits of arxiv version. Copied/pasted neurips version

@@
 \usepackage{fullpage}
+\usepackage{mathtools}
 
@@
 
+% Absolute value
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
+
 \newcommand{\diam}{\mathrm{diam}}
@@
 \newcommand{\cut}{\mathrm{cut}}
-\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
+% \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
 \newcommand{\N}{\mathbb{N}}
@@
 %%% Vectors
-\newcommand{\pbf}{\mathbf{p}}
+\newcommand{\pbf}{p}        % removed bold font
 \newcommand{\qbf}{\mathbf{q}}
@@
 \newcommand{\Abf}{\mathbf{A}}
-\newcommand{\Xbf}{\mathbf{X}}
+\newcommand{\Xbf}{X}             % removed bold font 
 \newcommand{\Wbf}{\mathbf{W}}
@@
 \newcommand{\Csig}{\Cset_{\sigma}}
+\newcommand{\Sset}{\mathcal{S}}
+
+%%% Graph quantities
+\newcommand{\Cest}{\widehat{C}}
 
@@
 clusters. Moreover, we prove that PPR, run on a neighborhood graph, extracts
-sufficiently salient density clusters.
+sufficiently salient density clusters. Finally, we provide empirical support of our theory.
 \end{abstract}
@@
 
-Let $\mathbf{X} = \{x_1, \ldots, x_n\}$ be a sample drawn i.i.d.\ from a
+Let $\Xbf = \{x_1, \ldots, x_n\}$ be a sample drawn i.i.d.\ from a
 distribution $\Pbb$ on $\Rd$, with density $f$, and consider the problem of 
@@
 To be more precise, let $G=(V,E,w)$ denote a weighted, undirected graph  
-constructed from the samples $\mathbf{X}$, where $V=\{1,\ldots,n\}$, and $w_{uv}
+constructed from the samples $\Xbf$, where $V=\{1,\ldots,n\}$, and $w_{uv}
 = K(x_u,x_v) \geq 0$ for $u,v \in V$, and a particular kernel function $K$.
@@
 \smash{$\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$}.  We also denote by $\Wbf,\Lbf$
-the random walk transition probability matrix and normalized\footnote{Other
+the (lazy) random walk transition probability matrix and normalized\footnote{Other
   popular choices here include the unnormalized Laplacian, and symmetric
@@
 $$
-\Wbf = \Dbf^{-1}\Abf, \quad \Lbf = \Ibf{} - \Wbf,
+\Wbf = \frac{\Ibf{} + \Dbf^{-1}\Abf}{2}, \quad \Lbf = \Ibf{} - \Wbf,
 $$
@@
 
-Define the cut between subsets $S,S' \subseteq V$ to be
-$$
-\cut(S, S'; G) = \sum_{u \in S} \sum_{v \in S'} w_{uv},
-$$
-and define
-\smash{$\vol(S; G) = \cut(S, V; G) = \sum_{u \in S} \sum_{v \in V} w_{uv}$}.  
+For subsets $S,S' \subseteq V$, we define the cut, degree, and volume functionals as usual,
+$$
+\cut(S, S'; G) = \sum_{u \in S} \sum_{v \in S'} w_{uv}, \quad \deg(u; G) = \sum_{v \in V} w_{uv}, \quad  \vol(S; G) = \sum_{u \in S} \deg(u;G).
+$$
 As our notion of external connectivity, we use the \emph{normalized cut}  
@@
 be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
-random walk matrix as usual, $\Wbf = \Dbf_S^{-1} \Abf_S$, and for $v \in V$,
+(lazy) random walk matrix as usual, $\Wbf = \frac{\Dbf_S^{-1} \Abf_S + \Ibf{\abs{S} \times \abs{S}}}{2}$, and for $v \in V$,
 write 
 $$
-q_{vu}^{(t)} = e_v\Wbf_S^t e_u
+q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
 $$
@@
   \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
-  steps.}   Also write \smash{$\widetilde\pibf = (\widetilde\pi_{u})_{u \in S}$}
+  steps.}   Also write \smash{$\pi = (\pi(u))_{u \in S}$}
 for the stationary distribution of this random walk.  (Given the definition of 
-$\Wbf_S$, it is well-known that the stationary distribution is given by
-\smash{$\widetilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)
+$\Wbf_S$, it is well-known that a unique stationary distribution exists and is given by
+\smash{$\pi(u) = \deg(u; G[S])/\vol(S; G[S])$}.)
 
@@
 $$
-\tau_{\infty}(G[S]) = \min\set{ m: \frac{|q_{vu}^{(m)} - 
-      \widetilde\pi_u|}{\widetilde\pi_u} \leq \frac{1}{4}, 
+\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)
+	}{\pi(u)} \leq \frac{1}{4}, 
 	\; \text{for $u,v \in V$}}. 
@@
 $\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted graph with vertices
-$V=\{1,\ldots,n\}$, and an edge $(u,v) \in E$ if and only if $\norm{x_u - x_v}
+$V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i - x_j}
 \leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.  Note that this is a
@@
 For a level $\beta > 0$ and a target volume $\vol_0 > 0$, we define a
-\emph{$\beta$-sweep cut} of $\pbf$ as  
+\emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$ as  
 \begin{equation}
 \label{eqn: sweep_cuts}
-S_\beta = \{u \in V: \textcolor{red}{\frac{p_u}{\Dbf_{uu}}} > \frac{\beta}{\vol_{0}}\}.
+S_\beta = \{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}\}.
 \end{equation}
@@
 algorithms, see, e.g., \citep{zhu2013}.}
-we output a cluster \smash{$\widehat{C} = S_{\beta^*}$}, based on the sweep cut
+we output a cluster \smash{$\Cest = S_{\beta^*}$}, based on the sweep cut
 $S_{\beta^*}$ that minimizes the normalized cut \smash{$\Phi(S_{\beta^*};
@@
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation 
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume $\pi_0 >
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume $\vol_0 >
 0$. \\   
-{\bfseries Output:} cluster $\widehat{C} \subseteq V$.
+{\bfseries Output:} cluster $\Cest \subseteq V$.
 \begin{algorithmic}[1]
@@
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-  \STATE Return \smash{$\widehat{C} = S_{\beta^*}$}, where 
+  \STATE Return \smash{$\Cest = S_{\beta^*}$}, where 
   $$
@@
 
-\begin{definition}[Misclassification rate]
+\begin{definition}[Misclassification error]
 \label{def: misclassification_rate}
-For an estimator \smash{$\widehat{\Cset} \subseteq \Xbf$} and set
-$\mathcal{S} \subseteq \Reals^d$, the \emph{misclassification rate} of $\mathcal{S}$ by $\widehat{\Cset}$ is
+For an estimator \smash{$\Cest \subseteq \Xbf$} and set
+$\mathcal{S} \subseteq \Reals^d$, the \emph{misclassification error} of $\mathcal{S}$ by $\Cest$ is
 \begin{equation}
 \label{eqn: misclassification_rate}
-\abs{\widehat{\Cset} \setminus (\mathcal{S} \cap \Xbf)} + \abs{(\mathcal{S} \cap \Xbf) \setminus \widehat{\Cset}}.
+\abs{\Cest \setminus (\mathcal{S} \cap \Xbf)} + \abs{(\mathcal{S} \cap \Xbf) \setminus \Cest}.
 \end{equation}
@@
 \label{def: consistent_density_cluster_estimation}
-For an estimator \smash{$\widehat{\Cset} \subseteq \Xbf$} and cluster 
-$\Cset \in \Cbb_f(\lambda)$, we say \smash{$\widehat{\Cset}$} is a consistent
+For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster 
+$\Cset \in \Cbb_f(\lambda)$, we say \smash{$\Cest$} is a consistent
 estimator of $\Cset$ if for all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset \not=
@@
 \label{eqn: consistent_density_cluster_recovery}
-\Cset[\Xbf] \subseteq \widehat{\Cset} \quad \text{and} \quad
-\widehat{\Cset} \cap \Cset'[\Xbf] = \emptyset,
+\Cset[\Xbf] \subseteq \Cest \quad \text{and} \quad
+\Cest \cap \Cset'[\Xbf] = \emptyset,
 \end{equation}
@@
 
-\item Under \textcolor{red}{largely the same set of geometric conditions}, we derive in Theorem
-  \ref{thm: inverse_lower_bound_nonconvex} a lower bound on the
+\item Under additional geometric conditions, which exclude sets with large diameter or small bottleneck, we derive in Theorem
+  \ref{thm: mixing_time_upper_bound} a lower bound on the
   inverse mixing time of a random walk over $\Csig[\Xbf]$.
@@
 \item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
-  Theorem \ref{thm: consistent_recovery_of_density_clusters} that the bounds on the cluster quality criteria established in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    inverse_mixing_time_lower_bound_nonconvex} have algorithmic consequences for \ppr: 
-  properly initialized, Algorithm \ref{alg: ppr} has low misclassification rate with respect to a small enlargement of the set $\Cset$, and if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-
-\item We show in Corollary \ref{cor: appr} that these statements hold also with respect to an approximate form of \pprspace, which can be efficiently computed.
+  Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} that the bounds on the cluster quality criteria established in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+    mixing_time_upper_bound} have algorithmic consequences for \ppr. 
+  Properly initialized, Algorithm \ref{alg: ppr} has low misclassification error with respect to a small enlargement of the set $\Cset$, and if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+Corollary \ref{cor: appr} establishes that these statements hold also with respect to an approximate form of \ppr, which can be efficiently computed.
 
 \item In Section \ref{sec: experiments}, we empirically
-  demonstrate the tightness of the bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, and provide examples showing how violations of the geometric conditions we require manifestly
+  demonstrate the tightness of the bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, and provide examples showing how violations of the geometric conditions we require manifestly
   impact density cluster recovery by \ppr.  
@@
 performance is well-understood in this context (see, e.g.,
-\citealt{tolliver2006,luxburg2007}).  In a similar vein, several recent works
+\citep{tolliver2006,luxburg2007}).  In a similar vein, several recent works
 \citep{mcsherry2001,rohe2011,kamalika2012,balakrishnan2011,lei2015,abbe2018} 
@@
 \emph{Lipschitz embedding:}
-There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
+There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying, for some $ L \geq 1$,
 \begin{equation*}
@@
 Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
-clusters and long clusters in \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
+clusters in \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
 
@@
 \ref{asmp: low_noise_density} is seen in, e.g., \citep{singh2009} (as well as
-many other works on density clustering and level set estimation.)  It is worth
+many other works on density clustering and level set estimation.) While \ref{asmp: embedding} may be less standard, as we will see, it is critical in order to achieve reasonably tight bounds on $\Psi(\Cset[\Xbf];
+G_{n,r})$.  It is also worth
 highlighting that these assumptions are all local in nature, a benefit of
@@
 
-We also note that while many of these geometric conditions are typical in the density clustering literature, the restrictions we will impose upon them in order to obtain meaningful implications for \pprspace will not be.
+We emphasize that while many of these geometric conditions are typical in the density clustering literature, the restrictions we will impose upon them in order to obtain meaningful implications for \pprspace will not be.
 This is natural.
@@
 and \ref{asmp: cluster_separation}, for some 
-$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/4d$ be such that
+$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/2d$ be such that
 \begin{equation}
@@
   \label{eqn: conductance_additive_error_bound}
-  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c \frac{d}{\sigma}
+  \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
   \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
@@
 \begin{equation*}
-\frac{\Pbb((\Csig + B(0,r)) \setminus \Csig)}{\Pbb(\Csig)} \geq d\frac{(\lambda - r^{\gamma}) r}{\sigma},
+\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) \geq c \lambda \nu_d r^d \Pbb((\Csig + B(0,r)), \quad \textrm{and} \quad \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r}) \leq c' \lambda \nu_d r^d \Pbb(\Csig)
 \end{equation*}
-and for some $c > 0$,
-\begin{equation*}
-\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) \setminus \Csig) \geq c \lambda \nu_d r^d \Pbb((\Csig + B(0,r)), \quad \textrm{and} \quad \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r}) \leq c \lambda \nu_d r^d \Pbb(\Csig)
-\end{equation*}
-so the ratio $\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) / \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r})$ matches \ref{eqn: conductance_additive_error_bound}, up to constants.
+for some constants $c,c' > 0$. Thus the ratio $\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) / \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r})$ matches \eqref{eqn: conductance_additive_error_bound}, up to constants.
 
@@
 Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
-	\begin{equation*}
+	\begin{equation}
+	\label{eqn: mixing_time_upper_bound}
 	\limsup_{n \to \infty}\tau_{n,r}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
-	\end{equation*}
+	\end{equation}
 \end{theorem}
@@
 
-We will outline the main techniques used to prove Theorem \ref{thm: mixing_time_upper_bound}, but first, we show that a straightforward and perhaps immediately obvious route to upper bounding the mixing time is insufficient for our purposes.
-Let $\widetilde{\Phi}_{n,r}$ be the \emph{conductance} of the induced subgraph $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$, given by
+Our proof technique involves two key geometric quantities: the \emph{local spread} $s(\widetilde{G}_{n,r})$ (where we abbreviate $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ and let $\widetilde{\pi}_{n,r}$ be the stationary distribution over $\widetilde{G}_{n,r}$) and the \emph{conductance} $\widetilde{\Phi}_{n,r}$, defined respectively as
+\begin{equation}
+\label{eqn: local_spread_and_conductance}
+s(\widetilde{G}_{n,r}) := \frac{9}{10} \min_{x \in \Csig[\Xbf]} \set{\deg(x; \widetilde{G}_{n,r}) \cdot \widetilde{\pi}_{n,r}(x) }, \quad \widetilde{\Phi}_{n,r} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; \widetilde{G}_{n,r}).
+\end{equation}
+
+We argue that the random walk over $\widetilde{G}_{n,r}$ quickly escapes sets with stationary distribution less than $s(\widetilde{G}_{n,r})$, and so we avoid a $\log\left(1/\pi_0\right)$ `start penalty' -- where $\pi_0 := \min_{x \in \Csig[\Xbf]} \widetilde{\pi}_{n,r} \lesssim \frac{1}{n}$ -- characteristic to analyses of mixing time, which would render any resultant upper bound on mixing time vacuous.
+Instead, we obtain the tighter upper bound \footnote{For sequences $a_n, b_n$, we write $a_n \lesssim b_n$ ($a_n \gtrsim b_n$) when there exists $c > 0$ such that $a_n \leq c b_n$ ($a_n \geq c b_n$) for all sufficiently large $n$.}
 \begin{equation*}
-\widetilde{\Phi}_{n,r} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; \widetilde{G}_{n,r}),
+\tau_{n,r}(\Csig[\Xbf]) \lesssim \frac{1}{\widetilde{\Phi}_{n,r}^2} \log^2\left(1/s(\widetilde{G}_{n,r})\right).
 \end{equation*}
-and $\widetilde{\mu}_2$ be the 2nd largest eigenvalue of $\Wbf_{\Csig[\Xbf]}$, the random walk matrix over $\widetilde{G}_{n,r}$. The famous Cheeger's inequality
-\begin{equation*}
-\frac{\widetilde{\Phi}_{n,r}^2}{2} \leq 1 - \widetilde{\mu}_2 \leq \widetilde{\Phi}_{n,r}
-\end{equation*}
-applied with well known theory on $\infty$-mixing time yields
-\begin{equation*}
-\abs{\widetilde{\pi}_{n,r}(u) - e_v \Wbf_{\Csig[\Xbf]}^te_u} \leq \left(1 - \frac{\widetilde{\Phi}_{n,r}^2}{2}\right)^t \sqrt{\frac{\deg(u; \widetilde{G}_{n,r})}{\min_{v \in \Csig[\Xbf]} \deg(v; \widetilde{G}_{n,r})}} \tag{$u,v \in \Csig[\Xbf]$}
-\end{equation*}
-where $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$ Unfortunately, even if $\widetilde{G}_{n,r}$ is an approximately degree-regular graph, (meaning we can ignore the term under the square root), this bound only yields \footnote{For sequences of numbers $\set{a_n}_{n \in \mathbb{N}}, \set{b_n}_{n \in \mathbb{N}}$, we say $a_n = \mathcal{O}(b_n)$ when there exists $c$ sufficiently large such that $a_n \leq c b_n$ for all $n$.}
-\begin{equation*}
-\tau_{n,r}(\Csig[\Xbf]) = \mathcal{O} \left( \frac{\log\left(\frac{1}{\widetilde{\pi}_{\min}}\right)}{\widetilde{\Phi}_{n,r}^2} \right).
-\end{equation*}
-where $\widetilde{\pi}_{\min} = \min_{u \in \Csig[\Xbf]} \widetilde{\pi}_{n,r}(u)$.
-As $\widetilde{\pi}_{\min} = \mathcal{O}(1/n)$, the upper bound on the right hand side will be of order $\log(n)$, and the bound becomes trivial as $n \to \infty$.
-
-\textcolor{red}{We therefore apply a more complex approach.}
-
+Then,
+\begin{itemize}
+	\item Some straightforward calculations yield $s(\widetilde{G}_{n,r}) \gtrsim \frac{\Lambda_{\sigma} r^d}{\lambda_{\sigma}}$.
+	\item To handle the conductance, we introduce a continuous analogue, 
+	\begin{equation}
+	\label{eqn: continuous_conductance}
+	\widetilde{\Phi}_{\Pbb,r} := \min_{\mathcal{S} \subseteq \Csig} \left(\frac{\int_{\Sset} \Pbb(B(x,r) \cap \Sset^c) f(x) dx}{\min \set{\int_{\Sset} \Pbb(B(x,r) \cap \Csig) f(x) dx, \int_{\Sset^c} \Pbb(B(x,r) \cap \Csig) f(x) dx}}\right), \quad \Sset^c = \Csig \setminus \Sset
+	\end{equation}
+	and show the asymptotic lower bound $\limsup_{n \to \infty} \widetilde{\Phi}_{n,r} \gtrsim \widetilde{\Phi}_{\Pbb,r}$.
+	\item Finally, we extend classical isoperimetric results lower bounding $\widetilde{\Phi}_{\Pbb,r}$, when $\Pbb$ is uniform and $\Csig$ convex, to hold under the more general conditions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
+\end{itemize}
+
+\begin{remark}
+	The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$ obviously play an important role in the upper bound of Theorem \ref{thm: mixing_time_upper_bound}.
+It is clear that there is some interdependence between $L$ and other geometric parameters $\sigma$ and $D$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
+However, it is not possible to eliminate this condition without incurring an additional factor of at least $(D/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ consists of two balls of diameter $D$ linked by a cylinder of length $D$ and radius $\sigma$.
+\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding biLipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
+\end{remark}
 \section{Consistent Cluster Estimation}
@@
 
-We focusing for a moment on the neighborhood graph radius $r$.
-While taking $r \to 0$ as $n \to \infty$ -- and thereby ensuring $G_{n,r}$ is sparse-- is computationally attractive, the presence of a factor of $\frac{1}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace for this regime.
-While the restriction to a kernel function fixed in $n$ is standard for theoretical analysis \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
+We focus for a moment on the neighborhood graph radius $r$.
+While taking $r \to 0$ as $n \to \infty$---and thereby ensuring $G_{n,r}$ is sparse---is computationally attractive, the presence of a factor of $\frac{1}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace in this regime.
+Although the restriction to a kernel function fixed in $n$ is standard for theoretical analysis of spectral clustering \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
 
@@
 
-In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
+In particular, for a well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we require
 \begin{align}
 \label{eqn: initialization}
-\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta), & ~r \leq \frac{\sigma}{2d} \nonumber,  \\
-\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, & ~v \in \Csig[\Xbf]^g
+r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta) \nonumber,  \\
+v \in \Csig[\Xbf]^g, & ~\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx
 \end{align}
 where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$.
-(Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
+(Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the data sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
 
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn: initialization} with respect to some $\Csig[\Xbf]$, we say the algorithm is  \emph{well-initialized}.
+	If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn: initialization} for some well-conditioned density cluster $\Cset$, we say the algorithm is \emph{well-initialized}.
 \end{definition}
@@
 In practice, a reasonable way to choose these hyperparameters is by tuning.
-For example, if one wanted to successfully recover a density cluster, one could vary each hyperparameter over a grid, retaining outputs $\widehat{\Cset}$ of Algorithm \ref{alg: ppr} only if they recover $\Cset[\Xbf]$ for some $\Cset \in \Cbb_f(\lambda)$ and discarding them otherwise.
-Then simply return the minimum normalized cut set from those $\widehat{\Cset}$ which were retained.
+For example, if one wanted to successfully recover a density cluster, one could vary each hyperparameter over a grid, retaining outputs $\Cest$ of Algorithm \ref{alg: ppr} only if they recover some $\Cset \in \Cbb_f(\lambda)$ and discarding them otherwise.
+Then simply return the minimum normalized cut set from those $\Cest$ which were retained.
 Assuming there existed $\lambda > 0, \Cset \in \Cbb_f(\lambda)$ such that $\Cset$ satisfied the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, and moreover some combination of tuning parameters in the chosen grid satisfied \eqref{eqn: initialization}, this scheme would inherit the consistency guarantees of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
 
-\paragraph{Misclassification rates for \ppr.}
+\paragraph{Misclassification error for \ppr.}
 
 In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
-This work, combined with the results of Section \ref{sec: cluster_quality_bounds}, immediately implies a bound on the volume of $\widehat{C} \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \widehat{C}$),
+This work, combined with the results of Section \ref{sec: cluster_quality_bounds}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference}
-\frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\vol_{n,r}(\Csig[\Xbf])}, \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\vol_{n,r}(\Csig[\Xbf])} = \mathcal{O}\bigl( \kappa(\Cset) \bigr).
-\end{equation}
-
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification rate, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
+\vol_{n,r}(\Cest \setminus \Csig[\Xbf]), \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \lesssim \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
+\end{equation}
+where we've written $\vol_{n,r}(S) := \vol(S; G_{n,r})$ for $S \subseteq \Xbf$. 
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification error, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
 To do so, we make some regularity assumptions on $\mathcal{X} = \mathrm{supp}(f)$.
@@
 	\label{eqn: misclassification_rate_ub}
-	\frac{\abs{\Csig[\Xbf] \setminus \widehat{C}}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}
-	\end{equation}
-	and
-	\begin{equation}
-	\label{eqn: misclassification_rate_ub_2}
-	\frac{\abs{\widehat{C} \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
-	\end{equation}
-	for universal constants $c_5, c_6 > 0$. 
+	\frac{\abs{\Csig[\Xbf] \setminus \Cest}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}, \quad \textrm{and} \quad \frac{\abs{\Cest \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
+	\end{equation}
+	for universal constants $c_4, c_5 > 0$. 
 \end{theorem}
@@
 \begin{remark}
-	A notable implication of our theory is that as the diameter $D$ increases, our upper bounded on the normalized cut of $\Csig$ remains unchanged, but $\kappa(\Cset)$, and therefore the misclassification rate, worsens (increases).
+	A notable implication of our theory is that as the diameter $D$ increases, our upper bound on the normalized cut of $\Csig[\Xbf]$ remains unchanged, but $\kappa(\Cset)$, and therefore the misclassification error, worsens (increases).
 This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
@@
 Neither \eqref{eqn: graph_symmetric_set_difference} nor Theorem \ref{thm: misclassification_rate} imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, u' \in \Cset'$, of the form
+This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, u' \in \Cset'$
 \begin{equation}
 \label{eqn: ppr_gap}
-\frac{\pbf(u')}{\Dbf_{uu}} \leq \frac{c}{\vol_0} < \frac{C}{\vol_0} \leq \frac{\pbf(u)}{\Dbf_{uu}}.
-\end{equation}
-so that a sweep cut $S_{\beta}$ for $\beta \vol_0 \in [c,C]$ would fulfill both conditions laid out in \eqref{eqn: consistent_density_cluster_recovery}.
-Theorem \ref{thm: consistent_recovery_of_density_clusters} provides sufficient conditions under which this gap will appear.
+\frac{p_{u'}}{\Dbf_{uu}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}}.
+\end{equation}
+so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e.
+any sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions laid out in \eqref{eqn: consistent_density_cluster_recovery}.
+In Theorem \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently small upper bound on $\kappa(\Cset)$ ensures such a gap exists with probability one as $n \to \infty$, and therefore guarantees $\Cest$ will be a consistent estimator.
 
@@
 	\end{equation}
-	then the output set $\widehat{C} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 \end{theorem}
@@
 
-As mentioned previously, in practice solving \eqref{eqn: ppr_vector} may be too computationally expensive.
+As mentioned previously, in practice exactly solving \eqref{eqn: ppr_vector} may be too computationally expensive.
 To address this limitation, \citet{andersen2006} introduced the \emph{$\epsilon$-approximate \pprspace vector} (aPPR), which we will denote $\pbf^{(\epsilon)}$.
@@
 	\label{cor: appr}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}.
-Set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\widehat{\Cset}$.
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
 	\begin{enumerate}
-		\item Assume \ref{asmp: valid_region} holds. Then \eqref{eqn: misclassification_rate_ub} and \eqref{eqn: misclassification_rate_ub_2} are still valid upper bounds.
+		\item Assume \ref{asmp: valid_region} holds. Then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
 		\item Assume \ref{asmp: C'_bounded_density} holds. If
@@
 		\end{equation*}
-		then $\widehat{\Cset} \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 	\end{enumerate}
@@
 	\end{subfigure}
-	\caption{}
+	\caption{Samples, empirical results, and theoretical bounds for mixing time and normalized cut as diameter and thickness are varied.
+In (a) and (b), points in $\Cset$ are colored in red; points in $\Csig \setminus \Cset$ are colored in yellow; and remaining points in blue.}
 	\label{fig:fig1}
@@
 We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$.
-It is in these regions that the slopes of the dashed and solid lines appear most distinct.
+It is in these regions that the slopes of the dashed and solid lines are most different.
 As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
@@
 for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the cluster tree estimator of \cite{chaudhuri2010}.
+The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
 
@@
 
-There are still many directions worth pursuing in this area.
-Concretely, we might wish to generalize our results to hold over a wider range of kernel functions, and hyperparameter inputs to the \pprspace algorithm.
-More broadly, we do not provide any sort of theoretical lower bound, although we give empirical evidence in Figures \ref{fig: graphic_1} and \ref{fig: graphic_2} that poorly conditioned density clusters are not consistently estimated by \pprspace.
-
-The initial motivation for this article was based on the intuition that density level sets, in the right conditions, will have small normalized cut.
-As a result, algorithms with normalized cut based guarantees (such as \pprspace) seemed likely to have density cluster recovery guarantees as well.
-However, the second-order behavior of \pprspace when failing to recover the conductance cut is also of interest.
-Are there situations when the conductance cut and density cut differ, yet \pprspace still recovers the latter?
-This is an open question.
+We do not provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
+Although we investigate the matter empirically, this is a direction for future work.
 

### 2019-05-14 arxiv/arxiv_local_density_clustering_proofs.tex
updated proofs, detailed edits of arxiv version. Copied/pasted neurips version

@@
 \let\ppr\relax
+\let\Cset\relax
+\let\Csig\relax
+
 \externaldocument{arxiv_local_density_clustering}
+
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 
@@
 \newcommand{\defeq}{\overset{\mathrm{def}}{=}}
+% \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
 \newcommand{\vol}{\mathrm{vol}}
-\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
 \newcommand{\N}{\mathbb{N}}
@@
 %%% Vectors
-\newcommand{\pbf}{\mathbf{p}}
+\newcommand{\pbf}{p} % no bold font
 \newcommand{\qbf}{\mathbf{q}}
 \newcommand{\ebf}[1]{\mathbf{e}_{#1}}
-\newcommand{\pibf}{\bm{\pi}}
+\newcommand{\pibf}{\pi} % no bold font
 \newcommand{\rhobf}{\bm{\rho}}
@@
 \newcommand{\Abf}{\mathbf{A}}
-\newcommand{\Xbf}{\mathbf{X}}
+\newcommand{\Xbf}{X} % no bold font
 \newcommand{\Wbf}{\mathbf{W}}
@@
 
-%\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-%\icmltitlerunning{Local clustering of density upper level sets}
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
 
 \begin{document}
-
-%\twocolumn[
-%\icmltitle{Supplement to ``Local clustering of density upper level sets''}
-
-%\icmlsetsymbol{equal}{*}
-
-%\begin{icmlauthorlist}
-%\icmlauthor{Alden Green}{cmu}
-%\icmlauthor{Sivaraman Balakrishnan}{cmu}
-%\icmlauthor{Ryan Tibshirani}{cmu}
-%\end{icmlauthorlist}
-
-%\icmlaffiliation{cmu}{Department of Statistics and Data Science, Carnegie Mellon University, Pittsburgh PA, USA}
-
-%\icmlcorrespondingauthor{Alden Green}{ajgreen@andrew.cmu.edu}
-
-%\icmlkeywords{local clustering}
-
-%\vskip 0.3in
-%]
-
-%\printAffiliationsAndNotice{} % otherwise use the standard text.
 
@@
 Sections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
-\ref{sec: mixing_time_on_graphs} develops a bound of the form of \eqref{eqn: average_conductance}, which we recall links the conductance function to mixing time; this will be necessary for both Theorems \ref{thm: inverse_mixing_time_lower_bound_nonconvex} and \ref{thm: inverse_mixing_time_lower_bound}.
-\ref{sec: non_convex_conductance_function_and_local_spread} and \ref{sec: inverse_mixing_time_lower_bound_nonconvex} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, while \ref{sec: convex_population_conductance_function}- \ref{sec: inverse_mixing_time_lower_bound} give the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}.
-\ref{sec: concentration} gives some general concentration results used throughout, before we finish with the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} in \ref{sec: proof_of_consistent_cluster_recovery}.
+In Sections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish a link between the conductance and local spread, and mixing time; this will be necessary for Theorem \ref{thm: mixing_time_upper_bound}.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in Sections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
+\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and Corollary \ref{cor: appr}, in Sections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
 
@@
 
+	% AJG 5/14/19: This argument makes sense, correct?
 	We first consider the term $\Sigma_k$.
-$\Cset$ has finite diameter by \ref{asmp: cluster_diameter}.
+$\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
 Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
@@
 
-For $N \in \mathbb{N}$ and a collection $V = \set{v_1,\ldots,v_N}$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, degree matrix $\Dbf$, and random walk matrix $\Wbf$.
-We consider the stationary distribution $\pi$ to be a mapping from $V$ to $[0,1]$, with $\pi(u) := \frac{\Dbf_{uu}}{\vol(V; G)}$ for $u \in V$.
-For $v \in V$, let $q: V \times V \to [0,1]$ represent the $m$-step transition probability of the random walk over $G$ originating from $v$, $q^{(m)}(v,u) = e_v\Wbf^m e_u$.
-The relative pointwise mixing time over $G$ is then
-\begin{equation*}
-\tau_{\infty}(G) = \min\set{m: \forall u,v \in V, \frac{\abs{q^{(m)}(v,u) - \pi(u)}}{\pi(u)} \leq 1/4}. 
-\end{equation*}
-
-Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined as
-\begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{v \in V} \set{\deg(v; G)} \cdot \min_{v \in V} \set{\pi(v)}
-\end{equation*}
-For $f: V \to \Reals$, and $S \subseteq V$, write $f(S) := \sum_{u \in S} f(u)$. We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
-\begin{lemma}
-	~
-
-	\label{lem: local_spread_G}
-	\begin{itemize}
-		\item If $\pi(S) \leq s(G)$, then for every $u \in S$, $q^{(1)}(u,S^c) \geq \frac{1}{10}$.
-		\item For any $v, u \in V$, and $m \in \mathbb{N}, m \geq 0$,
-		\begin{equation*}
-		q^{(m)}(v,u) \leq \frac{\min_{v \in V} \set{\pi(v)}}{s(G)}.
-		\end{equation*}
-	\end{itemize}
-
-\end{lemma}
-
-\begin{proof}
-	If $\pi(S) \leq s(G)$, divide both sides by $\min_{v \in V} \set{\pi(v)}$ to obtain $\abs{S} \leq 9\min_{v \in V} \set{\deg(v; G)}/10$,
-	which implies $q^{(1)}(v,S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.
-
-	The second statement follows from the fact $q^{(m)}(v,u) \leq 1/\min_{v \in V} \set{\deg(v; G)}$ for any $m$.
-\end{proof}
-
-The local spread facilitates conversion between $\tau_{\infty}(G)$ and the more easily manageable \emph{total variation} mixing time, given by
-\begin{equation*}
-\tau_1(G) = \min\biggl\{m: \forall v \in V, \norm{\rho^{(m)}(v,\cdot) - \pi}_{TV} \leq 1/4 \biggr\}
-\end{equation*}
-where $\rho^{(m)}(u,v) = \sum_{l = 1}^{m} p^{(l)}(u,v)$ 
-and $\norm{\rho(v,\cdot) - \pi}_{TV} = \sum_{u \in V}\abs{\rho(u,v) - \pi(v)}$ is the total variation norm between distributions $\rho(v,\cdot)$ and $\pi$. 
-\begin{lemma}
-	\label{lem: tv_mixing_to_pointwise_mixing1}
-	\begin{equation*}
-	\tau_{\infty}(G) \leq 2752 \cdot \tau_1(G) \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\}\right)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Masking dependence on the starting vertex $v$ for the moment, let
-	\begin{equation*}
-	\Delta^{(m)}(u) = q^{(m)}(v,u) - \pi(u), ~~ \delta^{(m)}(u) = \frac{\Delta^{(m)}(u)}{\pi(u)}
-	\end{equation*}
-	and denote $\Deltabf^{(m)} = \bigl(\Delta^{(m)}(u)\bigr)_{u \in V}$, $\deltabf^{(m)} = \bigl(\delta^{(m)}(u)\bigr)_{u \in V}$.
-For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pi)$ norm is given by
-	\begin{equation*}
-	\norm{\Deltabf}_{L^p(\pi)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi(u) \right)^{1/p}
-	\end{equation*}
-	To go between the $L^{\infty}(\pi)$ and $L^{1}(\pi)$ norms, we capitalize on a clever argument developed in \cite{morris2005}. For any $v,u \in V$, by the time-reversibility of the graph random walk,
+We recall some notation from the main text.
+For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
+Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$.
+An important intermediate quantity used to bound the relative pointwise mixing time $\tau_{\infty}(G)$ is the total variation distance between the distributions $q_v^{(m)} := q^{(m)}(v,\cdot)$ and $\pi$,
+\begin{equation*}
+\norm{q_v^{(t + 1)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
+\end{equation*}
+We recall the \emph{degree, cut} and \emph{volume} functionals over a graph. For $u \in V$, $S \subseteq V$, 
+\begin{equation*}
+\cut(A;G) = \sum_{u \in A} \sum_{v \in A^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(A;G) = \sum_{u \in A} \deg(u;G)
+\end{equation*}
+
+The \emph{local spread} is defined as
+\begin{equation*}
+s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}
+\end{equation*}
+
+Letting the \emph{normalized cut} $\Phi(S;G)$ be defined as
+\begin{equation*}
+\Phi(S;G) = \frac{\cut(S, S^c; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
+\end{equation*}
+the \emph{conductance} is
+\begin{equation*}
+\Phi(G) = \min_{S \subseteq V} \Phi(S;G).
+\end{equation*}
+
+Proposition \ref{prop: tv_mixing_time} relates these geometric quantities to the TV distance between $q_v^{(t)}$ and stationary distribution $\pi$.
+\begin{proposition}
+	\label{prop: tv_mixing_time}
+	For any $v \in V$, and any $0 < a \leq 1$,
+	\begin{equation*}
+	\norm{q_v^{(t + 3)} - \pi}_{TV} \leq \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2as(G)} + \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
+\end{proposition}
+
+As we will see, Proposition \ref{prop: tv_mixing_time} is an essential step to providing an upper bound on the uniform mixing time.
+We justify this statement next, before moving on to proving Proposition \ref{prop: tv_mixing_time} in the following subsection.
+
+\paragraph{Uniform mixing time.}
+Consider the uniform distance \footnote{Note $d_{\textrm{unif}}$ is not a formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
+\begin{equation*}
+d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: tv_to_uniform_distance}
+	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
+	\begin{equation*}
+	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
 	\begin{align}
-	\abs{\frac{q^{(2m)}(v,u) - \pi(u)}{\pi(u)}} & = \abs{\sum_{y \in V} \pi(y) \left( \frac{q^{(m)}(v,y) - \pi(y)}{\pi(y)}\right)\left(\frac{q^{(m)}(u,y) - \pi(y)}{\pi(y)} \right)} \nonumber \\
-	& \leq \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}, \label{eqn: infty_norm_to_one_norm}
+	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
+	& \overset{(i)}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
+	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
 	\end{align}
-	with the second line following by Holder's inequality.
-
-	Now, we upper bound the second factor on the right hand side by observing
-	\begin{align}
-	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q^{(m)}(v,u)}{\pi(u)} \right\} \nonumber \\
-	& \overset{(i)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\} \label{eqn: ub_infinity_norm}
-	\end{align}
-	where $(i)$ follows from Lemma \ref{lem: local_spread_G}.
-
-	Set $m_0 = 1376 \tau_1(G) $, which we will show implies $\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4}$.
-Now, we leverage the following well-known fact (see pg.
-1 of \cite{montenegro2002}): for any $\epsilon > 0$, if $m \geq m_0 \cdot \log(1/\epsilon)$ then for any $v \in V$,
-	\begin{equation}
-	\label{eqn: rapid_mixing}
-	\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \epsilon.
-	\end{equation}
-	But $\norm{q^{(m)}(v,\cdot) - \pi}_{TV}$ is exactly $\norm{\deltabf^{(m)}}_{L^{1}(\pi)}$. Letting
-	\begin{equation*}
-	m_1 = m_0 \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
-	\end{equation*} 
-	by \eqref{eqn: infty_norm_to_one_norm}, \eqref{eqn: ub_infinity_norm}, and \eqref{eqn: rapid_mixing}, $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_1$.  Recall that
-	\begin{equation*}
-	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u \in V}\left\{ \frac{\abs{q^{(m)}(v,u) - \pi(u)}}{\pi(u)} \right\}.
-	\end{equation*}
-	and since none of the above depended on a specific choice of $v$, the supremum can be taken over all starting vertices $v$ as well.
-Thus for all $m \geq 2m_1$, for any $v,u \in V$, $\abs{q^{m}(v,u) - \pi(u)} \leq \frac{\pi(u)}{4}$.
-
-	Finally, it is known (pg.15 of \citep{montenegro2002}) that
-	\begin{equation*}
-	\norm{\rho^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4} \Longrightarrow  \norm{q^{(1376m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4} 
-	\end{equation*}
-	and so $m_0 = 1376 \tau_1(G)$ implies $\norm{q^{(m)}(v,\cdot) - \pi}_{TV} \leq \frac{1}{4}$, completing the proof.
-\end{proof}
-
-The second key quantity is the \emph{conductance function}. For $\min_{u \in V}\set{\pi(u)} \leq t \leq 1/2$, the conductance function is defined as
-\begin{equation}
-\label{eqn: conductance_function}
-\Phi(t; G) := \min_{\substack{S \subseteq V, \\ 0 < \pibf(S) \leq t} } \Phi(S; G)
-\end{equation}
-where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}, and in the minimization $S$ may not be the empty set.
-
-Lemma \ref{lem: expansion_to_tv_distance} leverages the conductance function and local spread to produce an upper bound on the total variation distance between $\rhobf_{v}^{(m)}$ and $\pibf.$
-\begin{lemma}
-	\label{lem: expansion_to_tv_distance}
-	If $D_{\min} > 10$, for any $v \in V$:
-	\begin{equation*}
-	\norm{\rhobf_v^{(m)} - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, \frac{1}{10} +  \frac{70}{m}\left(\frac{20}{9} + \int_{t = s'(G)}^{1/2} \frac{4}{t \Phi^2(t; G)} dt\right) \right\}
-	\end{equation*}
-	where $s'(G) = s(G) / 9$.
-\end{lemma}
-
-To prove Lemma \ref{lem: expansion_to_tv_distance} we first introduce a generalization of $\Phi(t;G) \cdot \Phi(t;G)$ known as a blocking conductance function.
-\footnote{For more details, see \cite{montenegro2002}}
-
-\begin{definition}[Blocking Conductance Function of \cite{montenegro2002}]
-	\label{def: blocking_conductance_function}
-	For $t_0 \geq \pi_{\min}$, a function $\phi(t; G): [t_0, 1/2] \to [0,1]$ is a \emph{blocking conductance function} if for all $S \subset V$ with $\pibf(S) = t \in [t_0, 1/2]$, either of the following hold:
-	\begin{enumerate}
-		\item \emph{Exterior inequality.} For all $y \in \left[\frac{1}{2}t, t\right]: \phi_{int}(S) \geq \phi(\max\{t_0,y\})$
-		\item \emph{Interior inequality.} For all $y  \in \left[t, \frac{3}{2}t\right]: \phi_{ext}(S) \geq \phi(\max\{y,1 - y\})$.
-	\end{enumerate}
-	where $\phi_{int}$ and $\phi_{ext}$ are defined respectively as
-	\begin{align*}
-	\phi_{int}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2} \\
-	\phi_{ext}(S) & = \sup_{\lambda \leq \pibf(S)} \min_{\substack{B \subset S^c \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\pibf(S) \pibf(S^c)\right]^2}
-	\end{align*}
-\end{definition}
-
-\begin{theorem}[Theorem 3.2 of \cite{montenegro2002}]
-	\label{thm: montenegro}
-	Consider $\phi(t; G): [t_0, 1/2] \to [0,1]$ a blocking conductance function. Then, letting
-	\begin{equation*}
-	h^m(t_0) = \sup_{S: \pibf(S) < t_0}  \bigl(\rhobf_v^{(m)}(S) - \pibf(S) \bigr)
-	\end{equation*}
-	the following statement holds: if $\phi$ is a blocking conductance function,
-	\begin{align*}
-	\norm{\rhobf_v^{(m)} - \pibf}_{TV} & \leq \max\left\{ \frac{1}{4}, h^1(t_0) +  \frac{70}{m}\left(\frac{1}{\phi(t_0; G)} + \int_{t = t_0}^{1/2} \frac{4}{t \phi(t; G)} dt\right) \right\} \\
-	\end{align*}
+	where $(i)$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.
+
+	Then 
+	\begin{align*}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \\
+	\end{align*}
+	since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
+As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness  of the random walk guarantees  $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore
+	\begin{equation*}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \leq \frac{1}{14}.
+	\end{equation*}
+
+	Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
+	\begin{equation}
+	d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{2}{7} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
+	\end{equation}
+	The recurrence relation of \eqref{eqn: tv_to_uniform_distance_2} along with the initial condition $d_{\textrm{unif}}(q_v^{(t)}, \pi) \leq 1$ yields
+	\begin{equation*}
+	d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{10}{28} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
+	\end{equation*}
+	and the claim is shown.
+\end{proof}
+
+Together, Proposition \ref{prop: tv_mixing_time} and Lemma \ref{lem: tv_to_uniform_distance} imply the main result of this section.
+
+\begin{proposition}
+	\label{prop: pointwise_mixing_time}
+	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
+	\begin{equation*}
+	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+	\end{equation*}
+\end{proposition}
+\begin{proof}
+	Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$. Then,
+	\begin{equation*}
+	\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
+	\end{equation*}
+	and so by Proposition \ref{prop: tv_mixing_time},
+	\begin{equation*}
+	\norm{q_v^{(\tau_0 + 3)} - \pi}_{TV} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+	\end{equation*}
+
+	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{4}$, then for any $) < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{TV} \leq \epsilon$.
+Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
+	\begin{equation*}
+	\norm{q_v^{(\tau_1)} - \pi}_{TV} \leq \frac{1}{14 s(G)}
+	\end{equation*}
+	and so $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
+\end{proof}
+
+\subsection{Proof of Proposition \ref{prop: tv_mixing_time}.}
+\label{sec: proof_of_proposition_tv_mixing_time}
+
+For arbitrary starting distribution $q$ (meaning $\textrm{supp}(q) \subseteq V$ and $\sum_{u \in V}q(u) = 1$), and for $t \geq 0$ an integer, let $q^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $q$.
+Consider the distance function $h_q^{(t)}, t \geq 0$,
+\begin{equation*}
+h_q^{(t)}(x) = \max \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
+\end{equation*}
+where the maximum is over all $w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$.
+Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{e_v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
+
+\vskip 0.1 in
+\begin{remark}
+	$h_q^{(t)}$ permits an equivalent relation. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
+	\begin{equation*}
+	\frac{q^{(m)}(u_1)}{\pi(u_1)} \geq \frac{q^{(m)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q^{(m)}(u_N)}{\pi(u_N)}
+	\end{equation*}
+	and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that,
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_curve}
+	h_q^{(t)}(x) = \sum_{j = 1}^{k - 1} (q^{(m)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q^{(m)}(u_k) - \pi(u_k) \right).
+	\end{equation}
+	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}.
+\end{remark}
+
+\paragraph{Mixing over large sets.}
+
+For $0 \leq \mu \leq 1$ and $\mu \leq x \leq 1 - \mu$ let 
+\begin{equation*}
+\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(1 - \mu)
+\end{equation*}
+be the linear interpolator between $h_q^{(0)}(\mu)$ and $h_q^{(0)}(1 - \mu)$.
+
+\begin{lemma}
+	\label{lem: lt_ub}
+	For any $0 \leq \mu \leq 1/2$ and $\mu \leq x \leq 1 - \mu$ and $t \geq 0$, 
+	\begin{equation*}
+	h_q^{(t)}(x) \leq \ell_{\mu}(x) + \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 }\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
+\end{lemma}
+
+Theorem \ref{lem: lt_ub} is a direct consequence of Theorem 1.2 of \cite{lovasz1990}. To state the latter, we introduce
+\begin{equation*}
+C_{\mu} = \max \set{\frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu}
+\end{equation*}
+\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
+	\label{thm: lovasz_simonovits_1993}
+	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
+	\begin{equation*}
+	h_q^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
 \end{theorem}
 
-Note that in \cite{montenegro2002} this theorem is stated with respect to $h^0$.
-However, in the subsequent proof it holds with respect to $h^m$, and it is observed that $h^m$ is decreasing in $m$.
-For our purposes it is more useful to state it with respect to $h^1$, as we have done.
-
-\begin{proof}[Proof of Lemma \ref{lem:  expansion_to_tv_distance}]
-	Consider the function $\phi_0(t, G): [s(G), 1/2] \to [0,1]$ defined by
-	\begin{equation}
-	\label{eqn: local_spread_blocking_conductance_function}
-	\phi_0(t; G) = 
-	\begin{cases}
-	\frac{1}{5}, ~~~~~~~~~~~~ t = s'(G) \\
-	\frac{1}{4} \Phi^2(t; G), ~ t \in \left(s'(G), 1/2\right] \\
-	\end{cases}
-	\end{equation}
-	\begin{lemma}
-		\label{lem: local_spread_blocking_conductance_function}
-		If $D_{\min} > 10$, $\phi_0$ is a blocking conductance function.
-	\end{lemma}
-	We take Lemma \ref{lem: local_spread_blocking_conductance_function} as given, and defer the proof until after the proof of Lemma \ref{lem: expansion_to_tv_distance}.
-
-	Lemma \ref{lem: local_spread_blocking_conductance_function} and Theorem \ref{thm: montenegro} together yield:
-	\begin{equation*}
-	\norm{\rhobf^t - \pibf}_{TV} \leq \max\left\{ \frac{1}{4}, h^1(s'(G)) +  \frac{70}{m}\left(5 + \int_{t = s'(G)}^{1/2} \frac{4}{t \Phi^2(t; G)}\right) \right\}
-	\end{equation*}
-
-	Then, $h^1(s'(G)) \leq 1/10$ follows exactly from the proof of Lemma \ref{lem: local_spread_G}, except now $\pibf(S) \leq s'(G)$ results in the sharper bound of $\qbf_u^{(1)}(S^c) \geq 9/10$ for every $u \in S$.
-\end{proof}
-\begin{proof}[Lemma \ref{lem: local_spread_blocking_conductance_function}]
-	The condition $D_{\min} > 10$ ensures that $s(G) \geq \pi_{\min}$.
-
-	It is known that $\frac{1}{4} \Phi^2(x;G)$ satisfies the exterior inequality for all $t \in (\pi_{\min}, 1/2]$.
-
-	For $t = s'(G)$ we will instead use the interior inequality.
-For any $S$ such that $\pibf(S) \leq s'(G)$, the following statement holds: for every $u \in S$, $\cut(u, S^c; G) \geq 9/10 \cdot \deg(u; G)$.
-	Fixing $\lambda = \pi(S)/2$, we have
-	\begin{align*}
-	\phi_{int}(S) & \geq \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{\lambda \cut(S \setminus B, S^c; G)}{\vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
-	& \geq  \min_{\substack{B \subset S \\ \pibf(B) \leq \lambda} } \frac{9 \lambda \sum_{u \in S \setminus B} \deg(u; G)}{10 \vol(V; G) \left[\lambda (1 - \lambda)\right]^2} \\
-	& \geq \frac{9\lambda^2}{20[\lambda^2(1 - \lambda)^2]} \geq \frac{9}{20}. 
-	\end{align*} 
-\end{proof}
+\begin{proof}[Proof of Lemma \ref{lem: lt_ub}]
+	Fix $0 \leq \mu \leq \frac{1}{2}$. We will show that for all $\mu \leq x \leq 1 - \mu$
+	\begin{equation}
+	\label{eqn: lt_ub_1}
+	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
+	\end{equation}
+	whence the claim follows by Theorem \ref{thm: lovasz_simonovits_1993}.
+
+	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
+	\begin{equation*}
+	h_q^{(0)}(x) \leq h_q^{(0)}(\mu) + (x - \mu)\frac{h_q^{(0)}(\mu)}{\mu}
+	\end{equation*}
+	by the concavity of $h_0$ along with Lemma \ref{lem: lovasz_simonovits_subdifferential}. Some basic algebra then yields
+	\begin{align*}
+	h_q^{(0)}(x) - \ell_{\mu}(x) & \leq h_q^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu)\right) + \frac{h_q^{(0)}(\mu)}{\mu}(x - \mu) \\
+	& =  \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(\mu) + \frac{h_q^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu) \\
+	& \leq \sqrt{x - \mu} \left(\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} \right)
+	\end{align*}
+	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and Lemma \ref{lem: lovasz_simonovits_subdifferential},  for $x \leq 1 - \mu$
+	\begin{equation*}
+	h_q^{(0)}(x) \leq h_q^{(0)}(1 - \mu) + (1 - x - \mu).
+	\end{equation*}
+	Similar manipulations to above give the upper bound
+	\begin{align*}
+	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
+	\end{align*}
+	and \eqref{eqn: lt_ub_1} follows.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: lovasz_simonovits_subdifferential}
+	The subdifferential $v(x)$ of $h_q^{(0)}(x)$ satisfies
+	\begin{equation*}
+	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}
+	\end{equation*}
+\end{lemma}
+
+\paragraph{Mixing over small sets.}
+
+\begin{lemma}
+	\label{lem: mixing_time_small_sets}
+	Let $0 \leq a \leq 1$, and $t \geq 1$ an integer. Then for any $x \leq as(G)$ or $x \geq 1 - as(G)$,
+	\begin{equation*}
+	h_v^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_1}
+	h_v^{(t)}(x) \leq q_v^{(m)}(U_{k - 1}) + q_v^{(m)}(u_k)
+	\end{equation}
+
+	We will rely on the key fact that for any $u \neq v, t \geq 1$,
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_2}
+	q_v^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
+	\end{equation}
+
+	On the other hand if $u = v$,
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_3}
+	q_v^{(m)}(u) \leq \frac{1}{2^t} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
+	\end{equation}
+	Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
+	\begin{equation*}
+	h_v^{(t)}(x) \leq \frac{1}{2^t} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
+	\end{equation*}
+	Since $x \leq a s(G)$, 
+	\begin{equation*}
+	\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
+	\end{equation*}
+
+	For any $0 \leq b \leq 1$, $x \geq 1 - b$ implies $h_v^{(t)}(x) \leq b$. Taking $b = a s(G)$, the claim is shown.
+\end{proof}
+
+\paragraph{Proof of Proposition \ref{prop: tv_mixing_time}.}
+For any $A \subseteq V$ and any integer $t \geq 0$,
+\begin{equation*}
+\max \set{h_v^{(t)}(\pi(A)), h_v^{(t)}(1 - \pi(A))} \geq \abs{q_v^{(t)}(A) - \pi(A)}
+\end{equation*}
+and taking max over both sides, we have
+\begin{equation*}
+\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{TV}.
+\end{equation*}
+
+Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_v^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Proposition \ref{lem: lt_ub},
+\begin{align*}
+h_v^{(t + 3)}(x) & = h_q^{(t)}(x) \\
+& \leq \max \set{h_q^{(0)}(\mu), h_q^{(0)}(1 - \mu) }  + \left(\frac{1}{1 - 2 \mu} + \frac{1}{2\mu}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t\\
+& \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2a s(G)} + \frac{1}{2 a s(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{align*}
+where the last inequality comes from application of Lemma \ref{lem: mixing_time_small_sets} to $h_q^{(t)} = h_v^{(t + 3)}$.
+
+For $x \leq \mu$ or $x \geq 1 - \mu$,
+\begin{equation*}
+h_v^{(t + 3)}(x) \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}}
+\end{equation*}
+and the proof is complete.
 
@@
 \end{equation*}
-and the \emph{$\Pbb$-(continuous) conductance profile} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \piwt_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$.
+and the \emph{$\Pbb$-(continuous) conductance} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\Pbb,r}(\Sset)
+\end{equation*}
+where $\Sset^c = \Csig \setminus \Sset$, and we note this definition agrees with \eqref{eqn: continuous_conductance}.
 
@@
 	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the continuous conductance function of the $r$-ball walk satisfies
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
 	\begin{equation*}
@@
 	\end{equation*}
-	for any $0 < t \leq \frac{1}{2}$. 
 \end{proposition}
@@
 \begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\nu,r}(\Sset) \leq t} } \widetilde{\Phi}_{\nu,r}(\Sset).
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r}(t) := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
 \end{equation*}
@@
 	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance function of the $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r}(t) > \frac{r}{2^{12} D L \sqrt{d}}.
-	\end{equation*}
-	for any $0 < t \leq 1/2$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{12} D L \sqrt{d}}.
+	\end{equation*}
 \end{lemma}
@@
 \end{align*}
-Noting that $\widetilde{\Phi}_{\nu,r}(\Sset) = \widetilde{\Phi}_{\nu,r}(\Sset^c)$, and as $0 < \piwt_{\Pbb,r}(\Sset) < 1/2$, one of $0 < \pi_{\nu,r}(\Sset) \leq 1/2$ or $0 < \pi_{\nu,r}(\Sset^c) \leq 1/2$ must hold, the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
+and the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
 
 \subsection{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-
-As is standard, the proof of a lower bound on the conductance profile relies on an isoperimetric inequality.
+\label{sec: proof_of_lemma_continuous_conductance}
+
+As is standard, the proof of a lower bound on the conductance relies on an isoperimetric inequality.
 
@@
 The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even in the convex setting, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among others.
-Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting implied  Assumption \ref{asmp: embedding} is not difficult.
+Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting given by  Assumption \ref{asmp: embedding} is not difficult.
 
@@
 
-\subsection{Graph conductance profile and local spread.}
-
-Let $\widetilde{G}_{n,r} := G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denote the subgraph induced by $\Csig[\Xbf]$.$\widetilde{{\Phi}}_{n,r}(t)$, the graph conductance profile over $\widetilde{G}_{n,r}$ is defined in \eqref{eqn: graph_conductance_profile}.
+\subsection{Graph conductance and local spread.}
+\label{sec: graph_conductance_and_local_spread}
+
+Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes  the subgraph induced by $\Csig[\Xbf]$.
+$\widetilde{{\Phi}}_{n,r}$, the graph conductance over $\widetilde{G}_{n,r}$ is defined in \eqref{eqn: local_spread_and_conductance}.
 Write $\piminwt := \min_{u \in \Csig[\Xbf]} \piwt_{n,r}(u)$.
@@
 	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, with probability one the following lower bound holds on the graph conductance function:
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}} \tag{$0 < t \leq \frac{1}{2}$}
+Then, with probability one the following lower bound holds on the graph conductance:
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
 	\end{equation*}
@@
 \begin{proof}
-	Observing that
-	\begin{equation*}
-	\Phi(S;G) \geq \sum_{u \in S} q^{(1)}(u,S^c) \frac{\deg(u;G)}{\vol(S)},
-	\end{equation*}
-	the claim follows by Lemma \ref{lem: local_spread_G}.
+	The claim follows by simple manipulations:
+	\begin{align*}
+	\Phi(S;G) & \geq \sum_{u \in S} \frac{\cut(u, S^c; G)}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
+	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
+	\end{align*}
 \end{proof}
@@
 \subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+\label{sec: proof_of_lemma_graph_conductance}
 
@@
 	\end{equation*}
-	where the convergence occurs as $n \to \infty$. On the other hand, by hyptohesis
+	where the convergence occurs as $n \to \infty$. On the other hand, by hypothesis
 	\begin{equation*}
@@
 \subsection{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
-Lemma \ref{lem: expansion_to_tv_distance} implies
-\begin{equation}
-\label{eqn: expansion_to_tv_distance_1}
-\tau_1(\widetilde{G}_{n,r}) \leq 490 \cdot \left(\frac{20}{9} + \int_{s'(\widetilde{G}_{n,r})}^{1/2} \frac{4}{t \widetilde{\Phi}_{n,r}^2(t)} \dt \right)
-\end{equation}
-where we recall $s'(G) = \frac{s(G)}{9}$.
-
-By Lemmas \ref{lem: graph_conductance_profile_lb} and \ref{lem: local_spread_lb} for sufficiently large $n$, and for any $0 < t \leq \frac{1}{2}$
-\begin{equation*}
-s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20 \Lambda_{\sigma}}, \quad \widetilde{\Phi}_{n,r}(t) > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
-\end{equation*}
-which along with \eqref{eqn: expansion_to_tv_distance_1} and Lemma \ref{lem: tv_mixing_to_pointwise_mixing1} implies the desired result.
+\label{sec: proof_of_theorem_mixing_time}
+
+Since $r$ is fixed, $\min_{u \in V} \deg(u; \widetilde{G}_{n,r}) \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
+\begin{equation*}
+\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2}{\widetilde{\Phi}_{n,r}^2} \log\left(\frac{1440}{s(\widetilde{G}_{n,r})}\right) \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
+\end{equation*}
+and the claim follows from Proposition \ref{prop: graph_conductance_profile_lb} and Lemma \ref{lem: local_spread_lb}.
 
@@
 \label{sec: concentration}
-Given a symmetric kernel function $k: \mathcal{X}^m \to \Reals$, and data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$m$ $U$ statistic} to be 
-\begin{equation*}
-U := \frac{1}{ {n \choose m} } \sum_{1 \leq i_1 < \ldots < i_m \leq n} k(x_{i_1},\ldots,x_{i_m})
-\end{equation*}
-
-For Lemmas \ref{lem: bounded_difference}, let $X_1, \ldots, X_n \in \mathcal{X}$ be independent and identically distributed.
-We will additionally assume the order-$m$ kernel function $k$ satisfies the boundedness property $\sup_{x_1, \ldots, x_m} \abs{k(x_1, \ldots, x_m)} \leq 1$.
+
+Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$ statistic} to be
+\begin{equation*}
+U := \frac{1}{ {n \choose 2} } \sum_{1 \leq i < j \leq n} K(x_i,x_j).
+\end{equation*}
 
@@
 	\begin{align*}
-	U & \leq \mathbb{E}U + \sqrt{\frac{m \log(1 / \delta)}{2n} }, \\
-	U & \geq \mathbb{E}U - \sqrt{\frac{m \log(1 / \delta)}{2n} }
+	U & \leq \mathbb{E}U + \sqrt{\frac{\log(1 / \delta)}{n} }, \\
+	U & \geq \mathbb{E}U - \sqrt{\frac{\log(1 / \delta)}{n} }
 	\end{align*}
@@
 
-We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
+We will employ a sharper inequality to bound the sum of independent Bernoulli random variables.
 \begin{lemma}
 	\label{lem: multiplicative_Hoeffding}
-	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
+	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \sum_{i = 1}^n \Ebb(X_i)$. Then,
 	\begin{align*}
@@
 
-We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemma \ref{lem: multiplicative_Hoeffding}. Let
+We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}. Let
 \begin{alignat*}{2}
@@
 \degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
-\degmin & := \min_{u \in \Csig{\Xbf}} \deg(u; G_{n,r}).
+\degmin & := \min_{u \in \Xbf} \deg(u; G_{n,r}).
 \end{alignat*}
@@
 	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
-	\frac{\degmin}{n} & \geq  (1 - \epsilon)\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\frac{\degmin}{n} & \geq \frac{6}{25}(1 - \epsilon)\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
 	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
@@
 	Let $\epsilon \geq 0$, $v \in A^g$, $\alpha \leq \frac{\Psi(A; G)}{9}$, and $\vol_0 \in [1 - c,1 + c] \vol(A;G)$ for $0 < c < 1$.
-Consider taking sweep cuts of the \textcolor{red}{approximate \pprspace vector} $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
+Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
 	\begin{equation*}
@@
 
-Observe that by Theorem \ref{thm: inverse_mixing_time_lower_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}(\theta)}{9}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
-Moreover, i) we restrict $v \in \Csig[\Xbf]^g$; ii) the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$; iii) by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$, and iv) the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$.
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}(\theta)}{9}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Moreover,
+\begin{enumerate}[(i)]
+	\item we restrict $v \in \Csig[\Xbf]^g$
+	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$
+	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
+	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$.
+\end{enumerate}
+
 All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq \mathbf{\Psi}(\theta)/10$, the following bounds hold with probability tending to 1 as $n \to \infty$:
@@
 \begin{align*}
-\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) & \geq \abs{\widehat{C} \setminus \Csig[\Xbf]} \min_{x \in \Xbf} \{\deg_{n,r}(x)\} \\
-\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) & \geq \abs{\Csig[\Xbf] \setminus \widehat{C}} \min_{x \in \Csig[\Xbf]} \{\deg_{n,r}(x)\},~ \textrm{and} \\
-\vol_{n,r}(\Csig[\Xbf]) & \leq \abs{\Csig[\Xbf]} \max_{x \in \Csig[\Xbf]} \set{\deg_{n,r}(x)}
+\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) & \geq \abs{\widehat{C} \setminus \Csig[\Xbf]} \degmin \\
+\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) & \geq \abs{\Csig[\Xbf] \setminus \widehat{C}} \degminwt,~ \textrm{and} \\
+\vol_{n,r}(\Csig[\Xbf]) & \leq \abs{\Csig[\Xbf]} \max_{x \in \Csig[\Xbf]} \degmax
 \end{align*}
@@
 We begin with some notation.
-Let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and random walk matrices for the induced subgraph $G_{n,r}(\Csig[\Xbf]) = \widetilde{G}_{n,r}$, with vertex set $\widetilde{V} = \Csig[\Xbf]$ and edge set $\widetilde{E} = \set{(u,v) \in G_{n,r}: u,v \in \Csig[\Xbf]}$.
-Consider the function $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$
+Let $\Dbf$ and $\Wbf$ be the degree and (lazy) random walk matrices for the neighborhood graph $G_{n,r}$.
+Similarly, let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and (lazy) random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
+Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
 \begin{equation*}
@@
 \end{equation*}
-(Note $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
+(Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
 
@@
 	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
-(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \widetilde{V}$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
+(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
 
@@
 We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$.
-First, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$.
-As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-Second, for any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$, and any $t \geq 1$,
+	\begin{enumerate}
+		\item Since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
+		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$, and any $t \geq 1$,
 		\begin{align}
@@
 		where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
+	\end{enumerate}
 
@@
 	\begin{align*}
-	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
+	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}^t \right)(u)  \nonumber \\
+	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
+	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
 	& \leq \frac{\norm{\ell}_1 }{\degminwt}.
@@
 	\begin{align*}
-	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
+	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
 	& \leq \frac{\norm{s}_1}{\degminpr}
@@
 
-Observe that by Theorem \ref{thm: inverse_mixing_time_lower_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}}{9}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}}{9}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
 As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
@@
 	\begin{align*}
-	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
-	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
-	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf_n^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf_n^{T - t - 1} \right)(u)\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u) \\
-	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u) \\
-	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u) \\
+	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
+	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
+	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
+	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
+	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
 	& = \pbf_s(u)
@@
 	\begin{align*}
-	\norm{s_t}_1 & = \norm{q_t (\Wbf_n \widetilde{\mathbf{I}}_n^c)}_1 \\
-	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n^c)(u, u') \\
-	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1((u,u') \in G_{n,r}) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
-	& = \norm{q_t (\Ibf{n} - \Dbf_n^{-1} \widetilde{\Dbf}_n)}_1 = \norm{\ell_t}_1.
+	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{\mathbf{I}}^c)}_1 \\
+	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{\mathbf{I}}^c)(u, u') \\
+	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf)_{uu}} \1((u,u') \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf)_{uu} - (\widetilde{\Dbf})_{uu} \right)}{(\Dbf)_{uu}} \\
+	& = \norm{q_t (\Ibf{} - \Dbf^{-1} \widetilde{\Dbf})}_1 = \norm{\ell_t}_1.
 	\end{align*}
@@
 \section{Additional Experiments}
-
-\begin{figure}
-	\centering
-	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth,scale = .5]{example3plots/true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth,scale = .5]{example3plots/ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth,scale = .5]{example3plots/conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth,scale = .5]{example3plots/density_cluster}
-			\caption{}
-		\end{subfigure}
-	\caption{}
-	\end{adjustbox}
-\end{figure}
-
-\section{\textcolor{red}{OLD STUFF}}
-
-\subsection{Volume estimates}
-We will fix $\Aset \subset \Rd$ to be an arbitrary set.
-To simplify expressions, for the $\sigma$-expansion $\Asig$, we will write the set difference between $\Asig$ and the $(\sigma + r)$-expansion $\Aset_{\sigma + r}$ as
-\begin{equation*}
-\Asigr := \set{x: 0 < \dist(x, \Asig) \leq r},
-\end{equation*}
-where as a reminder $\dist(x, \Aset) = \min_{x' \in \Aset} \norm{x - x'}$.
-
-\paragraph{Lemma \ref{lem: interior_of_expansion_sets}.}
-
-We will repeatedly employ Lemma \ref{lem: expansion_sets} and Lemma \ref{lem: Taylor_series} in tandem.
-As a first example, in Lemma \ref{lem: interior_of_expansion_sets}, we bound the ratio of $\nu(\Aset)$ to $\nu(\Aset_{-\delta})$, where we write $\partial \Aset$ for the boundary of $\Aset$, and for $\delta > 0$ we let
-\begin{equation*}
-\Aset_{-\delta} : = \set{x \in \Aset: \dist(x, \partial \Aset) > \delta}.
-\end{equation*}
-
-This will be useful when we bound $\vol(\Csig)$.
-
-\begin{lemma}
-	\label{lem: interior_of_expansion_sets}
-	For $\sigma$, $\Asig$ as in Lemma \ref{lem: expansion_sets}, let $r > 0$ satisfy $r \leq \sigma/4d$. Then,
-	\begin{equation*}
-	\frac{\nu(\Asig)}{\nu(\Aset_{\sigma - r})} \leq 2.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $q = \sigma - r$. Then,
-	\begin{align*}
-	\nu(\Asig) & = \nu(\Aset_{q + \sigma - q}) = \nu(\Aset_q + (\sigma - q)B ) \\
-	& \leq \nu(\Aset_q + \frac{(\sigma - q)}{q} \Aset_q) = \left(1 + \frac{\sigma - q}{q}\right)^d \nu(\Aset_q)
-	\end{align*}
-	where the inequality follows from Lemma \ref{lem: expansion_sets}.
-Of course, $\sigma - q = r$, and $\frac{r}{q} \leq \frac{1}{2d}$ for $r \leq \frac{1}{4d}$.
-The claim then follows from Lemma \ref{lem: Taylor_series}.
-\end{proof}
-
-\subsection{Proof of Lemma \ref{lem: setup}}
-
-\begin{proof}
-	We will write $\Wbf_n = \Dbf_n \Abf_n^{-1}$ for the transition probability matrix over $G_{n,r}$, and let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$.
-
-	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
-	\begin{align*}
-	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
-	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
-	\end{align*}
-	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.
-
-	Roughly, the proof of Lemma \ref{lem: setup} will unfold in four steps.
-The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).
-We briefly summarize the approach before diving into the formal proof:
-
-	\begin{enumerate}
-		\item For $u \in \Cset[\Xbf]$, we use the results of \cite{zhu2013} to produce the lower bound 
-		\begin{equation*}
-		\pbf(u) \geq \frac{4}{5}\widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
-		\end{equation*}
-		where 
-		\begin{equation*}
-		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
-		\end{equation*}
-		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.
-
-		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $\Xbf \setminus \Csig[\Xbf]$.
-Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
-This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
-		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
-		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$.
-Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$.
-Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$.
-This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
-	\end{enumerate}
-
-	\paragraph{Step 1}
-	We will begin by restating some results of \cite{zhu2013}.
-
-	For seed node $v$, we write
-	\begin{align} \label{eqn: page_rank_body}
-	\widetilde{\pbf}_v & = \alpha e_v + (1 - \alpha) \widetilde{\pbf}_v \widetilde{\Wbf}_n \\
-	& = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(e_v \widetilde{\Wbf}_n^t \right)
-	\end{align}
-
-	From Lemma 3.1 of \cite{zhu2013} we have that there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ for all $v \in \Csig[\Xbf]^g$, $u \in \Csig[\Xbf]$
-
-	\begin{align} \label{eqn: zhu_body}
-	p_u & \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u) \nonumber \\
-	||\ell||_1 & \leq \frac{2 \widetilde{\Phi}_{n,r}}{\alpha}
-	\end{align}
-	where $\widetilde{\pbf}_v = (\widetilde{\pbf}_v(u))$ and likewise for $\widetilde{\pbf}_{\ell} = (\widetilde{\pbf}_{\ell}(u))$.
-(This will be the only time we need to restrict ourselves to this 'good set'.)
-
-	Moreover if, as we have specified, $\alpha \leq \widetilde{\Psi}_{n,r}/9$, Lemma 3.2 of \cite{zhu2013} yields a lower bound on $\widetilde{p}$
-	\begin{equation} \label{eqn: page_rank_mixes}
-	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u).
-	\end{equation}
-
-	\paragraph{Step 2}
-
-	We turn to upper bounding $\widetilde{\pbf}_{\ell}(u)$. For any $u \in \Cset[\Xbf]$, we have
-
-	\begin{align} \label{eqn: leakage_page_rank_body}
-	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
-	& = \|\ell\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& \overset{\text{(i)}}{=} \|\ell\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
-	& \overset{\text{(ii)}}{\leq} \|\ell\|_1 \frac{1}{\widetilde{D}_{\min}} 
-	\end{align}
-
-	where we use $\left(\ell \widetilde{\Wbf}_n^t \right)(u)$ to denote $\ell \widetilde{\Wbf}_n^te_u$.
-
-	$\text{(i)}$ follows from the fact that since $r < \sigma$, $\cut(\Cset[\Xbf], G_{n,r} / \Csig[\Xbf]; G_{n,r}) = 0$. Therefore $(\Dbf_n^{-1})_{uu} (\widetilde{\Dbf}_n)_{uu} = 1$, and as a result
-	\begin{equation*}
-	(\ell \widetilde{\Wbf}_n^0)(u) = \ell(u) = 0.
-	\end{equation*}
-	To see $\text{(ii)}$, let $q = \frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^{t-1}$. Then
-
-	\begin{align*}
-	\left(\frac{\ell}{\|\ell\|_1}  \widetilde{\Wbf}_n^t \right)(u) & = \left(q \widetilde{\Wbf}_n \right)(u) \\
-	& \leq \|q\|_1 \|\widetilde{\Wbf}_{\cdot u}\|_{\infty} \\
-	& \overset{\text{(iii)}}{\leq} \frac{1}{\widetilde{D}_{\min}}.
-	\end{align*}
-	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}_n$.
-$\text{(iii)}$ then follows from the fact that any vertex in $\Cset[\Xbf]$ is connected only to vertices in $\Csig[\Xbf]$, and therefore every entry of $\widetilde{\Wbf}_{\cdot u}$ is either $0$ or at most $1 / \widetilde{D}_{\min}$.
-
-	Combined, (\ref{eqn: leakage_page_rank_body}), (\ref{eqn: page_rank_mixes}), and \eqref{eqn: zhu_body} imply
-	\begin{equation*}
-	p_v(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - 18\frac{ \Phi_{n,r}(\Csig[\Xbf])}{\widetilde{D}_{\min} \alpha}.
-	\end{equation*}
-	for any $v \in \Csig[\Xbf]$.
-
-	\paragraph{Step 3}
-	To get the corresponding upper bound on $p_v(u')$, we will use the soakage vectors $s$ and $s_t$.
-We will first argue that $s$ is a worse starting distribution -- meaning it puts uniformly more mass outside the cluster -- than simply starting at $v$.
-
-	\begin{lemma} \label{lem: gained mass is soaked_body}
-		For all $u' \notin \Csig[\Xbf]$,
-		\begin{equation}
-		\pbf_v(u') \leq \pbf_{s}(u').
-		\end{equation}
-	\end{lemma}
-
-	\begin{proof}
-
-		We have
-		\begin{align*}
-		\pbf_v(u') & = \alpha \sum_{T=0}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u)\\
-		& \overset{(i)}{=} \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T (e_v \Wbf_n^T)(u')
-		\end{align*}
-
-		where $(i)$ follows from $v \in \Csig$ , $u \not\in \Csig$ and therefore $e_v(u) = 0$.
-
-		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
-		\begin{lemma}
-
-			Let $G = (V,E)$ be a graph, with associated random walk matrix $W$.
-
-			For any $T \geq 1$, $q$ vector, $S \subset V$, and $s_t = s_t(S^c,q)$
-			\begin{equation}
-			qW^T = \sum_{t = 0}^{T - 1} s_t W^{T - t - 1} + q(W I_S)^T
-			\end{equation}
-		\end{lemma}
-		We prove Lemma \ref{lem: sum_of_soakages} after completing the proof of Lemma \ref{lem: gained mass is soaked_body}.
-
-		Now, along with the fact $u \not\in \Csig$, we have
-
-		\begin{equation*}
-		\left(e_v \Wbf_n^T \right)(u') = \sum_{t = 0}^{T - 1} \left(s_t \Wbf_n^{T - t - 1} \right)(u')
-		\end{equation*}
-
-		and so
-
-		\begin{align*}
-		\pbf_v(u) & = \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u') \\
-		& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u')\\
-		& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u') \\
-		& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u') \\
-		& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u') \\
-		& = \pbf_s(u')
-		\end{align*}
-	\end{proof}
-
-	\begin{proof}[Proof of Lemma \ref{lem: sum_of_soakages}]
-		Proceed by induction. When $T = 1$,
-
-		\begin{align*}
-		qW & = q(WI_S) + q(WI_{S^c}) \\
-		& = q(W I_S)^T + s_0 
-		\end{align*}
-
-		Assume true for $T_0$. For $T = T_0 + 1$,
-
-		\begin{align*}
-		qW^T & = qW^{T_0}W \\
-		& = \left\{ \sum_{t = 0}^{T_0 - 1} s_t W^{T_0 - 1 - t} + q(WI_S)^{T_0} \right\} W \\
-		& =  \sum_{t = 0}^{T_0 - 1} s_t W^{T - 1 - t} + q(WI_S)^{T_0}(WI_S + WI_{S^c}) \\
-		& =  \sum_{t = 0}^{T - 1} s_t W^{T - 1 - t} + q(WI_S)^{T}
-		\end{align*}
-	\end{proof}
-
-	\paragraph{Step 4}
-
-	Just as we upper bounded the probability mass $\widetilde{\pbf}_{\ell}$ could assign to any one vertex, we can upper bound
-
-	\begin{align} \label{eqn: soakage_page_rank_body}
-	\pbf_{s}(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t \right)(u') \nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1} {\Wbf}_n^t \right)(u')\nonumber \\
-	& = \|s\|_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\|s\|_1}  {\Wbf}_n^t \right)(u')\nonumber \\
-	& \leq \|s\|_1 \frac{1}{\widetilde{D}_{\min}}.
-	\end{align}
-
-	Finally, letting $q_t = e_v (\Wbf_n \widetilde{\mathbf{I}}_n)^t$ for ease of notation, we have
-	\begin{align*}
-	\|s_t\|_1 & = \|q_t (\Wbf_n \widetilde{\mathbf{I}}_n)\|_1 \\
-	& = \sum_{u' \in \Xbf} \sum_{u \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n)(u, u')\\
-	& = \sum_{u' \in \Xbf / \Csig[\Xbf]} \sum_{u \in \Csig[\Xbf]} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1(e_{u,u'} \in G_{n,r}) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
-	& = \|q_t (I - \Dbf_n^{-1} \widetilde{\Dbf}_n)\|_1 = \|\ell_t\|_1.
-	\end{align*}
-
-	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
-\end{proof}
-
-\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-
-We note that by Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, 
-\begin{equation*}
-\kappa_2(\Cset) \geq \frac{\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])}.
-\end{equation*}
-As a result Lemma \ref{lem: setup} implies
-\begin{align}
-\label{eqn: theorem_4_1}
-p_u & \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~ (u \in \Cset[\Xbf]) \nonumber \\
-p_{u'} & \leq \frac{18 \kappa_2(\Cset)}{\widetilde{D}_{\min}} ~~~~~~~~~~~~~~~~~~~~~ (u' \in \Cset'[\Xbf])
-\end{align}
-
-We turn to bounding $\widetilde{\pi}_{n,r}(u)$. Clearly,
-\begin{align*}
-\widetilde{\pi}_{n,r}(u) & \geq \frac{\widetilde{D}_{\min}}{\widetilde{\vol}_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{\widetilde{D}_{\min}}{\wn \widetilde{D}_{\max}}.
-\end{align*}
-Application of Lemma \ref{lem: ball_bounds_in_probability} then yields
-\begin{equation}
-\label{eqn: theorem_4_2}
-\widetilde{\pi}_{n,r}(u) \geq 8 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
-\end{equation}
-as well as
-\begin{equation}
-\label{eqn: theorem_4_3}
-\frac{1}{\widetilde{D}_{\min}} \leq \frac{2}{\nu_d r^d \lambda_{\sigma}}
-\end{equation}
-with probability tending to $1$ as $n \to \infty$, for all $u \in \Cset[\Xbf]$ (indeed, all $u \in \Csig[\Xbf]$.)
-
-Combining \eqref{eqn: theorem_4_1}, \eqref{eqn: theorem_4_2} and \eqref{eqn: theorem_4_3}, along with the requirement on $\kappa_2(\Cset)$ given by \eqref{eqn: kappa2_ub}, we have
-\begin{align*}
-p_u & \geq 3/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2} \\
-p_{u'} & \leq 1/5 \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}
-\end{align*}
-for any $u \in \Cset$, $u' \in \Cset'$.
-As a result, if $\pi_0 \in (2/5, 3/5)\cdot \frac{\lambda_{\sigma}}{\nu(\Csig) \Lambda_{\sigma}^2}$, as $n \to \infty$ with probability tending to one any sweep cut of the form of \eqref{eqn: sweep_cuts}, including the output set $\widehat{C}$, will successfully recover $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
 

### 2019-05-20 neurips/local_spectral_density_clustering_monday.tex
added local spectral clustering changes for monday before neurips

--- 2019-05-14 arxiv/arxiv_local_density_clustering.tex
@@
-%%%%%%%% Local Spectral Clustering of Density Upper Level Sets %%%%%%%%%%%%%%%%%
+\documentclass{article}
 
-\documentclass{article}
+% if you need to pass options to natbib, use, e.g.:
+%     \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading neurips_2019
+
+% ready for submission
+% \usepackage{neurips_2019}
+
+% to compile a preprint version, e.g., for submission to arXiv, add add the
+% [preprint] option:
+%     \usepackage[preprint]{neurips_2019}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+%     \usepackage[final]{neurips_2019}
+
+\usepackage{neurips_2019}
+
+% to avoid loading the natbib package, add option nonatbib:
+%     \usepackage[nonatbib]{neurips_2019}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
 \usepackage{microtype}
@@
 \usepackage{bm}
-\usepackage{fullpage}
 \usepackage{mathtools}
 
-\usepackage[square,sort,comma,numbers]{natbib}
-\renewcommand{\bibname}{REFERENCES}
-\renewcommand{\bibsection}{\subsubsection*{\bibname}}
-
-% Left and right equations
-\makeatletter
-\newcommand{\leqnomode}{\tagsleft@true\let\veqno\@@leqno}
-\newcommand{\reqnomode}{\tagsleft@false\let\veqno\@@eqno}
-\makeatother
-
-% Absolute value
 \DeclarePairedDelimiter\abs{\lvert}{\rvert}
@@
   which extract clusters using locally-biased random walks around a user-specified
-seed node.  Several authors have shown that local methods, such as personalized
-PageRank (PPR), have worst-case guarantees for certain graph-based measures of
-cluster quality.  In contrast to existing works, we analyze PPR in a traditional
+  seed node.  In contrast to existing works, we analyze PPR in a traditional
   statistical learning setup, where we obtain samples from an unknown
   distribution, and aim to identify connected regions of high-density (density
-clusters).  We introduce two natural criteria for cluster quality, and derive
-bounds for these criteria when evaluated on empirical analogues of density
-clusters. Moreover, we prove that PPR, run on a neighborhood graph, extracts
-sufficiently salient density clusters. Finally, we provide empirical support of our theory.
+  clusters).  We prove that PPR, run on a neighborhood graph, extracts
+  sufficiently salient density clusters, and provide empirical support of our theory.
 \end{abstract}
@@
 
-\subsection{Graph Connectivity Criteria}
-
-Here we define a pair of criteria that reflect the quality of a cluster with
-respect to $G=(V,E,w)$.  There are many graph-based measures of cluster quality  
-that one could consider; see, e.g., \citep{yang2015,fortunato2010} for 
-an overview.  The pair of criteria that we focus on are (arguably) quite
-natural, and moreover, they play a fundamental role in our analysis 
-of the PPR algorithm.  Our two criteria capture the \emph{external} and
-\emph{internal} connectivity of a subset $S \subseteq V$, denoted $\Phi(S; G)$
-and $\Psi(S; G)$, respectively, and defined below in turn.
-
-\paragraph{External Connectivity: Normalized Cut}
-
-For subsets $S,S' \subseteq V$, we define the cut, degree, and volume functionals as usual,
-$$
-\cut(S, S'; G) = \sum_{u \in S} \sum_{v \in S'} w_{uv}, \quad \deg(u; G) = \sum_{v \in V} w_{uv}, \quad  \vol(S; G) = \sum_{u \in S} \deg(u;G).
-$$
-As our notion of external connectivity, we use the \emph{normalized cut}  
-of $S$, defined as 
-\begin{equation}
-\label{eqn: norm_cut}
-\Phi(S; G) = \frac{\cut(S; G)}{\min\{\vol(S; G), \vol(S^c; G)\}},
-\end{equation} 
-where we abbreviate $\cut(S; G) = \cut(S; S^c; G)$.
-
-\paragraph{Internal Connectivity: Inverse Mixing Time}
-
-For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
-$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Abf_S,\Dbf_S$
-be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
-(lazy) random walk matrix as usual, $\Wbf = \frac{\Dbf_S^{-1} \Abf_S + \Ibf{\abs{S} \times \abs{S}}}{2}$, and for $v \in V$,
-write 
-$$
-q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
-$$
-for the $t$-step transition probability of a random walk over $G[S]$
-originating at $v$.\footnote{Given a starting node $v$ and and a random walk
-  defined by transition probability matrix $\mathbf{P}$, the notation $e_v
-  \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
-  steps.}   Also write \smash{$\pi = (\pi(u))_{u \in S}$}
-for the stationary distribution of this random walk.  (Given the definition of 
-$\Wbf_S$, it is well-known that a unique stationary distribution exists and is given by
-\smash{$\pi(u) = \deg(u; G[S])/\vol(S; G[S])$}.)
-
-Our internal connectivity parameter will capture the time it takes for the
-random walk over $G[S]$ to mix (approach the stationary distribution)
-uniformly over $S$.  For this, we first define the \emph{relative pointwise mixing
-  time} of $G[S]$ as 
-$$
-\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)
-	}{\pi(u)} \leq \frac{1}{4}, 
-	\; \text{for $u,v \in V$}}. 
-$$
-%where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
-%\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. 
-% RJT: I got rid of the notational dependence on \qbf, because these quantities
-% are in turn just defined in terms of the induced subgraph G[S]
-% AJG: RESOLVED
-Now our internal connectivity parameter is simply the inverse mixing time, 
-\begin{equation}
-\label{eqn: inv_mixing_time}
-\Psi(S; G) = \frac{1}{\tau_{\infty}(G[S])}.
-\end{equation}
-
-If $S$ has normalized cut no greater than $\Phi$, and inverse mixing time no
-less than $\Psi$, we call it as a \emph{$(\Phi,\Psi)$-cluster}. Both
-local \citep{zhu2013} and global \citep{kannan04} spectral algorithms have been
-shown to output clusters (or partitions) which approximate the optimal $(\Phi,
-\Psi)$-cluster (or partition) for a given graph $G$.\footnote{In the case of
-  \citep{kannan04}, the internal connectivity parameter $\phi$ is actually the
-  conductance, i.e., the minimum normalized cut within the subgraph $G[S]$. See
-  Theorem 3.1 in their paper for details; however, note that $\phi^2 /
-  \log(\vol(S)) \leq O(\Psi)$, and so the lower bound on $\phi$ translates to a
-  lower bound on $\Psi$.}
-
 \subsection{PPR on a Neighborhood Graph}
@@
 \end{equation}
-Having computed sweep cuts over a range \smash{$\beta \in  
+
+Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
 (\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
 \smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}
-we output a cluster \smash{$\Cest = S_{\beta^*}$}, based on the sweep cut
-$S_{\beta^*}$ that minimizes the normalized cut \smash{$\Phi(S_{\beta^*};
-  G_{n,r})$} as defined in \eqref{eqn: norm_cut}. For concreteness, we summarize
-this procedure in Algorithm \ref{alg: ppr}.
+algorithms, see, e.g., \citep{zhu2013}.}, we then  output a cluster estimate $\widehat{C} = S_{\beta^*}$ to have minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$, where for $S \cup S^c = G_{n,r}$, $\cut(S;G_{n,r}) := |\set{(u,v) \in E : u \in S, v \in S^c}|$, $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and
+\begin{equation}
+\label{eqn: normalized_cut}
+\Phi(S; G_{n,r}) := \frac{\cut(S;G_{n,r})}{\min \set{\vol(S; G_{n,r}), \vol(S^c; G_{n,r})}}.
+\end{equation}
+For concreteness, we summarize this procedure in Algorithm \ref{alg: ppr}.
 
@@
 \begin{enumerate}
-\item In Section \ref{sec: cluster_quality_bounds}, we derive in Theorem
-  \ref{thm: conductance_upper_bound} an upper bound on the normalized cut of a  
-  (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
-  conditions (precluding clusters that are arbitrarily thin).
+	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions.
+We formalize a measure of difficulty based on these geometric conditions, and show that when properly initialized, the misclassification error of Algorithm \ref{alg: ppr} is upper bounded by this difficulty measure.
 
-\item Under additional geometric conditions, which exclude sets with large diameter or small bottleneck, we derive in Theorem
-  \ref{thm: mixing_time_upper_bound} a lower bound on the
-  inverse mixing time of a random walk over $\Csig[\Xbf]$.
+	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
 
-\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
-  Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} that the bounds on the cluster quality criteria established in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    mixing_time_upper_bound} have algorithmic consequences for \ppr. 
-  Properly initialized, Algorithm \ref{alg: ppr} has low misclassification error with respect to a small enlargement of the set $\Cset$, and if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-Corollary \ref{cor: appr} establishes that these statements hold also with respect to an approximate form of \ppr, which can be efficiently computed.
+	\item Corollary \ref{cor: appr} establishes that these statements hold also with respect to an approximate form of \ppr, which can be efficiently computed.
+
+	\item In \textcolor{red}{Section 3}, we detail some of the main technical machinery required to prove our main results, highlighting the part various geometric quantities play in the ultimate difficulty of the clustering problem.
 
@@
 In addition to the background given above, a few related lines of work are worth
-highlighting.
-Global spectral clustering methods were first developed in the
-context of graph partitioning \citep{fiedler1973,donath1973} and their
-performance is well-understood in this context (see, e.g.,
-\citep{tolliver2006,luxburg2007}).  In a similar vein, several recent works
-\citep{mcsherry2001,rohe2011,kamalika2012,balakrishnan2011,lei2015,abbe2018} 
-have studied the efficacy of spectral methods in successfully recovering the
-community structure in the stochastic block model and variants.
-
-Building on earlier work of
+highlighting. Building on earlier work of
 \citep{koltchinskii2000}, \citep{vonluxburg2008,hein2005} studied the limiting behaviour of spectral clustering
@@
 
-Perhaps most similar to our results are the works
+More similar to our results are the works
 \citep{vempala2004,shi2009,schiebinger2015}, who study the consistency of
@@
 
-\section{Cluster Quality Criteria Bounds for Density Clusters}  
-\label{sec: cluster_quality_bounds}
+\section{Estimation of Well-Conditioned Density Clusters.}
+\label{sec: consistent_cluster_estimation_with_ppr}
 
 \subsection{Geometric Conditions on Density Clusters}
+\label{subsec: geometric_conditions}
 
-In order to provide meaningful bounds on the normalized cut and inverse mixing
-time of an empirical density cluster, we must introduce conditions on the
-density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the closed
-ball of radius $r > 0$, centered at $x \in \Rd$.  Given a set $\Aset
-\subseteq \Rd$ and $\sigma > 0$, define $\Asig = \Aset + B(0,\sigma) = \{y \in
-\Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma\}$, which we call the
-$\sigma$-expansion of $\Aset$. For a differentiable function $g: \Rd \to \Rd$, write $\nabla g(x)$ to denote the Jacobian of $g$ evaluated at $x \in \Rd$.
+As mentioned previously, successful recovery of a density cluster by \pprspace requires the density cluster to be geometrically well-conditioned.
+At a minimum, we wish to avoid dumbbell-like sets $\Cset$ which contain an arbitrarily thin bridge, and as in \cite{chaudhuri2010} we therefore introduce a buffer zone around $\Cset$.
+Letting $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$, for a given cluster $\Cset \subseteq \Rd$ and $\sigma > 0$, we refer to $\Csig := \set{y \in \Reals^d: \inf_{x \in \Cset} \norm{y - x} \leq \sigma}$ as the $\sigma$-expansion of $\Cset$, and state our conditions with respect to $\Csig$.
 
-We are now ready to give our required conditions, stated with respect to a density
+More generally, over the neighborhood graph $G_{n,r}$ we would like the empirical cluster $\Csig[\Xbf]$ to be \textcolor{red}{well connected} everywhere in its interior, and \textcolor{red}{poorly connected} to the rest of $\Xbf$.
+This intuition motivates our required conditions, stated with respect to a density
 cluster $\Cset \in \Cbb_f(\lambda)$ for some threshold $\lambda > 0$, and an
@@
 	\item
+	\label{asmp: cluster_separation}
+	\emph{Cluster separation:}
+	For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$,
+	$$
+	\dist(\Csig,\Csig') > \sigma,
+	$$
+	where \smash{$\dist(\Cset,\Cset') = \inf_{x \in \Cset} \dist(x,\Cset')$}.
+
+	\item 
 	\label{asmp: low_noise_density}
@@
 	$$
-where \smash{$\dist(x,\Aset) = \inf_{x_0 \in \Aset} \norm{x - x_0}$}.
+	where \smash{$\dist(x,\Cset) = \inf_{x_0 \in \Cset} \norm{x - x_0}$}.
 
-\item
-\label{asmp: cluster_separation}
-\emph{Cluster separation:}
-For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$,
-$$
-\dist(\Csig,\Csig') > \sigma,
-$$
-where \smash{$\dist(\Aset,\Aset') = \inf_{x \in \Aset} \dist(x,\Aset')$}.
-
+	%%% AJG 5/20: Should I turn this into two conditions?
 	\item
@@
 	\emph{Lipschitz embedding:}
-There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying, for some $ L \geq 1$,
+	$\Csig$ is the image of a convex set under a biLipschitz, measure preserving mapping.
+Formally, there exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ such that $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, and for some $L \geq 1$,
 	\begin{equation*}
-\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
+	\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Csig$}
 	\end{equation*}
@@
 	$$
+	\item
+	\label{asmp: bounded_volume}
+	\emph{Bounded volume:}
+	Let the neighborhood graph radius $0 < r \leq \sigma/2d$ be such that
+	\begin{equation}
+	\label{eqn: weighted_cluster_volume}
+	\frac{\int_{\Csig} \Pbb(B(x,r)) f(x) dx }{\int_{\Rd} \Pbb(B(x,r)) f(x) dx} \leq \frac{1}{2}.
+	\end{equation}
 \end{enumerate}
 
-Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
-clusters in \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.
-
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
-and \ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
-G_{n,r})$, whereas \ref{asmp: bounded_density}, and \ref{asmp: embedding} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
-lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
-cluster_separation} are similar to the $(\sigma,\epsilon)$-saliency of
-\citep{chaudhuri2010}, a standard density clustering assumption, while
-\ref{asmp: low_noise_density} is seen in, e.g., \citep{singh2009} (as well as
-many other works on density clustering and level set estimation.) While \ref{asmp: embedding} may be less standard, as we will see, it is critical in order to achieve reasonably tight bounds on $\Psi(\Cset[\Xbf];
-G_{n,r})$.  It is also worth
-highlighting that these assumptions are all local in nature, a benefit of
-studying a local algorithm such as \ppr.
-
-%%% AJG 4/29: My attempt to explain why our results aren't fatuous.
-
-We emphasize that while many of these geometric conditions are typical in the density clustering literature, the restrictions we will impose upon them in order to obtain meaningful implications for \pprspace will not be.
-This is natural.
-The spectral algorithm we consider is not specifically designed for the task of level set estimation, and in fact one should expect \pprspace to fail to recover -- either in the sense of \eqref{eqn: consistent_density_cluster_recovery}, or indeed any reasonable notion of cluster recovery -- a density cluster of sufficiently large diameter or sufficiently small thickness (though we do not provide any lower bounds to this effect).
-Indeed, one of the primary motivations of this work was to better understand and characterize the distinctions between those level sets which are well conditioned for spectral algorithms, and those which are not.
-
-In the next several subsections, we will derive bounds on the cluster quality
-criteria evaluated on ($\sigma$-expansions of) density clusters. For notational simplicity,
-hereafter for $S \subseteq V$, we will abbreviate $\Phi(S; G_{n,r})$ by
-$\Phi_{n,r}(S)$, and similarly, $\Psi(S; G_{n,r})$ by $\Psi_{n,r}(S)$, and
-$\tau_{\infty}(G_{n,r}[S])$ by $\tau_{n,r}(S)$. We will also use $\nu$ for
-Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for the measure of the unit ball
-$B=B(0,1)$.
-
-\subsection{Upper Bound on Normalized Cut}
-
-We start with an upper bound on the normalized cut \eqref{eqn: norm_cut} of 
-$\Cset_\sigma[\Xbf]$. (In Theorem \ref{thm: conductance_upper_bound}, the upper bound on the density in
-Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
-the parameter $\Lambda_\sigma>0$ from the theorem statement.) For $\mathcal{S} \subseteq \Reals^d$ and $r > 0$, let
-\begin{equation*}
-\pi_{\Pbb,r}(\mathcal{S}) := \frac{\int_{\mathcal{S}} \Pbb(B(x,r)) f(x) dx }{\int_{\Rd} \Pbb(B(x,r)) f(x) dx}.
-\end{equation*}
-
-\begin{theorem}
-\label{thm: conductance_upper_bound}
-Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
-and \ref{asmp: cluster_separation}, for some 
-$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/2d$ be such that
-\begin{equation}
-\label{eqn: weighted_cluster_volume}
-\pi_{\Pbb,r}(\Csig) \leq \frac{1}{2}.
-\end{equation}
- Then for any $0 < \delta < 1$, $\epsilon > 0$, if
-\begin{equation}
-\label{eqn: conductance_sample_complexity}
-n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
-  {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
-\end{equation}
-then
-\begin{equation}
-  \label{eqn: conductance_additive_error_bound}
-  \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
-  \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-    c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
-\end{equation}
-with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
-\end{theorem}
-
-\begin{remark}
-The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other
-proofs in this paper, can be found in the supplementary document. The key 
-idea is that for any $x \in \Cset$, the simple fact
-$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Csig + rB) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
-  low_noise_density} to find a corresponding bound on the weighted volume,
-then apply standard concentration inequalities to convert from population-
-to sample-based results.  
-\end{remark}
-
-\begin{remark}
-The inequality in \eqref{eqn: conductance_additive_error_bound} is tight in the case of $\Cset = \set{0}$. To see this, let $\Csig = B(0,\sigma)$ and
-$$
- f(x)  = \begin{cases}
-   \lambda &\text{for $x \in \Csig$}, \\
-   \lambda - \dist(x,\Csig)^{\gamma} & \text{ for $0 < \dist(x,\Csig) < r$}, 
-\end{cases}
-$$
-Then, some simple calculations yield
-\begin{equation*}
-\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) \geq c \lambda \nu_d r^d \Pbb((\Csig + B(0,r)), \quad \textrm{and} \quad \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r}) \leq c' \lambda \nu_d r^d \Pbb(\Csig)
-\end{equation*}
-for some constants $c,c' > 0$. Thus the ratio $\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) / \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r})$ matches \eqref{eqn: conductance_additive_error_bound}, up to constants.
-
-\end{remark}
-
-\subsection{Lower Bound on Inverse Mixing Time}
-
-Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of $\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) = 1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time.
-
-\begin{theorem}
-	\label{thm: mixing_time_upper_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, K > 0$.
-Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
-	\begin{equation}
-	\label{eqn: mixing_time_upper_bound}
-	\limsup_{n \to \infty}\tau_{n,r}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
-	\end{equation}
-\end{theorem}
-for $c_2,c_3 > 0$ universal constants.
-
-Our proof technique involves two key geometric quantities: the \emph{local spread} $s(\widetilde{G}_{n,r})$ (where we abbreviate $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ and let $\widetilde{\pi}_{n,r}$ be the stationary distribution over $\widetilde{G}_{n,r}$) and the \emph{conductance} $\widetilde{\Phi}_{n,r}$, defined respectively as
-\begin{equation}
-\label{eqn: local_spread_and_conductance}
-s(\widetilde{G}_{n,r}) := \frac{9}{10} \min_{x \in \Csig[\Xbf]} \set{\deg(x; \widetilde{G}_{n,r}) \cdot \widetilde{\pi}_{n,r}(x) }, \quad \widetilde{\Phi}_{n,r} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; \widetilde{G}_{n,r}).
-\end{equation}
-
-We argue that the random walk over $\widetilde{G}_{n,r}$ quickly escapes sets with stationary distribution less than $s(\widetilde{G}_{n,r})$, and so we avoid a $\log\left(1/\pi_0\right)$ `start penalty' -- where $\pi_0 := \min_{x \in \Csig[\Xbf]} \widetilde{\pi}_{n,r} \lesssim \frac{1}{n}$ -- characteristic to analyses of mixing time, which would render any resultant upper bound on mixing time vacuous.
-Instead, we obtain the tighter upper bound \footnote{For sequences $a_n, b_n$, we write $a_n \lesssim b_n$ ($a_n \gtrsim b_n$) when there exists $c > 0$ such that $a_n \leq c b_n$ ($a_n \geq c b_n$) for all sufficiently large $n$.}
-\begin{equation*}
-\tau_{n,r}(\Csig[\Xbf]) \lesssim \frac{1}{\widetilde{\Phi}_{n,r}^2} \log^2\left(1/s(\widetilde{G}_{n,r})\right).
-\end{equation*}
-Then,
-\begin{itemize}
-	\item Some straightforward calculations yield $s(\widetilde{G}_{n,r}) \gtrsim \frac{\Lambda_{\sigma} r^d}{\lambda_{\sigma}}$.
-	\item To handle the conductance, we introduce a continuous analogue, 
-	\begin{equation}
-	\label{eqn: continuous_conductance}
-	\widetilde{\Phi}_{\Pbb,r} := \min_{\mathcal{S} \subseteq \Csig} \left(\frac{\int_{\Sset} \Pbb(B(x,r) \cap \Sset^c) f(x) dx}{\min \set{\int_{\Sset} \Pbb(B(x,r) \cap \Csig) f(x) dx, \int_{\Sset^c} \Pbb(B(x,r) \cap \Csig) f(x) dx}}\right), \quad \Sset^c = \Csig \setminus \Sset
-	\end{equation}
-	and show the asymptotic lower bound $\limsup_{n \to \infty} \widetilde{\Phi}_{n,r} \gtrsim \widetilde{\Phi}_{\Pbb,r}$.
-	\item Finally, we extend classical isoperimetric results lower bounding $\widetilde{\Phi}_{\Pbb,r}$, when $\Pbb$ is uniform and $\Csig$ convex, to hold under the more general conditions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
-\end{itemize}
-
-\begin{remark}
-	The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$ obviously play an important role in the upper bound of Theorem \ref{thm: mixing_time_upper_bound}.
-It is clear that there is some interdependence between $L$ and other geometric parameters $\sigma$ and $D$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
-However, it is not possible to eliminate this condition without incurring an additional factor of at least $(D/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ consists of two balls of diameter $D$ linked by a cylinder of length $D$ and radius $\sigma$.
-\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding biLipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
-\end{remark}
-\section{Consistent Cluster Estimation}
-\label{sec: consistent_cluster_estimation_with_ppr}
+The cluster separation \ref{asmp: cluster_separation} and low noise density \ref{asmp: low_noise_density} conditions guarantee \textcolor{red}{poor connectivity} between $\Csig[\Xbf]$ and $\Xbf \setminus \Csig[\Xbf]$, whereas \ref{asmp: bounded_density} and \ref{asmp: embedding} ensure high connectivity within $\Csig[\Xbf]$.
+\textcolor{red}{It may not be immediately obvious how \ref{asmp: embedding} contributes to geometric conditioning.
+For now, we observe merely that random walks will mix slowly over sets with large diameter, and make some more detailed commentary in Section 3.} Finally, \ref{asmp: bounded_volume} is a relatively harmless technical condition, merely excluding the case where $\Csig$ contains over half the total mass.
 
@@
 
-For \pprspace to accurately estimate a set, the ratio of normalized cut to inverse mixing time should be small.
-Letting $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the bounds given in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, further abbreviate
-\begin{align*}
+We turn to formally defining a \textcolor{red}{condition number}, $\kappa(\Cset)$, reflects the difficulty of the local spectral clustering task.
+The smaller $\kappa(\Cset)$ is, the more success \pprspace will have in recovering $\Cset$.
+Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those geometric parameters detailed in \ref{subsec: geometric_conditions}.
+
+\begin{definition}[Well-conditioned density clusters]
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$, and \textcolor{red}{ additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume} }.
+Then, setting
+	\begin{align}
+	\label{eqn: condition_number_1}
 	\mathbf{\Phi}(\theta) 
-& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \\
+	& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \nonumber \\
 	\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
-\end{align*}
-for these bounds (where all constants $c_0,c_1,c_2,c_3 >0$ are as in these theorems).
-
-Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf(\theta)$ and $\Psibf(\theta)$.
-\begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: embedding} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}.
-Then, setting
-	\begin{equation*}
-	\kappa(\Cset) := \frac{\mathbf{\Phi}(\theta)}{\mathbf{\Psi}(\theta)}
-	\end{equation*}
-	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster (with respect to $\theta$).}
+	\end{align}
+	and
+	\begin{equation}
+	\label{eqn: condition_number}
+	\kappa(\Cset) := \frac{\Phibf(\theta)}{\Psibf(\theta)}
+	\end{equation}
+	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
 \end{definition}
 
-We focus for a moment on the neighborhood graph radius $r$.
-While taking $r \to 0$ as $n \to \infty$---and thereby ensuring $G_{n,r}$ is sparse---is computationally attractive, the presence of a factor of $\frac{1}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace in this regime.
-Although the restriction to a kernel function fixed in $n$ is standard for theoretical analysis of spectral clustering \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
+At first glance \eqref{eqn: condition_number_1} may appear mysterious, but as will be shown in \textcolor{red}{Section 3}, these are merely upper bounds on the normalized cut and inverse mixing time of (the $\sigma$-expansion of) a given empirical density cluster $\Csig[\Xbf]$ in $G_{n,r}$.
+In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, it is shown that the ratio of normalized cut to inverse mixing time is a fundamental quantity governing the performance of \pprspace over a general graph.
+$\kappa(\Cset)$ upper bounds this ratio for an empirical density cluster over the neighborhood graph $G_{n,r}$, and is therefore a natural criterion to measure difficulty of the clustering task.
 
-\paragraph{Well-conditioned clusters.}
+\paragraph{Well-initialized algorithms.}
 
-As is typical in the local clustering literature, our results will be stated with respect to specific choices or ranges of each of the user-specified parameters, which in this case may depend on the underlying (unknown) density.
+As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific choices or ranges of each of the user-specified parameters.
 
@@
 \label{eqn: initialization}
-r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta) \nonumber,  \\
+r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \Psibf(\theta) \nonumber,  \\
 v \in \Csig[\Xbf]^g, & ~\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx
 \end{align}
-where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$.
-(Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the data sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)
+$\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ will be some large subset of $\Csig[\Xbf]$, in particular $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$.
 
@@
 
-%%% AJG 5/8/19: My attempt to explain how to choose these parameters
-%%% in practice. Not satisfied with it.
+In practice it is clearly not feasible to set hyperparameters based on the underlying (unknown) density $f$.
+Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as normalized cut; it is unclear how this scheme would affect the performance of \pprspace in the density clustering context.
 
-In practice, a reasonable way to choose these hyperparameters is by tuning.
-For example, if one wanted to successfully recover a density cluster, one could vary each hyperparameter over a grid, retaining outputs $\Cest$ of Algorithm \ref{alg: ppr} only if they recover some $\Cset \in \Cbb_f(\lambda)$ and discarding them otherwise.
-Then simply return the minimum normalized cut set from those $\Cest$ which were retained.
-Assuming there existed $\lambda > 0, \Cset \in \Cbb_f(\lambda)$ such that $\Cset$ satisfied the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, and moreover some combination of tuning parameters in the chosen grid satisfied \eqref{eqn: initialization}, this scheme would inherit the consistency guarantees of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+\paragraph{Density cluster estimation by \ppr.}
 
-\paragraph{Misclassification error for \ppr.}
-
-In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, theory is developed which links algorithmic performance of PPR to the normalized cut and mixing time parameters.
-This work, combined with the results of Section \ref{sec: cluster_quality_bounds}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),
+Theorem 1 of \cite{zhu2013}, combined with the results of \textcolor{red}{Section 3}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),
 \begin{equation}
@@
 \end{equation}
-where we've written $\vol_{n,r}(S) := \vol(S; G_{n,r})$ for $S \subseteq \Xbf$. 
 To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification error, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
-To do so, we make some regularity assumptions on $\mathcal{X} = \mathrm{supp}(f)$.
+To do so, we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 	\label{asmp: valid_region}
-	\emph{Valid region:} $0 < \lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
+	\emph{Valid region:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
 Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
 \end{enumerate}
-Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, $\mathcal{X}$ is a $\sigma$-expansion.
+Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, $\mathcal{X}$ is a $\sigma$-expanded set.
 
@@
 
-\begin{remark}
-	A notable implication of our theory is that as the diameter $D$ increases, our upper bound on the normalized cut of $\Csig[\Xbf]$ remains unchanged, but $\kappa(\Cset)$, and therefore the misclassification error, worsens (increases).
-This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
-It suggests that \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$.
-This intuition will be supported by simulations in Section \ref{sec: experiments}.
-\end{remark}
-
-\paragraph{Consistent density cluster estimation.}
+The proof of Theorem \ref{thm: misclassification_rate}, along with all other proofs in this paper, can be found in the supplementary material.
+We observe that the misclassification error is proportional to the difficulty of the clustering problem, as measured by the \textcolor{red}{condition number}.
 
@@
 In Theorem \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently small upper bound on $\kappa(\Cset)$ ensures such a gap exists with probability one as $n \to \infty$, and therefore guarantees $\Cest$ will be a consistent estimator.
-
-As before, we wish to preclude arbitrarily low degree vertices, this time for points $x \in \Cset'[\Xbf]$.
+As was the case before, we wish to preclude arbitrarily low degree vertices, this time for points $x \in \Cset'[\Xbf]$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 	\label{asmp: C'_bounded_density}
-	\emph{$\Cset'$- bounded density :} For each $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$, for all $x \in \Cset' + \sigma B$,
-	\begin{equation*}
-	\lambda_{\sigma} \leq f(x)
-	\end{equation*}
-	where $\sigma,\lambda_{\sigma}$ are as in \ref{asmp: bounded_density}.
+	\emph{$\Cset'$- bounded density :} For each $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$ and for all $x \in \Cset' + \sigma B$, $\lambda_{\sigma} \leq f(x)$ where $\sigma,\lambda_{\sigma}$ are as in \ref{asmp: bounded_density}.
 \end{enumerate}
@@
 \end{theorem}
+A few remarks are in order.
+
+\begin{remark}
+	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a misclassification rate on the order of $r^d$.
+(See Theorem \ref{thm: misclassification_rate}).
+In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points are misclassified.
+This strong condition is the price we pay in order to obtain the uniform bound of \ref{eqn: ppr_gap}.
+\end{remark}
+
+\begin{remark}
+	While taking the radius of the neighborhood graph $r \to 0$ as $n \to \infty$---and thereby ensuring $G_{n,r}$ is sparse---is computationally attractive, the presence of a factor of $\frac{\log^2(1/r)}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace in this regime.
+Although the restriction to a kernel function fixed in $n$ is standard for theoretical analysis of spectral clustering \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
+\end{remark}
 
@@
 
+\section{Analysis}
+Given an arbitrary graph $G = (V,E)$ and candidate cluster $S \subseteq G$, \cite{zhu2013} bound the volume of $\Cest \setminus S$ and $S \setminus \Cest$ in terms of the normalized cut and inverse mixing time of $S$.
+The key to deriving the algorithmic results of the previous section is therefore to show that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: embedding} translate to meaningful bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
+Doing so constitutes the bulk of our technical effort.
+
+\subsection{Upper Bound on Normalized Cut}
+
+We start with an upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
+$\Cset_\sigma[\Xbf]$. (In Theorem \ref{thm: conductance_upper_bound}, the upper bound on the density in
+Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
+the parameter $\Lambda_\sigma>0$ from the theorem statement.) For simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
+
+\begin{theorem}
+	\label{thm: conductance_upper_bound}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
+	Assumptions \ref{asmp: bounded_density}-\ref{asmp: low_noise_density}, and \ref{asmp: bounded_volume} for some 
+	$r, \sigma, \lambda_{\sigma}, c_0, \gamma > 0$. 
+	Then for any $0 < \delta < 1$, $\epsilon > 0$, if
+	\begin{equation}
+	\label{eqn: conductance_sample_complexity}
+	n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
+	{6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
+	\end{equation}
+	then
+	\begin{equation}
+	\label{eqn: conductance_additive_error_bound}
+	\frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
+	\frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
+		c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
+	\end{equation}
+	with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
+\end{theorem}
+
+\begin{remark}
+	Observe that the diameter $D$ is absent from Theorem \ref{thm: conductance_upper_bound}, in contrast to the difficulty function $\kappa(\Cset)$, which worsens (increases) as $D$ increases.
+This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
+It suggests that \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$, if the diameter $D$ is large.
+This intuition will be supported by simulations in Section \ref{sec: experiments}.
+\end{remark}
+
+\subsection{Lower Bound on Inverse Mixing Time}
+For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
+$S$ (where the edges are $E_S = E \cap (S \times S)$), let $\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write 
+$$
+q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
+$$
+for the $t$-step transition probability of a random walk over $G[S]$
+originating at $v$.\footnote{Given a starting node $v$ and and a random walk
+	defined by transition probability matrix $\mathbf{P}$, the notation $e_v
+	\mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
+	steps.}   Also write \smash{$\pi = (\pi(u))_{u \in S}$}
+for the stationary distribution of this random walk.  (Given the definition of 
+$\Wbf_S$, it is well-known that a unique stationary distribution exists and is given by
+\smash{$\pi(u) = \deg(u; G[S])/\vol(S; G[S])$}.)
+
+Then, the \emph{relative pointwise mixing time} of $G[S]$ is 
+\begin{equation}
+\label{eqn: mixing_time}
+\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)
+	}{\pi(u)} \leq \frac{1}{4}, 
+	\; \text{for $u,v \in V$}}. 
+\end{equation}
+We lower bound the inverse mixing time $\Psi_{n,r}(\Csig[\Xbf]) = 1/\tau_{\infty}(\Csig[\Xbf])$ of $\Csig[\Xbf]$, or equivalently we upper bound the mixing time.
+
+\begin{theorem}
+	\label{thm: mixing_time_upper_bound}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, K > 0$.
+Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
+	\begin{equation}
+	\label{eqn: mixing_time_upper_bound}
+	\limsup_{n \to \infty}\tau_{\infty}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
+	\end{equation}
+	for $c_2,c_3 > 0$ universal constants. 
+\end{theorem}
+
+So far as we are aware, Theorem \ref{thm: mixing_time_upper_bound} is a \textcolor{red}{novel bound} on the mixing time of random walks over neighborhood graphs. 
+\begin{remark}
+	The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$ play an important role in proving the upper bound of Theorem \ref{thm: mixing_time_upper_bound}.
+There is some interdependence between $L$ and other geometric parameters $\sigma$ and $D$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
+However, it is not possible to eliminate this condition without incurring an additional factor of at least $(D/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ is a dumbbell-like set consisting of two balls of diameter $D$ linked by a cylinder of radius $\sigma$.
+\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding biLipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
+\end{remark}
+
 \section{Experiments}
@@
 
-\subsection{Validating Theoretical Bounds}
+We provide numerical experiments to investigate the tightness of our bounds on the cluster quality criteria normalized cut and mixing time, and examine the performance of \pprspace on the 'two moons' dataset.
+For space reasons, we defer details of the experimental settings to the supplement.
+
+\paragraph{Validating Theoretical Bounds.}
 
@@
 
-As we do not provide any theoretical lower bounds, we validate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
-We sample points according to the density function $q$, where for $x \in \Rd$
-\begin{equation}
-q(x) :=
-\begin{cases}
-\lambda,~ & x \in [0,\sigma] \times D^{d-1} =: \Cset, \\
-\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
-(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
-0,~ & \textrm{otherwise},
-\end{cases}
-\end{equation}
-where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
-Panels $(a)$ and $(b)$ in Figure \ref{fig:fig1} show $20,000$ samples from two parameterizations of $q$.
-In $(a)$, $\sigma = D = 3.2$, while in $(b)$ $\sigma = .1$ and $D = 3.2$.
-(For both, $d = 2$).
+As we do not provide any theoretical lower bounds, we investigate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
+Figure \ref{fig:fig1} shows these theoretical bounds compared to the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $D$ and thickness $\sigma$ of the cluster $\Cset$.
 
-Panels $(c) - (f)$ in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ ($(c)$ and $(d)$) and $D$ ($(e)$ and $(f)$) are varied.
-In panels $(c)$ and $(d)$ $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $D$ is fixed at $3.2$.
-In panels $(e)$ and $(f)$, $D = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
-For each panel, the solid lines show, up to constants \footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
-Therefore only comparison of slopes, rather than intercepts, is meaningful.}, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for panels $(c)$ and $(e)$ and Theorem \ref{thm: mixing_time_upper_bound} for panels $(d)$ and $(f)$.
-The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in panels $(c)$ and $(e)$, and $m = 20$ for the mixing time, dashed lines in panel $(d)$ and $(f)$).
-For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
-Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
+Panels $(d)$ and $(f)$ show our theoretical bounds on mixing time tracking closely with empirical mixing time, in both 2 and 3 dimensions.\footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
+Therefore only comparison of slopes, rather than intercepts, is meaningful.} This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both expansion parameter $\sigma$ and diameter $D$.
+The story in panels $(c)$ and $(e)$ is less obvious.
+We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma \approx D$.
+As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
 
-Panels $(d)$ and $(f)$ show the solid lines tracking closely to the dashed lines, in both 2 and 3 dimensions.
-This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both thickness parameter  $\sigma$ and diameter $D$.
-
-The story in panels $(c)$ and $(e)$ is less obvious.
-We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$.
-It is in these regions that the slopes of the dashed and solid lines are most different.
-As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
-The takeaway message is that while the dependency in \eqref{eqn: conductance_additive_error_bound} on $\sigma$ and $D$ is loose for clusters with diameter close to thickness, it becomes tighter as $D/\sigma$ grows.
-
-\subsection{Empirical PPR, normalized cut, and density clustering comparison}
+\paragraph{\pprspace, normalized cut, and density clustering comparison.}
 
@@
 
-To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
-To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
-Formally, the (respective) generative models for the data are
-\begin{align}
-Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
-X(Z,\theta) & = 
-\begin{cases}
-\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
-\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
-\end{cases}
-\end{align}
-
-where 
-\begin{align*}
-\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
-\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
-\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} \\
-\mu_1 & = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}) \tag{row 4}
-\end{align*}
-for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
+The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
 
 Rows 1-3 show the degrading ability of \pprspace to recover density clusters as the two moons become less salient.
-In the first row, the normalized cut conforms to the density cluster, and \pprspace recovers both.
-In the second row, the normalized cut still conforms to the density cluster, but because the internal connectivity of the lower moon is low, \pprspace fails to recover the normalized cut.
-In the third row, the moons have such low saliency that even the normalized cut fails to recover the lower moon; we also see from $(k)$ that \pprspace does not somehow save us in this situation.
-Note that this is not a function of the finite sample: the 4th column shows us that a well-designed density clustering algorithm can recover the true density cluster.
+Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, and that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail.
 

### 2019-05-21 neurips/local_spectral_density_clustering_tuesday.tex
added Tuesday edits for neurips draft

--- 2019-05-20 neurips/local_spectral_density_clustering_monday.tex
@@
 
+\PassOptionsToPackage{numbers}{natbib}
 \usepackage{neurips_2019}
@@
 \newcommand{\1}{\mathbf{1}}
-\newcommand{\Phibf}{\mathbf{\Phi}}
-\newcommand{\Psibf}{\mathbf{\Psi}}
+\newcommand{\Phibf}{\Phi_{u}}
+\newcommand{\Psibf}{\Psi_{u}}
 \newcommand{\dist}{\mathrm{dist}}
@@
 
-To be more precise, let $G=(V,E,w)$ denote a weighted, undirected graph  
-constructed from the samples $\Xbf$, where $V=\{1,\ldots,n\}$, and $w_{uv}
-= K(x_u,x_v) \geq 0$ for $u,v \in V$, and a particular kernel function $K$.
-Here $(u,v) \in E$ if and only if $w_{uv} > 0$.  We denote by $\Abf \in
-\Reals^{n \times n}$ the weighted adjacency matrix, which has entries
-$A_{uv}=w_{uv}$, and by $\Dbf$ the degree matrix, with 
-\smash{$\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$}.  We also denote by $\Wbf,\Lbf$
-the (lazy) random walk transition probability matrix and normalized\footnote{Other
-	popular choices here include the unnormalized Laplacian, and symmetric
-	normalized Laplacian.} 
-Laplacian matrix, respectively, which are defined as
-$$
-\Wbf = \frac{\Ibf{} + \Dbf^{-1}\Abf}{2}, \quad \Lbf = \Ibf{} - \Wbf,
-$$
-where $\Ibf{} \in \Reals^{n\times n}$ is the identity matrix.  Classical global
-spectral methods take a eigendecomposition $L=U \Sigma U^T$, use some 
-number of eigenvectors (columns in $U$) as a feature representation for the
-samples, and then run (say) k-means in this new feature space.
-
 When applied to geometric graphs constructed from a large number of samples,
@@
 random walks around a user-specified seed node.  A popular local clustering
-algorithm is Personalized PageRank (PPR), first introduced by
-\citep{haveliwala2003}, and further developed by
+algorithm is Personalized PageRank (\ppr), first introduced by
+\citet{haveliwala2003}, and further developed in
 \citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
@@
 and examine what the output of a local clustering algorithm on $\Xbf$ reveals
-about the unknown density $f$.  In particular, we examine the ability of the PPR
-algorithm to recover \emph{density clusters} of $f$, which are defined as the
+about the unknown density $f$.  In particular, we examine the ability of the \pprspace algorithm to recover \emph{density clusters} of $f$, which are defined as the
 connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
@@
 
-\subsection{PPR on a Neighborhood Graph}
-
-We now describe the clustering algorithm that will be our focus for the rest of 
+\paragraph{PPR on a Neighborhood Graph.}We now describe the clustering algorithm that will be our focus for the rest of 
 the paper. We start with the geometric graph that we form based on the samples 
 $\Xbf$: for a radius $r > 0$, we consider the \emph{$r$-neighborhood graph} of 
-$\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted graph with vertices
+$\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted, undirected graph with vertices
 $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i - x_j}
-\leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.  Note that this is a
-special case of the general construction introduced above, with 
-$K(u,v) = 1(\norm{x_u - x_v} \leq r)$.
+\leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.
+We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if and only if $(u,v) \in E$, and by $\Dbf$ the degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$.
 
@@
 \end{equation}
-where $\Wbf$ is the random walk matrix of the underlying graph $G_{n,r}$ 
+where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the (lazy) random walk matrix over $G_{n,r}$ 
 and $e_{v}$ denotes indicator vector for node $v$ (with a 1 in the $v$th
-position and 0 elsewhere).  In practice, we can approximately solve the above
-linear system via a simple, efficient random walk, with appropriate restarts to
-$v$.
+position and 0 elsewhere).
 
@@
 \label{eqn: sweep_cuts}
-S_\beta = \{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}\}.
+S_\beta = \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
 \end{equation}
-
-Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
-\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we then  output a cluster estimate $\widehat{C} = S_{\beta^*}$ to have minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$, where for $S \cup S^c = G_{n,r}$, $\cut(S;G_{n,r}) := |\set{(u,v) \in E : u \in S, v \in S^c}|$, $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and
+For a set $S \subseteq V$ with complement $S^c = V \setminus S$, the normalized cut is defined to be 
 \begin{equation}
@@
 \end{equation}
+where $\cut(S;G_{n,r}) = \sum_{u \in S, v \in S^c} \Abf_{uv}$ and $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$. Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
+(\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
+\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
+algorithms, see, e.g., \citep{zhu2013}.}, we then output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
 For concreteness, we summarize this procedure in Algorithm \ref{alg: ppr}.
@@
 
-\subsection{Summary of Results}
-
-% It is worth calling attention to some other work on computing the normalized
-% cut over neighborhood graphs. In this context, continuous analogues to (for
-% instance) normalized cut have been defined, over the data-manifold rather than
-% the graph, and convergence finite sample graph-theoretic functionals to their
-% continuous counterparts has been shown 
-% \cite{garciatrillos16, arias-castro12, maier11}. 
-% However, in addition to the graph-minimization problem being computationally
-% infeasible, these continuous analogues are not always easily interpretable --
-% and their corresponding minimizers not always easily identifiable -- for the
-% particular density function under consideration. Of course, relating these
-% partitions to the arguably more simply defined high density clusters can be
-% also challenging in general. Intuitively, however, under the right conditions
-% such high-density clusters should have more edges within themselves than to
-% the remainder of the graph. We formalize this intuition next.
-
-%% RJT: I didn't know where to put this.  It was out of place, and now I'm not
-%% sure where it goes ... should it go in related work?
-
-%It is worth pointing out that in this context, some theory has been developed
-%regarding how graph theoretic quantities such as the normalized cut $\Phi$ (and
-%others) relate to properties of the underlying distribution $f$ as well as the
-%kernel function $k$. Such analyses typically proceed by defining a continuous
-%analogue to the measure of cluster quality under consideration. Then, under
-%appropriate specification of $k$ and a proper schedule of $(r_n)$, convergence
-%of clusters output by spectral (and other) algorithms to the corresponding
-%minima of these continuous analogues has been shown \cite{vonluxburg2008,
-%garciatrillos18}.
-
-%% RJT: This was already commented out before
+\paragraph{Estimation of density clusters.}
 
@@
 \Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
-	density cluster}. Below we give two notions of performance of a density cluster estimate.
+density cluster}.
+The symmetric set difference between estimated and empirical cluster is perhaps the most frequently used metric to quantify cluster estimation error \citep{korostelev2012,polonik1995,rigollet2009}.
 
-\begin{definition}[Misclassification error]
-	\label{def: misclassification_rate}
+\begin{definition}[Symmetric set difference]
+	\label{def: symmetric_set_diff}
 	For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-	$\mathcal{S} \subseteq \Reals^d$, the \emph{misclassification error} of $\mathcal{S}$ by $\Cest$ is
+	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S}$ is 
 	\begin{equation}
 	\label{eqn: misclassification_rate}
-	\abs{\Cest \setminus (\mathcal{S} \cap \Xbf)} + \abs{(\mathcal{S} \cap \Xbf) \setminus \Cest}.
+	\Delta(\Cest, \mathcal{S}) = \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup \mathcal{S}[\Xbf] \setminus \Cest}.
 	\end{equation}
 \end{definition}
+
+However, the symmetric set difference does not account for the distance points in $\widehat{C} \setminus \mathcal{S}[\Xbf]$ may be from $\mathcal{S}$ \citep{singh2009}.
+Therefore we introduce a second notion of cluster estimation, first introduced by \citet{hartigan1981} and defined asymptotically, which measures whether $\widehat{C}$ can distinguish any two distinct elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
 
@@
 \end{definition}
-
+\paragraph{Summary of results.}
 A summary of our main results (and outline for the rest of this paper) is as
@@
 \begin{enumerate}
-	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions.
-We formalize a measure of difficulty based on these geometric conditions, and show that when properly initialized, the misclassification error of Algorithm \ref{alg: ppr} is upper bounded by this difficulty measure.
+	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions, formalize a measure of difficulty based on these geometric conditions, and show that when properly initialized, the symmetric set difference of Algorithm \ref{alg: ppr} is upper bounded by this difficulty measure.
 
 	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+In Corollary \ref{cor: appr}, we establish that both metrics of cluster estimation can be bounded with respect to an approximate form of \ppr, which can be efficiently computed.
 
-	\item Corollary \ref{cor: appr} establishes that these statements hold also with respect to an approximate form of \ppr, which can be efficiently computed.
-
-	\item In \textcolor{red}{Section 3}, we detail some of the main technical machinery required to prove our main results, highlighting the part various geometric quantities play in the ultimate difficulty of the clustering problem.
+	\item In Section \ref{sec: analysis}, we detail some of the main technical machinery required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
 
@@
 
-On the topic of conditions, it is worth mentioning that, as density clusters
-are inherently local, focusing on the PPR algorithm actually eases our analysis
-and allows us to require fewer global regularity conditions relative to those
-needed for more classical global spectral algorithms.
+Our main takeaway can be summarized as follows: \ppr, run on a neighborhood graph, recovers geometrically compact high-density clusters.
 
-\subsection{Related Work}
-%In addition to the background given above, a few related lines of work are worth
-%highlighting. For neighborhood graphs of the type we consider, continuous analogues to (for
-%instance) normalized cut have been defined, over the data-manifold rather than
-%the graph, and convergence finite sample graph-theoretic functionals to their
-% continuous counterparts has been shown 
-% \cite{garciatrillos16, arias-castro12, maier11}.
+\paragraph{Related Work. }
 
-In addition to the background given above, a few related lines of work are worth
-highlighting. Building on earlier work of
-\citep{koltchinskii2000}, \citep{vonluxburg2008,hein2005} studied the limiting behaviour of spectral clustering
-algorithms. These authors show that when samples are obtained from a
-distribution, and we appropriately construct a geometric graph, the spectrum of
-the Laplacian converges to that of the Laplace-Beltrami operator on the
-data-manifold. However, relating the partition obtained using the
-Laplace-Beltrami operator to the more intuitively defined high-density
-clusters can be challenging in general.
-
-% AJG 4/29: I need to rewrite to explain how its similar, because
-% this is a good opportunity to show that implications
-% of the type given in our work are broadly of interest.
-
-More similar to our results are the works
-\citep{vempala2004,shi2009,schiebinger2015}, who study the consistency of
+In addition to the background given earlier, a few related lines of work are worth
+highlighting. Similar in spirit to our results are the works
+\citep{shi2009,schiebinger2015}, who study the consistency of
 spectral algorithms in recovering the latent labels in certain parametric and
@@
 clusters, which is the focus in our work.
+Perhaps most importantly, these works rely on general cluster saliency conditions, which depend implicitly on many distinct geometric aspects of the cluster $\Cset$ under consideration.
+We make this dependence explicit, and in so doing, expose the role each geometric condition plays in the clustering problem.
+
+Additionally, we note that density clustering and level set estimation is a well-studied problem.
+\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} prove minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
+Our goal is not to improve on these results, or offer yet another algorithm for level set estimation; indeed, seen as a density clustering algorithm, \pprspace has none of the optimality guarantees of the previous works.
+This is fact a major point of our article: \pprspace can provably recover density clusters, but only under strong geometric conditions.
 
@@
 
-\subsection{Geometric Conditions on Density Clusters}
-\label{subsec: geometric_conditions}
+We formalize some geometric conditions, before using these to define a measure $\kappa(\Cset)$ which encodes the difficulty \pprspace will have estimating $\Cset$.
+We motivate this measure, and the underlying geometric conditions, by giving density cluster estimation guarantees for Algorithm \ref{alg: ppr} in terms of $\kappa(\Cset)$.
+
+\paragraph{Geometric Conditions on Density Clusters.}
 
 As mentioned previously, successful recovery of a density cluster by \pprspace requires the density cluster to be geometrically well-conditioned.
-At a minimum, we wish to avoid dumbbell-like sets $\Cset$ which contain an arbitrarily thin bridge, and as in \cite{chaudhuri2010} we therefore introduce a buffer zone around $\Cset$.
-Letting $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$, for a given cluster $\Cset \subseteq \Rd$ and $\sigma > 0$, we refer to $\Csig := \set{y \in \Reals^d: \inf_{x \in \Cset} \norm{y - x} \leq \sigma}$ as the $\sigma$-expansion of $\Cset$, and state our conditions with respect to $\Csig$.
-
-More generally, over the neighborhood graph $G_{n,r}$ we would like the empirical cluster $\Csig[\Xbf]$ to be \textcolor{red}{well connected} everywhere in its interior, and \textcolor{red}{poorly connected} to the rest of $\Xbf$.
-This intuition motivates our required conditions, stated with respect to a density
-cluster $\Cset \in \Cbb_f(\lambda)$ for some threshold $\lambda > 0$, and an
-expansion parameter $\sigma > 0$.
+At a minimum, we wish to sets $\Cset$ which contain arbitrarily thin bridges or spikes, and therefore as in \cite{chaudhuri2010} we introduce a buffer zone around $\Cset$.
+Let $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$.
+For a some $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
+We denote the distance between $x$ and $\Cset$ as $\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$, and for a given $\sigma > 0$, we refer to $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$ as the $\sigma$-expansion of $\Cset$.
+We now state our conditions with respect to $\Csig$, and provide some intuition afterwards.
 
@@
 	\label{asmp: bounded_density}
-	\emph{Bounded density within cluster:} There are $0 < \lambda_{\sigma} <
-	\Lambda_{\sigma} < \infty$ such that
-	$$
-	\lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq
-	\Lambda_{\sigma}.
-	$$
-	% and 
-	% \begin{equation*}
-	% \frac{\diam \Asig}{\sigma} \leq \mu
-	% \end{equation*}
-	% where $\diam \Asig = \sup \set{d(x,y) : x,y \in \Asig}$
+	\emph{Bounded density within cluster:} There exist constants $\lambda_{\min}, \Lambda_{\min}$ $0 < \lambda_{\sigma} <
+	\Lambda_{\sigma} < \infty$ such that $ \lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma}.$
 
@@
 	\emph{Cluster separation:}
-	For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$,
-	$$
-	\dist(\Csig,\Csig') > \sigma,
-	$$
-	where \smash{$\dist(\Cset,\Cset') = \inf_{x \in \Cset} \dist(x,\Cset')$}.
+	For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$, $\dist(\Csig,\Csig') > \sigma$,
+	where \smash{$\dist(\Csig,\Csig') := \inf_{x \in \Csig} \dist(x,\Csig')$}.
 
@@
 	$$
-	where \smash{$\dist(x,\Cset) = \inf_{x_0 \in \Cset} \norm{x - x_0}$}.
 
@@
 	\emph{Lipschitz embedding:}
-	$\Csig$ is the image of a convex set under a biLipschitz, measure preserving mapping.
-Formally, there exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ such that $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, and for some $L \geq 1$,
+	There exists $g: \Reals^d \to \Reals^d$ which has the following properties: i) there exists a convex set $\mathcal{K} \subseteq \Rd$ with $\diam(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =: D < \infty$, such that $\Csig = g(\mathcal{K})$, ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; iii) for some $L \geq 1$,
 	\begin{equation*}
-	\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Csig$}
+	\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \mathcal{K}$}.
 	\end{equation*}
-	such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
-	Furthermore, there exists $D < \infty$ such that for all $x, x' \in \mathcal{K}$
-	$$
-	\norm{x - x'} \leq D.
-	$$
+	Simply put, $\Csig$ is the image of a convex set with finite diameter, under a biLipschitz, measure preserving transformation.
 	\item
@@
 	\label{eqn: weighted_cluster_volume}
-	\frac{\int_{\Csig} \Pbb(B(x,r)) f(x) dx }{\int_{\Rd} \Pbb(B(x,r)) f(x) dx} \leq \frac{1}{2}.
+	2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx
 	\end{equation}
@@
 
-The cluster separation \ref{asmp: cluster_separation} and low noise density \ref{asmp: low_noise_density} conditions guarantee \textcolor{red}{poor connectivity} between $\Csig[\Xbf]$ and $\Xbf \setminus \Csig[\Xbf]$, whereas \ref{asmp: bounded_density} and \ref{asmp: embedding} ensure high connectivity within $\Csig[\Xbf]$.
-\textcolor{red}{It may not be immediately obvious how \ref{asmp: embedding} contributes to geometric conditioning.
-For now, we observe merely that random walks will mix slowly over sets with large diameter, and make some more detailed commentary in Section 3.} Finally, \ref{asmp: bounded_volume} is a relatively harmless technical condition, merely excluding the case where $\Csig$ contains over half the total mass.
+Thinking of $\Csig[\Xbf]$ as a subset of vertices in $G_{n,r}$, we would like $\Csig[\Xbf]$ to be internally well-connected, while being poorly connected to the rest of $\Xbf$.
+The cluster separation \ref{asmp: cluster_separation} and low noise density \ref{asmp: low_noise_density} conditions guarantee low connectivity between $\Csig[\Xbf]$ and $\Xbf \setminus \Csig[\Xbf]$ in $G_{n,r}$, whereas \ref{asmp: bounded_density} and \ref{asmp: embedding} ensure high connectivity within $\Csig[\Xbf]$.
+It may not be immediately obvious how \ref{asmp: embedding} contributes to geometric conditioning.
+For now, we observe merely that random walks will mix slowly over sets with large diameter, and comment on this condition in more detail in Section \ref{sec: analysis}.
+Finally, \ref{asmp: bounded_volume} is a relatively harmless technical condition, merely excluding the case where $\vol(\Csig[\Xbf]; G_{n,r}) > \vol(\Xbf; G_{n,r})/2$.
 
-\subsection{Well-Conditioned Density Clusters}
-
-We turn to formally defining a \textcolor{red}{condition number}, $\kappa(\Cset)$, reflects the difficulty of the local spectral clustering task.
+We can now formally define the \textcolor{red}{condition number}, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
 The smaller $\kappa(\Cset)$ is, the more success \pprspace will have in recovering $\Cset$.
-Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those geometric parameters detailed in \ref{subsec: geometric_conditions}.
+Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those geometric parameters detailed in \ref{asmp: bounded_density} - \ref{asmp: bounded_volume}.
 
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$, and \textcolor{red}{ additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume} }.
-Then, setting
-	\begin{align}
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$, Then, for universal constants $c_1, c_2, c_3 > 0$ \textcolor{red}{to specified later}, we set
+	\begin{equation}
 	\label{eqn: condition_number_1}
-	\mathbf{\Phi}(\theta) 
-	& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \nonumber \\
-	\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
-	\end{align}
-	and
-	\begin{equation}
-	\label{eqn: condition_number}
-	\kappa(\Cset) := \frac{\Phibf(\theta)}{\Psibf(\theta)}
+	\Phibf(\theta) 
+	:= c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}},~ 
+	\Psibf(\theta) := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
 	\end{equation}
-	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
+	and letting $\kappa(\Cset) := \frac{\Phibf(\theta)}{\Psibf(\theta)}$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
 \end{definition}
 
-At first glance \eqref{eqn: condition_number_1} may appear mysterious, but as will be shown in \textcolor{red}{Section 3}, these are merely upper bounds on the normalized cut and inverse mixing time of (the $\sigma$-expansion of) a given empirical density cluster $\Csig[\Xbf]$ in $G_{n,r}$.
-In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, it is shown that the ratio of normalized cut to inverse mixing time is a fundamental quantity governing the performance of \pprspace over a general graph.
-$\kappa(\Cset)$ upper bounds this ratio for an empirical density cluster over the neighborhood graph $G_{n,r}$, and is therefore a natural criterion to measure difficulty of the clustering task.
+At first glance \eqref{eqn: condition_number_1} may appear mysterious, but as will be shown in Section \ref{sec: analysis}, $\Phibf(\theta)$ and $\Psibf(\theta)$ are merely upper bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
+In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, it is shown that the ratio of normalized cut to inverse mixing time is a fundamental quantity governing the clustering performance of \pprspace on a general graph.
+$\kappa(\Cset)$ upper bounds this ratio for an empirical density cluster over the neighborhood graph $G_{n,r}$, and is therefore a natural criterion to measure difficulty of the density clustering task.
 
-\paragraph{Well-initialized algorithms.}
+\paragraph{Well-initialized algorithm.}
 
@@
 \end{align}
-$\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ will be some large subset of $\Csig[\Xbf]$, in particular $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$.
+where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ will be some large subset of $\Csig[\Xbf]$.
+In particular, letting $\vol_{n,r}(S) := \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we have $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$.
 
@@
 In practice it is clearly not feasible to set hyperparameters based on the underlying (unknown) density $f$.
-Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as normalized cut; it is unclear how this scheme would affect the performance of \pprspace in the density clustering context.
+Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is unclear how this scheme would affect the performance of \pprspace in the density clustering context.
 
@@
 
-Theorem 1 of \cite{zhu2013}, combined with the results of \textcolor{red}{Section 3}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),
+Theorem 1 of \cite{zhu2013}, combined with the results of Section \ref{sec: analysis}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),\footnote{For sequences $a_n$ and $b_n$, we write $a_n \lesssim b_n$ if there exists constant $c$ such that $a_n \leq c b_n$ for all $n$ sufficiently large.
+}
 \begin{equation}
@@
 \end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification error, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
 To do so, we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
@@
 	\label{asmp: valid_region}
-	\emph{Valid region:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
+	\emph{Support of $f$:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
 Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
@@
 	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
-Then, with probability tending to one as $n \to \infty$,
+Then, there exists universal constant $c_4 > 0$ such that with probability tending to one as $n \to \infty$,
 	\begin{equation}
 	\label{eqn: misclassification_rate_ub}
-	\frac{\abs{\Csig[\Xbf] \setminus \Cest}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}, \quad \textrm{and} \quad \frac{\abs{\Cest \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
+	\Delta(\Csig[\Xbf], \Cest) \leq c_4 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
 	\end{equation}
-	for universal constants $c_4, c_5 > 0$. 
 \end{theorem}
@@
 The proof of Theorem \ref{thm: misclassification_rate}, along with all other proofs in this paper, can be found in the supplementary material.
-We observe that the misclassification error is proportional to the difficulty of the clustering problem, as measured by the \textcolor{red}{condition number}.
+We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the \textcolor{red}{condition number}.
 
 Neither \eqref{eqn: graph_symmetric_set_difference} nor Theorem \ref{thm: misclassification_rate} imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, u' \in \Cset'$
+This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, w \in \Cset'$
 \begin{equation}
 \label{eqn: ppr_gap}
-\frac{p_{u'}}{\Dbf_{uu}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}}.
+\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}}.
 \end{equation}
@@
 	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume \ref{asmp: C'_bounded_density} holds.
-If Algorithm \ref{alg: ppr} is well-initialized, there exists universal constant $c_7 > 0$ such that if
+If Algorithm \ref{alg: ppr} is well-initialized, there exists universal constant $c_5 > 0$ such that if
 	\begin{equation}
 	\label{eqn: kappa_ub}
-	\kappa(\Cset) \leq c_7 \frac{\lambda_{\sigma}^2r^d \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)},
+	\kappa(\Cset) \leq c_5 \frac{\lambda_{\sigma}^2r^d \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)},
 	\end{equation}
@@
 (See Theorem \ref{thm: misclassification_rate}).
-In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points are misclassified.
+In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points will be misclassified.
 This strong condition is the price we pay in order to obtain the uniform bound of \ref{eqn: ppr_gap}.
@@
 
-\paragraph{Cluster estimation with the approximate \pprspace vector.}
+\paragraph{Approximate \pprspace vector.}
 
-As mentioned previously, in practice exactly solving \eqref{eqn: ppr_vector} may be too computationally expensive.
+In practice, exactly solving \eqref{eqn: ppr_vector} may be too computationally expensive.
 To address this limitation, \citet{andersen2006} introduced the \emph{$\epsilon$-approximate \pprspace vector} (aPPR), which we will denote $\pbf^{(\epsilon)}$.
 We refer the curious reader to \cite{andersen2006} for a formal algorithmic definition of the a\pprspace vector, and limit ourselves to highlighting a few salient points.
-Namely, the aPPR vector can be computed in $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ time, while satisfying the following uniform error bound:
+Namely, the aPPR vector can be computed in  order $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ time, while satisfying the following uniform error bound:
 \begin{equation}
 \label{eqn: appr_error}
-\textrm{for all $x \in \Xbf$}, \quad \pbf(x) - \epsilon \deg_{n,r}(x)\leq \pbf^{(\epsilon)}(x) \leq \pbf(x)
+\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq \pbf^{(\epsilon)}(u) \leq \pbf(u)
 \end{equation}
@@
 	\begin{enumerate}
-		\item Assume \ref{asmp: valid_region} holds. Then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item Assume \ref{asmp: C'_bounded_density} holds. If
-		\begin{equation*}
-		\kappa(\Cset) \leq c_7 \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d \nu_d}{\nu(\Csig)}
-		\end{equation*}
+		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
 		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
@@
 \section{Analysis}
-Given an arbitrary graph $G = (V,E)$ and candidate cluster $S \subseteq G$, \cite{zhu2013} bound the volume of $\Cest \setminus S$ and $S \setminus \Cest$ in terms of the normalized cut and inverse mixing time of $S$.
+\label{sec: analysis}
+
+Given an arbitrary graph $G = (V,E)$ and candidate cluster $S \subseteq G$, \citet{zhu2013} bound the volume of $\Cest \setminus S$ and $S \setminus \Cest$ in terms of the normalized cut and inverse mixing time of $S$.
 The key to deriving the algorithmic results of the previous section is therefore to show that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: embedding} translate to meaningful bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
-Doing so constitutes the bulk of our technical effort.
+In doing so, we expose how some of the geometric conditions introduced in the last section contribute to the difficulty of the clustering problem.
 
-\subsection{Upper Bound on Normalized Cut}
-
-We start with an upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
-$\Cset_\sigma[\Xbf]$. (In Theorem \ref{thm: conductance_upper_bound}, the upper bound on the density in
-Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
-the parameter $\Lambda_\sigma>0$ from the theorem statement.) For simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
+\paragraph{Normalized cut.} We start with an upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
+$\Cset_\sigma[\Xbf]$. For simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
 
@@
 	Assumptions \ref{asmp: bounded_density}-\ref{asmp: low_noise_density}, and \ref{asmp: bounded_volume} for some 
-	$r, \sigma, \lambda_{\sigma}, c_0, \gamma > 0$. 
+	$r, \sigma, \lambda_{\sigma}, c_0, \gamma > 0$ (no bound on maximum density is needed). 
 	Then for any $0 < \delta < 1$, $\epsilon > 0$, if
@@
 
-\subsection{Lower Bound on Inverse Mixing Time}
+\paragraph{Inverse mixing time.}
 For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
@@
 for the $t$-step transition probability of a random walk over $G[S]$
-originating at $v$.\footnote{Given a starting node $v$ and and a random walk
-	defined by transition probability matrix $\mathbf{P}$, the notation $e_v
-	\mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
-	steps.}   Also write \smash{$\pi = (\pi(u))_{u \in S}$}
-for the stationary distribution of this random walk.  (Given the definition of 
-$\Wbf_S$, it is well-known that a unique stationary distribution exists and is given by
-\smash{$\pi(u) = \deg(u; G[S])/\vol(S; G[S])$}.)
+originating at $v$. Also write \smash{$\pi = (\pi_u)_{u \in S}$}
+for the stationary distribution of this random walk.  (As
+$\Wbf_S$ is the transition matrix of a lazy random walk, it is well-known that a unique stationary distribution exists and is given by
+\smash{$\pi_u = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where $\Dbf_S$ is the degree matrix of $G[S]$.)
 
@@
 	\label{thm: mixing_time_upper_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, K > 0$.
-Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, L > 0$.
+Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability $1$
 	\begin{equation}
@@
 
-So far as we are aware, Theorem \ref{thm: mixing_time_upper_bound} is a \textcolor{red}{novel bound} on the mixing time of random walks over neighborhood graphs. 
+So far as we are aware, Theorem \ref{thm: mixing_time_upper_bound} is the first bound on the mixing time of random walks over neighborhood graphs which is independent of $n$, the number of vertices.
 \begin{remark}
@@
 
-We provide numerical experiments to investigate the tightness of our bounds on the cluster quality criteria normalized cut and mixing time, and examine the performance of \pprspace on the 'two moons' dataset.
+We provide numerical experiments to investigate the tightness of our bounds in on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the 'two moons' dataset.
 For space reasons, we defer details of the experimental settings to the supplement.
@@
 Figure \ref{fig:fig1} shows these theoretical bounds compared to the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $D$ and thickness $\sigma$ of the cluster $\Cset$.
+Panels $(a)$ and $(b)$ show the empirical clusters under consideration for two different values of $D,\sigma$.
 
@@
 
-\paragraph{\pprspace, normalized cut, and density clustering comparison.}
+\paragraph{Empirical behavior of \ppr.}
 
@@
 
-To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the famous 'two moons' dataset (with added 2$d$ Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
+The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \citep{chaudhuri2010}.
 
@@
 Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, and that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail.
-
-The fourth row illustrates the effect of dimension.
+In the fourth row, 10$d$ Gaussian noise was added.
 The gray dots in $(m)$ (as in $(a), (e)$ and $(i)$ are observations in low-density regions.
@@
 \label{sec: discussion}
-For a clustering algorithm and a given object (such as a graph or set of points), there are an almost limitless number of ways to define what the 'right' clustering is.
-We have considered a few such ways -- density level sets, and the bicriteria of normalized cut, inverse mixing time -- and shown that under the right conditions, the latter agree with the former, with resulting algorithmic consequences.
-
+For given data, there are an almost limitless number of ways to define what the 'right' clustering is.
+We have considered one such notion -- density upper level sets -- and have detailed a set of natural geometric criteria which, when appropriately satisfied, translate to provable bounds on estimation of the cluster by \ppr.
 We do not provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.

### 2019-05-22 neurips/local_spectral_density_clustering_neurips.tex
wednesday edits, reorganized folder

--- 2019-05-21 neurips/local_spectral_density_clustering_tuesday.tex
@@
 
-\newcommand{\diam}{\mathrm{diam}}
+\newcommand{\diam}{\rho}
 \newcommand{\set}[1]{\left\{#1\right\}}
@@
 \newcommand{\Psibf}{\Psi_{u}}
+\newcommand{\taubf}{\tau_{u}}
 \newcommand{\dist}{\mathrm{dist}}
@@
 \newcommand{\qbf}{\mathbf{q}}
-\newcommand{\ebf}[1]{\mathbf{e}_{#1}}
+\newcommand{\ebf}[1]{{e}_{#1}}
 \newcommand{\pibf}{\bm{\pi}}
 
-%%% Matrices
-\newcommand{\Abf}{\mathbf{A}}
+%%% Matrices (no bold font)
+\newcommand{\Abf}{A}
 \newcommand{\Xbf}{X}             % removed bold font 
-\newcommand{\Wbf}{\mathbf{W}}
-\newcommand{\Lbf}{\mathbf{L}}
-\newcommand{\Dbf}{\mathbf{D}}
-\newcommand{\Ibf}[1]{\mathbf{I}_{#1}}
+\newcommand{\Wbf}{W}
+\newcommand{\Lbf}{L}
+\newcommand{\Dbf}{D}
+\newcommand{\Ibf}[1]{I_{#1}}
 
@@
   Spectral clustering methods are a family of popular nonparametric clustering
-  tools.  Recent works have proposed and analyzed \emph{local} spectral methods,
+  tools.  Recent works have proposed and analyzed \emph{local} spectral methods, such as Personalized PageRank (\ppr),
   which extract clusters using locally-biased random walks around a user-specified
-  seed node.  In contrast to existing works, we analyze PPR in a traditional
+  seed node.  In contrast to existing results, we analyze PPR in a traditional
   statistical learning setup, where we obtain samples from an unknown
@@
   clusters).  We prove that PPR, run on a neighborhood graph, extracts
-  sufficiently salient density clusters, and provide empirical support of our theory.
+  sufficiently salient density clusters, and provide empirical support for our theory.
 \end{abstract}
@@
 
-Local spectral clustering techinques have been practically very successful
+Local spectral clustering techniques have been practically very successful
 \citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
@@
 connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
-for some threshold $\lambda > 0$ (a central object of central interest in the
+for some threshold $\lambda > 0$ (a central object of interest in the
 classical statistical literature on clustering, dating back to
@@
 
-\paragraph{PPR on a Neighborhood Graph.}We now describe the clustering algorithm that will be our focus for the rest of 
+\paragraph{PPR on a neighborhood graph} We now describe the clustering algorithm that will be our focus for the rest of 
 the paper. We start with the geometric graph that we form based on the samples 
@@
 \leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.
-We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if and only if $(u,v) \in E$, and by $\Dbf$ the degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$.
+We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise, by $\Dbf$ the diagonal degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.
 
@@
 \end{equation}
-where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the (lazy) random walk matrix over $G_{n,r}$ 
-and $e_{v}$ denotes indicator vector for node $v$ (with a 1 in the $v$th
+where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over $G_{n,r}$ 
+and $e_{v}$ denotes the indicator vector for node $v$ (with a 1 in the $v$th
 position and 0 elsewhere).
@@
 \end{equation}
-For a set $S \subseteq V$ with complement $S^c = V \setminus S$, the normalized cut is defined to be 
+We will use normalized cut to determine which sweep cut $S_{\beta}$ is the best cluster estimate.
+For a set $S \subseteq V$ with complement $S^c = V \setminus S$, we define the cut as $\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c} \Abf_{uv}$, the volume as $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and the \emph{normalized cut} as
 \begin{equation}
@@
 \end{equation}
-where $\cut(S;G_{n,r}) = \sum_{u \in S, v \in S^c} \Abf_{uv}$ and $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$. Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
+Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
 (\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
 \smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we then output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
+algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
 For concreteness, we summarize this procedure in Algorithm \ref{alg: ppr}.
@@
 
-\paragraph{Estimation of density clusters.}
+\paragraph{Estimation of density clusters}
 
@@
 	For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S}$ is 
+	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$ is 
 	\begin{equation}
 	\label{eqn: misclassification_rate}
-	\Delta(\Cest, \mathcal{S}) = \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup \mathcal{S}[\Xbf] \setminus \Cest}.
+	\Delta(\Cest, \mathcal{S}) := \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup \mathcal{S}[\Xbf] \setminus \Cest}.
 	\end{equation}
@@
 However, the symmetric set difference does not account for the distance points in $\widehat{C} \setminus \mathcal{S}[\Xbf]$ may be from $\mathcal{S}$ \citep{singh2009}.
-Therefore we introduce a second notion of cluster estimation, first introduced by \citet{hartigan1981} and defined asymptotically, which measures whether $\widehat{C}$ can distinguish any two distinct elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
+We therefore give a second notion of cluster estimation, first introduced by \citet{hartigan1981} and defined asymptotically, which measures whether $\widehat{C}$ can distinguish any two distinct elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
 
@@
 \end{definition}
-\paragraph{Summary of results.}
+\paragraph{Summary of results}
 A summary of our main results (and outline for the rest of this paper) is as
@@
 \begin{enumerate}
-	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions, formalize a measure of difficulty based on these geometric conditions, and show that when properly initialized, the symmetric set difference of Algorithm \ref{alg: ppr} is upper bounded by this difficulty measure.
+	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions on the density cluster $\Cset$, formalize a measure of difficulty based on these geometric conditions, and show that when Algorithm \ref{alg: ppr} is properly initialized, the symmetric set difference of $\widehat{C}$ and a thickened version of the density cluster $\Csig$ is upper bounded by this difficulty measure.
 
-	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will perform consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-In Corollary \ref{cor: appr}, we establish that both metrics of cluster estimation can be bounded with respect to an approximate form of \ppr, which can be efficiently computed.
+	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will consistently estimate a density cluster in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
 
-	\item In Section \ref{sec: analysis}, we detail some of the main technical machinery required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
+	\item In Section \ref{sec: analysis}, we detail some of the analysis required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
 
 	\item In Section \ref{sec: experiments}, we empirically
-	demonstrate the tightness of the bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, and provide examples showing how violations of the geometric conditions we require manifestly
+	demonstrate the tightness of our analysis, and provide examples showing how violations of the geometric conditions we require manifestly
 	impact density cluster recovery by \ppr.  
@@
 
-\paragraph{Related Work. }
+\paragraph{Related work}
 
-In addition to the background given earlier, a few related lines of work are worth
+In addition to the background given previously, a few related lines of work are worth
 highlighting. Similar in spirit to our results are the works
 \citep{shi2009,schiebinger2015}, who study the consistency of
-spectral algorithms in recovering the latent labels in certain parametric and
+spectral algorithms in recovering the latent labels in certain
 nonparametric mixture models. These results focus on global rather than local
 algorithms, and as such impose global rather than local conditions on the nature
-of the density. Moreover, they do not in general ensure recovery of density
+of the density. Moreover, they do not in general guarantee recovery of density
 clusters, which is the focus in our work.
-Perhaps most importantly, these works rely on general cluster saliency conditions, which depend implicitly on many distinct geometric aspects of the cluster $\Cset$ under consideration.
-We make this dependence explicit, and in so doing, expose the role each geometric condition plays in the clustering problem.
+Perhaps most importantly, these works rely on general cluster saliency conditions, which implicitly depend on many distinct geometric aspects of the cluster $\Cset$ under consideration.
+We make this dependence more explicit, and in doing so expose the role each geometric condition plays in the clustering problem.
 
 Additionally, we note that density clustering and level set estimation is a well-studied problem.
-\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} prove minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
+\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} exhibit minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
 Our goal is not to improve on these results, or offer yet another algorithm for level set estimation; indeed, seen as a density clustering algorithm, \pprspace has none of the optimality guarantees of the previous works.
-This is fact a major point of our article: \pprspace can provably recover density clusters, but only under strong geometric conditions.
+Rather, our motivation is to better understand and characterize the distinctions between those density clusters which are well conditioned for local spectral algorithms, and those which are not.
 
-\section{Estimation of Well-Conditioned Density Clusters.}
+\section{Estimation of well-conditioned density clusters}
 \label{sec: consistent_cluster_estimation_with_ppr}
 
-We formalize some geometric conditions, before using these to define a measure $\kappa(\Cset)$ which encodes the difficulty \pprspace will have estimating $\Cset$.
+We formalize some geometric conditions, before using these to define a condition number $\kappa(\Cset)$ which measures the difficulty \pprspace will have in estimating $\Cset$.
 We motivate this measure, and the underlying geometric conditions, by giving density cluster estimation guarantees for Algorithm \ref{alg: ppr} in terms of $\kappa(\Cset)$.
 
-\paragraph{Geometric Conditions on Density Clusters.}
+\paragraph{Geometric conditions on density clusters}
 
 As mentioned previously, successful recovery of a density cluster by \pprspace requires the density cluster to be geometrically well-conditioned.
-At a minimum, we wish to sets $\Cset$ which contain arbitrarily thin bridges or spikes, and therefore as in \cite{chaudhuri2010} we introduce a buffer zone around $\Cset$.
+At a minimum, we wish to avoid sets $\Cset$ which contain arbitrarily thin bridges or spikes, and therefore as in \cite{chaudhuri2010} we introduce a buffer zone around $\Cset$.
 Let $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$.
-For a some $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
+For $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
 We denote the distance between $x$ and $\Cset$ as $\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$, and for a given $\sigma > 0$, we refer to $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$ as the $\sigma$-expansion of $\Cset$.
-We now state our conditions with respect to $\Csig$, and provide some intuition afterwards.
+We now state our conditions with respect to $\Csig$.
 
@@
 	\label{asmp: bounded_density}
-	\emph{Bounded density within cluster:} There exist constants $\lambda_{\min}, \Lambda_{\min}$ $0 < \lambda_{\sigma} <
-	\Lambda_{\sigma} < \infty$ such that $ \lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma}.$
+	\emph{Bounded density within cluster:} There exist constants $\lambda_{\sigma}, \Lambda_{\sigma}$ such that $0 < \lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma} < \infty$.
 
@@
 	$$
-	\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma},
+	\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}.
 	$$
@@
 	\emph{Lipschitz embedding:}
-	There exists $g: \Reals^d \to \Reals^d$ which has the following properties: i) there exists a convex set $\mathcal{K} \subseteq \Rd$ with $\diam(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =: D < \infty$, such that $\Csig = g(\mathcal{K})$, ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; iii) for some $L \geq 1$,
+	There exists $g: \Reals^d \to \Reals^d$ which has the following properties: i) there exists a convex set $\mathcal{K} \subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =: \diam < \infty$, such that $\Csig = g(\mathcal{K})$, ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$, and iii) for some $L \geq 1$,
 	\begin{equation*}
@@
 	\end{equation*}
-	Simply put, $\Csig$ is the image of a convex set with finite diameter, under a biLipschitz, measure preserving transformation.
+	Simply put, $\Csig$ is the image of a convex set with finite diameter, under a  measure preserving, biLipschitz transformation.
 	\item
@@
 	Let the neighborhood graph radius $0 < r \leq \sigma/2d$ be such that
-	\begin{equation}
-	\label{eqn: weighted_cluster_volume}
+	\begin{equation*}
 	2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx
-	\end{equation}
+	\end{equation*}
 \end{enumerate}
 
-Thinking of $\Csig[\Xbf]$ as a subset of vertices in $G_{n,r}$, we would like $\Csig[\Xbf]$ to be internally well-connected, while being poorly connected to the rest of $\Xbf$.
-The cluster separation \ref{asmp: cluster_separation} and low noise density \ref{asmp: low_noise_density} conditions guarantee low connectivity between $\Csig[\Xbf]$ and $\Xbf \setminus \Csig[\Xbf]$ in $G_{n,r}$, whereas \ref{asmp: bounded_density} and \ref{asmp: embedding} ensure high connectivity within $\Csig[\Xbf]$.
-It may not be immediately obvious how \ref{asmp: embedding} contributes to geometric conditioning.
-For now, we observe merely that random walks will mix slowly over sets with large diameter, and comment on this condition in more detail in Section \ref{sec: analysis}.
-Finally, \ref{asmp: bounded_volume} is a relatively harmless technical condition, merely excluding the case where $\vol(\Csig[\Xbf]; G_{n,r}) > \vol(\Xbf; G_{n,r})/2$.
+To motivate these conditions, for an arbitrary graph $G = (V,E)$ and subset of vertices $S \subseteq V$, consider the normalized cut $\Phi(S;G)$ (defined as in \eqref{eqn: normalized_cut}), as well as the mixing time of a random walk over the induced subgraph $G[S]$ (defined in Section \ref{sec: analysis} by \eqref{eqn: mixing_time}, and denoted by $\tau_{\infty}(G[S])$).
+In \citet{zhu2013}, it is shown that for a constant $c > 0$, the \pprspace estimate $\widehat{C}$ of $S$ satisfies
+\begin{equation}
+\label{eqn: graph_symmetric_set_difference_1}
+\vol(\widehat{C} \setminus S; G) + \vol(S \setminus \widehat{C}; G) \leq c \bigl( \Phi(S,G) \cdot \tau_{\infty}(G[S])\bigr) \vol(S;G)
+\end{equation}
+where the left hand side resembles a (degree-weighted) form of the symmetric set difference of \eqref{eqn: misclassification_rate}.
 
-We can now formally define the \textcolor{red}{condition number}, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
+As we will formally show in Section \ref{sec: analysis}, the conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume} allow us to upper bound the normalized cut $\Phi(\Csig[\Xbf]; G_{n,r})$, and the mixing time $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
+Intuitively, the low noise \ref{asmp: cluster_separation} and cluster separation \ref{asmp: low_noise_density} assumptions yield an upper bound on $\cut(\Csig[\Xbf]; G_{n,r})$, the lower bound on density in \ref{asmp: bounded_density} yields a lower bound on $\vol(\Csig[\Xbf]; G_{n,r})$, and along with \ref{asmp: bounded_volume}, which ensures $\vol(\Csig[\Xbf]; G_{n,r}) \leq \vol(\Csig[\Xbf]^c; G_{n,r})$, these imply an upper bound on the normalized cut.
+\ref{asmp: bounded_density} and \ref{asmp: embedding} preclude bottlenecks in the induced subgraph $G_{n,r}[\Csig[\Xbf]]$, and combined with the upper bound on diameter in \ref{asmp: embedding}, they yield an upper bound on the mixing time over this subgraph.
+
+\paragraph{Condition number} We will return to the topic of conditions in Section \ref{sec: analysis}.
+Now, we define the condition number, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
+Motivated by \eqref{eqn: graph_symmetric_set_difference_1}, we will set $\kappa(\Cset)$ to be an upper bound on $\Phi(\Csig[\Xbf]; G_{n,r}) \cdot \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
 The smaller $\kappa(\Cset)$ is, the more success \pprspace will have in recovering $\Cset$.
-Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those geometric parameters detailed in \ref{asmp: bounded_density} - \ref{asmp: bounded_volume}.
+Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain those geometric parameters detailed in \ref{asmp: bounded_density} - \ref{asmp: bounded_volume}.
 
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$, Then, for universal constants $c_1, c_2, c_3 > 0$ \textcolor{red}{to specified later}, we set
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$.
+Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later, we set
 	\begin{equation}
@@
 	:= c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}},~ 
-	\Psibf(\theta) := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
+	\taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
 	\end{equation}
-	and letting $\kappa(\Cset) := \frac{\Phibf(\theta)}{\Psibf(\theta)}$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
+	and letting $\kappa(\Cset) := \Phi_{u}(\theta) \cdot \tau_{u}(\theta)$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
 \end{definition}
 
-At first glance \eqref{eqn: condition_number_1} may appear mysterious, but as will be shown in Section \ref{sec: analysis}, $\Phibf(\theta)$ and $\Psibf(\theta)$ are merely upper bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
-In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, it is shown that the ratio of normalized cut to inverse mixing time is a fundamental quantity governing the clustering performance of \pprspace on a general graph.
-$\kappa(\Cset)$ upper bounds this ratio for an empirical density cluster over the neighborhood graph $G_{n,r}$, and is therefore a natural criterion to measure difficulty of the density clustering task.
+We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds on $\Phi(\Csig[\Xbf]; G_{n,r})$ and $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ that we derive in Section \ref{sec: analysis}.
 
-\paragraph{Well-initialized algorithm.}
+\paragraph{Well-initialized algorithm}
 
-As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific choices or ranges of each of the user-specified parameters.
+As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified parameters.
 
@@
 \label{eqn: initialization}
-r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \Psibf(\theta) \nonumber,  \\
+0 < r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)} \nonumber,  \\
 v \in \Csig[\Xbf]^g, & ~\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx
@@
 In practice it is clearly not feasible to set hyperparameters based on the underlying (unknown) density $f$.
-Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is unclear how this scheme would affect the performance of \pprspace in the density clustering context.
+Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is not obvious how this scheme would affect the performance of \pprspace in the density clustering context.
 
-\paragraph{Density cluster estimation by \ppr.}
+\paragraph{Density cluster estimation by \ppr}
 
-Theorem 1 of \cite{zhu2013}, combined with the results of Section \ref{sec: analysis}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),\footnote{For sequences $a_n$ and $b_n$, we write $a_n \lesssim b_n$ if there exists constant $c$ such that $a_n \leq c b_n$ for all $n$ sufficiently large.
-}
+The results of Section \ref{sec: analysis}, along with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the volume of $\Cest \setminus \Csig[\Xbf]$ and $\Csig[\Xbf] \setminus \Cest$,
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]), \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \lesssim \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
+\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
 \end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
-To do so, we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
+Let $\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure of the unit ball $B = B(0,1)$.
 \begin{enumerate}[label=(A\arabic*)]
-	\setcounter{enumi}{4}
+	\setcounter{enumi}{5}
 	\item 
 	\label{asmp: valid_region}
-	\emph{Support of $f$:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
-Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
+	\emph{Regular support:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
+Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$.
 \end{enumerate}
-Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, $\mathcal{X}$ is a $\sigma$-expanded set.
+Note that the latter condition in \ref{asmp: valid_region} will be satisfied if, for instance, the support $\mathcal{X}$ is a $\sigma$-expanded set.
 
@@
 	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
-Then, there exists universal constant $c_4 > 0$ such that with probability tending to one as $n \to \infty$,
+Then, there exists a universal constant $c_4 > 0$ such that with probability tending to $1$ as $n \to \infty$,
 	\begin{equation}
@@
 The proof of Theorem \ref{thm: misclassification_rate}, along with all other proofs in this paper, can be found in the supplementary material.
-We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the \textcolor{red}{condition number}.
+We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the condition number $\kappa(\Cset)$.
 
 Neither \eqref{eqn: graph_symmetric_set_difference} nor Theorem \ref{thm: misclassification_rate} imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over $\pbf$ for all $u \in \Cset, w \in \Cset'$
+This notion of consistency requires a uniform bound over $\pbf$: namely, for all $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$, and each $u \in \Cset, w \in \Cset'$,
 \begin{equation}
 \label{eqn: ppr_gap}
-\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}}.
+\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}},
 \end{equation}
@@
 \begin{enumerate}[label=(A\arabic*)]
-	\setcounter{enumi}{5}
+	\setcounter{enumi}{6}
 	\item 
 	\label{asmp: C'_bounded_density}
-	\emph{$\Cset'$- bounded density :} For each $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$ and for all $x \in \Cset' + \sigma B$, $\lambda_{\sigma} \leq f(x)$ where $\sigma,\lambda_{\sigma}$ are as in \ref{asmp: bounded_density}.
+	\emph{Bounded density:} Letting $\sigma,\lambda_{\sigma}$ be as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and for all $x \in \Csig'$, $\lambda_{\sigma} \leq f(x)$.
 \end{enumerate}
@@
 	\label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume \ref{asmp: C'_bounded_density} holds.
-If Algorithm \ref{alg: ppr} is well-initialized, there exists universal constant $c_5 > 0$ such that if
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}.
+If Algorithm \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 > 0$ such that if
 	\begin{equation}
@@
 \end{theorem}
-A few remarks are in order.
 
 \begin{remark}
-	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a misclassification rate on the order of $r^d$.
-(See Theorem \ref{thm: misclassification_rate}).
+	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$ on the order of $r^d$.
 In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points will be misclassified.
-This strong condition is the price we pay in order to obtain the uniform bound of \ref{eqn: ppr_gap}.
+This strong condition is the price we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}.
 \end{remark}
@@
 
-\paragraph{Approximate \pprspace vector.}
+\paragraph{Approximate \pprspace vector}
 
@@
 \label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq \pbf^{(\epsilon)}(u) \leq \pbf(u)
+\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq \pbf^{(\epsilon)}(u) \leq \pbf(u). 
 \end{equation}
@@
 Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} leads to analogous results which hold with respect to $\pbf^{(\epsilon)}$.
-
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
-	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
+We formally state and prove this fact in the supplementary material.
 
@@
 
-Given an arbitrary graph $G = (V,E)$ and candidate cluster $S \subseteq G$, \citet{zhu2013} bound the volume of $\Cest \setminus S$ and $S \setminus \Cest$ in terms of the normalized cut and inverse mixing time of $S$.
-The key to deriving the algorithmic results of the previous section is therefore to show that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: embedding} translate to meaningful bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
-In doing so, we expose how some of the geometric conditions introduced in the last section contribute to the difficulty of the clustering problem.
+The primary technical contribution of our work is showing that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} translate to meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
+In doing so, we elaborate on how some of the geometric conditions introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr} contribute to the difficulty of the clustering problem.
 
-\paragraph{Normalized cut.} We start with an upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
+\paragraph{Normalized cut} We start with a finite sample upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
 $\Cset_\sigma[\Xbf]$. For simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
@@
 \begin{remark}
-	Observe that the diameter $D$ is absent from Theorem \ref{thm: conductance_upper_bound}, in contrast to the difficulty function $\kappa(\Cset)$, which worsens (increases) as $D$ increases.
+	\label{rmk: diameter}
+	Observe that the diameter $\rho$ is absent from Theorem \ref{thm: conductance_upper_bound}, in contrast to the difficulty function $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases.
 This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
-It suggests that \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$, if the diameter $D$ is large.
+It suggests that if the diameter $\rho$ is large, \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$.
 This intuition will be supported by simulations in Section \ref{sec: experiments}.
@@
 
-\paragraph{Inverse mixing time.}
-For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
-$S$ (where the edges are $E_S = E \cap (S \times S)$), let $\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write 
+\paragraph{Inverse mixing time}
+For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the subgraph induced by 
+$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write 
 $$
@@
 $$
-for the $t$-step transition probability of a random walk over $G[S]$
-originating at $v$. Also write \smash{$\pi = (\pi_u)_{u \in S}$}
+for the $t$-step transition probability of the lazy random walk over $G[S]$
+originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
 for the stationary distribution of this random walk.  (As
 $\Wbf_S$ is the transition matrix of a lazy random walk, it is well-known that a unique stationary distribution exists and is given by
-\smash{$\pi_u = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where $\Dbf_S$ is the degree matrix of $G[S]$.)
+\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where $\Dbf_S$ is the degree matrix of $G[S]$.)
 
@@
 \end{equation}
-We lower bound the inverse mixing time $\Psi_{n,r}(\Csig[\Xbf]) = 1/\tau_{\infty}(\Csig[\Xbf])$ of $\Csig[\Xbf]$, or equivalently we upper bound the mixing time.
+In the following theorem, we give an asymptotic (in the number of vertices $n$) upper bound on $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
 
@@
 	\label{thm: mixing_time_upper_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, L > 0$.
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$.
 Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability $1$
@@
 	\label{eqn: mixing_time_upper_bound}
-	\limsup_{n \to \infty}\tau_{\infty}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
+	\limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
 	\end{equation}
@@
 
-So far as we are aware, Theorem \ref{thm: mixing_time_upper_bound} is the first bound on the mixing time of random walks over neighborhood graphs which is independent of $n$, the number of vertices.
+To the best of our knowledge, Theorem \ref{thm: mixing_time_upper_bound} is the first bound, albeit asymptotic, on the mixing time of random walks over neighborhood graphs which is independent of $n$, the number of vertices.
 \begin{remark}
 	The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$ play an important role in proving the upper bound of Theorem \ref{thm: mixing_time_upper_bound}.
-There is some interdependence between $L$ and other geometric parameters $\sigma$ and $D$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
-However, it is not possible to eliminate this condition without incurring an additional factor of at least $(D/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ is a dumbbell-like set consisting of two balls of diameter $D$ linked by a cylinder of radius $\sigma$.
+There is some interdependence between $L$ and other geometric parameters $\sigma$ and $\rho$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
+However, it is not possible to eliminate this condition without incurring an additional factor of at least $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
 \citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding biLipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
@@
 
-We provide numerical experiments to investigate the tightness of our bounds in on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the 'two moons' dataset.
+We provide numerical experiments to investigate the tightness of our bounds on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the ``two moons'' dataset.
 For space reasons, we defer details of the experimental settings to the supplement.
 
-\paragraph{Validating Theoretical Bounds.}
+\paragraph{Validating theoretical bounds}
 
@@
 	\centering
-	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+	\begin{adjustbox}{minipage=\linewidth}
 		\begin{subfigure}{.33\linewidth}
@@
 As we do not provide any theoretical lower bounds, we investigate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
-Figure \ref{fig:fig1} shows these theoretical bounds compared to the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $D$ and thickness $\sigma$ of the cluster $\Cset$.
-Panels $(a)$ and $(b)$ show the empirical clusters under consideration for two different values of $D,\sigma$.
+Figure \ref{fig:fig1} compares these theoretical bounds with the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\Cset$.
+Panels $(a)$ and $(b)$ show the resulting empirical clusters for two different values of $\rho$ and $\sigma$.
 
 Panels $(d)$ and $(f)$ show our theoretical bounds on mixing time tracking closely with empirical mixing time, in both 2 and 3 dimensions.\footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
-Therefore only comparison of slopes, rather than intercepts, is meaningful.} This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both expansion parameter $\sigma$ and diameter $D$.
+Therefore only comparison of slopes, rather than intercepts, is meaningful.} This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both expansion parameter $\sigma$ and diameter $\rho$.
 The story in panels $(c)$ and $(e)$ is less obvious.
-We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma \approx D$.
-As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
+We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma $ and $\rho$ are approximately equal.
+As the ratio $\rho/\sigma$ grows, we see the slopes of the empirical curves become more similar to those predicted by theory.
 
-\paragraph{Empirical behavior of \ppr.}
+\paragraph{Empirical behavior of \ppr}
 
@@
 	\centering
-	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+	\begin{adjustbox}{minipage=\linewidth}
 		\begin{subfigure}{.24\linewidth}
@@
 		\end{subfigure}
-
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\caption{True density (column 1), \pprspace (column 2), normalized cut (column 3) and estimated density (column 4) clusters for 4 different simulated data sets.
+		\caption{True density (column 1), \pprspace (column 2), normalized cut (column 3) and estimated density (column 4) clusters for 3 different simulated data sets.
 Seed node for \pprspace denoted by a black cross.}
@@
 
-To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the famous 'two moons' dataset (with added 2$d$ Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
+To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
 The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \citep{chaudhuri2010}.
 
-Rows 1-3 show the degrading ability of \pprspace to recover density clusters as the two moons become less salient.
-Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, and that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail.
-In the fourth row, 10$d$ Gaussian noise was added.
-The gray dots in $(m)$ (as in $(a), (e)$ and $(i)$ are observations in low-density regions.
-While the \pprspace sweep cut $(n)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C_n$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+Figure \ref{fig:fig2} shows the degrading ability of \pprspace to recover density clusters as the two moons become less well-separated.
+Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, supporting our claim from Remark \ref{rmk: diameter}.
+Additionally, we note that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail, lending empirical weight to our overall message that \pprspace recovers only geometrically well-conditioned density clusters.
 
@@
 \label{sec: discussion}
-For given data, there are an almost limitless number of ways to define what the 'right' clustering is.
+For given data, there are an almost limitless number of ways to define what the ``right'' clustering is.
 We have considered one such notion -- density upper level sets -- and have detailed a set of natural geometric criteria which, when appropriately satisfied, translate to provable bounds on estimation of the cluster by \ppr.
-We do not provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
+We do not, however, provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
 Although we investigate the matter empirically, this is a direction for future work.

### 2019-05-22 neurips/old_versions/local_spectral_density_clustering_monday.tex
wednesday edits, reorganized folder

--- 2019-05-20 neurips/local_spectral_density_clustering_monday.tex
@@
 	\label{asmp: valid_region}
-	\emph{Valid region:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
+	\emph{\textcolor{red}{Valid region:}} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
 Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
@@
 To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+The first column shows empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
 
-Rows 1-3 show the degrading ability of \pprspace to recover density clusters as the two moons become less salient.
+Figure \ref{fig:fig2} show the degrading ability of \pprspace to recover density clusters as the two moons become less salient.
 Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, and that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail.
-
-The fourth row illustrates the effect of dimension.
-The gray dots in $(m)$ (as in $(a), (e)$ and $(i)$ are observations in low-density regions.
-While the \pprspace sweep cut $(n)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C_n$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 

### 2019-05-22 neurips/old_versions/local_spectral_density_clustering_tuesday.tex
wednesday edits, reorganized folder

--- 2019-05-22 neurips/local_spectral_density_clustering_neurips.tex
@@
 \newcommand{\Psibf}{\Psi_{u}}
-\newcommand{\taubf}{\tau_{u}}
 \newcommand{\dist}{\mathrm{dist}}
@@
   Spectral clustering methods are a family of popular nonparametric clustering
-  tools.  Recent works have proposed and analyzed \emph{local} spectral methods, such as Personalized PageRank (\ppr),
+  tools.  Recent works have proposed and analyzed \emph{local} spectral methods,
   which extract clusters using locally-biased random walks around a user-specified
@@
 
-Local spectral clustering techniques have been practically very successful
+Local spectral clustering techinques have been practically very successful
 \citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
@@
 connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
-for some threshold $\lambda > 0$ (a central object of interest in the
+for some threshold $\lambda > 0$ (a central object of central interest in the
 classical statistical literature on clustering, dating back to
@@
 \leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.
-We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise, by $\Dbf$ the diagonal degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.
+We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if and only if $(u,v) \in E$, and by $\Dbf$ the diagonal degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$.
 
@@
 \end{equation}
-where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over $G_{n,r}$ 
-and $e_{v}$ denotes the indicator vector for node $v$ (with a 1 in the $v$th
+where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the (lazy) random walk matrix over $G_{n,r}$ 
+and $e_{v}$ denotes indicator vector for node $v$ (with a 1 in the $v$th
 position and 0 elsewhere).
@@
 \end{equation}
-We will use normalized cut to determine which sweep cut $S_{\beta}$ is the best cluster estimate.
-For a set $S \subseteq V$ with complement $S^c = V \setminus S$, we define the cut as $\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c} \Abf_{uv}$, the volume as $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and the \emph{normalized cut} as
+We need a metric to determine which sweep cut $S_{\beta}$ is the best cluster estimate.
+For a set $S \subseteq V$ with complement $S^c = V \setminus S$, we define the cut as $\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c} \Abf_{uv}$, the volume to be $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and the \emph{normalized cut} as
 \begin{equation}
@@
 \smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
+algorithms, see, e.g., \citep{zhu2013}.}, we then output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
 For concreteness, we summarize this procedure in Algorithm \ref{alg: ppr}.
@@
 	For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$ is 
+	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S} \cap \Xbf$ is 
 	\begin{equation}
@@
 \begin{enumerate}
-	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions on the density cluster $\Cset$, formalize a measure of difficulty based on these geometric conditions, and show that when Algorithm \ref{alg: ppr} is properly initialized, the symmetric set difference of $\widehat{C}$ and a thickened version of the density cluster $\Csig$ is upper bounded by this difficulty measure.
+	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions, formalize a measure of difficulty based on these geometric conditions, and show that when properly initialized, the symmetric set difference of Algorithm \ref{alg: ppr} is upper bounded by this difficulty measure.
 
-	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will consistently estimate a density cluster in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} consistently estimate a density cluster in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
 
-	\item In Section \ref{sec: analysis}, we detail some of the analysis required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
+	\item In Section \ref{sec: analysis}, we detail some of the main technical machinery required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
 
 	\item In Section \ref{sec: experiments}, we empirically
-	demonstrate the tightness of our analysis, and provide examples showing how violations of the geometric conditions we require manifestly
+	demonstrate the tightness of the bounds in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, and provide examples showing how violations of the geometric conditions we require manifestly
 	impact density cluster recovery by \ppr.  
@@
 
-\paragraph{Related work}
+\paragraph{Related Work. }
 
@@
 \citep{shi2009,schiebinger2015}, who study the consistency of
-spectral algorithms in recovering the latent labels in certain
+spectral algorithms in recovering the latent labels in certain parametric and
 nonparametric mixture models. These results focus on global rather than local
@@
 clusters, which is the focus in our work.
-Perhaps most importantly, these works rely on general cluster saliency conditions, which implicitly depend on many distinct geometric aspects of the cluster $\Cset$ under consideration.
-We make this dependence more explicit, and in doing so expose the role each geometric condition plays in the clustering problem.
+Perhaps most importantly, these works rely on general cluster saliency conditions, which depend implicitly on many distinct geometric aspects of the cluster $\Cset$ under consideration.
+We make this dependence explicit, and in so doing, expose the role each geometric condition plays in the clustering problem.
 
 Additionally, we note that density clustering and level set estimation is a well-studied problem.
-\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} exhibit minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
+\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} prove minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
 Our goal is not to improve on these results, or offer yet another algorithm for level set estimation; indeed, seen as a density clustering algorithm, \pprspace has none of the optimality guarantees of the previous works.
-Rather, our motivation is to better understand and characterize the distinctions between those density clusters which are well conditioned for local spectral algorithms, and those which are not.
+This is in fact a major point of our article: \pprspace can provably recover density clusters, but only under strong geometric conditions.
 
@@
 Let $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$.
-For $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
+For a some $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
 We denote the distance between $x$ and $\Cset$ as $\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$, and for a given $\sigma > 0$, we refer to $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$ as the $\sigma$-expansion of $\Cset$.
-We now state our conditions with respect to $\Csig$.
+We now state our conditions with respect to $\Csig$, and provide some intuition afterwards.
 
@@
 	$$
-	\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}.
+	\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma},
 	$$
@@
 
-To motivate these conditions, for an arbitrary graph $G = (V,E)$ and subset of vertices $S \subseteq V$, consider the normalized cut $\Phi(S;G)$ (defined as in \eqref{eqn: normalized_cut}), as well as the mixing time of a random walk over the induced subgraph $G[S]$ (defined in Section \ref{sec: analysis} by \eqref{eqn: mixing_time}, and denoted by $\tau_{\infty}(G[S])$).
-In \citet{zhu2013}, it is shown that for a constant $c > 0$, the \pprspace estimate $\widehat{C}$ of $S$ satisfies
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference_1}
-\vol(\widehat{C} \setminus S; G) + \vol(S \setminus \widehat{C}; G) \leq c \bigl( \Phi(S,G) \cdot \tau_{\infty}(G[S])\bigr) \vol(S;G)
-\end{equation}
-where the left hand side resembles a (degree-weighted) form of the symmetric set difference of \eqref{eqn: misclassification_rate}.
+Thinking of $\Csig[\Xbf]$ as a subset of vertices in $G_{n,r}$, we would like $\Csig[\Xbf]$ to be internally well-connected, while being poorly connected to the rest of $\Xbf$.
+The cluster separation \ref{asmp: cluster_separation} and low noise density \ref{asmp: low_noise_density} conditions guarantee low connectivity between $\Csig[\Xbf]$ and $\Xbf \setminus \Csig[\Xbf]$ in $G_{n,r}$, whereas \ref{asmp: bounded_density} and \ref{asmp: embedding} ensure high connectivity within $\Csig[\Xbf]$.
+It may not be immediately obvious how \ref{asmp: embedding} contributes to geometric conditioning.
+For now, we observe merely that random walks will mix slowly over sets with large diameter, and comment on this condition in more detail in Section \ref{sec: analysis}.
+Finally, \ref{asmp: bounded_volume} is a relatively harmless technical condition, merely excluding the case where $\vol(\Csig[\Xbf]; G_{n,r}) > \vol(\Xbf; G_{n,r})/2$.
 
-As we will formally show in Section \ref{sec: analysis}, the conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume} allow us to upper bound the normalized cut $\Phi(\Csig[\Xbf]; G_{n,r})$, and the mixing time $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
-Intuitively, the low noise \ref{asmp: cluster_separation} and cluster separation \ref{asmp: low_noise_density} assumptions yield an upper bound on $\cut(\Csig[\Xbf]; G_{n,r})$, the lower bound on density in \ref{asmp: bounded_density} yields a lower bound on $\vol(\Csig[\Xbf]; G_{n,r})$, and along with \ref{asmp: bounded_volume}, which ensures $\vol(\Csig[\Xbf]; G_{n,r}) \leq \vol(\Csig[\Xbf]^c; G_{n,r})$, these imply an upper bound on the normalized cut.
-\ref{asmp: bounded_density} and \ref{asmp: embedding} preclude bottlenecks in the induced subgraph $G_{n,r}[\Csig[\Xbf]]$, and combined with the upper bound on diameter in \ref{asmp: embedding}, they yield an upper bound on the mixing time over this subgraph.
-
-\paragraph{Condition number} We will return to the topic of conditions in Section \ref{sec: analysis}.
-Now, we define the condition number, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
-Motivated by \eqref{eqn: graph_symmetric_set_difference_1}, we will set $\kappa(\Cset)$ to be an upper bound on $\Phi(\Csig[\Xbf]; G_{n,r}) \cdot \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
+We can now formally define the condition number, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
 The smaller $\kappa(\Cset)$ is, the more success \pprspace will have in recovering $\Cset$.
@@
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$.
-Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later, we set
+	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$, Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later, we set
 	\begin{equation}
@@
 	:= c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}},~ 
-	\taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
+	\Psibf(\theta) := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \Biggr)^{-1}
 	\end{equation}
-	and letting $\kappa(\Cset) := \Phi_{u}(\theta) \cdot \tau_{u}(\theta)$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
+	and letting $\kappa(\Cset) := \frac{\Phibf(\theta)}{\Psibf(\theta)}$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
 \end{definition}
 
-We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds on $\Phi(\Csig[\Xbf]; G_{n,r})$ and $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ that we derive in Section \ref{sec: analysis}.
+At first glance \eqref{eqn: condition_number_1} may appear mysterious, but as will be shown in Section \ref{sec: analysis}, $\Phibf(\theta)$ and $\Psibf(\theta)$ are merely upper bounds on the normalized cut \eqref{eqn: normalized_cut} of $\Csig[\Xbf]$ in $G_{n,r}$, and the inverse of the mixing time (defined in Section \ref{sec: analysis} by \eqref{eqn: mixing_time}) of $\Csig[\Xbf]$ in $G_{n,r}$.
+In \cite{zhu2013}, building on the work of \cite{andersen2006} and others, it is shown that the ratio of normalized cut to inverse mixing time (or equivalently, the product of normalized cut and mixing time) is a fundamental quantity governing the clustering performance of \pprspace on a general graph.
+The condition number $\kappa(\Cset)$ is an asymptotic upper bound of this ratio for an empirical density cluster over the neighborhood graph $G_{n,r}$, and is therefore a natural criterion to measure difficulty of the density clustering task.
 
@@
 
-As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified parameters.
+As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific choices or ranges of each of the user-specified parameters.
 
@@
 \label{eqn: initialization}
-0 < r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)} \nonumber,  \\
+r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \Psibf(\theta) \nonumber,  \\
 v \in \Csig[\Xbf]^g, & ~\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx
@@
 In practice it is clearly not feasible to set hyperparameters based on the underlying (unknown) density $f$.
-Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is not obvious how this scheme would affect the performance of \pprspace in the density clustering context.
+Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is unclear how this scheme would affect the performance of \pprspace in the density clustering context.
 
@@
 
-The results of Section \ref{sec: analysis}, along with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the volume of $\Cest \setminus \Csig[\Xbf]$ and $\Csig[\Xbf] \setminus \Cest$,
+Theorem 1 of \cite{zhu2013}, combined with the results of Section \ref{sec: analysis}, immediately implies a bound on the volume of $\Cest \setminus \Csig[\Xbf]$ (and likewise $\Csig[\Xbf] \setminus \Cest$),\footnote{For sequences $a_n$ and $b_n$, we write $a_n \lesssim b_n$ if there exists constant $c$ such that $a_n \leq c b_n$ for all $n$ sufficiently large.
+}
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
+\vol_{n,r}(\Cest \setminus \Csig[\Xbf]), \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \lesssim \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
 \end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
-Let $\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure of the unit ball $B = B(0,1)$.
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree.
+To do so, we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
+Let $\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ be the measure of the unit ball $B = B(0,1)$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 \end{enumerate}
-Note that the latter condition in \ref{asmp: valid_region} will be satisfied if, for instance, the support $\mathcal{X}$ is a $\sigma$-expanded set.
+Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, the support $\mathcal{X}$ is a $\sigma$-expanded set.
 
@@
 	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
-Then, there exists a universal constant $c_4 > 0$ such that with probability tending to $1$ as $n \to \infty$,
+Then, there exists a universal constant $c_4 > 0$ such that with probability tending to one as $n \to \infty$,
 	\begin{equation}
@@
 The proof of Theorem \ref{thm: misclassification_rate}, along with all other proofs in this paper, can be found in the supplementary material.
-We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the condition number $\kappa(\Cset)$.
+We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the condition number.
 
@@
 	\label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}.
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume \ref{asmp: C'_bounded_density} holds.
 If Algorithm \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 > 0$ such that if
@@
 \begin{remark}
-	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$ on the order of $r^d$.
+	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a misclassification rate on the order of $r^d$.
+(See Theorem \ref{thm: misclassification_rate}).
 In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points will be misclassified.
@@
 
-The primary technical contribution of our work is showing that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} translate to meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
-In doing so, we elaborate on how some of the geometric conditions introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr} contribute to the difficulty of the clustering problem.
+Given an arbitrary graph $G = (V,E)$ and subset $S \subseteq G$, \citet{zhu2013} bound the volume of $\Cest \setminus S$ and $S \setminus \Cest$ in terms of the normalized cut and inverse mixing time of $S$.
+The key to deriving the algorithmic results of the previous section is therefore to show that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: embedding} translate to meaningful bounds on the normalized cut and inverse mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
+In doing so, we expose how some of the geometric conditions introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr} contribute to the difficulty of the clustering problem.
 
@@
 \begin{remark}
-	\label{rmk: diameter}
 	Observe that the diameter $\rho$ is absent from Theorem \ref{thm: conductance_upper_bound}, in contrast to the difficulty function $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases.
 This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
-It suggests that if the diameter $\rho$ is large, \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$.
+It suggests that \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$, if the diameter $\rho$ is large.
 This intuition will be supported by simulations in Section \ref{sec: experiments}.
@@
 \end{equation}
-In the following theorem, we give an asymptotic (in the number of vertices $n$) upper bound on $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
+We lower bound the inverse mixing time $\Psi_{n,r}(\Csig[\Xbf]) := 1/\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ of $\Csig[\Xbf]$, or equivalently we upper bound the mixing time.
 
@@
 
-We provide numerical experiments to investigate the tightness of our bounds on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the ``two moons'' dataset.
+We provide numerical experiments to investigate the tightness of our bounds in on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the 'two moons' dataset.
 For space reasons, we defer details of the experimental settings to the supplement.
@@
 As we do not provide any theoretical lower bounds, we investigate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
-Figure \ref{fig:fig1} compares these theoretical bounds with the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\Cset$.
+Figure \ref{fig:fig1} shows these theoretical bounds compared to the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\Cset$.
 Panels $(a)$ and $(b)$ show the resulting empirical clusters for two different values of $\rho$ and $\sigma$.
@@
 We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma $ and $\rho$ are approximately equal.
-As the ratio $\rho/\sigma$ grows, we see the slopes of the empirical curves become more similar to those predicted by theory.
+As the ratio $\rho/\sigma$ grows, we see the slopes of the empirical curves becoming more similar to those predicted by theory.
 
@@
 
-To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
+To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the well known 'two moons' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
 The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \citep{chaudhuri2010}.
@@
 Figure \ref{fig:fig2} shows the degrading ability of \pprspace to recover density clusters as the two moons become less well-separated.
-Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, supporting our claim from Remark \ref{rmk: diameter}.
-Additionally, we note that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail, lending empirical weight to our overall message that \pprspace recovers only geometrically well-conditioned density clusters.
+Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, and that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail.
 
@@
 \label{sec: discussion}
-For given data, there are an almost limitless number of ways to define what the ``right'' clustering is.
+For given data, there are an almost limitless number of ways to define what the 'right' clustering is.
 We have considered one such notion -- density upper level sets -- and have detailed a set of natural geometric criteria which, when appropriately satisfied, translate to provable bounds on estimation of the cluster by \ppr.
-We do not, however, provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
+We do not provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
 Although we investigate the matter empirically, this is a direction for future work.

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Through intro, saved a bit of space

@@
 
-\PassOptionsToPackage{numbers}{natbib}
+%\PassOptionsToPackage{numbers}{natbib}
 \usepackage{neurips_2019}
@@
 
+%%%%%% Begin Alden
 \DeclarePairedDelimiter\abs{\lvert}{\rvert}
@@
 \newtheorem{remark}{Remark}
+%%%%%% End Alden
 
@@
 \begin{document}
-
 \maketitle
@@
 \begin{abstract}
-\vskip 0.1 in
-  Spectral clustering methods are a family of popular nonparametric clustering
-  tools.  Recent works have proposed and analyzed \emph{local} spectral methods, such as Personalized PageRank (\ppr),
+We analyze Personalized PageRank (PPR), a local spectral method for clustering,
 which extract clusters using locally-biased random walks around a user-specified
-  seed node.  In contrast to existing results, we analyze PPR in a traditional
-  statistical learning setup, where we obtain samples from an unknown
-  distribution, and aim to identify connected regions of high-density (density
-  clusters).  We prove that PPR, run on a neighborhood graph, extracts
-  sufficiently salient density clusters, and provide empirical support for our theory.
+seed node.  In constrast to pervious work, we adopt a traditional statistical
+learning setup, where we obtain samples from an unknown distribution, and aim to
+identify connected regions of high-density (density clusters).  We prove that
+PPR, run on a neighborhood graph, extracts sufficiently salient density
+clusters. We also provide empirical support for our theory.
 \end{abstract}
@@
 
-Let $\Xbf = \{x_1, \ldots, x_n\}$ be a sample drawn i.i.d.\ from a
-distribution $\Pbb$ on $\Rd$, with density $f$, and consider the problem of 
-clustering: splitting the data into groups which satisfy some notion of
-within-group similarity and between-group difference.  We focus on spectral
-clustering methods, a family of powerful nonparametric clustering algorithms.
-Roughly speaking, a spectral technique first constructs a geometric graph $G$,
-where vertices are associated with samples, and edges correspond to proximities
-between samples. It then learns a feature embedding based on the Laplacian of
-$G$, and applies a simple clustering technique (such as k-means clustering) in
-the embedded feature space.
+In this paper, we study the problem of clustering: splitting a given data set
+into groups that satisfy some notion of within-group similarity and
+between-group difference.  We focus on spectral clustering, a family of powerful
+nonparametric clustering algorithms.  Generally speaking, a spectral algorithm
+first constructs a geometric graph $G$, where vertices correspond to samples,
+and edges correspond to proximities between samples. It then learns a feature
+embedding based on the Laplacian of $G$, and applies a simple clustering
+technique (like k-means clustering) in the embedded feature space.
 
-When applied to geometric graphs constructed from a large number of samples,
+When applied to geometric graphs built from a large number of samples,
 global spectral clustering methods can be computationally cumbersome and   
@@
 random walks around a user-specified seed node.  A popular local clustering
-algorithm is Personalized PageRank (\ppr), first introduced by
-\citet{haveliwala2003}, and further developed in
+algorithm is Personalized PageRank (PPR), first introduced by
+\citet{haveliwala2003}, and then further developed by
 \citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
@@
 Local spectral clustering techniques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
+\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, leading 
 many authors to develop supporting theory
 \citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
-guarantees on traditional graph-theoretic notions of cluster quality (like
+guarantees on traditional graph-theoretic notions of cluster quality (such as
 conductance).  In this paper, we adopt a more traditional statistical viewpoint,
-and examine what the output of a local clustering algorithm on $\Xbf$ reveals
-about the unknown density $f$.  In particular, we examine the ability of the \pprspace algorithm to recover \emph{density clusters} of $f$, which are defined as the
-connected components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$
-for some threshold $\lambda > 0$ (a central object of interest in the
-classical statistical literature on clustering, dating back to
-\citet{hartigan1981}).
+and examine what the output of local clustering on a data set reveals about the
+underlying density $f$.  In particular, we examine the ability of PPR to recover
+\emph{density clusters} of $f$, defined as the connected components of
+the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$
+(a central object of interest in the statistical clustering literature, dating
+back to \citet{hartigan1981}).
 
-\paragraph{PPR on a neighborhood graph} We now describe the clustering algorithm that will be our focus for the rest of 
-the paper. We start with the geometric graph that we form based on the samples 
-$\Xbf$: for a radius $r > 0$, we consider the \emph{$r$-neighborhood graph} of 
-$\Xbf$, denoted $G_{n,r}=(V,E)$, an unweighted, undirected graph with vertices
-$V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i - x_j}
-\leq  r$, where $\norm{\cdot}$ denotes Euclidean norm.
-We denote by $\Abf \in \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise, by $\Dbf$ the diagonal degree matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.
+\paragraph{PPR on a neighborhood graph.} We now describe the clustering
+algorithm that will be our focus for the rest of the paper. Let $\Xbf = \{x_1,
+\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$,
+with density $f$.  For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the
+\emph{$r$-neighborhood graph} of $\Xbf$, an unweighted, undirected graph with
+vertices $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i -
+x_j} \leq r$, where $\norm{\cdot}$ is the $\ell_2$ norm. We denote by $\Abf \in
+\Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if
+$(u,v) \in E$ and $0$ otherwise.  We also denote by $\Dbf$ the diagonal degree
+matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n
+\times n$ identity matrix.
 
-Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, with respect to  
+Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, based on
 a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be 
@@
 \end{equation}
-where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over $G_{n,r}$ 
-and $e_{v}$ denotes the indicator vector for node $v$ (with a 1 in the $v$th
-position and 0 elsewhere).
-
-For a level $\beta > 0$ and a target volume $\vol_0 > 0$, we define a
-\emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$ as  
+where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over
+$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
+$v$th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
+$\vol_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$
+as   
 \begin{equation}
 \label{eqn: sweep_cuts}
-S_\beta = \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
+S_\beta := \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
 \end{equation}
-We will use normalized cut to determine which sweep cut $S_{\beta}$ is the best cluster estimate.
-For a set $S \subseteq V$ with complement $S^c = V \setminus S$, we define the cut as $\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c} \Abf_{uv}$, the volume as $\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$, and the \emph{normalized cut} as
+We will use the normalized cut metric to determine which sweep cut $S_{\beta}$
+is the best cluster estimate. For a set $S \subseteq V$ with complement $S^c = V
+\setminus S$, we define \smash{$\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c}
+\Abf_{uv}$}, and \smash{$\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$}.  We
+define the \emph{normalized cut} of $S$ as
 \begin{equation}
@@
 Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(\frac{1}{40},\frac{1}{11})$},\footnote{The choice of a specific range such as 
+(\frac{1}{40},\frac{1}{11})$}\footnote{The choice of a specific range such as  
 \smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate $\widehat{C} = S_{\beta^*}$ which has minimum normalized cut $\Phi(S_{\beta^{\star}}; G_{n,r})$.
-For concreteness, we summarize this procedure in Algorithm \ref{alg: ppr}.
+algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate
+\smash{$\Cest = S_{\beta^*}$} that has minimum normalized cut.
+%\smash{$\Phi(S_{\beta^*}; G_{n,r})$}. 
+For concreteness, this is summarized in Algorithm \ref{alg: ppr}.
 
 \begin{algorithm}
-	\caption{PPR on a Neighborhood Graph}
+\caption{PPR on a neighborhood graph}
 \label{alg: ppr}	
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-	parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume $\vol_0 >
-	0$. \\   
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume
+$\vol_0 > 0$. \\     
 {\bfseries Output:} cluster $\Cest \subseteq V$.
@@
   \STATE Form the neighborhood graph $G_{n,r}$.
-		\STATE Compute the PPR vector $\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn:
+  \STATE Compute the PPR vector $p=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
     ppr_vector}. 
-		\STATE For $\beta \in (\frac{1}{40}, \frac{1}{11})$ compute sweep cuts
+  \STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-		\STATE Return \smash{$\Cest = S_{\beta^*}$}, where 
+  \STATE Return as a cluster \smash{$\Cest = S_{\beta^*}$}, where  
   $$
@@
 
-\paragraph{Estimation of density clusters}
-
-Let $\Cbb_f(\lambda)$ denote the connected components of the density upper level
-set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster $\Cset \in
-\Cbb_f(\lambda)$, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical
-density cluster}.
-The symmetric set difference between estimated and empirical cluster is perhaps the most frequently used metric to quantify cluster estimation error \citep{korostelev2012,polonik1995,rigollet2009}.
+\paragraph{Estimation of density clusters} Let \smash{$\Cbb_f(\lambda)$} denote
+the connected components of the density upper level set $\{x \in \Rd: f(x) >
+\lambda\}$.  For a given density cluster \smash{$\Cset \in \Cbb_f(\lambda)$}, we
+call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}. The
+size of the symmetric set difference between estimated and empirical clusters is 
+a commonly used metric to quantify cluster estimation error
+\citep{korostelev1993,polonik1995,rigollet2009}.
 
@@
   For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-	$\mathcal{S} \subseteq \Reals^d$, the symmetric set difference of $\Cest$ and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$ is 
+  $\mathcal{S} \subseteq \Reals^d$, we define   
   \begin{equation}
     \label{eqn: misclassification_rate}
-	\Delta(\Cest, \mathcal{S}) := \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup \mathcal{S}[\Xbf] \setminus \Cest}.
+    \Delta(\Cest, \mathcal{S}) := \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup
+      \mathcal{S}[\Xbf] \setminus \Cest},
   \end{equation}
+  the cardinality of the symmetric set difference between 
+  \smash{$\Cest$} and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$. 
 \end{definition}
 
-However, the symmetric set difference does not account for the distance points in $\widehat{C} \setminus \mathcal{S}[\Xbf]$ may be from $\mathcal{S}$ \citep{singh2009}.
-We therefore give a second notion of cluster estimation, first introduced by \citet{hartigan1981} and defined asymptotically, which measures whether $\widehat{C}$ can distinguish any two distinct elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
+Note that this symmetric set difference metric does not account for the distance
+points in \smash{$\Cest \setminus \mathcal{S}[\Xbf]$} may be from
+$\mathcal{S}$  \citep{singh2009}. Hence in this paper, in addition to the symmetric
+set difference metric, we also study a second asymptotic notion for the quality
+of a cluster estimator introduced by \citet{hartigan1981}.
+
+% which measures whether $\Cest$ can distinguish any two distinct
+% elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
 
@@
   For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster 
-	$\Cset \in \Cbb_f(\lambda)$, we say \smash{$\Cest$} is a consistent
-	estimator of $\Cset$ if for all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset \not=
-	\Cset'$ the following holds as $n \to \infty$: 
+  \smash{$\Cset \in \Cbb_f(\lambda)$}, we say \smash{$\Cest$} is a consistent 
+  estimator of $\Cset$ if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with
+  $\Cset \not= \Cset'$, the following holds as $n \to \infty$: 
   \begin{equation}
@@
 \end{definition}
-\paragraph{Summary of results}
-A summary of our main results (and outline for the rest of this paper) is as
-follows.
+
+\paragraph{Summary of results.} A summary of our results (and outline for this
+paper) is as follows.
 
 \begin{enumerate}
-	\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce a set of natural geometric conditions on the density cluster $\Cset$, formalize a measure of difficulty based on these geometric conditions, and show that when Algorithm \ref{alg: ppr} is properly initialized, the symmetric set difference of $\widehat{C}$ and a thickened version of the density cluster $\Csig$ is upper bounded by this difficulty measure.
+\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce
+  a set of natural geometric conditions on the density cluster $\Cset$
+  %formalize a measure of difficulty based on these geometric conditions, 
+  and show that when Algorithm \ref{alg: ppr} is properly initialized, the size of
+  the symmetric set difference of \smash{$\Cest$} and a thickened version of the
+  density cluster $\Csig$ can be bounded in a meaningful way.
+  % this difficulty measure.
 
-	\item We further show that if the density cluster $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr} will consistently estimate a density cluster in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+\item We further show in Section \ref{sec:
+    consistent_cluster_estimation_with_ppr} that if the density cluster 
+  $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
+  will consistently estimate a density cluster in the sense of
+  \eqref{eqn: consistent_density_cluster_recovery}.
 
-	\item In Section \ref{sec: analysis}, we detail some of the analysis required to prove our main results, and expose the part various geometric quantities play in the ultimate difficulty of the clustering problem.
+\item In Section \ref{sec: analysis}, we detail some of the analysis required to
+  prove our main results, and expose the parts various geometric quantities play 
+  in the difficulty of the clustering problem.
 
-	\item In Section \ref{sec: experiments}, we empirically
-	demonstrate the tightness of our analysis, and provide examples showing how violations of the geometric conditions we require manifestly
-	impact density cluster recovery by \ppr.  
+\item In Section \ref{sec: experiments}, we empirically investigate the
+  tightness of our analysis, and provide examples showing how violations of our
+  geometric conditions impact density cluster recovery by PPR.
 \end{enumerate}
 
-Our main takeaway can be summarized as follows: \ppr, run on a neighborhood graph, recovers geometrically compact high-density clusters.
+Our main takeaway: PPR, run on a neighborhood graph, recovers geometrically
+compact high-density clusters.
 
-\paragraph{Related work}
+\paragraph{Related work.} In addition to the background on local spectral
+clustering given previously, a few related lines of work are worth
+highlighting. \citep{shi2009,schiebinger2015} examine the consistency of  
+spectral algorithms in recovering the latent labels in certain
+nonparametric mixture models. Their results focus on global rather than local 
+methods, and thus impose global rather than local conditions on the nature
+of the density. Moreover, they do not in general guarantee recovery of density 
+clusters, which is the focus in our work. Perhaps most importantly, these works
+rely on general cluster saliency conditions, which implicitly depend on many
+distinct geometric aspects of the cluster $\Cset$ under consideration. We make
+this dependence more explicit, and in doing so expose the role each geometric
+condition plays in the clustering problem.
 
-In addition to the background given previously, a few related lines of work are worth
-highlighting. Similar in spirit to our results are the works
-\citep{shi2009,schiebinger2015}, who study the consistency of
-spectral algorithms in recovering the latent labels in certain
-nonparametric mixture models. These results focus on global rather than local
-algorithms, and as such impose global rather than local conditions on the nature
-of the density. Moreover, they do not in general guarantee recovery of density
-clusters, which is the focus in our work.
-Perhaps most importantly, these works rely on general cluster saliency conditions, which implicitly depend on many distinct geometric aspects of the cluster $\Cset$ under consideration.
-We make this dependence more explicit, and in doing so expose the role each geometric condition plays in the clustering problem.
-
-Additionally, we note that density clustering and level set estimation is a well-studied problem.
-\citep{polonik1995, rigollet2009} study density clustering under symmetric set difference, \citep{tsybakov1997, singh2009} exhibit minimax optimal level set estimators under Hausdorff loss and \citep{hartigan1981, chaudhuri2010} consider consistent estimation of the cluster tree, to note but a few works on the subject.
-Our goal is not to improve on these results, or offer yet another algorithm for level set estimation; indeed, seen as a density clustering algorithm, \pprspace has none of the optimality guarantees of the previous works.
-Rather, our motivation is to better understand and characterize the distinctions between those density clusters which are well conditioned for local spectral algorithms, and those which are not.
+More broadly, density clustering and level set estimation is a well-studied
+problem. \citet{polonik1995, rigollet2009} study density clustering under
+symmetric set difference, \citet{tsybakov1997, singh2009} exhibit minimax
+optimal level set estimators under Hausdorff loss and \citet{hartigan1981,
+  chaudhuri2010} consider consistent estimation of the cluster tree, to note but
+a few works in the area. Our goal is not to improve on these results, nor to 
+offer a new algorithm for level set estimation; indeed, seen as a density
+clustering algorithm, PPR has none of the optimality guarantees of the
+methods in the aforementioned works. Rather, our motivation is start with a 
+popular  and flexible local spectral algorithm, PPR, and to better understand
+and characterize the distinctions between those density clusters which are 
+well-conditioned for PPR, and those which are not.
 
@@
 To motivate these conditions, for an arbitrary graph $G = (V,E)$ and subset of vertices $S \subseteq V$, consider the normalized cut $\Phi(S;G)$ (defined as in \eqref{eqn: normalized_cut}), as well as the mixing time of a random walk over the induced subgraph $G[S]$ (defined in Section \ref{sec: analysis} by \eqref{eqn: mixing_time}, and denoted by $\tau_{\infty}(G[S])$).
-In \citet{zhu2013}, it is shown that for a constant $c > 0$, the \pprspace estimate $\widehat{C}$ of $S$ satisfies
+In \citet{zhu2013}, it is shown that for a constant $c > 0$, the \pprspace estimate $\Cest$ of $S$ satisfies
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference_1}
-\vol(\widehat{C} \setminus S; G) + \vol(S \setminus \widehat{C}; G) \leq c \bigl( \Phi(S,G) \cdot \tau_{\infty}(G[S])\bigr) \vol(S;G)
+\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G) \cdot \tau_{\infty}(G[S])\bigr) \vol(S;G)
 \end{equation}
@@
 	\label{thm: misclassification_rate}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
 Then, there exists a universal constant $c_4 > 0$ such that with probability tending to $1$ as $n \to \infty$,
@@
 	\label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}.
+	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}.
 If Algorithm \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 > 0$ such that if

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Through Sect 2

@@
 insensitive to the local geometry of the underlying distribution
-\citep{leskovec2010,mahoney2012}.  This has led to recent increased interest in
-local spectral algorithms, which leverage locally-biased spectra computed using
-random walks around a user-specified seed node.  A popular local clustering
-algorithm is Personalized PageRank (PPR), first introduced by
-\citet{haveliwala2003}, and then further developed by
+\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
+local spectral clustering algorithms, which leverage locally-biased spectra
+computed using random walks around some user-specified seed node.  A popular 
+local clustering algorithm is Personalized PageRank (PPR), first introduced by 
+\citet{haveliwala2003}, then further developed by
 \citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
@@
 
-\paragraph{Estimation of density clusters} Let \smash{$\Cbb_f(\lambda)$} denote
+\paragraph{Estimation of density clusters.} Let \smash{$\Cbb_f(\lambda)$} denote 
 the connected components of the density upper level set $\{x \in \Rd: f(x) >
@@
 
-Note that this symmetric set difference metric does not account for the distance
-points in \smash{$\Cest \setminus \mathcal{S}[\Xbf]$} may be from
-$\mathcal{S}$  \citep{singh2009}. Hence in this paper, in addition to the symmetric
-set difference metric, we also study a second asymptotic notion for the quality
-of a cluster estimator introduced by \citet{hartigan1981}.
-
-% which measures whether $\Cest$ can distinguish any two distinct
-% elements $\Cset, \Cset' \in \Cbb_f(\lambda)$.
+However, the symmetric set difference does not measure whether \smash{$\Cest$} 
+can distinguish any two distinct clusters \smash{$\Cset,\Cset' \in
+  \Cbb_f(\lambda)$}. We therefore also study a second notion of cluster
+estimation, first introduced by \citet{hartigan1981}, and defined
+asymptotically.
 
@@
 More broadly, density clustering and level set estimation is a well-studied
-problem. \citet{polonik1995, rigollet2009} study density clustering under
-symmetric set difference, \citet{tsybakov1997, singh2009} exhibit minimax
-optimal level set estimators under Hausdorff loss and \citet{hartigan1981,
-  chaudhuri2010} consider consistent estimation of the cluster tree, to note but
-a few works in the area. Our goal is not to improve on these results, nor to 
-offer a new algorithm for level set estimation; indeed, seen as a density
-clustering algorithm, PPR has none of the optimality guarantees of the
-methods in the aforementioned works. Rather, our motivation is start with a 
-popular  and flexible local spectral algorithm, PPR, and to better understand
-and characterize the distinctions between those density clusters which are 
+problem. \citet{polonik1995, rigollet2009} study density clustering under the 
+symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
+minimax optimal level set estimators under Hausdorff loss and
+\citet{hartigan1981, chaudhuri2010} consider consistent estimation of the
+cluster tree, to note but a few works. Our goal is not to improve on these
+results, nor to offer a better algorithm for level set estimation; indeed, seen as
+a density clustering algorithm, PPR has none of the optimality guarantees 
+found in the aforementioned works. Instead, our motivation is start with a
+widely-used local spectral method, PPR, and to better understand and
+characterize the distinctions between those density clusters which are
 well-conditioned for PPR, and those which are not.
@@
 
-We formalize some geometric conditions, before using these to define a condition number $\kappa(\Cset)$ which measures the difficulty \pprspace will have in estimating $\Cset$.
-We motivate this measure, and the underlying geometric conditions, by giving density cluster estimation guarantees for Algorithm \ref{alg: ppr} in terms of $\kappa(\Cset)$.
+We formalize some geometric conditions, and use these to define a condition
+number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
+estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
+of $\kappa(\Cset)$.)
 
-\paragraph{Geometric conditions on density clusters}
-
-As mentioned previously, successful recovery of a density cluster by \pprspace requires the density cluster to be geometrically well-conditioned.
-At a minimum, we wish to avoid sets $\Cset$ which contain arbitrarily thin bridges or spikes, and therefore as in \cite{chaudhuri2010} we introduce a buffer zone around $\Cset$.
-Let $B(x,r)$ be the closed ball of radius $r > 0$ centered at $x \in \Rd$.
-For $\lambda > 0$, consider a given cluster $\Cset \in \Cbb_f(\lambda)$.
-We denote the distance between $x$ and $\Cset$ as $\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$, and for a given $\sigma > 0$, we refer to $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$ as the $\sigma$-expansion of $\Cset$.
-We now state our conditions with respect to $\Csig$.
+\paragraph{Geometric conditions on density clusters.} At a high level, for PPR
+to be successful, the underlying density cluster must be geometrically
+well-conditioned.  At a minimum, we want to avoid sets that contain arbitrarily
+thin bridges or spikes.  Hence, as in \cite{chaudhuri2010}, we consider a
+thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
+$\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$, which 
+we call the \emph{$\sigma$-expansion} of $\Cset$. Here 
+\smash{$\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$}.  We now list our
+conditions on $\Csig$.
 
@@
   \label{asmp: bounded_density}
-	\emph{Bounded density within cluster:} There exist constants $\lambda_{\sigma}, \Lambda_{\sigma}$ such that $0 < \lambda_{\sigma} = \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x) \leq \Lambda_{\sigma} < \infty$.
+  \emph{Bounded density within cluster:} There exist constants
+  $0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
+  $\lambda_{\sigma} \leq \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x)
+  \leq \Lambda_{\sigma}$.
 
@@
   \emph{Cluster separation:}
-	For all $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$, $\dist(\Csig,\Csig') > \sigma$,
-	where \smash{$\dist(\Csig,\Csig') := \inf_{x \in \Csig} \dist(x,\Csig')$}.
+  For all clusters $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$, 
+  $\dist(\Csig,\Csig') > \sigma$, where $\dist(\Csig,\Csig') := \inf_{x
+    \in \Csig} \dist(x,\Csig')$.
 
@@
   \label{asmp: low_noise_density}
-	\emph{Low noise density:} There exists $\gamma,c_0 > 0$ such that for all $x
-	\in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-	$$
-	\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}.
-	$$
+  \emph{Low noise density:} There exist $\gamma,c_0 > 0$ such that for 
+  $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
+  $\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}$.
 
@@
   \emph{Lipschitz embedding:}
-	There exists $g: \Reals^d \to \Reals^d$ which has the following properties: i) there exists a convex set $\mathcal{K} \subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =: \diam < \infty$, such that $\Csig = g(\mathcal{K})$, ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$, and iii) for some $L \geq 1$,
+  There exists $g: \Reals^d \to \Reals^d$ with the following properties: i)
+  we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
+  with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =:
+  \diam < \infty$; ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
+  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; and iii) for some $L
+  \geq 1$,   
   \begin{equation*}
-	\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \mathcal{K}$}.
+    \frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~
+    \text{for all $x,y \in \mathcal{K}$}. 
   \end{equation*}
-	Simply put, $\Csig$ is the image of a convex set with finite diameter, under a  measure preserving, biLipschitz transformation.
+  Succintly, $\Csig$ is the image of a convex set with finite diameter 
+  under a  measure preserving, bi-Lipschitz transformation.
+
 \item
@@
   \begin{equation*}
-	2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx
+    2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx,
   \end{equation*}
+  where $B(x,r)$ is the closed ball of radius $r$ at $x$.
 \end{enumerate}
 
-To motivate these conditions, for an arbitrary graph $G = (V,E)$ and subset of vertices $S \subseteq V$, consider the normalized cut $\Phi(S;G)$ (defined as in \eqref{eqn: normalized_cut}), as well as the mixing time of a random walk over the induced subgraph $G[S]$ (defined in Section \ref{sec: analysis} by \eqref{eqn: mixing_time}, and denoted by $\tau_{\infty}(G[S])$).
-In \citet{zhu2013}, it is shown that for a constant $c > 0$, the \pprspace estimate $\Cest$ of $S$ satisfies
+To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
+(V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
+of subset $S$ satisfies, for a constant $c>0$,
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference_1}
-\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G) \cdot \tau_{\infty}(G[S])\bigr) \vol(S;G)
+\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
+\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
 \end{equation}
-where the left hand side resembles a (degree-weighted) form of the symmetric set difference of \eqref{eqn: misclassification_rate}.
+where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
+  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
+  time} of a random walk over the induced subgraph $G[S]$ (to be defined
+precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
+\eqref{eqn:  graph_symmetric_set_difference_1} resembles a (degree-weighted) 
+form of the symmetric set difference metric in \eqref{eqn:
+  misclassification_rate}.  As we will show in Section \ref{sec:
+  analysis}, the conditions \ref{asmp: bounded_density}-\ref{asmp:
+  bounded_volume} allow us to upper bound the normalized cut 
+\smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.  (Informally, 
+\ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
+bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
+yields a lower bound on \smash{$\vol(\Csig[\Xbf]; G_{n,r})$}; together with 
+\ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
+the other hand, \ref{asmp: bounded_density}, \ref{asmp: embedding} preclude
+bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
+with \ref{asmp: embedding}, this leads to an upper bound on the mixing time over 
+this subgraph.)
 
-As we will formally show in Section \ref{sec: analysis}, the conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume} allow us to upper bound the normalized cut $\Phi(\Csig[\Xbf]; G_{n,r})$, and the mixing time $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
-Intuitively, the low noise \ref{asmp: cluster_separation} and cluster separation \ref{asmp: low_noise_density} assumptions yield an upper bound on $\cut(\Csig[\Xbf]; G_{n,r})$, the lower bound on density in \ref{asmp: bounded_density} yields a lower bound on $\vol(\Csig[\Xbf]; G_{n,r})$, and along with \ref{asmp: bounded_volume}, which ensures $\vol(\Csig[\Xbf]; G_{n,r}) \leq \vol(\Csig[\Xbf]^c; G_{n,r})$, these imply an upper bound on the normalized cut.
-\ref{asmp: bounded_density} and \ref{asmp: embedding} preclude bottlenecks in the induced subgraph $G_{n,r}[\Csig[\Xbf]]$, and combined with the upper bound on diameter in \ref{asmp: embedding}, they yield an upper bound on the mixing time over this subgraph.
-
-\paragraph{Condition number} We will return to the topic of conditions in Section \ref{sec: analysis}.
-Now, we define the condition number, $\kappa(\Cset)$, which reflects the difficulty of the local spectral clustering task.
-Motivated by \eqref{eqn: graph_symmetric_set_difference_1}, we will set $\kappa(\Cset)$ to be an upper bound on $\Phi(\Csig[\Xbf]; G_{n,r}) \cdot \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
-The smaller $\kappa(\Cset)$ is, the more success \pprspace will have in recovering $\Cset$.
-Let $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain those geometric parameters detailed in \ref{asmp: bounded_density} - \ref{asmp: bounded_volume}.
+\paragraph{Condition number.} Motivated by \eqref{eqn:
+  graph_symmetric_set_difference_1}, we will define $\kappa(\Cset)$ to be an
+upper bound on the product \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
+  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. The smaller $\kappa(\Cset)$ is, the
+more success PPR will have in recovering $\Cset$. Let $\theta := (r, \sigma,
+\lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain the
+geometric parameters from \ref{asmp:  bounded_density}--\ref{asmp:
+  bounded_volume}.
 
 \begin{definition}[Well-conditioned density clusters]
-	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} for some $\theta$.
-Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later, we set
+  For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy 
+  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some
+  $\theta$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified
+  later, we set 
   \begin{equation}
@@
     \Phibf(\theta) 
-	:= c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}},~ 
-	\taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
+    := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
+    \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma +
+        1})}{\lambda_{\sigma}},~  
+    \taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
+      L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3,
   \end{equation}
-	and letting $\kappa(\Cset) := \Phi_{u}(\theta) \cdot \tau_{u}(\theta)$, we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster}.
+  and letting \smash{$\kappa(\Cset) := \Phi_{u}(\theta) \cdot
+    \tau_{u}(\theta)$}, we call $\Cset$ a 
+  \emph{$\kappa$-well-conditioned density cluster}.  
 \end{definition}
 
-We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds on $\Phi(\Csig[\Xbf]; G_{n,r})$ and $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ that we derive in Section \ref{sec: analysis}.
+We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
+on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in our analysis
+later, in Section \ref{sec: analysis}.
 
-\paragraph{Well-initialized algorithm}
-
-As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified parameters.
-
-In particular, for a well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we require
-\begin{align}
+\paragraph{Well-initialized algorithm.} As is typical in the local clustering
+literature, our algorithmic results will be stated with respect to specific
+ranges of each of the user-specified parameters. In particular, for a
+well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
+require 
+\begin{equation}
+\begin{gathered}
 \label{eqn: initialization}
-0 < r \leq \frac{\sigma}{2d}, & ~\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)} \nonumber,  \\
-v \in \Csig[\Xbf]^g, & ~\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx
-\end{align}
-where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ will be some large subset of $\Csig[\Xbf]$.
-In particular, letting $\vol_{n,r}(S) := \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we have $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$.
+0 < r \leq \frac{\sigma}{2d}, \quad 
+\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)}, \\
+v \in \Csig[\Xbf]^g, \quad
+\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, 
+\end{gathered}
+\end{equation}
+where \smash{$\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$} will be some large
+(``good'') subset of $\Csig[\Xbf]$. In particular, abbreviating $\vol_{n,r}(S)
+:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we will have
+\smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$}.
 
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn: initialization} for some well-conditioned density cluster $\Cset$, we say the algorithm is \emph{well-initialized}.
+If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn:
+  initialization} for some well-conditioned density cluster $\Cset$, we
+say the algorithm is \emph{well-initialized}. 
 \end{definition}
 
-In practice it is clearly not feasible to set hyperparameters based on the underlying (unknown) density $f$.
-Typically, one tunes \pprspace over a range of hyperparameters and optimizes for some criterion such as minimum normalized cut; it is not obvious how this scheme would affect the performance of \pprspace in the density clustering context.
+In practice it is clearly not feasible to set hyperparameters based on the
+underlying (unknown) density $f$. Typically, one tunes PPR over a range of
+hyperparameters and optimizes for some criterion such as minimum normalized cut;
+it is not obvious how this scheme would affect the performance of PPR in the
+density clustering context.
 
-\paragraph{Density cluster estimation by \ppr}
-
-The results of Section \ref{sec: analysis}, along with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the volume of $\Cest \setminus \Csig[\Xbf]$ and $\Csig[\Xbf] \setminus \Cest$,
+\paragraph{Main theorems.} The results of Section \ref{sec: analysis}, combined 
+with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
+volume of \smash{$\Cest \setminus \Csig[\Xbf]$} and \smash{$\Csig[\Xbf]
+  \setminus \Cest$},  
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus \Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]).
+\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus
+\Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]). 
 \end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$.
-Let $\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure of the unit ball $B = B(0,1)$.
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
+on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
+want to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and
+so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$. Let
+$\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure
+of the unit ball $B = B(0,1)$. 
 \begin{enumerate}[label=(A\arabic*)]
@@
   \label{asmp: valid_region}
-	\emph{Regular support:} There exists some number $\lambda_{\min} > 0$ such that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$.
-Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$.
+  \emph{Regular support:} There exists some constant $\lambda_{\min} > 0$ such 
+  that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$. Additionally, there
+  exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$,
+  $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$. 
 \end{enumerate}
-Note that the latter condition in \ref{asmp: valid_region} will be satisfied if, for instance, the support $\mathcal{X}$ is a $\sigma$-expanded set.
+Note that the latter condition in \ref{asmp: valid_region} will hold if the
+boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
+main bound on the symmetric set difference metric.
 
@@
   \label{thm: misclassification_rate}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}.
-Then, there exists a universal constant $c_4 > 0$ such that with probability tending to $1$ as $n \to \infty$,
+  Fix $\lambda > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
+  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
+  additionally assume $f$ satisfies \ref{asmp: valid_region}. If Algorithm
+  \ref{alg: ppr} is well-initialized, there exists a universal constant $c_4 >
+  0$ such that with probability tending to $1$ as $n \to \infty$,  
   \begin{equation}
     \label{eqn: misclassification_rate_ub}
-	\Delta(\Csig[\Xbf], \Cest) \leq c_4 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
+    \Delta(\Csig[\Xbf], \Cest) \leq c_4 \kappa(\Cset)
+    \frac{\Lambda_{\sigma}}{\lambda_{\min}}. 
   \end{equation}
@@
 
-The proof of Theorem \ref{thm: misclassification_rate}, along with all other proofs in this paper, can be found in the supplementary material.
-We observe that the symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$  is proportional to the difficulty of the clustering problem, as measured by the condition number $\kappa(\Cset)$.
+The proof of Theorem \ref{thm: misclassification_rate}, along with all other
+proofs in this paper, is deferred to the supplementary material. Note that this 
+result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
+  \Cest)$} is proportional to the difficulty of the clustering problem, as
+measured by the condition number $\kappa(\Cset)$.
 
-Neither \eqref{eqn: graph_symmetric_set_difference} nor Theorem \ref{thm: misclassification_rate} imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over $\pbf$: namely, for all $\Cset' \in \Cbb_f(\lambda), \Cset' \neq \Cset$, and each $u \in \Cset, w \in \Cset'$,
+Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
+  misclassification_rate_ub} imply consistent density cluster estimation in the 
+sense of \eqref{eqn: consistent_density_cluster_recovery}. This notion of
+consistency requires a uniform bound over $\pbf$: for all \smash{$\Cset'
+  \in \Cbb_f(\lambda), \Cset' \neq \Cset$}, and each $u \in \Cset, w \in
+\Cset'$,  
 \begin{equation}
 \label{eqn: ppr_gap}
-\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq \frac{p_u}{\Dbf_{uu}},
+\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq
+\frac{p_u}{\Dbf_{uu}}, 
 \end{equation}
-so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e.
-any sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions laid out in \eqref{eqn: consistent_density_cluster_recovery}.
-In Theorem \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently small upper bound on $\kappa(\Cset)$ ensures such a gap exists with probability one as $n \to \infty$, and therefore guarantees $\Cest$ will be a consistent estimator.
-As was the case before, we wish to preclude arbitrarily low degree vertices, this time for points $x \in \Cset'[\Xbf]$.
+so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e., any
+sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions
+laid out in \eqref{eqn: consistent_density_cluster_recovery}. In Theorem
+\ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently
+small upper bound on $\kappa(\Cset)$ ensures such a gap exists with probability
+1 as $n \to \infty$, and hence guarantees \smash{$\Cest$} will be a consistent  
+estimator. As was the case before, we wish to preclude arbitrarily low degree
+vertices, this time for points $x \in \Cset'[\Xbf]$. 
 \begin{enumerate}[label=(A\arabic*)]
@@
   \label{asmp: C'_bounded_density}
-	\emph{Bounded density:} Letting $\sigma,\lambda_{\sigma}$ be as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and for all $x \in \Csig'$, $\lambda_{\sigma} \leq f(x)$.
+  \emph{Bounded density in other clusters:} Letting $\sigma,\lambda_{\sigma}$ be 
+  as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and
+  for all $x \in \Csig'$, $\lambda_{\sigma} \leq f(x)$. 
 \end{enumerate}
+
+Next we give our main result on consistent cluster recovery by PPR.
 
@@
   \label{thm: consistent_recovery_of_density_clusters}
-	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}.
-If Algorithm \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 > 0$ such that if
+  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
+  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
+  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
+  \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 >
+  0$ such that if 
   \begin{equation}
     \label{eqn: kappa_ub}
-	\kappa(\Cset) \leq c_5 \frac{\lambda_{\sigma}^2r^d \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)},
+    \kappa(\Cset) \leq c_5 \frac{\lambda_{\sigma}^2r^d
+      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
   \end{equation}
-	then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
+  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
 \end{theorem}
@@
 \begin{remark}
-	We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in a symmetric set difference $\Delta(\Csig[\Xbf], \Cest)$ on the order of $r^d$.
-In plain terms, we are able to recover a density cluster $\Cset$ in the sense of \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a very small fraction of points will be misclassified.
-This strong condition is the price we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}.
+  We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
+    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
+    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
+  density cluster $\Cset$ in the sense of \eqref{eqn:
+    consistent_density_cluster_recovery} only when we can guarantee a very small
+  fraction of points will be misclassified. This strong condition is the price
+  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
 \end{remark}
@@
 \begin{remark}
-	While taking the radius of the neighborhood graph $r \to 0$ as $n \to \infty$---and thereby ensuring $G_{n,r}$ is sparse---is computationally attractive, the presence of a factor of $\frac{\log^2(1/r)}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace in this regime.
-Although the restriction to a kernel function fixed in $n$ is standard for theoretical analysis of spectral clustering \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.
+  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
+  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
+  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
+  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
+  behavior of PPR in this regime. Although the restriction to a kernel
+  function fixed in $n$ is standard for spectral clustering theory
+  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
+  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
+  this is merely looseness in our upper bounds.  
 \end{remark}
 
-\paragraph{Approximate \pprspace vector}
-
-In practice, exactly solving \eqref{eqn: ppr_vector} may be too computationally expensive.
-To address this limitation, \citet{andersen2006} introduced the \emph{$\epsilon$-approximate \pprspace vector} (aPPR), which we will denote $\pbf^{(\epsilon)}$.
-We refer the curious reader to \cite{andersen2006} for a formal algorithmic definition of the a\pprspace vector, and limit ourselves to highlighting a few salient points.
-Namely, the aPPR vector can be computed in  order $\mathcal{O}\left(\frac{1}{\epsilon \alpha}\right)$ time, while satisfying the following uniform error bound:
+\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
+  ppr_vector} may be too computationally expensive. To address this limitation,
+\citet{andersen2006} introduced the \emph{$\epsilon$-approximate} PPR vector
+(aPPR), which we will denote by \smash{$\pbf^{(\epsilon)}$}. We refer the
+curious reader to \citet{andersen2006} for a formal algorithmic definition of
+the aPPR vector, and limit ourselves to highlighting a few salient points: the
+aPPR vector can be computed in order $\mathcal{O}(1/(\epsilon\alpha))$ time,
+while satisfying the following uniform error bound: 
 \begin{equation}
 \label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq \pbf^{(\epsilon)}(u) \leq \pbf(u). 
+\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq
+\pbf^{(\epsilon)}(u) \leq \pbf(u).  
 \end{equation}
-
-Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} leads to analogous results which hold with respect to $\pbf^{(\epsilon)}$.
-We formally state and prove this fact in the supplementary material.
+Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
+  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
+leads to analogous results which hold for \smash{$\pbf^{(\epsilon)}$}. We
+formally state and prove this in the supplement.
 
@@
 
-\paragraph{Inverse mixing time}
+\paragraph{Mixing time.}
 For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the subgraph induced by 
@@
 However, it is not possible to eliminate this condition without incurring an additional factor of at least $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
-\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding biLipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
+\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding bi-Lipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
 \end{remark}

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Temp commit

@@
   misclassification_rate}.  As we will show in Section \ref{sec:
-  analysis}, the conditions \ref{asmp: bounded_density}-\ref{asmp:
+  analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
   bounded_volume} allow us to upper bound the normalized cut 
@@
 
-The primary technical contribution of our work is showing that the geometric conditions \ref{asmp: bounded_density} - \ref{asmp: bounded_volume} translate to meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in $G_{n,r}$.
-In doing so, we elaborate on how some of the geometric conditions introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr} contribute to the difficulty of the clustering problem.
+The primary technical contribution of our work is showing that the geometric
+conditions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} translate to 
+meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in
+$G_{n,r}$. In doing so, we elaborate on how some of the geometric conditions
+introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr}
+contribute to the difficulty of the clustering problem.
 
-\paragraph{Normalized cut} We start with a finite sample upper bound on the normalized cut \eqref{eqn: normalized_cut} of 
-$\Cset_\sigma[\Xbf]$. For simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
+\paragraph{Normalized cut.} We start with a finite sample upper bound on the
+normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
+simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
 
@@
   \label{thm: conductance_upper_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
-	Assumptions \ref{asmp: bounded_density}-\ref{asmp: low_noise_density}, and \ref{asmp: bounded_volume} for some 
-	$r, \sigma, \lambda_{\sigma}, c_0, \gamma > 0$ (no bound on maximum density is needed). 
-	Then for any $0 < \delta < 1$, $\epsilon > 0$, if
+  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
+  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
+  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
+  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
+  $\epsilon > 0$, if 
   \begin{equation}
@@
   \label{rmk: diameter}
-	Observe that the diameter $\rho$ is absent from Theorem \ref{thm: conductance_upper_bound}, in contrast to the difficulty function $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases.
-This phenomenon reflects established wisdom regarding spectral partitioning algorithms more generally \cite{guattery1995, hein2010}, albeit newly applied to the density clustering setting.
-It suggests that if the diameter $\rho$ is large, \pprspace may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized cut in $G_{n,r}$.
-This intuition will be supported by simulations in Section \ref{sec: experiments}.
+  Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
+    conductance_upper_bound}, in contrast to the condition number
+  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This
+  reflects established wisdom regarding spectral partitioning
+  algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
+  to the density clustering setting. It suggests that if the diameter $\rho$ is
+  large, PPR may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is
+  sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized
+  cut in $G_{n,r}$. This intuition will be supported by simulations in Section
+  \ref{sec: experiments}. 
 \end{remark}
 
-\paragraph{Mixing time.}
-For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the subgraph induced by 
-$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write 
+\paragraph{Mixing time.} For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
+subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
+$\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write  
 $$
@@
 for the stationary distribution of this random walk.  (As
-$\Wbf_S$ is the transition matrix of a lazy random walk, it is well-known that a unique stationary distribution exists and is given by
-\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where $\Dbf_S$ is the degree matrix of $G[S]$.)
-
-Then, the \emph{relative pointwise mixing time} of $G[S]$ is 
+$\Wbf_S$ is the transition matrix of a lazy random walk, 
+it is well-known that a unique stationary distribution exists and is given by 
+\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where we write $\Dbf_S$ for the  
+degree matrix of $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
 \begin{equation}
 \label{eqn: mixing_time}
-\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)
-	}{\pi(u)} \leq \frac{1}{4}, 
-	\; \text{for $u,v \in V$}}. 
+\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)}
+  {\pi(u)} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}. 
 \end{equation}
-In the following theorem, we give an asymptotic (in the number of vertices $n$) upper bound on $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
+Next, we give an asymptotic (in the number of vertices $n$) upper bound on
+$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
 

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Through Sect 3

@@
 well-conditioned.  At a minimum, we want to avoid sets that contain arbitrarily
-thin bridges or spikes.  Hence, as in \cite{chaudhuri2010}, we consider a
+thin bridges or spikes.  Hence, as in \citet{chaudhuri2010}, we consider a
 thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
@@
   additionally assume $f$ satisfies \ref{asmp: valid_region}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c_4 >
-  0$ such that with probability tending to $1$ as $n \to \infty$,  
+  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >
+  0$ such that with probability tending to 1 as $n \to \infty$,  
   \begin{equation}
     \label{eqn: misclassification_rate_ub}
-    \Delta(\Csig[\Xbf], \Cest) \leq c_4 \kappa(\Cset)
+    \Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
     \frac{\Lambda_{\sigma}}{\lambda_{\min}}. 
@@
   additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c_5 >
-  0$ such that if 
+  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
+  such that if  
   \begin{equation}
     \label{eqn: kappa_ub}
-    \kappa(\Cset) \leq c_5 \frac{\lambda_{\sigma}^2r^d
+    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
       \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
@@
   \label{thm: mixing_time_upper_bound}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$.
-Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability $1$
+  Fix $\lambda > 0$, and assume that \smash{$\Cset \in \Cbb_f(\lambda)$}
+  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
+  for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$. Then, for
+  any \smash{$0 < r < \sigma/2\sqrt{d}$}, with probability 1,
   \begin{equation} 
     \label{eqn: mixing_time_upper_bound}
-	\limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
+    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_1
+    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
+    \log^2\left(\frac{1}{r}\right) + c_2,
   \end{equation}
-	for $c_2,c_3 > 0$ universal constants. 
+  for $c_1,c_2 > 0$ universal constants. 
 \end{theorem}
 
-To the best of our knowledge, Theorem \ref{thm: mixing_time_upper_bound} is the first bound, albeit asymptotic, on the mixing time of random walks over neighborhood graphs which is independent of $n$, the number of vertices.
+To the best of our knowledge, Theorem \ref{thm: mixing_time_upper_bound} is the
+first bound, albeit asymptotic, on the mixing time of random walks over
+neighborhood graphs which is independent of $n$, the number of vertices.
+
 \begin{remark}
-	The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$ play an important role in proving the upper bound of Theorem \ref{thm: mixing_time_upper_bound}.
-There is some interdependence between $L$ and other geometric parameters $\sigma$ and $\rho$, which might lead one to hope that \ref{asmp: embedding} is non-essential.
-However, it is not possible to eliminate this condition without incurring an additional factor of at least $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for instance, when $\Csig$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
-\citep{abbasi-yadkori2016, abbasi-yadkori2016a} develop theory regarding bi-Lipschitz deformations of convex sets, wherein it is observed that star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding} for reasonably small values of $L$.
+  The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
+  play an important role in proving the upper bound of Theorem \ref{thm:
+    mixing_time_upper_bound}. There is some interdependence between $L$ and
+  $\sigma,\rho$, which might lead one to hope that \ref{asmp: embedding} is
+  non-essential. However, it is not possible to eliminate condition \ref{asmp:
+    embedding} without incurring an additional factor of at least
+  $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for
+  instance, when $\Csig$ is a dumbbell-like set consisting of two balls of
+  diameter $\rho$ linked by a cylinder of radius
+  $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
+  develop theory regarding bi-Lipschitz deformations of convex sets, wherein it
+  is observed that star-shaped sets as well as half-moon shapes of the type we
+  consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding}
+  for reasonably small values of $L$. 
 \end{remark}
@@
   \centering
-	\begin{adjustbox}{minipage=\linewidth}
-		\begin{subfigure}{.33\linewidth}
-			\includegraphics[width=\linewidth]{example1plots/sample2}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.33\linewidth}
-			\includegraphics[width=\linewidth]{example1plots/sample1}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.33\linewidth}
-			\includegraphics[width=\linewidth]{example1plots/sigma_normalized_cut_plot}
-			\caption{}
-		\end{subfigure}
+%  \begin{adjustbox}{minipage=\linewidth}
+%    \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.33\textwidth]{example1plots/sample2}
+%      \caption{}
+%    \end{subfigure}
+%    \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.33\textwidth]{example1plots/sample1}
+%      \caption{}
+%    \end{subfigure}
+%    \begin{subfigure}{.33\linewidth}
+      \includegraphics[width=0.33\textwidth]{example1plots/sigma_normalized_cut_plot}
+%      \caption{}
+%    \end{subfigure}
 
-		\begin{subfigure}{.33\linewidth}
-			\includegraphics[width=\linewidth]{example1plots/sigma_mixing_time_plot}
-			\caption{}
-		\end{subfigure}
+%    \begin{subfigure}{.33\linewidth}
+      \includegraphics[width=0.33\textwidth]{example1plots/sigma_mixing_time_plot}
+%      \caption{}
+%    \end{subfigure}
     \begin{subfigure}{.33\linewidth}
@@
     \end{subfigure}
-		\caption{Samples, empirical results, and theoretical bounds for mixing time and normalized cut as diameter and thickness are varied.
-In (a) and (b), points in $\Cset$ are colored in red; points in $\Csig \setminus \Cset$ are colored in yellow; and remaining points in blue.}
+    \caption{Samples, empirical results, and theoretical bounds for mixing time
+      and normalized cut as diameter and thickness are varied. In (a) and (b),
+      points in $\Cset$ are colored in red; points in $\Csig \setminus \Cset$
+      are colored in yellow; and remaining points in blue.} 
     \label{fig:fig1}

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Through Sects 4 and 5, DONE

@@
 a density clustering algorithm, PPR has none of the optimality guarantees 
-found in the aforementioned works. Instead, our motivation is start with a
+found in the aforementioned works. Instead, our motivation is to start with a 
 widely-used local spectral method, PPR, and to better understand and
@@
 \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.  (Informally, 
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.\footnote{Informally, assumptions  
 \ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
@@
 bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
-with \ref{asmp: embedding}, this leads to an upper bound on the mixing time over 
-this subgraph.)
+with the upper bound in \ref{asmp: embedding}, this leads to an upper bound on
+the mixing time over this subgraph.}
 
@@
     \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
+    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c \frac{d}{\sigma}
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
@@
   \end{equation}
-  with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
+  with probability at least $1-\delta$, where $c > 0$ is a universal constant. 
 \end{theorem}
@@
     \label{eqn: mixing_time_upper_bound}
-    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_1
+    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2
     \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{1}{r}\right) + c_2,
+    \log^2\left(\frac{1}{r}\right) + c_3,
   \end{equation}
-  for $c_1,c_2 > 0$ universal constants. 
+  for $c_2,c_3 > 0$ universal constants. 
 \end{theorem}
@@
 
-We provide numerical experiments to investigate the tightness of our bounds on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the ``two moons'' dataset.
-For space reasons, we defer details of the experimental settings to the supplement.
+We provide numerical experiments to investigate the tightness of our bounds on
+the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
+of PPR on the ``two moons'' dataset. For space reasons, we defer details of the
+experimental settings to the supplement.
 
-\paragraph{Validating theoretical bounds}
+\begin{figure}[tb]
+  \centering
+  % \begin{adjustbox}{minipage=\linewidth}
+  %   \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/sample2}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/sample1}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/sigma_normalized_cut_plot}
+  % \caption{}
+  % \end{subfigure}
+
+  % \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/sigma_mixing_time_plot}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/diameter_normalized_cut_plot}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.33\linewidth}
+  \includegraphics[width=0.32\textwidth]{example1plots/diameter_mixing_time_plot}
+  % \caption{}
+  % \end{subfigure}
+  \caption{\it\small Top left and top middle: samples from a geometrically
+    well- and poor-conditioned cluster. The points in $\Cset$ are colored in 
+    red, points in $\Csig \setminus \Cset$ are colored in yellow, and the
+    remaining points in blue. Other panels: empirical normalized cut and mixing
+    time, as a function of $\sigma$ or $\rho$, versus their theoretical upper
+    bounds.} 
+  \label{fig:fig1}
+%  \end{adjustbox}
+\end{figure}
+
+\paragraph{Validating theoretical bounds.}  We investigate the tightness of
+Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+  mixing_time_upper_bound} via simulation. Figure \ref{fig:fig1} compares our
+upper bounds with the actual empirically-computed quantities \eqref{eqn:
+  normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$
+and thickness $\sigma$ of a cluster $\Cset$. The top left and top middle panels
+display the resulting empirical clusters for two different values of
+$\rho,\sigma$.
+
+The bottom left and bottom right panels assure that our mixing  
+time upper bounds track closely the empirical mixing time, in both 2 and 3 
+dimensions.\footnote{We rescaled all values of theoretical upper
+  bounds by a constant, tto mask the effect of large universal constants
+  in these bounds. Therefore only the comparison of slopes, rather than
+  intercepts, is meaningful.} This provides empirical evidence that Theorem
+\ref{thm: mixing_time_upper_bound} has the right dependency on both expansion
+parameter $\sigma$ and diameter $\rho$. The story for the normalized cut panels
+is less obvious. We remark that while, broadly speaking, the trends do not
+appear to match, this gap between theory and empirical results seems largest
+when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
+grows, the slopes of empirical and theoretical curves become more similar.
+
+\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:fig2}, to drive home
+the main implications of Theorems \ref{thm: misclassification_rate} and
+\ref{thm: consistent_recovery_of_density_clusters}, we show the
+behavior of PPR, normalized cut, and the density clustering algorithm of
+\citet{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d 
+Gaussian noise), considered a prototypical success story for spectral clustering
+algorithms. The first column shows the empirical density clusters $C[X]$
+and $C'[X]'$ for a particular threshold $\lambda$ of the density function; the 
+second column shows the cluster recovered by PPR; the third column shows the
+global minimum normalized cut, computed according to the algorithm of
+\citet{szlam2010}; and the last column shows a cut of the density cluster tree
+estimator of \citet{chaudhuri2010}.  We can see the degrading ability of PPR to
+recover density clusters as the two moons become less well-separated. Of 
+particular interest is the fact that PPR fails to recover one of the moons even
+when normalized cut still succeeds in doing so, supporting our claim from Remark
+\ref{rmk: diameter}. Additionally, we note that the Chaudhuri-Dasgupta algorithm 
+succeeds even when both PPR and normalized cut fail.  While our main message was
+that PPR recovers geometrically well-conditioned density clusters, it would be  
+interesting to establish that it \emph{only} recovers such clusters, a point we
+return to below.
 
@@
   % \begin{adjustbox}{minipage=\linewidth}
-%    \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.33\textwidth]{example1plots/sample2}
+  %   \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth,scale = .5]{example2plots/row1_true_density_cluster}
   % \caption{}
   % \end{subfigure}
-%    \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.33\textwidth]{example1plots/sample1}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row1_ppr_cluster}
   % \caption{}
   % \end{subfigure}
-%    \begin{subfigure}{.33\linewidth}
-      \includegraphics[width=0.33\textwidth]{example1plots/sigma_normalized_cut_plot}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row1_conductance_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row1_density_cluster}
   % \caption{}
@@
 
-%    \begin{subfigure}{.33\linewidth}
-      \includegraphics[width=0.33\textwidth]{example1plots/sigma_mixing_time_plot}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row2_true_density_cluster}
   % \caption{}
   % \end{subfigure}
-    \begin{subfigure}{.33\linewidth}
-      \includegraphics[width=\linewidth]{example1plots/diameter_normalized_cut_plot}
-      \caption{}
-    \end{subfigure}
-    \begin{subfigure}{.33\linewidth}
-      \includegraphics[width=\linewidth]{example1plots/diameter_mixing_time_plot}
-      \caption{}
-    \end{subfigure}
-    \caption{Samples, empirical results, and theoretical bounds for mixing time
-      and normalized cut as diameter and thickness are varied. In (a) and (b),
-      points in $\Cset$ are colored in red; points in $\Csig \setminus \Cset$
-      are colored in yellow; and remaining points in blue.} 
-    \label{fig:fig1}
-  \end{adjustbox}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row2_ppr_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row2_conductance_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row2_density_cluster}
+  % \caption{}
+  % \end{subfigure}
+
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row3_true_density_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row3_ppr_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row3_conductance_cluster}
+  % \caption{}
+  % \end{subfigure}
+  % \begin{subfigure}{.24\linewidth}
+  \includegraphics[width=0.24\textwidth]{example2plots/row3_density_cluster}
+  % \caption{}
+  % \end{subfigure}
+  \caption{\it\small True density (column 1), PPR (column 2), normalized
+    cut (column 3) and estimated density (column 4) clusters for 3 different 
+    simulated data sets. Seed node for PPR denoted by a black cross.} 
+  \label{fig:fig2}
+  %\end{adjustbox}
 \end{figure}
-
-As we do not provide any theoretical lower bounds, we investigate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation.
-Figure \ref{fig:fig1} compares these theoretical bounds with the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\Cset$.
-Panels $(a)$ and $(b)$ show the resulting empirical clusters for two different values of $\rho$ and $\sigma$.
-
-Panels $(d)$ and $(f)$ show our theoretical bounds on mixing time tracking closely with empirical mixing time, in both 2 and 3 dimensions.\footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds.
-Therefore only comparison of slopes, rather than intercepts, is meaningful.} This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both expansion parameter $\sigma$ and diameter $\rho$.
-The story in panels $(c)$ and $(e)$ is less obvious.
-We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma $ and $\rho$ are approximately equal.
-As the ratio $\rho/\sigma$ grows, we see the slopes of the empirical curves become more similar to those predicted by theory.
-
-\paragraph{Empirical behavior of \ppr}
-
-\begin{figure}
-	\centering
-	\begin{adjustbox}{minipage=\linewidth}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth,scale = .5]{example2plots/row1_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row1_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row1_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row1_density_cluster}
-			\caption{}
-		\end{subfigure}
-
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row2_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row2_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row2_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row2_density_cluster}
-			\caption{}
-		\end{subfigure}
-
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row3_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row3_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row3_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row3_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\caption{True density (column 1), \pprspace (column 2), normalized cut (column 3) and estimated density (column 4) clusters for 3 different simulated data sets.
-Seed node for \pprspace denoted by a black cross.}
-		\label{fig:fig2}
-	\end{adjustbox}
-\end{figure}
-
-To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
-The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \citep{chaudhuri2010}.
-
-Figure \ref{fig:fig2} shows the degrading ability of \pprspace to recover density clusters as the two moons become less well-separated.
-Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, supporting our claim from Remark \ref{rmk: diameter}.
-Additionally, we note that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail, lending empirical weight to our overall message that \pprspace recovers only geometrically well-conditioned density clusters.
 
@@
 \label{sec: discussion}
-For given data, there are an almost limitless number of ways to define what the ``right'' clustering is.
-We have considered one such notion -- density upper level sets -- and have detailed a set of natural geometric criteria which, when appropriately satisfied, translate to provable bounds on estimation of the cluster by \ppr.
-We do not, however, provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set.
-Although we investigate the matter empirically, this is a direction for future work.
+
+There are an almost limitless number of ways to define what the ``right''
+clustering is. In this paper, we have considered one such notion---density upper
+level sets---and have detailed a set of natural geometric criteria which, when 
+appropriately satisfied, translate to provable bounds on estimation of the
+cluster by PPR. We do not, however, provide a theoretical lower bound showing
+that our geometric conditions are required for successful recovery on an upper
+level set. Although we investigate the matter empirically, this is a direction
+for future work.
 

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Sentence added by Alden

@@
 
-To the best of our knowledge, Theorem \ref{thm: mixing_time_upper_bound} is the
-first bound, albeit asymptotic, on the mixing time of random walks over
-neighborhood graphs which is independent of $n$, the number of vertices.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
+analogous mixing time bounds developed for the mixing time of the
+continuous-space ball walk over convex sets. To the best of our knowledge, our
+result is the first bound, albeit asymptotic, on the mixing time of random walks
+over neighborhood graphs that is independent of $n$, the number of vertices.
 

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Tweak to discussion

@@
 that PPR recovers geometrically well-conditioned density clusters, it would be  
-interesting to establish that it \emph{only} recovers such clusters, a point we
-return to below.
+interesting to establish that it \emph{only} recovers such clusters, a direction
+for future work.
 
@@
 appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We do not, however, provide a theoretical lower bound showing
-that our geometric conditions are required for successful recovery on an upper
-level set. Although we investigate the matter empirically, this is a direction
-for future work.
+cluster by PPR. We do not, however, provide theory to show that our geometric
+conditions are required for successful recovery of a density level set. This
+seems to be supported by our empirical work, and it remains a direction for
+future work.
 

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
fixed a few typos; final version

@@
 which extract clusters using locally-biased random walks around a user-specified
-seed node.  In constrast to pervious work, we adopt a traditional statistical
+seed node.  In constrast to previous work, we adopt a traditional statistical
 learning setup, where we obtain samples from an unknown distribution, and aim to
@@
 bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
-with the upper bound in \ref{asmp: embedding}, this leads to an upper bound on
+with the upper bound on diameter in \ref{asmp: embedding}, this leads to an upper bound on
 the mixing time over this subgraph.}
@@
 The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
-analogous mixing time bounds developed for the mixing time of the
-continuous-space ball walk over convex sets. To the best of our knowledge, our
+analogous mixing time bounds developed for the mixing time of a
+continuous-space ``ball walk'' over convex sets. To the best of our knowledge, our
 result is the first bound, albeit asymptotic, on the mixing time of random walks
@@
 Gaussian noise), considered a prototypical success story for spectral clustering
-algorithms. The first column shows the empirical density clusters $C[X]$
-and $C'[X]'$ for a particular threshold $\lambda$ of the density function; the 
+algorithms. The first column shows the empirical density clusters $\Cset[\Xbf]$
+and $\Cset'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the 
 second column shows the cluster recovered by PPR; the third column shows the

### 2019-05-24 neurips/local_spectral_density_clustering_arxiv.tex
Added arxiv version

--- 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
@@
 % [preprint] option:
-%     \usepackage[preprint]{neurips_2019}
+     \usepackage[preprint]{neurips_2019}
 
@@
 
-\author{%
-  David S.~Hippocampus\thanks{Use footnote for providing further information
-    about author (webpage, alternative address)---\emph{not} for acknowledging
-    funding agencies.} \\
-  Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  % examples of more authors
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \AND
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-}
+\author{
+Alden Green \And
+Sivaraman Balakrishnan \And
+Ryan J. Tibshirani}
 
@@
     \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c \frac{d}{\sigma}
+    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
@@
   \end{equation}
-  with probability at least $1-\delta$, where $c > 0$ is a universal constant. 
+  with probability at least $1-\delta$, where $c_1 > 0$ is a universal constant. 
 \end{theorem}
@@
 conditions are required for successful recovery of a density level set. This
-seems to be supported by our empirical work, and it remains a direction for
+seems to be supported by our empirical results, and it remains a direction for 
 future work.
@@
 \clearpage
+\appendix
 

### 2019-05-24 neurips/local_spectral_density_clustering_arxiv.tex
supplement -> appendix

@@
 The proof of Theorem \ref{thm: misclassification_rate}, along with all other
-proofs in this paper, is deferred to the supplementary material. Note that this 
+proofs in this paper, is deferred to the appendix. Note that this 
 result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
@@
 leads to analogous results which hold for \smash{$\pbf^{(\epsilon)}$}. We
-formally state and prove this in the supplement.
+formally state and prove this in the appendix.
 
@@
 the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
-of PPR on the ``two moons'' dataset. For space reasons, we defer details of the
-experimental settings to the supplement.
+of PPR on the ``two moons'' dataset. We defer details of the experimental
+settings to the appendix.
 

### 2019-05-27 neurips/local_density_clustering_proofs_neurips.tex

--- 2019-05-14 arxiv/arxiv_local_density_clustering_proofs.tex
@@
 \renewcommand{\theequation}{A.\arabic{equation}}
+\renewcommand{\thefigure}{\Alph{figure}}
 
@@
 
-\externaldocument{arxiv_local_density_clustering}
-
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
+\externaldocument{local_spectral_density_clustering_neurips}
+
+% \DeclarePairedDelimiter\abs{\left \lvert}{\right \rvert}
 
@@
 \newcommand{\defeq}{\overset{\mathrm{def}}{=}}
-% \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
+\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
 \newcommand{\vol}{\mathrm{vol}}
@@
 %%% Matrices
-\newcommand{\Abf}{\mathbf{A}}
+\newcommand{\Abf}{A}
 \newcommand{\Xbf}{X} % no bold font
-\newcommand{\Wbf}{\mathbf{W}}
-\newcommand{\Lbf}{\mathbf{L}}
-\newcommand{\Dbf}{\mathbf{D}}
-\newcommand{\Ibf}[1]{\mathbf{I}_{#1}}
+\newcommand{\Wbf}{W} % no bold font
+\newcommand{\Lbf}{L} % no
+\newcommand{\Dbf}{D}
+\newcommand{\Ibf}[1]{I_{#1}}
 
@@
 \newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}
+\newcommand{\Cest}{\widehat{C}}
 
@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
 
@@
 
+In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
+
 \section{Proofs}
 
-In this supplement, we present proofs for ``Local Clustering of Density Upper Level Sets''.
-Sections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
-In Sections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish a link between the conductance and local spread, and mixing time; this will be necessary for Theorem \ref{thm: mixing_time_upper_bound}.
-The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in Sections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
-\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and Corollary \ref{cor: appr}, in Sections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
+Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
+In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
+\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
 
@@
 
+We begin with some notation.
 Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
 Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
+Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
+
+Lemma \ref{lem: expansion_volume} allows us to reason about the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
 
@@
 	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
-	\begin{equation*}
+	\begin{equation}
+	\label{eqn: expansion_volume}
 	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
-	\end{equation*}
+	\end{equation}
 \end{lemma}
@@
 	\end{equation}
-	which is sufficient to prove the claim.
-
-	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ such that
-	\begin{equation*}
-	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon). \tag{$N := N(\epsilon)$}
-	\end{equation*}
-
-	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is itself compact, $\Asig$ is compact. Moreover,
+	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
+
+	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
+	\begin{equation*}
+	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
+	\end{equation*}
+	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
 	\begin{equation*}
@@
 	\end{equation*}
-	so by compactness there exists $x_1, \ldots,x_N \in \Aset$ such that
-	\begin{equation*}
+	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
+	\begin{equation}
+	\label{eqn: finite_subcover}
 	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
-	\end{equation*}
-
-	By the triangle inequality, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$.
-Of course, for each $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
+	\end{equation}
+	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
 Summarizing our findings, we have
 	\begin{equation}
-	\label{eqn: finite_subcover}
+	\label{eqn: finite_subcover-1}
 	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
@@
 	We next show a lower bound on $\nu(\Asig)$.
-Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and continuing, so that
+Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
 	\begin{equation*}
@@
 	\end{align*}
-	We turn to proving an upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
+	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
 	\begin{equation*}
@@
 	\begin{align*}
-	\nu(\Aset_{\sigma + \delta}) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
+	\nu(\Aset + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
 	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
@@
 
+We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
+
 \begin{lemma}
 	\label{lem: covering}
-	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Theorem \ref{lem: expansion_volume},
+	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Lemma \ref{lem: expansion_volume},
 	\begin{equation*}
@@
 Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
+We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
 
@@
 $\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
-Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
+Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
 As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
@@
 	\begin{equation*}
-	h = r - (r)^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
+	h = r - r^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
 	\end{equation*}	
@@
 	\end{equation*}
-	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{8d}$.
+	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{16d}$.
 
@@
 	\begin{align*}
-	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{2\sqrt{d}} \\
+	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{4\sqrt{d}} \\
 	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{\pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
@@
 	\label{lem: beta_integral}
-	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{8 d}$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{2\sqrt{d}}
+	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
 	\end{equation*}
@@
 	\end{equation*}
-	To upper bound the second integral, we apply the Taylor theorem with remainder to $(1 - u)^{-1/2}$, obtaining
+	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
 	\begin{equation*}
@@
 	\end{align*}
-	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the condition $\alpha \leq \frac{t^2}{8d}$. The result follows from the condition $\alpha \leq \frac{t^2}{8d}$. 
+	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
 \end{proof}
@@
 	\end{equation*}
-	each with probability at least $1 - \delta$. The claim follows in light of \eqref{eqn: weighted_cluster_volume}, which implies $p_V^c \geq p_V$. 
+	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
 \end{proof}
@@
 
-We recall some notation from the main text.
-For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
+We generalize some notation from the main text.
+For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
 Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$.
@@
 \begin{equation*}
-\norm{q_v^{(t + 1)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
-\end{equation*}
-We recall the \emph{degree, cut} and \emph{volume} functionals over a graph. For $u \in V$, $S \subseteq V$, 
-\begin{equation*}
-\cut(A;G) = \sum_{u \in A} \sum_{v \in A^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(A;G) = \sum_{u \in A} \deg(u;G)
+\norm{q_v^{(m)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
+\end{equation*}
+We recall the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well. For $u \in V$, $S \subseteq V$, 
+\begin{equation*}
+\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G)
 \end{equation*}
@@
 
-Letting the \emph{normalized cut} $\Phi(S;G)$ be defined as
-\begin{equation*}
-\Phi(S;G) = \frac{\cut(S, S^c; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
-\end{equation*}
-the \emph{conductance} is
-\begin{equation*}
-\Phi(G) = \min_{S \subseteq V} \Phi(S;G).
+Recalling the \emph{normalized cut} $\Phi(S;G)$ is defined (as in \eqref{eqn: normalized_cut}) as
+\begin{equation*}
+\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
+\end{equation*}
+we refer to the minimum normalized cut over $V$ as the \emph{conductance},
+\begin{equation*}
+\Phi(G) := \min_{S \subseteq V} \Phi(S;G).
 \end{equation*}
@@
 
-As we will see, Proposition \ref{prop: tv_mixing_time} is an essential step to providing an upper bound on the uniform mixing time.
+As we will see, Proposition \ref{prop: tv_mixing_time} is an essential step to proving an upper bound on the uniform mixing time.
 We justify this statement next, before moving on to proving Proposition \ref{prop: tv_mixing_time} in the following subsection.
 
-\paragraph{Uniform mixing time.}
-Consider the uniform distance \footnote{Note $d_{\textrm{unif}}$ is not a formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
+\paragraph{Uniform mixing time}
+Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
 \begin{equation*}
@@
 	Then 
-	\begin{align*}
-	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \\
-	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \\
-	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \\
-	\end{align*}
+	\begin{align}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
+	\end{align}
 	since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness  of the random walk guarantees  $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore
+As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and hypothesis,
 	\begin{equation*}
@@
 
-	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{4}$, then for any $) < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{TV} \leq \epsilon$.
+	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{TV} \leq \epsilon$.
 Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
@@
 	\end{equation*}
-	and so $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
+	and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
 \end{proof}
@@
 where the maximum is over all $w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$.
-Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{e_v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
+Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
 
@@
 \begin{remark}
-	$h_q^{(t)}$ permits an equivalent relation. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
+	$h_q^{(t)}$ permits an equivalent definition. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
 	\begin{equation*}
@@
 	\end{equation}
-	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}.
+	where we have used the standard notation $\pi(S) = \sum_{u \in S} \pi(u)$. 
+	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}, a concave, piecewise linear curve.
 \end{remark}
 
-\paragraph{Mixing over large sets.}
+\paragraph{Mixing over large sets}
 
@@
 
+	We observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_slope}
+	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}.
+	\end{equation}
+
 	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
@@
 	\end{equation*}
-	by the concavity of $h_0$ along with Lemma \ref{lem: lovasz_simonovits_subdifferential}. Some basic algebra then yields
+	by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
 	\begin{align*}
@@
 	\end{align*}
-	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and Lemma \ref{lem: lovasz_simonovits_subdifferential},  for $x \leq 1 - \mu$
+	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
 	\begin{equation*}
@@
 \end{proof}
-
-\begin{lemma}
-	\label{lem: lovasz_simonovits_subdifferential}
-	The subdifferential $v(x)$ of $h_q^{(0)}(x)$ satisfies
-	\begin{equation*}
-	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}
-	\end{equation*}
-\end{lemma}
 
@@
 \paragraph{Proof of Proposition \ref{prop: tv_mixing_time}.}
-For any $A \subseteq V$ and any integer $t \geq 0$,
-\begin{equation*}
-\max \set{h_v^{(t)}(\pi(A)), h_v^{(t)}(1 - \pi(A))} \geq \abs{q_v^{(t)}(A) - \pi(A)}
-\end{equation*}
-and taking max over both sides, we have
+For any $S \subseteq V$ and any integer $t \geq 0$,
+\begin{equation*}
+\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation*}
+and taking the maximum over all $S \subseteq V$ on both sides, we have
 \begin{equation*}
@@
 
-Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_v^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Proposition \ref{lem: lt_ub},
+Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_q^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Lemma \ref{lem: lt_ub},
 \begin{align*}
@@
 
-For $x \leq \mu$ or $x \geq 1 - \mu$,
+For $x \leq \mu$ or $x \geq 1 - \mu$, again by Lemma \ref{lem: mixing_time_small_sets},
 \begin{equation*}
@@
 
-\subsection{Population-level conductance profile.}
+\subsection{Population-level conductance.}
 \label{sec: population_conductance_function}
 
-We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability given by 
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
+We turn now to lower bounding the conductance over $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ (in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$).
+Our first step will be to introduce a population analogue $\widetilde{\Phi}_{\Pbb,r}$ of the conductance, and prove a lower bound on this quantity.
+Throughout this section, let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
+
+We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by 
+\begin{equation*}
+\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
+\end{equation*}
 
@@
 \begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
 \end{equation*}
@@
 \begin{equation*}
-\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr) \tag{$x \in \Csig$}
+\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
 \end{equation*}
@@
 \begin{equation*}
-\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
 \end{equation*}
@@
 \begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
+\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
 \end{equation*}
@@
 \begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
 \end{equation*}
@@
 \end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$, and we note this definition agrees with \eqref{eqn: continuous_conductance}.
+where $\Sset^c = \Csig \setminus \Sset$ and $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
 
@@
 	\label{prop: nonuniform_continuous_conductance}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
 Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
 	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r}(t) > \frac{\lambda_{\sigma}^2 r}{2^{12} \Lambda_{\sigma}^2 D L \sqrt{d}}.
+	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
 	\end{equation*}
@@
 \cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
-We first prove an analogous result for the special case of $f \equiv 1$ everywhere on $\Csig$.
-For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let
+In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a biLipschitz deformation of a convex set, but for completeness we produce all proofs here.
+
+\paragraph{Population-level conductance with uniform density}
+We first prove an analogous result for the special case of $f \propto 1$ everywhere on $\Csig$. For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let 
 \begin{equation*}
@@
 \end{equation*}
-The uniform continuous normalized cut and conductance profile are then defined analogously to the weighted case,
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r}(t) := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
+The uniform continuous normalized cut and conductance are then defined analogously to the weighted case,
+\begin{equation*}
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
 \end{equation*}
@@
 	\label{lem: uniform_continuous_conductance}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
 Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance of the $r$-ball walk satisfies
 	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{12} D L \sqrt{d}}.
+	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{13} \rho L \sqrt{d}}.
 	\end{equation*}
@@
 
-Assume Lemma \ref{lem: uniform_continuous_conductance} holds. Since $t \leq 1/2$, for any Borel $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq t$,
+Assume Lemma \ref{lem: uniform_continuous_conductance} holds, and note that for any $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq 1/2$,
 \begin{equation*}
@@
 	\label{lem: nonconvex_isoperimetry}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
 Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
 	\begin{equation*}
-	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{L D_{K}} \min(\nu(\Omega_1), \nu(\Omega_2))
+	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2))
 	\end{equation*}
@@
 	\begin{equation*}
-	R_i = \set{x \in K: g(x) \in \Omega_i}
+	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
 	\end{equation*}
@@
 	\begin{equation*}
-	\abs{x - y} \geq \frac{1}{L}\abs{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
+	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
 	\end{equation*}
@@
 	\begin{align*}
-	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{D} \min \{\nu(R_1), \nu(R_2)\} \\
-	& \geq \frac{2}{D L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
+	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
+	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
 	\end{align*}
@@
 	\begin{equation*}
-	\nu(\Omega_3) \geq\frac{2}{D L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
+	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
 	\end{equation*}
@@
 	\begin{equation*}
-	\norm{u - v} \leq \frac{r t}{\sqrt{d}}
+	\norm{u - v} \leq \frac{r t}{2\sqrt{d}}
 	\end{equation*}
@@
 
-The key result needed to show Lemma \ref{lem: one_step_distributions} is regarding the volume of the overlap $B(u,r) \cap B(v,r)$.
+The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$.
 
@@
 	\label{lem: overlap_balls_1}
-	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{\sqrt{d}}$ for some $0 < t < 1/8$. Then,
+	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1/8$. Then,
 	\begin{equation*}
@@
 	We will treat only the case where $\norm{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
-Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ is comprised of the union of two disjoint spherical caps, and thus
-	\begin{equation*}
-	\nu(I) = 2\nu(\mathrm{Cap}_r(r(1 - \frac{t}{2 \sqrt{d}}))).
+Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
+	\begin{equation*}
+	h = r\left(1 - \frac{t}{4\sqrt{d}}\right)
 	\end{equation*} 
@@
 	\begin{equation*}
-	\alpha = 1 - \frac{2r^2(1 - \frac{t}{2 \sqrt{d}}) - r^2(1 - \frac{t}{2 \sqrt{d}})^2}{r^2} = \frac{t^2}{4d}.
+	\alpha = 1 - \frac{2r^2(1 - \frac{t}{4 \sqrt{d}}) - r^2(1 - \frac{t}{4 \sqrt{d}})^2}{r^2} = \frac{t^2}{16d}.
 	\end{equation*}
@@
 	\end{align*}
-	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we can validly apply since $\alpha \leq \frac{t^2}{2d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.
+	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.
 \end{proof}
@@
 \begin{proof}[Proof of Lemma \ref{lem: one_step_distributions}]
-	Let $S_1 \cup S_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
-	\begin{equation*}
-	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
-	\end{equation*}
-	Since this will hold for arbitrary $S_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $S_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.
+	Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
+	\begin{equation*}
+	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
+	\end{equation*}
+	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.
 
@@
 	\begin{align*}
-	\widetilde{P}_{\nu,r}(u; S_1) - \widetilde{P}_{\nu,r}(v; S_1) & = 1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1)
+	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
 	\end{align*}
@@
 	\begin{equation*}
-	\widetilde{P}_{\nu,r}(u; S_2) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(S_2 \cap I)
-	\end{equation*}
-	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; S_1)$. As a result,
-	\begin{equation}
-	1 - \widetilde{P}_{\nu,r}(u; S_2) - \widetilde{P}_{\nu,r}(v; S_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
+	\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap I)
+	\end{equation*}
+	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; \Sset_1)$. As a result,
+	\begin{equation}
+	1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
 	\end{equation}
@@
 \paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-	Let $S_1 \cup S_2 = \Csig$, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
-\begin{equation*}
-\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{24 D L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
-\end{equation*}
-Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$. Then, dividing both sides by $\pi_{\nu,r}(S_1)$ yields the desired result.
+	Let $\Sset_1 \cup \Sset_2 = \Csig$ be arbitrary, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
+\end{equation*}
+Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$.
+Then, dividing both sides by $\pi_{\nu,r}(\Sset_1)$ yields the desired result, since $\Sset_1$ was arbitrary.
 
@@
 \end{align*}
-and $S_3' = \Csig \setminus S_1' \setminus S_2'$.
-
-Suppose $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$. Then,
-\begin{equation*}
-\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(S_1)}{8}
-\end{equation*}
-Similarly, if $\pi_{\nu,r}(S_1') < \pi_{\nu,r}(S_1)/2$, then since
+and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$.
+
+Suppose $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(\Sset_1)/2$. Then,
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(\Sset_1)}{8}
+\end{equation*}
+Similarly, if $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(S_1)/2$, then since
 \begin{equation*}
@@
 
-So we can assume $\pi_{\nu,r}(S_1') \geq \pi_{\nu,r}(S_1)/2$, and likewise for $S_2$. Now, for every $u \in S_1', v \in S_2'$, we have that
-\begin{equation*}
-\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;S_1) - \widetilde{P}_{\nu,r}(v;S_2) > 1 - \frac{\ell}{2}.
+So we can assume $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2$. Now, for every $u \in \Sset_1', v \in \Sset_2'$, we have that
+\begin{equation*}
+\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
 \end{equation*}
@@
 \begin{equation*}
-\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{3\sqrt{3 d}}.
-\end{equation*}
-and since $u \in S_1', v \in S_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(S_1', S_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
-\begin{equation*}
-\vol(S_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{3 D L \sqrt{3 d}} \min \set{\vol(S_1'), \vol(S_2')}
+\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{6\sqrt{3 d}}.
+\end{equation*}
+and since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
+\begin{equation*}
+\nu(\Sset_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{6 \rho L \sqrt{3 d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}
 \end{equation*}
@@
 \begin{align*}
-\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) & = \frac{1}{2} \bigl(\int_{S_2} \widetilde{P}_{\nu,r}(x; S_2)  d \pi_{\nu,r}(x) \bigr) \\
-& \geq \frac{\ell}{8} \pi_{\nu,r}(S_3') \\
-& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(S_3') \\
-& \geq \frac{\sqrt{2} r \ell^3}{12 D L \sqrt{d} \nu(\Csig)} \min \set{\nu(S_1'), \nu(S_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{12 D L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1'), \pi_{\nu,r}(S_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{24 D L \sqrt{d}} \min \set {\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}.
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) & = \frac{1}{2} \biggl(\int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_2)  d \pi_{\nu,r}(x) \biggr) \\
+& \geq \frac{\ell}{8} \pi_{\nu,r}(\Sset_3') \\
+& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \\
+& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1'), \pi_{\nu,r}(\Sset_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1), \pi_{\nu,r}(\Sset_2)}.
 \end{align*}
@@
 Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
-$\widetilde{{\Phi}}_{n,r}$, the graph conductance over $\widetilde{G}_{n,r}$ is defined in \eqref{eqn: local_spread_and_conductance}.
-Write $\piminwt := \min_{u \in \Csig[\Xbf]} \piwt_{n,r}(u)$.
-
-\begin{proposition}[Lower bound on graph conductance profile]
+We denote the graph conductance over $\widetilde{G}_{n,r}$ as $\widetilde{\Phi}_{n,r} := \Phi(G_{n,r}[\Csig[\Xbf]])$.
+To simplify notation, for $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
+\begin{equation*}
+\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
+\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
+\end{equation*}
+and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
+
+\begin{proposition}[Lower bound on graph conductance]
 	\label{prop: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, with probability one the following lower bound holds on the graph conductance:
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} > \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, with probability $1$ the following lower bound holds on the graph conductance:
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
 	\end{equation*}
@@
 	\label{lem: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $D$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$ Then with probability one,
-	\begin{equation*}
-	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then with probability $1$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
 	\end{equation*}
@@
 	\begin{align*}
-	\Phi(S;G) & \geq \sum_{u \in S} \frac{\cut(u, S^c; G)}{\vol(S;G)} \\
+	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
 	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
@@
 
-Proposition \ref{prop: graph_conductance_profile_lb} follows in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{12} D L \sqrt{d}} < \frac{1}{10}$.
+Proposition \ref{prop: graph_conductance_profile_lb} follows in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
+
+In Lemma \ref{lem: local_spread_lb}, we lower bound the local spread $s(\widetilde{G}_{n,r})$.
 
@@
 \begin{proof}
-	We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$ Therefore by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
+	Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
+Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
 	\begin{equation*}
@@
 
-Let $\mathfrak{B}(\Csig)$ be the Borel $\sigma$-algebra of $\Csig$, and define the conditional probability measures
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+For $\Sset \subseteq \Csig$ measurable, define the conditional probability measures
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
 \end{equation*} 
@@
 
-If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
+If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
 Proposition 5 of \cite{garciatrillos16} establishes that, for open connected domains with Lipschitz boundaries, such stagnating transportation maps exist.
-In particular, as $\Csig[\Xbf]$ consists of $\widetilde{n} = \abs{\Csig[\Xbf]}$ points sampled independently from $\widetilde{\Pbb}$, and $\Csig$ is a connected domain with Lipschitz boundary, the following implication is immediate.
+In particular, as $\Csig[\Xbf]$ consists of $\widetilde{n} := \abs{\Csig[\Xbf]}$ points sampled independently from $\widetilde{\Pbb}$, and $\Csig$ is a connected domain with Lipschitz boundary, the following implication is immediate.
 
@@
 
-Note that although $\Csig$ is closed not open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to $\Csig^o$, and \eqref{eqn: stagnating_transportation_maps} will hold for arbitrary extension of $T_n$ to $\Csig$.
+Note that although $\Csig$ is closed not open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and \eqref{eqn: stagnating_transportation_maps} will hold for any arbitrary extension of $T_n$ to $\Csig$.
 
@@
 
-We use stagnating transportation maps to relate the discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
+We use stagnating transportation maps to relate discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
 We fix some notation, letting $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$ for a transportation map $T_n$.
@@
 	\begin{equation*}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
+	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{2 \Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
 	\end{equation*}
@@
 	\begin{align}
-	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
+	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
+	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
+	& = \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \tag{change of variables} \nonumber \\
+	& \leq \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
+	& = \frac{1}{2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
 	\end{align}
 
-	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
+	By definition we have $\frac{d\Pbb(x)}{d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
 	\begin{align*}
@@
 	\end{align*}
-	which is the desired upper bound.
+	and we have the desired upper bound.
 \end{proof}
@@
 	\begin{equation*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{2 \Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
 	\end{equation*}
@@
 	\begin{align*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
+	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
+	& =  \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& \geq \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& = \frac{1}{2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
 	\end{align*}
@@
 
+Putting Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} together yields the following result, a lower bound on graph normalized cut.
+
 \begin{lemma}
@@
 	\label{lem: cont_stationary_dist}
-	Let $c > 0$ be a fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
+	Let $c > 0$ be any fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
 	\begin{equation*}
@@
 	\end{equation*}
-	uniformly over all sets $\Sset \subseteq \mathfrak{B}(\Csig)$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
+	uniformly over all measurable sets $\Sset \subseteq \Csig$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
 \end{lemma}
@@
 	\begin{equation*}
-	\liminf_{n \to \infty} \int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
-	\end{equation*}
-	where the convergence occurs as $n \to \infty$. On the other hand, by hypothesis
-	\begin{equation*}
-	\limsup_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
+	\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
+	\end{equation*}
+	where the convergence occurs uniformly over all $\Sset$ as $n \to \infty$. On the other hand, by hypothesis
+	\begin{equation*}
+	\liminf_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
 	\end{equation*}
@@
 	\end{equation*}
-	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is uniform over $\Sset$ as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
 
@@
 \widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
-& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{12} \Lambda_{\sigma}^2 D L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
+& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
 \end{align}
@@
 
-Since $r$ is fixed, $\min_{u \in V} \deg(u; \widetilde{G}_{n,r}) \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
-\begin{equation*}
+Since $r$ is fixed, $\degminwt \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
+\begin{equation}
+\label{eqn: tau_ub}
 \tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2}{\widetilde{\Phi}_{n,r}^2} \log\left(\frac{1440}{s(\widetilde{G}_{n,r})}\right) \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
-\end{equation*}
+\end{equation}
 and the claim follows from Proposition \ref{prop: graph_conductance_profile_lb} and Lemma \ref{lem: local_spread_lb}.
+In the statement of Theorem \ref{thm: mixing_time_upper_bound} we omit the factor of $3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right)$ as the first and third terms in \eqref{eqn: tau_ub} dominate.
 
@@
 	\begin{equation*}
-	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{- \frac{2nt^2}{m}\right\}
+	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{-nt^2\right\}
 	\end{equation*}
@@
 
-We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}. Let
+We will require large-sample and asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}.
+Let
 \begin{alignat*}{2}
@@
 	\label{lem: ball_bounds_in_probability}
-	Under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
+	Under the geometric conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
 	\begin{align}
-	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
-	\frac{\degmin}{n} & \geq \frac{6}{25}(1 - \epsilon)\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
 	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
@@
 	Additionally, with probability one,
-	\begin{align*}
-	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \\
-	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d
-	\end{align*}
+	\begin{align}
+	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
+	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d \label{eqn: max_vol_bound_asymp}
+	\end{align}
+
+	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
+	\begin{equation}
+	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\end{equation}
+
+	If additionally \ref{asmp: C'_bounded_density} holds (but not necessarily \ref{asmp: valid_region}): for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
+	\begin{equation}
+	\label{eqn: min_cluster_degree_bound_2}
+	\frac{\degminpr}{n} \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d
+	\end{equation}
 \end{lemma}
@@
 	\end{equation*}
-	As the same bound holds for $\degminpr$, \eqref{eqn: min_cluster_degree_bound} is shown. \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
+	and we have shown \eqref{eqn: min_cluster_degree_bound}.
+Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
+\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
 
@@
 	\end{equation*}
-	The final two statements therefore both follow from the Borel-Cantelli Lemma.
-\end{proof}
+	The two asymptotic statements \eqref{eqn: min_cluster_degree_bound_asymp} and \eqref{eqn: max_vol_bound_asymp} therefore both follow from the Borel-Cantelli Lemma.
+\end{proof}
+
+Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+	\begin{enumerate}
+		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
+\end{corollary}
 
@@
 Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $A \subseteq G = (V,E)$, and a good set $A^g \subseteq A$ with $\vol(A^g; G) \geq \vol(A; G)/2$.
-\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(A;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
+\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
 
@@
 	\label{lem: zhu}
-	Let $\epsilon \geq 0$, $v \in A^g$, $\alpha \leq \frac{\Psi(A; G)}{9}$, and $\vol_0 \in [1 - c,1 + c] \vol(A;G)$ for $0 < c < 1$.
+	Let $\epsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
 Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
@@
 
-	For any $\beta < \frac{3}{5(1 + c)}$, and $\epsilon \leq \frac{1}{10} \vol(A;G)$ the following bounds hold:
+	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \epsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
 	\begin{align}
-	\vol(S_{\beta} \setminus A; G) \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(A; G), \label{eqn: zhu_1}\\
-	\vol(A \setminus S_{\beta}; G) \leq \left(\frac{2\Phi(A;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(A;G)\right)\vol(A; G),  \label{eqn: zhu_2}
+	\vol(S_{\beta} \setminus S; G) & \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(S; G), \label{eqn: zhu_1}\\
+	\vol(S \setminus S_{\beta}; G) & \leq \left(\frac{2\Phi(S;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(S;G)\right)\vol(S; G).  \label{eqn: zhu_2}
 	\end{align}
@@
 
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}(\theta)}{9}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
 Moreover,
@@
 
-All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq \mathbf{\Psi}(\theta)/10$, the following bounds hold with probability tending to 1 as $n \to \infty$:
+All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq 1/10\tau_u(\theta)$, the following bounds hold with probability tending to 1 as $n \to \infty$:
 \begin{equation*}
@@
 \begin{align*}
-\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) & \geq \abs{\widehat{C} \setminus \Csig[\Xbf]} \degmin \\
-\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) & \geq \abs{\Csig[\Xbf] \setminus \widehat{C}} \degminwt,~ \textrm{and} \\
-\vol_{n,r}(\Csig[\Xbf]) & \leq \abs{\Csig[\Xbf]} \max_{x \in \Csig[\Xbf]} \degmax
-\end{align*}
-the claim follows in light of Lemma \ref{lem: ball_bounds_in_probability}.
+\abs{\widehat{C} \setminus \Csig[\Xbf]} & \leq \frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\degmin}   \\
+\abs{\Csig[\Xbf] \setminus \widehat{C}} & \leq \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\degminwt}, \quad \textrm{and} \\
+\abs{\Csig[\Xbf]} & \geq \frac{\vol_{n,r}(\Csig[\Xbf])}{\degmax}
+\end{align*}
+the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
 
@@
 We begin with some notation.
-Let $\Dbf$ and $\Wbf$ be the degree and (lazy) random walk matrices for the neighborhood graph $G_{n,r}$.
-Similarly, let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and (lazy) random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
+Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
 Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
@@
 
-Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(u) - \overline{\pibf}_{n,r}(u)$ over all $x \in \Xbf$ (where in an abuse of notation we consider $\overline{\pibf}_{n,r}(x) = 0$ for $x \in \Xbf \setminus \Csig[\Xbf]$).
+Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(x) - \overline{\pibf}_{n,r}(x)$.
+
 \begin{lemma} 
 	\label{lem: setup}
-	Let $0 < r < \sigma$ and $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
-Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
+	Let $0 < r < \sigma$ and $\alpha \leq \frac{1}{9 \tau_{\infty}(\widetilde{G}_{n,r})}$.
+Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
 	\begin{itemize}
@@
 		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminwt}
-		\end{equation}
-		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
+		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminwt}
+		\end{equation}
+		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy the cluster separation condition \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
 		\begin{equation}
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}.
+		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminpr}.
 		\end{equation}
@@
 	\label{eqn: leakage_soakage}
-	\ell_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\mathbf{I} - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
-	s_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\Wbf \widetilde{\mathbf{I}}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
+	\ell_t & := e_v (\Wbf \widetilde{I} )^t (I - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
+	s_t & := e_v (\Wbf \widetilde{I} )^t (\Wbf \widetilde{I}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
 	\end{align}
-	where $\mathbf{I}$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}$ is an $n \times n$ diagonal matrix with $\widetilde{\mathbf{I}}_{xx} = 1$ if $x \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}^c = \mathbf{I} - \widetilde{\mathbf{I}}$.
-
-	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step.
+	where $I$ is the $n \times n$ identity matrix, $\widetilde{I}$ is an $n \times n$ diagonal matrix with $\widetilde{I}_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{I}^c = I - \widetilde{I}$.
+
+	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $\Csig[\Xbf]$ on the $t + 1$th step.
 For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$.
-By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is soaked up into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
+By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is ``soaked up'' into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
 The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
@@
 
-	If additionally $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
+	If additionally $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
 	\begin{equation*}
@@
 		\item Since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$, and any $t \geq 1$,
+		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$ and $u \not\in \mathrm{supp}(q)$, and any $t \geq 1$,
 		\begin{align}
 		\label{eqn: one_step_bound}
-		q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
-		& \leq \frac{1}{\degminwt} 
+		q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 \max_{v \neq u} W_{vu} \nonumber \\
+		& \leq \frac{1}{2\degminwt} 
 		\end{align}
-		where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
+		where last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
 	\end{enumerate}
@@
 	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
-	& \leq \frac{\norm{\ell}_1 }{\degminwt}.
+	& \leq \frac{\norm{\ell}_1 }{\degminwt}. \tag{since $u \not\in \mathrm{supp}(\ell)$}
 	\end{align*}
@@
 	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
-	& \leq \frac{\norm{s}_1}{\degminpr}
+	& \leq \frac{\norm{s}_1}{2\degminpr}
 	\end{align*}
@@
 
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
+We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
 
@@
 
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}}{9}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$.
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
 As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
@@
 
-It remains to prove \eqref{eqn: gap_bounds}. Apply Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$ to obtain
+It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$ to obtain
 \begin{equation}
@@
 \end{equation}
-where the bound holds with probability tending to one as $n \to \infty$.
-
-By Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \mathbf{\Psi}}$ given by \eqref{eqn: initialization}, with probability tending to one as $n \to \infty$,
+
+Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
 \begin{equation}
 \label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa_1(\Cset).
+\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
 \end{equation}
@@
 	\begin{align*}
-	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{\mathbf{I}}^c)}_1 \\
-	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{\mathbf{I}}^c)(u, u') \\
+	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{I}^c)}_1 \\
+	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{I}^c)(u, u') \\
 	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf)_{uu}} \1((u,u') \in G_{n,r}) \\
@@
 
-\section{Additional Experiments}
+\section{Experiments}
+\label{sec: experimental_setting}
+
+In Section \ref{sec: experimental_setting}, we detail the experimental settings of Section \ref{sec: experiments} in the main text, and include an additional figure.
+
+\subsection{Experimental settings for Figure \ref{fig:fig1}}
+We sample points according to the density function $q$, where for $x \in \Rd$
+\begin{equation}
+q(x) :=
+\begin{cases}
+\lambda,~ & x \in [0,\sigma] \times \rho^{d-1} =: \Cset, \\
+\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
+(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
+0,~ & \textrm{otherwise},
+\end{cases}
+\end{equation}
+where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
+
+In the top-left and top-middle, we show draws of $n = 20000$ samples from two different density functions.
+In the top-left panel, $\sigma = \rho = 3.2$, while in the top-middle panel $\sigma = .1$ and $\rho = 3.2$.
+(For both, $d = 2$).
+
+The remaining four panels (top-right and the bottom row) in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
+In the top-right and bottom-left panels $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $\rho$ is fixed at $3.2$.
+In the bottom-middle and bottom-right panels, $\rho = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
+For each panel, the solid lines show, up to constants, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for the top-right and bottom-left panels and Theorem \ref{thm: mixing_time_upper_bound} for the bottom-middle and bottom-right panels.
+The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in the top-right and bottom-left panels, and $m = 20$ for the mixing time, dashed lines in the bottom-middle and bottom-right panels).
+For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
+Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
+
+\subsection{Experimental settings for Figure \ref{fig:fig2}}
+
+To form each of the three rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+Formally, the (respective) generative models for the data are
+\begin{align}
+Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
+X(Z,\theta) & = 
+\begin{cases}
+\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
+\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
+\end{cases}
+\end{align}
+
+where 
+\begin{align*}
+\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
+\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
+\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} 
+\end{align*}
+for $I_d$ the $d \times d$ identity matrix.
+The first column consists of the empirical density clusters $C[\Xbf]$ and $C'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+
+\subsection{Performance of \pprspace with high-dimensional noise.}
+
+Figure \ref{fig:fig3} is similar to Figure \ref{fig:fig2} of the main text, with parameters
+\begin{equation*}
+\mu_1 = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}).
+\end{equation*}
+The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:fig2} in the main text) represent observations in low-density regions.
+While the \pprspace sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C[\Xbf]$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\caption{}
+		\label{fig:fig3}
+	\end{adjustbox}
+\end{figure}
 

### 2019-05-27 neurips/local_spectral_density_clustering_arxiv.tex
small space tweak

@@
 \newcommand{\dist}{\mathrm{dist}}
+\newcommand{\Err}{\mathrm{Err}}
+\newcommand{\TV}{\mathrm{TV}}
 
@@
 \newcommand{\Csig}{\Cset_{\sigma}}
-\newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
+\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}
 
@@
 \newcommand{\Cest}{\widehat{C}}
+\newcommand{\degminpr}{\deg_{\min}'}
+\newcommand{\degminwt}{\widetilde{\deg}_{\min}}
+\newcommand{\degmaxwt}{\widetilde{\deg}_{\max}}
+\newcommand{\degmax}{\deg_{\max}}
+\newcommand{\piminwt}{\widetilde{\pi}_{\min}}
+\newcommand{\piminpr}{\pibf_{\min}'}
+\newcommand{\degmin}{\deg_{\min}}
 
@@
 \newcommand{\pprspace}{{\sc PPR~}}
+
+%%% Tilde notation for quantities over the expansion set 
+\newcommand{\wn}{\widetilde{n}}
+\newcommand{\wX}{\widetilde{\Xbf}}
+\newcommand{\wx}{\widetilde{x}}
+\newcommand{\wz}{\widetilde{z}}
+\newcommand{\wbz}{\widetilde{\bf{z}}}
+\newcommand{\wu}{\widetilde{u}}
+\newcommand{\wPbb}{\widetilde{\Pbb}}
+\newcommand{\wf}{\widetilde{f}}
+\newcommand{\wDbf}{\widetilde{\Dbf}}
+\newcommand{\piwt}{\widetilde{\pi}}
 
@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
 \newtheorem{corollary}{Corollary}
@@
 
+\vspace{0.1in}
 \begin{abstract}
@@
 
+In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
+
+\section{Proofs}
+
+Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
+In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
+\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
+
+\subsection{Volume estimates}
+\label{sec: volume_estimates}
+
+We begin with some notation.
+Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
+Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
+Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
+
+Lemma \ref{lem: expansion_volume} allows us to reason about the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
+
+\begin{lemma}
+	\label{lem: expansion_volume}
+	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
+	\begin{equation}
+	\label{eqn: expansion_volume}
+	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	We will show that for any $\epsilon > 0$, 
+	\begin{equation}
+	\label{eqn: ratio_of_volume}
+	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
+	\end{equation}
+	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
+
+	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
+	\begin{equation*}
+	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
+	\end{equation*}
+	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
+	\begin{equation*}
+	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
+	\end{equation*}
+	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
+	\begin{equation}
+	\label{eqn: finite_subcover}
+	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
+	\end{equation}
+	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
+Summarizing our findings, we have
+	\begin{equation}
+	\label{eqn: finite_subcover-1}
+	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
+	\end{equation}
+
+	We next show a lower bound on $\nu(\Asig)$.
+Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
+	\begin{equation*}
+	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
+	\end{equation*}
+	Observe that $\bigcup_{i = 1}^{N} \Asig^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$.
+As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
+	\begin{align*}
+	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
+	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
+	\begin{equation*}
+	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
+	\end{equation*}
+
+	As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
+	\begin{equation*}
+	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
+	\end{equation*}
+	and therefore
+	\begin{align*}
+	\nu(\Aset + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
+	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
+	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
+\end{proof}
+
+We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
+
+\begin{lemma}
+	\label{lem: covering}
+	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Lemma \ref{lem: expansion_volume},
+	\begin{equation*}
+	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
+	\begin{equation*}
+	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
+	\end{equation*}
+	since then
+	\begin{equation*}
+	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{(i)}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{(i)}).
+	\end{equation*}
+
+	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
+	\begin{equation}
+	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
+	\end{equation}
+	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
+Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
+	\begin{equation*}
+	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
+	\end{equation*}
+	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
+\end{proof}
+
+We will need to carefully control the volume of expansion sets using the estimate in Lemma \ref{lem: expansion_volume}; Lemma \ref{lem: Taylor_series} serves this purpose.
+\begin{lemma}
+	\label{lem: Taylor_series}
+	For any $0 \leq x \leq 1/2d$,
+	\begin{align*}
+	(1 + x)^d & \leq 1 + 2\dx \\
+	(1 - x)^d & \geq 1 - 2\dx.
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	We take the binomial expansion of $(1 + x)^d$:
+	\begin{align*}
+	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
+	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
+	\end{align*}
+
+	The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
+\end{proof}
+
+Let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}.
+Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
+We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
+
+\begin{lemma}
+	\label{lem: expected_number_boundary_points}
+	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	\Pbb(\Csigr) \leq \frac{2dr}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	\end{equation*}	
+\end{lemma}
+\begin{proof}
+	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
+	\begin{equation*}
+	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
+	\end{equation*}
+	where $t_i = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
+	\begin{equation}
+	\label{eqn: partition_ub}
+	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
+	\end{equation}
+
+	\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
+	\begin{equation*}
+	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
+	\end{equation*}
+	and writing
+	\begin{equation*}
+	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
+	\end{equation*}
+	we have
+	\begin{align}
+	\label{eqn: telescoping_sum}
+	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
+	& = \sum_{i = 1}^{k} 
+	\underbrace{\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
+	\end{align}
+	where the second equality comes from rearranging terms in the sum.
+
+	% AJG 5/14/19: This argument makes sense, correct?
+	We first consider the term $\Sigma_k$.
+$\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
+Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
+As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
+	\begin{equation}
+	\label{eqn: slice_volume_bound}
+	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
+	\end{equation}
+	which in turn gives
+	\begin{align}
+	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
+	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (u_{i,k} = t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
+	\end{align}
+	\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
+	\begin{align}
+	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
+	& \overset{(i)}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
+	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
+	\end{align}
+	where $(i)$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
+
+	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
+	\begin{align}
+	\xi & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
+	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
+\label{eqn: xi_ub}
+	\end{align}
+	where $(ii)$ follows from \eqref{eqn: slice_volume_bound}, and $(iii)$ from Lemma \ref{lem: Taylor_series}.
+As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
+\end{proof}
+
+Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
+\begin{equation*}
+\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr)
+\end{equation*}
+\begin{lemma}
+	\label{lem: local_conductance}
+	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
+	\begin{equation*}
+	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as $B(x,\sigma) \subseteq \Csig$,
+	\begin{equation*}
+	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr)
+	\end{equation*}
+	Without loss of generality, let $\norm{u - x} = \sigma$; it is not hard to see that if $\norm{u - x} < \sigma$, the volume of the overlap will only grow.
+Then, since $\norm{u  - x} = \sigma$, $B(u, r) \cap B(x, \sigma)$ contains a spherical cap of radius $r$ and height
+	\begin{equation*}
+	h = r - r^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
+	\end{equation*}	
+	which by Lemma \ref{lem: volume_of_spherical_cap} has volume
+	\begin{equation*}
+	\nu_{cap} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
+	\end{equation*}
+	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{16d}$.
+
+	Then by Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
+	\begin{align*}
+	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{4\sqrt{d}} \\
+	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{\pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
+	\end{align*}
+\end{proof}
+
+The following formula for the volume of the spherical cap, stated in terms of the incomplete beta function, is well known. We include it without proof.
+
+\begin{lemma}
+	\label{lem: volume_of_spherical_cap}
+	Let $\mathrm{Cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
+	\begin{equation*}
+	\nu\bigl( \mathrm{Cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	\end{equation*}
+	where
+	\begin{equation*}
+	\alpha := 1 - \frac{2 r h - h^2}{r^2}
+	\end{equation*}
+	and
+	\begin{equation*}
+	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
+	\end{equation*}
+	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
+\end{lemma}
+
+\begin{lemma}
+	\label{lem: beta_integral}
+	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We can write 
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
+	\end{equation*}
+	The first integral is simply the beta function, with
+	\begin{equation*}
+	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
+	\end{equation*}
+	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
+	\begin{equation*}
+	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
+	\end{equation*}
+	As a result,
+	\begin{align*}
+	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
+	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
+	& \overset{(iv)}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
+	& =  3\alpha^{1/2}.
+	\end{align*}
+	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
+\end{proof}
+
+Lemma \ref{lem: beta_function} follows from $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
+\begin{lemma}
+	\label{lem: beta_function}
+	\begin{equation*}
+	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
+	\end{equation*}
+\end{lemma}
+
+\subsection{Density-weighted cut and volume estimates}
+\label{sec: density_weighted_cut_and_volume_estimates}
+
+For notational ease, we write
+\begin{align*}
+\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
+\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
+\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+\end{align*}
+for the random variable, mean, and probability of cut size and volume, respectively.
+
+\begin{lemma}
+	\label{lem: expected_density_cut}
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We can write $\cut_{n,r}$ as a double sum,
+	\begin{equation}
+	\label{eqn: density_cut_expansion}
+	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r)
+	\end{equation}
+	and by linearity of expectation, we obtain
+	\begin{equation*}
+	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
+	\end{equation*}
+	Writing this with respect to the density function $f$, we have
+	\begin{align*}
+	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
+	\end{align*}
+	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
+Then, upper bounding the integral using Lemma \ref{lem: expected_density_cut} gives the final result.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: expected_density_volume}
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{equation*}
+	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
+	\begin{equation}
+	\label{eqn: volume_expansion}
+	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
+	\end{equation}
+	and by linearity of expectation we obtain
+	\begin{equation*}
+	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
+	\end{equation*}
+	Writing this with respect to the density function $f$, we have
+	\begin{align*}
+	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
+	\end{align*}
+	whence the claim then follows by Lemma \ref{lem: local_conductance}.
+\end{proof}
+
+To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
+\begin{equation*}
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
+\end{equation*}
+to $p_K$ and $p_V$.
+
+In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
+These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
+
+\begin{lemma}
+	\label{lem: prob_bound_cutvol}
+	For any $\delta \in (0,1]$,
+	\begin{equation}
+	\label{eqn: numerator_additive_bound}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
+	\end{equation}
+	each with probability at least $1 - \delta$. 
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
+	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
+	\end{equation*}
+	with kernels
+	\begin{align*}
+	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
+	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
+	\end{align*}
+
+	Similarly,
+	\begin{equation*}
+	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
+	\end{equation*}
+	with kernel,
+	\begin{equation*}
+	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
+	\end{equation*}
+
+	From Lemma \ref{lem: bounded_difference} we therefore have
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation*}
+	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
+\end{proof}
+
+\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
+\label{sec: proof_of_theorem_1}
+
+The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
+All that remains is some algebra, which we take care of below.
+
+Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
+\begin{equation}
+\label{eqn: conductance_representation_1}
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
+\end{equation}
+Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
+Along with (\ref{eqn: conductance_representation_1}) this means
+\begin{equation*}
+\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+\end{equation*}
+for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
+Now, some straightforward algebraic manipulations yield
+\begin{align*}
+\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
+& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
+& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
+\end{align*}
+By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
+\begin{equation*}
+\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
+\end{equation*}
+Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
+\begin{equation*}
+n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
+\end{equation*}
+which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+
+\subsection{Mixing time on graphs}
+\label{sec: mixing_time_on_graphs}
+
+We generalize some notation from the main text.
+For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
+Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$.
+An important intermediate quantity used to bound the relative pointwise mixing time $\tau_{\infty}(G)$ is the total variation distance between the distributions $q_v^{(m)} := q^{(m)}(v,\cdot)$ and $\pi$,
+\begin{equation*}
+\norm{q_v^{(m)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
+\end{equation*}
+We recall the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well. For $u \in V$, $S \subseteq V$, 
+\begin{equation*}
+\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G)
+\end{equation*}
+
+The \emph{local spread} is defined as
+\begin{equation*}
+s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}
+\end{equation*}
+
+Recalling the \emph{normalized cut} $\Phi(S;G)$ is defined (as in \eqref{eqn: normalized_cut}) as
+\begin{equation*}
+\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
+\end{equation*}
+we refer to the minimum normalized cut over $V$ as the \emph{conductance},
+\begin{equation*}
+\Phi(G) := \min_{S \subseteq V} \Phi(S;G).
+\end{equation*}
+
+Proposition \ref{prop: tv_mixing_time} relates these geometric quantities to the TV distance between $q_v^{(t)}$ and stationary distribution $\pi$.
+\begin{proposition}
+	\label{prop: tv_mixing_time}
+	For any $v \in V$, and any $0 < a \leq 1$,
+	\begin{equation*}
+	\norm{q_v^{(t + 3)} - \pi}_{TV} \leq \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2as(G)} + \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
+\end{proposition}
+
+As we will see, Proposition \ref{prop: tv_mixing_time} is an essential step to proving an upper bound on the uniform mixing time.
+We justify this statement next, before moving on to proving Proposition \ref{prop: tv_mixing_time} in the following subsection.
+
+\paragraph{Uniform mixing time}
+Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
+\begin{equation*}
+d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: tv_to_uniform_distance}
+	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
+	\begin{equation*}
+	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
+	\begin{align}
+	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
+	& \overset{(i)}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
+	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
+	\end{align}
+	where $(i)$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.
+
+	Then 
+	\begin{align}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
+	\end{align}
+	since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
+As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and hypothesis,
+	\begin{equation*}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \leq \frac{1}{14}.
+	\end{equation*}
+
+	Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
+	\begin{equation}
+	d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{2}{7} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
+	\end{equation}
+	The recurrence relation of \eqref{eqn: tv_to_uniform_distance_2} along with the initial condition $d_{\textrm{unif}}(q_v^{(t)}, \pi) \leq 1$ yields
+	\begin{equation*}
+	d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{10}{28} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
+	\end{equation*}
+	and the claim is shown.
+\end{proof}
+
+Together, Proposition \ref{prop: tv_mixing_time} and Lemma \ref{lem: tv_to_uniform_distance} imply the main result of this section.
+
+\begin{proposition}
+	\label{prop: pointwise_mixing_time}
+	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
+	\begin{equation*}
+	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+	\end{equation*}
+\end{proposition}
+\begin{proof}
+	Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$. Then,
+	\begin{equation*}
+	\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
+	\end{equation*}
+	and so by Proposition \ref{prop: tv_mixing_time},
+	\begin{equation*}
+	\norm{q_v^{(\tau_0 + 3)} - \pi}_{TV} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+	\end{equation*}
+
+	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{TV} \leq \epsilon$.
+Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
+	\begin{equation*}
+	\norm{q_v^{(\tau_1)} - \pi}_{TV} \leq \frac{1}{14 s(G)}
+	\end{equation*}
+	and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
+\end{proof}
+
+\subsection{Proof of Proposition \ref{prop: tv_mixing_time}.}
+\label{sec: proof_of_proposition_tv_mixing_time}
+
+For arbitrary starting distribution $q$ (meaning $\textrm{supp}(q) \subseteq V$ and $\sum_{u \in V}q(u) = 1$), and for $t \geq 0$ an integer, let $q^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $q$.
+Consider the distance function $h_q^{(t)}, t \geq 0$,
+\begin{equation*}
+h_q^{(t)}(x) = \max \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
+\end{equation*}
+where the maximum is over all $w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$.
+Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
+
+\vskip 0.1 in
+\begin{remark}
+	$h_q^{(t)}$ permits an equivalent definition. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
+	\begin{equation*}
+	\frac{q^{(m)}(u_1)}{\pi(u_1)} \geq \frac{q^{(m)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q^{(m)}(u_N)}{\pi(u_N)}
+	\end{equation*}
+	and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that,
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_curve}
+	h_q^{(t)}(x) = \sum_{j = 1}^{k - 1} (q^{(m)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q^{(m)}(u_k) - \pi(u_k) \right).
+	\end{equation}
+	where we have used the standard notation $\pi(S) = \sum_{u \in S} \pi(u)$. 
+	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}, a concave, piecewise linear curve.
+\end{remark}
+
+\paragraph{Mixing over large sets}
+
+For $0 \leq \mu \leq 1$ and $\mu \leq x \leq 1 - \mu$ let 
+\begin{equation*}
+\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(1 - \mu)
+\end{equation*}
+be the linear interpolator between $h_q^{(0)}(\mu)$ and $h_q^{(0)}(1 - \mu)$.
+
+\begin{lemma}
+	\label{lem: lt_ub}
+	For any $0 \leq \mu \leq 1/2$ and $\mu \leq x \leq 1 - \mu$ and $t \geq 0$, 
+	\begin{equation*}
+	h_q^{(t)}(x) \leq \ell_{\mu}(x) + \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 }\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
+\end{lemma}
+
+Theorem \ref{lem: lt_ub} is a direct consequence of Theorem 1.2 of \cite{lovasz1990}. To state the latter, we introduce
+\begin{equation*}
+C_{\mu} = \max \set{\frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu}
+\end{equation*}
+\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
+	\label{thm: lovasz_simonovits_1993}
+	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
+	\begin{equation*}
+	h_q^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation*}
+\end{theorem}
+
+\begin{proof}[Proof of Lemma \ref{lem: lt_ub}]
+	Fix $0 \leq \mu \leq \frac{1}{2}$. We will show that for all $\mu \leq x \leq 1 - \mu$
+	\begin{equation}
+	\label{eqn: lt_ub_1}
+	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
+	\end{equation}
+	whence the claim follows by Theorem \ref{thm: lovasz_simonovits_1993}.
+
+	We observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_slope}
+	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}.
+	\end{equation}
+
+	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
+	\begin{equation*}
+	h_q^{(0)}(x) \leq h_q^{(0)}(\mu) + (x - \mu)\frac{h_q^{(0)}(\mu)}{\mu}
+	\end{equation*}
+	by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
+	\begin{align*}
+	h_q^{(0)}(x) - \ell_{\mu}(x) & \leq h_q^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu)\right) + \frac{h_q^{(0)}(\mu)}{\mu}(x - \mu) \\
+	& =  \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(\mu) + \frac{h_q^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu) \\
+	& \leq \sqrt{x - \mu} \left(\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} \right)
+	\end{align*}
+	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
+	\begin{equation*}
+	h_q^{(0)}(x) \leq h_q^{(0)}(1 - \mu) + (1 - x - \mu).
+	\end{equation*}
+	Similar manipulations to above give the upper bound
+	\begin{align*}
+	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
+	\end{align*}
+	and \eqref{eqn: lt_ub_1} follows.
+\end{proof}
+
+\paragraph{Mixing over small sets.}
+
+\begin{lemma}
+	\label{lem: mixing_time_small_sets}
+	Let $0 \leq a \leq 1$, and $t \geq 1$ an integer. Then for any $x \leq as(G)$ or $x \geq 1 - as(G)$,
+	\begin{equation*}
+	h_v^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_1}
+	h_v^{(t)}(x) \leq q_v^{(m)}(U_{k - 1}) + q_v^{(m)}(u_k)
+	\end{equation}
+
+	We will rely on the key fact that for any $u \neq v, t \geq 1$,
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_2}
+	q_v^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
+	\end{equation}
+
+	On the other hand if $u = v$,
+	\begin{equation}
+	\label{eqn: mixing_time_small_sets_3}
+	q_v^{(m)}(u) \leq \frac{1}{2^t} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
+	\end{equation}
+	Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
+	\begin{equation*}
+	h_v^{(t)}(x) \leq \frac{1}{2^t} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
+	\end{equation*}
+	Since $x \leq a s(G)$, 
+	\begin{equation*}
+	\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
+	\end{equation*}
+
+	For any $0 \leq b \leq 1$, $x \geq 1 - b$ implies $h_v^{(t)}(x) \leq b$. Taking $b = a s(G)$, the claim is shown.
+\end{proof}
+
+\paragraph{Proof of Proposition \ref{prop: tv_mixing_time}.}
+For any $S \subseteq V$ and any integer $t \geq 0$,
+\begin{equation*}
+\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation*}
+and taking the maximum over all $S \subseteq V$ on both sides, we have
+\begin{equation*}
+\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{TV}.
+\end{equation*}
+
+Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_q^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Lemma \ref{lem: lt_ub},
+\begin{align*}
+h_v^{(t + 3)}(x) & = h_q^{(t)}(x) \\
+& \leq \max \set{h_q^{(0)}(\mu), h_q^{(0)}(1 - \mu) }  + \left(\frac{1}{1 - 2 \mu} + \frac{1}{2\mu}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t\\
+& \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2a s(G)} + \frac{1}{2 a s(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{align*}
+where the last inequality comes from application of Lemma \ref{lem: mixing_time_small_sets} to $h_q^{(t)} = h_v^{(t + 3)}$.
+
+For $x \leq \mu$ or $x \geq 1 - \mu$, again by Lemma \ref{lem: mixing_time_small_sets},
+\begin{equation*}
+h_v^{(t + 3)}(x) \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}}
+\end{equation*}
+and the proof is complete.
+
+\subsection{Population-level conductance.}
+\label{sec: population_conductance_function}
+
+We turn now to lower bounding the conductance over $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ (in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$).
+Our first step will be to introduce a population analogue $\widetilde{\Phi}_{\Pbb,r}$ of the conductance, and prove a lower bound on this quantity.
+Throughout this section, let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
+
+We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by 
+\begin{equation*}
+\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
+\end{equation*}
+
+Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
+\begin{equation*}
+\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
+\end{equation*}
+Letting the \emph{$\Pbb$-local conductance} be given by
+\begin{equation*}
+\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
+\end{equation*}
+a bit of algebra verifies that
+\begin{equation*}
+\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
+\end{equation*}
+
+We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
+\begin{equation*}
+\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
+\end{equation*}
+the \emph{$\Pbb$-(continuous) normalized cut} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
+\end{equation*}
+and the \emph{$\Pbb$-(continuous) conductance} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\Pbb,r}(\Sset)
+\end{equation*}
+where $\Sset^c = \Csig \setminus \Sset$ and $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
+
+\begin{proposition}
+	\label{prop: nonuniform_continuous_conductance}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
+	\end{equation*}
+\end{proposition}
+
+Similar results are already known (see e.g.
+\cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
+In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a biLipschitz deformation of a convex set, but for completeness we produce all proofs here.
+
+\paragraph{Population-level conductance with uniform density}
+We first prove an analogous result for the special case of $f \propto 1$ everywhere on $\Csig$. For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let 
+\begin{equation*}
+\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) d\pi_{\nu,r}(x).
+\end{equation*}
+The uniform continuous normalized cut and conductance are then defined analogously to the weighted case,
+\begin{equation*}
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
+\end{equation*}
+
+\begin{lemma}
+	\label{lem: uniform_continuous_conductance}
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{13} \rho L \sqrt{d}}.
+	\end{equation*}
+\end{lemma}
+
+Most of the technical work needed to show Proposition \ref{prop: nonuniform_continuous_conductance} involves proving Lemma \ref{lem: uniform_continuous_conductance}.
+We defer this work to the next subsection, and first show that Proposition \ref{prop: nonuniform_continuous_conductance} is a simple consequence of Lemma \ref{lem: uniform_continuous_conductance} along with \ref{asmp: bounded_density}.
+
+\paragraph{Proof of Proposition \ref{prop: nonuniform_continuous_conductance}.}
+
+Assume Lemma \ref{lem: uniform_continuous_conductance} holds, and note that for any $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq 1/2$,
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)}
+\end{equation*}
+By \ref{asmp: bounded_density} we obtain
+\begin{align*}
+\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(S \cap B(x,r)) f(x) \dx}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) f(x) \dx} \\
+& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(S \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
+& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \widetilde{\Phi}_{\nu,r}(\Sset)
+\end{align*}
+and the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
+
+\subsection{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
+\label{sec: proof_of_lemma_continuous_conductance}
+
+As is standard, the proof of a lower bound on the conductance relies on an isoperimetric inequality.
+
+\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
+	\label{lem: nonconvex_isoperimetry}
+	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
+	\begin{equation*}
+	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2))
+	\end{equation*}
+\end{lemma}
+The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even in the convex setting, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among others.
+Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting given by  Assumption \ref{asmp: embedding} is not difficult.
+
+\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
+	For $\Omega_i, i = 1,2,3$, denote the preimage
+	\begin{equation*}
+	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
+	\end{equation*}
+	For any $x \in R_1, y \in R_2$, 
+	\begin{equation*}
+	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
+	\end{equation*}
+	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
+	\begin{equation*}
+	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
+	\end{equation*}
+	By Theorem 2.2 of \cite{lovasz1990},
+	\begin{align*}
+	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
+	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
+	\end{align*}
+	and by the measure-preserving property of $g$, this implies
+	\begin{equation*}
+	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
+	\end{equation*}
+\end{proof}
+
+We will also need an upper bound on the distance between transition probability densities $\widetilde{P}_{\nu,r}(u,\cdot)$ and $\widetilde{P}_{\nu,r}(v,\cdot)$ for $u,v \in \Csig$ close together. 
+\begin{lemma}[One-step distributions]
+	\label{lem: one_step_distributions}
+	Let $u,v \in \Csig$ be such that 
+	\begin{equation*}
+	\norm{u - v} \leq \frac{r t}{2\sqrt{d}}
+	\end{equation*}
+	for some $0 < t < 1/8$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
+	\begin{equation*}
+	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
+	\end{equation*}
+	where $\norm{P - Q}_{TV}$ is the total variation distance between probabilities $P$ and $Q$. 
+\end{lemma}
+
+The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$.
+
+\begin{lemma}
+	\label{lem: overlap_balls_1}
+	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1/8$. Then,
+	\begin{equation*}
+	\nu(B(u,r) \cap B(v,r)) \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We will treat only the case where $\norm{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
+Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
+	\begin{equation*}
+	h = r\left(1 - \frac{t}{4\sqrt{d}}\right)
+	\end{equation*} 
+	From Lemma \ref{lem: volume_of_spherical_cap} we therefore obtain
+	\begin{equation*}
+	\nu(I) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	\end{equation*}
+	where
+	\begin{equation*}
+	\alpha = 1 - \frac{2r^2(1 - \frac{t}{4 \sqrt{d}}) - r^2(1 - \frac{t}{4 \sqrt{d}})^2}{r^2} = \frac{t^2}{16d}.
+	\end{equation*}
+	Expanding the incomplete beta function in integral form, we therefore have
+	\begin{align*}
+	\nu(I) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
+	& \overset{(i)}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
+	& \overset{(ii)}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
+	\end{align*}
+	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem: one_step_distributions}]
+	Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
+	\begin{equation*}
+	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
+	\end{equation*}
+	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.
+
+	Now, note that
+	\begin{align*}
+	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
+	\end{align*}
+	Let $I := B(u,r) \cap B(v,r)$. Then we have
+	\begin{equation*}
+	\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap I)
+	\end{equation*}
+	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; \Sset_1)$. As a result,
+	\begin{equation}
+	1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
+	\end{equation}
+	As \eqref{eqn: one_step_1} demonstrates, the overlap of the one-step distributions is related to the volume of the intersection between $B(u,r)$ and $B(v,r)$ within $\Csig$.
+
+	From here, some simple manipulations yield
+	\begin{align}
+	\nu(\Csig \cap I)  & = \nu(I) - \nu(I \setminus \Csig) \nonumber \\
+	& \geq \nu(I) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
+	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
+	\end{align}
+	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
+\end{proof}
+
+\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
+Let $\Sset_1 \cup \Sset_2 = \Csig$ be arbitrary, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
+\end{equation*}
+Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$.
+Then, dividing both sides by $\pi_{\nu,r}(\Sset_1)$ yields the desired result, since $\Sset_1$ was arbitrary.
+
+Now, consider the sets
+\begin{align*}
+S_1' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}} \\
+S_2' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}}
+\end{align*}
+and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$.
+
+Suppose $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(\Sset_1)/2$. Then,
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(\Sset_1)}{8}
+\end{equation*}
+Similarly, if $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(S_1)/2$, then since
+\begin{equation*}
+\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) = \int_{S_2} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x)
+\end{equation*}
+a symmetric result holds.
+
+So we can assume $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2$. Now, for every $u \in \Sset_1', v \in \Sset_2'$, we have that
+\begin{equation*}
+\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
+\end{equation*}
+
+By Lemma \ref{lem: one_step_distributions}, we therefore have
+\begin{equation*}
+\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{6\sqrt{3 d}}.
+\end{equation*}
+and since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
+\begin{equation*}
+\nu(\Sset_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{6 \rho L \sqrt{3 d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}
+\end{equation*}
+We now prove the desired result:
+\begin{align*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) & = \frac{1}{2} \biggl(\int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_2)  d \pi_{\nu,r}(x) \biggr) \\
+& \geq \frac{\ell}{8} \pi_{\nu,r}(\Sset_3') \\
+& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \\
+& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1'), \pi_{\nu,r}(\Sset_2')} \\
+& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1), \pi_{\nu,r}(\Sset_2)}.
+\end{align*}
+
+\subsection{Graph conductance and local spread.}
+\label{sec: graph_conductance_and_local_spread}
+
+Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
+We denote the graph conductance over $\widetilde{G}_{n,r}$ as $\widetilde{\Phi}_{n,r} := \Phi(G_{n,r}[\Csig[\Xbf]])$.
+To simplify notation, for $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
+\begin{equation*}
+\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
+\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
+\end{equation*}
+and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
+
+\begin{proposition}[Lower bound on graph conductance]
+	\label{prop: graph_conductance_profile_lb}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, with probability $1$ the following lower bound holds on the graph conductance:
+	\begin{equation*}
+	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
+	\end{equation*}
+\end{proposition}
+
+In order to prove Proposition \ref{prop: graph_conductance_profile_lb}, we will need to split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
+For any graph $G = (V,E)$, let $\mathcal{L}(G) = \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G$.)
+
+In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut of all sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
+
+\begin{lemma}
+	\label{lem: graph_conductance_profile_lb}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then with probability $1$,
+	\begin{equation*}
+	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
+	\end{equation*}
+	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
+\end{lemma}
+
+The proof of Lemma \ref{lem: graph_conductance_profile_lb} is nontrivial, and we devote the following subsection to it.
+
+Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
+\begin{lemma}
+	\label{lem: graph_conductance_profile_lb_1}
+	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
+	\begin{equation*}
+	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	The claim follows by simple manipulations:
+	\begin{align*}
+	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
+	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
+	\end{align*}
+\end{proof}
+
+Proposition \ref{prop: graph_conductance_profile_lb} follows in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
+
+In Lemma \ref{lem: local_spread_lb}, we lower bound the local spread $s(\widetilde{G}_{n,r})$.
+
+\begin{lemma}
+	\label{lem: local_spread_lb}
+	With probability one, the following bound holds:
+	\begin{equation*}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
+Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
+	\begin{equation*}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
+	\end{equation*}
+\end{proof}
+
+\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+\label{sec: proof_of_lemma_graph_conductance}
+
+For $\Sset \subseteq \Csig$ measurable, define the conditional probability measures
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
+\end{equation*} 
+A Borel map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
+\begin{equation*}
+\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
+\end{equation*}
+where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
+
+If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
+Proposition 5 of \cite{garciatrillos16} establishes that, for open connected domains with Lipschitz boundaries, such stagnating transportation maps exist.
+In particular, as $\Csig[\Xbf]$ consists of $\widetilde{n} := \abs{\Csig[\Xbf]}$ points sampled independently from $\widetilde{\Pbb}$, and $\Csig$ is a connected domain with Lipschitz boundary, the following implication is immediate.
+
+\begin{lemma}
+	\label{lem: stagnating_transportation_maps}
+	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
+	\begin{equation}
+	\label{eqn: stagnating_transportation_maps}
+	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
+	\end{equation}
+	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
+\end{lemma}
+
+%%% AJG 5/9/19: Need to strengthen this?
+
+Note that although $\Csig$ is closed not open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and \eqref{eqn: stagnating_transportation_maps} will hold for any arbitrary extension of $T_n$ to $\Csig$.
+
+\paragraph{Graph cuts to continuous cuts.}
+
+We use stagnating transportation maps to relate discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
+We fix some notation, letting $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$ for a transportation map $T_n$.
+
+Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
+
+\begin{lemma}
+	\label{lem: volume_bound}
+	Let $S \subseteq \Csig[\Xbf]$ and $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset := T_n^{-1}(S)$,
+	\begin{equation*}
+	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{2 \Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$, meaning
+	\begin{equation*}
+	\varphi(x) = 
+	\begin{cases}
+	1,~ x \in S \\
+	0,~ \text{otherwise}
+	\end{cases}
+	\end{equation*}
+
+	Now, we proceed
+	\begin{align}
+	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
+	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
+	& = \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \tag{change of variables} \nonumber \\
+	& \leq \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
+	& = \frac{1}{2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
+	\end{align}
+
+	By definition we have $\frac{d\Pbb(x)}{d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
+	\begin{align*}
+	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
+	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) \dx \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset)
+	\end{align*}
+	and we have the desired upper bound.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: cut_bound}
+	Let $S \subseteq \Csig[\Xbf]$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = T_n^{-1}(S)$,
+	\begin{equation*}
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{2 \Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	As in the proof of Lemma \ref{lem: volume_bound}, let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$.
+
+	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
+	\begin{align*}
+	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
+	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
+	& =  \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& \geq \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
+	& = \frac{1}{2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
+	\end{align*}
+	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
+	\begin{align*}
+	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r_n^-)\bigr)}{\ell_{\Pbb,r_n^-}(x)} d\piwt_{\Pbb,r}(x) \\
+	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
+	\end{align*}	
+\end{proof}
+
+Putting Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} together yields the following result, a lower bound on graph normalized cut.
+
+\begin{lemma}
+	\label{lem: graph_to_continuous_conductance}
+	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and fix $S \subseteq \Csig[\Xbf]$. Then, letting $\Sset =T_n^{-1}(S)$,
+	\begin{equation}
+	\label{eqn: graph_to_continuous_conductance}
+	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}  \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
+	\end{equation}
+\end{lemma}
+
+\begin{proof}
+
+	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset)}.
+	\end{equation*}
+
+	Then, noting that $\Sset^c = T_n^{-1}(S^c)$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
+	\begin{equation*}
+	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\piwt_{\Pbb,r_n^+}(\Sset^c)}
+	\end{equation*}
+	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
+	\begin{equation*}
+	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} },
+	\end{equation*}
+	and the proof is complete.
+\end{proof}
+
+\paragraph{Perturbation analysis.}
+
+If $r_n^- = r = r_n^+$, \eqref{eqn: graph_to_continuous_conductance} would simplify to $\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)$.
+We show that this conclusion is robust to asymptotically negligible perturbations of $r$.
+
+\begin{lemma}[Continuity of local conductance]
+	\label{lem: cont_local_conductance}
+	For $\seq{T_n}$ a sequence of stagnating transportation maps,
+	\begin{equation*}
+	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Letting $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
+	\begin{equation*}
+	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx + \int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx.
+	\end{equation*}
+	and therefore
+	\begin{equation*}
+	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}.
+	\end{equation*}
+	We upper bound the remainder term
+	\begin{equation*}
+	\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl((r_n^+)^d - r^d) \to 0
+	\end{equation*}
+	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	We apply a similar analysis to the denominator. By Lemma \ref{lem: local_conductance}
+	\begin{equation*}
+	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) \dy \dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d \to \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
+	\end{equation*}
+	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	Then the desired result follows from an application of Slutsky's Theorem.
+\end{proof}
+
+\begin{lemma}[Continuity of stationary distribution]
+	\label{lem: cont_stationary_dist}
+	Let $c > 0$ be any fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } = 1
+	\end{equation*}
+	uniformly over all measurable sets $\Sset \subseteq \Csig$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
+\end{lemma}
+\begin{proof}
+	It will be sufficient to show that
+	\begin{equation*}
+	\liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} \quad \text{and}  \quad \liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset^c)} = 1,
+	\end{equation*}
+	and we will show only the former, the proof of the latter being identical.
+
+	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
+	\begin{equation*}
+	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
+	\end{equation*}
+	we may rewrite
+	\begin{equation*}
+	\frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\piwt_{\Pbb,r_n^+}(\Sset)}.
+	\end{equation*}
+
+	By the stagnating property of $T_n$,
+	\begin{equation*}
+	\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
+	\end{equation*}
+	where the convergence occurs uniformly over all $\Sset$ as $n \to \infty$. On the other hand, by hypothesis
+	\begin{equation*}
+	\liminf_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
+	\end{equation*}
+	and the result follows by Slutsky's Theorem. 
+\end{proof}
+
+\begin{lemma}[Stationary distribution lower bound]
+	\label{lem: stationary_dist_lb}
+	Let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$. Then with probability one,
+	\begin{equation*}
+	\liminf_{n \to \infty} \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \piwt_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary, writing $\Sset := T_n^{-1}(S)$.
+Letting $\mathcal{R}_n(x)$ be as in the proof of Lemma \ref{lem: cont_stationary_dist}, we have
+	\begin{align}
+	\widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}. \label{eqn: stationary_dist_lb_1}
+	\end{align}
+	Clearly $\piwt_{\Pbb,r_n^-}(\Sset) \leq \piwt_{\Pbb,r}(\Sset)$. Moreover
+	\begin{equation*}
+	\frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
+	\end{equation*}
+	which along with \eqref{eqn: stationary_dist_lb_1} implies
+	\begin{equation*}
+	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d \to \piwt_{\Pbb,r}(\Sset).
+	\end{equation*}
+	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is uniform over $\Sset$ as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
+
+	By Lemma \ref{lem: local_spread_lb}, with probability one as $n \to \infty$,
+	\begin{equation*}
+	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
+	\end{equation*}
+	and the claim is shown.
+\end{proof}
+
+\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+
+By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
+
+Let $S \subseteq \Csig[\Xbf]$ be arbitrary, and define
+\begin{equation*}
+\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx},~ \gamma_n(S) := \frac{\min \set{\piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
+\end{equation*}
+where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
+By Proposition \ref{prop: nonuniform_continuous_conductance} and Lemma \ref{lem: graph_to_continuous_conductance} we have that
+\begin{align}
+\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
+& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
+\end{align}
+
+By Lemma \ref{lem: cont_local_conductance}, with probability one
+\begin{equation*}
+\liminf_{n \to \infty} \xi_n = 1.
+\end{equation*}
+
+By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $0 < c < \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}$, with probability one there exists some $m \in \mathbb{N}$ such that for all $n \geq m$,
+\begin{equation*}
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})}\piwt_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
+\end{equation*}
+and therefore by Lemma \ref{lem: cont_stationary_dist}
+\begin{equation*}
+\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
+\end{equation*}
+
+As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
+
+\subsection{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
+\label{sec: proof_of_theorem_mixing_time}
+
+Since $r$ is fixed, $\degminwt \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
+\begin{equation}
+\label{eqn: tau_ub}
+\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2}{\widetilde{\Phi}_{n,r}^2} \log\left(\frac{1440}{s(\widetilde{G}_{n,r})}\right) \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
+\end{equation}
+and the claim follows from Proposition \ref{prop: graph_conductance_profile_lb} and Lemma \ref{lem: local_spread_lb}.
+In the statement of Theorem \ref{thm: mixing_time_upper_bound} we omit the factor of $3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right)$ as the first and third terms in \eqref{eqn: tau_ub} dominate.
+
+\subsection{Concentration inequalities}
+\label{sec: concentration}
+
+Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$ statistic} to be
+\begin{equation*}
+U := \frac{1}{ {n \choose 2} } \sum_{1 \leq i < j \leq n} K(x_i,x_j).
+\end{equation*}
+
+\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
+	\label{lem: bounded_difference}
+	For any $t > 0$,
+	\begin{equation*}
+	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{-nt^2\right\}
+	\end{equation*}
+	Further, for any $\delta > 0$, we have
+	\begin{align*}
+	U & \leq \mathbb{E}U + \sqrt{\frac{\log(1 / \delta)}{n} }, \\
+	U & \geq \mathbb{E}U - \sqrt{\frac{\log(1 / \delta)}{n} }
+	\end{align*}
+	each with probability at least $1 - \delta$. 
+\end{lemma}
+
+We will employ a sharper inequality to bound the sum of independent Bernoulli random variables.
+\begin{lemma}
+	\label{lem: multiplicative_Hoeffding}
+	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \sum_{i = 1}^n \Ebb(X_i)$. Then,
+	\begin{align*}
+	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
+	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
+	\end{align*}
+\end{lemma}
+
+We will require large-sample and asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}.
+Let
+\begin{alignat*}{2}
+\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ && \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
+\degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
+\degmin & := \min_{u \in \Xbf} \deg(u; G_{n,r}).
+\end{alignat*}
+
+\begin{lemma}
+	\label{lem: ball_bounds_in_probability}
+	Under the geometric conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
+	\begin{align}
+	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
+	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
+	\frac{\abs{\Csig[\Xbf]}}{n} & \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}\\
+	\label{eqn: volwt_bound}
+	\frac{1}{2}\vol_0 \leq \vol_{n,r}(\Csig[\Xbf]) & \leq \frac{3}{2} \vol_0
+	\end{align}
+
+	Additionally, with probability one,
+	\begin{align}
+	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
+	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d \label{eqn: max_vol_bound_asymp}
+	\end{align}
+
+	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
+	\begin{equation}
+	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
+	\end{equation}
+
+	If additionally \ref{asmp: C'_bounded_density} holds (but not necessarily \ref{asmp: valid_region}): for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
+	\begin{equation}
+	\label{eqn: min_cluster_degree_bound_2}
+	\frac{\degminpr}{n} \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
+	\begin{equation*}
+	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
+	\end{equation*}
+	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
+	\begin{equation*}
+	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
+	\end{equation*}
+	and we have shown \eqref{eqn: min_cluster_degree_bound}.
+Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
+\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
+
+	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
+
+	Finally, note that
+	\begin{equation*}
+	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
+	\end{equation*}
+	can be rewritten as a U-statistic, and furthermore
+	\begin{equation*}
+	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
+	\end{equation*}
+
+	Therefore by Lemma \ref{lem: bounded_difference}
+	\begin{equation}
+	\label{eqn: ball_bounds_in_probability_1}
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
+	\end{equation}
+	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
+Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
+	\begin{equation*}
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
+	\end{equation*}
+
+	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
+	\begin{equation*}
+	\Pbb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} \geq (1 + \epsilon)\mu \right) \leq \exp(-n\epsilon^2\mu).
+	\end{equation*}
+	The two asymptotic statements \eqref{eqn: min_cluster_degree_bound_asymp} and \eqref{eqn: max_vol_bound_asymp} therefore both follow from the Borel-Cantelli Lemma.
+\end{proof}
+
+Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+	\begin{enumerate}
+		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
+\end{corollary}
+
+\subsection{Proof of Theorem \ref{thm: misclassification_rate}}
+\label{sec: proof_of_misclassification_rate}
+
+In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
+
+Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
+It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
+\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+
+\begin{lemma}
+	\label{lem: zhu}
+	Let $\epsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
+Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
+	\begin{equation*}
+	S_{\beta} := \left\{u \in V: \pbf^{(\epsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
+	\end{equation*}
+
+	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \epsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
+	\begin{align}
+	\vol(S_{\beta} \setminus S; G) & \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(S; G), \label{eqn: zhu_1}\\
+	\vol(S \setminus S_{\beta}; G) & \leq \left(\frac{2\Phi(S;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(S;G)\right)\vol(S; G).  \label{eqn: zhu_2}
+	\end{align}
+\end{lemma}
+
+\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
+
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
+Moreover,
+\begin{enumerate}[(i)]
+	\item we restrict $v \in \Csig[\Xbf]^g$
+	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$
+	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
+	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$.
+\end{enumerate}
+
+All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq 1/10\tau_u(\theta)$, the following bounds hold with probability tending to 1 as $n \to \infty$:
+\begin{equation*}
+\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
+\end{equation*}
+Noting that
+\begin{align*}
+\abs{\widehat{C} \setminus \Csig[\Xbf]} & \leq \frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\degmin}   \\
+\abs{\Csig[\Xbf] \setminus \widehat{C}} & \leq \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\degminwt}, \quad \textrm{and} \\
+\abs{\Csig[\Xbf]} & \geq \frac{\vol_{n,r}(\Csig[\Xbf])}{\degmax}
+\end{align*}
+the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
+
+\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
+
+The choice $\epsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\epsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\epsilon)}$.
+All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
+
+\subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
+\label{sec: proof_of_consistent_cluster_recovery}
+
+We begin with some notation.
+Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
+Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
+\begin{equation*}
+\overline{\pibf}_{n,r}(x) := \frac{\widetilde{\deg}_{n,r}(x)}{\vol_{n,r}(\Csig[\Xbf])}.
+\end{equation*}
+(Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
+
+Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(x) - \overline{\pibf}_{n,r}(x)$.
+
+\begin{lemma} 
+	\label{lem: setup}
+	Let $0 < r < \sigma$ and $\alpha \leq \frac{1}{9 \tau_{\infty}(\widetilde{G}_{n,r})}$.
+Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
+	\begin{itemize}
+		\item For each $u \in \Cset[\Xbf]$,
+		\begin{equation}
+		\label{eqn: lower_bound_PPR_in_cluster}
+		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminwt}
+		\end{equation}
+		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy the cluster separation condition \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
+		\begin{equation}
+		\label{eqn: upper_bound_PPR_in_other_cluster}
+		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminpr}.
+		\end{equation}
+	\end{itemize}
+\end{lemma}
+
+\begin{proof}
+	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. Given starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
+	\begin{equation}
+	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}
+	\end{equation}
+	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
+(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
+
+	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
+	\begin{align}
+	\label{eqn: leakage_soakage}
+	\ell_t & := e_v (\Wbf \widetilde{I} )^t (I - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
+	s_t & := e_v (\Wbf \widetilde{I} )^t (\Wbf \widetilde{I}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
+	\end{align}
+	where $I$ is the $n \times n$ identity matrix, $\widetilde{I}$ is an $n \times n$ diagonal matrix with $\widetilde{I}_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{I}^c = I - \widetilde{I}$.
+
+	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $\Csig[\Xbf]$ on the $t + 1$th step.
+For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$.
+By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is ``soaked up'' into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
+The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
+
+	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation.
+By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
+	\begin{equation}
+	\label{eqn: zhulemma3.1}
+	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
+	\end{equation}
+	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)
+
+	If additionally $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
+	\begin{equation*}
+	\widetilde{\pbf}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
+	\end{equation*}
+	and along with \eqref{eqn: zhulemma3.1}, we obtain
+	\begin{equation*}
+	\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
+	\end{equation*}
+
+	We proceed to show the upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \degminwt$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
+We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$.
+	\begin{enumerate}
+		\item Since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
+		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$ and $u \not\in \mathrm{supp}(q)$, and any $t \geq 1$,
+		\begin{align}
+		\label{eqn: one_step_bound}
+		q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 \max_{v \neq u} W_{vu} \nonumber \\
+		& \leq \frac{1}{2\degminwt} 
+		\end{align}
+		where last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
+	\end{enumerate}
+
+	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
+	\begin{align*}
+	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}^t \right)(u)  \nonumber \\
+	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
+	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
+	& \leq \frac{\norm{\ell}_1 }{\degminwt}. \tag{since $u \not\in \mathrm{supp}(\ell)$}
+	\end{align*}
+	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.
+
+	We turn to showing \eqref{eqn: upper_bound_PPR_in_other_cluster}. By Lemma \ref{lem: soakage_ppr_lb}, for all $u' \not\in \Csig[\Xbf]$,
+	\begin{equation*}
+	\pbf_v(u') \leq \pbf_s(u').
+	\end{equation*}
+
+	Note that by \ref{asmp: cluster_separation}, for every $u \in \Csig[\Xbf], (u',u) \not\in E$ and therefore $s(u') = 0$.
+Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
+	\begin{align*}
+	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
+	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
+	& \leq \frac{\norm{s}_1}{2\degminpr}
+	\end{align*}
+	where the last inequality follows from precisely the same reasoning as \eqref{eqn: one_step_bound}.
+The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
+\end{proof}
+
+We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+
+\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
+~
+
+In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
+
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
+As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
+\begin{align}
+\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
+\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
+\end{align}
+We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
+\begin{align}
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
+\end{align}
+
+The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\epsilon = \frac{1}{47}$} \\
+& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+Similarly, for each $u' \in \Cset'[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
+& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
+& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
+
+It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$ to obtain
+\begin{equation}
+\label{eqn: pimin_Dmin_lb}
+\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
+\end{equation}
+
+Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
+\begin{equation}
+\label{eqn: difficulty_bound}
+\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
+\end{equation}
+\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
+
+\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
+
+Using \eqref{eqn: appr_error} with $\epsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
+\begin{equation*}
+\pbf^{(\epsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
+\end{equation*}
+and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
+\begin{equation*}
+\frac{\pbf^{(\epsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
+\end{equation*}
+
+On the other hand $\pbf^{(\epsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\epsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+
+\subsection{Linear Algebra Facts}
+\label{sec: linalg}
+
+We state here a number of basic facts which follow from matrix manipulations, which are used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+
+\begin{lemma}
+	\label{lem: soakage_ppr_lb}
+	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
+	\begin{equation*}
+	\pbf_{v}(u) \leq \pbf_{s}(u)
+	\end{equation*}
+	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
+\end{lemma}
+\begin{proof}
+	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
+	\begin{align*}
+	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
+	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
+	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
+	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
+	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
+	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
+	& = \pbf_s(u)
+	\end{align*}
+\end{proof}
+
+Let $s_t := q(\Wbf \Ibf{S})^t(\Wbf(\Ibf{S^c}))$ be the soakage vector out of $S \subseteq V$, where $\Ibf{S}$ is a $\abs{V} \times \abs{V}$ diagonal matrix with $(\Ibf{S})_{uu} = 1$ if $u \in S$ and 0 otherwise, and $\Ibf{S^c} := \Ibf{} - \Ibf{S}$.
+\begin{lemma}
+	\label{lem: sum_of_soakages}
+	Let $G = (V,E)$ be an unweighted, undirected graph with associated random walk matrix $\Wbf$. For any $T \in \mathbb{N}, T \geq 1$, $q \in \Reals^{\abs{V}}$, and $S \subseteq V$
+	\begin{equation}
+	\label{eqn: sum_of_soakages}
+	q\Wbf^T = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} + q(\Wbf \Ibf{S})^T
+	\end{equation}
+	In particular, if $u \in V\setminus S$, then
+	\begin{equation}
+	\label{eqn: sum_of_soakages_2}
+	q\Wbf^T(u) = \sum_{t = 0}^{T - 1} \left(s_t \Wbf^{T - t - 1}\right)(u)
+	\end{equation}
+\end{lemma}
+\begin{proof}	
+	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.
+
+	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,
+	\begin{equation*}
+	q\Wbf = q\Wbf\Ibf{S} + q\Wbf\Ibf{S^c} =  q\Wbf\Ibf{S} + s_0. 
+	\end{equation*}
+
+	Then, for $T \in \mathbb{N},~ T \geq 2$,
+	\begin{align*}
+	q\Wbf^{T} & = q\Wbf^{T - 1}{\Wbf} \\
+	& = \left\{\sum_{t = 0}^{T - 2} s_t \Wbf^{T - 2 - t} + q(\Wbf \Ibf{S})^{T - 1} \right\} \Wbf \tag{by the inductive hypothesis}\\
+	& = \sum_{t = 0}^{T - 2} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S} + \Wbf \Ibf{S^c}) \\
+	& = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S})
+	\end{align*}
+	and the proof is complete.
+\end{proof}
+
+\begin{lemma}
+	\label{lem: total_leakage_equal_total_soakage}
+	Letting $s_t$, $\ell_t$ $s$ and $\ell$ be as in \eqref{eqn: leakage_soakage},
+	\begin{equation*}
+	\norm{s_t}_1 = \norm{\ell_t}_1,~ \textrm{for each $t \geq 0$}
+	\end{equation*}
+	and therefore $\norm{s}_1 = \norm{\ell}_1$. 
+\end{lemma}
+\begin{proof}
+	By the definition of $s_t$ and $\ell_t$, we have
+	\begin{align*}
+	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{I}^c)}_1 \\
+	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{I}^c)(u, u') \\
+	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf)_{uu}} \1((u,u') \in G_{n,r}) \\
+	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf)_{uu} - (\widetilde{\Dbf})_{uu} \right)}{(\Dbf)_{uu}} \\
+	& = \norm{q_t (\Ibf{} - \Dbf^{-1} \widetilde{\Dbf})}_1 = \norm{\ell_t}_1.
+	\end{align*}
+\end{proof}
+
+\section{Experiments}
+\label{sec: experimental_setting}
+
+In Section \ref{sec: experimental_setting}, we detail the experimental settings of Section \ref{sec: experiments} in the main text, and include an additional figure.
+
+\subsection{Experimental settings for Figure \ref{fig:fig1}}
+We sample points according to the density function $q$, where for $x \in \Rd$
+\begin{equation}
+q(x) :=
+\begin{cases}
+\lambda,~ & x \in [0,\sigma] \times \rho^{d-1} =: \Cset, \\
+\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
+(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
+0,~ & \textrm{otherwise},
+\end{cases}
+\end{equation}
+where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
+
+In the top-left and top-middle, we show draws of $n = 20000$ samples from two different density functions.
+In the top-left panel, $\sigma = \rho = 3.2$, while in the top-middle panel $\sigma = .1$ and $\rho = 3.2$.
+(For both, $d = 2$).
+
+The remaining four panels (top-right and the bottom row) in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
+In the top-right and bottom-left panels $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $\rho$ is fixed at $3.2$.
+In the bottom-middle and bottom-right panels, $\rho = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
+For each panel, the solid lines show, up to constants, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for the top-right and bottom-left panels and Theorem \ref{thm: mixing_time_upper_bound} for the bottom-middle and bottom-right panels.
+The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in the top-right and bottom-left panels, and $m = 20$ for the mixing time, dashed lines in the bottom-middle and bottom-right panels).
+For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
+Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
+
+\subsection{Experimental settings for Figure \ref{fig:fig2}}
+
+To form each of the three rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+Formally, the (respective) generative models for the data are
+\begin{align}
+Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
+X(Z,\theta) & = 
+\begin{cases}
+\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
+\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
+\end{cases}
+\end{align}
+
+where 
+\begin{align*}
+\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
+\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
+\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} 
+\end{align*}
+for $I_d$ the $d \times d$ identity matrix.
+The first column consists of the empirical density clusters $C[\Xbf]$ and $C'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+
+\subsection{Performance of \pprspace with high-dimensional noise.}
+
+Figure \ref{fig:fig3} is similar to Figure \ref{fig:fig2} of the main text, with parameters
+\begin{equation*}
+\mu_1 = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}).
+\end{equation*}
+The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:fig2} in the main text) represent observations in low-density regions.
+While the \pprspace sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C[\Xbf]$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\caption{}
+		\label{fig:fig3}
+	\end{adjustbox}
+\end{figure}
+
 \bibliographystyle{plainnat}

### 2019-06-04 neurips/local_spectral_density_clustering_arxiv.tex
format changes

@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-%     \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-     \usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-%     \usepackage[final]{neurips_2019}
-
-%\PassOptionsToPackage{numbers}{natbib}
-\usepackage{neurips_2019}
-
-% to avoid loading the natbib package, add option nonatbib:
-%     \usepackage[nonatbib]{neurips_2019}
+\documentclass[11pt,twoside]{article}
+\usepackage{fancyhdr}
+\usepackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue,bookmarks=false]{hyperref}
+\usepackage{amsfonts,epsfig,graphicx}
+\usepackage{afterpage}
+\usepackage{amsmath,amssymb,amsthm} 
+\usepackage{fullpage}
+\usepackage[T1]{fontenc} 
+\usepackage{epsf} 
+\usepackage{graphics} 
+\usepackage{amsfonts,amsmath}
+\usepackage[sort,numbers]{natbib} 
+\usepackage{psfrag,xspace}
+\usepackage{color,etoolbox}
+
+\setlength{\textwidth}{\paperwidth}
+\addtolength{\textwidth}{-6cm}
+\setlength{\textheight}{\paperheight}
+\addtolength{\textheight}{-4cm}
+\addtolength{\textheight}{-1.1\headheight}
+\addtolength{\textheight}{-\headsep}
+\addtolength{\textheight}{-\footskip}
+\setlength{\oddsidemargin}{0.5cm}
+\setlength{\evensidemargin}{0.5cm}
+
+\newtheorem{theorem}{Theorem} 
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{definition}{Definition}
+\newtheorem*{remark}{Remark}
 
@@
 \usepackage{xcolor}
-\usepackage{xr-hyper}
-\usepackage{hyperref}
-\usepackage[reqno]{amsmath}
-\usepackage{amsfonts, amsthm, amssymb}
+%\usepackage{xr-hyper}
+%\usepackage{hyperref}
+%\usepackage[reqno]{amsmath}
+%\usepackage{amsfonts, amsthm, amssymb}
 \usepackage{algorithm}
 \usepackage{algorithmic}
-\usepackage[parfill]{parskip}
+%\usepackage[parfill]{parskip}
 \usepackage{enumerate}
@@
 
-\newtheoremstyle{aldenthm}
-{6pt} % Space above
-{6pt} % Space below
-{\itshape} % Body font
-{} % Indent amount
-{\bfseries} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{aldenthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-
-\newtheoremstyle{aldenrmrk}
-{6pt} % Space above
-{6pt} % Space below
-{} % Body font
-{} % Indent amount
-{\itshape} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{aldenrmrk}
-\newtheorem{remark}{Remark}
+%\newtheoremstyle{aldenthm}
+%{6pt} % Space above
+%{6pt} % Space below
+%{\itshape} % Body font
+%{} % Indent amount
+%{\bfseries} % Theorem head font
+%{.} % Punctuation after theorem head
+%{.5em} % Space after theorem head
+%{} % Theorem head spec (can be left empty, meaning `normal')
+
+%\theoremstyle{aldenthm}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{definition}{Definition}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{corollary}{Corollary}
+
+%\newtheoremstyle{aldenrmrk}
+%{6pt} % Space above
+%{6pt} % Space below
+%{} % Body font
+%{} % Indent amount
+%{\itshape} % Theorem head font
+%{.} % Punctuation after theorem head
+%{.5em} % Space after theorem head
+%{} % Theorem head spec (can be left empty, meaning `normal')
+%
+%\theoremstyle{aldenrmrk}
+%\newtheorem{remark}{Remark}
 %%%%%% End Alden
 
-\title{Local Spectral Clustering of Density Upper Level Sets}
+%\title{Local Spectral Clustering of Density Upper Level Sets}
 
@@
 % \AND instead of \And before the third author name.
-
-\author{
-Alden Green \And
-Sivaraman Balakrishnan \And
-Ryan J. Tibshirani}
+%
+%\author{
+%Alden Green \And
+%Sivaraman Balakrishnan \And
+%Ryan J. Tibshirani}
+%
+%\begin{document}
+%\maketitle
+%
+%\vspace{0.1in}
+%\begin{abstract}
+
+\newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
+\newcommand{\Like}{\ensuremath{\mathcal{L}}}
+\newcommand{\Ball}[2]{\mathbb{B}_{#1}(#2)}
+\newcommand{\Complement}[1]{\overline{#1}}
+
+\newcommand{\xsam}{\ensuremath{x}}
+\newcommand{\samind}{\ensuremath{\ell}}
+\newcommand{\Xrv}{\ensuremath{X}}
+\newcommand{\Event}{\ensuremath{\mathcal{E}}}
+\newcommand{\Fevent}{\ensuremath{\mathcal{F}}}
+
+\newcommand{\usedim}{\ensuremath{d}}
+\newcommand{\mubold}{\ensuremath{\boldsymbol{\mu}}}
+\newcommand{\lambold}{\ensuremath{\boldsymbol{\lambda}}}
+\newcommand{\sep}{\ensuremath{\xi}}
+\newcommand{\mixind}{\ensuremath{i}}
+\newcommand{\mixtwo}{\ensuremath{j}}
+\newcommand{\nummix}{\ensuremath{M}}
+\newcommand{\mustar}{\ensuremath{\mu^*}}
+\newcommand{\muboldstar}{\ensuremath{\mubold^*}}
+\newcommand{\muboldt}{\ensuremath{\mubold^t}}
+
+\newcommand{\numobs}{\ensuremath{n}}
+\newcommand{\SamLike}{\ensuremath{\Like_\numobs}}
+\newcommand{\PopLike}{\ensuremath{\Like}}
+\newcommand{\Exs}{\E}
+\newcommand{\thetanew}{\ensuremath{\theta^{\text{\small{new}} }}}
+
+\newcommand{\stepsize}{\ensuremath{s}}
+
+\newcommand{\QMAT}{\ensuremath{\mathbf{Q}}} 
+\newcommand{\DMAT}{\ensuremath{\mathbf{D}}}
+
+\newcommand{\defn}{\ensuremath{: \, =}}
+\newcommand{\muboldtilde}{\ensuremath{\tilde{\mubold}}}
+
+%%% New version of \caption puts things in smaller type, single-spaced 
+%%% and indents them to set them off more from the text.
+\makeatletter
+\long\def\@makecaption#1#2{
+        \vskip 0.8ex
+        \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
+        \parindent 1.5em  %% How can we use the global value of this???
+        \dimen0=\hsize
+        \advance\dimen0 by -3em
+        \ifdim \wd\@tempboxa >\dimen0
+                \hbox to \hsize{
+                        \parindent 0em
+                        \hfil 
+                        \parbox{\dimen0}{\def\baselinestretch{0.96}\small
+                                {\bf #1.} #2
+                                %%\unhbox\@tempboxa
+                                } 
+                        \hfil}
+        \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
+        \fi
+        }
+\makeatother
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-\maketitle
-
-\vspace{0.1in}
+
+\begin{center} {\Large{\bf{Local Spectral Clustering of Density Upper Level Sets}}}
+
+\vspace*{.3cm}
+
+{\large{
+\begin{center}
+Alden Green ~~~~~ Sivaraman Balakrishnan~~~~~ Ryan Tibshirani\\
+\vspace{.2cm}
+\end{center}
+
+\begin{tabular}{c}
+Department of Statistics and Data Science \\
+Carnegie Mellon University
+\end{tabular}
+
+\vspace*{.2in}
+
+\begin{tabular}{c}
+\texttt{\{ajgreen,sbalakri,ryantibs\}@andrew.cmu.edu}
+\end{tabular}
+}}
+
+\vspace*{.2in}
+
+\today
+\vspace*{.2in}
+
 \begin{abstract}
-We analyze Personalized PageRank (PPR), a local spectral method for clustering,
-which extract clusters using locally-biased random walks around a user-specified
-seed node.  In constrast to previous work, we adopt a traditional statistical
+\noindent We analyze Personalized PageRank (PPR), a local spectral method for clustering,
+which extracts clusters using locally-biased random walks around a user-specified
+seed node.  In contrast to previous work, we adopt a traditional statistical
 learning setup, where we obtain samples from an unknown distribution, and aim to
@@
 \end{abstract}
-
+\end{center}
 \section{Introduction}
@@
 
-\clearpage
+\section{Acknowledgements}
+SB is grateful to Peter Bickel, Martin Wainwright and Larry Wasserman for helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+
 \appendix
 
-In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
+%In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
 
@@
 	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{equation}
-	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
-	\end{equation}
+	\begin{align}
+	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
+	\end{align}
 

### 2019-06-16 neurips/local_spectral_density_clustering_arxiv.tex
just a checkpoint for me

@@
 \newcommand{\piwt}{\widetilde{\pi}}
+
+\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
 
@@
 In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
-The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
-\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
+Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
 
@@
 
-Lemma \ref{lem: expansion_volume} allows us to reason about the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
+Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
 
@@
 	\begin{equation*}
-	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
-	\end{equation*}
-	Observe that $\bigcup_{i = 1}^{N} \Asig^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$.
+	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
+	\end{equation*}
+	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$.
 As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
 	\begin{align*}
-	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
-	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
+	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
 	\end{align*}
@@
 	\begin{equation*}
-	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
-	\end{equation*}
-
-	As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
-	\begin{equation*}
-	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
-	\end{equation*}
-	and therefore
-	\begin{align*}
-	\nu(\Aset + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
-	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
-	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
+	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
+	\end{equation*}
+As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
+	\begin{equation*}
+	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
+	\end{equation*}
+	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
+	\begin{align*}
+	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
+	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
+	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
 	\end{align*}
@@
 \end{proof}
-
-We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
-
-\begin{lemma}
-	\label{lem: covering}
-	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Lemma \ref{lem: expansion_volume},
-	\begin{equation*}
-	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
+\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
+\begin{lemma}
+	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
+	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
+	\begin{equation*}
+	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
 	\end{equation*}
@@
 	\begin{equation*}
-	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
+	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
 	\end{equation*}
@@
 	\begin{equation*}
-	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{(i)}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{(i)}).
-	\end{equation*}
-
-	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
+	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
+	\end{equation*}
+
+	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
 	\begin{equation}
@@
 	\end{equation*}
-	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
+	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
 \end{proof}
 
-We will need to carefully control the volume of expansion sets using the estimate in Lemma \ref{lem: expansion_volume}; Lemma \ref{lem: Taylor_series} serves this purpose.
+We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
 \begin{lemma}
@@
 	\end{align*}
-
 The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
@@
 	\end{align}
-	\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
+	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
 	\begin{align}
 	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-	& \overset{(i)}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
+	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
 	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
 	\end{align}
-	where $(i)$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
+	where $\text{(i)}$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
 
@@
 	\begin{align}
-	\xi & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
+	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
+	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
 \label{eqn: xi_ub}
 	\end{align}
-	where $(ii)$ follows from \eqref{eqn: slice_volume_bound}, and $(iii)$ from Lemma \ref{lem: Taylor_series}.
+	where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}.
 As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
@@
 	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
-	& \overset{(iv)}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
+	& \overset{\text{(iv)}}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
 	& =  3\alpha^{1/2}.
 	\end{align*}
-	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
+	where $\text{(iv)}$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
 \end{proof}
@@
 	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
-	& \overset{(i)}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
+	& \overset{\text{(i)}}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
 	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
 	\end{align}
-	where $(i)$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.
+	where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.
 
@@
 	\begin{equation*}
-	\nu(I) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	\nu\text{(i)} = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
 	\end{equation*}
@@
 	\begin{align*}
-	\nu(I) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{(i)}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
-	& \overset{(ii)}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
-	\end{align*}
-	where $(i)$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $(ii)$ from Lemma \ref{lem: beta_function}.
+	\nu\text{(i)} & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
+	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
+	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
+	\end{align*}
+	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
 \end{proof}
@@
 	\begin{align}
-	\nu(\Csig \cap I)  & = \nu(I) - \nu(I \setminus \Csig) \nonumber \\
-	& \geq \nu(I) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
+	\nu(\Csig \cap I)  & = \nu\text{(i)} - \nu(I \setminus \Csig) \nonumber \\
+	& \geq \nu\text{(i)} - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
 	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
@@
 Moreover,
-\begin{enumerate}[(i)]
+\begin{enumerate}[\text{(i)}]
 	\item we restrict $v \in \Csig[\Xbf]^g$

### 2019-06-16 neurips/local_spectral_density_clustering_arxiv.tex
on the verge of a more significant re-org

@@
 %In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
+\section{Proof of Theorem~\ref{}}
 
@@
 	\end{equation*}
-	where $t_i = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
+	\sbcomment{Changed $t_i$ to $t_{i,k}$.}
+	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
 	\begin{equation}
@@
 	\end{equation}
-
-	\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
+	Assumptions~\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
 	\begin{equation*}
@@
 	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
-	& = \sum_{i = 1}^{k} 
-	\underbrace{\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
+	& = \underbrace{\sum_{i = 1}^{k} 
+	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
 	\end{align}
-	where the second equality comes from rearranging terms in the sum.
+	\sbcomment{I changed the braces above -- I think they were incorrect earlier} where the second equality comes from rearranging terms in the sum.
 
@@
 	We first consider the term $\Sigma_k$.
-$\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
+$\Cset$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
 Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
@@
 	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (u_{i,k} = t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
+	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
 	\end{align}
@@
 \end{proof}
-
+\sbcomment{Here now.}
 Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be

### 2019-06-17 neurips/local_spectral_density_clustering_arxiv.tex
re-org of Theorem 3

@@
 
+\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
+changed this $\epsilon$ to $\varepsilon$.} 
 \paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
   ppr_vector} may be too computationally expensive. To address this limitation,
-\citet{andersen2006} introduced the \emph{$\epsilon$-approximate} PPR vector
-(aPPR), which we will denote by \smash{$\pbf^{(\epsilon)}$}. We refer the
+\citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
+(aPPR), which we will denote by \smash{$\pbf^{(\varepsilon)}$}. We refer the
 curious reader to \citet{andersen2006} for a formal algorithmic definition of
 the aPPR vector, and limit ourselves to highlighting a few salient points: the
-aPPR vector can be computed in order $\mathcal{O}(1/(\epsilon\alpha))$ time,
+aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time,
 while satisfying the following uniform error bound: 
@@
 \label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq
-\pbf^{(\epsilon)}(u) \leq \pbf(u).  
+\textrm{for all $u \in V$}, \quad \pbf(u) - \varepsilon \Dbf_{uu}\leq
+\pbf^{(\varepsilon)}(u) \leq \pbf(u).  
 \end{equation}
@@
   misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
-leads to analogous results which hold for \smash{$\pbf^{(\epsilon)}$}. We
-formally state and prove this in the appendix.
+leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
+formally state and prove this in Corollary~\ref{cor: appr} in 
+the appendix.
 
@@
   \end{equation}
-  then
+  then with probability at least $1-\delta$, for a universal constant $c_1 > 0$,
   \begin{equation}
@@
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
-  \end{equation}
-  with probability at least $1-\delta$, where $c_1 > 0$ is a universal constant. 
+      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
+  \end{equation}
 \end{theorem}
@@
 %In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
-\section{Proof of Theorem~\ref{}}
-
-\section{Proofs}
-
-Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
-In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
-The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
-Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
-
-\subsection{Volume estimates}
-\label{sec: volume_estimates}
-
-We begin with some notation.
-Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
-Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
-Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
-
-Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
-
+\section{Proof of Theorem \ref{thm: conductance_upper_bound}}
+\label{sec: proof_of_theorem_1}
+
+For notational ease, we write
+\begin{align*}
+\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
+\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
+\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+\end{align*}
+for the random variable, mean, and probability of cut size and volume, respectively.
+
+With this notation in place, the goal of Theorem~\ref{thm: conductance_upper_bound} is roughly to show that, with probability at least $1 - \delta$, for a universal constant $c_1 > 0$ and for any $\epsilon > 0$, for a sufficiently large sample size $n$:
+\begin{align*}
+\Phi_{n,r}(\Csig[\Xbf]) := \frac{\cut_{n,r}}{\min\{\vol_{n,r}, \vol_{n,r}^c\}} \leq c_1 \frac{d}{\sigma}
+    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
+      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
+\end{align*}
+
+The proof of this theorem follows essentially from two technical Lemmas. 
+The following Lemma relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values.
 \begin{lemma}
-	\label{lem: expansion_volume}
-	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
-	\begin{equation}
-	\label{eqn: expansion_volume}
-	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We will show that for any $\epsilon > 0$, 
-	\begin{equation}
-	\label{eqn: ratio_of_volume}
-	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
-	\end{equation}
-	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
-
-	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
-	\begin{equation*}
-	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
-	\end{equation*}
-	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
-	\begin{equation*}
-	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
-	\end{equation*}
-	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
-	\begin{equation}
-	\label{eqn: finite_subcover}
-	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
-	\end{equation}
-	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
-Summarizing our findings, we have
-	\begin{equation}
-	\label{eqn: finite_subcover-1}
-	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
-	\end{equation}
-
-	We next show a lower bound on $\nu(\Asig)$.
-Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
-	\begin{equation*}
-	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
-	\end{equation*}
-	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$.
-As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
-	\begin{align*}
-	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
-	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
-	\begin{equation*}
-	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
-	\end{equation*}
-As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
-	\begin{equation*}
-	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
-	\end{equation*}
-	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
-	\begin{align*}
-	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
-	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
-	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
-\end{proof}
-\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
+	\label{lem: prob_bound_cutvol}
+	For any $\delta \in (0,1]$,
+	\begin{equation}
+	\label{eqn: numerator_additive_bound}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}}, \\ 
+	\frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, \\
+	\frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}},
+	\end{equation}
+	each with probability at least $1 - \delta$. 
+\end{lemma}
+We note that as a consequence of~\ref{asmp: bounded_volume} we have that $p_V^c \geq p_V$, so it will suffice to lower bound $p_V$ (since a lower bound for $p_V^c$ follows).
+The 
+following result provides upper and lower bounds on the expected values $p_K$ and $p_V$ respectively:
 \begin{lemma}
-	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
-	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
-	\begin{equation*}
-	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
-	\begin{equation*}
-	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
-	\end{equation*}
-	since then
-	\begin{equation*}
-	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
-	\end{equation*}
-
-	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
-	\begin{equation}
-	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
-	\end{equation}
-	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
-Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
-	\begin{equation*}
-	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
-	\end{equation*}
-	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
-\end{proof}
-
-We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
-\begin{lemma}
-	\label{lem: Taylor_series}
-	For any $0 \leq x \leq 1/2d$,
-	\begin{align*}
-	(1 + x)^d & \leq 1 + 2\dx \\
-	(1 - x)^d & \geq 1 - 2\dx.
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	We take the binomial expansion of $(1 + x)^d$:
-	\begin{align*}
-	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
-	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
-	\end{align*}
-The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
-\end{proof}
-
-Let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}.
-Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
+	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	\begin{align}
+	p_K &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
+	p_V &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
+	\end{align}
+\end{lemma}
+%\begin{lemma}
+%	\label{lem: expected_density_volume}
+%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+%	\begin{equation*}
+%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).
+%	\end{equation*}
+%\end{lemma}
+
+Taking these two technical lemmas as given we can now complete the proof of the theorem. 
+We fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
+\begin{equation}
+\label{eqn: conductance_representation_1}
+\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
+\end{equation}
+By a union bound we see that all three bounds in \eqref{eqn: numerator_additive_bound} hold with probability at least $1 - \delta$.
+Along with (\ref{eqn: conductance_representation_1}) this yields the upper bound \sbcomment{Changed $\mathbf{X}$ to $X$}
+\begin{equation*}
+\Phi_{n,r}(\Csig[X]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+\end{equation*}
+for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
+Now, some straightforward algebraic manipulations yield,
+\begin{align*}
+\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
+& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
+& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
+\end{align*}
+
+%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
+All that remains is some algebra, which we take care of below.
+
+\noindent Using Lemma \ref{lem: expected_density_cut}, we have
+\begin{equation*}
+\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
+\end{equation*}
+Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
+\begin{equation*}
+n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
+\end{equation*}
+which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$, and this yields the desired bound on $\Phi_{n,r}(\Csig[X])$. In order to complete the proof of
+the theorem it remains to prove Lemmas~\ref{lem: prob_bound_cutvol} and~\ref{lem: expected_density_cut}.
+
+\subsection{Proof of Lemma~\ref{lem: prob_bound_cutvol}}
+We first note that we can write $\cut_{n,r}$ as a double sum,
+	\begin{equation}
+	\label{eqn: density_cut_expansion}
+	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r),
+	\end{equation}
+	and similarly we can write $\vol_{n,r}$ as a sum of indicator functions,
+	\begin{equation}
+	\label{eqn: volume_expansion}
+	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r)).
+	\end{equation}
+From this we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
+	\end{equation*}
+	with kernels
+	\begin{align*}
+	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
+	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
+	\end{align*}
+	Similarly,
+	\begin{equation*}
+	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
+	\end{equation*}
+	with kernel,
+	\begin{equation*}
+	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
+	\end{equation*}
+	Appealing to a standard concentration inequality for U-statistics (see Lemma \ref{lem: bounded_difference}) we therefore have
+	\begin{equation*}
+	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
+	\end{equation*}
+	each with probability at least $1 - \delta$. 
+	%The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$.
+
+\subsection{Proof of Lemma~\ref{lem: expected_density_cut}}
 We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
-
+We 
+let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
+Our goal will be to upper bound $p_K$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
+and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
+%Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
 \begin{lemma}
@@
 \end{lemma}
-\begin{proof}
+\noindent Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
+\begin{equation*}
+\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr).
+\end{equation*}
+In order to lower bound $p_V$ we will show the following lower bound on the uniform local conductance:
+\begin{lemma}
+	\label{lem: local_conductance}
+	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
+	\begin{equation*}
+	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
+	\end{equation*}
+\end{lemma}
+Taking these two results as given we can now prove each of the two claims~\eqref{eqn:claim_one} and~\eqref{eqn:claim_two} in turn.
+\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } Recalling,~\eqref{eqn: density_cut_expansion} 
+	and by the linearity of expectations, we obtain
+	\begin{equation*}
+	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
+	\end{equation*}
+	Writing this with respect to the density function $f$, we have
+	\begin{align*}
+	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
+	\end{align*}
+	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
+Then, upper bounding the integral using \sbcomment{I changed the Lemma referenced here.
+I think it was wrong before} Lemma \ref{lem: expected_number_boundary_points} gives the final result.
+
+%\subsection{Proof of Lemma~\ref{Z}}
+\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } Recalling,~\eqref{eqn: volume_expansion}
+%The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. 
+	and by the linearity of expectation we obtain
+	\begin{equation*}
+	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
+	\end{equation*}
+	Writing this with respect to the density function $f$, we have
+	\begin{align*}
+	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
+	\end{align*}
+	whence the claim then follows by Lemma \ref{lem: local_conductance}.
+It remains to prove Lemmas~\ref{lem: expected_number_boundary_points} and~\ref{lem: local_conductance}, and we turn our attention to this next.
+\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
+The proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
 	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
 	\begin{equation*}
-	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k}
+	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
 	\end{equation*}
@@
 	\end{align}
-	where $\text{(i)}$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
+	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
 
@@
 As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
-\end{proof}
-\sbcomment{Here now.}
-Lemma \ref{lem: local_conductance} will be necessary to lower bound the expected volume of $\Csig[\Xbf]$ in $G_{n,r}$. Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
-\begin{equation*}
-\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr)
-\end{equation*}
-\begin{lemma}
-	\label{lem: local_conductance}
-	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
-	\begin{equation*}
-	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
+
+%\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
+
+\subsection{Proof of Lemma~\ref{lem: local_conductance}}
+The proof of this result relies on estimates of the volume of spherical caps which we defer to Appendix~\ref{sec:caps}.
 	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as $B(x,\sigma) \subseteq \Csig$,
@@
 	\begin{equation*}
-	\nu_{cap} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
+	\nu_{\text{cap}} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
 	\end{equation*}
 	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{16d}$. 
-
-	Then by Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
+	By Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
 	\begin{align*}
@@
 	\end{align*}
+
+\subsection{Volume Estimates}
+\label{sec: volume_estimates}
+%\section{Proofs}
+%
+%Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
+In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
+The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
+Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
+
+%\subsection{Volume estimates}
+
+We begin by recalling some notation.
+We let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
+Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
+Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
+
+Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
+
+\begin{lemma}
+	\label{lem: expansion_volume}
+	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
+	\begin{equation}
+	\label{eqn: expansion_volume}
+	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	We will show that for any $\epsilon > 0$, 
+	\begin{equation}
+	\label{eqn: ratio_of_volume}
+	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
+	\end{equation}
+	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
+
+	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
+	\begin{equation*}
+	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
+	\end{equation*}
+	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
+	\begin{equation*}
+	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
+	\end{equation*}
+	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
+	\begin{equation}
+	\label{eqn: finite_subcover}
+	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
+	\end{equation}
+	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
+Summarizing our findings, we have
+	\begin{equation}
+	\label{eqn: finite_subcover-1}
+	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon).
+	\end{equation}
+\noindent	We next show a lower bound on $\nu(\Asig)$.
+Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
+	\begin{equation*}
+	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
+	\end{equation*}
+	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$.
+As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
+	\begin{align*}
+	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
+	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
+	\begin{equation*}
+	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
+	\end{equation*}
+As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
+	\begin{equation*}
+	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
+	\end{equation*}
+	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
+	\begin{align*}
+	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
+	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
+	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
+	\end{align*}
+	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
 \end{proof}
-
-The following formula for the volume of the spherical cap, stated in terms of the incomplete beta function, is well known. We include it without proof.
-
+\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
+\begin{lemma}
+	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
+	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
+	\begin{equation*}
+	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
+	\begin{equation*}
+	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
+	\end{equation*}
+	since then
+	\begin{equation*}
+	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
+	\end{equation*}
+
+	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
+	\begin{equation}
+	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
+	\end{equation}
+	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
+Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
+	\begin{equation*}
+	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
+	\end{equation*}
+	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
+\end{proof}
+
+We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
+\begin{lemma}
+	\label{lem: Taylor_series}
+	For any $0 \leq x \leq 1/2d$,
+	\begin{align*}
+	(1 + x)^d & \leq 1 + 2\dx \\
+	(1 - x)^d & \geq 1 - 2\dx.
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	We take the binomial expansion of $(1 + x)^d$:
+	\begin{align*}
+	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
+	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
+	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
+	\end{align*}
+The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
+\end{proof}
+
+\subsection{Spherical Caps and Associated Estimates}
+\label{sec:caps}
+In this section, we state a result for the volume of a spherical cap and derive some 
+useful upper bounds. 
 \begin{lemma}
 	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{Cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{Cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
+	\begin{equation*}
+	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
 	\end{equation*}
@@
 
+The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
+an upper bound on the ratio of Gamma functions. 
 \begin{lemma}
@@
 
-Lemma \ref{lem: beta_function} follows from $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
 \begin{lemma}
@@
 \end{lemma}
-
-\subsection{Density-weighted cut and volume estimates}
-\label{sec: density_weighted_cut_and_volume_estimates}
-
-For notational ease, we write
-\begin{align*}
-\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
-\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
-\end{align*}
-for the random variable, mean, and probability of cut size and volume, respectively.
-
-\begin{lemma}
-	\label{lem: expected_density_cut}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-	\begin{equation*}
-	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write $\cut_{n,r}$ as a double sum,
-	\begin{equation}
-	\label{eqn: density_cut_expansion}
-	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r)
-	\end{equation}
-	and by linearity of expectation, we obtain
-	\begin{equation*}
-	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
-	\end{align*}
-	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
-Then, upper bounding the integral using Lemma \ref{lem: expected_density_cut} gives the final result.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: expected_density_volume}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-	\begin{equation*}
-	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
-	\begin{equation}
-	\label{eqn: volume_expansion}
-	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
-	\end{equation}
-	and by linearity of expectation we obtain
-	\begin{equation*}
-	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-	\end{align*}
-	whence the claim then follows by Lemma \ref{lem: local_conductance}.
-\end{proof}
-
-To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
-\begin{equation*}
-\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
-\end{equation*}
-to $p_K$ and $p_V$.
-
-In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
+\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
+
+%\subsection{Density-weighted cut and volume estimates}
+%\label{sec: density_weighted_cut_and_volume_estimates}
+%
+%For notational ease, we write
+%\begin{align*}
+%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
+%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
+%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+%\end{align*}
+%for the random variable, mean, and probability of cut size and volume, respectively. 
+%
+%\begin{lemma}
+%	\label{lem: expected_density_cut}
+%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+%	\begin{equation*}
+%	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+%	\end{equation*}
+%\end{lemma}
+%\begin{proof}
+%
+%\end{proof}
+%
+%\begin{lemma}
+%	\label{lem: expected_density_volume}
+%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+%	\begin{equation*}
+%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
+%	\end{equation*}
+%\end{lemma}
+%\begin{proof}
+%	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
+%	\begin{equation}
+%	\label{eqn: volume_expansion}
+%	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
+%	\end{equation}
+%	and by linearity of expectation we obtain
+%	\begin{equation*}
+%	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
+%	\end{equation*}
+%	Writing this with respect to the density function $f$, we have
+%	\begin{align*}
+%	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+%	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
+%	\end{align*}
+%	whence the claim then follows by Lemma \ref{lem: local_conductance}.
+%\end{proof}
+%
+%To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
+%\begin{equation*}
+%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
+%\end{equation*}
+%to $p_K$ and $p_V$. 
+%
+%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
 These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
-
-\begin{lemma}
-	\label{lem: prob_bound_cutvol}
-	For any $\delta \in (0,1]$,
-	\begin{equation}
-	\label{eqn: numerator_additive_bound}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
-	\end{equation}
-	each with probability at least $1 - \delta$. 
-\end{lemma}
-
-\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
-	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-	\end{equation*}
-	with kernels
-	\begin{align*}
-	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{align*}
-
-	Similarly,
-	\begin{equation*}
-	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-	\end{equation*}
-	with kernel,
-	\begin{equation*}
-	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{equation*}
-
-	From Lemma \ref{lem: bounded_difference} we therefore have
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation*}
-	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
-\end{proof}
-
-\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
-\label{sec: proof_of_theorem_1}
-
-The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
+%
+%\begin{lemma}
+%	\label{lem: prob_bound_cutvol}
+%	For any $\delta \in (0,1]$,
+%	\begin{equation}
+%	\label{eqn: numerator_additive_bound}
+%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
+%	\end{equation}
+%	each with probability at least $1 - \delta$. 
+%\end{lemma}
+%
+%\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
+%	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
+%	\begin{equation*}
+%	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
+%	\end{equation*}
+%	with kernels
+%	\begin{align*}
+%	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
+%	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
+%	\end{align*}
+%	
+%	Similarly,
+%	\begin{equation*}
+%	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
+%	\end{equation*}
+%	with kernel,
+%	\begin{equation*}
+%	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
+%	\end{equation*}
+%	
+%	From Lemma \ref{lem: bounded_difference} we therefore have
+%	\begin{equation*}
+%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
+%	\end{equation*}
+%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
+%\end{proof}
+%
+%\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
+%\label{sec: proof_of_theorem_1}
+%
+%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
 All that remains is some algebra, which we take care of below.
-
-Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-\begin{equation}
-\label{eqn: conductance_representation_1}
-\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
-\end{equation}
-Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
+%
+%Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
+%\begin{equation}
+%\label{eqn: conductance_representation_1}
+%\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
+%\end{equation}
+%Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
 Along with (\ref{eqn: conductance_representation_1}) this means
-\begin{equation*}
-\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
-\end{equation*}
-for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-Now, some straightforward algebraic manipulations yield
-\begin{align*}
-\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
-& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
-\end{align*}
-By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
-\begin{equation*}
-\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-\end{equation*}
-Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-\begin{equation*}
-n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
-\end{equation*}
-which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+%\begin{equation*}
+%\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+%\end{equation*}
+%for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
+%Now, some straightforward algebraic manipulations yield
+%\begin{align*}
+%\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
+%& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
+%& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
+%\end{align*}
+%By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
+%\begin{equation*}
+%\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
+%\end{equation*}
+%Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
+%\begin{equation*}
+%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
+%\end{equation*}
+%which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+
+\section{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
 
@@
 
-Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$ statistic} to be
+Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$-statistic} to be
 \begin{equation*}
@@
 	\label{eqn: volwt_bound}
-	\frac{1}{2}\vol_0 \leq \vol_{n,r}(\Csig[\Xbf]) & \leq \frac{3}{2} \vol_0
+	\frac{1}{2}\vol_0 &\leq \vol_{n,r}(\Csig[\Xbf])  \leq \frac{3}{2} \vol_0
 	\end{align}
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\epsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\epsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
 	\begin{enumerate}
@@
 	\label{lem: zhu}
-	Let $\epsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
-Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
-	\begin{equation*}
-	S_{\beta} := \left\{u \in V: \pbf^{(\epsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
-	\end{equation*}
-
-	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \epsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
+	Let $\varepsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
+Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\varepsilon)} := \pbf^{(\varepsilon)}(v,\alpha; G)$ of the form
+	\begin{equation*}
+	S_{\beta} := \left\{u \in V: \pbf^{(\varepsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
+	\end{equation*}
+
+	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \varepsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
 	\begin{align}
@@
 	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
-	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$.
+	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\varepsilon = 0$.
 \end{enumerate}
@@
 
-The choice $\epsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\epsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\epsilon)}$.
+The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
 All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
@@
 \frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\epsilon = \frac{1}{47}$} \\
+& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
 & \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
@@
 
-It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\epsilon = 1/11$ to obtain
+It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
 \begin{equation}
@@
 
-Using \eqref{eqn: appr_error} with $\epsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
-\begin{equation*}
-\pbf^{(\epsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
+Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
+\begin{equation*}
+\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
 \end{equation*}
@@
 \begin{equation*}
-\frac{\pbf^{(\epsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
-\end{equation*}
-
-On the other hand $\pbf^{(\epsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\epsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
+\end{equation*}
+
+On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
 

### 2019-06-17 neurips/local_spectral_density_clustering_arxiv.tex
re-org of Theorem 3

@@
 clustering given previously, a few related lines of work are worth
-highlighting. \citep{shi2009,schiebinger2015} examine the consistency of  
+highlighting. \citet{shi2009} and \citet{schiebinger2015} examine the consistency of  
 spectral algorithms in recovering the latent labels in certain

### 2019-06-19 neurips/local_spectral_density_clustering_arxiv.tex
more random edits

@@
 first constructs a geometric graph $G$, where vertices correspond to samples,
-and edges correspond to proximities between samples. It then learns a feature
+and edges correspond to proximities between samples. It then estimates a feature
 embedding based on the Laplacian of $G$, and applies a simple clustering
@@
 \citet{haveliwala2003}, then further developed by
-\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013},
-among others.
+several others~\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
 
@@
 and examine what the output of local clustering on a data set reveals about the
-underlying density $f$.  In particular, we examine the ability of PPR to recover
+underlying density of the samples 
+$f$.  In particular, we examine the ability of PPR to recover
 \emph{density clusters} of $f$, defined as the connected components of
@@
 (a central object of interest in the statistical clustering literature, dating
-back to \citet{hartigan1981}).
+back to the work of \citet{hartigan1981}).
 
@@
 
-\paragraph{Summary of results.} A summary of our results (and outline for this
+\paragraph{Summary of results.} A summary of our results (and an outline for this
 paper) is as follows.
@@
 symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
-minimax optimal level set estimators under Hausdorff loss and
-\citet{hartigan1981, chaudhuri2010} consider consistent estimation of the
-cluster tree, to note but a few works. Our goal is not to improve on these
+minimax optimal level-set estimators under Hausdorff loss and
+\citet{hartigan1981, chaudhuri2010, balakrishnan2013} consider consistent estimation of the
+cluster tree.
+%, to note but a few works. 
+Our goal is not to improve on these
 results, nor to offer a better algorithm for level set estimation; indeed, seen as
@@
   $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
-  additionally assume $f$ satisfies \ref{asmp: valid_region}. If Algorithm
+  additionally assume that $f$ satisfies \ref{asmp: valid_region}. If Algorithm
   \ref{alg: ppr} is well-initialized, there exists a universal constant $c >
@@
 \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently
-small upper bound on $\kappa(\Cset)$ ensures such a gap exists with probability
+small upper bound on $\kappa(\Cset)$ ensures that such a gap exists with probability
 1 as $n \to \infty$, and hence guarantees \smash{$\Cest$} will be a consistent  
@@
 \begin{equation*}
-\norm{q_v^{(m)} - \pi}_{TV} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
+\norm{q_v^{(m)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
 \end{equation*}
@@
 Proposition \ref{prop: tv_mixing_time} relates these geometric quantities to the TV distance between $q_v^{(t)}$ and stationary distribution $\pi$.
+\sbcomment{Added $\max$ to the RHS.}
 \begin{proposition}
@@
 	For any $v \in V$, and any $0 < a \leq 1$,
-	\begin{equation*}
-	\norm{q_v^{(t + 3)} - \pi}_{TV} \leq \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2as(G)} + \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation*}
+	\begin{align*}
+	\norm{q_v^{(t + 3)} - \pi}_{\mathrm{TV}} \leq \max\set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} 
+	 \\
+	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{align*}
 \end{proposition}
@@
 	\label{lem: tv_to_uniform_distance}
-	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
+	Let $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
 	\begin{equation*}
@@
 	\begin{align}
-	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
-	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
-	& \leq \norm{q_v^{(m-1)} - \pi}_{TV} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
+	\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
+	& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
 	\end{align}
 	since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{TV} \leq \norm{q_v^{(t)} - \pi}_{TV}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and hypothesis,
+As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and hypothesis,
 	\begin{equation*}
@@
 	\begin{equation*}
-	\norm{q_v^{(\tau_0 + 3)} - \pi}_{TV} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-	\end{equation*}
-
-	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{TV} \leq \epsilon$.
+	\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+	\end{equation*}
+
+	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
 Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
 	\begin{equation*}
-	\norm{q_v^{(\tau_1)} - \pi}_{TV} \leq \frac{1}{14 s(G)}
+	\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
 	\end{equation*}
@@
 \begin{equation*}
-\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{TV}.
+\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}.
 \end{equation*}
@@
 	\begin{equation*}
-	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
-	\end{equation*}
-	where $\norm{P - Q}_{TV}$ is the total variation distance between probabilities $P$ and $Q$. 
+	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
+	\end{equation*}
+	where $\norm{P - Q}_{\mathrm{TV}}$ is the total variation distance between probabilities $P$ and $Q$. 
 \end{lemma}
@@
 	\end{equation*}
-	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{TV}$.
+	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}}$.
 
@@
 \begin{equation*}
-\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{TV} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
+\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{\mathrm{TV}} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
 \end{equation*}
@@
 
-\subsection{Proof of Theorem \ref{thm: misclassification_rate}}
+\section{Proof of Theorem \ref{thm: misclassification_rate}}
 \label{sec: proof_of_misclassification_rate}
-
 In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
@@
 	\end{equation*}
-
 	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \varepsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
@@
 
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
 We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
@@
 
-\subsection{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
+\section{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
 \label{sec: proof_of_consistent_cluster_recovery}
@@
 
-\begin{proof}
-	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. Given starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
+We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
+
+\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
+~
+
+In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
+
+Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
+As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
+\begin{align}
+\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
+\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
+\end{align}
+We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
+\begin{align}
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
+\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
+\end{align}
+
+The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
+& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
+& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+Similarly, for each $u' \in \Cset'[\Xbf]$,
+\begin{align*}
+\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
+& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
+& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
+\end{align*}
+and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
+
+It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
+\begin{equation}
+\label{eqn: pimin_Dmin_lb}
+\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
+\end{equation}
+
+Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
+\begin{equation}
+\label{eqn: difficulty_bound}
+\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
+\end{equation}
+\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
+
+\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
+
+Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
+\begin{equation*}
+\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
+\end{equation*}
+and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
+\begin{equation*}
+\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
+\end{equation*}
+
+On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+
+\subsection{Proof of Lemma~\ref{lem: setup}}
+	%The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. 
+	Given a starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
 	\begin{equation}
@@
 The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
-\end{proof}
-
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-~
-
-In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
-
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
-As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
-\begin{align}
-\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
-\end{align}
-We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
-\begin{align}
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
-\end{align}
-
-The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
-& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-Similarly, for each $u' \in \Cset'[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
-& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
-& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
-
-It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
-\begin{equation}
-\label{eqn: pimin_Dmin_lb}
-\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
-\end{equation}
-
-Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
-\begin{equation}
-\label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
-\end{equation}
-\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
-
-\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
-
-Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
-\begin{equation*}
-\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
-\end{equation*}
-and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
-\begin{equation*}
-\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
-\end{equation*}
-
-On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
 

### 2019-06-20 neurips/local_spectral_density_clustering_arxiv.tex
more random edits
edits to Sec 1 and 2

@@
 \begin{abstract}
-\noindent We analyze Personalized PageRank (PPR), a local spectral method for clustering,
+\noindent We analyze the Personalized PageRank (PPR) algorithm, a local spectral method for clustering,
 which extracts clusters using locally-biased random walks around a user-specified
@@
 \label{sec: introduction}
-
-In this paper, we study the problem of clustering: splitting a given data set
+In this paper, we consider the problem of clustering: splitting a given data set
 into groups that satisfy some notion of within-group similarity and
-between-group difference.  We focus on spectral clustering, a family of powerful
-nonparametric clustering algorithms.  Generally speaking, a spectral algorithm
+between-group difference.  Our particular focus is on
+spectral clustering methods, a family of powerful
+nonparametric clustering algorithms. Roughly speaking, a spectral algorithm
 first constructs a geometric graph $G$, where vertices correspond to samples,
-and edges correspond to proximities between samples. It then estimates a feature
-embedding based on the Laplacian of $G$, and applies a simple clustering
-technique (like k-means clustering) in the embedded feature space.
+and edges correspond to proximities between samples. The algorithm 
+then estimates a feature
+embedding based on (an appropriate) Laplacian matrix of the graph 
+$G$, and applies a simple clustering
+technique (like $k$-means clustering) in the embedded feature space.
+
+% Spectral clustering and density clustering
+%Spectral clustering algorithms, which
+%originated in the early work of Fiedler \cite{fiedler73}, have seen a recent revival 
+%(see for instance the recent review~\cite{XX}) focused mainly on understanding the performance of spectral clustering on the Stochastic Block Model (SBM) and closely related problems.
+%A parallel line of work \cite{shi09,schiebinger15}, has considered spectral partitioning applied to a non-parametric mixture model
+%where once again the clustering goal is to recover the latent labels of a sample $X_1,\ldots,X_n \sim P$.
+These works proceed by relating the eigenvectors of the graph Laplacian to eigenfunctions of an appropriately defined integral operator, and then using assumptions about the (non-)overlap of the mixture components to show that these eigenfunctions elucidate the latent labels.
 
@@
 computed using random walks around some user-specified seed node.  A popular 
-local clustering algorithm is Personalized PageRank (PPR), first introduced by 
+local clustering algorithm is the Personalized PageRank (PPR) algorithm, first introduced by 
 \citet{haveliwala2003}, then further developed by
@@
 guarantees on traditional graph-theoretic notions of cluster quality (such as
-conductance).  In this paper, we adopt a more traditional statistical viewpoint,
+conductance).  In this paper, we adopt a classical statistical viewpoint,
 and examine what the output of local clustering on a data set reveals about the
@@
 
-\paragraph{PPR on a neighborhood graph.} We now describe the clustering
+\section{Background and Related Work}
+We begin by providing some standard background on the PPR algorithm
+and the density clustering setup, before turning our attention to related work
+and a
+detailed summary of our contributions.
+
+\subsection{PPR on a neighborhood graph} 
+We now describe the clustering
 algorithm that will be our focus for the rest of the paper. Let $\Xbf = \{x_1,
 \ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$,
-with density $f$.  For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the
+with density~$f$.  For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the
 \emph{$r$-neighborhood graph} of $\Xbf$, an unweighted, undirected graph with
@@
 $G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
-$v$th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
+$v$-th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
 $\vol_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$
@@
 %\smash{$\Phi(S_{\beta^*}; G_{n,r})$}. 
-For concreteness, this is summarized in Algorithm \ref{alg: ppr}.
+For concreteness, the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.
 
@@
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-  \STATE Return as a cluster \smash{$\Cest = S_{\beta^*}$}, where  
+  \STATE Return the cluster \smash{$\Cest = S_{\beta^*}$}, where  
   $$
-  \beta^* = \argmin_{\beta \in (\frac{1}{40}, \frac{1}{11})} \Phi(S_{\beta}; G_{n,r}).
+  \beta^* = \argmin_{\beta \in (\frac{1}{40}, \frac{1}{11})}~ \Phi(S_{\beta}; G_{n,r}).
   $$
@@
 
-\paragraph{Estimation of density clusters.} Let \smash{$\Cbb_f(\lambda)$} denote 
+\subsection{Estimation of density clusters} 
+Let \smash{$\Cbb_f(\lambda)$} denote 
 the connected components of the density upper level set $\{x \in \Rd: f(x) >
@@
 \end{definition}
-
-\paragraph{Summary of results.} A summary of our results (and an outline for this
-paper) is as follows.
-
-\begin{enumerate}
-\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce
-  a set of natural geometric conditions on the density cluster $\Cset$
-  %formalize a measure of difficulty based on these geometric conditions, 
-  and show that when Algorithm \ref{alg: ppr} is properly initialized, the size of
-  the symmetric set difference of \smash{$\Cest$} and a thickened version of the
-  density cluster $\Csig$ can be bounded in a meaningful way.
-  % this difficulty measure.
-
-\item We further show in Section \ref{sec:
-    consistent_cluster_estimation_with_ppr} that if the density cluster 
-  $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
-  will consistently estimate a density cluster in the sense of
-  \eqref{eqn: consistent_density_cluster_recovery}.
-
-\item In Section \ref{sec: analysis}, we detail some of the analysis required to
-  prove our main results, and expose the parts various geometric quantities play 
-  in the difficulty of the clustering problem.
-
-\item In Section \ref{sec: experiments}, we empirically investigate the
-  tightness of our analysis, and provide examples showing how violations of our
-  geometric conditions impact density cluster recovery by PPR.
-\end{enumerate}
-
-Our main takeaway: PPR, run on a neighborhood graph, recovers geometrically
-compact high-density clusters.
-
-\paragraph{Related work.} In addition to the background on local spectral
+\noindent Consistent cluster recovery roughly ensures that, for a given $\lambda$, the estimated cluster $\Cest$ contains all
+points in a true
+density cluster $\Cset$, and simultaneously does not contain any points in any other density cluster $\Cset'$.
+
+With these definitions in place, our broad goal will be to understand the extent to which the PPR algorithm is able to
+recover a cluster which either guarantees low symmetric set difference to a true density cluster, or which consistently estimates
+a true density cluster.
+
+%\subsection{Our Contributions}
+
+\subsection{Related Work and Our Contributions}
+In addition to the background on local spectral
 clustering given previously, a few related lines of work are worth
@@
 %, to note but a few works. 
-Our goal is not to improve on these
+We emphasize that our goal is not to improve on these
 results, nor to offer a better algorithm for level set estimation; indeed, seen as
@@
 well-conditioned for PPR, and those which are not.
+
+A summary of our results (and an outline for this
+paper) is as follows.
+
+\begin{enumerate}
+\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce
+  a set of natural geometric conditions on the density cluster $\Cset$
+  %formalize a measure of difficulty based on these geometric conditions, 
+  and show that when Algorithm \ref{alg: ppr} is properly initialized, the size of
+  the symmetric set difference of \smash{$\Cest$} and a thickened version of the
+  density cluster $\Csig$ can be bounded in a meaningful way.
+  % this difficulty measure.
+
+\item We further show in Section \ref{sec:
+    consistent_cluster_estimation_with_ppr} that if the density cluster 
+  $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
+  will consistently estimate a density cluster in the sense of
+  \eqref{eqn: consistent_density_cluster_recovery}.
+
+\item In Section \ref{sec: analysis}, we detail some of the analysis required to
+  prove our main results, and expose the parts various geometric quantities play 
+  in the difficulty of the clustering problem.
+
+\item In Section \ref{sec: experiments}, we empirically investigate the
+  tightness of our analysis, and provide examples showing how violations of our
+  geometric conditions impact density cluster recovery by PPR.
+\end{enumerate}
+
+\noindent At this point we summarize one of our main takeaways: 
+PPR, run on a neighborhood graph, recovers \emph{geometrically
+compact} high-density clusters. Our main theoretical results, make this takeaway 
+precise, and provide concrete ways of quantifying the geometric
+compactness of a density cluster. To complement this, we also provide experimental
+evidence that the PPR algorithm can fail to recover high-density clusters which are not
+geometrically compact.
 
@@
 \begin{equation*}
-h_q^{(t)}(x) = \max \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
-\end{equation*}
-where the maximum is over all $w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$.
+h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
+\end{equation*}
+where the maximum is over:
+\begin{align*}
+\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
+\end{align*}
+%$w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$. 
 Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{v}^{(t)}(x)$ for all $0 \leq x \leq 1$.

### 2019-06-20 neurips/local_spectral_density_clustering_arxiv.tex
reorganized mixing time theorem section 1

@@
 \usepackage{fullpage}
-\usepackage[T1]{fontenc} 
 \usepackage{epsf} 
@@
 
-\subsection{Mixing time on graphs}
-\label{sec: mixing_time_on_graphs}
-
-We generalize some notation from the main text.
+Denote $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
+The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that, for universal constants $c_2, c_3 > 0$, with probability one as $n \to \infty$,
+\begin{equation*}
+\limsup_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3
+\end{equation*}
+We follow a two-step approach typically to used to establish upper bounds on the mixing time of Markov chains.
+
+In the first step, we relate the mixing time $\tau_{\infty}(G)$ of a generic graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
+We now build to a formal definition of these expansion properties.
+First, we recall the the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well.
+For $u \in V$, $S \subseteq V$,
+\begin{equation*}
+\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G).
+\end{equation*}
+Additionally, we recall the \emph{normalized cut} $\Phi(S;G)$ is defined (as in \eqref{eqn: normalized_cut}) as
+\begin{equation*}
+\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}}.
+\end{equation*}
+
+With these functionals in hand, we can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
+\begin{equation*}
+s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
+\end{equation*}
+
+The following Proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
+\begin{proposition}
+	\label{prop: pointwise_mixing_time}
+	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
+	\begin{equation*}
+	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+	\end{equation*}
+\end{proposition}
+
+The second step in our approach is to lower bound the local spread and conductance over the particular graph $\widetilde{G}_{n,r}$.
+The following result provides the desired lower bounds, which hold asymptotically as $n \to \infty$,
+\begin{proposition}
+	\label{prop: local_spread_conductance}
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one,
+	\begin{equation*}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
+	\end{equation*}
+	and
+	\begin{equation*}
+	\liminf_{n \to \infty} \Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+	\end{equation*}
+\end{proposition}
+
+Taking these results as given, the proof of the theorem is more or less complete.
+We note that since $r$ is fixed, \textcolor{red}{with probability one} $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty > 10$, and we may therefore apply Proposition \ref{prop: pointwise_mixing_time} with respect to $\widetilde{G}_{n,r}$.
+Along with Lemma \ref{prop: local_spread_conductance}, this yields
+\begin{equation*}
+\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
+\end{equation*}
+The first term dominates the middle term, and the theorem follows after an appropriate choice of $c_2$ and $c_3$.
+
+\subsection{Proof of Proposition \ref{prop: pointwise_mixing_time}}
+\label{sec: pointwise_mixing_time}
+
+We first generalize some notation from the main text.
 For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
-Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$.
-An important intermediate quantity used to bound the relative pointwise mixing time $\tau_{\infty}(G)$ is the total variation distance between the distributions $q_v^{(m)} := q^{(m)}(v,\cdot)$ and $\pi$,
-\begin{equation*}
-\norm{q_v^{(m)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
-\end{equation*}
-We recall the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well. For $u \in V$, $S \subseteq V$, 
-\begin{equation*}
-\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G)
-\end{equation*}
-
-The \emph{local spread} is defined as
-\begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}
-\end{equation*}
-
-Recalling the \emph{normalized cut} $\Phi(S;G)$ is defined (as in \eqref{eqn: normalized_cut}) as
-\begin{equation*}
-\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
-\end{equation*}
-we refer to the minimum normalized cut over $V$ as the \emph{conductance},
-\begin{equation*}
-\Phi(G) := \min_{S \subseteq V} \Phi(S;G).
-\end{equation*}
-
-Proposition \ref{prop: tv_mixing_time} relates these geometric quantities to the TV distance between $q_v^{(t)}$ and stationary distribution $\pi$.
-\sbcomment{Added $\max$ to the RHS.}
-\begin{proposition}
-	\label{prop: tv_mixing_time}
+Denote the $t$-step probability distribution of this random walk, originating from a particular $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
+
+Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
+\begin{equation*}
+d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
+\end{equation*}
+Our goal is to demonstrate that for sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$.
+To do so, we introduce the \emph{total variation distance} between the distributions $q_v^{(t)}$ and $\pi$, given by
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(t)}(u) - \pi(u)}.
+\end{equation*}
+As we will see, an upper bound on the uniform distance can be obtained from an analogous upper bound on the total variation distance.
+First, however, we upper bound the total variation distance $||q_v^{(t)} - \pi||_{\mathrm{TV}}$ as a function of the local spread $s(G)$, the conductance $\Phi(G)$ and the number of steps $t$.
+\begin{lemma}
+	\label{lem: tv_mixing_time}
 	For any $v \in V$, and any $0 < a \leq 1$,
@@
 	\end{align*}
-\end{proposition}
-
-As we will see, Proposition \ref{prop: tv_mixing_time} is an essential step to proving an upper bound on the uniform mixing time.
-We justify this statement next, before moving on to proving Proposition \ref{prop: tv_mixing_time} in the following subsection.
-
-\paragraph{Uniform mixing time}
-Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)}$ and $\pi$, given by
-\begin{equation*}
-d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
-\end{equation*}
-
+\end{lemma}
+
+As mentioned, a bound on the total variation distance implies a corresponding bound on the uniform distance $d_{\mathrm{unif}}$, given by the following result:
 \begin{lemma}
@@
 \end{lemma}
-\begin{proof}
-	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
+
+Taking these Lemmas as given, we proceed to prove the proposition. Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$. Then,
+\begin{equation*}
+\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
+\end{equation*}
+and so by Lemma \ref{lem: tv_mixing_time},
+\begin{equation*}
+\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+\end{equation*}
+It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
+Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
+\begin{equation*}
+\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
+\end{equation*}
+and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$.
+
+\subsection{Proof of Lemma \ref{lem: tv_mixing_time}}
+\label{sec: mixing_time_on_graphs}
+
+We generalize the notation of the previous subsection.
+For a starting distribution $z$ to be specified later (meaning $\textrm{supp}(z) \subseteq V$ and $\sum_{u \in V}z(u) = 1$), and for $t \geq 0$ an integer, let $q_z^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $z$.
+
+We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined as
+$h_z^{(t)}, t \geq 0$, 
+\begin{equation*}
+h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}
+\end{equation*}
+where the maximum is over:
+\begin{align*}
+\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
+\end{align*}
+The utility of the Lovasz-Simonovits curve comes from the following observations:
+first, note that
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sup_{S \subseteq V} \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation*}
+where we use the standard notation $\pi(S) := \sum_{u \in S} \pi(u)$, and likewise for $q_v^{(t)}(S)$. Moreover, observe that for any $S \subseteq V$ and any integer $t \geq 0$,
+\begin{equation*}
+\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation*}
+Therefore, taking the maximum over all $S \subseteq V$ on both sides, we have
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \max_{0 \leq x \leq 1} h_v^{(t)}(x).
+\end{equation*}
+Now, take $z = e_vW^3$.
+Observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
+To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$.
+
+To do so, we split the interval $[0,1]$--based on a number $\mu = as(G)$ for some $0 < a < 1$ to be specified later--into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$.
+Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,
+\begin{equation*}
+\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
+\end{equation*}
+
+The following technical Lemma collects the upper bounds which hold over $[\mu, 1 - \mu]$ and $[0,\mu) \cup (1 - \mu, 1]$, respectively:
+\begin{lemma}
+	\label{lem: mixing_all_sets}
+	For any $\mu \leq x \leq 1 - \mu$, 
+	\begin{equation}
+	\label{eqn: mixing_large_sets}
+	h_z^{(t)}(x) \leq \ell_{\mu}(x) + \left(\frac{1}{1 - 2\mu} + \frac{1}{\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t.
+	\end{equation}
+	For any $0 < x \leq \mu$ or $1 - \mu \leq x < 1$
+	\begin{equation}
+	\label{eqn: mixing_small_sets}
+	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+	\end{equation}
+\end{lemma}
+\noindent Taking Lemma \ref{lem: mixing_all_sets} as given, we have nearly completed our proof. Note that for any $\mu \leq x \leq 1 - \mu$,
+\begin{align*}
+\ell_{\mu}(x) & \leq \max\set{h_z^{(t)}(\mu),h_z^{(t)}(1 - \mu)} \\
+& \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+\end{align*}
+with the latter inequality following from \eqref{eqn: mixing_small_sets}. Therefore, for any $x \in [0,1]$,
+\begin{equation*}
+h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{equation*}
+which is the desired result.
+
+\subsection{Proof of Lemma \ref{lem: mixing_all_sets}}
+
+We first prove \eqref{eqn: mixing_large_sets}, and then \eqref{eqn: mixing_small_sets}.
+\paragraph{Proof of \eqref{eqn: mixing_large_sets}:}
+The desired result is a consequence of Theorem 1.2 of \cite{lovasz1990}. To state this theorem, we introduce the notation
+\begin{equation*}
+C_{\mu} = \max \set{\frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu},
+\end{equation*}
+and then the theorem itself.
+\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
+	\label{thm: lovasz_simonovits_1993}
+	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_1993}
+	h_z^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation}
+\end{theorem}
+In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show
+\begin{equation}
+\label{eqn: lt_ub_1}
+h_z^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
+\end{equation}
+which will in turn imply
+\begin{align*}
+C_{\mu} & \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \\
+& \leq \frac{1}{\mu} + \frac{1}{1 - 2\mu}.
+\end{align*}
+Plugging this upper bound into \eqref{eqn: lovasz_simonovits_1993}, we obtain
+\begin{align*}
+h_z^{(t)}(x) & \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t \\
+& \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{align*}
+which is the desired result.
+
+It remains to show \eqref{eqn: lt_ub_1}.
+To do so, we make use of an equivalent representation of the Lovasz-Simonovits curve $h_z^{(t)}$.
+Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
+\begin{equation*}
+\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)}
+\end{equation*}
+and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
+\begin{equation}
+\label{eqn: lovasz_simonovits_curve}
+h_z^{(t)}(x) = \sum_{j = 1}^{k - 1} (q_z^{(t)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q_z^{(t)}(u_k) - \pi(u_k) \right).
+\end{equation}
+The representation of the Lovasz-Simonovits curve given by \eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a concave, piecewise linear curve.
+Moreover, we observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
+\begin{equation}
+\label{eqn: lovasz_simonovits_slope}
+-1 \leq v(x) \leq \frac{h_z^{(0)}(\mu)}{\mu}.
+\end{equation}
+Note that $\ell_{\mu}(\mu) = h_z^{(0)}(\mu)$, and for $x \geq \mu$, 
+\begin{equation*}
+h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}
+\end{equation*}
+by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
+\begin{align*}
+h_z^{(0)}(x) - \ell_{\mu}(x) & \leq h_z^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu)\right) + \frac{h_z^{(0)}(\mu)}{\mu}(x - \mu) \\
+& =  \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(\mu) + \frac{h_z^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu) \\
+& \leq \sqrt{x - \mu} \left(\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} \right)
+\end{align*}
+On the other hand, $\ell_{\mu}(1 - \mu) = h_z^{(0)}(1 - \mu)$, and by the concavity of $h_z^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
+\begin{equation*}
+h_z^{(0)}(x) \leq h_z^{(0)}(1 - \mu) + (1 - x - \mu).
+\end{equation*}
+Similar manipulations to above give the upper bound
+\begin{align*}
+h_z^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
+\end{align*}
+and \eqref{eqn: lt_ub_1} follows.
+
+\paragraph{Proof of \eqref{eqn: mixing_small_sets}:}
+First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
+\begin{equation}
+\label{eqn: mixing_time_small_sets_1}
+h_z^{(t)}(x) \leq q_z^{(t)}(U_{k - 1}) + q_z^{(t)}(u_k)
+\end{equation}
+Recalling that $z = e_vW^3$, we will rely on the key fact that for any $u \neq v, t \geq 1$,
+\begin{equation}
+\label{eqn: mixing_time_small_sets_2}
+q_z^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
+\end{equation}
+On the other hand if $u = v$,
+\begin{equation}
+\label{eqn: mixing_time_small_sets_3}
+q_z^{(m)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
+\end{equation}
+Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
+\begin{equation*}
+h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
+\end{equation*}
+Finally, since $x \leq a s(G)$, 
+\begin{equation*}
+\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
+\end{equation*}
+and the desired result is shown.
+
+Now, we turn to the case where $x \geq 1 - as(G)$.
+But since $h_z^{(t)}(1) = 0$, and the slope of $h_z$, $v(x')$ is no less than $-1$ for all $x' \in [0,1]$, this implies $h_z^{(t)}(x) \leq 1 - x \leq as(G)$.
+
+\subsection{Proof of Lemma \ref{lem: tv_to_uniform_distance}}
+
+The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebra. Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
 \begin{align}
@@
 and the claim is shown.
-\end{proof}
-
-Together, Proposition \ref{prop: tv_mixing_time} and Lemma \ref{lem: tv_to_uniform_distance} imply the main result of this section.
-
-\begin{proposition}
-	\label{prop: pointwise_mixing_time}
-	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
-	\begin{equation*}
-	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-	\end{equation*}
-\end{proposition}
-\begin{proof}
-	Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$. Then,
-	\begin{equation*}
-	\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
-	\end{equation*}
-	and so by Proposition \ref{prop: tv_mixing_time},
-	\begin{equation*}
-	\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-	\end{equation*}
-
-	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
-Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
-	\begin{equation*}
-	\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
-	\end{equation*}
-	and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
-\end{proof}
 
@@
 \label{sec: proof_of_proposition_tv_mixing_time}
-
-For arbitrary starting distribution $q$ (meaning $\textrm{supp}(q) \subseteq V$ and $\sum_{u \in V}q(u) = 1$), and for $t \geq 0$ an integer, let $q^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $q$.
-Consider the distance function $h_q^{(t)}, t \geq 0$,
-\begin{equation*}
-h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
-\end{equation*}
-where the maximum is over:
-\begin{align*}
-\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
-\end{align*}
-%$w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$. 
-Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
-
-\vskip 0.1 in
-\begin{remark}
-	$h_q^{(t)}$ permits an equivalent definition. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
-	\begin{equation*}
-	\frac{q^{(m)}(u_1)}{\pi(u_1)} \geq \frac{q^{(m)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q^{(m)}(u_N)}{\pi(u_N)}
-	\end{equation*}
-	and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that,
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_curve}
-	h_q^{(t)}(x) = \sum_{j = 1}^{k - 1} (q^{(m)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q^{(m)}(u_k) - \pi(u_k) \right).
-	\end{equation}
-	where we have used the standard notation $\pi(S) = \sum_{u \in S} \pi(u)$. 
-	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}, a concave, piecewise linear curve.
-\end{remark}
-
-\paragraph{Mixing over large sets}
-
-For $0 \leq \mu \leq 1$ and $\mu \leq x \leq 1 - \mu$ let 
-\begin{equation*}
-\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(1 - \mu)
-\end{equation*}
-be the linear interpolator between $h_q^{(0)}(\mu)$ and $h_q^{(0)}(1 - \mu)$.
-
-\begin{lemma}
-	\label{lem: lt_ub}
-	For any $0 \leq \mu \leq 1/2$ and $\mu \leq x \leq 1 - \mu$ and $t \geq 0$, 
-	\begin{equation*}
-	h_q^{(t)}(x) \leq \ell_{\mu}(x) + \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 }\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation*}
-\end{lemma}
-
-Theorem \ref{lem: lt_ub} is a direct consequence of Theorem 1.2 of \cite{lovasz1990}. To state the latter, we introduce
-\begin{equation*}
-C_{\mu} = \max \set{\frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu}
-\end{equation*}
-\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
-	\label{thm: lovasz_simonovits_1993}
-	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
-	\begin{equation*}
-	h_q^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation*}
-\end{theorem}
-
-\begin{proof}[Proof of Lemma \ref{lem: lt_ub}]
-	Fix $0 \leq \mu \leq \frac{1}{2}$. We will show that for all $\mu \leq x \leq 1 - \mu$
-	\begin{equation}
-	\label{eqn: lt_ub_1}
-	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
-	\end{equation}
-	whence the claim follows by Theorem \ref{thm: lovasz_simonovits_1993}.
-
-	We observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_slope}
-	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}.
-	\end{equation}
-
-	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
-	\begin{equation*}
-	h_q^{(0)}(x) \leq h_q^{(0)}(\mu) + (x - \mu)\frac{h_q^{(0)}(\mu)}{\mu}
-	\end{equation*}
-	by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
-	\begin{align*}
-	h_q^{(0)}(x) - \ell_{\mu}(x) & \leq h_q^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu)\right) + \frac{h_q^{(0)}(\mu)}{\mu}(x - \mu) \\
-	& =  \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(\mu) + \frac{h_q^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu) \\
-	& \leq \sqrt{x - \mu} \left(\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} \right)
-	\end{align*}
-	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
-	\begin{equation*}
-	h_q^{(0)}(x) \leq h_q^{(0)}(1 - \mu) + (1 - x - \mu).
-	\end{equation*}
-	Similar manipulations to above give the upper bound
-	\begin{align*}
-	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
-	\end{align*}
-	and \eqref{eqn: lt_ub_1} follows.
-\end{proof}
-
-\paragraph{Mixing over small sets.}
-
-\begin{lemma}
-	\label{lem: mixing_time_small_sets}
-	Let $0 \leq a \leq 1$, and $t \geq 1$ an integer. Then for any $x \leq as(G)$ or $x \geq 1 - as(G)$,
-	\begin{equation*}
-	h_v^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_1}
-	h_v^{(t)}(x) \leq q_v^{(m)}(U_{k - 1}) + q_v^{(m)}(u_k)
-	\end{equation}
-
-	We will rely on the key fact that for any $u \neq v, t \geq 1$,
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_2}
-	q_v^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
-	\end{equation}
-
-	On the other hand if $u = v$,
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_3}
-	q_v^{(m)}(u) \leq \frac{1}{2^t} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
-	\end{equation}
-	Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
-	\begin{equation*}
-	h_v^{(t)}(x) \leq \frac{1}{2^t} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
-	\end{equation*}
-	Since $x \leq a s(G)$, 
-	\begin{equation*}
-	\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
-	\end{equation*}
-
-	For any $0 \leq b \leq 1$, $x \geq 1 - b$ implies $h_v^{(t)}(x) \leq b$. Taking $b = a s(G)$, the claim is shown.
-\end{proof}
-
-\paragraph{Proof of Proposition \ref{prop: tv_mixing_time}.}
-For any $S \subseteq V$ and any integer $t \geq 0$,
-\begin{equation*}
-\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation*}
-and taking the maximum over all $S \subseteq V$ on both sides, we have
-\begin{equation*}
-\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}.
-\end{equation*}
-
-Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_q^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Lemma \ref{lem: lt_ub},
-\begin{align*}
-h_v^{(t + 3)}(x) & = h_q^{(t)}(x) \\
-& \leq \max \set{h_q^{(0)}(\mu), h_q^{(0)}(1 - \mu) }  + \left(\frac{1}{1 - 2 \mu} + \frac{1}{2\mu}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t\\
-& \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2a s(G)} + \frac{1}{2 a s(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{align*}
-where the last inequality comes from application of Lemma \ref{lem: mixing_time_small_sets} to $h_q^{(t)} = h_v^{(t + 3)}$.
-
-For $x \leq \mu$ or $x \geq 1 - \mu$, again by Lemma \ref{lem: mixing_time_small_sets},
-\begin{equation*}
-h_v^{(t + 3)}(x) \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}}
-\end{equation*}
-and the proof is complete.
 

### 2019-06-20 neurips/local_spectral_density_clustering_arxiv.tex
fixed one typo

@@
 
-To do so, we split the interval $[0,1]$--based on a number $\mu = as(G)$ for some $0 < a < 1$ to be specified later--into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$.
+To do so, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$, where $\mu = as(G)$.
 Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates

--- 2019-06-20 neurips/local_spectral_density_clustering_arxiv.tex
@@
 \setlength{\evensidemargin}{0.5cm}
+\renewcommand{\floatpagefraction}{.8}%
 
@@
 
-\section{Estimation of well-conditioned density clusters}
+\section{Main Results}
 \label{sec: consistent_cluster_estimation_with_ppr}
-
-We formalize some geometric conditions, and use these to define a condition
+In this section we present our main results on the accuracy of the PPR algorithm 
+for recovering density clusters. 
+We begin by formally introducing a variety of geometric conditions, 
+and use these to define a condition
 number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
-of $\kappa(\Cset)$.)
-
-\paragraph{Geometric conditions on density clusters.} At a high level, for PPR
+estimating a density cluster $\Cset$.
+With this condition in place 
+our first main result (Theorem~\ref{thm: misclassification_rate}) provides a bound
+on the symmetric set difference between the estimated cluster $\Cest$,
+obtained by an appropriately initialized version of the PPR algorithm,
+and
+the target cluster $\Cset$.
+Our next main result (Theorem~\ref{thm: consistent_recovery_of_density_clusters})
+shows that for sufficiently well-conditioned target clusters $\Cset$, the output 
+of the PPR algorithm $\Cest$
+is consistent in the sense defined in Definition~\ref{def: consistent_density_cluster_estimation}.
+
+\subsection{Preliminaries}%: Geometric Conditions and the Condition Number of a Density Cluster}
+%We formalize some geometric conditions, and use these to define a condition
+%number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
+%estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
+%of $\kappa(\Cset)$.)
+%\paragraph{Geometric conditions on density clusters.} 
+At a high level, for PPR
 to be successful, the underlying density cluster must be geometrically
-well-conditioned.  At a minimum, we want to avoid sets that contain arbitrarily
-thin bridges or spikes.  Hence, as in \citet{chaudhuri2010}, we consider a
+well-conditioned.  A basic requirement is that we need to avoid clusters which contain arbitrarily
+thin bridges or spikes. As in the work of \citet{chaudhuri2010}, we consider a
 thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
@@
   $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-  $\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}$.
+  \begin{align*}
+  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}. 
+  \end{align*}
+  Roughly, 
+  this assumption ensures that the density decays sufficiently quickly as we move away from
+  the target cluster $\Csig$, and is a standard assumption in the level-set estimation literature
+  (see for instance~\cite{singh2009}).
 
@@
   \emph{Lipschitz embedding:}
-  There exists $g: \Reals^d \to \Reals^d$ with the following properties: i)
-  we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
+  There exists $g: \Reals^d \to \Reals^d$ with the following properties: 
+  \begin{enumerate}
+  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
   with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =:
-  \diam < \infty$; ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
-  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; and iii) for some $L
+  \diam < \infty$
+  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
+  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$ and
+  \item for some $L
   \geq 1$,   
@@
   \end{equation*}
-  Succintly, $\Csig$ is the image of a convex set with finite diameter 
+  \end{enumerate}
+  Succinctly, we assume that $\Csig$ is the image of a convex set with finite diameter 
   under a  measure preserving, bi-Lipschitz transformation.
@@
   \emph{Bounded volume:}
-  Let the neighborhood graph radius $0 < r \leq \sigma/2d$ be such that
+  We assume that neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
   \begin{equation*}
@@
 \end{enumerate}
-
-To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
+To motivate these conditions, we provide a brief high-level sketch
+of our analysis (we return to this more formally in Section~\ref{sec: analysis}).
+\citet{zhu2013} show for an arbitrary graph $G =
 (V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
@@
 where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
-  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
+  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is  the \emph{mixing
   time} of a random walk over the induced subgraph $G[S]$ (to be defined
@@
 form of the symmetric set difference metric in \eqref{eqn:
-  misclassification_rate}.  As we will show in Section \ref{sec:
+  misclassification_rate}, and our main goal will be to upper bound 
+  this quantity. 
+  Towards this goal, as we will show in Section \ref{sec:
   analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
@@
 \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.\footnote{Informally, assumptions  
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. In more detail, assumptions  
 \ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
@@
 with the upper bound on diameter in \ref{asmp: embedding}, this leads to an upper bound on
-the mixing time over this subgraph.}
-
-\paragraph{Condition number.} Motivated by \eqref{eqn:
+the mixing time over this subgraph.
+
+\subsubsection{Condition number} 
+Motivated by \eqref{eqn:
   graph_symmetric_set_difference_1}, we will define $\kappa(\Cset)$ to be an
 upper bound on the product \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
-  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. The smaller $\kappa(\Cset)$ is, the
-more success PPR will have in recovering $\Cset$. Let $\theta := (r, \sigma,
+  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Following, the analysis of \citet{zhu2013}
+  we see that the smaller $\kappa(\Cset)$ is, the
+more success PPR will have in recovering the target cluster $\Cset$. We let $\theta := (r, \sigma,
 \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain the
-geometric parameters from \ref{asmp:  bounded_density}--\ref{asmp:
+geometric parameters from Assumptions~\ref{asmp:  bounded_density}--\ref{asmp:
   bounded_volume}.
@@
 \end{definition}
-
-We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
+\noindent The condition number 
+$\kappa(\Cset)$ succinctly captures the role of the various
+geometric parameters. 
+We note in passing that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
 on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
@@
 
-\paragraph{Well-initialized algorithm.} As is typical in the local clustering
+\subsubsection{Well-initialized algorithm} As is typical in the local clustering
 literature, our algorithmic results will be stated with respect to specific
@@
 well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
-require 
+require that the tuning parameters of Algorithm~\ref{alg: ppr} are chosen as
 \begin{equation}
@@
 (``good'') subset of $\Csig[\Xbf]$. In particular, abbreviating $\vol_{n,r}(S)
-:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we will have
-\smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$}.
+:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, this good subset has large volume, i.e. 
+$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$.
 
@@
 \end{definition}
-
-In practice it is clearly not feasible to set hyperparameters based on the
+\noindent In practice it is  not feasible to set hyperparameters based on the
 underlying (unknown) density $f$. Typically, one tunes PPR over a range of
-hyperparameters and optimizes for some criterion such as minimum normalized cut;
-it is not obvious how this scheme would affect the performance of PPR in the
-density clustering context.
-
-\paragraph{Main theorems.} The results of Section \ref{sec: analysis}, combined 
+hyperparameters and selects the cluster which has the smallest normalized cut. 
+%it is not obvious how this scheme would affect the performance of PPR in the
+%density clustering context.
+
+\subsection{Cluster Recovery in Symmetric Set Difference}
+The results of Section \ref{sec: analysis}, combined 
 with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
@@
 \end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
+To translate the guarantee in~\eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
 on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
@@
 \end{enumerate}
-Note that the latter condition in \ref{asmp: valid_region} will hold if the
+We note that the latter condition in \ref{asmp: valid_region} will hold if the
 boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
-main bound on the symmetric set difference metric.
-
+first main result: a bound on the symmetric set difference metric.
 \begin{theorem}
@@
 \end{theorem}
-
-The proof of Theorem \ref{thm: misclassification_rate}, along with all other
-proofs in this paper, is deferred to the appendix. Note that this 
-result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
-  \Cest)$} is proportional to the difficulty of the clustering problem, as
+The proof of Theorem \ref{thm: misclassification_rate} is deferred to Appendix~\ref{sec: proof_of_misclassification_rate}.
+This result shows that the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
+  \Cest)$} is upper-bounded by a quantity proportional to the difficulty of the clustering problem, as
 measured by the condition number $\kappa(\Cset)$.
 
+\subsection{Consistent Cluster Recovery}
 Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
@@
 changed this $\epsilon$ to $\varepsilon$.}
-\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
+
+\subsection{Approximate PPR vector} 
+In practice, exactly solving \eqref{eqn:
   ppr_vector} may be too computationally expensive. To address this limitation,
@@
 
-\section{Analysis}
+\section{Analysis Overview}
 \label{sec: analysis}

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates -- almost done with main text

@@
 \end{theorem}
-
-\begin{remark}
-  We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
+\noindent Some remarks are in order: 
+ \begin{enumerate}  
+ \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
     kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
@@
   fraction of points will be misclassified. This strong condition is the price
-  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
-\end{remark}
-
-\begin{remark}
-  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
-  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
+  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
+ \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
+  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
   attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
@@
   this is merely looseness in our upper bounds.  
-\end{remark}
-
+\end{enumerate}
 \sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
@@
 \subsection{Approximate PPR vector} 
-In practice, exactly solving \eqref{eqn:
-  ppr_vector} may be too computationally expensive. To address this limitation,
+In practice, exactly solving the system of equations~\eqref{eqn:
+  ppr_vector} to compute the PPR vector 
+  may be too computationally expensive. To address this limitation,
 \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
@@
 \end{equation}
-Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
+For a sufficiently small choice of $\varepsilon$, the 
+application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
   misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
@@
 formally state and prove this in Corollary~\ref{cor: appr} in 
-the appendix.
+Appendix~\ref{sec:appr}.
 
@@
 
-\paragraph{Normalized cut.} We start with a finite sample upper bound on the
+\subsection{Upper Bound on the Normalized Cut} 
+We start with a finite sample upper bound on the
 normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
@@
 \end{theorem}
-
-\begin{remark}
-  \label{rmk: diameter}
+\noindent {\bf Remark: } 
 Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
@@
   \ref{sec: experiments}.
-\end{remark}
-
-\paragraph{Mixing time.} For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
+
+\subsection{Upper Bounds on the Mixing Time} 
+For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
 subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
@@
 
-\begin{remark}
+\vspace{0.2cm}
+
+\noindent {\bf Remark: } 
   The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
@@
   for reasonably small values of $L$.
-\end{remark}
 
@@
 appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We do not, however, provide theory to show that our geometric
-conditions are required for successful recovery of a density level set. This
-seems to be supported by our empirical results, and it remains a direction for 
+cluster by PPR. We do not, however, provide theory to show that (some variant of) 
+our geometric
+conditions are \emph{required} for successful recovery of a density level set. This
+seems to be supported by our empirical results, and establishing this necessity
+formally is an important direction for 
 future work.
@@
 
-Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
-	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
-
 \section{Proof of Theorem \ref{thm: misclassification_rate}}
@@
 the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
-
-\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
-
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
 
@@
 
-\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
+\subsection{The Approximate PPR Vector}
+\label{sec:appr}
+Before we proceed to the next section, we include a formal statement of our claims regarding the a\pprspace vector. 
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+	\begin{enumerate}
+		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
+\end{corollary}
+\begin{proof}
+The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
+All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
+
+%\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
 
@@
 \end{equation*}
-
 On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+
+\end{proof}
 
@@
 	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
+	\end{align*}
+	\begin{align*}
 	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates -- updates to proof of Thm 1

@@
 
-\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
+\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}:}
 
@@
 \label{sec: proof_of_misclassification_rate}
-In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
-
-Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
-\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+In this section, we prove both Theorem \ref{thm: misclassification_rate}.
+The result is in essence a consequence of the bounds in Theorem~\ref{thm: conductance_upper_bound} 
+and Theorem~\ref{thm: mixing_time_upper_bound} bounding the normalized cut and mixing time, together with the result of \citet{zhu2013} relating the quality of the PPR output to these quantities, and the result in Lemma~\ref{lem: ball_bounds_in_probability}
+that allows us to translate the guarantees on the volume to guarantees on the symmetric set difference.
+
+% and the relevant portions of Corollary \ref{cor: appr}.
+We begin with Lemma \ref{lem: zhu}, which is a restatement of Lemma 3.4 of \citet{zhu2013}, translated into notation consistent with the rest of this paper.
+It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
 
@@
 \end{lemma}
-
-\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
-
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
+%\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
+With this Lemma in place we
+observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
 Moreover,
-\begin{enumerate}[\text{(i)}]
+\begin{enumerate}
 	\item we restrict $v \in \Csig[\Xbf]^g$
-	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$
+	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$, for some $1/40 < \beta < 1/11$
 	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
@@
 \end{align*}
-the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
+the theorem follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
 
@@
 	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.
-
 	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates -- updates to proof of Thm 2

@@
 \newcommand{\ebf}[1]{{e}_{#1}}
-\newcommand{\pibf}{\bm{\pi}}
+\newcommand{\pibf}{\pi}
 
@@
   attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
-  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
+  $\kappa(\Cset)$ prevents us from making claims about the
   behavior of PPR in this regime. Although the restriction to a kernel
@@
 
-\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-~
+%\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
+%~
 
 In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
-
 Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
very minor updates
halfway through conductance lower bound reorganization

--- 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
@@
 \setlength{\evensidemargin}{0.5cm}
-\renewcommand{\floatpagefraction}{.8}%
 
@@
 
-\section{Main Results}
+\section{Estimation of well-conditioned density clusters}
 \label{sec: consistent_cluster_estimation_with_ppr}
-In this section we present our main results on the accuracy of the PPR algorithm 
-for recovering density clusters. 
-We begin by formally introducing a variety of geometric conditions, 
-and use these to define a condition
+
+We formalize some geometric conditions, and use these to define a condition
 number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-estimating a density cluster $\Cset$.
-With this condition in place 
-our first main result (Theorem~\ref{thm: misclassification_rate}) provides a bound
-on the symmetric set difference between the estimated cluster $\Cest$,
-obtained by an appropriately initialized version of the PPR algorithm,
-and
-the target cluster $\Cset$.
-Our next main result (Theorem~\ref{thm: consistent_recovery_of_density_clusters})
-shows that for sufficiently well-conditioned target clusters $\Cset$, the output 
-of the PPR algorithm $\Cest$
-is consistent in the sense defined in Definition~\ref{def: consistent_density_cluster_estimation}.
-
-\subsection{Preliminaries}%: Geometric Conditions and the Condition Number of a Density Cluster}
-%We formalize some geometric conditions, and use these to define a condition
-%number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-%estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
-%of $\kappa(\Cset)$.)
-%\paragraph{Geometric conditions on density clusters.} 
-At a high level, for PPR
+estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
+of $\kappa(\Cset)$.)
+
+\paragraph{Geometric conditions on density clusters.} At a high level, for PPR
 to be successful, the underlying density cluster must be geometrically
-well-conditioned.  A basic requirement is that we need to avoid clusters which contain arbitrarily
-thin bridges or spikes. As in the work of \citet{chaudhuri2010}, we consider a
+well-conditioned.  At a minimum, we want to avoid sets that contain arbitrarily
+thin bridges or spikes.  Hence, as in \citet{chaudhuri2010}, we consider a
 thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
@@
   $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-  \begin{align*}
-  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}. 
-  \end{align*}
-  Roughly, 
-  this assumption ensures that the density decays sufficiently quickly as we move away from
-  the target cluster $\Csig$, and is a standard assumption in the level-set estimation literature
-  (see for instance~\cite{singh2009}).
+  $\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}$.
 
@@
   \emph{Lipschitz embedding:}
-  There exists $g: \Reals^d \to \Reals^d$ with the following properties: 
-  \begin{enumerate}
-  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
+  There exists $g: \Reals^d \to \Reals^d$ with the following properties: i)
+  we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
   with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =:
-  \diam < \infty$
-  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
-  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$ and
-  \item for some $L
+  \diam < \infty$; ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
+  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; and iii) for some $L
   \geq 1$,   
@@
   \end{equation*}
-  \end{enumerate}
-  Succinctly, we assume that $\Csig$ is the image of a convex set with finite diameter 
+  Succintly, $\Csig$ is the image of a convex set with finite diameter 
   under a  measure preserving, bi-Lipschitz transformation.
@@
   \emph{Bounded volume:}
-  We assume that neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
+  Let the neighborhood graph radius $0 < r \leq \sigma/2d$ be such that
   \begin{equation*}
@@
 \end{enumerate}
-To motivate these conditions, we provide a brief high-level sketch
-of our analysis (we return to this more formally in Section~\ref{sec: analysis}).
-\citet{zhu2013} show for an arbitrary graph $G =
+
+To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
 (V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
@@
 where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
-  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is  the \emph{mixing
+  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
   time} of a random walk over the induced subgraph $G[S]$ (to be defined
@@
 form of the symmetric set difference metric in \eqref{eqn:
-  misclassification_rate}, and our main goal will be to upper bound 
-  this quantity. 
-  Towards this goal, as we will show in Section \ref{sec:
+  misclassification_rate}.  As we will show in Section \ref{sec:
   analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
@@
 \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. In more detail, assumptions  
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.\footnote{Informally, assumptions  
 \ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
@@
 with the upper bound on diameter in \ref{asmp: embedding}, this leads to an upper bound on
-the mixing time over this subgraph.
-
-\subsubsection{Condition number} 
-Motivated by \eqref{eqn:
+the mixing time over this subgraph.}
+
+\paragraph{Condition number.} Motivated by \eqref{eqn:
   graph_symmetric_set_difference_1}, we will define $\kappa(\Cset)$ to be an
 upper bound on the product \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
-  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Following, the analysis of \citet{zhu2013}
-  we see that the smaller $\kappa(\Cset)$ is, the
-more success PPR will have in recovering the target cluster $\Cset$. We let $\theta := (r, \sigma,
+  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. The smaller $\kappa(\Cset)$ is, the
+more success PPR will have in recovering $\Cset$. Let $\theta := (r, \sigma,
 \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain the
-geometric parameters from Assumptions~\ref{asmp:  bounded_density}--\ref{asmp:
+geometric parameters from \ref{asmp:  bounded_density}--\ref{asmp:
   bounded_volume}.
@@
 \end{definition}
-\noindent The condition number 
-$\kappa(\Cset)$ succinctly captures the role of the various
-geometric parameters. 
-We note in passing that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
+
+We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
 on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
@@
 
-\subsubsection{Well-initialized algorithm} As is typical in the local clustering
+\paragraph{Well-initialized algorithm.} As is typical in the local clustering
 literature, our algorithmic results will be stated with respect to specific
@@
 well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
-require that the tuning parameters of Algorithm~\ref{alg: ppr} are chosen as
+require 
 \begin{equation}
@@
 (``good'') subset of $\Csig[\Xbf]$. In particular, abbreviating $\vol_{n,r}(S)
-:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, this good subset has large volume, i.e. 
-$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$.
+:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we will have
+\smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$}.
 
@@
 \end{definition}
-\noindent In practice it is  not feasible to set hyperparameters based on the
+
+In practice it is clearly not feasible to set hyperparameters based on the
 underlying (unknown) density $f$. Typically, one tunes PPR over a range of
-hyperparameters and selects the cluster which has the smallest normalized cut. 
-%it is not obvious how this scheme would affect the performance of PPR in the
-%density clustering context.
-
-\subsection{Cluster Recovery in Symmetric Set Difference}
-The results of Section \ref{sec: analysis}, combined 
+hyperparameters and optimizes for some criterion such as minimum normalized cut;
+it is not obvious how this scheme would affect the performance of PPR in the
+density clustering context.
+
+\paragraph{Main theorems.} The results of Section \ref{sec: analysis}, combined 
 with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
@@
 \end{equation}
-To translate the guarantee in~\eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
+To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
 on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
@@
 \end{enumerate}
-We note that the latter condition in \ref{asmp: valid_region} will hold if the
+Note that the latter condition in \ref{asmp: valid_region} will hold if the
 boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
-first main result: a bound on the symmetric set difference metric.
+main bound on the symmetric set difference metric.
+
 \begin{theorem}
@@
 \end{theorem}
-The proof of Theorem \ref{thm: misclassification_rate} is deferred to Appendix~\ref{sec: proof_of_misclassification_rate}.
-This result shows that the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
-  \Cest)$} is upper-bounded by a quantity proportional to the difficulty of the clustering problem, as
+
+The proof of Theorem \ref{thm: misclassification_rate}, along with all other
+proofs in this paper, is deferred to the appendix. Note that this 
+result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
+  \Cest)$} is proportional to the difficulty of the clustering problem, as
 measured by the condition number $\kappa(\Cset)$.
 
-\subsection{Consistent Cluster Recovery}
 Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
@@
 \end{theorem}
-\noindent Some remarks are in order: 
- \begin{enumerate}  
- \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
+
+\begin{remark}
+  We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
     kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
@@
   fraction of points will be misclassified. This strong condition is the price
-  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
- \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
-  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
+  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
+\end{remark}
+
+\begin{remark}
+  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
+  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
   attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
@@
   this is merely looseness in our upper bounds.  
-\end{enumerate}
+\end{remark}
+
 \sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
 changed this $\epsilon$ to $\varepsilon$.} 
-
-\subsection{Approximate PPR vector} 
-In practice, exactly solving the system of equations~\eqref{eqn:
-  ppr_vector} to compute the PPR vector 
-  may be too computationally expensive. To address this limitation,
+\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
+  ppr_vector} may be too computationally expensive. To address this limitation,
 \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
@@
 \end{equation}
-For a sufficiently small choice of $\varepsilon$, the 
-application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
+Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
   misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
@@
 formally state and prove this in Corollary~\ref{cor: appr} in 
-Appendix~\ref{sec:appr}.
-
-\section{Analysis Overview}
+the appendix.
+
+\section{Analysis}
 \label{sec: analysis}
@@
 
-\subsection{Upper Bound on the Normalized Cut} 
-We start with a finite sample upper bound on the
+\paragraph{Normalized cut.} We start with a finite sample upper bound on the
 normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
@@
 \end{theorem}
-\noindent {\bf Remark: } 
+
+\begin{remark}
+  \label{rmk: diameter}
   Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
@@
   \ref{sec: experiments}. 
-
-\subsection{Upper Bounds on the Mixing Time} 
-For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
+\end{remark}
+
+\paragraph{Mixing time.} For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
 subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
@@
 
-\vspace{0.2cm}
-
-\noindent {\bf Remark: } 
+\begin{remark}
   The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
@@
   for reasonably small values of $L$. 
+\end{remark}
 
@@
 appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We do not, however, provide theory to show that (some variant of) 
-our geometric
-conditions are \emph{required} for successful recovery of a density level set. This
-seems to be supported by our empirical results, and establishing this necessity
-formally is an important direction for 
+cluster by PPR. We do not, however, provide theory to show that our geometric
+conditions are required for successful recovery of a density level set. This
+seems to be supported by our empirical results, and it remains a direction for 
 future work.
@@
 
-\subsection{Mixing time on graphs}
-\label{sec: mixing_time_on_graphs}
-
-We generalize some notation from the main text.
-For an undirected graph $G = (V,E)$, the lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
-Denote the $m$-step probability distribution of this random walk originating from a particular $v \in V$ as $q^{(m)}: V \times V \to [0,1]$, $q^{(m)}(v,u) = e_v \Wbf^m e_u$.
-An important intermediate quantity used to bound the relative pointwise mixing time $\tau_{\infty}(G)$ is the total variation distance between the distributions $q_v^{(m)} := q^{(m)}(v,\cdot)$ and $\pi$,
-\begin{equation*}
-\norm{q_v^{(m)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(m)}(u) - \pi(u)}
-\end{equation*}
-We recall the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well. For $u \in V$, $S \subseteq V$, 
-\begin{equation*}
-\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G)
-\end{equation*}
-
-The \emph{local spread} is defined as
-\begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}
-\end{equation*}
-
-Recalling the \emph{normalized cut} $\Phi(S;G)$ is defined (as in \eqref{eqn: normalized_cut}) as
-\begin{equation*}
-\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}},
-\end{equation*}
-we refer to the minimum normalized cut over $V$ as the \emph{conductance},
-\begin{equation*}
-\Phi(G) := \min_{S \subseteq V} \Phi(S;G).
-\end{equation*}
-
-Proposition \ref{prop: tv_mixing_time} relates these geometric quantities to the TV distance between $q_v^{(t)}$ and stationary distribution $\pi$.
-\sbcomment{Added $\max$ to the RHS.}
+Denote $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
+The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that, for universal constants $c_2, c_3,c_4 > 0$, with probability one
+\begin{equation*}
+\limsup_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{c_4 \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
+\end{equation*}
+We follow a two-step approach typically used to establish upper bounds on the mixing time of Markov chains.
+
+In the first step, we relate the mixing time $\tau_{\infty}(G)$ of a generic undirected graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
+We now build to a formal definition of these expansion properties.
+First, we recall the the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well.
+For $u \in V$, $S \subseteq V$,
+\begin{equation*}
+\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G).
+\end{equation*}
+Additionally, we recall the \emph{normalized cut} $\Phi(S;G)$, defined (as in \eqref{eqn: normalized_cut}) as
+\begin{equation*}
+\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}}.
+\end{equation*}
+
+With these functionals in hand, we can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
+\begin{equation*}
+s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
+\end{equation*}
+
+The following Proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
 \begin{proposition}
-	\label{prop: tv_mixing_time}
+	\label{prop: pointwise_mixing_time}
+	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
+	\begin{equation*}
+	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+	\end{equation*}
+\end{proposition}
+
+The second step in our approach is to lower bound the local spread and conductance over the particular graph $\widetilde{G}_{n,r}$.
+The following result provides the desired lower bounds, which hold asymptotically as $n \to \infty$,
+\begin{proposition}
+	\label{prop: local_spread_conductance}
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one,
+	\begin{equation}
+	\label{eqn: local_spread}
+	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
+	\end{equation}
+	and
+	\begin{equation}
+	\label{eqn: conductance}
+	\liminf_{n \to \infty} \Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+	\end{equation}
+\end{proposition}
+
+Taking these results as given, the proof of the theorem is more or less complete.
+We note that since $r$ is fixed, \textcolor{red}{with probability one} $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty > 10$, and we may therefore apply Proposition \ref{prop: pointwise_mixing_time} with respect to $\widetilde{G}_{n,r}$.
+Along with Lemma \ref{prop: local_spread_conductance}, this yields
+\begin{equation*}
+\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
+\end{equation*}
+The first term dominates the middle term, and the theorem follows after an appropriate choice of $c_2$ and $c_3$.
+
+\subsection{Proof of Proposition \ref{prop: pointwise_mixing_time}}
+\label{sec: pointwise_mixing_time}
+
+We first generalize some notation from the main text.
+Let $A$ be the adjacency matrix of an undirected graph $G = (V,E)$, and $D$ the associated diagonal degree matrix.
+The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
+Denote the $t$-step probability distribution of this random walk, originating from a particular $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
+
+Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
+\begin{equation*}
+d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
+\end{equation*}
+Our goal is to demonstrate that for sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$.
+To do so, we introduce the \emph{total variation distance} between the distributions $q_v^{(t)}$ and $\pi$, given by
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(t)}(u) - \pi(u)}.
+\end{equation*}
+As we will see, an upper bound on the uniform distance can be obtained from an analogous upper bound on the total variation distance.
+First, however, we upper bound the total variation distance $||q_v^{(t)} - \pi||_{\mathrm{TV}}$ as a function of the local spread $s(G)$, the conductance $\Phi(G)$ and the number of steps $t$.
+\begin{lemma}
+	\label{lem: tv_mixing_time}
 	For any $v \in V$, and any $0 < a \leq 1$,
@@
 \end{lemma}
-\begin{proof}
-	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
+
+\noindent Taking these Lemmas as given, we proceed that show that for
+\begin{equation*}
+\tau_1 = \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+\end{equation*}
+the uniform distance $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$, which proves the claim of Proposition \ref{prop: pointwise_mixing_time}.
+Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$.
+Then,
+\begin{equation*}
+\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
+\end{equation*}
+and so by Lemma \ref{lem: tv_mixing_time},
+\begin{equation*}
+\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+\end{equation*}
+It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
+Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
+\begin{equation*}
+\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
+\end{equation*}
+and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$.
+The proof is complete once we have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}.
+
+\subsection{Proof of Lemma \ref{lem: tv_mixing_time}}
+\label{sec: mixing_time_on_graphs}
+
+We generalize the notation of the previous subsection.
+For a starting distribution $z$ to be specified later, and for $t \geq 0$ an integer, let $q_z^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $z$.\footnote{We say $z$ is a starting distribution over a graph $G$ when $\textrm{supp}(z) \subseteq V$ and $\sum_{u \in V}z(u) = 1$.
+Then, $q_z^{(t)} = zW^t$.}
+
+We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined as
+$h_z^{(t)}, t \geq 0$, 
+\begin{equation*}
+h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}
+\end{equation*}
+where the maximum is over:
+\begin{align*}
+\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
+\end{align*}
+The utility of the Lovasz-Simonovits curve is demonstrated by the following observations. First, note that
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sup_{S \subseteq V} \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation*}
+where we use the standard notation $\pi(S) := \sum_{u \in S} \pi(u)$, and likewise for $q_v^{(t)}(S)$. Moreover, observe that for any $S \subseteq V$ and any integer $t \geq 0$,
+\begin{equation}
+\label{eqn: lovasz_simonivits_1}
+\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
+\end{equation}
+Therefore, taking the maximum on both sides of \eqref{eqn: lovasz_simonivits_1}  over all $S \subseteq V$, we have
+\begin{equation*}
+\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \max_{0 \leq x \leq 1} h_v^{(t)}(x).
+\end{equation*}
+Now, take $z = e_vW^3$.
+Observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
+To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$.
+
+To show this upper bound, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$, where $\mu = as(G)$.
+Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,
+\begin{equation*}
+\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
+\end{equation*}
+
+The following technical Lemma collects the upper bounds which hold over $[\mu, 1 - \mu]$ and $[0,\mu) \cup (1 - \mu, 1]$, respectively:
+\begin{lemma}
+	\label{lem: mixing_all_sets}
+	For any $\mu \leq x \leq 1 - \mu$, 
+	\begin{equation}
+	\label{eqn: mixing_large_sets}
+	h_z^{(t)}(x) \leq \ell_{\mu}(x) + \left(\frac{1}{1 - 2\mu} + \frac{1}{\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t.
+	\end{equation}
+	For any $0 < x \leq \mu$ or $1 - \mu \leq x < 1$
+	\begin{equation}
+	\label{eqn: mixing_small_sets}
+	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+	\end{equation}
+\end{lemma}
+\noindent Taking Lemma \ref{lem: mixing_all_sets} as given, we have nearly completed our proof of Lemma \ref{lem: tv_mixing_time}. Note that for any $\mu \leq x \leq 1 - \mu$,
+\begin{align*}
+\ell_{\mu}(x) & \leq \max\set{h_z^{(t)}(\mu),h_z^{(t)}(1 - \mu)} \\
+& \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+\end{align*}
+with the latter inequality following from \eqref{eqn: mixing_small_sets}. Therefore, for any $x \in [0,1]$,
+\begin{equation*}
+h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{equation*}
+which is the desired result.
+
+\subsection{Proof of Lemma \ref{lem: mixing_all_sets}}
+
+We first prove \eqref{eqn: mixing_large_sets}, and then \eqref{eqn: mixing_small_sets}.
+\paragraph{Proof of \eqref{eqn: mixing_large_sets}:}
+The desired result is a consequence of Theorem 1.2 of \cite{lovasz1990}. To state this theorem, we introduce the notation
+\begin{equation*}
+C_{\mu} = \max \set{\frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu},
+\end{equation*}
+and then the theorem itself.
+\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
+	\label{thm: lovasz_simonovits_1993}
+	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
+	\begin{equation}
+	\label{eqn: lovasz_simonovits_1993}
+	h_z^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
+	\end{equation}
+\end{theorem}
+In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show
+\begin{equation}
+\label{eqn: lt_ub_1}
+h_z^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
+\end{equation}
+which will in turn imply
+\begin{align*}
+C_{\mu} & \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \\
+& \leq \frac{1}{\mu} + \frac{1}{1 - 2\mu}.
+\end{align*}
+Plugging this upper bound into \eqref{eqn: lovasz_simonovits_1993}, we obtain
+\begin{align*}
+h_z^{(t)}(x) & \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t \\
+& \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{align*}
+which is the desired result.
+
+It remains to show \eqref{eqn: lt_ub_1}.
+To do so, we make use of an equivalent representation of the Lovasz-Simonovits curve $h_z^{(t)}$.
+Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
+\begin{equation*}
+\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)}
+\end{equation*}
+and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
+\begin{equation}
+\label{eqn: lovasz_simonovits_curve}
+h_z^{(t)}(x) = \sum_{j = 1}^{k - 1} (q_z^{(t)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q_z^{(t)}(u_k) - \pi(u_k) \right).
+\end{equation}
+The representation of the Lovasz-Simonovits curve given by \eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a concave, piecewise linear curve.
+Moreover, we observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
+\begin{equation}
+\label{eqn: lovasz_simonovits_slope}
+-1 \leq v(x) \leq \frac{h_z^{(0)}(\mu)}{\mu}.
+\end{equation}
+Note that $\ell_{\mu}(\mu) = h_z^{(0)}(\mu)$, and for $x \geq \mu$, 
+\begin{equation*}
+h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}
+\end{equation*}
+by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
+\begin{align*}
+h_z^{(0)}(x) - \ell_{\mu}(x) & \leq h_z^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu)\right) + \frac{h_z^{(0)}(\mu)}{\mu}(x - \mu) \\
+& =  \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(\mu) + \frac{h_z^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu) \\
+& \leq \sqrt{x - \mu} \left(\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} \right)
+\end{align*}
+On the other hand, $\ell_{\mu}(1 - \mu) = h_z^{(0)}(1 - \mu)$, and by the concavity of $h_z^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
+\begin{equation*}
+h_z^{(0)}(x) \leq h_z^{(0)}(1 - \mu) + (1 - x - \mu).
+\end{equation*}
+Similar manipulations to above give the upper bound
+\begin{align*}
+h_z^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
+\end{align*}
+and \eqref{eqn: lt_ub_1} follows.
+
+\paragraph{Proof of \eqref{eqn: mixing_small_sets}:}
+First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
+\begin{equation}
+\label{eqn: mixing_time_small_sets_1}
+h_z^{(t)}(x) \leq q_z^{(t)}(U_{k - 1}) + q_z^{(t)}(u_k)
+\end{equation}
+Recalling that $z = e_vW^3$, we will rely on the key fact that for any $u \neq v, t \geq 1$,
+\begin{equation}
+\label{eqn: mixing_time_small_sets_2}
+q_z^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
+\end{equation}
+On the other hand if $u = v$,
+\begin{equation}
+\label{eqn: mixing_time_small_sets_3}
+q_z^{(m)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
+\end{equation}
+Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
+\begin{equation*}
+h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
+\end{equation*}
+Finally, since $x \leq a s(G)$, 
+\begin{equation*}
+\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
+\end{equation*}
+and the desired result is shown.
+
+Now, we turn to the case where $x \geq 1 - as(G)$.
+But since $h_z^{(t)}(1) = 0$, and the slope of $h_z$, $v(x')$ is no less than $-1$ for all $x' \in [0,1]$, this implies $h_z^{(t)}(x) \leq 1 - x \leq as(G)$.
+
+\subsection{Proof of Lemma \ref{lem: tv_to_uniform_distance}}
+
+The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebra. Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
 \begin{align}
@@
 \end{align}
-	where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.
-
-	Then 
+where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$. Then,
 \begin{align}
@@
 since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well known \cite{lovasz1990} that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and hypothesis,
+As $m - 1 \geq t$, it is well known (see e.g.
+\cite{lovasz1990}) that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and the hypothesis of Lemma \ref{lem: tv_to_uniform_distance},
 \begin{equation*}
@@
 \end{equation*}
-
 Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
@@
 \end{equation*}
-	and the claim is shown.
+and the claim is shown. We have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}, and therefore Proposition \ref{prop: pointwise_mixing_time}.
+
+\subsection{Proof of Proposition \ref{prop: local_spread_conductance}}
+
+We first prove \eqref{eqn: local_spread} and then \eqref{eqn: conductance}.
+First, we introduce some notation.
+Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
+For $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
+\begin{equation*}
+\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
+\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
+\end{equation*}
+and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
+We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$.
+
+\paragraph{Proof of \eqref{eqn: local_spread}:}
+
+Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
+Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
+\begin{equation*}
+\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
+\end{equation*}
+
+\paragraph{Proof of \eqref{eqn: conductance}:}
+
+Our goal is to show that with probability one
+\begin{equation*}
+\liminf_{n \to \infty} \min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+\end{equation*}
+where we let $S^c = \Csig[\Xbf] \setminus S$.
+In order to show this bound holds uniformly over all sets $S \subseteq \Csig[\Xbf]$, we will split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
+To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G = (V,E)$.)
+
+Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for sets $S \subseteq \Csig[\Xbf]$ not sufficiently large enough to be in $\mathcal{L}(\widetilde{G}_{n,r})$, the graph normalized cut is of constant order.
+In fact, this statement holds for any graph $G$.
+\begin{lemma}
+	\label{lem: graph_conductance_profile_lb_1}
+	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
+	\begin{equation*}
+	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	The claim follows by simple manipulations:
+	\begin{align*}
+	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
+	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
+	\end{align*}
 \end{proof}
 
-Together, Proposition \ref{prop: tv_mixing_time} and Lemma \ref{lem: tv_to_uniform_distance} imply the main result of this section.
-
-\begin{proposition}
-	\label{prop: pointwise_mixing_time}
-	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
-	\begin{equation*}
-	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-	\end{equation*}
-\end{proposition}
-\begin{proof}
-	Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$. Then,
-	\begin{equation*}
-	\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
-	\end{equation*}
-	and so by Proposition \ref{prop: tv_mixing_time},
-	\begin{equation*}
-	\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-	\end{equation*}
-
-	It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
-Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
-	\begin{equation*}
-	\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
-	\end{equation*}
-	and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$. 
-\end{proof}
-
-\subsection{Proof of Proposition \ref{prop: tv_mixing_time}.}
-\label{sec: proof_of_proposition_tv_mixing_time}
-
-For arbitrary starting distribution $q$ (meaning $\textrm{supp}(q) \subseteq V$ and $\sum_{u \in V}q(u) = 1$), and for $t \geq 0$ an integer, let $q^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $q$.
-Consider the distance function $h_q^{(t)}, t \geq 0$,
-\begin{equation*}
-h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q^{(m)}(u) - \pi(u)\right)w(u)\right\}
-\end{equation*}
-where the maximum is over:
-\begin{align*}
-\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
-\end{align*}
-%$w: V \to [0,1]$ such that $0 \leq w(u) \leq 1$ for all $u$, and $\sum_{u \in V} w(u) \pi(u) = x$. 
-Writing $h_v^{(t)}(x) := h_{e_v}^{(t)}(x)$ in a small abuse of notation, in Lemmas \ref{lem: lt_ub} and \ref{lem: mixing_time_small_sets}, we give an upper bound on $h_{v}^{(t)}(x)$ for all $0 \leq x \leq 1$.
-
-\vskip 0.1 in
-\begin{remark}
-	$h_q^{(t)}$ permits an equivalent definition. Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
-	\begin{equation*}
-	\frac{q^{(m)}(u_1)}{\pi(u_1)} \geq \frac{q^{(m)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q^{(m)}(u_N)}{\pi(u_N)}
-	\end{equation*}
-	and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that,
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_curve}
-	h_q^{(t)}(x) = \sum_{j = 1}^{k - 1} (q^{(m)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q^{(m)}(u_k) - \pi(u_k) \right).
-	\end{equation}
-	where we have used the standard notation $\pi(S) = \sum_{u \in S} \pi(u)$. 
-	The formulation on the right hand side of \eqref{eqn: lovasz_simonovits_curve} has come to be known as the \emph{Lovasz-Simonovits curve}, a concave, piecewise linear curve.
-\end{remark}
-
-\paragraph{Mixing over large sets}
-
-For $0 \leq \mu \leq 1$ and $\mu \leq x \leq 1 - \mu$ let 
-\begin{equation*}
-\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(1 - \mu)
-\end{equation*}
-be the linear interpolator between $h_q^{(0)}(\mu)$ and $h_q^{(0)}(1 - \mu)$.
+In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut for the remaining sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
 
 \begin{lemma}
-	\label{lem: lt_ub}
-	For any $0 \leq \mu \leq 1/2$ and $\mu \leq x \leq 1 - \mu$ and $t \geq 0$, 
-	\begin{equation*}
-	h_q^{(t)}(x) \leq \ell_{\mu}(x) + \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 }\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation*}
-\end{lemma}
-
-Theorem \ref{lem: lt_ub} is a direct consequence of Theorem 1.2 of \cite{lovasz1990}. To state the latter, we introduce
-\begin{equation*}
-C_{\mu} = \max \set{\frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_q^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu}
-\end{equation*}
-\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
-	\label{thm: lovasz_simonovits_1993}
-	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
-	\begin{equation*}
-	h_q^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation*}
+	\label{lem: graph_conductance_profile_lb}
+	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then with probability $1$,
+	\begin{equation}
+	\label{eqn: graph_conductance_profile_lb}
+	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
+	\end{equation}
+	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
+\end{lemma}
+
+Taking Lemma \ref{lem: graph_conductance_profile_lb} as given, Proposition \ref{prop: graph_conductance_profile_lb} then follows from that Lemma, along with Lemma \ref{lem: graph_conductance_profile_lb_1}, in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
+We turn now to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
+
+\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}.}
+
+Let $\Sset \subseteq \Csig$ and $S \subseteq \Csig[\Xbf]$.
+The proof of \ref{lem: graph_conductance_profile_lb} will essentially follow from a pair of technical results.
+The first of these will demonstrate that the functional $\widetilde{\Phi}_{n,r}(S)$ can be lower bounded by a population analogue $\widetilde{\Phi}_{\Pbb,r}(\Sset)$, which we term the continuous normalized cut.
+This lower bound will hold uniformly over sets $S \subseteq \Csig[X]$.
+The second technical Lemma will build on known continuous space isoperimetric inequalities to lower bound the population-level quantity $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ uniformly over sets $\Sset \subseteq \Csig$.
+
+We will now build slowly toward a formal definition of the continuous normalized cut, before establishing a relation between it and it's discrete counterpart.
+Let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
+We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by
+\begin{equation*}
+\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
+\end{equation*}
+
+Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
+\begin{equation*}
+\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
+\end{equation*}
+Letting the \emph{$\Pbb$-local conductance} be given by
+\begin{equation*}
+\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
+\end{equation*}
+a bit of algebra verifies that
+\begin{equation*}
+\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
+\end{equation*}
+
+We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
+\begin{equation*}
+\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
+\end{equation*}
+the \emph{($\Pbb$) continuous normalized cut} by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
+\end{equation*}
+
+As the functionals $\widetilde{\Phi}_{n,r}$ and $\widetilde{\Phi}_{\Pbb,r}$ act in the different spaces $\Csig[\Xbf]$ and $\Csig$, respectively, it is not obvious how to relate them.
+To do so, we introduce transportation maps between the space $\Csig$ and the sample points $\Csig[\Xbf]$.
+Precisely, define the conditional probability measures
+\begin{equation*}
+\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
+\end{equation*} 
+A measurable map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
+\begin{equation*}
+\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
+\end{equation*}
+where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
+The following result lower bounds $\widetilde{\Phi}_{n,r}(S)$ by $\widetilde{\Phi}_{\Pbb,r}(T^{-1}(S))$, plus some perturbation.
+The magnitude of this perturbation, and thus the quality of the bound, will be dictated by the \emph{transportation distance} $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$.
+\begin{lemma}
+	\label{lem: graph_to_continuous_conductance}
+	Let $\seq{T_n}$ be a sequence of transportation maps between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.Then, letting $\Sset =T_n^{-1}(S)$, there exists a constant $c > 0$ fixed in sample size $n$ such that for any $S \in \mathcal{L}(\widetilde{G}_{n,r})$
+	\begin{equation}
+	\label{eqn: graph_to_continuous_conductance}
+	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right)
+	\end{equation}
+\end{lemma}
+
+(We note that hereafter in this section $c$ will represent a constant which may change from line to line, and may depend on the density $f$ and dimension $d$, but not on the sample size $n$).
+As mentioned previously, Lemma \ref{lem: graph_to_continuous_conductance} is useful only in conjunction with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
+Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures compactly supported over open connected domains with Lipschitz boundaries.
+The following result is a restatement of this Proposition with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
+Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
+Let $\widetilde{n} = \abs{\Csig{\Xbf}}$.
+
+\begin{theorem}[Restatement of Proposition 5 of \cite{garciatrillos16}]
+	\label{thm: stagnating_transportation_maps}
+	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
+	\begin{equation}
+	\label{eqn: stagnating_transportation_maps}
+	\limsup_{\widetilde{n} \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq c
+	\end{equation}
+	where $c$ is constant in $n$ and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
 \end{theorem}
 
-\begin{proof}[Proof of Lemma \ref{lem: lt_ub}]
-	Fix $0 \leq \mu \leq \frac{1}{2}$. We will show that for all $\mu \leq x \leq 1 - \mu$
-	\begin{equation}
-	\label{eqn: lt_ub_1}
-	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} , \frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
-	\end{equation}
-	whence the claim follows by Theorem \ref{thm: lovasz_simonovits_1993}.
-
-	We observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_slope}
-	-1 \leq v(x) \leq \frac{h_q^{(0)}(\mu)}{\mu}.
-	\end{equation}
-
-	Note that $\ell_{\mu}(\mu) = h_q^{(0)}(\mu)$, and for $x \geq \mu$, 
-	\begin{equation*}
-	h_q^{(0)}(x) \leq h_q^{(0)}(\mu) + (x - \mu)\frac{h_q^{(0)}(\mu)}{\mu}
-	\end{equation*}
-	by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
-	\begin{align*}
-	h_q^{(0)}(x) - \ell_{\mu}(x) & \leq h_q^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_q^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu)\right) + \frac{h_q^{(0)}(\mu)}{\mu}(x - \mu) \\
-	& =  \frac{x - \mu}{1 - 2\mu}h_q^{(0)}(\mu) + \frac{h_q^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_q^{(0)}(1 - \mu) \\
-	& \leq \sqrt{x - \mu} \left(\frac{h_q^{(0)}(\mu)}{1 - 2\mu} + \frac{h_q^{(0)}(\mu)}{\mu} \right)
-	\end{align*}
-	On the other hand, $\ell_{\mu}(1 - \mu) = h_q^{(0)}(1 - \mu)$, and by the concavity of $h_q^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
-	\begin{equation*}
-	h_q^{(0)}(x) \leq h_q^{(0)}(1 - \mu) + (1 - x - \mu).
-	\end{equation*}
-	Similar manipulations to above give the upper bound
-	\begin{align*}
-	h_q^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_q^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
-	\end{align*}
-	and \eqref{eqn: lt_ub_1} follows.
-\end{proof}
-
-\paragraph{Mixing over small sets.}
-
+The following result then supplies the last step, a uniform lower bound on the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ for all sets $\Sset \subseteq \Csig$.
+Let the \emph{$\Pbb$-(continuous) conductance} be given by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)
+\end{equation*}
+where $\Sset^c = \Csig \setminus \Sset$, and the minimum in the preceding display is taken over measurable sets $\Sset \subseteq \Csig$. 
 \begin{lemma}
-	\label{lem: mixing_time_small_sets}
-	Let $0 \leq a \leq 1$, and $t \geq 1$ an integer. Then for any $x \leq as(G)$ or $x \geq 1 - as(G)$,
-	\begin{equation*}
-	h_v^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_1}
-	h_v^{(t)}(x) \leq q_v^{(m)}(U_{k - 1}) + q_v^{(m)}(u_k)
-	\end{equation}
-
-	We will rely on the key fact that for any $u \neq v, t \geq 1$,
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_2}
-	q_v^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
-	\end{equation}
-
-	On the other hand if $u = v$,
-	\begin{equation}
-	\label{eqn: mixing_time_small_sets_3}
-	q_v^{(m)}(u) \leq \frac{1}{2^t} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
-	\end{equation}
-	Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
-	\begin{equation*}
-	h_v^{(t)}(x) \leq \frac{1}{2^t} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
-	\end{equation*}
-	Since $x \leq a s(G)$, 
-	\begin{equation*}
-	\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
-	\end{equation*}
-
-	For any $0 \leq b \leq 1$, $x \geq 1 - b$ implies $h_v^{(t)}(x) \leq b$. Taking $b = a s(G)$, the claim is shown.
-\end{proof}
-
-\paragraph{Proof of Proposition \ref{prop: tv_mixing_time}.}
-For any $S \subseteq V$ and any integer $t \geq 0$,
-\begin{equation*}
-\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation*}
-and taking the maximum over all $S \subseteq V$ on both sides, we have
-\begin{equation*}
-\max_{0 \leq x \leq 1} h_v^{(t)}(x) \geq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}.
-\end{equation*}
-
-Letting $q = e_v W^3$, observe that $h_v^{(t + 3)}(x) = h_q^{(t)}(x)$. Fix $\mu = as(G)$. Then, for $\mu \leq x \leq 1 - \mu$, by Lemma \ref{lem: lt_ub},
-\begin{align*}
-h_v^{(t + 3)}(x) & = h_q^{(t)}(x) \\
-& \leq \max \set{h_q^{(0)}(\mu), h_q^{(0)}(1 - \mu) }  + \left(\frac{1}{1 - 2 \mu} + \frac{1}{2\mu}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t\\
-& \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} + \left(\frac{1}{1 - 2a s(G)} + \frac{1}{2 a s(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{align*}
-where the last inequality comes from application of Lemma \ref{lem: mixing_time_small_sets} to $h_q^{(t)} = h_v^{(t + 3)}$.
-
-For $x \leq \mu$ or $x \geq 1 - \mu$, again by Lemma \ref{lem: mixing_time_small_sets},
-\begin{equation*}
-h_v^{(t + 3)}(x) \leq \max \set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}}
-\end{equation*}
-and the proof is complete.
+	\label{lem: nonuniform_continuous_conductance}
+	For any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
+	\begin{equation*}
+	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
+	\end{equation*}
+\end{lemma}
+
+With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}, which follows straightforwardly:
+\begin{align*}
+\liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S)} & \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right) } \\
+& \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}} - \limsup_{n \to \infty} c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \\
+& \geq \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
+\end{align*}
+
+It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we turn to in the following two subsections.
 
@@
 We turn now to lower bounding the conductance over $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ (in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$).
-Our first step will be to introduce a population analogue $\widetilde{\Phi}_{\Pbb,r}$ of the conductance, and prove a lower bound on this quantity.
-Throughout this section, let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
-
-We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by 
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
-\end{equation*}
-
-Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
-\begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
-\end{equation*}
-Letting the \emph{$\Pbb$-local conductance} be given by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
-\end{equation*}
-a bit of algebra verifies that
-\begin{equation*}
-\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
-\end{equation*}
-
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
-\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
-\end{equation*}
-the \emph{$\Pbb$-(continuous) normalized cut} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
-\end{equation*}
-and the \emph{$\Pbb$-(continuous) conductance} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\Pbb,r}(\Sset)
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$ and $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
-
-\begin{proposition}
-	\label{prop: nonuniform_continuous_conductance}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
-	\end{equation*}
-\end{proposition}
+Our first step will be to introduce a population analogue  of the conductance, and prove a lower bound on this quantity.
 
@@
 
-Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
-We denote the graph conductance over $\widetilde{G}_{n,r}$ as $\widetilde{\Phi}_{n,r} := \Phi(G_{n,r}[\Csig[\Xbf]])$.
-To simplify notation, for $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
-\begin{equation*}
-\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
-\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
-\end{equation*}
-and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
-
 \begin{proposition}[Lower bound on graph conductance]
@@
 
-In order to prove Proposition \ref{prop: graph_conductance_profile_lb}, we will need to split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
-For any graph $G = (V,E)$, let $\mathcal{L}(G) = \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G$.)
-
-In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut of all sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then with probability $1$,
-	\begin{equation*}
-	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
-	\end{equation*}
-	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
-\end{lemma}
-
-The proof of Lemma \ref{lem: graph_conductance_profile_lb} is nontrivial, and we devote the following subsection to it.
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb_1}
-	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
-	\begin{equation*}
-	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	The claim follows by simple manipulations:
-	\begin{align*}
-	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
-	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
-	\end{align*}
-\end{proof}
-
-Proposition \ref{prop: graph_conductance_profile_lb} follows in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
-
 In Lemma \ref{lem: local_spread_lb}, we lower bound the local spread $s(\widetilde{G}_{n,r})$.
-
-\begin{lemma}
-	\label{lem: local_spread_lb}
-	With probability one, the following bound holds:
-	\begin{equation*}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
-Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
-	\begin{equation*}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
-	\end{equation*}
-\end{proof}
 
@@
 
-For $\Sset \subseteq \Csig$ measurable, define the conditional probability measures
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
-\end{equation*} 
-A Borel map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
-\begin{equation*}
-\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
-\end{equation*}
-where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
+For $\Sset \subseteq \Csig$ measurable,
 
 If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
-Proposition 5 of \cite{garciatrillos16} establishes that, for open connected domains with Lipschitz boundaries, such stagnating transportation maps exist.
-In particular, as $\Csig[\Xbf]$ consists of $\widetilde{n} := \abs{\Csig[\Xbf]}$ points sampled independently from $\widetilde{\Pbb}$, and $\Csig$ is a connected domain with Lipschitz boundary, the following implication is immediate.
-
-\begin{lemma}
-	\label{lem: stagnating_transportation_maps}
-	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
-	\begin{equation}
-	\label{eqn: stagnating_transportation_maps}
-	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
-	\end{equation}
-	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
-\end{lemma}
-
-%%% AJG 5/9/19: Need to strengthen this?
-
-Note that although $\Csig$ is closed not open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and \eqref{eqn: stagnating_transportation_maps} will hold for any arbitrary extension of $T_n$ to $\Csig$.
 
@@
 Putting Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} together yields the following result, a lower bound on graph normalized cut.
-
-\begin{lemma}
-	\label{lem: graph_to_continuous_conductance}
-	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and fix $S \subseteq \Csig[\Xbf]$. Then, letting $\Sset =T_n^{-1}(S)$,
-	\begin{equation}
-	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}  \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
-	\end{equation}
-\end{lemma}
 
@@
 
+Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
+Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+	\begin{enumerate}
+		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
+\end{corollary}
+
 \section{Proof of Theorem \ref{thm: misclassification_rate}}
@@
 the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
+
+\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
+
+The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
+We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
+All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
 
@@
 
-\subsection{The Approximate PPR Vector}
-\label{sec:appr}
-Before we proceed to the next section, we include a formal statement of our claims regarding the a\pprspace vector. 
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
-	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
-\begin{proof}
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
-
-%\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
+\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
 
@@
 \end{equation*}
+
 On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
-
-\end{proof}
 
@@
 	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
-	\end{align*}
-	\begin{align*}
 	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\

### 2019-07-03 neurips/local_spectral_density_clustering_arxiv.tex
completed reorganization of theorem 4

@@
 %%%%%% Begin Alden
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 
@@
 \newcommand{\cut}{\mathrm{cut}}
-% \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
+\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
 \newcommand{\N}{\mathbb{N}}
@@
 
-Denote $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
+Let $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
 The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that, for universal constants $c_2, c_3,c_4 > 0$, with probability one
@@
 
-In the first step, we relate the mixing time $\tau_{\infty}(G)$ of a generic undirected graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
+In the first step, we relate the mixing time $\tau_{\infty}(G)$ of an arbitrary undirected graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
 We now build to a formal definition of these expansion properties.
 First, we recall the the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well.
-For $u \in V$, $S \subseteq V$,
+For $u \in V$, $S \subseteq V$, and $S^c = V \setminus S$,
 \begin{equation*}
@@
 	\label{prop: pointwise_mixing_time}
-	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
+	Assume $\min_{u \in V} \deg(u; G) \geq 10$. Then,
 	\begin{equation*}
@@
 
-The second step in our approach is to lower bound the local spread and conductance over the particular graph $\widetilde{G}_{n,r}$.
-The following result provides the desired lower bounds, which hold asymptotically as $n \to \infty$,
+The second step in our approach is to lower bound the local spread and conductance over the neighborhood graph $\widetilde{G}_{n,r}$.
+In the following result we give lower bounds for both quantities, which hold asymptotically as $n \to \infty$.
 \begin{proposition}
@@
 
-Taking these results as given, the proof of the theorem is more or less complete.
-We note that since $r$ is fixed, \textcolor{red}{with probability one} $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty > 10$, and we may therefore apply Proposition \ref{prop: pointwise_mixing_time} with respect to $\widetilde{G}_{n,r}$.
-Along with Lemma \ref{prop: local_spread_conductance}, this yields
-\begin{equation*}
-\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
-\end{equation*}
-The first term dominates the middle term, and the theorem follows after an appropriate choice of $c_2$ and $c_3$.
+Taking these results as given, the proof of Theorem \ref{thm: mixing_time_upper_bound} is more or less complete.
+We note that since $r$ is fixed, with probability one $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty$ (see Lemma \ref{lem: ball_bounds_in_probability}).
+In particular, for sufficiently large $n$ the condition $\min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}[\Xbf]) \geq 10$ is satisfied, again with probability one.
+We may therefore apply Proposition \ref{prop: pointwise_mixing_time} and obtain
+\begin{align*}
+\liminf_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) & \leq \liminf_{n \to \infty} \left\{\frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \right\}
+\\
+& \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
+\end{align*}
+whereupon the theorem follows after an appropriate choice of universal constants $c_2, c_3, c_4 > 0$.
+In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
 
@@
 Let $A$ be the adjacency matrix of an undirected graph $G = (V,E)$, and $D$ the associated diagonal degree matrix.
-The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
-Denote the $t$-step probability distribution of this random walk, originating from a particular $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
-
-Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
+The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$ with elements $\pi_u = D_{uu}/\vol(V;G)$.
+Denote the $t$-step probability distribution of this random walk, originating from a  vertex $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
+
+Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between the distributions $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
 \begin{equation*}
@@
 \end{equation*}
-Our goal is to demonstrate that for sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$.
+Our goal is to demonstrate that for a sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$ (see~\eqref{eqn: mixing_time} to recall the definition of $\tau_{\infty}(G)$).
 To do so, we introduce the \emph{total variation distance} between the distributions $q_v^{(t)}$ and $\pi$, given by
@@
 	\label{lem: tv_mixing_time}
-	For any $v \in V$, and any $0 < a \leq 1$,
-	\begin{align*}
-	\norm{q_v^{(t + 3)} - \pi}_{\mathrm{TV}} \leq \max\set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} 
-	\\
-	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{align*}
+	For any $v \in V$, and any $0 < a \leq 1/4$,
+	\begin{align}
+	\norm{q_v^{(t + 3)} - \pi}_{\mathrm{TV}} \leq \max\set{as(G), \frac{1}{8} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} 
+	\nonumber \\
+	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t \label{eqn: tv_mixing_time}
+	\end{align}
 \end{lemma}
@@
 	\label{lem: tv_to_uniform_distance}
-	Let $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
+	Let $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{s(G)}{14}$. Then,
 	\begin{equation*}
@@
 the uniform distance $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$, which proves the claim of Proposition \ref{prop: pointwise_mixing_time}.
-Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$.
-Then,
-\begin{equation*}
-\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
-\end{equation*}
-and so by Lemma \ref{lem: tv_mixing_time},
-\begin{equation*}
-\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-\end{equation*}
-It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
+Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$, so that
+\begin{equation*}
+\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}.
+\end{equation*}
+Recall that by assumption, $\min_{u \in V} \deg(u;G) \geq 10$.
+Moreover note that for $a \leq 1/4$, $2as(G) < 1/2 < 1 - 2as(G)$, since $s(G) \leq 9/10 < 1$.
+By Lemma \ref{lem: tv_mixing_time} we therefore obtain
+\begin{equation*}
+\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{1}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+\end{equation*}
+It is a well known fact (see e.g.~\cite{montenegro2002}) that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
 Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
 \begin{equation*}
-\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
+\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{s(G)}{14}
 \end{equation*}
 and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$.
-The proof is complete once we have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}.
+The proof of Proposition \ref{prop: pointwise_mixing_time} is therefore complete once we have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}.
 
@@
 
-We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined as
-$h_z^{(t)}, t \geq 0$, 
-\begin{equation*}
-h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}
-\end{equation*}
-where the maximum is over:
+We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined for any $t \in \mathbb{N}$ and starting distribution $z$ to be $h_z^{(t)}: [0,1] \to [0,1]$,
+\begin{equation*}
+h_z^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}.
+\end{equation*}
+The maximum in the preceding display is over the set of weight functions $\mathcal{W}_{x}$
 \begin{align*}
@@
 \begin{equation}
-\label{eqn: lovasz_simonivits_1}
-\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation}
-Therefore, taking the maximum on both sides of \eqref{eqn: lovasz_simonivits_1}  over all $S \subseteq V$, we have
+\label{eqn: lovasz_simonovits_1}
+\abs{q_v^{(t)}(S) - \pi(S)} \leq \max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))}
+\end{equation}
+(To see this, consider the weight functions $w(u) = \1(u \in S)$ and $w'(u) = 1 - w(u)$.) Taking the maximum on both sides of \eqref{eqn: lovasz_simonovits_1}  over all $S \subseteq V$, we have
 \begin{equation*}
@@
 \end{equation*}
-Now, take $z = e_vW^3$.
-Observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
-To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$.
-
-To show this upper bound, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$, where $\mu = as(G)$.
+Now, take $z = e_vW^3$, and trivially observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
+To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound -- the right hand side of~\eqref{eqn: tv_mixing_time}-- holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
+
+Let $\mu = as(G)$, and note under the condition $a < 1/4$, $\mu < 1 - \mu$.
+To show the desired upper bound, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$.
 Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,
@@
 	\label{lem: mixing_all_sets}
-	For any $\mu \leq x \leq 1 - \mu$, 
+	For any $\mu \leq x \leq 1 - \mu$ and any starting distribution $z = e_vW^3$,
 	\begin{equation}
@@
 	\end{equation}
-	For any $0 < x \leq \mu$ or $1 - \mu \leq x < 1$
+	For any $0 \leq x < \mu$ or $1 - \mu < x \leq 1$
 	\begin{equation}
 	\label{eqn: mixing_small_sets}
-	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^{t+3}} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
 	\end{equation}
@@
 \ell_{\mu}(x) & \leq \max\set{h_z^{(t)}(\mu),h_z^{(t)}(1 - \mu)} \\
-& \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
+& \leq \max\set{as(G), \frac{1}{2^{t + 3}} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
 \end{align*}
@@
 \begin{equation*}
-h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{equation*}
-which is the desired result.
+h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{8} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
+\end{equation*}
+which is exactly the claimed result of Lemma \ref{lem: tv_mixing_time}.
 
@@
 	\label{thm: lovasz_simonovits_1993}
-	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
+	For any $\mu \leq x \leq 1 - \mu$, $z$ an arbitrary starting distribution, and an integer $t \geq 0$,
 	\begin{equation}
@@
 \end{theorem}
-In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show
+In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show that for any $\mu < x < 1 - \mu$,
 \begin{equation}
@@
 To do so, we make use of an equivalent representation of the Lovasz-Simonovits curve $h_z^{(t)}$.
-Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
-\begin{equation*}
-\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)}
-\end{equation*}
-and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
+Order the elements of $V = \set{u_1, \ldots, u_N}$, where $N = \abs{V}$, such that
+\begin{equation}
+\label{eqn: lovasz_simonovits_curve_1}
+\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)},
+\end{equation}
+and for each $k = 1,\ldots, N$, let $U_k = \set{u_1, \ldots, u_k}$.
+Then for any $x \in [0,1]$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
 \begin{equation}
@@
 \end{equation}
-The representation of the Lovasz-Simonovits curve given by \eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a concave, piecewise linear curve.
-Moreover, we observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
-\begin{equation}
-\label{eqn: lovasz_simonovits_slope}
--1 \leq v(x) \leq \frac{h_z^{(0)}(\mu)}{\mu}.
-\end{equation}
-Note that $\ell_{\mu}(\mu) = h_z^{(0)}(\mu)$, and for $x \geq \mu$, 
-\begin{equation*}
-h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}
-\end{equation*}
-by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
+The representation of the Lovasz-Simonovits curve given by~\eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a piecewise linear curve, with knots at the points $x_k = \pi(U_k)$ for $k = 1,\ldots,N$, where the $k$th linear segment has slope $v_k = q_z^{(t)}(u_{k})/\pi(u_{k}) - 1$.
+By the ordering of~\eqref{eqn: lovasz_simonovits_curve_1}, we have that $v_1(x) > v_2(x) > \ldots > v_{N-1}(x)$, and the curve is therefore concave.
+
+In fact, letting $v(x) = \sum_{k = 1}^{N} v_k \1(x \in [U_k, U_{k+1}) )$ be the slope of the Lovasz-Simonovits curve, for any $x \geq \mu$ it can be shown that
+\begin{align}
+v(x) & \leq \min_{k: u_k \leq x} v_k \nonumber  \\
+& \leq \frac{h_z^{(0)}(\mu)}{\mu}. \label{eqn: lovasz_simonovits_slope}
+\end{align}
+From the upper bound in~\eqref{eqn: lovasz_simonovits_slope} along with the concavity of $h_z^{(0)}(x)$, we have that for any $x \geq \mu$,
+\begin{equation*}
+h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}.
+\end{equation*}
+Some algebra then yields that for any $x \geq \mu$,
 \begin{align*}
@@
 \paragraph{Proof of \eqref{eqn: mixing_small_sets}:}
-First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
+We let $z = e_vW^3$ for an arbitrary $v \in V$. First, we deal with the case $x \leq as(G)$. Letting $\pi(U_{k-1}) \leq x \leq \pi(U_{k})$, we have
 \begin{equation}
@@
 \end{equation}
-Recalling that $z = e_vW^3$, we will rely on the key fact that for any $u \neq v, t \geq 1$,
+We observe a few facts about the random walk defined by $q_z^{(t)}$. By the laziness of the random walk, for $u \neq v, t \geq 1$
 \begin{equation}
@@
 \label{eqn: mixing_time_small_sets_3}
-q_z^{(m)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
+q_z^{(t)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
 \end{equation}
@@
 \begin{equation*}
-h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
-\end{equation*}
-Finally, since $x \leq a s(G)$, 
-\begin{equation*}
-\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
-\end{equation*}
+h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_{k - 1}}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
+\end{equation*}
+Finally, since $x \leq a s(G)$ and $x \geq \pi(U_{k - 1})$,
+\begin{align*}
+\abs{U_{k - 1}} & \leq \frac{\pi(U_{k-1})}{\min_{u \in V} \pi(v) } \\
+& \leq \frac{as(G)}{\min_{u \in V} \pi(v) } \\
+& \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
+\end{align*}
 and the desired result is shown.
@@
 Now, we turn to the case where $x \geq 1 - as(G)$.
-But since $h_z^{(t)}(1) = 0$, and the slope of $h_z$, $v(x')$ is no less than $-1$ for all $x' \in [0,1]$, this implies $h_z^{(t)}(x) \leq 1 - x \leq as(G)$.
+Noting that the slope $v(x)$ of the Lovasz-Simonovits curve $h_z^{(t)}$ is bounded below by $-1$ for all $x \in [0,1]$, by the concavity of $h_z^{(t)}$ we have
+\begin{align*}
+h_z^{(t)}(x) & \leq h_z^{(t)}(1) + (1 - x) \\
+& = 1 - x \leq as(G).
+\end{align*}
+and the proof of Lemma~\ref{lem: tv_mixing_time} is complete.
 
@@
 
-The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebra. Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
+The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebraic manipulation.
+Fix $u \in V$ and let $m \geq t + 1$ be arbitrary.
+The stationarity of $\pi$ gives (see~(16) of \citep{morris2005})
 \begin{align}
@@
 & \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
-& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
+& \overset{(ii)}{\leq} \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \frac{1}{2 \pi(u) \min_{u' \in V} \deg(u';G) }} \nonumber \\
+& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \frac{1}{s(G)} \label{eqn: tv_to_uniform_distance_3}
 \end{align}
-since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
+where $(ii)$ follows from the fact that for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
 As $m - 1 \geq t$, it is well known (see e.g.
@@
 \begin{equation}
-d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{2}{7} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
+d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{1}{14} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
 \end{equation}
@@
 \begin{equation*}
-d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{10}{28} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
+d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{5}{14} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
 \end{equation*}
@@
 
-We first prove \eqref{eqn: local_spread} and then \eqref{eqn: conductance}.
-First, we introduce some notation.
+We prove~\eqref{eqn: local_spread} immediately before turning our attention to~\eqref{eqn: conductance}, which will require the bulk of our attention.
+First, however, we introduce some notation.
 Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
@@
 \begin{equation*}
-\liminf_{n \to \infty} \min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
-\end{equation*}
-where we let $S^c = \Csig[\Xbf] \setminus S$.
+\liminf_{n \to \infty} \set{\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S)} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+\end{equation*}
 In order to show this bound holds uniformly over all sets $S \subseteq \Csig[\Xbf]$, we will split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
-To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G = (V,E)$.)
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for sets $S \subseteq \Csig[\Xbf]$ not sufficiently large enough to be in $\mathcal{L}(\widetilde{G}_{n,r})$, the graph normalized cut is of constant order.
+To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S), \pi(S^c) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a lazy random walk over $G = (V,E)$.)
+
+Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for any subset $S \subseteq \Csig[\Xbf]$ not in $\mathcal{L}(\widetilde{G}_{n,r})$, the graph normalized cut of $S$ is at least $1/10$.
 In fact, this statement holds for any graph $G$.
@@
 	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \pi(S)/(\min_{u \in V}\pi(u))}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \\
 	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
@@
 	\label{lem: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then with probability $1$,
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one
 	\begin{equation}
 	\label{eqn: graph_conductance_profile_lb}
-	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
-	\end{equation}
-	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
-\end{lemma}
-
-Taking Lemma \ref{lem: graph_conductance_profile_lb} as given, Proposition \ref{prop: graph_conductance_profile_lb} then follows from that Lemma, along with Lemma \ref{lem: graph_conductance_profile_lb_1}, in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
+	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+	\end{equation}
+\end{lemma}
+
+The desired upper bound on graph conductance \eqref{eqn: conductance} follows from Lemma \ref{lem: graph_conductance_profile_lb}, along with Lemma \ref{lem: graph_conductance_profile_lb_1}, in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
 We turn now to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
@@
 
-Let $\Sset \subseteq \Csig$ and $S \subseteq \Csig[\Xbf]$.
-The proof of \ref{lem: graph_conductance_profile_lb} will essentially follow from a pair of technical results.
-The first of these will demonstrate that the functional $\widetilde{\Phi}_{n,r}(S)$ can be lower bounded by a population analogue $\widetilde{\Phi}_{\Pbb,r}(\Sset)$, which we term the continuous normalized cut.
+The proof of Lemma~\ref{lem: graph_conductance_profile_lb} will essentially follow from a pair of technical results.
+The first of these will demonstrate that the functional $\widetilde{\Phi}_{n,r}(S)$ can be lower bounded by a population analogue $\widetilde{\Phi}_{\Pbb,r}(\Sset)$, for an appropriately chosen $\Sset \subseteq \Csig$; we term this latter functional the continuous normalized cut.
 This lower bound will hold uniformly over sets $S \subseteq \Csig[X]$.
-The second technical Lemma will build on known continuous space isoperimetric inequalities to lower bound the population-level quantity $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ uniformly over sets $\Sset \subseteq \Csig$.
+The second technical Lemma will build on known continuous space isoperimetric inequalities to lower bound the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ uniformly over sets $\Sset \subseteq \Csig$.
 
 We will now build slowly toward a formal definition of the continuous normalized cut, before establishing a relation between it and it's discrete counterpart.
-Let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
+Let $\Sset \subseteq \Csig$ be measurable.
 We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by
@@
 \begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
+\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) \,d \piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
 \end{equation*}
@@
 \begin{equation*}
-\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
-\end{equation*}
-
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
-\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
-\end{equation*}
-the \emph{($\Pbb$) continuous normalized cut} by
+\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d \Pbb(x) }{\int_{\Csig} \ell_{\Pbb,r}(x) \,d \Pbb(x)}.
+\end{equation*}
+
+We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset \cap \Sset^c = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset$ and $\Sset$ is given by 
+\begin{equation*}
+\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) := \int_{\Sset} \widetilde{P}_{\Pbb,r}(x; \Sset^c) \,d\piwt_{\Pbb,r}(x), 
+\end{equation*}
+and the \emph{($\Pbb$) continuous normalized cut} by
 \begin{equation*}
@@
 As the functionals $\widetilde{\Phi}_{n,r}$ and $\widetilde{\Phi}_{\Pbb,r}$ act in the different spaces $\Csig[\Xbf]$ and $\Csig$, respectively, it is not obvious how to relate them.
-To do so, we introduce transportation maps between the space $\Csig$ and the sample points $\Csig[\Xbf]$.
-Precisely, define the conditional probability measures
+To do so, following the lead of \cite{garciatrillos16}, we introduce transportation maps between the space $\Csig$ and the sample points $\Csig[\Xbf]$.
+We note that by assumption~\ref{asmp: bounded_density}, $\Pbb(\Csig) > 0$, and therefore with probability one as $n \to \infty$, the number of sample points $\abs{\Csig[\Xbf]}$ will be non-zero as well.
+We may therefore define the conditional probability measures
 \begin{equation*}
@@
 \end{equation*} 
-A measurable map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
-\begin{equation*}
-\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
+We then define a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ to be any measurable map $T: \Csig \to \Csig[\Xbf]$ such that for every $S \subseteq \Csig[\Xbf]$,
+\begin{equation*}
+\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S),
 \end{equation*}
 where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
-The following result lower bounds $\widetilde{\Phi}_{n,r}(S)$ by $\widetilde{\Phi}_{\Pbb,r}(T^{-1}(S))$, plus some perturbation.
-The magnitude of this perturbation, and thus the quality of the bound, will be dictated by the \emph{transportation distance} $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$.
+Observe that by the definition of the transportation map $T$, for any $g \in L^1\bigl(\widetilde{\Pbb}_n\bigr)$ the following change of variables formula holds
+\begin{equation*}
+\int_{\Csig} g(x) \,d\widetilde{\Pbb}_{n}(x) = \int_{\Csig} g\bigl(T(x)\bigr) \,d\widetilde{\Pbb}(x)
+\end{equation*}
+Using the change of variables formula with an appropriate choice of $g$, after suitable rescaling we can relate $\widetilde{\cut}_{n,r}(S)$ to $\widetilde{Q}_{\Pbb,r}(T^{-1}(S), T^{-1}(S)^c)$.
+Similarly, we can relate $\widetilde{\vol}_{n,r}(S^c)$ to $\widetilde{\pi}_{\Pbb,r}(T^{-1}(S))$.
+Working along these lines, we obtain the following lower bound on $\widetilde{\Phi}_{n,r}(S)$, stated in terms of the transportation distance $\norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}$, where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$.
+
 \begin{lemma}
 	\label{lem: graph_to_continuous_conductance}
-	Let $\seq{T_n}$ be a sequence of transportation maps between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.Then, letting $\Sset =T_n^{-1}(S)$, there exists a constant $c > 0$ fixed in sample size $n$ such that for any $S \in \mathcal{L}(\widetilde{G}_{n,r})$
+	Let $T:\Csig \to \Csig[\Xbf]$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.
+uppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
+Then there exists a constant $c > 0$ which may depend on $\Pbb$, but does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
 	\begin{equation}
 	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right)
-	\end{equation}
-\end{lemma}
-
-(We note that hereafter in this section $c$ will represent a constant which may change from line to line, and may depend on the density $f$ and dimension $d$, but not on the sample size $n$).
-As mentioned previously, Lemma \ref{lem: graph_to_continuous_conductance} is useful only in conjunction with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures compactly supported over open connected domains with Lipschitz boundaries.
+	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} }{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}  }
+	\end{equation}
+\end{lemma}
+
+Clearly, Lemma \ref{lem: graph_to_continuous_conductance} is useful only when combined with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)}$.
+Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures supported on open, connected and bounded domains with Lipschitz boundaries.
 The following result is a restatement of this Proposition with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
 Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
-Let $\widetilde{n} = \abs{\Csig{\Xbf}}$.
+Let $\widetilde{n} = \abs{\Csig[\Xbf]}$.
 
@@
 \end{theorem}
-
+We remark that $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = \norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)}$, and therefore the preceding theorem shows that with probability one, $\limsup_{n \to \infty} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} = 0$.
 The following result then supplies the last step, a uniform lower bound on the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ for all sets $\Sset \subseteq \Csig$.
-Let the \emph{$\Pbb$-(continuous) conductance} be given by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$, and the minimum in the preceding display is taken over measurable sets $\Sset \subseteq \Csig$. 
+Let the \emph{$\Pbb$-continuous conductance} be given by
+\begin{equation*}
+\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset).
+\end{equation*} 
 \begin{lemma}
 	\label{lem: nonuniform_continuous_conductance}
-	For any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
 	\begin{equation*}
@@
 
-With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}, which follows straightforwardly:
-\begin{align*}
-\liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S)} & \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right) } \\
-& \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}} - \limsup_{n \to \infty} c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \\
-& \geq \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
-\end{align*}
-
-It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we turn to in the following two subsections.
-
-\subsection{Population-level conductance.}
-\label{sec: population_conductance_function}
-
-We turn now to lower bounding the conductance over $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ (in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$).
-Our first step will be to introduce a population analogue  of the conductance, and prove a lower bound on this quantity.
-
-Similar results are already known (see e.g.
+With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
+Observe that for any $c > 0$ fixed in $n$, for sufficiently large $n$ with probability one $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} \leq c$.
+This fact, along with the asymptotic upper bound on $s(\widetilde{G}_{n,r})$ given by~\eqref{eqn: local_spread}, guarantees that the conditions of Lemma~\ref{lem: graph_to_continuous_conductance} are satisfied with probability one as $n \to \infty$.
+Therefore,
+\begin{align*}
+\liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S)} & \geq \liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} }{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}  }} \\
+& \geq \widetilde{\Phi}_{\Pbb,r} - \liminf_{n \to \infty} \set{\frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}}{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}}} \\
+& = \widetilde{\Phi}_{\Pbb,r} \tag{Theorem \ref{thm: stagnating_transportation_maps},\eqref{eqn: local_spread}, and Slutsky's Theorem.}
+\end{align*}
+and the bound on $\widetilde{\Phi}_{\Pbb,r}$ given by Lemma \ref{lem: nonuniform_continuous_conductance} yields the desired result.
+It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we do in the following two subsections.
+
+\subsection{Proof of Lemma \ref{lem: graph_to_continuous_conductance}}
+Let $S \subseteq \Csig[\Xbf]$ be an element of $\mathcal{L}(\widetilde{G}_{n,r})$, and denote $\Sset := T^{-1}(S)$.
+Denote $\varDelta = \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}$, and let $r^{+} = r + \varDelta$ and $r^{-} = r - \varDelta$.
+Our goal is to lower bound
+\begin{equation*}
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c \varDelta}{s(\widetilde{G}_{n,r}) - c \varDelta}
+\end{equation*}
+for some constant $c > 0$ which may depend on the distribution $\Pbb$ but not on the sample size $n$.
+We first state the relationships between the discrete functionals $\widetilde{\cut}_{n,r}$ and $\widetilde{\vol}_{n,r}$, and the continuous functionals $\widetilde{Q}_{\Pbb,r}$ and $\widetilde{\pi}_{\Pbb,r}$, alluded to in the previous section.
+\begin{lemma}
+	\label{lem: cut_volume}
+	\begin{equation}
+	\label{eqn: cut}
+	\frac{1}{\widetilde{n}^2}\widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c)
+	\end{equation}
+	and 
+	\begin{equation}
+	\label{eqn: volume}
+	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{\pi}_{\Pbb,r^+}(\Sset)
+	\end{equation}
+\end{lemma}
+To make use of Lemma \ref{lem: cut_volume}, we provide deviation inequalities on $\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)$, $\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)$, $\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c)$, and $\widetilde{\pi}_{\Pbb,r^+}(\Sset)$ in terms of the transportation distance $\varDelta$.
+\begin{lemma}
+	\label{lem: deviation_transportation_distance}
+	Suppose $\Delta \leq r$. Then there exist constants $c_5,c_6 \geq 0$ which may depend on $\Pbb$ but do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
+	\begin{align*}
+	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5 \varDelta \\
+	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5 \varDelta \\
+	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_6 \varDelta \\
+	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_6 \varDelta.
+	\end{align*}
+\end{lemma}
+
+The combination of Lemmas \ref{lem: cut_volume} and \ref{lem: deviation_transportation_distance} brings us close to our goal, as demonstrated by the following manipulations:
+\begin{align}
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \frac{\widetilde{Q}_{\Pbb,r^-}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r^+}(\Sset)} \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \tag{Lemma \ref{lem: cut_volume}} \\
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_6 \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_6 \varDelta} \left(1 - \frac{2 c_5 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_6}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
+\end{align}
+where the last line follows from some basic algebra. The following result relates the unknown stationary distribution $\widetilde{\pi}_{\Pbb,r}(\Sset)$ to $\widetilde{\pi}_{n,r}(S)$.
+\begin{lemma}
+	\label{lem: continuous_pi_lb}
+	Suppose $\varDelta \leq \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)$.
+Then there exists a constant $c_7 > 0$ which may depend on the distribution $\Pbb$ but does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
+	\begin{equation*}
+	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_7 \varDelta
+	\end{equation*}
+\end{lemma}
+Combining this result with~\eqref{eqn: proof_of_lemma_graph_to_continuous_1}, we obtain
+\begin{align*}
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_6}{\widetilde{\pi}_{n,r}(S) - c_7\varDelta} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
+& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_6}{s(\widetilde{G}_{n,r}) - c_7\varDelta} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
+\end{align*}
+where the latter inequality follows as we assumed $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
+Choosing the constant $c$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c = \max\set{2c_5/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_6, c_7}f$, we achieve our desired result.
+It remains to show Lemmas~\ref{lem: cut_volume}, \ref{lem: deviation_transportation_distance}, and \ref{lem: continuous_pi_lb}, which we now turn to.
+
+\paragraph{Proof of Lemma~\ref{lem: cut_volume}: }
+
+We begin with $\widetilde{\cut}_{n,r}(S)$.
+\begin{align*}
+\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{ \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \1(x_i \in S) \1(x_j \not\in S)\\
+& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \1(x \in S) \1(y \not\in S) \,d\widetilde{\Pbb}_n(x) \,d\widetilde{\Pbb}_n(y) \\
+& =  \iint_{\Csig \times \Csig} \1(\norm{T(x) - T(y)} \leq r) \1(T(x) \in S) \1(T(y) \not\in S)\,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \tag{change of variables}  \\
+& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r^-) \1(T(x) \in S) \1(T(y) \not\in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \\
+& = \int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} 1 \,d\widetilde{\Pbb}(y) \,d\widetilde{\Pbb}(x)
+\end{align*}
+By definition we have $\frac{\,d\Pbb(x)}{\,d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
+\begin{align}
+\int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} d\Pbb(y) d\Pbb(x) \nonumber \\
+& = \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r^-)\bigr)}{\ell_{\Pbb,r^-}(x)} d\piwt_{\Pbb,r^-}(x) \nonumber \\
+& = \frac{\int_{\Csig} \ell_{\Pbb,r^-}\,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c). \label{eqn: cut_bound}
+\end{align}	
+We obtain an upper bound on $\widetilde{\vol}_{n,r}(S)$ by similar manipulations, as follows:
+\begin{align}
+\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{ \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \1(x_i \in S) \nonumber \\
+& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \1(x \in S) \,d\widetilde{\Pbb}_n(x) \,d\widetilde{\Pbb}_n(y) \nonumber \\
+& = \iint_{\Csig \times \Csig} \1(\norm{T(x) - T(y)} \leq r) \1(T(x) \in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \nonumber \\
+& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r^+) \1(x \in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \nonumber \\
+& = \int_{\Sset} \int_{\Csig \cap B(x,r^+)} 1 \,d\widetilde{\Pbb}(y) \,d\widetilde{\Pbb}(x) \nonumber \\
+& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r^+)} 1 \,d\Pbb(y) \,d\Pbb(x) \nonumber \\
+& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) \nonumber \\
+& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \piwt_{\Pbb,r^+}(\Sset). \label{eqn: vol_bound}
+\end{align}
+
+\paragraph{Proof of Lemma~\ref{lem: deviation_transportation_distance}: }
+
+Consider the set
+\begin{equation*}
+\mathcal{R}(x) := \set{y \in \Csig: y \in B(x,r^+), y \not\in B(x,r^-)}
+\end{equation*} 
+for $x \in \Csig$, and observe that
+\begin{equation*}
+\int_{\mathcal{R}(x)} \,d\Pbb(y) \leq \Lambda_{\sigma} \nu_d \left((r + \delta)^d - (r - \varDelta)^d\right)
+\end{equation*}
+and therefore
+\begin{equation}
+\label{eqn: deviation_transportation_distance_2}
+\int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \leq \Pbb(\Csig )\Lambda_{\sigma} \nu_d \left((r + \varDelta)^d - (r - \varDelta)^d\right).
+\end{equation}
+A first-order Taylor expansion of $(r + \varDelta)^d$ results in the upper bound $(r + \varDelta)^d \leq r^d + d\varDelta(r + \varDelta)^{d - 1}$, and similarly $(r - \varDelta)^d \geq r^d - d\varDelta(r + \varDelta)^{d - 1}$.
+Plugging these bounds into~\eqref{eqn: deviation_transportation_distance_2} yields
+\begin{align}
+\int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)  & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl( 2d(r + \Delta)^{d - 1}\varDelta \bigr) \tag{1st-order Taylor expansion of $(r + \Delta)^d$ } \\
+& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_5 \varDelta. \label{eqn: deviation_transportation_distance_1}
+\end{align}
+where the second line follows from the condition $\Delta \leq r$.
+Using~\eqref{eqn: deviation_transportation_distance_1}, we proceed to obtain each of the four bounds stated in Lemma~\ref{lem: deviation_transportation_distance}.
+First, as $\ell_{\Pbb,r^{+}}(x) \leq 1$ for all $x \in \Csig$, we have
+\begin{align*}
+\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \\
+& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5\varDelta.
+\end{align*}
+An equivalent bound for $\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)$ is obtained by similar reasoning. We now lower bound $\widetilde{Q}_{\Pbb,r^{-}}(\Sset, \Sset^c)$,
+\begin{align*}
+\widetilde{Q}_{\Pbb,r^{-}}(\Sset, \Sset^c) & = \int_{\Sset} \widetilde{P}_{\Pbb,r^-}(x; \Sset) \,d\widetilde{\pi}_{\Pbb,r}(x) \\
+& = \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r^-)) d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r^-)) d\Pbb(x)} \\
+& \geq \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) d\Pbb(x) - \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r)) d\Pbb(x)} \\
+& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_5 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_6 \varDelta.
+\end{align*}
+Finally, we upper bound $\widetilde{\pi}_{\Pbb,r^{+}}(\Sset)$,
+\begin{align*}
+\widetilde{\pi}_{\Pbb,r^{+}}(\Sset) & = \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \\
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Sset} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_6\varDelta.
+\end{align*}
+
+\paragraph{Proof of Lemma~\ref{lem: continuous_pi_lb}: }
+The proof of Lemma~\ref{lem: continuous_pi_lb} will not be too different from the proof of Lemma~\ref{lem: deviation_transportation_distance}. From the change of variables formula, we have
+\begin{align*}
+\widetilde{\pi}_{n,r}(S) & = \frac{\int_{\Sset}\int_{\Csig} \1(\norm{x - y} \leq r) \,d\widetilde{\Pbb}_n(y) \,d\widetilde{\Pbb}_n(x)}{\int_{\Csig}\int_{\Csig} \1(\norm{x - y} \leq r) \,d\widetilde{\Pbb}_n(y) \,d\widetilde{\Pbb}_n(x)} \\
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) }{\int_{\Csig}\ell_{\Pbb,r^-}(x) \,d\Pbb(x)} \\
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_7 \varDelta.
+\end{align*}
+where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_5\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
+
+\subsection{Proof of Lemma \ref{lem: nonuniform_continuous_conductance}. }
+We recall that our goal is to lower bound the continuous conductance $\widetilde{\Phi}_{\Pbb,r}$.
+Results along these lines are already known (see e.g.
 \cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
@@
 
-\paragraph{Population-level conductance with uniform density}
-We first prove an analogous result for the special case of $f \propto 1$ everywhere on $\Csig$. For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let 
-\begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) d\pi_{\nu,r}(x).
-\end{equation*}
-The uniform continuous normalized cut and conductance are then defined analogously to the weighted case,
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
-\end{equation*}
+\paragraph{Population-level conductance with uniform density.}
+We first state an analogous result for the special case where the density $f$ is uniform everywhere on $\Csig$. For $x \in \Csig$ and measurable $\Sset \subseteq \Csig$, let 
+\begin{equation*}
+\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
+\end{equation*}
+The uniform continuous normalized cut and conductance are then defined analogously to the $\Pbb$-weighted case,
+\begin{equation*}
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\nu,r}(\Sset).
+\end{equation*}
+where the minimum is over measurable sets $\Sset \subseteq \Csig$.
 
@@
 	\label{lem: uniform_continuous_conductance}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance of the $r$-ball walk satisfies
+	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance $\widetilde{\Phi}_{\nu,r}$ satisfies
 	\begin{equation*}
@@
 
-Most of the technical work needed to show Proposition \ref{prop: nonuniform_continuous_conductance} involves proving Lemma \ref{lem: uniform_continuous_conductance}.
-We defer this work to the next subsection, and first show that Proposition \ref{prop: nonuniform_continuous_conductance} is a simple consequence of Lemma \ref{lem: uniform_continuous_conductance} along with \ref{asmp: bounded_density}.
-
-\paragraph{Proof of Proposition \ref{prop: nonuniform_continuous_conductance}.}
-
-Assume Lemma \ref{lem: uniform_continuous_conductance} holds, and note that for any $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq 1/2$,
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)}
-\end{equation*}
-By \ref{asmp: bounded_density} we obtain
-\begin{align*}
-\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(S \cap B(x,r)) f(x) \dx}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) f(x) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(S \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \widetilde{\Phi}_{\nu,r}(\Sset)
-\end{align*}
-and the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
-
-\subsection{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-\label{sec: proof_of_lemma_continuous_conductance}
-
-As is standard, the proof of a lower bound on the conductance relies on an isoperimetric inequality.
-
+Most of the technical work needed to show Lemma~\ref{lem: nonuniform_continuous_conductance} involves proving Lemma~\ref{lem: uniform_continuous_conductance}.
+We first show that  Lemma~\ref{lem: nonuniform_continuous_conductance} is a simple consequence of Lemma~\ref{lem: uniform_continuous_conductance} -- and \ref{asmp: bounded_density} -- before turning to prove Lemma~\ref{lem: uniform_continuous_conductance}.
+
+To relate the uniform- and $\Pbb$-continuous conudctances, observe that by \ref{asmp: bounded_density} we obtain
+\begin{align*}
+\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) \,d\Pbb(x)}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) \,d\Pbb(x)} \\
+& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(\Sset^c \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
+& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\widetilde{Q}_{\nu,r}(\Sset,\Sset^c)}{\pi_{\nu,r}(\Sset)}
+\end{align*}
+with equivalent reasoning leading to bound $\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)/\piwt_{\Pbb,r}(\Sset) \leq (\lambda_{\sigma}^2/\Lambda_{\sigma}^2) \widetilde{Q}_{\nu,r}(\Sset,\Sset^c)/\piwt_{\nu,r}(\Sset)$.
+Lemma~\ref{lem: nonuniform_continuous_conductance} therefore follows from Lemma~\ref{lem: uniform_continuous_conductance}, and it remains to show the latter Lemma.
+
+\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}:}
+Lower bounds on the conductance of geometric random walks follow a typical pattern.
+The first step is to establish that an isoperimetric inequality holds uniformly over the domain of interest, in this case $\Csig$.
+The following result contains the isoperimetric inequality we will use.
+It is stated and proved in \cite{abbasi-yadkori2016a}; for completeness, we reproduce the proof here.
 \begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
 	\label{lem: nonconvex_isoperimetry}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
 Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
@@
 \end{lemma}
-The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even in the convex setting, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among others.
-Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting given by  Assumption \ref{asmp: embedding} is not difficult.
-
+The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\Csig$ is itself convex, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among (many) others.
+Once the result is shown in the convex setting, however, it is not hard to show that it applies to bi-Lipschitz transformations of convex sets as well.
 \begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
@@
 \end{proof}
-
-We will also need an upper bound on the distance between transition probability densities $\widetilde{P}_{\nu,r}(u,\cdot)$ and $\widetilde{P}_{\nu,r}(v,\cdot)$ for $u,v \in \Csig$ close together. 
+With an isoperimetric inequality in hand, the next step towards showing a lower bound on conductance is to prove that for any pair of sufficiently close points $u,v \in \Csig$, the total variation distance between the distributions $\widetilde{P}_{\nu,r}(u;\cdot)$ and $\widetilde{P}_{\nu,r}(v;\cdot)$ is small.
 \begin{lemma}[One-step distributions]
@@
 	\end{equation*}
-	for some $0 < t < 1/8$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
+	for some $0 < t < 1$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
 	\begin{equation*}
@@
 \end{lemma}
-
-The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$.
-
+For the moment, we will take Lemma \ref{lem: one_step_distributions} as given and prove Lemma \ref{lem: uniform_continuous_conductance}, before returning to prove Lemma \ref{lem: one_step_distributions}.
+Deriving a lower bound on conductance from a isoperimetric inequality (i.e Lemma \ref{lem: nonconvex_isoperimetry}) along with a bound on the one-step distributions is standard.
+Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$, and let $\ell = 6/25$.
+Note by Lemma \ref{lem: local_conductance}, as $r < \sigma/(2\sqrt{d})$ $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$ for all $x \in \Csig$.
+We will show that
+\begin{equation}
+\label{eqn: uniform_continuous_conductance_1}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \widetilde{\pi}_{\nu,r}(x) \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}.
+\end{equation}
+Then, dividing both sides by $\min\set{\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}$ yields the desired result~\eqref{eqn: uniform_continuous_conductance_1}, as $\Sset_1,\Sset_2$ was an arbitrary partition.
+
+Now, consider the sets
+\begin{align*}
+\Sset_1' & = \set{x \in \Sset_1: \widetilde{P}_{\nu,r}(x; \Sset_2) < \frac{\ell}{4}} \\
+\Sset_2' & = \set{x \in \Sset_2: \widetilde{P}_{\nu,r}(x; \Sset_1) < \frac{\ell}{4}}
+\end{align*}
+and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$. Suppose $\widetilde{\pi}_{\nu,r}(\Sset_1') < \widetilde{\pi}_{\nu,r}(\Sset_1)/2$. Then,
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \,d\widetilde{\pi}_{\nu,r}(x) \geq \frac{\ell \widetilde{\pi}_{\nu,r}(\Sset_1)}{8}
+\end{equation*}
+Similarly, if $\widetilde{\pi}_{\nu,r}(\Sset_1') < \widetilde{\pi}_{\nu,r}(\Sset_1)/2$, then since
+\begin{equation*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \,d\widetilde{\pi}_{\nu,r}(x) = \int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_1) \,d\widetilde{\pi}_{\nu,r}(x)
+\end{equation*}
+a symmetric result holds. In either case, \eqref{eqn: uniform_continuous_conductance_1} follows.
+
+Now, suppose $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2'$ and $\Sset_2$. For every $u \in \Sset_1'$ and $v \in \Sset_2'$ we have that
+\begin{equation*}
+\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{\mathrm{TV}} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
+\end{equation*}
+and thus by Lemma \ref{lem: one_step_distributions},
+\begin{equation*}
+\norm{u - v} \geq \frac{\sqrt{2 \pi } r \ell}{3 \sqrt{3 d}} \geq \frac{\sqrt{2}r \ell}{3\sqrt{d}}.
+\end{equation*}
+Since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
+\begin{equation}
+\label{eqn: uniform_continuous_conductance_2}
+\nu(\Sset_3') \geq  \frac{\sqrt{2} r \ell}{3 \rho L \sqrt{d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}.
+\end{equation}
+Let $\Sset \subseteq \Csig$ be arbitrary, and note that an upper (lower) bound on $\nu(\Sset)$ implies an upper (lower) bound on $\widetilde{\pi}_{\nu,r}(\Sset)$, as follows:
+\begin{equation}
+\label{eqn: uniform_continuous_conductance_3}
+\ell \nu_d r^d \nu(\Sset) \leq \widetilde{\pi}_{\nu,r}(\Sset) \leq \nu_d r^d \nu(\Sset).
+\end{equation}
+We now prove~\eqref{eqn: uniform_continuous_conductance_1}, the desired result:
+\begin{align*}
+\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \dx & = \frac{1}{2} \biggl(\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2)  \,d\widetilde{\pi}_{\nu,r}(x) + \int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_1) \,d\widetilde{\pi}_{\nu,r}(x)\biggr) \\
+& \geq \frac{\ell}{8} \Bigl( \widetilde{\pi}_{\nu,r}(\Sset_1 \setminus \Sset_1') + \widetilde{\pi}_{\nu,r}(\Sset_2 \setminus \Sset_2') \Bigr) \\
+& \geq \frac{\ell}{8} \widetilde{\pi}_{\nu,r}(\Sset_3') \\
+& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \tag{by \eqref{eqn: uniform_continuous_conductance_3}}\\
+& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \tag{by \eqref{eqn: uniform_continuous_conductance_2}}\\
+& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\widetilde{\pi}_{\nu,r}(\Sset_1'), \widetilde{\pi}_{\nu,r}(\Sset_2')} \tag{by \eqref{eqn: uniform_continuous_conductance_3}}\\
+& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}
+\end{align*}
+where the last line follows since $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2'$ and $\Sset_2$.
+To prove Lemma \ref{lem: uniform_continuous_conductance}, it remains to prove Lemma \ref{lem: one_step_distributions}, and we do this next.
+
+\paragraph{Proof of Lemma \ref{lem: one_step_distributions}:}
+
+The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$. We state this result and immediately prove it.
 \begin{lemma}
 	\label{lem: overlap_balls_1}
-	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1/8$. Then,
+	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1$. Then,
 	\begin{equation*}
@@
 \begin{proof}
-	We will treat only the case where $\norm{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
-Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
+	We will treat only the case where $\norm{u - v} = t\frac{r}{2\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
+Then, it is not hard to see that $\mathcal{I} := B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
 	\begin{equation*}
@@
 	\end{equation*} 
-	From Lemma \ref{lem: volume_of_spherical_cap} we therefore obtain
-	\begin{equation*}
-	\nu\text{(i)} = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
+	As a result, by Lemma \ref{lem: volume_of_spherical_cap} we have
+	\begin{equation*}
+	\nu\bigl(\mathcal{I}\bigr) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
 	\end{equation*}
@@
 	\begin{align*}
-	\nu\text{(i)} & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
+	\nu\bigl(\mathcal{I}\bigr) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
 	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
@@
 
-\begin{proof}[Proof of Lemma \ref{lem: one_step_distributions}]
-	Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
+We now complete the proof of Lemma \ref{lem: one_step_distributions}. Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
 \begin{equation*}
@@
 \end{equation*}
-	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}}$.
-
+Since this will hold for arbitrary $\Sset_1 \subset \Csig$, it will hold for the supremum over all such $\Sset_1$ as well, and therefore the same upper bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}}$.
 Now, note that
-	\begin{align*}
-	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
-	\end{align*}
-	Let $I := B(u,r) \cap B(v,r)$. Then we have
-	\begin{equation*}
-	\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap I)
+\begin{equation*}
+\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
+\end{equation*}
+As before, let $\mathcal{I} = B(u,r) \cap B(v,r)$. Then we have
+\begin{equation*}
+\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap \mathcal{I})
 \end{equation*}
@@
 \begin{equation}
-	1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
-	\end{equation}
-	As \eqref{eqn: one_step_1} demonstrates, the overlap of the one-step distributions is related to the volume of the intersection between $B(u,r)$ and $B(v,r)$ within $\Csig$.
-
+1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap \mathcal{I}) \label{eqn: one_step_1}
+\end{equation}
 From here, some simple manipulations yield
 \begin{align}
-	\nu(\Csig \cap I)  & = \nu\text{(i)} - \nu(I \setminus \Csig) \nonumber \\
-	& \geq \nu\text{(i)} - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
-	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
+\nu(\Csig \cap \mathcal{I})  & = \nu(\mathcal{I}) - \nu(\mathcal{I} \setminus \Csig) \nonumber \\
+& \geq \nu\bigl(\mathcal{I}\bigr) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
+& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \tag{Lemma \ref{lem: overlap_balls_1}} \\
+& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right) \label{eqn: one_step_2} 
 \end{align}
-	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
-\end{proof}
-
-\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-Let $\Sset_1 \cup \Sset_2 = \Csig$ be arbitrary, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
-\end{equation*}
-Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$.
-Then, dividing both sides by $\pi_{\nu,r}(\Sset_1)$ yields the desired result, since $\Sset_1$ was arbitrary.
-
-Now, consider the sets
-\begin{align*}
-S_1' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}} \\
-S_2' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}}
-\end{align*}
-and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$.
-
-Suppose $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(\Sset_1)/2$. Then,
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(\Sset_1)}{8}
-\end{equation*}
-Similarly, if $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(S_1)/2$, then since
-\begin{equation*}
-\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) = \int_{S_2} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x)
-\end{equation*}
-a symmetric result holds.
-
-So we can assume $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2$. Now, for every $u \in \Sset_1', v \in \Sset_2'$, we have that
-\begin{equation*}
-\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{\mathrm{TV}} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
-\end{equation*}
-
-By Lemma \ref{lem: one_step_distributions}, we therefore have
-\begin{equation*}
-\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{6\sqrt{3 d}}.
-\end{equation*}
-and since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
-\begin{equation*}
-\nu(\Sset_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{6 \rho L \sqrt{3 d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}
-\end{equation*}
-We now prove the desired result:
-\begin{align*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) & = \frac{1}{2} \biggl(\int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_2)  d \pi_{\nu,r}(x) \biggr) \\
-& \geq \frac{\ell}{8} \pi_{\nu,r}(\Sset_3') \\
-& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \\
-& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1'), \pi_{\nu,r}(\Sset_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1), \pi_{\nu,r}(\Sset_2)}.
-\end{align*}
-
-\subsection{Graph conductance and local spread.}
-\label{sec: graph_conductance_and_local_spread}
-
-\begin{proposition}[Lower bound on graph conductance]
-	\label{prop: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, with probability $1$ the following lower bound holds on the graph conductance:
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
-	\end{equation*}
-\end{proposition}
-
-In Lemma \ref{lem: local_spread_lb}, we lower bound the local spread $s(\widetilde{G}_{n,r})$.
-
-\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
-\label{sec: proof_of_lemma_graph_conductance}
-
-For $\Sset \subseteq \Csig$ measurable,
-
-If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
-
-\paragraph{Graph cuts to continuous cuts.}
-
-We use stagnating transportation maps to relate discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
-We fix some notation, letting $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$ for a transportation map $T_n$.
-
-Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
-
-\begin{lemma}
-	\label{lem: volume_bound}
-	Let $S \subseteq \Csig[\Xbf]$ and $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset := T_n^{-1}(S)$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{2 \Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	\varphi(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	Now, we proceed
-	\begin{align}
-	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
-	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
-	& = \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \tag{change of variables} \nonumber \\
-	& \leq \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& = \frac{1}{2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
-	\end{align}
-
-	By definition we have $\frac{d\Pbb(x)}{d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
-	\begin{align*}
-	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
-	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) \dx \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset)
-	\end{align*}
-	and we have the desired upper bound.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: cut_bound}
-	Let $S \subseteq \Csig[\Xbf]$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = T_n^{-1}(S)$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{2 \Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	As in the proof of Lemma \ref{lem: volume_bound}, let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$.
-
-	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
-	\begin{align*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
-	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
-	& =  \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& \geq \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& = \frac{1}{2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
-	\end{align*}
-	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
-	\begin{align*}
-	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r_n^-)\bigr)}{\ell_{\Pbb,r_n^-}(x)} d\piwt_{\Pbb,r}(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{align*}	
-\end{proof}
-
-Putting Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} together yields the following result, a lower bound on graph normalized cut.
-
-\begin{proof}
-
-	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset)}.
-	\end{equation*}
-
-	Then, noting that $\Sset^c = T_n^{-1}(S^c)$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\piwt_{\Pbb,r_n^+}(\Sset^c)}
-	\end{equation*}
-	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} },
-	\end{equation*}
-	and the proof is complete.
-\end{proof}
-
-\paragraph{Perturbation analysis.}
-
-If $r_n^- = r = r_n^+$, \eqref{eqn: graph_to_continuous_conductance} would simplify to $\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)$.
-We show that this conclusion is robust to asymptotically negligible perturbations of $r$.
-
-\begin{lemma}[Continuity of local conductance]
-	\label{lem: cont_local_conductance}
-	For $\seq{T_n}$ a sequence of stagnating transportation maps,
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Letting $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx + \int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx.
-	\end{equation*}
-	and therefore
-	\begin{equation*}
-	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}.
-	\end{equation*}
-	We upper bound the remainder term
-	\begin{equation*}
-	\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl((r_n^+)^d - r^d) \to 0
-	\end{equation*}
-	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	We apply a similar analysis to the denominator. By Lemma \ref{lem: local_conductance}
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) \dy \dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d \to \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
-	\end{equation*}
-	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	Then the desired result follows from an application of Slutsky's Theorem.
-\end{proof}
-
-\begin{lemma}[Continuity of stationary distribution]
-	\label{lem: cont_stationary_dist}
-	Let $c > 0$ be any fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } = 1
-	\end{equation*}
-	uniformly over all measurable sets $\Sset \subseteq \Csig$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
-\end{lemma}
-\begin{proof}
-	It will be sufficient to show that
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} \quad \text{and}  \quad \liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset^c)} = 1,
-	\end{equation*}
-	and we will show only the former, the proof of the latter being identical.
-
-	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
-	\begin{equation*}
-	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
-	\end{equation*}
-	we may rewrite
-	\begin{equation*}
-	\frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\piwt_{\Pbb,r_n^+}(\Sset)}.
-	\end{equation*}
-
-	By the stagnating property of $T_n$,
-	\begin{equation*}
-	\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
-	\end{equation*}
-	where the convergence occurs uniformly over all $\Sset$ as $n \to \infty$. On the other hand, by hypothesis
-	\begin{equation*}
-	\liminf_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
-	\end{equation*}
-	and the result follows by Slutsky's Theorem. 
-\end{proof}
-
-\begin{lemma}[Stationary distribution lower bound]
-	\label{lem: stationary_dist_lb}
-	Let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$. Then with probability one,
-	\begin{equation*}
-	\liminf_{n \to \infty} \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \piwt_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary, writing $\Sset := T_n^{-1}(S)$.
-Letting $\mathcal{R}_n(x)$ be as in the proof of Lemma \ref{lem: cont_stationary_dist}, we have
-	\begin{align}
-	\widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}. \label{eqn: stationary_dist_lb_1}
-	\end{align}
-	Clearly $\piwt_{\Pbb,r_n^-}(\Sset) \leq \piwt_{\Pbb,r}(\Sset)$. Moreover
-	\begin{equation*}
-	\frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	which along with \eqref{eqn: stationary_dist_lb_1} implies
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d \to \piwt_{\Pbb,r}(\Sset).
-	\end{equation*}
-	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is uniform over $\Sset$ as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	By Lemma \ref{lem: local_spread_lb}, with probability one as $n \to \infty$,
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
-	\end{equation*}
-	and the claim is shown.
-\end{proof}
-
-\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
-
-By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
-
-Let $S \subseteq \Csig[\Xbf]$ be arbitrary, and define
-\begin{equation*}
-\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx},~ \gamma_n(S) := \frac{\min \set{\piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
-\end{equation*}
-where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-By Proposition \ref{prop: nonuniform_continuous_conductance} and Lemma \ref{lem: graph_to_continuous_conductance} we have that
-\begin{align}
-\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
-& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
-\end{align}
-
-By Lemma \ref{lem: cont_local_conductance}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \xi_n = 1.
-\end{equation*}
-
-By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $0 < c < \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}$, with probability one there exists some $m \in \mathbb{N}$ such that for all $n \geq m$,
-\begin{equation*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})}\piwt_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
-\end{equation*}
-and therefore by Lemma \ref{lem: cont_stationary_dist}
-\begin{equation*}
-\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
-\end{equation*}
-
-As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
-
-\subsection{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
-\label{sec: proof_of_theorem_mixing_time}
-
-Since $r$ is fixed, $\degminwt \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
-\begin{equation}
-\label{eqn: tau_ub}
-\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2}{\widetilde{\Phi}_{n,r}^2} \log\left(\frac{1440}{s(\widetilde{G}_{n,r})}\right) \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
-\end{equation}
-and the claim follows from Proposition \ref{prop: graph_conductance_profile_lb} and Lemma \ref{lem: local_spread_lb}.
-In the statement of Theorem \ref{thm: mixing_time_upper_bound} we omit the factor of $3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right)$ as the first and third terms in \eqref{eqn: tau_ub} dominate.
+where the last inequality follows by the hypothesis $\ell_{\nu,r}(u),\ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then~\eqref{eqn: one_step_2} along with~\eqref{eqn: one_step_1} give the desired result
+\begin{align*}
+\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & \leq  1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap \mathcal{I}) \\
+& \leq 1 - \ell + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}.
+\end{align*}
+We have completed our proof of Lemma \ref{lem: one_step_distributions}, and therefore (in turn), Lemmas~\ref{lem: uniform_continuous_conductance}, \ref{lem: nonuniform_continuous_conductance}, and \ref{lem: graph_conductance_profile_lb}.
+As a result, Proposition \ref{prop: local_spread_conductance} is proved, and the proof of Theorem \ref{thm: mixing_time_upper_bound} is complete.
 

### 2019-07-03 neurips/local_spectral_density_clustering_arxiv.tex

@@
   fraction of points will be misclassified. This strong condition is the price
-  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
-\end{remark}
-
-\begin{remark}
-  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
-  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
+  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
+ \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
+  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
   attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
-  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
+  $\kappa(\Cset)$ prevents us from making claims about the
   behavior of PPR in this regime. Although the restriction to a kernel
@@
   this is merely looseness in our upper bounds.  
-\end{remark}
-
+\end{enumerate}
 \sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
 changed this $\epsilon$ to $\varepsilon$.}
-\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
-  ppr_vector} may be too computationally expensive. To address this limitation,
+
+\subsection{Approximate PPR vector} 
+In practice, exactly solving the system of equations~\eqref{eqn:
+  ppr_vector} to compute the PPR vector 
+  may be too computationally expensive. To address this limitation,
 \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
@@
 formally state and prove this in Corollary~\ref{cor: appr} in 
-the appendix.
-
-\section{Analysis}
+Appendix~\ref{sec:appr}.
+
+\section{Analysis Overview}
 \label{sec: analysis}
@@
 
-Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
-	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
-
 \section{Proof of Theorem \ref{thm: misclassification_rate}}
 \label{sec: proof_of_misclassification_rate}
-In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
-
-Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
-\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+In this section, we prove both Theorem \ref{thm: misclassification_rate}.
+The result is in essence a consequence of the bounds in Theorem~\ref{thm: conductance_upper_bound} 
+and Theorem~\ref{thm: mixing_time_upper_bound} bounding the normalized cut and mixing time, together with the result of \citet{zhu2013} relating the quality of the PPR output to these quantities, and the result in Lemma~\ref{lem: ball_bounds_in_probability}
+that allows us to translate the guarantees on the volume to guarantees on the symmetric set difference.
+
+% and the relevant portions of Corollary \ref{cor: appr}.
+We begin with Lemma \ref{lem: zhu}, which is a restatement of Lemma 3.4 of \citet{zhu2013}, translated into notation consistent with the rest of this paper.
+It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
 
@@
 \end{align*}
-the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
-
-\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
-
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
+the theorem follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
 

### 2019-10-04 arxiv/examples_section.tex
added relevant examples tuff

--- 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
@@
 
-\begin{abstract}
-\noindent We analyze the Personalized PageRank (PPR) algorithm, a local spectral method for clustering,
-which extracts clusters using locally-biased random walks around a user-specified
-seed node.  In contrast to previous work, we adopt a traditional statistical
-learning setup, where we obtain samples from an unknown distribution, and aim to
-identify connected regions of high-density (density clusters).  We prove that
-PPR, run on a neighborhood graph, extracts sufficiently salient density
-clusters. We also provide empirical support for our theory.
-\end{abstract}
 	\end{center}
-\section{Introduction}
-\label{sec: introduction}
-In this paper, we consider the problem of clustering: splitting a given data set
-into groups that satisfy some notion of within-group similarity and
-between-group difference.  Our particular focus is on
-spectral clustering methods, a family of powerful
-nonparametric clustering algorithms. Roughly speaking, a spectral algorithm
-first constructs a geometric graph $G$, where vertices correspond to samples,
-and edges correspond to proximities between samples. The algorithm 
-then estimates a feature
-embedding based on (an appropriate) Laplacian matrix of the graph 
-$G$, and applies a simple clustering
-technique (like $k$-means clustering) in the embedded feature space.
-
-% Spectral clustering and density clustering
-%Spectral clustering algorithms, which
-%originated in the early work of Fiedler \cite{fiedler73}, have seen a recent revival 
-%(see for instance the recent review~\cite{XX}) focused mainly on understanding the performance of spectral clustering on the Stochastic Block Model (SBM) and closely related problems.
-%A parallel line of work \cite{shi09,schiebinger15}, has considered spectral partitioning applied to a non-parametric mixture model
-%where once again the clustering goal is to recover the latent labels of a sample $X_1,\ldots,X_n \sim P$.
-These works proceed by relating the eigenvectors of the graph Laplacian to eigenfunctions of an appropriately defined integral operator, and then using assumptions about the (non-)overlap of the mixture components to show that these eigenfunctions elucidate the latent labels.
-
-When applied to geometric graphs built from a large number of samples,
-global spectral clustering methods can be computationally cumbersome and   
-insensitive to the local geometry of the underlying distribution
-\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
-local spectral clustering algorithms, which leverage locally-biased spectra
-computed using random walks around some user-specified seed node.  A popular 
-local clustering algorithm is the Personalized PageRank (PPR) algorithm, first introduced by 
-\citet{haveliwala2003}, then further developed by
-several others~\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
-
-Local spectral clustering techniques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, leading 
-many authors to develop supporting theory
-\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
-guarantees on traditional graph-theoretic notions of cluster quality (such as
-conductance).  In this paper, we adopt a classical statistical viewpoint,
-and examine what the output of local clustering on a data set reveals about the
-underlying density of the samples 
-$f$.  In particular, we examine the ability of PPR to recover
-\emph{density clusters} of $f$, defined as the connected components of
-the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$
-(a central object of interest in the statistical clustering literature, dating
-back to the work of \citet{hartigan1981}).
-
-\section{Background and Related Work}
-We begin by providing some standard background on the PPR algorithm
-and the density clustering setup, before turning our attention to related work
-and a
-detailed summary of our contributions.
-
-\subsection{PPR on a neighborhood graph} 
-We now describe the clustering
-algorithm that will be our focus for the rest of the paper. Let $\Xbf = \{x_1,
-\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$,
-with density~$f$.  For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the
-\emph{$r$-neighborhood graph} of $\Xbf$, an unweighted, undirected graph with
-vertices $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i -
-x_j} \leq r$, where $\norm{\cdot}$ is the $\ell_2$ norm. We denote by $\Abf \in
-\Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if
-$(u,v) \in E$ and $0$ otherwise.  We also denote by $\Dbf$ the diagonal degree
-matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n
-\times n$ identity matrix.
-
-Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, based on
-a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be 
-the solution of the following linear system:
+
+\section{Examples}
+\label{sec:examples}
+
+In this section, we demonstrate the implications of our theory, and compare the performance of PPR density clustering to some alternatives, by walking through a series of examples.
+In all of these examples, the generative model under consideration will be a mixture of uniform distributions, plus some noise distribution.
+To formally define this model, we specify a support $\mathcal{X}$ and disjoint subsets $\mathcal{C}_1,\ldots,\mathcal{C}_M$ of $\mathcal{X}$, where $M \geq 2$ is the number of mixture components.
+We sample the background noise uniformly over $\mathcal{C}_0 = \mathcal{X} \setminus \bigcup_{m = 1}^{M} \mathcal{C}_m$, and let $\epsilon \in [0,1]$ be the fraction of background noise.
+The mixture distribution $\Pbb$ is therefore
+\begin{equation*}
+\Pbb = \frac{1 - \epsilon}{M} \sum_{m = 1}^{M} \Psi_m + \epsilon \Psi_0,
+\end{equation*}
+where $\Psi_m$ is the uniform distribution over $\Cset_m$.
+
+Note that when $\epsilon$ is sufficiently small, for an appropriate choice of threshold $\lambda$ the density clustering will be $\Cbb_f(\lambda) = \set{\Cset_1,\ldots,\Cset_M}$.
+In this setup, therefore, estimating a density cluster is equivalent to recovering a mixture component.
+\subsection{1d uniform example.}
+
+We show the performance of our bounds in a mixture of uniforms in $\Reals$, and compare with the bound obtained via a global spectral clustering approach.
+
+\subsection{General uniform example.}
+
+We show the performance of our bounds in a mixture of uniforms in $\Reals^d$, and compare with the bound obtained via a density estimation approach.
+
+\subsection{Lower bound.}
+
+The theory we have developed so far gives tighter guarantees for plug-in density cluster estimators than for PPR.
+However, in both cases these are merely upper bounds on the clustering error.
+Now, we provide accompanying lower bounds for the PPR algorithm.
+These will demonstrate that there exist densities for which consistent estimation of density clusters is still possible, but for which \emph{PPR} will provably fail to recover density clusters (with high probability.) Moreover, they will show that the difficulty function $\kappa(\Cset)$ exhibits the right dependence on (some of) the geometric parameters we have introduced.
+
+Our hard case will be a mixture of $2$-uniforms with background noise.
+Given $0 < \sigma < \rho$, let $\mathcal{X} = [-1.5\sigma,1.5\sigma] \times [-.5\rho,.5\rho]$, and let $\Cset_1 = [-1.5\sigma,-.5\sigma] \times [.5\rho,1.5\rho]$, $\Cset_2 = [.5\sigma,1.5\sigma] \times [-.5\rho,.5\rho]$, so that the background noise is sampled over $\Cset_0 = [-.5\sigma,.5\sigma] \times [-.5\rho,.5\rho]$.
+We denote the resulting model by $\Pbb(\sigma,\rho,\epsilon)$ to emphasize the dependence of the distribution on the parameters of interest.
+
+\section{Technical results.}
+
+\subsection{Lower bound.}
+
+Let $\Sset = [-1.5\sigma,1.5\sigma] \times [-\rho/2,0]$. Let the \emph{cut} and \emph{volume} functionals be defined for $\Aset \subset \Rd$ as follows:
+\begin{equation*}
+\cut_{\Pbb,r}(\Aset) := \int_{\Aset} \int_{\mathcal{X} \setminus \Aset} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y), \vol_{\Pbb,r}(\Aset) := \int_{\Aset} \int_{\mathcal{X}} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y)
+\end{equation*}
+and the \emph{normalized cut},
+\begin{equation*}
+\Phi_{\Pbb,r}(\Aset) := \frac{\cut_{\Pbb,r}(\Aset)}{\min\{\vol_{\Pbb,r}(\Aset),\vol_{\Pbb,r}(\mathcal{X} \setminus \Aset)\}}.
+\end{equation*}
+
+\textbf{1.} We first upper bound the normalized cut $\Phi_{\Pbb,r}(\Sset)$ and lower bound the normalized cut $\Phi_{\Pbb,r}(\Cset_1)$, using the geometric parameters $\sigma$ and $\rho$, the \textcolor{red}{drop parameter} $\epsilon$, and the radius $r$.
+Our bounds will be crude, but will display the right dependence on these parameters, and so will be sufficient for our purposes.
+
+We begin with the upper bound on $\Phi_{\Pbb,r}(\Sset)$.
+Note that only points $x = (x_1,x_2)$ such that $-r < x_2 < 0$ contribute to the cut of $\Sset$.
+Letting $f$ be the density function of $\Pbb$, we have
+\begin{align*}
+\cut_{\Pbb,r}(\Sset) & \leq \Pbb(\set{x \in \mathcal{X}: -r < x_2 < 0}) \cdot \max_{x \in \mathcal{X}} \Pbb(B(x,r)) \\
+& \leq \frac{3 r}{\rho} \cdot \frac{\nu_d r^d}{\sigma \rho}.
+\end{align*}
+By symmetry, $\vol_{\Pbb,r}(\Sset) = \vol_{\Pbb,r}(\mathcal{X} \setminus \Sset)$, and therefore it is sufficient to lower bound $\vol_{\Pbb,r}(\Sset)$. We have
+\begin{align*}
+\vol_{\Pbb,r}(\Sset) & \geq \Pbb(\set{x \in \Cset_1 \cap \Sset: \dist(x, \partial \Cset_1) > r}) \cdot \frac{\nu_d r^d}{\sigma \rho} \\
+& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\nu_d r^d}{\sigma \rho}  \\
+& \geq \frac{3\nu_d r^d}{16\sigma \rho},
+\end{align*}
+where the last inequality follows since $r \leq \sigma/4$ and $\sigma < \rho$. Therefore,
+\begin{equation*}
+\Phi_{\Pbb,r}(\Sset) \leq 16 \frac{r}{\rho}.
+\end{equation*}
+Similar manipulations yield a lower bound on $\Phi_{\Pbb,r}(\Cset_1)$.
+We use our estimates of the volume of spherical caps from \textcolor{red}{A.6} to obtain a lower bound on $\cut_{\Pbb,r}(\Cset_1)$,
+\begin{align*}
+\cut_{\Pbb,r}(\Cset_1) & \geq \Pbb(\set{x \in \Cset_1: \dist(x,\Cset_0) < r/32}) \cdot \frac{\nu(\textrm{cap}_{r}(\frac{31r}{32})) \epsilon}{2\rho\sigma} \\
+& \geq \frac{r (1 - \epsilon)}{32 \sigma} \cdot \frac{3 \nu_d r^d \epsilon}{16\rho\sigma}.
+\end{align*}
+and we can immediately upper bound the volume of $\Cset_1$,
+\begin{equation*}
+\vol_{\Pbb,r}(\Cset_1) \leq (1 - \epsilon) \cdot  \frac{(1 - \epsilon)}{\rho \sigma} \nu_d r^d.
+\end{equation*}
+Observe that $\vol_{\Pbb,r}(\mathcal{X} \setminus \Cset_1) \geq \vol_{\Pbb,r}(\Cset_2) = \vol_{\Pbb,r}(\Cset_1)$. Therefore,
 \begin{equation}
-\label{eqn: ppr_vector}
-\pbf = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
+\label{eqn:lb_proof_2}
+\Phi_{\Pbb,r}(\Cset_1) \geq  \frac{\epsilon r}{256 \sigma}.
 \end{equation}
-where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over
-$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
-$v$-th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
-$\vol_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$
-as   
+
+\textbf{2.} The upper bound \eqref{eqn:lb_proof_2} can be extended to hold for all sets $\Aset$ with small symmetric set difference $\Aset \triangle \Cset_1$. Formally,
 \begin{equation}
-\label{eqn: sweep_cuts}
-S_\beta := \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
+\label{eqn:continuity_normalized_cut}
+\Phi_{\Pbb,r}(\Aset) \geq \frac{1}{2\pi} \cdot \frac{\epsilon^2r}{\sigma} \bigl(1 - 4 \cdot \Pbb(\Aset \triangle \Cset_1 )\bigr)
 \end{equation}
-We will use the normalized cut metric to determine which sweep cut $S_{\beta}$
-is the best cluster estimate. For a set $S \subseteq V$ with complement $S^c = V
-\setminus S$, we define \smash{$\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c}
-\Abf_{uv}$}, and \smash{$\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$}.  We
-define the \emph{normalized cut} of $S$ as
+The proof of \eqref{eqn:continuity_normalized_cut} is somewhat involved, and we defer it to the following section.
+
+\textbf{3.} We now convert from population to sample normalized cut.
+\textit{Claim 1:} There exist constants $c_1,c_2$ which may depend on $(\epsilon, \rho, \sigma)$ such that the following statements holds with respect to $c_1,c_2$: For all $n$ such that
+\begin{equation*}
+c_1 \cdot \left(\frac{\log n}{n}\right)^{1/d} \leq r,
+\end{equation*}
+the sample normalized cut of $\Aset$ is lower bounded
+\begin{equation*}
+\Phi_{n,r}(\Aset) \geq \frac{\Phi_{\Pbb,r}(\Aset)}{4} \quad \textrm{for all $\Aset \subset \Rd$,}
+\end{equation*}  
+and the sample normalized cut of $\Sset$ is upper bounded,
+\begin{equation*}
+\Phi_{n,r}(\Sset) \leq \frac{\Phi_{\Pbb,r}(\Sset)}{2}
+\end{equation*}
+with probability at least $1 - \frac{c_2}{n}$.
+
+\textbf{4.}
+
+We prove this claim in a following section.
+
+\subsubsection{Proof of \eqref{eqn:continuity_normalized_cut}}
+To prove \eqref{eqn:continuity_normalized_cut}, we will need to upper bound the cut of $\Aset$, and lower bound the volume.
+We begin by upper bounding the cut, which will be the more difficult of the two.
+To obtain the desired result, we will need to discretize $\Aset$.
+For simplicity, without loss of generality assume $\rho$ and $\sigma$ are constant multiples of $r$.
+For $i = 0,\ldots,\frac{6\sigma}{r} - 1$ and $j = 0,\ldots, \frac{2\rho}{r} - 1$, let
+\begin{equation*}
+B_{ij} = \left[\frac{-3\sigma + ir}{2}, \frac{-3\sigma + (i + 1)r}{2}\right] \times \left[\frac{-\rho + jr}{2}, \frac{-\rho + (j + 1)r}{2}\right] 
+\end{equation*}
+and let $\mathfrak{B} = \set{B_{ij}}$ be the collection of all such boxes. Our discrete version of $\mathcal{A}$ will be a subsets of $\mathfrak{B}$,
+\begin{equation*}
+\overline{\mathcal{A}} := \set{B_{ij} \in \mathfrak{B}: \Pbb(B_{ij} \cap \mathcal{A}) \geq \frac{\Pbb(B_{ij})}{2}}.
+\end{equation*}
+(Note that $\mathcal{C}_1 = \bigcup \overline{\Cset}_1$ where $\overline{\Cset}_1 = \set{B_{ij}: i \in 0,\ldots,\frac{2\sigma}{r} - 1 }$, and is therefore effectively already discretized.)
+The discretization of $\Aset$ is useful for several reasons.
+First, we use it to lower bound the cut of the continuous set $\Aset$.
+Define the boundary of the discretized set $\overline{\mathcal{A}}$ to be
+\begin{equation*}
+\overline{\partial \Aset} = \set{B_{ij} \in \overline{\mathcal{A}}: \exists B_{lk} \in \mathfrak{B} ~\textrm{such that}~\abs{l - i} + \abs{k - j} = 1, B_{lk} \not\in \overline{\mathcal{A}}}.
+\end{equation*}
+All boxes in the boundary $\overline{\partial \Aset}$ contribute substantially to the cut of $\Aset$,
 \begin{equation}
-\label{eqn: normalized_cut}
-\Phi(S; G_{n,r}) := \frac{\cut(S;G_{n,r})}{\min \set{\vol(S; G_{n,r}), \vol(S^c; G_{n,r})}}.
+\label{eqn:lb_proof}
+\cut_{\Pbb,r}(\mathcal{\Aset}) \geq \sum_{B_{ij} \in \overline{\partial\mathcal{A}}} \frac{\Pbb(B_{ij}) \cdot \min_{k,l} \Pbb(B_{kl})}{4}
 \end{equation}
-Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(\frac{1}{40},\frac{1}{11})$}\footnote{The choice of a specific range such as  
-\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate
-\smash{$\Cest = S_{\beta^*}$} that has minimum normalized cut.
-%\smash{$\Phi(S_{\beta^*}; G_{n,r})$}. 
-For concreteness, the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.
-
-\begin{algorithm}
-\caption{PPR on a neighborhood graph}
-\label{alg: ppr}	
-{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume
-$\vol_0 > 0$. \\     
-{\bfseries Output:} cluster $\Cest \subseteq V$.
-\begin{algorithmic}[1]
-  \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $p=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
-    ppr_vector}. 
-  \STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
-  $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
-  \STATE Return the cluster \smash{$\Cest = S_{\beta^*}$}, where  
-  $$
-  \beta^* = \argmin_{\beta \in (\frac{1}{40}, \frac{1}{11})}~ \Phi(S_{\beta}; G_{n,r}).
-  $$
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Estimation of density clusters} 
-Let \smash{$\Cbb_f(\lambda)$} denote 
-the connected components of the density upper level set $\{x \in \Rd: f(x) >
-\lambda\}$.  For a given density cluster \smash{$\Cset \in \Cbb_f(\lambda)$}, we
-call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}. The
-size of the symmetric set difference between estimated and empirical clusters is 
-a commonly used metric to quantify cluster estimation error
-\citep{korostelev1993,polonik1995,rigollet2009}.
-
-\begin{definition}[Symmetric set difference]
-  \label{def: symmetric_set_diff}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-  $\mathcal{S} \subseteq \Reals^d$, we define   
+Moreover, the symmetric set difference $\Aset \triangle \Cset_1$ can be related to the symmetric set difference $\overline{\Aset} \triangle \overline{\Cset}_1$,
 \begin{equation}
-    \label{eqn: misclassification_rate}
-    \Delta(\Cest, \mathcal{S}) := \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup
-      \mathcal{S}[\Xbf] \setminus \Cest},
+\label{eqn:lb_proof_1}
+\Pbb(\Aset \triangle \Cset_1) \geq \sum_{B \in \overline{\Aset} \triangle \overline{\Cset}_1} \frac{\Pbb(B_{ij})}{2}.
 \end{equation}
-  the cardinality of the symmetric set difference between 
-  \smash{$\Cest$} and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$. 
-\end{definition}
-
-However, the symmetric set difference does not measure whether \smash{$\Cest$} 
-can distinguish any two distinct clusters \smash{$\Cset,\Cset' \in
-  \Cbb_f(\lambda)$}. We therefore also study a second notion of cluster
-estimation, first introduced by \citet{hartigan1981}, and defined
-asymptotically.
-
-\begin{definition}[Consistent density cluster estimation]
-  \label{def: consistent_density_cluster_estimation}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster 
-  \smash{$\Cset \in \Cbb_f(\lambda)$}, we say \smash{$\Cest$} is a consistent 
-  estimator of $\Cset$ if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with
-  $\Cset \not= \Cset'$, the following holds as $n \to \infty$: 
-  \begin{equation}
-    \label{eqn: consistent_density_cluster_recovery}
-    \Cset[\Xbf] \subseteq \Cest \quad \text{and} \quad
-    \Cest \cap \Cset'[\Xbf] = \emptyset,
-  \end{equation}
-  with probability tending to 1.
-\end{definition}
-\noindent Consistent cluster recovery roughly ensures that, for a given $\lambda$, the estimated cluster $\Cest$ contains all
-points in a true
-density cluster $\Cset$, and simultaneously does not contain any points in any other density cluster $\Cset'$.
-
-With these definitions in place, our broad goal will be to understand the extent to which the PPR algorithm is able to
-recover a cluster which either guarantees low symmetric set difference to a true density cluster, or which consistently estimates
-a true density cluster.
-
-%\subsection{Our Contributions}
-
-\subsection{Related Work and Our Contributions}
-In addition to the background on local spectral
-clustering given previously, a few related lines of work are worth
-highlighting. \citet{shi2009} and \citet{schiebinger2015} examine the consistency of  
-spectral algorithms in recovering the latent labels in certain
-nonparametric mixture models. Their results focus on global rather than local 
-methods, and thus impose global rather than local conditions on the nature
-of the density. Moreover, they do not in general guarantee recovery of density 
-clusters, which is the focus in our work. Perhaps most importantly, these works
-rely on general cluster saliency conditions, which implicitly depend on many
-distinct geometric aspects of the cluster $\Cset$ under consideration. We make
-this dependence more explicit, and in doing so expose the role each geometric
-condition plays in the clustering problem.
-
-More broadly, density clustering and level set estimation is a well-studied
-problem. \citet{polonik1995, rigollet2009} study density clustering under the 
-symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
-minimax optimal level-set estimators under Hausdorff loss and
-\citet{hartigan1981, chaudhuri2010, balakrishnan2013} consider consistent estimation of the
-cluster tree.
-%, to note but a few works. 
-We emphasize that our goal is not to improve on these
-results, nor to offer a better algorithm for level set estimation; indeed, seen as
-a density clustering algorithm, PPR has none of the optimality guarantees 
-found in the aforementioned works. Instead, our motivation is to start with a 
-widely-used local spectral method, PPR, and to better understand and
-characterize the distinctions between those density clusters which are
-well-conditioned for PPR, and those which are not.
-
-A summary of our results (and an outline for this
-paper) is as follows.
-
-\begin{enumerate}
-\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce
-  a set of natural geometric conditions on the density cluster $\Cset$
-  %formalize a measure of difficulty based on these geometric conditions, 
-  and show that when Algorithm \ref{alg: ppr} is properly initialized, the size of
-  the symmetric set difference of \smash{$\Cest$} and a thickened version of the
-  density cluster $\Csig$ can be bounded in a meaningful way.
-  % this difficulty measure.
-
-\item We further show in Section \ref{sec:
-    consistent_cluster_estimation_with_ppr} that if the density cluster 
-  $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
-  will consistently estimate a density cluster in the sense of
-  \eqref{eqn: consistent_density_cluster_recovery}.
-
-\item In Section \ref{sec: analysis}, we detail some of the analysis required to
-  prove our main results, and expose the parts various geometric quantities play 
-  in the difficulty of the clustering problem.
-
-\item In Section \ref{sec: experiments}, we empirically investigate the
-  tightness of our analysis, and provide examples showing how violations of our
-  geometric conditions impact density cluster recovery by PPR.
+Next, divide $\mathcal{X}$ into rectangles horizontally, $\mathfrak{R}_j = \set{B_{ij}: i = 0,\ldots,\frac{6\sigma}{r} - 1}$. We divide our analysis into cases. For each $j$, one of
+\begin{enumerate}[(i)]
+	\item $\overline{\Aset} \cap \mathfrak{R}_j = \emptyset$, and therefore $(\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j = \overline{\Cset}_1 \cap \mathfrak{R}_j$, or
+	\item $\overline{\Aset} \cap \mathfrak{R}_j = \mathfrak{R}_j$, and therefore $(\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j \supset \overline{\Cset}_2 \cap \mathfrak{R}_j$, or
+	\item $\overline{\partial\mathcal{A}} \cap \mathfrak{R}_j \neq \emptyset$.
 \end{enumerate}
-
-\noindent At this point we summarize one of our main takeaways: 
-PPR, run on a neighborhood graph, recovers \emph{geometrically
-compact} high-density clusters. Our main theoretical results, make this takeaway 
-precise, and provide concrete ways of quantifying the geometric
-compactness of a density cluster. To complement this, we also provide experimental
-evidence that the PPR algorithm can fail to recover high-density clusters which are not
-geometrically compact.
-
-\section{Estimation of well-conditioned density clusters}
-\label{sec: consistent_cluster_estimation_with_ppr}
-
-We formalize some geometric conditions, and use these to define a condition
-number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
-of $\kappa(\Cset)$.)
-
-\paragraph{Geometric conditions on density clusters.} At a high level, for PPR
-to be successful, the underlying density cluster must be geometrically
-well-conditioned.  At a minimum, we want to avoid sets that contain arbitrarily
-thin bridges or spikes.  Hence, as in \citet{chaudhuri2010}, we consider a
-thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
-$\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$, which 
-we call the \emph{$\sigma$-expansion} of $\Cset$. Here 
-\smash{$\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$}.  We now list our
-conditions on $\Csig$.
-
-\begin{enumerate}[label=(A\arabic*)]
-\item
-  \label{asmp: bounded_density}
-  \emph{Bounded density within cluster:} There exist constants
-  $0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
-  $\lambda_{\sigma} \leq \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x)
-  \leq \Lambda_{\sigma}$.
-
-\item
-  \label{asmp: cluster_separation}
-  \emph{Cluster separation:}
-  For all clusters $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$, 
-  $\dist(\Csig,\Csig') > \sigma$, where $\dist(\Csig,\Csig') := \inf_{x
-    \in \Csig} \dist(x,\Csig')$.
-
-\item 
-  \label{asmp: low_noise_density}
-  \emph{Low noise density:} There exist $\gamma,c_0 > 0$ such that for 
-  $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-  $\inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}$.
-
-  %%% AJG 5/20: Should I turn this into two conditions?
-\item
-  \label{asmp: embedding}
-  \emph{Lipschitz embedding:}
-  There exists $g: \Reals^d \to \Reals^d$ with the following properties: i)
-  we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
-  with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =:
-  \diam < \infty$; ii) $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
-  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$; and iii) for some $L
-  \geq 1$,   
-  \begin{equation*}
-    \frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~
-    \text{for all $x,y \in \mathcal{K}$}. 
-  \end{equation*}
-  Succintly, $\Csig$ is the image of a convex set with finite diameter 
-  under a  measure preserving, bi-Lipschitz transformation.
-
-\item
-  \label{asmp: bounded_volume}
-  \emph{Bounded volume:}
-  Let the neighborhood graph radius $0 < r \leq \sigma/2d$ be such that
-  \begin{equation*}
-    2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx,
-  \end{equation*}
-  where $B(x,r)$ is the closed ball of radius $r$ at $x$.
-\end{enumerate}
-
-To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
-(V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
-of subset $S$ satisfies, for a constant $c>0$,
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference_1}
-\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
-\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
-\end{equation}
-where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
-  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
-  time} of a random walk over the induced subgraph $G[S]$ (to be defined
-precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
-\eqref{eqn:  graph_symmetric_set_difference_1} resembles a (degree-weighted) 
-form of the symmetric set difference metric in \eqref{eqn:
-  misclassification_rate}.  As we will show in Section \ref{sec:
-  analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
-  bounded_volume} allow us to upper bound the normalized cut 
-\smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.\footnote{Informally, assumptions  
-\ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
-bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
-yields a lower bound on \smash{$\vol(\Csig[\Xbf]; G_{n,r})$}; together with 
-\ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
-the other hand, \ref{asmp: bounded_density}, \ref{asmp: embedding} preclude
-bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
-with the upper bound on diameter in \ref{asmp: embedding}, this leads to an upper bound on
-the mixing time over this subgraph.}
-
-\paragraph{Condition number.} Motivated by \eqref{eqn:
-  graph_symmetric_set_difference_1}, we will define $\kappa(\Cset)$ to be an
-upper bound on the product \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
-  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. The smaller $\kappa(\Cset)$ is, the
-more success PPR will have in recovering $\Cset$. Let $\theta := (r, \sigma,
-\lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain the
-geometric parameters from \ref{asmp:  bounded_density}--\ref{asmp:
-  bounded_volume}.
-
-\begin{definition}[Well-conditioned density clusters]
-  For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy 
-  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some
-  $\theta$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified
-  later, we set 
-  \begin{equation}
-    \label{eqn: condition_number_1}
-    \Phibf(\theta) 
-    := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
-    \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma +
-        1})}{\lambda_{\sigma}},~  
-    \taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
-      L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3,
-  \end{equation}
-  and letting \smash{$\kappa(\Cset) := \Phi_{u}(\theta) \cdot
-    \tau_{u}(\theta)$}, we call $\Cset$ a 
-  \emph{$\kappa$-well-conditioned density cluster}.  
-\end{definition}
-
-We note that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
-on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in our analysis
-later, in Section \ref{sec: analysis}.
-
-\paragraph{Well-initialized algorithm.} As is typical in the local clustering
-literature, our algorithmic results will be stated with respect to specific
-ranges of each of the user-specified parameters. In particular, for a
-well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
-require 
-\begin{equation}
-\begin{gathered}
-\label{eqn: initialization}
-0 < r \leq \frac{\sigma}{2d}, \quad 
-\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)}, \\
-v \in \Csig[\Xbf]^g, \quad
-\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, 
-\end{gathered}
-\end{equation}
-where \smash{$\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$} will be some large
-(``good'') subset of $\Csig[\Xbf]$. In particular, abbreviating $\vol_{n,r}(S)
-:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, we will have
-\smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$}.
-
-\begin{definition}
-If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn:
-  initialization} for some well-conditioned density cluster $\Cset$, we
-say the algorithm is \emph{well-initialized}. 
-\end{definition}
-
-In practice it is clearly not feasible to set hyperparameters based on the
-underlying (unknown) density $f$. Typically, one tunes PPR over a range of
-hyperparameters and optimizes for some criterion such as minimum normalized cut;
-it is not obvious how this scheme would affect the performance of PPR in the
-density clustering context.
-
-\paragraph{Main theorems.} The results of Section \ref{sec: analysis}, combined 
-with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
-volume of \smash{$\Cest \setminus \Csig[\Xbf]$} and \smash{$\Csig[\Xbf]
-  \setminus \Cest$},  
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus
-\Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]). 
-\end{equation}
-To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
-on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
-want to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and
-so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$. Let
-$\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure
-of the unit ball $B = B(0,1)$. 
-\begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{5}
-\item 
-  \label{asmp: valid_region}
-  \emph{Regular support:} There exists some constant $\lambda_{\min} > 0$ such 
-  that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$. Additionally, there
-  exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$,
-  $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$. 
-\end{enumerate}
-Note that the latter condition in \ref{asmp: valid_region} will hold if the
-boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
-main bound on the symmetric set difference metric.
-
-\begin{theorem}
-  \label{thm: misclassification_rate}
-  Fix $\lambda > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
-  additionally assume that $f$ satisfies \ref{asmp: valid_region}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >
-  0$ such that with probability tending to 1 as $n \to \infty$,  
-  \begin{equation}
-    \label{eqn: misclassification_rate_ub}
-    \Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
-    \frac{\Lambda_{\sigma}}{\lambda_{\min}}. 
-  \end{equation}
-\end{theorem}
-
-The proof of Theorem \ref{thm: misclassification_rate}, along with all other
-proofs in this paper, is deferred to the appendix. Note that this 
-result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
-  \Cest)$} is proportional to the difficulty of the clustering problem, as
-measured by the condition number $\kappa(\Cset)$.
-
-Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
-  misclassification_rate_ub} imply consistent density cluster estimation in the 
-sense of \eqref{eqn: consistent_density_cluster_recovery}. This notion of
-consistency requires a uniform bound over $\pbf$: for all \smash{$\Cset'
-  \in \Cbb_f(\lambda), \Cset' \neq \Cset$}, and each $u \in \Cset, w \in
-\Cset'$,  
-\begin{equation}
-\label{eqn: ppr_gap}
-\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq
-\frac{p_u}{\Dbf_{uu}}, 
-\end{equation}
-so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e., any
-sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions
-laid out in \eqref{eqn: consistent_density_cluster_recovery}. In Theorem
-\ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently
-small upper bound on $\kappa(\Cset)$ ensures that such a gap exists with probability
-1 as $n \to \infty$, and hence guarantees \smash{$\Cest$} will be a consistent  
-estimator. As was the case before, we wish to preclude arbitrarily low degree
-vertices, this time for points $x \in \Cset'[\Xbf]$. 
-\begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{6}
-\item 
-  \label{asmp: C'_bounded_density}
-  \emph{Bounded density in other clusters:} Letting $\sigma,\lambda_{\sigma}$ be 
-  as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and
-  for all $x \in \Csig'$, $\lambda_{\sigma} \leq f(x)$. 
-\end{enumerate}
-
-Next we give our main result on consistent cluster recovery by PPR.
-
-\begin{theorem}
-  \label{thm: consistent_recovery_of_density_clusters}
-  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
-  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
-  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
-  such that if  
-  \begin{equation}
-    \label{eqn: kappa_ub}
-    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
-      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
-  \end{equation}
-  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
-  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
-\end{theorem}
-
-\begin{remark}
-  We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
-    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
-    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
-  density cluster $\Cset$ in the sense of \eqref{eqn:
-    consistent_density_cluster_recovery} only when we can guarantee a very small
-  fraction of points will be misclassified. This strong condition is the price
-  we pay in order to obtain the uniform bound of \eqref{eqn: ppr_gap}. 
-\end{remark}
-
-\begin{remark}
-  While taking the radius of the neighborhood graph $r \to 0$ as $n \to
-  \infty$ (thereby ensuring $G_{n,r}$ is sparse) is computationally
-  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
-  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
-  behavior of PPR in this regime. Although the restriction to a kernel
-  function fixed in $n$ is standard for spectral clustering theory
-  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
-  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
-  this is merely looseness in our upper bounds.  
-\end{remark}
-
-\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
-changed this $\epsilon$ to $\varepsilon$.} 
-\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
-  ppr_vector} may be too computationally expensive. To address this limitation,
-\citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
-(aPPR), which we will denote by \smash{$\pbf^{(\varepsilon)}$}. We refer the
-curious reader to \citet{andersen2006} for a formal algorithmic definition of
-the aPPR vector, and limit ourselves to highlighting a few salient points: the
-aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time,
-while satisfying the following uniform error bound: 
-\begin{equation}
-\label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad \pbf(u) - \varepsilon \Dbf_{uu}\leq
-\pbf^{(\varepsilon)}(u) \leq \pbf(u).  
-\end{equation}
-Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
-  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
-leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
-formally state and prove this in Corollary~\ref{cor: appr} in 
-the appendix.
-
-\section{Analysis}
-\label{sec: analysis}
-
-The primary technical contribution of our work is showing that the geometric
-conditions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} translate to 
-meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in
-$G_{n,r}$. In doing so, we elaborate on how some of the geometric conditions
-introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr}
-contribute to the difficulty of the clustering problem.
-
-\paragraph{Normalized cut.} We start with a finite sample upper bound on the
-normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
-simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
-
-\begin{theorem}
-  \label{thm: conductance_upper_bound}
-  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
-  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
-  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
-  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
-  $\epsilon > 0$, if 
-  \begin{equation}
-    \label{eqn: conductance_sample_complexity}
-    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
-      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
-  \end{equation}
-  then with probability at least $1-\delta$, for a universal constant $c_1 > 0$,
-  \begin{equation}
-    \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
-    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
-  \end{equation}
-\end{theorem}
-
-\begin{remark}
-  \label{rmk: diameter}
-  Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
-    conductance_upper_bound}, in contrast to the condition number
-  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This
-  reflects established wisdom regarding spectral partitioning
-  algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
-  to the density clustering setting. It suggests that if the diameter $\rho$ is
-  large, PPR may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is
-  sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized
-  cut in $G_{n,r}$. This intuition will be supported by simulations in Section
-  \ref{sec: experiments}. 
-\end{remark}
-
-\paragraph{Mixing time.} For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
-subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
-$\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write  
-$$
-q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
-$$
-for the $t$-step transition probability of the lazy random walk over $G[S]$
-originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
-for the stationary distribution of this random walk.  (As
-$\Wbf_S$ is the transition matrix of a lazy random walk, 
-it is well-known that a unique stationary distribution exists and is given by 
-\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where we write $\Dbf_S$ for the  
-degree matrix of $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
-\begin{equation}
-\label{eqn: mixing_time}
-\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)}
-  {\pi(u)} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}. 
-\end{equation}
-Next, we give an asymptotic (in the number of vertices $n$) upper bound on
-$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
-
-\begin{theorem}
-  \label{thm: mixing_time_upper_bound}
-  Fix $\lambda > 0$, and assume that \smash{$\Cset \in \Cbb_f(\lambda)$}
-  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
-  for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$. Then, for
-  any \smash{$0 < r < \sigma/2\sqrt{d}$}, with probability 1,
-  \begin{equation} 
-    \label{eqn: mixing_time_upper_bound}
-    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2
-    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{1}{r}\right) + c_3,
-  \end{equation}
-  for $c_2,c_3 > 0$ universal constants. 
-\end{theorem}
-
-The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
-analogous mixing time bounds developed for the mixing time of a
-continuous-space ``ball walk'' over convex sets. To the best of our knowledge, our
-result is the first bound, albeit asymptotic, on the mixing time of random walks
-over neighborhood graphs that is independent of $n$, the number of vertices.
-
-\begin{remark}
-  The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
-  play an important role in proving the upper bound of Theorem \ref{thm:
-    mixing_time_upper_bound}. There is some interdependence between $L$ and
-  $\sigma,\rho$, which might lead one to hope that \ref{asmp: embedding} is
-  non-essential. However, it is not possible to eliminate condition \ref{asmp:
-    embedding} without incurring an additional factor of at least
-  $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for
-  instance, when $\Csig$ is a dumbbell-like set consisting of two balls of
-  diameter $\rho$ linked by a cylinder of radius
-  $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
-  develop theory regarding bi-Lipschitz deformations of convex sets, wherein it
-  is observed that star-shaped sets as well as half-moon shapes of the type we
-  consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding}
-  for reasonably small values of $L$. 
-\end{remark}
-
-\section{Experiments}
-\label{sec: experiments}
-
-We provide numerical experiments to investigate the tightness of our bounds on
-the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
-of PPR on the ``two moons'' dataset. We defer details of the experimental
-settings to the appendix.
-
-\begin{figure}[tb]
-  \centering
-  % \begin{adjustbox}{minipage=\linewidth}
-  %   \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/sample2}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/sample1}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/sigma_normalized_cut_plot}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/sigma_mixing_time_plot}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/diameter_normalized_cut_plot}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
-  \includegraphics[width=0.32\textwidth]{example1plots/diameter_mixing_time_plot}
-  % \caption{}
-  % \end{subfigure}
-  \caption{\it\small Top left and top middle: samples from a geometrically
-    well- and poor-conditioned cluster. The points in $\Cset$ are colored in 
-    red, points in $\Csig \setminus \Cset$ are colored in yellow, and the
-    remaining points in blue. Other panels: empirical normalized cut and mixing
-    time, as a function of $\sigma$ or $\rho$, versus their theoretical upper
-    bounds.} 
-  \label{fig:fig1}
-%  \end{adjustbox}
-\end{figure}
-
-\paragraph{Validating theoretical bounds.}  We investigate the tightness of
-Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-  mixing_time_upper_bound} via simulation. Figure \ref{fig:fig1} compares our
-upper bounds with the actual empirically-computed quantities \eqref{eqn:
-  normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$
-and thickness $\sigma$ of a cluster $\Cset$. The top left and top middle panels
-display the resulting empirical clusters for two different values of
-$\rho,\sigma$.
-
-The bottom left and bottom right panels assure that our mixing  
-time upper bounds track closely the empirical mixing time, in both 2 and 3 
-dimensions.\footnote{We rescaled all values of theoretical upper
-  bounds by a constant, tto mask the effect of large universal constants
-  in these bounds. Therefore only the comparison of slopes, rather than
-  intercepts, is meaningful.} This provides empirical evidence that Theorem
-\ref{thm: mixing_time_upper_bound} has the right dependency on both expansion
-parameter $\sigma$ and diameter $\rho$. The story for the normalized cut panels
-is less obvious. We remark that while, broadly speaking, the trends do not
-appear to match, this gap between theory and empirical results seems largest
-when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
-grows, the slopes of empirical and theoretical curves become more similar.
-
-\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:fig2}, to drive home
-the main implications of Theorems \ref{thm: misclassification_rate} and
-\ref{thm: consistent_recovery_of_density_clusters}, we show the
-behavior of PPR, normalized cut, and the density clustering algorithm of
-\citet{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d 
-Gaussian noise), considered a prototypical success story for spectral clustering
-algorithms. The first column shows the empirical density clusters $\Cset[\Xbf]$
-and $\Cset'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the 
-second column shows the cluster recovered by PPR; the third column shows the
-global minimum normalized cut, computed according to the algorithm of
-\citet{szlam2010}; and the last column shows a cut of the density cluster tree
-estimator of \citet{chaudhuri2010}.  We can see the degrading ability of PPR to
-recover density clusters as the two moons become less well-separated. Of 
-particular interest is the fact that PPR fails to recover one of the moons even
-when normalized cut still succeeds in doing so, supporting our claim from Remark
-\ref{rmk: diameter}. Additionally, we note that the Chaudhuri-Dasgupta algorithm 
-succeeds even when both PPR and normalized cut fail.  While our main message was
-that PPR recovers geometrically well-conditioned density clusters, it would be  
-interesting to establish that it \emph{only} recovers such clusters, a direction
-for future work.
-
-\begin{figure}
-  \centering
-  % \begin{adjustbox}{minipage=\linewidth}
-  %   \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth,scale = .5]{example2plots/row1_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  \caption{\it\small True density (column 1), PPR (column 2), normalized
-    cut (column 3) and estimated density (column 4) clusters for 3 different 
-    simulated data sets. Seed node for PPR denoted by a black cross.} 
-  \label{fig:fig2}
-  %\end{adjustbox}
-\end{figure}
-
-\section{Discussion}
-\label{sec: discussion}
-
-There are an almost limitless number of ways to define what the ``right''
-clustering is. In this paper, we have considered one such notion---density upper
-level sets---and have detailed a set of natural geometric criteria which, when 
-appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We do not, however, provide theory to show that our geometric
-conditions are required for successful recovery of a density level set. This
-seems to be supported by our empirical results, and it remains a direction for 
-future work.
-
-\section{Acknowledgements}
-SB is grateful to Peter Bickel, Martin Wainwright and Larry Wasserman for helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
-
-\appendix
-
-%In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
-\section{Proof of Theorem \ref{thm: conductance_upper_bound}}
-\label{sec: proof_of_theorem_1}
-
-For notational ease, we write
+occurs.
+Moreover, (a) for every row $\mathfrak{R}_j$, $\abs{\overline{\Cset}_1 \cap \mathfrak{R}_j} =  \abs{\overline{\Cset}_2 \cap \mathfrak{R}_j} = \frac{2\sigma}{r}$, and (b) for every $B_{ij} \in \overline{\Cset}_1 \cup \overline{\Cset}_2$, the probability
+\begin{equation*}
+\Pbb(B_{ij}) \geq  \frac{r^2(1 - \epsilon)}{4\rho \sigma}.
+\end{equation*}
+Therefore, letting $J_1 = \set{j: \textrm{(i) occurs}}$, and similarly $J_2 = \set{j: \textrm{(ii) occurs}}$ and  $J_3 = \set{j: \textrm{(iii) occurs}}$, we have from \eqref{eqn:lb_proof_1} that
 \begin{align*}
-\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
-\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+\Pbb(\Aset \triangle \Cset_1) & \geq \sum_{j = 0}^{\frac{2\rho}{r} - 1} \sum_{B \in (\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j} \frac{\Pbb(B_{ij})}{2} \\
+& \geq \left(\abs{J_1} + \abs{J_2}\right) \cdot \frac{\sigma}{r} \cdot \frac{r^2(1 - \epsilon)}{4\rho \sigma} \\
+& = \left(\frac{2\rho}{r} - \abs{J_3}\right) \frac{r(1 - \epsilon)}{4\rho}
 \end{align*}
-for the random variable, mean, and probability of cut size and volume, respectively.
-
-With this notation in place, the goal of Theorem~\ref{thm: conductance_upper_bound} is roughly to show that, with probability at least $1 - \delta$, for a universal constant $c_1 > 0$ and for any $\epsilon > 0$, for a sufficiently large sample size $n$:
-\begin{align*}
-\Phi_{n,r}(\Csig[\Xbf]) := \frac{\cut_{n,r}}{\min\{\vol_{n,r}, \vol_{n,r}^c\}} \leq c_1 \frac{d}{\sigma}
-    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
-\end{align*}
-
-The proof of this theorem follows essentially from two technical Lemmas. 
-The following Lemma relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values.
-\begin{lemma}
-	\label{lem: prob_bound_cutvol}
-	For any $\delta \in (0,1]$,
-	\begin{equation}
-	\label{eqn: numerator_additive_bound}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}}, \\ 
-	\frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, \\
-	\frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}},
-	\end{equation}
-	each with probability at least $1 - \delta$. 
-\end{lemma}
-We note that as a consequence of~\ref{asmp: bounded_volume} we have that $p_V^c \geq p_V$, so it will suffice to lower bound $p_V$ (since a lower bound for $p_V^c$ follows).
-The 
-following result provides upper and lower bounds on the expected values $p_K$ and $p_V$ respectively:
-\begin{lemma}
-	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+Rearranging, we obtain
+\begin{equation*}
+\abs{J_3} \geq \frac{2\rho}{r}\left(1 - \frac{2\Pbb(\Aset \triangle \Cset_1)}{1 - \epsilon}\right) \geq \frac{2\rho}{r}\left(1 - 4\Pbb(\Aset \triangle \Cset_1)\right)
+\end{equation*}
+since \textcolor{red}{$\epsilon < 1/2$.} From \eqref{eqn:lb_proof} and the prior inequality, we have
 \begin{align}
-	p_K &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
-	p_V &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
+\cut_{\Pbb,r}(\Aset) & \geq \sum_{j = 0}^{\frac{2\rho}{r} - 1} \sum_{B_{ij}} \frac{\Pbb(B_{ij}) \cdot \min_{k,l} \Pbb(B_{kl})}{4} \nonumber \\
+& \geq \abs{J_3} \frac{r^4\epsilon^2}{16\rho^2\sigma^2} \nonumber \\
+& \geq \frac{\epsilon r}{2\sigma} \cdot \frac{r^2 \epsilon}{\rho\sigma} \cdot \bigl(1 - 4\Pbb(\Aset \triangle \Cset_1)\bigr) \label{eqn:lb_proof_3}
 \end{align}
-\end{lemma}
-%\begin{lemma}
-%	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-%	\begin{equation*}
-%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).
-%	\end{equation*}
-%\end{lemma}
-
-Taking these two technical lemmas as given we can now complete the proof of the theorem. 
-We fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-\begin{equation}
-\label{eqn: conductance_representation_1}
-\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
-\end{equation}
-By a union bound we see that all three bounds in \eqref{eqn: numerator_additive_bound} hold with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this yields the upper bound \sbcomment{Changed $\mathbf{X}$ to $X$}
-\begin{equation*}
-\Phi_{n,r}(\Csig[X]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
-\end{equation*}
-for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-Now, some straightforward algebraic manipulations yield,
-\begin{align*}
-\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
-& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
-\end{align*}
-
-%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
-All that remains is some algebra, which we take care of below.
-
-\noindent Using Lemma \ref{lem: expected_density_cut}, we have
-\begin{equation*}
-\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-\end{equation*}
-Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-\begin{equation*}
-n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
-\end{equation*}
-which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$, and this yields the desired bound on $\Phi_{n,r}(\Csig[X])$. In order to complete the proof of
-the theorem it remains to prove Lemmas~\ref{lem: prob_bound_cutvol} and~\ref{lem: expected_density_cut}.
-
-\subsection{Proof of Lemma~\ref{lem: prob_bound_cutvol}}
-We first note that we can write $\cut_{n,r}$ as a double sum,
-	\begin{equation}
-	\label{eqn: density_cut_expansion}
-	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r),
-	\end{equation}
-	and similarly we can write $\vol_{n,r}$ as a sum of indicator functions,
-	\begin{equation}
-	\label{eqn: volume_expansion}
-	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r)).
-	\end{equation}
-From this we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-	\end{equation*}
-	with kernels
-	\begin{align*}
-	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{align*}
-	Similarly,
-	\begin{equation*}
-	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-	\end{equation*}
-	with kernel,
-	\begin{equation*}
-	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{equation*}
-	Appealing to a standard concentration inequality for U-statistics (see Lemma \ref{lem: bounded_difference}) we therefore have
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation*}
-	each with probability at least $1 - \delta$. 
-	%The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$.
-
-\subsection{Proof of Lemma~\ref{lem: expected_density_cut}}
-We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
-We 
-let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
-Our goal will be to upper bound $p_K$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
-and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
-%Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
-\begin{lemma}
-	\label{lem: expected_number_boundary_points}
-	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-	\begin{equation*}
-	\Pbb(\Csigr) \leq \frac{2dr}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-	\end{equation*}	
-\end{lemma}
-\noindent Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
-\begin{equation*}
-\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr).
-\end{equation*}
-In order to lower bound $p_V$ we will show the following lower bound on the uniform local conductance:
-\begin{lemma}
-	\label{lem: local_conductance}
-	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
-	\begin{equation*}
-	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
-	\end{equation*}
-\end{lemma}
-Taking these two results as given we can now prove each of the two claims~\eqref{eqn:claim_one} and~\eqref{eqn:claim_two} in turn.
-\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } Recalling,~\eqref{eqn: density_cut_expansion} 
-	and by the linearity of expectations, we obtain
-	\begin{equation*}
-	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
-	\end{align*}
-	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
-Then, upper bounding the integral using \sbcomment{I changed the Lemma referenced here.
-I think it was wrong before} Lemma \ref{lem: expected_number_boundary_points} gives the final result.
-
-%\subsection{Proof of Lemma~\ref{Z}}
-\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } Recalling,~\eqref{eqn: volume_expansion}
-%The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. 
-	and by the linearity of expectation we obtain
-	\begin{equation*}
-	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-	\end{align*}
-	whence the claim then follows by Lemma \ref{lem: local_conductance}.
-It remains to prove Lemmas~\ref{lem: expected_number_boundary_points} and~\ref{lem: local_conductance}, and we turn our attention to this next.
-\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
-The proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
-	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
-	\begin{equation*}
-	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
-	\end{equation*}
-	\sbcomment{Changed $t_i$ to $t_{i,k}$.}
-	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
-	\begin{equation}
-	\label{eqn: partition_ub}
-	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
-	\end{equation}
-	Assumptions~\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
-	\begin{equation*}
-	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
-	\end{equation*}
-	and writing
-	\begin{equation*}
-	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
-	\end{equation*}
-	we have
-	\begin{align}
-	\label{eqn: telescoping_sum}
-	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
-	& = \underbrace{\sum_{i = 1}^{k} 
-	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
-	\end{align}
-	\sbcomment{I changed the braces above -- I think they were incorrect earlier} where the second equality comes from rearranging terms in the sum.
-
-	% AJG 5/14/19: This argument makes sense, correct?
-	We first consider the term $\Sigma_k$.
-$\Cset$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
-Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
-As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
-	\begin{equation}
-	\label{eqn: slice_volume_bound}
-	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
-	\end{equation}
-	which in turn gives
-	\begin{align}
-	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
-	\end{align}
-	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
-	\begin{align}
-	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
-	\end{align}
-	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
-
-	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
-	\begin{align}
-	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
-\label{eqn: xi_ub}
-	\end{align}
-	where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}.
-As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
-
-%\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
-
-\subsection{Proof of Lemma~\ref{lem: local_conductance}}
-The proof of this result relies on estimates of the volume of spherical caps which we defer to Appendix~\ref{sec:caps}.
-	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as $B(x,\sigma) \subseteq \Csig$,
-	\begin{equation*}
-	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr)
-	\end{equation*}
-	Without loss of generality, let $\norm{u - x} = \sigma$; it is not hard to see that if $\norm{u - x} < \sigma$, the volume of the overlap will only grow.
-Then, since $\norm{u  - x} = \sigma$, $B(u, r) \cap B(x, \sigma)$ contains a spherical cap of radius $r$ and height
-	\begin{equation*}
-	h = r - r^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
-	\end{equation*}	
-	which by Lemma \ref{lem: volume_of_spherical_cap} has volume
-	\begin{equation*}
-	\nu_{\text{cap}} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
-	\end{equation*}
-	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{16d}$. 
-	By Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
-	\begin{align*}
-	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{4\sqrt{d}} \\
-	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{\pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
-	\end{align*}
-
-\subsection{Volume Estimates}
-\label{sec: volume_estimates}
-%\section{Proofs}
-%
-%Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
-In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
-The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
-Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
-
-%\subsection{Volume estimates}
-
-We begin by recalling some notation.
-We let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
-Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
-Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
-
-Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
-
-\begin{lemma}
-	\label{lem: expansion_volume}
-	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
-	\begin{equation}
-	\label{eqn: expansion_volume}
-	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We will show that for any $\epsilon > 0$, 
-	\begin{equation}
-	\label{eqn: ratio_of_volume}
-	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
-	\end{equation}
-	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
-
-	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
-	\begin{equation*}
-	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
-	\end{equation*}
-	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
-	\begin{equation*}
-	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
-	\end{equation*}
-	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
-	\begin{equation}
-	\label{eqn: finite_subcover}
-	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
-	\end{equation}
-	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
-Summarizing our findings, we have
-	\begin{equation}
-	\label{eqn: finite_subcover-1}
-	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon).
-	\end{equation}
-\noindent	We next show a lower bound on $\nu(\Asig)$.
-Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
-	\begin{equation*}
-	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
-	\end{equation*}
-	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$.
-As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
-	\begin{align*}
-	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
-	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
-	\begin{equation*}
-	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
-	\end{equation*}
-As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
-	\begin{equation*}
-	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
-	\end{equation*}
-	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
-	\begin{align*}
-	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
-	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
-	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
-\end{proof}
-\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
-\begin{lemma}
-	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
-	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
-	\begin{equation*}
-	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
-	\begin{equation*}
-	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
-	\end{equation*}
-	since then
-	\begin{equation*}
-	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
-	\end{equation*}
-
-	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
-	\begin{equation}
-	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
-	\end{equation}
-	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
-Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
-	\begin{equation*}
-	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
-	\end{equation*}
-	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
-\end{proof}
-
-We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
-\begin{lemma}
-	\label{lem: Taylor_series}
-	For any $0 \leq x \leq 1/2d$,
-	\begin{align*}
-	(1 + x)^d & \leq 1 + 2\dx \\
-	(1 - x)^d & \geq 1 - 2\dx.
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	We take the binomial expansion of $(1 + x)^d$:
-	\begin{align*}
-	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
-	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
-	\end{align*}
-The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
-\end{proof}
-
-\subsection{Spherical Caps and Associated Estimates}
-\label{sec:caps}
-In this section, we state a result for the volume of a spherical cap and derive some 
-useful upper bounds. 
-\begin{lemma}
-	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha := 1 - \frac{2 r h - h^2}{r^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
-	\end{equation*}
-	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
-\end{lemma}
-
-The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
-an upper bound on the ratio of Gamma functions. 
-\begin{lemma}
-	\label{lem: beta_integral}
-	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write 
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
-	\end{equation*}
-	The first integral is simply the beta function, with
-	\begin{equation*}
-	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
-	\end{equation*}
-	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
-	\begin{equation*}
-	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
-	\end{equation*}
-	As a result,
-	\begin{align*}
-	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
-	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
-	& \overset{\text{(iv)}}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
-	& =  3\alpha^{1/2}.
-	\end{align*}
-	where $\text{(iv)}$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
-\end{proof}
-
-\begin{lemma}
-	\label{lem: beta_function}
-	\begin{equation*}
-	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
-	\end{equation*}
-\end{lemma}
-\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
-
-%\subsection{Density-weighted cut and volume estimates}
-%\label{sec: density_weighted_cut_and_volume_estimates}
-%
-%For notational ease, we write
-%\begin{align*}
-%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
-%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
-%\end{align*}
-%for the random variable, mean, and probability of cut size and volume, respectively. 
-%
-%\begin{lemma}
-%	\label{lem: expected_density_cut}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-%	\begin{equation*}
-%	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%
-%\end{proof}
-%
-%\begin{lemma}
-%	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-%	\begin{equation*}
-%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
-%	\begin{equation}
-%	\label{eqn: volume_expansion}
-%	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
-%	\end{equation}
-%	and by linearity of expectation we obtain
-%	\begin{equation*}
-%	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-%	\end{equation*}
-%	Writing this with respect to the density function $f$, we have
-%	\begin{align*}
-%	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-%	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-%	\end{align*}
-%	whence the claim then follows by Lemma \ref{lem: local_conductance}.
-%\end{proof}
-%
-%To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
-%\end{equation*}
-%to $p_K$ and $p_V$. 
-%
-%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
-These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
-%
-%\begin{lemma}
-%	\label{lem: prob_bound_cutvol}
-%	For any $\delta \in (0,1]$,
-%	\begin{equation}
-%	\label{eqn: numerator_additive_bound}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
-%	\end{equation}
-%	each with probability at least $1 - \delta$. 
-%\end{lemma}
-%
-%\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
-%	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-%	\end{equation*}
-%	with kernels
-%	\begin{align*}
-%	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-%	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{align*}
-%	
-%	Similarly,
-%	\begin{equation*}
-%	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-%	\end{equation*}
-%	with kernel,
-%	\begin{equation*}
-%	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{equation*}
-%	
-%	From Lemma \ref{lem: bounded_difference} we therefore have
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
-%	\end{equation*}
-%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
-%\end{proof}
-%
-%\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
-%\label{sec: proof_of_theorem_1}
-%
-%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
-All that remains is some algebra, which we take care of below.
-%
-%Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-%\begin{equation}
-%\label{eqn: conductance_representation_1}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
-%\end{equation}
-%Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this means
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
-%\end{equation*}
-%for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-%Now, some straightforward algebraic manipulations yield
-%\begin{align*}
-%\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-%& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
-%& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
-%\end{align*}
-%By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
-%\begin{equation*}
-%\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-%\end{equation*}
-%Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-%\begin{equation*}
-%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
-%\end{equation*}
-%which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
-
-\section{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
-
-Denote $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
-The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that, for universal constants $c_2, c_3,c_4 > 0$, with probability one
-\begin{equation*}
-\limsup_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{c_4 \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
-\end{equation*}
-We follow a two-step approach typically used to establish upper bounds on the mixing time of Markov chains.
-
-In the first step, we relate the mixing time $\tau_{\infty}(G)$ of a generic undirected graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
-We now build to a formal definition of these expansion properties.
-First, we recall the the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well.
-For $u \in V$, $S \subseteq V$,
-\begin{equation*}
-\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G).
-\end{equation*}
-Additionally, we recall the \emph{normalized cut} $\Phi(S;G)$, defined (as in \eqref{eqn: normalized_cut}) as
-\begin{equation*}
-\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}}.
-\end{equation*}
-
-With these functionals in hand, we can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
-\begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
-\end{equation*}
-
-The following Proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
-\begin{proposition}
-	\label{prop: pointwise_mixing_time}
-	Assume $\min_{u \in v} \deg(u; G) \geq 10$. Then,
-	\begin{equation*}
-	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-	\end{equation*}
-\end{proposition}
-
-The second step in our approach is to lower bound the local spread and conductance over the particular graph $\widetilde{G}_{n,r}$.
-The following result provides the desired lower bounds, which hold asymptotically as $n \to \infty$,
-\begin{proposition}
-	\label{prop: local_spread_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one,
-	\begin{equation}
-	\label{eqn: local_spread}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
-	\end{equation}
-	and
-	\begin{equation}
-	\label{eqn: conductance}
-	\liminf_{n \to \infty} \Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
-	\end{equation}
-\end{proposition}
-
-Taking these results as given, the proof of the theorem is more or less complete.
-We note that since $r$ is fixed, \textcolor{red}{with probability one} $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty > 10$, and we may therefore apply Proposition \ref{prop: pointwise_mixing_time} with respect to $\widetilde{G}_{n,r}$.
-Along with Lemma \ref{prop: local_spread_conductance}, this yields
-\begin{equation*}
-\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
-\end{equation*}
-The first term dominates the middle term, and the theorem follows after an appropriate choice of $c_2$ and $c_3$.
-
-\subsection{Proof of Proposition \ref{prop: pointwise_mixing_time}}
-\label{sec: pointwise_mixing_time}
-
-We first generalize some notation from the main text.
-Let $A$ be the adjacency matrix of an undirected graph $G = (V,E)$, and $D$ the associated diagonal degree matrix.
-The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$.
-Denote the $t$-step probability distribution of this random walk, originating from a particular $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
-
-Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
-\begin{equation*}
-d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
-\end{equation*}
-Our goal is to demonstrate that for sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$.
-To do so, we introduce the \emph{total variation distance} between the distributions $q_v^{(t)}$ and $\pi$, given by
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(t)}(u) - \pi(u)}.
-\end{equation*}
-As we will see, an upper bound on the uniform distance can be obtained from an analogous upper bound on the total variation distance.
-First, however, we upper bound the total variation distance $||q_v^{(t)} - \pi||_{\mathrm{TV}}$ as a function of the local spread $s(G)$, the conductance $\Phi(G)$ and the number of steps $t$.
-\begin{lemma}
-	\label{lem: tv_mixing_time}
-	For any $v \in V$, and any $0 < a \leq 1$,
-	\begin{align*}
-	\norm{q_v^{(t + 3)} - \pi}_{\mathrm{TV}} \leq \max\set{as(G), \frac{1}{8} + \frac{1}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} 
-	\\
-	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{align*}
-\end{lemma}
-
-As mentioned, a bound on the total variation distance implies a corresponding bound on the uniform distance $d_{\mathrm{unif}}$, given by the following result:
-\begin{lemma}
-	\label{lem: tv_to_uniform_distance}
-	Let $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
-	\begin{equation*}
-	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
-	\end{equation*}
-\end{lemma}
-
-\noindent Taking these Lemmas as given, we proceed that show that for
-\begin{equation*}
-\tau_1 = \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-\end{equation*}
-the uniform distance $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$, which proves the claim of Proposition \ref{prop: pointwise_mixing_time}.
-Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$.
-Then,
-\begin{equation*}
-\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}
-\end{equation*}
-and so by Lemma \ref{lem: tv_mixing_time},
-\begin{equation*}
-\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{2}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-\end{equation*}
-It is a well known fact \cite{montenegro2002} that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
-Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
-\begin{equation*}
-\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{1}{14 s(G)}
-\end{equation*}
-and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$.
-The proof is complete once we have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}.
-
-\subsection{Proof of Lemma \ref{lem: tv_mixing_time}}
-\label{sec: mixing_time_on_graphs}
-
-We generalize the notation of the previous subsection.
-For a starting distribution $z$ to be specified later, and for $t \geq 0$ an integer, let $q_z^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $z$.\footnote{We say $z$ is a starting distribution over a graph $G$ when $\textrm{supp}(z) \subseteq V$ and $\sum_{u \in V}z(u) = 1$.
-Then, $q_z^{(t)} = zW^t$.}
-
-We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined as
-$h_z^{(t)}, t \geq 0$, 
-\begin{equation*}
-h_q^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}
-\end{equation*}
-where the maximum is over:
-\begin{align*}
-\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
-\end{align*}
-The utility of the Lovasz-Simonovits curve is demonstrated by the following observations. First, note that
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sup_{S \subseteq V} \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation*}
-where we use the standard notation $\pi(S) := \sum_{u \in S} \pi(u)$, and likewise for $q_v^{(t)}(S)$. Moreover, observe that for any $S \subseteq V$ and any integer $t \geq 0$,
-\begin{equation}
-\label{eqn: lovasz_simonivits_1}
-\max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))} \geq \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation}
-Therefore, taking the maximum on both sides of \eqref{eqn: lovasz_simonivits_1}  over all $S \subseteq V$, we have
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \max_{0 \leq x \leq 1} h_v^{(t)}(x).
-\end{equation*}
-Now, take $z = e_vW^3$.
-Observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
-To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$.
-
-To show this upper bound, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$, where $\mu = as(G)$.
-Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,
-\begin{equation*}
-\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
-\end{equation*}
-
-The following technical Lemma collects the upper bounds which hold over $[\mu, 1 - \mu]$ and $[0,\mu) \cup (1 - \mu, 1]$, respectively:
-\begin{lemma}
-	\label{lem: mixing_all_sets}
-	For any $\mu \leq x \leq 1 - \mu$, 
-	\begin{equation}
-	\label{eqn: mixing_large_sets}
-	h_z^{(t)}(x) \leq \ell_{\mu}(x) + \left(\frac{1}{1 - 2\mu} + \frac{1}{\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t.
-	\end{equation}
-	For any $0 < x \leq \mu$ or $1 - \mu \leq x < 1$
-	\begin{equation}
-	\label{eqn: mixing_small_sets}
-	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-	\end{equation}
-\end{lemma}
-\noindent Taking Lemma \ref{lem: mixing_all_sets} as given, we have nearly completed our proof of Lemma \ref{lem: tv_mixing_time}. Note that for any $\mu \leq x \leq 1 - \mu$,
-\begin{align*}
-\ell_{\mu}(x) & \leq \max\set{h_z^{(t)}(\mu),h_z^{(t)}(1 - \mu)} \\
-& \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-\end{align*}
-with the latter inequality following from \eqref{eqn: mixing_small_sets}. Therefore, for any $x \in [0,1]$,
-\begin{equation*}
-h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^t} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{equation*}
-which is the desired result.
-
-\subsection{Proof of Lemma \ref{lem: mixing_all_sets}}
-
-We first prove \eqref{eqn: mixing_large_sets}, and then \eqref{eqn: mixing_small_sets}.
-\paragraph{Proof of \eqref{eqn: mixing_large_sets}:}
-The desired result is a consequence of Theorem 1.2 of \cite{lovasz1990}. To state this theorem, we introduce the notation
-\begin{equation*}
-C_{\mu} = \max \set{\frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu},
-\end{equation*}
-and then the theorem itself.
-\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
-	\label{thm: lovasz_simonovits_1993}
-	For any $0 \leq \mu \leq \frac{1}{2}$, $\mu \leq x \leq 1 - \mu$ and an integer $t \geq 0$,
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_1993}
-	h_z^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation}
-\end{theorem}
-In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show
-\begin{equation}
-\label{eqn: lt_ub_1}
-h_z^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
-\end{equation}
-which will in turn imply
-\begin{align*}
-C_{\mu} & \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \\
-& \leq \frac{1}{\mu} + \frac{1}{1 - 2\mu}.
-\end{align*}
-Plugging this upper bound into \eqref{eqn: lovasz_simonovits_1993}, we obtain
-\begin{align*}
-h_z^{(t)}(x) & \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t \\
-& \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{align*}
-which is the desired result.
-
-It remains to show \eqref{eqn: lt_ub_1}.
-To do so, we make use of an equivalent representation of the Lovasz-Simonovits curve $h_z^{(t)}$.
-Order the elements of $V = \set{u_1, \ldots, u_N}$ ($N$ = $\abs{V}$), such that
-\begin{equation*}
-\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)}
-\end{equation*}
-and let $U_k = \set{u_1, \ldots, u_k}$. Then for any $x$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
-\begin{equation}
-\label{eqn: lovasz_simonovits_curve}
-h_z^{(t)}(x) = \sum_{j = 1}^{k - 1} (q_z^{(t)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q_z^{(t)}(u_k) - \pi(u_k) \right).
-\end{equation}
-The representation of the Lovasz-Simonovits curve given by \eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a concave, piecewise linear curve.
-Moreover, we observe that the slope $v(x)$ of each linear segment of the Lovasz-Simonovits curve satisfies
-\begin{equation}
-\label{eqn: lovasz_simonovits_slope}
--1 \leq v(x) \leq \frac{h_z^{(0)}(\mu)}{\mu}.
-\end{equation}
-Note that $\ell_{\mu}(\mu) = h_z^{(0)}(\mu)$, and for $x \geq \mu$, 
-\begin{equation*}
-h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}
-\end{equation*}
-by the concavity of $h_0$ along with \eqref{eqn: lovasz_simonovits_slope}. Some algebra then yields
-\begin{align*}
-h_z^{(0)}(x) - \ell_{\mu}(x) & \leq h_z^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu)\right) + \frac{h_z^{(0)}(\mu)}{\mu}(x - \mu) \\
-& =  \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(\mu) + \frac{h_z^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu) \\
-& \leq \sqrt{x - \mu} \left(\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} \right)
-\end{align*}
-On the other hand, $\ell_{\mu}(1 - \mu) = h_z^{(0)}(1 - \mu)$, and by the concavity of $h_z^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
-\begin{equation*}
-h_z^{(0)}(x) \leq h_z^{(0)}(1 - \mu) + (1 - x - \mu).
-\end{equation*}
-Similar manipulations to above give the upper bound
-\begin{align*}
-h_z^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
-\end{align*}
-and \eqref{eqn: lt_ub_1} follows.
-
-\paragraph{Proof of \eqref{eqn: mixing_small_sets}:}
-First, we deal with the case $x \leq as(G)$. Letting $U_k$ be as in \eqref{eqn: lovasz_simonovits_curve}, we have
-\begin{equation}
-\label{eqn: mixing_time_small_sets_1}
-h_z^{(t)}(x) \leq q_z^{(t)}(U_{k - 1}) + q_z^{(t)}(u_k)
-\end{equation}
-Recalling that $z = e_vW^3$, we will rely on the key fact that for any $u \neq v, t \geq 1$,
-\begin{equation}
-\label{eqn: mixing_time_small_sets_2}
-q_z^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
-\end{equation}
-On the other hand if $u = v$,
-\begin{equation}
-\label{eqn: mixing_time_small_sets_3}
-q_z^{(m)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
-\end{equation}
-Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
-\begin{equation*}
-h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_k}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
-\end{equation*}
-Finally, since $x \leq a s(G)$, 
-\begin{equation*}
-\abs{U_k} \leq \frac{x}{10 \min_{u \in V}(\pi(v))} \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
-\end{equation*}
-and the desired result is shown.
-
-Now, we turn to the case where $x \geq 1 - as(G)$.
-But since $h_z^{(t)}(1) = 0$, and the slope of $h_z$, $v(x')$ is no less than $-1$ for all $x' \in [0,1]$, this implies $h_z^{(t)}(x) \leq 1 - x \leq as(G)$.
-
-\subsection{Proof of Lemma \ref{lem: tv_to_uniform_distance}}
-
-The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebra. Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
-\begin{align}
-\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
-& \overset{\text{(i)}}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
-& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
-\end{align}
-where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$. Then,
-\begin{align}
-\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
-& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
-& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \frac{1}{s(G)}} \label{eqn: tv_to_uniform_distance_3}
-\end{align}
-since for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well known (see e.g.
-\cite{lovasz1990}) that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and the hypothesis of Lemma \ref{lem: tv_to_uniform_distance},
-\begin{equation*}
-\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \leq \frac{1}{14}.
-\end{equation*}
-Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
-\begin{equation}
-d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{2}{7} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
-\end{equation}
-The recurrence relation of \eqref{eqn: tv_to_uniform_distance_2} along with the initial condition $d_{\textrm{unif}}(q_v^{(t)}, \pi) \leq 1$ yields
-\begin{equation*}
-d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{10}{28} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
-\end{equation*}
-and the claim is shown. We have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}, and therefore Proposition \ref{prop: pointwise_mixing_time}.
-
-\subsection{Proof of Proposition \ref{prop: local_spread_conductance}}
-
-We first prove \eqref{eqn: local_spread} and then \eqref{eqn: conductance}.
-First, we introduce some notation.
-Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
-For $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
-\begin{equation*}
-\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
-\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
-\end{equation*}
-and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
-We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$.
-
-\paragraph{Proof of \eqref{eqn: local_spread}:}
-
-Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
-Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
-\end{equation*}
-
-\paragraph{Proof of \eqref{eqn: conductance}:}
-
-Our goal is to show that with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
-\end{equation*}
-where we let $S^c = \Csig[\Xbf] \setminus S$.
-In order to show this bound holds uniformly over all sets $S \subseteq \Csig[\Xbf]$, we will split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
-To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a random walk over $G = (V,E)$.)
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for sets $S \subseteq \Csig[\Xbf]$ not sufficiently large enough to be in $\mathcal{L}(\widetilde{G}_{n,r})$, the graph normalized cut is of constant order.
-In fact, this statement holds for any graph $G$.
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb_1}
-	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
-	\begin{equation*}
-	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	The claim follows by simple manipulations:
-	\begin{align*}
-	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $\pi(S) \leq s(G)$}\\ 
-	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
-	\end{align*}
-\end{proof}
-
-In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut for the remaining sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then with probability $1$,
-	\begin{equation}
-	\label{eqn: graph_conductance_profile_lb}
-	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
-	\end{equation}
-	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \Csig[\Xbf]: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$.
-\end{lemma}
-
-Taking Lemma \ref{lem: graph_conductance_profile_lb} as given, Proposition \ref{prop: graph_conductance_profile_lb} then follows from that Lemma, along with Lemma \ref{lem: graph_conductance_profile_lb_1}, in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
-We turn now to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
-
-\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}.}
-
-Let $\Sset \subseteq \Csig$ and $S \subseteq \Csig[\Xbf]$.
-The proof of \ref{lem: graph_conductance_profile_lb} will essentially follow from a pair of technical results.
-The first of these will demonstrate that the functional $\widetilde{\Phi}_{n,r}(S)$ can be lower bounded by a population analogue $\widetilde{\Phi}_{\Pbb,r}(\Sset)$, which we term the continuous normalized cut.
-This lower bound will hold uniformly over sets $S \subseteq \Csig[X]$.
-The second technical Lemma will build on known continuous space isoperimetric inequalities to lower bound the population-level quantity $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ uniformly over sets $\Sset \subseteq \Csig$.
-
-We will now build slowly toward a formal definition of the continuous normalized cut, before establishing a relation between it and it's discrete counterpart.
-Let $\Sset, \Sset_1, \Sset_2 \subseteq \Csig$ be measurable.
-We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
-\end{equation*}
-
-Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
-\begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
-\end{equation*}
-Letting the \emph{$\Pbb$-local conductance} be given by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
-\end{equation*}
-a bit of algebra verifies that
-\begin{equation*}
-\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}.
-\end{equation*}
-
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
-\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\piwt_{\Pbb,r}(x), 
-\end{equation*}
-the \emph{($\Pbb$) continuous normalized cut} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
-\end{equation*}
-
-As the functionals $\widetilde{\Phi}_{n,r}$ and $\widetilde{\Phi}_{\Pbb,r}$ act in the different spaces $\Csig[\Xbf]$ and $\Csig$, respectively, it is not obvious how to relate them.
-To do so, we introduce transportation maps between the space $\Csig$ and the sample points $\Csig[\Xbf]$.
-Precisely, define the conditional probability measures
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
-\end{equation*} 
-A measurable map $T: \Csig \to \Csig[\Xbf]$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for any $S \subseteq \Csig[\Xbf]$
-\begin{equation*}
-\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S).
-\end{equation*}
-where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
-The following result lower bounds $\widetilde{\Phi}_{n,r}(S)$ by $\widetilde{\Phi}_{\Pbb,r}(T^{-1}(S))$, plus some perturbation.
-The magnitude of this perturbation, and thus the quality of the bound, will be dictated by the \emph{transportation distance} $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$.
-\begin{lemma}
-	\label{lem: graph_to_continuous_conductance}
-	Let $\seq{T_n}$ be a sequence of transportation maps between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.Then, letting $\Sset =T_n^{-1}(S)$, there exists a constant $c > 0$ fixed in sample size $n$ such that for any $S \in \mathcal{L}(\widetilde{G}_{n,r})$
-	\begin{equation}
-	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right)
-	\end{equation}
-\end{lemma}
-
-(We note that hereafter in this section $c$ will represent a constant which may change from line to line, and may depend on the density $f$ and dimension $d$, but not on the sample size $n$).
-As mentioned previously, Lemma \ref{lem: graph_to_continuous_conductance} is useful only in conjunction with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures compactly supported over open connected domains with Lipschitz boundaries.
-The following result is a restatement of this Proposition with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
-Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
-Let $\widetilde{n} = \abs{\Csig{\Xbf}}$.
-
-\begin{theorem}[Restatement of Proposition 5 of \cite{garciatrillos16}]
-	\label{thm: stagnating_transportation_maps}
-	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
-	\begin{equation}
-	\label{eqn: stagnating_transportation_maps}
-	\limsup_{\widetilde{n} \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq c
-	\end{equation}
-	where $c$ is constant in $n$ and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
-\end{theorem}
-
-The following result then supplies the last step, a uniform lower bound on the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ for all sets $\Sset \subseteq \Csig$.
-Let the \emph{$\Pbb$-(continuous) conductance} be given by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$, and the minimum in the preceding display is taken over measurable sets $\Sset \subseteq \Csig$. 
-\begin{lemma}
-	\label{lem: nonuniform_continuous_conductance}
-	For any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
-	\end{equation*}
-\end{lemma}
-
-With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}, which follows straightforwardly:
-\begin{align*}
-\liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S)} & \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset)\left(1 - c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}\right) } \\
-& \geq \liminf_{n \to \infty} \set{ \min_{\Sset \in \Csig} \widetilde{\Phi}_{\Pbb,r}} - \limsup_{n \to \infty} c \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \\
-& \geq \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
-\end{align*}
-
-It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we turn to in the following two subsections.
-
-\subsection{Population-level conductance.}
-\label{sec: population_conductance_function}
-
-We turn now to lower bounding the conductance over $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$ (in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$).
-Our first step will be to introduce a population analogue  of the conductance, and prove a lower bound on this quantity.
-
-Similar results are already known (see e.g.
-\cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
-In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a biLipschitz deformation of a convex set, but for completeness we produce all proofs here.
-
-\paragraph{Population-level conductance with uniform density}
-We first prove an analogous result for the special case of $f \propto 1$ everywhere on $\Csig$. For $x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$, let 
-\begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \pi_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) d\pi_{\nu,r}(x).
-\end{equation*}
-The uniform continuous normalized cut and conductance are then defined analogously to the weighted case,
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min \set{\pi_{\nu,r}(\Sset),\pi_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \in \mathfrak{B}(\Csig)} \widetilde{\Phi}_{\nu,r}(\Sset).
-\end{equation*}
-
-\begin{lemma}
-	\label{lem: uniform_continuous_conductance}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance of the $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{13} \rho L \sqrt{d}}.
-	\end{equation*}
-\end{lemma}
-
-Most of the technical work needed to show Proposition \ref{prop: nonuniform_continuous_conductance} involves proving Lemma \ref{lem: uniform_continuous_conductance}.
-We defer this work to the next subsection, and first show that Proposition \ref{prop: nonuniform_continuous_conductance} is a simple consequence of Lemma \ref{lem: uniform_continuous_conductance} along with \ref{asmp: bounded_density}.
-
-\paragraph{Proof of Proposition \ref{prop: nonuniform_continuous_conductance}.}
-
-Assume Lemma \ref{lem: uniform_continuous_conductance} holds, and note that for any $\Sset \subseteq \Csig$ with $\piwt_{\Pbb,r}(\Sset) \leq 1/2$,
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) = \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)}
-\end{equation*}
-By \ref{asmp: bounded_density} we obtain
-\begin{align*}
-\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(S \cap B(x,r)) f(x) \dx}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) f(x) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(S \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \widetilde{\Phi}_{\nu,r}(\Sset)
-\end{align*}
-and the statement follows by Lemma \ref{lem: uniform_continuous_conductance}.
-
-\subsection{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-\label{sec: proof_of_lemma_continuous_conductance}
-
-As is standard, the proof of a lower bound on the conductance relies on an isoperimetric inequality.
-
-\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
-	\label{lem: nonconvex_isoperimetry}
-	Let $\Cset$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
-	\begin{equation*}
-	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2))
-	\end{equation*}
-\end{lemma}
-The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even in the convex setting, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among others.
-Once the result is shown in the case where $\Omega$ is convex, however, generalizing to the setting given by  Assumption \ref{asmp: embedding} is not difficult.
-
-\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
-	For $\Omega_i, i = 1,2,3$, denote the preimage
-	\begin{equation*}
-	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
-	\end{equation*}
-	For any $x \in R_1, y \in R_2$, 
-	\begin{equation*}
-	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
-	\end{equation*}
-	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
-	\begin{equation*}
-	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
-	\end{equation*}
-	By Theorem 2.2 of \cite{lovasz1990},
-	\begin{align*}
-	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
-	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
-	\end{align*}
-	and by the measure-preserving property of $g$, this implies
-	\begin{equation*}
-	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
-	\end{equation*}
-\end{proof}
-
-We will also need an upper bound on the distance between transition probability densities $\widetilde{P}_{\nu,r}(u,\cdot)$ and $\widetilde{P}_{\nu,r}(v,\cdot)$ for $u,v \in \Csig$ close together. 
-\begin{lemma}[One-step distributions]
-	\label{lem: one_step_distributions}
-	Let $u,v \in \Csig$ be such that 
-	\begin{equation*}
-	\norm{u - v} \leq \frac{r t}{2\sqrt{d}}
-	\end{equation*}
-	for some $0 < t < 1/8$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
-	\begin{equation*}
-	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
-	\end{equation*}
-	where $\norm{P - Q}_{\mathrm{TV}}$ is the total variation distance between probabilities $P$ and $Q$. 
-\end{lemma}
-
-The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$.
-
-\begin{lemma}
-	\label{lem: overlap_balls_1}
-	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1/8$. Then,
-	\begin{equation*}
-	\nu(B(u,r) \cap B(v,r)) \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We will treat only the case where $\norm{u - v} = t\frac{r}{\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
-Then, it is not hard to see that $I = B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
-	\begin{equation*}
-	h = r\left(1 - \frac{t}{4\sqrt{d}}\right)
-	\end{equation*} 
-	From Lemma \ref{lem: volume_of_spherical_cap} we therefore obtain
-	\begin{equation*}
-	\nu\text{(i)} = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha = 1 - \frac{2r^2(1 - \frac{t}{4 \sqrt{d}}) - r^2(1 - \frac{t}{4 \sqrt{d}})^2}{r^2} = \frac{t^2}{16d}.
-	\end{equation*}
-	Expanding the incomplete beta function in integral form, we therefore have
-	\begin{align*}
-	\nu\text{(i)} & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
-	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
-	\end{align*}
-	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem: one_step_distributions}]
-	Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
-	\begin{equation*}
-	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
-	\end{equation*}
-	Since this will hold for arbitrary $\Sset_1 \in \mathfrak{B}(\Csig)$, it will hold for the infimum over all such $\Sset_1$ as well, and therefore the same lower bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}}$.
-
-	Now, note that
-	\begin{align*}
-	\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
-	\end{align*}
-	Let $I := B(u,r) \cap B(v,r)$. Then we have
-	\begin{equation*}
-	\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap I)
-	\end{equation*}
-	with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; \Sset_1)$. As a result,
-	\begin{equation}
-	1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap I) \label{eqn: one_step_1}
-	\end{equation}
-	As \eqref{eqn: one_step_1} demonstrates, the overlap of the one-step distributions is related to the volume of the intersection between $B(u,r)$ and $B(v,r)$ within $\Csig$.
-
-	From here, some simple manipulations yield
-	\begin{align}
-	\nu(\Csig \cap I)  & = \nu\text{(i)} - \nu(I \setminus \Csig) \nonumber \\
-	& \geq \nu\text{(i)} - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
-	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
-	\end{align}
-	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
-\end{proof}
-
-\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}.}
-Let $\Sset_1 \cup \Sset_2 = \Csig$ be arbitrary, and let $\ell \geq 0$ satisfy $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$. We will show that 
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\sqrt{2 \pi} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\pi_{\nu,r}(S_1), \pi_{\nu,r}(S_2)}
-\end{equation*}
-Once we have shown this, Lemma \ref{lem: local_conductance} gives the bound $\ell \geq \frac{6}{25}$.
-Then, dividing both sides by $\pi_{\nu,r}(\Sset_1)$ yields the desired result, since $\Sset_1$ was arbitrary.
-
-Now, consider the sets
-\begin{align*}
-S_1' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}} \\
-S_2' & = \set{x \in S_1: \widetilde{P}_{\nu,r}(x; S_2) < \frac{\ell}{4}}
-\end{align*}
-and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$.
-
-Suppose $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(\Sset_1)/2$. Then,
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \pi_{\nu,r}(x) \geq \frac{\ell  \pi_{\nu,r}(\Sset_1)}{8}
-\end{equation*}
-Similarly, if $\pi_{\nu,r}(\Sset_1') < \pi_{\nu,r}(S_1)/2$, then since
-\begin{equation*}
-\int_{S_1} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x) = \int_{S_2} \widetilde{P}_{\nu,r}(x; S_2) d \pi_{\nu,r}(x)
-\end{equation*}
-a symmetric result holds.
-
-So we can assume $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2$. Now, for every $u \in \Sset_1', v \in \Sset_2'$, we have that
-\begin{equation*}
-\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{\mathrm{TV}} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
-\end{equation*}
-
-By Lemma \ref{lem: one_step_distributions}, we therefore have
-\begin{equation*}
-\norm{u - v} \geq \frac{2 \sqrt{2 \pi } r \ell}{6\sqrt{3 d}}.
-\end{equation*}
-and since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
-\begin{equation*}
-\nu(\Sset_3') \geq  \frac{2 \sqrt{2 \pi} r \ell}{6 \rho L \sqrt{3 d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}
-\end{equation*}
-We now prove the desired result:
-\begin{align*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) & = \frac{1}{2} \biggl(\int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_2)  d \pi_{\nu,r}(x) \biggr) \\
-& \geq \frac{\ell}{8} \pi_{\nu,r}(\Sset_3') \\
-& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \\
-& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1'), \pi_{\nu,r}(\Sset_2')} \\
-& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\pi_{\nu,r}(\Sset_1), \pi_{\nu,r}(\Sset_2)}.
-\end{align*}
-
-\subsection{Graph conductance and local spread.}
-\label{sec: graph_conductance_and_local_spread}
-
-\begin{proposition}[Lower bound on graph conductance]
-	\label{prop: graph_conductance_profile_lb}
-	Let $\Cset$ satisfy Assumption \ref{asmp: bounded_density} for some $\lambda_{\sigma} \leq \Lambda_{\sigma}$ and Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
-Then, with probability $1$ the following lower bound holds on the graph conductance:
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}
-	\end{equation*}
-\end{proposition}
-
-In Lemma \ref{lem: local_spread_lb}, we lower bound the local spread $s(\widetilde{G}_{n,r})$.
-
-\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
-\label{sec: proof_of_lemma_graph_conductance}
-
-For $\Sset \subseteq \Csig$ measurable,
-
-If a sequence of transportation maps $\seq{T_n}$ satisfies $\lim_{n \to \infty}\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = 0$ (where $\mathrm{Id}$ is the identity mapping), we refer to it as a sequence of \emph{stagnating transportation maps}.
-
-\paragraph{Graph cuts to continuous cuts.}
-
-We use stagnating transportation maps to relate discrete graph normalized cuts to the continuous normalized cuts discussed in Section \ref{sec: population_conductance_function}.
-We fix some notation, letting $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$ for a transportation map $T_n$.
-
-Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
-
-\begin{lemma}
-	\label{lem: volume_bound}
-	Let $S \subseteq \Csig[\Xbf]$ and $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset := T_n^{-1}(S)$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{2 \Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset).
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	\varphi(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	Now, we proceed
-	\begin{align}
-	\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i)} \nonumber \\
-	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
-	& = \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \tag{change of variables} \nonumber \\
-	& \leq \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{\varphi \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& = \frac{1}{2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
-	\end{align}
-
-	By definition we have $\frac{d\Pbb(x)}{d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
-	\begin{align*}
-	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
-	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) \dx \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) \dx}{\Pbb(\Csig)^2} \piwt_{\Pbb,r_n^+}(\Sset)
-	\end{align*}
-	and we have the desired upper bound.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: cut_bound}
-	Let $S \subseteq \Csig[\Xbf]$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = T_n^{-1}(S)$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{2 \Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	As in the proof of Lemma \ref{lem: volume_bound}, let $\varphi: \Csig[\Xbf] \to \set{0,1}$ be the characteristic function for $S$.
-
-	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
-	\begin{align*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{2 \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \abs{\varphi(x_i) - \varphi(x_j)} \\
-	& = \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{\varphi(x) - \varphi(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
-	& =  \frac{1}{2}\iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& \geq \frac{1}{2} \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{\varphi \circ T_n(x) - \varphi \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& = \frac{1}{2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
-	\end{align*}
-	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
-	\begin{align*}
-	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r_n^-)\bigr)}{\ell_{\Pbb,r_n^-}(x)} d\piwt_{\Pbb,r}(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) \dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{align*}	
-\end{proof}
-
-Putting Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} together yields the following result, a lower bound on graph normalized cut.
-
-\begin{proof}
-
-	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S)}{\widetilde{\vol}_{n,r}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset)}.
-	\end{equation*}
-
-	Then, noting that $\Sset^c = T_n^{-1}(S^c)$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
-	\begin{equation*}
-	\frac{\widetilde{\cut}_{n,r}(S^c)}{\widetilde{\vol}_{n,r}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\piwt_{\Pbb,r_n^+}(\Sset^c)}
-	\end{equation*}
-	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} },
-	\end{equation*}
-	and the proof is complete.
-\end{proof}
-
-\paragraph{Perturbation analysis.}
-
-If $r_n^- = r = r_n^+$, \eqref{eqn: graph_to_continuous_conductance} would simplify to $\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(\Sset)$.
-We show that this conclusion is robust to asymptotically negligible perturbations of $r$.
-
-\begin{lemma}[Continuity of local conductance]
-	\label{lem: cont_local_conductance}
-	For $\seq{T_n}$ a sequence of stagnating transportation maps,
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Letting $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx + \int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx.
-	\end{equation*}
-	and therefore
-	\begin{equation*}
-	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}.
-	\end{equation*}
-	We upper bound the remainder term
-	\begin{equation*}
-	\int_{\Csig} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl((r_n^+)^d - r^d) \to 0
-	\end{equation*}
-	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	We apply a similar analysis to the denominator. By Lemma \ref{lem: local_conductance}
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) \dy \dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d \to \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
-	\end{equation*}
-	where the convergence happens as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	Then the desired result follows from an application of Slutsky's Theorem.
-\end{proof}
-
-\begin{lemma}[Continuity of stationary distribution]
-	\label{lem: cont_stationary_dist}
-	Let $c > 0$ be any fixed constant, and $\seq{T_n}$ be a sequence of stagnating transportation maps. Then,
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\min \set{\piwt_{\Pbb,r_n^-}(\Sset), \piwt_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\piwt_{\Pbb,r_n^+}(\Sset), \piwt_{\Pbb,r_n^+}(\Sset^c)} } = 1
-	\end{equation*}
-	uniformly over all measurable sets $\Sset \subseteq \Csig$ satisfying $\min \set{\piwt_{\Pbb,r}(\Sset), \piwt_{\Pbb,r}(\Sset^c)}> c$. 
-\end{lemma}
-\begin{proof}
-	It will be sufficient to show that
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} \quad \text{and}  \quad \liminf_{n \to \infty} \frac{\piwt_{\Pbb,r_n^-}(\Sset^c)}{\piwt_{\Pbb,r_n^+}(\Sset^c)} = 1,
-	\end{equation*}
-	and we will show only the former, the proof of the latter being identical.
-
-	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
-	\begin{equation*}
-	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
-	\end{equation*}
-	we may rewrite
-	\begin{equation*}
-	\frac{\piwt_{\Pbb,r_n^-}(\Sset)}{\piwt_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx}{\piwt_{\Pbb,r_n^+}(\Sset)}.
-	\end{equation*}
-
-	By the stagnating property of $T_n$,
-	\begin{equation*}
-	\int_{\Sset} \int_{\mathcal{R}_n(x)} f(y) f(x) \dy \dx \leq \Pbb(\Sset) \Lambda_{\sigma} \bigl( (r_n^+)^d - (r_n^-)^d\bigr) \to 0 
-	\end{equation*}
-	where the convergence occurs uniformly over all $\Sset$ as $n \to \infty$. On the other hand, by hypothesis
-	\begin{equation*}
-	\liminf_{n \to \infty} \piwt_{\Pbb,r_n^+}(\Sset) \geq c > 0.
-	\end{equation*}
-	and the result follows by Slutsky's Theorem. 
-\end{proof}
-
-\begin{lemma}[Stationary distribution lower bound]
-	\label{lem: stationary_dist_lb}
-	Let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$. Then with probability one,
-	\begin{equation*}
-	\liminf_{n \to \infty} \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \piwt_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary, writing $\Sset := T_n^{-1}(S)$.
-Letting $\mathcal{R}_n(x)$ be as in the proof of Lemma \ref{lem: cont_stationary_dist}, we have
-	\begin{align}
-	\widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}. \label{eqn: stationary_dist_lb_1}
-	\end{align}
-	Clearly $\piwt_{\Pbb,r_n^-}(\Sset) \leq \piwt_{\Pbb,r}(\Sset)$. Moreover
-	\begin{equation*}
-	\frac{\int_\Sset \int_{\mathcal{R}_n(x)}  f(y) f(x) \dy \dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	which along with \eqref{eqn: stationary_dist_lb_1} implies
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \piwt_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d \to \piwt_{\Pbb,r}(\Sset).
-	\end{equation*}
-	where the first lower bound comes from the fact $S \in \mathcal{L}(\widetilde{G}_{n,r})$, and the convergence is uniform over $\Sset$ as $n \to \infty$ by the stagnating property of $\seq{T_n}$.
-
-	By Lemma \ref{lem: local_spread_lb}, with probability one as $n \to \infty$,
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}
-	\end{equation*}
-	and the claim is shown.
-\end{proof}
-
-\paragraph{Proof of Lemma \ref{lem: graph_conductance_profile_lb}}
-
-By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
-
-Let $S \subseteq \Csig[\Xbf]$ be arbitrary, and define
-\begin{equation*}
-\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) \dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) \dx},~ \gamma_n(S) := \frac{\min \set{\piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \piwt_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
-\end{equation*}
-where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-By Proposition \ref{prop: nonuniform_continuous_conductance} and Lemma \ref{lem: graph_to_continuous_conductance} we have that
-\begin{align}
-\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
-& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^2r_n^{-}}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
-\end{align}
-
-By Lemma \ref{lem: cont_local_conductance}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \xi_n = 1.
-\end{equation*}
-
-By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $0 < c < \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}$, with probability one there exists some $m \in \mathbb{N}$ such that for all $n \geq m$,
-\begin{equation*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})}\piwt_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
-\end{equation*}
-and therefore by Lemma \ref{lem: cont_stationary_dist}
-\begin{equation*}
-\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
-\end{equation*}
-
-As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
-
-\subsection{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
-\label{sec: proof_of_theorem_mixing_time}
-
-Since $r$ is fixed, $\degminwt \to \infty$ with $n$. Therefore for sufficiently large $n$ we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
-\begin{equation}
-\label{eqn: tau_ub}
-\tau_{\infty}(\widetilde{G}_{n,r}) \leq \frac{2}{\widetilde{\Phi}_{n,r}^2} \log\left(\frac{1440}{s(\widetilde{G}_{n,r})}\right) \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
-\end{equation}
-and the claim follows from Proposition \ref{prop: graph_conductance_profile_lb} and Lemma \ref{lem: local_spread_lb}.
-In the statement of Theorem \ref{thm: mixing_time_upper_bound} we omit the factor of $3 \log\left(\frac{14}{s(\widetilde{G}_{n,r})}\right)$ as the first and third terms in \eqref{eqn: tau_ub} dominate.
-
-\subsection{Concentration inequalities}
-\label{sec: concentration}
-
-Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$-statistic} to be
-\begin{equation*}
-U := \frac{1}{ {n \choose 2} } \sum_{1 \leq i < j \leq n} K(x_i,x_j).
-\end{equation*}
-
-\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
-	\label{lem: bounded_difference}
-	For any $t > 0$,
-	\begin{equation*}
-	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{-nt^2\right\}
-	\end{equation*}
-	Further, for any $\delta > 0$, we have
-	\begin{align*}
-	U & \leq \mathbb{E}U + \sqrt{\frac{\log(1 / \delta)}{n} }, \\
-	U & \geq \mathbb{E}U - \sqrt{\frac{\log(1 / \delta)}{n} }
-	\end{align*}
-	each with probability at least $1 - \delta$. 
-\end{lemma}
-
-We will employ a sharper inequality to bound the sum of independent Bernoulli random variables.
-\begin{lemma}
-	\label{lem: multiplicative_Hoeffding}
-	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \sum_{i = 1}^n \Ebb(X_i)$. Then,
-	\begin{align*}
-	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
-	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
-	\end{align*}
-\end{lemma}
-
-We will require large-sample and asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}.
-Let
-\begin{alignat*}{2}
-\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ && \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
-\degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
-\degmin & := \min_{u \in \Xbf} \deg(u; G_{n,r}).
-\end{alignat*}
-
-\begin{lemma}
-	\label{lem: ball_bounds_in_probability}
-	Under the geometric conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
-	\begin{align}
-	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
-	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
-	\frac{\abs{\Csig[\Xbf]}}{n} & \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}\\
-	\label{eqn: volwt_bound}
-	\frac{1}{2}\vol_0 &\leq \vol_{n,r}(\Csig[\Xbf])  \leq \frac{3}{2} \vol_0
-	\end{align}
-
-	Additionally, with probability one,
-	\begin{align}
-	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
-	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d \label{eqn: max_vol_bound_asymp}
-	\end{align}
-
-	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{align}
-	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
-	\end{align}
-
-	If additionally \ref{asmp: C'_bounded_density} holds (but not necessarily \ref{asmp: valid_region}): for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{equation}
-	\label{eqn: min_cluster_degree_bound_2}
-	\frac{\degminpr}{n} \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
-	\end{equation*}
-	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
-	\begin{equation*}
-	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
-	\end{equation*}
-	and we have shown \eqref{eqn: min_cluster_degree_bound}.
-Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
-\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
-
-	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
-
-	Finally, note that
-	\begin{equation*}
-	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
-	\end{equation*}
-	can be rewritten as a U-statistic, and furthermore
-	\begin{equation*}
-	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
-	\end{equation*}
-
-	Therefore by Lemma \ref{lem: bounded_difference}
-	\begin{equation}
-	\label{eqn: ball_bounds_in_probability_1}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
-	\end{equation}
-	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
-Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
-	\begin{equation*}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
-	\end{equation*}
-
-	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
-	\begin{equation*}
-	\Pbb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} \geq (1 + \epsilon)\mu \right) \leq \exp(-n\epsilon^2\mu).
-	\end{equation*}
-	The two asymptotic statements \eqref{eqn: min_cluster_degree_bound_asymp} and \eqref{eqn: max_vol_bound_asymp} therefore both follow from the Borel-Cantelli Lemma.
-\end{proof}
-
-Before we proceed to the next subsection, we include a formal statement of our claims regarding the a\pprspace vector. 
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
-	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
-
-\section{Proof of Theorem \ref{thm: misclassification_rate}}
-\label{sec: proof_of_misclassification_rate}
-In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.
-
-Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
-\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
-
-\begin{lemma}
-	\label{lem: zhu}
-	Let $\varepsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
-Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\varepsilon)} := \pbf^{(\varepsilon)}(v,\alpha; G)$ of the form
-	\begin{equation*}
-	S_{\beta} := \left\{u \in V: \pbf^{(\varepsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
-	\end{equation*}
-	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \varepsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
-	\begin{align}
-	\vol(S_{\beta} \setminus S; G) & \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(S; G), \label{eqn: zhu_1}\\
-	\vol(S \setminus S_{\beta}; G) & \leq \left(\frac{2\Phi(S;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(S;G)\right)\vol(S; G).  \label{eqn: zhu_2}
-	\end{align}
-\end{lemma}
-
-\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
-
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
-Moreover,
-\begin{enumerate}[\text{(i)}]
-	\item we restrict $v \in \Csig[\Xbf]^g$
-	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$
-	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
-	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\varepsilon = 0$.
-\end{enumerate}
-
-All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq 1/10\tau_u(\theta)$, the following bounds hold with probability tending to 1 as $n \to \infty$:
-\begin{equation*}
-\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
-\end{equation*}
-Noting that
-\begin{align*}
-\abs{\widehat{C} \setminus \Csig[\Xbf]} & \leq \frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\degmin}   \\
-\abs{\Csig[\Xbf] \setminus \widehat{C}} & \leq \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\degminwt}, \quad \textrm{and} \\
-\abs{\Csig[\Xbf]} & \geq \frac{\vol_{n,r}(\Csig[\Xbf])}{\degmax}
-\end{align*}
-the claim follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
-
-\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}
-
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
-
-\section{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
-\label{sec: proof_of_consistent_cluster_recovery}
-
-We begin with some notation.
-Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
-Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
-\begin{equation*}
-\overline{\pibf}_{n,r}(x) := \frac{\widetilde{\deg}_{n,r}(x)}{\vol_{n,r}(\Csig[\Xbf])}.
-\end{equation*}
-(Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
-
-Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(x) - \overline{\pibf}_{n,r}(x)$.
-
-\begin{lemma} 
-	\label{lem: setup}
-	Let $0 < r < \sigma$ and $\alpha \leq \frac{1}{9 \tau_{\infty}(\widetilde{G}_{n,r})}$.
-Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
-	\begin{itemize}
-		\item For each $u \in \Cset[\Xbf]$,
-		\begin{equation}
-		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminwt}
-		\end{equation}
-		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy the cluster separation condition \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
-		\begin{equation}
-		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminpr}.
-		\end{equation}
-	\end{itemize}
-\end{lemma}
-
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-~
-
-In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
-
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
-As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
-\begin{align}
-\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
-\end{align}
-We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
-\begin{align}
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
-\end{align}
-
-The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
-& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-Similarly, for each $u' \in \Cset'[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
-& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
-& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
-
-It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
-\begin{equation}
-\label{eqn: pimin_Dmin_lb}
-\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
-\end{equation}
-
-Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
-\begin{equation}
-\label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
-\end{equation}
-\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
-
-\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
-
-Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
-\begin{equation*}
-\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
-\end{equation*}
-and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
-\begin{equation*}
-\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
-\end{equation*}
-
-On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
-
-\subsection{Proof of Lemma~\ref{lem: setup}}
-	%The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. 
-	Given a starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
-	\begin{equation}
-	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}
-	\end{equation}
-	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
-(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
-
-	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
-	\begin{align}
-	\label{eqn: leakage_soakage}
-	\ell_t & := e_v (\Wbf \widetilde{I} )^t (I - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
-	s_t & := e_v (\Wbf \widetilde{I} )^t (\Wbf \widetilde{I}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
-	\end{align}
-	where $I$ is the $n \times n$ identity matrix, $\widetilde{I}$ is an $n \times n$ diagonal matrix with $\widetilde{I}_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{I}^c = I - \widetilde{I}$.
-
-	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $\Csig[\Xbf]$ on the $t + 1$th step.
-For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$.
-By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is ``soaked up'' into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
-The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
-
-	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation.
-By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
-	\begin{equation}
-	\label{eqn: zhulemma3.1}
-	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
-	\end{equation}
-	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)
-
-	If additionally $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
-	\begin{equation*}
-	\widetilde{\pbf}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
-	\end{equation*}
-	and along with \eqref{eqn: zhulemma3.1}, we obtain
-	\begin{equation*}
-	\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
-	\end{equation*}
-
-	We proceed to show the upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \degminwt$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
-We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$.
-	\begin{enumerate}
-		\item Since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$ and $u \not\in \mathrm{supp}(q)$, and any $t \geq 1$,
-		\begin{align}
-		\label{eqn: one_step_bound}
-		q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 \max_{v \neq u} W_{vu} \nonumber \\
-		& \leq \frac{1}{2\degminwt} 
-		\end{align}
-		where last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
-	\end{enumerate}
-
-	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
-	\begin{align*}
-	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}^t \right)(u)  \nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
-	& \leq \frac{\norm{\ell}_1 }{\degminwt}. \tag{since $u \not\in \mathrm{supp}(\ell)$}
-	\end{align*}
-	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.
-
-	We turn to showing \eqref{eqn: upper_bound_PPR_in_other_cluster}. By Lemma \ref{lem: soakage_ppr_lb}, for all $u' \not\in \Csig[\Xbf]$,
-	\begin{equation*}
-	\pbf_v(u') \leq \pbf_s(u').
-	\end{equation*}
-
-	Note that by \ref{asmp: cluster_separation}, for every $u \in \Csig[\Xbf], (u',u) \not\in E$ and therefore $s(u') = 0$.
-Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
-	\begin{align*}
-	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
-	& \leq \frac{\norm{s}_1}{2\degminpr}
-	\end{align*}
-	where the last inequality follows from precisely the same reasoning as \eqref{eqn: one_step_bound}.
-The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
-
-\subsection{Linear Algebra Facts}
-\label{sec: linalg}
-
-We state here a number of basic facts which follow from matrix manipulations, which are used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-\begin{lemma}
-	\label{lem: soakage_ppr_lb}
-	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
-	\begin{equation*}
-	\pbf_{v}(u) \leq \pbf_{s}(u)
-	\end{equation*}
-	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
-\end{lemma}
-\begin{proof}
-	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
-	\begin{align*}
-	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
-	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
-	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
-	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
-	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
-	& = \pbf_s(u)
-	\end{align*}
-\end{proof}
-
-Let $s_t := q(\Wbf \Ibf{S})^t(\Wbf(\Ibf{S^c}))$ be the soakage vector out of $S \subseteq V$, where $\Ibf{S}$ is a $\abs{V} \times \abs{V}$ diagonal matrix with $(\Ibf{S})_{uu} = 1$ if $u \in S$ and 0 otherwise, and $\Ibf{S^c} := \Ibf{} - \Ibf{S}$.
-\begin{lemma}
-	\label{lem: sum_of_soakages}
-	Let $G = (V,E)$ be an unweighted, undirected graph with associated random walk matrix $\Wbf$. For any $T \in \mathbb{N}, T \geq 1$, $q \in \Reals^{\abs{V}}$, and $S \subseteq V$
-	\begin{equation}
-	\label{eqn: sum_of_soakages}
-	q\Wbf^T = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} + q(\Wbf \Ibf{S})^T
-	\end{equation}
-	In particular, if $u \in V\setminus S$, then
-	\begin{equation}
-	\label{eqn: sum_of_soakages_2}
-	q\Wbf^T(u) = \sum_{t = 0}^{T - 1} \left(s_t \Wbf^{T - t - 1}\right)(u)
-	\end{equation}
-\end{lemma}
-\begin{proof}	
-	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.
-
-	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,
-	\begin{equation*}
-	q\Wbf = q\Wbf\Ibf{S} + q\Wbf\Ibf{S^c} =  q\Wbf\Ibf{S} + s_0. 
-	\end{equation*}
-
-	Then, for $T \in \mathbb{N},~ T \geq 2$,
-	\begin{align*}
-	q\Wbf^{T} & = q\Wbf^{T - 1}{\Wbf} \\
-	& = \left\{\sum_{t = 0}^{T - 2} s_t \Wbf^{T - 2 - t} + q(\Wbf \Ibf{S})^{T - 1} \right\} \Wbf \tag{by the inductive hypothesis}\\
-	& = \sum_{t = 0}^{T - 2} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S} + \Wbf \Ibf{S^c}) \\
-	& = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S})
-	\end{align*}
-	and the proof is complete.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: total_leakage_equal_total_soakage}
-	Letting $s_t$, $\ell_t$ $s$ and $\ell$ be as in \eqref{eqn: leakage_soakage},
-	\begin{equation*}
-	\norm{s_t}_1 = \norm{\ell_t}_1,~ \textrm{for each $t \geq 0$}
-	\end{equation*}
-	and therefore $\norm{s}_1 = \norm{\ell}_1$. 
-\end{lemma}
-\begin{proof}
-	By the definition of $s_t$ and $\ell_t$, we have
-	\begin{align*}
-	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{I}^c)}_1 \\
-	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{I}^c)(u, u') \\
-	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf)_{uu}} \1((u,u') \in G_{n,r}) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf)_{uu} - (\widetilde{\Dbf})_{uu} \right)}{(\Dbf)_{uu}} \\
-	& = \norm{q_t (\Ibf{} - \Dbf^{-1} \widetilde{\Dbf})}_1 = \norm{\ell_t}_1.
-	\end{align*}
-\end{proof}
-
-\section{Experiments}
-\label{sec: experimental_setting}
-
-In Section \ref{sec: experimental_setting}, we detail the experimental settings of Section \ref{sec: experiments} in the main text, and include an additional figure.
-
-\subsection{Experimental settings for Figure \ref{fig:fig1}}
-We sample points according to the density function $q$, where for $x \in \Rd$
-\begin{equation}
-q(x) :=
-\begin{cases}
-\lambda,~ & x \in [0,\sigma] \times \rho^{d-1} =: \Cset, \\
-\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
-(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
-0,~ & \textrm{otherwise},
-\end{cases}
-\end{equation}
-where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
-
-In the top-left and top-middle, we show draws of $n = 20000$ samples from two different density functions.
-In the top-left panel, $\sigma = \rho = 3.2$, while in the top-middle panel $\sigma = .1$ and $\rho = 3.2$.
-(For both, $d = 2$).
-
-The remaining four panels (top-right and the bottom row) in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
-In the top-right and bottom-left panels $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $\rho$ is fixed at $3.2$.
-In the bottom-middle and bottom-right panels, $\rho = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
-For each panel, the solid lines show, up to constants, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for the top-right and bottom-left panels and Theorem \ref{thm: mixing_time_upper_bound} for the bottom-middle and bottom-right panels.
-The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in the top-right and bottom-left panels, and $m = 20$ for the mixing time, dashed lines in the bottom-middle and bottom-right panels).
-For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
-Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
-
-\subsection{Experimental settings for Figure \ref{fig:fig2}}
-
-To form each of the three rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
-Formally, the (respective) generative models for the data are
-\begin{align}
-Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
-X(Z,\theta) & = 
-\begin{cases}
-\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
-\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
-\end{cases}
-\end{align}
-
-where 
-\begin{align*}
-\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
-\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
-\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} 
-\end{align*}
-for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $C[\Xbf]$ and $C'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
-
-\subsection{Performance of \pprspace with high-dimensional noise.}
-
-Figure \ref{fig:fig3} is similar to Figure \ref{fig:fig2} of the main text, with parameters
-\begin{equation*}
-\mu_1 = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}).
-\end{equation*}
-The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:fig2} in the main text) represent observations in low-density regions.
-While the \pprspace sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C[\Xbf]$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-
-\begin{figure}
-	\centering
-	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\caption{}
-		\label{fig:fig3}
-	\end{adjustbox}
-\end{figure}
-
-\bibliographystyle{plainnat}
-\bibliography{../local_spectral_bibliography}
-
+
+We provide the following very crude upper bound on $\vol_{\Pbb,r}(\Aset)$,
+\begin{equation*}
+\vol_{\Pbb,r}(\Aset) \leq \vol_{\Pbb,r}(\mathcal{X}) \leq \frac{\pi r^2}{\rho \sigma},
+\end{equation*}
+which along with~\eqref{eqn:lb_proof_3} results in an upper bound on the normalized cut of $\Aset$,
+\begin{equation*}
+\Phi_{\Pbb,r}(\Aset) \leq \frac{1}{2\pi} \cdot \frac{\epsilon^2r}{\sigma} \bigl(1 - 4 \cdot \Pbb(\Aset \triangle \Cset_1 )\bigr).
+\end{equation*}
+
+\subsubsection{Proof of Claim 1.}
 \end{document}

### 2019-10-04 arxiv/local_spectral_density_clustering_arxiv.tex
added relevant examples tuff

--- 2019-07-03 neurips/local_spectral_density_clustering_arxiv.tex
@@
 vertices $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i -
-x_j} \leq r$, where $\norm{\cdot}$ is the $\ell_2$ norm. We denote by $\Abf \in
+x_j} \leq r$, where $\norm{\cdot}$ is the Euclidean norm. We denote by $\Abf \in
 \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if
@@
 
-Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, based on
+Next, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on
 a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be 
@@
 \label{eqn: ppr_vector}
-\pbf = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
+\pbf_v = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
 \end{equation}
@@
 $G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
-$v$-th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
-$\vol_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$
+$v$-th position and 0 elsewhere).
+
+\subsection{Sweep cut.}
+\label{subsection: sweep_cut}
+
+Finally, we employ the sweep cut method to obtain a local cluster from the PPR embedding $\pbf_v$.
+For a level $\beta > 0$ and a target stationary probability $\pi_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$
 as   
@@
 \label{eqn: sweep_cuts}
-S_\beta := \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
+S_\beta := \set{u \in V: \pbf_v(u) > \beta \pi_0}.
 \end{equation}
@@
 Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(\frac{1}{40},\frac{1}{11})$}\footnote{The choice of a specific range such as  
-\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
+(\frac{1}{40},\frac{1}{12})$}\footnote{The choice of a specific range such as  
+\smash{$(\frac{1}{40}, \frac{1}{12})$} is standard in the analysis of PPR
 algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate
@@
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume
-$\vol_0 > 0$. \\     
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary probability
+$\pi_0 > 0$. \\     
 {\bfseries Output:} cluster $\Cest \subseteq V$.
@@
   \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $p=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
+  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
     ppr_vector}. 
-  \STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
+  \STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{12})$} compute sweep cuts 
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
@@
 clustering given previously, a few related lines of work are worth
-highlighting. \citet{shi2009} and \citet{schiebinger2015} examine the consistency of  
-spectral algorithms in recovering the latent labels in certain
-nonparametric mixture models. Their results focus on global rather than local 
+highlighting.
+In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+The ability of spectral clustering to perform community detection, in this context is well-understood.
+In particular, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM,  \citet{lei2015} extend these results to the sparse (low average degree) regime, and \citet{balakrishnan2011} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+The framework we consider, where nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
+
+The study of spectral algorithms on neighborhood graphs has focused on establishing consistency results-- that is, asymptotic convergence of eigenvalues and eigenvectors of matrices to eigenvalues and eigenfunctions of limiting operators.
+\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
+\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood of fixed radius.
+\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime $r \to 0$ as $n \to \infty$.
+
+These results are of fundamental importance; however, the behavior of the spectra of these underlying integral operators is somewhat hard to grasp.
+Therefore, further work relating this spectra to the geometry of the distribution $\Pbb$ is of interest.
+In this spirit, \citet{shi2009} and \citet{schiebinger2015} examine the ability of
+spectral algorithms to recover the latent labels in certain geometrically well-conditioned nonparametric mixture models. Their results focus on global rather than local 
 methods, and thus impose global rather than local conditions on the nature
@@
 
-More broadly, density clustering and level set estimation is a well-studied
-problem. \citet{polonik1995, rigollet2009} study density clustering under the 
+A substantial portion of our technical effort involves estimating graph-theoretic connectivity properties of empirical density clusters in the neighborhood graph $G_{n,r}$.
+In particular, we prove an upper bound on the mixing time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall within the empirical density cluster $\Cset[\Xbf]$.
+To do so, we rely on a series of seminal works upper bounding the mixing time of \emph{geometric random walks} (see \citet{vempala2005} for a comprehensive review.)  \citet{dyer1991} initiated this study, using these random walks as a fundamental subroutine to efficiently compute volumes of high-dimensional convex bodies.
+These results are improved in \citep{lovasz1990,kannan97,kannan06}, who show, among other things, that the bounds on mixing time can be sharpened by avoiding so-called ``start-penalties''.(These improvements are crucial to our work, for they allow us to avoid factors of $\log n$ which would imply divergence as $n \to \infty$.) Following the lead of \citep{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold for Lipschitz deformations of convex sets.
+Additionally, we relate the mixing time of these (continuous-space) geometric random walks to the mixing time of random walks over (discrete) neighborhood graphs.
+
+Finally, it is worth mentioning that density clustering and level set estimation is of course a well-studied problem. \citet{polonik1995, rigollet2009} study density clustering under the 
 symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
@@
   in the difficulty of the clustering problem.
+
+\item In Section \ref{sec: examples}, we show the implications of our theory for some simple generative models, and compare our upper bounds on the symmetric set difference metric to those achievable by classical density cluster estimators.
 
@@
 
-  %%% AJG 5/20: Should I turn this into two conditions?
 \item
@@
   \begin{equation*}
-    \frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~
+    \norm{g(x) - g(y)} \leq L \norm{x - y} ~
     \text{for all $x,y \in \mathcal{K}$}. 
@@
   Succinctly, we assume that $\Csig$ is the image of a convex set with finite diameter 
-  under a  measure preserving, bi-Lipschitz transformation.
+  under a  measure preserving, Lipschitz transformation.
 
@@
 \end{enumerate}
+
 To motivate these conditions, we provide a brief high-level sketch
@@
 \vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
-\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
+\cdot \tau_{\infty}(G[S])\bigr),
 \end{equation}
@@
 
+\textcolor{red}{Mention Arias-Castro and Little here.}
+
 \subsubsection{Condition number} 
@@
 \begin{definition}[Well-conditioned density clusters]
+  \label{def:well_conditioned_density_cluster}
   For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy 
@@
 ranges of each of the user-specified parameters. In particular, for a
-well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
-require that the tuning parameters of Algorithm~\ref{alg: ppr} are chosen as
+well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we require that the tuning parameters of Algorithm~\ref{alg: ppr} are chosen to fall within the ranges
 \begin{equation}
@@
 v \in \Csig[\Xbf]^g, \quad
-\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, 
+\pi_0 \in [3/4,5/4] \cdot \frac{\lambda_{\sigma}}{n\Lambda_{\sigma}\Pbb(\Csig)},
 \end{gathered}
@@
 hyperparameters and selects the cluster which has the smallest normalized cut.
-%it is not obvious how this scheme would affect the performance of PPR in the
-%density clustering context.
 
 \subsection{Cluster Recovery in Symmetric Set Difference}
-The results of Section \ref{sec: analysis}, combined 
-with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
-volume of \smash{$\Cest \setminus \Csig[\Xbf]$} and \smash{$\Csig[\Xbf]
-  \setminus \Cest$},  
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus
-\Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]). 
-\end{equation}
-To translate the guarantee in~\eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
-on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
-want to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and
-so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$. Let
-$\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure
-of the unit ball $B = B(0,1)$. 
-\begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{5}
-\item 
-  \label{asmp: valid_region}
-  \emph{Regular support:} There exists some constant $\lambda_{\min} > 0$ such 
-  that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$. Additionally, there
-  exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$,
-  $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$. 
-\end{enumerate}
-We note that the latter condition in \ref{asmp: valid_region} will hold if the
-boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
-first main result: a bound on the symmetric set difference metric.
+We now present our first main result: a bound on the symmetric set difference metric between the estimated cluster $\widehat{C}$ and empirical cluster $\Csig[\Xbf]$.
 \begin{theorem}
   \label{thm: misclassification_rate}
-  Fix $\lambda > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
-  additionally assume that $f$ satisfies \ref{asmp: valid_region}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >
-  0$ such that with probability tending to 1 as $n \to \infty$,  
+  Fix $\lambda > 0$ and let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
+  $\kappa$-well-conditioned density cluster (with respect to some $\theta$).
+If Algorithm \ref{alg: ppr} is well-initialized, there exists a universal constant $c > 0$ such that with probability tending to 1 as $n \to \infty$,
   \begin{equation}
     \label{eqn: misclassification_rate_ub}
-    \Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
-    \frac{\Lambda_{\sigma}}{\lambda_{\min}}. 
+    \Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)  \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \abs{\Csig[\Xbf]}
   \end{equation}
@@
 \subsection{Consistent Cluster Recovery}
-Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
-  misclassification_rate_ub} imply consistent density cluster estimation in the 
-sense of \eqref{eqn: consistent_density_cluster_recovery}. This notion of
+The bound on symmetric set difference \eqref{eqn: misclassification_rate_ub} does not imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+This notion of
 consistency requires a uniform bound over $\pbf$: for all \smash{$\Cset'
@@
 \label{eqn: ppr_gap}
-\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq
-\frac{p_u}{\Dbf_{uu}}, 
-\end{equation}
-so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e., any
+\pbf_v(w) \leq \frac{\pi_0}{40} < \frac{\pi_0}{11} \leq \pbf_v(u),
+\end{equation}
+so that any sweep cut $S_{\beta}$ for $\beta \in [1/40,1/11]$ (i.e., any
 sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions
@@
 \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently
-small upper bound on $\kappa(\Cset)$ ensures that such a gap exists with probability
-1 as $n \to \infty$, and hence guarantees \smash{$\Cest$} will be a consistent  
-estimator. As was the case before, we wish to preclude arbitrarily low degree
-vertices, this time for points $x \in \Cset'[\Xbf]$. 
+small upper bound on $\kappa(\Cset)$ ensures that as $n \to \infty$, such a gap exists with probability
+1, and hence guarantees \smash{$\Cest$} will be a consistent  
+estimator. We will need one additional regularity condition, to preclude arbitrarily low degree
+vertices for points $x \in \Cset'[\Xbf]$. 
 \begin{enumerate}[label=(A\arabic*)]
@@
  \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
-    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
+    kappa_ub} results in an upper bound on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
     \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
@@
 \end{enumerate}
-\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
-changed this $\epsilon$ to $\varepsilon$.}
 
@@
 \end{equation}
-Next, we give an asymptotic (in the number of vertices $n$) upper bound on
+Next, we give an asymptotic (in the number of samples $n$) upper bound on
 $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
@@
     \label{eqn: mixing_time_upper_bound}
-    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2
-    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{1}{r}\right) + c_3,
-  \end{equation}
-  for $c_2,c_3 > 0$ universal constants. 
+    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{c_4 \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
+  \end{equation}
+  for $c_2,c_3,c_4 > 0$ universal constants. 
 \end{theorem}
@@
   $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
-  develop theory regarding bi-Lipschitz deformations of convex sets, wherein it
+  develop theory regarding Lipschitz deformations of convex sets, wherein it
   is observed that star-shaped sets as well as half-moon shapes of the type we
@@
   for reasonably small values of $L$.
+
+\section{Examples}
+\label{sec: examples}
+
+We illustrate the implications of our theory on some common generative models for nonparametric clustering, and compare our theoretical bounds on PPR to those derived for more classical density cluster estimators.
+
+\subsection{Uniform clusters plus noise, dimension $d = 1$.}
+\label{subsec: uniform_clusters}
+
+We begin with a very simple model $\Pbb$ that fits ideally into our framework.
+For $i = 1,\ldots,n$, let $z_i \sim \delta \textrm{Bern}(1/2)$ be a latent class assignment, and let $w_i \sim \sigma \textrm{Unif}([-\sigma, \sigma])$ where $\delta$ and $\sigma$ are positive numbers such that $\delta > 3 \sigma$ (to ensure adequate separation of the density clusters).
+Assume we sample $x_1, \ldots, x_n$ from the following contaminated mixture model:
+\begin{equation*}
+x_i = 
+\begin{cases}
+z_i + w_i,& \quad \textrm{with probability $1 - \epsilon$} \\
+\widetilde{w}_i, & \quad \textrm{with probability $\epsilon$}
+\end{cases}
+\end{equation*}
+where $\widetilde{w}_i \sim \textrm{Unif}(\sigma, \delta - \sigma)$ and $\epsilon$ is a positive number between $0$ and $1$.
+In other words, $\Pbb = (1-\epsilon)\bigl((1/2)\textrm{Unif}[-\sigma,\sigma] + (1/2)\textrm{Unif}[\delta - \sigma,\delta + \sigma]\bigr) + \epsilon \textrm{Unif}(\sigma,\delta - \sigma)$ is a mixture of two uniforms with added background noise.
+We will consider $\Cset = \set{0}$, so that the $\sigma$-expansion of $\Cset$ is $\Csig = [-\sigma,\sigma]$.\footnote{Although $\Cset$ is not a density level set of $\Pbb$, one can add a small bump to the density around $0$ to make $\set{0}$ a well defined density cluster for an appropriate choice of threshold $\lambda$, without changing any of the subsequent calculations.
+For ease of presentation, we ignore this detail.}
+
+We verify that each of the assumptions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume} hold on $\Csig$.
+The maximum and minimum density over $\Csig$ are the same, $\Lambda_{\sigma} = \lambda_{\sigma} = (1 - \epsilon)/(4\sigma)$.
+Letting $\Csig' = [\delta - \sigma, \delta + \sigma]$ be the $\sigma$-expansion around $\Cset' = \set{\delta}$, the condition $\dist(\Csig, \Csig') > \sigma$ holds since $\delta > 3\sigma$.
+The low noise density assumption holds with parameter $\gamma = 0$ and $c_0 = (1 - \epsilon)/(4\sigma) - \epsilon/2\sigma$.
+The set $\Csig$ is convex with diameter $\rho = 2\sigma$.
+Finally, for any $0 < r < \sigma$ the bounded volume condition of \ref{asmp: bounded_volume} holds.
+
+We can now give an upper bound on misclassification error that holds with probability $1$ as $n \to \infty$.
+To do so, we begin by computing $\Phibf(\theta)$ and $\taubf(\theta)$ as defined in \eqref{eqn: condition_number_1},
+\begin{equation*}
+\Phibf(\theta) = \frac{c_1 r \epsilon}{(\delta - 2\sigma)(1 - \epsilon)}, \quad \taubf(\theta) = 4 c_2 \frac{\sigma^2}{r^2} \log\left(\frac{4c_4\sigma}{(1 - \epsilon)r}\right) + c_3.
+\end{equation*}
+Therefore, if we set $r = \sigma/2$, the largest value permissible under the conditions of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, we obtain the condition number
+\begin{equation*}
+\kappa(\Cset) = \frac{4c_1c_2\sigma\epsilon}{(\delta - 2\sigma)(1 - \epsilon)}\log^2\left(\frac{8c_4}{(1 - \epsilon)}\right) + \frac{c_3c_1\epsilon\sigma}{2(\delta - 2\sigma)}
+\end{equation*}
+
+Therefore, by Theorem \ref{thm: misclassification_rate}, if Algorithm \ref{alg: ppr} is well-initialized with respect to $\Cset$, then we have that the fraction of misclassified points $\frac{\Delta(\Cest, \Csig[\Xbf])}{\abs{\Csig[\Xbf]}}$ is roughly upper bounded by $\sigma \epsilon / (\delta - 2\sigma)$ (ignoring constants and logarithmic terms).
+Qualitatively speaking, this exhibits the correct dependence on the mixture model parameters $\sigma$, $\epsilon$, and $\delta$.
+In particular, as the expected fraction of background noise $\epsilon$, or the ratio of cluster width to cluster separation $\sigma/(\delta - 2\sigma)$, decrease, so does our estimate of the symmetric set difference $\Delta(\Cest, \Csig[\Xbf])$.
+
+\subsection{Uniform clusters plus noise, general dimension.}
+
+To better demonstrate the flexibility of our theory, we now generalize the previous example in several respects.
+For an integer $d' < d$, consider the $d'$-dimensional unit cube embedded in $\Reals^d$ by letting
+\begin{equation*}
+[0,1]^{d'} = \{(x_1,\ldots,x_d) \in \Rd: 0 \leq x_i \leq 1 ~\textrm{for}~ i = 1,\ldots,d', x_i = 0 ~\textrm{for}~ i = d'+ 1,\ldots,d\},
+\end{equation*}
+and denoting the $\sigma$-expansion of $[0,1]^{d'}$ by $[0,1]_{\sigma}^{d'} = \{x \in \Rd: \dist(x,[0,1]^{d'}) < \sigma\}$.
+For a number of clusters $K > 2$, let $f_1,\ldots,f_K: [0,1]_{\sigma}^{d'} \to [0,1]^{d}$ be Lipschitz, measure-preserving maps, with Lipschitz constant $\norm{f_k}_{\textrm{Lip}}, ||f_k^{-1}||_{\textrm{Lip}} \leq L$ for each $k$.
+Write $\Csig^k$ for the image $f_k([0,1]_{\sigma}^{d'})$, and let $\Psi_k$ be the uniform distribution over $\Csig^k$.
+Additionally, let $\Psi_0$ be the uniform distribution over $\Cset^0 = [0,1]^d \setminus \bigcup_{k = 1}^{K} \Csig^k$.
+For $\epsilon \in [0,1)$, let $\Pbb$ be the $K$-component mixture model given by
+\begin{equation*}
+\Pbb = \frac{(1 - \epsilon)}{K} \sum_{k = 1}^{K} \Psi_k + \epsilon \Psi_0. 
+\end{equation*}
+
+Suppose we observe $x_1,\ldots,x_n$ sampled i.i.d from $\Pbb$.
+Letting $f$ be the density function of $\Pbb$, for sufficiently small $\epsilon > 0$, and an appropriate choice of $\lambda$, the density upper level set $\Cbb_f(\lambda)$ will contain components $\Csig^1,\ldots,\Csig^k$.
+Let's say the set we are interested in recovering is $\Csig^1$.
+Under certain regularity conditions, this framework fits smoothly into the theory developed Sections~\ref{sec: consistent_cluster_estimation_with_ppr} and \ref{sec: analysis}.
+We will assume that for each $k$, $\Csig^k$ is a $\sigma/2$-expansion\footnote{Note that it is possible that $\Csig^k = f_k([0,1]_{\sigma}^{d'})$ for a Lipschitz function $f_k$, and yet itself not be an $\sigma/2$-expansion of any set.
+As we need $\Csig^k$ to be a $\sigma$-expansion, we make this requirement explicit.} of some $\Cset^k \subset [0,1]^d$ and additionally that
+\begin{equation*}
+\min_{k \neq \ell} \dist(\Csig^k,\Csig^\ell) > \sigma, \min_{k}\dist(\Csig^k,\partial [0,1]^d) > \sigma, \quad \textrm{and}~ 5 < K < \frac{\sigma^{d - d'}}{2^{d' + 1}}.
+\end{equation*}
+
+Now, we verify that each of the assumptions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume} hold with respect to $\Csig^1$. 
+\begin{itemize}
+	\item \ref{asmp: bounded_density}.
+In this case, the minimum and maximum density within the $\sigma/2$-expansion $\Csig^1$ are the same, $\Lambda_{\sigma} = \lambda_{\sigma} = (1 - \epsilon)/(K \nu(\Csig^1))$.
+(Indeed, this holds for each $\Csig^k$.)
+	\item \ref{asmp: cluster_separation}. By assumption, $\dist(\Csig^1,\Csig^k) > \sigma$ for each $k = 2,\ldots,K$. 
+	\item \ref{asmp: low_noise_density}. The low noise condition is satisfied with $\gamma = 0$ and $c_0 = (1 - \epsilon)/(K \nu(\Csig^1)) - \epsilon/(\nu(\Cset^0))$. 
+	\item \ref{asmp: embedding} By assumption, the embedding condition is satisfied with $\rho = 1 + \sigma < 2$, and $L = L$. 
+	\item \ref{asmp: bounded_volume}. When $r < \sigma/(2d)$ we have that $\nu( B(x,r) \cap \Csig^k)\geq \frac{6}{25}\lambda_{\sigma}\nu_d r^d$ (see Lemma~\ref{lem: local_conductance}). Therefore
+	\begin{align*}
+	\sum_{k = 2}^{K} \int_{\Csig^k} \Pbb(B(x,r)) \,dx & \geq \frac{6}{25}\sum_{k = 2}^{K}\nu(\Csig^k) \lambda_{\sigma} \nu_d r^d \\
+	& \overset{(i)}{\geq} \nu(\Csig^1) \lambda_{\sigma} \nu_d r^d \\
+	&  \geq \int_{\Csig^1} \Pbb(B(x,r)) \,dx.
+	\end{align*} 
+	where $(i)$ follows from the fact that $\nu(\Csig^k) = \nu([0,1]_{\sigma}^{d'})$ for all $k$ and the assumption that $K \geq 5$. Therefore \ref{asmp: bounded_volume} is satisfied.
+\end{itemize}
+
+The restriction that $f$ be measure-preserving implies $\nu(\Csig^k) = \nu([0,1]_{\sigma}^{d'}) \leq 2^{d'} \sigma^{d - d'}$ for each $k$.
+Along with the upper bound on number of clusters $K$, we additionally have $\nu(\Cset^0) \geq (1 - K 2^{d'} \sigma^{d - d'}) \geq 1/2$.
+We can therefore bound $\Phibf(\theta)$ and $\taubf(\theta)$,
+\begin{equation}
+\label{eqn:normalized_cut_mixing_time_ub_example2}
+\Phibf(\theta) \leq c \frac{K dr \epsilon}{\sigma 2^{d'} \sigma^{d - d'} (1 - \epsilon)}, \quad \Psibf(\theta) \leq c \frac{d^3 L^2}{r^2} \log^2\left(\frac{K \sigma^{d - d'}}{(1 - \epsilon)r}\right),
+\end{equation}
+and letting $r = \sigma/(2d)$, we obtain the following bound on the condition number $\kappa(\Cset)$:
+\begin{equation}
+\label{eqn:kappa_example2}
+\kappa(\Cset) \leq c \frac{\epsilon \sigma^{d - d' - 2} K d^5 L^2}{(1 - \epsilon)} \log^2\left(\frac{d K \sigma^{d - d'}}{\sigma(1 - \epsilon)}\right),
+\end{equation}
+which likewise implies a bound on the symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ (assuming that Algorithm~\ref{alg: ppr} is well-initialized.)
+
+\subsubsection{Plug-in density clustering.}
+It is interesting to compare \eqref{eqn:kappa_example2} to the symmetric set difference obtained by a more classical density cluster estimator.
+In particular, we consider the plugin approach to density cluster estimation, which we now briefly summarize (see e.g.
+\cite{chaudhuri2010} for a more formal algorithmic description).
+To motivate this approach, note that one can view the degrees $\deg_{n,r}(x_1), \ldots, \deg_{n,r}(x_n)$ in the graph $G_{n,r}$ as estimates of the density evaluated at data $f(x_1),\ldots,f(x_n)$.
+Therefore, a natural way to identify points in high-density regions is to throw out points without sufficiently high degree.
+To identify the high-density regions $\Csig^1,\ldots,\Csig^k$, consider the threshold
+\begin{equation*}
+\lambda' = \frac{\epsilon}{\nu(\Cset^0)} + \frac{c_0}{2}.
+\end{equation*}
+For any $x_i \in \bigcup_{k = 1}^{K}\Csig^k[\Xbf]$ such that $\dist(x_i, \Cset^0) > r$, the expected degree of $x_i$ is lower bounded $\Ebb(\deg_{n,r}(x_i)) = \lambda_{\sigma} \nu_d r^d = (\lambda' + \frac{c_0}{2})\nu_dr^d$.
+On the other hand, for any $x_i \in \Cset^0[\Xbf]$ such that $\dist(x_i, \bigcup_{k = 1}^{K}\Csig^k[\Xbf]) > r$, the expected degree of $x_i$ is upper bounded $\Ebb(\deg_{n,r}(x_i)) \leq (\lambda' - \frac{c_0}{2})\nu_dr^d$.
+Let $n$ be large enough to allow for concentration of the degrees around their means.
+Then the set $C_n(\lambda') = \set{x_i \in \Xbf: \deg_{n,r}(x_i) > \lambda'\nu_dr^d}$ serves as a reasonable estimate of $\bigcup_{k = 1}^{K} \Cset_{\sigma}^k[\Xbf]$, in the sense that with high probability $\bigcup_{k = 1}^{K} \Cset_{\sigma - r}^k[\Xbf] \subseteq C_n(\lambda') \subseteq \bigcup_{k = 1}^{K} \Cset_{\sigma + r}^k[\Xbf]$
+
+For a sufficiently large choice of radius $r$, we can draw the additional conclusion that the subsets $\Cset_{\sigma - r}^k[\Xbf]$ are connected in $G_{n,r}$, and therefore in the graph $G_{n,r}[C_n(\lambda')]$ as well.
+This implies that there are connected components $C^1, \ldots, C^K$ of $G_{n,r}[C_n(\lambda')]$ which are good estimates of $\Csig^1[\Xbf],\ldots,\Csig^K[\Xbf]$, since with high probability $\Cset_{\sigma - r}^k[\Xbf] \subseteq C^k \subseteq \Cset_{\sigma + r}^k[\Xbf]$.
+
+Those points $x_i \in \Xbf$ which are in $\Cset_{\sigma + r}^k$ but not $\Cset_{\sigma}^k$ are those points for which $\Ebb(\deg_{n,r}(x_i))$ may be  approximately equal to $\lambda'$, and so we cannot rule out their belonging to $C^k$.
+The symmetric set difference $\Delta(C^k, \Csig^k[\Xbf])$ is therefore roughly equal to the cardinality of $\{x_i \in X: 0 < \dist(x_i,\Csig^k) \leq r\}$.
+
+To compare this to \eqref{eqn:kappa_example2}, we must provide an estimate of the cardinality of $\{x_i \in X: 0 < \dist(x_i,\Csig^k) \leq r\}$.
+By Lemma~\ref{lem: expected_number_boundary_points}, we have the following upper bound on the expected number of points in this set,
+\begin{equation*}
+\Ebb \abs{\{x_i \in X: 0 < \dist(x_i,\Csig^k) \leq r\}} \leq \frac{4ndr}{\sigma}\left(\lambda_{\sigma} - c_0\right)\nu(\Csig).
+\end{equation*}
+Combined with the fact that $\Ebb \abs{\Csig^k[\Xbf]} = n \lambda_{\sigma} \nu(\Csig)$--and using our bounds on $\lambda_{\sigma}$ and $c_0$ from the previous section--we obtain
+\begin{equation*}
+\frac{\Ebb\abs{\{x_i \in X: 0 < \dist(x_i,\Csig^k) \leq r\}} }{\Ebb \abs{\Csig^k[\Xbf]}} \leq c \frac{K dr \epsilon}{\sigma 2^{d'} \sigma^{d - d'} (1 - \epsilon)},
+\end{equation*}
+where we recognize the right hand side as being identical to the bound on normalized cut we derived in \eqref{eqn:normalized_cut_mixing_time_ub_example2}.
+
+Let us summarize our findings with respect to the particular density cluster $\Csig^1$.
+First, with high probability, only those points $x_i \in X$  such that $0 < \dist(x_i,\Csig^1) \leq r$ will be misclassified by the plug in approach.
+Second, the expected ratio of the number of such points, to the number of total data points that fall in $\Csig^1$, is upper bounded by the same upper bound that we derived on the normalized cut $\Phi_{n,r}(\Csig^1[\Xbf];G_{n,r})$.
+In other words, for a particular choice of radius $r$, the symmetric set difference $\Delta(C^1,\Csig^1[\Xbf])/\abs{\Csig^1[\Xbf]}$ is comparable to the normalized cut of $\Csig^1[\Xbf]$ in $G_{n,r}$, whereas the symmetric set difference $\Delta(C^1,\Csig^1[\Xbf])/\abs{\Csig^1[\Xbf]}$ is upper bounded by the \emph{product} of the normalized cut and the mixing time, which is a looser bound.
+This comparison elucidates an important distinction between estimation of density clusters via PPR, and more classical methods based on plug in estimators.
+The latter approach is robust to poor internal connectivity of the $\sigma$-expansion $\Csig$, whereas the former may not be.
 
@@
 particular interest is the fact that PPR fails to recover one of the moons even
-when normalized cut still succeeds in doing so, supporting our claim from Remark
-\ref{rmk: diameter}. Additionally, we note that the Chaudhuri-Dasgupta algorithm 
-succeeds even when both PPR and normalized cut fail.  While our main message was
+when normalized cut still succeeds in doing so. Additionally, we note that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.  While our main message was
 that PPR recovers geometrically well-conditioned density clusters, it would be  
@@
 By a union bound we see that all three bounds in \eqref{eqn: numerator_additive_bound} hold with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this yields the upper bound \sbcomment{Changed $\mathbf{X}$ to $X$}
-\begin{equation*}
-\Phi_{n,r}(\Csig[X]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+Along with (\ref{eqn: conductance_representation_1}) this yields the upper bound
+\begin{equation*}
+\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
 \end{equation*}
@@
 	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
-Then, upper bounding the integral using \sbcomment{I changed the Lemma referenced here.
-I think it was wrong before} Lemma \ref{lem: expected_number_boundary_points} gives the final result.
+Then, upper bounding the integral using Lemma \ref{lem: expected_number_boundary_points} gives the final result.
 
@@
 	\end{equation*}
-	\sbcomment{Changed $t_i$ to $t_{i,k}$.}
 	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
@@
 	\end{align}
-	\sbcomment{I changed the braces above -- I think they were incorrect earlier} where the second equality comes from rearranging terms in the sum.
+	where the second equality comes from rearranging terms in the sum.
 
@@
 	\end{equation*}
-	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
+	and therefore 
 	\begin{align*}
@@
 \begin{lemma}
-	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
+	\label{lem: covering}
 	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
@@
 \cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
-In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a biLipschitz deformation of a convex set, but for completeness we produce all proofs here.
+In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a Lipschitz deformation of a convex set, but for completeness we produce all proofs here.
 
@@
 	\label{lem: uniform_continuous_conductance}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with Lipschitz constant $L$.
 Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance $\widetilde{\Phi}_{\nu,r}$ satisfies
@@
 	\label{lem: nonconvex_isoperimetry}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with biLipschitz constant $L$.
+	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with Lipschitz constant $L$.
 Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
@@
 The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\Csig$ is itself convex, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among (many) others.
-Once the result is shown in the convex setting, however, it is not hard to show that it applies to bi-Lipschitz transformations of convex sets as well.
+Once the result is shown in the convex setting, however, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
 \begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
@@
 
-\subsection{Concentration inequalities}
+\section{Probabilistic bounds}
 \label{sec: concentration}
 
-Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$-statistic} to be
+Given a symmetric kernel function $K: \Rd \times \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$-statistic} to be
 \begin{equation*}
@@
 We will require large-sample and asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}.
-Let
+Let $\Cset' \in \Cbb_f(\lambda)$ be a high-density cluster, with $\sigma$-expansion $\Csig' = \Cset' + \sigma B$, and recall the notation $\widetilde{\deg}_{n,r}(x) = \deg_{n,r}(x,G_{n,r}[\Csig[\Xbf]])$ for $x \in \Csig[\Xbf]$.
+Then, let
 \begin{alignat*}{2}
@@
 \end{alignat*}
-
+We collect the bounds we need in Lemma \ref{lem: ball_bounds_in_probability}.
 \begin{lemma}
@@
 	\begin{align}
-	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
+	\frac{\degminwt}{n - 1} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
 	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
-	\frac{\abs{\Csig[\Xbf]}}{n} & \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}\\
-	\label{eqn: volwt_bound}
-	\frac{1}{2}\vol_0 &\leq \vol_{n,r}(\Csig[\Xbf])  \leq \frac{3}{2} \vol_0
+	(1 - \epsilon)\Pbb(\Csig) & \leq \frac{\abs{\Csig[\Xbf]}}{n} \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}
 	\end{align}
@@
 	\begin{align}
-	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
+	\liminf_{n \to \infty} \frac{\degminwt}{n - 1} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
 	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d \label{eqn: max_vol_bound_asymp}
@@
 
-	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{align}
-	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
-	\end{align}
-
-	If additionally \ref{asmp: C'_bounded_density} holds (but not necessarily \ref{asmp: valid_region}): for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
+	If additionally \ref{asmp: C'_bounded_density} holds, then for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
 	\begin{equation}
@@
 \begin{proof}
-	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
-	\end{equation*}
-	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
-	\begin{equation*}
-	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
+	We first note that \eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
+Now, we examine~\eqref{eqn: min_cluster_degree_bound}.
+Note that for any $x \in \Csig$, by assumption \ref{asmp: bounded_density} and Lemma~\ref{lem: local_conductance},
+	\begin{equation*}
+	\Ebb(\widetilde{\deg}_{n,r}(x_i)|x_i = x) \geq \frac{6}{25} \lambda_{\sigma}r^d\nu_d,
+	\end{equation*}
+	Conditional on $x_i = x$, the functional $\widetilde{\deg}_{n,r}(x_i)$ is a sum of $n - 1$ independent Bernoulli random variables. Therefore by Lemma \ref{lem: multiplicative_Hoeffding}
+	\begin{equation*}
+	\Pbb\left(\widetilde{\deg}_{n,r}(x_i) \leq (n-1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \mid x_i = x \right) \leq \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} }
+	\end{equation*}
+	Since this holds for all $x \in \Csig$, by the law of total probability it holds unconditionally as well, i.e.
+	\begin{equation*}
+	\Pbb\left(\widetilde{\deg}_{n,r}(x_i) \leq (n - 1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} }
+	\end{equation*}
+	Taking a union bound over all $x_i \in \Csig[\Xbf]$ (of which, of course, there are no more $n$), we have
+	\begin{equation*}
+	\Pbb \left(\degminwt \leq (n - 1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
 	\end{equation*}
 	and we have shown \eqref{eqn: min_cluster_degree_bound}.
-Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
-\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
-
-	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
-
-	Finally, note that
-	\begin{equation*}
-	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
-	\end{equation*}
-	can be rewritten as a U-statistic, and furthermore
-	\begin{equation*}
-	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
-	\end{equation*}
-
-	Therefore by Lemma \ref{lem: bounded_difference}
-	\begin{equation}
-	\label{eqn: ball_bounds_in_probability_1}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
-	\end{equation}
-	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
-Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
-	\begin{equation*}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
-	\end{equation*}
-
-	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
+The equivalent bound \eqref{eqn: max_degree_bound} on maximum degree of vertices $x \in \Csig[\Xbf]$ follows from similar reasoning.
+Under~\ref{asmp: C'_bounded_density}, equivalent reasoning leads to \eqref{eqn: min_cluster_degree_bound_2}.
+Additionally, taking $\epsilon_n \downarrow 0$ sufficiently slowly so that
+	\begin{equation*}
+	\sum_{n = 1}^{\infty }n \exp\set{- \frac{6 n \epsilon_n^2  \lambda_{\sigma} r^d \nu_d}{50} } < \infty
+	\end{equation*}
+	application of the Borel-Cantelli Lemma yields~\eqref{eqn: min_cluster_degree_bound_asymp}.
+
+	Now, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x) = \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
 	\begin{equation*}
@@
 	\end{equation*}
-	The two asymptotic statements \eqref{eqn: min_cluster_degree_bound_asymp} and \eqref{eqn: max_vol_bound_asymp} therefore both follow from the Borel-Cantelli Lemma.
+	Therefore, taking a sequence $\epsilon_n$ such that $\epsilon_n \downarrow 0$ sufficiently slowly so that
+	\begin{equation*}
+	\sum_{n = 1}^{\infty}\exp(-n\epsilon_n^2\mu) < \infty,
+	\end{equation*}
+	the almost-sure bound~\eqref{eqn: max_vol_bound_asymp} follows by the Borel-Cantelli Lemma.
 \end{proof}
@@
 \label{sec: proof_of_misclassification_rate}
-In this section, we prove both Theorem \ref{thm: misclassification_rate}.
-The result is in essence a consequence of the bounds in Theorem~\ref{thm: conductance_upper_bound} 
-and Theorem~\ref{thm: mixing_time_upper_bound} bounding the normalized cut and mixing time, together with the result of \citet{zhu2013} relating the quality of the PPR output to these quantities, and the result in Lemma~\ref{lem: ball_bounds_in_probability}
-that allows us to translate the guarantees on the volume to guarantees on the symmetric set difference.
-
-% and the relevant portions of Corollary \ref{cor: appr}.
-We begin with Lemma \ref{lem: zhu}, which is a restatement of Lemma 3.4 of \citet{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
+In this section, we prove Theorem \ref{thm: misclassification_rate}.
+The result is in essence a consequence of i) a result of \citet{zhu2013} relating the quality of the PPR output to normalized cut and mixing time, and ii) the upper bounds in Theorem~\ref{thm: conductance_upper_bound}
+and Theorem~\ref{thm: mixing_time_upper_bound} on these functionals.
+
+We begin with Lemma \ref{lem: zhu}, which is a restatement of Corollary 3.3 of \citet{zhu2013}, translated into notation consistent with the rest of this paper.
+It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.
 
@@
 	\label{lem: zhu}
-	Let $\varepsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
-Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\varepsilon)} := \pbf^{(\varepsilon)}(v,\alpha; G)$ of the form
-	\begin{equation*}
-	S_{\beta} := \left\{u \in V: \pbf^{(\varepsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
-	\end{equation*}
-	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \varepsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
+	Let $\varepsilon \geq 0$, and suppose $v \in S^g$ and $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$. Consider the approximate PPR vector $p^{(\varepsilon)}_v := p^{(\varepsilon)}(v,\alpha;G)$. Then,
+	\begin{equation}
+	\label{eqn:zhu_1}
+	p^{(\varepsilon)}_v(V \setminus S) \leq 2\frac{\Phi(S;G)}{\alpha},
+	\end{equation}
+	and additionally there exists a residual vector $p_{\ell} \in [0,1]^V$ with $\norm{p_{\ell}}_1 \leq 2\Phi(S;G)/\alpha$ such that
+	\begin{equation}
+	\label{eqn:zhu_2}
+	\textrm{for all $u \in S$}, \quad p^{(\varepsilon)}_v(u) \geq \frac{4}{5} \frac{\deg(u;G[S])}{\vol(S;G)} - \varepsilon \deg(u;G) - p_{\ell}(u).
+	\end{equation}
+\end{lemma}
+
+\noindent Now, consider the sweep cut set
+\begin{equation*}
+S_{\beta} := \set{u \in V: p^{(\varepsilon)} \geq \beta \pi_0},
+\end{equation*}
+and suppose the conditions (on seed node $v$ and teleportation parameter $\alpha$) of Lemma~\ref{lem: zhu} are met.
+Some straightforward calculations show the implications of Lemma~\ref{lem: zhu} on the symmetric set difference metric $\Delta(S_{\beta},S)$.
+In particular,
+\begin{equation}
+\abs{S_{\beta} \setminus S} \leq \frac{p_v(V \setminus S; G)}{\min_{u \in S_{\beta}}p^{(\varepsilon)}_v(u)} \leq \frac{2 \Phi(S;G)/\alpha}{\beta \pi_0}. \label{eqn:zhu_3}
+\end{equation}
+To upper bound $\abs{S \setminus S_{\beta}}$, we first observe that by definition, for every node $u \in S \setminus S_{\beta}$ $p^{(\varepsilon)}(u) \leq \beta \pi_0$.
+Therefore by \eqref{eqn:zhu_2} we have that the residual vector is lower bounded
+\begin{equation}
+\label{eqn:zhu_5}
+p_{\ell}(u) \geq \frac{4\deg(u;G[S])}{5\vol(S;G)} - \varepsilon \deg(u;G) - \beta\pi_0  = \underbrace{\left(\frac{4}{5} - \varepsilon \vol(S;G) \frac{\deg(u;G)}{\deg(u;G[S])}\right)}_{T_1(u,\varepsilon)}\frac{\deg(u;G[S])}{\vol(S;G)} - \beta\pi_0
+\end{equation}
+
+Since $\norm{p_{\ell}}_1 \leq 2\Phi(S;G)/\alpha$, this implies an upper bound on the number of vertices in $S \setminus S_{\beta}$. In particular,
 \begin{align}
-	\vol(S_{\beta} \setminus S; G) & \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(S; G), \label{eqn: zhu_1}\\
-	\vol(S \setminus S_{\beta}; G) & \leq \left(\frac{2\Phi(S;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(S;G)\right)\vol(S; G).  \label{eqn: zhu_2}
+\label{eqn:zhu_4}
+\abs{S \setminus S_{\beta}} \leq \frac{2 \Phi(S;G)/\alpha}{\min_{u \in S} \{T_1(u,\varepsilon)(\deg(u;G[S])/\vol(S;G))\} - \beta\pi_0}. 
 \end{align}
-\end{lemma}
-%\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
-With this Lemma in place we
-observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
-Moreover,
+
+\noindent Together \eqref{eqn:zhu_3} and \eqref{eqn:zhu_4} establish an upper bound on the symmetric set difference $\Delta(S_{\beta},S)$ for a general graph $G$, in terms of several graph functionals and input parameters to Algorithm \ref{alg: ppr}.
+We will move on to establishing bounds on these functionals and parameters in the specific case of $G = G_{n,r}$ and $S = \Csig[\Xbf]$, and the ranges for parameters specified in \eqref{eqn: initialization}.
+First, however, we verify that the conditions of Lemma \ref{lem: zhu} are satisfied under the setup of Theorem~\ref{thm: misclassification_rate}.
+Indeed,
 \begin{enumerate}
-	\item we restrict $v \in \Csig[\Xbf]^g$
-	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$, for some $1/40 < \beta < 1/11$
-	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
+	\item The initialization condition of \eqref{eqn: initialization} explicitly restricts $v \in \Csig[\Xbf]^g$,
+	\item By Theorem \ref{thm: mixing_time_upper_bound} along with the initialization condition of \eqref{eqn: initialization}, we have that with probability tending to 1 as $n \to \infty$, $\alpha \leq 1/(9\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))$,
 	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\varepsilon = 0$.
@@
 
-All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq 1/10\tau_u(\theta)$, the following bounds hold with probability tending to 1 as $n \to \infty$:
-\begin{equation*}
-\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
-\end{equation*}
-Noting that
-\begin{align*}
-\abs{\widehat{C} \setminus \Csig[\Xbf]} & \leq \frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\degmin}   \\
-\abs{\Csig[\Xbf] \setminus \widehat{C}} & \leq \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\degminwt}, \quad \textrm{and} \\
-\abs{\Csig[\Xbf]} & \geq \frac{\vol_{n,r}(\Csig[\Xbf])}{\degmax}
-\end{align*}
-the theorem follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
+All conditions of Lemma~\ref{lem: zhu} are therefore satisfied.
+We now collect the bounds on graph functionals and algorithm parameters we will use to complete the proof of Theorem~\ref{thm: misclassification_rate}.
+\begin{enumerate}
+	\item By Theorem 3, with probability tending to $1$ as $n \to \infty$, $\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\theta)$.
+By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$.
+Therefore, recalling the definition of $\kappa(\Cset)$ in Definition~\eqref{def:well_conditioned_density_cluster}, we have $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
+	\item Since $\pbf(v,\alpha;G_{n,r})$ is an exact PPR vector (i.e. an approximate PPR vector with $\varepsilon = 0$), the expression $T_1(u,\varepsilon)$ defined in \eqref{eqn:zhu_5} reduces to $4/5$.
+	\item From Lemma~\ref{lem: ball_bounds_in_probability} we have that with probability tending to $1$ as $n \to \infty$, for any $\epsilon > 0$, the following statements hold:
+	\begin{equation*}
+	\min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \degminwt \geq 6/25 n (1 - \epsilon) \lambda_{\sigma} \nu_d r^d
+	\end{equation*}
+	and 
+	\begin{equation*}
+	\vol(\Csig[\Xbf];\widetilde{G}_{n,r}) \leq \abs{\Csig[\Xbf]} \degmaxwt \leq \abs{\Csig[\Xbf]} n (1 + \epsilon) \Lambda_{\sigma} \nu_d r^d.
+	\end{equation*}
+	\item Recalling Algorithm \eqref{alg: ppr}, we have that $\widehat{C} = S_{\beta}$ for some $1/40 \leq \beta \leq 1/12$.
+Moreover, by the initialization condition of \eqref{eqn: initialization}, $(3/4)(\lambda_{\sigma}/(\Lambda_{\sigma} n \Pbb(\Csig)) \leq \pi_0 \leq (5/4)(\lambda_{\sigma}/(\Lambda_{\sigma} n \Pbb(\Csig))$.
+Therefore, by \eqref{eqn: Csig_cardinality_bound}, with probability tending to $1$ as $n \to \infty$, $\pi_0$ is contained in the random interval
+	\begin{equation*}
+	(1/2)(\lambda_{\sigma}/(\Lambda_{\sigma} \abs{\Csig{\Xbf}}) \leq \pi_0 \leq (3/2)(\lambda_{\sigma}/(\Lambda_{\sigma} \abs{\Csig{\Xbf}}).
+	\end{equation*}
+\end{enumerate}
+The latter two points imply that with probability tending to $1$ as $n \to \infty$,
+\begin{equation}
+\label{eqn:misclassification_rate_proof_1}
+4 \degminwt/(5\vol_{n,r}(\Csig[\Xbf])) - \beta\pi_0  \geq \frac{1}{24} \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\abs{\Csig[\Xbf]}}.
+\end{equation}
+Therefore,
+\begin{align}
+\Delta(\Cest, \Csig[\Xbf]) & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\beta \pi_0} + \frac{2 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{4 \degminwt/(5\vol_{n,r}(\Csig[\Xbf])) - \beta\pi_0} \nonumber \\
+& \leq \frac{1200 \kappa(\Cset)\Lambda_{\sigma} \abs{\Csig[\Xbf]}}{\lambda_{\sigma}} + \frac{48 \kappa(\Cset) \Lambda_{\sigma} \abs{\Csig{\Xbf}}}{\lambda_{\sigma}}.
+\label{eqn:misclassification_rate_proof_2}
+\end{align}
+and the proof of Theorem \ref{thm: misclassification_rate} is complete.
 
@@
 
-We begin with some notation.
-Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
-Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
+As a reminder, to prove Theorem~\ref{thm: consistent_recovery_of_density_clusters} it will be sufficient to show that under the conditions of that theorem, we have that
+\begin{equation}
+\label{eqn: PPR_gap}
+\min_{u' \in \Cset'[\Xbf]} p_v(u') \leq \beta \pi_0 \leq \min_{u \in \Cset[\Xbf]} p_v(u), \quad \textrm{for every $\beta \in [1/40,1/12]$},
+\end{equation}
+holds with probability tending to $1$ as $n \to \infty$.
+
+To show this, we first establish in Lemma~\ref{lem: setup} that when Algorithm \ref{alg: ppr} is properly initialized, the resulting PPR vector is large for every vertex $u \in \Cset$, and small for every vertex $u' \in \Cset'$.
+Let $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ be the vector given by
 \begin{equation*}
@@
 (Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
-
-Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(x) - \overline{\pibf}_{n,r}(x)$.
 
@@
 	Let $0 < r < \sigma$ and $\alpha \leq \frac{1}{9 \tau_{\infty}(\widetilde{G}_{n,r})}$.
-Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
+Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf_v := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
 	\begin{itemize}
@@
 		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminwt}
+		\pbf_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminwt}
 		\end{equation}
@@
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminpr}.
+		\pbf_v(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminpr}.
 		\end{equation}
@@
 
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-%\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-%~
-
-In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
-As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
-\begin{align}
-\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
-\end{align}
-We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
-\begin{align}
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
-\end{align}
-
-The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
-& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-Similarly, for each $u' \in \Cset'[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
-& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
-& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
-
-It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
-\begin{equation}
-\label{eqn: pimin_Dmin_lb}
-\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
-\end{equation}
-
-Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
-\begin{equation}
-\label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
-\end{equation}
-\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
+We immediately note that by assumption, Algorithm \ref{alg: ppr} is well-initialized, and therefore the seed node $v$ is chosen in $\Csig[\Xbf]^g$.
+Since we additionally assume $\Cset$ is a $\kappa$-well-conditioned density cluster, we have that $r < \sigma/(2d) < \sigma$, and the upper bound $\alpha \leq 1/(9 \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))$ holds by Theorem \ref{thm: mixing_time_upper_bound}, with probability tending to $1$ as $n \to \infty$.
+Therefore, all the conditions of Lemma \ref{lem: setup} are met.
+
+We now collect the estimates on graph functionals and PPR parameters we will use to complete the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}. 
+\begin{itemize}
+	\item By Theorem 3, with probability tending to $1$ as $n \to \infty$, $\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\theta)$.
+By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$.
+Therefore, recalling the definition of $\kappa(\Cset)$ in Definition~\eqref{def:well_conditioned_density_cluster}, we have $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
+	\item By Lemma \ref{lem: ball_bounds_in_probability}, for some $\epsilon > 0$ to be chosen later, 
+	\begin{equation*}
+	\degminwt, \degminpr \geq (6/25)(1 - \epsilon)nr^d \nu_d \lambda_{\sigma}
+	\end{equation*}
+	and additionally
+	\begin{equation*}
+	\widetilde{\vol}_{n,r}(\Csig[\Xbf]) \leq n^2 \Pbb(\Csig) \nu_d r^d \Lambda_{\sigma}
+	\end{equation*}
+	each with probability tending to $1$ as $n \to \infty$.
+
+	\item By the initialization condition of \eqref{eqn: initialization}, $\pi_0 \in [3/4,5/4] \lambda_{\sigma}/(n\Pbb(\Csig)\Lambda_{\sigma})$. 
+\end{itemize}
+
+Assuming these bounds hold, for sufficiently small choices of $\epsilon > 0$ and the constant $c$ in the upper bound \eqref{eqn: kappa_ub}, we have that for all $u \in \Cset[\Xbf]$,
+\begin{equation}
+\label{eqn:proof_consistent_cluster_recovery_2}
+p_v(u) \geq \frac{24(1-\epsilon) \lambda_{\sigma}}{125 n \Pbb(\Csig) \Lambda_{\sigma}} - \frac{250 \kappa(\Cset)}{3(1-\epsilon)nr^d\nu_d\lambda_{\sigma}} \geq \frac{5\lambda_{\sigma}}{48\Lambda_{\sigma} \Pbb(\Csig)} \geq \pi_0/12.
+\end{equation}
+and for all $u' \in \Cset'[\Xbf]$,
+\begin{equation}
+\label{eqn:proof_consistent_cluster_recovery_1}
+p_v(u') \leq \frac{250 \kappa(\Cset)}{3(1-\epsilon)nr^d\nu_d\lambda_{\sigma}} < \frac{3\lambda_{\sigma}}{160\Lambda_{\sigma} \Pbb(\Csig)} \leq \pi_0/40. 
+\end{equation}
+and \eqref{eqn: PPR_gap} follows.
+
+We defer the proof of Lemma \ref{lem: setup}, and first extend Theorems~\ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters} to apply with respect to the aPPR vector.
 
@@
 \label{sec:appr}
-Before we proceed to the next section, we include a formal statement of our claims regarding the a\pprspace vector. 
+We are now in a position to formally state and prove our claims regarding the a\pprspace vector. 
 \begin{corollary}
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+Choose input parameters $\alpha, r, \pi_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, additionally set
+	\begin{equation}
+	\label{eqn: appr_parameter}
+	\varepsilon = \frac{1}{25 n^2 \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d}
+	\end{equation}
+	and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}_v$ rather than the exact \pprspace vector $\pbf_v$, with resulting output $\Cest$. Then
 	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item The upper bound on symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ given by \eqref{eqn: misclassification_rate_ub} is still valid.
 		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
@@
 \begin{proof}
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
+To prove the first claim, note that in the proof of Theorem~\ref{thm: misclassification_rate}, the only time we use the fact that $p(v,\alpha; G_{n,r})$ is an exact PPR vector is to show $T_1(u,\varepsilon) \geq 4/5$.
+Now, we will show that the choice of $\varepsilon$ given by \eqref{eqn: appr_parameter} results in the upper bound $T_1(u,\varepsilon) \geq 3/5$.
+As a result, \eqref{eqn:misclassification_rate_proof_1} and therefore \eqref{eqn:misclassification_rate_proof_2} will still hold, up to constants.
+
+To show the desired upper bound on $T_1(u,\varepsilon)$, observe that for any $\epsilon > 0$, with probability tending to $1$ as $n \to \infty$, 
+\begin{equation}
+\label{eqn: appr_parameter_lb}
+\varepsilon \leq \frac{1}{25(1 - \epsilon)\vol_{n,r}(\Csig[\Xbf])},
+\end{equation}
+and
+\begin{equation*}
+\max_{u \in \Csig[\Xbf]} \bigl\{ \deg_{n,r}(u) - \widetilde{\deg}_{n,r}(u)\bigr\} \leq (19/25)(1 + \epsilon) \lambda \nu_d r^d.
+\end{equation*}
+Assuming these bounds hold, we can upper bound $T_1(u,\varepsilon)$ when $G = G_{n,r}$, as follows:
+\begin{align*}
+T_1(u,\varepsilon) & = \frac{4}{5} - \varepsilon \vol(\Csig[\Xbf];G_{n,r}) \frac{\deg(u;G_{n,r})}{\deg(u; \widetilde{G}_{n,r})} \\
+& \geq \frac{4}{5} - \frac{(1 + \epsilon) \lambda \nu_d r^d + \widetilde{\deg}_{n,r}(u)}{25(1 - \epsilon)\widetilde{\deg}_{n,r}(u)} \\
+& \geq \frac{4}{5} - \frac{(1 + \epsilon) \lambda \nu_d r^d + \degminwt}{25(1 - \epsilon)\degminwt} \\
+& \geq \frac{4}{5} - \frac{(19/25)(1 + \epsilon) + 6/25}{6(1 - \epsilon)}
+\end{align*}
+and so, for $\epsilon > 0$ sufficiently small, we have $T_1(u,\varepsilon) \geq 3/5$.
 
@@
 
-Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
-\begin{equation*}
-\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
-\end{equation*}
-and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
-\begin{equation*}
-\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
-\end{equation*}
-On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+We now prove the second claim, by showing that both bounds in \eqref{eqn: PPR_gap} hold with respect to the aPPR vector.
+The upper bound follows immediately.
+Since $p^{(\varepsilon)}_v(x) \leq p_v(x)$ for all $x \in \Xbf$, the upper bound on $\max_{u' \in \Cset'[\Xbf]} p_v(u')$ also applies to $\max_{u' \in \Cset'[\Xbf]} p^{(\varepsilon)}_v(u')$.
+
+To show the desired lower bound on $\min_{u \in \Cset[\Xbf]} p^{(\varepsilon)}_v(u)$, we use the uniform approximation guarantee in \eqref{eqn: appr_error}.
+Note that for every $u \in \Cset[\Xbf]$, since $r < \sigma$, every point $x \in \Xbf$ connected to $u$ must be contained in $\Csig$.
+Therefore $\widetilde{\deg}_{n,r}(u) = \deg_{n,r}(u)$.
+Along with \eqref{eqn: appr_parameter_lb}, this means
+\begin{equation*}
+\varepsilon \deg_{n,r}(u) \leq \frac{\overline{\pi}_{n,r}(u)}{25(1 - \epsilon)}
+\end{equation*}
+and therefore by \eqref{eqn: lower_bound_PPR_in_cluster}, for every $u \in \Cset[\Xbf]$,
+\begin{equation*}
+p^{(\varepsilon)}_v(u) \geq \left\{\frac{4}{5} - \frac{1}{25(1 - \epsilon)}\right\} \overline{\pi}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\widetilde{\deg}_{\min}}.
+\end{equation*}
+\noindent Using the arguments given in the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}, and choosing the universal constant in \eqref{eqn: kappa_ub} to be sufficiently small, the upper bound in \eqref{eqn:proof_consistent_cluster_recovery_2} follows.
 
@@
 \subsection{Proof of Lemma~\ref{lem: setup}}
-	%The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. 
+
+To state Lemma~\ref{lem: setup}, we introduce some notation.
+Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices over the induced subgraph $\widetilde{G}_{n,r}$.
 Given a starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
@@
 	\label{eqn: zhulemma3.1}
-	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
+	\pbf_v(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
 	\end{equation}
@@
 	\begin{equation*}
-	\widetilde{\pbf}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
+	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
 	\end{equation*}
@@
 	\begin{equation*}
-	\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
+	\pbf_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
 	\end{equation*}

### 2019-10-11 notes/weekly_notes/10.11.19.NotesForWeek.tex
added this weeks notes on PPR partionining and lower bound

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\newcommand{\Holder}{H{\"o}lder}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}
\newcommand{\Leb}{\mathcal{L}}
\newcommand{\dist}{\mathrm{dist}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{Notes for week of 10/4/19 - 10/11/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $G = (V,E)$ be an undirected, unweighted graph with $m = \abs{E}$ total edges, defined on vertices $v_1, \ldots, v_n$. Let $A = (A_{ij})$ be the adjacency matrix of $G$, $W = (D^{-1}A + I)/2$ be the lazy random walk matrix over $G$, and for $s \in \Reals^n$ and $\alpha \in [0,1]$, define the PPR vector
\begin{equation*}
p(\alpha,s) = \alpha s + (1 - \alpha) s p(\alpha,s)W.
\end{equation*}
(We will often drop the dependence on $\alpha,s$ and denote the PPR vector as $p$.)

Order the vertices $v_{(1)},\ldots,v_{(n)}$ so that $p(v_{(1)})/d(v_{(1)}) \geq \ldots, p(v_{(n)})/d(v_{(n)})$, where $d(v_i) = \sum_{i = 1}^{n} A_{ij}$ is the degree of $v_i$. We refer to
\begin{equation*}
S_j = \set{v_{(1)},\ldots,v_{(j)}}
\end{equation*}
as the $j$th sweep cut of the PPR vector.

It is known that if there exists a set $S \subset V$ with small normalized cut, then when the PPR vector is properly initialized, some sweep cut $S_j$ of the PPR vector will itself have small normalized cut. Normalized cut is defined as
\begin{equation*}
\Phi(S) = \frac{\sum_{v_i \in S}\sum_{v_j \in S^c} A_{ij}}{\min{\vol(S),2m - \vol(S)}}
\end{equation*}
where $\vol(S) = \sum_{v_i \in S} d(v_i)$ is the volume of $S$.

The proof that PPR is a good local partitioning algorithm (i.e. it concentrates on sets of small normalized cut) is heavily dependent on mixing time results for the PPR vector. We now give these results, before stating and proving some improvements.

\section{Mixing of the PPR vector.}

To quantify the mixing of the PPR vector, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$. For $k_j = \vol(S_j)$ for some sweep cut $S_j$, we let $p[k_j] = p(S_j)$, where we adopt the convention $p(S) = \sum_{v_i \in S} p_i$ for a vector $p \in \Reals^n$. We then define $p[\cdot]$ over its domain by interpolating between $0, p[k_1], \ldots, p[k_n]$. The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$
\begin{equation*}
h(k) = p[k] - \frac{k}{2m}.
\end{equation*}

\subsection{Previous work.}

The following theorem, given by \textcolor{red}{Anderson,Chung,Lang}, gives an upper bound on $h(k)$ as a function of $\Phi(p)$, where $\Phi(p) = \min_{j = 1,\ldots,n} \Phi(S_j)$ is the smallest normalized cut of any sweep cut of $p$. 
\begin{theorem}[Theorem 3 of \textcolor{red}{ACL}]
	\label{thm:acl_1}
	Let $p = p(\alpha,s)$ be a PPR vector, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$ and any $k \in [0,2m]$:
	\begin{equation*}
	h(k) \leq \alpha t + \sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t.
	\end{equation*}
	(where $\overline{k} = \min\set{k,2m-k}$), or $\Phi(p) < \phi$. 
\end{theorem}

The following result is essentially the contrapositive of Theorem \ref{thm:acl_1}.
\begin{theorem}
	\label{thm:acl_2}
	If there exists a set $S \subset V$ and a constant $\delta \geq \frac{2}{\sqrt{m}}$ satisfying
	\begin{equation*}
	p(\alpha,s) - \frac{\vol(S)}{2m} > \delta,
	\end{equation*}
	then
	\begin{equation*}
	\Phi(p) < \sqrt{\frac{18\alpha \log(m)}{\delta}}.
	\end{equation*}
\end{theorem}

\subsection{Improved bounds.}

The presence of the factor of $\sqrt{\log(m)}$ is antagonistic to any work trying to prove consistency results, meaning results when $\abs{V} \to \infty$. We therefore state and prove alternatives to Theorems~\ref{thm:acl_1} and \ref{thm:acl_2}, which allow us to avoid this factor of $\sqrt{\log(m)}$ under certain conditions. These theorems are related to the mixing time results proved by \textcolor{red}{Lovasz,Simonovits}. To state them, we must introduce some additional notation.For a given $0 \leq K_0 \leq m$, let 
\begin{equation*}
L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
\end{equation*}
be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$. Additionally, let
\begin{equation*}
C(K_0) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
\end{equation*}
\begin{theorem}
	\label{thm: mixing_time_PPR}
	Let $p = p(\alpha,s)$ be a PPR vector, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$, any $0 < K_0 < m$, and any $k \in [K_0,2m - K_0]$:
	\begin{equation}
	\label{eqn:mixing_time_PPR}
	h(k) \leq \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
	\end{equation}
	or $\Phi(p) < \phi$.
\end{theorem}

As a sanity check, we confirm that Theorem~\ref{thm: mixing_time_PPR} is no weaker than Theorem~\ref{thm:acl_1}. It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0) \leq 1$ for any $K_0$. Setting $K_0 = 0$ in Theorem~\ref{thm: mixing_time_PPR}, we therefore recover Theorem~\ref{thm:acl_1}.

We now proceed to identify when Theorem~\ref{thm: mixing_time_PPR} may offer some improvement on Theorem~\ref{thm:acl_1}, by showing when we can upper bound $C(K_0) << 1$. The critical point is that since $h(k)$ is concave and $L_{K_0}(k) = h(k)$ when $k = K_0$, the upper bound
\begin{equation*}
\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq h'(K_0) \sqrt{k}.
\end{equation*}
holds whenever $k < m$. For similar reasons, when $k > m$, 
\begin{equation*}
\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq -h'(2m - K_0) \sqrt{2m - k}.
\end{equation*} 
(Since $h$ is not differentiable at points $k = \vol(S_j)$, here we use $h'$ to denote the left derivative of $h$ whenever $k < m$, and the right derivative of $h$ whenever $k \geq m$)

The following Lemma gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, and a resulting upper bound on $C(K_0)$. Let $d_{\min}$ and $d_{\max}$ be the minimum and maximum degrees of $G$, respectively. 
\begin{lemma}
	\label{lem:linearization_bound}
	Assume $s = \chi_v$ for some $v \in V$. If $S_1 = \set{v}$, let $K_0 = d(v)$ otherwise let $K_0 = 0$. Then, 
	\begin{equation}
	\label{eqn:left_derivative}
	h'(K_0) \leq  \frac{1}{2d_{\min}^2}.
	\end{equation}
	Additionally, for all $K_0 \in [0,2m]$,
	\begin{equation}
	\label{eqn:right_derivative}
	h'(2m - K_0) \geq \frac{d_{\max}}{d_{\min}\vol(G)}.
	\end{equation}
	As a result,
	\begin{equation*}
	C(K_0) \leq \frac{\sqrt{m}}{d_{\min}^2}.
	\end{equation*}
\end{lemma}

To bring Theorem~\ref{thm: mixing_time_PPR} to bear, we must also upper bound the linear interpolator $L_{K_0}(k)$. Of course, trivially $L_{K_0}(k) \leq \max\set{h(K_0), h(2m - K_0)}$ for all $k$. As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$.
\begin{lemma}
	\label{lem:interpolator_bound}
	Assume $s = \chi_v$ for some $v \in V$. Let $K_0 = \vol(S_j)$ for some $j = 0,\ldots,n$. Then, 
	\begin{equation*}
	h(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h(K_0) \leq \frac{K_0}{2d_{\min}^2} + \frac{2\alpha}{1 + \alpha}.
	\end{equation*}
	Therefore, for any $k \in \Reals$,
	\begin{equation*}
	L_{K_0}(k) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2}.
	\end{equation*}
\end{lemma}

Combining Theorem~\ref{thm: mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound}, we have the following result.
\begin{corollary}
	\label{cor:mixing_time_PPR}
	Let $p = p(\alpha,\chi_v)$ be a PPR vector with seed node $v \in V$, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$ and any $k \in [d(v),2m - d(v)]$:
	\begin{equation*}
	h(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t}
	\end{equation*}
	or $\Phi(p) < \phi$.
\end{corollary}
\begin{proof}
	If $S_1 = \set{v}$, choose $K_0 = d(v)$; otherwise, choose $K_0 = 0$. As a result, Lemma~\ref{lem:linearization_bound} holds. Then, apply Theorem~\ref{thm: mixing_time_PPR} and Lemma~\ref{lem:interpolator_bound}.
\end{proof}
It is worth briefly comparing Corollary~\ref{cor:mixing_time_PPR} to Theorem~\ref{thm:acl_1}. Corollary~\ref{cor:mixing_time_PPR} will give better estimates of $h(k)$ when $\alpha$ is small, the degrees $d(u)$ are relatively uniform across $u \in V$, and $\frac{\sqrt{m}}{d_{\min}^2} << 1$, i.e. $d_{\min} >> \sqrt{n}$. This last point is the key: it reflects the fact that, all else being equal, random walks mix faster on graphs where all the very small sets (e.g singletons) have very large expansion. More nuanced improvements of this nature are discussed further in \textcolor{red}{Kannan,Lovasz,Montenegro}, albeit with respect to continuous space random walks, rather than the case of PPR over a graph we consider here.

We are now in a position to state the main result of this section. It is similar in form to Theorem~\ref{thm:acl_2}, but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR} as opposed to Theorem~\ref{thm:acl_1}.
\begin{theorem}
	\label{thm:mixing_time_PPR_contrapositive}
	Let $p = p(\alpha,\chi_v)$ be a PPR vector with seed node $v \in V$. Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$, such that
	\begin{equation}
	\label{eqn:mixing_time_PPR_contrapositive_1}
	p(S) - \frac{\vol(S)}{\vol(G)} > \delta
	\end{equation}
	for a set $S$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$. Then there exists a sweep cut $S_j$ of $p$, such that
	\begin{equation*}
	\Phi(S_j) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
	\end{equation*}
	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
\end{theorem}
\begin{proof}
	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}. Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.

	Now, letting
	\begin{equation*}
	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
	\end{equation*}
	we have that
	\begin{equation*}
	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
	\end{equation*}
	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
\end{proof}

\section{Improved Local Partitioning with PPR.}

As in \textcolor{red}{Anderson,Chung,Lang}, the mixing time results of the previous section lead to an upper bound on the conductance of the PPR vector $\Phi(p) = \min_{j = 1,\ldots,n} \Phi(S_j)$. First, we restate a theorem of \textcolor{red}{ACL} which lower bounds the probability mass $p(\alpha,s)(C)$ as a function of the normalized cut $\Phi(C)$.
\begin{theorem}
	\label{thm:acl_3}
	For any set $C$ and any constant $\alpha$, there exists a subset $C_{\alpha} \subset C$ with $\vol(C_{\alpha}) \geq \vol(C)/2$, such that for any vertex $v \in C_{\alpha}$, the PPR vector $p(\alpha,\chi_v)$ satisfies
	\begin{equation*}
	p(\alpha,\chi_v)(C) \geq 1 - \frac{\Phi(C)}{\alpha}.
	\end{equation*}
\end{theorem}

Combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3} leads to an upper bound on $\Phi(p)$.
\begin{theorem}
	\label{thm:conductance_ppr}
	Let $C$ be a set satisfying
	\begin{itemize}
		\item $\vol(C) \leq \frac{2}{3}\vol(G)$,
		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
		\item $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
	\end{itemize}
Set $\alpha = 10\Phi(C)$. Then, for any $v \in C_{\alpha}$,
\begin{equation*}
\Phi(p(\alpha,\chi_v)) \leq \sqrt{1600\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C)}
\end{equation*}
\end{theorem}

\section{Local Partitioning of Neighborhood Graphs.}

Let $\mathcal{X} \subseteq \Reals^d$ be a compact domain, and let $\mathbb{P}$ be a probability distribution defined on $\mathcal{X}$ with density $f$. Sample $X = \set{x_1,\ldots,x_n}$ independently from $f$. For a given radius $r \in (0,\infty)$, the neighborhood graph $G := G_{n,r}$ has vertices $V = X$, and edges $E = \set{(x_i,x_j): \abs{x_i - x_j} \leq r}$.

To apply Theorem~\ref{thm:mixing_time_PPR_contrapositive} to the specific case of $G$ a neighborhood graph, we will need estimates on the degree and volume graph functionals. These estimates will rely on certain regularity properties of $\mathcal{X}$ and $f$. In particular, we will assume
\begin{itemize}
	\label{asmp:regularity_conditions}
	\item There exist $\lambda_{\min}$ and $\lambda_{\max}$ such that for any $x \in \mathcal{X}$:
	\begin{equation*}
	0 < \lambda_{\min} < f(x) < \lambda_{\max} < \infty.
	\end{equation*}
	\item There exists some $a > 0$ such that for any $r >0 $ and any $x \in \mathcal{X}$,
	\begin{equation*}
	\nu(B(x,r) \cap \mathcal{X}) \geq \frac{r^d}{a},
	\end{equation*}
	where $\nu(\cdot)$ is Lebesgue measure on $\Reals^d$ and $B(x,r)$ is the ball centered at $x$ of radius $r$. 
\end{itemize}
We collect our bounds on graph functionals in the following Lemma.
\begin{lemma}
	\label{lem:graph_functional_concentration}
	Suppose $\mathcal{X}$ and $f$ satisfy the regularity properties. Fix $\mathcal{S} \subseteq \mathcal{X}$, and write $\mathcal{S}[X] = \mathcal{X} \cap \set{x_1,\ldots,x_n}$.  For any $\delta \in (0,1)$, suppose
	\begin{equation}
	\label{eqn:graph_functional_concentration_1}
	n \geq a \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{\lambda_{\max}}{\lambda_{\min}} \max\set{\frac{1}{\Pbb(\mathcal{S})}, \frac{10a}{(1-\delta)\lambda_{\min}\nu_dr^d}}.
	\end{equation}
	Then there exists constants $c_1,c_2$ independent of $n$ such that following statements hold with probability at least $1 - c_1n\exp\{-c_2n\}$:
	\begin{itemize}
		\item $\abs{\mathcal{S}[X]} \geq \frac{d_{\max}}{d_{\min}}$, 
		\item $\frac{d_{\max}}{2d_{\min}^2} < \frac{1}{20}$. 
	\end{itemize}
	If additionally
	\begin{equation}
	\label{eqn:graph_functional_concentration_2}
	\mathbb{E}[\vol(\mathcal{S}[X])] \leq 2\frac{(1 - \delta)}{(1 + \delta)} \mathbb{E}[\vol((\mathcal{X}\setminus\mathcal{S})[X])]
	\end{equation}
	then $\vol(\mathcal{S}[X]) \leq \frac{2}{3} \vol(G)$ with probability at least $1 - c_3n\exp\{-c_4n\}$, where $c_3,c_4$ are constants independent of $n$. 
\end{lemma}

Together Lemma~\ref{lem:graph_functional_concentration} and Theorem~\ref{thm:mixing_time_PPR_contrapositive} imply the following result.
\begin{corollary}
	\label{cor:conductance_ppr_neighborhood_graph}
	Fix $\mathcal{S} \subset \mathcal{X}$, and $\delta \in (0,1)$. Suppose 
	\begin{itemize}
		\item $\mathcal{X}$ and $f$ satisfy the regularity properties,
		\item  $\mathcal{S}$ satisfies \eqref{eqn:graph_functional_concentration_2} for any $r \in (0,\infty)$, and
		\item The sample size $n$ satisfies \eqref{eqn:graph_functional_concentration_1},
		\item The normalized cut $\Phi(\mathcal{S}[X]) \leq \frac{1}{200}$.
	\end{itemize}.
	Set $\alpha = \Phi(\mathcal{S}[X])$. For any $v \in \mathcal{S}[X]_{\alpha}$,
	\begin{equation*}
	\Phi(p(\alpha,\chi_v)) \leq \sqrt{1600\left\{2\log\left(\frac{a}{(1 - \delta)\lambda_{\min}\nu_d r^d}\right) + \log 20\right\} \Phi(\mathcal{S}[X])}
	\end{equation*}
	with probability at least $1 - cn\exp\set{-cn}$. 
\end{corollary}
The important takeaway is that $\Phi(p) \lesssim \sqrt{\Phi(\mathcal{S}[X])}$ (where we write $a_n \lesssim b_n$ when there exists constant $c$ such that $a_n \leq c b_n$ for all $n$.) In particular, we have eliminated the factor of $\log(\vol(G))$ which made upper bounds derived from Theorem~\ref{thm:acl_2} facile as $n,\vol(G) \to \infty$.

\section{Implications for Density Clustering Lower Bound.}

To show a lower bound for density clustering using PPR, we exhibit a hard case: that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster. Let $\mathcal{C}_0$, $\mathcal{C}_1$, and $\mathcal{C}_2$ be rectangles in $\Reals^2$, 
\begin{equation*}
\mathcal{C}_0 = \left[-\frac{3\sigma}{2}, -\frac{\sigma}{2}\right] \times \left[-\frac{\rho}{2}, \frac{\rho}{2}\right], \quad \mathcal{C}_1 = \mathcal{C}_0 + (\sigma,0), \quad \mathcal{C}_2 = \mathcal{C}_0 + (2\sigma,0)
\end{equation*}
and let $\mathbb{P}$ be the mixture distribution
\begin{equation*}
\mathbb{P} = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 + \frac{\epsilon}{2} \Psi_0
\end{equation*}
where $\Psi_m$ is the uniform distribution over $\mathcal{C}_m$ for $m = 0,1,2$. 
The density function $f$ of $\Pbb$ is clearly
\begin{equation*}
f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_1) + \frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_2) + \frac{\epsilon}{2}\1(x \in \mathcal{C}_0)  \right)
\end{equation*}
so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_1, \mathcal{C}_2}$.

Sample $x_1,\ldots,x_n$ from $f$, and form the neighborhood graph $G$. Let $p(\alpha,\chi_v)$ be a PPR vector defined on $G$, and suppose our goal is to recover $\mathcal{C}_1$ using $\widehat{C} = \argmin_{i = 1,\ldots,n} \Phi(S_j)$, the minimum conductance sweep cut of $p$. As the following Lemma demonstrates, even when $p(\alpha,\chi_v)$ is reasonably initialized, if the density cluster $\mathcal{C}_1$ is sufficiently geometrically ill-conditioned there are many seed nodes $v \in \mathcal{C}_1$ such that $\widehat{C}$ will fail to recover $\mathcal{C}_1$.

\begin{theorem}
	Let \textcolor{red}{$\alpha = 10 \Phi_{n,r}(\mathcal{L}[X])$} and $r = \sigma/4$. Suppose $\frac{r}{\sigma} < \frac{1}{6400}$. Then, there exists a set $C_{\alpha}$ with $\abs{C_{\alpha} \cap \mathcal{C}_1[X]} \geq \abs{\mathcal{C}_1[X]}/6$ such that for any $v \in C_{\alpha}$, the minimum conductance sweep cut $\widehat{C}$ of $p(\alpha,\chi_v)$,
	\begin{equation*}
	\frac{\abs{\widehat{C} \triangle \mathcal{C}_1[X]}}{n} \geq 1 - c \frac{1}{\epsilon^2} \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right)\frac{\sigma}{\rho}}
	\end{equation*}
	with probability at least $1 - c_1 n \exp\set{-c_2n}$, where $c_1,c_2$ are constants which do not depend on $n$.
\end{theorem}
\begin{proof}
	Let $\mathcal{L}$ be the bottom half of the rectangle $\mathcal{X}$,
	\begin{equation*}
	\mathcal{L} = \left[-\frac{3\sigma}{2}, \frac{3\sigma}{2}\right] \times \left[-\frac{\rho}{2},\frac{\rho}{2}\right].
	\end{equation*}
	We will take for granted that with probability at least $1 - c_1 n \exp\set{-c_2n}$, the following two statements are true
	\begin{enumerate}
		\item $\Phi(\mathcal{L}[X]) \leq 32 \frac{r}{\rho}$, and
		\item For any set $A \subset X$,
		\begin{equation}
		\label{eqn:conductance_C1}
		\Phi(A) \geq \frac{\epsilon^2 r}{\sigma}\left(1 - \frac{\abs{\widehat{C} \triangle \mathcal{C}_1[X]}}{n(1 - \epsilon)}\right)
		\end{equation}
	\end{enumerate}
	It can be shown that $\mathcal{L}$ and $\mathcal{X},f$ satisfy all of the conditions of Corollary~\ref{cor:conductance_ppr_neighborhood_graph}. Therefore, choosing $\alpha = 10 \Phi_{n,r}(\mathcal{L}[X])$, there exists a set $C_{\alpha}$ with $\vol(C_{\alpha}) \geq \vol(\mathcal{L}[X])/2$ such that 
	\begin{equation*}
	\Phi(\widehat{C}) \leq c \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right) \Phi(\mathcal{L}[X])} \leq c \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right) \frac{r}{\rho}}.
	\end{equation*}
	Combining this inequality with \eqref{eqn:conductance_C1}, we have
	\begin{equation*}
	\frac{\epsilon^2 r}{\sigma}\left(1 - \frac{\abs{\widehat{C} \triangle \mathcal{C}_1[X]}}{n(1 - \epsilon)}\right) \leq c \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right) \frac{r}{\rho}}.
	\end{equation*}
	Plugging in $r = \sigma/4$, and solving for $\frac{\abs{\widehat{C} \triangle \mathcal{C}_1[X]}}{n}$, we obtain the desired result.
\end{proof}

\section{Proofs.}

\subsection{Proof of Theorem~\ref{thm: mixing_time_PPR}.}
The proof of Theorem~\ref{thm: mixing_time_PPR} is essentially a combination of the proofs of Theorem~\ref{thm:acl_1} and Theorem 1.2 in \textcolor{red}{Lovasz and Simonovits.} We will show that if $\Phi(p) > \phi$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in (K_0,2m - K_0)$.

We proceed by induction on $t$. Our base case will be $t = 0$. Observe that $C(K_0) \cdot \sqrt{\overline{k}} \geq  h(k) - L_{K_0}(k)$ for all $k \in [K_0,2m - K_0]$, which implies
\begin{equation*}
L_{K_0}(k) + C(K_0) \cdot \sqrt{\overline{k}} \geq h(k).
\end{equation*}

Now, we proceed with the inductive step. We will show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$. Once this is shown, it holds for all $k \in [K_0,2m - K_0]$ by the concavity of the square root function.

By Lemma~\ref{lem:acl_1}, we have
\begin{align}
p[k_j] & \leq \alpha s(S_j) + \frac{1 - \alpha}{2} \left(p[k_j +  \abs{\partial(S_j)}] + p[k_j - \abs{\partial{S_j}}]  \right) \nonumber \\
& \leq \alpha + \frac{1}{2}  \left(p[k_j - \abs{\partial(S_j)}] + p[k_j + \abs{\partial{S_j}}]  \right) \nonumber\\
& \leq \alpha + \frac{1}{2} \left(p[k_j - \Phi(S_j) \overline{k}_j] + p[k_j + \Phi(S_j) \overline{k}_j]  \right) \nonumber \\
& \leq \alpha + \frac{1}{2} \left(p[k_j - \phi \overline{k}_j] + p[k_j + \phi \overline{k}_j]\right) \nonumber
\end{align}
and subtracting $k_j/2m$ from both sides, we get
\begin{equation}
\label{eqn:mixing_time_PPR_pf1}
h(k_j) \leq \alpha + \frac{1}{2} \bigl(h(k_j - \phi \overline{k}_j) + h(k_j +  \phi \overline{k}_j) \bigr)
\end{equation}
From this point, we divide our analysis into cases.

\textbf{Case 1.}
Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
\begin{align*}
h(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
\end{align*}
A Taylor expansion of $\sqrt{1 + \phi}$ around $\phi = 0$ yields the following bound (see Lemma \ref{lem:taylor_expansion}):
\begin{equation*}
\sqrt{1 + \phi} + \sqrt{1 - \phi} \leq 2 - \frac{\phi^2}{4}
\end{equation*}
and therefore
\begin{equation*}
h(k_j) \leq  \alpha t + L_{K_0}(k) + \frac{C(K_0)}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
\end{equation*}

\textbf{Case 2.}

Now, assume one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. By the concavity of $h$, and applying the inductive hypothesis when valid, we have
\begin{align*}
h(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0) + L_{K_0}(2k_j - K_0\bigr) + C(K_0)\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
\end{align*}

\subsection{Proof of Lemma~\ref{lem:linearization_bound}.}
The result of the Lemma is obvious once we show \eqref{eqn:left_derivative} and \eqref{eqn:right_derivative}.

Assume $k < m$, and let $\vol(S_j) \leq k < \vol(S_{j + 1})$ (where we let $S_0 = \emptyset$. The function $h$ has the following representation:
\begin{equation}
\label{eqn:lovasz_simonovits}
h(k) = \sum_{i = 0}^{j} \left(p(v_{(i)}) - \pi(v_{(i)})\right) + \frac{k - \vol(S_j)}{d(v_{(j + 1)})} \left(p(v_{(j+1)}) - \pi(v_{(j+1)})\right) 
\end{equation}
where $\pi(s) = d(s)/\vol(G)$.

From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
\begin{equation}
\label{eqn:linearization_bound_pf1}
h'(k) \leq \frac{p(v_{(j + 1)})}{d(v_{(j + 1)})}
\end{equation}

By Lemma~\ref{lem:crude_ppr_bound}, if $v_{(1)} = v$, then
\begin{equation*}
p(\alpha,s)(v_{(2)}) \leq \frac{1}{2d_{\min}},
\end{equation*}
and if $v_{(1)} \neq v$ then the same inequality holds with respect to $p(\alpha,s)(v_{(1)})$. 
As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = d(v)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}.

Now assume $k \geq m$. The inequality \eqref{eqn:right_derivative} follows almost immediately from the representation \eqref{eqn:lovasz_simonovits}, since
\begin{equation*}
h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}}.
\end{equation*}

\subsection{Proof of Lemma~\ref{lem:interpolator_bound}.}
We make use of the representation~\ref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
\begin{align*}
h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
\end{align*}

To upper bound $h(K_0)$, we invoke the crude bounds of Lemma~\ref{lem:crude_ppr_bound},
\begin{align*}
h(K_0) & \leq p(S_j) \leq p(\set{v}) + p(S_j \setminus \set{v}) \\
& \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \\
& \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
\end{align*}
where the last line follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.

\subsection{Proof of Theorem~\ref{thm:conductance_ppr}.}
Since $\alpha = 10\Phi(C)$ and $v \in C_{\alpha}$, by Theorem~\ref{thm:acl_3},
\begin{equation*}
p(\alpha,\chi_v)(C) \geq \frac{9}{10}.
\end{equation*}
This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p(\alpha,\chi_v)(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$. Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{thm:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$, and we have
\begin{equation*}
\Phi(p(\alpha,\chi_v)) \leq \sqrt{\frac{160\Phi(C)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
\end{equation*}
Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
\begin{equation*}
\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
\end{equation*}
completing the proof of the theorem.
\section{Technical results.}

The following Lemma relates $p(S)$ to itself. It is Lemma~5 in \textcolor{red}{Anderson,Chung,Lang}.
\begin{lemma}
	\label{lem:acl_1}
	For each $j \in [1,n-1]$,
	\begin{equation*}
	p[\vol(S_j)] \leq \alpha s(S_j) + \frac{1 - \alpha}{2} \left(p[\vol(S_j) + \abs{\partial(S_j)}] + p[\vol(S_j) - \abs{\partial{S_j}}]  \right)
	\end{equation*}
	where $\partial{S} = \set{u \in S: \exists v \in S^c, (u,v) \in E}$ is the boundary of $S$.
\end{lemma}

The following Lemma provides some Taylor expansions of the functions $\sqrt{1 + x}$ and $\sqrt{1 - x}$ about $x = 0$.
\begin{lemma}
	\label{lem:taylor_expansion}
	For any $x \in [0,1]$,
	\begin{equation*}
	\sqrt{1 + x} \leq 1 + \frac{x}{2} - \frac{x^2}{8} + \frac{x^3}{16}
	\end{equation*}
	and
	\begin{equation*}
	\sqrt{1 - x} \leq 1 - \frac{x}{2} - \frac{x^2}{8} - \frac{x^3}{16}.
	\end{equation*}
\end{lemma}

Next, we provide some very crude bounds on the maximum value the PPR vector $p(\alpha,\chi_v)$ can attain.
\begin{lemma}
	\label{lem:crude_ppr_bound}
	For every $u \in V$,
	\begin{equation*}
	p(\alpha,\chi_v) \leq \1(u = v)\frac{2\alpha}{1 + \alpha} + \frac{1}{2d_{\min}}.
	\end{equation*}
\end{lemma}
\begin{proof}
	For any $u \in V$ besides the seed node $v$, we can show by induction that
	\begin{equation*}
	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
	\end{equation*} 
	for any $t \geq 0$, and therefore
	\begin{align*}
	p(\alpha,\chi_v)(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \\
	& \leq  \frac{1}{2d_{\min}}.
	\end{align*}

	When $u = v$, we have that 
	\begin{equation*}
	\chi_v W^t(v) \leq \frac{1}{2^t} + \frac{1}{2d_{\min}}
	\end{equation*}
	and the result follows.
\end{proof}

\subsection{Concentration Inequalities.}

\paragraph{Bernstein's inequality.}

Let $S_m$ be a binomial random variable, $S_m \sim \textrm{Bin}(n,p)$, and let $\mu = np$.  Then, Bernstein's inequality gives
\begin{equation*}
P\left(\abs{S_m - \mu} \geq \delta \mu \right) \leq 2 \exp\set{- \frac{\frac{1}{2}\delta^2\mu}{1 + \frac{\delta}{3}}}
\end{equation*}
for any $\delta > 0$. Now suppose $S_{m1},\ldots,S_{mm}$ are each binomial random variables, with $S_{mj} \sim \textrm{Bin}(n,p_j)$. Taking a union bound over $j = 1,\ldots,m$, we have that
\begin{equation*}
P\left(\max_{j = 1,\ldots,m}\abs{S_m - \mu_j} \geq \delta \mu_j \right) \leq 2 n \exp\set{- \frac{\frac{1}{2}\delta^2\mu_{\min}}{1 + \frac{\delta}{3}}} 
\end{equation*}
where $\mu_{\min} = \min_{j = 1,\ldots,n} \mu_j$. Similarly letting $\mu_{\max} = \max_{j = 1,\ldots,n} \mu_j$, we have that with probability at least $1 - 2 n \exp\set{- \frac{\frac{1}{2}\delta^2\mu_{\min}}{1 + \frac{\delta}{3}}}$,
\begin{equation*}
(1 - \delta) \mu_{\min} \leq S_{mj} \leq (1 + \delta) \mu_{\max}, \quad \textrm{for all $j = 1,\ldots,m$.}
\end{equation*}

\paragraph{Hoeffding's Inequality for U-statistics.}
Let $U_m$ be a degree-2 U-statistic with kernel $h$, i.e.
\begin{equation*}
U_m = \sum_{i = 1}^{m} \sum_{j \neq i} h(X_i,X_j).
\end{equation*}
where $X_1,\ldots, X_m$ are i.i.d random variables. Let $\mu_h = \mathbb{E}(U_m) = n(n-1)\mathbb{E}(h(X_1),h(X_2)) =:n(n-1)p_h$, and assume $\norm{h}_{\infty} \leq 1$. Then, Hoeffding's inequality gives
\begin{equation*}
P(\abs{U_n - \mu} \geq \delta \mu) \leq 2 \exp\left(-\frac{\delta^2 \mu_h p_h}{4}\right).
\end{equation*}
Therefore, with probability at least $1 - 2 \exp\left(-\frac{\delta^2 \mu_h p_h}{4}\right)$,
\begin{equation*}
(1 - \delta) \mu_h \leq U_n \leq (1 + \delta) \mu_h.
\end{equation*}

\end{document}

### 2019-11-03 arxiv/local_spectral_density_clustering_arxiv.tex
alden arxiv draft complete

--- 2019-07-03 neurips/local_spectral_density_clustering_arxiv.tex
@@
 \newcommand{\Cest}{\widehat{C}}
-\newcommand{\degminpr}{\deg_{\min}'}
-\newcommand{\degminwt}{\widetilde{\deg}_{\min}}
-\newcommand{\degmaxwt}{\widetilde{\deg}_{\max}}
-\newcommand{\degmax}{\deg_{\max}}
+\newcommand{\degminpr}{d_{\min}'}
+\newcommand{\degminwt}{\widetilde{d}_{\min}}
+\newcommand{\degmaxwt}{\widetilde{d}_{\max}}
+\newcommand{\degmax}{d_{\max}}
 \newcommand{\piminwt}{\widetilde{\pi}_{\min}}
 \newcommand{\piminpr}{\pibf_{\min}'}
-\newcommand{\degmin}{\deg_{\min}}
+\newcommand{\degmin}{d_{\min}}
 
@@
 PPR, run on a neighborhood graph, extracts sufficiently salient density
-clusters. We also provide empirical support for our theory.
+clusters, and conversely fails to recover geometrically poorly conditioned density clusters. We also provide empirical support to illustrate our theoretical results.
 \end{abstract}
@@
 vertices $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i -
-x_j} \leq r$, where $\norm{\cdot}$ is the $\ell_2$ norm. We denote by $\Abf \in
+x_j} \leq r$, where $\norm{\cdot}$ is the Euclidean norm. We denote by $\Abf \in
 \Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if
 $(u,v) \in E$ and $0$ otherwise.  We also denote by $\Dbf$ the diagonal degree
-matrix, with $\Dbf_{uu} = \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n
+matrix, with entries $\Dbf_{uu} := \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n
 \times n$ identity matrix.
 
-Next, we define the PPR vector $\pbf = \pbf(v,\alpha;G_{n,r})$, based on
+Next, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on
 a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be 
@@
 $G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
-$v$-th position and 0 elsewhere). For a level $\beta > 0$ and a target volume
-$\vol_0 > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf = (p_u)_{u \in V}$
+$v$-th position and 0 elsewhere).
+
+\subsection{Sweep cut.}
+\label{subsection: sweep_cut}
+
+We employ the sweep cut method to obtain a local cluster from the PPR embedding $\pbf_v$. For a level $\beta > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$
 as   
@@
 \label{eqn: sweep_cuts}
-S_\beta := \set{u \in V: \frac{p_u}{\Dbf_{uu}} > \frac{\beta}{\vol_{0}}}.
+S_{\beta,v} := \set{u \in V: \frac{\pbf_v(u)}{\Dbf_{uu}} > \beta}.
 \end{equation}
@@
 Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(\frac{1}{40},\frac{1}{11})$}\footnote{The choice of a specific range such as  
-\smash{$(\frac{1}{40}, \frac{1}{11})$} is standard in the analysis of PPR
-algorithms, see, e.g., \citep{zhu2013}.}, we output the cluster estimate
+(L, U)$} (where the range $(L,U)$ is also a user-specified parameter), we output the cluster estimate
 \smash{$\Cest = S_{\beta^*}$} that has minimum normalized cut.
@@
 {\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary volume
-$\vol_0 > 0$. \\     
+parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, sweep cut range $(L,U)$. \\     
 {\bfseries Output:} cluster $\Cest \subseteq V$.
@@
   \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $p=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
+  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
     ppr_vector}. 
-  \STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
+  \STATE For \smash{$\beta \in (L,U)$} compute sweep cuts 
   $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
@@
   $$
-  \beta^* = \argmin_{\beta \in (\frac{1}{40}, \frac{1}{11})}~ \Phi(S_{\beta}; G_{n,r}).
+  \beta^* = \argmin_{\beta \in (L,U)}~ \Phi(S_{\beta}; G_{n,r}).
   $$
@@
 \lambda\}$.  For a given density cluster \smash{$\Cset \in \Cbb_f(\lambda)$}, we
-call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}. The
-size of the symmetric set difference between estimated and empirical clusters is 
+call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}. The size of the symmetric set difference between estimated and empirical cluster is 
 a commonly used metric to quantify cluster estimation error
-\citep{korostelev1993,polonik1995,rigollet2009}.
-
-\begin{definition}[Symmetric set difference]
-  \label{def: symmetric_set_diff}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-  $\mathcal{S} \subseteq \Reals^d$, we define   
-  \begin{equation}
-    \label{eqn: misclassification_rate}
-    \Delta(\Cest, \mathcal{S}) := \abs{\Cest \setminus \mathcal{S}[\Xbf] \cup
-      \mathcal{S}[\Xbf] \setminus \Cest},
-  \end{equation}
-  the cardinality of the symmetric set difference between 
-  \smash{$\Cest$} and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$. 
+\citep{korostelev1993,polonik1995,rigollet2009}. We will consider a related metric, the volume of the symmetric set difference, which weights points according to their degree in $G_{n,r}$. 
+\begin{definition}
+	\label{def:volume_symmetric_set_difference}
+	For an estimator $\widehat{C} \subseteq \Xbf$ and a set $\mathcal{S} \subseteq \Rd$, the symmetric set difference is 
+	\begin{equation*}
+	\widehat{C} \vartriangle \mathcal{S}[\Xbf] := \bigl(\widehat{C} \cap \setminus \mathcal{S}[\Xbf]\bigr) \cup \bigl(\Xbf\setminus\widehat{C} \cap \mathcal{S}[\Xbf]\bigr).
+	\end{equation*}
+	We will measure the discrepancy of $\widehat{C}$ to the set $\mathcal{S}[\Xbf]$ by the volume of the symmetric set difference,
+	\begin{equation*}
+	\Delta(\widehat{C}, \mathcal{S}[\Xbf]) := \vol(\widehat{C} \vartriangle \mathcal{S}[\Xbf]; G_{n,r})
+	\end{equation*}
 \end{definition}
-
 However, the symmetric set difference does not measure whether \smash{$\Cest$} 
@@
 \end{definition}
-\noindent Consistent cluster recovery roughly ensures that, for a given $\lambda$, the estimated cluster $\Cest$ contains all
+\noindent Consistent cluster recovery roughly ensures that, for a given density threshold $\lambda$, the estimated cluster $\Cest$ contains all
 points in a true
-density cluster $\Cset$, and simultaneously does not contain any points in any other density cluster $\Cset'$.
+density cluster $\Cset \in \Cbb_f(\lambda)$, and simultaneously does not contain any points in any other density cluster $\Cset' \in \Cbb_f(\lambda)$.
 
@@
 clustering given previously, a few related lines of work are worth
-highlighting. \citet{shi2009} and \citet{schiebinger2015} examine the consistency of  
-spectral algorithms in recovering the latent labels in certain
-nonparametric mixture models. Their results focus on global rather than local 
+highlighting.
+In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+The ability of spectral algorithms to perform clustering -- community detection-- in this context is well-understood.
+In particular, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM,  \citet{lei2015} extend these results to the sparse (low average degree) regime, and \citet{balakrishnan2011} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+The framework we consider, where nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
+
+The study of spectral algorithms on neighborhood graphs has focused on establishing consistency results-- that is, asymptotic convergence of eigenvalues and eigenvectors of matrices to eigenvalues and eigenfunctions of limiting operators.
+\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
+\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood of fixed radius.
+\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime where the radius $r \to 0$ as $n \to \infty$.
+
+These results are of fundamental importance; however, the behavior of the spectra of these continuum operators can in general be hard to grasp.
+Therefore, further work relating this spectra to the geometry of the distribution $\Pbb$ is of interest.
+In this spirit, \citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of
+spectral algorithms to recover the latent labels in certain geometrically well-conditioned nonparametric mixture models. Their results focus on global rather than local 
 methods, and thus impose global rather than local conditions on the nature
@@
 
-More broadly, density clustering and level set estimation is a well-studied
-problem. \citet{polonik1995, rigollet2009} study density clustering under the 
+A substantial portion of our technical effort involves estimating graph-theoretic connectivity properties of empirical density clusters in the neighborhood graph $G_{n,r}$.
+In particular, we prove an upper bound on the mixing time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall within a density cluster $\Cset$.
+To do so, we rely on a series of seminal works upper bounding the mixing time of \emph{geometric random walks} (see \citet{vempala2005} for a comprehensive review.)  This study was initiated by \citet{dyer1991}, who used geometric random walks as a fundamental subroutine to efficiently compute volumes of high-dimensional convex bodies.
+These results are improved in \citet{lovasz1990,kannan97,kannan06}, who show \textit{inter alia} that the bounds on mixing time can be sharpened by avoiding so-called ``start-penalties''.(These improvements are crucial to our work, for they allow us to avoid factors of $\log n$ which would imply divergence as $n \to \infty$.) Following the lead of \citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold for Lipschitz deformations of convex sets.
+Additionally, we relate the mixing time of these (continuous-space) geometric random walks to the mixing time of random walks over (discrete) neighborhood graphs.
+
+Finally, it is worth mentioning that density clustering and level set estimation are well-studied problems. \citet{polonik1995, rigollet2009} study density clustering under the 
 symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
@@
 
-A summary of our results (and an outline for this
+Specifically, a summary of our results (and an outline for this
 paper) is as follows.
@@
 
+\item In Section \ref{sec:lower_bound}, we provide an accompanying lower bound, demonstrating that when the cluster $\Cset$ is sufficiently poorly conditioned, it will not be recovered by Algorithm~\ref{alg: ppr}.
+
 \item In Section \ref{sec: experiments}, we empirically investigate the
@@
 \noindent At this point we summarize one of our main takeaways: 
-PPR, run on a neighborhood graph, recovers \emph{geometrically
+PPR, run on a neighborhood graph, recovers only \emph{geometrically
 compact} high-density clusters. Our main theoretical results, make this takeaway 
 precise, and provide concrete ways of quantifying the geometric
-compactness of a density cluster. To complement this, we also provide experimental
-evidence that the PPR algorithm can fail to recover high-density clusters which are not
-geometrically compact.
+compactness of a density cluster.
 
@@
 With this condition in place 
-our first main result (Theorem~\ref{thm: misclassification_rate}) provides a bound
+our first main result (Theorem~\ref{thm:volume_ssd}) provides a bound
 on the symmetric set difference between the estimated cluster $\Cest$,
@@
 \item 
-  \label{asmp: cluster_separation}
-  \emph{Cluster separation:}
-  For all clusters $\Cset' \in \Cbb_f(\lambda)$ with $\Cset' \not= \Cset$, 
-  $\dist(\Csig,\Csig') > \sigma$, where $\dist(\Csig,\Csig') := \inf_{x
-    \in \Csig} \dist(x,\Csig')$.
-
-\item 
   \label{asmp: low_noise_density}
-  \emph{Low noise density:} There exist $\gamma,c_0 > 0$ such that for 
-  $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
+  \emph{Low noise density:} There exists $c_0 > 0$ and $\gamma \in [0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
   \begin{align*}
@@
   \emph{Bounded volume:}
+  For a set $\mathcal{S} \subseteq \Reals^d$, define the $\Pbb$-weighted volume of $\mathcal{S}$ to be
+  \begin{equation}
+  \label{eqn:volume}
+  \vol_{\Pbb,r}(\mathcal{S}) := \int_{\mathcal{S}} \Pbb(B(x,r)) \,d\Pbb(x).
+  \end{equation}
+  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$.
+
   We assume that neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
   \begin{equation*}
-    2 \int_{\Csig} \Pbb(B(x,r)) f(x) dx \leq \int_{\Rd} \Pbb(B(x,r)) f(x) dx,
-  \end{equation*}
-  where $B(x,r)$ is the closed ball of radius $r$ at $x$.
+  \vol_{\Pbb,r}(\mathcal{S}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d).
+  \end{equation*}
+
 \end{enumerate}
+
 To motivate these conditions, we provide a brief high-level sketch
@@
 \label{eqn: graph_symmetric_set_difference_1}
-\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
-\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
+\vol(\Cest \vartriangle S; G) \leq c \bigl( \Phi(S,G)
+\cdot \tau_{\infty}(G[S])\bigr),
 \end{equation}
@@
 precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
-\eqref{eqn:  graph_symmetric_set_difference_1} resembles a (degree-weighted) 
-form of the symmetric set difference metric in \eqref{eqn:
-  misclassification_rate}, and our main goal will be to upper bound 
-  this quantity. 
+\eqref{eqn: graph_symmetric_set_difference_1} is precisely
+the volume of the symmetric set difference, and our main goal is therefore to upper bound the graph functionals $\Phi$ and $\tau_{\infty}$.
   Towards this goal, as we will show in Section \ref{sec:
@@
 \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. In more detail, assumptions  
-\ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. In more detail, assumption 
+\ref{asmp: low_noise_density} yields an upper
 bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
@@
 \ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
-the other hand, \ref{asmp: bounded_density}, \ref{asmp: embedding} preclude
+the other hand, \ref{asmp: bounded_density} and \ref{asmp: embedding} preclude
 bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
@@
   we see that the smaller $\kappa(\Cset)$ is, the
-more success PPR will have in recovering the target cluster $\Cset$. We let $\theta := (r, \sigma,
-\lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, \diam, L)$ contain the
-geometric parameters from Assumptions~\ref{asmp:  bounded_density}--\ref{asmp:
-  bounded_volume}.
+more success PPR will have in recovering the target cluster $\Cset$.
 
 \begin{definition}[Well-conditioned density clusters]
+  \label{def:well_conditioned_density_cluster}
   For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy 
-  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some
-  $\theta$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified
+  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma > 0$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified
   later, we set 
@@
     \label{eqn: condition_number_1}
-    \Phibf(\theta) 
+    \Phibf(\Cset) 
     := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
@@
         1})}{\lambda_{\sigma}},~  
-    \taubf(\theta) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
-      L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3,
-  \end{equation}
-  and letting \smash{$\kappa(\Cset) := \Phi_{u}(\theta) \cdot
-    \tau_{u}(\theta)$}, we call $\Cset$ a 
+    \taubf(\Cset) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
+      L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c_3,
+  \end{equation}
+  and letting \smash{$\kappa(\Cset) := \Phi_{u}(\Cset) \cdot
+    \tau_{u}(\Cset)$}, we call $\Cset$ a 
   \emph{$\kappa$-well-conditioned density cluster}.  
@@
 geometric parameters. 
-We note in passing that $\Phibf(\theta)$ and $\taubf(\theta)$ are exactly the upper bounds 
+We note in passing that $\Phibf(\Cset)$ and $\taubf(\Cset)$ are exactly the upper bounds 
 on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
@@
 ranges of each of the user-specified parameters. In particular, for a
-well-conditioned density cluster $\Cset$ (with respect to some $\theta$), we
-require that the tuning parameters of Algorithm~\ref{alg: ppr} are chosen as
+well-conditioned density cluster $\Cset$, we require that some of the tuning parameters of Algorithm~\ref{alg: ppr} are chosen to fall within specific ranges,
 \begin{equation}
@@
 0 < r \leq \frac{\sigma}{2d}, \quad 
-\alpha \in [1/10, 1/9] \cdot \frac{1}{\taubf(\theta)}, \\
-v \in \Csig[\Xbf]^g, \quad
-\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, 
+\alpha \in [1/10, 1/9) \cdot \frac{1}{\taubf(\theta)}, \\
+(L,U) \subseteq (1/50,1/5) \cdot \frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}.
 \end{gathered}
 \end{equation}
-where \smash{$\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$} will be some large
-(``good'') subset of $\Csig[\Xbf]$. In particular, abbreviating $\vol_{n,r}(S)
-:= \vol(S; G_{n,r})$ for $S \subseteq \Xbf$, this good subset has large volume, i.e. 
-$\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$.
 
@@
 hyperparameters and selects the cluster which has the smallest normalized cut.
-%it is not obvious how this scheme would affect the performance of PPR in the
-%density clustering context.
 
 \subsection{Cluster Recovery in Symmetric Set Difference}
-The results of Section \ref{sec: analysis}, combined 
-with \eqref{eqn: graph_symmetric_set_difference_1}, give an upper bound on the
-volume of \smash{$\Cest \setminus \Csig[\Xbf]$} and \smash{$\Csig[\Xbf]
-  \setminus \Cest$},  
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference}
-\vol_{n,r}(\Cest \setminus \Csig[\Xbf]) + \vol_{n,r}(\Csig[\Xbf] \setminus
-\Cest) \leq c \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]). 
-\end{equation}
-To translate the guarantee in~\eqref{eqn: graph_symmetric_set_difference} into meaningful bounds
-on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf], \Cest)$}, we
-want to preclude vertices $x \in \Xbf$ from having arbitrarily small degree, and
-so we make some regularity assumptions on $\mathcal{X} := \mathrm{supp}(f)$. Let
-$\nu$ denote the Lebesgue measure on $\Rd$, and $\nu_d := \nu(B)$ be the measure
-of the unit ball $B = B(0,1)$. 
-\begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{5}
-\item 
-  \label{asmp: valid_region}
-  \emph{Regular support:} There exists some constant $\lambda_{\min} > 0$ such 
-  that $\lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$. Additionally, there
-  exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$,
-  $\nu(B(x,r) \cap \mathcal{X}) \geq c \nu_d r^d$. 
-\end{enumerate}
-We note that the latter condition in \ref{asmp: valid_region} will hold if the
-boundary $\partial \mathcal{X}$ is sufficiently regular.  Now we present our
-first main result: a bound on the symmetric set difference metric.
+We now present our first main result: a bound on the volume of the symmetric set difference between the estimated cluster $\widehat{C}$ and empirical cluster $\Csig[\Xbf]$. 
 \begin{theorem}
-  \label{thm: misclassification_rate}
-  Fix $\lambda > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
-  additionally assume that $f$ satisfies \ref{asmp: valid_region}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >
-  0$ such that with probability tending to 1 as $n \to \infty$,  
-  \begin{equation}
-    \label{eqn: misclassification_rate_ub}
-    \Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
-    \frac{\Lambda_{\sigma}}{\lambda_{\min}}. 
-  \end{equation}
+  \label{thm:volume_ssd}
+  Fix $\lambda > 0$ and let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
+  $\kappa$-well-conditioned density cluster for some $\sigma > 0$.
+If Algorithm \ref{alg: ppr} is \emph{well-initialized} with respect to $\Cset$, then there exists a universal constant $c > 0$, constants in sample size $c_1(\Pbb,r)$ - $c_6(\Pbb,r)$, and a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that the following statement holds: let Algorithm~\ref{alg: ppr} be run with any seed node $v \in \Csig[\Xbf]^g$.
+Then, for any $n$ large enough so that
+  \begin{equation*}
+  n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\},
+  \end{equation*}
+  the volume of the symmetric set difference is upper bounded
+  \begin{equation}
+    \label{eqn:volume_ssd}
+    \Delta(\Csig[\Xbf], \Cest) \leq c \cdot \kappa(\Cset) \cdot \vol_{n,r}(\Csig[\Xbf]),
+  \end{equation}
+  with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$. 
 \end{theorem}
-The proof of Theorem \ref{thm: misclassification_rate} is deferred to Appendix~\ref{sec: proof_of_misclassification_rate}.
-This result shows that the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
+The proof of Theorem \ref{thm:volume_ssd} is deferred to Appendix~\ref{sec:proof_of_volume_ssd}.
+In this theorem, and hereafter, we let $c, c_i > 0$ represent universal constants, and $c_i(\Pbb,r)$ represent constants which depend only on $\Pbb$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
+This result shows that the volume of the symmetric set difference \smash{$\Delta(\Csig[\Xbf],
   \Cest)$} is upper-bounded by a quantity proportional to the difficulty of the clustering problem, as
@@
 \subsection{Consistent Cluster Recovery}
-Neither \eqref{eqn: graph_symmetric_set_difference} nor \eqref{eqn:
-  misclassification_rate_ub} imply consistent density cluster estimation in the 
-sense of \eqref{eqn: consistent_density_cluster_recovery}. This notion of
-consistency requires a uniform bound over $\pbf$: for all \smash{$\Cset'
+The bound on symmetric set difference \eqref{eqn:volume_ssd} does not imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
+This notion of consistency requires a uniform bound over $\pbf$: as an example, for all \smash{$\Cset'
   \in \Cbb_f(\lambda), \Cset' \neq \Cset$}, and each $u \in \Cset, w \in
@@
 \label{eqn: ppr_gap}
-\frac{p_{w}}{\Dbf_{ww}} \leq \frac{1}{40\vol_0} < \frac{1}{11\vol_0} \leq
-\frac{p_u}{\Dbf_{uu}}, 
-\end{equation}
-so that any sweep cut $S_{\beta}$ for $\beta \vol_0 \in [1/40,1/11]$ (i.e., any
-sweep cut considered by Algorithm \ref{alg: ppr}) will fulfill both conditions
+\frac{\pbf_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} < \frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \frac{\pbf_v(u)}{D_{uu}}.
+\end{equation}
+Then, any $(L,U)$ satisfying~\eqref{eqn: initialization} and any sweep cut $S_{\beta}$ for $\beta \in (L,U)$ will fulfill both conditions
 laid out in \eqref{eqn: consistent_density_cluster_recovery}. In Theorem
 \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently
-small upper bound on $\kappa(\Cset)$ ensures that such a gap exists with probability
-1 as $n \to \infty$, and hence guarantees \smash{$\Cest$} will be a consistent  
-estimator. As was the case before, we wish to preclude arbitrarily low degree
-vertices, this time for points $x \in \Cset'[\Xbf]$. 
+small upper bound on $\kappa(\Cset)$ ensures that with high probability the uniform bound~\eqref{eqn: ppr_gap} is satisfied, and hence implies \smash{$\Cest$} will be a consistent  
+estimator. We will need one additional regularity condition, to preclude arbitrarily low degree
+vertices for points $x \in \Cset'[\Xbf]$. 
 \begin{enumerate}[label=(A\arabic*)]
@@
   Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
-  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
+  $\kappa$-well-conditioned density cluster for some $\sigma > 0$, and
   additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
-  such that if  
+  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$ and constants in sample size $c_1(\Pbb,r)$-$c_6(\Pbb,r)$ such that if  
   \begin{equation}
     \label{eqn: kappa_ub}
-    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
-      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
-  \end{equation}
-  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
-  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
+    \kappa(\Cset) \leq c \frac{(\lambda_{\sigma} r^d
+      \nu_d)^2}{\vol_{\Pbb,r}(\Csig)}, 
+  \end{equation}
+  then $\Cest$ satisfies~\eqref{eqn: consistent_density_cluster_recovery} with respect to $\Cset$ with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$.
+Therefore, $\Cest$ is a consistent estimator of $\Cset$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 \end{theorem}
@@
   behavior of PPR in this regime. Although the restriction to a kernel
-  function fixed in $n$ is standard for spectral clustering theory
+  function fixed in $n$ is common in spectral clustering theory
   \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
@@
 For a sufficiently small choice of $\varepsilon$, the 
-application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
-  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
+application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters}
 leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
@@
 
-The primary technical contribution of our work is showing that the geometric
+One of the primary technical contributions of our work is showing that the geometric
 conditions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} translate to 
@@
   Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
-  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
-  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
-  $\epsilon > 0$, if 
-  \begin{equation}
-    \label{eqn: conductance_sample_complexity}
-    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
-      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
-  \end{equation}
-  then with probability at least $1-\delta$, for a universal constant $c_1 > 0$,
+  \ref{asmp: bounded_volume} for some $\sigma > 0$. Then there exists a universal constant $c_1 > 0$ and a constant in sample size $c_1(\Pbb,r)$ such that
   \begin{equation}
@@
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
-  \end{equation}
+      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
+  \end{equation}
+  with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$. 
 \end{theorem}
@@
 originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
-for the stationary distribution of this random walk.  (As
+for the stationary distribution of this random walk.(As
 $\Wbf_S$ is the transition matrix of a lazy random walk, 
 it is well-known that a unique stationary distribution exists and is given by 
-\smash{$\pi(u) = (\Dbf_S)_{uu}/\vol(S; G[S])$}, where we write $\Dbf_S$ for the  
-degree matrix of $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
+\smash{$\pi(u) = \deg(u;G[S])/\vol(S; G[S])$}, where we write $\deg(u;G[S]) = \sum_{w \in S} \1((u,w) \in E_S)$ for the degree of $u$ in $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
 \begin{equation}
@@
   satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
-  for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$. Then, for
-  any \smash{$0 < r < \sigma/2\sqrt{d}$}, with probability 1,
+  for some $\sigma > 0$.
+Additionally assume that the radius $0 < r < \sigma/2\sqrt{d}$.
+Then there exist universal constants $c_2$ and $c_3$, and constants in sample size $c_2(\Pbb,r)$ - $c_6(\Pbb,r)$ such that the following statement holds: for any
+  \begin{equation*}
+  n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\}
+  \end{equation*}
+  the mixing time $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ satisfies
   \begin{equation} 
     \label{eqn: mixing_time_upper_bound}
-    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2
-    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{1}{r}\right) + c_3,
-  \end{equation}
-  for $c_2,c_3 > 0$ universal constants. 
+    \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{ \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
+  \end{equation}
+  with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$.
 \end{theorem}
@@
 continuous-space ``ball walk'' over convex sets. To the best of our knowledge, our
-result is the first bound, albeit asymptotic, on the mixing time of random walks
+result is the first bound on the mixing time of random walks
 over neighborhood graphs that is independent of $n$, the number of vertices.
@@
   for reasonably small values of $L$.
+
+\section{Lower bound.}
+\label{sec:lower_bound}
+
+To show a lower bound for density clustering using PPR, we exhibit a hard case: that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
+Let $\mathcal{C}_{\sigma}^{(0)}$, $\mathcal{C}_{\sigma}^{(1)}$, and $\mathcal{C}_{\sigma}^{(2)}$ be rectangles in $\Reals^2$,
+\begin{equation*}
+\mathcal{C}_{\sigma}^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times \biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad \mathcal{C}_{\sigma}^{(1)} = \mathcal{C}_{\sigma}^{(0)} - \set{(\sigma,0)}, \quad \mathcal{C}_{\sigma}^{(2)} = \mathcal{C}_{\sigma}^{(0)} + \set{(\sigma,0)} \tag{$0 < \sigma < \rho$}
+\end{equation*}
+and let $\mathbb{P}$ be the mixture distribution over $\mathcal{X} = \mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)} \cup \mathcal{C}_{\sigma}^{(2)}$ given by
+\begin{equation*}
+\mathbb{P} = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 + \frac{\epsilon}{2} \Psi_0,
+\end{equation*}
+where $\Psi_m$ is the uniform distribution over $\Csig^{(m)}$ for $m = 0,1,2$. 
+The density function $f$ of $\Pbb$ is simply
+\begin{equation}
+\label{eqn:lb_density}
+f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(2)}) + \frac{\epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(0)})  \right)
+\end{equation}
+so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_{\sigma}^{(1)}, \mathcal{C}_{\sigma}^{(2)}}$.
+
+\subsection{Lower bound for PPR.}
+
+As the following theorem demonstrates, even when Algorithm~\ref{alg: ppr} is reasonably initialized, if the density cluster $\mathcal{C}_{\sigma}^{(1)}$ is sufficiently geometrically ill-conditioned the cluster estimator $\widehat{C}$ will fail to recover $\mathcal{C}_{\sigma}^{(1)}$.
+Let
+\begin{equation}
+\label{eqn:lower_set}
+\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
+\end{equation}
+\begin{theorem}
+	\label{thm:ppr_lb}
+	Suppose $r < \frac{1}{40}\rho \wedge \frac{1}{4}\sigma$,  $\alpha = 65 \Phi_{\Pbb}(\mathcal{L})$, and $(L,U) = (0,1)$ are inputs to Algorithm~\ref{alg: ppr}. Then, for any
+	\begin{equation}
+	\label{eqn:lb_sample_size}
+	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2}, \frac{8}{\epsilon}}
+	\end{equation}
+	the following statement holds: there exists a set $C^{g} \subset \Xbf$ with $\vol(C^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$ such that for any seed node $v \in C^g$, the estimator $\widehat{C}$ computed by Algorithm~\ref{alg: ppr} has symmetric set difference with $\Csig^{(1)}[\Xbf]$ of volume at least
+	\begin{equation}
+	\label{eqn:ppr_lb}
+	\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2} \geq \frac{1}{4} -  c \frac{\sqrt{\frac{\sigma}{\rho}}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
+	\end{equation}
+	with probability at least $1 - c_1(\Pbb,r) n \exp\set{-c_2(\Pbb,r)n}$, where $c$ is a universal constant and $c_1(\Pbb,r),c_2(\Pbb,r)$ are constants which do not depend on $n$.
+	Consequently, if
+	\begin{equation*} 
+	\epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
+	\end{equation*}
+	then with high probability $\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2}$ is at least $1/8$. 
+\end{theorem}
+
+Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
+
+Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.
+Although we picked this setting to make the theorem statement simple, our results are easily generalized to $\Reals^d$ and to non-rectangular clusters.
+Additionally, although we state our lower bound with respect to PPR run on neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\frac{\sigma}{\rho}$, the normalized cut of $\Cset_1$ will be much larger than that of $\mathcal{L}$.
+In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Cset_1$.
+In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus it stands to reason that all the aforementioned approaches should struggle to estimate $\Csig^{(1)}[\Xbf]$.
+
+\subsection{Comparison with upper bound.}
+
+To better digest the implications of Theorem~\ref{thm:ppr_lb}, we apply our upper bound to the density function $f$ given in \eqref{eqn:lb_density}.
+Observe that $\Csig^{(1)}$ satisfies each of the assumptions~\ref{asmp: bounded_density}-\ref{asmp: bounded_volume}.
+In particular
+\begin{enumerate}[label=(A\arabic*)]
+	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in \Csig^{(1)}$.
+	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such that $0 < \dist(x,\Csig^{(1)}) \leq \sigma$. Therefore for all such $x$,
+	\begin{equation*}
+	\inf_{x' \in \Csig^{(1)}} f(x') - f(x)  > \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma}.
+	\end{equation*}
+	\item The set $\Csig^{(1)}$ is itself convex, and has diameter $\rho$.
+	\item By symmetry, $\vol_{\Pbb,r}(\Csig^{(1)}) = \vol_{\Pbb,r}(\Csig^{(2)})$ and therefore $\vol_{\Pbb,r}(\Csig^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$. 
+\end{enumerate}
+
+%Technically, this density does not fit nicely into the setup of Theorem~\textcolor{red}{1}, because the sets $\Cset_{\sigma}^{(m)}$ ($ m = 1,2$) play the role of both the $\sigma$-expanded sets and the density clusters themselves.
+However, this truly is only a technical objection.
+One could modify the distribution $\Pbb$ by adding a small amount of mass to the $\sigma$-interior $\Cset^{(m)} = \set{x \in \Cset_{\sigma}^{(m)}: \dist(x,\partial\Cset_{\sigma}) \geq \sigma}$.
+Appropriately choosing a threshold $\lambda > \frac{(1 - \epsilon)}{2\rho\sigma}$, the resulting $\lambda$-density clusters would be $\Cbb_f(\lambda) = \set{\Cset^{(1)},\Cset^{(2)}}$, and their $\sigma$-expansions would resemble the rectangles $\Csig^{(1)}, \Csig^{(2)}$ except with slightly rounded corners.
+%Alternatively, one could directly modify Lemma~\textcolor{red}{6} -- an auxiliary Lemma, used in the proof of Theorem~\textcolor{red}{3}, which establishes an upper bound on the Lebesgue measure of $\Csig + B(0,r)$ -- to hold under the assumption $\Csig$ is a rectangle of width $\sigma$ rather than a $\sigma$-expansion.
+The proof of this Lemma is the only time we use the fact that $\Csig$ is a $\sigma$-expansion of a density cluster.
+\textcolor{red}{(Ryan and Siva.)}
+
+\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners.
+To fix this, one can either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume} in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with respect to rectangles of width $\sigma$, or change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
+As these details do not meaningfully change our conclusions, for simplicity we will keep our upper and lower bounds as is.
+\end{remark}
+
+If the user-specified parameters are initialized according to~\eqref{eqn: initialization}, we may apply Theorem~\ref{thm:volume_ssd}.
+This implies that there exists a set $\Csig^{(1)}[\Xbf] \subset \Csig^{(1)}$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any seed node $v \in \Csig^{(1)}[\Xbf]$, the estimated cluster $\widehat{C}$ output by Algorithm 1 satisfies the following upper bound:
+\begin{equation*}
+\vol_{n,r}(\widehat{C} \vartriangle \Csig^{(1)}[\Xbf]) \leq c \cdot \kappa(\Cset^{(1)}) \cdot \vol_{n,r}(\Csig^{(1)}[\Xbf])
+\end{equation*}
+where the condition number is given by
+\begin{equation*}
+\kappa(\Cset^{(1)}) = c \frac{\epsilon}{\sigma}\left(\frac{\rho^2}{r}\log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c\right).
+\end{equation*}
+
+To facilitate comparisons between our upper and lower bounds, assume $\frac{1}{4}\sigma \leq \frac{1}{40}\rho$ and set $r = \frac{1}{4}\sigma$. 
+For some universal constant $c > 0$, the following statements each hold with high probability:
+\begin{itemize}
+	\item If the user-specified parameters satisfy~\eqref{eqn: initialization}, and additionally for some $b > 0$
+	\begin{equation*}
+	\epsilon < c\frac{b\sigma^2}{\rho^2 \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2\sigma}\right)}
+	\end{equation*}
+	then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+	\item If the user-specified parameters are given as in Theorem~\ref{thm:ppr_lb}, and 
+	\begin{equation*}
+	\epsilon > c\left({\frac{\sigma}{\rho}} \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\right)^{1/4}
+	\end{equation*}
+	then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+\end{itemize}
+
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-geometrically conditioned for recovery using PPR.
+
+\begin{remark}
+	It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
+\end{remark}
+
+%It is worth pointing out that both our lower and upper bounds are stated with respect to specific choices of the input parameters to Algorithm~\ref{alg: ppr}, and that these choices are in fact different in the case of the teleportation parameter $\alpha$ and sweep cut range $(L,U)$.
+At a high level, we do not believe this substantially weakens the takeaway messages of our work: if a density cluster $\mathcal{C}$ is geometrically well-conditioned, then a reasonable initialization of PPR will recover $\Csig[\Xbf]$ with low error, whereas if it is geometrically poorly-conditioned, then a different but also reasonable initialization of PPR will fail to recover $\Csig[\Xbf]$.
+Of course, it would be more satisfying if both our upper and lower bounds could be stated with respect to the same choices of these input parameters.
+Unfortunately, it is not at all obvious how to prove such a claim, as to the best of our knowledge all existing work on PPR assumes similar initialization conditions to the ones we assume; effectively, that the algorithm is well-initialized with respect to the set $S \subset G$ one is interested in recovering.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
+Even so, we reiterate our belief that in tandem our upper and lower bounds represent a substantial step forward in characterizing the behavior of local clustering algorithms in a statistical context \textcolor{red}{(Ryan and Siva)}.
+
+\begin{remark}
+	We also note that our lower bound is of course specific to the PPR algorithm.
+As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
+That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
+Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
+\end{remark}
 
@@
 \paragraph{Empirical behavior of PPR.} In Figure \ref{fig:fig2}, to drive home
-the main implications of Theorems \ref{thm: misclassification_rate} and
+the main implications of Theorems \ref{thm:volume_ssd} and
 \ref{thm: consistent_recovery_of_density_clusters}, we show the
@@
 appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We do not, however, provide theory to show that (some variant of) 
-our geometric
-conditions are \emph{required} for successful recovery of a density level set. This
-seems to be supported by our empirical results, and establishing this necessity
-formally is an important direction for 
-future work.
+cluster by PPR.
+We have also exhibited a hard case, showing that when a density cluster is sufficiently geometrically ill-conditioned, PPR may fail to recover it.
+Finally, we have empirically demonstrated the tightness of our analysis for reasonable sample sizes.
 
@@
 
-For notational ease, we write
-\begin{align*}
-\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
-\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
-\end{align*}
-for the random variable, mean, and probability of cut size and volume, respectively.
-
-With this notation in place, the goal of Theorem~\ref{thm: conductance_upper_bound} is roughly to show that, with probability at least $1 - \delta$, for a universal constant $c_1 > 0$ and for any $\epsilon > 0$, for a sufficiently large sample size $n$:
-\begin{align*}
-\Phi_{n,r}(\Csig[\Xbf]) := \frac{\cut_{n,r}}{\min\{\vol_{n,r}, \vol_{n,r}^c\}} \leq c_1 \frac{d}{\sigma}
+For notational ease, we let $\mathcal{S} \subseteq \Rd$ and write
+\begin{align*}
+\cut_{n,r}(\Csig[\Xbf]) = \cut(\Csig[\Xbf]; G_{n,r}),& ~ \cut_{\Pbb,r}(\Csig)= \frac{\mathbb{E}[\cut_{n,r}(\Csig[\Xbf])]}{2{n \choose 2}} \\
+\vol_{n,r}(\Csig[\Xbf]) = \vol(\Csig[\Xbf]; G_{n,r}),& ~ \vol_{\Pbb,r}(\Csig)= \frac{\mathbb{E}[\vol_{n,r}(\Csig[\Xbf])]}{2{n \choose 2}}
+\end{align*}
+for the random variable and mean of cut size and volume, respectively. (Note that this definition of $\vol_{\Pbb,r}(\Sset)$ agrees with that of~\eqref{eqn:volume}).
+
+With this notation in place, the goal of Theorem~\ref{thm: conductance_upper_bound} is to show that for a universal constant $c_1 > 0$,
+\begin{align*}
+\Phi_{n,r}(\Csig[\Xbf]) := \frac{\cut_{n,r}(\Csig[\Xbf])}{\min\{\vol_{n,r}(\Csig[\Xbf]), \vol_{n,r}((\Rd \setminus \Csig)[\Xbf])\}} \leq c_1 \frac{d}{\sigma}
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon.
-\end{align*}
+      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
+\end{align*}
+with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$.
 
 The proof of this theorem follows essentially from two technical Lemmas. 
-The following Lemma relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values.
-\begin{lemma}
-	\label{lem: prob_bound_cutvol}
-	For any $\delta \in (0,1]$,
-	\begin{equation}
-	\label{eqn: numerator_additive_bound}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}}, \\ 
-	\frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, \\
-	\frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}},
-	\end{equation}
-	each with probability at least $1 - \delta$. 
-\end{lemma}
-We note that as a consequence of~\ref{asmp: bounded_volume} we have that $p_V^c \geq p_V$, so it will suffice to lower bound $p_V$ (since a lower bound for $p_V^c$ follows).
-The 
-following result provides upper and lower bounds on the expected values $p_K$ and $p_V$ respectively:
+Lemma~\ref{lem:ball_bounds_in_probability} relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values.
+We restate the conclusions of this Lemma: for any $\delta > 0$,
+\begin{align}
+\frac{\cut_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq (1 + \delta)\cut_{\Pbb,r}(\Csig) &, \quad \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \geq (1 - \delta)\vol_{\Pbb,r}(\Csig) \nonumber \\ \frac{\vol_{n,r}((\Rd \setminus \Csig)[\Xbf])}{2{n \choose 2}}& \geq (1 - \delta)\vol_{\Pbb,r}(\Rd \setminus \Csig) \label{eqn: conductance_upper_bound_pf1}
+\end{align}
+with probability at least 
+\begin{align*}
+1 - & \exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Rd\setminus \Csig))^2} \\
+& \geq 1 - 3\exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2}.
+\end{align*} 
+We note that as a consequence of~\ref{asmp: bounded_volume} we have that $\vol_{\Pbb,r}(\Rd \setminus \Csig)  \geq \vol_{\Pbb,r}(\Csig)$, so it will suffice to lower bound $\vol_{\Pbb,r}(\Csig)$ (since a lower bound for $\vol_{\Pbb,r}(\Rd \setminus \Csig)$ follows).
+The following result provides upper and lower bounds on the expected values $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$ respectively:
 \begin{lemma}
@@
 	\begin{align}
-	p_K &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
-	p_V &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
+	\cut_{\Pbb,r}(\Csig) &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
+	\vol_{\Pbb,r}(\Csig) &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
 	\end{align}
 \end{lemma}
-%\begin{lemma}
-%	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
-%	\begin{equation*}
-%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).
-%	\end{equation*}
-%\end{lemma}
-
-Taking these two technical lemmas as given we can now complete the proof of the theorem. 
-We fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-\begin{equation}
-\label{eqn: conductance_representation_1}
-\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
-\end{equation}
-By a union bound we see that all three bounds in \eqref{eqn: numerator_additive_bound} hold with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this yields the upper bound \sbcomment{Changed $\mathbf{X}$ to $X$}
-\begin{equation*}
-\Phi_{n,r}(\Csig[X]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
-\end{equation*}
-for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-Now, some straightforward algebraic manipulations yield,
-\begin{align*}
-\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
-& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
-\end{align*}
-
-%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
-All that remains is some algebra, which we take care of below.
-
-\noindent Using Lemma \ref{lem: expected_density_cut}, we have
-\begin{equation*}
-\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-\end{equation*}
-Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-\begin{equation*}
-n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
-\end{equation*}
-which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$, and this yields the desired bound on $\Phi_{n,r}(\Csig[X])$. In order to complete the proof of
-the theorem it remains to prove Lemmas~\ref{lem: prob_bound_cutvol} and~\ref{lem: expected_density_cut}.
-
-\subsection{Proof of Lemma~\ref{lem: prob_bound_cutvol}}
-We first note that we can write $\cut_{n,r}$ as a double sum,
-	\begin{equation}
-	\label{eqn: density_cut_expansion}
-	\cut_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \not\in \Csig) \1(x_j \in \Csig) \1(\norm{x_i - x_j} \leq r),
-	\end{equation}
-	and similarly we can write $\vol_{n,r}$ as a sum of indicator functions,
-	\begin{equation}
-	\label{eqn: volume_expansion}
-	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r)).
-	\end{equation}
-From this we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-	\end{equation*}
-	with kernels
-	\begin{align*}
-	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{align*}
-	Similarly,
-	\begin{equation*}
-	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-	\end{equation*}
-	with kernel,
-	\begin{equation*}
-	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-	\end{equation*}
-	Appealing to a standard concentration inequality for U-statistics (see Lemma \ref{lem: bounded_difference}) we therefore have
-	\begin{equation*}
-	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
-	\end{equation*}
-	each with probability at least $1 - \delta$. 
-	%The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$.
+Taking Lemma~\ref{lem: expected_density_cut} and \eqref{eqn: conductance_upper_bound_pf1} as given we can now complete the proof of the theorem. We lower bound $\Phi_{n,r}(\Csig[\Xbf])$ as follows:
+\begin{equation*}
+\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{25(1 + \delta)d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{3(1 - \delta) \sigma \lambda_{\sigma}^2}.
+\end{equation*}
+Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $c_1(\Pbb,r) = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
 
@@
 let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
-Our goal will be to upper bound $p_K$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
+Our goal will be to upper bound $\cut_{\Pbb,r}(\Csig)$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
 and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
@@
 \end{equation*}
-In order to lower bound $p_V$ we will show the following lower bound on the uniform local conductance:
+In order to lower bound $\vol_{\Pbb,r}(\Csig)$ we will show the following lower bound on the uniform local conductance:
 \begin{lemma}
@@
 Taking these two results as given we can now prove each of the two claims~\eqref{eqn:claim_one} and~\eqref{eqn:claim_two} in turn.
-\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } Recalling,~\eqref{eqn: density_cut_expansion} 
-	and by the linearity of expectations, we obtain
-	\begin{equation*}
-	p_K = \frac{\mu_K}{{n \choose 2}} = 2 \cdot \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r). \tag{for each $i,j$, $i \neq j$}
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_K & = 2 \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& = 2 \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-	& \leq 2 \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = 2 \nu_d r^d \lambda \Pbb(\Csigr).
-	\end{align*}
-	where the inequality follows from \ref{asmp: cluster_separation}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
-Then, upper bounding the integral using \sbcomment{I changed the Lemma referenced here.
-I think it was wrong before} Lemma \ref{lem: expected_number_boundary_points} gives the final result.
+\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } For each $i,j$ such that $i \neq j$, we can write 
+\begin{equation*}
+\cut_{\Pbb,r}(\Csig) =  \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r).
+\end{equation*}
+Writing this as an integral, we have
+\begin{align*}
+\cut_{\Pbb,r}(\Csig) & = \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+& = \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
+& \leq \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = \nu_d r^d \lambda \Pbb(\Csigr).
+\end{align*}
+where the inequality follows from \ref{asmp: low_noise_density}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
+Then, upper bounding the integral using Lemma \ref{lem: expected_number_boundary_points} gives the final result.
 
 %\subsection{Proof of Lemma~\ref{Z}}
-\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } Recalling,~\eqref{eqn: volume_expansion}
-%The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. 
-	and by the linearity of expectation we obtain
-	\begin{equation*}
-	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-	\end{equation*}
-	Writing this with respect to the density function $f$, we have
-	\begin{align*}
-	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+\paragraph{Proof of Claim~\eqref{eqn:claim_two}: }  For each $i,j$ such that $i \neq j$, we can write 
+\begin{equation*}
+\vol_{\Pbb,r}(\Csig) = \Pbb(x_i \in \Csig, x_j \in B(x_i,r))
+\end{equation*}
+Writing this as an integral, we have
+\begin{align*}
+\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
 & \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
@@
 %\begin{align*}
-%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ p_K = \frac{\mu_K}{{n \choose 2}} \\
-%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ p_V = \frac{\mu_V}{{n \choose 2}} \\
-%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ p_V^c = \frac{\mu_V^c}{{n \choose 2}}
+%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ \cut_{\Pbb,r}(\Csig) = \frac{\mu_K}{{n \choose 2}} \\
+%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ \vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} \\
+%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ \vol_{\Pbb,r}(\Csig)^c = \frac{\mu_V^c}{{n \choose 2}}
 %\end{align*}
@@
 %	\begin{equation*}
-%	p_K \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+%	\cut_{\Pbb,r}(\Csig) \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
 %	\end{equation*}
@@
 %	\begin{equation*}
-%	p_V \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
+%	\vol_{\Pbb,r}(\Csig) \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
 %	\end{equation*}
@@
 %	\begin{equation*}
-%	p_V = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
+%	\vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
 %	\end{equation*}
@@
 %	\begin{align*}
-%	p_V & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+%	\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
 %	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
@@
 %\end{equation*}
-%to $p_K$ and $p_V$. 
+%to $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$. 
 %
-%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $p_K$ and $p_V$.
+%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$.
 These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
@@
 %	\label{eqn: numerator_additive_bound}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}.
+%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}.
 %	\end{equation}
@@
 %	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq p_K + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq p_V - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq p_V^c - \sqrt{\frac{\log(1/\delta)}{n}}
+%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig)^c - \sqrt{\frac{\log(1/\delta)}{n}}
 %	\end{equation*}
-%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $p_V^c \geq p_V$. 
+%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $\vol_{\Pbb,r}(\Csig)^c \geq \vol_{\Pbb,r}(\Csig)$. 
 %\end{proof}
@@
 %\label{eqn: conductance_representation_1}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{p_K + \left(\frac{\cut_{n,r}}{{n \choose 2}} - p_K\right)}{p_V + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - p_V\right)}.
+%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{\Pbb,r}(\Csig) + \left(\frac{\cut_{n,r}}{{n \choose 2}} - \cut_{\Pbb,r}(\Csig)\right)}{\vol_{\Pbb,r}(\Csig) + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - \vol_{\Pbb,r}(\Csig)\right)}.
 %\end{equation}
@@
 %\begin{equation*}
-%\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{p_K + \Err_n}{p_V - \Err_n}
+%\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}
 %\end{equation*}
@@
 %\begin{align*}
-%\frac{p_K + \Err_n}{p_V - \Err_n} & = \frac{p_K}{p_V} \left(\frac{p_V}{p_V - \Err_n}\right) + \frac{\Err_n}{p_V - \Err_n} \\
-%& = \frac{p_K}{p_V} + \left(\frac{p_K}{p_V} + 1\right)\frac{\Err_n}{p_V - \Err_n} \\
-%& \leq \frac{p_K}{p_V} + 2 \frac{\Err_n}{p_V - \Err_n}.
+%\frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} & = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \left(\frac{\vol_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig) - \Err_n}\right) + \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
+%& = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + \left(\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 1\right)\frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
+%& \leq \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}.
 %\end{align*}
@@
 %\begin{equation*}
-%\frac{p_K}{p_V} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
+%\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
 %\end{equation*}
@@
 %\begin{equation*}
-%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 p_V^2}
+%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 \vol_{\Pbb,r}(\Csig)^2}
 %\end{equation*}
-%which implies $2 \frac{\Err_n}{p_V - \Err_n} \leq \epsilon$.
+%which implies $2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \leq \epsilon$.
 
@@
 Let $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
-The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that, for universal constants $c_2, c_3,c_4 > 0$, with probability one
-\begin{equation*}
-\limsup_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{c_4 \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
+The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that with high probability,
+\begin{equation*}
+\tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{ \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3.
 \end{equation*}
@@
 \end{equation*}
-
-With these functionals in hand, we can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
+We can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
 \begin{equation*}
@@
 
-The following Proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
+The following proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
 \begin{proposition}
@@
 
-The second step in our approach is to lower bound the local spread and conductance over the neighborhood graph $\widetilde{G}_{n,r}$.
-In the following result we give lower bounds for both quantities, which hold asymptotically as $n \to \infty$.
+The second step in our approach is to lower bound the local spread and conductance over the neighborhood graph $\widetilde{G}_{n,r}$. In the following result we give lower bounds for both quantities. 
 \begin{proposition}
 	\label{prop: local_spread_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one,
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_2(\Pbb,r)$, $c_3(\Pbb,r)$, and $c_4(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\}
+	\end{equation*}
+	the following inequalities:
+	\begin{equation}
+	\label{eqn:min_degree}
+	\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10,
+	\end{equation}
+	and
 	\begin{equation}
 	\label{eqn: local_spread}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}} 
+	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}},
 	\end{equation}
@@
 	\label{eqn: conductance}
-	\liminf_{n \to \infty} \Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
-	\end{equation}
+	\Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}},
+	\end{equation}
+	hold with probability at least $1 - \frac{c_3(\Pbb,r)}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
 \end{proposition}
@@
 Taking these results as given, the proof of Theorem \ref{thm: mixing_time_upper_bound} is more or less complete.
-We note that since $r$ is fixed, with probability one $\liminf_{n \to \infty} \min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}_{n,r}) = \infty$ (see Lemma \ref{lem: ball_bounds_in_probability}).
-In particular, for sufficiently large $n$ the condition $\min_{u \in \Csig[\Xbf]} \deg(u; \widetilde{G}[\Xbf]) \geq 10$ is satisfied, again with probability one.
-We may therefore apply Proposition \ref{prop: pointwise_mixing_time} and obtain
-\begin{align*}
-\liminf_{n \to \infty} \tau_{\infty}(\widetilde{G}_{n,r}) & \leq \liminf_{n \to \infty} \left\{\frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \right\}
+Since the condition $\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10$ is satisfied, we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
+\begin{align*}
+\tau_{\infty}(\widetilde{G}_{n,r}) & \leq  \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
 \\
-& \leq \frac{2^{27}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
-\end{align*}
-whereupon the theorem follows after an appropriate choice of universal constants $c_2, c_3, c_4 > 0$.
+& \leq \frac{2^{29}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \\
+& \leq \frac{2^{34}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
+\end{align*}
+whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, $c_4(\Pbb,r) := \frac{2\lambda_{\sigma} \nu_d r^d}{1875}$ and $c_5(\Pbb,r) := \frac{2}{25}(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$.
 In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
@@
 
-We prove~\eqref{eqn: local_spread} immediately before turning our attention to~\eqref{eqn: conductance}, which will require the bulk of our attention.
+We prove~\eqref{eqn:min_degree} and~\eqref{eqn: local_spread} immediately before turning our attention to~\eqref{eqn: conductance}, which will require the bulk of our attention.
 First, however, we introduce some notation.
-Recall that $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$ denotes the subgraph induced by $\Csig[\Xbf]$.
 For $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
@@
 and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
-We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$.
+We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$, and $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$,
+
+\paragraph{Proof of~\eqref{eqn:min_degree}:}
+Applying Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/5$, we have that
+\begin{equation*}
+\widetilde{d}_{\min} \geq \frac{24}{125} \lambda_{\sigma} \nu_d r^d n
+\end{equation*} 
+with probability at least $1 - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}}$, and therefore for any  
+\begin{equation*}
+n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: c_3(\Pbb,r)
+\end{equation*}
+the minimum degree $\widetilde{d}_{\min} \geq 10$.
 
@@
 
-Letting $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$, we rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
-Then by Lemma \ref{lem: ball_bounds_in_probability}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{36 \lambda_{\sigma} r^d \nu_d}{625 \Pbb(\Csig) \Lambda_{\sigma}} \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}}.
-\end{equation*}
+We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$. Then applying Lemma \ref{lem:ball_bounds_in_probability} with $\delta = 1/5$, we have
+\begin{align*}
+s(\widetilde{G}_{n,r}) & \geq \frac{9}{10} \cdot \frac{\left(\frac{6}{25}\right)^2 (1 - \delta)^2 \lambda_{\sigma}^2 \nu_d r^{2d}}{(1 + \delta)\widetilde{\vol}_{\Pbb,r}(\Csig)n^2} \\
+& \geq \frac{1}{40} \frac{\lambda_{\sigma^2} \nu_d r^{d}}{\Lambda_{\sigma}}
+\end{align*}
+with probability at least $1 - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
 
@@
 
-Our goal is to show that with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \set{\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S)} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
+Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$
+\begin{equation*}
+\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}}.
 \end{equation*}
 In order to show this bound holds uniformly over all sets $S \subseteq \Csig[\Xbf]$, we will split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
-To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S), \pi(S^c) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a lazy random walk over $G = (V,E)$.)
+To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S), \pi(S^c) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a lazy random walk over $G$.)
 
@@
 	\label{lem: graph_conductance_profile_lb}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, with probability one
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_2(\Pbb,r)$ and $c_4(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_1}\right)^d
+	\end{equation*}
+	the following upper bound holds
 	\begin{equation}
 	\label{eqn: graph_conductance_profile_lb}
-	\liminf_{n \to \infty} \left\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \right\} \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}}.
-	\end{equation}
+	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}},
+	\end{equation}
+	with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$. 
 \end{lemma}
@@
 	Let $T:\Csig \to \Csig[\Xbf]$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.
-uppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
-Then there exists a constant $c > 0$ which may depend on $\Pbb$, but does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
+Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
+Then there exists a constant $c_7(\Pbb,r) > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
 	\begin{equation}
 	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} }{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}  }
+	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
 	\end{equation}
@@
 
-Clearly, Lemma \ref{lem: graph_to_continuous_conductance} is useful only when combined with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)}$.
+Clearly, Lemma \ref{lem: graph_to_continuous_conductance} is useful only when combined with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
 Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures supported on open, connected and bounded domains with Lipschitz boundaries.
@@
 	\label{thm: stagnating_transportation_maps}
-	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \Csig[\Xbf]$ such that the following statement holds:
-	\begin{equation}
-	\label{eqn: stagnating_transportation_maps}
-	\limsup_{\widetilde{n} \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq c
-	\end{equation}
-	where $c$ is constant in $n$ and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
+	There exists constants $c_2(\Pbb,r)$ and $c_3(\Pbb,r)$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_2(\Pbb,r)\delta}\right)^{d}
+	\end{equation*}
+	then with probability at least $1 - \frac{c_3(\Pbb,r)}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
+	which satisfies
+	\begin{equation*}
+	\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \leq \delta.
+	\end{equation*}
 \end{theorem}
-We remark that $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} = \norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)}$, and therefore the preceding theorem shows that with probability one, $\limsup_{n \to \infty} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} = 0$.
+Lemma~\ref{lem: graph_to_continuous_conductance} and Theorem~\ref{thm: stagnating_transportation_maps} show that with high probability, the discrete normalized cut $\widetilde{\Phi}_{n,r}(S)$ is lower bounded by the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S))$ over all sufficiently large sets $S \subseteq \Xbf$.
 The following result then supplies the last step, a uniform lower bound on the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ for all sets $\Sset \subseteq \Csig$.
@@
 \end{lemma}
-
 With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
-Observe that for any $c > 0$ fixed in $n$, for sufficiently large $n$ with probability one $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} \leq c$.
-This fact, along with the asymptotic upper bound on $s(\widetilde{G}_{n,r})$ given by~\eqref{eqn: local_spread}, guarantees that the conditions of Lemma~\ref{lem: graph_to_continuous_conductance} are satisfied with probability one as $n \to \infty$.
-Therefore,
-\begin{align*}
-\liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S)} & \geq \liminf_{n \to \infty} \set{\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)} }{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}  }} \\
-& \geq \widetilde{\Phi}_{\Pbb,r} - \liminf_{n \to \infty} \set{\frac{c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}}{s(\widetilde{G}_{n,r}) - c \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}}} \\
-& = \widetilde{\Phi}_{\Pbb,r} \tag{Theorem \ref{thm: stagnating_transportation_maps},\eqref{eqn: local_spread}, and Slutsky's Theorem.}
-\end{align*}
-and the bound on $\widetilde{\Phi}_{\Pbb,r}$ given by Lemma \ref{lem: nonuniform_continuous_conductance} yields the desired result.
+Fix
+\begin{equation*}
+\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2c_7(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
+\end{equation*}
+and suppose $n$ is large enough so that $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} \leq \delta$ for the optimal transportation map $T_n$.
+By \eqref{eqn: local_spread}, $\delta \leq s(\widetilde{G}_{n,r})$ . Therefore, we may apply Lemma~\ref{lem: graph_to_continuous_conductance} and obtain
+\begin{align*}
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq \frac{\widetilde{\Phi}_{\Pbb,r}}{2},
+\end{align*}
+where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2c_7(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}}$.
+Then, Lemma~\ref{lem: nonuniform_continuous_conductance} yields the desired result.
 It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we do in the following two subsections.
@@
 \subsection{Proof of Lemma \ref{lem: graph_to_continuous_conductance}}
-Let $S \subseteq \Csig[\Xbf]$ be an element of $\mathcal{L}(\widetilde{G}_{n,r})$, and denote $\Sset := T^{-1}(S)$.
-Denote $\varDelta = \norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}$, and let $r^{+} = r + \varDelta$ and $r^{-} = r - \varDelta$.
+Let $S \subseteq \Csig[\Xbf]$ belong to $\mathcal{L}(\widetilde{G}_{n,r})$, and denote $\Sset := T^{-1}(S)$.
+Further let $\varDelta := \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}$, and $r^{+} := r + \varDelta$ and $r^{-} := r - \varDelta$.
 Our goal is to lower bound
 \begin{equation*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c \varDelta}{s(\widetilde{G}_{n,r}) - c \varDelta}
-\end{equation*}
-for some constant $c > 0$ which may depend on the distribution $\Pbb$ but not on the sample size $n$.
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c_7(\Pbb,r)\varDelta}{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r) \varDelta}
+\end{equation*}
+for some constant $c_7(\Pbb,r) > 0$.
 We first state the relationships between the discrete functionals $\widetilde{\cut}_{n,r}$ and $\widetilde{\vol}_{n,r}$, and the continuous functionals $\widetilde{Q}_{\Pbb,r}$ and $\widetilde{\pi}_{\Pbb,r}$, alluded to in the previous section.
@@
 	\label{lem: cut_volume}
+	For any set $S \subseteq \Csig[\Xbf]$ and $\mathcal{S} = T^{-1}(S)$, 
 	\begin{equation}
@@
 	\label{lem: deviation_transportation_distance}
-	Suppose $\Delta \leq r$. Then there exist constants $c_5,c_6 \geq 0$ which may depend on $\Pbb$ but do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
-	\begin{align*}
-	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5 \varDelta \\
-	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5 \varDelta \\
-	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_6 \varDelta \\
-	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_6 \varDelta.
+	Suppose $\Delta \leq r$. Then there exist constants $c_8(\Pbb,r),c_9(\Pbb,r) \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
+	\begin{align*}
+	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r) \varDelta \\
+	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r) \varDelta \\
+	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_9(\Pbb,r) \varDelta \\
+	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_9(\Pbb,r) \varDelta.
 	\end{align*}
@@
 \frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \frac{\widetilde{Q}_{\Pbb,r^-}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r^+}(\Sset)} \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \tag{Lemma \ref{lem: cut_volume}} \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_6 \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_6 \varDelta} \left(1 - \frac{2 c_5 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_6}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_9(\Pbb,r) \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_9(\Pbb,r) \varDelta} \left(1 - \frac{2 c_8(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_9(\Pbb,r)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
 \end{align}
@@
 	Suppose $\varDelta \leq \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)$.
-Then there exists a constant $c_7 > 0$ which may depend on the distribution $\Pbb$ but does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
-	\begin{equation*}
-	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_7 \varDelta
+Then there exists a constant $c_{10}(\Pbb,r) > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
+	\begin{equation*}
+	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_{10}(\Pbb,r) \varDelta
 	\end{equation*}
@@
 \begin{align*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_6}{\widetilde{\pi}_{n,r}(S) - c_7\varDelta} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
-& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_6}{s(\widetilde{G}_{n,r}) - c_7\varDelta} + \frac{2c_5}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_9(\Pbb,r)}{\widetilde{\pi}_{n,r}(S) - c_{10}(\Pbb,r)\varDelta} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
+& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_9(\Pbb,r)}{s(\widetilde{G}_{n,r}) - c_{10}(\Pbb,r)\varDelta} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
 \end{align*}
 where the latter inequality follows as we assumed $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-Choosing the constant $c$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c = \max\set{2c_5/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_6, c_7}f$, we achieve our desired result.
+Choosing the constant $c_7(\Pbb,r)$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c_7(\Pbb,r) = \max\set{2c_8(\Pbb,r)/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_9(\Pbb,r), c_{10}(\Pbb,r)}f$, we achieve our desired result.
 It remains to show Lemmas~\ref{lem: cut_volume}, \ref{lem: deviation_transportation_distance}, and \ref{lem: continuous_pi_lb}, which we now turn to.
@@
 \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)  & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl( 2d(r + \Delta)^{d - 1}\varDelta \bigr) \tag{1st-order Taylor expansion of $(r + \Delta)^d$ } \\
-& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_5 \varDelta. \label{eqn: deviation_transportation_distance_1}
+& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_8(\Pbb,r) \varDelta. \label{eqn: deviation_transportation_distance_1}
 \end{align}
@@
 \int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5\varDelta.
+& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r)\varDelta.
 \end{align*}
@@
 & \geq \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) d\Pbb(x) - \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r)) d\Pbb(x)} \\
-& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_5 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_6 \varDelta.
+& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_8(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_9(\Pbb,r) \varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Sset} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_6\varDelta.
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_9(\Pbb,r)\varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) }{\int_{\Csig}\ell_{\Pbb,r^-}(x) \,d\Pbb(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_5\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_5\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_7 \varDelta.
-\end{align*}
-where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_5\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r)\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r)\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{10}(\Pbb,r) \varDelta.
+\end{align*}
+where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_8(\Pbb,r)\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
 
@@
 
-\subsection{Concentration inequalities}
-\label{sec: concentration}
-
-Given a symmetric kernel function $K: \Rd \to \Reals$ with $\sup_{x,y \in \Rd} \abs{K(x,y)} \leq 1$, and independent and identically distributed data $\set{x_1, \ldots, x_n}$, we define the \textit{order-$2$ $U$-statistic} to be
-\begin{equation*}
-U := \frac{1}{ {n \choose 2} } \sum_{1 \leq i < j \leq n} K(x_i,x_j).
-\end{equation*}
-
-\begin{lemma}[Hoeffding's inequality for $U$-statistics.]
-	\label{lem: bounded_difference}
-	For any $t > 0$,
-	\begin{equation*}
-	\mathbb{P}(\abs{U - \mathbb{E}U} \geq t) \leq 2 \exp\left\{-nt^2\right\}
-	\end{equation*}
-	Further, for any $\delta > 0$, we have
-	\begin{align*}
-	U & \leq \mathbb{E}U + \sqrt{\frac{\log(1 / \delta)}{n} }, \\
-	U & \geq \mathbb{E}U - \sqrt{\frac{\log(1 / \delta)}{n} }
-	\end{align*}
-	each with probability at least $1 - \delta$. 
+\section{Proof of Theorem~\ref{thm:volume_ssd}}
+\label{sec:proof_of_volume_ssd}
+
+In this section, we prove Theorem \ref{thm:volume_ssd}. The theorem is a consequence of Lemma 3.4 in \citet{zhu2013}, which relates the quality of the PPR output to normalized cut and mixing time. 
+\begin{lemma}[Lemma 3.4 of \citet{zhu2013}.]
+	\label{lem:zhu}
+	Let $G = (V,E)$ be a undirected, unweighted graph, let $A \subseteq V$, and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
+For $\beta \in (0,1)$,  the sweep cut $S_{v,\beta}$ is
+	\begin{equation*}
+	S_{v,\beta} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}
+	\end{equation*} Suppose $\alpha \leq \frac{1}{9 \tau_{\infty}(G[S])}$,  $\varepsilon \leq \frac{1}{20}\vol(A;G)$.
+Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in S^g$ and $\beta \in \frac{1}{\vol(A;G)}(\frac{1}{100},\frac{2}{5})$ the sweep cut $S_{\beta,v}$ satisfies
+	\begin{equation*}
+	\vol(A \vartriangle S_{\beta,v}) \leq \left(218\frac{\Phi(A;G)}{\alpha}\right) \vol(A;G)
+	\end{equation*}
 \end{lemma}
 
-We will employ a sharper inequality to bound the sum of independent Bernoulli random variables.
-\begin{lemma}
-	\label{lem: multiplicative_Hoeffding}
-	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \sum_{i = 1}^n \Ebb(X_i)$. Then,
-	\begin{align*}
-	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
-	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
-	\end{align*}
-\end{lemma}
-
-We will require large-sample and asymptotic bounds on several different degree and volume functionals, which follow from Lemmas \ref{lem: bounded_difference} and \ref{lem: multiplicative_Hoeffding}.
-Let
-\begin{alignat*}{2}
-\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ && \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
-\degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
-\degmin & := \min_{u \in \Xbf} \deg(u; G_{n,r}).
-\end{alignat*}
-
-\begin{lemma}
-	\label{lem: ball_bounds_in_probability}
-	Under the geometric conditions \ref{asmp: bounded_density}-\ref{asmp: bounded_volume}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
+\paragraph{Proof of Theorem~\ref{thm:volume_ssd}.}
+First, we verify that the conditions of Lemma~\ref{lem:zhu} are met when $S = \mathcal{C}_{\sigma}[\Xbf]$, $G = G_{n,r}$, and the user-specified parameters satisfy the initialization conditions~\eqref{eqn: initialization}.
+By Theorem~\ref{thm: mixing_time_upper_bound} and \eqref{eqn: initialization}, the teleportation parameter $\alpha$ is upper bounded
+\begin{equation*}
+\alpha < \frac{1}{9\tau_{u}(\theta)} \leq \frac{1}{9\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])}
+\end{equation*}
+with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$.
+Since we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets in Algorithm~\ref{alg: ppr}, we may apply Lemma~\ref{lem:zhu}.
+By this Lemma, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}(\frac{1}{100},\frac{2}{5})$, the sweep cut $S_{v,\beta}$ of $p(\alpha, v; G_{n,r})$ satisfies
 \begin{align}
-	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
-	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
-	\frac{\abs{\Csig[\Xbf]}}{n} & \leq (1 + \epsilon)\Pbb(\Csig) \label{eqn: Csig_cardinality_bound}\\
-	\label{eqn: volwt_bound}
-	\frac{1}{2}\vol_0 &\leq \vol_{n,r}(\Csig[\Xbf])  \leq \frac{3}{2} \vol_0
+\vol_{n,r}(\Csig[\Xbf] \vartriangle S_{\beta,v}) & \leq \left(218\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}\right) \vol_{n,r}(\Csig[\Xbf]) \nonumber \\
+& \leq 2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf]) \label{eqn:volume_ssd_pf1}
 \end{align}
-
-	Additionally, with probability one,
-	\begin{align}
-	\liminf_{n \to \infty} \frac{\degminwt}{n} & \geq \frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound_asymp}\\
-	\limsup_{n \to \infty} \frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d r^d \label{eqn: max_vol_bound_asymp}
-	\end{align}
-
-	If additionally \ref{asmp: valid_region} holds: for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{align}
-	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
-	\end{align}
-
-	If additionally \ref{asmp: C'_bounded_density} holds (but not necessarily \ref{asmp: valid_region}): for any $\epsilon > 0$, the following bound holds with probability tending to one as $n \to \infty$:
-	\begin{equation}
-	\label{eqn: min_cluster_degree_bound_2}
-	\frac{\degminpr}{n} \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
-	\end{equation*}
-	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
-	\begin{equation*}
-	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
-	\end{equation*}
-	and we have shown \eqref{eqn: min_cluster_degree_bound}.
-Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
-\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
-
-	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
-
-	Finally, note that
-	\begin{equation*}
-	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
-	\end{equation*}
-	can be rewritten as a U-statistic, and furthermore
-	\begin{equation*}
-	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
-	\end{equation*}
-
-	Therefore by Lemma \ref{lem: bounded_difference}
-	\begin{equation}
-	\label{eqn: ball_bounds_in_probability_1}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
-	\end{equation}
-	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
-Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
-	\begin{equation*}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
-	\end{equation*}
-
-	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
-	\begin{equation*}
-	\Pbb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)} \geq (1 + \epsilon)\mu \right) \leq \exp(-n\epsilon^2\mu).
-	\end{equation*}
-	The two asymptotic statements \eqref{eqn: min_cluster_degree_bound_asymp} and \eqref{eqn: max_vol_bound_asymp} therefore both follow from the Borel-Cantelli Lemma.
-\end{proof}
-
-\section{Proof of Theorem \ref{thm: misclassification_rate}}
-\label{sec: proof_of_misclassification_rate}
-In this section, we prove both Theorem \ref{thm: misclassification_rate}.
-The result is in essence a consequence of the bounds in Theorem~\ref{thm: conductance_upper_bound} 
-and Theorem~\ref{thm: mixing_time_upper_bound} bounding the normalized cut and mixing time, together with the result of \citet{zhu2013} relating the quality of the PPR output to these quantities, and the result in Lemma~\ref{lem: ball_bounds_in_probability}
-that allows us to translate the guarantees on the volume to guarantees on the symmetric set difference.
-
-% and the relevant portions of Corollary \ref{cor: appr}.
-We begin with Lemma \ref{lem: zhu}, which is a restatement of Lemma 3.4 of \citet{zhu2013}, translated into notation consistent with the rest of this paper.
-It is stated with respect to an arbitrary $S \subseteq G = (V,E)$, and a good set $S^g \subseteq S$ with $\vol(S^g; G) \geq \vol(S; G)/2$.\footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(S;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}
-
-\begin{lemma}
-	\label{lem: zhu}
-	Let $\varepsilon \geq 0$, $v \in S^g$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$, and $\vol_0 \in [1 - c,1 + c] \vol(S;G)$ for $0 < c < 1$.
-Consider taking sweep cuts of the approximate \pprspace vector $\pbf^{(\varepsilon)} := \pbf^{(\varepsilon)}(v,\alpha; G)$ of the form
-	\begin{equation*}
-	S_{\beta} := \left\{u \in V: \pbf^{(\varepsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
-	\end{equation*}
-	For any $\beta < \frac{3}{5(1 + c)}$, and $0 \leq \varepsilon \leq \frac{1}{10} \vol(S;G)$ the following bounds hold:
-	\begin{align}
-	\vol(S_{\beta} \setminus S; G) & \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(S; G), \label{eqn: zhu_1}\\
-	\vol(S \setminus S_{\beta}; G) & \leq \left(\frac{2\Phi(S;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(S;G)\right)\vol(S; G).  \label{eqn: zhu_2}
-	\end{align}
-\end{lemma}
-%\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}
-With this Lemma in place we
-observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_u(\theta)}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9\tau_{\infty}(G[S])}$.
-Moreover,
-\begin{enumerate}
-	\item we restrict $v \in \Csig[\Xbf]^g$
-	\item the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$, for some $1/40 < \beta < 1/11$
-	\item by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$
-	\item the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\varepsilon = 0$.
-\end{enumerate}
-
-All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq 1/10\tau_u(\theta)$, the following bounds hold with probability tending to 1 as $n \to \infty$:
-\begin{equation*}
-\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
-\end{equation*}
-Noting that
-\begin{align*}
-\abs{\widehat{C} \setminus \Csig[\Xbf]} & \leq \frac{\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf])}{\degmin}   \\
-\abs{\Csig[\Xbf] \setminus \widehat{C}} & \leq \frac{\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C})}{\degminwt}, \quad \textrm{and} \\
-\abs{\Csig[\Xbf]} & \geq \frac{\vol_{n,r}(\Csig[\Xbf])}{\degmax}
-\end{align*}
-the theorem follows in light of \eqref{eqn: min_degree_bound}, \eqref{eqn: min_cluster_degree_bound} and \eqref{eqn: max_degree_bound} from Lemma \ref{lem: ball_bounds_in_probability}.
-
-\section{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}
+where the latter inequality holds with probability at least $1 - 3\exp\set{-c_1(\Pbb,r)n}$, and follows from Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_u(\theta)}$ given in \eqref{eqn: initialization}.
+
+Now we show that we can apply~\eqref{eqn:volume_ssd_pf1} to the cluster estimate $\Cest$ output by Algorithm~\ref{alg: ppr}.
+Observe that $\Cest$ is itself a sweep cut; precisely $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{50},\frac{1}{5}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
+Moreover, applying  Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/2$,
+\begin{equation}
+\label{eqn:volume_ssd_pf2}
+\frac{1}{2}\vol_{\Pbb,r}(\Csig) \leq \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq \frac{3}{2}\vol_{\Pbb,r}(\Csig)
+\end{equation}
+with probability at least $1 - 2\exp\{-\frac{1}{4} n \vol_{\Pbb,r}(\Csig)^2\}$.
+Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\widehat{C} \vartriangle \Csig[\Xbf])$.
+This completes the proof of Theorem~\ref{thm:volume_ssd}.
+
+\section{Proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}}
 \label{sec: proof_of_consistent_cluster_recovery}
 
-We begin with some notation.
-Let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$, and $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices for the induced subgraph $\widetilde{G}_{n,r}$.
-Consider $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ given by
-\begin{equation*}
-\overline{\pibf}_{n,r}(x) := \frac{\widetilde{\deg}_{n,r}(x)}{\vol_{n,r}(\Csig[\Xbf])}.
-\end{equation*}
-(Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)
-
-Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(x) - \overline{\pibf}_{n,r}(x)$.
+As a reminder, to prove Theorem~\ref{thm: consistent_recovery_of_density_clusters} it will be sufficient to show that
+\begin{equation}
+\label{eqn: PPR_gap}
+\max_{u' \in \Cset'[\Xbf]} \frac{p_v(u')}{\deg_{n,r}(u')} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} < \frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \min_{u \in \Cset[\Xbf]} \frac{p_v(u)}{\deg_{n,r}(u)}
+\end{equation}
+with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$.
+
+To show this, we first establish in Lemma~\ref{lem: setup} that when Algorithm \ref{alg: ppr} is properly initialized, the resulting PPR vector is large for every vertex $u \in \Cset$, and small for every vertex $u' \in \Cset'$.
+Let $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ be the vector given by\footnote{Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.}
+\begin{equation*}
+\overline{\pibf}_{n,r}(u) := \frac{\widetilde{\deg}_{n,r}(u)}{\vol_{n,r}(\Csig[\Xbf])}.
+\end{equation*} Additionally, let $\degminpr = \min_{u \in \Cset'[\Xbf]} \deg_{n,r}(u')$.
 
@@
 		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminwt}
-		\end{equation}
-		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy the cluster separation condition \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
+		\pbf_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminwt}
+		\end{equation}
+		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ be another $\lambda$-density cluster. Then for each $u' \in \Cset'[\Xbf]$,
 		\begin{equation}
 		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf]) \tau_{\infty}(\widetilde{G}_{n,r})}{\degminpr}.
+		\pbf_v(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminpr}.
 		\end{equation}
@@
 
-We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-%\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
-%~
-
-In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
-Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$.
-As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
+We immediately note that by assumption, Algorithm \ref{alg: ppr} is well-initialized, and therefore the seed node $v$ is chosen in $\Csig[\Xbf]^g$.
+Since we additionally assume $\Cset$ is a $\kappa$-well-conditioned density cluster, we have that $r < \sigma/(2d) < \sigma$, and the upper bound
+\begin{equation*}
+\alpha < \frac{1}{9\tau_{u}(\theta)} \leq \frac{1}{(9 \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))}
+\end{equation*}
+holds with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$ by Theorem~\ref{thm: mixing_time_upper_bound}.
+Therefore, all the conditions of Lemma \ref{lem: setup} are met.
+
+We now collect the estimates on graph functionals we will use to complete the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}. 
+\begin{itemize}
+	\item By Theorem~\ref{thm: conductance_upper_bound},
+	\begin{equation*}
+	\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\theta) 
+	\end{equation*}
+	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)^2\}$.
+By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
+	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
+	\begin{equation*}
+	\degminwt \geq \frac{6}{25}(1 - \delta) \lambda_{\sigma} r^d \nu_d n,
+	\end{equation*}
+	with probability at least $1 - n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$.
+	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
+	\begin{equation*}
+	\degminpr \geq (1 - \delta) \lambda_{\sigma} r^d \nu_d n,
+	\end{equation*}
+	with probability at least $1 - n\exp\set{-\frac{\delta^2 \lambda_{\sigma} \nu_d r^d n}{3(1 + \frac{\delta}{3})}}$.
+
+	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
+	\begin{equation*}
+	d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_d r^d
+	\end{equation*}
+	with probability at least $1 - n\exp\set{-\frac{2\delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$.
+
+	\item 
+	\begin{equation*}
+	\widetilde{\vol}_{n,r}(\Csig[\Xbf]) \leq 2(1 + \delta) \vol_{\Pbb,r}(\Csig){n \choose 2}
+	\end{equation*}
+	with probability at least $1 - \exp\set{-\delta^2 (\vol_{\Pbb,r}(\Csig))^2}$.
+\end{itemize}
+
+In the rest of this proof we assume the above bounds hold. For all $u \in \Cset[\Xbf]$, $\widetilde{\deg}_{n,r}(u) = \deg_{n,r}(u)$, so by \eqref{eqn: lower_bound_PPR_in_cluster},
+\begin{align*}
+\frac{p_v(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5 \vol_{n,r}(\Csig[\Xbf])} - \frac{20 \kappa(\Cset)}{\widetilde{d}_{\min}^2} \\
+& \geq \frac{4}{5(1+\delta)\vol_{\Pbb,r}(\Csig)n^2} - \frac{20\kappa(\Cset)}{\left(\frac{6}{25}(1 - \delta)\lambda_{\sigma}\nu_dr^dn\right)^2} \\
+& \geq \frac{1}{10{n \choose 2}\vol_{\Pbb,r}(\Csig)},
+\end{align*}
+where the last inequality follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}. For all $u' \in \Cset'[\Xbf]$, 
 \begin{align}
-\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
-\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
+\frac{p_v(u')}{\deg_{n,r}(u')} & \leq \frac{20\kappa(\Cset)}{(d_{\min}')^2} \nonumber \\
+& \leq \frac{20\kappa(\Cset)}{\left((1 - \delta)\lambda_{\sigma}\nu_dr^dn\right)^2} \nonumber \\
+& \leq \frac{1}{100{n \choose 2}\vol_{\Pbb,r}(\Csig)} \label{eqn:consistent_recovery_of_density_clusters_pf1}
 \end{align}
-We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
-\begin{align}
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
-\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
-\end{align}
-
-The bounds in \eqref{eqn: gap_bounds} along with \eqref{eqn: setup_redux} imply that for each $u \in \Cset[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5} \frac{\widetilde{\deg}_{n,r}(u)}{\deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} - \frac{\degminwt}{125 \deg_{n,r}(u) \vol_{n,r}(\Csig[\Xbf])} \\
-& \geq \frac{22}{125 \vol_{n,r}(\Csig[\Xbf])} \tag{by \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound}, applied with $\varepsilon = \frac{1}{47}$} \\
-& \geq \frac{44}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-Similarly, for each $u' \in \Cset'[\Xbf]$,
-\begin{align*}
-\frac{\pbf(u')}{\deg_{n,r}(u')} & \leq \frac{\degminpr}{\deg_{n,r}(u') 125 \vol_{n,r}(\Csig[\Xbf])}  \\
-& \leq \frac{1}{125 \vol_{n,r}(\Csig[\Xbf])} \\
-& \leq \frac{8}{375 \vol_0}. \tag{by \eqref{eqn: volwt_bound}}
-\end{align*}
-and as every sweep cut $S_\beta$ under consideration in Algorithm \ref{alg: ppr} satisfies $8/375 < \frac{\beta}{\vol_0} < 44/375$, \eqref{eqn: consistent_density_cluster_recovery} must hold for the output $\widehat{C} = S_{\beta^*}$.
-
-It remains to prove \eqref{eqn: gap_bounds}. First, apply Lemma \ref{lem: ball_bounds_in_probability} with $\varepsilon = 1/11$ to obtain
-\begin{equation}
-\label{eqn: pimin_Dmin_lb}
-\frac{\degminpr^2}{\vol_{n,r}(\Csig[\Xbf])},~ \frac{\degminwt^2}{\vol_{n,r}(\Csig[\Xbf])} \geq \left(\frac{6}{25}\right)^2 \frac{\lambda_{\sigma}^2 \nu_d r^d}{\Lambda_{\sigma}\Pbb(\Csig)}  
-\end{equation}
-
-Then, by Theorem \ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_{u}(\theta)}$ given by \eqref{eqn: initialization},
-\begin{equation}
-\label{eqn: difficulty_bound}
-\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha} \leq 20\kappa(\Cset).
-\end{equation}
-\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa_ub} together show \eqref{eqn: gap_bounds}.
+where the last inequality again follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}.
+We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters}.
+
+We defer the proof of Lemma \ref{lem: setup}, and first extend Theorems~\ref{thm:volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters} to apply with respect to the aPPR vector.
 
@@
 	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $\alpha, r, \vol_0, v$ to be well-initialized in the sense of \eqref{eqn: initialization}, set $\varepsilon = \frac{1}{20 \vol_0}$, and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}$ rather than the exact \pprspace vector $\pbf$, with resulting output $\Cest$.
+Choose input parameters $r, \alpha, v, (L,U)$ to be well-initialized in the sense of \eqref{eqn: initialization}, additionally set
+	\begin{equation}
+	\label{eqn: appr_parameter}
+	\varepsilon = \frac{1}{25}\vol_{\Pbb,r}(\Csig)
+	\end{equation}
+	and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}_v$ rather than the exact \pprspace vector $\pbf_v$, with resulting output $\Cest$. Then
 	\begin{enumerate}
-		\item If \ref{asmp: valid_region} holds, then \eqref{eqn: misclassification_rate_ub} is still a valid upper bound for the misclassification error of $\Cest$.
+		\item The upper bound on symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ given by \eqref{eqn:volume_ssd} is still valid.
 		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
@@
 \begin{proof}
-The choice $\varepsilon = \frac{1}{20 \vol_0}$, along with Lemma~\ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\varepsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$.
-We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\varepsilon)}$.
-All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.
-
-%\paragraph{Proof of Corollary \ref{cor: appr}: consistent cluster estimation.}
-
-Using \eqref{eqn: appr_error} with $\varepsilon = \frac{1}{20}\vol_0$ along with \eqref{eqn: lower_bound_PPR_in_cluster} we obtain
-\begin{equation*}
-\pbf^{(\varepsilon)}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{\deg_{n,r}(u)}{20\vol_0} - \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt}, \quad \textrm{for all $u \in \Cset[\Xbf]$}
-\end{equation*}
-and similar reasoning as used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} yields
-\begin{equation*}
-\frac{\pbf^{(\varepsilon)}(u)}{\deg_{n,r}(u)} \geq \frac{15}{125\vol_0} \geq \frac{1}{11 \vol_0}, \quad \textrm{for all $u \in \Cset[\Xbf]$}.
-\end{equation*}
-On the other hand $\pbf^{(\varepsilon)}(u) \leq \pbf(u)$. Therefore $\frac{\pbf^{(\varepsilon)}(u')}{\deg_{n,r}(u')} \leq \frac{8}{375\vol_0}$, and the claim is proved.
+To prove the first claim, we must show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
+In particular, we must show that $\varepsilon \leq \frac{1}{20}\vol_{n,r}(\Csig)$.
+However by Lemma~\ref{lem:ball_bounds_in_probability},
+\begin{equation}
+\label{eqn:appr_pf1}
+\vol_{n,r}(\Csig[\Xbf]) \geq (1 - \delta)\vol_{\Pbb,r}(\Csig)
+\end{equation}
+with probability at least $1 - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2}$, and by setting $\delta = 1/5$ the desired claim follows.
+
+We now prove the second claim, by showing that both bounds in \eqref{eqn: PPR_gap} hold with respect to the aPPR vector.
+The upper bound follows immediately.
+Since $p^{(\varepsilon)}_v(x) \leq p_v(x)$ for all $x \in \Xbf$, the upper bound on $\max_{u' \in \Cset'[\Xbf]} p_v(u')$ also applies to $\max_{u' \in \Cset'[\Xbf]} p^{(\varepsilon)}_v(u')$.
+
+To show the desired lower bound on $\min_{u \in \Cset[\Xbf]} p^{(\varepsilon)}_v(u)$, we use the uniform approximation guarantee in \eqref{eqn: appr_error}.
+As previously observed, since $r < \sigma$, for any $u \in \Csig$ the ball $B(u,r) \subseteq \Csig$, and so $\widetilde{\deg}_{n,r}(u) = \deg_{n,r}(u)$.
+Along with \eqref{eqn: appr_parameter} and \eqref{eqn:appr_pf1}, this means
+\begin{equation*}
+\varepsilon \deg_{n,r}(u) \leq \frac{\overline{\pi}_{n,r}(u)}{25(1 - \delta)}
+\end{equation*}
+and therefore by \eqref{eqn: lower_bound_PPR_in_cluster}, for every $u \in \Cset[\Xbf]$,
+\begin{equation*}
+p^{(\varepsilon)}_v(u) \geq \left\{\frac{4}{5} - \frac{1}{25(1 - \delta)}\right\} \overline{\pi}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminwt}.
+\end{equation*}
+\noindent Using the arguments given in the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}, and choosing the universal constant in \eqref{eqn: kappa_ub} to be sufficiently small, the upper bound in \eqref{eqn:consistent_recovery_of_density_clusters_pf1} follows.
 
@@
 \subsection{Proof of Lemma~\ref{lem: setup}}
-	%The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. 
+
+In this subsection, we will let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$.
+Additionally we let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices over the induced subgraph $\widetilde{G}_{n,r}$.
 Given a starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
@@
 
-	Note that by \ref{asmp: cluster_separation}, for every $u \in \Csig[\Xbf], (u',u) \not\in E$ and therefore $s(u') = 0$.
+	Note that by \ref{asmp: low_noise_density}, $\dist(\Csig,\Cset') > r$.
+Therefore for every $u \in \Csig[\Xbf]$ and $u' \in \Cset'[\Xbf]$ $(u',u) \not\in E$ and so $s(u') = 0$.
 Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
@@
 	\end{align*}
+\end{proof}
+
+\section{Proof of Lower Bound.}
+
+To prove Theorem~\ref{thm:ppr_lb}, we will proceeding according to the following steps:
+\begin{enumerate}
+	\item We study the spectral partitioning properties of PPR on an arbitrary graph $G$, and show that when suitably initialized inside a subset $S \subset V$, the normalized cut of the PPR sweep cut is upper bounded by (a function of) $\Phi(S)$.
+	\item We specialize to the graph $G = G_{n,r}$ and the subset $\mathcal{L}[\Xbf] \subset \Xbf$, and show that the normalized cut $\Phi_{n,r}(\mathcal{L}[\Xbf])$ is small (with high probability) when the diameter $\rho$ is large.
+	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\ref{alg: ppr} $\widehat{C}$ must therefore also have small normalized cut.
+	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Csig^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Csig^{(1)}[\Xbf])$.
+In fact, we generalize this to hold for any set $A \subset \Xbf$ for which the symmetric set distance metric $\Delta(A,\Cset_1[\Xbf])$ is small.
+	\item We conclude that the symmetric set distance metric $\Delta(\widehat{C},\Csig^{(1)}[\Xbf])$ must not be small.
+\end{enumerate}
+
+We devote the subsequent sections to proving each of the aforementioned steps.
+
+\subsection{Spectral partitioning properties of PPR.}
+
+Let $G = (V,E)$ be an undirected, unweighted graph with $m = \abs{E}$ total edges, defined on vertices $V = \set{v_1, \ldots, v_n}$.
+Let $C$ be a subset of the vertices $V$, Recall that for a given $\beta \in (0,1)$ the sweep cut
+\begin{equation*}
+S_{\beta,v} = \set{u \in V: \frac{p_v(u)}{\deg(u;G)} > \beta}
+\end{equation*} 
+The following theorem relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of $C$; it is stated with respect to the graph functionals 
+\begin{equation*}
+d_{\max} := \max_{u \in V} \deg(u;G), ~~\textrm{and}~~ d_{\min} := \min_{u \in V} \deg(u;G).
+\end{equation*}
+\begin{theorem}
+	\label{thm:conductance_ppr}
+	Let $C \subseteq V$ satisfy the following conditions:
+	\begin{itemize}
+		\item $\vol(C;G) \leq \frac{2}{3}\vol(G)$,
+		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
+		\item $\frac{20\Phi(C;G)}{1 + 10\Phi(C;G)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
+	\end{itemize}
+	Suppose $60\Phi(C;G) \leq \alpha \leq 70\Phi(C;G)$, and let $(L,U) = (0,1)$.
+Then, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$ such that for any $v \in C^g$ the following statement holds: For the PPR vector $p_v := p(v,\alpha;G)$, the minimum conductance sweep cut set satisfies
+	\begin{equation*}
+	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C;G)}
+	\end{equation*}
+\end{theorem}
+Although this theorem appears quite similar to standard results in the PPR literature -- for instance, Theorem 6 of \citet{andersen2006} -- crucially the above bound depends on $\log\left(\frac{m}{d_{\min}^2}\right)$ rather than $\log m$.
+In the case where $d_{\min} \asymp n$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$.
+
+Notwithstanding these improvements, the proof of Theorem~\ref{thm:conductance_ppr} follows the same general outline as the proof of Theorem~6 of \citet{andersen2006}.
+We now walk through this outline step by step, modifying the results of \citet{andersen2006} as needed.
+As with their work, we begin by proving a mixing time bound on the PPR vector $p_v$.
+
+\subsubsection{Mixing time of PPR.}
+
+To quantify the mixing of a PPR vector $p_v$, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$.
+For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that $S_{\beta_j}$ contains at least $j$ vertices.
+(For notational ease, we will write $S_{i} := S_{\beta_i}$, so that $S_1,S_2,\ldots,S_n$ comprise the $n$ unique sweep cuts of $p_v$.)
+For each $j = 1,\ldots,n$, we let $p[\vol(S_j)] =  \sum_{u \in S} p_v(u)$.
+Additionally, we let $p[0] = 0$ and $p[2m] = 1$.
+Finally, we extend $p[\cdot]$  by piecewise interpolation to be defined everywhere on its domain.
+The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$, defined as
+\begin{equation*}
+h(k) = p[k] - \frac{k}{2m}.
+\end{equation*}
+Next, for a given $0 \leq K_0 \leq m$, let 
+\begin{equation*}
+L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
+\end{equation*}
+be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$, and additionally let
+\begin{equation*}
+C(K_0) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
+\end{equation*}
+where we use the notation $\overline{k} := \min\{k, 2m - k\}$.
+
+Theorem~\ref{thm:mixing_time_PPR} implies that if the PPR random walk is not well mixed, then some sweep cut of $p_v$ must have small normalized cut.
+\begin{theorem}
+	\label{thm:mixing_time_PPR}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$, any $0 < K_0 < m$, and any $k \in [K_0,2m - K_0]$:
+	\begin{equation}
+	\label{eqn:mixing_time_PPR}
+	h(k) \leq \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
+	\end{equation}
+	or else there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
+\end{theorem}
+
+\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_PPR}).]
+	The proof of Theorem~\ref{thm:mixing_time_PPR} is essentially a combination of the proofs of Theorem~3 in \citet{andersen2006} and Theorem 1.2 in \citet{lovasz1990}.
+We will show that if $\Phi(S_j) > \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in (K_0,2m - K_0)$.
+
+	We proceed by induction on $t$. Our base case will be $t = 0$. Observe that $C(K_0) \cdot \sqrt{\overline{k}} \geq  h(k) - L_{K_0}(k)$ for all $k \in [K_0,2m - K_0]$, which implies
+	\begin{equation*}
+	L_{K_0}(k) + C(K_0) \cdot \sqrt{\overline{k}} \geq h(k).
+	\end{equation*}
+
+	Now, we proceed with the inductive step.
+By the definition of $L_{K_0}$, the inequality~\eqref{eqn:mixing_time_PPR} holds when $k = K_0$ or $k = 2m - K_0$.
+We will additionally show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$.
+Once this is shown, the concavity of the expression on the right hands side of~\eqref{eqn:mixing_time_PPR} implies that the inequality holds for all $k \in [K_0,2m - K_0]$.
+
+	By Lemma 5 of \citet{andersen2006}, we have that
+	\begin{align}
+	p[k_j] & \leq \alpha + \frac{1}{2}  \left(p[k_j - \abs{\partial(S_j)}] + p[k_j + \abs{\partial{S_j}}]  \right) \nonumber\\
+	& \leq \alpha + \frac{1}{2} \left(p[k_j - \Phi(S_j) \overline{k}_j] + p[k_j + \Phi(S_j) \overline{k}_j]  \right) \nonumber \\
+	& \leq \alpha + \frac{1}{2} \left(p[k_j - \phi \overline{k}_j] + p[k_j + \phi \overline{k}_j]\right) \nonumber
+	\end{align}
+	and subtracting $k_j/2m$ from both sides, we get
+	\begin{equation}
+	\label{eqn:mixing_time_PPR_pf1}
+	h(k_j) \leq \alpha + \frac{1}{2} \bigl(h(k_j - \phi \overline{k}_j) + h(k_j +  \phi \overline{k}_j) \bigr)
+	\end{equation}
+	From this point, we divide our analysis into cases.
+
+	\textbf{Case 1.}
+	Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$.
+We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
+	\begin{align*}
+	h(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
+	\end{align*}
+	A Taylor expansion of $\sqrt{1 + \phi}$ around $\phi = 0$ yields the following bound:
+	\begin{equation*}
+	\sqrt{1 + \phi} + \sqrt{1 - \phi} \leq 2 - \frac{\phi^2}{4},
+	\end{equation*}
+	and therefore
+	\begin{equation*}
+	h(k_j) \leq  \alpha t + L_{K_0}(k) + \frac{C(K_0)}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
+	\end{equation*}
+
+	\textbf{Case 2.}
+
+	Now, assume one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$.
+Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
+By the concavity of $h$, and applying the inductive hypothesis to $h(2k_j - K_0)$, we have
+	\begin{align*}
+	h(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
+	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0) + L_{K_0}(2k_j - K_0\bigr) + C(K_0)\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
+	& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
+	& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
+	\end{align*}
+\end{proof}
+
+As a sanity check, we confirm that Theorem~\ref{thm:mixing_time_PPR} is no weaker than Theorem~3 of \citet{andersen2006}.
+It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0) \leq 1$ for any $K_0$.
+Setting $K_0 = 0$ in Theorem~\ref{thm:mixing_time_PPR}, we therefore recover Theorem~3 of \citet{andersen2006}.
+
+We now proceed to identify when Theorem~\ref{thm:mixing_time_PPR} may offer some improvement on Theorem~3 of \citet{andersen2006}, by showing when we can upper bound $C(K_0) << 1$.
+The critical point is that since $h(k)$ is concave and $L_{K_0}(K_0) = h(K_0)$ the upper bound
+\begin{equation*}
+\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq h'(K_0) \sqrt{k}
+\end{equation*}
+holds whenever $k < m$. For similar reasons, when $k > m$, 
+\begin{equation*}
+\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq -h'(2m - K_0) \sqrt{2m - k}.
+\end{equation*} 
+(Since $h$ is not differentiable at points $k = \vol(S_j)$, here we use $h'$ to denote the left derivative of $h$ whenever $k < m$, and the right derivative of $h$ whenever $k \geq m$)
+
+The following Lemma gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, and a resulting upper bound on $C(K_0)$.
+\begin{lemma}
+	\label{lem:linearization_bound}
+	There exists $K_0 \in \set{0,\deg(v;G)}$ such that
+	\begin{equation}
+	\label{eqn:left_derivative}
+	h'(K_0) \leq  \frac{1}{2d_{\min}^2}.
+	\end{equation}
+	Additionally, for all $K_0 \in [0,2m]$,
+	\begin{equation}
+	\label{eqn:right_derivative}
+	h'(2m - K_0) \geq -\frac{d_{\max}}{d_{\min}\vol(G)}.
+	\end{equation}
+	As a result,
+	\begin{equation*}
+	C(K_0) \leq \frac{\sqrt{m}}{d_{\min}^2}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
+	The result of the Lemma is obvious once we show \eqref{eqn:left_derivative} and \eqref{eqn:right_derivative}.
+To show either inequality, it will be useful to work with an alternative representation of $h$.
+In particular,  whenever $\vol(S_j) \leq k < \vol(S_{j + 1})$ (where we let $S_0 = \emptyset$), the function $h(k)$ may be written as
+	\begin{equation}
+	\label{eqn:lovasz_simonovits}
+	h(k) = \sum_{i = 0}^{j} \left(p_v(u_{(i)}) - \pi(u_{(i)};G)\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(p_v(u_{(j+1)}) - \pi(u_{(j+1)};G)\right) 
+	\end{equation}
+	where the vertices are ordered $\frac{p_v(u_{(1)})}{\deg(u_{(1)};G)} \geq \frac{p_v(u_{(2)})}{\deg(u_{(2)};G)} \geq \cdots \geq \frac{p_v(u_{(n)})}{\deg(u_{(n)};G)}$, and as usual $\pi(u;G) = \frac{\deg(u;G)}{\vol(G)}$.
+
+	From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
+	\begin{equation}
+	\label{eqn:linearization_bound_pf1}
+	h'(k) \leq \frac{p(v_{(j + 1)})}{\deg(v_{(j + 1)};G)}
+	\end{equation}
+
+	We now upper bound $p(u)$ uniformly over all $u$ except the seed node $v$. For any $u \in V$ besides the seed node $v$, we can show by induction that
+	\begin{equation*}
+	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
+	\end{equation*} 
+	for any $t \geq 0$, and therefore
+	\begin{equation}
+	\label{eqn:linearization_bound_pf2}
+	p(\alpha,\chi_v)(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \leq  \frac{1}{2d_{\min}}.
+	\end{equation}
+	As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = \deg(v;G)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}.
+The inequality \eqref{eqn:right_derivative} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since
+	\begin{equation*}
+	h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}},
+	\end{equation*}
+	and the proof of the Lemma is therefore complete.
+\end{proof}
+
+To apply Theorem~\ref{thm:mixing_time_PPR}, we must also upper bound the linear interpolator $L_{K_0}(k)$.
+Of course, trivially $L_{K_0}(k) \leq \max\set{h(K_0), h(2m - K_0)}$ for all $k$.
+As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$.
+\begin{lemma}
+	\label{lem:interpolator_bound}
+	Assume $s = \chi_v$ for some $v \in V$. Let $K_0 = \vol(S_j)$ for some $j = 0,\ldots,n$. Then, 
+	\begin{equation*}
+	h(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h(K_0) \leq \frac{K_0}{2d_{\min}^2} + \frac{2\alpha}{1 + \alpha}.
+	\end{equation*}
+	and as a result for any $k \in \Reals$,
+	\begin{equation*}
+	L_{K_0}(k) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound})]
+	We make use of the representation~\eqref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
+	\begin{align*}
+	h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
+	& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
+	& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
+	\end{align*}
+
+	We will upper bound $h(K_0)$ by $p[\vol(S_j)] \leq p_v(v) + \sum_{u \in S_j \setminus \set{v}}p_v(u)$.
+In the proof of Lemma~\ref{lem:linearization_bound} we have already given an upper bound on $p_v(u)$ when $u \neq v$.
+Now, we additionally observe that for all $t$,
+	\begin{equation*}
+	e_vW^t(v) \leq \frac{1}{2d_{\min}} + \left(\frac{1}{2}\right)^t
+	\end{equation*}
+	and therefore $p_v(v) \leq \frac{1}{2d_{\min}} + \frac{2\alpha}{1 + \alpha}$.
+	As a result,
+	\begin{equation}
+	h(K_0) \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
+	\end{equation}
+	where the latter inequality follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.
+\end{proof}
+
+Combining Theorem~\ref{thm:mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound}, we have the following result.
+\begin{corollary}
+	\label{cor:mixing_time_PPR}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$, and let $\phi$ be any constant in $[0,1]$.
+Then, either the following bound holds for any integer $t$ and any $k \in [d_{\max},2m - d_{\min}]$:
+	\begin{equation*}
+	h(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t}
+	\end{equation*}
+	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
+\end{corollary}
+
+We arrive now at the main result of this section.
+It is similar in form to Theorem 2 of \citet{andersen2006} but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR}.
+To simplify notation, we will write the total mass placed by $p_v$ on a subset $S \subset V$ as $p_v(S) := \sum_{u \in S} p_v(u)$.
+\begin{theorem}
+	\label{thm:mixing_time_PPR_contrapositive}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$. Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}}{2d_{\min}^2}$, such that
+	\begin{equation}
+	\label{eqn:mixing_time_PPR_contrapositive_1}
+	p_v(S) - \frac{\vol(S;G)}{\vol(G)} > \delta
+	\end{equation}
+	for a set $S$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$. Then there exists a sweep cut $S_j$ of $p$, such that
+	\begin{equation*}
+	\Phi(S_j) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
+	\end{equation*}
+	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
+\end{theorem}
+\begin{proof}
+	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}.
+Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.
+
+	Now, letting
+	\begin{equation*}
+	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
+	\end{equation*}
+	we have that
+	\begin{equation*}
+	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
+	\end{equation*}
+	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
+\end{proof}
+
+\subsubsection{Improved Local Partitioning with PPR.}
+
+As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\widehat{C};G)$.
+First, we restate a theorem of \citet{andersen2006} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.
+
+\begin{theorem}
+	\label{thm:acl_3}
+	For any set $C$ and any constant $\alpha$, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$, such that for any vertex $v \in C^g$, the PPR vector $p(v,\alpha;G)$ satisfies
+	\begin{equation*}
+	p(v,\alpha;G) \geq 1 - 6\frac{\Phi(C;G)}{\alpha}.
+	\end{equation*}
+\end{theorem}
+We are now in a position to prove Theorem~\ref{thm:conductance_ppr} by combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3}.
+
+\begin{proof}[Proof (of Theorem~\ref{thm:conductance_ppr})]
+	Since $\alpha \geq 60\Phi(C)$ and $v \in C^g$, by Theorem~\ref{thm:acl_3},
+	\begin{equation*}
+	p_v(C) \geq \frac{9}{10}.
+	\end{equation*}
+	This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p_v(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$.
+Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{thm:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$.
+Therefore, the minimum conductance sweep cut satisfies
+	\begin{equation*}
+	\min_{j = 1,\ldots,n} \Phi(S_j;G) \leq \sqrt{\frac{1120\cdot \Phi(C;G)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
+	\end{equation*}
+	Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
+	\begin{equation*}
+	\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
+	\end{equation*}
+	completing the proof of the theorem.
+\end{proof}
+
+\subsection{Normalized cut of $\mathcal{L}[\Xbf]$.}
+
+Recall that for any set $\mathcal{A} \subset \mathcal{X}$, the $\Pbb$-weighted \emph{cut} and \emph{volume} functionals can be written as
+\begin{equation*}
+\cut_{\Pbb,r}(\Aset) = \int_{\Aset} \int_{\mathcal{X} \setminus \Aset} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y), \vol_{\Pbb,r}(\Aset):= \int_{\Aset} \int_{\mathcal{X}} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y),
+\end{equation*}
+and the continuous \emph{normalized cut} is
+\begin{equation*}
+\Phi_{\Pbb,r}(\Aset) := \frac{\cut_{\Pbb,r}(\Aset)}{\min\{\vol_{\Pbb,r}(\Aset),\vol_{\Pbb,r}(\mathcal{X} \setminus \Aset)\}}.
+\end{equation*}
+
+We now upper bound the normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ as a function of the diameter $\rho$, and the neighborhood graph radius $r$.
+Our bounds will be simple and not tight, but will display the right dependence on these parameters, and so will be sufficient for our purposes.
+
+To upper bound $\cut_{\Pbb,r}(\mathcal{L})$, note that for any $x = (x_1,x_2) \in \mathcal{L}$, if $x_2 \leq -r$ the ball $B(x,r)$ and the set $\mathcal{X}\setminus\mathcal{L}$ are disjoint.
+This implies
+\begin{align*}
+\cut_{\Pbb,r}(\mathcal{L}) & \leq \Pbb(\set{x \in \mathcal{X}: -r < x_2 < 0}) \cdot \max_{x \in \mathcal{X}} \Pbb(B(x,r)) \\
+& \leq \frac{r}{2 \rho} \cdot \frac{\pi r^2}{2 \sigma \rho}.
+\end{align*}
+By symmetry, $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, and therefore to upper bound $\Phi_{\Pbb,r}(\mathcal{L})$, it is sufficient to lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
+We have
+\begin{align*}
+\vol_{\Pbb,r}(\mathcal{L}) & \geq \Pbb(\set{x \in \Cset_1 \cap \mathcal{L}: \dist(x, \partial \Cset_1) > r}) \cdot \frac{\pi r^2}{2 \sigma \rho} \\
+& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\nu_d r^d}{2 \sigma \rho}  \\
+& \geq \frac{3}{16} \cdot \frac{\pi r^2}{2 \sigma \rho}
+\end{align*}
+where the last inequality follows since $r \leq \frac{1}{4}\sigma < \frac{1}{4}\rho$. Therefore, $\Phi_{\Pbb,r}(\mathcal{L}) \leq \frac{8r}{3\rho}.$
+
+Then, Lemma~\ref{lem:graph_functional_concentration} implies that the graph functionals $\cut_{n,r}(\mathcal{L}[\Xbf])$ and $\vol_{n,r}(\mathcal{L}[\Xbf])$--and in turn $\Phi_{n,r}(\mathcal{L}[\Xbf])$-- concentrate around their expectations.
+Precisely, we have that
+\begin{align}
+\Phi_{n,r}(\mathcal{L}[\Xbf]) & = \frac{\cut_{n,r}(\mathcal{L}[\Xbf])}{\min\set{\vol_{n,r}(\mathcal{L}[\Xbf]),\vol_{n,r}((\mathcal{X}\setminus\mathcal{L})[\Xbf])}} \nonumber \\
+& \leq \frac{3}{2}\Phi_{\Pbb,r}(\Aset) \leq \frac{4 r}{\rho} \label{eqn:lb_pf2}
+\end{align}
+with probability at least $1 - 3\exp\{-\frac{1}{25}n(\cut_{\Pbb,r}(\mathcal{L}))^2\}$.
+
+\subsection{Normalized cut of $\widehat{C}$.}
+
+To upper bound $\Phi_{n,r}(\widehat{C})$, we need to show that the conditions of Theorem~\ref{thm:conductance_ppr} are met with respect to the graph $G = G_{n,r}$ and subset $C = \mathcal{L}[\Xbf]$.
+To do, we require the following inequalities, which are satisfied with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2\delta^2n}{8 \rho \sigma(1 + \frac{\delta}{3})}} - 6 \exp\set{-n\delta^2(\cut_{\Pbb,r}(\mathcal{L}[\Xbf]))^2}$:
+\begin{itemize}
+	\item For any $r \in (0,\frac{1}{4}\sigma)$ and any $x \in \mathcal{X}$,
+	\begin{equation*}
+	\frac{\epsilon}{4\rho\sigma}\pi r^2 \leq \Pbb((B(x,r))) \leq  \frac{1}{2\rho\sigma} \pi r^2.
+	\end{equation*}
+	Therefore by Lemma~\ref{lem:bernstein_union}, $\frac{(1 - \delta)\epsilon \pi r^2}{4\rho \sigma}n \leq d_{\min} \leq d_{\max} \leq \frac{(1 + \delta)\pi r^2}{2\rho \sigma }n$. 
+	\item $\frac{(1 - \delta)}{2} n \leq \abs{\mathcal{L}[\Xbf]} \leq \frac{(1 + \delta)}{2} n$, 
+	\item $\vol_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta)\vol_{\Pbb,r}(\mathcal{L}) = \frac{(1 + \delta)}{2} \vol_{\Pbb,r}(\mathcal{X}) \leq \frac{(1 + \delta)}{2} \vol(G_{n,r})$, and
+	\item $(1 - \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf]) \leq \cut_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf])$.
+\end{itemize}
+We now condition on these inequalities, and letting $\delta = \frac{2}{67}$ we verify that under the setup of Theorem~\ref{thm:ppr_lb}, each of the conditions of Theorem~\ref{thm:conductance_ppr} are met:
+\begin{itemize}
+	\item $\vol(\mathcal{L}[X]) \leq \frac{(1 + \delta)}{2(1 - \delta)}\vol(G_{n,r}) \leq \frac{2}{3}\vol(G_{n,r})$ since $\delta < 1/7$,
+	\item $\abs{\mathcal{L}[X]} \geq \frac{n(1 - \delta)}{2} \geq \frac{2(1 + \delta)}{(1 - \delta)\epsilon} \geq \frac{d_{\max}}{d_{\min}}$ and $\frac{d_{\max}}{2d_{\min}^2} \leq \frac{8(1 + \delta)}{(1 - \delta)^2 \epsilon^2 \rho \sigma \pi r^2} \cdot \frac{1}{n} \leq \frac{1}{10}$ by \eqref{eqn:lb_sample_size},
+	\item $\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{4r}{\rho} \leq \frac{1}{10}$, by assumption on $r$ and $\rho$, and
+	\item $60\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{60(1 + \delta)}{1 - \delta}\Phi_{\Pbb,r}(\mathcal{L}) \leq \alpha \leq \frac{65(1 + \delta)}{1 - \delta}\Phi_{n,r}(\mathcal{L}[X]) \leq 70\Phi_{n,r}(\mathcal{L}[X])$ since $\delta < 2/67$.
+\end{itemize}
+
+We may therefore apply Theorem~\ref{thm:conductance_ppr}, which allow us to upper bound the minimum conductance sweep cut $\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G)$ or equivalently the output of Algorithm~\ref{alg: ppr}.
+
+To be precise, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6} \vol_{n,r}(\mathcal{L}[\Xbf])$, such that the following statement holds for any $v \in \mathcal{L}[\Xbf]^g$: when Algorithm~\ref{alg: ppr} is run with inputs $\Xbf, r < \frac{1}{4}\sigma,\alpha = 65 \Phi_{\Pbb,r}(\mathcal{L}[\Xbf]),v \in \mathcal{L}[\Xbf]^g$ and $(L,U) = (0,1)$, the resulting PPR cluster estimate $\widehat{C}$ satisfies
+\begin{align}
+\Phi_{n,r}(\widehat{C}) & \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi_{n,r}(\mathcal{L[X]})} \nonumber \\
+& \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}} \label{eqn:lb_pf4} 
+\end{align}
+with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2 n}{8978 \rho \sigma}} - 6 \exp\set{-\frac{1}{1123}(\cut_{\Pbb,r}(\mathcal{L}))^2n}$ (where the latter inequality follows from \eqref{eqn:lb_pf2} and Lemma~\ref{lem:graph_functional_concentration}.)
+
+\subsection{Lower bound on normalized cut.}
+
+The precise statement we will prove is contained in the following Lemma.
+\begin{lemma}
+	\label{lem:normalized_cut_lb}
+	The normalized cut $\Phi_{n,r}(A)$ is upper bounded
+	\begin{equation*}
+	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
+	\end{equation*}
+	uniformly over all $A \subset X$ with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
+\end{lemma}
+\begin{proof}
+	To lower bound the normalized cut $\Phi_{n,r}(A)$, we must lower bound $\cut_{n,r}(A)$ and upper bound $\vol_{n,r}(A)$. A naive upper bound on the volume is simply 
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf4}
+	\vol_{n,r}(A) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
+	\end{equation}
+	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this will suffice for our purposes.
+(Here and in the rest of this proof we take $\delta = 1/2$.)
+
+	We turn to lower bounding $\cut_{n,r}(A)$.
+We will approximate the cut of $A$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $A$ to the boundary of the binned set $\overline{A}$, and then lower bound the size of the boundary of $\overline{A}$.
+
+	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right hand corner of the cube
+	\begin{equation*}
+	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
+	\end{equation*}
+	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
+For a set $A \subset X$ we define the binned set $\overline{A} \subset \overline{Q}$ as follows
+	\begin{equation*}
+	\overline{A} := \set{Q \in \overline{Q}: \Pbb_n(A \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
+	\end{equation*}
+	and we let 
+	\begin{equation*}
+	\partial \overline{A} := \set{Q_{(k_1,k_2)} \in \overline{A}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \overline{A}, \norm{k - \ell}_1 = 1}.
+	\end{equation*}
+	be the boundary set of $\overline{A}$ in $\overline{Q}$.
+Intuitively, every point $x_i \in A$ in the boundary set of $\overline{A}$ will have many edges to $X\setminus A$.
+Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \mathbb{P}_n(Q)$, we have
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf1}
+	\cut_{n,r}(A) \geq \cut_{n,r}(A \cap \set{x_i \in \overline{A}}) \geq \frac{1}{4} \abs{\partial \overline{A}} Q_{\min}^2,
+	\end{equation}
+	where the last inequality follows since for every cube $Q_k \in \partial\overline{A}$, there exists a cube $Q_\ell \not\in \overline{A}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
+
+	Now we move on lower bounding the size of the boundary $\abs{\partial\overline{A}}$.
+To do so, we divide $\mathcal{X}$ into slices horizontally.
+Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\overline{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
+For each $k$, either
+	\begin{enumerate}
+		\item $\overline{R}_k \cap \overline{A} = \emptyset$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_1[\Xbf] \cap R_k), ~~ \textrm{or}
+		\end{equation*}
+		\item $\overline{R}_k \cap \overline{A} = \overline{R}_k$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_2[\Xbf] \cap R_k), ~~\textrm{or}
+		\end{equation*}
+		\item $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$.
+	\end{enumerate}
+	Let $N(R)$ be the number of slices for which $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$. By the cases elucidated above, letting
+	\begin{equation*} R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(C_1[\Xbf] \cap R_k) \wedge \vol_{n,r}(C_2[\Xbf] \cap R_k)\Bigr\}
+	\end{equation*} 
+	we obtain the following lower bound on the volume of the symmetric set difference,
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf2}
+	\vol_{n,r}(A \vartriangle C_1[\Xbf]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right].
+	\end{equation}
+	Finally note that $\abs{\partial\overline{A}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
+	\begin{align}
+	\cut_{n,r}(A) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
+	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(A \vartriangle C_1[\Xbf])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
+	\end{align}
+	for all $A \subset \Xbf$.
+
+	It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
+	To do so, we first lower bound the expected probability of any cell $Q$,
+	\begin{align*}
+	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
+	\end{align*}
+	and the expected volume of $\mathcal{C}_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\mathcal{C}_{\sigma}^{(2)}[\Xbf] \cap R_k$,
+	\begin{equation}
+	\vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
+	\end{equation}
+
+	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
+Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
+Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
+	\begin{equation*}
+	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq \frac{(1 - \delta)}{2}\frac{\pi r^3}{\sigma \rho^2 },
+	\end{equation*}
+	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
+Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
+	\begin{equation*}	
+	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
+	\end{equation*}
+	and plugging in $\delta = 1/2$ yields the claim of Lemma~\ref{lem:normalized_cut_lb}.
+\end{proof}
+
+\paragraph{Conclusion.}
+Combining \eqref{eqn:lb_pf4} and Lemma~\ref{lem:normalized_cut_lb}, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf])$ such that for any seed node $v \in \mathcal{L}[\Xbf]^g$, the following bounds hold:
+\begin{equation*}
+\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\widehat{C}) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
+\end{equation*}
+Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\mathcal{C}_{\sigma}^{(1)}[\Xbf]$:
+\begin{align*}
+\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(2)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \mathcal{C}_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
+& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}) \\
+& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])
+\end{align*}
+where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}))^2}$.
+Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$.
+
+\section{Bounding the misclassification rate.}
+\label{sec: proof_of_misclassification_rate}
+
+A common loss function for clustering is the misclassification rate.
+\begin{definition}[Misclassification rate.]
+	\label{def: symmetric_set_diff}
+	For an estimator \smash{$\Cest \subseteq \Xbf$} and set
+	$\mathcal{S} \subseteq \Reals^d$, we define   
+	\begin{equation}
+	\label{eqn: misclassification_rate}
+	\Delta_{\textrm{mc}}(\Cest, \mathcal{S}) := \abs{\Cset \vartriangle \mathcal{S}[\Xbf]},
+	\end{equation}
+	the cardinality of the symmetric set difference between 
+	\smash{$\Cest$} and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$. 
+\end{definition}
+
+In order to upper bound the misclassification rate of a PPR cluster estimate, we will need to slightly modify our approach to computing sweep cuts, and no longer normalize by degree; we formally define this modified algorithm in Algorithm~\ref{alg:ppr2}.
+Intuitively, this change helps us avoid including many low-degree vertices $w \not\in \Csig[\Xbf]$ in our estimated cluster.
+\begin{algorithm}
+	\caption{Unnormalized PPR on a neighborhood graph}
+	\label{alg:ppr2}	
+	{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
+	parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary probability
+	$\pi_0 > 0$, range $(L,U)$. \\     
+	{\bfseries Output:} cluster $\Cest \subseteq V$.
+	\begin{algorithmic}[1]
+		\STATE Form the neighborhood graph $G_{n,r}$.
+		\STATE Compute the PPR vector $p_v=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
+			ppr_vector}. 
+		\STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
+		$S_{\beta}$
+		\begin{equation}
+		\label{eqn:sweep_cuts2}
+		S_\beta := \set{u \in V: p_v(u) > \beta \pi_0}.
+		\end{equation}
+		\STATE Return as a cluster \smash{$\Cest_{\textrm{un}} = S_{\beta^*}$}, where  
+		$$
+		\beta^* = \argmin_{\beta \in (L,U)} \Phi(S_{\beta}; G_{n,r}).
+		$$
+	\end{algorithmic}
+\end{algorithm}
+
+We say Algorithm \ref{alg:ppr2} is well-initialized if $r,\alpha$ and $v$ satisfy~\eqref{eqn: initialization}, and additionally
+\begin{equation}
+\label{eqn:initialization_2}
+\pi_0 = \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\Pbb(\Csig)n}, ~~\textrm{and}~~ (L,U) \in \left(\frac{1}{100},\frac{1}{50}\right).
+\end{equation}
+
+\begin{theorem}
+	\label{thm:misclassification_rate}
+	Fix $\lambda > 0$ and suppose \smash{$\Cset \in \Cbb_f(\lambda)$} is a
+	$\kappa$-well-conditioned density cluster. If Algorithm
+	\ref{alg:ppr2} is well-initialized, there exists a universal constant $c >
+	0$ such that,
+	\begin{equation}
+	\label{eqn: misclassification_rate_ub}
+	\Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
+	\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}. 
+	\end{equation}
+	with probability at least $1 - \frac{c_1(\Pbb,r)}{n} - 2n\exp\set{-c_2(\Pbb,r)n} - 2\exp\set{-c_3(\Pbb,r)n}$.
+\end{theorem}
+
+\subsection{Proof of Theorem~\ref{thm:misclassification_rate}.}
+The proof of Theorem~\ref{thm:misclassification_rate} follows from Corollary 3.3 of \citet{zhu2013}.
+
+\paragraph{Corollary 3.3 of Zhu.}
+Let $G = (V,E)$ be an undirected, unweighted graph, let $p_v := p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$ and teleportation parameter $\alpha \in (0,1)$. 
+\begin{lemma}[Corollary 3.3 of \citet{zhu2013}.]
+	\label{cor:zhu}
+	Let $A \subseteq G$, and suppose $\alpha \leq \frac{1}{9\tau_{\infty}(G[A])}$.
+Then, there exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that the following statement holds: for any $v \in A$; the PPR vector $p_v$ satisfies
+	\begin{equation}
+	\label{eqn:zhu_1}
+	p_v(V \setminus A) \leq 2\frac{\Phi(A;G)}{\alpha}
+	\end{equation}
+	and additionally there exists a residual vector $p_{\ell} \in [0,1]^V$ with $\norm{p_{\ell}}_1 \leq \frac{2\Phi(A;G)}{\alpha}$ such that
+	\begin{equation}
+	\label{eqn:zhu_2}
+	\textrm{for all $u \in A$}, \quad p_v(u) \geq \frac{4}{5} \frac{\deg(u;G[A])}{\vol(A;G)} - p_{\ell}(u).
+	\end{equation}
+\end{lemma}
+
+\paragraph{Upper bound on $\abs{S_{\beta} \vartriangle A}$.}
+
+For given $\pi_0$ and $\beta \in (0,1)$, consider the sweep cut
+\begin{equation*}
+S_{\beta,v} := \set{u \in V: p_v(u) \geq \beta \pi_0}.
+\end{equation*}
+Suppose the conditions $\alpha \leq \frac{1}{9\tau_{\infty}(G[A])}$ and $v \in A^g$ are met. Then by~\eqref{eqn:zhu_1},
+\begin{equation}
+\label{eqn:zhu_3}
+\abs{S_{\beta,v} \setminus A} \leq \frac{p_v(V \setminus A)}{\min_{u \in S_{\beta}}p_v(u)} \leq \frac{2 \Phi(A;G)}{\alpha \beta \pi_0}. 
+\end{equation}
+To upper bound $\abs{A \setminus S_{\beta}}$, note that for every $u \in A \setminus S_{\beta}$, $p_v(u) \leq \beta \pi_0$. Therefore by~\eqref{eqn:zhu_2},
+\begin{equation*}
+p_{\ell}(u) \geq \frac{4\deg(u;G[A])}{5\vol(A;G)} - \beta\pi_0, \textrm{for all $u \in A \setminus S_{\beta}$}
+\end{equation*}
+Since additionally $\norm{p_{\ell}}_1 \leq 2\Phi(S;G)/\alpha$, we have
+\begin{align}
+\sum_{u \in A \setminus S_{\beta,v}} \left(\frac{4\deg(u;G[A])}{5\vol(A;G)} - \beta\pi_0\right) & \leq \frac{2\Phi(S;G)}{\alpha} \nonumber \Longrightarrow\\
+\abs{A \setminus S_{\beta,v}}\underbrace{\left(\frac{4\min_{u \in A}\deg(u;G[A])}{\abs{A}5\max_{u \in A}\deg(u;G)} - \beta\pi_0\right)}_{:=T_1(A;G)} & \leq \frac{2\Phi(S;G)}{\alpha} \Longrightarrow \nonumber \\
+\abs{A \setminus S_{\beta,v}} \leq \frac{2\Phi(S;G)}{\alpha T_1(A;G)} .
+\label{eqn:zhu_4}
+\end{align}
+
+\paragraph{Bounds on graph functionals for $G_{n,r}$.}
+
+To apply~\eqref{eqn:zhu_3} and~\eqref{eqn:zhu_4} when $G = G_{n,r}$ and $A = \Csig[\Xbf]$, we need to verify the condition $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, and additionally upper bound $\Phi_{n,r}(\Csig[\Xbf])$ and $T_1(G_{n,r}; \Csig[\Xbf])$.
+We now state the necessary upper bounds, and the probability with which they hold:
+\begin{itemize}
+	\item Since $\alpha < \frac{1}{9\tau_u(\Csig)}$, by Theorem~\ref{thm: mixing_time_upper_bound} 
+	\begin{equation*}
+	\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})},
+	\end{equation*}
+	with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$. 
+	\item  By Theorem~\ref{thm: conductance_upper_bound}, 
+	\begin{equation*}
+	\Phi_{n,r}(\Csig[\Xbf]) \leq \Phi_{u}(\Csig) 
+	\end{equation*}
+	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)^2\}$. 
+	\item By Lemma~\ref{lem:ball_bounds_in_probability},
+	\begin{equation*}
+	\frac{\min_{u \in \Csig[\Xbf]}\widetilde{\deg}_{n,r}(u)}{\max_{u \in \Csig[\Xbf]}\deg_{n,r}(u)}= \frac{\degminwt}{\degmax} \geq \frac{(1 - \delta)6\lambda_{\sigma}}{(1+\delta)25\Lambda_{\sigma}},
+	\end{equation*}
+	and
+	\begin{equation*}
+	\abs{\Csig[\Xbf]} \leq (1 + \delta)n\Pbb(\Csig[\Xbf])
+	\end{equation*}
+	all with probability at least $1 - 2n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}} - 2\exp\set{-2\delta^2 \Pbb(\Csig)^2}$.
+These bounds along with the initialization conditions~\eqref{eqn:initialization_2} imply
+	\begin{align}
+	T_1(G_{n,r}, \Csig[\Xbf]) & \geq \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\abs{\Csig[\Xbf]}}\left(\frac{(1 - \delta)6}{(1+\delta)25} - (1 + \delta)\beta\right) \nonumber \\
+	& \geq \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\abs{\Csig[\Xbf]}}\left(\frac{(1 - \delta)6}{(1+\delta)25} - \frac{(1 + \delta)}{50}\right). \label{eqn:misclassification_rate_pf1}
+	\end{align}
+\end{itemize}
+We assume these high probability bounds are satisfied with $\delta = \frac{1}{2}$ and move on to upper bounding $\Delta_{\textrm{mc}}(\widehat{C}_{\textrm{un}}, \Csig[\Xbf])$.
+
+\paragraph{Upper bound on misclassification rate.}
+Since $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, we may apply Lemma~\ref{cor:zhu} to the graph $G_{n,r}$ and subset $\Csig[\Xbf]$.
+Combined with the inequalities we've already derived, this implies the following: there exists a subset $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]) \leq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that the following bounds hold,
+\begin{equation*}
+\abs{S_{\beta,v} \setminus \Csig[\Xbf]} \leq \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \beta \pi_0} \leq \frac{2000 \kappa(\Cset)}{\pi_0} \leq \frac{4000 \kappa(\Cset) \Lambda_{\sigma}}{\lambda_{\sigma}}\abs{\Csig[\Xbf]},
+\end{equation*}
+and
+\begin{equation*}
+\abs{\Csig[\Xbf] \setminus S_{\beta,v}} \leq \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha T_1(\Csig[\Xbf];G_{n,r})} \leq \frac{1000 \kappa(\Cset) \Lambda_{\sigma}}{\lambda_{\sigma}}\abs{\Csig[\Xbf]}.
+\end{equation*}
+This completes the proof of Theorem~\ref{thm:misclassification_rate}.
+
+\section{Probabilistic bounds}
+\label{sec: concentration}
+
+In our theory, we frequently appeal to concentration of graph functionals such as degree, volume, and cut size around their means.
+In this section, we establish such concentration inequalities.
+We begin with Lemma~\ref{lem:hoeffding}, Hoeffding's inequality, which we will use to bound the empirical probability of a fixed set.
+\begin{lemma}[Hoeffding's Inequality.]
+	\label{lem:hoeffding_2}
+	Let $\mathcal{A}$ be a subset of $\Reals^d$. Then,
+	\begin{equation*}
+	(1 - \delta) \Pbb(\mathcal{A}) \leq \Pbb_n(\mathcal{A}) \leq (1 + \delta)\Pbb(\mathcal{A})
+	\end{equation*}
+	with probability at least $1 - \exp\set{-2\delta^2(\Pbb(\mathcal{A}))^2}$. 
+\end{lemma}
+
+To bound minimum and maximum degrees, we will use Lemma~\ref{lem:bernstein_union}, which is a combination of Bernstein's inequality and a union bound.
+
+\begin{lemma}[Bernstein's inequality + Union bound.]
+	\label{lem:bernstein_union}
+	For $M \geq 1$, let $\mathcal{A}_1,\ldots,\mathcal{A}_M$ be subsets of $\Reals^d$.
+Denote the minimum probability mass among these sets as $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$.
+Then
+	\begin{equation*}
+	(1 - \delta)p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq (1 + \delta)p_{\max}
+	\end{equation*}
+	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.  
+\end{lemma}
+The above Lemma will allow us to upper and lower bound the minimum and maximum degrees within the neighborhood graphs $G_{n,r}$ and $\widetilde{G}_{n,r}$.
+To bound cut size and volume functionals, we will use Hoeffding's inequality for U-statistics.
+Recall that $U_n$ is an order-2 U-statistic with kernel $h: \Rd \times \Rd \to \Reals$ if
+\begin{equation*}
+U_n = \frac{1}{2{n \choose 2}}\sum_{i = 1}^{n} \sum_{j \neq i} h(x_i,x_j).
+\end{equation*}
+\begin{lemma}[Hoeffding's Inequality for U-statistics.]
+	\label{lem:hoeffding}
+	Assume $\norm{h}_{\infty} \leq 1$. Then,
+	\begin{equation*}
+	(1 - \delta) \mathbb{E}(U_m) \leq U_n \leq (1 + \delta) \mathbb{E}(U_m).
+	\end{equation*}
+	with probability at least $1 - 2 \exp\left(-\delta^2 (\mathbb{E}(U_m))^2 n\right)$.
+\end{lemma}
+
+We collect the bounds on graph functionals we need in Lemma~\ref{lem:ball_bounds_in_probability}.
+Let $S \subset X$ and $\mathcal{S} \subseteq \Rd$.
+As a reminder, for notational ease we write $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$ and
+\begin{alignat*}{2}
+\widetilde{d}_{\min} & = \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u), \quad && d_{\min}' = \min_{u' \in \Cset'[\Xbf]} {\deg}_{n,r}(u') \\
+d_{\max} & = \max_{u \in \Csig[\Xbf]} \deg_{n,r}(u), \quad && \widetilde{\vol}_{n,r}(S) = \vol(S; \widetilde{G}_{n,r}). 
+\end{alignat*}
+Additionally, let $\widetilde{\vol}_{\Pbb,r}(\mathcal{S}) := \frac{1}{2{n \choose 2}}\mathbb{E}[\widetilde{\vol}_{n,r}(\mathcal{S}[\Xbf])]$.
+\begin{lemma}
+	\label{lem:ball_bounds_in_probability} \label{lem:graph_functional_concentration}
+	\item[]
+	The following statements hold for any $\delta \in (0,1)$:
+
+	\noindent With probability at least $1 - 2\exp\{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\mathcal{S}))^2\}$,
+	\begin{equation}
+	\label{eqn:volwt_bound}
+	(1 - \delta) \widetilde{\vol}_{\Pbb,r}(\mathcal{S}) \leq \frac{\widetilde{\vol}_{n,r}(\mathcal{S}[\Xbf])}{2{n \choose 2}} \leq (1 + \delta) \widetilde{\vol}_{\Pbb,r}(\mathcal{S}).
+	\end{equation}
+	With probability at least $1 - 2\exp\set{-n \delta^2 \vol_{\Pbb,r}(\Sset)^2}$,
+	\begin{equation}
+	\label{eqn:vol_bound}
+	(1 - \delta)\vol_{\Pbb,r}(\Sset) \leq \frac{\vol_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq 2(1 + \delta)\vol_{\Pbb,r}(\Sset).
+	\end{equation}
+	With probability at least $1 - 2\exp\set{-n \delta^2 \cut_{\Pbb,r}(\Sset)^2}$,
+	\begin{equation}
+	\label{eqn:cut_bound}
+	(1 - \delta)\cut_{\Pbb,r}(\Sset) \leq \frac{\cut_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq (1 + \delta)\vol_{\Pbb,r}(\Sset).
+	\end{equation}
+	With probability at least $1 - 2\exp\{-n\delta^2\Pbb(\Csig)^2\}$, 
+	\begin{equation}
+	\label{eqn:cardinality}
+	(1 - \delta) \Pbb(\Csig) \leq \abs{\Csig[\Xbf]} \leq (1 + \delta) \Pbb(\Csig).
+	\end{equation}
+
+	\noindent The following statements hold for any $0 < r < \frac{\sigma}{2\sqrt{d}}$:
+
+	\noindent Assuming $\Csig$ satisfies~\ref{asmp: bounded_density}, with probability at least $1 - 2n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$,
+	\begin{equation}
+	\label{eqn:degwt_bound}
+	\frac{6}{25}(1 - \delta)\lambda_{\sigma}\nu_dr^dn \leq \degminwt \leq d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_dr^dn.
+	\end{equation}
+	Assuming $\Cset'$ satisfies~\ref{asmp: C'_bounded_density}, with probability at least $1 - n\exp\set{-\frac{\delta^2 \lambda_{\sigma} \nu_d r^d n}{3(1 + \frac{\delta}{3})}}$,
+	\begin{equation}
+	\label{eqn:degpr_bound}
+	\degminpr \geq (1 - \delta)\lambda_{\sigma}\nu_dr^dn.
+	\end{equation}
+\end{lemma}
+\begin{proof}{(of Lemma~\ref{lem:ball_bounds_in_probability})}
+	\item[]
+	\paragraph{Proof of \eqref{eqn:degwt_bound}, \eqref{eqn:degpr_bound}:}
+	Under~\ref{asmp: bounded_density}, we have that for every $x_j \in \Csig[\Xbf]$
+	\begin{equation*}
+	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j)) \leq \Lambda_{\sigma} \nu_d r^d;
+	\end{equation*}
+	furthermore, recalling the weighted local conductance $\ell_{\Pbb,r}(x) = \Pbb(B(x,r) \cap \Csig)$, we have,
+	\begin{equation*}
+	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j)) = \ell_{\Pbb,r}(x_j) \geq \frac{6}{25} \lambda_{\sigma} \nu_d r^d
+	\end{equation*}
+	where the last inequality follows from Lemma~\ref{lem: local_conductance}.  Under~\ref{asmp: C'_bounded_density} we have for every $x_i \in \Cset'[\Xbf]$
+	\begin{equation*}
+	\mathbb{E}(\widetilde{\deg}_{n,r}(x_i)) \geq \lambda_{
+		\sigma} \nu_d r^d.
+	\end{equation*} 
+	Then \eqref{eqn:degwt_bound} and \eqref{eqn:degpr_bound} each follow from Lemma~\ref{lem:bernstein_union}.
+
+	\paragraph{Proof of \eqref{eqn:volwt_bound}, \eqref{eqn:vol_bound}, \eqref{eqn:cut_bound}:}
+
+	We have that $\frac{1}{2{n \choose 2}}\widetilde{\vol}_{n,r}(\Csig[\Xbf])$, $\frac{1}{2{n \choose 2}}\vol_{n,r}(\Sset[\Xbf])$, $\frac{1}{2{n \choose 2}}\cut_{n,r}(\Sset[\Xbf])$ are each order-2 U statistics, with respective kernels
+	\begin{align*}
+	h_{\widetilde{\vol}}(x_i,x_j) & = \1(x_i \in \Csig)\1(x_j \in \Csig)\1(\norm{x_i - x_j} \leq r), \\ h_{\cut}(x_i,x_j) & = \1(x_i \in \Csig)\1(x_j \notin \Csig)\1(\norm{x_i - x_j} \leq r) \\
+	h_{\vol}(x_i,x_j) & = \1(x_i \in \Csig)\1(\norm{x_i - x_j} \leq r).
+	\end{align*}
+	We may therefore apply Lemma~\ref{lem:hoeffding} in each case to obtain the stated bounds.
+
+	\paragraph{Proof of \eqref{eqn:cardinality}:}
+	Apply Lemma~\ref{lem:hoeffding_2} to $\Csig$.
 \end{proof}

### 2019-11-03 arxiv/local_spectral_density_clustering_arxiv.tex
few typos fixed

@@
 	\end{equation*}
-	then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+	then $\Delta(\widehat{C}, \Csig^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\Csig^{(1)}[\Xbf])$.
 	\item If the user-specified parameters are given as in Theorem~\ref{thm:ppr_lb}, and 
@@
 	\end{equation*}
-	then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+	then $\Delta(\widehat{C}, \Csig^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\Csig^{(1)}[\Xbf])$.
 \end{itemize}
@@
 particular interest is the fact that PPR fails to recover one of the moons even
-when normalized cut still succeeds in doing so. Additionally, we note that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.  While our main message was
-that PPR recovers geometrically well-conditioned density clusters, it would be  
-interesting to establish that it \emph{only} recovers such clusters, a direction
-for future work.
+when normalized cut still succeeds in doing so.
+Additionally, we note that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.
+This supports our main message, which is that PPR recovers only geometrically well-conditioned density clusters.
 

### 2019-11-04 arxiv/local_spectral_density_clustering_arxiv.tex
just testing

@@
 	We also note that our lower bound is of course specific to the PPR algorithm.
-As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
+As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$ \sbcomment{small?}.
 That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.

### 2019-11-07 arxiv/local_spectral_density_clustering_arxiv.tex
siva's updates

@@
 \begin{center}
-Alden Green ~~~~~ Sivaraman Balakrishnan~~~~~ Ryan Tibshirani\\
+Alden Green~~~~~ Sivaraman Balakrishnan~~~~~ Ryan Tibshirani\\
 \vspace{.2cm}
@@
 which extracts clusters using locally-biased random walks around a user-specified
-seed node.  In contrast to previous work, we adopt a traditional statistical
+seed node.  In contrast to previous work, we adopt a classical statistical
 learning setup, where we obtain samples from an unknown distribution, and aim to
@@
 PPR, run on a neighborhood graph, extracts sufficiently salient density
-clusters, and conversely fails to recover geometrically poorly conditioned density clusters. We also provide empirical support to illustrate our theoretical results.
+clusters. We also show a surprising converse result, that PPR can fail 
+to recover geometrically poorly conditioned density clusters, even asymptotically. Finally, we provide empirical support to illustrate our theoretical results.
 \end{abstract}
@@
 $G$, and applies a simple clustering
-technique (like $k$-means clustering) in the embedded feature space.
+technique (like $k$-means clustering) in the embedded feature~space.
 
@@
 \citep{leskovec2010,mahoney2012}.  This has led to increased interest in
-local spectral clustering algorithms, which leverage locally-biased spectra
+\emph{local} spectral clustering algorithms, which leverage locally-biased spectra
 computed using random walks around some user-specified seed node.  A popular 
@@
 and examine what the output of local clustering on a data set reveals about the
-underlying density of the samples 
-$f$.  In particular, we examine the ability of PPR to recover
+underlying density $f$ of the samples.  In particular, we examine the ability of PPR to recover
 \emph{density clusters} of $f$, defined as the connected components of
@@
 
-\subsection{Sweep cut.}
+\subsubsection{Sweep cut}
 \label{subsection: sweep_cut}
-
-We employ the sweep cut method to obtain a local cluster from the PPR embedding $\pbf_v$. For a level $\beta > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$
+We employ the sweep cut method to obtain a local cluster from the PPR embedding $\pbf_v$.
+In more detail, for a level $\beta > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$
 as   
@@
 The ability of spectral algorithms to perform clustering -- community detection-- in this context is well-understood.
-In particular, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM,  \citet{lei2015} extend these results to the sparse (low average degree) regime, and \citet{balakrishnan2011} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+\sbcomment{Add reference to McSherry -- spectral partitioning...} In particular, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM,  \citet{lei2015} extend these results to the sparse (low average degree) regime, and \citet{balakrishnan2011} analyze the misclassification rate when the block model exhibits some hierarchical structure
+\sbcomment{add reference to Cris Moore, Newman et.
+al., and Liza Levina, Bickel, Sarkar have a recent paper that looks at this same hierarchical model}.
 The framework we consider, where nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
@@
 To do so, we rely on a series of seminal works upper bounding the mixing time of \emph{geometric random walks} (see \citet{vempala2005} for a comprehensive review.)  This study was initiated by \citet{dyer1991}, who used geometric random walks as a fundamental subroutine to efficiently compute volumes of high-dimensional convex bodies.
-These results are improved in \citet{lovasz1990,kannan97,kannan06}, who show \textit{inter alia} that the bounds on mixing time can be sharpened by avoiding so-called ``start-penalties''.(These improvements are crucial to our work, for they allow us to avoid factors of $\log n$ which would imply divergence as $n \to \infty$.) Following the lead of \citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold for Lipschitz deformations of convex sets.
+These results are improved in \citet{lovasz1990,kannan97,kannan06}, who show, inter alia, that the bounds on mixing time can be sharpened by avoiding so-called ``start-penalties''.
+As we discuss further in the sequel, these improvements are crucial to our work.
+Following the work of \citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold for Lipschitz deformations of convex sets.
 Additionally, we relate the mixing time of these (continuous-space) geometric random walks to the mixing time of random walks over (discrete) neighborhood graphs.
+\sbcomment{Refer to and add a couple of lines about the paper of Zhu et al.}
 
@@
 minimax optimal level-set estimators under Hausdorff loss and
-\citet{hartigan1981, chaudhuri2010, balakrishnan2013} consider consistent estimation of the
+\citet{hartigan1981, chaudhuri2010, balakrishnan2013} \sbcomment{Add reference to Kpotufe, von Luxburg} consider consistent estimation of the
 cluster tree.
@@
   $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
-  will consistently estimate a density cluster in the sense of
-  \eqref{eqn: consistent_density_cluster_recovery}.
+  will consistently estimate a density cluster in a strong sense (see~\eqref{eqn: consistent_density_cluster_recovery}).
 
 \item In Section \ref{sec: analysis}, we detail some of the analysis required to
-  prove our main results, and expose the parts various geometric quantities play 
+  prove our main results, and expose the roles that various geometric quantities play 
   in the difficulty of the clustering problem.
@@
 PPR, run on a neighborhood graph, recovers only \emph{geometrically
-compact} high-density clusters. Our main theoretical results, make this takeaway 
-precise, and provide concrete ways of quantifying the geometric
+compact} high-density clusters. Our main theoretical results, makes this takeaway 
+precise, and provides concrete ways of quantifying the geometric
 compactness of a density cluster.
@@
 
-  We assume that neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
+  We assume that the neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
   \begin{equation*}
@@
 We now present our first main result: a bound on the volume of the symmetric set difference between the estimated cluster $\widehat{C}$ and empirical cluster $\Csig[\Xbf]$. 
+In this theorem, and hereafter, we let 
+$c, c_i > 0$ represent universal constants, and 
+$c_i(\Pbb,r)$ represent constants which depend only on $\Pbb$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
 \begin{theorem}
@@
   Fix $\lambda > 0$ and let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-  $\kappa$-well-conditioned density cluster for some $\sigma > 0$.
-If Algorithm \ref{alg: ppr} is \emph{well-initialized} with respect to $\Cset$, then there exists a universal constant $c > 0$, constants in sample size $c_1(\Pbb,r)$ - $c_6(\Pbb,r)$, and a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that the following statement holds: let Algorithm~\ref{alg: ppr} be run with any seed node $v \in \Csig[\Xbf]^g$.
+  $\kappa$-well-conditioned density cluster for some $\sigma > 0$. If Algorithm \ref{alg: ppr} is \emph{well-initialized} with respect to $\Cset$, then 
+  %there exists a universal constant $c > 0$, constants in sample size $c_1(\Pbb,r)$ - $c_6(\Pbb,r)$, and 
+  there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume 
+  with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that the following statement holds: let Algorithm~\ref{alg: ppr} be run with any seed node $v \in \Csig[\Xbf]^g$.
 Then, for any $n$ large enough so that
@@
 \end{theorem}
+\sbcomment{At this point not sure why you need so many different constants. I would in general assume that $d$ is a constant. Can you not just write for 
+$n \geq c_1(\Pbb,r)  (\log n)^{\max\{\frac{3}{d},1\}}$, with probability at least $1 - c_2(\Pbb,r)/n$ blah...?}
 The proof of Theorem \ref{thm:volume_ssd} is deferred to Appendix~\ref{sec:proof_of_volume_ssd}. 
-In this theorem, and hereafter, we let $c, c_i > 0$ represent universal constants, and $c_i(\Pbb,r)$ represent constants which depend only on $\Pbb$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
 This result shows that the volume of the symmetric set difference \smash{$\Delta(\Csig[\Xbf],
@@
 measured by the condition number $\kappa(\Cset)$.
+\sbcomment{Not completely clear what you are doing above Zhu et.
+al.
+Perhaps emphasize again that the technical work is in showing that $\tau_u$ and $\phi_u$ are valid upper bounds on the normalized cut and mixing time, and once
+this is established the result follows from Zhu et al.? (unless I am missing something) }
 
@@
 The bound on symmetric set difference \eqref{eqn:volume_ssd} does not imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over $\pbf$: as an example, for all \smash{$\Cset'
+This notion of consistency requires a uniform bound over
+the PPR vector $\pbf_v$: as an example, suppose that we were able to show that for all \smash{$\Cset'
   \in \Cbb_f(\lambda), \Cset' \neq \Cset$}, and each $u \in \Cset, w \in
@@
   additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$ and constants in sample size $c_1(\Pbb,r)$-$c_6(\Pbb,r)$ such that if  
+  \ref{alg: ppr} is well-initialized and if 
+  %, there exists a universal constant $c >  0$ and constants in sample size $c_1(\Pbb,r)$-$c_6(\Pbb,r)$ such that if  
   \begin{equation}
@@
 \end{theorem}
+\sbcomment{Same suggestion about removing unnecessary constants in the statement of the theorem. You can leave them in the proof.}
 \noindent Some remarks are in order: 
@@
 Appendix~\ref{sec:appr}.
+\sbcomment{Maybe we should discuss approximate PPR briefly in the Background section -- and just state the corollary here (not in a separate section).}
 
@@
 $G_{n,r}$. In doing so, we elaborate on how some of the geometric conditions
-introduced in Section \ref{sec: consistent_cluster_estimation_with_ppr}
+introduced in Section~\ref{sec: consistent_cluster_estimation_with_ppr}
 contribute to the difficulty of the clustering problem.
@@
 \end{theorem}
-
+\sbcomment{Same comment about constants.}
 The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
@@
 so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_{\sigma}^{(1)}, \mathcal{C}_{\sigma}^{(2)}}$. 
+\sbcomment{Maybe a figure would be helpful.}
 
@@
 \end{theorem}
-
-Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
+\sbcomment{Same comment about eliminating constants.}
+Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, \sbcomment{Isn't there something strange about this comment -- where the factor of $n^2$ go?} which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
 
@@
 In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Cset_1$.
-In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus it stands to reason that all the aforementioned approaches should struggle to estimate $\Csig^{(1)}[\Xbf]$.
+In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that all the aforementioned approaches would fail to estimate $\Csig^{(1)}[\Xbf]$.
 
@@
 
-\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners.
-To fix this, one can either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume} in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with respect to rectangles of width $\sigma$, or change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
-As these details do not meaningfully change our conclusions, for simplicity we will keep our upper and lower bounds as is.
+\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners. To fix this, one can 
+%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume} in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with respect to rectangles of width $\sigma$, or 
+change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
+With some additional bookkeeping, using rounded rectangles does not change our lower bound significantly so we ignore this technicality in our
+subsequent discussion.
 \end{remark}
@@
 \end{remark}
+
+\sbcomment{Sometimes you make remarks in a remark environment (so it is italicized) and sometimes not. Can you use the same format throughout? I have a preference for \emph{not} italicizing. }
 
@@
 dimensions.\footnote{We rescaled all values of theoretical upper
-  bounds by a constant, tto mask the effect of large universal constants
+  bounds by a constant, to mask the effect of large universal constants
   in these bounds. Therefore only the comparison of slopes, rather than

### 2019-11-10 arxiv/local_spectral_density_clustering_arxiv.tex
Updated per Siva comments

@@
 In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
-The ability of spectral algorithms to perform clustering -- community detection-- in this context is well-understood.
-\sbcomment{Add reference to McSherry -- spectral partitioning...} In particular, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM,  \citet{lei2015} extend these results to the sparse (low average degree) regime, and \citet{balakrishnan2011} analyze the misclassification rate when the block model exhibits some hierarchical structure
-\sbcomment{add reference to Cris Moore, Newman et.
-al., and Liza Levina, Bickel, Sarkar have a recent paper that looks at this same hierarchical model}.
+The ability of spectral algorithms to perform clustering -- community detection-- in this context is well-understood, dating back to \citet{mcsherry2001} who gives conditions under which the entire community structure can be recovered.
+In more recent work, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM and \citet{lei2015} extend these results to the sparse (low average degree) regime.
+Relatedly, \citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate when the block model exhibits some hierarchical structure.
 The framework we consider, where nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
@@
 
-A substantial portion of our technical effort involves estimating graph-theoretic connectivity properties of empirical density clusters in the neighborhood graph $G_{n,r}$.
+Our analysis naturally builds on a few of the aforementioned theoretical analyses of PPR.
+For an arbitrary graph $G$ and subset $S \subset G$, \citet{andersen2006} relate the quality of the PPR cluster $\hat{C}$ to the normalized cut functional $\Phi(S;G)$.
+While this analysis is tight, it fails to account for improvements possible when the cluster $S$ is additionally assumed to be internally well-connected, which is intuitively a more favorable case for clustering.
+Building on this intuition, \citet{zhu2013} assume that the subgraph $G[S]$ is internally well-connected-- measured by a functional such as mixing time of a random walk over $G[S]$-- and prove upper bounds on $\vol(\widehat{C} \vartriangle S;G)$.
+Both of these analyzes hold with respect to a approximate form of PPR (APPR) which can be efficiently computed.
+
+We apply these results to our setting by estimating these functionals in the particular case of $G = G_{n,r}$ and $S = \mathcal{C}[X]$.
 In particular, we prove an upper bound on the mixing time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall within a density cluster $\Cset$.
@@
 Additionally, we relate the mixing time of these (continuous-space) geometric random walks to the mixing time of random walks over (discrete) neighborhood graphs.
-\sbcomment{Refer to and add a couple of lines about the paper of Zhu et al.}
 
@@
 minimax optimal level-set estimators under Hausdorff loss and
-\citet{hartigan1981, chaudhuri2010, balakrishnan2013} \sbcomment{Add reference to Kpotufe, von Luxburg} consider consistent estimation of the
+\citet{hartigan1981, chaudhuri2010, balakrishnan2013,kpotufe11} consider consistent estimation of the
 cluster tree.
@@
 $c, c_i > 0$ represent universal constants, and 
-$c_i(\Pbb,r)$ represent constants which depend only on $\Pbb$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
+$c(\Pbb,r), c_i(\Pbb,r) > 0$ represent constants which may depend on $\Pbb,\lambda$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
 \begin{theorem}
@@
   \begin{equation*}
-  n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\},
+  n \geq c_1(\Pbb,r)\cdot (\log n)^{\max\{\frac{3}{d},1\}}
   \end{equation*}
@@
   \end{equation}
-  with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$. 
+  with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$. 
 \end{theorem}
-\sbcomment{At this point not sure why you need so many different constants. I would in general assume that $d$ is a constant. Can you not just write for 
-$n \geq c_1(\Pbb,r)  (\log n)^{\max\{\frac{3}{d},1\}}$, with probability at least $1 - c_2(\Pbb,r)/n$ blah...?}
 The proof of Theorem \ref{thm:volume_ssd} is deferred to Appendix~\ref{sec:proof_of_volume_ssd}.
-This result shows that the volume of the symmetric set difference \smash{$\Delta(\Csig[\Xbf],
+We reiterate that the primary technical work involved in proving Theorem~\ref{thm:volume_ssd} involves showing that $\tau_{u}$ and $\phi_u$ are valid upper bounds on the normalized cut and mixing time; once this is established, the result follows more or less straightforwardly from~\citet{zhu2013}.
+This result establishes that the volume of the symmetric set difference \smash{$\Delta(\Csig[\Xbf],
   \Cest)$} is upper-bounded by a quantity proportional to the difficulty of the clustering problem, as
 measured by the condition number $\kappa(\Cset)$.
-\sbcomment{Not completely clear what you are doing above Zhu et.
-al.
-Perhaps emphasize again that the technical work is in showing that $\tau_u$ and $\phi_u$ are valid upper bounds on the normalized cut and mixing time, and once
-this is established the result follows from Zhu et al.? (unless I am missing something) }
 
@@
   additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized and if 
+  \ref{alg: ppr} is well-initialized with respect to $\Cset$ and if 
   %, there exists a universal constant $c >  0$ and constants in sample size $c_1(\Pbb,r)$-$c_6(\Pbb,r)$ such that if  
@@
   \end{equation}
-  then $\Cest$ satisfies~\eqref{eqn: consistent_density_cluster_recovery} with respect to $\Cset$ with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$.
+  then the following statement holds: there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume 
+  with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that if Algorithm~\ref{alg: ppr} is run with any seed node $v \in \Csig[\Xbf]^g$,  then for any $n$ large enough so that
+  \begin{equation*}
+  n \geq c_1(\Pbb,r)\cdot (\log n)^{\max\{\frac{3}{d},1\}}
+  \end{equation*}$\Cest$ satisfies~\eqref{eqn: consistent_density_cluster_recovery} with respect to $\Cset$ with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$.
 Therefore, $\Cest$ is a consistent estimator of $\Cset$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
 \end{theorem}
-\sbcomment{Same suggestion about removing unnecessary constants in the statement of the theorem. You can leave them in the proof.}
 \noindent Some remarks are in order: 
@@
 application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters}
-leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}. We
-formally state and prove this in Corollary~\ref{cor: appr} in 
-Appendix~\ref{sec:appr}.
-\sbcomment{Maybe we should discuss approximate PPR briefly in the Background section -- and just state the corollary here (not in a separate section).}
+leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}.
+
+\begin{corollary}
+	\label{cor: appr}
+	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster for some $\sigma > 0$.
+Choose input parameters $r, \alpha, v, (L,U)$ to be well-initialized in the sense of \eqref{eqn: initialization}, additionally set
+	\begin{equation}
+	\label{eqn: appr_parameter}
+	\varepsilon = \frac{1}{25}\vol_{\Pbb,r}(\Csig)
+	\end{equation}
+	and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}_v$ rather than the exact \pprspace vector $\pbf_v$, with resulting output $\Cest$. Then
+	\begin{enumerate}
+		\item The upper bound on symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ given by \eqref{eqn:volume_ssd} is still valid.
+		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
+		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+	\end{enumerate}
+\end{corollary}
 
@@
   Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
-  \ref{asmp: bounded_volume} for some $\sigma > 0$. Then there exists a universal constant $c_1 > 0$ and a constant in sample size $c_1(\Pbb,r)$ such that
+  \ref{asmp: bounded_volume} for some $\sigma > 0$. Then
   \begin{equation}
@@
   \end{equation}
-  with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$. 
+  with probability at least $1 - 3\exp\{-nc_3(\Pbb,r)\}$. 
 \end{theorem}
@@
   satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
-  for some $\sigma > 0$.
-Additionally assume that the radius $0 < r < \sigma/2\sqrt{d}$.
-Then there exist universal constants $c_2$ and $c_3$, and constants in sample size $c_2(\Pbb,r)$ - $c_6(\Pbb,r)$ such that the following statement holds: for any
-  \begin{equation*}
-  n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\}
+  for some $\sigma > 0$. Additionally assume that the radius $0 < r < \sigma/2\sqrt{d}$. Then the following statement holds: for any
+  \begin{equation*}
+  n \geq c_1(\Pbb,r)\cdot(\log n)^{\max\{\frac{3}{d},1\}}
   \end{equation*}
@@
   \end{equation}
-  with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$.
+  with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
 \end{theorem}
-\sbcomment{Same comment about constants.}
 The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
@@
 so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_{\sigma}^{(1)}, \mathcal{C}_{\sigma}^{(2)}}$.
-\sbcomment{Maybe a figure would be helpful.}
+Figure~\ref{fig:fig0} shows $f$ for two different choices of $\epsilon, \sigma$ and $\rho$.
+
+\begin{figure}[tb]
+	\centering
+
+	\includegraphics[width=0.4\textwidth]{lower_bound_plots/lower_bound_1}
+	\includegraphics[width=0.4\textwidth]{lower_bound_plots/lower_bound_2}
+
+	\caption{\it\small The density $f$ given by~\eqref{eqn:lb_density}, for two different choices of $\epsilon$ and $\sigma$.
+Left: $\epsilon = .3,\sigma = .1$; Right: $\epsilon = .2,\sigma = .2$.
+In both $\rho = 1$.
+}
+	\label{fig:fig0}
+
+\end{figure}
 
@@
 	\end{equation}
-	with probability at least $1 - c_1(\Pbb,r) n \exp\set{-c_2(\Pbb,r)n}$, where $c$ is a universal constant and $c_1(\Pbb,r),c_2(\Pbb,r)$ are constants which do not depend on $n$.
+	with probability at least $1 - c_1(\Pbb,r) n \exp\set{-c_2(\Pbb,r)n}$.
 	Consequently, if
@@
 \end{theorem}
-\sbcomment{Same comment about eliminating constants.}
-Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, \sbcomment{Isn't there something strange about this comment -- where the factor of $n^2$ go?} which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
+Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
 
@@
 Additionally, although we state our lower bound with respect to PPR run on neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
-In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\frac{\sigma}{\rho}$, the normalized cut of $\Cset_1$ will be much larger than that of $\mathcal{L}$.
-In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Cset_1$.
-In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that all the aforementioned approaches would fail to estimate $\Csig^{(1)}[\Xbf]$.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\frac{\sigma}{\rho}$, the normalized cut of $\Csig^{(1)}$ will be much larger than that of $\mathcal{L}$.
+In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Csig^{(1)}$.
+In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that all the aforementioned approaches would fail to estimate $\Csig^{(1)}$.
 
@@
 
-\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners. To fix this, one can 
+\vspace{0.2cm}
+
+\textbf{Remark:}~~Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners. To fix this, one can 
 %either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume} in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with respect to rectangles of width $\sigma$, or 
@@
 subsequent discussion.
-\end{remark}
+
+\vspace{0.2cm}
 
@@
 
-\begin{remark}
-	It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+\vspace{0.2cm}
+
+\textbf{Remark:}~~It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
 We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
-\end{remark}
 
@@
 
-\begin{remark}
-	We also note that our lower bound is of course specific to the PPR algorithm.
-As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$ \sbcomment{small?}.
+\vspace{0.2cm}
+
+\textbf{Remark:}~~We also note that our lower bound is of course specific to the PPR algorithm.
+As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
 That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
 Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
-\end{remark}
-
-\sbcomment{Sometimes you make remarks in a remark environment (so it is italicized) and sometimes not. Can you use the same format throughout? I have a preference for \emph{not} italicizing. }
 
@@
 \end{figure}
-
 \paragraph{Validating theoretical bounds.}  We investigate the tightness of
@@
 \end{equation*}
-Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $c_1(\Pbb,r) = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
+Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $c_3(\Pbb,r) = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
 
@@
 	\label{prop: local_spread_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_2(\Pbb,r)$, $c_3(\Pbb,r)$, and $c_4(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_2(\Pbb,r)}\right)^d, c_3(\Pbb,r)\right\}
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_5(\Pbb,r)$,$c_6(\Pbb,r)$, and $c_7(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_{5}(\Pbb,r)}\right)^d, c_{6}(\Pbb,r)\right\}
 	\end{equation*}
@@
 	\end{equation}
-	hold with probability at least $1 - \frac{c_3(\Pbb,r)}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
+	hold with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
 \end{proposition}
@@
 \end{align*}
-whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, $c_4(\Pbb,r) := \frac{2\lambda_{\sigma} \nu_d r^d}{1875}$ and $c_5(\Pbb,r) := \frac{2}{25}(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$.
+whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, and constants $c_{4}(\Pbb,r) := c_7(\Pbb,r) + \frac{7500}{\lambda_{\sigma}\nu_dr^d} + 25(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$ and $c_1(\Pbb,r) = \frac{1}{c_5(\Pbb,r)^d} + c_6(\Pbb,r)$.
 In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
@@
 \begin{equation*}
-n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: c_3(\Pbb,r)
+n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: c_{6}(\Pbb,r)
 \end{equation*}
@@
 
-Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$
+Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$
 \begin{equation*}
@@
 	\label{lem: graph_conductance_profile_lb}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_2(\Pbb,r)$ and $c_4(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_1}\right)^d
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_{5}(\Pbb,r)$ and $c_{7}(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_5(\Pbb,r)}\right)^d
 	\end{equation*}
@@
 	\end{equation}
-	with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$. 
+	with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$. 
 \end{lemma}
@@
 Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
-Then there exists a constant $c_7(\Pbb,r) > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
+Then there exists a constant $c_{9}(\Pbb,r) > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
 	\begin{equation}
 	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
+	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
 	\end{equation}
@@
 	\label{thm: stagnating_transportation_maps}
-	There exists constants $c_2(\Pbb,r)$ and $c_3(\Pbb,r)$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_2(\Pbb,r)\delta}\right)^{d}
-	\end{equation*}
-	then with probability at least $1 - \frac{c_3(\Pbb,r)}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
+	There exists constants $c_5(\Pbb,r)$ and $c_{7}(\Pbb,r)$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_5(\Pbb,r)\delta}\right)^{d}
+	\end{equation*}
+	then with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
 	which satisfies
@@
 \begin{equation*}
-\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2c_7(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
+\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2c_{9}(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
 \end{equation*}
@@
 \begin{align*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{c_7(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
 & \geq \frac{\widetilde{\Phi}_{\Pbb,r}}{2},
 \end{align*}
-where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2c_7(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}}$.
+where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2c_{9}(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}}$.
 Then, Lemma~\ref{lem: nonuniform_continuous_conductance} yields the desired result.
@@
 \begin{equation*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c_7(\Pbb,r)\varDelta}{s(\widetilde{G}_{n,r}) - c_7(\Pbb,r) \varDelta}
-\end{equation*}
-for some constant $c_7(\Pbb,r) > 0$.
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c_{9}(\Pbb,r)\varDelta}{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r) \varDelta}
+\end{equation*}
+for some constant $c_{9}(\Pbb,r) > 0$.
 We first state the relationships between the discrete functionals $\widetilde{\cut}_{n,r}$ and $\widetilde{\vol}_{n,r}$, and the continuous functionals $\widetilde{Q}_{\Pbb,r}$ and $\widetilde{\pi}_{\Pbb,r}$, alluded to in the previous section.
@@
 	\label{lem: deviation_transportation_distance}
-	Suppose $\Delta \leq r$. Then there exist constants $c_8(\Pbb,r),c_9(\Pbb,r) \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
-	\begin{align*}
-	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r) \varDelta \\
-	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r) \varDelta \\
-	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_9(\Pbb,r) \varDelta \\
-	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_9(\Pbb,r) \varDelta.
+	Suppose $\Delta \leq r$. Then there exist constants $c_{10}(\Pbb,r),c_{11}(\Pbb,r) \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
+	\begin{align*}
+	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r) \varDelta \\
+	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r) \varDelta \\
+	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_{11}(\Pbb,r) \varDelta \\
+	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{11}(\Pbb,r) \varDelta.
 	\end{align*}
@@
 \frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \frac{\widetilde{Q}_{\Pbb,r^-}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r^+}(\Sset)} \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \tag{Lemma \ref{lem: cut_volume}} \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_9(\Pbb,r) \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_9(\Pbb,r) \varDelta} \left(1 - \frac{2 c_8(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_9(\Pbb,r)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_{11}(\Pbb,r) \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_{11}(\Pbb,r) \varDelta} \left(1 - \frac{2 c_{10}(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_{11}(\Pbb,r)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
 \end{align}
@@
 	Suppose $\varDelta \leq \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)$.
-Then there exists a constant $c_{10}(\Pbb,r) > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
-	\begin{equation*}
-	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_{10}(\Pbb,r) \varDelta
+Then there exists a constant $c_{12}(\Pbb,r) > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
+	\begin{equation*}
+	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_{12}(\Pbb,r) \varDelta
 	\end{equation*}
@@
 \begin{align*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_9(\Pbb,r)}{\widetilde{\pi}_{n,r}(S) - c_{10}(\Pbb,r)\varDelta} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
-& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_9(\Pbb,r)}{s(\widetilde{G}_{n,r}) - c_{10}(\Pbb,r)\varDelta} + \frac{2c_8(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_{11}(\Pbb,r)}{\widetilde{\pi}_{n,r}(S) - c_{12}(\Pbb,r)\varDelta} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
+& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_{11}(\Pbb,r)}{s(\widetilde{G}_{n,r}) - c_{12}(\Pbb,r)\varDelta} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
 \end{align*}
 where the latter inequality follows as we assumed $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-Choosing the constant $c_7(\Pbb,r)$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c_7(\Pbb,r) = \max\set{2c_8(\Pbb,r)/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_9(\Pbb,r), c_{10}(\Pbb,r)}f$, we achieve our desired result.
+Choosing the constant $c_{9}(\Pbb,r)$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c_{9}(\Pbb,r) = \max\set{2c_{10}(\Pbb,r)/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_{11}(\Pbb,r), c_{12}(\Pbb,r)}f$, we achieve our desired result.
 It remains to show Lemmas~\ref{lem: cut_volume}, \ref{lem: deviation_transportation_distance}, and \ref{lem: continuous_pi_lb}, which we now turn to.
@@
 \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)  & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl( 2d(r + \Delta)^{d - 1}\varDelta \bigr) \tag{1st-order Taylor expansion of $(r + \Delta)^d$ } \\
-& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_8(\Pbb,r) \varDelta. \label{eqn: deviation_transportation_distance_1}
+& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_{10}(\Pbb,r) \varDelta. \label{eqn: deviation_transportation_distance_1}
 \end{align}
@@
 \int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r)\varDelta.
+& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r)\varDelta.
 \end{align*}
@@
 & \geq \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) d\Pbb(x) - \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r)) d\Pbb(x)} \\
-& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_8(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_9(\Pbb,r) \varDelta.
+& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_{10}(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_{11}(\Pbb,r) \varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Sset} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_9(\Pbb,r)\varDelta.
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{11}(\Pbb,r)\varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) }{\int_{\Csig}\ell_{\Pbb,r^-}(x) \,d\Pbb(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r)\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_8(\Pbb,r)\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_8(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{10}(\Pbb,r) \varDelta.
-\end{align*}
-where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_8(\Pbb,r)\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r)\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r)\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{12}(\Pbb,r) \varDelta.
+\end{align*}
+where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_{10}(\Pbb,r)\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
 
@@
 \end{equation*}
-with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$.
+with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
 Since we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets in Algorithm~\ref{alg: ppr}, we may apply Lemma~\ref{lem:zhu}.
@@
 Now we show that we can apply~\eqref{eqn:volume_ssd_pf1} to the cluster estimate $\Cest$ output by Algorithm~\ref{alg: ppr}.
-Observe that $\Cest$ is itself a sweep cut; precisely $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{50},\frac{1}{5}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
+Observe that $\Cest$ is itself a sweep cut as $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{50},\frac{1}{5}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
 Moreover, applying  Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/2$,
@@
 Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\widehat{C} \vartriangle \Csig[\Xbf])$.
-This completes the proof of Theorem~\ref{thm:volume_ssd}.
+To summarize, we have shown that when
+\begin{equation*}
+n \geq c_1(\Pbb,r)(\log(n))^{\max\{\frac{3}{d},1\}}
+\end{equation*}
+then
+\begin{equation*}
+\vol_{n,r}(\Csig[\Xbf] \vartriangle \widehat{C}) \leq  2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
+\end{equation*} 
+with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 3\exp\set{-(c_3(\Pbb,r) + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
+Since $c_3(\Pbb,r) \leq \vol_{\Pbb,r}(\Csig)^2$, letting $c_2(\Pbb,r) := c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)}$ we have proved Theorem~\ref{thm:volume_ssd}.
 
@@
 \end{equation}
-with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-(c_1(\Pbb,r) + c_6(\Pbb,r))n}$.
+with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$.
 
@@
 \end{equation*}
-holds with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$ by Theorem~\ref{thm: mixing_time_upper_bound}.
+holds with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
 Therefore, all the conditions of Lemma \ref{lem: setup} are met.
@@
 	\end{equation*}
-	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)^2\}$.
-By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
+	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$. By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
 	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
@@
 where the last inequality again follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}.
-We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters}.
+We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters} (choosing $c_2(\Pbb,r) = c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)} + \frac{900}{\lambda_{\sigma}\nu_dr^d} + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2$).
 
@@
 
-\subsection{The Approximate PPR Vector}
+\subsection{Proof of Corollary~\ref{cor: appr}.}
 \label{sec:appr}
-We are now in a position to formally state and prove our claims regarding the a\pprspace vector. 
-\begin{corollary}
-	\label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster (with respect to some $\theta$).
-Choose input parameters $r, \alpha, v, (L,U)$ to be well-initialized in the sense of \eqref{eqn: initialization}, additionally set
-	\begin{equation}
-	\label{eqn: appr_parameter}
-	\varepsilon = \frac{1}{25}\vol_{\Pbb,r}(\Csig)
-	\end{equation}
-	and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}_v$ rather than the exact \pprspace vector $\pbf_v$, with resulting output $\Cest$. Then
-	\begin{enumerate}
-		\item The upper bound on symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ given by \eqref{eqn:volume_ssd} is still valid.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
-\end{corollary}
-\begin{proof}
-To prove the first claim, we must show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
+To prove the first claim of Corollary~\ref{cor: appr}, we must show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
 In particular, we must show that $\varepsilon \leq \frac{1}{20}\vol_{n,r}(\Csig)$.
@@
 \noindent Using the arguments given in the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}, and choosing the universal constant in \eqref{eqn: kappa_ub} to be sufficiently small, the upper bound in \eqref{eqn:consistent_recovery_of_density_clusters_pf1} follows.
-
-\end{proof}
 

### 2019-11-18 arxiv/local_spectral_density_clustering_arxiv.tex
Made my pass through the paper

@@
 \newtheorem{corollary}{Corollary}
+\theoremstyle{definition}
 \newtheorem{definition}{Definition}
-\newtheorem*{remark}{Remark}
+\newtheorem{remark}{Remark}
 
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\newcommand{\1}{\mathbf{1}}
+\usepackage{bbm}
+\newcommand{\1}{\mathbbm{1}}
 \newcommand{\Phibf}{\Phi_{u}}
@@
 
-%%% Vectors
+%%% Vectors (no bold font)
 \newcommand{\pbf}{p}        % removed bold font
-\newcommand{\qbf}{\mathbf{q}}
+\newcommand{\qbf}{q}
 \newcommand{\ebf}[1]{{e}_{#1}}
@@
 %%% Matrices (no bold font)
-\newcommand{\Abf}{A}
-\newcommand{\Xbf}{X}             % removed bold font 
+\newcommand{\Abf}{A}       % removed bold font 
+\newcommand{\Xbf}{X}             
 \newcommand{\Wbf}{W}
@@
 \begin{center}
-Alden Green~~~~~ Sivaraman Balakrishnan~~~~~ Ryan Tibshirani\\
+Alden Green~~~~~ Sivaraman Balakrishnan~~~~~ Ryan J. Tibshirani\\
 \vspace{.2cm}
@@
 \begin{tabular}{c}
-\texttt{\{ajgreen,sbalakri,ryantibs\}@andrew.cmu.edu}
+\texttt{\{ajgreen,sbalakri,ryantibs\}@stat.cmu.edu}
 \end{tabular}
@@
 \begin{abstract}
-\noindent We analyze the Personalized PageRank (PPR) algorithm, a local spectral method for clustering,
-which extracts clusters using locally-biased random walks around a user-specified
-seed node.  In contrast to previous work, we adopt a classical statistical
-learning setup, where we obtain samples from an unknown distribution, and aim to
-identify connected regions of high-density (density clusters).  We prove that
-PPR, run on a neighborhood graph, extracts sufficiently salient density
-clusters. We also show a surprising converse result, that PPR can fail 
-to recover geometrically poorly conditioned density clusters, even asymptotically. Finally, we provide empirical support to illustrate our theoretical results.
+We analyze the Personalized PageRank (PPR) algorithm, a local spectral method
+for clustering, which extracts clusters using locally-biased random walks around
+a given seed node.  In contrast to previous work, we adopt a classical
+statistical learning setup, where we obtain samples from an unknown
+distribution, and aim to identify connected regions of high-density (density
+clusters).  We prove that PPR, run on a neighborhood graph, extracts
+sufficiently salient density clusters, that satisfy a set of natural geometric
+conditions. We also show a converse result, that PPR can fail to recover
+geometrically poorly-conditioned density clusters, even asymptotically. Finally,
+we provide empirical support our theory.
 \end{abstract}
 \end{center}
+
 \section{Introduction}
 \label{sec: introduction}
+
 In this paper, we consider the problem of clustering: splitting a given data set
 into groups that satisfy some notion of within-group similarity and
-between-group difference.  Our particular focus is on
-spectral clustering methods, a family of powerful
-nonparametric clustering algorithms. Roughly speaking, a spectral algorithm
-first constructs a geometric graph $G$, where vertices correspond to samples,
-and edges correspond to proximities between samples. The algorithm 
-then estimates a feature
-embedding based on (an appropriate) Laplacian matrix of the graph 
-$G$, and applies a simple clustering
-technique (like $k$-means clustering) in the embedded feature~space.
-
-% Spectral clustering and density clustering
-%Spectral clustering algorithms, which
-%originated in the early work of Fiedler \cite{fiedler73}, have seen a recent revival 
-%(see for instance the recent review~\cite{XX}) focused mainly on understanding the performance of spectral clustering on the Stochastic Block Model (SBM) and closely related problems.
-%A parallel line of work \cite{shi09,schiebinger15}, has considered spectral partitioning applied to a non-parametric mixture model
-%where once again the clustering goal is to recover the latent labels of a sample $X_1,\ldots,X_n \sim P$.
-These works proceed by relating the eigenvectors of the graph Laplacian to eigenfunctions of an appropriately defined integral operator, and then using assumptions about the (non-)overlap of the mixture components to show that these eigenfunctions elucidate the latent labels.
-
-When applied to geometric graphs built from a large number of samples,
-global spectral clustering methods can be computationally cumbersome and   
-insensitive to the local geometry of the underlying distribution
+between-group difference.  Our particular focus is on spectral clustering
+methods, a family of powerful nonparametric clustering algorithms. Roughly
+speaking, a spectral algorithm first constructs a geometric graph $G$, where
+vertices correspond to samples, and edges correspond to proximities between
+samples. The algorithm then estimates a feature embedding based on (an
+appropriate) Laplacian matrix of $G$, and applies a simple clustering technique
+(like $k$-means clustering) in the embedded feature space.
+
+When applied to geometric graphs built from a large number of samples, global
+spectral clustering methods can be computationally cumbersome and insensitive to
+the local geometry of the underlying distribution
 \citep{leskovec2010,mahoney2012}.  This has led to increased interest in
-\emph{local} spectral clustering algorithms, which leverage locally-biased spectra
-computed using random walks around some user-specified seed node.  A popular 
-local clustering algorithm is the Personalized PageRank (PPR) algorithm, first introduced by 
-\citet{haveliwala2003}, then further developed by
-several others~\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
+\emph{local} spectral clustering algorithms, which leverage locally-biased
+spectra computed using random walks around some user-specified seed node.  A
+popular local clustering algorithm is the Personalized PageRank (PPR) algorithm,
+first introduced by \citet{haveliwala2003}, and then further developed by
+several others
+\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
 
 Local spectral clustering techniques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, leading 
+\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
 many authors to develop supporting theory
@@
 guarantees on traditional graph-theoretic notions of cluster quality (such as
-conductance).  In this paper, we adopt a classical statistical viewpoint,
-and examine what the output of local clustering on a data set reveals about the
-underlying density $f$ of the samples.  In particular, we examine the ability of PPR to recover
-\emph{density clusters} of $f$, defined as the connected components of
-the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$
-(a central object of interest in the statistical clustering literature, dating
-back to the work of \citet{hartigan1981}).
-
-\section{Background and Related Work}
+conductance).  In this paper, we adopt a classical statistical viewpoint, and
+examine what the output of local clustering on a data set reveals about the
+underlying density $f$ of the samples.  In particular, we examine the ability of
+PPR to recover \emph{density clusters} of $f$, defined as the connected
+components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some
+$\lambda > 0$ (an object of central interest in the statistical clustering
+literature, dating back to the work of \citet{hartigan1981}).
+
+\section{Background and related work}
+
 We begin by providing some standard background on the PPR algorithm
 and the density clustering setup, before turning our attention to related work
-and a
-detailed summary of our contributions.
+and a detailed summary of our contributions.
 
 \subsection{PPR on a neighborhood graph}
-We now describe the clustering
-algorithm that will be our focus for the rest of the paper. Let $\Xbf = \{x_1,
-\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$,
-with density~$f$.  For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the
-\emph{$r$-neighborhood graph} of $\Xbf$, an unweighted, undirected graph with
-vertices $V=\Xbf$, and an edge $(x_i,x_j) \in E$ if and only if $\norm{x_i -
-x_j} \leq r$, where $\norm{\cdot}$ is the Euclidean norm. We denote by $\Abf \in
-\Reals^{n \times n}$ the adjacency matrix, with entries $\Abf_{uv} = 1$ if
-$(u,v) \in E$ and $0$ otherwise.  We also denote by $\Dbf$ the diagonal degree
-matrix, with entries $\Dbf_{uu} := \sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n
-\times n$ identity matrix.
-
-Next, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on
-a seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to be 
-the solution of the following linear system:
+
+Let $\Xbf = \{x_1,\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution
+$\Pbb$ on $\Rd$, with density $f$.  For a radius $r > 0$, we define
+$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $\Xbf$, an
+unweighted, undirected graph with vertices $V=\Xbf$, and an edge $(x_i,x_j) \in
+E$ if and only if $\norm{x_i - x_j} \leq r$, where $\norm{\cdot}$ is the
+Euclidean norm. We denote by $\Abf \in \Reals^{n \times n}$ the adjacency
+matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
+also denote by $\Dbf$ the diagonal degree matrix, with entries $\Dbf_{uu} :=
+\sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.
+
+First, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on 
+a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to
+be the solution of the following linear system:
 \begin{equation}
@@
 where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over
-$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in the
-$v$-th position and 0 elsewhere).
-
-\subsubsection{Sweep cut}
-\label{subsection: sweep_cut}
-We employ the sweep cut method to obtain a local cluster from the PPR embedding $\pbf_v$.
-In more detail, for a level $\beta > 0$, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$
-as   
+$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
+position $v$ and 0 elsewhere).
+
+%\subsubsection{Sweep cut}
+%\label{subsection: sweep_cut}
+Next, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$,
+for a given level $\beta > 0$, as    
 \begin{equation}
@@
 \Abf_{uv}$}, and \smash{$\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$}.  We
-define the \emph{normalized cut} of $S$ as
+then define the \emph{normalized cut} of $S$ as
 \begin{equation}
@@
 \end{equation}
-Having computed sweep cuts $S_{\beta}$ over a range \smash{$\beta \in  
-(L, U)$} (where the range $(L,U)$ is also a user-specified parameter), we output the cluster estimate
-\smash{$\Cest = S_{\beta^*}$} that has minimum normalized cut.
-%\smash{$\Phi(S_{\beta^*}; G_{n,r})$}. 
-For concreteness, the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.
+Having computed sweep cuts $S_{\beta}$ over \smash{$\beta \in (L, U)$} (where
+the range $(L,U)$ is user-specified), we output the cluster estimate
+\smash{$\Cest = S_{\beta^*}$} with minimum normalized cut.  For concreteness,
+the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.
 
@@
 parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, sweep cut range $(L,U)$. \\     
-{\bfseries Output:} cluster $\Cest \subseteq V$.
+{\bfseries Output:} cluster estimate $\Cest \subseteq V$.
 \begin{algorithmic}[1]
   \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
-    ppr_vector}. 
-  \STATE For \smash{$\beta \in (L,U)$} compute sweep cuts 
-  $S_{\beta}$ as in \eqref{eqn: sweep_cuts}.
+  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in
+  \eqref{eqn: ppr_vector}.  
+  \STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
+  \eqref{eqn: sweep_cuts}. 
   \STATE Return the cluster \smash{$\Cest = S_{\beta^*}$}, where  
@@
 \subsection{Estimation of density clusters}
-Let \smash{$\Cbb_f(\lambda)$} denote 
-the connected components of the density upper level set $\{x \in \Rd: f(x) >
-\lambda\}$.  For a given density cluster \smash{$\Cset \in \Cbb_f(\lambda)$}, we
-call $\Cset[\Xbf] = \Cset \cap \Xbf$ the \emph{empirical density cluster}. The size of the symmetric set difference between estimated and empirical cluster is 
-a commonly used metric to quantify cluster estimation error
-\citep{korostelev1993,polonik1995,rigollet2009}. We will consider a related metric, the volume of the symmetric set difference, which weights points according to their degree in $G_{n,r}$. 
+
+Let \smash{$\Cbb_f(\lambda)$} denote the connected components of the density
+upper level set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster
+\smash{$\Cset \in \Cbb_f(\lambda)$}, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the
+\emph{empirical density cluster}. The size of the symmetric set difference
+between estimated and empirical cluster is a commonly used metric to quantify
+cluster estimation error \citep{korostelev1993,polonik1995,rigollet2009}. We
+will consider a related metric, the volume of the symmetric set difference,
+which weights points according to their degree in $G_{n,r}$.
 \begin{definition}
   \label{def:volume_symmetric_set_difference}
-	For an estimator $\widehat{C} \subseteq \Xbf$ and a set $\mathcal{S} \subseteq \Rd$, the symmetric set difference is 
-	\begin{equation*}
-	\widehat{C} \vartriangle \mathcal{S}[\Xbf] := \bigl(\widehat{C} \cap \setminus \mathcal{S}[\Xbf]\bigr) \cup \bigl(\Xbf\setminus\widehat{C} \cap \mathcal{S}[\Xbf]\bigr).
-	\end{equation*}
-	We will measure the discrepancy of $\widehat{C}$ to the set $\mathcal{S}[\Xbf]$ by the volume of the symmetric set difference,
-	\begin{equation*}
-	\Delta(\widehat{C}, \mathcal{S}[\Xbf]) := \vol(\widehat{C} \vartriangle \mathcal{S}[\Xbf]; G_{n,r})
-	\end{equation*}
+  For an estimator \smash{$\Cest \subseteq \Xbf$} and a set 
+  $\mathcal{S} \subseteq \Rd$, their symmetric set difference is 
+  $$
+  \Cest \vartriangle \mathcal{S}[\Xbf] :=
+    \bigl(\Cest \setminus \mathcal{S}[\Xbf]\bigr) \cup
+    \bigl(\mathcal{S}[\Xbf] \setminus \Cest\bigr).
+  $$
+  Furthermore, we denote the volume of the symmetric set difference by 
+  $$
+  \Delta(\Cest, \mathcal{S}[\Xbf]) := \vol(\Cest \vartriangle \mathcal{S}[\Xbf];
+  G_{n,r}). 
+  $$
 \end{definition}
-However, the symmetric set difference does not measure whether \smash{$\Cest$} 
-can distinguish any two distinct clusters \smash{$\Cset,\Cset' \in
+
+Note that the symmetric set difference does not measure whether \smash{$\Cest$}
+can (perfectly) distinguish any two distinct clusters \smash{$\Cset,\Cset' \in 
   \Cbb_f(\lambda)$}. We therefore also study a second notion of cluster 
@@
 
-\begin{definition}[Consistent density cluster estimation]
+\begin{definition}
   \label{def: consistent_density_cluster_estimation}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster 
-  \smash{$\Cset \in \Cbb_f(\lambda)$}, we say \smash{$\Cest$} is a consistent 
-  estimator of $\Cset$ if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with
-  $\Cset \not= \Cset'$, the following holds as $n \to \infty$: 
+  For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster \smash{$\Cset \in
+    \Cbb_f(\lambda)$}, we call \smash{$\Cest$} \emph{consistent} for
+  \smash{$\Cset$} if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with  
+  \smash{$\Cset \not= \Cset'$}, the following holds as $n \to \infty$: 
   \begin{equation}
@@
 \end{definition}
-\noindent Consistent cluster recovery roughly ensures that, for a given density threshold $\lambda$, the estimated cluster $\Cest$ contains all
-points in a true
-density cluster $\Cset \in \Cbb_f(\lambda)$, and simultaneously does not contain any points in any other density cluster $\Cset' \in \Cbb_f(\lambda)$.
-
-With these definitions in place, our broad goal will be to understand the extent to which the PPR algorithm is able to
-recover a cluster which either guarantees low symmetric set difference to a true density cluster, or which consistently estimates
-a true density cluster.
-
-%\subsection{Our Contributions}
-
-\subsection{Related Work and Our Contributions}
-In addition to the background on local spectral
-clustering given previously, a few related lines of work are worth
-highlighting.
-In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
-The ability of spectral algorithms to perform clustering -- community detection-- in this context is well-understood, dating back to \citet{mcsherry2001} who gives conditions under which the entire community structure can be recovered.
-In more recent work, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM and \citet{lei2015} extend these results to the sparse (low average degree) regime.
-Relatedly, \citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate when the block model exhibits some hierarchical structure.
-The framework we consider, where nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
-
-The study of spectral algorithms on neighborhood graphs has focused on establishing consistency results-- that is, asymptotic convergence of eigenvalues and eigenvectors of matrices to eigenvalues and eigenfunctions of limiting operators.
-\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
-\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood of fixed radius.
-\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime where the radius $r \to 0$ as $n \to \infty$.
-
-These results are of fundamental importance; however, the behavior of the spectra of these continuum operators can in general be hard to grasp.
-Therefore, further work relating this spectra to the geometry of the distribution $\Pbb$ is of interest.
-In this spirit, \citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of
-spectral algorithms to recover the latent labels in certain geometrically well-conditioned nonparametric mixture models. Their results focus on global rather than local 
-methods, and thus impose global rather than local conditions on the nature
-of the density. Moreover, they do not in general guarantee recovery of density 
-clusters, which is the focus in our work. Perhaps most importantly, these works
-rely on general cluster saliency conditions, which implicitly depend on many
-distinct geometric aspects of the cluster $\Cset$ under consideration. We make
-this dependence more explicit, and in doing so expose the role each geometric
-condition plays in the clustering problem.
-
-Our analysis naturally builds on a few of the aforementioned theoretical analyses of PPR.
-For an arbitrary graph $G$ and subset $S \subset G$, \citet{andersen2006} relate the quality of the PPR cluster $\hat{C}$ to the normalized cut functional $\Phi(S;G)$.
-While this analysis is tight, it fails to account for improvements possible when the cluster $S$ is additionally assumed to be internally well-connected, which is intuitively a more favorable case for clustering.
-Building on this intuition, \citet{zhu2013} assume that the subgraph $G[S]$ is internally well-connected-- measured by a functional such as mixing time of a random walk over $G[S]$-- and prove upper bounds on $\vol(\widehat{C} \vartriangle S;G)$.
-Both of these analyzes hold with respect to a approximate form of PPR (APPR) which can be efficiently computed.
-
-We apply these results to our setting by estimating these functionals in the particular case of $G = G_{n,r}$ and $S = \mathcal{C}[X]$.
-In particular, we prove an upper bound on the mixing time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall within a density cluster $\Cset$.
-To do so, we rely on a series of seminal works upper bounding the mixing time of \emph{geometric random walks} (see \citet{vempala2005} for a comprehensive review.)  This study was initiated by \citet{dyer1991}, who used geometric random walks as a fundamental subroutine to efficiently compute volumes of high-dimensional convex bodies.
-These results are improved in \citet{lovasz1990,kannan97,kannan06}, who show, inter alia, that the bounds on mixing time can be sharpened by avoiding so-called ``start-penalties''.
-As we discuss further in the sequel, these improvements are crucial to our work.
-Following the work of \citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold for Lipschitz deformations of convex sets.
-Additionally, we relate the mixing time of these (continuous-space) geometric random walks to the mixing time of random walks over (discrete) neighborhood graphs.
-
-Finally, it is worth mentioning that density clustering and level set estimation are well-studied problems. \citet{polonik1995, rigollet2009} study density clustering under the 
-symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
-minimax optimal level-set estimators under Hausdorff loss and
-\citet{hartigan1981, chaudhuri2010, balakrishnan2013,kpotufe11} consider consistent estimation of the
-cluster tree.
-%, to note but a few works. 
-We emphasize that our goal is not to improve on these
-results, nor to offer a better algorithm for level set estimation; indeed, seen as
-a density clustering algorithm, PPR has none of the optimality guarantees 
-found in the aforementioned works. Instead, our motivation is to start with a 
-widely-used local spectral method, PPR, and to better understand and
-characterize the distinctions between those density clusters which are
-well-conditioned for PPR, and those which are not.
-
-Specifically, a summary of our results (and an outline for this
-paper) is as follows.
+
+Consistent cluster recovery roughly ensures that, for a given 
+threshold $\lambda>0$, the estimated cluster \smash{$\Cest$} contains all points
+in a true density cluster $\Cset \in \Cbb_f(\lambda)$, and simultaneously does 
+not contain any points in any other density cluster $\Cset' \in
+\Cbb_f(\lambda)$.
+
+With these definitions in place, our broad goal will be to understand the extent
+to which the PPR algorithm is able to recover a cluster which either guarantees
+a low symmetric set difference to a true density cluster, or which consistently
+estimates a true density cluster.
+
+\subsection{Related work}
+
+In addition to the background on local spectral clustering given above, a
+few related lines of work are worth highlighting. In the stochastic block model
+(SBM), arguably one of the simplest models of network formation, edges between
+nodes independently occur with probability based on a latent community
+membership. In the SBM, the ability of spectral algorithms to perform
+clustering---or community detection---is well-understood, dating 
+back to \citet{mcsherry2001} who gives conditions under which the entire
+community structure can be recovered. In more recent work, \citet{rohe2011}
+upper bound the fraction of nodes misclassified by a spectral algorithm for the
+high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
+results to the sparse (low average degree) regime. Relatedly,
+\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
+when the block model exhibits some hierarchical structure. The framework we
+consider, in which nodes correspond to data points sampled from an underlying 
+density, and edges between nodes are formed based on geometric proximity, is
+quite different than the SBM, and therefore so is our analysis.
+
+In general, the study of spectral algorithms on neighborhood graphs has been
+focused on establishing asymptotic convergence of eigenvalues and eigenvectors
+of certain sample objects to the eigenvalues and eigenfunctions of corresponding
+limiting operators. \citet{koltchinskii2000} establish convergence of spectral
+projections of the adjacency matrix to a limiting integral operator, with
+similar results obtained using simplified proofs in
+\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
+the Laplacian matrix for a neighborhood of fixed radius. \citet{belkin07} and
+\citet{garciatrillos18} extend these results to the regime where the radius $r
+\to 0$ as $n \to \infty$.
+
+These results are of fundamental importance; however, the behavior of the
+spectra of these continuum operators can in general be hard to grasp. Therefore,
+further work relating this spectra to the geometry of the unlerlying
+distribution $\Pbb$ is of interest. In this spirit,
+\citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of spectral
+algorithms to recover the latent labels in certain geometrically
+well-conditioned nonparametric mixture models. Their results focus on global
+rather than local methods, and thus impose global rather than local conditions
+on the nature of the density. Moreover, they do not in general guarantee
+recovery of density clusters, which is the focus in our work. Perhaps most
+importantly, these works rely on general cluster saliency conditions, which
+implicitly depend on many distinct geometric aspects of the cluster $\Cset$
+under consideration. We make this dependence more explicit, and in doing so
+expose the role each geometric condition plays in the clustering problem.
+
+Our analysis naturally builds on a few of the aforementioned theoretical
+analyses of PPR. For an arbitrary graph $G$ and subset $S \subseteq G$,
+\citet{andersen2006} relate the quality of the PPR cluster \smash{$\Cest$} to
+the normalized cut functional $\Phi(S;G)$. While this analysis is tight in a
+worst-case sense, it fails to account for possible improvements when the cluster
+$S$ is additionally assumed to be internally well-connected, which is an
+intuitively more favorable case for clustering. Building on this intuition,  
+\citet{zhu2013} assume that the subgraph $G[S]$ is internally
+well-connected---as measured by a functional such as mixing time of a random
+walk over $G[S]$---and prove upper bounds on \smash{$\vol(\Cest \vartriangle
+  S;G)$}. Both of these analyses also hold with respect to an approximate form 
+of PPR  (APPR), which can be efficiently computed.
+
+We apply these results to our setting by carefully analyzing the normalized cut
+and mixing time functionals in the particular case of $G = G_{n,r}$ and $S =
+\Cset[X]$. One of our main challenges is to prove an upper bound on the mixing 
+time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall
+within a density cluster $\Cset$. To do so, we rely on a series of seminal works
+upper bounding the mixing time of \emph{geometric random walks} (see 
+\citet{vempala2005} for a comprehensive review.)  This study was initiated by
+\citet{dyer1991}, who used geometric random walks as a fundamental subroutine to
+efficiently compute volumes of high-dimensional convex bodies. These results are
+improved in \citet{lovasz1990,kannan97,kannan06}, who show, inter alia, that the
+bounds on mixing time can be sharpened by avoiding so-called
+``start-penalties''. As we discuss further in what follows, these improvements
+are crucial to our work. Following the work of
+\citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold
+for Lipschitz deformations of convex sets. Additionally, we relate the mixing
+time of these (continuous-space) geometric random walks to the mixing time of
+random walks over (discrete) neighborhood graphs.
+
+Finally, it is worth mentioning that density clustering and level set estimation
+are themselves very well-studied problems in statistics. \citet{polonik1995,
+  rigollet2009} study density clustering under the symmetric set difference
+metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
+estimators under Hausdorff loss and
+\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
+consistent estimation of the cluster tree. We emphasize that our goal is
+not to improve on these results, nor to offer a better algorithm for level set
+estimation; indeed, seen as a density clustering algorithm, PPR has none 
+of the optimality guarantees found in the aforementioned works. Instead, our
+motivation is to start with a widely-used local spectral method, PPR, and to
+better understand and characterize the distinctions between those density 
+clusters which are well-conditioned for PPR, and those which are not.
+
+\subsection{Summary of results}
+
+A summary of our results (and an outline for this paper) is as follows.
 
@@
   %formalize a measure of difficulty based on these geometric conditions, 
-  and show that when Algorithm \ref{alg: ppr} is properly initialized, the size of
-  the symmetric set difference of \smash{$\Cest$} and a thickened version of the
-  density cluster $\Csig$ can be bounded in a meaningful way.
-  % this difficulty measure.
+  and show that if Algorithm~\ref{alg: ppr} is properly initialized, then the size of
+  the symmetric set difference between \smash{$\Cest$} and a thickened version
+  of the density cluster $\Csig$ can be bounded in a meaningful way based on the
+  geometric parameters.
 
@@
     consistent_cluster_estimation_with_ppr} that if the density cluster  
-  $\Cset$ is particularly well-conditioned, Algorithm \ref{alg: ppr}
-  will consistently estimate a density cluster in a strong sense (see~\eqref{eqn: consistent_density_cluster_recovery}).
+  $\Cset$ is particularly well-conditioned, then Algorithm~\ref{alg: ppr} 
+  will consistently estimate a density cluster in the strong sense of
+  \eqref{eqn: consistent_density_cluster_recovery}.
 
 \item In Section \ref{sec: analysis}, we detail some of the analysis required to 
-  prove our main results, and expose the roles that various geometric quantities play 
-  in the difficulty of the clustering problem.
-
-\item In Section \ref{sec:lower_bound}, we provide an accompanying lower bound, demonstrating that when the cluster $\Cset$ is sufficiently poorly conditioned, it will not be recovered by Algorithm~\ref{alg: ppr}.
+  prove our main results, and expose the roles that various geometric quantities 
+  play in the difficulty of the clustering problem.
+
+\item In Section \ref{sec:lower_bound}, we provide an accompanying lower bound,
+  which demonstrates that when the cluster $\Cset$ is sufficiently poorly
+  conditioned, it will not be recovered by Algorithm~\ref{alg: ppr}.
 
@@
 
-\noindent At this point we summarize one of our main takeaways: 
-PPR, run on a neighborhood graph, recovers only \emph{geometrically
-compact} high-density clusters. Our main theoretical results, makes this takeaway 
-precise, and provides concrete ways of quantifying the geometric
-compactness of a density cluster.
-
-\section{Main Results}
+One of our main takeaways can be paraphrased as follows: PPR, run on a
+neighborhood graph, recovers only \emph{geometrically compact} high-density
+clusters. Our theoretical results make this takeaway precise, and provide a 
+concrete way of quantifying the geometric compactness of a density 
+cluster.
+
+\section{Main results}
 \label{sec: consistent_cluster_estimation_with_ppr}
-In this section we present our main results on the accuracy of the PPR algorithm 
-for recovering density clusters. 
-We begin by formally introducing a variety of geometric conditions, 
-and use these to define a condition
-number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-estimating a density cluster $\Cset$.
-With this condition in place 
-our first main result (Theorem~\ref{thm:volume_ssd}) provides a bound
-on the symmetric set difference between the estimated cluster $\Cest$,
-obtained by an appropriately initialized version of the PPR algorithm,
-and
-the target cluster $\Cset$.
-Our next main result (Theorem~\ref{thm: consistent_recovery_of_density_clusters})
-shows that for sufficiently well-conditioned target clusters $\Cset$, the output 
-of the PPR algorithm $\Cest$
-is consistent in the sense defined in Definition~\ref{def: consistent_density_cluster_estimation}.
-
-\subsection{Preliminaries}%: Geometric Conditions and the Condition Number of a Density Cluster}
-%We formalize some geometric conditions, and use these to define a condition
-%number $\kappa(\Cset)$, which measures the difficulty PPR will have in  
-%estimating $\Cset$. (Our theoretical guarantees for PPR will be framed in terms 
-%of $\kappa(\Cset)$.)
-%\paragraph{Geometric conditions on density clusters.} 
-At a high level, for PPR
-to be successful, the underlying density cluster must be geometrically
-well-conditioned.  A basic requirement is that we need to avoid clusters which contain arbitrarily
-thin bridges or spikes. As in the work of \citet{chaudhuri2010}, we consider a
-thickened version of \smash{$\Cset \in \Cbb_f(\lambda)$} defined as 
-$\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq \sigma}$, which 
-we call the \emph{$\sigma$-expansion} of $\Cset$. Here 
+
+In this section, we present our main results on accuracy of the PPR algorithm
+for recovering density clusters.  We begin by formally introducing various
+geometric conditions, and use these to define a condition number
+$\kappa(\Cset)$, which measures the difficulty PPR will have in estimating a
+density cluster $\Cset$. With this condition in place our first main result
+(Theorem~\ref{thm: volume_ssd}) provides a bound on the symmetric set difference
+between the estimated cluster $\Cest$, obtained by an appropriately initialized 
+version of the PPR algorithm, and the target cluster $\Cset$.  Our next main
+result (Theorem~\ref{thm: consistent_recovery_of_density_clusters}) shows that
+for sufficiently well-conditioned target clusters $\Cset$, the output of the PPR
+algorithm $\Cest$ is consistent in the sense of Definition~\ref{def:
+consistent_density_cluster_estimation}.
+
+\subsection{Preliminaries}
+
+At a high level, for PPR to be successful, the underlying density cluster must
+be geometrically well-conditioned.  A basic requirement is that we need to avoid
+clusters which contain arbitrarily thin bridges or spikes. As in the work of
+\citet{chaudhuri2010}, we consider a thickened version of \smash{$\Cset \in
+\Cbb_f(\lambda)$} defined as $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq
+\sigma}$, which we call the \emph{$\sigma$-expansion} of $\Cset$. Here
 \smash{$\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$}.  We now list our
@@
   $0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
-  $\lambda_{\sigma} \leq \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x)
-  \leq \Lambda_{\sigma}$.
+  $$
+  \lambda_{\sigma} \leq \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x)
+  \leq \Lambda_{\sigma}.
+  $$
 
@@
   \label{asmp: low_noise_density}
-  \emph{Low noise density:} There exists $c_0 > 0$ and $\gamma \in [0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,   
-  \begin{align*}
-  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \dist(x, \Csig)^{\gamma}. 
-  \end{align*}
-  Roughly, 
-  this assumption ensures that the density decays sufficiently quickly as we move away from
-  the target cluster $\Csig$, and is a standard assumption in the level-set estimation literature
-  (see for instance~\cite{singh2009}).
+  \emph{Low noise density:} There exists constants $c_0 > 0$ and $\gamma \in
+  [0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,     
+  $$
+  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \cdot \dist(x, \Csig)^{\gamma}.  
+  $$
+  Roughly, this assumption ensures that the density decays sufficiently quickly
+  as we move away from the target cluster $\Csig$, and is a standard assumption
+  in the level-set estimation literature (see for instance \citet{singh2009}).
 
@@
   \begin{enumerate}
-  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K} \subseteq \Rd$
-  with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} =:
-  \diam < \infty$
-  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where
-  $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x$ and
-  \item for some $L
-  \geq 1$,   
-  \begin{equation*}
+  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K}
+    \subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
+      \mathcal{K}}\norm{x - y} =: \diam < \infty$;
+  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is
+    the Jacobian of $g$ evaluated at $x;$ and 
+  \item for some $L \geq 1$,   
+    $$
     \norm{g(x) - g(y)} \leq L \norm{x - y} ~
     \text{for all $x,y \in \mathcal{K}$}. 
-  \end{equation*}
+    $$
   \end{enumerate}
-  Succinctly, we assume that $\Csig$ is the image of a convex set with finite diameter 
-  under a  measure preserving, Lipschitz transformation.
+  Succinctly, we assume that $\Csig$ is the image of a convex set with finite
+  diameter under a measure preserving, Lipschitz transformation.
 
@@
   \emph{Bounded volume:}
-  For a set $\mathcal{S} \subseteq \Reals^d$, define the $\Pbb$-weighted volume of $\mathcal{S}$ to be
+  For a set $\mathcal{S} \subseteq \Reals^d$, define a $\Pbb$-weighted volume of 
+  $\mathcal{S}$ to be  
   \begin{equation}
   \label{eqn:volume}
-  \vol_{\Pbb,r}(\mathcal{S}) := \int_{\mathcal{S}} \Pbb(B(x,r)) \,d\Pbb(x).
-  \end{equation}
-  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$.
-
-  We assume that the neighborhood graph radius $0 < r \leq \sigma/2d$ is chosen such that
-  \begin{equation*}
-  \vol_{\Pbb,r}(\mathcal{S}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d).
-  \end{equation*}
-
+  \vol_{\Pbb,r}(\mathcal{S}) := \int_{\mathcal{S}} \Pbb(B(x,r)) f(x) \, dx.
+  \end{equation}
+  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$. We assume
+  that the radius of the neighborhood graph $0 < r \leq \sigma/(2d)$ is chosen 
+  such that  
+  $$
+  \vol_{\Pbb,r}(\Cset_\sigma) \leq \frac{1}{2} \vol_{\Pbb,r}(\Reals^d). 
+  $$
 \end{enumerate}
 
-To motivate these conditions, we provide a brief high-level sketch
-of our analysis (we return to this more formally in Section~\ref{sec: analysis}). 
-\citet{zhu2013} show for an arbitrary graph $G =
-(V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
-of subset $S$ satisfies, for a constant $c>0$,
+To motivate these conditions, we now give a brief high-level sketch
+of our analysis (which we will return to more formally in Section~\ref{sec:  
+  analysis}).  \citet{zhu2013} show that for an arbitrary graph $G = (V,E)$ and
+subset of vertices $S \subseteq V$, the PPR algorithm (properly initialized
+within $S$) will output an estimate \smash{$\Cest$} of $S$ satisfying, for a
+constant $M>0$, 
 \begin{equation}
 \label{eqn: graph_symmetric_set_difference_1}
-\vol(\Cest \vartriangle S; G) \leq c \bigl( \Phi(S,G)
-\cdot \tau_{\infty}(G[S])\bigr),
+\vol(\Cest \vartriangle S; G) \leq M \cdot \Phi(S,G) \cdot \tau_{\infty}(G[S]),    
 \end{equation}
@@
 precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
-\eqref{eqn: graph_symmetric_set_difference_1} is precisely
-the volume of the symmetric set difference, and our main goal is therefore to upper bound the graph functionals $\Phi$ and $\tau_{\infty}$.
-  Towards this goal, as we will show in Section \ref{sec:
-  analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
+\eqref{eqn: graph_symmetric_set_difference_1} is one of our principle metrics
+of interest, the volume of the symmetric set difference, and our main goal will 
+therefore be to upper bound the graph functionals $\Phi$ and $\tau_{\infty}$.
+Towards this goal, as we will show in Section
+\ref{sec: analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp: 
   bounded_volume} allow us to upper bound the normalized cut 
 \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. In more detail, assumption 
+\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Specifically, assumption 
 \ref{asmp: low_noise_density} yields an upper
@@
 \subsubsection{Condition number}
-Motivated by \eqref{eqn:
-  graph_symmetric_set_difference_1}, we will define $\kappa(\Cset)$ to be an
-upper bound on the product \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
-  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Following, the analysis of \citet{zhu2013}
-  we see that the smaller $\kappa(\Cset)$ is, the
-more success PPR will have in recovering the target cluster $\Cset$.
-
-\begin{definition}[Well-conditioned density clusters]
+
+We will define the condition number $\kappa(\Cset)$ of a cluster $\Cset$ in 
+terms of a suitable upper bound---expressed in terms of the geometric parameters
+from \ref{asmp: bounded_density}--\ref{asmp: bounded_volume}---on the product of
+normalized cut and mixing time, \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
+  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Following \eqref{eqn:
+  graph_symmetric_set_difference_1}, we see that the smaller the condition
+number $\kappa(\Cset)$ is, the more success PPR will have in recovering the
+target $\Cset$.
+
+\begin{definition}
   \label{def:well_conditioned_density_cluster}
   For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy  
-  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma > 0$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified
-  later, we set 
-  \begin{equation}
-    \label{eqn: condition_number_1}
+  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma >
+  0$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later
+  (in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
+    mixing_time_upper_bound}), define
+  \begin{equation}
+    \label{eqn: condition_number}
     \Phibf(\Cset) 
@@
     \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma +
-        1})}{\lambda_{\sigma}},~  
+        1})}{\lambda_{\sigma}}, \quad
     \taubf(\Cset) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
-      L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c_3,
-  \end{equation}
-  and letting \smash{$\kappa(\Cset) := \Phi_{u}(\Cset) \cdot
-    \tau_{u}(\Cset)$}, we call $\Cset$ a 
-  \emph{$\kappa$-well-conditioned density cluster}.  
+      L^2}{\lambda_{\sigma}^4 r^2}
+    \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c_3.
+  \end{equation}
+  Letting \smash{$\kappa(\Cset) := \Phibf(\Cset) \cdot \taubf(\Cset)$},
+  we call $\kappa(\Cset)$ the \emph{condition number} of $\Cset$.  We also call
+  the set $\Cset$ a \emph{$\kappa$-well-conditioned} density cluster.  
 \end{definition}
-\noindent The condition number 
-$\kappa(\Cset)$ succinctly captures the role of the various
-geometric parameters. 
-We note in passing that $\Phibf(\Cset)$ and $\taubf(\Cset)$ are exactly the upper bounds 
-on \smash{$\Phi(\Csig[\Xbf]; G_{n,r})$} and
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in our analysis
-later, in Section \ref{sec: analysis}.
-
-\subsubsection{Well-initialized algorithm} As is typical in the local clustering
-literature, our algorithmic results will be stated with respect to specific
-ranges of each of the user-specified parameters. In particular, for a
-well-conditioned density cluster $\Cset$, we require that some of the tuning parameters of Algorithm~\ref{alg: ppr} are chosen to fall within specific ranges,
+
+The condition number $\kappa(\Cset)$ succinctly captures the role of the various 
+geometric parameters.  We note in passing that $\Phibf(\Cset)$ and
+$\taubf(\Cset)$ are exactly the upper bounds  on \smash{$\Phi(\Csig[\Xbf];
+  G_{n,r})$} and \smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in
+our analysis later, in Section \ref{sec: analysis}.
+
+\subsubsection{Well-initialized algorithm}
+
+As is typical in the local clustering literature, our algorithmic results will
+be stated with respect to specific ranges of each of the user-specified
+parameters. In particular, for a well-conditioned density cluster $\Cset$, we
+require that some of the tuning parameters of Algorithm~\ref{alg: ppr} are
+chosen to fall within specific ranges,
+
 \begin{equation}
@@
 0 < r \leq \frac{\sigma}{2d}, \quad 
-\alpha \in [1/10, 1/9) \cdot \frac{1}{\taubf(\theta)}, \\
-(L,U) \subseteq (1/50,1/5) \cdot \frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}.
+\alpha \in {\textstyle [\frac{1}{10}, \frac{1}{9})} \cdot
+\frac{1}{\taubf(\theta)}, \\ 
+(L,U) \subseteq {\textstyle(\frac{1}{50},\frac{1}{5})} \cdot 
+\frac{1}{2{n \choose 2} \vol_{\Pbb,r}(\Csig)}.  
 \end{gathered}
@@
 If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn:
-  initialization} for some well-conditioned density cluster $\Cset$, we
+  initialization} (for some well-conditioned density cluster $\Cset$), then we  
 say the algorithm is \emph{well-initialized}. 
 \end{definition}
-\noindent In practice it is  not feasible to set hyperparameters based on the
-underlying (unknown) density $f$. Typically, one tunes PPR over a range of
-hyperparameters and selects the cluster which has the smallest normalized cut.
-
-\subsection{Cluster Recovery in Symmetric Set Difference}
-We now present our first main result: a bound on the volume of the symmetric set difference between the estimated cluster $\widehat{C}$ and empirical cluster $\Csig[\Xbf]$. 
-In this theorem, and hereafter, we let 
-$c, c_i > 0$ represent universal constants, and 
-$c(\Pbb,r), c_i(\Pbb,r) > 0$ represent constants which may depend on $\Pbb,\lambda$ and $r$ but not on the sample size $n$; where possible, we keep track of all constants in our proofs.
+
+In practice of course, it is not feasible to set tuning parameters based on the 
+underlying (unknown) density $f$. Typically, one runs PPR over some range of
+tuning parameter values and selects the cluster which has the smallest
+normalized cut.
+
+\subsection{Cluster recovery in symmetric set difference}
+
+We now present our first main result: a bound on the volume of the symmetric set
+difference between the estimated cluster \smash{$\Cest$} and empirical cluster 
+$\Csig[\Xbf]$. In this theorem, and hereafter, we let $c, c_i > 0$ denote
+universal constants, and $b,b_i > 0$ denote constants which may depend on  
+$\Pbb,\lambda,r,d$ and so on, but \emph{not} on the sample size 
+$n$.  % where possible, we keep track of all constants in our proofs.
+
 \begin{theorem}
-  \label{thm:volume_ssd}
-  Fix $\lambda > 0$ and let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-  $\kappa$-well-conditioned density cluster for some $\sigma > 0$. If Algorithm \ref{alg: ppr} is \emph{well-initialized} with respect to $\Cset$, then 
-  %there exists a universal constant $c > 0$, constants in sample size $c_1(\Pbb,r)$ - $c_6(\Pbb,r)$, and 
-  there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume 
-  with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that the following statement holds: let Algorithm~\ref{alg: ppr} be run with any seed node $v \in \Csig[\Xbf]^g$.
-Then, for any $n$ large enough so that
-  \begin{equation*}
-  n \geq c_1(\Pbb,r)\cdot (\log n)^{\max\{\frac{3}{d},1\}}
-  \end{equation*}
-  the volume of the symmetric set difference is upper bounded
-  \begin{equation}
-    \label{eqn:volume_ssd}
-    \Delta(\Csig[\Xbf], \Cest) \leq c \cdot \kappa(\Cset) \cdot \vol_{n,r}(\Csig[\Xbf]),
-  \end{equation}
-  with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$. 
+  \label{thm: volume_ssd}
+  Fix $\lambda,\sigma > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a   
+  $\kappa$-well-conditioned density cluster, and assume Algorithm \ref{alg: ppr}
+  is well-initialized with respect to $\Cset$. There exists a set $\Csig[\Xbf]^g 
+  \subseteq \Csig[\Xbf]$ of large volume, \smash{$\vol(\Csig[\Xbf]^g; G_{n,r})
+    \geq \vol(\Csig[\Xbf];G_{n,r})/2$}, such that the following holds: if 
+  Algorithm~\ref{alg: ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then
+  for 
+  $$
+  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
+  $$
+  the PPR estimated cluster \smash{$\Cest$} satisfies
+  \begin{equation}
+    \label{eqn: volume_ssd}
+    \Delta(\Cest, \Csig[\Xbf]) \leq c \cdot \kappa(\Cset) \cdot
+    \vol_{n,r}(\Csig[\Xbf]),  
+  \end{equation}
+  with probability at least $1 - b_2/n$. 
 \end{theorem}
-The proof of Theorem \ref{thm:volume_ssd} is deferred to Appendix~\ref{sec:proof_of_volume_ssd}.
-We reiterate that the primary technical work involved in proving Theorem~\ref{thm:volume_ssd} involves showing that $\tau_{u}$ and $\phi_u$ are valid upper bounds on the normalized cut and mixing time; once this is established, the result follows more or less straightforwardly from~\citet{zhu2013}.
-This result establishes that the volume of the symmetric set difference \smash{$\Delta(\Csig[\Xbf],
-  \Cest)$} is upper-bounded by a quantity proportional to the difficulty of the clustering problem, as
-measured by the condition number $\kappa(\Cset)$.
-
-\subsection{Consistent Cluster Recovery}
-The bound on symmetric set difference \eqref{eqn:volume_ssd} does not imply consistent density cluster estimation in the sense of \eqref{eqn: consistent_density_cluster_recovery}.
-This notion of consistency requires a uniform bound over
-the PPR vector $\pbf_v$: as an example, suppose that we were able to show that for all \smash{$\Cset'
-  \in \Cbb_f(\lambda), \Cset' \neq \Cset$}, and each $u \in \Cset, w \in
-\Cset'$,  
+
+The proof of Theorem \ref{thm: volume_ssd}, as with all results in this paper,
+is deferred to the appendix.  We reiterate that the primary technical 
+work involved in proving Theorem~\ref{thm: volume_ssd} involves showing that
+$\Phibf(\Cset)$ and $\taubf(\Cset)$ in \eqref{eqn: condition_number} are
+valid upper bounds on the normalized cut and mixing time; once this has been 
+established, the result follows more or less straightforwardly
+from \citet{zhu2013}.  
+% This result establishes that the volume of the symmetric
+% set difference \smash{$\Delta(\Cest, \Csig[\Xbf])$} is upper-bounded by a  
+% quantity proportional to the difficulty of the clustering problem, as measured 
+% by the condition number $\kappa(\Cset)$.
+
+\subsection{Consistent cluster recovery}
+
+The bound on symmetric set difference \eqref{eqn: volume_ssd} does not imply 
+consistent density cluster estimation in the sense of \eqref{eqn:
+  consistent_density_cluster_recovery}. This notion of consistency requires a
+uniform bound over the PPR vector $\pbf_v$: as an example, suppose that we were
+able to show that for all \smash{$\Cset' \in \Cbb_f(\lambda), \Cset' \neq
+  \Cset$}, and each $u \in \Cset, w \in \Cset'$,  
 \begin{equation}
 \label{eqn: ppr_gap}
-\frac{\pbf_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} < \frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \frac{\pbf_v(u)}{D_{uu}}.
-\end{equation}
-Then, any $(L,U)$ satisfying~\eqref{eqn: initialization} and any sweep cut $S_{\beta}$ for $\beta \in (L,U)$ will fulfill both conditions
-laid out in \eqref{eqn: consistent_density_cluster_recovery}. In Theorem
+\frac{\pbf_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} <
+\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \frac{\pbf_v(u)}{D_{uu}}. 
+\end{equation}
+Then, any $(L,U)$ satisfying~\eqref{eqn: initialization} and any sweep cut
+$S_{\beta}$ for $\beta \in (L,U)$ will fulfill both conditions laid out in
+\eqref{eqn: consistent_density_cluster_recovery}. In Theorem 
 \ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently 
-small upper bound on $\kappa(\Cset)$ ensures that with high probability the uniform bound~\eqref{eqn: ppr_gap} is satisfied, and hence implies \smash{$\Cest$} will be a consistent  
-estimator. We will need one additional regularity condition, to preclude arbitrarily low degree
-vertices for points $x \in \Cset'[\Xbf]$. 
+small upper bound on $\kappa(\Cset)$ ensures that with high probability the
+uniform bound~\eqref{eqn: ppr_gap} is satisfied, and hence implies
+\smash{$\Cest$} will be a consistent  estimator. We will need one additional 
+regularity condition, to preclude arbitrarily low degree vertices for points $x
+\in \Cset'[\Xbf]$.
+
 \begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{6}
+  \setcounter{enumi}{4}
 \item 
@@
   as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and
-  for all $x \in \Csig'$, $\lambda_{\sigma} \leq f(x)$. 
+  for all $x \in \Csig'$, it holds that $\lambda_{\sigma} \leq f(x)$. 
 \end{enumerate}
@@
   \label{thm: consistent_recovery_of_density_clusters}
-  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
-  $\kappa$-well-conditioned density cluster for some $\sigma > 0$, and
-  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
-  \ref{alg: ppr} is well-initialized with respect to $\Cset$ and if 
-  %, there exists a universal constant $c >  0$ and constants in sample size $c_1(\Pbb,r)$-$c_6(\Pbb,r)$ such that if  
+  Under the assumptions of Theorem \ref{thm: volume_ssd}, additionally assume 
+  \ref{asmp: C'_bounded_density}, and 
   \begin{equation}
@@
     \kappa(\Cset) \leq c \frac{(\lambda_{\sigma} r^d
-      \nu_d)^2}{\vol_{\Pbb,r}(\Csig)}, 
-  \end{equation}
-  then the following statement holds: there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume 
-  with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$ such that if Algorithm~\ref{alg: ppr} is run with any seed node $v \in \Csig[\Xbf]^g$,  then for any $n$ large enough so that
-  \begin{equation*}
-  n \geq c_1(\Pbb,r)\cdot (\log n)^{\max\{\frac{3}{d},1\}}
-  \end{equation*}$\Cest$ satisfies~\eqref{eqn: consistent_density_cluster_recovery} with respect to $\Cset$ with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$.
-Therefore, $\Cest$ is a consistent estimator of $\Cset$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
+      \nu_d)^2}{\vol_{\Pbb,r}(\Csig)}.
+  \end{equation}
+  There exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, 
+  \smash{$\vol(\Csig[\Xbf]^g; G_{n,r}) \geq
+    \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$}, such that if Algorithm~\ref{alg:
+    ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then for
+  $$
+  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
+  $$
+  the PPR estimated cluster \smash{$\Cest$} satisfies \eqref{eqn:
+    consistent_density_cluster_recovery} with probability at least $1-b_2/n$.
 \end{theorem}
-\noindent Some remarks are in order: 
- \begin{enumerate}  
- \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
-    kappa_ub} results in an upper bound on the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
-    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
-  density cluster $\Cset$ in the sense of \eqref{eqn:
-    consistent_density_cluster_recovery} only when we can guarantee a very small
-  fraction of points will be misclassified. This strong condition is the price
-  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
- \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
-  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
-  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
-  $\kappa(\Cset)$ prevents us from making claims about the
-  behavior of PPR in this regime. Although the restriction to a kernel
-  function fixed in $n$ is common in spectral clustering theory
-  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
-  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
-  this is merely looseness in our upper bounds.  
-\end{enumerate}
+
+Some remarks are in order.
+
+\begin{remark}
+We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: 
+    kappa_ub} results in an upper bound on the symmetric set difference metric
+  \smash{$\Delta(\Cest, \Csig[\Xbf])$} on the order of $r^d$. In plain terms, we 
+  are able to recover a  density cluster $\Cset$ in the strong sense of
+  \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a
+  very small fraction of points will be misclassified. This strong condition is
+  the price we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}.  
+\end{remark}
+
+\begin{remark}
+  Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to  
+  \infty$, would be computationally attractive (it would ensure that the graph 
+  $G_{n,r}$ is sparse), but the presence of a factor of \smash{$\log^2(1/r)/r$}
+  in $\kappa(\Cset)$ prevents us from making claims about the behavior of PPR in
+  this regime. Although the restriction to a kernel function fixed in $n$ is
+  common in spectral clustering theory \citep{schiebinger2015,vonluxburg2008},
+  it is an interesting question whether PPR exhibits some degeneracy over 
+  neighborhood graphs such that $r \to 0$, or if this is merely looseness in our  
+  upper bounds.
+\end{remark}
 
 \subsection{Approximate PPR vector}
+
 In practice, exactly solving the system of equations~\eqref{eqn:
@@
 For a sufficiently small choice of $\varepsilon$, the 
-application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters}
+application of \eqref{eqn: appr_error} within the proofs of Theorems
+\ref{thm: volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters}  
 leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}.
@@
   \label{cor: appr}
-	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well-conditioned cluster for some $\sigma > 0$.
-Choose input parameters $r, \alpha, v, (L,U)$ to be well-initialized in the sense of \eqref{eqn: initialization}, additionally set
+  Under the assumptions of Theorem \ref{thm: volume_ssd}, consider instead of
+  Algorithm \ref{alg: ppr}, using the approximate PPR vector from
+  \citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
+  corresponding cluster estimate \smash{$\Cest$} in the same manner.  Then 
+  provided we take 
   \begin{equation}
     \label{eqn: appr_parameter}
-	\varepsilon = \frac{1}{25}\vol_{\Pbb,r}(\Csig)
-	\end{equation}
-	and modify Algorithm \ref{alg: ppr} to compute the a\pprspace vector $\pbf^{(\varepsilon)}_v$ rather than the exact \pprspace vector $\pbf_v$, with resulting output $\Cest$. Then
-	\begin{enumerate}
-		\item The upper bound on symmetric set difference metric $\Delta(\Cest,\Csig[\Xbf])$ given by \eqref{eqn:volume_ssd} is still valid.
-		\item If \ref{asmp: C'_bounded_density} and \eqref{eqn: kappa_ub} hold, 
-		then $\Cest \subseteq \Xbf$ is a consistent estimator for $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-	\end{enumerate}
+    \varepsilon = \frac{1}{25} \vol_{\Pbb,r}(\Csig),
+  \end{equation}
+  the upper bound on symmetric set difference in \eqref{eqn: volume_ssd} still
+  holds. Further, under the assumptions of Theorem \ref{thm:
+    consistent_recovery_of_density_clusters}, the estimator \smash{$\Cest$} is
+  still consistent, in the sense of Definition \ref{def:
+    consistent_density_cluster_estimation}.  
 \end{corollary}
 
-\section{Analysis Overview}
+\section{Analysis overview}
 \label{sec: analysis}
 
-One of the primary technical contributions of our work is showing that the geometric
-conditions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} translate to 
-meaningful bounds on the normalized cut and mixing time of $\Csig[\Xbf]$ in
-$G_{n,r}$. In doing so, we elaborate on how some of the geometric conditions
-introduced in Section~\ref{sec: consistent_cluster_estimation_with_ppr}
-contribute to the difficulty of the clustering problem.
-
-\subsection{Upper Bound on the Normalized Cut} 
-We start with a finite sample upper bound on the
-normalized cut \eqref{eqn: normalized_cut} of $\Cset_\sigma[\Xbf]$. For
-simplicity, we write $\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
+The primary technical contribution in our work is to show that the
+geometric assumptions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} 
+translate to  meaningful bounds on the normalized cut and mixing time of 
+$\Csig[\Xbf]$ in the neighborhood graph $G_{n,r}$. In doing so, we elucidate 
+how these geometric conditions contribute to the difficulty of the clustering 
+problem.
+
+\subsection{Upper bound on normalized cut}
+
+We start with a finite-sample upper bound on the normalized cut \eqref{eqn:
+  normalized_cut} of $\Cset_\sigma[\Xbf]$. For simplicity, we write
+$\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
 
@@
   \label{thm: conductance_upper_bound}
-  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
-  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
-  \ref{asmp: bounded_volume} for some $\sigma > 0$. Then
+  Fix $\lambda,\sigma>0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies    
+  Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and   
+  \ref{asmp: bounded_volume}. Then
   \begin{equation}
@@
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
-  \end{equation}
-  with probability at least $1 - 3\exp\{-nc_3(\Pbb,r)\}$. 
+      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
+  \end{equation}
+  with probability at least $1 - 3\exp\set{-b n}$. 
 \end{theorem}
-\noindent {\bf Remark: } 
+
+\begin{remark}
   Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
-    conductance_upper_bound}, in contrast to the condition number
-  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This
-  reflects established wisdom regarding spectral partitioning
+    conductance_upper_bound}, in contrast to ultimate bound in Theorem    
+  \ref{thm: volume_ssd} (where the diameter enters through the condition number 
+  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This reflects
+  (what may be regarded as) established wisdom regarding spectral partitioning
   algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
-  to the density clustering setting. It suggests that if the diameter $\rho$ is
-  large, PPR may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is
-  sufficiently well-conditioned to ensure $\Csig[\Xbf]$ has a small normalized
-  cut in $G_{n,r}$. This intuition will be supported by simulations in Section
-  \ref{sec: experiments}.
-
-\subsection{Upper Bounds on the Mixing Time} 
+  to the density clustering setting: if the diameter $\rho$ is large, then PPR
+  may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently
+  well-conditioned to ensure that $\Csig[\Xbf]$ has a small normalized cut in 
+  $G_{n,r}$. This will be supported by simulations in Section \ref{sec:
+    experiments}.   
+\end{remark}
+
+\subsection{Upper bound on mixing time}
+
 For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
-subgraph induced by $S$ (where the edges are $E_S = E \cap (S \times S)$). Let
-$\Wbf_S$ be the (lazy) random walk matrix over $G[S]$, and write  
+subgraph induced by $S$ (where $E_S = E \cap (S \times S)$). Let 
+$\Wbf_S$ be the lazy random walk matrix over $G[S]$, and write  
 $$
@@
 $$
-for the $t$-step transition probability of the lazy random walk over $G[S]$
-originating at $v \in V$. Also write \smash{$\pi = (\pi(u))_{u \in S}$}
-for the stationary distribution of this random walk.(As
-$\Wbf_S$ is the transition matrix of a lazy random walk, 
-it is well-known that a unique stationary distribution exists and is given by 
-\smash{$\pi(u) = \deg(u;G[S])/\vol(S; G[S])$}, where we write $\deg(u;G[S]) = \sum_{w \in S} \1((u,w) \in E_S)$ for the degree of $u$ in $G[S]$.) We define the \emph{mixing time} of $G[S]$ as
+for the $t$-step transition probability of the random walk over $G[S]$
+originating at $v \in V$. Also let \smash{$\pi = (\pi(u))_{u \in S}$} be 
+the stationary distribution of this random walk. (As $\Wbf_S$ is the transition 
+matrix of a lazy random walk, it is well-known that a unique stationary
+distribution exists and is given by  \smash{$\pi(u) = \deg(u;G[S])/\vol(S;
+  G[S])$}, where we write $\deg(u;G[S]) = \sum_{w \in S} \1((u,w) \in E_S)$ for
+the degree of $u$ in $G[S]$.) We define the \emph{mixing time} of $G[S]$ as 
 \begin{equation}
@@
   \label{thm: mixing_time_upper_bound}
-  Fix $\lambda > 0$, and assume that \smash{$\Cset \in \Cbb_f(\lambda)$}
-  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
-  for some $\sigma > 0$. Additionally assume that the radius $0 < r < \sigma/2\sqrt{d}$. Then the following statement holds: for any
-  \begin{equation*}
-  n \geq c_1(\Pbb,r)\cdot(\log n)^{\max\{\frac{3}{d},1\}}
-  \end{equation*}
-  the mixing time $\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$ satisfies
+  Fix $\lambda, \sigma > 0$, and assume \smash{$\Cset \in \Cbb_f(\lambda)$} 
+  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
+  Also assume that \smash{$0 < r \leq \sigma/(2\sqrt{d})$}. Then for
+  $$
+  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
+  $$
+  the mixing time satisfies
   \begin{equation} 
     \label{eqn: mixing_time_upper_bound}
-    \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{ \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3
-  \end{equation}
-  with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
+    \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 
+      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{
+        \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3, 
+  \end{equation}
+  with probability at least $1 - b_2/n$.
 \end{theorem}
 The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
-analogous mixing time bounds developed for the mixing time of a
-continuous-space ``ball walk'' over convex sets. To the best of our knowledge, our
-result is the first bound on the mixing time of random walks
-over neighborhood graphs that is independent of $n$, the number of vertices.
-
-\vspace{0.2cm}
-
-\noindent {\bf Remark: } 
+analogous mixing time bounds developed for a continuous-space ``ball walk'' over
+convex sets. To the best of our knowledge, our result is the first bound on the
+mixing time of random walks over neighborhood graphs that is independent of $n$,
+the number of vertices.
+
+\begin{remark}
   The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
-  play an important role in proving the upper bound of Theorem \ref{thm:
+  play an important role in proving the upper bound in Theorem \ref{thm:
     mixing_time_upper_bound}. There is some interdependence between $L$ and
@@
   for reasonably small values of $L$. 
-
-\section{Lower bound.}
+\end{remark}
+
+\section{Negative result}
 \label{sec:lower_bound}
 
-To show a lower bound for density clustering using PPR, we exhibit a hard case: that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
-Let $\mathcal{C}_{\sigma}^{(0)}$, $\mathcal{C}_{\sigma}^{(1)}$, and $\mathcal{C}_{\sigma}^{(2)}$ be rectangles in $\Reals^2$,
-\begin{equation*}
-\mathcal{C}_{\sigma}^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times \biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad \mathcal{C}_{\sigma}^{(1)} = \mathcal{C}_{\sigma}^{(0)} - \set{(\sigma,0)}, \quad \mathcal{C}_{\sigma}^{(2)} = \mathcal{C}_{\sigma}^{(0)} + \set{(\sigma,0)} \tag{$0 < \sigma < \rho$}
-\end{equation*}
-and let $\mathbb{P}$ be the mixture distribution over $\mathcal{X} = \mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)} \cup \mathcal{C}_{\sigma}^{(2)}$ given by
-\begin{equation*}
-\mathbb{P} = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 + \frac{\epsilon}{2} \Psi_0,
-\end{equation*}
-where $\Psi_m$ is the uniform distribution over $\Csig^{(m)}$ for $m = 0,1,2$. 
+In this section, we exhibit a hard case for density clustering using PPR, that 
+is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
+cluster. Let \smash{$\Cset^{(0)}, \Cset^{(1)}, \Cset^{(2)}$} be rectangles in
+$\Reals^2$,    
+$$
+\Cset^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times 
+\biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
+\Cset^{(1)} = \Cset^{(0)} - \set{(\sigma,0)}, \quad
+\Cset^{(2)} = \Cset^{(0)} + \set{(\sigma,0)},
+$$
+where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over
+\smash{$\mathcal{X} = \Cset^{(0)} \cup \Cset^{(1)} \cup \Cset^{(2)}$} given by   
+$$
+\Pbb = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 +
+\frac{\epsilon}{2} \Psi_0, 
+$$
+where $\Psi_k$ is the uniform distribution over $\Cset^{(k)}$ for $k = 0,1,2$.  
 The density function $f$ of $\Pbb$ is simply
@@
 \label{eqn:lb_density}
-f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(2)}) + \frac{\epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(0)})  \right)
-\end{equation}
-so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_{\sigma}^{(1)}, \mathcal{C}_{\sigma}^{(2)}}$.
-Figure~\ref{fig:fig0} shows $f$ for two different choices of $\epsilon, \sigma$ and $\rho$.
+f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in
+  \Cset^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \Cset^{(2)}) +
+  \frac{\epsilon}{2}\1(x \in \Cset^{(0)})  \right), 
+\end{equation}
+so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have 
+\smash{$\Cbb_f(\lambda) = \set{\Cset^{(1)}, \Cset^{(2)}}$}. Figure~\ref{fig:
+  hard_case} visualizes the density $f$ for two different choices of $\epsilon,
+\sigma, \rho$.
 
@@
   \centering
-
-	\includegraphics[width=0.4\textwidth]{lower_bound_plots/lower_bound_1}
-	\includegraphics[width=0.4\textwidth]{lower_bound_plots/lower_bound_2}
-
-	\caption{\it\small The density $f$ given by~\eqref{eqn:lb_density}, for two different choices of $\epsilon$ and $\sigma$.
-Left: $\epsilon = .3,\sigma = .1$; Right: $\epsilon = .2,\sigma = .2$.
-In both $\rho = 1$.
-}
-	\label{fig:fig0}
-
+  \includegraphics[width=0.495\textwidth]{lower_bound_plots/lower_bound_1}
+  \includegraphics[width=0.495\textwidth]{lower_bound_plots/lower_bound_2}
+  \caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
+    $\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
+    $\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
+    $\sigma = 0.2$.} 
+  \label{fig: hard_case}
 \end{figure}
 
-\subsection{Lower bound for PPR.}
-
-As the following theorem demonstrates, even when Algorithm~\ref{alg: ppr} is reasonably initialized, if the density cluster $\mathcal{C}_{\sigma}^{(1)}$ is sufficiently geometrically ill-conditioned the cluster estimator $\widehat{C}$ will fail to recover $\mathcal{C}_{\sigma}^{(1)}$.
-Let
+\subsection{Lower bound on symmetric set difference}
+
+As the following theorem demonstrates, even when Algorithm~\ref{alg: ppr} is
+reasonably initialized, if the density cluster \smash{$\Cset^{(1)}$} is 
+sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
+estimator $\Cest$ will fail to recover \smash{$\Cset^{(1)}$}. Let  
 \begin{equation}
@@
 \end{equation}
+
 \begin{theorem}
   \label{thm:ppr_lb}
-	Suppose $r < \frac{1}{40}\rho \wedge \frac{1}{4}\sigma$,  $\alpha = 65 \Phi_{\Pbb}(\mathcal{L})$, and $(L,U) = (0,1)$ are inputs to Algorithm~\ref{alg: ppr}. Then, for any
-	\begin{equation}
-	\label{eqn:lb_sample_size}
-	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2}, \frac{8}{\epsilon}}
-	\end{equation}
-	the following statement holds: there exists a set $C^{g} \subset \Xbf$ with $\vol(C^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$ such that for any seed node $v \in C^g$, the estimator $\widehat{C}$ computed by Algorithm~\ref{alg: ppr} has symmetric set difference with $\Csig^{(1)}[\Xbf]$ of volume at least
+  Assume Algorithm~\ref{alg: ppr} is initialized using inputs $r < 
+  \min\set{\frac{1}{40}\rho, \frac{1}{4}\sigma}$, $\alpha = 65  
+  \Phi_{\Pbb}(\mathcal{L})$, and $(L,U) = (0,1)$.  Then, for any 
+  $$
+  n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2},
+    \frac{8}{\epsilon}}, 
+  $$
+  there exists a set $\Cset[X]^g$ of large volume, \smash{$\vol(\Cset[X]^g \cap 
+    \Cset^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset^{(1)}[\Xbf])$}, such
+  that for any seed node $v \in \Cset[X]^g$, the PPR estimated cluster
+  \smash{$\Cest$} satisfies    
   \begin{equation}
     \label{eqn:ppr_lb}
-	\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2} \geq \frac{1}{4} -  c \frac{\sqrt{\frac{\sigma}{\rho}}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
-	\end{equation}
-	with probability at least $1 - c_1(\Pbb,r) n \exp\set{-c_2(\Pbb,r)n}$.
-	Consequently, if
-	\begin{equation*} 
-	\epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
-	\end{equation*}
-	then with high probability $\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2}$ is at least $1/8$. 
+    \frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle
+    \Cset^{(1)}[\Xbf]) \geq \frac{1}{4} -  c
+    \frac{\sqrt{\sigma/\rho}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}
+        {\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
+  \end{equation}
+  with probability at least $1 - b_1 n \exp\set{-b_2 n}$.  Consequently, if
+  $$
+  \epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ 
+    \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}, 
+  $$
+  then with high probability \smash{$\frac{\sigma
+    \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) 
+  \geq 1/8$}.    
 \end{theorem}
-Note that the factor of $\frac{\sigma\rho}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\ref{thm:volume_ssd}.
-
-Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.
-Although we picked this setting to make the theorem statement simple, our results are easily generalized to $\Reals^d$ and to non-rectangular clusters.
-Additionally, although we state our lower bound with respect to PPR run on neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
-In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\frac{\sigma}{\rho}$, the normalized cut of $\Csig^{(1)}$ will be much larger than that of $\mathcal{L}$.
-In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Csig^{(1)}$.
-In particular, local spectral clustering algorithms based on truncated random walks \citet{spielman2013}, global spectral clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings \citet{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that all the aforementioned approaches would fail to estimate $\Csig^{(1)}$.
-
-\subsection{Comparison with upper bound.}
-
-To better digest the implications of Theorem~\ref{thm:ppr_lb}, we apply our upper bound to the density function $f$ given in \eqref{eqn:lb_density}.
-Observe that $\Csig^{(1)}$ satisfies each of the assumptions~\ref{asmp: bounded_density}-\ref{asmp: bounded_volume}.
-In particular
+
+Note that $\vol_{n,r}(\Cset^{(1)})$ for large enough $n$ will be of the order
+$n^2 r^2/(\sigma\rho)$, and therefore the quantity \smash{$\frac{\sigma
+    \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf])$} in 
+\eqref{eqn:ppr_lb} is comparable to \smash{$\vol_{n,r}(\Cest
+  \vartriangle \Cset^{(1)}[\Xbf]) / \vol_{n,r}(\Cset^{(1)}[\Xbf])$}, which
+corresponds to the quantity we upper bound in Theorem~\ref{thm: volume_ssd}.
+
+Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where
+the density clusters are rectangular subsets of $\Reals^2$.  We chose this
+setting to make the theorem simple to state, and our results are generalizable
+to $\Reals^d$ and to non-rectangular clusters.  Moreover, although we state
+our lower bound with respect to PPR run on neighborhood graph, the conclusion is
+likely to hold for a much broader class of spectral clustering algorithms. In
+the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when
+$\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of
+$\Cset^{(1)}$ will be much larger than that of $\mathcal{L}$. In this case, not
+merely PPR but any algorithm that approximates the minimum normalized cut is
+unlikely to recover $\Cset^{(1)}$. In particular, local spectral clustering
+algorithms based on truncated random walks \citet{spielman2013}, global spectral
+clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings
+\citet{hein2010} all have provable upper bounds on the normalized cut of cluster
+they output, and thus we expect that they would all fail to estimate
+$\Cset^{(1)}$.
+
+\subsection{Comparison with previous upper bound}
+
+To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
+results of our upper bound in Theorem~\ref{thm: volume_ssd} to the density $f$
+given in \eqref{eqn:lb_density}. Observe that $\Cset^{(1)}$ satisfies each of
+the Assumptions~\ref{asmp: bounded_density}--\ref{asmp: bounded_volume}:
+
 \begin{enumerate}[label=(A\arabic*)]
-	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in \Csig^{(1)}$.
-	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such that $0 < \dist(x,\Csig^{(1)}) \leq \sigma$. Therefore for all such $x$,
-	\begin{equation*}
-	\inf_{x' \in \Csig^{(1)}} f(x') - f(x)  > \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma}.
-	\end{equation*}
-	\item The set $\Csig^{(1)}$ is itself convex, and has diameter $\rho$.
-	\item By symmetry, $\vol_{\Pbb,r}(\Csig^{(1)}) = \vol_{\Pbb,r}(\Csig^{(2)})$ and therefore $\vol_{\Pbb,r}(\Csig^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$. 
+\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
+  \Cset^{(1)}$.  
+\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such
+  that $0 < \dist(x,\Cset^{(1)}) \leq \sigma$. Therefore for all such $x$, 
+  $$
+  \inf_{x' \in \Cset^{(1)}} f(x') - f(x)  = \left\{\frac{1 - \epsilon}{2} -
+    \epsilon \right\} \frac{1}{\rho \sigma},
+  $$
+  which meets the decay requirement with exponent $\gamma=0$. 
+\item The set $\Cset^{(1)}$ is itself convex, and has diameter $\rho$.
+\item By symmetry, \smash{$\vol_{\Pbb,r}(\Cset^{(1)}) =
+    \vol_{\Pbb,r}(\Cset^{(2)})$}, and therefore
+  \smash{$\vol_{\Pbb,r}(\Cset^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$}.   
 \end{enumerate}
 
-%Technically, this density does not fit nicely into the setup of Theorem~\textcolor{red}{1}, because the sets $\Cset_{\sigma}^{(m)}$ ($ m = 1,2$) play the role of both the $\sigma$-expanded sets and the density clusters themselves.
-However, this truly is only a technical objection.
-One could modify the distribution $\Pbb$ by adding a small amount of mass to the $\sigma$-interior $\Cset^{(m)} = \set{x \in \Cset_{\sigma}^{(m)}: \dist(x,\partial\Cset_{\sigma}) \geq \sigma}$.
-Appropriately choosing a threshold $\lambda > \frac{(1 - \epsilon)}{2\rho\sigma}$, the resulting $\lambda$-density clusters would be $\Cbb_f(\lambda) = \set{\Cset^{(1)},\Cset^{(2)}}$, and their $\sigma$-expansions would resemble the rectangles $\Csig^{(1)}, \Csig^{(2)}$ except with slightly rounded corners.
-%Alternatively, one could directly modify Lemma~\textcolor{red}{6} -- an auxiliary Lemma, used in the proof of Theorem~\textcolor{red}{3}, which establishes an upper bound on the Lebesgue measure of $\Csig + B(0,r)$ -- to hold under the assumption $\Csig$ is a rectangle of width $\sigma$ rather than a $\sigma$-expansion.
-The proof of this Lemma is the only time we use the fact that $\Csig$ is a $\sigma$-expansion of a density cluster.
-\textcolor{red}{(Ryan and Siva.)}
-
-\vspace{0.2cm}
-
-\textbf{Remark:}~~Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners. To fix this, one can 
-%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume} in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with respect to rectangles of width $\sigma$, or 
-change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
-With some additional bookkeeping, using rounded rectangles does not change our lower bound significantly so we ignore this technicality in our
-subsequent discussion.
-
-\vspace{0.2cm}
-
-If the user-specified parameters are initialized according to~\eqref{eqn: initialization}, we may apply Theorem~\ref{thm:volume_ssd}.
-This implies that there exists a set $\Csig^{(1)}[\Xbf] \subset \Csig^{(1)}$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any seed node $v \in \Csig^{(1)}[\Xbf]$, the estimated cluster $\widehat{C}$ output by Algorithm 1 satisfies the following upper bound:
-\begin{equation*}
-\vol_{n,r}(\widehat{C} \vartriangle \Csig^{(1)}[\Xbf]) \leq c \cdot \kappa(\Cset^{(1)}) \cdot \vol_{n,r}(\Csig^{(1)}[\Xbf])
-\end{equation*}
-where the condition number is given by
-\begin{equation*}
-\kappa(\Cset^{(1)}) = c \frac{\epsilon}{\sigma}\left(\frac{\rho^2}{r}\log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c\right).
-\end{equation*}
-
-To facilitate comparisons between our upper and lower bounds, assume $\frac{1}{4}\sigma \leq \frac{1}{40}\rho$ and set $r = \frac{1}{4}\sigma$. 
-For some universal constant $c > 0$, the following statements each hold with high probability:
+\begin{remark}
+Technically, the rectangles $\Cset^{(0)},\Cset^{(1)},\Cset^{(2)}$ are not
+$\sigma$-expansions due to their sharp corners. To fix this, one can   
+%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume}
+%in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with
+%respect to rectangles of width $\sigma$, or  
+simply modify these sets to have appropriately rounded corners, and our lower
+bound arguments do not need to change significantly, subject to some
+additional bookkeeping.  Thus we ignore this technicality in our subsequent
+discussion. 
+\end{remark}
+
+If the user-specified parameters are initialized according to~\eqref{eqn:
+  initialization}, we may apply Theorem~\ref{thm: volume_ssd}. This implies that 
+there exists a set $\Cset^{(1)}[\Xbf] \subseteq \Cset^{(1)}$ with
+\smash{$\vol_{n,r}(\Cset[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Cset[\Xbf])$} such
+that for any seed node $v \in \Cset^{(1)}[\Xbf]$, and for large enough $n$, the
+PPR estimated cluster $\Cest$ satisfies with high probability
+$$
+\vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) \leq c \cdot
+\kappa(\Cset^{(1)}) \cdot \vol_{n,r}(\Cset^{(1)}[\Xbf]), 
+$$
+where the condition number may be taken to be
+$$
+\kappa(\Cset^{(1)}) = c_1 \frac{\epsilon}{\sigma} 
+\left(\frac{\rho^2}{r} \log^2\left(\frac{1}{r}\right) \right) + c_2. 
+$$
+for universal constants $c_1,c_2>0$. To facilitate comparisons between our upper
+and lower bounds, assume $\sigma/4 \leq \rho/40$ and set $r = \sigma/4$.  Then
+the following statements each hold with high probability.
+
 \begin{itemize}
-	\item If the user-specified parameters satisfy~\eqref{eqn: initialization}, and additionally for some $b > 0$
-	\begin{equation*}
-	\epsilon < c\frac{b\sigma^2}{\rho^2 \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2\sigma}\right)}
-	\end{equation*}
-	then $\Delta(\widehat{C}, \Csig^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\Csig^{(1)}[\Xbf])$.
-	\item If the user-specified parameters are given as in Theorem~\ref{thm:ppr_lb}, and 
-	\begin{equation*}
-	\epsilon > c\left({\frac{\sigma}{\rho}} \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\right)^{1/4}
-	\end{equation*}
-	then $\Delta(\widehat{C}, \Csig^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\Csig^{(1)}[\Xbf])$.
+\item If the user-specified parameters satisfy~\eqref{eqn: initialization}, and
+  for some $c > 0$
+  $$
+  \epsilon < c \left(\frac{\sigma}{\rho \log(1/\sigma)}\right)^2,
+  $$
+  then \smash{$\Delta(\Cest, \Cset^{(1)}[\Xbf]) \leq c \cdot
+    \vol_{n,r}(\Cset^{(1)}[\Xbf])$}.
+
+\item If the user-specified parameters are as in Theorem~\ref{thm:ppr_lb},
+  and for some $c>0$
+  $$
+  \epsilon > c \left({\frac{\sigma}{\rho}} \log^2 \left(\frac{\rho}
+      {\epsilon^2 \sigma}\right)\right)^{1/4},
+  $$
+  then \smash{$\Delta(\Cest, \Cset^{(1)}[\Xbf]) \geq \frac{1}{8}
+    \vol_{n,r}(\Cset^{(1)}[\Xbf])$}. 
 \end{itemize}
 
-Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-geometrically conditioned for recovery using PPR.
-
-\vspace{0.2cm}
-
-\textbf{Remark:}~~It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
-We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
-
-%It is worth pointing out that both our lower and upper bounds are stated with respect to specific choices of the input parameters to Algorithm~\ref{alg: ppr}, and that these choices are in fact different in the case of the teleportation parameter $\alpha$ and sweep cut range $(L,U)$.
-At a high level, we do not believe this substantially weakens the takeaway messages of our work: if a density cluster $\mathcal{C}$ is geometrically well-conditioned, then a reasonable initialization of PPR will recover $\Csig[\Xbf]$ with low error, whereas if it is geometrically poorly-conditioned, then a different but also reasonable initialization of PPR will fail to recover $\Csig[\Xbf]$.
-Of course, it would be more satisfying if both our upper and lower bounds could be stated with respect to the same choices of these input parameters.
-Unfortunately, it is not at all obvious how to prove such a claim, as to the best of our knowledge all existing work on PPR assumes similar initialization conditions to the ones we assume; effectively, that the algorithm is well-initialized with respect to the set $S \subset G$ one is interested in recovering.
-We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
-Even so, we reiterate our belief that in tandem our upper and lower bounds represent a substantial step forward in characterizing the behavior of local clustering algorithms in a statistical context \textcolor{red}{(Ryan and Siva)}.
-
-\vspace{0.2cm}
-
-\textbf{Remark:}~~We also note that our lower bound is of course specific to the PPR algorithm.
-As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
-That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
-Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
+Jointly, these upper and lower bounds give a relatively precise characterization
+of what it means for a density cluster to be well- or poorly-geometrically
+conditioned for recovery using PPR.
+
+\begin{remark}
+It is worth pointing out that the above conclusions are reliant on specific
+(albeit reasonable) ranges and choices of input parameters, which in some
+instances differ between the upper and lower bounds. We suspect that our lower
+bound continues to hold even when choosing input parameters as dictated by our
+upper bound, but do not pursue the details.
+\end{remark}
+
+\begin{remark}
+It is not hard to show that, in the example under consideration, classical
+plug-in density cluster estimators can consistently recover the
+$\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even if $\epsilon$ is
+large compared to $\sigma/\rho$. That PPR has trouble recovering density
+clusters here (where standard plug-in approaches do not) is not meant to
+be a knock on PPR. Rather, it simply reflects that while classical density
+clustering approaches are specifically designed to identify high-density regions
+regardless of their geometry, PPR relies on geometry as well as density when
+forming the output cluster. 
+\end{remark}
 
@@
   \centering
-  % \begin{adjustbox}{minipage=\linewidth}
-  %   \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/sample2}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/sample1}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/sigma_normalized_cut_plot}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/sigma_mixing_time_plot}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/diameter_normalized_cut_plot}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.33\linewidth}
   \includegraphics[width=0.32\textwidth]{example1plots/diameter_mixing_time_plot}
-  % \caption{}
-  % \end{subfigure}
   \caption{\it\small Top left and top middle: samples from a geometrically
@@
     bounds.} 
-  \label{fig:fig1}
-%  \end{adjustbox}
+  \label{fig:bounds}
 \end{figure}
+
 \paragraph{Validating theoretical bounds.}  We investigate the tightness of
 Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-  mixing_time_upper_bound} via simulation. Figure \ref{fig:fig1} compares our
+  mixing_time_upper_bound} via simulation. Figure \ref{fig:bounds} compares our
 upper bounds with the actual empirically-computed quantities \eqref{eqn:
@@
 
-\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:fig2}, to drive home
-the main implications of Theorems \ref{thm:volume_ssd} and
-\ref{thm: consistent_recovery_of_density_clusters}, we show the
-behavior of PPR, normalized cut, and the density clustering algorithm of
-\citet{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d 
-Gaussian noise), considered a prototypical success story for spectral clustering
-algorithms. The first column shows the empirical density clusters $\Cset[\Xbf]$
-and $\Cset'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the 
-second column shows the cluster recovered by PPR; the third column shows the
-global minimum normalized cut, computed according to the algorithm of
-\citet{szlam2010}; and the last column shows a cut of the density cluster tree
-estimator of \citet{chaudhuri2010}.  We can see the degrading ability of PPR to
-recover density clusters as the two moons become less well-separated. Of 
-particular interest is the fact that PPR fails to recover one of the moons even
-when normalized cut still succeeds in doing so.
-Additionally, we note that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.
-This supports our main message, which is that PPR recovers only geometrically well-conditioned density clusters.
+\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:moons}, to drive home 
+the implications of Theorems \ref{thm: volume_ssd} and \ref{thm:
+consistent_recovery_of_density_clusters}, we show the behavior of PPR,
+normalized cut, and the density clustering algorithm of \citet{chaudhuri2010} on
+the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
+a prototypical success story for spectral clustering algorithms. The first
+column shows the empirical density clusters $\Cset[\Xbf]$ and $\Cset'[\Xbf]$ for
+a particular threshold $\lambda$ of the density function; the second column
+shows the cluster recovered by PPR; the third column shows the global minimum
+normalized cut, computed according to the algorithm of \citet{szlam2010}; and
+the last column shows a cut of the density cluster tree estimator of
+\citet{chaudhuri2010}.  We can see the degrading ability of PPR to recover
+density clusters as the two moons become less well-separated. Of particular
+interest is the fact that PPR fails to recover one of the moons even when
+normalized cut still succeeds in doing so. Additionally, we note that the
+Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
+fail.  This supports our main message, which is that PPR recovers only
+geometrically well-conditioned density clusters.
 
@@
   \centering
-  % \begin{adjustbox}{minipage=\linewidth}
-  %   \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth,scale = .5]{example2plots/row1_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row1_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row1_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row1_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row2_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row2_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row2_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row2_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row3_true_density_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row3_ppr_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row3_conductance_cluster}
-  % \caption{}
-  % \end{subfigure}
-  % \begin{subfigure}{.24\linewidth}
   \includegraphics[width=0.24\textwidth]{example2plots/row3_density_cluster}
-  % \caption{}
-  % \end{subfigure}
   \caption{\it\small True density (column 1), PPR (column 2), normalized
@@
     simulated data sets. Seed node for PPR denoted by a black cross.} 
-  \label{fig:fig2}
-  %\end{adjustbox}
+  \label{fig:moons}
 \end{figure}
@@
 appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR.
-We have also exhibited a hard case, showing that when a density cluster is sufficiently geometrically ill-conditioned, PPR may fail to recover it.
-Finally, we have empirically demonstrated the tightness of our analysis for reasonable sample sizes.
-
-\section{Acknowledgements}
-SB is grateful to Peter Bickel, Martin Wainwright and Larry Wasserman for helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+cluster by PPR. We have also exhibited a hard case, showing that when a density
+cluster is sufficiently geometrically ill-conditioned, PPR can fail to recover
+it. Finally, we have empirically demonstrated the tightness of our analysis for
+reasonable sample sizes.
+
+\section*{Acknowledgements}
+
+SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
+helpful and inspiring conversations. RJT thanks Terrence Tao for that time we
+hung out recently, and shared tips on how we each cope with massive fame.
+This work was supported in part by the NSF grant DMS-1713003.
 
@@
 	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
 	\begin{align}
@@
 	\label{lem: expected_number_boundary_points}
-	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
 	\begin{equation*}
@@
 	\end{align}
-	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.
+	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(2d)$.
 
@@
 %	\label{lem: expected_density_cut}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
 %	\begin{equation*}
@@
 %	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/2d$,
+%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
 %	\begin{equation*}
@@
 %\begin{equation*}
-%\Phi_{n,r}(\Csig[\mathbf{X}]) \leq \frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}
+%\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}
 %\end{equation*}
@@
 \end{equation*}
-It is a well known fact (see e.g.~\cite{montenegro2002}) that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
+It is a well-known fact (see e.g.~\cite{montenegro2002}) that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
 Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
@@
 Now, take $z = e_vW^3$, and trivially observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
-To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound -- the right hand side of~\eqref{eqn: tv_mixing_time}-- holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
+To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound -- the right-hand side of~\eqref{eqn: tv_mixing_time}-- holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
 
@@
 where $(ii)$ follows from the fact that for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well known (see e.g.
+As $m - 1 \geq t$, it is well-known (see e.g.
 \cite{lovasz1990}) that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and the hypothesis of Lemma \ref{lem: tv_to_uniform_distance},
@@
 	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with Lipschitz constant $L$.
-Then, for any $0 < r < \frac{\sigma}{2\sqrt{d}}$, the uniform conductance $\widetilde{\Phi}_{\nu,r}$ satisfies
+Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$, the uniform conductance $\widetilde{\Phi}_{\nu,r}$ satisfies
 	\begin{equation*}
@@
 For the moment, we will take Lemma \ref{lem: one_step_distributions} as given and prove Lemma \ref{lem: uniform_continuous_conductance}, before returning to prove Lemma \ref{lem: one_step_distributions}.
-Deriving a lower bound on conductance from a isoperimetric inequality (i.e Lemma \ref{lem: nonconvex_isoperimetry}) along with a bound on the one-step distributions is standard.
+Deriving a lower bound on conductance from a isoperimetric inequality (i.e., Lemma \ref{lem: nonconvex_isoperimetry}) along with a bound on the one-step distributions is standard.
 Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$, and let $\ell = 6/25$.
-Note by Lemma \ref{lem: local_conductance}, as $r < \sigma/(2\sqrt{d})$ $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$ for all $x \in \Csig$.
+Note by Lemma \ref{lem: local_conductance}, as $r \leq \sigma/(2\sqrt{d})$, $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$ for all $x \in \Csig$.
 We will show that
@@
 
-\section{Proof of Theorem~\ref{thm:volume_ssd}}
+\section{Proof of Theorem~\ref{thm: volume_ssd}}
 \label{sec:proof_of_volume_ssd}
 
-In this section, we prove Theorem \ref{thm:volume_ssd}. The theorem is a consequence of Lemma 3.4 in \citet{zhu2013}, which relates the quality of the PPR output to normalized cut and mixing time. 
+In this section, we prove Theorem \ref{thm: volume_ssd}. The theorem is a consequence of Lemma 3.4 in \citet{zhu2013}, which relates the quality of the PPR output to normalized cut and mixing time. 
 \begin{lemma}[Lemma 3.4 of \citet{zhu2013}.]
@@
 
-\paragraph{Proof of Theorem~\ref{thm:volume_ssd}.}
-First, we verify that the conditions of Lemma~\ref{lem:zhu} are met when $S = \mathcal{C}_{\sigma}[\Xbf]$, $G = G_{n,r}$, and the user-specified parameters satisfy the initialization conditions~\eqref{eqn: initialization}.
+\paragraph{Proof of Theorem~\ref{thm: volume_ssd}.}
+First, we verify that the conditions of Lemma~\ref{lem:zhu} are met when $S = \Cset_{\sigma}[\Xbf]$, $G = G_{n,r}$, and the user-specified parameters satisfy the initialization conditions~\eqref{eqn: initialization}.
 By Theorem~\ref{thm: mixing_time_upper_bound} and \eqref{eqn: initialization}, the teleportation parameter $\alpha$ is upper bounded
 \begin{equation*}
-\alpha < \frac{1}{9\tau_{u}(\theta)} \leq \frac{1}{9\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])}
+\alpha < \frac{1}{9\taubf(\theta)} \leq \frac{1}{9\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])}
 \end{equation*}
@@
 with probability at least $1 - 2\exp\{-\frac{1}{4} n \vol_{\Pbb,r}(\Csig)^2\}$.
-Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\widehat{C} \vartriangle \Csig[\Xbf])$.
+Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\Cest \vartriangle \Csig[\Xbf])$.
 To summarize, we have shown that when
@@
 \begin{equation*}
-\vol_{n,r}(\Csig[\Xbf] \vartriangle \widehat{C}) \leq  2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
+\vol_{n,r}(\Csig[\Xbf] \vartriangle \Cest) \leq  2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
 \end{equation*} 
 with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 3\exp\set{-(c_3(\Pbb,r) + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
-Since $c_3(\Pbb,r) \leq \vol_{\Pbb,r}(\Csig)^2$, letting $c_2(\Pbb,r) := c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)}$ we have proved Theorem~\ref{thm:volume_ssd}.
+Since $c_3(\Pbb,r) \leq \vol_{\Pbb,r}(\Csig)^2$, letting $c_2(\Pbb,r) := c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)}$ we have proved Theorem~\ref{thm: volume_ssd}.
 
@@
 \begin{equation*}
-\alpha < \frac{1}{9\tau_{u}(\theta)} \leq \frac{1}{(9 \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))}
+\alpha < \frac{1}{9\taubf(\theta)} \leq \frac{1}{(9 \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))}
 \end{equation*}
@@
 
-We defer the proof of Lemma \ref{lem: setup}, and first extend Theorems~\ref{thm:volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters} to apply with respect to the aPPR vector.
+We defer the proof of Lemma \ref{lem: setup}, and first extend Theorems~\ref{thm: volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters} to apply with respect to the aPPR vector.
 
@@
 	\item We specialize to the graph $G = G_{n,r}$ and the subset $\mathcal{L}[\Xbf] \subset \Xbf$, and show that the normalized cut $\Phi_{n,r}(\mathcal{L}[\Xbf])$ is small (with high probability) when the diameter $\rho$ is large.
-	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\ref{alg: ppr} $\widehat{C}$ must therefore also have small normalized cut.
+	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\ref{alg: ppr} $\Cest$ must therefore also have small normalized cut.
 	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Csig^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Csig^{(1)}[\Xbf])$.
 In fact, we generalize this to hold for any set $A \subset \Xbf$ for which the symmetric set distance metric $\Delta(A,\Cset_1[\Xbf])$ is small.
-	\item We conclude that the symmetric set distance metric $\Delta(\widehat{C},\Csig^{(1)}[\Xbf])$ must not be small.
+	\item We conclude that the symmetric set distance metric $\Delta(\Cest,\Csig^{(1)}[\Xbf])$ must not be small.
 \end{enumerate}
@@
 We will additionally show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$.
-Once this is shown, the concavity of the expression on the right hands side of~\eqref{eqn:mixing_time_PPR} implies that the inequality holds for all $k \in [K_0,2m - K_0]$.
+Once this is shown, the concavity of the expression on the right-hand side of~\eqref{eqn:mixing_time_PPR} implies that the inequality holds for all $k \in [K_0,2m - K_0]$.
 
@@
 
-As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\widehat{C};G)$.
+As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\Cest;G)$.
 First, we restate a theorem of \citet{andersen2006} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.
@@
 
-\subsection{Normalized cut of $\widehat{C}$.}
-
-To upper bound $\Phi_{n,r}(\widehat{C})$, we need to show that the conditions of Theorem~\ref{thm:conductance_ppr} are met with respect to the graph $G = G_{n,r}$ and subset $C = \mathcal{L}[\Xbf]$.
+\subsection{Normalized cut of $\Cest$.}
+
+To upper bound $\Phi_{n,r}(\Cest)$, we need to show that the conditions of Theorem~\ref{thm:conductance_ppr} are met with respect to the graph $G = G_{n,r}$ and subset $C = \mathcal{L}[\Xbf]$.
 To do, we require the following inequalities, which are satisfied with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2\delta^2n}{8 \rho \sigma(1 + \frac{\delta}{3})}} - 6 \exp\set{-n\delta^2(\cut_{\Pbb,r}(\mathcal{L}[\Xbf]))^2}$:
@@
 	\item $\vol(\mathcal{L}[X]) \leq \frac{(1 + \delta)}{2(1 - \delta)}\vol(G_{n,r}) \leq \frac{2}{3}\vol(G_{n,r})$ since $\delta < 1/7$,
-	\item $\abs{\mathcal{L}[X]} \geq \frac{n(1 - \delta)}{2} \geq \frac{2(1 + \delta)}{(1 - \delta)\epsilon} \geq \frac{d_{\max}}{d_{\min}}$ and $\frac{d_{\max}}{2d_{\min}^2} \leq \frac{8(1 + \delta)}{(1 - \delta)^2 \epsilon^2 \rho \sigma \pi r^2} \cdot \frac{1}{n} \leq \frac{1}{10}$ by \eqref{eqn:lb_sample_size},
+	\item $\abs{\mathcal{L}[X]} \geq \frac{n(1 - \delta)}{2} \geq \frac{2(1 + \delta)}{(1 - \delta)\epsilon} \geq \frac{d_{\max}}{d_{\min}}$ and $\frac{d_{\max}}{2d_{\min}^2} \leq \frac{8(1 + \delta)}{(1 - \delta)^2 \epsilon^2 \rho \sigma \pi r^2} \cdot \frac{1}{n} \leq \frac{1}{10}$ by the assumed lower bound on the sample size,
 	\item $\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{4r}{\rho} \leq \frac{1}{10}$, by assumption on $r$ and $\rho$, and
@@
 
-To be precise, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6} \vol_{n,r}(\mathcal{L}[\Xbf])$, such that the following statement holds for any $v \in \mathcal{L}[\Xbf]^g$: when Algorithm~\ref{alg: ppr} is run with inputs $\Xbf, r < \frac{1}{4}\sigma,\alpha = 65 \Phi_{\Pbb,r}(\mathcal{L}[\Xbf]),v \in \mathcal{L}[\Xbf]^g$ and $(L,U) = (0,1)$, the resulting PPR cluster estimate $\widehat{C}$ satisfies
+To be precise, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6} \vol_{n,r}(\mathcal{L}[\Xbf])$, such that the following statement holds for any $v \in \mathcal{L}[\Xbf]^g$: when Algorithm~\ref{alg: ppr} is run with inputs $\Xbf, r < \frac{1}{4}\sigma,\alpha = 65 \Phi_{\Pbb,r}(\mathcal{L}[\Xbf]),v \in \mathcal{L}[\Xbf]^g$ and $(L,U) = (0,1)$, the resulting PPR cluster estimate $\Cest$ satisfies
 \begin{align}
-\Phi_{n,r}(\widehat{C}) & \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi_{n,r}(\mathcal{L[X]})} \nonumber \\
+\Phi_{n,r}(\Cest) & \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi_{n,r}(\mathcal{L[X]})} \nonumber \\
 & \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}} \label{eqn:lb_pf4} 
@@
 	\begin{equation*}
-	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
+	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
 	\end{equation*}
@@
 
-	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right hand corner of the cube
+	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube
 	\begin{equation*}
@@
 Intuitively, every point $x_i \in A$ in the boundary set of $\overline{A}$ will have many edges to $X\setminus A$.
-Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \mathbb{P}_n(Q)$, we have
+Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \Pbb_n(Q)$, we have
 	\begin{equation}
@@
 	\end{align*}
-	and the expected volume of $\mathcal{C}_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\mathcal{C}_{\sigma}^{(2)}[\Xbf] \cap R_k$,
-	\begin{equation}
-	\vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
+	and the expected volume of $\Cset_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\Cset_{\sigma}^{(2)}[\Xbf] \cap R_k$,
+	\begin{equation}
+	\vol_{\Pbb,r}(\Cset_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\Cset_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
 	\end{equation}
@@
 	\begin{equation*}	
-	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
+	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
 	\end{equation*}
@@
 \begin{equation*}
-\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\widehat{C}) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
-\end{equation*}
-Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\mathcal{C}_{\sigma}^{(1)}[\Xbf]$:
-\begin{align*}
-\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(2)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \mathcal{C}_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
+\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\Cest \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\Cest) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
+\end{equation*}
+Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\Cset_{\sigma}^{(1)}[\Xbf]$:
+\begin{align*}
+\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset_{\sigma}^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\Cset_{\sigma}^{(0)} \cup \Cset_{\sigma}^{(2)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\Cset_{\sigma}^{(0)} \cup \Cset_{\sigma}^{(1)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \Cset_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
 & \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}) \\
-& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])
+& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\Cset_{\sigma}^{(1)}[\Xbf])
 \end{align*}
 where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}))^2}$.
-Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$.
+Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset_{\sigma}^{(1)}[\Xbf])$.
 
@@
 	\begin{equation*}
-	\Phi_{n,r}(\Csig[\Xbf]) \leq \Phi_{u}(\Csig) 
+	\Phi_{n,r}(\Csig[\Xbf]) \leq \Phibf(\Csig) 
 	\end{equation*}
@@
 \end{itemize}
-We assume these high probability bounds are satisfied with $\delta = \frac{1}{2}$ and move on to upper bounding $\Delta_{\textrm{mc}}(\widehat{C}_{\textrm{un}}, \Csig[\Xbf])$.
+We assume these high probability bounds are satisfied with $\delta = \frac{1}{2}$ and move on to upper bounding $\Delta_{\textrm{mc}}(\Cest_{\textrm{un}}, \Csig[\Xbf])$.
 
@@
 
-	\noindent The following statements hold for any $0 < r < \frac{\sigma}{2\sqrt{d}}$:
+	\noindent The following statements hold for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$:
 
@@
 
-\subsection{Experimental settings for Figure \ref{fig:fig1}}
+\subsection{Experimental settings for Figure \ref{fig:bounds}}
 We sample points according to the density function $q$, where for $x \in \Rd$
@@
 
-The remaining four panels (top-right and the bottom row) in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
+The remaining four panels (top-right and the bottom row) in Figure \ref{fig:bounds} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
 In the top-right and bottom-left panels $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $\rho$ is fixed at $3.2$.
@@
 
-\subsection{Experimental settings for Figure \ref{fig:fig2}}
-
-To form each of the three rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+\subsection{Experimental settings for Figure \ref{fig:moons}}
+
+To form each of the three rows in Figure \ref{fig:moons}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
 Formally, the (respective) generative models for the data are
@@
 
-Figure \ref{fig:fig3} is similar to Figure \ref{fig:fig2} of the main text, with parameters
+Figure \ref{fig:moons_hd} is similar to Figure \ref{fig:moons} of the main text, with parameters
 \begin{equation*}
@@
 \end{equation*}
-The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:fig2} in the main text) represent observations in low-density regions.
+The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:moons} in the main text) represent observations in low-density regions.
 While the \pprspace sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C[\Xbf]$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
@@
 		\caption{}
-		\label{fig:fig3}
+		\label{fig:moons_hd}
 	\end{adjustbox}

### 2019-11-21 arxiv/local_spectral_density_clustering_arxiv.tex
arxived version

@@
 geometrically poorly-conditioned density clusters, even asymptotically. Finally,
-we provide empirical support our theory.
+we provide empirical support for our theory.
 \end{abstract}
@@
 \label{eqn: ppr_vector}
-\pbf_v = \alpha \ebf{v} + (1 - \alpha) \pbf \Wbf,
+\pbf_v = \alpha \ebf{v} + (1 - \alpha) \pbf_v \Wbf,
 \end{equation}
@@
 will consider a related metric, the volume of the symmetric set difference,
-which weights points according to their degree in $G_{n,r}$.
+which weights points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq \Xbf$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
 \begin{definition}
@@
   $$
-  \Delta(\Cest, \mathcal{S}[\Xbf]) := \vol(\Cest \vartriangle \mathcal{S}[\Xbf];
-  G_{n,r}). 
+  \Delta(\Cest, \mathcal{S}[\Xbf]) := \vol_{n,r}(\Cest \vartriangle \mathcal{S}[\Xbf]). 
   $$
@@
 spectra of these continuum operators can in general be hard to grasp. Therefore,
-further work relating this spectra to the geometry of the unlerlying
+further work relating this spectra to the geometry of the underlying
 distribution $\Pbb$ is of interest. In this spirit,
@@
   S;G)$}. Both of these analyses also hold with respect to an approximate form 
-of PPR  (APPR), which can be efficiently computed.
+of PPR  (aPPR), which can be efficiently computed.
 
@@
 bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
-yields a lower bound on \smash{$\vol(\Csig[\Xbf]; G_{n,r})$}; together with 
+yields a lower bound on \smash{$\vol_{n,r}(\Csig[\Xbf])$}; together with 
 \ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
@@
   $\kappa$-well-conditioned density cluster, and assume Algorithm \ref{alg: ppr}
-  is well-initialized with respect to $\Cset$. There exists a set $\Csig[\Xbf]^g 
-  \subseteq \Csig[\Xbf]$ of large volume, \smash{$\vol(\Csig[\Xbf]^g; G_{n,r})
-    \geq \vol(\Csig[\Xbf];G_{n,r})/2$}, such that the following holds: if 
+  is well-initialized with respect to $\Cset$. Then for any 
+  $$
+  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
+  $$
+  there exists a set $\Csig[\Xbf]^g 
+  \subseteq \Csig[\Xbf]$ of large volume, \smash{$\vol_{n,r}(\Csig[\Xbf]^g)
+    \geq \vol_{n,r}(\Csig[\Xbf])/2$}, such that the following holds: if 
   Algorithm~\ref{alg: ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then
-  for 
-  $$
-  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
-  $$
   the PPR estimated cluster \smash{$\Cest$} satisfies
@@
 Then, any $(L,U)$ satisfying~\eqref{eqn: initialization} and any sweep cut
-$S_{\beta}$ for $\beta \in (L,U)$ will fulfill both conditions laid out in
+$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
 \eqref{eqn: consistent_density_cluster_recovery}. In Theorem 
@@
   \end{equation}
-  There exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, 
-  \smash{$\vol(\Csig[\Xbf]^g; G_{n,r}) \geq
-    \frac{1}{2}\vol(\Csig[\Xbf];G_{n,r})$}, such that if Algorithm~\ref{alg:
-    ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then for
+  Then for any
   $$
@@
   $$
-  the PPR estimated cluster \smash{$\Cest$} satisfies \eqref{eqn:
-    consistent_density_cluster_recovery} with probability at least $1-b_2/n$.
+  there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, 
+  \smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq
+    \vol_{n,r}(\Csig[\Xbf])/2$}, such that if Algorithm~\ref{alg:
+    ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then the PPR estimated cluster \smash{$\Cest$} satisfies \eqref{eqn: consistent_density_cluster_recovery} with probability at least $1-b_2/n$.
 \end{theorem}
@@
 \begin{remark}
-We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: 
-    kappa_ub} results in an upper bound on the symmetric set difference metric
+We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in an upper bound on the symmetric set difference metric
   \smash{$\Delta(\Cest, \Csig[\Xbf])$} on the order of $r^d$. In plain terms, we 
@@
   it is an interesting question whether PPR exhibits some degeneracy over 
-  neighborhood graphs such that $r \to 0$, or if this is merely looseness in our  
+  neighborhood graphs as $r \to 0$, or if this is merely looseness in our  
   upper bounds.
@@
   \label{cor: appr}
-  Under the assumptions of Theorem \ref{thm: volume_ssd}, consider instead of
-  Algorithm \ref{alg: ppr}, using the approximate PPR vector from
+  Consider instead of
+  Algorithm \ref{alg: ppr} using the approximate PPR vector from
   \citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
@@
   \end{equation}
-  the upper bound on symmetric set difference in \eqref{eqn: volume_ssd} still
-  holds. Further, under the assumptions of Theorem \ref{thm:
-    consistent_recovery_of_density_clusters}, the estimator \smash{$\Cest$} is
-  still consistent, in the sense of Definition \ref{def:
-    consistent_density_cluster_estimation}.  
+  under the assumptions of Theorem~\ref{thm: volume_ssd} the upper bound on symmetric set difference in \eqref{eqn: volume_ssd} still
+  holds, and under the assumptions of Theorem \ref{thm: consistent_recovery_of_density_clusters} the set inclusion and disjointedness statements in \eqref{eqn: consistent_density_cluster_recovery} still hold, each with probability at least $1 - b_2/n$ (under possibly different choices of the constants $c_i$ and $b_i$).
 \end{corollary}
@@
   Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
-    conductance_upper_bound}, in contrast to ultimate bound in Theorem    
-  \ref{thm: volume_ssd} (where the diameter enters through the condition number 
+    conductance_upper_bound}, in contrast to the ultimate bound in Theorem    
+  \ref{thm: volume_ssd} where the diameter enters through the condition number 
   $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This reflects
@@
   satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
-  Also assume that \smash{$0 < r \leq \sigma/(2\sqrt{d})$}. Then for
+  Also assume that \smash{$0 < r \leq \sigma/(2\sqrt{d})$}. Then for any
   $$
@@
   \centering
-  \includegraphics[width=0.495\textwidth]{lower_bound_plots/lower_bound_1}
-  \includegraphics[width=0.495\textwidth]{lower_bound_plots/lower_bound_2}
+  \includegraphics[width=0.495\textwidth]{lower_bound_1}
+  \includegraphics[width=0.495\textwidth]{lower_bound_2}
   \caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
@@
   $$
-  there exists a set $\Cset[X]^g$ of large volume, \smash{$\vol(\Cset[X]^g \cap 
-    \Cset^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset^{(1)}[\Xbf])$}, such
+  there exists a set $\Cset[X]^g$ of large volume, \smash{$\vol_{n,r}(\Cset[X]^g \cap 
+    \Cset^{(1)}[\Xbf]) \geq \vol_{n,r}(\Cset^{(1)}[\Xbf];G_{n,r})/10$}, such
   that for any seed node $v \in \Cset[X]^g$, the PPR estimated cluster
@@
 
-Note that $\vol_{n,r}(\Cset^{(1)})$ for large enough $n$ will be of the order
+Note that $\vol_{n,r}(\Cset^{(1)}[\Xbf])$ for large enough $n$ will be of the order
 $n^2 r^2/(\sigma\rho)$, and therefore the quantity \smash{$\frac{\sigma
@@
 to $\Reals^d$ and to non-rectangular clusters.  Moreover, although we state
-our lower bound with respect to PPR run on neighborhood graph, the conclusion is
+our lower bound with respect to PPR run on a neighborhood graph, the conclusion is
 likely to hold for a much broader class of spectral clustering algorithms. In
@@
   \centering
-  \includegraphics[width=0.32\textwidth]{example1plots/sample2}
-  \includegraphics[width=0.32\textwidth]{example1plots/sample1}
-  \includegraphics[width=0.32\textwidth]{example1plots/sigma_normalized_cut_plot}
-  \includegraphics[width=0.32\textwidth]{example1plots/sigma_mixing_time_plot}
-  \includegraphics[width=0.32\textwidth]{example1plots/diameter_normalized_cut_plot}
-  \includegraphics[width=0.32\textwidth]{example1plots/diameter_mixing_time_plot}
+  \includegraphics[width=0.32\textwidth]{sample2}
+  \includegraphics[width=0.32\textwidth]{sample1}
+  \includegraphics[width=0.32\textwidth]{sigma_normalized_cut_plot}
+  \includegraphics[width=0.32\textwidth]{sigma_mixing_time_plot}
+  \includegraphics[width=0.32\textwidth]{diameter_normalized_cut_plot}
+  \includegraphics[width=0.32\textwidth]{diameter_mixing_time_plot}
   \caption{\it\small Top left and top middle: samples from a geometrically
@@
   \centering
-  \includegraphics[width=0.24\textwidth,scale = .5]{example2plots/row1_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row1_density_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row2_density_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{example2plots/row3_density_cluster}
+  \includegraphics[width=0.24\textwidth,scale = .5]{row1_true_density_cluster}
+  \includegraphics[width=0.24\textwidth]{row1_ppr_cluster}
+  \includegraphics[width=0.24\textwidth]{row1_conductance_cluster}
+  \includegraphics[width=0.24\textwidth]{row1_density_cluster}
+  \includegraphics[width=0.24\textwidth]{row2_true_density_cluster}
+  \includegraphics[width=0.24\textwidth]{row2_ppr_cluster}
+  \includegraphics[width=0.24\textwidth]{row2_conductance_cluster}
+  \includegraphics[width=0.24\textwidth]{row2_density_cluster}
+  \includegraphics[width=0.24\textwidth]{row3_true_density_cluster}
+  \includegraphics[width=0.24\textwidth]{row3_ppr_cluster}
+  \includegraphics[width=0.24\textwidth]{row3_conductance_cluster}
+  \includegraphics[width=0.24\textwidth]{row3_density_cluster}
   \caption{\it\small True density (column 1), PPR (column 2), normalized
@@
 SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
-helpful and inspiring conversations. RJT thanks Terrence Tao for that time we
-hung out recently, and shared tips on how we each cope with massive fame.
-This work was supported in part by the NSF grant DMS-1713003.
+helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+
+\bibliographystyle{plainnat}
+\bibliography{local_spectral_bibliography}
 
@@
 
-For notational ease, we let $\mathcal{S} \subseteq \Rd$ and write
-\begin{align*}
-\cut_{n,r}(\Csig[\Xbf]) = \cut(\Csig[\Xbf]; G_{n,r}),& ~ \cut_{\Pbb,r}(\Csig)= \frac{\mathbb{E}[\cut_{n,r}(\Csig[\Xbf])]}{2{n \choose 2}} \\
-\vol_{n,r}(\Csig[\Xbf]) = \vol(\Csig[\Xbf]; G_{n,r}),& ~ \vol_{\Pbb,r}(\Csig)= \frac{\mathbb{E}[\vol_{n,r}(\Csig[\Xbf])]}{2{n \choose 2}}
-\end{align*}
-for the random variable and mean of cut size and volume, respectively. (Note that this definition of $\vol_{\Pbb,r}(\Sset)$ agrees with that of~\eqref{eqn:volume}).
+To ease notation, letting $S \subseteq X$ and $\Sset \subseteq \Reals^d$, we write
+\begin{equation*}
+\cut_{n,r}(S) = \cut(\Csig[\Xbf]; G_{n,r}), ~ \cut_{\Pbb,r}(\Sset)= \frac{\mathbb{E}[\cut_{n,r}(\Sset)]}{2{n \choose 2}}
+\end{equation*}
+for the random variable and mean of cut size, respectively.
 
@@
 \end{align*}
-with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$.
+with probability at least $1 - 3\exp\{-nb\}$.
 
@@
 \end{equation*}
-Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $c_3(\Pbb,r) = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
+Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $b = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
 
@@
 	\label{prop: local_spread_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_5(\Pbb,r)$,$c_6(\Pbb,r)$, and $c_7(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{c_{5}(\Pbb,r)}\right)^d, c_{6}(\Pbb,r)\right\}
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$,$b_4$, and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{b_3}\right)^d, b_4\right\}
 	\end{equation*}
@@
 	\end{equation}
-	hold with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
+	hold with probability at least $1 - \frac{b_5}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
 \end{proposition}
@@
 \end{align*}
-whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, and constants $c_{4}(\Pbb,r) := c_7(\Pbb,r) + \frac{7500}{\lambda_{\sigma}\nu_dr^d} + 25(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$ and $c_1(\Pbb,r) = \frac{1}{c_5(\Pbb,r)^d} + c_6(\Pbb,r)$.
+whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, and constants $b_2 = b_5 + \frac{7500}{\lambda_{\sigma}\nu_dr^d} + 25(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$ and $b_1 = \frac{1}{b_3^d} + b_4$.
 In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
@@
 Now, take $z = e_vW^3$, and trivially observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
-To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound -- the right-hand side of~\eqref{eqn: tv_mixing_time}-- holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
+To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound \eqref{eqn: tv_mixing_time} holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
 
@@
 \begin{equation*}
-n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: c_{6}(\Pbb,r)
+n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: b_4
 \end{equation*}
@@
 
-Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$
+Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{b_5}{n}$
 \begin{equation*}
@@
 	\label{lem: graph_conductance_profile_lb}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $c_{5}(\Pbb,r)$ and $c_{7}(\Pbb,r)$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_5(\Pbb,r)}\right)^d
+	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$ and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{b_3}\right)^d
 	\end{equation*}
@@
 	\end{equation}
-	with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$. 
+	with probability at least $1 - \frac{b_5}{n}$. 
 \end{lemma}
@@
 Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
-Then there exists a constant $c_{9}(\Pbb,r) > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
+Then there exists a constant $b_6 > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
 	\begin{equation}
 	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
+	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
 	\end{equation}
@@
 	\label{thm: stagnating_transportation_maps}
-	There exists constants $c_5(\Pbb,r)$ and $c_{7}(\Pbb,r)$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{c_5(\Pbb,r)\delta}\right)^{d}
-	\end{equation*}
-	then with probability at least $1 - \frac{c_{7}(\Pbb,r)}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
+	There exists constants $b_3$ and $b_5$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
+	\begin{equation*}
+	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{b_3\delta}\right)^{d}
+	\end{equation*}
+	then with probability at least $1 - \frac{b_5}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
 	which satisfies
@@
 \begin{equation*}
-\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2c_{9}(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
+\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2b_6 + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
 \end{equation*}
@@
 \begin{align*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{c_{9}(\Pbb,r) \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r)\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
 & \geq \frac{\widetilde{\Phi}_{\Pbb,r}}{2},
 \end{align*}
-where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2c_{9}(\Pbb,r) + \widetilde{\Phi}_{\Pbb,r}}$.
+where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2b_6 + \widetilde{\Phi}_{\Pbb,r}}$.
 Then, Lemma~\ref{lem: nonuniform_continuous_conductance} yields the desired result.
@@
 \begin{equation*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{c_{9}(\Pbb,r)\varDelta}{s(\widetilde{G}_{n,r}) - c_{9}(\Pbb,r) \varDelta}
-\end{equation*}
-for some constant $c_{9}(\Pbb,r) > 0$.
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{b_6\varDelta}{s(\widetilde{G}_{n,r}) - b_6 \varDelta}
+\end{equation*}
+for some constant $b_6 > 0$.
 We first state the relationships between the discrete functionals $\widetilde{\cut}_{n,r}$ and $\widetilde{\vol}_{n,r}$, and the continuous functionals $\widetilde{Q}_{\Pbb,r}$ and $\widetilde{\pi}_{\Pbb,r}$, alluded to in the previous section.
@@
 	\label{lem: deviation_transportation_distance}
-	Suppose $\Delta \leq r$. Then there exist constants $c_{10}(\Pbb,r),c_{11}(\Pbb,r) \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
-	\begin{align*}
-	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r) \varDelta \\
-	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r) \varDelta \\
-	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_{11}(\Pbb,r) \varDelta \\
-	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{11}(\Pbb,r) \varDelta.
+	Suppose $\Delta \leq r$. Then there exist constants $b_7,b_8 \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
+	\begin{align*}
+	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7 \varDelta \\
+	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7 \varDelta \\
+	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - b_8 \varDelta \\
+	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + b_8 \varDelta.
 	\end{align*}
@@
 \frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \frac{\widetilde{Q}_{\Pbb,r^-}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r^+}(\Sset)} \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \tag{Lemma \ref{lem: cut_volume}} \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - c_{11}(\Pbb,r) \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + c_{11}(\Pbb,r) \varDelta} \left(1 - \frac{2 c_{10}(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2c_{11}(\Pbb,r)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - b_8 \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + b_8 \varDelta} \left(1 - \frac{2 b_7 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
+& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2b_8}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
 \end{align}
@@
 	Suppose $\varDelta \leq \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)$.
-Then there exists a constant $c_{12}(\Pbb,r) > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
-	\begin{equation*}
-	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - c_{12}(\Pbb,r) \varDelta
+Then there exists a constant $b_9 > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
+	\begin{equation*}
+	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - b_9 \varDelta
 	\end{equation*}
@@
 \begin{align*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_{11}(\Pbb,r)}{\widetilde{\pi}_{n,r}(S) - c_{12}(\Pbb,r)\varDelta} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
-& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2c_{11}(\Pbb,r)}{s(\widetilde{G}_{n,r}) - c_{12}(\Pbb,r)\varDelta} + \frac{2c_{10}(\Pbb,r)}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
+\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2b_8}{\widetilde{\pi}_{n,r}(S) - b_9\varDelta} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
+& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2b_8}{s(\widetilde{G}_{n,r}) - b_9\varDelta} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
 \end{align*}
 where the latter inequality follows as we assumed $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-Choosing the constant $c_{9}(\Pbb,r)$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $c_{9}(\Pbb,r) = \max\set{2c_{10}(\Pbb,r)/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2c_{11}(\Pbb,r), c_{12}(\Pbb,r)}f$, we achieve our desired result.
+Choosing the constant $b_6$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $b_6 = \max\set{2b_7/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2b_8, b_9}$, we achieve our desired result.
 It remains to show Lemmas~\ref{lem: cut_volume}, \ref{lem: deviation_transportation_distance}, and \ref{lem: continuous_pi_lb}, which we now turn to.
@@
 \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)  & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl( 2d(r + \Delta)^{d - 1}\varDelta \bigr) \tag{1st-order Taylor expansion of $(r + \Delta)^d$ } \\
-& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: c_{10}(\Pbb,r) \varDelta. \label{eqn: deviation_transportation_distance_1}
+& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: b_7 \varDelta. \label{eqn: deviation_transportation_distance_1}
 \end{align}
@@
 \int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r)\varDelta.
+& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7\varDelta.
 \end{align*}
@@
 & \geq \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) d\Pbb(x) - \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r)) d\Pbb(x)} \\
-& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{c_{10}(\Pbb,r) \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - c_{11}(\Pbb,r) \varDelta.
+& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{b_7 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - b_8 \varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Sset} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{11}(\Pbb,r)\varDelta.
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + b_8\varDelta.
 \end{align*}
@@
 & \leq \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) }{\int_{\Csig}\ell_{\Pbb,r^-}(x) \,d\Pbb(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r)\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - c_{10}(\Pbb,r)\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4c_{10}(\Pbb,r)\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + c_{12}(\Pbb,r) \varDelta.
-\end{align*}
-where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $c_{10}(\Pbb,r)\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
+& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7\varDelta} \\
+& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + b_9 \varDelta.
+\end{align*}
+where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $b_7\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
 
@@
 	Let $G = (V,E)$ be a undirected, unweighted graph, let $A \subseteq V$, and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
-For $\beta \in (0,1)$,  the sweep cut $S_{v,\beta}$ is
-	\begin{equation*}
-	S_{v,\beta} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}
+For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
+	\begin{equation*}
+	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}
 	\end{equation*} Suppose $\alpha \leq \frac{1}{9 \tau_{\infty}(G[S])}$,  $\varepsilon \leq \frac{1}{20}\vol(A;G)$.
@@
 	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v}) \leq \left(218\frac{\Phi(A;G)}{\alpha}\right) \vol(A;G)
+	\vol(A \vartriangle S_{\beta,v};G) \leq \left(218\frac{\Phi(A;G)}{\alpha}\right) \vol(A;G)
 	\end{equation*}
@@
 \end{equation*}
-with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
+with probability at least $1 - \frac{b_2}{n}$.
 Since we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets in Algorithm~\ref{alg: ppr}, we may apply Lemma~\ref{lem:zhu}.
-By this Lemma, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}(\frac{1}{100},\frac{2}{5})$, the sweep cut $S_{v,\beta}$ of $p(\alpha, v; G_{n,r})$ satisfies
+By this Lemma, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}(\frac{1}{100},\frac{2}{5})$, the sweep cut $S_{\beta,v}$ of $p(\alpha, v; G_{n,r})$ satisfies
 \begin{align}
@@
 \end{align}
-where the latter inequality holds with probability at least $1 - 3\exp\set{-c_1(\Pbb,r)n}$, and follows from Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_u(\theta)}$ given in \eqref{eqn: initialization}.
+where the latter inequality holds with probability at least $1 - 3\exp\set{-bn}$, and follows from Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_u(\theta)}$ given in \eqref{eqn: initialization}.
 
@@
 \begin{equation*}
-n \geq c_1(\Pbb,r)(\log(n))^{\max\{\frac{3}{d},1\}}
+n \geq b_1(\log(n))^{\max\{\frac{3}{d},1\}}
 \end{equation*}
@@
 \end{equation*} 
-with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 3\exp\set{-(c_3(\Pbb,r) + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
-Since $c_3(\Pbb,r) \leq \vol_{\Pbb,r}(\Csig)^2$, letting $c_2(\Pbb,r) := c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)}$ we have proved Theorem~\ref{thm: volume_ssd}.
+with probability at least $1 - \frac{b_2}{n} - 3\exp\set{-(b + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
+We have proved Theorem~\ref{thm: volume_ssd} (upon appropriate choice of constants $b_2$ and $c$ in the theorem statement).
 
@@
 \end{equation}
-with probability at least $1 - \frac{c_2(\Pbb,r)}{n}$.
+with probability at least $1 - \frac{b_2}{n}$.
 
@@
 \end{equation*}
-holds with probability at least $1 - \frac{c_4(\Pbb,r)}{n}$.
+holds with probability at least $1 - \frac{b_2}{n}$.
 Therefore, all the conditions of Lemma \ref{lem: setup} are met.
@@
 	\end{equation*}
-	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)\}$. By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
+	with probability at least $1 - 3\exp\{-nb\}$. By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
 	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
@@
 where the last inequality again follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}.
-We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters} (choosing $c_2(\Pbb,r) = c_4(\Pbb,r) + \frac{6}{c_3(\Pbb,r)} + \frac{900}{\lambda_{\sigma}\nu_dr^d} + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2$).
+We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters} (upon an appropriate choice of constants $b_2$ and $c$ in the statement of the theorem).
+
+% (choosing $b_2 = c_4(\Pbb,r) + \frac{6}{b} + \frac{900}{\lambda_{\sigma}\nu_dr^d} + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2$).
 
@@
 \label{sec:appr}
-To prove the first claim of Corollary~\ref{cor: appr}, we must show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
+To prove the first claim of Corollary~\ref{cor: appr}, it will be sufficient to show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
 In particular, we must show that $\varepsilon \leq \frac{1}{20}\vol_{n,r}(\Csig)$.
@@
 \begin{enumerate}
-	\item We study the spectral partitioning properties of PPR on an arbitrary graph $G$, and show that when suitably initialized inside a subset $S \subset V$, the normalized cut of the PPR sweep cut is upper bounded by (a function of) $\Phi(S)$.
+	\item We study the spectral partitioning properties of PPR on an arbitrary graph $G$, and show that when suitably initialized inside a subset $S \subset V$, the normalized cut of the PPR sweep cut is upper bounded by (a function of) $\Phi(S;G)$.
 	\item We specialize to the graph $G = G_{n,r}$ and the subset $\mathcal{L}[\Xbf] \subset \Xbf$, and show that the normalized cut $\Phi_{n,r}(\mathcal{L}[\Xbf])$ is small (with high probability) when the diameter $\rho$ is large.
 	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\ref{alg: ppr} $\Cest$ must therefore also have small normalized cut.
-	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Csig^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Csig^{(1)}[\Xbf])$.
+	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Cset^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Cset^{(1)}[\Xbf])$.
 In fact, we generalize this to hold for any set $A \subset \Xbf$ for which the symmetric set distance metric $\Delta(A,\Cset_1[\Xbf])$ is small.
-	\item We conclude that the symmetric set distance metric $\Delta(\Cest,\Csig^{(1)}[\Xbf])$ must not be small.
+	\item We conclude that the symmetric set distance metric $\Delta(\Cest,\Cset^{(1)}[\Xbf])$ must not be small.
 \end{enumerate}
@@
 	\begin{equation*}
-	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
+	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
 	\end{equation*}
@@
 	\end{align*}
-	and the expected volume of $\Cset_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\Cset_{\sigma}^{(2)}[\Xbf] \cap R_k$,
-	\begin{equation}
-	\vol_{\Pbb,r}(\Cset_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\Cset_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
+	and the expected volume of $\Cset^{(1)}[\Xbf] \cap R_k$ and $\Cset^{(2)}[\Xbf] \cap R_k$,
+	\begin{equation}
+	\vol_{\Pbb,r}(\Cset^{(1)} \cap R_k) = \vol_{\Pbb,r}(\Cset^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
 	\end{equation}
@@
 	\begin{equation*}	
-	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
+	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
 	\end{equation*}
@@
 \begin{equation*}
-\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\Cest \vartriangle \Cset_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\Cest) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
-\end{equation*}
-Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\Cset_{\sigma}^{(1)}[\Xbf]$:
-\begin{align*}
-\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset_{\sigma}^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\Cset_{\sigma}^{(0)} \cup \Cset_{\sigma}^{(2)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\Cset_{\sigma}^{(0)} \cup \Cset_{\sigma}^{(1)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \Cset_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
-& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}) \\
-& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\Cset_{\sigma}^{(1)}[\Xbf])
-\end{align*}
-where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}))^2}$.
-Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset_{\sigma}^{(1)}[\Xbf])$.
+\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\Cest) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
+\end{equation*}
+with probability at least $1 - b_2/n$ for an appropriate choice of constant $b_2$.
+Solving for $\vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf])$ in the previous equation, we obtain \eqref{eqn:ppr_lb} (for an appropriate choice of constant $c$).
+Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\Cset^{(1)}[\Xbf]$:
+\begin{align*}
+\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\Cset^{(0)} \cup \Cset^{(2)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\Cset^{(0)} \cup \Cset^{(1)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \Cset^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
+& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Cset^{(1)}) \\
+& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\Cset^{(1)}[\Xbf])
+\end{align*}
+where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Cset^{(1)}))^2}$.
+Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset^{(1)}[\Xbf])$.
 
@@
 	\label{thm:misclassification_rate}
-	Fix $\lambda > 0$ and suppose \smash{$\Cset \in \Cbb_f(\lambda)$} is a
-	$\kappa$-well-conditioned density cluster. If Algorithm
-	\ref{alg:ppr2} is well-initialized, there exists a universal constant $c >
-	0$ such that,
+	Fix $\lambda > 0$ let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
+	$\kappa$-well-conditioned density cluster, and assume If Algorithm
+	\ref{alg:ppr2} is well-initialized with respect to $\Cset$. Then for any
+	\begin{equation*}
+	n \geq b_1(\log n)^{\max\{\frac{3}{d},1\}}
+	\end{equation*}
+	there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$, such that the following holds: if Algorithm~\ref{alg:ppr2} is run with any seed node $v \in \Csig[\Xbf]^g$, then the PPR estimated cluster $\Cest$ satisfies
 	\begin{equation}
@@
 	\Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
-	\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}. 
-	\end{equation}
-	with probability at least $1 - \frac{c_1(\Pbb,r)}{n} - 2n\exp\set{-c_2(\Pbb,r)n} - 2\exp\set{-c_3(\Pbb,r)n}$.
+	\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}, 
+	\end{equation}
+	with probability at least $1 - \frac{b_2}{n}$.
 \end{theorem}
@@
 	\end{equation*}
-	with probability at least $1 - \frac{c_4(\Pbb,r)}{n} - 2n\exp\set{-c_5(\Pbb,r)n} - 2\exp\set{-c_6(\Pbb,r)n}$. 
+	with probability at least $1 - \frac{b_2}{n} - 2n\exp\set{-b_3n} - 2\exp\set{-b_4n}$. 
 	\item  By Theorem~\ref{thm: conductance_upper_bound}, 
@@
 	\end{equation*}
-	with probability at least $1 - 3\exp\{-nc_1(\Pbb,r)^2\}$. 
+	with probability at least $1 - 3\exp\{-nb\}$. 
 	\item By Lemma~\ref{lem:ball_bounds_in_probability},
@@
 In this section, we establish such concentration inequalities.
-We begin with Lemma~\ref{lem:hoeffding}, Hoeffding's inequality, which we will use to bound the empirical probability of a fixed set.
+We begin with Lemma~\ref{lem:hoeffding_2}, Hoeffding's inequality, which we will use to bound the empirical probability of a fixed set.
 \begin{lemma}[Hoeffding's Inequality.]
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_true_density_cluster}
+			\includegraphics[width=\linewidth]{row4_true_density_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_ppr_cluster}
+			\includegraphics[width=\linewidth]{row4_ppr_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_conductance_cluster}
+			\includegraphics[width=\linewidth]{row4_conductance_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{example2plots/row4_density_cluster}
+			\includegraphics[width=\linewidth]{row4_density_cluster}
 			\caption{}
@@
 
-\bibliographystyle{plainnat}
-\bibliography{../local_spectral_bibliography}
-
 \end{document}

### 2020-10-31 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex
Separate folder for JMLR revision.

--- 2019-11-21 arxiv/local_spectral_density_clustering_arxiv.tex
@@
 \documentclass[11pt,twoside]{article}
+\usepackage[preprint]{jmlr2e}
+\usepackage{color}
 \usepackage{fancyhdr}
-\usepackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue,bookmarks=false]{hyperref}
 \usepackage{amsfonts,epsfig,graphicx}
 \usepackage{afterpage}
-\usepackage{amsmath,amssymb,amsthm} 
-\usepackage{fullpage}
+\usepackage{amsmath,amssymb} 
+% \usepackage{fullpage}
 \usepackage{epsf} 
@@
 \usepackage{amsfonts,amsmath}
-\usepackage[sort,numbers]{natbib} 
+% \usepackage[sort,numbers]{natbib} 
 \usepackage{psfrag,xspace}
@@
 
-\newtheorem{theorem}{Theorem} 
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
+%\newtheorem{theorem}{Theorem} 
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{corollary}{Corollary}
+%\theoremstyle{definition}
+%\newtheorem{definition}{Definition}
+%\newtheorem{remark}{Remark}
 
@@
 
+\ShortHeadings{Local Spectral Clustering of Density Level Sets}{Green, Balakrishnan and Tibshirani}
+\firstpageno{1}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{center} {\Large{\bf{Local Spectral Clustering of Density Upper Level Sets}}}
-
-\vspace*{.3cm}
-
-{\large{
-\begin{center}
-Alden Green~~~~~ Sivaraman Balakrishnan~~~~~ Ryan J. Tibshirani\\
-\vspace{.2cm}
-\end{center}
-
-\begin{tabular}{c}
-Department of Statistics and Data Science \\
-Carnegie Mellon University
-\end{tabular}
-
-\vspace*{.2in}
-
-\begin{tabular}{c}
-\texttt{\{ajgreen,sbalakri,ryantibs\}@stat.cmu.edu}
-\end{tabular}
-}}
-
-\vspace*{.2in}
-
-\today
-\vspace*{.2in}
+\title{Local Spectral Clustering of Density Upper Level Sets}
+
+\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213
+	\AND
+	\name Sivaraman Balakrishnan \email sbalakri@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213
+	\AND
+	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213}
+
+\maketitle
 
@@
 \end{abstract}
-\end{center}
+
+\begin{keywords}
+	graphs, spectral clustering, density clustering, Personalized PageRank, unsupervised learning
+\end{keywords}
 
@@
 
-\begin{figure}[tb]
-  \centering
-  \includegraphics[width=0.495\textwidth]{lower_bound_1}
-  \includegraphics[width=0.495\textwidth]{lower_bound_2}
-  \caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
-    $\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
-    $\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
-    $\sigma = 0.2$.} 
-  \label{fig: hard_case}
-\end{figure}
+% PUT FIGURE BACK HERE
 
@@
 
-\begin{figure}[tb]
-  \centering
-  \includegraphics[width=0.32\textwidth]{sample2}
-  \includegraphics[width=0.32\textwidth]{sample1}
-  \includegraphics[width=0.32\textwidth]{sigma_normalized_cut_plot}
-  \includegraphics[width=0.32\textwidth]{sigma_mixing_time_plot}
-  \includegraphics[width=0.32\textwidth]{diameter_normalized_cut_plot}
-  \includegraphics[width=0.32\textwidth]{diameter_mixing_time_plot}
-  \caption{\it\small Top left and top middle: samples from a geometrically
-    well- and poor-conditioned cluster. The points in $\Cset$ are colored in 
-    red, points in $\Csig \setminus \Cset$ are colored in yellow, and the
-    remaining points in blue. Other panels: empirical normalized cut and mixing
-    time, as a function of $\sigma$ or $\rho$, versus their theoretical upper
-    bounds.} 
-  \label{fig:bounds}
-\end{figure}
+% PUT FIGURE BACK HERE
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.24\textwidth,scale = .5]{row1_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{row1_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{row1_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{row1_density_cluster}
-  \includegraphics[width=0.24\textwidth]{row2_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{row2_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{row2_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{row2_density_cluster}
-  \includegraphics[width=0.24\textwidth]{row3_true_density_cluster}
-  \includegraphics[width=0.24\textwidth]{row3_ppr_cluster}
-  \includegraphics[width=0.24\textwidth]{row3_conductance_cluster}
-  \includegraphics[width=0.24\textwidth]{row3_density_cluster}
-  \caption{\it\small True density (column 1), PPR (column 2), normalized
-    cut (column 3) and estimated density (column 4) clusters for 3 different 
-    simulated data sets. Seed node for PPR denoted by a black cross.} 
-  \label{fig:moons}
-\end{figure}
+% PUT FIGURE BACK HERE
 
@@
 helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
-
-\bibliographystyle{plainnat}
-\bibliography{local_spectral_bibliography}
 
@@
 \begin{proof}{(of Lemma~\ref{lem:ball_bounds_in_probability})}
-	\item[]
+	\hfill 
 	\paragraph{Proof of \eqref{eqn:degwt_bound}, \eqref{eqn:degpr_bound}:}
@@
 
-\begin{figure}
-	\centering
-	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{row4_true_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{row4_ppr_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{row4_conductance_cluster}
-			\caption{}
-		\end{subfigure}
-		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{row4_density_cluster}
-			\caption{}
-		\end{subfigure}
-		\caption{}
-		\label{fig:moons_hd}
-	\end{adjustbox}
-\end{figure}
+% PUT FIGURE BACK HERE
+
+\clearpage
+
+% \bibliographystyle{plainnat}
+\bibliography{../../local_spectral_bibliography}
 

### 2020-11-29 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex
test commit
Improved constants in upper bounds of normalized cut and mixing time.

@@
 %%% Sets
+\newcommand{\mc}[1]{\mathcal{#1}}
 \newcommand{\Sset}{\mathcal{S}}
@@
 %%% Tilde notation for quantities over the expansion set 
+\newcommand{\wt}[1]{\widetilde{#1}}
 \newcommand{\wn}{\widetilde{n}}
@@
 \newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
+\newcommand{\ag}[1]{\textcolor{red}{#1}}
 
@@
 
+\textcolor{red}{Need to fix this definition: (1) the universal constants are not given in the Theorem statements, and (2) the definition of $\tau_u(\mc{C})$ has changed.}
+
 \begin{definition}
@@
 $n$.  % where possible, we keep track of all constants in our proofs.
+
+\textcolor{red}{Need to fix this Theorem.}
 
@@
   Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and   
-  \ref{asmp: bounded_volume}. Then
+  \ref{asmp: bounded_volume}. Then for any $\delta \in (0,1/2)$, it holds that
   \begin{equation}
     \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
+    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq (1 + 4\delta) c_1\frac{d}{\sigma}
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
@@
   \end{equation}
-  with probability at least $1 - 3\exp\set{-b n}$. 
+  with probability at least $1 - 3\exp\set{-b n \delta^2}$. 
 \end{theorem}
@@
   satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
-  Also assume that \smash{$0 < r \leq \sigma/(2\sqrt{d})$}. Then for any
-  $$
-  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
+  Also assume that \smash{$0 < r \leq \sigma/(4d)$}. Then for any \smash{$\delta \in \bigl(0,1/(8 + 16/d)\bigr)$}, and any
+  $$
+  n \geq b_1 \cdot (1 + 4\delta) \cdot 
+  \begin{cases*}
+  \log(n)^{3/2},& ~~\textrm{if $d = 2$,} \\
+  \log(n),& ~~\textrm{if $d \neq 2$}
+  \end{cases*}
   $$
   the mixing time satisfies
-  \begin{equation} 
+  \begin{align} 
     \label{eqn: mixing_time_upper_bound}
-    \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 
-      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{
-        \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3, 
-  \end{equation}
-  with probability at least $1 - b_2/n$.
+    \tau_{\infty}\bigl(G_{n,r}[\Csig[\Xbf]]\bigr) & \leq (1 + 40\delta) c_2 \frac{\Lambda_{\sigma}^4 d^3 
+      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr)\log\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + \\
+  &~~c_3\biggl((1 + 32\delta)d\log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + 1\biggr), 
+  \end{align}
+  with probability at least $1 - b_5/n - 4n\exp\{-\delta^2 b_2 n\}$.
 \end{theorem}
@@
 
-\subsection{Comparison with previous upper bound}
+\subsection{Comparison \ag{between upper and lower bounds}.}
 
@@
 	\begin{align}
-	\cut_{\Pbb,r}(\Csig) &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
-	\vol_{\Pbb,r}(\Csig) &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
+	\cut_{\Pbb,r}(\Csig) &\leq \frac{ d \nu_d r^{d+1} \lambda}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
+	\vol_{\Pbb,r}(\Csig) &\geq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)^{-1} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
 	\end{align}
@@
 \begin{equation*}
-\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{25(1 + \delta)d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{3(1 - \delta) \sigma \lambda_{\sigma}^2}.
-\end{equation*}
-Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $b = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.
+\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{(1 + \delta)}{(1 - \delta)(1 - dr/\sigma)^2}\frac{d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\sigma \lambda_{\sigma}^2}.
+\end{equation*}
+Noting that $(1 - dr/\sigma)^{-2} \leq 1 + 6dr/\sigma \leq 4$ for all $r \leq \sigma/2d$, the theorem is satisfied by choosing $c_1 = 4$ and $b = (\cut_{\Pbb,r}(\Csig))^2$.
 
@@
 and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
-%Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$.
 \begin{lemma}
 	\label{lem: expected_number_boundary_points}
-	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-	\begin{equation*}
-	\Pbb(\Csigr) \leq \frac{2dr}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	For any $0 < r \leq \sigma/(2d)$, under the conditions of Theorem \ref{thm: conductance_upper_bound} it holds that
+	\begin{equation*}
+	\Pbb(\Csigr) \leq \frac{dr}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
 	\end{equation*}	
 \end{lemma}
-\noindent Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
-\begin{equation*}
-\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr).
-\end{equation*}
-In order to lower bound $\vol_{\Pbb,r}(\Csig)$ we will show the following lower bound on the uniform local conductance:
-\begin{lemma}
-	\label{lem: local_conductance}
-	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
-	\begin{equation*}
-	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
-	\end{equation*}
-\end{lemma}
-Taking these two results as given we can now prove each of the two claims~\eqref{eqn:claim_one} and~\eqref{eqn:claim_two} in turn.
+Taking this result as given we can now prove the claim~\eqref{eqn:claim_one}.
 \paragraph{Proof of Claim~\eqref{eqn:claim_one}: } For each $i,j$ such that $i \neq j$, we can write 
@@
 
-%\subsection{Proof of Lemma~\ref{Z}}
-\paragraph{Proof of Claim~\eqref{eqn:claim_two}: }  For each $i,j$ such that $i \neq j$, we can write 
-\begin{equation*}
-\vol_{\Pbb,r}(\Csig) = \Pbb(x_i \in \Csig, x_j \in B(x_i,r))
-\end{equation*}
-Writing this as an integral, we have
-\begin{align*}
-\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-\end{align*}
-whence the claim then follows by Lemma \ref{lem: local_conductance}.
-It remains to prove Lemmas~\ref{lem: expected_number_boundary_points} and~\ref{lem: local_conductance}, and we turn our attention to this next.
+\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } On the other hand, the proof of Claim~\eqref{eqn:claim_two} follows from relating $\vol_{\Pbb,r}(\Csig)$ to the Lebesgue measure of $\mc{C}_{\sigma - r}$.
+In particular, since $f(y) \geq \lambda_{\sigma}$ for all $x \in \Csig$, and $B(x,r) \subset \Csig$ for all $x \in \mc{C}_{\sigma - r}$, it follows that
+\begin{align*}
+\vol_{\Pbb,r}(\Csig) & = \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
+& \geq \int_{\mc{C}_{\sigma - r}} f(x) \Pbb(B(x,r)) \dx \\
+& \geq \lambda_{\sigma}^2 \nu_d r^d \nu(\mc{C}_{\sigma - r}).
+\end{align*}
+Then, noting that by the triangle inequality $\mc{C}_{\sigma} \subseteq \mc{C}_{\sigma - r} + \sigma B$, applying Lemma~\ref{lem: expansion_volume} (given in Appendix~\ref{sec: volume_estimates}) and the Bernoulli inequality (Lemma~\ref{lem: Taylor_series}) gives
+\begin{equation*}
+\nu(\Cset_{\sigma}) \leq \nu(\Cset_{\sigma - r} + \sigma B) \leq \biggl(1 + \frac{r}{\sigma - r}\biggr)^d \nu(\Cset_{\sigma - r}) \leq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)\nu(\mc{C}_{\sigma - r}),
+\end{equation*}
+thus establishing the claim.
+
+It remains to prove Lemma~\ref{lem: expected_number_boundary_points} and we turn our attention to this now.
 \subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
-The proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
-	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
+We note that the proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
+
+We begin by partitioning $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
 	\begin{equation*}
@@
 	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
+	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
+	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
 	\end{align}
@@
 	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
+	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
 \label{eqn: xi_ub}
@@
 
-%\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
-
-\subsection{Proof of Lemma~\ref{lem: local_conductance}}
-The proof of this result relies on estimates of the volume of spherical caps which we defer to Appendix~\ref{sec:caps}.
-	Since $u \in \Csig$ there exists $x \in \Cset$ such that $u \in B(x, \sigma)$, and as $B(x,\sigma) \subseteq \Csig$,
-	\begin{equation*}
-	\nu\bigl(B(u, r) \cap B(x, \sigma)\bigr) \leq \nu\bigl(B(u, r) \cap \Csig \bigr)
-	\end{equation*}
-	Without loss of generality, let $\norm{u - x} = \sigma$; it is not hard to see that if $\norm{u - x} < \sigma$, the volume of the overlap will only grow.
-Then, since $\norm{u  - x} = \sigma$, $B(u, r) \cap B(x, \sigma)$ contains a spherical cap of radius $r$ and height
-	\begin{equation*}
-	h = r - r^2/2\sigma = r \left( 1 - \frac{r}{2 \sigma} \right)
-	\end{equation*}	
-	which by Lemma \ref{lem: volume_of_spherical_cap} has volume
-	\begin{equation*}
-	\nu_{\text{cap}} = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right)
-	\end{equation*}
-	with $\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{r^2}{4 \sigma^2} \leq \frac{1}{16d}$. 
-	By Lemmas \ref{lem: beta_integral} (applied with $t = 1$) and \ref{lem: beta_function},
-	\begin{align*}
-	I_{1 - \alpha}\left( \frac{d + 1}{2}  ,\frac{1}{2}\right) & \geq 1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3}{4\sqrt{d}} \\
-	& \geq 1 - \frac{3}{4}\sqrt{\frac{d+2}{\pi d}} \geq 1 - \frac{3}{4}\sqrt{\frac{3}{2 \pi}}.
-	\end{align*}
-
 \subsection{Volume Estimates}
 \label{sec: volume_estimates}
-%\section{Proofs}
-%
-%Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}.
-In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs.
-The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}.
-Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.
-
-%\subsection{Volume estimates}
-
 We begin by recalling some notation.
-We let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
+We let $\Aset \subseteq \Reals^d$, and for $\sigma > 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
 Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
@@
 	\label{lem: expansion_volume}
-	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
+	If $\Aset$ is closed and bounded, then for any $\sigma$ and $\delta > 0$,
 	\begin{equation}
@@
 
-We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
+We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} (Bernoulli's inequality) serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
 \begin{lemma}
 	\label{lem: Taylor_series}
-	For any $0 \leq x \leq 1/2d$,
-	\begin{align*}
-	(1 + x)^d & \leq 1 + 2\dx \\
-	(1 - x)^d & \geq 1 - 2\dx.
+	For any $-1 \leq x \leq 1/(d - 1)$, it holds that
+	\begin{equation*}
+	(1 + x)^{d} \leq 1 + \frac{dx}{1 - (d - 1)x}
+	\end{equation*}
+	and
+	\begin{equation*}
+	(1 - x)^d \geq 1 - d x.
+	\end{equation*}
+	If additionally $0 \leq x \leq 1/(2d - 2)$, then
+	\begin{align*}
+	(1 + x)^d & \leq 1 + 2d x.
 	\end{align*}
 \end{lemma}
-\begin{proof}
-	We take the binomial expansion of $(1 + x)^d$:
-	\begin{align*}
-	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
-	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
-	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
-	\end{align*}
-The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
-\end{proof}
-
-\subsection{Spherical Caps and Associated Estimates}
-\label{sec:caps}
-In this section, we state a result for the volume of a spherical cap and derive some 
-useful upper bounds. 
-\begin{lemma}
-	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha := 1 - \frac{2 r h - h^2}{r^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
-	\end{equation*}
-	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
-\end{lemma}
-
-The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
-an upper bound on the ratio of Gamma functions. 
-\begin{lemma}
-	\label{lem: beta_integral}
-	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write 
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
-	\end{equation*}
-	The first integral is simply the beta function, with
-	\begin{equation*}
-	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
-	\end{equation*}
-	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
-	\begin{equation*}
-	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
-	\end{equation*}
-	As a result,
-	\begin{align*}
-	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
-	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
-	& \overset{\text{(iv)}}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
-	& =  3\alpha^{1/2}.
-	\end{align*}
-	where $\text{(iv)}$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
-\end{proof}
-
-\begin{lemma}
-	\label{lem: beta_function}
-	\begin{equation*}
-	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
-	\end{equation*}
-\end{lemma}
-\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
 
@@
 \begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(v)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
+s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(u)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
 \end{equation*}
@@
 The second step in our approach is to lower bound the local spread and conductance over the neighborhood graph $\widetilde{G}_{n,r}$. In the following result we give lower bounds for both quantities.
+
 \begin{proposition}
 	\label{prop: local_spread_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$,$b_4$, and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	n \geq \max\left\{(\log n)^{\max\{\frac{3}{d},1\}}\left(\frac{1}{b_3}\right)^d, b_4\right\}
+	Fix $\delta \in (0,1)$.
+Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$, $b_4$, and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
+	\begin{equation*}
+	n \geq \max\left\{\frac{(1 + \delta)^2}{(1 - \delta)^2} \cdot (\log n)^{dp_d}\cdot b_3^d, b_4\right\}
 	\end{equation*}
@@
 	\label{eqn: local_spread}
-	s(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 \nu_d r^d}{20\Lambda_{\sigma}},
+	s(\widetilde{G}_{n,r}) \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\lambda_{\sigma}^2(2r)^d}{\Lambda_{\sigma}^2(L\rho)^d},
 	\end{equation}
@@
 	\label{eqn: conductance}
-	\Phi(\widetilde{G}_{n,r}) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}},
-	\end{equation}
-	hold with probability at least $1 - \frac{b_5}{n} - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
+	\Phi(\widetilde{G}_{n,r}) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}
+	\end{equation}
+	hold with probability at least $1 - \frac{b_5}{n} - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
 \end{proposition}
@@
 Taking these results as given, the proof of Theorem \ref{thm: mixing_time_upper_bound} is more or less complete.
-Since the condition $\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10$ is satisfied, we may apply Proposition \ref{prop: pointwise_mixing_time} and obtain
-\begin{align*}
-\tau_{\infty}(\widetilde{G}_{n,r}) & \leq  \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3
-\\
-& \leq \frac{2^{29}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{28800\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \log^2\left(\frac{280\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3 \\
-& \leq \frac{2^{34}\Lambda_{\sigma}^4\rho^2L^2 d^3}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + 3
-\end{align*}
-whereupon the theorem follows after an appropriate choice of universal constants $c_2 = 2^{34}, c_3 = 3$, and constants $b_2 = b_5 + \frac{7500}{\lambda_{\sigma}\nu_dr^d} + 25(\widetilde{\vol}_{\Pbb,r}(\Csig))^2$ and $b_1 = \frac{1}{b_3^d} + b_4$.
+Since the condition $\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10$ is satisfied, we may apply Proposition \ref{prop: pointwise_mixing_time}.
+Noting that:
+\begin{itemize}
+	\item by~\eqref{eqn: local_spread}, for any constant $c > 0$,
+	\begin{align*}
+	\log\biggl(\frac{1}{s(\wt{G}_{n,r})}\biggr) & \leq d \log\biggl(c^{1/d}\frac{40^{1/d}}{9^{1/d}} \cdot \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \cdot \frac{\lambda_{\sigma}^{2/d}L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \\
+	& \leq d \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(\frac{40^{1/d}}{9^{1/d}} \cdot \frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr)
+	\end{align*}
+	\item By assumption $r/\sigma \leq 1/(4d)$. Thus 
+	\begin{equation*}
+	1 - \frac{r}{4\rho L} \geq 1 - \frac{r}{4\sigma} \geq \frac{15}{16}
+	\end{equation*}
+	and
+	\begin{equation*}
+	\Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr) \geq 1 - \frac{1}{4}\sqrt{\frac{d + 2}{2d^2\pi}} \geq 1 - \frac{1}{4\sqrt{2}}.
+	\end{equation*}
+
+	Thus from~\eqref{eqn: conductance}, we obtain
+	\begin{align*}
+	\frac{1}{\Phi^2(\wt{G}_{n,r})} & \leq \frac{36^2 \cdot 16^2}{15^2(1 - \delta)^2(1 - 1/(4\sqrt{2}))^4 2\pi} \cdot \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \\
+	& \leq \frac{511}{(1 - \delta)^2} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4}.
+	\end{align*}
+\end{itemize}
+Hence, by Proposition~\ref{prop: pointwise_mixing_time} it holds that
+\begin{align*}
+\tau_{\infty}(\widetilde{G}_{n,r}) & \leq \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \\
+& \leq \frac{1022(1 + \delta)^{4/d}}{(1 - \delta)^{4/d + 2}} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
+& ~~ 3d\frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 \\
+& \leq 1022\biggl(1 + \Bigl(\frac{32}{d} + 8\Bigr)\delta\biggr) \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
+& ~~ 3d(1 + 32\delta)\log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 
+\end{align*}
+where $c_4 := 63, c_5 := 2240$, and the final inequality holds whenever $\delta < 1/(8 + 16/d)$.
+Thus the Theorem holds upon proper choice of universal constants $c_2 = 1022$, $c_3 = 3$, and constants $b_1 = b_3^d + b_4$, $b_2 = \min\{\wt{\vol}_{\Pbb,r}(\Csig), \lambda_{\sigma}\nu_dr^d/8\}$.
+
 In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
@@
 Let $A$ be the adjacency matrix of an undirected graph $G = (V,E)$, and $D$ the associated diagonal degree matrix.
-The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$ with elements $\pi_u = D_{uu}/\vol(V;G)$.
+The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$ with elements $\pi(u) = D_{uu}/\vol(V;G)$.
 Denote the $t$-step probability distribution of this random walk, originating from a  vertex $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
@@
 and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
-We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$, and $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$,
+We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$, and $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$.
 
 \paragraph{Proof of~\eqref{eqn:min_degree}:}
-Applying Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/5$, we have that
-\begin{equation*}
-\widetilde{d}_{\min} \geq \frac{24}{125} \lambda_{\sigma} \nu_d r^d n
-\end{equation*} 
-with probability at least $1 - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}}$, and therefore for any  
-\begin{equation*}
-n \geq \frac{53}{\lambda_\sigma \nu_dr^d} =: b_4
-\end{equation*}
-the minimum degree $\widetilde{d}_{\min} \geq 10$.
+
+Applying Lemma~\ref{lem:graph_functional_concentration} with $\delta = 1/2$, we see that
+\begin{align*}
+\wt{d}_{\min} & \geq \frac{n}{4}\biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)\lambda_{\sigma} \nu_d r^d \\
+& \geq \frac{n}{8}\lambda_{\sigma} \nu_d r^d,
+\end{align*}
+with probability at least $1 - 2n\exp\Bigl\{-\lambda_{\sigma} \nu_dr^dn/28\Bigr\}$. Therefore for any
+\begin{equation*}
+n \geq \frac{80}{\lambda_{\sigma}\nu_dr^d} =:b_4
+\end{equation*}
+the minimum degree $\wt{d}_{\min} \geq 10$.
 
@@
 
-We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$. Then applying Lemma \ref{lem:ball_bounds_in_probability} with $\delta = 1/5$, we have
-\begin{align*}
-s(\widetilde{G}_{n,r}) & \geq \frac{9}{10} \cdot \frac{\left(\frac{6}{25}\right)^2 (1 - \delta)^2 \lambda_{\sigma}^2 \nu_d r^{2d}}{(1 + \delta)\widetilde{\vol}_{\Pbb,r}(\Csig)n^2} \\
-& \geq \frac{1}{40} \frac{\lambda_{\sigma^2} \nu_d r^{d}}{\Lambda_{\sigma}}
-\end{align*}
-with probability at least $1 - 2n\exp\set{-\frac{2\lambda_{\sigma} \nu_d r^d n}{1875}} - 2\exp\set{-\frac{2}{25}n(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
+We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
+Then applying Lemma \ref{lem:ball_bounds_in_probability} to upper bound the minimum degree and lower bound the volume, we have that with probability at least $1 - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$
+\begin{align*}
+s(\widetilde{G}_{n,r}) & \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\nu_d^2 r^{2d} \lambda_{\sigma}^2}{\wt{\vol}_{\Pbb,r}(\mc{C}_{\sigma})} \\
+& \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\nu_d r^d \lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \nu(\mc{C}_{\sigma})} \\
+& \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\lambda_{\sigma}^2(2r)^d}{\Lambda_{\sigma}^2(L\rho)^d},
+\end{align*}
+where the last inequality follows by Assumption~\ref{asmp: embedding}, which ensures that $\mc{C}_{\sigma}$ is contained in a ball of radius $L\rho/2$.
 
 \paragraph{Proof of \eqref{eqn: conductance}:}
-
-Roughly, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{b_5}{n}$
-\begin{equation*}
-\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}}.
+Roughly speaking, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{b_5}{n}$,
+\begin{equation*}
+\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}
 \end{equation*}
@@
 \begin{proof}
-	The claim follows by simple manipulations:
+	The claim follows by direct manipulations:
 	\begin{align*}
@@
 	& \geq \sum_{u \in S} \frac{\deg(u;G) - \pi(S)/(\min_{u \in V}\pi(u))}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \\
+	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $S \not\in \mc{L}(G)$} \\
 	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
@@
 In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut for the remaining sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
+Let $p_d = 3/4$ if $d = 2$, and $p_d = 1/d$ if $d \neq 2$.
 
@@
 	\label{lem: graph_conductance_profile_lb}
+	Fix $\delta \in (0,1)$.
 Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$ and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
 	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{b_3}\right)^d
+	\frac{n}{(\log n)^{d p_d}} \geq \frac{(1 + \delta)^2}{(1 - \delta)^2}b_3^d
 	\end{equation*}
@@
 	\label{eqn: graph_conductance_profile_lb}
-	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \geq \frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{14} \rho L \sqrt{d}},
-	\end{equation}
-	with probability at least $1 - \frac{b_5}{n}$. 
+	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}.
+	\end{equation}
+	with probability at least $1 - \frac{b_5}{n} - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$. 
 \end{lemma}
@@
 	Let $T:\Csig \to \Csig[\Xbf]$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.
-Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}),r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)}$.
+Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}), \lambda_{\sigma}r/(2^{d+3}d\Lambda_{\sigma})}$.
 Then there exists a constant $b_6 > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
@@
 Clearly, Lemma \ref{lem: graph_to_continuous_conductance} is useful only when combined with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-Proposition 5 of \cite{garciatrillos16} establishes such an upper bound, with respect to transportation maps on measures supported on open, connected and bounded domains with Lipschitz boundaries.
-The following result is a restatement of this Proposition with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
-Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Proposition 5 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
+Theorem 1.1 of \cite{garciatrillos16b} establishes such an upper bound, with respect to transportation maps on measures supported on open, connected and bounded domains with Lipschitz boundaries.
+The following result is a restatement of this Theorem with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
+Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Theorem 1.1 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
 Let $\widetilde{n} = \abs{\Csig[\Xbf]}$.
 
-\begin{theorem}[Restatement of Proposition 5 of \cite{garciatrillos16}]
+\begin{theorem}[Restatement of Theorem 1.1 of \cite{garciatrillos16b}]
 	\label{thm: stagnating_transportation_maps}
-	There exists constants $b_3$ and $b_5$ which do not depend on the sample size such that for any $\delta > 0$, the following statement holds: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{\max\{\frac{3}{d},1\}}} \geq \left(\frac{1}{b_3\delta}\right)^{d}
-	\end{equation*}
-	then with probability at least $1 - \frac{b_5}{n}$ there exists a transportation map $T_n$ between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$
-	which satisfies
-	\begin{equation*}
-	\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \leq \delta.
+	There exists a constant $b_5$ which do not depend on $n$ such that with probability at least $1 - \frac{b_5}{n}$:
+	\begin{equation*}
+	\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \leq 
+	b_{5} \begin{cases*}
+	\frac{\log(n)^{3/4}}{n^{1/2}},&~~\textrm{if $d = 2$,} \\
+	\frac{\log(n)^{1/d}}{n^{1/d}},&~~\textrm{if $d \neq 2$.}
+	\end{cases*} 
 	\end{equation*}
@@
 	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r} > \frac{\lambda_{\sigma}^2 r}{2^{13} \Lambda_{\sigma}^2 \rho L \sqrt{d}}.
+	\widetilde{\Phi}_{\Pbb,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}.
 	\end{equation*}
@@
 With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
-Fix
-\begin{equation*}
-\delta = \min\set{\frac{\lambda_{\sigma}^2\nu_dr^d}{40\Lambda_{\sigma}},r, \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r),\frac{\widetilde{\Phi}_{\Pbb,r} \lambda_{\sigma}^2\nu_dr^d}{40(2b_6 + \widetilde{\Phi}_{\Pbb,r}) \Lambda_{\sigma}}};
-\end{equation*}
-and suppose $n$ is large enough so that $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\Pbb)} \leq \delta$ for the optimal transportation map $T_n$.
-By \eqref{eqn: local_spread}, $\delta \leq s(\widetilde{G}_{n,r})$ . Therefore, we may apply Lemma~\ref{lem: graph_to_continuous_conductance} and obtain
-\begin{align*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq \frac{\widetilde{\Phi}_{\Pbb,r}}{2},
+\begin{proof}[Lemma~\ref{lem: graph_conductance_profile_lb}]
+To invoke Lemma~\ref{lem: graph_to_continuous_conductance}, we must establish an appropriate upper bound on $\|\mathrm{Id} - T_n\|_{L^{\infty}(\wt{P})}$.
+We do so using Theorem~\ref{thm: stagnating_transportation_maps}, which implies that if
+\begin{equation*}
+n^{1/d} > b_5\log(n)^{p_d} \cdot \frac{(1 + \delta)^2}{(1 - \delta)^2}  \max\Biggl\{\frac{b_6 (1 + \delta)^2 \Lambda_{\sigma}^2 (L\rho)^d}{9(1 - \delta)^2 \lambda_{\sigma}^2 (2r)^d \wt{\Phi}_{\Pbb,r}}, \frac{2^{d + 3}d \Lambda_{\sigma}}{r \lambda_{\sigma}}\Biggr\} =: \log(n)^{p_d} \cdot b_3 \cdot \frac{(1 + \delta)^2}{(1 - \delta)^2}
+\end{equation*}
+then
+\begin{equation*}
+\|\mathrm{Id} - T_n\|_{L^{\infty}(\wt{P})} \leq \min\biggl\{\frac{\delta \cdot s(\wt{G}_{n,r}) \wt{\Phi}_{\Pbb,r}}{b_6(1 + \delta \wt{\Phi}_{\Pbb,r})}, \frac{\lambda_\sigma r}{2^{d + 3}d \Lambda_{\sigma}}\biggr\}
+\end{equation*}
+(In the above, we take as given that the inequality~\eqref{eqn: local_spread} is satisfied.) As a result we may apply Lemma~\ref{lem: graph_to_continuous_conductance}, from which we obtain
+\begin{align*}
+\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{b_6 \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{b_6 \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}} \\
+& \geq (1- \delta)\widetilde{\Phi}_{\Pbb,r},
 \end{align*}
@@
 Then, Lemma~\ref{lem: nonuniform_continuous_conductance} yields the desired result.
-It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we do in the following two subsections.
+\end{proof}
+It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we do in Appendices~\ref{subsec:pf_graph_to_continuous_conductance}-\ref{subsec:pf_uniform_continuous_conductance}.
 
 \subsection{Proof of Lemma \ref{lem: graph_to_continuous_conductance}}
+\label{subsec:pf_graph_to_continuous_conductance}
 Let $S \subseteq \Csig[\Xbf]$ belong to $\mathcal{L}(\widetilde{G}_{n,r})$, and denote $\Sset := T^{-1}(S)$.
@@
 	\label{lem: continuous_pi_lb}
-	Suppose $\varDelta \leq \lambda_{\sigma}/(2^{d+1}d\Lambda_{\sigma}r)$.
+	Suppose $\varDelta \leq \lambda_{\sigma}r/(2^{d+3}d\Lambda_{\sigma})$.
 Then there exists a constant $b_9 > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
@@
 \end{align*}
-where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}/(2^{d + 1} dr\Lambda_{\sigma})$, which implies $b_7\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
+where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}r/(2^{d + 3} d\Lambda_{\sigma})$, which implies $b_7\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
 
@@
 \paragraph{Population-level conductance with uniform density.}
-We first state an analogous result for the special case where the density $f$ is uniform everywhere on $\Csig$. For $x \in \Csig$ and measurable $\Sset \subseteq \Csig$, let 
-\begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\Csig \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{\int_{\Sset} \ell_{\nu,r}(x) \dx}{\int_{\Csig} \ell_{\nu,r}(x) \dx}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
-\end{equation*}
-The uniform continuous normalized cut and conductance are then defined analogously to the $\Pbb$-weighted case,
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\nu,r}(\Sset).
-\end{equation*}
-where the minimum is over measurable sets $\Sset \subseteq \Csig$.
+For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$.
+Further define
+\begin{equation*}
+\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
+\end{equation*}
+The uniform continuous normalized cut and conductance are then
+\begin{equation*}
+\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
+\end{equation*}
+where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.
 
@@
 	\label{lem: uniform_continuous_conductance}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with Lipschitz constant $L$.
-Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$, the uniform conductance $\widetilde{\Phi}_{\nu,r}$ satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} > \frac{r}{2^{13} \rho L \sqrt{d}}.
+	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
+Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.
+Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
+	\begin{equation*}
+	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
 	\end{equation*}
 \end{lemma}
-
-Most of the technical work needed to show Lemma~\ref{lem: nonuniform_continuous_conductance} involves proving Lemma~\ref{lem: uniform_continuous_conductance}.
-We first show that  Lemma~\ref{lem: nonuniform_continuous_conductance} is a simple consequence of Lemma~\ref{lem: uniform_continuous_conductance} -- and \ref{asmp: bounded_density} -- before turning to prove Lemma~\ref{lem: uniform_continuous_conductance}.
-
-To relate the uniform- and $\Pbb$-continuous conudctances, observe that by \ref{asmp: bounded_density} we obtain
+Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
+\begin{corollary}
+	\label{cor: uniform_continuous_conductance}
+	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
+Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
+	\begin{equation*}
+	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
+	\end{equation*}
+\end{corollary}
+
+Most of the technical work needed to show Lemma~\ref{lem: nonuniform_continuous_conductance}---and in turn, Corollary~\ref{cor: uniform_continuous_conductance}---involves proving Lemma~\ref{lem: uniform_continuous_conductance}.
+We first show that  Lemma~\ref{lem: nonuniform_continuous_conductance} is a simple consequence of Corollary~\ref{cor: uniform_continuous_conductance}---and \ref{asmp: bounded_density}---before turning to prove Lemma~\ref{lem: uniform_continuous_conductance}.
+
+\begin{proof}[of Lemma~\ref{lem: nonuniform_continuous_conductance}]
+To relate the uniform- and $\Pbb$-continuous conductances, observe that by \ref{asmp: bounded_density} we obtain
 \begin{align*}
@@
 & \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(\Sset^c \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\widetilde{Q}_{\nu,r}(\Sset,\Sset^c)}{\pi_{\nu,r}(\Sset)}
-\end{align*}
-with equivalent reasoning leading to bound $\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)/\piwt_{\Pbb,r}(\Sset) \leq (\lambda_{\sigma}^2/\Lambda_{\sigma}^2) \widetilde{Q}_{\nu,r}(\Sset,\Sset^c)/\piwt_{\nu,r}(\Sset)$.
-Lemma~\ref{lem: nonuniform_continuous_conductance} therefore follows from Lemma~\ref{lem: uniform_continuous_conductance}, and it remains to show the latter Lemma.
-
-\paragraph{Proof of Lemma \ref{lem: uniform_continuous_conductance}:}
-Lower bounds on the conductance of geometric random walks follow a typical pattern.
-The first step is to establish that an isoperimetric inequality holds uniformly over the domain of interest, in this case $\Csig$.
-The following result contains the isoperimetric inequality we will use.
-It is stated and proved in \cite{abbasi-yadkori2016a}; for completeness, we reproduce the proof here.
+& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\widetilde{Q}_{\nu,r}(\Sset,\Sset^c)}{\pi_{\nu,r}(\Sset)}.
+\end{align*}
+Exchanging $\mc{S}$ and $\mc{S}^c$ in the above, we also have $\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)/\piwt_{\Pbb,r}(\Sset^c) \geq (\lambda_{\sigma}^2/\Lambda_{\sigma}^2) \widetilde{Q}_{\nu,r}(\Sset,\Sset^c)/\piwt_{\nu,r}(\Sset^c)$, and the claim follows by~\ref{cor: uniform_continuous_conductance}.
+\end{proof}
+
+Lemma~\ref{lem: nonuniform_continuous_conductance} therefore follows from Lemma~\ref{lem: uniform_continuous_conductance} (by way of~\ref{cor: uniform_continuous_conductance}), and it remains to prove this Lemma.
+
+\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
+\label{subsec:pf_uniform_continuous_conductance}
+Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance.
+The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use.
+For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
+\begin{equation*}
+\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
+\end{equation*}
+where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
+\begin{enumerate}
+	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
+	\begin{equation*}
+	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
+	\end{equation*}
+	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
+	\begin{equation*}
+	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
+	\end{equation*}
+	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
 	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
 		\label{lem: nonconvex_isoperimetry}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \Csig$ with Lipschitz constant $L$.
-Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\Csig$,
-	\begin{equation*}
-	\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2))
+		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
+Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$,
+		\begin{equation*}
+		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
 		\end{equation*}
 	\end{lemma}
-The proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\Csig$ is itself convex, and is a primary technical contribution of the seminal work \cite{lovasz1990}, extended by \cite{dyer1991} among (many) others.
-Once the result is shown in the convex setting, however, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
+	\item[4.] 
+	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
+	\begin{equation*}
+	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
+	\end{equation*}
+	\begin{lemma}
+		\label{lem: one_step_distributions}
+		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
+		\begin{equation}
+		\label{eqn:one_step_distributions_1}
+		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
+		\end{equation}
+		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
+		\begin{equation}
+		\label{eqn:one_step_distributions_2}
+		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
+		\end{equation}
+	\end{lemma}
+	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
+	\begin{equation*}
+	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
+	\end{equation*}
+	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
+	\begin{equation*}
+	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
+	\end{equation*}
+\end{enumerate}
+The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e.
+a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show.
+In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
+\begin{equation*}
+\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
+\end{equation*}
+Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$.
+Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
+\begin{equation*}
+\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
+\end{equation*}
+Otherwise, we deduce that
+\begin{align*}
+\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
+& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
+& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
+& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
+& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
+\end{align*}
+Setting $\delta = 1/3$, we have
+\begin{equation*}
+\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
+\end{equation*}
+and putting $a = r\ell/(2\rho L)$ yields the claim.
+
+Now, we turn to establishing the inequalities used in the above chain.
+
+\paragraph{Step 1: Lower bound the ergodic flow.}
+By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
+\begin{equation*}
+2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
+\end{equation*}
+
+\paragraph{Step 2: Estimate the stationary distribution.}
+
+Both the upper and lower  bounds on $\wt{\pi}_{\nu,r}(\mc{S})$ are a direct consequence of the following inequalities:
+\begin{equation*}
+\ell \nu_d r^d \nu(\mc{S})  \leq {J}_{\nu,r}(\mc{S}) \leq \nu_d r^d \nu(\mc{S}).
+\end{equation*}
+\paragraph{Step 3: Isoperimetric inequality.}
+NB: the proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\mc{C}_{\sigma}$ is itself convex, and is a primary technical contribution of the seminal work \textcolor{red}{(Lovasz 1990)}, extended by \textcolor{red}{(Dyer 1991)} among others.
+However, once the result is shown in the convex setting, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
 \begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
@@
 	\end{equation*}
-	By Theorem 2.2 of \cite{lovasz1990},
+	By Theorem 2.2 of \textcolor{red}{(Lovasz 1990)},
 	\begin{align*}
@@
 \end{proof}
-With an isoperimetric inequality in hand, the next step towards showing a lower bound on conductance is to prove that for any pair of sufficiently close points $u,v \in \Csig$, the total variation distance between the distributions $\widetilde{P}_{\nu,r}(u;\cdot)$ and $\widetilde{P}_{\nu,r}(v;\cdot)$ is small.
-\begin{lemma}[One-step distributions]
-	\label{lem: one_step_distributions}
-	Let $u,v \in \Csig$ be such that 
-	\begin{equation*}
-	\norm{u - v} \leq \frac{r t}{2\sqrt{d}}
-	\end{equation*}
-	for some $0 < t < 1$, and further assume there exists $\ell > 0$ such that $\ell_{\nu,r}(u), \ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then,
-	\begin{equation*}
-	\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}} \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell
-	\end{equation*}
-	where $\norm{P - Q}_{\mathrm{TV}}$ is the total variation distance between probabilities $P$ and $Q$. 
-\end{lemma}
-For the moment, we will take Lemma \ref{lem: one_step_distributions} as given and prove Lemma \ref{lem: uniform_continuous_conductance}, before returning to prove Lemma \ref{lem: one_step_distributions}.
-Deriving a lower bound on conductance from a isoperimetric inequality (i.e., Lemma \ref{lem: nonconvex_isoperimetry}) along with a bound on the one-step distributions is standard.
-Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$, and let $\ell = 6/25$.
-Note by Lemma \ref{lem: local_conductance}, as $r \leq \sigma/(2\sqrt{d})$, $\ell \nu_d r^d  \leq \ell_{\nu,r}(x)$ for all $x \in \Csig$.
-We will show that
-\begin{equation}
-\label{eqn: uniform_continuous_conductance_1}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) d \widetilde{\pi}_{\nu,r}(x) \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min\set{\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}.
-\end{equation}
-Then, dividing both sides by $\min\set{\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}$ yields the desired result~\eqref{eqn: uniform_continuous_conductance_1}, as $\Sset_1,\Sset_2$ was an arbitrary partition.
-
-Now, consider the sets
-\begin{align*}
-\Sset_1' & = \set{x \in \Sset_1: \widetilde{P}_{\nu,r}(x; \Sset_2) < \frac{\ell}{4}} \\
-\Sset_2' & = \set{x \in \Sset_2: \widetilde{P}_{\nu,r}(x; \Sset_1) < \frac{\ell}{4}}
-\end{align*}
-and $\Sset_3' = \Csig \setminus (\Sset_1' \cup \Sset_2')$. Suppose $\widetilde{\pi}_{\nu,r}(\Sset_1') < \widetilde{\pi}_{\nu,r}(\Sset_1)/2$. Then,
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \,d\widetilde{\pi}_{\nu,r}(x) \geq \frac{\ell \widetilde{\pi}_{\nu,r}(\Sset_1)}{8}
-\end{equation*}
-Similarly, if $\widetilde{\pi}_{\nu,r}(\Sset_1') < \widetilde{\pi}_{\nu,r}(\Sset_1)/2$, then since
-\begin{equation*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \,d\widetilde{\pi}_{\nu,r}(x) = \int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_1) \,d\widetilde{\pi}_{\nu,r}(x)
-\end{equation*}
-a symmetric result holds. In either case, \eqref{eqn: uniform_continuous_conductance_1} follows.
-
-Now, suppose $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2'$ and $\Sset_2$. For every $u \in \Sset_1'$ and $v \in \Sset_2'$ we have that
-\begin{equation*}
-\norm{\widetilde{P}_{\nu,r}(u;\cdot) - \widetilde{P}_{\nu,r}(v;\cdot)}_{\mathrm{TV}} \geq 1 - \widetilde{P}_{\nu,r}(u;\Sset_1) - \widetilde{P}_{\nu,r}(v;\Sset_2) > 1 - \frac{\ell}{2}.
-\end{equation*}
-and thus by Lemma \ref{lem: one_step_distributions},
-\begin{equation*}
-\norm{u - v} \geq \frac{\sqrt{2 \pi } r \ell}{3 \sqrt{3 d}} \geq \frac{\sqrt{2}r \ell}{3\sqrt{d}}.
-\end{equation*}
-Since $u \in \Sset_1', v \in \Sset_2'$ were arbitrary, the same inequality holds for $\mathrm{dist}(\Sset_1', \Sset_2')$. Therefore by Lemma \ref{lem: nonconvex_isoperimetry}
-\begin{equation}
-\label{eqn: uniform_continuous_conductance_2}
-\nu(\Sset_3') \geq  \frac{\sqrt{2} r \ell}{3 \rho L \sqrt{d}} \min \set{\nu(\Sset_1'), \nu(\Sset_2')}.
-\end{equation}
-Let $\Sset \subseteq \Csig$ be arbitrary, and note that an upper (lower) bound on $\nu(\Sset)$ implies an upper (lower) bound on $\widetilde{\pi}_{\nu,r}(\Sset)$, as follows:
-\begin{equation}
-\label{eqn: uniform_continuous_conductance_3}
-\ell \nu_d r^d \nu(\Sset) \leq \widetilde{\pi}_{\nu,r}(\Sset) \leq \nu_d r^d \nu(\Sset).
-\end{equation}
-We now prove~\eqref{eqn: uniform_continuous_conductance_1}, the desired result:
-\begin{align*}
-\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2) \dx & = \frac{1}{2} \biggl(\int_{\Sset_1} \widetilde{P}_{\nu,r}(x; \Sset_2)  \,d\widetilde{\pi}_{\nu,r}(x) + \int_{\Sset_2} \widetilde{P}_{\nu,r}(x; \Sset_1) \,d\widetilde{\pi}_{\nu,r}(x)\biggr) \\
-& \geq \frac{\ell}{8} \Bigl( \widetilde{\pi}_{\nu,r}(\Sset_1 \setminus \Sset_1') + \widetilde{\pi}_{\nu,r}(\Sset_2 \setminus \Sset_2') \Bigr) \\
-& \geq \frac{\ell}{8} \widetilde{\pi}_{\nu,r}(\Sset_3') \\
-& \geq \frac{\ell^2}{8 \nu(\Csig)} \nu(\Sset_3') \tag{by \eqref{eqn: uniform_continuous_conductance_3}}\\
-& \geq \frac{\sqrt{2} r \ell^3}{24 \rho L \sqrt{d} \nu(\Csig)} \min \set{\nu(\Sset_1'), \nu(\Sset_2')} \tag{by \eqref{eqn: uniform_continuous_conductance_2}}\\
-& \geq \frac{\sqrt{2} r \ell^4}{24 \rho L \sqrt{d}} \min \set {\widetilde{\pi}_{\nu,r}(\Sset_1'), \widetilde{\pi}_{\nu,r}(\Sset_2')} \tag{by \eqref{eqn: uniform_continuous_conductance_3}}\\
-& \geq \frac{\sqrt{2} r \ell^4}{48 \rho L \sqrt{d}} \min \set {\widetilde{\pi}_{\nu,r}(\Sset_1), \widetilde{\pi}_{\nu,r}(\Sset_2)}
-\end{align*}
-where the last line follows since $\pi_{\nu,r}(\Sset_1') \geq \pi_{\nu,r}(\Sset_1)/2$, and likewise for $\Sset_2'$ and $\Sset_2$.
-To prove Lemma \ref{lem: uniform_continuous_conductance}, it remains to prove Lemma \ref{lem: one_step_distributions}, and we do this next.
-
-\paragraph{Proof of Lemma \ref{lem: one_step_distributions}:}
-
-The key result needed to show Lemma \ref{lem: one_step_distributions} deals with volume of the overlap $B(u,r) \cap B(v,r)$. We state this result and immediately prove it.
+
+\paragraph{Step 4: Total variation distance.}
+
+\begin{proof}[Proof of Lemma~\ref{lem: one_step_distributions}]
+	Note that~\eqref{eqn:one_step_distributions_2} follows from~\eqref{eqn:one_step_distributions_1} by first taking the supremum over all $\mc{S} \subseteq \mc{C}_{\sigma}$, and then the infimum over all $x \in \mc{S}_1$ and $y \in \mc{S}_2$.
+
+	It remains to show~\eqref{eqn:one_step_distributions_1}.
+Let $\mc{R} = \mc{C}_{\sigma} \setminus \mc{S}$ and $\mc{I} = B(x,y) \cap B(y,r)$, and suppose without loss of generality that $\ell_{\nu,r}(x) > \ell_{\nu,r}(y)$.
+We can relate $\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})$ to the volume of the intersection $\mc{I}$ as follows:
+	\begin{align*}
+	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) & = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \\
+	& = 1 - \biggl(\frac{\nu\bigl(B(x,r) \cap \mc{R}\bigr)}{\ell_{\nu,r}(x)} + \frac{\nu\bigl(B(y,r) \cap \mc{S}\bigr)}{\ell_{\nu,r}(y)}\biggr) \\
+	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr)\Bigr) \\
+	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\nu\bigl(\mc{I} \cap \mc{C}_{\sigma}\bigr) \\
+	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu(\mc{I}) - \nu\bigl(B(x,r)\bigr) + \ell_{\nu,r}(x)\Bigr) \\
+	& = \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu_dr^d - \nu(\mc{I})\Bigr).
+	\end{align*}
+	Now, by hypothesis $\ell_{\nu,r}(x) \geq \ell \nu_dr^d$. On the other hand, Lemma~\ref{lem: volume_of_spherical_cap} gives a lower bound on the volume of $\mc{I}$, and from this we obtain
+	\begin{equation*}
+	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) \leq \frac{\|x - y\|}{\ell r} \sqrt{\frac{d + 2}{2\pi}};
+	\end{equation*}
+	solving for $\|x - y\|$ yields~\eqref{eqn:one_step_distributions_1}.
+\end{proof}
+
+We have completed our proof of (in turn) Lemmas~\ref{lem: uniform_continuous_conductance}, \ref{lem: nonuniform_continuous_conductance}, and \ref{lem: graph_conductance_profile_lb}.
+As a result, Proposition \ref{prop: local_spread_conductance} is proved, and the proof of Theorem \ref{thm: mixing_time_upper_bound} is complete.
+
+\section{Volume Estimates}
+In this section, we establish some inequalities regarding the volume of (intersections of) balls, which we used in Appendices A and B. 
 \begin{lemma}
-	\label{lem: overlap_balls_1}
-	Let $u,v \in \Rd$ be points such that $\norm{u - v} \leq t\frac{r}{2\sqrt{d}}$ for some $0 < t < 1$. Then,
-	\begin{equation*}
-	\nu(B(u,r) \cap B(v,r)) \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
-	\end{equation*}
+	\label{lem: overlap_balls}
+	For any $x,y \in \Rd$, it holds that
+	\begin{equation}
+	\label{eqn:overlap_balls_1}
+	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
+	If additionally $\|x - y\| \leq \sigma$, then
+	\begin{equation}
+	\label{eqn:overlap_balls_2}
+	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
+	An immediate implication of~\eqref{eqn:overlap_balls_2} is that for any $x \in \mc{C}_{\sigma}$:
+	\begin{equation}
+	\label{eqn:uniform_local_conductance}
+	\ell_{\nu,r}(x) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
 \end{lemma}
 \begin{proof}
-	We will treat only the case where $\norm{u - v} = t\frac{r}{2\sqrt{d}}$; if they are closer together the overlap of the volume will only increase.
-Then, it is not hard to see that $\mathcal{I} := B(u,r) \cap B(v,r)$ consists of two symmetric spherical caps, each with height
-	\begin{equation*}
-	h = r\left(1 - \frac{t}{4\sqrt{d}}\right)
+	We first prove~\eqref{eqn:overlap_balls_1}. It is not hard to see that $\mathcal{I} := B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height
+	\begin{equation*}
+	h = r - \frac{\|x - y\|}{2}
 	\end{equation*} 
@@
 	\begin{equation*}
-	\alpha = 1 - \frac{2r^2(1 - \frac{t}{4 \sqrt{d}}) - r^2(1 - \frac{t}{4 \sqrt{d}})^2}{r^2} = \frac{t^2}{16d}.
-	\end{equation*}
-	Expanding the incomplete beta function in integral form, we therefore have
+	\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{\|x - y\|^2}{4r^2}.
+	\end{equation*}
+	Expanding the incomplete beta function in integral form, we obtain
 	\begin{align*}
 	\nu\bigl(\mathcal{I}\bigr) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{3 t}{4\sqrt{d}} \right) \\
-	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 -  \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} \right)
-	\end{align*}
-	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral} (which we may validly apply since $\alpha \leq \frac{t^2}{16d}$), and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
+	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{ \|x - y\|}{r} \right) \\
+	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}} \right),
+	\end{align*}
+	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral}, and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
+
+	We now establish~\eqref{eqn:overlap_balls_2}.
+Assume that $\|x - y\| = \sigma$, as otherwise if $\|x - y\| < \sigma$ the volume of the overlap will only grow.
+Then $B(x,r) \cap B(y,\sigma)$ contains a spherical cap of radius $r$ and height $r - \frac{r^2}{2\sigma}$, and similar derivations to those used to show~\eqref{eqn:overlap_balls_1} imply that
+	\begin{equation*}
+	\nu(\cap_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation*}
 \end{proof}
 
-We now complete the proof of Lemma \ref{lem: one_step_distributions}. Let $\Sset_1 \cup \Sset_2 = \Csig$ be an arbitrary partition of $\Csig$. We will show that 
-\begin{equation*}
-\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - \ell.
-\end{equation*}
-Since this will hold for arbitrary $\Sset_1 \subset \Csig$, it will hold for the supremum over all such $\Sset_1$ as well, and therefore the same upper bound will hold for $\norm{\widetilde{P}_{\nu,r}(u; \cdot) - \widetilde{P}_{\nu,r}(v; \cdot)}_{\mathrm{TV}}$.
-Now, note that
-\begin{equation*}
-\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) = 1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1)
-\end{equation*}
-As before, let $\mathcal{I} = B(u,r) \cap B(v,r)$. Then we have
-\begin{equation*}
-\widetilde{P}_{\nu,r}(u; \Sset_2) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap (B(u,r)) \geq \frac{1}{\nu(B(u,r))} \nu(\Sset_2 \cap \mathcal{I})
-\end{equation*}
-with a symmetric inequality holding for $\widetilde{P}_{\nu,r}(v; \Sset_1)$. As a result,
-\begin{equation}
-1 - \widetilde{P}_{\nu,r}(u; \Sset_2) - \widetilde{P}_{\nu,r}(v; \Sset_1) \leq 1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap \mathcal{I}) \label{eqn: one_step_1}
-\end{equation}
-From here, some simple manipulations yield
-\begin{align}
-\nu(\Csig \cap \mathcal{I})  & = \nu(\mathcal{I}) - \nu(\mathcal{I} \setminus \Csig) \nonumber \\
-& \geq \nu\bigl(\mathcal{I}\bigr) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
-& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \tag{Lemma \ref{lem: overlap_balls_1}} \\
-& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right) \label{eqn: one_step_2} 
-\end{align}
-where the last inequality follows by the hypothesis $\ell_{\nu,r}(u),\ell_{\nu,r}(v) \geq \ell \nu_d r^d$. Then~\eqref{eqn: one_step_2} along with~\eqref{eqn: one_step_1} give the desired result
-\begin{align*}
-\widetilde{P}_{\nu,r}(u; \Sset_1) - \widetilde{P}_{\nu,r}(v; \Sset_1) & \leq  1 - \frac{1}{\nu_d r^d} \nu(\Csig \cap \mathcal{I}) \\
-& \leq 1 - \ell + \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}.
-\end{align*}
-We have completed our proof of Lemma \ref{lem: one_step_distributions}, and therefore (in turn), Lemmas~\ref{lem: uniform_continuous_conductance}, \ref{lem: nonuniform_continuous_conductance}, and \ref{lem: graph_conductance_profile_lb}.
-As a result, Proposition \ref{prop: local_spread_conductance} is proved, and the proof of Theorem \ref{thm: mixing_time_upper_bound} is complete.
+\subsection{Spherical caps and associated estimates}
+\label{subsec:caps}
+In this section, we state a result for the volume of a spherical cap and derive some 
+useful upper bounds. 
+\begin{lemma}
+	\label{lem: volume_of_spherical_cap}
+	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
+	\begin{equation*}
+	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
+	\end{equation*}
+	where
+	\begin{equation*}
+	\alpha := 1 - \frac{2 r h - h^2}{r^2}
+	\end{equation*}
+	and
+	\begin{equation*}
+	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
+	\end{equation*}
+	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
+\end{lemma}
+The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
+an upper bound on the ratio of Gamma functions. 
+\begin{lemma}
+	\label{lem: beta_integral}
+	For any $0 \leq \alpha \leq 1$,
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - 2\sqrt{\alpha}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	We can write 
+	\begin{equation*}
+	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
+	\end{equation*}
+	The first integral is simply the beta function, with
+	\begin{equation*}
+	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
+	\end{equation*}
+	Noting that for all $u \in [0,1]$ and $d \geq 1$, $u^{(d - 1)/2} \leq 1$, the second integral can be upper bounded as follows:
+	\begin{equation*}
+	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du \leq \int_{1 - \alpha}^{1}(1 - u)^{-1/2}du = \int_{0}^{\alpha} u^{-1/2}du = 2\sqrt{\alpha}.
+	\end{equation*}
+\end{proof}
+
+\begin{lemma}
+	\label{lem: beta_function}
+	\begin{equation*}
+	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
+	\end{equation*}
+\end{lemma}
+\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
 
@@
 	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}
-	\end{equation*} Suppose $\alpha \leq \frac{1}{9 \tau_{\infty}(G[S])}$,  $\varepsilon \leq \frac{1}{20}\vol(A;G)$.
-Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in S^g$ and $\beta \in \frac{1}{\vol(A;G)}(\frac{1}{100},\frac{2}{5})$ the sweep cut $S_{\beta,v}$ satisfies
+	\end{equation*} Suppose $\alpha \leq \frac{1}{9 \tau_{\infty}(G[S])}$,  $\varepsilon \leq \frac{1}{20\vol(A;G)}$.
+Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$ and $\beta \in \frac{1}{\vol(A;G)}(\frac{1}{100},\frac{2}{5})$ the sweep cut $S_{\beta,v}$ satisfies
 	\begin{equation*}
@@
 
-	\noindent The following statements hold for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$:
-
-	\noindent Assuming $\Csig$ satisfies~\ref{asmp: bounded_density}, with probability at least $1 - 2n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$,
+	\noindent The following statements hold for any $0 < r \leq \frac{\sigma}{2d}$:
+
+	\noindent Assuming $\Csig$ satisfies~\ref{asmp: bounded_density}, with probability at least $1 - 2n\exp\set{-\frac{ \delta^2 \lambda_{\sigma} \nu_d r^d n}{6(1 + \frac{\delta}{3})}}$,
 	\begin{equation}
 	\label{eqn:degwt_bound}
-	\frac{6}{25}(1 - \delta)\lambda_{\sigma}\nu_dr^dn \leq \degminwt \leq d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_dr^dn.
+	\frac{1}{2}\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2 \pi}}\biggr)(1 - \delta)\lambda_{\sigma}\nu_dr^dn \leq \degminwt \leq d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_dr^dn.
 	\end{equation}
@@
 	\begin{equation*}
-	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j)) = \ell_{\Pbb,r}(x_j) \geq \frac{6}{25} \lambda_{\sigma} \nu_d r^d
-	\end{equation*}
-	where the last inequality follows from Lemma~\ref{lem: local_conductance}.  Under~\ref{asmp: C'_bounded_density} we have for every $x_i \in \Cset'[\Xbf]$
-	\begin{equation*}
-	\mathbb{E}(\widetilde{\deg}_{n,r}(x_i)) \geq \lambda_{
+	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j) | x_j) \geq n \cdot \ell_{\Pbb,r}(x_j) \geq n \lambda_{\sigma} \cdot \biggl\{\min_{x \in \mc{C}_{\sigma}} \ell_{\nu,r}(x)\biggr\} \geq \frac{n}{2}\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2 \pi}}\biggr)\lambda_{\sigma}\nu_dr^d
+	\end{equation*}
+	where the last inequality follows from Lemma~\ref{lem: overlap_balls}.  Under~\ref{asmp: C'_bounded_density} we have for every $x_i \in \Cset'[\Xbf]$
+	\begin{equation*}
+	\mathbb{E}({\deg}_{n,r}(x_i)|x_i) \geq n \lambda_{
 		\sigma} \nu_d r^d.
@@
 	Then \eqref{eqn:degwt_bound} and \eqref{eqn:degpr_bound} each follow from Lemma~\ref{lem:bernstein_union}.
-
 	\paragraph{Proof of \eqref{eqn:volwt_bound}, \eqref{eqn:vol_bound}, \eqref{eqn:cut_bound}:}

### 2020-12-23 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Added revised version of JMLR submission, local_spectral_clustering_jmlr_revision_2.tex.

\documentclass[11pt,twoside]{article}
\usepackage[preprint]{jmlr2e}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{amsfonts,epsfig,graphicx}
\usepackage{afterpage}
\usepackage{amsmath,amssymb} 
% \usepackage{fullpage}
\usepackage{epsf} 
\usepackage{graphics} 
\usepackage{amsfonts,amsmath}
% \usepackage[sort,numbers]{natbib} 
\usepackage{psfrag,xspace}
\usepackage{color,etoolbox}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\renewcommand{\floatpagefraction}{.8}%

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{float}
\usepackage[export]{adjustbox}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{mathtools}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\cut}{\mathrm{cut}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

\ShortHeadings{Local Spectral Density Clustering}{Green, Balakrishnan and Tibshirani}
\firstpageno{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\begin{document}

\title{\textcolor{red}{The Geometry of Local Spectral Clustering}}

\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213
	\AND
	\name Sivaraman Balakrishnan \email sbalakri@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213
	\AND
	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213}

\maketitle

\begin{abstract}
	We analyze the Personalized PageRank (PPR) algorithm, a local spectral method
	for clustering, which extracts clusters using locally-biased random walks around
	a given seed node.  In contrast to previous work, we adopt a classical
	statistical learning setup, where we obtain samples from an unknown non-parametric distribution, and aim to identify geometrically salient clusters.  We introduce a pair of population-level geometric functionals---the \emph{normalized cut} and \emph{conductance}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large population conductance. We apply our general theory to establish that PPR identifies connected regions of high density (density clusters) that satisfy a set of natural geometric conditions. We also show a converse result, that PPR can fail to recover
	geometrically poorly-conditioned density clusters, even asymptotically. Finally,
	we provide empirical support for our theory.
\end{abstract}

\begin{keywords}
	graphs, spectral clustering, density clustering, Personalized PageRank, unsupervised learning
\end{keywords}

\section{Introduction}
In this paper, we consider the problem of clustering: splitting a given data set
into groups that satisfy some notion of within-group similarity and
between-group difference.  Our particular focus is on spectral clustering
methods, a family of powerful nonparametric clustering algorithms. Roughly
speaking, a spectral algorithm first constructs a geometric graph $G$, where
vertices correspond to samples, and edges correspond to proximities between
samples. The algorithm then estimates a feature embedding based on (an
appropriate) Laplacian matrix of $G$, and applies a simple clustering technique
(like $k$-means clustering) in the embedded feature space.

When applied to geometric graphs built from a large number of samples, global
spectral clustering methods can be computationally cumbersome and insensitive to
the local geometry of the underlying distribution
\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
\emph{local} spectral clustering algorithms, which leverage locally-biased
spectra computed using random walks around some user-specified seed node.  A
popular local clustering algorithm is the Personalized PageRank (PPR) algorithm,
first introduced by \citet{haveliwala2003}, and then further developed by
several others
\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.

Local spectral clustering techniques have been practically very successful
\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
many authors to develop supporting theory
\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
guarantees on traditional graph-theoretic notions of cluster quality (such as normalized cut and conductance). In contrast, in this paper we adopt a classical statistical viewpoint, and examine what the output of local clustering on a data set reveals about the underlying density $f$ of the samples. \textcolor{red}{(We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C}$, will approximately recover this candidate cluster. We pay special attention to the case where $\mc{C}$ is a \emph{density cluster} of $f$---defined as a connected component of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$---and show precisely how PPR accounts for both geometry and density in estimating a cluster.)}\\

\textcolor{red}{Alden: In our original submission, the preceding paragraph ended with the following sentence:
\begin{quote}
	In particular, we examine the ability of
	PPR to recover \emph{density clusters} of $f$, defined as the connected
	components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some
	$\lambda > 0$ (an object of central interest in the statistical clustering
	literature, dating back to the work of \citet{hartigan1981}). 
\end{quote}
This sentence no longer accurately describes our paper, so I substituted the part in parentheses above.}\\

Before giving a more detailed overview of our main results, we review some of the aforementioned worst-case guarantees, formally define PPR on a neighborhood graph, and introduce the population-level functionals that govern the behavior of local clustering \textcolor{red}{(in our statistical context)}.

\subsection{Review: worst-case guarantees for local spectral clustering}
As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.  For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR. For a set $C \subseteq V$ with complement $C^c = V \!\setminus\! C$, the \emph{cut} and \emph{volume} are respectively,
\begin{equation}
\label{eqn:cut_volume}
\cut(C;G) := \sum_{u \in C} \sum_{v \in C^c}
\1\{(u,v) \in E\},~~ \vol(C; G) := \sum_{u \in C}  \sum_{v \in V} \1\{(u,v) \in E\},
\end{equation}
and the \emph{normalized cut} of $C$ is
\begin{equation}
\label{eqn:normalized_cut}
\Phi(C; G) := \frac{\cut(C;G)}{\min \set{\vol(C; G), \vol(C^c; G)}}.
\end{equation} 
\cite{andersen2006} show that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of the candidate cluster is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$. \cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(C;G)$, defined as 
\begin{equation}
\label{eqn:conductance}
\Psi(C;G) := \min_{S \subseteq C} \Phi(S;G[C]),
\end{equation}
where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$---and show that if $\Phi(C;G)$ is much smaller than $\Psi(C;G)^2$, then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$. Our own analysis will build on that of~\cite{zhu2013}, and we will give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random geometric graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.

\subsection{PPR on a neighborhood graph}

We now formally describe this setting, as well as the method we will study: PPR on a neighborhood graph. Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution
$\Pbb$ on $\Rd$. We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure on $\Rd$. For a radius $r > 0$, we define
$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an
unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in
E$ if and only if $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
Euclidean norm. We denote by $A \in \Reals^{n \times n}$ the adjacency
matrix, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
also denote by $D$ the diagonal degree matrix, with entries $D_{uu} :=
\sum_{v \in V} A_{uv}$, and by $I{}$ the $n \times n$ identity matrix.

The PPR vector $p_v = p(v,\alpha;G_{n,r})$ is defined with respect to
a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
\begin{equation}
\label{eqn: ppr_vector}
p_v = \alpha e_{v} + (1 - \alpha) p_v W,
\end{equation}
where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over
$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
position $v$ and 0 elsewhere).

Once $p_v$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut of $p_v$. For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is 
\begin{equation}
\label{eqn: sweep_cuts}
S_{\beta,v} := \set{u \in V: \frac{p_v(u)}{D_{uu}} > \beta}.
\end{equation}
To determine $\wh{C}$, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate
\smash{$\wh{C} = S_{\beta^*}$} with minimum normalized cut.  For concreteness,
the PPR algorithm is summarized in Algorithm~\ref{alg:ppr}.

\begin{algorithm}
	\caption{PPR on a neighborhood graph}
	\label{alg:ppr}	
	{\bfseries Input:} data $X=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
	parameter $\alpha \in [0,1]$, seed $v \in X$, sweep cut range $(L,U)$. \\     
	{\bfseries Output:} cluster estimate $\wh{C} \subseteq V$.
	\begin{algorithmic}[1]
		\STATE Form the neighborhood graph $G_{n,r}$.
		\STATE Compute the PPR vector $p_v=p(v, \alpha; G_{n,r})$ as in
		\eqref{eqn: ppr_vector}.  
		\STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
		\eqref{eqn: sweep_cuts}. 
		\STATE Return the cluster \smash{$\wh{C} = S_{\beta^*}$}, where  
		$$
		\beta^* = \argmin_{\beta \in (L,U)}~ \Phi(S_{\beta}; G_{n,r}).
		$$
	\end{algorithmic}
\end{algorithm}

\subsection{Cluster estimation}
We need a metric to assess the accuracy with which $\wh{C}$ estimates the candidate cluster $\mc{C}$. One commonly used metric is the misclassification error, i.e. the size of the symmetric set difference
between $\wh{C}$ and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}. We
will consider a related metric, the volume of the symmetric set difference,
which weights misclassified points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
\begin{definition}
	\label{def:volume_symmetric_set_difference}
	For an estimator \smash{$\wh{C} \subseteq X$} and a set 
	$\mathcal{C} \subseteq \Rd$, their symmetric set difference is 
	\begin{equation*}
	\wh{C} \vartriangle \mathcal{C}[X] :=
	\bigl(\wh{C} \setminus \mathcal{C}[X]\bigr) \cup
	\bigl(\mathcal{C}[X] \setminus \wh{C}\bigr).
	\end{equation*}
	Furthermore, we denote the volume of the symmetric set difference by 
	$$
	\Delta(\wh{C}, \mathcal{C}[X]) := \vol_{n,r}(\wh{C} \vartriangle \mathcal{C}[X]). 
	$$
\end{definition}

\subsection{Population normalized cut and conductance}
As we will show, the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$ is intrinsically related to two population-level functionals of $\mc{C}$, the normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$, which we now define. Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) = \vol(\mc{C}[X]; G_{n,r})$; i.e. let
\begin{equation*}
\mathrm{cut}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\mc{C}^c} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x)~~ \mathrm{vol}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\Rd} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),
\end{equation*}
where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$.
\begin{definition}[Population normalized cut]
	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the \emph{population normalized cut} is
	\begin{equation}
	\label{eqn:population_normalized_cut}
	\Phi_{\Pbb,r}(\mc{C}) := \frac{\mathrm{cut}_{\Pbb,r}(\mc{C})}{\min\{\mathrm{vol}_{\Pbb,r}(\mc{C}), \mathrm{vol}_{\Pbb,r}(\mc{C}^c)\}}
	\end{equation}
\end{definition}

Let $\wt{\mathbb{P}}(\cdot) = \mathbb{P}(\cdot|x \in \mc{C})$ be the conditional distribution of $x$, i.e. the distribution with density function
\begin{equation*}
\wt{f}(x) :=
\begin{cases*}
\frac{1}{\mathbb{P}(\mc{C})} f(x),~~ & \textrm{if $x \in \mc{C}$} \\
0,~~ & \textrm{otherwise.}
\end{cases*}
\end{equation*}

\begin{definition}[Population conductance]
	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the \emph{population conductance} is
	\begin{equation}
	\label{eqn:population_conductance}
	\Psi_{\mathbb{P},r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S})
	\end{equation}
\end{definition}

It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering. Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) = \Psi(\mc{C}[X];G_{n,r})$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference. For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context. We will comment more on the relationship between these works and our own results in~\ref{subsec:related_work}.

\subsection{Summary of results}
A summary of our results (and an outline for this paper) is as follows.
\begin{itemize}
	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$. As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a non-parametric statistical context.
\end{itemize}
In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$---an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}.
\begin{itemize}
	\item In~\ref{subsec:recovery_well-conditioned_density_clusters}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$. These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Corollary~\ref{cor:density_cluster_volume_ssd_ub}).
	\item In~\ref{subsec:consistent_recovery_density_clusters}, we introduce a notion of \emph{density cluster consistency}, and establish conditions under which $\wh{C}$ is a consistent estimate of $\mc{C}_{\lambda}$.
	\item In~\ref{subsec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ will be provably large.
\end{itemize}
In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.

\subsection{Related Work}
\label{subsec:related_work}
First, however, we conclude this Section by summarizing some related work (in addition to the background already given above). In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership. In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating 
back to \citet{mcsherry2001} who gives conditions under which the entire
community structure can be recovered. In more recent work, \citet{rohe2011}
upper bound the fraction of nodes misclassified by a spectral algorithm for the
high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
results to the sparse (low average degree) regime. Relatedly,
\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
when the block model exhibits some hierarchical structure. The framework we
consider, in which nodes correspond to data points sampled from an underlying 
density, and edges between nodes are formed based on geometric proximity, is
quite different than the SBM, and therefore so is our analysis.

In general, the study of spectral algorithms on neighborhood graphs has been
focused on establishing asymptotic convergence of eigenvalues and eigenvectors
of certain sample objects to the eigenvalues and eigenfunctions of corresponding
limiting operators. \citet{koltchinskii2000} establish convergence of spectral
projections of the adjacency matrix to a limiting integral operator, with
similar results obtained using simplified proofs in
\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
the Laplacian matrix for a neighborhood graph of fixed radius. \citet{belkin07} and
\citet{garciatrillos18} extend these results to the regime where the radius $r
\to 0$ as $n \to \infty$.

These results are of fundamental importance; however, the behavior of the
spectra of these continuum operators can in general be hard to grasp. Therefore,
further work relating this spectra to the geometry of the underlying
distribution $\Pbb$ is of interest. In this spirit, \citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of spectral
algorithms to recover the latent labels in certain geometrically
well-conditioned nonparametric mixture models. Connecting the behavior of a spectral method (PPR) to the geometry of $\Pbb$ is also the motivation of our own paper, and these works are probably the most similar to our own. However, these results focus on global rather than local methods, and thus impose global rather than local conditions on $\Pbb$. Moreover, they do not explicitly consider 
recovery of density clusters, which is an important concern of our work.

% In the context of PPR clustering on a fixed graph $G$ and candidate cluster $C$, \textcolor{red}{(Allen-Zhu 13)} provide the sharpest known bounds on the size of the symmetric set difference $\Delta(\wh{C},C)$. We build on these results in the statistical context, where the graph $G_{n,r}$ is a random neighborhood graph, formed over samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\Pbb$, and the candidate cluster $\mc{C} \subset \Rd$.

%\begin{itemize}
	%\item In Proposition~\ref{prop:sample_to_population}, we show that with high probability the empirical quantities $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{\mathbb{P},r}(\mc{C}[X])$ are close to their population-level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$. As a consequence, in Theorem~\ref{thm:volume_ssd_ub} we show that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})$. These give the first population-level guarantees for PPR clustering in a non-parametric statistical context.
%\end{itemize}

%We specialize to the case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$ (an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}). 
%\begin{itemize}
%	\item In Propositions~\ref{prop:density_cluster_normalized_cut} and~\ref{prop:density_cluster_conductance}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$; these upper bounds depend on $\lambda$ as well as some other natural parameters. These immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Corollary~\ref{cor:density_cluster_volume_ssd_ub}),  giving new connections between (local) spectral and density clustering.
%	\item We introduce a notion of \emph{density cluster consistency}. In Theorem~\ref{thm:density_cluster_consistent_recovery}, we give conditions under which $\wh{C}$ is a consistent estimate of the density cluster $\mc{C}_{\lambda}$.
%	\item In Theorem~\ref{thm:ppr_density_cluster_lb} we give a lower bound: we exhibit a hard class of densities $\mc{F}$ and corresponding density clusters $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ will be provably large.
% \end{itemize}

\section{Upper bound on the symmetric set difference metric}
\label{sec:ub_symmetric_set_difference}

In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$. We build to this Theorem slowly, giving new structural results in two distinct directions. First, we build on some previous work (mentioned in the Introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$. Second, we argue that when $n$ is large, $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ can be suitably bounded by their population-level analogues $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.

\subsection{PPR cluster recovery: the fixed graph case.}

When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$. Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Technically speaking, Lemma~3.4 of~\cite{zhu2013} differs from Lemma~\ref{lem:zhu} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in our appendix. Nevertheless, to be clear the essential idea of Lemma~\ref{lem:zhu} is no different than that of~\cite{zhu2013}, and we do not claim any novelty.}

In their most general form, the results of~\citet{zhu2013} depend on the mixing time of a lazy random walk over the induced subgraph $G[C] = (C, E \cap (C \times C))$. Letting 
$W_C$ be the lazy random walk matrix over $G[C]$, we write  
\begin{equation*}
q_{v}^{(t)}(u) = e_vW_C^t e_u
\end{equation*}
for the probability that after $t$-steps, the lazy random walk originating at $v$ arrives at $u$. Assuming $G[C]$ is a connected graph, the random walk with transition probabilities given by $W_C$ is an irreducible and aperiodic Markov Chain; thus a unique stationary distribution exists and is given by \smash{$\pi_C(u) := \deg(u;G[C])/\vol(C;
	G[C])$}, where we write $\deg(u;G[C]) = \sum_{w \in C} \1\{(u,w) \in E_C\}$ for
the degree of $u$ in $G[C]$. The \emph{mixing time} over $G[C]$ is then
\begin{equation}
\label{eqn:mixing_time}
\tau_{\infty}(C;G) := \min\set{ t: \frac{\pi_C(u) - q_{v}^{(t)}(u)}
	{\pi_C(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in C$}}
\end{equation}
\begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
	\label{lem:zhu}
	For a set $C \subseteq V$, suppose that
	\begin{equation}
	\label{eqn:zhu_condition}
	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(C;G)}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}
	\end{equation}
	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
	\begin{equation}
	\label{eqn:zhu_ub}
	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
	\end{equation}
\end{lemma}
The upper bound in~\eqref{eqn:zhu_ub} does not obviously depend on the conductance $\Psi(C;G)$. However, as \cite{zhu2013} point out, letting $\pi_{\min}(C;G) := \min_{u \in C}\{\pi_C(u)\}$ denote the minimum stationary probability over $C$, it follows from Cheeger's inequality~\citep{chung1997} that 
\begin{equation}
\label{eqn:mixing_time_cheeger}
\tau_{\infty}(C;G) \leq \frac{\log(1/\pi_{\min}(C;G))}{\Psi(C;G)^2}.
\end{equation}
Therefore, setting (for instance) $\alpha = \frac{\Psi(C;G)^2}{2\log(1/\pi_{\min}(C;G))}$ and $\wh{C} = S_{\beta_0,v}$ for $\beta_0 = \frac{1}{5 \vol(C;G)}$, we obtain from~\eqref{eqn:zhu_ub} that 
\begin{equation}
\label{eqn:zhu_ub2}
\frac{\vol(C \vartriangle \wh{C};G)}{\vol(C; G)} \leq 60\frac{\Phi(C;G) \log\bigl( 1/\pi_{\min}(G[C])\bigr)}{\Psi(C;G)^2}.
\end{equation}

\paragraph{Improved bounds on mixing time.} Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$. Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Phi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$. Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}(\mc{C}[X];G_{n,r}) \lesssim 1/n$. Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a rate of at least $\log n$, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.\footnote{To be clear: $\pi_{\min}(G)$ is obviously at most $1/n$ for any graph $G$ with $n$ total vertices, not merely $G = G_{n,r}$. However, while in general it is certainly possible that $\Phi(C;G) \leq \frac{1}{\log(n)} \Psi(C;G)$, this will not be the case in our specific setting, where $G = G_{n,r}$ and $C = \mc{C}[X]$. Hence the need for a sharper bound.}

To fix this, we will improve the bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}. While in the worst case (over the input graph $G$) the ``start penalty'' $\log(1/\pi_{\min}(C;G))$ is unavoidable, fortunately better bounds are possible when $G$ is a geometric graph such as $G_{n,r}$. Intuitively, this is because in geometric graphs, small sets are expanders---that is, if a set $R \subseteq V$ has sufficiently small volume, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(V; G)$. As a consequence, a random walk over $G$ should rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' as if the random walk were given a warm start over a larger set $S$. To delineate small sets $R$ from larger sets $S$, we introduce the \emph{local spread} functional $s(C; G)$, defined as\footnote{The prefactor $9/10$ in the definition of $s(G)$ is arbitrary. It can be altered to any constant less than $1$, and Proposition~\ref{prop:pointwise_mixing_time} will still hold after appropriate changes to the constants.}
\begin{equation*}
s(C; G) := \frac{9}{10} \cdot \min_{u \in C} \set{\deg(u; G[C])} \cdot \min_{u \in C} \set{\pi_C(u)}.
\end{equation*}
Using a careful analysis we can make the intuition of the prior paragraph rigorous, leading to an improved upper bound on mixing time in Proposition~\ref{prop:pointwise_mixing_time}. The proof of this proposition, as with all results in this paper, is deferred to the appendix.
\begin{proposition}
	\label{prop:pointwise_mixing_time}
	Assume $\min_{u \in V} \deg(u; G) \geq 10$. Then,
	\begin{equation}
	\label{eqn:pointwise_mixing_time}
	\tau_{\infty}(C; G) \leq \frac{2}{\Psi^2(C; G)} \ln \left(\frac{320}{s(C; G)}\right)\log_2 \left(\frac{14}{s(C; G)}\right)  + 3 \log_2 \left(\frac{14}{s(C; G)}\right) + 3
	\end{equation}
\end{proposition}

We emphasize that while Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the minimum degree is at least 10), it is particularly useful when $G$ is a geometric graph. We give a precise upper bound on $s(\mc{C}[X]; G_{n,r})$ in Proposition~\ref{prop:sample_to_population}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:mixing_time}.

\subsection{Sample-to-population results}
In Proposition~\ref{prop:sample_to_population}, we establish high probability bounds on the sample normalized cut, conductance, and local spread, in terms of their population-level analogues. We have already introduced the population normalized cut~\eqref{eqn:population_normalized_cut} and conductance~\eqref{eqn:population_conductance}; writing $s_{n,r}(\mc{C}[X]) := s(\mc{C}[X];G_{n,r})$ for the sample local spread, we now define the population local spread to be
\begin{equation}
\label{eqn:local_spread}
s_{\Pbb,r}(\mc{C}) := \frac{9}{10} \cdot \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
\end{equation}
where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $\wt{G}_{n,r} = G_{n,r}[\mc{C}[X]]$.

\begin{proposition}
	\label{prop:sample_to_population}
	Fix $\delta \in (0,1)$. There exist universal constants $C_1$-$C_3$, and constants $b_1$,$b_2$ and $B_2$ that do not depend on $n$ or $\delta$, such that each of the following statements hold.
	\begin{itemize}
		\item With probability at least $1 - 3\exp\{-b_1\delta^2n\}$,
		\begin{equation}
		\label{eqn:sample_to_population_normalized_cut}
		\Phi_{n,r}(\mc{C}[X]) \leq (1 - C_1\delta) \Phi_{\Pbb,r}(\mc{C}[X]).
		\end{equation}
		\item With probability at least $1 - B_2n\exp\{-b_2\delta^2n\}$,
		\begin{equation}
		\label{eqn:sample_to_population_conductance}
		\Psi_{n,r}(\mc{C}[X]) \geq (1 - C_2\delta) \Psi_{\Pbb,r}(\mc{C}[X]),
		\end{equation}
		and 
		\begin{equation}
		\label{eqn:sample_to_population_local_spread}
		s_{n,r}(\mc{C}[X]) \geq (1 - C_3\delta) s_{\Pbb,r}(\mc{C}).
		\end{equation}
	\end{itemize}
\end{proposition}
A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Hoeffding's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X],\mc{C}^c[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic). To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $\min_{u \in C} \{\deg(u;\wt{G}_{n,r})\}$, but otherwise the proof is similarly straightforward. On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated. We mention here only that our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$. For further details, we refer to Appendix~\textcolor{red}{(?)}, where we prove~\eqref{eqn:sample_to_population_conductance}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance.

\paragraph{Well-initialized algorithm.} As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified
parameters. In particular, for a candidate cluster $\mc{C}$ and $\delta \in (0,1)$, we require that some of the tuning parameters of Algorithm~\ref{alg:ppr} be chosen to fall within specific ranges,

\begin{equation}
\label{eqn:initialization}
\begin{aligned}
& \alpha \in \Bigl[(1 - 2C_2\delta)^2, (1 - C_2\delta)^2\Bigr) \cdot
 \frac{\alpha_{\Pbb,r}(\mc{C})}{2} \\
& (L,U) \subseteq \Bigl(\frac{1}{5(1 + 2\delta)},\frac{1}{5(1 + \delta)}\Bigr) \cdot 
\frac{1}{n(n - 1)\vol_{\Pbb,r}(\mc{C})}.
\end{aligned}  
\end{equation}
where
\begin{equation}\
\label{eqn:alpha_initialization}
\alpha_{\Pbb,r}(\mc{C}) := \biggl\{ \frac{2}{\Psi_{\Pbb,r}^2(\mc{C})} \ln \left(\frac{320}{(1 - C_3\delta)s_{\Pbb,r}(\mc{C})}\right)\log_2 \left(\frac{14}{(1 - C_3\delta)s_{\Pbb,r}(\mc{C})}\right)  + 3 \log_2 \left(\frac{14}{(1 - C_3\delta) s_{\Pbb,r}(\mc{C})}\right) + 3\biggr\}^{-1}.
\end{equation}

\textcolor{red}{This still seems rather ugly; not sure if there's a way to make it look nicer.}

\begin{definition}
	If the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
\end{definition}

In practice of course, it is not feasible to set tuning parameters based on the 
underlying (unknown) distribution $\Pbb$. Typically, one runs PPR over some range of
tuning parameter values and selects the cluster which has the smallest
normalized cut.

\paragraph{Cluster recovery in symmetric set difference.} By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time} and~\ref{prop:sample_to_population}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$. To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$ as
\begin{equation}
\label{eqn:condition_number}
\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{120 (1 + C_1\delta)}{(1 - 2C_2\delta)^2(1 + 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C})}
\end{equation}

\begin{theorem}
	\label{thm:volume_ssd_ub} 
	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$. With probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
	\begin{equation}
	\label{eqn:volume_ssd_ub}
	\begin{aligned}
	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq \kappa_{\Pbb,r}(\mc{C},\delta)
	\end{aligned}
	\end{equation}
\end{theorem}
Roughly, the takeaway of Theorem~\ref{thm:volume_ssd_ub} is as follows: if PPR is well-initialized within a candidate cluster $\mc{C}$ for which $\Phi_{\Pbb,r}(\mc{C})$ is significantly smaller than $\Psi_{\Pbb,r}(\mc{C})^2/\log\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ will be a small fraction of the overall volume of $\mc{C}[X]$. We now make some other remarks:
\begin{itemize}
	\item It is useful to compare Theorem~\ref{thm:volume_ssd_ub} with what is already known regarding \emph{global} spectral clustering in the context of non-parametric statistics. \citep{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^{k}$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters $\wh{C}_1,\ldots,\wh{C}_k$  using $k$-means clustering. They derive error bounds on the misclassification error that depend on a difficulty function $\varphi(\Pbb)$. In our context, where the goal is to successfully distinguish $\mc{C}$ and $\mc{C}^c$ and thus $k = 2$, this difficulty function is roughly
	\begin{equation}
	\label{eqn:schiebinger}
	\varphi(\Pbb) \approx \sqrt{\Phi_{\Pbb,r}(\mc{C})} \cdot \max\biggl\{ \frac{1}{\Psi_{\Pbb,r}(\mc{C})^2}; \frac{1}{\Psi_{\Pbb,r}(\mc{C}^c)^2}\biggr\}.
	\end{equation}
	We point out two ways in which~\eqref{eqn:volume_ssd_ub} is a tighter bound than~\eqref{eqn:schiebinger}. First,~\eqref{eqn:schiebinger} depends on $\Psi_{\Pbb,r}(\mc{C}^c)$ in addition to $\Psi_{\Pbb,r}(\mc{C})$, and is thus a useful bound only if $\mc{C}^c$ and $\mc{C}$ are both internally well-connected. In contrast~\eqref{eqn:volume_ssd_ub} depends only on $\Psi_{\Pbb,r}(\mc{C})$, and is thus a useful bound if $\mc{C}$ has small conductance, regardless of the conductance of $\mc{C}^c$. This is intuitive: PPR is a local rather than global algorithm, and as such the analysis requires only local rather than global conditions. Second,~\eqref{eqn:schiebinger} depends on $\sqrt{\Phi_{\Pbb,r}(\mc{C})}$ rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citep{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup. Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}. Notwithstanding these particular differences, at a high level the conclusions of~\citep{schiebinger2015} are similar to those suggested by our Theorem~\ref{thm:volume_ssd_ub}, and our Theorem~\ref{thm:volume_ssd_ub} thus gives qualitatively similar bounds on local spectral clustering as have already been derived with respect to a global spectral algorithm in the non-parametric statistical context.

	\textcolor{red}{I think this last sentence is a bit of a mess, but kept trying and failing to improve it.}
\end{itemize}

\subsection{Approximate PPR vector}

\textcolor{red}{This subsection seems tangential to our main points, both in this section and in the paper as a whole. How do you feel about making it a remark, instead of a whole subsection?}

In practice, exactly solving the system of equations~\eqref{eqn: ppr_vector} to compute the PPR vector may be too computationally expensive. To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p^{(\varepsilon)}$}. We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound: 
\begin{equation}
\label{eqn: appr_error}
\textrm{for all $u \in V$}, \quad p(u) - \varepsilon D_{uu}\leq
p^{(\varepsilon)}(u) \leq p(u).  
\end{equation}
For a sufficiently small choice of $\varepsilon$, the 
application of \eqref{eqn: appr_error} within the proof of Theorem
\ref{thm:volume_ssd_ub} leads to an analogous result which holds for \smash{$p^{(\varepsilon)}$}.

\begin{corollary}
	\label{cor: appr}
	Consider instead of
	Algorithm \ref{alg:ppr} using the approximate PPR vector from
	\citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
	corresponding cluster estimate \smash{$\wh{C}$} in the same manner.  Then 
	provided we take 
	\begin{equation}
	\label{eqn: appr_parameter}
	\varepsilon = \frac{1}{25 n(n - 1)\vol_{\Pbb,r}(\mc{C})} ,
	\end{equation}
	under the assumptions of Theorem~\ref{thm:volume_ssd_ub} the upper bound on symmetric set difference in \eqref{eqn:volume_ssd_ub} still
	holds.
\end{corollary}

\section{Recovery of a density cluster with PPR}
\label{sec:ppr_density_cluster}

We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$. In addition, we introduce a separate notion of consistency that is particularly relevant to the density clustering problem, and establish conditions under which local clustering with PPR is consistent in this sense. Finally, we derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster. Viewed as a whole, the results of this section can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if $\mc{C}_{\lambda}$ is \emph{well-conditioned}, both geometrically---meaning it is not too long and thin--- and vertically---meaning $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near it's boundary.

\textcolor{red}{It would be more symmetric to replace the word ``geometrically'' by ``horizontally''; thoughts?}

\subsection{Background and setup}

We start with some background on density clustering. Let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$. In the density clustering problem, initiated by~\cite{hartigan1981}, the goal is to recover $\mathbb{C}_{f}(\lambda)$. By now, density clustering (and the related problem of level-set estimation) are relatively well-understood. \citet{polonik1995,
	rigollet2009} study density clustering under the symmetric set difference
metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
estimators under Hausdorff loss and
\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$. We emphasize at the outset that our goal is
not to improve on these results, nor to offer a better algorithm for level set
estimation---indeed, seen as a density clustering algorithm, PPR has none 
of the optimality guarantees found in the aforementioned works---but rather to better understand the implications of our general theory by applying it within an already well-studied framework. We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.

Each of the aforementioned results assume the density $f$ satisfies some regularity conditions. A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus cannot be resolved by any finite number of samples. This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} \textcolor{red}{(...)}. We choose to follow the \textcolor{red}{(simple and elegant)} approach of~\cite{chaudhuri2010}, who conduct their analysis with respect to a thickened version of $\mc{C}_{\lambda}$ defined as $C_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) \leq \sigma\}$ for some $\sigma > 0$. (Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.)

\textcolor{red}{This subsection feels too casual to me. In particular the second paragraph probably needs to be made more precise and detailed. But for now I'll leave it, and you can tell me if agree it needs work, or think it's basically fine as is.}

\subsection{Recovery of well-conditioned density clusters}
\label{subsec:recovery_well-conditioned_density_clusters}

Our goal is therefore to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$. We have already derived upper bounds on the volume of the symmetric set difference which that on some population-level functionals of the candidate cluster. What remains is to analyze these functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$. To carry out this analysis, we will need to impose some conditions, and for the rest of this subsection we will assume the following.

\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:bounded_density}
	\emph{Bounded density within cluster:} There exist constants
	$0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
	$$
	\lambda_{\sigma} \leq \inf_{x \in \mc{C}_{\lambda,\sigma}} f(x) \leq \sup_{x \in \mc{C}_{\lambda,\sigma}} f(x)
	\leq \Lambda_{\sigma}.
	$$

	\item 
	\label{asmp:low_noise_density}
	\emph{Low noise density:} There exist $\theta \in (0,\infty)$ and $\gamma \in
	[0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \mc{C}_{\lambda,\sigma}) \leq \sigma$,     
	$$
	\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}.  
	$$
	Roughly, this assumption ensures that the density decays sufficiently quickly
	as we move away from the target cluster $\mc{C}_{\lambda,\sigma}$, and is a standard assumption
	in the level-set estimation literature (see for instance \citet{singh2009}).

	\item
	\label{asmp:embedding}
	\emph{Lipschitz embedding:}
	There exists $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $L \in [1,\infty)$ such that
	\begin{enumerate}
		\item we have $\mc{C}_{\lambda,\sigma} = g(\mathcal{K})$, for a convex set $\mathcal{K}
		\subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
			\mathcal{K}}\|x - y\| \leq \rho < \infty$;
		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{C}_{\lambda,\sigma}$, where $\nabla g(x)$ is
		the Jacobian of $g$ evaluated at $x;$ and 
		\item for some $L \geq 1$,   
		$$
		\|g(x) - g(y)\| \leq L \|x - y\| ~
		\text{for all $x,y \in \mathcal{K}$}. 
		$$
	\end{enumerate}
	Succinctly, we assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set with finite
	diameter under a measure preserving, Lipschitz transformation. 
\end{enumerate}

\emph{For convenience only}, we will also make the following assumption, 
\begin{enumerate}[label=(A\arabic*)]
	\setcounter{enumi}{3}
	\item
	\label{asmp:bounded_volume}
	\emph{Bounded volume:}
	The volume of $\mc{C}_{\lambda,\sigma}$ is no more than half the total volume of $\Rd$:
	$$
	\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}^c). 
	$$
	Roughly, this assumption ensures that with high probability $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]) \leq (1 + \delta) \cdot \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^c)$, and thus $\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X]) \leq (1 + \delta) \cdot \cut_{n,r}(\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$. 
\end{enumerate}

\paragraph{Normalized cut, conductance, and local spread of a density cluster.} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$. These bounds depend on the various geometric conditions just introduced. 
\begin{lemma}
	\label{lem:density_cluster_local_spread}
	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $L$. Then,
	\begin{equation}
	\label{eqn:density_cluster_local_spread}
	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{2} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{r}{2L\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr)
	\end{equation}
\end{lemma}

\begin{proposition}
	\label{prop:density_cluster_normalized_cut}
	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density},~\ref{asmp:low_noise_density} and~\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta$, and $\gamma$, and additionally that $0 < r \leq \frac{\sigma}{4d}$. Then,
	\begin{equation}
	\label{eqn:density_cluster_normalized_cut}
	\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \frac{16}{9} \cdot \frac{dr}{\sigma} \cdot \frac{\lambda\Bigl(\lambda_{\sigma} - \theta \frac{r^{\gamma}}{\gamma + 1}\Bigr)}{\lambda_{\sigma}^2}
	\end{equation}
\end{proposition}

\begin{proposition}
	\label{prop:density_cluster_conductance}
	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$. Then,
	\begin{equation}
	\label{eqn:density_cluster_conductance}
	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
	\end{equation}
\end{proposition}
Some remarks are in order:
\begin{itemize}
	\item We prove Proposition~\ref{prop:density_cluster_normalized_cut} by separately upper bounding $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma}, \mc{C}_{\lambda,\sigma}^c)$ and lower bounding the volume $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$. Of these two bounds, the trickier to prove is the upper bound on the cut, which involves carefully estimating the probability mass of thin tubes around the boundary of $\mc{C}_{\lambda,\sigma}$. 
	\item Proposition~\ref{prop:density_cluster_conductance} is proved in a completely different way. The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g. \cite{lovasz1990} or \cite{dyer1991}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $L$
	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
	\item There is some interdependence between $L$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
	non-essential. However, it is not possible to eliminate condition \ref{asmp:embedding} without incurring an additional factor of at least
	$(\rho/\sigma)^d$ in \eqref{eqn:density_cluster_conductance}, achieved, for
	instance, when $\mc{C}_{\lambda,\sigma}$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$. In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $L$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
\end{itemize}

\noindent Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$.

\begin{corollary}
	\label{cor:density_cluster_volume_ssd_ub}
	Assume $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$, and that $0 < r \leq \sigma/4d$. For any $\delta \in (0,1)$, with probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exist constants $C_{1,\delta}$ and $C_{2,\delta}$, and a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
	\begin{equation}
	\label{eqn:density_cluster_volume_ssd_ub}
	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}r}\biggr)
	\end{equation}
\end{corollary}
Inequality~\eqref{eqn:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster. For instance, if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is both geometrically well-conditioned---i.e. $L^2\rho^2/(\sigma r) \approx 1$---and vertically well-conditioned---i.e. $\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $(\lambda - \theta r^{\gamma}/(\gamma + 1)) \ll \lambda$---then PPR will approximately recover it.  Some other remarks:
\begin{itemize}
	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Corollary~\ref{cor:density_cluster_volume_ssd_ub} through the conductance. This reflects
	(what may be regarded as) established wisdom regarding spectral partitioning
	algorithms more generally \citep{guattery1995, hein2010}, but newly applied
	to the density clustering setting: if the diameter $\rho$ is large, then PPR
	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$. This will be supported by simulations in Section \ref{sec:experiments}.   
	\item Several modifications of global spectral clustering have been proposed with the intent of making such procedures essentially independent of the geometry of the density cluster $\mc{C}_{\lambda}$. For instance,~\citep{pelletier2011,arias-castro2009} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance. The resulting procedures come with stronger density cluster recovery guarantees. However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, with spectral clustering functioning as more of a post-processing step. These methods are thus very different in spirit to PPR, which is a canonical local spectral clustering algorithm. 
	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population-level normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms. It seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} apply to the output of global spectral clustering methods as well, albeit with suitable alterations as per our discussion after Theorem~\ref{thm:volume_ssd_ub}, but formalizing this is outside the scope of our work.
\end{itemize}

\subsection{Consistency}
\label{subsec:consistent_recovery_density_clusters}

\textcolor{red}{For the moment, I have kept the ordering of this subsection and the following subsection, which gives our negative example. But I think it might make sense to switch them?}\\

The symmetric set difference does not measure whether \smash{$\wh{C}$}
can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in 
	\mathbb{C}_f(\lambda)$}. We therefore also study a second notion of cluster 
estimation, first introduced by \citet{hartigan1981}, and defined
asymptotically.

\begin{definition}
	\label{def:density_cluster_consistency}
	For an estimator \smash{$\wh{C} \subseteq X$} and cluster \smash{$\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$}, we call \smash{$\wh{C}$} \emph{consistent} for
	\smash{$\mc{C}_{\lambda}$} if for all \smash{$\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$} with  
	\smash{$\mc{C} \not= \mc{C}'$}, the following holds with probability tending to 1 as $n \to \infty$: 
	\begin{equation}
	\label{eqn:density_cluster_consistency}
	\mc{C}[X] \subseteq \wh{C} \quad \text{and} \quad
	\wh{C} \cap \mc{C}'[X] = \emptyset.
	\end{equation}
\end{definition}

Consistent cluster recovery roughly ensures that, for a given 
threshold $\lambda>0$, the estimated cluster \smash{$\wh{C}$} contains all points
in a true density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$, and simultaneously does 
not contain any points in any other density cluster $\mc{C}_{\lambda}' \in
\mathbb{C}_f(\lambda)$.

The bound on symmetric set difference \eqref{eqn:density_cluster_volume_ssd_ub} does not imply consistent density cluster estimation in the sense of \eqref{eqn:density_cluster_consistency}. This notion of consistency requires a
uniform bound over the PPR vector $p_v$: as an example, suppose that we were
able to show that for all \smash{$\mc{C}' \in \mathbb{C}_f(\lambda), \mc{C}' \neq \mc{C}$}, and each $u \in \mc{C}, w \in \mc{C}'$,  
\begin{equation}
\label{eqn:ppr_gap}
\frac{p_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} <
\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \leq \frac{p_v(u)}{D_{uu}}. 
\end{equation}
Then, any $(L,U)$ satisfying~\eqref{eqn:initialization} and any sweep cut
$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
\eqref{eqn:density_cluster_consistency}. In Theorem 
\ref{thm:density_cluster_consistent_recovery}, we show that a sufficiently 
small upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ ensures that with high probability the uniform bound~\eqref{eqn:ppr_gap} is satisfied, and hence implies
\smash{$\wh{C}$} will be a consistent estimator.
\begin{theorem}
	\label{thm:density_cluster_consistent_recovery}
	For any $\delta \in (0,1)$, the following statement holds with probability at least $1 - 3\exp\{-b_1\delta^2n\} - B_2n\exp\{-b_2\delta^2n\}$: there exists a constant $c_1$ and a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,  \smash{$\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$}, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
	\begin{equation}
	\label{eqn:density_cluster_consistent_recovery_condition}
	\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta) \leq c_1 \cdot \min_{x: f(x) \geq \lambda} \Bigl\{\deg_{\Pbb,r}(x)\Bigr\},
	\end{equation}
then the PPR estimated cluster \smash{$\wh{C}$} satisfies \eqref{eqn:density_cluster_consistency}.
\end{theorem}
\textcolor{red}{(In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.)}\vspace{1 mm}

On the other hand, unfortunately the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition} is rather restrictive. Specifically, from the following chain of inequalities,
\begin{equation*}
\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
\end{equation*}
we see that in order for~\eqref{eqn:density_cluster_consistent_recovery_condition} to be met, it is necessary that \smash{$\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$} be at most $c_1 \cdot \Lambda_{\sigma} \nu_d r^d$. In plain terms, we 
are able to recover a density cluster $\mc{C}_{\lambda}$ in the strong sense of
\eqref{eqn:density_cluster_consistency} only when we can guarantee the volume of the symmetric set difference will be very small. This strong condition is
the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}.\vspace{1 mm}

\textcolor{red}{Originally, we had only (something like) the preceding paragraph, which in my opinion is very negative and invites the reader to discount the preceding result. I added the paragraph in red above it, to make it clear that the Corollary is interesting even if the required conditions are strong.}

\subsection{Negative result}
\label{subsec:lower_bound}
We conclude this section by exhibiting a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
cluster. Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in
$\Reals^2$,    
$$
\mc{C}^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times 
\biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
\mc{C}^{(1)} = \mc{C}^{(0)} - \set{(\sigma,0)}, \quad
\mc{C}^{(2)} = \mc{C}^{(0)} + \set{(\sigma,0)},
$$
where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over
\smash{$\mathcal{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
$$
\Pbb = \frac{1 - \epsilon}{2} \Pbb_1 + \frac{1 - \epsilon}{2} \Pbb_2 +
\frac{\epsilon}{2} \Pbb_0, 
$$
where $\Pbb_k$ is the uniform distribution over $\mc{C}^{(k)}$ for $k = 0,1,2$.  
The density function $f$ of $\Pbb$ is simply
\begin{equation}
\label{eqn:lb_density}
f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in
\mc{C}^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \mc{C}^{(2)}) +
\epsilon\1(x \in \mc{C}^{(0)})  \right), 
\end{equation}
so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have 
\smash{$\mathbb{C}_f(\lambda) = \set{\mc{C}^{(1)}, \mc{C}^{(2)}}$}. Figure~\ref{fig:hard_case} visualizes the density $f$ for two different choices of $\epsilon,
\sigma, \rho$.

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.495\textwidth]{../lower_bound_1}
	\includegraphics[width=0.495\textwidth]{../lower_bound_2}
	\caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
		$\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
		$\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
		$\sigma = 0.2$.} 
	\label{fig:hard_case}
\end{figure}

\paragraph{Lower bound on symmetric set difference.}

As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is 
sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}. Let
\begin{equation}
\label{eqn:lower_set}
\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
\end{equation}

\begin{theorem}
	\label{thm:ppr_lb}
	Assume the radius $r < \min\set{\frac{1}{40}\rho, \frac{1}{4}\sigma}$, and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 65  
	\Phi_{\Pbb,r}(\mathcal{L})$, and $(L,U) = (0,1)$.  Then, for any 
	\begin{equation*}
	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2},
		\frac{8}{\epsilon}}, 
	\end{equation*}
	the following statement holds with probability at least $1 - B_3 n \exp\set{-b_3 n}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap 
		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/10$}, such
	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
	\smash{$\wh{C}$} satisfies    
	\begin{equation}
	\label{eqn:ppr_lb}
	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
	\mc{C}^{(1)}[X]) \geq \frac{1}{4} -  C_4 \cdot 
	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(\frac{\rho \sigma}
		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
	\end{equation}
	Consequently, if
	\begin{equation*}
	\epsilon^2 \geq \frac{C_4}{8} \cdot \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ 
		\log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}, 
	\end{equation*}
	then with high probability \smash{$\frac{\sigma
			\rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) 
		\geq 1/8$}.    
\end{theorem}

%Note that for large enough $n$, $\vol_{n,r}(\mc{C}^{(1)}[X])$  will be close to $n^2 r^2/(\sigma\rho)$, and therefore the quantity \smash{$\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$} in \eqref{eqn:ppr_lb} is comparable to \smash{$\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) / \vol_{n,r}(\mc{C}^{(1)}[X])$}, which corresponds to the quantity we upper bound in Corollary~\ref{thm:volume_ssd_ub}.

Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where
the density clusters are rectangular subsets of $\Reals^2$.  We chose this
setting to make the theorem simple to state, and our results are generalizable
to $\Reals^d$ and to non-rectangular clusters.  Moreover, although we state
our lower bound with respect to PPR run on a neighborhood graph, the conclusion is
likely to hold for a much broader class of spectral clustering algorithms. In
the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when
$\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of
$\mc{C}^{(1)}$ will be much larger than that of $\mathcal{L}$. In this case, not
merely PPR but any algorithm that approximates the minimum normalized cut is
unlikely to recover $\mc{C}^{(1)}$. In particular, local spectral clustering
algorithms based on truncated random walks \citep{spielman2013}, global spectral
clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings
\citep{hein2010} all have provable upper bounds on the normalized cut of cluster
they output, and thus we expect that they would all fail to estimate
$\mc{C}^{(1)}$.

\paragraph{Comparison between upper and lower bounds.}

To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
results of our upper bound in Corollary~\ref{cor:density_cluster_volume_ssd_ub} to the density $f$ given in \eqref{eqn:lb_density}. Observe that $\mc{C}^{(1)}$ satisfies each of the Assumptions~\ref{asmp:bounded_density}--\ref{asmp:bounded_volume}:

\begin{enumerate}[label=(A\arabic*)]
	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
	\mc{C}^{(1)}$.  
	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such
	that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
	$$
	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  = \left\{\frac{1 - \epsilon}{2} -
	\epsilon \right\} \frac{1}{\rho \sigma},
	$$
	which meets the decay requirement with exponent $\gamma=0$.
	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\rho$.
	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) =
		\vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore
	\smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$}.   
\end{enumerate}

\begin{remark}
	Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
	$\sigma$-expansions due to their sharp corners. To fix this, one can   
	%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume}
	%in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with
	%respect to rectangles of width $\sigma$, or  
	simply modify these sets to have appropriately rounded corners, and our lower
	bound arguments do not need to change significantly, subject to some
	additional bookkeeping.  Thus we ignore this technicality in our subsequent
	discussion. 
\end{remark}

If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Corollary~\ref{cor:density_cluster_volume_ssd_ub}. This implies that 
there exists a set $\mc{C}^{(1)}[X] \subseteq \mc{C}^{(1)}$ with
\smash{$\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X])$} such
that for any seed node $v \in \mc{C}^{(1)}[X]$, and for large enough $n$, the
PPR estimated cluster $\wh{C}$ satisfies with high probability
\begin{equation*}
\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 64 C_{1,\delta} \cdot \frac{\rho^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{r}\biggr)
\end{equation*}
To facilitate comparisons between our upper
and lower bounds, assume $\sigma/4 \leq \rho/40$ and set $r = \sigma/8$.  Then
the following statements each hold with high probability. 
\begin{itemize}
	\item If the user-specified parameters satisfy~\eqref{eqn:initialization}, and
	\begin{equation*}
	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{64C_{1,\delta}} \left(\frac{\sigma}{\rho \log(\rho/\sigma \sqrt{C_{2,\delta}})}\right)^2,
	\end{equation*}
	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \leq a \cdot
		\vol_{n,r}(\mc{C}^{(1)}[X])$}.

	\item If the user-specified parameters are as in Theorem~\ref{thm:ppr_lb}, and
	\begin{equation*}
	\epsilon \geq \sqrt{\frac{C_4}{8}} \left({\frac{\sigma}{\rho}} \log^2 \left(\frac{\rho}
	{\epsilon^2 \sigma}\right)\right)^{1/4},
	\end{equation*}
	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{8}
		\vol_{n,r}(\mc{C}^{(1)}[X])$}. 
\end{itemize}

Jointly, these upper and lower bounds give a relatively precise characterization
of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.

\begin{remark}
	It is worth pointing out that the above conclusions are reliant on specific
	(albeit reasonable) ranges and choices of input parameters, which in some
	instances differ between the upper and lower bounds. We suspect that our lower
	bound continues to hold even when choosing input parameters as dictated by our
	upper bound, but do not pursue the details.
\end{remark}

Finally, it is not hard to show that in the example under consideration, classical
plug-in density cluster estimators can consistently recover the
$\sigma$-expansion $\mc{C}_{\lambda,\sigma}$ of a density cluster $\mc{C}_{\lambda}$, even if $\epsilon$ is
large compared to $\sigma/\rho$. That PPR has trouble recovering density
clusters here (where standard plug-in approaches do not) is not meant to
be a knock on PPR. Rather, it simply reflects that while classical density
clustering approaches are specifically designed to identify high-density regions
regardless of their geometry, PPR relies on geometry as well as density when
forming the output cluster.

\section{Experiments}
\label{sec:experiments}

We provide numerical experiments to investigate the tightness of our theoretical results, and examine the performance of PPR on the ``two moons'' dataset. We defer details of the experimental settings to the appendix.

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.32\textwidth]{../sample2}
	\includegraphics[width=0.32\textwidth]{../sample1}
	\includegraphics[width=0.32\textwidth]{../sigma_normalized_cut_plot}
	\includegraphics[width=0.32\textwidth]{../sigma_mixing_time_plot}
	\includegraphics[width=0.32\textwidth]{../diameter_normalized_cut_plot}
	\includegraphics[width=0.32\textwidth]{../diameter_mixing_time_plot}
	\caption{\it\small Top left and top middle: samples from a geometrically
		well- and poor-conditioned cluster. The points in $\mc{C}_{\lambda}$ are colored in red, points in $\mc{C}_{\lambda,\sigma} \!\setminus\! \mc{C}_{\lambda}$ are colored in yellow, and the remaining points in blue. Other panels: empirical normalized cut and mixing time, as a function of $\sigma$ or $\rho$, versus their theoretical upper bounds.} 
	\label{fig:bounds}
\end{figure}

\paragraph{Validating theoretical bounds.}  We investigate the tightness of
Propositions~\ref{prop:density_cluster_normalized_cut} and Proposition~\ref{prop:density_cluster_conductance}, as well as the resulting Corollary~\ref{cor:density_cluster_volume_ssd_ub}, via simulation. Figure \ref{fig:bounds} compares our bounds on normalized cut and conductance with the actual empirically-computed quantities \eqref{eqn:normalized_cut} and \eqref{eqn:conductance}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\mc{C}$. The top left and top middle panels display the resulting empirical clusters for two different values of $\rho,\sigma$.

The bottom left and bottom right panels assure that our lower bounds on conductance track closely with the empirical conductance, in both 2 and 3 
dimensions.\footnote{We rescaled all values of theoretical bounds by a constant, to mask the effect of large universal constants in these bounds. Therefore only the comparison of slopes, rather than intercepts, is meaningful.} \textcolor{red}{(TODO): Need to change the ``mixing time'' panels to ``conductance'' panels.} This provides empirical evidence that Proposition~\ref{prop:density_cluster_conductance} has the right dependency on both expansion parameter $\sigma$ and diameter $\rho$. The story for the normalized cut panels
is less obvious. We remark that while, broadly speaking, the trends do not
appear to match, this gap between theory and empirical results seems largest
when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
grows, the slopes of empirical and theoretical curves become more similar.

\textcolor{red}{(TODO): Include a second figure comparing the volume of the symmetric set difference with our upper bound on the volume of the symmetric set difference. Point out that this comparison also validates Theorem~\ref{thm:volume_ssd_ub}, since Corollary~\ref{cor:density_cluster_volume_ssd_ub} is a corollary of this theorem.}

\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:moons}, to drive home 
the implications of Section~\ref{sec:ppr_density_cluster}, we show the behavior of PPR,
normalized cut, and the density clustering algorithm of \citet{chaudhuri2010} on
the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
a prototypical success story for spectral clustering algorithms. The first
column shows the empirical density clusters $\mc{C}[X]$ and $\mc{C}'[X]$ for
a particular threshold $\lambda$ of the density function; the second column
shows the cluster recovered by PPR; the third column shows the global minimum
normalized cut, computed according to the algorithm of \citet{szlam2010}; and
the last column shows a cut of the density cluster tree estimator of
\citet{chaudhuri2010}.  We can see the degrading ability of PPR to recover
density clusters as the two moons become less well-separated. Of particular
interest is the fact that PPR fails to recover one of the moons even when
normalized cut still succeeds in doing so. Additionally, we note that the
Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
fail.  This supports our main message, which is that PPR recovers only
geometrically well-conditioned density clusters.

\begin{figure}
	\centering
	\includegraphics[width=0.24\textwidth,scale = .5]{../row1_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_density_cluster}
	\caption{\it\small True density (column 1), PPR (column 2), normalized
		cut (column 3) and estimated density (column 4) clusters for 3 different 
		simulated data sets. Seed node for PPR denoted by a black cross.} 
	\label{fig:moons}
\end{figure}

\section{Discussion}
\label{sec:discussion}
In this work, we have analyzed the behavior of PPR in the classical setup of non-parametric statistics. We have shown how PPR depends on the geometry of the distribution $\Pbb$ through the population level normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.  In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if it is geometrically and vertically well-conditioned. We now conclude by summarizing several interesting directions for future work.

Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to  
\infty$, would be computationally attractive, as it would ensure that the graph 
$G_{n,r}$ is sparse. However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in
this regime. Although the restriction to a kernel function fixed in $n$ is
common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017},
recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.

In another direction, it would be very useful to find reasonable conditions under which the ratio $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ would tend to $0$ as $n \to \infty$. It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR (similar to~\eqref{eqn:ppr_gap}). Although most work thus far on spectral clustering methods has focused on deriving bounds on the $\Leb^1$- or $\Leb^2$-error, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator. It is not clear whether the techniques used in these works can be applied to PPR.

Finally, after reading our Section~\ref{sec:ppr_density_cluster}, the practitioner may be tempted to ask why they should estimate a density cluster using PPR, when other methods are available with superior statistical guarantees. A rather prosaic, if undoubtedly correct, answer is that the ``ideal'' cluster is entirely in the eye of the beholder. For instance, it is quite common to define an ideal cluster as one with a small normalized cut, in which case the cluster output by PPR may be quite preferable to standard density clustering procedures. A more intriguing answer is that a (local) spectral method such as PPR may be more stable in the presence of noise than traditional density clustering procedures.\footnote{In the context of semi-supervised learning, a similar argument was alluded to by Misha Belkin and Partha Niyogi~\citep{belkin2002}, who say:
\begin{quote}
One possible simple approach is to use ``geodesic nearest neighbors''. However, while simple and well-motivated, this method is potentially unstable.	
\end{quote}
} Such a question could be answered by comparing the sample complexity of spectral clustering methods with density clustering procedures, but to our knowledge, the sample complexity of spectral methods remains unknown.

\section*{Acknowledgements}

SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.

\clearpage

\bibliography{../../local_spectral_bibliography}

\end{document}

### 2020-12-28 jmlr/revision/proofs.tex
Outline of new appendices in proofs.tex. Fixed graph results partially filld in.

\documentclass{article}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{xr}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{fullpage}

\externaldocument{local_spectral_clustering_jmlr_revision_2}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}

% Make a widecheck symbol (thanks, Stack Exchange!)
\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
	<5> <6> <7> <8> <9> <10>
	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
	mathx10
}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathAccent{\widecheck}{0}{mathx}{"71}
% widecheck made

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\iid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
\newcommand{\lambdavec}{\boldsymbol{\lambda}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
\newcommand{\Lap}{L}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}
\newcommand{\Id}{I}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Vset}{\mathcal{V}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\SM}{\mathrm{SM}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}

%%% Theorem environments
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Proofs for ``Geometry of Local Spectral Clustering''}
\author{Alden Green}
\date{\today}
\maketitle

The proofs of our major theorems all consist of at most three modular parts.
\begin{enumerate}
	\item~\textbf{Fixed graph results.} Analysis which holds with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
	\item~\textbf{Finite-sample bounds.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
	\item~\textbf{Population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}. This proves~\textcolor{red}{(?)}
\end{enumerate}
The first three sections of this appendix will correspond to each of these three parts. In Section~\ref{sec:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, \textcolor{red}{(...)}. Finally, in Section~\ref{sec:appr_misclassification_error} we derive upper bounds for the aPPR vector, and in Section~\ref{sec:experimental_details} we give relevant details regarding our experiments.

\section{Fixed graph results}
In this section, we give all results that hold with respect to an arbitrary graph $G$. For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.

\paragraph{Notation.}
The graph $G = (V,E)$ is an undirected and connected but otherwise arbitrary graph, defined over vertices $V = \{1,\ldots,n\}$ with $m = |E|$ total edges. The adjacency matrix of $G$ is $A$, the degree matrix is $D$, and the lazy random walk matrix over $G$ is $W = (I + D^{-1}A)/2$. If the lazy random walk originates at a node $v$, the distribution of the lazy random walk $q_v^{(t)} := q(v,t;G)$ after $t$ steps is $q_v^{(t)} := e_v W^t$, with stationary distribution $\pi := \lim_{t \to \infty} q_v^{(t)}$ with entries $\pi(u) = \deg(u;G)/\vol(u;G)$.

The PPR vector $p_v = p(v,\alpha;G)$ is defined as the solution to~\textcolor{red}{(?)}

Given a distribution $q$ (by distribution we mean a vector with non-negative entries; for instance, $q = q_v^{(t)}$ for $t \in \mathbb{N}$, $q = p_v$, or $q = \pi$) and $\beta \in (0,1)$, the $\beta$-sweep cut of $q$ is
\begin{equation*}
S_{\beta}(q) = \set{u: \frac{q(u)}{\deg(u;G)} > \beta};
\end{equation*} 
in the special case where $q = p_v$ we write $S_{\beta,v}$ for $S_{\beta}(p_v)$. The argument of $S_{\beta}(\cdot)$ will usually be clear from context, in which case we will drop it and simply write $S_{\beta}$. For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that the sweep cut $S_{\beta_j}$ contains at least $j$ vertices. For notational ease, we will write $S_j := S_{\beta_j}$, and $S_0 = \emptyset$. We adopt the

We now introduce a function $h_q(\cdot): [0,2m] \to [0,1]$ to measure the extent to which a distribution $q$ is mixed. To do so, we first define a piecewise linear function $q[\cdot]: [0,2m] \to [0,1]$. Letting $q(S) := \sum_{u \in S} q(u)$, we take $q[\vol(S_j)] = q(S_j)$ for each sweep cut $S_j$, and then extend $q[\cdot]$ by piecewise linear interpolation to be defined everywhere on its domain. Then the mixedness of $q$ is measured by
\begin{equation*}
h_q(k) := q[k] - \frac{k}{2m}.
\end{equation*}
Note that $h_{\pi} = 0$. By construction both $q[\cdot]$ and $h_q(\cdot)$ are concave functions, which will be an important fact later on.

% For a connected subset of the vertices $C \subseteq V$, the subgraph induced by $C$ is $G[C] = (C, E \cap (C \times C))$. The lazy random walk matrix over $C$ is $W_C = (I_C + D^{-1}_C A_C)/2$ (where for a matrix $M \in \Reals^{n \times n}$ we write $M_C$ for the submatrix of $M$ induced by $C$), the vector  
%\begin{equation}
%\label{eqn:lazy_random_walk}
%q_{v}^{(t)}(u) = e_vW_C^t e_u
%\end{equation}
%denotes the probability that after $t$-steps the lazy random walk originating at $v$ arrives at $u$. The stationary distribution of this random walk is $\pi_C$.

The conductance of the vertex set $V$ is abbreviated as $\Psi(G) := \Psi(V;G)$, and likewise for the local spread $s(G) := s(V;G)$. Finally, for convenience we introduce the following functionals:
\begin{equation*}
\begin{aligned}
& d_{\max}(C; G) := \max_{u \in C} \deg(u; G), && d_{\min}(C; G) := \min_{u \in C} \deg(u;G) \\
& d_{\max}(G) := d_{\max}(V;G),~~ && d_{\min}(G) := d_{\min}(V; G)
\end{aligned}
\end{equation*}

In the following subsections we establish: (1) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}); (2) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (3) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); (4) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example); and (5) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR). 
\subsection{Proof of Lemma~\ref{lem:zhu}}
\label{subsec:pf_lem_zhu}
\textcolor{red}{(TODO)}

\subsection{Mixedness of lazy random walk and PPR vectors}
In this subsection, we give upper bounds on $h^{(t)} := h_{q_v^{(t)}}$ and $h^{(\alpha)} := h_{p_v}$. Although similar bounds exist in the literature (see in particular Theorem~1.1 of \citep{lovasz1990} and Theorem~3 of~\citep{andersen2006}), we could not find precisely the results we needed, and so for completeness we state and prove these results ourselves.

\begin{theorem}
	\label{thm:mixing_time_rw}
	For any $k \in [d_{\max}(G), 2m - d_{\max}(G)]$ and $t \geq 3$,
	\begin{equation}
	\label{eqn:mixing_time_rw_1}
	h^{(t)}(k) \leq \frac{1}{8} + \frac{d_{\max}(G)}{2d_{\min}(G)^2} + \frac{\sqrt{m}}{d_{\min}(G)^2} \sqrt{\wb{k}} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t - 3}.
	\end{equation}
	For any $k \in [0, d_{\max}(G)) \cup (2m - d_{\max}(G),2m]$,
	\begin{equation}
	\label{eqn:mixing_time_rw_2}
	h^{(t)}(k) \leq \frac{1}{8} + \frac{d_{\max}(G)}{2d_{\min}(G)^2}.
	\end{equation}
\end{theorem}

\begin{theorem}
	\label{thm:mixing_time_PPR}
	Let $\phi$ be any constant in $[0,1]$. Either the following bound holds for any $t \in \mathbb{N}$ and any $k \in [d_{\max}(G),2m - d_{\max}(G)]$:
	\begin{equation*}
	h^{(\alpha)}(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t},
	\end{equation*}
	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) \leq \phi$.
\end{theorem}

The proofs of these upper bounds will be similar to each other (in places word-for-word alike), and will follow a similar approach and use similar notation to that of \citep{lovasz1990,andersen2006}. For a given $0 \leq K_0 \leq m$ and a function $h: [0,2m] \to [0,1]$, let 
\begin{equation*}
L_{K_0}(k;h) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
\end{equation*}
be the linear interpolant of $h(K_0)$ and $h(2m - K_0)$, and additionally let
\begin{equation*}
C(K_0;h) := \max\set{\frac{h(k) - L_{K_0}(k;h)}{\sqrt{\overline{k}}}: K_0 \leq k \leq  2m - K_0}.
\end{equation*}
where we use the notation $\overline{k} := \min\{k, 2m - k\}$, and set $0/0$ equal to $0$. Our first pair of Lemmas upper bound $h^{(t)}$ and $h^{(\alpha)}$ as a function of $L_{K_0}$ and $C(K_0)$. Lemma~\ref{lem:mixing_random_walk} implies that if $t$ is large relative to $\Psi(G)$, then $h^{(t)}(\cdot)$ must be small.

\begin{lemma}[\textbf{c.f. Theorem 1.2 of~\citep{lovasz1990}}]
	\label{lem:mixing_random_walk}
	For any $K_0 \in [0,m]$, $k \in [K_0, 2m - K_0]$, $t_0 \in \mathbb{N}$ and $t \geq t_0$,
	\begin{equation}
	\label{eqn:mixing_random_walk}
	h^{(t)}(k) \leq L_{K_0}(k;h^{(t_0)}) + C(K_0; h^{(t_0)}) \sqrt{\wb{k}} \cdot \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t - t_0}
	\end{equation}
\end{lemma}

Lemma~\ref{lem:mixing_time_PPR} implies that if the PPR random walk is not well mixed, then some sweep cut of $p_v$ must have small normalized cut.

\begin{lemma}[\textbf{c.f Theorem~3 of \citep{andersen2006}}]
	\label{lem:mixing_time_PPR}
	Let $\phi \in [0,1]$. Either the following bound holds for any $t \in \mathbb{N}$, any $K_0 \in [0,m]$, and any $k \in [K_0,2m - K_0]$:
	\begin{equation}
	\label{eqn:mixing_time_PPR}
	h^{(\alpha)}(k) \leq \alpha t + L_{K_0}(k; h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
	\end{equation}
	or else there exists some sweep cut $S_{j}$ of $p_v$ such that $\Phi(S_j;G) \leq \phi$.
\end{lemma}

In order to make use of these Lemmas, we require upper bounds on $L_{K_0}(\cdot,h)$ and $C(K_0;h)$, for each of $h = h^{(3)}$ and $h = h^{(\alpha)}$. Of course, trivially $L_{K_0}(k;h) \leq \max\{h(K_0); h(2m - K_0)\}$ for any $k \in [K_0, 2m - K_0]$. As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$. 
\begin{lemma}
	\label{lem:interpolator_bound_rw}
	For any $K_0 \in [0,2m]$, it holds that
	\begin{equation*}
	h^{(3)}\bigl(2m - K_0\bigr) \leq \frac{K_0}{2m}~~\textrm{and}~~h^{(3)}\bigl(K_0\bigr) \leq \frac{K_0}{2d_{\min}(G)^2} + \frac{1}{8}.
	\end{equation*}
	As a result, for any $k \in [K_0, 2m - K_0]$,
	\begin{equation*}
	L_{K_0}(k;h^{(3)}) \leq \frac{1}{8} + \frac{K_0}{2d_{\min}(G)^2}.
	\end{equation*}
\end{lemma}

\begin{lemma}
	\label{lem:interpolator_bound_ppr}
	For any $K_0 \in [0,2m]$, it holds that 
	\begin{equation*}
	h^{(\alpha)}(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h^{(\alpha)}(K_0) \leq \frac{K_0}{2d_{\min}(G)^2} + \frac{2\alpha}{1 + \alpha}.
	\end{equation*}
	As a result, for any $k \in [K_0,2m - K_0]$,
	\begin{equation*}
	L_{K_0}(k; h^{(\alpha)}) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}(G)^2}.
	\end{equation*}
\end{lemma}

We next establish an upper bound on $C_{K_0}(k;h)$, which rests on the following key observation: since $h(k)$ is concave and $L_{K_0}(K_0;h) = h(K_0)$, it holds that
\begin{equation*}
\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq
\begin{cases}
h'(K_0) \sqrt{k},~& k \leq m \\
-h'(2m - K_0) \sqrt{2m - k},~& k > m.
\end{cases}
\end{equation*}
(Since $h$ is not differentiable at $k = k_j$, here $h'$ refers to the right derivative of $h$.)

Lemma~\ref{lem:linearization_bound} gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, which hold for both $h = h^{(3)}$ and $h = h^{(\alpha)}$, and result in an upper bound on $C(K_0;h)$. Both the statement and proof of this Lemma are made easier by the \emph{Lovasz-Simonovits curve}, which is an explicit representation of the function $h_q(\cdot)$ that holds for any distribution $q$. Ordering the vertices $\frac{q(u_{(1)})}{\deg(u_{(1)};G)} \geq \frac{q(u_{(2)})}{\deg(u_{(2)};G)} \geq \cdots \geq \frac{q(u_{(n)})}{\deg(u_{(n)};G)}$, the function $h_q(k)$ satisfies
\begin{equation}
\label{eqn:lovasz_simonovits}
h_q(k) = \sum_{i = 0}^{j} \left(q(u_{(i)}) - \pi(u_{(i)})\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(q(u_{(j+1)}) - \pi(u_{(j+1)})\right) 
\end{equation}
for all $k \in [\vol(S_j),\vol(S_{j + 1}))$ and $j = 0,\ldots,n-1$.
\begin{lemma}
	\label{lem:linearization_bound}
	The following statements hold for both $h = h^{(\alpha)}$ and $h = h^{(3)}$.

	If $u_{(1)} = v$, then 
	\begin{equation}
	\label{eqn:right_derivative_1}
	h'\bigl(\deg(v;G)\bigr) \leq \frac{1}{2\deg_{\min}(G)^2};
	\end{equation}
	otherwise $u_{(1)} \neq v$ and
	\begin{equation}
	\label{eqn:right_derivative_2}
	h'(0) \leq \frac{1}{2\deg_{\min}(G)^2};
	\end{equation}
	for all $K \in [0,m]$,
	\begin{equation}
	\label{eqn:right_derivative_3}
	h'(2m - K) \geq -\frac{d_{\max}}{d_{\min}\cdot \vol(G)}.
	\end{equation}
	As a result, letting $K_0 = \deg(v;G)$ if $u_{(1)} = v$, and otherwise letting $K_0 = 0$, we have
	\begin{equation*}
	C(K_0,h) \leq \frac{\sqrt{m}}{d_{\min}(G)^2}.
	\end{equation*}
\end{lemma}
\paragraph{Proof of Theorems~\ref{thm:mixing_time_rw} and~\ref{thm:mixing_time_PPR}.}
\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_rw})]
	\textcolor{red}{(TODO)}
\end{proof}

The proof of Theorem~\ref{thm:mixing_time_PPR} follows immediately from Lemmas~\ref{lem:mixing_time_PPR},~\ref{lem:interpolator_bound_ppr} and~\ref{lem:linearization_bound}, taking $K_0 = 0$ if $u_{(1)} \neq v$ and otherwise $K_0 = \deg(v;G)$.

\paragraph{Proofs of Lemmas.}
In our proof of Lemma~\ref{lem:mixing_random_walk}, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$. 
\begin{proof}[Proof (of Lemma~\ref{lem:mixing_random_walk})]
	 We will prove Lemma~\ref{lem:mixing_random_walk} by induction on $t$. In the base case $t = t_0$, observe that $C(K_0;h^{(t_0)}) \cdot \sqrt{\wb{k}} \geq h^{(t_0)}(k) - L_{K_0}(k;h^{(t_0)})$ for all $k \in [K_0, 2m - K_0]$, which implies 
	\begin{equation*}
	L_{K_0}(k;h^{(t_0)}) + C(K_0; h^{(t_0)}) \cdot \sqrt{\wb{k}} \geq h^{(t_0)}(k).
	\end{equation*}

	Now, we proceed with the inductive step, assuming that the inequality holds for $t_0,t_0 + 1,\ldots,t - 1$, and proving that it thus also holds for $t$. By the definition of $L_{K_0}$, the inequality~\eqref{eqn:mixing_random_walk} holds when $k = K_0$ or $k = 2m - K_0$. We will additionally show that~\eqref{eqn:mixing_random_walk} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$. This suffices to show that the inequality~\eqref{eqn:mixing_random_walk} holds for all $k \in [K_0,2m - K_0]$, since the right hand side of~\eqref{eqn:mixing_random_walk} is a concave function of $k$.

	Now, we claim that for each $k_j$, it holds that
	\begin{equation}
	\label{pf:mixing_random_walk_inductive_step}
	q_v^{(t)}[k_j] \leq \frac{1}{2}\Bigl(q_v^{(t - 1)}[k_j - \wb{k}_j \Psi(G)] + q_v^{(t - 1)}[k_j + \wb{k}_j \Psi(G)]\Bigr).
	\end{equation}
	To establish this claim, we note that for any $u \in V$
	\begin{equation*}
	q_v^{(t)}(u) = \frac{1}{2}q_v^{(t - 1)}(u) + \frac{1}{2}\sum_{w \in V}q_v^{(t - 1)}(w,u) = \frac{1}{2} \sum_{w \in V} \bigl(q_v^{(t - 1)}(u,w) + q_v^{(t - 1)}(w,u)\bigr),
	\end{equation*}
	and consequentially for any $S \subset V$,
	\begin{align*}
	q_v^{(t)}(S) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}(\mathrm{in}(S)) +  q_v^{(t - 1)}(\mathrm{out}(S))\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cup \mathrm{out}(S)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S) \cap \mathrm{out}(S)\bigr)\bigr\}
	\end{align*}
	where $\mathrm{in}(S) = \{(u,w) \in E: u \in S\}$ and $\mathrm{out}(S) = \{(w,u) \in E: w \in S\}$. We deduce that
	\begin{align*}
	q_v^{(t)}[k_j] = q_v^{(t)}(S_j) & = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cup \mathrm{out}(S_j)\bigr) +  q_v^{(t - 1)}\bigl(\mathrm{in}(S_j) \cap \mathrm{out}(S_j)\bigr)\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cup \mathrm{out}(S_j)|\bigr] +  q_v^{(t - 1)}\bigl[|\mathrm{in}(S_j) \cap \mathrm{out}(S_j)|\bigr]\bigr\} \\
	& = \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \mathrm{cut}(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \mathrm{cut}(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Phi(S_j;G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Phi(S_j;G)\bigr]\bigr\} \\
	& \leq \frac{1}{2}\bigl\{q_v^{(t - 1)}\bigl[k_j + \wb{k}_j\Psi(G)\bigr] +  q_v^{(t - 1)}\bigl[k_j - \wb{k}_j\Psi(G)\bigr]\bigr\},
	\end{align*}
	establishing~\eqref{pf:mixing_random_walk_inductive_step}. The final two inequalities both follow from the concavity of $q_v^{(t)}[\cdot]$.

	Subtracting $k_j/2m$ from both sides, we get
	\begin{equation}
	\label{pf:mixing_random_walk_inductive_step_h}
	h^{(t)}(k_j) \leq \frac{1}{2}\bigl\{h^{(t - 1)}\bigl(k_j + \wb{k}_j\Psi(G)\bigr)+  h^{(t - 1)}\bigl(k_j - \wb{k}_j\Psi(G)\bigr)\bigr\}.
	\end{equation}
	At this point, we divide our analysis into cases.

	\textbf{Case 1.}
	Assume $k_j - \Psi(G) \overline{k}_j$ and $k_j + 2 \Psi(G) \overline{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h} and obtain the following:
	\begin{align*}
	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \overline{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \overline{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\overline{k_j - \Psi(G) \overline{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \overline{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\overline{k_j - \Psi(G) \overline{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \overline{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\overline{k}_j - \Psi(G) \overline{k}_j} + \sqrt{\overline{k}_j + \Psi(G) \overline{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
	\end{align*}
	A Taylor expansion of $\sqrt{1 + \Psi(G)}$ around $\Psi(G) = 0$ yields the following bound:
	\begin{equation*}
	\sqrt{1 + \Psi(G)} + \sqrt{1 - \Psi(G)} \leq 2 - \frac{\Psi(G)^2}{4},
	\end{equation*}
	and therefore
	\begin{align*}
	h^{(t)}(k_j) & \leq L_{K_0}(k;h^{(t_0)}) + \frac{C(K_0;h^{(t_0)})}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\Psi(G)^2}{4}\right)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-1} \\
	&= L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)})\sqrt{\overline{k}_j}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}.
	\end{align*}

	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \overline{k}_j$ or $k_j + 2 \Psi(G) \overline{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. We deduce the following:
	\begin{align*}
	h^{(t)}(k_j) & \overset{(\textrm{i})}{\leq} \frac{1}{2}\Bigl(h^{(t - 1)}(K_0) + h^{(t - 1)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
	\end{align*}
	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$. 	
\end{proof}

\begin{proof}[Proof (of Theorem~\ref{lem:mixing_time_PPR}).]
	We will show that if $\Phi(S_j; g) > \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.

	We proceed by induction on $t$. Our base case will be $t = 0$. Observe that $C(K_0;h^{(\alpha)}) \cdot \sqrt{\overline{k}} \geq h^{(\alpha)}(k) - L_{K_0}(k;h^{(\alpha)})$ for all $k \in [K_0,2m - K_0]$, which implies
	\begin{equation*}
	L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)}) \cdot \sqrt{\overline{k}} \geq h^{(\alpha)}(k).
	\end{equation*}

	Now, we proceed with the inductive step. By the definition of $L_{K_0}$, the inequality~\eqref{eqn:mixing_time_PPR} holds when $k = K_0$ or $k = 2m - K_0$. We will additionally show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$. This suffices to show that the inequality~\eqref{eqn:mixing_time_PPR} holds for all $k \in [K_0,2m - K_0]$, since the right hand side of~\eqref{eqn:mixing_time_PPR} is a concave function of $k$.

	By Lemma 5 of \citet{andersen2006}, we have that
	\begin{align}
	p_v[k_j] & \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \mathrm{cut}(S_j;G)] + p_v[k_j + \mathrm{cut}(S_j;G)] \bigr) \nonumber\\
	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \Phi(S_j;G) \overline{k}_j] + p_v[k_j + \Phi(S_j;G) \overline{k}_j]  \bigr) \nonumber \\
	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \phi \overline{k}_j] + p_v[k_j + \phi \overline{k}_j]\bigr) \nonumber
	\end{align}
	and subtracting $k_j/2m$ from both sides, we get
	\begin{equation}
	\label{eqn:mixing_time_PPR_pf1}
	h^{(\alpha)}(k_j) \leq \alpha + \frac{1}{2} \bigl(h^{(\alpha)}(k_j - \phi \overline{k}_j) + h^{(\alpha)}(k_j +  \phi \overline{k}_j) \bigr)
	\end{equation}
	From this point, we divide our analysis into cases.

	\textbf{Case 1.}
	Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
	\end{align*}
	and therefore
	\begin{equation*}
	h^{(\alpha)}(k_j) \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
	\end{equation*}

	\textbf{Case 2.} Otherwise one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. By the concavity of $h$, and applying the inductive hypothesis to $h^{(\alpha)}2k_j - K_0)$, we have
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h^{(\alpha)}(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0;p^{\alpha}) + L_{K_0}(2k_j - K_0\bigr) + C(K_0;h^{(\alpha)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
	\end{align*}
\end{proof}

\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_rw})]
	\textcolor{red}{(TODO)}
\end{proof}

\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_ppr})]
	\textcolor{red}{(TODO): Revise the notation in this proof.}

	We make use of the representation~\eqref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
	\begin{align*}
	h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
	& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
	& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
	\end{align*}

	We will upper bound $h(K_0)$ by $p[\vol(S_j)] \leq p_v(v) + \sum_{u \in S_j \setminus \set{v}}p_v(u)$. In the proof of Lemma~\ref{lem:linearization_bound} we have already given an upper bound on $p_v(u)$ when $u \neq v$. Now, we additionally observe that for all $t$,
	\begin{equation*}
	e_vW^t(v) \leq \frac{1}{2d_{\min}} + \left(\frac{1}{2}\right)^t
	\end{equation*}
	and therefore $p_v(v) \leq \frac{1}{2d_{\min}} + \frac{2\alpha}{1 + \alpha}$.
	As a result,
	\begin{equation}
	h(K_0) \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
	\end{equation}
	where the latter inequality follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.
\end{proof}

\begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
	The result of the Lemma is obvious once we show \eqref{eqn:right_derivative_1}-\eqref{eqn:right_derivative_2}. From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
	\begin{equation}
	\label{eqn:linearization_bound_pf1}
	h'(k) \leq \frac{p(v_{(j + 1)})}{\deg(v_{(j + 1)};G)}
	\end{equation}

	We now upper bound $p(u)$ uniformly over all $u$ except the seed node $v$. For any $u \in V$ besides the seed node $v$, we can show by induction that
	\begin{equation*}
	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
	\end{equation*} 
	for any $t \geq 0$, and therefore
	\begin{equation}
	\label{eqn:linearization_bound_pf2}
	p(\alpha,\chi_v)(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \leq  \frac{1}{2d_{\min}}.
	\end{equation}
	As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = \deg(v;G)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}. The inequality \eqref{eqn:right_derivative} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since
	\begin{equation*}
	h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}},
	\end{equation*}
	and the proof of the Lemma is therefore complete.
\end{proof}

\clearpage

\subsection{Proof of Proposition~\ref{prop:pointwise_mixing_time}}
\label{subsec:pf_prop_pointwise_mixing_time}
To prove Proposition~\ref{prop:pointwise_mixing_time}, we will establish an upper bound on a total variation distance between $q_v^{(t)}$ and $\pi$, then upgrade to the desired uniform upper bound. The \emph{total variation distance} between distributions $q$ and $p$ is
\begin{equation*}
d_{\mathrm{TV}}(q,p) := \sum_{u \in v} \bigl|q(u) - p(u)\bigr|
\end{equation*}
It is a matter of some basic algebra~\textcolor{red}{(Either show it yourself or point to a reference)} to show that
\begin{equation*}
d_{\mathrm{TV}}(q,\pi) \leq \sup_{k \in [0,2m]} h_q(k).
\end{equation*}

\subsection{Spectral partitioning properties of PPR}
\label{subsec:ppr_spectral_partitioning}
The following theorem is the main theorem of this section. It relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of $C$.

\begin{theorem}
	\label{thm:conductance_ppr}
	Let $C \subseteq V$ satisfy the following conditions:
	\begin{itemize}
		\item $\vol(C;G) \leq \frac{2}{3}\vol(G)$,
		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
		\item $\frac{20\Phi(C;G)}{1 + 10\Phi(C;G)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
	\end{itemize}
	Suppose $60\Phi(C;G) \leq \alpha \leq 70\Phi(C;G)$, and let $(L,U) = (0,1)$. Then, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$ such that for any $v \in C^g$ the following statement holds: For the PPR vector $p_v := p(v,\alpha;G)$, the minimum normalized cut of the sweep sets satisfies 
	\begin{equation*}
	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C;G)}
	\end{equation*}
\end{theorem}

\begin{remark}
	Although this theorem appears quite similar to standard results in the PPR literature -- for instance, Theorem 6 of \citet{andersen2006} -- crucially the above bound depends on $\log\left(\frac{m}{d_{\min}^2}\right)$ rather than $\log m$. In the case where $d_{\min} \asymp n$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$. 
\end{remark}
Notwithstanding the aforementioned improvements, the proof of Theorem~\ref{thm:conductance_ppr} follows the same general outline as the proof of Theorem~6 of \citet{andersen2006}. We now walk through this outline step by step, modifying the results of \citet{andersen2006} as needed. As with their work, we begin by proving a mixing time bound on the PPR vector $p_v$.

\subsubsection{Mixing time of PPR.}

To quantify the mixing of a PPR vector $p_v$, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$. For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that $S_{\beta_j}$ contains at least $j$ vertices. (For notational ease, we will write $S_{i} := S_{\beta_i}$, so that $S_1,S_2,\ldots,S_n$ comprise the $n$ unique sweep cuts of $p_v$.)
For each $j = 1,\ldots,n$, we let $p[\vol(S_j)] =  \sum_{u \in S} p_v(u)$. Additionally, we let $p[0] = 0$ and $p[2m] = 1$. Finally, we extend $p[\cdot]$  by piecewise interpolation to be defined everywhere on its domain. The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$, defined as 
\begin{equation*}
h(k) = p[k] - \frac{k}{2m}.
\end{equation*}
Next, for a given $0 \leq K_0 \leq m$, let 
\begin{equation*}
L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
\end{equation*}
be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$, and additionally let
\begin{equation*}
C(K_0;h^{(\alpha)}) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
\end{equation*}
where we use the notation $\overline{k} := \min\{k, 2m - k\}$.

As a sanity check, we confirm that Theorem~\ref{lem:mixing_time_PPR} is no weaker than Theorem~3 of \citet{andersen2006}. It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0;h^{(\alpha)}) \leq 1$ for any $K_0$. Setting $K_0 = 0$ in Theorem~\ref{lem:mixing_time_PPR}, we therefore recover Theorem~3 of \citet{andersen2006}.

We now proceed to identify when Theorem~\ref{lem:mixing_time_PPR} may offer some improvement on Theorem~3 of \citet{andersen2006}, by showing when we can upper bound $C(K_0) \ll 1$.

Combining Theorem~\ref{lem:mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound_ppr}, we have the following result.

We arrive now at the main result of this section. It is similar to Theorem 2 of \citet{andersen2006} but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR} in place of~\textcolor{red}{(?)}. To simplify notation, we will write the total mass placed by $p_v$ on a subset $S \subset V$ as $p_v(S) := \sum_{u \in S} p_v(u)$.
\begin{theorem}
	\label{lem:mixing_time_PPR_contrapositive}
	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$. Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}}{2d_{\min}^2}$, and a set $S \subseteq V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$,  such that
	\begin{equation}
	\label{eqn:mixing_time_PPR_contrapositive_1}
	p_v(S) - \frac{\vol(S;G)}{\vol(G)} > \delta.
	\end{equation}
	Then there exists a sweep cut $S_j$ of $p$, such that
	\begin{equation*}
	\Phi(S_j; G) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
	\end{equation*}
	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
\end{theorem}
\begin{proof}
	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}. Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.

	Now, letting
	\begin{equation*}
	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
	\end{equation*}
	we have that
	\begin{equation*}
	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
	\end{equation*}
	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
\end{proof}

\subsubsection{Improved Local Partitioning with PPR.}

As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\wh{C};G)$. First, we restate a theorem of \citet{andersen2006} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.

\begin{theorem}
	\label{thm:acl_3}
	For any set $C$ and any constant $\alpha$, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$, such that for any vertex $v \in C^g$, the PPR vector $p(v,\alpha;G)$ satisfies
	\begin{equation*}
	p(v,\alpha;G) \geq 1 - 6\frac{\Phi(C;G)}{\alpha}.
	\end{equation*}
\end{theorem}
We are now in a position to prove Theorem~\ref{thm:conductance_ppr} by combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3}.

\begin{proof}[Proof (of Theorem~\ref{thm:conductance_ppr})]
	Since $\alpha \geq 60\Phi(C)$ and $v \in C^g$, by Theorem~\ref{thm:acl_3},
	\begin{equation*}
	p_v(C) \geq \frac{9}{10}.
	\end{equation*}
	This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p_v(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$. Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{lem:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$. Therefore, the minimum conductance sweep cut satisfies
	\begin{equation*}
	\min_{j = 1,\ldots,n} \Phi(S_j;G) \leq \sqrt{\frac{1120\cdot \Phi(C;G)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
	\end{equation*}
	Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
	\begin{equation*}
	\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
	\end{equation*}
	completing the proof of the theorem.
\end{proof}

\subsection{Uniform bounds on PPR}
\label{subsec:ppr_uniform_bounds}
\textcolor{red}{(TODO)}

\section{Finite sample results}
In this section, we prove high-probability finite-sample bounds on functionals of the random graph $G_{n,r}$. To do so, we will need several different \textcolor{red}{(concentration inequalities)}, and we begin by reviewing these.

\subsection{Concentration inequalities}
\textcolor{red}{(TODO)}

\section{Population functionals for density clusters}

\section{Proof of Major Theorems}
\label{sec:pf_major_theorems}

\section{aPPR and Misclassification Error}
\label{sec:appr_misclassification_error}

\section{Experimental Details}
\label{sec:experimental_details}

\clearpage
\bibliographystyle{plainnat}
\bibliography{../../local_spectral_bibliography}

\end{document}

### 2020-12-30 jmlr/revision/proofs.tex
Completed fixed graph proofs.

@@
 %%% Theorem environments
-\newtheorem{theorem}{Theorem}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{lemma}{Lemma}
-\newtheorem{example}{Example}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{conjecture}{Conjecture}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{example}{Example}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{assumption}{Assumption}[section]
+\newtheorem{remark}{Remark}[section]
 
@@
 \begin{enumerate}
-	\item~\textbf{Fixed graph results.} Analysis which holds with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e.
-normalized cut, conductance, and local spread) of $G$;
+	\item~\textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
 	\item~\textbf{Finite-sample bounds.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
@@
 The adjacency matrix of $G$ is $A$, the degree matrix is $D$, and the lazy random walk matrix over $G$ is $W = (I + D^{-1}A)/2$.
-If the lazy random walk originates at a node $v$, the distribution of the lazy random walk $q_v^{(t)} := q(v,t;G)$ after $t$ steps is $q_v^{(t)} := e_v W^t$, with stationary distribution $\pi := \lim_{t \to \infty} q_v^{(t)}$ with entries $\pi(u) = \deg(u;G)/\vol(u;G)$.
+If the lazy random walk originates at a node $v$, the distribution of the lazy random walk $q_v^{(t)} := q(v,t;G)$ after $t$ steps is $q_v^{(t)} := e_v W^t$, with stationary distribution $\pi := \pi(G) := \lim_{t \to \infty} q_v^{(t)}$ with entries $\pi(u) = \deg(u;G)/\vol(u;G)$.
 
-The PPR vector $p_v = p(v,\alpha;G)$ is defined as the solution to~\textcolor{red}{(?)}
+For a starting distribution $s$ (by distribution we mean a vector with non-negative entries), the PPR vector $p_s = p(s,\alpha;G)$ is the solution of
+\begin{equation}
+\label{eqn:ppr}
+p_s = \alpha s + (1 - \alpha) p_s W.
+\end{equation}
+When $s = e_v$, we write $p_v := p_{e_v}$.
+It is easy to check that $p_s = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t q_s^{(t)}$.
+Note that $s$ need not be a probability distribution (i.e.
+its entries need not sum to $1$) to make sense of~\eqref{eqn:ppr}.
 
-Given a distribution $q$ (by distribution we mean a vector with non-negative entries; for instance, $q = q_v^{(t)}$ for $t \in \mathbb{N}$, $q = p_v$, or $q = \pi$) and $\beta \in (0,1)$, the $\beta$-sweep cut of $q$ is
+Given a distribution $q$ (for instance, $q = q_v^{(t)}$ for $t \in \mathbb{N}$, $q = p_v$, or $q = \pi$) and $\beta \in (0,1)$, the $\beta$-sweep cut of $q$ is
 \begin{equation*}
@@
 For notational ease, we will write $S_j := S_{\beta_j}$, and $S_0 = \emptyset$.
-We adopt the
 
-We now introduce a function $h_q(\cdot): [0,2m] \to [0,1]$ to measure the extent to which a distribution $q$ is mixed.
+We now introduce the~\emph{Lovasz-Simonovits curve} $h_q(\cdot): [0,2m] \to [0,1]$ to measure the extent to which a distribution $q$ is mixed.
 To do so, we first define a piecewise linear function $q[\cdot]: [0,2m] \to [0,1]$.
@@
 \end{equation*}
-Note that $h_{\pi} = 0$. By construction both $q[\cdot]$ and $h_q(\cdot)$ are concave functions, which will be an important fact later on.
+The Lovasz-Simonovits curve is a non-negative function, with $h_q(0) = h_q(2m) = 0$.
+The stationary distribution $\pi$ is mixed, i.e.
+$h_{\pi}(k) = 0$ for all $k \in [0,2m]$.
+Finally, both $q[\cdot]$ and $h_q(\cdot)$ are concave functions, which will be an important fact later on.
 
-% For a connected subset of the vertices $C \subseteq V$, the subgraph induced by $C$ is $G[C] = (C, E \cap (C \times C))$.
-The lazy random walk matrix over $C$ is $W_C = (I_C + D^{-1}_C A_C)/2$ (where for a matrix $M \in \Reals^{n \times n}$ we write $M_C$ for the submatrix of $M$ induced by $C$), the vector
-%\begin{equation}
-%\label{eqn:lazy_random_walk}
-%q_{v}^{(t)}(u) = e_vW_C^t e_u
-%\end{equation}
-%denotes the probability that after $t$-steps the lazy random walk originating at $v$ arrives at $u$. The stationary distribution of this random walk is $\pi_C$.
-
-The conductance of the vertex set $V$ is abbreviated as $\Psi(G) := \Psi(V;G)$, and likewise for the local spread $s(G) := s(V;G)$. Finally, for convenience we introduce the following functionals:
+The conductance of $V$ is abbreviated as $\Psi(G) := \Psi(V;G)$, and likewise for the local spread $s(G) := s(V;G)$. Finally, for convenience we introduce the following functionals:
 \begin{equation*}
@@
 \end{equation*}
+We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq n \cdot d_{\max}(G)$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)
 
-In the following subsections we establish: (1) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}); (2) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (3) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); (4) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example); and (5) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR).
+\paragraph{Organization.} In the following subsections we establish: (\ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}); (\ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (\ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (\ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (\ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
+
 \subsection{Proof of Lemma~\ref{lem:zhu}}
 \label{subsec:pf_lem_zhu}
-\textcolor{red}{(TODO)}
+For a candidate cluster $C \subseteq V$, we use the tilde-notation $\wt{G} = G[C]$ to refer to the subgraph of $G$ induced by $C$.
+Similarly we write $\wt{q}_v^{(t)} := q(v,t;\wt{G})$ for the $t$-step distribution of the lazy random walk over $\wt{G}$, $\wt{\pi} = \pi(G[C])$ for the stationary distribution of $\wt{q}_v^{(t)}$ (we will always assume $G[C]$ is connected), and $\wt{p}_v := p(v,\alpha;\wt{G})$ for the PPR vector over $\wt{G}$.
+
+As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma.
+In fact, we directly use the following three inequalities, derived in that work:
+\begin{itemize}
+	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
+	\begin{equation}
+	\label{pf:zhu1}
+	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
+	\end{equation}
+	\item \textbf{(c.f.
+Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and
+	\begin{equation}
+	\label{pf:zhu2}
+	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
+	\end{equation}
+	\item \textbf{(c.f.
+Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
+	\begin{equation}
+	\label{pf:zhu3}
+	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
+	\end{equation}
+\end{itemize}
+We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
+\begin{equation*}
+C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
+\end{equation*}
+consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.
+
+First we upper bound $\vol(S_{\beta,v} \setminus C;G)$.
+Observe that for any $u \in S_{\beta,v} \setminus C$, $p_v(u) > \beta \cdot \deg(u;G)$.
+Summing up over all such vertices, from~\eqref{pf:zhu3} we conclude that
+\begin{equation}
+\label{pf:zhu3.5}
+\vol(S_{\beta,v} \setminus C; G) \leq \frac{p_v(C^c)}{\beta} \leq 2\frac{\Phi(C;G)}{\beta \cdot \alpha}.
+\end{equation}
+
+Next we upper bound $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$. From~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we see that 
+\begin{equation*}
+p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$.}
+\end{equation*}
+If additionally $u \not\in S_{\beta,v}$ then $p_v(u) \leq \beta \deg(u;G)$, and for all such $u \in C \setminus S_{\beta,v}$,
+\begin{equation}
+\label{pf:zhu4}
+\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  \beta\deg(u;G) \leq \wt{p}_{\ell}(u).
+\end{equation}
+On the other hand, for any $u \in C^{\mathrm{int}}$ it holds that
+\begin{equation*}
+\wt{\pi}(u) = \frac{\deg(u;\wt{G})}{\vol(\wt{G})} \geq \frac{\deg(u;\wt{G})}{\vol(G)} \geq \frac{(1 - \alpha \beta \vol(C;G))\deg(u;G)}{\vol(C;G)};
+\end{equation*}
+by plugging this in to~\eqref{pf:zhu4} we obtain
+\begin{equation*}
+\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u),~~\textrm{for all $u \in C^{\mathrm{int}} \setminus S_{\beta,v}$},
+\end{equation*}
+and summing over all such $u$ gives
+\begin{equation*}
+\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
+\end{equation*}
+The upper bounds in~\eqref{eqn:zhu_condition} imply
+\begin{equation*}
+\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
+\end{equation*}
+and we conclude that
+\begin{equation}
+\label{pf:zhu5}
+\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
+\end{equation}
+
+Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
+\begin{equation*}
+\frac{1}{\vol(C;G)}\sum_{w \not\in C} \1((u,w) \in E) \geq \alpha \cdot \beta \cdot \deg(u;G)
+\end{equation*}
+and summing over all such vertices yields
+\begin{equation}
+\label{pf:zhu6}
+\vol(C^{\mathrm{bdry}};G) \leq \frac{1}{\alpha \beta \vol(C;G)}\sum_{\substack{u \in C^{\mathrm{bdry}} \\ w \not\in C}} \1((u,w) \in E) \leq \frac{\Phi(C;G)}{\alpha \cdot \beta}.
+\end{equation} 
+The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
+
+\subsection{Uniform bounds on PPR}
+\label{subsec:ppr_uniform_bounds}
+As mentioned in our main text, in order to prove Theorem~\ref{thm:density_cluster_consistent_recovery}, we require a uniform bound on the PPR vector.
+Actually, we require two such bounds: for a candidate cluster $C \subseteq V$ and an alternative cluster $C' \subseteq V$, we require a lower bound on $p_v(u)$ for all $u \in C$, and an upper bound on $p_v(u')$ for all $u' \in C'$.
+In Lemma~\ref{lem:ppr_uniform_bound} we establish an upper bound that holds for all vertices $u$ in the interior $C_{o}$ of $C$, and a lower bound holds for all vertices $u'$ in the interior of $C_{o}'$ of $C'$; here
+\begin{equation*}
+C_{o} = \Bigl\{u \in C: \deg(u,\wt{G}) =  \deg(u;G)\Bigr\},~~\textrm{and}~~C_{o}'= \Bigl\{u \in C': \deg(u,G[C']) =  \deg(u;G)\Bigr\},
+\end{equation*}
+and we remind the reader that $\wt{G} = G[C]$. 
+\begin{lemma}
+	\label{lem:ppr_uniform_bound}
+	Let $C$ and $C'$ be disjoint subsets of $V$, and suppose that
+	\begin{equation*}
+	\alpha \leq \frac{1}{2\tau_{\infty}(\wt{G})}.
+	\end{equation*}
+	Then there exists a set $C^g \subseteq C$ with $\vol(C^g;G) \geq \vol(C;G)/2$ such that for any $v \in C^g$,
+	\begin{equation}
+	\label{eqn:ppr_uniform_bound_C}
+	p_v(u) \geq \frac{3}{8}\wt{\pi}(u) - \frac{2 \Phi(C;G)}{d_{\min}(\wt{G})\cdot \alpha}~~\textrm{for all $u \in C_{o}$}
+	\end{equation}
+	and
+	\begin{equation}
+	\label{eqn:ppr_uniform_bound_Cprime}
+	p_v(u') \leq \frac{2\Phi(C;G)}{d_{\min}(C';G) \cdot \alpha}~~\textrm{for all $u \in C_{o}'$.}
+	\end{equation}
+\end{lemma}
+
+\paragraph{``Leakage'' and ``soakage'' vectors.} To prove Lemma~\ref{lem:ppr_uniform_bound}, we will make use of the following explicit representation of the \emph{leakage} distribution $\ell$ from~\eqref{pf:zhu3}, as well as an analogously defined \emph{soakage} distribution $s$:
+\begin{equation}
+\label{eqn:leakage_soakage}
+\begin{aligned}
+\ell^{(t)} & := e_v(W \wt{I})^t(I - D^{-1}\wt{D}),~~&& \ell = \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell^{(t)} \\
+s^{(t)} & := e_v(W \wt{I})^t W (I - \wt{I}),~~&& s = \sum_{t = 0}^{\infty} (1 - \alpha)^t s^{(t)}.
+\end{aligned}
+\end{equation}
+In the above, $\wt{I} \in \Reals^{n \times n}$ is a diagonal matrix with $I_{uu} = 1$ if $u \in C$ and $0$ otherwise, and $\wt{D}$ is the diagonal matrix with $\wt{D}_{uu} = \deg(u;\wt{G})$ if $u \in C$, and $0$ otherwise.
+
+These quantities admit a natural interpretation in terms of random walks.
+For $u \in C$, $\ell^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $C$ on the $(t + 1)$st step.
+On the other hand, for $u \not\in C$, $s^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps and is then ``soaked up'' into $u$ on the $(t + 1)$st step.
+The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the PPR vector.
+
+Three properties of $\ell$ and $s$ are worth pointing out.
+First, $\mathrm{supp}(\ell) \subseteq C \setminus C_o$ and $\mathrm{supp}(s) \subseteq V \setminus C$.
+Second, $\|\ell^{(t)}\|_1 = \|s^{(t)}\|_1$ for all $t \in \mathbb{N}$, and so $\|\ell\|_1 = \|s\|_1$.
+Third, for any $u \in V \setminus C$, $p_v(u) = p_s(u)$.
+The first two properties are immediate.
+The third property follows by the law of total probability, which implies that
+\begin{equation*}
+q_v^{(\tau)}(u) = \sum_{t = 0}^{\tau} q_{s^{(t)}}^{(\tau - t)}(u),~~\textrm{for all $u \in V \setminus C$.}
+\end{equation*}
+or in terms of the PPR vector,
+\begin{equation*}
+p_v(u) = \alpha \sum_{\tau = 0}^{\infty} (1 - \alpha)^{\tau} q_v^{(\tau)}(u) = \alpha \sum_{\tau = 0}^{\infty} \sum_{t = 0}^{\tau} (1 - \alpha)^{\tau} q_{s^{(t)}}^{(\tau - t)}(u).
+\end{equation*}
+Substituting $\Delta = \tau + t$ and rearranging gives the claimed property, as
+\begin{equation*}
+p_v(u) = \alpha \sum_{\tau = 0}^{\infty} \sum_{t = 0}^{\tau} (1 - \alpha)^{\tau} q_{s^{(t)}}^{(\tau - t)}(u) = \sum_{\Delta = 0}^{\infty} \sum_{t = 0}^{\infty} (1 - \alpha)^{\Delta + t} q_{s^{(t)}}^{(\Delta)}(u) = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} q_s^{(\Delta)}(u) = p_s(u).
+\end{equation*}
+
+\begin{proof}[Proof (of Lemma~\ref{lem:ppr_uniform_bound})]
+	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
+	\begin{equation*}
+	p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$,}
+	\end{equation*}
+	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$.
+Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry},
+	\begin{equation*}
+	\wt{p}_{\ell}(u) \leq \frac{\|\ell\|_1}{d_{\min}(\wt{G})}~~\textrm{for all $u \in C_{o}$,}
+	\end{equation*}
+	establishing~\eqref{eqn:ppr_uniform_bound_C}. The proof of~\eqref{eqn:ppr_uniform_bound_Cprime} follows similarly:
+	\begin{equation*}
+	p_v(u) = p_s(u) \overset{(i)}{\leq} \frac{\|s\|_1}{d_{\min}(C';G)} = \frac{\|\ell\|_1}{d_{\min}(C';G)},~~\textrm{for all $u \in C_{o}'$},
+	\end{equation*}
+	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}. 	
+\end{proof}
 
 \subsection{Mixedness of lazy random walk and PPR vectors}
+\label{subsec:lovasz_simonovits_bounds}
 In this subsection, we give upper bounds on $h^{(t)} := h_{q_v^{(t)}}$ and $h^{(\alpha)} := h_{p_v}$.
@@
 	\label{thm:mixing_time_rw}
-	For any $k \in [d_{\max}(G), 2m - d_{\max}(G)]$ and $t \geq 3$,
+	For any $k \in [0, 2m]$, $t_0 \in \mathbb{N}$ and $t \geq t_0$,
 	\begin{equation}
 	\label{eqn:mixing_time_rw_1}
-	h^{(t)}(k) \leq \frac{1}{8} + \frac{d_{\max}(G)}{2d_{\min}(G)^2} + \frac{\sqrt{m}}{d_{\min}(G)^2} \sqrt{\wb{k}} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t - 3}.
-	\end{equation}
-	For any $k \in [0, d_{\max}(G)) \cup (2m - d_{\max}(G),2m]$,
-	\begin{equation}
-	\label{eqn:mixing_time_rw_2}
-	h^{(t)}(k) \leq \frac{1}{8} + \frac{d_{\max}(G)}{2d_{\min}(G)^2}.
+	h^{(t)}(k) \leq \frac{1}{2^{t_0}} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{m}{d_{\min}(G)^2} \biggl(1 - \frac{\Psi(G)^2}{8}\biggr)^{t - t_0}.
 	\end{equation}
@@
 	\begin{equation*}
-	h^{(\alpha)}(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t},
+	h^{(\alpha)}(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{m}{d_{\min}(G)^2} \left(1 - \frac{\phi^2}{8}\right)^{t},
 	\end{equation*}
-	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) \leq \phi$.
+	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
 \end{theorem}
@@
 The proofs of these upper bounds will be similar to each other (in places word-for-word alike), and will follow a similar approach and use similar notation to that of \citep{lovasz1990,andersen2006}.
-For a given $0 \leq K_0 \leq m$ and a function $h: [0,2m] \to [0,1]$, let
+For $h: [0,2m] \to [0,1]$, $0 \leq K_0 \leq m$ and $k \in [K_0,2m - K_0]$, define
 \begin{equation*}
@@
 \end{equation*}
-be the linear interpolant of $h(K_0)$ and $h(2m - K_0)$, and additionally let
+to be the linear interpolant of $h(K_0)$ and $h(2m - K_0)$, and additionally let
 \begin{equation*}
@@
 \end{equation*}
-where we use the notation $\overline{k} := \min\{k, 2m - k\}$, and set $0/0$ equal to $0$.
+where we use the notation $\overline{k} := \min\{k, 2m - k\}$, and treat $0/0$ as equal to $1$.
 Our first pair of Lemmas upper bound $h^{(t)}$ and $h^{(\alpha)}$ as a function of $L_{K_0}$ and $C(K_0)$.
@@
 	\end{equation}
-	or else there exists some sweep cut $S_{j}$ of $p_v$ such that $\Phi(S_j;G) \leq \phi$.
+	or else there exists some sweep cut $S_{j}$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
 \end{lemma}
 
-In order to make use of these Lemmas, we require upper bounds on $L_{K_0}(\cdot,h)$ and $C(K_0;h)$, for each of $h = h^{(3)}$ and $h = h^{(\alpha)}$.
+In order to make use of these Lemmas, we require upper bounds on $L_{K_0}(\cdot,h)$ and $C(K_0;h)$, for each of $h = h^{(t_0)}$ and $h = h^{(\alpha)}$.
 Of course, trivially $L_{K_0}(k;h) \leq \max\{h(K_0); h(2m - K_0)\}$ for any $k \in [K_0, 2m - K_0]$.
-As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$.
+As it happens, this observation will lead to sufficient upper bounds on $L_{K_0}(k,h)$ for both $h = h^{(t_0)}$ (Lemma~\ref{lem:interpolator_bound_rw}) and $h = h^{(\alpha)}$ (Lemma~\ref{lem:interpolator_bound_ppr}).
 \begin{lemma}
 	\label{lem:interpolator_bound_rw}
-	For any $K_0 \in [0,2m]$, it holds that
-	\begin{equation*}
-	h^{(3)}\bigl(2m - K_0\bigr) \leq \frac{K_0}{2m}~~\textrm{and}~~h^{(3)}\bigl(K_0\bigr) \leq \frac{K_0}{2d_{\min}(G)^2} + \frac{1}{8}.
-	\end{equation*}
+	For any $t_0 \in \mathbb{N}$ and $K_0 \in [0,m]$, the following inequalities hold:
+	\begin{equation}
+	\label{eqn:interpolator_bound_rw}
+	h^{(t_0)}\bigl(2m - K_0\bigr) \leq \frac{K_0}{2m}~~\textrm{and}~~h^{(t_0)}\bigl(K_0\bigr) \leq \frac{K_0}{d_{\min}(G)^2} + \frac{1}{2^{t_0}}.
+	\end{equation}
 	As a result, for any $k \in [K_0, 2m - K_0]$,
-	\begin{equation*}
-	L_{K_0}(k;h^{(3)}) \leq \frac{1}{8} + \frac{K_0}{2d_{\min}(G)^2}.
-	\end{equation*}
+	\begin{equation}
+	\label{eqn:interpolator_bound_rw_2}
+	L_{K_0}(k;h^{(t_0)}) \leq \max\Bigl\{\frac{K_0}{2m}, \frac{K_0}{d_{\min}(G)^2} + \frac{1}{2^{t_0}}\Bigr\} = \frac{K_0}{d_{\min}(G)^2} + \frac{1}{2^{t_0}}.
+	\end{equation}
 \end{lemma}
@@
 	\label{lem:interpolator_bound_ppr}
-	For any $K_0 \in [0,2m]$, it holds that 
-	\begin{equation*}
-	h^{(\alpha)}(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h^{(\alpha)}(K_0) \leq \frac{K_0}{2d_{\min}(G)^2} + \frac{2\alpha}{1 + \alpha}.
-	\end{equation*}
-	As a result, for any $k \in [K_0,2m - K_0]$,
-	\begin{equation*}
-	L_{K_0}(k; h^{(\alpha)}) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}(G)^2}.
-	\end{equation*}
+	For any $\alpha \in [0,1]$ and $K_0 \in [0,m]$, the following inequalities hold:
+	\begin{equation}
+	\label{eqn:interpolator_bound_ppr}
+	h^{(\alpha)}\bigl(2m - K_0\bigr) \leq \frac{K_0}{2m}~~\textrm{and}~~h^{(\alpha)}\bigl(K_0\bigr) \leq \frac{K_0}{d_{\min}(G)^2} + \frac{2\alpha}{1 + \alpha}.
+	\end{equation}
+	As a result, for any $k \in [K_0, 2m - K_0]$,
+	\begin{equation}
+	\label{eqn:interpolator_bound_ppr_2}
+	L_{K_0}(k;h^{(\alpha)}) \leq \max\Bigl\{\frac{K_0}{2m}, \frac{K_0}{d_{\min}(G)^2} + \frac{2\alpha}{1 + \alpha}\Bigr\} = \frac{K_0}{d_{\min}(G)^2} + \frac{2\alpha}{1 + \alpha}.
+	\end{equation}
 \end{lemma}
@@
 We next establish an upper bound on $C_{K_0}(k;h)$, which rests on the following key observation: since $h(k)$ is concave and $L_{K_0}(K_0;h) = h(K_0)$, it holds that
-\begin{equation*}
+\begin{equation}
+\label{pf:linearization_bound_1}
 \frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq
@@
 \end{cases}
-\end{equation*}
+\end{equation}
 (Since $h$ is not differentiable at $k = k_j$, here $h'$ refers to the right derivative of $h$.)
 
-Lemma~\ref{lem:linearization_bound} gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, which hold for both $h = h^{(3)}$ and $h = h^{(\alpha)}$, and result in an upper bound on $C(K_0;h)$.
-Both the statement and proof of this Lemma are made easier by the \emph{Lovasz-Simonovits curve}, which is an explicit representation of the function $h_q(\cdot)$ that holds for any distribution $q$.
-Ordering the vertices $\frac{q(u_{(1)})}{\deg(u_{(1)};G)} \geq \frac{q(u_{(2)})}{\deg(u_{(2)};G)} \geq \cdots \geq \frac{q(u_{(n)})}{\deg(u_{(n)};G)}$, the function $h_q(k)$ satisfies
+Lemma~\ref{lem:linearization_bound} gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, which hold for both $h = h^{(t_0)}$ and $h = h^{(\alpha)}$, and result in an upper bound on $C(K_0;h)$.
+Both the statement and proof of this Lemma rely on the following explicit representation of the Lovasz-Simonovits curve $h_q(\cdot)$.
+Order the vertices $q(u_{(1)})/\deg(u_{(1)};G) \geq q(u_{(2)})/\deg(u_{(2)};G) \geq \cdots \geq q(u_{(n)})/\deg(u_{(n)};G)$.
+Then for each $j = 0,\ldots,n - 1$, and for all $k \in [\vol(S_j),\vol(S_{j + 1}))$,  the function $h_q(k)$ satisfies
 \begin{equation}
 \label{eqn:lovasz_simonovits}
-h_q(k) = \sum_{i = 0}^{j} \left(q(u_{(i)}) - \pi(u_{(i)})\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(q(u_{(j+1)}) - \pi(u_{(j+1)})\right) 
+h_q(k) = \sum_{i = 0}^{j} \left(q(u_{(i)}) - \pi(u_{(i)})\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(q(u_{(j+1)}) - \pi(u_{(j+1)})\right). 
 \end{equation}
-for all $k \in [\vol(S_j),\vol(S_{j + 1}))$ and $j = 0,\ldots,n-1$.
 \begin{lemma}
 	\label{lem:linearization_bound}
-	The following statements hold for both $h = h^{(\alpha)}$ and $h = h^{(3)}$.
-
-	If $u_{(1)} = v$, then 
+	The following statements hold for both $h = h^{(\alpha)}$ and $h = h^{(t_0)}$. 
+	\begin{itemize}
+		\item Let $K_0 = k_1 = \deg(v;G)$ if $u_{(1)} = v$, and otherwise $K = 0$. Then  
 		\begin{equation}
 		\label{eqn:right_derivative_1}
-	h'\bigl(\deg(v;G)\bigr) \leq \frac{1}{2\deg_{\min}(G)^2};
+		h'\bigl(K_0\bigr) \leq \frac{1}{d_{\min}(G)^2}.
 		\end{equation}
-	otherwise $u_{(1)} \neq v$ and
+		\item For all $K_0 \in [0,m]$,
 		\begin{equation}
 		\label{eqn:right_derivative_2}
-	h'(0) \leq \frac{1}{2\deg_{\min}(G)^2};
+		h'(2m - K_0) \geq -\frac{d_{\max}(G)}{d_{\min}(G)\cdot \vol(G)}.
 		\end{equation}
-	for all $K \in [0,m]$,
-	\begin{equation}
-	\label{eqn:right_derivative_3}
-	h'(2m - K) \geq -\frac{d_{\max}}{d_{\min}\cdot \vol(G)}.
-	\end{equation}
+	\end{itemize}
 	As a result, letting $K_0 = \deg(v;G)$ if $u_{(1)} = v$, and otherwise letting $K_0 = 0$, we have
@@
 \begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_rw})]
-	\textcolor{red}{(TODO)}
+	Take $K_0 = 0$ if $u_{(1)} \neq v$, and otherwise take $K_0 = \deg(v;G)$.
+Combining Lemmas~\ref{lem:mixing_random_walk},~\ref{lem:interpolator_bound_rw} and~\ref{lem:linearization_bound}, we obtain that for any $k \in [K_0,2m - K_0]$,
+	\begin{align*}
+	h^{(t)}(k) & \leq \frac{1}{2^{t_0}} + \frac{K_0}{d_{\min}(G)^2}  + \frac{\sqrt{m}}{d_{\min}(G)^2} \sqrt{\wb{k}} \Bigl(1 - \frac{\Psi^2(G)}{8}\Bigr)^{t-t_0} \\
+	& \leq \frac{1}{2^{t_0}} + \frac{d_{\max}(G)}{d_{\min}(G)^2}  + \frac{m}{d_{\min}(G)^2} \Bigl(1 - \frac{\Psi^2(G)}{8}\Bigr)^{t-t_0},
+	\end{align*}
+	where the second inequality follows since we have chosen $K_0 \leq d_{\max}(G)$, and since $\wb{k} \leq m$. If $K_0 = 0$, we are done.
+
+	Otherwise, we must still establish that~\eqref{eqn:mixing_random_walk} is a valid upper bound when $k \in [0, \deg(v;G)) ~\cup~ (2m - \deg(v;G),2m]$. If $k \in [0, \deg(v;G))$ then
+	\begin{equation}
+	\label{pf:mixing_random_walk_1}
+	h^{(t)}(k) \overset{\eqref{pf:mixing_random_walk_inductive_step}}{\leq} h^{(t_0)}(k) \overset{(\textrm{i})}{\leq} h^{(t_0)}(K_0) \overset{\eqref{eqn:interpolator_bound_rw}}{\leq} \frac{K_0}{d_{\min}(G)^2} + \frac{1}{2^{t_0}},
+	\end{equation}
+	where $(\textrm{i})$ follows since $k \in [0,K_0]$, and $h^{(t_0)}$ is linear over $[0,K_0)$ with $h^{(t_0)}(0) = 0$ and $h^{(t_0)}(K_0) \geq 0$. For similar reasons,
+	\begin{equation}
+	\label{pf:mixing_random_walk_2}
+	h^{(t)}(k) \leq h^{(t_0)}(k) \leq h^{(t_0)}(2m - K_0) \leq \frac{\deg(v;G)}{2m}.
+	\end{equation}
+	Since the ultimate upper bounds in~\eqref{pf:mixing_random_walk_1} and~\eqref{pf:mixing_random_walk_2} are each no greater than that of~\eqref{eqn:mixing_random_walk}, the claim follows.
 \end{proof}
 
+\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_PPR})]
 	The proof of Theorem~\ref{thm:mixing_time_PPR} follows immediately from Lemmas~\ref{lem:mixing_time_PPR},~\ref{lem:interpolator_bound_ppr} and~\ref{lem:linearization_bound}, taking $K_0 = 0$ if $u_{(1)} \neq v$ and otherwise $K_0 = \deg(v;G)$.
+\end{proof}
 
 \paragraph{Proofs of Lemmas.}
-In our proof of Lemma~\ref{lem:mixing_random_walk}, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$.
+In what follows, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$.
 \begin{proof}[Proof (of Lemma~\ref{lem:mixing_random_walk})]
@@
 
-\begin{proof}[Proof (of Theorem~\ref{lem:mixing_time_PPR}).]
-	We will show that if $\Phi(S_j; g) > \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.
+\begin{proof}[Proof (of Lemma~\ref{lem:mixing_time_PPR}).]
+	We will show that if $\Phi(S_j; g) \geq \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.
 
@@
 \begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_rw})]
-	\textcolor{red}{(TODO)}
+	We will prove that the inequalities of~\eqref{eqn:interpolator_bound_rw} hold at the knot points of $h^{(t_0)}$, whence they follow for all $K_0 \in [0,m]$.
+
+	We first prove the upper bound on $h^{(t_0)}(2m - K_0)$, when $2m - K_0 = k_j$ for some $j = 0,\ldots,n - 1$.
+Indeed, the following manipulations show the upper bound holds for $h_q(\cdot)$ regardless of the distribution $q$.
+Noting that $h_q(2m) = 0$, we have that,
+	\begin{equation*}
+	h_q(k_j) = h_q(k_j) - h_q(2m) = \sum_{i = j + 1}^{n} q(u_{(i)}) - \pi(u_{(i)}) \leq \sum_{i = j + 1}^{n} \pi(u_{(i)}) = 1 - \frac{k_j}{2m} = \frac{K_0}{2m}.
+	\end{equation*}
+
+	In contrast, when $K_0 = k_j$ the upper bound on $h^{(t_0)}(\cdot)$ depends on the properties of $q = q_v^{(t_0)}$. In particular, we claim that for any $t \in \mathbb{N}$,
+	\begin{equation}
+	\label{pf:interpolator_bound_max_entry}
+	q_v^{(t)}(u) \leq
+	\begin{dcases*}
+	\frac{1}{d_{\min}(G)},& ~~\textrm{if $u \neq v$} \\
+	\frac{1}{d_{\min}(G)} + \frac{1}{2^t},& ~~\textrm{if $u = v$.}
+	\end{dcases*}
+	\end{equation}
+	This claim follows straightforwardly by induction. In the base case $t = 0$, the claim is obvious. If the claim holds true for a given $t \in \mathbb{N}$, then for $u \neq v$,
+	\begin{equation}
+	\label{pf:interpolator_bound_max_entry_inductive_step}
+	\begin{aligned}
+	q_v^{(t + 1)}(u) & = \frac{1}{2}\sum_{w \neq u}q_v^{(t)}(w,u)  + \frac{1}{2}q_v^{(t)}(u) \\
+	& \leq \frac{1}{2d_{\min}(G)}\sum_{w \neq u}q_v^{(t)}(w)  + \frac{1}{2d_{\min}(G)} \\
+	& \leq \frac{1}{d_{\min}(G)},
+	\end{aligned}
+	\end{equation}
+	where the last inequality holds because $q_v^{(t)}$ is a probability distribution (i.e. the sum of its entries is equal to $1$). Similarly, if $u = v$, then
+	\begin{align*}
+	q_v^{(t + 1)}(v) & = \frac{1}{2}\sum_{w \neq v}q_v^{(t)}(w,v)  + \frac{1}{2}q_v^{(t)}(v) \\
+	& \leq \frac{1}{2d_{\min}(G)}\sum_{w \neq u}q_v^{(t)}(w)  + \frac{1}{2d_{\min(G)}} + \frac{1}{2^{t + 1}} \\
+	& \leq \frac{1}{d_{\min}(G)} + \frac{1}{2^{t + 1}},
+	\end{align*}
+	and the claim~\eqref{pf:interpolator_bound_max_entry} is shown. The upper bound on $h^{(t_0)}(K_0)$ for $K_0 = k_j$ follows straightforwardly:
+	\begin{equation*}
+	h^{(t_0)}(K_0) \leq \sum_{i = 0}^{j} q_v^{(t_0)}(u_{(j)}) \leq \frac{j}{d_{\min}(G)} + \frac{1}{2^{t_0}} \leq \frac{K_0}{d_{\min}(G)^2} + \frac{1}{2^{t_0}},
+	\end{equation*}
+	where the last inequality follows since $\vol(S) \geq |S| \cdot d_{\min}(G)$ for any set $S \subseteq V$. 
 \end{proof}
@@
 \begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_ppr})]
-	\textcolor{red}{(TODO): Revise the notation in this proof.}
-
-	We make use of the representation~\eqref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
-	\begin{align*}
-	h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
-	& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
-	& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
-	\end{align*}
-
-	We will upper bound $h(K_0)$ by $p[\vol(S_j)] \leq p_v(v) + \sum_{u \in S_j \setminus \set{v}}p_v(u)$.
-In the proof of Lemma~\ref{lem:linearization_bound} we have already given an upper bound on $p_v(u)$ when $u \neq v$.
-Now, we additionally observe that for all $t$,
-	\begin{equation*}
-	e_vW^t(v) \leq \frac{1}{2d_{\min}} + \left(\frac{1}{2}\right)^t
-	\end{equation*}
-	and therefore $p_v(v) \leq \frac{1}{2d_{\min}} + \frac{2\alpha}{1 + \alpha}$.
-	As a result,
+	We have already established the first upper bound in~\eqref{eqn:interpolator_bound_ppr}, in the proof of Lemma~\ref{lem:interpolator_bound_rw}.
+Then, noting that from~\eqref{pf:interpolator_bound_max_entry},
 	\begin{equation}
-	h(K_0) \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
+	\label{eqn:ppr_max_entry}
+	p_v(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t q_v^{(t)}(u) \leq
+	\begin{dcases*}
+	\alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \Bigl(\frac{1}{d_{\min}(G)} + \frac{1}{2^t}\Bigr) = \frac{1}{d_{\min}(G)} + \frac{2\alpha}{1 - \alpha}& ~~\textrm{if $u = v$} \\
+	\alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \frac{1}{d_{\min}(G)} = \frac{1}{d_{\min}(G)} & ~~\textrm{if $u \neq v$,}
+	\end{dcases*}
 	\end{equation}
-	where the latter inequality follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.
+	the second upper bound in~\eqref{eqn:interpolator_bound_ppr} follows similarly to the proof of the equivalent upper bound in~Lemma~\ref{lem:interpolator_bound_rw}.
 \end{proof}
@@
 \begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
-	The result of the Lemma is obvious once we show \eqref{eqn:right_derivative_1}-\eqref{eqn:right_derivative_2}.
-From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
-	\begin{equation}
-	\label{eqn:linearization_bound_pf1}
-	h'(k) \leq \frac{p(v_{(j + 1)})}{\deg(v_{(j + 1)};G)}
-	\end{equation}
+	The result of the Lemma follows obviously from~\eqref{pf:linearization_bound_1}, once we show \eqref{eqn:right_derivative_1}-\eqref{eqn:right_derivative_2}.
+We begin by showing~\eqref{eqn:right_derivative_1}.
+Inspecting the representation~\eqref{eqn:lovasz_simonovits}, we see that for any distribution $q$ and knot point $k_j$, the right derivative of $h_q$ can always be upper bounded,
+	\begin{equation*}
+	h_{q}'(k_j) \leq \frac{q(u_{(j + 1)})}{\deg(u_{(j + 1)};G)}.
+	\end{equation*}
+	Thus, as long as $u_{(j + 1)} \neq v$ we have from~\eqref{pf:interpolator_bound_max_entry} that---for either $q = q_v^{(t)}$ or $q = p_v$---the inequality $h_{q}'(k_j) \leq 1/(d_{\min}(G)^2)$ holds.
+The statement of~\eqref{eqn:right_derivative_1} guarantees that $u_{(j + 1)} \neq v$.
 
-	We now upper bound $p(u)$ uniformly over all $u$ except the seed node $v$. For any $u \in V$ besides the seed node $v$, we can show by induction that
+	On the other hand, the inequality \eqref{eqn:right_derivative_2} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since for any $K \in [0,m]$, taking $j$ so that $2m - K \in [k_j, k_{j + 1})$,
 	\begin{equation*}
-	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
+	h'(2m - K) \geq -\frac{\pi(u_{(j+1)})}{\mathrm{deg}(u_{(j + 1)};G)} \geq -\frac{d_{\max}(G)}{d_{\min}(G) \cdot \vol(G)}.
 	\end{equation*}
-	for any $t \geq 0$, and therefore
-	\begin{equation}
-	\label{eqn:linearization_bound_pf2}
-	p(\alpha,\chi_v)(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \leq  \frac{1}{2d_{\min}}.
-	\end{equation}
-	As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = \deg(v;G)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}.
-The inequality \eqref{eqn:right_derivative} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since
-	\begin{equation*}
-	h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}},
-	\end{equation*}
-	and the proof of the Lemma is therefore complete.
 \end{proof}
-
-\clearpage
 
@@
 \label{subsec:pf_prop_pointwise_mixing_time}
-To prove Proposition~\ref{prop:pointwise_mixing_time}, we will establish an upper bound on a total variation distance between $q_v^{(t)}$ and $\pi$, then upgrade to the desired uniform upper bound.
+To prove Proposition~\ref{prop:pointwise_mixing_time}, we will upgrade from an upper bound on the total variation distance between $q_v^{(t)}$ and $\pi$ to the desired uniform upper bound.
 The \emph{total variation distance} between distributions $q$ and $p$ is
 \begin{equation*}
-d_{\mathrm{TV}}(q,p) := \sum_{u \in v} \bigl|q(u) - p(u)\bigr|
+\mathrm{TV}(q,p) := \frac{1}{2}\sum_{u \in v} \bigl|q(u) - p(u)\bigr|
 \end{equation*}
-It is a matter of some basic algebra~\textcolor{red}{(Either show it yourself or point to a reference)} to show that
+It follows from the representation~\eqref{eqn:lovasz_simonovits} that
 \begin{equation*}
-d_{\mathrm{TV}}(q,\pi) \leq \sup_{k \in [0,2m]} h_q(k).
+\mathrm{TV}(q,\pi) = \max_{S \subseteq V} \Bigl\{q(S) - \pi(S)\Bigr\} = \max_{j = 1,\ldots,n} \Bigl\{q(S_j) - \pi(S_j)\Bigr\} = \max_{k \in [0,2m]} h_q(k),
 \end{equation*}
+so that Theorem~\ref{thm:mixing_time_rw} gives an upper bound on $\mathrm{TV}(q_v^{(t)},\pi)$. We can then use the following result to upgrade to a uniform upper bound.
+
+\begin{lemma}
+	\label{lem:tv_to_pointwise}
+	For any $t \in \mathbb{N}$,
+	\begin{equation*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{2 \cdot \mathrm{TV}(q_v^{(t)}, \pi)}{s(G)}.
+	\end{equation*}
+\end{lemma}
+
+The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward.
+\begin{proof}[Proof (of Proposition~\ref{prop:pointwise_mixing_time})]
+	Put $t_{\ast} = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
+We will use Theorem~\ref{thm:mixing_time_rw} to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$.
+This will in turn imply (\cite{montenegro2002} pg.
+13) that for $\tau_{\ast} = t_{\ast} \log_2(8/s(G))$,
+	\begin{equation*}
+	\mathrm{TV}(q_v^{(\tau_{\ast})},\pi) \leq \frac{1}{8}s(G),
+	\end{equation*}
+	and applying Lemma~\ref{lem:tv_to_pointwise} gives
+	\begin{equation*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(\tau_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{1}{4}.
+	\end{equation*}
+	Taking maximum over all $v \in V$, we conclude that $\tau_{\infty}(G) \leq \tau_{\ast} + 1$, which is exactly the claim of Proposition~\ref{prop:pointwise_mixing_time}.
+
+	It remains to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$. Choosing $t_0 = 4$ in the statement of Theorem~\ref{thm:mixing_time_rw}, we have that
+	\begin{align*}
+	\mathrm{TV}(q_v^{(t_{\ast})},\pi) & \leq \frac{1}{16} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
+	& \leq \frac{1}{8} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
+	& \leq \frac{1}{8} + \frac{1}{2s(G)} \exp\Bigl(-\frac{\Psi(G)^2}{8}(t_{\ast} - 4)\Bigr) = \frac{1}{4},
+	\end{align*}
+	where the middle inequality follows by assumption.
+\end{proof}
+
+\begin{proof}[Proof (of Lemma~\ref{lem:tv_to_pointwise})]
+	We proceed by induction. In the base case $t = 0$, we have that
+	\begin{equation*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq 1 \leq 2(1 - \pi(v)) \leq 2\frac{\mathrm{TV}(q_v^{(0)},\pi)}{s(G)},
+	\end{equation*},
+	where the second inequality follows since $\pi(v) \leq d_{\max}(G)/(2m) \leq d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$.
+
+	To prove the inductive step, the key observation is the following equivalence (see equation (16) of \citep{morris2005}):
+	\begin{align}
+	\label{pf:tv_to_pointwise_1}
+	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} & = \sum_{w \in V} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) \nonumber \\
+	& = \sum_{w \neq u} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) + \bigl(\pi(u) - q_v^{(t)}(u) \bigr) \cdot \Bigl(\frac{q_u^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr)
+	\end{align}
+	We separately upper bound each term on the right hand side of~\eqref{pf:tv_to_pointwise_1}.
+The sum over all $w \neq u$ can be related to the TV distance between $q_v^{(t)}$ and $\pi$ using H{\"o}lder's inequality,
+	\begin{align*}
+	\sum_{w \neq u} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) & \leq 2\mathrm{TV}(q_v^{(t)},\pi) \cdot \max_{w \neq u}\Bigl|\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr| \\
+	& \leq 2\mathrm{TV}(q_v^{(t)},\pi) \cdot \max\biggl\{1, \max_{w \neq u} \frac{q_w^{(1)}(u)}{\pi(u)} \biggr\} \\
+	& \leq 2\mathrm{TV}(q_v^{(t)},\pi) \cdot \frac{m}{d_{\min}(G)^2} = \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)}.
+	\end{align*}
+	On the other hand, the second term on the right hand side of~\eqref{pf:tv_to_pointwise_1} satisfies
+	\begin{align*}
+	\bigl(\pi(u) - q_v^{(t)}(u) \bigr) \cdot \Bigl(\frac{q_u^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) \leq \bigl(\pi(u) - q_v^{(t)}(u) \bigr) \cdot \Bigl(\frac{1/2 - \pi(u)}{\pi(u)}\Bigr) \leq \frac{\pi(u) - q_v^{(t)}(u)}{2\pi(u)},
+	\end{align*}
+	so that we obtain the recurrence relation
+	\begin{equation*}
+	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} +\frac{\pi(u) - q_v^{(t)}(u)}{2\pi(u)}.
+	\end{equation*}
+	Then by the inductive hypothesis $\bigl(\pi(u) - q_v^{(t)}(u)\bigr)/\bigl(2\pi(u)\bigr) \leq \mathrm{TV}(q_v^{(t - 1)},\pi)/s(G)$, and consequentially
+	\begin{equation*}
+	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} + \frac{\mathrm{TV}(q_v^{(t - 1)},\pi) }{s(G)} \leq 2\frac{\mathrm{TV}(q_v^{(t)},\pi)}{s(G)}.
+	\end{equation*}
+	This completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
+\end{proof}
 
@@
 \label{subsec:ppr_spectral_partitioning}
-The following theorem is the main theorem of this section. It relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of $C$.
+The following theorem is the main result of~\ref{subsec:ppr_spectral_partitioning}.
+It relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of a candidate cluster $C \subseteq V$, when $p_v$ is properly initialized within $C$.
 
-\begin{theorem}
-	\label{thm:conductance_ppr}
-	Let $C \subseteq V$ satisfy the following conditions:
+\begin{theorem}[\textbf{c.f. Theorem~6 of \cite{andersen2006}}]
+	\label{thm:normalized_cut_ppr}
+	Suppose that
+	\begin{equation}
+	\label{eqn:normalized_cut_ppr_vol}
+	d_{\max}(G) \leq \vol(C;G) \leq \max\Bigl\{\frac{2}{3}\vol(G); \vol(G) - d_{\max}(G)\Bigr\}
+	\end{equation}
+	and
+	\begin{equation}
+	\label{eqn:normalized_cut_ppr_ncut}
+	\max\Bigl\{288\Phi(C;G)\cdot \ln\Bigl(\frac{36}{s(G)}\Bigr),72\Phi(C;G) + \frac{d_{\max}(G)}{d_{\min}(G)^2}\Bigr\} < \frac{1}{18}.
+	\end{equation}
+	Set $\alpha = 36 \cdot \Phi(C;G)$.
+The following statement holds: there exists a set $C^g \subseteq C$ of large volume, $\vol(C^g;G) \geq 5/6 \cdot \vol(C;G)$, such that for any $v \in C^g$,  the minimum normalized cut of the sweep sets of $p_v$ satisfies
+	\begin{equation}
+	\label{eqn:normalized_cut_ppr}
+	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) < 72\sqrt{\Phi(C;G) \cdot \ln\Bigl(\frac{36}{s(G)}\Bigr)}.
+	\end{equation}
+\end{theorem}
+A few remarks:
 \begin{itemize}
-		\item $\vol(C;G) \leq \frac{2}{3}\vol(G)$,
-		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
-		\item $\frac{20\Phi(C;G)}{1 + 10\Phi(C;G)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
+	\item Theorem~\ref{thm:normalized_cut_ppr} is similar to Theorem 6 of \citet{andersen2006}, but crucially the above bound depends on $\log\bigl(1/s(G)\bigr)$ rather than $\log m$.
+In the case where $d_{\min}(G)^2 \asymp \vol(G)$ and thus $s(G) \asymp 1$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$.
+	\item For simplicity, we have chosen to state Theorem~\ref{thm:normalized_cut_ppr} with respect to a specific choice of $\alpha = 36 \cdot \Phi(C;G)$, but if $\alpha \approx 36 \cdot \Phi(C;G)$ then the Theorem will still hold up to constant factors.
 \end{itemize}
-	Suppose $60\Phi(C;G) \leq \alpha \leq 70\Phi(C;G)$, and let $(L,U) = (0,1)$.
-Then, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$ such that for any $v \in C^g$ the following statement holds: For the PPR vector $p_v := p(v,\alpha;G)$, the minimum normalized cut of the sweep sets satisfies
+
+It follows from Markov's inequality (see Theorem~4 of \cite{andersen2006}) that there exists a set $C^g \subseteq C$ of volume $\vol(C^g;G) \geq 5/6 \cdot \vol(C;G)$ such that for any $v \in C^g$,
+\begin{equation}
+\label{eqn:ppr_leakage}
+p_v(C) \geq 1 - \frac{6\Phi(C;G)}{\alpha}.
+\end{equation}
+The claim of Theorem~\ref{thm:normalized_cut_ppr} is a consequence of~\eqref{eqn:ppr_leakage} along with Theorem~\ref{thm:mixing_time_PPR}, as we now demonstrate.
+\begin{proof}[Proof (of Theorem~\ref{thm:normalized_cut_ppr})]
+	From~\eqref{eqn:ppr_leakage}, the upper bound in~\eqref{eqn:normalized_cut_ppr_vol}, and the choice of $\alpha = 36 \cdot \Phi(C;G)$, 
+	\begin{equation}
+	\label{pf:normalized_cut_ppr}
+	p_v(C) - \pi(C) \geq \frac{1}{3} - \frac{6 \Phi(C;G)}{\alpha} = \frac{1}{6}.
+	\end{equation}
+	Now, put 
 	\begin{equation*}
-	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C;G)}
+	t_{\ast} = \frac{1}{648 \Phi(C;G)},~~\phi_{\ast}^2 = \frac{8}{t_{\ast}} \cdot \ln\Bigl(\frac{36}{s(G)}\Bigr),
 	\end{equation*}
-\end{theorem}
-
-\begin{remark}
-	Although this theorem appears quite similar to standard results in the PPR literature -- for instance, Theorem 6 of \citet{andersen2006} -- crucially the above bound depends on $\log\left(\frac{m}{d_{\min}^2}\right)$ rather than $\log m$.
-In the case where $d_{\min} \asymp n$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$.
-\end{remark}
-Notwithstanding the aforementioned improvements, the proof of Theorem~\ref{thm:conductance_ppr} follows the same general outline as the proof of Theorem~6 of \citet{andersen2006}.
-We now walk through this outline step by step, modifying the results of \citet{andersen2006} as needed.
-As with their work, we begin by proving a mixing time bound on the PPR vector $p_v$.
-
-\subsubsection{Mixing time of PPR.}
-
-To quantify the mixing of a PPR vector $p_v$, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$.
-For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that $S_{\beta_j}$ contains at least $j$ vertices.
-(For notational ease, we will write $S_{i} := S_{\beta_i}$, so that $S_1,S_2,\ldots,S_n$ comprise the $n$ unique sweep cuts of $p_v$.)
-For each $j = 1,\ldots,n$, we let $p[\vol(S_j)] =  \sum_{u \in S} p_v(u)$.
-Additionally, we let $p[0] = 0$ and $p[2m] = 1$.
-Finally, we extend $p[\cdot]$  by piecewise interpolation to be defined everywhere on its domain.
-The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$, defined as
+	and note that by~\eqref{eqn:normalized_cut_ppr_ncut} $\phi_{\ast}^2 \in [0,1]$. It therefore follows from~\eqref{pf:normalized_cut_ppr} and Theorem~\ref{thm:mixing_time_PPR} that either
+	\begin{equation}
+	\label{pf:normalized_cut_ppr_2}
+	\frac{1}{6} \leq p_v(C) - \pi(C) \leq \frac{1}{18} + 72 \Phi(C;G) + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \cdot \left(1 - \frac{\phi_{\ast}^2}{8}\right)^{t_{\ast}},
+	\end{equation}
+	or $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. But by~\eqref{eqn:normalized_cut_ppr_ncut}
 	\begin{equation*}
-h(k) = p[k] - \frac{k}{2m}.
+	72 \Phi(C;G) + \frac{d_{\max}(G)}{d_{\min}(G)^2} < \frac{1}{18},
 	\end{equation*}
-Next, for a given $0 \leq K_0 \leq m$, let 
+	and we have chosen $\phi_{\ast}$ precisely so that
 	\begin{equation*}
-L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
+	\frac{1}{2s(G)} \cdot \left(1 - \frac{\phi_{\ast}^2}{8}\right)^{t_{\ast}} \leq \frac{1}{2s(G)} \exp\Bigl(-\frac{\phi_{\ast}^2 t_{\ast}}{8}\Bigr) \leq \frac{1}{18}.
 	\end{equation*}
-be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$, and additionally let
-\begin{equation*}
-C(K_0;h^{(\alpha)}) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
-\end{equation*}
-where we use the notation $\overline{k} := \min\{k, 2m - k\}$.
-
-As a sanity check, we confirm that Theorem~\ref{lem:mixing_time_PPR} is no weaker than Theorem~3 of \citet{andersen2006}.
-It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0;h^{(\alpha)}) \leq 1$ for any $K_0$.
-Setting $K_0 = 0$ in Theorem~\ref{lem:mixing_time_PPR}, we therefore recover Theorem~3 of \citet{andersen2006}.
-
-We now proceed to identify when Theorem~\ref{lem:mixing_time_PPR} may offer some improvement on Theorem~3 of \citet{andersen2006}, by showing when we can upper bound $C(K_0) \ll 1$.
-
-Combining Theorem~\ref{lem:mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound_ppr}, we have the following result.
-
-We arrive now at the main result of this section.
-It is similar to Theorem 2 of \citet{andersen2006} but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR} in place of~\textcolor{red}{(?)}.
-To simplify notation, we will write the total mass placed by $p_v$ on a subset $S \subset V$ as $p_v(S) := \sum_{u \in S} p_v(u)$.
-\begin{theorem}
-	\label{lem:mixing_time_PPR_contrapositive}
-	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$.
-Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}}{2d_{\min}^2}$, and a set $S \subseteq V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$,  such that
-	\begin{equation}
-	\label{eqn:mixing_time_PPR_contrapositive_1}
-	p_v(S) - \frac{\vol(S;G)}{\vol(G)} > \delta.
-	\end{equation}
-	Then there exists a sweep cut $S_j$ of $p$, such that
-	\begin{equation*}
-	\Phi(S_j; G) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
-	\end{equation*}
-	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
-\end{theorem}
-\begin{proof}
-	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}.
-Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.
-
-	Now, letting
-	\begin{equation*}
-	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
-	\end{equation*}
-	we have that
-	\begin{equation*}
-	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
-	\end{equation*}
-	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
+	Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be the case $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem.
 \end{proof}
 
-\subsubsection{Improved Local Partitioning with PPR.}
-
-As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\wh{C};G)$.
-First, we restate a theorem of \citet{andersen2006} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.
-
-\begin{theorem}
-	\label{thm:acl_3}
-	For any set $C$ and any constant $\alpha$, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$, such that for any vertex $v \in C^g$, the PPR vector $p(v,\alpha;G)$ satisfies
-	\begin{equation*}
-	p(v,\alpha;G) \geq 1 - 6\frac{\Phi(C;G)}{\alpha}.
-	\end{equation*}
-\end{theorem}
-We are now in a position to prove Theorem~\ref{thm:conductance_ppr} by combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3}.
-
-\begin{proof}[Proof (of Theorem~\ref{thm:conductance_ppr})]
-	Since $\alpha \geq 60\Phi(C)$ and $v \in C^g$, by Theorem~\ref{thm:acl_3},
-	\begin{equation*}
-	p_v(C) \geq \frac{9}{10}.
-	\end{equation*}
-	This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p_v(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$.
-Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{lem:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$.
-Therefore, the minimum conductance sweep cut satisfies
-	\begin{equation*}
-	\min_{j = 1,\ldots,n} \Phi(S_j;G) \leq \sqrt{\frac{1120\cdot \Phi(C;G)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
-	\end{equation*}
-	Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
-	\begin{equation*}
-	\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
-	\end{equation*}
-	completing the proof of the theorem.
-\end{proof}
-
-\subsection{Uniform bounds on PPR}
-\label{subsec:ppr_uniform_bounds}
-\textcolor{red}{(TODO)}
-
 \section{Finite sample results}
-In this section, we prove high-probability finite-sample bounds on functionals of the random graph $G_{n,r}$.
+In this section, we prove high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, minimum and maximum degree, normalized cut, local spread, and conductance.
 To do so, we will need several different \textcolor{red}{(concentration inequalities)}, and we begin by reviewing these.

### 2021-01-03 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Completed fixed graph proofs.
Added proofs of convergence of random graph functionals.

@@
 \cite{andersen2006} show that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of the candidate cluster is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.
-\cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(C;G)$, defined as
+\cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
 \begin{equation}
 \label{eqn:conductance}
-\Psi(C;G) := \min_{S \subseteq C} \Phi(S;G[C]),
-\end{equation}
-where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$---and show that if $\Phi(C;G)$ is much smaller than $\Psi(C;G)^2$, then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
+\Psi(G) := \min_{S \subseteq V} \Phi(S;G),
+\end{equation}
+and show that if $\Phi(C;G)$ is much smaller than $\Psi(G[C])^2$---where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$--- then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
 Our own analysis will build on that of~\cite{zhu2013}, and we will give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
@@
 It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
-Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) = \Psi(\mc{C}[X];G_{n,r})$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
+Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) = \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
 For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
@@
 
-% In the context of PPR clustering on a fixed graph $G$ and candidate cluster $C$, \textcolor{red}{(Allen-Zhu 13)} provide the sharpest known bounds on the size of the symmetric set difference $\Delta(\wh{C},C)$.
-We build on these results in the statistical context, where the graph $G_{n,r}$ is a random neighborhood graph, formed over samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\Pbb$, and the candidate cluster $\mc{C} \subset \Rd$.
-
-%\begin{itemize}
-	%\item In Proposition~\ref{prop:sample_to_population}, we show that with high probability the empirical quantities $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{\mathbb{P},r}(\mc{C}[X])$ are close to their population-level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
-As a consequence, in Theorem~\ref{thm:volume_ssd_ub} we show that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})$.
-These give the first population-level guarantees for PPR clustering in a non-parametric statistical context.
-%\end{itemize}
-
-%We specialize to the case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$ (an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}).
-%\begin{itemize}
-%	\item In Propositions~\ref{prop:density_cluster_normalized_cut} and~\ref{prop:density_cluster_conductance}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$; these upper bounds depend on $\lambda$ as well as some other natural parameters.
-These immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Corollary~\ref{cor:density_cluster_volume_ssd_ub}),  giving new connections between (local) spectral and density clustering.
-%	\item We introduce a notion of \emph{density cluster consistency}.
-In Theorem~\ref{thm:density_cluster_consistent_recovery}, we give conditions under which $\wh{C}$ is a consistent estimate of the density cluster $\mc{C}_{\lambda}$.
-%	\item In Theorem~\ref{thm:ppr_density_cluster_lb} we give a lower bound: we exhibit a hard class of densities $\mc{F}$ and corresponding density clusters $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ will be provably large.
-% \end{itemize}
-
 \section{Upper bound on the symmetric set difference metric}
@@
 \subsection{PPR cluster recovery: the fixed graph case.}
-
+\label{subsec:ppr_cluster_recovery_fixed_graph}
 When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$.
@@
 
-In their most general form, the results of~\citet{zhu2013} depend on the mixing time of a lazy random walk over the induced subgraph $G[C] = (C, E \cap (C \times C))$. Letting 
-$W_C$ be the lazy random walk matrix over $G[C]$, we write  
-\begin{equation*}
-q_{v}^{(t)}(u) = e_vW_C^t e_u
-\end{equation*}
-for the probability that after $t$-steps, the lazy random walk originating at $v$ arrives at $u$.
-Assuming $G[C]$ is a connected graph, the random walk with transition probabilities given by $W_C$ is an irreducible and aperiodic Markov Chain; thus a unique stationary distribution exists and is given by \smash{$\pi_C(u) := \deg(u;G[C])/\vol(C;
-	G[C])$}, where we write $\deg(u;G[C]) = \sum_{w \in C} \1\{(u,w) \in E_C\}$ for
-the degree of $u$ in $G[C]$. The \emph{mixing time} over $G[C]$ is then
+In their most general form, the results of~\citet{zhu2013} depend on the mixing time of a lazy random walk over the induced subgraph $G[C]$.
+The \emph{mixing time} of a lazy random walk over a graph $G$ is
 \begin{equation}
 \label{eqn:mixing_time}
-\tau_{\infty}(C;G) := \min\set{ t: \frac{\pi_C(u) - q_{v}^{(t)}(u)}
-	{\pi_C(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in C$}}
-\end{equation}
+\tau_{\infty}(G) := \min\set{ t: \frac{{\pi}(u) - {q}_{v}^{(t)}(u)}
+	{{\pi}(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in V$}},
+\end{equation}
+where $q_v^{(t)} = e_v W^t$ is the distribution of a lazy random walk starting at node $v$ and running for $t$ steps, and $\pi = \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
 \begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
@@
 	\label{eqn:zhu_condition}
-	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(C;G)}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}
+	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}
 	\end{equation}
@@
 \end{lemma}
-The upper bound in~\eqref{eqn:zhu_ub} does not obviously depend on the conductance $\Psi(C;G)$.
-However, as \cite{zhu2013} point out, letting $\pi_{\min}(C;G) := \min_{u \in C}\{\pi_C(u)\}$ denote the minimum stationary probability over $C$, it follows from Cheeger's inequality~\citep{chung1997} that
+The upper bound in~\eqref{eqn:zhu_ub} does not obviously depend on the conductance $\Psi(G[C])$.
+However, as \cite{zhu2013} point out, letting $\pi_{\min}(G) := \min_{u \in V}\{\pi(u)\}$, it follows from Cheeger's inequality~\citep{chung1997} that
 \begin{equation}
 \label{eqn:mixing_time_cheeger}
-\tau_{\infty}(C;G) \leq \frac{\log(1/\pi_{\min}(C;G))}{\Psi(C;G)^2}.
-\end{equation}
-Therefore, setting (for instance) $\alpha = \frac{\Psi(C;G)^2}{2\log(1/\pi_{\min}(C;G))}$ and $\wh{C} = S_{\beta_0,v}$ for $\beta_0 = \frac{1}{5 \vol(C;G)}$, we obtain from~\eqref{eqn:zhu_ub} that 
+\tau_{\infty}(G) \leq \frac{\log(1/\pi_{\min}(G))}{\Psi(G)^2}.
+\end{equation}
+Therefore, setting (for instance) $\alpha = \frac{\Psi(G[C])^2}{2\log(1/\pi_{\min}(G))}$ and $\wh{C} = S_{\beta_0,v}$ for $\beta_0 = \frac{1}{5 \vol(C;G)}$, we obtain from~\eqref{eqn:zhu_ub} that 
 \begin{equation}
 \label{eqn:zhu_ub2}
-\frac{\vol(C \vartriangle \wh{C};G)}{\vol(C; G)} \leq 60\frac{\Phi(C;G) \log\bigl( 1/\pi_{\min}(G[C])\bigr)}{\Psi(C;G)^2}.
+\frac{\vol(C \vartriangle \wh{C};G)}{\vol(C; G)} \leq 60\frac{\Phi(C;G) \log\bigl( 1/\pi_{\min}(G[C])\bigr)}{\Psi(G[C])^2}.
 \end{equation}
@@
 Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Phi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}(\mc{C}[X];G_{n,r}) \lesssim 1/n$.
-Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a rate of at least $\log n$, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.\footnote{To be clear: $\pi_{\min}(G)$ is obviously at most $1/n$ for any graph $G$ with $n$ total vertices, not merely $G = G_{n,r}$.
-However, while in general it is certainly possible that $\Phi(C;G) \leq \frac{1}{\log(n)} \Psi(C;G)$, this will not be the case in our specific setting, where $G = G_{n,r}$ and $C = \mc{C}[X]$.
+Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \lesssim 1/n$.
+Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a rate of at least $\log n$, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.\footnote{To be clear: $\pi_{\min}(G)$ is obviously at most $1/|V|$ for any graph $G$ with $|V|$ total vertices, not merely $G_{n,r}\bigl[\mc{C}[X]\bigr]$.
+However, while in general it is certainly possible that $\Phi(C;G) \leq \frac{1}{\log(n)} \Psi(G[C])$, this will not be the case in our specific setting, where $G = G_{n,r}$ and $C = \mc{C}[X]$.
 Hence the need for a sharper bound.}
@@
 To fix this, we will improve the bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
-While in the worst case (over the input graph $G$) the ``start penalty'' $\log(1/\pi_{\min}(C;G))$ is unavoidable, fortunately better bounds are possible when $G$ is a geometric graph such as $G_{n,r}$.
-Intuitively, this is because in geometric graphs, small sets are expanders---that is, if a set $R \subseteq V$ has sufficiently small volume, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(V; G)$.
-As a consequence, a random walk over $G$ should rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' as if the random walk were given a warm start over a larger set $S$.
-To delineate small sets $R$ from larger sets $S$, we introduce the \emph{local spread} functional $s(C; G)$, defined as\footnote{The prefactor $9/10$ in the definition of $s(G)$ is arbitrary.
-It can be altered to any constant less than $1$, and Proposition~\ref{prop:pointwise_mixing_time} will still hold after appropriate changes to the constants.}
+While in the worst case (over an arbitrary input graph $G$) a ``start penalty'' of $\log(1/\pi_{\min}(G))$ is unavoidable, fortunately better bounds are possible when $G$ is a geometric graph such as $G_{n,r}$.
+Intuitively, this is because in geometric graphs, small sets are expanders---that is, if a set $R \subseteq V$ has sufficiently small volume, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(G)$.
+As a consequence, a random walk over $G$ will rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' as if the random walk were given a warm start over a larger set $S$.
+To delineate small sets $R$ from larger sets $S$, we introduce the \emph{local spread} functional $s(G)$, defined as
 \begin{equation*}
-s(C; G) := \frac{9}{10} \cdot \min_{u \in C} \set{\deg(u; G[C])} \cdot \min_{u \in C} \set{\pi_C(u)}.
+s(G) := d_{\min}(G) \cdot \pi_{\min}(G),
 \end{equation*}
+where $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$.
+
 Using a careful analysis we can make the intuition of the prior paragraph rigorous, leading to an improved upper bound on mixing time in Proposition~\ref{prop:pointwise_mixing_time}.
@@
 	\label{prop:pointwise_mixing_time}
-	Assume $\min_{u \in V} \deg(u; G) \geq 10$. Then,
+	Assume $d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$. Then,
 	\begin{equation}
 	\label{eqn:pointwise_mixing_time}
-	\tau_{\infty}(C; G) \leq \frac{2}{\Psi^2(C; G)} \ln \left(\frac{320}{s(C; G)}\right)\log_2 \left(\frac{14}{s(C; G)}\right)  + 3 \log_2 \left(\frac{14}{s(C; G)}\right) + 3
+	\tau_{\infty}(G) \leq \frac{8}{\Psi^2(G)} \ln \left(\frac{4}{s(G)}\right)\log_2 \left(\frac{8}{s(G)}\right)  + 4\log_2 \left(\frac{8}{s(G)}\right) + 1.
 	\end{equation}
@@
 
-We emphasize that while Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the minimum degree is at least 10), it is particularly useful when $G$ is a geometric graph.
-We give a precise upper bound on $s(\mc{C}[X]; G_{n,r})$ in Proposition~\ref{prop:sample_to_population}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:mixing_time}.
+We emphasize that while Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
+We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:mixing_time}.
 
 \subsection{Sample-to-population results}
-In Proposition~\ref{prop:sample_to_population}, we establish high probability bounds on the sample normalized cut, conductance, and local spread, in terms of their population-level analogues.
-We have already introduced the population normalized cut~\eqref{eqn:population_normalized_cut} and conductance~\eqref{eqn:population_conductance}; writing $s_{n,r}(\mc{C}[X]) := s(\mc{C}[X];G_{n,r})$ for the sample local spread, we now define the population local spread to be
+\label{subsec:sample_to_population}
+\textcolor{red}{(TODO): Fix $\deg_{\min}$ notation, and fix Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}.}\\
+
+In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, local spread, and conductance, in terms of their population-level analogues.
+We have already introduced the population normalized cut~\eqref{eqn:population_normalized_cut} and conductance~\eqref{eqn:population_conductance}; denoting $s_{n,r}(\mc{C}[X]) := s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, we now define the population local spread to be
 \begin{equation}
 \label{eqn:local_spread}
-s_{\Pbb,r}(\mc{C}) := \frac{9}{10} \cdot \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
-\end{equation}
-where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $\wt{G}_{n,r} = G_{n,r}[\mc{C}[X]]$.
-
+s_{\Pbb,r}(\mc{C}) := \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
+\end{equation}
+where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $G_{n,r}\bigl[\mc{C}[X]\bigr]$.
+In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to constants that may depend on $\Pbb$ and $\mc{C}$, but do not depend on $n$ or $\delta$.
+We explicitly keep track of all constants in our proofs.
 \begin{proposition}
-	\label{prop:sample_to_population}
-	Fix $\delta \in (0,1)$. There exist universal constants $C_1$-$C_3$, and constants $b_1$,$b_2$ and $B_2$ that do not depend on $n$ or $\delta$, such that each of the following statements hold.
+	\label{prop:sample_to_population_1}
+	Fix $\delta \in (0,1/3)$. There exist positive constants $b_1$-$b_3$ such that each of the following statements hold.
 	\begin{itemize}
@@
 		\label{eqn:sample_to_population_normalized_cut}
-		\Phi_{n,r}(\mc{C}[X]) \leq (1 - C_1\delta) \Phi_{\Pbb,r}(\mc{C}[X]).
-		\end{equation}
-		\item With probability at least $1 - B_2n\exp\{-b_2\delta^2n\}$,
-		\begin{equation}
-		\label{eqn:sample_to_population_conductance}
-		\Psi_{n,r}(\mc{C}[X]) \geq (1 - C_2\delta) \Psi_{\Pbb,r}(\mc{C}[X]),
-		\end{equation}
-		and 
+		\Phi_{n,r}(\mc{C}[X]) \leq (1 + 3\delta) \Phi_{\Pbb,r}(\mc{C}).
+		\end{equation}
+		\item With probability at least $1 - 2\exp\{-b_2\delta^2n\} - n\exp\{-b_3\delta^2n\}$,
 		\begin{equation}
 		\label{eqn:sample_to_population_local_spread}
-		s_{n,r}(\mc{C}[X]) \geq (1 - C_3\delta) s_{\Pbb,r}(\mc{C}).
+		s_{n,r}(\mc{C}[X]) \geq (1 - 3\delta) s_{\Pbb,r}(\mc{C}).
 		\end{equation}
@@
 \end{proposition}
+To lower bound the sample conductance $\Psi_{n,r}(\mc{C}[X])$, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
+\begin{enumerate}[label=(A\arabic*)]
+	\item 
+	\label{asmp:domain} 
+	The candidate cluster $\mc{C} \subseteq \Rd$ for $d \geq 2$, is a bounded, connected, open set with Lipschitz boundary. 
+	\item 
+	\label{asmp:bounded_density} 
+	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ such that there exist $f_{\min} \leq 1 \leq f_{\max}$ for which
+	\begin{equation*}
+	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}.
+	\end{equation*}
+\end{enumerate}
+Let $p_d := 3/4$ if $d = 2$, and else $p_d := 1/d$ for $d \geq 3$. 
+\begin{proposition}
+	\label{prop:sample_to_population_2}
+	Fix $\delta \in (0,1/2)$.
+Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+Then there exist positive constants $B_1$, $B_2$ that do not depend on $n$ or $\delta$, such that for any $n \in \mathbb{N}$ for which
+	\begin{equation}
+	\label{eqn:sample_to_population_conductance_sample_complexity}
+	\frac{\log(n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,
+	\end{equation}
+	the following inequality holds with probability at least $1 - B_2/n - (n + 2)\exp\{-b_2n/\sqrt{2}\}$:
+	\begin{equation}
+	\label{eqn:sample_to_population_conductance}
+	\Psi_{n,r}(\mc{C}[X]) \geq (1 - 2\delta) \Psi_{\Pbb,r}(\mc{C}).
+	\end{equation}
+\end{proposition}
+
 A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Hoeffding's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X],\mc{C}^c[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
-To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $\min_{u \in C} \{\deg(u;\wt{G}_{n,r})\}$, but otherwise the proof is similarly straightforward.
+To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, but otherwise the proof is similarly straightforward.
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
@@
 
-\paragraph{Cluster recovery in symmetric set difference.} By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time} and~\ref{prop:sample_to_population}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
+\paragraph{Cluster recovery in symmetric set difference.} By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
 To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$ as
@@
 	\item
-	\label{asmp:bounded_density}
+	\label{asmp:lambda_bounded_density}
 	\emph{Bounded density within cluster:} There exist constants
@@
 	\label{lem:density_cluster_local_spread}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $L$. Then,
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $L$. Then,
 	\begin{equation}
@@
 	\label{prop:density_cluster_normalized_cut}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density},~\ref{asmp:low_noise_density} and~\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta$, and $\gamma$, and additionally that $0 < r \leq \frac{\sigma}{4d}$.
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density},~\ref{asmp:low_noise_density} and~\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta$, and $\gamma$, and additionally that $0 < r \leq \frac{\sigma}{4d}$.
 Then,
@@
 	\label{prop:density_cluster_conductance}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$. Then,
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$. Then,
 	\begin{equation}
@@
 	\label{cor:density_cluster_volume_ssd_ub}
-	Assume $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$, and that $0 < r \leq \sigma/4d$.
+	Assume $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$, and that $0 < r \leq \sigma/4d$.
 For any $\delta \in (0,1)$, with probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exist constants $C_{1,\delta}$ and $C_{2,\delta}$, and a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
@@
 However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, with spectral clustering functioning as more of a post-processing step.
-These methods are thus very different in spirit to PPR, which is a canonical local spectral clustering algorithm.
+These methods are thus very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
 	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population-level normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
@@
 \begin{equation*}
-\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
+\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:lambda_bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
 \end{equation*}
@@
 results of our upper bound in Corollary~\ref{cor:density_cluster_volume_ssd_ub} to the density $f$ given in \eqref{eqn:lb_density}.
-Observe that $\mc{C}^{(1)}$ satisfies each of the Assumptions~\ref{asmp:bounded_density}--\ref{asmp:bounded_volume}:
+Observe that $\mc{C}^{(1)}$ satisfies each of the Assumptions~\ref{asmp:lambda_bounded_density}--\ref{asmp:bounded_volume}:
 

### 2021-01-13 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex

@@
 
-In this section, we prove Theorem \ref{thm: volume_ssd}. The theorem is a consequence of Lemma 3.4 in \citet{zhu2013}, which relates the quality of the PPR output to normalized cut and mixing time. 
-\begin{lemma}[Lemma 3.4 of \citet{zhu2013}.]
+In this section, we prove Theorem \ref{thm: volume_ssd}.
+To do so, we apply the following Lemma, which upper bounds the volume of the symmetric set difference in terms of normalized cut and mixing time on an arbitrary graph $G$.
+It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
+\begin{lemma}
 	\label{lem:zhu}
-	Let $G = (V,E)$ be a undirected, unweighted graph, let $A \subseteq V$, and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
+	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
 For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
 	\begin{equation*}
-	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}
-	\end{equation*} Suppose $\alpha \leq \frac{1}{9 \tau_{\infty}(G[S])}$,  $\varepsilon \leq \frac{1}{20\vol(A;G)}$.
-Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$ and $\beta \in \frac{1}{\vol(A;G)}(\frac{1}{100},\frac{2}{5})$ the sweep cut $S_{\beta,v}$ satisfies
-	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v};G) \leq \left(218\frac{\Phi(A;G)}{\alpha}\right) \vol(A;G)
+	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}.
+	\end{equation*} 
+	For some $A \subseteq V$, suppose that 
+	\begin{equation*}
+	\alpha \leq \min\Bigl\{\frac{1}{15}, \frac{1}{5\tau_{\infty}(G[A])}\Bigr\},~~ \beta, \varepsilon \leq \frac{1}{4\vol(A;G)}.
+	\end{equation*}
+	Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$, the sweep cut $S_{\beta,v}$ satisfies
+	\begin{equation*}
+	\vol(A \vartriangle S_{\beta,v};G) \leq \left(\frac{3}{\beta} + \frac{200}{9\vol(A;G)}\right) \frac{\Phi(A;G)}{\alpha}
 	\end{equation*}
 \end{lemma}
+\begin{proof}
+	We adopt the notation $\wt{p}_v$ for the (exact) PPR vector computed over the subgraph $G[A]$, and 
+	\begin{equation*}
+	\wt{\pi}(u) = \frac{\deg(u;G[A])}{\vol(A;G[A])}
+	\end{equation*}
+	for the stationary distribution of a random walk over $G[A]$.
+The proof of this Lemma proceeds along very similar lines to that of~\textcolor{red}{(Zhu 2013 Lemma 3.4)}.
+We directly use the following three inequalities, derived in that work:
+	\begin{itemize}
+		\item \textcolor{red}{(Zhu 2013 Lemma 3.2.)} For any seed node $v \in A$, the following inequalities hold for every $u \in A$:
+		\begin{equation}
+		\label{pf:zhu1}
+		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u)
+		\end{equation}
+		\item \textcolor{red}{(Zhu 2013 Corollary 3.3)} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
+		\begin{equation}
+		\label{pf:zhu2}
+		p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G),
+		\end{equation}
+		and $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
+		\item \textcolor{red}{(Zhu 2013 Lemma 3.1, Anderson 2007 Theorem 5.1)} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
+		\begin{equation}
+		\label{pf:zhu3}
+		\sum_{u \neq A} p_v(u) \leq 2\frac{\Phi(A;G)}{\alpha}.
+		\end{equation}
+	\end{itemize}
+	From~\eqref{pf:zhu1}-\eqref{pf:zhu3}, we can upper bound the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
+First of all, observe that any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$.
+Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
+	\begin{equation}
+	\label{pf:zhu3.5}
+	\vol(S_{\beta,v} \setminus A; G) \leq \frac{1}{\beta} \sum_{u \not\in A}p_v^{(\varepsilon)}(u) \leq 2\frac{\Phi(A;G)}{\beta \cdot \alpha}.
+	\end{equation} 
+	Next, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$ for any $u \in A$:
+	\begin{equation*}
+	p_v^{(\varepsilon)}(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G).
+	\end{equation*}
+	If additionally $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
+	\begin{equation}
+	\label{pf:zhu4}
+	\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr)\wt{\pi}(u) - (\varepsilon + \beta)\deg(u;G) \leq \wt{p}_{\ell}(u).
+	\end{equation}
+	Let us restrict our attention for the moment to those vertices $u \in A$ with sufficiently large degree in $G[A]$. Defining
+	\begin{equation*}
+	A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\},
+	\end{equation*}
+	we note that for any $u \in A^{\mathrm{int}}$,
+	\begin{equation*}
+	\wt{\pi}(u) > \frac{(1 - \alpha \beta \vol(A;G))\deg(u;G)}{\vol(A;G)},
+	\end{equation*}
+	plugging this in to~\eqref{pf:zhu4}, we have that
+	\begin{equation*}
+	\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u)
+	\end{equation*}
+	for any $u \in A^{\mathrm{int}} \setminus S_{\beta,v}$. Summing over all such u, we obtain
+	\begin{equation*}
+	\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \sum_{u \in A^{\mathrm{int}} \setminus S_{\beta,v}} \wt{p}_{\ell}(u) \leq 2\frac{\Phi(A;G)}{\alpha}
+	\end{equation*}
+	where the second upper bound follows from the upper bound on $\|\ell\|_1$, since $\sum_{u \in A} \wt{p}_{\ell}(u) = \|\ell\|_1$. 
+	Then, from the assumed upper bounds on $\alpha, \beta$ and $\varepsilon$ we obtain the inequality
+	\begin{equation*}
+	\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{9}{100\vol(A;G)}.
+	\end{equation*}
+	We conclude that
+	\begin{equation}
+	\label{pf:zhu5}
+	\vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{200\Phi(A;G)}{9\alpha}.
+	\end{equation}
+	Otherwise $u \in A \setminus A^{\mathrm{int}}$, and so $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$. Summing over all such vertices, we obtain
+	\begin{equation}
+	\label{pf:zhu6}
+	\vol(A \setminus A^{\mathrm{int}};G) \leq \frac{\Phi(A;G)}{\alpha \cdot \beta}.
+	\end{equation} 
+	The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\ref{pf:zhu6}.
+	\end{proof}
 

### 2021-01-13 jmlr/revision/proofs.tex

@@
 \newcommand{\vol}{\mathrm{vol}}
+\newcommand{\cut}{\mathrm{cut}}
 \newcommand{\spansp}{\mathrm{span}~}
@@
 \newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\mbb}[1]{\mathbb{#1}}
 
@@
 	\end{equation*}
-	Thus, as long as $u_{(j + 1)} \neq v$ we have from~\eqref{pf:interpolator_bound_max_entry} that---for either $q = q_v^{(t)}$ or $q = p_v$---the inequality $h_{q}'(k_j) \leq 1/(d_{\min}(G)^2)$ holds.
-The statement of~\eqref{eqn:right_derivative_1} guarantees that $u_{(j + 1)} \neq v$.
-
-	On the other hand, the inequality \eqref{eqn:right_derivative_2} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since for any $K \in [0,m]$, taking $j$ so that $2m - K \in [k_j, k_{j + 1})$,
-	\begin{equation*}
-	h'(2m - K) \geq -\frac{\pi(u_{(j+1)})}{\mathrm{deg}(u_{(j + 1)};G)} \geq -\frac{d_{\max}(G)}{d_{\min}(G) \cdot \vol(G)}.
+	We have chosen $K_0 = k_j$ so that $v \neq u_{(j + 1)}$, and so~\eqref{pf:interpolator_bound_max_entry} implies that $h_{q}'(k_j) \leq 1/(d_{\min}(G)^2)$, for either $q = q_v^{(t)}$ or $q = p_v$.
+
+	On the other hand, the inequality \eqref{eqn:right_derivative_2} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since for any $K_0 \in [0,m]$, taking $j$ so that $2m - K_0 \in [k_j, k_{j + 1})$,
+	\begin{equation*}
+	h'(2m - K_0) \geq -\frac{\pi(u_{(j+1)})}{\mathrm{deg}(u_{(j + 1)};G)} \geq -\frac{d_{\max}(G)}{d_{\min}(G) \cdot \vol(G)}.
 	\end{equation*}
@@
 	\end{equation*}
-	Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be the case $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem.
+	Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be that $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem.
 \end{proof}
 
-\section{Finite sample results}
-In this section, we prove high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, minimum and maximum degree, normalized cut, local spread, and conductance.
-To do so, we will need several different \textcolor{red}{(concentration inequalities)}, and we begin by reviewing these.
-
-\subsection{Concentration inequalities}
-\textcolor{red}{(TODO)}
+\section{Sample-to-population bounds}
+\label{sec:sample_to_population}
+In this section, we prove Proposition~\ref{prop:sample_to_population_1}, by establishing high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, and normalized cut~(\ref{subsec:sample_to_population_ncut}), minimum and maximum degree, and local spread~(\ref{subsec:sample_to_population_local_spread}), and conductance~(\ref{subsec:sample_to_population_conductance}).
+To establish these results, we will use several different concentration inequalities, and we begin by reviewing these in~(\ref{subsec:concentration}).
+Throughout, we denote the empirical probability of a set $\mc{S} \subseteq \Rd$ as $\Pbb_n(\mc{S}) = \sum_{i = 1}^{n} \1\{x_i \in \mc{S}\}/n$, and the conditional (on being in $\mc{C}$) empirical probability as $\wt{\Pbb}_n = \sum_{i = 1}^{n} \1\{x_i \in (\mc{S} \cap \mc{C})\}/\wt{n}$, where $\wt{n} = |\mc{C}[X]|$ is the number of sample points that are in $\mc{C}$.
+For a probability measure $\Qbb$, we also write
+\begin{equation*}
+d_{\min}(\Qbb) := \inf_{x \in \mathrm{supp}(\mbb{Q})} \deg_{\Pbb,r}(x),~~\textrm{and}~~d_{\max}(\Qbb) := \sup_{x \in \mathrm{supp}(\mbb{Q})} \deg_{\Pbb,r}(x).
+\end{equation*}
+
+\subsection{Review: concentration inequalities}
+\label{subsec:concentration}
+We use Hoeffding's inequality to control the deviations of the empirical measure of $\mc{S}$.
+\begin{lemma}[Hoeffding's Inequality.]
+	\label{lem:hoeffding_2}
+	Fix $\delta \in (0,1)$. For any measurable $\mc{S} \subseteq \Rd$,
+	\begin{equation*}
+	(1 - \delta) \Pbb(\mathcal{S}) \leq \Pbb_n(\mathcal{S}) \leq (1 + \delta)\Pbb(\mathcal{S})
+	\end{equation*}
+	with probability at least $1 - 2\exp\set{-2\delta^2(\Pbb(\mathcal{S}))^2n}$. 
+\end{lemma}
+
+Many graph functionals are order-2 U-statistics, and we use Hoeffding's inequality to control the deviations of these functionals from their expectations.
+Recall that $U_n$ is an order-2 U-statistic with kernel $\varphi: \Rd \times \Rd \to \Reals$ if
+\begin{equation*}
+U_n = \frac{1}{n(n-1)}\sum_{i = 1}^{n} \sum_{j \neq i} \varphi(x_i,x_j).
+\end{equation*}
+We write $\norm{\varphi}_{\infty} = \sup_{x,y} |\varphi(x,y)|$. 
+\begin{lemma}[Hoeffding's Inequality for U-statistics.]
+	\label{lem:hoeffding}
+	Fix $\delta \in (0,1)$. Assume $\norm{\varphi}_{\infty} \leq 1$. Then,
+	\begin{equation*}
+	(1 - \delta) \mathbb{E}[U_n] \leq U_n \leq (1 + \delta) \mathbb{E}[U_n]
+	\end{equation*}
+	with probability at least $1 - 2 \exp\left(-\delta^2 (\mathbb{E}[U_n])^2 n\right)$.
+\end{lemma}
+
+Finally, we use Lemma~\ref{lem:bernstein_union}---a combination of Bernstein's inequality and a union bound---to upper and lower bound $d_{\max}(G_{n,r})$ and $d_{\min}(G_{n,r})$.
+For measurable sets $\mc{S}_1,\ldots,\mc{S}_M$, we denote $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$
+\begin{lemma}[Bernstein's inequality + union bound.]
+	\label{lem:bernstein_union}
+	Fix $\delta \in (0,1)$. For any measurable $\mathcal{S}_1,\ldots,\mathcal{S}_M \subseteq \Rd$, 
+	\begin{equation*}
+	(1 - \delta) p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M}  \Pbb_n(\mathcal{A}_m) \leq (1 + \delta) p_{\max}
+	\end{equation*}
+	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.  
+\end{lemma}
+
+\subsection{Sample-to-population: normalized cut}
+\label{subsec:sample_to_population_ncut}
+In this subsection we establish~\eqref{eqn:sample_to_population_normalized_cut}.
+For a set $\mc{S} \subseteq \Rd$, both $\mathrm{cut}_{n,r}(\mc{S}[X])$ and $\mathrm{vol}_{n,r}(\mc{S}[X])$ are order-$2$ U-statistics:
+\begin{align*}
+\mathrm{cut}_{n,r}(\mc{S}[X]) & = \sum_{i = 1}^{n} \sum_{j \neq i} \1\{\|x_i - x_j\| \leq r\} \cdot \1\{x_i \in \mc{S}\} \cdot \1\{x_j \not\in \mc{S}\},
+\intertext{and}
+\mathrm{vol}_{n,r}(\mc{S}[X]) & = \sum_{i = 1}^{n} \sum_{j \neq i} \1\{\|x_i - x_j\| \leq r\} \cdot \1\{x_i \in \mc{S}\}.
+\end{align*}
+Therefore with probability at least $1 - \exp\{-\delta^2 \cut_{\Pbb,r}(\mc{S})\}$,
+\begin{equation*}
+\frac{1}{n(n - 1)} \mathrm{cut}_{n,r}(\mc{S}[X]) \leq (1 + \delta) \cut_{\Pbb,r}(\mc{S}),
+\end{equation*}
+and likewise with probability at least $1 - \exp\{-\delta^2 \vol_{\Pbb,r}(\mc{S})\}$,
+\begin{equation*}
+(1 - \delta) \vol_{\Pbb,r}(\mc{S}) \leq \frac{1}{n(n - 1)} \vol_{n,r}(\mc{S}[X]).
+\end{equation*}
+Consequently, for any $\delta \in (0,1/3)$,  
+\begin{equation*}
+\Phi_{n,r}(\mc{C}[X]) \leq \frac{1 + \delta}{1 - \delta} \frac{\cut_{\Pbb,r}(\mc{C})}{\min\{\vol_{\Pbb,r}(\mc{C}), \vol_{\Pbb,r}(\mc{C}^c)\}} = \frac{1 + \delta}{1 - \delta} \Phi_{\Pbb,r}(\mc{C}) \leq (1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{C})
+\end{equation*}
+with probability at least $1 - 3\exp\{-\delta^2 \cut_{\Pbb,r}(\mc{C})\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 = \cut_{\Pbb,r}(\mc{C})$ and $C_1 = 3$.
+
+\subsection{Sample-to-population: local spread}
+\label{subsec:sample_to_population_local_spread}
+In this subsection we establish~\eqref{eqn:sample_to_population_local_spread}.
+To ease the notational burden, let $\wt{G}_{n,r} := G_{n,r}\bigl[\mc{C}[X]\bigr]$.
+By Lemma~\ref{lem:hoeffding}, with probability at least $1 - \exp\{-2\delta^2 \Pbb(\mc{C})^2n\}$
+\begin{equation}
+\label{pf:sample_to_population_local_spread_1}
+\wt{n} \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}).
+\end{equation}
+Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-2(1 - \delta)\delta^2d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n\}$,
+\begin{equation}
+\label{pf:sample_to_population_local_spread_2}
+\frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq (1 - \delta) \cdot d_{\min}(\wt{\Pbb}),
+\end{equation}
+and likewise it follows from Lemma~\ref{lem:hoeffding_2} that with probability at least $1 - \exp\{-2\delta^2(1 - \delta) \vol_{\wt{\Pbb},r}(\mc{C})^2 \Pbb(\mc{C})n \}$,
+\begin{equation*}
+\frac{1}{\wt{n}(\wt{n} - 1)} \vol(\wt{G}_{n,r}) \geq (1 - \delta) \cdot \vol_{\wt{\Pbb},r}(\mc{C}).
+\end{equation*}
+Consequently, for any $\delta \in (0,1/3)$,
+\begin{equation*}
+s_{n,r}(\mc{C}[X]) = \frac{d_{\min}(\wt{G}_{n,r})^2}{\vol(\wt{G}_{n,r})} \geq \frac{\frac{1}{\wt{n}^2}d_{\min}(\wt{G}_{n,r})^2}{\frac{1}{\wt{n}(\wt{n} - 1)}\vol(\wt{G}_{n,r})} \geq \frac{(1 - \delta)^2}{(1 + \delta)} \frac{d_{\min}(\wt{\Pbb})^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{C}).
+\end{equation*}
+with probability at least $1 - 2\exp\bigl\{-\delta^2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})n\bigr\} - n\exp\bigl\{-\delta^2\bigl(d_{\min}(\wt{\Pbb})\bigr)^2 \Pbb(\mc{C}) n\bigr\}$.
+This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 = \bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})$, $b_3 = \bigl(d_{\min}(\wt{\Pbb})\bigr)^2 \Pbb(\mc{C})$, and $C_2 = 3$.
+
+\subsection{Sample-to-population: conductance}
+\label{subsec:sample_to_population_conductance}
+
+In this subsection we establish~\eqref{eqn:sample_to_population_conductance}.
+As mentioned in our main text, the proof of~\eqref{eqn:sample_to_population_conductance} relies on a high-probability upper bound of the $\infty$-transportation distance between $\mbb{P}$ and $\mbb{P}_n$, from~\citep{garciatrillos16b}.
+We begin by reviewing this upper bound, in Theorem~\ref{thm:garciatrillos16}.
+Subsequently in Proposition~\ref{prop:conductance_lb_transportation_distance}, we relate the $\infty$-transportation distance between two measures $\mbb{Q}_1$ and $\mbb{Q}_2$ to the difference of their conductances.
+Together these results will imply~\eqref{eqn:sample_to_population_conductance}.
+
+\paragraph{Review: $\infty$-transportation distance and transportation maps.}
+We give a brief review of some of the main ideas regarding $\infty$-transportation distance, and transportation maps.
+This discussion is largely taken from~\citep{garciatrillos16b,garciatrillos16}, and the reader should consult these works for more detail.
+
+For two measures $\mbb{Q}_1$ and $\mbb{Q}_2$ on a domain $D$, the \emph{$\infty$-transportation distance} $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$ is
+\begin{equation*}
+\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2) := \inf_{\gamma}\Bigl\{\mathrm{esssup}_{\gamma} \bigl\{|x - y|: (x,y) \in D \times D\bigr\}: \gamma \in \Gamma(\mbb{Q}_1,\mbb{Q}_2) \Bigr\}
+\end{equation*}
+where $\Gamma(\mbb{Q}_1,\mbb{Q}_2)$ is the set of all couplings of $\mbb{Q}_1$ and $\mbb{Q}_2$, that is the set of all probability measures on $D \times D$ for which the marginal distribution in the first variable is $\mbb{Q}_1$, and the marginal distribution in the second variable is $\mbb{Q}_2$.
+
+Suppose $\mbb{Q}_1$ is absolutely continuous with respect to the Lebesgue measure.
+Then $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$ can be more simply defined in terms of push-forward measures and transportation maps.
+For a Borel map $T: D \to D$, the \emph{push-forward} of $\mbb{Q}_1$ by $T$ is $T_{\sharp}\mbb{Q}_1$, defined for Borel sets $U$ as
+\begin{equation*}
+T_{\sharp}\mbb{Q}_1(U) = \mbb{Q}_1(T^{-1}(U)).
+\end{equation*}
+A \emph{transportation map} from $\mbb{Q}_1$ to $\mbb{Q}_2$ is a Borel map $T$ for which $T_{\sharp}\mbb{Q}_1 = \mbb{Q}_2$.
+Transportation maps satisfy two important properties.
+First, the transportation distance can be formulated in terms of transportation maps:
+\begin{equation*}
+\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2) = \inf_{T} \|\mathrm{Id} - T\|_{\Leb^{\infty}(\mbb{Q}_1)}
+\end{equation*}
+where $\mathrm{Id}: D \to D$ is the identity mapping, and the infimum is over transportation maps $T$ from $\mbb{Q}_1$ to $\mbb{Q}_2$.
+Second, they result in the following change of variables formula; if $T_{\sharp}\mbb{Q}_1 = \mbb{Q}_2$, then for any $g \in L^1(\mbb{Q}_2)$,
+\begin{equation}
+\label{eqn:transportation_map_change_of_variable}
+\int g(y) \,d\mbb{Q}_2(y) = \int g(T(x)) \,d\mbb{Q}_1(x).
+\end{equation}
+
+\paragraph{$\infty$-transportation distance between empirical and population measures.}
+Under mild regularity conditions, \cite{garciatrillos16b} upper bound the transportation distance $\Delta_{\infty}(\mbb{P},\mbb{P}_n)$. 
+\begin{enumerate}[label=(A\arabic*)]
+	\item 
+	\label{asmp:domain} 
+	The distribution $\Pbb$ is defined on a domain $D \subseteq \Rd$, which is a bounded, connected, open set with Lipschitz boundary. 
+	\item 
+	\label{asmp:bounded_density} 
+	The distribution $\Pbb$ has density $g: D \to (0,\infty)$ such that there exist $g_{\min} \leq 1 \leq g_{\max}$ for which
+	\begin{equation*}
+	(\forall x \in D)~~ g_{\min} \leq g(x) \leq g_{\max}
+	\end{equation*}
+\end{enumerate}
+\begin{theorem}[Theorem~1.1 of \cite{garciatrillos16}]
+	\label{thm:garciatrillos16}
+	Suppose $\Pbb$ satisfies~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+Then, there exists positive constants $B_{2}$ and $B_3$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
+	\begin{equation*}
+	\Delta_{\infty}(\mbb{P},\mbb{P}_n) \leq B_{3} \cdot 
+	\begin{dcases*}
+	\frac{\ln(n)^{3/4}}{n^{1/2}},&~~\textrm{if $d = 2$,} \\
+	\frac{\ln(n)^{1/d}}{n^{1/d}},&~~\textrm{if $d \geq 3$.}
+	\end{dcases*}
+	\end{equation*}
+\end{theorem}
+Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}, then Theorem~\ref{thm:garciatrillos16} applies to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use this upper bound on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
+
+\paragraph{Lower bound on conductance using transportation maps.}
+Let $\mbb{Q}_1$ and $\mbb{Q}_2$ be probability measures, with $\mbb{Q}_1$ absolutely continuous with respect to Lebesgue measure, and let $T$ be a transportation map from $\mbb{Q}_1$ to $\mbb{Q}_2$.
+We write $\Delta_T(\mbb{Q}_1,\mbb{Q}_2) := \|\mathrm{Id} - T\|_{\Leb^{\infty}(\mbb{Q}_1)}$.
+To facilitate easy comparison between the conductances of two arbitrary distributions, let $\Psi_r(\mbb{Q}) := \Psi_{\mbb{Q},r}(\mathrm{supp}(\mbb{Q}))$ for a distribution $\mbb{Q}$.
+In the following Proposition, we lower bound $\Psi_r(\mbb{Q}_2)$ by $\Psi_r(\mbb{Q}_1)$, plus an error term that depends on $\Delta(\mbb{Q}_1,\mbb{Q}_2)$.
+\begin{proposition}
+	\label{prop:conductance_lb_transportation_distance}
+	Let $\mbb{Q}_1$ be a probability measure that admits a density $g$ with respect to $\nu(\cdot)$, let $\mbb{Q}_2$ be an arbitrary probability measure, and let $T$ be a transportation map from $\mbb{Q}_1$ to $\mbb{Q}_2$.
+Suppose $\Delta_T(\mbb{Q}_1,\mbb{Q}_2) \leq r/(4(d - 1))$.
+It follows that
+	\begin{equation}
+	\label{eqn:conductance_lb_transportation_distance}
+	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{2b_4\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{b_4 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
+	\end{equation}
+	where $b_4 := 2d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
+\end{proposition}
+We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$. 
+\begin{proof}[Proof (of Proposition~\ref{prop:conductance_lb_transportation_distance})]
+	Throughout this proof, we will write $\Delta_{12} = \Delta_T(\mbb{Q}_1,\mbb{Q}_2)$, and $\wb{\vol}_{\mbb{Q},r}(\mc{R}) = \min\bigl\{\vol_{\mbb{Q},r}\bigl(\mc{R}\bigr),\vol_{\mbb{Q},r}\bigl(\mc{R}^c\bigr)\bigr\}$ for conciseness.
+Naturally, the proof of Proposition~\ref{prop:conductance_lb_transportation_distance} involves using the transportation map $T$ to relate $\cut_{\mbb{Q}_2,r}(\cdot)$ to $\cut_{\mbb{Q}_1,r}(\cdot)$, and likewise $\vol_{\mbb{Q}_2,r}(\cdot)$ to $\vol_{\mbb{Q}_1,r}(\cdot)$.
+Define the remainder term $R_{\epsilon,\mbb{Q}_1}^{(\Delta)}(x) = \int \1\{\epsilon \leq \|x - y\| \leq \epsilon + \Delta\} \,d\mbb{Q}_1(y)$ for any $\epsilon, \Delta > 0$.
+Then for any set $\mc{S} \subseteq \mathrm{supp}(\mbb{Q}_2)$, we have that
+	\begin{align}
+	\cut_{\mbb{Q}_2,r}(\mc{S}) & = \iint \1\{\|x - y\|\leq r\} \cdot \1\{x \in \mc{S} \} \cdot \1\{y \in \mc{S}^c \} \,d\mbb{Q}_2(y) \,d\mbb{Q}_2(x) \nonumber \\ 
+	& \overset{\mathrm{(i)}}{=} \iint \1\{\|T(x) - T(y)\|\leq r\} \cdot \1\{x \in T^{-1}(\mc{S}) \} \cdot \1\{y \in T^{-1}(\mc{S})^c \} \,d\mbb{Q}_1(y) \,d\mbb{Q}_1(x) \nonumber \\
+	& \overset{\mathrm{(ii)}}{\geq} \iint \1\{\|x - y\|\leq r - 2\Delta_{12}\} \cdot \1\{x \in T^{-1}(\mc{S}) \} \cdot \1\{y \in T^{-1}(\mc{S}^c) \} \,d\mbb{Q}_1(y) \,d\mbb{Q}_1(x) \nonumber \\
+	& = \cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - \int R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \,d\mbb{Q}_1(x) \label{pf:conductance_lb_transportation_distance_1}
+	\end{align} 
+	where $\mathrm{(i)}$ follows from the change of variables formula~\eqref{eqn:transportation_map_change_of_variable}, and $\mathrm{(ii)}$ follows from the triangle inequality.
+Similar reasoning implies that
+	\begin{equation}
+	\label{pf:conductance_lb_transportation_distance_2}
+	\vol_{\mbb{Q}_2,r}(\mc{S}) \leq \vol_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) + \int R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x)  \,d\mbb{Q}_1(x).
+	\end{equation}
+	For any $x \in \Rd$, the remainder terms can be upper bounded: for any $\Delta_{12} \geq 0$,
+	\begin{equation*}
+	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{2 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= b_4} \cdot \Delta_{12},
+	\end{equation*}
+	and for any $0 \leq \Delta_{12} \leq r/(4(d - 1))$,
+	\begin{equation*}
+	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq 2 b_4 \cdot \Delta_{12}.
+	\end{equation*} 
+	Plugging these bounds on the remainder terms back into~\eqref{pf:conductance_lb_transportation_distance_1} and~\eqref{pf:conductance_lb_transportation_distance_2} respectively, we see that
+	\begin{align*}
+	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - b_4 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4\Delta_{12}}\biggr) - \frac{b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4\Delta_{12}} \\
+	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - 2b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
+	\end{align*}
+	We would like to conclude by taking an infimum over $\mc{S}$ on both sides, but in order to ensure that the remainder term is small we must specially handle the case where $\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})$ is small.
+Let
+	\begin{equation*}
+	\mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2) = \bigl\{\mc{S} \subseteq \mathrm{supp}(\mbb{Q}_2): \wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) \geq (1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2 \bigr\}.
+	\end{equation*}
+	On the one hand, taking an infimum over all sets $\mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)$, we have that
+	\begin{equation*}
+	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{2 b_4 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{b_4\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
+	\end{equation*}
+	On the other hand, we claim that 
+	\begin{equation}
+	\label{pf:conductance_lb_transportation_distance_3}
+	\Phi_{r,\mbb{Q}_2}(\mc{R}) \geq \Psi_{r}(\mbb{Q}_1),~~\textrm{for any $\mc{R} \not\in \mathfrak{L}(\mbb{Q}_1,\mbb{Q}_2)$}.
+	\end{equation}
+	To derive~\eqref{pf:conductance_lb_transportation_distance_3}, suppose that $\mc{R} \subseteq \mathrm{supp}(\mbb{Q}_2)$ and $\mc{R} \not\in \mathfrak{L}(\mbb{Q}_1,\mbb{Q}_2)$.
+Without loss of generality, we shall assume that $\vol_{\mbb{Q}_2,r}(\mc{R}) \leq (1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2$ (otherwise we can work with respect to $\mc{R}^c$.)  Then, for all $x \in \mc{R}$:
+	\begin{equation*}
+	\int \1\{\|x - y\| \leq r\}\cdot \1\{y \in \mc{R}^c\} \,d\mbb{Q}_2(y) \geq \deg_{\Qbb_2,r}(x) -  \mbb{Q}_2(\mc{R}) \geq \deg_{\Qbb_2,r}(x) - \frac{\vol_{\mbb{Q}_2,r}(\mc{R})}{d_{\min}(\mbb{Q}_2)} \geq d_{\min}(\mbb{Q}_2) \cdot \Psi_{r}(\mbb{Q}_2),
+	\end{equation*}
+	whence integrating over all $x \in \mc{R}$ and dividing by~$\vol_{\mbb{Q}_2,r}(\mc{R})$ yields~\eqref{pf:conductance_lb_transportation_distance_3}.
+This completes the proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.
+\end{proof}
+
+\paragraph{Putting the pieces together.} 
+First, we note that
+\begin{equation*}
+\Psi_r(\wt{\mbb{P}}) = \Psi_{\wt{\mbb{P}},r}(\mathrm{supp}(\wt{\mbb{P}})) = \Psi_{\Pbb,r}(\mc{C}), ~~\textrm{and}~~\Psi_{r}(\wt{\mbb{P}}_n) = \Psi_{\wt{\mbb{P}}_n, r}(\mathrm{supp}(\wt{\mbb{P}}_n)) = \Psi_{n,r}(\mc{C}[X]),
+\end{equation*}
+so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$.
+Next, as we have already derived in~\eqref{pf:sample_to_population_local_spread_2}, with probability at least $1 - \exp\{-\mbb{P}(\mc{C})^2n\} - \exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$,
+\begin{equation*}
+d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
+\end{equation*}
+Finally, taking
+\begin{equation*}
+b_5 := \frac{1}{2b_4}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := \frac{1}{B_4}\min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\}
+\end{equation*}
+by Theorem~\ref{thm:garciatrillos16} and~\eqref{eqn:sample_to_population_conductance_sample_complexity} we have that
+\begin{equation*}
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_3 \frac{\log(n)^{p_d}}{n^{1/d}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+\end{equation*}
+with probability at least $1 - B_2/n$. Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance},
+\begin{equation*}
+\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2b_4\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{b_4 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
+\end{equation*}
+with probability at least $1 - B_2/n - (n + 2)\exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$, establishing~\eqref{eqn:sample_to_population_conductance}.
 

### 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex

--- 2021-01-13 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex
@@
-\documentclass[11pt,twoside]{article}
-\usepackage[preprint]{jmlr2e}
-\usepackage{color}
-\usepackage{fancyhdr}
-\usepackage{amsfonts,epsfig,graphicx}
-\usepackage{afterpage}
-\usepackage{amsmath,amssymb} 
-% \usepackage{fullpage}
-\usepackage{epsf} 
-\usepackage{graphics} 
-\usepackage{amsfonts,amsmath}
-% \usepackage[sort,numbers]{natbib} 
-\usepackage{psfrag,xspace}
-\usepackage{color,etoolbox}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-6cm}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-4cm}
-\addtolength{\textheight}{-1.1\headheight}
-\addtolength{\textheight}{-\headsep}
-\addtolength{\textheight}{-\footskip}
-\setlength{\oddsidemargin}{0.5cm}
-\setlength{\evensidemargin}{0.5cm}
-\renewcommand{\floatpagefraction}{.8}%
-
-%\newtheorem{theorem}{Theorem} 
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
-%\newtheorem{remark}{Remark}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-\usepackage{microtype}
+\documentclass{report}
+\usepackage{amsmath}
+\usepackage{amsfonts, amsthm, amssymb}
 \usepackage{graphicx}
-\usepackage{float}
-\usepackage[export]{adjustbox}
-\usepackage{subcaption}
-\usepackage{booktabs}
-\usepackage{xcolor}
-%\usepackage{xr-hyper}
-%\usepackage{hyperref}
-%\usepackage[reqno]{amsmath}
-%\usepackage{amsfonts, amsthm, amssymb}
+\usepackage[colorlinks]{hyperref}
+\usepackage[parfill]{parskip}
+\usepackage{algpseudocode}
 \usepackage{algorithm}
-\usepackage{algorithmic}
-%\usepackage[parfill]{parskip}
 \usepackage{enumerate}
 \usepackage[shortlabels]{enumitem}
-\usepackage{bm}
+\usepackage{fullpage}
 \usepackage{mathtools}
-
-%%%%%% Begin Alden
-
-\newcommand{\diam}{\rho}
+\usepackage{subcaption}
+\usepackage{tikz}
+
+\usepackage{natbib}
+\renewcommand{\bibname}{REFERENCES}
+\renewcommand{\bibsection}{\subsubsection*{\bibname}}
+
+\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
+\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
+\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
+\DeclareMathAccent{\wb}{0}{mathx}{"73}
+
+\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
+
+\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
+\newcommand{\Graph}{\mathcal{G}}
+\newcommand{\Reals}{\mathbb{R}}
+\newcommand{\Identity}{\mathbb{I}}
+\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
+\newcommand{\convprob}{\overset{p}{\to}}
+\newcommand{\convdist}{\overset{w}{\to}}
+\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
+\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
+\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
+\newcommand{\iset}{\mathbf{i}}
+\newcommand{\jset}{\mathbf{j}}
+\newcommand{\myexp}[1]{\exp \{ #1 \}}
+\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
+\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
+\newcommand{\ext}[1]{\widetilde{#1}}
 \newcommand{\set}[1]{\left\{#1\right\}}
-\newcommand{\seq}[1]{\left\{#1\right\}_{n \in \mathbb{N}}}
-\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
+\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
+\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\Var}{\mathrm{Var}}
+\newcommand{\Cov}{\mathrm{Cov}}
+\newcommand{\Xsetiam}{\mathrm{diam}}
+
+\newcommand{\emC}{C_n}
+\newcommand{\emCpr}{C'_n}
+\newcommand{\emCthick}{C^{\sigma}_n}
+\newcommand{\emCprthick}{C'^{\sigma}_n}
+\newcommand{\emS}{S^{\sigma}_n}
+\newcommand{\estC}{\widehat{C}_n}
+\newcommand{\hC}{\hat{C^{\sigma}_n}}
 \newcommand{\vol}{\mathrm{vol}}
-\newcommand{\cut}{\mathrm{cut}}
-\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Reals}{\mathbb{R}}
+\newcommand{\spansp}{\mathrm{span}~}
+\newcommand{\1}{\mathbf{1}}
+
+\newcommand{\Linv}{L^{\Xsetagger}}
+\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\argmax}{argmax}
+
+\newcommand{\emF}{\mathbb{F}_n}
+\newcommand{\emG}{\mathbb{G}_n}
+\newcommand{\emP}{\mathbb{P}_n}
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\D}{\mathcal{D}}
+\newcommand{\R}{\mathcal{R}}
 \newcommand{\Rd}{\Reals^d}
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\usepackage{bbm}
-\newcommand{\1}{\mathbbm{1}}
-\newcommand{\Phibf}{\Phi_{u}}
-\newcommand{\Psibf}{\Psi_{u}}
-\newcommand{\taubf}{\tau_{u}}
+\newcommand{\Nbb}{\mathbb{N}}
+
+%%% Vectors
+\newcommand{\thetast}{\theta^{\star}}
+\newcommand{\betap}{\beta^{(p)}}
+\newcommand{\betaq}{\beta^{(q)}}
+\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
+
+%%% Matrices
+\newcommand{\X}{X} % no bold
+\newcommand{\Y}{Y} % no bold
+\newcommand{\Z}{Z} % no bold
+\newcommand{\Lgrid}{L_{\grid}}
+\newcommand{\Xsetgrid}{D_{\grid}}
+\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
+\newcommand{\Lap}{{\bf L}}
+\newcommand{\NLap}{{\bf N}}
+\newcommand{\PLap}{{\bf P}}
+
+%%% Sets and classes
+\newcommand{\Xset}{\mathcal{X}}
+\newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Hclass}{\mathcal{H}}
+\newcommand{\Pclass}{\mathcal{P}}
+\newcommand{\Leb}{L}
+\newcommand{\mc}[1]{\mathcal{#1}}
+
+%%% Distributions and related quantities
+\newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Ebb}{\mathbb{E}}
+\newcommand{\Qbb}{\mathbb{Q}}
+\newcommand{\Ibb}{\mathbb{I}}
+
+%%% Operators
+\newcommand{\Tadj}{T^{\star}}
+\newcommand{\Xsetive}{\mathrm{div}}
+\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
+\newcommand{\gradient}{\mathcal{D}}
+\newcommand{\Hessian}{\mathcal{D}^2}
+\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
+\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}
+
+%%% Misc
+\newcommand{\grid}{\mathrm{grid}}
+\newcommand{\critr}{R_n}
+\newcommand{\Xsetx}{\,dx}
+\newcommand{\Xsety}{\,dy}
+\newcommand{\Xsetr}{\,dr}
+\newcommand{\Xsetxpr}{\,dx'}
+\newcommand{\Xsetypr}{\,dy'}
+\newcommand{\wt}[1]{\widetilde{#1}}
+\newcommand{\wh}[1]{\widehat{#1}}
+\newcommand{\ol}[1]{\overline{#1}}
+\newcommand{\spec}{\mathrm{spec}}
+\newcommand{\LE}{\mathrm{LE}}
+\newcommand{\LS}{\mathrm{LS}}
+\newcommand{\OS}{\mathrm{OS}}
+\newcommand{\PLS}{\mathrm{PLS}}
 \newcommand{\dist}{\mathrm{dist}}
-\newcommand{\Err}{\mathrm{Err}}
-\newcommand{\TV}{\mathrm{TV}}
-
-%%% Vectors (no bold font)
-\newcommand{\pbf}{p}        % removed bold font
-\newcommand{\qbf}{q}
-\newcommand{\ebf}[1]{{e}_{#1}}
-\newcommand{\pibf}{\pi}
-
-%%% Matrices (no bold font)
-\newcommand{\Abf}{A}       % removed bold font 
-\newcommand{\Xbf}{X}             
-\newcommand{\Wbf}{W}
-\newcommand{\Lbf}{L}
-\newcommand{\Dbf}{D}
-\newcommand{\Ibf}[1]{I_{#1}}
-
-%%% Probability distributions (and related items)
-\newcommand{\Pbb}{\mathbb{P}}
-\newcommand{\Cbb}{\mathbb{C}}
-\newcommand{\Ebb}{\mathbb{E}}
-
-%%% Sets
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\Sset}{\mathcal{S}}
-\newcommand{\Cset}{\mathcal{C}}
-\newcommand{\Aset}{\mathcal{A}}
-\newcommand{\Asig}{\Aset_{\sigma}}
-\newcommand{\Csig}{\Cset_{\sigma}}
-\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
-\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}
-
-%%% Graph quantities
-\newcommand{\Cest}{\widehat{C}}
-\newcommand{\degminpr}{d_{\min}'}
-\newcommand{\degminwt}{\widetilde{d}_{\min}}
-\newcommand{\degmaxwt}{\widetilde{d}_{\max}}
-\newcommand{\degmax}{d_{\max}}
-\newcommand{\piminwt}{\widetilde{\pi}_{\min}}
-\newcommand{\piminpr}{\pibf_{\min}'}
-\newcommand{\degmin}{d_{\min}}
-
-%%% Operators
-\DeclareMathOperator*{\argmin}{arg\,min}
-\newcommand{\dx}{\,dx}
-\newcommand{\dy}{\,dy}
-\newcommand{\dt}{\,dt}
-
-%%% Algorithm notation
-\newcommand{\ppr}{{\sc PPR}}
-\newcommand{\pprspace}{{\sc PPR~}}
-
-%%% Tilde notation for quantities over the expansion set 
-\newcommand{\wt}[1]{\widetilde{#1}}
-\newcommand{\wn}{\widetilde{n}}
-\newcommand{\wX}{\widetilde{\Xbf}}
-\newcommand{\wx}{\widetilde{x}}
-\newcommand{\wz}{\widetilde{z}}
-\newcommand{\wbz}{\widetilde{\bf{z}}}
-\newcommand{\wu}{\widetilde{u}}
-\newcommand{\wPbb}{\widetilde{\Pbb}}
-\newcommand{\wf}{\widetilde{f}}
-\newcommand{\wDbf}{\widetilde{\Dbf}}
-\newcommand{\piwt}{\widetilde{\pi}}
-
-\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
-\newcommand{\ag}[1]{\textcolor{red}{#1}}
-
-%\newtheoremstyle{aldenthm}
-%{6pt} % Space above
-%{6pt} % Space below
-%{\itshape} % Body font
-%{} % Indent amount
-%{\bfseries} % Theorem head font
-%{.} % Punctuation after theorem head
-%{.5em} % Space after theorem head
-%{} % Theorem head spec (can be left empty, meaning `normal')
-
-%\theoremstyle{aldenthm}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{definition}{Definition}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-
-%\newtheoremstyle{aldenrmrk}
-%{6pt} % Space above
-%{6pt} % Space below
-%{} % Body font
-%{} % Indent amount
-%{\itshape} % Theorem head font
-%{.} % Punctuation after theorem head
-%{.5em} % Space after theorem head
-%{} % Theorem head spec (can be left empty, meaning `normal')
-%
-%\theoremstyle{aldenrmrk}
-%\newtheorem{remark}{Remark}
-%%%%%% End Alden
-
-%\title{Local Spectral Clustering of Density Upper Level Sets}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to break the
-% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
-% \AND instead of \And before the third author name.
-%
-%\author{
-%Alden Green \And
-%Sivaraman Balakrishnan \And
-%Ryan J. Tibshirani}
-%
-%\begin{document}
-%\maketitle
-%
-%\vspace{0.1in}
-%\begin{abstract}
-
-\newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
-\newcommand{\Like}{\ensuremath{\mathcal{L}}}
-\newcommand{\Ball}[2]{\mathbb{B}_{#1}(#2)}
-\newcommand{\Complement}[1]{\overline{#1}}
-
-\newcommand{\xsam}{\ensuremath{x}}
-\newcommand{\samind}{\ensuremath{\ell}}
-\newcommand{\Xrv}{\ensuremath{X}}
-\newcommand{\Event}{\ensuremath{\mathcal{E}}}
-\newcommand{\Fevent}{\ensuremath{\mathcal{F}}}
-
-\newcommand{\usedim}{\ensuremath{d}}
-\newcommand{\mubold}{\ensuremath{\boldsymbol{\mu}}}
-\newcommand{\lambold}{\ensuremath{\boldsymbol{\lambda}}}
-\newcommand{\sep}{\ensuremath{\xi}}
-\newcommand{\mixind}{\ensuremath{i}}
-\newcommand{\mixtwo}{\ensuremath{j}}
-\newcommand{\nummix}{\ensuremath{M}}
-\newcommand{\mustar}{\ensuremath{\mu^*}}
-\newcommand{\muboldstar}{\ensuremath{\mubold^*}}
-\newcommand{\muboldt}{\ensuremath{\mubold^t}}
-
-\newcommand{\numobs}{\ensuremath{n}}
-\newcommand{\SamLike}{\ensuremath{\Like_\numobs}}
-\newcommand{\PopLike}{\ensuremath{\Like}}
-\newcommand{\Exs}{\E}
-\newcommand{\thetanew}{\ensuremath{\theta^{\text{\small{new}} }}}
-
-\newcommand{\stepsize}{\ensuremath{s}}
-
-\newcommand{\QMAT}{\ensuremath{\mathbf{Q}}} 
-\newcommand{\DMAT}{\ensuremath{\mathbf{D}}}
-
-\newcommand{\defn}{\ensuremath{: \, =}}
-\newcommand{\muboldtilde}{\ensuremath{\tilde{\mubold}}}
-
-%%% New version of \caption puts things in smaller type, single-spaced 
-%%% and indents them to set them off more from the text.
-\makeatletter
-\long\def\@makecaption#1#2{
-        \vskip 0.8ex
-        \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
-        \parindent 1.5em  %% How can we use the global value of this???
-        \dimen0=\hsize
-        \advance\dimen0 by -3em
-        \ifdim \wd\@tempboxa >\dimen0
-                \hbox to \hsize{
-                        \parindent 0em
-                        \hfil 
-                        \parbox{\dimen0}{\def\baselinestretch{0.96}\small
-                                {\bf #1.} #2
-                                %%\unhbox\@tempboxa
-                                } 
-                        \hfil}
-        \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
-        \fi
-        }
-\makeatother
-
-\ShortHeadings{Local Spectral Clustering of Density Level Sets}{Green, Balakrishnan and Tibshirani}
-\firstpageno{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% Order of magnitude
+\newcommand{\soom}{\sim}
+
+% \newcommand{\span}{\textrm{span}}
+
+\newtheoremstyle{alden}
+{6pt} % Space above
+{6pt} % Space below
+{} % Body font
+{} % Indent amount
+{\bfseries} % Theorem head font
+{.} % Punctuation after theorem head
+{.5em} % Space after theorem head
+{} % Theorem head spec (can be left empty, meaning `normal')
+
+\theoremstyle{alden}
+
+\newtheoremstyle{aldenthm}
+{6pt} % Space above
+{6pt} % Space below
+{\itshape} % Body font
+{} % Indent amount
+{\bfseries} % Theorem head font
+{.} % Punctuation after theorem head
+{.5em} % Space after theorem head
+{} % Theorem head spec (can be left empty, meaning `normal')
+
+\theoremstyle{aldenthm}
+\newtheorem{theorem}{Theorem}
+\newtheorem{conjecture}{Conjecture}
+\newtheorem{lemma}{Lemma}
+\newtheorem{example}{Example}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+\newtheorem{assumption}{Assumption}
+\newtheorem{remark}{Remark}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+
+\theoremstyle{remark}
 
 \begin{document}
-
-\title{Local Spectral Clustering of Density Upper Level Sets}
-
-\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213
-	\AND
-	\name Sivaraman Balakrishnan \email sbalakri@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213
-	\AND
-	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213}
-
+\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
+\author{Alden Green}
+\date{\today}
 \maketitle
 
-\begin{abstract}
-We analyze the Personalized PageRank (PPR) algorithm, a local spectral method
-for clustering, which extracts clusters using locally-biased random walks around
-a given seed node.  In contrast to previous work, we adopt a classical
-statistical learning setup, where we obtain samples from an unknown
-distribution, and aim to identify connected regions of high-density (density
-clusters).  We prove that PPR, run on a neighborhood graph, extracts
-sufficiently salient density clusters, that satisfy a set of natural geometric
-conditions. We also show a converse result, that PPR can fail to recover
-geometrically poorly-conditioned density clusters, even asymptotically. Finally,
-we provide empirical support for our theory.
-\end{abstract}
-
-\begin{keywords}
-	graphs, spectral clustering, density clustering, Personalized PageRank, unsupervised learning
-\end{keywords}
-
-\section{Introduction}
-\label{sec: introduction}
-
-In this paper, we consider the problem of clustering: splitting a given data set
-into groups that satisfy some notion of within-group similarity and
-between-group difference.  Our particular focus is on spectral clustering
-methods, a family of powerful nonparametric clustering algorithms. Roughly
-speaking, a spectral algorithm first constructs a geometric graph $G$, where
-vertices correspond to samples, and edges correspond to proximities between
-samples. The algorithm then estimates a feature embedding based on (an
-appropriate) Laplacian matrix of $G$, and applies a simple clustering technique
-(like $k$-means clustering) in the embedded feature space.
-
-When applied to geometric graphs built from a large number of samples, global
-spectral clustering methods can be computationally cumbersome and insensitive to
-the local geometry of the underlying distribution
-\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
-\emph{local} spectral clustering algorithms, which leverage locally-biased
-spectra computed using random walks around some user-specified seed node.  A
-popular local clustering algorithm is the Personalized PageRank (PPR) algorithm,
-first introduced by \citet{haveliwala2003}, and then further developed by
-several others
-\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
-
-Local spectral clustering techniques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
-many authors to develop supporting theory
-\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
-guarantees on traditional graph-theoretic notions of cluster quality (such as
-conductance).  In this paper, we adopt a classical statistical viewpoint, and
-examine what the output of local clustering on a data set reveals about the
-underlying density $f$ of the samples.  In particular, we examine the ability of
-PPR to recover \emph{density clusters} of $f$, defined as the connected
-components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some
-$\lambda > 0$ (an object of central interest in the statistical clustering
-literature, dating back to the work of \citet{hartigan1981}).
-
-\section{Background and related work}
-
-We begin by providing some standard background on the PPR algorithm
-and the density clustering setup, before turning our attention to related work
-and a detailed summary of our contributions.
-
-\subsection{PPR on a neighborhood graph}
-
-Let $\Xbf = \{x_1,\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution
-$\Pbb$ on $\Rd$, with density $f$.  For a radius $r > 0$, we define
-$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $\Xbf$, an
-unweighted, undirected graph with vertices $V=\Xbf$, and an edge $(x_i,x_j) \in
-E$ if and only if $\norm{x_i - x_j} \leq r$, where $\norm{\cdot}$ is the
-Euclidean norm. We denote by $\Abf \in \Reals^{n \times n}$ the adjacency
-matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
-also denote by $\Dbf$ the diagonal degree matrix, with entries $\Dbf_{uu} :=
-\sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.
-
-First, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on 
-a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to
-be the solution of the following linear system:
-\begin{equation}
-\label{eqn: ppr_vector}
-\pbf_v = \alpha \ebf{v} + (1 - \alpha) \pbf_v \Wbf,
-\end{equation}
-where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over
-$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
-position $v$ and 0 elsewhere).
-
-%\subsubsection{Sweep cut}
-%\label{subsection: sweep_cut}
-Next, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$,
-for a given level $\beta > 0$, as    
-\begin{equation}
-\label{eqn: sweep_cuts}
-S_{\beta,v} := \set{u \in V: \frac{\pbf_v(u)}{\Dbf_{uu}} > \beta}.
-\end{equation}
-We will use the normalized cut metric to determine which sweep cut $S_{\beta}$
-is the best cluster estimate. For a set $S \subseteq V$ with complement $S^c = V
-\setminus S$, we define \smash{$\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c}
-\Abf_{uv}$}, and \smash{$\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$}.  We
-then define the \emph{normalized cut} of $S$ as
-\begin{equation}
-\label{eqn: normalized_cut}
-\Phi(S; G_{n,r}) := \frac{\cut(S;G_{n,r})}{\min \set{\vol(S; G_{n,r}), \vol(S^c; G_{n,r})}}.
-\end{equation}
-Having computed sweep cuts $S_{\beta}$ over \smash{$\beta \in (L, U)$} (where
-the range $(L,U)$ is user-specified), we output the cluster estimate
-\smash{$\Cest = S_{\beta^*}$} with minimum normalized cut.  For concreteness,
-the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.
-
-\begin{algorithm}
-\caption{PPR on a neighborhood graph}
-\label{alg: ppr}	
-{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, sweep cut range $(L,U)$. \\     
-{\bfseries Output:} cluster estimate $\Cest \subseteq V$.
-\begin{algorithmic}[1]
-  \STATE Form the neighborhood graph $G_{n,r}$.
-  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in
-  \eqref{eqn: ppr_vector}.  
-  \STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
-  \eqref{eqn: sweep_cuts}. 
-  \STATE Return the cluster \smash{$\Cest = S_{\beta^*}$}, where  
-  $$
-  \beta^* = \argmin_{\beta \in (L,U)}~ \Phi(S_{\beta}; G_{n,r}).
-  $$
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Estimation of density clusters}
-
-Let \smash{$\Cbb_f(\lambda)$} denote the connected components of the density
-upper level set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster
-\smash{$\Cset \in \Cbb_f(\lambda)$}, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the
-\emph{empirical density cluster}. The size of the symmetric set difference
-between estimated and empirical cluster is a commonly used metric to quantify
-cluster estimation error \citep{korostelev1993,polonik1995,rigollet2009}. We
-will consider a related metric, the volume of the symmetric set difference,
-which weights points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq \Xbf$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
-\begin{definition}
-  \label{def:volume_symmetric_set_difference}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and a set 
-  $\mathcal{S} \subseteq \Rd$, their symmetric set difference is 
-  $$
-  \Cest \vartriangle \mathcal{S}[\Xbf] :=
-    \bigl(\Cest \setminus \mathcal{S}[\Xbf]\bigr) \cup
-    \bigl(\mathcal{S}[\Xbf] \setminus \Cest\bigr).
-  $$
-  Furthermore, we denote the volume of the symmetric set difference by 
-  $$
-  \Delta(\Cest, \mathcal{S}[\Xbf]) := \vol_{n,r}(\Cest \vartriangle \mathcal{S}[\Xbf]). 
-  $$
-\end{definition}
-
-Note that the symmetric set difference does not measure whether \smash{$\Cest$}
-can (perfectly) distinguish any two distinct clusters \smash{$\Cset,\Cset' \in 
-  \Cbb_f(\lambda)$}. We therefore also study a second notion of cluster 
-estimation, first introduced by \citet{hartigan1981}, and defined
-asymptotically.
-
-\begin{definition}
-  \label{def: consistent_density_cluster_estimation}
-  For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster \smash{$\Cset \in
-    \Cbb_f(\lambda)$}, we call \smash{$\Cest$} \emph{consistent} for
-  \smash{$\Cset$} if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with  
-  \smash{$\Cset \not= \Cset'$}, the following holds as $n \to \infty$: 
-  \begin{equation}
-    \label{eqn: consistent_density_cluster_recovery}
-    \Cset[\Xbf] \subseteq \Cest \quad \text{and} \quad
-    \Cest \cap \Cset'[\Xbf] = \emptyset,
-  \end{equation}
-  with probability tending to 1.
-\end{definition}
-
-Consistent cluster recovery roughly ensures that, for a given 
-threshold $\lambda>0$, the estimated cluster \smash{$\Cest$} contains all points
-in a true density cluster $\Cset \in \Cbb_f(\lambda)$, and simultaneously does 
-not contain any points in any other density cluster $\Cset' \in
-\Cbb_f(\lambda)$.
-
-With these definitions in place, our broad goal will be to understand the extent
-to which the PPR algorithm is able to recover a cluster which either guarantees
-a low symmetric set difference to a true density cluster, or which consistently
-estimates a true density cluster.
-
-\subsection{Related work}
-
-In addition to the background on local spectral clustering given above, a
-few related lines of work are worth highlighting. In the stochastic block model
-(SBM), arguably one of the simplest models of network formation, edges between
-nodes independently occur with probability based on a latent community
-membership. In the SBM, the ability of spectral algorithms to perform
-clustering---or community detection---is well-understood, dating 
-back to \citet{mcsherry2001} who gives conditions under which the entire
-community structure can be recovered. In more recent work, \citet{rohe2011}
-upper bound the fraction of nodes misclassified by a spectral algorithm for the
-high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
-results to the sparse (low average degree) regime. Relatedly,
-\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
-when the block model exhibits some hierarchical structure. The framework we
-consider, in which nodes correspond to data points sampled from an underlying 
-density, and edges between nodes are formed based on geometric proximity, is
-quite different than the SBM, and therefore so is our analysis.
-
-In general, the study of spectral algorithms on neighborhood graphs has been
-focused on establishing asymptotic convergence of eigenvalues and eigenvectors
-of certain sample objects to the eigenvalues and eigenfunctions of corresponding
-limiting operators. \citet{koltchinskii2000} establish convergence of spectral
-projections of the adjacency matrix to a limiting integral operator, with
-similar results obtained using simplified proofs in
-\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
-the Laplacian matrix for a neighborhood of fixed radius. \citet{belkin07} and
-\citet{garciatrillos18} extend these results to the regime where the radius $r
-\to 0$ as $n \to \infty$.
-
-These results are of fundamental importance; however, the behavior of the
-spectra of these continuum operators can in general be hard to grasp. Therefore,
-further work relating this spectra to the geometry of the underlying
-distribution $\Pbb$ is of interest. In this spirit,
-\citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of spectral
-algorithms to recover the latent labels in certain geometrically
-well-conditioned nonparametric mixture models. Their results focus on global
-rather than local methods, and thus impose global rather than local conditions
-on the nature of the density. Moreover, they do not in general guarantee
-recovery of density clusters, which is the focus in our work. Perhaps most
-importantly, these works rely on general cluster saliency conditions, which
-implicitly depend on many distinct geometric aspects of the cluster $\Cset$
-under consideration. We make this dependence more explicit, and in doing so
-expose the role each geometric condition plays in the clustering problem.
-
-Our analysis naturally builds on a few of the aforementioned theoretical
-analyses of PPR. For an arbitrary graph $G$ and subset $S \subseteq G$,
-\citet{andersen2006} relate the quality of the PPR cluster \smash{$\Cest$} to
-the normalized cut functional $\Phi(S;G)$. While this analysis is tight in a
-worst-case sense, it fails to account for possible improvements when the cluster
-$S$ is additionally assumed to be internally well-connected, which is an
-intuitively more favorable case for clustering. Building on this intuition,  
-\citet{zhu2013} assume that the subgraph $G[S]$ is internally
-well-connected---as measured by a functional such as mixing time of a random
-walk over $G[S]$---and prove upper bounds on \smash{$\vol(\Cest \vartriangle
-  S;G)$}. Both of these analyses also hold with respect to an approximate form 
-of PPR  (aPPR), which can be efficiently computed.
-
-We apply these results to our setting by carefully analyzing the normalized cut
-and mixing time functionals in the particular case of $G = G_{n,r}$ and $S =
-\Cset[X]$. One of our main challenges is to prove an upper bound on the mixing 
-time of a random walk run only over the subset of nodes in $G_{n,r}$ which fall
-within a density cluster $\Cset$. To do so, we rely on a series of seminal works
-upper bounding the mixing time of \emph{geometric random walks} (see 
-\citet{vempala2005} for a comprehensive review.)  This study was initiated by
-\citet{dyer1991}, who used geometric random walks as a fundamental subroutine to
-efficiently compute volumes of high-dimensional convex bodies. These results are
-improved in \citet{lovasz1990,kannan97,kannan06}, who show, inter alia, that the
-bounds on mixing time can be sharpened by avoiding so-called
-``start-penalties''. As we discuss further in what follows, these improvements
-are crucial to our work. Following the work of
-\citet{abbasi-yadkori2016,abbasi-yadkori2016a}, we extend these results to hold
-for Lipschitz deformations of convex sets. Additionally, we relate the mixing
-time of these (continuous-space) geometric random walks to the mixing time of
-random walks over (discrete) neighborhood graphs.
-
-Finally, it is worth mentioning that density clustering and level set estimation
-are themselves very well-studied problems in statistics. \citet{polonik1995,
-  rigollet2009} study density clustering under the symmetric set difference
-metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
-estimators under Hausdorff loss and
-\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
-consistent estimation of the cluster tree. We emphasize that our goal is
-not to improve on these results, nor to offer a better algorithm for level set
-estimation; indeed, seen as a density clustering algorithm, PPR has none 
-of the optimality guarantees found in the aforementioned works. Instead, our
-motivation is to start with a widely-used local spectral method, PPR, and to
-better understand and characterize the distinctions between those density 
-clusters which are well-conditioned for PPR, and those which are not.
-
-\subsection{Summary of results}
-
-A summary of our results (and an outline for this paper) is as follows.
-
-\begin{enumerate}
-\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we introduce 
-  a set of natural geometric conditions on the density cluster $\Cset$
-  %formalize a measure of difficulty based on these geometric conditions, 
-  and show that if Algorithm~\ref{alg: ppr} is properly initialized, then the size of
-  the symmetric set difference between \smash{$\Cest$} and a thickened version
-  of the density cluster $\Csig$ can be bounded in a meaningful way based on the
-  geometric parameters.
-
-\item We further show in Section \ref{sec:
-    consistent_cluster_estimation_with_ppr} that if the density cluster  
-  $\Cset$ is particularly well-conditioned, then Algorithm~\ref{alg: ppr} 
-  will consistently estimate a density cluster in the strong sense of
-  \eqref{eqn: consistent_density_cluster_recovery}.
-
-\item In Section \ref{sec: analysis}, we detail some of the analysis required to 
-  prove our main results, and expose the roles that various geometric quantities 
-  play in the difficulty of the clustering problem.
-
-\item In Section \ref{sec:lower_bound}, we provide an accompanying lower bound,
-  which demonstrates that when the cluster $\Cset$ is sufficiently poorly
-  conditioned, it will not be recovered by Algorithm~\ref{alg: ppr}.
-
-\item In Section \ref{sec: experiments}, we empirically investigate the
-  tightness of our analysis, and provide examples showing how violations of our  
-  geometric conditions impact density cluster recovery by PPR.
-\end{enumerate}
-
-One of our main takeaways can be paraphrased as follows: PPR, run on a
-neighborhood graph, recovers only \emph{geometrically compact} high-density
-clusters. Our theoretical results make this takeaway precise, and provide a 
-concrete way of quantifying the geometric compactness of a density 
-cluster.
-
-\section{Main results}
-\label{sec: consistent_cluster_estimation_with_ppr}
-
-In this section, we present our main results on accuracy of the PPR algorithm
-for recovering density clusters.  We begin by formally introducing various
-geometric conditions, and use these to define a condition number
-$\kappa(\Cset)$, which measures the difficulty PPR will have in estimating a
-density cluster $\Cset$. With this condition in place our first main result
-(Theorem~\ref{thm: volume_ssd}) provides a bound on the symmetric set difference
-between the estimated cluster $\Cest$, obtained by an appropriately initialized 
-version of the PPR algorithm, and the target cluster $\Cset$.  Our next main
-result (Theorem~\ref{thm: consistent_recovery_of_density_clusters}) shows that
-for sufficiently well-conditioned target clusters $\Cset$, the output of the PPR
-algorithm $\Cest$ is consistent in the sense of Definition~\ref{def:
-consistent_density_cluster_estimation}.
-
-\subsection{Preliminaries}
-
-At a high level, for PPR to be successful, the underlying density cluster must
-be geometrically well-conditioned.  A basic requirement is that we need to avoid
-clusters which contain arbitrarily thin bridges or spikes. As in the work of
-\citet{chaudhuri2010}, we consider a thickened version of \smash{$\Cset \in
-\Cbb_f(\lambda)$} defined as $\Csig := \set{x \in \Reals^d: \dist(x,\Cset) \leq
-\sigma}$, which we call the \emph{$\sigma$-expansion} of $\Cset$. Here
-\smash{$\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$}.  We now list our
-conditions on $\Csig$.
-
-\begin{enumerate}[label=(A\arabic*)]
-\item
-  \label{asmp: bounded_density}
-  \emph{Bounded density within cluster:} There exist constants
-  $0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
-  $$
-  \lambda_{\sigma} \leq \inf_{x \in \Csig} f(x) \leq \sup_{x \in \Csig} f(x)
-  \leq \Lambda_{\sigma}.
-  $$
-
-\item 
-  \label{asmp: low_noise_density}
-  \emph{Low noise density:} There exists constants $c_0 > 0$ and $\gamma \in
-  [0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,     
-  $$
-  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \cdot \dist(x, \Csig)^{\gamma}.  
-  $$
-  Roughly, this assumption ensures that the density decays sufficiently quickly
-  as we move away from the target cluster $\Csig$, and is a standard assumption
-  in the level-set estimation literature (see for instance \citet{singh2009}).
-
-\item
-  \label{asmp: embedding}
-  \emph{Lipschitz embedding:}
-  There exists $g: \Reals^d \to \Reals^d$ with the following properties: 
-  \begin{enumerate}
-  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K}
-    \subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
-      \mathcal{K}}\norm{x - y} =: \diam < \infty$;
-  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is
-    the Jacobian of $g$ evaluated at $x;$ and 
-  \item for some $L \geq 1$,   
-    $$
-    \norm{g(x) - g(y)} \leq L \norm{x - y} ~
-    \text{for all $x,y \in \mathcal{K}$}. 
-    $$
-  \end{enumerate}
-  Succinctly, we assume that $\Csig$ is the image of a convex set with finite
-  diameter under a measure preserving, Lipschitz transformation.
-
-\item
-  \label{asmp: bounded_volume}
-  \emph{Bounded volume:}
-  For a set $\mathcal{S} \subseteq \Reals^d$, define a $\Pbb$-weighted volume of 
-  $\mathcal{S}$ to be  
-  \begin{equation}
-  \label{eqn:volume}
-  \vol_{\Pbb,r}(\mathcal{S}) := \int_{\mathcal{S}} \Pbb(B(x,r)) f(x) \, dx.
-  \end{equation}
-  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$. We assume
-  that the radius of the neighborhood graph $0 < r \leq \sigma/(2d)$ is chosen 
-  such that  
-  $$
-  \vol_{\Pbb,r}(\Cset_\sigma) \leq \frac{1}{2} \vol_{\Pbb,r}(\Reals^d). 
-  $$
-\end{enumerate}
-
-To motivate these conditions, we now give a brief high-level sketch
-of our analysis (which we will return to more formally in Section~\ref{sec:  
-  analysis}).  \citet{zhu2013} show that for an arbitrary graph $G = (V,E)$ and
-subset of vertices $S \subseteq V$, the PPR algorithm (properly initialized
-within $S$) will output an estimate \smash{$\Cest$} of $S$ satisfying, for a
-constant $M>0$, 
-\begin{equation}
-\label{eqn: graph_symmetric_set_difference_1}
-\vol(\Cest \vartriangle S; G) \leq M \cdot \Phi(S,G) \cdot \tau_{\infty}(G[S]),    
-\end{equation}
-where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
-  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is  the \emph{mixing
-  time} of a random walk over the induced subgraph $G[S]$ (to be defined
-precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
-\eqref{eqn: graph_symmetric_set_difference_1} is one of our principle metrics
-of interest, the volume of the symmetric set difference, and our main goal will 
-therefore be to upper bound the graph functionals $\Phi$ and $\tau_{\infty}$.
-Towards this goal, as we will show in Section
-\ref{sec: analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp: 
-  bounded_volume} allow us to upper bound the normalized cut 
-\smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
-\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Specifically, assumption 
-\ref{asmp: low_noise_density} yields an upper
-bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
-yields a lower bound on \smash{$\vol_{n,r}(\Csig[\Xbf])$}; together with 
-\ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
-the other hand, \ref{asmp: bounded_density} and \ref{asmp: embedding} preclude
-bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
-with the upper bound on diameter in \ref{asmp: embedding}, this leads to an upper bound on
-the mixing time over this subgraph.
-
-\subsubsection{Condition number}
-
-We will define the condition number $\kappa(\Cset)$ of a cluster $\Cset$ in 
-terms of a suitable upper bound---expressed in terms of the geometric parameters
-from \ref{asmp: bounded_density}--\ref{asmp: bounded_volume}---on the product of
-normalized cut and mixing time, \smash{$\Phi(\Csig[\Xbf]; G_{n,r}) \cdot
-  \tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}. Following \eqref{eqn:
-  graph_symmetric_set_difference_1}, we see that the smaller the condition
-number $\kappa(\Cset)$ is, the more success PPR will have in recovering the
-target $\Cset$.
-
-\textcolor{red}{Need to fix this definition: (1) the universal constants are not given in the Theorem statements, and (2) the definition of $\tau_u(\mc{C})$ has changed.}
-
-\begin{definition}
-  \label{def:well_conditioned_density_cluster}
-  For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy  
-  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma >
-  0$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later
-  (in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    mixing_time_upper_bound}), define
-  \begin{equation}
-    \label{eqn: condition_number}
-    \Phibf(\Cset) 
-    := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
-    \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma +
-        1})}{\lambda_{\sigma}}, \quad
-    \taubf(\Cset) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
-      L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c_3.
-  \end{equation}
-  Letting \smash{$\kappa(\Cset) := \Phibf(\Cset) \cdot \taubf(\Cset)$},
-  we call $\kappa(\Cset)$ the \emph{condition number} of $\Cset$.  We also call
-  the set $\Cset$ a \emph{$\kappa$-well-conditioned} density cluster.  
-\end{definition}
-
-The condition number $\kappa(\Cset)$ succinctly captures the role of the various 
-geometric parameters.  We note in passing that $\Phibf(\Cset)$ and
-$\taubf(\Cset)$ are exactly the upper bounds  on \smash{$\Phi(\Csig[\Xbf];
-  G_{n,r})$} and \smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in
-our analysis later, in Section \ref{sec: analysis}.
-
-\subsubsection{Well-initialized algorithm}
-
-As is typical in the local clustering literature, our algorithmic results will
-be stated with respect to specific ranges of each of the user-specified
-parameters. In particular, for a well-conditioned density cluster $\Cset$, we
-require that some of the tuning parameters of Algorithm~\ref{alg: ppr} are
-chosen to fall within specific ranges,
-
-\begin{equation}
-\begin{gathered}
-\label{eqn: initialization}
-0 < r \leq \frac{\sigma}{2d}, \quad 
-\alpha \in {\textstyle [\frac{1}{10}, \frac{1}{9})} \cdot
-\frac{1}{\taubf(\theta)}, \\ 
-(L,U) \subseteq {\textstyle(\frac{1}{50},\frac{1}{5})} \cdot 
-\frac{1}{2{n \choose 2} \vol_{\Pbb,r}(\Csig)}.  
-\end{gathered}
-\end{equation}
-
-\begin{definition}
-If the input parameters to Algorithm \ref{alg: ppr} satisfy \eqref{eqn:
-  initialization} (for some well-conditioned density cluster $\Cset$), then we  
-say the algorithm is \emph{well-initialized}. 
-\end{definition}
-
-In practice of course, it is not feasible to set tuning parameters based on the 
-underlying (unknown) density $f$. Typically, one runs PPR over some range of
-tuning parameter values and selects the cluster which has the smallest
-normalized cut.
-
-\subsection{Cluster recovery in symmetric set difference}
-
-We now present our first main result: a bound on the volume of the symmetric set
-difference between the estimated cluster \smash{$\Cest$} and empirical cluster 
-$\Csig[\Xbf]$. In this theorem, and hereafter, we let $c, c_i > 0$ denote
-universal constants, and $b,b_i > 0$ denote constants which may depend on  
-$\Pbb,\lambda,r,d$ and so on, but \emph{not} on the sample size 
-$n$.  % where possible, we keep track of all constants in our proofs.
-
-\textcolor{red}{Need to fix this Theorem.}
-
-\begin{theorem}
-  \label{thm: volume_ssd}
-  Fix $\lambda,\sigma > 0$, let \smash{$\Cset \in \Cbb_f(\lambda)$} be a   
-  $\kappa$-well-conditioned density cluster, and assume Algorithm \ref{alg: ppr}
-  is well-initialized with respect to $\Cset$. Then for any 
-  $$
-  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
-  $$
-  there exists a set $\Csig[\Xbf]^g 
-  \subseteq \Csig[\Xbf]$ of large volume, \smash{$\vol_{n,r}(\Csig[\Xbf]^g)
-    \geq \vol_{n,r}(\Csig[\Xbf])/2$}, such that the following holds: if 
-  Algorithm~\ref{alg: ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then
-  the PPR estimated cluster \smash{$\Cest$} satisfies
-  \begin{equation}
-    \label{eqn: volume_ssd}
-    \Delta(\Cest, \Csig[\Xbf]) \leq c \cdot \kappa(\Cset) \cdot
-    \vol_{n,r}(\Csig[\Xbf]),  
-  \end{equation}
-  with probability at least $1 - b_2/n$. 
-\end{theorem}
-
-The proof of Theorem \ref{thm: volume_ssd}, as with all results in this paper,
-is deferred to the appendix.  We reiterate that the primary technical 
-work involved in proving Theorem~\ref{thm: volume_ssd} involves showing that
-$\Phibf(\Cset)$ and $\taubf(\Cset)$ in \eqref{eqn: condition_number} are
-valid upper bounds on the normalized cut and mixing time; once this has been 
-established, the result follows more or less straightforwardly
-from \citet{zhu2013}.  
-% This result establishes that the volume of the symmetric
-% set difference \smash{$\Delta(\Cest, \Csig[\Xbf])$} is upper-bounded by a  
-% quantity proportional to the difficulty of the clustering problem, as measured 
-% by the condition number $\kappa(\Cset)$.
-
-\subsection{Consistent cluster recovery}
-
-The bound on symmetric set difference \eqref{eqn: volume_ssd} does not imply 
-consistent density cluster estimation in the sense of \eqref{eqn:
-  consistent_density_cluster_recovery}. This notion of consistency requires a
-uniform bound over the PPR vector $\pbf_v$: as an example, suppose that we were
-able to show that for all \smash{$\Cset' \in \Cbb_f(\lambda), \Cset' \neq
-  \Cset$}, and each $u \in \Cset, w \in \Cset'$,  
-\begin{equation}
-\label{eqn: ppr_gap}
-\frac{\pbf_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} <
-\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \frac{\pbf_v(u)}{D_{uu}}. 
-\end{equation}
-Then, any $(L,U)$ satisfying~\eqref{eqn: initialization} and any sweep cut
-$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
-\eqref{eqn: consistent_density_cluster_recovery}. In Theorem 
-\ref{thm: consistent_recovery_of_density_clusters}, we show that a sufficiently 
-small upper bound on $\kappa(\Cset)$ ensures that with high probability the
-uniform bound~\eqref{eqn: ppr_gap} is satisfied, and hence implies
-\smash{$\Cest$} will be a consistent  estimator. We will need one additional 
-regularity condition, to preclude arbitrarily low degree vertices for points $x
-\in \Cset'[\Xbf]$.
-
-\begin{enumerate}[label=(A\arabic*)]
-  \setcounter{enumi}{4}
-\item 
-  \label{asmp: C'_bounded_density}
-  \emph{Bounded density in other clusters:} Letting $\sigma,\lambda_{\sigma}$ be   
-  as in \ref{asmp: bounded_density}, for each $\Cset' \in \Cbb_f(\lambda)$ and
-  for all $x \in \Csig'$, it holds that $\lambda_{\sigma} \leq f(x)$. 
-\end{enumerate}
-
-Next we give our main result on consistent cluster recovery by PPR.
-
-\begin{theorem}
-  \label{thm: consistent_recovery_of_density_clusters}
-  Under the assumptions of Theorem \ref{thm: volume_ssd}, additionally assume 
-  \ref{asmp: C'_bounded_density}, and 
-  \begin{equation}
-    \label{eqn: kappa_ub}
-    \kappa(\Cset) \leq c \frac{(\lambda_{\sigma} r^d
-      \nu_d)^2}{\vol_{\Pbb,r}(\Csig)}.
-  \end{equation}
-  Then for any
-  $$
-  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
-  $$
-  there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, 
-  \smash{$\vol_{n,r}(\Csig[\Xbf]^g) \geq
-    \vol_{n,r}(\Csig[\Xbf])/2$}, such that if Algorithm~\ref{alg:
-    ppr} is run with any seed node $v \in \Csig[\Xbf]^g$, then the PPR estimated cluster \smash{$\Cest$} satisfies \eqref{eqn: consistent_density_cluster_recovery} with probability at least $1-b_2/n$.
-\end{theorem}
-
-Some remarks are in order.
-
-\begin{remark}
-We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn: kappa_ub} results in an upper bound on the symmetric set difference metric
-  \smash{$\Delta(\Cest, \Csig[\Xbf])$} on the order of $r^d$. In plain terms, we 
-  are able to recover a  density cluster $\Cset$ in the strong sense of
-  \eqref{eqn: consistent_density_cluster_recovery} only when we can guarantee a
-  very small fraction of points will be misclassified. This strong condition is
-  the price we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}.  
-\end{remark}
-
-\begin{remark}
-  Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to  
-  \infty$, would be computationally attractive (it would ensure that the graph 
-  $G_{n,r}$ is sparse), but the presence of a factor of \smash{$\log^2(1/r)/r$}
-  in $\kappa(\Cset)$ prevents us from making claims about the behavior of PPR in
-  this regime. Although the restriction to a kernel function fixed in $n$ is
-  common in spectral clustering theory \citep{schiebinger2015,vonluxburg2008},
-  it is an interesting question whether PPR exhibits some degeneracy over 
-  neighborhood graphs as $r \to 0$, or if this is merely looseness in our  
-  upper bounds.
-\end{remark}
-
-\subsection{Approximate PPR vector}
-
-In practice, exactly solving the system of equations~\eqref{eqn:
-  ppr_vector} to compute the PPR vector 
-  may be too computationally expensive. To address this limitation,
-\citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector
-(aPPR), which we will denote by \smash{$\pbf^{(\varepsilon)}$}. We refer the
-curious reader to \citet{andersen2006} for a formal algorithmic definition of
-the aPPR vector, and limit ourselves to highlighting a few salient points: the
-aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time,
-while satisfying the following uniform error bound: 
-\begin{equation}
-\label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad \pbf(u) - \varepsilon \Dbf_{uu}\leq
-\pbf^{(\varepsilon)}(u) \leq \pbf(u).  
-\end{equation}
-For a sufficiently small choice of $\varepsilon$, the 
-application of \eqref{eqn: appr_error} within the proofs of Theorems
-\ref{thm: volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters}  
-leads to analogous results which hold for \smash{$\pbf^{(\varepsilon)}$}.
-
-\begin{corollary}
-  \label{cor: appr}
-  Consider instead of
-  Algorithm \ref{alg: ppr} using the approximate PPR vector from
-  \citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
-  corresponding cluster estimate \smash{$\Cest$} in the same manner.  Then 
-  provided we take 
-  \begin{equation}
-    \label{eqn: appr_parameter}
-    \varepsilon = \frac{1}{25} \vol_{\Pbb,r}(\Csig),
-  \end{equation}
-  under the assumptions of Theorem~\ref{thm: volume_ssd} the upper bound on symmetric set difference in \eqref{eqn: volume_ssd} still
-  holds, and under the assumptions of Theorem \ref{thm: consistent_recovery_of_density_clusters} the set inclusion and disjointedness statements in \eqref{eqn: consistent_density_cluster_recovery} still hold, each with probability at least $1 - b_2/n$ (under possibly different choices of the constants $c_i$ and $b_i$).
-\end{corollary}
-
-\section{Analysis overview}
-\label{sec: analysis}
-
-The primary technical contribution in our work is to show that the
-geometric assumptions \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} 
-translate to  meaningful bounds on the normalized cut and mixing time of 
-$\Csig[\Xbf]$ in the neighborhood graph $G_{n,r}$. In doing so, we elucidate 
-how these geometric conditions contribute to the difficulty of the clustering 
-problem.
-
-\subsection{Upper bound on normalized cut}
-
-We start with a finite-sample upper bound on the normalized cut \eqref{eqn:
-  normalized_cut} of $\Cset_\sigma[\Xbf]$. For simplicity, we write
-$\Phi_{n,r}(\Csig[\Xbf]) := \Phi(\Csig[\Xbf]; G_{n,r})$.
-
-\begin{theorem}
-  \label{thm: conductance_upper_bound}
-  Fix $\lambda,\sigma>0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies    
-  Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and   
-  \ref{asmp: bounded_volume}. Then for any $\delta \in (0,1/2)$, it holds that
-  \begin{equation}
-    \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq (1 + 4\delta) c_1\frac{d}{\sigma}
-    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
-  \end{equation}
-  with probability at least $1 - 3\exp\set{-b n \delta^2}$. 
-\end{theorem}
-
-\begin{remark}
-  Observe that the diameter $\rho$ is absent from Theorem \ref{thm:
-    conductance_upper_bound}, in contrast to the ultimate bound in Theorem    
-  \ref{thm: volume_ssd} where the diameter enters through the condition number 
-  $\kappa(\Cset)$, which worsens (increases) as $\rho$ increases. This reflects
-  (what may be regarded as) established wisdom regarding spectral partitioning
-  algorithms more generally \citep{guattery1995, hein2010}, albeit newly applied
-  to the density clustering setting: if the diameter $\rho$ is large, then PPR
-  may fail to recover $\Csig[\Xbf]$ even when $\Cset$ is sufficiently
-  well-conditioned to ensure that $\Csig[\Xbf]$ has a small normalized cut in 
-  $G_{n,r}$. This will be supported by simulations in Section \ref{sec:
-    experiments}.   
-\end{remark}
-
-\subsection{Upper bound on mixing time}
-
-For $S \subseteq V$, denote by $G[S] = (S, E_S)$ the
-subgraph induced by $S$ (where $E_S = E \cap (S \times S)$). Let 
-$\Wbf_S$ be the lazy random walk matrix over $G[S]$, and write  
-$$
-q_{v}^{(t)}(u) = e_v\Wbf_S^t e_u
-$$
-for the $t$-step transition probability of the random walk over $G[S]$
-originating at $v \in V$. Also let \smash{$\pi = (\pi(u))_{u \in S}$} be 
-the stationary distribution of this random walk. (As $\Wbf_S$ is the transition 
-matrix of a lazy random walk, it is well-known that a unique stationary
-distribution exists and is given by  \smash{$\pi(u) = \deg(u;G[S])/\vol(S;
-  G[S])$}, where we write $\deg(u;G[S]) = \sum_{w \in S} \1((u,w) \in E_S)$ for
-the degree of $u$ in $G[S]$.) We define the \emph{mixing time} of $G[S]$ as 
-\begin{equation}
-\label{eqn: mixing_time}
-\tau_{\infty}(G[S]) = \min\set{ t: \frac{\pi(u) - q_{v}^{(t)}(u)}
-  {\pi(u)} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}. 
-\end{equation}
-Next, we give an asymptotic (in the number of samples $n$) upper bound on
-$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$.
-
-\begin{theorem}
-  \label{thm: mixing_time_upper_bound}
-  Fix $\lambda, \sigma > 0$, and assume \smash{$\Cset \in \Cbb_f(\lambda)$} 
-  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
-  Also assume that \smash{$0 < r \leq \sigma/(4d)$}. Then for any \smash{$\delta \in \bigl(0,1/(8 + 16/d)\bigr)$}, and any
-  $$
-  n \geq b_1 \cdot (1 + 4\delta) \cdot 
-  \begin{cases*}
-  \log(n)^{3/2},& ~~\textrm{if $d = 2$,} \\
-  \log(n),& ~~\textrm{if $d \neq 2$}
-  \end{cases*}
-  $$
-  the mixing time satisfies
-  \begin{align} 
-    \label{eqn: mixing_time_upper_bound}
-    \tau_{\infty}\bigl(G_{n,r}[\Csig[\Xbf]]\bigr) & \leq (1 + 40\delta) c_2 \frac{\Lambda_{\sigma}^4 d^3 
-      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr)\log\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + \\
-  &~~c_3\biggl((1 + 32\delta)d\log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + 1\biggr), 
-  \end{align}
-  with probability at least $1 - b_5/n - 4n\exp\{-\delta^2 b_2 n\}$.
-\end{theorem}
-The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
-analogous mixing time bounds developed for a continuous-space ``ball walk'' over
-convex sets. To the best of our knowledge, our result is the first bound on the
-mixing time of random walks over neighborhood graphs that is independent of $n$,
-the number of vertices.
-
-\begin{remark}
-  The embedding assumption \ref{asmp: embedding} and Lipschitz parameter $L$
-  play an important role in proving the upper bound in Theorem \ref{thm:
-    mixing_time_upper_bound}. There is some interdependence between $L$ and
-  $\sigma,\rho$, which might lead one to hope that \ref{asmp: embedding} is
-  non-essential. However, it is not possible to eliminate condition \ref{asmp:
-    embedding} without incurring an additional factor of at least
-  $(\rho/\sigma)^d$ in \eqref{eqn: mixing_time_upper_bound}, achieved, for
-  instance, when $\Csig$ is a dumbbell-like set consisting of two balls of
-  diameter $\rho$ linked by a cylinder of radius
-  $\sigma$. \citet{abbasi-yadkori2016, abbasi-yadkori2016a}  
-  develop theory regarding Lipschitz deformations of convex sets, wherein it
-  is observed that star-shaped sets as well as half-moon shapes of the type we
-  consider in Section \ref{sec: experiments} both satisfy \ref{asmp: embedding}
-  for reasonably small values of $L$. 
-\end{remark}
-
-\section{Negative result}
-\label{sec:lower_bound}
-
-In this section, we exhibit a hard case for density clustering using PPR, that 
-is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
-cluster. Let \smash{$\Cset^{(0)}, \Cset^{(1)}, \Cset^{(2)}$} be rectangles in
-$\Reals^2$,    
-$$
-\Cset^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times 
-\biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
-\Cset^{(1)} = \Cset^{(0)} - \set{(\sigma,0)}, \quad
-\Cset^{(2)} = \Cset^{(0)} + \set{(\sigma,0)},
-$$
-where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over
-\smash{$\mathcal{X} = \Cset^{(0)} \cup \Cset^{(1)} \cup \Cset^{(2)}$} given by   
-$$
-\Pbb = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 +
-\frac{\epsilon}{2} \Psi_0, 
-$$
-where $\Psi_k$ is the uniform distribution over $\Cset^{(k)}$ for $k = 0,1,2$.  
-The density function $f$ of $\Pbb$ is simply
-\begin{equation}
-\label{eqn:lb_density}
-f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in
-  \Cset^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \Cset^{(2)}) +
-  \frac{\epsilon}{2}\1(x \in \Cset^{(0)})  \right), 
-\end{equation}
-so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have 
-\smash{$\Cbb_f(\lambda) = \set{\Cset^{(1)}, \Cset^{(2)}}$}. Figure~\ref{fig:
-  hard_case} visualizes the density $f$ for two different choices of $\epsilon,
-\sigma, \rho$.
-
-% PUT FIGURE BACK HERE
-
-\subsection{Lower bound on symmetric set difference}
-
-As the following theorem demonstrates, even when Algorithm~\ref{alg: ppr} is
-reasonably initialized, if the density cluster \smash{$\Cset^{(1)}$} is 
-sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
-estimator $\Cest$ will fail to recover \smash{$\Cset^{(1)}$}. Let
-\begin{equation}
-\label{eqn:lower_set}
-\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
-\end{equation}
-
-\begin{theorem}
-  \label{thm:ppr_lb}
-  Assume Algorithm~\ref{alg: ppr} is initialized using inputs $r < 
-  \min\set{\frac{1}{40}\rho, \frac{1}{4}\sigma}$, $\alpha = 65  
-  \Phi_{\Pbb}(\mathcal{L})$, and $(L,U) = (0,1)$.  Then, for any 
-  $$
-  n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2},
-    \frac{8}{\epsilon}}, 
-  $$
-  there exists a set $\Cset[X]^g$ of large volume, \smash{$\vol_{n,r}(\Cset[X]^g \cap 
-    \Cset^{(1)}[\Xbf]) \geq \vol_{n,r}(\Cset^{(1)}[\Xbf];G_{n,r})/10$}, such
-  that for any seed node $v \in \Cset[X]^g$, the PPR estimated cluster
-  \smash{$\Cest$} satisfies    
-  \begin{equation}
-    \label{eqn:ppr_lb}
-    \frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle
-    \Cset^{(1)}[\Xbf]) \geq \frac{1}{4} -  c
-    \frac{\sqrt{\sigma/\rho}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}
-        {\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
-  \end{equation}
-  with probability at least $1 - b_1 n \exp\set{-b_2 n}$.  Consequently, if
-  $$
-  \epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ 
-    \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}, 
-  $$
-  then with high probability \smash{$\frac{\sigma
-    \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) 
-  \geq 1/8$}.    
-\end{theorem}
-
-Note that $\vol_{n,r}(\Cset^{(1)}[\Xbf])$ for large enough $n$ will be of the order
-$n^2 r^2/(\sigma\rho)$, and therefore the quantity \smash{$\frac{\sigma
-    \rho}{r^2 n^2} \cdot \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf])$} in 
-\eqref{eqn:ppr_lb} is comparable to \smash{$\vol_{n,r}(\Cest
-  \vartriangle \Cset^{(1)}[\Xbf]) / \vol_{n,r}(\Cset^{(1)}[\Xbf])$}, which
-corresponds to the quantity we upper bound in Theorem~\ref{thm: volume_ssd}.
-
-Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where
-the density clusters are rectangular subsets of $\Reals^2$.  We chose this
-setting to make the theorem simple to state, and our results are generalizable
-to $\Reals^d$ and to non-rectangular clusters.  Moreover, although we state
-our lower bound with respect to PPR run on a neighborhood graph, the conclusion is
-likely to hold for a much broader class of spectral clustering algorithms. In
-the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when
-$\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of
-$\Cset^{(1)}$ will be much larger than that of $\mathcal{L}$. In this case, not
-merely PPR but any algorithm that approximates the minimum normalized cut is
-unlikely to recover $\Cset^{(1)}$. In particular, local spectral clustering
-algorithms based on truncated random walks \citet{spielman2013}, global spectral
-clustering algorithms \citet{shi00}, and $p$-Laplacian based spectral embeddings
-\citet{hein2010} all have provable upper bounds on the normalized cut of cluster
-they output, and thus we expect that they would all fail to estimate
-$\Cset^{(1)}$.
-
-\subsection{Comparison \ag{between upper and lower bounds}.}
-
-To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
-results of our upper bound in Theorem~\ref{thm: volume_ssd} to the density $f$
-given in \eqref{eqn:lb_density}. Observe that $\Cset^{(1)}$ satisfies each of
-the Assumptions~\ref{asmp: bounded_density}--\ref{asmp: bounded_volume}:
-
-\begin{enumerate}[label=(A\arabic*)]
-\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
-  \Cset^{(1)}$.  
-\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such
-  that $0 < \dist(x,\Cset^{(1)}) \leq \sigma$. Therefore for all such $x$, 
-  $$
-  \inf_{x' \in \Cset^{(1)}} f(x') - f(x)  = \left\{\frac{1 - \epsilon}{2} -
-    \epsilon \right\} \frac{1}{\rho \sigma},
-  $$
-  which meets the decay requirement with exponent $\gamma=0$. 
-\item The set $\Cset^{(1)}$ is itself convex, and has diameter $\rho$.
-\item By symmetry, \smash{$\vol_{\Pbb,r}(\Cset^{(1)}) =
-    \vol_{\Pbb,r}(\Cset^{(2)})$}, and therefore
-  \smash{$\vol_{\Pbb,r}(\Cset^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$}.   
-\end{enumerate}
-
-\begin{remark}
-Technically, the rectangles $\Cset^{(0)},\Cset^{(1)},\Cset^{(2)}$ are not
-$\sigma$-expansions due to their sharp corners. To fix this, one can   
-%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume}
-%in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with
-%respect to rectangles of width $\sigma$, or  
-simply modify these sets to have appropriately rounded corners, and our lower
-bound arguments do not need to change significantly, subject to some
-additional bookkeeping.  Thus we ignore this technicality in our subsequent
-discussion. 
-\end{remark}
-
-If the user-specified parameters are initialized according to~\eqref{eqn:
-  initialization}, we may apply Theorem~\ref{thm: volume_ssd}. This implies that 
-there exists a set $\Cset^{(1)}[\Xbf] \subseteq \Cset^{(1)}$ with
-\smash{$\vol_{n,r}(\Cset[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Cset[\Xbf])$} such
-that for any seed node $v \in \Cset^{(1)}[\Xbf]$, and for large enough $n$, the
-PPR estimated cluster $\Cest$ satisfies with high probability
-$$
-\vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) \leq c \cdot
-\kappa(\Cset^{(1)}) \cdot \vol_{n,r}(\Cset^{(1)}[\Xbf]), 
-$$
-where the condition number may be taken to be
-$$
-\kappa(\Cset^{(1)}) = c_1 \frac{\epsilon}{\sigma} 
-\left(\frac{\rho^2}{r} \log^2\left(\frac{1}{r}\right) \right) + c_2. 
-$$
-for universal constants $c_1,c_2>0$. To facilitate comparisons between our upper
-and lower bounds, assume $\sigma/4 \leq \rho/40$ and set $r = \sigma/4$.  Then
-the following statements each hold with high probability.
-
-\begin{itemize}
-\item If the user-specified parameters satisfy~\eqref{eqn: initialization}, and
-  for some $c > 0$
-  $$
-  \epsilon < c \left(\frac{\sigma}{\rho \log(1/\sigma)}\right)^2,
-  $$
-  then \smash{$\Delta(\Cest, \Cset^{(1)}[\Xbf]) \leq c \cdot
-    \vol_{n,r}(\Cset^{(1)}[\Xbf])$}.
-
-\item If the user-specified parameters are as in Theorem~\ref{thm:ppr_lb},
-  and for some $c>0$
-  $$
-  \epsilon > c \left({\frac{\sigma}{\rho}} \log^2 \left(\frac{\rho}
-      {\epsilon^2 \sigma}\right)\right)^{1/4},
-  $$
-  then \smash{$\Delta(\Cest, \Cset^{(1)}[\Xbf]) \geq \frac{1}{8}
-    \vol_{n,r}(\Cset^{(1)}[\Xbf])$}. 
-\end{itemize}
-
-Jointly, these upper and lower bounds give a relatively precise characterization
-of what it means for a density cluster to be well- or poorly-geometrically
-conditioned for recovery using PPR.
-
-\begin{remark}
-It is worth pointing out that the above conclusions are reliant on specific
-(albeit reasonable) ranges and choices of input parameters, which in some
-instances differ between the upper and lower bounds. We suspect that our lower
-bound continues to hold even when choosing input parameters as dictated by our
-upper bound, but do not pursue the details.
-\end{remark}
-
-\begin{remark}
-It is not hard to show that, in the example under consideration, classical
-plug-in density cluster estimators can consistently recover the
-$\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even if $\epsilon$ is
-large compared to $\sigma/\rho$. That PPR has trouble recovering density
-clusters here (where standard plug-in approaches do not) is not meant to
-be a knock on PPR. Rather, it simply reflects that while classical density
-clustering approaches are specifically designed to identify high-density regions
-regardless of their geometry, PPR relies on geometry as well as density when
-forming the output cluster. 
-\end{remark}
-
-\section{Experiments}
-\label{sec: experiments}
-
-We provide numerical experiments to investigate the tightness of our bounds on
-the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
-of PPR on the ``two moons'' dataset. We defer details of the experimental
-settings to the appendix.
-
-% PUT FIGURE BACK HERE
-
-\paragraph{Validating theoretical bounds.}  We investigate the tightness of
-Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-  mixing_time_upper_bound} via simulation. Figure \ref{fig:bounds} compares our
-upper bounds with the actual empirically-computed quantities \eqref{eqn:
-  normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$
-and thickness $\sigma$ of a cluster $\Cset$. The top left and top middle panels
-display the resulting empirical clusters for two different values of
-$\rho,\sigma$.
-
-The bottom left and bottom right panels assure that our mixing  
-time upper bounds track closely the empirical mixing time, in both 2 and 3 
-dimensions.\footnote{We rescaled all values of theoretical upper
-  bounds by a constant, to mask the effect of large universal constants
-  in these bounds. Therefore only the comparison of slopes, rather than
-  intercepts, is meaningful.} This provides empirical evidence that Theorem
-\ref{thm: mixing_time_upper_bound} has the right dependency on both expansion
-parameter $\sigma$ and diameter $\rho$. The story for the normalized cut panels
-is less obvious. We remark that while, broadly speaking, the trends do not
-appear to match, this gap between theory and empirical results seems largest
-when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
-grows, the slopes of empirical and theoretical curves become more similar.
-
-\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:moons}, to drive home 
-the implications of Theorems \ref{thm: volume_ssd} and \ref{thm:
-consistent_recovery_of_density_clusters}, we show the behavior of PPR,
-normalized cut, and the density clustering algorithm of \citet{chaudhuri2010} on
-the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
-a prototypical success story for spectral clustering algorithms. The first
-column shows the empirical density clusters $\Cset[\Xbf]$ and $\Cset'[\Xbf]$ for
-a particular threshold $\lambda$ of the density function; the second column
-shows the cluster recovered by PPR; the third column shows the global minimum
-normalized cut, computed according to the algorithm of \citet{szlam2010}; and
-the last column shows a cut of the density cluster tree estimator of
-\citet{chaudhuri2010}.  We can see the degrading ability of PPR to recover
-density clusters as the two moons become less well-separated. Of particular
-interest is the fact that PPR fails to recover one of the moons even when
-normalized cut still succeeds in doing so. Additionally, we note that the
-Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
-fail.  This supports our main message, which is that PPR recovers only
-geometrically well-conditioned density clusters.
-
-% PUT FIGURE BACK HERE
-
-\section{Discussion}
-\label{sec: discussion}
-
-There are an almost limitless number of ways to define what the ``right''
-clustering is. In this paper, we have considered one such notion---density upper
-level sets---and have detailed a set of natural geometric criteria which, when 
-appropriately satisfied, translate to provable bounds on estimation of the
-cluster by PPR. We have also exhibited a hard case, showing that when a density
-cluster is sufficiently geometrically ill-conditioned, PPR can fail to recover
-it. Finally, we have empirically demonstrated the tightness of our analysis for
-reasonable sample sizes.
-
-\section*{Acknowledgements}
-
-SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
-helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
-
-\appendix
-
-%In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
-\section{Proof of Theorem \ref{thm: conductance_upper_bound}}
-\label{sec: proof_of_theorem_1}
-
-To ease notation, letting $S \subseteq X$ and $\Sset \subseteq \Reals^d$, we write
-\begin{equation*}
-\cut_{n,r}(S) = \cut(\Csig[\Xbf]; G_{n,r}), ~ \cut_{\Pbb,r}(\Sset)= \frac{\mathbb{E}[\cut_{n,r}(\Sset)]}{2{n \choose 2}}
-\end{equation*}
-for the random variable and mean of cut size, respectively.
-
-With this notation in place, the goal of Theorem~\ref{thm: conductance_upper_bound} is to show that for a universal constant $c_1 > 0$,
-\begin{align*}
-\Phi_{n,r}(\Csig[\Xbf]) := \frac{\cut_{n,r}(\Csig[\Xbf])}{\min\{\vol_{n,r}(\Csig[\Xbf]), \vol_{n,r}((\Rd \setminus \Csig)[\Xbf])\}} \leq c_1 \frac{d}{\sigma}
-    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
-\end{align*}
-with probability at least $1 - 3\exp\{-nb\}$.
-
-The proof of this theorem follows essentially from two technical Lemmas. 
-Lemma~\ref{lem:ball_bounds_in_probability} relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values.
-We restate the conclusions of this Lemma: for any $\delta > 0$,
-\begin{align}
-\frac{\cut_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq (1 + \delta)\cut_{\Pbb,r}(\Csig) &, \quad \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \geq (1 - \delta)\vol_{\Pbb,r}(\Csig) \nonumber \\ \frac{\vol_{n,r}((\Rd \setminus \Csig)[\Xbf])}{2{n \choose 2}}& \geq (1 - \delta)\vol_{\Pbb,r}(\Rd \setminus \Csig) \label{eqn: conductance_upper_bound_pf1}
-\end{align}
-with probability at least 
-\begin{align*}
-1 - & \exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Rd\setminus \Csig))^2} \\
-& \geq 1 - 3\exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2}.
-\end{align*} 
-We note that as a consequence of~\ref{asmp: bounded_volume} we have that $\vol_{\Pbb,r}(\Rd \setminus \Csig)  \geq \vol_{\Pbb,r}(\Csig)$, so it will suffice to lower bound $\vol_{\Pbb,r}(\Csig)$ (since a lower bound for $\vol_{\Pbb,r}(\Rd \setminus \Csig)$ follows).
-The following result provides upper and lower bounds on the expected values $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$ respectively:
-\begin{lemma}
-	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
-	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-	\begin{align}
-	\cut_{\Pbb,r}(\Csig) &\leq \frac{ d \nu_d r^{d+1} \lambda}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
-	\vol_{\Pbb,r}(\Csig) &\geq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)^{-1} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
-	\end{align}
-\end{lemma}
-Taking Lemma~\ref{lem: expected_density_cut} and \eqref{eqn: conductance_upper_bound_pf1} as given we can now complete the proof of the theorem. We lower bound $\Phi_{n,r}(\Csig[\Xbf])$ as follows:
-\begin{equation*}
-\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{(1 + \delta)}{(1 - \delta)(1 - dr/\sigma)^2}\frac{d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\sigma \lambda_{\sigma}^2}.
-\end{equation*}
-Noting that $(1 - dr/\sigma)^{-2} \leq 1 + 6dr/\sigma \leq 4$ for all $r \leq \sigma/2d$, the theorem is satisfied by choosing $c_1 = 4$ and $b = (\cut_{\Pbb,r}(\Csig))^2$.
-
-\subsection{Proof of Lemma~\ref{lem: expected_density_cut}}
-We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
-We 
-let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
-Our goal will be to upper bound $\cut_{\Pbb,r}(\Csig)$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
-and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
-\begin{lemma}
-	\label{lem: expected_number_boundary_points}
-	For any $0 < r \leq \sigma/(2d)$, under the conditions of Theorem \ref{thm: conductance_upper_bound} it holds that
-	\begin{equation*}
-	\Pbb(\Csigr) \leq \frac{dr}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-	\end{equation*}	
-\end{lemma}
-Taking this result as given we can now prove the claim~\eqref{eqn:claim_one}.
-\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } For each $i,j$ such that $i \neq j$, we can write 
-\begin{equation*}
-\cut_{\Pbb,r}(\Csig) =  \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r).
-\end{equation*}
-Writing this as an integral, we have
-\begin{align*}
-\cut_{\Pbb,r}(\Csig) & = \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-& = \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
-& \leq \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = \nu_d r^d \lambda \Pbb(\Csigr).
-\end{align*}
-where the inequality follows from \ref{asmp: low_noise_density}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$.
-Then, upper bounding the integral using Lemma \ref{lem: expected_number_boundary_points} gives the final result.
-
-\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } On the other hand, the proof of Claim~\eqref{eqn:claim_two} follows from relating $\vol_{\Pbb,r}(\Csig)$ to the Lebesgue measure of $\mc{C}_{\sigma - r}$.
-In particular, since $f(y) \geq \lambda_{\sigma}$ for all $x \in \Csig$, and $B(x,r) \subset \Csig$ for all $x \in \mc{C}_{\sigma - r}$, it follows that
-\begin{align*}
-\vol_{\Pbb,r}(\Csig) & = \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-& \geq \int_{\mc{C}_{\sigma - r}} f(x) \Pbb(B(x,r)) \dx \\
-& \geq \lambda_{\sigma}^2 \nu_d r^d \nu(\mc{C}_{\sigma - r}).
-\end{align*}
-Then, noting that by the triangle inequality $\mc{C}_{\sigma} \subseteq \mc{C}_{\sigma - r} + \sigma B$, applying Lemma~\ref{lem: expansion_volume} (given in Appendix~\ref{sec: volume_estimates}) and the Bernoulli inequality (Lemma~\ref{lem: Taylor_series}) gives
-\begin{equation*}
-\nu(\Cset_{\sigma}) \leq \nu(\Cset_{\sigma - r} + \sigma B) \leq \biggl(1 + \frac{r}{\sigma - r}\biggr)^d \nu(\Cset_{\sigma - r}) \leq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)\nu(\mc{C}_{\sigma - r}),
-\end{equation*}
-thus establishing the claim.
-
-It remains to prove Lemma~\ref{lem: expected_number_boundary_points} and we turn our attention to this now.
-\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
-We note that the proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
-
-We begin by partitioning $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
-	\begin{equation*}
-	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
-	\end{equation*}
-	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
-	\begin{equation}
-	\label{eqn: partition_ub}
-	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
-	\end{equation}
-	Assumptions~\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
-	\begin{equation*}
-	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
-	\end{equation*}
-	and writing
-	\begin{equation*}
-	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
-	\end{equation*}
-	we have
-	\begin{align}
-	\label{eqn: telescoping_sum}
-	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
-	& = \underbrace{\sum_{i = 1}^{k} 
-	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
-	\end{align}
-	where the second equality comes from rearranging terms in the sum.
-
-	% AJG 5/14/19: This argument makes sense, correct?
-	We first consider the term $\Sigma_k$.
-$\Cset$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$.
-Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero).
-As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
-	\begin{equation}
-	\label{eqn: slice_volume_bound}
-	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
-	\end{equation}
-	which in turn gives
-	\begin{align}
-	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
-	\end{align}
-	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
-	\begin{align}
-	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
-	\end{align}
-	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(2d)$.
-
-	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
-	\begin{align}
-	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
-\label{eqn: xi_ub}
-	\end{align}
-	where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}.
-As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
-
-\subsection{Volume Estimates}
-\label{sec: volume_estimates}
-We begin by recalling some notation.
-We let $\Aset \subseteq \Reals^d$, and for $\sigma > 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball).
-Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$, $\Asig = \set{z = x + y: x \in \Aset, y \in \sigma B}$.
-Recall that we use $\nu$ for Lebesgue measure, and $\nu_d = \nu(B)$ for $B = (0,1)$.
-
-Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.
-
-\begin{lemma}
-	\label{lem: expansion_volume}
-	If $\Aset$ is closed and bounded, then for any $\sigma$ and $\delta > 0$,
-	\begin{equation}
-	\label{eqn: expansion_volume}
-	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We will show that for any $\epsilon > 0$, 
-	\begin{equation}
-	\label{eqn: ratio_of_volume}
-	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
-	\end{equation}
-	Taking the limit as $\epsilon \to 0$ results in \eqref{eqn: expansion_volume}.
-
-	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ (where $N$ is a finite number that may implicitly depend on $\epsilon$) such that
-	\begin{equation*}
-	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon).
-	\end{equation*}
-	Note that $\Asig$ is the direct sum of two compact sets, and is therefore itself compact. Moreover, for any $\epsilon > 0$,
-	\begin{equation*}
-	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
-	\end{equation*}
-	so by compactness there exists a finite subcover $x_1, \ldots,x_N \in \Aset$ such that
-	\begin{equation}
-	\label{eqn: finite_subcover}
-	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
-	\end{equation}
-	As a direct consequence of \eqref{eqn: finite_subcover}, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$, and by definition for every $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$.
-Summarizing our findings, we have
-	\begin{equation}
-	\label{eqn: finite_subcover-1}
-	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon).
-	\end{equation}
-\noindent	We next show a lower bound on $\nu(\Asig)$.
-Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
-	\begin{equation*}
-	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
-	\end{equation*}
-	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$.
-As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
-	\begin{align*}
-	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
-	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
-	\begin{equation*}
-	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
-	\end{equation*}
-As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
-	\begin{equation*}
-	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
-	\end{equation*}
-	and therefore 
-	\begin{align*}
-	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
-	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
-	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
-	\end{align*}
-	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
-\end{proof}
-\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
-\begin{lemma}
-	\label{lem: covering}
-	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
-	\begin{equation*}
-	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
-	\begin{equation*}
-	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
-	\end{equation*}
-	since then
-	\begin{equation*}
-	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
-	\end{equation*}
-
-	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
-	\begin{equation}
-	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
-	\end{equation}
-	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$.
-Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
-	\begin{equation*}
-	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
-	\end{equation*}
-	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
-\end{proof}
-
-We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} (Bernoulli's inequality) serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}).
-\begin{lemma}
-	\label{lem: Taylor_series}
-	For any $-1 \leq x \leq 1/(d - 1)$, it holds that
-	\begin{equation*}
-	(1 + x)^{d} \leq 1 + \frac{dx}{1 - (d - 1)x}
-	\end{equation*}
-	and
-	\begin{equation*}
-	(1 - x)^d \geq 1 - d x.
-	\end{equation*}
-	If additionally $0 \leq x \leq 1/(2d - 2)$, then
-	\begin{align*}
-	(1 + x)^d & \leq 1 + 2d x.
-	\end{align*}
-\end{lemma}
-
-%\subsection{Density-weighted cut and volume estimates}
-%\label{sec: density_weighted_cut_and_volume_estimates}
-%
-%For notational ease, we write
-%\begin{align*}
-%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ \cut_{\Pbb,r}(\Csig) = \frac{\mu_K}{{n \choose 2}} \\
-%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ \vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} \\
-%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ \vol_{\Pbb,r}(\Csig)^c = \frac{\mu_V^c}{{n \choose 2}}
-%\end{align*}
-%for the random variable, mean, and probability of cut size and volume, respectively. 
-%
-%\begin{lemma}
-%	\label{lem: expected_density_cut}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-%	\begin{equation*}
-%	\cut_{\Pbb,r}(\Csig) \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%
-%\end{proof}
-%
-%\begin{lemma}
-%	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-%	\begin{equation*}
-%	\vol_{\Pbb,r}(\Csig) \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
-%	\begin{equation}
-%	\label{eqn: volume_expansion}
-%	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
-%	\end{equation}
-%	and by linearity of expectation we obtain
-%	\begin{equation*}
-%	\vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-%	\end{equation*}
-%	Writing this with respect to the density function $f$, we have
-%	\begin{align*}
-%	\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-%	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-%	\end{align*}
-%	whence the claim then follows by Lemma \ref{lem: local_conductance}.
-%\end{proof}
-%
-%To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
-%\end{equation*}
-%to $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$. 
-%
-%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$.
-These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
-%
-%\begin{lemma}
-%	\label{lem: prob_bound_cutvol}
-%	For any $\delta \in (0,1]$,
-%	\begin{equation}
-%	\label{eqn: numerator_additive_bound}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}.
-%	\end{equation}
-%	each with probability at least $1 - \delta$. 
-%\end{lemma}
-%
-%\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
-%	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-%	\end{equation*}
-%	with kernels
-%	\begin{align*}
-%	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-%	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{align*}
-%	
-%	Similarly,
-%	\begin{equation*}
-%	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-%	\end{equation*}
-%	with kernel,
-%	\begin{equation*}
-%	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{equation*}
-%	
-%	From Lemma \ref{lem: bounded_difference} we therefore have
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig)^c - \sqrt{\frac{\log(1/\delta)}{n}}
-%	\end{equation*}
-%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $\vol_{\Pbb,r}(\Csig)^c \geq \vol_{\Pbb,r}(\Csig)$. 
-%\end{proof}
-%
-%\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
-%\label{sec: proof_of_theorem_1}
-%
-%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
-All that remains is some algebra, which we take care of below.
-%
-%Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-%\begin{equation}
-%\label{eqn: conductance_representation_1}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{\Pbb,r}(\Csig) + \left(\frac{\cut_{n,r}}{{n \choose 2}} - \cut_{\Pbb,r}(\Csig)\right)}{\vol_{\Pbb,r}(\Csig) + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - \vol_{\Pbb,r}(\Csig)\right)}.
-%\end{equation}
-%Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this means
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}
-%\end{equation*}
-%for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-%Now, some straightforward algebraic manipulations yield
-%\begin{align*}
-%\frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} & = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \left(\frac{\vol_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig) - \Err_n}\right) + \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
-%& = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + \left(\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 1\right)\frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
-%& \leq \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}.
-%\end{align*}
-%By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
-%\begin{equation*}
-%\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-%\end{equation*}
-%Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-%\begin{equation*}
-%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 \vol_{\Pbb,r}(\Csig)^2}
-%\end{equation*}
-%which implies $2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \leq \epsilon$.
-
-\section{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
-
-Let $\widetilde{G}_{n,r} := G_{n,r}[\Csig[\Xbf]]$; in general, we will use tilde notation to refer to quantities computed over $\Csig$ or over the induced subgraph $\widetilde{G}_{n,r}$.
-The goal of Theorem \ref{thm: mixing_time_upper_bound} is to show that with high probability,
-\begin{equation*}
-\tau_{\infty}(\widetilde{G}_{n,r}) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{ \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3.
-\end{equation*}
-We follow a two-step approach typically used to establish upper bounds on the mixing time of Markov chains.
-
-In the first step, we relate the mixing time $\tau_{\infty}(G)$ of an arbitrary undirected graph $G = (V,E)$ to expansion properties of subsets $U \subseteq V$.
-We now build to a formal definition of these expansion properties.
-First, we recall the the \emph{cut} and \emph{volume} functionals over a graph, and introduce the \emph{degree} functional as well.
-For $u \in V$, $S \subseteq V$, and $S^c = V \setminus S$,
-\begin{equation*}
-\cut(S;G) = \sum_{u \in S} \sum_{v \in S^c} \1((u,v) \in E), \quad \deg(u;G) = \sum_{v \in V} \1((u,v) \in E), \quad \vol(S;G) = \sum_{u \in S} \deg(u;G).
-\end{equation*}
-Additionally, we recall the \emph{normalized cut} $\Phi(S;G)$, defined (as in \eqref{eqn: normalized_cut}) as
-\begin{equation*}
-\Phi(S;G) = \frac{\cut(S; G)}{\min\set{\vol(S; G),\vol(S^c; G)}}.
-\end{equation*}
-We can now formally define the expansion parameters \emph{local spread} $s(G)$ and \emph{conductance} $\Phi(G)$,
-\begin{equation*}
-s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(u)}, \quad \Phi(G) := \min_{S \subseteq V} \Phi(S;G).
-\end{equation*}
-
-The following proposition establishes an upper bound on the mixing time $\tau_{\infty}(G)$ in terms of the local spread $s(G)$ and conductance $\Phi(G)$.
-\begin{proposition}
-	\label{prop: pointwise_mixing_time}
-	Assume $\min_{u \in V} \deg(u; G) \geq 10$. Then,
-	\begin{equation*}
-	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-	\end{equation*}
-\end{proposition}
-
-The second step in our approach is to lower bound the local spread and conductance over the neighborhood graph $\widetilde{G}_{n,r}$. In the following result we give lower bounds for both quantities.
-
-\begin{proposition}
-	\label{prop: local_spread_conductance}
-	Fix $\delta \in (0,1)$.
-Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$, $b_4$, and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	n \geq \max\left\{\frac{(1 + \delta)^2}{(1 - \delta)^2} \cdot (\log n)^{dp_d}\cdot b_3^d, b_4\right\}
-	\end{equation*}
-	the following inequalities:
-	\begin{equation}
-	\label{eqn:min_degree}
-	\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10,
-	\end{equation}
-	and
-	\begin{equation}
-	\label{eqn: local_spread}
-	s(\widetilde{G}_{n,r}) \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\lambda_{\sigma}^2(2r)^d}{\Lambda_{\sigma}^2(L\rho)^d},
-	\end{equation}
-	and
-	\begin{equation}
-	\label{eqn: conductance}
-	\Phi(\widetilde{G}_{n,r}) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}
-	\end{equation}
-	hold with probability at least $1 - \frac{b_5}{n} - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$.
-\end{proposition}
-
-Taking these results as given, the proof of Theorem \ref{thm: mixing_time_upper_bound} is more or less complete.
-Since the condition $\min_{u \in \Csig[\Xbf]} \deg(u;\widetilde{G}_{n,r}) \geq 10$ is satisfied, we may apply Proposition \ref{prop: pointwise_mixing_time}.
-Noting that:
-\begin{itemize}
-	\item by~\eqref{eqn: local_spread}, for any constant $c > 0$,
-	\begin{align*}
-	\log\biggl(\frac{1}{s(\wt{G}_{n,r})}\biggr) & \leq d \log\biggl(c^{1/d}\frac{40^{1/d}}{9^{1/d}} \cdot \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \cdot \frac{\lambda_{\sigma}^{2/d}L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \\
-	& \leq d \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(\frac{40^{1/d}}{9^{1/d}} \cdot \frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr)
-	\end{align*}
-	\item By assumption $r/\sigma \leq 1/(4d)$. Thus 
-	\begin{equation*}
-	1 - \frac{r}{4\rho L} \geq 1 - \frac{r}{4\sigma} \geq \frac{15}{16}
-	\end{equation*}
-	and
-	\begin{equation*}
-	\Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr) \geq 1 - \frac{1}{4}\sqrt{\frac{d + 2}{2d^2\pi}} \geq 1 - \frac{1}{4\sqrt{2}}.
-	\end{equation*}
-
-	Thus from~\eqref{eqn: conductance}, we obtain
-	\begin{align*}
-	\frac{1}{\Phi^2(\wt{G}_{n,r})} & \leq \frac{36^2 \cdot 16^2}{15^2(1 - \delta)^2(1 - 1/(4\sqrt{2}))^4 2\pi} \cdot \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \\
-	& \leq \frac{511}{(1 - \delta)^2} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4}.
-	\end{align*}
-\end{itemize}
-Hence, by Proposition~\ref{prop: pointwise_mixing_time} it holds that
-\begin{align*}
-\tau_{\infty}(\widetilde{G}_{n,r}) & \leq \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \\
-& \leq \frac{1022(1 + \delta)^{4/d}}{(1 - \delta)^{4/d + 2}} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
-& ~~ 3d\frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 \\
-& \leq 1022\biggl(1 + \Bigl(\frac{32}{d} + 8\Bigr)\delta\biggr) \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
-& ~~ 3d(1 + 32\delta)\log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 
-\end{align*}
-where $c_4 := 63, c_5 := 2240$, and the final inequality holds whenever $\delta < 1/(8 + 16/d)$.
-Thus the Theorem holds upon proper choice of universal constants $c_2 = 1022$, $c_3 = 3$, and constants $b_1 = b_3^d + b_4$, $b_2 = \min\{\wt{\vol}_{\Pbb,r}(\Csig), \lambda_{\sigma}\nu_dr^d/8\}$.
-
-In the rest of this section we proceed to proving Propositions \ref{prop: pointwise_mixing_time} and \ref{prop: local_spread_conductance}.
-
-\subsection{Proof of Proposition \ref{prop: pointwise_mixing_time}}
-\label{sec: pointwise_mixing_time}
-
-We first generalize some notation from the main text.
-Let $A$ be the adjacency matrix of an undirected graph $G = (V,E)$, and $D$ the associated diagonal degree matrix.
-The lazy random walk over $G$ is the Markov chain with transition probabilities given by $\Wbf := \frac{\Ibf{} + \Dbf^{-1} \Abf}{2}$ and stationary distribution $\pi$ with elements $\pi(u) = D_{uu}/\vol(V;G)$.
-Denote the $t$-step probability distribution of this random walk, originating from a  vertex $v \in V$, as $q^{(t)}: V \times V \to [0,1]$, $q^{(t)}(v,u) = e_v \Wbf^t e_u$.
-
-Consider the uniform distance\footnote{Note $d_{\textrm{unif}}$ is not formally a distance as it is not symmetric.} between the distributions $q_v^{(t)} := q^{(t)}(v,\cdot)$ and $\pi$, given by
-\begin{equation*}
-d_{\textrm{unif}}(q_v^{(t)},\pi) = \max_{u \in V} \set{\frac{\pi(u) - q_v^{(t)}(u)}{\pi(u)}}.
-\end{equation*}
-Our goal is to demonstrate that for a sufficiently large $t$, $d_{\textrm{unif}}(q_v^{(t)},\pi) \leq \frac{1}{4}$ for every $v \in V$ (see~\eqref{eqn: mixing_time} to recall the definition of $\tau_{\infty}(G)$).
-To do so, we introduce the \emph{total variation distance} between the distributions $q_v^{(t)}$ and $\pi$, given by
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sum_{u \in V} \abs{q_v^{(t)}(u) - \pi(u)}.
-\end{equation*}
-As we will see, an upper bound on the uniform distance can be obtained from an analogous upper bound on the total variation distance.
-First, however, we upper bound the total variation distance $||q_v^{(t)} - \pi||_{\mathrm{TV}}$ as a function of the local spread $s(G)$, the conductance $\Phi(G)$ and the number of steps $t$.
-\begin{lemma}
-	\label{lem: tv_mixing_time}
-	For any $v \in V$, and any $0 < a \leq 1/4$,
-	\begin{align}
-	\norm{q_v^{(t + 3)} - \pi}_{\mathrm{TV}} \leq \max\set{as(G), \frac{1}{8} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V} \deg(u;G)}} 
-	\nonumber \\
-	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t \label{eqn: tv_mixing_time}
-	\end{align}
-\end{lemma}
-
-As mentioned, a bound on the total variation distance implies a corresponding bound on the uniform distance $d_{\mathrm{unif}}$, given by the following result:
-\begin{lemma}
-	\label{lem: tv_to_uniform_distance}
-	Let $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{s(G)}{14}$. Then,
-	\begin{equation*}
-	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
-	\end{equation*}
-\end{lemma}
-
-\noindent Taking these Lemmas as given, we proceed that show that for
-\begin{equation*}
-\tau_1 = \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
-\end{equation*}
-the uniform distance $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$, which proves the claim of Proposition \ref{prop: pointwise_mixing_time}.
-Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$, so that
-\begin{equation*}
-\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}.
-\end{equation*}
-Recall that by assumption, $\min_{u \in V} \deg(u;G) \geq 10$.
-Moreover note that for $a \leq 1/4$, $2as(G) < 1/2 < 1 - 2as(G)$, since $s(G) \leq 9/10 < 1$.
-By Lemma \ref{lem: tv_mixing_time} we therefore obtain
-\begin{equation*}
-\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{1}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
-\end{equation*}
-It is a well-known fact (see e.g.~\cite{montenegro2002}) that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
-Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
-\begin{equation*}
-\norm{q_v^{(\tau_1)} - \pi}_{\mathrm{TV}} \leq \frac{s(G)}{14}
-\end{equation*}
-and so by Lemma \ref{lem: tv_to_uniform_distance}, $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$.
-The proof of Proposition \ref{prop: pointwise_mixing_time} is therefore complete once we have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}.
-
-\subsection{Proof of Lemma \ref{lem: tv_mixing_time}}
-\label{sec: mixing_time_on_graphs}
-
-We generalize the notation of the previous subsection.
-For a starting distribution $z$ to be specified later, and for $t \geq 0$ an integer, let $q_z^{(t)}$ be the $t$-step probability distribution of the lazy random walk with starting distribution $z$.\footnote{We say $z$ is a starting distribution over a graph $G$ when $\textrm{supp}(z) \subseteq V$ and $\sum_{u \in V}z(u) = 1$.
-Then, $q_z^{(t)} = zW^t$.}
-
-We will find it useful to introduce the \emph{Lovasz-Simonovits curve}, defined for any $t \in \mathbb{N}$ and starting distribution $z$ to be $h_z^{(t)}: [0,1] \to [0,1]$,
-\begin{equation*}
-h_z^{(t)}(x) = \max_{w \in \mathcal{W}_x} \left\{ \sum_{u \in V} \left(q_z^{(t)}(u) - \pi(u)\right)w(u)\right\}.
-\end{equation*}
-The maximum in the preceding display is over the set of weight functions $\mathcal{W}_{x}$
-\begin{align*}
-\mathcal{W}_x = \left\{w: V \to [0,1] \Big\vert 0 \leq w(u) \leq 1~~\forall~u,~~\text{and}~~\sum_{u \in V} w(u) \pi(u) = x\right\}.
-\end{align*}
-The utility of the Lovasz-Simonovits curve is demonstrated by the following observations. First, note that
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} = \sup_{S \subseteq V} \abs{q_v^{(t)}(S) - \pi(S)}
-\end{equation*}
-where we use the standard notation $\pi(S) := \sum_{u \in S} \pi(u)$, and likewise for $q_v^{(t)}(S)$. Moreover, observe that for any $S \subseteq V$ and any integer $t \geq 0$,
-\begin{equation}
-\label{eqn: lovasz_simonovits_1}
-\abs{q_v^{(t)}(S) - \pi(S)} \leq \max \set{h_v^{(t)}(\pi(S)), h_v^{(t)}(1 - \pi(S))}
-\end{equation}
-(To see this, consider the weight functions $w(u) = \1(u \in S)$ and $w'(u) = 1 - w(u)$.) Taking the maximum on both sides of \eqref{eqn: lovasz_simonovits_1}  over all $S \subseteq V$, we have
-\begin{equation*}
-\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \max_{0 \leq x \leq 1} h_v^{(t)}(x).
-\end{equation*}
-Now, take $z = e_vW^3$, and trivially observe that $h_v^{(t+3)}(x) = h_z^{(t)}(x)$.
-To prove Lemma \ref{lem: tv_mixing_time}, it is therefore sufficient to show the desired upper bound \eqref{eqn: tv_mixing_time} holds with respect to $h_z^{(t)}(x)$ for all $x \in [0,1]$, and all starting distributions $z = e_vW^3$.
-
-Let $\mu = as(G)$, and note under the condition $a < 1/4$, $\mu < 1 - \mu$.
-To show the desired upper bound, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$.
-Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$,
-\begin{equation*}
-\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
-\end{equation*}
-
-The following technical Lemma collects the upper bounds which hold over $[\mu, 1 - \mu]$ and $[0,\mu) \cup (1 - \mu, 1]$, respectively:
-\begin{lemma}
-	\label{lem: mixing_all_sets}
-	For any $\mu \leq x \leq 1 - \mu$ and any starting distribution $z = e_vW^3$,
-	\begin{equation}
-	\label{eqn: mixing_large_sets}
-	h_z^{(t)}(x) \leq \ell_{\mu}(x) + \left(\frac{1}{1 - 2\mu} + \frac{1}{\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t.
-	\end{equation}
-	For any $0 \leq x < \mu$ or $1 - \mu < x \leq 1$
-	\begin{equation}
-	\label{eqn: mixing_small_sets}
-	h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{2^{t+3}} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-	\end{equation}
-\end{lemma}
-\noindent Taking Lemma \ref{lem: mixing_all_sets} as given, we have nearly completed our proof of Lemma \ref{lem: tv_mixing_time}. Note that for any $\mu \leq x \leq 1 - \mu$,
-\begin{align*}
-\ell_{\mu}(x) & \leq \max\set{h_z^{(t)}(\mu),h_z^{(t)}(1 - \mu)} \\
-& \leq \max\set{as(G), \frac{1}{2^{t + 3}} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} }
-\end{align*}
-with the latter inequality following from \eqref{eqn: mixing_small_sets}. Therefore, for any $x \in [0,1]$,
-\begin{equation*}
-h_z^{(t)}(x) \leq \max\set{as(G), \frac{1}{8} + \frac{9a}{20} + \frac{1}{2 \min_{u \in V}\deg(u;G)} } + \left(\frac{1}{1 - 2as(G)} + \frac{1}{as(G)}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{equation*}
-which is exactly the claimed result of Lemma \ref{lem: tv_mixing_time}.
-
-\subsection{Proof of Lemma \ref{lem: mixing_all_sets}}
-
-We first prove \eqref{eqn: mixing_large_sets}, and then \eqref{eqn: mixing_small_sets}.
-\paragraph{Proof of \eqref{eqn: mixing_large_sets}:}
-The desired result is a consequence of Theorem 1.2 of \cite{lovasz1990}. To state this theorem, we introduce the notation
-\begin{equation*}
-C_{\mu} = \max \set{\frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{x - \mu}}, \frac{h_z^{(0)}(x) - \ell_{\mu}(x)}{\sqrt{1 - x - \mu}}: \mu < x < 1 - \mu},
-\end{equation*}
-and then the theorem itself.
-\begin{theorem}[Theorem 1.2 of \cite{lovasz1990}]
-	\label{thm: lovasz_simonovits_1993}
-	For any $\mu \leq x \leq 1 - \mu$, $z$ an arbitrary starting distribution, and an integer $t \geq 0$,
-	\begin{equation}
-	\label{eqn: lovasz_simonovits_1993}
-	h_z^{(t)}(x) \leq \ell_{\mu}(x) + C_{\mu} \min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t
-	\end{equation}
-\end{theorem}
-In order to show \eqref{eqn: mixing_large_sets}, we must therefore provide an appropriate bound on the quantity $C_{\mu}$. Precisely, we will show that for any $\mu < x < 1 - \mu$,
-\begin{equation}
-\label{eqn: lt_ub_1}
-h_z^{(0)}(x) - \ell_{\mu}(x) \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \min \set{\sqrt{x - \mu},\sqrt{1 - x - \mu}}
-\end{equation}
-which will in turn imply
-\begin{align*}
-C_{\mu} & \leq \max \set{\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} , \frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1 } \\
-& \leq \frac{1}{\mu} + \frac{1}{1 - 2\mu}.
-\end{align*}
-Plugging this upper bound into \eqref{eqn: lovasz_simonovits_1993}, we obtain
-\begin{align*}
-h_z^{(t)}(x) & \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\min \set{\sqrt{x - \mu}, \sqrt{1 - x - \mu}} \left(1 - \frac{\Phi^2(G)}{2}\right)^t \\
-& \leq \ell_{\mu}(x) +  \left(\frac{1}{\mu} + \frac{1}{1 - 2\mu}\right)\left(1 - \frac{\Phi^2(G)}{2}\right)^t
-\end{align*}
-which is the desired result.
-
-It remains to show \eqref{eqn: lt_ub_1}.
-To do so, we make use of an equivalent representation of the Lovasz-Simonovits curve $h_z^{(t)}$.
-Order the elements of $V = \set{u_1, \ldots, u_N}$, where $N = \abs{V}$, such that
-\begin{equation}
-\label{eqn: lovasz_simonovits_curve_1}
-\frac{q_z^{(t)}(u_1)}{\pi(u_1)} \geq \frac{q_z^{(t)}(u_2)}{\pi(u_2)} \geq \ldots \geq \frac{q_z^{(t)}(u_N)}{\pi(u_N)},
-\end{equation}
-and for each $k = 1,\ldots, N$, let $U_k = \set{u_1, \ldots, u_k}$.
-Then for any $x \in [0,1]$, letting $k$ satisfy $\pi(U_{k - 1}) < x < \pi(U_k)$, it can be shown that\footnote{See \cite{lovasz1990} for a formal justification.},
-\begin{equation}
-\label{eqn: lovasz_simonovits_curve}
-h_z^{(t)}(x) = \sum_{j = 1}^{k - 1} (q_z^{(t)}(u_j) - \pi(u_j)) + \frac{x - \pi(U_{k - 1})}{\pi(u_k)} \left(q_z^{(t)}(u_k) - \pi(u_k) \right).
-\end{equation}
-The representation of the Lovasz-Simonovits curve given by~\eqref{eqn: lovasz_simonovits_curve} makes it clear that $h_z^{(t)}(x)$ is a piecewise linear curve, with knots at the points $x_k = \pi(U_k)$ for $k = 1,\ldots,N$, where the $k$th linear segment has slope $v_k = q_z^{(t)}(u_{k})/\pi(u_{k}) - 1$.
-By the ordering of~\eqref{eqn: lovasz_simonovits_curve_1}, we have that $v_1(x) > v_2(x) > \ldots > v_{N-1}(x)$, and the curve is therefore concave.
-
-In fact, letting $v(x) = \sum_{k = 1}^{N} v_k \1(x \in [U_k, U_{k+1}) )$ be the slope of the Lovasz-Simonovits curve, for any $x \geq \mu$ it can be shown that
-\begin{align}
-v(x) & \leq \min_{k: u_k \leq x} v_k \nonumber  \\
-& \leq \frac{h_z^{(0)}(\mu)}{\mu}. \label{eqn: lovasz_simonovits_slope}
-\end{align}
-From the upper bound in~\eqref{eqn: lovasz_simonovits_slope} along with the concavity of $h_z^{(0)}(x)$, we have that for any $x \geq \mu$,
-\begin{equation*}
-h_z^{(0)}(x) \leq h_z^{(0)}(\mu) + (x - \mu)\frac{h_z^{(0)}(\mu)}{\mu}.
-\end{equation*}
-Some algebra then yields that for any $x \geq \mu$,
-\begin{align*}
-h_z^{(0)}(x) - \ell_{\mu}(x) & \leq h_z^{(0)}(\mu) - \left(\frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu)\right) + \frac{h_z^{(0)}(\mu)}{\mu}(x - \mu) \\
-& =  \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(\mu) + \frac{h_z^{(0)}(\mu)}{\mu} (x - \mu) - \frac{x - \mu}{1 - 2\mu} h_z^{(0)}(1 - \mu) \\
-& \leq \sqrt{x - \mu} \left(\frac{h_z^{(0)}(\mu)}{1 - 2\mu} + \frac{h_z^{(0)}(\mu)}{\mu} \right)
-\end{align*}
-On the other hand, $\ell_{\mu}(1 - \mu) = h_z^{(0)}(1 - \mu)$, and by the concavity of $h_z^{(0)}$ and \eqref{eqn: lovasz_simonovits_slope},  for $x \leq 1 - \mu$
-\begin{equation*}
-h_z^{(0)}(x) \leq h_z^{(0)}(1 - \mu) + (1 - x - \mu).
-\end{equation*}
-Similar manipulations to above give the upper bound
-\begin{align*}
-h_z^{(0)}(x) - \ell_{\mu}(x) \leq \sqrt{1 - \mu - x}\left(\frac{h_z^{(0)}(1 - \mu) }{1 - 2\mu} + 1\right)
-\end{align*}
-and \eqref{eqn: lt_ub_1} follows.
-
-\paragraph{Proof of \eqref{eqn: mixing_small_sets}:}
-We let $z = e_vW^3$ for an arbitrary $v \in V$. First, we deal with the case $x \leq as(G)$. Letting $\pi(U_{k-1}) \leq x \leq \pi(U_{k})$, we have
-\begin{equation}
-\label{eqn: mixing_time_small_sets_1}
-h_z^{(t)}(x) \leq q_z^{(t)}(U_{k - 1}) + q_z^{(t)}(u_k)
-\end{equation}
-We observe a few facts about the random walk defined by $q_z^{(t)}$. By the laziness of the random walk, for $u \neq v, t \geq 1$
-\begin{equation}
-\label{eqn: mixing_time_small_sets_2}
-q_z^{(t)}(u) \leq \frac{1}{2 \min_{u \in V}\deg(u;G)}
-\end{equation}
-On the other hand if $u = v$,
-\begin{equation}
-\label{eqn: mixing_time_small_sets_3}
-q_z^{(t)}(u) \leq \frac{1}{2^{t + 3}} + \frac{1}{2\min_{u \in V}\deg(u;G)}.
-\end{equation}
-Therefore by \eqref{eqn: mixing_time_small_sets_1}, \eqref{eqn: mixing_time_small_sets_2}, and \eqref{eqn: mixing_time_small_sets_3}
-\begin{equation*}
-h_z^{(t)}(x) \leq \frac{1}{2^{t + 3}} + \frac{\abs{U_{k - 1}}}{2 \min_{u \in V}\deg(u;G)} + \frac{1}{2 \min_{u \in V}\deg(u;G)}.
-\end{equation*}
-Finally, since $x \leq a s(G)$ and $x \geq \pi(U_{k - 1})$,
-\begin{align*}
-\abs{U_{k - 1}} & \leq \frac{\pi(U_{k-1})}{\min_{u \in V} \pi(v) } \\
-& \leq \frac{as(G)}{\min_{u \in V} \pi(v) } \\
-& \leq \frac{9a\min_{u \in V}\deg(u;G)}{10}.
-\end{align*}
-and the desired result is shown.
-
-Now, we turn to the case where $x \geq 1 - as(G)$.
-Noting that the slope $v(x)$ of the Lovasz-Simonovits curve $h_z^{(t)}$ is bounded below by $-1$ for all $x \in [0,1]$, by the concavity of $h_z^{(t)}$ we have
-\begin{align*}
-h_z^{(t)}(x) & \leq h_z^{(t)}(1) + (1 - x) \\
-& = 1 - x \leq as(G).
-\end{align*}
-and the proof of Lemma~\ref{lem: tv_mixing_time} is complete.
-
-\subsection{Proof of Lemma \ref{lem: tv_to_uniform_distance}}
-
-The proof of Lemma \ref{lem: tv_to_uniform_distance} follows from straightforward algebraic manipulation.
-Fix $u \in V$ and let $m \geq t + 1$ be arbitrary.
-The stationarity of $\pi$ gives (see~(16) of \citep{morris2005})
-\begin{align}
-\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
-& \overset{\text{(i)}}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
-& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
-\end{align}
-where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$. Then,
-\begin{align}
-\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) & \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max_{y \neq u} \abs{\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}} \nonumber \\
-& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \max_{y \neq u}\set{\frac{q^{(1)}(y,u)}{\pi(u)}}} \nonumber \\
-& \overset{(ii)}{\leq} \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \max \set{1, \frac{1}{2 \pi(u) \min_{u' \in V} \deg(u';G) }} \nonumber \\
-& \leq \norm{q_v^{(m-1)} - \pi}_{\mathrm{TV}} \frac{1}{s(G)} \label{eqn: tv_to_uniform_distance_3}
-\end{align}
-where $(ii)$ follows from the fact that for $y \neq u$, $q^{(1)}(y,u) \leq 1/\left(2 \min_{u \in V} \deg(u; G)\right)$.
-As $m - 1 \geq t$, it is well-known (see e.g.
-\cite{lovasz1990}) that the laziness of the random walk guarantees $\norm{q_v^{(m - 1)} - \pi}_{\mathrm{TV}} \leq \norm{q_v^{(t)} - \pi}_{\mathrm{TV}}$, and therefore by \eqref{eqn: tv_to_uniform_distance_3} and the hypothesis of Lemma \ref{lem: tv_to_uniform_distance},
-\begin{equation*}
-\sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \leq \frac{1}{14}.
-\end{equation*}
-Plugging this in to \eqref{eqn: tv_to_uniform_distance_1} and taking maximum on both sides, we obtain
-\begin{equation}
-d_{\textrm{unif}}(q_v^{(m)}, \pi) \leq \frac{1}{14} + \frac{d_{\textrm{unif}}(q_v^{(m - 1)}, \pi)}{2} \label{eqn: tv_to_uniform_distance_2}
-\end{equation}
-The recurrence relation of \eqref{eqn: tv_to_uniform_distance_2} along with the initial condition $d_{\textrm{unif}}(q_v^{(t)}, \pi) \leq 1$ yields
-\begin{equation*}
-d_{\textrm{unif}}(q_v^{(t + 1)}, \pi) \leq \frac{8}{14} \Rightarrow d_{\textrm{unif}}(q_v^{(t + 2)}, \pi) \leq \frac{5}{14} \Rightarrow  d_{\textrm{unif}}(q_v^{(t + 3)}, \pi) \leq \frac{1}{4}
-\end{equation*}
-and the claim is shown. We have proved Lemmas \ref{lem: tv_mixing_time} and \ref{lem: tv_to_uniform_distance}, and therefore Proposition \ref{prop: pointwise_mixing_time}.
-
-\subsection{Proof of Proposition \ref{prop: local_spread_conductance}}
-
-We prove~\eqref{eqn:min_degree} and~\eqref{eqn: local_spread} immediately before turning our attention to~\eqref{eqn: conductance}, which will require the bulk of our attention.
-First, however, we introduce some notation.
-For $S \subseteq \Csig[\Xbf]$ and $u \in \Csig[\Xbf]$, we will write
-\begin{equation*}
-\widetilde{\cut}_{n,r}(S) := \cut(S; \widetilde{G}_{n,r}), \quad \widetilde{\deg}_{n,r}(u) := \deg(u; \widetilde{G}_{n,r}), \quad 
-\widetilde{\vol}_{n,r}(S) := \vol(S; \widetilde{G}_{n,r})
-\end{equation*}
-and let $\widetilde{\pi}_{n,r}(u) = \widetilde{\deg}_{n,r}(u)/\widetilde{\vol}_{n,r}(\Csig[\Xbf])$ be the stationary distribution of the lazy random walk over $\widetilde{G}_{n,r}$.
-We also let $\widetilde{\Phi}_{n,r}(S) := \Phi(S; \widetilde{G}_{n,r})$ denote the normalized cut functional over $\widetilde{G}_{n,r}$, and $\degminwt := \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u)$.
-
-\paragraph{Proof of~\eqref{eqn:min_degree}:}
-
-Applying Lemma~\ref{lem:graph_functional_concentration} with $\delta = 1/2$, we see that
-\begin{align*}
-\wt{d}_{\min} & \geq \frac{n}{4}\biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)\lambda_{\sigma} \nu_d r^d \\
-& \geq \frac{n}{8}\lambda_{\sigma} \nu_d r^d,
-\end{align*}
-with probability at least $1 - 2n\exp\Bigl\{-\lambda_{\sigma} \nu_dr^dn/28\Bigr\}$. Therefore for any
-\begin{equation*}
-n \geq \frac{80}{\lambda_{\sigma}\nu_dr^d} =:b_4
-\end{equation*}
-the minimum degree $\wt{d}_{\min} \geq 10$.
-
-\paragraph{Proof of \eqref{eqn: local_spread}:}
-
-We rewrite $s(\widetilde{G}_{n,r}) = \frac{9 \degminwt^2}{10\widetilde{\vol}_{n,r}(\Csig[\Xbf])}$.
-Then applying Lemma \ref{lem:ball_bounds_in_probability} to upper bound the minimum degree and lower bound the volume, we have that with probability at least $1 - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$
-\begin{align*}
-s(\widetilde{G}_{n,r}) & \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\nu_d^2 r^{2d} \lambda_{\sigma}^2}{\wt{\vol}_{\Pbb,r}(\mc{C}_{\sigma})} \\
-& \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\nu_d r^d \lambda_{\sigma}^2}{\Lambda_{\sigma}^2 \nu(\mc{C}_{\sigma})} \\
-& \geq \frac{9}{40} \cdot \biggl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\biggr)^2 \cdot \frac{(1 - \delta)^2}{(1 + \delta)} \cdot \frac{\lambda_{\sigma}^2(2r)^d}{\Lambda_{\sigma}^2(L\rho)^d},
-\end{align*}
-where the last inequality follows by Assumption~\ref{asmp: embedding}, which ensures that $\mc{C}_{\sigma}$ is contained in a ball of radius $L\rho/2$.
-
-\paragraph{Proof of \eqref{eqn: conductance}:}
-Roughly speaking, our goal is to show that for sufficiently large $n$, with probability at least $1 - \frac{b_5}{n}$,
-\begin{equation*}
-\min_{S \subseteq \Csig[\Xbf]} \widetilde{\Phi}_{n,r}(S) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}
-\end{equation*}
-In order to show this bound holds uniformly over all sets $S \subseteq \Csig[\Xbf]$, we will split the analysis into two cases based on the size of $S \subseteq \Csig[\Xbf]$.
-To do so, we introduce $\mathcal{L}(G) := \set{S \subseteq V: \pi(S), \pi(S^c) \geq s(G)}$ (where as usual $\pi$ denotes the stationary distribution of a lazy random walk over $G$.)
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for any subset $S \subseteq \Csig[\Xbf]$ not in $\mathcal{L}(\widetilde{G}_{n,r})$, the graph normalized cut of $S$ is at least $1/10$.
-In fact, this statement holds for any graph $G$.
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb_1}
-	Let $G = (V,E)$ be an arbitrary undirected graph. Then, for non-empty subsets $S \subseteq V$, 
-	\begin{equation*}
-	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	The claim follows by direct manipulations:
-	\begin{align*}
-	\Phi(S;G) & \geq \frac{\cut(S;G)}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \abs{S}}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \pi(S)/(\min_{u \in V}\pi(u))}{\vol(S;G)} \\
-	& \geq \sum_{u \in S} \frac{\deg(u;G) - \frac{9}{10} \min_{u \in V}\deg(u;G)}{\vol(S;G)} \tag{since $S \not\in \mc{L}(G)$} \\
-	& \geq \frac{1}{10} \sum_{u \in S} \frac{\deg(u;G)}{\vol(S;G)} = \frac{1}{10}.
-	\end{align*}
-\end{proof}
-
-In Lemma \ref{lem: graph_conductance_profile_lb}, we establish a uniform lower bound on the normalized cut for the remaining sets $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-Let $p_d = 3/4$ if $d = 2$, and $p_d = 1/d$ if $d \neq 2$.
-
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb}
-	Fix $\delta \in (0,1)$.
-Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, there exist constants $b_3$ and $b_5$ independent of $n$ such that the following statement holds true: for any $n$ such that
-	\begin{equation*}
-	\frac{n}{(\log n)^{d p_d}} \geq \frac{(1 + \delta)^2}{(1 - \delta)^2}b_3^d
-	\end{equation*}
-	the following upper bound holds
-	\begin{equation}
-	\label{eqn: graph_conductance_profile_lb}
-	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \geq \Bigl(1 - \delta\Bigr)\Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}.
-	\end{equation}
-	with probability at least $1 - \frac{b_5}{n} - 2n\exp\Bigl\{-\delta^2 \lambda_{\sigma} \nu_dr^dn/(6 + 2\delta)\Bigr\} - 2\exp\set{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\Csig))^2}$. 
-\end{lemma}
-
-The desired upper bound on graph conductance \eqref{eqn: conductance} follows from Lemma \ref{lem: graph_conductance_profile_lb}, along with Lemma \ref{lem: graph_conductance_profile_lb_1}, in light of the fact $\frac{\lambda_{\sigma}^2 r}{\Lambda_{\sigma}^2 2^{13} \rho L \sqrt{d}} < \frac{1}{10}$.
-We turn now to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
-
-\subsection{Proof of Lemma \ref{lem: graph_conductance_profile_lb}.}
-
-The proof of Lemma~\ref{lem: graph_conductance_profile_lb} will essentially follow from a pair of technical results.
-The first of these will demonstrate that the functional $\widetilde{\Phi}_{n,r}(S)$ can be lower bounded by a population analogue $\widetilde{\Phi}_{\Pbb,r}(\Sset)$, for an appropriately chosen $\Sset \subseteq \Csig$; we term this latter functional the continuous normalized cut.
-This lower bound will hold uniformly over sets $S \subseteq \Csig[X]$.
-The second technical Lemma will build on known continuous space isoperimetric inequalities to lower bound the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ uniformly over sets $\Sset \subseteq \Csig$.
-
-We will now build slowly toward a formal definition of the continuous normalized cut, before establishing a relation between it and it's discrete counterpart.
-Let $\Sset \subseteq \Csig$ be measurable.
-We introduce the \emph{$r$-ball walk}, a Markov chain over $\Csig$ with transition probability at $x \in \Csig$ given by
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\Pbb(\Sset \cap B(x,r))}{\Pbb(\Csig \cap B(x,r))}.
-\end{equation*}
-
-Denote the stationary distribution for this Markov chain by $\piwt_{\Pbb,r}$, which is defined by the relation
-\begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) \,d \piwt_{\Pbb,r}(x) = \piwt_{\Pbb,r}(\Sset).
-\end{equation*}
-Letting the \emph{$\Pbb$-local conductance} be given by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \Pbb\bigl(\Csig \cap B(x,r)\bigr)
-\end{equation*}
-a bit of algebra verifies that
-\begin{equation*}
-\piwt_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d \Pbb(x) }{\int_{\Csig} \ell_{\Pbb,r}(x) \,d \Pbb(x)}.
-\end{equation*}
-
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset \cap \Sset^c = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset$ and $\Sset$ is given by 
-\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) := \int_{\Sset} \widetilde{P}_{\Pbb,r}(x; \Sset^c) \,d\piwt_{\Pbb,r}(x), 
-\end{equation*}
-and the \emph{($\Pbb$) continuous normalized cut} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c)}{\min \set{\piwt_{\Pbb,r}(\Sset),\piwt_{\Pbb,r}(\Sset^c)}},
-\end{equation*}
-
-As the functionals $\widetilde{\Phi}_{n,r}$ and $\widetilde{\Phi}_{\Pbb,r}$ act in the different spaces $\Csig[\Xbf]$ and $\Csig$, respectively, it is not obvious how to relate them.
-To do so, following the lead of \cite{garciatrillos16}, we introduce transportation maps between the space $\Csig$ and the sample points $\Csig[\Xbf]$.
-We note that by assumption~\ref{asmp: bounded_density}, $\Pbb(\Csig) > 0$, and therefore with probability one as $n \to \infty$, the number of sample points $\abs{\Csig[\Xbf]}$ will be non-zero as well.
-We may therefore define the conditional probability measures
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\abs{\Csig[\Xbf]}} \sum_{x_i \in \Csig[\Xbf]} \1(x_i \in \Sset).
-\end{equation*} 
-We then define a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ to be any measurable map $T: \Csig \to \Csig[\Xbf]$ such that for every $S \subseteq \Csig[\Xbf]$,
-\begin{equation*}
-\widetilde{\Pbb}(T^{-1}(S)) = \widetilde{\Pbb}_n(S),
-\end{equation*}
-where $T^{-1}(S) = \set{x \in \Csig: T(x) \in S}$ is the preimage of $T$.
-Observe that by the definition of the transportation map $T$, for any $g \in L^1\bigl(\widetilde{\Pbb}_n\bigr)$ the following change of variables formula holds
-\begin{equation*}
-\int_{\Csig} g(x) \,d\widetilde{\Pbb}_{n}(x) = \int_{\Csig} g\bigl(T(x)\bigr) \,d\widetilde{\Pbb}(x)
-\end{equation*}
-Using the change of variables formula with an appropriate choice of $g$, after suitable rescaling we can relate $\widetilde{\cut}_{n,r}(S)$ to $\widetilde{Q}_{\Pbb,r}(T^{-1}(S), T^{-1}(S)^c)$.
-Similarly, we can relate $\widetilde{\vol}_{n,r}(S^c)$ to $\widetilde{\pi}_{\Pbb,r}(T^{-1}(S))$.
-Working along these lines, we obtain the following lower bound on $\widetilde{\Phi}_{n,r}(S)$, stated in terms of the transportation distance $\norm{\mathrm{Id} - T}_{L^{\infty}(\Pbb)}$, where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$.
-
-\begin{lemma}
-	\label{lem: graph_to_continuous_conductance}
-	Let $T:\Csig \to \Csig[\Xbf]$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$.
-Suppose $\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} < \min \set{s(\widetilde{G}_{n,r}), \lambda_{\sigma}r/(2^{d+3}d\Lambda_{\sigma})}$.
-Then there exists a constant $b_6 > 0$ which does not depend on the sample size $n$, such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
-	\begin{equation}
-	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \widetilde{\Phi}_{\Pbb,r}(T^{-1}(S)) - \frac{b_6\norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6 \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}  }
-	\end{equation}
-\end{lemma}
-
-Clearly, Lemma \ref{lem: graph_to_continuous_conductance} is useful only when combined with an upper bound on the transportation distance $\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-Theorem 1.1 of \cite{garciatrillos16b} establishes such an upper bound, with respect to transportation maps on measures supported on open, connected and bounded domains with Lipschitz boundaries.
-The following result is a restatement of this Theorem with respect to the domain $\Csig$, and the measure $\widetilde{\Pbb}$.
-Although $\Csig$ is closed rather than open, as $\nu(\partial \Csig) = 0$ we may apply Theorem 1.1 of \cite{garciatrillos16} to the interior $\Csig^o$ of $\Csig$, and the desired result will hold for any arbitrary extension of $T_n$ to $\Csig$.
-Let $\widetilde{n} = \abs{\Csig[\Xbf]}$.
-
-\begin{theorem}[Restatement of Theorem 1.1 of \cite{garciatrillos16b}]
-	\label{thm: stagnating_transportation_maps}
-	There exists a constant $b_5$ which do not depend on $n$ such that with probability at least $1 - \frac{b_5}{n}$:
-	\begin{equation*}
-	\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} \leq 
-	b_{5} \begin{cases*}
-	\frac{\log(n)^{3/4}}{n^{1/2}},&~~\textrm{if $d = 2$,} \\
-	\frac{\log(n)^{1/d}}{n^{1/d}},&~~\textrm{if $d \neq 2$.}
-	\end{cases*} 
-	\end{equation*}
-\end{theorem}
-Lemma~\ref{lem: graph_to_continuous_conductance} and Theorem~\ref{thm: stagnating_transportation_maps} show that with high probability, the discrete normalized cut $\widetilde{\Phi}_{n,r}(S)$ is lower bounded by the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S))$ over all sufficiently large sets $S \subseteq \Xbf$.
-The following result then supplies the last step, a uniform lower bound on the continuous normalized cut $\widetilde{\Phi}_{\Pbb,r}(\Sset)$ for all sets $\Sset \subseteq \Csig$.
-Let the \emph{$\Pbb$-continuous conductance} be given by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r} := \min_{\Sset \subseteq \Csig} \widetilde{\Phi}_{\Pbb,r}(\Sset).
-\end{equation*} 
-\begin{lemma}
-	\label{lem: nonuniform_continuous_conductance}
-	Under the setup and conditions of Theorem \ref{thm: mixing_time_upper_bound}, the $\Pbb$-continuous conductance of the $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r\lambda_{\sigma}^2}{\Lambda_{\sigma}^2\rho L \sqrt{d + 2}}.
-	\end{equation*}
-\end{lemma}
-With Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, as well as Theorem \ref{thm: stagnating_transportation_maps}, in hand, we proceed to the proof of Lemma \ref{lem: graph_conductance_profile_lb}.
-\begin{proof}[Lemma~\ref{lem: graph_conductance_profile_lb}]
-To invoke Lemma~\ref{lem: graph_to_continuous_conductance}, we must establish an appropriate upper bound on $\|\mathrm{Id} - T_n\|_{L^{\infty}(\wt{P})}$.
-We do so using Theorem~\ref{thm: stagnating_transportation_maps}, which implies that if
-\begin{equation*}
-n^{1/d} > b_5\log(n)^{p_d} \cdot \frac{(1 + \delta)^2}{(1 - \delta)^2}  \max\Biggl\{\frac{b_6 (1 + \delta)^2 \Lambda_{\sigma}^2 (L\rho)^d}{9(1 - \delta)^2 \lambda_{\sigma}^2 (2r)^d \wt{\Phi}_{\Pbb,r}}, \frac{2^{d + 3}d \Lambda_{\sigma}}{r \lambda_{\sigma}}\Biggr\} =: \log(n)^{p_d} \cdot b_3 \cdot \frac{(1 + \delta)^2}{(1 - \delta)^2}
-\end{equation*}
-then
-\begin{equation*}
-\|\mathrm{Id} - T_n\|_{L^{\infty}(\wt{P})} \leq \min\biggl\{\frac{\delta \cdot s(\wt{G}_{n,r}) \wt{\Phi}_{\Pbb,r}}{b_6(1 + \delta \wt{\Phi}_{\Pbb,r})}, \frac{\lambda_\sigma r}{2^{d + 3}d \Lambda_{\sigma}}\biggr\}
-\end{equation*}
-(In the above, we take as given that the inequality~\eqref{eqn: local_spread} is satisfied.) As a result we may apply Lemma~\ref{lem: graph_to_continuous_conductance}, from which we obtain
-\begin{align*}
-\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) & \geq \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{\Pbb,r}(T_n^{-1}(S)) - \frac{b_6 \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq  \widetilde{\Phi}_{\Pbb,r} -  \frac{b_6 \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})} }{s(\widetilde{G}_{n,r}) - b_6\norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}} \\
-& \geq (1- \delta)\widetilde{\Phi}_{\Pbb,r},
-\end{align*}
-where the last inequality follows since $\delta < \frac{\widetilde{\Phi}_{\Pbb,r}\cdot s(\widetilde{G}_{n,r})}{2b_6 + \widetilde{\Phi}_{\Pbb,r}}$.
-Then, Lemma~\ref{lem: nonuniform_continuous_conductance} yields the desired result.
-\end{proof}
-It remains to prove Lemmas \ref{lem: graph_to_continuous_conductance} and \ref{lem: nonuniform_continuous_conductance}, which we do in Appendices~\ref{subsec:pf_graph_to_continuous_conductance}-\ref{subsec:pf_uniform_continuous_conductance}.
-
-\subsection{Proof of Lemma \ref{lem: graph_to_continuous_conductance}}
-\label{subsec:pf_graph_to_continuous_conductance}
-Let $S \subseteq \Csig[\Xbf]$ belong to $\mathcal{L}(\widetilde{G}_{n,r})$, and denote $\Sset := T^{-1}(S)$.
-Further let $\varDelta := \norm{\mathrm{Id} - T}_{L^{\infty}(\widetilde{\Pbb})}$, and $r^{+} := r + \varDelta$ and $r^{-} := r - \varDelta$.
-Our goal is to lower bound
-\begin{equation*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \frac{b_6\varDelta}{s(\widetilde{G}_{n,r}) - b_6 \varDelta}
-\end{equation*}
-for some constant $b_6 > 0$.
-We first state the relationships between the discrete functionals $\widetilde{\cut}_{n,r}$ and $\widetilde{\vol}_{n,r}$, and the continuous functionals $\widetilde{Q}_{\Pbb,r}$ and $\widetilde{\pi}_{\Pbb,r}$, alluded to in the previous section.
-\begin{lemma}
-	\label{lem: cut_volume}
-	For any set $S \subseteq \Csig[\Xbf]$ and $\mathcal{S} = T^{-1}(S)$, 
-	\begin{equation}
-	\label{eqn: cut}
-	\frac{1}{\widetilde{n}^2}\widetilde{\cut}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c)
-	\end{equation}
-	and 
-	\begin{equation}
-	\label{eqn: volume}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}_{n,r}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{\pi}_{\Pbb,r^+}(\Sset)
-	\end{equation}
-\end{lemma}
-To make use of Lemma \ref{lem: cut_volume}, we provide deviation inequalities on $\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)$, $\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)$, $\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c)$, and $\widetilde{\pi}_{\Pbb,r^+}(\Sset)$ in terms of the transportation distance $\varDelta$.
-\begin{lemma}
-	\label{lem: deviation_transportation_distance}
-	Suppose $\Delta \leq r$. Then there exist constants $b_7,b_8 \geq 0$ which do not depend on the sample size $n$, such that for every $\Sset \subseteq \Csig$,
-	\begin{align*}
-	\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7 \varDelta \\
-	\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x) & \geq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7 \varDelta \\
-	\widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c) & \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - b_8 \varDelta \\
-	\widetilde{\pi}_{\Pbb,r^+}(\Sset) & \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + b_8 \varDelta.
-	\end{align*}
-\end{lemma}
-
-The combination of Lemmas \ref{lem: cut_volume} and \ref{lem: deviation_transportation_distance} brings us close to our goal, as demonstrated by the following manipulations:
-\begin{align}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \frac{\widetilde{Q}_{\Pbb,r^-}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r^+}(\Sset)} \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \tag{Lemma \ref{lem: cut_volume}} \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c) - b_8 \varDelta }{\widetilde{\pi}_{\Pbb,r^+}(\Sset) + b_8 \varDelta} \left(1 - \frac{2 b_7 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right) \tag{Lemma \ref{lem: deviation_transportation_distance} } \\
-& \geq \frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\widetilde{\pi}_{\Pbb,r}(\Sset)} - \left(\frac{2b_8}{\widetilde{\pi}_{\Pbb,r}(\Sset)} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \label{eqn: proof_of_lemma_graph_to_continuous_1}
-\end{align}
-where the last line follows from some basic algebra. The following result relates the unknown stationary distribution $\widetilde{\pi}_{\Pbb,r}(\Sset)$ to $\widetilde{\pi}_{n,r}(S)$.
-\begin{lemma}
-	\label{lem: continuous_pi_lb}
-	Suppose $\varDelta \leq \lambda_{\sigma}r/(2^{d+3}d\Lambda_{\sigma})$.
-Then there exists a constant $b_9 > 0$ which does not depend on the sample size $n$ such that for every $S \subseteq \Csig[\Xbf]$,
-	\begin{equation*}
-	\widetilde{\pi}_{\Pbb,r}(\Sset) \geq \widetilde{\pi}_{n,r}(S) - b_9 \varDelta
-	\end{equation*}
-\end{lemma}
-Combining this result with~\eqref{eqn: proof_of_lemma_graph_to_continuous_1}, we obtain
-\begin{align*}
-\frac{\widetilde{\cut}_{n,r}(S,S^c)}{\widetilde{\vol}_{n,r}(S)} & \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2b_8}{\widetilde{\pi}_{n,r}(S) - b_9\varDelta} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta \\
-& \geq \widetilde{\Phi}_{\Pbb,r}(\Sset) - \left(\frac{2b_8}{s(\widetilde{G}_{n,r}) - b_9\varDelta} + \frac{2b_7}{\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x)}\right)\varDelta
-\end{align*}
-where the latter inequality follows as we assumed $S \in \mathcal{L}(\widetilde{G}_{n,r})$.
-Choosing the constant $b_6$ in Lemma \ref{lem: graph_to_continuous_conductance} to be $b_6 = \max\set{2b_7/\bigl(\int_{\Csig}\ell_{\Pbb,r}(x)\,d\Pbb(x) \bigr) + 2b_8, b_9}$, we achieve our desired result.
-It remains to show Lemmas~\ref{lem: cut_volume}, \ref{lem: deviation_transportation_distance}, and \ref{lem: continuous_pi_lb}, which we now turn to.
-
-\paragraph{Proof of Lemma~\ref{lem: cut_volume}: }
-
-We begin with $\widetilde{\cut}_{n,r}(S)$.
-\begin{align*}
-\frac{1}{\widetilde{n}^2} \widetilde{\cut}_{n,r}(S) & = \frac{1}{ \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \1(x_i \in S) \1(x_j \not\in S)\\
-& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \1(x \in S) \1(y \not\in S) \,d\widetilde{\Pbb}_n(x) \,d\widetilde{\Pbb}_n(y) \\
-& =  \iint_{\Csig \times \Csig} \1(\norm{T(x) - T(y)} \leq r) \1(T(x) \in S) \1(T(y) \not\in S)\,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \tag{change of variables}  \\
-& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r^-) \1(T(x) \in S) \1(T(y) \not\in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \\
-& = \int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} 1 \,d\widetilde{\Pbb}(y) \,d\widetilde{\Pbb}(x)
-\end{align*}
-By definition we have $\frac{\,d\Pbb(x)}{\,d\widetilde{\Pbb}(x)} = \Pbb(\Csig)$. Therefore,
-\begin{align}
-\int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r^-)} d\Pbb(y) d\Pbb(x) \nonumber \\
-& = \frac{\int_{\Csig} \ell_{\Pbb,r^-}(x) d\Pbb(x)}{\Pbb(\Csig)^2} \int_{\Sset} \frac{\Pbb\bigl(\Sset^c \cap B(x,r^-)\bigr)}{\ell_{\Pbb,r^-}(x)} d\piwt_{\Pbb,r^-}(x) \nonumber \\
-& = \frac{\int_{\Csig} \ell_{\Pbb,r^-}\,d\Pbb(x)}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r^-}(\Sset, \Sset^c). \label{eqn: cut_bound}
-\end{align}	
-We obtain an upper bound on $\widetilde{\vol}_{n,r}(S)$ by similar manipulations, as follows:
-\begin{align}
-\frac{1}{\widetilde{n}^2} \widetilde{\vol}_{n,r}(S) & \leq \frac{1}{ \widetilde{n}^2} \sum_{x_i, x_j \in \Csig[\Xbf]} \1(\norm{x_i - x_j} \leq r) \1(x_i \in S) \nonumber \\
-& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \1(x \in S) \,d\widetilde{\Pbb}_n(x) \,d\widetilde{\Pbb}_n(y) \nonumber \\
-& = \iint_{\Csig \times \Csig} \1(\norm{T(x) - T(y)} \leq r) \1(T(x) \in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \nonumber \\
-& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r^+) \1(x \in S) \,d\widetilde{\Pbb}(x) \,d\widetilde{\Pbb}(y) \nonumber \\
-& = \int_{\Sset} \int_{\Csig \cap B(x,r^+)} 1 \,d\widetilde{\Pbb}(y) \,d\widetilde{\Pbb}(x) \nonumber \\
-& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r^+)} 1 \,d\Pbb(y) \,d\Pbb(x) \nonumber \\
-& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) \nonumber \\
-& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)}{\Pbb(\Csig)^2} \piwt_{\Pbb,r^+}(\Sset). \label{eqn: vol_bound}
-\end{align}
-
-\paragraph{Proof of Lemma~\ref{lem: deviation_transportation_distance}: }
-
-Consider the set
-\begin{equation*}
-\mathcal{R}(x) := \set{y \in \Csig: y \in B(x,r^+), y \not\in B(x,r^-)}
-\end{equation*} 
-for $x \in \Csig$, and observe that
-\begin{equation*}
-\int_{\mathcal{R}(x)} \,d\Pbb(y) \leq \Lambda_{\sigma} \nu_d \left((r + \delta)^d - (r - \varDelta)^d\right)
-\end{equation*}
-and therefore
-\begin{equation}
-\label{eqn: deviation_transportation_distance_2}
-\int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \leq \Pbb(\Csig )\Lambda_{\sigma} \nu_d \left((r + \varDelta)^d - (r - \varDelta)^d\right).
-\end{equation}
-A first-order Taylor expansion of $(r + \varDelta)^d$ results in the upper bound $(r + \varDelta)^d \leq r^d + d\varDelta(r + \varDelta)^{d - 1}$, and similarly $(r - \varDelta)^d \geq r^d - d\varDelta(r + \varDelta)^{d - 1}$.
-Plugging these bounds into~\eqref{eqn: deviation_transportation_distance_2} yields
-\begin{align}
-\int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)  & \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d \bigl( 2d(r + \Delta)^{d - 1}\varDelta \bigr) \tag{1st-order Taylor expansion of $(r + \Delta)^d$ } \\
-& \leq \Pbb(\Csig) \Lambda_{\sigma} \nu_d  2^{d}d r^{d-1}\varDelta =: b_7 \varDelta. \label{eqn: deviation_transportation_distance_1}
-\end{align}
-where the second line follows from the condition $\Delta \leq r$.
-Using~\eqref{eqn: deviation_transportation_distance_1}, we proceed to obtain each of the four bounds stated in Lemma~\ref{lem: deviation_transportation_distance}.
-First, as $\ell_{\Pbb,r^{+}}(x) \leq 1$ for all $x \in \Csig$, we have
-\begin{align*}
-\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) & \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq \int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7\varDelta.
-\end{align*}
-An equivalent bound for $\int_{\Csig} \ell_{\Pbb,r^-}(x) \,d\Pbb(x)$ is obtained by similar reasoning. We now lower bound $\widetilde{Q}_{\Pbb,r^{-}}(\Sset, \Sset^c)$,
-\begin{align*}
-\widetilde{Q}_{\Pbb,r^{-}}(\Sset, \Sset^c) & = \int_{\Sset} \widetilde{P}_{\Pbb,r^-}(x; \Sset) \,d\widetilde{\pi}_{\Pbb,r}(x) \\
-& = \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r^-)) d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r^-)) d\Pbb(x)} \\
-& \geq \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) d\Pbb(x) - \int_{\Csig} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \Pbb(\Csig \cap B(x,r)) d\Pbb(x)} \\
-& \geq \widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - \frac{b_7 \varDelta}{\int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x)} =:\widetilde{Q}_{\Pbb,r}(\Sset, \Sset^c) - b_8 \varDelta.
-\end{align*}
-Finally, we upper bound $\widetilde{\pi}_{\Pbb,r^{+}}(\Sset)$,
-\begin{align*}
-\widetilde{\pi}_{\Pbb,r^{+}}(\Sset) & = \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r^+}(x) \,d\Pbb(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + \int_{\Sset} \int_{\mathcal{R}(x)} \,d\Pbb(y) \,d\Pbb(x)}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + b_8\varDelta.
-\end{align*}
-
-\paragraph{Proof of Lemma~\ref{lem: continuous_pi_lb}: }
-The proof of Lemma~\ref{lem: continuous_pi_lb} will not be too different from the proof of Lemma~\ref{lem: deviation_transportation_distance}. From the change of variables formula, we have
-\begin{align*}
-\widetilde{\pi}_{n,r}(S) & = \frac{\int_{\Sset}\int_{\Csig} \1(\norm{x - y} \leq r) \,d\widetilde{\Pbb}_n(y) \,d\widetilde{\Pbb}_n(x)}{\int_{\Csig}\int_{\Csig} \1(\norm{x - y} \leq r) \,d\widetilde{\Pbb}_n(y) \,d\widetilde{\Pbb}_n(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r^+}(x) \,d\Pbb(x) }{\int_{\Csig}\ell_{\Pbb,r^-}(x) \,d\Pbb(x)} \\
-& \leq \frac{\int_{\Sset} \ell_{\Pbb,r}(x) \,d\Pbb(x) + b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{2b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x) - b_7\varDelta} \\
-& \leq \widetilde{\pi}_{\Pbb,r}(\Sset) + \frac{4b_7\varDelta}{\int_{\Csig} \ell_{\Pbb,r}(x) \,d\Pbb(x)} =: \widetilde{\pi}_{\Pbb,r}(\Sset) + b_9 \varDelta.
-\end{align*}
-where the last inequality follows from the assumption $\varDelta \leq \lambda_{\sigma}r/(2^{d + 3} d\Lambda_{\sigma})$, which implies $b_7\varDelta \leq \int_{\Csig}\ell_{\Pbb,r}(x) \,d\Pbb(x) / 2$.
-
-\subsection{Proof of Lemma \ref{lem: nonuniform_continuous_conductance}. }
-We recall that our goal is to lower bound the continuous conductance $\widetilde{\Phi}_{\Pbb,r}$.
-Results along these lines are already known (see e.g.
-\cite{kannan04}) when the density $f$ is uniform (or log-concave) and $\Csig$ is itself a convex set -- indeed, in this case stronger versions of it exist, though we will not require them.
-In \cite{abbasi-yadkori2016a}, a statement of this sort is made with respect to uniform density $f$ and $\Csig$ a Lipschitz deformation of a convex set, but for completeness we produce all proofs here.
-
-\paragraph{Population-level conductance with uniform density.}
+\chapter{Lower bound for conductance of continuous-space ball walk}
 For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$.
@@
 	\label{lem: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
+	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
 Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.
@@
 	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
+	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
 	\end{equation*}
@@
 	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
+	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
 	\end{equation*}
@@
 
-Most of the technical work needed to show Lemma~\ref{lem: nonuniform_continuous_conductance}---and in turn, Corollary~\ref{cor: uniform_continuous_conductance}---involves proving Lemma~\ref{lem: uniform_continuous_conductance}.
-We first show that  Lemma~\ref{lem: nonuniform_continuous_conductance} is a simple consequence of Corollary~\ref{cor: uniform_continuous_conductance}---and \ref{asmp: bounded_density}---before turning to prove Lemma~\ref{lem: uniform_continuous_conductance}.
-
-\begin{proof}[of Lemma~\ref{lem: nonuniform_continuous_conductance}]
-To relate the uniform- and $\Pbb$-continuous conductances, observe that by \ref{asmp: bounded_density} we obtain
-\begin{align*}
-\frac{\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)}{\piwt_{\Pbb,r}(\Sset)} & = \frac{\int_{\Sset} \Pbb(\Sset^c \cap B(x,r)) \,d\Pbb(x)}{\int_{\Sset} \Pbb(\Csig \cap B(x,r)) \,d\Pbb(x)} \\
-& \geq \frac{\lambda_{\sigma}^2 \int_{\Sset} \nu(\Sset^c \cap B(x,r)) \dx}{\Lambda_{\sigma}^2 \int_{\Sset} \nu(\Csig \cap B(x,r)) \dx} \\
-& \geq \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{\widetilde{Q}_{\nu,r}(\Sset,\Sset^c)}{\pi_{\nu,r}(\Sset)}.
-\end{align*}
-Exchanging $\mc{S}$ and $\mc{S}^c$ in the above, we also have $\widetilde{Q}_{\Pbb,r}(\Sset,\Sset^c)/\piwt_{\Pbb,r}(\Sset^c) \geq (\lambda_{\sigma}^2/\Lambda_{\sigma}^2) \widetilde{Q}_{\nu,r}(\Sset,\Sset^c)/\piwt_{\nu,r}(\Sset^c)$, and the claim follows by~\ref{cor: uniform_continuous_conductance}.
-\end{proof}
-
-Lemma~\ref{lem: nonuniform_continuous_conductance} therefore follows from Lemma~\ref{lem: uniform_continuous_conductance} (by way of~\ref{cor: uniform_continuous_conductance}), and it remains to prove this Lemma.
-
 \subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
-\label{subsec:pf_uniform_continuous_conductance}
 Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance.
@@
 \end{equation*}
-and putting $a = r\ell/(2\rho L)$ yields the claim.
+and putting $a = r\ell/(2\rho)$ yields the claim.
 
@@
 
-We have completed our proof of (in turn) Lemmas~\ref{lem: uniform_continuous_conductance}, \ref{lem: nonuniform_continuous_conductance}, and \ref{lem: graph_conductance_profile_lb}.
-As a result, Proposition \ref{prop: local_spread_conductance} is proved, and the proof of Theorem \ref{thm: mixing_time_upper_bound} is complete.
-
 \section{Volume Estimates}
-In this section, we establish some inequalities regarding the volume of (intersections of) balls, which we used in Appendices A and B. 
+
 \begin{lemma}
@@
 	\label{eqn:overlap_balls_2}
-	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation}
-	An immediate implication of~\eqref{eqn:overlap_balls_2} is that for any $x \in \mc{C}_{\sigma}$:
-	\begin{equation}
-	\label{eqn:uniform_local_conductance}
-	\ell_{\nu,r}(x) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr)
 	\end{equation}
@@
 
-\section{Proof of Theorem~\ref{thm: volume_ssd}}
-\label{sec:proof_of_volume_ssd}
-
-In this section, we prove Theorem \ref{thm: volume_ssd}.
-To do so, we apply the following Lemma, which upper bounds the volume of the symmetric set difference in terms of normalized cut and mixing time on an arbitrary graph $G$.
+\section{Other derived results}
+
+Lemma~\ref{lem:volume_perturbation} bounds the difference $\nu(B(x,r) \cap \mc{C}_{\sigma}) - \nu(B(y,r) \cap \mc{C}_{\sigma})$ as a function of $\|x - y\|_{\Rd}$.
+Unfortunately, it only kicks in when $\|x - y\| \lesssim r/d$, whereas we would like something which applies when $\|x - y\| \lesssim r/\sqrt{d}$.
+
+\begin{lemma}
+	\label{lem:volume_perturbation}
+	Let $x,y \in \mc{C}_{\sigma}$ satisfy $\|x - y\| < \frac{r}{d - 1}$. Then,
+	\begin{equation*}
+	\Bigl|\nu\bigl(B(x,r) \cap \mc{C}_{\sigma}\bigr) - \nu\bigl(B(y,r) \cap \mc{C}_{\sigma}\bigr)\Bigr| \leq \nu_dr^d\frac{d\|y - x\|}{(r - (d - 1)\|y - x\|)}
+	\end{equation*}
+\end{lemma}
+\begin{proof}
+	By the triangle inequality, 
+	\begin{align*}
+	\nu(B(x,r) \cap \mc{C}_{\sigma}) & = \int_{\mc{C}_{\sigma}} \1(\|z - x\| \leq r) \,dz \\
+	& \leq \int_{\mc{C}_{\sigma}} \1(\|z - y\| \leq r + \|y - x\|) \,dz \\
+	& = \int_{\mc{C}_{\sigma}} \bigl(\1(\|z - y\| \leq r) + \1(r < \|z - y\| \leq r + \|y - x\|) \bigr)  \,dz \\
+	& \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) + \nu_d\bigl((r + \|y - x\|)^d - r^d\bigr),
+	\end{align*}
+	and the upper bound $\nu(B(x,r) \cap \mc{C}_{\sigma}) \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) +  \nu_dr^dd\|y - x\|/(r - (d - 1)\|y - x\|)$ follows by Bernoulli's inequality (\textcolor{red}{(Lemma 22)}).
+Reversing $x$ and $y$ gives an equivalent upper bound on $\nu(B(y,r) \cap \mc{C}_{\sigma})$.
+\end{proof}
+
+\chapter{Misclassification error of PPR}
+The following Lemma upper bounds the misclassification error of (a sweep cut of) a PPR vector, in terms of the \emph{normalized cut} and \emph{mixing time} functionals.
 It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
 \begin{lemma}
-	\label{lem:zhu}
 	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
@@
 	\end{itemize}
-	From~\eqref{pf:zhu1}-\eqref{pf:zhu3}, we can upper bound the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
-First of all, observe that any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$.
-Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
-	\begin{equation}
-	\label{pf:zhu3.5}
+	From these we can derive the following upper bound on the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
+	\begin{itemize}
+		\item For any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
+		\begin{equation*}
 		\vol(S_{\beta,v} \setminus A; G) \leq \frac{1}{\beta} \sum_{u \not\in A}p_v^{(\varepsilon)}(u) \leq 2\frac{\Phi(A;G)}{\beta \cdot \alpha}.
-	\end{equation} 
-	Next, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$ for any $u \in A$:
+		\end{equation*} 
+		\item For any $u \in A$, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$,
 		\begin{equation*}
@@
 		\end{equation*}
-	If additionally $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
+		If $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
 		\begin{equation}
@@
 		\end{equation}
-	Let us restrict our attention for the moment to those vertices $u \in A$ with sufficiently large degree in $G[A]$. Defining
-	\begin{equation*}
-	A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\},
-	\end{equation*}
-	we note that for any $u \in A^{\mathrm{int}}$,
+
+		Let us restrict our attention for the moment to those vertices $u$ with sufficiently large degree in $G[A]$; precisely speaking, let
+		\begin{equation*}
+		A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\}.
+		\end{equation*}
+		We note that for any $u \in A^{\mathrm{int}}$,
 		\begin{equation*}
@@
 		\end{equation*}
-	plugging this in to~\eqref{pf:zhu4}, we have that
+		so that by~\eqref{pf:zhu4} it holds that
 		\begin{equation*}
@@
 		\end{equation*}
-	We conclude that
-	\begin{equation}
-	\label{pf:zhu5}
-	\vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{200\Phi(A;G)}{9\alpha}.
-	\end{equation}
-	Otherwise $u \in A \setminus A^{\mathrm{int}}$, and so $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$. Summing over all such vertices, we obtain
-	\begin{equation}
-	\label{pf:zhu6}
+		\item Finally, for every $u \in A \setminus A^{\mathrm{int}} $, it holds that $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$.
+Summing over all such vertices, we obtain
+		\begin{equation*}
 		\vol(A \setminus A^{\mathrm{int}};G) \leq \frac{\Phi(A;G)}{\alpha \cdot \beta}.
-	\end{equation} 
-	The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\ref{pf:zhu6}.
+		\end{equation*}	
+	\end{itemize}
 \end{proof}
 
-\paragraph{Proof of Theorem~\ref{thm: volume_ssd}.}
-First, we verify that the conditions of Lemma~\ref{lem:zhu} are met when $S = \Cset_{\sigma}[\Xbf]$, $G = G_{n,r}$, and the user-specified parameters satisfy the initialization conditions~\eqref{eqn: initialization}.
-By Theorem~\ref{thm: mixing_time_upper_bound} and \eqref{eqn: initialization}, the teleportation parameter $\alpha$ is upper bounded
-\begin{equation*}
-\alpha < \frac{1}{9\taubf(\theta)} \leq \frac{1}{9\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])}
-\end{equation*}
-with probability at least $1 - \frac{b_2}{n}$.
-Since we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets in Algorithm~\ref{alg: ppr}, we may apply Lemma~\ref{lem:zhu}.
-By this Lemma, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}(\frac{1}{100},\frac{2}{5})$, the sweep cut $S_{\beta,v}$ of $p(\alpha, v; G_{n,r})$ satisfies
-\begin{align}
-\vol_{n,r}(\Csig[\Xbf] \vartriangle S_{\beta,v}) & \leq \left(218\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}\right) \vol_{n,r}(\Csig[\Xbf]) \nonumber \\
-& \leq 2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf]) \label{eqn:volume_ssd_pf1}
-\end{align}
-where the latter inequality holds with probability at least $1 - 3\exp\set{-bn}$, and follows from Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_u(\theta)}$ given in \eqref{eqn: initialization}.
-
-Now we show that we can apply~\eqref{eqn:volume_ssd_pf1} to the cluster estimate $\Cest$ output by Algorithm~\ref{alg: ppr}.
-Observe that $\Cest$ is itself a sweep cut as $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{50},\frac{1}{5}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
-Moreover, applying  Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/2$,
-\begin{equation}
-\label{eqn:volume_ssd_pf2}
-\frac{1}{2}\vol_{\Pbb,r}(\Csig) \leq \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq \frac{3}{2}\vol_{\Pbb,r}(\Csig)
-\end{equation}
-with probability at least $1 - 2\exp\{-\frac{1}{4} n \vol_{\Pbb,r}(\Csig)^2\}$.
-Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\Cest \vartriangle \Csig[\Xbf])$.
-To summarize, we have shown that when
-\begin{equation*}
-n \geq b_1(\log(n))^{\max\{\frac{3}{d},1\}}
-\end{equation*}
-then
-\begin{equation*}
-\vol_{n,r}(\Csig[\Xbf] \vartriangle \Cest) \leq  2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
-\end{equation*} 
-with probability at least $1 - \frac{b_2}{n} - 3\exp\set{-(b + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
-We have proved Theorem~\ref{thm: volume_ssd} (upon appropriate choice of constants $b_2$ and $c$ in the theorem statement).
-
-\section{Proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}}
-\label{sec: proof_of_consistent_cluster_recovery}
-
-As a reminder, to prove Theorem~\ref{thm: consistent_recovery_of_density_clusters} it will be sufficient to show that
-\begin{equation}
-\label{eqn: PPR_gap}
-\max_{u' \in \Cset'[\Xbf]} \frac{p_v(u')}{\deg_{n,r}(u')} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\Csig)} < \frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\Csig)} \leq \min_{u \in \Cset[\Xbf]} \frac{p_v(u)}{\deg_{n,r}(u)}
-\end{equation}
-with probability at least $1 - \frac{b_2}{n}$.
-
-To show this, we first establish in Lemma~\ref{lem: setup} that when Algorithm \ref{alg: ppr} is properly initialized, the resulting PPR vector is large for every vertex $u \in \Cset$, and small for every vertex $u' \in \Cset'$.
-Let $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ be the vector given by\footnote{Note that $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.}
-\begin{equation*}
-\overline{\pibf}_{n,r}(u) := \frac{\widetilde{\deg}_{n,r}(u)}{\vol_{n,r}(\Csig[\Xbf])}.
-\end{equation*} Additionally, let $\degminpr = \min_{u \in \Cset'[\Xbf]} \deg_{n,r}(u')$.
-
-\begin{lemma} 
-	\label{lem: setup}
-	Let $0 < r < \sigma$ and $\alpha \leq \frac{1}{9 \tau_{\infty}(\widetilde{G}_{n,r})}$.
-Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$ such that the following bounds hold with respect to $\pbf_v := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
-	\begin{itemize}
-		\item For each $u \in \Cset[\Xbf]$,
-		\begin{equation}
-		\label{eqn: lower_bound_PPR_in_cluster}
-		\pbf_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminwt}
-		\end{equation}
-		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ be another $\lambda$-density cluster. Then for each $u' \in \Cset'[\Xbf]$,
-		\begin{equation}
-		\label{eqn: upper_bound_PPR_in_other_cluster}
-		\pbf_v(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminpr}.
-		\end{equation}
-	\end{itemize}
-\end{lemma}
-
-We immediately note that by assumption, Algorithm \ref{alg: ppr} is well-initialized, and therefore the seed node $v$ is chosen in $\Csig[\Xbf]^g$.
-Since we additionally assume $\Cset$ is a $\kappa$-well-conditioned density cluster, we have that $r < \sigma/(2d) < \sigma$, and the upper bound
-\begin{equation*}
-\alpha < \frac{1}{9\taubf(\theta)} \leq \frac{1}{(9 \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]))}
-\end{equation*}
-holds with probability at least $1 - \frac{b_2}{n}$.
-Therefore, all the conditions of Lemma \ref{lem: setup} are met.
-
-We now collect the estimates on graph functionals we will use to complete the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}. 
-\begin{itemize}
-	\item By Theorem~\ref{thm: conductance_upper_bound},
-	\begin{equation*}
-	\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\theta) 
-	\end{equation*}
-	with probability at least $1 - 3\exp\{-nb\}$. By \eqref{eqn: initialization}, $\alpha \geq 1/(10 \taubf(\theta))$ and therefore $2 \Phi(\Csig[\Xbf]; G_{n,r})/\alpha \leq 20 \kappa(\Cset)$.
-	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
-	\begin{equation*}
-	\degminwt \geq \frac{6}{25}(1 - \delta) \lambda_{\sigma} r^d \nu_d n,
-	\end{equation*}
-	with probability at least $1 - n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$.
-	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
-	\begin{equation*}
-	\degminpr \geq (1 - \delta) \lambda_{\sigma} r^d \nu_d n,
-	\end{equation*}
-	with probability at least $1 - n\exp\set{-\frac{\delta^2 \lambda_{\sigma} \nu_d r^d n}{3(1 + \frac{\delta}{3})}}$.
-
-	\item By Lemma~\ref{lem:ball_bounds_in_probability}, for any $\delta \in (0,1)$,
-	\begin{equation*}
-	d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_d r^d
-	\end{equation*}
-	with probability at least $1 - n\exp\set{-\frac{2\delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}}$.
-
-	\item 
-	\begin{equation*}
-	\widetilde{\vol}_{n,r}(\Csig[\Xbf]) \leq 2(1 + \delta) \vol_{\Pbb,r}(\Csig){n \choose 2}
-	\end{equation*}
-	with probability at least $1 - \exp\set{-\delta^2 (\vol_{\Pbb,r}(\Csig))^2}$.
-\end{itemize}
-
-In the rest of this proof we assume the above bounds hold. For all $u \in \Cset[\Xbf]$, $\widetilde{\deg}_{n,r}(u) = \deg_{n,r}(u)$, so by \eqref{eqn: lower_bound_PPR_in_cluster},
-\begin{align*}
-\frac{p_v(u)}{\deg_{n,r}(u)} & \geq \frac{4}{5 \vol_{n,r}(\Csig[\Xbf])} - \frac{20 \kappa(\Cset)}{\widetilde{d}_{\min}^2} \\
-& \geq \frac{4}{5(1+\delta)\vol_{\Pbb,r}(\Csig)n^2} - \frac{20\kappa(\Cset)}{\left(\frac{6}{25}(1 - \delta)\lambda_{\sigma}\nu_dr^dn\right)^2} \\
-& \geq \frac{1}{10{n \choose 2}\vol_{\Pbb,r}(\Csig)},
-\end{align*}
-where the last inequality follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}. For all $u' \in \Cset'[\Xbf]$, 
-\begin{align}
-\frac{p_v(u')}{\deg_{n,r}(u')} & \leq \frac{20\kappa(\Cset)}{(d_{\min}')^2} \nonumber \\
-& \leq \frac{20\kappa(\Cset)}{\left((1 - \delta)\lambda_{\sigma}\nu_dr^dn\right)^2} \nonumber \\
-& \leq \frac{1}{100{n \choose 2}\vol_{\Pbb,r}(\Csig)} \label{eqn:consistent_recovery_of_density_clusters_pf1}
-\end{align}
-where the last inequality again follows by choosing $\delta = 1/2$ and \eqref{eqn: kappa_ub}.
-We have shown~\eqref{eqn: PPR_gap} and therefore proved Theorem~\ref{thm: consistent_recovery_of_density_clusters} (upon an appropriate choice of constants $b_2$ and $c$ in the statement of the theorem).
-
-% (choosing $b_2 = c_4(\Pbb,r) + \frac{6}{b} + \frac{900}{\lambda_{\sigma}\nu_dr^d} + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2$).
-
-We defer the proof of Lemma \ref{lem: setup}, and first extend Theorems~\ref{thm: volume_ssd} and \ref{thm: consistent_recovery_of_density_clusters} to apply with respect to the aPPR vector.
-
-\subsection{Proof of Corollary~\ref{cor: appr}.}
-\label{sec:appr}
-To prove the first claim of Corollary~\ref{cor: appr}, it will be sufficient to show that the conditions of Lemma~\ref{lem:zhu} are still met when we use the approximate PPR vector $p^{(\varepsilon)}_v$ rather than the exact PPR vector $p_v$.
-In particular, we must show that $\varepsilon \leq \frac{1}{20}\vol_{n,r}(\Csig)$.
-However by Lemma~\ref{lem:ball_bounds_in_probability},
-\begin{equation}
-\label{eqn:appr_pf1}
-\vol_{n,r}(\Csig[\Xbf]) \geq (1 - \delta)\vol_{\Pbb,r}(\Csig)
-\end{equation}
-with probability at least $1 - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2}$, and by setting $\delta = 1/5$ the desired claim follows.
-
-We now prove the second claim, by showing that both bounds in \eqref{eqn: PPR_gap} hold with respect to the aPPR vector.
-The upper bound follows immediately.
-Since $p^{(\varepsilon)}_v(x) \leq p_v(x)$ for all $x \in \Xbf$, the upper bound on $\max_{u' \in \Cset'[\Xbf]} p_v(u')$ also applies to $\max_{u' \in \Cset'[\Xbf]} p^{(\varepsilon)}_v(u')$.
-
-To show the desired lower bound on $\min_{u \in \Cset[\Xbf]} p^{(\varepsilon)}_v(u)$, we use the uniform approximation guarantee in \eqref{eqn: appr_error}.
-As previously observed, since $r < \sigma$, for any $u \in \Csig$ the ball $B(u,r) \subseteq \Csig$, and so $\widetilde{\deg}_{n,r}(u) = \deg_{n,r}(u)$.
-Along with \eqref{eqn: appr_parameter} and \eqref{eqn:appr_pf1}, this means
-\begin{equation*}
-\varepsilon \deg_{n,r}(u) \leq \frac{\overline{\pi}_{n,r}(u)}{25(1 - \delta)}
-\end{equation*}
-and therefore by \eqref{eqn: lower_bound_PPR_in_cluster}, for every $u \in \Cset[\Xbf]$,
-\begin{equation*}
-p^{(\varepsilon)}_v(u) \geq \left\{\frac{4}{5} - \frac{1}{25(1 - \delta)}\right\} \overline{\pi}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])/\alpha}{\degminwt}.
-\end{equation*}
-\noindent Using the arguments given in the proof of Theorem~\ref{thm: consistent_recovery_of_density_clusters}, and choosing the universal constant in \eqref{eqn: kappa_ub} to be sufficiently small, the upper bound in \eqref{eqn:consistent_recovery_of_density_clusters_pf1} follows.
-
-\subsection{Proof of Lemma~\ref{lem: setup}}
-
-In this subsection, we will let $\Dbf$ and $\Wbf$ be the degree and lazy random walk matrices over $G_{n,r}$.
-Additionally we let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and lazy random walk matrices over the induced subgraph $\widetilde{G}_{n,r}$.
-Given a starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
-	\begin{equation}
-	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}
-	\end{equation}
-	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$.
-(When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).
-
-	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
-	\begin{align}
-	\label{eqn: leakage_soakage}
-	\ell_t & := e_v (\Wbf \widetilde{I} )^t (I - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
-	s_t & := e_v (\Wbf \widetilde{I} )^t (\Wbf \widetilde{I}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
-	\end{align}
-	where $I$ is the $n \times n$ identity matrix, $\widetilde{I}$ is an $n \times n$ diagonal matrix with $\widetilde{I}_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{I}^c = I - \widetilde{I}$.
-
-	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $\Csig[\Xbf]$ on the $t + 1$th step.
-For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$.
-By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is ``soaked up'' into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$.
-The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.
-
-	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation.
-By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
-	\begin{equation}
-	\label{eqn: zhulemma3.1}
-	\pbf_v(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
-	\end{equation}
-	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)
-
-	If additionally $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
-	\begin{equation*}
-	\widetilde{\pbf}_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
-	\end{equation*}
-	and along with \eqref{eqn: zhulemma3.1}, we obtain
-	\begin{equation*}
-	\pbf_v(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
-	\end{equation*}
-
-	We proceed to show the upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \degminwt$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}.
-We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$.
-	\begin{enumerate}
-		\item Since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.
-		\item For any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$ and $u \not\in \mathrm{supp}(q)$, and any $t \geq 1$,
-		\begin{align}
-		\label{eqn: one_step_bound}
-		q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 \max_{v \neq u} W_{vu} \nonumber \\
-		& \leq \frac{1}{2\degminwt} 
-		\end{align}
-		where last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.
-	\end{enumerate}
-
-	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
-	\begin{align*}
-	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}^t \right)(u)  \nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
-	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}^t \right)(u)\nonumber \\
-	& \leq \frac{\norm{\ell}_1 }{\degminwt}. \tag{since $u \not\in \mathrm{supp}(\ell)$}
-	\end{align*}
-	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.
-
-	We turn to showing \eqref{eqn: upper_bound_PPR_in_other_cluster}. By Lemma \ref{lem: soakage_ppr_lb}, for all $u' \not\in \Csig[\Xbf]$,
-	\begin{equation*}
-	\pbf_v(u') \leq \pbf_s(u').
-	\end{equation*}
-
-	Note that by \ref{asmp: low_noise_density}, $\dist(\Csig,\Cset') > r$.
-Therefore for every $u \in \Csig[\Xbf]$ and $u' \in \Cset'[\Xbf]$ $(u',u) \not\in E$ and so $s(u') = 0$.
-Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
-	\begin{align*}
-	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
-	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf^t\right)(u') \\
-	& \leq \frac{\norm{s}_1}{2\degminpr}
-	\end{align*}
-	where the last inequality follows from precisely the same reasoning as \eqref{eqn: one_step_bound}.
-The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
-
-\subsection{Linear Algebra Facts}
-\label{sec: linalg}
-
-We state here a number of basic facts which follow from matrix manipulations, which are used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.
-
-\begin{lemma}
-	\label{lem: soakage_ppr_lb}
-	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
-	\begin{equation*}
-	\pbf_{v}(u) \leq \pbf_{s}(u)
-	\end{equation*}
-	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
-\end{lemma}
-\begin{proof}
-	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
-	\begin{align*}
-	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
-	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf^T\right)(u) \\
-	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf^{T - t - 1} \right)(u)\\
-	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf^{\Delta} \right)(u) \\
-	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf^{\Delta} \right)(u) \\
-	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf^{\Delta}\right)(u) \\
-	& = \pbf_s(u)
-	\end{align*}
-\end{proof}
-
-Let $s_t := q(\Wbf \Ibf{S})^t(\Wbf(\Ibf{S^c}))$ be the soakage vector out of $S \subseteq V$, where $\Ibf{S}$ is a $\abs{V} \times \abs{V}$ diagonal matrix with $(\Ibf{S})_{uu} = 1$ if $u \in S$ and 0 otherwise, and $\Ibf{S^c} := \Ibf{} - \Ibf{S}$.
-\begin{lemma}
-	\label{lem: sum_of_soakages}
-	Let $G = (V,E)$ be an unweighted, undirected graph with associated random walk matrix $\Wbf$. For any $T \in \mathbb{N}, T \geq 1$, $q \in \Reals^{\abs{V}}$, and $S \subseteq V$
-	\begin{equation}
-	\label{eqn: sum_of_soakages}
-	q\Wbf^T = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} + q(\Wbf \Ibf{S})^T
-	\end{equation}
-	In particular, if $u \in V\setminus S$, then
-	\begin{equation}
-	\label{eqn: sum_of_soakages_2}
-	q\Wbf^T(u) = \sum_{t = 0}^{T - 1} \left(s_t \Wbf^{T - t - 1}\right)(u)
-	\end{equation}
-\end{lemma}
-\begin{proof}	
-	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.
-	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,
-	\begin{equation*}
-	q\Wbf = q\Wbf\Ibf{S} + q\Wbf\Ibf{S^c} =  q\Wbf\Ibf{S} + s_0. 
-	\end{equation*}
-
-	Then, for $T \in \mathbb{N},~ T \geq 2$,
-	\begin{align*}
-	q\Wbf^{T} & = q\Wbf^{T - 1}{\Wbf} \\
-	& = \left\{\sum_{t = 0}^{T - 2} s_t \Wbf^{T - 2 - t} + q(\Wbf \Ibf{S})^{T - 1} \right\} \Wbf \tag{by the inductive hypothesis}\\
-	& = \sum_{t = 0}^{T - 2} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S} + \Wbf \Ibf{S^c}) \\
-	& = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S})
-	\end{align*}
-	and the proof is complete.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: total_leakage_equal_total_soakage}
-	Letting $s_t$, $\ell_t$ $s$ and $\ell$ be as in \eqref{eqn: leakage_soakage},
-	\begin{equation*}
-	\norm{s_t}_1 = \norm{\ell_t}_1,~ \textrm{for each $t \geq 0$}
-	\end{equation*}
-	and therefore $\norm{s}_1 = \norm{\ell}_1$. 
-\end{lemma}
-\begin{proof}
-	By the definition of $s_t$ and $\ell_t$, we have
-	\begin{align*}
-	\norm{s_t}_1 & = \norm{q_t (\Wbf \widetilde{I}^c)}_1 \\
-	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf \widetilde{I}^c)(u, u') \\
-	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf)_{uu}} \1((u,u') \in G_{n,r}) \\
-	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf)_{uu} - (\widetilde{\Dbf})_{uu} \right)}{(\Dbf)_{uu}} \\
-	& = \norm{q_t (\Ibf{} - \Dbf^{-1} \widetilde{\Dbf})}_1 = \norm{\ell_t}_1.
-	\end{align*}
-\end{proof}
-
-\section{Proof of Lower Bound.}
-
-To prove Theorem~\ref{thm:ppr_lb}, we will proceeding according to the following steps:
-\begin{enumerate}
-	\item We study the spectral partitioning properties of PPR on an arbitrary graph $G$, and show that when suitably initialized inside a subset $S \subset V$, the normalized cut of the PPR sweep cut is upper bounded by (a function of) $\Phi(S;G)$.
-	\item We specialize to the graph $G = G_{n,r}$ and the subset $\mathcal{L}[\Xbf] \subset \Xbf$, and show that the normalized cut $\Phi_{n,r}(\mathcal{L}[\Xbf])$ is small (with high probability) when the diameter $\rho$ is large.
-	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\ref{alg: ppr} $\Cest$ must therefore also have small normalized cut.
-	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Cset^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Cset^{(1)}[\Xbf])$.
-In fact, we generalize this to hold for any set $A \subset \Xbf$ for which the symmetric set distance metric $\Delta(A,\Cset_1[\Xbf])$ is small.
-	\item We conclude that the symmetric set distance metric $\Delta(\Cest,\Cset^{(1)}[\Xbf])$ must not be small.
-\end{enumerate}
-
-We devote the subsequent sections to proving each of the aforementioned steps.
-
-\subsection{Spectral partitioning properties of PPR.}
-
-Let $G = (V,E)$ be an undirected, unweighted graph with $m = \abs{E}$ total edges, defined on vertices $V = \set{v_1, \ldots, v_n}$.
-Let $C$ be a subset of the vertices $V$, Recall that for a given $\beta \in (0,1)$ the sweep cut
-\begin{equation*}
-S_{\beta,v} = \set{u \in V: \frac{p_v(u)}{\deg(u;G)} > \beta}
-\end{equation*} 
-The following theorem relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of $C$; it is stated with respect to the graph functionals 
-\begin{equation*}
-d_{\max} := \max_{u \in V} \deg(u;G), ~~\textrm{and}~~ d_{\min} := \min_{u \in V} \deg(u;G).
-\end{equation*}
-\begin{theorem}
-	\label{thm:conductance_ppr}
-	Let $C \subseteq V$ satisfy the following conditions:
-	\begin{itemize}
-		\item $\vol(C;G) \leq \frac{2}{3}\vol(G)$,
-		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
-		\item $\frac{20\Phi(C;G)}{1 + 10\Phi(C;G)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
-	\end{itemize}
-	Suppose $60\Phi(C;G) \leq \alpha \leq 70\Phi(C;G)$, and let $(L,U) = (0,1)$.
-Then, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$ such that for any $v \in C^g$ the following statement holds: For the PPR vector $p_v := p(v,\alpha;G)$, the minimum conductance sweep cut set satisfies
-	\begin{equation*}
-	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C;G)}
-	\end{equation*}
-\end{theorem}
-Although this theorem appears quite similar to standard results in the PPR literature -- for instance, Theorem 6 of \citet{andersen2006} -- crucially the above bound depends on $\log\left(\frac{m}{d_{\min}^2}\right)$ rather than $\log m$.
-In the case where $d_{\min} \asymp n$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$.
-
-Notwithstanding these improvements, the proof of Theorem~\ref{thm:conductance_ppr} follows the same general outline as the proof of Theorem~6 of \citet{andersen2006}.
-We now walk through this outline step by step, modifying the results of \citet{andersen2006} as needed.
-As with their work, we begin by proving a mixing time bound on the PPR vector $p_v$.
-
-\subsubsection{Mixing time of PPR.}
-
-To quantify the mixing of a PPR vector $p_v$, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$.
-For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that $S_{\beta_j}$ contains at least $j$ vertices.
-(For notational ease, we will write $S_{i} := S_{\beta_i}$, so that $S_1,S_2,\ldots,S_n$ comprise the $n$ unique sweep cuts of $p_v$.)
-For each $j = 1,\ldots,n$, we let $p[\vol(S_j)] =  \sum_{u \in S} p_v(u)$.
-Additionally, we let $p[0] = 0$ and $p[2m] = 1$.
-Finally, we extend $p[\cdot]$  by piecewise interpolation to be defined everywhere on its domain.
-The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$, defined as
-\begin{equation*}
-h(k) = p[k] - \frac{k}{2m}.
-\end{equation*}
-Next, for a given $0 \leq K_0 \leq m$, let 
-\begin{equation*}
-L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
-\end{equation*}
-be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$, and additionally let
-\begin{equation*}
-C(K_0) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
-\end{equation*}
-where we use the notation $\overline{k} := \min\{k, 2m - k\}$.
-
-Theorem~\ref{thm:mixing_time_PPR} implies that if the PPR random walk is not well mixed, then some sweep cut of $p_v$ must have small normalized cut.
-\begin{theorem}
-	\label{thm:mixing_time_PPR}
-	Let $p_v = p(v,\alpha;G)$ be a PPR vector, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$, any $0 < K_0 < m$, and any $k \in [K_0,2m - K_0]$:
-	\begin{equation}
-	\label{eqn:mixing_time_PPR}
-	h(k) \leq \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
-	\end{equation}
-	or else there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
-\end{theorem}
-
-\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_PPR}).]
-	The proof of Theorem~\ref{thm:mixing_time_PPR} is essentially a combination of the proofs of Theorem~3 in \citet{andersen2006} and Theorem 1.2 in \citet{lovasz1990}.
-We will show that if $\Phi(S_j) > \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in (K_0,2m - K_0)$.
-
-	We proceed by induction on $t$. Our base case will be $t = 0$. Observe that $C(K_0) \cdot \sqrt{\overline{k}} \geq  h(k) - L_{K_0}(k)$ for all $k \in [K_0,2m - K_0]$, which implies
-	\begin{equation*}
-	L_{K_0}(k) + C(K_0) \cdot \sqrt{\overline{k}} \geq h(k).
-	\end{equation*}
-
-	Now, we proceed with the inductive step.
-By the definition of $L_{K_0}$, the inequality~\eqref{eqn:mixing_time_PPR} holds when $k = K_0$ or $k = 2m - K_0$.
-We will additionally show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$.
-Once this is shown, the concavity of the expression on the right-hand side of~\eqref{eqn:mixing_time_PPR} implies that the inequality holds for all $k \in [K_0,2m - K_0]$.
-
-	By Lemma 5 of \citet{andersen2006}, we have that
-	\begin{align}
-	p[k_j] & \leq \alpha + \frac{1}{2}  \left(p[k_j - \abs{\partial(S_j)}] + p[k_j + \abs{\partial{S_j}}]  \right) \nonumber\\
-	& \leq \alpha + \frac{1}{2} \left(p[k_j - \Phi(S_j) \overline{k}_j] + p[k_j + \Phi(S_j) \overline{k}_j]  \right) \nonumber \\
-	& \leq \alpha + \frac{1}{2} \left(p[k_j - \phi \overline{k}_j] + p[k_j + \phi \overline{k}_j]\right) \nonumber
-	\end{align}
-	and subtracting $k_j/2m$ from both sides, we get
-	\begin{equation}
-	\label{eqn:mixing_time_PPR_pf1}
-	h(k_j) \leq \alpha + \frac{1}{2} \bigl(h(k_j - \phi \overline{k}_j) + h(k_j +  \phi \overline{k}_j) \bigr)
-	\end{equation}
-	From this point, we divide our analysis into cases.
-
-	\textbf{Case 1.}
-	Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$.
-We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
-	\begin{align*}
-	h(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
-	& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
-	& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
-	\end{align*}
-	A Taylor expansion of $\sqrt{1 + \phi}$ around $\phi = 0$ yields the following bound:
-	\begin{equation*}
-	\sqrt{1 + \phi} + \sqrt{1 - \phi} \leq 2 - \frac{\phi^2}{4},
-	\end{equation*}
-	and therefore
-	\begin{equation*}
-	h(k_j) \leq  \alpha t + L_{K_0}(k) + \frac{C(K_0)}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
-	\end{equation*}
-
-	\textbf{Case 2.}
-
-	Now, assume one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$.
-Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
-By the concavity of $h$, and applying the inductive hypothesis to $h(2k_j - K_0)$, we have
-	\begin{align*}
-	h(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0) + L_{K_0}(2k_j - K_0\bigr) + C(K_0)\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
-	& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
-	& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
-	\end{align*}
-\end{proof}
-
-As a sanity check, we confirm that Theorem~\ref{thm:mixing_time_PPR} is no weaker than Theorem~3 of \citet{andersen2006}.
-It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0) \leq 1$ for any $K_0$.
-Setting $K_0 = 0$ in Theorem~\ref{thm:mixing_time_PPR}, we therefore recover Theorem~3 of \citet{andersen2006}.
-
-We now proceed to identify when Theorem~\ref{thm:mixing_time_PPR} may offer some improvement on Theorem~3 of \citet{andersen2006}, by showing when we can upper bound $C(K_0) << 1$.
-The critical point is that since $h(k)$ is concave and $L_{K_0}(K_0) = h(K_0)$ the upper bound
-\begin{equation*}
-\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq h'(K_0) \sqrt{k}
-\end{equation*}
-holds whenever $k < m$. For similar reasons, when $k > m$, 
-\begin{equation*}
-\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq -h'(2m - K_0) \sqrt{2m - k}.
-\end{equation*} 
-(Since $h$ is not differentiable at points $k = \vol(S_j)$, here we use $h'$ to denote the left derivative of $h$ whenever $k < m$, and the right derivative of $h$ whenever $k \geq m$)
-
-The following Lemma gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, and a resulting upper bound on $C(K_0)$.
-\begin{lemma}
-	\label{lem:linearization_bound}
-	There exists $K_0 \in \set{0,\deg(v;G)}$ such that
-	\begin{equation}
-	\label{eqn:left_derivative}
-	h'(K_0) \leq  \frac{1}{2d_{\min}^2}.
-	\end{equation}
-	Additionally, for all $K_0 \in [0,2m]$,
-	\begin{equation}
-	\label{eqn:right_derivative}
-	h'(2m - K_0) \geq -\frac{d_{\max}}{d_{\min}\vol(G)}.
-	\end{equation}
-	As a result,
-	\begin{equation*}
-	C(K_0) \leq \frac{\sqrt{m}}{d_{\min}^2}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
-	The result of the Lemma is obvious once we show \eqref{eqn:left_derivative} and \eqref{eqn:right_derivative}.
-To show either inequality, it will be useful to work with an alternative representation of $h$.
-In particular,  whenever $\vol(S_j) \leq k < \vol(S_{j + 1})$ (where we let $S_0 = \emptyset$), the function $h(k)$ may be written as
-	\begin{equation}
-	\label{eqn:lovasz_simonovits}
-	h(k) = \sum_{i = 0}^{j} \left(p_v(u_{(i)}) - \pi(u_{(i)};G)\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(p_v(u_{(j+1)}) - \pi(u_{(j+1)};G)\right) 
-	\end{equation}
-	where the vertices are ordered $\frac{p_v(u_{(1)})}{\deg(u_{(1)};G)} \geq \frac{p_v(u_{(2)})}{\deg(u_{(2)};G)} \geq \cdots \geq \frac{p_v(u_{(n)})}{\deg(u_{(n)};G)}$, and as usual $\pi(u;G) = \frac{\deg(u;G)}{\vol(G)}$.
-
-	From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
-	\begin{equation}
-	\label{eqn:linearization_bound_pf1}
-	h'(k) \leq \frac{p(v_{(j + 1)})}{\deg(v_{(j + 1)};G)}
-	\end{equation}
-
-	We now upper bound $p(u)$ uniformly over all $u$ except the seed node $v$. For any $u \in V$ besides the seed node $v$, we can show by induction that
-	\begin{equation*}
-	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
-	\end{equation*} 
-	for any $t \geq 0$, and therefore
-	\begin{equation}
-	\label{eqn:linearization_bound_pf2}
-	p(\alpha,\chi_v)(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \leq  \frac{1}{2d_{\min}}.
-	\end{equation}
-	As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = \deg(v;G)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}.
-The inequality \eqref{eqn:right_derivative} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since
-	\begin{equation*}
-	h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}},
-	\end{equation*}
-	and the proof of the Lemma is therefore complete.
-\end{proof}
-
-To apply Theorem~\ref{thm:mixing_time_PPR}, we must also upper bound the linear interpolator $L_{K_0}(k)$.
-Of course, trivially $L_{K_0}(k) \leq \max\set{h(K_0), h(2m - K_0)}$ for all $k$.
-As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$.
-\begin{lemma}
-	\label{lem:interpolator_bound}
-	Assume $s = \chi_v$ for some $v \in V$. Let $K_0 = \vol(S_j)$ for some $j = 0,\ldots,n$. Then, 
-	\begin{equation*}
-	h(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h(K_0) \leq \frac{K_0}{2d_{\min}^2} + \frac{2\alpha}{1 + \alpha}.
-	\end{equation*}
-	and as a result for any $k \in \Reals$,
-	\begin{equation*}
-	L_{K_0}(k) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound})]
-	We make use of the representation~\eqref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
-	\begin{align*}
-	h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
-	& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
-	& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
-	\end{align*}
-
-	We will upper bound $h(K_0)$ by $p[\vol(S_j)] \leq p_v(v) + \sum_{u \in S_j \setminus \set{v}}p_v(u)$.
-In the proof of Lemma~\ref{lem:linearization_bound} we have already given an upper bound on $p_v(u)$ when $u \neq v$.
-Now, we additionally observe that for all $t$,
-	\begin{equation*}
-	e_vW^t(v) \leq \frac{1}{2d_{\min}} + \left(\frac{1}{2}\right)^t
-	\end{equation*}
-	and therefore $p_v(v) \leq \frac{1}{2d_{\min}} + \frac{2\alpha}{1 + \alpha}$.
-	As a result,
-	\begin{equation}
-	h(K_0) \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
-	\end{equation}
-	where the latter inequality follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.
-\end{proof}
-
-Combining Theorem~\ref{thm:mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound}, we have the following result.
-\begin{corollary}
-	\label{cor:mixing_time_PPR}
-	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$, and let $\phi$ be any constant in $[0,1]$.
-Then, either the following bound holds for any integer $t$ and any $k \in [d_{\max},2m - d_{\min}]$:
-	\begin{equation*}
-	h(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t}
-	\end{equation*}
-	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
-\end{corollary}
-
-We arrive now at the main result of this section.
-It is similar in form to Theorem 2 of \citet{andersen2006} but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR}.
-To simplify notation, we will write the total mass placed by $p_v$ on a subset $S \subset V$ as $p_v(S) := \sum_{u \in S} p_v(u)$.
-\begin{theorem}
-	\label{thm:mixing_time_PPR_contrapositive}
-	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$. Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}}{2d_{\min}^2}$, such that
-	\begin{equation}
-	\label{eqn:mixing_time_PPR_contrapositive_1}
-	p_v(S) - \frac{\vol(S;G)}{\vol(G)} > \delta
-	\end{equation}
-	for a set $S$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$. Then there exists a sweep cut $S_j$ of $p$, such that
-	\begin{equation*}
-	\Phi(S_j) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
-	\end{equation*}
-	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
-\end{theorem}
-\begin{proof}
-	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}.
-Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.
-
-	Now, letting
-	\begin{equation*}
-	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
-	\end{equation*}
-	we have that
-	\begin{equation*}
-	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
-	\end{equation*}
-	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
-\end{proof}
-
-\subsubsection{Improved Local Partitioning with PPR.}
-
-As in \citet{andersen2006}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\Cest;G)$.
-First, we restate a theorem of \citet{andersen2006} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.
-
-\begin{theorem}
-	\label{thm:acl_3}
-	For any set $C$ and any constant $\alpha$, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$, such that for any vertex $v \in C^g$, the PPR vector $p(v,\alpha;G)$ satisfies
-	\begin{equation*}
-	p(v,\alpha;G) \geq 1 - 6\frac{\Phi(C;G)}{\alpha}.
-	\end{equation*}
-\end{theorem}
-We are now in a position to prove Theorem~\ref{thm:conductance_ppr} by combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3}.
-
-\begin{proof}[Proof (of Theorem~\ref{thm:conductance_ppr})]
-	Since $\alpha \geq 60\Phi(C)$ and $v \in C^g$, by Theorem~\ref{thm:acl_3},
-	\begin{equation*}
-	p_v(C) \geq \frac{9}{10}.
-	\end{equation*}
-	This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p_v(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$.
-Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{thm:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$.
-Therefore, the minimum conductance sweep cut satisfies
-	\begin{equation*}
-	\min_{j = 1,\ldots,n} \Phi(S_j;G) \leq \sqrt{\frac{1120\cdot \Phi(C;G)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
-	\end{equation*}
-	Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
-	\begin{equation*}
-	\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
-	\end{equation*}
-	completing the proof of the theorem.
-\end{proof}
-
-\subsection{Normalized cut of $\mathcal{L}[\Xbf]$.}
-
-Recall that for any set $\mathcal{A} \subset \mathcal{X}$, the $\Pbb$-weighted \emph{cut} and \emph{volume} functionals can be written as
-\begin{equation*}
-\cut_{\Pbb,r}(\Aset) = \int_{\Aset} \int_{\mathcal{X} \setminus \Aset} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y), \vol_{\Pbb,r}(\Aset):= \int_{\Aset} \int_{\mathcal{X}} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y),
-\end{equation*}
-and the continuous \emph{normalized cut} is
-\begin{equation*}
-\Phi_{\Pbb,r}(\Aset) := \frac{\cut_{\Pbb,r}(\Aset)}{\min\{\vol_{\Pbb,r}(\Aset),\vol_{\Pbb,r}(\mathcal{X} \setminus \Aset)\}}.
-\end{equation*}
-
-We now upper bound the normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ as a function of the diameter $\rho$, and the neighborhood graph radius $r$.
-Our bounds will be simple and not tight, but will display the right dependence on these parameters, and so will be sufficient for our purposes.
-
-To upper bound $\cut_{\Pbb,r}(\mathcal{L})$, note that for any $x = (x_1,x_2) \in \mathcal{L}$, if $x_2 \leq -r$ the ball $B(x,r)$ and the set $\mathcal{X}\setminus\mathcal{L}$ are disjoint.
-This implies
-\begin{align*}
-\cut_{\Pbb,r}(\mathcal{L}) & \leq \Pbb(\set{x \in \mathcal{X}: -r < x_2 < 0}) \cdot \max_{x \in \mathcal{X}} \Pbb(B(x,r)) \\
-& \leq \frac{r}{2 \rho} \cdot \frac{\pi r^2}{2 \sigma \rho}.
-\end{align*}
-By symmetry, $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, and therefore to upper bound $\Phi_{\Pbb,r}(\mathcal{L})$, it is sufficient to lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
-We have
-\begin{align*}
-\vol_{\Pbb,r}(\mathcal{L}) & \geq \Pbb(\set{x \in \Cset_1 \cap \mathcal{L}: \dist(x, \partial \Cset_1) > r}) \cdot \frac{\pi r^2}{2 \sigma \rho} \\
-& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\nu_d r^d}{2 \sigma \rho}  \\
-& \geq \frac{3}{16} \cdot \frac{\pi r^2}{2 \sigma \rho}
-\end{align*}
-where the last inequality follows since $r \leq \frac{1}{4}\sigma < \frac{1}{4}\rho$. Therefore, $\Phi_{\Pbb,r}(\mathcal{L}) \leq \frac{8r}{3\rho}.$
-
-Then, Lemma~\ref{lem:graph_functional_concentration} implies that the graph functionals $\cut_{n,r}(\mathcal{L}[\Xbf])$ and $\vol_{n,r}(\mathcal{L}[\Xbf])$--and in turn $\Phi_{n,r}(\mathcal{L}[\Xbf])$-- concentrate around their expectations.
-Precisely, we have that
-\begin{align}
-\Phi_{n,r}(\mathcal{L}[\Xbf]) & = \frac{\cut_{n,r}(\mathcal{L}[\Xbf])}{\min\set{\vol_{n,r}(\mathcal{L}[\Xbf]),\vol_{n,r}((\mathcal{X}\setminus\mathcal{L})[\Xbf])}} \nonumber \\
-& \leq \frac{3}{2}\Phi_{\Pbb,r}(\Aset) \leq \frac{4 r}{\rho} \label{eqn:lb_pf2}
-\end{align}
-with probability at least $1 - 3\exp\{-\frac{1}{25}n(\cut_{\Pbb,r}(\mathcal{L}))^2\}$.
-
-\subsection{Normalized cut of $\Cest$.}
-
-To upper bound $\Phi_{n,r}(\Cest)$, we need to show that the conditions of Theorem~\ref{thm:conductance_ppr} are met with respect to the graph $G = G_{n,r}$ and subset $C = \mathcal{L}[\Xbf]$.
-To do, we require the following inequalities, which are satisfied with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2\delta^2n}{8 \rho \sigma(1 + \frac{\delta}{3})}} - 6 \exp\set{-n\delta^2(\cut_{\Pbb,r}(\mathcal{L}[\Xbf]))^2}$:
-\begin{itemize}
-	\item For any $r \in (0,\frac{1}{4}\sigma)$ and any $x \in \mathcal{X}$,
-	\begin{equation*}
-	\frac{\epsilon}{4\rho\sigma}\pi r^2 \leq \Pbb((B(x,r))) \leq  \frac{1}{2\rho\sigma} \pi r^2.
-	\end{equation*}
-	Therefore by Lemma~\ref{lem:bernstein_union}, $\frac{(1 - \delta)\epsilon \pi r^2}{4\rho \sigma}n \leq d_{\min} \leq d_{\max} \leq \frac{(1 + \delta)\pi r^2}{2\rho \sigma }n$. 
-	\item $\frac{(1 - \delta)}{2} n \leq \abs{\mathcal{L}[\Xbf]} \leq \frac{(1 + \delta)}{2} n$, 
-	\item $\vol_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta)\vol_{\Pbb,r}(\mathcal{L}) = \frac{(1 + \delta)}{2} \vol_{\Pbb,r}(\mathcal{X}) \leq \frac{(1 + \delta)}{2} \vol(G_{n,r})$, and
-	\item $(1 - \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf]) \leq \cut_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf])$.
-\end{itemize}
-We now condition on these inequalities, and letting $\delta = \frac{2}{67}$ we verify that under the setup of Theorem~\ref{thm:ppr_lb}, each of the conditions of Theorem~\ref{thm:conductance_ppr} are met:
-\begin{itemize}
-	\item $\vol(\mathcal{L}[X]) \leq \frac{(1 + \delta)}{2(1 - \delta)}\vol(G_{n,r}) \leq \frac{2}{3}\vol(G_{n,r})$ since $\delta < 1/7$,
-	\item $\abs{\mathcal{L}[X]} \geq \frac{n(1 - \delta)}{2} \geq \frac{2(1 + \delta)}{(1 - \delta)\epsilon} \geq \frac{d_{\max}}{d_{\min}}$ and $\frac{d_{\max}}{2d_{\min}^2} \leq \frac{8(1 + \delta)}{(1 - \delta)^2 \epsilon^2 \rho \sigma \pi r^2} \cdot \frac{1}{n} \leq \frac{1}{10}$ by the assumed lower bound on the sample size,
-	\item $\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{4r}{\rho} \leq \frac{1}{10}$, by assumption on $r$ and $\rho$, and
-	\item $60\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{60(1 + \delta)}{1 - \delta}\Phi_{\Pbb,r}(\mathcal{L}) \leq \alpha \leq \frac{65(1 + \delta)}{1 - \delta}\Phi_{n,r}(\mathcal{L}[X]) \leq 70\Phi_{n,r}(\mathcal{L}[X])$ since $\delta < 2/67$.
-\end{itemize}
-
-We may therefore apply Theorem~\ref{thm:conductance_ppr}, which allow us to upper bound the minimum conductance sweep cut $\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G)$ or equivalently the output of Algorithm~\ref{alg: ppr}.
-
-To be precise, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6} \vol_{n,r}(\mathcal{L}[\Xbf])$, such that the following statement holds for any $v \in \mathcal{L}[\Xbf]^g$: when Algorithm~\ref{alg: ppr} is run with inputs $\Xbf, r < \frac{1}{4}\sigma,\alpha = 65 \Phi_{\Pbb,r}(\mathcal{L}[\Xbf]),v \in \mathcal{L}[\Xbf]^g$ and $(L,U) = (0,1)$, the resulting PPR cluster estimate $\Cest$ satisfies
-\begin{align}
-\Phi_{n,r}(\Cest) & \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi_{n,r}(\mathcal{L[X]})} \nonumber \\
-& \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}} \label{eqn:lb_pf4} 
-\end{align}
-with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2 n}{8978 \rho \sigma}} - 6 \exp\set{-\frac{1}{1123}(\cut_{\Pbb,r}(\mathcal{L}))^2n}$ (where the latter inequality follows from \eqref{eqn:lb_pf2} and Lemma~\ref{lem:graph_functional_concentration}.)
-
-\subsection{Lower bound on normalized cut.}
-
-The precise statement we will prove is contained in the following Lemma.
-\begin{lemma}
-	\label{lem:normalized_cut_lb}
-	The normalized cut $\Phi_{n,r}(A)$ is upper bounded
-	\begin{equation*}
-	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
-	\end{equation*}
-	uniformly over all $A \subset X$ with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
-\end{lemma}
-\begin{proof}
-	To lower bound the normalized cut $\Phi_{n,r}(A)$, we must lower bound $\cut_{n,r}(A)$ and upper bound $\vol_{n,r}(A)$. A naive upper bound on the volume is simply 
-	\begin{equation}
-	\label{eqn:normalized_cut_lb_pf4}
-	\vol_{n,r}(A) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
-	\end{equation}
-	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this will suffice for our purposes.
-(Here and in the rest of this proof we take $\delta = 1/2$.)
-
-	We turn to lower bounding $\cut_{n,r}(A)$.
-We will approximate the cut of $A$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $A$ to the boundary of the binned set $\overline{A}$, and then lower bound the size of the boundary of $\overline{A}$.
-
-	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube
-	\begin{equation*}
-	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
-	\end{equation*}
-	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
-For a set $A \subset X$ we define the binned set $\overline{A} \subset \overline{Q}$ as follows
-	\begin{equation*}
-	\overline{A} := \set{Q \in \overline{Q}: \Pbb_n(A \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
-	\end{equation*}
-	and we let 
-	\begin{equation*}
-	\partial \overline{A} := \set{Q_{(k_1,k_2)} \in \overline{A}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \overline{A}, \norm{k - \ell}_1 = 1}.
-	\end{equation*}
-	be the boundary set of $\overline{A}$ in $\overline{Q}$.
-Intuitively, every point $x_i \in A$ in the boundary set of $\overline{A}$ will have many edges to $X\setminus A$.
-Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \Pbb_n(Q)$, we have
-	\begin{equation}
-	\label{eqn:normalized_cut_lb_pf1}
-	\cut_{n,r}(A) \geq \cut_{n,r}(A \cap \set{x_i \in \overline{A}}) \geq \frac{1}{4} \abs{\partial \overline{A}} Q_{\min}^2,
-	\end{equation}
-	where the last inequality follows since for every cube $Q_k \in \partial\overline{A}$, there exists a cube $Q_\ell \not\in \overline{A}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
-
-	Now we move on lower bounding the size of the boundary $\abs{\partial\overline{A}}$.
-To do so, we divide $\mathcal{X}$ into slices horizontally.
-Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\overline{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
-For each $k$, either
-	\begin{enumerate}
-		\item $\overline{R}_k \cap \overline{A} = \emptyset$, in which case
-		\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_1[\Xbf] \cap R_k), ~~ \textrm{or}
-		\end{equation*}
-		\item $\overline{R}_k \cap \overline{A} = \overline{R}_k$, in which case
-		\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_2[\Xbf] \cap R_k), ~~\textrm{or}
-		\end{equation*}
-		\item $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$.
-	\end{enumerate}
-	Let $N(R)$ be the number of slices for which $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$. By the cases elucidated above, letting
-	\begin{equation*} R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(C_1[\Xbf] \cap R_k) \wedge \vol_{n,r}(C_2[\Xbf] \cap R_k)\Bigr\}
-	\end{equation*} 
-	we obtain the following lower bound on the volume of the symmetric set difference,
-	\begin{equation}
-	\label{eqn:normalized_cut_lb_pf2}
-	\vol_{n,r}(A \vartriangle C_1[\Xbf]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right].
-	\end{equation}
-	Finally note that $\abs{\partial\overline{A}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
-	\begin{align}
-	\cut_{n,r}(A) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
-	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(A \vartriangle C_1[\Xbf])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
-	\end{align}
-	for all $A \subset \Xbf$.
-
-	It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
-	To do so, we first lower bound the expected probability of any cell $Q$,
-	\begin{align*}
-	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
-	\end{align*}
-	and the expected volume of $\Cset^{(1)}[\Xbf] \cap R_k$ and $\Cset^{(2)}[\Xbf] \cap R_k$,
-	\begin{equation}
-	\vol_{\Pbb,r}(\Cset^{(1)} \cap R_k) = \vol_{\Pbb,r}(\Cset^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
-	\end{equation}
-
-	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
-Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
-Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
-	\begin{equation*}
-	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq \frac{(1 - \delta)}{2}\frac{\pi r^3}{\sigma \rho^2 },
-	\end{equation*}
-	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
-Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
-	\begin{equation*}	
-	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
-	\end{equation*}
-	and plugging in $\delta = 1/2$ yields the claim of Lemma~\ref{lem:normalized_cut_lb}.
-\end{proof}
-
-\paragraph{Conclusion.}
-Combining \eqref{eqn:lb_pf4} and Lemma~\ref{lem:normalized_cut_lb}, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf])$ such that for any seed node $v \in \mathcal{L}[\Xbf]^g$, the following bounds hold:
-\begin{equation*}
-\frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\Cest) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
-\end{equation*}
-with probability at least $1 - b_2/n$ for an appropriate choice of constant $b_2$.
-Solving for $\vol_{n,r}(\Cest \vartriangle \Cset^{(1)}[\Xbf])$ in the previous equation, we obtain \eqref{eqn:ppr_lb} (for an appropriate choice of constant $c$).
-Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\Cset^{(1)}[\Xbf]$:
-\begin{align*}
-\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\Cset^{(0)} \cup \Cset^{(2)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\Cset^{(0)} \cup \Cset^{(1)})[\Xbf])[\Xbf]) \\
-& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \Cset^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
-& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Cset^{(1)}) \\
-& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\Cset^{(1)}[\Xbf])
-\end{align*}
-where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Cset^{(1)}))^2}$.
-Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \Cset^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\Cset^{(1)}[\Xbf])$.
-
-\section{Bounding the misclassification rate.}
-\label{sec: proof_of_misclassification_rate}
-
-A common loss function for clustering is the misclassification rate.
-\begin{definition}[Misclassification rate.]
-	\label{def: symmetric_set_diff}
-	For an estimator \smash{$\Cest \subseteq \Xbf$} and set
-	$\mathcal{S} \subseteq \Reals^d$, we define   
-	\begin{equation}
-	\label{eqn: misclassification_rate}
-	\Delta_{\textrm{mc}}(\Cest, \mathcal{S}) := \abs{\Cset \vartriangle \mathcal{S}[\Xbf]},
-	\end{equation}
-	the cardinality of the symmetric set difference between 
-	\smash{$\Cest$} and $\mathcal{S} \cap \Xbf = \mathcal{S}[\Xbf]$. 
-\end{definition}
-
-In order to upper bound the misclassification rate of a PPR cluster estimate, we will need to slightly modify our approach to computing sweep cuts, and no longer normalize by degree; we formally define this modified algorithm in Algorithm~\ref{alg:ppr2}.
-Intuitively, this change helps us avoid including many low-degree vertices $w \not\in \Csig[\Xbf]$ in our estimated cluster.
-\begin{algorithm}
-	\caption{Unnormalized PPR on a neighborhood graph}
-	\label{alg:ppr2}	
-	{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
-	parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, target stationary probability
-	$\pi_0 > 0$, range $(L,U)$. \\     
-	{\bfseries Output:} cluster $\Cest \subseteq V$.
-	\begin{algorithmic}[1]
-		\STATE Form the neighborhood graph $G_{n,r}$.
-		\STATE Compute the PPR vector $p_v=\pbf(v, \alpha; G_{n,r})$ as in \eqref{eqn: 
-			ppr_vector}. 
-		\STATE For \smash{$\beta \in (\frac{1}{40}, \frac{1}{11})$} compute sweep cuts 
-		$S_{\beta}$
-		\begin{equation}
-		\label{eqn:sweep_cuts2}
-		S_\beta := \set{u \in V: p_v(u) > \beta \pi_0}.
-		\end{equation}
-		\STATE Return as a cluster \smash{$\Cest_{\textrm{un}} = S_{\beta^*}$}, where  
-		$$
-		\beta^* = \argmin_{\beta \in (L,U)} \Phi(S_{\beta}; G_{n,r}).
-		$$
-	\end{algorithmic}
-\end{algorithm}
-
-We say Algorithm \ref{alg:ppr2} is well-initialized if $r,\alpha$ and $v$ satisfy~\eqref{eqn: initialization}, and additionally
-\begin{equation}
-\label{eqn:initialization_2}
-\pi_0 = \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\Pbb(\Csig)n}, ~~\textrm{and}~~ (L,U) \in \left(\frac{1}{100},\frac{1}{50}\right).
-\end{equation}
-
-\begin{theorem}
-	\label{thm:misclassification_rate}
-	Fix $\lambda > 0$ let \smash{$\Cset \in \Cbb_f(\lambda)$} be a
-	$\kappa$-well-conditioned density cluster, and assume If Algorithm
-	\ref{alg:ppr2} is well-initialized with respect to $\Cset$. Then for any
-	\begin{equation*}
-	n \geq b_1(\log n)^{\max\{\frac{3}{d},1\}}
-	\end{equation*}
-	there exists a set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ of large volume, $\vol_{n,r}(\Csig[\Xbf]^g) \geq \vol_{n,r}(\Csig[\Xbf])/2$, such that the following holds: if Algorithm~\ref{alg:ppr2} is run with any seed node $v \in \Csig[\Xbf]^g$, then the PPR estimated cluster $\Cest$ satisfies
-	\begin{equation}
-	\label{eqn: misclassification_rate_ub}
-	\Delta(\Csig[\Xbf], \Cest) \leq c \kappa(\Cset)
-	\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}, 
-	\end{equation}
-	with probability at least $1 - \frac{b_2}{n}$.
-\end{theorem}
-
-\subsection{Proof of Theorem~\ref{thm:misclassification_rate}.}
-The proof of Theorem~\ref{thm:misclassification_rate} follows from Corollary 3.3 of \citet{zhu2013}.
-
-\paragraph{Corollary 3.3 of Zhu.}
-Let $G = (V,E)$ be an undirected, unweighted graph, let $p_v := p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$ and teleportation parameter $\alpha \in (0,1)$. 
-\begin{lemma}[Corollary 3.3 of \citet{zhu2013}.]
-	\label{cor:zhu}
-	Let $A \subseteq G$, and suppose $\alpha \leq \frac{1}{9\tau_{\infty}(G[A])}$.
-Then, there exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that the following statement holds: for any $v \in A$; the PPR vector $p_v$ satisfies
-	\begin{equation}
-	\label{eqn:zhu_1}
-	p_v(V \setminus A) \leq 2\frac{\Phi(A;G)}{\alpha}
-	\end{equation}
-	and additionally there exists a residual vector $p_{\ell} \in [0,1]^V$ with $\norm{p_{\ell}}_1 \leq \frac{2\Phi(A;G)}{\alpha}$ such that
-	\begin{equation}
-	\label{eqn:zhu_2}
-	\textrm{for all $u \in A$}, \quad p_v(u) \geq \frac{4}{5} \frac{\deg(u;G[A])}{\vol(A;G)} - p_{\ell}(u).
-	\end{equation}
-\end{lemma}
-
-\paragraph{Upper bound on $\abs{S_{\beta} \vartriangle A}$.}
-
-For given $\pi_0$ and $\beta \in (0,1)$, consider the sweep cut
-\begin{equation*}
-S_{\beta,v} := \set{u \in V: p_v(u) \geq \beta \pi_0}.
-\end{equation*}
-Suppose the conditions $\alpha \leq \frac{1}{9\tau_{\infty}(G[A])}$ and $v \in A^g$ are met. Then by~\eqref{eqn:zhu_1},
-\begin{equation}
-\label{eqn:zhu_3}
-\abs{S_{\beta,v} \setminus A} \leq \frac{p_v(V \setminus A)}{\min_{u \in S_{\beta}}p_v(u)} \leq \frac{2 \Phi(A;G)}{\alpha \beta \pi_0}. 
-\end{equation}
-To upper bound $\abs{A \setminus S_{\beta}}$, note that for every $u \in A \setminus S_{\beta}$, $p_v(u) \leq \beta \pi_0$. Therefore by~\eqref{eqn:zhu_2},
-\begin{equation*}
-p_{\ell}(u) \geq \frac{4\deg(u;G[A])}{5\vol(A;G)} - \beta\pi_0, \textrm{for all $u \in A \setminus S_{\beta}$}
-\end{equation*}
-Since additionally $\norm{p_{\ell}}_1 \leq 2\Phi(S;G)/\alpha$, we have
-\begin{align}
-\sum_{u \in A \setminus S_{\beta,v}} \left(\frac{4\deg(u;G[A])}{5\vol(A;G)} - \beta\pi_0\right) & \leq \frac{2\Phi(S;G)}{\alpha} \nonumber \Longrightarrow\\
-\abs{A \setminus S_{\beta,v}}\underbrace{\left(\frac{4\min_{u \in A}\deg(u;G[A])}{\abs{A}5\max_{u \in A}\deg(u;G)} - \beta\pi_0\right)}_{:=T_1(A;G)} & \leq \frac{2\Phi(S;G)}{\alpha} \Longrightarrow \nonumber \\
-\abs{A \setminus S_{\beta,v}} \leq \frac{2\Phi(S;G)}{\alpha T_1(A;G)} .
-\label{eqn:zhu_4}
-\end{align}
-
-\paragraph{Bounds on graph functionals for $G_{n,r}$.}
-
-To apply~\eqref{eqn:zhu_3} and~\eqref{eqn:zhu_4} when $G = G_{n,r}$ and $A = \Csig[\Xbf]$, we need to verify the condition $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, and additionally upper bound $\Phi_{n,r}(\Csig[\Xbf])$ and $T_1(G_{n,r}; \Csig[\Xbf])$.
-We now state the necessary upper bounds, and the probability with which they hold:
-\begin{itemize}
-	\item Since $\alpha < \frac{1}{9\tau_u(\Csig)}$, by Theorem~\ref{thm: mixing_time_upper_bound} 
-	\begin{equation*}
-	\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})},
-	\end{equation*}
-	with probability at least $1 - \frac{b_2}{n} - 2n\exp\set{-b_3n} - 2\exp\set{-b_4n}$. 
-	\item  By Theorem~\ref{thm: conductance_upper_bound}, 
-	\begin{equation*}
-	\Phi_{n,r}(\Csig[\Xbf]) \leq \Phibf(\Csig) 
-	\end{equation*}
-	with probability at least $1 - 3\exp\{-nb\}$. 
-	\item By Lemma~\ref{lem:ball_bounds_in_probability},
-	\begin{equation*}
-	\frac{\min_{u \in \Csig[\Xbf]}\widetilde{\deg}_{n,r}(u)}{\max_{u \in \Csig[\Xbf]}\deg_{n,r}(u)}= \frac{\degminwt}{\degmax} \geq \frac{(1 - \delta)6\lambda_{\sigma}}{(1+\delta)25\Lambda_{\sigma}},
-	\end{equation*}
-	and
-	\begin{equation*}
-	\abs{\Csig[\Xbf]} \leq (1 + \delta)n\Pbb(\Csig[\Xbf])
-	\end{equation*}
-	all with probability at least $1 - 2n\exp\set{-\frac{2 \delta^2 \lambda_{\sigma} \nu_d r^d n}{75(1 + \frac{\delta}{3})}} - 2\exp\set{-2\delta^2 \Pbb(\Csig)^2}$.
-These bounds along with the initialization conditions~\eqref{eqn:initialization_2} imply
-	\begin{align}
-	T_1(G_{n,r}, \Csig[\Xbf]) & \geq \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\abs{\Csig[\Xbf]}}\left(\frac{(1 - \delta)6}{(1+\delta)25} - (1 + \delta)\beta\right) \nonumber \\
-	& \geq \frac{\lambda_{\sigma}}{\Lambda_{\sigma}\abs{\Csig[\Xbf]}}\left(\frac{(1 - \delta)6}{(1+\delta)25} - \frac{(1 + \delta)}{50}\right). \label{eqn:misclassification_rate_pf1}
-	\end{align}
-\end{itemize}
-We assume these high probability bounds are satisfied with $\delta = \frac{1}{2}$ and move on to upper bounding $\Delta_{\textrm{mc}}(\Cest_{\textrm{un}}, \Csig[\Xbf])$.
-
-\paragraph{Upper bound on misclassification rate.}
-Since $\alpha \leq \frac{1}{9\tau_{\infty}(\widetilde{G}_{n,r})}$, we may apply Lemma~\ref{cor:zhu} to the graph $G_{n,r}$ and subset $\Csig[\Xbf]$.
-Combined with the inequalities we've already derived, this implies the following: there exists a subset $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]) \leq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that the following bounds hold,
-\begin{equation*}
-\abs{S_{\beta,v} \setminus \Csig[\Xbf]} \leq \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha \beta \pi_0} \leq \frac{2000 \kappa(\Cset)}{\pi_0} \leq \frac{4000 \kappa(\Cset) \Lambda_{\sigma}}{\lambda_{\sigma}}\abs{\Csig[\Xbf]},
-\end{equation*}
-and
-\begin{equation*}
-\abs{\Csig[\Xbf] \setminus S_{\beta,v}} \leq \frac{2\Phi_{n,r}(\Csig[\Xbf])}{\alpha T_1(\Csig[\Xbf];G_{n,r})} \leq \frac{1000 \kappa(\Cset) \Lambda_{\sigma}}{\lambda_{\sigma}}\abs{\Csig[\Xbf]}.
-\end{equation*}
-This completes the proof of Theorem~\ref{thm:misclassification_rate}.
-
-\section{Probabilistic bounds}
-\label{sec: concentration}
-
-In our theory, we frequently appeal to concentration of graph functionals such as degree, volume, and cut size around their means.
-In this section, we establish such concentration inequalities.
-We begin with Lemma~\ref{lem:hoeffding_2}, Hoeffding's inequality, which we will use to bound the empirical probability of a fixed set.
-\begin{lemma}[Hoeffding's Inequality.]
-	\label{lem:hoeffding_2}
-	Let $\mathcal{A}$ be a subset of $\Reals^d$. Then,
-	\begin{equation*}
-	(1 - \delta) \Pbb(\mathcal{A}) \leq \Pbb_n(\mathcal{A}) \leq (1 + \delta)\Pbb(\mathcal{A})
-	\end{equation*}
-	with probability at least $1 - \exp\set{-2\delta^2(\Pbb(\mathcal{A}))^2}$. 
-\end{lemma}
-
-To bound minimum and maximum degrees, we will use Lemma~\ref{lem:bernstein_union}, which is a combination of Bernstein's inequality and a union bound.
-
-\begin{lemma}[Bernstein's inequality + Union bound.]
-	\label{lem:bernstein_union}
-	For $M \geq 1$, let $\mathcal{A}_1,\ldots,\mathcal{A}_M$ be subsets of $\Reals^d$.
-Denote the minimum probability mass among these sets as $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$.
-Then
-	\begin{equation*}
-	(1 - \delta)p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq (1 + \delta)p_{\max}
-	\end{equation*}
-	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.  
-\end{lemma}
-The above Lemma will allow us to upper and lower bound the minimum and maximum degrees within the neighborhood graphs $G_{n,r}$ and $\widetilde{G}_{n,r}$.
-To bound cut size and volume functionals, we will use Hoeffding's inequality for U-statistics.
-Recall that $U_n$ is an order-2 U-statistic with kernel $h: \Rd \times \Rd \to \Reals$ if
-\begin{equation*}
-U_n = \frac{1}{2{n \choose 2}}\sum_{i = 1}^{n} \sum_{j \neq i} h(x_i,x_j).
-\end{equation*}
-\begin{lemma}[Hoeffding's Inequality for U-statistics.]
-	\label{lem:hoeffding}
-	Assume $\norm{h}_{\infty} \leq 1$. Then,
-	\begin{equation*}
-	(1 - \delta) \mathbb{E}(U_m) \leq U_n \leq (1 + \delta) \mathbb{E}(U_m).
-	\end{equation*}
-	with probability at least $1 - 2 \exp\left(-\delta^2 (\mathbb{E}(U_m))^2 n\right)$.
-\end{lemma}
-
-We collect the bounds on graph functionals we need in Lemma~\ref{lem:ball_bounds_in_probability}.
-Let $S \subset X$ and $\mathcal{S} \subseteq \Rd$.
-As a reminder, for notational ease we write $\widetilde{G}_{n,r} = G_{n,r}[\Csig[\Xbf]]$ and
-\begin{alignat*}{2}
-\widetilde{d}_{\min} & = \min_{u \in \Csig[\Xbf]} \widetilde{\deg}_{n,r}(u), \quad && d_{\min}' = \min_{u' \in \Cset'[\Xbf]} {\deg}_{n,r}(u') \\
-d_{\max} & = \max_{u \in \Csig[\Xbf]} \deg_{n,r}(u), \quad && \widetilde{\vol}_{n,r}(S) = \vol(S; \widetilde{G}_{n,r}). 
-\end{alignat*}
-Additionally, let $\widetilde{\vol}_{\Pbb,r}(\mathcal{S}) := \frac{1}{2{n \choose 2}}\mathbb{E}[\widetilde{\vol}_{n,r}(\mathcal{S}[\Xbf])]$.
-\begin{lemma}
-	\label{lem:ball_bounds_in_probability} \label{lem:graph_functional_concentration}
-	\item[]
-	The following statements hold for any $\delta \in (0,1)$:
-
-	\noindent With probability at least $1 - 2\exp\{-n\delta^2(\widetilde{\vol}_{\Pbb,r}(\mathcal{S}))^2\}$,
-	\begin{equation}
-	\label{eqn:volwt_bound}
-	(1 - \delta) \widetilde{\vol}_{\Pbb,r}(\mathcal{S}) \leq \frac{\widetilde{\vol}_{n,r}(\mathcal{S}[\Xbf])}{2{n \choose 2}} \leq (1 + \delta) \widetilde{\vol}_{\Pbb,r}(\mathcal{S}).
-	\end{equation}
-	With probability at least $1 - 2\exp\set{-n \delta^2 \vol_{\Pbb,r}(\Sset)^2}$,
-	\begin{equation}
-	\label{eqn:vol_bound}
-	(1 - \delta)\vol_{\Pbb,r}(\Sset) \leq \frac{\vol_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq 2(1 + \delta)\vol_{\Pbb,r}(\Sset).
-	\end{equation}
-	With probability at least $1 - 2\exp\set{-n \delta^2 \cut_{\Pbb,r}(\Sset)^2}$,
-	\begin{equation}
-	\label{eqn:cut_bound}
-	(1 - \delta)\cut_{\Pbb,r}(\Sset) \leq \frac{\cut_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq (1 + \delta)\vol_{\Pbb,r}(\Sset).
-	\end{equation}
-	With probability at least $1 - 2\exp\{-n\delta^2\Pbb(\Csig)^2\}$, 
-	\begin{equation}
-	\label{eqn:cardinality}
-	(1 - \delta) \Pbb(\Csig) \leq \abs{\Csig[\Xbf]} \leq (1 + \delta) \Pbb(\Csig).
-	\end{equation}
-
-	\noindent The following statements hold for any $0 < r \leq \frac{\sigma}{2d}$:
-
-	\noindent Assuming $\Csig$ satisfies~\ref{asmp: bounded_density}, with probability at least $1 - 2n\exp\set{-\frac{ \delta^2 \lambda_{\sigma} \nu_d r^d n}{6(1 + \frac{\delta}{3})}}$,
-	\begin{equation}
-	\label{eqn:degwt_bound}
-	\frac{1}{2}\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2 \pi}}\biggr)(1 - \delta)\lambda_{\sigma}\nu_dr^dn \leq \degminwt \leq d_{\max} \leq (1 + \delta) \Lambda_{\sigma} \nu_dr^dn.
-	\end{equation}
-	Assuming $\Cset'$ satisfies~\ref{asmp: C'_bounded_density}, with probability at least $1 - n\exp\set{-\frac{\delta^2 \lambda_{\sigma} \nu_d r^d n}{3(1 + \frac{\delta}{3})}}$,
-	\begin{equation}
-	\label{eqn:degpr_bound}
-	\degminpr \geq (1 - \delta)\lambda_{\sigma}\nu_dr^dn.
-	\end{equation}
-\end{lemma}
-\begin{proof}{(of Lemma~\ref{lem:ball_bounds_in_probability})}
-	\hfill 
-	\paragraph{Proof of \eqref{eqn:degwt_bound}, \eqref{eqn:degpr_bound}:}
-	Under~\ref{asmp: bounded_density}, we have that for every $x_j \in \Csig[\Xbf]$
-	\begin{equation*}
-	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j)) \leq \Lambda_{\sigma} \nu_d r^d;
-	\end{equation*}
-	furthermore, recalling the weighted local conductance $\ell_{\Pbb,r}(x) = \Pbb(B(x,r) \cap \Csig)$, we have,
-	\begin{equation*}
-	\mathbb{E}(\widetilde{\deg}_{n,r}(x_j) | x_j) \geq n \cdot \ell_{\Pbb,r}(x_j) \geq n \lambda_{\sigma} \cdot \biggl\{\min_{x \in \mc{C}_{\sigma}} \ell_{\nu,r}(x)\biggr\} \geq \frac{n}{2}\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2 \pi}}\biggr)\lambda_{\sigma}\nu_dr^d
-	\end{equation*}
-	where the last inequality follows from Lemma~\ref{lem: overlap_balls}.  Under~\ref{asmp: C'_bounded_density} we have for every $x_i \in \Cset'[\Xbf]$
-	\begin{equation*}
-	\mathbb{E}({\deg}_{n,r}(x_i)|x_i) \geq n \lambda_{
-		\sigma} \nu_d r^d.
-	\end{equation*} 
-	Then \eqref{eqn:degwt_bound} and \eqref{eqn:degpr_bound} each follow from Lemma~\ref{lem:bernstein_union}.
-	\paragraph{Proof of \eqref{eqn:volwt_bound}, \eqref{eqn:vol_bound}, \eqref{eqn:cut_bound}:}
-
-	We have that $\frac{1}{2{n \choose 2}}\widetilde{\vol}_{n,r}(\Csig[\Xbf])$, $\frac{1}{2{n \choose 2}}\vol_{n,r}(\Sset[\Xbf])$, $\frac{1}{2{n \choose 2}}\cut_{n,r}(\Sset[\Xbf])$ are each order-2 U statistics, with respective kernels
-	\begin{align*}
-	h_{\widetilde{\vol}}(x_i,x_j) & = \1(x_i \in \Csig)\1(x_j \in \Csig)\1(\norm{x_i - x_j} \leq r), \\ h_{\cut}(x_i,x_j) & = \1(x_i \in \Csig)\1(x_j \notin \Csig)\1(\norm{x_i - x_j} \leq r) \\
-	h_{\vol}(x_i,x_j) & = \1(x_i \in \Csig)\1(\norm{x_i - x_j} \leq r).
-	\end{align*}
-	We may therefore apply Lemma~\ref{lem:hoeffding} in each case to obtain the stated bounds.
-
-	\paragraph{Proof of \eqref{eqn:cardinality}:}
-	Apply Lemma~\ref{lem:hoeffding_2} to $\Csig$.
-\end{proof}
-
-\section{Experiments}
-\label{sec: experimental_setting}
-
-In Section \ref{sec: experimental_setting}, we detail the experimental settings of Section \ref{sec: experiments} in the main text, and include an additional figure.
-
-\subsection{Experimental settings for Figure \ref{fig:bounds}}
-We sample points according to the density function $q$, where for $x \in \Rd$
-\begin{equation}
-q(x) :=
-\begin{cases}
-\lambda,~ & x \in [0,\sigma] \times \rho^{d-1} =: \Cset, \\
-\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
-(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B) \setminus \Csig, \\
-0,~ & \textrm{otherwise},
-\end{cases}
-\end{equation}
-where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$.
-
-In the top-left and top-middle, we show draws of $n = 20000$ samples from two different density functions.
-In the top-left panel, $\sigma = \rho = 3.2$, while in the top-middle panel $\sigma = .1$ and $\rho = 3.2$.
-(For both, $d = 2$).
-
-The remaining four panels (top-right and the bottom row) in Figure \ref{fig:bounds} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ (top-right and bottom-left) and $\rho$ (bottom-middle and bottom-right) are varied.
-In the top-right and bottom-left panels $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $\rho$ is fixed at $3.2$.
-In the bottom-middle and bottom-right panels, $\rho = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
-For each panel, the solid lines show, up to constants, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for the top-right and bottom-left panels and Theorem \ref{thm: mixing_time_upper_bound} for the bottom-middle and bottom-right panels.
-The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in the top-right and bottom-left panels, and $m = 20$ for the mixing time, dashed lines in the bottom-middle and bottom-right panels).
-For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency.
-Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.
-
-\subsection{Experimental settings for Figure \ref{fig:moons}}
-
-To form each of the three rows in Figure \ref{fig:moons}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
-Formally, the (respective) generative models for the data are
-\begin{align}
-Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
-X(Z,\theta) & = 
-\begin{cases}
-\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
-\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
-\end{cases}
-\end{align}
-
-where 
-\begin{align*}
-\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
-\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
-\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} 
-\end{align*}
-for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $C[\Xbf]$ and $C'[\Xbf]$ for a particular threshold $\lambda$ of the density function; the second column shows the ~\pprspace plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
-
-\subsection{Performance of \pprspace with high-dimensional noise.}
-
-Figure \ref{fig:moons_hd} is similar to Figure \ref{fig:moons} of the main text, with parameters
-\begin{equation*}
-\mu_1 = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}).
-\end{equation*}
-The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:moons} in the main text) represent observations in low-density regions.
-While the \pprspace sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers $C[\Xbf]$ in the sense of Definition \ref{def: consistent_density_cluster_estimation}.
-
-% PUT FIGURE BACK HERE
-
-\clearpage
-
-% \bibliographystyle{plainnat}
-\bibliography{../../local_spectral_bibliography}
-
 \end{document}

### 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex
Cleaning up.

@@
 \maketitle
+
+\chapter{Normalized cut}
+To recall, our upper bound on normalized cut---ignoring the terms that depend on the density---is 
+\begin{equation*}
+\wt{\Phi}_{\nu,r}(\mc{C}_{\sigma}) \lessapprox \frac{16dr}{9\sigma}.
+\end{equation*}
+\section{Lower bound on normalized cut}
+Our goal is to examine the tightness of our upper bound on normalized cut (Theorem 10 of our JMLR submission), by giving a comparable lower bound.
+Recall that the (uniform, population level) normalized cut of a set $\mc{C}_{\sigma}$ is given by
+\begin{equation*}
+\Phi_{\nu,r}(\mc{C}_{\sigma}) := \frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx}.
+\end{equation*}
+As informed by the isoperimetric ratio, the worst-case for a functional like normalized cut should be when $\mc{C}_{\sigma}$ by a $d$-dimensional ball.
+Letting $\mc{C}_{\sigma} = B(0,\sigma)$, we have that
+\begin{equation*}
+\frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx} = \frac{1}{\nu_d^2 r^d \sigma^d} \int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx.
+\end{equation*}
+If $\|x\| < \sigma - r$, then $B(x,r) \setminus \mc{C}_{\sigma} = \emptyset$.
+Otherwise $\sigma - r \leq \|x\| \leq \sigma$, and if $r \ll \sigma$ then $B(x,r) \setminus \mc{C}_{\sigma} \approx \mathrm{cap}_{r}(\|x\| - (\sigma - r))$.
+Converting to polar coordinates, we have:
+\begin{align*}
+\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx & \approx s_d \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(x - (\sigma - r))) t^{d - 1} \,dt \\
+& \geq s_d (\sigma - r)^{d - 1} \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(t - (\sigma - r)))  \,dt \\
+& = s_d (\sigma - r)^{d - 1} \int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz.
+\end{align*}
+As calculated below~\eqref{eqn:lb_conductance_1}, $\int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz = \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma(d/2 + 1/2)\sqrt{\pi}} \approx \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}}$ and hence
+\begin{equation*}
+\Phi_{\nu,r}(\mc{C}_{\sigma}) \approx s_d (\sigma - r)^{d - 1}\frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}} \frac{1}{\nu_d^2 r^d \sigma^d} \approx \frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}} \cdot \frac{dr}{\sigma}.
+\end{equation*}
+By contrast, our upper bound is $\approx dr/\sigma$, revealing a gap of roughly $\frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}$.
 
@@
 
+\section{Upper bound on conductance}
+To investigate the tightness of Lemma~\ref{lem: uniform_continuous_conductance}, we give an accompanying upper bound on $\wt{\Phi}_{\nu,r}$. Let 
+\begin{equation*}
+\mc{C}_{\sigma} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,\rho/2],
+\end{equation*}
+and consider the partition of $\mc{C}_{\sigma}$ induced by the hyperplane $\{x \in \Rd: x_d = 0\}$, i.e
+\begin{equation*}
+\mc{L} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,0),~~\mc{R} = [-\sigma,\sigma]^{d - 1} \otimes [0,\rho/2].
+\end{equation*}
+Recalling that 
+\begin{equation*}
+\wt{\Phi}_{\nu,r}(\mc{L}) = \frac{\wt{Q}_{\nu,r}(\mc{L},\mc{R})}{\wt{\pi}_{\nu,r}(\mc{L})} = \frac{\int_{\mc{L}} \nu(B(x,r) \cap \mc{R}) \,dx}{\int_{\mc{L}} \nu(B(x,r) \cap \mc{C}_{\sigma}) \,dx} 
+\end{equation*}
+our goal will be to upper bound the numerator and lower bound the denominator of the above expression.
+
+We begin by upper bounding the numerator.
+For any $x \in \mc{L}$, either $\dist(x,\mc{R}) = -x \leq r$ in which case $B(x,r) \cap \mc{R} \subset \mathrm{cap}_r(r + x)$, or $\dist(x,\mc{R}) = -x > r$ in which case $B(x,r) \cap \mc{R} = \emptyset$.
+Thus
+\begin{equation}
+\label{eqn:lb_conductance_1}
+\int_{\mc{L}} \nu\bigl(B(x,r) \cap \mc{R}\bigr) \,dx \leq (2\sigma)^{d - 1} \int_{-r}^{0} \nu(\mathrm{cap}_r(r + x)) \,dx = (2\sigma)^{d - 1} \int_{0}^{r} \nu\bigl(\mathrm{cap}_r(r - x)\bigr) \,dx.
+\end{equation}
+Recalling that the volume of a hyperspherical cap is given by $\nu(\mathrm{cap}_r(h)) = \frac{1}{2}\nu_dr^dI_{1 - \alpha}\biggl(\frac{d + 1}{2};\frac{1}{2}\biggr)$ for $\alpha = 1 - \frac{2rh - h^2}{r^2}$, we have that
+\begin{align*}
+\int_{0}^{r} \nu\bigl(\mathrm{cap}_r(r - x)\bigr) \,dx & = \frac{1}{2}\nu_dr^d \int_{0}^{r} I_{1 - x^2/r^2}\Bigl(\frac{d + 1}{2}; \frac{1}{2}\Bigr) \,dx \\
+& = \frac{1}{2}\nu_dr^{d + 1} \int_{0}^{1} I_{1 - z^2}\Bigl(\frac{d + 1}{2}; \frac{1}{2}\Bigr) \,dz \tag{substituting $z = x/r$}\\ 
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} \int_{0}^{1 - z^2} u^{(d - 1)/2} (1 - u)^{-1/2} \,du \,dz \\
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} \int_{0}^{\sqrt{1 - u}} u^{(d - 1)/2} (1 - u)^{-1/2} \,dz \,du \tag{Fubini's Theorem} \\
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} u^{(d - 1)/2} \,du \\
+& = \frac{1}{d + 1}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}},
+\end{align*}
+and plugging back in to~\eqref{eqn:lb_conductance_1}, we obtain
+\begin{equation*}
+\int_{\mc{L}} \nu\bigl(B(x,r) \cap \mc{R}\bigr) \,dx \leq \frac{(2\sigma)^{d-1}}{d + 1}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \leq \frac{(2\sigma)^{d - 1} \nu_d r^{d + 1}\sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}.
+\end{equation*}
+On the other hand, when $r \ll \sigma$ the denominator is $\int_{\mc{L}}\nu(B(x,r) \cap \mc{C}_{\sigma}) \,dx \approx \frac{1}{2}(2\sigma)^{d - 1} \rho \nu_d r^d$. Therefore,
+\begin{equation*}
+\wt{\Phi}_{\nu,r} \lessapprox \frac{2r(d + 2)^{1/2}}{(d + 1)\rho \sqrt{2\pi}}.
+\end{equation*}
+This matches our lower bound on $\wt{\Phi}_{\nu,r}$ up to a factor of $18/(2\pi\ell^2) \cdot \sqrt{(d + 2)/(d + 1)} < 3/\ell^2.$
+
 \chapter{Misclassification error of PPR}
@@
 
+\chapter{Examples}
+
+In this chapter, we calculate a numerical value of our upper bounds for a few example density functions.
+
+\section{Mixture of two-(quasi)-uniforms}
+\textcolor{red}{(NOTE): This is quite similar to the density function used in our experiment, but not exactly the same.}
+
+The density function $q(x) \propto \wt{q}(x) + \wt{q}\bigl(x - z\bigr)$, where $z = (4\sigma,0) \in \Reals^2$, and 
+\begin{equation}
+\wt{q}(x) :\propto
+\begin{cases}
+\lambda,~ & x \in \{0\} \times [0,\wt{\rho}] =: \mc{C}, \\
+\lambda - \eta \cdot \dist(x,\mc{C}),~ & x \in \mc{C}_{\sigma} \setminus \mc{C}, \\
+(\lambda - \eta\sigma - \theta \cdot \dist(x,\mc{C}_{\sigma})^{\gamma}, & x \in (\mc{C}_{\sigma} + \sigma B) \setminus \mc{C}_{\sigma}, \\
+0,~ & \textrm{otherwise}.
+\end{cases}
+\end{equation}
+When $d = 2$, our upper bounds on mixing time and normalized cut become,
+\begin{align}
+\label{eqn: condition_number}
+\Phi_u(\mc{C}) 
+& = \frac{32}{9} \cdot \frac{r}{\sigma} \frac{\lambda}{(\lambda - \eta \sigma)}
+\frac{(\lambda - \eta \sigma - \theta \frac{r^{\gamma}}{\gamma +
+		1})}{(\lambda - \eta \sigma)} \\
+\tau_u(\mc{C}) & = 1028 \cdot 64 \cdot \frac{\lambda^4
+	(4\sigma^2 + \wt{\rho}^2)}{(\lambda - \eta \sigma)^4 r^2} \ln^2\Bigl(\sqrt{2134} \frac{\Lambda_{\sigma} \sqrt{4\sigma^2 + \wt{\rho}^2}}{\lambda_{\sigma} 2r}\Bigr)
+\end{align}
+Let us see how good these bounds are in the best-case.
+Put $\wt{\rho} = 0$, so that $\mc{C}_{\sigma} = B(0,\sigma)$ is geometrically well-conditioned.
+Put $\eta = 0$ and $\gamma = 1$ so that $\mc{C}$ is sharply vertically defined.
+Finally, put $r = \sigma/8$; our bounds improve as $r$ increases, but $r$ can be at most $\sigma/(4d)$ for our theory to apply.
+Our bounds then become
+\begin{align}
+\label{eqn: condition_number2}
+\Phi_u(\mc{C}) 
+& = \frac{4}{9} \cdot
+\frac{(\lambda - \theta)}{\lambda} \\
+\tau_u(\mc{C}) & = 1028 \cdot 4^7 \cdot \ln^2\Bigl(\sqrt{2134} \cdot 8 \Bigr)
+\end{align}
+with a resulting bound on PPR misclassification error of 
+\begin{equation*}
+\frac{1}{\vol_{n,r}(\mc{C}_{\sigma}[X])}\Delta(\wh{C},\mc{C}_{\sigma}[X]) \leq 175 \cdot \Phi_u(\mc{C}) \cdot \tau_u(\mc{C}) = 175 \cdot 115 \cdot 4^8 \cdot  \ln^2\Bigl(\sqrt{2134} \cdot 8 \Bigr) \cdot \frac{(\lambda - \theta)}{\lambda} \approx 10^{10.67} \cdot \frac{(\lambda - \theta)}{\lambda}
+\end{equation*}
+holding with high probability.
+Therefore if $\theta \geq (1 - 10^{-11.67})\lambda$, then with high probability $\frac{1}{\vol_{n,r}(\mc{C}_{\sigma}[X])}\Delta(\wh{C},\mc{C}_{\sigma}[X]) \leq \frac{1}{10}$.
+But of course, for such a value of $\theta$ the probability of $X ~ q$ landing in $\mc{C}_{\sigma, \sigma + r} = B(0,2\sigma) \setminus B(0,\sigma)$ would be only about $\frac{1}{2} \cdot \frac{3}{4}\pi \cdot 10^{-11.67}$.
+
+The parameters $\gamma$ and $\theta$ will be made explicit later, but of course they are chosen so that $\lambda - \sigma \eta - \theta \sigma^{\gamma} \geq 0$.
+Finally $q_2$ is an arbitrary distribution over a repository of mass $\mc{R}$ that is non-intersecting with $\mc{C}_{\sigma}$ (the density $q_2$ and set $\mc{R}$ should be chosen to meet the requirement of (A4)---for instance, $\mc{R}$ might be a translation of $\mc{C}_{\sigma}$---but are otherwise unimportant.).
+
+The set $\mc{C}_{\sigma}$ meets each of the assumptions (A1)-(A3), for parameter values:
+\begin{itemize}
+	\item \textit{Bounded density within cluster}: the maximum in-cluster density $\Lambda_{\sigma} = \lambda/2 = \frac{75}{81}\sigma^{\gamma}$, and the minimum in-cluster density  $\lambda_{\sigma} = \frac{1}{2}(\lambda - \sigma \eta) = \frac{135}{162} \sigma^{\gamma}$.
+	\item \textit{Low noise density}: $\theta = \textcolor{red}{(?)}$ and $\gamma = \textcolor{red}{(?)}$. 
+	\item \textit{Lipschitz embedding}: The set $\mc{C}_{\sigma}$ is itself a convex set with diameter $\sqrt{4\sigma^2 + \rho^2}$. 
+\end{itemize}
+From this, we can compute the following upper bounds on normalized cut and mixing time:
+\begin{equation*}
+\Phi_u(\mc{C}) \leq \frac{4}{9} \cdot \frac{150}{135} \cdot \Bigl(1 - \frac{81}{135} \cdot \frac{\theta}{8^{\gamma}(\gamma + 1)}\Bigr)
+\end{equation*}
+and
+\begin{equation*}
+\tau_u(\mc{C}) \leq 1028 \cdot \Bigl(\frac{150}{135}\Bigr)^4 \cdot 4^6 \cdot \frac{4\sigma^2 + \rho^2}{\sigma^2} \ln^2\biggl(\sqrt{2134} \cdot \frac{150}{135} \cdot \frac{8 \sqrt{4\sigma^2 + \rho^2}}{\sigma}\biggr).
+\end{equation*}
+Hence,
+\begin{equation*}
+\kappa(\mc{C}) \leq 10^{6.51} \cdot \Bigl(1 - \frac{81}{135} \cdot \frac{\theta}{8^{\gamma}(\gamma + 1)}\Bigr) \cdot \frac{4\sigma^2 + \rho^2}{\sigma^2} \ln^2\biggl(\sqrt{2134} \cdot \frac{150}{135} \cdot \frac{8 \sqrt{4\sigma^2 + \rho^2}}{\sigma}\biggr)
+\end{equation*}
+and it follows from Theorem 5 that for $n$ sufficiently large,
+\begin{equation*}
+\Delta(\wh{C},\mc{C}_{\sigma}[X]) \leq 10^{8.75} \cdot \Bigl(1 - \frac{81}{135} \cdot \frac{\theta}{8^{\gamma}(\gamma + 1)}\Bigr) \cdot \frac{4\sigma^2 + \rho^2}{\sigma^2} \ln^2\biggl(\sqrt{2134} \cdot \frac{150}{135} \cdot \frac{8 \sqrt{4\sigma^2 + \rho^2}}{\sigma}\biggr)
+\end{equation*}
+with high probability.
+
+Thus, when $\rho = 0$, $\gamma = 0$ and $\theta = 135/81 \cdot (1 - 10^{-12})$ we have that
+\begin{equation*}
+\Delta(\wh{C},\mc{C}_{\sigma}[X]) \leq .1.
+\end{equation*}
+
 \end{document}

### 2021-01-13 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex

@@
 
-\ShortHeadings{Local Spectral Density Clustering}{Green, Balakrishnan and Tibshirani}
+\ShortHeadings{PPR Clustering on Neighborhood Graphs}{Green, Balakrishnan and Tibshirani}
 \firstpageno{1}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{\textcolor{red}{The Geometry of Local Spectral Clustering}}
+\title{Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs}
 
@@
 	\AND
-	\name Sivaraman Balakrishnan \email sbalakri@stat.cmu.edu \\
+	\name Sivaraman Balakrishnan \email siva@stat.cmu.edu \\
 	\addr Department of Statistics and Data Science\\
@@
 	a given seed node.  In contrast to previous work, we adopt a classical
-	statistical learning setup, where we obtain samples from an unknown non-parametric distribution, and aim to identify geometrically salient clusters.
-We introduce a pair of population-level geometric functionals---the \emph{normalized cut} and \emph{conductance}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large population conductance.
+	statistical learning setup, where we obtain samples from an unknown nonparametric distribution, and aim to identify sufficiently salient clusters.
+We introduce a pair of population-level functionals---the \emph{normalized cut} and \emph{conductance}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large population conductance.
 We apply our general theory to establish that PPR identifies connected regions of high density (density clusters) that satisfy a set of natural geometric conditions.
@@
 vertices correspond to samples, and edges correspond to proximities between
-samples. The algorithm then estimates a feature embedding based on (an
-appropriate) Laplacian matrix of $G$, and applies a simple clustering technique
+samples. The algorithm then estimates a feature embedding based on a (suitable) Laplacian matrix of $G$, and applies a simple clustering technique
 (like $k$-means clustering) in the embedded feature space.
@@
 In contrast, in this paper we adopt a classical statistical viewpoint, and examine what the output of local clustering on a data set reveals about the underlying density $f$ of the samples.
-\textcolor{red}{(We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C}$, will approximately recover this candidate cluster.
-We pay special attention to the case where $\mc{C}$ is a \emph{density cluster} of $f$---defined as a connected component of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$---and show precisely how PPR accounts for both geometry and density in estimating a cluster.)}\\
-
-\textcolor{red}{Alden: In our original submission, the preceding paragraph ended with the following sentence:
-\begin{quote}
-	In particular, we examine the ability of
-	PPR to recover \emph{density clusters} of $f$, defined as the connected
-	components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some
-	$\lambda > 0$ (an object of central interest in the statistical clustering
-	literature, dating back to the work of \citet{hartigan1981}). 
-\end{quote}
-This sentence no longer accurately describes our paper, so I substituted the part in parentheses above.}\\
-
-Before giving a more detailed overview of our main results, we review some of the aforementioned worst-case guarantees, formally define PPR on a neighborhood graph, and introduce the population-level functionals that govern the behavior of local clustering \textcolor{red}{(in our statistical context)}.
-
-\subsection{Review: worst-case guarantees for local spectral clustering}
-As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
-For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR.
-For a set $C \subseteq V$ with complement $C^c = V \!\setminus\!
-C$, the \emph{cut} and \emph{volume} are respectively,
+We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C}$, will approximately recover this candidate cluster.
+We pay special attention to the case where $\mc{C}$ is a \emph{density cluster} of $f$---defined as a connected component of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$---and show precisely how PPR accounts for both geometry and density in estimating a cluster.
+
+Before giving a more detailed overview of our main results, we review some of the aforementioned worst-case guarantees, formally define PPR on a neighborhood graph, and introduce the population-level functionals that govern the behavior of local clustering in our statistical context.
+
+\subsection{PPR clustering, and worst-case guarantees}
+We now review the PPR clustering algorithm, and some worst-case guarantees on the quality of the resulting cluster.
+Let $G = (V,E)$ be an undirected, unweighted, and connected graph.
+We denote by $A \in \Reals^{n \times n}$ the adjacency
+matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
+also denote by $D$ the diagonal degree matrix, with entries $D_{uu} :=
+\sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
+The PPR vector $p_v = p(v,\alpha;G)$ is defined with respect to a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
+\begin{equation}
+\label{eqn:ppr_vector}
+p_v = \alpha e_{v} + (1 - \alpha) p_v W,
+\end{equation}
+where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over
+$G$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
+position $v$ and 0 elsewhere).
+
+In practice, exactly solving the system of equations~\eqref{eqn:ppr_vector} to compute the PPR vector may be too computationally expensive.
+To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p^{(\varepsilon)}$}.
+We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
+\begin{equation}
+\label{eqn: appr_error}
+\textrm{for all $u \in V$}, \quad p_v(u) - \varepsilon D_{uu}\leq
+p_v^{(\varepsilon)}(u) \leq p_v(u).  
+\end{equation}
+
+Once $p_v$ or $p_v^{(\varepsilon)}$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut of $p_v$.
+For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is
+\begin{equation}
+\label{eqn:sweep_cuts}
+S_{\beta,v} := \set{u \in V: \frac{p_v(u)}{D_{uu}} > \beta}.
+\end{equation}
+To determine $\wh{C}$, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate
+\smash{$\wh{C} = S_{\beta^*,v}$} with minimum normalized cut. For a set $C \subseteq V$ with complement $C^c = V \!\setminus\! C$, the \emph{cut} and \emph{volume} are respectively,
 \begin{equation}
@@
 \end{equation}
-\cite{andersen2006} show that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of the candidate cluster is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.
+
+As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
+For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of $\wh{C}$ is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.
 \cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
@@
 and show that if $\Phi(C;G)$ is much smaller than $\Psi(G[C])^2$---where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$--- then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
-Our own analysis will build on that of~\cite{zhu2013}, and we will give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
-For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random geometric graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.
+Our own analysis builds on that of~\cite{zhu2013}, and we give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
+For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random geometric graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
 
 \subsection{PPR on a neighborhood graph}
-
-We now formally describe this setting, as well as the method we will study: PPR on a neighborhood graph. Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution
-$\Pbb$ on $\Rd$. We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure on $\Rd$. For a radius $r > 0$, we define
+We now formally describe the statistical setting in which we operate, as well as the method we will study: PPR on a neighborhood graph.
+Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution
+$\Pbb$ on $\Rd$. We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ . For a radius $r > 0$, we define
 $G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an
@@
 E$ if and only if $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
-Euclidean norm. We denote by $A \in \Reals^{n \times n}$ the adjacency
-matrix, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
-also denote by $D$ the diagonal degree matrix, with entries $D_{uu} :=
-\sum_{v \in V} A_{uv}$, and by $I{}$ the $n \times n$ identity matrix.
-
-The PPR vector $p_v = p(v,\alpha;G_{n,r})$ is defined with respect to
-a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
-\begin{equation}
-\label{eqn: ppr_vector}
-p_v = \alpha e_{v} + (1 - \alpha) p_v W,
-\end{equation}
-where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over
-$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
-position $v$ and 0 elsewhere).
-
-Once $p_v$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut of $p_v$. For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is 
-\begin{equation}
-\label{eqn: sweep_cuts}
-S_{\beta,v} := \set{u \in V: \frac{p_v(u)}{D_{uu}} > \beta}.
-\end{equation}
-To determine $\wh{C}$, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate
-\smash{$\wh{C} = S_{\beta^*}$} with minimum normalized cut.  For concreteness,
-the PPR algorithm is summarized in Algorithm~\ref{alg:ppr}.
+Euclidean norm.
+Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate $\wh{C} \subseteq X$.
+The precise PPR algorithm we analyze is summarized in Algorithm~\ref{alg:ppr}.
 
@@
 		\STATE Compute the PPR vector $p_v=p(v, \alpha; G_{n,r})$ as in
-		\eqref{eqn: ppr_vector}.  
+		\eqref{eqn:ppr_vector}.  
 		\STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
-		\eqref{eqn: sweep_cuts}. 
+		\eqref{eqn:sweep_cuts}. 
 		\STATE Return the cluster \smash{$\wh{C} = S_{\beta^*}$}, where  
@@
 \subsection{Population normalized cut and conductance}
-As we will show, the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$ is intrinsically related to two population-level functionals of $\mc{C}$, the normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$, which we now define.
-Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) = \vol(\mc{C}[X]; G_{n,r})$; i.e.
+Next we define two population-level functionals of $\mc{C}$, the normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$, which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
+Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e.
 let
@@
 \begin{definition}[Population normalized cut]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the \emph{population normalized cut} is
+	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population normalized cut} is
 	\begin{equation}
 	\label{eqn:population_normalized_cut}
-	\Phi_{\Pbb,r}(\mc{C}) := \frac{\mathrm{cut}_{\Pbb,r}(\mc{C})}{\min\{\mathrm{vol}_{\Pbb,r}(\mc{C}), \mathrm{vol}_{\Pbb,r}(\mc{C}^c)\}}
+	\Phi_{\Pbb,r}(\mc{C}) := \frac{\mathrm{cut}_{\Pbb,r}(\mc{C})}{\min\{\mathrm{vol}_{\Pbb,r}(\mc{C}), \mathrm{vol}_{\Pbb,r}(\mc{C}^c)\}}.
 	\end{equation}
@@
 \begin{definition}[Population conductance]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the \emph{population conductance} is
+	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population conductance} is
 	\begin{equation}
 	\label{eqn:population_conductance}
-	\Psi_{\mathbb{P},r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S})
+	\Psi_{\mathbb{P},r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S}).
 	\end{equation}
@@
 For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
-We will comment more on the relationship between these works and our own results in~\ref{subsec:related_work}.
+We will comment more on the relationship between these works and our own results in Section~\ref{subsec:related_work}.
+\\
+
+\textcolor{red}{(TODO): Possibly add a section here \emph{giving}---rather than summarizing---our main results.}
 
 \subsection{Summary of results}
+
 A summary of our results (and an outline for this paper) is as follows.
 \begin{itemize}
-	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
-As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a non-parametric statistical context.
+	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that under certain conditions the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
+As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a nonparametric statistical context.
 \end{itemize}
@@
 \begin{itemize}
-	\item In~\ref{subsec:recovery_well-conditioned_density_clusters}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
+	\item In Section~\ref{subsec:recovery_well-conditioned_density_clusters}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
 These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Corollary~\ref{cor:density_cluster_volume_ssd_ub}).
-	\item In~\ref{subsec:consistent_recovery_density_clusters}, we introduce a notion of \emph{density cluster consistency}, and establish conditions under which $\wh{C}$ is a consistent estimate of $\mc{C}_{\lambda}$.
-	\item In~\ref{subsec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ will be provably large.
+	\item In Section~\ref{subsec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
 \end{itemize}
@@
 
-These results are of fundamental importance; however, the behavior of the
-spectra of these continuum operators can in general be hard to grasp. Therefore,
-further work relating this spectra to the geometry of the underlying
-distribution $\Pbb$ is of interest. In this spirit, \citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of spectral
-algorithms to recover the latent labels in certain geometrically
-well-conditioned nonparametric mixture models.
-Connecting the behavior of a spectral method (PPR) to the geometry of $\Pbb$ is also the motivation of our own paper, and these works are probably the most similar to our own.
-However, these results focus on global rather than local methods, and thus impose global rather than local conditions on $\Pbb$.
-Moreover, they do not explicitly consider
-recovery of density clusters, which is an important concern of our work.
+These results are of fundamental importance.
+However, they remain silent on the following natural question: do the spectra of these continuum operators induce a partition of the sample space which is ``good'' in some sense?
+\citet{shi2009,schiebinger2015,garciatrillos19} address this question, showing that spectral algorithms will recover the latent labels in certain well-conditioned nonparametric mixture models.
+These works are probably the most similar to our own: the conditioning of these mixture models depend on population-level functionals resembling the population-level normalized cut and conductance introduced above, and the resulting bounds on the error of spectral clustering are comparable to those we establish in Theorem~\ref{thm:volume_ssd_ub}.
+However, these results focus on global rather than local methods, and impose global rather than local conditions on $\Pbb$.
+Moreover, they do not explicitly consider recovery of density clusters, which is an important concern of our work.
+We comment further on the relationship between our results and these works after Theorem~\ref{thm:volume_ssd_ub}.
 
@@
 When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$.
-Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Technically speaking, Lemma~3.4 of~\cite{zhu2013} differs from Lemma~\ref{lem:zhu} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in our appendix.
+Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in our appendix.
 Nevertheless, to be clear the essential idea of Lemma~\ref{lem:zhu} is no different than that of~\cite{zhu2013}, and we do not claim any novelty.}
@@
 \tau_{\infty}(G) := \min\set{ t: \frac{{\pi}(u) - {q}_{v}^{(t)}(u)}
-	{{\pi}(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in V$}},
-\end{equation}
-where $q_v^{(t)} = e_v W^t$ is the distribution of a lazy random walk starting at node $v$ and running for $t$ steps, and $\pi = \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+	{{\pi}(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in V$}};
+\end{equation}
+here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ that originates at node $v$ and runs for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
 \begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
@@
 \paragraph{Improved bounds on mixing time.} Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$.
-Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Phi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \lesssim 1/n$.
-Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a rate of at least $\log n$, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.\footnote{To be clear: $\pi_{\min}(G)$ is obviously at most $1/|V|$ for any graph $G$ with $|V|$ total vertices, not merely $G_{n,r}\bigl[\mc{C}[X]\bigr]$.
-However, while in general it is certainly possible that $\Phi(C;G) \leq \frac{1}{\log(n)} \Psi(G[C])$, this will not be the case in our specific setting, where $G = G_{n,r}$ and $C = \mc{C}[X]$.
-Hence the need for a sharper bound.}
-
-To fix this, we will improve the bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
-While in the worst case (over an arbitrary input graph $G$) a ``start penalty'' of $\log(1/\pi_{\min}(G))$ is unavoidable, fortunately better bounds are possible when $G$ is a geometric graph such as $G_{n,r}$.
-Intuitively, this is because in geometric graphs, small sets are expanders---that is, if a set $R \subseteq V$ has sufficiently small volume, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(G)$.
-As a consequence, a random walk over $G$ will rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' as if the random walk were given a warm start over a larger set $S$.
-To delineate small sets $R$ from larger sets $S$, we introduce the \emph{local spread} functional $s(G)$, defined as
+Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
+Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.
+Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.
+
+To fix this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
+Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the \emph{local spread} of $G$, defined as
 \begin{equation*}
@@
 \end{equation*}
-where $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$.
-
-Using a careful analysis we can make the intuition of the prior paragraph rigorous, leading to an improved upper bound on mixing time in Proposition~\ref{prop:pointwise_mixing_time}.
-The proof of this proposition, as with all results in this paper, is deferred to the appendix.
+for $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$. Note that $s(G) \geq \pi_{\min}(G)$.
 \begin{proposition}
@@
 	\label{eqn:pointwise_mixing_time}
-	\tau_{\infty}(G) \leq \frac{8}{\Psi^2(G)} \ln \left(\frac{4}{s(G)}\right)\log_2 \left(\frac{8}{s(G)}\right)  + 4\log_2 \left(\frac{8}{s(G)}\right) + 1.
+	\tau_{\infty}(G) \leq \frac{13}{\ln(2)} \biggl(\frac{\ln\bigl(8/s(G)\bigr)}{\Psi(G)}\biggr)^2
 	\end{equation}
 \end{proposition}
-
-We emphasize that while Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
-We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:mixing_time}.
+While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
+In the case where $G = G_{n,r}\bigl[\mc{C}[X]\bigr]$ for a fixed radius $r$, the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp n$, and therefore $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1$.
+We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
+
+The local spread $s(G)$ plays an intuitive role in the analysis of mixing time.
+Indeed, in any graph $G$ sufficiently small sets are expanders---that is, if a set $R \subseteq V$ has cardinality less than the minimum degree, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(G)$.
+As a consequence, a random walk over $G$ will rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' that the random walk was given a warm start over a larger set $S$.
+The local spread $s(G)$ simply delineates small sets $R$ from larger sets $S$.
+Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a substantially more careful analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
 
@@
 \label{subsec:sample_to_population}
-\textcolor{red}{(TODO): Fix $\deg_{\min}$ notation, and fix Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}.}\\
-
 In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, local spread, and conductance, in terms of their population-level analogues.
@@
 where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $G_{n,r}\bigl[\mc{C}[X]\bigr]$.
-In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to constants that may depend on $\Pbb$ and $\mc{C}$, but do not depend on $n$ or $\delta$.
-We explicitly keep track of all constants in our proofs.
-\begin{proposition}
-	\label{prop:sample_to_population_1}
-	Fix $\delta \in (0,1/3)$. There exist positive constants $b_1$-$b_3$ such that each of the following statements hold.
-	\begin{itemize}
-		\item With probability at least $1 - 3\exp\{-b_1\delta^2n\}$,
-		\begin{equation}
-		\label{eqn:sample_to_population_normalized_cut}
-		\Phi_{n,r}(\mc{C}[X]) \leq (1 + 3\delta) \Phi_{\Pbb,r}(\mc{C}).
-		\end{equation}
-		\item With probability at least $1 - 2\exp\{-b_2\delta^2n\} - n\exp\{-b_3\delta^2n\}$,
-		\begin{equation}
-		\label{eqn:sample_to_population_local_spread}
-		s_{n,r}(\mc{C}[X]) \geq (1 - 3\delta) s_{\Pbb,r}(\mc{C}).
-		\end{equation}
-	\end{itemize}
-\end{proposition}
-To lower bound the sample conductance $\Psi_{n,r}(\mc{C}[X])$, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
+
+To establish these bounds, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 \end{enumerate}
+In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to constants that may depend on $\Pbb$ and $\mc{C}$, but do not depend on $n$ or $\delta$.
+We explicitly keep track of all constants in our proofs.
+\begin{proposition}
+	\label{prop:sample_to_population_1}
+	Fix $\delta \in (0,1/3)$.
+Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+There exist positive constants $b_1$-$b_3$ such that each of the following statements hold.
+	\begin{itemize}
+		\item With probability at least $1 - 3\exp\{-b_1\delta^2n\}$,
+		\begin{equation}
+		\label{eqn:sample_to_population_normalized_cut}
+		\Phi_{n,r}(\mc{C}[X]) \leq (1 + 3\delta) \Phi_{\Pbb,r}(\mc{C}).
+		\end{equation}
+		\item With probability at least $1 - 2\exp\{-b_2\delta^2n\} - n\exp\{-b_3\delta^2n\}$,
+		\begin{equation}
+		\label{eqn:sample_to_population_local_spread}
+		s_{n,r}(\mc{C}[X]) \geq (1 - 3\delta) s_{\Pbb,r}(\mc{C}).
+		\end{equation}
+	\end{itemize}
+\end{proposition}
 Let $p_d := 3/4$ if $d = 2$, and else $p_d := 1/d$ for $d \geq 3$. 
@@
 Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
-Then there exist positive constants $B_1$, $B_2$ that do not depend on $n$ or $\delta$, such that for any $n \in \mathbb{N}$ for which
+Then there exist positive constants $B_1$ and $B_2$, such that for any $n \in \mathbb{N}$ for which
 	\begin{equation}
@@
 
-A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Hoeffding's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X],\mc{C}^c[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
+A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Hoeffding's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
 To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, but otherwise the proof is similarly straightforward.
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
-We mention here only that our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$.
+Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$.
 For further details, we refer to Appendix~\textcolor{red}{(?)}, where we prove~\eqref{eqn:sample_to_population_conductance}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance.
@@
 \paragraph{Well-initialized algorithm.} As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified
-parameters. In particular, for a candidate cluster $\mc{C}$ and $\delta \in (0,1)$, we require that some of the tuning parameters of Algorithm~\ref{alg:ppr} be chosen to fall within specific ranges,
+parameters. In particular, for $\delta \in (0,1/4)$ and a candidate cluster $\mc{C} \in \Rd$, we require that some of the tuning parameters of Algorithm~\ref{alg:ppr} be chosen within specific ranges,
 
@@
 \begin{aligned}
-& \alpha \in \Bigl[(1 - 2C_2\delta)^2, (1 - C_2\delta)^2\Bigr) \cdot
- \frac{\alpha_{\Pbb,r}(\mc{C})}{2} \\
+& \alpha \in \Bigl[(1 - 4\delta)^2, (1 - 2\delta)^2\Bigr) \cdot
+ \frac{\alpha_{\Pbb,r}(\mc{C},\delta)}{2} \\
 & (L,U) \subseteq \Bigl(\frac{1}{5(1 + 2\delta)},\frac{1}{5(1 + \delta)}\Bigr) \cdot 
@@
 \label{eqn:alpha_initialization}
-\alpha_{\Pbb,r}(\mc{C}) := \biggl\{ \frac{2}{\Psi_{\Pbb,r}^2(\mc{C})} \ln \left(\frac{320}{(1 - C_3\delta)s_{\Pbb,r}(\mc{C})}\right)\log_2 \left(\frac{14}{(1 - C_3\delta)s_{\Pbb,r}(\mc{C})}\right)  + 3 \log_2 \left(\frac{14}{(1 - C_3\delta) s_{\Pbb,r}(\mc{C})}\right) + 3\biggr\}^{-1}.
-\end{equation}
-
-\textcolor{red}{This still seems rather ugly; not sure if there's a way to make it look nicer.}
+\alpha_{\Pbb,r}(\mc{C},\delta) := \min\biggl\{\frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{(1 - 3\delta)s_{\Pbb,r}(\mc{C})}{8}\Bigr)}, \frac{1}{45}\biggr\}
+\end{equation}
 
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
+	If the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
 \end{definition}
 
-In practice of course, it is not feasible to set tuning parameters based on the 
-underlying (unknown) distribution $\Pbb$. Typically, one runs PPR over some range of
+Of course, in practice it is not feasible to set tuning parameters based on the 
+underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$. Typically, one runs PPR over some range of
 tuning parameter values and selects the cluster which has the smallest
@@
 \paragraph{Cluster recovery in symmetric set difference.} By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
-To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$ as
+To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
 \begin{equation}
 \label{eqn:condition_number}
-\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{120 (1 + C_1\delta)}{(1 - 2C_2\delta)^2(1 + 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C})}
+\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)}{(1 - 4\delta)^2(1 - 3\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}
 \end{equation}
@@
 	\label{thm:volume_ssd_ub} 
-	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1)$.
-With probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$.
+With probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 	\begin{aligned}
-	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq \kappa_{\Pbb,r}(\mc{C},\delta)
+	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 30 \cdot \kappa_{\Pbb,r}(\mc{C},\delta)
 	\end{aligned}
@@
 \end{theorem}
-Roughly, the takeaway of Theorem~\ref{thm:volume_ssd_ub} is as follows: if PPR is well-initialized within a candidate cluster $\mc{C}$ for which $\Phi_{\Pbb,r}(\mc{C})$ is significantly smaller than $\Psi_{\Pbb,r}(\mc{C})^2/\log\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ will be a small fraction of the overall volume of $\mc{C}[X]$.
+To summarize: if PPR is well-initialized within a candidate cluster $\mc{C}$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ is upper bounded by the following function of the population-level functionals:
+\begin{equation*}
+\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \lesssim \Phi_{\Pbb,r}(\mc{C})  \cdot \frac{\log^2\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)}{\Psi^2_{\Pbb,r}(\mc{C})}.
+\end{equation*}
 We now make some other remarks:
 \begin{itemize}
-	\item It is useful to compare Theorem~\ref{thm:volume_ssd_ub} with what is already known regarding \emph{global} spectral clustering in the context of non-parametric statistics.
-\citep{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^{k}$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters $\wh{C}_1,\ldots,\wh{C}_k$  using $k$-means clustering.
+	\item It is useful to compare Theorem~\ref{thm:volume_ssd_ub} with what is already known regarding \emph{global} spectral clustering in the context of nonparametric statistics.
+\cite{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^{k}$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters $\wh{C}_1,\ldots,\wh{C}_k$  using $k$-means clustering.
 They derive error bounds on the misclassification error that depend on a difficulty function $\varphi(\Pbb)$.
@@
 Second,~\eqref{eqn:schiebinger} depends on $\sqrt{\Phi_{\Pbb,r}(\mc{C})}$ rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citep{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
-Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}.
-Notwithstanding these particular differences, at a high level the conclusions of~\citep{schiebinger2015} are similar to those suggested by our Theorem~\ref{thm:volume_ssd_ub}, and our Theorem~\ref{thm:volume_ssd_ub} thus gives qualitatively similar bounds on local spectral clustering as have already been derived with respect to a global spectral algorithm in the non-parametric statistical context.
-
-	\textcolor{red}{I think this last sentence is a bit of a mess, but kept trying and failing to improve it.}
-\end{itemize}
-
-\subsection{Approximate PPR vector}
-
-\textcolor{red}{This subsection seems tangential to our main points, both in this section and in the paper as a whole. How do you feel about making it a remark, instead of a whole subsection?}
-
-In practice, exactly solving the system of equations~\eqref{eqn: ppr_vector} to compute the PPR vector may be too computationally expensive.
-To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p^{(\varepsilon)}$}.
-We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
-\begin{equation}
-\label{eqn: appr_error}
-\textrm{for all $u \in V$}, \quad p(u) - \varepsilon D_{uu}\leq
-p^{(\varepsilon)}(u) \leq p(u).  
-\end{equation}
-For a sufficiently small choice of $\varepsilon$, the 
+Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}.
+
+	\item Although Theroem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
 	application of \eqref{eqn: appr_error} within the proof of Theorem
-\ref{thm:volume_ssd_ub} leads to an analogous result which holds for \smash{$p^{(\varepsilon)}$}.
-
+	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
 	\begin{corollary}
@@
 	\end{corollary}	
+\end{itemize}
 
@@
 We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
-In addition, we introduce a separate notion of consistency that is particularly relevant to the density clustering problem, and establish conditions under which local clustering with PPR is consistent in this sense.
-Finally, we derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
-Viewed as a whole, the results of this section can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if $\mc{C}_{\lambda}$ is \emph{well-conditioned}, both geometrically---meaning it is not too long and thin--- and vertically---meaning $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near it's boundary.
-
-\textcolor{red}{It would be more symmetric to replace the word ``geometrically'' by ``horizontally''; thoughts?}
+We also derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
+Together, these results can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if $\mc{C}_{\lambda}$ is \emph{well-conditioned}, both geometrically---meaning it is not too long and thin--- and vertically---meaning $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near its boundary.
 
@@
 We start with some background on density clustering.
-Let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$.
-In the density clustering problem, initiated by~\cite{hartigan1981}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
+For a given threshod $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$.
+In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
 By now, density clustering (and the related problem of level-set estimation) are relatively well-understood.
-\citet{polonik1995,
-	rigollet2009} study density clustering under the symmetric set difference
+\citet{polonik1995,rigollet2009} study density clustering under the symmetric set difference
 metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
@@
 not to improve on these results, nor to offer a better algorithm for level set
-estimation---indeed, seen as a density clustering algorithm, PPR has none 
-of the optimality guarantees found in the aforementioned works---but rather to better understand the implications of our general theory by applying it within an already well-studied framework.
+estimation, but rather to better understand the implications of our general theory by applying it within an already well-studied framework.
+Indeed, seen as a density clustering algorithm, PPR has none
+of the optimality guarantees found in the aforementioned works.
 We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
@@
 A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus cannot be resolved by any finite number of samples.
-This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} \textcolor{red}{(...)}.
-We choose to follow the \textcolor{red}{(simple and elegant)} approach of~\cite{chaudhuri2010}, who conduct their analysis with respect to a thickened version of $\mc{C}_{\lambda}$ defined as $C_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) \leq \sigma\}$ for some $\sigma > 0$.
-(Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.)
-
-\textcolor{red}{This subsection feels too casual to me.
-In particular the second paragraph probably needs to be made more precise and detailed.
-But for now I'll leave it, and you can tell me if agree it needs work, or think it's basically fine as is.}
+This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to a lower semi-continuous version of $f$.
+We instead choose to follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) \leq \sigma\}$ for some $\sigma > 0$.
+(Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.) The set $\mc{C}_{\lambda,\sigma}$ is full dimensional with a smooth boundary, and thus no continuity assumption on $f$ is required.
+
+\textcolor{blue}{Alden for Siva: I need to follow up on whether we have handled the "discontinuous" density case correctly or not.}
 
@@
 \begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{2}
 	\item
@@
 			\mathcal{K}}\|x - y\| \leq \rho < \infty$;
-		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{C}_{\lambda,\sigma}$, where $\nabla g(x)$ is
+		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is
 		the Jacobian of $g$ evaluated at $x;$ and 
@@
 \begin{enumerate}[label=(A\arabic*)]
-	\setcounter{enumi}{3}
+	\setcounter{enumi}{5}
 	\item
@@
 \paragraph{Normalized cut, conductance, and local spread of a density cluster.} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
-These bounds depend on the various geometric conditions just introduced.
+These bounds depend on the various geometric parameters just introduced.
 \begin{lemma}
@@
 	\label{eqn:density_cluster_local_spread}
-	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{2} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{r}{2L\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr)
+	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{4} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{2r}{\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr)
 	\end{equation}
@@
 \noindent Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$.
+In the following, $C_{1,\delta}$ and $C_{2,\delta}$ are constants which may depend only on $\delta$, but not $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$.
 
@@
 	\item Several modifications of global spectral clustering have been proposed with the intent of making such procedures essentially independent of the geometry of the density cluster $\mc{C}_{\lambda}$.
-For instance,~\citep{pelletier2011,arias-castro2009} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance.
+For instance,~\citet{pelletier2011,arias-castro2009} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance.
 The resulting procedures come with stronger density cluster recovery guarantees.
@@
 	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population-level normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
-It seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} apply to the output of global spectral clustering methods as well, albeit with suitable alterations as per our discussion after Theorem~\ref{thm:volume_ssd_ub}, but formalizing this is outside the scope of our work.
+It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
 \end{itemize}
-
-\subsection{Consistency}
-\label{subsec:consistent_recovery_density_clusters}
-
-\textcolor{red}{For the moment, I have kept the ordering of this subsection and the following subsection, which gives our negative example. But I think it might make sense to switch them?}\\
-
-The symmetric set difference does not measure whether \smash{$\wh{C}$}
-can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in 
-	\mathbb{C}_f(\lambda)$}. We therefore also study a second notion of cluster 
-estimation, first introduced by \citet{hartigan1981}, and defined
-asymptotically.
-
-\begin{definition}
-	\label{def:density_cluster_consistency}
-	For an estimator \smash{$\wh{C} \subseteq X$} and cluster \smash{$\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$}, we call \smash{$\wh{C}$} \emph{consistent} for
-	\smash{$\mc{C}_{\lambda}$} if for all \smash{$\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$} with  
-	\smash{$\mc{C} \not= \mc{C}'$}, the following holds with probability tending to 1 as $n \to \infty$: 
-	\begin{equation}
-	\label{eqn:density_cluster_consistency}
-	\mc{C}[X] \subseteq \wh{C} \quad \text{and} \quad
-	\wh{C} \cap \mc{C}'[X] = \emptyset.
-	\end{equation}
-\end{definition}
-
-Consistent cluster recovery roughly ensures that, for a given 
-threshold $\lambda>0$, the estimated cluster \smash{$\wh{C}$} contains all points
-in a true density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$, and simultaneously does 
-not contain any points in any other density cluster $\mc{C}_{\lambda}' \in
-\mathbb{C}_f(\lambda)$.
-
-The bound on symmetric set difference \eqref{eqn:density_cluster_volume_ssd_ub} does not imply consistent density cluster estimation in the sense of \eqref{eqn:density_cluster_consistency}.
-This notion of consistency requires a
-uniform bound over the PPR vector $p_v$: as an example, suppose that we were
-able to show that for all \smash{$\mc{C}' \in \mathbb{C}_f(\lambda), \mc{C}' \neq \mc{C}$}, and each $u \in \mc{C}, w \in \mc{C}'$,  
-\begin{equation}
-\label{eqn:ppr_gap}
-\frac{p_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} <
-\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \leq \frac{p_v(u)}{D_{uu}}. 
-\end{equation}
-Then, any $(L,U)$ satisfying~\eqref{eqn:initialization} and any sweep cut
-$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
-\eqref{eqn:density_cluster_consistency}. In Theorem 
-\ref{thm:density_cluster_consistent_recovery}, we show that a sufficiently 
-small upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ ensures that with high probability the uniform bound~\eqref{eqn:ppr_gap} is satisfied, and hence implies
-\smash{$\wh{C}$} will be a consistent estimator.
-\begin{theorem}
-	\label{thm:density_cluster_consistent_recovery}
-	For any $\delta \in (0,1)$, the following statement holds with probability at least $1 - 3\exp\{-b_1\delta^2n\} - B_2n\exp\{-b_2\delta^2n\}$: there exists a constant $c_1$ and a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,  \smash{$\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$}, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
-	\begin{equation}
-	\label{eqn:density_cluster_consistent_recovery_condition}
-	\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta) \leq c_1 \cdot \min_{x: f(x) \geq \lambda} \Bigl\{\deg_{\Pbb,r}(x)\Bigr\},
-	\end{equation}
-then the PPR estimated cluster \smash{$\wh{C}$} satisfies \eqref{eqn:density_cluster_consistency}.
-\end{theorem}
-\textcolor{red}{(In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.)}\vspace{1 mm}
-
-On the other hand, unfortunately the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition} is rather restrictive. Specifically, from the following chain of inequalities,
-\begin{equation*}
-\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:lambda_bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
-\end{equation*}
-we see that in order for~\eqref{eqn:density_cluster_consistent_recovery_condition} to be met, it is necessary that \smash{$\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$} be at most $c_1 \cdot \Lambda_{\sigma} \nu_d r^d$.
-In plain terms, we
-are able to recover a density cluster $\mc{C}_{\lambda}$ in the strong sense of
-\eqref{eqn:density_cluster_consistency} only when we can guarantee the volume of the symmetric set difference will be very small. This strong condition is
-the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}.\vspace{1 mm}
-
-\textcolor{red}{Originally, we had only (something like) the preceding paragraph, which in my opinion is very negative and invites the reader to discount the preceding result.
-I added the paragraph in red above it, to make it clear that the Corollary is interesting even if the required conditions are strong.}
 
@@
 \label{subsec:lower_bound}
-We conclude this section by exhibiting a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
+We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
 cluster. Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in
@@
 \end{theorem}
+
+\textcolor{red}{(TODO): Either (preferably) replace $C_4$ by a number, or otherwise say that it is a universal constant.}
 
@@
 
-We provide numerical experiments to investigate the tightness of our theoretical results, and examine the performance of PPR on the ``two moons'' dataset.
+We provide numerical experiments to investigate the tightness of our theoretical results in Section~\ref{sec:ppr_density_cluster}, and examine the performance of PPR on the ``two moons'' dataset.
 We defer details of the experimental settings to the appendix.
 
-\begin{figure}[tb]
+\paragraph{Validating theoretical bounds.}
+We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance} via simulation.
+Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities.
+In the first row we vary the diameter $\rho$ of the candidate cluster, in the second row we vary the thickness $\sigma$ of the candidate cluster, and in the last row we vary the magnitude $\theta$ of the density drop.
+In each case, we see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude or less.
+The looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
+Nevertheless, for sufficiently well-conditioned enough densities our upper bound will be $\ll 1$; for instance, when $\sigma = \textcolor{red}{(?)}$, $\rho = \textcolor{red}{(?)}$ and $\theta = \textcolor{red}{(?)}$.\\
+
+\textcolor{red}{Alden for Ryan: the last couple of sentences are an attempt at what we discussed in our meeting. I am not satisfied with it, but could not do better.}
+
+\begin{figure}[htb]
 	\centering
-	\includegraphics[width=0.32\textwidth]{../sample2}
-	\includegraphics[width=0.32\textwidth]{../sample1}
-	\includegraphics[width=0.32\textwidth]{../sigma_normalized_cut_plot}
-	\includegraphics[width=0.32\textwidth]{../sigma_mixing_time_plot}
-	\includegraphics[width=0.32\textwidth]{../diameter_normalized_cut_plot}
-	\includegraphics[width=0.32\textwidth]{../diameter_mixing_time_plot}
-	\caption{\it\small Top left and top middle: samples from a geometrically
-		well- and poor-conditioned cluster.
-The points in $\mc{C}_{\lambda}$ are colored in red, points in $\mc{C}_{\lambda,\sigma} \!\setminus\!
-\mc{C}_{\lambda}$ are colored in yellow, and the remaining points in blue.
-Other panels: empirical normalized cut and mixing time, as a function of $\sigma$ or $\rho$, versus their theoretical upper bounds.}
+	\includegraphics[width=0.32\textwidth]{plots/experiment_1/normalized_cut.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/experiment_1/conductance.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/experiment_1/local_spread.pdf}
+	\caption{\it \small Empirical normalized cut, conductance, and local spread (in blue), versus their theoretical upper bounds (in red).
+In the top row we vary the diameter $\rho$, in the middle row we vary the thickness $\sigma$, and in the bottom row we vary the density drop $\theta$.
+\textcolor{red}{(TODO): Add middle and bottom row.}}
 	\label{fig:bounds}
 \end{figure}
-
-\paragraph{Validating theoretical bounds.}  We investigate the tightness of
-Propositions~\ref{prop:density_cluster_normalized_cut} and Proposition~\ref{prop:density_cluster_conductance}, as well as the resulting Corollary~\ref{cor:density_cluster_volume_ssd_ub}, via simulation.
-Figure \ref{fig:bounds} compares our bounds on normalized cut and conductance with the actual empirically-computed quantities \eqref{eqn:normalized_cut} and \eqref{eqn:conductance}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\mc{C}$.
-The top left and top middle panels display the resulting empirical clusters for two different values of $\rho,\sigma$.
-
-The bottom left and bottom right panels assure that our lower bounds on conductance track closely with the empirical conductance, in both 2 and 3 
-dimensions.\footnote{We rescaled all values of theoretical bounds by a constant, to mask the effect of large universal constants in these bounds.
-Therefore only the comparison of slopes, rather than intercepts, is meaningful.} \textcolor{red}{(TODO): Need to change the ``mixing time'' panels to ``conductance'' panels.} This provides empirical evidence that Proposition~\ref{prop:density_cluster_conductance} has the right dependency on both expansion parameter $\sigma$ and diameter $\rho$.
-The story for the normalized cut panels
-is less obvious. We remark that while, broadly speaking, the trends do not
-appear to match, this gap between theory and empirical results seems largest
-when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
-grows, the slopes of empirical and theoretical curves become more similar.
-
-\textcolor{red}{(TODO): Include a second figure comparing the volume of the symmetric set difference with our upper bound on the volume of the symmetric set difference.
-Point out that this comparison also validates Theorem~\ref{thm:volume_ssd_ub}, since Corollary~\ref{cor:density_cluster_volume_ssd_ub} is a corollary of this theorem.}
 
@@
 \label{sec:discussion}
-In this work, we have analyzed the behavior of PPR in the classical setup of non-parametric statistics.
-We have shown how PPR depends on the geometry of the distribution $\Pbb$ through the population level normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
+In this work, we have analyzed the behavior of PPR in the classical setup of nonparametric statistics.
+We have shown how PPR depends on the distribution $\Pbb$ through the population-level normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
 In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if it is geometrically and vertically well-conditioned.
@@
 In another direction, it would be very useful to find reasonable conditions under which the ratio $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ would tend to $0$ as $n \to \infty$.
-It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR (similar to~\eqref{eqn:ppr_gap}).
-Although most work thus far on spectral clustering methods has focused on deriving bounds on the $\Leb^1$- or $\Leb^2$-error, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
+It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR.
+Although most results thus far derive bounds on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
 It is not clear whether the techniques used in these works can be applied to PPR.
@@
 Finally, after reading our Section~\ref{sec:ppr_density_cluster}, the practitioner may be tempted to ask why they should estimate a density cluster using PPR, when other methods are available with superior statistical guarantees.
-A rather prosaic, if undoubtedly correct, answer is that the ``ideal'' cluster is entirely in the eye of the beholder.
+A undoubtedly correct, if perhaps unsatisfying, answer is that the ``ideal'' cluster is entirely in the eye of the beholder.
 For instance, it is quite common to define an ideal cluster as one with a small normalized cut, in which case the cluster output by PPR may be quite preferable to standard density clustering procedures.
-A more intriguing answer is that a (local) spectral method such as PPR may be more stable in the presence of noise than traditional density clustering procedures.\footnote{In the context of semi-supervised learning, a similar argument was alluded to by Misha Belkin and Partha Niyogi~\citep{belkin2002}, who say:
-\begin{quote}
-One possible simple approach is to use ``geodesic nearest neighbors''. However, while simple and well-motivated, this method is potentially unstable.	
-\end{quote}
-} Such a question could be answered by comparing the sample complexity of spectral clustering methods with density clustering procedures, but to our knowledge, the sample complexity of spectral methods remains unknown.
+On the other hand, it would also be interesting to know whether a (local) spectral method such as PPR converges more rapidly (as a function of $n$) than standard density clustering procedures.
+Such a question could be answered by comparing the sample complexity of spectral clustering methods with that of density clustering procedures, but to our knowledge, the sample complexity of spectral methods remains unknown.
 

### 2021-01-13 jmlr/revision/proofs.tex

@@
 \newcommand{\wh}[1]{\widehat{#1}}
-\newcommand{\ol}[1]{\overline{#1}}
+\newcommand{\ol}[1]{\wb{#1}}
 \newcommand{\spec}{\mathrm{spec}}
@@
 \begin{equation*}
-C(K_0;h) := \max\set{\frac{h(k) - L_{K_0}(k;h)}{\sqrt{\overline{k}}}: K_0 \leq k \leq  2m - K_0}.
-\end{equation*}
-where we use the notation $\overline{k} := \min\{k, 2m - k\}$, and treat $0/0$ as equal to $1$.
+C(K_0;h) := \max\set{\frac{h(k) - L_{K_0}(k;h)}{\sqrt{\wb{k}}}: K_0 \leq k \leq  2m - K_0}.
+\end{equation*}
+where we use the notation $\wb{k} := \min\{k, 2m - k\}$, and treat $0/0$ as equal to $1$.
 Our first pair of Lemmas upper bound $h^{(t)}$ and $h^{(\alpha)}$ as a function of $L_{K_0}$ and $C(K_0)$.
@@
 	\label{eqn:mixing_time_PPR}
-	h^{(\alpha)}(k) \leq \alpha t + L_{K_0}(k; h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
+	h^{(\alpha)}(k) \leq \alpha t + L_{K_0}(k; h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}}\left(1 - \frac{\phi^2}{8}\right)^t
 	\end{equation}
@@
 \label{pf:linearization_bound_1}
-\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq
+\frac{h(k) - L_{K_0}(k)}{\sqrt{\wb{k}}} \leq
 \begin{cases}
@@
 	\textbf{Case 1.}
-	Assume $k_j - \Psi(G) \overline{k}_j$ and $k_j + 2 \Psi(G) \overline{k}_j$ are both in $[K_0,2m  - K_0]$.
+	Assume $k_j - \Psi(G) \wb{k}_j$ and $k_j + 2 \Psi(G) \wb{k}_j$ are both in $[K_0,2m  - K_0]$.
 We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h} and obtain the following:
 	\begin{align*}
-	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \overline{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \overline{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
-	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\overline{k_j - \Psi(G) \overline{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \overline{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
-	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\overline{k_j - \Psi(G) \overline{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \overline{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
-	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\overline{k}_j - \Psi(G) \overline{k}_j} + \sqrt{\overline{k}_j + \Psi(G) \overline{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
+	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
+	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
+	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
+	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
 	\end{align*}
@@
 	\begin{align*}
-	h^{(t)}(k_j) & \leq L_{K_0}(k;h^{(t_0)}) + \frac{C(K_0;h^{(t_0)})}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\Psi(G)^2}{4}\right)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-1} \\
-	&= L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)})\sqrt{\overline{k}_j}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}.
-	\end{align*}
-
-	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \overline{k}_j$ or $k_j + 2 \Psi(G) \overline{k}_j$ is not in $[K_0,2m  - K_0]$.
-Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
+	h^{(t)}(k_j) & \leq L_{K_0}(k;h^{(t_0)}) + \frac{C(K_0;h^{(t_0)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\Psi(G)^2}{4}\right)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-1} \\
+	&= L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)})\sqrt{\wb{k}_j}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}.
+	\end{align*}
+
+	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \wb{k}_j$ or $k_j + 2 \Psi(G) \wb{k}_j$ is not in $[K_0,2m  - K_0]$.
+Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
 We deduce the following:
@@
 	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
-	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
-	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
+	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
+	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
+	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
 	\end{align*}
@@
 Our base case will be $t = 0$.
-Observe that $C(K_0;h^{(\alpha)}) \cdot \sqrt{\overline{k}} \geq h^{(\alpha)}(k) - L_{K_0}(k;h^{(\alpha)})$ for all $k \in [K_0,2m - K_0]$, which implies
-	\begin{equation*}
-	L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)}) \cdot \sqrt{\overline{k}} \geq h^{(\alpha)}(k).
+Observe that $C(K_0;h^{(\alpha)}) \cdot \sqrt{\wb{k}} \geq h^{(\alpha)}(k) - L_{K_0}(k;h^{(\alpha)})$ for all $k \in [K_0,2m - K_0]$, which implies
+	\begin{equation*}
+	L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)}) \cdot \sqrt{\wb{k}} \geq h^{(\alpha)}(k).
 	\end{equation*}
@@
 	p_v[k_j] & \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \mathrm{cut}(S_j;G)] + p_v[k_j + \mathrm{cut}(S_j;G)] \bigr) \nonumber\\
-	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \Phi(S_j;G) \overline{k}_j] + p_v[k_j + \Phi(S_j;G) \overline{k}_j]  \bigr) \nonumber \\
-	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \phi \overline{k}_j] + p_v[k_j + \phi \overline{k}_j]\bigr) \nonumber
+	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \Phi(S_j;G) \wb{k}_j] + p_v[k_j + \Phi(S_j;G) \wb{k}_j]  \bigr) \nonumber \\
+	& \leq \alpha + \frac{1}{2} \bigl(p_v[k_j - \phi \wb{k}_j] + p_v[k_j + \phi \wb{k}_j]\bigr) \nonumber
 	\end{align}
@@
 	\label{eqn:mixing_time_PPR_pf1}
-	h^{(\alpha)}(k_j) \leq \alpha + \frac{1}{2} \bigl(h^{(\alpha)}(k_j - \phi \overline{k}_j) + h^{(\alpha)}(k_j +  \phi \overline{k}_j) \bigr)
+	h^{(\alpha)}(k_j) \leq \alpha + \frac{1}{2} \bigl(h^{(\alpha)}(k_j - \phi \wb{k}_j) + h^{(\alpha)}(k_j +  \phi \wb{k}_j) \bigr)
 	\end{equation}
@@
 	\textbf{Case 1.}
-	Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$.
-We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
-	\begin{align*}
-	h^{(\alpha)}(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
-	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
-	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
+	Assume $k_j - 2 \phi \wb{k}_j$ and $k_j + 2 \phi \wb{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
+	\begin{align*}
+	h^{(\alpha)}(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k}_j - \phi \wb{k}_j} + \sqrt{\wb{k}_j + \phi \wb{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
 	\end{align*}
@@
 	\begin{equation*}
-	h^{(\alpha)}(k_j) \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
-	\end{equation*}
-
-	\textbf{Case 2.} Otherwise one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$.
-Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
+	h^{(\alpha)}(k_j) \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
+	\end{equation*}
+
+	\textbf{Case 2.} Otherwise one of $k_j - 2 \phi \wb{k}_j$ or $k_j + 2 \phi \wb{k}_j$ is not in $[K_0,2m  - K_0]$.
+Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
 By the concavity of $h$, and applying the inductive hypothesis to $h^{(\alpha)}2k_j - K_0)$, we have
@@
 	h^{(\alpha)}(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h^{(\alpha)}(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0;p^{\alpha}) + L_{K_0}(2k_j - K_0\bigr) + C(K_0;h^{(\alpha)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
-	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
-	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
+	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0;p^{\alpha}) + L_{K_0}(2k_j - K_0\bigr) + C(K_0;h^{(\alpha)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
+	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
+	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
 	\end{align*}
@@
 \label{sec:sample_to_population}
-In this section, we prove Proposition~\ref{prop:sample_to_population_1}, by establishing high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, and normalized cut~(\ref{subsec:sample_to_population_ncut}), minimum and maximum degree, and local spread~(\ref{subsec:sample_to_population_local_spread}), and conductance~(\ref{subsec:sample_to_population_conductance}).
+In this section, we prove Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, by establishing high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, and normalized cut~(\ref{subsec:sample_to_population_ncut}), minimum and maximum degree, and local spread~(\ref{subsec:sample_to_population_local_spread}), and conductance~(\ref{subsec:sample_to_population_conductance}).
 To establish these results, we will use several different concentration inequalities, and we begin by reviewing these in~(\ref{subsec:concentration}).
@@
 For a probability measure $\Qbb$, we also write
-\begin{equation*}
+\begin{equation}
+\label{eqn:population_minmax_degree}
 d_{\min}(\Qbb) := \inf_{x \in \mathrm{supp}(\mbb{Q})} \deg_{\Pbb,r}(x),~~\textrm{and}~~d_{\max}(\Qbb) := \sup_{x \in \mathrm{supp}(\mbb{Q})} \deg_{\Pbb,r}(x).
-\end{equation*}
+\end{equation}
 
@@
 We write $\norm{\varphi}_{\infty} = \sup_{x,y} |\varphi(x,y)|$. 
-\begin{lemma}[Hoeffding's Inequality for U-statistics.]
+\begin{lemma}[Hoeffding's Inequality for Order-2 U-statistics.]
 	\label{lem:hoeffding}
@@
 	\end{equation}
-	For any $x \in \Rd$, the remainder terms can be upper bounded: for any $\Delta_{12} \geq 0$,
+	For any $x \in \Rd$, the remainder terms can be upper bounded: since $\Delta_{12} \geq 0$,
 	\begin{equation*}
@@
 	\end{equation*}
-	and for any $0 \leq \Delta_{12} \leq r/(4(d - 1))$,
+	if $0 \leq \Delta_{12} \leq r/(4(d - 1))$,
 	\begin{equation*}
@@
 	To derive~\eqref{pf:conductance_lb_transportation_distance_3}, suppose that $\mc{R} \subseteq \mathrm{supp}(\mbb{Q}_2)$ and $\mc{R} \not\in \mathfrak{L}(\mbb{Q}_1,\mbb{Q}_2)$.
-Without loss of generality, we shall assume that $\vol_{\mbb{Q}_2,r}(\mc{R}) \leq (1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2$ (otherwise we can work with respect to $\mc{R}^c$.)  Then, for all $x \in \mc{R}$:
+Without loss of generality, we shall assume that $\vol_{\mbb{Q}_2,r}(\mc{R}) \leq (1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2$ (otherwise we can work with respect to $\mc{R}^c$.)  Then, for all $x \in \mc{R}$,
 	\begin{equation*}
@@
 \section{Population functionals for density clusters}
+\label{sec:density_cluster_population_functionals}
+In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
+In these proofs, we make use of some estimates on the volume of spherical caps, and we detail these in Section~\ref{subsec:spherical caps}; we also use some isoperimetric inequalities that we detail in Section~\textcolor{red}{(?)}.
+Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
+
+\subsection{Proof of Lemma~\ref{lem:density_cluster_local_spread}}
+\label{subsec:density_cluster_local_spread}
+The population-level local spread of $\mc{C}_{\lambda,\sigma}$ is
+\begin{equation*}
+s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \frac{\bigl(d_{\min}(\wt{\Pbb})\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)}
+\end{equation*}
+where we recall that $\wt{\Pbb}(\mc{S}) = \frac{\Pbb(\mc{S} \cap \mc{C}_{\lambda,\sigma})}{\Pbb(\mc{C}_{\lambda,\sigma})}$ for Borel sets $\mc{S}$, and $d_{\min}(\wt{\Pbb}) := \min_{x \in \mc{C}_{\lambda,\sigma}}\{\deg_{\wt{\Pbb},r}(x)\}^2$.
+To lower bound $s_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, we first lower bound $d_{\min}(\wt{\Pbb})$, and then upper bound $\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)$.
+Using the lower bound $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$ stipulated in~\ref{asmp:lambda_bounded_density}, we deduce that
+\begin{align*}
+d_{\min}(\wt{\Pbb}) & = \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int \1\{\|x - y\| \leq r\} \,d\wt{\Pbb}(y) \Bigr\} \\
+& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\| \leq r\} \,dy \Bigr\} \\
+& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \frac{1}{2}\nu_dr^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr),
+\end{align*}
+where the final inequality follows from Lemma~\ref{lem:overlap_balls}.
+
+On the other hand, using the upper bound $f(x) \leq \Lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$, we deduce that
+\begin{align*}
+\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\|\leq r\} \,d\wt{\Pbb}(y) \,d\wt{\Pbb}(x) \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \int_{\mc{C}_{\lambda,\sigma}} \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\|\leq r\} \,dy \,dx \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d r^d \cdot \nu(\mc{C}_{\lambda,\sigma}) \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d^2 r^d  \cdot \Bigl(\frac{\rho}{2}\Bigr)^d;
+\end{align*}
+the final inequality follows from~\ref{asmp:embedding}, which implies that $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
+The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
+
+\subsection{Proof of Proposition~\ref{prop:density_cluster_normalized_cut}}
+\label{subsec:density_cluster_ncut}
+By Assumption~\ref{asmp:bounded_volume}, we have that $\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})/\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, and to prove Proposition~\ref{prop:density_cluster_normalized_cut} we must therefore upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ and lower bound $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
+
+Let $\mc{C}_{\lambda,\sigma + r} = \{x: \mathrm{dist}(x,\mc{C}_{\lambda}) \leq \sigma + r\}$.
+We upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the probability mass of $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$:
+\begin{align*}
+\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \not\in \mc{C}_{\lambda,\sigma} \} \,d\Pbb(y) \,d\Pbb(x) \\
+& \leq  \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \in \mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}  \} \,d\Pbb(y) \,d\Pbb(x) \\
+& \leq \lambda \nu_d r^d \cdot \Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr).
+\end{align*}
+On the other hand, using the lower bound $f(x) \geq \lambda_{\sigma} $ for all $x \in \mc{C}_{\lambda,\sigma}$, we lower bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the Lebesgue measure of $\mc{C}_{\lambda,\sigma}$:
+\begin{align*}
+\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \,d\Pbb(y) \,d\Pbb(x) \\
+& \geq \lambda_{\sigma}^2 \cdot \iint \1\{\|x - y\| \leq r \} \cdot \1\{x,y \in \mc{C}_{\lambda,\sigma}\} \,dy \,dy \\
+& \geq \lambda_{\sigma}^2 \cdot \frac{1}{2} \nu_d r^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr) \cdot \nu(\mc{C}_{\lambda,\sigma}).
+\end{align*}
+Finally, we claim that under Assumption~\ref{asmp:low_noise_density}, for any $r \leq \sigma/4d$ the $(\sigma + r)$-thickened set $\mc{C}_{\lambda,\sigma + r}$ satisfies the following isoperimetric inequality:
+\begin{equation}
+\label{pf:density_cluster_normalized_cut}
+\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \frac{dr}{\sigma - dr} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}),
+\end{equation}
+whence the claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows.
+
+\paragraph{Proof of~\eqref{pf:density_cluster_normalized_cut}.}
+For conciseness, we denote $\mc{B}_{\lambda,r} := \mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$.
+To upper bound $\Pbb(\mc{B}_{\lambda,r})$, we begin by partitioning $\mc{B}_{\lambda,r}$ into slices based on distance from $\mc{C}_{\lambda,\sigma}$ as follows: for $k \in \mathbb{N}$,
+\begin{equation*}
+\mathcal{T}_{i,k} = \set{x \in \mc{B}_{\lambda,r}: t_{i,k} < \frac{\mathrm{dist}(x, \mc{C}_{\lambda,\sigma})}{r} \leq t_{i+1,k}}, ~~ \mc{B}_{\lambda,r} = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
+\end{equation*}
+where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
+\begin{equation}
+\label{eqn: partition_ub}
+\Pbb(\mc{B}_{\lambda,r}) = \int_{\mc{B}_{\lambda,r}} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \Bigl(\nu(\mathcal{T}_{i,k}) \cdot \max_{x \in \mathcal{T}_{i,k}}\{f(x)\}\Bigr)
+\end{equation}
+Assumptions~\ref{asmp:lambda_bounded_density} and \ref{asmp:low_noise_density} imply the upper bound
+\begin{equation*}
+\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma},
+\end{equation*}
+and writing
+\begin{equation*}
+\nu(\mathcal{T}_{i,k}) = \nu(\mc{C}_{\lambda,\sigma} + rt_{i+1,k}B) - \nu(\mc{C}_{\lambda,\sigma} + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
+\end{equation*}
+we have
+\begin{align}
+\label{eqn: telescoping_sum}
+\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma} \biggr) \nonumber \\
+& = \underbrace{\sum_{i = 1}^{k} 
+	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - \theta(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - \theta(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - \theta r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi_k},
+\end{align}
+and we now move to upper bound $\Sigma_k$ and $\xi_k$.
+
+\textcolor{red}{(TODO)}.
+
+We first upper bound $\xi_k$, since it is the simpler of the two to upper bound, and the technique we use will be useful in the upper bound on $\Sigma_k$ as well.
+
+We first consider the term $\Sigma_k$.
+$\mc{C}$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\mc{C}_{\lambda,\sigma}} f(x) dx = \infty$.
+Letting $\wb{\mc{C}}$ be the closure of $\mc{C}$, we observe that $\wb{\mc{C}_{\lambda,\sigma}} = \wb{\mc{C}} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\wb{\mc{C}_{\lambda,\sigma}} + \delta B) = \nu(\mc{C}_{\lambda,\sigma} + \delta B)$ (as the boundary $\partial(\mc{C}_{\lambda,\sigma} + \delta B)$ is Lipschitz and therefore has measure zero).
+As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\wb{\mc{C}}$ and obtain
+\begin{equation}
+\label{eqn: slice_volume_bound}
+\nu_{i,k} = \nu(\mc{C}_{\lambda,\sigma} + rt_{i,k}B) \leq \nu(\mc{C}_{\lambda,\sigma})\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
+\end{equation}
+which in turn gives
+\begin{align}
+\Sigma_k & \leq \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
+& = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
+\end{align}
+The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
+\begin{align}
+\lim_{k \to \infty} \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
+& \overset{\text{(i)}}{\leq} \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
+& = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
+\end{align}
+where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(4d)$.
+
+An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
+\begin{align}
+\xi & \overset{\text{(ii)}}{\leq} \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
+& \overset{\text{(iii)}}{\leq} \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - \theta r^{\gamma}) - \theta r^{\gamma} \biggr\}.
+\label{eqn: xi_ub}
+\end{align}
+where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}.
+As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
+
+\subsection{Proof of Proposition~\ref{prop:density_cluster_conductance}}
+\label{subsec:density_cluster_conductance}
+\textcolor{red}{(TODO)}
+
+\subsection{Balls, Spherical Caps, and Associated Estimates}
+\label{subsec:spherical caps}
+In this section, we derive lower bounds on the volume of the intersection between two balls in $\Rd$, and the volume of a spherical cap.
+Results of this type are well-known, but since we could not find exactly the statements we desire, for completeness we also supply proofs.
+We use the notation $B(x,r)$ for a ball of radius $r$ centered at $x \in \Rd$, and $\mathrm{cap}_{r}(h)$ for a spherical cap of height $r$ and radius $r$.
+Recall that the Lebesgue measure of a spherical cap is
+\begin{equation*}
+\nu\bigl(\mathrm{cap}_r(h)\bigr) = \frac{1}{2} \nu_d r^d I_{1 - a}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
+\end{equation*}
+where $a = (r - h)^2/r^2$, and
+\begin{equation*}
+I_{1 - a}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - a} u^{z - 1} (1 - u)^{w - 1} du.
+\end{equation*}
+is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - a$. (Here $\Gamma(\cdot)$ is the gamma function).
+\begin{lemma}
+	\label{lem:overlap_balls}
+	 For any $x,y \in \Rd$ and $r > 0$, it holds that
+	\begin{equation}
+	\label{eqn:overlap_balls_1}
+	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
+	For any $x,y \in \Rd$ and $r,\sigma > 0$ such that $\|x - y\| \leq \sigma$, it holds that,
+	\begin{equation}
+	\label{eqn:overlap_balls_2}
+	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
+\end{lemma}
+\begin{lemma}
+	\label{lem:volume_of_spherical_cap}
+	For any $0 < h \leq r$, and $a = 1 - (2 r h - h^2)/r^2$,
+	\begin{equation*}
+	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d\bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
+	\end{equation*}
+\end{lemma}
+An immediate implication of~\eqref{eqn:overlap_balls_2} is that for any $x \in \mc{C}_{\lambda,\sigma}$,
+\begin{equation}
+\label{eqn:uniform_local_conductance}
+\nu\bigl(B(x,r) \cap \mc{C}_{\lambda,\sigma}\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+\end{equation}  
+\begin{proof}[Proof (of Lemma~\ref{lem:overlap_balls})]
+	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
+	As a result, by Lemma~\ref{lem:volume_of_spherical_cap} we have
+	\begin{equation*}
+	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d \bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
+	\end{equation*}
+	where $a = \|x - y\|^2/(4r^2)$, and the claim follows.
+
+	Next we prove~\eqref{eqn:overlap_balls_2}.
+Assume that $\|x - y\| = \sigma$, as otherwise if $0 \leq \|x - y\| < \sigma$ the volume of the overlap will only be larger.
+Then $B(x,r) \cap B(y,\sigma)$ contains a spherical cap of radius $r$ and height $h = r - \frac{r^2}{2\sigma}$, from Lemma~\ref{lem:volume_of_spherical_cap} we deduce
+	\begin{equation*}
+	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2}\nu_dr^d\biggl(1 - 2\sqrt{a}\cdot\sqrt{\frac{d + 2}{2\pi}}\biggr)
+	\end{equation*}
+	for $a = (r - h)^2/r^2 = r^2/(4\sigma^2)$, and the claim follows.
+\end{proof}
+
+\begin{proof}[Proof (of Lemma~\ref{lem:volume_of_spherical_cap})]
+	For any $0 \leq a \leq 1$, we have that
+	\begin{equation*}
+	\int_{0}^{1 - a}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - a}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du. 
+	\end{equation*}
+	The first integral is simply
+	\begin{equation*}
+	\int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du = \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)},
+	\end{equation*}
+	whereas for all $u \in [0,1]$ and $d \geq 1$, the second integral can be upper bounded as follows:
+	\begin{equation*}
+	\int_{1 - a}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du \leq \int_{1 - a}^{1}(1 - u)^{-1/2}du = \int_{0}^{a} u^{-1/2}du = 2\sqrt{a}.
+	\end{equation*}
+	As a result, 
+	\begin{equation*}
+	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a}\frac{\Gamma(\frac{d}{2} + 1)}{\Gamma(\frac{d + 1}{2})\Gamma(\frac{1}{2})}\biggr)  \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation*}
+\end{proof}
 
@@
 
-\section{aPPR and Misclassification Error}
+\section{Additional results: aPPR and Consistency of PPR}
 \label{sec:appr_misclassification_error}
+
+\subsection{Consistency}
+\label{subsec:consistent_recovery_density_clusters}
+
+The symmetric set difference does not measure whether \smash{$\wh{C}$}
+can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in 
+	\mathbb{C}_f(\lambda)$}. We therefore also study a second notion of cluster 
+estimation, first introduced by \citet{hartigan1981}, and defined
+asymptotically.
+
+\begin{definition}
+	\label{def:density_cluster_consistency}
+	For an estimator \smash{$\wh{C} \subseteq X$} and cluster \smash{$\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$}, we call \smash{$\wh{C}$} \emph{consistent} for
+	\smash{$\mc{C}_{\lambda}$} if for all \smash{$\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$} with  
+	\smash{$\mc{C} \not= \mc{C}'$}, the following holds with probability tending to 1 as $n \to \infty$: 
+	\begin{equation}
+	\label{eqn:density_cluster_consistency}
+	\mc{C}[X] \subseteq \wh{C} \quad \text{and} \quad
+	\wh{C} \cap \mc{C}'[X] = \emptyset.
+	\end{equation}
+\end{definition}
+
+Consistent cluster recovery roughly ensures that, for a given 
+threshold $\lambda>0$, the estimated cluster \smash{$\wh{C}$} contains all points
+in a true density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$, and simultaneously does 
+not contain any points in any other density cluster $\mc{C}_{\lambda}' \in
+\mathbb{C}_f(\lambda)$.
+
+The bound on symmetric set difference \eqref{eqn:density_cluster_volume_ssd_ub} does not imply consistent density cluster estimation in the sense of \eqref{eqn:density_cluster_consistency}.
+This notion of consistency requires a
+uniform bound over the PPR vector $p_v$: as an example, suppose that we were
+able to show that for all \smash{$\mc{C}' \in \mathbb{C}_f(\lambda), \mc{C}' \neq \mc{C}$}, and each $u \in \mc{C}, w \in \mc{C}'$,  
+\begin{equation}
+\label{eqn:ppr_gap}
+\frac{p_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} <
+\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \leq \frac{p_v(u)}{D_{uu}}. 
+\end{equation}
+Then, any $(L,U)$ satisfying~\eqref{eqn:initialization} and any sweep cut
+$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
+\eqref{eqn:density_cluster_consistency}. In Theorem 
+\ref{thm:density_cluster_consistent_recovery}, we show that a sufficiently 
+small upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ ensures that with high probability the uniform bound~\eqref{eqn:ppr_gap} is satisfied, and hence implies
+\smash{$\wh{C}$} will be a consistent estimator.
+\begin{theorem}
+	\label{thm:density_cluster_consistent_recovery}
+	For any $\delta \in (0,1)$, the following statement holds with probability at least $1 - 3\exp\{-b_1\delta^2n\} - B_2n\exp\{-b_2\delta^2n\}$: there exists a constant $c_1$ and a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,  \smash{$\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$}, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
+	\begin{equation}
+	\label{eqn:density_cluster_consistent_recovery_condition}
+	\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta) \leq c_1 \cdot \min_{x: f(x) \geq \lambda} \Bigl\{\deg_{\Pbb,r}(x)\Bigr\},
+	\end{equation}
+	then the PPR estimated cluster \smash{$\wh{C}$} satisfies \eqref{eqn:density_cluster_consistency}.
+\end{theorem}
+\textcolor{red}{(In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.)}\vspace{1 mm}
+
+On the other hand, unfortunately the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition} is rather restrictive. Specifically, from the following chain of inequalities,
+\begin{equation*}
+\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:lambda_bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
+\end{equation*}
+we see that in order for~\eqref{eqn:density_cluster_consistent_recovery_condition} to be met, it is necessary that \smash{$\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$} be at most $c_1 \cdot \Lambda_{\sigma} \nu_d r^d$.
+In plain terms, we
+are able to recover a density cluster $\mc{C}_{\lambda}$ in the strong sense of
+\eqref{eqn:density_cluster_consistency} only when we can guarantee the volume of the symmetric set difference will be very small. This strong condition is
+the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}.\vspace{1 mm}
+
+\textcolor{red}{Originally, we had only (something like) the preceding paragraph, which in my opinion is very negative and invites the reader to discount the preceding result.
+I added the paragraph in red above it, to make it clear that the Corollary is interesting even if the required conditions are strong.}
 

### 2021-01-13 jmlr/revision/response_to_reviewers.tex
Updated rebuttal.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
First of all, we would like to thank the reviewers and associate editor for their thoughtful comments and helpful suggestions, and for the invitation to resubmit. In response to this feedback, we have significantly reworked our manuscript, making the following major changes:

\begin{itemize}
	\item \textbf{New theoretical results.} In a new Section 2, we establish conditions under which Personalized PageRank (PPR), run on a geometric graph, will recover an \emph{arbitrary} candidate cluster $\mc{C} \subseteq \Rd$ (i.e. not necessarily a density cluster).  Our upper bound in Theorem 9 (new version) on the error $\Delta(\wh{C},\mc{C}[X])$ depends on population-level functionals---normalized cut, local spread, and conductance---that have previously been used to analyze the behavior of (global) spectral clustering algorithms in nonparametric mixture models, and we explicitly connect our results to this related work.

	\item \textbf{Improved upper bounds.} In Section 3, we apply this general theory to the specific case where $\mc{C} = \mc{C}_{\lambda}$ is a density cluster. The resulting upper bound on $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ (Corollary 14) is comparable to Theorem~5 of our previous submission, but with significantly smaller universal constants.

	\item \textbf{Reworked exposition.} In particular: 
	\begin{itemize}
		\item We comment more extensively on our major theoretical results, explaining their significance and tying them to related work;
		\item We precisely use universal constants throughout, and in particular offer a cleaner comparison between our upper and lower bounds;
		\item We \textcolor{red}{(emphasize)} the three modular components of our analysis: (i) bounds on PPR in terms of graph functionals; (ii) bounds on graph functionals in terms of population functionals; (iii) in the case of density cluster recovery, bounds on population functionals in terms of geometric parameters. \textcolor{red}{(Do I need to add a sentence here, or is modularity an obviously good goal on its own?)}
	\end{itemize}
\end{itemize}

\section{Response to Associate Editor's Comments}

(\textit{``...usefulness of the key Theorem 5...''}) As outlined above, in our resubmission we have replaced Theorem 5 (old version) by Theorem 9 and Corollary 14 (new version).

Theorem~9 (new version)  is substantially more general than Theorem~5 (old version), as it upper bounds $\Delta(\wh{C},\mc{C}[X])$ for an arbitrary set $\mc{C} \subseteq \Rd$ in terms of the population-level normalized cut and conductance. To the best of our knowledge, this is the first result on the clustering performance of PPR in the non-parametric statistical setup. In some remarks, we compare Theorem~9 to some related literature on global spectral clustering, showing both that Theorem~9 is in certain respect sharper than these related results while naturally requiring (weaker) local rather than global conditions.

Corollary~14 (new version) treats the case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster. It gives substantially tighter (in terms of constants) upper bound on $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ than Theorem~5 (old version). To our knowledge, this is the first resulting tying the clustering performance of a canonical spectral method to recovery of a density cluster.

(\textit{``...sets of zero measure may dramatically alter the topological structure of the level sets.''}) We deal with this difficulty by assuming the density $f(x) \geq \lambda_{\sigma}$ everywhere on the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} = \mc{C}_{\lambda} + B(0,\sigma)$. In our revised submission, we comment explicitly on the difficulty measure-zero sets can play in the definition of density clusters, and clarify how the $\sigma$-thickening resolves this difficulty.

(\textit{``...literature mentioned on density-based clustering (see page 5) abruptly ends in 2013...''}) We have updated our literature review to include more recent works.

\section{Response to Reviewer 1's Comments}

(\textit{``Is $\kappa(\mc{C})$ uniquely defined?''}) We have modified our definition of the condition number so as to make it uniquely defined. We now denote the condition number by $\kappa_{\Pbb,r}(\mc{C},\delta)$, to make clear exactly what the condition number depends on: the distribution $\Pbb$, the graph radius $r > 0$, the candidate cluster $\mc{C} \subset \Rd$, and a high-probability parameter $\delta \in (0,1)$.

(\textit{``...not clear whether or not $c \cdot \kappa(\mc{C}) \leq \vol(X \setminus \mc{C}) / \vol(\mc{C} \cap X)$''}) Whenever the thickened density-cluster $\mc{C}_{\lambda,\sigma}$ satisfies a sufficiently strong low-noise condition---i.e. $\theta$ and $\gamma$ in (A2) are sufficiently large--- it will hold that $\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \vol(X \setminus \mc{C}_{\lambda}) / \vol(\mc{C}_{\lambda} \cap X)$.

(\textit{``...there is a risk that the upper bounds presented here could be too loose that they do not reflect the real performance of the algorithm.''}) In our view, the most useful way to interpret our upper and lower bounds is by focusing on how these bounds depend on the geometric parameters $\sigma, \rho$ and $L$, the density parameters $\lambda,\Lambda_{\sigma},\lambda_{\sigma},\gamma$ and $\theta$, and the dimension $d$, and we have clarified this in our exposition.

Nevertheless, we acknowledge that practically speaking it is useful to have reasonable values for constants, and in our resubmission we have also substantially improved the constants in our upper bounds on normalized cut and mixing time. While it is very hard to know the sharpest possible values for all constants, at relevant points in our appendices we do include discussions of the tightness of our bounds with regards to constants. Finally, we have modified our experiments section so that the reader may more easily compare our upper bounds with empirical reality.

(``[In] \textit{the example used to produce Fig. 2... Thm.5 becomes $\vol\bigl(\wh{C} \vartriangle (\mc{C} \cap X)\bigr) \leq 70950 \cdot \vol\bigl(\mc{C} \cap X\bigr)$. This looks much worse than the trivial case $\wh{C} = \emptyset$.''}) We have substantially improved our bounds, including our bounds on the population-level normalized cut and conductance of density clusters, as well as the difference between sample and population-level normalized cut and conductance. In the specific example used for Fig. 2, our upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ is $\leq 1/2$ whenever $\theta \geq \textcolor{red}{(...)}$.

(``\textit{The use of universal constants throughout the paper is not consistent.}'') We apologize for the confusion. In our new submission, we have clarified our use of constants so as to avoid any ambiguity.

(``\textit{$\kappa(\mc{C})$ should be explicitly reported} [in experiments]'') The condition number will be a rather loose bound (in terms of constants) on the actual performance of the algorithm, a fact we frankly acknowledge in our experiments section. Nevertheless, as pointed out previous, the bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ will be small when $\theta \geq \textcolor{red}{(...)}$.

\textcolor{red}{Alden for Siva: I guess somewhere around here is where it might be helpful to comment on how seriously one should take our constants?}

(``\textit{...parameters used in the first experiment...}'') We now report all parameters for our experiment in Appendix~\textcolor{red}{(?)}.

(``\textit{Minor comments}) We have addressed all of the errors noticed by the reviewer, and we thank them for their careful attention.

\section{Response to Reviewer 2's Comments}

(\textit{``...no explicit smoothness assumption on the density function...''}) This is resolved by assuming $f(x) \geq \lambda_{\sigma}$ on the thickened set $\mc{C}_{\lambda, \sigma} = \mc{C} + B(0,\sigma)$, as in \textcolor{green}{(Chaudhuri and Dasgupta)}. The set $\mc{C}_{\lambda, \sigma}$ is full dimensional with a smooth boundary, and thus no smoothness assumption on $f$ is required.

(\textit{``The bound in Theorem 5 doesn't appear to be something that can go to 0 as $n \to \infty$ and $r \to 0$...''}) This comment is correct. This bound---in Theorem~5 (old version), and now in Theorem~9 (new version)--- is
\begin{equation}
\label{eqn:volume_ssd_ppr}
\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])} \leq 30 \cdot \kappa_{\Pbb,r}(\mc{C},\delta),
\end{equation}
and the right hand side will not converge to $0$ as $n \to \infty$. This is typical in the analysis of spectral clustering algorithms in a non-parametric statistical context~\textcolor{green}{(Shi, Schiebinger, Garcia-Trillos)}, and we make some detailed comparison between our bound and these related works after Theorem~9 (new version). We also confirm, both theoretically and experimentally, that indeed that the misclassification error of PPR will not go to zero as $n \to \infty$, even for some fairly well-conditioned density clusters.

(``\textit{...assumptions for Theorem 6 to hold seem very strong...}'')  We would point out that Theorem~6  is, to the best of our knowledge, the first of its kind---that is, the first to show that spectral clustering can \emph{consistently} recover a geometrically-defined cluster. However, we agree that the assumptions are quite strong, in our revised submission we have moved this Theorem to one of our appendices, so as not to distract from our major points.

(``\textit{...(Def 2) doesn't appear to guarantee a bijection between the true clusters and the estimated clusters...''}) The reviewer is correct that this is fundamental to the local nature of the problem, in which we ask the algorithm to return only one cluster, rather than a clustering. We have clarified this point in our exposition.

\end{document}

### 2021-01-15 jmlr/revision/proofs.tex
Completed proof of upper bound on population ncut.

@@
 In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
-In these proofs, we make use of some estimates on the volume of spherical caps, and we detail these in Section~\ref{subsec:spherical caps}; we also use some isoperimetric inequalities that we detail in Section~\textcolor{red}{(?)}.
+In these proofs, we make use of some estimates on the volume of spherical caps, and we detail these in Section~\ref{subsec:spherical caps}; we also use some isoperimetric inequalities, which we detail in Section~\ref{subsec:isoperimetric_inequalities}.
 Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
-
-\subsection{Proof of Lemma~\ref{lem:density_cluster_local_spread}}
-\label{subsec:density_cluster_local_spread}
-The population-level local spread of $\mc{C}_{\lambda,\sigma}$ is
-\begin{equation*}
-s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \frac{\bigl(d_{\min}(\wt{\Pbb})\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)}
-\end{equation*}
-where we recall that $\wt{\Pbb}(\mc{S}) = \frac{\Pbb(\mc{S} \cap \mc{C}_{\lambda,\sigma})}{\Pbb(\mc{C}_{\lambda,\sigma})}$ for Borel sets $\mc{S}$, and $d_{\min}(\wt{\Pbb}) := \min_{x \in \mc{C}_{\lambda,\sigma}}\{\deg_{\wt{\Pbb},r}(x)\}^2$.
-To lower bound $s_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, we first lower bound $d_{\min}(\wt{\Pbb})$, and then upper bound $\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)$.
-Using the lower bound $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$ stipulated in~\ref{asmp:lambda_bounded_density}, we deduce that
-\begin{align*}
-d_{\min}(\wt{\Pbb}) & = \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int \1\{\|x - y\| \leq r\} \,d\wt{\Pbb}(y) \Bigr\} \\
-& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\| \leq r\} \,dy \Bigr\} \\
-& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \frac{1}{2}\nu_dr^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr),
-\end{align*}
-where the final inequality follows from Lemma~\ref{lem:overlap_balls}.
-
-On the other hand, using the upper bound $f(x) \leq \Lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$, we deduce that
-\begin{align*}
-\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\|\leq r\} \,d\wt{\Pbb}(y) \,d\wt{\Pbb}(x) \\
-& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \int_{\mc{C}_{\lambda,\sigma}} \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\|\leq r\} \,dy \,dx \\
-& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d r^d \cdot \nu(\mc{C}_{\lambda,\sigma}) \\
-& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d^2 r^d  \cdot \Bigl(\frac{\rho}{2}\Bigr)^d;
-\end{align*}
-the final inequality follows from~\ref{asmp:embedding}, which implies that $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
-The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
-
-\subsection{Proof of Proposition~\ref{prop:density_cluster_normalized_cut}}
-\label{subsec:density_cluster_ncut}
-By Assumption~\ref{asmp:bounded_volume}, we have that $\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})/\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, and to prove Proposition~\ref{prop:density_cluster_normalized_cut} we must therefore upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ and lower bound $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
-
-Let $\mc{C}_{\lambda,\sigma + r} = \{x: \mathrm{dist}(x,\mc{C}_{\lambda}) \leq \sigma + r\}$.
-We upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the probability mass of $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$:
-\begin{align*}
-\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \not\in \mc{C}_{\lambda,\sigma} \} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq  \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \in \mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}  \} \,d\Pbb(y) \,d\Pbb(x) \\
-& \leq \lambda \nu_d r^d \cdot \Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr).
-\end{align*}
-On the other hand, using the lower bound $f(x) \geq \lambda_{\sigma} $ for all $x \in \mc{C}_{\lambda,\sigma}$, we lower bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the Lebesgue measure of $\mc{C}_{\lambda,\sigma}$:
-\begin{align*}
-\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \,d\Pbb(y) \,d\Pbb(x) \\
-& \geq \lambda_{\sigma}^2 \cdot \iint \1\{\|x - y\| \leq r \} \cdot \1\{x,y \in \mc{C}_{\lambda,\sigma}\} \,dy \,dy \\
-& \geq \lambda_{\sigma}^2 \cdot \frac{1}{2} \nu_d r^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr) \cdot \nu(\mc{C}_{\lambda,\sigma}).
-\end{align*}
-Finally, we claim that under Assumption~\ref{asmp:low_noise_density}, for any $r \leq \sigma/4d$ the $(\sigma + r)$-thickened set $\mc{C}_{\lambda,\sigma + r}$ satisfies the following isoperimetric inequality:
-\begin{equation}
-\label{pf:density_cluster_normalized_cut}
-\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \frac{dr}{\sigma - dr} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}),
-\end{equation}
-whence the claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows.
-
-\paragraph{Proof of~\eqref{pf:density_cluster_normalized_cut}.}
-For conciseness, we denote $\mc{B}_{\lambda,r} := \mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$.
-To upper bound $\Pbb(\mc{B}_{\lambda,r})$, we begin by partitioning $\mc{B}_{\lambda,r}$ into slices based on distance from $\mc{C}_{\lambda,\sigma}$ as follows: for $k \in \mathbb{N}$,
-\begin{equation*}
-\mathcal{T}_{i,k} = \set{x \in \mc{B}_{\lambda,r}: t_{i,k} < \frac{\mathrm{dist}(x, \mc{C}_{\lambda,\sigma})}{r} \leq t_{i+1,k}}, ~~ \mc{B}_{\lambda,r} = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
-\end{equation*}
-where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
-\begin{equation}
-\label{eqn: partition_ub}
-\Pbb(\mc{B}_{\lambda,r}) = \int_{\mc{B}_{\lambda,r}} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \Bigl(\nu(\mathcal{T}_{i,k}) \cdot \max_{x \in \mathcal{T}_{i,k}}\{f(x)\}\Bigr)
-\end{equation}
-Assumptions~\ref{asmp:lambda_bounded_density} and \ref{asmp:low_noise_density} imply the upper bound
-\begin{equation*}
-\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma},
-\end{equation*}
-and writing
-\begin{equation*}
-\nu(\mathcal{T}_{i,k}) = \nu(\mc{C}_{\lambda,\sigma} + rt_{i+1,k}B) - \nu(\mc{C}_{\lambda,\sigma} + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
-\end{equation*}
-we have
-\begin{align}
-\label{eqn: telescoping_sum}
-\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma} \biggr) \nonumber \\
-& = \underbrace{\sum_{i = 1}^{k} 
-	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - \theta(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - \theta(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - \theta r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi_k},
-\end{align}
-and we now move to upper bound $\Sigma_k$ and $\xi_k$.
-
-\textcolor{red}{(TODO)}.
-
-We first upper bound $\xi_k$, since it is the simpler of the two to upper bound, and the technique we use will be useful in the upper bound on $\Sigma_k$ as well.
-
-We first consider the term $\Sigma_k$.
-$\mc{C}$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\mc{C}_{\lambda,\sigma}} f(x) dx = \infty$.
-Letting $\wb{\mc{C}}$ be the closure of $\mc{C}$, we observe that $\wb{\mc{C}_{\lambda,\sigma}} = \wb{\mc{C}} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\wb{\mc{C}_{\lambda,\sigma}} + \delta B) = \nu(\mc{C}_{\lambda,\sigma} + \delta B)$ (as the boundary $\partial(\mc{C}_{\lambda,\sigma} + \delta B)$ is Lipschitz and therefore has measure zero).
-As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\wb{\mc{C}}$ and obtain
-\begin{equation}
-\label{eqn: slice_volume_bound}
-\nu_{i,k} = \nu(\mc{C}_{\lambda,\sigma} + rt_{i,k}B) \leq \nu(\mc{C}_{\lambda,\sigma})\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
-\end{equation}
-which in turn gives
-\begin{align}
-\Sigma_k & \leq \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
-& = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
-\end{align}
-The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
-\begin{align}
-\lim_{k \to \infty} \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-& \overset{\text{(i)}}{\leq} \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
-& = \theta\nu(\mc{C}_{\lambda,\sigma}) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
-\end{align}
-where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(4d)$.
-
-An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
-\begin{align}
-\xi & \overset{\text{(ii)}}{\leq} \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-& \overset{\text{(iii)}}{\leq} \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\mc{C}_{\lambda,\sigma}) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - \theta r^{\gamma}) - \theta r^{\gamma} \biggr\}.
-\label{eqn: xi_ub}
-\end{align}
-where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}.
-As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
-
-\subsection{Proof of Proposition~\ref{prop:density_cluster_conductance}}
-\label{subsec:density_cluster_conductance}
-\textcolor{red}{(TODO)}
 
@@
 \end{proof}
+
+\subsection{\textcolor{red}{Isoperimetric inequalities}}
+\label{subsec:isoperimetric_inequalities}
+
+For any set $\mc{C} \subseteq \Rd$ and $\sigma > 0$, recall that $\mc{C}_{\sigma} := \{x: \mathrm{dist}(x,\mc{C}) \leq \sigma\}$.
+We begin with an upper bound on the volume of $\mc{C}_{\sigma + \delta}$ as compared to $\mc{C}_{\sigma}$.
+\begin{lemma}
+	\label{lem:external_isoperimetric_inequality}
+	For any bounded set $\mc{C} \subseteq \Rd$ and  $\sigma, \delta > 0$, it holds that
+	\begin{equation}
+	\label{eqn:external_isoperimetric_inequality}
+	\nu(\mc{C}_{\sigma + \delta}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
+	\end{equation}
+\end{lemma}
+To prove Lemma~\ref{lem:external_isoperimetric_inequality} for a general bounded set $\mc{C}$, we first construct a particular covering of $\mc{C}_{\sigma + \delta}$, then apply~\eqref{eqn:external_isoperimetric_inequality_1} to each set in the covering.
+
+For $\delta \leq \sigma/d$ we have that $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:external_isoperimetric_inequality} that
+\begin{equation}
+\label{eqn:external_isoperimetric_inequality_2}
+\nu(\mc{C}_{\sigma + \delta} \setminus \mc{C}_{\sigma}) = \nu(\mc{C}_{\sigma + \delta}) - \nu(\mc{C}_{\sigma}) \leq d \cdot \frac{\delta}{\sigma - d\delta} \cdot \nu(\mc{C}_{\sigma}).
+\end{equation}
+We use~\eqref{eqn:external_isoperimetric_inequality_2} along with Assumption~\ref{asmp:low_noise_density} to derive a density-weighted isoperimetric inequality. 
+\begin{lemma}
+	\label{lem:external_isoperimetric_inequality_density_weighted}
+	Let $\mc{C}_{\lambda,\sigma}$ satisfy Assumption~\ref{asmp:bounded_density} and~\ref{asmp:low_noise_density} for some $\theta, \gamma$ and $\lambda_{\sigma}$.
+Then for any $0 < r \leq \sigma/d$, it holds that
+	\begin{equation}
+	\label{eqn:external_isoperimetric_inequality_density_weighted}
+	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}).
+	\end{equation}
+\end{lemma}
+
+Before we prove Lemma~\ref{lem:external_isoperimetric_inequality}, we observe that in the special case where $\mc{C}$ is a single point---say $\mc{C} = \{0\}$--- the inequality~\eqref{eqn:external_isoperimetric_inequality} holds with equality.
+In this case $\mc{C}_{\sigma + \delta} = B(0,\sigma + \delta)$ and $\mc{C}_{\sigma} = B(0,\sigma)$, and
+\begin{equation}
+\label{eqn:external_isoperimetric_inequality_1}
+\nu(\mc{C}_{\sigma + \delta}) = \nu_d (\sigma + \delta)^d = \nu_d \sigma^d \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d = \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
+\end{equation}
+\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality})] 
+	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
+	\begin{equation*}
+	\label{pf:external_isoperimetric_inequality}
+	\nu(\mc{C}_{\sigma + \epsilon}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d,
+	\end{equation*}
+	whence taking a limit as $\delta' \to 0$ yields the claim.
+
+	To show~\eqref{pf:external_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$.
+To do so, we first take a finite set of points $x_1,\ldots,x_N$ such that the net $B(x_1,\sigma + \epsilon),\ldots,B(x_N,\sigma + \epsilon)$ covers $\mc{C}_{\sigma + \delta}$.
+Note that such a covering exists for some finite $N = N(\epsilon)$ because $\mc{C}_{\sigma + \delta}$ is bounded, and the closure of $\mc{C}_{\sigma + \delta}$ is thus a compact subset of $\cup_{x \in \mc{C}} B(x,\sigma + \epsilon)$.
+Defining $\mc{A}_1(s), \ldots, \mc{A}_N(s)$ for a given $s > 0$ to be
+	\begin{equation*}
+	\mc{A}_1(s) := B(x_1,s),~~\textrm{and}~~ \mc{A}_{j + 1}(s) := B(x_{j + 1},s) \setminus \bigcup_{i = 1}^{j} B(x_i,s) ~~\textrm{for $j = 1,\ldots,N - 1$},
+	\end{equation*}
+	we have that $\mc{A}_1(\sigma + \epsilon),\ldots,\mc{A}_N(\sigma + \epsilon)$ is a disjoint covering of $\mc{C}_{\sigma + \delta}$, and so $\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon))$.
+
+	We claim that for all $j = 1,\ldots,N$, the function $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing in $s$.
+Once this claim is verified, it follows that
+	\begin{equation*}
+	\nu(\mc{A}_j(\sigma + \epsilon)) = \nu\bigl(B(x_j,\sigma + \epsilon)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)}{\nu\bigl(B(x_j,\sigma + \epsilon)\bigr)} \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot  \nu\bigl(B(x_j,\sigma)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma)\bigr)}{\nu\bigl(B(x_j,\sigma)\bigr)} = \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \nu\bigl(\mc{A}_j(\sigma)
+	\end{equation*}
+	and summing over $j$, we see that
+	\begin{equation*}
+	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon)) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma}
+	\end{equation*}
+	with the last inequality following since $\mc{A}_1(\sigma),\ldots,\mc{A}_N(\sigma)$ are disjoint subsets of $\mc{C}_{\sigma}$.
+
+	It remains to verify that $x \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing.
+For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
+Thus $(s/t)x \in B(0,s)$, and
+	\begin{equation*}
+	\|(s/t)x - (x_i - x_j)\| \geq \|x - (x_i - x_j)\| - \|x - (s/t)x\| > t - (1 - s/t)\|x\| \geq t - (1 - s/t)t = s,
+	\end{equation*}
+	or in other words $(s/t)x \not\in B(x_i - x_j,s)$ for any $i = 1,\ldots,j - 1$. Consequently,
+	\begin{equation*}
+	\Bigl(\mc{A}_j(t) - \{x_j\}\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- \{x_j\}\Bigr),
+	\end{equation*}
+	and applying $\nu(\cdot)$ to both sides yields the claim.
+\end{proof}
+
+\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality_density_weighted})]
+	Fix $k \in \mathbb{N}$.
+To establish~\eqref{eqn:external_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:external_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
+	\begin{equation*}
+	\nu(\mc{T}_j) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + (j - 1)r/k}) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + r}) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr/k}{\sigma - dr/k}  \cdot \nu(\mc{C}_{\lambda,\sigma}),
+	\end{equation*}
+	and the maximum density within each tube using~\ref{asmp:low_noise_density}:
+	\begin{equation*}
+	\max_{x \in \mc{T}_j} f(x) \leq \lambda_{\sigma} - \theta \Bigl(\frac{j - 1}{k}r\Bigr)^{\gamma};
+	\end{equation*}
+	combining these upper bounds, we see that
+	\begin{equation}
+	\label{pf:external_isoperimetric_inequality_density_weighted_1}
+	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) = \sum_{j = 1}^{k} \Pbb(\mc{T}_j) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot  \frac{dr/k}{\sigma - dr/k} \cdot \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma} \biggr).
+	\end{equation}
+	Treating the sum in the previous expression as a Riemann sum of a non-increasing function evaluated at $0,\ldots,k -1$ gives the upper bound
+	\begin{equation*}
+	\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma } \leq \lambda_{\sigma} + \int_{0}^{k - 1} \Bigl(\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{x}{k}\Bigr)^{\gamma}\Bigr) \,dx \leq k\lambda_{\sigma} + (k - 1)\frac{\theta r^{\gamma}}{\gamma + 1} \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma},
+	\end{equation*}
+	and plugging back in to~\eqref{pf:external_isoperimetric_inequality_density_weighted_1}, we obtain
+	\begin{equation*}
+	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq  \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\lambda - \frac{\theta r^{\gamma}}{\gamma + 1} \cdot \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma + 1} \biggl).
+	\end{equation*}
+	The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim.
+\end{proof}
+
+\subsection{Proof of Lemma~\ref{lem:density_cluster_local_spread}}
+\label{subsec:density_cluster_local_spread}
+The population-level local spread of $\mc{C}_{\lambda,\sigma}$ is
+\begin{equation*}
+s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \frac{\bigl(d_{\min}(\wt{\Pbb})\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)}
+\end{equation*}
+where we recall that $\wt{\Pbb}(\mc{S}) = \frac{\Pbb(\mc{S} \cap \mc{C}_{\lambda,\sigma})}{\Pbb(\mc{C}_{\lambda,\sigma})}$ for Borel sets $\mc{S}$, and $d_{\min}(\wt{\Pbb}) := \min_{x \in \mc{C}_{\lambda,\sigma}}\{\deg_{\wt{\Pbb},r}(x)\}^2$.
+To lower bound $s_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, we first lower bound $d_{\min}(\wt{\Pbb})$, and then upper bound $\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)$.
+Using the lower bound $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$ stipulated in~\ref{asmp:lambda_bounded_density}, we deduce that
+\begin{align*}
+d_{\min}(\wt{\Pbb}) & = \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int \1\{\|x - y\| \leq r\} \,d\wt{\Pbb}(y) \Bigr\} \\
+& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \min_{x \in \mc{C}_{\lambda,\sigma}} \Bigl\{ \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\| \leq r\} \,dy \Bigr\} \\
+& \geq \frac{\lambda_{\sigma}}{\Pbb(\mc{C}_{\lambda,\sigma})} \cdot \frac{1}{2}\nu_dr^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr),
+\end{align*}
+where the final inequality follows from Lemma~\ref{lem:overlap_balls}.
+
+On the other hand, using the upper bound $f(x) \leq \Lambda_{\sigma}$ for all $x \in \mc{C}_{\lambda,\sigma}$, we deduce that
+\begin{align*}
+\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\|\leq r\} \,d\wt{\Pbb}(y) \,d\wt{\Pbb}(x) \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \int_{\mc{C}_{\lambda,\sigma}} \int_{\mc{C}_{\lambda,\sigma}} \1\{\|x - y\|\leq r\} \,dy \,dx \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d r^d \cdot \nu(\mc{C}_{\lambda,\sigma}) \\
+& \leq \frac{\Lambda_{\sigma}^2}{\Pbb(\mc{C}_{\lambda,\sigma})^2} \cdot \nu_d^2 r^d  \cdot \Bigl(\frac{\rho}{2}\Bigr)^d;
+\end{align*}
+the final inequality follows from~\ref{asmp:embedding}, which implies that $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
+The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
+
+\subsection{Proof of Proposition~\ref{prop:density_cluster_normalized_cut}}
+\label{subsec:density_cluster_ncut}
+By Assumption~\ref{asmp:bounded_volume}, we have that $\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})/\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$, and to prove Proposition~\ref{prop:density_cluster_normalized_cut} we must therefore upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ and lower bound $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
+
+Let $\mc{C}_{\lambda,\sigma + r} = \{x: \mathrm{dist}(x,\mc{C}_{\lambda}) \leq \sigma + r\}$.
+We upper bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the probability mass of $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$:
+\begin{align*}
+\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \not\in \mc{C}_{\lambda,\sigma} \} \,d\Pbb(y) \,d\Pbb(x) \\
+& \leq  \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \cdot \1\{y \in \mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}  \} \,d\Pbb(y) \,d\Pbb(x) \\
+& \leq \lambda \nu_d r^d \cdot \Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr).
+\end{align*}
+On the other hand, using the lower bound $f(x) \geq \lambda_{\sigma} $ for all $x \in \mc{C}_{\lambda,\sigma}$, we lower bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the Lebesgue measure of $\mc{C}_{\lambda,\sigma}$:
+\begin{align*}
+\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) & = \iint \1\{\|x - y\| \leq r \} \cdot \1\{x \in \mc{C}_{\lambda,\sigma}\} \,d\Pbb(y) \,d\Pbb(x) \\
+& \geq \lambda_{\sigma}^2 \cdot \iint \1\{\|x - y\| \leq r \} \cdot \1\{x,y \in \mc{C}_{\lambda,\sigma}\} \,dy \,dy \\
+& \geq \lambda_{\sigma}^2 \cdot \frac{1}{2} \nu_d r^d \cdot \Bigl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\Bigr) \cdot \nu(\mc{C}_{\lambda,\sigma}).
+\end{align*}
+The claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows upon using Lemma~\ref{lem:external_isoperimetric_inequality_density_weighted} to upper bound $\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr)$.
+
+\subsection{Proof of Proposition~\ref{prop:density_cluster_conductance}}
+\label{subsec:density_cluster_conductance}
+\textcolor{red}{(TODO)}
 

### 2021-01-15 jmlr/revision/proofs.tex
Completed bounds on population functionals of density clusters.

@@
 In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
-In these proofs, we make use of some estimates on the volume of spherical caps, and we detail these in Section~\ref{subsec:spherical caps}; we also use some isoperimetric inequalities, which we detail in Section~\ref{subsec:isoperimetric_inequalities}.
+In these proofs, we make use of some estimates on the volume of spherical caps (given in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (given in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
 Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
@@
 \subsection{Balls, Spherical Caps, and Associated Estimates}
-\label{subsec:spherical caps}
+\label{subsec:spherical_caps}
 In this section, we derive lower bounds on the volume of the intersection between two balls in $\Rd$, and the volume of a spherical cap.
@@
 
-\subsection{\textcolor{red}{Isoperimetric inequalities}}
+\subsection{Isoperimetric inequalities}
 \label{subsec:isoperimetric_inequalities}
+\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
+\begin{lemma}[Isoperimetry of a convex set.]
+	\label{lem:convex_isoperimetric_inequality}
+	For any partition $(\mc{R}_1,\mc{R}_2,\mc{R}_3)$ of a convex set $\mc{K} \subseteq \Rd$, it holds that
+	\begin{equation*}
+	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
+	\end{equation*}
+\end{lemma}
+\citet{abbasi-yadkori2016a} points out that if $\mc{S}$ is the image of a convex set under a Lipschitz measure-preserving mapping $g: \Rd \to \Rd$, a similar inequality can be obtained.
+\begin{corollary}[Isoperimetry of Lipschitz embeddings of convex sets.]
+	\label{cor:nonconvex_isoperimetric_inequality}
+	Suppose $\mc{S}$ is the image of a convex set $\mathcal{K}$ under a mapping $g:\Rd \to \Rd$ such that
+	\begin{equation*}
+	\|g(x) - g(y)\| \leq L \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
+	\end{equation*}
+	Then for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{S}$, 
+	\begin{equation*}
+	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) L} \min(\nu(\Omega_1), \nu(\Omega_2)).
+	\end{equation*}
+\end{corollary}
+
+\subsection{Reverse isoperimetric inequalities}
+\label{subsec:reverse_isoperimetric_inequalities}
 
@@
 \begin{lemma}
-	\label{lem:external_isoperimetric_inequality}
+	\label{lem:reverse_isoperimetric_inequality}
 	For any bounded set $\mc{C} \subseteq \Rd$ and  $\sigma, \delta > 0$, it holds that
 	\begin{equation}
-	\label{eqn:external_isoperimetric_inequality}
+	\label{eqn:reverse_isoperimetric_inequality}
 	\nu(\mc{C}_{\sigma + \delta}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
@@
 \end{lemma}
-To prove Lemma~\ref{lem:external_isoperimetric_inequality} for a general bounded set $\mc{C}$, we first construct a particular covering of $\mc{C}_{\sigma + \delta}$, then apply~\eqref{eqn:external_isoperimetric_inequality_1} to each set in the covering.
-
-For $\delta \leq \sigma/d$ we have that $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:external_isoperimetric_inequality} that
-\begin{equation}
-\label{eqn:external_isoperimetric_inequality_2}
-\nu(\mc{C}_{\sigma + \delta} \setminus \mc{C}_{\sigma}) = \nu(\mc{C}_{\sigma + \delta}) - \nu(\mc{C}_{\sigma}) \leq d \cdot \frac{\delta}{\sigma - d\delta} \cdot \nu(\mc{C}_{\sigma}).
-\end{equation}
-We use~\eqref{eqn:external_isoperimetric_inequality_2} along with Assumption~\ref{asmp:low_noise_density} to derive a density-weighted isoperimetric inequality. 
+Lemma~\ref{lem:reverse_isoperimetric_inequality} should be interpreted as a reverse isoperimetric inequality.
+To see this, note that if $\delta \leq \sigma/d$ then $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:reverse_isoperimetric_inequality} that
+\begin{equation}
+\label{eqn:reverse_isoperimetric_inequality_2}
+\nu(\mc{C}_{\sigma + \delta} \setminus \mc{C}_{\sigma}) = \nu(\mc{C}_{\sigma + \delta}) - \nu(\mc{C}_{\delta}) \leq \frac{d\delta}{\sigma - d\delta} \cdot \nu(\mc{C}_{\sigma}).
+\end{equation}
+We use~\eqref{eqn:reverse_isoperimetric_inequality_2} along with Assumption~\ref{asmp:low_noise_density} to derive a density-weighted reverse isoperimetric inequality. 
 \begin{lemma}
-	\label{lem:external_isoperimetric_inequality_density_weighted}
+	\label{lem:reverse_isoperimetric_inequality_density_weighted}
 	Let $\mc{C}_{\lambda,\sigma}$ satisfy Assumption~\ref{asmp:bounded_density} and~\ref{asmp:low_noise_density} for some $\theta, \gamma$ and $\lambda_{\sigma}$.
@@
 	\begin{equation}
-	\label{eqn:external_isoperimetric_inequality_density_weighted}
+	\label{eqn:reverse_isoperimetric_inequality_density_weighted}
 	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}).
@@
 \end{lemma}
-
-Before we prove Lemma~\ref{lem:external_isoperimetric_inequality}, we observe that in the special case where $\mc{C}$ is a single point---say $\mc{C} = \{0\}$--- the inequality~\eqref{eqn:external_isoperimetric_inequality} holds with equality.
-In this case $\mc{C}_{\sigma + \delta} = B(0,\sigma + \delta)$ and $\mc{C}_{\sigma} = B(0,\sigma)$, and
-\begin{equation}
-\label{eqn:external_isoperimetric_inequality_1}
-\nu(\mc{C}_{\sigma + \delta}) = \nu_d (\sigma + \delta)^d = \nu_d \sigma^d \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d = \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
-\end{equation}
-\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality})] 
+\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality})] 
 	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
 	\begin{equation*}
-	\label{pf:external_isoperimetric_inequality}
+	\label{pf:reverse_isoperimetric_inequality}
 	\nu(\mc{C}_{\sigma + \epsilon}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d,
@@
 
-	To show~\eqref{pf:external_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$.
+	To show~\eqref{pf:reverse_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$.
 To do so, we first take a finite set of points $x_1,\ldots,x_N$ such that the net $B(x_1,\sigma + \epsilon),\ldots,B(x_N,\sigma + \epsilon)$ covers $\mc{C}_{\sigma + \delta}$.
@@
 	\begin{equation*}
-	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon)) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma}
+	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma},
 	\end{equation*}
@@
 
-\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality_density_weighted})]
+\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted})]
 	Fix $k \in \mathbb{N}$.
-To establish~\eqref{eqn:external_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:external_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
+To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
 	\begin{equation*}
@@
 	\begin{equation}
-	\label{pf:external_isoperimetric_inequality_density_weighted_1}
+	\label{pf:reverse_isoperimetric_inequality_density_weighted_1}
 	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) = \sum_{j = 1}^{k} \Pbb(\mc{T}_j) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot  \frac{dr/k}{\sigma - dr/k} \cdot \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma} \biggr).
@@
 	\end{equation*}
-	and plugging back in to~\eqref{pf:external_isoperimetric_inequality_density_weighted_1}, we obtain
+	and plugging back in to~\eqref{pf:reverse_isoperimetric_inequality_density_weighted_1}, we obtain
 	\begin{equation*}
@@
 \end{align*}
-The claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows upon using Lemma~\ref{lem:external_isoperimetric_inequality_density_weighted} to upper bound $\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr)$.
+The claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows upon using Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted} to upper bound $\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr)$.
 
@@
 \label{subsec:density_cluster_conductance}
-\textcolor{red}{(TODO)}
+The following Lemma upper bounds the population-level uniform conductance $\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma})$. 
+\begin{lemma}
+	\label{lem:uniform_density_cluster_conductance}
+	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho > 0$ and $L \geq 1$. For any $0 < r \leq \sigma \sqrt{2\pi/(d + 2)}$, it holds that
+	\begin{equation}
+	\label{eqn:uniform_density_cluster_conductance}
+	\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}.
+	\end{equation}
+\end{lemma}
+Noting that $\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \cdot \lambda_{\sigma}^2/\Lambda_{\sigma}^2$, Proposition~\ref{prop:density_cluster_conductance} follows from~\eqref{eqn:uniform_density_cluster_conductance}.
+
+\begin{proof}[Proof (of Lemma~\ref{lem:uniform_density_cluster_conductance})]
+	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.
+
+	Let $\mc{S}$ be an arbitrary measurable subset of $\mc{C}_{\lambda,\sigma}$, and let $\mc{R} = \mc{C}_{\lambda,\sigma} \setminus \mc{S}$.
+For a given $\delta \in (0,1)$, let the $\delta$-interior of $\mc{S}$ be
+	\begin{equation*}
+	\mc{S}^{\delta} := \{x \in \mc{S}: \nu\bigl(B(x,r) \cap \mc{R}\bigr) \leq \ell \delta \nu_d r^d\};
+	\end{equation*}
+	define $\mc{R}^{\delta}$ likewise, and let $\mc{B}^{\delta} = \mc{C}_{\lambda,\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$ consist of the remaining boundary points.
+	As is standard (see for example~\cite{dyer1991,lovasz1990}), the proof of Lemma~\ref{lem:uniform_density_cluster_conductance} uses several inequalities to lower bound the normalized cut $\Phi_{\wt{\nu},r}(\mc{S})$.
+	\begin{itemize}
+		\item \textbf{Bounds on cut and volume.}
+		We can lower bound $\cut_{\wt{\nu},r}(\mc{S})$ as follows:
+		\begin{align*}
+		\nu(\mc{C}_{\lambda,\sigma})^2 \cdot \cut_{\wt{\nu},r}(\mc{S}) & = \int_{\mc{S}} \int_{\mc{R}} \1(\|x - y\| \leq r) \,dy \,dx \\
+		& = \frac{1}{2}\Bigl(\int_{\mc{S}} \int_{\mc{R}} \1(\|x - y\| \leq r) \,dy \,dx + \int_{\mc{R}} \int_{\mc{S}} \1(\|x - y\| \leq r) \,dy \,dx\Bigr) \\
+		& \geq \frac{1}{2} \delta \ell \nu_d r^d \cdot \nu(\mc{B}^{\delta}).
+		\end{align*}
+		We can upper bound $\vol_{\wt{\nu},r}(\mc{S})$ as follows:
+		\begin{equation*}
+		\nu(\mc{C}_{\lambda,\sigma})^2 \cdot \vol_{\wt{\nu},r}(\mc{S}) = \int_{\mc{C}_{\lambda,\sigma}} \int_{\mc{S}} \1(\|x - y\| \leq r) \,dy \,dx \leq \nu_d r^d \nu(\mc{S})
+		\end{equation*}
+		and likewise for $\vol_{\wt{\nu},r}(\mc{S})$. Therefore,
+		\begin{equation}
+		\label{pf:uniform_density_cluster_conductance_1}
+		\Phi_{\wt{\nu},r}(\mc{S}) \geq \frac{\delta \ell \cdot \nu(\mc{B}^{\delta})}{2 \cdot \min\{\nu(\mc{S}), \nu(\mc{R})\}}.
+		\end{equation}
+		\item \textbf{Isoperimetric inequality.}
+		Applying Corollary~\ref{cor:nonconvex_isoperimetric_inequality}, we have that
+		\begin{equation}
+		\label{pf:uniform_density_cluster_conductance_2}
+		\nu(\mc{B}^{\delta}) \geq \frac{2 \cdot \mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \cdot \min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\}.
+		\end{equation}
+		\item \textbf{Volume of $\delta$-interiors.} Suppose $\nu(\mc{S}^{\delta}) \leq (1 - a) \cdot \nu(\mc{S})$ or $\nu(\mc{R}^{\delta}) \leq (1 - a) \cdot \nu(\mc{R})$. Then 
+		$\nu(\mc{B}^{\delta}) \geq a \cdot \min\{\nu(\mc{S}), \nu(\mc{R})\}$, and combined with~\eqref{pf:uniform_density_cluster_conductance_1} we have that $\Phi_{\wt{\nu},r}(\mc{S}) \geq \delta a \ell/2$.
+Otherwise,
+		\begin{equation}
+		\label{pf:uniform_density_cluster_conductance_3}
+		\min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\} \geq (1- a) \cdot \min\bigl\{\nu(\mc{S}),\nu(\mc{R})\bigr\}.
+		\end{equation}
+		\item \textbf{Distance between $\delta$-interiors.} For any $x \in \mc{S}^{\delta}$ and $y \in \mc{R}^{\delta}$, we have that 
+		\begin{align*}
+		\nu\bigl(B(x,r) \cap B(y,r)\bigr) & = \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{R}\bigr) + \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{S}\bigr) + \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{C}_{\lambda,\sigma}^c\bigr) \\
+		& \leq \nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr) + \nu\bigl(B(x,r) \cap \mc{C}_{\lambda,\sigma}^c\bigr) \\
+		& \leq \bigl(2\ell\delta + (1 - \ell)\bigr) \cdot \nu_dr^d.
+		\end{align*}
+		It follows from~\eqref{eqn:overlap_balls_1} that
+		\begin{equation*}
+		\|x - y\| \geq \frac{r}{\nu_d r^d} \cdot \Bigl(\nu_d r^d - \nu\bigl(B(x,r) \cap B(y,r)\bigr)\Bigr) \cdot \sqrt{\frac{2\pi}{d + 2}} \geq r \cdot \ell \cdot (1 - 2\delta) \cdot \sqrt{\frac{2\pi}{d + 2}},
+		\end{equation*}
+		and taking the infimum over all $x \in \mc{S}^{\delta}$ and $y \in \mc{R}^{\delta}$, we have
+		\begin{equation}
+		\label{pf:uniform_density_cluster_conductance_4}
+		\mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta}) \geq r \cdot \ell \cdot (1 - 2\delta) \cdot \sqrt{\frac{2\pi}{d + 2}}.
+		\end{equation}
+	\end{itemize}	
+	Combining~\eqref{pf:uniform_density_cluster_conductance_1}-\eqref{pf:uniform_density_cluster_conductance_4} and taking $\delta = 1/3$ implies that
+	\begin{equation*}
+	\Phi_{\wt{\nu},r}(\mc{S}) \geq \min\biggl\{(1 - a) \cdot \frac{r}{\rho L} \cdot \frac{\ell^2}{9} \cdot \sqrt{\frac{2\pi}{d + 2}}, \frac{a\ell}{6}\biggr\}
+	\end{equation*}
+	and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$.
+\end{proof}
 
@@
 \label{sec:pf_major_theorems}
+In this section, we prove Theorem~\ref{thm:volume_ssd_ub} (in Section), Corollary~\ref{cor:density_cluster_volume_ssd_ub}, and Theorem~\ref{thm:ppr_lb}.
+
+\subsection{Proof of Theorem~\ref{thm:volume_ssd_ub}}
+
+\subsection{Proof of Corollary~\ref{cor:density_cluster_volume_ssd_ub}}
+
+\subsection{Proof of Theorem~\ref{thm:ppr_lb}}
 

### 2021-01-20 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Completed revised proof of lower bound.

@@
 
-	\item Although Theroem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
+	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
 	application of \eqref{eqn: appr_error} within the proof of Theorem
@@
 \paragraph{Lower bound on symmetric set difference.}
-
 As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
@@
 \end{equation}
-
+In what follows, we put
+\begin{align*}
+C_{3,\delta} & := 768 \cdot (1 + 3\delta),&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
+C_{5,\delta} & := \frac{(1 + \delta)^2}{(1 - \delta)^2},&&C_{6,\delta} := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}.
+\end{align*}
 \begin{theorem}
 	\label{thm:ppr_lb}
-	Assume the radius $r < \min\set{\frac{1}{40}\rho, \frac{1}{4}\sigma}$, and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 65  
-	\Phi_{\Pbb,r}(\mathcal{L})$, and $(L,U) = (0,1)$.  Then, for any 
-	\begin{equation*}
-	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2},
-		\frac{8}{\epsilon}}, 
-	\end{equation*}
-	the following statement holds with probability at least $1 - B_3 n \exp\set{-b_3 n}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap 
-		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/10$}, such
+	Fix $\delta \in (0,1/7)$. Assume the neighborhood graph radius $r < \sigma/2$, that
+	\begin{equation}
+	\label{eqn:ppr_lb_condition}
+	\max\biggl\{C_{3,\delta} \cdot \frac{r}{\rho} \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr), \frac{C_{5,\delta}}{n} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq \frac{6 \sigma \rho (1 + \delta)}{(\sigma - 2r)(\rho - r) (1 - \delta)},
+	\end{equation} 
+	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot   
+	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.
+Then the following statement holds with probability at least $1 - B_3 \exp\set{- \delta^2 b_4 n/(3 + \delta)} - n \exp\{-\delta^2 b_5 n/(3 + \delta)\}$: there exists a set $\mc{C}[X]^g$ of large volume, \\ \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
+		\mc{C}^{(1)}[X]) \geq 6\vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/49$}, such
 	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
@@
 	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
-	\mc{C}^{(1)}[X]) \geq \frac{1}{4} -  C_4 \cdot 
-	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(\frac{\rho \sigma}
+	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{6,\delta} \cdot 
+	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}
 		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
 	\end{equation} 
-	Consequently, if
-	\begin{equation*}
-	\epsilon^2 \geq \frac{C_4}{8} \cdot \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ 
-		\log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}, 
-	\end{equation*}
-	then with high probability \smash{$\frac{\sigma
-			\rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) 
-		\geq 1/8$}.    
 \end{theorem}
 
-\textcolor{red}{(TODO): Either (preferably) replace $C_4$ by a number, or otherwise say that it is a universal constant.}
+\textcolor{red}{(TODO): Check that the assumptions of the Theorem match those used in the proof.}
 

### 2021-01-20 jmlr/revision/proofs.tex
Completed revised proof of lower bound.

@@
 
-The proofs of our major theorems all consist of at most three modular parts.
+The proofs of our major theorems largely consist of (at most) three modular parts.
 \begin{enumerate}
-	\item~\textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
-	\item~\textbf{Finite-sample bounds.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
-	\item~\textbf{Population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}.
+	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
+	\item \textbf{Finite-sample bounds.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
+	\item \textbf{Population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}.
 This proves~\textcolor{red}{(?)}
@@
 \end{equation}
-Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-2(1 - \delta)\delta^2d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n\}$,
+Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-2(1 - \delta)\delta^2d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n\}$,
 \begin{equation}
@@
 with probability at least $1 - 2\exp\bigl\{-\delta^2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})n\bigr\} - n\exp\bigl\{-\delta^2\bigl(d_{\min}(\wt{\Pbb})\bigr)^2 \Pbb(\mc{C}) n\bigr\}$.
-This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 = \bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})$, $b_3 = \bigl(d_{\min}(\wt{\Pbb})\bigr)^2 \Pbb(\mc{C})$, and $C_2 = 3$.
+This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 = \bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})$ and $b_3 = d_{\min}(\wt{\Pbb}) \Pbb(\mc{C})$
 
@@
 so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$.
-Next, as we have already derived in~\eqref{pf:sample_to_population_local_spread_2}, with probability at least $1 - \exp\{-\mbb{P}(\mc{C})^2n\} - \exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$,
+Next, as we have already derived in~\eqref{pf:sample_to_population_local_spread_2}, with probability at least $1 - \exp\{-\mbb{P}(\mc{C})n\} - \exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$,
 \begin{equation*}
@@
 \end{equation*}
-with probability at least $1 - B_2/n - (n + 2)\exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$, establishing~\eqref{eqn:sample_to_population_conductance}.
+with probability at least $1 - B_2/n - (n + 2)\exp\{-d_{\min}(\wt{\Pbb})\cdot \Pbb(\mc{C}) n/\sqrt{2}\}$, establishing~\eqref{eqn:sample_to_population_conductance}.
 
@@
 In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
-In these proofs, we make use of some estimates on the volume of spherical caps (given in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (given in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
+In these proofs, we make use of some estimates on the volume of spherical caps (in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
+Finally, in Section~\ref{subsec:density_cluster_hard_case}, for the hard case distribution $\Pbb$ defined in~\eqref{eqn:lb_density} and $\mc{L}$ defined in~\eqref{eqn:lower_set}, establish bounds on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{L})$ and local spread $s_{\Pbb,r}(\mc{X})$; these will be useful in the proof of Theorem~\ref{thm:ppr_lb}.
 Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
@@
 	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
-	\begin{equation*}
+	\begin{equation}
 	\label{pf:reverse_isoperimetric_inequality}
 	\nu(\mc{C}_{\sigma + \epsilon}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d,
-	\end{equation*}
+	\end{equation}
 	whence taking a limit as $\delta' \to 0$ yields the claim.
 
-	To show~\eqref{pf:reverse_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$.
+	To show~\eqref{pf:reverse_isoperimetric_inequality}, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$.
 To do so, we first take a finite set of points $x_1,\ldots,x_N$ such that the net $B(x_1,\sigma + \epsilon),\ldots,B(x_N,\sigma + \epsilon)$ covers $\mc{C}_{\sigma + \delta}$.
@@
 	\end{equation*}
-	we have that $\mc{A}_1(\sigma + \epsilon),\ldots,\mc{A}_N(\sigma + \epsilon)$ is a disjoint covering of $\mc{C}_{\sigma + \delta}$, and so $\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon))$.
+	we have that $\mc{A}_1(\sigma + \epsilon),\ldots,\mc{A}_N(\sigma + \epsilon)$ is a disjoint covering of $\mc{C}_{\sigma + \delta}$, and so $\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)$.
 
@@
 \label{subsec:density_cluster_conductance}
-The following Lemma upper bounds the population-level uniform conductance $\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma})$. 
+The following Lemma lower bounds the population-level uniform conductance $\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma})$.
 \begin{lemma}
 	\label{lem:uniform_density_cluster_conductance}
-	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho > 0$ and $L \geq 1$. For any $0 < r \leq \sigma \sqrt{2\pi/(d + 2)}$, it holds that
+	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho \in (0,\infty)$ and $L \in [1,\infty)$.
+For any $0 < r \leq \sigma \cdot \sqrt{2\pi/(d + 2)}$, it holds that
 	\begin{equation}
@@
 
+\subsection{Population functionals, hard case}
+\label{subsec:density_cluster_hard_case}
+Let $\Pbb$ be the hard case distribution over rectangular domain $\mc{X}$, defined as in~\eqref{eqn:lb_density}, and $\mc{L}$ the lower half of $\mc{X}$.
+Suppose $r \in (0,\sigma/2)$.
+Then the population normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ is lower bounded,
+\begin{equation}
+\label{eqn:ncut_lower_set}
+\Phi_{\Pbb,r}(\mc{L}) \leq \frac{8}{3} \cdot \frac{r}{\rho}.
+\end{equation}
+and the population local spread $s_{\Pbb,r}(\mc{X})$ is upper bounded,
+\begin{equation}
+\label{eqn:local_spread_ub}
+s_{\Pbb,r}(\mc{X}) \geq \frac{\pi r^2 \epsilon^2}{2 \rho\sigma}
+\end{equation}
+
+\begin{proof}[Proof of~\eqref{eqn:ncut_lower_set}.]
+	Noting that $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, it suffices to upper bound $\cut_{\Pbb,r}(\mathcal{L})$ and lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
+Note that for any $x = (x_1,x_2) \in \mathcal{L}$, if $x_2 \leq -r$ the ball $B(x,r)$ and the set $\mathcal{X}\setminus\mathcal{L}$ are disjoint.
+As a result,
+	\begin{equation*}
+	\cut_{\Pbb,r}(\mathcal{L}) \leq \Pbb\Bigl(\bigl\{x \in \mathcal{X}: x_2 \in (-r,0)\bigr\}\Bigr) \cdot d_{\max}(\Pbb) \leq \frac{r}{2 \rho} \cdot \frac{\pi r^2}{2 \sigma \rho}.
+	\end{equation*}
+	On the other hand, noting that $\deg_{\Pbb,r}(x) \geq \frac{\pi r^2}{2 \sigma \rho}$ for all $x \in \mc{C}^{(1)}$ such that $\mathrm{dist}(x, \partial \mc{C}^{(1)}) > r$, we have
+	\begin{align*}
+	\vol_{\Pbb,r}(\mathcal{L}) & \geq \Pbb\Bigl(\bigl\{x \in \mc{C}^{(1)} \cap \mathcal{L}: \mathrm{dist}(x, \partial \mc{C}^{(1)}) > r\bigr\}\Bigr) \cdot \frac{\pi r^2}{2 \sigma \rho} \\
+	& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\pi r^2}{2 \sigma \rho}  \\
+	& \geq \frac{3}{16} \cdot \frac{\pi r^2}{2 \sigma \rho}
+	\end{align*}
+	where the last inequality follows since $r \leq \frac{1}{4}\sigma < \frac{1}{4}\rho$. 
+\end{proof}
+
+\begin{proof}[Proof of~\eqref{eqn:local_spread_ub}.]
+	\textcolor{red}{(TODO)}
+\end{proof}
+
 \section{Proof of Major Theorems}
@@
 \subsection{Proof of Theorem~\ref{thm:ppr_lb}}
+To prove Theorem~\ref{thm:ppr_lb}, we use Theorem~\ref{thm:normalized_cut_ppr}, Proposition~\ref{prop:sample_to_population_1} and~\eqref{eqn:ncut_lower_set} to show that the cluster estimate $\wh{C}$ must have a small normalized cut.
+On the other hand, in Lemma~\ref{lem:normalized_cut_lb} we establish that any set $Z \subseteq X$ which is close to $\mc{C}^{(1)}[X]$---meaning $\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])$ is small---has a large normalized cut.
+\begin{lemma}
+	\label{lem:normalized_cut_lb}
+	With probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$, the following statement holds:
+	\begin{equation*}
+	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
+	\end{equation*}
+	for all $Z \subseteq X$.
+\end{lemma}
+We therefore conclude that $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ must be large. Now, we give a formal proof Theorem~\ref{thm:ppr_lb}, and then of Lemma~\ref{lem:normalized_cut_lb}.
+\begin{proof}[Proof (of Theorem~\ref{thm:ppr_lb})]
+	As mentioned, we would like to use Theorem~\ref{thm:normalized_cut_ppr} to upper bound $\Phi_{n,r}(\wh{C})$, and so we first verify that the conditions of Theorem~\ref{thm:normalized_cut_ppr} are met.
+In particular, we have each of the following.
+	\begin{itemize}
+		\item Recalling that $n \geq \frac{6 \sigma \rho (1 + \delta)}{(\sigma - 2r)(\rho - r) (1 - \delta)}$ and that $\vol_{\Pbb,r}(\mc{L}) \geq \frac{(\sigma - 2r)(\rho - r)}{2\sigma \rho}$, it follows from Lemmas~\ref{lem:bernstein_union} and~\ref{lem:hoeffding_2} that with probability at least $1 - n\exp\{\delta^2 d_{\min}(\Pbb) /(3 + \delta)\} - \exp\{-\delta^2 \vol_{\Pbb,r}(\mc{L})^2 n\}$,
+		\begin{equation}
+		\label{pf:ppr_lb_1}
+		d_{\max}(G_{n,r}) \leq n \cdot (1 + \delta) d_{\max}(\Pbb) \leq \frac{1}{3}n^2 (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \leq \frac{1}{3}\vol_{n,r}(\mc{L}[X]).
+		\end{equation}
+		Therefore the lower bound in condition~\eqref{eqn:normalized_cut_ppr_vol} is satisfied.
+		\item Noting that $\delta \in (0,1/7)$ implies $\frac{(1 - \delta)}{(1 + \delta)} > \frac{3}{4}$, it follows from Lemma~\ref{lem:hoeffding_2} that with probability at least $1 - 2\exp\{-\delta^2 \vol_{\Pbb,r}(\mc{L})^2 n\}$,
+		\begin{equation}
+		\label{pf:ppr_lb_2}
+		\vol_{n,r}(X) \geq n^2(1 - \delta) \vol_{\Pbb,r}(\mc{X}) \geq 2n^2 (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \geq 2\frac{(1 - \delta)}{(1 + \delta)} \vol_{n,r}(\mc{L}[X]) \geq \frac{3}{2} \vol_{n,r}(\mc{L}[X]).
+		\end{equation}
+		Therefore the upper bound in condition~\eqref{eqn:normalized_cut_ppr_vol} is satisfied.
+		\item It follows from Proposition~\ref{prop:sample_to_population_1} and equations~\eqref{eqn:ncut_lower_set} and~\eqref{eqn:local_spread_ub} that with probability at least $1 - 3\exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{L}))^2n\} - 2\exp\bigl\{-\delta^2\bigl(\vol_{\Pbb,r}(\mc{X}) n\bigr\} - n\exp\bigl\{-\delta^2d_{\min}(\Pbb) n\bigr/(3 + \delta)\}$,
+		\begin{equation}
+		\Phi_{n,r}(\mc{L}[X]) \leq (1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{L}) \leq (8/3 + 8\delta) \cdot  \frac{r}{\rho}, 
+		\end{equation}
+		and
+		\begin{equation}
+		s_{n,r}(X) \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{X}) \geq (1 - 3\delta) \cdot \frac{\pi r^2}{2\rho\sigma}.
+		\end{equation}
+		Therefore by Assumption~\textcolor{red}{(?)}, condition~\eqref{eqn:normalized_cut_ppr_ncut} is satisfied.
+	\end{itemize}
+	As a result, we may apply Theorem~\ref{thm:normalized_cut_ppr}, and deduce the following: there exists a set $\mc{L}[X]^g \subset \mc{L}$ of large volume, $\vol_{n,r}(\mc{L}[X]^g) \geq 5/6 \cdot \vol_{n,r}(\mc{L}[X])$, such that for any seed node $v \in \mc{L}[X]^g$, the normalized cut of the PPR cluster estimate $\Phi_{n,r}(\wh{C})$ satisfies the following upper bound:
+	\begin{align*}
+	\Phi_{n,r}(\wh{C}) & \overset{(\textrm{Thm.}~\ref{thm:normalized_cut_ppr})}{<} 72\sqrt{\Phi_{n,r}(\mc{L}[X]) \cdot \ln\Bigl(\frac{36}{s_{n,r}(X)}\Bigr)} \\
+	& \overset{\eqref{pf:ppr_lb_1},\eqref{pf:ppr_lb_2}}{\leq} 72\sqrt{(1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{L}) \cdot \ln\Bigl(\frac{36}{(1 - 3\delta)s_{\Pbb,r}(\mc{X})}\Bigr)} \\
+	& \overset{\eqref{eqn:ncut_lower_set}, \eqref{eqn:local_spread_ub}}{\leq} 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)}.
+	\end{align*}	
+	Combined with Lemma~\ref{lem:normalized_cut_lb}, this implies
+	\begin{equation}
+	\label{pf:ppr_lb_3}
+	\frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+	\end{equation}
+	with probability at least $1 - 5\exp\set{-\delta^2(\cut_{\Pbb,r}(\mathcal{L}))^2n} - n\exp\bigl\{-\delta^2 d_{\min}(\Pbb) n/(3 + \delta)\bigr\} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
+Solving the inequality~\eqref{pf:ppr_lb_3} for $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ yields~\eqref{eqn:ppr_lb}.
+
+	We conclude by observing that the set $\mc{L}[X]^g$ must have significant overlap with $\mc{C}^{(1)}[X]$: 
+	\begin{align*}
+	\vol_{n,r}(\mathcal{L}[X]^g \cap \mc{C}^{(1)}[X]) & \geq  \vol_{n,r}(\mathcal{L}[X]^g) - \vol_{n,r}((\mathcal{L}[X]^g \cap (\mc{C}^{(0)} \cup \mc{C}^{(2)})[X])[X]) \\
+	& \geq \frac{5}{6}\vol_{n,r}\bigl(\mathcal{L}[X]\bigr) - \vol_{n,r}\bigl((\mathcal{L} \cap (\mc{C}^{(0)} \cup \mc{C}^{(1)}))[X]\bigr) \\
+	& \geq \frac{5}{6}\vol_{n,r}\bigl((\mathcal{L} \cap \mc{C}^{(1)})[X]\bigr) - \frac{1}{6}\vol_{n,r}\bigl(\mathcal{L}[X]\bigr) \\
+	& \overset{\mathrm{(i)}}{\geq} \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}) \\
+	& \overset{\mathrm{(ii)}}{\geq} \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mc{C}^{(1)}[X]) \geq \frac{6}{49} \cdot \vol_{n,r}(\mc{C}^{(1)}[X]),
+	\end{align*}
+	where $\mathrm{(i)}$ and $\mathrm{(ii)}$ follow from Lemma~\ref{lem:hoeffding} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}))^2}$, and the last inequality follows since $\delta \in (0,1/7)$.
+The claim of Theorem~\ref{thm:ppr_lb} follows upon taking constants $B_3:= 8 + 12\sigma\rho/r^2 + 2\rho/r$, $b_4 := \cut_{\Pbb,r}(\mc{L})^2 \wedge \epsilon r^2/(\rho \sigma) \wedge \pi r^3/(2\sigma\rho^2) \wedge \vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)})^2$ and $b_5 := d_{\min}(\Pbb)$.
+\end{proof}
+
+\begin{proof}[Proof (of Lemma~\ref{lem:normalized_cut_lb}).]
+	To lower bound the normalized cut $\Phi_{n,r}(Z)$, it suffices to lower bound $\cut_{n,r}(Z)$ and upper bound $\vol_{n,r}(Z)$. A crude upper bound on the volume is simply 
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf4}
+	\vol_{n,r}(Z) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
+	\end{equation}
+	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this crude upper bound will suffice for our purposes.
+
+	We turn to lower bounding $\cut_{n,r}(Z)$.
+We will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $Z$ to the boundary of the binned set $\overline{Z}$, and then lower bound the size of the boundary of $\overline{Z}$.
+
+	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube
+	\begin{equation*}
+	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
+	\end{equation*}
+	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
+For a set $Z \subset X$ we define the binned set $\overline{Z} \subset \overline{Q}$ as follows
+	\begin{equation*}
+	\overline{Z} := \set{Q \in \overline{Q}: \Pbb_n(Z \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
+	\end{equation*}
+	and we let 
+	\begin{equation*}
+	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{k - \ell}_1 = 1}.
+	\end{equation*}
+	be the boundary set of $\overline{Z}$ in $\overline{Q}$.
+Intuitively, every point $x_i \in Z$ in the boundary set of $\overline{Z}$ will have many edges to $X\setminus Z$.
+Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \Pbb_n(Q)$, we have
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf1}
+	\cut_{n,r}(Z) \geq \cut_{n,r}(Z \cap \set{x_i \in \overline{Z}}) \geq \frac{1}{4} \abs{\partial \overline{Z}} Q_{\min}^2,
+	\end{equation}
+	where the last inequality follows since for every cube $Q_k \in \partial\overline{Z}$, there exists a cube $Q_\ell \not\in \overline{Z}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
+
+	Now we move on lower bounding the size of the boundary $\abs{\partial\wb{Z}}$.
+To do so, we divide $\mathcal{X}$ into slices horizontally.
+Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
+For each $k$, either
+	\begin{enumerate}
+		\item $\wb{R}_k \cap \wb{Z} = \emptyset$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle \mc{C}^{(1)}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k), ~~ \textrm{or}
+		\end{equation*}
+		\item $\wb{R}_k \cap \wb{Z} = \wb{R}_k$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle \mc{C}^{}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
+		\end{equation*}
+		\item $\wb{R}_k \cap \partial \wb{Z} \neq \emptyset$.
+	\end{enumerate}
+	Let $N(R)$ be the number of slices for which $\wb{R}_k \cap \partial \wb{Z} \neq \emptyset$. By the cases elucidated above, letting
+	\begin{equation*} R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}
+	\end{equation*} 
+	we obtain the following lower bound on the volume of the symmetric set difference,
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf2}
+	\vol_{n,r}(A \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right].
+	\end{equation}
+	Finally note that $\abs{\partial\wb{Z}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
+	\begin{align}
+	\cut_{n,r}(Z) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
+	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
+	\end{align}
+	for all $Z \subset X$.
+
+	It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
+	To do so, we first lower bound the expected probability of any cell $Q$,
+	\begin{align*}
+	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
+	\end{align*}
+	and the expected volume of $\mc{C}^{(1)}[X] \cap R_k$ and $\mc{C}^{(2)}[X] \cap R_k$,
+	\begin{equation}
+	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
+	\end{equation}
+
+	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
+Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
+Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
+	\begin{equation*}
+	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq \frac{(1 - \delta)}{2}\frac{\pi r^3}{\sigma \rho^2 },
+	\end{equation*}
+	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
+Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
+	\begin{equation*}	
+	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
+	\end{equation*}
+	for all $Z \subseteq X$.
+\end{proof}
 
@@
 not contain any points in any other density cluster $\mc{C}_{\lambda}' \in
-\mathbb{C}_f(\lambda)$.
+\mathbb{C}_f(\lambda)$. \textcolor{red}{TODO: explain why this is a desirable property for a cluster estimate $\wh{C}$.}
 
@@
 \end{theorem}
-\textcolor{red}{(In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.)}\vspace{1 mm}
+In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.
 
@@
 \eqref{eqn:density_cluster_consistency} only when we can guarantee the volume of the symmetric set difference will be very small. This strong condition is
-the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}.\vspace{1 mm}
-
-\textcolor{red}{Originally, we had only (something like) the preceding paragraph, which in my opinion is very negative and invites the reader to discount the preceding result.
-I added the paragraph in red above it, to make it clear that the Corollary is interesting even if the required conditions are strong.}
+the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}.
 

### 2021-01-24 jmlr/revision/proofs.tex
All proofs completed.

@@
 	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
-	\item \textbf{Finite-sample bounds.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
-	\item \textbf{Population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}.
+	\item \textbf{Sample-to-population results.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
+	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}.
 This proves~\textcolor{red}{(?)}
@@
 
-\paragraph{Organization.} In the following subsections we establish: (\ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}); (\ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (\ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (\ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (\ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
-
-\subsection{Proof of Lemma~\ref{lem:zhu}}
+\paragraph{Organization.} In the following subsections we establish: (\ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (\ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (\ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (\ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (\ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
+
+\subsection{Misclassification error of clustering with PPR and aPPR}
 \label{subsec:pf_lem_zhu}
@@
 
+\begin{proof}[Proof (of Lemma~\ref{lem:zhu})]
 As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma.
@@
 \begin{equation*}
-\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u),~~\textrm{for all $u \in C^{\mathrm{int}} \setminus S_{\beta,v}$},
+\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u),~~\textrm{for all $u \in C^{\mathrm{int}} \setminus S_{\beta,v}$};
 \end{equation*}
@@
 \end{equation*}
-The upper bounds in~\eqref{eqn:zhu_condition} imply
+The upper bounds on $\alpha$ and $\beta$ in~\eqref{eqn:zhu_condition} imply
 \begin{equation*}
@@
 The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
+\end{proof}
+
+If the cluster estimate $\wh{C}$ is instead obtained by sweep cutting the aPPR vector $p_v^{(\varepsilon)}$, a similar upper bound on $\vol(\wh{C} \vartriangle C)$ holds, provided that $\varepsilon$ is sufficiently small.
+\begin{corollary}
+	\label{cor:zhu}
+	For a set $C \subseteq V$, suppose that $\alpha,\beta$ satisfy~\eqref{eqn:zhu_condition}, and additionally that 
+	\begin{equation}
+	\label{eqn:zhu_condition_2}
+	\varepsilon \leq \frac{1}{25\vol(C;G)}.
+	\end{equation}
+	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ of the aPPR vector $p_v^{(\varepsilon)}$ satisfies
+	\begin{equation}
+	\label{eqn:zhu_ub}
+	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
+	\end{equation}
+\end{corollary}
+\begin{proof}[Proof (of Corollary~\ref{cor:zhu})]
+	Recall that the upper bound~\eqref{eqn:zhu_ub} on $\vol(\wh{C} \vartriangle C;G)$ comes from combining the upper bounds on $\vol(\wh{C} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus \wh{C};G)$ and $\vol(C^{\mathrm{bdry}} \setminus \wh{C};G)$ in~\eqref{pf:zhu3.5},~\eqref{pf:zhu5} and~\eqref{pf:zhu6}.
+From the upper bound $p_v^{(\varepsilon)}(u) \leq p_v(u)$ for all $u \in V$, it is clear that both~\eqref{pf:zhu3.5} and~\eqref{pf:zhu6} continue to hold when the aPPR vector is used instead of the PPR vector.
+
+	It remains only to establish an upper bound on~$\vol(C^{\mathrm{int}} \setminus \wh{C};G)$.
+For any $u \in C \setminus S_{\beta,v}$, from inequality~\eqref{pf:zhu2} and the lower bound $p_v^{(\varepsilon)}(u) \geq p_v(u)  - \varepsilon \deg(u;G)$ in~\eqref{eqn:appr_error} we deduce that
+	\begin{equation}
+	\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  (\beta + \varepsilon)\deg(u;G) \leq \wt{p}_{\ell}(u).
+	\end{equation}
+	Following the same steps as used in the proof of Lemma~\ref{lem:zhu} yields the following inequality:
+	\begin{equation*}
+	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
+	\end{equation*}
+	The upper bounds on $\alpha,\beta$ in~\eqref{eqn:zhu_condition},  and on $\varepsilon$ in~\eqref{eqn:zhu_condition_2}, imply that
+	\begin{equation*}
+	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
+	\end{equation*}
+	and we conclude that
+	\begin{equation}
+	\label{pf:zhu2_1}
+	\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
+	\end{equation}
+	Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim.
+\end{proof}
 
@@
 \end{align*}
-Therefore with probability at least $1 - \exp\{-\delta^2 \cut_{\Pbb,r}(\mc{S})\}$,
+Therefore with probability at least $1 - \exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{S}))^2\}$,
 \begin{equation*}
@@
 \end{equation*}
-and likewise with probability at least $1 - \exp\{-\delta^2 \vol_{\Pbb,r}(\mc{S})\}$,
+and likewise with probability at least $1 - \exp\{-\delta^2 (\vol_{\Pbb,r}(\mc{S}))^2\}$,
 \begin{equation*}
@@
 \begin{equation*}
-\Phi_{n,r}(\mc{C}[X]) \leq \frac{1 + \delta}{1 - \delta} \frac{\cut_{\Pbb,r}(\mc{C})}{\min\{\vol_{\Pbb,r}(\mc{C}), \vol_{\Pbb,r}(\mc{C}^c)\}} = \frac{1 + \delta}{1 - \delta} \Phi_{\Pbb,r}(\mc{C}) \leq (1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{C})
-\end{equation*}
-with probability at least $1 - 3\exp\{-\delta^2 \cut_{\Pbb,r}(\mc{C})\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 = \cut_{\Pbb,r}(\mc{C})$ and $C_1 = 3$.
+\Phi_{n,r}(\mc{C}[X]) \leq \frac{1 + \delta}{1 - \delta} \cdot  \frac{\cut_{\Pbb,r}(\mc{C})}{\min\{\vol_{\Pbb,r}(\mc{C}), \vol_{\Pbb,r}(\mc{C}^c)\}} = \frac{1 + \delta}{1 - \delta} \cdot \Phi_{\Pbb,r}(\mc{C}) \leq (1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{C})
+\end{equation*}
+with probability at least $1 - 3\exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{C}))^2\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 := (\cut_{\Pbb,r}(\mc{C}))^2$.
 
@@
 To ease the notational burden, let $\wt{G}_{n,r} := G_{n,r}\bigl[\mc{C}[X]\bigr]$.
-By Lemma~\ref{lem:hoeffding}, with probability at least $1 - \exp\{-2\delta^2 \Pbb(\mc{C})^2n\}$
+By Lemma~\ref{lem:hoeffding_2}, with probability at least $1 - \exp\{-2\delta^2 (\Pbb(\mc{C}))^2n\}$
 \begin{equation}
@@
 \end{equation}
-Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-2(1 - \delta)\delta^2d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n\}$,
+Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-\delta^2d_{\min}(\wt{\Pbb}) \cdot (1 - \delta) \Pbb(\mc{C}) n/(3 + \delta)\}$,
 \begin{equation}
@@
 \end{equation}
-and likewise it follows from Lemma~\ref{lem:hoeffding_2} that with probability at least $1 - \exp\{-2\delta^2(1 - \delta) \vol_{\wt{\Pbb},r}(\mc{C})^2 \Pbb(\mc{C})n \}$,
+and likewise it follows from Lemma~\ref{lem:hoeffding} that with probability at least $1 - \exp\{-\delta^2(\vol_{\wt{\Pbb},r}(\mc{C}))^2 \cdot (1 - \delta) \Pbb(\mc{C}) n \}$,
 \begin{equation*}
@@
 \end{equation*}
-Consequently, for any $\delta \in (0,1/3)$,
-\begin{equation*}
-s_{n,r}(\mc{C}[X]) = \frac{d_{\min}(\wt{G}_{n,r})^2}{\vol(\wt{G}_{n,r})} \geq \frac{\frac{1}{\wt{n}^2}d_{\min}(\wt{G}_{n,r})^2}{\frac{1}{\wt{n}(\wt{n} - 1)}\vol(\wt{G}_{n,r})} \geq \frac{(1 - \delta)^2}{(1 + \delta)} \frac{d_{\min}(\wt{\Pbb})^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{C}).
-\end{equation*}
-with probability at least $1 - 2\exp\bigl\{-\delta^2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})n\bigr\} - n\exp\bigl\{-\delta^2\bigl(d_{\min}(\wt{\Pbb})\bigr)^2 \Pbb(\mc{C}) n\bigr\}$.
-This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 = \bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})$ and $b_3 = d_{\min}(\wt{\Pbb}) \Pbb(\mc{C})$
+Consequently for any $\delta \in (0,1/3)$,
+\begin{equation*}
+s_{n,r}(\mc{C}[X]) = \frac{d_{\min}(\wt{G}_{n,r})^2}{\vol(\wt{G}_{n,r})} \geq \frac{\frac{1}{\wt{n}^2}d_{\min}(\wt{G}_{n,r})^2}{\frac{1}{\wt{n}(\wt{n} - 1)}\vol(\wt{G}_{n,r})} \geq \frac{(1 - \delta)^2}{(1 + \delta)} \cdot  \frac{d_{\min}(\wt{\Pbb})^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{C}).
+\end{equation*}
+with probability at least $1 - \exp\{-2\delta^2 (\Pbb(\mc{C}))^2n\} - \exp\bigl\{-2\delta^2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})n/3\bigr\} - n\exp\bigl\{-\delta^2 d_{\min}(\wt{\Pbb}) \cdot \Pbb(\mc{C}) n/5\bigr\}$.
+This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 := (\Pbb(\mc{C}))^2 \wedge 2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})/3 \wedge d_{\min}(\wt{\Pbb}) \cdot \Pbb(\mc{C})/5$.
 
@@
 	Suppose $\Pbb$ satisfies~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
-Then, there exists positive constants $B_{2}$ and $B_3$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
-	\begin{equation*}
-	\Delta_{\infty}(\mbb{P},\mbb{P}_n) \leq B_{3} \cdot 
+Then, there exists positive constants $B_{2}$ and $B_4$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
+	\begin{equation*}
+	\Delta_{\infty}(\mbb{P},\mbb{P}_n) \leq B_4 \cdot 
 	\begin{dcases*}
@@
 so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$.
-Next, as we have already derived in~\eqref{pf:sample_to_population_local_spread_2}, with probability at least $1 - \exp\{-\mbb{P}(\mc{C})n\} - \exp\{-d_{\min}(\wt{\Pbb})^2 \Pbb(\mc{C}) n/\sqrt{2}\}$,
+Next, taking $1 - \delta = 1/\sqrt{2}$ in~\eqref{pf:sample_to_population_local_spread_2}, we have that with probability at least $1 - \exp\{-(\mbb{P}(\mc{C}))^2n/5\} - n\exp\{-d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n/50\}$,
 \begin{equation*}
@@
 \begin{equation*}
-\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_3 \frac{\log(n)^{p_d}}{n^{1/d}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_4 \frac{(\log n)^{p_d}}{n^{1/d}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
 \end{equation*}
@@
 \end{equation*}
-with probability at least $1 - B_2/n - (n + 2)\exp\{-d_{\min}(\wt{\Pbb})\cdot \Pbb(\mc{C}) n/\sqrt{2}\}$, establishing~\eqref{eqn:sample_to_population_conductance}.
+with probability at least $1 - B_2/n - \exp\{-(\mbb{P}(\mc{C}))^2n/5\} - n\exp\{-d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n/50\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := (\mbb{P}(\mc{C}))^2/5 \wedge d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) /50$.
 
@@
 		\end{equation}
-		\item \textbf{Volume of $\delta$-interiors.} Suppose $\nu(\mc{S}^{\delta}) \leq (1 - a) \cdot \nu(\mc{S})$ or $\nu(\mc{R}^{\delta}) \leq (1 - a) \cdot \nu(\mc{R})$. Then 
+		\item \textbf{Lebesgue measure of $\delta$-interiors.} Suppose $\nu(\mc{S}^{\delta}) \leq (1 - a) \cdot \nu(\mc{S})$ or $\nu(\mc{R}^{\delta}) \leq (1 - a) \cdot \nu(\mc{R})$. Then 
 		$\nu(\mc{B}^{\delta}) \geq a \cdot \min\{\nu(\mc{S}), \nu(\mc{R})\}$, and combined with~\eqref{pf:uniform_density_cluster_conductance_1} we have that $\Phi_{\wt{\nu},r}(\mc{S}) \geq \delta a \ell/2$.
@@
 \label{sec:pf_major_theorems}
-In this section, we prove Theorem~\ref{thm:volume_ssd_ub} (in Section), Corollary~\ref{cor:density_cluster_volume_ssd_ub}, and Theorem~\ref{thm:ppr_lb}.
+We now prove the three major theorems of our paper: Theorem~\ref{thm:volume_ssd_ub} (in Section~\ref{subsec:pf_volume_ssd_ub}), Theorem~\ref{thm:density_cluster_volume_ssd_ub}, and Theorem~\ref{thm:ppr_lb}.
+Throughout, we use the notation $\wt{n} = |\mc{C}[X]|$ and $\wt{G}_{n,r} = G_{n,r}\bigl[\mc{C}[X]\bigr]$ as defined above.
 
 \subsection{Proof of Theorem~\ref{thm:volume_ssd_ub}}
-
-\subsection{Proof of Corollary~\ref{cor:density_cluster_volume_ssd_ub}}
+\label{subsec:pf_volume_ssd_ub}
+We begin by recalling some probabilistic estimates needed for the proof of Theorem~\ref{thm:volume_ssd_ub}, along with the probability with which they hold.
+
+\textit{Probablistic estimates.}
+Throughout the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume (i) that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} are satisfied; (ii) that the volume of $\mc{C}[X]$ is upper and lower bounded,
+\begin{equation}
+\label{pf:volume_ssd_ub_1}
+(1 - \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C}) \leq \vol_{n,r}(\mc{C}[X]) \leq (1 + \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C});
+\end{equation}
+(iii) that the number of sample points in $\mc{C}$ is lower bounded,
+\begin{equation}
+\label{pf:volume_ssd_ub_2}
+\wt{n} \geq (1 - \delta) \cdot n \cdot \mbb{P}(\mc{C});
+\end{equation}
+and finally (iv) that the minimum and maximum degree of $\wt{G}_{n,r}$ are lower and upper bounded respectively,
+\begin{equation}
+\label{pf:volume_ssd_ub_3}
+~~\frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq (1 - \delta) \cdot d_{\min}(\wt{\Pbb}),~~\textrm{and}~~\frac{1}{\wt{n}} d_{\max}(\wt{G}_{n,r}) \leq (1 + \delta) \cdot d_{\max}(\wt{\Pbb}).
+\end{equation}
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$.
+
+% AJG comment: The presence of a pre-factor of 4 in the second term, instead of 3, accounts for the extra upper bound needed on the vol_{n,r}(\mc{C}[X]).
+The presence of a pre-factor of 2(n + 2) in the third term, instead of (n + 2), accounts for the extra upper bound needed on d_{\max}(\wt{G}_{n,r}).
+
+\begin{proof}[Proof (of Theorem~\ref{thm:volume_ssd_ub})]
+We use Lemma~\ref{lem:zhu} to upper bound $\Delta(\wh{C},\mc{C}[X])$.
+In order to do so, we must verify that the tuning parameters $\alpha$ and $(L,U)$ satisfy the condition \eqref{eqn:zhu_condition} of this lemma.
+In order to verify that $\alpha \leq 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$, we will use Proposition~\ref{prop:conductance_lb_transportation_distance} to upper bound $\tau_{\infty}(\wt{G}_{n,r})$, which we may use because
+\begin{equation*}
+\frac{d_{\max}(\wt{G}_{n,r})}{\bigl(d_{\min}(\wt{G}_{n,r})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{d_{\max}(\wt{\Pbb})}{\wt{n}\bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^3} \cdot \frac{d_{\max}(\wt{\Pbb})}{n\Pbb(\mc{C})\bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{1}{16},
+\end{equation*}
+with the last inequality following by~\eqref{eqn:volume_ssd_ub_sample_complexity} upon taking $B_3 := 16 \cdot d_{\max}(\wt{\Pbb})/\bigl(d_{\min}(\wt{\Pbb})\bigr)^2$ in that equation.
+Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance}, and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$.
+On the other hand, by the upper bound on $\vol_{n,r}(\mc{C}[X])$ given in~\eqref{pf:volume_ssd_ub_3} and~\eqref{eqn:initialization}, we have that $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
+
+Invoking Lemma~\ref{lem:zhu}, we conclude that there exists a set $\mc{C}[X]^g \subset \mc{C}[X]$ of volume at least $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that for any $\beta \in (L,U)$,
+\begin{equation*}
+\vol_{n,r}(S_{\beta,v} \vartriangle \mc{C}[X]) \leq 60 \cdot \frac{\Phi_{n,r}(\mc{C}[X])}{\alpha L} \leq 60 \frac{(1 + 2\delta)}{(1 - 4\delta)^2} \cdot \frac{\Phi_{n,r}(\mc{C}[X])}{\alpha_{\Pbb,r}(\mc{C},\delta)}\cdot n(n-1)\vol_{\Pbb,r}(\mc{C})
+\end{equation*}
+Noting that $\wh{C} = S_{\beta,v}$ for some $\beta \in (L,U)$, the claimed upper bound~\eqref{eqn:volume_ssd_ub} on $\Delta(\wh{C},\mc{C}[X])$ then follows from the upper bound~\eqref{eqn:sample_to_population_normalized_cut} on $\Phi_{n,r}(\mc{C}[X])$ and the upper bound on $\vol_{\Pbb,r}(\mc{C})$ in~\eqref{pf:volume_ssd_ub_1}.
+\end{proof}
+\subsection{Proof of Theorem~\ref{thm:density_cluster_volume_ssd_ub}}
+From Theorem~\ref{thm:volume_ssd_ub}, we have with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
+\begin{align*}
+\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} & \leq 60 \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\alpha_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)} \\
+& \leq \frac{780}{\ln(2)} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2} \cdot \ln^2\Bigl(\frac{8}{(1 - 3\delta) s_{\Pbb,r}(\mc{C})}\Bigr)
+\end{align*}
+The claimed upper bound~\eqref{eqn:density_cluster_volume_ssd_ub} on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ then follows from the bounds~\eqref{eqn:density_cluster_local_spread}-\eqref{eqn:density_cluster_conductance} on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$, noting that the condition $r \leq \sigma/(4d)$ implies that $(1 - r/(4\rho L)) \geq 1 - 1/16$ and $1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)} \geq 1 - 1/\sqrt{32}$, and taking
+\begin{equation*}
+C_{1,\delta} := \frac{898560}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)},~~\textrm{and}~~C_{2,\delta} := \frac{36}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
+\end{equation*}
 
@@
 \begin{proof}[Proof (of Theorem~\ref{thm:ppr_lb})]
+	Put
+	\begin{align*}
+	C_{3,\delta} & := 768 \cdot (1 + 3\delta),&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
+	C_{5,\delta} & := \frac{(1 + \delta)^2}{(1 - \delta)^2},&&C_{6,\delta} := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}.
+	\end{align*}
 	As mentioned, we would like to use Theorem~\ref{thm:normalized_cut_ppr} to upper bound $\Phi_{n,r}(\wh{C})$, and so we first verify that the conditions of Theorem~\ref{thm:normalized_cut_ppr} are met.
@@
 		\end{equation}
-		Therefore by Assumption~\textcolor{red}{(?)}, condition~\eqref{eqn:normalized_cut_ppr_ncut} is satisfied.
+		The assumption~\eqref{eqn:ppr_lb_condition} implies that  condition~\eqref{eqn:normalized_cut_ppr_ncut} is satisfied.
 	\end{itemize}
@@
 
-	We conclude by observing that the set $\mc{L}[X]^g$ must have significant overlap with $\mc{C}^{(1)}[X]$: 
-	\begin{align*}
-	\vol_{n,r}(\mathcal{L}[X]^g \cap \mc{C}^{(1)}[X]) & \geq  \vol_{n,r}(\mathcal{L}[X]^g) - \vol_{n,r}((\mathcal{L}[X]^g \cap (\mc{C}^{(0)} \cup \mc{C}^{(2)})[X])[X]) \\
+	We conclude by observing that the set $\mc{L}[X]^g$ must have significant overlap with $\mc{C}^{(1)}[X]$. In particular,
+	\begin{align*}
+	\vol_{n,r}(\mathcal{L}[X]^g \cap \mc{C}^{(1)}[X]) & \geq  \vol_{n,r}(\mathcal{L}[X]^g) - \vol_{n,r}\bigl((\mathcal{L}[X]^g \cap (\mc{C}^{(0)} \cup \mc{C}^{(2)})[X])\bigr) \\
 	& \geq \frac{5}{6}\vol_{n,r}\bigl(\mathcal{L}[X]\bigr) - \vol_{n,r}\bigl((\mathcal{L} \cap (\mc{C}^{(0)} \cup \mc{C}^{(1)}))[X]\bigr) \\
@@
 \label{sec:appr_misclassification_error}
-
-\subsection{Consistency}
+In this section, we prove two additional results regarding PPR remarked upon in our main text.
+In Section~\ref{subsec:appr_volume_ssd_ub}, we show that clustering using the aPPR vector satisfies an equivalent guarantee to Theorem~\ref{thm:volume_ssd_ub}.
+In Section~\ref{subsec:consistent_recovery_density_clusters}, we show that the PPR vector can perfectly distinguish two distinct density clusters $\mc{C}_{\lambda},\mc{C}_{\lambda}'$.
+
+\subsection{Generic cluster recovery with aPPR}
+\label{subsec:appr_volume_ssd_ub}
+Our formal claim regarding cluster recovery with aPPR is contained in Corollary~\ref{cor:appr}.
+\begin{corollary}
+	\label{cor:appr}
+	Consider instead of
+	Algorithm \ref{alg:ppr} using the approximate PPR vector from
+	\citet{andersen2006} satisfying \eqref{eqn:appr_error}, and forming the 
+	corresponding cluster estimate \smash{$\wh{C}$} in the same manner.  Then 
+	provided we take 
+	\begin{equation}
+	\label{eqn:appr_parameter}
+	\varepsilon = \frac{1}{25(1 + \delta)n(n - 1)\vol_{\Pbb,r}(\mc{C})} ,
+	\end{equation}
+	under the assumptions of Theorem~\ref{thm:volume_ssd_ub} the upper bound on symmetric set difference in \eqref{eqn:volume_ssd_ub} still
+	holds.
+\end{corollary}	
+\begin{proof}[Proof (of Corollary~\ref{cor:appr})]
+	Note that the choice of $\varepsilon$ in~\eqref{eqn:appr_parameter} implies $\varepsilon \leq 1/25\vol_{n,r}(\mc{C}[X])$ with probability at least $1 - \exp\bigl\{-\delta^2\bigl(\vol_{\Pbb,r}(\mc{C})\bigr)^2\bigr\}$.
+The proof of Corollary~\ref{cor:appr} is then identical to that of Theorem~\ref{thm:volume_ssd_ub}, except we use Corollary~\ref{cor:zhu} rather than Lemma~\ref{lem:zhu} to relate the symmetric set difference to the graph normalized cut and mixing time.
+\end{proof}
+
+\subsection{Perfectly distinguishing two density clusters}
 \label{subsec:consistent_recovery_density_clusters}
 
-The symmetric set difference does not measure whether \smash{$\wh{C}$}
+As mentioned in our main text, the symmetric set difference does not measure whether \smash{$\wh{C}$}
 can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in 
 	\mathbb{C}_f(\lambda)$}. We therefore also study a second notion of cluster 
-estimation, first introduced by \citet{hartigan1981}, and defined
-asymptotically.
+estimation, first introduced by \citet{hartigan1981}.
 
@@
 	\label{def:density_cluster_consistency}
-	For an estimator \smash{$\wh{C} \subseteq X$} and cluster \smash{$\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$}, we call \smash{$\wh{C}$} \emph{consistent} for
-	\smash{$\mc{C}_{\lambda}$} if for all \smash{$\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$} with  
-	\smash{$\mc{C} \not= \mc{C}'$}, the following holds with probability tending to 1 as $n \to \infty$: 
+	For an estimator \smash{$\wh{C} \subseteq X$} and distinct clusters \smash{$\mc{C}_{\lambda}, \mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$}, we say \smash{$\wh{C}$} \emph{separates} $\mc{C}_{\lambda}$ from $\mc{C}_{\lambda}'$ if
 	\begin{equation}
 	\label{eqn:density_cluster_consistency}
-	\mc{C}[X] \subseteq \wh{C} \quad \text{and} \quad
-	\wh{C} \cap \mc{C}'[X] = \emptyset.
+	\mc{C}_{\lambda}[X] \subseteq \wh{C} \quad \text{and} \quad
+	\wh{C} \cap \mc{C}_{\lambda}'[X] = \emptyset.
 	\end{equation}
@@
 
-Consistent cluster recovery roughly ensures that, for a given 
-threshold $\lambda>0$, the estimated cluster \smash{$\wh{C}$} contains all points
-in a true density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$, and simultaneously does 
-not contain any points in any other density cluster $\mc{C}_{\lambda}' \in
-\mathbb{C}_f(\lambda)$. \textcolor{red}{TODO: explain why this is a desirable property for a cluster estimate $\wh{C}$.}
-
-The bound on symmetric set difference \eqref{eqn:density_cluster_volume_ssd_ub} does not imply consistent density cluster estimation in the sense of \eqref{eqn:density_cluster_consistency}.
-This notion of consistency requires a
-uniform bound over the PPR vector $p_v$: as an example, suppose that we were
-able to show that for all \smash{$\mc{C}' \in \mathbb{C}_f(\lambda), \mc{C}' \neq \mc{C}$}, and each $u \in \mc{C}, w \in \mc{C}'$,  
+The bound on symmetric set difference \eqref{eqn:density_cluster_volume_ssd_ub} does not imply \eqref{eqn:density_cluster_consistency}, which requires a
+uniform bound over the PPR vector $p_v$. As an example, suppose that we were
+able to show that for all \smash{$\mc{C}' \in \mathbb{C}_f(\lambda), \mc{C}' \neq \mc{C}$}, and each $u \in \mc{C}, u' \in \mc{C}'$,  
 \begin{equation}
 \label{eqn:ppr_gap}
-\frac{p_v(w)}{D_{ww}} \leq \frac{1}{100 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} <
-\frac{1}{10 {n \choose 2} \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \leq \frac{p_v(u)}{D_{uu}}. 
+\frac{p_v(u')}{\deg(u';G)} \leq \frac{1}{10} \cdot \frac{1}{n (n - 1) \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} <
+\frac{1}{5} \cdot \frac{1}{n (n-1) \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \leq \frac{p_v(u)}{\deg(u;G)}. 
 \end{equation}
@@
 small upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ ensures that with high probability the uniform bound~\eqref{eqn:ppr_gap} is satisfied, and hence implies
-\smash{$\wh{C}$} will be a consistent estimator.
+that \smash{$\wh{C}$} will separate $\mc{C}_{\lambda}$ from $\mc{C}_{\lambda}'$. In what follows, put
+\begin{equation*}
+c_{1,\delta} := \frac{(1 - \delta)^3}{4} \cdot \min\Bigl\{\Bigl(\frac{3}{8(1 + \delta)} - \frac{1}{5}\Bigr),\frac{1}{10}\Bigr\}
+\end{equation*}
+and note that if $\delta \in (0,7/8)$ then $c_{1,\delta} > 0$.
+(In fact, we will have to take $\delta \in (0,1/4)$ in order to use Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}).
+Additionally, denote $\Pbb'$ for the conditional distribution of a sample point given that it falls in $\mc{C}_{\lambda,\sigma}'$, i.e.
+$\Pbb'(\mc{S}) := \Pbb(\mc{S} \cap \mc{C}_{\lambda,\sigma}')/\Pbb(\mc{C}_{\lambda,\sigma}')$, and $G_{n,r}' := G_{n,r}[\mc{C}_{\lambda,\sigma}']$ for the subgraph of $G_{n,r}$ induced by $\mc{C}_{\lambda,\sigma}'$.
 \begin{theorem}
 	\label{thm:density_cluster_consistent_recovery}
-	For any $\delta \in (0,1)$, the following statement holds with probability at least $1 - 3\exp\{-b_1\delta^2n\} - B_2n\exp\{-b_2\delta^2n\}$: there exists a constant $c_1$ and a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,  \smash{$\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$}, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
+	For any $\delta \in (0,1/4)$, and otherwise under the same conditions as Theorem~\ref{thm:volume_ssd_ub}, the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
 	\begin{equation}
 	\label{eqn:density_cluster_consistent_recovery_condition}
-	\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta) \leq c_1 \cdot \min_{x: f(x) \geq \lambda} \Bigl\{\deg_{\Pbb,r}(x)\Bigr\},
+	\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta) \leq c_{1,\delta} \cdot \frac{\min\bigl\{\Pbb(\mc{C}_{\lambda,\sigma})^2 \cdot d_{\min}(\wt{\Pbb})^2, \Pbb(\mc{C}_{\lambda,\sigma}')^2 \cdot d_{\min}(\Pbb')^2\bigl\}}{\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}
 	\end{equation}
@@
 \end{theorem}
-In one sense, this is a strong result: if the density cluster $\mc{C}_{\lambda}$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Corollary~\ref{cor:density_cluster_volume_ssd_ub} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from all other connected components $\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda), \mc{C}_\lambda' \not= \mc{C}_{\lambda}$.
-
-On the other hand, unfortunately the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition} is rather restrictive. Specifically, from the following chain of inequalities,
-\begin{equation*}
-\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_1 \cdot \min_{x: f(x) \geq \lambda} \bigl\{\deg_{\Pbb,r}(x)\bigr\} \overset{\ref{asmp:lambda_bounded_density}}{\leq} c_1 \cdot \Lambda_{\sigma} \nu_d r^d,
-\end{equation*}
-we see that in order for~\eqref{eqn:density_cluster_consistent_recovery_condition} to be met, it is necessary that \smash{$\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$} be at most $c_1 \cdot \Lambda_{\sigma} \nu_d r^d$.
+
+Before we prove Theorem~\ref{thm:density_cluster_consistent_recovery}, we make a few brief remarks:
+\begin{itemize}
+	\item In one sense, Theroem~\ref{thm:density_cluster_consistent_recovery} is a strong result: if the density clusters $\mc{C}_{\lambda},\mc{C}_{\lambda}'$ satisfies the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition}, and we are willing to ignore the behavior of the algorithm in low-density regions, Theorem~\ref{thm:density_cluster_consistent_recovery} guarantees that PPR will \emph{perfectly distinguish} the candidate cluster $\mc{C}_{\lambda}$ from $\mc{C}_{\lambda}'$.
+
+	\item On the other hand, unfortunately the requirement~\eqref{eqn:density_cluster_consistent_recovery_condition} is rather restrictive.
+Suppose the density cluster $\mc{C}_{\lambda,\sigma}$ satisfies~\ref{asmp:lambda_bounded_density}.
+Then from the following chain of inequalities,
+	\begin{equation*}
+	\frac{\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} \overset{(\textrm{Thm.~\ref{thm:volume_ssd_ub}})}{\leq} \kappa_{\Pbb,r}(\mc{C},\delta) \overset{\eqref{eqn:density_cluster_consistent_recovery_condition}}{\leq} c_{1,\delta} \cdot \frac{\Pbb(\mc{C}_{\lambda,\sigma})^2 \cdot d_{\min}(\wt{\Pbb})^2}{\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} \overset{\ref{asmp:lambda_bounded_density}}{\leq} c_{1,\delta} \cdot \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \nu_d r^d,
+	\end{equation*}
+	we see that in order for~\eqref{eqn:density_cluster_consistent_recovery_condition} to be met, it is necessary that \smash{$\Delta(\wh{C}, \mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$} be on the order of $r^d$.
 In plain terms, we
@@
 	the price we pay in order to obtain the uniform bound in~\eqref{eqn:ppr_gap}. 
+	\item The proof of Theorem~\ref{thm:density_cluster_consistent_recovery} relies heavily on Lemma~\ref{lem:ppr_uniform_bound}.
+This lemma---or more accurately, the equation~\eqref{pf:interpolator_bound_max_entry} used in the proof of the lemma---can be thought of as a smoothness result for the PPR vector, showing that the mass of $p_v(\cdot)$ cannot be overly concentrated at any one node $u$.
+However,~\eqref{pf:interpolator_bound_max_entry} is a somewhat crude bound.
+By plugging a stronger result on the smoothness of $p_v(\cdot)$ in to the proof of Lemma~\ref{lem:ppr_uniform_bound}, we could improve the uniform bounds of the lemma in turn show that the conclusion of Theorem~\ref{thm:density_cluster_consistent_recovery} holds under weaker conditions than~\eqref{eqn:density_cluster_consistent_recovery_condition}.
+\end{itemize}
+
+Now we recall some probabilistic estimates before proceeding to the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.
+
+\textit{Probabilistic estimates.}
+As in the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} and~\eqref{pf:volume_ssd_ub_1}-\eqref{pf:volume_ssd_ub_3} are satisfied.
+We will additionally assume that
+\begin{equation}
+n' \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}_{\lambda,\sigma}')
+\end{equation}
+and that 
+\begin{equation}
+\frac{1}{n'} d_{\min}(G_{n,r}') \geq (1 - \delta) n \cdot d_{\min}(\Pbb').
+\end{equation}
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$, taking $b_6 := b_2 \wedge d_{\min}(\Pbb')/4 \wedge \bigl(\Pbb(\mc{C}_{\lambda,\sigma}')\bigr)^2$.
+
+% The pre-factor of 1/4 in the definition of b_6 is to handle the factor of 1/(3 + \delta) in Bernstein's inequality.
+
+\begin{proof}[Proof (of Theorem~\ref{thm:density_cluster_consistent_recovery})]
+We have already verified in the proof of Theorem~\ref{thm:volume_ssd_ub} that $\alpha \leq 1/(2\tau_{\infty}(\wt{G}_{n,r}))$, and we may therefore apply Lemma~\ref{lem:ppr_uniform_bound}, which gives an upper bound on $p_v(u)$ for all $u \in \mc{C}_{\lambda,\sigma}[X]_o$ and a lower bound on $p_v(u')$ for all $p_v(u')$ for all $u' \in \mc{C}_{\lambda,\sigma}'[X]_o$.
+These bounds are useful because $r \leq \sigma$, which implies that $\mc{C}_{\lambda}[X] \subseteq\mc{C}_{\lambda,\sigma}[X]_o$ and likewise that $C_{\lambda}'[X] \subseteq\mc{C}_{\lambda,\sigma}'[X]_o$.
+We will show that these bounds in turn imply~\eqref{eqn:ppr_gap}, from which the claim of the theorem follows.
+
+We begin with the lower bound in~\eqref{eqn:ppr_gap}.
+From (in order) Lemma~\ref{lem:ppr_uniform_bound}, our assorted probabilistic estimates, and the assumed lower bound~\eqref{eqn:density_cluster_consistent_recovery_condition} on $\kappa_{\Pbb,r}(\mc{C},\delta)$, we have that for all $u \in \mc{C}_{\lambda}[X]$,
+\begin{align*}
+\frac{p_v(u)}{\deg_{n,r}(u)} & \geq \frac{3}{8\vol_{n,r}(\mc{C}[X])} - 2\frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(\wt{G}_{n,r})^2 \alpha} \\
+& \geq \frac{1}{n^2}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{n^2}{\wt{n}^2} \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\wt{\Pbb})^2}\biggr) \\
+& \geq \frac{1}{n^2}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta)^3 \Pbb(\mc{C})^2 d_{\min}(\wt{\Pbb})^2}\biggr) \\
+& \geq \frac{1}{5 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}.
+\end{align*}
+An equivalent derivation implies the upper bound in~\eqref{eqn:ppr_gap}: for all $u' \in \mc{C}_{\lambda}'[X]$,
+\begin{equation*}
+\frac{p_v(u')}{\deg_{n,r}(u')} \leq 2 \frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(G_{n,r}')^2 \alpha} \leq 4 \cdot \frac{n^2}{(n')^2} \cdot 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\Pbb')^2} \leq 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{n^2 (1 - \delta)^3 \Pbb(\mc{C}_{\lambda,\sigma}')^2 d_{\min}(\Pbb')^2} \leq \frac{1}{10 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})},
+\end{equation*}
+completing the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.
+
+\end{proof}
 
@@
 \label{sec:experimental_details}
+
+\textcolor{red}{(TODO)}
 

### 2021-01-24 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Addressed (nearly) all of Ryan's comments on the revised manuscript.

@@
 \newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Ubb}{\mathbb{U}}
 \newcommand{\Ebb}{\mathbb{E}}
@@
 
-\subsection{PPR clustering, and worst-case guarantees}
+\subsection{PPR clustering}
+\label{subsec:ppr_clustering}
 We now review the PPR clustering algorithm, and some worst-case guarantees on the quality of the resulting cluster.
@@
 \begin{equation}
-\label{eqn: appr_error}
+\label{eqn:appr_error}
 \textrm{for all $u \in V$}, \quad p_v(u) - \varepsilon D_{uu}\leq
@@
 
+\subsection{Worst-case guarantees for PPR clustering}
 As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
-For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of $\wh{C}$ is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.
-\cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
+For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of $\wh{C}$ is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.\footnote{We say $a \lesssim b$ when $a \leq $} \cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
 \begin{equation}
@@
 Our own analysis builds on that of~\cite{zhu2013}, and we give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
-For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random geometric graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
+For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random neighborhood graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
 
 \subsection{PPR on a neighborhood graph}
+\label{subsec:ppr_neighborhood_graph}
 We now formally describe the statistical setting in which we operate, as well as the method we will study: PPR on a neighborhood graph.
@@
 
-\subsection{Cluster estimation}
+\subsection{Cluster accuracy}
 We need a metric to assess the accuracy with which $\wh{C}$ estimates the candidate cluster $\mc{C}$.
@@
 It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
-Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) = \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
+Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
 For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
@@
 \subsection{Summary of results}
-
 A summary of our results (and an outline for this paper) is as follows.
@@
 	\item In Section~\ref{subsec:recovery_well-conditioned_density_clusters}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
-These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Corollary~\ref{cor:density_cluster_volume_ssd_ub}).
-	\item In Section~\ref{subsec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
+These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
 \end{itemize}
@@
 \label{subsec:related_work}
-First, however, we conclude this Section by summarizing some related work (in addition to the background already given above).
-In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+We conclude this section by summarizing some related work (in addition to the background already given above).
+
+\paragraph{Spectral clustering.}In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
 In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating
@@
 
-\section{Upper bound on the symmetric set difference metric}
+\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$.
+In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
+By now, density clustering (and the related problem of level-set estimation) are relatively well-understood.
+\citet{polonik1995,rigollet2009} study density clustering under the symmetric set difference
+metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
+estimators under Hausdorff loss and
+\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
+consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$. \textcolor{red}{Add, at a minimum, references to Larry + Ale and Ingo's papers.}
+
+We emphasize that our goal is
+not to improve on these results, nor to offer a better algorithm for level set
+estimation, but rather to better understand the implications of our general theory by applying it within an already well-studied framework.
+Indeed, seen as a density clustering algorithm, PPR has none
+of the optimality guarantees found in the aforementioned works.
+We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
+
+\section{Recovery of a generic cluster with PPR}
 \label{sec:ub_symmetric_set_difference}
@@
 In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$.
-We build to this Theorem slowly, giving new structural results in two distinct directions.
-First, we build on some previous work (mentioned in the Introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$.
+We build to this theorem slowly, giving new structural results in two distinct directions.
+First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$.
 Second, we argue that when $n$ is large, $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ can be suitably bounded by their population-level analogues $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
 
-\subsection{PPR cluster recovery: the fixed graph case.}
+\subsection{PPR cluster recovery: the fixed graph case}
 \label{subsec:ppr_cluster_recovery_fixed_graph}
@@
 
-\paragraph{Improved bounds on mixing time.} Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$.
+\subsection{Improved bounds on mixing time} 
+\label{subsec:mixing_time}
+Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$.
 Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
@@
 Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
-There exist positive constants $b_1$-$b_3$ such that each of the following statements hold.
+There exist positive constants $b_1$ and $b_2$ such that each of the following statements hold.
 	\begin{itemize}
@@
 		\end{equation}
-		\item With probability at least $1 - 2\exp\{-b_2\delta^2n\} - n\exp\{-b_3\delta^2n\}$,
+		\item With probability at least $1 - (n + 2)\exp\{-b_2\delta^2n\}$,
 		\begin{equation}
@@
 Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
-Then there exist positive constants $B_1$ and $B_2$, such that for any $n \in \mathbb{N}$ for which
+Then there exist positive constants $B_1$,$B_2$, and $b_3$ such that for any $n \in \mathbb{N}$ for which
 	\begin{equation}
 	\label{eqn:sample_to_population_conductance_sample_complexity}
-	\frac{\log(n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,
-	\end{equation}
-	the following inequality holds with probability at least $1 - B_2/n - (n + 2)\exp\{-b_2n/\sqrt{2}\}$:
+	\frac{(\log n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,
+	\end{equation}
+	the following inequality holds with probability at least $1 - B_2/n - (n + 2)\exp\{-b_3n\}$:
 	\begin{equation}
@@
 
-\paragraph{Well-initialized algorithm.} As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified
+\subsection{Cluster recovery}
+\label{subsec:cluster_recovery}
+As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified
 parameters. In particular, for $\delta \in (0,1/4)$ and a candidate cluster $\mc{C} \in \Rd$, we require that some of the tuning parameters of Algorithm~\ref{alg:ppr} be chosen within specific ranges,
@@
 \label{eqn:alpha_initialization}
-\alpha_{\Pbb,r}(\mc{C},\delta) := \min\biggl\{\frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{(1 - 3\delta)s_{\Pbb,r}(\mc{C})}{8}\Bigr)}, \frac{1}{45}\biggr\}
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 3\delta)s_{\Pbb,r}(\mc{C})}\Bigr)} 
 \end{equation}
@@
 \label{eqn:condition_number}
-\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)}{(1 - 4\delta)^2(1 - 3\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}
+\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)(1+2\delta)}{(1 - 4\delta)^2(1 - \delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}
 \end{equation}
@@
 	\label{thm:volume_ssd_ub} 
-	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$.
-With probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, and suppose that
+	\begin{equation}
+	\label{eqn:volume_ssd_ub_sample_complexity}
+	\frac{(\log n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,~~\textrm{and}~~\frac{(1 + \delta)}{(1 - \delta)^3} \cdot B_3 \leq n.
+	\end{equation} 
+	With probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 	\begin{aligned}
-	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 30 \cdot \kappa_{\Pbb,r}(\mc{C},\delta)
+	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 60 \cdot \kappa_{\Pbb,r}(\mc{C},\delta)
 	\end{aligned}
@@
 Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}.
+\\
+	\textcolor{red}{(TODO): Add a comment explaining why we get different bounds.}
 
 	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
-	application of \eqref{eqn: appr_error} within the proof of Theorem
+	application of \eqref{eqn:appr_error} within the proof of Theorem
 	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
-	\begin{corollary}
-		\label{cor: appr}
-		Consider instead of
-		Algorithm \ref{alg:ppr} using the approximate PPR vector from
-		\citet{andersen2006} satisfying \eqref{eqn: appr_error}, and forming the 
-		corresponding cluster estimate \smash{$\wh{C}$} in the same manner.  Then 
-		provided we take 
-		\begin{equation}
-		\label{eqn: appr_parameter}
-		\varepsilon = \frac{1}{25 n(n - 1)\vol_{\Pbb,r}(\mc{C})} ,
-		\end{equation}
-		under the assumptions of Theorem~\ref{thm:volume_ssd_ub} the upper bound on symmetric set difference in \eqref{eqn:volume_ssd_ub} still
-		holds.
-	\end{corollary}	
+We formally state and proof this result in our appendix (Corollary~\textcolor{red}{(?)}).
 \end{itemize}
@@
 \label{sec:ppr_density_cluster}
-
 We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
@@
 
-\subsection{Background and setup}
-
-We start with some background on density clustering.
-For a given threshod $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$.
-In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
-By now, density clustering (and the related problem of level-set estimation) are relatively well-understood.
-\citet{polonik1995,rigollet2009} study density clustering under the symmetric set difference
-metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
-estimators under Hausdorff loss and
-\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
-consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$. We emphasize at the outset that our goal is
-not to improve on these results, nor to offer a better algorithm for level set
-estimation, but rather to better understand the implications of our general theory by applying it within an already well-studied framework.
-Indeed, seen as a density clustering algorithm, PPR has none
-of the optimality guarantees found in the aforementioned works.
-We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
-
-Each of the aforementioned results assume the density $f$ satisfies some regularity conditions.
+\subsection{Recovery of well-conditioned density clusters}
+\label{subsec:recovery_well-conditioned_density_clusters}
+
+All results on density clustering assume the density $f$ satisfies some regularity conditions.
 A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus cannot be resolved by any finite number of samples.
-This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to a lower semi-continuous version of $f$.
+This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to the lower semi-continuous version of $f$.
 We instead choose to follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) \leq \sigma\}$ for some $\sigma > 0$.
 (Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.) The set $\mc{C}_{\lambda,\sigma}$ is full dimensional with a smooth boundary, and thus no continuity assumption on $f$ is required.
-
-\textcolor{blue}{Alden for Siva: I need to follow up on whether we have handled the "discontinuous" density case correctly or not.}
-
-\subsection{Recovery of well-conditioned density clusters}
-\label{subsec:recovery_well-conditioned_density_clusters}
-
-Our goal is therefore to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
-We have already derived upper bounds on the volume of the symmetric set difference which that on some population-level functionals of the candidate cluster.
-What remains is to analyze these functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
-To carry out this analysis, we will need to impose some conditions, and for the rest of this subsection we will assume the following.
+\\
+
+\textcolor{red}{(TODO): Follow the advice of Siva, don't irritate Ingo.}\\
+
+In summary, our goal is to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
+We have already derived upper bounds on the volume of the symmetric set difference that depend on some population-level functionals of the candidate cluster.
+What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
+To carry out this analysis, we will need to impose some conditions, and for the rest of this section we will assume the following.
 
@@
 \begin{itemize}
-	\item We prove Proposition~\ref{prop:density_cluster_normalized_cut} by separately upper bounding $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma}, \mc{C}_{\lambda,\sigma}^c)$ and lower bounding the volume $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
+	\item We prove Proposition~\ref{prop:density_cluster_normalized_cut} by separately upper bounding $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ and lower bounding the volume $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
 Of these two bounds, the trickier to prove is the upper bound on the cut, which involves carefully estimating the probability mass of thin tubes around the boundary of $\mc{C}_{\lambda,\sigma}$.
@@
 \noindent Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$.
-In the following, $C_{1,\delta}$ and $C_{2,\delta}$ are constants which may depend only on $\delta$, but not $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$.
-
-\begin{corollary}
-	\label{cor:density_cluster_volume_ssd_ub}
-	Assume $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$, and that $0 < r \leq \sigma/4d$.
-For any $\delta \in (0,1)$, with probability at least $1 - 3\exp\{-b_1\delta^2 n\} - B_2n\exp\{-b_2\delta^2n\}$, the following statement holds: there exist constants $C_{1,\delta}$ and $C_{2,\delta}$, and a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+In what follows, $C_{1,\delta},C_{2,\delta},\ldots$ are constants which may depend on $\delta$, but not on $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$, and which we keep track of in our proofs.
+\begin{theorem}
+	\label{thm:density_cluster_volume_ssd_ub}
+	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
+Suppose that $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that $n$ satisfies~\eqref{eqn:volume_ssd_ub_sample_complexity}.
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
 	\label{eqn:density_cluster_volume_ssd_ub}
-	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}r}\biggr)
-	\end{equation}
-\end{corollary}
+	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
+	\end{equation}
+\end{theorem}
 Inequality~\eqref{eqn:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
@@
 \begin{itemize}
-	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Corollary~\ref{cor:density_cluster_volume_ssd_ub} through the conductance.
+	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} through the conductance.
 This reflects
@@
 It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
+	\item The symmetric set difference does not measure whether \smash{$\wh{C}$}
+	can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$}.
+In Appendix~\textcolor{red}{(?)}, we show in Theorem~\textcolor{red}{(?)} that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
 \end{itemize}
 
-\subsection{Negative result}
-\label{subsec:lower_bound}
+\section{Negative result}
+\label{sec:lower_bound}
 We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
@@
 \end{equation}
-In what follows, we put
-\begin{align*}
-C_{3,\delta} & := 768 \cdot (1 + 3\delta),&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
-C_{5,\delta} & := \frac{(1 + \delta)^2}{(1 - \delta)^2},&&C_{6,\delta} := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}.
-\end{align*}
+In the following Theorem, the samples $x_1,\ldots,x_n$ are drawn from the distribution $\Pbb$ with density $f$ given by~\eqref{eqn:lb_density}. \textcolor{red}{(TODO): Clean this up.}
 \begin{theorem}
@@
 
-%Note that for large enough $n$, $\vol_{n,r}(\mc{C}^{(1)}[X])$  will be close to $n^2 r^2/(\sigma\rho)$, and therefore the quantity \smash{$\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$} in \eqref{eqn:ppr_lb} is comparable to \smash{$\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) / \vol_{n,r}(\mc{C}^{(1)}[X])$}, which corresponds to the quantity we upper bound in Corollary~\ref{thm:volume_ssd_ub}.
-
-Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where
-the density clusters are rectangular subsets of $\Reals^2$.  We chose this
+We make a few remarks:
+\begin{itemize}
+	\item Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.  We chose this
 	setting to make the theorem simple to state, and our results are generalizable
-to $\Reals^d$ and to non-rectangular clusters.  Moreover, although we state
-our lower bound with respect to PPR run on a neighborhood graph, the conclusion is
-likely to hold for a much broader class of spectral clustering algorithms. In
-the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when
-$\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of
-$\mc{C}^{(1)}$ will be much larger than that of $\mathcal{L}$. In this case, not
-merely PPR but any algorithm that approximates the minimum normalized cut is
-unlikely to recover $\mc{C}^{(1)}$. In particular, local spectral clustering
+	to $\Reals^d$ and to non-rectangular clusters.
+
+	\item Although we state our lower bound with respect to PPR run on a neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mathcal{L}$.
+In this case, not merely PPR but any algorithm that approximates the minimum normalized cut is unlikely to recover $\mc{C}^{(1)}$.
+In particular, local spectral clustering
 	algorithms based on truncated random walks \citep{spielman2013}, global spectral
@@
 	\citep{hein2010} all have provable upper bounds on the normalized cut of cluster
-they output, and thus we expect that they would all fail to estimate
-$\mc{C}^{(1)}$.
-
-\paragraph{Comparison between upper and lower bounds.}
+	they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
+
+	\item Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
+	$\sigma$-expansions due to their sharp corners. To fix this, one can   
+	simply modify these sets to have appropriately rounded corners, and our lower
+	bound arguments do not need to change significantly, subject to some
+	additional bookkeeping.  Thus we ignore this technicality in our subsequent
+	discussion. 
+\end{itemize}
+
+\subsection{Comparison between upper and lower bounds}
+\label{subsec:comparison_upper_lower_bounds}
 
 To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
-results of our upper bound in Corollary~\ref{cor:density_cluster_volume_ssd_ub} to the density $f$ given in \eqref{eqn:lb_density}.
+results of our upper bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} to the density $f$ given in \eqref{eqn:lb_density}.
 Observe that $\mc{C}^{(1)}$ satisfies each of the Assumptions~\ref{asmp:lambda_bounded_density}--\ref{asmp:bounded_volume}:
@@
 
-\begin{remark}
-	Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
-	$\sigma$-expansions due to their sharp corners. To fix this, one can   
-	%either modify the upper bound (specifically, Lemma~\ref{lem: expansion_volume}
-	%in the proof of Theorem~\ref{thm: conductance_upper_bound}) to hold with
-	%respect to rectangles of width $\sigma$, or  
-	simply modify these sets to have appropriately rounded corners, and our lower
-	bound arguments do not need to change significantly, subject to some
-	additional bookkeeping.  Thus we ignore this technicality in our subsequent
-	discussion. 
-\end{remark}
-
-If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Corollary~\ref{cor:density_cluster_volume_ssd_ub}. This implies that 
+If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}. This implies that 
 there exists a set $\mc{C}^{(1)}[X] \subseteq \mc{C}^{(1)}$ with
@@
 \begin{equation*}
-\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 64 C_{1,\delta} \cdot \frac{\rho^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{r}\biggr)
+\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 32 C_{1,\delta} \cdot \frac{\rho^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
 \end{equation*}
 To facilitate comparisons between our upper
-and lower bounds, assume $\sigma/4 \leq \rho/40$ and set $r = \sigma/8$.  Then
+and lower bounds set $r = \sigma/8$.  Then
 the following statements each hold with high probability. 
@@
 	\begin{equation*}
-	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{64C_{1,\delta}} \left(\frac{\sigma}{\rho \log(\rho/\sigma \sqrt{C_{2,\delta}})}\right)^2,
+	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{256 C_{1,\delta}} \left(\frac{\sigma}{\rho \log(\rho/\sigma \sqrt{C_{2,\delta}})}\right)^2,
 	\end{equation*}
@@
 
-	\item If the user-specified parameters are as in Theorem~\ref{thm:ppr_lb}, and
+	\item The population-level volume $\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq (1 - \epsilon)/2 \cdot \pi r^2/(\rho\sigma)$, and
 	\begin{equation*}
-	\epsilon \geq \sqrt{\frac{C_4}{8}} \left({\frac{\sigma}{\rho}} \log^2 \left(\frac{\rho}
+	\vol_{n,r}(\mc{C}^{(1)}[X]) \leq (1 + \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C}^{(1)}). 
+	\end{equation*}
+	Therefore, if the user-specified parameters are as in Theorem~\ref{thm:ppr_lb}, and
+	\begin{equation*}
+	\epsilon \geq \sqrt{8 C_{6,\delta}} \left({\frac{\sigma}{\rho}} \log \left(64C_{4,\delta} \cdot \frac{\rho}
 	{\epsilon^2 \sigma}\right)\right)^{1/4},

### 2021-01-27 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
Editing pass over the main document complete.

@@
 \begin{keywords}
-	graphs, spectral clustering, density clustering, Personalized PageRank, unsupervised learning
+	graphs, spectral clustering, Personalized PageRank, density clustering, unsupervised learning
 \end{keywords}
@@
 
-Before giving a more detailed overview of our main results, we review some of the aforementioned worst-case guarantees, formally define PPR on a neighborhood graph, and introduce the population-level functionals that govern the behavior of local clustering in our statistical context.
+Before giving a more detailed overview of our main results, we formally define PPR on a neighborhood graph, review some of the aforementioned worst-case guarantees, and introduce the population-level functionals that govern the behavior of local clustering in our statistical context.
 
@@
 
-Once $p_v$ or $p_v^{(\varepsilon)}$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut of $p_v$.
+Once $p_v$ or $p_v^{(\varepsilon)}$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut.
 For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is
@@
 As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
-For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut of $\wh{C}$ is upper bounded $\Phi(\wh{C};G) \lesssim \sqrt{\Phi(C;G)}$.\footnote{We say $a \lesssim b$ when $a \leq $} \cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
+For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut $\Phi(\wh{C};G)$ is upper bounded by (a constant times)  $\sqrt{\Phi(C;G)}$.
+\cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
 \begin{equation}
@@
 unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in
-E$ if and only if $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
+E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
 Euclidean norm.
@@
 \subsection{Population normalized cut and conductance}
-Next we define two population-level functionals of $\mc{C}$, the normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$, which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
+Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
 Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e.
@@
 \begin{equation*}
-\mathrm{cut}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\mc{C}^c} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x)~~ \mathrm{vol}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\Rd} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),
+\mathrm{cut}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\mc{C}^c} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),~~ \mathrm{vol}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\Rd} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),
 \end{equation*}
-where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$.
+where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ to be the expected degree of $x$ in $G_{n,r}$. 
 \begin{definition}[Population normalized cut]
@@
 \end{definition}
+\begin{definition}[Population local spread]
+	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population local spread} is
+	\begin{equation}
+	\label{eqn:local_spread}
+	s_{\Pbb,r}(\mc{C}) := \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
+	\end{equation}
+\end{definition}
 
@@
 We will comment more on the relationship between these works and our own results in Section~\ref{subsec:related_work}.
-\\
-
-\textcolor{red}{(TODO): Possibly add a section here \emph{giving}---rather than summarizing---our main results.}
-
-\subsection{Summary of results}
-A summary of our results (and an outline for this paper) is as follows.
-\begin{itemize}
-	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that under certain conditions the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
-As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a nonparametric statistical context.
-\end{itemize}
-In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$---an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}.
-\begin{itemize}
-	\item In Section~\ref{subsec:recovery_well-conditioned_density_clusters}, we derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
-These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
-	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
-\end{itemize}
-In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
+
+The role played by $s_{\Pbb,r}(\mc{C})$ is somewhat less obvious.
+For now, we mention only that it plays an essential role in obtaining tight bounds on the mixing time of a particular random walk that can be related to the PPR vector, and defer further discussion until later, in Section~\ref{sec:ub_symmetric_set_difference}.
+
+\subsection{Main Results}
+We now informally state our two main upper bounds, regarding the recovery of a generic cluster $\mc{C}$, and a density cluster $\mc{C}_{\lambda}$.
+Theorem~\ref{thm:volume_ssd_ub_informal} informally summarizes the first of our main results, formally stated in Theorem~\ref{thm:volume_ssd_ub}, regarding the recovery of a generic cluster $\mc{C}$, .
+\begin{theorem}[Informal]
+	\label{thm:volume_ssd_ub_informal}
+	Let $\mc{C} \subset \Rd$ and $\Pbb$ satisfy appropriate regularity conditions, and suppose Algorithm~\ref{alg:ppr} is well-initialized with respect to $\mc{C}$.
+For all $n \in \mathbb{N}$ sufficiently large, with high probability it holds that
+	\begin{equation*}
+	\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq c \cdot\Phi_{\Pbb,r}(\mc{C}) \cdot  \biggl(\frac{\log(1/s_{\Pbb,r}(\mc{C}))}{\Psi_{\Pbb,r}(\mc{C})}\biggr)^2.
+	\end{equation*}
+\end{theorem}
+(In the above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put even more succinctly, we find that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$ (ignoring $\log$ factors).
+To the best of our knowledge, this gives the first population-level guarantees for local clustering in the nonparametric statistical context.
+
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results, formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}, regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
+For reasons that we explain later, in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
+The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under an Lipschitz, Lebesgue-measure-preserving mapping $g$, with Lipschitz constant $L$.
+We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
+\begin{equation*}
+0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\textrm{for all $x \in \mc{C}_{\lambda,\sigma}$}
+\end{equation*}
+while satisfying the low-noise condition 
+\begin{equation*}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $\dist(x,\mc{C}_{\lambda,\sigma}) \leq r$.}
+\end{equation*}
+(Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.) 
+\begin{theorem}[Informal]
+	\label{thm:density_cluster_volume_ssd_ub_informal}
+	Let $\mc{C}_{\lambda} \subset \Rd$ be a $\lambda$-density cluster of a distribution $\Pbb$ that satisfies appropriate regularity conditions, and suppose Algorithm~\ref{alg:ppr} is well-initialized with respect to $\mc{C}_{\lambda,\sigma}$.
+For all $n \in \mathbb{N}$ sufficiently large, with high probability it holds that
+	\begin{equation}
+	\label{eqn:density_cluster_volume_ssd_ub_informal}
+	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
+	\end{equation}
+\end{theorem}
+Equation~\eqref{eqn:density_cluster_volume_ssd_ub_informal} reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
+The parameters $L$, $\rho$ and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
+Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$ and $\theta$ measure whether $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside the density cluster) or poorly conditioned (vice versa).
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is well-conditioned---i.e.
+$L^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
+$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $(\lambda - \theta r^{\gamma}/(\gamma + 1)) \ll \lambda$---then PPR will approximately recover the (thickened) density cluster.
 
@@
 \label{subsec:related_work}
-We conclude this section by summarizing some related work (in addition to the background already given above).
-
-\paragraph{Spectral clustering.}In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+We now summarize some related work (in addition to the background already given above), regarding the theory of spectral clustering, and of density cluster recovery.
+
+\paragraph{Spectral clustering.}
+In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
 In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating
@@
 However, they remain silent on the following natural question: do the spectra of these continuum operators induce a partition of the sample space which is ``good'' in some sense?
-\citet{shi2009,schiebinger2015,garciatrillos19} address this question, showing that spectral algorithms will recover the latent labels in certain well-conditioned nonparametric mixture models.
+\citet{shi2009,schiebinger2015,garciatrillos19,hoffmann2019} address this question, showing that spectral algorithms will recover the latent labels in certain well-conditioned nonparametric mixture models.
 These works are probably the most similar to our own: the conditioning of these mixture models depend on population-level functionals resembling the population-level normalized cut and conductance introduced above, and the resulting bounds on the error of spectral clustering are comparable to those we establish in Theorem~\ref{thm:volume_ssd_ub}.
@@
 
-\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) > \lambda\}$.
+\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
 In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
-By now, density clustering (and the related problem of level-set estimation) are relatively well-understood.
-\citet{polonik1995,rigollet2009} study density clustering under the symmetric set difference
-metric, \citet{tsybakov1997,singh2009} describe minimax optimal level-set
-estimators under Hausdorff loss and
-\citet{hartigan1981,chaudhuri2010,balakrishnan2013,kpotufe11} consider
-consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$. \textcolor{red}{Add, at a minimum, references to Larry + Ale and Ingo's papers.}
+By now, density clustering (and the related problem of level-set estimation) are quite well-understood.
+For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference
+metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and
+\citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider
+consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
 
 We emphasize that our goal is
-not to improve on these results, nor to offer a better algorithm for level set
-estimation, but rather to better understand the implications of our general theory by applying it within an already well-studied framework.
-Indeed, seen as a density clustering algorithm, PPR has none
+not to improve on these results, nor to offer a better algorithm for density clustering. Indeed, seen as a density clustering algorithm, PPR has none 
 of the optimality guarantees found in the aforementioned works.
+Rather, we hope to better understand the implications of our general theory by applying it within an already well-studied framework.
 We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
+
+\subsection{Organization}
+We now outline the rest of the paper.
+\begin{itemize}
+	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that under certain conditions the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
+As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a nonparametric statistical context.
+	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$---an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}.
+We derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
+These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
+	\item In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
+\end{itemize}
+
+\textcolor{red}{(TODO): Edit this, based on whether or not the Main Results section passes muster. }
 
@@
 Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.
-Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.
+Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mathbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.
 
@@
 \end{equation}
-where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $G_{n,r}\bigl[\mc{C}[X]\bigr]$.
+where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $G_{n,r}\bigl[\mc{C}[X]\bigr]$ (normalized by a factor of $1/(n - 1)$.)
 
@@
 \begin{enumerate}[label=(A\arabic*)]
-	\item 
-	\label{asmp:domain} 
-	The candidate cluster $\mc{C} \subseteq \Rd$ for $d \geq 2$, is a bounded, connected, open set with Lipschitz boundary. 
 	\item 
@@
 	\end{equation*}
+	\item 
+	\label{asmp:domain} 
+	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set. If $d \geq 2$ then it has a Lipschitz boundary. 
 \end{enumerate}
-In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to constants that may depend on $\Pbb$ and $\mc{C}$, but do not depend on $n$ or $\delta$.
+In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$,$\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
 We explicitly keep track of all constants in our proofs.
@@
 	Fix $\delta \in (0,1/3)$.
-Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
 There exist positive constants $b_1$ and $b_2$ such that each of the following statements hold.
@@
 		\end{equation}
-		\item With probability at least $1 - (n + 2)\exp\{-b_2\delta^2n\}$,
+		\item For any $n \in \mathbb{N}$ for which 
+		\begin{equation}
+		\label{eqn:sample_to_population_local_spread_sample_complexity}
+		\frac{1}{n} \leq \delta \cdot \frac{2\Pbb(\mc{C})}{3}
+		\end{equation}
+		the following inequality holds with probability at least \smash{$1 - (n + 2)\exp\{-b_2\delta^2n\}$}:
 		\begin{equation}
 		\label{eqn:sample_to_population_local_spread}
-		s_{n,r}(\mc{C}[X]) \geq (1 - 3\delta) s_{\Pbb,r}(\mc{C}).
+		s_{n,r}(\mc{C}[X]) \geq (1 - 4\delta) s_{\Pbb,r}(\mc{C}).
 		\end{equation}
@@
 \end{proposition}
-Let $p_d := 3/4$ if $d = 2$, and else $p_d := 1/d$ for $d \geq 3$. 
+Let $p_d := 1/2$ if $d = 1$, $p_d := 3/4$ if $d = 2$, and otherwise $p_d := 1/d$ for $d \geq 3$. 
 \begin{proposition}
@@
 	Fix $\delta \in (0,1/2)$.
-Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+Suppose  $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
 Then there exist positive constants $B_1$,$B_2$, and $b_3$ such that for any $n \in \mathbb{N}$ for which
@@
 	\label{eqn:sample_to_population_conductance_sample_complexity}
-	\frac{(\log n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,
-	\end{equation}
-	the following inequality holds with probability at least $1 - B_2/n - (n + 2)\exp\{-b_3n\}$:
+	\frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \delta \cdot B_1,
+	\end{equation}
+	the following inequality holds with probability at least $1 - B_2/n - (n + 1)\exp\{-b_3n\}$:
 	\begin{equation}
@@
 Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$.
-For further details, we refer to Appendix~\textcolor{red}{(?)}, where we prove~\eqref{eqn:sample_to_population_conductance}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance.
+For further details, we refer to Appendix~\textcolor{red}{(?)}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance.
 
@@
 \label{eqn:alpha_initialization}
-\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 3\delta)s_{\Pbb,r}(\mc{C})}\Bigr)} 
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)} 
 \end{equation}
@@
 	\label{thm:volume_ssd_ub} 
-	Let $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, and suppose that
+	Fix $\delta \in (0,1/4)$.
+Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
+Then there exists a positive constant $B_3$ such that for any $n \in \mathbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
 	\begin{equation}
 	\label{eqn:volume_ssd_ub_sample_complexity}
-	\frac{(\log n)^{p_d}}{n^{1/d}} \leq \delta \cdot B_1,~~\textrm{and}~~\frac{(1 + \delta)}{(1 - \delta)^3} \cdot B_3 \leq n.
-	\end{equation} 
-	With probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	\frac{(1 + \delta)}{(1 - \delta)^4} \cdot B_3 \leq n,
+	\end{equation} 
+	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 \end{theorem}
-To summarize: if PPR is well-initialized within a candidate cluster $\mc{C}$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ is upper bounded by the following function of the population-level functionals:
-\begin{equation*}
-\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \lesssim \Phi_{\Pbb,r}(\mc{C})  \cdot \frac{\log^2\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)}{\Psi^2_{\Pbb,r}(\mc{C})}.
-\end{equation*}
-We now make some other remarks:
+% The following lines are commented out, because they are superseded by the informal statement of our theorem above.
+%
+% To summarize: if PPR is well-initialized within a candidate cluster $\mc{C}$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ is upper bounded by the following function of the population-level functionals:
+% \begin{equation*}
+% \frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \lesssim \Phi_{\Pbb,r}(\mc{C})  % \cdot \frac{\log^2\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)}{\Psi^2_{\Pbb,r}(\mc{C})}.
+% \end{equation*}
+%
+
+We now make some remarks:
 \begin{itemize}
@@
 Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}.
-\\
-	\textcolor{red}{(TODO): Add a comment explaining why we get different bounds.}
 
@@
 	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
-We formally state and proof this result in our appendix (Corollary~\textcolor{red}{(?)}).
+We formally state and prove this result in our appendix (Corollary~\textcolor{red}{(?)}).
 \end{itemize}
@@
 We also derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
-Together, these results can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if $\mc{C}_{\lambda}$ is \emph{well-conditioned}, both geometrically---meaning it is not too long and thin--- and vertically---meaning $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near its boundary.
+Together, these results can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if both $\mc{C}_{\lambda}$ and $f$ are well-conditioned, meaning that $\mc{C}_{\lambda}$ is not too long and thin, and that $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near its boundary.
 
@@
 All results on density clustering assume the density $f$ satisfies some regularity conditions.
-A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus cannot be resolved by any finite number of samples.
-This requirement can be enforced in several different ways: for instance, many of the aforementioned works assume that the density $f$ is continuous, while~\cite{rinaldo2010} allow for discontinuous $f$ by defining the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to the lower semi-continuous version of $f$.
-We instead choose to follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) \leq \sigma\}$ for some $\sigma > 0$.
-(Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.) The set $\mc{C}_{\lambda,\sigma}$ is full dimensional with a smooth boundary, and thus no continuity assumption on $f$ is required.
-\\
-
-\textcolor{red}{(TODO): Follow the advice of Siva, don't irritate Ingo.}\\
+A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus may not be resolved by any finite number of samples.
+To rule out such problematic clusters, we follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) < \sigma\}$ for a given $\sigma > 0$.
+The point is that regardless of the dimension of $\mc{C}_{\lambda}$, the set $\mc{C}_{\lambda,\sigma}$ is full dimensional.
+Under typical uniform continuity conditions, the requirement that the density be lower bounded over $\mc{C}_{\lambda,\sigma}$ will be satisfied.
+We note that such continuity conditions can be weakened---for instance,~\cite{rinaldo2010} define the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to the lower semi-continuous version of $f$---but do not pursue the matter further.
 
@@
 
-\emph{For convenience only}, we will also make the following assumption, 
+\emph{For convenience only}, we will also make the following assumption.
 \begin{enumerate}[label=(A\arabic*)]
@@
 	$$
-	Roughly, this assumption ensures that with high probability $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]) \leq (1 + \delta) \cdot \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^c)$, and thus $\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X]) \leq (1 + \delta) \cdot \cut_{n,r}(\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$.
+	This assumption implies that the normalized cut of $\mc{C}_{\lambda,\sigma}$ will be equal to the ratio of $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ to $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
 \end{enumerate}
@@
 	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
-Suppose that $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that $n$ satisfies~\eqref{eqn:volume_ssd_ub_sample_complexity}.
-Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+Suppose that $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 \end{theorem}
-Inequality~\eqref{eqn:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-For instance, if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is both geometrically well-conditioned---i.e.
-$L^2\rho^2/(\sigma r) \approx 1$---and vertically well-conditioned---i.e.
-$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $(\lambda - \theta r^{\gamma}/(\gamma + 1)) \ll \lambda$---then PPR will approximately recover it.
-Some other remarks:
+As we have previously summarized, Theorem~\ref{thm:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
+Now, we make some other remarks:
 \begin{itemize}
@@
 The resulting procedures come with stronger density cluster recovery guarantees.
-However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, with spectral clustering functioning as more of a post-processing step.
+However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, and spectral clustering functions as more of a post-processing step.
 These methods are thus very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
@@
 
-\paragraph{Lower bound on symmetric set difference.}
+\subsection{Lower bound on symmetric set difference}
 As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
@@
 \end{equation}
-In the following Theorem, the samples $x_1,\ldots,x_n$ are drawn from the distribution $\Pbb$ with density $f$ given by~\eqref{eqn:lb_density}. \textcolor{red}{(TODO): Clean this up.}
+
+In the following Theorem, $B_{1,\delta}$ and $B_{2,\delta}$ are constants which may depend on $\delta,\Pbb,\mc{C}_{\lambda,\sigma}$ and $r$, but not on $n$.
 \begin{theorem}
@@
 	\label{eqn:ppr_lb_condition}
-	\max\biggl\{C_{3,\delta} \cdot \frac{r}{\rho} \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr), \frac{C_{5,\delta}}{n} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq \frac{6 \sigma \rho (1 + \delta)}{(\sigma - 2r)(\rho - r) (1 - \delta)},
+	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
 	\end{equation} 
@@
 	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.
-Then the following statement holds with probability at least $1 - B_3 \exp\set{- \delta^2 b_4 n/(3 + \delta)} - n \exp\{-\delta^2 b_5 n/(3 + \delta)\}$: there exists a set $\mc{C}[X]^g$ of large volume, \\ \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
-		\mc{C}^{(1)}[X]) \geq 6\vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/49$}, such
+Then the following statement holds with probability at least $1 - (B_5 + 2n + 10)\exp\{-n\delta^2 b_6\}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
+		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/8$}, such
 	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
@@
 	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
-	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{6,\delta} \cdot 
+	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot 
 	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}
@@
 \end{theorem}
-
-\textcolor{red}{(TODO): Check that the assumptions of the Theorem match those used in the proof.}
-
-We make a few remarks:
+We make a couple of remarks:
 \begin{itemize}
@@
 	setting to make the theorem simple to state, and our results are generalizable
-	to $\Reals^d$ and to non-rectangular clusters.
+	to $\Reals^d$ and to non-rectangular clusters. Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
+	$\sigma$-expansions due to their sharp corners. To fix this, one can   
+	simply modify these sets to have appropriately rounded corners, and our lower
+	bound arguments do not need to change significantly, subject to some
+	additional bookkeeping.  Thus we ignore this technicality in our subsequent
+	discussion.
 
@@
 	they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
-
-	\item Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
-	$\sigma$-expansions due to their sharp corners. To fix this, one can   
-	simply modify these sets to have appropriately rounded corners, and our lower
-	bound arguments do not need to change significantly, subject to some
-	additional bookkeeping.  Thus we ignore this technicality in our subsequent
-	discussion. 
 \end{itemize}
@@
 \begin{itemize}
-	\item If the user-specified parameters satisfy~\eqref{eqn:initialization}, and
+	\item If the user-specified parameters satisfy~\eqref{eqn:initialization}, and for some $a \geq 0$,
 	\begin{equation*}
@@
 Jointly, these upper and lower bounds give a relatively precise characterization
-of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.
-
-\begin{remark}
-	It is worth pointing out that the above conclusions are reliant on specific
+of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR. \footnote{It is worth pointing out that the above conclusions are reliant on specific
 (albeit reasonable) ranges and choices of input parameters, which in some
@@
 bound continues to hold even when choosing input parameters as dictated by our
-	upper bound, but do not pursue the details.
-\end{remark}
-
-Finally, it is not hard to show that in the example under consideration, classical
+upper bound, but do not pursue the details.}
+
+Of course, it is not hard to show that in the example under consideration, classical
 plug-in density cluster estimators can consistently recover the
@@
 
-We provide numerical experiments to investigate the tightness of our theoretical results in Section~\ref{sec:ppr_density_cluster}, and examine the performance of PPR on the ``two moons'' dataset.
+We provide numerical experiments to investigate the tightness of our theoretical results in Section~\ref{sec:ppr_density_cluster}, and compare the performance of PPR with a density clustering algorithm on the ``two moons'' dataset.
 We defer details of the experimental settings to the appendix.
 
-\paragraph{Validating theoretical bounds.}
-We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance} via simulation.
+\subsection{Validating theoretical bounds}
+We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e.
+the bounds on core graph functionals needed for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
 Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities.
 In the first row we vary the diameter $\rho$ of the candidate cluster, in the second row we vary the thickness $\sigma$ of the candidate cluster, and in the last row we vary the magnitude $\theta$ of the density drop.
-In each case, we see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude or less.
-The looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
-Nevertheless, for sufficiently well-conditioned enough densities our upper bound will be $\ll 1$; for instance, when $\sigma = \textcolor{red}{(?)}$, $\rho = \textcolor{red}{(?)}$ and $\theta = \textcolor{red}{(?)}$.\\
-
-\textcolor{red}{Alden for Ryan: the last couple of sentences are an attempt at what we discussed in our meeting. I am not satisfied with it, but could not do better.}
+In each case, it is encouraging to see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude or less.
+On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
 
@@
 
-\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:moons}, to drive home 
+\subsection{Empirical behavior of PPR} 
+In Figure \ref{fig:moons}, to drive home 
 the implications of Section~\ref{sec:ppr_density_cluster}, we show the behavior of PPR,
-normalized cut, and the density clustering algorithm of \citet{chaudhuri2010} on
+as compared with the density clustering algorithm of \citet{chaudhuri2010} on
 the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
-a prototypical success story for spectral clustering algorithms. The first
-column shows the empirical density clusters $\mc{C}[X]$ and $\mc{C}'[X]$ for
+a prototypical success story for spectral clustering algorithms.
+We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
+The first
+column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for
 a particular threshold $\lambda$ of the density function; the second column
 shows the cluster recovered by PPR; the third column shows the global minimum
-normalized cut, computed according to the algorithm of \citet{szlam2010}; and
+normalized cut, computed according to the algorithm of \citet{bresson2013}; and
 the last column shows a cut of the density cluster tree estimator of
@@
 We have shown how PPR depends on the distribution $\Pbb$ through the population-level normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
-In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if it is geometrically and vertically well-conditioned.
-We now conclude by summarizing several interesting directions for future work.
+In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if both the density cluster and density are well-conditioned.
+We now conclude by summarizing a couple of interesting directions for future work.
 
@@
 It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR.
-Although most results thus far derive bounds on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
+Although most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
 It is not clear whether the techniques used in these works can be applied to PPR.
-
-Finally, after reading our Section~\ref{sec:ppr_density_cluster}, the practitioner may be tempted to ask why they should estimate a density cluster using PPR, when other methods are available with superior statistical guarantees.
-A undoubtedly correct, if perhaps unsatisfying, answer is that the ``ideal'' cluster is entirely in the eye of the beholder.
-For instance, it is quite common to define an ideal cluster as one with a small normalized cut, in which case the cluster output by PPR may be quite preferable to standard density clustering procedures.
-On the other hand, it would also be interesting to know whether a (local) spectral method such as PPR converges more rapidly (as a function of $n$) than standard density clustering procedures.
-Such a question could be answered by comparing the sample complexity of spectral clustering methods with that of density clustering procedures, but to our knowledge, the sample complexity of spectral methods remains unknown.
 

### 2021-01-27 jmlr/revision/proofs.tex
Editing pass over the main document complete.

@@
 	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
-	\item \textbf{Sample-to-population results.} For the specific choice of $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. This proves~\textcolor{red}{(?)} 
-	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\textcolor{red}{(?)}.
-This proves~\textcolor{red}{(?)}
+	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. 
+	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
 \end{enumerate}
 The first three sections of this appendix will correspond to each of these three parts.
-In Section~\ref{sec:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, \textcolor{red}{(...)}.
-Finally, in Section~\ref{sec:appr_misclassification_error} we derive upper bounds for the aPPR vector, and in Section~\ref{sec:experimental_details} we give relevant details regarding our experiments.
+In Section~\ref{sec:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, Theorems~\ref{thm:volume_ssd_ub} and~\ref{thm:density_cluster_volume_ssd_ub}, as well as our negative result, Theorem~\ref{thm:ppr_lb}.
+In Section~\ref{sec:appr_misclassification_error} we derive upper bounds for the aPPR vector, and show that under certain conditions the PPR vector can perfectly separate two density clusters.
+Finally, in Section~\ref{sec:experimental_details} we give relevant details regarding our experiments.
 
@@
 
-\paragraph{Organization.} In the following subsections we establish: (\ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (\ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (\ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (\ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (\ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
+\paragraph{Organization.} In the following sections we establish: (Section \ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (Section \ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (Section \ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (Section \ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (Section \ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
 
@@
 	\end{equation*}
-	Taking maximum over all $v \in V$, we conclude that $\tau_{\infty}(G) \leq \tau_{\ast} + 1$, which is exactly the claim of Proposition~\ref{prop:pointwise_mixing_time}.
+	Taking maximum over all $v \in V$, we conclude that $\tau_{\infty}(G) \leq \tau_{\ast} + 1$, which implies the claim of Proposition~\ref{prop:pointwise_mixing_time}.
 
@@
 \label{subsec:ppr_spectral_partitioning}
-The following theorem is the main result of~\ref{subsec:ppr_spectral_partitioning}.
+The following theorem is the main result of Section~\ref{subsec:ppr_spectral_partitioning}.
 It relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of a candidate cluster $C \subseteq V$, when $p_v$ is properly initialized within $C$.
@@
 \label{subsec:concentration}
-We use Hoeffding's inequality to control the deviations of the empirical measure of $\mc{S}$.
-\begin{lemma}[Hoeffding's Inequality.]
+We use Bernstein's inequality to control the deviations of the empirical probability of $\mc{S}$.
+\begin{lemma}[Bernstein's Inequality.]
 	\label{lem:hoeffding_2}
-	Fix $\delta \in (0,1)$. For any measurable $\mc{S} \subseteq \Rd$,
-	\begin{equation*}
-	(1 - \delta) \Pbb(\mathcal{S}) \leq \Pbb_n(\mathcal{S}) \leq (1 + \delta)\Pbb(\mathcal{S})
-	\end{equation*}
-	with probability at least $1 - 2\exp\set{-2\delta^2(\Pbb(\mathcal{S}))^2n}$. 
+	Fix $\delta \in (0,1)$. For any measurable $\mc{S} \subseteq \Rd$, each of the inequalities,
+	\begin{equation*}
+	(1 - \delta) \Pbb(\mathcal{S}) \leq \Pbb_n(\mathcal{S})~~\textrm{and}~~\Pbb_n(\mathcal{S}) \leq (1 + \delta)\Pbb(\mathcal{S}),
+	\end{equation*}
+	hold with probability at least $1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/(2 + 2\delta)} \leq 1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/4}$. 
 \end{lemma}
 
-Many graph functionals are order-2 U-statistics, and we use Hoeffding's inequality to control the deviations of these functionals from their expectations.
+Many graph functionals are order-2 U-statistics, and we use Bernstein's inequality to control the deviations of these functionals from their expectations.
 Recall that $U_n$ is an order-2 U-statistic with kernel $\varphi: \Rd \times \Rd \to \Reals$ if
@@
 We write $\norm{\varphi}_{\infty} = \sup_{x,y} |\varphi(x,y)|$. 
-\begin{lemma}[Hoeffding's Inequality for Order-2 U-statistics.]
+\begin{lemma}[Bernstein's Inequality for Order-2 U-statistics.]
 	\label{lem:hoeffding}
-	Fix $\delta \in (0,1)$. Assume $\norm{\varphi}_{\infty} \leq 1$. Then,
-	\begin{equation*}
-	(1 - \delta) \mathbb{E}[U_n] \leq U_n \leq (1 + \delta) \mathbb{E}[U_n]
-	\end{equation*}
-	with probability at least $1 - 2 \exp\left(-\delta^2 (\mathbb{E}[U_n])^2 n\right)$.
+	Fix $\delta \in (0,1)$. Assume $\norm{\varphi}_{\infty} \leq 1$. Then each of the inequalities,
+	\begin{equation*}
+	(1 - \delta) \mathbb{E}U_n \leq U_n~~\textrm{and}~~ U_n\leq (1 + \delta) \mathbb{E}U_n,
+	\end{equation*}
+	hold with probability at least $1 - \exp\{-n\delta^2 \Ebb U_n/(4 + 4\delta/3)\} \leq 1 - \exp\{-n\delta^2 \Ebb U_n/6\}$.
 \end{lemma}
@@
 	\label{lem:bernstein_union}
-	Fix $\delta \in (0,1)$. For any measurable $\mathcal{S}_1,\ldots,\mathcal{S}_M \subseteq \Rd$, 
-	\begin{equation*}
-	(1 - \delta) p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M}  \Pbb_n(\mathcal{A}_m) \leq (1 + \delta) p_{\max}
-	\end{equation*}
-	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.  
+	Fix $\delta \in (0,1)$. For any measurable $\mathcal{S}_1,\ldots,\mathcal{S}_M \subseteq \Rd$, each of the inequalities
+	\begin{equation*}
+	(1 - \delta) p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m),~~\textrm{and}~~\max_{m = 1,\ldots,M}  \Pbb_n(\mathcal{A}_m) \leq (1 + \delta) p_{\max}
+	\end{equation*}
+	hold with probability at least $1 - M \exp \{-n\delta^2p_{\min}/(2 + 2\delta) \} \geq 1 - M \exp\{-n\delta^2p_{\min}/4\}$.  
 \end{lemma}
@@
 \end{align*}
-Therefore with probability at least $1 - \exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{S}))^2\}$,
+Therefore with probability at least $1 - \exp\{-n\delta^2\cut_{\Pbb,r}(\mc{S})/4\}$,
 \begin{equation*}
@@
 \end{equation*}
-and likewise with probability at least $1 - \exp\{-\delta^2 (\vol_{\Pbb,r}(\mc{S}))^2\}$,
-\begin{equation*}
-(1 - \delta) \vol_{\Pbb,r}(\mc{S}) \leq \frac{1}{n(n - 1)} \vol_{n,r}(\mc{S}[X]).
+and likewise with probability at least $1 - \exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{S})/4\} - \exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{S}^c)/4\}$,
+\begin{equation*}
+(1 - \delta) \vol_{\Pbb,r}(\mc{S}) \leq \frac{1}{n(n - 1)} \vol_{n,r}(\mc{S}[X]),~~\textrm{and}~~(1 - \delta) \vol_{\Pbb,r}(\mc{S}^c) \leq \frac{1}{n(n - 1)} \vol_{n,r}(\mc{S}^c[X])
 \end{equation*}
@@
 \end{equation*}
-with probability at least $1 - 3\exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{C}))^2\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 := (\cut_{\Pbb,r}(\mc{C}))^2$.
+with probability at least $1 - 3\exp\{-n \delta^2 \cut_{\Pbb,r}(\mc{C})/4\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 := 3\cut_{\Pbb,r}(\mc{C})/4$.
 
@@
 \label{subsec:sample_to_population_local_spread}
-In this subsection we establish~\eqref{eqn:sample_to_population_local_spread}.
-To ease the notational burden, let $\wt{G}_{n,r} := G_{n,r}\bigl[\mc{C}[X]\bigr]$.
-By Lemma~\ref{lem:hoeffding_2}, with probability at least $1 - \exp\{-2\delta^2 (\Pbb(\mc{C}))^2n\}$
+In this subsection we establish~\eqref{eqn:sample_to_population_local_spread}. To ease the notational burden, let $\wt{G}_{n,r} := G_{n,r}\bigl[\mc{C}[X]\bigr]$. 
+Conditional on~$\wt{n}$, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 - \wt{n}\exp\{-(\wt{n} - 1) \delta^2d_{\min}(\wt{\Pbb})/4\}$,
+\begin{equation}
+\label{pf:sample_to_population_local_spread_2}
+(1 - \delta) \cdot d_{\min}(\wt{\Pbb}) \leq \frac{1}{\wt{n} - 1} d_{\min}(\wt{G}_{n,r}),
+\end{equation}
+Likewise it follows from Lemma~\ref{lem:hoeffding} that with probability at least $1 - \exp\{-\wt{n}\delta^2 \vol_{\wt{\Pbb},r}(\mc{C})/6\}$,
+\begin{equation*}
+(1 - \delta) \cdot \vol_{\wt{\Pbb},r}(\mc{C}) \leq \frac{1}{\wt{n}(\wt{n} - 1)} \vol(\wt{G}_{n,r}).
+\end{equation*}
+Finally, it follows from Lemma~\ref{lem:hoeffding_2} that with probability at least $1 - \exp\{-n\delta^2 \Pbb(\mc{C})/4\}$
 \begin{equation}
 \label{pf:sample_to_population_local_spread_1}
-\wt{n} \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}).
-\end{equation}
-Conditional on~\eqref{pf:sample_to_population_local_spread_1}, it follows from Lemma~\ref{lem:bernstein_union} that with probability at least $1 -n\exp\{-\delta^2d_{\min}(\wt{\Pbb}) \cdot (1 - \delta) \Pbb(\mc{C}) n/(3 + \delta)\}$,
-\begin{equation}
-\label{pf:sample_to_population_local_spread_2}
-\frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq (1 - \delta) \cdot d_{\min}(\wt{\Pbb}),
-\end{equation}
-and likewise it follows from Lemma~\ref{lem:hoeffding} that with probability at least $1 - \exp\{-\delta^2(\vol_{\wt{\Pbb},r}(\mc{C}))^2 \cdot (1 - \delta) \Pbb(\mc{C}) n \}$,
-\begin{equation*}
-\frac{1}{\wt{n}(\wt{n} - 1)} \vol(\wt{G}_{n,r}) \geq (1 - \delta) \cdot \vol_{\wt{\Pbb},r}(\mc{C}).
-\end{equation*}
-Consequently for any $\delta \in (0,1/3)$,
-\begin{equation*}
-s_{n,r}(\mc{C}[X]) = \frac{d_{\min}(\wt{G}_{n,r})^2}{\vol(\wt{G}_{n,r})} \geq \frac{\frac{1}{\wt{n}^2}d_{\min}(\wt{G}_{n,r})^2}{\frac{1}{\wt{n}(\wt{n} - 1)}\vol(\wt{G}_{n,r})} \geq \frac{(1 - \delta)^2}{(1 + \delta)} \cdot  \frac{d_{\min}(\wt{\Pbb})^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{C}).
-\end{equation*}
-with probability at least $1 - \exp\{-2\delta^2 (\Pbb(\mc{C}))^2n\} - \exp\bigl\{-2\delta^2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})n/3\bigr\} - n\exp\bigl\{-\delta^2 d_{\min}(\wt{\Pbb}) \cdot \Pbb(\mc{C}) n/5\bigr\}$.
-This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 := (\Pbb(\mc{C}))^2 \wedge 2\bigl(\vol_{\wt{\Pbb},r}(\mc{C})\bigr)^2 \Pbb(\mc{C})/3 \wedge d_{\min}(\wt{\Pbb}) \cdot \Pbb(\mc{C})/5$.
+\wt{n} \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}),
+\end{equation}
+and therefore by~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, $(\wt{n} - 1)/\wt{n} \geq 1 - \delta$. Consequently for any $\delta \in (0,1/3)$,
+\begin{equation*}
+s_{n,r}(\mc{C}[X]) = \frac{d_{\min}(\wt{G}_{n,r})^2}{\vol(\wt{G}_{n,r})} = \frac{\wt{n} - 1}{\wt{n}} \cdot \frac{\frac{1}{(\wt{n} - 1)^2}d_{\min}(\wt{G}_{n,r})^2}{\frac{1}{\wt{n}(\wt{n} - 1)}\vol(\wt{G}_{n,r})} \geq \frac{(1 - \delta)^3}{(1 + \delta)} \cdot  \frac{d_{\min}(\wt{\Pbb})^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \geq (1 - 4\delta) \cdot s_{\Pbb,r}(\mc{C}).
+\end{equation*}
+with probability at least $1 - n\exp\{-n\Pbb(\mc{C}) \cdot \delta^2d_{\min}(\wt{\Pbb})/9\} - \exp\{-n\Pbb(\mc{C})\delta^2 \cdot \vol_{\wt{\Pbb},r}(\mc{C})/14\} - \exp\{-n\delta^2 \Pbb(\mc{C})/4\}$.
+This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 := \Pbb(\mc{C}) \cdot d_{\min}(\wt{\Pbb})/14$.
+
+% AJG: To get the ``with high probability'' statement, I
+%   (i) Used {eqn:sample_to_population_local_spread_sample_complexity} to deduce that \wt{n} - 1 \geq (1 - \delta)^2 \Pbb(\mc{C}) n;
+%   (ii) replaced (1 - \delta) terms by factors of 2/3.
 
@@
 
-In this subsection we establish~\eqref{eqn:sample_to_population_conductance}.
+In this section we establish~\eqref{eqn:sample_to_population_conductance}.
 As mentioned in our main text, the proof of~\eqref{eqn:sample_to_population_conductance} relies on a high-probability upper bound of the $\infty$-transportation distance between $\mbb{P}$ and $\mbb{P}_n$, from~\citep{garciatrillos16b}.
-We begin by reviewing this upper bound, in Theorem~\ref{thm:garciatrillos16}.
+We begin by reviewing this upper bound, which we restate in Theorem~\ref{thm:garciatrillos16}.
 Subsequently in Proposition~\ref{prop:conductance_lb_transportation_distance}, we relate the $\infty$-transportation distance between two measures $\mbb{Q}_1$ and $\mbb{Q}_2$ to the difference of their conductances.
@@
 \paragraph{$\infty$-transportation distance between empirical and population measures.}
-Under mild regularity conditions, \cite{garciatrillos16b} upper bound the transportation distance $\Delta_{\infty}(\mbb{P},\mbb{P}_n)$. 
+We now review the relevant upper bound on $\Delta_{\infty}(\Pbb,\Pbb_n)$, which holds under the following mild regularity conditions.
 \begin{enumerate}[label=(A\arabic*)]
-	\item 
-	\label{asmp:domain} 
-	The distribution $\Pbb$ is defined on a domain $D \subseteq \Rd$, which is a bounded, connected, open set with Lipschitz boundary. 
 	\item 
@@
 	\begin{equation*}
-	(\forall x \in D)~~ g_{\min} \leq g(x) \leq g_{\max}
-	\end{equation*}
+	(\forall x \in D)~~ g_{\min} \leq g(x) \leq g_{\max}.
+	\end{equation*}
+	\item 
+	\label{asmp:domain} 
+	The distribution $\Pbb$ is defined on a bounded, connected, open domain $D \subseteq \Rd$. If $d \geq 2$ then additionally $D$ has Lipschitz boundary.
 \end{enumerate}
+When $d = 1$, it follows from Proposition~6.2 of \textcolor{red}{Dudley} that $\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_4 \|F - F_n\|_{\infty}$ for some positive constant $B_4$, and in turn from the DKW inequality (\textcolor{red}{Massart}) that
+\begin{equation}
+\label{eqn:ot_distance_1d}
+\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_4 \sqrt{\frac{\ln(2n/B_2)}{n}}
+\end{equation}
+with probability at least $1 - B_2/n$.
+
+When $d \geq 2$, \cite{garciatrillos16b} derive an upper bound on the transportation distance $\Delta_{\infty}(\mbb{P},\mbb{P}_n)$.
 \begin{theorem}[Theorem~1.1 of \cite{garciatrillos16}]
@@
 \end{theorem}
-Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}, then Theorem~\ref{thm:garciatrillos16} applies to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use this upper bound on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
+Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}, then~\eqref{eqn:ot_distance_1d} ($d = 1)$ or Theorem~\ref{thm:garciatrillos16} ($d \geq 2$) apply to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use these upper bounds on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
 
@@
 so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$.
-Next, taking $1 - \delta = 1/\sqrt{2}$ in~\eqref{pf:sample_to_population_local_spread_2}, we have that with probability at least $1 - \exp\{-(\mbb{P}(\mc{C}))^2n/5\} - n\exp\{-d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n/50\}$,
-\begin{equation*}
-d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
-\end{equation*}
-Finally, taking
-\begin{equation*}
-b_5 := \frac{1}{2b_4}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := \frac{1}{B_4}\min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\}
-\end{equation*}
-by Theorem~\ref{thm:garciatrillos16} and~\eqref{eqn:sample_to_population_conductance_sample_complexity} we have that
-\begin{equation*}
-\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_4 \frac{(\log n)^{p_d}}{n^{1/d}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+We now use the bounds we have derived on transportation distance and minimum degree.
+From the derivations in Section~\ref{subsec:sample_to_population_conductance}, it follows with probability at least $1 - (n + 1)\exp\{-nb_2/16\}$ that,
+\begin{equation*}
+d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} \bigl(d_{\min}(\wt{G}_{n,r}) + 1\bigr) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
+\end{equation*}
+% Here I replaced a factor of (1 - 1/sqrt{2})^2 by 1/16, for convenience.
+On the other hand, taking
+\begin{equation*}
+b_5 := \frac{1}{2b_4}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := \frac{1}{B_4}\min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\},
+\end{equation*}
+by~\eqref{eqn:ot_distance_1d} (if $d = 1$) or Theorem~\ref{thm:garciatrillos16} (if $d \geq 2$) along with~\eqref{eqn:sample_to_population_conductance_sample_complexity}, we have that
+\begin{equation*}
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_4 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
 \end{equation*}
@@
 \end{equation*}
-with probability at least $1 - B_2/n - \exp\{-(\mbb{P}(\mc{C}))^2n/5\} - n\exp\{-d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) n/50\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := (\mbb{P}(\mc{C}))^2/5 \wedge d_{\min}(\wt{\Pbb}) \Pbb(\mc{C}) /50$.
+with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$.
 
@@
 Suppose $r \in (0,\sigma/2)$.
-Then the population normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ is lower bounded,
+Then the population normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ is upper bounded,
 \begin{equation}
@@
 \end{equation}
-and the population local spread $s_{\Pbb,r}(\mc{X})$ is upper bounded,
+and the population local spread $s_{\Pbb,r}(\mc{X})$ is lower bounded,
 \begin{equation}
@@
 \label{pf:volume_ssd_ub_1}
-(1 - \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C}) \leq \vol_{n,r}(\mc{C}[X]) \leq (1 + \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C});
+(1 - \delta) \cdot \vol_{\Pbb,r}(\mc{C}) \leq \frac{1}{n(n-1)}\vol_{n,r}(\mc{C}[X]) \leq (1 + \delta) \cdot \vol_{\Pbb,r}(\mc{C});
 \end{equation}
@@
 \label{pf:volume_ssd_ub_2}
-\wt{n} \geq (1 - \delta) \cdot n \cdot \mbb{P}(\mc{C});
+\wt{n} \geq (1 - \delta) \cdot n \cdot \mbb{P}(\mc{C}) \overset{\eqref{eqn:sample_to_population_local_spread_sample_complexity}}{\Longrightarrow} \wt{n} - 1 \geq (1 - \delta)^2 \cdot n \cdot \mbb{P}(\mc{C});
 \end{equation}
@@
 \label{pf:volume_ssd_ub_3}
-~~\frac{1}{\wt{n}} d_{\min}(\wt{G}_{n,r}) \geq (1 - \delta) \cdot d_{\min}(\wt{\Pbb}),~~\textrm{and}~~\frac{1}{\wt{n}} d_{\max}(\wt{G}_{n,r}) \leq (1 + \delta) \cdot d_{\max}(\wt{\Pbb}).
-\end{equation}
-By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$.
-
-% AJG comment: The presence of a pre-factor of 4 in the second term, instead of 3, accounts for the extra upper bound needed on the vol_{n,r}(\mc{C}[X]).
-The presence of a pre-factor of 2(n + 2) in the third term, instead of (n + 2), accounts for the extra upper bound needed on d_{\max}(\wt{G}_{n,r}).
+~~\frac{1}{\wt{n} - 1} d_{\min}(\wt{G}_{n,r}) \geq (1 - \delta) \cdot d_{\min}(\wt{\Pbb}),~~\textrm{and}~~\frac{1}{\wt{n} - 1} d_{\max}(\wt{G}_{n,r}) \leq (1 + \delta) \cdot d_{\max}(\wt{\Pbb}).
+\end{equation}
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$.
+
+% AJG: The presence of a pre-factor of 4 in the second term, instead of 3, accounts for the extra upper bound needed on the vol_{n,r}(\mc{C}[X]).
+The presence of a pre-factor of (2n + 2) in the third term, instead of (n + 2), accounts for the extra upper bound needed on d_{\max}(\wt{G}_{n,r}).
 
@@
 We use Lemma~\ref{lem:zhu} to upper bound $\Delta(\wh{C},\mc{C}[X])$.
-In order to do so, we must verify that the tuning parameters $\alpha$ and $(L,U)$ satisfy the condition \eqref{eqn:zhu_condition} of this lemma.
-In order to verify that $\alpha \leq 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$, we will use Proposition~\ref{prop:conductance_lb_transportation_distance} to upper bound $\tau_{\infty}(\wt{G}_{n,r})$, which we may use because
-\begin{equation*}
-\frac{d_{\max}(\wt{G}_{n,r})}{\bigl(d_{\min}(\wt{G}_{n,r})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{d_{\max}(\wt{\Pbb})}{\wt{n}\bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^3} \cdot \frac{d_{\max}(\wt{\Pbb})}{n\Pbb(\mc{C})\bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{1}{16},
-\end{equation*}
-with the last inequality following by~\eqref{eqn:volume_ssd_ub_sample_complexity} upon taking $B_3 := 16 \cdot d_{\max}(\wt{\Pbb})/\bigl(d_{\min}(\wt{\Pbb})\bigr)^2$ in that equation.
-Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance}, and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$.
-On the other hand, by the upper bound on $\vol_{n,r}(\mc{C}[X])$ given in~\eqref{pf:volume_ssd_ub_3} and~\eqref{eqn:initialization}, we have that $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
+In order to do so, we must verify that the tuning parameters $\alpha$ and $(L,U)$ satisfy the condition \eqref{eqn:zhu_condition} of this lemma, i.e.
+that $\alpha \leq 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$ and $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
+In order to verify the upper bound on $\alpha$, we will use Proposition~\ref{prop:conductance_lb_transportation_distance} to upper bound $\tau_{\infty}(\wt{G}_{n,r})$, which we may validly apply because
+\begin{equation*}
+\frac{d_{\max}(\wt{G}_{n,r})}{\bigl(d_{\min}(\wt{G}_{n,r})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{d_{\max}(\wt{\Pbb})}{(\wt{n} - 1) \cdot \bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{(1 + \delta)}{(1 - \delta)^4} \cdot \frac{d_{\max}(\wt{\Pbb})}{n\Pbb(\mc{C})\bigl(d_{\min}(\wt{\Pbb})\bigr)^2} \leq \frac{1}{16}.
+\end{equation*}
+The last inequality in the above follows by taking $B_3 := 16 \cdot d_{\max}(\wt{\Pbb})/\bigl(d_{\min}(\wt{\Pbb})\bigr)^2$ in~\eqref{eqn:volume_ssd_ub_sample_complexity}.
+
+Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, along with inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance} and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$ and .
+On the other hand, by the upper bound on $\vol_{n,r}(\mc{C}[X])$ given in~\eqref{pf:volume_ssd_ub_1} and the initialization condition~\eqref{eqn:initialization}, we have that $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
+In summary, we have confirmed that the condition~\eqref{eqn:zhu_condition} is satisfied.
 
@@
 \subsection{Proof of Theorem~\ref{thm:density_cluster_volume_ssd_ub}}
-From Theorem~\ref{thm:volume_ssd_ub}, we have with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - 2(n + 2)\exp\{-b_2\delta^2n\} - (n + 2)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
+From Theorem~\ref{thm:volume_ssd_ub}, we have with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
 \begin{align*}
@@
 \subsection{Proof of Theorem~\ref{thm:ppr_lb}}
+We start by defining some constants, to make our proof statements easier to digest. Put
+\begin{align*}
+C_{3,\delta} & := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}
+,&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
+B_{1,\delta} & := 768 \cdot (1 + 3\delta) \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr),&&B_{2,\delta} := \frac{(1 + \delta)^2}{(1 - \delta)^2} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \\
+B_4 &:= \frac{6 \sigma \rho}{(\sigma - 2r)(\rho - r)},&&B_5 := 1 + \frac{12\sigma\rho}{r^2} + \frac{2\rho}{r} \\
+b_6 &:=  b_7 \wedge \cut_{\Pbb,r}(\mc{L}) \wedge d_{\min}(\Pbb)/14 \wedge \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}),&&b_7 := \vol_{\Pbb,r}(\mc{X})/4 \wedge \frac{\epsilon r^2}{4\rho\sigma} \wedge \frac{\pi r^3}{8\sigma \rho^2}.
+\end{align*}
 To prove Theorem~\ref{thm:ppr_lb}, we use Theorem~\ref{thm:normalized_cut_ppr}, Proposition~\ref{prop:sample_to_population_1} and~\eqref{eqn:ncut_lower_set} to show that the cluster estimate $\wh{C}$ must have a small normalized cut.
@@
 	\label{lem:normalized_cut_lb}
-	With probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$, the following statement holds:
-	\begin{equation*}
-	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
-	\end{equation*}
-	for all $Z \subseteq X$.
+	Fix $\delta \in (0,1)$. With probability at least $1 - B_5\exp\{-n\delta^2b_7\}$, the following statement holds:
+	\begin{equation}
+	\label{eqn:normalized_cut_lb}
+	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},~~\textrm{for all $Z \subseteq X$}.
+	\end{equation}
 \end{lemma}
-We therefore conclude that $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ must be large. Now, we give a formal proof Theorem~\ref{thm:ppr_lb}, and then of Lemma~\ref{lem:normalized_cut_lb}.
+We therefore conclude that $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ must be large.
+In the remainder of this, we detail the probabilistic estimates used in the proof of Theorem~\ref{thm:ppr_lb}, and then give a formal proof of Theorem~\ref{thm:ppr_lb} and then of Lemma~\ref{lem:normalized_cut_lb}.
+
+\textit{Probabilistic estimates.}
+In addition to~\eqref{eqn:normalized_cut_lb}, we will assume (i) that the graph normalized cut of $\mc{L}$ and local spread of $\mc{X}$ are respectively upper and lower bounded,
+\begin{equation*}
+\Phi_{n,r}(\mc{L}[X]) \leq (1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{L}),~~\textrm{and}~~s_{n,r}(X) \geq (1 - 3\delta) \cdot s_{\Pbb,r}(\mc{X});
+\end{equation*}
+(ii) that the graph volume of $\mc{L}$ is upper and lower bounded,
+\begin{equation*}
+(1 - \delta) \vol_{\Pbb,r}(\mc{L}) \leq \frac{1}{n(n - 1)}\vol_{n,r}(\mc{L}[X]) \leq (1 + \delta) \vol_{\Pbb,r}(\mc{L});
+\end{equation*}
+(iii) that the graph volumes of $\mc{L} \cap \mc{C}^{(1)}$ and $\mc{C}^{(1)}$ are respectively lower and upper bounded,
+\begin{equation}
+(1 - \delta) \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}) \leq \frac{1}{n(n - 1)}\vol_{n,r}({\mc{L}[X] \cap \mc{C}^{(1)}}[X])~~\textrm{and}~~\frac{1}{n(n - 1)}\vol_{n,r}(\mc{C}^{(1)}[X]) \leq (1 + \delta) \vol_{\Pbb,r}(\mc{C}^{(1)});
+\end{equation}
+(iv) that the graph volume of $\mc{X}$ is lower bounded,
+\begin{equation*}
+\frac{1}{n(n - 1)}\vol_{n,r}(X) \geq (1 - \delta) \vol_{\Pbb,r}(\mc{X});
+\end{equation*}
+and finally (v) that the maximum degree of $G_{n,r}$ is upper bounded,
+\begin{equation*}
+\frac{1}{n - 1}d_{\max}(G_{n,r}) \leq (1 + \delta) d_{\max}(\Pbb).
+\end{equation*}
+It follows from Lemma~\ref{lem:normalized_cut_lb}, Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2} and~\ref{lem:bernstein_union} that these estimates are together satisfied with probability at least $1 - B_5\exp\{-n\delta^2b_7\} - 3\exp\{-n\delta^2 \cut_{\Pbb,r}(\mc{L})\} - (2n + 2)\exp\{-n\delta^2 \cdot d_{\min}(\Pbb)/14\} - 5\exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)})\} \geq 1 - (B_5 + 2n + 10)\exp\{-n\delta^2 b_6\}$.
+
 \begin{proof}[Proof (of Theorem~\ref{thm:ppr_lb})]
-	Put
-	\begin{align*}
-	C_{3,\delta} & := 768 \cdot (1 + 3\delta),&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
-	C_{5,\delta} & := \frac{(1 + \delta)^2}{(1 - \delta)^2},&&C_{6,\delta} := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}.
-	\end{align*}
 	As mentioned, we would like to use Theorem~\ref{thm:normalized_cut_ppr} to upper bound $\Phi_{n,r}(\wh{C})$, and so we first verify that the conditions of Theorem~\ref{thm:normalized_cut_ppr} are met.
@@
 	\begin{itemize}
-		\item Recalling that $n \geq \frac{6 \sigma \rho (1 + \delta)}{(\sigma - 2r)(\rho - r) (1 - \delta)}$ and that $\vol_{\Pbb,r}(\mc{L}) \geq \frac{(\sigma - 2r)(\rho - r)}{2\sigma \rho}$, it follows from Lemmas~\ref{lem:bernstein_union} and~\ref{lem:hoeffding_2} that with probability at least $1 - n\exp\{\delta^2 d_{\min}(\Pbb) /(3 + \delta)\} - \exp\{-\delta^2 \vol_{\Pbb,r}(\mc{L})^2 n\}$,
+		\item Recall that $n \geq 8 \cdot (1 + \delta)/(1 - \delta)$ \eqref{eqn:ppr_lb_condition} and that $\vol_{\Pbb,r}(\mc{L}) \geq 3/16 \cdot \pi r^2/(2\sigma\rho)$ (as shown in the proof of~\eqref{eqn:ncut_lower_set}).
+It is additionally clear that $d_{\max}(\Pbb) \leq \pi r^2 /(2\rho\sigma)$, and consequently,
 		\begin{equation}
 		\label{pf:ppr_lb_1}
-		d_{\max}(G_{n,r}) \leq n \cdot (1 + \delta) d_{\max}(\Pbb) \leq \frac{1}{3}n^2 (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \leq \frac{1}{3}\vol_{n,r}(\mc{L}[X]).
+		d_{\max}(G_{n,r}) \leq (n - 1) \cdot (1 + \delta) d_{\max}(\Pbb) \leq \frac{1}{3}n^2 (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \leq \frac{1}{3}\vol_{n,r}(\mc{L}[X]).
 		\end{equation}
 		Therefore the lower bound in condition~\eqref{eqn:normalized_cut_ppr_vol} is satisfied.
-		\item Noting that $\delta \in (0,1/7)$ implies $\frac{(1 - \delta)}{(1 + \delta)} > \frac{3}{4}$, it follows from Lemma~\ref{lem:hoeffding_2} that with probability at least $1 - 2\exp\{-\delta^2 \vol_{\Pbb,r}(\mc{L})^2 n\}$,
+		\item Note that $\delta \in (0,1/7)$ implies $(1 - \delta)/(1 + \delta) > 3/4$, and additionally that $\vol_{\Pbb,r}(\mc{L}) \leq \vol_{\Pbb,r}(\mc{X})/2$. It follows that
 		\begin{equation}
 		\label{pf:ppr_lb_2}
-		\vol_{n,r}(X) \geq n^2(1 - \delta) \vol_{\Pbb,r}(\mc{X}) \geq 2n^2 (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \geq 2\frac{(1 - \delta)}{(1 + \delta)} \vol_{n,r}(\mc{L}[X]) \geq \frac{3}{2} \vol_{n,r}(\mc{L}[X]).
+		\vol_{n,r}(X) \geq n(n - 1)(1 - \delta) \vol_{\Pbb,r}(\mc{X}) \geq 2n(n - 1) (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \geq 2\frac{(1 - \delta)}{(1 + \delta)} \vol_{n,r}(\mc{L}[X]) \geq \frac{3}{2} \vol_{n,r}(\mc{L}[X]).
 		\end{equation}
 		Therefore the upper bound in condition~\eqref{eqn:normalized_cut_ppr_vol} is satisfied.
-		\item It follows from Proposition~\ref{prop:sample_to_population_1} and equations~\eqref{eqn:ncut_lower_set} and~\eqref{eqn:local_spread_ub} that with probability at least $1 - 3\exp\{-\delta^2 (\cut_{\Pbb,r}(\mc{L}))^2n\} - 2\exp\bigl\{-\delta^2\bigl(\vol_{\Pbb,r}(\mc{X}) n\bigr\} - n\exp\bigl\{-\delta^2d_{\min}(\Pbb) n\bigr/(3 + \delta)\}$,
+		\item By~\eqref{eqn:ncut_lower_set}, the normalized cut of $\mc{L}$ satisfies the following lower bound,
 		\begin{equation}
@@
 		\end{equation}
-		and
+		and by~\eqref{eqn:local_spread_ub} the local spread of $\mc{X}$ satisfies the following upper bound,
 		\begin{equation}
@@
 		\end{equation}
-		The assumption~\eqref{eqn:ppr_lb_condition} implies that  condition~\eqref{eqn:normalized_cut_ppr_ncut} is satisfied.
+		The constants $B_{1,\delta}$ and $B_{2,\delta}$ in assumption~\eqref{eqn:ppr_lb_condition} are chosen so that condition~\eqref{eqn:normalized_cut_ppr_ncut} is satisfied.
 	\end{itemize}
 	As a result, we may apply Theorem~\ref{thm:normalized_cut_ppr}, and deduce the following: there exists a set $\mc{L}[X]^g \subset \mc{L}$ of large volume, $\vol_{n,r}(\mc{L}[X]^g) \geq 5/6 \cdot \vol_{n,r}(\mc{L}[X])$, such that for any seed node $v \in \mc{L}[X]^g$, the normalized cut of the PPR cluster estimate $\Phi_{n,r}(\wh{C})$ satisfies the following upper bound:
-	\begin{align*}
-	\Phi_{n,r}(\wh{C}) & \overset{(\textrm{Thm.}~\ref{thm:normalized_cut_ppr})}{<} 72\sqrt{\Phi_{n,r}(\mc{L}[X]) \cdot \ln\Bigl(\frac{36}{s_{n,r}(X)}\Bigr)} \\
-	& \overset{\eqref{pf:ppr_lb_1},\eqref{pf:ppr_lb_2}}{\leq} 72\sqrt{(1 + 3\delta) \cdot \Phi_{\Pbb,r}(\mc{L}) \cdot \ln\Bigl(\frac{36}{(1 - 3\delta)s_{\Pbb,r}(\mc{X})}\Bigr)} \\
-	& \overset{\eqref{eqn:ncut_lower_set}, \eqref{eqn:local_spread_ub}}{\leq} 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)}.
-	\end{align*}	
+	\begin{equation*}
+	\Phi_{n,r}(\wh{C}) < 72\sqrt{\Phi_{n,r}(\mc{L}[X]) \cdot \ln\Bigl(\frac{36}{s_{n,r}(X)}\Bigr)} \leq  72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)}.
+	\end{equation*}	
 	Combined with Lemma~\ref{lem:normalized_cut_lb}, this implies
@@
 	\end{equation}
-	with probability at least $1 - 5\exp\set{-\delta^2(\cut_{\Pbb,r}(\mathcal{L}))^2n} - n\exp\bigl\{-\delta^2 d_{\min}(\Pbb) n/(3 + \delta)\bigr\} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
-Solving the inequality~\eqref{pf:ppr_lb_3} for $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ yields~\eqref{eqn:ppr_lb}.
+	and solving for $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ yields~\eqref{eqn:ppr_lb}.
 
@@
 	\begin{align*}
-	\vol_{n,r}(\mathcal{L}[X]^g \cap \mc{C}^{(1)}[X]) & \geq  \vol_{n,r}(\mathcal{L}[X]^g) - \vol_{n,r}\bigl((\mathcal{L}[X]^g \cap (\mc{C}^{(0)} \cup \mc{C}^{(2)})[X])\bigr) \\
-	& \geq \frac{5}{6}\vol_{n,r}\bigl(\mathcal{L}[X]\bigr) - \vol_{n,r}\bigl((\mathcal{L} \cap (\mc{C}^{(0)} \cup \mc{C}^{(1)}))[X]\bigr) \\
-	& \geq \frac{5}{6}\vol_{n,r}\bigl((\mathcal{L} \cap \mc{C}^{(1)})[X]\bigr) - \frac{1}{6}\vol_{n,r}\bigl(\mathcal{L}[X]\bigr) \\
-	& \overset{\mathrm{(i)}}{\geq} \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}) \\
-	& \overset{\mathrm{(ii)}}{\geq} \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mc{C}^{(1)}[X]) \geq \frac{6}{49} \cdot \vol_{n,r}(\mc{C}^{(1)}[X]),
-	\end{align*}
-	where $\mathrm{(i)}$ and $\mathrm{(ii)}$ follow from Lemma~\ref{lem:hoeffding} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}))^2}$, and the last inequality follows since $\delta \in (0,1/7)$.
-The claim of Theorem~\ref{thm:ppr_lb} follows upon taking constants $B_3:= 8 + 12\sigma\rho/r^2 + 2\rho/r$, $b_4 := \cut_{\Pbb,r}(\mc{L})^2 \wedge \epsilon r^2/(\rho \sigma) \wedge \pi r^3/(2\sigma\rho^2) \wedge \vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)})^2$ and $b_5 := d_{\min}(\Pbb)$.
+	\vol_{n,r}(\mathcal{L}[X]^g \cap \mc{C}^{(1)}[X]) & \geq \vol_{n,r}\bigl((\mathcal{L} \cap \mc{C}^{(1)})[X]\bigr) - \frac{1}{6}\vol_{n,r}\bigl(\mc{L}[X]\bigr) \\
+	& \overset{\mathrm{(i)}}{\geq} n(n-1) \cdot \left((1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}) \\
+	& \overset{\mathrm(ii)}{\geq} n(n - 1) \cdot \frac{1}{7} \vol_{\Pbb,r}( \mathcal{L} \cap \mc{C}^{(1)}) \\
+	& \overset{\mathrm(iii)}{\geq} \frac{1}{8} \vol_{n,r}( \mathcal{L} \cap \mc{C}^{(1)})
+	\end{align*}
+	where in $\mathrm{(i)}$ we have used $\vol_{\Pbb,r}(\mc{L}) \leq 3 \vol_{\Pbb,r}(\mc{C}^{(1)})$, and in $\mathrm{(ii)}$ and $\mathrm{(iii)}$ we have used $\delta \in (0,1/7)$.
 \end{proof}
@@
 	\label{eqn:normalized_cut_lb_pf4}
-	\vol_{n,r}(Z) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
-	\end{equation}
-	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this crude upper bound will suffice for our purposes.
-
-	We turn to lower bounding $\cut_{n,r}(Z)$.
+	\vol_{n,r}(Z) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n (n - 1) \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
+	\end{equation}
+	where by Lemma~\ref{lem:hoeffding}, inequality $(i)$ holds with probability at least $1 - \exp\set{-n\delta^2 \vol_{\Pbb,r}(\mathcal{X})/4}$. This crude upper bound will suffice for our purposes.
+
+	We turn to lower bounding $\cut_{n,r}(Z)$, which is considerably more involved.
 We will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $Z$ to the boundary of the binned set $\overline{Z}$, and then lower bound the size of the boundary of $\overline{Z}$.
@@
 		\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(A \vartriangle \mc{C}^{(1)}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k), ~~ \textrm{or}
+		\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{(1)}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k), ~~ \textrm{or}
 		\end{equation*}
@@
 		\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(A \vartriangle \mc{C}^{}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
+		\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
 		\end{equation*}
@@
 	Let $N(R)$ be the number of slices for which $\wb{R}_k \cap \partial \wb{Z} \neq \emptyset$. By the cases elucidated above, letting
-	\begin{equation*} R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}
+	\begin{equation*} 
+	R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}
 	\end{equation*} 
@@
 	\label{eqn:normalized_cut_lb_pf2}
-	\vol_{n,r}(A \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right].
+	\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right] \Longleftrightarrow N(R) \geq 2\Bigl(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\Bigr)
 	\end{equation}
@@
 	To do so, we first lower bound the expected probability of any cell $Q$,
-	\begin{align*}
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf4.5}
 	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
-	\end{align*}
+	\end{equation}
 	and the expected volume of $\mc{C}^{(1)}[X] \cap R_k$ and $\mc{C}^{(2)}[X] \cap R_k$,
 	\begin{equation}
-	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
+	\label{eqn:normalized_cut_lb_pf5}
+	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2}~~\textrm{for all $k$.} 
 	\end{equation}
@@
 Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
-Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
-	\begin{equation*}
-	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq \frac{(1 - \delta)}{2}\frac{\pi r^3}{\sigma \rho^2 },
-	\end{equation*}
-	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
+Along with \eqref{eqn:normalized_cut_lb_pf4.5} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
+	\begin{equation*}
+	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq (1 - \delta)\frac{\pi r^3}{2\sigma \rho^2 },
+	\end{equation*}
+	with probability at least $1 - \frac{12 \sigma \rho}{r^2}\exp\set{-\frac{n\delta^2\epsilon r^2 n}{4 \rho \sigma}} - \frac{2\rho}{r}\exp\set{-\frac{n\delta^2\pi r^3}{8\sigma\rho^2}}$.
 Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
@@
 \begin{proof}[Proof (of Corollary~\ref{cor:appr})]
-	Note that the choice of $\varepsilon$ in~\eqref{eqn:appr_parameter} implies $\varepsilon \leq 1/25\vol_{n,r}(\mc{C}[X])$ with probability at least $1 - \exp\bigl\{-\delta^2\bigl(\vol_{\Pbb,r}(\mc{C})\bigr)^2\bigr\}$.
-The proof of Corollary~\ref{cor:appr} is then identical to that of Theorem~\ref{thm:volume_ssd_ub}, except we use Corollary~\ref{cor:zhu} rather than Lemma~\ref{lem:zhu} to relate the symmetric set difference to the graph normalized cut and mixing time.
+	Note that the choice of $\varepsilon$ in~\eqref{eqn:appr_parameter} implies $\varepsilon \leq 1/\bigl(25\vol_{n,r}(\mc{C}[X])\bigr)$ with probability at least $1 - \exp\bigl\{-n\delta^2\vol_{\Pbb,r}(\mc{C})\bigr\}$.
+The proof of Corollary~\ref{cor:appr} is then identical to that of Theorem~\ref{thm:volume_ssd_ub}, except one uses Corollary~\ref{cor:zhu} rather than Lemma~\ref{lem:zhu} to relate the symmetric set difference to the graph normalized cut and mixing time.
 \end{proof}
@@
 \begin{equation*}
-c_{1,\delta} := \frac{(1 - \delta)^3}{4} \cdot \min\Bigl\{\Bigl(\frac{3}{8(1 + \delta)} - \frac{1}{5}\Bigr),\frac{1}{10}\Bigr\}
+c_{1,\delta} := \frac{(1 - \delta)^5}{4} \cdot \min\Bigl\{\Bigl(\frac{3}{8(1 + \delta)} - \frac{1}{5}\Bigr),\frac{1}{10}\Bigr\}
 \end{equation*}
@@
 	\label{thm:density_cluster_consistent_recovery}
-	For any $\delta \in (0,1/4)$, and otherwise under the same conditions as Theorem~\ref{thm:volume_ssd_ub}, the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
+	For any $\delta \in (0,1/4)$ any $n \in \mathbb{N}$ such that
+	\begin{equation}
+	\label{eqn:density_cluster_consistent_recovery_sample_complexity}
+	\frac{1}{n} \leq \delta \cdot \frac{4\Pbb(\mc{C}_{\lambda,\sigma}')}{3}
+	\end{equation} 
+	and otherwise under the same conditions as Theorem~\ref{thm:volume_ssd_ub}, the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
 	\begin{equation}
@@
 	\item The proof of Theorem~\ref{thm:density_cluster_consistent_recovery} relies heavily on Lemma~\ref{lem:ppr_uniform_bound}.
-This lemma---or more accurately, the equation~\eqref{pf:interpolator_bound_max_entry} used in the proof of the lemma---can be thought of as a smoothness result for the PPR vector, showing that the mass of $p_v(\cdot)$ cannot be overly concentrated at any one node $u$.
+This lemma---or more accurately, the equation~\eqref{pf:interpolator_bound_max_entry} used in the proof of the lemma---can be thought of as a smoothness result for the PPR vector, showing that the mass of $p_v(\cdot)$ cannot be overly concentrated at any one vertex $u \in V$.
 However,~\eqref{pf:interpolator_bound_max_entry} is a somewhat crude bound.
@@
 \begin{equation}
-n' \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}_{\lambda,\sigma}')
+n' \geq (1 - \delta) \cdot n \cdot \Pbb(\mc{C}_{\lambda,\sigma}') \overset{\eqref{eqn:density_cluster_consistent_recovery_sample_complexity}}{\Longrightarrow} n' - 1 \geq (1 - \delta)^2 \cdot n \cdot \Pbb(\mc{C}_{\lambda,\sigma}')
 \end{equation}
@@
 \begin{equation}
-\frac{1}{n'} d_{\min}(G_{n,r}') \geq (1 - \delta) n \cdot d_{\min}(\Pbb').
-\end{equation}
-By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$, taking $b_6 := b_2 \wedge d_{\min}(\Pbb')/4 \wedge \bigl(\Pbb(\mc{C}_{\lambda,\sigma}')\bigr)^2$.
-
-% The pre-factor of 1/4 in the definition of b_6 is to handle the factor of 1/(3 + \delta) in Bernstein's inequality.
+\frac{1}{n' - 1} d_{\min}(G_{n,r}') \geq (1 - \delta) \cdot d_{\min}(\Pbb').
+\end{equation}
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities hold with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 1)\exp\{-b_3n\} - (3n + 3)\exp\{-b_6\delta^2n\}$, taking $b_6 := b_2 \wedge \Pbb(\mc{C}_{\lambda,\sigma}') \cdot d_{\min}(\Pbb')/9$.
+
+% AJG: The term after \wedge is needed to condition on the two new inequalities.
 
@@
 \frac{p_v(u)}{\deg_{n,r}(u)} & \geq \frac{3}{8\vol_{n,r}(\mc{C}[X])} - 2\frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(\wt{G}_{n,r})^2 \alpha} \\
-& \geq \frac{1}{n^2}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{n^2}{\wt{n}^2} \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\wt{\Pbb})^2}\biggr) \\
-& \geq \frac{1}{n^2}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta)^3 \Pbb(\mc{C})^2 d_{\min}(\wt{\Pbb})^2}\biggr) \\
+& \geq \frac{1}{n(n - 1)}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{n(n - 1)}{(\wt{n} - 1)^2} \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\wt{\Pbb})^2}\biggr) \\
+& \geq \frac{1}{n(n - 1)}\biggl(\frac{3}{8(1 + \delta)\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})} - 4 \cdot \frac{\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta)^5 \Pbb(\mc{C})^2 d_{\min}(\wt{\Pbb})^2}\biggr) \\
 & \geq \frac{1}{5 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}.
 \end{align*}
+% AJG: The factor of only 1/(1 - \delta), rather than 1/(1 - \delta)^2, in the second term inside the parenthesis of the second inequality comes from the definition of \kappa, which absorbs one factor of 1/(1 - \delta).
+The same applies to the following equation.
 An equivalent derivation implies the upper bound in~\eqref{eqn:ppr_gap}: for all $u' \in \mc{C}_{\lambda}'[X]$,
 \begin{equation*}
-\frac{p_v(u')}{\deg_{n,r}(u')} \leq 2 \frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(G_{n,r}')^2 \alpha} \leq 4 \cdot \frac{n^2}{(n')^2} \cdot 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\Pbb')^2} \leq 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{n^2 (1 - \delta)^3 \Pbb(\mc{C}_{\lambda,\sigma}')^2 d_{\min}(\Pbb')^2} \leq \frac{1}{10 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})},
+\frac{p_v(u')}{\deg_{n,r}(u')} \leq 2 \frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(G_{n,r}')^2 \alpha} \leq 4 \cdot \frac{1}{(n' - 1)^2} \cdot \frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\Pbb')^2} \leq 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{n^2 (1 - \delta)^5 \Pbb(\mc{C}_{\lambda,\sigma}')^2 d_{\min}(\Pbb')^2} \leq \frac{1}{10 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})},
 \end{equation*}

### 2021-01-27 jmlr/code/configs/2d_uniform_rectangles_rho.R
Code updated.

@@ -1,0 +1,76 @@
+# -----------------------------------------------------------------------------#
+# Distribution is 
+#
+# \mathbb{P} = (1 - \epsilon)/2 \cdot \sum_{k = 1}^{2} P(C_k) + epsilon \cdot P(\Omega \ C_1 \cup C_2)
+#
+# where \mathbb{P} is parameterized in terms of \epsilon,\sigma,\rho with
+# -- \Omega = [-1,1]^2
+# -- C_1 = [-1/2 - sigma/2,-1/2 + sigma/2] x [-rho/2,rho/2]
+# -- C_2 = [1/2 - sigma/2,1/2 + sigma/2] x   [-rho/2,rho/2]
+
+# for \sigma <= \rho <= 2, and \sigma < 1 - r, and r <= sigma/4d, and
+# epsilon = 1 - 2*lambda*rho*sigma, and 1/4 <= lambda <= 1/(2 * rho * sigma)
+# -----------------------------------------------------------------------------#
+
+
+# Global parameters
+n_samples <- 4000
+n_iters <- 50
+d <- 2
+n_mixtures <- 2
+n_distributions <- 10
+
+# PPR hyperparameters
+seed_location <- c(-.5,0)
+tune_LU <- function(G)
+{
+  return(c(1/(6 * volume(G)), 1/(5 * volume(G))))
+}
+tune_alpha <- function(G,psi = NULL)
+{
+  if(is.null(psi))
+  {
+    psi <- conductance(G)
+  }
+  s <- local_spread(G)
+  alpha_theoretical <- 1/2 * 1 / (8/psi^2 * log(4/s,base = exp(1)) * log(8/s,base = 2) + 4*log(8/s,base = 2) + 1)
+  return(10000*alpha_theoretical)
+}
+
+## Distributions
+
+# Sample space
+domain <- function(x)
+{
+  all(-1 <= x && x <= 1)
+}
+attributes(domain) <- list("d" = d, "measure" = 4)
+
+# Parameters
+sigma <- rep(.5,n_distributions)
+rho <- exp(seq(log(.5),log(2),length = n_distributions))
+lambda <- 2/(5 * max(rho) * max(sigma))
+epsilon <- 1 - 2*rho*sigma*lambda
+stopifnot(lambda > 1/4) # Make sure it is in fact a density cluster.
+stopifnot(all(epsilon > 0)) # Make sure it is in fact a density.
+
+# Make distributions
+make_distribution_jj <- function(jj){
+  distribution <- list(
[…]

### 2021-01-27 jmlr/code/configs/2d_uniform_rectangles_sigma.R

@@ -1,0 +1,76 @@
+# -----------------------------------------------------------------------------#
+# Distribution is 
+#
+# \mathbb{P} = (1 - \epsilon)/2 \cdot \sum_{k = 1}^{2} P(C_k) + epsilon \cdot P(\Omega \ C_1 \cup C_2)
+#
+# where \mathbb{P} is parameterized in terms of \epsilon,\sigma,\rho with
+# -- \Omega = [-1,1]^2
+# -- C_1 = [-1/2 - sigma/2,-1/2 + sigma/2] x [-rho/2,rho/2]
+# -- C_2 = [1/2 - sigma/2,1/2 + sigma/2] x   [-rho/2,rho/2]
+
+# for \sigma <= \rho <= 2, and \sigma < 1 - r, and r <= sigma/4d, and
+# epsilon = 1 - 2*lambda*rho*sigma, and 1/4 <= lambda <= 1/(2 * rho * sigma)
+# -----------------------------------------------------------------------------#
+
+
+# Global parameters
+n_samples <- 4000
+n_iters <- 50
+d <- 2
+n_mixtures <- 2
+n_distributions <- 10
+
+# PPR hyperparameters
+seed_location <- c(-.5,0)
+tune_LU <- function(G)
+{
+  return(c(1/(6 * volume(G)), 1/(5 * volume(G))))
+}
+tune_alpha <- function(G,psi = NULL)
+{
+  if(is.null(psi))
+  {
+    psi <- conductance(G)
+  }
+  s <- local_spread(G)
+  alpha_theoretical <- 1/2 * 1 / (8/psi^2 * log(4/s,base = exp(1)) * log(8/s,base = 2) + 4*log(8/s,base = 2) + 1)
+  return(10000*alpha_theoretical)
+}
+
+## Distributions
+
+# Sample space
+domain <- function(x)
+{
+  all(-1 <= x && x <= 1)
+}
+attributes(domain) <- list("d" = d, "measure" = 4)
+
+# Parameters
+sigma <- exp(seq(log(.4),log(.8),length.out = n_distributions))
+rho <- rep(.8,n_distributions)
+lambda <- 2/(5 * max(rho) * max(sigma))
+epsilon <- 1 - 2*rho*sigma*lambda
+stopifnot(lambda > 1/4) # Make sure it is in fact a density cluster.
+stopifnot(all(epsilon > 0)) # Make sure it is in fact a density.
+
+# Make distributions
+make_distribution_jj <- function(jj){
[…]

### 2021-01-27 jmlr/code/configs/2d_uniform_rectangles_theta.R

@@ -1,0 +1,77 @@
+# -----------------------------------------------------------------------------#
+# Distribution is 
+#
+# \mathbb{P} = (1 - \epsilon)/2 \cdot \sum_{k = 1}^{2} P(C_k) + epsilon \cdot P(\Omega \ C_1 \cup C_2)
+#
+# where \mathbb{P} is parameterized in terms of \epsilon,\sigma,\rho with
+# -- \Omega = [-1,1]^2
+# -- C_1 = [-1/2 - sigma/2,-1/2 + sigma/2] x [-rho/2,rho/2]
+# -- C_2 = [1/2 - sigma/2,1/2 + sigma/2] x   [-rho/2,rho/2]
+
+# for \sigma <= \rho <= 2, and \sigma < 1 - r, and r <= sigma/4d, and
+# epsilon = 1 - 2*lambda*rho*sigma, and 1/4 <= lambda <= 1/(2 * rho * sigma)
+# -----------------------------------------------------------------------------#
+
+# Global parameters
+n_samples <- 4000
+n_iters <- 50
+d <- 2
+n_mixtures <- 2
+n_distributions <- 10
+
+# PPR hyperparameters
+seed_location <- c(-.5,0)
+tune_LU <- function(G)
+{
+  return(c(1/(6 * volume(G)), 1/(5 * volume(G))))
+}
+tune_alpha <- function(G,psi = NULL)
+{
+  if(is.null(psi))
+  {
+    psi <- conductance(G)
+  }
+  s <- local_spread(G)
+  alpha_theoretical <- 1/2 * 1 / (8/psi^2 * log(4/s,base = exp(1)) * log(8/s,base = 2) + 4*log(8/s,base = 2) + 1)
+  return(10000*alpha_theoretical)
+}
+
+## Distributions
+
+# Sample space
+domain <- function(x)
+{
+  all(-1 <= x && x <= 1)
+}
+attributes(domain) <- list("d" = d, "measure" = 4)
+
+# Parameters
+rho <- rep(.8,n_distributions)
+sigma <- rep(.4,n_distributions)
+theta <- exp(seq(log(.1),log(1),length.out = n_distributions))
+lambda <- (theta + 1)/(1 + 2*rho*sigma) # Solve for lambda from theta
+epsilon <- 1 - 2*rho*sigma*lambda       # Solve for epsilon from lambda
+
+stopifnot(lambda >= 1/4) # Make sure it is in fact a density cluster.
[…]

### 2021-01-27 jmlr/code/plot.R

@@ -1,16 +1,16 @@
 #----------------------------------------------------#
 # Plot results from validate theory pipeline
+# 
+# Plotting options are 
+# 
+# -- vectors <- c("samples","normalized_ppr","sweep_cut")
+# -- quantities <- c("normalized_cut","conductance","local_spread","normalized_volume_ssd")
 #----------------------------------------------------#
 
-# What is to be plotted? # (NOTE: this script is not robust to changing these; they are global variables.)
-vectors <- c("samples","normalized_ppr","sweep_cut")
-quantities <- c("normalized_cut","conductance","local_spread","normalized_volume_ssd")
-n_vectors <- 3
-n_quantities <- 4
-parameter <- "diameter"
-
-# Please specify the name of the directory containing the saved data here.
-dir_name <- "20210111200827"
+# What is to be plotted?
+vectors <- NULL
+quantities <- c("conductance","local_spread")
+parameter <- "lambda"
 
 # Would you like to save plots to file?
 save_plots <- TRUE
@@ -23,11 +23,8 @@ list_of_plot_data <- vector(mode = "list", length = n_quantities)
 names(list_of_plot_data) <- quantities
 
 # Load results
-save_directory <- paste0("data/",dir_name)
-for(file_name in list.files(save_directory, pattern = "*.R"))
-{
-  load(paste0(save_directory,"/",file_name))
-}
+save_file <- paste0("2d_uniform_rectangles_",parameter,".rda")
+load(file.path("data",save_file))
 empirical_data <- list(ncut = empirical_ncuts,
                        conductance = empirical_conductances,
                        local_spread = empirical_local_spreads,
@@ -37,13 +34,15 @@ population_bounds <- list(ncut = population_ncuts,
                        local_spread = population_local_spreads,
                        normalized_volume_ssd = population_condition_numbers)
 
+##
+empirical_data <- empirical_data[quantities]
+population_bounds <- population_bounds[quantities]
+
+
 # Data for plotting
-distributions <- configs$distributions
-seed_location <- configs$seed_location
[…]

### 2021-01-27 jmlr/code/sample.R

@@ -4,12 +4,19 @@
 
 make_two_2drectangular_sampler <- function(epsilon,sigma,rho,d){
   function(n){
+    cluster_sets <- make_two_2drectangular_cluster_sets(sigma,rho)
     X <- matrix(nrow = n,ncol = d)
     for(ii in 1:n)
     {
       if(runif(1) <= epsilon)
       {
-        X[ii,] <- runif(d, min = -1, max = 1) # Omega
+        # Rejection sample
+        tryX <- runif(d,min = -1,max = 1)
+        while(any(sapply(cluster_sets, FUN = function(set){set(tryX)})))
+        {
+          tryX <- runif(d,min = -1,max = 1)
+        }
+        X[ii,] <- tryX
       }
       else if(runif(1) <= .5)
       {

### 2021-01-27 jmlr/code/validate_ncut_theory_pipeline.R

@@ -1,0 +1,68 @@
+# How noisy should the pipeline be?
+verbose <- F
+
+# Dependencies
+library(magrittr)
+library(Matrix)
+library(RANN)
+library(reshape2)
+
+source("bounds.R")
+source("geometry.R")
+source("graph.R")
+source("sample.R")
+
+# Read configs.
+source("configs/2d_uniform_rectangles_theta.R")
+
+# Structures to save data.
+Xs <- vector(mode = "list",length = length(distributions))
+ps <- matrix(nrow = length(distributions),ncol = n_samples)
+empirical_candidate_clusters <- matrix(nrow = length(distributions),ncol = n_samples)
+estimated_clusters <-  matrix(nrow = length(distributions),ncol = n_samples)
+hyperparameters <- vector(mode = "list",length = length(distributions))
+for(jj in 1:n_distributions)
+{
+  hyperparameters[[jj]] <- vector(mode = "list",length = n_iters)
+}
+
+empirical_ncuts <- matrix(nrow = length(distributions),ncol = n_iters)
+empirical_conductances <- matrix(nrow = length(distributions),ncol = n_iters)
+empirical_local_spreads <- matrix(nrow = length(distributions),ncol = n_iters)
+empirical_normalized_volume_ssd <- matrix(nrow = length(distributions),ncol = n_iters)
+
+population_ncuts <- numeric(length(distributions))
+population_conductances <- numeric(length(distributions))
+population_local_spreads <- numeric(length(distributions))
+population_condition_numbers <- numeric(length(distributions))
+
+for(iter in 1:n_iters)
+{
+  for(jj in 1:length(distributions))
+  {
+    distribution <- distributions[[jj]]
+    
+    # Sample X_1,...,X_n
+    X <- distribution$sampler(n_samples)
+    
+    # Form neighborhood graph
+    G <- neighborhood_graph(X,r)
+    
+    # Find candidate cluster (and associated quantities)
+    candidate_cluster <- distribution$partition(seed_location) 
+    empirical_candidate_cluster <- which(apply(X,1,FUN = function(x){candidate_cluster(x)}))
+    G_candidate_cluster <- G[empirical_candidate_cluster,empirical_candidate_cluster]
+    
+    # Compute empirical quantities
+    phi_hat <- ncut(empirical_candidate_cluster,G)
+    empirical_ncuts[jj,iter] <- phi_hat
+    
+    
+    # Compute population quantities
[…]

### 2021-01-27 jmlr/code/validate_theory_pipeline.R

@@ -12,8 +12,8 @@
 #---------------------------------------#
 
 # How noisy should the pipeline be?
-verbose <- F
-
+verbose <- T
+  
 # Dependencies
 library(magrittr)
 library(Matrix)
@@ -26,7 +26,8 @@ source("graph.R")
 source("sample.R")
 
 # Read configs.
-source("configs/2d_uniform_rectangles.R")
+configs_name <- "2d_uniform_rectangles_theta"
+source(file.path("configs",paste0(configs_name,".R")))
 
 # Structures to save data.
 Xs <- vector(mode = "list",length = length(distributions))
@@ -123,33 +124,5 @@ for(iter in 1:n_iters)
 }
 
 # Save data
-save_directory <- file.path("data",gsub("[^[:alnum:]]", "", Sys.time()))
-for(directory in c(save_directory))
-{
-  dir.create(directory)
-}
-configs <- list(n_samples = n_samples,
-                n_iter = n_iters,
-                d = d,
-                n_mixtures = n_mixtures,
-                n_distributions = n_distributions,
-                distributions = distributions,
-                r = r,
-                seed_location = seed_location)
-save(configs, file = paste0(save_directory, '/configs.R'))
-save(Xs, file = paste0(save_directory, '/Xs.R'))
-save(ps, file = paste0(save_directory, '/ps.R'))
-save(empirical_candidate_clusters, file = paste0(save_directory, '/empirical_candidate_clusters.R'))
-save(estimated_clusters, file = paste0(save_directory, '/estimated_clusters.R'))
-
-save(hyperparameters, file = paste0(save_directory, '/hyperparameters.R'))
-
-save(empirical_ncuts, file = paste0(save_directory, '/empirical_ncuts.R'))
-save(empirical_conductances, file = paste0(save_directory, '/empirical_conductances.R'))
-save(empirical_local_spreads, file = paste0(save_directory, '/empirical_local_spreads.R'))
-save(empirical_normalized_volume_ssd, file = paste0(save_directory, '/empirical_normalized_volume_ssd.R'))
-
-save(population_ncuts, file = paste0(save_directory, '/population_ncuts.R'))
-save(population_conductances, file = paste0(save_directory, '/population_conductances.R'))
-save(population_local_spreads, file = paste0(save_directory, '/population_local_spreads.R'))
-save(population_condition_numbers, file = paste0(save_directory, '/population_condition_numbers.R'))
[…]

### 2021-01-31 jmlr/revision/archive/local_spectral_density_clustering_jmlr_revision.tex
Final draft to be submitted to JMLR uploaded, in revision/ppr_clustering_neighborhood_graph

--- 2021-01-13 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex
@@
 
-%\subsubsection{Sweep cut}
-%\label{subsection: sweep_cut}
 Next, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$,
@@
 \citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
-the Laplacian matrix for a neighborhood of fixed radius. \citet{belkin07} and
+the Laplacian matrix for a neighborhood graph of fixed radius. \citet{belkin07} and
 \citet{garciatrillos18} extend these results to the regime where the radius $r
@@
 \smash{$\dist(x,\Cset) := \inf_{y \in \Cset} \norm{y - x}$}.  We now list our
-conditions on $\Csig$.
+conditions on $\Csig$, which are defined with respect to $\sigma$ as well as positive numbers $\lambda_{\sigma}, \Lambda_{\sigma}, L$, $\theta \in (0,\infty)$, $\gamma \in [0,1]$, and $r \in (0,\frac{\sigma}{4d}]$.
 
@@
   \label{asmp: bounded_density}
-  \emph{Bounded density within cluster:} There exist constants
-  $0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
+  \emph{Bounded density within cluster:} The density is bounded above and below in $\mc{C}_{\sigma}$:
   $$
@@
   \label{asmp: low_noise_density}
-  \emph{Low noise density:} There exists constants $c_0 > 0$ and $\gamma \in
-  [0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \Csig) \leq \sigma$,     
+  \emph{Low noise density:} For any $x \in \Rd$ such that $0 < \dist(x, \Csig) \leq \sigma$,     
   $$
-  \inf_{x' \in \Csig} f(x') - f(x) \geq  c_0 \cdot \dist(x, \Csig)^{\gamma}.  
+  \inf_{x' \in \Csig} f(x') - f(x) \geq  \theta \cdot \dist(x, \Csig)^{\gamma}.  
   $$
@@
   \emph{Lipschitz embedding:}
-  There exists $g: \Reals^d \to \Reals^d$ with the following properties: 
+  There exists some $g: \Reals^d \to \Reals^d$ satisfying each of the following:
   \begin{enumerate}
-  \item we have $\Csig = g(\mathcal{K})$, for a convex set $\mathcal{K}
-    \subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
-      \mathcal{K}}\norm{x - y} =: \diam < \infty$;
-  \item $\det(\nabla g (x)) = 1$ for all $x \in \Csig$, where $\nabla g(x)$ is
+  \item the thickened set $\Csig = g(\mathcal{K})$, where $\mathcal{K}
+    \subseteq \Rd$ is a convex set with diameter $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in \mathcal{K}}\norm{x - y} \leq \diam$;
+  \item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is
     the Jacobian of $g$ evaluated at $x;$ and 
-  \item for some $L \geq 1$,   
+  \item The restriction of $g$ to $\mc{K}$ is $L$-Lipschitz, i.e.
     $$
@@
   \end{equation}
-  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$. We assume
-  that the radius of the neighborhood graph $0 < r \leq \sigma/(2d)$ is chosen 
-  such that  
+  where $B(x,r)$ is the closed ball of radius $r$ centered at $x$. It holds that
   $$
-  \vol_{\Pbb,r}(\Cset_\sigma) \leq \frac{1}{2} \vol_{\Pbb,r}(\Reals^d). 
+  \vol_{\Pbb,r}(\Cset_\sigma) \leq \vol_{\Pbb,r}(\Reals^d \setminus \mc{C}_{\sigma}). 
   $$
@@
 
-\textcolor{red}{Need to fix this definition: (1) the universal constants are not given in the Theorem statements, and (2) the definition of $\tau_u(\mc{C})$ has changed.}
-
 \begin{definition}
@@
   For $\lambda > 0$ and \smash{$\Cset \in \Cbb_f(\lambda)$}, let $\Cset$ satisfy  
-  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma >
-  0$. Then, for universal constants $c_1, c_2, c_3 > 0$ to be specified later
-  (in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
-    mixing_time_upper_bound}), define
-  \begin{equation}
+  \ref{asmp: bounded_density}--\ref{asmp: bounded_volume} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, L > 0$,  $\theta \in (0,\infty)$, $\gamma \in [0,1]$ and $r \in (0,\sigma/4d]$.
+Then, for positive universal constants $c_1$-$c_5$ to be specified later
+  (in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}), define
+  \begin{align}
     \label{eqn: condition_number}
     \Phibf(\Cset) 
-    := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
-    \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma +
-        1})}{\lambda_{\sigma}}, \quad
-    \taubf(\Cset) := c_2 \frac{\Lambda_{\sigma}^4 d^3 \rho^2
-      L^2}{\lambda_{\sigma}^4 r^2}
-    \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c_3.
-  \end{equation}
+    & := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}}
+    \frac{(\lambda_{\sigma} - \theta \frac{r^{\gamma}}{\gamma +
+        1})}{\lambda_{\sigma}} \\
+    \taubf(\Cset) & := c_2 \frac{\Lambda_{\sigma}^4 (d + 2)^3 
+    	\rho^2 L^2}{\lambda_{\sigma}^4 r^2} \ln^2\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{2\lambda_{\sigma}^{2/d}r}\Bigr)
+  \end{align}
   Letting \smash{$\kappa(\Cset) := \Phibf(\Cset) \cdot \taubf(\Cset)$},
@@
 The condition number $\kappa(\Cset)$ succinctly captures the role of the various 
-geometric parameters.  We note in passing that $\Phibf(\Cset)$ and
-$\taubf(\Cset)$ are exactly the upper bounds  on \smash{$\Phi(\Csig[\Xbf];
+geometric parameters.\footnote{Technically speaking, the condition number depends on the numbers $\sigma, \lambda_{\sigma}, \Lambda_{\sigma},L > 0$, $\theta \in (0,\infty)$, $\gamma \in [0,1]$, and $r \in (0,\sigma/(4d))$ rather than on $\mc{C}$.
+However, we use the notation $\kappa(\mc{C})$ to make clear that the purpose of $\kappa$ is to measure the quality of the cluster $\mc{C}$.}  We note in passing that $\Phibf(\Cset)$ and
+$\taubf(\Cset)$ are essentially the upper bounds  on \smash{$\Phi(\Csig[\Xbf];
   G_{n,r})$} and \smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$} that we derive in
@@
 \label{eqn: initialization}
-0 < r \leq \frac{\sigma}{2d}, \quad 
-\alpha \in {\textstyle [\frac{1}{10}, \frac{1}{9})} \cdot
-\frac{1}{\taubf(\theta)}, \\ 
+0 < r \leq \frac{\sigma}{4d}, \quad 
+\alpha \in {\textstyle [\frac{1}{3}, \frac{5}{12})} \cdot
+\frac{1}{\taubf(\mc{C})}, \\ 
 (L,U) \subseteq {\textstyle(\frac{1}{50},\frac{1}{5})} \cdot 
@@
 difference between the estimated cluster \smash{$\Cest$} and empirical cluster 
-$\Csig[\Xbf]$. In this theorem, and hereafter, we let $c, c_i > 0$ denote
-universal constants, and $b,b_i > 0$ denote constants which may depend on  
+$\Csig[\Xbf]$. In this theorem, and hereafter, we let $c_i > 0$ denote
+universal constants, and $b_i > 0$ denote constants which may depend on  
 $\Pbb,\lambda,r,d$ and so on, but \emph{not} on the sample size 
-$n$.  % where possible, we keep track of all constants in our proofs.
-
-\textcolor{red}{Need to fix this Theorem.}
+$n$.
 
@@
   is well-initialized with respect to $\Cset$. Then for any 
-  $$
-  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
-  $$
+  \begin{equation*}
+  n \geq b_0 \cdot 
+  \begin{cases*}
+  \log(n)^{3/2},& ~~\textrm{if $d = 2$,} \\
+  \log(n),& ~~\textrm{if $d \neq 2$}
+  \end{cases*}
+  \end{equation*}
   there exists a set $\Csig[\Xbf]^g 
@@
     \label{eqn: volume_ssd}
-    \Delta(\Cest, \Csig[\Xbf]) \leq c \cdot \kappa(\Cset) \cdot
+    \Delta(\Cest, \Csig[\Xbf]) \leq c_0 \cdot \kappa(\Cset) \cdot
     \vol_{n,r}(\Csig[\Xbf]),  
   \end{equation}
-  with probability at least $1 - b_2/n$. 
+  with probability at least $1 - b_0/n - c_0n\exp\{-b_{11}n\}$. 
 \end{theorem}
@@
     \label{eqn: conductance_additive_error_bound}
-    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq (1 + 4\delta) c_1\frac{d}{\sigma}
+    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq (1 + 4\delta) c_1\frac{dr}{\sigma}
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
-  \end{equation}
-  with probability at least $1 - 3\exp\set{-b n \delta^2}$. 
+      \theta\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
+  \end{equation}
+  with probability at least $1 - 3\exp\set{-b_{10} n \delta^2}$. 
 \end{theorem}
@@
   Also assume that \smash{$0 < r \leq \sigma/(4d)$}. Then for any \smash{$\delta \in \bigl(0,1/(8 + 16/d)\bigr)$}, and any
-  $$
+  \begin{equation}
+  \label{eqn: mixing_time_sample_size}
   n \geq b_1 \cdot (1 + 4\delta) \cdot 
@@
   \end{cases*}
-  $$
+  \end{equation}
   the mixing time satisfies
-  \begin{align} 
+  \begin{equation} 
     \label{eqn: mixing_time_upper_bound}
-    \tau_{\infty}\bigl(G_{n,r}[\Csig[\Xbf]]\bigr) & \leq (1 + 40\delta) c_2 \frac{\Lambda_{\sigma}^4 d^3 
-      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr)\log\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + \\
-  &~~c_3\biggl((1 + 32\delta)d\log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + 1\biggr), 
-  \end{align}
+    \tau_{\infty}\bigl(G_{n,r}[\Csig[\Xbf]]\bigr) \leq (1 + c_3\delta) c_2 \frac{\Lambda_{\sigma}^4 (d + 2)^3 
+      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \ln^2\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{2\lambda_{\sigma}^{2/d}r}\Bigr)
+  \end{equation}
   with probability at least $1 - b_5/n - 4n\exp\{-\delta^2 b_2 n\}$.
@@
 
-%In this supplement, we present proofs and experimental details for the article ``Local Spectral Clustering of Density Upper Level Sets''.
 \section{Proof of Theorem \ref{thm: conductance_upper_bound}}
@@
     \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
-      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
+      \theta\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}
 \end{align*}
@@
 	\begin{align}
-	\cut_{\Pbb,r}(\Csig) &\leq \frac{ d \nu_d r^{d+1} \lambda}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
+	\cut_{\Pbb,r}(\Csig) &\leq \frac{ d \nu_d r^{d+1} \lambda}{\sigma - dr} \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
 	\vol_{\Pbb,r}(\Csig) &\geq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)^{-1} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
@@
 \begin{equation*}
-\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{(1 + \delta)}{(1 - \delta)(1 - dr/\sigma)^2}\frac{d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\sigma \lambda_{\sigma}^2}.
-\end{equation*}
-Noting that $(1 - dr/\sigma)^{-2} \leq 1 + 6dr/\sigma \leq 4$ for all $r \leq \sigma/2d$, the theorem is satisfied by choosing $c_1 = 4$ and $b = (\cut_{\Pbb,r}(\Csig))^2$.
+\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{(1 + \delta)}{(1 - \delta)(1 - dr/\sigma)^2}\frac{d r \lambda \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right)}{\sigma \lambda_{\sigma}^2}.
+\end{equation*}
+Noting that $(1 - dr/\sigma)^{-2} \leq 16/9$ for all $r \leq \sigma/(4d)$, the theorem is satisfied by choosing $c_1 = 16/9$ and $b = (\cut_{\Pbb,r}(\Csig))^2$.
 
@@
 	\begin{equation*}
-	\Pbb(\Csigr) \leq \frac{dr}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
+	\Pbb(\Csigr) \leq \frac{dr}{\sigma - dr} \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
 	\end{equation*}	
@@
 	\begin{equation*}
-	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
+	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma},
 	\end{equation*}
@@
 	\label{eqn: telescoping_sum}
-	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
+	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - \theta(rt_{i,k})^{\gamma} \biggr) \nonumber \\
 	& = \underbrace{\sum_{i = 1}^{k} 
-	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
+	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - \theta(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - \theta(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - \theta r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
 	\end{align}
@@
 	\begin{align}
-	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
+	\Sigma_k & \leq \theta\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
+	& = \theta\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
 	\end{align}
@@
 	\begin{align}
-	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
-	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
-	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
+	\lim_{k \to \infty} \theta\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = \theta\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
+	& \overset{\text{(i)}}{\leq} \theta\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
+	& = \theta\nu(\Csig) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
 	\end{align}
-	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(2d)$.
+	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(4d)$.
 
@@
 	\begin{align}
-	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
-	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}.
+	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
+	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{d r}{\sigma - dr}\right)(\lambda_{\sigma} - \theta r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{dr}{\sigma - dr}(\lambda_{\sigma} - \theta r^{\gamma}) - \theta r^{\gamma} \biggr\}.
 \label{eqn: xi_ub}
@@
 
-%\subsection{Density-weighted cut and volume estimates}
-%\label{sec: density_weighted_cut_and_volume_estimates}
-%
-%For notational ease, we write
-%\begin{align*}
-%\cut_{n,r} = \cut(\Csig[\Xbf]; G_{n,r}), ~ \mu_K = \mathbb{E}(\cut_{n,r}), ~ \cut_{\Pbb,r}(\Csig) = \frac{\mu_K}{{n \choose 2}} \\
-%\vol_{n,r} = \vol(\Csig[\Xbf]; G_{n,r}), ~ \mu_V = \mathbb{E}(\vol_{n,r}), ~ \vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} \\
-%\vol_{n,r}^c = \vol(\Xbf \setminus \Csig[\Xbf]; G_{n,r}), ~ \mu_V^c = \mathbb{E}(\vol_{n,r}^c), ~ \vol_{\Pbb,r}(\Csig)^c = \frac{\mu_V^c}{{n \choose 2}}
-%\end{align*}
-%for the random variable, mean, and probability of cut size and volume, respectively. 
-%
-%\begin{lemma}
-%	\label{lem: expected_density_cut}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-%	\begin{equation*}
-%	\cut_{\Pbb,r}(\Csig) \leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%
-%\end{proof}
-%
-%\begin{lemma}
-%	\label{lem: expected_density_volume}
-%	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
-%	\begin{equation*}
-%	\vol_{\Pbb,r}(\Csig) \geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig)
-%	\end{equation*}
-%\end{lemma}
-%\begin{proof}
-%	The proof will proceed similarly to Lemma \ref{lem: expected_density_cut}. We begin by writing $\vol_{n,r}$ as the sum of indicator functions,
-%	\begin{equation}
-%	\label{eqn: volume_expansion}
-%	\vol_{n,r} = \sum_{i = 1}^{n} \sum_{j \neq i} \1(x_i \in \Csig) \1(x_j \in B(x_i, r))
-%	\end{equation}
-%	and by linearity of expectation we obtain
-%	\begin{equation*}
-%	\vol_{\Pbb,r}(\Csig) = \frac{\mu_V}{{n \choose 2}} = 2 \cdot \Pbb(x_i \in \Csig, x_j \in B(x_i,r)). \tag{for any $i,j$, $i \neq j$. }
-%	\end{equation*}
-%	Writing this with respect to the density function $f$, we have
-%	\begin{align*}
-%	\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
-%	& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
-%	\end{align*}
-%	whence the claim then follows by Lemma \ref{lem: local_conductance}.
-%\end{proof}
-%
-%To employ Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume} in the proof of Theorem \ref{thm: conductance_upper_bound}, we must relate the random variable
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{n,r}}{\min \set{\vol_{n,r}, \vol_{n,r}^c}}
-%\end{equation*}
-%to $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$. 
-%
-%In Lemma \ref{lem: prob_bound_cutvol}, we give probabilistic bounds on the $\cut_{n,r}$, $\vol_{n,r}$ and $\vol_{n,r}^c$ in terms of $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$.
-These bounds are a straightforward consequence of Lemma \ref{lem: bounded_difference}, Hoeffding's inequality for U-statistics.
-%
-%\begin{lemma}
-%	\label{lem: prob_bound_cutvol}
-%	For any $\delta \in (0,1]$,
-%	\begin{equation}
-%	\label{eqn: numerator_additive_bound}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~\text{and}~ \frac{\vol_{n,r}}{{n \choose 2}}, \frac{\vol_{n,r}^c}{{n \choose 2}}  \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}.
-%	\end{equation}
-%	each with probability at least $1 - \delta$. 
-%\end{lemma}
-%
-%\begin{proof}[Proof of Lemma \ref{lem: prob_bound_cutvol}]
-%	From \eqref{eqn: density_cut_expansion} and \eqref{eqn: volume_expansion}, we see that $\cut_{n,r}$ and $\vol_{n,r}$, properly scaled, can be expressed as order-$2$ $U$-statistics,
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_K(x_i, x_j),~~ \frac{\vol_{n,r}}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_V(x_i, x_j)
-%	\end{equation*}
-%	with kernels
-%	\begin{align*}
-%	\phi_K(x_i,x_j) & = \1(x_i \in \Csig, x_j \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, x_i \not\in \Csig, \norm{x_i - x_j} \leq r) \\
-%	\phi_V(x_i,x_j) & = \1(x_i \in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{align*}
-%	
-%	Similarly,
-%	\begin{equation*}
-%	\frac{\vol_{n,r}^c}{{n \choose 2}} = \frac{1}{{n \choose 2}} \sum_{1 \leq i < j \leq n} \phi_{V^c}(x_i, x_j)
-%	\end{equation*}
-%	with kernel,
-%	\begin{equation*}
-%	\phi_{V^c}(x_i,x_j) = \1(x_i \not\in \Csig, \norm{x_i - x_j} \leq r) + \1(x_j \not\in \Csig, \norm{x_i - x_j} \leq r). 
-%	\end{equation*}
-%	
-%	From Lemma \ref{lem: bounded_difference} we therefore have
-%	\begin{equation*}
-%	\frac{\cut_{n,r}}{{n \choose 2}} \leq \cut_{\Pbb,r}(\Csig) + \sqrt{\frac{\log(1/\delta)}{n}},~  \frac{\vol_{n,r}}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig) - \sqrt{\frac{\log(1/\delta)}{n}}, ~ \frac{\vol_{n,r}^c}{{n \choose 2}} \geq \vol_{\Pbb,r}(\Csig)^c - \sqrt{\frac{\log(1/\delta)}{n}}
-%	\end{equation*}
-%	each with probability at least $1 - \delta$. The claim follows in light of \ref{asmp: bounded_volume}, which implies $\vol_{\Pbb,r}(\Csig)^c \geq \vol_{\Pbb,r}(\Csig)$. 
-%\end{proof}
-%
-%\subsection{Proof of Theorem \ref{thm: conductance_upper_bound}}
-%\label{sec: proof_of_theorem_1}
-%
-%The proof of Theorem \ref{thm: conductance_upper_bound} is more or less given by Lemmas \ref{lem: expected_density_cut}, \ref{lem: expected_density_volume}, and \ref{lem: prob_bound_cutvol}.
-All that remains is some algebra, which we take care of below.
-%
-%Fix $\delta \in (0,1]$ and let $\delta' = \delta/3$. We rewrite
-%\begin{equation}
-%\label{eqn: conductance_representation_1}
-%\Phi_{n,r}(\Csig[\Xbf]) = \frac{\cut_{\Pbb,r}(\Csig) + \left(\frac{\cut_{n,r}}{{n \choose 2}} - \cut_{\Pbb,r}(\Csig)\right)}{\vol_{\Pbb,r}(\Csig) + \left(\frac{\min\set{\vol_{n,r}, \vol_{n,r}^c}}{{n \choose 2}} - \vol_{\Pbb,r}(\Csig)\right)}.
-%\end{equation}
-%Assume (\ref{eqn: numerator_additive_bound}) holds with respect to $\delta'$, keeping in mind that this will happen with probability at least $1 - \delta$.
-Along with (\ref{eqn: conductance_representation_1}) this means
-%\begin{equation*}
-%\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}
-%\end{equation*}
-%for $\Err_n = \sqrt{\frac{\log(1/\delta')}{n}}$.
-%Now, some straightforward algebraic manipulations yield
-%\begin{align*}
-%\frac{\cut_{\Pbb,r}(\Csig) + \Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} & = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \left(\frac{\vol_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig) - \Err_n}\right) + \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
-%& = \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + \left(\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 1\right)\frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \\
-%& \leq \frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} + 2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n}.
-%\end{align*}
-%By Lemmas \ref{lem: expected_density_cut} and \ref{lem: expected_density_volume}, we have
-%\begin{equation*}
-%\frac{\cut_{\Pbb,r}(\Csig)}{\vol_{\Pbb,r}(\Csig)} \leq \frac{100rd}{12\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{\left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\lambda_{\sigma}}.
-%\end{equation*}
-%Then, by the choice of sample size in \eqref{eqn: conductance_sample_complexity}, 
-%\begin{equation*}
-%n \geq \frac{(2 + \epsilon)^2 \log\left(\frac{3}{\delta}\right)}{\epsilon^2 \vol_{\Pbb,r}(\Csig)^2}
-%\end{equation*}
-%which implies $2 \frac{\Err_n}{\vol_{\Pbb,r}(\Csig) - \Err_n} \leq \epsilon$.
-
 \section{Proof of Theorem \ref{thm: mixing_time_upper_bound}}
@@
 	\begin{equation*}
-	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \log \left(\frac{1440}{s(G)}\right)\log \left(\frac{14}{s(G)}\right)  + 3 \log \left(\frac{14}{s(G)}\right) + 3
+	\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)} \ln \left(\frac{320}{s(G)}\right)\log_2 \left(\frac{14}{s(G)}\right)  + 3 \log_2 \left(\frac{14}{s(G)}\right) + 3
 	\end{equation*}
@@
 \begin{itemize}
-	\item by~\eqref{eqn: local_spread}, for any constant $c > 0$,
-	\begin{align*}
-	\log\biggl(\frac{1}{s(\wt{G}_{n,r})}\biggr) & \leq d \log\biggl(c^{1/d}\frac{40^{1/d}}{9^{1/d}} \cdot \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \cdot \frac{\lambda_{\sigma}^{2/d}L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \\
-	& \leq d \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(\frac{40^{1/d}}{9^{1/d}} \cdot \frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr)
-	\end{align*}
 	\item By assumption $r/\sigma \leq 1/(4d)$. Thus 
@@
 	\end{align*}
+	\item by~\eqref{eqn: local_spread}, for any constant $c \geq 1$,
+	\begin{align*}
+	\log\biggl(\frac{c}{s(\wt{G}_{n,r})}\biggr) & \leq d \log\biggl(c^{1/d}\frac{40^{1/d}}{9^{1/d}\bigl(1 - \sqrt{\frac{d + 2}{2\pi}}\frac{r}{\sigma}\bigr)^{2/d}} \cdot \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \cdot \frac{\lambda_{\sigma}^{2/d}L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \\
+	& \leq d \frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(c^{1/d}\frac{60^{1/d}}{9^{1/d} } \cdot \frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr)
+	\end{align*}
 \end{itemize}
@@
 \begin{align*}
-\tau_{\infty}(\widetilde{G}_{n,r}) & \leq \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \log \left(\frac{1440}{s(\widetilde{G}_{n,r})}\right)\log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \\
-& \leq \frac{1022(1 + \delta)^{4/d}}{(1 - \delta)^{4/d + 2}} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
-& ~~ 3d\frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 \\
-& \leq 1022\biggl(1 + \Bigl(\frac{32}{d} + 8\Bigr)\delta\biggr) \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)}{r^2 \lambda_{\sigma}^4} \log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \log\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
-& ~~ 3d(1 + 32\delta)\log\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 
-\end{align*}
-where $c_4 := 63, c_5 := 2240$, and the final inequality holds whenever $\delta < 1/(8 + 16/d)$.
-Thus the Theorem holds upon proper choice of universal constants $c_2 = 1022$, $c_3 = 3$, and constants $b_1 = b_3^d + b_4$, $b_2 = \min\{\wt{\vol}_{\Pbb,r}(\Csig), \lambda_{\sigma}\nu_dr^d/8\}$.
+\tau_{\infty}(\widetilde{G}_{n,r}) & \leq \frac{2}{\Phi^2(\widetilde{G}_{n,r})} \ln \left(\frac{320}{s(\widetilde{G}_{n,r})}\right)\log_2 \left(\frac{14}{s(\widetilde{G}_{n,r})}\right)  + 3 \log_2 \left(\frac{14}{s(\widetilde{G}_{n,r})}\right) + 3 \\
+& \leq \frac{1022(1 + \delta)^{4/d}}{(1 - \delta)^{4/d + 2}} \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)^3}{r^2 \lambda_{\sigma}^4} \log_2\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \ln\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
+& ~~ 3d\frac{(1 + \delta)^{2/d}}{(1 - \delta)^{2/d}} \log_2\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 \\
+& \leq 1022\biggl(1 + \Bigl(\frac{32}{d} + 8\Bigr)\delta\biggr) \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)^3}{r^2 \lambda_{\sigma}^4} \log_2\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) \ln\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + \\
+& ~~ 3d(1 + 32\delta)\log_2\biggl(c_4^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr) + 3 \\
+& \leq 1028 \biggl(1 + 40\delta\biggr) \frac{\Lambda_{\sigma}^4\rho^2 L^2 (d + 2)^3}{r^2 \lambda_{\sigma}^4} \ln^2\biggl(c_5^{1/d}\frac{\lambda_{\sigma}^{2/d} L\rho}{\Lambda_{\sigma}^{2/d} 2r}\biggr)
+\end{align*}
+where $c_4 := 94, c_5 := 2134$, and the second to last inequality holds whenever $\delta < 1/(8 + 16/d)$.
+Thus the Theorem holds upon proper choice of universal constants $c_2 = 1028$, $c_3 = 40$, and constants $b_1 = b_3^d + b_4$, $b_2 = \min\{\wt{\vol}_{\Pbb,r}(\Csig), \lambda_{\sigma}\nu_dr^d/8\}$.
 
@@
 	\label{lem: tv_mixing_time}
-	For any $v \in V$, and any $0 < a \leq 1/4$,
+	For any $v \in V$, and any $0 < a < 1/4$,
 	\begin{align}
@@
 	\nonumber \\
-	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t \label{eqn: tv_mixing_time}
+	~~~~~~~~~~~~~~~~~~~~~ + \left(\frac{1}{1 - 2as(G)} +  \frac{1}{2 as(G)}\right) \left(1 - \frac{\Phi^2(G)}{2}\right)^t. \label{eqn: tv_mixing_time}
 	\end{align}
@@
 	\begin{equation*}
-	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
+	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}.
 	\end{equation*}
@@
 the uniform distance $d_{\textrm{unif}}(q_v^{(\tau_1 + 3)}, \pi) \leq \frac{1}{4}$, which proves the claim of Proposition \ref{prop: pointwise_mixing_time}.
-Fix $a = \frac{1}{18}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \log \left(\frac{80}{a s(G)}\right)$, so that
-\begin{equation*}
-\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{as(G)}{80}.
+Fix $a = \frac{1}{12}$, and let $\tau_0 = \frac{2}{\Phi^2(G)} \ln \left(\frac{320}{ s(G)}\right)$, so that
+\begin{equation*}
+\left(1 - \frac{\Phi^2(G)}{2}\right)^{\tau_0} \leq \exp(- \tau_0\Phi^2(G)/2) \leq \frac{s(G)}{320}.
 \end{equation*}
 Recall that by assumption, $\min_{u \in V} \deg(u;G) \geq 10$.
-Moreover note that for $a \leq 1/4$, $2as(G) < 1/2 < 1 - 2as(G)$, since $s(G) \leq 9/10 < 1$.
+Moreover note that since $a = 1/12 \leq 1/4$ and $s(G) \leq 9/10 < 1$, we have $2as(G) < 1/2 < 1 - 2as(G)$.
 By Lemma \ref{lem: tv_mixing_time} we therefore obtain
 \begin{equation*}
-\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{1}{20} + \frac{1}{20}} + \left(\frac{1}{as(G)}\right) \frac{as(G)}{80} \leq \frac{1}{4}.
+\norm{q_v^{(\tau_0 + 3)} - \pi}_{\mathrm{TV}} \leq \max \set{\frac{1}{20}, \frac{1}{8} + \frac{9}{240} + \frac{1}{20}} + \left(\frac{12}{s(G)}\right) \frac{s(G)}{320} = \frac{1}{4}.
 \end{equation*}
 It is a well-known fact (see e.g.~\cite{montenegro2002}) that if $\norm{q_v^{(t)} - \pi}_{\mathrm{TV}} \leq \frac{1}{4}$, then for any $0 < \epsilon < 1$, $\norm{q_v^{(t\log_2(1/\epsilon))} - \pi}_{\mathrm{TV}} \leq \epsilon$.
-Therefore, letting $\tau_1 = (\tau_0 + 3) \log(\frac{14}{s(G)})$,
+Therefore, letting $\tau_1 = (\tau_0 + 3) \log_2(\frac{14}{s(G)})$,
 \begin{equation*}
@@
 	\begin{equation*}
-	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
+	\frac{\nu_dr^d\nu(\mc{S})}{J(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{J(\mc{C}_{\sigma})}
 	\end{equation*}
@@
 \begin{align*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
+\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2J(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
 & \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
@@
 	\begin{equation*}
-	\nu(\cap_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\nu(\mathrm{cap}_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
 	\end{equation*}
@@
 To do so, we apply the following Lemma, which upper bounds the volume of the symmetric set difference in terms of normalized cut and mixing time on an arbitrary graph $G$.
-It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
+It is essentially identical to Lemma 3.4 of~\citep{zhu2013}, except with tighter constants.
 \begin{lemma}
@@
 	\begin{equation*}
-	\alpha \leq \min\Bigl\{\frac{1}{15}, \frac{1}{5\tau_{\infty}(G[A])}\Bigr\},~~ \beta, \varepsilon \leq \frac{1}{4\vol(A;G)}.
+	\alpha \leq \min\Bigl\{\frac{1}{2000}, \frac{1}{2\tau_{\infty}(G[A])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(A;G)},~~ \varepsilon \leq \frac{1}{25\vol(A;G)}
 	\end{equation*}
@@
 	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v};G) \leq \left(\frac{3}{\beta} + \frac{200}{9\vol(A;G)}\right) \frac{\Phi(A;G)}{\alpha}
+	\vol(A \vartriangle S_{\beta,v};G) \leq 6\frac{\Phi(A;G)}{\alpha \beta}.
 	\end{equation*}
@@
 	for the stationary distribution of a random walk over $G[A]$.
-The proof of this Lemma proceeds along very similar lines to that of~\textcolor{red}{(Zhu 2013 Lemma 3.4)}.
-We directly use the following three inequalities, derived in that work:
+The proof of this Lemma proceeds along very similar lines to that of~\citep[Lemma 3.4]{zhu2013}.
+In fact, we directly use the following three inequalities, derived in that work:
 	\begin{itemize}
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.2.)} For any seed node $v \in A$, the following inequalities hold for every $u \in A$:
+		\item \citep[Lemma 3.2]{zhu2013} For any seed node $v \in A$, the PPR vector is lower bounded,
 		\begin{equation}
 		\label{pf:zhu1}
-		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u)
-		\end{equation}
-		\item \textcolor{red}{(Zhu 2013 Corollary 3.3)} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
+		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u),
+		\end{equation}
+		for every $u \in A$.
+		\item \citep[Corollary 3.3]{zhu2013} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
 		\begin{equation}
@@
 		\end{equation}
-		and $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.1, Anderson 2007 Theorem 5.1)} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
+		for all $u \in A$. Furthermore $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
+		\item \citep[Lemma 3.1][Theorem 5.1]{zhu2013,andersen2006} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
 		\begin{equation}
@@
 	\begin{equation*}
-	\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{9}{100\vol(A;G)}.
-	\end{equation*}
-	We conclude that
+	\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{2}{3}\beta,
+	\end{equation*}
+	and we conclude that
 	\begin{equation}
 	\label{pf:zhu5}
-	\vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{200\Phi(A;G)}{9\alpha}.
+	\vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(A;G)}{\alpha\beta}.
 	\end{equation}
@@
 	\end{equation} 
-	The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\ref{pf:zhu6}.
+	The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
 	\end{proof}
@@
 \paragraph{Proof of Theorem~\ref{thm: volume_ssd}.}
-First, we verify that the conditions of Lemma~\ref{lem:zhu} are met when $S = \Cset_{\sigma}[\Xbf]$, $G = G_{n,r}$, and the user-specified parameters satisfy the initialization conditions~\eqref{eqn: initialization}.
-By Theorem~\ref{thm: mixing_time_upper_bound} and \eqref{eqn: initialization}, the teleportation parameter $\alpha$ is upper bounded
-\begin{equation*}
-\alpha < \frac{1}{9\taubf(\theta)} \leq \frac{1}{9\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])}
-\end{equation*}
-with probability at least $1 - \frac{b_2}{n}$.
-Since we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets in Algorithm~\ref{alg: ppr}, we may apply Lemma~\ref{lem:zhu}.
-By this Lemma, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}(\frac{1}{100},\frac{2}{5})$, the sweep cut $S_{\beta,v}$ of $p(\alpha, v; G_{n,r})$ satisfies
+To prove Theorem~\ref{thm: volume_ssd}, we simply apply Lemma~\ref{lem:zhu} to the specific graph $G = G_{n,r}$ and cluster $A = \mc{C}_{\sigma}[\Xbf]$.
+We must first establish that the conditions of Lemma~\ref{lem:zhu} are met in this setting.
+Applying Theorem~\ref{thm: mixing_time_upper_bound} with $\delta = 1/200$ and recalling \eqref{eqn: initialization}, we have that for all $n$ sufficiently large, the following upper bound on $\alpha$:
+\begin{equation*}
+\alpha < \frac{5}{12\taubf(\mc{C})} \leq \min\biggl\{\frac{1}{2000},\frac{1}{2\tau_\infty(G_{n,r}(\Cset_{\sigma}[\Xbf])} \biggr\}
+\end{equation*}
+holds with probability at least $1 - \frac{b_5}{n} - 4n\exp\{-b_2n/200^2\}$.
+Additionally, in Algorithm~\ref{alg: ppr} we use an exact PPR vector $p_v = p_v^{(0)}$ to construct the sweep cut sets.
+Therefore by Lemma~\ref{lem:zhu}, there exists a set $\Csig[\Xbf]^g \subset \Csig[\Xbf]$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any $\beta \leq  \frac{1}{5\vol_{n,r}(\Csig[\Xbf])}$, the sweep cut $S_{\beta,v}$ of $p(\alpha, v; G_{n,r})$ satisfies
 \begin{align}
-\vol_{n,r}(\Csig[\Xbf] \vartriangle S_{\beta,v}) & \leq \left(218\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}\right) \vol_{n,r}(\Csig[\Xbf]) \nonumber \\
-& \leq 2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf]) \label{eqn:volume_ssd_pf1}
+\vol_{n,r}(\Csig[\Xbf] \vartriangle S_{\beta,v}) & \leq \frac{6}{\alpha \beta}\Phi_{n,r}(\mc{C}_{\sigma}) \\
+& \leq \frac{20}{\beta} (1 + 4\delta) \kappa(\mc{C}) \label{eqn:volume_ssd_pf1}
 \end{align}
-where the latter inequality holds with probability at least $1 - 3\exp\set{-bn}$, and follows from Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{10 \tau_u(\theta)}$ given in \eqref{eqn: initialization}.
-
-Now we show that we can apply~\eqref{eqn:volume_ssd_pf1} to the cluster estimate $\Cest$ output by Algorithm~\ref{alg: ppr}.
-Observe that $\Cest$ is itself a sweep cut as $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{50},\frac{1}{5}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
-Moreover, applying  Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/2$,
+where the latter inequality holds with probability at least $1 - 3\exp\set{-1/(36)^2b_{10}n}$, and follows from setting $\delta = 1/36$ in Theorem~\ref{thm: conductance_upper_bound} and the lower bound $\alpha \geq \frac{1}{3 \tau_u(\mc{C})}$ given in \eqref{eqn: initialization}.
+
+Finally, note that $\Cest = S_{\beta,v}$ for some $\beta \in \left(\frac{1}{7},\frac{1}{6}\right)\cdot\frac{1}{2{n \choose 2}\vol_{\Pbb,r}(\Csig)}$.
+Applying  Lemma~\ref{lem:ball_bounds_in_probability} with $\delta = 1/5$, we obtain
 \begin{equation}
 \label{eqn:volume_ssd_pf2}
-\frac{1}{2}\vol_{\Pbb,r}(\Csig) \leq \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq \frac{3}{2}\vol_{\Pbb,r}(\Csig)
-\end{equation}
-with probability at least $1 - 2\exp\{-\frac{1}{4} n \vol_{\Pbb,r}(\Csig)^2\}$.
-Therefore, conditional on \eqref{eqn:volume_ssd_pf2} the cluster estimate $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{1}{100},\frac{2}{5}\right)$, and therefore the upper bound \eqref{eqn:volume_ssd_pf1} holds with respect to $\vol_{n,r}(\Cest \vartriangle \Csig[\Xbf])$.
-To summarize, we have shown that when
-\begin{equation*}
-n \geq b_1(\log(n))^{\max\{\frac{3}{d},1\}}
-\end{equation*}
+\frac{4}{5}\vol_{\Pbb,r}(\Csig) \leq \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq \frac{6}{5}\vol_{\Pbb,r}(\Csig)
+\end{equation}
+with probability at least $1 - 2\exp\{-\frac{1}{25} n \vol_{\Pbb,r}(\Csig)^2\}$; thus $\Cest = S_{\beta,v}$ for some $\beta \in \frac{1}{\vol_{n,r}(\Csig[\Xbf])}\left(\frac{4}{35},\frac{1}{5}\right)$, and from \eqref{eqn:volume_ssd_pf1} we have that
+\begin{equation*}
+\vol_{n,r}(\Cest \vartriangle \Csig[\Xbf]) \leq 175 \cdot \kappa(\mc{C}) \cdot \vol_{n,r}(\mc{C}_{\sigma}[\Xbf]).
+\end{equation*}
+To summarize, we have shown that when $n$ is sufficiently large (as determined by setting $\delta = 1/200$ in ~\eqref{eqn: mixing_time_sample_size})
 then
 \begin{equation*}
-\vol_{n,r}(\Csig[\Xbf] \vartriangle \Cest) \leq  2180 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
-\end{equation*} 
-with probability at least $1 - \frac{b_2}{n} - 3\exp\set{-(b + \frac{1}{4}\vol_{\Pbb,r}(\Csig)^2)n}$.
-We have proved Theorem~\ref{thm: volume_ssd} (upon appropriate choice of constants $b_2$ and $c$ in the theorem statement).
+\vol_{n,r}(\Csig[\Xbf] \vartriangle \Cest) \leq 175 \cdot\kappa(\Cset)\cdot\vol_{n,r}(\Csig[\Xbf])
+\end{equation*} 
+with probability at least $1 - \frac{b_5}{n} - 4n\exp\{-b_2n/200^2\} - 3\exp\set{-(b_{10} + \frac{1}{5}\vol_{\Pbb,r}(\Csig)^2)n}$.
+We have proved Theorem~\ref{thm: volume_ssd} (upon appropriate choice of universal constant $c_0 = 175$, and constants $b_0 = \max\{2b_1, b_5\}$ and $b_{11} = \min\{b_2/200^2, b_{10} + \frac{1}{5}\vol_{\Pbb,r}(\Csig)^2\}$ in the theorem statement).
 
@@
 	\begin{equation*}
-	\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\theta) 
+	\Phi(\Csig[\Xbf]; G_{n,r}) \leq \Phibf(\mc{C}) 
 	\end{equation*}
@@
 	\label{eqn:vol_bound}
-	(1 - \delta)\vol_{\Pbb,r}(\Sset) \leq \frac{\vol_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq 2(1 + \delta)\vol_{\Pbb,r}(\Sset).
+	(1 - \delta)\vol_{\Pbb,r}(\Sset) \leq \frac{\vol_{n,r}(\Sset[\Xbf])}{2{n \choose 2}}\leq 2(1 + \delta)\cut_{\Pbb,r}(\Sset).
 	\end{equation}
@@
 \begin{proof}{(of Lemma~\ref{lem:ball_bounds_in_probability})}
+	\\
+	\\
 	\hfill 
-	\paragraph{Proof of \eqref{eqn:degwt_bound}, \eqref{eqn:degpr_bound}:}
+	\textit{Proof of \eqref{eqn:degwt_bound}, \eqref{eqn:degpr_bound}:}
 	Under~\ref{asmp: bounded_density}, we have that for every $x_j \in \Csig[\Xbf]$
@@
 	Then \eqref{eqn:degwt_bound} and \eqref{eqn:degpr_bound} each follow from Lemma~\ref{lem:bernstein_union}.
-	\paragraph{Proof of \eqref{eqn:volwt_bound}, \eqref{eqn:vol_bound}, \eqref{eqn:cut_bound}:}
-
+	\\
+	\\
+	\noindent \textit{Proof of \eqref{eqn:volwt_bound}, \eqref{eqn:vol_bound}, \eqref{eqn:cut_bound}:}
 	We have that $\frac{1}{2{n \choose 2}}\widetilde{\vol}_{n,r}(\Csig[\Xbf])$, $\frac{1}{2{n \choose 2}}\vol_{n,r}(\Sset[\Xbf])$, $\frac{1}{2{n \choose 2}}\cut_{n,r}(\Sset[\Xbf])$ are each order-2 U statistics, with respective kernels
@@
 	We may therefore apply Lemma~\ref{lem:hoeffding} in each case to obtain the stated bounds.
-
-	\paragraph{Proof of \eqref{eqn:cardinality}:}
+	\\
+	\\
+	\noindent
+	\textit{Proof of \eqref{eqn:cardinality}:}
 	Apply Lemma~\ref{lem:hoeffding_2} to $\Csig$.

### 2021-01-31 jmlr/revision/archive/proofs.tex
Final draft to be submitted to JMLR uploaded, in revision/ppr_clustering_neighborhood_graph

--- 2021-01-27 jmlr/revision/proofs.tex
@@
 \usepackage[shortlabels]{enumitem}
+\usepackage{graphics}
+\usepackage[export]{adjustbox} 
+\usepackage{subcaption}
 \usepackage{mathtools}
@@
 \end{enumerate}
-When $d = 1$, it follows from Proposition~6.2 of \textcolor{red}{Dudley} that $\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_4 \|F - F_n\|_{\infty}$ for some positive constant $B_4$, and in turn from the DKW inequality (\textcolor{red}{Massart}) that
+When $d = 1$, it follows from Proposition~6.2 of \textcolor{red}{Dudley} that $\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_5 \|F - F_n\|_{\infty}$ for some positive constant $B_5$, and in turn from the DKW inequality (\textcolor{red}{Massart}) that
 \begin{equation}
 \label{eqn:ot_distance_1d}
-\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_4 \sqrt{\frac{\ln(2n/B_2)}{n}}
+\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_5 \sqrt{\frac{\ln(2n/B_2)}{n}}
 \end{equation}
@@
 	Suppose $\Pbb$ satisfies~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
-Then, there exists positive constants $B_{2}$ and $B_4$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
-	\begin{equation*}
-	\Delta_{\infty}(\mbb{P},\mbb{P}_n) \leq B_4 \cdot 
+Then, there exists positive constants $B_{2}$ and $B_5$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
+	\begin{equation*}
+	\Delta_{\infty}(\mbb{P},\mbb{P}_n) \leq B_5 \cdot 
 	\begin{dcases*}
@@
 	\label{eqn:conductance_lb_transportation_distance}
-	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{2b_4\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{b_4 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
-	\end{equation}
-	where $b_4 := 2d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
+	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{2B_6\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{B_6 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
+	\end{equation}
+	where $B_6 := 2d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
 \end{proposition}
@@
 	\begin{equation*}
-	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{2 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= b_4} \cdot \Delta_{12},
+	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{2 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= B_6} \cdot \Delta_{12},
 	\end{equation*}
@@
 	\begin{equation*}
-	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq 2 b_4 \cdot \Delta_{12}.
+	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq 2 B_6 \cdot \Delta_{12}.
 	\end{equation*} 
@@
 	\begin{align*}
-	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - b_4 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4\Delta_{12}}\biggr) - \frac{b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2b_4\Delta_{12}} \\
-	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - 2b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{b_4\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
+	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - B_6 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}} \\
+	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - 2B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
 	\end{align*}
@@
 	\begin{equation*}
-	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{2 b_4 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{b_4\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
+	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{2 B_6 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{B_6\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
 	\end{equation*}
@@
 \begin{equation*}
-b_5 := \frac{1}{2b_4}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := \frac{1}{B_4}\min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\},
+b_6 := \frac{1}{2B_6}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := B_5 \Bigl(\min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\}\Bigr)^{-1},
 \end{equation*}
@@
 \begin{equation*}
-\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_4 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_5}{2\Psi_r(\wt{\Pbb})}, b_5, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
 \end{equation*}
@@
 \begin{equation*}
-\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2b_4\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{b_4 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
+\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
 \end{equation*}
@@
 \begin{proof}[Proof of~\eqref{eqn:local_spread_ub}.]
-	\textcolor{red}{(TODO)}
+	The statement follows since 
+	\begin{equation*}
+	d_{\min}(\Pbb) \geq \frac{\pi r^2}{2} \cdot \min_{x \in \mc{X}} f(x) = \frac{\pi r^2}{2} \cdot \frac{\epsilon}{\rho \sigma}
+	\end{equation*}
+	and
+	\begin{equation*}
+	\vol_{\Pbb,r}(\mc{X}) \leq d_{\max}(\Pbb) \leq \frac{\pi r^2}{2 \sigma \rho}.
+	\end{equation*}
 \end{proof}
@@
 B_{1,\delta} & := 768 \cdot (1 + 3\delta) \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr),&&B_{2,\delta} := \frac{(1 + \delta)^2}{(1 - \delta)^2} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \\
-B_4 &:= \frac{6 \sigma \rho}{(\sigma - 2r)(\rho - r)},&&B_5 := 1 + \frac{12\sigma\rho}{r^2} + \frac{2\rho}{r} \\
-b_6 &:=  b_7 \wedge \cut_{\Pbb,r}(\mc{L}) \wedge d_{\min}(\Pbb)/14 \wedge \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}),&&b_7 := \vol_{\Pbb,r}(\mc{X})/4 \wedge \frac{\epsilon r^2}{4\rho\sigma} \wedge \frac{\pi r^3}{8\sigma \rho^2}.
+B_4 & := 1 + \frac{12\sigma\rho}{r^2} + \frac{2\rho}{r},&&b_4 :=  b_8 \wedge \cut_{\Pbb,r}(\mc{L}) \wedge d_{\min}(\Pbb)/14 \wedge \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}), \\
+b_8 &:= \vol_{\Pbb,r}(\mc{X})/4 \wedge \frac{\epsilon r^2}{4\rho\sigma} \wedge \frac{\pi r^3}{8\sigma \rho^2}.
 \end{align*}
@@
 	\label{lem:normalized_cut_lb}
-	Fix $\delta \in (0,1)$. With probability at least $1 - B_5\exp\{-n\delta^2b_7\}$, the following statement holds:
+	Fix $\delta \in (0,1)$. With probability at least $1 - B_4\exp\{-n\delta^2b_8\}$, the following statement holds:
 	\begin{equation}
@@
 \end{equation*}
-It follows from Lemma~\ref{lem:normalized_cut_lb}, Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2} and~\ref{lem:bernstein_union} that these estimates are together satisfied with probability at least $1 - B_5\exp\{-n\delta^2b_7\} - 3\exp\{-n\delta^2 \cut_{\Pbb,r}(\mc{L})\} - (2n + 2)\exp\{-n\delta^2 \cdot d_{\min}(\Pbb)/14\} - 5\exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)})\} \geq 1 - (B_5 + 2n + 10)\exp\{-n\delta^2 b_6\}$.
+It follows from Lemma~\ref{lem:normalized_cut_lb}, Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2} and~\ref{lem:bernstein_union} that these estimates are together satisfied with probability at least $1 - B_4\exp\{-n\delta^2b_8\} - 3\exp\{-n\delta^2 \cut_{\Pbb,r}(\mc{L})\} - (2n + 2)\exp\{-n\delta^2 \cdot d_{\min}(\Pbb)/14\} - 5\exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)})\} \geq 1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$.
 
@@
 	\end{equation} 
-	and otherwise under the same conditions as Theorem~\ref{thm:volume_ssd_ub}, the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_6\delta^2n\}$: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
+	and otherwise under the same conditions as Theorem~\ref{thm:volume_ssd_ub}, the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 2)\exp\{-b_3n\} - 3(n + 3)\exp\{-b_7\delta^2n\}$: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, and moreover
 	\begin{equation}
@@
 \end{equation}
-By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities hold with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 1)\exp\{-b_3n\} - (3n + 3)\exp\{-b_6\delta^2n\}$, taking $b_6 := b_2 \wedge \Pbb(\mc{C}_{\lambda,\sigma}') \cdot d_{\min}(\Pbb')/9$.
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities hold with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 1)\exp\{-b_3n\} - (3n + 3)\exp\{-b_7\delta^2n\}$, taking $b_7 := b_2 \wedge \Pbb(\mc{C}_{\lambda,\sigma}') \cdot d_{\min}(\Pbb')/9$.
 
@@
 \label{sec:experimental_details}
-
-\textcolor{red}{(TODO)}
+Finally, we detail the settings of our experiments, and include an additional figure.
+
+\subsection{Experimental settings for Figure~\ref{fig:bounds}}
+Let $\mc{R}_{\sigma,\rho} = [-\sigma/2,\sigma/2] \times [-\rho/2,\rho/2]$ be the two-dimensional rectangle of width $\sigma$ and height $\rho$, centered at the origin.
+We sample $n = 8000$ points according to the density function $f_{\rho,\sigma,\lambda}$, defined over domain $\mc{X} = [-1,1]^2$ and parameterized by $\rho, \sigma$ and $\lambda$ as follows:
+\begin{equation}
+f_{\rho,\sigma,\lambda}(x) :=
+\begin{dcases}
+\lambda,~~& \textrm{if $x \in R_{\sigma,\rho} - (-.5,0)$ or $x \in R_{\sigma,\rho} + (-.5,0)$} \\
+\frac{4 - 2 \lambda \rho \sigma}{1 - 2\rho\sigma},~~& \textrm{if $x \in \mc{X}$, $x \not\in R_{\sigma,\rho} - (-.5,0)$ and $x \not\in R_{\sigma,\rho} + (-.5,0)$.}
+\end{dcases}
+\end{equation}
+Then $\theta := \lambda - \frac{4 - 2 \lambda \rho \sigma}{1 - 2\rho\sigma}$ measures the difference in density between the density clusters and the rest of the domain.
+The first column displays $n = 8000$ points sampled from three different parameterizations of $f_{\rho,\sigma,\lambda}$:
+\begin{align*}
+\rho &= .913, &&\sigma = .25, &&&(\lambda - \theta)/\lambda = .25 \tag{top panel} \\
+\rho &= (?), &&\sigma = (?), &&&(\lambda - \theta)/\lambda = (?) \tag{middle panel} \\
+\rho &= .5, &&\sigma = .25, &&&(\lambda - \theta)/\lambda = .12 \tag{bottom panel.}
+\end{align*}
+In each of the second, third, and fourth columns, we fix two parameters and vary the third.
+In the second column, we fix $\sigma = .25$, $(\lambda - \theta)/\lambda = .25$, and vary $\rho$ from $.25$ to $2$.
+In the third column, we \textcolor{red}{(?)}.
+In the fourth column, we fix $\rho = .5$, $\sigma = .25$ and vary $(\lambda - \theta)/\lambda$ from $.1$ to $.25$.
+In the second and fourth columns, we take $r = \sigma/8$; in the third column, where we vary $\sigma$, we take $r = .1/8$.
+
+\subsection{Experimental settings for Figure \ref{fig:moons}}
+
+To form each of the three rows in Figure \ref{fig:moons}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+Formally, the (respective) generative models for the data are
+\begin{align}
+Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
+X(Z,\theta) & = 
+\begin{cases}
+\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
+\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
+\end{cases}
+\end{align}
+where 
+\begin{align*}
+\mu_1 & = (-.5, 0),~ \mu_2 = (0,0),~ \epsilon \sim N(0, I_2) \tag{row 1} \\
+\mu_1 & = (-.5, -.07),~ \mu_2 = (0,.07),~ \epsilon \sim N(0, I_2) \tag{row 2} \\
+\mu_1 & = (-.5, -.125),~ \mu_2 = (0,.125),~ \epsilon \sim N(0, I_2) \tag{row 3} 
+\end{align*}
+for $I_d$ the $d \times d$ identity matrix.
+The first column consists of the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the PPR plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+
+\paragraph{Performance of PPR with high-dimensional noise.} Figure \ref{fig:moons_hd} is similar to Figure \ref{fig:moons} of the main text, but with parameters
+\begin{equation*}
+\mu_1 = (-.5, -.025),~ \mu_2 = (0,.025),~ \epsilon \sim N(0, I_{10}).
+\end{equation*}
+The gray dots in $(a)$ (as in the left-hand column of Figure \ref{fig:moons} in the main text) represent observations in low-density regions.
+While the PPR sweep cut $(b)$ has relatively high symmetric set difference with the chosen density cut, it still recovers separates $C_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$, in the sense of Definition \ref{def:density_cluster_consistency}.
+
+\begin{figure}
+	\centering
+	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{../row4_true_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{../row4_ppr_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{../row4_conductance_cluster}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{.24\linewidth}
+			\includegraphics[width=\linewidth]{../row4_density_cluster}
+			\caption{}
+		\end{subfigure}
+		\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
+			cut (column 3) and estimated density (column 4) clusters for two-moons with 10 dimensional noise. Seed node for PPR denoted by a black cross.} 
+		\label{fig:moons_hd}
+	\end{adjustbox}
+\end{figure}
 

### 2021-01-31 jmlr/code/configs/2d_uniform_rectangles_epsilon.R
Updated all code used to form Figure 2 in revised submission.

@@ -13,7 +13,7 @@
 # -----------------------------------------------------------------------------#
 
 # Global parameters
-n_samples <- 8000
+n_samples <- 10000
 n_iters <- 50
 d <- 2
 n_mixtures <- 2
@@ -48,7 +48,7 @@ attributes(domain) <- list("d" = d, "measure" = 4)
 # Parameters
 sigma <- rep(.25,n_distributions)
 rho <- rep(.5,n_distributions)
-density_ratio <- exp(seq(log(.1),log(.5),length.out = n_distributions))
+density_ratio <- exp(seq(log(.1),log(.25),length.out = n_distributions))
 epsilon <- density_ratio/(2*rho*sigma/(4 - 2*rho*sigma) + density_ratio)
 
 # Make distributions

### 2021-01-31 jmlr/code/graph.R

@@ -150,7 +150,7 @@ conductance <- function(G, verbose = TRUE)
   n_runs <- 0                     # How many random initializations?
   n_iters <- 500                  # How many passes over numerator and denominator of ncut?
   n_iters_inloop <- 150           # How many steps of gradient descent?
-  g_0 <- fiedler_vector(G)
+  g_0 <- fiedler_vector(G)        # Initialization at 2nd eigenvector.
   deg <- degree(G)
   theta <- .99
   tol <- 10e-10
@@ -169,6 +169,13 @@ conductance <- function(G, verbose = TRUE)
     } else{
       p <- runif(n = n, min = 0, max = .33)
       h_0 <- g_0 * (2 * rbinom(n = n,size = 1,prob = p) - 1)
+    }
+    
+    # If the 2nd eigenvalue is 0, then fiedler_vector() may not have converged.
+    # In that case, the conductance is 0.
+    if(is.null(g_0)){
+      ncuts[kk] <- 0
+      next
     }
     f_0 <- h_0 - weighted_median(h_0,w = deg); f <- f_0/norm(f_0,type = "2")
     for(ii in 1:n_iters)
@@ -220,7 +227,7 @@ conductance <- function(G, verbose = TRUE)
       # 4. Center (according to degree weighted median) and normalize
       h <- as.numeric(u - weighted_median(u,deg)); f <- h/norm(h,type = "2")
       
-      # 5. If you terminated without improving the energy, take the previous estimate.
+      # 5. If you terminated without improving the energy, take the previous estimate
       if(energy(G,f) > energy(G,f_old)){
         f <- f_old
       }
@@ -229,17 +236,20 @@ conductance <- function(G, verbose = TRUE)
         break
       }
     }
+    
+    # Find the optimal sweep cut
+    opt_sweep_cut <- best_sweep_cut(G,f, c(-1,1))
     if(verbose)
     {
       logger::log_info("Outer loop iterations: ",ii,".")
       logger::log_info("Number of runs: ",kk,".")
       logger::log_info("Energy: ",round(energy(G,f),4),".")
-      logger::log_info("Ncut: ", round(ncut(best_sweep_cut(G,f, c(-1,1)),G),4),".")
+      logger::log_info("Ncut: ", round(ncut(opt_sweep_cut,G),4),".")
[…]

### 2021-01-31 jmlr/code/plot.R

@@ -9,9 +9,9 @@
 #----------------------------------------------------#
 
 # What is to be plotted?
-vectors <- NULL
+vectors <- "samples"
 quantities <- c("normalized_cut", "conductance","local_spread")
-parameter <- "rho"
+parameter <- "sigma"
 
 # Would you like to save plots to file?
 save_plots <- TRUE
@@ -42,6 +42,10 @@ population_bounds <- population_bounds[quantities]
 
 # Data for plotting
 parameter_values <- get(parameter)
+if(parameter == "epsilon"){
+  parameter <- "density_ratio"
+  parameter_values <- 2*rho*sigma/(4 - 2*rho*sigma) * epsilon/(1 - epsilon)
+}
 
 for(ii in 1:n_quantities)
 {
@@ -51,14 +55,23 @@ for(ii in 1:n_quantities)
 } 
 
 # Generic plotting functions.
-generic_2ddata_plot <- function(X,colors,pch){
-  plot(X[,1],X[,2],col = colors, pch = 16, xlab = "x1", ylab = "x2")
+generic_2ddata_plot <- function(X,colors,subsample = FALSE,cex = 2){
+  if(subsample){
+    n <- nrow(X)
+    indx <- sample(1:n,size = 8000)
+    X <- X[indx,]
+    colors <- colors[indx]
+  }
+  plot(X[,1],X[,2],col = colors, pch = 16, xlab = "x1", ylab = "x2",
+       cex.lab = cex, cex.axis = cex)
 }
 
 generic_quantity_plot <- function(x, list_of_ys, log = "xy", xlab = "diameter", ylab = "y",
                       colors, pchs, lwd = 2, cex = cex){
   ylims <- c(.5 * min(unlist(list_of_ys)), 2 * max(unlist(list_of_ys)))
   xlims <- c(min(x),max(x))
+  xlab <- gsub("_", " ", xlab)
+  ylab <- gsub("_", " ", ylab)
   plot(x = x,y = list_of_ys[[1]], ylim = ylims, type = "n",log = log, xlab = xlab,ylab = ylab,
        cex.lab = cex, cex.axis = cex)
   grid(lwd = 3*lwd)
@@ -88,6 +101,7 @@ if(save_plots){
 }
 
 # Plot the samples, the normalized (by degree) PPR vector, and resulting sweep cut
+subsample <- TRUE
 plot_vectors <- if(is.null(vectors)) FALSE else TRUE
 if(plot_vectors){
[…]

### 2021-01-31 jmlr/revision/archive/outline.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}

\title{Outline: Local Spectral Density Clustering}
\date{}
\maketitle

\section{Introduction}

\textbf{(1)} \textbf{Introduce spectral clustering.} The problem of clustering involves partitioning data into sets which satisfy some notion of within-set similarity and between-set difference. In this paper, we focus on spectral clustering, a powerful family of nonparametric clustering algorithms. \textcolor{red}{Perhaps rework this, to immediately introduce relevant results on spectral clustering in a statistical context.}

\textbf{(2)} \textbf{Motivate local spectral clustering.} Spectral clustering suffers from known issues: it is insensitive to geometry, and computationally infeasible. For these reasons, there has been increased interest in local spectral clustering algorithm, and in particular Personal PageRank (PPR).

\textbf{(3)} \textbf{Review what is known.} To date, most analysis of PPR clustering has focused on worst-case guarantees, with respect to an \textit{a priori} fixed graph $G$. For instance, \textcolor{red}{(Andersen et al.)} assume that PPR is appropriately seeded within a candidate cluster $C \subseteq V$, and relate the quality of a cluster estimate $\wh{C}$---as measured by the normalized cut
\begin{equation}
\label{eqn:normalized_cut}
\end{equation}
---to the normalized cut $\Phi(C;G)$ of the candidate cluster.
\textcolor{red}{(Allen-Zhu et al.)} build on this: they introduce a second functional, the \emph{conductance} $\Psi(C;G)$,
\begin{equation}
\label{eqn:conductance}
\end{equation}
and show that if $\Phi(C;G)$ is much smaller than $\Psi(C;G)$, then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$. 
These works, however, are not applicable to the classic statistical setting, where the input data are random samples $\{X_1,\ldots,X_n\}$ drawn from a density $f$, the graph $G$ is a random geometric graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.

\textbf{(4)} \textbf{Establish the gap.} Our work operates in this latter setting, and addresses the following question:
\begin{quote}
	Under what conditions on the density $f$ and candidate cluster $\mc{C} \subset \Rd$ does the PPR cluster estimate $\wh{C}$ approximately recover $\mc{C}$?
\end{quote}
To answer this question, we introduce population-level versions of normalized cut (denoted by $\Phi_{\Pbb,r}(\mc{C})$) and conductance ($\Psi_{\Pbb,r}(\mc{C})$). We show that when $n$ is sufficiently large, with high probability the empirical quantities $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ are close to their population counterparts. As a result, we obtain meaningful upper bounds on the discrepancy between $\wh{C}$ and $\mc{C}$ which depend only on the density $f$ and candidate cluster $\mc{C}$. In the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of $\{x: f(x) \geq \lambda \}$---we establish specific bounds on $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$ that depend on $\lambda$ as well as some other natural parameters. These immediately translate into an upper bound on the difference between $\wh{C}$ and $\mc{C}_{\lambda}$, giving new connections between spectral and density clustering.

\textbf{(5)} \textbf{Organization.} The remainder of this paper is organized as follows. \textcolor{red}{(TODO)}

\section{Background and Setup}
\textbf{(1)} \textbf{Summary of the section.} To more precisely summarize our results, we will first review how to run the PPR algorithm on a neighborhood graph, then define the population-level normalized cut and conductance, and introduce a metric to measure the difference between two clusters.

\subsection{PPR on a neighborhood graph}

\textbf{(2)} \textbf{PPR on a neighborhood graph.} To produce $\wh{C} \subset X$ involves three separate components---forming the neighborhood graph $G_{n,r}$ over the vertices $X$, computing the PPR vector $p$, and outputting a set $\mc{C}$ by a sweep cut.

\subsection{Cluster estimation}

\textbf{(3)} \textbf{Metric between clusters.} We now introduce a way to measure the quality of a cluster estimate: the size of the symmetric set difference $\wh{C} \vartriangle \mc{C}[X]$.

\subsection{Population normalized cut and conductance}
\textbf{(4)} \textbf{Definition of normalized cut and conductance.} Let the population-level \emph{cut} and \emph{volume} be given by,
\begin{equation*}
\mathrm{cut}_{\Pbb,r}(\mc{C},\mc{S}) := \int_{\mc{C}} \int_{\mc{S}} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x)~~ \mathrm{vol}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\Rd} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x).
\end{equation*}

\begin{definition}[Population-level normalized cut]
	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the population normalized cut is
	\begin{equation*}
	\Phi_{\Pbb,r}(\mc{C}) := \frac{\mathrm{cut}_{\Pbb,r}(\mc{C},\mc{C}^c)}{\min\{\mathrm{vol}_{\Pbb,r}(\mc{C}), \mathrm{vol}_{\Pbb,r}(\mc{C}^c)\}}
	\end{equation*}
\end{definition}

Let $\wt{\mathbb{P}}(\cdot) = \mathbb{P}(\cdot|x \in \mc{C})$ be the conditional distribution of $x$, i.e. the distribution with density function
\begin{equation*}
\wt{f}(x) :=
\begin{cases*}
\frac{1}{\mathbb{P}(\mc{C})} f(x),~~ & \textrm{if $x \in \mc{C}$} \\
0,~~ & \textrm{otherwise.}
\end{cases*}
\end{equation*}

\begin{definition}[Population-level conductance]
	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ with density $f$, and radius $r > 0$, the population conductance is
	\begin{equation*}
	\Psi_{\mathbb{P},r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S})
	\end{equation*}
\end{definition}

\textcolor{red}{(TODO)}: (1) These functionals are the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$. (2) It is thus natural that they should play a prominent role in the analysis of spectral clustering. (3) Indeed, similar functionals are used by \textcolor{red}{(Shi, Schiebinger, Garcia-Trillos.)} in the analysis of \emph{global} spectral clustering in a statistical context. We will comment more on the connection between the results of these works, and our own results, in Section~\textcolor{red}{(?)}.

\subsection{Summary of results}
\textbf{(5)} We can now detail our main contributions:

\begin{itemize}
	\item In Proposition~\ref{prop:sample_to_population}, we show that with high probability the empirical quantities $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{\mathbb{P},r}(\mc{C}[X])$ are close to their population-level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$. As a consequence, we establish in Theorem~\ref{thm:volume_ssd_ub} that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small $\Phi_{\Pbb,r}(\mc{C})$. 
	\item We specialize to the case where $\mc{C}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$---and derive specific upper bounds on the normalized cut $\Phi(\mc{C})$ and conductance $\Psi(\mc{C})$, as a function of $\lambda$ as well as some other natural parameters. This immediately translates into an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting, giving new connections between spectral and density clustering.
	\item We also introduce a notion of \emph{density cluster consistency}, and derive conditions under which $\wh{C}$ is a consistent estimate of the density cluster $\mc{C}$.
	\item We give a lower bound, by exhibiting a hard class of densities $\mc{F}$ and corresponding density clusters $\mc{C}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$ will be provably large.
\end{itemize}

\section{Upper bound on the symmetric set difference metric}
\label{sec:ub_symmetric_set_difference}

\textbf{(1)} \textbf{Summary of the section.} In the main result (Theorem~\textcolor{red}{(?)}) of this section, we give a high probability upper bound on $\Delta(\wh{C}, \mc{C}[X])$, in terms of a pair of population-level functionals, the normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$. We build to this Theorem slowly, revealing our general approach, which in essence consists of two modular steps: first, we build on some previous work (mentioned in the Introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to sample-level functionals $\Phi_{n,r}(\mc{C})$ and $\Psi_{n,r}(\mc{C})$, and second we argue that when $n$ is large $\Phi_{n,r}(\mc{C})$ and $\Psi_{n,r}(\mc{C})$ can be suitably bounded by their population-level analogues $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.

We begin by defining both sample- and population-level functionals, as well as reviewing their relevance to the (local) spectral clustering problem.

\subsection{Review of PPR on a fixed graph}

\textbf{(8.3)} \textbf{Existing results in the graph clustering literature.} \textcolor{red}{(Allen-Zhu)} formalizes this intuition but in a different setup, where the input is an arbitrary graph $G = (V,E)$, and the PPR algorithm is properly initialized within a subset of vertices $C \subseteq V$. Loosely speaking, they show that the symmetric set difference metric $\Delta(\wh{C},C)$ is upper bounded whenever the graph normalized cut $\Phi(C;G)$ is sufficiently smaller than the squared graph conductance $\Psi(C;G)^2$, where
\begin{equation*}
\Psi(C;G) := \min_{S \subseteq C} \Phi(S;G[C]).
\end{equation*}
Since these results will play a major part in our analysis, in Lemma~\textcolor{red}{(?)} we restate them for the convenience of the reader.\footnote{Technically speaking, Lemma~3.4 of \textcolor{red}{(Allen-Zhu)} differs from Lemma~\ref{lem:zhu} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in our appendix. Nevertheless, to be clear the essential idea of Lemma~\ref{lem:zhu} is no different than that of \textcolor{red}{(Allen-Zhu)}, and we do not claim any novelty.}. Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$. For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
\begin{equation*}
S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}.
\end{equation*} 
\begin{lemma}[Lemma~3.4 of \textcolor{red}{(Allen-Zhu)}]
	\label{lem:zhu}
	For some $C \subseteq V$, suppose that 
	\begin{equation}
	\label{eqn:zhu_condition}
	\alpha \leq \min\Bigl\{\frac{1}{2000}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)},~~ \varepsilon \leq \frac{1}{25\vol(C;G)}
	\end{equation}
	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
	\begin{equation}
	\label{eqn:zhu_ub}
	\vol(C \vartriangle S_{\beta,v};G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
	\end{equation}
\end{lemma}
As further pointed out in \textcolor{red}{(Allen-Zhu)}, letting
\begin{equation*}
\pi_{\min}(G[C]) := \min_{v \in C} \frac{\deg(v;G[C])}{\vol(G[C])},
\end{equation*}
denote the minimum of the stationary distribution over $C$, it follows from Cheeger's inequality that 
\begin{equation}
\label{eqn:mixing_time_cheeger}
\tau_{\infty}(G[C]) \leq \frac{\log( 1/\pi_{\min}(G[C]))}{\Psi(C;G)^2}.
\end{equation}
Therefore, setting (for instance) $\alpha = \frac{\Psi(C;G)^2}{2\log \vol(C;G)}$ and $\wh{C} = S_{\beta_0,v}$ for $\beta_0 = \frac{1}{5 \vol(C;G)}$, we obtain from~\eqref{eqn:zhu_ub} that 
\begin{equation}
\label{eqn:zhu_ub2}
\frac{\vol(C \vartriangle \wh{C};G)}{\vol(C; G)} \leq 60\frac{\Phi(C;G) \log\bigl( 1/\pi_{\min}(G[C])\bigr)}{\Psi(C;G)^2}.
\end{equation}

\textbf{(9)} \textbf{Improved bounds on mixing time.} Having reviewed the conclusions of \textcolor{red}{(Allen-Zhu)}, we return now to our own setting, where the input data is not a fixed graph $G$ but instead random samples $\{X_1,\ldots,X_n\}$, and our goal is to recover the population set $\mc{C}$. Ideally, we would like to relate the sample normalized cut $\Phi(\mc{C}[X];G_{n,r}) := \Phi_{n,r}(\mc{C}[X])$ and sample conductance $\Psi(\mc{C}[X];G_{n,r})$ to their population analogues, and thereby obtain an upper bound on the symmetric set difference metric which depends only on population-level quantities. Indeed, this will be our general strategy.

Unfortunately, however, there is a catch: since $\pi_{\min}(G_{n,r}[C]) = O(1/n)$, in the limit as $n \to \infty$ the right hand side of~\eqref{eqn:zhu_ub2} grows like $\Omega(\log(n))$, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound.\footnote{In fact, $\pi_{\min}(G)$ is clearly at most $1/n$ for any graph $G$ with $n$ total vertices, not merely $G = G_{n,r}$. However, while in general it may be possible for $\Phi(C;G) \leq \frac{1}{\log(n)} \Psi(C;G)$, this will not be the case in our specific setting, where $G = G_{n,r}$ and $C = \mc{C}[X]$. Hence the need for a sharper bound.} Fortunately, while in the worst  case (over arbitrary input $G$) the ``start penalty'' $\log(1/\pi_{\min}(G_n,r[C]))$ is unavoidable, when $G$ is a geometric graph such as $G_{n,r}$ a better bound can be attained. Intuitively, this is because is in geometric graphs small sets---such as $S = \{v\}$ for any $v \in \mc{C}[X]$---are very good expanders. To precisely capture this, we introduce the \emph{local spread} functional $s(G)$, to delineate what counts as a small set:
\begin{equation*}
s(G) := \frac{9}{10} \cdot \min_{u \in V} \set{\deg(u; G)} \cdot \min_{u \in V} \set{\pi(u)}.
\end{equation*}
The idea is that a random walk will rapidly mix over any set $S \subseteq G$ for which $\vol(S) \leq s(G)$.\footnote{The prefactor $9/10$ in the definition of $s(G)$ is arbitrary. It can be altered to any constant less than $1$, and Proposition~\ref{prop:pointwise_mixing_time} will still hold after appropriate changes to the constants.} In Proposition~\ref{prop:pointwise_mixing_time}, we state an alternative bound that precisely captures this idea.
\begin{proposition}
	\label{prop:pointwise_mixing_time}
	Assume $\min_{u \in V} \deg(u; G) \geq 10$. Then,
	\begin{equation*}
	\tau_{\infty}(G) \leq \frac{2}{\Psi^2(C; G)} \ln \left(\frac{320}{s(G)}\right)\log_2 \left(\frac{14}{s(G)}\right)  + 3 \log_2 \left(\frac{14}{s(G)}\right) + 3
	\end{equation*}
\end{proposition}
Some remarks:
\begin{itemize}
	\item We emphasize that while Proposition~\ref{prop:pointwise_mixing_time} \emph{applies} to any graph $G$ (as long as the minimum degree is at least 10), it is particularly \emph{useful} when $G$ is a geometric graph. In this case, under some typical regularity conditions $s(G) = \Theta(1)$ (treating $r$ as fixed), removing the unwanted $O(\log(n))$ from the upper bound in~\eqref{eqn:zhu_ub2}. We give a precise upper bound on $s(\wt{G}_{n,r})$ in Proposition~\ref{prop:sample_to_population}.
	\item Proof techniques, and related literature. \textcolor{red}{(TODO)}.
\end{itemize}

\subsection{Sample-to-population results}
\textbf{(10)} \textbf{Sample-to-population results.} In Proposition~\ref{prop:sample_to_population}, we establish relationship between the sample normalized cut, conductance, and local spread, and their population-level analogues.

\begin{proposition}
	\label{prop:sample_to_population}
	\textcolor{red}{(TODO)}
\end{proposition}

\textbf{(11)} \textbf{Upper bound on the symmetric set difference metric.} Combining Lemma~\ref{lem:zhu}, Proposition~\ref{prop:pointwise_mixing_time} and~Proposition~\ref{prop:sample_to_population}, we arrive at Theorem~\ref{thm:volume_ssd_ub}, the main result of this section, which gives an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on population-level quantities.

\begin{theorem}
	\label{thm:volume_ssd_ub} 
	\textcolor{red}{(TODO)}
\end{theorem}

Some remarks:
\begin{itemize}
	\item \textbf{Takeaway}
	\item \textbf{(11.1)} \textbf{Comparison with other results.} Particularly the results of \textcolor{red}{(Schiebinger)}. 
	\item \textbf{(11.2)} \textbf{Potential improvements.} Particularly with respect to the dependence on $r$.
\end{itemize}

\section{Density clustering}

\textbf{(1)} \textbf{Summary of section.} We will demonstrate the usefulness of Theorem~\ref{thm:volume_ssd_ub}, by applying it in the setting where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster: that is, a connected component of an upper level set. In Proposition~\textcolor{red}{(?)}, we establish bounds on (a thickened version of) $\Phi(\mc{C})$ and $\Psi(\mc{C})$ in terms of $\lambda$ as well as some other parameters, and thereby on the volume of the symmetric set difference as well. In addition, we review a separate notion of consistency with particular relevance to the density clustering problem, and establish conditions under which local clustering with PPR is consistent in this sense. Finally, we derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster. Viewed as a whole, the results of this section can be summarized as follows: PPR recovers density clusters $\mc{C}$ if and only if they are \emph{geometrically well-conditioned}---meaning not too long and thin--- and \emph{vertically well-separated}---meaning they satisfy a low-noise condition.

\subsection{Background}

\textbf{(2)} \textbf{Background on density clustering.} Density clustering is a widely accepted way of defining the target cluster to be recovered.

\textbf{(3)} \textbf{Handling difficulties with sets of topological measure zero.} \textcolor{red}{(TODO)}

\subsection{Recovery of well-conditioned density clusters}
\label{subsec:recovery_well-conditioned_density_clusters}

\textbf{(4)} \textbf{Definition of geometrically well-conditioned and vertically well-separated sets.} The upper bound in Theorem~\ref{thm:volume_ssd_ub} will be small when  $\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \ll \Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2$ (and also when $s_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ is large). As mentioned, this will be the case when $\mc{C}_{\lambda,\sigma}$ is both \emph{geometrically well-conditioned}---meaning not too long and thin--- and \emph{vertically well-separated}---meaning $f(x)$ drops off sharply around the boundary of $\mc{C}_{\lambda,\sigma}$. We now introduce the parameters that, along with $\sigma$ and $\lambda$, allow us to precisely measure these properties.

\textbf{(5)} \textbf{Upper bounds on population-level functionals.} In Propositions~\ref{prop:density_cluster_normalized_cut}-\ref{prop:density_cluster_conductance}, we establish bounds on $\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the parameters just defined.

\begin{proposition}
	\label{prop:density_cluster_normalized_cut}
	\textcolor{red}{(TODO)}
\end{proposition}

\begin{proposition}
	\label{prop:density_cluster_conductance}
	\textcolor{red}{(TODO)}
\end{proposition}

\textbf{(6)} Some remarks are in order:
\begin{itemize}
	\item \textbf{How Proposition~\ref{prop:density_cluster_conductance} is proved.}
	\item \textbf{How we use the bi-Lipschitz assumption, and what we can do without it.}
	\item \textbf{Constants.} The constants in Propositions~\ref{prop:density_cluster_normalized_cut} and~\ref{prop:density_cluster_conductance} are unlikely to be tight.
\end{itemize}

\textbf{(7)} Applying these propositions along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma})$.

\begin{corollary}
	\label{cor:density_cluster_volume_ssd_ub}
	\textcolor{red}{(TODO)}
\end{corollary}

Some remarks:
\begin{itemize}
	\item \textbf{Compare with the ``blue-sky'' problem}. Offer potential improvements, through algorithms that more explicitly optimize for the minimum normalized cut (e.g. flow-based algorithms).
	\item \textbf{Compare with ``density-defined-distance + spectral clustering'' algorithms.}
	\item \textbf{Comparison with density clustering algorithms.}
\end{itemize}

\subsection{Consistency}

\textbf{(8)} A common notion of consistency in the density clustering literature is \textcolor{red}{(cluster tree)} consistency. Corollary~\ref{cor:density_cluster_volume_ssd_ub} does not imply that $\wh{C}$ is a \textcolor{red}{(cluster tree)}-consistent estimator of $\mc{C}_{\lambda,\sigma}$. In Theorem~\ref{thm:density_cluster_consistent_recovery}, we show that when $\Delta(\wh{C},\mc{C}_{\lambda,\sigma})$ is sufficiently small, $\wh{C}$ is \textcolor{red}{(cluster tree)}-consistent.

\begin{theorem}
	\label{thm:density_cluster_consistent_recovery} \textcolor{red}{(TODO)}
\end{theorem}

\subsection{Negative result}
\textbf{(9)} In this section, we exhibit a hard case for density clustering using PPR; that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
cluster.

\begin{theorem}
\textcolor{red}{(TODO)}
\end{theorem}

Some remarks:
\begin{itemize}
	\item \textbf{Explanation of proof + implications.} Our lower bound is likely to apply to any algorithm which approximates the minimum normalized cut set, including not merely PPR but some of those mentioned above.
	\item \textbf{Clarify the takeaway.} It is not a knock on PPR...
\end{itemize}

\section{Experiments}

\section{Discussion}
In this work, we have analyzed the behavior of PPR in a classical nonparametric statistics context.

Some issues for future work:
\begin{itemize}
	\item \textbf{(Regime as $r \to 0$.)}
	\item \textbf{(Stronger consistency guarantees under smoothness conditions.)}
	\item \textbf{(Sample complexity.)}
\end{itemize}

\end{document}

### 2021-01-31 jmlr/revision/cover_letter.tex

\documentclass{article}
\usepackage{enumerate}

\begin{document}

Please find our attached revised submission titled: Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs. We analyze the Personalized PageRank (PPR) algorithm, a local spectral method for clustering, run over a neighborhood graph, and derive upper bounds with which PPR will recover a generic cluster. We also provide geometric conditions under which the PPR algorithm provably recovers density clusters, and show accompanying lower bounds. No previous publications by any of the authors significantly overlap with the submission. All of the co-authors are aware of the current submission and consent to its review. Thank you for your consideration of this manuscript.

\vspace{.2 in}

Sincerely,

\vspace{.1 in}
Alden Green, Sivaraman Balakrishnan, and Ryan Tibshirani

\end{document}

### 2021-01-31 jmlr/revision/ppr_clustering_neighborhood_graph.tex

--- 2021-01-27 jmlr/revision/local_spectral_clustering_jmlr_revision_2.tex
@@
 \usepackage{hyperref}       % hyperlinks
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	citecolor=blue
+}
 \usepackage{url}            % simple URL typesetting
@@
 
+%%% Norms
+\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
+\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}
+
 %%% Matrices
@@
 \newcommand{\cut}{\mathrm{cut}}
+\newcommand{\diam}{\mathrm{diam}}
 
@@
 	statistical learning setup, where we obtain samples from an unknown nonparametric distribution, and aim to identify sufficiently salient clusters.
-We introduce a pair of population-level functionals---the \emph{normalized cut} and \emph{conductance}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large population conductance.
+We introduce a trio of population-level functionals---the \emph{normalized cut}, \emph{conductance}, and \emph{local spread}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large conductance and local spread.
 We apply our general theory to establish that PPR identifies connected regions of high density (density clusters) that satisfy a set of natural geometric conditions.
@@
 In contrast, in this paper we adopt a classical statistical viewpoint, and examine what the output of local clustering on a data set reveals about the underlying density $f$ of the samples.
-We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C}$, will approximately recover this candidate cluster.
+We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C} \subseteq \Rd$, will approximately recover this candidate cluster.
 We pay special attention to the case where $\mc{C}$ is a \emph{density cluster} of $f$---defined as a connected component of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$---and show precisely how PPR accounts for both geometry and density in estimating a cluster.
@@
 \label{subsec:ppr_clustering}
-We now review the PPR clustering algorithm, and some worst-case guarantees on the quality of the resulting cluster.
-Let $G = (V,E)$ be an undirected, unweighted, and connected graph.
-We denote by $A \in \Reals^{n \times n}$ the adjacency
+We start by reviewing the PPR clustering algorithm. Let $G = (V,E)$ be an undirected, unweighted, and connected graph. We denote by $A \in \Reals^{n \times n}$ the adjacency
 matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
@@
 In practice, exactly solving the system of equations~\eqref{eqn:ppr_vector} to compute the PPR vector may be too computationally expensive.
-To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p^{(\varepsilon)}$}.
+To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p_v^{(\varepsilon)}$}.
 We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
@@
 Our own analysis builds on that of~\cite{zhu2013}, and we give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
-For now, we merely reiterate that the conclusions of \citep{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random neighborhood graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
+For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random neighborhood graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
 
@@
 		\STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
-		\eqref{eqn:sweep_cuts}. 
+		\eqref{eqn:sweep_cuts}.\footnotemark
 		\STATE Return the cluster \smash{$\wh{C} = S_{\beta^*}$}, where  
@@
 \end{algorithm}
+\footnotetext{Technically speaking, for each $\beta \in (L,U) \cap \{p_v(u)/D_{uu}: u \in V\}$.}
 
@@
 
-\subsection{Population normalized cut and conductance}
+\subsection{Population normalized cut, conductance, and local spread}
 Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
@@
 
-Let $\wt{\mathbb{P}}(\cdot) = \mathbb{P}(\cdot|x \in \mc{C})$ be the conditional distribution of $x$, i.e. the distribution with density function
-\begin{equation*}
-\wt{f}(x) :=
-\begin{cases*}
-\frac{1}{\mathbb{P}(\mc{C})} f(x),~~ & \textrm{if $x \in \mc{C}$} \\
-0,~~ & \textrm{otherwise.}
-\end{cases*}
-\end{equation*}
+Let $\wt{\mathbb{P}}(\cdot) = \mathbb{P}(\cdot|x \in \mc{C})$ be the conditional distribution of $x$, i.e let $\wt{\mbb{P}}(\mc{S}) = \wt{\Pbb}(\mc{S} \cap \mc{C})/\wt{\Pbb}(\mc{C})$ for measurable sets $\mc{S} \subseteq \Rd$.
 
@@
 The role played by $s_{\Pbb,r}(\mc{C})$ is somewhat less obvious.
-For now, we mention only that it plays an essential role in obtaining tight bounds on the mixing time of a particular random walk that can be related to the PPR vector, and defer further discussion until later, in Section~\ref{sec:ub_symmetric_set_difference}.
+For now, we mention only that it plays an essential part in obtaining tight bounds on the mixing time of a particular random walk that is closely related to the PPR vector, and defer further discussion until later in Section~\ref{sec:ub_symmetric_set_difference}.
 
@@
 We now informally state our two main upper bounds, regarding the recovery of a generic cluster $\mc{C}$, and a density cluster $\mc{C}_{\lambda}$.
-Theorem~\ref{thm:volume_ssd_ub_informal} informally summarizes the first of our main results, formally stated in Theorem~\ref{thm:volume_ssd_ub}, regarding the recovery of a generic cluster $\mc{C}$, .
+Theorem~\ref{thm:volume_ssd_ub_informal} informally summarizes the first of our main results (formally stated in Theorem~\ref{thm:volume_ssd_ub}) regarding the recovery of a generic cluster $\mc{C}$.
 \begin{theorem}[Informal]
@@
 \end{theorem}
-(In the above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put even more succinctly, we find that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$ (ignoring $\log$ factors).
+(In the above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put even more succinctly, we find that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\bigl(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C}))\bigr)^2$.
 To the best of our knowledge, this gives the first population-level guarantees for local clustering in the nonparametric statistical context.
 
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results, formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}, regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
-For reasons that we explain later, in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
+For reasons that we explain later in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
 The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
-We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under an Lipschitz, Lebesgue-measure-preserving mapping $g$, with Lipschitz constant $L$.
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under an Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $L$.
 We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
 \begin{equation*}
-0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\textrm{for all $x \in \mc{C}_{\lambda,\sigma}$}
+0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\textrm{for all $x \in \mc{C}_{\lambda,\sigma}$},
 \end{equation*}
-while satisfying the low-noise condition 
+while satisfying the following low-noise condition:
 \begin{equation*}
@@
 $L^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
-$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $(\lambda - \theta r^{\gamma}/(\gamma + 1)) \ll \lambda$---then PPR will approximately recover the (thickened) density cluster.
+$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
 
@@
 \begin{itemize}
-	\item In Section~\ref{sec:ub_symmetric_set_difference}, we show that under certain conditions the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ are close to their population level counterparts $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
-As a consequence, we find that $\Delta(\wh{C},\mc{C}[X])$ is small whenever $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\Psi_{\Pbb,r}(\mc{C})^2$, giving the first population-level guarantees for local clustering in a nonparametric statistical context.
-	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$---an object of central interest in the statistical clustering literature, dating back to the work of \citet{hartigan1981}.
-We derive specific upper bounds on the normalized cut $\Phi_{\Pbb,r}(\mc{C}_{\lambda})$ and conductance $\Psi_{\Pbb,r}(\mc{C}_{\lambda})$.
-These upper bounds depend on $\lambda$ as well as some other natural parameters, and immediately result in an upper bound on $\Delta(\wh{C},\mc{C}[X])$ in the density cluster setting (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
-	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ is provably large.
+	\item In Section~\ref{sec:ub_symmetric_set_difference}, we derive bounds on the error of PPR as a function of sample normalized cut, conductance, and local spread.
+We then show that under certain conditions the sample normalized cut, conductance, and local spread are close to their population-level counterparts, with high probability for sufficient number of samples.
+As a result, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ purely in terms of these population functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
+We derive bounds on the population normalized cut, conductance, and local spread of the density cluster, which depend on $\lambda$ as well as some other natural parameters.
+This leads to an upper bound on the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster.
+(Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster is provably large.
 	\item In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
@@
 
-\textcolor{red}{(TODO): Edit this, based on whether or not the Main Results section passes muster. }
-
 \section{Recovery of a generic cluster with PPR}
@@
 We build to this theorem slowly, giving new structural results in two distinct directions.
-First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$.
-Second, we argue that when $n$ is large, $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ can be suitably bounded by their population-level analogues $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$.
+First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$.
+Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues.
 
@@
 When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$.
-Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in our appendix.
+Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in the Appendix.
 Nevertheless, to be clear the essential idea of Lemma~\ref{lem:zhu} is no different than that of~\cite{zhu2013}, and we do not claim any novelty.}
@@
 Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mathbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} grows at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound when the number of samples is sufficiently large.
+Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mathbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound whenever the number of samples is sufficiently large.
 
 To fix this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
-Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the \emph{local spread} of $G$, defined as
+Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the graph local spread, defined as
 \begin{equation*}
@@
 \label{subsec:sample_to_population}
-In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, local spread, and conductance, in terms of their population-level analogues.
-We have already introduced the population normalized cut~\eqref{eqn:population_normalized_cut} and conductance~\eqref{eqn:population_conductance}; denoting $s_{n,r}(\mc{C}[X]) := s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, we now define the population local spread to be
-\begin{equation}
-\label{eqn:local_spread}
-s_{\Pbb,r}(\mc{C}) := \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
-\end{equation}
-where $\deg_{\wt{\Pbb},r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\wt{\Pbb}(y)$ is the expected degree of $x$ in $G_{n,r}\bigl[\mc{C}[X]\bigr]$ (normalized by a factor of $1/(n - 1)$.)
-
+In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, conductance, and local spread in terms of their population-level analogues.
 To establish these bounds, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
@@
 	\label{asmp:bounded_density} 
-	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ such that there exist $f_{\min} \leq 1 \leq f_{\max}$ for which
+	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ with respect to Lebesgue measure. There exist $0 < f_{\min} \leq 1 \leq f_{\max} < \infty$ for which
 	\begin{equation*}
-	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}.
+	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}
 	\end{equation*}
@@
 \end{enumerate}
-In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$,$\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
+In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$, $\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
 We explicitly keep track of all constants in our proofs.
@@
 	\label{prop:sample_to_population_1}
-	Fix $\delta \in (0,1/3)$.
-Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
-There exist positive constants $b_1$ and $b_2$ such that each of the following statements hold.
+	Fix $\delta \in (0,1/3)$. Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
 	\begin{itemize}
@@
 	\label{prop:sample_to_population_2}
-	Fix $\delta \in (0,1/2)$.
-Suppose  $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
-Then there exist positive constants $B_1$,$B_2$, and $b_3$ such that for any $n \in \mathbb{N}$ for which
+	Fix $\delta \in (0,1/2)$. Suppose  $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then for any $n \in \mathbb{N}$ satisfying
 	\begin{equation}
 	\label{eqn:sample_to_population_conductance_sample_complexity}
-	\frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \delta \cdot B_1,
+	B_1 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \delta,
 	\end{equation}
@@
 
-A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Hoeffding's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
+A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
 To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, but otherwise the proof is similarly straightforward.
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
-Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$.
-For further details, we refer to Appendix~\textcolor{red}{(?)}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance.
+Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\mathbb{P}_n$ and $\mathbb{P}$.
+For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
 
@@
 where
-\begin{equation}\
+\begin{equation}
 \label{eqn:alpha_initialization}
-\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)} 
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}.
 \end{equation}
@@
 
-\paragraph{Cluster recovery in symmetric set difference.} By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
+By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
 To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
@@
 \label{eqn:condition_number}
-\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)(1+2\delta)}{(1 - 4\delta)^2(1 - \delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}
+\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)(1+2\delta)}{(1 - 4\delta)^2(1 - \delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}.
 \end{equation}
@@
 Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
-Then there exists a positive constant $B_3$ such that for any $n \in \mathbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
+Then for any $n \in \mathbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
 	\begin{equation}
@@
 	\label{eqn:volume_ssd_ub}
-	\begin{aligned}
-	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 60 \cdot \kappa_{\Pbb,r}(\mc{C},\delta)
-	\end{aligned}
+	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 60 \cdot \kappa_{\Pbb,r}(\mc{C},\delta).
 	\end{equation}
 \end{theorem}
-% The following lines are commented out, because they are superseded by the informal statement of our theorem above.
+% AJG: The following lines are commented out, because they are superseded by the informal statement of our theorem above.
 %
@@
 Second,~\eqref{eqn:schiebinger} depends on $\sqrt{\Phi_{\Pbb,r}(\mc{C})}$ rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citep{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
-Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$ which does not appear in~\eqref{eqn:schiebinger}.
+Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$, which is due to the locally-biased nature of the PPR algorithm, and does not appear in~\eqref{eqn:schiebinger}.
 
@@
 	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
-We formally state and prove this result in our appendix (Corollary~\textcolor{red}{(?)}).
+We formally state and prove this fact in Appendix~\ref{apdx:appr_misclassification_error}.
 \end{itemize}
@@
 \label{sec:ppr_density_cluster}
-We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
-We also derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
+We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
+In Section~\ref{sec:lower_bound}, we also derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
 Together, these results can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if both $\mc{C}_{\lambda}$ and $f$ are well-conditioned, meaning that $\mc{C}_{\lambda}$ is not too long and thin, and that $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near its boundary.
@@
 Under typical uniform continuity conditions, the requirement that the density be lower bounded over $\mc{C}_{\lambda,\sigma}$ will be satisfied.
-We note that such continuity conditions can be weakened---for instance,~\cite{rinaldo2010} define the level sets with respect to a convolution $k \ast \mathbb{P}$ (where $k$ is a continuous kernel on $\Rd$ with compact support), and \cite{steinwart2015} takes the level set with respect to the lower semi-continuous version of $f$---but do not pursue the matter further.
+Such continuity conditions can be weakened (see for instance \citet{rinaldo2010,steinwart2015}) but we do not pursue the matter further.
 
 In summary, our goal is to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
-We have already derived upper bounds on the volume of the symmetric set difference that depend on some population-level functionals of the candidate cluster.
+We have already derived upper bounds on the symmetric set difference of $\wh{C}$ and a generic cluster $\mc{C}$ that depend on some population-level functionals $\mc{C}$.
 What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
@@
 	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
-Suppose that $C_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
-Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
-This will be supported by simulations in Section \ref{sec:experiments}.
-	\item Several modifications of global spectral clustering have been proposed with the intent of making such procedures essentially independent of the geometry of the density cluster $\mc{C}_{\lambda}$.
-For instance,~\citet{pelletier2011,arias-castro2009} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance.
+This will be supported by simulations in Section~\ref{subsec:empirical_behavior_ppr}.
+	\item Several modifications of global spectral clustering have been proposed with the intent of making such procedures essentially independent of the shape of the density cluster $\mc{C}_{\lambda}$.
+For instance,~\citet{arias-castro2009,pelletier2011} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance.
 The resulting procedures come with stronger density cluster recovery guarantees.
@@
 	can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$}.
-In Appendix~\textcolor{red}{(?)}, we show in Theorem~\textcolor{red}{(?)} that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
+In Appendix~\ref{apdx:appr_misclassification_error}, we show that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
 \end{itemize}
@@
 	\label{thm:ppr_lb}
-	Fix $\delta \in (0,1/7)$. Assume the neighborhood graph radius $r < \sigma/2$, that
+	Fix $\delta \in (0,1/7)$. Assume the neighborhood graph radius $r < \sigma/4$, that
 	\begin{equation}
@@
 	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.
-Then the following statement holds with probability at least $1 - (B_5 + 2n + 10)\exp\{-n\delta^2 b_6\}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
+Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
 		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/8$}, such
@@
 	\begin{equation*}
-	\epsilon \geq \sqrt{8 C_{6,\delta}} \left({\frac{\sigma}{\rho}} \log \left(64C_{4,\delta} \cdot \frac{\rho}
+	\epsilon \geq \sqrt{8 C_{3,\delta}} \left({\frac{\sigma}{\rho}} \log \left(64C_{4,\delta} \cdot \frac{\rho}
 	{\epsilon^2 \sigma}\right)\right)^{1/4},
@@
 \end{itemize}
-
-Jointly, these upper and lower bounds give a relatively precise characterization
-of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR. \footnote{It is worth pointing out that the above conclusions are reliant on specific
+Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even when reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific
 (albeit reasonable) ranges and choices of input parameters, which in some
@@
 \label{sec:experiments}
-
 We provide numerical experiments to investigate the tightness of our theoretical results in Section~\ref{sec:ppr_density_cluster}, and compare the performance of PPR with a density clustering algorithm on the ``two moons'' dataset.
-We defer details of the experimental settings to the appendix.
+We defer details of the experimental settings to Appendix~\ref{apdx:experimental_details}.
 
@@
 We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e.
-the bounds on core graph functionals needed for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
-Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities.
-In the first row we vary the diameter $\rho$ of the candidate cluster, in the second row we vary the thickness $\sigma$ of the candidate cluster, and in the last row we vary the magnitude $\theta$ of the density drop.
-In each case, it is encouraging to see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude or less.
+the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
+Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities, when samples are drawn from a mixture of uniform distributions over rectangular clusters.
+In the first row we vary the diameter $\rho$ of the candidate cluster, in the second row we vary the width $\sigma$, and in the third row we vary the ratio $(\lambda - \theta)/\lambda$ of the density within and outside the cluster.
+In almost all cases, it is encouraging to see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude at most.
+The one exception to this is the dependence of local spread on the width $\sigma$; this theoretical deficiency stems from a loose bound on the volume of sets with large aspect ratio (meaning $\rho/\sigma$ is much greater than $1$), but in any case the local spread contributes only $\log$ factors to the ultimate bound on cluster recovery.
 On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
@@
 	\centering
-	\includegraphics[width=0.32\textwidth]{plots/experiment_1/normalized_cut.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/experiment_1/conductance.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/experiment_1/local_spread.pdf}
-	\caption{\it \small Empirical normalized cut, conductance, and local spread (in blue), versus their theoretical upper bounds (in red).
-In the top row we vary the diameter $\rho$, in the middle row we vary the thickness $\sigma$, and in the bottom row we vary the density drop $\theta$.
-\textcolor{red}{(TODO): Add middle and bottom row.}}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/samples5.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/local_spread.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/samples1.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/local_spread.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/samples3.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/local_spread.pdf}
+	\caption{\it \small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
+In the first row we vary the diameter $\rho$, in the second row we vary the thickness $\sigma$, and in the third row we vary the density ratio $(\lambda - \theta)/\lambda$.
+The first column shows $n = 8000$ samples for three different parameter values.}
 	\label{fig:bounds}
@@
 \subsection{Empirical behavior of PPR} 
+\label{subsec:empirical_behavior_ppr}
 In Figure \ref{fig:moons}, to drive home 
-the implications of Section~\ref{sec:ppr_density_cluster}, we show the behavior of PPR,
-as compared with the density clustering algorithm of \citet{chaudhuri2010} on
+the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR
+and the density clustering algorithm of \citet{chaudhuri2010} on
 the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
@@
 Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
-fail.  This supports our main message, which is that PPR recovers only
+fail.  This supports one of our main messages, which is that PPR recovers only
 geometrically well-conditioned density clusters.
@@
 	\includegraphics[width=0.24\textwidth]{../row3_density_cluster}
-	\caption{\it\small True density (column 1), PPR (column 2), normalized
+	\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
 		cut (column 3) and estimated density (column 4) clusters for 3 different 
@@
 
+\bibliography{../../local_spectral_bibliography}
+
 \clearpage
-
-\bibliography{../../local_spectral_bibliography}
+\appendix
+
+\input{appendix.tex}
 

### 2021-09-01 arxiv/examples_section.tex
Cleaned out arxiv folder.

@@
 
-%\newtheoremstyle{aldenthm}
-%{6pt} % Space above
-%{6pt} % Space below
-%{\itshape} % Body font
-%{} % Indent amount
-%{\bfseries} % Theorem head font
-%{.} % Punctuation after theorem head
-%{.5em} % Space after theorem head
-%{} % Theorem head spec (can be left empty, meaning `normal')
-
-%\theoremstyle{aldenthm}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{definition}{Definition}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-
-%\newtheoremstyle{aldenrmrk}
-%{6pt} % Space above
-%{6pt} % Space below
-%{} % Body font
-%{} % Indent amount
-%{\itshape} % Theorem head font
-%{.} % Punctuation after theorem head
-%{.5em} % Space after theorem head
-%{} % Theorem head spec (can be left empty, meaning `normal')
-%
-%\theoremstyle{aldenrmrk}
-%\newtheorem{remark}{Remark}
-%%%%%% End Alden
-
-%\title{Local Spectral Clustering of Density Upper Level Sets}
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to break the
-% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
-% \AND instead of \And before the third author name.
-%
-%\author{
-%Alden Green \And
-%Sivaraman Balakrishnan \And
-%Ryan J. Tibshirani}
-%
-%\begin{document}
-%\maketitle
-%
-%\vspace{0.1in}
-%\begin{abstract}
-
 \newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
@@
 
-\section{Examples}
-\label{sec:examples}
+\section{Lower bound.}
+\label{sec:lower_bound.}
 
-In this section, we demonstrate the implications of our theory, and compare the performance of PPR density clustering to some alternatives, by walking through a series of examples.
-In all of these examples, the generative model under consideration will be a mixture of uniform distributions, plus some noise distribution.
-To formally define this model, we specify a support $\mathcal{X}$ and disjoint subsets $\mathcal{C}_1,\ldots,\mathcal{C}_M$ of $\mathcal{X}$, where $M \geq 2$ is the number of mixture components.
-We sample the background noise uniformly over $\mathcal{C}_0 = \mathcal{X} \setminus \bigcup_{m = 1}^{M} \mathcal{C}_m$, and let $\epsilon \in [0,1]$ be the fraction of background noise.
-The mixture distribution $\Pbb$ is therefore
+To show a lower bound for density clustering using PPR, we exhibit a hard case: that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
+Let $\mathcal{C}_{\sigma}^{(0)}$, $\mathcal{C}_{\sigma}^{(1)}$, and $\mathcal{C}_{\sigma}^{(2)}$ be rectangles in $\Reals^2$,
 \begin{equation*}
-\Pbb = \frac{1 - \epsilon}{M} \sum_{m = 1}^{M} \Psi_m + \epsilon \Psi_0,
+\mathcal{C}_{\sigma}^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times \biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad \mathcal{C}_{\sigma}^{(1)} = \mathcal{C}_{\sigma}^{(0)} - \set{(\sigma,0)}, \quad \mathcal{C}_{\sigma}^{(2)} = \mathcal{C}_{\sigma}^{(0)} + \set{(\sigma,0)} \tag{$0 < \sigma < \rho$}
 \end{equation*}
-where $\Psi_m$ is the uniform distribution over $\Cset_m$.
+and let $\mathbb{P}$ be the mixture distribution over $\mathcal{X} = \mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)} \cup \mathcal{C}_{\sigma}^{(2)}$ given by
+\begin{equation*}
+\mathbb{P} = \frac{1 - \epsilon}{2} \Psi_1 + \frac{1 - \epsilon}{2} \Psi_2 + \frac{\epsilon}{2} \Psi_0,
+\end{equation*}
+where $\Psi_m$ is the uniform distribution over $\mathcal{C}_m$ for $m = 0,1,2$. 
+The density function $f$ of $\Pbb$ is simply
+\begin{equation}
+\label{eqn:lb_density}
+f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(2)}) + \frac{\epsilon}{2}\1(x \in \mathcal{C}_{\sigma}^{(0)})  \right)
+\end{equation}
+so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, $\mathbb{C}_{f}(\lambda) = \set{\mathcal{C}_{\sigma}^{(1)}, \mathcal{C}_{\sigma}^{(2)}}$.
 
-Note that when $\epsilon$ is sufficiently small, for an appropriate choice of threshold $\lambda$ the density clustering will be $\Cbb_f(\lambda) = \set{\Cset_1,\ldots,\Cset_M}$.
-In this setup, therefore, estimating a density cluster is equivalent to recovering a mixture component.
-\subsection{1d uniform example.}
+\subsection{Lower bound for PPR.}
 
-We show the performance of our bounds in a mixture of uniforms in $\Reals$, and compare with the bound obtained via a global spectral clustering approach.
+As the following theorem demonstrates, even when Algorithm~\textcolor{red}{1} is reasonably initialized, if the density cluster $\mathcal{C}_{\sigma}^{(1)}$ is sufficiently geometrically ill-conditioned the cluster estimator $\widehat{C}$ will fail to recover $\mathcal{C}_{\sigma}^{(1)}$.
+Let
+\begin{equation}
+\label{eqn:lower_set}
+\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
+\end{equation}
+\begin{theorem}
+	\label{thm:ppr_lb}
+	Suppose $r < \frac{1}{40}\rho \wedge \frac{1}{4}\sigma$,  $\alpha = 65 \Phi_{\Pbb}(\mathcal{L})$, and $(L,U) = (0,1)$ are inputs to Algorithm~\textcolor{red}{1}. Then, for any
+	\begin{equation}
+	\label{eqn:lb_sample_size}
+	n \geq \max\set{\frac{64}{\epsilon^2 \rho \sigma \pi r^2}, \frac{8}{\epsilon}}
+	\end{equation}
+	the following statement holds: there exists a set $C^{g} \subset \Xbf$ with $\vol(C^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$ such that for any seed node $v \in C^g$, the estimator $\widehat{C}$ computed by Algorithm~\textcolor{red}{1} has symmetric set difference with $\Csig^{(1)}[\Xbf]$ of volume at least
+	\begin{equation}
+	\label{eqn:ppr_lb}
+	\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2} \geq \frac{1}{4} -  c \frac{\sqrt{\frac{\sigma}{\rho}}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
+	\end{equation}
+	with probability at least $1 - c_1 n \exp\set{-c_2n}$, where $c$ is a universal constant and $c_1,c_2$ are constants which do not depend on $n$.
+	Consequently, if
+	\begin{equation*} 
+	\epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
+	\end{equation*}
+	then with high probability $\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2}$ is at least $1/8$. 
+\end{theorem}
 
-\subsection{General uniform example.}
+Note that the factor of $\frac{\sigma}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\textcolor{red}{1}.
 
-We show the performance of our bounds in a mixture of uniforms in $\Reals^d$, and compare with the bound obtained via a density estimation approach.
+Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.
+Although we picked this setting to make the theorem statement simple, our results are easily generalized to $\Reals^d$ and to non-rectangular clusters.
+Additionally, although we state our lower bound with respect to PPR run on neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\frac{\sigma}{\rho}$, the normalized cut of $\Cset_1$ will be much larger than that of $\mathcal{L}$.
+In this case, not merely PPR but any algorithm which approximates the minimum normalized cut is unlikely to recover $\Cset_1$.
+Local spectral clustering algorithms based on truncated random walks \textcolor{red}{Spielman and Teng}, global spectral clustering algorithms \textcolor{red}{Shi and Malik}, and $p$-Laplacian based spectral embeddings \textcolor{red}{Buhler and Hein} all have provable upper bounds on the normalized cut of cluster they output, and thus it stands to reason that all the aforementioned approaches should struggle to estimate $\Cset_1[\Xbf]$.
 
-\subsection{Lower bound.}
+\subsection{Comparison with upper bound.}
 
-The theory we have developed so far gives tighter guarantees for plug-in density cluster estimators than for PPR.
-However, in both cases these are merely upper bounds on the clustering error.
-Now, we provide accompanying lower bounds for the PPR algorithm.
-These will demonstrate that there exist densities for which consistent estimation of density clusters is still possible, but for which \emph{PPR} will provably fail to recover density clusters (with high probability.) Moreover, they will show that the difficulty function $\kappa(\Cset)$ exhibits the right dependence on (some of) the geometric parameters we have introduced.
+To better digest the implications of Theorem~\ref{thm:ppr_lb}, we apply our upper bound to the density function $f$ given in \eqref{eqn:lb_density}.
+Observe that $\Csig^{(1)}$ satisfies each of the assumptions~\textcolor{red}{(A1) - (A5).} In particular
+\begin{enumerate}[label=(A\arabic*)]
+	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in \Csig^{(1)}$.
+	\item The clusters $\Csig^{(1)}$ and $\Csig^{(2)}$ are separated, $\dist(\Csig^{(1)}, \Csig^{(2)}) \geq \sigma$. 
+	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such that $0 < \dist(x,\Csig^{(1)}) \leq \sigma$. Therefore for all such $x$,
+	\begin{equation*}
+	\inf_{x' \in \Csig^{(1)}} f(x') - f(x)  > \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma}.
+	\end{equation*}
+	\item The set $\Csig^{(1)}$ is itself convex, and has diameter $\rho$.
+	\item By symmetry, $\vol_{\Pbb,r}(\Csig^{(1)}) = \vol_{\Pbb,r}(\Csig^{(2)})$ and therefore $\vol_{\Pbb,r}(\Csig^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$. 
+\end{enumerate}
 
-Our hard case will be a mixture of $2$-uniforms with background noise.
-Given $0 < \sigma < \rho$, let $\mathcal{X} = [-1.5\sigma,1.5\sigma] \times [-.5\rho,.5\rho]$, and let $\Cset_1 = [-1.5\sigma,-.5\sigma] \times [.5\rho,1.5\rho]$, $\Cset_2 = [.5\sigma,1.5\sigma] \times [-.5\rho,.5\rho]$, so that the background noise is sampled over $\Cset_0 = [-.5\sigma,.5\sigma] \times [-.5\rho,.5\rho]$.
-We denote the resulting model by $\Pbb(\sigma,\rho,\epsilon)$ to emphasize the dependence of the distribution on the parameters of interest.
+%Technically, this density does not fit nicely into the setup of Theorem~\textcolor{red}{1}, because the sets $\Cset_{\sigma}^{(m)}$ ($ m = 1,2$) play the role of both the $\sigma$-expanded sets and the density clusters themselves.
+However, this truly is only a technical objection.
+One could modify the distribution $\Pbb$ by adding a small amount of mass to the $\sigma$-interior $\Cset^{(m)} = \set{x \in \Cset_{\sigma}^{(m)}: \dist(x,\partial\Cset_{\sigma}) \geq \sigma}$.
+Appropriately choosing a threshold $\lambda > \frac{(1 - \epsilon)}{2\rho\sigma}$, the resulting $\lambda$-density clusters would be $\Cbb_f(\lambda) = \set{\Cset^{(1)},\Cset^{(2)}}$, and their $\sigma$-expansions would resemble the rectangles $\Csig^{(1)}, \Csig^{(2)}$ except with slightly rounded corners.
+%Alternatively, one could directly modify Lemma~\textcolor{red}{6} -- an auxiliary Lemma, used in the proof of Theorem~\textcolor{red}{3}, which establishes an upper bound on the Lebesgue measure of $\Csig + B(0,r)$ -- to hold under the assumption $\Csig$ is a rectangle of width $\sigma$ rather than a $\sigma$-expansion.
+The proof of this Lemma is the only time we use the fact that $\Csig$ is a $\sigma$-expansion of a density cluster.
+\textcolor{red}{(Ryan and Siva.)}
 
-\section{Technical results.}
+\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners.
+To fix this, one can either modify the upper bound (specifically, Lemma~\textcolor{red}{6}) to hold with respect to rectangles of width $\sigma$, or change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
+As these details do not meaningfully change our conclusions, for simplicity we will keep our upper and lower bounds as is.
+\end{remark}
 
-\subsection{Lower bound.}
+If the user-specified parameters are initialized according to \textcolor{red}{(14)}, we may apply Theorem~\textcolor{red}{1}.
+This implies that there exists a set $\Csig^{(1)}[\Xbf] \subset \Csig^{(1)}$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any seed node $v \in \Csig^{(1)}[\Xbf]$, the estimated cluster $\widehat{C}$ output by Algorithm 1 satisfies the following upper bound:
+\begin{equation*}
+\vol_{n,r}(\widehat{C} \vartriangle \Csig^{(1)}[\Xbf]) \leq c \cdot \kappa(\Cset^{(1)}) \cdot \vol_{n,r}(\Csig^{(1)}[\Xbf])
+\end{equation*}
+where the condition number is given by
+\begin{equation*}
+\kappa(\Cset^{(1)}) = c \frac{\epsilon}{\sigma}\left(\frac{\rho^2}{r}\log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2r}\right) + c\right).
+\end{equation*}
 
-Let $\Sset = [-1.5\sigma,1.5\sigma] \times [-\rho/2,0]$. Let the \emph{cut} and \emph{volume} functionals be defined for $\Aset \subset \Rd$ as follows:
+To facilitate comparisons between our upper and lower bounds, assume $\frac{1}{4}\sigma \leq \frac{1}{40}\rho$ and set $r = \frac{1}{4}\sigma$. 
+For some universal constant $c > 0$, the following statements each hold with high probability:
+\begin{itemize}
+\item If the user-specified parameters satisfy \textcolor{red}{(14)} and for $b > 0$,
 \begin{equation*}
-\cut_{\Pbb,r}(\Aset) := \int_{\Aset} \int_{\mathcal{X} \setminus \Aset} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y), \vol_{\Pbb,r}(\Aset) := \int_{\Aset} \int_{\mathcal{X}} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y)
+\epsilon < c\frac{b\sigma^2}{\rho^2 \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2\sigma}\right)}
 \end{equation*}
-and the \emph{normalized cut},
+then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+\item If the user-specified parameters are given as in Theorem~\ref{thm:ppr_lb}, and 
+\begin{equation*}
+\epsilon > c\left({\frac{\sigma}{\rho}} \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\right)^{1/4}
+\end{equation*}
+then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
+\end{itemize}
+
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-geometrically conditioned for recovery using PPR.
+
+\begin{remark}
+	It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
+\end{remark}
+
+%It is worth pointing out that both our lower and upper bounds are stated with respect to specific choices of the input parameters to Algorithm~\ref{alg:ppr}, and that these choices are in fact different in the case of the teleportation parameter $\alpha$ and sweep cut range $(L,U)$.
+At a high level, we do not believe this substantially weakens the takeaway messages of our work: if a density cluster $\mathcal{C}$ is geometrically well-conditioned, then a reasonable initialization of PPR will recover $\Csig[\Xbf]$ with low error, whereas if it is geometrically poorly-conditioned, then a different but also reasonable initialization of PPR will fail to recover $\Csig[\Xbf]$.
+Of course, it would be more satisfying if both our upper and lower bounds could be stated with respect to the same choices of these input parameters.
+Unfortunately, it is not at all obvious how to prove such a claim, as to the best of our knowledge all existing work on PPR assumes similar initialization conditions to the ones we assume; effectively, that the algorithm is well-initialized with respect to the set $S \subset G$ one is interested in recovering.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
+Even so, we reiterate our belief that in tandem our upper and lower bounds represent a substantial step forward in characterizing the behavior of local clustering algorithms in a statistical context \textcolor{red}{(Ryan and Siva)}.
+
+\begin{remark}
+	We also note that our lower bound is of course specific to the PPR algorithm.
+As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
+That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
+Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
+\end{remark}
+
+\clearpage
+
+\section{Proof of Lower Bound.}
+
+To prove Theorem~\ref{thm:ppr_lb}, we will proceeding according to the following steps:
+\begin{enumerate}
+	\item We study the spectral partitioning properties of PPR on an arbitrary graph $G$, and show that when suitably initialized inside a subset $S \subset V$, the normalized cut of the PPR sweep cut is upper bounded by (a function of) $\Phi(S)$.
+	\item We specialize to the graph $G = G_{n,r}$ and the subset $\mathcal{L}[\Xbf] \subset \Xbf$, and show that the normalized cut $\Phi_{n,r}(\mathcal{L}[\Xbf])$ is small (with high probability) when the diameter $\rho$ is large.
+	\item We reason that for the input parameters given in Theorem~\ref{thm:ppr_lb}, the output of Algorithm~\textcolor{red}{1} $\widehat{C}$ must therefore also have small normalized cut.
+	\item On other hand, we show that when the noise parameter $\epsilon$ is not too small, the empirical density cluster $\Csig^{(1)}[\Xbf]$ will have large normalized cut $\Phi_{n,r}(\Csig^{(1)}[\Xbf])$.
+In fact, we generalize this to hold for any set $A \subset \Xbf$ for which the symmetric set distance metric $\Delta(A,\Cset_1[\Xbf])$ is small.
+	\item We conclude that the symmetric set distance metric $\Delta(\widehat{C},\Csig^{(1)}[\Xbf])$ must not be small.
+\end{enumerate}
+
+We devote the subsequent sections to proving each of the aforementioned steps.
+
+\subsection{Spectral partitioning properties of PPR.}
+
+Let $G = (V,E)$ be an undirected, unweighted graph with $m = \abs{E}$ total edges, defined on vertices $V = \set{v_1, \ldots, v_n}$.
+Let $C$ be a subset of the vertices $V$, Recall that for a given $\beta \in (0,1)$ the sweep cut
+\begin{equation*}
+S_{\beta,v} = \set{u \in V: \frac{p_v(u)}{\deg(u;G)} > \beta}
+\end{equation*} 
+The following theorem relates the normalized cut of the sweep sets $\Phi(S_{\beta};G)$ to the normalized cut of $C$; it is stated with respect to the graph functionals 
+\begin{equation*}
+d_{\max} := \max_{u \in V} \deg(u;G), ~~\textrm{and}~~ d_{\min} := \min_{u \in V} \deg(u;G).
+\end{equation*}
+\begin{theorem}
+	\label{thm:conductance_ppr}
+	Let $C \subseteq V$ satisfy the following conditions:
+	\begin{itemize}
+		\item $\vol(C;G) \leq \frac{2}{3}\vol(G)$,
+		\item $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, and
+		\item $\frac{20\Phi(C;G)}{1 + 10\Phi(C;G)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$.
+	\end{itemize}
+	Suppose $60\Phi(C;G) \leq \alpha \leq 70\Phi(C;G)$, and let $(L,U) = (0,1)$.
+Then, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$ such that for any $v \in C^g$ the following statement holds: For the PPR vector $p_v := p(v,\alpha;G)$, the minimum conductance sweep cut set satisfies
+	\begin{equation*}
+	\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G) \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C;G)}
+	\end{equation*}
+\end{theorem}
+Although this theorem appears quite similar to standard results in the PPR literature -- for instance, Theorem 6 of \textcolor{red}{Anderson,Chung,Lang} -- crucially the above bound depends on $\log\left(\frac{m}{d_{\min}^2}\right)$ rather than $\log m$.
+In the case where $d_{\min} \asymp n$, this amounts to replacing a factor of $O(\log m)$ by a factor of ${O}(1)$, and therefore allows us to obtain meaningful results in the limit as $m \to \infty$.
+
+Notwithstanding these improvements, the proof of Theorem~\ref{thm:conductance_ppr} follows the same general outline as the proof of Theorem~6 of \textcolor{red}{Anderson,Chung,Lang}.
+We now walk through this outline step by step, modifying the results of \textcolor{red}{Anderson,Chung,Lang} as needed.
+As with their work, we begin by proving a mixing time bound on the PPR vector $p_v$.
+
+\subsubsection{Mixing time of PPR.}
+
+To quantify the mixing of a PPR vector $p_v$, we introduce the function $p[\cdot]: [0,2m] \to [0,1]$.
+For $j = 1,\ldots,n$, let $\beta_j$ be the smallest value of $\beta \in (0,1)$ such that $S_{\beta_j}$ contains at least $j$ vertices.
+(For notational ease, we will write $S_{i} := S_{\beta_i}$, so that $S_1,S_2,\ldots,S_n$ comprise the $n$ unique sweep cuts of $p_v$.)
+For each $j = 1,\ldots,n$, we let $p[\vol(S_j)] =  \sum_{u \in S} p_v(u)$.
+Additionally, we let $p[0] = 0$ and $p[2m] = 1$.
+Finally, we extend $p[\cdot]$  by piecewise interpolation to be defined everywhere on its domain.
+The mixedness of the PPR vector is then measured by the function $h:[0,2m] \to [0,1]$, defined as
+\begin{equation*}
+h(k) = p[k] - \frac{k}{2m}.
+\end{equation*}
+Next, for a given $0 \leq K_0 \leq m$, let 
+\begin{equation*}
+L_{K_0}(k) = \frac{2m - K_0 - k}{2m - 2K_0}h(K_0) + \frac{k - K_0}{2m - 2K_0}h(2m - K_0)
+\end{equation*}
+be the linear interpolator of $h(K_0)$ and $h(2m - K_0)$, and additionally let
+\begin{equation*}
+C(K_0) = \max\set{\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}}: K_0 < k < 2m - K_0}.
+\end{equation*}
+where we use the notation $\overline{k} := \min\{k, 2m - k\}$.
+
+Theorem~\ref{thm:mixing_time_PPR} implies that if the PPR random walk is not well mixed, then some sweep cut of $p_v$ must have small normalized cut.
+\begin{theorem}
+	\label{thm:mixing_time_PPR}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector, and let $\phi$ be any constant in $[0,1]$. Then, either the following bound holds for any integer $t$, any $0 < K_0 < m$, and any $k \in [K_0,2m - K_0]$:
+	\begin{equation}
+	\label{eqn:mixing_time_PPR}
+	h(k) \leq \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}}\left(1 - \frac{\phi^2}{8}\right)^t
+	\end{equation}
+	or else there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
+\end{theorem}
+
+\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_PPR}).]
+The proof of Theorem~\ref{thm:mixing_time_PPR} is essentially a combination of the proofs of Theorem~3 in \textcolor{red}{Anderson,Chung,Lang} and Theorem 1.2 in \textcolor{red}{Lovasz and Simonovits.} We will show that if $\Phi(S_j) > \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in (K_0,2m - K_0)$.
+
+We proceed by induction on $t$. Our base case will be $t = 0$. Observe that $C(K_0) \cdot \sqrt{\overline{k}} \geq  h(k) - L_{K_0}(k)$ for all $k \in [K_0,2m - K_0]$, which implies
+\begin{equation*}
+L_{K_0}(k) + C(K_0) \cdot \sqrt{\overline{k}} \geq h(k).
+\end{equation*}
+
+Now, we proceed with the inductive step.
+By the definition of $L_{K_0}$, the inequality~\eqref{eqn:mixing_time_PPR} holds when $k = K_0$ or $k = 2m - K_0$.
+We will additionally show that~\eqref{eqn:mixing_time_PPR} holds for every $k_j = \vol(S_j), j = 1,2,\ldots,n$ such that $k_j \in [K_0, 2m - K_0]$.
+Once this is shown, the concavity of the expression on the right hands side of~\eqref{eqn:mixing_time_PPR} implies that the inequality holds for all $k \in [K_0,2m - K_0]$.
+
+By Lemma 5 of \textcolor{red}{Anderson,Chung,Lang}, we have that
+\begin{align}
+p[k_j] & \leq \alpha + \frac{1}{2}  \left(p[k_j - \abs{\partial(S_j)}] + p[k_j + \abs{\partial{S_j}}]  \right) \nonumber\\
+& \leq \alpha + \frac{1}{2} \left(p[k_j - \Phi(S_j) \overline{k}_j] + p[k_j + \Phi(S_j) \overline{k}_j]  \right) \nonumber \\
+& \leq \alpha + \frac{1}{2} \left(p[k_j - \phi \overline{k}_j] + p[k_j + \phi \overline{k}_j]\right) \nonumber
+\end{align}
+and subtracting $k_j/2m$ from both sides, we get
+\begin{equation}
+\label{eqn:mixing_time_PPR_pf1}
+h(k_j) \leq \alpha + \frac{1}{2} \bigl(h(k_j - \phi \overline{k}_j) + h(k_j +  \phi \overline{k}_j) \bigr)
+\end{equation}
+From this point, we divide our analysis into cases.
+
+\textbf{Case 1.}
+Assume $k_j - 2 \phi \overline{k}_j$ and $k_j + 2 \phi \overline{k}_j$ are both in $[K_0,2m  - K_0]$.
+We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
+\begin{align*}
+h(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \overline{k}_j) + L_{K_0}(k_j + \phi \overline{k}_j) + C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k_j - \phi \overline{k}_j}} + \sqrt{\overline{k_j + \phi \overline{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+& \leq \alpha t + L_{K_0}(k) + \frac{1}{2}\biggl(C(K_0)\bigl(\sqrt{\overline{k}_j - \phi \overline{k}_j} + \sqrt{\overline{k}_j + \phi \overline{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
+\end{align*}
+A Taylor expansion of $\sqrt{1 + \phi}$ around $\phi = 0$ yields the following bound:
+\begin{equation*}
+\sqrt{1 + \phi} + \sqrt{1 - \phi} \leq 2 - \frac{\phi^2}{4},
+\end{equation*}
+and therefore
+\begin{equation*}
+h(k_j) \leq  \alpha t + L_{K_0}(k) + \frac{C(K_0)}{2}\cdot \sqrt{\overline{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k) + C(K_0)\sqrt{\overline{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
+\end{equation*}
+
+\textbf{Case 2.}
+
+Now, assume one of $k_j - 2 \phi \overline{k}_j$ or $k_j + 2 \phi \overline{k}_j$ is not in $[K_0,2m  - K_0]$.
+Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \phi \overline{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$.
+By the concavity of $h$, and applying the inductive hypothesis to $h(2k_j - K_0)$, we have
+\begin{align*}
+h(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
+& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0) + L_{K_0}(2k_j - K_0\bigr) + C(K_0)\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
+& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \frac{\sqrt{2\overline{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
+& \leq \alpha t + L_{K_0}(k_j) + C(K_0) \sqrt{\overline{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
+\end{align*}
+\end{proof}
+
+As a sanity check, we confirm that Theorem~\ref{thm:mixing_time_PPR} is no weaker than Theorem~3 of \textcolor{red}{Anderson, Chung,Lang}.
+It is not hard to show that $h(k) \leq \min\{1,\sqrt{k}\}$, and therefore that $C(K_0) \leq 1$ for any $K_0$.
+Setting $K_0 = 0$ in Theorem~\ref{thm:mixing_time_PPR}, we therefore recover Theorem~3 of \textcolor{red}{Anderson, Chung,Lang}.
+
+We now proceed to identify when Theorem~\ref{thm:mixing_time_PPR} may offer some improvement on Theorem~3 of \textcolor{red}{Anderson, Chung,Lang}, by showing when we can upper bound $C(K_0) << 1$.
+The critical point is that since $h(k)$ is concave and $L_{K_0}(K_0) = h(K_0)$ the upper bound
+\begin{equation*}
+\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq h'(K_0) \sqrt{k}
+\end{equation*}
+holds whenever $k < m$. For similar reasons, when $k > m$, 
+\begin{equation*}
+\frac{h(k) - L_{K_0}(k)}{\sqrt{\overline{k}}} \leq -h'(2m - K_0) \sqrt{2m - k}.
+\end{equation*} 
+(Since $h$ is not differentiable at points $k = \vol(S_j)$, here we use $h'$ to denote the left derivative of $h$ whenever $k < m$, and the right derivative of $h$ whenever $k \geq m$)
+
+The following Lemma gives good estimates for $h'(K_0)$ and $h'(2m - K_0)$, and a resulting upper bound on $C(K_0)$.
+\begin{lemma}
+	\label{lem:linearization_bound}
+	There exists $K_0 \in \set{0,\deg(v;G)}$ such that
+	\begin{equation}
+	\label{eqn:left_derivative}
+	h'(K_0) \leq  \frac{1}{2d_{\min}^2}.
+	\end{equation}
+	Additionally, for all $K_0 \in [0,2m]$,
+	\begin{equation}
+	\label{eqn:right_derivative}
+	h'(2m - K_0) \geq -\frac{d_{\max}}{d_{\min}\vol(G)}.
+	\end{equation}
+	As a result,
+	\begin{equation*}
+	C(K_0) \leq \frac{\sqrt{m}}{d_{\min}^2}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
+	The result of the Lemma is obvious once we show \eqref{eqn:left_derivative} and \eqref{eqn:right_derivative}.
+To show either inequality, it will be useful to work with an alternative representation of $h$.
+In particular,  whenever $\vol(S_j) \leq k < \vol(S_{j + 1})$ (where we let $S_0 = \emptyset$), the function $h(k)$ may be written as
+	\begin{equation}
+	\label{eqn:lovasz_simonovits}
+	h(k) = \sum_{i = 0}^{j} \left(p_v(u_{(i)}) - \pi(u_{(i)};G)\right) + \frac{\bigl(k - \vol(S_j;G)\bigr)}{\deg(u_{(j + 1)};G)} \left(p_v(u_{(j+1)}) - \pi(u_{(j+1)};G)\right) 
+	\end{equation}
+	where the vertices are ordered $\frac{p_v(u_{(1)})}{\deg(u_{(1)};G)} \geq \frac{p_v(u_{(2)})}{\deg(u_{(2)};G)} \geq \cdots \geq \frac{p_v(u_{(n)})}{\deg(u_{(n)};G)}$, and as usual $\pi(u;G) = \frac{\deg(u;G)}{\vol(G)}$.
+
+	From this representation, it is not hard to verify that the left derivative $h'(k)$ can be upper bounded
+	\begin{equation}
+	\label{eqn:linearization_bound_pf1}
+	h'(k) \leq \frac{p(v_{(j + 1)})}{\deg(v_{(j + 1)};G)}
+	\end{equation}
+
+	We now upper bound $p(u)$ uniformly over all $u$ except the seed node $v$. For any $u \in V$ besides the seed node $v$, we can show by induction that
+	\begin{equation*}
+	e_v W^t(u) \leq \frac{1}{2 d_{\min}}
+	\end{equation*} 
+	for any $t \geq 0$, and therefore
+	\begin{equation}
+	\label{eqn:linearization_bound_pf2}
+	p(\alpha,\chi_v)(u) = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \chi_v W^t(u) \leq  \frac{1}{2d_{\min}}.
+	\end{equation}
+	As a result, by \eqref{eqn:linearization_bound_pf1}, for either $K_0 = \deg(v;G)$ (in the case where $v_{(1)} = v$) or otherwise for $K_0 = 0$, the inequality $h'(K_0) \leq \frac{1}{2d_{\min}^2}$ holds, proving \eqref{eqn:left_derivative}.
+The inequality \eqref{eqn:right_derivative} follows immediately from the representation \eqref{eqn:lovasz_simonovits}, since
+	\begin{equation*}
+	h'(k) \geq -\frac{\pi(v_{(j+1)})}{d(v_{(j + 1)})} \geq -\frac{\pi_{\max}}{d_{\min}},
+	\end{equation*}
+	and the proof of the Lemma is therefore complete.
+\end{proof}
+
+To apply Theorem~\ref{thm:mixing_time_PPR}, we must also upper bound the linear interpolator $L_{K_0}(k)$.
+Of course, trivially $L_{K_0}(k) \leq \max\set{h(K_0), h(2m - K_0)}$ for all $k$.
+As it happens, this observation will lead to a sufficient upper bound on $L_{K_0}$.
+\begin{lemma}
+	\label{lem:interpolator_bound}
+	Assume $s = \chi_v$ for some $v \in V$. Let $K_0 = \vol(S_j)$ for some $j = 0,\ldots,n$. Then, 
+	\begin{equation*}
+	h(2m - K_0) \leq \frac{K_0}{2m} ~\mathrm{and}~ h(K_0) \leq \frac{K_0}{2d_{\min}^2} + \frac{2\alpha}{1 + \alpha}.
+	\end{equation*}
+	and as a result for any $k \in \Reals$,
+	\begin{equation*}
+	L_{K_0}(k) \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2}.
+	\end{equation*}
+\end{lemma}
+\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound})]
+	We make use of the representation~\eqref{eqn:lovasz_simonovits} to prove the desired upper bounds on $h(2m - K_0)$ and $h(K_0)$. We first upper bound $h(2m - K_0)$,
+	\begin{align*}
+	h(2m - K_0) & = \sum_{i = 1}^{j} p(v_{(i)}) - \pi(v_{(i)}) \\
+	& \leq 1 - \sum_{i = 1}^{j} \pi(v_{(i)}) \\
+	& = 1 - \sum_{i = 1}^{j} \frac{d(v_{i})}{2m} = \frac{K_0}{2m}.
+	\end{align*}
+
+	We will upper bound $h(K_0)$ by $p[\vol(S_j)] \leq p_v(v) + \sum_{u \in S_j \setminus \set{v}}p_v(u)$.
+In the proof of Lemma~\ref{lem:linearization_bound} we have already given an upper bound on $p_v(u)$ when $u \neq v$.
+Now, we additionally observe that for all $t$,
+	\begin{equation*}
+	e_vW^t(v) \leq \frac{1}{2d_{\min}} + \left(\frac{1}{2}\right)^t
+	\end{equation*}
+	and therefore $p_v(v) \leq \frac{1}{2d_{\min}} + \frac{2\alpha}{1 + \alpha}$.
+	As a result,
+	\begin{equation}
+	h(K_0) \leq \frac{2\alpha}{1 + \alpha} + \frac{\abs{S_j}}{2d_{\min}} \leq \frac{2\alpha}{1 + \alpha} + \frac{K_0}{2d_{\min}^2},
+	\end{equation}
+	where the latter inequality follows since $K_0 = \vol(S_j) \geq \abs{S_j}\cdot d_{\min}$.
+\end{proof}
+
+Combining Theorem~\ref{thm:mixing_time_PPR}, Lemma~\ref{lem:linearization_bound} and Lemma~\ref{lem:interpolator_bound}, we have the following result.
+\begin{corollary}
+	\label{cor:mixing_time_PPR}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$, and let $\phi$ be any constant in $[0,1]$.
+Then, either the following bound holds for any integer $t$ and any $k \in [d_{\max},2m - d_{\min}]$:
+	\begin{equation*}
+	h(k) \leq \alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t}
+	\end{equation*}
+	or there exists some sweep cut $S_j$ of $p_v$ such that $\Phi(S_j;G) < \phi$.
+\end{corollary}
+
+We arrive now at the main result of this section.
+It is similar in form to Theorem 2 of \textcolor{red}{Anderson,Chung,Lang} but reflects the improvements due to using Corollary~\ref{cor:mixing_time_PPR}.
+To simplify notation, we will write the total mass placed by $p_v$ on a subset $S \subset V$ as $p_v(S) := \sum_{u \in S} p_v(u)$.
+\begin{theorem}
+	\label{thm:mixing_time_PPR_contrapositive}
+	Let $p_v = p(v,\alpha;G)$ be a PPR vector with seed node $v \in V$. Suppose there exists some $\delta > \frac{2\alpha}{1 + \alpha} + \frac{d_{\max}}{2d_{\min}^2}$, such that
+	\begin{equation}
+	\label{eqn:mixing_time_PPR_contrapositive_1}
+	p_v(S) - \frac{\vol(S;G)}{\vol(G)} > \delta
+	\end{equation}
+	for a set $S$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$. Then there exists a sweep cut $S_j$ of $p$, such that
+	\begin{equation*}
+	\Phi(S_j) < \sqrt{\frac{16\alpha\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
+	\end{equation*}
+	where $\delta' = \delta - \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2}$. 
+\end{theorem}
+\begin{proof}
+	Suppose the assumption of the theorem is satisified, that is there exists a set $S \subset V$ with cardinality $\abs{S} \geq \frac{d_{\max}}{d_{\min}}$ which satisfies \eqref{eqn:mixing_time_PPR_contrapositive_1}.
+Then for $j = \abs{S}$ the sweep cut $S_j$ has volume at least $d_{\max}$, and by hypothesis $h(\vol(S_j)) >  \delta$.
+
+	Now, letting
+	\begin{equation*}
+	t = \frac{8}{\phi^2}\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}, \quad \phi^2 = \frac{16\alpha\set{\log\left(\frac{m}{d_{\min}^2}\right) + \log(\frac{2}{\delta'})}}{\delta'}
+	\end{equation*}
+	we have that
+	\begin{equation*}
+	\alpha t + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\sqrt{m}}{d_{\min}^2} \cdot \sqrt{\overline{k}} \left(1 - \frac{\phi^2}{8}\right)^{t} \leq \frac{\delta'}{2} + \frac{2\alpha}{1 + \alpha} + \frac{d(v)}{2d_{\min}^2} + \frac{\delta'}{2} < \delta,
+	\end{equation*}
+	and the Theorem follows by Corollary~\ref{cor:mixing_time_PPR}.
+\end{proof}
+
+\subsubsection{Improved Local Partitioning with PPR.}
+
+As in \textcolor{red}{Anderson,Chung,Lang}, the mixing time results of the previous section lead to an upper bound on the normalized cut $\Phi(\widehat{C};G)$.
+First, we restate a theorem of \textcolor{red}{Anderson,Chung,Lang} which lower bounds the probability mass $p(v,\alpha;G)(C)$ as a function of the normalized cut $\Phi(C)$.
+
+\begin{theorem}
+	\label{thm:acl_3}
+	For any set $C$ and any constant $\alpha$, there exists a subset $C^g \subset C$ with $\vol(C^g;G) \geq \frac{5}{6}\vol(C;G)$, such that for any vertex $v \in C^g$, the PPR vector $p(v,\alpha;G)$ satisfies
+	\begin{equation*}
+	p(v,\alpha;G) \geq 1 - 6\frac{\Phi(C;G)}{\alpha}.
+	\end{equation*}
+\end{theorem}
+We are now in a position to prove Theorem~\ref{thm:conductance_ppr} by combining Corollary~\ref{cor:mixing_time_PPR} and Theorem~\ref{thm:acl_3}.
+
+\begin{proof}[Proof (of Theorem~\ref{thm:conductance_ppr})]
+	Since $\alpha \geq 60\Phi(C)$ and $v \in C^g$, by Theorem~\ref{thm:acl_3},
+	\begin{equation*}
+	p_v(C) \geq \frac{9}{10}.
+	\end{equation*}
+	This inequality along with the assumption $\vol(C) \leq \frac{2}{3}\vol(G)$ implies that $p_v(C) - \frac{\vol(C)}{\vol(G)} \geq \frac{1}{5}$.
+Since we assume $\abs{C} \geq \frac{d_{\max}}{d_{\min}}$, the hypothesis of Theorem~\ref{thm:mixing_time_PPR_contrapositive} is satisfied with $\delta = 1/5$.
+Therefore, the minimum conductance sweep cut satisfies
+	\begin{equation*}
+	\min_{j = 1,\ldots,n} \Phi(S_j;G) \leq \sqrt{\frac{1120\cdot \Phi(C;G)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
+	\end{equation*}
+	Finally, we assume $\frac{20\Phi(C)}{1 + 10\Phi(C)} + \frac{d_{\max}}{2d_{\min}^2} \leq \frac{1}{10}$ which implies that
+	\begin{equation*}
+	\delta' = \delta - \frac{20\alpha}{1 + 10\alpha} + \frac{d_{\max}}{2d_{\min}^2} \geq \frac{1}{10} 
+	\end{equation*}
+	completing the proof of the theorem.
+\end{proof}
+
+\subsection{Normalized cut of $\mathcal{L}[\Xbf]$.}
+
+Recall that for any set $\mathcal{A} \subset \mathcal{X}$, the $\Pbb$-weighted \emph{cut} and \emph{volume} functionals can be written as
+\begin{equation*}
+\cut_{\Pbb,r}(\Aset) = \int_{\Aset} \int_{\mathcal{X} \setminus \Aset} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y), \vol_{\Pbb,r}(\Aset):= \int_{\Aset} \int_{\mathcal{X}} \1(\norm{x - y} \leq r) \,d\Pbb(x) \,d\Pbb(y),
+\end{equation*}
+and the continuous \emph{normalized cut} is
 \begin{equation*}
@@
 
-\textbf{1.} We first upper bound the normalized cut $\Phi_{\Pbb,r}(\Sset)$ and lower bound the normalized cut $\Phi_{\Pbb,r}(\Cset_1)$, using the geometric parameters $\sigma$ and $\rho$, the \textcolor{red}{drop parameter} $\epsilon$, and the radius $r$.
-Our bounds will be crude, but will display the right dependence on these parameters, and so will be sufficient for our purposes.
+We now upper bound the normalized cut $\Phi_{\Pbb,r}(\mathcal{L})$ as a function of the diameter $\rho$, and the neighborhood graph radius $r$.
+Our bounds will be simple and not tight, but will display the right dependence on these parameters, and so will be sufficient for our purposes.
 
-We begin with the upper bound on $\Phi_{\Pbb,r}(\Sset)$.
-Note that only points $x = (x_1,x_2)$ such that $-r < x_2 < 0$ contribute to the cut of $\Sset$.
-Letting $f$ be the density function of $\Pbb$, we have
+To upper bound $\cut_{\Pbb,r}(\mathcal{L})$, note that for any $x = (x_1,x_2) \in \mathcal{L}$, if $x_2 \leq -r$ the ball $B(x,r)$ and the set $\mathcal{X}\setminus\mathcal{L}$ are disjoint.
+This implies
 \begin{align*}
-\cut_{\Pbb,r}(\Sset) & \leq \Pbb(\set{x \in \mathcal{X}: -r < x_2 < 0}) \cdot \max_{x \in \mathcal{X}} \Pbb(B(x,r)) \\
-& \leq \frac{3 r}{\rho} \cdot \frac{\nu_d r^d}{\sigma \rho}.
+\cut_{\Pbb,r}(\mathcal{L}) & \leq \Pbb(\set{x \in \mathcal{X}: -r < x_2 < 0}) \cdot \max_{x \in \mathcal{X}} \Pbb(B(x,r)) \\
+& \leq \frac{r}{2 \rho} \cdot \frac{\pi r^2}{2 \sigma \rho}.
 \end{align*}
-By symmetry, $\vol_{\Pbb,r}(\Sset) = \vol_{\Pbb,r}(\mathcal{X} \setminus \Sset)$, and therefore it is sufficient to lower bound $\vol_{\Pbb,r}(\Sset)$. We have
+By symmetry, $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, and therefore to upper bound $\Phi_{\Pbb,r}(\mathcal{L})$, it is sufficient to lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
+We have
 \begin{align*}
-\vol_{\Pbb,r}(\Sset) & \geq \Pbb(\set{x \in \Cset_1 \cap \Sset: \dist(x, \partial \Cset_1) > r}) \cdot \frac{\nu_d r^d}{\sigma \rho} \\
-& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\nu_d r^d}{\sigma \rho}  \\
-& \geq \frac{3\nu_d r^d}{16\sigma \rho},
+\vol_{\Pbb,r}(\mathcal{L}) & \geq \Pbb(\set{x \in \Cset_1 \cap \mathcal{L}: \dist(x, \partial \Cset_1) > r}) \cdot \frac{\pi r^2}{2 \sigma \rho} \\
+& = \frac{(\sigma - 2r)(\rho - r)}{2 \sigma \rho} \cdot \frac{\nu_d r^d}{2 \sigma \rho}  \\
+& \geq \frac{3}{16} \cdot \frac{\pi r^2}{2 \sigma \rho}
 \end{align*}
-where the last inequality follows since $r \leq \sigma/4$ and $\sigma < \rho$. Therefore,
+where the last inequality follows since $r \leq \frac{1}{4}\sigma < \frac{1}{4}\rho$. Therefore, $\Phi_{\Pbb,r}(\mathcal{L}) \leq \frac{8r}{3\rho}.$
+
+Then, Lemma~\ref{lem:graph_functional_concentration} implies that the graph functionals $\cut_{n,r}(\mathcal{L}[\Xbf])$ and $\vol_{n,r}(\mathcal{L}[\Xbf])$--and in turn $\Phi_{n,r}(\mathcal{L}[\Xbf])$-- concentrate around their expectations.
+Precisely, we have that
+\begin{align}
+\Phi_{n,r}(\mathcal{L}[\Xbf]) & = \frac{\cut_{n,r}(\mathcal{L}[\Xbf])}{\min\set{\vol_{n,r}(\mathcal{L}[\Xbf]),\vol_{n,r}((\mathcal{X}\setminus\mathcal{L})[\Xbf])}} \nonumber \\
+& \leq \frac{3}{2}\Phi_{\Pbb,r}(\Aset) \leq \frac{4 r}{\rho} \label{eqn:lb_pf2}
+\end{align}
+with probability at least $1 - 3\exp\{-\frac{1}{25}n(\cut_{\Pbb,r}(\mathcal{L}))^2\}$.
+
+\subsection{Normalized cut of $\widehat{C}$.}
+
+We will use Lemma~\ref{lem:graph_functional_concentration} to show that the set $\mathcal{L}[X] \subset X$ and the neighborhood graph $G_{n,r}$ satisfy the required conditions of Theorem~\ref{thm:conductance_ppr}.
+This Theorem will imply an upper bound on the normalized cut of $\widehat{C}$.
+
+Note that $\mathcal{X}$ and $f$ satisfy the regularity conditions~\ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2}, with parameters $\lambda_{\min} = \frac{\epsilon}{\rho\sigma}, \lambda_{\max} = \frac{1}{2\rho\sigma}$, and $a = 4, R = \frac{1}{4}\sigma$.
+We therefore have that for any $\delta \in (0,1)$ and any $r \in (0,\frac{1}{4}\sigma)$, each of the following inequalities are satisfied with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2\delta^2n}{8 \rho \sigma(1 + \frac{\delta}{3})}} - 6 \exp\set{-n\delta^2(\cut_{\Pbb,r}(\mathcal{L}[\Xbf]))^2}$:
+\begin{itemize}
+	\item $\frac{(1 - \delta)\epsilon \pi r^2}{4\rho \sigma}n \leq d_{\min} \leq d_{\max} \leq \frac{(1 + \delta)\pi r^2}{2\rho \sigma }n$, 
+	\item $\frac{(1 - \delta)}{2} n \leq \abs{\mathcal{L}[\Xbf]} \leq \frac{(1 + \delta)}{2} n$, 
+	\item $\vol_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta)\vol_{\Pbb,r}(\mathcal{L}) = \frac{(1 + \delta)}{2} \vol_{\Pbb,r}(\mathcal{X}) \leq \frac{(1 + \delta)}{2} \vol(G_{n,r})$, and
+	\item $(1 - \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf]) \leq \cut_{n,r}(\mathcal{L}[\Xbf]) \leq (1 + \delta) \cut_{\Pbb,r}(\mathcal{L}[\Xbf])$.
+\end{itemize}
+We now condition on these inequalities, and letting $\delta = \frac{2}{67}$ we verify that under the setup of Theorem~\ref{thm:ppr_lb}, each of the conditions of Theorem~\ref{thm:conductance_ppr} are met:
+\begin{itemize}
+	\item $\vol(\mathcal{L}[X]) \leq \frac{(1 + \delta)}{2(1 - \delta)}\vol(G_{n,r}) \leq \frac{2}{3}\vol(G_{n,r})$ since $\delta < 1/7$,
+	\item $\abs{\mathcal{L}[X]} \geq \frac{n(1 - \delta)}{2} \geq \frac{2(1 + \delta)}{(1 - \delta)\epsilon} \geq \frac{d_{\max}}{d_{\min}}$ and $\frac{d_{\max}}{2d_{\min}^2} \leq \frac{8(1 + \delta)}{(1 - \delta)^2 \epsilon^2 \rho \sigma \pi r^2} \cdot \frac{1}{n} \leq \frac{1}{10}$ by \eqref{eqn:lb_sample_size},
+	\item $\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{4r}{\rho} \leq \frac{1}{10}$, by assumption on $r$ and $\rho$, and
+	\item $60\Phi_{n,r}(\mathcal{L}[X]) \leq \frac{60(1 + \delta)}{1 - \delta}\Phi_{\Pbb,r}(\mathcal{L}) \leq \alpha \leq \frac{65(1 + \delta)}{1 - \delta}\Phi_{n,r}(\mathcal{L}[X]) \leq 70\Phi_{n,r}(\mathcal{L}[X])$ since $\delta < 2/67$.
+\end{itemize}
+
+We may therefore apply Theorem~\ref{thm:conductance_ppr}, which allow us to upper bound the minimum conductance sweep cut $\min_{\beta \in (0,1)}\Phi(S_{\beta,v};G)$ or equivalently the output of Algorithm~\textcolor{red}{1}.
+
+To be precise, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6} \vol_{n,r}(\mathcal{L}[\Xbf])$, such that the following statement holds for any $v \in \mathcal{L}[\Xbf]^g$: when Algorithm~\textcolor{red}{1} is run with inputs $\Xbf, r < \frac{1}{4}\sigma,\alpha = 65 \Phi_{\Pbb,r}(\mathcal{L}[\Xbf]),v \in \mathcal{L}[\Xbf]^g$ and $(L,U) = (0,1)$, the resulting PPR cluster estimate $\widehat{C}$ satisfies
+\begin{align}
+\Phi_{n,r}(\widehat{C}) & \leq \sqrt{11200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi_{n,r}(\mathcal{L[X]})} \nonumber \\
+& \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}} \label{eqn:lb_pf4} 
+\end{align}
+with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2 n}{8978 \rho \sigma}} - 6 \exp\set{-\frac{1}{1123}(\cut_{\Pbb,r}(\mathcal{L}))^2n}$ (where the latter inequality follows from \eqref{eqn:lb_pf2} and Lemma~\ref{lem:graph_functional_concentration}.)
+
+\subsection{Lower bound on normalized cut.}
+
+The precise statement we will prove is contained in the following Lemma.
+\begin{lemma}
+	\label{lem:normalized_cut_lb}
+	The normalized cut $\Phi_{n,r}(A)$ is upper bounded
 	\begin{equation*}
-\Phi_{\Pbb,r}(\Sset) \leq 16 \frac{r}{\rho}.
+	\Phi_{n,r}(A) \geq \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
 	\end{equation*}
-Similar manipulations yield a lower bound on $\Phi_{\Pbb,r}(\Cset_1)$.
-We use our estimates of the volume of spherical caps from \textcolor{red}{A.6} to obtain a lower bound on $\cut_{\Pbb,r}(\Cset_1)$,
+	uniformly over all $A \subset X$ with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
+\end{lemma}
+\begin{proof}
+	To lower bound the normalized cut $\Phi_{n,r}(A)$, we must lower bound $\cut_{n,r}(A)$ and upper bound $\vol_{n,r}(A)$. A naive upper bound on the volume is simply 
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf4}
+	\vol_{n,r}(A) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
+ 	\end{equation}
+	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this will suffice for our purposes.
+(Here and in the rest of this proof we take $\delta = 1/2$.)
+
+	We turn to lower bounding $\cut_{n,r}(A)$.
+We will approximate the cut of $A$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $A$ to the boundary of the binned set $\overline{A}$, and then lower bound the size of the boundary of $\overline{A}$.
+
+	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right hand corner of the cube
+	\begin{equation*}
+	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
+	\end{equation*}
+	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
+For a set $A \subset X$ we define the binned set $\overline{A} \subset \overline{Q}$ as follows
+	\begin{equation*}
+	\overline{A} := \set{Q \in \overline{Q}: \Pbb_n(A \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
+	\end{equation*}
+	and we let 
+	\begin{equation*}
+	\partial \overline{A} := \set{Q_{(k_1,k_2)} \in \overline{A}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \overline{A}, \norm{k - \ell}_1 = 1}.
+	\end{equation*}
+	be the boundary set of $\overline{A}$ in $\overline{Q}$.
+Intuitively, every point $x_i \in A$ in the boundary set of $\overline{A}$ will have many edges to $X\setminus A$.
+Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \mathbb{P}_n(Q)$, we have
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf1}
+	\cut_{n,r}(A) \geq \cut_{n,r}(A \cap \set{x_i \in \overline{A}}) \geq \frac{1}{4} \abs{\partial \overline{A}} Q_{\min}^2,
+	\end{equation}
+	where the last inequality follows since for every cube $Q_k \in \partial\overline{A}$, there exists a cube $Q_\ell \not\in \overline{A}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
+
+	Now we move on lower bounding the size of the boundary $\abs{\partial\overline{A}}$.
+To do so, we divide $\mathcal{X}$ into slices horizontally.
+Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\overline{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
+For each $k$, either
+	\begin{enumerate}
+		\item $\overline{R}_k \cap \overline{A} = \emptyset$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_1[\Xbf] \cap R_k), ~~ \textrm{or}
+		\end{equation*}
+		\item $\overline{R}_k \cap \overline{A} = \overline{R}_k$, in which case
+		\begin{equation*}
+		\vol_{n,r}\Bigl( \bigl(A \vartriangle C_1[\Xbf]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(C_2[\Xbf] \cap R_k), ~~\textrm{or}
+		\end{equation*}
+		\item $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$.
+	\end{enumerate}
+	Let $N(R)$ be the number of slices for which $\overline{R}_k \cap \partial \overline{A} \neq \emptyset$. By the cases elucidated above, letting
+	\begin{equation*} R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(C_1[\Xbf] \cap R_k) \wedge \vol_{n,r}(C_2[\Xbf] \cap R_k)\Bigr\}
+	\end{equation*} 
+	we obtain the following lower bound on the volume of the symmetric set difference,
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf2}
+	\vol_{n,r}(A \vartriangle C_1[\Xbf]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right].
+	\end{equation}
+	Finally note that $\abs{\partial\overline{A}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
+	\begin{align}
+	\cut_{n,r}(A) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
+	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(A \vartriangle C_1[\Xbf])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
+	\end{align}
+	for all $A \subset \Xbf$.
+
+	It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
+	To do so, we first lower bound the expected probability of any cell $Q$,
 	\begin{align*}
-\cut_{\Pbb,r}(\Cset_1) & \geq \Pbb(\set{x \in \Cset_1: \dist(x,\Cset_0) < r/32}) \cdot \frac{\nu(\textrm{cap}_{r}(\frac{31r}{32})) \epsilon}{2\rho\sigma} \\
-& \geq \frac{r (1 - \epsilon)}{32 \sigma} \cdot \frac{3 \nu_d r^d \epsilon}{16\rho\sigma}.
+	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
 	\end{align*}
-and we can immediately upper bound the volume of $\Cset_1$,
-\begin{equation*}
-\vol_{\Pbb,r}(\Cset_1) \leq (1 - \epsilon) \cdot  \frac{(1 - \epsilon)}{\rho \sigma} \nu_d r^d.
-\end{equation*}
-Observe that $\vol_{\Pbb,r}(\mathcal{X} \setminus \Cset_1) \geq \vol_{\Pbb,r}(\Cset_2) = \vol_{\Pbb,r}(\Cset_1)$. Therefore,
+	and the expected volume of $\mathcal{C}_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\mathcal{C}_{\sigma}^{(2)}[\Xbf] \cap R_k$,
 	\begin{equation}
-\label{eqn:lb_proof_2}
-\Phi_{\Pbb,r}(\Cset_1) \geq  \frac{\epsilon r}{256 \sigma}.
+	\vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
 	\end{equation}
 
-\textbf{2.} The upper bound \eqref{eqn:lb_proof_2} can be extended to hold for all sets $\Aset$ with small symmetric set difference $\Aset \triangle \Cset_1$. Formally,
-\begin{equation}
-\label{eqn:continuity_normalized_cut}
-\Phi_{\Pbb,r}(\Aset) \geq \frac{1}{2\pi} \cdot \frac{\epsilon^2r}{\sigma} \bigl(1 - 4 \cdot \Pbb(\Aset \triangle \Cset_1 )\bigr)
-\end{equation}
-The proof of \eqref{eqn:continuity_normalized_cut} is somewhat involved, and we defer it to the following section.
+	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
+Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
+Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
+	\begin{equation*}
+	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq \frac{(1 - \delta)}{2}\frac{\pi r^3}{\sigma \rho^2 },
+	\end{equation*}
+	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
+Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
+	\begin{equation*}	
+	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
+	\end{equation*}
+	and plugging in $\delta = 1/2$ yields the claim of Lemma~\ref{lem:normalized_cut_lb}.
+\end{proof}
 
-\textbf{3.} We now convert from population to sample normalized cut.
-\textit{Claim 1:} There exist constants $c_1,c_2$ which may depend on $(\epsilon, \rho, \sigma)$ such that the following statements holds with respect to $c_1,c_2$: For all $n$ such that
+\paragraph{Conclusion.}
+Combining \eqref{eqn:lb_pf4} and Lemma~\ref{lem:normalized_cut_lb}, we have that there exists a set $\mathcal{L}[\Xbf]^g \subset \mathcal{L}[\Xbf]$ with $\vol_{n,r}(\mathcal{L}[\Xbf]^g) \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf])$ such that for any seed node $v \in \mathcal{L}[\Xbf]^g$, the following bounds hold:
 \begin{equation*}
-c_1 \cdot \left(\frac{\log n}{n}\right)^{1/d} \leq r,
+ \frac{1}{12\pi} \left(1 - 4\frac{\sigma \rho}{r^2 n^2} \vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma} \leq \Phi_{n,r}(\widehat{C}) \leq \sqrt{89600\left\{\log\left(\frac{\rho \sigma}{\epsilon^2 \pi r^2}\right) + \log 20\right\} \frac{r}{\rho}},
 \end{equation*}
-the sample normalized cut of $\Aset$ is lower bounded
+Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\mathcal{C}_{\sigma}^{(1)}[\Xbf]$:
+\begin{align*}
+\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) & \geq  \vol_{n,r}(\mathcal{L}[\Xbf]^g) - \vol_{n,r}((\mathcal{L}[\Xbf]^g \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(2)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) - \vol_{n,r}((\mathcal{L} \cap (\mathcal{C}_{\sigma}^{(0)} \cup \mathcal{C}_{\sigma}^{(1)})[\Xbf])[\Xbf]) \\
+& \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \mathcal{C}_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
+& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}) \\
+& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])
+\end{align*}
+where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}))^2}$.
+Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$.
+
+\section{Concentration Inequalities.}
+
+Let $f$ be a density function, defined on the domain $\mathcal{X}$.
+In our theory, we frequently appeal to concentration of degree and volume graph functionals around their means.
+In this section, we establish that this concentration holds under certain regularity conditions on $f$.
+In particular, we will assume
+\begin{enumerate}[(A)]
+	\item 
+	\label{asmp:regularity_condition_1}
+	There exist $\lambda_{\min}$ and $\lambda_{\max}$ such that for any $x \in \mathcal{X}$:
 	\begin{equation*}
-\Phi_{n,r}(\Aset) \geq \frac{\Phi_{\Pbb,r}(\Aset)}{4} \quad \textrm{for all $\Aset \subset \Rd$,}
+	0 < \lambda_{\min} < f(x) < \lambda_{\max} < \infty.
 	\end{equation*}
-and the sample normalized cut of $\Sset$ is upper bounded,
+	\item
+	\label{asmp:regularity_condition_2}
+	There exists some $a,R > 0$ such that for any $0 < r < R$ and any $x \in \mathcal{X}$,
 	\begin{equation*}
-\Phi_{n,r}(\Sset) \leq \frac{\Phi_{\Pbb,r}(\Sset)}{2}
+	\nu(B(x,r) \cap \mathcal{X}) \geq \frac{\nu_d r^d}{a},
 	\end{equation*}
-with probability at least $1 - \frac{c_2}{n}$.
+	where $\nu(\cdot)$ is Lebesgue measure on $\Reals^d$ and $B(x,r)$ is the ball centered at $x$ of radius $r$. 
+\end{enumerate}
+We collect our bounds on graph functionals in the following Lemma. 
+\begin{lemma}
+	\label{lem:graph_functional_concentration}
+	Let $X = \set{x_1,\ldots,x_n}$ be sampled independently from $\Pbb$, let $G := G_{n,r}$ be a neighborhood graph over $X$, and let $\mathcal{S}$ be a subset of $\mathcal{X}$.
+Suppose the density $f$ of $\Pbb$ satisfies the regularity conditions \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2}.
+Then, for any $\delta \in (0,1)$ and any $r \in (0,R)$, there exists numbers $c_1 := c_1(f)$ and $c_2 := c_2(f)$ independent of the sample size $n$ such that each of the following bounds hold.
 
-\textbf{4.}
-
-We prove this claim in a following section.
-
-\subsubsection{Proof of \eqref{eqn:continuity_normalized_cut}}
-To prove \eqref{eqn:continuity_normalized_cut}, we will need to upper bound the cut of $\Aset$, and lower bound the volume.
-We begin by upper bounding the cut, which will be the more difficult of the two.
-To obtain the desired result, we will need to discretize $\Aset$.
-For simplicity, without loss of generality assume $\rho$ and $\sigma$ are constant multiples of $r$.
-For $i = 0,\ldots,\frac{6\sigma}{r} - 1$ and $j = 0,\ldots, \frac{2\rho}{r} - 1$, let
+	With probability at least $1 - 2n\exp\set{-\frac{\frac{1}{2}\delta^2 \frac{\lambda_{\min} \nu_d r^d}{a}n}{1 + \frac{\delta}{3}}}$,
 	\begin{equation*}
-B_{ij} = \left[\frac{-3\sigma + ir}{2}, \frac{-3\sigma + (i + 1)r}{2}\right] \times \left[\frac{-\rho + jr}{2}, \frac{-\rho + (j + 1)r}{2}\right] 
-\end{equation*}
-and let $\mathfrak{B} = \set{B_{ij}}$ be the collection of all such boxes. Our discrete version of $\mathcal{A}$ will be a subsets of $\mathfrak{B}$,
-\begin{equation*}
-\overline{\mathcal{A}} := \set{B_{ij} \in \mathfrak{B}: \Pbb(B_{ij} \cap \mathcal{A}) \geq \frac{\Pbb(B_{ij})}{2}}.
-\end{equation*}
-(Note that $\mathcal{C}_1 = \bigcup \overline{\Cset}_1$ where $\overline{\Cset}_1 = \set{B_{ij}: i \in 0,\ldots,\frac{2\sigma}{r} - 1 }$, and is therefore effectively already discretized.)
-The discretization of $\Aset$ is useful for several reasons.
-First, we use it to lower bound the cut of the continuous set $\Aset$.
-Define the boundary of the discretized set $\overline{\mathcal{A}}$ to be
-\begin{equation*}
-\overline{\partial \Aset} = \set{B_{ij} \in \overline{\mathcal{A}}: \exists B_{lk} \in \mathfrak{B} ~\textrm{such that}~\abs{l - i} + \abs{k - j} = 1, B_{lk} \not\in \overline{\mathcal{A}}}.
-\end{equation*}
-All boxes in the boundary $\overline{\partial \Aset}$ contribute substantially to the cut of $\Aset$,
-\begin{equation}
-\label{eqn:lb_proof}
-\cut_{\Pbb,r}(\mathcal{\Aset}) \geq \sum_{B_{ij} \in \overline{\partial\mathcal{A}}} \frac{\Pbb(B_{ij}) \cdot \min_{k,l} \Pbb(B_{kl})}{4}
-\end{equation}
-Moreover, the symmetric set difference $\Aset \triangle \Cset_1$ can be related to the symmetric set difference $\overline{\Aset} \triangle \overline{\Cset}_1$,
-\begin{equation}
-\label{eqn:lb_proof_1}
-\Pbb(\Aset \triangle \Cset_1) \geq \sum_{B \in \overline{\Aset} \triangle \overline{\Cset}_1} \frac{\Pbb(B_{ij})}{2}.
-\end{equation}
-Next, divide $\mathcal{X}$ into rectangles horizontally, $\mathfrak{R}_j = \set{B_{ij}: i = 0,\ldots,\frac{6\sigma}{r} - 1}$. We divide our analysis into cases. For each $j$, one of
-\begin{enumerate}[(i)]
-	\item $\overline{\Aset} \cap \mathfrak{R}_j = \emptyset$, and therefore $(\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j = \overline{\Cset}_1 \cap \mathfrak{R}_j$, or
-	\item $\overline{\Aset} \cap \mathfrak{R}_j = \mathfrak{R}_j$, and therefore $(\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j \supset \overline{\Cset}_2 \cap \mathfrak{R}_j$, or
-	\item $\overline{\partial\mathcal{A}} \cap \mathfrak{R}_j \neq \emptyset$.
-\end{enumerate}
-occurs.
-Moreover, (a) for every row $\mathfrak{R}_j$, $\abs{\overline{\Cset}_1 \cap \mathfrak{R}_j} =  \abs{\overline{\Cset}_2 \cap \mathfrak{R}_j} = \frac{2\sigma}{r}$, and (b) for every $B_{ij} \in \overline{\Cset}_1 \cup \overline{\Cset}_2$, the probability
-\begin{equation*}
-\Pbb(B_{ij}) \geq  \frac{r^2(1 - \epsilon)}{4\rho \sigma}.
-\end{equation*}
-Therefore, letting $J_1 = \set{j: \textrm{(i) occurs}}$, and similarly $J_2 = \set{j: \textrm{(ii) occurs}}$ and  $J_3 = \set{j: \textrm{(iii) occurs}}$, we have from \eqref{eqn:lb_proof_1} that
-\begin{align*}
-\Pbb(\Aset \triangle \Cset_1) & \geq \sum_{j = 0}^{\frac{2\rho}{r} - 1} \sum_{B \in (\overline{\Aset} \triangle \overline{\Cset}_1) \cap \mathfrak{R}_j} \frac{\Pbb(B_{ij})}{2} \\
-& \geq \left(\abs{J_1} + \abs{J_2}\right) \cdot \frac{\sigma}{r} \cdot \frac{r^2(1 - \epsilon)}{4\rho \sigma} \\
-& = \left(\frac{2\rho}{r} - \abs{J_3}\right) \frac{r(1 - \epsilon)}{4\rho}
-\end{align*}
-Rearranging, we obtain
-\begin{equation*}
-\abs{J_3} \geq \frac{2\rho}{r}\left(1 - \frac{2\Pbb(\Aset \triangle \Cset_1)}{1 - \epsilon}\right) \geq \frac{2\rho}{r}\left(1 - 4\Pbb(\Aset \triangle \Cset_1)\right)
-\end{equation*}
-since \textcolor{red}{$\epsilon < 1/2$.} From \eqref{eqn:lb_proof} and the prior inequality, we have
-\begin{align}
-\cut_{\Pbb,r}(\Aset) & \geq \sum_{j = 0}^{\frac{2\rho}{r} - 1} \sum_{B_{ij}} \frac{\Pbb(B_{ij}) \cdot \min_{k,l} \Pbb(B_{kl})}{4} \nonumber \\
-& \geq \abs{J_3} \frac{r^4\epsilon^2}{16\rho^2\sigma^2} \nonumber \\
-& \geq \frac{\epsilon r}{2\sigma} \cdot \frac{r^2 \epsilon}{\rho\sigma} \cdot \bigl(1 - 4\Pbb(\Aset \triangle \Cset_1)\bigr) \label{eqn:lb_proof_3}
-\end{align}
-
-We provide the following very crude upper bound on $\vol_{\Pbb,r}(\Aset)$,
-\begin{equation*}
-\vol_{\Pbb,r}(\Aset) \leq \vol_{\Pbb,r}(\mathcal{X}) \leq \frac{\pi r^2}{\rho \sigma},
-\end{equation*}
-which along with~\eqref{eqn:lb_proof_3} results in an upper bound on the normalized cut of $\Aset$,
-\begin{equation*}
-\Phi_{\Pbb,r}(\Aset) \leq \frac{1}{2\pi} \cdot \frac{\epsilon^2r}{\sigma} \bigl(1 - 4 \cdot \Pbb(\Aset \triangle \Cset_1 )\bigr).
+	(1 - \delta) \lambda_{\min} \frac{\nu_dr^d}{a} n \leq d_{\min} \leq d_{\max} \leq (1 + \delta) \lambda_{\min} \frac{\nu_dr^d}{a}n.
 	\end{equation*}
 
-\subsubsection{Proof of Claim 1.}
+	With probability at least $1 - 2\exp\set{-2n\delta^2\Pbb(S)^2}$,
+	\begin{equation*}
+	(1 - \delta) \mathbb{P}(\mathcal{S}) n \leq \abs{\mathcal{S}[X]} \leq (1 - \delta) \mathbb{P}(\mathcal{S}) n.
+	\end{equation*}
+
+	With probability at least $1 - 2\exp\set{-n\delta^2\vol_{\Pbb,r}(\mathcal{S})^2}$,
+	\begin{equation*}
+	(1 - \delta) n (n - 1) \vol_{\Pbb,r}(\mathcal{S}) \leq \vol_{n,r}(\mathcal{S}[X]) \leq (1 + \delta) n (n - 1) \vol_{\Pbb,r}(\mathcal{S}).
+	\end{equation*}
+
+	Finally, with probability at least $1 - 2\exp\set{-n\delta^2\cut_{\Pbb,r}(\mathcal{S})^2}$,
+	\begin{equation*}
+	(1 - \delta) n (n - 1) \cut_{\Pbb,r}(\mathcal{S}) \leq \cut_{n,r}(\mathcal{S}[X]) \leq (1 + \delta) n (n - 1) \cut_{\Pbb,r}(\mathcal{S}).
+	\end{equation*}	
+\end{lemma}
+\begin{proof}[Proof of Lemma~\ref{lem:graph_functional_concentration}]
+The bounds on $d_{\min}$ and $d_{\max}$ follow from standard reasoning, in which we first use the regularity conditions \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2} to upper and lower bound the expected degree $\mathbb{E}(\deg_{n,r}(x_i))$ over all $x_i$,
+\begin{equation*}
+\lambda_{\min} \frac{\nu_d r^d}{a} \leq \min_{i = 1,\ldots,n} \mathbb{E}(\deg_{n,r}(x_i)) \leq \max_{i = 1,\ldots,n} \mathbb{E}(\deg_{n,r}(x_i)) \leq \lambda_{\max} \nu_d r^d,
+\end{equation*}
+and then apply Bernstein's inequality and a union bound (formally, Lemma) to control the maximal deviation $\deg_{n,r}(x_i) - \mathbb{E}(\deg_{n,r}(x_i))$.
+We state this second step as a separate Lemma, as it will be useful in contexts besides the proof of Lemma~\ref{lem:graph_functional_concentration}.
+
+Hoeffding's inequality for binomial random variables leads to a bound on the deviation of $\abs{S[X]}$ from its mean.
+Finally, the functionals $\vol(\mathcal{S}[X])$ and $\mathrm{cut}(\mathcal{S}[X])$ are U-statistics and therefore by Hoeffding's inequality concentrate around their respective expectations.
+\end{proof}
+
+\begin{lemma}[Union bound.]
+	\label{lem:bernstein_union}
+	For $M \geq 1$, let $\mathcal{A}_1,\ldots,\mathcal{A}_M$ be subsets of $\Reals^d$.
+Denote the minimum probability mass among these sets as $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$.
+Then
+	\begin{equation*}
+	(1 - \delta)p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq (1 + \delta)p_{\max}
+	\end{equation*}
+	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.
+
+	Similarly, for $r > 0$ let $v_{\min} = \min_{m = 1,\ldots,M} \vol_{\Pbb,r}(\mathcal{A}_m)$ and $v_{\max} = \max_{m = 1,\ldots,M} \vol_{\Pbb,r}(\mathcal{A}_m)$. Then
+	\begin{equation*}
+	(1 - \delta)v_{\min} \leq \min_{m = 1,\ldots,M} \vol_{n,r}(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \vol_{n,r}(\mathcal{A}_m) \leq (1 + \delta)v_{\max}
+	\end{equation*}
+	with probability at least $1 - 2M \exp\set{-\delta^2 v_{\min}^2n}$. 
+\end{lemma}
+
 \end{document}

### 2021-09-01 arxiv/examples_section_backup.tex
Cleaned out arxiv folder.

--- 2021-09-01 arxiv/examples_section.tex
@@
 	\end{equation}
-	the following statement holds: there exists a set $C^{g} \subset \Xbf$ with $\vol(C^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$ such that for any seed node $v \in C^g$, the estimator $\widehat{C}$ computed by Algorithm~\textcolor{red}{1} has symmetric set difference with $\Csig^{(1)}[\Xbf]$ of volume at least
+	the following statement holds: there exists a set $C^{g} \subset \Xbf$ with $\vol(C^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{4}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$ such that for any seed node $v \in C^g$, the estimator $\widehat{C}$ computed by Algorithm~\textcolor{red}{1} has symmetric set difference with $\Csig^{(1)}[\Xbf]$ of volume at least
 	\begin{equation}
 	\label{eqn:ppr_lb}
-	\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2} \geq \frac{1}{4} -  c \frac{\sqrt{\frac{\sigma}{\rho}}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
+	\frac{\sigma \rho}{r^2 n^2}\frac{\vol(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n} \geq \frac{1}{4} -  c \frac{\sqrt{\frac{\sigma}{\rho}}}{\epsilon^2} \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
 	\end{equation}
 	with probability at least $1 - c_1 n \exp\set{-c_2n}$, where $c$ is a universal constant and $c_1,c_2$ are constants which do not depend on $n$.
-	Consequently, if
-	\begin{equation*} 
-	\epsilon^2 > \frac{c}{8} \sqrt{\frac{\sigma}{\rho}} \cdot \sqrt{ \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\frac{\sigma}{r}}
-	\end{equation*}
-	then with high probability $\frac{\sigma \rho}{r^2}\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{n^2}$ is at least $1/8$. 
 \end{theorem}
 
-Note that the factor of $\frac{\sigma}{r^2}$ on the left hand side of \eqref{eqn:ppr_lb} is a constant multiple of $(1/\vol_{\Pbb,r}(\Csig^{(1)}))$; hence the left hand side is directly comparable to $\frac{\vol_{n,r}(\widehat{C} \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf])}{\vol_{n,r}(\Csig^{(1)}[\Xbf])}$, which is the quantity we upper bound in Theorem~\textcolor{red}{1}.
+Roughly speaking, our lower bound implies that if $\sigma\sqrt{\frac{1}{r\rho}} \gg \epsilon^2$, then PPR will fail to recover the empirical density cluster $\Cset_1[\Xbf]$, for many seed nodes $v \in \Cset_1[\Xbf]$.
 
 Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.
-Although we picked this setting to make the theorem statement simple, our results are easily generalized to $\Reals^d$ and to non-rectangular clusters.
+Although we picked this setting to make the Theorem statement simple, our results are easily generalized to $\Reals^d$ and to non-rectangular clusters.
 Additionally, although we state our lower bound with respect to PPR run on neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
@@
 To better digest the implications of Theorem~\ref{thm:ppr_lb}, we apply our upper bound to the density function $f$ given in \eqref{eqn:lb_density}.
-Observe that $\Csig^{(1)}$ satisfies each of the assumptions~\textcolor{red}{(A1) - (A5).} In particular
+
+Technically, this density does not fit nicely into the setup of Theorem~\textcolor{red}{1}, because the sets $\Cset_{\sigma}^{(m)}$ ($ m = 1,2$) play the role of both the $\sigma$-expanded sets and the density clusters themselves.
+However, this truly is only a technical objection.
+One could modify the distribution $\Pbb$ by adding a small amount of mass to the $\sigma$-interior $\Cset^{(m)} = \set{x \in \Cset_{\sigma}^{(m)}: \dist(x,\partial\Cset_{\sigma}) \geq \sigma}$.
+Appropriately choosing a threshold $\lambda > \frac{(1 - \epsilon)}{2\rho\sigma}$, the resulting $\lambda$-density clusters would be $\Cbb_f(\lambda) = \set{\Cset^{(1)},\Cset^{(2)}}$, and their $\sigma$-expansions would resemble the rectangles $\Csig^{(1)}, \Csig^{(2)}$ except with slightly rounded corners.
+Alternatively, one could directly modify Lemma~\textcolor{red}{6} -- an auxiliary Lemma, used in the proof of Theorem~\textcolor{red}{3}, which establishes an upper bound on the Lebesgue measure of $\Csig + B(0,r)$ -- to hold with respect to rectangles of width $\sigma$ rather than $\sigma$-expansions.
+The proof of this Lemma is the only time we use the fact that $\Csig$ is a $\sigma$-expansion of a density cluster.
+\textcolor{red}{(Ryan and Siva.)}
+
+Regardless, we will proceed to showing the behavior of our upper bound in this example. Observe that $\Csig^{(1)}$ satisfies each of the assumptions~\textcolor{red}{(A1) - (A5).} In particular
 \begin{enumerate}[label=(A\arabic*)]
@@
 \end{enumerate}
-
-%Technically, this density does not fit nicely into the setup of Theorem~\textcolor{red}{1}, because the sets $\Cset_{\sigma}^{(m)}$ ($ m = 1,2$) play the role of both the $\sigma$-expanded sets and the density clusters themselves.
-However, this truly is only a technical objection.
-One could modify the distribution $\Pbb$ by adding a small amount of mass to the $\sigma$-interior $\Cset^{(m)} = \set{x \in \Cset_{\sigma}^{(m)}: \dist(x,\partial\Cset_{\sigma}) \geq \sigma}$.
-Appropriately choosing a threshold $\lambda > \frac{(1 - \epsilon)}{2\rho\sigma}$, the resulting $\lambda$-density clusters would be $\Cbb_f(\lambda) = \set{\Cset^{(1)},\Cset^{(2)}}$, and their $\sigma$-expansions would resemble the rectangles $\Csig^{(1)}, \Csig^{(2)}$ except with slightly rounded corners.
-%Alternatively, one could directly modify Lemma~\textcolor{red}{6} -- an auxiliary Lemma, used in the proof of Theorem~\textcolor{red}{3}, which establishes an upper bound on the Lebesgue measure of $\Csig + B(0,r)$ -- to hold under the assumption $\Csig$ is a rectangle of width $\sigma$ rather than a $\sigma$-expansion.
-The proof of this Lemma is the only time we use the fact that $\Csig$ is a $\sigma$-expansion of a density cluster.
-\textcolor{red}{(Ryan and Siva.)}
-
-\begin{remark}Technically, the rectangles $\Csig^{(1)}$ and $\Csig^{(2)}$ are not $\sigma$-expansions due to their sharp corners.
-To fix this, one can either modify the upper bound (specifically, Lemma~\textcolor{red}{6}) to hold with respect to rectangles of width $\sigma$, or change the sets $\Csig^{(1)}$ and $\Csig^{(2)}$ to be rectangles with rounded corners.
-As these details do not meaningfully change our conclusions, for simplicity we will keep our upper and lower bounds as is.
-\end{remark}
-
-If the user-specified parameters are initialized according to \textcolor{red}{(14)}, we may apply Theorem~\textcolor{red}{1}.
+As long as the user-specified parameters are well-initialized, we may therefore apply Theorem~\textcolor{red}{1}.
 This implies that there exists a set $\Csig^{(1)}[\Xbf] \subset \Csig^{(1)}$ with $\vol_{n,r}(\Csig[\Xbf]^g) \geq \frac{1}{2}\vol_{n,r}(\Csig[\Xbf])$ such that for any seed node $v \in \Csig^{(1)}[\Xbf]$, the estimated cluster $\widehat{C}$ output by Algorithm 1 satisfies the following upper bound:
@@
 
-To facilitate comparisons between our upper and lower bounds, assume $\frac{1}{4}\sigma \leq \frac{1}{40}\rho$ and set $r = \frac{1}{4}\sigma$. 
-For some universal constant $c > 0$, the following statements each hold with high probability:
-\begin{itemize}
-\item If the user-specified parameters satisfy \textcolor{red}{(14)} and for $b > 0$,
-\begin{equation*}
-\epsilon < c\frac{b\sigma^2}{\rho^2 \log^2\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}^2\sigma}\right)}
-\end{equation*}
-then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \leq b \cdot  \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
-\item If the user-specified parameters are given as in Theorem~\ref{thm:ppr_lb}, and 
-\begin{equation*}
-\epsilon > c\left({\frac{\sigma}{\rho}} \log\left(\frac{\rho \sigma}{\epsilon^2 r^2}\right)\right)^{1/4}
-\end{equation*}
-then $\Delta(\widehat{C}, \mathcal{C}^{(1)}[\Xbf]) \geq \frac{1}{8} \vol_{n,r}(\mathcal{C}^{(1)}[\Xbf])$.
-\end{itemize}
-
+Broadly speaking, our upper bound implies that when $\epsilon \ll \frac{\sigma r}{\rho^2}$, the volume of the symmetric set difference $\widehat{C} \vartriangle \Csig^{(1)}[\Xbf]$ will be small.
+To facilitate comparisons with our lower bound, assume $\frac{1}{4}\sigma \leq \frac{1}{40}\rho$ and set $r = \frac{1}{4}\sigma$.
+In this case, when $\epsilon \ll \frac{\sigma^2}{\rho^2}$ and the user-specified parameters satisfy \textcolor{red}{(14)}, then with high probability the resulting PPR cluster estimator $\widehat{C}$ will have small symmetric set difference with $\Csig^{(1)}[\Xbf]$.
+On the other hand, if $\epsilon \gg \left(\frac{\sigma}{\rho}\right)^{1/4}$ and the user-specified parameters satisfy the setup of Theorem~\ref{thm:ppr_lb}, then with high probability $\widehat{C}$ will have large symmetric set difference with $\Csig^{(1)}[\Xbf]$.
 Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-geometrically conditioned for recovery using PPR.
 
-\begin{remark}
-	It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
-We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
-\end{remark}
-
-%It is worth pointing out that both our lower and upper bounds are stated with respect to specific choices of the input parameters to Algorithm~\ref{alg:ppr}, and that these choices are in fact different in the case of the teleportation parameter $\alpha$ and sweep cut range $(L,U)$.
+It is worth pointing out that both our lower and upper bounds are stated with respect to specific choices of the input parameters to Algorithm~\ref{alg:ppr}, and that these choices are in fact different in the case of the teleportation parameter $\alpha$ and sweep cut range $(L,U)$.
 At a high level, we do not believe this substantially weakens the takeaway messages of our work: if a density cluster $\mathcal{C}$ is geometrically well-conditioned, then a reasonable initialization of PPR will recover $\Csig[\Xbf]$ with low error, whereas if it is geometrically poorly-conditioned, then a different but also reasonable initialization of PPR will fail to recover $\Csig[\Xbf]$.
@@
 We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound; however, proving this is currently beyond our technical grasp, and is a matter for future work.
-Even so, we reiterate our belief that in tandem our upper and lower bounds represent a substantial step forward in characterizing the behavior of local clustering algorithms in a statistical context \textcolor{red}{(Ryan and Siva)}.
+Even so, we reiterate our belief that in tandem our upper and lower bounds represent a substantial step forward in characterizing the behavior of local clustering algorithms in a statistical context \textcolor{red}{Ryan and Siva}
 
-\begin{remark}
-	We also note that our lower bound is of course specific to the PPR algorithm.
-As mentioned previously, density clustering is a well-studied problem, and in particular under our assumptions classical plug-in density cluster estimators can consistently recover the $\sigma$-expansion $\Csig$ of a density cluster $\Cset$, even when $\epsilon$ is large compared to $\frac{\sigma}{\rho}$.
-That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
+\subsection{Sample complexity.}
+
+\begin{itemize}
+	\item We stress that our lower bound characterizes the difficulty PPR has in identifying geometrically poorly-conditioned density clusters, but not the overall hardness of the density clustering problem in a statistical sense.
+	\item It is a simple matter to prove that consistent estimation of the set $\Csig$ is possible. \textcolor{red}{(Ryan and Siva).}
+	\item To the best of our knowledge minimax rates for density clustering are known only when the density function is Lipschitz smooth, whereas in our setup the density $f$ may not even be continuous.
+However, as a practical matter the extra cases included our setup are those where the clusters are very sharply defined, and therefore should be even easier to recover.
+See \textcolor{red}{Rinaldo and Wasserman} for a more thorough discussion on this matter.
+	\item That PPR has difficulty recovering density clusters which can be easily estimated by standard plug-in approaches is not surprising, nor is it a knock on PPR.
 Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR considers geometry as well as density when deciding upon the optimal cluster.
-\end{remark}
+\end{itemize}
 
@@
 \end{align}
-with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2 n}{8978 \rho \sigma}} - 6 \exp\set{-\frac{1}{1123}(\cut_{\Pbb,r}(\mathcal{L}))^2n}$ (where the latter inequality follows from \eqref{eqn:lb_pf2} and Lemma~\ref{lem:graph_functional_concentration}.)
+with probability at least $1 - 2n\exp\set{-\frac{\pi\epsilon r^2 n}{8978 \rho \sigma}} - 6 \exp\set{-\frac{1}{1123}(\cut_{\Pbb,r}(\mathcal{L}[\Xbf]))^2n}$ (where the latter inequality follows from \eqref{eqn:lb_pf2} and Lemma~\ref{lem:graph_functional_concentration}.)
 
@@
 	\end{equation*}
-	uniformly over all $A \subset X$ with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2} - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi r^3n}{2\sigma\rho^2(3 + \delta)}}$.
+	uniformly over all $A \subset X$ with probability at least $1 - c_1\exp\{-c_2n\}$.
 \end{lemma}
@@
 	\label{eqn:normalized_cut_lb_pf4}
-	\vol_{n,r}(A) \leq \vol_{n,r}(G_{n,r}) \overset{(i)}{\leq} (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
+	\vol_{n,r}(A) \leq \vol_{n,r}(G_{n,r}) \leq (1 + \delta)  \vol_{\Pbb,r}(\mathcal{X}) n^2 \leq (1 + \delta)\frac{\pi r^2}{\rho \sigma} n^2
  	\end{equation}
-	where $(i)$ holds with probability at least $1 - \exp\set{-2n\delta^2(\vol_{\Pbb,r}(\mathcal{X}))^2}$, and it turns out this will suffice for our purposes.
-(Here and in the rest of this proof we take $\delta = 1/2$.)
+	where the last inequality holds with probability at least $1 - c_1\exp\{-c_2n\}$, and it turns out this will suffice for our purposes. (Here and in the rest of this proof we take $\delta = 1/2$.)
 
@@
 	and the expected volume of $\mathcal{C}_{\sigma}^{(1)}[\Xbf] \cap R_k$ and $\mathcal{C}_{\sigma}^{(2)}[\Xbf] \cap R_k$,
-	\begin{equation}
-	\vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2} \label{eqn:normalized_cut_lb_pf5}
-	\end{equation}
+	\begin{equation*}
+	\mathbb{E}(\vol_{n,r}\bigl(\mathcal{C}_{\sigma}^{(2)}[\Xbf] \cap R_k\bigr)) = \mathbb{E}(\vol_{n,r}\bigl(\mathcal{C}_{\sigma}^{(1)}[\Xbf] \cap R_k\bigr)) = \vol_{\Pbb,r}(\mathcal{C}_{\sigma}^{(1)} \cap R_k) \geq \frac{1}{2} \frac{\pi r^3}{\sigma \rho^2}
+	\end{equation*}
 
-	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
-Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
-Along with \eqref{eqn:normalized_cut_lb_pf3} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
+	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, applying Bernstein's inequality and a union bound gives
 	\begin{equation*}
@@
 	\end{equation*}
-	with probability at least $1 - \frac{12\sigma \rho}{r^2} \exp\set{-\frac{\delta^2\epsilon r^2 n}{\rho \sigma(3 + \delta)}} - \frac{2\rho}{r}\exp\set{-\frac{\delta^2\pi^2 r^6n}{4\sigma^2\rho^4}}$.
-Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
+	with probability at least $1 - c_1 \exp\{-c_2 n\}$. Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
 	\begin{equation*}	
-	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma},
+	\Phi_{n,r}(A) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(A \vartriangle \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \right) \frac{\epsilon^2 r}{\sigma}
 	\end{equation*}
-	and plugging in $\delta = 1/2$ yields the claim of Lemma~\ref{lem:normalized_cut_lb}.
+	with probability at least $1 - c_1 \exp\{-c_2 n\}$.
 \end{proof}
@@
 \end{equation*}
+with probability at least $1 - c_1\exp\{-c_1 n\}$.
 Finally, we show that the volume of $\mathcal{L}[\Xbf]^g$ is sufficiently large to ensure that it includes many points in $\mathcal{C}_{\sigma}^{(1)}[\Xbf]$:
@@
 & \geq \frac{5}{6}\vol_{n,r}((\mathcal{L} \cap \mathcal{C}_{\sigma}^{(1)})[\Xbf]) - \frac{1}{6}\vol_{n,r}(\mathcal{L}[\Xbf]) \\
-& \geq \left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}) \\
-& \geq \frac{(1 - \delta)}{2}\left(\frac{5}{6}(1 - \delta) - \frac{1}{2}(1 + \delta)\right)\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])
+& \geq \left(\frac{5}{6} - \frac{(1 + \delta)}{2(1 - \delta)}\right)\vol_{n,r}((\mathcal{L} \cap \mathcal{C}_{\sigma}^{(1)})[\Xbf]) \\
+& \geq \frac{(1 - \delta)}{2(1 + \delta)}\left(\frac{5}{6} - \frac{(1 + \delta)}{2(1 - \delta)}\right)\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])
 \end{align*}
-where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration} and hold with probability at least $1 - 3\exp\set{-n\delta^2(\vol_{\Pbb,r}( \mathcal{L} \cap \Csig^{(1)}))^2}$.
-Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{10}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$.
+with high probability, where the final two inequalities follow from Lemma~\ref{lem:graph_functional_concentration}.
+Setting $\delta = 1/13$, we have that $\vol_{n,r}(\mathcal{L}[\Xbf]^g \cap \mathcal{C}_{\sigma}^{(1)}[\Xbf]) \geq \frac{1}{4}\vol_{n,r}(\mathcal{C}_{\sigma}^{(1)}[\Xbf])$.
 
@@
 
-\begin{lemma}[Union bound.]
-	\label{lem:bernstein_union}
-	For $M \geq 1$, let $\mathcal{A}_1,\ldots,\mathcal{A}_M$ be subsets of $\Reals^d$.
-Denote the minimum probability mass among these sets as $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$.
+\begin{lemma}[Bernstein's inequality and a union bound.]
+	For $M \geq 1$, let $\mathcal{A}_1,\ldots,\mathcal{A}_M$ be subsets of $\Reals^d$, and denote the minimum probability $p_{\min} := \min_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$, and likewise let $p_{\max} := \max_{m = 1,\ldots,M} \Pbb(\mathcal{A}_m)$.
 Then
 	\begin{equation*}
-	(1 - \delta)p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \Pbb_n(\mathcal{A}_m) \leq (1 + \delta)p_{\max}
+	(1 - \delta)p_{\min} \leq \min_{m = 1,\ldots,M} \Pbb_n(M) \leq \max_{m = 1,\ldots,M} \Pbb_n(M) \leq (1 + \delta)p_{\max}
 	\end{equation*}
-	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{3}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$.
-
-	Similarly, for $r > 0$ let $v_{\min} = \min_{m = 1,\ldots,M} \vol_{\Pbb,r}(\mathcal{A}_m)$ and $v_{\max} = \max_{m = 1,\ldots,M} \vol_{\Pbb,r}(\mathcal{A}_m)$. Then
-	\begin{equation*}
-	(1 - \delta)v_{\min} \leq \min_{m = 1,\ldots,M} \vol_{n,r}(\mathcal{A}_m) \leq \max_{m = 1,\ldots,M} \vol_{n,r}(\mathcal{A}_m) \leq (1 + \delta)v_{\max}
-	\end{equation*}
-	with probability at least $1 - 2M \exp\set{-\delta^2 v_{\min}^2n}$. 
+	with probability at least $1 - 2 M \exp\left\{-\frac{\frac{1}{2}\delta^2p_{\min}n}{1 + \frac{\delta}{3}}\right\}$. 
 \end{lemma}

### 2021-09-01 notes/weekly_notes/9.16.19.NotesForWeek.tex
Added a bunch of notes.

--- 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex
@@
-\documentclass{report}
+\documentclass{article}
 \usepackage{amsmath}
@@
 \usepackage{fullpage}
-\usepackage{mathtools}
-\usepackage{subcaption}
-\usepackage{tikz}
 
@@
 
-\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
-\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
-\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
-\DeclareMathAccent{\wb}{0}{mathx}{"73}
-
-\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
-
 \newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
@@
 \newcommand{\Identity}{\mathbb{I}}
-\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
+\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
 \newcommand{\convprob}{\overset{p}{\to}}
@@
 \newcommand{\myexp}[1]{\exp \{ #1 \}}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
 \newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
@@
 \newcommand{\seq}[1]{\set{#1}_{n \in \N}}
-\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
+\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
 \newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
 \newcommand{\Var}{\mathrm{Var}}
-\newcommand{\Cov}{\mathrm{Cov}}
-\newcommand{\Xsetiam}{\mathrm{diam}}
+\newcommand{\diam}{\mathrm{diam}}
 
@@
 \newcommand{\hC}{\hat{C^{\sigma}_n}}
-\newcommand{\vol}{\mathrm{vol}}
+\newcommand{\vol}{\text{vol}}
 \newcommand{\spansp}{\mathrm{span}~}
@@
 
-\newcommand{\Linv}{L^{\Xsetagger}}
-\DeclareMathOperator*{\argmin}{argmin}
+\newcommand{\Linv}{L^{\dagger}}
+
 \DeclareMathOperator*{\argmax}{argmax}
@@
 \newcommand{\Rd}{\Reals^d}
-\newcommand{\Nbb}{\mathbb{N}}
+
+%%% Data
+\newcommand{\Xbf}{X}
 
@@
 \newcommand{\thetast}{\theta^{\star}}
-\newcommand{\betap}{\beta^{(p)}}
-\newcommand{\betaq}{\beta^{(q)}}
-\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
 
@@
 \newcommand{\Lgrid}{L_{\grid}}
-\newcommand{\Xsetgrid}{D_{\grid}}
-\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
-\newcommand{\Lap}{{\bf L}}
-\newcommand{\NLap}{{\bf N}}
-\newcommand{\PLap}{{\bf P}}
+\newcommand{\Dgrid}{D_{\grid}}
+\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
 
@@
 \newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Cset}{\mathcal{C}}
+\newcommand{\Csig}{\Cset_{\sigma}}
 \newcommand{\Hclass}{\mathcal{H}}
 \newcommand{\Pclass}{\mathcal{P}}
-\newcommand{\Leb}{L}
-\newcommand{\mc}[1]{\mathcal{#1}}
 
@@
 \newcommand{\Qbb}{\mathbb{Q}}
-\newcommand{\Ibb}{\mathbb{I}}
+
+%%% Vector spaces
+\newcommand{\Zbb}{\mathbb{Z}}
 
@@
 \newcommand{\Tadj}{T^{\star}}
-\newcommand{\Xsetive}{\mathrm{div}}
-\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
+\newcommand{\dive}{\mathrm{div}}
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
 \newcommand{\gradient}{\mathcal{D}}
 \newcommand{\Hessian}{\mathcal{D}^2}
-\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
-\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}
 
@@
 \newcommand{\critr}{R_n}
-\newcommand{\Xsetx}{\,dx}
-\newcommand{\Xsety}{\,dy}
-\newcommand{\Xsetr}{\,dr}
-\newcommand{\Xsetxpr}{\,dx'}
-\newcommand{\Xsetypr}{\,dy'}
+\newcommand{\dx}{\,dx}
+\newcommand{\dy}{\,dy}
+\newcommand{\dr}{\,dr}
 \newcommand{\wt}[1]{\widetilde{#1}}
-\newcommand{\wh}[1]{\widehat{#1}}
-\newcommand{\ol}[1]{\overline{#1}}
-\newcommand{\spec}{\mathrm{spec}}
-\newcommand{\LE}{\mathrm{LE}}
-\newcommand{\LS}{\mathrm{LS}}
-\newcommand{\OS}{\mathrm{OS}}
-\newcommand{\PLS}{\mathrm{PLS}}
-\newcommand{\dist}{\mathrm{dist}}
 
@@
 \begin{document}
-\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
+\title{Notes for 9/16/19 - 9/20/19}
 \author{Alden Green}
@@
 
-\chapter{Lower bound for conductance of continuous-space ball walk}
-For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$.
-Further define
-\begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
-\end{equation*}
-The uniform continuous normalized cut and conductance are then
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
-\end{equation*}
-where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.
+In the local spectral density clustering problem, one observes data $x_1,\ldots,x_n$ sampled independently from a density function $f$ supported on $\mathcal{X}$.
+Letting $\Cset$ be a connected component of the upper level set $\set{x:f(x) > \lambda}$, since we observe a finite sample we can only hope to recover $\Csig = \Cset + B(0,\sigma)$ for some $\sigma > 0$.
+Our strategy will be to
+\begin{itemize}
+	\item Form a neighborhood graph $G_{n,r}$ by connecting points at scale $r$ (i.e. using the kernel function $\1(\norm{x - y} \leq r)$. 
+	\item Operate in some manner on the neighborhood graph $G_{n,r}$ to form a cluster estimate $\hat{C}$. 
+\end{itemize}
 
-\begin{lemma}
-	\label{lem: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
-	\end{equation*}
-\end{lemma}
-Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
-\begin{corollary}
-	\label{cor: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
-	\end{equation*}
-\end{corollary}
+This week, we focus on lower bounds for the density clustering problem.
+To begin, let's detail the various lower bounds one might hope to prove (roughly in order from weakest to strongest.) In the following, $\Sset[\Xbf]$ will always be a set with high symmmetric set difference metric to $\Csig[\Xbf]$.
+For example, assume $\Delta(\Sset[\Xbf],\Csig[\Xbf]) \geq 1/8$ with high probability as $n \to \infty$.
+All but the last lower bound are inconsistency statements for various classes of algorithms; the last lower bound is a statement regarding sample complexity.
+\begin{enumerate}
+	\item There exists some $\Sset \subset \mathcal{X}$ such that if you perform PPR over $G_{n,r}$, and tune hyperparameters appropriately for $\Sset$, with high probability you will recover $\Sset[\Xbf]$ as $n \to \infty$.
 
-\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
-Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance.
-The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use.
-For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
-\begin{equation*}
-\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
-\end{equation*}
-where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
-\begin{enumerate}
-	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
-	\begin{equation*}
-	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
-	\end{equation*}
-	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
-	\begin{equation*}
-	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
-	\end{equation*}
-	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
-	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
-		\label{lem: nonconvex_isoperimetry}
-		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$,
-		\begin{equation*}
-		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
-		\end{equation*}
-	\end{lemma}
-	\item[4.] 
-	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
-	\begin{equation*}
-	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
-	\end{equation*}
-	\begin{lemma}
-		\label{lem: one_step_distributions}
-		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_1}
-		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
-		\end{equation}
-		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_2}
-		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
-		\end{equation}
-	\end{lemma}
-	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
-	\end{equation*}
-	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
-	\begin{equation*}
-	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
-	\end{equation*}
+	\item There exists some $\Sset \subset \mathcal{X}$ such that if you perform PPR over $G_{n,r}$, and tune hyperparameters appropriately for $\Csig$, with high probability you will recover $\Sset[\Xbf]$ as $n \to \infty$.
+
+	\item If you perform PPR over $G_{n,r}$ with $r$ tuned appropriately for $\Csig$, for any choice of hyperparameters $v, \alpha$ and $\pi_0$, with high probability you will recover some $\Sset_{(v,\alpha,\pi_0)}[\Xbf]$ as $n \to \infty$.
+
+	\item If you perform PPR over $G_{n,r}$ for any choice of hyperparameters $r, v, \alpha$ and $\pi_0$, with high probability you will recover some $\Sset_{(r, v,\alpha,\pi_0)}[\Xbf]$ as $n \to \infty$.
+
+	\item If you perform any spectral algorithm over $G_{n,r}$, you will fail to recover $\Csig[\Xbf]$ as $n \to \infty$.
+
+	\item For a fixed $n$ and for any $r > 0$, any algorithm operating on $G_{n,r}$ will have $\Delta(\widehat{C}, \Csig[\Xbf]) > \eta$ for some critical radius $\eta$ which may depend on $n$ and $r$. 
 \end{enumerate}
-The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e.
-a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show.
-In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
-\begin{equation*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
-\end{equation*}
-Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$.
-Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
-\end{equation*}
-Otherwise, we deduce that
-\begin{align*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
-& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
-& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
-\end{align*}
-Setting $\delta = 1/3$, we have
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
-\end{equation*}
-and putting $a = r\ell/(2\rho)$ yields the claim.
 
-Now, we turn to establishing the inequalities used in the above chain.
+The first lower bound is very weak, and we do not investigate it further.
+We include it merely to note that the strategy of applying an upper bound on PPR misclassification error to an appropriately chosen $\Sset \subset \Xset$ would result in this type of weak lower bound.
+Our lower bound will therefore require at least in part different proof techniques than the one we use for our upper bound.
 
-\paragraph{Step 1: Lower bound the ergodic flow.}
-By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
-\begin{equation*}
-2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
-\end{equation*}
+\section{PPR with any hyperparameters.}
 
-\paragraph{Step 2: Estimate the stationary distribution.}
+\section{Any spectral algorithm.}
 
-Both the upper and lower  bounds on $\wt{\pi}_{\nu,r}(\mc{S})$ are a direct consequence of the following inequalities:
-\begin{equation*}
-\ell \nu_d r^d \nu(\mc{S})  \leq {J}_{\nu,r}(\mc{S}) \leq \nu_d r^d \nu(\mc{S}).
-\end{equation*}
-\paragraph{Step 3: Isoperimetric inequality.}
-NB: the proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\mc{C}_{\sigma}$ is itself convex, and is a primary technical contribution of the seminal work \textcolor{red}{(Lovasz 1990)}, extended by \textcolor{red}{(Dyer 1991)} among others.
-However, once the result is shown in the convex setting, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
-\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
-	For $\Omega_i, i = 1,2,3$, denote the preimage
-	\begin{equation*}
-	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
-	\end{equation*}
-	For any $x \in R_1, y \in R_2$, 
-	\begin{equation*}
-	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
-	\end{equation*}
-	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
-	\begin{equation*}
-	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
-	\end{equation*}
-	By Theorem 2.2 of \textcolor{red}{(Lovasz 1990)},
-	\begin{align*}
-	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
-	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
-	\end{align*}
-	and by the measure-preserving property of $g$, this implies
-	\begin{equation*}
-	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
-	\end{equation*}
-\end{proof}
+Note: this section will be consistent in spirit, but not in technical details, with the problem as introduced previously.
 
-\paragraph{Step 4: Total variation distance.}
-
-\begin{proof}[Proof of Lemma~\ref{lem: one_step_distributions}]
-	Note that~\eqref{eqn:one_step_distributions_2} follows from~\eqref{eqn:one_step_distributions_1} by first taking the supremum over all $\mc{S} \subseteq \mc{C}_{\sigma}$, and then the infimum over all $x \in \mc{S}_1$ and $y \in \mc{S}_2$.
-
-	It remains to show~\eqref{eqn:one_step_distributions_1}.
-Let $\mc{R} = \mc{C}_{\sigma} \setminus \mc{S}$ and $\mc{I} = B(x,y) \cap B(y,r)$, and suppose without loss of generality that $\ell_{\nu,r}(x) > \ell_{\nu,r}(y)$.
-We can relate $\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})$ to the volume of the intersection $\mc{I}$ as follows:
-	\begin{align*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) & = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \\
-	& = 1 - \biggl(\frac{\nu\bigl(B(x,r) \cap \mc{R}\bigr)}{\ell_{\nu,r}(x)} + \frac{\nu\bigl(B(y,r) \cap \mc{S}\bigr)}{\ell_{\nu,r}(y)}\biggr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr)\Bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\nu\bigl(\mc{I} \cap \mc{C}_{\sigma}\bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu(\mc{I}) - \nu\bigl(B(x,r)\bigr) + \ell_{\nu,r}(x)\Bigr) \\
-	& = \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu_dr^d - \nu(\mc{I})\Bigr).
-	\end{align*}
-	Now, by hypothesis $\ell_{\nu,r}(x) \geq \ell \nu_dr^d$. On the other hand, Lemma~\ref{lem: volume_of_spherical_cap} gives a lower bound on the volume of $\mc{I}$, and from this we obtain
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) \leq \frac{\|x - y\|}{\ell r} \sqrt{\frac{d + 2}{2\pi}};
-	\end{equation*}
-	solving for $\|x - y\|$ yields~\eqref{eqn:one_step_distributions_1}.
-\end{proof}
-
-\section{Volume Estimates}
-
-\begin{lemma}
-	\label{lem: overlap_balls}
-	For any $x,y \in \Rd$, it holds that
-	\begin{equation}
-	\label{eqn:overlap_balls_1}
-	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation}
-	If additionally $\|x - y\| \leq \sigma$, then
-	\begin{equation}
-	\label{eqn:overlap_balls_2}
-	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr)
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We first prove~\eqref{eqn:overlap_balls_1}. It is not hard to see that $\mathcal{I} := B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height
-	\begin{equation*}
-	h = r - \frac{\|x - y\|}{2}
-	\end{equation*} 
-	As a result, by Lemma \ref{lem: volume_of_spherical_cap} we have
-	\begin{equation*}
-	\nu\bigl(\mathcal{I}\bigr) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{\|x - y\|^2}{4r^2}.
-	\end{equation*}
-	Expanding the incomplete beta function in integral form, we obtain
-	\begin{align*}
-	\nu\bigl(\mathcal{I}\bigr) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{ \|x - y\|}{r} \right) \\
-	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}} \right),
-	\end{align*}
-	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral}, and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
-
-	We now establish~\eqref{eqn:overlap_balls_2}.
-Assume that $\|x - y\| = \sigma$, as otherwise if $\|x - y\| < \sigma$ the volume of the overlap will only grow.
-Then $B(x,r) \cap B(y,\sigma)$ contains a spherical cap of radius $r$ and height $r - \frac{r^2}{2\sigma}$, and similar derivations to those used to show~\eqref{eqn:overlap_balls_1} imply that
-	\begin{equation*}
-	\nu(\cap_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation*}
-\end{proof}
-
-\subsection{Spherical caps and associated estimates}
-\label{subsec:caps}
-In this section, we state a result for the volume of a spherical cap and derive some 
-useful upper bounds. 
-\begin{lemma}
-	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha := 1 - \frac{2 r h - h^2}{r^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
-	\end{equation*}
-	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
-\end{lemma}
-The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
-an upper bound on the ratio of Gamma functions. 
-\begin{lemma}
-	\label{lem: beta_integral}
-	For any $0 \leq \alpha \leq 1$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - 2\sqrt{\alpha}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write 
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
-	\end{equation*}
-	The first integral is simply the beta function, with
-	\begin{equation*}
-	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
-	\end{equation*}
-	Noting that for all $u \in [0,1]$ and $d \geq 1$, $u^{(d - 1)/2} \leq 1$, the second integral can be upper bounded as follows:
-	\begin{equation*}
-	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du \leq \int_{1 - \alpha}^{1}(1 - u)^{-1/2}du = \int_{0}^{\alpha} u^{-1/2}du = 2\sqrt{\alpha}.
-	\end{equation*}
-\end{proof}
-
-\begin{lemma}
-	\label{lem: beta_function}
-	\begin{equation*}
-	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
-	\end{equation*}
-\end{lemma}
-\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
-
-\section{Other derived results}
-
-Lemma~\ref{lem:volume_perturbation} bounds the difference $\nu(B(x,r) \cap \mc{C}_{\sigma}) - \nu(B(y,r) \cap \mc{C}_{\sigma})$ as a function of $\|x - y\|_{\Rd}$.
-Unfortunately, it only kicks in when $\|x - y\| \lesssim r/d$, whereas we would like something which applies when $\|x - y\| \lesssim r/\sqrt{d}$.
-
-\begin{lemma}
-	\label{lem:volume_perturbation}
-	Let $x,y \in \mc{C}_{\sigma}$ satisfy $\|x - y\| < \frac{r}{d - 1}$. Then,
-	\begin{equation*}
-	\Bigl|\nu\bigl(B(x,r) \cap \mc{C}_{\sigma}\bigr) - \nu\bigl(B(y,r) \cap \mc{C}_{\sigma}\bigr)\Bigr| \leq \nu_dr^d\frac{d\|y - x\|}{(r - (d - 1)\|y - x\|)}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	By the triangle inequality, 
-	\begin{align*}
-	\nu(B(x,r) \cap \mc{C}_{\sigma}) & = \int_{\mc{C}_{\sigma}} \1(\|z - x\| \leq r) \,dz \\
-	& \leq \int_{\mc{C}_{\sigma}} \1(\|z - y\| \leq r + \|y - x\|) \,dz \\
-	& = \int_{\mc{C}_{\sigma}} \bigl(\1(\|z - y\| \leq r) + \1(r < \|z - y\| \leq r + \|y - x\|) \bigr)  \,dz \\
-	& \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) + \nu_d\bigl((r + \|y - x\|)^d - r^d\bigr),
-	\end{align*}
-	and the upper bound $\nu(B(x,r) \cap \mc{C}_{\sigma}) \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) +  \nu_dr^dd\|y - x\|/(r - (d - 1)\|y - x\|)$ follows by Bernoulli's inequality (\textcolor{red}{(Lemma 22)}).
-Reversing $x$ and $y$ gives an equivalent upper bound on $\nu(B(y,r) \cap \mc{C}_{\sigma})$.
-\end{proof}
-
-\chapter{Misclassification error of PPR}
-The following Lemma upper bounds the misclassification error of (a sweep cut of) a PPR vector, in terms of the \emph{normalized cut} and \emph{mixing time} functionals.
-It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
-\begin{lemma}
-	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
-For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
-	\begin{equation*}
-	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}.
-	\end{equation*} 
-	For some $A \subseteq V$, suppose that 
-	\begin{equation*}
-	\alpha \leq \min\Bigl\{\frac{1}{15}, \frac{1}{5\tau_{\infty}(G[A])}\Bigr\},~~ \beta, \varepsilon \leq \frac{1}{4\vol(A;G)}.
-	\end{equation*}
-	Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$, the sweep cut $S_{\beta,v}$ satisfies
-	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v};G) \leq \left(\frac{3}{\beta} + \frac{200}{9\vol(A;G)}\right) \frac{\Phi(A;G)}{\alpha}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We adopt the notation $\wt{p}_v$ for the (exact) PPR vector computed over the subgraph $G[A]$, and 
-	\begin{equation*}
-	\wt{\pi}(u) = \frac{\deg(u;G[A])}{\vol(A;G[A])}
-	\end{equation*}
-	for the stationary distribution of a random walk over $G[A]$.
-The proof of this Lemma proceeds along very similar lines to that of~\textcolor{red}{(Zhu 2013 Lemma 3.4)}.
-We directly use the following three inequalities, derived in that work:
-	\begin{itemize}
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.2.)} For any seed node $v \in A$, the following inequalities hold for every $u \in A$:
-		\begin{equation}
-		\label{pf:zhu1}
-		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u)
-		\end{equation}
-		\item \textcolor{red}{(Zhu 2013 Corollary 3.3)} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
-		\begin{equation}
-		\label{pf:zhu2}
-		p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G),
-		\end{equation}
-		and $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.1, Anderson 2007 Theorem 5.1)} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
-		\begin{equation}
-		\label{pf:zhu3}
-		\sum_{u \neq A} p_v(u) \leq 2\frac{\Phi(A;G)}{\alpha}.
-		\end{equation}
-	\end{itemize}
-	From these we can derive the following upper bound on the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
-	\begin{itemize}
-		\item For any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
-		\begin{equation*}
-		\vol(S_{\beta,v} \setminus A; G) \leq \frac{1}{\beta} \sum_{u \not\in A}p_v^{(\varepsilon)}(u) \leq 2\frac{\Phi(A;G)}{\beta \cdot \alpha}.
-		\end{equation*} 
-		\item For any $u \in A$, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$,
-		\begin{equation*}
-		p_v^{(\varepsilon)}(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G).
-		\end{equation*}
-		If $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
-		\begin{equation}
-		\label{pf:zhu4}
-		\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr)\wt{\pi}(u) - (\varepsilon + \beta)\deg(u;G) \leq \wt{p}_{\ell}(u).
-		\end{equation}
-
-		Let us restrict our attention for the moment to those vertices $u$ with sufficiently large degree in $G[A]$; precisely speaking, let
-		\begin{equation*}
-		A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\}.
-		\end{equation*}
-		We note that for any $u \in A^{\mathrm{int}}$,
-		\begin{equation*}
-		\wt{\pi}(u) > \frac{(1 - \alpha \beta \vol(A;G))\deg(u;G)}{\vol(A;G)},
-		\end{equation*}
-		so that by~\eqref{pf:zhu4} it holds that
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u)
-		\end{equation*}
-		for any $u \in A^{\mathrm{int}} \setminus S_{\beta,v}$. Summing over all such u, we obtain
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \sum_{u \in A^{\mathrm{int}} \setminus S_{\beta,v}} \wt{p}_{\ell}(u) \leq 2\frac{\Phi(A;G)}{\alpha}
-		\end{equation*}
-		where the second upper bound follows from the upper bound on $\|\ell\|_1$, since $\sum_{u \in A} \wt{p}_{\ell}(u) = \|\ell\|_1$. 
-		Then, from the assumed upper bounds on $\alpha, \beta$ and $\varepsilon$ we obtain the inequality
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{9}{100\vol(A;G)}.
-		\end{equation*}
-		\item Finally, for every $u \in A \setminus A^{\mathrm{int}} $, it holds that $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$.
-Summing over all such vertices, we obtain
-		\begin{equation*}
-		\vol(A \setminus A^{\mathrm{int}};G) \leq \frac{\Phi(A;G)}{\alpha \cdot \beta}.
-		\end{equation*}	
-	\end{itemize}
-\end{proof}
+Let $K(x,y)$ be a positive semi-definite kernel function in $\Rd$.
 

### 2021-09-01 jmlr/revision/appendix.tex
Newest version of jmlr tex and bib files.

--- 2021-01-31 jmlr/revision/archive/proofs.tex
@@
-\documentclass{article}
-\usepackage{amsmath, amsfonts, amsthm, amssymb}
-\usepackage{xr}
-\usepackage[colorlinks]{hyperref}
-\usepackage[parfill]{parskip}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{enumerate}
-\usepackage[shortlabels]{enumitem}
-\usepackage{graphics}
-\usepackage[export]{adjustbox} 
-\usepackage{subcaption}
-\usepackage{mathtools}
-\usepackage{tikz}
-\usepackage{verbatim}
-\usepackage{fullpage}
-
-\externaldocument{local_spectral_clustering_jmlr_revision_2}
-
-\usepackage{natbib}
-\renewcommand{\bibname}{REFERENCES}
-\renewcommand{\bibsection}{\subsubsection*{\bibname}}
-
-\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
-\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
-\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
-\DeclareMathAccent{\wb}{0}{mathx}{"73}
-
-\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
-\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}
-
-% Make a widecheck symbol (thanks, Stack Exchange!)
-\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
-\DeclareFontShape{U}{mathx}{m}{n}{
-	<5> <6> <7> <8> <9> <10>
-	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
-	mathx10
-}{}
-\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
-\DeclareFontSubstitution{U}{mathx}{m}{n}
-\DeclareMathAccent{\widecheck}{0}{mathx}{"71}
-% widecheck made
-
-\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
-\newcommand{\Graph}{\mathcal{G}}
-\newcommand{\Reals}{\mathbb{R}}
-\newcommand{\iid}{\overset{\text{i.i.d}}{\sim}}
-\newcommand{\convprob}{\overset{p}{\to}}
-\newcommand{\convdist}{\overset{w}{\to}}
-\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
-\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
-\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
-\newcommand{\iset}{\mathbf{i}}
-\newcommand{\jset}{\mathbf{j}}
-\newcommand{\myexp}[1]{\exp \{ #1 \}}
-\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
-\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
-\newcommand{\ext}[1]{\widetilde{#1}}
-\newcommand{\set}[1]{\left\{#1\right\}}
-\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
-\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\newcommand{\Var}{\mathrm{Var}}
-\newcommand{\Cov}{\mathrm{Cov}}
-\newcommand{\diam}{\mathrm{diam}}
-
-\newcommand{\emC}{C_n}
-\newcommand{\emCpr}{C'_n}
-\newcommand{\emCthick}{C^{\sigma}_n}
-\newcommand{\emCprthick}{C'^{\sigma}_n}
-\newcommand{\emS}{S^{\sigma}_n}
-\newcommand{\estC}{\widehat{C}_n}
-\newcommand{\hC}{\hat{C^{\sigma}_n}}
-\newcommand{\vol}{\mathrm{vol}}
-\newcommand{\cut}{\mathrm{cut}}
-\newcommand{\spansp}{\mathrm{span}~}
-\newcommand{\1}{\mathbf{1}}
-
-\newcommand{\Linv}{L^{\dagger}}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\argmax}{argmax}
-
-\newcommand{\emF}{\mathbb{F}_n}
-\newcommand{\emG}{\mathbb{G}_n}
-\newcommand{\emP}{\mathbb{P}_n}
-\newcommand{\F}{\mathcal{F}}
-\newcommand{\D}{\mathcal{D}}
-\newcommand{\R}{\mathcal{R}}
-\newcommand{\Rd}{\Reals^d}
-\newcommand{\Nbb}{\mathbb{N}}
-
-%%% Vectors
-\newcommand{\thetast}{\theta^{\star}}
-\newcommand{\betap}{\beta^{(p)}}
-\newcommand{\betaq}{\beta^{(q)}}
-\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
-\newcommand{\lambdavec}{\boldsymbol{\lambda}}
-
-%%% Matrices
-\newcommand{\X}{X} % no bold
-\newcommand{\Y}{Y} % no bold
-\newcommand{\Z}{Z} % no bold
-\newcommand{\Lgrid}{L_{\grid}}
-\newcommand{\Dgrid}{D_{\grid}}
-\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
-\newcommand{\Lap}{L}
-\newcommand{\NLap}{{\bf N}}
-\newcommand{\PLap}{{\bf P}}
-\newcommand{\Id}{I}
-
-%%% Sets and classes
-\newcommand{\Xset}{\mathcal{X}}
-\newcommand{\Vset}{\mathcal{V}}
-\newcommand{\Sset}{\mathcal{S}}
-\newcommand{\Hclass}{\mathcal{H}}
-\newcommand{\Pclass}{\mathcal{P}}
-\newcommand{\Leb}{L}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-
-%%% Distributions and related quantities
-\newcommand{\Pbb}{\mathbb{P}}
-\newcommand{\Ebb}{\mathbb{E}}
-\newcommand{\Qbb}{\mathbb{Q}}
-\newcommand{\Ibb}{\mathbb{I}}
-
-%%% Operators
-\newcommand{\Tadj}{T^{\star}}
-\newcommand{\dive}{\mathrm{div}}
-\newcommand{\dif}{\mathop{}\!\mathrm{d}}
-\newcommand{\gradient}{\mathcal{D}}
-\newcommand{\Hessian}{\mathcal{D}^2}
-\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
-\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}
-
-%%% Misc
-\newcommand{\grid}{\mathrm{grid}}
-\newcommand{\critr}{R_n}
-\newcommand{\dx}{\,dx}
-\newcommand{\dy}{\,dy}
-\newcommand{\dr}{\,dr}
-\newcommand{\dxpr}{\,dx'}
-\newcommand{\dypr}{\,dy'}
-\newcommand{\wt}[1]{\widetilde{#1}}
-\newcommand{\wh}[1]{\widehat{#1}}
-\newcommand{\ol}[1]{\wb{#1}}
-\newcommand{\spec}{\mathrm{spec}}
-\newcommand{\LE}{\mathrm{LE}}
-\newcommand{\LS}{\mathrm{LS}}
-\newcommand{\SM}{\mathrm{SM}}
-\newcommand{\OS}{\mathrm{OS}}
-\newcommand{\PLS}{\mathrm{PLS}}
-
-%%% Theorem environments
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}{Conjecture}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{assumption}{Assumption}[section]
-\newtheorem{remark}{Remark}[section]
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\theoremstyle{remark}
-
-\begin{document}
-\title{Proofs for ``Geometry of Local Spectral Clustering''}
-\author{Alden Green}
-\date{\today}
-\maketitle
-
-The proofs of our major theorems largely consist of (at most) three modular parts.
+\noindent The proofs of our major theorems largely consist of (at most) three modular parts.
 \begin{enumerate}
 	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
-	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. 
+	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, w  e relate the aforementioned functionals to their population analogues. 
 	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
 \end{enumerate}
-The first three sections of this appendix will correspond to each of these three parts.
-In Section~\ref{sec:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, Theorems~\ref{thm:volume_ssd_ub} and~\ref{thm:density_cluster_volume_ssd_ub}, as well as our negative result, Theorem~\ref{thm:ppr_lb}.
-In Section~\ref{sec:appr_misclassification_error} we derive upper bounds for the aPPR vector, and show that under certain conditions the PPR vector can perfectly separate two density clusters.
-Finally, in Section~\ref{sec:experimental_details} we give relevant details regarding our experiments.
+
+Appendices \ref{apdx:fixed_graph}-\ref{apdx:density_cluster_population_functionals} will correspond to each of these three parts.
+In Appendix~\ref{apdx:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, Theorems~\ref{thm:volume_ssd_ub} and~\ref{thm:density_cluster_volume_ssd_ub}, as well as our negative result, Theorem~\ref{thm:ppr_lb}.
+In Appendix~\ref{apdx:appr_misclassification_error} we derive upper bounds for the aPPR vector, and show that under certain conditions the PPR vector can perfectly separate two density clusters.
+Finally, in Appendix~\ref{apdx:experimental_details} we give relevant details regarding our experiments.
 
 \section{Fixed graph results}
-In this section, we give all results that hold with respect to an arbitrary graph $G$.
+\label{apdx:fixed_graph}
+In this appendix, we give all results that hold with respect to an arbitrary graph $G$.
 For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.
@@
 
-\begin{proof}[Proof (of Lemma~\ref{lem:zhu})]
+\paragraph{Proof of Lemma~\ref{lem:zhu}.}
 As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma.
@@
 \end{itemize}
-We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
+teWe use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
 \begin{equation*}
@@
 The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
-\end{proof}
 
@@
 	\begin{equation}
-	\label{eqn:zhu_ub}
+	\label{eqn:zhu_ub_appr}
 	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
@@
 \end{corollary}
-\begin{proof}[Proof (of Corollary~\ref{cor:zhu})]
+
+\paragraph{Proof of Corollary~\ref{cor:zhu}.}
 	Recall that the upper bound~\eqref{eqn:zhu_ub} on $\vol(\wh{C} \vartriangle C;G)$ comes from combining the upper bounds on $\vol(\wh{C} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus \wh{C};G)$ and $\vol(C^{\mathrm{bdry}} \setminus \wh{C};G)$ in~\eqref{pf:zhu3.5},~\eqref{pf:zhu5} and~\eqref{pf:zhu6}.
@@
 	Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim.
-\end{proof}
 
@@
 
-\begin{proof}[Proof (of Lemma~\ref{lem:ppr_uniform_bound})]
+\paragraph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
 	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
@@
 	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.
-\end{proof}
 
@@
 \end{lemma}
-\paragraph{Proof of Theorems~\ref{thm:mixing_time_rw} and~\ref{thm:mixing_time_PPR}.}
-\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_rw})]
+
+\subsubsection{Proof of Theorems~\ref{thm:mixing_time_rw} and~\ref{thm:mixing_time_PPR}}
+
+\paragraph{Proof of Theorem~\ref{thm:mixing_time_rw}.}
 	Take $K_0 = 0$ if $u_{(1)} \neq v$, and otherwise take $K_0 = \deg(v;G)$.
@@
 	Since the ultimate upper bounds in~\eqref{pf:mixing_random_walk_1} and~\eqref{pf:mixing_random_walk_2} are each no greater than that of~\eqref{eqn:mixing_random_walk}, the claim follows.
-\end{proof}
-
-\begin{proof}[Proof (of Theorem~\ref{thm:mixing_time_PPR})]
+
+\paragraph{Proof of Theorem~\ref{thm:mixing_time_PPR}.}
 	The proof of Theorem~\ref{thm:mixing_time_PPR} follows immediately from Lemmas~\ref{lem:mixing_time_PPR},~\ref{lem:interpolator_bound_ppr} and~\ref{lem:linearization_bound}, taking $K_0 = 0$ if $u_{(1)} \neq v$ and otherwise $K_0 = \deg(v;G)$.
-\end{proof}
-
-\paragraph{Proofs of Lemmas.}
+
+\subsubsection{Proofs of Lemmas}
 In what follows, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$.
-\begin{proof}[Proof (of Lemma~\ref{lem:mixing_random_walk})]
+\paragraph{Proof of Lemma~\ref{lem:mixing_random_walk}.}
 	 We will prove Lemma~\ref{lem:mixing_random_walk} by induction on $t$.
@@
 	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:mixing_time_PPR}).]
+
+\paragraph{Proof (of Lemma~\ref{lem:mixing_time_PPR}).}
 	We will show that if $\Phi(S_j; g) \geq \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.
@@
 	\begin{align*}
-	h^{(\alpha)}(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	h^{(\alpha)}(k_j) & \leq \alpha +~~ \\
+	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
 	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
@@
 	and therefore
-	\begin{equation*}
-	h^{(\alpha)}(k_j) \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
-	\end{equation*}
+	\begin{align*}
+	h^{(\alpha)}(k_j) & \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \\
+	& = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
+	\end{align*}
 
@@
 	\end{align*}
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_rw})]
+
+\paragraph{Proof of Lemma~\ref{lem:interpolator_bound_rw}.}
 	We will prove that the inequalities of~\eqref{eqn:interpolator_bound_rw} hold at the knot points of $h^{(t_0)}$, whence they follow for all $K_0 \in [0,m]$.
@@
 	where the last inequality follows since $\vol(S) \geq |S| \cdot d_{\min}(G)$ for any set $S \subseteq V$.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:interpolator_bound_ppr})]
+
+\paragraph{Proof of Lemma~\ref{lem:interpolator_bound_ppr}.}
 	We have already established the first upper bound in~\eqref{eqn:interpolator_bound_ppr}, in the proof of Lemma~\ref{lem:interpolator_bound_rw}.
@@
 	the second upper bound in~\eqref{eqn:interpolator_bound_ppr} follows similarly to the proof of the equivalent upper bound in~Lemma~\ref{lem:interpolator_bound_rw}.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:linearization_bound}).]
+
+\paragraph{Proof of Lemma~\ref{lem:linearization_bound}.}
 	The result of the Lemma follows obviously from~\eqref{pf:linearization_bound_1}, once we show \eqref{eqn:right_derivative_1}-\eqref{eqn:right_derivative_2}.
@@
 	\end{equation*}
-\end{proof}
 
@@
 The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward.
-\begin{proof}[Proof (of Proposition~\ref{prop:pointwise_mixing_time})]
+\paragraph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
 	Put $t_{\ast} = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
@@
 	where the middle inequality follows by assumption.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:tv_to_pointwise})]
+
+\paragraph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
 	We proceed by induction. In the base case $t = 0$, we have that
@@
 	This completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
-\end{proof}
 
@@
 The claim of Theorem~\ref{thm:normalized_cut_ppr} is a consequence of~\eqref{eqn:ppr_leakage} along with Theorem~\ref{thm:mixing_time_PPR}, as we now demonstrate.
-\begin{proof}[Proof (of Theorem~\ref{thm:normalized_cut_ppr})]
+\paragraph{Proof of Theorem~\ref{thm:normalized_cut_ppr}.}
 	From~\eqref{eqn:ppr_leakage}, the upper bound in~\eqref{eqn:normalized_cut_ppr_vol}, and the choice of $\alpha = 36 \cdot \Phi(C;G)$, 
@@
 	Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be that $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem.
-\end{proof}
 
 \section{Sample-to-population bounds}
-\label{sec:sample_to_population}
-In this section, we prove Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, by establishing high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, and normalized cut~(\ref{subsec:sample_to_population_ncut}), minimum and maximum degree, and local spread~(\ref{subsec:sample_to_population_local_spread}), and conductance~(\ref{subsec:sample_to_population_conductance}).
+\label{apdx:sample_to_population}
+In this appendix, we prove Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, by establishing high-probability finite-sample bounds on various functionals of the random graph $G_{n,r}$: cut, volume, and normalized cut~(\ref{subsec:sample_to_population_ncut}), minimum and maximum degree, and local spread~(\ref{subsec:sample_to_population_local_spread}), and conductance~(\ref{subsec:sample_to_population_conductance}).
 To establish these results, we will use several different concentration inequalities, and we begin by reviewing these in~(\ref{subsec:concentration}).
@@
 \end{enumerate}
-When $d = 1$, it follows from Proposition~6.2 of \textcolor{red}{Dudley} that $\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_5 \|F - F_n\|_{\infty}$ for some positive constant $B_5$, and in turn from the DKW inequality (\textcolor{red}{Massart}) that
+When $d = 1$, it follows from Proposition~6.2 of \cite{dudley1968} that $\Delta_{\infty}(\Pbb,\Pbb_n) \leq B_5 \|F - F_n\|_{\infty}$ for some positive constant $B_5$, and in turn from the DKW inequality that
 \begin{equation}
@@
 When $d \geq 2$, \cite{garciatrillos16b} derive an upper bound on the transportation distance $\Delta_{\infty}(\mbb{P},\mbb{P}_n)$.
-\begin{theorem}[Theorem~1.1 of \cite{garciatrillos16}]
+\begin{theorem}[Theorem~1.1 of \cite{garciatrillos16b}]
 	\label{thm:garciatrillos16}
-	Suppose $\Pbb$ satisfies~\ref{asmp:domain} and~\ref{asmp:bounded_density}.
+	Suppose $\Pbb$ satisfies~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
 Then, there exists positive constants $B_{2}$ and $B_5$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
@@
 \end{theorem}
-Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:domain} and~\ref{asmp:bounded_density}, then~\eqref{eqn:ot_distance_1d} ($d = 1)$ or Theorem~\ref{thm:garciatrillos16} ($d \geq 2$) apply to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use these upper bounds on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
+Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}, then~\eqref{eqn:ot_distance_1d} ($d = 1)$ or Theorem~\ref{thm:garciatrillos16} ($d \geq 2$) apply to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use these upper bounds on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
 
@@
 We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$. 
-\begin{proof}[Proof (of Proposition~\ref{prop:conductance_lb_transportation_distance})]
+\paragraph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}
 	Throughout this proof, we will write $\Delta_{12} = \Delta_T(\mbb{Q}_1,\mbb{Q}_2)$, and $\wb{\vol}_{\mbb{Q},r}(\mc{R}) = \min\bigl\{\vol_{\mbb{Q},r}\bigl(\mc{R}\bigr),\vol_{\mbb{Q},r}\bigl(\mc{R}^c\bigr)\bigr\}$ for conciseness.
@@
 This completes the proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.
-\end{proof}
 
@@
 \section{Population functionals for density clusters}
-\label{sec:density_cluster_population_functionals}
-In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
+\label{apdx:density_cluster_population_functionals}
+In this appendix, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
 In these proofs, we make use of some estimates on the volume of spherical caps (in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
@@
 \end{equation}  
-\begin{proof}[Proof (of Lemma~\ref{lem:overlap_balls})]
+\paragraph{Proof of Lemma~\ref{lem:overlap_balls}.}
 	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
@@
 	for $a = (r - h)^2/r^2 = r^2/(4\sigma^2)$, and the claim follows.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:volume_of_spherical_cap})]
+
+\paragraph{Proof of Lemma~\ref{lem:volume_of_spherical_cap}.}
 	For any $0 \leq a \leq 1$, we have that
@@
 
-For any set $\mc{C} \subseteq \Rd$ and $\sigma > 0$, recall that $\mc{C}_{\sigma} := \{x: \mathrm{dist}(x,\mc{C}) \leq \sigma\}$.
+For any set $\mc{C} \subseteq \Rd$ and $\sigma > 0$, let $\mc{C}_{\sigma} := \{x: \mathrm{dist}(x,\mc{C}) \leq \sigma\}$.
 We begin with an upper bound on the volume of $\mc{C}_{\sigma + \delta}$ as compared to $\mc{C}_{\sigma}$.
@@
 \end{lemma}
-Lemma~\ref{lem:reverse_isoperimetric_inequality} should be interpreted as a reverse isoperimetric inequality.
+Lemma~\ref{lem:reverse_isoperimetric_inequality} is a reverse isoperimetric inequality.
 To see this, note that if $\delta \leq \sigma/d$ then $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:reverse_isoperimetric_inequality} that
@@
 \end{lemma}
-\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality})] 
+\paragraph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality}.}
 	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
@@
 	\begin{equation*}
-	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma},
-	\end{equation*}
-	with the last inequality following since $\mc{A}_1(\sigma),\ldots,\mc{A}_N(\sigma)$ are disjoint subsets of $\mc{C}_{\sigma}$.
+	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \nu(\mc{C}_{\sigma}).
+	\end{equation*}
+	The last inequality follows since $\mc{A}_1(\sigma),\ldots,\mc{A}_N(\sigma)$ are disjoint subsets of the closure of $\mc{C}_{\sigma}$.
 
@@
 	and applying $\nu(\cdot)$ to both sides yields the claim.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted})]
+
+\paragraph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted}.}
 	Fix $k \in \mathbb{N}$.
@@
 	The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim.
-\end{proof}
 
@@
 
-\begin{proof}[Proof (of Lemma~\ref{lem:uniform_density_cluster_conductance})]
+\paragraph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
 	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.
@@
 	and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$.
-\end{proof}
 
@@
 
-\begin{proof}[Proof of~\eqref{eqn:ncut_lower_set}.]
+\paragraph{Proof of~\eqref{eqn:ncut_lower_set}.}
 	Noting that $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, it suffices to upper bound $\cut_{\Pbb,r}(\mathcal{L})$ and lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
@@
 	\end{align*}
-	where the last inequality follows since $r \leq \frac{1}{4}\sigma < \frac{1}{4}\rho$. 
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eqn:local_spread_ub}.]
+	where the last inequality follows since $r \leq \frac{1}{4}\sigma \leq \frac{1}{4}\rho$.
+
+\paragraph{Proof of~\eqref{eqn:local_spread_ub}.}
 	The statement follows since 
 	\begin{equation*}
-	d_{\min}(\Pbb) \geq \frac{\pi r^2}{2} \cdot \min_{x \in \mc{X}} f(x) = \frac{\pi r^2}{2} \cdot \frac{\epsilon}{\rho \sigma}
+	d_{\min}(\Pbb) \geq \frac{\pi r^2}{2} \cdot \min_{x \in \mc{X}} f(x) = \frac{\pi r^2}{2} \cdot \frac{\epsilon}{\rho \sigma},
 	\end{equation*}
@@
 	\end{equation*}
-\end{proof}
-
 \section{Proof of Major Theorems}
-\label{sec:pf_major_theorems}
+\label{apdx:pf_major_theorems}
 We now prove the three major theorems of our paper: Theorem~\ref{thm:volume_ssd_ub} (in Section~\ref{subsec:pf_volume_ssd_ub}), Theorem~\ref{thm:density_cluster_volume_ssd_ub}, and Theorem~\ref{thm:ppr_lb}.
@@
 
-\textit{Probablistic estimates.}
+\paragraph{Probabilistic estimates.}
 Throughout the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume (i) that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} are satisfied; (ii) that the volume of $\mc{C}[X]$ is upper and lower bounded,
@@
 \end{equation}
-By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$.
+By Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$.
 
@@
 
-\begin{proof}[Proof (of Theorem~\ref{thm:volume_ssd_ub})]
+\paragraph{Proof of Theorem~\ref{thm:volume_ssd_ub}.}
 We use Lemma~\ref{lem:zhu} to upper bound $\Delta(\wh{C},\mc{C}[X])$.
@@
 
-Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, along with inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance} and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$ and .
+Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, along with inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance} and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$.
 On the other hand, by the upper bound on $\vol_{n,r}(\mc{C}[X])$ given in~\eqref{pf:volume_ssd_ub_1} and the initialization condition~\eqref{eqn:initialization}, we have that $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
@@
 Noting that $\wh{C} = S_{\beta,v}$ for some $\beta \in (L,U)$, the claimed upper bound~\eqref{eqn:volume_ssd_ub} on $\Delta(\wh{C},\mc{C}[X])$ then follows from the upper bound~\eqref{eqn:sample_to_population_normalized_cut} on $\Phi_{n,r}(\mc{C}[X])$ and the upper bound on $\vol_{\Pbb,r}(\mc{C})$ in~\eqref{pf:volume_ssd_ub_1}.
-\end{proof}
+
 \subsection{Proof of Theorem~\ref{thm:density_cluster_volume_ssd_ub}}
@@
 
-\textit{Probabilistic estimates.}
+\paragraph{Probabilistic estimates.}
 In addition to~\eqref{eqn:normalized_cut_lb}, we will assume (i) that the graph normalized cut of $\mc{L}$ and local spread of $\mc{X}$ are respectively upper and lower bounded,
@@
 
-\begin{proof}[Proof (of Theorem~\ref{thm:ppr_lb})]
+\paragraph{Proof of Theorem~\ref{thm:ppr_lb}.}
 	As mentioned, we would like to use Theorem~\ref{thm:normalized_cut_ppr} to upper bound $\Phi_{n,r}(\wh{C})$, and so we first verify that the conditions of Theorem~\ref{thm:normalized_cut_ppr} are met.
@@
 	where in $\mathrm{(i)}$ we have used $\vol_{\Pbb,r}(\mc{L}) \leq 3 \vol_{\Pbb,r}(\mc{C}^{(1)})$, and in $\mathrm{(ii)}$ and $\mathrm{(iii)}$ we have used $\delta \in (0,1/7)$.
-\end{proof}
-
-\begin{proof}[Proof (of Lemma~\ref{lem:normalized_cut_lb}).]
+
+\paragraph{Proof of Lemma~\ref{lem:normalized_cut_lb}.}
 	To lower bound the normalized cut $\Phi_{n,r}(Z)$, it suffices to lower bound $\cut_{n,r}(Z)$ and upper bound $\vol_{n,r}(Z)$. A crude upper bound on the volume is simply 
@@
 	for all $Z \subseteq X$.
-\end{proof}
 
 \section{Additional results: aPPR and Consistency of PPR}
-\label{sec:appr_misclassification_error}
-In this section, we prove two additional results regarding PPR remarked upon in our main text.
+\label{apdx:appr_misclassification_error}
+In this appendix, we prove two additional results regarding PPR remarked upon in our main text.
 In Section~\ref{subsec:appr_volume_ssd_ub}, we show that clustering using the aPPR vector satisfies an equivalent guarantee to Theorem~\ref{thm:volume_ssd_ub}.
@@
 \end{corollary}	
-\begin{proof}[Proof (of Corollary~\ref{cor:appr})]
+\paragraph{Proof of Corollary~\ref{cor:appr}.}
 	Note that the choice of $\varepsilon$ in~\eqref{eqn:appr_parameter} implies $\varepsilon \leq 1/\bigl(25\vol_{n,r}(\mc{C}[X])\bigr)$ with probability at least $1 - \exp\bigl\{-n\delta^2\vol_{\Pbb,r}(\mc{C})\bigr\}$.
 The proof of Corollary~\ref{cor:appr} is then identical to that of Theorem~\ref{thm:volume_ssd_ub}, except one uses Corollary~\ref{cor:zhu} rather than Lemma~\ref{lem:zhu} to relate the symmetric set difference to the graph normalized cut and mixing time.
-\end{proof}
 
@@
 However,~\eqref{pf:interpolator_bound_max_entry} is a somewhat crude bound.
-By plugging a stronger result on the smoothness of $p_v(\cdot)$ in to the proof of Lemma~\ref{lem:ppr_uniform_bound}, we could improve the uniform bounds of the lemma in turn show that the conclusion of Theorem~\ref{thm:density_cluster_consistent_recovery} holds under weaker conditions than~\eqref{eqn:density_cluster_consistent_recovery_condition}.
+By plugging a stronger result on the smoothness of $p_v(\cdot)$ in to the proof of Lemma~\ref{lem:ppr_uniform_bound}, we could improve the uniform bounds of the lemma, and in turn show that the conclusion of Theorem~\ref{thm:density_cluster_consistent_recovery} holds under weaker conditions than~\eqref{eqn:density_cluster_consistent_recovery_condition}.
 \end{itemize}
@@
 
-\textit{Probabilistic estimates.}
+\paragraph{Probabilistic estimates.}
 As in the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} and~\eqref{pf:volume_ssd_ub_1}-\eqref{pf:volume_ssd_ub_3} are satisfied.
@@
 % AJG: The term after \wedge is needed to condition on the two new inequalities.
-
-\begin{proof}[Proof (of Theorem~\ref{thm:density_cluster_consistent_recovery})]
+\paragraph{Proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.}
 We have already verified in the proof of Theorem~\ref{thm:volume_ssd_ub} that $\alpha \leq 1/(2\tau_{\infty}(\wt{G}_{n,r}))$, and we may therefore apply Lemma~\ref{lem:ppr_uniform_bound}, which gives an upper bound on $p_v(u)$ for all $u \in \mc{C}_{\lambda,\sigma}[X]_o$ and a lower bound on $p_v(u')$ for all $p_v(u')$ for all $u' \in \mc{C}_{\lambda,\sigma}'[X]_o$.
@@
 An equivalent derivation implies the upper bound in~\eqref{eqn:ppr_gap}: for all $u' \in \mc{C}_{\lambda}'[X]$,
-\begin{equation*}
-\frac{p_v(u')}{\deg_{n,r}(u')} \leq 2 \frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(G_{n,r}')^2 \alpha} \leq 4 \cdot \frac{1}{(n' - 1)^2} \cdot \frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\Pbb')^2} \leq 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{n^2 (1 - \delta)^5 \Pbb(\mc{C}_{\lambda,\sigma}')^2 d_{\min}(\Pbb')^2} \leq \frac{1}{10 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})},
-\end{equation*}
+\begin{align*}
+\frac{p_v(u')}{\deg_{n,r}(u')} & \leq 2 \frac{\Phi_{n,r}(\mc{C}_{\lambda,\sigma}[X])}{d_{\min}(G_{n,r}')^2 \alpha} \\
+& \leq 4 \cdot \frac{1}{(n' - 1)^2} \cdot \frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{(1 - \delta) d_{\min}(\Pbb')^2} \\
+& \leq 4\frac{ \kappa(\mc{C}_{\lambda,\sigma},\delta)}{n^2 (1 - \delta)^5 \Pbb(\mc{C}_{\lambda,\sigma}')^2 d_{\min}(\Pbb')^2} \leq \frac{1}{10 n^2\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})},
+\end{align*}
 completing the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.
 
-\end{proof}
-
 \section{Experimental Details}
-\label{sec:experimental_details}
+\label{apdx:experimental_details}
 Finally, we detail the settings of our experiments, and include an additional figure.
@@
 \rho &= .913, &&\sigma = .25, &&&(\lambda - \theta)/\lambda = .25 \tag{top panel} \\
-\rho &= (?), &&\sigma = (?), &&&(\lambda - \theta)/\lambda = (?) \tag{middle panel} \\
+\rho &= .25, &&\sigma = , &&&(\lambda - \theta)/\lambda = .05 \tag{middle panel} \\
 \rho &= .5, &&\sigma = .25, &&&(\lambda - \theta)/\lambda = .12 \tag{bottom panel.}
 \end{align*}
-In each of the second, third, and fourth columns, we fix two parameters and vary the third.
-In the second column, we fix $\sigma = .25$, $(\lambda - \theta)/\lambda = .25$, and vary $\rho$ from $.25$ to $2$.
-In the third column, we \textcolor{red}{(?)}.
-In the fourth column, we fix $\rho = .5$, $\sigma = .25$ and vary $(\lambda - \theta)/\lambda$ from $.1$ to $.25$.
-In the second and fourth columns, we take $r = \sigma/8$; in the third column, where we vary $\sigma$, we take $r = .1/8$.
+In each of the first, second, and third rows, we fix two parameters and vary the third.
+In the first row, we fix $\sigma = .25$, $(\lambda - \theta)/\lambda = .25$, and vary $\rho$ from $.25$ to $2$.
+In the second row, we fix $\rho = 1.8$, $(\lambda - \theta)/\lambda = .05$, and vary $\sigma$ from $.1$ to $.2$ In the third row, we fix $\rho = .5$, $\sigma = .25$ and vary $(\lambda - \theta)/\lambda$ from $.1$ to $.25$.
+In the first and third rows, we take $r = \sigma/8$; in the second row, where we vary $\sigma$, we take $r = .1/8$.
 
@@
 
-To form each of the three rows in Figure \ref{fig:moons}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'.
+To form each of the three rows in Figure \ref{fig:moons}, $n = 800$ points are independently sampled following a 'two moons plus Gaussian noise model'.
 Formally, the (respective) generative models for the data are
@@
 for $I_d$ the $d \times d$ identity matrix.
-The first column consists of the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the PPR plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
+In all cases $\sigma = .07$.
+In each case $\lambda$ is taken as small as possible such that there exist exactly two distinct density clusters, which we call $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$; $r$ is taken as small as possible so that each vertex has at least $2$ neighbors.
+The first column consists of the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the PPR plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{bresson2013}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
 
@@
 \end{figure}
-
-\clearpage
-\bibliographystyle{plainnat}
-\bibliography{../../local_spectral_bibliography}
-
-\end{document}

### 2021-09-01 jmlr/cover_letter.tex
Added some old stuff from original JMLR submission.

\documentclass{article}
\usepackage{enumerate}

\begin{document}

Dear Editors,

\vspace{.2 in}

Please find our attached submission titled: Local Spectral Clustering of Density Upper Level Sets. We analyze the Personalized PageRank (PPR) algorithm, a local spectral method for clustering, and provide geometric conditions under which the PPR algorithm provably recovers density clusters; we also show accompanying lower bounds. No previous publications by any of the authors significantly overlap with the submission. All of the co-authors are aware of the current submission and consent to its review. Sivaraman Balakrishnan has recently collaborated with Arthur Gretton; otherwise there are no potential conflicts of interest between action editors and the authors of this submission. We suggest Ingo Steinwart and Michael Mahoney as action editors particularly well-suited to handle the submitted manuscript. We would also suggest Vahab Mirrokni as a reasonable choice to serve as action editor for this submission. Thank you for your consideration of this manuscript.

\vspace{.2 in}

Sincerely,

\vspace{.1 in}
Alden Green, Sivaraman Balakrishnan, and Ryan Tibshirani

\end{document}

### 2021-09-01 jmlr/local_spectral_density_clustering_jmlr.tex
Added some old stuff from original JMLR submission.

--- 2019-11-21 arxiv/local_spectral_density_clustering_arxiv.tex
@@
 
+\clearpage
+
+\bibliographystyle{plainnat}
+\bibliography{../local_spectral_bibliography}
+
 \end{document}

### 2021-09-01 jmlr/revision2/appendix.tex
Added plots to new folder.

--- 2021-09-01 jmlr/revision/appendix.tex
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{../row4_true_density_cluster}
+			\includegraphics[width=\linewidth]{plots/experiment_2/row4_true_density_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{../row4_ppr_cluster}
+			\includegraphics[width=\linewidth]{plots/experiment_2/row4_ppr_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{../row4_conductance_cluster}
+			\includegraphics[width=\linewidth]{plots/experiment_2/row4_conductance_cluster}
 			\caption{}
@@
 		\begin{subfigure}{.24\linewidth}
-			\includegraphics[width=\linewidth]{../row4_density_cluster}
+			\includegraphics[width=\linewidth]{plots/experiment_2/row4_density_cluster}
 			\caption{}

### 2021-09-05 jmlr/revision2/appendix.tex
Through checking + copy-editting Appendices A and B.

@@
 	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
-	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, w  e relate the aforementioned functionals to their population analogues. 
-	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
+	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, results relating the aforementioned functionals to their population analogues. 
+	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, bounds on population functionals as a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
 \end{enumerate}
@@
 \label{apdx:fixed_graph}
-In this appendix, we give all results that hold with respect to an arbitrary graph $G$.
+In this section, we give all results that hold with respect to an arbitrary graph $G$.
 For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.
@@
 The adjacency matrix of $G$ is $A$, the degree matrix is $D$, and the lazy random walk matrix over $G$ is $W = (I + D^{-1}A)/2$.
-If the lazy random walk originates at a node $v$, the distribution of the lazy random walk $q_v^{(t)} := q(v,t;G)$ after $t$ steps is $q_v^{(t)} := e_v W^t$, with stationary distribution $\pi := \pi(G) := \lim_{t \to \infty} q_v^{(t)}$ with entries $\pi(u) = \deg(u;G)/\vol(u;G)$.
-
-For a starting distribution $s$ (by distribution we mean a vector with non-negative entries), the PPR vector $p_s = p(s,\alpha;G)$ is the solution of
+The lazy random walk originating at node $v \in V$ has distribution $q(v,t;G) = e_vW^t$ after $t$ steps; we use the notational shorthand $q_v^{(t)} := q(v,t;G)$.
+The stationary distribution of the lazy random walk is $\pi := \pi(G) := \lim_{t \to \infty} q_v^{(t)}$ is given by $\pi(u) = \deg(u;G)/\vol(u;G)$.
+
+For a starting distribution $s$ (by distribution we mean a vector with non-negative entries), the PPR vector $p_s = p(s,\alpha;G)$ is the solution to
 \begin{equation}
@@
 \end{equation*}
-We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq n \cdot d_{\max}(G)$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)
+We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq d_{\max}(G) \cdot n$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)
 
@@
 \end{itemize}
-teWe use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
+We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
 \begin{equation*}
@@
 \end{equation} 
-
 Next we upper bound $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$. From~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we see that 
@@
 \end{equation}
-
 Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
@@
 These quantities admit a natural interpretation in terms of random walks.
-For $u \in C$, $\ell^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $C$ on the $(t + 1)$st step.
-On the other hand, for $u \not\in C$, $s^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $\wt{G}$ for $t$ steps and is then ``soaked up'' into $u$ on the $(t + 1)$st step.
+For $u \in C$, $\ell^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $C$ for $t$ steps, arriving at $u$ on the $t$th step, and then ``leaks out'' of $C$ on the $(t + 1)$st step.
+On the other hand, for $u \not\in C$, $s^{(t)}(u)$ is the probability that a lazy random walk over $G$ originating at $v$ stays within $C$ for $t$ steps and is then ``soaked up'' into $u$ on the $(t + 1)$st step.
 The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the PPR vector.
@@
 	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$.
-Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry},
+Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(\ell)$, as a consequence of~\eqref{pf:interpolator_bound_max_entry},
 	\begin{equation*}
@@
 	\end{equation*}
-	and consequentially for any $S \subset V$,
+	and consequently for any $S \subset V$,
 	\begin{align*}
@@
 	Assume $k_j - \Psi(G) \wb{k}_j$ and $k_j + 2 \Psi(G) \wb{k}_j$ are both in $[K_0,2m  - K_0]$.
-We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h} and obtain the following:
+We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h}, and obtain the following:
 	\begin{align*}
 	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
-	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
-	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
+	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
+	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
 	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
@@
 	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
+	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
 	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
@@
 	h^{(\alpha)}(k_j) & \leq \alpha +~~ \\
-	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
-	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
 	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k}_j - \phi \wb{k}_j} + \sqrt{\wb{k}_j + \phi \wb{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
@@
 \label{subsec:pf_prop_pointwise_mixing_time}
-To prove Proposition~\ref{prop:pointwise_mixing_time}, we will upgrade from an upper bound on the total variation distance between $q_v^{(t)}$ and $\pi$ to the desired uniform upper bound.
+To prove Proposition~\ref{prop:pointwise_mixing_time}, we first give an upper bound on the total variation distance between $q_v^{(t)}$ and its limiting distribution $\pi$, then upgrade to the desired uniform upper bound~\eqref{eqn:pointwise_mixing_time}.
 The \emph{total variation distance} between distributions $q$ and $p$ is
@@
 	\label{lem:tv_to_pointwise}
-	For any $t \in \mathbb{N}$,
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{2 \cdot \mathrm{TV}(q_v^{(t)}, \pi)}{s(G)}.
+	For any $t_{\ast} \in \mathbb{N}$,
+	\begin{equation*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{1}{s(G)} \biggl(\sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{t_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{t_{\ast}}}\biggr).
 	\end{equation*}
 \end{lemma}
-
 The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward.
 \paragraph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
-	Put $t_{\ast} = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
-We will use Theorem~\ref{thm:mixing_time_rw} to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$.
+	Put $T = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
+We will use Theorem~\ref{thm:mixing_time_rw} to show that $\mathrm{TV}(q_v^{(T)},\pi) \leq 1/4$.
 This will in turn imply (\cite{montenegro2002} pg.
-13) that for $\tau_{\ast} = t_{\ast} \log_2(8/s(G))$,
-	\begin{equation*}
-	\mathrm{TV}(q_v^{(\tau_{\ast})},\pi) \leq \frac{1}{8}s(G),
-	\end{equation*}
-	and applying Lemma~\ref{lem:tv_to_pointwise} gives
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(\tau_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{1}{4}.
-	\end{equation*}
+13) that for all $t \geq t_{\ast} := T \log_2(32/s(G))$,
+	\begin{equation}
+	\label{pf:pointwise_mixing_time_1}
+	\mathrm{TV}(q_v^{(t)},\pi) \leq \frac{1}{32}s(G).
+	\end{equation}
+	Finally, let $\tau_{\ast} = t_{\ast} + 4\log_2(1/s(G))$. Applying Lemma~\ref{lem:tv_to_pointwise} gives
+	\begin{align*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(\tau_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} & \leq \frac{1}{s(G)}\biggl(\sum_{t = 0}^{\tau_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{\tau_{\ast}}}\biggr) \\
+	& = \frac{1}{s(G)}\biggl(\sum_{t = t_{\ast} + 1}^{\tau_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{\tau_{\ast}}}\biggr) \\
+	& \leq \frac{1}{4},
+	\end{align*}
+	where the final inequality follows from~\eqref{pf:pointwise_mixing_time_1} and the crude upper bound $\mathrm{TV}(q,\pi) \leq 1$, which holds for any distribution $q$.
 Taking maximum over all $v \in V$, we conclude that $\tau_{\infty}(G) \leq \tau_{\ast} + 1$, which implies the claim of Proposition~\ref{prop:pointwise_mixing_time}.
 
-	It remains to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$. Choosing $t_0 = 4$ in the statement of Theorem~\ref{thm:mixing_time_rw}, we have that
-	\begin{align*}
-	\mathrm{TV}(q_v^{(t_{\ast})},\pi) & \leq \frac{1}{16} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
-	& \leq \frac{1}{8} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
-	& \leq \frac{1}{8} + \frac{1}{2s(G)} \exp\Bigl(-\frac{\Psi(G)^2}{8}(t_{\ast} - 4)\Bigr) = \frac{1}{4},
+	It remains to show that $\mathrm{TV}(q_v^{(T)},\pi) \leq 1/4$. Choosing $t_0 = 4$ in the statement of Theorem~\ref{thm:mixing_time_rw}, we have that
+	\begin{align*}
+	\mathrm{TV}(q_v^{(T)},\pi) & \leq \frac{1}{16} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{T - 4} \\
+	& \leq \frac{1}{8} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{T - 4} \\
+	& \leq \frac{1}{8} + \frac{1}{2s(G)} \exp\Bigl(-\frac{\Psi(G)^2}{8}(T - 4)\Bigr) = \frac{1}{4},
 	\end{align*}
@@
 \paragraph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
-	We proceed by induction. In the base case $t = 0$, we have that
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq 1 \leq 2(1 - \pi(v)) \leq 2\frac{\mathrm{TV}(q_v^{(0)},\pi)}{s(G)},
-	\end{equation*},
-	where the second inequality follows since $\pi(v) \leq d_{\max}(G)/(2m) \leq d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$.
-
-	To prove the inductive step, the key observation is the following equivalence (see equation (16) of \citep{morris2005}):
+	Our goal will be to establish the recurrence relation~\eqref{pf:tv_to_pointwise_2}. 
+	To derive~\eqref{pf:tv_to_pointwise_2}, the key observation is the following equivalence (see equation (16) of \citep{morris2005}):
 	\begin{align}
@@
 	so that we obtain the recurrence relation
-	\begin{equation*}
+	\begin{equation}
+	\label{pf:tv_to_pointwise_2}
 	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} +\frac{\pi(u) - q_v^{(t)}(u)}{2\pi(u)}.
-	\end{equation*}
-	Then by the inductive hypothesis $\bigl(\pi(u) - q_v^{(t)}(u)\bigr)/\bigl(2\pi(u)\bigr) \leq \mathrm{TV}(q_v^{(t - 1)},\pi)/s(G)$, and consequentially
-	\begin{equation*}
-	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} + \frac{\mathrm{TV}(q_v^{(t - 1)},\pi) }{s(G)} \leq 2\frac{\mathrm{TV}(q_v^{(t)},\pi)}{s(G)}.
-	\end{equation*}
-	This completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
+	\end{equation}
+	From~\eqref{pf:tv_to_pointwise_2} alogn with the initial condition
+	\begin{equation*}
+	\Bigl\{\frac{\pi(u) - q_v^{(1)}(u)}{\pi(u)}\Bigr\} \leq 1 \leq 2(1 - \pi(v)) \leq 2\frac{\mathrm{TV}(q_v^{(0)},\pi)}{s(G)},
+	\end{equation*}
+	---where the second inequality follows because $\pi(v) \leq d_{\max}(G)/(2m) \leq d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$---we obtain the upper bound
+	\begin{equation*}
+	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{1}{s(G)} \biggl(\sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{t_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{t_{\ast}}}\biggr).
+	\end{equation*}
+	This inequality holds for each $u \in V$, and taking the maximum over $u$ completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
 
@@
 	\end{equation*}
-	hold with probability at least $1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/(2 + 2\delta)} \leq 1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/4}$. 
+	hold with probability at least $1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/(2 + 2\delta)} \geq 1 - \exp\set{-n\delta^2\Pbb(\mathcal{S})/4}$. 
 \end{lemma}
@@
 	\end{equation*}
-	hold with probability at least $1 - \exp\{-n\delta^2 \Ebb U_n/(4 + 4\delta/3)\} \leq 1 - \exp\{-n\delta^2 \Ebb U_n/6\}$.
+	hold with probability at least $1 - \exp\{-n\delta^2 \Ebb U_n/(4 + 4\delta/3)\} \geq 1 - \exp\{-n\delta^2 \Ebb U_n/6\}$.
 \end{lemma}
@@
 	\label{eqn:conductance_lb_transportation_distance}
-	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{2B_6\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{B_6 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
-	\end{equation}
-	where $B_6 := 2d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
+	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{B_6\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{B_6 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
+	\end{equation}
+	where $B_6 := 4d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
 \end{proposition}
@@
 	\end{equation}
-	For any $x \in \Rd$, the remainder terms can be upper bounded: since $\Delta_{12} \geq 0$,
-	\begin{equation*}
-	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{2 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= B_6} \cdot \Delta_{12},
-	\end{equation*}
-	if $0 \leq \Delta_{12} \leq r/(4(d - 1))$,
-	\begin{equation*}
-	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq 2 B_6 \cdot \Delta_{12}.
+	For any $x \in \Rd$, since $0 \leq \Delta_{12} \leq r/(4(d - 1))$, the remainder terms can be upper bounded as follows:
+	\begin{equation*}
+	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{4 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= B_6} \cdot \Delta_{12},
+	\end{equation*}
+	and
+	\begin{equation*}
+	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq B_6 \cdot \Delta_{12}.
 	\end{equation*} 
@@
 	\begin{align*}
-	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - B_6 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}} \\
-	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - 2B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
+	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - B_6 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6\Delta_{12}}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6\Delta_{12}} \\
+	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
 	\end{align*}
@@
 	\begin{equation*}
-	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{2 B_6 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{B_6\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
+	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{B_6 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{B_6\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
 	\end{equation*}
@@
 so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$.
-We now use the bounds we have derived on transportation distance and minimum degree.
-From the derivations in Section~\ref{subsec:sample_to_population_conductance}, it follows with probability at least $1 - (n + 1)\exp\{-nb_2/16\}$ that,
-\begin{equation*}
-d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} \bigl(d_{\min}(\wt{G}_{n,r}) + 1\bigr) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
+To begin, we recall from Section~\ref{subsec:sample_to_population_local_spread} that the lower bound on minimum degree,
+\begin{equation*}
+d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} \bigl(d_{\min}(\wt{G}_{n,r}) + 1\bigr) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}),
 \end{equation*}
 % Here I replaced a factor of (1 - 1/sqrt{2})^2 by 1/16, for convenience.
-On the other hand, taking
-\begin{equation*}
-b_6 := \frac{1}{2B_6}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := B_5 \Bigl(\min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\}\Bigr)^{-1},
+is satisfied with probability at least $1 - (n + 1)\exp\{-nb_2/16\}$. On the other hand, taking
+\begin{equation*}
+b_6 := \frac{1}{B_6}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := B_5 \Bigl(\min\Bigl\{b_6, \frac{r}{4(d - 1)} \Bigr\}\Bigr)^{-1},
 \end{equation*}
@@
 \begin{equation*}
-\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
-\end{equation*}
-with probability at least $1 - B_2/n$. Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance},
-\begin{equation*}
-\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+\end{equation*}
+with probability at least $1 - B_2/n$.
+Finally, appealing first to  Proposition~\ref{prop:conductance_lb_transportation_distance} and then to the bounds we have just established on $d_{\min}(\wt{\Pbb}_n)$ and $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$, we conclude that the sample conductance is lower bounded,
+\begin{equation*}
+\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
 \end{equation*}
@@
 	\begin{equation*}
-	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
+	\nu(\mc{R}_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
 	\end{equation*}
@@
 	\begin{equation*}
-	\|g(x) - g(y)\| \leq L \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
+	\|g(x) - g(y)\| \leq M \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
 	\end{equation*}
@@
 	\begin{equation*}
-	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) L} \min(\nu(\Omega_1), \nu(\Omega_2)).
+	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) M} \min(\nu(\Omega_1), \nu(\Omega_2)).
 	\end{equation*}
@@
 
-	It remains to verify that $x \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing.
+	It remains to verify that $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing.
 For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
@@
 	\label{lem:uniform_density_cluster_conductance}
-	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho \in (0,\infty)$ and $L \in [1,\infty)$.
+	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho \in (0,\infty)$ and $M \in [1,\infty)$.
 For any $0 < r \leq \sigma \cdot \sqrt{2\pi/(d + 2)}$, it holds that
@@
 	\label{eqn:uniform_density_cluster_conductance}
-	\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}.
+	\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho M}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho M \sqrt{d + 2}}.
 	\end{equation}
@@
 \paragraph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
-	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.
+	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho M)$.
 
@@
 		\end{equation*}
-		and likewise for $\vol_{\wt{\nu},r}(\mc{S})$. Therefore,
+		and likewise for $\vol_{\wt{\nu},r}(\mc{R})$. Therefore,
 		\begin{equation}
@@
 		\label{pf:uniform_density_cluster_conductance_2}
-		\nu(\mc{B}^{\delta}) \geq \frac{2 \cdot \mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \cdot \min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\}.
+		\nu(\mc{B}^{\delta}) \geq \frac{2 \cdot \mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho M} \cdot \min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\}.
 		\end{equation}
@@
 	\begin{equation*}
-	\Phi_{\wt{\nu},r}(\mc{S}) \geq \min\biggl\{(1 - a) \cdot \frac{r}{\rho L} \cdot \frac{\ell^2}{9} \cdot \sqrt{\frac{2\pi}{d + 2}}, \frac{a\ell}{6}\biggr\}
+	\Phi_{\wt{\nu},r}(\mc{S}) \geq \min\biggl\{(1 - a) \cdot \frac{r}{\rho M} \cdot \frac{\ell^2}{9} \cdot \sqrt{\frac{2\pi}{d + 2}}, \frac{a\ell}{6}\biggr\}
 	\end{equation*}
@@
 that $\alpha \leq 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$ and $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
-In order to verify the upper bound on $\alpha$, we will use Proposition~\ref{prop:conductance_lb_transportation_distance} to upper bound $\tau_{\infty}(\wt{G}_{n,r})$, which we may validly apply because
+In order to verify the upper bound on $\alpha$, we will use Proposition~\ref{prop:pointwise_mixing_time} to upper bound $\tau_{\infty}(\wt{G}_{n,r})$, which we may validly apply because
 \begin{equation*}
@@
 
-Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance}, along with inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance} and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$.
+Therefore by Proposition~\ref{prop:pointwise_mixing_time}, along with inequalities~\eqref{eqn:sample_to_population_local_spread} and~\eqref{eqn:sample_to_population_conductance} and the initialization conditions~\eqref{eqn:initialization} and \eqref{eqn:alpha_initialization}, we have that $\alpha \leq 1/45 \wedge 1/\bigl(2\tau_{\infty}(\wt{G}_{n,r})\bigr)$.
 On the other hand, by the upper bound on $\vol_{n,r}(\mc{C}[X])$ given in~\eqref{pf:volume_ssd_ub_1} and the initialization condition~\eqref{eqn:initialization}, we have that $U \leq 1/\bigl(5 \vol_{n,r}(\mc{C}[X])\bigr)$.
@@
 \frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} & \leq 60 \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\alpha_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)} \\
-& \leq \frac{780}{\ln(2)} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2} \cdot \ln^2\Bigl(\frac{8}{(1 - 3\delta) s_{\Pbb,r}(\mc{C})}\Bigr)
+& \leq \frac{1020}{\ln(2)} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2} \cdot \ln^2\Bigl(\frac{32}{(1 - 3\delta) s_{\Pbb,r}(\mc{C})}\Bigr)
 \end{align*}
@@
 \begin{equation*}
-C_{1,\delta} := \frac{898560}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)},~~\textrm{and}~~C_{2,\delta} := \frac{36}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
+C_{1,\delta} := \frac{1175040}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)},~~\textrm{and}~~C_{2,\delta} := \frac{144}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
 \end{equation*}
@@
 		Therefore the upper bound in condition~\eqref{eqn:normalized_cut_ppr_vol} is satisfied.
-		\item By~\eqref{eqn:ncut_lower_set}, the normalized cut of $\mc{L}$ satisfies the following lower bound,
+		\item By~\eqref{eqn:ncut_lower_set}, the normalized cut of $\mc{L}$ satisfies the following upper bound,
 		\begin{equation}
@@
 		\end{equation}
-		and by~\eqref{eqn:local_spread_ub} the local spread of $\mc{X}$ satisfies the following upper bound,
+		and by~\eqref{eqn:local_spread_ub} the local spread of $\mc{X}$ satisfies the following lower bound,
 		\begin{equation}
@@
 
-	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube
+	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube\footnote{Here we are assuming, without loss of generality, that $6\sigma/r \in \mathbb{N}$ and $2\rho/r \in \mathbb{N}$, and using the notation $[x] = \{1,\ldots,x\}$ for $x \in \mathbb{N}$.}
 	\begin{equation*}
@@
 	\begin{equation*}
-	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{k - \ell}_1 = 1}.
+	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
 	\end{equation*}
@@
 \paragraph{Proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.}
-We have already verified in the proof of Theorem~\ref{thm:volume_ssd_ub} that $\alpha \leq 1/(2\tau_{\infty}(\wt{G}_{n,r}))$, and we may therefore apply Lemma~\ref{lem:ppr_uniform_bound}, which gives an upper bound on $p_v(u)$ for all $u \in \mc{C}_{\lambda,\sigma}[X]_o$ and a lower bound on $p_v(u')$ for all $p_v(u')$ for all $u' \in \mc{C}_{\lambda,\sigma}'[X]_o$.
+We have already verified in the proof of Theorem~\ref{thm:volume_ssd_ub} that $\alpha \leq 1/(2\tau_{\infty}(\wt{G}_{n,r}))$, and we may therefore apply Lemma~\ref{lem:ppr_uniform_bound}, which gives a lower bound on $p_v(u)$ for all $u \in \mc{C}_{\lambda,\sigma}[X]_o$ and an upper bound on $p_v(u')$ for all $p_v(u')$ for all $u' \in \mc{C}_{\lambda,\sigma}'[X]_o$.
 These bounds are useful because $r \leq \sigma$, which implies that $\mc{C}_{\lambda}[X] \subseteq\mc{C}_{\lambda,\sigma}[X]_o$ and likewise that $C_{\lambda}'[X] \subseteq\mc{C}_{\lambda,\sigma}'[X]_o$.

### 2021-09-05 jmlr/revision2/ppr_clustering_neighborhood_graph.tex
Through checking + copy-editting Appendices A and B.

--- 2021-01-31 jmlr/revision/ppr_clustering_neighborhood_graph.tex
@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue,
-	citecolor=blue
-}
 \usepackage{url}            % simple URL typesetting
@@
 \usepackage{mathtools}
+\usepackage{hyperref}       % hyperlinks
+\hypersetup{
+	colorlinks,
+	citecolor=blue,
+	urlcolor=blue,
+	linkcolor=blue,
+	bookmarks=false
+}
 
@@
 \subsection{Population normalized cut, conductance, and local spread}
-Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
+Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which we will use to upper bound the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$ with high probability.
 Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e.
@@
 \end{equation*}
-where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ to be the expected degree of $x$ in $G_{n,r}$. 
+where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ be the expected degree of $x$ in $G_{n,r}$. 
 \begin{definition}[Population normalized cut]
@@
 It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
-Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
-For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
+Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities can be used to upper bound the volume of the symmetric set difference.
+For this reason, similar population-level functionals are used by \cite{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
 We will comment more on the relationship between these works and our own results in Section~\ref{subsec:related_work}.
@@
 The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
-We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under an Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $L$.
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $M$.
 We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
@@
 \end{equation*}
-while satisfying the following low-noise condition:
+and additionally satisfies the following low-noise condition:
 \begin{equation*}
-\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $\dist(x,\mc{C}_{\lambda,\sigma}) \leq r$.}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
 \end{equation*}
@@
 Equation~\eqref{eqn:density_cluster_volume_ssd_ub_informal} reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-The parameters $L$, $\rho$ and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
-Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$ and $\theta$ measure whether $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside the density cluster) or poorly conditioned (vice versa).
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is well-conditioned---i.e.
+The parameters $M$, $\rho$ and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
+Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$ and $\theta$ measure whether the density $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside the density cluster) or poorly conditioned (vice versa).
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---i.e.
 $L^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
@@
 results to the sparse (low average degree) regime. Relatedly,
-\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
+\citet{clauset08,balakrishnan2011,li2018} analyze the misclassification rate
 when the block model exhibits some hierarchical structure. The framework we
@@
 
-In general, the study of spectral algorithms on neighborhood graphs has been
+In general, the study of spectral algorithms on neighborhood graphs has
 focused on establishing asymptotic convergence of eigenvalues and eigenvectors
@@
 \citet{shi2009,schiebinger2015,garciatrillos19,hoffmann2019} address this question, showing that spectral algorithms will recover the latent labels in certain well-conditioned nonparametric mixture models.
-These works are probably the most similar to our own: the conditioning of these mixture models depend on population-level functionals resembling the population-level normalized cut and conductance introduced above, and the resulting bounds on the error of spectral clustering are comparable to those we establish in Theorem~\ref{thm:volume_ssd_ub}.
+These works are probably the most similar to our own: the conditioning of these mixture models depends on population-level functionals resembling the population normalized cut and conductance introduced above, and the resulting bounds on the error of spectral clustering are comparable to those we establish in Theorem~\ref{thm:volume_ssd_ub}.
 However, these results focus on global rather than local methods, and impose global rather than local conditions on $\Pbb$.
@@
 We then show that under certain conditions the sample normalized cut, conductance, and local spread are close to their population-level counterparts, with high probability for sufficient number of samples.
-As a result, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ purely in terms of these population functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+As a result, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ purely in terms of these population-level functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
 	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
@@
 
-In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$.
+In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on the volume of the symmetric set difference $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$.
 We build to this theorem slowly, giving new structural results in two distinct directions.
-First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$.
-Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues.
+First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s(G_{n,r}[\mc{C}[X]])$.
+Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues with high probability.
 
@@
 \end{equation}
-here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ that originates at node $v$ and runs for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ initialized at node $v$ and run for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
 \begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
@@
 	\label{eqn:zhu_condition}
-	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}
-	\end{equation}
-	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
+	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}.
+	\end{equation}
+	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
 	\begin{equation}
@@
 	\label{eqn:pointwise_mixing_time}
-	\tau_{\infty}(G) \leq \frac{13}{\ln(2)} \biggl(\frac{\ln\bigl(8/s(G)\bigr)}{\Psi(G)}\biggr)^2
+	\tau_{\infty}(G) \leq \frac{17}{\ln(2)} \biggl(\frac{\ln\bigl(32/s(G)\bigr)}{\Psi(G)}\biggr)^2
 	\end{equation}
@@
 While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
-In the case where $G = G_{n,r}\bigl[\mc{C}[X]\bigr]$ for a fixed radius $r$, the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp n$, and therefore $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1$.
+In particular, when $G = G_{n,r}\bigl[\mc{C}[X]\bigr]$ for a fixed radius $r > 0$, the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp n$, and therefore $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1$.
 We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
@@
 	\begin{equation*}
-	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}
+	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}.
 	\end{equation*}
+	% (AG 9/2/21): A reviewer has questioned the relevance of the "1" in the above inequalities. 
 	\item 
 	\label{asmp:domain} 
-	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set. If $d \geq 2$ then it has a Lipschitz boundary. 
+	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set.
+If $d \geq 2$ then it has a Lipschitz boundary $\partial \mc{C}$, meaning it is locally the graph of a Lipschitz function (see Definition 9.57 of~\cite{leoni2017}).
 \end{enumerate}
@@
 \label{eqn:alpha_initialization}
-\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}.
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{17} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{32}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}.
 \end{equation}
@@
 By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
-To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
+To ease presentation, we introduce a \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
 \begin{equation}
@@
 In summary, our goal is to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
-We have already derived upper bounds on the symmetric set difference of $\wh{C}$ and a generic cluster $\mc{C}$ that depend on some population-level functionals $\mc{C}$.
+We have already derived upper bounds on the symmetric set difference of $\wh{C}$ and a generic cluster $\mc{C}$ that depend on some population-level functionals of $\mc{C}$.
 What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
@@
 	\label{asmp:low_noise_density}
-	\emph{Low noise density:} There exist $\theta \in (0,\infty)$ and $\gamma \in
+	\emph{Low-noise density:} There exist $\theta \in (0,\infty)$ and $\gamma \in
 	[0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \mc{C}_{\lambda,\sigma}) \leq \sigma$,     
@@
 	\emph{Lipschitz embedding:}
-	There exists $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $L \in [1,\infty)$ such that
+	There exists a differentiable function $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $M \in [1,\infty)$ such that
 	\begin{enumerate}
@@
 		the Jacobian of $g$ evaluated at $x;$ and 
-		\item for some $L \geq 1$,   
-		$$
-		\|g(x) - g(y)\| \leq L \|x - y\| ~
+		\item for some $M \geq 1$,   
+		$$
+		\|g(x) - g(y)\| \leq M \|x - y\| ~
 		\text{for all $x,y \in \mathcal{K}$}. 
@@
 
-\paragraph{Normalized cut, conductance, and local spread of a density cluster.} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
+\paragraph{Normalized cut, conductance, and local spread of a density cluster.} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
 These bounds depend on the various geometric parameters just introduced.
@@
 	\label{lem:density_cluster_local_spread}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $L$. Then,
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $M$. Then,
 	\begin{equation}
 	\label{eqn:density_cluster_local_spread}
-	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{4} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{2r}{\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr)
+	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{4} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{2r}{\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr).
 	\end{equation}
@@
 	\label{eqn:density_cluster_normalized_cut}
-	\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \frac{16}{9} \cdot \frac{dr}{\sigma} \cdot \frac{\lambda\Bigl(\lambda_{\sigma} - \theta \frac{r^{\gamma}}{\gamma + 1}\Bigr)}{\lambda_{\sigma}^2}
+	\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \frac{16}{9} \cdot \frac{dr}{\sigma} \cdot \frac{\lambda\Bigl(\lambda_{\sigma} - \theta \frac{r^{\gamma}}{\gamma + 1}\Bigr)}{\lambda_{\sigma}^2}.
 	\end{equation}
@@
 	\label{prop:density_cluster_conductance}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$. Then,
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $M$. Then,
 	\begin{equation}
 	\label{eqn:density_cluster_conductance}
-	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
+	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho M}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho M \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}.
 	\end{equation}
@@
 The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g.
-\cite{lovasz1990} or \cite{dyer1991}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $L$
+\cite{lovasz1990} or \cite{dyer1991}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
 	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
-	\item There is some interdependence between $L$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
+	\item There is some interdependence between $M$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
 	non-essential. However, it is not possible to eliminate condition \ref{asmp:embedding} without incurring an additional factor of at least
@@
 	instance, when $\mc{C}_{\lambda,\sigma}$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
-In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $L$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
+In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $M$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
 \end{itemize}
@@
 	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
-Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $M$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:volume_ssd_ub}.
 Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
@@
 	\label{eqn:density_cluster_volume_ssd_ub}
-	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
+	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
 	\end{equation}
@@
 \biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
-\mc{C}^{(1)} = \mc{C}^{(0)} - \set{(\sigma,0)}, \quad
-\mc{C}^{(2)} = \mc{C}^{(0)} + \set{(\sigma,0)},
+\mc{C}^{(1)} = \mc{C}^{(0)} - (\sigma,0), \quad
+\mc{C}^{(2)} = \mc{C}^{(0)} + (\sigma,0),
 $$
@@
 	\centering
-	\includegraphics[width=0.495\textwidth]{../lower_bound_1}
-	\includegraphics[width=0.495\textwidth]{../lower_bound_2}
+	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_1}
+	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_2}
 	\caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
@@
 \begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{2}
 	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
 	\mc{C}^{(1)}$.  
-	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such
+	\item The density $f(x) \leq \frac{\epsilon}{\rho\sigma}$ for all $x \in \Reals^2$ such
 	that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
 	$$
-	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  = \left\{\frac{1 - \epsilon}{2} -
+	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  \geq \left\{\frac{1 - \epsilon}{2} -
 	\epsilon \right\} \frac{1}{\rho \sigma},
@@
 	which meets the decay requirement with exponent $\gamma=0$.
-	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\rho$.
+	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\sqrt{\rho^2 + \sigma^2}$.
 	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) =
@@
 \begin{equation*}
-\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 32 C_{1,\delta} \cdot \frac{\rho^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
+\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 64 C_{1,\delta} \cdot \frac{\rho^2 + \sigma^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
 \end{equation*}
@@
 	\begin{equation*}
-	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{256 C_{1,\delta}} \left(\frac{\sigma}{\rho \log(\rho/\sigma \sqrt{C_{2,\delta}})}\right)^2,
+	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{512 C_{1,\delta}} \frac{\sigma^2}{(\rho^2 + \sigma^2) \log^2(\rho/\sigma \sqrt{C_{2,\delta}})},
 	\end{equation*}
@@
 	\end{equation*}
-	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{8}
+	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{20}
 		\vol_{n,r}(\mc{C}^{(1)}[X])$}. 
@@
 Of course, it is not hard to show that in the example under consideration, classical
-plug-in density cluster estimators can consistently recover the
-$\sigma$-expansion $\mc{C}_{\lambda,\sigma}$ of a density cluster $\mc{C}_{\lambda}$, even if $\epsilon$ is
+plug-in density cluster estimators can consistently recover $\mc{C}^{(1)}$, even if $\epsilon$ is
 large compared to $\sigma/\rho$. That PPR has trouble recovering density
@@
 the last column shows a cut of the density cluster tree estimator of
-\citet{chaudhuri2010}.  We can see the degrading ability of PPR to recover
-density clusters as the two moons become less well-separated. Of particular
-interest is the fact that PPR fails to recover one of the moons even when
-normalized cut still succeeds in doing so. Additionally, we note that the
+\citet{chaudhuri2010}.
+Each row corresponds to a different separation between the two moons.
+In the second row, we see that as the two moons become less well-separated, PPR becomes unable to recover the density clusters, but
+normalized cut still succeeds in doing so. In the third row, we see that the
 Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
@@
 	\centering
-	\includegraphics[width=0.24\textwidth,scale = .5]{../row1_true_density_cluster}
-	\includegraphics[width=0.24\textwidth]{../row1_ppr_cluster}
-	\includegraphics[width=0.24\textwidth]{../row1_conductance_cluster}
-	\includegraphics[width=0.24\textwidth]{../row1_density_cluster}
-	\includegraphics[width=0.24\textwidth]{../row2_true_density_cluster}
-	\includegraphics[width=0.24\textwidth]{../row2_ppr_cluster}
-	\includegraphics[width=0.24\textwidth]{../row2_conductance_cluster}
-	\includegraphics[width=0.24\textwidth]{../row2_density_cluster}
-	\includegraphics[width=0.24\textwidth]{../row3_true_density_cluster}
-	\includegraphics[width=0.24\textwidth]{../row3_ppr_cluster}
-	\includegraphics[width=0.24\textwidth]{../row3_conductance_cluster}
-	\includegraphics[width=0.24\textwidth]{../row3_density_cluster}
+	\includegraphics[width=0.24\textwidth,scale = .5]{plots/experiment_2/row1_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_density_cluster}
 	\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
@@
 \clearpage
+
 \appendix
-
 \input{appendix.tex}

### 2021-09-10 jmlr/revision2/appendix.tex
Completed edit of paper and appendices. Added a brief response letter.

@@
 In this appendix, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
-In these proofs, we make use of some estimates on the volume of spherical caps (in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
-Finally, in Section~\ref{subsec:density_cluster_hard_case}, for the hard case distribution $\Pbb$ defined in~\eqref{eqn:lb_density} and $\mc{L}$ defined in~\eqref{eqn:lower_set}, establish bounds on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{L})$ and local spread $s_{\Pbb,r}(\mc{X})$; these will be useful in the proof of Theorem~\ref{thm:ppr_lb}.
+In these proofs, we make use of some estimates on the volume of spherical caps (given in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (Section~\ref{subsec:reverse_isoperimetric_inequalities}).
+Finally, in Section~\ref{subsec:density_cluster_hard_case}, for the hard case distribution $\Pbb$ defined in~\eqref{eqn:lb_density} and $\mc{L}$ defined in~\eqref{eqn:lower_set}, we establish bounds on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{L})$ and local spread $s_{\Pbb,r}(\mc{X})$; these will be useful in the proof of Theorem~\ref{thm:ppr_lb}.
 Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
@@
 Results of this type are well-known, but since we could not find exactly the statements we desire, for completeness we also supply proofs.
-We use the notation $B(x,r)$ for a ball of radius $r$ centered at $x \in \Rd$, and $\mathrm{cap}_{r}(h)$ for a spherical cap of height $r$ and radius $r$.
+We use the notation $B(x,r)$ for a ball of radius $r$ centered at $x \in \Rd$, and $\mathrm{cap}_{r}(h)$ for a spherical cap of height $h$ and radius $r$.
 Recall that the Lebesgue measure of a spherical cap is
 \begin{equation*}
-\nu\bigl(\mathrm{cap}_r(h)\bigr) = \frac{1}{2} \nu_d r^d I_{1 - a}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
+\nu\bigl(\mathrm{cap}_r(h)\bigr) = \frac{1}{2} \nu_d r^d I_{1 - a}\left(\frac{d + 1}{2}; \frac{1}{2}\right),
 \end{equation*}
@@
 \begin{equation*}
-I_{1 - a}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - a} u^{z - 1} (1 - u)^{w - 1} du.
+I_{1 - a}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - a} u^{z - 1} (1 - u)^{w - 1} du,
 \end{equation*}
@@
 	\begin{equation*}
-	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d\bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
+	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d\biggl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\biggr).
 	\end{equation*}
@@
 \paragraph{Proof of Lemma~\ref{lem:overlap_balls}.}
-	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
+	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each of height $h = r - \frac{\|x - y\|}{2}$. 
 	As a result, by Lemma~\ref{lem:volume_of_spherical_cap} we have
@@
 \label{subsec:isoperimetric_inequalities}
-\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
+\citet{dyer1991b} establish the following isoperimetric inequality for convex sets.
 \begin{lemma}[Isoperimetry of a convex set.]
@@
 	It remains to verify that $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing.
-For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
+For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - x_j$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
 Thus $(s/t)x \in B(0,s)$, and
@@
 	\begin{equation*}
-	\Bigl(\mc{A}_j(t) - \{x_j\}\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- \{x_j\}\Bigr),
+	\Bigl(\mc{A}_j(t) - x_j\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- x_j\Bigr),
 	\end{equation*}
@@
 	Fix $k \in \mathbb{N}$.
-To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
+To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma} > 0$ for all $x \in \mc{C}$.}
 	\begin{equation*}
@@
 \begin{equation*}
-s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \frac{\bigl(d_{\min}(\wt{\Pbb})\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)}
+s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) = \frac{\bigl(d_{\min}(\wt{\Pbb})\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C}_{\lambda},\sigma)},
 \end{equation*}
@@
 \end{align*}
-the final inequality follows from~\ref{asmp:embedding}, which implies that $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
+the final inequality follows from~\ref{asmp:embedding}, which along with the isodiametric inequality for convex sets~\citep{gruber2007} implies $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
 The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
@@
 \end{align*}
-On the other hand, using the lower bound $f(x) \geq \lambda_{\sigma} $ for all $x \in \mc{C}_{\lambda,\sigma}$, we lower bound $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the Lebesgue measure of $\mc{C}_{\lambda,\sigma}$:
+On the other hand, using the lower bound $f(x) \geq \lambda_{\sigma} $ for all $x \in \mc{C}_{\lambda,\sigma}$, we lower bound $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ in terms of the Lebesgue measure of $\mc{C}_{\lambda,\sigma}$:
 \begin{align*}
@@
 The following Lemma lower bounds the population-level uniform conductance $\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma})$.
+We note that for convex sets, results of this type are well known (see e.g.~\cite{vempala2005} and references therein).
 \begin{lemma}
@@
 	define $\mc{R}^{\delta}$ likewise, and let $\mc{B}^{\delta} = \mc{C}_{\lambda,\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$ consist of the remaining boundary points.
-	As is standard (see for example~\cite{dyer1991,lovasz1990}), the proof of Lemma~\ref{lem:uniform_density_cluster_conductance} uses several inequalities to lower bound the normalized cut $\Phi_{\wt{\nu},r}(\mc{S})$.
+	As is standard (see for example~\cite{dyer1991b,lovasz1990}), the proof of Lemma~\ref{lem:uniform_density_cluster_conductance} uses several inequalities to lower bound the normalized cut $\Phi_{\wt{\nu},r}(\mc{S})$.
 	\begin{itemize}
@@
 \subsection{Proof of Theorem~\ref{thm:density_cluster_volume_ssd_ub}}
-From Theorem~\ref{thm:volume_ssd_ub}, we have with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
+From Theorem~\ref{thm:volume_ssd_ub}, we have that with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
 \begin{align*}
@@
 \begin{align*}
-C_{3,\delta} & := \frac{72(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}
+C_{3,\delta} & := \frac{288(1 + \delta)}{(1 - \delta)} \sqrt{8/3 + 8 \delta}
 ,&&C_{4,\delta} := \frac{72}{(1 - 3\delta)\pi}, \\
 B_{1,\delta} & := 768 \cdot (1 + 3\delta) \cdot \ln\Bigl(C_{4,\delta} \frac{\rho\sigma}{r^2 \epsilon^2} \Bigr),&&B_{2,\delta} := \frac{(1 + \delta)^2}{(1 - \delta)^2} \cdot \frac{\rho \sigma}{r^2 \epsilon^2} \\
-B_4 & := 1 + \frac{12\sigma\rho}{r^2} + \frac{2\rho}{r},&&b_4 :=  b_8 \wedge \cut_{\Pbb,r}(\mc{L}) \wedge d_{\min}(\Pbb)/14 \wedge \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}), \\
+B_4 & := 1 + \frac{48\sigma\rho}{r^2} + \frac{4\rho}{r},&&b_4 :=  b_8 \wedge \cut_{\Pbb,r}(\mc{L}) \wedge d_{\min}(\Pbb)/14 \wedge \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}), \\
 b_8 &:= \vol_{\Pbb,r}(\mc{X})/4 \wedge \frac{\epsilon r^2}{4\rho\sigma} \wedge \frac{\pi r^3}{8\sigma \rho^2}.
@@
 	\label{eqn:normalized_cut_lb}
-	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},~~\textrm{for all $Z \subseteq X$}.
+	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},~~\textrm{for all $Z \subseteq X$}.
 	\end{equation}
@@
 	\label{pf:ppr_lb_3}
-	\frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+	\frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
 	\end{equation}
@@
 
-	We turn to lower bounding $\cut_{n,r}(Z)$, which is considerably more involved.
-We will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $Z$ to the boundary of the binned set $\overline{Z}$, and then lower bound the size of the boundary of $\overline{Z}$.
-
-	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube\footnote{Here we are assuming, without loss of generality, that $6\sigma/r \in \mathbb{N}$ and $2\rho/r \in \mathbb{N}$, and using the notation $[x] = \{1,\ldots,x\}$ for $x \in \mathbb{N}$.}
-	\begin{equation*}
-	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
-	\end{equation*}
-	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
-For a set $Z \subset X$ we define the binned set $\overline{Z} \subset \overline{Q}$ as follows
-	\begin{equation*}
-	\overline{Z} := \set{Q \in \overline{Q}: \Pbb_n(Z \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
-	\end{equation*}
-	and we let 
-	\begin{equation*}
-	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
-	\end{equation*}
-	be the boundary set of $\overline{Z}$ in $\overline{Q}$.
-Intuitively, every point $x_i \in Z$ in the boundary set of $\overline{Z}$ will have many edges to $X\setminus Z$.
+	We turn to lower bounding $\cut_{n,r}(Z)$. Establishing this lower bound is considerably more involved, and we start by giving an outline of our approach to build intuition.
+	\begin{itemize}
+		\item \emph{Discretization}.
+Intuitively, we will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into a collection of rectangular bins $\wb{Q}$.
+We will consider a subset of bins $\partial \wb{Z} \subseteq \wb{Q}$, which we call the discretized boundary of $Z$, and which consists of those bins $Q \in \wb{Q}$ containing many points $x_i \in Z$ adjacent, in the graph $G_{n,r}$, to many $x_j \in X \setminus Z$.
+This discretization allows us to relate $\cut_{n,r}(Z)$ to the number of bins in the discretized boundary $\partial \wb{Z}$, as in~\eqref{eqn:normalized_cut_lb_pf1}.
+		\item \emph{Slicing}.
+In order to lower bound the number of bins in the discretized boundary $|\partial \wb{Z}|$, we consider a second partition of $\mc{X}$ into horizontal slices $R$.
+We argue that for each slice $R$, one of two things must be true: either $R$ contains a bin belonging to the discretized boundary of $Z$, $Q \in \partial \wb{Z}$, or $(Z \vartriangle \mc{C}^{(1)}[X]) \cap R$ has a ``substantial'' volume,
+		\begin{equation*}
+		\vol_{n,r}\Bigl((Z \vartriangle \mc{C}^{(1)}[X]) \cap R\Bigr) \geq R_{\min},
+		\end{equation*}
+		where $R_{\min}$ is a random quantity defined in~\eqref{eqn:normalized_cut_lb_pf2}.
+		Summing over all slices $R$ then gives a lower bound on $|\partial \wb{Z}|$, as in~\eqref{eqn:normalized_cut_lb_pf2}. 
+		\item \emph{Probabilistic Guarantees}.
+The lower bound~\eqref{eqn:normalized_cut_lb_pf2} depends on two random quantities: the minimum number of points in any bin (denoted by $Q_{\min}$), and $R_{\min}$, which was discussed in the previous bullet.
+We give suitable lower bounds on each quantity, which hold with high probability, and which suffice to complete the proof of Lemma~\ref{lem:normalized_cut_lb}.
+	\end{itemize}
+
+	Now, we fill in the details, working step-by-step.
+
+	\emph{\underline{Step 1: Discretization}.}
+	We begin by discretizing $\mc{X}$ into a collection of bins.
+To that end, to each $k_1 \in \bigl[\frac{12\sigma}{r}\bigr], k_2 \in \bigl[\frac{4\rho}{r}\bigr]$ associate the bin\footnote{Here we are assuming, without loss of generality, that $12\sigma/r \in \mathbb{N}$ and $4\rho/r \in \mathbb{N}$, and using the notation $[x] = \{1,\ldots,x\}$ for $x \in \mathbb{N}$.}
+	\begin{equation*}
+	Q_{(k_1,k_2)} := \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{4}r, -\frac{3\sigma}{2} + \frac{k_1}{4}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{4}r, -\frac{\rho}{2} + \frac{k_2}{4}r\biggr];
+	\end{equation*}
+	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{12\sigma}{r}\right], k_2 \in \bigl[\frac{4\rho}{r}\bigr]}$ be the collection of such bins.
+Next, we define the binned set $\overline{Z} \subset \overline{Q}$ to contain all bins $Q \in \wb{Q}$ for which $Z \cap Q$ is larger than $X\setminus Z \cap Q$; in mathematical notation,
+	\begin{equation*}
+	\overline{Z} := \set{Q \in \overline{Q}: \Pbb_n(Z \cap Q) \geq \frac{1}{2}\Pbb_n(Q)}.
+	\end{equation*}
+	Then the discretized boundary $\partial \wb{Z}$ is 
+	\begin{equation*}
+	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{12\sigma}{r}\Bigr] \times \Bigl[\frac{4\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
+	\end{equation*}
+	Intuitively, every point $x_i \in Z$ which belongs to a cube in the boundary set $\partial\overline{Z}$ will have many edges to $X\setminus Z$.
 Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \Pbb_n(Q)$, we have
@@
 	\label{eqn:normalized_cut_lb_pf1}
-	\cut_{n,r}(Z) \geq \cut_{n,r}(Z \cap \set{x_i \in \overline{Z}}) \geq \frac{1}{4} \abs{\partial \overline{Z}} Q_{\min}^2,
-	\end{equation}
-	where the last inequality follows since for every cube $Q_k \in \partial\overline{Z}$, there exists a cube $Q_\ell \not\in \overline{Z}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
-
-	Now we move on lower bounding the size of the boundary $\abs{\partial\wb{Z}}$.
+	\cut_{n,r}(Z) \geq \cut_{n,r}(Z \cap \set{x_i \in \overline{Z}}) \geq \frac{1}{4} \abs{\partial \overline{Z}} Q_{\min}^2.
+	\end{equation}
+	To establish the last inequality, we reason as follows: first, for every cube $Q_{(k_1,k_2)} \in \partial\overline{Z}$, there exists a cube $Q_{(\ell_1,\ell_2)} \not\in \overline{Z}$ such that $\norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 \leq 1$; second, since each cube has side length $r/4$, this implies that for every $x_i \in Q_{(k_1,k_2)}$ and $x_j \in Q_{(\ell_1,\ell_2)}$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
+
+	\emph{\underline{Step 2: Slicing}.}
+	Now we move on lower bounding the size of the discretized boundary $\abs{\partial\wb{Z}}$.
 To do so, we divide $\mathcal{X}$ into slices horizontally.
-Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
-For each $k$, either
+Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{4}r, -\frac{\rho}{2} + \frac{k}{4}r\bigr]}$ be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{12\sigma}{r}]}$ be the binned version of $R_k$.
+For every $k$, we are in one of three cases:
 	\begin{enumerate}
@@
 		\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
+		\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{(1)}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
 		\end{equation*}
@@
 	\end{enumerate}
-	Let $N(R)$ be the number of slices for which $\wb{R}_k \cap \partial \wb{Z} \neq \emptyset$. By the cases elucidated above, letting
-	\begin{equation*} 
-	R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}
-	\end{equation*} 
-	we obtain the following lower bound on the volume of the symmetric set difference,
+	In words, these cases describe, for each slice $R$, the situation in which the set $Z$ has a ``substantial'' boundary (Case 3), or the situation in which $Z$ does not have a substantial boundary, and instead has a substantial difference with $\mc{C}^{(1)}$ (Cases 1 and 2).
+
+	Now, let $N(R)$ be the number of slices which contain a boundary cell,
+	\begin{equation*}
+	N(R) := \#\biggl\{k \in \biggl[\frac{2\rho}{r}\biggr]: \wb{R}_k \cap \partial \wb{Z} \neq \emptyset\biggr\}.
+	\end{equation*}
+	and let $R_{\min}$ be the minimum volume of the intersection of any slice $R_k$ with the density clusters $\mc{C}^{(1)}, \mc{C}^{(2)}$; formally,
+	\begin{equation}
+	\label{eqn:normalized_cut_lb_pf1.5}
+	R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}.
+	\end{equation} 
+	Summing over all slices $R_k$, we have from our previous analysis that,
+	\begin{equation*}
+	\vol_{n,r}\biggl(Z \vartriangle \mc{C}^{(1)}[X]\biggr) = \sum_{k \in [2\rho/r]} \vol_{n,r}\biggl( (Z \vartriangle \mc{C}^{(1)}[X]) \cap R_k\biggr) \geq R_{\min}  \left[\frac{2\rho}{r} - \frac{N(R)}{2}\right].
+	\end{equation*}
+	Rearranging this expression and noting that $\abs{\partial\wb{Z}} \geq N(R)$,  we obtain the following lower bound on the cardinality of the discretized boundary,
 	\begin{equation}
 	\label{eqn:normalized_cut_lb_pf2}
-	\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right] \Longleftrightarrow N(R) \geq 2\Bigl(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\Bigr)
-	\end{equation}
-	Finally note that $\abs{\partial\wb{Z}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
+	\abs{\partial\wb{Z}} \geq N(R) \geq 2\Bigl(\frac{2\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\Bigr).
+	\end{equation}
+	Combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
 	\begin{align}
 	\cut_{n,r}(Z) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
-	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
+	& \geq \left(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{2R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
 	\end{align}
@@
 
+	\emph{\underline{Step 3: Probabilistic guarantees.}}
 	It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
@@
 	\label{eqn:normalized_cut_lb_pf4.5}
-	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
+	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{4 \rho \sigma},
 	\end{equation}
@@
 	\label{eqn:normalized_cut_lb_pf5}
-	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2}~~\textrm{for all $k$.} 
+	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{4 \sigma \rho^2}~~\textrm{for all $k$.} 
 	\end{equation}
@@
 	Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
-Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
+Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{48 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{4\rho}{r}$.
 Along with \eqref{eqn:normalized_cut_lb_pf4.5} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
 	\begin{equation*}
-	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq (1 - \delta)\frac{\pi r^3}{2\sigma \rho^2 },
-	\end{equation*}
-	with probability at least $1 - \frac{12 \sigma \rho}{r^2}\exp\set{-\frac{n\delta^2\epsilon r^2 n}{4 \rho \sigma}} - \frac{2\rho}{r}\exp\set{-\frac{n\delta^2\pi r^3}{8\sigma\rho^2}}$.
+	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{4 \rho \sigma}n ~~\textrm{and}~~ R_{\min} \geq (1 - \delta)\frac{\pi r^3}{4\sigma \rho^2 }n(n - 1),
+	\end{equation*}
+	with probability at least $1 - \frac{48 \sigma \rho}{r^2}\exp\set{-\frac{n\delta^2\epsilon r^2}{4 \rho \sigma}} - \frac{4\rho}{r}\exp\set{-\frac{n(n - 1)\delta^2\pi r^3}{8\sigma\rho^2}}$.
 Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
 	\begin{equation*}	
-	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
+	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
 	\end{equation*}
@@
 Then, any $(L,U)$ satisfying~\eqref{eqn:initialization} and any sweep cut
-$S_{\beta}$ for $\beta \in (L,U)$ would fulfill both conditions laid out in
+$S_{\beta}$ for $\beta \in (L,U)$ would result in a cluster estimate $\wh{C}$ fulfilling both conditions laid out in
 \eqref{eqn:density_cluster_consistency}. In Theorem 

### 2021-09-10 jmlr/revision2/ppr_clustering_neighborhood_graph.tex
Completed edit of paper and appendices. Added a brief response letter.

@@
 	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
+	\addr Department of Statistics and Data Science; \\
+	Machine Learning Department\\
 	Carnegie Mellon University\\
@@
 	\label{eqn:density_cluster_volume_ssd_ub_informal}
-	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
+	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
 	\end{equation}
@@
 Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---i.e.
-$L^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
+$M^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
 $\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
@@
 	\label{asmp:bounded_density} 
-	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ with respect to Lebesgue measure. There exist $0 < f_{\min} \leq 1 \leq f_{\max} < \infty$ for which
+	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ with respect to Lebesgue measure. There exist $0 < f_{\min} \leq f_{\max} < \infty$ for which
 	\begin{equation*}
@@
 	\end{equation*}
-	% (AG 9/2/21): A reviewer has questioned the relevance of the "1" in the above inequalities. 
+	For convenience, we will assume $f_{\min} \leq 1$ and $f_{\max} \geq 1$.
 	\item 
@@
 	\label{prop:sample_to_population_1}
-	Fix $\delta \in (0,1/3)$. Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
+	Fix $\delta \in (0,1/3)$. Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
 	\begin{itemize}
@@
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
-Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\mathbb{P}_n$ and $\mathbb{P}$.
-For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
+Our proof relies on the recent results of \citet{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\mathbb{P}_n$ and $\mathbb{P}$.
+For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citet{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
 
@@
 
-	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
+	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$ the 
 	application of \eqref{eqn:appr_error} within the proof of Theorem
@@
 The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g.
-\cite{lovasz1990} or \cite{dyer1991}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
+\cite{lovasz1990} or \cite{dyer1991b}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
 	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
@@
 These methods are thus very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
-	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population-level normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
+	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
 It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
@@
 If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}. This implies that 
-there exists a set $\mc{C}^{(1)}[X] \subseteq \mc{C}^{(1)}$ with
-\smash{$\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X])$} such
-that for any seed node $v \in \mc{C}^{(1)}[X]$, and for large enough $n$, the
+there exists a set $\mc{C}^{(1)}[X]^g \subseteq \mc{C}^{(1)}[X]$ with
+\smash{$\vol_{n,r}(\mc{C}^{(1)}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X])$} such
+that for any seed node $v \in \mc{C}^{(1)}[X]^g$, and for large enough $n$, the
 PPR estimated cluster $\wh{C}$ satisfies with high probability
@@
 The one exception to this is the dependence of local spread on the width $\sigma$; this theoretical deficiency stems from a loose bound on the volume of sets with large aspect ratio (meaning $\rho/\sigma$ is much greater than $1$), but in any case the local spread contributes only $\log$ factors to the ultimate bound on cluster recovery.
-On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
+On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$, which as a result is loose by several orders of magnitude.
 
@@
 a prototypical success story for spectral clustering algorithms.
-We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
+We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be seen as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
 The first
@@
 In this work, we have analyzed the behavior of PPR in the classical setup of nonparametric statistics.
-We have shown how PPR depends on the distribution $\Pbb$ through the population-level normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
+We have shown how PPR depends on the distribution $\Pbb$ through the population normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
 In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if both the density cluster and density are well-conditioned.
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 

### 2021-09-10 arxiv/appendix.tex

--- 2021-09-01 jmlr/revision/appendix.tex
@@
 \begin{equation*}
-\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
+\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
 \end{equation*}

### 2021-11-14 jmlr/revision2/appendix.tex
Copyedits

@@
 
-\subsubsection{Proofs of Lemmas}
+\subsubsection{Proofs of lemmas}
 In what follows, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$.
@@
 
-\subsection{Balls, Spherical Caps, and Associated Estimates}
+\subsection{Balls, spherical caps, and associated estimates}
 \label{subsec:spherical_caps}
@@
 	\end{equation*}
-\section{Proof of Major Theorems}
+
+\section{Proof of major theorems}
 \label{apdx:pf_major_theorems}
@@
 
-\section{Additional results: aPPR and Consistency of PPR}
+\section{Additional results: aPPR and consistency of PPR}
 \label{apdx:appr_misclassification_error}
@@
 
-\section{Experimental Details}
+\section{Experimental details}
 \label{apdx:experimental_details}

### 2021-11-14 jmlr/revision2/ppr_clustering_neighborhood_graph.tex
Copyedits

@@
 	\addr Department of Statistics and Data Science\\
+	Machine Learning Department\\
 	Carnegie Mellon University\\
@@
 	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science; \\
+	\addr Department of Statistics and Data Science\\
 	Machine Learning Department\\
@@
 \begin{abstract}
-	We analyze the Personalized PageRank (PPR) algorithm, a local spectral method
-	for clustering, which extracts clusters using locally-biased random walks around
-	a given seed node.  In contrast to previous work, we adopt a classical
-	statistical learning setup, where we obtain samples from an unknown nonparametric distribution, and aim to identify sufficiently salient clusters.
+	We study the Personalized PageRank (PPR) algorithm, a local spectral method for clustering, which extracts clusters using locally-biased random walks around a given seed node.
+In contrast to previous work, we adopt a classical statistical learning setup, where we obtain samples from an unknown nonparametric distribution, and aim to identify sufficiently salient clusters.
 We introduce a trio of population-level functionals---the \emph{normalized cut}, \emph{conductance}, and \emph{local spread}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large conductance and local spread.
 We apply our general theory to establish that PPR identifies connected regions of high density (density clusters) that satisfy a set of natural geometric conditions.
-We also show a converse result, that PPR can fail to recover
-	geometrically poorly-conditioned density clusters, even asymptotically. Finally,
-	we provide empirical support for our theory.
+We also show a converse result, that PPR can fail to recover geometrically poorly-conditioned density clusters, even asymptotically.
+Finally, we provide empirical support for our theory.
 \end{abstract}
@@
 \section{Introduction}
-In this paper, we consider the problem of clustering: splitting a given data set
-into groups that satisfy some notion of within-group similarity and
-between-group difference.  Our particular focus is on spectral clustering
-methods, a family of powerful nonparametric clustering algorithms. Roughly
-speaking, a spectral algorithm first constructs a geometric graph $G$, where
-vertices correspond to samples, and edges correspond to proximities between
-samples. The algorithm then estimates a feature embedding based on a (suitable) Laplacian matrix of $G$, and applies a simple clustering technique
-(like $k$-means clustering) in the embedded feature space.
-
-When applied to geometric graphs built from a large number of samples, global
-spectral clustering methods can be computationally cumbersome and insensitive to
-the local geometry of the underlying distribution
-\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
-\emph{local} spectral clustering algorithms, which leverage locally-biased
-spectra computed using random walks around some user-specified seed node.  A
-popular local clustering algorithm is the Personalized PageRank (PPR) algorithm,
-first introduced by \citet{haveliwala2003}, and then further developed by
-several others
-\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
-
-Local spectral clustering techniques have been practically very successful
-\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
-many authors to develop supporting theory
-\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
-guarantees on traditional graph-theoretic notions of cluster quality (such as normalized cut and conductance).
+In this paper, we consider the problem of clustering: splitting a given data set into groups that satisfy some notion of within-group similarity and between-group difference.
+Our particular focus is on spectral clustering methods, a family of powerful nonparametric clustering algorithms.
+Roughly speaking, a spectral algorithm first constructs a geometric graph $G$, where vertices correspond to samples, and edges correspond to proximities between samples.
+The algorithm then estimates a feature embedding based on a (suitable) Laplacian matrix of $G$, and applies a simple clustering technique (like $k$-means clustering) in the embedded feature space.
+
+When applied to geometric graphs built from a large number of samples, global spectral clustering methods can be computationally cumbersome and insensitive to the local geometry of the underlying distribution \citep{leskovec2010,mahoney2012}.
+This has led to increased interest in \emph{local} spectral clustering algorithms, which leverage locally-biased spectra computed using random walks around some user-specified seed node.
+A popular local clustering algorithm is the Personalized PageRank (PPR) algorithm, first introduced by \citet{haveliwala2003}, and then further developed by several others \citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
+
+Local spectral clustering techniques have been practically very successful \citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led many authors to develop supporting theory \citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case guarantees on traditional graph-theoretic notions of cluster quality (such as normalized cut and conductance).
 In contrast, in this paper we adopt a classical statistical viewpoint, and examine what the output of local clustering on a data set reveals about the underlying density $f$ of the samples.
@@
 \label{subsec:ppr_clustering}
-We start by reviewing the PPR clustering algorithm. Let $G = (V,E)$ be an undirected, unweighted, and connected graph. We denote by $A \in \Reals^{n \times n}$ the adjacency
-matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
-also denote by $D$ the diagonal degree matrix, with entries $D_{uu} :=
-\sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
+We start by reviewing the PPR clustering algorithm.
+Let $G = (V,E)$ be an undirected, unweighted, and connected graph.
+We denote by $A \in \Reals^{n \times n}$ the adjacency matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.
+We also denote by $D$ the diagonal degree matrix, with entries $D_{uu} := \sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
 The PPR vector $p_v = p(v,\alpha;G)$ is defined with respect to a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
@@
 \end{equation}
-where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over
-$G$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
-position $v$ and 0 elsewhere).
+where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over $G$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in position $v$ and 0 elsewhere).
 
@@
 To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p_v^{(\varepsilon)}$}.
-We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mathcal{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
+We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mc{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
 \begin{equation}
 \label{eqn:appr_error}
-\textrm{for all $u \in V$}, \quad p_v(u) - \varepsilon D_{uu}\leq
-p_v^{(\varepsilon)}(u) \leq p_v(u).  
-\end{equation}
-
-Once $p_v$ or $p_v^{(\varepsilon)}$ is computed, the cluster estimate $\wh{C}$ is chosen by taking a particular sweep cut.
+p_v(u) - \varepsilon D_{uu}\leq p_v^{(\varepsilon)}(u) \leq p_v(u), 
+\quad \text{for all $u \in V$}.
+\end{equation}
+
+Once $p_v$ or \smash{$p_v^{(\varepsilon)}$} is computed, the cluster estimate \smash{$\wh{C}$} is chosen by taking a particular sweep cut.
 For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is
@@
 \end{equation}
-To determine $\wh{C}$, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate
-\smash{$\wh{C} = S_{\beta^*,v}$} with minimum normalized cut. For a set $C \subseteq V$ with complement $C^c = V \!\setminus\! C$, the \emph{cut} and \emph{volume} are respectively,
+To define \smash{$\wh{C}$}, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate \smash{$\wh{C} = S_{\beta^*,v}$} with minimum normalized cut.
+For a set $C \subseteq V$ with complement $C^c = V \!\setminus\!
+C$, the \emph{cut} and \emph{volume} are respectively,
 \begin{equation}
@@
 \subsection{Worst-case guarantees for PPR clustering}
-As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
+As mentioned, most analyses of local clustering have focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
 For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut $\Phi(\wh{C};G)$ is upper bounded by (a constant times)  $\sqrt{\Phi(C;G)}$.
@@
 and show that if $\Phi(C;G)$ is much smaller than $\Psi(G[C])^2$---where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$--- then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
-Our own analysis builds on that of~\cite{zhu2013}, and we give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
-For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random neighborhood graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
+Our own analysis builds on that of~\cite{zhu2013}, and we present a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
+For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\Pbb$, the graph $G$ is a random neighborhood graph formed from the samples, and the candidate cluster is a set $\mc{C} \subseteq \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
 
@@
 We now formally describe the statistical setting in which we operate, as well as the method we will study: PPR on a neighborhood graph.
-Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution
-$\Pbb$ on $\Rd$. We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ . For a radius $r > 0$, we define
-$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an
-unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in
-E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
-Euclidean norm.
-Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate $\wh{C} \subseteq X$.
-The precise PPR algorithm we analyze is summarized in Algorithm~\ref{alg:ppr}.
+Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$.
+We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ .
+For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the Euclidean norm.
+Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate \smash{$\wh{C} \subseteq X$}.
+The precise algorithm is summarized in Algorithm~\ref{alg:ppr}.
 
@@
 		\eqref{eqn:ppr_vector}.  
-		\STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
-		\eqref{eqn:sweep_cuts}.\footnotemark
-		\STATE Return the cluster \smash{$\wh{C} = S_{\beta^*}$}, where  
+		\STATE Compute sweep cuts $S_{\beta}$ as in \eqref{eqn:sweep_cuts}, for each $\beta \in (L,U)$.\footnotemark 
+		\STATE Return \smash{$\wh{C} = S_{\beta^*}$}, where  
 		$$
@@
 We need a metric to assess the accuracy with which $\wh{C}$ estimates the candidate cluster $\mc{C}$.
-One commonly used metric is the misclassification error, i.e.
-the size of the symmetric set difference
-between $\wh{C}$ and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}. We
-will consider a related metric, the volume of the symmetric set difference,
-which weights misclassified points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
+One commonly used metric is the misclassification error, i.e., the size of the symmetric set difference between \smash{$\wh{C}$} and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}.
+We will consider a related metric, the volume of the symmetric set difference, which weights misclassified points according to their degree in $G_{n,r}$.
+To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$.
+
 \begin{definition}
 	\label{def:volume_symmetric_set_difference}
-	For an estimator \smash{$\wh{C} \subseteq X$} and a set 
-	$\mathcal{C} \subseteq \Rd$, their symmetric set difference is 
-	\begin{equation*}
-	\wh{C} \vartriangle \mathcal{C}[X] :=
-	\bigl(\wh{C} \setminus \mathcal{C}[X]\bigr) \cup
-	\bigl(\mathcal{C}[X] \setminus \wh{C}\bigr).
+	For an estimator \smash{$\wh{C} \subseteq X$} and a set $\mc{C} \subseteq \Rd$, their symmetric set difference is  
+	\begin{equation*}
+	\wh{C} \vartriangle \mc{C}[X] :=
+	\bigl(\wh{C} \setminus \mc{C}[X]\bigr) \cup
+	\bigl(\mc{C}[X] \setminus \wh{C}\bigr).
 	\end{equation*}
@@
 	$$
-	\Delta(\wh{C}, \mathcal{C}[X]) := \vol_{n,r}(\wh{C} \vartriangle \mathcal{C}[X]). 
+	\Delta(\wh{C}, \mc{C}[X]) := \vol_{n,r}(\wh{C} \vartriangle \mc{C}[X]). 
 	$$
@@
 \subsection{Population normalized cut, conductance, and local spread}
-Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which we will use to upper bound the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$ with high probability.
-Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e.
-let
+Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and the local spread $s_{\Pbb,r}(\mc{C})$---which we will use to upper bound the volume of the symmetric set difference \smash{$\Delta(\wh{C},\mc{C}[X])$} with high probability.
+
+Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e., let
 \begin{equation*}
@@
 \begin{definition}[Population normalized cut]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population normalized cut} is
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$, and radius $r > 0$, the \emph{population normalized cut} is
 	\begin{equation}
@@
 
-Let $\wt{\mathbb{P}}(\cdot) = \mathbb{P}(\cdot|x \in \mc{C})$ be the conditional distribution of $x$, i.e let $\wt{\mbb{P}}(\mc{S}) = \wt{\Pbb}(\mc{S} \cap \mc{C})/\wt{\Pbb}(\mc{C})$ for measurable sets $\mc{S} \subseteq \Rd$.
+Let \smash{$\wt{\Pbb}(\cdot) = \Pbb(\cdot|x \in \mc{C})$} be the conditional distribution of $x$, i.e., let \smash{$\wt{\Pbb}(\mc{S}) = \wt{\Pbb}(\mc{S} \cap \mc{C})/\wt{\Pbb}(\mc{C})$} for measurable sets $\mc{S} \subseteq \Rd$.
 
 \begin{definition}[Population conductance]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population conductance} is
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population conductance} is
 	\begin{equation}
 	\label{eqn:population_conductance}
-	\Psi_{\mathbb{P},r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S}).
+	\Psi_{\Pbb,r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S}).
 	\end{equation}
 \end{definition}
+
 \begin{definition}[Population local spread]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population local spread} is
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population local spread} is
 	\begin{equation}
@@
 It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
-Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities can be used to upper bound the volume of the symmetric set difference.
+Indeed, these functionals are the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities can be used to upper bound the volume of the symmetric set difference.
 For this reason, similar population-level functionals are used by \cite{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
@@
 
-\subsection{Main Results}
+\subsection{Main results}
 We now informally state our two main upper bounds, regarding the recovery of a generic cluster $\mc{C}$, and a density cluster $\mc{C}_{\lambda}$.
@@
 	\label{thm:volume_ssd_ub_informal}
-	Let $\mc{C} \subset \Rd$ and $\Pbb$ satisfy appropriate regularity conditions, and suppose Algorithm~\ref{alg:ppr} is well-initialized with respect to $\mc{C}$.
-For all $n \in \mathbb{N}$ sufficiently large, with high probability it holds that
+	If $\mc{C} \subseteq \Rd$ and $\Pbb$ satisfy appropriate regularity conditions, and Algorithm~\ref{alg:ppr} is initialized properly with respect to $\mc{C}$, then for all sufficiently large $n$, with high probability it holds that
 	\begin{equation*}
@@
 \end{theorem}
-(In the above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put even more succinctly, we find that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\bigl(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C}))\bigr)^2$.
+
+(Above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put more succinctly, we find that \smash{$\Delta(\wh{C},\mc{C}[X])$} is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C})))^2$.
 To the best of our knowledge, this gives the first population-level guarantees for local clustering in the nonparametric statistical context.
 
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
+Next, Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
 For reasons that we explain later in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
@@
 We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $M$.
-We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
-\begin{equation*}
-0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\textrm{for all $x \in \mc{C}_{\lambda,\sigma}$},
+We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$:
+\begin{equation*}
+0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\text{for all $x \in \mc{C}_{\lambda,\sigma}$},
 \end{equation*}
@@
 \begin{equation*}
-\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\text{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
 \end{equation*}
@@
 	\label{thm:density_cluster_volume_ssd_ub_informal}
-	Let $\mc{C}_{\lambda} \subset \Rd$ be a $\lambda$-density cluster of a distribution $\Pbb$ that satisfies appropriate regularity conditions, and suppose Algorithm~\ref{alg:ppr} is well-initialized with respect to $\mc{C}_{\lambda,\sigma}$.
-For all $n \in \mathbb{N}$ sufficiently large, with high probability it holds that
-	\begin{equation}
-	\label{eqn:density_cluster_volume_ssd_ub_informal}
+	If $\mc{C}_{\lambda} \subseteq \Rd$ is a $\lambda$-density cluster of a distribution $\Pbb$, which satisfies appropriate regularity conditions, and Algorithm~\ref{alg:ppr} is initialized properly with respect to $\mc{C}_{\lambda,\sigma}$, then for all sufficiently large $n$, with high probability it holds that
+	\begin{equation*}
 	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
-	\end{equation}
+	\end{equation*}
 \end{theorem}
-Equation~\eqref{eqn:density_cluster_volume_ssd_ub_informal} reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-The parameters $M$, $\rho$ and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
-Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$ and $\theta$ measure whether the density $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside the density cluster) or poorly conditioned (vice versa).
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---i.e.
-$M^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
-$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
-
-\subsection{Related Work}
+
+The above result reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
+Here $M$, $\rho$, and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
+Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$, and $\theta$ measure whether the density $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside of it) or poorly conditioned (vice versa).
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} says that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---meaning, $M^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---meaning, $\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
+
+\subsection{Related work}
 \label{subsec:related_work}
-We now summarize some related work (in addition to the background already given above), regarding the theory of spectral clustering, and of density cluster recovery.
-
-\paragraph{Spectral clustering.}
-In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
-In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating
-back to \citet{mcsherry2001} who gives conditions under which the entire
-community structure can be recovered. In more recent work, \citet{rohe2011}
-upper bound the fraction of nodes misclassified by a spectral algorithm for the
-high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
-results to the sparse (low average degree) regime. Relatedly,
-\citet{clauset08,balakrishnan2011,li2018} analyze the misclassification rate
-when the block model exhibits some hierarchical structure. The framework we
-consider, in which nodes correspond to data points sampled from an underlying 
-density, and edges between nodes are formed based on geometric proximity, is
-quite different than the SBM, and therefore so is our analysis.
-
-In general, the study of spectral algorithms on neighborhood graphs has
-focused on establishing asymptotic convergence of eigenvalues and eigenvectors
-of certain sample objects to the eigenvalues and eigenfunctions of corresponding
-limiting operators. \citet{koltchinskii2000} establish convergence of spectral
-projections of the adjacency matrix to a limiting integral operator, with
-similar results obtained using simplified proofs in
-\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
-the Laplacian matrix for a neighborhood graph of fixed radius. \citet{belkin07} and
-\citet{garciatrillos18} extend these results to the regime where the radius $r
-\to 0$ as $n \to \infty$.
+We now summarize some related work (in addition to the background material already given above), regarding the theory of spectral clustering, and of density cluster recovery.
+
+\paragraph{Spectral clustering.} In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating back to \citet{mcsherry2001} who gives conditions under which the entire community structure can be recovered.
+In more recent work, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these results to the sparse (low average degree) regime.
+Relatedly, \citet{clauset08,balakrishnan2011,li2018} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+The framework we consider, in which nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
+
+In general, the study of spectral algorithms on neighborhood graphs has been focused on establishing asymptotic convergence of eigenvalues and eigenvectors of certain sample objects to the eigenvalues and eigenfunctions of corresponding limiting operators.
+\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
+\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood graph of fixed radius.
+\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime where the radius $r \to 0$ as $n \to \infty$.
 
@@
 
-\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
-In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
-By now, density clustering (and the related problem of level-set estimation) are quite well-understood.
-For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference
-metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and
-\citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider
-consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
-
-We emphasize that our goal is
-not to improve on these results, nor to offer a better algorithm for density clustering. Indeed, seen as a density clustering algorithm, PPR has none 
-of the optimality guarantees found in the aforementioned works.
+\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, we denote by \smash{$\mbb{C}_f(\lambda)$} the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
+In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mbb{C}_{f}(\lambda)$.
+By now, density clustering, and the related problem of level-set estimation, have been thoroughly studied.
+For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and \citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider estimation of the cluster tree $\{\mbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
+
+We emphasize that our goal is not to improve on these results, nor is it to offer a better algorithm for density clustering.
+Indeed, seen as a density clustering algorithm, PPR has none of the optimality guarantees found in the aforementioned works.
 Rather, we hope to better understand the implications of our general theory by applying it within an already well-studied framework.
-We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
+We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mbb{C}_f(\lambda)$.
 
@@
 We then show that under certain conditions the sample normalized cut, conductance, and local spread are close to their population-level counterparts, with high probability for sufficient number of samples.
-As a result, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ purely in terms of these population-level functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+As a result, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} purely in terms of these population-level functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
 	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
 We derive bounds on the population normalized cut, conductance, and local spread of the density cluster, which depend on $\lambda$ as well as some other natural parameters.
-This leads to an upper bound on the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster.
-(Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
-	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster is provably large.
+This leads to a bound on the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster is provably large.
 	\item In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
@@
 
-In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on the volume of the symmetric set difference $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$.
+In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on the volume of the symmetric set difference \smash{$\Delta(\wh{C}, \mc{C}[X])$}, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$.
 We build to this theorem slowly, giving new structural results in two distinct directions.
-First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s(G_{n,r}[\mc{C}[X]])$.
+First, we build on some previous work (mentioned in the introduction) to relate \smash{$\Delta(\wh{C}, \mc{C}[X])$} to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s(G_{n,r}[\mc{C}[X]])$.
 Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues with high probability.
 
-\subsection{PPR cluster recovery: the fixed graph case}
+\subsection{The fixed graph case}
 \label{subsec:ppr_cluster_recovery_fixed_graph}
-When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$.
+When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subseteq V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate \smash{$\wh{C}$} and candidate cluster $C$.
 Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in the Appendix.
@@
 here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ initialized at node $v$ and run for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+
 \begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
@@
 	\end{equation}
-	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
+	Then there exists a set $C^g \subseteq C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
 	\begin{equation}
@@
 \end{equation}
-Therefore, setting (for instance) $\alpha = \frac{\Psi(G[C])^2}{2\log(1/\pi_{\min}(G))}$ and $\wh{C} = S_{\beta_0,v}$ for $\beta_0 = \frac{1}{5 \vol(C;G)}$, we obtain from~\eqref{eqn:zhu_ub} that 
+Therefore, setting (for instance) \smash{$\alpha = \frac{\Psi(G[C])^2}{2\log(1/\pi_{\min}(G))}$} and \smash{$\wh{C} = S_{\beta_0,v}$} for \smash{$\beta_0 = \frac{1}{5 \vol(C;G)}$}, we obtain from~\eqref{eqn:zhu_ub} that
 \begin{equation}
@@
 \label{subsec:mixing_time}
-Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$.
-Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mathbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound whenever the number of samples is sufficiently large.
-
-To fix this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
+Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subseteq \Rd$.
+Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on \smash{$\Delta(\wh{C};\mc{C}[X])$} that depends only on $\Pbb$ and $\mc{C}$.
+Unfortunately, however, there is a catch: when the graph is $G = G_{n,r}$ and the candidate cluster is $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}(G_{n,r}[\mc{C}[X]]) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, which turns~\eqref{eqn:zhu_ub2} into a vacuous upper bound whenever the number of samples is sufficiently large.
+
+To address this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on the mixing time in~\eqref{eqn:mixing_time_cheeger}.
 Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the graph local spread, defined as
@@
 \end{equation*}
-for $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$. Note that $s(G) \geq \pi_{\min}(G)$.
+for $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$. Notice that $s(G) \geq \pi_{\min}(G)$.
 \begin{proposition}
@@
 	\label{eqn:pointwise_mixing_time}
-	\tau_{\infty}(G) \leq \frac{17}{\ln(2)} \biggl(\frac{\ln\bigl(32/s(G)\bigr)}{\Psi(G)}\biggr)^2
+	\tau_{\infty}(G) \leq \frac{17}{\ln(2)} \biggl(\frac{\ln\bigl(32/s(G)\bigr)}{\Psi(G)}\biggr)^2.
 	\end{equation}
 \end{proposition}
-While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
-In particular, when $G = G_{n,r}\bigl[\mc{C}[X]\bigr]$ for a fixed radius $r > 0$, the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp n$, and therefore $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1$.
-We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
+
+While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (provided that the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful for geometric graphs: when $G = G_{n,r}[\mc{C}[X]]$ for a fixed radius $r > 0$, we have $d_{\min}(G_{n,r}[\mc{C}[X]]) \asymp n$, and thus $s(G_{n,r}[\mc{C}[X]]) \asymp 1$.
+We give a precise upper bound on $s(G_{n,r}[\mc{C}[X]])$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
 
@@
 The local spread $s(G)$ simply delineates small sets $R$ from larger sets $S$.
-Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a substantially more careful analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
+Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a much more intricate analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
 
@@
 In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, conductance, and local spread in terms of their population-level analogues.
-To establish these bounds, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
+To establish these bounds, we impose the following regularity conditions on \smash{$\wt{\Pbb}$} and $\mc{C}$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 	\label{asmp:bounded_density} 
-	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ with respect to Lebesgue measure. There exist $0 < f_{\min} \leq f_{\max} < \infty$ for which
+	The distribution \smash{$\wt{\Pbb}$} has a density \smash{$\wt{f}: \mc{C} \to (0,\infty)$} with respect to Lebesgue measure. There exist $0 < f_{\min} \leq f_{\max} < \infty$ for which
 	\begin{equation*}
@@
 	\label{asmp:domain} 
-	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set.
-If $d \geq 2$ then it has a Lipschitz boundary $\partial \mc{C}$, meaning it is locally the graph of a Lipschitz function (see Definition 9.57 of~\cite{leoni2017}).
+	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set, and for $d \geq 2$, it has a Lipschitz boundary $\partial \mc{C}$, meaning it is locally the graph of a Lipschitz function (e.g., see Definition 9.57 of~\cite{leoni2017}).
 \end{enumerate}
+
 In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$, $\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
 We explicitly keep track of all constants in our proofs.
+
 \begin{proposition}
 	\label{prop:sample_to_population_1}
-	Fix $\delta \in (0,1/3)$. Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
+	Fix $\delta \in (0,1/3)$. Suppose \smash{$\wt{\Pbb}$} and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
 	\begin{itemize}
@@
 		\end{equation}
-		\item For any $n \in \mathbb{N}$ for which 
+		\item For any $n \in \mbb{N}$ for which 
 		\begin{equation}
 		\label{eqn:sample_to_population_local_spread_sample_complexity}
-		\frac{1}{n} \leq \delta \cdot \frac{2\Pbb(\mc{C})}{3}
+		\frac{1}{n} \leq \delta \cdot \frac{2\Pbb(\mc{C})}{3},
 		\end{equation}
@@
 	\label{prop:sample_to_population_2}
-	Fix $\delta \in (0,1/2)$. Suppose  $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then for any $n \in \mathbb{N}$ satisfying
+	Fix $\delta \in (0,1/2)$. Suppose \smash{$\wt{\Pbb}$} and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. For any $n \in \mbb{N}$ satisfying
 	\begin{equation}
@@
 
-A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
-To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, but otherwise the proof is similarly straightforward.
+A note on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$, and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
+To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}(G_{n,r}[\mc{C}[X]])$, but otherwise the proof is similarly straightforward.
+
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
-Our proof relies on the recent results of \citet{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\mathbb{P}_n$ and $\mathbb{P}$.
+Our proof relies on the recent results of \citet{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\Pbb_n$ and $\Pbb$.
 For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citet{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
@@
 & (L,U) \subseteq \Bigl(\frac{1}{5(1 + 2\delta)},\frac{1}{5(1 + \delta)}\Bigr) \cdot 
-\frac{1}{n(n - 1)\vol_{\Pbb,r}(\mc{C})}.
+\frac{1}{n(n - 1)\vol_{\Pbb,r}(\mc{C})},
 \end{aligned}  
@@
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
+	When the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
 \end{definition}
 
-Of course, in practice it is not feasible to set tuning parameters based on the 
-underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$. Typically, one runs PPR over some range of
-tuning parameter values and selects the cluster which has the smallest
-normalized cut.
+Of course, in practice it is not feasible to set tuning parameters based on the underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$.
+Typically, one runs PPR over some range of tuning parameter values and selects the cluster which has the smallest normalized cut.
 
@@
 Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
-Then for any $n \in \mathbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
+Then for any $n \in \mbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
 	\begin{equation}
@@
 	\end{equation} 
-	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume,
+$$
+\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X]),
+$$ 
+such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}[X]$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 \end{theorem}
-% AJG: The following lines are commented out, because they are superseded by the informal statement of our theorem above.
-%
-% To summarize: if PPR is well-initialized within a candidate cluster $\mc{C}$, then the volume of the symmetric set difference between $\wh{C}$ and $\mc{C}[X]$ is upper bounded by the following function of the population-level functionals:
-% \begin{equation*}
-% \frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \lesssim \Phi_{\Pbb,r}(\mc{C})  % \cdot \frac{\log^2\bigl(1/s_{\Pbb,r}(\mc{C})\bigr)}{\Psi^2_{\Pbb,r}(\mc{C})}.
-% \end{equation*}
-%
-
-We now make some remarks:
+
+We now make some remarks.
 \begin{itemize}
 	\item It is useful to compare Theorem~\ref{thm:volume_ssd_ub} with what is already known regarding \emph{global} spectral clustering in the context of nonparametric statistics.
-\cite{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^{k}$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters $\wh{C}_1,\ldots,\wh{C}_k$  using $k$-means clustering.
+\cite{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^k$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters \smash{$\wh{C}_1,\ldots,\wh{C}_k$} using $k$-means clustering.
 They derive error bounds on the misclassification error that depend on a difficulty function $\varphi(\Pbb)$.
-In our context, where the goal is to successfully distinguish $\mc{C}$ and $\mc{C}^c$ and thus $k = 2$, this difficulty function is roughly
+In our context, where the goal is to successfully distinguish $\mc{C}$ and $\mc{C}^c$, thus where $k = 2$, this difficulty function is roughly
 	\begin{equation}
@@
 This is intuitive: PPR is a local rather than global algorithm, and as such the analysis requires only local rather than global conditions.
-Second,~\eqref{eqn:schiebinger} depends on $\sqrt{\Phi_{\Pbb,r}(\mc{C})}$ rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citep{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
+Second,~\eqref{eqn:schiebinger} depends on \smash{$\sqrt{\Phi_{\Pbb,r}(\mc{C})}$} rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citet{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
 Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$, which is due to the locally-biased nature of the PPR algorithm, and does not appear in~\eqref{eqn:schiebinger}.
@@
 A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus may not be resolved by any finite number of samples.
-To rule out such problematic clusters, we follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Reals^d: \dist(x,\mc{C}) < \sigma\}$ for a given $\sigma > 0$.
-The point is that regardless of the dimension of $\mc{C}_{\lambda}$, the set $\mc{C}_{\lambda,\sigma}$ is full dimensional.
+To rule out such problematic clusters, we follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \dist(x,\mc{C}) < \sigma\}$ for a given $\sigma > 0$.
+Regardless of the dimension of $\mc{C}_{\lambda}$, the set $\mc{C}_{\lambda,\sigma}$ is full dimensional.
 Under typical uniform continuity conditions, the requirement that the density be lower bounded over $\mc{C}_{\lambda,\sigma}$ will be satisfied.
@@
 
-In summary, our goal is to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
-We have already derived upper bounds on the symmetric set difference of $\wh{C}$ and a generic cluster $\mc{C}$ that depend on some population-level functionals of $\mc{C}$.
+In summary, our goal is to obtain upper bounds on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}, for some fixed $\lambda$ and $\sigma > 0$.
+We have already derived upper bounds on the symmetric set difference of \smash{$\wh{C}$} and a generic cluster $\mc{C}$ that depend on some population-level functionals of $\mc{C}$.
 What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
@@
 	Roughly, this assumption ensures that the density decays sufficiently quickly
-	as we move away from the target cluster $\mc{C}_{\lambda,\sigma}$, and is a standard assumption
-	in the level-set estimation literature (see for instance \citet{singh2009}).
+	as we move away from the target cluster $\mc{C}_{\lambda,\sigma}$, and is a standard assumption in the level-set estimation literature (see for instance \citet{singh2009}).
 
@@
 	\emph{Lipschitz embedding:}
-	There exists a differentiable function $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $M \in [1,\infty)$ such that
+	There exists a differentiable function $g: \Rd \to \Rd$, $\rho \in (0,\infty)$ and $M \in [1,\infty)$ such that
 	\begin{enumerate}
-		\item we have $\mc{C}_{\lambda,\sigma} = g(\mathcal{K})$, for a convex set $\mathcal{K}
-		\subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
-			\mathcal{K}}\|x - y\| \leq \rho < \infty$;
-		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is
-		the Jacobian of $g$ evaluated at $x;$ and 
+		\item $\mc{C}_{\lambda,\sigma} = g(\mc{K})$, for a convex set $\mc{K} \subseteq \Rd$ with $\mathrm{diam}(\mc{K}) = \sup_{x,y \in \mc{K}}\|x - y\| \leq \rho < \infty$;
+		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x;$ and 
 		\item for some $M \geq 1$,   
 		$$
-		\|g(x) - g(y)\| \leq M \|x - y\| ~
-		\text{for all $x,y \in \mathcal{K}$}. 
+		\|g(x) - g(y)\| \leq M \|x - y\| ~	\text{for all $x,y \in \mc{K}$}. 
 		$$
@@
 \end{proposition}
-Some remarks are in order:
+
+Some remarks are in order.
 \begin{itemize}
@@
 	\item Proposition~\ref{prop:density_cluster_conductance} is proved in a completely different way.
-The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g.
-\cite{lovasz1990} or \cite{dyer1991b}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
+The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g., \cite{lovasz1990} or \cite{dyer1991b}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
 	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
@@
 
-\noindent Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$.
+Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}.
 In what follows, $C_{1,\delta},C_{2,\delta},\ldots$ are constants which may depend on $\delta$, but not on $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$, and which we keep track of in our proofs.
+
 \begin{theorem}
@@
 Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $M$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:volume_ssd_ub}.
-Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,
+$$
+\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \frac{1}{2} \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]).
+$$ 
+such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster \smash{$\wh{C}$} satisfies
 	\begin{equation}
@@
 \end{theorem}
-As we have previously summarized, Theorem~\ref{thm:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-Now, we make some other remarks:
+
+Several further remarks are as follows.
 \begin{itemize}
 	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} through the conductance.
-This reflects
-	(what may be regarded as) established wisdom regarding spectral partitioning
-	algorithms more generally \citep{guattery1995, hein2010}, but newly applied
-	to the density clustering setting: if the diameter $\rho$ is large, then PPR
-	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
+This reflects (what may be regarded as) established wisdom regarding spectral partitioning algorithms more generally \citep{guattery1995, hein2010}, but newly applied to the density clustering setting: if the diameter $\rho$ is large, then PPR	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
 This will be supported by simulations in Section~\ref{subsec:empirical_behavior_ppr}.
@@
 However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, and spectral clustering functions as more of a post-processing step.
-These methods are thus very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
+These methods are as such very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
 	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
 It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
-	\item The symmetric set difference does not measure whether \smash{$\wh{C}$}
-	can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$}.
+	\item The symmetric set difference does not measure whether \smash{$\wh{C}$} can (perfectly) distinguish any two distinct clusters $\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mbb{C}_f(\lambda)$.
 In Appendix~\ref{apdx:appr_misclassification_error}, we show that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
@@
 \label{sec:lower_bound}
-We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
-cluster. Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in
-$\Reals^2$,    
+We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
+Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in $\Reals^2$,
 $$
@@
 $$
-where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over
-\smash{$\mathcal{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
+where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over \smash{$\mc{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
 $$
@@
 \end{equation}
-so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have 
-\smash{$\mathbb{C}_f(\lambda) = \set{\mc{C}^{(1)}, \mc{C}^{(2)}}$}. Figure~\ref{fig:hard_case} visualizes the density $f$ for two different choices of $\epsilon,
-\sigma, \rho$.
+so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have \smash{$\mbb{C}_f(\lambda) = \set{\mc{C}^{(1)}, \mc{C}^{(2)}}$}.
+Figure~\ref{fig:hard_case} visualizes the density $f$ for two different choices of $\epsilon, \sigma, \rho$.
 
@@
 \subsection{Lower bound on symmetric set difference}
-As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
-reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is 
-sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
-estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}. Let
+As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}.
+Let
 \begin{equation}
 \label{eqn:lower_set}
-\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
+\mc{L} = \set{(x_1,x_2) \in \mc{X}: x_2 < 0}.
 \end{equation}
@@
 	\label{eqn:ppr_lb_condition}
-	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
-	\end{equation} 
-	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot   
-	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.
-Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
-		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/8$}, such
-	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
+	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\text{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
+	\end{equation} 
+	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot \Phi_{n,r}(\mc{L}[X])$, and $(L,U) = (0,1)$.
+Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume,
+$$
+\vol_{n,r}(\mc{C}[X]^g \cap \mc{C}^{(1)}[X]) \geq \frac{1}{8} \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r}),
+$$
+suchthat for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
 	\smash{$\wh{C}$} satisfies    
@@
 	\label{eqn:ppr_lb}
-	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
-	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot 
-	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}
-		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
+	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot ]frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}{\epsilon^2 r^2}\right) \frac{\sigma}{r}},
 	\end{equation} 
 \end{theorem}
-We make a couple of remarks:
+
+We make a couple of remarks.
 \begin{itemize}
@@
 	setting to make the theorem simple to state, and our results are generalizable
-	to $\Reals^d$ and to non-rectangular clusters. Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
+	to $\Rd$ and to non-rectangular clusters. Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
 	$\sigma$-expansions due to their sharp corners. To fix this, one can   
@@
 	\item Although we state our lower bound with respect to PPR run on a neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
-In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mathcal{L}$.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mc{L}$.
 In this case, not merely PPR but any algorithm that approximates the minimum normalized cut is unlikely to recover $\mc{C}^{(1)}$.
-In particular, local spectral clustering
-	algorithms based on truncated random walks \citep{spielman2013}, global spectral
-	clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings
-	\citep{hein2010} all have provable upper bounds on the normalized cut of cluster
-	they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
+In particular, local spectral clustering methods that are based on truncated random walks \citep{spielman2013}, global spectral clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings \citep{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
 \end{itemize}
@@
 \label{subsec:comparison_upper_lower_bounds}
-
 To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
@@
 	\setcounter{enumi}{2}
-	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
-	\mc{C}^{(1)}$.  
-	\item The density $f(x) \leq \frac{\epsilon}{\rho\sigma}$ for all $x \in \Reals^2$ such
-	that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
-	$$
-	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  \geq \left\{\frac{1 - \epsilon}{2} -
-	\epsilon \right\} \frac{1}{\rho \sigma},
+	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in	\mc{C}^{(1)}$.  
+	\item The density $f(x) \leq \frac{\epsilon}{\rho\sigma}$ for all $x \in \Reals^2$ such that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
+	$$
+	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  \geq \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma},
 	$$
@@
 	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\sqrt{\rho^2 + \sigma^2}$.
-	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) =
-		\vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore
-	\smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$}.   
+	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) = \vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Rd)$}.   
 \end{enumerate}
 
-If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}. This implies that 
-there exists a set $\mc{C}^{(1)}[X]^g \subseteq \mc{C}^{(1)}[X]$ with
-\smash{$\vol_{n,r}(\mc{C}^{(1)}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X])$} such
-that for any seed node $v \in \mc{C}^{(1)}[X]^g$, and for large enough $n$, the
-PPR estimated cluster $\wh{C}$ satisfies with high probability
+If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+This implies that there exists a set $\mc{C}^{(1)}[X]^g \subseteq \mc{C}^{(1)}[X]$ with \smash{$\vol_{n,r}(\mc{C}^{(1)}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X])$} such that for any seed node $v \in \mc{C}^{(1)}[X]^g$, and for large enough $n$, the PPR estimated cluster \smash{$\wh{C}$} satisfies with high probability
 \begin{equation*}
@@
 \end{equation*}
-To facilitate comparisons between our upper
-and lower bounds set $r = \sigma/8$.  Then
-the following statements each hold with high probability. 
+To facilitate comparisons between our upper and lower bounds set $r = \sigma/8$.  Then the following statements each hold with high probability. 
 \begin{itemize}
@@
 	\end{equation*}
-	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{20}
-		\vol_{n,r}(\mc{C}^{(1)}[X])$}. 
+	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{20} \vol_{n,r}(\mc{C}^{(1)}[X])$}. 
 \end{itemize}
-Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even when reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
-Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific
-(albeit reasonable) ranges and choices of input parameters, which in some
-instances differ between the upper and lower bounds. We suspect that our lower
-bound continues to hold even when choosing input parameters as dictated by our
-upper bound, but do not pursue the details.}
-
-Of course, it is not hard to show that in the example under consideration, classical
-plug-in density cluster estimators can consistently recover $\mc{C}^{(1)}$, even if $\epsilon$ is
-large compared to $\sigma/\rho$. That PPR has trouble recovering density
-clusters here (where standard plug-in approaches do not) is not meant to
-be a knock on PPR. Rather, it simply reflects that while classical density
-clustering approaches are specifically designed to identify high-density regions
-regardless of their geometry, PPR relies on geometry as well as density when
-forming the output cluster.
+Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even if it is reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound, but do not pursue the details.}
+
+Of course, it is not hard to show that in the example under consideration, classical plug-in density cluster estimators can consistently recover $\mc{C}^{(1)}$, even if $\epsilon$ is large compared to $\sigma/\rho$.
+That PPR has trouble recovering density clusters here (where standard plug-in approaches do not) is not meant to be a knock on PPR.
+Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR relies on geometry as well as density when forming the output cluster.
 
@@
 \subsection{Validating theoretical bounds}
-We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e.
-the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
+We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e., the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
 Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities, when samples are drawn from a mixture of uniform distributions over rectangular clusters.
@@
 The one exception to this is the dependence of local spread on the width $\sigma$; this theoretical deficiency stems from a loose bound on the volume of sets with large aspect ratio (meaning $\rho/\sigma$ is much greater than $1$), but in any case the local spread contributes only $\log$ factors to the ultimate bound on cluster recovery.
-On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$, which as a result is loose by several orders of magnitude.
+On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$}, which as a result is loose by several orders of magnitude.
 
@@
 	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/local_spread.pdf}
-	\caption{\it \small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
+	\caption{\it\small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
 In the first row we vary the diameter $\rho$, in the second row we vary the thickness $\sigma$, and in the third row we vary the density ratio $(\lambda - \theta)/\lambda$.
@@
 \label{subsec:empirical_behavior_ppr}
-In Figure \ref{fig:moons}, to drive home 
-the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR
-and the density clustering algorithm of \citet{chaudhuri2010} on
-the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
-a prototypical success story for spectral clustering algorithms.
+In Figure \ref{fig:moons}, to drive home the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR and the density clustering algorithm of \citet{chaudhuri2010} on the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
 We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be seen as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
-The first
-column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for
-a particular threshold $\lambda$ of the density function; the second column
-shows the cluster recovered by PPR; the third column shows the global minimum
-normalized cut, computed according to the algorithm of \citet{bresson2013}; and
-the last column shows a cut of the density cluster tree estimator of
-\citet{chaudhuri2010}.
+The first column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by PPR; the third column shows the global minimum normalized cut, computed according to the algorithm of \citet{bresson2013}; and the last column shows a cut of the density cluster tree estimator of \citet{chaudhuri2010}.
 Each row corresponds to a different separation between the two moons.
-In the second row, we see that as the two moons become less well-separated, PPR becomes unable to recover the density clusters, but
-normalized cut still succeeds in doing so. In the third row, we see that the
-Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
-fail. This supports one of our main messages, which is that PPR recovers only
-geometrically well-conditioned density clusters.
+In the second row, we see that as the two moons become less well-separated, PPR becomes unable to recover the density clusters, but normalized cut still succeeds in doing so.
+In the third row, we see that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.
+This supports one of our main messages, which is that PPR recovers only geometrically well-conditioned density clusters.
 
@@
 
-Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to  
-\infty$, would be computationally attractive, as it would ensure that the graph 
-$G_{n,r}$ is sparse.
-However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in
-this regime. Although the restriction to a kernel function fixed in $n$ is
-common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017},
-recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.
-
-In another direction, it would be very useful to find reasonable conditions under which the ratio $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ would tend to $0$ as $n \to \infty$.
+Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to \infty$, would be computationally attractive, as it would ensure that the graph $G_{n,r}$ is sparse.
+However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in this regime.
+Although the restriction to a kernel function fixed in $n$ is common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017}, recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.
+
+In another direction, it would be very useful to find reasonable conditions under which the ratio \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} would tend to $0$ as $n \to \infty$.
 It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR.
-Although most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
+Though most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
 It is not clear whether the techniques used in these works can be applied to PPR.
@@
 
-SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
-helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for early inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
 

### 2021-12-23 jmlr/revision/response_to_reviewers.tex

@@
 \usepackage{graphicx}
-\usepackage[colorlinks]{hyperref}
 \usepackage[parfill]{parskip}
@@
 \usepackage{tikz}
+\usepackage{hyperref}       % hyperlinks
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	citecolor=blue
+}
 
@@
 \begin{document}
-First of all, we would like to thank the reviewers and associate editor for their thoughtful comments and helpful suggestions, and for the invitation to resubmit.
+First of all, we would like to thank the reviewers and associate editor for their thoughtful comments and helpful suggestions.
 In response to this feedback, we have significantly reworked our manuscript, making the following major changes:
@@
 \begin{itemize}
-	\item \textbf{New theoretical results.} In a new Section 2, we establish conditions under which Personalized PageRank (PPR), run on a geometric graph, will recover an \emph{arbitrary} candidate cluster $\mc{C} \subseteq \Rd$ (i.e.
+	\item \textbf{New theoretical results.} In a new Section 2, we establish conditions under which Personalized PageRank (PPR), run on a geometric graph, will recover an \emph{generic} candidate cluster $\mc{C} \subseteq \Rd$ (i.e.
 not necessarily a density cluster).
-Our upper bound in Theorem 9 (new version) on the error $\Delta(\wh{C},\mc{C}[X])$ depends on population-level functionals---normalized cut, local spread, and conductance---that have previously been used to analyze the behavior of (global) spectral clustering algorithms in nonparametric mixture models, and we explicitly connect our results to this related work.
+Our upper bound in Theorem 12 (new version) on the error $\Delta(\wh{C},\mc{C}[X])$ depends on population-level functionals---normalized cut,conductance, and local spread---that have previously been used to analyze the behavior of global spectral clustering algorithms in nonparametric mixture models, and we comment in detail on the relation between our results and previous work.
 
 	\item \textbf{Improved upper bounds.} In Section 3, we apply this general theory to the specific case where $\mc{C} = \mc{C}_{\lambda}$ is a density cluster.
-The resulting upper bound on $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ (Corollary 14) is comparable to Theorem~5 of our previous submission, but with significantly smaller universal constants.
+In  Theorem 16, we upper bound the volume of the symmetric set difference between the cluster estimate and the true density cluster; this theorem is comparable to Theorem~5 of our previous submission, but with significantly smaller universal constants.
+
+	\item \textbf{Improved empirical section.} We have modified the first figure in our empirical section (Figure~2) to allow for a precise comparison between our theoretical bounds on graph functionals of a density cluster, and their empirical values.
+We see that in almost all cases, our bounds correctly predict the behavior of these graph functionals as the geometry of the density cluster is changed, and are off by at most one order of magnitude.
 
@@
 	\begin{itemize}
+		\item We offer informal statements of our main upper bounds, in order to emphasize (what we view as) the crucial takeaways;
 		\item We comment more extensively on our major theoretical results, explaining their significance and tying them to related work;
 		\item We precisely use universal constants throughout, and in particular offer a cleaner comparison between our upper and lower bounds;
-		\item We \textcolor{red}{(emphasize)} the three modular components of our analysis: (i) bounds on PPR in terms of graph functionals; (ii) bounds on graph functionals in terms of population functionals; (iii) in the case of density cluster recovery, bounds on population functionals in terms of geometric parameters.
-\textcolor{red}{(Do I need to add a sentence here, or is modularity an obviously good goal on its own?)}
+		\item We build slowly to our main results in Section 2 and 3.
+This exposes three modular components of our analysis---(i) bounds on PPR in terms of graph functionals; (ii) bounds on graph functionals in terms of population functionals; (iii) in the case of density cluster recovery, bounds on population functionals in terms of geometric parameters---and has the effect of making our major theorems easier to digest, as well as highlighting our various technical contributions.
 	\end{itemize}
@@
 
-(\textit{``...usefulness of the key Theorem 5...''}) As outlined above, in our resubmission we have replaced Theorem 5 (old version) by Theorem 9 and Corollary 14 (new version).
+(\textit{``...usefulness of the key Theorem 5...''}) As outlined above, in our resubmission we have replaced Theorem 5 (old version) by Theorem 12 and Theorem 16 (new version).
 
-Theorem~9 (new version)  is substantially more general than Theorem~5 (old version), as it upper bounds $\Delta(\wh{C},\mc{C}[X])$ for an arbitrary set $\mc{C} \subseteq \Rd$ in terms of the population-level normalized cut and conductance.
-To the best of our knowledge, this is the first result on the clustering performance of PPR in the non-parametric statistical setup.
-In some remarks, we compare Theorem~9 to some related literature on global spectral clustering, showing both that Theorem~9 is in certain respect sharper than these related results while naturally requiring (weaker) local rather than global conditions.
+Theorem 12 (new version)  is substantially more general than Theorem~5 (old version), as it upper bounds $\Delta(\wh{C},\mc{C}[X])$ for a generic clusters $\mc{C} \subseteq \Rd$ in terms of the population-level normalized cut, conductance, and local spread.
+To the best of our knowledge, this is the first result on the clustering performance of PPR, or indeed any local spectral clustering algorithm, in the non-parametric statistical setup.
+In some remarks, we compare Theorem 12 to some related literature on global spectral clustering, showing both that Theorem 12 is in certain important respects sharper than previous results while naturally requiring (weaker) local rather than global conditions.
 
-Corollary~14 (new version) treats the case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster.
-It gives substantially tighter (in terms of constants) upper bound on $\Delta(\wh{C},\mc{C}_{\lambda}[X])$ than Theorem~5 (old version).
-To our knowledge, this is the first resulting tying the clustering performance of a canonical spectral method to recovery of a density cluster.
+Theorem 16 (new version) treats the case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, and is thus directly comparable to Theorem~5 (old version).
+It gives a substantially tighter (in terms of constants) upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ than Theorem~5 (old version).
+To our knowledge, this is the first result tying the performance of a spectral clustering method to recovery of a density cluster.
 
-(\textit{``...sets of zero measure may dramatically alter the topological structure of the level sets.''}) We deal with this difficulty by assuming the density $f(x) \geq \lambda_{\sigma}$ everywhere on the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} = \mc{C}_{\lambda} + B(0,\sigma)$.
-In our revised submission, we comment explicitly on the difficulty measure-zero sets can play in the definition of density clusters, and clarify how the $\sigma$-thickening resolves this difficulty.
+(\textit{``...sets of zero measure may dramatically alter the topological structure of the level sets.''}) Following the lead of~\citet{chaudhuri2010}, we assume the density $f(x) \geq \lambda_{\sigma} > 0$ everywhere on the full-dimensional set $\mc{C}_{\lambda,\sigma} = \mc{C}_{\lambda} + B(0,\sigma)$.
+Our ultimate bound on density cluster recovery is with respect to the enlarged set $\mc{C}_{\lambda,\sigma}$, and depends on $\lambda_{\sigma}$.
+If $f$ satisfies a uniform continuity condition, the density will be lower bounded over $\mc{C}_{\lambda,\sigma}$, and we now make this point explicitly in our setup.
+We also mention that such continuity conditions can be weakened, and point to relevant references \citep{rinaldo2010, steinwart2015}.
 
@@
 
-(\textit{``Is $\kappa(\mc{C})$ uniquely defined?''}) We have modified our definition of the condition number so as to make it uniquely defined.
-We now denote the condition number by $\kappa_{\Pbb,r}(\mc{C},\delta)$, to make clear exactly what the condition number depends on: the distribution $\Pbb$, the graph radius $r > 0$, the candidate cluster $\mc{C} \subset \Rd$, and a high-probability parameter $\delta \in (0,1)$.
+(\textit{``Is $\kappa(\mc{C})$ uniquely defined?''}) We have modified our definition of the condition number so as to make it uniquely defined in terms of functionals of a generic cluster $\mc{C}$.
+In our revision, for $\delta \in (0,1/4)$ we define
+\begin{equation*}
+\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)(1+2\delta)}{(1 - 4\delta)^2(1 - \delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}.
+\end{equation*}
+where
+\begin{equation*}
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{13} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}.
+\end{equation*}
+The condition number thus depends on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$ of the candidate cluster, as well as on the high-probability parameter $\delta$.
 
-(\textit{``...not clear whether or not $c \cdot \kappa(\mc{C}) \leq \vol(X \setminus \mc{C}) / \vol(\mc{C} \cap X)$''}) Whenever the thickened density-cluster $\mc{C}_{\lambda,\sigma}$ satisfies a sufficiently strong low-noise condition---i.e.
-$\theta$ and $\gamma$ in (A2) are sufficiently large--- it will hold that $\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \vol(X \setminus \mc{C}_{\lambda}) / \vol(\mc{C}_{\lambda} \cap X)$.
+(\textit{``...not clear whether or not $c \cdot \kappa(\mc{C}) \leq \vol(X \setminus \mc{C}) / \vol(\mc{C} \cap X)$''}) For a given $a > 0$, our revised definition of condition number $\kappa_{\Pbb,r}(\mc{C},\delta)$ will be less than $a/60$ if
+\begin{equation}
+\label{eqn:rebuttal1}
+\Phi_{\Pbb,r}(\mc{C}) < a \cdot \frac{\ln 2(1 - \delta)(1 - 4\delta)^2}{780(1 + 3\delta)(1 + 2\delta)} \cdot \frac{\ln^2\Bigl(\frac{8}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}{\Psi_{\Pbb,r}(\mc{C})^2}.
+\end{equation}
+Theorem~12 (new version) guarantees that if $\mc{C}$ satisfies~\eqref{eqn:rebuttal1}, then for $n$ sufficiently large \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X]) < a$} with high probability.
+Taking $a = \min\{\vol_{\Pbb,r}(\mc{C}),\vol_{\Pbb,r}(\Rd \setminus \mc{C})\} $ (or some small fraction thereof), our theory shows that $\Delta(\wh{C},\mc{C}[X])$ will be (much) smaller than that of the trivial estimators $\wh{C} = \emptyset$ or $\wh{C} = X$.
 
-(\textit{``...there is a risk that the upper bounds presented here could be too loose that they do not reflect the real performance of the algorithm.''}) In our view, the most useful way to interpret our upper and lower bounds is by focusing on how these bounds depend on the geometric parameters $\sigma, \rho$ and $L$, the density parameters $\lambda,\Lambda_{\sigma},\lambda_{\sigma},\gamma$ and $\theta$, and the dimension $d$, and we have clarified this in our exposition.
+If $\mc{C} = \mc{C}_{\lambda,\sigma}$ is a (thickened) density cluster, Proposition~14 (new version) tells us that~\eqref{eqn:rebuttal1} will hold if $f$ satisfies a sufficiently strong low-noise condition around the boundary of $\mc{C}_{\lambda,\sigma}$---i.e.
+$f$ satisfies~(A4) for sufficiently large $\theta$ and $\gamma$.
 
-Nevertheless, we acknowledge that practically speaking it is useful to have reasonable values for constants, and in our resubmission we have also substantially improved the constants in our upper bounds on normalized cut and mixing time.
-While it is very hard to know the sharpest possible values for all constants, at relevant points in our appendices we do include discussions of the tightness of our bounds with regards to constants.
-Finally, we have modified our experiments section so that the reader may more easily compare our upper bounds with empirical reality.
+(\textit{``...there is a risk that the upper bounds presented here could be too loose that they do not reflect the real performance of the algorithm.''}) Our response to this comment focuses on the density cluster recovery results of Section~3, since these results are directly comparable to those of our previous submission, and are thus the results the reviewer was concerned about.
+However, it is worth pointing out two facts about our new generic cluster recovery results of Section~2: first, that it is widely accepted that the local spectral clustering algorithms such as PPR intrinsically depend on functionals such as normalized cut and conductance; and second, that our particular bounds on PPR are in some key respects stronger than those derived in previous works, as we comment on in a remark after Theorem~12.
 
-(``[In] \textit{the example used to produce Fig.
+Now, with regards to our density cluster recovery results: in our view the most useful way to interpret our upper and lower bounds is by focusing on how these bounds depend on the geometric parameters $\sigma, \rho$ and $L$, the density parameters $\lambda,\Lambda_{\sigma},\lambda_{\sigma},\gamma$ and $\theta$, and the dimension $d$.
+We have tried to emphasize this in our exposition.
+At the same time, we have also substantially improved the constants in our bounds on normalized cut, conductance, and local spread.
+In Figure~2, we show that our bounds on each of these functionals are reasonably close to empirical reality, off by an order of magnitude or less.
+
+However, we would like to emphasize that despite our best efforts at optimizing various constants and dependencies, our ultimate bounds are still too loose to make quantitative predictions on the behavior of PPR.
+Our upper bound on $\kappa_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)$ often yields correct qualitative predictions (as we have confirmed in theory by complementary lower bounds) but, as we acknowledge in the main text, will yield quite pessimistic quantitative predictions.
+
+Indeed, even for the much simpler density clustering algorithm of~\citet{chaudhuri2010}, selecting tuning parameters according to their prescription(s) (based on finite-sample concentration inequalities) would lead to vacuous guarantees except for extremely large sample-sizes, or for extreme geometric cluster parameters (separation and density-drop).
+When these geometric parameters take large values the density clustering problem is trivial.
+As is a general theme in most work in statistical learning theory, their work gives useful qualitative insights even when the precise quantitative bounds are vacuous.
+
+% AJG: Removed this, as our response to this point is the same as the one above.
+%
+%(``[In] \textit{the example used to produce Fig.
 2...
@@
 
+(``\textit{$\kappa(\mc{C})$ should be explicitly reported} [in experiments]'') The condition number will be a loose bound on the actual performance of the algorithm, a fact we frankly acknowledge in our main text, and so we do not think it would be useful to report it.
+
 (``\textit{The use of universal constants throughout the paper is not consistent.}'') We apologize for the confusion.
 In our new submission, we have clarified our use of constants so as to avoid any ambiguity.
+We explicitly keep track of all constants in our appendices.
 
-(``\textit{$\kappa(\mc{C})$ should be explicitly reported} [in experiments]'') The condition number will be a rather loose bound (in terms of constants) on the actual performance of the algorithm, a fact we frankly acknowledge in our experiments section.
-Nevertheless, as pointed out previous, the bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ will be small when $\theta \geq \textcolor{red}{(...)}$.
+(``\textit{...parameters used in the first experiment...}'') We now report all parameters for our experiment in Appendix~F.
 
-\textcolor{red}{Alden for Siva: I guess somewhere around here is where it might be helpful to comment on how seriously one should take our constants?}
-
-(``\textit{...parameters used in the first experiment...}'') We now report all parameters for our experiment in Appendix~\textcolor{red}{(?)}.
-
-(``\textit{Minor comments}) We have addressed all of the errors noticed by the reviewer, and we thank them for their careful attention.
+(``\textit{Minor comments}.'') We have addressed all of the errors noticed by the reviewer, and we thank them for their careful attention.
 
@@
 
-(\textit{``...no explicit smoothness assumption on the density function...''}) This is resolved by assuming $f(x) \geq \lambda_{\sigma}$ on the thickened set $\mc{C}_{\lambda, \sigma} = \mc{C} + B(0,\sigma)$, as in \textcolor{green}{(Chaudhuri and Dasgupta)}.
-The set $\mc{C}_{\lambda, \sigma}$ is full dimensional with a smooth boundary, and thus no smoothness assumption on $f$ is required.
+(\textit{``...no explicit smoothness assumption on the density function...''}) See our comment above; the assumption that $f(x) \geq \lambda_{\sigma}$ on the thickened set $\mc{C}_{\lambda,\sigma}$ is analogous to (more specifically, implied by) a uniform continuity condition on $f$ within $\mc{C}_{\lambda,\sigma}$.
 
 (\textit{``The bound in Theorem 5 doesn't appear to be something that can go to 0 as $n \to \infty$ and $r \to 0$...''}) This comment is correct.
-This bound---in Theorem~5 (old version), and now in Theorem~9 (new version)--- is
+This bound---in Theorem~5 (old version), and now in Theorem~12 (new version)--- is
 \begin{equation}
 \label{eqn:volume_ssd_ppr}
-\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])} \leq 30 \cdot \kappa_{\Pbb,r}(\mc{C},\delta),
+\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])} \leq 60 \cdot \kappa_{\Pbb,r}(\mc{C},\delta),
 \end{equation}
 and the right hand side will not converge to $0$ as $n \to \infty$.
-This is typical in the analysis of spectral clustering algorithms in a non-parametric statistical context~\textcolor{green}{(Shi, Schiebinger, Garcia-Trillos)}, and we make some detailed comparison between our bound and these related works after Theorem~9 (new version).
-We also confirm, both theoretically and experimentally, that indeed that the misclassification error of PPR will not go to zero as $n \to \infty$, even for some fairly well-conditioned density clusters.
+This is typical in the analysis of spectral clustering algorithms in a non-parametric statistical context~\citep{shi2009,schiebinger2015,garciatrillos19}, and we make some detailed comparison between our bound and these related works after Theorem~12 (new version).
+We also confirm, both theoretically and experimentally, that indeed the misclassification error of PPR will not go to zero as $n \to \infty$, even for some fairly well-conditioned density clusters.
 
-(``\textit{...assumptions for Theorem 6 to hold seem very strong...}'')  We would point out that Theorem~6  is, to the best of our knowledge, the first of its kind---that is, the first to show that spectral clustering can \emph{consistently} recover a geometrically-defined cluster.
-However, we agree that the assumptions are quite strong, in our revised submission we have moved this Theorem to one of our appendices, so as not to distract from our major points.
+(``\textit{...assumptions for Theorem 6 to hold seem very strong...}'')  We would point out that Theorem~6  is, to the best of our knowledge, the first of its kind---that is, the first to show that a spectral clustering method will distinguish two density clusters.
+However, we agree that the assumptions are quite strong, and in our revised submission we have moved this theorem to one of our appendices, so as not to distract from our major points.
 
@@
 
+\bibliographystyle{plainnat}
+\bibliography{../../local_spectral_bibliography}
+
 \end{document}

### 2021-12-23 neurips/rebuttal.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbb{I}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}

We thank all reviewers for their comments and feedback. We first respond to a common concern among the reviewers, before making individual responses below.

A common critique from reviewers is that the set of assumptions we impose on a given density cluster $\mathcal{C}$ are not sufficiently motivated. Our motivation is as follows: on the one hand, a commonly analyzed paradigm in nonparametric clustering is density clustering, and on the other hand many common nonparametric clustering algorithms are spectral in nature. Oftentimes, spectral clustering algorithms are intuitively thought of as identifying groups of points in connected high-density regions. However, in past theoretical studies of spectral clustering algorithms (such as Shi et al. and Schiebinger et al.), while the requirement that a cluster have high density is often implicit in the formally stated assumptions, a formal assumption of this nature is neither explicitly stated, nor is it sufficient to satisfy the required assumptions in these works. 
We start from the same basic premise that a good candidate set $\mathcal{C}$ for recovery by a spectral clustering algorithm should have high density. In our case, however, we restrict $\mathcal{C}$ to have uniformly lower bounded density by requiring it to be an upper-level set of the density function. Our goal is then to detail what \textit{other} properties a cluster should have, in addition to being a high-density set, in order for it to be a good candidate for a spectral algorithm (in our case, \textrm{PPR}).

\textbf{Response to Reviewer 1.}

[``Challenges to the proof...''] We agree that more discussion of proof techniques would be useful for the interested reader. The main two technical contributions of the work are Theorems 3 and 4, upper bounds on normalized cut and mixing time over a neighborhood graph. The main challenge in upper bounding the expected normalized cut is to upper bound the probability mass assigned to $\set{x: 0 \leq \mathrm{dist}(x,\mathcal{C}) \leq r}$, as all edges which cross the cut $\mathrm{cut}(\mathcal{C}_{\sigma}[X]; G_{n,r})$ must have (exactly) one endpoint in this set. Then, passing from an upper bound on expected normalized cut to a finite-sample bound is relatively straightforward. Upper bounding mixing time of a random walk over $\mathcal{C}_{\sigma}[X]$ is less straightforward, as it requires a \textit{uniform} lower bound on the normalized cut of subsets of $\mathcal{C}_{\sigma}[X]$. We invoke population-level results to lower bound the conductance (minimum normalized cut) of subsets of $\mathcal{C}_{\sigma}$, then rely on optimal transportation theory to relate this bound to a bound on the conductance of $\mathcal{C}_{\sigma}[X]$.

[``What type of distributional properties needed...''] We agree adding common examples would help clarify the significance of our contribution. The common nonparametric mixture model most suited to our assumptions is the mixture of uniforms. To be specific, for connected and geometrically compact but otherwise arbitrary subsets $U_1, \ldots, U_p$,  of domain $\mathcal{X}$, we would consider the density function $f(x) \propto \sum_{i = 1}^{p} \pi_i \mathbf{1}(x \in U_i) + \pi_0 \mathbf{1}(x \in \mathcal{X})$.

[``standard multi-modal densities...''] We do not believe our theory is tight in the case of gaussian mixtures. This is a consequence of the generality of our setup, where the only regularity on the density within $\mathcal{C}$ is imposed by the minimum/maximum density parameters $\lambda_{\sigma}$ and $\Lambda_{\sigma}$. More explicit assumptions about the density -- such as smoothness or unimodality -- within $\mathcal{C}$ would be needed to strengthen our theory in the GMM setup.

\textbf{Response to Reviewer 2.}

[``weakness in the experiments section...''] We will add more extensive experiments for a camera-ready version.

[``natural set of geometric conditions...''] See above.

[``restructuring and rewriting...''] We thank the reviewer for the suggestion to reorganize, including the suggestion to define well-conditioned density clusters earlier.

\textbf{Response to Reviewer 3. }

[``exact aim of this paper...''] See above. In particular, however, we note that our definition of density-based upper level sets and recovery of their $\sigma$-expansions is standard in the density clustering literature, (e.g. it matches that of Chaudhuri and Dasgupta.) We apologize for any confusion.

[``samples from an unknown distribution...''] Included in our supplement is a detailed description of our experimental setup. We would include more experimental details in our main text for a camera-ready version.

[``more than two clusters...''] Yes, the method (and theory) holds for any number of clusters, which is one of the appeals of considering a local clustering approach.

[``PPR on a graph network is not new...''] We agree with the reviewer's points re: novelty of PPR on graphs and recovery of two moons. We feel in fact that the extensive study of PPR on graphs is helpful in the study of statistical properties of PPR, as it reduces our analysis task to showing that the required graph-theoretic properties are satisfied by an appropriate neighborhood graph over point cloud data. Our two moons example was designed to show how, even in a canonical example for spectral algorithms, geometric constraints beyond merely high-density region are required for the successful recovery of one of the moons.

\end{document}

### 2021-12-23 neurips/rebuttal_neurips.tex

--- 2021-12-23 neurips/rebuttal.tex
@@
 \documentclass{article}
-\usepackage{amsmath}
-\usepackage{amsfonts, amsthm, amssymb}
-\usepackage{graphicx}
-\usepackage[colorlinks]{hyperref}
-\usepackage[parfill]{parskip}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{enumerate}
-\usepackage[shortlabels]{enumitem}
-\usepackage{fullpage}
-\usepackage{mathtools}
 
-\usepackage{natbib}
-\renewcommand{\bibname}{REFERENCES}
-\renewcommand{\bibsection}{\subsubsection*{\bibname}}
+\usepackage{neurips_2019_author_response}
 
-\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
 
-\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
-\newcommand{\Graph}{\mathcal{G}}
-\newcommand{\Reals}{\mathbb{R}}
-\newcommand{\Identity}{\mathbb{I}}
-\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
-\newcommand{\convprob}{\overset{p}{\to}}
-\newcommand{\convdist}{\overset{w}{\to}}
-\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
-\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
-\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
-\newcommand{\iset}{\mathbf{i}}
-\newcommand{\jset}{\mathbf{j}}
-\newcommand{\myexp}[1]{\exp \{ #1 \}}
-\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
-\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
-\newcommand{\ext}[1]{\widetilde{#1}}
-\newcommand{\set}[1]{\left\{#1\right\}}
-\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
-\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
-\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\newcommand{\Var}{\mathrm{Var}}
-\newcommand{\Cov}{\mathrm{Cov}}
-\newcommand{\diam}{\mathrm{diam}}
-
-\newcommand{\emC}{C_n}
-\newcommand{\emCpr}{C'_n}
-\newcommand{\emCthick}{C^{\sigma}_n}
-\newcommand{\emCprthick}{C'^{\sigma}_n}
-\newcommand{\emS}{S^{\sigma}_n}
-\newcommand{\estC}{\widehat{C}_n}
-\newcommand{\hC}{\hat{C^{\sigma}_n}}
-\newcommand{\vol}{\text{vol}}
-\newcommand{\spansp}{\mathrm{span}~}
-\newcommand{\1}{\mathbb{I}}
-
-\newcommand{\Linv}{L^{\dagger}}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\argmax}{argmax}
-
-\newcommand{\emF}{\mathbb{F}_n}
-\newcommand{\emG}{\mathbb{G}_n}
-\newcommand{\emP}{\mathbb{P}_n}
-\newcommand{\F}{\mathcal{F}}
-\newcommand{\D}{\mathcal{D}}
-\newcommand{\R}{\mathcal{R}}
-\newcommand{\Rd}{\Reals^d}
-
-%%% Vectors
-\newcommand{\thetast}{\theta^{\star}}
-
-%%% Matrices
-\newcommand{\X}{X} % no bold
-\newcommand{\Y}{Y} % no bold
-\newcommand{\Z}{Z} % no bold
-\newcommand{\Lgrid}{L_{\grid}}
-\newcommand{\Dgrid}{D_{\grid}}
-\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
-
-%%% Sets and classes
-\newcommand{\Xset}{\mathcal{X}}
-\newcommand{\Sset}{\mathcal{S}}
-\newcommand{\Hclass}{\mathcal{H}}
-\newcommand{\Pclass}{\mathcal{P}}
-
-%%% Distributions and related quantities
-\newcommand{\Pbb}{\mathbb{P}}
-\newcommand{\Ebb}{\mathbb{E}}
-\newcommand{\Qbb}{\mathbb{Q}}
-
-%%% Operators
-\newcommand{\Tadj}{T^{\star}}
-\newcommand{\dive}{\mathrm{div}}
-\newcommand{\dif}{\mathop{}\!\mathrm{d}}
-\newcommand{\gradient}{\mathcal{D}}
-\newcommand{\Hessian}{\mathcal{D}^2}
-
-%%% Misc
-\newcommand{\grid}{\mathrm{grid}}
-\newcommand{\critr}{R_n}
-\newcommand{\dx}{\,dx}
-\newcommand{\dy}{\,dy}
-\newcommand{\dr}{\,dr}
-\newcommand{\dxpr}{\,dx'}
-\newcommand{\dypr}{\,dy'}
-\newcommand{\wt}[1]{\widetilde{#1}}
-
-%%% Order of magnitude
-\newcommand{\soom}{\sim}
-
-% \newcommand{\span}{\textrm{span}}
-
-\newtheoremstyle{alden}
-{6pt} % Space above
-{6pt} % Space below
-{} % Body font
-{} % Indent amount
-{\bfseries} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{alden}
-
-\newtheoremstyle{aldenthm}
-{6pt} % Space above
-{6pt} % Space below
-{\itshape} % Body font
-{} % Indent amount
-{\bfseries} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{aldenthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{lemma}{Lemma}
-\newtheorem{example}{Example}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\newtheorem{assumption}{Assumption}
-\newtheorem{remark}{Remark}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\theoremstyle{remark}
+\usepackage{lipsum}
 
 \begin{document}
-
-We thank all reviewers for their comments and feedback. We first respond to a common concern among the reviewers, before making individual responses below.
+We thank the reviewers for their comments and feedback. We first respond to a common concern among the reviewers, before making individual responses below.
 
 A common critique from reviewers is that the set of assumptions we impose on a given density cluster $\mathcal{C}$ are not sufficiently motivated. 
-Our motivation is as follows: on the one hand, a commonly analyzed paradigm in nonparametric clustering is density clustering, and on the other hand many common nonparametric clustering algorithms are spectral in nature.
-Oftentimes, spectral clustering algorithms are intuitively thought of as identifying groups of points in connected high-density regions.
+In the statistical learning setup, it is natural to investigate the extent to which a clustering algorithm identifies ``natural clusters'' of the underlying distribution.
+%Our motivation is as follows: on the one hand, a commonly analyzed paradigm in nonparametric clustering is density clustering, and on the other hand many common nonparametric clustering algorithms are spectral in nature.
+Often, spectral clustering algorithms are intuitively thought of as identifying groups of points in connected high-density regions.
 However, in past theoretical studies of spectral clustering algorithms (such as Shi et al.
-and Schiebinger et al.), while the requirement that a cluster have high density is often implicit in the formally stated assumptions, a formal assumption of this nature is neither explicitly stated, nor is it sufficient to satisfy the required assumptions in these works.
-We start from the same basic premise that a good candidate set $\mathcal{C}$ for recovery by a spectral clustering algorithm should have high density.
+and Schiebinger et al.), the requirement that a cluster have high density is often implicit in the formally stated assumptions.
+A formal assumption of this nature is neither explicitly stated, nor is it sufficient to satisfy the required assumptions in these works.
+As a result, it is still unclear when, if ever, spectral clustering algorithms do recover high-density clusters.
+
+Spectral algorithms trade-off different considerations (connectivity and compactness) in a complex way and are able to only recover a subset of geometrically-compact density clusters (our assumptions provide precise quantification to this statement).
+In more detail, our work provides conditions on the underlying density and the target density cluster, in order for it to be a good candidate for a spectral algorithm (in our case, \textrm{PPR}).
+
+%In essence we find that geometrically-compact high-density clusters
+
+%We start from the same basic premise that a good candidate set $\mathcal{C}$ for recovery by a spectral clustering algorithm should have high density.
 In our case, however, we restrict $\mathcal{C}$ to have uniformly lower bounded density by requiring it to be an upper-level set of the density function.
-Our goal is then to detail what \textit{other} properties a cluster should have, in addition to being a high-density set, in order for it to be a good candidate for a spectral algorithm (in our case, \textrm{PPR}).
+Our goal is then to detail what \textit{other} properties a cluster should have, in addition to being a high-density set,
 
@@
 
-[``Challenges to the proof...''] We agree that more discussion of proof techniques would be useful for the interested reader.
+[``Challenges to the proof...''] We agree that more discussion of proof techniques would be useful for the interested reader and we will elaborate on this in our revision.
 The main two technical contributions of the work are Theorems 3 and 4, upper bounds on normalized cut and mixing time over a neighborhood graph.
-The main challenge in upper bounding the expected normalized cut is to upper bound the probability mass assigned to $\set{x: 0 \leq \mathrm{dist}(x,\mathcal{C}) \leq r}$, as all edges which cross the cut $\mathrm{cut}(\mathcal{C}_{\sigma}[X]; G_{n,r})$ must have (exactly) one endpoint in this set.
+The main challenge in upper bounding the expected normalized cut is to upper bound the probability mass assigned to $\{x: 0 \leq \mathrm{dist}(x,\mathcal{C}) \leq r\}$, as all edges which cross the cut $\mathrm{cut}(\mathcal{C}_{\sigma}[X]; G_{n,r})$ must have (exactly) one endpoint in this set.
 Then, passing from an upper bound on expected normalized cut to a finite-sample bound is relatively straightforward.
@@
 [``What type of distributional properties needed...''] We agree adding common examples would help clarify the significance of our contribution.
-The common nonparametric mixture model most suited to our assumptions is the mixture of uniforms.
+The common nonparametric mixture model most suited to our assumptions is the mixture of uniforms (with a background noise component).
 To be specific, for connected and geometrically compact but otherwise arbitrary subsets $U_1, \ldots, U_p$,  of domain $\mathcal{X}$, we would consider the density function $f(x) \propto \sum_{i = 1}^{p} \pi_i \mathbf{1}(x \in U_i) + \pi_0 \mathbf{1}(x \in \mathcal{X})$.
@@
 
-[``restructuring and rewriting...''] We thank the reviewer for the suggestion to reorganize, including the suggestion to define well-conditioned density clusters earlier.
+[``restructuring and rewriting...''] We thank the reviewer for the suggestion to re-organize, including the suggestion to define well-conditioned density clusters earlier.
 
@@
 
-[``exact aim of this paper...''] See above.
-In particular, however, we note that our definition of density-based upper level sets and recovery of their $\sigma$-expansions is standard in the density clustering literature, (e.g.
-it matches that of Chaudhuri and Dasgupta.) We apologize for any confusion.
+[``exact aim...''] See above.
+We also note that our definition of density upper level sets and recovery of their $\sigma$-expansions is standard in the density clustering literature (e.g.
+Chaudhuri and Dasgupta).
+We apologize for any confusion.
+
+% (e.g. it matches that of Chaudhuri and Dasgupta.)
 
 [``samples from an unknown distribution...''] Included in our supplement is a detailed description of our experimental setup.
-We would include more experimental details in our main text for a camera-ready version.
+We will include more experimental details in our main text for a camera-ready version.
 
@@
 Our two moons example was designed to show how, even in a canonical example for spectral algorithms, geometric constraints beyond merely high-density region are required for the successful recovery of one of the moons.
-
 \end{document}

### 2021-12-23 arxiv/ppr_clustering_neighborhood_graph.tex

--- 2021-09-10 jmlr/revision/ppr_clustering_neighborhood_graph.tex
@@
 \documentclass[11pt,twoside]{article}
-\usepackage[preprint]{jmlr2e}
-\usepackage{color}
 \usepackage{fancyhdr}
+\usepackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue,bookmarks=false]{hyperref}
 \usepackage{amsfonts,epsfig,graphicx}
 \usepackage{afterpage}
-\usepackage{amsmath,amssymb} 
-% \usepackage{fullpage}
+\usepackage{amsmath,amssymb,amsthm} 
+\usepackage{fullpage}
 \usepackage{epsf} 
@@
 \usepackage{amsfonts,amsmath}
-% \usepackage[sort,numbers]{natbib} 
+\usepackage[sort,numbers]{natbib} 
 \usepackage{psfrag,xspace}
@@
 
+\newtheorem{theorem}{Theorem} 
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{remark}{Remark}
+
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 \usepackage{hyperref}       % hyperlinks
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue,
-	citecolor=blue
-}
 \usepackage{url}            % simple URL typesetting
@@
 \usepackage{xcolor}
+%\usepackage{xr-hyper}
+%\usepackage{hyperref}
+%\usepackage[reqno]{amsmath}
+%\usepackage{amsfonts, amsthm, amssymb}
 \usepackage{algorithm}
 \usepackage{algorithmic}
+%\usepackage[parfill]{parskip}
 \usepackage{enumerate}
@@
 
+%%%%%% Begin Alden
 \DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
@@
 
-\ShortHeadings{PPR Clustering on Neighborhood Graphs}{Green, Balakrishnan and Tibshirani}
-\firstpageno{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% End Alden 
+\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
+
+\newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
+\newcommand{\Like}{\ensuremath{\mathcal{L}}}
+\newcommand{\Ball}[2]{\mathbb{B}_{#1}(#2)}
+\newcommand{\Complement}[1]{\overline{#1}}
+
+\newcommand{\xsam}{\ensuremath{x}}
+\newcommand{\samind}{\ensuremath{\ell}}
+\newcommand{\Xrv}{\ensuremath{X}}
+\newcommand{\Event}{\ensuremath{\mathcal{E}}}
+\newcommand{\Fevent}{\ensuremath{\mathcal{F}}}
+
+\newcommand{\usedim}{\ensuremath{d}}
+\newcommand{\mubold}{\ensuremath{\boldsymbol{\mu}}}
+\newcommand{\lambold}{\ensuremath{\boldsymbol{\lambda}}}
+\newcommand{\sep}{\ensuremath{\xi}}
+\newcommand{\mixind}{\ensuremath{i}}
+\newcommand{\mixtwo}{\ensuremath{j}}
+\newcommand{\nummix}{\ensuremath{M}}
+\newcommand{\mustar}{\ensuremath{\mu^*}}
+\newcommand{\muboldstar}{\ensuremath{\mubold^*}}
+\newcommand{\muboldt}{\ensuremath{\mubold^t}}
+
+\newcommand{\numobs}{\ensuremath{n}}
+\newcommand{\SamLike}{\ensuremath{\Like_\numobs}}
+\newcommand{\PopLike}{\ensuremath{\Like}}
+\newcommand{\Exs}{\E}
+\newcommand{\thetanew}{\ensuremath{\theta^{\text{\small{new}} }}}
+
+\newcommand{\stepsize}{\ensuremath{s}}
+
+\newcommand{\QMAT}{\ensuremath{\mathbf{Q}}} 
+\newcommand{\DMAT}{\ensuremath{\mathbf{D}}}
+
+\newcommand{\defn}{\ensuremath{: \, =}}
+\newcommand{\muboldtilde}{\ensuremath{\tilde{\mubold}}}
+
+%%% New version of \caption puts things in smaller type, single-spaced 
+%%% and indents them to set them off more from the text.
+\makeatletter
+\long\def\@makecaption#1#2{
+        \vskip 0.8ex
+        \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
+        \parindent 1.5em  %% How can we use the global value of this???
+        \dimen0=\hsize
+        \advance\dimen0 by -3em
+        \ifdim \wd\@tempboxa >\dimen0
+                \hbox to \hsize{
+                        \parindent 0em
+                        \hfil 
+                        \parbox{\dimen0}{\def\baselinestretch{0.96}\small
+                                {\bf #1.} #2
+                                %%\unhbox\@tempboxa
+                                } 
+                        \hfil}
+        \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
+        \fi
+        }
+\makeatother
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs}
-
-\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213
-	\AND
-	\name Sivaraman Balakrishnan \email siva@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213
-	\AND
-	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
-	\addr Department of Statistics and Data Science\\
-	Carnegie Mellon University\\
-	Pittsburgh, PA 15213}
-
-\maketitle
+\begin{center} {\Large{\bf{Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs}}}
+
+\vspace*{.3cm}
+
+{\large{
+\begin{center}
+Alden Green~~~~~ Sivaraman Balakrishnan~~~~~ Ryan J. Tibshirani\\
+\vspace{.2cm}
+\end{center}
+
+\begin{tabular}{c}
+Department of Statistics and Data Science \\
+Carnegie Mellon University
+\end{tabular}
+
+\vspace*{.2in}
+
+\begin{tabular}{c}
+\texttt{\{ajgreen,sbalakri,ryantibs\}@stat.cmu.edu}
+\end{tabular}
+}}
+
+\vspace*{.2in}
+
+\today
+\vspace*{.2in}
+\end{center}
 
@@
 \end{abstract}
-
-\begin{keywords}
-	graphs, spectral clustering, Personalized PageRank, density clustering, unsupervised learning
-\end{keywords}
 
@@
 The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
-We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under an Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $L$.
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $L$.
 We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
@@
 \begin{equation*}
-\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $\dist(x,\mc{C}_{\lambda,\sigma}) \leq r$.}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
 \end{equation*}
@@
 	\end{equation}
-	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
+	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
 	\begin{equation}
@@
 	\emph{Lipschitz embedding:}
-	There exists $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $L \in [1,\infty)$ such that
+	There exists a differentiable function $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $L \in [1,\infty)$ such that
 	\begin{enumerate}
@@
 \begin{equation*}
-\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 32 C_{1,\delta} \cdot \frac{\rho^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
+\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 32 C_{1,\delta} \cdot \frac{\rho^2 + \sigma^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
 \end{equation*}
@@
 	\begin{equation*}
-	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{256 C_{1,\delta}} \left(\frac{\sigma}{\rho \log(\rho/\sigma \sqrt{C_{2,\delta}})}\right)^2,
+	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{256 C_{1,\delta}} \frac{\sigma^2}{(\rho^2 + \sigma^2) \log^2(\rho/\sigma \sqrt{C_{2,\delta}})},
 	\end{equation*}
@@
 
-\bibliography{../../local_spectral_bibliography}
+\bibliographystyle{plainnat}
+\bibliography{../local_spectral_bibliography}
 
 \clearpage
+
 \appendix
-
 \input{appendix.tex}

### 2021-12-23 jmlr/final/19-1016.tex

--- 2021-09-10 jmlr/revision2/appendix.tex
@@
-\noindent The proofs of our major theorems largely consist of (at most) three modular parts.
+\documentclass[twoside,11pt]{article}
+
+%%%%%%%%% Packages %%%%%%%%%%%
+\usepackage[export]{adjustbox}
+\usepackage{subcaption}
+\usepackage[abbrvbib]{jmlr2e}
+
+%% Essentials
+\usepackage{mathtools}
+\usepackage{float}
+\usepackage{xcolor}
+\usepackage{algorithm,algorithmic}
+\usepackage[shortlabels]{enumitem}     
+\usepackage{bm}
+
+%% Beautify
+\usepackage{xspace}         % better line spacing
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\hypersetup{
+	colorlinks,
+	citecolor=blue,
+	urlcolor=blue,
+	linkcolor=blue,
+	bookmarks=false
+}
+
+%%%%%%%%% Macros %%%%%%%%%%%
+\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
+\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
+\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
+\DeclareMathAccent{\wb}{0}{mathx}{"73}
+
+\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
+\newcommand{\Graph}{\mathcal{G}}
+\newcommand{\Reals}{\mathbb{R}}
+\newcommand{\Identity}{\mathbb{I}}
+\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
+\newcommand{\convprob}{\overset{p}{\to}}
+\newcommand{\convdist}{\overset{w}{\to}}
+\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
+\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
+\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
+\newcommand{\iset}{\mathbf{i}}
+\newcommand{\jset}{\mathbf{j}}
+\newcommand{\myexp}[1]{\exp \{ #1 \}}
+\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
+\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
+\newcommand{\ext}[1]{\widetilde{#1}}
+\newcommand{\set}[1]{\left\{#1\right\}}
+\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
+\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\Var}{\mathrm{Var}}
+\newcommand{\Cov}{\mathrm{Cov}}
+\newcommand{\Xsetiam}{\mathrm{diam}}
+
+\newcommand{\emC}{C_n}
+\newcommand{\emCpr}{C'_n}
+\newcommand{\emCthick}{C^{\sigma}_n}
+\newcommand{\emCprthick}{C'^{\sigma}_n}
+\newcommand{\emS}{S^{\sigma}_n}
+\newcommand{\estC}{\widehat{C}_n}
+\newcommand{\hC}{\hat{C^{\sigma}_n}}
+\newcommand{\spansp}{\mathrm{span}~}
+\newcommand{\1}{\mathbf{1}}
+
+\newcommand{\Linv}{L^{\Xsetagger}}
+\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\argmax}{argmax}
+
+\newcommand{\emF}{\mathbb{F}_n}
+\newcommand{\emG}{\mathbb{G}_n}
+\newcommand{\emP}{\mathbb{P}_n}
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\D}{\mathcal{D}}
+\newcommand{\R}{\mathcal{R}}
+\newcommand{\Rd}{\Reals^d}
+\newcommand{\Nbb}{\mathbb{N}}
+
+%%% Vectors
+\newcommand{\thetast}{\theta^{\star}}
+\newcommand{\betap}{\beta^{(p)}}
+\newcommand{\betaq}{\beta^{(q)}}
+\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
+
+%%% Norms
+\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
+\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}
+
+%%% Matrices
+\newcommand{\X}{X} % no bold
+\newcommand{\Y}{Y} % no bold
+\newcommand{\Z}{Z} % no bold
+\newcommand{\Lgrid}{L_{\grid}}
+\newcommand{\Xsetgrid}{D_{\grid}}
+\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
+\newcommand{\Lap}{{\bf L}}
+\newcommand{\NLap}{{\bf N}}
+\newcommand{\PLap}{{\bf P}}
+
+%%% Sets and classes
+\newcommand{\Xset}{\mathcal{X}}
+\newcommand{\Sset}{\mathcal{S}}
+\newcommand{\Hclass}{\mathcal{H}}
+\newcommand{\Pclass}{\mathcal{P}}
+\newcommand{\Leb}{L}
+\newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\mbb}[1]{\mathbb{#1}}
+
+%%% Distributions and related quantities
+\newcommand{\Pbb}{\mathbb{P}}
+\newcommand{\Ubb}{\mathbb{U}}
+\newcommand{\Ebb}{\mathbb{E}}
+\newcommand{\Qbb}{\mathbb{Q}}
+\newcommand{\Ibb}{\mathbb{I}}
+
+%%% Operators
+\newcommand{\Tadj}{T^{\star}}
+\newcommand{\Xsetive}{\mathrm{div}}
+\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
+\newcommand{\gradient}{\mathcal{D}}
+\newcommand{\Hessian}{\mathcal{D}^2}
+\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
+\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}
+
+%%% Misc
+\newcommand{\grid}{\mathrm{grid}}
+\newcommand{\critr}{R_n}
+\newcommand{\Xsetx}{\,dx}
+\newcommand{\Xsety}{\,dy}
+\newcommand{\Xsetr}{\,dr}
+\newcommand{\Xsetxpr}{\,dx'}
+\newcommand{\Xsetypr}{\,dy'}
+\newcommand{\wt}[1]{\widetilde{#1}}
+\newcommand{\wh}[1]{\widehat{#1}}
+\newcommand{\ol}[1]{\overline{#1}}
+\newcommand{\spec}{\mathrm{spec}}
+\newcommand{\LE}{\mathrm{LE}}
+\newcommand{\LS}{\mathrm{LS}}
+\newcommand{\OS}{\mathrm{OS}}
+\newcommand{\PLS}{\mathrm{PLS}}
+\newcommand{\dist}{\mathrm{dist}}
+\newcommand{\vol}{\mathrm{vol}}
+\newcommand{\cut}{\mathrm{cut}}
+\newcommand{\diam}{\mathrm{diam}}
+\newcommand{\qed}{\hfill $\blacksquare$}
+
+%%% Order of magnitude
+\newcommand{\soom}{\sim}
+
+%%%%%%%%% Headings %%%%%%%%%%%
+
+\usepackage{lastpage}
+\jmlrheading{22}{2021}{1-\pageref{LastPage}}{12/19; Revised
+	9/21}{11/21}{19-1016}{Alden Green, Sivaraman Balakrishnan, and Ryan J. Tibshirani}
+\ShortHeadings{PPR Clustering on Neighborhood Graphs}{Green, Balakrishnan and Tibshirani}
+\firstpageno{1}
+
+\begin{document}
+
+\title{Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs}
+
+\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213
+	\AND
+	\name Sivaraman Balakrishnan \email siva@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Machine Learning Department\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213
+	\AND
+	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
+	\addr Department of Statistics and Data Science\\
+	Machine Learning Department\\
+	Carnegie Mellon University\\
+	Pittsburgh, PA 15213}
+
+\editor{Ingo Steinwart}
+
+\maketitle
+
+\begin{abstract}% <- trailing % for backward compatibility of style file
+	We study the Personalized PageRank (PPR) algorithm, a local spectral method for clustering, which extracts clusters using locally-biased random walks around a given seed node.
+In contrast to previous work, we adopt a classical statistical learning setup, where we obtain samples from an unknown nonparametric distribution, and aim to identify sufficiently salient clusters.
+We introduce a trio of population-level functionals---the \emph{normalized cut}, \emph{conductance}, and \emph{local spread}, analogous to graph-based functionals of the same name---and prove that PPR, run on a neighborhood graph, recovers clusters with small population normalized cut and large conductance and local spread.
+We apply our general theory to establish that PPR identifies connected regions of high density (density clusters) that satisfy a set of natural geometric conditions.
+We also show a converse result, that PPR can fail to recover geometrically poorly-conditioned density clusters, even asymptotically.
+Finally, we provide empirical support for our theory.
+\end{abstract}
+
+\begin{keywords}
+	graphs, spectral clustering, Personalized PageRank, density clustering, unsupervised learning
+\end{keywords}
+
+\section{Introduction}
+In this paper, we consider the problem of clustering: splitting a given data set into groups that satisfy some notion of within-group similarity and between-group difference.
+Our particular focus is on spectral clustering methods, a family of powerful nonparametric clustering algorithms.
+Roughly speaking, a spectral algorithm first constructs a geometric graph $G$, where vertices correspond to samples, and edges correspond to proximities between samples.
+The algorithm then estimates a feature embedding based on a (suitable) Laplacian matrix of $G$, and applies a simple clustering technique (like $k$-means clustering) in the embedded feature space.
+
+When applied to geometric graphs built from a large number of samples, global spectral clustering methods can be computationally cumbersome and insensitive to the local geometry of the underlying distribution \citep{leskovec2010,mahoney2012}.
+This has led to increased interest in \emph{local} spectral clustering algorithms, which leverage locally-biased spectra computed using random walks around some user-specified seed node.
+A popular local clustering algorithm is the Personalized PageRank (PPR) algorithm, first introduced by \citet{haveliwala2003}, and then further developed by several others \citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.
+
+Local spectral clustering techniques have been practically very successful \citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led many authors to develop supporting theory \citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case guarantees on traditional graph-theoretic notions of cluster quality (such as normalized cut and conductance).
+In contrast, in this paper we adopt a classical statistical viewpoint, and examine what the output of local clustering on a data set reveals about the underlying density $f$ of the samples.
+We establish conditions on $f$ under which PPR, when appropriately tuned and initialized inside a candidate cluster $\mc{C} \subseteq \Rd$, will approximately recover this candidate cluster.
+We pay special attention to the case where $\mc{C}$ is a \emph{density cluster} of $f$---defined as a connected component of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some $\lambda > 0$---and show precisely how PPR accounts for both geometry and density in estimating a cluster.
+
+Before giving a more detailed overview of our main results, we formally define PPR on a neighborhood graph, review some of the aforementioned worst-case guarantees, and introduce the population-level functionals that govern the behavior of local clustering in our statistical context.
+
+\subsection{PPR Clustering}
+\label{subsec:ppr_clustering}
+We start by reviewing the PPR clustering algorithm.
+Let $G = (V,E)$ be an undirected, unweighted, and connected graph.
+We denote by $A \in \Reals^{n \times n}$ the adjacency matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.
+We also denote by $D$ the diagonal degree matrix, with entries $D_{uu} := \sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
+The PPR vector $p_v = p(v,\alpha;G)$ is defined with respect to a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
+\begin{equation}
+\label{eqn:ppr_vector}
+p_v = \alpha e_{v} + (1 - \alpha) p_v W,
+\end{equation}
+where $W = (I + D^{-1}A)/2$ is the lazy random walk matrix over $G$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in position $v$ and 0 elsewhere).
+
+In practice, exactly solving the system of equations~\eqref{eqn:ppr_vector} to compute the PPR vector may be too computationally expensive.
+To address this limitation, \citet{andersen2006} introduced the \emph{$\varepsilon$-approximate} PPR vector (aPPR), which we will denote by \smash{$p_v^{(\varepsilon)}$}.
+We refer the curious reader to \citet{andersen2006} for a formal algorithmic definition of the aPPR vector, and limit ourselves to highlighting a few salient points: the aPPR vector can be computed in order $\mc{O}(1/(\varepsilon\alpha))$ time, while satisfying the following uniform error bound:
+\begin{equation}
+\label{eqn:appr_error}
+p_v(u) - \varepsilon D_{uu}\leq p_v^{(\varepsilon)}(u) \leq p_v(u), 
+\quad \text{for all $u \in V$}.
+\end{equation}
+
+Once $p_v$ or \smash{$p_v^{(\varepsilon)}$} is computed, the cluster estimate \smash{$\wh{C}$} is chosen by taking a particular sweep cut.
+For a given level $\beta > 0$, the \emph{$\beta$-sweep cut} of $p_v = (p_v(u))_{u \in V}$ is
+\begin{equation}
+\label{eqn:sweep_cuts}
+S_{\beta,v} := \set{u \in V: \frac{p_v(u)}{D_{uu}} > \beta}.
+\end{equation}
+To define \smash{$\wh{C}$}, one computes $S_{\beta,v}$ over all \smash{$\beta \in (L, U)$} (where the range $(L,U)$ is user-specified), and then outputs the cluster estimate \smash{$\wh{C} = S_{\beta^*,v}$} with minimum normalized cut.
+For a set $C \subseteq V$ with complement $C^c = V \!\setminus\!
+C$, the \emph{cut} and \emph{volume} are respectively,
+\begin{equation}
+\label{eqn:cut_volume}
+\cut(C;G) := \sum_{u \in C} \sum_{v \in C^c}
+\1\{(u,v) \in E\},~~ \vol(C; G) := \sum_{u \in C}  \sum_{v \in V} \1\{(u,v) \in E\},
+\end{equation}
+and the \emph{normalized cut} of $C$ is
+\begin{equation}
+\label{eqn:normalized_cut}
+\Phi(C; G) := \frac{\cut(C;G)}{\min \set{\vol(C; G), \vol(C^c; G)}}.
+\end{equation}
+
+\subsection{Worst-Case Guarantees for PPR Clustering}
+As mentioned, most analyses of local clustering have focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
+For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut $\Phi(\wh{C};G)$ is upper bounded by (a constant times)  $\sqrt{\Phi(C;G)}$.
+\cite{zhu2013} build on this: they introduce a second functional, the \emph{conductance} $\Psi(G)$, defined as
+\begin{equation}
+\label{eqn:conductance}
+\Psi(G) := \min_{S \subseteq V} \Phi(S;G),
+\end{equation}
+and show that if $\Phi(C;G)$ is much smaller than $\Psi(G[C])^2$---where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$--- then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
+Our own analysis builds on that of~\cite{zhu2013}, and we present a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
+For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\Pbb$, the graph $G$ is a random neighborhood graph formed from the samples, and the candidate cluster is a set $\mc{C} \subseteq \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
+
+\subsection{PPR on a Neighborhood Graph}
+\label{subsec:ppr_neighborhood_graph}
+We now formally describe the statistical setting in which we operate, as well as the method we will study: PPR on a neighborhood graph.
+Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$.
+We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ .
+For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the Euclidean norm.
+Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate \smash{$\wh{C} \subseteq X$}.
+The precise algorithm is summarized in Algorithm~\ref{alg:ppr}.
+
+\begin{algorithm}
+	\caption{PPR on a neighborhood graph}
+	\label{alg:ppr}	
+	{\bfseries Input:} data $X=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
+	parameter $\alpha \in [0,1]$, seed $v \in X$, sweep cut range $(L,U)$. \\     
+	{\bfseries Output:} cluster estimate $\wh{C} \subseteq V$.
+	\begin{algorithmic}[1]
+		\STATE Form the neighborhood graph $G_{n,r}$.
+		\STATE Compute the PPR vector $p_v=p(v, \alpha; G_{n,r})$ as in
+		\eqref{eqn:ppr_vector}.  
+		\STATE Compute sweep cuts $S_{\beta}$ as in \eqref{eqn:sweep_cuts}, for each $\beta \in (L,U)$.\footnotemark 
+		\STATE Return \smash{$\wh{C} = S_{\beta^*}$}, where  
+		$$
+		\beta^* = \argmin_{\beta \in (L,U)}~ \Phi(S_{\beta}; G_{n,r}).
+		$$
+	\end{algorithmic}
+\end{algorithm}
+\footnotetext{Technically speaking, for each $\beta \in (L,U) \cap \{p_v(u)/D_{uu}: u \in V\}$.}
+
+\subsection{Cluster Accuracy}
+We need a metric to assess the accuracy with which $\wh{C}$ estimates the candidate cluster $\mc{C}$.
+One commonly used metric is the misclassification error, i.e., the size of the symmetric set difference between \smash{$\wh{C}$} and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}.
+We will consider a related metric, the volume of the symmetric set difference, which weights misclassified points according to their degree in $G_{n,r}$.
+To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$.
+
+\begin{definition}
+	\label{def:volume_symmetric_set_difference}
+	For an estimator \smash{$\wh{C} \subseteq X$} and a set $\mc{C} \subseteq \Rd$, their symmetric set difference is  
+	\begin{equation*}
+	\wh{C} \vartriangle \mc{C}[X] :=
+	\bigl(\wh{C} \setminus \mc{C}[X]\bigr) \cup
+	\bigl(\mc{C}[X] \setminus \wh{C}\bigr).
+	\end{equation*}
+	Furthermore, we denote the volume of the symmetric set difference by 
+	$$
+	\Delta(\wh{C}, \mc{C}[X]) := \vol_{n,r}(\wh{C} \vartriangle \mc{C}[X]). 
+	$$
+\end{definition}
+
+\subsection{Population Normalized Cut, Conductance, and Local Spread}
+Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and the local spread $s_{\Pbb,r}(\mc{C})$---which we will use to upper bound the volume of the symmetric set difference \smash{$\Delta(\wh{C},\mc{C}[X])$} with high probability.
+
+Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e., let
+\begin{equation*}
+\mathrm{cut}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\mc{C}^c} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),~~ \mathrm{vol}_{\Pbb,r}(\mc{C}) := \int_{\mc{C}} \int_{\Rd} \1\{\|x - y\| \leq r\} \,d\Pbb(y) \,d\Pbb(x),
+\end{equation*}
+where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ be the expected degree of $x$ in $G_{n,r}$. 
+\begin{definition}[Population normalized cut]
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$, and radius $r > 0$, the \emph{population normalized cut} is
+	\begin{equation}
+	\label{eqn:population_normalized_cut}
+	\Phi_{\Pbb,r}(\mc{C}) := \frac{\mathrm{cut}_{\Pbb,r}(\mc{C})}{\min\{\mathrm{vol}_{\Pbb,r}(\mc{C}), \mathrm{vol}_{\Pbb,r}(\mc{C}^c)\}}.
+	\end{equation}
+\end{definition}
+
+Let \smash{$\wt{\Pbb}(\cdot) = \Pbb(\cdot|x \in \mc{C})$} be the conditional distribution of $x$, i.e., let \smash{$\wt{\Pbb}(\mc{S}) = \wt{\Pbb}(\mc{S} \cap \mc{C})/\wt{\Pbb}(\mc{C})$} for measurable sets $\mc{S} \subseteq \Rd$.
+
+\begin{definition}[Population conductance]
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population conductance} is
+	\begin{equation}
+	\label{eqn:population_conductance}
+	\Psi_{\Pbb,r}(\mc{C}) = \inf_{\mc{S} \subseteq \mc{C}} \Phi_{\wt{\Pbb},r}(\mc{S}).
+	\end{equation}
+\end{definition}
+
+\begin{definition}[Population local spread]
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population local spread} is
+	\begin{equation}
+	\label{eqn:local_spread}
+	s_{\Pbb,r}(\mc{C}) := \min_{x \in \mc{C}} \biggl\{\frac{\bigl(\deg_{\wt{\Pbb},r}(x)\bigr)^2}{\vol_{\wt{\Pbb},r}(\mc{C})} \biggr\},
+	\end{equation}
+\end{definition}
+
+It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
+Indeed, these functionals are the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities can be used to upper bound the volume of the symmetric set difference.
+For this reason, similar population-level functionals are used by \cite{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
+We will comment more on the relationship between these works and our own results in Section~\ref{subsec:related_work}.
+
+The role played by $s_{\Pbb,r}(\mc{C})$ is somewhat less obvious.
+For now, we mention only that it plays an essential part in obtaining tight bounds on the mixing time of a particular random walk that is closely related to the PPR vector, and defer further discussion until later in Section~\ref{sec:ub_symmetric_set_difference}.
+
+\subsection{Main Results}
+We now informally state our two main upper bounds, regarding the recovery of a generic cluster $\mc{C}$, and a density cluster $\mc{C}_{\lambda}$.
+Theorem~\ref{thm:volume_ssd_ub_informal} informally summarizes the first of our main results (formally stated in Theorem~\ref{thm:volume_ssd_ub}) regarding the recovery of a generic cluster $\mc{C}$.
+\begin{theorem}[Informal]
+	\label{thm:volume_ssd_ub_informal}
+	If $\mc{C} \subseteq \Rd$ and $\Pbb$ satisfy appropriate regularity conditions, and Algorithm~\ref{alg:ppr} is initialized properly with respect to $\mc{C}$, then for all sufficiently large $n$, with high probability it holds that
+	\begin{equation*}
+	\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq c \cdot\Phi_{\Pbb,r}(\mc{C}) \cdot  \biggl(\frac{\log(1/s_{\Pbb,r}(\mc{C}))}{\Psi_{\Pbb,r}(\mc{C})}\biggr)^2.
+	\end{equation*}
+\end{theorem}
+
+(Above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put more succinctly, we find that \smash{$\Delta(\wh{C},\mc{C}[X])$} is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C})))^2$.
+To the best of our knowledge, this gives the first population-level guarantees for local clustering in the nonparametric statistical context.
+
+Next, Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
+For reasons that we explain later in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
+The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $M$.
+We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$:
+\begin{equation*}
+0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\text{for all $x \in \mc{C}_{\lambda,\sigma}$},
+\end{equation*}
+and additionally satisfies the following low-noise condition:
+\begin{equation*}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\text{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
+\end{equation*}
+(Here $\dist(x,\mc{C}) := \inf_{y \in \mc{C}} \|y - x\|$.) 
+\begin{theorem}[Informal]
+	\label{thm:density_cluster_volume_ssd_ub_informal}
+	If $\mc{C}_{\lambda} \subseteq \Rd$ is a $\lambda$-density cluster of a distribution $\Pbb$, which satisfies appropriate regularity conditions, and Algorithm~\ref{alg:ppr} is initialized properly with respect to $\mc{C}_{\lambda,\sigma}$, then for all sufficiently large $n$, with high probability it holds that
+	\begin{equation*}
+	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
+	\end{equation*}
+\end{theorem}
+
+The above result reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
+Here $M$, $\rho$, and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
+Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$, and $\theta$ measure whether the density $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside of it) or poorly conditioned (vice versa).
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} says that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---meaning, $M^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---meaning, $\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
+
+\subsection{Related Work}
+\label{subsec:related_work}
+We now summarize some related work (in addition to the background material already given above), regarding the theory of spectral clustering, and of density cluster recovery.
+
+\subsubsection{Spectral Clustering} 
+In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
+In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating back to \citet{mcsherry2001} who gives conditions under which the entire community structure can be recovered.
+In more recent work, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these results to the sparse (low average degree) regime.
+Relatedly, \citet{clauset08,balakrishnan2011,li2018} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+The framework we consider, in which nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
+
+In general, the study of spectral algorithms on neighborhood graphs has been focused on establishing asymptotic convergence of eigenvalues and eigenvectors of certain sample objects to the eigenvalues and eigenfunctions of corresponding limiting operators.
+\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
+\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood graph of fixed radius.
+\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime where the radius $r \to 0$ as $n \to \infty$.
+
+These results are of fundamental importance.
+However, they remain silent on the following natural question: do the spectra of these continuum operators induce a partition of the sample space which is ``good'' in some sense?
+\citet{shi2009,schiebinger2015,garciatrillos19,hoffmann2019} address this question, showing that spectral algorithms will recover the latent labels in certain well-conditioned nonparametric mixture models.
+These works are probably the most similar to our own: the conditioning of these mixture models depends on population-level functionals resembling the population normalized cut and conductance introduced above, and the resulting bounds on the error of spectral clustering are comparable to those we establish in Theorem~\ref{thm:volume_ssd_ub}.
+However, these results focus on global rather than local methods, and impose global rather than local conditions on $\Pbb$.
+Moreover, they do not explicitly consider recovery of density clusters, which is an important concern of our work.
+We comment further on the relationship between our results and these works after Theorem~\ref{thm:volume_ssd_ub}.
+
+\subsubsection{Density Clustering} 
+For a given threshold $\lambda \in (0,\infty)$, we denote by \smash{$\mbb{C}_f(\lambda)$} the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
+In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mbb{C}_{f}(\lambda)$.
+By now, density clustering, and the related problem of level-set estimation, have been thoroughly studied.
+For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and \citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider estimation of the cluster tree $\{\mbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
+
+We emphasize that our goal is not to improve on these results, nor is it to offer a better algorithm for density clustering.
+Indeed, seen as a density clustering algorithm, PPR has none of the optimality guarantees found in the aforementioned works.
+Rather, we hope to better understand the implications of our general theory by applying it within an already well-studied framework.
+We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mbb{C}_f(\lambda)$.
+
+\subsection{Organization}
+We now outline the rest of the paper.
+\begin{itemize}
+	\item In Section~\ref{sec:ub_symmetric_set_difference}, we derive bounds on the error of PPR as a function of sample normalized cut, conductance, and local spread.
+We then show that under certain conditions the sample normalized cut, conductance, and local spread are close to their population-level counterparts, with high probability for sufficient number of samples.
+As a result, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} purely in terms of these population-level functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
+We derive bounds on the population normalized cut, conductance, and local spread of the density cluster, which depend on $\lambda$ as well as some other natural parameters.
+This leads to a bound on the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster is provably large.
+	\item In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
+\end{itemize}
+
+\section{Recovery of a Generic Cluster with PPR}
+\label{sec:ub_symmetric_set_difference}
+
+In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on the volume of the symmetric set difference \smash{$\Delta(\wh{C}, \mc{C}[X])$}, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$.
+We build to this theorem slowly, giving new structural results in two distinct directions.
+First, we build on some previous work (mentioned in the introduction) to relate \smash{$\Delta(\wh{C}, \mc{C}[X])$} to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s(G_{n,r}[\mc{C}[X]])$.
+Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues with high probability.
+
+\subsection{The Fixed Graph Case}
+\label{subsec:ppr_cluster_recovery_fixed_graph}
+When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subseteq V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate \smash{$\wh{C}$} and candidate cluster $C$.
+Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in the Appendix.
+Nevertheless, to be clear the essential idea of Lemma~\ref{lem:zhu} is no different than that of~\cite{zhu2013}, and we do not claim any novelty.}
+
+In their most general form, the results of~\citet{zhu2013} depend on the mixing time of a lazy random walk over the induced subgraph $G[C]$.
+The \emph{mixing time} of a lazy random walk over a graph $G$ is
+\begin{equation}
+\label{eqn:mixing_time}
+\tau_{\infty}(G) := \min\set{ t: \frac{{\pi}(u) - {q}_{v}^{(t)}(u)}
+	{{\pi}(u)} \leq \frac{1}{4}, \; \text{for all $u,v \in V$}};
+\end{equation}
+here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ initialized at node $v$ and run for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+
+\begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
+	\label{lem:zhu}
+	For a set $C \subseteq V$, suppose that
+	\begin{equation}
+	\label{eqn:zhu_condition}
+	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}.
+	\end{equation}
+	Then there exists a set $C^g \subseteq C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
+	\begin{equation}
+	\label{eqn:zhu_ub}
+	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
+	\end{equation}
+\end{lemma}
+The upper bound in~\eqref{eqn:zhu_ub} does not obviously depend on the conductance $\Psi(G[C])$.
+However, as \cite{zhu2013} point out, letting $\pi_{\min}(G) := \min_{u \in V}\{\pi(u)\}$, it follows from Cheeger's inequality~\citep{chung1997} that
+\begin{equation}
+\label{eqn:mixing_time_cheeger}
+\tau_{\infty}(G) \leq \frac{\log(1/\pi_{\min}(G))}{\Psi(G)^2}.
+\end{equation}
+Therefore, setting (for instance) \smash{$\alpha = \frac{\Psi(G[C])^2}{2\log(1/\pi_{\min}(G))}$} and \smash{$\wh{C} = S_{\beta_0,v}$} for \smash{$\beta_0 = \frac{1}{5 \vol(C;G)}$}, we obtain from~\eqref{eqn:zhu_ub} that
+\begin{equation}
+\label{eqn:zhu_ub2}
+\frac{\vol(C \vartriangle \wh{C};G)}{\vol(C; G)} \leq 60\frac{\Phi(C;G) \log\bigl( 1/\pi_{\min}(G[C])\bigr)}{\Psi(G[C])^2}.
+\end{equation}
+
+\subsection{Improved Bounds on Mixing Time} 
+\label{subsec:mixing_time}
+Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subseteq \Rd$.
+Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on \smash{$\Delta(\wh{C};\mc{C}[X])$} that depends only on $\Pbb$ and $\mc{C}$.
+Unfortunately, however, there is a catch: when the graph is $G = G_{n,r}$ and the candidate cluster is $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}(G_{n,r}[\mc{C}[X]]) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, which turns~\eqref{eqn:zhu_ub2} into a vacuous upper bound whenever the number of samples is sufficiently large.
+
+To address this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on the mixing time in~\eqref{eqn:mixing_time_cheeger}.
+Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the graph local spread, defined as
+\begin{equation*}
+s(G) := d_{\min}(G) \cdot \pi_{\min}(G),
+\end{equation*}
+for $d_{\min}(G) = \min_{u \in V}\bigl\{\deg(u;G)\bigr\}$, and likewise $d_{\max}(G) = \max_{u \in V}\bigl\{\deg(u;G)\bigr\}$. Notice that $s(G) \geq \pi_{\min}(G)$.
+\begin{proposition}
+	\label{prop:pointwise_mixing_time}
+	Assume $d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$. Then,
+	\begin{equation}
+	\label{eqn:pointwise_mixing_time}
+	\tau_{\infty}(G) \leq \frac{17}{\ln(2)} \biggl(\frac{\ln\bigl(32/s(G)\bigr)}{\Psi(G)}\biggr)^2.
+	\end{equation}
+\end{proposition}
+
+While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (provided that the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful for geometric graphs: when $G = G_{n,r}[\mc{C}[X]]$ for a fixed radius $r > 0$, we have $d_{\min}(G_{n,r}[\mc{C}[X]]) \asymp n$, and thus $s(G_{n,r}[\mc{C}[X]]) \asymp 1$.
+We give a precise upper bound on $s(G_{n,r}[\mc{C}[X]])$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
+
+The local spread $s(G)$ plays an intuitive role in the analysis of mixing time.
+Indeed, in any graph $G$ sufficiently small sets are expanders---that is, if a set $R \subseteq V$ has cardinality less than the minimum degree, the normalized cut $\Phi(R;G)$ will be much larger than the conductance $\Psi(G)$.
+As a consequence, a random walk over $G$ will rapidly mix over all small sets $R$, and in our analysis of the mixing time we may therefore ``pretend'' that the random walk was given a warm start over a larger set $S$.
+The local spread $s(G)$ simply delineates small sets $R$ from larger sets $S$.
+Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a much more intricate analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
+
+\subsection{Sample-to-Population Results}
+\label{subsec:sample_to_population}
+In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, conductance, and local spread in terms of their population-level analogues.
+To establish these bounds, we impose the following regularity conditions on \smash{$\wt{\Pbb}$} and $\mc{C}$.
+\begin{enumerate}[label=(A\arabic*)]
+	\item 
+	\label{asmp:bounded_density} 
+	The distribution \smash{$\wt{\Pbb}$} has a density \smash{$\wt{f}: \mc{C} \to (0,\infty)$} with respect to Lebesgue measure. There exist $0 < f_{\min} \leq f_{\max} < \infty$ for which
+	\begin{equation*}
+	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}.
+	\end{equation*}
+	For convenience, we will assume $f_{\min} \leq 1$ and $f_{\max} \geq 1$.
+	\item 
+	\label{asmp:domain} 
+	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set, and for $d \geq 2$, it has a Lipschitz boundary $\partial \mc{C}$, meaning it is locally the graph of a Lipschitz function (e.g., see Definition 9.57 of~\cite{leoni2017}).
+\end{enumerate}
+
+In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$, $\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
+We explicitly keep track of all constants in our proofs.
+
+\begin{proposition}
+	\label{prop:sample_to_population_1}
+	Fix $\delta \in (0,1/3)$. Suppose \smash{$\wt{\Pbb}$} and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
+	\begin{itemize}
+		\item With probability at least $1 - 3\exp\{-b_1\delta^2n\}$,
+		\begin{equation}
+		\label{eqn:sample_to_population_normalized_cut}
+		\Phi_{n,r}(\mc{C}[X]) \leq (1 + 3\delta) \Phi_{\Pbb,r}(\mc{C}).
+		\end{equation}
+		\item For any $n \in \mbb{N}$ for which 
+		\begin{equation}
+		\label{eqn:sample_to_population_local_spread_sample_complexity}
+		\frac{1}{n} \leq \delta \cdot \frac{2\Pbb(\mc{C})}{3},
+		\end{equation}
+		the following inequality holds with probability at least \smash{$1 - (n + 2)\exp\{-b_2\delta^2n\}$}:
+		\begin{equation}
+		\label{eqn:sample_to_population_local_spread}
+		s_{n,r}(\mc{C}[X]) \geq (1 - 4\delta) s_{\Pbb,r}(\mc{C}).
+		\end{equation}
+	\end{itemize}
+\end{proposition}
+Let $p_d := 1/2$ if $d = 1$, $p_d := 3/4$ if $d = 2$, and otherwise $p_d := 1/d$ for $d \geq 3$. 
+\begin{proposition}
+	\label{prop:sample_to_population_2}
+	Fix $\delta \in (0,1/2)$. Suppose \smash{$\wt{\Pbb}$} and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. For any $n \in \mbb{N}$ satisfying
+	\begin{equation}
+	\label{eqn:sample_to_population_conductance_sample_complexity}
+	B_1 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \delta,
+	\end{equation}
+	the following inequality holds with probability at least $1 - B_2/n - (n + 1)\exp\{-b_3n\}$:
+	\begin{equation}
+	\label{eqn:sample_to_population_conductance}
+	\Psi_{n,r}(\mc{C}[X]) \geq (1 - 2\delta) \Psi_{\Pbb,r}(\mc{C}).
+	\end{equation}
+\end{proposition}
+
+A note on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$, and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
+To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}(G_{n,r}[\mc{C}[X]])$, but otherwise the proof is similarly straightforward.
+
+On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
+Our proof relies on the recent results of \citet{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\Pbb_n$ and $\Pbb$.
+For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citet{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
+
+\subsection{Cluster Recovery}
+\label{subsec:cluster_recovery}
+As is typical in the local clustering literature, our algorithmic results will be stated with respect to specific ranges of each of the user-specified
+parameters. In particular, for $\delta \in (0,1/4)$ and a candidate cluster $\mc{C} \in \Rd$, we require that some of the tuning parameters of Algorithm~\ref{alg:ppr} be chosen within specific ranges,
+
+\begin{equation}
+\label{eqn:initialization}
+\begin{aligned}
+& \alpha \in \Bigl[(1 - 4\delta)^2, (1 - 2\delta)^2\Bigr) \cdot
+\frac{\alpha_{\Pbb,r}(\mc{C},\delta)}{2} \\
+& (L,U) \subseteq \Bigl(\frac{1}{5(1 + 2\delta)},\frac{1}{5(1 + \delta)}\Bigr) \cdot 
+\frac{1}{n(n - 1)\vol_{\Pbb,r}(\mc{C})},
+\end{aligned}  
+\end{equation}
+where
+\begin{equation}
+\label{eqn:alpha_initialization}
+\alpha_{\Pbb,r}(\mc{C},\delta) := \frac{\ln(2)}{17} \cdot \frac{\Psi_{\Pbb,r}^2(\mc{C})}{\ln^2\Bigl(\frac{32}{(1 - 4\delta)s_{\Pbb,r}(\mc{C})}\Bigr)}.
+\end{equation}
+
+\begin{definition}
+	When the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
+\end{definition}
+
+Of course, in practice it is not feasible to set tuning parameters based on the underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$.
+Typically, one runs PPR over some range of tuning parameter values and selects the cluster which has the smallest normalized cut.
+
+By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
+To ease presentation, we introduce a \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
+\begin{equation}
+\label{eqn:condition_number}
+\kappa_{\Pbb,r}(\mc{C},\delta) := \frac{(1 + 3\delta)(1+2\delta)}{(1 - 4\delta)^2(1 - \delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C})}{\alpha_{\Pbb,r}(\mc{C},\delta)}.
+\end{equation}
+
+\begin{theorem}
+	\label{thm:volume_ssd_ub} 
+	Fix $\delta \in (0,1/4)$.
+Suppose $\wt{\Pbb}$ and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
+Then for any $n \in \mbb{N}$ which satisfies~\eqref{eqn:sample_to_population_local_spread_sample_complexity}, \eqref{eqn:sample_to_population_conductance_sample_complexity}, and
+	\begin{equation}
+	\label{eqn:volume_ssd_ub_sample_complexity}
+	\frac{(1 + \delta)}{(1 - \delta)^4} \cdot B_3 \leq n,
+	\end{equation} 
+	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X]),
+	$$ 
+	such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}[X]$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	\begin{equation}
+	\label{eqn:volume_ssd_ub}
+	\frac{\Delta(\wh{C};\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} \leq 60 \cdot \kappa_{\Pbb,r}(\mc{C},\delta).
+	\end{equation}
+\end{theorem}
+
+We now make some remarks.
+\begin{itemize}
+	\item It is useful to compare Theorem~\ref{thm:volume_ssd_ub} with what is already known regarding \emph{global} spectral clustering in the context of nonparametric statistics.
+\cite{schiebinger2015} consider the following variant of spectral clustering: first embed the data $X$ into $\Reals^k$ using the bottom $k$ eigenvectors of the degree-normalized Laplacian $I - D^{-1/2}AD^{-1/2}$, and then partition the embedded data into estimated clusters \smash{$\wh{C}_1,\ldots,\wh{C}_k$} using $k$-means clustering.
+They derive error bounds on the misclassification error that depend on a difficulty function $\varphi(\Pbb)$.
+In our context, where the goal is to successfully distinguish $\mc{C}$ and $\mc{C}^c$, thus where $k = 2$, this difficulty function is roughly
+	\begin{equation}
+	\label{eqn:schiebinger}
+	\varphi(\Pbb) \approx \sqrt{\Phi_{\Pbb,r}(\mc{C})} \cdot \max\biggl\{ \frac{1}{\Psi_{\Pbb,r}(\mc{C})^2}; \frac{1}{\Psi_{\Pbb,r}(\mc{C}^c)^2}\biggr\}.
+	\end{equation}
+	We point out two ways in which~\eqref{eqn:volume_ssd_ub} is a tighter bound than~\eqref{eqn:schiebinger}.
+First,~\eqref{eqn:schiebinger} depends on $\Psi_{\Pbb,r}(\mc{C}^c)$ in addition to $\Psi_{\Pbb,r}(\mc{C})$, and is thus a useful bound only if $\mc{C}^c$ and $\mc{C}$ are both internally well-connected.
+In contrast~\eqref{eqn:volume_ssd_ub} depends only on $\Psi_{\Pbb,r}(\mc{C})$, and is thus a useful bound if $\mc{C}$ has small conductance, regardless of the conductance of $\mc{C}^c$.
+This is intuitive: PPR is a local rather than global algorithm, and as such the analysis requires only local rather than global conditions.
+Second,~\eqref{eqn:schiebinger} depends on \smash{$\sqrt{\Phi_{\Pbb,r}(\mc{C})}$} rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citet{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
+Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$, which is due to the locally-biased nature of the PPR algorithm, and does not appear in~\eqref{eqn:schiebinger}.
+
+	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$ the 
+	application of \eqref{eqn:appr_error} within the proof of Theorem
+	\ref{thm:volume_ssd_ub} leads to an analogous result which holds for the aPPR vector \smash{$p_v^{(\varepsilon)}$}.
+We formally state and prove this fact in Appendix~\ref{apdx:appr_misclassification_error}.
+\end{itemize}
+
+\section{Recovery of a Density Cluster with PPR}
+\label{sec:ppr_density_cluster}
+We now apply the general theory established in the last section to the special case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster---that is, a connected component of the upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
+In Section~\ref{sec:lower_bound}, we also derive a lower bound, giving a ``hard problem'' for which PPR will provably fail to recover a density cluster.
+Together, these results can be summarized as follows: PPR recovers a density cluster $\mc{C}_{\lambda}$ if and only if both $\mc{C}_{\lambda}$ and $f$ are well-conditioned, meaning that $\mc{C}_{\lambda}$ is not too long and thin, and that $f$ is approximately uniform inside $\mc{C}_{\lambda}$ while satisfying a low-noise condition near its boundary.
+
+\subsection{Recovery of Well-Conditioned Density Clusters}
+\label{subsec:recovery_well-conditioned_density_clusters}
+
+All results on density clustering assume the density $f$ satisfies some regularity conditions.
+A basic requirement is the need to avoid clusters which contain arbitrarily thin bridges or spikes, or more generally clusters which can be disconnected by removing a subset of (Lebesgue) measure $0$, and thus may not be resolved by any finite number of samples.
+To rule out such problematic clusters, we follow the approach of~\cite{chaudhuri2010}, who assume the density is lower bounded on a thickened version of $\mc{C}_{\lambda}$, defined as $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \dist(x,\mc{C}) < \sigma\}$ for a given $\sigma > 0$.
+Regardless of the dimension of $\mc{C}_{\lambda}$, the set $\mc{C}_{\lambda,\sigma}$ is full dimensional.
+Under typical uniform continuity conditions, the requirement that the density be lower bounded over $\mc{C}_{\lambda,\sigma}$ will be satisfied.
+Such continuity conditions can be weakened (see for instance \citet{rinaldo2010,steinwart2015}) but we do not pursue the matter further.
+
+In summary, our goal is to obtain upper bounds on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}, for some fixed $\lambda$ and $\sigma > 0$.
+We have already derived upper bounds on the symmetric set difference of \smash{$\wh{C}$} and a generic cluster $\mc{C}$ that depend on some population-level functionals of $\mc{C}$.
+What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
+To carry out this analysis, we will need to impose some conditions, and for the rest of this section we will assume the following.
+
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{2}
+	\item
+	\label{asmp:lambda_bounded_density}
+	\emph{Bounded density within cluster:} There exist constants
+	$0<\lambda_{\sigma}< \Lambda_{\sigma}<\infty$ such that 
+	$$
+	\lambda_{\sigma} \leq \inf_{x \in \mc{C}_{\lambda,\sigma}} f(x) \leq \sup_{x \in \mc{C}_{\lambda,\sigma}} f(x)
+	\leq \Lambda_{\sigma}.
+	$$
+
+	\item 
+	\label{asmp:low_noise_density}
+	\emph{Low-noise density:} There exist $\theta \in (0,\infty)$ and $\gamma \in
+	[0,1]$ such that for any $x \in \Rd$ with $0 < \dist(x, \mc{C}_{\lambda,\sigma}) \leq \sigma$,     
+	$$
+	\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}.  
+	$$
+	Roughly, this assumption ensures that the density decays sufficiently quickly
+	as we move away from the target cluster $\mc{C}_{\lambda,\sigma}$, and is a standard assumption in the level-set estimation literature (see for instance \citet{singh2009}).
+
+	\item
+	\label{asmp:embedding}
+	\emph{Lipschitz embedding:}
+	There exists a differentiable function $g: \Rd \to \Rd$, $\rho \in (0,\infty)$ and $M \in [1,\infty)$ such that
+	\begin{enumerate}
+		\item $\mc{C}_{\lambda,\sigma} = g(\mc{K})$, for a convex set $\mc{K} \subseteq \Rd$ with $\mathrm{diam}(\mc{K}) = \sup_{x,y \in \mc{K}}\|x - y\| \leq \rho < \infty$;
+		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x;$ and 
+		\item for some $M \geq 1$,   
+		$$
+		\|g(x) - g(y)\| \leq M \|x - y\| ~	\text{for all $x,y \in \mc{K}$}. 
+		$$
+	\end{enumerate}
+	Succinctly, we assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set with finite
+	diameter under a measure preserving, Lipschitz transformation. 
+\end{enumerate}
+
+\emph{For convenience only}, we will also make the following assumption.
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{5}
+	\item
+	\label{asmp:bounded_volume}
+	\emph{Bounded volume:}
+	The volume of $\mc{C}_{\lambda,\sigma}$ is no more than half the total volume of $\Rd$:
+	$$
+	\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma}^c). 
+	$$
+	This assumption implies that the normalized cut of $\mc{C}_{\lambda,\sigma}$ will be equal to the ratio of $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ to $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
+\end{enumerate}
+
+\subsubsection{Normalized Cut, Conductance, and Local Spread of a Density Cluster} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
+These bounds depend on the various geometric parameters just introduced.
+\begin{lemma}
+	\label{lem:density_cluster_local_spread}
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma},\Lambda_{\sigma},\rho$ and $M$. Then,
+	\begin{equation}
+	\label{eqn:density_cluster_local_spread}
+	s_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \frac{1}{4} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \cdot \biggl(\frac{2r}{\rho}\biggr)^{d} \cdot \biggl(1 - \frac{r}{\sigma} \sqrt{\frac{d + 2}{2\pi}}\biggr).
+	\end{equation}
+\end{lemma}
+
+\begin{proposition}
+	\label{prop:density_cluster_normalized_cut}
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density},~\ref{asmp:low_noise_density} and~\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta$, and $\gamma$, and additionally that $0 < r \leq \frac{\sigma}{4d}$.
+Then,
+	\begin{equation}
+	\label{eqn:density_cluster_normalized_cut}
+	\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \leq \frac{16}{9} \cdot \frac{dr}{\sigma} \cdot \frac{\lambda\Bigl(\lambda_{\sigma} - \theta \frac{r^{\gamma}}{\gamma + 1}\Bigr)}{\lambda_{\sigma}^2}.
+	\end{equation}
+\end{proposition}
+
+\begin{proposition}
+	\label{prop:density_cluster_conductance}
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $M$. Then,
+	\begin{equation}
+	\label{eqn:density_cluster_conductance}
+	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho M}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho M \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}.
+	\end{equation}
+\end{proposition}
+
+Some remarks are in order.
+\begin{itemize}
+	\item We prove Proposition~\ref{prop:density_cluster_normalized_cut} by separately upper bounding $\cut_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$ and lower bounding the volume $\vol_{\Pbb,r}(\mc{C}_{\lambda,\sigma})$.
+Of these two bounds, the trickier to prove is the upper bound on the cut, which involves carefully estimating the probability mass of thin tubes around the boundary of $\mc{C}_{\lambda,\sigma}$.
+	\item Proposition~\ref{prop:density_cluster_conductance} is proved in a completely different way.
+The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g., \cite{lovasz1990} or \cite{dyer1991b}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
+	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
+	\item There is some interdependence between $M$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
+	non-essential. However, it is not possible to eliminate condition \ref{asmp:embedding} without incurring an additional factor of at least
+	$(\rho/\sigma)^d$ in \eqref{eqn:density_cluster_conductance}, achieved, for
+	instance, when $\mc{C}_{\lambda,\sigma}$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
+In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $M$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
+\end{itemize}
+
+Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}.
+In what follows, $C_{1,\delta},C_{2,\delta},\ldots$ are constants which may depend on $\delta$, but not on $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$, and which we keep track of in our proofs.
+
+\begin{theorem}
+	\label{thm:density_cluster_volume_ssd_ub}
+	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
+Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $M$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:volume_ssd_ub}.
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \frac{1}{2} \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]).
+	$$ 
+	such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster \smash{$\wh{C}$} satisfies
+	\begin{equation}
+	\label{eqn:density_cluster_volume_ssd_ub}
+	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
+	\end{equation}
+\end{theorem}
+
+Several further remarks are as follows.
+\begin{itemize}
+	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} through the conductance.
+This reflects (what may be regarded as) established wisdom regarding spectral partitioning algorithms more generally \citep{guattery1995, hein2010}, but newly applied to the density clustering setting: if the diameter $\rho$ is large, then PPR	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
+This will be supported by simulations in Section~\ref{subsec:empirical_behavior_ppr}.
+	\item Several modifications of global spectral clustering have been proposed with the intent of making such procedures essentially independent of the shape of the density cluster $\mc{C}_{\lambda}$.
+For instance,~\citet{arias-castro2009,pelletier2011} introduce a cleaning step to remove low-degree vertices, whereas~\cite{little2020} use a weighted geometric graph, where the weights are computed with respect to a density-dependent distance.
+The resulting procedures come with stronger density cluster recovery guarantees.
+However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, and spectral clustering functions as more of a post-processing step.
+These methods are as such very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
+	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
+It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
+	\item The symmetric set difference does not measure whether \smash{$\wh{C}$} can (perfectly) distinguish any two distinct clusters $\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mbb{C}_f(\lambda)$.
+In Appendix~\ref{apdx:appr_misclassification_error}, we show that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
+\end{itemize}
+
+\section{Negative Result}
+\label{sec:lower_bound}
+We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
+Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in $\Reals^2$,
+$$
+\mc{C}^{(0)} = \biggl[-\frac{\sigma}{2}, \frac{\sigma}{2}\biggr] \times 
+\biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
+\mc{C}^{(1)} = \mc{C}^{(0)} - (\sigma,0), \quad
+\mc{C}^{(2)} = \mc{C}^{(0)} + (\sigma,0),
+$$
+where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over \smash{$\mc{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
+$$
+\Pbb = \frac{1 - \epsilon}{2} \Pbb_1 + \frac{1 - \epsilon}{2} \Pbb_2 +
+\frac{\epsilon}{2} \Pbb_0, 
+$$
+where $\Pbb_k$ is the uniform distribution over $\mc{C}^{(k)}$ for $k = 0,1,2$.  
+The density function $f$ of $\Pbb$ is simply
+\begin{equation}
+\label{eqn:lb_density}
+f(x) = \frac{1}{\rho\sigma}\left(\frac{1 - \epsilon}{2}\1(x \in
+\mc{C}^{(1)}) + \frac{1 - \epsilon}{2}\1(x \in \mc{C}^{(2)}) +
+\epsilon\1(x \in \mc{C}^{(0)})  \right), 
+\end{equation}
+so that for any $\epsilon < \lambda < (1 - \epsilon)/2$, we have \smash{$\mbb{C}_f(\lambda) = \set{\mc{C}^{(1)}, \mc{C}^{(2)}}$}.
+Figure~\ref{fig:hard_case} visualizes the density $f$ for two different choices of $\epsilon, \sigma, \rho$.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_1}
+	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_2}
+	\caption{\small The density $f$ in \eqref{eqn:lb_density}, for
+		$\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
+		$\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
+		$\sigma = 0.2$.} 
+	\label{fig:hard_case}
+\end{figure}
+
+\subsection{Lower Bound on Symmetric Set Difference}
+As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}.
+Let
+\begin{equation}
+\label{eqn:lower_set}
+\mc{L} = \set{(x_1,x_2) \in \mc{X}: x_2 < 0}.
+\end{equation}
+
+In the following Theorem, $B_{1,\delta}$ and $B_{2,\delta}$ are constants which may depend on $\delta,\Pbb,\mc{C}_{\lambda,\sigma}$ and $r$, but not on $n$.
+\begin{theorem}
+	\label{thm:ppr_lb}
+	Fix $\delta \in (0,1/7)$. Assume the neighborhood graph radius $r < \sigma/4$, that
+	\begin{equation}
+	\label{eqn:ppr_lb_condition}
+	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\text{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
+	\end{equation} 
+	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot \Phi_{n,r}(\mc{L}[X])$, and $(L,U) = (0,1)$.
+Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}[X]^g \cap \mc{C}^{(1)}[X]) \geq \frac{1}{8} \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r}),
+	$$
+	such that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
+	\smash{$\wh{C}$} satisfies    
+	\begin{equation}
+	\label{eqn:ppr_lb}
+	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot \frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}{\epsilon^2 r^2}\right) \frac{\sigma}{r}},
+	\end{equation} 
+\end{theorem}
+
+We make a couple of remarks.
+\begin{itemize}
+	\item Theorem~\ref{thm:ppr_lb} is stated with respect to a particular hard case, where the density clusters are rectangular subsets of $\Reals^2$.  We chose this
+	setting to make the theorem simple to state, and our results are generalizable
+	to $\Rd$ and to non-rectangular clusters. Technically, the rectangles $\mc{C}^{(0)},\mc{C}^{(1)},\mc{C}^{(2)}$ are not
+	$\sigma$-expansions due to their sharp corners. To fix this, one can   
+	simply modify these sets to have appropriately rounded corners, and our lower
+	bound arguments do not need to change significantly, subject to some
+	additional bookkeeping.  Thus we ignore this technicality in our subsequent
+	discussion.
+
+	\item Although we state our lower bound with respect to PPR run on a neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mc{L}$.
+In this case, not merely PPR but any algorithm that approximates the minimum normalized cut is unlikely to recover $\mc{C}^{(1)}$.
+In particular, local spectral clustering methods that are based on truncated random walks \citep{spielman2013}, global spectral clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings \citep{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
+\end{itemize}
+
+\subsection{Comparison Between Upper and Lower Bounds}
+\label{subsec:comparison_upper_lower_bounds}
+To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
+results of our upper bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} to the density $f$ given in \eqref{eqn:lb_density}.
+Observe that $\mc{C}^{(1)}$ satisfies each of the Assumptions~\ref{asmp:lambda_bounded_density}--\ref{asmp:bounded_volume}:
+
+\begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{6}
+	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in	\mc{C}^{(1)}$.  
+	\item The density $f(x) \leq \frac{\epsilon}{\rho\sigma}$ for all $x \in \Reals^2$ such that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
+	$$
+	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  \geq \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma},
+	$$
+	which meets the decay requirement with exponent $\gamma=0$.
+	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\sqrt{\rho^2 + \sigma^2}$.
+	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) = \vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Rd)$}.   
+\end{enumerate}
+
+If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+This implies that there exists a set $\mc{C}^{(1)}[X]^g \subseteq \mc{C}^{(1)}[X]$ with \smash{$\vol_{n,r}(\mc{C}^{(1)}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X])$} such that for any seed node $v \in \mc{C}^{(1)}[X]^g$, and for large enough $n$, the PPR estimated cluster \smash{$\wh{C}$} satisfies with high probability
+\begin{equation*}
+\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 64 C_{1,\delta} \cdot \frac{\rho^2 + \sigma^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
+\end{equation*}
+To facilitate comparisons between our upper and lower bounds set $r = \sigma/8$.  Then the following statements each hold with high probability. 
+\begin{itemize}
+	\item If the user-specified parameters satisfy~\eqref{eqn:initialization}, and for some $a \geq 0$,
+	\begin{equation*}
+	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{512 C_{1,\delta}} \frac{\sigma^2}{(\rho^2 + \sigma^2) \log^2(\rho/\sigma \sqrt{C_{2,\delta}})},
+	\end{equation*}
+	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \leq a \cdot
+		\vol_{n,r}(\mc{C}^{(1)}[X])$}.
+
+	\item The population-level volume $\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq (1 - \epsilon)/2 \cdot \pi r^2/(\rho\sigma)$, and
+	\begin{equation*}
+	\vol_{n,r}(\mc{C}^{(1)}[X]) \leq (1 + \delta) \cdot n(n - 1) \vol_{\Pbb,r}(\mc{C}^{(1)}). 
+	\end{equation*}
+	Therefore, if the user-specified parameters are as in Theorem~\ref{thm:ppr_lb}, and
+	\begin{equation*}
+	\epsilon \geq \sqrt{8 C_{3,\delta}} \left({\frac{\sigma}{\rho}} \log \left(64C_{4,\delta} \cdot \frac{\rho}
+	{\epsilon^2 \sigma}\right)\right)^{1/4},
+	\end{equation*}
+	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{20} \vol_{n,r}(\mc{C}^{(1)}[X])$}. 
+\end{itemize}
+Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even if it is reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound, but do not pursue the details.}
+
+Of course, it is not hard to show that in the example under consideration, classical plug-in density cluster estimators can consistently recover $\mc{C}^{(1)}$, even if $\epsilon$ is large compared to $\sigma/\rho$.
+That PPR has trouble recovering density clusters here (where standard plug-in approaches do not) is not meant to be a knock on PPR.
+Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR relies on geometry as well as density when forming the output cluster.
+
+\section{Experiments}
+\label{sec:experiments}
+We provide numerical experiments to investigate the tightness of our theoretical results in Section~\ref{sec:ppr_density_cluster}, and compare the performance of PPR with a density clustering algorithm on the ``two moons'' dataset.
+We defer details of the experimental settings to Appendix~\ref{apdx:experimental_details}.
+
+\subsection{Validating Theoretical Bounds}
+We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e., the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
+Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities, when samples are drawn from a mixture of uniform distributions over rectangular clusters.
+In the first row we vary the diameter $\rho$ of the candidate cluster, in the second row we vary the width $\sigma$, and in the third row we vary the ratio $(\lambda - \theta)/\lambda$ of the density within and outside the cluster.
+In almost all cases, it is encouraging to see that our bounds track closely with their empirical counterparts, and are loose by roughly an order of magnitude at most.
+The one exception to this is the dependence of local spread on the width $\sigma$; this theoretical deficiency stems from a loose bound on the volume of sets with large aspect ratio (meaning $\rho/\sigma$ is much greater than $1$), but in any case the local spread contributes only $\log$ factors to the ultimate bound on cluster recovery.
+On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$}, which as a result is loose by several orders of magnitude.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/samples5.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/rho/local_spread.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/samples1.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/sigma/local_spread.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/samples3.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/normalized_cut.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/conductance.pdf}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/local_spread.pdf}
+	\caption{\small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
+In the first row we vary the diameter $\rho$, in the second row we vary the thickness $\sigma$, and in the third row we vary the density ratio $(\lambda - \theta)/\lambda$.
+The first column shows $n = 8000$ samples for three different parameter values.}
+	\label{fig:bounds}
+\end{figure}
+
+\subsection{Empirical Behavior of PPR} 
+\label{subsec:empirical_behavior_ppr}
+In Figure \ref{fig:moons}, to drive home the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR and the density clustering algorithm of \citet{chaudhuri2010} on the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
+We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be seen as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
+The first column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by PPR; the third column shows the global minimum normalized cut, computed according to the algorithm of \citet{bresson2013}; and the last column shows a cut of the density cluster tree estimator of \citet{chaudhuri2010}.
+Each row corresponds to a different separation between the two moons.
+In the second row, we see that as the two moons become less well-separated, PPR becomes unable to recover the density clusters, but normalized cut still succeeds in doing so.
+In the third row, we see that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.
+This supports one of our main messages, which is that PPR recovers only geometrically well-conditioned density clusters.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.24\textwidth,scale = .5]{plots/experiment_2/row1_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_true_density_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_ppr_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_conductance_cluster}
+	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_density_cluster}
+	\caption{\small True density (column 1), PPR (column 2), minimum normalized
+		cut (column 3) and estimated density (column 4) clusters for 3 different 
+		simulated data sets. Seed node for PPR denoted by a black cross.} 
+	\label{fig:moons}
+\end{figure}
+
+\section{Discussion}
+\label{sec:discussion}
+In this work, we have analyzed the behavior of PPR in the classical setup of nonparametric statistics.
+We have shown how PPR depends on the distribution $\Pbb$ through the population normalized cut, conductance, and local spread, and established upper bounds on the error with which PPR recovers an arbitrary candidate cluster $\mc{C} \subseteq \Rd$.
+In the particularly important case where $\mc{C} = \mc{C}_{\lambda}$ is a $\lambda$-density cluster, we have shown that PPR recovers $\mc{C}_{\lambda}$ if and only if both the density cluster and density are well-conditioned.
+We now conclude by summarizing a couple of interesting directions for future work.
+
+Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to \infty$, would be computationally attractive, as it would ensure that the graph $G_{n,r}$ is sparse.
+However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in this regime.
+Although the restriction to a kernel function fixed in $n$ is common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017}, recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.
+
+In another direction, it would be very useful to find reasonable conditions under which the ratio \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} would tend to $0$ as $n \to \infty$.
+It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR.
+Though most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
+It is not clear whether the techniques used in these works can be applied to PPR.
+
+\acks{
+	SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for early inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+}
+
+\clearpage
+\appendix
+The proofs of our major theorems largely consist of (at most) three modular parts.
 \begin{enumerate}
@@
 
-\section{Fixed graph results}
+\section{Fixed Graph Results}
 \label{apdx:fixed_graph}
@@
 For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.
+\\
 
@@
 \end{equation*}
-We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq d_{\max}(G) \cdot n$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)
-
-\paragraph{Organization.} In the following sections we establish: (Section \ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (Section \ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (Section \ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (Section \ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (Section \ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
-
-\subsection{Misclassification error of clustering with PPR and aPPR}
+We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq d_{\max}(G) \cdot n$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.) \\
+
+\emph{Organization.} In the following sections we establish: (Section \ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (Section \ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (Section \ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (Section \ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (Section \ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
+
+\subsection{Misclassification Error of Clustering with PPR and aPPR}
 \label{subsec:pf_lem_zhu}
@@
 Similarly we write $\wt{q}_v^{(t)} := q(v,t;\wt{G})$ for the $t$-step distribution of the lazy random walk over $\wt{G}$, $\wt{\pi} = \pi(G[C])$ for the stationary distribution of $\wt{q}_v^{(t)}$ (we will always assume $G[C]$ is connected), and $\wt{p}_v := p(v,\alpha;\wt{G})$ for the PPR vector over $\wt{G}$.
-
-\paragraph{Proof of Lemma~\ref{lem:zhu}.}
+\\
+
+\emph{Proof of Lemma~\ref{lem:zhu}.}
 As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma.
@@
 \end{equation} 
-The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
+The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}. \qed
 
@@
 
-\paragraph{Proof of Corollary~\ref{cor:zhu}.}
+\noindent \emph{Proof of Corollary~\ref{cor:zhu}.}
 Recall that the upper bound~\eqref{eqn:zhu_ub} on $\vol(\wh{C} \vartriangle C;G)$ comes from combining the upper bounds on $\vol(\wh{C} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus \wh{C};G)$ and $\vol(C^{\mathrm{bdry}} \setminus \wh{C};G)$ in~\eqref{pf:zhu3.5},~\eqref{pf:zhu5} and~\eqref{pf:zhu6}.
@@
 \end{equation}
-	Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim.
-
-\subsection{Uniform bounds on PPR}
+Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim. \qed
+
+\subsection{Uniform Bounds on PPR}
 \label{subsec:ppr_uniform_bounds}
@@
 
-\paragraph{``Leakage'' and ``soakage'' vectors.} To prove Lemma~\ref{lem:ppr_uniform_bound}, we will make use of the following explicit representation of the \emph{leakage} distribution $\ell$ from~\eqref{pf:zhu3}, as well as an analogously defined \emph{soakage} distribution $s$:
+\noindent\emph{``Leakage'' and ``soakage'' vectors.} To prove Lemma~\ref{lem:ppr_uniform_bound}, we will make use of the following explicit representation of the \emph{leakage} distribution $\ell$ from~\eqref{pf:zhu3}, as well as an analogously defined \emph{soakage} distribution $s$:
 \begin{equation}
@@
 
-\paragraph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
+\noindent\emph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
 We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
@@
 \end{equation*}
-	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.
-
-\subsection{Mixedness of lazy random walk and PPR vectors}
+where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.  \qed
+
+\subsection{Mixedness of Lazy Random Walk and PPR Vectors}
 \label{subsec:lovasz_simonovits_bounds}
@@
 
-\paragraph{Proof of Theorem~\ref{thm:mixing_time_rw}.}
+\noindent \emph{Proof of Theorem~\ref{thm:mixing_time_rw}.}
 Take $K_0 = 0$ if $u_{(1)} \neq v$, and otherwise take $K_0 = \deg(v;G)$.
@@
 
-	Otherwise, we must still establish that~\eqref{eqn:mixing_random_walk} is a valid upper bound when $k \in [0, \deg(v;G)) ~\cup~ (2m - \deg(v;G),2m]$. If $k \in [0, \deg(v;G))$ then
+Otherwise, we suppose $k \in [0, \deg(v;G)) ~\cup~ (2m - \deg(v;G),2m]$. If $k \in [0, \deg(v;G))$ then
 \begin{equation}
@@
 \end{equation}
-	where $(\textrm{i})$ follows since $k \in [0,K_0]$, and $h^{(t_0)}$ is linear over $[0,K_0)$ with $h^{(t_0)}(0) = 0$ and $h^{(t_0)}(K_0) \geq 0$. For similar reasons,
+where $(\textrm{i})$ follows since $k \in [0,K_0]$, and $h^{(t_0)}$ is linear over $[0,K_0)$ with $h^{(t_0)}(0) = 0$ and $h^{(t_0)}(K_0) \geq 0$.
+For similar reasons, if $k \in (2m - \deg(v;G),2m]$ then
 \begin{equation}
@@
 \end{equation}
-	Since the ultimate upper bounds in~\eqref{pf:mixing_random_walk_1} and~\eqref{pf:mixing_random_walk_2} are each no greater than that of~\eqref{eqn:mixing_random_walk}, the claim follows.
-
-\paragraph{Proof of Theorem~\ref{thm:mixing_time_PPR}.}
+Since the ultimate upper bounds in~\eqref{pf:mixing_random_walk_1} and~\eqref{pf:mixing_random_walk_2} are each no greater than that of~\eqref{eqn:mixing_random_walk}, the claim follows. \qed \\
+
+\noindent \emph{Proof of Theorem~\ref{thm:mixing_time_PPR}.}
 The proof of Theorem~\ref{thm:mixing_time_PPR} follows immediately from Lemmas~\ref{lem:mixing_time_PPR},~\ref{lem:interpolator_bound_ppr} and~\ref{lem:linearization_bound}, taking $K_0 = 0$ if $u_{(1)} \neq v$ and otherwise $K_0 = \deg(v;G)$.
+\qed
 
@@
 In what follows, for a distribution $q$ and vertices $u,w \in V$, we write $q(u,w) := q(u)/d(u) \cdot 1\{(u,w) \in E\}$, and similarly for a collection of dyads $\wt{E} \subseteq V \times V$ we write $q(\wt{E}) := \sum_{(u,w) \in \wt{E}} q(u,w)$.
-\paragraph{Proof of Lemma~\ref{lem:mixing_random_walk}.}
+\\
+
+\noindent\emph{Proof of Lemma~\ref{lem:mixing_random_walk}.}
 We will prove Lemma~\ref{lem:mixing_random_walk} by induction on $t$.
@@
 & \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
-	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
-	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
+& = L_{K_0}(k;h^{(t_0)}) ~~+ \\
+& \quad~\frac{1}{2}C(K_0;h^{t_0})\biggl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\biggr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
+& \leq L_{K_0}(k;h^{(t_0)}) ~~+ \\
+& \quad~\frac{1}{2}C(K_0;h^{(t_0)})\biggl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\biggr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1}.
 \end{align*}
@@
 & \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
+& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) ~~+ \\
+& \quad~ C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
 & \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
@@
 \end{align*}
-	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.
-
-\paragraph{Proof (of Lemma~\ref{lem:mixing_time_PPR}).}
+where $\textrm{(i)}$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.
+\qed \\
+
+\noindent\emph{Proof (of Lemma~\ref{lem:mixing_time_PPR}).}
 We will show that if $\Phi(S_j; g) \geq \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.
@@
 \begin{align*}
-	h^{(\alpha)}(k_j) & \leq \alpha +~~ \\
-	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
+h^{(\alpha)}(k_j) & \leq \alpha + \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j)\biggr) ~~+ \\
+& \quad~ \frac{1}{2}C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \\
 & \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
@@
 h^{(\alpha)}(k_j) & \leq \alpha + \frac{1}{2}\Bigl(h^{(\alpha)}(K_0) + h\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
-	& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0;p^{\alpha}) + L_{K_0}(2k_j - K_0\bigr) + C(K_0;h^{(\alpha)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
+& \leq\alpha + \frac{\alpha(t - 1)}{2} + \frac{1}{2}\Bigl(L_{K_0}(K_0;p^{\alpha}) + L_{K_0}(2k_j - K_0\bigr)\Bigr) ~~+ \\
+& \quad~ C(K_0;h^{(\alpha)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\phi^2}{8}\right)^{t - 1}\Bigr) \\
 & \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\phi^2}{8}\right)^{t - 1} \\
-	& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}
-	\end{align*}
-
-\paragraph{Proof of Lemma~\ref{lem:interpolator_bound_rw}.}
+& \leq \alpha t + L_{K_0}(k_j) + C(K_0;h^{(\alpha)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\phi^2}{8}\right)^{t}.
+\end{align*} \qed
+
+\noindent \emph{Proof of Lemma~\ref{lem:interpolator_bound_rw}.}
 We will prove that the inequalities of~\eqref{eqn:interpolator_bound_rw} hold at the knot points of $h^{(t_0)}$, whence they follow for all $K_0 \in [0,m]$.
@@
 \end{equation*}
-	where the last inequality follows since $\vol(S) \geq |S| \cdot d_{\min}(G)$ for any set $S \subseteq V$.
-
-\paragraph{Proof of Lemma~\ref{lem:interpolator_bound_ppr}.}
+where the last inequality follows since $\vol(S) \geq |S| \cdot d_{\min}(G)$ for any set $S \subseteq V$. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:interpolator_bound_ppr}.}
 We have already established the first upper bound in~\eqref{eqn:interpolator_bound_ppr}, in the proof of Lemma~\ref{lem:interpolator_bound_rw}.
@@
 \end{equation}
-	the second upper bound in~\eqref{eqn:interpolator_bound_ppr} follows similarly to the proof of the equivalent upper bound in~Lemma~\ref{lem:interpolator_bound_rw}.
-
-\paragraph{Proof of Lemma~\ref{lem:linearization_bound}.}
+the second upper bound in~\eqref{eqn:interpolator_bound_ppr} follows similarly to the proof of the equivalent upper bound in~Lemma~\ref{lem:interpolator_bound_rw}. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:linearization_bound}.}
 The result of the Lemma follows obviously from~\eqref{pf:linearization_bound_1}, once we show \eqref{eqn:right_derivative_1}-\eqref{eqn:right_derivative_2}.
@@
 h'(2m - K_0) \geq -\frac{\pi(u_{(j+1)})}{\mathrm{deg}(u_{(j + 1)};G)} \geq -\frac{d_{\max}(G)}{d_{\min}(G) \cdot \vol(G)}.
-	\end{equation*}
+\end{equation*} \qed
 
@@
 \end{lemma}
-The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward.
-\paragraph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
+The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward. \\
+
+\noindent\emph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
 Put $T = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
@@
 \end{align*}
-	where the middle inequality follows by assumption.
-
-\paragraph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
+where the middle inequality follows by assumption. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
 Our goal will be to establish the recurrence relation~\eqref{pf:tv_to_pointwise_2}. 
-	To derive~\eqref{pf:tv_to_pointwise_2}, the key observation is the following equivalence (see equation (16) of \citep{morris2005}):
+To derive~\eqref{pf:tv_to_pointwise_2}, the key observation is the following equivalence (see equation (16) of \cite{morris2005}):
 \begin{align}
@@
 \frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} & = \sum_{w \in V} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) \nonumber \\
-	& = \sum_{w \neq u} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) + \bigl(\pi(u) - q_v^{(t)}(u) \bigr) \cdot \Bigl(\frac{q_u^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr)
+& = \sum_{w \neq u} \bigl(\pi(w) - q_v^{(t)}(w) \bigr) \cdot \Bigl(\frac{q_w^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr) ~~+ \\
+& \quad~\bigl(\pi(u) - q_v^{(t)}(u) \bigr) \cdot \Bigl(\frac{q_u^{(1)}(u) - \pi(u)}{\pi(u)}\Bigr).
 \end{align}
@@
 \end{equation}
-	From~\eqref{pf:tv_to_pointwise_2} alogn with the initial condition
+From~\eqref{pf:tv_to_pointwise_2} along with the initial condition
 \begin{equation*}
@@
 \end{equation*}
-	This inequality holds for each $u \in V$, and taking the maximum over $u$ completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
-
-\subsection{Spectral partitioning properties of PPR}
+This inequality holds for each $u \in V$, and taking the maximum over $u$ completes the proof of Lemma~\ref{lem:tv_to_pointwise}. \qed
+
+\subsection{Spectral Partitioning Properties of PPR}
 \label{subsec:ppr_spectral_partitioning}
@@
 \end{equation}
-The claim of Theorem~\ref{thm:normalized_cut_ppr} is a consequence of~\eqref{eqn:ppr_leakage} along with Theorem~\ref{thm:mixing_time_PPR}, as we now demonstrate.
-\paragraph{Proof of Theorem~\ref{thm:normalized_cut_ppr}.}
+The claim of Theorem~\ref{thm:normalized_cut_ppr} is a consequence of~\eqref{eqn:ppr_leakage} along with Theorem~\ref{thm:mixing_time_PPR}, as we now demonstrate. \\
+
+\noindent \emph{Proof of Theorem~\ref{thm:normalized_cut_ppr}.}
 From~\eqref{eqn:ppr_leakage}, the upper bound in~\eqref{eqn:normalized_cut_ppr_vol}, and the choice of $\alpha = 36 \cdot \Phi(C;G)$, 
@@
 \end{equation*}
-	Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be that $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem.
-
-\section{Sample-to-population bounds}
+Thus the inequality~\eqref{pf:normalized_cut_ppr_2} cannot hold, and so it must be that $\min_{\beta \in (0,1)} \Phi(S_{\beta,v};G) \leq \phi_{\ast}^2$. This is exactly the claim of the theorem. \qed
+
+\section{Sample-to-Population Bounds}
 \label{apdx:sample_to_population}
@@
 
-\subsection{Review: concentration inequalities}
+\subsection{Review: Concentration Inequalities}
 \label{subsec:concentration}
@@
 
-\subsection{Sample-to-population: normalized cut}
+\subsection{Sample-to-Population: Normalized Cut}
 \label{subsec:sample_to_population_ncut}
@@
 \end{equation*}
-with probability at least $1 - 3\exp\{-n \delta^2 \cut_{\Pbb,r}(\mc{C})/4\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 := 3\cut_{\Pbb,r}(\mc{C})/4$.
-
-\subsection{Sample-to-population: local spread}
+with probability at least $1 - 3\exp\{-n \delta^2 \cut_{\Pbb,r}(\mc{C})/4\}$. This establishes~\eqref{eqn:sample_to_population_normalized_cut} upon taking $b_1 := 3\cut_{\Pbb,r}(\mc{C})/4$. \qed
+
+\subsection{Sample-to-Population: Local Spread}
 \label{subsec:sample_to_population_local_spread}
@@
 This establishes~\eqref{eqn:sample_to_population_local_spread} upon taking $b_2 := \Pbb(\mc{C}) \cdot d_{\min}(\wt{\Pbb})/14$.
+\qed
 
@@
 
-\subsection{Sample-to-population: conductance}
+\subsection{Sample-to-Population: Conductance}
 \label{subsec:sample_to_population_conductance}
@@
 Subsequently in Proposition~\ref{prop:conductance_lb_transportation_distance}, we relate the $\infty$-transportation distance between two measures $\mbb{Q}_1$ and $\mbb{Q}_2$ to the difference of their conductances.
-Together these results will imply~\eqref{eqn:sample_to_population_conductance}.
-
-\paragraph{Review: $\infty$-transportation distance and transportation maps.}
+Together these results will imply~\eqref{eqn:sample_to_population_conductance}.\\
+
+\noindent \emph{Review: $\infty$-transportation distance and transportation maps.}
 We give a brief review of some of the main ideas regarding $\infty$-transportation distance, and transportation maps.
@@
 \begin{equation*}
-\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2) := \inf_{\gamma}\Bigl\{\mathrm{esssup}_{\gamma} \bigl\{|x - y|: (x,y) \in D \times D\bigr\}: \gamma \in \Gamma(\mbb{Q}_1,\mbb{Q}_2) \Bigr\}
+\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2) := \inf_{\gamma}\Bigl\{\mathrm{ess sup}_{\gamma} \bigl\{|x - y|: (x,y) \in D \times D\bigr\}: \gamma \in \Gamma(\mbb{Q}_1,\mbb{Q}_2) \Bigr\}
 \end{equation*}
@@
 
-\paragraph{$\infty$-transportation distance between empirical and population measures.}
+\noindent \emph{$\infty$-transportation distance between empirical and population measures.}
 We now review the relevant upper bound on $\Delta_{\infty}(\Pbb,\Pbb_n)$, which holds under the following mild regularity conditions.
 \begin{enumerate}[label=(A\arabic*)]
+	\setcounter{enumi}{10}
 	\item 
-	\label{asmp:bounded_density} 
+	\label{asmp:bounded_density_full} 
 	The distribution $\Pbb$ has density $g: D \to (0,\infty)$ such that there exist $g_{\min} \leq 1 \leq g_{\max}$ for which
@@
 	\item 
-	\label{asmp:domain} 
+	\label{asmp:domain_full} 
 	The distribution $\Pbb$ is defined on a bounded, connected, open domain $D \subseteq \Rd$. If $d \geq 2$ then additionally $D$ has Lipschitz boundary.
@@
 	\label{thm:garciatrillos16}
-	Suppose $\Pbb$ satisfies~\ref{asmp:bounded_density} and~\ref{asmp:domain}.
+	Suppose $\Pbb$ satisfies~\ref{asmp:bounded_density_full} and~\ref{asmp:domain_full}.
 Then, there exists positive constants $B_{2}$ and $B_5$ that do not depend on $n$, such that with probability at least $1 - B_2/n$:
@@
 \end{theorem}
-Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}, then~\eqref{eqn:ot_distance_1d} ($d = 1)$ or Theorem~\ref{thm:garciatrillos16} ($d \geq 2$) apply to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use these upper bounds on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.
-
-\paragraph{Lower bound on conductance using transportation maps.}
+Assuming the candidate cluster $\mc{C}$ and conditional distribution $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}, then~\eqref{eqn:ot_distance_1d} ($d = 1)$ or Theorem~\ref{thm:garciatrillos16} ($d \geq 2$) apply to $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$; we will use these upper bounds on $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$ to show~\eqref{eqn:sample_to_population_conductance}.\\
+
+\noindent \emph{Lower bound on conductance using transportation maps.}
 Let $\mbb{Q}_1$ and $\mbb{Q}_2$ be probability measures, with $\mbb{Q}_1$ absolutely continuous with respect to Lebesgue measure, and let $T$ be a transportation map from $\mbb{Q}_1$ to $\mbb{Q}_2$.
@@
 \end{proposition}
-We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$. 
-\paragraph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}
+We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$.\\
+
+\noindent \emph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}
 Throughout this proof, we will write $\Delta_{12} = \Delta_T(\mbb{Q}_1,\mbb{Q}_2)$, and $\wb{\vol}_{\mbb{Q},r}(\mc{R}) = \min\bigl\{\vol_{\mbb{Q},r}\bigl(\mc{R}\bigr),\vol_{\mbb{Q},r}\bigl(\mc{R}^c\bigr)\bigr\}$ for conciseness.
@@
 Without loss of generality, we shall assume that $\vol_{\mbb{Q}_2,r}(\mc{R}) \leq (1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2$ (otherwise we can work with respect to $\mc{R}^c$.)  Then, for all $x \in \mc{R}$,
-	\begin{equation*}
-	\int \1\{\|x - y\| \leq r\}\cdot \1\{y \in \mc{R}^c\} \,d\mbb{Q}_2(y) \geq \deg_{\Qbb_2,r}(x) -  \mbb{Q}_2(\mc{R}) \geq \deg_{\Qbb_2,r}(x) - \frac{\vol_{\mbb{Q}_2,r}(\mc{R})}{d_{\min}(\mbb{Q}_2)} \geq d_{\min}(\mbb{Q}_2) \cdot \Psi_{r}(\mbb{Q}_2),
-	\end{equation*}
+\begin{align*}
+\int \1\{\|x - y\| \leq r\}\cdot \1\{y \in \mc{R}^c\} \,d\mbb{Q}_2(y) & \geq \deg_{\Qbb_2,r}(x) -  \mbb{Q}_2(\mc{R}) \\
+& \geq \deg_{\Qbb_2,r}(x) - \frac{\vol_{\mbb{Q}_2,r}(\mc{R})}{d_{\min}(\mbb{Q}_2)} \\
+& \geq d_{\min}(\mbb{Q}_2) \cdot \Psi_{r}(\mbb{Q}_2),
+\end{align*}
 whence integrating over all $x \in \mc{R}$ and dividing by~$\vol_{\mbb{Q}_2,r}(\mc{R})$ yields~\eqref{pf:conductance_lb_transportation_distance_3}.
 This completes the proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.
-
-\paragraph{Putting the pieces together.} 
+\\
+
+\noindent \emph{Putting the pieces together.} 
 First, we note that
@@
 Finally, appealing first to  Proposition~\ref{prop:conductance_lb_transportation_distance} and then to the bounds we have just established on $d_{\min}(\wt{\Pbb}_n)$ and $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$, we conclude that the sample conductance is lower bounded,
-\begin{equation*}
-\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
-\end{equation*}
-with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$.
-
-\section{Population functionals for density clusters}
+\begin{align*}
+\Psi_r(\wt{\Pbb}_n) & \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \\
+& \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta),
+\end{align*}
+with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$. \qed
+
+\section{Population Functionals for Density Clusters}
 \label{apdx:density_cluster_population_functionals}
@@
 \end{equation}  
-\paragraph{Proof of Lemma~\ref{lem:overlap_balls}.}
+\emph{Proof of Lemma~\ref{lem:overlap_balls}.}
 First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each of height $h = r - \frac{\|x - y\|}{2}$. 
@@
 \end{equation*}
-	for $a = (r - h)^2/r^2 = r^2/(4\sigma^2)$, and the claim follows.
-
-\paragraph{Proof of Lemma~\ref{lem:volume_of_spherical_cap}.}
+for $a = (r - h)^2/r^2 = r^2/(4\sigma^2)$, and the claim follows. \qed \\
+
+\noindent\emph{Proof of Lemma~\ref{lem:volume_of_spherical_cap}.}
 For any $0 \leq a \leq 1$, we have that
@@
 \nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a}\frac{\Gamma(\frac{d}{2} + 1)}{\Gamma(\frac{d + 1}{2})\Gamma(\frac{1}{2})}\biggr)  \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation*}
-
-\subsection{Isoperimetric inequalities}
+\end{equation*} \qed
+
+\subsection{Isoperimetric Inequalities}
 \label{subsec:isoperimetric_inequalities}
@@
 
-\subsection{Reverse isoperimetric inequalities}
+\subsection{Reverse Isoperimetric Inequalities}
 \label{subsec:reverse_isoperimetric_inequalities}
@@
 \end{lemma}
-\paragraph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality}.}
+\emph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality}.}
 Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
@@
 
-	We claim that for all $j = 1,\ldots,N$, the function $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing in $s$.
-Once this claim is verified, it follows that
-	\begin{equation*}
-	\nu(\mc{A}_j(\sigma + \epsilon)) = \nu\bigl(B(x_j,\sigma + \epsilon)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)}{\nu\bigl(B(x_j,\sigma + \epsilon)\bigr)} \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot  \nu\bigl(B(x_j,\sigma)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma)\bigr)}{\nu\bigl(B(x_j,\sigma)\bigr)} = \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \nu\bigl(\mc{A}_j(\sigma)
-	\end{equation*}
+We claim that for all $j = 1,\ldots,N$, the function $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing in $s$. Once this claim is verified, it follows that
+\begin{align*}
+\nu(\mc{A}_j(\sigma + \epsilon)) & = \nu\bigl(B(x_j,\sigma + \epsilon)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)}{\nu\bigl(B(x_j,\sigma + \epsilon)\bigr)} \\
+& \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot  \nu\bigl(B(x_j,\sigma)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma)\bigr)}{\nu\bigl(B(x_j,\sigma)\bigr)} \\
+& = \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \nu\bigl(\mc{A}_j(\sigma),
+\end{align*}
 and summing over $j$, we see that
@@
 \end{equation*}
-	and applying $\nu(\cdot)$ to both sides yields the claim.
-
-\paragraph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted}.}
+and applying $\nu(\cdot)$ to both sides yields the claim. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted}.}
 Fix $k \in \mathbb{N}$.
@@
 \end{equation*}
-	The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim.
+The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim. \qed
 
@@
 The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
+\qed
 
@@
 The claim of Proposition~\ref{prop:density_cluster_normalized_cut} follows upon using Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted} to upper bound $\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr)$.
+\qed
 
@@
 Noting that $\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \cdot \lambda_{\sigma}^2/\Lambda_{\sigma}^2$, Proposition~\ref{prop:density_cluster_conductance} follows from~\eqref{eqn:uniform_density_cluster_conductance}.
-
-\paragraph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
+\\
+
+\noindent \emph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
 For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho M)$.
@@
 	\begin{align*}
-		\nu\bigl(B(x,r) \cap B(y,r)\bigr) & = \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{R}\bigr) + \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{S}\bigr) + \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{C}_{\lambda,\sigma}^c\bigr) \\
+	\nu\bigl(B(x,r) \cap B(y,r)\bigr) & = \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{R}\bigr) + \nu\bigl(B(x,r) \cap B(y,r) \cap \mc{S}\bigr) ~~+ \\
+	& \quad~\nu\bigl(B(x,r) \cap B(y,r) \cap \mc{C}_{\lambda,\sigma}^c\bigr) \\
 	& \leq \nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr) + \nu\bigl(B(x,r) \cap \mc{C}_{\lambda,\sigma}^c\bigr) \\
@@
 \end{equation*}
-	and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$.
-
-\subsection{Population functionals, hard case}
+and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$. \qed
+
+\subsection{Population functionals, Hard Case}
 \label{subsec:density_cluster_hard_case}
@@
 \end{equation}
-
-\paragraph{Proof of~\eqref{eqn:ncut_lower_set}.}
+\emph{Proof of~\eqref{eqn:ncut_lower_set}.}
 Noting that $\vol_{\Pbb,r}(\mathcal{L}) = \vol_{\Pbb,r}(\mathcal{X} \setminus \mathcal{L})$, it suffices to upper bound $\cut_{\Pbb,r}(\mathcal{L})$ and lower bound $\vol_{\Pbb,r}(\mathcal{L})$.
@@
 \end{align*}
-	where the last inequality follows since $r \leq \frac{1}{4}\sigma \leq \frac{1}{4}\rho$.
-
-\paragraph{Proof of~\eqref{eqn:local_spread_ub}.}
+where the last inequality follows since $r \leq \frac{1}{4}\sigma \leq \frac{1}{4}\rho$. \qed \\
+
+\noindent \emph{Proof of~\eqref{eqn:local_spread_ub}.}
 The statement follows since 
@@
 \vol_{\Pbb,r}(\mc{X}) \leq d_{\max}(\Pbb) \leq \frac{\pi r^2}{2 \sigma \rho}.
-	\end{equation*}
+\end{equation*} \qed
+
 \section{Proof of Major Theorems}
@@
 \label{subsec:pf_volume_ssd_ub}
-We begin by recalling some probabilistic estimates needed for the proof of Theorem~\ref{thm:volume_ssd_ub}, along with the probability with which they hold.
-
-\paragraph{Probabilistic estimates.}
+We begin by recalling some probabilistic estimates needed for the proof of Theorem~\ref{thm:volume_ssd_ub}, along with the probability with which they hold.\\
+
+\noindent\emph{Probabilistic estimates.}
 Throughout the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume (i) that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} are satisfied; (ii) that the volume of $\mc{C}[X]$ is upper and lower bounded,
@@
 \end{equation}
-By Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$.
+By Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities are satisfied with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$.\\
 
@@
 
-\paragraph{Proof of Theorem~\ref{thm:volume_ssd_ub}.}
+\noindent \emph{Proof of Theorem~\ref{thm:volume_ssd_ub}.}
 We use Lemma~\ref{lem:zhu} to upper bound $\Delta(\wh{C},\mc{C}[X])$.
@@
 Noting that $\wh{C} = S_{\beta,v}$ for some $\beta \in (L,U)$, the claimed upper bound~\eqref{eqn:volume_ssd_ub} on $\Delta(\wh{C},\mc{C}[X])$ then follows from the upper bound~\eqref{eqn:sample_to_population_normalized_cut} on $\Phi_{n,r}(\mc{C}[X])$ and the upper bound on $\vol_{\Pbb,r}(\mc{C})$ in~\eqref{pf:volume_ssd_ub_1}.
+\qed
 
@@
 The claimed upper bound~\eqref{eqn:density_cluster_volume_ssd_ub} on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ then follows from the bounds~\eqref{eqn:density_cluster_local_spread}-\eqref{eqn:density_cluster_conductance} on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$, noting that the condition $r \leq \sigma/(4d)$ implies that $(1 - r/(4\rho L)) \geq 1 - 1/16$ and $1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)} \geq 1 - 1/\sqrt{32}$, and taking
-\begin{equation*}
-C_{1,\delta} := \frac{1175040}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)},~~\textrm{and}~~C_{2,\delta} := \frac{144}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
-\end{equation*}
+\begin{align*}
+C_{1,\delta} & := \frac{1175040}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)}\\
+C_{2,\delta} & := \frac{144}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
+\end{align*} \qed
 
@@
 We therefore conclude that $\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])$ must be large.
-In the remainder of this, we detail the probabilistic estimates used in the proof of Theorem~\ref{thm:ppr_lb}, and then give a formal proof of Theorem~\ref{thm:ppr_lb} and then of Lemma~\ref{lem:normalized_cut_lb}.
-
-\paragraph{Probabilistic estimates.}
+In the remainder of this, we detail the probabilistic estimates used in the proof of Theorem~\ref{thm:ppr_lb}, and then give a formal proof of Theorem~\ref{thm:ppr_lb} and then of Lemma~\ref{lem:normalized_cut_lb}.\\
+
+\noindent \emph{Probabilistic estimates.}
 In addition to~\eqref{eqn:normalized_cut_lb}, we will assume (i) that the graph normalized cut of $\mc{L}$ and local spread of $\mc{X}$ are respectively upper and lower bounded,
@@
 (iii) that the graph volumes of $\mc{L} \cap \mc{C}^{(1)}$ and $\mc{C}^{(1)}$ are respectively lower and upper bounded,
-\begin{equation}
-(1 - \delta) \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}) \leq \frac{1}{n(n - 1)}\vol_{n,r}({\mc{L}[X] \cap \mc{C}^{(1)}}[X])~~\textrm{and}~~\frac{1}{n(n - 1)}\vol_{n,r}(\mc{C}^{(1)}[X]) \leq (1 + \delta) \vol_{\Pbb,r}(\mc{C}^{(1)});
-\end{equation}
+\begin{align*}
+(1 - \delta) \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)}) & \leq \frac{1}{n(n - 1)}\vol_{n,r}({\mc{L}[X] \cap \mc{C}^{(1)}}[X]) \\
+\frac{1}{n(n - 1)}\vol_{n,r}(\mc{C}^{(1)}[X]) & \leq (1 + \delta) \vol_{\Pbb,r}(\mc{C}^{(1)});
+\end{align*}
 (iv) that the graph volume of $\mc{X}$ is lower bounded,
@@
 It follows from Lemma~\ref{lem:normalized_cut_lb}, Propositions~\ref{prop:sample_to_population_1} and \ref{prop:sample_to_population_2}, and Lemmas~\ref{lem:hoeffding_2} and~\ref{lem:bernstein_union} that these estimates are together satisfied with probability at least $1 - B_4\exp\{-n\delta^2b_8\} - 3\exp\{-n\delta^2 \cut_{\Pbb,r}(\mc{L})\} - (2n + 2)\exp\{-n\delta^2 \cdot d_{\min}(\Pbb)/14\} - 5\exp\{-n\delta^2 \vol_{\Pbb,r}(\mc{L} \cap \mc{C}^{(1)})\} \geq 1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$.
-
-\paragraph{Proof of Theorem~\ref{thm:ppr_lb}.}
+\\
+
+\noindent \emph{Proof of Theorem~\ref{thm:ppr_lb}.}
 As mentioned, we would like to use Theorem~\ref{thm:normalized_cut_ppr} to upper bound $\Phi_{n,r}(\wh{C})$, and so we first verify that the conditions of Theorem~\ref{thm:normalized_cut_ppr} are met.
@@
 	\begin{equation}
+	\begin{aligned}
 	\label{pf:ppr_lb_2}
-		\vol_{n,r}(X) \geq n(n - 1)(1 - \delta) \vol_{\Pbb,r}(\mc{X}) \geq 2n(n - 1) (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \geq 2\frac{(1 - \delta)}{(1 + \delta)} \vol_{n,r}(\mc{L}[X]) \geq \frac{3}{2} \vol_{n,r}(\mc{L}[X]).
+	\vol_{n,r}(X) & \geq n(n - 1)(1 - \delta) \vol_{\Pbb,r}(\mc{X}) \\
+	& \geq 2n(n - 1) (1 - \delta) \vol_{\Pbb,r}(\mc{L}) \geq 2\frac{(1 - \delta)}{(1 + \delta)} \vol_{n,r}(\mc{L}[X]) \\
+	& \geq \frac{3}{2} \vol_{n,r}(\mc{L}[X]).
+	\end{aligned}
 	\end{equation}
@@
 \begin{equation}
+\begin{aligned}
 \label{pf:ppr_lb_3}
-	\frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+&\frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \\
+& \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+\end{aligned}
 \end{equation}
@@
 \end{align*}
-	where in $\mathrm{(i)}$ we have used $\vol_{\Pbb,r}(\mc{L}) \leq 3 \vol_{\Pbb,r}(\mc{C}^{(1)})$, and in $\mathrm{(ii)}$ and $\mathrm{(iii)}$ we have used $\delta \in (0,1/7)$.
-
-\paragraph{Proof of Lemma~\ref{lem:normalized_cut_lb}.}
+where in $\mathrm{(i)}$ we have used $\vol_{\Pbb,r}(\mc{L}) \leq 3 \vol_{\Pbb,r}(\mc{C}^{(1)})$, and in $\mathrm{(ii)}$ and $\mathrm{(iii)}$ we have used $\delta \in (0,1/7)$. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:normalized_cut_lb}.}
 To lower bound the normalized cut $\Phi_{n,r}(Z)$, it suffices to lower bound $\cut_{n,r}(Z)$ and upper bound $\vol_{n,r}(Z)$. A crude upper bound on the volume is simply 
@@
 
-	Now, we fill in the details, working step-by-step.
-
-	\emph{\underline{Step 1: Discretization}.}
+Now, we fill in the details, working step-by-step.\\
+
+\noindent \emph{Step 1: Discretization.}
 We begin by discretizing $\mc{X}$ into a collection of bins.
@@
 \begin{equation*}
-	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{12\sigma}{r}\Bigr] \times \Bigl[\frac{4\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
+\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{12\sigma}{r}\Bigr] \times \Bigl[\frac{4\rho}{r}\Bigr]~~\textrm{s.t.}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
 \end{equation*}
@@
 \end{equation}
-	To establish the last inequality, we reason as follows: first, for every cube $Q_{(k_1,k_2)} \in \partial\overline{Z}$, there exists a cube $Q_{(\ell_1,\ell_2)} \not\in \overline{Z}$ such that $\norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 \leq 1$; second, since each cube has side length $r/4$, this implies that for every $x_i \in Q_{(k_1,k_2)}$ and $x_j \in Q_{(\ell_1,\ell_2)}$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
-
-	\emph{\underline{Step 2: Slicing}.}
+To establish the last inequality, we reason as follows: first, for every cube $Q_{(k_1,k_2)} \in \partial\overline{Z}$, there exists a cube $Q_{(\ell_1,\ell_2)} \not\in \overline{Z}$ such that $\norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 \leq 1$; second, since each cube has side length $r/4$, this implies that for every $x_i \in Q_{(k_1,k_2)}$ and $x_j \in Q_{(\ell_1,\ell_2)}$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.\\
+
+\noindent \emph{Step 2: Slicing.}
 Now we move on lower bounding the size of the discretized boundary $\abs{\partial\wb{Z}}$.
 To do so, we divide $\mathcal{X}$ into slices horizontally.
-Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{4}r, -\frac{\rho}{2} + \frac{k}{4}r\bigr]}$ be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{12\sigma}{r}]}$ be the binned version of $R_k$.
-For every $k$, we are in one of three cases:
+Let $$R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{4}r, -\frac{\rho}{2} + \frac{k}{4}r\bigr]}$$
+be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{12\sigma}{r}]}$ be the binned version of $R_k$. For every $k$, we are in one of three cases:
 \begin{enumerate}
@@
 \end{align}
-	for all $Z \subset X$.
-
-	\emph{\underline{Step 3: Probabilistic guarantees.}}
+for all $Z \subset X$.\\
+
+\noindent \emph{Step 3: Probabilistic guarantees.}
 It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
@@
 \end{equation*}
-	for all $Z \subseteq X$.
-
-\section{Additional results: aPPR and Consistency of PPR}
+for all $Z \subseteq X$. \qed
+
+\section{Additional Results: aPPR and Separation of Clusters via PPR}
 \label{apdx:appr_misclassification_error}
@@
 
-\subsection{Generic cluster recovery with aPPR}
+\subsection{Generic Cluster Recovery with aPPR}
 \label{subsec:appr_volume_ssd_ub}
@@
 \end{corollary}	
-\paragraph{Proof of Corollary~\ref{cor:appr}.}
+\emph{Proof of Corollary~\ref{cor:appr}.}
 Note that the choice of $\varepsilon$ in~\eqref{eqn:appr_parameter} implies $\varepsilon \leq 1/\bigl(25\vol_{n,r}(\mc{C}[X])\bigr)$ with probability at least $1 - \exp\bigl\{-n\delta^2\vol_{\Pbb,r}(\mc{C})\bigr\}$.
 The proof of Corollary~\ref{cor:appr} is then identical to that of Theorem~\ref{thm:volume_ssd_ub}, except one uses Corollary~\ref{cor:zhu} rather than Lemma~\ref{lem:zhu} to relate the symmetric set difference to the graph normalized cut and mixing time.
-
-\subsection{Perfectly distinguishing two density clusters}
+\qed
+
+\subsection{Perfectly Distinguishing Two Density Clusters}
 \label{subsec:consistent_recovery_density_clusters}
@@
 
-Now we recall some probabilistic estimates before proceeding to the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.
-
-\paragraph{Probabilistic estimates.}
+Now we recall some probabilistic estimates before proceeding to the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.\\
+
+\noindent \emph{Probabilistic estimates.}
 As in the proof of Theorem~\ref{thm:volume_ssd_ub}, we will assume that the inequalities~\eqref{eqn:sample_to_population_normalized_cut}-\eqref{eqn:sample_to_population_conductance} and~\eqref{pf:volume_ssd_ub_1}-\eqref{pf:volume_ssd_ub_3} are satisfied.
@@
 \end{equation}
-By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities hold with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 1)\exp\{-b_3n\} - (3n + 3)\exp\{-b_7\delta^2n\}$, taking $b_7 := b_2 \wedge \Pbb(\mc{C}_{\lambda,\sigma}') \cdot d_{\min}(\Pbb')/9$.
+By Propositions~\ref{prop:sample_to_population_1}-\ref{prop:sample_to_population_2} and Lemmas~\ref{lem:hoeffding_2}-\ref{lem:bernstein_union}, these inequalities hold with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (n + 1)\exp\{-b_3n\} - (3n + 3)\exp\{-b_7\delta^2n\}$, taking $b_7 := b_2 \wedge \Pbb(\mc{C}_{\lambda,\sigma}') \cdot d_{\min}(\Pbb')/9$.\\
 
 % AJG: The term after \wedge is needed to condition on the two new inequalities.
-\paragraph{Proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.}
+\noindent \emph{Proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.}
 We have already verified in the proof of Theorem~\ref{thm:volume_ssd_ub} that $\alpha \leq 1/(2\tau_{\infty}(\wt{G}_{n,r}))$, and we may therefore apply Lemma~\ref{lem:ppr_uniform_bound}, which gives a lower bound on $p_v(u)$ for all $u \in \mc{C}_{\lambda,\sigma}[X]_o$ and an upper bound on $p_v(u')$ for all $p_v(u')$ for all $u' \in \mc{C}_{\lambda,\sigma}'[X]_o$.
@@
 \end{align*}
-completing the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}.
+completing the proof of Theorem~\ref{thm:density_cluster_consistent_recovery}. \qed
 
@@
 
-\subsection{Experimental settings for Figure~\ref{fig:bounds}}
+\subsection{Experimental Settings for Figure~\ref{fig:bounds}}
 Let $\mc{R}_{\sigma,\rho} = [-\sigma/2,\sigma/2] \times [-\rho/2,\rho/2]$ be the two-dimensional rectangle of width $\sigma$ and height $\rho$, centered at the origin.
@@
 The first column consists of the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the PPR plus minimum normalized sweep cut cluster, with hyperparameter $\alpha$ and all sweep cuts considered; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{bresson2013}; and the last column shows a cut of the density cluster tree estimator of \cite{chaudhuri2010}.
-
-\paragraph{Performance of PPR with high-dimensional noise.} Figure \ref{fig:moons_hd} is similar to Figure \ref{fig:moons} of the main text, but with parameters
+\\
+
+\noindent \emph{Performance of PPR with high-dimensional noise.} Figure \ref{fig:moons_hd} is similar to Figure \ref{fig:moons} of the main text, but with parameters
 \begin{equation*}
@@
 		\end{subfigure}
-		\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
+		\caption{\small True density (column 1), PPR (column 2), minimum normalized
 			cut (column 3) and estimated density (column 4) clusters for two-moons with 10 dimensional noise. Seed node for PPR denoted by a black cross.} 
@@
 \end{figure}
+
+\bibliography{local_spectral_bibliography}
+
+\end{document}

### 2021-12-23 neurips/local_spectral_density_clustering_arxiv.tex

@@
 	\begin{align}
-	\frac{\degminwt}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
+	\frac{\degminwt}{n - 1} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
 	\frac{\degmax}{n} & \leq (1 + \epsilon)\Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
@@
 	\begin{align}
-	\frac{\degmin}{n} \geq (1 - \epsilon)\frac{6}{25}\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
+	\frac{\degmin}{n - 1} \geq (1 - \epsilon)c\lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} 
 	\end{align}
@@
 \begin{proof}
-	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
-	\end{equation*}
-	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
-	\begin{equation*}
-	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
+	We first note that \eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
+Now, we examine~\eqref{eqn: min_cluster_degree_bound}.
+Note that for any $x \in \Csig$, by assumption \ref{asmp: bounded_density} and Lemma~\ref{lem: local_conductance},
+	\begin{equation*}
+	\Ebb(\widetilde{\deg}_{n,r}(x_i)|x_i = x) \geq \frac{6}{25} \lambda_{\sigma}r^d\nu_d,
+	\end{equation*}
+	Conditional on $x_i = x$, the functional $\widetilde{\deg}_{n,r}(x_i)$ is a sum of $n - 1$ independent Bernoulli random variables. Therefore by Lemma \ref{lem: multiplicative_Hoeffding}
+	\begin{equation*}
+	\Pbb\left(\widetilde{\deg}_{n,r}(x_i) \leq (n-1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \mid x_i = x \right) \leq \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} }
+	\end{equation*}
+	Since this holds for all $x \in \Csig$, by the law of total probability it holds unconditionally as well, i.e.
+	\begin{equation*}
+	\Pbb\left(\widetilde{\deg}_{n,r}(x_i) \leq (n - 1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} }
+	\end{equation*}
+	Taking a union bound over all $x_i \in \Csig[\Xbf]$ (of which, of course, there are no more $n$), we have
+	\begin{equation*}
+	\Pbb \left(\degminwt \leq (n - 1) (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
 	\end{equation*}
 	and we have shown \eqref{eqn: min_cluster_degree_bound}.
-Under \ref{asmp: C'_bounded_density}, the same bound holds for $\degminpr$, and \eqref{eqn: min_cluster_degree_bound_2} follows.
-\eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.
-
-	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.
-
-	Finally, note that
+The equivalent bound \eqref{eqn: max_degree_bound} on maximum degree of vertices $x \in \Csig[\Xbf]$ follows from similar reasoning.
+Under~\ref{asmp: C'_bounded_density} [or \ref{asmp: valid_region}], equivalent reasoning leads to \eqref{eqn: min_cluster_degree_bound_2}[or \eqref{eqn: min_degree_bound}].
+Additionally, taking $\epsilon_n \downarrow 0$ sufficiently slowly so that
+	\begin{equation*}
+	\sum_{n = 1}^{\infty }n \exp\set{- \frac{6 n \epsilon_n^2  \lambda_{\sigma} r^d \nu_d}{50} } < \infty
+	\end{equation*}
+	application of the Borel-Cantelli Lemma yields~\eqref{eqn: min_cluster_degree_bound_asymp}.
+
+	We next prove~\eqref{eqn: volwt_bound}, which is only slightly more involved. Note that
 	\begin{equation*}
@@
 	\begin{equation*}
-	\int_{\Csig} \Pbb(B(x,r)) \dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
-	\end{equation*}
-
-	Therefore by Lemma \ref{lem: bounded_difference}
+	\Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right) = \int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x)
+	\end{equation*}
+	\noindent so that by Lemma \ref{lem: bounded_difference}
 	\begin{equation}
 	\label{eqn: ball_bounds_in_probability_1}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
-	\end{equation}
-	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \dx) \to 0$ as $n \to \infty$.
-Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx$ given by \eqref{eqn: initialization}, yields
-	\begin{equation*}
-	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx \leq \frac{1}{2} \vol_0.
-	\end{equation*}
-
-	By similar reasoning to \eqref{eqn: ball_bounds_in_probability_1}, for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r) \dx) \geq \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x) }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) \dx 
+	\end{equation}
+	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) \,d\Pbb(x))$.
+Assume \eqref{eqn: ball_bounds_in_probability_1} holds; then, since by \eqref{eqn: initialization} the volume estimate $\vol_0$ must lie in $[3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x)$, we obtain
+	\begin{equation*}
+	\abs{\vol_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x) \leq \frac{1}{2} \vol_0.
+	\end{equation*}
+	with probability tending to $0$ as $n \to \infty$. This shows \eqref{eqn: volwt_bound}.
+
+	In fact,  for any $\epsilon > 0$, letting $\mu = \int_{\Csig} \Pbb(B(x,r)) \,d\Pbb(x) = \Ebb\left(\frac{\widetilde{\vol}_{n,r}(\Csig[\Xbf])}{n(n-1)}\right)$ we have
 	\begin{equation*}

### 2021-12-23 notes/reference_notes/nonparametric_clustering.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbb{I}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}

%%% Vector spaces
\newcommand{\Zbb}{\mathbb{Z}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\ol}[1]{\overline{#1}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Nonparametric clustering}
\author{Alden Green}
\date{\today}
\maketitle

The articles summarized in this document are about one of two types of nonparametric clustering: either latent membership recovery in the nonparametric mixture model, or density clustering.

\section{Optimal construction of $k$-nearest neighbor graphs for identifying noisy clusters(Maier09).}

\section{Clustering Based on Pairwise Distance When the Data is of Mixed Dimensions(Arias-Castro09).}

We begin by specifying the idealized generative model under which we observe data $x_1, \ldots, x_N \subset [0,1]^D$. For a positive integer $d \leq D$, and a constant $\kappa \geq 1$, let $\mathcal{S}_{d}(\kappa)$ be the class of measurable, connected sets (surfaces) $S \subset [0,1]^D$ such that
\begin{equation*}
\forall x \in S: \kappa^{-1}\epsilon^d \leq \vol_d(B(x,\epsilon) \cap \mathcal{S}) \leq \kappa \epsilon^d, \quad \textrm{for all $\epsilon \in [0,\diam(S)]$}
\end{equation*}
(Note that this contains the image $f([0,1]^d)$ of locally bi-Lipschitz functions $f: [0,1]^d \to [0,1]^D$ satisfying:
\begin{equation*}
M^{-1} \norm{b - a} \leq \norm{f(b) - f(a)} \leq M \norm{b - a}, \quad \textrm{for all $a,b \in [0,1]^d,$}
\end{equation*}
for $M$ small enough.

For $S \subset \mathcal{X}$ and $\tau > 0$, define
\begin{equation*}
B(S,\tau) = \set{x \in [0,1]^D: \min_{y \in S} \norm{x - y} \leq \tau}.
\end{equation*}
Given cluster $S_1, \ldots, S_{K} \in \mathcal{S}(\kappa)$, we generate clusters $\mathcal{X}_1, \ldots, \mathcal{X}_K$ by sampling $N_k$ points in $B(S_k, \tau)$ according to distribution $\Psi_k$, with density $\psi_k$ with respect to the uniform distribution over $B(S_k,\tau)$. We require that $\kappa^{-1} \leq \psi_k \leq \kappa$, so that the cluster is somewhat uniformly sampled. Letting $N = N_k$, we therefore observe points $\set{x_1, \ldots, x_N} = \cup_{k = 1}^{K} \mathcal{X}_k$.

Assume that the underlying surfaces are well-separated:
\begin{equation*}
\mathrm{dist}(S_k,S_{\ell}) \geq \delta
\end{equation*}
so that the actual clusters are separated by a distance of at least $\delta - 2\tau$. Our task is as follows: given data $\set{x_1, \ldots, x_N}$, recover the clusters $\mathcal{X}_1, \ldots, \mathcal{X}_K$.

\section{Data Spectroscopic Clustering(Shi09)}

Let $K(x,y)$ be a positive semi-definite kernel function over $\Reals^d$. Given a distribution $P$, define the convolution operator $\mathcal{K}_{P}:L^2(P) \to L^2(P)$ to be
\begin{equation*}
\mathcal{K}_Pf(x) = \int_{\Reals^d} K(x,y) f(y) \,dP(y).
\end{equation*}

Assume that 
\begin{equation*}
\iint K^2(x,y) \,dP(y) \,dP(x) < \infty
\end{equation*}
so that $\mathcal{K}_P$ is a trace class operator, and is therefore compact and has a discrete spectrum, which we denote by $\lambda_0 \geq \lambda_1 \geq \cdots \geq 0$. Let $\phi_k$ be the eigenfunction associated with eigenvalue $\lambda_k$, i.e. $\lambda_k \phi_k = \mathcal{K}_P \phi_k$ and $\norm{\phi_k}_{L^2(P)} = 1$.

The first pair of theorems detail basic properties of the eigenfunctions of $\mathcal{K}_P$.

\begin{theorem}[Tail decay property of eigenfunctions]
	\label{thm:shi_1}
	An eigenfunction $\phi$ with eigenvalue $\lambda > 0$ of $\mathcal{K}_P$ satisfies
	\begin{equation*}
	\abs{\phi(x)} \leq \frac{1}{\lambda} \sqrt{\int K^2(x,y) \,dP(y) }.
	\end{equation*}
\end{theorem}

\begin{theorem}
	\label{thm:shi_2}
	Let $K(x,y)$ have full support on $\Rd$. The top eigenfunction $\phi_0(x)$ of the convolution operator $\mathcal{K}_{P}$:
	\begin{enumerate}
		\item is the only eigenfunction with no sign change on $\Rd$;
		\item has multiplicity one;
		\item is nonzero everywhere on $\Rd$.
	\end{enumerate}
\end{theorem}
\begin{proof}
	We will prove the theorem through the following steps:
	\begin{enumerate}
		\item We review basic facts of integration.
		\item We show that $\phi_0$ must have constant sign $P$-a.e.
		\item We show that $\phi_0$ must be have no sign change, and must be supported, everywhere on $\Rd$.
		\item We show that $\phi_0$ has multiplicity one.
	\end{enumerate}

	\textbf{1. Basic integration facts.}

	Let $\mu$ be a measure over $(A,\Sigma)$, and let $R \in \Sigma$ satisfy $\mu(R) > 0$. Then, if $f,g$ are measurable functions from $A$ to $\Reals$, 
	\begin{equation*}
	f > g \quad \textrm{implies} \int_R f \,d\mu > \int_R g \,d\mu.
	\end{equation*}

	\textbf{2. Sign change on the support of $P$}

	Let $R$ denote the support of $P$. Let $R^+ = \set{x \in \Rd: \phi(x) > 0}$ and let $R^- = \set{x \in \Rd: \phi(x) < 0}$. We will show that either $P(R^+) = 0$ or $P(R^-) = 0$.

	Assume not. Then, let $\bar{\phi_0} = \abs{\phi_0}$, and let $g(x,y) = K(x,y) \phi_0(x) \phi_0(y)$ and likewise $\overline{g}(x,y) = K(x,y) \overline{\phi}_0(x) \overline{\phi}_0(y)$. Then,
	\begin{equation*}
	\iint \ol{g}(x,y) \,dP(y) \,dP(x) = \iint_{R^+ \times R^+} g(x,y) \,dP(y) \,dP(x) + \iint_{R^- \times R^-} g(x,y) \,dP(y) \,dP(x) + 2 \iint_{R^+ \times R^-} \ol{g}(x,y) \,dP(y) \,dP(x).
	\end{equation*}
	However, $\overline{g}(x,y) > 0 > g(x,y)$ for all $(x,y) \in R^+ \times R^-$. Therefore, by 1. $\iint \ol{g}(x,y) \,dP(y) \,dP(x) > \iint {g}(x,y) \,dP(y) \,dP(x)$ unless either $P(R^+)$ or $P(R^-) = 0$.

	\textbf{3. Sign change over $\Reals^d$.}
	Assume without loss of generality that $\phi(y) \geq 0$, $P$-a.e. Next, observe that $\lambda_0 > 0$ (try $\phi = \1(x \in R)$ as a test function)
	\begin{equation*}
	\lambda_0 \phi_0(x) = \int K(x,y) \phi_0(y) \,dP(y) = \int_{R} K(x,y) \phi_0(y) \,dP(y).
	\end{equation*}
	It immediately follows that $\phi_0(x) \geq 0$ for all $x \in \Rd$. Moreover, if $\phi_0(x) = 0$, $K(x,y) \phi_0(y) = 0$ everywhere except a set $S$ such that $P(S) = 0$. Since $K(x,y) > 0$ for all $x,y$, this means $\phi_0(y) = 0$, everywhere except a set $S$ such that $P(S) = 0$. However, that implies $\lambda_0 = 0$, which is a contradiction. Therefore, for all $x \in \Rd$, $\phi_0(x) > 0$.

	\textbf{4. Multiplicity one.}
	If $\lambda_0$ has multiplicity more than one, then there exist $\phi_0$ and $\wt{\phi}_0$, which are both positive everywhere on $\Rd$. But then
	\begin{equation*}
	\iint \phi_0(x) \wt{\phi}_0(y) \,dP(x) \,dP(y) > 0
	\end{equation*}
	which contradicts orthogonality of eigenfunctions.
\end{proof}

Next, we perform some perturbation analysis.

\begin{theorem}[Top eigenvalue of mixture distribution.]
	\label{thm:shi_3}
	Let $P = \pi_1 P_1 + \pi_2 P_2$ be a mixture distribution on $\Rd$ with $\pi_1 + \pi_2 = 1$. Denote the top eigenvalue of $\mathcal{K}_P$, $\mathcal{K}_{P_1}$ and $\mathcal{K}_{P_2}$ as $\lambda_0$, $\lambda_{0,1}$ and $\lambda_{0,2}$, respectively. Then $\lambda_0$ satisfies
	\begin{equation*}
	\max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\} \leq \lambda_0 \leq \max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\} + r
	\end{equation*}
	where
	\begin{equation*}
	r = \left[\pi_1 \pi_2 \iint K^2(x,y) \,dP_1(y) \,dP_2(x)\right]^{1/2}
	\end{equation*}
\end{theorem}
\begin{proof}
	Assume Letting $g(x,y) = K(x,y) f(y)$, we have that for any $f \in L^2(P)$ with $\norm{f}_{L^2(P)} = 1$,
	\begin{align}
	\dotp{\mathcal{K}_Pf}{f} & = \int \left(\pi_1 \int g(x,y) \,dP_1(x) + \pi_2 \int g(x,y)\,dP_2(x)\right) f(y) \,dP(y) \nonumber \\
	& = \pi_1^2 \iint g(x,y) f(y) \,dP_1(x) \,dP_1(y) +  \pi_2^2 \iint g(x,y) f(y) \,dP_2(x) \,dP_2(y) + 2 \pi_1 \pi_2 \iint g(x,y) f(y) \,dP_2(x) \,dP_1(y)  \label{eqn:shi_1}
	\end{align}
	Using the Cauchy-Schwarz inequality and the identity $2\sqrt{ab} \leq a + b$ when $a,b > 0$, we upper bound the final term as follows:
	\begin{align*}
	2 \pi_1 \pi_2 \iint g(x,y) f(y) \,dP_2(x) \,dP_1(y) & \leq 2 \pi_1 \pi_2  \left(\iint K^2(x,y) \,dP_2(x) \,dP_1(y)\right)^{1/2} \times \left(\iint f^2(x) f^2(y)  \,dP_2(x) \,dP_1(y)\right)^{1/2} \\
	& \leq \left(\pi_1 \pi_2 \iint K^2(x,y) \,dP_2(x) \,dP_1(y)\right)^{1/2} \times \left(\pi_1 \int f^2(x) \,dP_1(x) + \pi_2 \int f^2(x)\,dP_2(x)\right) \\
	& = r.
	\end{align*}
	It is not hard to bound the first two terms of \eqref{eqn:shi_1},
	\begin{equation*}
	\pi_1^2 \iint g(x,y) f(y) \,dP_1(x) \,dP_1(y) +  \pi_2^2 \iint g(x,y) f(y) \,dP_2(x) \,dP_2(y) \leq \pi_1^2 \lambda_{0,1} + \pi_2^2 \lambda_{0,2} \leq \max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\}
	\end{equation*}
	which proves the desired upper bound on $\dotp{\mathcal{K_P}f}{f}$ for all unit norm $f$, and therefore on $\lambda_0$. The lower bound is trivial.
\end{proof}

\begin{lemma}
	Consider an operator $\mathcal{K}_P$ with the discrete spectrum $\lambda_0 \geq \lambda_1 \geq \cdots$. 
	\begin{enumerate}
		\item If 
		\begin{equation*}
		\norm{\mathcal{K}_P - \lambda f}_{L^2(P)} \leq \epsilon
		\end{equation*}
		for some $\lambda,\epsilon> 0$ and $f \in L^2(P), \norm{f}_{L^2(P)} = 1$, then $\mathcal{K}_P$ has an eigenvalue $\lambda_k$ such that $\abs{\lambda_k - \lambda} \leq \epsilon$. 
		\item If we further assume that $s = \min_i: \abs{\lambda_i - \lambda_k} = s > \epsilon$, then $\mathcal{K}_P$ has an eigenfunction $f_k$ corresponding to $\lambda_k$ such that $\norm{f - f_k}_{L^2(P)} \leq \frac{\epsilon}{s - \epsilon}$. 
	\end{enumerate}
\end{lemma}
\begin{proof}
	\item[]
	\textbf{Proof of 1.} Assume $\min_{j}\abs{\lambda_j - \lambda} > 0$, otherwise the statement clearly holds. Then by Cauchy-Schwarz
	\begin{align*}
	1 = \norm{(\mathcal{K}_P - \lambda I) (\mathcal{K}_P - \lambda I)^{-1} f}_{L^2(P)} \leq \epsilon \norm{(\mathcal{K}_P - \lambda I)^{-1} f}_{L^2(P)}  \leq \frac{\epsilon}{\min_{j}\abs{\lambda_j - \lambda}}.
	\end{align*}

	\textbf{Proof of 2.} Let $\lambda_k$ achieve the minimum $\min_{j}\abs{\lambda_j - \lambda}$, and let $g_1,\ldots,g_m$ be an orthonormal basis of the subspace $E_{\lambda_k}$. Note that the projection of $f$ onto $E_{\lambda_k}$,
	\begin{equation*}
	f_k = \dotp{f}{g_1}g_1 + \ldots + \dotp{f}{g_m}g_m,
	\end{equation*}
	is an eigenfunction of $\mathcal{K}_P$ with eigenvalue $\lambda_k$. We will show that $f_k$ is close to $f$ in $L_2(P)$ norm. We have
	\begin{align*}
	(\mathcal{K}_P - \lambda I) f & = (\mathcal{K}_P - \lambda I) f_k + (\mathcal{K}_P - \lambda I) (f - f_k) \\
	& = (\lambda_k - \lambda) f_k + (\mathcal{K}_P - \lambda I) (f - f_k).
	\end{align*}
	We now take norm on each side of the preceding equation. By assumption, $\norm{(\mathcal{K}_P - \lambda I) f} \leq \epsilon$. Moreover, since $f - f_k \in E_{\lambda_k}^{\perp}$, we have
	\begin{equation*}
	\norm{(\lambda_k - \lambda) f_k + (\mathcal{K}_P - \lambda I) (f - f_k)} = \abs{\lambda_k - \lambda} \norm{f_k} + \norm{(\mathcal{K}_P - \lambda I) (f - f_k)}.
	\end{equation*}
	Finally, since $f - f_k \in E_{\lambda_k^{\perp}}$, we have that $\norm{(\mathcal{K}_P - \lambda_k I) (f - f_k)} \geq \min_{j \neq k} \abs{\lambda_j - \lambda_k} \norm{f - f_k} = s \norm{f - f_k}$. Putting the pieces together, we obtain
	\begin{align*}
	\epsilon & \geq \abs{\lambda_k - \lambda} \norm{f_k} + \norm{(\mathcal{K}_P - \lambda I) (f - f_k)} \\
	& \geq \norm{(\mathcal{K}_P - \lambda_k I) (f - f_k)} - \abs{\lambda - \lambda_k} \norm{f - f_k} \\
	& \geq (s - \epsilon) \norm{f - f_k}
	\end{align*}
	and the proof is complete.
\end{proof}

See Remark A.2 of \cite{diaconis08} for an example that \textbf{2.} is tight.

\section{Generalized Density Clustering(Ale + Larry10)}

Suppose we observe data $X_1,\ldots,X_N$ sampled from distribution $P$ with density $p$ on $\Reals^d$. (NOTE: a major point of this paper is that one does not need to assume the existence of a finite density $p$, i.e $P$ may be singular with respect to $d$-dimensional Lebesgue measure. For the purposes of this note, we will ignore this case.) For a given $\lambda > 0$, let $L(\lambda) = \set{x \in \Rd: p(x) \geq \lambda}$ be the $\lambda$-upper level set of $p$, and let $C_1(\lambda),\ldots,C_{k}(\lambda)$ be the $\lambda$ density clusters, i.e. disjoint, connected components such that 
\begin{equation*}
L(\lambda) = \bigcup_{j = 1}^{k} C_j(\lambda).
\end{equation*}

Given finite samples, it is only possible to accurately estimate a biased version of $p$. Let $K_h: \Rd \to \Reals$ be a kernel and let the smoothed density $p_h$ be given by
\begin{equation*}
p_h(x) = \int_{\Rd} K_h(x - y) \,dP(y).
\end{equation*}
We will write the density clusters of $p_h$ as $C_1^{h}(\lambda), \ldots, C_k^{h}(\lambda)$. To estimate $p_h$, we introduce the kernel density estimator
\begin{equation*}
\widehat{p}_h(x) = \frac{1}{n} \sum_{i = 1}^{n} \frac{1}{c_d h^d} K\left(\frac{x - X_i}{h}\right).
\end{equation*}

Under limited conditions -- i.e. much weaker conditions needed than for nonparametric density estimation -- it is possible to estimate the density clusters $C_j(\lambda)$.

\begin{enumerate}[label=(C\arabic*)]
	\item 
	\label{cond:low_noise}There exist positive constants $\gamma, C_1$ and $\overline{\varepsilon}$ such that
	\begin{equation*}
	\mathbb{P}\left(\abs{p(X) - \lambda} < \epsilon\right)\leq C_1 \varepsilon^{\gamma},~~ \forall \varepsilon \in [0,\overline{\epsilon}).
	\end{equation*}

	\item 
	\label{cond:level_set_inclusion}There exist a positive constant $\overline{h}$ and permutation $\sigma$ of $\set{1,\ldots,k}$ such that $\forall h \in (0,\overline{h})$ an all $\lambda' \in (\lambda - \overline{\varepsilon}, \lambda + \overline{\varepsilon})$, 
	\begin{equation*}
	L_h(\lambda') = \bigcup_{j = 1}^{k} C_j^h(\lambda')
	\end{equation*}
	where
	\begin{enumerate}[(a)]
		\item $C_i^h(\lambda') \cap C_j^h(\lambda') = \emptyset$ for all $1 \leq i \leq j \leq k$; 
		\item $C_j(\lambda') \subseteq C_{\sigma(j)}^h(\lambda')$ for all $1 \leq j \leq k$. 
	\end{enumerate}

	\item 
	\label{cond:fringe_bias}There exists a positive constant $C_2$ such that for all $h \in (0,\overline{h})$ and $\lambda' \in (\lambda - \overline{\epsilon},\lambda]$,
	\begin{equation*}
	L(\lambda') = \bigcup_{j = 1}^{k} C_j(\lambda')
	\end{equation*}
	where
	\begin{equation*}
	\mu(\partial C_j(\lambda') \oplus B(0,j)) \leq C_2 h.
	\end{equation*}
\end{enumerate}

The level set risk is defined to be $R^L(p,\widehat{p}_h) = \mathbb{E}(\rho(p,\widehat{p}_h,P))$, where
\begin{equation*}
\rho(r,q,P) = \int_{ \{x: r(x) \geq \lambda\} \vartriangle \{x: q(x) \geq \lambda\}} \,dP(x).
\end{equation*}

\begin{theorem}[Theorem 10]
	Suppose that \ref{cond:low_noise},\ref{cond:level_set_inclusion}, and \ref{cond:fringe_bias} are satisfied. Then there exists a constant $C_L$ such that for any $h \in (0,\overline{h})$ and $\varepsilon \in (0,\overline{\varepsilon})$,
	\begin{equation*}
	R^L(p,\widehat{p}_h) \leq C_L(\varepsilon^{\gamma} + h + e^{-C_K n h^d \epsilon^2}).
	\end{equation*}
	In particular, setting
	\begin{equation*}
	h_n = \left(\frac{\log n}{n}\right)^{\gamma/(2 \xi + d \gamma)} ~~\textrm{and}~~ \varepsilon_n = \sqrt{\frac{\log n}{C_K n h_n^d}}
	\end{equation*}
	we obtain
	\begin{equation*}
	R^L(p, \widehat{p}_{h_n}) = O\left(\max\set{\left(\frac{\log n}{n}\right)^{\gamma \xi/2 \xi + d \gamma}, \frac{1}{n}}\right).
	\end{equation*}
\end{theorem}

\clearpage
\bibliographystyle{plainnat}
\bibliography{../local_spectral_bibliography}

\end{document}

### 2021-12-23 notes/reference_notes/spectral_clustering_gaussian_mixtures.tex

--- 2021-12-23 notes/reference_notes/nonparametric_clustering.tex
@@
 \newcommand{\wt}[1]{\widetilde{#1}}
-\newcommand{\ol}[1]{\overline{#1}}
 
@@
 \begin{document}
-\title{Nonparametric clustering}
+\title{Spectral clustering for the Gaussian Mixture Model (GMM)}
 \author{Alden Green}
@@
 
-The articles summarized in this document are about one of two types of nonparametric clustering: either latent membership recovery in the nonparametric mixture model, or density clustering.
+\section{General setup.}
 
-\section{Optimal construction of $k$-nearest neighbor graphs for identifying noisy clusters(Maier09).}
+\section{The geometry of spectral clustering (Schiebinger, Yu, Wainwright15)}
 
-\section{Clustering Based on Pairwise Distance When the Data is of Mixed Dimensions(Arias-Castro09).}
+(Although this paper is focused on nonparametric mixture model clustering -- latent label identification -- rather than clustering under the (parametric) GMM, Example 2 lays out how the geometric functionals which govern the rates of label identification are affected by mean distance in the GMM.)
 
-We begin by specifying the idealized generative model under which we observe data $x_1, \ldots, x_N \subset [0,1]^D$.
-For a positive integer $d \leq D$, and a constant $\kappa \geq 1$, let $\mathcal{S}_{d}(\kappa)$ be the class of measurable, connected sets (surfaces) $S \subset [0,1]^D$ such that
+We begin by reviewing necessary background.
+We observe data $X_1, \ldots, X_n$ from a given mixture distribution $\overline{\Pbb} = \sum_{m = 1}^{k} w_m \Pbb_m$.
+Form the weighted complete graph $G$ by applying kernel function $k(x,y)$ to pairs of data, and let $L$ be the corresponding normalized Laplacian matrix.
+Let $q_m(x) = \sqrt{k(x,\cdot) \ast p_{\ell}}$ be the \emph{square root kernelized density}, and let $k_m(x,y) = k(x,y)/(q_m(x) q_m(y))$.
+Consider the integral operator $\mathbb{L}_m$, given by
 \begin{equation*}
-\forall x \in S: \kappa^{-1}\epsilon^d \leq \vol_d(B(x,\epsilon) \cap \mathcal{S}) \leq \kappa \epsilon^d, \quad \textrm{for all $\epsilon \in [0,\diam(S)]$}
+\mathbb{L}_{m}f(x) = \int k_m(x,y) f(y) \,dP_m(y).
 \end{equation*}
-(Note that this contains the image $f([0,1]^d)$ of locally bi-Lipschitz functions $f: [0,1]^d \to [0,1]^D$ satisfying:
+The first eigenvector of $\mathbb{L}_m$ is $q_m$.
+The aforementioned geometric functionals in effect allow us to i) bound the perturbation between $\sum_{m = 1}^{k} w_m \mathbb{L}_m$ and $\overline{\mathbb{L}}$, given by
 \begin{equation*}
-M^{-1} \norm{b - a} \leq \norm{f(b) - f(a)} \leq M \norm{b - a}, \quad \textrm{for all $a,b \in [0,1]^d,$}
+\overline{\mathbb{L}} f(x) = \int \overline{k}(x,y) f(y) \,d\overline{\Pbb}(y) 
 \end{equation*}
-for $M$ small enough.
+and ii) show that the $k$ largest eigenvalues of $\sum_{m = 1}^{k} w_m \mathbb{L}_m$ do in fact correspond to the $k$ square root kernelized densities.
 
-For $S \subset \mathcal{X}$ and $\tau > 0$, define
+Now, we may define the aforementioned functionals. These are the \emph{coupling parameter} $\mathbb{C}(\overline{\Pbb})$, given by
 \begin{equation*}
-B(S,\tau) = \set{x \in [0,1]^D: \min_{y \in S} \norm{x - y} \leq \tau}.
+\mathbb{C}(\overline{\Pbb}) = \max_{m = 1,\ldots,k} \norm{k_m - w_m\overline{k}}_{\Pbb_m \otimes \Pbb_m},
 \end{equation*}
-Given cluster $S_1, \ldots, S_{K} \in \mathcal{S}(\kappa)$, we generate clusters $\mathcal{X}_1, \ldots, \mathcal{X}_K$ by sampling $N_k$ points in $B(S_k, \tau)$ according to distribution $\Psi_k$, with density $\psi_k$ with respect to the uniform distribution over $B(S_k,\tau)$.
-We require that $\kappa^{-1} \leq \psi_k \leq \kappa$, so that the cluster is somewhat uniformly sampled.
-Letting $N = N_k$, we therefore observe points $\set{x_1, \ldots, x_N} = \cup_{k = 1}^{K} \mathcal{X}_k$.
+the \emph{similarity parameter} $\mathbb{S}_{\textrm{max}}(\overline{\Pbb})$, given by
+\begin{equation*}
+\mathbb{S}(\Pbb_{\ell}, \Pbb_{m}) = \frac{\int_{\Xset} \int_{\Xset} k(x,y) \,d\Pbb_{\ell}(y) \,d\Pbb_{m}(x)}{\int_{\Xset} \int_{\Xset} k(x,y) \,d\overline{\Pbb}(y) \,d\Pbb_{m}(x)}, \quad \mathbb{S}_{\textrm{max}}(\overline{\Pbb}) = \max_{\ell \neq m}~ \mathbb{S}(\Pbb_{\ell}, \Pbb_{m}),
+\end{equation*}
+and the \emph{indivisibility parameter} $\Gamma_{\textrm{min}}(\overline{\Pbb})$, given by
+\begin{equation*}
+\Gamma(\Pbb) = \inf_{S \subset \Xset }\frac{\int_{S} \int_{S^c} k(x,y) \,d\Pbb_m(y) \,d\Pbb(x)}{p(S)p(S^c)}, \quad \Gamma_{\textrm{min}}(\overline{\Pbb}) = \min_{m = 1,\ldots,k} \Gamma_{\min}(\Pbb_{\ell})
+\end{equation*}
+where $p(S) = \int_{S} \int_{\mathcal{X}} k(x,y) \,d\Pbb(y) \,d\Pbb(x)$.
 
-Assume that the underlying surfaces are well-separated:
-\begin{equation*}
-\mathrm{dist}(S_k,S_{\ell}) \geq \delta
-\end{equation*}
-so that the actual clusters are separated by a distance of at least $\delta - 2\tau$.
-Our task is as follows: given data $\set{x_1, \ldots, x_N}$, recover the clusters $\mathcal{X}_1, \ldots, \mathcal{X}_K$.
+The first two geometric parameters govern the perturbation of $\sum_{m = 1}^{k} w_m \mathbb{L}_m - \overline{\mathbb{L}}.$ In particular, the coupling parameter is needed to upper bound the perturbation due to the change in normalization, $\norm{\sum_{m = 1}^{k}w_m\mathbb{L}_{m,k_m} - \sum_{m = 1}^{k}w_m\mathbb{L}_{m,\overline{k}}}_{\textrm{op}}$, and the similarity parameter is needed to bound the perturbation due to overlap in distributions, $\sum_{m = 1}^{k}w_m\mathbb{L}_{m,\overline{k}} - \overline{\mathbb{L}}$.
+All three geometric parameters govern the $\lambda_k - \lambda_{k+1}$ eigenvalue gap.
 
-\section{Data Spectroscopic Clustering(Shi09)}
-
-Let $K(x,y)$ be a positive semi-definite kernel function over $\Reals^d$. Given a distribution $P$, define the convolution operator $\mathcal{K}_{P}:L^2(P) \to L^2(P)$ to be
-\begin{equation*}
-\mathcal{K}_Pf(x) = \int_{\Reals^d} K(x,y) f(y) \,dP(y).
-\end{equation*}
-
-Assume that 
-\begin{equation*}
-\iint K^2(x,y) \,dP(y) \,dP(x) < \infty
-\end{equation*}
-so that $\mathcal{K}_P$ is a trace class operator, and is therefore compact and has a discrete spectrum, which we denote by $\lambda_0 \geq \lambda_1 \geq \cdots \geq 0$.
-Let $\phi_k$ be the eigenfunction associated with eigenvalue $\lambda_k$, i.e.
-$\lambda_k \phi_k = \mathcal{K}_P \phi_k$ and $\norm{\phi_k}_{L^2(P)} = 1$.
-
-The first pair of theorems detail basic properties of the eigenfunctions of $\mathcal{K}_P$.
-
-\begin{theorem}[Tail decay property of eigenfunctions]
-	\label{thm:shi_1}
-	An eigenfunction $\phi$ with eigenvalue $\lambda > 0$ of $\mathcal{K}_P$ satisfies
-	\begin{equation*}
-	\abs{\phi(x)} \leq \frac{1}{\lambda} \sqrt{\int K^2(x,y) \,dP(y) }.
-	\end{equation*}
-\end{theorem}
-
-\begin{theorem}
-	\label{thm:shi_2}
-	Let $K(x,y)$ have full support on $\Rd$. The top eigenfunction $\phi_0(x)$ of the convolution operator $\mathcal{K}_{P}$:
-	\begin{enumerate}
-		\item is the only eigenfunction with no sign change on $\Rd$;
-		\item has multiplicity one;
-		\item is nonzero everywhere on $\Rd$.
-	\end{enumerate}
-\end{theorem}
-\begin{proof}
-	We will prove the theorem through the following steps:
-	\begin{enumerate}
-		\item We review basic facts of integration.
-		\item We show that $\phi_0$ must have constant sign $P$-a.e.
-		\item We show that $\phi_0$ must be have no sign change, and must be supported, everywhere on $\Rd$.
-		\item We show that $\phi_0$ has multiplicity one.
-	\end{enumerate}
-
-	\textbf{1. Basic integration facts.}
-
-	Let $\mu$ be a measure over $(A,\Sigma)$, and let $R \in \Sigma$ satisfy $\mu(R) > 0$. Then, if $f,g$ are measurable functions from $A$ to $\Reals$, 
-	\begin{equation*}
-	f > g \quad \textrm{implies} \int_R f \,d\mu > \int_R g \,d\mu.
-	\end{equation*}
-
-	\textbf{2. Sign change on the support of $P$}
-
-	Let $R$ denote the support of $P$. Let $R^+ = \set{x \in \Rd: \phi(x) > 0}$ and let $R^- = \set{x \in \Rd: \phi(x) < 0}$. We will show that either $P(R^+) = 0$ or $P(R^-) = 0$.
-
-	Assume not. Then, let $\bar{\phi_0} = \abs{\phi_0}$, and let $g(x,y) = K(x,y) \phi_0(x) \phi_0(y)$ and likewise $\overline{g}(x,y) = K(x,y) \overline{\phi}_0(x) \overline{\phi}_0(y)$. Then,
-	\begin{equation*}
-	\iint \ol{g}(x,y) \,dP(y) \,dP(x) = \iint_{R^+ \times R^+} g(x,y) \,dP(y) \,dP(x) + \iint_{R^- \times R^-} g(x,y) \,dP(y) \,dP(x) + 2 \iint_{R^+ \times R^-} \ol{g}(x,y) \,dP(y) \,dP(x).
-	\end{equation*}
-	However, $\overline{g}(x,y) > 0 > g(x,y)$ for all $(x,y) \in R^+ \times R^-$.
-Therefore, by 1.
-$\iint \ol{g}(x,y) \,dP(y) \,dP(x) > \iint {g}(x,y) \,dP(y) \,dP(x)$ unless either $P(R^+)$ or $P(R^-) = 0$.
-
-	\textbf{3. Sign change over $\Reals^d$.}
-	Assume without loss of generality that $\phi(y) \geq 0$, $P$-a.e. Next, observe that $\lambda_0 > 0$ (try $\phi = \1(x \in R)$ as a test function)
-	\begin{equation*}
-	\lambda_0 \phi_0(x) = \int K(x,y) \phi_0(y) \,dP(y) = \int_{R} K(x,y) \phi_0(y) \,dP(y).
-	\end{equation*}
-	It immediately follows that $\phi_0(x) \geq 0$ for all $x \in \Rd$.
-Moreover, if $\phi_0(x) = 0$, $K(x,y) \phi_0(y) = 0$ everywhere except a set $S$ such that $P(S) = 0$.
-Since $K(x,y) > 0$ for all $x,y$, this means $\phi_0(y) = 0$, everywhere except a set $S$ such that $P(S) = 0$.
-However, that implies $\lambda_0 = 0$, which is a contradiction.
-Therefore, for all $x \in \Rd$, $\phi_0(x) > 0$.
-
-	\textbf{4. Multiplicity one.}
-	If $\lambda_0$ has multiplicity more than one, then there exist $\phi_0$ and $\wt{\phi}_0$, which are both positive everywhere on $\Rd$. But then
-	\begin{equation*}
-	\iint \phi_0(x) \wt{\phi}_0(y) \,dP(x) \,dP(y) > 0
-	\end{equation*}
-	which contradicts orthogonality of eigenfunctions.
-\end{proof}
-
-Next, we perform some perturbation analysis.
-
-\begin{theorem}[Top eigenvalue of mixture distribution.]
-	\label{thm:shi_3}
-	Let $P = \pi_1 P_1 + \pi_2 P_2$ be a mixture distribution on $\Rd$ with $\pi_1 + \pi_2 = 1$.
-Denote the top eigenvalue of $\mathcal{K}_P$, $\mathcal{K}_{P_1}$ and $\mathcal{K}_{P_2}$ as $\lambda_0$, $\lambda_{0,1}$ and $\lambda_{0,2}$, respectively.
-Then $\lambda_0$ satisfies
-	\begin{equation*}
-	\max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\} \leq \lambda_0 \leq \max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\} + r
-	\end{equation*}
-	where
-	\begin{equation*}
-	r = \left[\pi_1 \pi_2 \iint K^2(x,y) \,dP_1(y) \,dP_2(x)\right]^{1/2}
-	\end{equation*}
-\end{theorem}
-\begin{proof}
-	Assume Letting $g(x,y) = K(x,y) f(y)$, we have that for any $f \in L^2(P)$ with $\norm{f}_{L^2(P)} = 1$,
-	\begin{align}
-	\dotp{\mathcal{K}_Pf}{f} & = \int \left(\pi_1 \int g(x,y) \,dP_1(x) + \pi_2 \int g(x,y)\,dP_2(x)\right) f(y) \,dP(y) \nonumber \\
-	& = \pi_1^2 \iint g(x,y) f(y) \,dP_1(x) \,dP_1(y) +  \pi_2^2 \iint g(x,y) f(y) \,dP_2(x) \,dP_2(y) + 2 \pi_1 \pi_2 \iint g(x,y) f(y) \,dP_2(x) \,dP_1(y)  \label{eqn:shi_1}
-	\end{align}
-	Using the Cauchy-Schwarz inequality and the identity $2\sqrt{ab} \leq a + b$ when $a,b > 0$, we upper bound the final term as follows:
+\subsection{Calculations in the Gaussian Mixture Model.}
+Consider the 2-mixture Gaussian $\overline{\mathbb{N}} = \frac{1}{2}\mathbb{N}(0,1) + \frac{1}{2}\mathbb{N}(\mu,1)$, with kernel function $k_{\nu}(x,y) = (2\pi\nu^2)^{-1/2} \exp\{-\abs{x - y}^2/2\nu^2 \}$.
+We begin by computing the similarity parameter $\mathbb{S}_{\max}(\overline{\mathbb{N}})$.
 \begin{align*}
-	2 \pi_1 \pi_2 \iint g(x,y) f(y) \,dP_2(x) \,dP_1(y) & \leq 2 \pi_1 \pi_2  \left(\iint K^2(x,y) \,dP_2(x) \,dP_1(y)\right)^{1/2} \times \left(\iint f^2(x) f^2(y)  \,dP_2(x) \,dP_1(y)\right)^{1/2} \\
-	& \leq \left(\pi_1 \pi_2 \iint K^2(x,y) \,dP_2(x) \,dP_1(y)\right)^{1/2} \times \left(\pi_1 \int f^2(x) \,dP_1(x) + \pi_2 \int f^2(x)\,dP_2(x)\right) \\
-	& = r.
-	\end{align*}
-	It is not hard to bound the first two terms of \eqref{eqn:shi_1},
-	\begin{equation*}
-	\pi_1^2 \iint g(x,y) f(y) \,dP_1(x) \,dP_1(y) +  \pi_2^2 \iint g(x,y) f(y) \,dP_2(x) \,dP_2(y) \leq \pi_1^2 \lambda_{0,1} + \pi_2^2 \lambda_{0,2} \leq \max\{\pi_1 \lambda_{0,1}, \pi_2 \lambda_{0,2}\}
-	\end{equation*}
-	which proves the desired upper bound on $\dotp{\mathcal{K_P}f}{f}$ for all unit norm $f$, and therefore on $\lambda_0$. The lower bound is trivial.
-\end{proof}
-
-\begin{lemma}
-	Consider an operator $\mathcal{K}_P$ with the discrete spectrum $\lambda_0 \geq \lambda_1 \geq \cdots$. 
-	\begin{enumerate}
-		\item If 
-		\begin{equation*}
-		\norm{\mathcal{K}_P - \lambda f}_{L^2(P)} \leq \epsilon
-		\end{equation*}
-		for some $\lambda,\epsilon> 0$ and $f \in L^2(P), \norm{f}_{L^2(P)} = 1$, then $\mathcal{K}_P$ has an eigenvalue $\lambda_k$ such that $\abs{\lambda_k - \lambda} \leq \epsilon$. 
-		\item If we further assume that $s = \min_i: \abs{\lambda_i - \lambda_k} = s > \epsilon$, then $\mathcal{K}_P$ has an eigenfunction $f_k$ corresponding to $\lambda_k$ such that $\norm{f - f_k}_{L^2(P)} \leq \frac{\epsilon}{s - \epsilon}$.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\item[]
-	\textbf{Proof of 1.} Assume $\min_{j}\abs{\lambda_j - \lambda} > 0$, otherwise the statement clearly holds. Then by Cauchy-Schwarz
-	\begin{align*}
-	1 = \norm{(\mathcal{K}_P - \lambda I) (\mathcal{K}_P - \lambda I)^{-1} f}_{L^2(P)} \leq \epsilon \norm{(\mathcal{K}_P - \lambda I)^{-1} f}_{L^2(P)}  \leq \frac{\epsilon}{\min_{j}\abs{\lambda_j - \lambda}}.
+\mathbb{S}_{\max}(\overline{\mathbb{N}}) = \frac{2\exp\{-\mu^2/(2\nu^2 + 4)\}}{1 + \exp\{-\mu^2/(2\nu^2 + 4)\}} \leq 2\exp\{-\mu^2/(2\nu^2 + 4)\}.
 \end{align*}
 
-	\textbf{Proof of 2.} Let $\lambda_k$ achieve the minimum $\min_{j}\abs{\lambda_j - \lambda}$, and let $g_1,\ldots,g_m$ be an orthonormal basis of the subspace $E_{\lambda_k}$.
-Note that the projection of $f$ onto $E_{\lambda_k}$,
-	\begin{equation*}
-	f_k = \dotp{f}{g_1}g_1 + \ldots + \dotp{f}{g_m}g_m,
-	\end{equation*}
-	is an eigenfunction of $\mathcal{K}_P$ with eigenvalue $\lambda_k$. We will show that $f_k$ is close to $f$ in $L_2(P)$ norm. We have
-	\begin{align*}
-	(\mathcal{K}_P - \lambda I) f & = (\mathcal{K}_P - \lambda I) f_k + (\mathcal{K}_P - \lambda I) (f - f_k) \\
-	& = (\lambda_k - \lambda) f_k + (\mathcal{K}_P - \lambda I) (f - f_k).
-	\end{align*}
-	We now take norm on each side of the preceding equation. By assumption, $\norm{(\mathcal{K}_P - \lambda I) f} \leq \epsilon$. Moreover, since $f - f_k \in E_{\lambda_k}^{\perp}$, we have
-	\begin{equation*}
-	\norm{(\lambda_k - \lambda) f_k + (\mathcal{K}_P - \lambda I) (f - f_k)} = \abs{\lambda_k - \lambda} \norm{f_k} + \norm{(\mathcal{K}_P - \lambda I) (f - f_k)}.
-	\end{equation*}
-	Finally, since $f - f_k \in E_{\lambda_k^{\perp}}$, we have that $\norm{(\mathcal{K}_P - \lambda_k I) (f - f_k)} \geq \min_{j \neq k} \abs{\lambda_j - \lambda_k} \norm{f - f_k} = s \norm{f - f_k}$.
-Putting the pieces together, we obtain
-	\begin{align*}
-	\epsilon & \geq \abs{\lambda_k - \lambda} \norm{f_k} + \norm{(\mathcal{K}_P - \lambda I) (f - f_k)} \\
-	& \geq \norm{(\mathcal{K}_P - \lambda_k I) (f - f_k)} - \abs{\lambda - \lambda_k} \norm{f - f_k} \\
-	& \geq (s - \epsilon) \norm{f - f_k}
-	\end{align*}
-	and the proof is complete.
-\end{proof}
-
-See Remark A.2 of \cite{diaconis08} for an example that \textbf{2.} is tight.
-
-\section{Generalized Density Clustering(Ale + Larry10)}
-
-Suppose we observe data $X_1,\ldots,X_N$ sampled from distribution $P$ with density $p$ on $\Reals^d$.
-(NOTE: a major point of this paper is that one does not need to assume the existence of a finite density $p$, i.e $P$ may be singular with respect to $d$-dimensional Lebesgue measure.
-For the purposes of this note, we will ignore this case.) For a given $\lambda > 0$, let $L(\lambda) = \set{x \in \Rd: p(x) \geq \lambda}$ be the $\lambda$-upper level set of $p$, and let $C_1(\lambda),\ldots,C_{k}(\lambda)$ be the $\lambda$ density clusters, i.e.
-disjoint, connected components such that
-\begin{equation*}
-L(\lambda) = \bigcup_{j = 1}^{k} C_j(\lambda).
-\end{equation*}
-
-Given finite samples, it is only possible to accurately estimate a biased version of $p$. Let $K_h: \Rd \to \Reals$ be a kernel and let the smoothed density $p_h$ be given by
-\begin{equation*}
-p_h(x) = \int_{\Rd} K_h(x - y) \,dP(y).
-\end{equation*}
-We will write the density clusters of $p_h$ as $C_1^{h}(\lambda), \ldots, C_k^{h}(\lambda)$. To estimate $p_h$, we introduce the kernel density estimator
-\begin{equation*}
-\widehat{p}_h(x) = \frac{1}{n} \sum_{i = 1}^{n} \frac{1}{c_d h^d} K\left(\frac{x - X_i}{h}\right).
-\end{equation*}
-
-Under limited conditions -- i.e. much weaker conditions needed than for nonparametric density estimation -- it is possible to estimate the density clusters $C_j(\lambda)$.
-
-\begin{enumerate}[label=(C\arabic*)]
-	\item 
-	\label{cond:low_noise}There exist positive constants $\gamma, C_1$ and $\overline{\varepsilon}$ such that
-	\begin{equation*}
-	\mathbb{P}\left(\abs{p(X) - \lambda} < \epsilon\right)\leq C_1 \varepsilon^{\gamma},~~ \forall \varepsilon \in [0,\overline{\epsilon}).
-	\end{equation*}
-
-	\item 
-	\label{cond:level_set_inclusion}There exist a positive constant $\overline{h}$ and permutation $\sigma$ of $\set{1,\ldots,k}$ such that $\forall h \in (0,\overline{h})$ an all $\lambda' \in (\lambda - \overline{\varepsilon}, \lambda + \overline{\varepsilon})$,
-	\begin{equation*}
-	L_h(\lambda') = \bigcup_{j = 1}^{k} C_j^h(\lambda')
-	\end{equation*}
-	where
-	\begin{enumerate}[(a)]
-		\item $C_i^h(\lambda') \cap C_j^h(\lambda') = \emptyset$ for all $1 \leq i \leq j \leq k$; 
-		\item $C_j(\lambda') \subseteq C_{\sigma(j)}^h(\lambda')$ for all $1 \leq j \leq k$. 
-	\end{enumerate}
-
-	\item 
-	\label{cond:fringe_bias}There exists a positive constant $C_2$ such that for all $h \in (0,\overline{h})$ and $\lambda' \in (\lambda - \overline{\epsilon},\lambda]$,
-	\begin{equation*}
-	L(\lambda') = \bigcup_{j = 1}^{k} C_j(\lambda')
-	\end{equation*}
-	where
-	\begin{equation*}
-	\mu(\partial C_j(\lambda') \oplus B(0,j)) \leq C_2 h.
-	\end{equation*}
-\end{enumerate}
-
-The level set risk is defined to be $R^L(p,\widehat{p}_h) = \mathbb{E}(\rho(p,\widehat{p}_h,P))$, where
-\begin{equation*}
-\rho(r,q,P) = \int_{ \{x: r(x) \geq \lambda\} \vartriangle \{x: q(x) \geq \lambda\}} \,dP(x).
-\end{equation*}
-
-\begin{theorem}[Theorem 10]
-	Suppose that \ref{cond:low_noise},\ref{cond:level_set_inclusion}, and \ref{cond:fringe_bias} are satisfied.
-Then there exists a constant $C_L$ such that for any $h \in (0,\overline{h})$ and $\varepsilon \in (0,\overline{\varepsilon})$,
-	\begin{equation*}
-	R^L(p,\widehat{p}_h) \leq C_L(\varepsilon^{\gamma} + h + e^{-C_K n h^d \epsilon^2}).
-	\end{equation*}
-	In particular, setting
-	\begin{equation*}
-	h_n = \left(\frac{\log n}{n}\right)^{\gamma/(2 \xi + d \gamma)} ~~\textrm{and}~~ \varepsilon_n = \sqrt{\frac{\log n}{C_K n h_n^d}}
-	\end{equation*}
-	we obtain
-	\begin{equation*}
-	R^L(p, \widehat{p}_{h_n}) = O\left(\max\set{\left(\frac{\log n}{n}\right)^{\gamma \xi/2 \xi + d \gamma}, \frac{1}{n}}\right).
-	\end{equation*}
-\end{theorem}
-
-\clearpage
-\bibliographystyle{plainnat}
-\bibliography{../local_spectral_bibliography}
-
 \end{document}

### 2021-12-23 notes/weekly_notes/10.11.19.NotesForWeek.tex

@@
 	\end{itemize}
-Set $\alpha = 10\Phi(C)$. Then, for any $v \in C_{\alpha}$,
+Suppose $10\Phi(C) \leq \alpha \leq 20\Phi(C)$. Then, there exists a subset $C_{\alpha} \subset C$ with $\vol(C_{\alpha}) \geq \vol(C)/2$ such that for any $v \in C_{\alpha}$,
 \begin{equation*}
-\Phi(p(\alpha,\chi_v)) \leq \sqrt{1600\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C)}
+\Phi(p(\alpha,\chi_v)) \leq \sqrt{3200\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log 20\right\} \Phi(C)}
 \end{equation*}
@@
 
-To apply Theorem~\ref{thm:mixing_time_PPR_contrapositive} to the specific case of $G$ a neighborhood graph, we will need estimates on the degree and volume graph functionals.
+To apply Theorem~\ref{thm:conductance_ppr} when $G$ is a random geometric graph, we will need estimates on the degree and volume graph functionals.
 These estimates will rely on certain regularity properties of $\mathcal{X}$ and $f$.
 In particular, we will assume
-\begin{itemize}
-	\label{asmp:regularity_conditions}
-	\item There exist $\lambda_{\min}$ and $\lambda_{\max}$ such that for any $x \in \mathcal{X}$:
+\begin{enumerate}[(A)]
+	\item 
+	\label{asmp:regularity_condition_1}
+	There exist $\lambda_{\min}$ and $\lambda_{\max}$ such that for any $x \in \mathcal{X}$:
 	\begin{equation*}
@@
 	\end{equation*}
-	\item There exists some $a > 0$ such that for any $r >0 $ and any $x \in \mathcal{X}$,
+	\item
+	\label{asmp:regularity_condition_2}
+	There exists some $a > 0$ such that for any $r >0 $ and any $x \in \mathcal{X}$,
 	\begin{equation*}
-	\nu(B(x,r) \cap \mathcal{X}) \geq \frac{r^d}{a},
+	\nu(B(x,r) \cap \mathcal{X}) \geq \frac{\nu_d r^d}{a},
 	\end{equation*}
 	where $\nu(\cdot)$ is Lebesgue measure on $\Reals^d$ and $B(x,r)$ is the ball centered at $x$ of radius $r$. 
-\end{itemize}
-We collect our bounds on graph functionals in the following Lemma.
+\end{enumerate}
+We collect our bounds on graph functionals in the following Lemma. Let $\mathcal{S} \subset \mathcal{X}$.
 \begin{lemma}
 	\label{lem:graph_functional_concentration}
-	Suppose $\mathcal{X}$ and $f$ satisfy the regularity properties.
-Fix $\mathcal{S} \subseteq \mathcal{X}$, and write $\mathcal{S}[X] = \mathcal{X} \cap \set{x_1,\ldots,x_n}$.
-For any $\delta \in (0,1)$, suppose
+	Let $X = \set{x_1,\ldots,x_n}$ be sampled independently from $\Pbb$, and let $G := G_{n,r}$ be a neighborhood graph over $X$.
+Suppose $\mathcal{X}$ and $f$ satisfy the regularity properties \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2}.
+Then, for any $\delta \in (0,1)$ and any $r \in (0,\infty)$, there exists numbers $c_1 := c_1(f,\mathcal{X},a)$ and $c_2 := c_2(f,\mathcal{X},a)$ independent of the sample size $n$ such that each of the following bounds hold with probability at least $1 - c_1n\exp\set{-c_2n}$:
+	\begin{itemize}
+		\item $(1 - \delta) \lambda_{\min} \frac{\nu_dr^d}{a} n \leq d_{\min} \leq d_{\max} \leq (1 + \delta) \lambda_{\min} \frac{\nu_dr^d}{a}n$, 
+		\item $(1 - \delta) \mathbb{P}(\mathcal{S}) n \leq \abs{\mathcal{S}[X]} \leq (1 - \delta) \mathbb{P}(\mathcal{S}) n$,
+		\item $(1 - \delta) \mathbb{E}[\vol(\mathcal{S}[X])] \leq \vol(\mathcal{S}[X]) \leq (1 + \delta) \mathbb{E}[\vol(\mathcal{S}[X])]$,
+		\item $(1 - \delta) \mathbb{E}[\mathrm{cut}(\mathcal{S}[X])] \leq \mathrm{cut}(\mathcal{S}[X]) \leq (1 + \delta) \mathbb{E}[\mathrm{cut}(\mathcal{S}[X])]$,
+	\end{itemize}
+\end{lemma}
+The bounds on $d_{\min}$ and $d_{\max}$ follow from standard reasoning, in which we i) use the regularity conditions \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2} to upper and lower bound the expected degree $\mathbb{E}(d(x_i))$ over all $x_i$, ii) apply Bernstein's inequality to obtain bounds on the deviation $\abs{d(x_i) - \mathbb{E}d(x_i)}$ for a given $i$, and  iii) apply a union bound.
+Bernstein's inequality also leads to a bound on the deviation of $\abs{S[X]}$ from its mean.
+Finally, the functionals $\vol(\mathcal{S}[X])$ and $\mathrm{cut}(\mathcal{S}[X])$ are U-statistics and therefore by Hoeffding's inequality concentrate around their respective expectations.
+
+Lemma~\ref{lem:graph_functional_concentration} implies that when the sample size is sufficiently large, the conditions of Theorem~\ref{thm:conductance_ppr} will be met.
+We therefore obtain the following upper bound on the normalized cut of PPR computed on a neighborhood graph.
+\begin{corollary}
+	\label{cor:conductance_ppr_neighborhood_graph}
+	Fix $\mathcal{S} \subset \mathcal{X}$, radius $r \in (0,\infty)$, and $\delta \in (0,1/7]$.
+Suppose $\mathcal{X}$ and $f$ satisfy the regularity properties \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2}, that
 	\begin{equation}
 	\label{eqn:graph_functional_concentration_1}
-	n \geq a \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{\lambda_{\max}}{\lambda_{\min}} \max\set{\frac{1}{\Pbb(\mathcal{S})}, \frac{10a}{(1-\delta)\lambda_{\min}\nu_dr^d}}.
+	n \geq a \frac{(1 + \delta)}{(1 - \delta)^2} \cdot \frac{\lambda_{\max}}{\lambda_{\min}} \max\set{\frac{1}{\Pbb(\mathcal{S})}, \frac{10a}{(1-\delta)\lambda_{\min}\nu_dr^d}},
 	\end{equation}
-	Then there exists constants $c_1,c_2$ independent of $n$ such that following statements hold with probability at least $1 - c_1n\exp\{-c_2n\}$:
-	\begin{itemize}
-		\item $\abs{\mathcal{S}[X]} \geq \frac{d_{\max}}{d_{\min}}$, 
-		\item $\frac{d_{\max}}{2d_{\min}^2} < \frac{1}{20}$. 
-	\end{itemize}
-	If additionally
+	and
 	\begin{equation}
 	\label{eqn:graph_functional_concentration_2}
-	\mathbb{E}[\vol(\mathcal{S}[X])] \leq 2\frac{(1 - \delta)}{(1 + \delta)} \mathbb{E}[\vol((\mathcal{X}\setminus\mathcal{S})[X])]
+	\mathbb{E}[\vol(\mathcal{S}[X])] \leq 2\frac{(1 - \delta)}{(1 + \delta)} \mathbb{E}[\vol((\mathcal{X}\setminus\mathcal{S})[X])],
 	\end{equation}
-	then $\vol(\mathcal{S}[X]) \leq \frac{2}{3} \vol(G)$ with probability at least $1 - c_3n\exp\{-c_4n\}$, where $c_3,c_4$ are constants independent of $n$. 
-\end{lemma}
-
-Together Lemma~\ref{lem:graph_functional_concentration} and Theorem~\ref{thm:mixing_time_PPR_contrapositive} imply the following result.
-\begin{corollary}
-	\label{cor:conductance_ppr_neighborhood_graph}
-	Fix $\mathcal{S} \subset \mathcal{X}$, and $\delta \in (0,1)$. Suppose 
-	\begin{itemize}
-		\item $\mathcal{X}$ and $f$ satisfy the regularity properties,
-		\item  $\mathcal{S}$ satisfies \eqref{eqn:graph_functional_concentration_2} for any $r \in (0,\infty)$, and
-		\item The sample size $n$ satisfies \eqref{eqn:graph_functional_concentration_1},
-		\item The normalized cut $\Phi(\mathcal{S}[X]) \leq \frac{1}{200}$.
-	\end{itemize}.
-	Set $\alpha = \Phi(\mathcal{S}[X])$. For any $v \in \mathcal{S}[X]_{\alpha}$,
+	and that $\Phi_{\Pbb}(\mathcal{S}) \leq \frac{1}{200(1 + \delta)}$.
+Set $\alpha = 15\Phi_{\Pbb}(\mathcal{S})$.
+Then, there exists a set $\mathcal{S}[X]_{\alpha} \subset \mathcal{S}[X]$ with $\vol(\mathcal{S}[X]_{\alpha}) \leq \vol(\mathcal{S}[X])/2$, such that for any $v \in \mathcal{S}[X]_{\alpha}$,
 	\begin{equation*}
-	\Phi(p(\alpha,\chi_v)) \leq \sqrt{1600\left\{2\log\left(\frac{a}{(1 - \delta)\lambda_{\min}\nu_d r^d}\right) + \log 20\right\} \Phi(\mathcal{S}[X])}
+	\Phi(p(\alpha,\chi_v)) \leq \sqrt{3200\left\{2\log\left(\frac{a}{(1 - \delta)\lambda_{\min}\nu_d r^d}\right) + \log 20\right\} \Phi(\mathcal{S}[X])}
 	\end{equation*}
-	with probability at least $1 - cn\exp\set{-cn}$. 
+	with probability at least $1 - c_1n\exp\set{-c_2n}$.
 \end{corollary}
-The important takeaway is that $\Phi(p) \lesssim \sqrt{\Phi(\mathcal{S}[X])}$ (where we write $a_n \lesssim b_n$ when there exists constant $c$ such that $a_n \leq c b_n$ for all $n$.) In particular, we have eliminated the factor of $\log(\vol(G))$ which made upper bounds derived from Theorem~\ref{thm:acl_2} facile as $n,\vol(G) \to \infty$.
+The important takeaway is that $\Phi(p) \lesssim \sqrt{\Phi(\mathcal{S}[X])}$ (where we write $a_n \lesssim b_n$ when there exists constant $c$ such that $a_n \leq c b_n$ for all $n$.) In particular, we have eliminated the factor of $\log(\vol(G))$ which made upper bounds derived from Theorem~\ref{thm:acl_2} facile as the sample size $n$ and the volume $\vol(G) \to \infty$.
 
@@
 where $\Psi_m$ is the uniform distribution over $\mathcal{C}_m$ for $m = 0,1,2$. 
-The density function $f$ of $\Pbb$ is clearly
+The density function $f$ of $\Pbb$ is simply
 \begin{equation*}
@@
 \begin{theorem}
-	Let \textcolor{red}{$\alpha = 10 \Phi_{n,r}(\mathcal{L}[X])$} and $r = \sigma/4$.
-Suppose $\frac{r}{\sigma} < \frac{1}{6400}$.
-Then, there exists a set $C_{\alpha}$ with $\abs{C_{\alpha} \cap \mathcal{C}_1[X]} \geq \abs{\mathcal{C}_1[X]}/6$ such that for any $v \in C_{\alpha}$, the minimum conductance sweep cut $\widehat{C}$ of $p(\alpha,\chi_v)$,
+	Let $\alpha = 15\Phi_{\Pbb}(\mathcal{L})$ and $r = \frac{1}{4}\sigma$.
+Suppose $\sigma < \frac{\rho}{1600}$.
+Then, there exists a set $C_{\alpha}$ with $\abs{C_{\alpha} \cap \mathcal{C}_1[X]} \geq \abs{\mathcal{C}_1[X]}/6$ such that for any $v \in C_{\alpha}$, the minimum conductance sweep cut $\widehat{C}$ of $p(\alpha,\chi_v)$ satisfies
 	\begin{equation*}
-	\frac{\abs{\widehat{C} \triangle \mathcal{C}_1[X]}}{n} \geq 1 - c \frac{1}{\epsilon^2} \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right)\frac{\sigma}{\rho}}
+	\frac{\Delta(\widehat{C},\mathcal{C}_1[X])}{n} \geq 1 - c \frac{1}{\epsilon^2} \sqrt{\log\left(\frac{\rho \sigma}{\epsilon\sigma^d}\right)\frac{\sigma}{\rho}}
 	\end{equation*}
-	with probability at least $1 - c_1 n \exp\set{-c_2n}$, where $c_1,c_2$ are constants which do not depend on $n$.
+	with probability at least $1 - c_1 n \exp\set{-c_2n}$, where $c, c_1,c_2$ are constants which do not depend on $n$.
 \end{theorem}
@@
 	\begin{enumerate}
-		\item $\Phi(\mathcal{L}[X]) \leq 32 \frac{r}{\rho}$, and
+		\item $\Phi_{n,r}(\mathcal{L}[X]) \leq 32 \frac{r}{\rho}$, and
 		\item For any set $A \subset X$,
@@
 \subsection{Proof of Theorem~\ref{thm:conductance_ppr}.}
-Since $\alpha = 10\Phi(C)$ and $v \in C_{\alpha}$, by Theorem~\ref{thm:acl_3},
+Since $\alpha \geq 10\Phi(C)$ and $v \in C_{\alpha}$, by Theorem~\ref{thm:acl_3},
 \begin{equation*}
@@
 \begin{equation*}
-\Phi(p(\alpha,\chi_v)) \leq \sqrt{\frac{160\Phi(C)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
+\Phi(p(\alpha,\chi_v)) \leq \sqrt{\frac{320\Phi(C)\left\{\log\left(\frac{m}{d_{\min}^2}\right) + \log\left(\frac{2}{\delta'}\right)\right\}}{\delta'}}
 \end{equation*}
@@
 completing the proof of the theorem.
+
+\subsection{Proof of Corollary~\ref{cor:conductance_ppr_neighborhood_graph}.}
+
+Since we assume $\mathcal{X}$ and $f$ satisfy the regularity conditions \ref{asmp:regularity_condition_1} and \ref{asmp:regularity_condition_2}, the inequalities in Lemma~\ref{lem:graph_functional_concentration} hold with probability at least $1 - n c_5 \exp\set{-c_6n}$.
+We will condition on these inequalities throughout.
+
+We now verify that the conditions required to apply Theorem~\ref{thm:conductance_ppr} are met.
+The first two results in Lemma \ref{lem:graph_functional_concentration} imply that $\frac{d_{\max}}{d_{\min}} \lesssim \abs{S[X]}$ and $\frac{d_{\max}}{d_{\min}^2} \lesssim 1$; the lower bound on $n$ given in \eqref{eqn:graph_functional_concentration_1} ensures that these bounds hold exactly.
+
+Since we additionally assume that $\Phi_{\Pbb}(\mathcal{S}) \leq \frac{1 - \delta}{200(1 + \delta)}$, the third and fourth results in Lemma \ref{lem:graph_functional_concentration} imply the third condition in Theorem~\ref{thm:conductance_ppr} is also met.
+Finally, setting $\alpha = 15\Phi_{\Pbb}(\mathcal{S})$, these results imply that
+\begin{equation*}
+10 \Phi(S)\leq 15\frac{(1 - \delta)}{1 + \delta} \Phi(S)\leq \alpha \leq 15\frac{(1 + \delta)}{1 - \delta} \Phi(S) \leq 20 \Phi(S)
+\end{equation*}
+where the first and last inequalities follow since $\delta \leq 1/7$. We may therefore apply Theorem~\ref{thm:conductance_ppr} and obtain that
+\begin{equation*}
+\Phi(p(\alpha,\chi_v)) \leq \sqrt{3200\left\{\log\left(\frac{\vol(G)}{d_{\min}^2}\right) + \log 20\right\} \Phi(C)}
+\end{equation*}
+Using the (potentially loose) bound $\vol(G) \leq n^2$, Corollary~\ref{cor:conductance_ppr_neighborhood_graph} follows from the first result in Lemma~\ref{lem:graph_functional_concentration}.
+
 \section{Technical results.}
@@
 \subsection{Concentration Inequalities.}
+\label{subsec:concentration}
 
@@
 
+\section{Old Stuff.}
+\subsection{Proof of Lemma~\ref{lem:graph_functional_concentration}.}
+Each statement in Lemma~\ref{lem:graph_functional_concentration} is a standard consequence of the concentration results of \ref{subsec:concentration}.
+For each $i = 1,\ldots,n$, conditional on $x_i$ the degree functional $d(x_i)$ follows a binomial distribution $d(x_i) \sim \textrm{Bin}(n - 1, \Pbb(B(x_i,r)))$.
+Moreover by the regularity properties, for any $x \in \mathcal{X}$,
+\begin{equation*}
+\lambda_{\min} \frac{\nu_d r^d}{a} \leq \Pbb(B(x,r)) \leq \lambda_{\max} \nu_d r^d.
+\end{equation*}
+Therefore, for any $\delta > 0$, applying Bernstein's inequality and a union bound yields
+\begin{equation}
+\label{eqn:graph_functional_concentration_pf1}
+\lambda_{\min} (1 - \delta) \frac{\nu_d r^d}{a} n \leq d_{\min} \leq d_{\max} \leq  \lambda_{\max} (1 - \delta) \nu_d r^d n
+\end{equation}
+with probability at least $1 - 2 n\exp\set{-\frac{\delta^2 n \lambda_{\min} \nu_d r^d}{a\left(1 + \frac{\delta}{3}\right)}}$. Additionally $\abs{S[X]} \sim \mathrm{Bin}(n, \Pbb(S))$, and therefore
+\begin{equation}
+\label{eqn:graph_functional_concentration_pf2}
+(1 - \delta) \Pbb(\mathcal{S}) n \leq \abs{S[X]}
+\end{equation}
+with probability at least $1 - \exp\set{-\frac{\delta^2n\Pbb(\mathcal{S})}{1 + \frac{\delta}{3}}}$.
+
+The inequalities \eqref{eqn:graph_functional_concentration_pf1} and \eqref{eqn:graph_functional_concentration_pf2} imply that with high probability $\frac{d_{\max}}{d_{\min}} \lesssim \abs{S[X]}$ and $\frac{d_{\max}}{d_{\min}^2} \lesssim 1$; the lower bound on $n$ given in \eqref{eqn:graph_functional_concentration_1} ensures that these bounds hold exactly.
+
+Finally, the statement $\vol\bigl(\mathcal{S}[X]\bigr) \leq \frac{2}{3}\vol(G)$ is equivalent to $\vol\bigl(\mathcal{X}\setminus\mathcal{S}[X]\bigr) \geq \frac{1}{2}\vol\bigl(\mathcal{S}[X]\bigr)$.
+For any set $\mathcal{A} \subseteq \Reals^d$, the volume $\vol\bigl(\mathcal{A}[X]\bigr)$ is a $U$-statistic, since it can be written as
+\begin{equation*}
+\vol\bigl(\mathcal{A}[X]\bigr) = \sum_{i = 1}^{m} \sum_{j \neq i} \underbrace{\frac{\1(x_i \in \mathcal{S}) \vee \1(x_j \in \mathcal{S})}{2} \1(\norm{x_i - x_j} \leq r)}_{h_\mathcal{A}(x_i,x_j)}
+\end{equation*}
+Let $p_{h_\mathcal{A}} = \mathbb{E}[h_\mathcal{A}(X_1,X_2)]$ for $X_1$ and $X_2$ independent random variables with distribution $\Pbb$. By Hoeffding's inequality for $U$-statistics we have
+\begin{equation}
+\label{eqn:graph_functional_concentration_pf3}
+\vol\bigl(\mathcal{S}[X]\bigr) \leq (1 + \delta)\mathbb{E}\left[\vol(\mathcal{S}[X])\right], \quad \vol\bigl(\mathcal{S}[X]\bigr) \leq (1 - \delta)\mathbb{E}\left[\vol(\mathcal{X}\setminus\mathcal{S}[X])\right]
+\end{equation}
+with probability at least $1 - 2\exp\set{-\frac{\delta^2 (n - 1)^2 \min\{p_{h_\mathcal{S}}, p_{h_{\mathcal{X}\setminus{\mathcal{S}}}}\}}{4}}$.
+If \eqref{eqn:graph_functional_concentration_pf3} is satisfied, then by~\eqref{eqn:graph_functional_concentration_2} the inequality $\vol\bigl(\mathcal{X}\setminus\mathcal{S}[X]\bigr) \geq \frac{1}{2}\vol\bigl(\mathcal{S}[X]\bigr)$ holds, and therefore $\vol\bigl(\mathcal{S}[X]\bigr) \leq \frac{2}{3}\vol(G)$.
+
 \end{document}

### 2021-12-23 notes/weekly_notes/10.31.20.NotesForWeek.tex

--- 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex
@@
 \newcommand{\PLS}{\mathrm{PLS}}
-\newcommand{\dist}{\mathrm{dist}}
 
@@
 \begin{document}
-\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
+\title{Notes on: Revision for JMLR Submission on Local Spectral Clustering of Density Upper Level Sets}
 \author{Alden Green}
@@
 
-\chapter{Lower bound for conductance of continuous-space ball walk}
-For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$.
-Further define
+Recall: our Theorem 5 (JMLR numbering) says that with high probability, the following statement holds: when the PPR algorithm is properly initialized, the resulting estimator $\wh{C}$ of an empirical density cluster $\mc{C}_{\sigma}[X]$ satisfies
+\begin{equation}
+\label{eqn:volume_ssd_ppr}
+\frac{\Delta(\wh{C},C_{\sigma}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])} \leq c \cdot \kappa(\mc{C}).
+\end{equation}
+Both reviewers and the editor treated Theorem~5 as our main result, and viewed it as too weak, in related but slightly different ways. Specifically, they worried that:
+\begin{itemize}
+	\item \textbf{Reviewer 1.} For an example provided in our experiments section, the right hand side is (many times) larger than $1$. Since the trivial estimator $\wh{C} = \emptyset$ will always have
 	\begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
+	\frac{\Delta(\emptyset,C_{\sigma}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])}  = 1,
 	\end{equation*}
-The uniform continuous normalized cut and conductance are then
+	our bound is vacuous.
+	\item \textbf{Reviewer 2.} The right hand side of~\eqref{eqn:volume_ssd_ppr} does not go to $0$ as $n \to \infty$. 
+	\item \textbf{Editor.} ``...either the three of us did not get the 
+	point of Theorem 5, in which case the presentation
+	is obviously not satisfying, or Theorem 5 is not
+	as strong as one would like to have it."
+\end{itemize}
+
+Both Reviewer 1 and Reviewer 2 make accurate statements, motivating the following pair of research questions:
+\begin{enumerate}
+	\item \textbf{Addressing the concerns of Reviewer 1.} What are some distributions $P$ and resulting density clusters $\mc{C}$ for which our bound is not vacuous, i.e. for which
 	\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
+	c \cdot \kappa(\mc{C}) < 1?
 	\end{equation*}
-where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.
+	\item \textbf{Addressing the concerns of Reviewer 2.} Should we expect the right hand side of~\eqref{eqn:volume_ssd_ppr} to go to $0$ as $n \to \infty$?
+\end{enumerate}
+We address these concerns in the following two sections.
 
-\begin{lemma}
-	\label{lem: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
+\section{Concerns of Reviewer 1}
+
+\subsection{Uniform rectangles + $\epsilon$-background noise model.}
+Let us recall the model used in the construction of our ``hard case''. Letting $\theta = (\epsilon,w,h)$, the distribution $P = P_{\theta}$ is a mixtures of uniforms over the unit square $[-1,1]^2$:
 \begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
+P_{\theta} := \frac{1 - \epsilon}{2} P_{(1)} + \frac{1 - \epsilon}{2} P_{(2)} + \epsilon Q;
 \end{equation*}
-\end{lemma}
-Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
-\begin{corollary}
-	\label{cor: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
+here $Q$ is the uniform distribution over $[-1,1]^2$, and the mixture component $P_{(i)}$ is the uniform distribution over the rectangle $\mc{C}_{(i)}$, 
 \begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
+\mc{C}_{(i)} := c_{(i)} + \frac{1}{2}\Bigl([-w,w] \times [-h,h]\Bigr)
 \end{equation*}
-\end{corollary}
+with $c_{(1)} = (-.5,0)$ and $c_{(2)} = (.5,0)$, and. Letting $f_{\theta}$ be the density function of $P_{\theta}$---which has the simple closed form expression
+\begin{equation*}
+f_{\theta}(x) =
+\begin{cases}
+\frac{(1 - \epsilon)}{2wh} + \frac{1}{4}\epsilon,& ~~ x \in \mc{C}_{(i)} \\
+\frac{1}{4}\epsilon,& ~~ x \in [-1,1]^2 \setminus \bigl(\mc{C}_{(1)} \cup \mc{C}_{(2)}\bigr)
+\end{cases}
+\end{equation*}
+---it is clear that $\mc{C}_{(1)}$ and $\mc{C}_{(2)}$ have higher density than the rest of $[-1,1]^2$, and in particular that for any $\epsilon/4 < \lambda \leq (1 - \epsilon)/(2wh) + \epsilon/4$ we have $\mathbb{C}_f(\lambda) = \{\mc{C}_{(1)}, \mc{C}_{(2)}\}$.
 
-\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
-Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance.
-The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use.
-For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
+\paragraph{Our bound.}
+To be more explicit, our bound upper bound on the volume of the symmetric set difference is given by
+\begin{equation}
+\label{eqn:volume_ssd_ppr_explicit}
+\frac{\Delta(\wh{C},\mc{C}_{\sigma}[X])}{\vol_{n,r}(\mc{C}_{\sigma}[X])} \leq 2180 \cdot \Phi_u(\mc{C}) \cdot \tau_{u}(\mc{C}),
+\end{equation}
+i.e.
+the constant in~\eqref{eqn:volume_ssd_ppr} is $c = 2180$, and the condition number $\kappa(\mc{C})$ is equal to the product of (upper bounds on) the normalized cut $\Phi_u(\mc{C})$ and mixing time $\tau_u(\mc{C})$.
+Technically speaking the density clusters $\mc{C}_{(i)}$ do not satisfy our assumptions on density clusters $\mc{C}_{\sigma}$, but modulo some additional bookkeeping we can compute the following upper bounds:
 \begin{equation*}
-\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
-\end{equation*}
-where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
-\begin{enumerate}
-	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
-	\begin{equation*}
-	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
-	\end{equation*}
-	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
-	\begin{equation*}
-	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
-	\end{equation*}
-	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
-	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
-		\label{lem: nonconvex_isoperimetry}
-		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$,
-		\begin{equation*}
-		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
-		\end{equation*}
-	\end{lemma}
-	\item[4.] 
-	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
-	\begin{equation*}
-	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
-	\end{equation*}
-	\begin{lemma}
-		\label{lem: one_step_distributions}
-		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_1}
-		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
-		\end{equation}
-		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_2}
-		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
-		\end{equation}
-	\end{lemma}
-	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
-	\end{equation*}
-	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
-	\begin{equation*}
-	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
-	\end{equation*}
-\end{enumerate}
-The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e.
-a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show.
-In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
-\begin{equation*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
-\end{equation*}
-Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$.
-Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
-\end{equation*}
-Otherwise, we deduce that
-\begin{align*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
-& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
-& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
-\end{align*}
-Setting $\delta = 1/3$, we have
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
-\end{equation*}
-and putting $a = r\ell/(2\rho)$ yields the claim.
-
-Now, we turn to establishing the inequalities used in the above chain.
-
-\paragraph{Step 1: Lower bound the ergodic flow.}
-By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
-\begin{equation*}
-2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
+\Phi_u(\mc{C}) = 
 \end{equation*}
 
-\paragraph{Step 2: Estimate the stationary distribution.}
+\paragraph{}
 
-Both the upper and lower  bounds on $\wt{\pi}_{\nu,r}(\mc{S})$ are a direct consequence of the following inequalities:
+\begin{itemize}
+	\item There exist choices of $\theta$ for which:
+	\begin{enumerate}[(i)]
+		\item  Our bound on 
 		\begin{equation*}
-\ell \nu_d r^d \nu(\mc{S})  \leq {J}_{\nu,r}(\mc{S}) \leq \nu_d r^d \nu(\mc{S}).
+		\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])}
 		\end{equation*}
-\paragraph{Step 3: Isoperimetric inequality.}
-NB: the proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\mc{C}_{\sigma}$ is itself convex, and is a primary technical contribution of the seminal work \textcolor{red}{(Lovasz 1990)}, extended by \textcolor{red}{(Dyer 1991)} among others.
-However, once the result is shown in the convex setting, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
-\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
-	For $\Omega_i, i = 1,2,3$, denote the preimage
+		will be less than $1$. 
+		\item 
 		\begin{equation*}
-	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
+		\frac{\Delta(\wh{C},\mc{C}[X])}{\vol_{n,r}(\mc{C}[X])} < 1,
 		\end{equation*}
-	For any $x \in R_1, y \in R_2$, 
-	\begin{equation*}
-	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
-	\end{equation*}
-	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
-	\begin{equation*}
-	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
-	\end{equation*}
-	By Theorem 2.2 of \textcolor{red}{(Lovasz 1990)},
-	\begin{align*}
-	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
-	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
-	\end{align*}
-	and by the measure-preserving property of $g$, this implies
-	\begin{equation*}
-	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
-	\end{equation*}
-\end{proof}
+		but any bound based on the results of \textcolor{red}{(Allen-Zhu)} will be $ > 1$.
+	\end{enumerate}
+	The point (i) is an obvious response to Reviewer 1.
+The concern is that the values of $\theta$ for which (i) holds are implausible, for instance if $\epsilon$ must be absurdly small.
+Point (ii) addresses this concern, giving the values of $\theta$ one should expect to derive for if one must use the results of \textcolor{red}{(Allen-Zhu)}.
+	\item \textbf{Rates of convergence in $\epsilon$.} As $\epsilon \to 0$, it is obvious that PPR will come to consistently recover $\mc{C}$.
+Our upper bound correctly reflects this fact.
+The following question is perhaps more interesting: does our upper bound correctly capture the rate of convergence?
+\end{itemize}
 
-\paragraph{Step 4: Total variation distance.}
+\subsection{Other models?}
 
-\begin{proof}[Proof of Lemma~\ref{lem: one_step_distributions}]
-	Note that~\eqref{eqn:one_step_distributions_2} follows from~\eqref{eqn:one_step_distributions_1} by first taking the supremum over all $\mc{S} \subseteq \mc{C}_{\sigma}$, and then the infimum over all $x \in \mc{S}_1$ and $y \in \mc{S}_2$.
+\textcolor{red}{(Discuss with Siva.)}
 
-	It remains to show~\eqref{eqn:one_step_distributions_1}.
-Let $\mc{R} = \mc{C}_{\sigma} \setminus \mc{S}$ and $\mc{I} = B(x,y) \cap B(y,r)$, and suppose without loss of generality that $\ell_{\nu,r}(x) > \ell_{\nu,r}(y)$.
-We can relate $\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})$ to the volume of the intersection $\mc{I}$ as follows:
-	\begin{align*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) & = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \\
-	& = 1 - \biggl(\frac{\nu\bigl(B(x,r) \cap \mc{R}\bigr)}{\ell_{\nu,r}(x)} + \frac{\nu\bigl(B(y,r) \cap \mc{S}\bigr)}{\ell_{\nu,r}(y)}\biggr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr)\Bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\nu\bigl(\mc{I} \cap \mc{C}_{\sigma}\bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu(\mc{I}) - \nu\bigl(B(x,r)\bigr) + \ell_{\nu,r}(x)\Bigr) \\
-	& = \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu_dr^d - \nu(\mc{I})\Bigr).
-	\end{align*}
-	Now, by hypothesis $\ell_{\nu,r}(x) \geq \ell \nu_dr^d$. On the other hand, Lemma~\ref{lem: volume_of_spherical_cap} gives a lower bound on the volume of $\mc{I}$, and from this we obtain
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) \leq \frac{\|x - y\|}{\ell r} \sqrt{\frac{d + 2}{2\pi}};
-	\end{equation*}
-	solving for $\|x - y\|$ yields~\eqref{eqn:one_step_distributions_1}.
-\end{proof}
+\section{Concerns of Reviewer 2}
+We first point out that to the best of our knowledge, all other works on spectral clustering on random geometric graphs fall into three categories. 
+\begin{enumerate}[(1)]
+	\item Define clusters with respect to geometric conditions, obtain upper bound on classification error that does not go to $0$ as $n \to \infty$.
+	\item Obtain consistency, but for clusters defined with respect to a continuum PDE or eigenfunction problem.
+	\item Obtain consistency for geometrically defined clusters, by changing the algorithm.
+\end{enumerate} 
+Our work falls into category (1), and so trades a weaker result---non-vanishing upper bound on classification error---for a more natural definition of cluster.
 
-\section{Volume Estimates}
+Of course, simply because other works in category (1) share the non-vanishing upper bound property does not mean that such a property is fundamental to the problem.
+We investigate the question empirically.
 
-\begin{lemma}
-	\label{lem: overlap_balls}
-	For any $x,y \in \Rd$, it holds that
-	\begin{equation}
-	\label{eqn:overlap_balls_1}
-	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation}
-	If additionally $\|x - y\| \leq \sigma$, then
-	\begin{equation}
-	\label{eqn:overlap_balls_2}
-	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr)
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We first prove~\eqref{eqn:overlap_balls_1}. It is not hard to see that $\mathcal{I} := B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height
-	\begin{equation*}
-	h = r - \frac{\|x - y\|}{2}
-	\end{equation*} 
-	As a result, by Lemma \ref{lem: volume_of_spherical_cap} we have
-	\begin{equation*}
-	\nu\bigl(\mathcal{I}\bigr) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{\|x - y\|^2}{4r^2}.
-	\end{equation*}
-	Expanding the incomplete beta function in integral form, we obtain
-	\begin{align*}
-	\nu\bigl(\mathcal{I}\bigr) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{ \|x - y\|}{r} \right) \\
-	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}} \right),
-	\end{align*}
-	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral}, and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
+\subsection{Uniform rectangles + $\epsilon$-background noise model}
 
-	We now establish~\eqref{eqn:overlap_balls_2}.
-Assume that $\|x - y\| = \sigma$, as otherwise if $\|x - y\| < \sigma$ the volume of the overlap will only grow.
-Then $B(x,r) \cap B(y,\sigma)$ contains a spherical cap of radius $r$ and height $r - \frac{r^2}{2\sigma}$, and similar derivations to those used to show~\eqref{eqn:overlap_balls_1} imply that
-	\begin{equation*}
-	\nu(\cap_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation*}
-\end{proof}
+Let $X_1,\ldots,X_n$ be drawn from $P_{\theta}$, with $w = .5, h = 1$ and $\epsilon \approx .72$.
+In Figure~\ref{fig:fig1}, we plot the error---volume of the symmetric set difference, normalized by the volume of $\mc{C}_{(1)}$--- of PPR clustering against the sample size $n$.
+We see that PPR--even when optimally seeded, tuned, and with the optimal sweep cut taken---fails to consistently recover $\mc{C}_{(1)}$.
+\begin{figure}
+	\centering
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=.8\linewidth]{figures/11_05_2020/error.pdf}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{figures/11_05_2020/error_upper_bound.pdf}
+	\end{subfigure}
+	\caption{Error---$\Delta(\wh{C},\mc{C}[X])$ divided by $\vol_{n,r}(\mc{C}_{(1)}[X])$---of PPR clusters $\wh{C}$, averaged over 5 iterations.
+Different curves correspond to different values of radius $r$.
+For each value of radius $r$, a range of teleportation parameters $\alpha$ and sweep cuts was considered; we have plotted the smallest error among these ranges.}
+	\label{fig:fig1}
+\end{figure}
 
-\subsection{Spherical caps and associated estimates}
-\label{subsec:caps}
-In this section, we state a result for the volume of a spherical cap and derive some 
-useful upper bounds. 
-\begin{lemma}
-	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha := 1 - \frac{2 r h - h^2}{r^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
-	\end{equation*}
-	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
-\end{lemma}
-The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
-an upper bound on the ratio of Gamma functions. 
-\begin{lemma}
-	\label{lem: beta_integral}
-	For any $0 \leq \alpha \leq 1$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - 2\sqrt{\alpha}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write 
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
-	\end{equation*}
-	The first integral is simply the beta function, with
-	\begin{equation*}
-	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
-	\end{equation*}
-	Noting that for all $u \in [0,1]$ and $d \geq 1$, $u^{(d - 1)/2} \leq 1$, the second integral can be upper bounded as follows:
-	\begin{equation*}
-	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du \leq \int_{1 - \alpha}^{1}(1 - u)^{-1/2}du = \int_{0}^{\alpha} u^{-1/2}du = 2\sqrt{\alpha}.
-	\end{equation*}
-\end{proof}
-
-\begin{lemma}
-	\label{lem: beta_function}
-	\begin{equation*}
-	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
-	\end{equation*}
-\end{lemma}
-\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
-
-\section{Other derived results}
-
-Lemma~\ref{lem:volume_perturbation} bounds the difference $\nu(B(x,r) \cap \mc{C}_{\sigma}) - \nu(B(y,r) \cap \mc{C}_{\sigma})$ as a function of $\|x - y\|_{\Rd}$.
-Unfortunately, it only kicks in when $\|x - y\| \lesssim r/d$, whereas we would like something which applies when $\|x - y\| \lesssim r/\sqrt{d}$.
-
-\begin{lemma}
-	\label{lem:volume_perturbation}
-	Let $x,y \in \mc{C}_{\sigma}$ satisfy $\|x - y\| < \frac{r}{d - 1}$. Then,
-	\begin{equation*}
-	\Bigl|\nu\bigl(B(x,r) \cap \mc{C}_{\sigma}\bigr) - \nu\bigl(B(y,r) \cap \mc{C}_{\sigma}\bigr)\Bigr| \leq \nu_dr^d\frac{d\|y - x\|}{(r - (d - 1)\|y - x\|)}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	By the triangle inequality, 
-	\begin{align*}
-	\nu(B(x,r) \cap \mc{C}_{\sigma}) & = \int_{\mc{C}_{\sigma}} \1(\|z - x\| \leq r) \,dz \\
-	& \leq \int_{\mc{C}_{\sigma}} \1(\|z - y\| \leq r + \|y - x\|) \,dz \\
-	& = \int_{\mc{C}_{\sigma}} \bigl(\1(\|z - y\| \leq r) + \1(r < \|z - y\| \leq r + \|y - x\|) \bigr)  \,dz \\
-	& \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) + \nu_d\bigl((r + \|y - x\|)^d - r^d\bigr),
-	\end{align*}
-	and the upper bound $\nu(B(x,r) \cap \mc{C}_{\sigma}) \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) +  \nu_dr^dd\|y - x\|/(r - (d - 1)\|y - x\|)$ follows by Bernoulli's inequality (\textcolor{red}{(Lemma 22)}).
-Reversing $x$ and $y$ gives an equivalent upper bound on $\nu(B(y,r) \cap \mc{C}_{\sigma})$.
-\end{proof}
-
-\chapter{Misclassification error of PPR}
-The following Lemma upper bounds the misclassification error of (a sweep cut of) a PPR vector, in terms of the \emph{normalized cut} and \emph{mixing time} functionals.
-It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
-\begin{lemma}
-	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
-For $\beta \in (0,1)$,  the sweep cut $S_{\beta,v}$ is
-	\begin{equation*}
-	S_{\beta,v} = \set{u \in V: \frac{p_v^{(\varepsilon)}(u)}{\deg(u;G)} \geq \beta}.
-	\end{equation*} 
-	For some $A \subseteq V$, suppose that 
-	\begin{equation*}
-	\alpha \leq \min\Bigl\{\frac{1}{15}, \frac{1}{5\tau_{\infty}(G[A])}\Bigr\},~~ \beta, \varepsilon \leq \frac{1}{4\vol(A;G)}.
-	\end{equation*}
-	Then there exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A^g;G)$ such that for any $v \in A^g$, the sweep cut $S_{\beta,v}$ satisfies
-	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v};G) \leq \left(\frac{3}{\beta} + \frac{200}{9\vol(A;G)}\right) \frac{\Phi(A;G)}{\alpha}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We adopt the notation $\wt{p}_v$ for the (exact) PPR vector computed over the subgraph $G[A]$, and 
-	\begin{equation*}
-	\wt{\pi}(u) = \frac{\deg(u;G[A])}{\vol(A;G[A])}
-	\end{equation*}
-	for the stationary distribution of a random walk over $G[A]$.
-The proof of this Lemma proceeds along very similar lines to that of~\textcolor{red}{(Zhu 2013 Lemma 3.4)}.
-We directly use the following three inequalities, derived in that work:
-	\begin{itemize}
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.2.)} For any seed node $v \in A$, the following inequalities hold for every $u \in A$:
-		\begin{equation}
-		\label{pf:zhu1}
-		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u)
-		\end{equation}
-		\item \textcolor{red}{(Zhu 2013 Corollary 3.3)} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
-		\begin{equation}
-		\label{pf:zhu2}
-		p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G),
-		\end{equation}
-		and $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.1, Anderson 2007 Theorem 5.1)} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
-		\begin{equation}
-		\label{pf:zhu3}
-		\sum_{u \neq A} p_v(u) \leq 2\frac{\Phi(A;G)}{\alpha}.
-		\end{equation}
-	\end{itemize}
-	From these we can derive the following upper bound on the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
-	\begin{itemize}
-		\item For any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
-		\begin{equation*}
-		\vol(S_{\beta,v} \setminus A; G) \leq \frac{1}{\beta} \sum_{u \not\in A}p_v^{(\varepsilon)}(u) \leq 2\frac{\Phi(A;G)}{\beta \cdot \alpha}.
-		\end{equation*} 
-		\item For any $u \in A$, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$,
-		\begin{equation*}
-		p_v^{(\varepsilon)}(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G).
-		\end{equation*}
-		If $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
-		\begin{equation}
-		\label{pf:zhu4}
-		\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr)\wt{\pi}(u) - (\varepsilon + \beta)\deg(u;G) \leq \wt{p}_{\ell}(u).
-		\end{equation}
-
-		Let us restrict our attention for the moment to those vertices $u$ with sufficiently large degree in $G[A]$; precisely speaking, let
-		\begin{equation*}
-		A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\}.
-		\end{equation*}
-		We note that for any $u \in A^{\mathrm{int}}$,
-		\begin{equation*}
-		\wt{\pi}(u) > \frac{(1 - \alpha \beta \vol(A;G))\deg(u;G)}{\vol(A;G)},
-		\end{equation*}
-		so that by~\eqref{pf:zhu4} it holds that
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u)
-		\end{equation*}
-		for any $u \in A^{\mathrm{int}} \setminus S_{\beta,v}$. Summing over all such u, we obtain
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \sum_{u \in A^{\mathrm{int}} \setminus S_{\beta,v}} \wt{p}_{\ell}(u) \leq 2\frac{\Phi(A;G)}{\alpha}
-		\end{equation*}
-		where the second upper bound follows from the upper bound on $\|\ell\|_1$, since $\sum_{u \in A} \wt{p}_{\ell}(u) = \|\ell\|_1$. 
-		Then, from the assumed upper bounds on $\alpha, \beta$ and $\varepsilon$ we obtain the inequality
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{9}{100\vol(A;G)}.
-		\end{equation*}
-		\item Finally, for every $u \in A \setminus A^{\mathrm{int}} $, it holds that $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$.
-Summing over all such vertices, we obtain
-		\begin{equation*}
-		\vol(A \setminus A^{\mathrm{int}};G) \leq \frac{\Phi(A;G)}{\alpha \cdot \beta}.
-		\end{equation*}	
-	\end{itemize}
-\end{proof}
+In Figures 2 and 3, we see what the set is that PPR actually recovers.
+The lesson is unsurprising: PPR trades off geometry for density, preferring an estimate $\wh{C}$ which is somewhat more geometrically well-behaved (i.e lower aspect ratio) even at the expense of including some low-density areas.
+\begin{figure}
+	\centering
+	\includegraphics[width = .5\textwidth]{figures/11_05_2020/ppr_cluster.pdf}
+	\caption{PPR cluster estimate, for different values of $r$.}
+	\label{fig:fig2}
+\end{figure}
 

### 2021-12-23 notes/weekly_notes/11.11.20.NotesForWeek.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mb}[1]{\mathbb{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Note on: Cluster tree consistency of spectral clustering.}
\author{Alden Green}
\date{\today}
\maketitle

\textbf{Motivation:} Try to obtain ``cluster tree consistency''---as defined below--- in more realistic scenarios than those obtained in our previous work.

Suppose we observe samples $X_1,\ldots,X_n \sim P$, where
\begin{equation*}
P  := \frac{1}{2}P_{(1)} + \frac{1}{2}P_{(2)};
\end{equation*}
here $P_{(1)}$ and $P_{(2)}$ should be thought of as mixture components which are \emph{indivisible} and \emph{separate}. This will be made formal later on, but at the bare minimum we will insist that for some $p^{\star} > 0$, the upper level set $\{x:p(x) \geq p^{\star}\}$ can be divided into exactly two disjoint connected components $\mb{C}_{(1)}$ and $\mb{C}_{(2)}$, given respectively by
\begin{equation*}
\mb{C}_{(1)} = \Bigl\{x:p(x) \geq p^{\star}\Bigr\} \cap \Bigl\{x: p_1(x) > p_2(x)\Bigr\}
\end{equation*}
and conversely
\begin{equation*}
\mb{C}_{(2)} = \Bigl\{x:p(x) \geq p^{\star}\Bigr\} \cap \Bigl\{x: p_2(x) \geq p_1(x)\Bigr\}.
\end{equation*}

\paragraph{Spectral clustering.}
In (this version of) spectral clustering, we partition the domain of $P$ into two sets, based on an eigenvector of an appropriately defined operator. Let $\Delta_P$ be a weighted differential operator associated with $P$, for instance the \emph{normalized weighted Laplace-Beltrami} operator
\begin{equation}
\label{eqn:normalized_laplace}
\Delta_Pf := -\frac{1}{p} \mathrm{div}(p \nabla f);
\end{equation}
here $p$ is the density of $P$ with respect to the full-dimensional Lebesgue measure. Define $v_2$ according to:
\begin{equation*}
v_2 := \argmin_{\langle 1,v \rangle_{P} = 0} \frac{\langle \Delta_P v, v \rangle_{P}}{\langle v,v \rangle_{P}}
\end{equation*}
i.e the 1st non-trivial eigenvector of $\Delta_P$. (Note that $v_2$ is determined only up to its sign, and so we assign a sign arbitrarily.)

\paragraph{Consistency of spectral clustering.}
We are interested in the following question:
\begin{quote}
	Under what conditions on $P_{(1)}$ and $P_{(2)}$ does there exist a sweep cut $S_{\beta} = \{x: v(x) \geq \beta \}$ such that $S_{\beta}$ is \emph{consistent} with the density clustering $\{\mb{C}_{(1)}, \mb{C}_{(2)}\}$?
\end{quote} 
There are various notions of consistent recover of density clusters, but in this case I will be interested in \emph{cluster tree consistency}: that is, the existence of a sweep cut for which 
\begin{equation}
\label{eqn:cluster_tree_consistency}
\mb{C}_{(1)} \subset S_{\beta} ~~\textrm{and}~~ S_{\beta} \cap \mb{C}_{(2)} = \emptyset.
\end{equation}

\paragraph{Proof Strategy.}
Proving results in this vein requires uniform control of the values of $v(x)$ for all $x \in U_{P}(p^{\star})$. To obtain such control, we will adopt the following strategy:
\begin{enumerate}
	\item Letting
	\begin{equation}
	\label{eqn:square_root_likelihood}
	q_k = \sqrt{\frac{p_k}{2p}},~~\textrm{for $k = 1,2$}
	\end{equation}
	establish conditions under which $e :\propto q_1 - q_2$ can be $\beta$-thresholded with the resulting estimate $S_{\beta}$ satisfying~\eqref{eqn:cluster_tree_consistency},
	\item Show that $\|v_2 - e\|_{P}$ is small.
	\item Upgrade from a bound on $\|v_2 - e\|_{\Leb^2(P)}$ to a (weaker) bound on $\|v_2 - e\|_{\Leb^{\infty}(U_P(p^{\star}))}$ by the Sobolev Embedding Theorem.
\end{enumerate}

\paragraph{Result.}
The following four quantities are used to assess the condition of $P$ for clustering.
\begin{itemize}
	\item The \emph{overlapping} parameter $\mc{S}$, given by
	\begin{equation*}
	\mc{S} := 4 \langle q_1^2, q_2^2 \rangle_P = \int_{\mc{M}} \frac{p_1 p_2}{p} \,dx.
	\end{equation*}
	\item The \emph{coupling} parameter $\mc{C} := \max_{k} \mc{C}_k$, where
	\begin{equation*}
	\mc{C}_k := \int_{\mc{M}} \biggl| \frac{\nabla p_k}{p_k} - \frac{\nabla p}{p} \biggr|^2 p_k \,dx
	\end{equation*}
	\item The \emph{indivisibility} parameter $\Theta := \min_{k} \Theta_k$, where
	\begin{equation*}
	\Theta_k := \inf_{u \perp 1} \frac{\langle \Delta_{p_{k}}u,u \rangle_{P_{(k)}}}{\langle u,u \rangle_{P_{(k)}}}
	\end{equation*}
	is essentially the smallest non-trivial eigenvalue of $\Delta_{P_{(k)}}$. 
	\item The \emph{saliency} parameter $\sigma_{\star} = \min_{k} \sigma_k$, where
	\begin{equation*}
	\sigma_k = \sup\biggl\{\sigma: p_k(x) \geq (1 + \sigma)^2 p(x)~~\textrm{for all $x \in \mb{C}_{(k)}$} \biggr\}
	\end{equation*}
\end{itemize}
The first three quantities are directly lifted from \textcolor{red}{(Garcia Trillos 2019)}. The last parameter is new, and can be interpreted as a type of cluster saliency condition.\footnote{Cluster saliency conditions are standard in the density clustering literature, in order to give finite sample results. Note, however, that it is certainly possible to have salient density clusters $\mb{C}_{(1)}$ and $\mb{C}_{(2)}$, in the usual sense of saliency, for which $\sigma_{\star} = 0$. This essentially has to do with identifiability issues, but it renders the saliency condition as I've currently written it a tad unnatural; discuss with Siva.}

The following result shows that if the parameters $\mc{S}, \mc{C}$ are sufficiently small, and the parameters $\Theta$ and $\sigma_{\star}$ are sufficiently large, then $v_2$ is uniformly large for all $x \in \mathbb{C}_{(1)}$ and uniformly small for all $x \in \mathbb{C}_{(2)}$. 
\begin{theorem}
	\label{thm:uniform_bound}
	Fix $p^{\star} > 0$. There exists an $a \in \{-1,+1\}$ such that the following statements hold.
	\begin{itemize}
		\item For every $x \in \mb{C}_{(1)}$,
		\begin{equation*}
		av_2(x) \geq \frac{\sigma_{\star}}{\sqrt{2(1 - \mc{S}^{1/2})}} - \frac{1}{p^{\star}}\Bigl(\frac{1}{\mathrm{Leb}(\mb{C}_{(1)})} + 2\mc{C}^{1/2}  \Bigr) \Bigl(\frac{\mc{S}^{1/4} + 2^{1/4}[\kappa(P)]^{1/4}}{(1 - \mc{S}^{1/2})^{1/4}}\Bigr) - \frac{2\mc{C}^{1/2}}{p^{\star}\sqrt{1 - \mc{S}^{1/2}}},
		\end{equation*}
		\item Conversely, for every $x \in \mb{C}_{(2)}$,
		\begin{equation*}
		av_2(x) \leq -\frac{\sigma_{\star}}{\sqrt{2(1 - \mc{S}^{1/2})}} + \frac{1}{p^{\star}}\Bigl(\frac{1}{\mathrm{Leb}(\mb{C}_{(2)})} + 2\mc{C}^{1/2}  \Bigr) \Bigl(\frac{\mc{S}^{1/4} + 2^{1/4}[\kappa(P)]^{1/4}}{\sqrt{1 - \mc{S}^{1/2}}}\Bigr) + \frac{2\mc{C}^{1/2}}{p^{\star}\sqrt{1 - \mc{S}^{1/2}}}.
		\end{equation*}
	\end{itemize}
\end{theorem}

\section{Examples}

As a sanity check, we start with the fully-separated mixture model case.

\subsection{Fully separated mixture}
\textcolor{red}{(TODO)}

\subsection{Gaussian mixture model}
In the Gaussian mixture model, we let
\begin{equation*}
P_{(1)} = N(0,1),~~P_{(2)}= N(\gamma,1).
\end{equation*}
It will be convenient in what follows to reparameterize. Define $z_{\star}$ to satisfy the identity
\begin{equation*}
\frac{1}{\sqrt{2\pi}} \exp(-z_{\star}^2/2) = p_{\star}.
\end{equation*}
Our question is: given a $z_{\star}$, for what values of $\gamma > 2z_{\star}$ does (an appropriately chosen sweep cut of) $v_2$ recover the density cluster $\mb{C}_{(1)}$?

\paragraph{Bounds on parameters.}
We would like to upper bound $\mc{S}, \mc{C}$, and lower bound $\Theta$ and $\sigma_{\star}$. 
\begin{itemize}
	\item \textbf{Separation.} To upper bound $\mc{S}$, we divide the real line into $(-\infty,\gamma/2)$ (where $p_1(x) > p_2(x)$) and $(\gamma/2,\infty)$ (where $p_1(x) \leq p_2(x)$) and deduce that
	\begin{align*}
	\mc{S} & = 2 \int \frac{p_1(x)p_2(x)}{p_1(x) + p_2(x)} \,dx \\
	& = 2 \Bigl( \int_{-\infty}^{\gamma/2} \frac{p_1(x)p_2(x)}{p_1(x) + p_2(x)} \,dx + \int_{\gamma/2}^{\infty} \frac{p_1(x)p_2(x)}{p_1(x) + p_2(x)} \,dx  \Bigr) \\
	& \leq 2 \Bigl( \int_{-\infty}^{\gamma/2} p_2(x) \,dx + \int_{\gamma/2}^{\infty} p_1(x) \,dx  \Bigr) = 4\Phi(-\gamma/2)
	\end{align*}
	where $\Phi$ is the standard Normal CDF. Thus by Mill's inequality,
	\begin{equation*}
	\mc{S} \leq 4\sqrt{\frac{2}{\pi}} \frac{\exp(-\gamma^2/8)}{\gamma^2}
	\end{equation*}
	\item \textbf{Coupling.} It is derived in \textcolor{red}{(Garcia Trillos 19)} that $\mc{C} \leq \frac{\gamma^2}{8}\mc{S}$, from which we deduce
	\begin{equation*}
	\mc{C} \leq \sqrt{\frac{1}{2\pi}}\exp(-\gamma^2/8).
	\end{equation*}
	\item \textbf{Indivisibility.} Clearly $\Theta_1 = \Theta_2$, and to lower bound $\Theta$ it therefore suffices to lower bound $\Theta_1$. From Cheeger's inequality, we know that
	\begin{equation*}
	\Theta_1 \geq \frac{1}{4}h(\Reals,P_{(1)})
	\end{equation*}
	where for a distribution $Q$ with density $q$, 
	\begin{equation*}
	h(\Reals,Q) := \min_{A \subset \Reals} \frac{\int_{\partial A} q(x) \,dS(x)}{\min \{\int_A q(x)\,dx, \int_{A^c} q(x)\} \,dx}.
	\end{equation*}
	For $Q = P_{(1)}$, the minimum is achieved by $A = (0,\infty)$, and so we have
	\begin{equation*}
	h(\Reals,P_{(1)}) \geq \sqrt{\frac{2}{\pi}}  \Longrightarrow \Theta \geq \sqrt{\frac{1}{8\pi}}.
	\end{equation*}
	\item \textbf{Salience.} Similarly $\sigma_{1} = \sigma_2$, and we will concentrate on lower bounding $\sigma_1$. Observe that
	\begin{equation*}
	\frac{p_2(x)}{p_1(x)} \leq 1 - 4\sigma \Longrightarrow p_1(x) \geq (1 + \sigma)^2 p(x).
	\end{equation*}
	Since $p_2(x)/p_1(x)$ is monotonically decreasing in $x$, letting $x_{\star} = \sup \mb{C}_1$ we have that
	\begin{equation*}
	\sigma_1 \geq \frac{1}{4}\Bigl(1 - \frac{p_1(x_{\star})}{p_2(x_{\star})}\Bigr).
	\end{equation*}
	We can further simplify this by noting that, by the definition of $\mb{C}_{(1)}$, $p_1(x_{\star}) \geq p(x_\star)$, and therefore
	\begin{equation*}
	x_{\star} \leq \sup \{x:p_1(x) \geq p_{\star}\} = z_{\star}
	\end{equation*}
	and hence
	\begin{align*}
	\sigma_1 & \geq \frac{1}{4}\Bigl(1 - \frac{p_1(z_{\star})}{p_2(z_{\star})}\Bigr) \\
	& = \frac{1}{4}\Bigl(1 - \exp(\gamma z_{\star} - \gamma^2/2)\Bigr).
	\end{align*}
\end{itemize}
Now, under the assumptions that $z_{\star}^2 \geq 2\log(4)$ and $\gamma^2 \geq 8\log\bigl(32/\pi^{1/2}\bigr)$ some crude calculations---which are briefly alluded to in Section~\ref{sec:some_calculations}---along with Theorem~\ref{thm:uniform_bound} give that for all $x \in \mb{C}_{(1)}$:
\begin{align*}
av_2(x) & \geq \sigma_{\star} - \frac{80 \pi^{1/4} \mc{C}^{1/2}}{p^{\star}} \\
& \geq \frac{1}{4} - \frac{1}{4}\exp(\gamma z^{\star} - \gamma^2/2) - 2^{3/4} \cdot 80\pi\exp(z_{\star}^2/2 - \gamma^2/2),
\end{align*}
and some standard arithmetic implies that if
\begin{equation*}
\gamma \geq \max\biggl\{z_{\star} + \sqrt{z_{\star}^2 + 2\log(2)}, \sqrt{z_{\star}^2 + 2\log(8 2^{3/4} 80 \pi)}  \biggr\}
\end{equation*}
then $av_2(x) > 0$,  Under the same conditions on $\gamma$, $av_2(x) < 0$ for all $x \in \mb{C}_{(2)}$, and so the sweep cut $S_0 = \{av_2(x) > 0\}$ consistently recovers the density clustering $\{\mb{C}_1, \mb{C}_2\}$.

\section{Supporting Theory}

\subsection{(1). Conditions under which $e$ can be $\beta$-thresholded.}
A direct calculation establishes that
\begin{equation*}
e(x) \geq \frac{\sigma_{\star}}{\sqrt{2}\|q_1 - q_2\|_P}~~\textrm{for all $x \in \mathbb{C}_{(1)}$}
\end{equation*} 
and conversely
\begin{equation*}
e(x) \leq -\frac{\sigma_{\star}}{\sqrt{2}\|q_1 - q_2\|_P}~~\textrm{for all $x \in \mathbb{C}_{(2)}$}.
\end{equation*}

\subsection{(2). Establish bounds in $\Leb^2(P)$ norm}
\textcolor{red}{(Garcia Trillos et al 2019)} establish that $q_1$ and $q_2$ are close to the span of $v_1$ and $v_2$, 
\begin{equation}
\label{eqn:garciatrillos19_1}
\|q_k - \Pi_2(q_k)\|_{P}^2 \leq w_k \kappa(P),~~\kappa(P) := \biggl(\sqrt{\frac{\Theta(1 - 2\mc{S})}{\mc{C}}} - \sqrt{\frac{2\mc{S}}{1 - \mc{S}}}\biggr)^{-2},
\end{equation}
for $k = 1$ and $k = 2$. ($\kappa(P)$ is a condition number, quantifying the clusterability of $P$.)

Of course $v_1 = 1$, which is approximately orthogonal to $q_1 - q_2$. Therefore, letting
\begin{equation*}
e := \frac{q_1 - q_2}{\|q_1 - q_2\|_P}
\end{equation*} 
it holds that $e$ is close to $v_2$ in $\Leb^2(P)$ norm.
\begin{proposition}
	It holds that
	\begin{equation}
	\label{eqn:l2_error}
	\|e - v_2\|_P^2 \leq (\|q_1 - q_2\|_P)^{-1}\Biggl(\mc{S}^{1/2} + \sqrt{2}\bigl[\kappa(P)\bigr]^{1/2} \Biggr)
	\end{equation}
\end{proposition}
\begin{proof}
	Throughout we shall assume that $\dotp{e}{v_2}_P > 0$---otherwise, we may simply deal with $-v_2$ throughout the proof.

	We begin by squaring the error on the left hand side of~\eqref{eqn:l2_error}, 
	\begin{align}
	\|e - v_2\|_P^2 = 2(1 - \dotp{e}{v_2}_P).
	\end{align}
	Since $\{v_k\}$ is an orthonormal basis of $L^2(P)$, Parseval's identity implies
	\begin{equation*}
	1 = \|e\|_P^2 = \dotp{e}{v_1}_P^2 + \dotp{e}{v_2}_P^2 + \|e - \Pi_2(e)\|_P^2 \Longrightarrow \dotp{e}{v_2}_P = 1 - \sqrt{\dotp{v_1}{e}_P^2 + \|e - \Pi_2(e)\|^2}
	\end{equation*}
	and therefore
	\begin{equation*}
	\|e - v_2\|_P^2 = 2\biggl(\sqrt{\dotp{v_1}{e}_P^2 + \|e - \Pi_2(e)\|_P^2}\biggr)\leq 2\biggl(|\dotp{v_1}{e}_P| + \|e - \Pi_2(e)\|_P\biggr)
	\end{equation*}
	We now show that $q_1 - q_2$ is approximately mean zero. By the triangle inequality,
	\begin{equation*}
	\bigl|\langle q_1 - q_2,1 \rangle_P\bigr| \leq \bigl| \langle q_1 - q_1^2,1\rangle_{P} \bigr| + \bigl| \langle q_1^2 - q_2^2,1\rangle_{P} \bigr| + \bigl| \langle q_2^2 - q_2,1\rangle_{P} \bigr|
	\end{equation*}
	The first and third terms can be controlled as follows:
	\begin{align*}
	\bigl| \langle q_k - q_k^2,1\rangle_{P} \bigr| & = \int_{\mc{M}} \bigl(q_k(x) - q_k^2(x)\bigr) p(x) \,dx \\
	& = \int_{\mc{M}} \bigl(\sqrt{w_kp_k(x)p(x)} - w_kp_k(x)\bigr) \,dx \\
	& = w_k \int_{\mc{M}} \bigl(\sqrt{p_k^2(x) + p_1(x)p_2(x)} - p_k(x)\bigr)  \,dx \\
	& \leq w_k \int_{\mc{M}} \sqrt{p_1(x)p_2(x)}\,dx \\
	& = w_k \int_{\mc{M}} \sqrt{\frac{p_1(x)p_2(x)}{p(x)}} \sqrt{p(x)} \,dx \\
	& \leq w_k \mc{S}^{1/2},
	\end{align*}
	where the last upper bound follows by Cauchy-Schwarz inequality. The middle term is $\langle q_1^2 - q_2^2,1\rangle_{P} = \int p_1 - p_2 = 0$. Therefore
	\begin{equation*}
	\bigl|\langle q_1 - q_2,1 \rangle_P\bigr| \leq (w_1 + w_2)\mc{S}^{1/2} = \mc{S}^{1/2}.
	\end{equation*}
	On the other hand, by~\eqref{eqn:garciatrillos19_1}, 
	\begin{equation*}
	\|e - \Pi_2(e)\|_P \leq \frac{1}{\|q_1 - q_2\|_P}\biggl(\|q_1 - \Pi_2(q_1)\|_P + \|q_1 - \Pi_2(q_1)\|_P\biggr) \leq \frac{1}{\|q_1 - q_2\|_P}\bigl(\sqrt{w_1} + \sqrt{w_2}\bigr)\kappa(P)^{1/2}
	\end{equation*}
	completing the proof of the Proposition.
\end{proof}

As we will see momentarily, it will also be important to establish upper bounds on $\langle \Delta_P(e - v_2), (e - v_2) \rangle_P$.
\begin{lemma}
	It holds that
	\begin{equation}
	\label{eqn:dirichlet_energy_perturbation_1}
	\bigl\langle \Delta_P(e - v_2), (e - v_2) \bigr\rangle_P \leq \frac{3\mc{C}}{\|q_1 - q_2\|_P^2} + 2\mc{C}\|e - v_2\|_P^2.
	\end{equation}
\end{lemma}
\begin{proof}
	Expanding the inner product gives
	\begin{align*}
	\bigl\langle \Delta_P(e - v_2), (e - v_2) \bigr\rangle_P & = \bigl\langle \Delta_Pe, e \bigr\rangle_P + \bigl\langle \Delta_Pv_2, v_2 \bigr\rangle_P - 2\bigl\langle \Delta_Pv_2, e \bigr\rangle_P \\
	& = \bigl\langle \Delta_Pe, e \bigr\rangle_P + \lambda_2 - 2\lambda_2 \bigl\langle v_2, e \bigr\rangle_P \\
	& = \bigl\langle \Delta_Pe, e \bigr\rangle_P - \lambda_2 + 2\lambda_2 \|e - v_2\|_P^2
 	\end{align*}
 	whence the problem reduces to upper bounding $\bigl\langle \Delta_Pe, e \bigr\rangle_P$ and $\lambda_2$.

 	For the first, we expand the inner product once again:
 	\begin{align*}
	\bigl\langle \Delta_Pe, e \bigr\rangle_P & = \frac{1}{\|q_1 - q_2\|_P^2}\biggl(\bigl\langle \Delta_Pq_1, q_1 \bigr\rangle_P + \bigl\langle \Delta_Pq_2, q_2 \bigr\rangle_P - 2 \bigl\langle \Delta_Pq_1, q_2 \bigr\rangle_P\biggr) \\
	& = \frac{1}{\|q_1 - q_2\|_P^2}\biggl(w_1\mc{C}_1 + w_2\mc{C}_2 - 2\int_{\mc{M}} q_1'(x) q_2'(x) p(x) \,dx\biggr) \\
	& \leq \frac{1}{\|q_1 - q_2\|_P^2} \biggl((w_1 + w_2)\mc{C} + 2\Bigl(\int_{\mc{M}} \bigl(q_1'(x)\bigr)^2 p(x)\,dx\Bigr)^{1/2}\Bigl(\int_{\mc{M}} \bigl(q_2'(x)\bigr)^2 p(x)\,dx\Bigr)^{1/2}\biggr) \\
	& \leq \frac{3\mc{C}}{\|q_1 - q_2\|_P^2}.
 	\end{align*}
\end{proof}
For the second, we characterize the eigenvalue $\lambda_2$ using the max-min theorem:
\begin{equation*}
\lambda_2 = \inf_{U: \dim(U) = 2} \sup_{u \in U} \frac{\dotp{\Delta_Pu}{u}_P}{\dotp{u}{u}_P} \leq \sup_{u \in \mathrm{span}\{q_1,q_2\}} \frac{\dotp{\Delta_Pu}{u}_P}{\dotp{u}{u}_P}
\end{equation*}
Writing $u \in \mathrm{span}\{q_1,q_2\}$ as $u = \alpha q_1 + \beta q_2$, we have 
\begin{equation*}
\dotp{\Delta_Pu}{u}_P = \alpha^2\dotp{\Delta_Pq_1}{q_1}_P + \beta^2\dotp{\Delta_Pq_2}{q_2}_P + 2\alpha\beta\dotp{\Delta_Pq_1}{q_2}_{P} \leq (\alpha + \beta)^2 \mc{C}
\end{equation*}
whereas $\|u\|_P^2 \geq \alpha^2 + \beta^2$, leaving us with 
\begin{equation*}
\lambda_2 \leq \frac{(\alpha + \beta)^2\mc{C}}{\alpha^2 + \beta^2} \leq 2\mc{C}.
\end{equation*}

\subsection{(3). Upgrade to $\Leb^{\infty}$ norm}
As mentioned, we would like to upgrade from $\Leb^2$ to $\Leb^{\infty}$ convergence, trading off the more permissive norm by insisting on more regularity in our solution. We have the following result when $d = 1$, reminiscent of a Sobolev embedding theorem.
\begin{proposition}
	\label{prop:}
	Assume $d = 1$. Let $\mb{C}$ be a connected component of $\{x:p(x) \geq p_{\star}\}$. Then, for any $g \in C_c^1(\Reals)$, we have that
	\begin{equation*}
	\|g\|_{\Leb^{\infty}(\mb{C})} \leq \frac{1}{p^{\star}}\Bigl(\frac{1}{\mathrm{Leb}(\mb{C})} \|g\|_{\Leb^2(P)} + \bigl(\langle \Delta_Pg , g \rangle\bigr)^{1/2}\Bigr)
	\end{equation*}
\end{proposition}
\begin{proof}
	By the fundamental theorem of calculus, for any $x,y \in \mc{C}$, we have
	\begin{equation*}
	g(x) - g(y) = \int_{y}^{x} g'(t) \,dt
	\end{equation*}
	and as a result
	\begin{equation*}
	\bigl|g(x)\bigr| - \bigl|g(y)\bigr| \leq \bigl|g(x) - g(y)\bigr| \leq \int_{y}^{x} \bigl|g'(t)\bigr| \,dt \leq \int_{\mb{C}} \bigl|g'(t)\bigr| \,dt.
	\end{equation*}
	Now, take $x$ such that $\bigl|g(x)\bigr| = \|g\|_{\Leb^{\infty}(\mb{C})}$. We have that for any $y \in \mb{C}$,
	\begin{equation*}
	\|g\|_{\Leb^{\infty}(\mb{C})} \leq \bigl|g(y)\bigr| + \int_{\mb{C}} \bigl|g'(t)\bigr| \,dt,
	\end{equation*}
	and integrating both sides with respect to $p$ gives
	\begin{equation*}
	P(\mb{C})\|g\|_{\Leb^{\infty}(\mb{C})} \leq \|g\|_{\Leb^1(P)} + P(\mb{C}) \|g'\|_{\Leb^1(\mb{C})}
	\end{equation*}
	Finally, noting that for any $f \in \Leb^1(\mb{C})$ we have $p^{\star} \|f\|_{\Leb^1(\mb{C})} \leq \|f\|_{\Leb^1(P)}$, we have
	\begin{align*}
	\|g\|_{\Leb^{\infty}(\mb{C})} & \leq \Bigl(\frac{1}{P(\mb{C})} \|g\|_{\Leb^1(P)} + \|g'\|_{\Leb^1(\mb{C})}\Bigr) \\
	& \leq \frac{1}{p^{\star}}\Bigl(\frac{1}{\mathrm{Leb}(\mb{C})} \|g\|_{\Leb^1(P)} + \|g'\|_{\Leb^1(P)}\Bigr) \\
	& \leq \frac{1}{p^{\star}}\Bigl(\frac{1}{\mathrm{Leb}(\mb{C})} \|g\|_{\Leb^2(P)} + \|g'\|_{\Leb^2(P)}\Bigr)
	\end{align*}
	A direct computation shows that $\langle\Delta_{P}g,g \rangle_{P} = \|g'\|_{\Leb^2(P)}$ for any $g$ compactly supported in $\Reals$, yielding the claim.
\end{proof}

\section{Some calculations in the Gaussian case}
\label{sec:some_calculations}
Here I state as facts what can be derived via some (ugly, tedious, and crude) calculations. I decline to include the calculations, because they are crude. In all cases, the notation and parameters are for the mixture-of-two-Gaussians case.
\begin{itemize}
	\item Noting that $p(x) \geq \frac{1}{2}p_1(x)$ for all $x \in \mb{C}_{(1)}$, some arithmetic implies that
	\begin{equation*}
	[-y_{\star},y_{\star}] \subseteq \mc{C}_{(1)}~~\textrm{for $y_{\star} := \sqrt{z_{\star}^2 - \log(4)}$.}
	\end{equation*}
	assuming $z_{\star}^2 > \log(4)$. 
	\item If $z_{\star}^2 \geq 2\log(4)$, then
	\begin{equation}
	\label{eqn:crude1}
	2\sqrt{z_{\star}^2 - \log(4)} \geq z_{\star} \geq 1.
	\end{equation}
	\item If $\gamma/2 > z_{\star}^2 \geq 2\log(4)$, then 
	\begin{equation}
	\label{eqn:crude2}
	1 - 2\mc{S} \geq 1/2.
	\end{equation}
	\item If
	\begin{equation*}
	8\log\biggl(\frac{32}{\pi^{1/2}}\biggr) \leq \gamma^2
	\end{equation*}
	then 
	\begin{equation}
	\label{eqn:crude3}
	\sqrt{\frac{\Theta(1 - 2\mc{S})}{\mc{C}}} \geq 2\sqrt{\frac{2\mc{S}}{1 - \mc{S}}}.
	\end{equation}
	\item Under~\eqref{eqn:crude1} - \eqref{eqn:crude3}, from Theorem~\ref{thm:uniform_bound} it holds that
	\begin{equation*}
	av_2(x) \geq \sigma_{\star} - \frac{80 \pi^{1/4} \mc{C}^{1/2}}{p^{\star}}.
	\end{equation*}
\end{itemize}

\end{document}

### 2021-12-23 notes/weekly_notes/12.3.20.NotesForWeek.tex

--- 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex
@@
-\documentclass{report}
-\usepackage{amsmath}
-\usepackage{amsfonts, amsthm, amssymb}
+\documentclass{article}
+\usepackage{amsmath, amsfonts, amsthm, amssymb}
 \usepackage{graphicx}
@@
 \usepackage[shortlabels]{enumitem}
+\usepackage{mathtools}
+\usepackage{tikz}
+\usepackage{verbatim}
 \usepackage{fullpage}
-\usepackage{mathtools}
-\usepackage{subcaption}
-\usepackage{tikz}
 
@@
 \DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
+\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}
+
+% Make a widecheck symbol (thanks, Stack Exchange!)
+\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
+\DeclareFontShape{U}{mathx}{m}{n}{
+	<5> <6> <7> <8> <9> <10>
+	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
+	mathx10
+}{}
+\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
+\DeclareFontSubstitution{U}{mathx}{m}{n}
+\DeclareMathAccent{\widecheck}{0}{mathx}{"71}
+% widecheck made
 
@@
 \newcommand{\Reals}{\mathbb{R}}
-\newcommand{\Identity}{\mathbb{I}}
-\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
+\newcommand{\iid}{\overset{\text{i.i.d}}{\sim}}
 \newcommand{\convprob}{\overset{p}{\to}}
@@
 \newcommand{\seq}[1]{\set{#1}_{n \in \N}}
-\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
 \newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
@@
 \newcommand{\Cov}{\mathrm{Cov}}
-\newcommand{\Xsetiam}{\mathrm{diam}}
+\newcommand{\diam}{\mathrm{diam}}
 
@@
 \newcommand{\vol}{\mathrm{vol}}
+\newcommand{\dist}{\mathrm{dist}}
 \newcommand{\spansp}{\mathrm{span}~}
@@
 
-\newcommand{\Linv}{L^{\Xsetagger}}
+\newcommand{\Linv}{L^{\dagger}}
 \DeclareMathOperator*{\argmin}{argmin}
@@
 \newcommand{\vardeltapq}{\varDelta^{(p,q)}}
+\newcommand{\lambdavec}{\boldsymbol{\lambda}}
 
@@
 \newcommand{\Lgrid}{L_{\grid}}
-\newcommand{\Xsetgrid}{D_{\grid}}
-\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
-\newcommand{\Lap}{{\bf L}}
+\newcommand{\Dgrid}{D_{\grid}}
+\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
+\newcommand{\Lap}{L}
 \newcommand{\NLap}{{\bf N}}
 \newcommand{\PLap}{{\bf P}}
+\newcommand{\Id}{I}
 
@@
 \newcommand{\Xset}{\mathcal{X}}
+\newcommand{\Vset}{\mathcal{V}}
 \newcommand{\Sset}{\mathcal{S}}
@@
 \newcommand{\Tadj}{T^{\star}}
-\newcommand{\Xsetive}{\mathrm{div}}
-\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
+\newcommand{\dive}{\mathrm{div}}
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
 \newcommand{\gradient}{\mathcal{D}}
@@
 \newcommand{\critr}{R_n}
-\newcommand{\Xsetx}{\,dx}
-\newcommand{\Xsety}{\,dy}
-\newcommand{\Xsetr}{\,dr}
-\newcommand{\Xsetxpr}{\,dx'}
-\newcommand{\Xsetypr}{\,dy'}
+\newcommand{\dx}{\,dx}
+\newcommand{\dy}{\,dy}
+\newcommand{\dr}{\,dr}
+\newcommand{\dxpr}{\,dx'}
+\newcommand{\dypr}{\,dy'}
 \newcommand{\wt}[1]{\widetilde{#1}}
@@
 \newcommand{\LS}{\mathrm{LS}}
+\newcommand{\SM}{\mathrm{SM}}
 \newcommand{\OS}{\mathrm{OS}}
 \newcommand{\PLS}{\mathrm{PLS}}
-\newcommand{\dist}{\mathrm{dist}}
 
-%%% Order of magnitude
-\newcommand{\soom}{\sim}
-
-% \newcommand{\span}{\textrm{span}}
-
-\newtheoremstyle{alden}
-{6pt} % Space above
-{6pt} % Space below
-{} % Body font
-{} % Indent amount
-{\bfseries} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{alden}
-
-\newtheoremstyle{aldenthm}
-{6pt} % Space above
-{6pt} % Space below
-{\itshape} % Body font
-{} % Indent amount
-{\bfseries} % Theorem head font
-{.} % Punctuation after theorem head
-{.5em} % Space after theorem head
-{} % Theorem head spec (can be left empty, meaning `normal')
-
-\theoremstyle{aldenthm}
+%%% Theorem environments
 \newtheorem{theorem}{Theorem}
@@
 \begin{document}
-\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
+\title{Note on: Tightness of Upper Bounds on PPR Misclassification Error}
 \author{Alden Green}
@@
 
-\chapter{Lower bound for conductance of continuous-space ball walk}
-For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$.
-Further define
+\textbf{Setup}: We observe samples $x_1,\ldots,x_n \sim p$.
+For a given threshold $\lambda > 0$, we use a local clustering algorithm involving the PPR vector to recover an element $\mc{C}$ of the $\lambda$-upper-level-set of $p$.
+Letting $\mc{C}_{\sigma} = \mc{C} + B(0,\sigma)$, we obtain the following upper bound on the volume of the symmetric set difference $\Delta(\mc{C}_{\sigma}[X], \wh{C})  = \vol_{n,r}(\mc{C}_{\sigma}[X] \vartriangle \wh{C})$:
 \begin{equation*}
-\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
+\Delta(\mc{C}_{\sigma}[X], \wh{C}) \leq \underbrace{60}_{\textrm{PPR on a graph}} \cdot \underbrace{1028 \frac{\Lambda_{\sigma}^4 \rho^2 L^2 (d + 2)^3}{\lambda_{\sigma}^4 r^2} \log^2\biggl(c \frac{L\rho\Lambda_{\sigma}^{2/d}}{\lambda_{\sigma}^{2/d}r}\biggr)}_{\textrm{Upper bound on mixing time}} \cdot \underbrace{\frac{16}{9} \frac{dr\lambda(\lambda_{\sigma} - \theta r^{\gamma}/(\gamma + 1))}{\sigma \lambda_{\sigma}^2}}_{\textrm{Upper bound on normalized cut.}} \cdot (1 + c_\delta)
 \end{equation*} 
-The uniform continuous normalized cut and conductance are then
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
-\end{equation*}
-where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.
+with probability at least $1 - \delta$, for $n$ sufficiently large. The captions refer to the contribution to error of the three modular parts of our proof, which we detail next.
 
+\section{PPR on a graph}
+The following is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
 \begin{lemma}
-	\label{lem: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
-	\end{equation*}
-\end{lemma}
-Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
-\begin{corollary}
-	\label{cor: uniform_continuous_conductance}
-	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
-	\end{equation*}
-\end{corollary}
-
-\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
-Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance.
-The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use.
-For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
-\begin{equation*}
-\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
-\end{equation*}
-where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
-\begin{enumerate}
-	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
-	\begin{equation*}
-	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
-	\end{equation*}
-	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
-	\begin{equation*}
-	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
-	\end{equation*}
-	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
-	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
-		\label{lem: nonconvex_isoperimetry}
-		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$.
-Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$,
-		\begin{equation*}
-		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
-		\end{equation*}
-	\end{lemma}
-	\item[4.] 
-	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
-	\begin{equation*}
-	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
-	\end{equation*}
-	\begin{lemma}
-		\label{lem: one_step_distributions}
-		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_1}
-		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
-		\end{equation}
-		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
-		\begin{equation}
-		\label{eqn:one_step_distributions_2}
-		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
-		\end{equation}
-	\end{lemma}
-	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
-	\end{equation*}
-	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
-	\begin{equation*}
-	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
-	\end{equation*}
-\end{enumerate}
-The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e.
-a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show.
-In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
-\begin{equation*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
-\end{equation*}
-Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$.
-Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
-\end{equation*}
-Otherwise, we deduce that
-\begin{align*}
-\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
-& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
-& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
-& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
-\end{align*}
-Setting $\delta = 1/3$, we have
-\begin{equation*}
-\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
-\end{equation*}
-and putting $a = r\ell/(2\rho)$ yields the claim.
-
-Now, we turn to establishing the inequalities used in the above chain.
-
-\paragraph{Step 1: Lower bound the ergodic flow.}
-By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
-\begin{equation*}
-2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
-\end{equation*}
-
-\paragraph{Step 2: Estimate the stationary distribution.}
-
-Both the upper and lower  bounds on $\wt{\pi}_{\nu,r}(\mc{S})$ are a direct consequence of the following inequalities:
-\begin{equation*}
-\ell \nu_d r^d \nu(\mc{S})  \leq {J}_{\nu,r}(\mc{S}) \leq \nu_d r^d \nu(\mc{S}).
-\end{equation*}
-\paragraph{Step 3: Isoperimetric inequality.}
-NB: the proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\mc{C}_{\sigma}$ is itself convex, and is a primary technical contribution of the seminal work \textcolor{red}{(Lovasz 1990)}, extended by \textcolor{red}{(Dyer 1991)} among others.
-However, once the result is shown in the convex setting, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
-\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
-	For $\Omega_i, i = 1,2,3$, denote the preimage
-	\begin{equation*}
-	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
-	\end{equation*}
-	For any $x \in R_1, y \in R_2$, 
-	\begin{equation*}
-	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
-	\end{equation*}
-	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
-	\begin{equation*}
-	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
-	\end{equation*}
-	By Theorem 2.2 of \textcolor{red}{(Lovasz 1990)},
-	\begin{align*}
-	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
-	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
-	\end{align*}
-	and by the measure-preserving property of $g$, this implies
-	\begin{equation*}
-	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
-	\end{equation*}
-\end{proof}
-
-\paragraph{Step 4: Total variation distance.}
-
-\begin{proof}[Proof of Lemma~\ref{lem: one_step_distributions}]
-	Note that~\eqref{eqn:one_step_distributions_2} follows from~\eqref{eqn:one_step_distributions_1} by first taking the supremum over all $\mc{S} \subseteq \mc{C}_{\sigma}$, and then the infimum over all $x \in \mc{S}_1$ and $y \in \mc{S}_2$.
-
-	It remains to show~\eqref{eqn:one_step_distributions_1}.
-Let $\mc{R} = \mc{C}_{\sigma} \setminus \mc{S}$ and $\mc{I} = B(x,y) \cap B(y,r)$, and suppose without loss of generality that $\ell_{\nu,r}(x) > \ell_{\nu,r}(y)$.
-We can relate $\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})$ to the volume of the intersection $\mc{I}$ as follows:
-	\begin{align*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) & = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \\
-	& = 1 - \biggl(\frac{\nu\bigl(B(x,r) \cap \mc{R}\bigr)}{\ell_{\nu,r}(x)} + \frac{\nu\bigl(B(y,r) \cap \mc{S}\bigr)}{\ell_{\nu,r}(y)}\biggr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu\bigl(B(x,r) \cap \mc{R}\bigr) + \nu\bigl(B(y,r) \cap \mc{S}\bigr)\Bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\nu\bigl(\mc{I} \cap \mc{C}_{\sigma}\bigr) \\
-	& \leq 1 - \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu(\mc{I}) - \nu\bigl(B(x,r)\bigr) + \ell_{\nu,r}(x)\Bigr) \\
-	& = \frac{1}{\ell_{\nu,r}(x)}\Bigl(\nu_dr^d - \nu(\mc{I})\Bigr).
-	\end{align*}
-	Now, by hypothesis $\ell_{\nu,r}(x) \geq \ell \nu_dr^d$. On the other hand, Lemma~\ref{lem: volume_of_spherical_cap} gives a lower bound on the volume of $\mc{I}$, and from this we obtain
-	\begin{equation*}
-	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) \leq \frac{\|x - y\|}{\ell r} \sqrt{\frac{d + 2}{2\pi}};
-	\end{equation*}
-	solving for $\|x - y\|$ yields~\eqref{eqn:one_step_distributions_1}.
-\end{proof}
-
-\section{Volume Estimates}
-
-\begin{lemma}
-	\label{lem: overlap_balls}
-	For any $x,y \in \Rd$, it holds that
-	\begin{equation}
-	\label{eqn:overlap_balls_1}
-	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation}
-	If additionally $\|x - y\| \leq \sigma$, then
-	\begin{equation}
-	\label{eqn:overlap_balls_2}
-	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr)
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	We first prove~\eqref{eqn:overlap_balls_1}. It is not hard to see that $\mathcal{I} := B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height
-	\begin{equation*}
-	h = r - \frac{\|x - y\|}{2}
-	\end{equation*} 
-	As a result, by Lemma \ref{lem: volume_of_spherical_cap} we have
-	\begin{equation*}
-	\nu\bigl(\mathcal{I}\bigr) = \nu_d r^d I_{1 - \alpha}(\frac{d + 1}{2}; \frac{1}{2})
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha = 1 - \frac{2rh - h^2}{r^2} = \frac{\|x - y\|^2}{4r^2}.
-	\end{equation*}
-	Expanding the incomplete beta function in integral form, we obtain
-	\begin{align*}
-	\nu\bigl(\mathcal{I}\bigr) & = \nu_d r^d \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \\
-	& \overset{\text{(i)}}{\geq} \nu_d r^d \left(1 - \frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \frac{ \|x - y\|}{r} \right) \\
-	& \overset{\text{(ii)}}{\geq} \nu_d r^d \left(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}} \right),
-	\end{align*}
-	where $\text{(i)}$ follows from Lemma \ref{lem: beta_integral}, and $\text{(ii)}$ from Lemma \ref{lem: beta_function}.
-
-	We now establish~\eqref{eqn:overlap_balls_2}.
-Assume that $\|x - y\| = \sigma$, as otherwise if $\|x - y\| < \sigma$ the volume of the overlap will only grow.
-Then $B(x,r) \cap B(y,\sigma)$ contains a spherical cap of radius $r$ and height $r - \frac{r^2}{2\sigma}$, and similar derivations to those used to show~\eqref{eqn:overlap_balls_1} imply that
-	\begin{equation*}
-	\nu(\cap_r(r - r^2/(2\sigma))) \geq \frac{1}{2}\nu_dr^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation*}
-\end{proof}
-
-\subsection{Spherical caps and associated estimates}
-\label{subsec:caps}
-In this section, we state a result for the volume of a spherical cap and derive some 
-useful upper bounds. 
-\begin{lemma}
-	\label{lem: volume_of_spherical_cap}
-	Let $\mathrm{cap}_r(h)$ denote a spherical cap of radius $r$ and height $h$. Then, 
-	\begin{equation*}
-	\nu\bigl( \mathrm{cap}_r(h)  \bigr) = \frac{1}{2} \nu_d r^d I_{1 - \alpha}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
-	\end{equation*}
-	where
-	\begin{equation*}
-	\alpha := 1 - \frac{2 r h - h^2}{r^2}
-	\end{equation*}
-	and
-	\begin{equation*}
-	I_{1 - \alpha}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - \alpha} u^{z - 1} (1 - u)^{w - 1} du.
-	\end{equation*}
-	is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - \alpha$. 
-\end{lemma}
-The following result provides a lower bound on the Beta integral, and the result in Lemma~\ref{lem: beta_function} provides
-an upper bound on the ratio of Gamma functions. 
-\begin{lemma}
-	\label{lem: beta_integral}
-	For any $0 \leq \alpha \leq 1$,
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - 2\sqrt{\alpha}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We can write 
-	\begin{equation*}
-	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
-	\end{equation*}
-	The first integral is simply the beta function, with
-	\begin{equation*}
-	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
-	\end{equation*}
-	Noting that for all $u \in [0,1]$ and $d \geq 1$, $u^{(d - 1)/2} \leq 1$, the second integral can be upper bounded as follows:
-	\begin{equation*}
-	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du \leq \int_{1 - \alpha}^{1}(1 - u)^{-1/2}du = \int_{0}^{\alpha} u^{-1/2}du = 2\sqrt{\alpha}.
-	\end{equation*}
-\end{proof}
-
-\begin{lemma}
-	\label{lem: beta_function}
-	\begin{equation*}
-	\frac{\Gamma\bigl(\frac{d}{2}+ 1\bigr)}{\Gamma\bigl(\frac{d + 1}{2}\bigr) \Gamma\bigl(\frac{1}{2}\bigr)} \leq \sqrt{\frac{d + 2}{2\pi}}
-	\end{equation*}
-\end{lemma}
-\noindent The proof of Lemma \ref{lem: beta_function} is straightforward and follows from the fact that $\Gamma(1/2) = \sqrt{\pi}$ and the upper bound $\Gamma(x + 1)/ \Gamma(x+s) \leq (x + 1)^{1-s}$ for $s \in [0,1]$.
-
-\section{Other derived results}
-
-Lemma~\ref{lem:volume_perturbation} bounds the difference $\nu(B(x,r) \cap \mc{C}_{\sigma}) - \nu(B(y,r) \cap \mc{C}_{\sigma})$ as a function of $\|x - y\|_{\Rd}$.
-Unfortunately, it only kicks in when $\|x - y\| \lesssim r/d$, whereas we would like something which applies when $\|x - y\| \lesssim r/\sqrt{d}$.
-
-\begin{lemma}
-	\label{lem:volume_perturbation}
-	Let $x,y \in \mc{C}_{\sigma}$ satisfy $\|x - y\| < \frac{r}{d - 1}$. Then,
-	\begin{equation*}
-	\Bigl|\nu\bigl(B(x,r) \cap \mc{C}_{\sigma}\bigr) - \nu\bigl(B(y,r) \cap \mc{C}_{\sigma}\bigr)\Bigr| \leq \nu_dr^d\frac{d\|y - x\|}{(r - (d - 1)\|y - x\|)}
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	By the triangle inequality, 
-	\begin{align*}
-	\nu(B(x,r) \cap \mc{C}_{\sigma}) & = \int_{\mc{C}_{\sigma}} \1(\|z - x\| \leq r) \,dz \\
-	& \leq \int_{\mc{C}_{\sigma}} \1(\|z - y\| \leq r + \|y - x\|) \,dz \\
-	& = \int_{\mc{C}_{\sigma}} \bigl(\1(\|z - y\| \leq r) + \1(r < \|z - y\| \leq r + \|y - x\|) \bigr)  \,dz \\
-	& \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) + \nu_d\bigl((r + \|y - x\|)^d - r^d\bigr),
-	\end{align*}
-	and the upper bound $\nu(B(x,r) \cap \mc{C}_{\sigma}) \leq \nu(B(y,r) \cap \mc{C}_{\sigma}) +  \nu_dr^dd\|y - x\|/(r - (d - 1)\|y - x\|)$ follows by Bernoulli's inequality (\textcolor{red}{(Lemma 22)}).
-Reversing $x$ and $y$ gives an equivalent upper bound on $\nu(B(y,r) \cap \mc{C}_{\sigma})$.
-\end{proof}
-
-\chapter{Misclassification error of PPR}
-The following Lemma upper bounds the misclassification error of (a sweep cut of) a PPR vector, in terms of the \emph{normalized cut} and \emph{mixing time} functionals.
-It is essentially identical to Lemma 3.4 of~\textcolor{red}{(Zhu 2013)}, except with tighter constants.
-\begin{lemma}
+	\label{lem:zhu}
 	Let $G = (V,E)$ be a undirected, unweighted, connected graph and let $p_v^{(\varepsilon)}$ be an $\varepsilon$-approximation to the PPR vector $p_v := p(v,\alpha;G)$.
@@
 	\begin{equation*}
-	\vol(A \vartriangle S_{\beta,v};G) \leq \left(\frac{3}{\beta} + \frac{200}{9\vol(A;G)}\right) \frac{\Phi(A;G)}{\alpha}
+	\vol(A \vartriangle S_{\beta,v};G) \leq 6\frac{\Phi(A;G)}{\alpha \beta}.
 	\end{equation*}
 \end{lemma}
-\begin{proof}
-	We adopt the notation $\wt{p}_v$ for the (exact) PPR vector computed over the subgraph $G[A]$, and 
+I don't know how close to tight this is for a neighborhood graph.
+
+\section{Mixing time}
+We wish to upper bound the mixing time of a random walk over the subgraph $\wt{G}_{n,r} = G_{n,r}(\mc{C}_{\sigma}[X])$. Recall that our upper bound on mixing time for a general graph looks like
 \begin{equation*}
-	\wt{\pi}(u) = \frac{\deg(u;G[A])}{\vol(A;G[A])}
+\tau_{\infty}(G) \leq \frac{2}{\Phi^2(G)}\log(\mathrm{something}).
 \end{equation*}
-	for the stationary distribution of a random walk over $G[A]$.
-The proof of this Lemma proceeds along very similar lines to that of~\textcolor{red}{(Zhu 2013 Lemma 3.4)}.
-We directly use the following three inequalities, derived in that work:
-	\begin{itemize}
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.2.)} For any seed node $v \in A$, the following inequalities hold for every $u \in A$:
+where $\Phi^2(G)$ is the conductance of $G$; I don't know how close this is to tight.
+We relate the sample conductance $\Phi(\wt{G}_{n,r})$ to the population conductance $\wt{\Phi}_{\Pbb,r}$ using some bounds on the optimal transport distance between $\mathbb{P}_n$ and $\mathbb{P}$, and in turn relate $\wt{\Phi}_{\Pbb,r}$ to the uniform conductance $\wt{\Phi}_{\nu,r}$ using the upper and lower bounds on density $p$ within $\mc{C}_{\sigma}$.
+Now I want to investigate of our lower bound on $\wt{\Phi}_{\nu,r}$, which is
+\begin{equation*}
+\wt{\Phi}_{\nu,r} \geq \frac{\sqrt{2\pi}}{36} \ell^2 \frac{r}{\rho L}
+\end{equation*}
+
+\subsection{Tightness of lower bound on }
+Let's an accompanying upper bound on $\wt{\Phi}_{\nu,r}$. Let 
+\begin{equation*}
+\mc{C}_{\sigma} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,\rho/2],
+\end{equation*}
+and consider the partition of $\mc{C}_{\sigma}$ induced by the hyperplane $\{x \in \Rd: x_d = 0\}$, i.e
+\begin{equation*}
+\mc{L} = [-\sigma,\sigma]^{d - 1} \otimes [-\rho/2,0),~~\mc{R} = [-\sigma,\sigma]^{d - 1} \otimes [0,\rho/2].
+\end{equation*}
+Recalling that 
+\begin{equation*}
+\wt{\Phi}_{\nu,r}(\mc{L}) = \frac{\wt{Q}_{\nu,r}(\mc{L},\mc{R})}{\wt{\pi}_{\nu,r}(\mc{L})} = \frac{\int_{\mc{L}} \nu(B(x,r) \cap \mc{R}) \,dx}{\int_{\mc{L}} \nu(B(x,r) \cap \mc{C}_{\sigma}) \,dx} 
+\end{equation*}
+our goal will be to upper bound the numerator and lower bound the denominator of the above expression.
+
+We begin by upper bounding the numerator.
+For any $x \in \mc{L}$, either $\dist(x,\mc{R}) = -x \leq r$ in which case $B(x,r) \cap \mc{R} \subset \mathrm{cap}_r(r + x)$, or $\dist(x,\mc{R}) = -x > r$ in which case $B(x,r) \cap \mc{R} = \emptyset$.
+Thus
 \begin{equation}
-		\label{pf:zhu1}
-		\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u)
+\label{eqn:lb_conductance_1}
+\int_{\mc{L}} \nu\bigl(B(x,r) \cap \mc{R}\bigr) \,dx \leq (2\sigma)^{d - 1} \int_{-r}^{0} \nu(\mathrm{cap}_r(r + x)) \,dx = (2\sigma)^{d - 1} \int_{0}^{r} \nu\bigl(\mathrm{cap}_r(r - x)\bigr) \,dx.
 \end{equation}
-		\item \textcolor{red}{(Zhu 2013 Corollary 3.3)} For any seed node $v \in A$, there exists a non-negative distribution vector $\ell$ supported on $A$ for which
-		\begin{equation}
-		\label{pf:zhu2}
-		p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G),
-		\end{equation}
-		and $\|\ell\|_1 \leq 2\frac{\Phi(A;G)}{\alpha}$.
-		\item \textcolor{red}{(Zhu 2013 Lemma 3.1, Anderson 2007 Theorem 5.1)} There exists a set $A^g \subset A$ with $\vol(A^g;G) \geq \frac{1}{2}\vol(A;G)$ such that for every seed node $v \in A^g$, it holds that
-		\begin{equation}
-		\label{pf:zhu3}
-		\sum_{u \neq A} p_v(u) \leq 2\frac{\Phi(A;G)}{\alpha}.
-		\end{equation}
-	\end{itemize}
-	From these we can derive the following upper bound on the volumes of $S_{\beta,v} \setminus A$ and $A \setminus S_{\beta,v}$.
-	\begin{itemize}
-		\item For any $u \in S_{\beta,v} \setminus A$, $p_v^{(\varepsilon)}(u) > \beta \cdot \deg(u;G)$. Summing up over all such vertices, from~\eqref{pf:zhu3} we may conclude that
+Recalling that the volume of a hyperspherical cap is given by $\nu(\mathrm{cap}_r(h)) = \frac{1}{2}\nu_dr^dI_{1 - \alpha}\biggl(\frac{d + 1}{2};\frac{1}{2}\biggr)$ for $\alpha = 1 - \frac{2rh - h^2}{r^2}$, we have that
+\begin{align*}
+\int_{0}^{r} \nu\bigl(\mathrm{cap}_r(r - x)\bigr) \,dx & = \frac{1}{2}\nu_dr^d \int_{0}^{r} I_{1 - x^2/r^2}\Bigl(\frac{d + 1}{2}; \frac{1}{2}\Bigr) \,dx \\
+& = \frac{1}{2}\nu_dr^{d + 1} \int_{0}^{1} I_{1 - z^2}\Bigl(\frac{d + 1}{2}; \frac{1}{2}\Bigr) \,dz \tag{substituting $z = x/r$}\\ 
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} \int_{0}^{1 - z^2} u^{(d - 1)/2} (1 - u)^{-1/2} \,du \,dz \\
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} \int_{0}^{\sqrt{1 - u}} u^{(d - 1)/2} (1 - u)^{-1/2} \,dz \,du \tag{Fubini's Theorem} \\
+& = \frac{1}{2}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \int_{0}^{1} u^{(d - 1)/2} \,du \\
+& = \frac{1}{d + 1}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}},
+\end{align*}
+and plugging back in to~\eqref{eqn:lb_conductance_1}, we obtain
 \begin{equation*}
-		\vol(S_{\beta,v} \setminus A; G) \leq \frac{1}{\beta} \sum_{u \not\in A}p_v^{(\varepsilon)}(u) \leq 2\frac{\Phi(A;G)}{\beta \cdot \alpha}.
+\int_{\mc{L}} \nu\bigl(B(x,r) \cap \mc{R}\bigr) \,dx \leq \frac{(2\sigma)^{d-1}}{d + 1}\nu_dr^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma((d + 1)/2)\sqrt{\pi}} \leq \frac{(2\sigma)^{d - 1} \nu_d r^{d + 1}\sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}.
 \end{equation*}
-		\item For any $u \in A$, from~\eqref{pf:zhu1} and~\eqref{pf:zhu2} we obtain a lower bound on $p_v^{(\varepsilon)}(u)$,
+On the other hand, when $r \ll \sigma$ the denominator is $\int_{\mc{L}}\nu(B(x,r) \cap \mc{C}_{\sigma}) \,dx \approx \frac{1}{2}(2\sigma)^{d - 1} \rho \nu_d r^d$. Therefore,
 \begin{equation*}
-		p_v^{(\varepsilon)}(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u) - \varepsilon \cdot \deg(u;G).
+\wt{\Phi}_{\nu,r} \lessapprox \frac{2r(d + 2)^{1/2}}{(d + 1)\rho \sqrt{2\pi}}.
 \end{equation*}
-		If $u \not\in S_{\beta,v}$ then $p_v(u) < \beta \deg(u;G)$, and thus for all $u \in A \setminus S_{\beta,v}$ it must be that
-		\begin{equation}
-		\label{pf:zhu4}
-		\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(G[A])\bigr)\wt{\pi}(u) - (\varepsilon + \beta)\deg(u;G) \leq \wt{p}_{\ell}(u).
-		\end{equation}
+This matches our lower bound on $\wt{\Phi}_{\nu,r}$ up to a factor of $18/(2\pi\ell^2) \cdot \sqrt{(d + 2)/(d + 1)} < 3/\ell^2.$
 
-		Let us restrict our attention for the moment to those vertices $u$ with sufficiently large degree in $G[A]$; precisely speaking, let
+\section{Normalized cut}
+our upper bound on normalized cut---ignoring the terms that depend on the density---is 
 \begin{equation*}
-		A^{\mathrm{int}} := \Bigl\{u \in A: \deg(u;G[A]) > \bigl(1 - \alpha \cdot \beta \cdot \vol(A;G)\bigr) \deg(u;G) \Bigr\}.
+\wt{\Phi}_{\nu,r}(\mc{C}_{\sigma}) \lessapprox \frac{16dr}{9\sigma}.
 \end{equation*}
-		We note that for any $u \in A^{\mathrm{int}}$,
+\section{Lower bound on normalized cut}
+Our goal is to examine the tightness of our upper bound on normalized cut (Theorem 10 of our JMLR submission), by giving a comparable lower bound.
+Recall that the (uniform, population level) normalized cut of a set $\mc{C}_{\sigma}$ is given by
 \begin{equation*}
-		\wt{\pi}(u) > \frac{(1 - \alpha \beta \vol(A;G))\deg(u;G)}{\vol(A;G)},
+\Phi_{\nu,r}(\mc{C}_{\sigma}) := \frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx}.
 \end{equation*}
-		so that by~\eqref{pf:zhu4} it holds that
+As informed by the isoperimetric ratio, the worst-case for a functional like normalized cut should be when $\mc{C}_{\sigma}$ by a $d$-dimensional ball.
+Letting $\mc{C}_{\sigma} = B(0,\sigma)$, we have that
 \begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \deg(u;G) \leq \wt{p}_{\ell}(u)
+\frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx} = \frac{1}{\nu_d^2 r^d \sigma^d} \int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx.
 \end{equation*}
-		for any $u \in A^{\mathrm{int}} \setminus S_{\beta,v}$. Summing over all such u, we obtain
+If $\|x\| < \sigma - r$, then $B(x,r) \setminus \mc{C}_{\sigma} = \emptyset$.
+Otherwise $\sigma - r \leq \|x\| \leq \sigma$, and if $r \ll \sigma$ then $B(x,r) \setminus \mc{C}_{\sigma} \approx \mathrm{cap}_{r}(\|x\| - (\sigma - r))$.
+Converting to polar coordinates, we have:
+\begin{align*}
+\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx & \approx s_d \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(x - (\sigma - r))) t^{d - 1} \,dt \\
+& \geq s_d (\sigma - r)^{d - 1} \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(t - (\sigma - r)))  \,dt \\
+& = s_d (\sigma - r)^{d - 1} \int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz.
+\end{align*}
+As calculated below~\eqref{eqn:lb_conductance_1}, $\int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz = \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma(d/2 + 1/2)\sqrt{\pi}} \approx \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}}$ and hence
 \begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \cdot \vol(A^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \sum_{u \in A^{\mathrm{int}} \setminus S_{\beta,v}} \wt{p}_{\ell}(u) \leq 2\frac{\Phi(A;G)}{\alpha}
+\Phi_{\nu,r}(\mc{C}_{\sigma}) \approx s_d (\sigma - r)^{d - 1}\frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}} \frac{1}{\nu_d^2 r^d \sigma^d} \approx \frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}} \cdot \frac{dr}{\sigma}.
 \end{equation*}
-		where the second upper bound follows from the upper bound on $\|\ell\|_1$, since $\sum_{u \in A} \wt{p}_{\ell}(u) = \|\ell\|_1$. 
-		Then, from the assumed upper bounds on $\alpha, \beta$ and $\varepsilon$ we obtain the inequality
-		\begin{equation*}
-		\biggl(\frac{3(1 - \alpha \beta \vol(A;G))\cdot\bigl(1 - \alpha \tau_{\infty}(G[A])\bigr)}{4\vol(A;G)} - (\beta + \varepsilon)\biggr) \geq \frac{9}{100\vol(A;G)}.
-		\end{equation*}
-		\item Finally, for every $u \in A \setminus A^{\mathrm{int}} $, it holds that $\mathrm{cut}(u, A^C;G[A]) \geq \alpha \cdot \beta \cdot \vol(A;G) \cdot \deg(u;G)$.
-Summing over all such vertices, we obtain
-		\begin{equation*}
-		\vol(A \setminus A^{\mathrm{int}};G) \leq \frac{\Phi(A;G)}{\alpha \cdot \beta}.
-		\end{equation*}	
-	\end{itemize}
-\end{proof}
+By contrast, our upper bound is $\approx dr/\sigma$, revealing a gap of roughly $\frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}$.
 

### 2021-12-23 notes/weekly_notes/9.20.19.NotesForWeek.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}

\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}

%%% Data
\newcommand{\Xbf}{X}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}

%%% Vector spaces
\newcommand{\Zbb}{\mathbb{Z}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\nabla}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\spl}{\textrm{sp}}
\newcommand{\dist}{\textrm{dist}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Notes for 9/20/19 - 9/27/19}
\author{Alden Green}
\date{\today}
\maketitle

\section{Consistency of spectral clustering in the $\epsilon$-outlier model.}

Let $X = x_1,\ldots,x_n \in \Rd$ be sampled independently from the nonparametric mixture distribution
\begin{equation*}
P = \sum_{m = 1}^{M} \pi_k \Psi_k + \epsilon \Psi_0,
\end{equation*}
where $0 < \epsilon < 1$ is the fraction of ``outliers'', and $\pi_1,\cdots,\pi_M$ are mixture weights such that $\pi_1 + \cdots + \pi_M = 1 - \epsilon$. $\Psi_1, \ldots, \Psi_k$ will each be uniform distributions over sets $\mathcal{C}_1, \ldots, \mathcal{C}_m \subset \Rd$, and $\Psi_0$ will be the outlier distribution, a uniform distribution on $[-1,1]^d$.

We wish to examine the consistency properties of kernel-based spectral clustering algorithms in the $\epsilon$-outlier model. Since there are many variants of kernel-based spectral clustering algorithms, we will begin by formalizing the specific method we analyze. To keep things simple, suppose $M = 2$. Our algorithm requires two inputs from the user: a kernel function $K(x,y)$ and a threshold $t$.

\begin{algorithm}
	\caption{Kernel-based spectral clustering.}
	\label{alg: ppr}	
	{\bfseries Input:} data $X =\{x_1,\ldots,x_n\}$, kernel function $K(x,y)$, threshold $t \in \Reals$. \\     
	{\bfseries Output:} cluster $\widehat{C} \subseteq [n]$.
	\begin{algorithmic}[1]
		\STATE Form the $n \times n$ symmetric kernel matrix $A$ with entries = $A_{ij} = (K(x_i),K(x_j))$, and the normalized (Laplacian) $L = I - D^{-1/2}AD^{-1/2}$. 
		\STATE Compute the second eigenvector of $L$, $v_2 = (v_{2,1},\ldots,v_{2,n})$. 
		\STATE Output $\widehat{C} = \set{i: v_{2,i} > t}$. 
	\end{algorithmic}
\end{algorithm}

Let $C_m = \set{i: x_i \in \mathcal{C}_m}$ be the empirical analogue to the population $\mathcal{C}_m$. We say the estimator $\widehat{C}$ is a consistent cluster estimator of the mixture model $P$ if
\begin{equation*}
\lim_{n \to \infty} \left\{\min_{m = 1,\ldots,M} \frac{1}{n} \abs{\widehat{C} \cap C_m} \right\} = 0
\end{equation*}
with probability one.

\paragraph{Summary of analysis.}

It has been shown that the spectra of the Laplacian $L$ asymptotically converges to that of a population-level integral operator, which we now define. Consider the distribution-dependent convolution operator $\mathcal{K}_P: L^2(P) \to L^2(P)$, given by
\begin{equation*}
\mathcal{K}_Pf(x) = \int K(x,y) f(y) \,dP(y),
\end{equation*}
with associated degree functional $d(x) = \int K(x,y) \,dP(y)$ for $x \in \Rd$. The population-level version of the normalized Laplacian $L$ is given by
\begin{equation}
\label{eqn:normalized_Laplacian_operator}
\overline{L}_Pf(x) = f(x) - \int \overline{K}(x,y) f(y) \,dP(y) =: f(x) - \overline{K}_Pf(x)
\end{equation}
where $\overline{K}(x,y)$ is the normalized kernel function defined as
\begin{equation*}
\overline{K}(x,y) = 
\begin{cases}
\frac{K(x,y)}{\sqrt{d(x)}\sqrt{d(y)}}, & \textrm{if $d(x), d(y) > 0$} \\
0, & \textrm{otherwise.}
\end{cases}
\end{equation*}

The operators $\overline{L}_P$ and $\overline{K}_P$ share all the same eigenfunctions, and if $\lambda_k$ is an eigenvalue of $\overline{K}_P$ then $\mu_k = 1 - \lambda_k$ is an eigenvalue of $\overline{L}_P$. We therefore analyze the properties of the leading eigenvalues of $\overline{K}_P$, which we denote $\lambda_1 \geq \lambda_2 \geq \cdots$.\footnote{In order to ensure that $\overline{K}_P$ is compact and therefore has a discrete spectrum, we assume throughout that $\iint \overline{K}^2(x,y) \,dP(x) \,dP(y) < \infty$, so that $\overline{K}_P$ is a trace-class operator.}

\subsection{Consistency of spectral clustering under the noise-free model.}

In the noise-free model, $\epsilon = 0$ and our mixture model reduces to $P = \pi_1 \Psi_1 + \pi_2 \Psi_2$ and $\pi_1 + \pi_2 = 1$, $\pi_1, \pi_2 > 0$.

\subsubsection{Spectral analysis of the $p$-weighted Laplacian in the noise-free model.}

Let $\mathcal{S}$ be the support of $P$. For $u \in H^1(\mathcal{S})$, the weighted, normalized Laplacian operator $\overline{L}_{P}$ is given by
\begin{equation*}
L_Pu = -\frac{1}{p^{3/2}} \dive(p^2 \gradient(\frac{u}{p^{1/2}}))
\end{equation*}
(where we associate functions which are equal $P$-a.e.) We say $\lambda \in \Reals$ is an eigenfunction of $L_p$ if there exists $u \in H^1(\mathcal{S}), u \neq 0$ such that
\begin{equation}
\label{eqn:weighted_Laplacian_spectra}
\int_{\mathcal{S}} \gradient u \cdot \gradient v p^2(x) \,dx = \lambda \int_{\mathcal{S}} u v p(x) \,dx, \quad \textrm{for all $v \in H^1(\mathcal{S})$.}
\end{equation}
If $u \in H^1(D)$ satisfies \eqref{eqn:weighted_Laplacian_spectra}, then we say $u$ is an eigenvector of $L_P$.

Our first result concerns the null space of $L_P$. 
\begin{lemma}
	Suppose $\mathcal{C}_1$ and $\mathcal{C}_2$ are open, bounded, and connected domains with Lipschitz boundaries. Write $p_1$ and $p_2$ for the uniform densities over $\mathcal{C}_1$ and $\mathcal{C}_2$, and let $\lambda_0$ be the smallest eigenvalue of $L_P$. Then,
	\begin{itemize}
		\item $\lambda_0 = 0$.
		\item If additionally $\dist(\mathcal{C}_1, \mathcal{C}_2) > 0$, then $u_1 \propto \sqrt{p_1}$ and $u_2 \propto \sqrt{p_2}$ are both eigenvectors of $L_P$, with eigenvalue $\lambda_0$. 
		\item If $v \in H^1(\mathcal{S})$ is an eigenvector of $L_p$ and  $v \neq u_1, v \neq u_2$, then $v$ has eigenvalue greater than $0$.
	\end{itemize}
\end{lemma}

\subsubsection{Convergence of $\overline{L}_P$.}

We will require some (very mild) conditions on the internal and external connectivity of $\Cset_1$ and $\Cset_2$ to ensure the consistency of spectral clustering under this model. We assume the clusters $\Cset_m$ are each connected sets, and have interiors of positive probability, i.e. for $\Cset_m^{\sigma} = \set{x \in \Cset_m: \dist(x,\partial \Cset_m)}$, we assume $P(\Cset_m^{\sigma}) > 0$. Further, we assume that the separation between $\mathcal{C}_1$ and $\mathcal{C}_2$ is positive, meaning $s = \dist(\mathcal{C}_1,\mathcal{C}_2) > 0$.

Suppose $K(x,y) = k(\norm{x - y})$ for a kernel function supported on $[0,r)$. The following lemma details some useful properties of the leading eigenfunctions of the associated operator $\overline{K}_P$, when $r$ is chosen to be suitably small.

\begin{lemma}
	Assume $r < s$, and further that the conductance 
	\begin{equation*}
	\Psi(\Sset) = 
	\end{equation*}
\end{lemma}

\subsection{Perturbation analysis.}

In order to demonstrate that

\subsubsection{Cheeger's inequality.}

\subsection{Asymptotic analysis.}

\section{To add.}

\begin{itemize}
	\item Explain why this distribution is interesting.
	\item Detail the various possible generalizations (non-compact kernel function,non-uniform distributions,)
	\item Flesh out the summary of analysis section.
	\item Replace assumption on normalized cut by assumption that the clusters are $\sigma$-expanded sets. 
	\item Define $H^1(\mathcal{S})$.
	\item Background on the spectra of $L_P$ (i.e. how do we know it is countable?)
\end{itemize}

\end{document}

### 2021-12-23 references/notes/alberti97.tex

--- 2019-04-20 notes/weekly_notes/4.12.19.NotesForWeek.tex
@@
 \newcommand{\Qbb}{\mathbb{Q}}
-\newcommand{\Ebb}{\mathbb{E}}
 % \newcommand{\Pr}{\mathrm{Pr}}}
@@
 
-%%% Functionals over graphs
+%%% Functions over graphs
 \newcommand{\cut}{\mathrm{cut}}
 \newcommand{\vol}{\mathrm{vol}}
-% \newcommand{\deg}{\mathrm{deg}}
 
@@
 
-\title{Notes for the week of 4/8/19 - 4/12/19}
+\title{Notes on ``A nonlocal anisotropic model for phase transitions (Alberti 97)''}
 \author{Alden Green}
@@
 
-Let $\set{x_1, x_2, \ldots}$ be a sequence of points sampled independently from probability measure $\Pbb$ with density function $f$.
-For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ .
-Given some $\lambda, \sigma > 0$, let
+Let $\Csig = \Cset + B(0,\sigma)$ for some $\Cset \subset \Reals^d$. Define the nonlocal functional $F_{r}(v, \Csig)$ to be
 \begin{equation*}
-\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
+F_r(v, \Csig) := \frac{1}{4r} \iint_{\Csig} \frac{\1(\norm{x - y} \leq r)}{r^d} (v(x) - v(y))^2 dx dy + \frac{1}{r} \int_{\Csig} W(v(x)) dx
+\end{equation*}
+where $W:\Reals \to \Reals$ is a continuous function which vanishes at $\pm 1$ only and has at least \textcolor{red}{linear growth at infinity}.
+
+\begin{theorem}[Theorem 3.1]
+	Let $r_n \to 0$, $v_{n}: \Csig \to [-1,1]$ be such that $F_{r_n}(v_n, \Csig)$ is bounded. Then the sequence $\seq{v_n}$ is precompact in $L^1(\Csig)$. 
+\end{theorem}
+\begin{proof}
+	Throughout, let  $J_r(\norm{x - y}) := \frac{\1(\norm{x - y} \leq r)}{r^d}$. 
+	\item
+
+	\textbf{Step 1:} At first, we will assume each $v_n$ takes values in $\pm1$ only.
+
+	Extend each function $v_n$ to $1$ in $\Reals^d \setminus \Csig$, and observe that our hypothesis implies (\textcolor{red}{omitting the proof})
+	\begin{equation}
+	\label{eqn: nonlocal_functional_bound}
+	\iint_{\Reals^d \times \Reals^d} J_r(\norm{x - y}) \abs{v_n(x) - v_n(y)} dy dx = \mathcal{O}(r)
+	\end{equation} 
+	Moreover, it is an easily verifiable fact that for every non-negative $g \in L^1(\Reals^d)$,
+	\begin{equation*}
+	\iint_{\Reals^d \times \Reals^d} (g \ast g)(x - y) \abs{u(x) - u(y)} dy dx \leq 2 \norm{g}_1 \iint_{\Reals^d \times \Reals^d} g(x - y) \abs{u(x) - u(y)} dx dy
+	\end{equation*}
+	and in combination with \eqref{eqn: nonlocal_functional_bound} this implies
+	\begin{equation}
+	\label{eqn: nonlocal_functional_bound_1}
+	\iint_{\Reals^d \times \Reals^d} (J_r \ast J_r)(x - y) \abs{u(x) - u(y)} dy dx = \mathcal{O}(r)
+	\end{equation}
+
+	Since $J \ast J$ is a nonnegative continuous function, we may find a nonnegative smooth function $\varphi$ with compact support such that
+	\begin{equation}
+	\label{eqn: varphi}
+	\varphi \leq J_r \ast J_r,~ \abs{\nabla \varphi} \leq J \ast J.
+	\end{equation}
+	Letting $c = \int_{\Reals^d} \varphi(y) dy$, for $y \in \Reals^d$ define
+	\begin{equation*}
+	\varphi_r(y) := \frac{1}{cr^d} \varphi\left(\frac{y}{r}\right),~ w_n(y) := \varphi_{r_n} \ast v_n(y)
+	\end{equation*}
+	We claim that $\seq{w_n}$ is asymptotically equivalent to $\seq{v_n}$ in $L^1(\Reals^d)$ and that the gradients $\nabla{w_n}$ are uniformly bounded in $L^1(\Reals^d)$.
+Suppose this were true; then by Theorem \ref{thm: poincare}
+	\begin{equation*}
+	\norm{w_n}_{L^1(\Csig)} \leq \norm{w_n}_{L^{p^{\star}}(\Csig)} \leq \norm{w_n}_{L^{p*}(\Reals^d)} \leq C \norm{\nabla w_n}_{L^1(\Reals^d)} < \infty
+	\end{equation*}
+	and so $w_n \in W_{1,1}(\Csig)$. By the Rellich-Kondrachov Compactness Theorem (Theorem \ref{thm: arzela_ascoli}), $\seq{w_n}$ is precompact in $L^1(\Csig)$.
+
+	It remains to prove the claim. We have
+	\begin{align*}
+	\int_{\Reals^d} \abs{w_n(x) - v_n(x)} dx & = \int_{\Reals^d} \abs{ \int_{\Reals^d} \varphi_{r_n}(v_n(y) - v_n(x)) dy} dx \\
+	& \leq \iint_{\Reals^d \times \Reals^d} \abs{\varphi_{r_n}(\norm{x - y})} \abs{v_n(y) - v_n(x)} dy dx \\
+	& \leq \frac{1}{c} \iint_{\Reals^d \times \Reals^d} (J \ast J)(\norm{x - y}) \abs{v_n(y) - v_n(x)} dy dx = \mathcal{O}(r).
+	\end{align*}
+	where the last equality follows from \eqref{eqn: nonlocal_functional_bound_1}.
+
+	Moreover, 
+	\begin{align*}
+	\int_{\Reals^d} \abs{\nabla w_n} dx & = \int_{\Reals^d} \abs{\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) u_n(y) dy} dx \\
+	& \overset{(i)}{=} \int_{\Reals^d} \abs{\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) (u_n(y) - u_n(x)) dy} dx \\
+	& \leq \iint_{\Reals^d \times \Reals^d} \abs{\nabla \varphi_{r_n}(x - y)} (u_n(y) - u_n(x)) dy dx \\
+	& \overset{(ii)}{\leq} \frac{1}{cr}  \iint_{\Reals^d \times \Reals^d} (J_r \ast J_r)(x-y) (u_n(y) - u_n(x)) dy dx \\
+	& \overset{(iii)}{=} \mathcal{O}(1),
+	\end{align*}
+	where $(i)$ follows from $\int_{\Reals^d} \nabla \varphi_{r_n}(x - y) dy = 0$, in the light of the fact that $\varphi$ has compact support; $(ii)$ follows from \eqref{eqn: varphi}; and $(iii)$ from \eqref{eqn: nonlocal_functional_bound_1}.
+\end{proof}
+
+\section{Additional Information}
+
+For a function $J$, we write $J_r(x) := \frac{1}{r^d} J\left(\frac{x}{r}\right)$.
+
+The mollification of a function $f:\Reals^d \to \Reals$ by a mollifier $J_{r}$ is written $f_r: \Reals^d \to \Reals$, and is given by
+\begin{equation*}
+f_r(x) := J_r \ast f = \int_{\Reals^d} J_r(x - y) f(y) dy.
 \end{equation*}
 
-Write $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}$ and let $\widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr)$.
-For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
+\begin{theorem}[Arzela-Ascoli]
+	\label{thm: arzela_ascoli}
+	Suppose $\seq{f_n}$ is a sequence of real-valued functions defined on $\Reals^d$ such that for all $k \in \Naturals$, $x \in \Reals^d$,
 	\begin{equation*}
-\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \textrm{where}~ \widetilde{\cut}(S) := \cut(S;\widetilde{G}_{n,r}),~ \widetilde{\vol}(S) := \vol(S;\widetilde{G}_{n,r})
+	\abs{f_n(x)} \leq M
 	\end{equation*}
-and in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$. Then, the \emph{graph conductance profile} over $\widetilde{G}_{n,r}$ is
+	for some constant $M$, and that moreover the functions $f_n$ are \emph{uniformly equicontinuous}, meaning that for each $\epsilon > 0$ there exists $\delta > 0$ such that 
 	\begin{equation*}
-\widetilde{\Phi}_{n,r}(t) := \min_{\substack{S \subseteq \widetilde{\Xbf}_n: \\ 0 < \widetilde{\pi}_n(S) < t} } \widetilde{\Phi}_{n,r}(S)
-\end{equation*}
-where $\widetilde{\pi}_{n,r}(S) = \frac{\widetilde{\vol}(S)}{\widetilde{\vol}(\widetilde{\Xbf}_n)}$. We will prove a lower bound on the graph conductance profile by a continuous analogue.
-
-\subsection{Continuous conductance}
-
-Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. For $\Sset \subset \Rd$ a Borel set,
-\begin{equation*}
-\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
-\end{equation*}
-is the weighted volume.
-
-The $r$-ball walk over $\Csig$ is a Markov chain, with transition probability given by 
-\begin{equation*}
-\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\nu_{\Pbb}(\Sset \cap B(x,r))}{\nu_{\Pbb}(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.
-
-Denote the stationary distribution for this Markov chain by $\pi_{\Pbb,r}$, which is defined by the relation
-\begin{equation*}
-\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-Letting the \emph{local conductance} be given by
-\begin{equation*}
-\ell_{\Pbb,r}(x) := \nu_{\Pbb}(\Csig \cap B(x,r)) \tag{$x \in \Csig$}
-\end{equation*}
-a bit of algebra verifies that
-\begin{equation*}
-\pi_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
+	\abs{x - y} < \delta~ \Longrightarrow~ \abs{f_n(x) - f(n)}. \tag{for all $x,y \in \Reals^d$}
 	\end{equation*}
 
-We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
+	Then, there exists a subsequence $(f_{n_k})_{k \in \Naturals}$ and a continuous function $f$ such that
 	\begin{equation*}
-\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\pi_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-the \emph{(continuous) normalized cut} by
-\begin{equation*}
-\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2)}{\min \set{\pi_{\Pbb,r}(\Sset),\pi_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*}
-and the \emph{(continuous) conductance profile} by
-\begin{equation*}
-\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
-\end{equation*}
-where $\Sset^c = \Csig \setminus \Sset$.
-
-To relate the graph and continuous conductance profiles, we introduce mappings between the data $\widetilde{\Xbf}_n$ and the space $\Csig$.
-
-\subsection{Transportation maps and $TL^1$ distance. }
-Let
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
-\end{equation*} 
-be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$).
-A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,
-\begin{equation*}
-\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
-\end{equation*}
-
-If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}.
-Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.
-In fact, under suitable conditions, the convergence happens at rate $\left(\frac{\log n}{n}\right)^{1/d}$.
-
-\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
-	\label{lem: stagnating_transportation_maps}
-	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
-	\end{equation*}
-	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
-\end{lemma}
-
-\begin{definition}
-	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
-	\begin{equation}
-	\label{eqn: transportation_distance_1}
-	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
-	\end{equation}
-	and denote it $u_n \overset{TL^1}{\to} u$.
-\end{definition}
-
-\begin{remark}
-	\label{rmk: transportation_distance_equivalence}
-	Note that as written this is not a metric, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
-	\begin{equation}
-	\label{eqn: transportation_distance_2}
-	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
-	\end{equation}
-	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$.
-However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and
-	\begin{equation*}
-	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
-	\end{equation*}
-
-	Since this additional condition will be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}.
-See \textcolor{red}{Garcia Trillos 15} for more details.
-\end{remark}
-
-\section{Lower bound graph conductance profile}
-
-In order to lower bound the graph conductance profile $\widetilde{\Phi}_{n,r}(\cdot)$, we will need to split the analysis into two cases based on the size of $S \subseteq \widetilde{\Xbf}_n$.
-Define the \emph{graph local spread} to be
-\begin{equation*}
-s(G) := \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \cdot \min_{u \in V} \set{\pi(u;G)}.  \tag{$G = (V,E)$}
-\end{equation*}
-
-Theorem \ref{thm: graph_conductance_profile_lb_1} states that for subsets of $\widetilde{\Xbf}_n$ with volume at least $s(G)$, the graph normalized cut can be uniformly lower bounded by the continuous normalized cut.
-Sections \ref{sec: proof_and_supporting_theory} and \ref{sec: other_results} contains the proof of Theorem \ref{thm: graph_conductance_profile_lb_1} along with other relevant results.
-
-\begin{theorem}
-	\label{thm: graph_conductance_profile_lb_1}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then,
-	\begin{equation*}
-	\liminf_{n \to \infty} \Bigl\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \Bigr\} \geq \frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}
-	\end{equation*}
-	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \widetilde{\Xbf}_n: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$
-\end{theorem}
-
-Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
-\begin{lemma}
-	\label{lem: graph_conductance_profile_lb_1}
-	Let $G = (V,E)$ be an undirected graph, and $\mathcal{L}(G) = \set{S \subseteq V: \pi(S; G) \geq s(G)}$. Then,
-	\begin{equation*}
-	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Clearly, for any $u \in S$
-	\begin{equation}
-	\label{eqn: graph_conductance_profile_lb_1}
-	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \abs{S}
-	\end{equation}
-
-	Then, since $\pi(S;G) \leq s(G)$,
-	\begin{equation*}
-	\abs{S} \leq \pi(S;G) \cdot \frac{\vol(V;G)}{\min_{u \in V} \set{\mathrm{deg}(u;G)}} = \frac{\pi(S;G)}{\min_{u \in V} \set{\pi(u;G)}} \leq \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)},
-	\end{equation*}
-	and therefore by \eqref{eqn: graph_conductance_profile_lb_1}, for any $u \in S$
-	\begin{equation*}
-	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \geq \frac{1}{10}\deg(u;G)
-	\end{equation*}
-	and the statement follows by summing over all $u \in S$. 
-\end{proof}
-
-Theorem \ref{thm: graph_conductance_profile_lb_1} and Lemma \ref{lem: graph_conductance_profile_lb_1} together yield Corollary \ref{cor: graph_conductance_profile_lb}, the main result of these notes.
-
-\begin{corollary}[Lower bound on graph conductance profile]
-	\label{cor: graph_conductance_profile_lb}
-	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$.
-Then, with probability one the following asymptotic lower bound holds on the graph conductance function
-	\begin{equation*}
-	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\set{\frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}, \frac{1}{10}} \tag{$0 \leq t \leq \frac{1}{2}$}
-	\end{equation*}
-\end{corollary}
-
-\section{Proofs and Supporting Theory}
-\label{sec: proof_and_supporting_theory}
-
-\subsection{Proof of Theorem \ref{thm: graph_conductance_profile_lb_1}.}
-
-By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.
-
-For $S \subseteq \widetilde{\Xbf}_n$, let $T_n^{-1}(S) = \set{x \in \Csig: T_n(x) \in S}$ be the preimage of $T_n$, and note that $T_n^{-1}(S^c) = \Csig \setminus T_n^{-1}(S)$.
-
-Letting
-\begin{equation*}
-\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx},~ \gamma_n(S) := \frac{\min \set{\pi_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\pi_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^+}(T_n^{-1}(S^c))} }
-\end{equation*}
-where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, by Lemma \ref{lem: graph_to_continuous_conductance} and Corollary \ref{cor: nonuniform_continuous_conductance} we have that for all $S \subseteq \widetilde{\Xbf}_n$,
-\begin{align}
-\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
-& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^4r_n^{-}}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
-\end{align}
-
-By Lemma \ref{lem: cont_local_conductance}, with probability one
-\begin{equation*}
-\liminf_{n \to \infty} \xi_n = 1.
-\end{equation*}
-
-By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $c > \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}$, there exists some $n \in \Naturals$ such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
-\begin{equation*}
-\pi_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
-\end{equation*}
-and therefore by Lemma \ref{lem: cont_stationary_dist}
-\begin{equation*}
-\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
-\end{equation*}
-
-As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.
-
-\subsection{Graph functionals to continuous functionals.}
-
-Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.
-
-\begin{lemma}
-	\label{lem: volume_bound}
-	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2}\widetilde{\vol}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
-	\end{equation*}
-	where $r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$. 
-\end{lemma}
-\begin{proof}
-	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	u(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	Now, we proceed
-	\begin{align}
-	\frac{1}{\widetilde{n}^2} \widetilde{\vol}(S_n) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i)} \nonumber \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
-	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \label{eqn: vol_ub}\\
-	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
-	\end{align}
-
-	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
-	\begin{align*}
-	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
-	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) dx \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
-	\end{align*}
-	which is the desired upper bound. The lower bound follows a similar proof, with the only change being \eqref{eqn: vol_ub}, where $r_n^+$ is replaced by $r_n^-$ and the inequality is reversed.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: cut_bound}
-	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
-	\begin{equation*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c) 
-	\end{equation*}
-	where $r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^\infty(\widetilde{\Pbb})}$
-\end{lemma}
-\begin{proof}
-	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
-	\begin{equation*}
-	u(x) = 
-	\begin{cases}
-	1,~ x \in S \\
-	0,~ \text{otherwise}
-	\end{cases}
-	\end{equation*}
-
-	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
-	\begin{align*}
-	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i) - u(x_j)} \\
-	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x) - u(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
-	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
-	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
-	\end{align*}
-	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
-	\begin{align*}
-	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
-	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
-	\end{align*}	
-\end{proof}
-
-\begin{lemma}
-	\label{lem: graph_to_continuous_conductance}
-	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and let
-	\begin{equation*}
-	r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})},~ r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}.
-	\end{equation*}
-
-	Fix $S \subseteq \widetilde{\Xbf}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
-	\begin{equation}
-	\label{eqn: graph_to_continuous_conductance}
-	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}  \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
-	\end{equation}
-\end{lemma}
-\begin{proof}
-
-	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\widetilde{\vol}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset)}
-	\end{equation*}
-
-	But, noting that $\Sset^c = \set{x \in \Csig: T_n(x) \in S^c}$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S^c)}{\widetilde{\vol}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\pi_{\Pbb,r_n^+}(\Sset^c)}
-	\end{equation*}
-	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
-	\begin{equation*}
-	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} },
-	\end{equation*}
-	and the proof is complete.
-\end{proof}
-
-\subsection{Perturbation asymptotics.}
-
-In light of Lemma \ref{lem: stagnating_transportation_maps}, the error incurred in \eqref{eqn: graph_to_continuous_conductance} by the use of $r_n^{+}$ and $r_n^{-}$ as opposed to $r$ is asymptotically negligible.
-
-\begin{lemma}[Continuity of local conductance]
-	\label{lem: cont_local_conductance}
-	Letting $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, with probability one the following holds:
-	\begin{equation*}
-	\limsup_{n \to \infty} \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Let $\mathcal{R}_n(x) := \set{x' \in \Csig: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-)}$, we have
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx = \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx + \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx.
-	\end{equation*}
-	and therefore
-	\begin{equation*}
-	\frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx} = 1 + \frac{\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}. 
-	\end{equation*}
-	We upper bound the remainder term
-	\begin{equation*}
-	\int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d
-	\end{equation*}
-	and taking limits as $n \to \infty$ we obtain with probability one
-	\begin{equation*}
-	\limsup_{n \to \infty} \int_{\Csig} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \limsup_{n \to \infty} P(\Csig) \Lambda_{\sigma} \bigl((r_n^+)^d - r^d)\nu^d = 0
-	\end{equation*}
-	by the stagnating property of $\seq{T_n}$.
-
-	We apply a similar analysis to the denominator.
-	\begin{equation*}
-	\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx = \int_{\Csig} \int_{B(x,r_n^-)} f(y) f(x) dy dx \geq \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma} (r_n^{-})^d \nu_d
-	\end{equation*}
-	and therefore by the stagnating property of $\seq{T_n}$ and Lemma \ref{lem: local_conductance},
-	\begin{equation*}
-	\liminf_{n \to \infty} \int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx  = \frac{6}{25} \Pbb(\Csig) \lambda_{\sigma}^2 r^d \nu_d > 0
-	\end{equation*}
-	again with probability one.
-
-	The desired result then follows from an application of Slutsky's Theorem.
-\end{proof}
-
-\begin{lemma}[Continuity of stationary distribution]
-	\label{lem: cont_stationary_dist}
-	Let $c > 0$ be a fixed constant, $\seq{T_n}$ be a sequence of stagnating transportation maps, and $r_n^{\pm} = r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$.
-With probability one the following statement holds:
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } = 1
-	\end{equation*}
-	uniformly over all sets $\Sset \subseteq \mathfrak{B}(\Csig)$ satisfying $\min \set{\pi_{\Pbb,r}(\Sset), \pi_{\Pbb,r}(\Sset^c)}> c$. 
-\end{lemma}
-\begin{proof}
-	It will be sufficient to show that
-	\begin{equation*}
-	\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} ~ \text{and} \liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset^c)} = 1.
-	\end{equation*}
-	and we will show only that $\liminf_{n \to \infty} \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1$. The result for $\Sset^c$ is identical.
-
-	The proof proceeds similarly to Lemma \ref{lem: cont_local_conductance}. Letting 
-	\begin{equation*}
-	\mathcal{R}_n(x) := \set{x' \in \Sset: x' \in B(x,r_n^+), x' \not\in B(x,r_n^-}
-	\end{equation*}
-	Rewriting
-	\begin{equation*}
-	 \frac{\pi_{\Pbb,r_n^-}(\Sset)}{\pi_{\Pbb,r_n^+}(\Sset)} = 1 - \frac{\int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx}{\pi_{\Pbb,r_n^+}(\Sset)}
-	\end{equation*}
-	we have that
-	\begin{equation*}
-	\liminf_{n \to \infty} \int_{\Sset} \int_{\mathcal{R}_n} f(y) f(x) dy dx \leq \Pbb(\Sset) \Lambda_{\sigma} \liminf_{n \to \infty}\bigl( (r_n^+)^d - (r_n^-)^d\bigr) \nu^d = 0
-	\end{equation*}
-	where the equality occurs with probability one. On the other hand by hypothesis
-	\begin{equation*}
-	\limsup_{n \to \infty} \pi_{\Pbb,r_n^+}(\Sset) \geq c > 0.
-	\end{equation*}
-	and the result follows by Slutsky's Theorem. 
-\end{proof}
-
-\begin{lemma}[Stationary distribution lower bound]
-	\label{lem: stationary_dist_lb}
-	With probability one, the following statement holds: let $\seq{T_n}$ be a sequence of stagnating transportation maps from $\Pbb$ to $\Pbb_n$.
-Then, for any $\epsilon > 0$, there exists some $m \in \Naturals$ such that for all $n \geq m$,
-	\begin{equation*}
-	\min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \pi_{\Pbb,r}(T_n^{-1}(S)) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}  - \epsilon
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	Fix $\epsilon > 0$, and let $S \in \mathcal{L}(\widetilde{G}_{n,r})$ be arbitrary. Write $\Sset := T_n^{-1}(S)$.
-
-	We can upper bound $\widetilde{\pi}_{n,r}(S)$ by $\pi_{\Pbb,r}(\Sset)$ plus a remainder term.
-	\begin{align}
-	\widetilde{\pi}_{n,r}(S) & \leq \frac{\int_\Sset \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \nonumber \\
-	& = \pi_{\Pbb,r_n^-}(\Sset) + \frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x- x'} \leq r_n^+) f(x') f(x) dx' dx} \label{eqn: stationary_dist_lb_1}
-	\end{align}
-	Clearly $\pi_{\Pbb,r_n^-}(\Sset) \leq \pi_{\Pbb,r}(\Sset)$. Moreover
-	\begin{equation*}
-	\frac{\int_\Sset \int_{\Csig} \1(r_n^- \leq \norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx}{\int_{\Csig} \int_{\Csig} \1(\norm{x - x'} \leq r_n^+) f(x') f(x) dx' dx} \leq \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	and by \eqref{eqn: stationary_dist_lb_1}, we have
-	\begin{equation*}
-	s(\widetilde{G}_{n,r}) \leq \widetilde{\pi}_{n,r}(S) \leq \pi_{\Pbb,r}(\Sset) + \frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d
-	\end{equation*}
-	The remainder term $\frac{\Lambda_{\sigma}}{\lambda_{\sigma}} \left(\frac{r_n^+ - r_n^-}{r_n^-}\right)^d$ is independent of $S$ and asymptotically $o_p(1)$ by Lemma \ref{lem: stagnating_transportation_maps}.
-	An application of Lemma \ref{lem: local_spread_lb} completes the proof.
-\end{proof}
-
-\subsection{Continuous conductance function.}
-
-In Theorem \ref{thm: continuous_conductance_function}, we restate a necessary result from the 3/20 weekly notes.
-
-\begin{assumption}[Embedding]
-	\label{asmp: embedding}
-	Assume there exists $K \subset \Rd$ convex space, mapping $g: K \to \Csig$, and constant $L < \infty$ such that
-	\begin{equation*}
-	\forall x,y \in K,  \abs{g(x) - g(y)} \leq L \abs{x - y},~\text{and}~ \det(D_x g) = 1.
-	\end{equation*}
-	In other words, $g$ is measure-preserving and $L$-Lipschitz.
-\end{assumption}
-
-\begin{theorem}
-	\label{thm: continuous_conductance_function}
-	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$.
-Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
-	\begin{equation*}
-	\widetilde{\Phi}_{\nu,r}(t) \geq \frac{r}{2^{12} D_K L \sqrt{d}}.
+	f_{n_k} \to f~~ \textrm{uniformly on compact subsets of}~ \Reals^d
 	\end{equation*}
@@
 
-Corollary \ref{cor: nonuniform_continuous_conductance} follows \textcolor{red}{almost immediately} for Theorem \ref{thm: continuous_conductance_function}.
+\begin{definition}
+	Let $X$ and $Y$ be Banach spaces, $X \subset Y$. We say that $X$ is \emph{compactly embedded} in $Y$, written
+	\begin{equation*}
+	X \subset \subset Y
+	\end{equation*}
+	if 
+	\begin{enumerate}[(i)]
+		\item $\norm{u}_Y \leq C \norm{u}_X$ for some constant $C$, and
+		\item each bounded sequence in $X$ is precompact in $Y$. 
+	\end{enumerate}
+\end{definition}
 
-\begin{corollary}
-	\label{cor: nonuniform_continuous_conductance}
-	Assume $\Csig \subset \Rd$ satisfies Assumption \ref{asmp: embedding} with respect to some convex set $K \subset \Rd$ and Lipschitz function $g$ with Lipschitz constant $L <  \infty$.
-Then, for any $0 < r < \sigma / 2 \sqrt{d}$, the continuous conductance function of the speedy $r$-ball walk satisfies
+Recall that the Sobolev conjugate is $p^*= \frac{pn}{n - p}$.
+
+\begin{theorem}[Rellich-Kondrachov Compactness Theorem]
+	\label{thm: compact_embedding}
+	Assume $U$ is a bounded open subset of $\Reals^d$ and $\partial U$ is $C^1$. Suppose $1 \leq p < d$. Then
 	\begin{equation*}
-	\widetilde{\Phi}_{\Pbb,r}(t) \geq \frac{\lambda_{\sigma}^4 r}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}.
+	W^{1,p}(U) \subset \subset L^q(U)
 	\end{equation*}
-	where we recall $\lambda_{\sigma} = \inf_{x \in \Csig} f(x)$ and $\Lambda_{\sigma} = \sup_{x \in \Csig} f(x)$. 
-\end{corollary}
+	for $1 \leq q < p^{\star}$. In particular, since $p^{*} > p$, we have
+	\begin{equation*}
+	W^{1,p}(U) \subset \subset L^p(U)
+	\end{equation*}
+	for all $1 \leq p$.
+\end{theorem}
 
-\section{Other results}
-\label{sec: other_results}
-
-We state Lemma \ref{lem: local_conductance} without proof. The proof in the uniform case can be found in the 3/20 notes.
-
-\begin{lemma}
-	\label{lem: local_conductance}
-	Let $x \in \Csig$. Then, for any $r < \frac{\sigma}{2\sqrt{d}}$,
+\begin{theorem}[Gagliardo-Nirenberg-Sobolev]
+	\label{thm: poincare}
+	Assume $1 \leq p < d$. There exists constant $C$, depending only on $p$ and $d$, such that
 	\begin{equation*}
-	\ell_{\Pbb,r}(x) \geq \frac{6\lambda_{\sigma}^2}{25} r^d \nu_d
+	\norm{u}_{L^{p^*}(\Reals^d)} \leq C \norm{D u}_{L^{p}(\Reals)}
 	\end{equation*}
-	and for any $r > 0$,
-	\begin{equation*}
-	\ell_{\Pbb,r}(x) \leq \Lambda_{\sigma}^2 r^d \nu_d
-	\end{equation*}
-\end{lemma}
-
-\begin{lemma}
-	\label{lem: max_degree} 
-	Let 
-	\begin{equation*}
-	\mu' = \frac{6(n - 1)\lambda_{\sigma}^2}{25} r^d \nu_d,~ \mu = (n-1) \Lambda_{\sigma}^2 r^d \nu_d.
-	\end{equation*}
-	Then for any $\delta \in [0,1]$,
-	\begin{align*}
-	\Pr \biggl(\min_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \leq (1 - \delta) \mu' \biggr) \leq (n - 1)\exp\{-\delta^2 \mu' / 2\} \\
-	\Pr \biggl(\max_{x_i \in \widetilde{\Xbf}_n} \deg(x_i; \widetilde{G}_{n,r}) & \geq (1 + \delta) \mu \biggr) \leq (n - 1)\exp\{-\delta^2 \mu / 3\}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	For each $x_i \in \widetilde{\Xbf}_n$, letting $Y_{ij} =  \1(x_j \in \Csig, \norm{x_i - x_j} \leq r)$ we can write $\deg(x_i; \widetilde{G}_{n,r}) = \sum_{i \neq j} Y_{ij}$.
-Note that $\Ebb(Y_{ij} | x_i) = \ell_{\Pbb,r}(x_i)$, and $Y_ij$ and $Y_{ij'}$ are independent for all $j \neq j'$.
-Therefore the desired result follows from Lemmas \ref{lem: local_conductance} and \ref{lem: multiplicative_chernoff_bound} along with a union bound.
-\end{proof}
-
-\begin{lemma}
-	\label{lem: local_spread_lb}
-	With probability one, the following statement holds:
-	\begin{equation*}
-	\liminf_{n \to \infty} s(\widetilde{G}_{n,r}) \geq \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2} 
-	\end{equation*}
-\end{lemma}
-\begin{proof}
-	We rewrite
-	\begin{align*}
-	s(\widetilde{G}_{n,r}) & = \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{\widetilde{\vol}_{n,r}(\widetilde{\Xbf}_n)} \\
-	& \geq \frac{9 \left[\min_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}\right]^2}{n \max_{x \in \widetilde{\Xbf}_n}\set{\widetilde{\deg}_{n,r}(x)}}
-	\end{align*}
-	The statement follows by Lemma \ref{lem: max_degree} and the Borel-Cantelli Lemma.
-\end{proof}
-
-\begin{lemma}[Multiplicative Chernoff Bound]
-	\label{lem: multiplicative_chernoff_bound}
-	Let $p', p \in [0,1]$, and let $Y_1, \ldots, Y_n$ be independent $\{0,1\}$-valued random variables with $p' \leq E(Y_i) \leq p$ for all $i = 1,\ldots,n$. Then, letting $\mu = pn$ and $\mu' = p'n$,
-	\begin{align*}
-	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \leq (1 - \delta)\mu' \biggr) \leq \exp\{-\delta^2 \mu' / 2\} \\
-	\Pr \biggl(\sum_{i = 1}^{n} {Y_i} \geq (1 + \delta)\mu \biggr) \leq \exp\{-\delta^2 \mu / 3\}
-	\end{align*}
-	for any $\delta \in [0,1]$.
-\end{lemma}
-
+	for all $u \in C_c^1(\Reals^d)$. 
+\end{theorem}
 \end{document}

### 2021-12-23 arxiv/appendix.tex
Updated arxiv version of paper.

@@
 
-\section{Fixed graph results}
+\section{Fixed Graph Results}
 \label{apdx:fixed_graph}
-In this appendix, we give all results that hold with respect to an arbitrary graph $G$.
+In this section, we give all results that hold with respect to an arbitrary graph $G$.
 For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.
+\\
 
@@
 \end{equation*}
-We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq n \cdot d_{\max}(G)$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.)
-
-\paragraph{Organization.} In the following sections we establish: (Section \ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (Section \ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (Section \ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (Section \ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (Section \ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
-
-\subsection{Misclassification error of clustering with PPR and aPPR}
+We note that $d_{\min}(G)^2 \leq d_{\min}(G) \cdot n \leq \vol(G) \leq d_{\max}(G) \cdot n$, and that for any $S \subseteq V$, $|S| \cdot d_{\min}(G) \leq \vol(S;G)$ (where $|S|$ is the cardinality of $S$.) \\
+
+\emph{Organization.} In the following sections we establish: (Section \ref{subsec:pf_lem_zhu}) an upper bound on the misclassification error of PPR in terms of $\alpha$ and $\Phi(C;G)$ (Lemma~\ref{lem:zhu}), and an analogous result for aPPR (Corollary~\ref{cor:zhu}); (Section \ref{subsec:ppr_uniform_bounds}) a uniform bound on the perturbations of the PPR vector, to be used later in the proof of Theorem~\ref{thm:density_cluster_consistent_recovery} (consistency of PPR);  (Section \ref{subsec:lovasz_simonovits_bounds}) upper bounds on the mixedness of $q_v^{(t)}$ (as a function of $t$) and $p_v$ (as a function of $\alpha$), which will be helpful in the proofs of Proposition~\ref{prop:pointwise_mixing_time} and Theorem~\ref{thm:ppr_lb}; (Section \ref{subsec:pf_prop_pointwise_mixing_time}) an upper bound on $\tau_{\infty}(G)$ in terms of $\Psi(G)$ and $s(G)$ (Proposition~\ref{prop:pointwise_mixing_time}); and (Section \ref{subsec:ppr_spectral_partitioning}) an upper bound on the normalized cut $\Phi(\wh{C};G)$ in terms of $\Phi(C;G)$, to be used later in the proof of Theorem~\ref{thm:ppr_lb} (negative example).
+
+\subsection{Misclassification Error of Clustering with PPR and aPPR}
 \label{subsec:pf_lem_zhu}
@@
 where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$.
-Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry},
+Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(\ell)$, as a consequence of~\eqref{pf:interpolator_bound_max_entry},
 \begin{equation*}
@@
 \end{equation*}
-	and consequentially for any $S \subset V$,
+and consequently for any $S \subset V$,
 \begin{align*}
@@
 	\label{lem:tv_to_pointwise}
-	For any $t \in \mathbb{N}$,
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{2 \cdot \mathrm{TV}(q_v^{(t)}, \pi)}{s(G)}.
+	For any $t_{\ast} \in \mathbb{N}$,
+	\begin{equation*}
+	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{1}{s(G)} \biggl(\sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{t_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{t_{\ast}}}\biggr).
 	\end{equation*}
 \end{lemma}
-
-The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward.
-\paragraph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
-	Put $t_{\ast} = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
-We will use Theorem~\ref{thm:mixing_time_rw} to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$.
+The proof of Proposition~\ref{prop:pointwise_mixing_time} is then straightforward. \\
+
+\noindent\emph{Proof of Proposition~\ref{prop:pointwise_mixing_time}.}
+Put $T = 8/(\Psi(G)^2) \ln(4/s(G)) + 4$.
+We will use Theorem~\ref{thm:mixing_time_rw} to show that $\mathrm{TV}(q_v^{(T)},\pi) \leq 1/4$.
 This will in turn imply (\cite{montenegro2002} pg.
-13) that for $\tau_{\ast} = t_{\ast} \log_2(8/s(G))$,
-	\begin{equation*}
-	\mathrm{TV}(q_v^{(\tau_{\ast})},\pi) \leq \frac{1}{8}s(G),
-	\end{equation*}
-	and applying Lemma~\ref{lem:tv_to_pointwise} gives
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(\tau_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} \leq \frac{1}{4}.
-	\end{equation*}
+13) that for all $t \geq t_{\ast} := T \log_2(32/s(G))$,
+\begin{equation}
+\label{pf:pointwise_mixing_time_1}
+\mathrm{TV}(q_v^{(t)},\pi) \leq \frac{1}{32}s(G).
+\end{equation}
+Finally, let $\tau_{\ast} = t_{\ast} + 4\log_2(1/s(G))$. Applying Lemma~\ref{lem:tv_to_pointwise} gives
+\begin{align*}
+\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(\tau_{\ast} + 1)}(u)}{\pi(u)}\Bigr\} & \leq \frac{1}{s(G)}\biggl(\sum_{t = 0}^{\tau_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{\tau_{\ast}}}\biggr) \\
+& = \frac{1}{s(G)}\biggl(\sum_{t = t_{\ast} + 1}^{\tau_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{\tau_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{\tau_{\ast}}}\biggr) \\
+& \leq \frac{1}{4},
+\end{align*}
+where the final inequality follows from~\eqref{pf:pointwise_mixing_time_1} and the crude upper bound $\mathrm{TV}(q,\pi) \leq 1$, which holds for any distribution $q$.
 Taking maximum over all $v \in V$, we conclude that $\tau_{\infty}(G) \leq \tau_{\ast} + 1$, which implies the claim of Proposition~\ref{prop:pointwise_mixing_time}.
 
-	It remains to show that $\mathrm{TV}(q_v^{(t_{\ast})},\pi) \leq 1/4$. Choosing $t_0 = 4$ in the statement of Theorem~\ref{thm:mixing_time_rw}, we have that
-	\begin{align*}
-	\mathrm{TV}(q_v^{(t_{\ast})},\pi) & \leq \frac{1}{16} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
-	& \leq \frac{1}{8} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{t_{\ast} - 4} \\
-	& \leq \frac{1}{8} + \frac{1}{2s(G)} \exp\Bigl(-\frac{\Psi(G)^2}{8}(t_{\ast} - 4)\Bigr) = \frac{1}{4},
-	\end{align*}
-	where the middle inequality follows by assumption.
-
-\paragraph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
-	We proceed by induction. In the base case $t = 0$, we have that
-	\begin{equation*}
-	\max_{u \in V} \Bigl\{\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)}\Bigr\} \leq 1 \leq 2(1 - \pi(v)) \leq 2\frac{\mathrm{TV}(q_v^{(0)},\pi)}{s(G)},
-	\end{equation*},
-	where the second inequality follows since $\pi(v) \leq d_{\max}(G)/(2m) \leq d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$.
-
-	To prove the inductive step, the key observation is the following equivalence (see equation (16) of \citep{morris2005}):
+It remains to show that $\mathrm{TV}(q_v^{(T)},\pi) \leq 1/4$. Choosing $t_0 = 4$ in the statement of Theorem~\ref{thm:mixing_time_rw}, we have that
+\begin{align*}
+\mathrm{TV}(q_v^{(T)},\pi) & \leq \frac{1}{16} + \frac{d_{\max}(G)}{d_{\min}(G)^2} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{T - 4} \\
+& \leq \frac{1}{8} + \frac{1}{2s(G)} \Bigl(1 - \frac{\Psi(G)^2}{8}\Bigr)^{T - 4} \\
+& \leq \frac{1}{8} + \frac{1}{2s(G)} \exp\Bigl(-\frac{\Psi(G)^2}{8}(T - 4)\Bigr) = \frac{1}{4},
+\end{align*}
+where the middle inequality follows by assumption. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:tv_to_pointwise}.}
+Our goal will be to establish the recurrence relation~\eqref{pf:tv_to_pointwise_2}. 
+To derive~\eqref{pf:tv_to_pointwise_2}, the key observation is the following equivalence (see equation (16) of \cite{morris2005}):
 \begin{align}
@@
 so that we obtain the recurrence relation
-	\begin{equation*}
+\begin{equation}
+\label{pf:tv_to_pointwise_2}
 \frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} +\frac{\pi(u) - q_v^{(t)}(u)}{2\pi(u)}.
-	\end{equation*}
-	Then by the inductive hypothesis $\bigl(\pi(u) - q_v^{(t)}(u)\bigr)/\bigl(2\pi(u)\bigr) \leq \mathrm{TV}(q_v^{(t - 1)},\pi)/s(G)$, and consequentially
-	\begin{equation*}
-	\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{\mathrm{TV}(q_v^{(t)},\pi) }{s(G)} + \frac{\mathrm{TV}(q_v^{(t - 1)},\pi) }{s(G)} \leq 2\frac{\mathrm{TV}(q_v^{(t)},\pi)}{s(G)}.
-	\end{equation*}
-	This completes the proof of Lemma~\ref{lem:tv_to_pointwise}.
-
-\subsection{Spectral partitioning properties of PPR}
+\end{equation}
+From~\eqref{pf:tv_to_pointwise_2} along with the initial condition
+\begin{equation*}
+\Bigl\{\frac{\pi(u) - q_v^{(1)}(u)}{\pi(u)}\Bigr\} \leq 1 \leq 2(1 - \pi(v)) \leq 2\frac{\mathrm{TV}(q_v^{(0)},\pi)}{s(G)},
+\end{equation*}
+---where the second inequality follows because $\pi(v) \leq d_{\max}(G)/(2m) \leq d_{\max}(G)/d_{\min}(G)^2 \leq 1/16$---we obtain the upper bound
+\begin{equation*}
+\frac{\pi(u) - q_v^{(t + 1)}(u)}{\pi(u)} \leq \frac{1}{s(G)} \biggl(\sum_{t = 0}^{t_{\ast}} \frac{\mathrm{TV}(q_v^{(t)}, \pi)}{2^{t_{\ast} - t}} + \frac{\mathrm{TV}(q_v^{(0)}, \pi)}{2^{t_{\ast}}}\biggr).
+\end{equation*}
+This inequality holds for each $u \in V$, and taking the maximum over $u$ completes the proof of Lemma~\ref{lem:tv_to_pointwise}. \qed
+
+\subsection{Spectral Partitioning Properties of PPR}
 \label{subsec:ppr_spectral_partitioning}
@@
 	\label{eqn:conductance_lb_transportation_distance}
-	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{2B_6\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{B_6 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
-	\end{equation}
-	where $B_6 := 2d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
+	\Psi_r(\mbb{Q}_2) \geq \Psi_r(\mbb{Q}_1) \cdot \biggl(1 - \frac{B_6\Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2}\biggr) - \frac{B_6 \Delta_T(\mbb{Q}_1,\mbb{Q}_2)}{\bigl(1 - \Psi_r(\mbb{Q}_1)\bigr) \cdot \bigl(d_{\min}(\mbb{Q}_2)\bigr)^2},
+	\end{equation}
+	where $B_6 := 4d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}$ is a positive constant that does not depend on $\mbb{Q}_2$. 
 \end{proposition}
-We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$. 
-\paragraph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}
+We note that the lower bound can also be stated with respect to the $\infty$-optimal transport distance $\Delta_{\infty}(\mbb{Q}_1,\mbb{Q}_2)$.\\
+
+\noindent \emph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}
 Throughout this proof, we will write $\Delta_{12} = \Delta_T(\mbb{Q}_1,\mbb{Q}_2)$, and $\wb{\vol}_{\mbb{Q},r}(\mc{R}) = \min\bigl\{\vol_{\mbb{Q},r}\bigl(\mc{R}\bigr),\vol_{\mbb{Q},r}\bigl(\mc{R}^c\bigr)\bigr\}$ for conciseness.
@@
 \end{equation}
-	For any $x \in \Rd$, the remainder terms can be upper bounded: since $\Delta_{12} \geq 0$,
-	\begin{equation*}
-	R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{2 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= B_6} \cdot \Delta_{12},
-	\end{equation*}
-	if $0 \leq \Delta_{12} \leq r/(4(d - 1))$,
-	\begin{equation*}
-	R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq 2 B_6 \cdot \Delta_{12}.
+For any $x \in \Rd$, since $0 \leq \Delta_{12} \leq r/(4(d - 1))$, the remainder terms can be upper bounded as follows:
+\begin{equation*}
+R_{r - 2\Delta_{12} ,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{1 - \Bigl(1 - \frac{2\Delta_{12}}{r}\Bigr)^d \Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq \underbrace{4 d \nu_d r^{d - 1} \cdot \max_{x \in \Rd}\{g(x)\}}_{= B_6} \cdot \Delta_{12},
+\end{equation*}
+and
+\begin{equation*}
+R_{r,\mbb{Q}_1}^{(2\Delta_{12})}(x) \leq \nu_dr^d\Bigl\{\Bigl(1 + \frac{2\Delta_{12}}{r}\Bigr)^d - 1\Bigr\} \cdot \max_{x \in \Rd}\{g(x)\} \leq B_6 \cdot \Delta_{12}.
 \end{equation*} 
@@
 \begin{align*}
-	\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - B_6 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + 2B_6\Delta_{12}} \\
-	& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - 2B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
+\Phi_{\mbb{Q}_2,r}(\mc{S}) & \geq \frac{\cut_{\mbb{Q}_1,r}\bigl(T^{-1}(\mc{S})\bigr) - B_6 \Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6 \Delta_{12}} \\ & = \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S}))}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6\Delta_{12}}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) + B_6\Delta_{12}} \\
+& \overset{\eqref{pf:conductance_lb_transportation_distance_2}}{\geq} \Phi_{\mbb{Q}_1,r}(T^{-1}(\mc{S})) \cdot \biggl(\frac{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S}) - B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}\biggr) - \frac{B_6\Delta_{12}}{\wb{\vol}_{\mbb{Q}_2,r}(\mc{S})}.
 \end{align*}
@@
 \begin{equation*}
-	\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{2 B_6 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{B_6\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
+\inf_{\mc{S}: \mc{S} \in \mathfrak{L}_{r}(\mbb{Q}_1,\mbb{Q}_2)} \Phi_{\mbb{Q}_2,r}(\mc{S}) \geq \Psi_{r}(\mbb{Q}_1) \cdot \biggl(1 - \frac{B_6 \Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}\biggr) - \frac{B_6\Delta_{12}}{(1 - \Psi_r(\mbb{Q}_1)) \cdot d_{\min}(\mbb{Q}_2)^2}
 \end{equation*}
@@
 \begin{equation*}
-\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
-\end{equation*}
-with probability at least $1 - B_2/n$. Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance},
-\begin{equation*}
-\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
-\end{equation*}
-with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$.
-
-\section{Population functionals for density clusters}
+\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
+\end{equation*}
+with probability at least $1 - B_2/n$.
+Finally, appealing first to  Proposition~\ref{prop:conductance_lb_transportation_distance} and then to the bounds we have just established on $d_{\min}(\wt{\Pbb}_n)$ and $\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n)$, we conclude that the sample conductance is lower bounded,
+\begin{align*}
+\Psi_r(\wt{\Pbb}_n) & \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \\
+& \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta),
+\end{align*}
+with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$. \qed
+
+\section{Population Functionals for Density Clusters}
 \label{apdx:density_cluster_population_functionals}
 In this appendix, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$.
-In these proofs, we make use of some estimates on the volume of spherical caps (in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}).
-Finally, in Section~\ref{subsec:density_cluster_hard_case}, for the hard case distribution $\Pbb$ defined in~\eqref{eqn:lb_density} and $\mc{L}$ defined in~\eqref{eqn:lower_set}, establish bounds on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{L})$ and local spread $s_{\Pbb,r}(\mc{X})$; these will be useful in the proof of Theorem~\ref{thm:ppr_lb}.
+In these proofs, we make use of some estimates on the volume of spherical caps (given in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (Section~\ref{subsec:reverse_isoperimetric_inequalities}).
+Finally, in Section~\ref{subsec:density_cluster_hard_case}, for the hard case distribution $\Pbb$ defined in~\eqref{eqn:lb_density} and $\mc{L}$ defined in~\eqref{eqn:lower_set}, we establish bounds on the population-level normalized cut $\Phi_{\Pbb,r}(\mc{L})$ and local spread $s_{\Pbb,r}(\mc{X})$; these will be useful in the proof of Theorem~\ref{thm:ppr_lb}.
 Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.
@@
 \end{equation}  
-\paragraph{Proof of Lemma~\ref{lem:overlap_balls}.}
-	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
+\emph{Proof of Lemma~\ref{lem:overlap_balls}.}
+First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each of height $h = r - \frac{\|x - y\|}{2}$. 
 As a result, by Lemma~\ref{lem:volume_of_spherical_cap} we have
@@
 \nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a}\frac{\Gamma(\frac{d}{2} + 1)}{\Gamma(\frac{d + 1}{2})\Gamma(\frac{1}{2})}\biggr)  \geq \frac{1}{2}\nu_dr^d \biggl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\biggr).
-	\end{equation*}
-
-\subsection{Isoperimetric inequalities}
+\end{equation*} \qed
+
+\subsection{Isoperimetric Inequalities}
 \label{subsec:isoperimetric_inequalities}
-\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
+\citet{dyer1991b} establish the following isoperimetric inequality for convex sets.
 \begin{lemma}[Isoperimetry of a convex set.]
@@
 It remains to verify that $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing.
-For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
+For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - x_j$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$.
 Thus $(s/t)x \in B(0,s)$, and
@@
 \begin{equation*}
-	\Bigl(\mc{A}_j(t) - \{x_j\}\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- \{x_j\}\Bigr),
-	\end{equation*}
-	and applying $\nu(\cdot)$ to both sides yields the claim.
-
-\paragraph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted}.}
+\Bigl(\mc{A}_j(t) - x_j\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- x_j\Bigr),
+\end{equation*}
+and applying $\nu(\cdot)$ to both sides yields the claim. \qed \\
+
+\noindent \emph{Proof of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted}.}
 Fix $k \in \mathbb{N}$.
-To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
+To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma} > 0$ for all $x \in \mc{C}$.}
 \begin{equation*}
@@
 \end{align*}
-the final inequality follows from~\ref{asmp:embedding}, which implies that $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
+the final inequality follows from~\ref{asmp:embedding}, which along with the isodiametric inequality for convex sets~\citep{gruber2007} implies $\nu(\mc{C}_{\lambda,\sigma}) = \nu(\mc{K}) \leq \nu_d(\rho/2)^d$.
 The claim of Lemma~\ref{lem:density_cluster_local_spread} follows.
+\qed
 
@@
 The following Lemma lower bounds the population-level uniform conductance $\Psi_{\nu,r}(\mc{C}_{\lambda,\sigma})$.
+We note that for convex sets, results of this type are well known (see e.g.~\cite{vempala2005} and references therein).
 \begin{lemma}
 	\label{lem:uniform_density_cluster_conductance}
-	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho \in (0,\infty)$ and $L \in [1,\infty)$.
+	Suppose $\mc{C}_{\lambda,\sigma}$ satisfies Assumption~\ref{asmp:embedding} with respect to some $\rho \in (0,\infty)$ and $M \in [1,\infty)$.
 For any $0 < r \leq \sigma \cdot \sqrt{2\pi/(d + 2)}$, it holds that
@@
 Noting that $\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Psi_{\nu,r}(\mc{C}_{\lambda,\sigma}) \cdot \lambda_{\sigma}^2/\Lambda_{\sigma}^2$, Proposition~\ref{prop:density_cluster_conductance} follows from~\eqref{eqn:uniform_density_cluster_conductance}.
-
-\paragraph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
-	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.
+\\
+
+\noindent \emph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
+For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho M)$.
 
@@
 define $\mc{R}^{\delta}$ likewise, and let $\mc{B}^{\delta} = \mc{C}_{\lambda,\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$ consist of the remaining boundary points.
-	As is standard (see for example~\cite{dyer1991,lovasz1990}), the proof of Lemma~\ref{lem:uniform_density_cluster_conductance} uses several inequalities to lower bound the normalized cut $\Phi_{\wt{\nu},r}(\mc{S})$.
+As is standard (see for example~\cite{dyer1991b,lovasz1990}), the proof of Lemma~\ref{lem:uniform_density_cluster_conductance} uses several inequalities to lower bound the normalized cut $\Phi_{\wt{\nu},r}(\mc{S})$.
 \begin{itemize}
@@
 	\label{pf:uniform_density_cluster_conductance_2}
-		\nu(\mc{B}^{\delta}) \geq \frac{2 \cdot \mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \cdot \min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\}.
+	\nu(\mc{B}^{\delta}) \geq \frac{2 \cdot \mathrm{dist}(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho M} \cdot \min\bigl\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\bigr\}.
 	\end{equation}
@@
 \begin{equation*}
-	\Phi_{\wt{\nu},r}(\mc{S}) \geq \min\biggl\{(1 - a) \cdot \frac{r}{\rho L} \cdot \frac{\ell^2}{9} \cdot \sqrt{\frac{2\pi}{d + 2}}, \frac{a\ell}{6}\biggr\}
-	\end{equation*}
-	and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$.
-
-\subsection{Population functionals, hard case}
+\Phi_{\wt{\nu},r}(\mc{S}) \geq \min\biggl\{(1 - a) \cdot \frac{r}{\rho M} \cdot \frac{\ell^2}{9} \cdot \sqrt{\frac{2\pi}{d + 2}}, \frac{a\ell}{6}\biggr\}
+\end{equation*}
+and the claim follows from~\eqref{eqn:uniform_local_conductance}, which implies that $\ell \geq 1/2 \cdot (1 - r/\sigma)\sqrt{2\pi/(d + 2)}$. \qed
+
+\subsection{Population Functionals, Hard Case}
 \label{subsec:density_cluster_hard_case}
@@
 Noting that $\wh{C} = S_{\beta,v}$ for some $\beta \in (L,U)$, the claimed upper bound~\eqref{eqn:volume_ssd_ub} on $\Delta(\wh{C},\mc{C}[X])$ then follows from the upper bound~\eqref{eqn:sample_to_population_normalized_cut} on $\Phi_{n,r}(\mc{C}[X])$ and the upper bound on $\vol_{\Pbb,r}(\mc{C})$ in~\eqref{pf:volume_ssd_ub_1}.
+\qed
 
 \subsection{Proof of Theorem~\ref{thm:density_cluster_volume_ssd_ub}}
-From Theorem~\ref{thm:volume_ssd_ub}, we have with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
+From Theorem~\ref{thm:volume_ssd_ub}, we have that with probability $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subset \mc{C}_{\lambda,\sigma}[X]$ of volume at least $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that
 \begin{align*}
 \frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])} & \leq 60 \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\alpha_{\Pbb,r}(\mc{C}_{\lambda,\sigma},\delta)} \\
-& \leq \frac{780}{\ln(2)} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2} \cdot \ln^2\Bigl(\frac{8}{(1 - 3\delta) s_{\Pbb,r}(\mc{C})}\Bigr)
+& \leq \frac{1020}{\ln(2)} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)} \cdot \frac{\Phi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})}{\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma})^2} \cdot \ln^2\Bigl(\frac{32}{(1 - 3\delta) s_{\Pbb,r}(\mc{C})}\Bigr)
 \end{align*}
 The claimed upper bound~\eqref{eqn:density_cluster_volume_ssd_ub} on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$ then follows from the bounds~\eqref{eqn:density_cluster_local_spread}-\eqref{eqn:density_cluster_conductance} on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$, noting that the condition $r \leq \sigma/(4d)$ implies that $(1 - r/(4\rho L)) \geq 1 - 1/16$ and $1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)} \geq 1 - 1/\sqrt{32}$, and taking
-\begin{equation*}
-C_{1,\delta} := \frac{898560}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)},~~\textrm{and}~~C_{2,\delta} := \frac{36}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
-\end{equation*}
+\begin{align*}
+C_{1,\delta} & := \frac{1175040}{\pi \cdot \ln(2) \cdot (1 - 1/16)^2 \cdot (1 - 1/\sqrt{32})^4} \cdot \frac{(1 + 3\delta)(1 + 2\delta)}{(1 - 4\delta)^2(1 - 2\delta)}\\
+C_{2,\delta} & := \frac{144}{(1 - 1/\sqrt{32})} \cdot \frac{1}{1-3\delta}.
+\end{align*} \qed
 
@@
 \begin{equation}
+\begin{aligned}
 \label{pf:ppr_lb_3}
-	\frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+&\frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma} \\
+& \leq 72\sqrt{(8/3 + 8\delta) \cdot \frac{r}{\rho} \cdot \ln\Bigl(\frac{72 \rho \sigma}{(1 - 3\delta)\pi r^2 \epsilon^2}\Bigr)},
+\end{aligned}
 \end{equation}
@@
 
-	We turn to lower bounding $\cut_{n,r}(Z)$, which is considerably more involved.
-We will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into bins, relate the cut of $Z$ to the boundary of the binned set $\overline{Z}$, and then lower bound the size of the boundary of $\overline{Z}$.
-
-	Let $(k_1,k_2)$ for $k_1 \in \bigl[\frac{6\sigma}{r}\bigr], k_2 \in \bigl[\frac{2\rho}{r}\bigr]$ be the upper right  corner of the cube\footnote{Here we are assuming, without loss of generality, that $6\sigma/r \in \mathbb{N}$ and $2\rho/r \in \mathbb{N}$, and using the notation $[x] = \{1,\ldots,x\}$ for $x \in \mathbb{N}$.}
-	\begin{equation*}
-	Q_{(k_1,k_2)} = \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{2}r, -\frac{3\sigma}{2} + \frac{k_1}{2}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{2}r, -\frac{\rho}{2} + \frac{k_2}{2}r\biggr]
-	\end{equation*}
-	and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{6\sigma}{r}\right], k_2 \in \bigl[\frac{2\rho}{r}\bigr]}$ be the collection of such cubes.
-For a set $Z \subset X$ we define the binned set $\overline{Z} \subset \overline{Q}$ as follows
-	\begin{equation*}
-	\overline{Z} := \set{Q \in \overline{Q}: \Pbb_n(Z \cap Q) \geq \frac{1}{2}\Pbb_n(Q)},
-	\end{equation*}
-	and we let 
-	\begin{equation*}
-	\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{3\sigma}{r}\Bigr] \times \Bigl[\frac{\rho}{r}\Bigr]~~\textrm{such that}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
-	\end{equation*}
-	be the boundary set of $\overline{Z}$ in $\overline{Q}$.
-Intuitively, every point $x_i \in Z$ in the boundary set of $\overline{Z}$ will have many edges to $X\setminus Z$.
+We turn to lower bounding $\cut_{n,r}(Z)$. Establishing this lower bound is considerably more involved, and we start by giving an outline of our approach to build intuition.
+\begin{itemize}
+	\item \emph{Discretization}.
+Intuitively, we will approximate the cut of $Z$ by discretizing the space $\mathcal{X}$ into a collection of rectangular bins $\wb{Q}$.
+We will consider a subset of bins $\partial \wb{Z} \subseteq \wb{Q}$, which we call the discretized boundary of $Z$, and which consists of those bins $Q \in \wb{Q}$ containing many points $x_i \in Z$ adjacent, in the graph $G_{n,r}$, to many $x_j \in X \setminus Z$.
+This discretization allows us to relate $\cut_{n,r}(Z)$ to the number of bins in the discretized boundary $\partial \wb{Z}$, as in~\eqref{eqn:normalized_cut_lb_pf1}.
+	\item \emph{Slicing}.
+In order to lower bound the number of bins in the discretized boundary $|\partial \wb{Z}|$, we consider a second partition of $\mc{X}$ into horizontal slices $R$.
+We argue that for each slice $R$, one of two things must be true: either $R$ contains a bin belonging to the discretized boundary of $Z$, $Q \in \partial \wb{Z}$, or $(Z \vartriangle \mc{C}^{(1)}[X]) \cap R$ has a ``substantial'' volume,
+	\begin{equation*}
+	\vol_{n,r}\Bigl((Z \vartriangle \mc{C}^{(1)}[X]) \cap R\Bigr) \geq R_{\min},
+	\end{equation*}
+	where $R_{\min}$ is a random quantity defined in~\eqref{eqn:normalized_cut_lb_pf2}.
+	Summing over all slices $R$ then gives a lower bound on $|\partial \wb{Z}|$, as in~\eqref{eqn:normalized_cut_lb_pf2}. 
+	\item \emph{Probabilistic Guarantees}.
+The lower bound~\eqref{eqn:normalized_cut_lb_pf2} depends on two random quantities: the minimum number of points in any bin (denoted by $Q_{\min}$), and $R_{\min}$, which was discussed in the previous bullet.
+We give suitable lower bounds on each quantity, which hold with high probability, and which suffice to complete the proof of Lemma~\ref{lem:normalized_cut_lb}.
+\end{itemize}
+
+Now, we fill in the details, working step-by-step.\\
+
+\noindent \emph{Step 1: Discretization.}
+We begin by discretizing $\mc{X}$ into a collection of bins.
+To that end, to each $k_1 \in \bigl[\frac{12\sigma}{r}\bigr], k_2 \in \bigl[\frac{4\rho}{r}\bigr]$ associate the bin\footnote{Here we are assuming, without loss of generality, that $12\sigma/r \in \mathbb{N}$ and $4\rho/r \in \mathbb{N}$, and using the notation $[x] = \{1,\ldots,x\}$ for $x \in \mathbb{N}$.}
+\begin{equation*}
+Q_{(k_1,k_2)} := \biggl[-\frac{3\sigma}{2} + \frac{(k_1 - 1)}{4}r, -\frac{3\sigma}{2} + \frac{k_1}{4}r\biggr] \times \biggl[-\frac{\rho}{2} + \frac{(k_2 - 1)}{4}r, -\frac{\rho}{2} + \frac{k_2}{4}r\biggr];
+\end{equation*}
+and let $\overline{Q} = \set{Q_{(k_1,k_2)}: k_1 \in \left[\frac{12\sigma}{r}\right], k_2 \in \bigl[\frac{4\rho}{r}\bigr]}$ be the collection of such bins.
+Next, we define the binned set $\overline{Z} \subset \overline{Q}$ to contain all bins $Q \in \wb{Q}$ for which $Z \cap Q$ is larger than $X\setminus Z \cap Q$; in mathematical notation,
+\begin{equation*}
+\overline{Z} := \set{Q \in \overline{Q}: \Pbb_n(Z \cap Q) \geq \frac{1}{2}\Pbb_n(Q)}.
+\end{equation*}
+Then the discretized boundary $\partial \wb{Z}$ is 
+\begin{equation*}
+\partial \overline{Z} := \set{Q_{(k_1,k_2)} \in \overline{Z}: \exists (\ell_1,\ell_2) \in \Bigl[\frac{12\sigma}{r}\Bigr] \times \Bigl[\frac{4\rho}{r}\Bigr]~~\textrm{s.t.}~~Q_{(\ell_1,\ell_2)} \not\in \wb{Z}, \norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 = 1}.
+\end{equation*}
+Intuitively, every point $x_i \in Z$ which belongs to a cube in the boundary set $\partial\overline{Z}$ will have many edges to $X\setminus Z$.
 Formally, letting $Q_{\min} := \min_{Q \in \overline{Q}} \Pbb_n(Q)$, we have
@@
 \label{eqn:normalized_cut_lb_pf1}
-	\cut_{n,r}(Z) \geq \cut_{n,r}(Z \cap \set{x_i \in \overline{Z}}) \geq \frac{1}{4} \abs{\partial \overline{Z}} Q_{\min}^2,
-	\end{equation}
-	where the last inequality follows since for every cube $Q_k \in \partial\overline{Z}$, there exists a cube $Q_\ell \not\in \overline{Z}$ such that $\norm{i - j}_1 \leq 1$, and since each cube has side length $r/2$, this implies that for every $x_i \in Q_k$ and $x_j \in Q_\ell$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.
-
-	Now we move on lower bounding the size of the boundary $\abs{\partial\wb{Z}}$.
+\cut_{n,r}(Z) \geq \cut_{n,r}(Z \cap \set{x_i \in \overline{Z}}) \geq \frac{1}{4} \abs{\partial \overline{Z}} Q_{\min}^2.
+\end{equation}
+To establish the last inequality, we reason as follows: first, for every cube $Q_{(k_1,k_2)} \in \partial\overline{Z}$, there exists a cube $Q_{(\ell_1,\ell_2)} \not\in \overline{Z}$ such that $\norm{(k_1,k_2) - (\ell_1,\ell_2)}_1 \leq 1$; second, since each cube has side length $r/4$, this implies that for every $x_i \in Q_{(k_1,k_2)}$ and $x_j \in Q_{(\ell_1,\ell_2)}$ the edge $(x_i,x_j)$ belongs to $G_{n,r}$.\\
+
+\noindent \emph{Step 2: Slicing.}
+Now we move on lower bounding the size of the discretized boundary $\abs{\partial\wb{Z}}$.
 To do so, we divide $\mathcal{X}$ into slices horizontally.
-Let $R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{2}r, -\frac{\rho}{2} + \frac{k}{2}r\bigr]}$ be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{6\sigma}{r}]}$ be the binned version of $R_k$.
-For each $k$, either
+Let $$R_k = \set{(x_1,x_2) \in \mathcal{X}: x_2 \in \bigl[-\frac{\rho}{2} + \frac{(k - 1)}{4}r, -\frac{\rho}{2} + \frac{k}{4}r\bigr]}$$
+be the $k$th horizontal slice, and $\wb{R}_k = \set{Q_{(k_1,k)} \in \overline{Q}:k_1 \in [\frac{12\sigma}{r}]}$ be the binned version of $R_k$. For every $k$, we are in one of three cases:
 \begin{enumerate}
@@
 	\begin{equation*}
-		\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
+	\vol_{n,r}\Bigl( \bigl(Z \vartriangle \mc{C}^{(1)}[X]\bigr) \cap R_k \Bigr) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k), ~~\textrm{or}
 	\end{equation*}
@@
 \end{enumerate}
-	Let $N(R)$ be the number of slices for which $\wb{R}_k \cap \partial \wb{Z} \neq \emptyset$. By the cases elucidated above, letting
-	\begin{equation*} 
-	R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}
-	\end{equation*} 
-	we obtain the following lower bound on the volume of the symmetric set difference,
+In words, these cases describe, for each slice $R$, the situation in which the set $Z$ has a ``substantial'' boundary (Case 3), or the situation in which $Z$ does not have a substantial boundary, and instead has a substantial difference with $\mc{C}^{(1)}$ (Cases 1 and 2).
+
+Now, let $N(R)$ be the number of slices which contain a boundary cell,
+\begin{equation*}
+N(R) := \#\biggl\{k \in \biggl[\frac{2\rho}{r}\biggr]: \wb{R}_k \cap \partial \wb{Z} \neq \emptyset\biggr\}.
+\end{equation*}
+and let $R_{\min}$ be the minimum volume of the intersection of any slice $R_k$ with the density clusters $\mc{C}^{(1)}, \mc{C}^{(2)}$; formally,
+\begin{equation}
+\label{eqn:normalized_cut_lb_pf1.5}
+R_{\min} := \min_{k}\Bigl\{\vol_{n,r}(\mc{C}^{(1)}[X] \cap R_k) \wedge \vol_{n,r}(\mc{C}^{(2)}[X] \cap R_k)\Bigr\}.
+\end{equation} 
+Summing over all slices $R_k$, we have from our previous analysis that,
+\begin{equation*}
+\vol_{n,r}\biggl(Z \vartriangle \mc{C}^{(1)}[X]\biggr) = \sum_{k \in [2\rho/r]} \vol_{n,r}\biggl( (Z \vartriangle \mc{C}^{(1)}[X]) \cap R_k\biggr) \geq R_{\min}  \left[\frac{2\rho}{r} - \frac{N(R)}{2}\right].
+\end{equation*}
+Rearranging this expression and noting that $\abs{\partial\wb{Z}} \geq N(R)$,  we obtain the following lower bound on the cardinality of the discretized boundary,
 \begin{equation}
 \label{eqn:normalized_cut_lb_pf2}
-	\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1}{2} R_{\min}  \left[\frac{2\rho}{r} - N(R)\right] \Longleftrightarrow N(R) \geq 2\Bigl(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\Bigr)
-	\end{equation}
-	Finally note that $\abs{\partial\wb{Z}} \geq N(R)$. Therefore combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
+\abs{\partial\wb{Z}} \geq N(R) \geq 2\Bigl(\frac{2\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\Bigr).
+\end{equation}
+Combining \eqref{eqn:normalized_cut_lb_pf1} and \eqref{eqn:normalized_cut_lb_pf2}, we have that
 \begin{align}
 \cut_{n,r}(Z) & \geq \frac{1}{4}N(R) Q_{\min}^2 \nonumber \\
-	& \geq \frac{1}{2}\left(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
+& \geq \left(\frac{\rho}{r} - \frac{\vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X])}{2R_{\min}}\right) Q_{\min}^2 \label{eqn:normalized_cut_lb_pf3}
 \end{align}
-	for all $Z \subset X$.
-
+for all $Z \subset X$.\\
+
+\noindent \emph{Step 3: Probabilistic guarantees.}
 It remains to lower bound the random quantities $R_{\min}$ and $Q_{\min}$.
@@
 \label{eqn:normalized_cut_lb_pf4.5}
-	\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{\rho \sigma}.
+\min_{Q \in \overline{Q}} \Pbb(Q) \geq \frac{\epsilon r^2}{4 \rho \sigma},
 \end{equation}
@@
 \label{eqn:normalized_cut_lb_pf5}
-	\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{2 \sigma \rho^2}~~\textrm{for all $k$.} 
+\vol_{\Pbb,r}(\mc{C}^{(1)} \cap R_k) = \vol_{\Pbb,r}(\mc{C}^{(2)} \cap R_k) \geq \frac{\pi r^3}{4 \sigma \rho^2}~~\textrm{for all $k$.} 
 \end{equation}
@@
 Since $Q_{\min}$ and $R_{\min}$ are obtained by taking the minimum of functionals over a fixed number of sets in $n$, they concentrate tightly around their means.
-Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{12 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{2\rho}{r}$.
+Specifically, note that the total number of cubes is $\abs{\overline{Q}} = \frac{48 \sigma \rho}{r^2}$, and the total number of horizontal slices is $\frac{4\rho}{r}$.
 Along with \eqref{eqn:normalized_cut_lb_pf4.5} and \eqref{eqn:normalized_cut_lb_pf5}, by Lemma~\ref{lem:bernstein_union}
 \begin{equation*}
-	Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{\rho \sigma} ~~\textrm{and}~~ R_{\min} \geq (1 - \delta)\frac{\pi r^3}{2\sigma \rho^2 },
-	\end{equation*}
-	with probability at least $1 - \frac{12 \sigma \rho}{r^2}\exp\set{-\frac{n\delta^2\epsilon r^2 n}{4 \rho \sigma}} - \frac{2\rho}{r}\exp\set{-\frac{n\delta^2\pi r^3}{8\sigma\rho^2}}$.
+Q_{\min} \geq (1 - \delta)\frac{\epsilon r^2}{4 \rho \sigma}n ~~\textrm{and}~~ R_{\min} \geq (1 - \delta)\frac{\pi r^3}{4\sigma \rho^2 }n(n - 1),
+\end{equation*}
+with probability at least $1 - \frac{48 \sigma \rho}{r^2}\exp\set{-\frac{n\delta^2\epsilon r^2}{4 \rho \sigma}} - \frac{4\rho}{r}\exp\set{-\frac{n(n - 1)\delta^2\pi r^3}{8\sigma\rho^2}}$.
 Combining these lower bounds with \eqref{eqn:normalized_cut_lb_pf4} and \eqref{eqn:normalized_cut_lb_pf3}, we obtain
 \begin{equation*}	
-	\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{2(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
-	\end{equation*}
-	for all $Z \subseteq X$.
-
-\section{Additional results: aPPR and Consistency of PPR}
+\Phi_{n,r}(Z) \geq \frac{(1 - \delta)^2}{4(1 + \delta)\pi} \left(1 - 2 \frac{\sigma \rho}{(1 - \delta) r^2 n^2} \vol_{n,r}(Z \vartriangle \mc{C}^{(1)}[X]) \right) \frac{\epsilon^2 r}{\sigma},
+\end{equation*}
+for all $Z \subseteq X$. \qed
+
+\section{Additional Results: aPPR and Separation of Clusters via PPR}
 \label{apdx:appr_misclassification_error}
@@
 
-\subsection{Experimental settings for Figure \ref{fig:moons}}
+\subsection{Experimental Settings for Figure \ref{fig:moons}}
 

### 2021-12-23 arxiv/ppr_clustering_neighborhood_graph.tex
Updated arxiv version of paper.

@@
 
-\subsection{PPR clustering}
+\subsection{PPR Clustering}
 \label{subsec:ppr_clustering}
-We start by reviewing the PPR clustering algorithm. Let $G = (V,E)$ be an undirected, unweighted, and connected graph. We denote by $A \in \Reals^{n \times n}$ the adjacency
-matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
-also denote by $D$ the diagonal degree matrix, with entries $D_{uu} :=
-\sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
+We start by reviewing the PPR clustering algorithm.
+Let $G = (V,E)$ be an undirected, unweighted, and connected graph.
+We denote by $A \in \Reals^{n \times n}$ the adjacency matrix of $G$, with entries $A_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.
+We also denote by $D$ the diagonal degree matrix, with entries $D_{uu} := \sum_{v \in V} A_{uv}$, and by $I$ the $n \times n$ identity matrix.
 The PPR vector $p_v = p(v,\alpha;G)$ is defined with respect to a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, as the solution of the following linear system:
@@
 
-\subsection{Worst-case guarantees for PPR clustering}
-As mentioned, to date most analysis of local clustering has focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
+\subsection{Worst-Case Guarantees for PPR Clustering}
+As mentioned, most analyses of local clustering have focused on worst-case guarantees, defined with respect to functionals of an a priori fixed graph $G = (V,E)$.
 For instance, \cite{andersen2006} analyze the normalized cut of the cluster estimate $\wh{C}$ output by PPR, showing that when PPR is appropriately seeded within a candidate cluster $C \subseteq V$, the normalized cut $\Phi(\wh{C};G)$ is upper bounded by (a constant times)  $\sqrt{\Phi(C;G)}$.
@@
 and show that if $\Phi(C;G)$ is much smaller than $\Psi(G[C])^2$---where $G[C] = (C,E \cap (C \times C))$ is the subgraph of $G$ induced by $C$--- then (in addition to having a small normalized cut) the cluster estimate $\wh{C}$ approximately recovers $C$.
-Our own analysis builds on that of~\cite{zhu2013}, and we give a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
-For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our statistical setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\mathbb{P}$, the graph $G$ is a random neighborhood graph formed by the user, and the candidate cluster is a set $\mc{C} \subset \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
-
-\subsection{PPR on a neighborhood graph}
+Our own analysis builds on that of~\cite{zhu2013}, and we present a more detailed summary of their results in Section~\ref{sec:ub_symmetric_set_difference}.
+For now, we merely reiterate that the conclusions of \citet{andersen2006,zhu2013} cannot be straightforwardly applied to our setting, where the input data are random samples $\{x_1,\ldots,x_n\}$ drawn from a distribution $\Pbb$, the graph $G$ is a random neighborhood graph formed from the samples, and the candidate cluster is a set $\mc{C} \subseteq \Rd$.\footnote{Throughout, we use calligraphic notation to refer to subsets of $\Rd$.}
+
+\subsection{PPR on a Neighborhood Graph}
 \label{subsec:ppr_neighborhood_graph}
 We now formally describe the statistical setting in which we operate, as well as the method we will study: PPR on a neighborhood graph.
-Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution
-$\Pbb$ on $\Rd$. We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ . For a radius $r > 0$, we define
-$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an
-unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in
-E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the
-Euclidean norm.
-Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate $\wh{C} \subseteq X$.
-The precise PPR algorithm we analyze is summarized in Algorithm~\ref{alg:ppr}.
+Let $X = \{x_1,\ldots, x_n\}$ be samples drawn i.i.d.\ from a distribution $\Pbb$ on $\Rd$.
+We will assume throughout that $\Pbb$ has a density $f$ with respect to the Lebesgue measure $\nu$ on $\Rd$ .
+For a radius $r > 0$, we define $G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $X$, an unweighted, undirected graph with vertices $V=X$, and an edge $(x_i,x_j) \in E$ if and only if $i \neq j$ and $\|x_i - x_j\| \leq r$, where $\|\cdot\|$ is the Euclidean norm.
+Once the neighborhood graph $G_{n,r}$ is formed, the PPR vector $p_v$ is then computed over $G_{n,r}$, with a resulting cluster estimate \smash{$\wh{C} \subseteq X$}.
+The precise algorithm is summarized in Algorithm~\ref{alg:ppr}.
 
@@
 
-\subsection{Cluster accuracy}
+\subsection{Cluster Accuracy}
 We need a metric to assess the accuracy with which $\wh{C}$ estimates the candidate cluster $\mc{C}$.
-One commonly used metric is the misclassification error, i.e.
-the size of the symmetric set difference
-between $\wh{C}$ and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}. We
-will consider a related metric, the volume of the symmetric set difference,
-which weights misclassified points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
+One commonly used metric is the misclassification error, i.e., the size of the symmetric set difference between \smash{$\wh{C}$} and the empirical cluster $\mc{C}[X] = \mc{C} \cap X$ \citep{korostelev1993,polonik1995,rigollet2009}.
+We will consider a related metric, the volume of the symmetric set difference, which weights misclassified points according to their degree in $G_{n,r}$.
+To keep things simple, for a given set $S \subseteq X$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$.
+
 \begin{definition}
 	\label{def:volume_symmetric_set_difference}
-	For an estimator \smash{$\wh{C} \subseteq X$} and a set 
-	$\mathcal{C} \subseteq \Rd$, their symmetric set difference is 
+	For an estimator \smash{$\wh{C} \subseteq X$} and a set $\mc{C} \subseteq \Rd$, their symmetric set difference is  
 	\begin{equation*}
-	\wh{C} \vartriangle \mathcal{C}[X] :=
-	\bigl(\wh{C} \setminus \mathcal{C}[X]\bigr) \cup
-	\bigl(\mathcal{C}[X] \setminus \wh{C}\bigr).
+	\wh{C} \vartriangle \mc{C}[X] :=
+	\bigl(\wh{C} \setminus \mc{C}[X]\bigr) \cup
+	\bigl(\mc{C}[X] \setminus \wh{C}\bigr).
 	\end{equation*}
@@
 
-\subsection{Population normalized cut, conductance, and local spread}
-Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$---which govern the volume of the symmetric set difference $\Delta(\wh{C},\mc{C}[X])$.
-Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e.
-let
+\subsection{Population Normalized Cut, Conductance, and Local Spread}
+Next we define three population-level functionals of $\mc{C}$---the normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and the local spread $s_{\Pbb,r}(\mc{C})$---which we will use to upper bound the volume of the symmetric set difference \smash{$\Delta(\wh{C},\mc{C}[X])$} with high probability.
+
+Let the population-level \emph{cut} of $\mc{C}$ be the expectation (up to a rescaling) of $\cut_{n,r}(\mc{C}[X]) := \cut(\mc{C}[X]; G_{n,r})$,  and likewise let the population-level \emph{volume} of $\mc{C}$ be the expectation (up to a rescaling) of $\vol_{n,r}(\mc{C}[X]) := \vol(\mc{C}[X]; G_{n,r})$; i.e., let
 \begin{equation*}
@@
 \end{equation*}
-where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ to be the expected degree of $x$ in $G_{n,r}$. 
+where $\mc{C}^c := \Rd \!\setminus\! \mc{C}$. Also let $\deg_{\Pbb,r}(x) := \int_{\Rd} \1\{\|y - x\| \leq r\} \,d\Pbb(y)$ be the expected degree of $x$ in $G_{n,r}$. 
 \begin{definition}[Population normalized cut]
-	For a set $\mc{C} \subset \Rd$, distribution $\Pbb$ and radius $r > 0$, the \emph{population normalized cut} is
+	For a set $\mc{C} \subseteq \Rd$, distribution $\Pbb$, and radius $r > 0$, the \emph{population normalized cut} is
 	\begin{equation}
@@
 It is quite natural that $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ should help quantify the role geometry plays in local spectral clustering.
-Indeed, by construction these functionals are quite obviously the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities in turn suffice to upper bound the volume of the symmetric set difference.
-For this reason, similar population level functionals are used by \citep{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
+Indeed, these functionals are the population-level analogues of the empirical quantities $\Phi_{n,r}(\mc{C}[X]) := \Phi(\mc{C}[X];G_{n,r})$ and $\Psi_{n,r}(\mc{C}[X]) := \Psi(G_{n,r}\bigl[\mc{C}[X]\bigr])$, and as we have already mentioned, these empirical quantities can be used to upper bound the volume of the symmetric set difference.
+For this reason, similar population-level functionals are used by \cite{shi2009,schiebinger2015,garciatrillos19} in the analysis of \emph{global} spectral clustering in a statistical context.
 We will comment more on the relationship between these works and our own results in Section~\ref{subsec:related_work}.
@@
 \end{theorem}
-(In the above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put even more succinctly, we find that $\Delta(\wh{C},\mc{C}[X])$ is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $\bigl(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C}))\bigr)^2$.
+
+(Above, and throughout, $c$ stands for a universal constant that may change from line to line.) Put more succinctly, we find that \smash{$\Delta(\wh{C},\mc{C}[X])$} is small when $\Phi_{\Pbb,r}(\mc{C})$ is small relative to $(\Psi_{\Pbb,r}(\mc{C})/\log(1/s_{\Pbb,r}(\mc{C})))^2$.
 To the best of our knowledge, this gives the first population-level guarantees for local clustering in the nonparametric statistical context.
 
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
+Next, Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} informally summarizes the second of our main results (formally stated in Theorem~\ref{thm:density_cluster_volume_ssd_ub}) regarding the recovery of a $\lambda$-density cluster $\mc{C}_{\lambda}$ by PPR.
 For reasons that we explain later in Section~\ref{sec:ppr_density_cluster}, our cluster recovery statement will actually be with respect to the $\sigma$-thickened set $\mc{C}_{\lambda,\sigma} := \{x \in \Rd: \mathrm{dist}(x,\mc{C}_{\lambda}) < \sigma\}$, for a given $\sigma > 0$.
 The upper bound we establish is a function of various parameters that measure the conditioning of both the density cluster $\mc{C}_{\lambda,\sigma}$ and density $f$ for recovery by PPR.
-We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $L$.
-We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$,
+We assume that $\mc{C}_{\lambda,\sigma}$ is the image of a convex set $\mc{K}$ of finite diameter $\mathrm{diam}(\mc{K}) \leq \rho < \infty$ under a Lipschitz, measure-preserving mapping $g$, with Lipschitz constant $M$.
+We also assume that $f$ is bounded away from $0$ and $\infty$ on $\mc{C}_{\lambda,\sigma}$:
 \begin{equation*}
-0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\textrm{for all $x \in \mc{C}_{\lambda,\sigma}$},
+0 < \lambda_{\sigma} \leq f(x) \leq \Lambda_{\sigma} < \infty~~\text{for all $x \in \mc{C}_{\lambda,\sigma}$},
 \end{equation*}
-while satisfying the following low-noise condition:
+and additionally satisfies the following low-noise condition:
 \begin{equation*}
-\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\textrm{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
+\inf_{y \in \mc{C}_{\lambda,\sigma}} f(y) - f(x) \geq  \theta \cdot \dist(x, \mc{C}_{\lambda,\sigma})^{\gamma}~~\text{for all $x$ such that $0 < \dist(x,\mc{C}_{\lambda,\sigma}) \leq \sigma$.}
 \end{equation*}
@@
 	\label{thm:density_cluster_volume_ssd_ub_informal}
-	Let $\mc{C}_{\lambda} \subset \Rd$ be a $\lambda$-density cluster of a distribution $\Pbb$ that satisfies appropriate regularity conditions, and suppose Algorithm~\ref{alg:ppr} is well-initialized with respect to $\mc{C}_{\lambda,\sigma}$.
-For all $n \in \mathbb{N}$ sufficiently large, with high probability it holds that
-	\begin{equation}
-	\label{eqn:density_cluster_volume_ssd_ub_informal}
-	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
-	\end{equation}
+	If $\mc{C}_{\lambda} \subseteq \Rd$ is a $\lambda$-density cluster of a distribution $\Pbb$, which satisfies appropriate regularity conditions, and Algorithm~\ref{alg:ppr} is initialized properly with respect to $\mc{C}_{\lambda,\sigma}$, then for all sufficiently large $n$, with high probability it holds that
+	\begin{equation*}
+	\frac{\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}_{\lambda,\sigma})} \leq c \cdot d^4 \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(\frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr).
+	\end{equation*}
 \end{theorem}
-Equation~\eqref{eqn:density_cluster_volume_ssd_ub_informal} reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-The parameters $L$, $\rho$ and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
-Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$ and $\theta$ measure whether $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside the density cluster) or poorly conditioned (vice versa).
-Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} tells us that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is well-conditioned---i.e.
-$L^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---i.e.
-$\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
+
+The above result reveals the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
+Here $M$, $\rho$, and $\sigma$ capture whether $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned (short and fat) or poorly-conditioned (long and thin) for recovery by PPR.
+Likewise, the parameters $\lambda_{\sigma}, \Lambda_{\sigma}, \gamma$, and $\theta$ measure whether the density $f$ is well-conditioned (approximately uniform over the density cluster, and having thin tails outside of it) or poorly conditioned (vice versa).
+Theorem~\ref{thm:density_cluster_volume_ssd_ub_informal} says that if the thickened density cluster $\mc{C}_{\lambda,\sigma}$ is geometrically well-conditioned---meaning, $M^2\rho^2/(\sigma r) \approx 1$---and the density $f$ is well-conditioned near $\mc{C}_{\lambda,\sigma}$---meaning, $\Lambda_{\sigma} \approx \lambda \approx \lambda_{\sigma}$ and $\lambda - \theta r^{\gamma}/(\gamma + 1)$ is much less than $\lambda_{\sigma}$---then PPR will approximately recover $\mc{C}_{\lambda,\sigma}$.
 
@@
 \label{subsec:related_work}
-We now summarize some related work (in addition to the background already given above), regarding the theory of spectral clustering, and of density cluster recovery.
-
-\paragraph{Spectral clustering.}
+We now summarize some related work (in addition to the background material already given above), regarding the theory of spectral clustering, and of density cluster recovery.
+
+\subsubsection{Spectral Clustering} 
 In the stochastic block model (SBM), arguably one of the simplest models of network formation, edges between nodes independently occur with probability based on a latent community membership.
-In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating
-back to \citet{mcsherry2001} who gives conditions under which the entire
-community structure can be recovered. In more recent work, \citet{rohe2011}
-upper bound the fraction of nodes misclassified by a spectral algorithm for the
-high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
-results to the sparse (low average degree) regime. Relatedly,
-\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
-when the block model exhibits some hierarchical structure. The framework we
-consider, in which nodes correspond to data points sampled from an underlying 
-density, and edges between nodes are formed based on geometric proximity, is
-quite different than the SBM, and therefore so is our analysis.
-
-In general, the study of spectral algorithms on neighborhood graphs has been
-focused on establishing asymptotic convergence of eigenvalues and eigenvectors
-of certain sample objects to the eigenvalues and eigenfunctions of corresponding
-limiting operators. \citet{koltchinskii2000} establish convergence of spectral
-projections of the adjacency matrix to a limiting integral operator, with
-similar results obtained using simplified proofs in
-\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
-the Laplacian matrix for a neighborhood graph of fixed radius. \citet{belkin07} and
-\citet{garciatrillos18} extend these results to the regime where the radius $r
-\to 0$ as $n \to \infty$.
+In the SBM, the ability of spectral algorithms to perform clustering---or community detection---is well-understood, dating back to \citet{mcsherry2001} who gives conditions under which the entire community structure can be recovered.
+In more recent work, \citet{rohe2011} upper bound the fraction of nodes misclassified by a spectral algorithm for the high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these results to the sparse (low average degree) regime.
+Relatedly, \citet{clauset08,balakrishnan2011,li2018} analyze the misclassification rate when the block model exhibits some hierarchical structure.
+The framework we consider, in which nodes correspond to data points sampled from an underlying density, and edges between nodes are formed based on geometric proximity, is quite different than the SBM, and therefore so is our analysis.
+
+In general, the study of spectral algorithms on neighborhood graphs has been focused on establishing asymptotic convergence of eigenvalues and eigenvectors of certain sample objects to the eigenvalues and eigenfunctions of corresponding limiting operators.
+\citet{koltchinskii2000} establish convergence of spectral projections of the adjacency matrix to a limiting integral operator, with similar results obtained using simplified proofs in \citet{rosasco10}.
+\citet{vonluxburg2008} studies convergence of eigenvectors of the Laplacian matrix for a neighborhood graph of fixed radius.
+\citet{belkin07} and \citet{garciatrillos18} extend these results to the regime where the radius $r \to 0$ as $n \to \infty$.
 
@@
 
-\paragraph{Density clustering.} For a given threshold $\lambda \in (0,\infty)$, let \smash{$\mathbb{C}_f(\lambda)$} denote the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
-In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mathbb{C}_{f}(\lambda)$.
-By now, density clustering (and the related problem of level-set estimation) are quite well-understood.
-For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference
-metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and
-\citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider
-consistent estimation of the cluster tree $\{\mathbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
-
-We emphasize that our goal is
-not to improve on these results, nor to offer a better algorithm for density clustering. Indeed, seen as a density clustering algorithm, PPR has none 
-of the optimality guarantees found in the aforementioned works.
+\subsubsection{Density Clustering} 
+For a given threshold $\lambda \in (0,\infty)$, we denote by \smash{$\mbb{C}_f(\lambda)$} the connected components of the density upper level set $\{x \in \Rd: f(x) \geq \lambda\}$.
+In the density clustering problem, initiated by~\cite{hartigan1975}, the goal is to recover $\mbb{C}_{f}(\lambda)$.
+By now, density clustering, and the related problem of level-set estimation, have been thoroughly studied.
+For instance, \citet{polonik1995,rigollet2009, rinaldo2010, steinwart2015} study density clustering under the symmetric set difference metric, \citet{tsybakov1997,singh2009,jiang2017} describe minimax optimal level-set and cluster estimators under Hausdorff loss, and \citet{hartigan1981,chaudhuri2010,kpotufe11,balakrishnan2013,steinwart2017,wang2019} consider estimation of the cluster tree $\{\mbb{C}_f(\lambda): \lambda \in (0,\infty)\}$.
+
+We emphasize that our goal is not to improve on these results, nor is it to offer a better algorithm for density clustering.
+Indeed, seen as a density clustering algorithm, PPR has none of the optimality guarantees found in the aforementioned works.
 Rather, we hope to better understand the implications of our general theory by applying it within an already well-studied framework.
-We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mathbb{C}_f(\lambda)$.
+We should also note that since we study a local algorithm, our interest will be in a local version of the density clustering problem, where the goal is to recover a single density cluster $\mc{C}_{\lambda} \in \mbb{C}_f(\lambda)$.
 
@@
 We then show that under certain conditions the sample normalized cut, conductance, and local spread are close to their population-level counterparts, with high probability for sufficient number of samples.
-As a result, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ purely in terms of these population functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+As a result, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} purely in terms of these population-level functionals (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
 	\item In Section~\ref{sec:ppr_density_cluster}, we focus on the special case where the candidate cluster $\mc{C} = \mc{C}_{\lambda}$ is a \emph{$\lambda$-density cluster}---that is, a connected component of the upper level set $\{x: f(x) \geq \lambda\}$.
 We derive bounds on the population normalized cut, conductance, and local spread of the density cluster, which depend on $\lambda$ as well as some other natural parameters.
-This leads to an upper bound on the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster.
-(Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
-	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between $\wh{C}$ and the $\lambda$-density cluster is provably large.
+This leads to a bound on the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster (Theorem~\ref{thm:density_cluster_volume_ssd_ub}).
+	\item In Section~\ref{sec:lower_bound}, we prove a negative result: we give a hard distribution $\Pbb$ with corresponding density cluster $\mc{C}_{\lambda}$ for which the symmetric set difference between \smash{$\wh{C}$} and the $\lambda$-density cluster is provably large.
 	\item In Section~\ref{sec:experiments} we empirically investigate some of our conclusions, before ending with some discussion in Section~\ref{sec:discussion}.
@@
 
-\section{Recovery of a generic cluster with PPR}
+\section{Recovery of a Generic Cluster with PPR}
 \label{sec:ub_symmetric_set_difference}
 
-In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on $\Delta(\wh{C}, \mc{C}[X])$, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$ and conductance $\Psi_{\Pbb,r}(\mc{C})$.
+In the main result (Theorem~\ref{thm:volume_ssd_ub}) of this section, we give a high probability upper bound on the volume of the symmetric set difference \smash{$\Delta(\wh{C}, \mc{C}[X])$}, in terms of the population normalized cut $\Phi_{\Pbb,r}(\mc{C})$, conductance $\Psi_{\Pbb,r}(\mc{C})$, and local spread $s_{\Pbb,r}(\mc{C})$.
 We build to this theorem slowly, giving new structural results in two distinct directions.
-First, we build on some previous work (mentioned in the introduction) to relate $\Delta(\wh{C}, \mc{C}[X])$ to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$.
-Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues.
-
-\subsection{PPR cluster recovery: the fixed graph case}
+First, we build on some previous work (mentioned in the introduction) to relate \smash{$\Delta(\wh{C}, \mc{C}[X])$} to the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$, conductance $\Psi_{n,r}(\mc{C}[X])$, and local spread $s_{n,r}(\mc{C}[X]) := s(G_{n,r}[\mc{C}[X]])$.
+Second, we argue that when $n$ is large, each of these graph functionals can be bounded by their population-level analogues with high probability.
+
+\subsection{The Fixed Graph Case}
 \label{subsec:ppr_cluster_recovery_fixed_graph}
-When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subset V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate $\wh{C}$ and candidate cluster $C$.
+When PPR is run on a fixed graph $G = (V,E)$ with the goal of recovering a candidate cluster $C \subseteq V$, \cite{zhu2013} provide the sharpest known bounds on the volume of the symmetric set difference between the cluster estimate \smash{$\wh{C}$} and candidate cluster $C$.
 Since these results will play a major part in our analysis, in Lemma~\ref{lem:zhu} we restate them for the convenience of the reader.\footnote{Lemma~\ref{lem:zhu} improves on Lemma~3.4 of~\cite{zhu2013} by some constant factors, and for completeness we prove Lemma~\ref{lem:zhu} in the Appendix.
@@
 \end{equation}
-here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ that originates at node $v$ and runs for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+here $q_v^{(t)} := e_v W^t$ is the distribution of a lazy random walk over $G$ initialized at node $v$ and run for $t$ steps, and $\pi := \lim_{t \to \infty} q_v^{(t)}$ is the limiting distribution of $q_v^{(t)}$.
+
 \begin{lemma}[Lemma~3.4 of \cite{zhu2013}]
@@
 	\label{eqn:zhu_condition}
-	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}
-	\end{equation}
-	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
+	\alpha \leq \min\Bigl\{\frac{1}{45}, \frac{1}{2\tau_{\infty}(G[C])}\Bigr\},~~ \beta \leq \frac{1}{5\vol(C;G)}.
+	\end{equation}
+	Then there exists a set $C^g \subseteq C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ satisfies
 	\begin{equation}
@@
 
-\subsection{Improved bounds on mixing time} 
+\subsection{Improved Bounds on Mixing Time} 
 \label{subsec:mixing_time}
-Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subset \Rd$.
-Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on $\Delta(\wh{C};\mc{C}[X])$ that depends only on $\Pbb$ and $\mc{C}$.
-Unfortunately, however, there is a catch: when the graph $G = G_{n,r}$ and the candidate cluster $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mathbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, rendering~\eqref{eqn:zhu_ub2} a vacuous upper bound whenever the number of samples is sufficiently large.
-
-To fix this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on mixing time given in~\eqref{eqn:mixing_time_cheeger}.
+Having reviewed the conclusions of~\cite{zhu2013}, we return now to our own setting, where the data is not a fixed graph $G$ but instead random samples $\{x_1,\ldots,x_n\}$, and our goal is to recover a candidate cluster $\mc{C} \subseteq \Rd$.
+Ideally, we would like to apply~\eqref{eqn:zhu_ub2} with $C = \mc{C}[X]$ and $G = G_{n,r}$, replace $\Phi_{n,r}(\mc{C}[X])$ and $\Psi_{n,r}(\mc{C}[X])$ by $\Phi_{\Pbb,r}(\mc{C})$ and $\Psi_{\Pbb,r}(\mc{C})$ inside~\eqref{eqn:zhu_ub2}, and thereby obtain an upper bound on \smash{$\Delta(\wh{C};\mc{C}[X])$} that depends only on $\Pbb$ and $\mc{C}$.
+Unfortunately, however, there is a catch: when the graph is $G = G_{n,r}$ and the candidate cluster is $C = \mc{C}[X]$, as $n \to \infty$ the sample normalized cut $\Phi_{n,r}(\mc{C}[X])$ and conductance $\Psi_{n,r}(\mc{C}[X])$ each converge to their population-level analogues, but $\pi_{\min}(G_{n,r}[\mc{C}[X]]) \asymp 1/n$.\footnote{For sequences $(a_n)$ and $(b_n)$, we say $a_n \asymp b_n$ if there exists a constant $c \geq 1$ such that $a_n/c \leq b_n \leq c a_n$ for all $n \in \mbb{N}$.} Therefore the right hand side of~\eqref{eqn:zhu_ub2} diverges at a $\log n$ rate, which turns~\eqref{eqn:zhu_ub2} into a vacuous upper bound whenever the number of samples is sufficiently large.
+
+To address this, in Proposition~\ref{prop:pointwise_mixing_time} we improve the upper bound on the mixing time in~\eqref{eqn:mixing_time_cheeger}.
 Specifically, in~\eqref{eqn:pointwise_mixing_time} the ``start penalty'' of $\log(1/\pi_{\min}(G))$ is replaced by $\log(1/s(G))$, where $s(G)$ is the graph local spread, defined as
@@
 	\label{eqn:pointwise_mixing_time}
-	\tau_{\infty}(G) \leq \frac{13}{\ln(2)} \biggl(\frac{\ln\bigl(8/s(G)\bigr)}{\Psi(G)}\biggr)^2
+	\tau_{\infty}(G) \leq \frac{17}{\ln(2)} \biggl(\frac{\ln\bigl(32/s(G)\bigr)}{\Psi(G)}\biggr)^2.
 	\end{equation}
 \end{proposition}
-While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (as long as the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful when $G$ is a geometric graph.
-In the case where $G = G_{n,r}\bigl[\mc{C}[X]\bigr]$ for a fixed radius $r$, the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp n$, and therefore $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr) \asymp 1$.
-We give a precise upper bound on $s\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
+
+While Proposition~\ref{prop:pointwise_mixing_time} can be applied to \emph{any} graph $G$ (provided that the ratio of maximum degree to squared minimum degree is at most $1/16$), it is particularly useful for geometric graphs: when $G = G_{n,r}[\mc{C}[X]]$ for a fixed radius $r > 0$, we have $d_{\min}(G_{n,r}[\mc{C}[X]]) \asymp n$, and thus $s(G_{n,r}[\mc{C}[X]]) \asymp 1$.
+We give a precise upper bound on $s(G_{n,r}[\mc{C}[X]])$ in Proposition~\ref{prop:sample_to_population_1}, which does not grow with $n$, and in combination with Proposition~\ref{prop:pointwise_mixing_time} this allows us to remove the unwanted $\log n$ factor from the upper bound in~\eqref{eqn:zhu_ub2}.
 
@@
 The local spread $s(G)$ simply delineates small sets $R$ from larger sets $S$.
-Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a substantially more careful analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
-
-\subsection{Sample-to-population results}
+Of course, the proof of Proposition~\ref{prop:pointwise_mixing_time} requires a much more intricate analysis, and---as with the proofs of all results in this paper---it is deferred to the appendix.
+
+\subsection{Sample-to-Population Results}
 \label{subsec:sample_to_population}
 In Propositions~\ref{prop:sample_to_population_1} and~\ref{prop:sample_to_population_2}, we establish high probability bounds on the sample normalized cut, conductance, and local spread in terms of their population-level analogues.
-To establish these bounds, we impose the following regularity conditions on $\wt{\Pbb}$ and $\mc{C}$.
+To establish these bounds, we impose the following regularity conditions on \smash{$\wt{\Pbb}$} and $\mc{C}$.
 \begin{enumerate}[label=(A\arabic*)]
@@
 	\label{asmp:bounded_density} 
-	The distribution $\wt{\Pbb}$ has a density $\wt{f}: \mc{C} \to (0,\infty)$ with respect to Lebesgue measure. There exist $0 < f_{\min} \leq 1 \leq f_{\max} < \infty$ for which
+	The distribution \smash{$\wt{\Pbb}$} has a density \smash{$\wt{f}: \mc{C} \to (0,\infty)$} with respect to Lebesgue measure. There exist $0 < f_{\min} \leq f_{\max} < \infty$ for which
 	\begin{equation*}
-	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}
+	(\forall x \in \mc{C})~~ f_{\min} \leq \wt{f}(x) \leq f_{\max}.
 	\end{equation*}
+	For convenience, we will assume $f_{\min} \leq 1$ and $f_{\max} \geq 1$.
 	\item 
 	\label{asmp:domain} 
-	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set. If $d \geq 2$ then it has a Lipschitz boundary. 
+	The candidate cluster $\mc{C} \subseteq \Rd$ is a bounded, connected, open set, and for $d \geq 2$, it has a Lipschitz boundary $\partial \mc{C}$, meaning it is locally the graph of a Lipschitz function (e.g., see Definition 9.57 of~\cite{leoni2017}).
 \end{enumerate}
+
 In what follows, we use $b_1,b_2,\ldots$ and $B_1,B_2,\ldots$ to refer to positive constants that may depend on $\Pbb$, $\mc{C}$, and $r$, but do not depend on $n$ or $\delta$.
 We explicitly keep track of all constants in our proofs.
+
 \begin{proposition}
 	\label{prop:sample_to_population_1}
-	Fix $\delta \in (0,1/3)$. Suppose $\mc{C}$ and $\wt{\Pbb}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
+	Fix $\delta \in (0,1/3)$. Suppose \smash{$\wt{\Pbb}$} and $\mc{C}$ satisfy~\ref{asmp:bounded_density} and~\ref{asmp:domain}. Then each of the following statements hold.
 	\begin{itemize}
@@
 
-A word on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$ and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
-To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}\bigl(G_{n,r}\bigl[\mc{C}[X]\bigr]\bigr)$, but otherwise the proof is similarly straightforward.
+A note on the proof techniques: the upper bound in~\eqref{eqn:sample_to_population_normalized_cut} follows by applying Bernstein's inequality to control the deviations of $\cut_{n,r}(\mc{C}[X])$, $\vol_{n,r}(\mc{C}[X])$, and $\vol_{n,r}(\mc{C}^c[X])$ around their expectations (noting that each of these is an order-$2$ U-statistic).
+To prove the lower bound~\eqref{eqn:sample_to_population_local_spread}, we require a union bound to control the minimum degree $d_{\min}(G_{n,r}[\mc{C}[X]])$, but otherwise the proof is similarly straightforward.
+
 On the other hand, the proof of~\eqref{eqn:sample_to_population_conductance} is considerably more complicated.
-Our proof relies on the recent results of \citep{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\mathbb{P}_n$ and $\mathbb{P}$.
-For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citep{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
-
-\subsection{Cluster recovery}
+Our proof relies on the recent results of \citet{garciatrillos16b}, who upper bound the  $\Leb^{\infty}$-optimal transport distance between the empirical measure $\Pbb_n$ and $\Pbb$.
+For further details, we refer to Appendix~\ref{subsec:sample_to_population_conductance}, where we prove Proposition~\ref{prop:sample_to_population_2}, as well as~\citet{garciatrillos16}, who establish the asymptotic convergence of the sample conductance as $n \to \infty$ and $r \to 0$.
+
+\subsection{Cluster Recovery}
 \label{subsec:cluster_recovery}
@@
 \begin{definition}
-	If the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
+	When the input parameters to Algorithm \ref{alg:ppr} satisfy \eqref{eqn:initialization} for some $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$, we say the algorithm is $\delta$-\emph{well-initialized} with respect to $\mc{C}$.
 \end{definition}
 
-Of course, in practice it is not feasible to set tuning parameters based on the 
-underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$. Typically, one runs PPR over some range of
-tuning parameter values and selects the cluster which has the smallest
-normalized cut.
+Of course, in practice it is not feasible to set tuning parameters based on the underlying (unknown) distribution $\Pbb$ and candidate cluster $\mc{C}$.
+Typically, one runs PPR over some range of tuning parameter values and selects the cluster which has the smallest normalized cut.
 
 By combining Lemma~\ref{lem:zhu} and Propositions~\ref{prop:pointwise_mixing_time}-\ref{prop:sample_to_population_2}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}[X])$ that depends solely on the distribution $\Pbb$ and candidate cluster $\mc{C}$.
-To ease presentation, we introduce the \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
+To ease presentation, we introduce a \emph{condition number}, defined for a given $\mc{C} \subseteq \Rd$ and $\delta \in (0,1/4)$ as
 \begin{equation}
@@
 	\end{equation} 
-	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume, $\vol_{n,r}(\mc{C}[X]^g) \geq \vol_{n,r}(\mc{C}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+	the following statement holds with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$: there exists a set $\mc{C}[X]^g \subseteq \mc{C}[X]$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X]),
+	$$ 
+	such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}[X]$, and run with any seed node $v \in \mc{C}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
 	\begin{equation}
@@
 This is intuitive: PPR is a local rather than global algorithm, and as such the analysis requires only local rather than global conditions.
-Second,~\eqref{eqn:schiebinger} depends on $\sqrt{\Phi_{\Pbb,r}(\mc{C})}$ rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citep{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
+Second,~\eqref{eqn:schiebinger} depends on \smash{$\sqrt{\Phi_{\Pbb,r}(\mc{C})}$} rather than $\Phi_{\Pbb,r}(\mc{C})$, and since $\Phi_{\Pbb,r}(\mc{C}) \leq 1$ this results in a weaker bound.~\citet{schiebinger2015} provide experiments suggesting that the linear, rather than square-root, dependence is correct, and we theoretically confirm this in the local clustering setup.
 Of course, on the other hand~\eqref{eqn:volume_ssd_ub} depends on $\log^2(1/s_{\Pbb,r}(\mc{C}))$, which is due to the locally-biased nature of the PPR algorithm, and does not appear in~\eqref{eqn:schiebinger}.
 
-	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$, the 
+	\item Although Theorem~\ref{thm:volume_ssd_ub} is stated with respect to the exact PPR vector $p_v$, for a sufficiently small choice of $\varepsilon$ the 
 	application of \eqref{eqn:appr_error} within the proof of Theorem
@@
 
-\section{Recovery of a density cluster with PPR}
+\section{Recovery of a Density Cluster with PPR}
 \label{sec:ppr_density_cluster}
@@
 
-\subsection{Recovery of well-conditioned density clusters}
+\subsection{Recovery of Well-Conditioned Density Clusters}
 \label{subsec:recovery_well-conditioned_density_clusters}
@@
 
-In summary, our goal is to obtain upper bounds on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$, for some fixed $\lambda$ and $\sigma > 0$.
-We have already derived upper bounds on the symmetric set difference of $\wh{C}$ and a generic cluster $\mc{C}$ that depend on some population-level functionals $\mc{C}$.
+In summary, our goal is to obtain upper bounds on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}, for some fixed $\lambda$ and $\sigma > 0$.
+We have already derived upper bounds on the symmetric set difference of \smash{$\wh{C}$} and a generic cluster $\mc{C}$ that depend on some population-level functionals of $\mc{C}$.
 What remains is to analyze these population-level functionals in the specific case where the candidate cluster is $\mc{C}_{\lambda,\sigma}$.
@@
 	\emph{Lipschitz embedding:}
-	There exists a differentiable function $g: \Reals^d \to \Reals^d$, $\rho \in (0,\infty)$ and $L \in [1,\infty)$ such that
+	There exists a differentiable function $g: \Rd \to \Rd$, $\rho \in (0,\infty)$ and $M \in [1,\infty)$ such that
 	\begin{enumerate}
-		\item we have $\mc{C}_{\lambda,\sigma} = g(\mathcal{K})$, for a convex set $\mathcal{K}
-		\subseteq \Rd$ with $\mathrm{diam}(\mathcal{K}) = \sup_{x,y \in
-			\mathcal{K}}\|x - y\| \leq \rho < \infty$;
-		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is
-		the Jacobian of $g$ evaluated at $x;$ and 
-		\item for some $L \geq 1$,   
-		$$
-		\|g(x) - g(y)\| \leq L \|x - y\| ~
-		\text{for all $x,y \in \mathcal{K}$}. 
+		\item $\mc{C}_{\lambda,\sigma} = g(\mc{K})$, for a convex set $\mc{K} \subseteq \Rd$ with $\mathrm{diam}(\mc{K}) = \sup_{x,y \in \mc{K}}\|x - y\| \leq \rho < \infty$;
+		\item $\det(\nabla g (x)) = 1$ for all $x \in \mc{K}$, where $\nabla g(x)$ is the Jacobian of $g$ evaluated at $x;$ and 
+		\item for some $M \geq 1$,   
+		$$
+		\|g(x) - g(y)\| \leq M \|x - y\| ~	\text{for all $x,y \in \mc{K}$}. 
 		$$
@@
 
-\paragraph{Normalized cut, conductance, and local spread of a density cluster.} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population-level local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
+\subsubsection{Normalized Cut, Conductance, and Local Spread of a Density Cluster} In Lemma~\ref{lem:density_cluster_local_spread}, Proposition~\ref{prop:density_cluster_normalized_cut}, and Proposition~\ref{prop:density_cluster_conductance}, we give bounds on the population local spread, normalized cut, and conductance of $\mc{C}_{\lambda,\sigma}$.
 These bounds depend on the various geometric parameters just introduced.
@@
 	\label{prop:density_cluster_conductance}
-	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $L$. Then,
+	Assume $\mc{C}_{\lambda,\sigma}$ satisfies Assumptions~\ref{asmp:lambda_bounded_density} and~\ref{asmp:embedding} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \rho$ and $M$. Then,
 	\begin{equation}
 	\label{eqn:density_cluster_conductance}
-	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho L}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
+	\Psi_{\Pbb,r}(\mc{C}_{\lambda,\sigma}) \geq \Bigl(1 - \frac{r}{4\rho M}\Bigr) \cdot \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho M \sqrt{d + 2}} \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}.
 	\end{equation}
 \end{proposition}
-Some remarks are in order:
+
+Some remarks are in order.
 \begin{itemize}
@@
 	\item Proposition~\ref{prop:density_cluster_conductance} is proved in a completely different way.
-The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g.
-\cite{lovasz1990} or \cite{dyer1991}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $L$
+The proof relies heavily on bounds on the isoperimetric ratio of convex sets (as derived by e.g., \cite{lovasz1990} or \cite{dyer1991b}), and thus the embedding assumption \ref{asmp:embedding} and Lipschitz parameter $M$
 	play an important role in proving the upper bound in Proposition~\ref{prop:density_cluster_conductance}. 
-	\item There is some interdependence between $L$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
+	\item There is some interdependence between $M$ and $\sigma,\rho$, which might lead one to hope that \ref{asmp:embedding} is
 	non-essential. However, it is not possible to eliminate condition \ref{asmp:embedding} without incurring an additional factor of at least
@@
 	instance, when $\mc{C}_{\lambda,\sigma}$ is a dumbbell-like set consisting of two balls of diameter $\rho$ linked by a cylinder of radius $\sigma$.
-In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $L$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
+In contrast,~\eqref{eqn:density_cluster_conductance} depends polynomially on $d$, and many reasonably shaped sets---such as star-shaped sets as well as half-moon shapes of the type we consider in Section \ref{sec:experiments}---satisfy \ref{asmp:embedding} for reasonably small values of $M$ \citep{abbasi-yadkori2016a, abbasi-yadkori2016}.
 \end{itemize}
 
-\noindent Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on $\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$.
+Applying these results along with Theorem~\ref{thm:volume_ssd_ub}, we obtain an upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])$}.
 In what follows, $C_{1,\delta},C_{2,\delta},\ldots$ are constants which may depend on $\delta$, but not on $n$, $\Pbb$ or $\mc{C}_{\lambda,\sigma}$, and which we keep track of in our proofs.
+
 \begin{theorem}
@@
 	Let $C_{\lambda} \subseteq \Rd$ and $\delta \in (0,1/4)$.
-Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $L$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
-Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume, $\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])/2$, such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster $\wh{C}$ satisfies
+Suppose that $C_{\lambda,\sigma}$ satisfies~\ref{asmp:domain}-\ref{asmp:bounded_volume} for some $\lambda_{\sigma}, \Lambda_{\sigma}, \theta, \gamma, \rho$ and $M$, that $0 < r \leq \sigma/4d$, and that the sample size $n$ satisfies the same conditions as in Theorem~\ref{thm:volume_ssd_ub}.
+Then with probability at least $1 - B_2/n - 4\exp\{-b_1\delta^2n\} - (2n + 2)\exp\{-b_2\delta^2n\} - (n + 1)\exp\{-b_3n\}$, the following statement holds: there exists a set $\mc{C}_{\lambda,\sigma}[X]^g \subseteq \mc{C}_{\lambda,\sigma}[X]$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]^g) \geq \frac{1}{2} \vol_{n,r}(\mc{C}_{\lambda,\sigma}[X]).
+	$$ 
+	such that if Algorithm~\ref{alg:ppr} is $\delta$-well-initialized with respect to $\mc{C}_{\lambda,\sigma}$, and run with any seed node $v \in \mc{C}_{\lambda,\sigma}[X]^g$, then the PPR estimated cluster \smash{$\wh{C}$} satisfies
 	\begin{equation}
 	\label{eqn:density_cluster_volume_ssd_ub}
-	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{L^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} L\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
+	\frac{\Delta(\wh{C};\mc{C}_{\lambda,\sigma}[X])}{\vol_{n,r}(\mc{C}[X])} \leq C_{1,\delta} \cdot d^3(d + 2) \cdot \frac{M^2\rho^2}{\sigma r} \cdot \frac{\Lambda_{\sigma}^2 \lambda (\lambda - \theta \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}^4} \cdot \log^2\biggl(C_{2,\delta}^{1/d} \frac{\Lambda_{\sigma}^{2/d} M\rho}{\lambda_{\sigma}^{2/d}2r}\biggr)
 	\end{equation}
 \end{theorem}
-As we have previously summarized, Theorem~\ref{thm:density_cluster_volume_ssd_ub} shows the separate roles played by geometry and density in the ability of PPR to recover a density cluster.
-Now, we make some other remarks:
+
+Several further remarks are as follows.
 \begin{itemize}
 	\item Observe that while the diameter $\rho$ is absent from our upper bound on normalized cut in Proposition \ref{prop:density_cluster_normalized_cut}, it enters the ultimate bound in Theorem~\ref{thm:density_cluster_volume_ssd_ub} through the conductance.
-This reflects
-	(what may be regarded as) established wisdom regarding spectral partitioning
-	algorithms more generally \citep{guattery1995, hein2010}, but newly applied
-	to the density clustering setting: if the diameter $\rho$ is large, then PPR
-	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
+This reflects (what may be regarded as) established wisdom regarding spectral partitioning algorithms more generally \citep{guattery1995, hein2010}, but newly applied to the density clustering setting: if the diameter $\rho$ is large, then PPR	may fail to recover $\mc{C}_{\lambda,\sigma}[X]$ even when $\mc{C}_{\lambda}$ is sufficiently well-conditioned to ensure that $\mc{C}_{\lambda,\sigma}[X]$ has a small normalized cut in $G_{n,r}$.
 This will be supported by simulations in Section~\ref{subsec:empirical_behavior_ppr}.
@@
 However, the key ingredient in such procedures is the explicitly density-dependent part of the algorithm, and spectral clustering functions as more of a post-processing step.
-These methods are thus very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
-	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population-level normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
+These methods are as such very different in spirit to PPR, which is a bona fide (local) spectral clustering algorithm.
+	\item As mentioned in the discussion after Theorem~\ref{thm:volume_ssd_ub}, the population normalized cut and conductance also play a leading role in the analysis of global spectral clustering algorithms.
 It therefore seems likely that similar bounds to~\eqref{eqn:density_cluster_volume_ssd_ub} would apply to the output of global spectral clustering methods as well, but formalizing this is outside the scope of our work.
-	\item The symmetric set difference does not measure whether \smash{$\wh{C}$}
-	can (perfectly) distinguish any two distinct clusters \smash{$\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mathbb{C}_f(\lambda)$}.
+	\item The symmetric set difference does not measure whether \smash{$\wh{C}$} can (perfectly) distinguish any two distinct clusters $\mc{C}_{\lambda},\mc{C}_{\lambda}' \in \mbb{C}_f(\lambda)$.
 In Appendix~\ref{apdx:appr_misclassification_error}, we show that the PPR estimate $\wh{C}$ can in fact distinguish two distinct clusters $\mc{C}_{\lambda}$ and $\mc{C}_{\lambda}'$, but the result holds only under relatively restrictive conditions.
@@
 
-\section{Negative result}
+\section{Negative Result}
 \label{sec:lower_bound}
-We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density
-cluster. Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in
-$\Reals^2$,    
+We now exhibit a hard case for density clustering using PPR, that is, a distribution $\Pbb$ for which PPR is unlikely to recover a density cluster.
+Let \smash{$\mc{C}^{(0)}, \mc{C}^{(1)}, \mc{C}^{(2)}$} be rectangles in $\Reals^2$,
 $$
@@
 \biggl[-\frac{\rho}{2}, \frac{\rho}{2}\biggr], \quad 
-\mc{C}^{(1)} = \mc{C}^{(0)} - \set{(\sigma,0)}, \quad
-\mc{C}^{(2)} = \mc{C}^{(0)} + \set{(\sigma,0)},
-$$
-where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over
-\smash{$\mathcal{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
+\mc{C}^{(1)} = \mc{C}^{(0)} - (\sigma,0), \quad
+\mc{C}^{(2)} = \mc{C}^{(0)} + (\sigma,0),
+$$
+where $0 < \sigma < \rho$, and let $\Pbb$ be the mixture distribution over \smash{$\mc{X} = \mc{C}^{(0)} \cup \mc{C}^{(1)} \cup \mc{C}^{(2)}$} given by   
 $$
@@
 	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_2}
-	\caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
+	\caption{\small The density $f$ in \eqref{eqn:lb_density}, for
 		$\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
@@
 
-\subsection{Lower bound on symmetric set difference}
-As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is
-reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is 
-sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster 
-estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}. Let
+\subsection{Lower Bound on Symmetric Set Difference}
+As the following theorem demonstrates, even when Algorithm~\ref{alg:ppr} is reasonably initialized, if the density cluster \smash{$\mc{C}^{(1)}$} is sufficiently geometrically ill-conditioned (in words, tall and thin) the cluster estimator $\wh{C}$ will fail to recover \smash{$\mc{C}^{(1)}$}.
+Let
 \begin{equation}
 \label{eqn:lower_set}
-\mathcal{L} = \set{(x_1,x_2) \in \mathcal{X}: x_2 < 0}.
+\mc{L} = \set{(x_1,x_2) \in \mc{X}: x_2 < 0}.
 \end{equation}
@@
 	\label{eqn:ppr_lb_condition}
-	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\textrm{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
-	\end{equation} 
-	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot   
-	\Phi_{n,r}(\mathcal{L}[X])$, and $(L,U) = (0,1)$.
-Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume, \smash{$\vol_{n,r}(\mc{C}[X]^g \cap
-		\mc{C}^{(1)}[X]) \geq \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r})/8$}, such
-	that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
+	\max\biggl\{ B_{1,\delta} \cdot \frac{r}{\rho}, B_{2,\delta} \cdot \frac{1}{n} \biggr\} < \frac{1}{18}~~\text{and}~~n \geq 8 \frac{(1 + \delta)}{(1 - \delta)},
+	\end{equation} 
+	and that Algorithm~\ref{alg:ppr} is initialized using inputs $\alpha = 36 \cdot \Phi_{n,r}(\mc{L}[X])$, and $(L,U) = (0,1)$.
+Then the following statement holds with probability at least $1 - (B_4 + 2n + 10)\exp\{-n\delta^2 b_4\}$: there exists a set $\mc{C}[X]^g$ of large volume,
+	$$
+	\vol_{n,r}(\mc{C}[X]^g \cap \mc{C}^{(1)}[X]) \geq \frac{1}{8} \vol_{n,r}(\mc{C}^{(1)}[X];G_{n,r}),
+	$$
+	such that for any seed node $v \in \mc{C}[X]^g$, the PPR estimated cluster
 	\smash{$\wh{C}$} satisfies    
@@
 	\label{eqn:ppr_lb}
-	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle
-	\mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot 
-	\frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}
-		{\epsilon^2 r^2}\right) \frac{\sigma}{r}},   
+	\frac{\sigma \rho}{r^2 n^2} \cdot \vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X]) \geq \frac{1 - \delta}{2} -  C_{3,\delta} \cdot \frac{\sqrt{\sigma/\rho}}{\epsilon^2} \cdot \sqrt{ \log\left(C_{4,\delta} \cdot \frac{\rho \sigma}{\epsilon^2 r^2}\right) \frac{\sigma}{r}},
 	\end{equation} 
 \end{theorem}
-We make a couple of remarks:
+
+We make a couple of remarks.
 \begin{itemize}
@@
 	\item Although we state our lower bound with respect to PPR run on a neighborhood graph, the conclusion is likely to hold for a much broader class of spectral clustering algorithms.
-In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mathcal{L}$.
+In the proof of Theorem~\ref{thm:ppr_lb}, we rely heavily on the fact that when $\epsilon^2$ is sufficiently greater than $\sigma/\rho$, the normalized cut of $\mc{C}^{(1)}$ will be much larger than that of $\mc{L}$.
 In this case, not merely PPR but any algorithm that approximates the minimum normalized cut is unlikely to recover $\mc{C}^{(1)}$.
-In particular, local spectral clustering
-	algorithms based on truncated random walks \citep{spielman2013}, global spectral
-	clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings
-	\citep{hein2010} all have provable upper bounds on the normalized cut of cluster
-	they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
+In particular, local spectral clustering methods that are based on truncated random walks \citep{spielman2013}, global spectral clustering algorithms \citep{shi00}, and $p$-Laplacian based spectral embeddings \citep{hein2010} all have provable upper bounds on the normalized cut of cluster they output, and thus we expect that they would all fail to estimate $\mc{C}^{(1)}$.
 \end{itemize}
 
-\subsection{Comparison between upper and lower bounds}
+\subsection{Comparison Between Upper and Lower Bounds}
 \label{subsec:comparison_upper_lower_bounds}
-
 To better digest the implications of Theorem~\ref{thm:ppr_lb}, we translate the
@@
 \begin{enumerate}[label=(A\arabic*)]
-	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in
-	\mc{C}^{(1)}$.  
-	\item The density $f(x) = \frac{\epsilon}{\rho\sigma}$ for all $x$ such
-	that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
-	$$
-	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  = \left\{\frac{1 - \epsilon}{2} -
-	\epsilon \right\} \frac{1}{\rho \sigma},
+	\setcounter{enumi}{6}
+	\item The density $f(x) = \frac{1 - \epsilon}{2 \rho \sigma}$ for all $x \in	\mc{C}^{(1)}$.  
+	\item The density $f(x) \leq \frac{\epsilon}{\rho\sigma}$ for all $x \in \Reals^2$ such that $0 < \dist(x,\mc{C}^{(1)}) \leq \sigma$. Therefore for all such $x$, 
+	$$
+	\inf_{x' \in \mc{C}^{(1)}} f(x') - f(x)  \geq \left\{\frac{1 - \epsilon}{2} - \epsilon \right\} \frac{1}{\rho \sigma},
 	$$
@@
 	\item The set $\mc{C}^{(1)}$ is itself convex, and has diameter $\sqrt{\rho^2 + \sigma^2}$.
-	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) =
-		\vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore
-	\smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Reals^d)$}.   
+	\item By symmetry, \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) = \vol_{\Pbb,r}(\mc{C}^{(2)})$}, and therefore \smash{$\vol_{\Pbb,r}(\mc{C}^{(1)}) \leq \frac{1}{2}\vol_{\Pbb,r}(\Rd)$}.   
 \end{enumerate}
 
-If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}. This implies that 
-there exists a set $\mc{C}^{(1)}[X] \subseteq \mc{C}^{(1)}$ with
-\smash{$\vol_{n,r}(\mc{C}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}[X])$} such
-that for any seed node $v \in \mc{C}^{(1)}[X]$, and for large enough $n$, the
-PPR estimated cluster $\wh{C}$ satisfies with high probability
+If the user-specified parameters are initialized according to~\eqref{eqn:initialization}, we may apply Theorem~\ref{thm:density_cluster_volume_ssd_ub}.
+This implies that there exists a set $\mc{C}^{(1)}[X]^g \subseteq \mc{C}^{(1)}[X]$ with \smash{$\vol_{n,r}(\mc{C}^{(1)}[X]^g) \geq \frac{1}{2}\vol_{n,r}(\mc{C}^{(1)}[X])$} such that for any seed node $v \in \mc{C}^{(1)}[X]^g$, and for large enough $n$, the PPR estimated cluster \smash{$\wh{C}$} satisfies with high probability
 \begin{equation*}
-\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 32 C_{1,\delta} \cdot \frac{\rho^2 + \sigma^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
+\frac{\vol_{n,r}(\wh{C} \vartriangle \mc{C}^{(1)}[X])}{\vol_{n,r}(\mc{C}^{(1)}[X])} \leq 64 C_{1,\delta} \cdot \frac{\rho^2 + \sigma^2}{\sigma r} \cdot \frac{\epsilon}{1 - \epsilon} \cdot \log^2\biggl(\sqrt{C_{2,\delta}} \frac{\rho}{2r}\biggr)
 \end{equation*}
-To facilitate comparisons between our upper
-and lower bounds set $r = \sigma/8$.  Then
-the following statements each hold with high probability. 
+To facilitate comparisons between our upper and lower bounds set $r = \sigma/8$.  Then the following statements each hold with high probability. 
 \begin{itemize}
@@
 	\begin{equation*}
-	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{256 C_{1,\delta}} \frac{\sigma^2}{(\rho^2 + \sigma^2) \log^2(\rho/\sigma \sqrt{C_{2,\delta}})},
+	\frac{\epsilon}{1 - \epsilon} \leq \frac{a}{512 C_{1,\delta}} \frac{\sigma^2}{(\rho^2 + \sigma^2) \log^2(\rho/\sigma \sqrt{C_{2,\delta}})},
 	\end{equation*}
@@
 	\end{equation*}
-	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{8}
-		\vol_{n,r}(\mc{C}^{(1)}[X])$}. 
+	then \smash{$\Delta(\wh{C}, \mc{C}^{(1)}[X]) \geq \frac{1}{20} \vol_{n,r}(\mc{C}^{(1)}[X])$}. 
 \end{itemize}
-Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even when reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
-Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific
-	(albeit reasonable) ranges and choices of input parameters, which in some
-	instances differ between the upper and lower bounds. We suspect that our lower
-	bound continues to hold even when choosing input parameters as dictated by our
-	upper bound, but do not pursue the details.}
-
-Of course, it is not hard to show that in the example under consideration, classical
-plug-in density cluster estimators can consistently recover the
-$\sigma$-expansion $\mc{C}_{\lambda,\sigma}$ of a density cluster $\mc{C}_{\lambda}$, even if $\epsilon$ is
-large compared to $\sigma/\rho$. That PPR has trouble recovering density
-clusters here (where standard plug-in approaches do not) is not meant to
-be a knock on PPR. Rather, it simply reflects that while classical density
-clustering approaches are specifically designed to identify high-density regions
-regardless of their geometry, PPR relies on geometry as well as density when
-forming the output cluster.
+Ignoring constants and log factors, we can summarize the above conclusions as follows: if $\epsilon$ is much less than $(\sigma/\rho)^2$, then PPR will approximately recover the density cluster $\mc{C}^{(1)}$, whereas if $\epsilon$ is much greater than $(\sigma/\rho)^{1/4}$ then PPR will fail to recover $\mc{C}^{(1)}$, even if it is reasonably initialized with a seed node $v \in \mc{C}^{(1)}$.
+Jointly, these upper and lower bounds give a relatively precise characterization of what it means for a density cluster to be well- or poorly-conditioned for recovery using PPR.\footnote{It is worth pointing out that the above conclusions are reliant on specific (albeit reasonable) ranges and choices of input parameters, which in some instances differ between the upper and lower bounds.
+We suspect that our lower bound continues to hold even when choosing input parameters as dictated by our upper bound, but do not pursue the details.}
+
+Of course, it is not hard to show that in the example under consideration, classical plug-in density cluster estimators can consistently recover $\mc{C}^{(1)}$, even if $\epsilon$ is large compared to $\sigma/\rho$.
+That PPR has trouble recovering density clusters here (where standard plug-in approaches do not) is not meant to be a knock on PPR.
+Rather, it simply reflects that while classical density clustering approaches are specifically designed to identify high-density regions regardless of their geometry, PPR relies on geometry as well as density when forming the output cluster.
 
@@
 
-\subsection{Validating theoretical bounds}
-We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e.
-the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
+\subsection{Validating Theoretical Bounds}
+We investigate the tightness of Lemma~\ref{lem:density_cluster_local_spread} and Propositions~\ref{prop:density_cluster_normalized_cut} and \ref{prop:density_cluster_conductance}--- i.e., the bounds on population functionals required for the eventual density cluster recovery result in Theorem~\ref{thm:density_cluster_volume_ssd_ub}---via simulation.
 Figure \ref{fig:bounds} compares our bounds on normalized cut, conductance, and local spread of a density cluster with the actual empirically-computed quantities, when samples are drawn from a mixture of uniform distributions over rectangular clusters.
@@
 The one exception to this is the dependence of local spread on the width $\sigma$; this theoretical deficiency stems from a loose bound on the volume of sets with large aspect ratio (meaning $\rho/\sigma$ is much greater than $1$), but in any case the local spread contributes only $\log$ factors to the ultimate bound on cluster recovery.
-On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on $\Delta(\wh{C},\mc{C}_{\sigma}[X])/\vol_{n,r}(\mc{C}_{\sigma}[X])$, which as a result is loose by several orders of magnitude.
+On the other hand, the looseness in each of these bounds will propagate to our eventual upper bound on \smash{$\Delta(\wh{C},\mc{C}_{\lambda,\sigma}[X])/\vol_{n,r}(\mc{C}_{\lambda,\sigma}[X])$}, which as a result is loose by several orders of magnitude.
 
@@
 	\includegraphics[width=0.24\textwidth]{plots/experiment_1/density_ratio/local_spread.pdf}
-	\caption{\it \small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
+	\caption{\small Empirical normalized cut, conductance, and local spread (in \textcolor{red}{red}), versus their theoretical bounds (in \textcolor{blue}{blue}).
 In the first row we vary the diameter $\rho$, in the second row we vary the thickness $\sigma$, and in the third row we vary the density ratio $(\lambda - \theta)/\lambda$.
@@
 
-\subsection{Empirical behavior of PPR} 
+\subsection{Empirical Behavior of PPR} 
 \label{subsec:empirical_behavior_ppr}
-In Figure \ref{fig:moons}, to drive home 
-the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR
-and the density clustering algorithm of \citet{chaudhuri2010} on
-the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered
-a prototypical success story for spectral clustering algorithms.
-We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
-The first
-column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for
-a particular threshold $\lambda$ of the density function; the second column
-shows the cluster recovered by PPR; the third column shows the global minimum
-normalized cut, computed according to the algorithm of \citet{bresson2013}; and
-the last column shows a cut of the density cluster tree estimator of
-\citet{chaudhuri2010}.  We can see the degrading ability of PPR to recover
-density clusters as the two moons become less well-separated. Of particular
-interest is the fact that PPR fails to recover one of the moons even when
-normalized cut still succeeds in doing so. Additionally, we note that the
-Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut
-fail.  This supports one of our main messages, which is that PPR recovers only
-geometrically well-conditioned density clusters.
+In Figure \ref{fig:moons}, to drive home the implications of Sections~\ref{sec:ppr_density_cluster} and~\ref{sec:lower_bound}, we compare the behavior of PPR and the density clustering algorithm of \citet{chaudhuri2010} on the well-known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms.
+We also examine the cluster which minimizes the normalized cut; as we have discussed previously, this can be seen as a middle ground between the geometric sensitivity of PPR, and the geometric insensitivity of density clustering.
+The first column shows the empirical density clusters $\mc{C}_{\lambda}[X]$ and $\mc{C}_{\lambda}'[X]$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by PPR; the third column shows the global minimum normalized cut, computed according to the algorithm of \citet{bresson2013}; and the last column shows a cut of the density cluster tree estimator of \citet{chaudhuri2010}.
+Each row corresponds to a different separation between the two moons.
+In the second row, we see that as the two moons become less well-separated, PPR becomes unable to recover the density clusters, but normalized cut still succeeds in doing so.
+In the third row, we see that the Chaudhuri-Dasgupta algorithm succeeds even when both PPR and normalized cut fail.
+This supports one of our main messages, which is that PPR recovers only geometrically well-conditioned density clusters.
 
@@
 	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_density_cluster}
-	\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
+	\caption{\small True density (column 1), PPR (column 2), minimum normalized
 		cut (column 3) and estimated density (column 4) clusters for 3 different 
@@
 
-Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to  
-\infty$, would be computationally attractive, as it would ensure that the graph 
-$G_{n,r}$ is sparse.
-However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in
-this regime. Although the restriction to a kernel function fixed in $n$ is
-common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017},
-recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.
-
-In another direction, it would be very useful to find reasonable conditions under which the ratio $\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$ would tend to $0$ as $n \to \infty$.
+Letting the radius of the neighborhood graph shrink, $r \to 0$ as $n \to \infty$, would be computationally attractive, as it would ensure that the graph $G_{n,r}$ is sparse.
+However, the bounds~\eqref{eqn:volume_ssd_ub} and~\eqref{eqn:density_cluster_volume_ssd_ub} will blow up as the radius $r$ goes to $0$, preventing us from making claims about the behavior of PPR in this regime.
+Although the restriction to a kernel function fixed in $n$ is common in spectral clustering theory \citep{vonluxburg2008, schiebinger2015, singer2017}, recent works~\citep{shi2015, calder2019, garciatrillos18, garciatrillos2020, yuan2020} have demonstrated that spectral methods have meaningful continuum limits when $r \to 0$ as $n \to \infty$, and given precise rates of convergence.~\cite{garciatrillos19} have applied these results to analyze global spectral clustering in the nonparametric mixture model, obtaining asymptotic upper bounds that do not depend on $r$; it seems plausible that similar bounds could be obtained for local spectral clustering with PPR, although the arguments would necessarily be quite different.
+
+In another direction, it would be very useful to find reasonable conditions under which the ratio \smash{$\Delta(\wh{C},\mc{C}[X])/\vol_{n,r}(\mc{C}[X])$} would tend to $0$ as $n \to \infty$.
 It seems likely that such a strong result would entail bounds on the $\Leb^{\infty}$-error of PPR.
-Although most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
+Though most results thus far derive bounds only on the $\Leb^1$- or $\Leb^2$-error of spectral clustering methods, some recent works~\citep{dunson2020,calder2020} have established $\Leb^{\infty}$-bounds on the error with which the eigenvectors of a graph Laplacian matrix approximate the eigenvectors of a weighted Laplace-Beltrami operator.
 It is not clear whether the techniques used in these works can be applied to PPR.
 
-\section*{Acknowledgements}
-
-SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for
-helpful and inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
+\section*{Acknowledgments}
+	SB is grateful to Peter Bickel, Martin Wainwright, and Larry Wasserman for early inspiring conversations. This work was supported in part by the NSF grant DMS-1713003.
 
 \bibliographystyle{plainnat}
-\bibliography{../local_spectral_bibliography}
+\input{ppr_clustering_neighborhood_graph.bbl}
 

### 2021-12-23 code/archive/archive.R
Add .tar file with final jmlr version.

@@ -1,0 +1,244 @@
+clusterer <- function(X, cluster_methods)
+{
+  # objects for storing output of cluster methods, such as local clusters
+  cluster_data <- vector(mode = 'list',length(cluster_methods))
+  names(cluster_data) = names(cluster_methods)
+  
+  # run each cluster method
+  for(cluster_method_name in names(cluster_methods) )
+  {
+    cluster_method <- cluster_methods[[cluster_method_name]]
+    
+    # form graph
+    graph_type <- cluster_method$graph_type
+    if(graph_type == 'kNN')
+    {
+      A <- knn_grapher(X, cluster_method)
+    } else if(graph_type == 'kernel')
+    {
+      A <- kernel_grapher(X, cluster_method)
+    }
+    
+    # calculate cluster
+    cluster_type <- cluster_method$cluster_type
+    if(cluster_type == 'PPR')
+    {
+      cluster <- ppr_cluster(A, X, cluster_method)
+    }
+    cluster_data[[cluster_method_name]] <- list(
+      cluster_method = cluster_method,
+      A = A,
+      cluster = cluster
+    )
+  }
+  return(cluster_data)
+}
+
+
+
+
+
+graphical_evaluator_example2_plot1 <- function(X, cluster_data)
+{
+  component_densities <- gaussian_mixture_densities(P)
+  f_nk <- matrix(nrow = nrow(X), ncol = length(component_densities))
+  for(i in 1:nrow(X))
+  {
+    f_nk[i,] <- sapply(component_densities,FUN = function(density){density(X[i,])})
+  }
+  density_cluster_membership <- apply(f_nk,1,FUN = function(f){which.max(f)})
+  cluster_probabilities <- P$cluster_probabilities
+  f_n <- f_nk %*% cluster_probabilities
+  
+  origin_node <- which.min(apply(X,1,FUN = function(x){sum(x^2)}))
+  density_cluster <- which(density_cluster_membership == density_cluster_membership[origin_node])
+  
+  cluster_matrix <- matrix(0,nrow = nrow(X), ncol = length(cluster_data))
+  colnames(cluster_matrix) <- names(cluster_data)
+  for(cluster_method_name in names(cluster_data))
+  {
+    cluster_results <- cluster_data[[cluster_method_name]]
+    estimated_cluster <- cluster_results$cluster
+    cluster_matrix[estimated_cluster,cluster_method_name] <- 1
+  }
+  
[…]

### 2021-12-23 code/cluster_methods.R

@@ -1,0 +1,146 @@
+local_clusterer <- function(data, adjacency_matrix, method, parameters)
+{
+  # Input: similarity (n vector)
+  #        adjacency_matrix (n x n matrix)
+  #        evaluation_configs (list)
+  #        -$metric (flag) ('ncut')
+  
+  # unpack parameters
+  method_type <- method$method_type
+  evaluation_configs <- method$evaluation_configs
+  
+  # Compute similarities
+  if(method_type %in% c('ppr', 'local_density', 'conductance', 'spectral'))
+  {
+    similarity <- similarity_scorer(method_type, adjacency_matrix, parameters, data)
+    cluster <- sweep_cut(similarity, evaluation_configs, adjacency_matrix)
+  } 
+  return(list(similarity = similarity,
+              cluster = cluster))
+}
+
+tree_clusterer <- function(data, adjacency_matrix, method, parameters)
+{
+  # Input: data (n x d matrix)
+  #        adjacency_matrix (n x n matrix)
+  #        method (list of configurations which define a method)
+  #        parameters (inputs to method)
+  #        N (number samples to augment with)
+  
+  # unpack necessary parameters
+  method_type <- method$method_type
+  
+  if(method_type == 'density')
+  {
+    cluster_tree <- density_cluster_tree(data, adjacency_matrix, parameters)$empirical_cluster_tree
+  }
+  
+}
+
+tree_to_clustering <- function(cluster_tree, parameters, P)
+{
+  # unpack necessary parameters
+  p <- length(P$cluster_probabilities)
+  
+  # cut the (density) cluster tree 
+  clustering <- cluster_tree[parameters['density_cut'],]
+  
+  # all nodes with density less than the cut should not be in a cluster
+  cluster_sizes <- sort(table(clustering), decreasing = T)
+  cluster_names <- as.numeric(names(cluster_sizes)[cluster_sizes  > 1])
+  clustering[!(clustering %in% cluster_names)] <- 0
+  
+  return(clustering)
+}
+density_cluster_tree <- function(data,adjacency_matrix, parameters)
+{
+  density_data <- density(NULL, data, 0) # TODO: make P optional input to density
+  cluster_tree_data <- cluster_tree(NULL, data, approx = F, density_data)
+  return(cluster_tree_data)
+}
+
[…]

### 2021-12-23 code/clustering_pipeline.R

@@ -1,0 +1,53 @@
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+require(gurobi)
+require(dplyr)
+julia_setup('C:/Users/alden/AppData/Local/Julia-1.1.0/bin')
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+script_names <- c('configs/clustering_config.R', 'sample.R', 'hyperparameter.R',
+                  'similarity.R','cluster_methods.R','graph.R','geometric_methods.R',
+                  'evaluate.R','plot_methods.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# Generate data
+data <- distribution_sample(P, n)
+
+# Generate similarity graph (we consider the graph as given to us a priori)
+adjacency_matrix <- grapher(data, graph_configs)
+
+# Generating clusters
+cluster_data <- vector(mode = 'list', length = length(cluster_methods))
+names(cluster_data) <- names(cluster_methods)
+
+for(cluster_method_name in names(cluster_methods))
+{
+  method <- cluster_methods[[cluster_method_name]]
+  
+  evaluation0 <- 1 # 1 should be the worst possible evaluation a cluster can receive
+  
+  # Form hyperparameters to optimize over
+  parameter_combinations <- parameter_combiner(method, data,adjacency_matrix,graph_configs)
+  
+  for(ii in 1:nrow(parameter_combinations) )
+  {
+    # Particular value of hyperparameters
+    parameters <- parameter_combinations[ii,]
+    
+    # Make a clustering
+    clustering_data <- clustering_maker(data, adjacency_matrix, method, parameters)
+  }
+}

### 2021-12-23 code/configs/config.R

@@ -1,0 +1,59 @@
+### Fundamental parameters
+
+# Salience
+sigma <- .3
+epsilon <- .8
+
+# Level set threshold
+tau <- 1 / (2 * sigma * (3 - epsilon))
+
+# Neighborhood graph radius
+r <- sigma/1.01
+
+# which cluster we will begin in
+cluster_original <- 1
+
+
+### Density function parameters
+
+distribution_type <- 'gaussian_mixture' # distribution type
+distribution_parameters <- list(
+  muC = c(0,rep(0,1)), # mean of first mixture component
+  muCpr = c(.325,rep(0,1)), # mean of second mixture component
+  SigmaC = diag(2) - 
+           c(1, rep(0, 1)) %*% t(c(1, rep(0, 1))) + 
+           c(.08, rep(0,1)) %*% t(c(.08, rep(0, 1))), # covariance matrix of first mixture component
+  SigmaCpr = diag(2) - 
+    c(1, rep(0, 1)) %*% t(c(1, rep(0, 1))) + 
+    c(.08, rep(0,1)) %*% t(c(.08, rep(0, 1))), # covariance matrix of second mixture component
+  pi = c(.5,.5) # mixture weight distribution
+)
+
+n = 2000 # sample size
+N = 6000 # number of samples needed to approximate full distribution
+
+# Page-rank parameter grid
+local_cluster_parameter_grid <- list(
+  r = seq(.03,.07, by = .005), # radius for the neighborhood graph
+  v = 'None',
+  alpha = c(.00001, .00005, .0001, .0005, .001),
+  tau = .5, # needed to find estimated density cluster, the medioid of which is used to initialize v
+  cluster_size = c('.5', '.8', '1' , '1.2', '1.5', '2'),
+  tol = 'None',
+  normalize = TRUE
+)
+
+# Density cluster parameter grid
+density_cluster_parameter_grid <- list(
+  r = seq(.03,.07, by = .005),
+  tau = .5,
+  k = c('5','10','20','40','80')
+)
+
+true_cluster_parameters <- list(
+  tau = .5
+)
+
+## simulation parameters
+n_grid <- 20
+n_sims <- 25

### 2021-12-23 code/configs/diameter_mixing_time_config.R

@@ -1,0 +1,35 @@
+# sample size
+n <- 20000
+
+# parameters
+sigma <- .1
+gamma <- 1/10
+lambda_sigma = (15/9)*sigma^gamma
+
+# range parameters
+d_range <- seq(2,3, by = 1)
+D_range <- sigma*(2^seq(3,6.5, by = .5))
+
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma = .1,
+  gamma = gamma,
+  d_range = d_range,
+  D_range = D_range,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= 2*sigma/sqrt(d) for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = model$sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 20
+)

### 2021-12-23 code/configs/diameter_normalized_cut_config.R

@@ -1,0 +1,34 @@
+# sample size
+n <- 640000
+
+# parameters
+sigma <- .1
+gamma <- .05
+lambda_sigma = (15/9)*(sigma^gamma)
+
+# range parameters
+d_range <- c(2,3)
+D_range <- sigma * 2^{seq(3,6.5,by = .5)}
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma = sigma,
+  gamma = gamma,
+  d_range = d_range,
+  D_range = D_range,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= sigma / 4d for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 100
+)

### 2021-12-23 code/configs/full_config.R

@@ -1,0 +1,118 @@
+# sample size
+n <- 800
+
+# distribution
+P <- list(distribution_class = 'two_moons',
+          d = 4,
+          centers = matrix(c(-.5,-.075,
+                             0,.075),ncol = 2, byrow = T),
+          r = .5,
+          sigma = .075,
+          cluster_probabilities = c(.5,.5),
+          theta_dist = 'uniform'
+) 
+
+# graph
+graph_configs <- list(graph_type = 'kNN',
+                      connectivity = 6)
+
+# clustering methods
+cluster_methods <- list(
+  method_D = list(
+    method_type = 'conductance',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35),
+      tol = 10^(-6),
+      c = 1,
+      f0 = 'tune_spectral'
+    )
+  ),
+  method_A = list(
+    method_type = 'ppr',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.425),
+      teleportation_parameter = list(
+        type = 'tune',
+        range = c(.001,.3,25),
+        length = 25
+      )
+    )
+  ),
+  method_B = list(
+    method_type = 'local_density',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    )
+  ),
+  method_C = list(
+    method_type = 'spectral',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    )
+  )
+)
+
+evaluation_configs <- list(metric = 'ncut')
+
+
+# cluster_methods <- list(
+#   method_A = list(
+#     graph_type = 'kernel',
+#     kernel_type = 'uniform',
+#     h = 'quantile',
+#     quantile = .2,
+#     cluster_type = 'PPR',
+#     seed_node = 'nearest_origin',
+#     teleportation_parameter = list(
+#       type = 'tune',
+#       L = .001,
+#       U = .3,
+#       length = 25),
+#     target_volume = 'tune'
+#   ),
+#   method_B = list(
+#     graph_type = 'kernel',
+#     kernel_type = 'uniform',
+#     h = 'quantile',
+#     quantile = .1,
+#     cluster_type = 'PPR',
+#     seed_node = 'nearest_origin',
+#     teleportation_parameter = list(
+#       type = 'tune',
+#       L = .001,
+#       U = .3,
+#       length = 25),
[…]

### 2021-12-23 code/configs/gamma_normalized_cut_config.R

@@ -1,0 +1,33 @@
+# sample size
+n <- 80000
+
+# parameters
+sigma <- .1
+D <- 2*sigma
+gamma_range <- .05*2^{seq(-2,3,length.out = 10)}
+lambda_sigma = (15/9)*(D^gamma_range)
+d_range <- c(2,3)
+
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma = sigma,
+  gamma_range = gamma_range,
+  d_range = d_range,
+  D = D,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= sigma / 4d for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 100
+)

### 2021-12-23 code/configs/hyperparameter_evaluation_config.R

@@ -1,0 +1,73 @@
+# sample size
+n <- 400
+
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+            d = 1,
+            cluster_probabilities = c(.2,.4,.4),
+            mu_type = 'evenly_spaced',
+            Sigma_type = 'scaled',
+            Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .2,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  ),
+  method_B = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  ),
+  method_C = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .05,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  ),
+  method_D = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .01,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+# simulation hyperparameters (?)
+n_sims <- 100

### 2021-12-23 code/configs/icml_example1_config.R

@@ -1,0 +1,17 @@
+# sample size
+n <- 5000
+
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+          d = 1,
+          cluster_probabilities = c(.5,.5),
+          mu_type = 'evenly_spaced',
+          Sigma_type = 'scaled',
+          Sigma_scale = 1/2)
+
+# density cluster parameters
+density_cluster_parameters <- list(
+  lambda_path = seq(1.5,1, length.out = 5),
+  sigma = .01,
+  r = 'sigma/4d'
+)

### 2021-12-23 code/configs/icml_example2.R

@@ -1,0 +1,14 @@
+### load each of the four graphs
+load(file = paste0(save_path, 'example2_plot1.R'))
+load(file = paste0(save_path, 'example2_plot2.R'))
+load(file = paste0(save_path, 'example2_plot3.R'))
+load(file = paste0(save_path, 'example2_plot4.R'))
+### arrange them on a panel
+
+pdf(paste0(save_path,'graphic_1.pdf'))
+grid.arrange(example2_plot1,
+             example2_plot4,
+             example2_plot2,
+             example2_plot3,
+             nrow = 2)
+dev.off()

### 2021-12-23 code/configs/icml_example2_config.R

@@ -1,0 +1,31 @@
+# sample size
+n <- 400
+
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+          d = 1,
+          cluster_probabilities = c(.5,.5),
+          mu_type = 'evenly_spaced',
+          Sigma_type = 'scaled',
+          Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+# simulation hyperparameters (?)
+n_sims <- 100

### 2021-12-23 code/configs/icml_example2_plot2_config.R

@@ -1,0 +1,31 @@
+# sample size
+n <- 400
+
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+          d = 2,
+          cluster_probabilities = c(.5,.5),
+          mu_type = 'evenly_spaced',
+          Sigma_type = 'scaled',
+          Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+# simulation hyperparameters (?)
+n_sims <- 100

### 2021-12-23 code/configs/icml_example2_plot3_config.R

@@ -1,0 +1,35 @@
+# distribution
+P_sequence <- list(distribution_class = 'gaussian_mixtures',
+          d = 2,
+          cluster_probabilities = c(.5,.5),
+          mu_type = 'evenly_spaced',
+          mu_distance_scale = seq(.5,1.5,length.out = 10),
+          Sigma_type = 'scaled',
+          Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+density_cluster_parameters <- list(
+  lambda_path = seq(1.5,1, length.out = 5),
+  sigma = .12*4,
+  r = 'sigma/4d'
+)
+
+# simulation hyperparameters (?)
+n_sims <- 5

### 2021-12-23 code/configs/icml_example2_plot4_config.R

@@ -1,0 +1,31 @@
+# sample size
+n <- 400
+
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+          d = 1,
+          cluster_probabilities = c(.2,.4,.4),
+          mu_type = 'evenly_spaced',
+          Sigma_type = 'scaled',
+          Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .15,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+# simulation hyperparameters (?)
+n_sims <- 100

### 2021-12-23 code/configs/icml_example3.R

@@ -1,0 +1,31 @@
+load(file = paste0(save_path, 'metric_evaluation_table.R'))
+metric_evaluation_table_isotropic <- metric_evaluation_table
+
+load(file = paste0(save_path, 'metric_evaluation_table_2.R'))
+metric_evaluation_table_anisotropic <- metric_evaluation_table
+
+symmetric_set_difference <- matrix(c(rowMeans(metric_evaluation_table_isotropic),
+                                     rowMeans(metric_evaluation_table_anisotropic)), ncol = 2)
+cluster_center_distance <- P_sequence$mu_distance_scale * .5
+
+plot_df = data.frame(X = cluster_center_distance, 
+                     Y_1 = symmetric_set_difference[,1],
+                     Y_2 = symmetric_set_difference[,2])
+plot_df <- melt(plot_df, id = 'X')
+example3_plot1 <- ggplot(data = plot_df, aes(x = X, y = value, colour = variable, shape = variable)) + 
+  geom_line(size = 1.2) +
+  scale_colour_manual(name = 'Mixture model', labels = c('GMM-isotropic', 'GMM-anisotropic'),
+                      values = c('orangered1', 'purple')) +
+  geom_point(size = 5) +
+  scale_shape_manual(name = 'Mixture model', labels = c('GMM-isotropic', 'GMM-anisotropic'),
+                     values = c(18, 20)) +
+  xlab('Distance between component centers') + ylab('symmetric set difference') + 
+  theme_classic() +
+  theme(legend.justification=c(1,1), legend.position=c(1,1), 
+        legend.background = element_rect(linetype = 1, size = 0.5, colour = 1),
+        axis.text.x = element_text(size = 16),
+        axis.title.x = element_text(size = 16),
+        axis.text.y = element_text(size = 16),
+        axis.title.y = element_text(size = 16),
+        legend.text = element_text(size = 16),
+        legend.title = element_text(size = 16))

### 2021-12-23 code/configs/icml_example3_plot1.R

@@ -1,0 +1,45 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example3_plot2_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+
+save_path <- paste0(code_source_path,'icml/')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+P <- P_sequence
+X <- distribution_sample(P, n)
+    
+# Cluster
+cluster_data <- clusterer(X, cluster_methods)
+
+# graphical evaluation
+graphical_evaluation <- graphical_evaluator_plot4(P_sequence, metric_evaluation_table)
+
+
+# Save
+save(plot4, file = paste0(save_path, 'plot_4.R'))
+save(metric_evaluation_table, file = paste0(save_path, 'metric_evaluation_table.R'))

### 2021-12-23 code/configs/icml_example3_plot1_config.R

@@ -1,0 +1,35 @@
+# distribution
+P <- list(distribution_class = 'gaussian_mixtures',
+                   d = 2,
+                   cluster_probabilities = c(.5,.5),
+                   mu_type = 'evenly_spaced',
+                   Sigma = matrix(c(33/32,-31/32,
+                                    -31/32,33/32),nrow = 2)/4,
+                   Sigma_type = 'None') 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+density_cluster_parameters <- list(
+  lambda_path = seq(1.5,1, length.out = 5),
+  sigma = .12*4,
+  r = 'sigma/4d'
+)
+
+# simulation hyperparameters (?)
+n_sims <- 5

### 2021-12-23 code/configs/icml_example3_plot2_config.R

@@ -1,0 +1,36 @@
+# distribution
+P_sequence <- list(distribution_class = 'gaussian_mixtures',
+                   d = 2,
+                   cluster_probabilities = c(.5,.5),
+                   mu_type = 'evenly_spaced',
+                   mu_distance_scale = seq(.5,1.5,length.out = 10),
+                   Sigma = matrix(c(9/32,-7/32,
+                                  -7/32,9/32),nrow = 2)/4,
+                   Sigma_type = 'None') 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+density_cluster_parameters <- list(
+  lambda_path = seq(1.5,1, length.out = 5),
+  sigma = .12*4,
+  r = 'sigma/4d'
+)
+
+# simulation hyperparameters (?)
+n_sims <- 5

### 2021-12-23 code/configs/icml_example3_plot3_config.R

@@ -1,0 +1,29 @@
+# distribution
+P_sequence <- list(distribution_class = 'gaussian_mixtures',
+          d = 2,
+          cluster_probabilities = c(.5,.5),
+          mu_type = 'evenly_spaced',
+          mu_distance_scale = seq(.5,1.5,length.out = 10),
+          Sigma_type = 'scaled',
+          Sigma_scale = 1) 
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    graph_type = 'kernel',
+    kernel_type = 'uniform',
+    h = 'quantile',
+    quantile = .1,
+    cluster_type = 'PPR',
+    seed_node = 'nearest_origin',
+    teleportation_parameter = list(
+      type = 'tune',
+      L = .001,
+      U = .3,
+      length = 25),
+    target_volume = 'tune'
+  )
+)
+
+# simulation hyperparameters (?)
+n_sims <- 100

### 2021-12-23 code/configs/lambdaratio_mixing_time_config.R

@@ -1,0 +1,31 @@
+# sample size
+n <- 20000
+
+# parameters
+sigma <- .1
+gamma <- 1/10
+lambda_sigma = (15/9)*sigma^gamma
+lambda_ratio <- (2^seq(0,3, length.out = 10))
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma = .1,
+  gamma = gamma,
+  d_range = seq(2,3, by = 1),
+  D = 8*sigma,
+  lambda_sigma = lambda_sigma, 
+  lambda_range = lambda_sigma * lambda_ratio
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= 2*sigma/sqrt(d) for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = model$sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 20
+)

### 2021-12-23 code/configs/mixing_time_config.R

@@ -1,0 +1,35 @@
+# sample size
+n <- 20000
+
+# parameters
+sigma <- .1
+gamma <- 1/10
+lambda_sigma = (15/9)*sigma^gamma
+
+# range parameters
+d_range <- seq(2,3, by = 1)
+D_range <- sigma*(2^seq(0,5, length.out = 10))
+
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma = .1,
+  gamma = gamma,
+  d_range = d_range,
+  D_range = D_range,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= 2*sigma/sqrt(d) for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = model$sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 20
+)

### 2021-12-23 code/configs/normalized_cut_config.R

@@ -1,0 +1,33 @@
+# sample size
+n <- 20000
+
+# parameters
+sigma <- .1
+D <- sigma * 2^5
+gamma <- .05
+lambda_sigma = (15/9)*(D^gamma)
+d_range <- c(2,3)
+
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma_range = sigma * 2^{seq(0,5,length.out = 10)},
+  gamma = .05,
+  d_range = d_range,
+  D = D,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= sigma / 4d for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = sigma / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 100
+)

### 2021-12-23 code/configs/sigma_mixing_time_config.R

@@ -1,0 +1,31 @@
+# sample size
+n <- 20000
+
+# parameters
+sigma <- .1
+D <- sigma * 2^5
+gamma <- 1/10
+lambda_sigma = (15/9)*sigma^gamma
+
+# family of distributions
+model <- list(
+  distribution_class = 'rounded_box_2_distribution',
+  sigma_range = sigma * 2^{seq(0,5,length.out = 10)},
+  gamma = gamma,
+  d_range = seq(2,3, by = 1),
+  D = D,
+  lambda_sigma = lambda_sigma, 
+  lambda = lambda_sigma * (10/9)
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= 2*sigma/sqrt(d) for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = 'k_degree',
+  l = min(model$sigma_range) / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 50
+)

### 2021-12-23 code/configs/small_config.R

@@ -1,0 +1,144 @@
+# sample size
+n <- 800
+
+# distribution
+P <- list(distribution_class = 'two_moons',
+          d = 2,
+          centers = matrix(c(-.5,0,
+                             0,0),ncol = 2, byrow = T),
+          r = .5,
+          sigma = .075,
+          cluster_probabilities = c(.5,.5),
+          theta_dist = 'uniform'
+) 
+
+# graph
+graph_configs <- list(graph_type = 'k_to_epsilon',
+                      connectivity = 2)
+
+# clustering methods
+local_cluster_methods <- list(
+  method_D = list(
+    method_type = 'conductance',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35),
+      tol = 10^(-6),
+      c = 1,
+      f0 = 'tune_spectral'
+    ),
+    evaluation_configs = list(
+      metric = 'ncut'
+    )
+  ),
+  method_A = list(
+    method_type = 'ppr',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.425),
+      teleportation_parameter = list(
+        type = 'tune',
+        range = c(.001,.3,25),
+        length = 25
+      )
+    ),
+    evaluation_configs = list(
+      metric = 'ncut'
+    )
+  ),
+  method_B = list(
+    method_type = 'local_density',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    ),
+    evaluation_configs = list(
+      metric = 'ncut'
+    )
+  ),
+  method_C = list(
+    method_type = 'spectral',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    ),
+    evaluation_configs = list(
+      metric = 'ncut'
+    )
+  )
+)
+
+cluster_tree_methods <- list(
+  method_A = list(
+    method_type = 'density',
+    hyperparameter_configs = list(
+      N = 0,
+      density_cut = list(
+        type = 'tune',
+        length = n
+      )
+    ),
+    evaluation_configs = list(
+      metric = 'oracle_density_clustering'
+    )
+  )
+)
+
+
+# cluster_methods <- list(
+#   method_A = list(
+#     graph_type = 'kernel',
+#     kernel_type = 'uniform',
+#     h = 'quantile',
+#     quantile = .2,
+#     cluster_type = 'PPR',
[…]

### 2021-12-23 code/configs/theoretical_pipeline_config.R

@@ -1,0 +1,22 @@
+# sample size
+n <- 20000
+
+# family of distributions
+model <- list(
+  distribution_class = 'theory_distribution',
+  sigma_range = seq(1/20, 1/10, length.out = 10),
+  gamma_range = seq(1/10, 1/5, length.out = 10),
+  d_range = seq(2,3, by = 1),
+  D = .1
+)
+
+# graph configs
+# connectivity should be small enough to satisfy r <= sigma / 4d for all sigma and d
+graph_configs <- list(
+  graph_type = 'epsilon',
+  connectivity = min(model$sigma_range) / (4 * sqrt(max(model$d_range)) )
+)
+
+empirical_configs <- list(
+  n_sims = 20
+)

### 2021-12-23 code/configs/two_moons_config.R

@@ -1,0 +1,123 @@
+# sample size
+n <- 800
+
+# distribution
+P <- list(distribution_class = 'two_moons',
+          d = 15,
+          centers = matrix(c(-.5,-.075,
+                             0,.075),ncol = 2, byrow = T),
+          r = .5,
+          sigma = .075,
+          cluster_probabilities = c(.5,.5)
+          ) 
+
+# graph
+graph_configs <- list(graph_type = 'kNN',
+                      connectivity = 6)
+
+# clustering methods
+cluster_methods <- list(
+  method_A = list(
+    method_type = 'ppr',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.425),
+      teleportation_parameter = list(
+        type = 'tune',
+        range = c(.001,.3,25),
+        length = 25
+      )
+    )
+  ),
+  method_B = list(
+    method_type = 'density',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    )
+  ),
+  method_C = list(
+    method_type = 'spectral',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.35)
+    )
+  ),
+  method_D = list(
+    method_type = 'appr',
+    hyperparameter_configs = list(
+      seed_node_manifold_location = c(.05, -.425),
+      teleportation_parameter = list(
+        type = 'tune',
+        range = c(.001,.3,25),
+        length = 25
+      ),
+      approximation_parameter = list(
+        type = 'tune',
+        proportion_volume = 1/16
+      )
+    )
+  )
+)
+
+evaluation_configs <- list(metric = 'ncut')
+
+
+# cluster_methods <- list(
+#   method_A = list(
+#     graph_type = 'kernel',
+#     kernel_type = 'uniform',
+#     h = 'quantile',
+#     quantile = .2,
+#     cluster_type = 'PPR',
+#     seed_node = 'nearest_origin',
+#     teleportation_parameter = list(
+#       type = 'tune',
+#       L = .001,
+#       U = .3,
+#       length = 25),
+#     target_volume = 'tune'
+#   ),
+#   method_B = list(
+#     graph_type = 'kernel',
+#     kernel_type = 'uniform',
+#     h = 'quantile',
+#     quantile = .1,
+#     cluster_type = 'PPR',
+#     seed_node = 'nearest_origin',
[…]

### 2021-12-23 code/density_cluster.R

@@ -1,0 +1,204 @@
+# returns the density cluster of minimal average distance to the origin
+density_cluster <- function(P, X, density_cluster_parameters, lambda)
+{
+  # unpack parameters
+  sigma <- density_cluster_parameters$sigma
+  r <- density_cluster_parameters$r
+  d <- P$d
+  
+  # compute density level set
+  Cbb_f <- density_level_set(P, X, lambda)
+  
+  # compute connected components of the density level set in the r-radius neighborhood graph
+  if(r == 'sigma/4d')
+  {
+    r <- sigma/(4*d)
+  }
+  D <- distance(X, X)
+  kernel_function <- kernel_function_definer('uniform', r, d)
+  A <- kernel_function(D)
+  A_level_set <- A[Cbb_f, Cbb_f]
+  density_clusters <- components(graph_from_adjacency_matrix(A_level_set))
+  
+  origin_node <- which.min(apply(as.matrix(X[Cbb_f,]),1,FUN = function(x){sum(x^2)}))
+  density_cluster <- which(density_clusters$membership == density_clusters$membership[origin_node])
+  return(Cbb_f[density_cluster])
+}
+
+density_clustering <- function(P,X,density_cluster_parameters, lambda)
+{
+  # unpack parameters
+  sigma <- density_cluster_parameters$sigma
+  r <- density_cluster_parameters$r
+  d <- P$d
+  
+  # compute density level set
+  Cbb_f <- density_level_set(P, X, lambda)
+  
+  # compute connected components of the density level set in the r-radius neighborhood graph
+  if(r == 'sigma/4d')
+  {
+    r <- sigma/(4*d)
+  }
+  D <- distance(X, X)
+  kernel_function <- kernel_function_definer('uniform', r, d)
+  A <- kernel_function(D)
+  A_level_set <- A[Cbb_f, Cbb_f]
+  density_clusters <- components(graph_from_adjacency_matrix(A_level_set))
+  return(density_clusters)
+}
+
+density_level_set <- function(P, X, lambda)
+{
+  # compute the density function for P
+  if(P$distribution_class == 'gaussian_mixtures')
+  {
+    f <- gaussian_mixture_density(P)
+  }
+  
+  # evaluate the density function over X
+  f_n <- apply(X, 1, FUN = function(x){f(x)})
+  
+  # return the indices of those points in X which have density function greater than lambda
[…]

### 2021-12-23 code/distribution_functions.R

@@ -1,0 +1,78 @@
+gaussian_mixture_sampler <- function(distribution_parameters, n)
+{
+  # unlist parameters
+  muC <- distribution_parameters$muC
+  muCpr <- distribution_parameters$muCpr
+  SigmaC <- distribution_parameters$SigmaC
+  SigmaCpr <- distribution_parameters$SigmaCpr
+  pi <- distribution_parameters$pi
+  
+  # assign number of samples to each cluster
+  N_class <- rmultinom(1,n,pi)
+  
+  z_1 <- mvrnorm(n = N_class[1], mu = muC, Sigma = SigmaC) # density of first mixture component
+  z_2 <- mvrnorm(n = N_class[2], mu = muCpr, Sigma = SigmaCpr) # density of second mixture component
+  z <- rbind(z_1, z_2) # density of the mixture
+  
+  return(z)
+}
+
+uniform_mixture_sampler <- function(sigma, epsilon, nC, nCpr)
+{
+  ### Specify parameters here
+  n_points <- 100000
+  d <- 2
+  ### 1. Sample uniformly on the cube [0,5 \sigma] x [0,1]
+  
+  z <- matrix(ncol = 2, nrow = n_points)
+  z[,1] <- runif(n_points, 0, 5 * sigma)
+  z[,2] <- runif(n_points)
+  
+  ### 2. Assign equal probability to each point.
+  ###    Take all points with x_1 \in [2 \sigma, 3 \sigma] and downweight by 1 - epsilon
+  
+  sampling_probabilities <- rep(1,nrow(z))
+  S <- (z[,1] >= 2 * sigma) & (z[,1] <= 3 * sigma)
+  sampling_probabilities[S] <- 1 - epsilon
+  
+  sigma_boundaries <- ( (z[,1] >= 1 * sigma) & (z[,1] <= 2 * sigma) ) | ( (z[,1] >= 3 * sigma) & (z[,1] <= 4 * sigma) )
+  sampling_probabilities[sigma_boundaries] <- 1 - .00001 # we need this to be some constant amount arbitrarily lower than 1
+  ### 3. sample points with replacement
+  y <- z[sample.int(nrow(z), size = nC + nCpr, replace = TRUE, prob = sampling_probabilities),]
+  
+  return(y)
+}
+
+distribution_maker <- function(distribution_type)
+{
+  if(distribution_type == 'gaussian_mixture')
+  {
[…]

### 2021-12-23 code/evaluate.R

@@ -1,0 +1,113 @@
+evaluator <- function(evaluation_configs, cluster, adjacency_matrix, data, P)
+{
+  # unpack necessary parameters
+  metric <- evaluation_configs$metric
+  
+  # compute the desired metric
+  if(metric == 'ncut')
+  {
+    evaluation_data <- list(
+      evaluation = normalized_cut(cluster,adjacency_matrix)
+    )
+  } else if(metric == 'density_clustertree')
+  {
+    evaluation_data <- density_clustertree_recovery(cluster, data, P)
+  } else if(metric == 'oracle_density_clustering')
+  {
+    evaluation_data <- oracle_density_evaluation(cluster, P)
+  }
+  
+  return(evaluation_data)
+}
+
+oracle_density_evaluation <- function(clustering, P)
+{
+  # oracle_density_evaluation should give lower (better) scores
+  # to clusterings which assign most points to the top p cluster
+  # where p is the number of mixture components in P
+  # 
+  # INPUT: clustering (n x 1 vector of cluster membership for each data points)
+  #        P (list of specifications for mixture model)
+  
+  # unpack necessary parameters
+  p <- length(P$cluster_probabilities)
+  
+  # size of pth largest cluster
+  cluster_sizes <- sort(table(clustering[clustering != 0]), decreasing = T)
+  if(length(cluster_sizes) < p)
+  {
+    pth_largest_cluster_size <- 1
+  } else{
+    pth_largest_cluster_size <- cluster_sizes[p]
+  }
+  
+  return(list(
+    evaluation = 1/pth_largest_cluster_size
+    )
+  )
+  
+}
+
+density_clustertree_recovery <- function(cluster, data, P, cluster_tree_data,
+                                         evaluation_metric = 'set_difference')
+{
+  # TODO: function definition here
+  # Output: (list)
+  #         - C_nlprime: indices of data points with density at least
+  #                      that of threshold for density cluster but not 
+  #                      part of best density cluster
+  
+  if(is.null(cluster_tree_data))
+  {
+    cluster_tree_data <- cluster_tree(P, data)
+  }
+  empirical_cluster_tree <- cluster_tree_data$empirical_cluster_tree
+  density_rank <- cluster_tree_data$density_rank
+  n_tree_cuts <- nrow(empirical_cluster_tree)
+  
+  # For each radius value, find connected components in the graph
+  evaluation0_min <- 1
+  evaluation0 <- rep(1,n_tree_cuts)
[…]

### 2021-12-23 code/explore/bound.R

@@ -1,0 +1,22 @@
+ppr_empirical_error_bound <- function(theta, seed, empirical_cluster, error_metric, G)
+{
+  alpha <- theta$alpha
+  (15 * ncut(empirical_cluster, G) / alpha  + 8  * ncut(empirical_cluster,G))
+}
+
+ppr_theoretical_error_bound <- function(theta)
+{
+  r <- theta$r
+  h <- .25*aspect_ratio*2
+  w <- .25*2
+  epsilon <- (c(rep(class_ratio,n_mixtures),1) %>% (function(p){p/sum(p)}))[n_mixtures+1]
+  
+  p_out <- epsilon / 4
+  p_in <-  (epsilon / 4 + (1 - epsilon)/(h*w))
+  ncut_predicted <- r * p_out / p_in * 2*(w + h)/(w*h)
+  
+  fiedler_predicted <- 4 * r^2/h^2 / 2
+  
+  condition_number <- ncut_predicted / fiedler_predicted
+  
+}

### 2021-12-23 code/explore/cluster.R

@@ -1,0 +1,133 @@
+make_ppr_cluster <- function(theta,seed,empirical_cluster,error_metric)
+{
+  # Rank samples according to PPR on a neighborhood graph from seed,
+  # output best sweep cut--- as measured by error_metric(sweep_cut,empirical_cluster)
+  # as cluster estimate.
+  
+  r <- theta[["r"]]
+  alpha <- theta[["alpha"]]
+  
+  ppr_cluster <- function(X){
+    # graph
+    G <- neighborhood_graph(X,r)
+    
+    # random walk matrix 
+    W <- random_walk_Laplacian(G)
+    
+    if(abs(alpha) < 1e-10){
+      components <- igraph::graph.adjacency(G) %>% igraph::components()
+      cluster_estimate <- which(components$membership == components$membership[seed])
+      attr(cluster_estimate,"preference") <- ifelse(1:n %in% cluster_estimate,1,0)
+      return(cluster_estimate)
+    }
+    
+    # compute PPR
+    source <- ifelse(1:n == seed,1,0)
+    B <- t(diag(n) - (1 - alpha)*W)
+    ppr <- solve(B, alpha*source)
+    ppr_normalized <- ifelse(is.na(ppr/degree(G)*volume(G)),source,ppr/degree(G)*volume(G))
+    
+    # estimate by thresholding
+    cluster_estimate <- best_sweep_cut(ppr_normalized,empirical_cluster,error_metric, G)
+    
+    attr(cluster_estimate,"preference") <- as.numeric(ppr_normalized)
+    return(cluster_estimate)
+  }
+}
+
+make_initialize_ppr_thetas <- function(rs)
+{
+  initialize_ppr_thetas <- function(sample_X,n)
+  {
+    # Empirically choose tuning parameters for clustering.
+    cluster_center <- c(-.5,0)
+    cluster_proportions <- .25 * c(1,aspect_ratio)
+    iters <- 10 # number of iterations over which to average
+    
+    # radii
+    if(is.null(rs))
+    {
+      # set grid
+      try_n <- 1000                       # if we know connectivity_radius for try_n...
+      try_r_length <- 10                  # number of radii choices to try
+      try_r_max <- min(cluster_proportions)/2 # maximum radius choice
+      try_r_min <- try_r_max/10               # minimum radius choice
+      rs_length <- 8                      # number of radii choices to end up with
+      
[…]

### 2021-12-23 code/explore/configs/ppr_consistency_2d_configs.R

@@ -1,0 +1,26 @@
+### General configs. ###
+n_iters <- 5
+d <- 2
+ns <- round( seq(1000,4000,length.out = 10) )
+
+### Configs for sampling. ###
+n_mixtures <- 2
+aspect_ratio <- 2
+class_ratio <- .2
+sample_X <- make_sample_mixture_of_uniforms(d, n_mixtures, aspect_ratio, class_ratio)
+
+### Configs for neighborhood graph. ###
+rs <- seq(.02,.1,by = .02)
+
+### Methods ###
+methods <- list(
+  ppr = make_ppr_cluster
+)
+
+initialize_thetas <- list(ppr = make_initialize_ppr_thetas(rs))
+
+### Error metric
+error_metric <- volume_ssd
+error_bounds <- list(ppr = ppr_empirical_error_bound)
+
+

### 2021-12-23 code/explore/evaluate.R

@@ -1,0 +1,32 @@
+volume_ssd <- function(v,act,G){
+  # Return the volume of the symmetric set difference between
+  # a (series of) clusters v[1], v[1:2], v[1:3], ...
+  # and the actual cluster act.
+  
+  # v: ordering (i.e. ranking) of vertices 1:n
+  # act: subset of 1:n
+  # G: graph
+  
+  # vectorized for speed
+  loss_denom <- sum(degree(G)[act])
+  
+  belongs_to_act <- ifelse(v %in% act,1,-1)
+  deg_v <- degree(G)[v]
+  loss_num <- sum(degree(G)[act]) + cumsum(-deg_v*belongs_to_act)
+  loss_num/loss_denom
+}
+
+cardinality_ssd <- function(v,act,G){
+  # Return the cardinality of the symmetric set difference between
+  # a (series of) clusters v[1], v[1:2], v[1:3], ...
+  # and the actual cluster act.
+  
+  # v: ordering (i.e. ranking) of vertices 1:n
+  # act: subset of 1:n
+  # G: graph
+  loss_denom <- length(act)
+  
+  belongs_to_act <- ifelse(p_order %in% act,1,-1)
+  loss_num <- length(act) + cumsum(-belongs_to_act)
+  loss_num/loss_denom
+}

### 2021-12-23 code/explore/graph.R

@@ -1,0 +1,111 @@
+neighborhood_graph <- function(X, r)
+{
+  # unpack necessary parameters
+  d <- ncol(X)
+  N <- nrow(X)
+  
+  k_max <- max(min(round(N*pi^{d/2}/(gamma(d/2 + 1))*r^d*2),N - 1),5)
+  A <- knn_to_neighborhood_graph(X,r,k_max)
+  return(A)
+}
+
+knn_to_neighborhood_graph <- function(X, r, k_max)
+{
+  #--------------------#
+  # Input: X (n x d matrix)
+  #        r connectivity parameter
+  #        k_max maximum degree in graph
+  # Output: A (m x n sparse adjacency matrix)
+  # Function: compute adjacency matrix A
+  # with A = (A_ij)_{i,j in 1:n}, A_ij = 1 iff ||X[i,] - X[j,]||_2 < r
+  #--------------------#
+  
+  # unpack necessary parameters
+  n <- nrow(X)
+  d <- ncol(X)
+  A <- Matrix(0, nrow = n, ncol = n)
+  
+  # compute distance matrix
+  rneighbors <- nn2(data = X, query = X, searchtype = 'radius', k = k_max, radius = r)$nn.idx[,-1]
+  rneighbors[rneighbors == 0] <- NA
+  r_neighbors_list <- as.matrix(melt(rneighbors)[,-2])
+  r_neighbors_list <- r_neighbors_list[rowSums(is.na(r_neighbors_list)) == 0,]
+  A[r_neighbors_list] <- 1
+  
+  # if k_max was not high enough, at least one vertex in A will have exactly k_max - 1 neighbors.
+  # Increase k_max and recalculate.
+  while((max(rowSums(A)) == k_max - 1) & (k_max < n - 1))
+  {
+    A <- Matrix(0, nrow = n, ncol = n)
+    k_max <- min(2*k_max,n - 1)
+    rneighbors <- nn2(data = X, query = X, searchtype = 'radius', k = k_max, radius = r)$nn.idx[,-1]
+    rneighbors[rneighbors == 0] <- NA
+    r_neighbors_list <- as.matrix(melt(rneighbors)[,-2])
+    r_neighbors_list <- r_neighbors_list[rowSums(is.na(r_neighbors_list)) == 0,]
+    A[r_neighbors_list] <- 1
+  }
+  
[…]

### 2021-12-23 code/explore/ppr_consistency_pipeline.R

@@ -1,0 +1,272 @@
+# Dependencies
+library(dplyr)
+library(ggplot2)
+library(gridExtra)
+library(magrittr)
+library(Matrix)
+library(RANN)
+library(reshape2)
+library(tibble)
+library(tidyr)
+source("sample.R")
+source("graph.R")
+source("cluster.R")
+source("bound.R")
+source("evaluate.R")
+
+# Configuration
+source("configs/ppr_consistency_2d_configs.R")
+
+
+# Set up data structures
+Xs <- vector(mode = "list", length = length(ns))
+estimates <- vector(mode = "list", length = length(ns))
+thetas <- vector(mode = "list", length = length(ns))
+errors <- vector(mode = "list", length = length(ns))
+bounds <- vector(mode = "list", length = length(ns))
+
+for(ii in 1:length(ns))
+{
+  n <- ns[ii]
+  
+  thetas[[ii]] <- vector(mode = "list", length = length(methods))
+  estimates[[ii]] <- vector(mode = "list", length = length(methods))
+  bounds[[ii]] <- vector(mode = "list", length = length(methods))
+  errors[[ii]] <- vector(mode = "list",length = length(methods))
+  for(jj in 1:length(methods))
+  {
+    thetas[[ii]][[jj]] <- initialize_thetas[[jj]](sample_X,n)
+    n_thetas <- nrow(thetas[[ii]][[jj]])
+    estimates[[ii]][[jj]] <- vector(mode = "list",length = n_thetas)
+    errors[[ii]][[jj]] <- matrix(nrow = n_thetas, ncol = n_iters)
+    bounds[[ii]][[jj]] <- matrix(nrow = n_thetas, ncol = n_iters)
+  }
+  logger::log_info("Completed hyperparameter setup for n = ", n, ".")
+}
+
+# Estimate clusters
+for(iter in 1:n_iters)
+{
+  save_run <- (iter == 1)
+  for(ii in 1:length(ns))
+  {
+    n <- ns[ii]
+    X <- sample_X(n)
+    
+    # REPLACE BY
+    # empirical_cluster <- get_empirical_cluster(X,sample_X)
+    cluster_center <- -c(.5,0)
+    cluster_proportions <- .25*c(1,aspect_ratio)
+    empirical_cluster <- get_empirical_cluster(X,cluster_center,cluster_proportions)
+    
+    seed <- which.min(dist_to_point(X,cluster_center))
+    
[…]

### 2021-12-23 code/explore/ppr_convergence_pipeline.R

@@ -1,0 +1,272 @@
+# Dependencies
+library(dplyr)
+library(ggplot2)
+library(gridExtra)
+library(magrittr)
+library(Matrix)
+library(RANN)
+library(reshape2)
+library(tibble)
+library(tidyr)
+source("sample.R")
+source("graph.R")
+source("cluster.R")
+source("bound.R")
+source("evaluate.R")
+
+# Configuration
+source("configs/ppr_consistency_2d_configs.R")
+
+
+# Set up data structures
+Xs <- vector(mode = "list", length = length(ns))
+estimates <- vector(mode = "list", length = length(ns))
+thetas <- vector(mode = "list", length = length(ns))
+errors <- vector(mode = "list", length = length(ns))
+bounds <- vector(mode = "list", length = length(ns))
+
+for(ii in 1:length(ns))
+{
+  n <- ns[ii]
+  
+  thetas[[ii]] <- vector(mode = "list", length = length(methods))
+  estimates[[ii]] <- vector(mode = "list", length = length(methods))
+  bounds[[ii]] <- vector(mode = "list", length = length(methods))
+  errors[[ii]] <- vector(mode = "list",length = length(methods))
+  for(jj in 1:length(methods))
+  {
+    thetas[[ii]][[jj]] <- initialize_thetas[[jj]](sample_X,n)
+    n_thetas <- nrow(thetas[[ii]][[jj]])
+    estimates[[ii]][[jj]] <- vector(mode = "list",length = n_thetas)
+    errors[[ii]][[jj]] <- matrix(nrow = n_thetas, ncol = n_iters)
+    bounds[[ii]][[jj]] <- matrix(nrow = n_thetas, ncol = n_iters)
+  }
+  logger::log_info("Completed hyperparameter setup for n = ", n, ".")
+}
+
+# Estimate clusters
+for(iter in 1:n_iters)
+{
+  save_run <- (iter == 1)
+  for(ii in 1:length(ns))
+  {
+    n <- ns[ii]
+    X <- sample_X(n)
+    
+    # REPLACE BY
+    # empirical_cluster <- get_empirical_cluster(X,sample_X)
+    cluster_center <- -c(.5,0)
+    cluster_proportions <- .25*c(1,aspect_ratio)
+    empirical_cluster <- get_empirical_cluster(X,cluster_center,cluster_proportions)
+    
+    seed <- which.min(dist_to_point(X,cluster_center))
+    
+    for(jj in 1:length(methods))
+    {
[…]

### 2021-12-23 code/explore/sample.R

@@ -1,0 +1,40 @@
+make_sample_uniform <- function(d)
+{
+  sample_X <- function(n){
+    X <- matrix(runif(n*d,-1,1),ncol = d)
+    return(X)
+  }
+}
+
+make_sample_mixture_of_uniforms <- function(d, n_mixtures, aspect_ratio, class_ratio)
+{
+  sample_X <- function(n){
+    cluster_centers <- .5 * matrix(
+      c(cos(seq(0,2*pi,length.out = n_mixtures + 1))[-n_mixtures + 1], 
+        sin(seq(0,2*pi,length.out = n_mixtures + 1))[-n_mixtures + 1]),
+      ncol = 2
+    )
+    
+    cluster_proportions <- .25 * matrix(
+      c(rep(1,n_mixtures),
+        rep(aspect_ratio,n_mixtures)),
+      ncol = 2
+    )
+    
+    Z <- make_sample_uniform(d)(n)
+    probs <- c(rep(class_ratio,n_mixtures),1) %>% (function(p){p/sum(p)})
+    classes <- rmultinom(n, size = 1, probs) %>% (function(M){apply(M,2,which.max)})
+    X <- matrix(nrow = n, ncol = d)
+    for(ii in 1:n)
+    {
+      if(classes[ii] <= n_mixtures)
+      {
+        X[ii,] <- Z[ii,]*cluster_proportions[classes[ii],] + cluster_centers[classes[ii],]
+      } else{
+        X[ii,] <- Z[ii,]
+      }
+    }
+    
+    X
+  }
+}

### 2021-12-23 code/geometric_methods.R

@@ -1,0 +1,360 @@
+# Find the expansion of a geometric set
+expansion <- function(C,X,sigma)
+{
+  # compute the minimum distance of X to C
+  D_XC <- distance(X,as.matrix(X[C,]))
+  distance_to_C <- apply(D_XC,1,FUN = function(d){min(d)})
+  
+  # return the sigma expansion set
+  return(which(distance_to_C <= sigma))
+}
+
+# Compute the density cluster of the 'rounded_box' distribution over points X
+rounded_box_cluster <- function(P,X)
+{
+  # unpack parameters
+  D <- P$D
+  sigma <- P$sigma
+  gamma <- P$gamma
+  d <- ncol(X)
+  n <- nrow(X)
+  
+  vol_Bsigma <- (sigma^d * pi^{d/2} / base::gamma(d/2 + 1))
+  c <- (1 / vol_Bsigma + d * sigma^{gamma}/(gamma + 1)) / 2^d
+  l <- sigma / (8 * sqrt(d)) # grid length
+  
+  # set up full grid
+  lim <- vector(mode = 'list', length = d)
+  lim[[1]] <- seq(-2*sigma, 3*sigma, by = l )
+  for(ii in 2:d)
+  {
+    lim[[ii]] <-  seq(-2*sigma, D + 2*sigma, by = l )
+  }
+  g <- as.matrix(expand.grid(lim))
+  
+  # set up grid over box
+  lim <- vector(mode = 'list', length = d)
+  lim[[1]] <- seq(0, sigma, by = l )
+  for(ii in 2:d)
+  {
+    lim[[ii]] <-  seq(0, D, by = l )
+  }
+  g_box <- as.matrix(expand.grid(lim))
+  
+  # for each point in the grid, compute the density
+  dist <- distance(g, g_box)
+  grid_density_point <- matrix(0, ncol = ncol(dist), nrow = nrow(dist))
+  one_sigma <- (dist <= sigma)
+  two_sigma <- (dist > sigma) & (dist <= 2*sigma)
+  grid_density_point[one_sigma] <- c
+  grid_density_point[two_sigma] <-
+    c - ((dist[two_sigma] - sigma)^{gamma}*sigma^{d - 1})/dist[two_sigma]^{d-1}
+  
+  grid_density <- rowSums(grid_density_point) * l^d * 1/(sigma * D^{d-1})
+  
+  # for each  point in X, compute the density
+  dist <- distance(X, g)
+  
+  X_density <- numeric(n)
+  for(ii in 1:n)
+  {
[…]

### 2021-12-23 code/graph.R

@@ -1,0 +1,247 @@
+library(RANN)
+grapher <- function(data, graph_configs, sigma = NULL)
+{
+  # Input: data (matrix)
+  #        graph_configs (list of parameters)
+  #        - graph_configs$graph_type: flag for type of graph ('kNN', 'epsilon', 'Gaussian')
+  #        - graph_configs$connectivity: minimum number of neighbors each point should have
+  
+  # unpack parameters
+  graph_type <- graph_configs$graph_type
+  connectivity <- graph_configs$connectivity
+  d <- ncol(data)
+  
+  if(graph_type == 'kNN')
+  {
+    adjacency_matrix <- knn_grapher(data, connectivity)
+  } else if(graph_type == 'epsilon')
+  {
+    if(connectivity == 'theoretical_max')
+    {
+      # derive value of r from theory
+      r <- sigma / (4 * d)
+    } else{
+      r <- connectivity
+    }
+    cluster_method <- list(
+      kernel = 'uniform',
+      h = r
+    )
+    adjacency_matrix <- kernel_grapher(data, cluster_method)
+  } else if(graph_type == 'k_to_epsilon')
+  {
+    adjacency_matrix <- k_to_r_graph(connectivity,data)
+  }
+  return(adjacency_matrix)
+}
+
+knn_grapher <- function(data,k)
+{
+  # Input: data (n x d matrix)
+  #        k: number of neighbors
+  # Output: n x n adjacency matrix, with (u ~ v) if either u is a jth-nearest neighbor for v
+  #                                 or v is a jth-nearest neighbor for u
+  
+  # compute necessary parameters
+  n <- nrow(data)
+  
+  # form kNN graph
+  kNN_list <- nn2(data, k = k)$nn.idx
+  A <- matrix(0, nrow = n, ncol = n)
+  for(i in 1:n)
+  {
+    u <- i
+    N_i <- kNN_list[i,]
+    for(j in 1:k)
+    {
+      v <- N_i[j]
+      A[u,v] <- 1
+      A[v,u] <- 1 # (u,v) in the graph if u is a nearest neighbor of v or vice versa
+    }
+  }
+  return(A)
+}
+
+set_distance <- function(X,Y = NULL)
+{
+  #--------------------#
+  # Input: X (n x d matrix)
[…]

### 2021-12-23 code/hyperparameter.R

@@ -1,0 +1,211 @@
+parameter_combiner <- function(method, data, adjacency_matrix, graph_configs = NULL)
+{
+  # unpack necessary parameters
+  method_type <- method$method_type
+  hyperparameter_configs <- method$hyperparameter_configs
+  
+  if(method_type == 'appr')
+  {
+    parameter_combinations <- appr_parameter_combiner(hyperparameter_configs, data, adjacency_matrix)
+  } else if(method_type == 'local_density')
+  {
+    parameter_combinations <- local_density_parameter_combiner(hyperparameter_configs, data, adjacency_matrix,
+                                                         graph_configs)
+  } else if(method_type == 'spectral')
+  {
+    parameter_combinations <- spectral_parameter_combiner(hyperparameter_configs, data)
+  } else if(method_type == 'ppr')
+  {
+    parameter_combinations <- ppr_parameter_combiner(hyperparameter_configs, data)
+  } else if(method_type == 'conductance')
+  {
+   parameter_combinations <- conductance_parameter_combiner(hyperparameter_configs,adjacency_matrix,
+                                                            data)
+  } else if(method_type == 'density')
+  {
+    parameter_combinations <- density_parameter_combiner(hyperparameter_configs, data)
+  }
+  return(parameter_combinations)
+}
+
+density_parameter_combiner <- function(density_hyperparameter_configs, data)
+{
+  # Input: density_hyperparameter_configs
+  #        - $density_cut (list)
+  #        - - $type ('tune')
+  
+  # unpack necessary parameters
+  density_cut_type <- density_hyperparameter_configs$density_cut$type
+  density_cut_length <- density_hyperparameter_configs$density_cut$length
+  N <- density_hyperparameter_configs$N
+  n <- nrow(data)
+  
+  if(density_cut_type == 'tune')
+  {
+    density_cut <- seq(1, N + n, length.out = density_cut_length)
+  }
+  n_parameters <- 2 # density_cut, N extra points
+  parameter_combinations <- matrix(ncol = n_parameters, nrow = length(density_cut),
+                                   dimnames = list(NULL, c('density_cut', 'N')))
+  for(ii in 1:length(density_cut))
+  {
+    parameter_combinations[ii,] = c(density_cut[ii], N)
+  }
+  return(parameter_combinations)
+}
+
[…]

### 2021-12-23 code/hyperparameter_evaluation.R

@@ -1,0 +1,41 @@
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/hyperparameter_evaluation_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+# save_path <- paste(source_path, 'data/',gsub("[^[:alnum:]]", "", Sys.time()), sep = '')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+data <- distribution_sample(P, n)
+
+# Generate similarity graph
+adjacency_matrix <- grapher(data, graph_configs)
+
+# Cluster
+cluster_data <- clusterer(X, cluster_methods)
+
+# Evaluate
+graphical_evaluation <- graphical_evaluator(X, cluster_data)

### 2021-12-23 code/icml_example3_plot2.R

@@ -1,0 +1,56 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example3_plot2_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+
+save_path <- paste0(code_source_path,'icml/')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+for(i in 1:length(mu_distance_scale))
+{
+  for(j in 1:n_sims)
+  {
+    P <- P_sequence
+    P$mu_distance_scale <- P_sequence$mu_distance_scale[i]
+    X <- distribution_sample(P, n)
+    
+    # Cluster
+    cluster_data <- clusterer(X, cluster_methods)
+    
+    # Evaluate
+    metric_evaluation <- metric_evaluator(P,X,cluster_data,density_cluster_parameters)
+    metric_evaluation_table[i,j] <- metric_evaluation
+    print(paste0('Metric evaluation: ',metric_evaluation, ' simulation: ', j, 
+                 ' mu_distance_scale: ',P$mu_distance_scale))
+  }
+}
+graphical_evaluation <- graphical_evaluator_plot3(P_sequence, metric_evaluation_table)
+
+
+# Save
+save(plot4, file = paste0(save_path, 'plot_4.R'))
+save(metric_evaluation_table, file = paste0(save_path, 'metric_evaluation_table_2.R'))

### 2021-12-23 code/icml_example_1.R

@@ -1,0 +1,64 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example1_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+density_cluster_path <- paste0(code_source_path, "density_cluster.R")
+geometric_path <- paste0(code_source_path, "geometric_methods.R")
+theoretical_path <- paste0(code_source_path, "theoretical_bounds.R")
+# save_path <- paste(source_path, 'data/',gsub("[^[:alnum:]]", "", Sys.time()), sep = '')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+source(density_cluster_path)
+source(geometric_path)
+source(theoretical_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+X <- distribution_sample(P, n)
+
+# Find normalized cut
+lambda_path <-  density_cluster_parameters$lambda_path
+sigma <- density_cluster_parameters$sigma
+
+Phi <- matrix(nrow = length(lambda_path),ncol = 2)
+i = 1
+for(lambda in lambda_path)
+{
+  # Compute empirical density cluster
+  C <- density_cluster(P,X,density_cluster_parameters,lambda)
+  
+  # Find expansion of empirical density cluster
+  Csig <- expansion(C,X,sigma)
+  
+  # Compute normalized cut of thickened set
[…]

### 2021-12-23 code/icml_example_2.R

@@ -1,0 +1,43 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example2_plot2_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+
+save_path <- paste0(code_source_path,'icml/')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+X <- distribution_sample(P, n)
+
+# Cluster
+cluster_data <- clusterer(X, cluster_methods)
+
+# Evaluate
+metric_evaluation <- metric_evaluator(X, cluster_data)
+graphical_evaluation <- graphical_evaluator_plot2(P, X, cluster_data)
+
+# Save
+save(plot2, file = paste0(save_path, 'plot_2.R'))

### 2021-12-23 code/icml_example_2_plot3.R

@@ -1,0 +1,59 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example2_plot3_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+
+save_path <- paste0(code_source_path,'icml/')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+mu_distance_scale <- P_sequence$mu_distance_scale
+metric_evaluation_table <- matrix(nrow = length(mu_distance_scale), ncol = n_sims)
+for(i in 1:length(mu_distance_scale))
+{
+  for(j in 1:n_sims)
+  {
+    P <- P_sequence
+    P$mu_distance_scale <- P_sequence$mu_distance_scale[i]
+    X <- distribution_sample(P, n)
+    
+    # Cluster
+    cluster_data <- clusterer(X, cluster_methods)
+    
+    # Evaluate
+    metric_evaluation <- metric_evaluator(P,X,cluster_data,density_cluster_parameters)
+    metric_evaluation_table[i,j] <- metric_evaluation
+    print(paste0('Metric evaluation: ',metric_evaluation, ' simulation: ', j, 
+                  ' mu_distance_scale: ',P$mu_distance_scale))
+  }
+  
+}
+graphical_evaluation <- graphical_evaluator_plot3(P_sequence, metric_evaluation_table)
+
+
+# Save
[…]

### 2021-12-23 code/icml_example_2_plot4.R

@@ -1,0 +1,37 @@
+# Import libraries
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+julia_setup('C:/Users/alden/AppData/Local/JuliaPro-0.6.2.1/Julia-0.6.2/bin') # takes about 20 seconds
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/spectral-sparsification/'
+code_source_path <- paste(source_path, "code/density_clustering/", sep = '')
+config_path <- paste(code_source_path, 'configs/icml_example3_plot1_config.R', sep = '')
+distribution_path <- paste(code_source_path, 'sample.R', sep = '')
+cluster_path <- paste(code_source_path, 'cluster_methods.R',sep = '')
+graph_path <- paste0(code_source_path, "graph.R")
+evaluation_path <- paste(code_source_path, 'evaluate.R', sep = '')
+
+save_path <- paste0(code_source_path,'icml/')
+
+source(distribution_path)
+source(cluster_path)
+source(graph_path)
+source(evaluation_path)
+
+# Read in parameters
+source(config_path)
+
+# Generate data
+X <- distribution_sample(P, n)
+    
+# Cluster
+cluster_data <- clusterer(X, cluster_methods)
+    

### 2021-12-23 code/misc.R

@@ -1,0 +1,19 @@
+plot_df <- data.frame(x_1 = g_enl[,1], x_2 = g_enl[,2], col = q_dens)
+
+ggplot(plot_df, aes(x = x_1, y = x_2, color = col)) + geom_point()
+
+plot(X, col = alpha(ifelse((1:n) %in% Csig, 'red', 'blue'),.04), asp = 1, pch = 20,
+     xlab = 'x1', ylab = 'x2')
+
+plot(X, col = ifelse((1:n) %in% Csig[rowSums(Csig_adjacency_matrix) == 1], 'red', 'blue'), asp = 1)
+
+C_box <- which(X[,1] <= sigma & X[,1] >= 0 & 
+               X[,2] <= D & X[,2] >= 0)
+
+
+plot(X, col = ifelse((1:n) %in% C_box, 'red', 'blue'), asp = 1)
+
+
+plot(X, col = alpha(ifelse((1:n) %in% Csig, 'red', 'blue'),.04), asp = 1, pch = 20,
+     xlab = 'x1', ylab = 'x2')
+

### 2021-12-23 code/mixing_time_pipeline.R

@@ -1,0 +1,98 @@
+# mixing_time_pipeline.R is the main script for showing theoretical upper bounds vs. empirical
+# bounds for mixing time over a density cluster
+# Function: Iterates over sigma (thickness) and gamma (density drop) parameters
+#           computing theoretical bounds and empirical estimates for
+#           normalized cut and mixing time.
+
+
+
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(igraph)
+require(RANN)
+require(Matrix)
+require(reshape2)
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+script_names <- c('configs/diameter_mixing_time_config.R','theoretical_methods.R','sample.R',
+                  'geometric_methods.R','numeric_methods.R','graph.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# unpack necessary parameters
+distribution_class <- model$distribution_class
+sigma <- model$sigma
+gamma <- model$gamma
+lambda_sigma <- model$lambda_sigma
+lambda <- model$lambda
+
+# unpack range parameters
+d_range <- model$d_range
+D_range <- model$D_range
+
+# compute theoretical mixing time 
+theoretical_mixing_time <- matrix(0, ncol = length(D_range), nrow = length(d_range))
+for (ii in 1:length(D_range))
+{
+  D <- D_range[ii]
+  for (jj in 1:length(d_range))
+  {
+    d <- d_range[jj]
+    P <- list(
+      distribution_class = distribution_class,
+      sigma = sigma,
+      gamma = gamma,
+      D = D,
+      d = d,
+      lambda_sigma = lambda_sigma,
+      lambda = lambda
+    )
+    
+    print(paste0('Dimension:',d, '; Diameter:', D))
+    # mixing time theoretical bound 
+    theoretical_mixing_time[jj,ii] <- mixing_time_upper_bound(P, graph_configs)
+  }
+}
+
+# compute empirical mixing time
+n_sims <- empirical_configs$n_sims
+empirical_mixing_time <- array(0, dim = c(length(D_range),length(d_range), n_sims) )
+for (ii in 1:length(D_range))
+{
+  D <- D_range[ii]
+  for (jj in 1:length(d_range))
+  {
+    d <- d_range[jj]
+    P <- list(
[…]

### 2021-12-23 code/mixing_time_plot.R

@@ -1,0 +1,110 @@
+#----------------------#
+# script to generate plot for mixing time data
+#----------------------#
+
+library(sfsmisc)
+
+# load data
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/data/'
+data_directory <- 'mixing_time_data/sigma_data/'
+data_path <- paste0(source_path, data_directory)
+for(file in list.files(data_path))
+{
+  load(paste0(data_path,file))
+}
+
+# setup plot file
+plot_path <- paste0(source_path, 'example1plots/')
+plot_filename <- paste0(plot_path,'sigma_mixing_time_plot.pdf')
+pdf(plot_filename, 6, 6)
+
+# compute necessary quantities for plot
+theoretical_data <- theoretical_mixing_time
+empirical_data <- empirical_mixing_time
+
+plot_empirical_data <- t(apply(empirical_data,c(1,2),FUN = function(x){median(x,na.rm = T)}))
+plot_theoretical_data <- matrix(0, nrow = nrow(theoretical_data), ncol = ncol(theoretical_data))
+for(ii in 1:nrow(theoretical_data))
+{
+  plot_theoretical_data[ii,] <- theoretical_data[ii,] * 1.2*(max(plot_empirical_data[ii,]/theoretical_data[ii,]))
+}
+
+sigma <- configs$model$sigma
+x_var_range <- configs$model$sigma_range + 2 * sigma
+# plot_df <- data.frame(x = log(D_range), 
+#                       y_emp = log(med_empirical_mixing_time),
+#                       y_the = log(t(theoretical_mixing_time))
+#                       )
+col <- c('green4','mediumpurple4')
+# col <- c('chartreuse','deeppink')
+
+# plot specifications
+line.lwd <- 2
+y.min <- min(c(plot_empirical_data, plot_theoretical_data))
+y.max <- max(c(plot_empirical_data, 
+               plot_theoretical_data))
+ylim <- c(y.min, y.max)
+old.par <- par(no.readonly = TRUE)
+x.at <- x_var_range
+
+# shadow plot
+plot(x_var_range, plot_empirical_data[1,], log = 'xy',
[…]

### 2021-12-23 code/normalized_cut_pipeline.R

@@ -1,0 +1,104 @@
+# normalized_cut_pipeline.R is the main script for showing theoretical upper bounds vs. empirical samples of
+# normalized cut
+# Function: Iterates over sigma (thickness) and gamma (density drop) parameters
+#           computing theoretical bounds and empirical estimates for
+#           normalized cut.
+
+
+
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(igraph)
+require(RANN)
+require(Matrix)
+require(reshape2)
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+script_names <- c('configs/diameter_normalized_cut_config.R','theoretical_methods.R','sample.R',
+                  'geometric_methods.R','numeric_methods.R','graph.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# compute theoretical and sample normalized cut
+
+# unpack necessary parameters
+distribution_class <- model$distribution_class
+sigma_range <- model$sigma_range
+gamma <- model$gamma
+lambda_sigma <- model$lambda_sigma
+lambda <- model$lambda
+
+# unpack range parameters
+D_range <- model$D_range
+d_range <- model$d_range
+
+theoretical_ncut <- matrix(0, ncol = length(D_range), nrow = length(d_range))
+for (ii in 1:length(D_range))
+{
+  D <- D_range[ii]
+  for (jj in 1:length(d_range))
+  {
+    d <- d_range[jj]
+    
+    P <- list(
+      distribution_class = distribution_class,
+      sigma = sigma,
+      gamma = gamma,
+      D = D,
+      d = d,
+      lambda_sigma = lambda_sigma,
+      lambda = lambda
+    )
+    # normalized cut theoretical bound 
+    print(paste0('Diameter:',D, '; Dimension:', d))
+    theoretical_ncut[jj,ii] <- ncut_upper_bound(P, graph_configs)
+  }
+}
+
+# unpack necessary parameters
+n_sims <- empirical_configs$n_sims
+
+empirical_ncut <- array(0, dim = c(length(d_range),length(D_range),n_sims))
+
+# sample normalized cut
+for (ii in 1:length(D_range))
+{
+  D <- D_range[ii]
+  for (jj in 1:length(d_range))
+  {
+    d <- d_range[jj]
+    
[…]

### 2021-12-23 code/normalized_cut_plot.R

@@ -1,0 +1,105 @@
+# script to generate plot for mixing time data
+library(sfsmisc)
+
+# load data
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/data/'
+plot_path <- paste0(source_path, 'example1plots_2/')
+
+data_directory <- 'normalized_cut_data/sigma_data/'
+data_path <- paste0(source_path, data_directory)
+for(file in list.files(data_path))
+{
+  load(paste0(data_path,file))
+}
+
+# setup plot file
+plot_path <- paste0(source_path, 'example1plots/')
+plot_filename <- paste0(plot_path,'sigma_normalized_cut_plot.pdf')
+pdf(plot_filename, 6, 6)
+
+# compute necessary quantities for plot
+plot_empirical_data <- apply(empirical_ncut,c(1,2),FUN = function(x){mean(x,na.rm = T)})
+plot_theoretical_data <- matrix(0, nrow = nrow(theoretical_ncut), ncol = ncol(theoretical_ncut))
+for(ii in 1:nrow(theoretical_ncut))
+{
+  plot_theoretical_data[ii,] <- theoretical_ncut[ii,] * 1.2 * (max(plot_empirical_data[ii,]/theoretical_ncut[ii,]))
+}
+
+sigma <- configs$model$sigma
+x_var_range <- configs$model$sigma_range + 2*sigma
+col <- c('green4','mediumpurple4')
+# col <- c('chartreuse','deeppink')
+
+
+# plot specifications
+line.lwd <- 2
+y.min <- min(c(plot_empirical_data, plot_theoretical_data))
+y.max <- max(c(plot_empirical_data, 
+               plot_theoretical_data))
+ylim <- c(y.min, y.max)
+x.at <- round(x_var_range,2)
+
+# shadow plot
+plot(x_var_range, plot_empirical_data[1,], log = 'xy',
+     xlab = 'sigma', ylab = '      Normalized cut', ylim = ylim, cex.lab = 1.7,
+     axes = FALSE, frame.plot = TRUE, type = 'n')
+x_axis <- axis(1, cex.axis = 1.7)
+rug_x <- numeric(length(x_axis) - 1)*4
+for(ii in 2:(length(x_axis)))
+{
+  for(jj in 1:4)
+  {
+    kk <- 4*(ii - 2) + jj
[…]

### 2021-12-23 code/numeric_methods.R

@@ -1,0 +1,158 @@
+integrate <- function(f,g,d)
+{
+  #---------------#
+  # Input: f function
+  #        g grid over rectangular domain D
+  #        d dimension
+  # Output: a number
+  # Function: estimate int_D f dx by sum_{x in g} f(x) * vol(grid_cell)
+  
+  # calculate necessary parameters
+  l <- abs(sum(g[1,] - g[2,]))
+  vol <- (l)^d
+  
+  return(sum(f(g)) * vol)
+}
+
+max_degree_bound <- function(P,n,r)
+{
+  # unpack necessary parameters
+  D <- P$D
+  sigma <- P$sigma
+  lambda <- P$lambda
+  lambda_sigma <- P$lambda_sigma
+  gamma <- P$gamma
+  d <- P$d
+  
+  # calculate additional parameters
+  eta <- (lambda - lambda_sigma)/(sigma) # to compute density function q
+  l <- (D + 4*sigma)/(100000^{1/d}) # to approximate integral
+  
+  # Upper bound expected degree
+  # by E \leq r^d nu_d lambda / (int_R^d q(x) dx)
+  # where the normalization comes from the fact that p(x) = q(x) / int_R^d q(x) dx
+  
+  ## 1. Average q over small cells in a grid, g_enl
+  lim <- vector(mode = 'list', length = d)
+  lim[[1]] <- seq(0, 5*sigma, by = l)
+  for(ii in 2:d)
+  {
+    lim[[ii]] <-  seq(0, D + 4*sigma, by = l)
+  }
+  g_enl <- as.matrix(expand.grid(lim)) # grid over [-2sigma, 3sigma] x [0,D]^{d-1} supset C_2sigma
+  
+  # compute density function of each point
+  q <- function(X)
+  {
+    # compute necessary parameters
+    n_obs <- nrow(X)
+    
+    # compute distance of X to C
+    C_vertices <- matrix(0, nrow = d, ncol = 2)
+    C_vertices[1,] <- c(2*sigma,3*sigma)
+    C_vertices[2:d,] <- c(rep(2*sigma,d-1), rep(D + 2*sigma,d - 1))
+    dist <- dist_to_rectangle(X, C_vertices)
+    
+    # compute which expansion points in X are in
+    C <- (dist == 0)
+    C_sigma <- (dist > 0 & dist <= sigma)
+    C_2sigma <- (dist > sigma & dist < 2*sigma)
+    
[…]

### 2021-12-23 code/pipeline.R

@@ -1,0 +1,154 @@
+# pipeline.R is the main *local* clustering script of local_spectral_density_clustering_project.
+# Function: 1. Simulates data
+#           2. Forms adjacency matrix encoding 'nearness' of data points according to a distance metric.
+#           3. Iterates over clustering methods, and for each clustering method
+#           -3a. Creates all hyperparameter possibilities
+#           -3b. Calculates similarity scores and cluster for each hyperparameter possibility
+#           -3c. Retains similarities and cluster for 'best' choice of hyperparameter
+# Output: clustering_data (list)
+#         - clustering_data$method (list)
+#         - - clustering_data$method$similarity: similarity (vector) for given method
+#         - - clustering_data$method$cluster: cluster (vector) for given method
+#         - - clustering_data$method$evaluation: evaluation (numeric) for each method
+  
+
+
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(forcats)
+require(igraph)
+require(rdist)
+require(gridExtra)
+require(KernSmooth)
+require(JuliaCall)
+require(gurobi)
+require(dplyr)
+julia_setup('C:/Users/alden/AppData/Local/Julia-1.1.0/bin')
+julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+script_names <- c('configs/small_config.R', 'sample.R', 'hyperparameter.R',
+                  'similarity.R','cluster_methods.R','graph.R','geometric_methods.R','numeric_methods.R',
+                  'evaluate.R','plot_methods.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# Generate data
+data <- distribution_sample(P, n)
+
+# Compute similarity graph
+adjacency_matrix <- grapher(data, graph_configs)
+
+# Generating local clusters
+local_cluster_data <- vector(mode = 'list', length = length(local_cluster_methods))
+names(local_cluster_data) <- names(local_cluster_methods)
+for(cluster_method_name in names(local_cluster_methods))
+{
+  method <- local_cluster_methods[[cluster_method_name]]
+  
+  evaluation0 <- 1 # 1 should be the worst possible evaluation a cluster can receive
+  
+  # Form hyperparameters to optimize over
[…]

### 2021-12-23 code/plot_density.R

@@ -1,0 +1,72 @@
+library(fields)
+
+## input parameters
+pdf <- TRUE
+filename <- "lower_bound_1"
+rho <- 1
+sigma <- .2
+epsilon <- .2
+n_eval <- 200^2
+x_range <- c(-.6,.6)
+y_range <- c(-.6,.6)
+
+density_maker <- function(rho,sigma,epsilon)
+{
+  density <- function(x)
+  {
+    if(x[1] < -3*sigma/2 || x[1] > 3*sigma/2 || x[2] < -rho/2 || x[2] > rho/2)
+    {
+      return(0)
+    }
+    else if(x[1] <= -sigma/2 || x[1] >= sigma/2)
+    {
+      return( (1-epsilon)/(2*sigma*rho) )
+    } else{
+      return(epsilon/(sigma*rho))
+    }
+  }
+}
+
+density <- density_maker(rho,sigma,epsilon)
+eval_points <- matrix(0,ncol = 2,nrow = n_eval)
+for(ii in 1:sqrt(n_eval))
+{
+  x <- x_range[1] + ii/sqrt(n_eval)*(x_range[2] - x_range[1])
+  for(jj in 1:sqrt(n_eval))
+  {
+    kk <- (ii - 1)*sqrt(n_eval) + jj
+    y <- y_range[1] + jj/sqrt(n_eval)*(y_range[2] - y_range[1])
+    eval_points[kk,] <- c(x,y)
+  }
+}
+p <- apply(eval_points,1,FUN = density)
+
+if(pdf)
+{
+  source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+  data_path <- paste0(source_path, "data/")
+  file_path <- paste0(data_path,filename,".pdf")
+  pdf(file_path)
+}
+
+# create colors
+n_colors <- 100
+colfunc <- colorRampPalette(c("blue", "red"))
+colors <- colfunc(n_colors)
+color_range <- c(.25,2.25)
+# breaks <- seq(min(color_range),max(color_range),length.out = n_colors)
+# p_colors <- colors[cut(p,breaks,include.lowest = T)]
+# plot(eval_points, pch = 20, col = p_colors,
+#       xlab = 'x1', ylab = 'x2', xlim = c(-.6,.6), ylim = c(-.6,.6), cex.lab = 1.2, cex.axis = 1.2)
+
[…]

### 2021-12-23 code/plot_methods.R

@@ -1,0 +1,334 @@
+require(RColorBrewer)
+
+clustering_plotter <- function(clustering_data, adjacency_matrix, data, plot_directory)
+{
+  # unpack necessary parameters
+  for(method in clustering_data)
+  {
+    clustering <- method$cluster
+    color_vector <- clustering_to_color(clustering, data)
+    
+    plot_filename <- paste0(plot_directory, method$method$method_type, '_cluster.pdf')
+    data_plotter(data, adjacency_matrix, color_vector = color_vector, 
+                 plot_filename = plot_filename,
+                 color_palette = density_cluster_palette)
+  }
+}
+
+clustering_to_color <- function(clustering, data)
+{
+  cluster_vector <- clustering
+  
+  # TODO: make seed node a global parameter. Different algorithms should have the same seed.
+  seed_node_manifold_location <- c(.05, -.35)
+  d <- ncol(data)
+  seed_node_location <- intrinsic_to_extrinsic(d,seed_node_manifold_location)
+  seed_node <- which.min(apply(data, 1, FUN = function(x){sum((x - seed_node_location)^2)}))
+  
+  cluster_vector <- factor(cluster_vector)
+  cluster_vector <- relevel(cluster_vector, as.character(cluster_vector[seed_node]) )
+  cluster_vector <- relevel(cluster_vector,  '0')
+  cluster_vector <- as.numeric(cluster_vector) # convert to right numbers
+  
+  return(cluster_vector)
+}
+plotter <- function(cluster_data, adjacency_matrix, data, P = NULL, plot_directory = NULL)
+{
+  # unpack necessary parameters
+  n <- nrow(data)
+  
+  # compute density
+  density_data <- density(P, data)
+    
+  # compute cluster tree
+  cluster_tree_data <- cluster_tree(P, data, density_data = density_data)
+  
+  ### Plot (1): raw data
+  plot_filename <- paste0(plot_directory, 'data', '.pdf')
+  data_plotter(data, plot_filename = plot_filename)
+  
+  ### Plot (2): graph
+  plot_filename <- paste0(plot_directory, 'graph', '.pdf')
+  data_plotter(data, adjacency_matrix, plot_filename = plot_filename)
+  
+  ### Plot (3): density heatmap
+  plot_filename <- paste0(plot_directory, 'density_heatmap', '.pdf')
+  data_plotter(data,adjacency_matrix, plot_filename = plot_filename,
[…]

### 2021-12-23 code/sample.R

@@ -1,0 +1,548 @@
+# wrapper for sampling from arbitrary distribution
+distribution_sample <- function(P, n)
+{
+  # unpack necessary parameters
+  distribution_class <- P$distribution_class
+  
+  # use correct model
+  if(distribution_class == 'gaussian')
+  {
+    data <- gaussian_sample(P,n)
+  } else if(distribution_class == 'gaussian_mixtures')
+  {
+    data <- gaussian_mixture_sample(P,n)
+  } else if(distribution_class == 'two_moons')
+  {
+    data <- two_moons_sample(P,n)
+  } else if(distribution_class == 'theory_distribution')
+  {
+    data <- theory_sample(P,n)
+  } else if(distribution_class == 'ellipse_distribution')
+  {
+    data <- ellipse_sample(P,n)
+  } else if(distribution_class == 'rounded_box_distribution')
+  {
+    data <- rounded_box_sample(P,n)
+  } else if(distribution_class == 'rounded_box_2_distribution')
+  {
+    data <- rounded_box_2_sample(P,n)
+  }
+  return(data)
+}
+
+rounded_box_2_sample <- function(P,n, method = 'rejection')
+{
+  #--------------#
+  # Sample from pdf p:[0,1]^d -> (0,infty)
+  # Given parameters D, sigma, lambda, lambda_sigma, gamma, d.
+  # Let C = [2*sigma,3*sigma] x [2*sigma,D + 2*sigma]^{d-1}, eta = log(lambda_sigma)/log(sigma),
+  #     C_sigma = C + B(0,sigma), C_2sigma = C + B(0,2*sigma).
+  # q(x) = 
+  # {
+  #   lambda,                                x in C, 
+  #   lambda - dist(x, C)^eta,               x in C_sigma \ C,
+  #   lambda - sigma^eta - dist(x, C_sigma), x in C_2sigma \ C_sigma
+  # }
+  # Let a = (1 - int(C_2sigma) p(x)) / vol([0,1]^d / C_2sigma).
+  # p(x) = 
+  # {
+  #   q(x), x in C_2sigma
+  #   a,    x in [0,1]^d / C_2sigma
+  # }
+  #--------------#
+  
+  # unpack necessary parameters
+  D <- P$D
[…]

### 2021-12-23 code/similarity.R

@@ -1,0 +1,216 @@
+similarity_scorer <- function(method_type, adjacency_matrix, parameters, data)
+{
+  # Input: method_type (flag) local clustering method ('appr', 'density', 'spectral', 'ppr')
+  #        adjacency_matrix (n x n matrix)
+  #        parameters (named vector) vector of parameters for use
+  
+  if(method_type == 'appr')
+  {
+    similarity <- appr(adjacency_matrix,parameters)
+  } else if(method_type == 'local_density')
+  {
+    similarity <- local_density(adjacency_matrix,parameters,data)
+  } else if(method_type == 'spectral')
+  {
+    similarity <- spectral(adjacency_matrix,parameters)
+  } else if(method_type == 'ppr')
+  {
+    similarity <- ppr(adjacency_matrix,parameters)
+  } else if(method_type == 'conductance')
+  {
+    similarity <- conductance(adjacency_matrix, parameters)
+  }
+  return(similarity)
+}
+
+appr <- function(A, parameters)
+{
+  # Input: A (n x n matrix) adjacency matrix
+  #        parameters (vector)
+  #        -['seed_node']
+  #        -['teleportation_parameter']
+  #        -['approximation_parameter']
+  
+  # unpack necessary parameters
+  v <- as.integer(parameters['seed_node']) # integer conversion necessary for Julia call
+  alpha <- parameters['teleportation_parameter']
+  eps <- parameters['approximation_parameter']
+  
+  # compute personalized PageRank
+  A_list <- which(A == 1, arr.ind = T)
+  aprJL <- julia_call("apr_wrapper", A_list, v, alpha, eps)
+  appr_vector <- unlist(aprJL) * rowSums(A)[as.numeric(names(unlist(aprJL)))]
+  ppr_vector <- numeric(nrow(A)); ppr_vector[as.numeric(names(appr_vector))] <- appr_vector
+  
+  similarity <- ppr_vector / rowSums(A)
+  
+  return(similarity)
+}
+
+conductance <- function(A, parameters)
+{
+  # Input: A (n x n matrix) adjacency matrix,
+  #        data (n x d matrix) data matrix
+  # Output: second eigenvector as 'similarity' vector
+  
+  # unpack necessary parameters
+  seed_node <- strtoi(parameters['seed_node'])
[…]

### 2021-12-23 code/theoretical_bounds.R

@@ -1,0 +1,164 @@
+theoretical_upper_bound_normalized_cut <- function(P, X, Csig, density_cluster_parameters, lambda)
+{
+  ### unpack parameters
+  sigma <- density_cluster_parameters$sigma
+  r <- density_cluster_parameters$r
+  
+  ### check separation
+  
+  ### compute lambda_sigma
+  
+  # compute the density function for P
+  if(P$distribution_class == 'gaussian_mixtures')
+  {
+    f <- gaussian_mixture_density(P)
+  }
+  
+  # evaluate the density function over X
+  f_n <- apply(as.matrix(X[Csig,]), 1, FUN = function(x){f(x)})
+  lambda_sigma <- min(f_n)
+  
+  ### compute c_1 for low-noise condition
+  
+  # compute parameters and density functions for each cluster component
+  mixture_components <- gaussian_mixture_density_parameterization(P)
+  
+  # the 'local' cluster component
+  mixture_densities <- lapply(mixture_components,FUN = function(m){m$density})
+  f_mixture_n <- matrix(ncol = length(mixture_densities), nrow = length(Csig))
+  for(i in 1:nrow(f_mixture_n))
+  {
+    x <- X[Csig[i],]
+    f_mixture_n[i,] <- sapply(mixture_densities, FUN = function(d){d(x)})
+  }
+  
+  local_component_index <- which.max(colMeans(f_mixture_n))
+  local_component <- mixture_components[[local_component_index]]
+  
+  # positive derivative term given by the 'local' cluster component
+  local_Sigma <- local_component$Sigma
+  local_mu <- local_component$mu
+  local_density <- local_component$density
+  
+  distance_from_local_mu <- ginv_normal_density(local_Sigma,lambda) + sigma
+  local_derivative <- distance_from_local_mu*(local_density(local_mu + distance_from_local_mu + sigma))
+  
+  # negative derivative term given by the 'other' components
+  other_component_indices = which(1:length(mixture_components) != local_component_index)
+  component_derivatives <- numeric(length(other_component_indices))
+  i = 1
+  for(index in other_component_indices)
+  {
+    component <- mixture_components[[index]]
+    Sigma <- component$Sigma
+    mu <- component$mu
+    density <- component$density
+    
[…]

### 2021-12-23 code/theoretical_data_plot.R

@@ -1,0 +1,108 @@
+# theoretical_data_plot.R is the main script
+# for plotting the data, complete with highlighting of the density cluster and expanded set
+
+
+
+
+# Dependencies
+require(MASS)
+require(ggplot2)
+require(igraph)
+require(RANN)
+require(Matrix)
+require(reshape2)
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+data_path <- paste0(source_path, "data/")
+script_names <- c('configs/normalized_cut_config.R','theoretical_methods.R','sample.R',
+                  'geometric_methods.R','numeric_methods.R','graph.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# compute theoretical and sample normalized cut
+
+# unpack necessary parameters
+distribution_class <- model$distribution_class
+sigma_range <- model$sigma_range
+gamma <- model$gamma
+d_range <- model$d_range
+lambda_sigma <- model$lambda_sigma
+lambda <- model$lambda
+
+#---------------------#
+# Plot 1: sigma = .466, d = 2
+#---------------------#
+
+sigma <- sigma_range[5]
+d <- d_range[1]
+P <- list(
+  distribution_class = distribution_class,
+  sigma = sigma,
+  gamma = gamma,
+  D = D,
+  d = d,
+  lambda_sigma = lambda_sigma,
+  lambda = lambda
+)
+
+file_path <- paste0(data_path, "sample1.pdf")
+
+plot_sample(P,n,file_path)
+
+#---------------------#
+# Plot 1: sigma = 3.2, d = 2
+#---------------------#
+
+sigma <- sigma_range[10]
+d <- d_range[1]
+P <- list(
+  distribution_class = distribution_class,
+  sigma = sigma,
+  gamma = gamma,
+  D = D,
+  d = d,
+  lambda_sigma = lambda_sigma,
+  lambda = lambda
+)
+
+file_path <- paste0(data_path, "sample2.pdf")
+
+plot_sample(P,n,file_path)
+
+
+### the plotting function
+
+plot_sample <- function(P,n, filename = NULL)
+{
+  if(!is.null(filename))
+  {
+    pdf(filename)
+  }
[…]

### 2021-12-23 code/theoretical_methods.R

@@ -1,0 +1,237 @@
+ncut_upper_bound <- function(P, graph_configs)
+{
+  # Input: - distribution_class (flag),
+  #        - sigma (number),
+  #        - gamma (number),
+  #        - graph_configs (list)
+  
+  ## unpack necessary parameters
+  sigma <- P$sigma
+  lambda <- P$lambda
+  lambda_sigma <- P$lambda_sigma
+  gamma <- P$gamma
+  d <- P$d
+  graph_type <- graph_configs$graph_type
+  r <- graph_configs$connectivity
+  
+  # calculate necessary parameters
+  if(r == 'theoretical_max')
+  {
+    r <- sigma / 4*sqrt(d)
+  } else if (r == 'k_degree') {
+    r <- min_r_bound(P,n,1)
+  }
+  # enforce the condition on r required by normalized cut upper bound
+  if(r >= (3*sigma) / (2*d))
+  {
+    r <- (3*sigma) / (2*d)
+  }
+  
+  bound <- r * 4 / sigma * d * lambda / lambda_sigma * (lambda_sigma - r^{gamma}/(gamma + 1)) /
+    lambda_sigma
+  return(bound)
+}
+
+mixing_time_upper_bound <- function(P, graph_configs)
+{
+  # Input: - distribution_class (flag),
+  #        - sigma (number),
+  #        - gamma (number),
+  #        - graph_configs (list)
+  
+  ## unpack necessary parameters
+  lambda <- P$lambda
+  lambda_sigma <- P$lambda_sigma
+  Lambda_sigma <- lambda # TODO: change this; it holds only when the density is uniform over C.
+  D <- P$D
+  d <- P$d
+  r <- graph_configs$connectivity
+  
+  # calculate necessary parameters
+  if(r == 'theoretical_max')
+  {
+    r <- sigma / 4*sqrt(d)
+  } else if (r == 'k_degree') {
+    r <- min_r_bound(P,n,1)
+  }
+  
+  # r must be less than the maximum allowed by theory
+  if(r >= 4 * sigma / sqrt(d) )
+  {
+    r <- 4*sigma / sqrt(d)
+  }
+  
+  lambda_ratio <- Lambda_sigma / lambda_sigma
+  c_lambda <- 2*log(lambda_ratio)
+  mu <- log(2*(D + 2*sigma) / r)
+  
[…]

### 2021-12-23 code/theoretical_pipeline.R

@@ -1,0 +1,80 @@
+# theoretical_pipeline.R is the main script for showing theoretical upper bounds vs. empirical samples of
+# 
+# Function: Iterates over sigma (thickness) and gamma (density drop) parameters
+#           computing theoretical bounds and empirical estimates for
+#           normalized cut.
+
+
+
+# Dependencies
+# require(MASS)
+# require(ggplot2)
+# require(forcats)
+require(igraph)
+# require(rdist)
+# require(gridExtra)
+# require(KernSmooth)
+# require(JuliaCall)
+# require(gurobi)
+# require(dplyr)
+# julia_setup('C:/Users/alden/AppData/Local/Julia-1.1.0/bin')
+# julia_source("C:/Users/alden/OneDrive/Documents/Spectral Sparsification Work/apr.jl")
+
+# Source methods
+source_path <- 'C:/Users/alden/OneDrive/Documents/Statistics/local_spectral_density_clustering/'
+code_source_path <- paste(source_path, "code/", sep = '')
+script_names <- c('configs/theoretical_pipeline_config.R','theoretical_methods.R','sample.R',
+                  'geometric_methods.R','graph.R')
+for(script_name in script_names)
+{
+  source(paste(code_source_path, script_name, sep = ''))
+}
+
+# compute theoretical and sample normalized cut
+
+# unpack necessary parameters
+distribution_class <- model$distribution_class
+sigma_range <- model$sigma_range
+gamma_range <- model$gamma_range
+d <- 2 # only considering 2 dimensions for now
+
+theoretical_ncut <- matrix(0, ncol = length(sigma_range), nrow = length(gamma_range))
+for (ii in 1:length(sigma_range))
+{
+  sigma <- sigma_range[ii]
+  for (jj in 1:length(gamma_range))
+  {
+    gamma <- gamma_range[jj]
+    
+    # normalized cut theoretical bound 
+    theoretical_ncut[jj,ii] <- ncut_upper_bound(distribution_class, sigma, gamma, d, graph_configs)
+  }
+}
+
+# unpack necessary parameters
+D <- model$D
+
+empirical_ncut <- matrix(0, ncol = length(sigma_range), nrow = length(gamma_range))
+
+# sample normalized cut
+for (ii in 1:length(sigma_range))
+{
+  sigma <- sigma_range[ii]
+  for (jj in 1:length(gamma_range))
+  {
+    gamma <- gamma_range[jj]
+    
+    # distribution
[…]
